### 2013-01-18 EconGrowth.Rnw
Created a data folder and moved USData.txt into that folder.

\documentclass[10pt]{article}

\usepackage[margin=.5in]{geometry}

\begin{document}
<<setup,include=FALSE>>=
require(knitr)
require(lattice)
require(ggplot2)
require(car)
require(mosaic)
require(xtable)
trellis.par.set(theme=theme.mosaic())
options(width=75)
options(show.signif.stars=FALSE)
opts_chunk$set(
  tidy=FALSE,
  fig.width=4.5,
  fig.height=3.8,
  out.width=".45\\textwidth",
  out.height=".38\\textwidth",
  comment=NA)
@

<<loadData>>=
fileName <- "data/USData.txt"

# Read the data file as a table with a header.  
## dataTable is a poor name.  Name it after contents, unless this is the 
## start of a script where this will be provided at the command line.
dataTable <- read.table(fileName, header = TRUE)

# Identifies the header names associated with dataTable
names(dataTable)
@

\section{Cobb-Douglas Without Energy}

<<cobb-douglass>>=
# Establish guess values for alpha and lambda.
lambdaGuess <- 0.0 # guessing lambda = 0 means there is no technological progress.
alphaGuess <- 0.3 # a typical value for alpha, the coefficient on capital stock

# Runs a non-linear least squares fit to the data. We've replaced beta with 1-alpha for simplicity.
modelCD <- nls(iGDP ~ exp(lambda*iYear) * iCapStk^alpha * iLabor^(1 - alpha), 
               start=(list(lambda=lambdaGuess,alpha=alphaGuess)),
               data=dataTable)

# Checks validity of the model. AIC stands for Akaike's Information Criterion.
aicCD  <- AIC(modelCD, k=2); aicCD

summaryCD <- summary(modelCD) # Gives the nls summary table.
print(summaryCD)
ciCD <- confint(modelCD, level = 0.95); ciCD # Displays confidence intervals for the CD model.

# Calculate beta and its confidence interval and report it.
alpha <- as.numeric(coef(modelCD)["alpha"])
beta <- 1.0 - alpha
beta.est <- deltaMethod(modelCD, "1 - alpha"); beta.est # Estimates beta and its standard error (SE).
# Now calculate a confidence interval on beta
dofCD <- summaryCD$df[2]; dofCD # Gives the degrees of freedom for the model.
tvalCD <- qt(0.975, df = dofCD); tvalCD
betaCICD <- with(beta.est, Estimate + c(-1.0, 1.0) * tvalCD * SE); betaCICD # Gives the confidence interval on beta.

coef(modelCD)

# Combine all estimates and their confidence intervals into data frames with intelligent row names
estCD <- data.frame(lambda = coef(modelCD)["lambda"], alpha = coef(modelCD)["alpha"], beta = beta, gamma = NA)
row.names(estCD) <- "Cobb-Douglas"
#row.names(estCD) <- "Cobb-Douglas: $y = e^{\\lambda t}k^{\\alpha}l^{\\beta}$"
 # The [1] subscripts pick off the lower confidence interval
lowerCD <- data.frame(lambda = ciCD["lambda","2.5%"], alpha = ciCD["alpha", "2.5%"], beta = betaCICD[1], gamma = NA) 
row.names(lowerCD) <- "- 95% CI"
 # The [2] subscripts pick off the lower confidence interval
upperCD <- data.frame(lambda = ciCD["lambda","97.5%"], alpha = ciCD["alpha", "97.5%"], beta = betaCICD[2], gamma = NA)
row.names(upperCD) <- "+ 95% CI"

# Now create the data for a table.
dataCD <- rbind(lowerCD, estCD, upperCD); dataCD
colnames(dataCD)  <- c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$")
tableCD  <- xtable(dataCD)
@

<<CD Results, results='asis'>>=
print(xtable(dataCD), floating=FALSE)
# According to http://cran.r-project.org/web/packages/xtable/vignettes/xtableGallery.pdf, Section 3.1, I should 
# be able to use the "sanitize.text.function" parameter to allow markup in column headers. But this next
# line is not working at the present time. --MKH, 18 Jan 2012.
# print(tableCD, sanitize.text.function = function(x){x})
@

\section{Cobb-Douglas With Q}

<<cdq>>=
# Establish guess values for alpha, beta, and lambda.
# lambdaGuess <- 0.0 # guessing lambda = 0 means there is no technological progress.
# alphaGuess <- 0.2 # a typical value for alpha
# betaGuess <- 0.6 # a typical value for beta

# Runs a non-linear least squares fit to the data.
# modelCDQ <- nls(iGDP ~ exp(lambda*iYear) * iCapStk^alpha * iLabor^beta * iQ^(1.0 - alpha - beta), 
#                 start=(list(lambda=lambdaGuess,alpha=alphaGuess,beta=betaGuess)),
#                 data=dataTable)

# Reparameterize to ensure that we meet the constraint that alpha + beta + gamma = 1.0.
# 0 < a < 1
# 0 < b < 1
# alpha = min(a, b)
# beta = b - a
# gamma = 1 - max(a, b)

lambdaGuess <- 0.0 # guessing lambda = 0 means there is no technological progress.
alphaGuess <- 0.2 # a typical value for alpha
betaGuess <- 0.8 # a typical value for beta
modelCDq <- nls(iGDP ~ exp(lambda*iYear) * 
                            iCapStk^min(a,b) * iLabor^abs(b-a) * 
                            iQ^(1.0 - max(a,b)), 
  algorithm = "port",
  start = list(lambda=lambdaGuess, a=alphaGuess, b=alphaGuess+betaGuess),
	lower = list(lambda=-Inf, a=0, b=0),
	upper = list(lambda=Inf, a=1, b=1),
  data = dataTable)

aicCDq <- AIC(modelCDq, k=2); aicCDq # Checks validity of the model. AIC stands for Akaike's Information Criterion

summaryCDq <- summary(modelCDq); summaryCDq # Gives the nls summary table

# Provides confidence intervals on lambda, a, and b. But, we need CIs on alpha and beta.
ciCDq <- confint(modelCDq, level = 0.95); ciCDq

a <- as.numeric(coef(modelCDq)["a"])
b <- as.numeric(coef(modelCDq)["b"])
lambda <- as.numeric(coef(modelCDq)["lambda"])
alpha <- a
beta <- b - a
gamma <- 1.0 - alpha - beta

# Report results with SE
beta.est <- deltaMethod(modelCDq, "b-a"); beta.est # Reports results for beta, because beta = b - a.
gamma.est <- deltaMethod(modelCDq, "1-b"); gamma.est # Reports results for gamma, because gamma = 1 - b.

# Now calculate confidence intervals.
dofCDq <- summaryCDq$df[2]; dofCDq # Gives the degrees of freedom for the model.
tvalCDq <- qt(0.975, df = dofCDq); tvalCDq
betaCICDq <- with(beta.est, Estimate + c(-1.0, 1.0) * tvalCDq * SE); betaCICDq # Gives the confidence interval on beta.
gammaCICDq <- with(gamma.est, Estimate + c(-1.0, 1.0) * tvalCDq * SE); gammaCICDq # Gives the confidence interval on alpha.

# Combine all estimates and their confidence intervals into data frames with intelligent row names
estCDq <- data.frame(lambda = lambda, alpha = alpha, beta = beta, gamma = gamma); estCDq
#row.names(estCDq) <- "Cobb-Douglas with q: $y = e^{\\lambda t}k^{\\alpha}l^{\\beta}q^{\\gamma}$"
row.names(estCDq) <- "CobbDouglas with q"
# The [1] subscripts pick off the lower confidence interval
lowerCDq <- data.frame(lambda = ciCDq["lambda","2.5%"], alpha = ciCDq["a", "2.5%"], beta = betaCICDq[1], gamma = gammaCICDq[1])
row.names(lowerCDq) <- "- 95% CI"
# The [2] subscripts pick off the lower confidence interval
upperCDq <- data.frame(lambda = ciCDq["lambda","97.5%"], alpha = ciCDq["a", "97.5%"], beta = betaCICDq[2], gamma = gammaCICDq[2])
row.names(upperCDq) <- "+ 95% CI"

# Now create the data for a table.
dataCDq <- rbind(lowerCDq, estCDq, upperCDq); dataCDq
colnames(dataCDq)  <- c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$")
tableCDq <- xtable(dataCDq)

dataAll <- rbind(dataCD, dataCDq); dataAll
@

<<CDq Results, results='asis'>>=
print(xtable(dataCDq), floating=FALSE)
# According to http://cran.r-project.org/web/packages/xtable/vignettes/xtableGallery.pdf, Section 3.1, I should 
# be able to use the "sanitize.text.function" parameter to allow markup in column headers. But this next
# line is not working at the present time. --MKH, 18 Jan 2012.
# print(tableCDq, sanitize.text.function = function(x){x})

print(xtable(dataAll, floating=FALSE))
@

<<Combined Table, results='asis'>>=

@

\section{Cobb-Douglas With X}

<<cdx>>=
# Establish guess values for alpha, beta, and lambda.
lambdaGuess <- 0.0 # guessing lambda = 0 means there is no technological progress.
alphaGuess <- 0.2 # a typical value for alpha
betaGuess <- 0.6 # a typical value for beta

# Runs a non-linear least squares fit to the data.
modelCDX <- nls(iGDP ~ exp(lambda*iYear) * iCapStk^alpha * iLabor^beta * iX^(1.0 - alpha - beta), 
                start=(list(lambda=lambdaGuess,alpha=alphaGuess,beta=betaGuess)),
                data=dataTable)

# Gives the nls summary table
summary(modelCDX)
confint(modelCDX, level = 0.95)

# Calculate gamma and report it.
alpha <- coef(modelCDX)["alpha"] 
beta <- coef(modelCDX)["beta"] 
gamma <- as.numeric(1.0 - alpha - beta)
c(coef(modelCDX),gamma=gamma)

# Checks validity of the model. AIC stands for Akaike's Information Criterion
AIC(modelCDX, k=2)
@

\section{Cobb-Douglas With U}

An issue arrises in this example because contraining $\alpha$ and $\beta$ is not sufficient to 
guarantee that $\gamma$ is properly constrained.

<<cdu>>=
# Establish guess values for alpha, beta, and lambda.
lambdaGuess <- 0.0 # guessing lambda = 0 means there is no technological progress.
alphaGuess <- 0.2 # a typical value for alpha
betaGuess <- 0.6 # a typical value for beta
gammaGuess <- 0.01 # a nice low value

# Runs a non-linear least squares fit to the data with constraints
modelCDU <- nls(iGDP ~ exp(lambda*iYear) * iCapStk^alpha * iLabor^beta * iU^(1.0 - alpha - beta), 
  algorithm="port",
	start = list(lambda=lambdaGuess, alpha=alphaGuess, beta=betaGuess),
	lower = list(lambda=-Inf, alpha=0, beta=0),
	upper = list(lambda=Inf, alpha=1, beta=1),
  data=dataTable)

# Gives the nls summary table
summary(modelCDU)
confint(modelCDU, level = 0.95)
@

<<>>=
# Checks validity of the model. AIC stands for Akaike's Information Criterion
AIC(modelCDU, k=2)
@

The problem here is that $\hat \gamma < 0$.
<<>>=
# Calculate gamma and report it.
alpha <- coef(modelCDU)["alpha"] 
beta <- coef(modelCDU)["beta"] 
gamma <- as.numeric(1.0 - alpha - beta)
c(coef(modelCDU), gamma=gamma)
@

Our $\hat\gamma$ is not much below $0$.  Let's compute the standard error.
<<>>=
require(car)  # the methods in alr3 have been deprecated.  Use car instead.
gamma.est <- deltaMethod(modelCDU, "1-alpha-beta"); gamma.est
# crude CI (using 2 as a rough estimate for critical value)
with(gamma.est, Estimate + c(-1,1) * 2 * SE)
@
So no real cause for concern: our data don't convince us that the real $\gamma$ is different from $0$.

\subsection{Forcing $\gamma\ge0$}

We can force $\alpha$, $\beta$, and $\gamma$ to be in $[0,1]$ by a reparameterization:

\[ a \in[0,1], b \in [0,1], \alpha=\min(a,b), \beta=|b-a|, \gamma = 1-\max(a,b) \]

<<>>=
modelCDUforced <- nls(iGDP ~ exp(lambda*iYear) * 
                            iCapStk^min(a,b) * iLabor^abs(b-a) * 
                            iU^(1.0 - max(a,b)), 
  algorithm="port",
	start = list(lambda=lambdaGuess, a=alphaGuess, b=alphaGuess + betaGuess),
	lower = list(lambda=-Inf, a=0, b=0),
	upper = list(lambda=Inf, a=1, b=1),
  data=dataTable)

coef(summary(modelCDUforced))
with( as.data.frame(t(coef(modelCDUforced))), c(alpha=min(a,b), beta=abs(b-a), gamma=1-max(a,b)))
@
But the naive delta method to calculate significance information fails because R doesn't know how to calculate the derivatives for the minimum and maximum functions.  So we need to be clever, using the fact that we know now that $a < b$:
<<>>=
# alpha = a
deltaMethod( modelCDUforced, "a")
# beta = b - a
deltaMethod( modelCDUforced, "b-a")
# gamma = 1-b
deltaMethod( modelCDUforced, "1-b")
@

So this seems to give us what we want for this case:  We have parameter estimates and standard errors subject to all of our constraints.

It may be that we can avoid using min and max and just
use $a$, $b-a$ and $1-b$.  If that works, then this generalizes fairly easily to any number of parameters that must be bounded by 0 and 1 and sum to 1.  (Else we have to ``sort'' the dummy parameters first, which is OK but makes the coding a bit uglier.)

\section{CES With Q}

<<>>=
# Establish guess values for alpha, beta, and lambda.
phiGuess <- -20
betaGuess <- 0.5 # a typical value for beta (exponent on labor)
zetaGuess <- 0.0004 # a small value
lambda_LGuess <- 0.007 #assuming no technical progress on the labor-capital portion of the function
lambda_EGuess <- 0.008 #assuming no technical progress on the energy portion of the function

# Runs a non-linear least squares fit to the data with constraints
modelCESQ <- nls(iGDP ~ ((1-zeta) * (exp(lambda_L*iYear) * iLabor^beta * iCapStk^(1-beta))^phi 
                         + zeta*(exp(lambda_E*iYear) * iQ)^phi)^(1/phi), 
  algorithm = "port",
	control = nls.control(maxiter = 500, tol = 1e-06, minFactor = 1/1024, 
                        printEval = FALSE, warnOnly = FALSE),
	start = list(phi=phiGuess, beta=betaGuess, zeta=zetaGuess, lambda_L=lambda_LGuess, 
               lambda_E=lambda_EGuess),
	lower = list(phi=-Inf, beta=0, zeta=0, lambda_L=-Inf, lambda_E=-Inf),
	upper = list(phi=0, beta=1, zeta=1, lambda_L=Inf, lambda_E=Inf),
  data=dataTable)

# Gives the nls summary table
summary(modelCESQ)
xyplot( resid(modelCESQ) ~ fitted(modelCESQ) )
histogram( ~resid(modelCESQ) )
qqmath( ~resid(modelCESQ) )
@

\end{document}

### 2013-01-18 EconGrowth.Rnw
First commit after adding the Energy Economics template.

@@
-\documentclass[10pt]{article}
+% This article has been prepared for publication in Energy Economics in RStudio with knitr.
+% According to http://www.elsevier.com/author-schemas/the-elsarticle-latex-document-class, we should be using the
+% elsarticle.cls file.
+% According to http://cdn.elsevier.com/assets/pdf_file/0006/109392/journal_refstyles.pdf, we should be using
+% elsarticle-template-2-harv.tex as the template for the text.
+% Furthermore, we should be using model2-names.bst for the bibliographic references.
+% The approach here is to load the frontmatter and backmatter from elsarticle-template-2-harv.tex
+% both ahead of and behind the text for our paper.
+% -- Matthew Kuperus Heun, 2013-01-18
 
-\usepackage[margin=.5in]{geometry}
+%% This is file `elsarticle-template-2-harv.tex',
+%%
+%% Copyright 2009 Elsevier Ltd
+%%
+%% This file is part of the 'Elsarticle Bundle'.
+%% ---------------------------------------------
+%%
+%% It may be distributed under the conditions of the LaTeX Project Public
+%% License, either version 1.2 of this license or (at your option) any
+%% later version.  The latest version of this license is in
+%%    http://www.latex-project.org/lppl.txt
+%% and version 1.2 or later is part of all distributions of LaTeX
+%% version 1999/12/01 or later.
+%%
+%% The list of all files belonging to the 'Elsarticle Bundle' is
+%% given in the file `manifest.txt'.
+%%
+%% Template article for Elsevier's document class `elsarticle'
+%% with harvard style bibliographic references
+%%
+%% $Id: elsarticle-template-2-harv.tex 155 2009-10-08 05:35:05Z rishi $
+%% $URL: http://lenova.river-valley.com/svn/elsbst/trunk/elsarticle-template-2-harv.tex $
+%%
+\documentclass[preprint,authoryear,12pt]{elsarticle}
+
+%% Use the option review to obtain double line spacing
+%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}
+
+%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
+%% for a journal layout:
+%% \documentclass[final,authoryear,1p,times]{elsarticle}
+%% \documentclass[final,authoryear,1p,times,twocolumn]{elsarticle}
+%% \documentclass[final,authoryear,3p,times]{elsarticle}
+%% \documentclass[final,authoryear,3p,times,twocolumn]{elsarticle}
+%% \documentclass[final,authoryear,5p,times]{elsarticle}
+%% \documentclass[final,authoryear,5p,times,twocolumn]{elsarticle}
+
+%% if you use PostScript figures in your article
+%% use the graphics package for simple commands
+%% \usepackage{graphics}
+%% or use the graphicx package for more complicated commands
+%% \usepackage{graphicx}
+%% or use the epsfig package if you prefer to use the old commands
+%% \usepackage{epsfig}
+
+%% The amssymb package provides various useful mathematical symbols
+\usepackage{amssymb}
+%% The amsthm package provides extended theorem environments
+%% \usepackage{amsthm}
+
+%% The lineno packages adds line numbers. Start line numbering with
+%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
+%% for the whole article with \linenumbers after \end{frontmatter}.
+%% \usepackage{lineno}
+
+%% natbib.sty is loaded by default. However, natbib options can be
+%% provided with \biboptions{...} command. Following options are
+%% valid:
+
+%%   round  -  round parentheses are used (default)
+%%   square -  square brackets are used   [option]
+%%   curly  -  curly braces are used      {option}
+%%   angle  -  angle brackets are used    <option>
+%%   semicolon  -  multiple citations separated by semi-colon (default)
+%%   colon  - same as semicolon, an earlier confusion
+%%   comma  -  separated by comma
+%%   authoryear - selects author-year citations (default)
+%%   numbers-  selects numerical citations
+%%   super  -  numerical citations as superscripts
+%%   sort   -  sorts multiple citations according to order in ref. list
+%%   sort&compress   -  like sort, but also compresses numerical citations
+%%   compress - compresses without sorting
+%%   longnamesfirst  -  makes first citation full author list
+%%
+%% \biboptions{longnamesfirst,comma}
+
+% \biboptions{}
+
+\journal{Energy Economics}
 
 \begin{document}
+
+\begin{frontmatter}
+
+%% Title, authors and addresses
+
+%% use the tnoteref command within \title for footnotes;
+%% use the tnotetext command for the associated footnote;
+%% use the fnref command within \author or \address for footnotes;
+%% use the fntext command for the associated footnote;
+%% use the corref command within \author for corresponding author footnotes;
+%% use the cortext command for the associated footnote;
+%% use the ead command for the email address,
+%% and the form \ead[url] for the home page:
+%%
+%% \title{Title\tnoteref{label1}}
+%% \tnotetext[label1]{}
+%% \author{Name\corref{cor1}\fnref{label2}}
+%% \ead{email address}
+%% \ead[url]{home page}
+%% \fntext[label2]{}
+%% \cortext[cor1]{}
+%% \address{Address\fnref{label3}}
+%% \fntext[label3]{}
+
+\title{}
+
+%% use optional labels to link authors explicitly to addresses:
+%% \author[label1,label2]{<author name>}
+%% \address[label1]{<address>}
+%% \address[label2]{<address>}
+
+\author{}
+
+\address{}
+
+\begin{abstract}
+%% Text of abstract
+
+\end{abstract}
+
+\begin{keyword}
+%% keywords here, in the form: keyword \sep keyword
+
+%% MSC codes here, in the form: \MSC code \sep code
+%% or \MSC[2008] code \sep code (2000 is the default)
+
+\end{keyword}
+
+\end{frontmatter}
+
+% \linenumbers
+%% main text
+
 <<setup,include=FALSE>>=
@@
 
+%% The Appendices part is started with the command \appendix;
+%% appendix sections are then done as normal sections
+%% \appendix
+
+%% \section{}
+%% \label{}
+
+%% References
+%%
+%% Following citation commands can be used in the body text:
+%%
+%%  \citet{key}  ==>>  Jones et al. (1990)
+%%  \citep{key}  ==>>  (Jones et al., 1990)
+%%
+%% Multiple citations as normal:
+%% \citep{key1,key2}         ==>> (Jones et al., 1990; Smith, 1989)
+%%                            or  (Jones et al., 1990, 1991)
+%%                            or  (Jones et al., 1990a,b)
+%% \cite{key} is the equivalent of \citet{key} in author-year mode
+%%
+%% Full author lists may be forced with \citet* or \citep*, e.g.
+%%   \citep*{key}            ==>> (Jones, Baker, and Williams, 1990)
+%%
+%% Optional notes as:
+%%   \citep[chap. 2]{key}    ==>> (Jones et al., 1990, chap. 2)
+%%   \citep[e.g.,][]{key}    ==>> (e.g., Jones et al., 1990)
+%%   \citep[see][pg. 34]{key}==>> (see Jones et al., 1990, pg. 34)
+%%  (Note: in standard LaTeX, only one note is allowed, after the ref.
+%%   Here, one note is like the standard, two make pre- and post-notes.)
+%%
+%%   \citealt{key}          ==>> Jones et al. 1990
+%%   \citealt*{key}         ==>> Jones, Baker, and Williams 1990
+%%   \citealp{key}          ==>> Jones et al., 1990
+%%   \citealp*{key}         ==>> Jones, Baker, and Williams, 1990
+%%
+%% Additional citation possibilities
+%%   \citeauthor{key}       ==>> Jones et al.
+%%   \citeauthor*{key}      ==>> Jones, Baker, and Williams
+%%   \citeyear{key}         ==>> 1990
+%%   \citeyearpar{key}      ==>> (1990)
+%%   \citetext{priv. comm.} ==>> (priv. comm.)
+%%   \citenum{key}          ==>> 11 [non-superscripted]
+%% Note: full author lists depends on whether the bib style supports them;
+%%       if not, the abbreviated list is printed even when full requested.
+%%
+%% For names like della Robbia at the start of a sentence, use
+%%   \Citet{dRob98}         ==>> Della Robbia (1998)
+%%   \Citep{dRob98}         ==>> (Della Robbia, 1998)
+%%   \Citeauthor{dRob98}    ==>> Della Robbia
+
+%% References with bibTeX database:
+
+\bibliographystyle{model2-names}
+\bibliography{<your-bib-database>}
+
+%% Authors are advised to submit their bibtex database files. They are
+%% requested to list a bibtex style file in the manuscript if they do
+%% not want to use model2-names.bst.
+
+%% References without bibTeX database:
+
+% \begin{thebibliography}{00}
+
+%% \bibitem must have one of the following forms:
+%%   \bibitem[Jones et al.(1990)]{key}...
+%%   \bibitem[Jones et al.(1990)Jones, Baker, and Williams]{key}...
+%%   \bibitem[Jones et al., 1990]{key}...
+%%   \bibitem[\protect\citeauthoryear{Jones, Baker, and Williams}{Jones
+%%       et al.}{1990}]{key}...
+%%   \bibitem[\protect\citeauthoryear{Jones et al.}{1990}]{key}...
+%%   \bibitem[\protect\astroncite{Jones et al.}{1990}]{key}...
+%%   \bibitem[\protect\citename{Jones et al., }1990]{key}...
+%%   \harvarditem[Jones et al.]{Jones, Baker, and Williams}{1990}{key}...
+%%
+
+% \bibitem[ ()]{}
+
+% \end{thebibliography}
+
 \end{document}
+
+%%
+%% End of file `elsarticle-template-2-harv.tex'.

### 2013-01-18 EconGrowth.Rnw
Added author and contact information to the frontmatter of the article.
Now using 4 digits after the decimal in tables.

@@
 
-\title{}
+\title{Empirical Analysis of the Role of Energy in Economic Growth}
 
@@
 
-\author{}
+\author[Calvin]{Caleb Reese}
+\author[Calvin]{Lucas Timmer}
+\author[Calvin]{Matthew Kuperus Heun \corref{cor1}}
+\ead{mkh2@calvin.edu, tel: +1 (616) 526-6663, fax: +1 (616) 526-6501}
 
-\address{}
+\cortext[cor1]{Corresponding author}
+\address[Calvin]{Engineering Department, Calvin College, Grand Rapids, MI 49546, USA}
 
@@
 %% Text of abstract
-
+*********** Add abstract ***********
 \end{abstract}
@@
 %% keywords here, in the form: keyword \sep keyword
-
+economic growth \sep energy \sep cobb-douglas \sep CES \sep LINEX
 %% MSC codes here, in the form: \MSC code \sep code
 %% or \MSC[2008] code \sep code (2000 is the default)
-
 \end{keyword}
@@
 # Combine all estimates and their confidence intervals into data frames with intelligent row names
-estCD <- data.frame(lambda = coef(modelCD)["lambda"], alpha = coef(modelCD)["alpha"], beta = beta, gamma = NA)
+estCD <- data.frame(lambda = coef(modelCD)["lambda"], alpha = coef(modelCD)["alpha"], beta = beta, gamma = 0)
 row.names(estCD) <- "Cobb-Douglas"
@@
 colnames(dataCD)  <- c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$")
-tableCD  <- xtable(dataCD)
+tableCD <- xtable(dataCD, caption="U.S. Cobb-Douglas, 1980-2011", digit = c(4))
 @
@@
 <<CD Results, results='asis'>>=
-print(xtable(dataCD), floating=FALSE)
+print(tableCD, caption.placement="top")
 # According to http://cran.r-project.org/web/packages/xtable/vignettes/xtableGallery.pdf, Section 3.1, I should 
@@
 colnames(dataCDq)  <- c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$")
-tableCDq <- xtable(dataCDq)
+tableCDq <- xtable(dataCDq, caption="U.S. 1980-2011.", digit = c(4))
 
-dataAll <- rbind(dataCD, dataCDq); dataAll
+dataAll <- rbind(estCD, estCDq); dataAll
+tableAll <- xtable(dataAll, caption="U.S. 1980-2011, All Models.", digit = c(4))
 @
@@
 <<CDq Results, results='asis'>>=
-print(xtable(dataCDq), floating=FALSE)
+print(tableCDq, caption.placement="top")
 # According to http://cran.r-project.org/web/packages/xtable/vignettes/xtableGallery.pdf, Section 3.1, I should 
@@
 
-print(xtable(dataAll, floating=FALSE))
+print(tableAll, caption.placement="top")
 @

### 2013-01-18 EconGrowth.Rnw
Adjusted number of decimal places in tables.

@@
 
+<<testing>>=
+mat <- round(matrix(c(0.9, 0.89, 200, 0.045, 2.0), c(1, 5)), 4)
+rownames(mat) <- "$y_{t-1}$"
+# colnames(mat) <- c("$R^2$", "$\\bar{R}^2$", "F-stat", "S.E.E", "DW")
+colnames(mat) <- c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$", "DW")
+mat <- xtable(mat)
+@
+
+<<Test Print Sanitized Table, results='asis'>>=
+print(mat, sanitize.text.function = function(x){x})
+@
+
 <<loadData>>=
@@
 colnames(dataCD) <- c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$")
-tableCD <- xtable(dataCD, caption="U.S. Cobb-Douglas, 1980-2011", digit = c(4))
+tableCD <- xtable(dataCD, caption="U.S. Cobb-Douglas, 1980-2011", digit = c(4, 4, 2, 2, 1))
 @
@@
 # line is not working at the present time. --MKH, 18 Jan 2012.
-# print(tableCD, sanitize.text.function = function(x){x})
+# print(tableCD, caption.placement="top", sanitize.text.function = function(x){x})
 @
@@
 colnames(dataCDq)  <- c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$")
-tableCDq <- xtable(dataCDq, caption="U.S. 1980-2011.", digit = c(4))
+tableCDq <- xtable(dataCDq, caption="U.S. 1980-2011.", digit = c(4, 4, 2, 2, 3))
 
 dataAll <- rbind(estCD, estCDq); dataAll
-tableAll <- xtable(dataAll, caption="U.S. 1980-2011, All Models.", digit = c(4))
+tableAll <- xtable(dataAll, caption="U.S. 1980-2011, All Models.", digit = c(4, 4, 2, 2, 3))
 @

### 2013-01-19 EconGrowth.Rnw
Now includes a function to do Cobb-Douglas with energy.

@@
 
-<<testing>>=
-mat <- round(matrix(c(0.9, 0.89, 200, 0.045, 2.0), c(1, 5)), 4)
-rownames(mat) <- "$y_{t-1}$"
-# colnames(mat) <- c("$R^2$", "$\\bar{R}^2$", "F-stat", "S.E.E", "DW")
-colnames(mat) <- c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$", "DW")
-mat <- xtable(mat)
-@
-
-<<Test Print Sanitized Table, results='asis'>>=
-print(mat, sanitize.text.function = function(x){x})
-@
-
 <<loadData>>=
@@
 
-<<cobb-douglass>>=
+<<cobb-douglas>>=
 # Establish guess values for alpha and lambda.
@@
 
-\section{Cobb-Douglas With Q}
+\section{Cobb-Douglas With Energy}
+
+<<cobbDouglasEnergy function>>=
+###############################
+# This function fits the Cobb Douglas production function including energy to historical data
+# The functional form is
+#
+# iGDP = exp(lambda * itime) * iCapStk^alpha * iLabor^beta * iEnergy^gamma
+# 
+# iYear: time indexed to 0.0 at the first year [years since beginning of data set]
+# iGDP = time series GDP data indexed to 1.0 at the first year [-]
+# iCapStk = time series capital stock data indexed to 1.0 at the first year [-]
+# iLabor = time series labor data indexed to 1.0 at the first year [-]
+# iEnergy = time series energy data indexed to 1.0 at the first year [-]. 
+#      This may be any of heat (iQ), exergy (iX), or useful work (iU).
+# 
+# returns a data object containing three rows and 5 columns.
+#   col 1: lambda
+#   col 2: alpha
+#   col 3: beta
+#   col 4: gamma
+#   row 1: -95% CI for each parameter
+#   row 2: estimate for each parameter
+#   row 3: +95% CI for each parameter
+#
+# dataTable is the table to be used for this curve fit
+# iEnergy is the name of the column to be used for energy.
+#   This may be any of heat (iQ), exergy (iX), or useful work (iU).
+##
+cobbDouglasEnergy <- function(dataTable, iEnergy){
+  # Reparameterize to ensure that we meet the constraints:
+  # * alpha + beta + gamma = 1.0.
+  # * alpha, beta, and gamma are all between 0.0 and 1.0.
+  # To do this, we reparameterize as
+  # * 0 < a < 1
+  # * 0 < b < 1
+  # * alpha = min(a, b)
+  # * beta = b - a
+  # * gamma = 1 - max(a, b)
+  lambdaGuess <- 0.0 # guessing lambda = 0 means there is no technological progress.
+  alphaGuess <- 0.3 # a typical value for alpha
+  betaGuess <- 0.7 # a typical value for beta
+  modelCDe <- nls(iGDP ~ exp(lambda*iYear) * 
+                    iCapStk^min(a,b) * iLabor^abs(b-a) * 
+                    iQ^(1.0 - max(a,b)), 
+                  algorithm = "port",
+                  start = list(lambda=lambdaGuess, a=alphaGuess, b=alphaGuess+betaGuess),
+                  lower = list(lambda=-Inf, a=0, b=0),
+                  upper = list(lambda=Inf, a=1, b=1),
+                  data = dataTable)
+  aicCDe <- AIC(modelCDe, k=2); aicCDe # Checks validity of the model. AIC stands for Akaike's Information Criterion
+
+  summaryCDe <- summary(modelCDe); summaryCDe # Gives the nls summary table
+
+  # Provides confidence intervals on lambda, a, and b. But, we need CIs on alpha and beta.
+  ciCDe <- confint(modelCDe, level = 0.95); ciCDe
+
+  a <- as.numeric(coef(modelCDe)["a"])
+  b <- as.numeric(coef(modelCDe)["b"])
+  lambda <- as.numeric(coef(modelCDe)["lambda"])
+  alpha <- a
+  beta <- b - a
+  gamma <- 1.0 - alpha - beta
+
+  # Report results with SE
+  beta.est <- deltaMethod(modelCDe, "b-a"); beta.est # Reports results for beta, because beta = b - a.
+  gamma.est <- deltaMethod(modelCDe, "1-b"); gamma.est # Reports results for gamma, because gamma = 1 - b.
+
+  # Now calculate confidence intervals.
+  dofCDe <- summaryCDe$df[2]; dofCDe # Gives the degrees of freedom for the model.
+  tvalCDe <- qt(0.975, df = dofCDe); tvalCDe
+  betaCICDe <- with(beta.est, Estimate + c(-1.0, 1.0) * tvalCDe * SE); betaCICDe # Gives the confidence interval on beta.
+  gammaCICDe <- with(gamma.est, Estimate + c(-1.0, 1.0) * tvalCDe * SE); gammaCICDe # Gives the confidence interval on alpha.
+
+  # Combine all estimates and their confidence intervals into data frames with intelligent row names
+  estCDe <- data.frame(lambda = lambda, alpha = alpha, beta = beta, gamma = gamma); estCDe
+  #row.names(estCDe) <- "Cobb-Douglas with e: $y = e^{\\lambda t}k^{\\alpha}l^{\\beta}e^{\\gamma}$"
+  row.names(estCDe) <- "CobbDouglas with e"
+  # The [1] subscripts pick off the lower confidence interval
+  lowerCDe <- data.frame(lambda = ciCDe["lambda","2.5%"], alpha = ciCDe["a", "2.5%"], beta = betaCICDe[1], gamma = gammaCICDe[1])
+  row.names(lowerCDe) <- "- 95% CI"
+  # The [2] subscripts pick off the lower confidence interval
+  upperCDe <- data.frame(lambda = ciCDe["lambda","97.5%"], alpha = ciCDe["a", "97.5%"], beta = betaCICDe[2], gamma = gammaCICDe[2])
+  row.names(upperCDe) <- "+ 95% CI"
+
+  # Now create the data for a table.
+  dataCDe <- rbind(lowerCDe, estCDe, upperCDe); dataCDe
+
+  return(dataCDe)
+}
+@
+
+\subsection{Cobb-Douglas with Q}
 
 <<cdq>>=
+
+dataCDe <- cobbDouglasEnergy(dataTable, dataTable["iQ"])
+
+tableCDe <- xtable(dataCDe, caption="U.S. 1980-2011.", digit = c(4, 4, 2, 2, 3))
+
+print("********** Done with function call **************")
+
 # Establish guess values for alpha, beta, and lambda.
@@
 # betaGuess <- 0.6 # a typical value for beta
-
+# 
 # Runs a non-linear least squares fit to the data.
@@
 #                 data=dataTable)
-
+# 
 # Reparameterize to ensure that we meet the constraint that alpha + beta + gamma = 1.0.
@@
 <<CDq Results, results='asis'>>=
+
+print(tableCDe, caption.placement="top")
 print(tableCDq, caption.placement="top")

### 2013-01-19 EconGrowth.Rnw
Now using the Cobb-Douglas with energy function for Q and X. Not yet working for U.

--- 2013-01-18 EconGrowth.Rnw
@@
 # line is not working at the present time. --MKH, 18 Jan 2012.
-# print(tableCD, sanitize.text.function = function(x){x})
+# print(tableCD, caption.placement="top", sanitize.text.function = function(x){x})
 @
 
-\section{Cobb-Douglas With Q}
+\section{Cobb-Douglas With Energy}
 
-<<cdq>>=
-# Establish guess values for alpha, beta, and lambda.
-# lambdaGuess <- 0.0 # guessing lambda = 0 means there is no technological progress.
-# alphaGuess <- 0.2 # a typical value for alpha
-# betaGuess <- 0.6 # a typical value for beta
-
-# Runs a non-linear least squares fit to the data.
-# modelCDQ <- nls(iGDP ~ exp(lambda*iYear) * iCapStk^alpha * iLabor^beta * iQ^(1.0 - alpha - beta), 
-#                 start=(list(lambda=lambdaGuess,alpha=alphaGuess,beta=betaGuess)),
-#                 data=dataTable)
-
-# Reparameterize to ensure that we meet the constraint that alpha + beta + gamma = 1.0.
-# 0 < a < 1
-# 0 < b < 1
-# alpha = min(a, b)
-# beta = b - a
-# gamma = 1 - max(a, b)
-
+<<cobbDouglasEnergy function>>=
+###############################
+# This function fits the Cobb Douglas production function including energy to historical data
+# The functional form is
+#
+# iGDP = exp(lambda * itime) * iCapStk^alpha * iLabor^beta * iEnergy^gamma
+# 
+# iYear: time indexed to 0.0 at the first year [years since beginning of data set]
+# iGDP = time series GDP data indexed to 1.0 at the first year [-]
+# iCapStk = time series capital stock data indexed to 1.0 at the first year [-]
+# iLabor = time series labor data indexed to 1.0 at the first year [-]
+# iEnergy = time series energy data indexed to 1.0 at the first year [-]. 
+#      This may be any of heat (iQ), exergy (iX), or useful work (iU).
+# 
+# returns a data object containing three rows and 5 columns.
+#   col 1: lambda
+#   col 2: alpha
+#   col 3: beta
+#   col 4: gamma
+#   row 1: -95% CI for each parameter
+#   row 2: estimate for each parameter
+#   row 3: +95% CI for each parameter
+#
+# dataTable is the table to be used for this curve fit
+# iEnergy is the name of the column to be used for energy.
+#   This may be any of heat (iQ), exergy (iX), or useful work (iU).
+##
+cobbDouglasEnergy <- function(dataTable, iEnergy){
+  # Reparameterize to ensure that we meet the constraints:
+  # * alpha + beta + gamma = 1.0.
+  # * alpha, beta, and gamma are all between 0.0 and 1.0.
+  # To do this, we reparameterize as
+  # * 0 < a < 1
+  # * 0 < b < 1
+  # * alpha = min(a, b)
+  # * beta = b - a
+  # * gamma = 1 - max(a, b)
+  energyName = names(iEnergy) #grabs the name of the energy column
   lambdaGuess <- 0.0 # guessing lambda = 0 means there is no technological progress.
-alphaGuess <- 0.2 # a typical value for alpha
-betaGuess <- 0.8 # a typical value for beta
-modelCDq <- nls(iGDP ~ exp(lambda*iYear) * 
+  alphaGuess <- 0.3 # a typical value for alpha
+  betaGuess <- 0.7 # a typical value for beta
+  modelCDe <- nls(iGDP ~ exp(lambda*iYear) * 
                     iCapStk^min(a,b) * iLabor^abs(b-a) * 
-                            iQ^(1.0 - max(a,b)), 
+                    iEnergy^(1.0 - max(a,b)), 
                   algorithm = "port",
@@
                   data = dataTable)
+  aicCDe <- AIC(modelCDe, k=2) # Checks validity of the model. AIC stands for Akaike's Information Criterion
+  print(aicCDe)
 
-aicCDq <- AIC(modelCDq, k=2); aicCDq # Checks validity of the model. AIC stands for Akaike's Information Criterion
-
-summaryCDq <- summary(modelCDq); summaryCDq # Gives the nls summary table
+  summaryCDe <- summary(modelCDe) # Gives the nls summary table
+  print(summaryCDe)
 
   # Provides confidence intervals on lambda, a, and b. But, we need CIs on alpha and beta.
-ciCDq <- confint(modelCDq, level = 0.95); ciCDq
+  ciCDe <- confint(modelCDe, level = 0.95)
+  print(ciCDe)
 
-a <- as.numeric(coef(modelCDq)["a"])
-b <- as.numeric(coef(modelCDq)["b"])
-lambda <- as.numeric(coef(modelCDq)["lambda"])
+  a <- as.numeric(coef(modelCDe)["a"])
+  b <- as.numeric(coef(modelCDe)["b"])
+  lambda <- as.numeric(coef(modelCDe)["lambda"])
   alpha <- a
@@
   # Report results with SE
-beta.est <- deltaMethod(modelCDq, "b-a"); beta.est # Reports results for beta, because beta = b - a.
-gamma.est <- deltaMethod(modelCDq, "1-b"); gamma.est # Reports results for gamma, because gamma = 1 - b.
+  beta.est <- deltaMethod(modelCDe, "b-a") # Reports results for beta, because beta = b - a.
+  gamma.est <- deltaMethod(modelCDe, "1-b") # Reports results for gamma, because gamma = 1 - b.
 
   # Now calculate confidence intervals.
-dofCDq <- summaryCDq$df[2]; dofCDq # Gives the degrees of freedom for the model.
-tvalCDq <- qt(0.975, df = dofCDq); tvalCDq
-betaCICDq <- with(beta.est, Estimate + c(-1.0, 1.0) * tvalCDq * SE); betaCICDq # Gives the confidence interval on beta.
-gammaCICDq <- with(gamma.est, Estimate + c(-1.0, 1.0) * tvalCDq * SE); gammaCICDq # Gives the confidence interval on alpha.
+  dofCDe <- summaryCDe$df[2] # Gives the degrees of freedom for the model.
+  print(dofCDe)
+  tvalCDe <- qt(0.975, df = dofCDe)
+  print(tvalCDe)
+  betaCICDe <- with(beta.est, Estimate + c(-1.0, 1.0) * tvalCDe * SE) # Gives the confidence interval on beta.
+  print(betaCICDe)
+  gammaCICDe <- with(gamma.est, Estimate + c(-1.0, 1.0) * tvalCDe * SE) # Gives the confidence interval on alpha.
+  print(gammaCICDe)
 
   # Combine all estimates and their confidence intervals into data frames with intelligent row names
-estCDq <- data.frame(lambda = lambda, alpha = alpha, beta = beta, gamma = gamma); estCDq
-#row.names(estCDq) <- "Cobb-Douglas with q: $y = e^{\\lambda t}k^{\\alpha}l^{\\beta}q^{\\gamma}$"
-row.names(estCDq) <- "CobbDouglas with q"
+  estCDe <- data.frame(lambda = lambda, alpha = alpha, beta = beta, gamma = gamma)
+  print(estCDe);
+  #row.names(estCDe) <- "Cobb-Douglas with e: $y = e^{\\lambda t}k^{\\alpha}l^{\\beta}e^{\\gamma}$"
+  row.names(estCDe) <- paste("Cobb-Douglas with ", energyName, sep="")
   # The [1] subscripts pick off the lower confidence interval
-lowerCDq <- data.frame(lambda = ciCDq["lambda","2.5%"], alpha = ciCDq["a", "2.5%"], beta = betaCICDq[1], gamma = gammaCICDq[1])
-row.names(lowerCDq) <- "- 95% CI"
+  lowerCDe <- data.frame(lambda = ciCDe["lambda","2.5%"], alpha = ciCDe["a", "2.5%"], beta = betaCICDe[1], gamma = gammaCICDe[1])
+  row.names(lowerCDe) <- "- 95% CI"
   # The [2] subscripts pick off the lower confidence interval
-upperCDq <- data.frame(lambda = ciCDq["lambda","97.5%"], alpha = ciCDq["a", "97.5%"], beta = betaCICDq[2], gamma = gammaCICDq[2])
-row.names(upperCDq) <- "+ 95% CI"
+  upperCDe <- data.frame(lambda = ciCDe["lambda","97.5%"], alpha = ciCDe["a", "97.5%"], beta = betaCICDe[2], gamma = gammaCICDe[2])
+  row.names(upperCDe) <- "+ 95% CI"
 
   # Now create the data for a table.
-dataCDq <- rbind(lowerCDq, estCDq, upperCDq); dataCDq
-colnames(dataCDq)  <- c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$")
-tableCDq <- xtable(dataCDq, caption="U.S. 1980-2011.", digit = c(4))
+  dataCDe <- rbind(lowerCDe, estCDe, upperCDe)
+  print(dataCDe)
 
-dataAll <- rbind(estCD, estCDq); dataAll
-tableAll <- xtable(dataAll, caption="U.S. 1980-2011, All Models.", digit = c(4))
+  return(dataCDe)
+}
+@
+
+\subsection{Cobb-Douglas with Q}
+
+<<cdq>>=
+dataCDe <- cobbDouglasEnergy(dataTable, dataTable["iQ"])
+tableCDe <- xtable(dataCDe, caption="U.S. 1980-2011.", digit = c(4, 4, 2, 2, 3))
+#estCDe <- dataCDe[2]
+#dataAll <- rbind(estCD, estCDe); dataAll
+#tableAll <- xtable(dataAll, caption="U.S. 1980-2011, All Models.", digit = c(4, 4, 2, 2, 3))
 @
@@
 <<CDq Results, results='asis'>>=
-print(tableCDq, caption.placement="top")
+
+print(tableCDe, caption.placement="top")
 # According to http://cran.r-project.org/web/packages/xtable/vignettes/xtableGallery.pdf, Section 3.1, I should 
@@
 # line is not working at the present time. --MKH, 18 Jan 2012.
-# print(tableCDq, sanitize.text.function = function(x){x})
+# print(tableCDe, sanitize.text.function = function(x){x})
 
-print(tableAll, caption.placement="top")
+#print(tableAll, caption.placement="top")
 @
 
-<<Combined Table, results='asis'>>=
+\subsection{Cobb-Douglas With X}
 
+<<cdx>>=
+dataCDx <- cobbDouglasEnergy(dataTable, dataTable["iX"])
+tableCDx <- xtable(dataCDx, caption="U.S. 1980-2011.", digit = c(4, 4, 2, 2, 3))
 @
 
-\section{Cobb-Douglas With X}
-
-<<cdx>>=
-# Establish guess values for alpha, beta, and lambda.
-lambdaGuess <- 0.0 # guessing lambda = 0 means there is no technological progress.
-alphaGuess <- 0.2 # a typical value for alpha
-betaGuess <- 0.6 # a typical value for beta
-
-# Runs a non-linear least squares fit to the data.
-modelCDX <- nls(iGDP ~ exp(lambda*iYear) * iCapStk^alpha * iLabor^beta * iX^(1.0 - alpha - beta), 
-                start=(list(lambda=lambdaGuess,alpha=alphaGuess,beta=betaGuess)),
-                data=dataTable)
-
-# Gives the nls summary table
-summary(modelCDX)
-confint(modelCDX, level = 0.95)
-
-# Calculate gamma and report it.
-alpha <- coef(modelCDX)["alpha"] 
-beta <- coef(modelCDX)["beta"] 
-gamma <- as.numeric(1.0 - alpha - beta)
-c(coef(modelCDX),gamma=gamma)
-
-# Checks validity of the model. AIC stands for Akaike's Information Criterion
-AIC(modelCDX, k=2)
+<<CDx Results, results='asis'>>=
+print(tableCDx, caption.placement="top")
 @
 
-\section{Cobb-Douglas With U}
+\subsection{Cobb-Douglas With U}
+
+<<cdu>>=
+dataCDu <- cobbDouglasEnergy(dataTable, dataTable["iU"])
+tableCDu <- xtable(dataCDu, caption="U.S. 1980-2011.", digit = c(4, 4, 2, 2, 3))
+@
+
+<<CDu Results, results='asis'>>=
+print(tableCDu, caption.placement="top")
+@
 
@@
 
-<<cdu>>=
+<<cduold>>=
 # Establish guess values for alpha, beta, and lambda.

### 2013-01-19 EconGrowth.Rnw
Changed order of confidence intervals in tables.

@@
 # Now create the data for a table.
-dataCD <- rbind(lowerCD, estCD, upperCD); dataCD
+dataCD <- rbind(upperCD, estCD, lowerCD); dataCD
 colnames(dataCD) <- c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$")
@@
   # Now create the data for a table.
-  dataCDe <- rbind(lowerCDe, estCDe, upperCDe)
+  dataCDe <- rbind(upperCDe, estCDe, lowerCDe)
   print(dataCDe)

### 2013-01-21 EconGrowth.Rnw
Now sending column name string and text to be used in tables into the C-D with energy function.

@@
 
+We can force $\alpha$, $\beta$, and $\gamma$ to be in $[0,1]$ by a reparameterization:
+
+\[ a \in[0,1], b \in [0,1], \alpha=\min(a,b), \beta=|b-a|, \gamma = 1-\max(a,b) \]
+
 <<cobbDouglasEnergy function>>=
@@
 ##
-cobbDouglasEnergy <- function(dataTable, iEnergy){
+cobbDouglasEnergy <- function(dataTable, energyColumnName, energyString){
   # Reparameterize to ensure that we meet the constraints:
@@
   # * gamma = 1 - max(a, b)
-  energyName = names(iEnergy) #grabs the name of the energy column
+  iEnergy <- dataTable[energyColumnName] #grabs the energy column
   lambdaGuess <- 0.0 # guessing lambda = 0 means there is no technological progress.
@@
   #row.names(estCDe) <- "Cobb-Douglas with e: $y = e^{\\lambda t}k^{\\alpha}l^{\\beta}e^{\\gamma}$"
-  row.names(estCDe) <- paste("Cobb-Douglas with ", energyName, sep="")
+  row.names(estCDe) <- paste("C-D with ", energyString, sep="")
   # The [1] subscripts pick off the lower confidence interval
@@
 <<cdq>>=
-dataCDe <- cobbDouglasEnergy(dataTable, dataTable["iQ"])
-tableCDe <- xtable(dataCDe, caption="U.S. 1980-2011.", digit = c(4, 4, 2, 2, 3))
+dataCDq <- cobbDouglasEnergy(dataTable, "iQ", "q")
+# TODO Develop a better caption for the table based on the data automatically.
+tableCDq <- xtable(dataCDq, caption="U.S., 1980-2011.", digit = c(4, 4, 2, 2, 3))
 #estCDe <- dataCDe[2]
@@
 
-print(tableCDe, caption.placement="top")
+print(tableCDq, caption.placement="top")
 # According to http://cran.r-project.org/web/packages/xtable/vignettes/xtableGallery.pdf, Section 3.1, I should 
@@
 <<cdx>>=
-dataCDx <- cobbDouglasEnergy(dataTable, dataTable["iX"])
-tableCDx <- xtable(dataCDx, caption="U.S. 1980-2011.", digit = c(4, 4, 2, 2, 3))
+dataCDx <- cobbDouglasEnergy(dataTable, "iX", "x")
+tableCDx <- xtable(dataCDx, caption="U.S., 1980-2011.", digit = c(4, 4, 2, 2, 3))
 @
@@
 <<cdu>>=
-dataCDu <- cobbDouglasEnergy(dataTable, dataTable["iU"])
-tableCDu <- xtable(dataCDu, caption="U.S. 1980-2011.", digit = c(4, 4, 2, 2, 3))
+dataCDu <- cobbDouglasEnergy(dataTable, "iU", "U")
+tableCDu <- xtable(dataCDu, caption="U.S., 1980-2011.", digit = c(4, 4, 2, 2, 3))
 @
@@
 @
-
-An issue arrises in this example because contraining $\alpha$ and $\beta$ is not sufficient to 
-guarantee that $\gamma$ is properly constrained.
-
-<<cduold>>=
-# Establish guess values for alpha, beta, and lambda.
-lambdaGuess <- 0.0 # guessing lambda = 0 means there is no technological progress.
-alphaGuess <- 0.2 # a typical value for alpha
-betaGuess <- 0.6 # a typical value for beta
-gammaGuess <- 0.01 # a nice low value
-
-# Runs a non-linear least squares fit to the data with constraints
-modelCDU <- nls(iGDP ~ exp(lambda*iYear) * iCapStk^alpha * iLabor^beta * iU^(1.0 - alpha - beta), 
-                algorithm="port",
-                start = list(lambda=lambdaGuess, alpha=alphaGuess, beta=betaGuess),
-                lower = list(lambda=-Inf, alpha=0, beta=0),
-                upper = list(lambda=Inf, alpha=1, beta=1),
-                data=dataTable)
-
-# Gives the nls summary table
-summary(modelCDU)
-confint(modelCDU, level = 0.95)
-@
-
-<<>>=
-# Checks validity of the model. AIC stands for Akaike's Information Criterion
-AIC(modelCDU, k=2)
-@
-
-The problem here is that $\hat \gamma < 0$.
-<<>>=
-# Calculate gamma and report it.
-alpha <- coef(modelCDU)["alpha"] 
-beta <- coef(modelCDU)["beta"] 
-gamma <- as.numeric(1.0 - alpha - beta)
-c(coef(modelCDU), gamma=gamma)
-@
-
-Our $\hat\gamma$ is not much below $0$.  Let's compute the standard error.
-<<>>=
-require(car)  # the methods in alr3 have been deprecated.  Use car instead.
-gamma.est <- deltaMethod(modelCDU, "1-alpha-beta"); gamma.est
-# crude CI (using 2 as a rough estimate for critical value)
-with(gamma.est, Estimate + c(-1,1) * 2 * SE)
-@
-So no real cause for concern: our data don't convince us that the real $\gamma$ is different from $0$.
-
-\subsection{Forcing $\gamma\ge0$}
-
-We can force $\alpha$, $\beta$, and $\gamma$ to be in $[0,1]$ by a reparameterization:
-
-\[ a \in[0,1], b \in [0,1], \alpha=\min(a,b), \beta=|b-a|, \gamma = 1-\max(a,b) \]
-
-<<>>=
-modelCDUforced <- nls(iGDP ~ exp(lambda*iYear) * 
-                        iCapStk^min(a,b) * iLabor^abs(b-a) * 
-                        iU^(1.0 - max(a,b)), 
-                      algorithm="port",
-                      start = list(lambda=lambdaGuess, a=alphaGuess, b=alphaGuess + betaGuess),
-                      lower = list(lambda=-Inf, a=0, b=0),
-                      upper = list(lambda=Inf, a=1, b=1),
-                      data=dataTable)
-
-coef(summary(modelCDUforced))
-with( as.data.frame(t(coef(modelCDUforced))), c(alpha=min(a,b), beta=abs(b-a), gamma=1-max(a,b)))
-@
-But the naive delta method to calculate significance information fails because R doesn't know how to calculate the derivatives for the minimum and maximum functions.
-So we need to be clever, using the fact that we know now that $a < b$:
-<<>>=
-# alpha = a
-deltaMethod( modelCDUforced, "a")
-# beta = b - a
-deltaMethod( modelCDUforced, "b-a")
-# gamma = 1-b
-deltaMethod( modelCDUforced, "1-b")
-@
-
-So this seems to give us what we want for this case:  We have parameter estimates and standard errors subject to all of our constraints.
-
-It may be that we can avoid using min and max and just
-use $a$, $b-a$ and $1-b$.
-If that works, then this generalizes fairly easily to any number of parameters that must be bounded by 0 and 1 and sum to 1.
-(Else we have to ``sort'' the dummy parameters first, which is OK but makes the coding a bit uglier.)
 

### 2013-01-21 EconGrowth.Rnw
Trying to use apply for energy types and countries. Still not working.

@@
 
-<<loadData>>=
-fileName <- "data/USData.txt"
-
+<<Load Data>>=
+#################################
+# This function loads data given a country name.
+#
+# countryName = the name of the country for which data is to be loaded. The file names is assumed to be 
+#   named <countryName>Data.txt. The file is assumed to exist in a subfolder of this project called "data".
+#
+# returns a matrix with the data that has been loaded
+##
+loadData <- function(countryName){
   # Read the data file as a table with a header.  
-## dataTable is a poor name.  Name it after contents, unless this is the 
-## start of a script where this will be provided at the command line.
+  fileName <- paste("data/", countryName, "Data.txt", sep="")
   dataTable <- read.table(fileName, header = TRUE)
-
   # Identifies the header names associated with dataTable
   names(dataTable)
+  return(dataTable)
+}
 @
@@
 <<cobb-douglas>>=
+
+cobbDouglas <- function(countryName){
+
+  # Load the data that we need.
+  dataTable <- loadData(countryName)
+
   # Establish guess values for alpha and lambda.
@@
   colnames(dataCD) <- c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$")
-tableCD <- xtable(dataCD, caption="U.S. Cobb-Douglas, 1980-2011", digit = c(4, 4, 2, 2, 1))
+  tableCD <- xtable(dataCD, caption=paste(countryName, " Cobb-Douglas, 1980-2011", sep=""), digit = c(4, 4, 2, 2, 1))
+  return(tableCD)
+}
+
+tableCD <- cobbDouglas("US")
+
+countries <- c("US", "CN")
+tablesCD <- apply(countries, 1, cobbDouglas)
 @
@@
 #
-# dataTable is the table to be used for this curve fit
-# iEnergy is the name of the column to be used for energy.
-#   This may be any of heat (iQ), exergy (iX), or useful work (iU).
+# countryName is a string containint the 2-letter abbreviation for the country, e.g. "US" or "CN"
+# energyColumnName is the name of the column to be used for energy.
+#   This may be any of heat ("iQ"), exergy ("iX"), or useful work ("iU").
+# energyString is the string to be used in table captions reprsenting the type of energy. Typically, "q", "x", or "u"
 ##
-cobbDouglasEnergy <- function(dataTable, energyColumnName, energyString){
+cobbDouglasEnergy <- function(countryName, energyColumnName, energyString){
+
+  # Load the data that we need.
+  dataTable <- loadData(countryName)
+
   # Reparameterize to ensure that we meet the constraints:
@@
   # * gamma = 1 - max(a, b)
-  iEnergy <- dataTable[energyColumnName] #grabs the energy column
+  iEnergy <- dataTable[energyColumnName] #grabs the desired energy column
   lambdaGuess <- 0.0 # guessing lambda = 0 means there is no technological progress.
@@
 <<cdq>>=
-dataCDq <- cobbDouglasEnergy(dataTable, "iQ", "q")
+countryName <- "US"
+energyColumn <- "iQ"; energyString <- "q"
+dataCDq <- cobbDouglasEnergy(countryName, energyColumn, energyString)
 # TODO Develop a better caption for the table based on the data automatically.
-tableCDq <- xtable(dataCDq, caption="U.S., 1980-2011.", digit = c(4, 4, 2, 2, 3))
+tableCDq <- xtable(dataCDq, caption=paste(countryName, ", 1980-2011.", sep=""), digit = c(4, 4, 2, 2, 3))
 #estCDe <- dataCDe[2]
@@
 <<cdx>>=
-dataCDx <- cobbDouglasEnergy(dataTable, "iX", "x")
-tableCDx <- xtable(dataCDx, caption="U.S., 1980-2011.", digit = c(4, 4, 2, 2, 3))
+energyColumn <- "iX"; energyString <- "x"
+dataCDx <- cobbDouglasEnergy(countryName, energyColumn, energyString)
+tableCDx <- xtable(dataCDx, caption=paste(countryName, ", 1980-2011.", sep=""), digit = c(4, 4, 2, 2, 3))
 @
@@
 <<cdu>>=
-dataCDu <- cobbDouglasEnergy(dataTable, "iU", "U")
-tableCDu <- xtable(dataCDu, caption="U.S., 1980-2011.", digit = c(4, 4, 2, 2, 3))
+energyColumn <- "iU"; energySTring <- "u"
+dataCDu <- cobbDouglasEnergy(countryName, energyColumn, energyString)
+tableCDu <- xtable(dataCDu, caption=paste(countryName, ", 1980-2011.", sep=""), digit = c(4, 4, 2, 2, 3))
 @

### 2013-01-21 EconGrowth.Rnw
The cobbDouglas curve fits are now implemented as a function.

@@
 #
-# countryName = the name of the country for which data is to be loaded. The file names is assumed to be 
-#   named <countryName>Data.txt. The file is assumed to exist in a subfolder of this project called "data".
+# countryName = a string of the 2-digit code for the country for which data is to be loaded. 
+#   The file name from which data will be loaded is assumed to be of the form 
+#   "<countryName>Data.txt". The file is assumed to exist in a subfolder of this project called "data".
 #
@@
   # Identifies the header names associated with dataTable
-  names(dataTable)
+  print(names(dataTable))
   return(dataTable)
@@
   # Checks validity of the model. AIC stands for Akaike's Information Criterion.
-  aicCD  <- AIC(modelCD, k=2); aicCD
+  aicCD  <- AIC(modelCD, k=2)
+  #print(aicCD)
 
   summaryCD <- summary(modelCD) # Gives the nls summary table.
-  print(summaryCD)
+  #print(summaryCD)
   ciCD <- confint(modelCD, level = 0.95); ciCD # Displays confidence intervals for the CD model.
@@
 
-  coef(modelCD)
+  #print(coef(modelCD))
 
@@
   estCD <- data.frame(lambda = coef(modelCD)["lambda"], alpha = coef(modelCD)["alpha"], beta = beta, gamma = 0)
+  #print(estCD)
   row.names(estCD) <- "Cobb-Douglas"
@@
   # Now create the data for a table.
-  dataCD <- rbind(upperCD, estCD, lowerCD); dataCD
+  dataCD <- rbind(upperCD, estCD, lowerCD)
+  #print(dataCD)
   colnames(dataCD) <- c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$")
   tableCD <- xtable(dataCD, caption=paste(countryName, " Cobb-Douglas, 1980-2011", sep=""), digit = c(4, 4, 2, 2, 1))
+  #print(tableCD)
   return(tableCD)
@@
 tableCD <- cobbDouglas("US")
+print(tableCD)
 
 countries <- c("US", "CN")
-tablesCD <- apply(countries, 1, cobbDouglas)
+tablesCD <- lapply(countries, cobbDouglas)
+#tablesCD <- sapply(countries, cobbDouglas, USE.NAMES = TRUE)
 @

### 2013-01-22 EconGrowth.Rnw
Now using the lapply function to "loop" over various statistical analyses. I have implemented lapply for CD and CDq at this point. I still need to do CDx.

@@
 
-<<setup,include=FALSE>>=
+<<setup, include=FALSE>>=
 require(knitr)
@@
   comment=NA)
+
+# Statistical significance levels. We'll work with 95% CIs
+ciLevel <- 0.95
+ciHalfLevel <- ciLevel + (1.0-ciLevel)/2.0
+# List of countries
+countries <- c(US = "US", ZA = "ZA")
+# List of energy types
+energyTypes <- c(Q = "Q", X = "X", U = "U")
 @
 
-<<Load Data>>=
+<<Load Data, include=FALSE>>=
 #################################
@@
   # Identifies the header names associated with dataTable
-  print(names(dataTable))
+  #print(names(dataTable))
   return(dataTable)
@@
 
-cobbDouglas <- function(countryName){
+#################################################
+# Calculates parameter estimates and confidence intervals
+# for the Cobb-Douglas production function given a country.
+#
+# countryName is a string containint the 2-letter abbreviation for the country, e.g. "US" or "CN"
+#
+# returns a vector of data for the Cobb-Douglas model. 
+# First item is the +95% CI on all parameters
+# Second item contains the parameter estimates
+# Third item is the -95% CI on all parameters
+# Each row has names: lambda, alpha, beta, gamma, corresponding to the parameters in the model.
+##
+cobbDouglasData <- function(countryName){
 
@@
   #print(summaryCD)
-  ciCD <- confint(modelCD, level = 0.95); ciCD # Displays confidence intervals for the CD model.
+  ciCD <- confint(modelCD, level = ciLevel); ciCD # Displays confidence intervals for the CD model.
 
@@
   dofCD <- summaryCD$df[2]; dofCD # Gives the degrees of freedom for the model.
-  tvalCD <- qt(0.975, df = dofCD); tvalCD
+  tvalCD <- qt(ciHalfLevel, df = dofCD); tvalCD
   betaCICD <- with(beta.est, Estimate + c(-1.0, 1.0) * tvalCD * SE); betaCICD # Gives the confidence interval on beta.
@@
   #print(estCD)
-  row.names(estCD) <- "Cobb-Douglas"
+  row.names(estCD) <- "CD"
   #row.names(estCD) <- "Cobb-Douglas: $y = e^{\\lambda t}k^{\\alpha}l^{\\beta}$"
@@
   #print(dataCD)
+  return(dataCD)
+}
+
+####################################
+# Creates a LaTeX printable table from the data. This function first calls cobbDouglasData.
+#
+# countryName is a string containint the 2-letter abbreviation for the country, e.g. "US" or "CN"
+#
+# returns a printable LaTeX table from xtable.
+##
+cobbDouglasTable <- function(countryName){
+  dataCD <- cobbDouglasData(countryName) 
   colnames(dataCD) <- c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$")
@@
 }
+@
 
-tableCD <- cobbDouglas("US")
-print(tableCD)
-
-countries <- c("US", "CN")
-tablesCD <- lapply(countries, cobbDouglas)
-#tablesCD <- sapply(countries, cobbDouglas, USE.NAMES = TRUE)
+<<CD Analysis>>=
+tablesCD <- lapply(countries, cobbDouglasTable)
 @
@@
 <<CD Results, results='asis'>>=
-print(tableCD, caption.placement="top")
+print(tablesCD[["US"]], caption.placement="top")
+print(tablesCD[["ZA"]], caption.placement="top")
 # According to http://cran.r-project.org/web/packages/xtable/vignettes/xtableGallery.pdf, Section 3.1, I should 
@@
 ##
-cobbDouglasEnergy <- function(countryName, energyColumnName, energyString){
+cobbDouglasEnergyData <- function(countryName, energyString){
+
+  energyColumnName  <- paste("i", energyString, sep="")
+  #print(energyColumnName)
 
@@
   aicCDe <- AIC(modelCDe, k=2) # Checks validity of the model. AIC stands for Akaike's Information Criterion
-  print(aicCDe)
+  #print(aicCDe)
 
   summaryCDe <- summary(modelCDe) # Gives the nls summary table
-  print(summaryCDe)
+  #print(summaryCDe)
 
   # Provides confidence intervals on lambda, a, and b. But, we need CIs on alpha and beta.
-  ciCDe <- confint(modelCDe, level = 0.95)
-  print(ciCDe)
+  ciCDe <- confint(modelCDe, level = ciLevel)
+  #print(ciCDe)
 
@@
   dofCDe <- summaryCDe$df[2] # Gives the degrees of freedom for the model.
-  print(dofCDe)
-  tvalCDe <- qt(0.975, df = dofCDe)
-  print(tvalCDe)
+  #print(dofCDe)
+  tvalCDe <- qt(ciHalfLevel, df = dofCDe)
+  #print(tvalCDe)
   betaCICDe <- with(beta.est, Estimate + c(-1.0, 1.0) * tvalCDe * SE) # Gives the confidence interval on beta.
-  print(betaCICDe)
+  #print(betaCICDe)
   gammaCICDe <- with(gamma.est, Estimate + c(-1.0, 1.0) * tvalCDe * SE) # Gives the confidence interval on alpha.
-  print(gammaCICDe)
+  #print(gammaCICDe)
 
@@
   estCDe <- data.frame(lambda = lambda, alpha = alpha, beta = beta, gamma = gamma)
-  print(estCDe);
+  #print(estCDe);
   #row.names(estCDe) <- "Cobb-Douglas with e: $y = e^{\\lambda t}k^{\\alpha}l^{\\beta}e^{\\gamma}$"
@@
   dataCDe <- rbind(upperCDe, estCDe, lowerCDe)
-  print(dataCDe)
-
+  #print(dataCDe)
   return(dataCDe)
 }
+
+cobbDouglasEnergyTable <- function(countryName, energyType){
+  dataCDe <- cobbDouglasEnergyData(countryName, energyType)
+  tableCDe <- xtable(dataCDe, caption=paste(countryName, ", 1980-2011.", sep=""), digit = c(4, 4, 2, 2, 3))
+  return(tableCDe)
+}
+
 @
@@
 
-<<cdq>>=
-countryName <- "US"
-energyColumn <- "iQ"; energyString <- "q"
-dataCDq <- cobbDouglasEnergy(countryName, energyColumn, energyString)
-# TODO Develop a better caption for the table based on the data automatically.
-tableCDq <- xtable(dataCDq, caption=paste(countryName, ", 1980-2011.", sep=""), digit = c(4, 4, 2, 2, 3))
-#estCDe <- dataCDe[2]
-#dataAll <- rbind(estCD, estCDe); dataAll
-#tableAll <- xtable(dataAll, caption="U.S. 1980-2011, All Models.", digit = c(4, 4, 2, 2, 3))
+<<CDe analysis>>=
+# Note that the anlaysis of ZA is taking a long time here. Need to figure out why.
+CDqTables <- lapply(countries, cobbDouglasEnergyTable, energyType="Q")
 @
@@
 <<CDq Results, results='asis'>>=
-
-print(tableCDq, caption.placement="top")
+print(CDqTables[["US"]], caption.placement="top")
+print(CDqTables[["ZA"]], caption.placement="top")
 # According to http://cran.r-project.org/web/packages/xtable/vignettes/xtableGallery.pdf, Section 3.1, I should 
@@
 
-<<>>=
-# Establish guess values for alpha, beta, and lambda.
+<<CES function>>=
+
+ces <- function(countryName, energyColumnName, energyString){
+
+  # Load the data that we need.
+  dataTable <- loadData(countryName)
+
+  # Establish guess values for phi beta, zeta, lambda_L and lambda_E.
   phiGuess <- -20
@@
   # Runs a non-linear least squares fit to the data with constraints
-modelCESQ <- nls(iGDP ~ ((1-zeta) * (exp(lambda_L*iYear) * iLabor^beta * iCapStk^(1-beta))^phi 
+  modelCES <- nls(iGDP ~ ((1-zeta) * (exp(lambda_L*iYear) * iCapStk^(1-beta) * iLabor^beta)^phi 
                            + zeta*(exp(lambda_E*iYear) * iQ)^phi)^(1/phi), 
@@
 
+  aicCES <- AIC(modelCES, k=2) # Checks validity of the model. AIC stands for Akaike's Information Criterion
+  print(aicCES)
+
   # Gives the nls summary table
-summary(modelCESQ)
-xyplot( resid(modelCESQ) ~ fitted(modelCESQ) )
-histogram( ~resid(modelCESQ) )
-qqmath( ~resid(modelCESQ) )
+  summaryCES <- summary(modelCES) # Gives the nls summary table
+  print(summaryCES)
+
+  # Provides confidence intervals on phi, beta, zeta, lambda_L, and lambda_E. But, we need the CI on alpha.
+  ciCES <- confint(modelCES, level = ciLevel)
+  print(ciCES)
+
+  # Get the estimate for alpha
+  beta <- as.numeric(coef(modelCES)["beta"])
+  alpha <- 1.0 - beta
+  alpha.est <- deltaMethod(modelCES, "1 - beta") # Estimates alpha and its standard error (SE).
+  print(alpha.est)
+
+  # Now calculate a confidence interval on alpha
+  dofCES <- summaryCES$df[2]
+  print(dofCES) # Gives the degrees of freedom for the model.
+  tvalCES <- qt(ciHalfLevel, df = dofCES); tvalCES
+  # Get confidence intervals for each parameter in the model
+  alphaCICES <- with(alpha.est, Estimate + c(-1.0, 1.0) * tvalCES * SE) # CI on alpha.
+  print(alphaCICES)
+
+  # Assemble the data into data frames for the table.
+  estCES <- data.frame(phi = coef(modelCES)["phi"], alpha = alpha, 
+                       beta = coef(modelCES)["beta"], zeta = coef(modelCES)["zeta"], 
+                       lambda_L = coef(modelCES)["lambda_L"], lambda_E = coef(modelCES)["lambda_E"])
+  row.names(estCES) <- paste("CES with ", energyString, sep="")
+  #print(estCES)  
+  # The [1] subscripts pick off the lower confidence interval
+  lowerCES <- data.frame(phi = ciCES["phi","2.5%"], alpha = alphaCICES[1], 
+                         beta = ciCES["beta", "2.5%"], zeta = ciCES["zeta", "2.5%"],
+                         lambda_L = ciCES["lambda_L", "2.5%"], lambda_E = ciCES["lambda_E", "2.5%"])
+  row.names(lowerCES) <- "- 95% CI"
+  # The [2] subscripts pick off the lower confidence interval
+  upperCES <- data.frame(phi = ciCES["phi","97.5%"], alpha = alphaCICES[2], 
+                         beta = ciCES["beta", "97.5%"], zeta = ciCES["zeta", "97.5%"],
+                         lambda_L = ciCES["lambda_L", "97.5%"], lambda_E = ciCES["lambda_E", "97.5%"])
+  row.names(upperCES) <- "+ 95% CI"
+
+  # Now create the data for a table.
+  dataCES <- rbind(upperCES, estCES, lowerCES)
+  print(dataCES)
+  return(dataCES)
+
+  #xyplot( resid(modelCESQ) ~ fitted(modelCESQ) )
+  #histogram( ~resid(modelCESQ) )
+  #qqmath( ~resid(modelCESQ) )
+}
+@
+
+<<CES with Q>>=
+countryName <- "US"
+energyColumn <- "iQ"; energyString <- "q"
+dataCESq <- ces(countryName, energyColumn, energyString)
+tableCESq <- xtable(dataCESq, caption=paste(countryName, ", 1980-2011.", sep=""), digit = c(4, 1, 2, 2, 6, 5, 5))
+@
+
+<<CESq Results, results='asis'>>=
+print(tableCESq, caption.placement="top")
 @

### 2013-01-23 EconGrowth.Rnw
Added a comment where Caleb should start adding text.
Cleaned up nomenclature for functions. Functionized CES curve fits. Tried CES curve fit for ZA, but it fails.

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Caleb, put your LaTeX code here.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 <<setup, include=FALSE>>=
@@
 # This function loads data given a country name.
-#
-# countryName = a string of the 2-digit code for the country for which data is to be loaded. 
 # The file name from which data will be loaded is assumed to be of the form 
 # "<countryName>Data.txt". The file is assumed to exist in a subfolder of this project called "data".
+#
+# countryName is a string containing the 2-letter abbreviation for the country, e.g. "US" or "CN"
 #
@@
 #
-# countryName is a string containint the 2-letter abbreviation for the country, e.g. "US" or "CN"
+# countryName is a string containing the 2-letter abbreviation for the country, e.g. "US" or "CN"
 #
@@
 ####################################
-# Creates a LaTeX printable table from the data. This function first calls cobbDouglasData.
+# Creates a LaTeX printable table from the Cobb Douglas data. This function first calls cobbDouglasData.
 #
@@
 # countryName is a string containint the 2-letter abbreviation for the country, e.g. "US" or "CN"
-# energyColumnName is the name of the column to be used for energy.
-#   This may be any of heat ("iQ"), exergy ("iX"), or useful work ("iU").
-# energyString is the string to be used in table captions reprsenting the type of energy. Typically, "q", "x", or "u"
+# energyType is a string to be used in table captions reprsenting the type of energy. Typically, "Q", "X", or "U"
 ##
-cobbDouglasEnergyData <- function(countryName, energyString){
+cobbDouglasEnergyData <- function(countryName, energyType){
 
-  energyColumnName  <- paste("i", energyString, sep="")
+  print(countryName)
+  energyColumnName  <- paste("i", energyType, sep="")
   #print(energyColumnName)
@@
   summaryCDe <- summary(modelCDe) # Gives the nls summary table
-  #print(summaryCDe)
+  print(summaryCDe)
 
@@
   #row.names(estCDe) <- "Cobb-Douglas with e: $y = e^{\\lambda t}k^{\\alpha}l^{\\beta}e^{\\gamma}$"
-  row.names(estCDe) <- paste("C-D with ", energyString, sep="")
+  row.names(estCDe) <- paste("C-D with ", energyType, sep="")
   # The [1] subscripts pick off the lower confidence interval
@@
 
+####################################
+# Creates a LaTeX printable table from the CES data. This function first calls cobbDouglasEnergyData.
+#
+# countryName is a string containint the 2-letter abbreviation for the country, e.g. "US" or "CN"
+# energyType is a string to be used in table captions reprsenting the type of energy. Typically, "Q", "X", or "U"
+#
+# returns a printable LaTeX table from xtable.
+##
 cobbDouglasEnergyTable <- function(countryName, energyType){
@@
 }
-
 @
 
-\subsection{Cobb-Douglas with Q}
+\subsection{Cobb-Douglas with $Q$}
 
-<<CDe analysis>>=
+<<CDq analysis>>=
 # Note that the anlaysis of ZA is taking a long time here. Need to figure out why.
@@
 
-\subsection{Cobb-Douglas With X}
+\subsection{Cobb-Douglas With $X$}
 
-<<cdx>>=
-energyColumn <- "iX"; energyString <- "x"
-dataCDx <- cobbDouglasEnergy(countryName, energyColumn, energyString)
-tableCDx <- xtable(dataCDx, caption=paste(countryName, ", 1980-2011.", sep=""), digit = c(4, 4, 2, 2, 3))
+<<CDx analysis>>=
+# Note that the anlaysis of ZA is taking a long time here. Need to figure out why.
+CDxTables <- lapply(countries, cobbDouglasEnergyTable, energyType="X")
 @
@@
 <<CDx Results, results='asis'>>=
-print(tableCDx, caption.placement="top")
+print(CDxTables[["US"]], caption.placement="top")
+print(CDxTables[["ZA"]], caption.placement="top")
 @
 
-\subsection{Cobb-Douglas With U}
+\subsection{Cobb-Douglas With $U$}
 
-<<cdu>>=
-energyColumn <- "iU"; energySTring <- "u"
-dataCDu <- cobbDouglasEnergy(countryName, energyColumn, energyString)
-tableCDu <- xtable(dataCDu, caption=paste(countryName, ", 1980-2011.", sep=""), digit = c(4, 4, 2, 2, 3))
+<<CDu analysis>>=
+CDuTables <- lapply(countries, cobbDouglasEnergyTable, energyType="U")
 @
@@
 <<CDu Results, results='asis'>>=
-print(tableCDu, caption.placement="top")
+print(CDuTables[["US"]], caption.placement="top")
+print(CDuTables[["ZA"]], caption.placement="top")
 @
 
-\section{CES With Q}
+\section{CES}
 
 <<CES function>>=
-
-ces <- function(countryName, energyColumnName, energyString){
-
+cesData <- function(countryName, energyType){
+  energyColumnName <- paste("i", energyType, sep="")
   # Load the data that we need.
@@
                        lambda_L = coef(modelCES)["lambda_L"], lambda_E = coef(modelCES)["lambda_E"])
-  row.names(estCES) <- paste("CES with ", energyString, sep="")
+  row.names(estCES) <- paste("CES with ", energyType, sep="")
   #print(estCES)  
@@
 }
+
+####################################
+# Creates a LaTeX printable table from the CES data. This function first calls cesData.
+#
+# countryName is a string containint the 2-letter abbreviation for the country, e.g. "US" or "CN"
+# energyType is a string to be used in table captions reprsenting the type of energy. Typically, "Q", "X", or "U"
+#
+# returns a printable LaTeX table from xtable.
+##
+cesTable <- function(countryName, energyType){
+  dataCESe <- cesData(countryName, energyType)
+  tableCESq <- xtable(dataCESe, caption=paste(countryName, ", 1980-2011.", sep=""), digit = c(4, 1, 2, 2, 6, 5, 5))
+}
 @
 
-<<CES with Q>>=
+\subsection{CES with $Q$}
+<<CESq analysisQ>>=
 countryName <- "US"
-energyColumn <- "iQ"; energyString <- "q"
-dataCESq <- ces(countryName, energyColumn, energyString)
-tableCESq <- xtable(dataCESq, caption=paste(countryName, ", 1980-2011.", sep=""), digit = c(4, 1, 2, 2, 6, 5, 5))
+energyType <- "Q"
+tableCESq <- cesTable(countryName, energyType)
+
+#CESqTables <- lapply(countries, cesTable, energyType="Q")
 @
@@
 print(tableCESq, caption.placement="top")
+
+#print(CESqTables[["US"]], caption.placement="top")
+#print(CESqTables[["ZA"]], caption.placement="top")
 @

### 2013-01-25 EconGrowth.Rnw
Committed text changes.
Now drawing a graph of US GDP vs. time data.

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Caleb, put your LaTeX code here.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Caleb, put your LaTeX code here.
 
@@
   tidy=FALSE,
-  fig.width=4.5,
+  fig.width=4,
   fig.height=3.8,
@@
 # List of countries
-countries <- c(US = "US", ZA = "ZA")
+countries <- c(US="US", UK="UK", JP="JP", ZA = "ZA", CN="CN", IR="IR", SA="SA", TZ="TZ", ZM="ZM")
 # List of energy types
@@
 }
+@
+
+<<creategraph>>=
+
+createCountryGraph <- function(countryName){
+  dataTable <- loadData(countryName)
+  graph <- xyplot(iGDP ~ iYear, data=dataTable)
+  return(graph)
+}
+
+#graph <- createCountryGraph("US")
+print(createCountryGraph("US"))
+
 @
@@
   modelCD <- nls(iGDP ~ exp(lambda*iYear) * iCapStk^alpha * iLabor^(1 - alpha), 
-                 start=(list(lambda=lambdaGuess,alpha=alphaGuess)),
+#                 algorithm = "port",
+                 start = list(lambda=lambdaGuess, alpha=alphaGuess),
+#                 lower = list(lambda=-Inf, alpha=0),
+#                 upper = list(lambda=Inf, alpha=1),
                  data=dataTable)
@@
 print(tablesCD[["US"]], caption.placement="top")
+print(tablesCD[["UK"]], caption.placement="top")
+print(tablesCD[["JP"]], caption.placement="top")
 print(tablesCD[["ZA"]], caption.placement="top")
+print(tablesCD[["CN"]], caption.placement="top")
+print(tablesCD[["SA"]], caption.placement="top")
+print(tablesCD[["IR"]], caption.placement="top")
+print(tablesCD[["TZ"]], caption.placement="top")
+print(tablesCD[["ZM"]], caption.placement="top")
+
 # According to http://cran.r-project.org/web/packages/xtable/vignettes/xtableGallery.pdf, Section 3.1, I should 
@@
 
-<<cobbDouglasEnergy function>>=
+<<cobbDouglasEnergy function, include=TRUE, echo=FALSE>>=
 ###############################
@@
   b <- as.numeric(coef(modelCDe)["b"])
+  print(a)
+  print(b)
   lambda <- as.numeric(coef(modelCDe)["lambda"])
@@
 
-<<CDq analysis>>=
+<<CDq analysis, eval=FALSE>>=
 # Note that the anlaysis of ZA is taking a long time here. Need to figure out why.
@@
 
-<<CDq Results, results='asis'>>=
+<<CDq Results, results='asis', echo=TRUE, eval=FALSE>>=
 print(CDqTables[["US"]], caption.placement="top")
@@
 
-<<CDx analysis>>=
+<<CDx analysis, eval=FALSE>>=
 # Note that the anlaysis of ZA is taking a long time here. Need to figure out why.
@@
 
-<<CDx Results, results='asis'>>=
+<<CDx Results, results='asis', eval=FALSE>>=
 print(CDxTables[["US"]], caption.placement="top")
@@
 
-<<CDu analysis>>=
+<<CDu analysis, eval=FALSE>>=
 CDuTables <- lapply(countries, cobbDouglasEnergyTable, energyType="U")
@@
 
-<<CDu Results, results='asis'>>=
+<<CDu Results, results='asis', eval=FALSE>>=
 print(CDuTables[["US"]], caption.placement="top")

### 2013-01-26 EconGrowth.Rnw
Adjusting the formatting of the US figure.

@@
   tidy=FALSE,
-  fig.width=4,
-  fig.height=3.8,
-  out.width=".45\\textwidth",
-  out.height=".38\\textwidth",
+  fig.width=6,
+  fig.height=4,
+#  out.width=".45\\textwidth",
+#  out.height=".38\\textwidth",
   comment=NA)
@@
 
-createCountryGraph <- function(countryName){
+createCountryInputGraph <- function(countryName){
   dataTable <- loadData(countryName)
-  graph <- xyplot(iGDP ~ iYear, data=dataTable)
+  graph <- xyplot(iGDP+iQ+iX+iU ~ iYear, data=dataTable,
+                  type="l",
+                  scales=list(cex=1.5, tck=-1),
+                  ylab="Indexed (1980=1)",
+                  auto.key=list(columns=1))
   return(graph)
@@
 
-#graph <- createCountryGraph("US")
-print(createCountryGraph("US"))
+createCountryInputGraph("US")
 

### 2013-01-26 EconGrowth.Rnw
Now generating data graphs for all countries.

@@
   dataTable <- loadData(countryName)
-  graph <- xyplot(iGDP+iQ+iX+iU ~ iYear, data=dataTable,
+  graph <- xyplot(iGDP+iQ+iX+iCapStk+iLabor ~ iYear, data=dataTable,
                   type="l",
-                  scales=list(cex=1.5, tck=-1),
+                  scales=list(cex=1.0, tck=-0.5),
                   ylab="Indexed (1980=1)",
-                  auto.key=list(columns=1))
+                  auto.key=list(columns=1, x=0.0, y=0.98))
   return(graph)
@@
 createCountryInputGraph("US")
+lapply(countries, createCountryInputGraph)
 

### 2013-01-27 EconGrowth.Rnw
Now creating much better graph for the factors of production. Colors are all black, lines are the way I want them. Beginning work on developing a GDP comparison graph.

--- 2013-01-26 EconGrowth.Rnw
@@
 
-<<creategraph>>=
+<<graphs>>=
 
-createCountryInputGraph <- function(countryName){
+createCountryFactorsGraph <- function(countryName){
   dataTable <- loadData(countryName)
-  graph <- xyplot(iGDP+iQ+iX+iU ~ iYear, data=dataTable,
+  lineSpec <- list(lty=c(1, 5, 2, 4), #line type
+                   col=c("black", "black", "black", "black"), #line colors
+                   lwd=c(1, 1, 1, 1)) #line widths
+  graph <- xyplot(iCapStk+iLabor+iQ+iX ~ iYear, data=dataTable,
+                  key=list(text=list(c("k", "l", "q", "x")),
                            type="l",
-                  scales=list(cex=1.5, tck=-1),
-                  ylab="Indexed (1980=1)",
-                  auto.key=list(columns=1))
+                           lines=lineSpec,
+                           columns=1, x=0.0, y=0.98),
+                  type="l",
+                  par.settings = list(superpose.line = lineSpec),
+                  scales=list(cex=1.0, #controls text size on scales
+                              tck=-0.5), #controls tick mark length
+                  ylab="Indexed (1980=1)")
   return(graph)
@@
 
-createCountryInputGraph("US")
+createGDPComparisonGraph <- function(countryName){
+  dataTable <- loadData(countryName)
+  colors <- c("black", "black", "black", "black", "black") #line and point colors
+  lineSpec <- list(lty=c(1, 1, 5, 2, 4), #line type
+                   col=colors,
+                   lwd=c(0, 1, 1, 1, 1)) #line widths. 0 suppresses the line for historical GDP.
+  pointSpec <- list(col=colors)
+  graph <- xyplot(iGDP ~ iYear, data=dataTable,
+                  key=list(text=list(c("GDP")),
+                           type="b",
+                           lines=lineSpec,
+                           columns=1, x=0.0, y=0.98),
+                  type="b",
+                  par.settings = list(superpose.line = lineSpec),
+                  scales=list(cex=1.0, #controls text size on scales
+                              tck=-0.5), #controls tick mark length
+                  ylab="Indexed (1980=1)")
+  return(graph)
+
+}
+
+createGDPComparisonGraph("US")
+
+#createCountryFactorsGraph("US")
+#lapply(countries, createCountryFactorsGraph)
 

### 2013-01-27 EconGrowth.Rnw
Trying to make the GDP comparison graph.

--- 2013-01-26 EconGrowth.Rnw
@@
 
-<<creategraph>>=
-
-createCountryInputGraph <- function(countryName){
+<<graphs>>=
+createCountryFactorsGraph <- function(countryName){
   dataTable <- loadData(countryName)
-  graph <- xyplot(iGDP+iQ+iX+iU ~ iYear, data=dataTable,
-                  type="l",
-                  scales=list(cex=1.5, tck=-1),
-                  ylab="Indexed (1980=1)",
-                  auto.key=list(columns=1))
+  graphType <- "l"
+  colors <- c("black", "black", "black", "black") #line and point colors
+  lineWidths <- c(1, 1, 1, 1) #line widths
+  lineTypes <- c(1, 5, 2, 4) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
+  lineSpec <- list(lty=lineTypes, lwd=lineWidths, col=colors)
+  graph <- xyplot(iCapStk+iLabor+iQ+iX ~ iYear, data=dataTable,
+                  key=list(text=list(c("k", "l", "q", "x")),
+                           type=graphType,
+                           lines=lineSpec,
+                           columns=1, x=0.0, y=0.98),
+                  type=graphType,
+                  par.settings = list(superpose.line = lineSpec),
+                  scales=list(cex=1.0, #controls text size on scales
+                              tck=-0.5), #controls tick mark length
+                  ylab="Indexed (1980=1)")
   return(graph)
@@
 
-createCountryInputGraph("US")
+createGDPComparisonGraph <- function(countryName){
+  dataTable <- loadData(countryName)
+  graphType <- "l"
+  colors <- c("black", "black", "black", "black") #line and point colors
+  lineWidths <- c(1, 1, 1, 1) #line widths
+  lineTypes <- c(1, 5, 2, 4) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
+  lineSpec <- list(lty=lineTypes, lwd=lineWidths, col=colors)
+  pointSpec <- list(col=colors)
+  graph <- xyplot(iGDP ~ iYear, data=dataTable,
+                  key=list(text=list(c("GDP")),
+                           type=graphType,
+                           lines=lineSpec,
+                           columns=1, x=0.0, y=0.98),
+                  type=graphType,
+                  par.settings = list(superpose.line = lineSpec),
+#                                      superpose.symbol = pointSpec),
+                  scales=list(cex=1.0, #controls text size on scales
+                              tck=-0.5), #controls tick mark length
+                  ylab="Indexed (1980=1)")
+  return(graph)
+
+}
+
+createGDPComparisonGraph("US")
+
+createCountryFactorsGraph("US")
+#lapply(countries, createCountryFactorsGraph)
 

### 2013-01-27 EconGrowth.Rnw
Now generating a lattice graph for factors of production for each country.

--- 2013-01-26 EconGrowth.Rnw
@@
   tidy=FALSE,
-  fig.width=6,
-  fig.height=4,
+  fig.width=6.5,
+  fig.height=4.5,
 #  out.width=".45\\textwidth",
@@
 
-<<creategraph>>=
-
-createCountryInputGraph <- function(countryName){
+<<graphs>>=
+createCountryFactorsGraph <- function(countryName){
   dataTable <- loadData(countryName)
-  graph <- xyplot(iGDP+iQ+iX+iCapStk+iLabor ~ iYear, data=dataTable,
-                  type="l",
-                  scales=list(cex=1.0, tck=-0.5),
-                  ylab="Indexed (1980=1)",
-                  auto.key=list(columns=1, x=0.0, y=0.98))
+  graphType <- "l"
+  lineTypes <- c(1, 5, 2, 4, 6) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
+  lineWidths <- c(1, 1, 1, 1, 1) #line widths
+  colors <- c("black", "black", "black", "black", "black") #line and point colors
+  lineSpec <- list(lty=lineTypes, lwd=lineWidths, col=colors)
+  graph <- xyplot(iCapStk+iLabor+iQ+iX+iU ~ Year, data=dataTable,
+                  type=graphType,
+                  par.settings = list(superpose.line = lineSpec),
+                  key=list(text=list(c("k", "l", "q", "x", "u")),
+                           type=graphType,
+                           lines=lineSpec,
+                           columns=1, x=0.0, y=0.98),
+                  scales=list(cex=1.0, #controls text size on scales
+                              tck=-0.5), #controls tick mark length
+                  ylab="Indexed (1980=1)")
   return(graph)
@@
 
-createCountryInputGraph("US")
-lapply(countries, createCountryInputGraph)
+createFactorsLatticeGraph <- function(countryName){
+  dataTable <- loadData(countryName)
+  graphType <- "l"
+  lineTypes <- c(1, 5, 2, 4, 6) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
+  lineWidths <- c(1, 1, 1, 1, 1) #line widths
+  colors <- c("black", "black", "black", "black", "black") #line and point colors
+  lineSpec <- list(lty=lineTypes, lwd=lineWidths, col=colors)
+  graph <- xyplot(iCapStk+iLabor+iQ+iX+iU ~ Year | Country, data=dataTable,
+                  type=graphType,
+                  par.settings = list(superpose.line = lineSpec),
+                  key=list(text=list(c("k", "l", "q", "x", "u")),
+                           type=graphType,
+                           cex=0.85,
+                           lines=lineSpec,
+                           columns=1, x=0.01, y=0.92),
+                  scales=list(cex=0.75, #controls text size on scales
+                              tck=-0.5), #controls tick mark length
+                  ylab="Indexed (1980=1)")
+  return(graph)
+}
+
+createGDPComparisonGraph <- function(countryName){
+  dataTable <- loadData(countryName)
+  graphType <- "l"
+  lineTypes <- c(1) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
+  lineWidths <- c(1) #line widths
+  colors <- c("black") #line and point colors
+  lineSpec <- list(lty=lineTypes, lwd=lineWidths, col=colors)
+  graph <- xyplot(iGDP ~ Year, data=dataTable,
+                  key=list(text=list(c("GDP")),
+                           type=graphType,
+                           lines=lineSpec,
+                           columns=1, x=0.0, y=0.98),
+                  type=graphType,
+                  par.settings = list(superpose.line = lineSpec),
+                  scales=list(cex=1.0, #controls text size on scales
+                              tck=-0.5), #controls tick mark length
+                  ylab="Indexed (1980=1)")
+  return(graph)
+}
+
+# createGDPComparisonGraph <- function(countryName){
+#   dataTable <- loadData(countryName)
+#   graphType <- "l"
+#   colors <- c("black", "black", "black", "black") #line and point colors
+#   lineWidths <- c(1, 1, 1, 1) #line widths
+#   lineTypes <- c(1, 5, 2, 4) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
+#   lineSpec <- list(lty=lineTypes, lwd=lineWidths, col=colors)
+#   pointSpec <- list(col=colors)
+#   graph <- xyplot(iGDP ~ iYear, data=dataTable,
+#                   key=list(text=list(c("GDP")),
+#                            type=graphType,
+#                            lines=lineSpec,
+#                            columns=1, x=0.0, y=0.98),
+#                   type=graphType,
+#                   par.settings = list(superpose.line = lineSpec),
+# #                                      superpose.symbol = pointSpec),
+#                   scales=list(cex=1.0, #controls text size on scales
+#                               tck=-0.5), #controls tick mark length
+#                   ylab="Indexed (1980=1)")
+#   return(graph)
+# 
+#                     
+# }
+
+createFactorsLatticeGraph("All")
+
+#createGDPComparisonGraph("US")
+
+#createCountryFactorsGraph("US")
+#lapply(countries, createCountryFactorsGraph)
 

### 2013-01-27 EconGrowth.Rnw
Production factors lattice graph is now to my liking, more or less.

@@
   tidy=FALSE,
-  fig.width=6.5,
-  fig.height=4.5,
+  fig.width=6,
+  fig.height=4,
 #  out.width=".45\\textwidth",
@@
 
+<<Factors of Production Lattice Graph, fig.width=6.5, fig.height=7.5, fig.cap="Factors of Production for All Countries. (China's indexed capital stock rises to $k = 9.2$ in 2011.)", echo=FALSE>>=
+createFactorsLatticeGraph <- function(countryName){
+  dataTable <- loadData(countryName)
+  graphType <- "l"
+  lineTypes <- c(1, 5, 2, 4, 6) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
+  lineWidths <- c(1, 1, 1, 1, 1) #line widths
+  colors <- c("black", "black", "black", "black", "black") #line and point colors
+  lineSpec <- list(lty=lineTypes, lwd=lineWidths, col=colors)
+  graph <- xyplot(iCapStk+iLabor+iQ+iX+iU ~ Year | Country, data=dataTable,
+                  index.cond=list(c(7,6,3,1,8,5,4,2,9)), #orders the panels. Default is alphabetical.
+                  as.table=TRUE,
+                  type=graphType,
+                  layout=c(3,3),
+                  par.settings = list(superpose.line = lineSpec),
+                  key=list(text=list(c("k", "l", "q", "x", "u")),
+                           type=graphType,
+                           cex=0.85,
+                           lines=lineSpec,
+                           columns=1, x=0.01, y=0.95),
+                  scales=list(cex=0.75, #controls text size on scales
+                              tck=-0.5, #controls tick mark length
+                              y=list(at=c(1,2,3,4,5,6,7,8,9,10))), 
+                  xlab="",
+                  ylim=c(0.5,4.5),
+                  ylab="Indexed (1980=1 or 1991=1)")
+  return(graph)
+}
+createFactorsLatticeGraph("All") #Reads data from the "AllData.txt" file.
+@
+
 <<graphs>>=
@@
                   scales=list(cex=1.0, #controls text size on scales
-                              tck=-0.5), #controls tick mark length
-                  ylab="Indexed (1980=1)")
-  return(graph)
-}
-
-createFactorsLatticeGraph <- function(countryName){
-  dataTable <- loadData(countryName)
-  graphType <- "l"
-  lineTypes <- c(1, 5, 2, 4, 6) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
-  lineWidths <- c(1, 1, 1, 1, 1) #line widths
-  colors <- c("black", "black", "black", "black", "black") #line and point colors
-  lineSpec <- list(lty=lineTypes, lwd=lineWidths, col=colors)
-  graph <- xyplot(iCapStk+iLabor+iQ+iX+iU ~ Year | Country, data=dataTable,
-                  type=graphType,
-                  par.settings = list(superpose.line = lineSpec),
-                  key=list(text=list(c("k", "l", "q", "x", "u")),
-                           type=graphType,
-                           cex=0.85,
-                           lines=lineSpec,
-                           columns=1, x=0.01, y=0.92),
-                  scales=list(cex=0.75, #controls text size on scales
                               tck=-0.5), #controls tick mark length
@@
 # }
-
-createFactorsLatticeGraph("All")
 

### 2013-01-27 EconGrowth.Rnw
Now creating a table for all CD countries. Unfortunately, I have one additional column (don't know why), and there are way too many significant figures in the table. The digit=c() parameter doesn't seem to be working yet.

@@
 # List of countries
-countries <- c(US="US", UK="UK", JP="JP", ZA = "ZA", CN="CN", IR="IR", SA="SA", TZ="TZ", ZM="ZM")
+countries <- c(US="US", UK="UK", JP="JP", CN="CN", ZA = "ZA", SA="SA", IR="IR", TZ="TZ", ZM="ZM")
 # List of energy types
@@
 
-<<Factors of Production Lattice Graph, fig.width=6.5, fig.height=7.5, fig.cap="Factors of Production for All Countries. (China's indexed capital stock rises to $k = 9.2$ in 2011.)", echo=FALSE>>=
+<<Factors Lattice Graph, fig.width=6.5, fig.height=7.5, fig.cap="Factors of Production for All Countries. (China's indexed capital stock rises to $k = 9.2$ in 2011.)", echo=FALSE>>=
 createFactorsLatticeGraph <- function(countryName){
@@
 
-<<graphs>>=
+<<Country Factors Graph>>=
 createCountryFactorsGraph <- function(countryName){
@@
 
+############
+# Creates a row for the Cobb Douglas parameters table
+##
+cobbDouglasCountryRow <- function(countryName){
+  dataCD <- cobbDouglasData(countryName)
+  # Create CI ranges
+  out <- cbind(countryName, 
+               dataCD["- 95% CI", "lambda"], dataCD["CD", "lambda"], dataCD["+ 95% CI", "lambda"],
+               dataCD["- 95% CI", "alpha"],  dataCD["CD", "alpha"],  dataCD["+ 95% CI", "alpha"],
+               dataCD["- 95% CI", "beta"],   dataCD["CD", "beta"],   dataCD["+ 95% CI", "beta"])
+
+  return(out)
+}
+
+cobbDouglasParamsTable <- function(){
+  dataCD <- rbind(cobbDouglasCountryRow("US"),
+                cobbDouglasCountryRow("UK"),
+                cobbDouglasCountryRow("JP"),
+                cobbDouglasCountryRow("CN"),
+                cobbDouglasCountryRow("ZA"),
+                cobbDouglasCountryRow("SA"),
+                cobbDouglasCountryRow("IR"),
+                cobbDouglasCountryRow("TZ"),
+                cobbDouglasCountryRow("ZM"))
+  colnames(dataCD) <- c("", "-95% CI", "$\\lambda$", "+95% CI", 
+                        "-95% CI", "$\\alpha$",  "+95% CI",
+                        "-95% CI", "$\\beta$",   "+95% CI")
+  rownames(dataCD) <- countries
+  print("************** Trying to print dataCD **********************")
+#   print(class(dataCD))
+#   print(dataCD)
+  tableCD <- xtable(dataCD, caption="Cobb-Douglas, 1980-2011 or 1991-2011", digit = c(1,1, 4,4,4, 4,4,4, 4,4,4))
+  #print(tableCD)
+  return(tableCD)
+}
+cobbDouglasParamsTable()
+
 ####################################
@@
 ##
-cobbDouglasTable <- function(countryName){
+cobbDouglasCountryTable <- function(countryName){
   dataCD <- cobbDouglasData(countryName) 
@@
 <<CD Analysis>>=
-tablesCD <- lapply(countries, cobbDouglasTable)
+tablesCD <- lapply(countries, cobbDouglasCountryTable)
 @
 
-<<CD Results, results='asis'>>=
+<<CD Results, results='asis', echo=FALSE>>=
+print(cobbDouglasParamsTable(), caption.placement="top")
+
 print(tablesCD[["US"]], caption.placement="top")
@@
 print(tablesCD[["JP"]], caption.placement="top")
+print(tablesCD[["CN"]], caption.placement="top")
 print(tablesCD[["ZA"]], caption.placement="top")
-print(tablesCD[["CN"]], caption.placement="top")
 print(tablesCD[["SA"]], caption.placement="top")

### 2013-01-28 EconGrowth.Rnw
Now creating the Cobb-Douglas parameters table exactly the way I want it.

@@
 
-<<Country Factors Graph>>=
+<<Country Factors Graph, echo=FALSE>>=
 createCountryFactorsGraph <- function(countryName){
@@
 }
-
-createGDPComparisonGraph <- function(countryName){
-  dataTable <- loadData(countryName)
-  graphType <- "l"
-  lineTypes <- c(1) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
-  lineWidths <- c(1) #line widths
-  colors <- c("black") #line and point colors
-  lineSpec <- list(lty=lineTypes, lwd=lineWidths, col=colors)
-  graph <- xyplot(iGDP ~ Year, data=dataTable,
-                  key=list(text=list(c("GDP")),
-                           type=graphType,
-                           lines=lineSpec,
-                           columns=1, x=0.0, y=0.98),
-                  type=graphType,
-                  par.settings = list(superpose.line = lineSpec),
-                  scales=list(cex=1.0, #controls text size on scales
-                              tck=-0.5), #controls tick mark length
-                  ylab="Indexed (1980=1)")
-  return(graph)
-}
-
-# createGDPComparisonGraph <- function(countryName){
-#   dataTable <- loadData(countryName)
-#   graphType <- "l"
-#   colors <- c("black", "black", "black", "black") #line and point colors
-#   lineWidths <- c(1, 1, 1, 1) #line widths
-#   lineTypes <- c(1, 5, 2, 4) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
-#   lineSpec <- list(lty=lineTypes, lwd=lineWidths, col=colors)
-#   pointSpec <- list(col=colors)
-#   graph <- xyplot(iGDP ~ iYear, data=dataTable,
-#                   key=list(text=list(c("GDP")),
-#                            type=graphType,
-#                            lines=lineSpec,
-#                            columns=1, x=0.0, y=0.98),
-#                   type=graphType,
-#                   par.settings = list(superpose.line = lineSpec),
-# #                                      superpose.symbol = pointSpec),
-#                   scales=list(cex=1.0, #controls text size on scales
-#                               tck=-0.5), #controls tick mark length
-#                   ylab="Indexed (1980=1)")
-#   return(graph)
-# 
-#                     
-# }
-
-#createGDPComparisonGraph("US")
-
-#createCountryFactorsGraph("US")
-#lapply(countries, createCountryFactorsGraph)
-
 @
@@
 
-<<cobb-douglas>>=
+<<cobb-douglas, echo=FALSE>>=
 
@@
   # Create CI ranges
-  out <- cbind(countryName, 
-               dataCD["- 95% CI", "lambda"], dataCD["CD", "lambda"], dataCD["+ 95% CI", "lambda"],
+  out <- cbind(dataCD["- 95% CI", "lambda"], dataCD["CD", "lambda"], dataCD["+ 95% CI", "lambda"],
                dataCD["- 95% CI", "alpha"],  dataCD["CD", "alpha"],  dataCD["+ 95% CI", "alpha"],
                dataCD["- 95% CI", "beta"],   dataCD["CD", "beta"],   dataCD["+ 95% CI", "beta"])
-
   return(out)
@@
                 cobbDouglasCountryRow("ZM"))
-  colnames(dataCD) <- c("", "-95% CI", "$\\lambda$", "+95% CI", 
-                        "-95% CI", "$\\alpha$",  "+95% CI",
-                        "-95% CI", "$\\beta$",   "+95% CI")
+  colnames(dataCD) <- c(" ", "$\\lambda$", " ", 
+                        " ", "$\\alpha$",  " ",
+                        " ", "$\\beta$",   " ")
   rownames(dataCD) <- countries
-  print("************** Trying to print dataCD **********************")
-#   print(class(dataCD))
-#   print(dataCD)
-  tableCD <- xtable(dataCD, caption="Cobb-Douglas, 1980-2011 or 1991-2011", digit = c(1,1, 4,4,4, 4,4,4, 4,4,4))
-  #print(tableCD)
+  tableCD <- xtable(dataCD, 
+                    caption="Cobb-Douglas parameters for 1980-2011 (developed nations) or 1991-2011 (others). (Parameter estimates beneath symbol. 95\\% confidence bounds to left and right.)", 
+                    digit = c(1, 4,4,4, 2,2,2, 2,2,2),
+                    align = "r|ccc|ccc|ccc")
   return(tableCD)
 }
-cobbDouglasParamsTable()
 
@@
 
-<<CD Analysis>>=
-tablesCD <- lapply(countries, cobbDouglasCountryTable)
-@
-
 <<CD Results, results='asis', echo=FALSE>>=
-print(cobbDouglasParamsTable(), caption.placement="top")
-
-print(tablesCD[["US"]], caption.placement="top")
-print(tablesCD[["UK"]], caption.placement="top")
-print(tablesCD[["JP"]], caption.placement="top")
-print(tablesCD[["CN"]], caption.placement="top")
-print(tablesCD[["ZA"]], caption.placement="top")
-print(tablesCD[["SA"]], caption.placement="top")
-print(tablesCD[["IR"]], caption.placement="top")
-print(tablesCD[["TZ"]], caption.placement="top")
-print(tablesCD[["ZM"]], caption.placement="top")
-
-# According to http://cran.r-project.org/web/packages/xtable/vignettes/xtableGallery.pdf, Section 3.1, I should 
-# be able to use the "sanitize.text.function" parameter to allow markup in column headers. But this next
-# line is not working at the present time. --MKH, 18 Jan 2012.
-# print(tableCD, caption.placement="top", sanitize.text.function = function(x){x})
+print(cobbDouglasParamsTable(), caption.placement="top", sanitize.colnames.function = identity)
 @

### 2013-01-28 EconGrowth.Rnw
Adjusted the formatting of the factors of production graph slightly to highlight the k and l lines as opposed to the energy lines.

@@
 \author[Calvin]{Lucas Timmer}
-\author[Calvin]{Matthew Kuperus Heun \corref{cor1}}
+\author[Calvin]{Matthew Kuperus Heun\corref{cor1}}
 \ead{mkh2@calvin.edu, tel: +1 (616) 526-6663, fax: +1 (616) 526-6501}
@@
   fig.height=4,
-#  out.width=".45\\textwidth",
-#  out.height=".38\\textwidth",
   comment=NA)
@@
 
-<<Factors Lattice Graph, fig.width=6.5, fig.height=7.5, fig.cap="Factors of Production for All Countries. (China's indexed capital stock rises to $k = 9.2$ in 2011.)", echo=FALSE>>=
-createFactorsLatticeGraph <- function(countryName){
+<<Country Factors Graph, echo=FALSE>>=
+createCountryFactorsGraph <- function(countryName){
   dataTable <- loadData(countryName)
@@
   colors <- c("black", "black", "black", "black", "black") #line and point colors
+  lineSpec <- list(lty=lineTypes, lwd=lineWidths, col=colors)
+  graph <- xyplot(iCapStk+iLabor+iQ+iX+iU ~ Year, data=dataTable,
+                  type=graphType,
+                  par.settings = list(superpose.line = lineSpec),
+                  key=list(text=list(c("k", "l", "q", "x", "u")),
+                           type=graphType,
+                           lines=lineSpec,
+                           columns=1, x=0.0, y=0.98),
+                  scales=list(cex=1.0, #controls text size on scales
+                              tck=-0.5), #controls tick mark length
+                  ylab="Indexed (1980=1)")
+  return(graph)
+}
+@
+<<Factors Lattice Graph, fig.width=6.5, fig.height=7.5, fig.cap="Factors of Production for All Countries. (China's indexed capital stock rises to $k = 9.2$ in 2011.)", echo=FALSE>>=
+createFactorsLatticeGraph <- function(countryName){
+  dataTable <- loadData(countryName)
+  graphType <- "l"
+  lineTypes <- c(1, 5, 2, 4, 3) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
+  lineWidths <- c(2, 2, 1, 1, 1) #line widths
+  colors <- c("black", "black", "red", "blue", "black") #line and point colors
   lineSpec <- list(lty=lineTypes, lwd=lineWidths, col=colors)
@@
 createFactorsLatticeGraph("All") #Reads data from the "AllData.txt" file.
-@
-
-<<Country Factors Graph, echo=FALSE>>=
-createCountryFactorsGraph <- function(countryName){
-  dataTable <- loadData(countryName)
-  graphType <- "l"
-  lineTypes <- c(1, 5, 2, 4, 6) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
-  lineWidths <- c(1, 1, 1, 1, 1) #line widths
-  colors <- c("black", "black", "black", "black", "black") #line and point colors
-  lineSpec <- list(lty=lineTypes, lwd=lineWidths, col=colors)
-  graph <- xyplot(iCapStk+iLabor+iQ+iX+iU ~ Year, data=dataTable,
-                  type=graphType,
-                  par.settings = list(superpose.line = lineSpec),
-                  key=list(text=list(c("k", "l", "q", "x", "u")),
-                           type=graphType,
-                           lines=lineSpec,
-                           columns=1, x=0.0, y=0.98),
-                  scales=list(cex=1.0, #controls text size on scales
-                              tck=-0.5), #controls tick mark length
-                  ylab="Indexed (1980=1)")
-  return(graph)
-}
 @
@@
 
+####################################
+# Creates a LaTeX printable table from the Cobb Douglas data. This function first calls cobbDouglasData.
+#
+# countryName is a string containint the 2-letter abbreviation for the country, e.g. "US" or "CN"
+#
+# returns a printable LaTeX table from xtable.
+##
+cobbDouglasCountryTable <- function(countryName){
+  dataCD <- cobbDouglasData(countryName) 
+  colnames(dataCD) <- c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$")
+  tableCD <- xtable(dataCD, caption=paste(countryName, " Cobb-Douglas, 1980-2011", sep=""), digit = c(4, 4, 2, 2, 1))
+  #print(tableCD)
+  return(tableCD)  
+}
+
 ############
@@
                     align = "r|ccc|ccc|ccc")
-  return(tableCD)
-}
-
-####################################
-# Creates a LaTeX printable table from the Cobb Douglas data. This function first calls cobbDouglasData.
-#
-# countryName is a string containint the 2-letter abbreviation for the country, e.g. "US" or "CN"
-#
-# returns a printable LaTeX table from xtable.
-##
-cobbDouglasCountryTable <- function(countryName){
-  dataCD <- cobbDouglasData(countryName) 
-  colnames(dataCD) <- c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$")
-  tableCD <- xtable(dataCD, caption=paste(countryName, " Cobb-Douglas, 1980-2011", sep=""), digit = c(4, 4, 2, 2, 1))
-  #print(tableCD)
   return(tableCD)

### 2013-01-28 EconGrowth.Rnw
Now including GDP on the factors of production graph. Also, the graph is in EXACTLY the format that I want.

@@
                   index.cond=list(c(7,6,3,1,8,5,4,2,9)), #orders the panels. Default is alphabetical.
-                  as.table=TRUE,
+                  as.table=TRUE, #indexing of panels starts in upper left and goes across rows.
                   type=graphType,
@@
                               y=list(at=c(1,2,3,4,5,6,7,8,9,10))), 
+                  ylim=c(0.5,4.5),
                   xlab="",
-                  ylim=c(0.5,4.5),
                   ylab="Indexed (1980=1 or 1991=1)")
@@
   tableCD <- xtable(dataCD, 
-                    caption="Cobb-Douglas parameters for 1980-2011 (developed nations) or 1991-2011 (others). (Parameter estimates beneath symbol. 95\\% confidence bounds to left and right.)", 
+                    caption="Cobb-Douglas parameters for 1980-2011 (US, UK, JP) or 1991-2011 (others). (Parameter estimates beneath symbol. 95\\% confidence bounds to left and right.)", 
                     digit = c(1, 4,4,4, 2,2,2, 2,2,2),

### 2013-01-30 EconGrowth.Rnw
Now factors of production graph is exactly as I want it.

@@
 @
-<<Factors Lattice Graph, fig.width=6.5, fig.height=7.5, fig.cap="Factors of Production for All Countries. (China's indexed capital stock rises to $k = 9.2$ in 2011.)", echo=FALSE>>=
+<<Factors Lattice Graph, fig.width=6.5, fig.height=7.5, fig.cap="GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$) for all economies.
+(China's indexed GDP and indexed capital stock rise to $y = 7.3$ and $k = 9.2$ in 2011.)", echo=FALSE>>=
 createFactorsLatticeGraph <- function(countryName){
   dataTable <- loadData(countryName)
-  graphType <- "l"
-  lineTypes <- c(1, 5, 2, 4, 3) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
-  lineWidths <- c(2, 2, 1, 1, 1) #line widths
-  colors <- c("black", "black", "red", "blue", "black") #line and point colors
-  lineSpec <- list(lty=lineTypes, lwd=lineWidths, col=colors)
-  graph <- xyplot(iCapStk+iLabor+iQ+iX+iU ~ Year | Country, data=dataTable,
+  graphType <- "b"
+  lineTypes <- c(0, 1, 5, 2, 4, 1) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
+  lineWidths <- c(0, 2, 2, 1, 1, 1) #line widths
+  colors <- c("black", "black", "black", "red", "blue", "black") #line and point colors
+  #symbols <- c("o", "", "", "", "", "")
+  symbols <- c(1, NA_integer_, NA_integer_, NA_integer_, NA_integer_, NA_integer_)  
+  lineSpec <- list(lty=lineTypes, lwd=lineWidths)
+  graph <- xyplot(iGDP+iCapStk+iLabor+iQ+iX+iU ~ Year | Country, data=dataTable,
                   index.cond=list(c(7,6,3,1,8,5,4,2,9)), #orders the panels. Default is alphabetical.
@@
                   layout=c(3,3),
-                  par.settings = list(superpose.line = lineSpec),
-                  key=list(text=list(c("k", "l", "q", "x", "u")),
+                  lty = lineTypes, lwd = lineWidths, col = colors, #Controls line parameters
+                  pch = symbols, col.symbol = colors, #Controls symbol parameters
+                  key=list(text=list(c("y", "k", "l", "q", "x", "u")),
                            type=graphType,
@@
                            lines=lineSpec,
+                           pch=symbols,
+                           col=colors,
                            columns=1, x=0.01, y=0.95),

### 2013-01-30 EconGrowth.Rnw
Added many comments to the lattice graph section so that I can remember all the settings and parameters later.

@@
   lineTypes <- c(0, 1, 5, 2, 4, 1) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
-  lineWidths <- c(0, 2, 2, 1, 1, 1) #line widths
+  lineWidths <- c(0, 2, 2, 1, 1, 1) #line widths. 0 means no line.
   colors <- c("black", "black", "black", "red", "blue", "black") #line and point colors
-  #symbols <- c("o", "", "", "", "", "")
-  symbols <- c(1, NA_integer_, NA_integer_, NA_integer_, NA_integer_, NA_integer_)  
-  lineSpec <- list(lty=lineTypes, lwd=lineWidths)
+  symbols <- c(1, NA_integer_, NA_integer_, NA_integer_, NA_integer_, NA_integer_)  #NA_integer_ gives no symbol.
   graph <- xyplot(iGDP+iCapStk+iLabor+iQ+iX+iU ~ Year | Country, data=dataTable,
+                  type=graphType,
                   index.cond=list(c(7,6,3,1,8,5,4,2,9)), #orders the panels. Default is alphabetical.
+                  layout=c(3,3), #indicates a 3x3 arrangement of panels.
                   as.table=TRUE, #indexing of panels starts in upper left and goes across rows.
-                  type=graphType,
-                  layout=c(3,3),
                   lty = lineTypes, lwd = lineWidths, col = colors, #Controls line parameters
@@
                            type=graphType,
-                           cex=0.85,
-                           lines=lineSpec,
-                           pch=symbols,
-                           col=colors,
-                           columns=1, x=0.01, y=0.95),
-                  scales=list(cex=0.75, #controls text size on scales
-                              tck=-0.5, #controls tick mark length
-                              y=list(at=c(1,2,3,4,5,6,7,8,9,10))), 
-                  ylim=c(0.5,4.5),
-                  xlab="",
-                  ylab="Indexed (1980=1 or 1991=1)")
+                           cex=0.85, #controls size of text in the key
+                           lines=list(lty=lineTypes, lwd=lineWidths), #controls line types
+                           pch=symbols, col=colors, #controls symbol (plot characters) types
+                           columns=1, x=0.01, y=0.95), #We want only one column and sets location of the key
+                  scales=list(cex=0.75, #controls text size on scales.
+                              tck=-0.5, #controls tick mark length. < 0 for inside the graph.
+                              y=list(at=c(1,2,3,4,5,6,7,8,9,10))), #tick mark locations
+                  ylim=c(0.5,4.5), #y axis limits
+                  xlab="", ylab="Indexed (1980=1 or 1991=1)") #axis labels
   return(graph)

### 2013-01-30 EconGrowth.Rnw
Now gathering predictions for the US from the CD model.

@@
 @
-<<Factors Lattice Graph, fig.width=6.5, fig.height=7.5, fig.cap="GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$) for all economies.
+<<Factors_Lattice_Graph, fig.width=6.5, fig.height=7.5, fig.cap="GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$) for all economies.
 (China's indexed GDP and indexed capital stock rise to $y = 7.3$ and $k = 9.2$ in 2011.)", echo=FALSE>>=
@@
 <<cobb-douglas, echo=FALSE>>=
+####################
+# Returns an nls Cobb-Douglas model for the country specified
+##
+cobbDouglasModel <- function(countryName){
+  # Load the data that we need.
+  dataTable <- loadData(countryName)
+
+  # Establish guess values for alpha and lambda.
+  lambdaGuess <- 0.0 # guessing lambda = 0 means there is no technological progress.
+  alphaGuess <- 0.3 # a typical value for alpha, the coefficient on capital stock
+
+  # Runs a non-linear least squares fit to the data. We've replaced beta with 1-alpha for simplicity.
+  modelCD <- nls(iGDP ~ exp(lambda*iYear) * iCapStk^alpha * iLabor^(1 - alpha), 
+#                 algorithm = "port",
+                 start = list(lambda=lambdaGuess, alpha=alphaGuess),
+#                 lower = list(lambda=-Inf, alpha=0),
+#                 upper = list(lambda=Inf, alpha=1),
+                 data=dataTable)
+  return(modelCD)
+}
 
@@
 cobbDouglasData <- function(countryName){
-
-  # Load the data that we need.
-  dataTable <- loadData(countryName)
-
-  # Establish guess values for alpha and lambda.
-  lambdaGuess <- 0.0 # guessing lambda = 0 means there is no technological progress.
-  alphaGuess <- 0.3 # a typical value for alpha, the coefficient on capital stock
-
-  # Runs a non-linear least squares fit to the data. We've replaced beta with 1-alpha for simplicity.
-  modelCD <- nls(iGDP ~ exp(lambda*iYear) * iCapStk^alpha * iLabor^(1 - alpha), 
-#                 algorithm = "port",
-                 start = list(lambda=lambdaGuess, alpha=alphaGuess),
-#                 lower = list(lambda=-Inf, alpha=0),
-#                 upper = list(lambda=Inf, alpha=1),
-                 data=dataTable)
+  modelCD <- cobbDouglasModel(countryName)
 
@@
 
+############################
+# Aggregates the Cobb-Douglas results into a big data table
+##
 cobbDouglasParamsTable <- function(){
@@
 print(cobbDouglasParamsTable(), caption.placement="top", sanitize.colnames.function = identity)
+@
+
+<<CD Lattice Graph>>=
+usModel <- cobbDouglasModel("US")
+coefs <- coef(usModel)
+print(coef(usModel))
+usPred <- predict(usModel)
+class(usPred)
+print(usPred)
+data.frame(usPred)
+
 @

### 2013-01-31 EconGrowth.Rnw
Added a predGDP title to the column of predictions.

@@
 
+#########################
+# Takes the Cobb-Douglas fitted models and creates per-country predictions for them.
+# Returns a data.frame with the predictions.
+##
+cobbDouglasPredictions <- function(countryName){
+  model <- cobbDouglasModel(countryName)
+  coefs <- coef(usModel)
+  pred <- predict(model) #See http://stackoverflow.com/questions/9918807/how-get-plot-from-nls-in-r
+  return(data.frame(pred))
+}
+
+#########################
+# Takes the Cobb-Douglas fitted models and creates a single column of predicted GDP values
+# that corresponds to the AllData.txt file.
+##
+cobbDouglasPredictionsColumn <- function(){
+  preds <- lapply(countries, cobbDouglasPredictions)
+  out <- rbind(preds[["US"]], preds[["UK"]], preds[["JP"]], preds[["CN"]], preds[["ZA"]], preds[["SA"]], preds[["IR"]], preds[["TZ"]], preds[["ZM"]])
+  colnames(out) <- c("predGDP")
+  print(out)
+  return(out)
+}
+
 #################################################
@@
 coefs <- coef(usModel)
-print(coef(usModel))
-usPred <- predict(usModel)
+# print(coef(usModel))
+usPred <- predict(usModel) #See http://stackoverflow.com/questions/9918807/how-get-plot-from-nls-in-r
 class(usPred)
-print(usPred)
+#print(usPred)
 data.frame(usPred)
 
+allData <- loadData("All")
+predictions <- cobbDouglasPredictionsColumn()
+allData <- cbind(allData, predictions)
+
+print(allData)
 @

### 2013-01-31 EconGrowth.Rnw
Now using global variables for much of the control parameters for the graphs. This will ensure consistent appearance among all lattice (9-panel) graphs.

@@
 countries <- c(US="US", UK="UK", JP="JP", CN="CN", ZA = "ZA", SA="SA", IR="IR", TZ="TZ", ZM="ZM")
+# Set the order for presenting countries in 3x3 lattice graphs. Default is alphabetical. "1" means first alphabetically.
+# So, this list sets the order as US, UK, JP, CN, ZA, TZ, SA, IR, ZM.
+countryOrderForGraphs <- c(7,6,3,1,8,5,4,2,9)
+# Full page lattice plot sizes and other parameters
+layoutSpec <- c(3,3) #indicates a 3x3 arrangement of panels.
+figWidth <- 6.5 #Inches
+figHeight <- 7.5 #Inches
+keyTextSize <- 0.85 #85% of normal size
+keyColumns <- 1 #Want only 1 column in the key for lattice graphs
+keyXLoc <- 0.01 #x position of the key
+keyYLoc <- 0.95 #y position of the key
+scaleTextSize <- 0.75 #75% of normal size
+scaleTickSize <- -0.5 #50% of normal size and pointing INWARD!
 # List of energy types
@@
                   scales=list(cex=1.0, #controls text size on scales
-                              tck=-0.5), #controls tick mark length
+                              tck=scaleTickSize), #controls tick mark length
                   ylab="Indexed (1980=1)")
@@
 @
-<<Factors_Lattice_Graph, fig.width=6.5, fig.height=7.5, fig.cap="GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$) for all economies.
+<<Factors_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.cap="GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$) for all economies.
 (China's indexed GDP and indexed capital stock rise to $y = 7.3$ and $k = 9.2$ in 2011.)", echo=FALSE>>=
-createFactorsLatticeGraph <- function(countryName){
-  dataTable <- loadData(countryName)
-  graphType <- "b"
+createFactorsLatticeGraph <- function(){
+  dataTable <- loadData("All")
+  graphType <- "b" #b is for both line and symbol
   lineTypes <- c(0, 1, 5, 2, 4, 1) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
   lineWidths <- c(0, 2, 2, 1, 1, 1) #line widths. 0 means no line.
-  colors <- c("black", "black", "black", "red", "blue", "black") #line and point colors
-  symbols <- c(1, NA_integer_, NA_integer_, NA_integer_, NA_integer_, NA_integer_)  #NA_integer_ gives no symbol.
+  colors <- c("black", "black", "black", "red", "blue", "black") #line and symbol colors
+  symbols <- c(1, NA, NA, NA, NA, NA)  #NA gives no symbol.
   graph <- xyplot(iGDP+iCapStk+iLabor+iQ+iX+iU ~ Year | Country, data=dataTable,
                   type=graphType,
-                  index.cond=list(c(7,6,3,1,8,5,4,2,9)), #orders the panels. Default is alphabetical.
-                  layout=c(3,3), #indicates a 3x3 arrangement of panels.
+                  index.cond=list(countryOrderForGraphs), #orders the panels.
+                  layout=layoutSpec, 
                   as.table=TRUE, #indexing of panels starts in upper left and goes across rows.
@@
                            type=graphType,
-                           cex=0.85, #controls size of text in the key
+                           cex=keyTextSize, #controls size of text in the key
                            lines=list(lty=lineTypes, lwd=lineWidths), #controls line types
                            pch=symbols, col=colors, #controls symbol (plot characters) types
-                           columns=1, x=0.01, y=0.95), #We want only one column and sets location of the key
-                  scales=list(cex=0.75, #controls text size on scales.
-                              tck=-0.5, #controls tick mark length. < 0 for inside the graph.
+                           columns=keyColumns, x=keyXLoc, y=keyYLoc), #controls columns and position of the key
+                  scales=list(cex=scaleTextSize, #controls text size on scales.
+                              tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
                               y=list(at=c(1,2,3,4,5,6,7,8,9,10))), #tick mark locations
@@
 }
-createFactorsLatticeGraph("All") #Reads data from the "AllData.txt" file.
+createFactorsLatticeGraph()
 @
@@
 # Takes the Cobb-Douglas fitted models and creates a single column of predicted GDP values
-# that corresponds to the AllData.txt file.
+# that corresponds, row for row, with the AllData.txt file.
 ##
@@
 
-<<CD Lattice Graph>>=
+<<US_CD_Graph>>=
 usModel <- cobbDouglasModel("US")
-coefs <- coef(usModel)
 # print(coef(usModel))
 usPred <- predict(usModel) #See http://stackoverflow.com/questions/9918807/how-get-plot-from-nls-in-r
-class(usPred)
 #print(usPred)
@@
 
-allData <- loadData("All")
-predictions <- cobbDouglasPredictionsColumn()
-allData <- cbind(allData, predictions)
+# allData <- loadData("All")
+# predictions <- cobbDouglasPredictionsColumn()
+# allData <- cbind(allData, predictions)
+# 
+# print(allData)
+@
 
-print(allData)
+<<CD_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.cap="Cobb-Douglas model results.", echo=FALSE>>=
+createCDLatticeGraph <- function(){
+  dataTable <- loadData("All") #Grab the raw data
+  predictions <- cobbDouglasPredictionsColumn() #Get the predictions from the models
+  dataTable <- cbind(dataTable, predictions) #Now add the predictions column to the data. Column name = "predGDP".
+  graphType <- "b" #b is for both line and symbol
+  lineTypes <- c(0, 1) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
+  lineWidths <- c(0, 1) #line widths. 0 means no line.
+  colors <- c("black", "black") #line and symbol colors
+  symbols <- c(1, NA)  #NA gives no symbol.
+  graph <- xyplot(iGDP+predGDP ~ Year | Country, data=dataTable,
+                  type=graphType,
+                  index.cond=list(countryOrderForGraphs), #orders the panels.
+                  layout=layoutSpec, #indicates a 3x3 arrangement of panels.
+                  as.table=TRUE, #indexing of panels starts in upper left and goes across rows.
+                  lty = lineTypes, lwd = lineWidths, col = colors, #Controls line parameters
+                  pch = symbols, col.symbol = colors, #Controls symbol parameters
+                  key=list(text=list(c("y", "y_pred")),
+                           type=graphType,
+                           cex=keyTextSize, #controls size of text in the key
+                           lines=list(lty=lineTypes, lwd=lineWidths), #controls line types
+                           pch=symbols, col=colors, #controls symbol (plot characters) types
+                           columns=keyColumns, x=keyXLoc, y=keyYLoc), #controls columns and position of the key
+                  scales=list(cex=scaleTextSize, #controls text size on scales.
+                              tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
+                              y=list(at=c(1,2,3,4,5,6,7,8,9,10))), #tick mark locations
+                  ylim=c(0.5,4.5), #y axis limits
+                  xlab="", ylab="Indexed (1980=1 or 1991=1)") #axis labels
+  return(graph)
+}
+createCDLatticeGraph()
 @

### 2013-01-31 EconGrowth.Rnw
Now generating a comparison between predicted and actual GDP for all countries in a lattice graph.

@@
 # List of countries
-countries <- c(US="US", UK="UK", JP="JP", CN="CN", ZA = "ZA", SA="SA", IR="IR", TZ="TZ", ZM="ZM")
+countryAbbrevs <- c(US="US", UK="UK", JP="JP", CN="CN", ZA="ZA", SA="SA", IR="IR", TZ="TZ", ZM="ZM")
+countryNamesAlph <- c(CN="China", IR="Iran", JP="Japan", SA="Saudi Arabia", TZ="Tanzania", UK="United Kingdom", US="USA", ZA="South Africa", ZM="Zambia") #In alphabetical order.
+
 # Set the order for presenting countries in 3x3 lattice graphs. Default is alphabetical. "1" means first alphabetically.
@@
 # List of energy types
-energyTypes <- c(Q = "Q", X = "X", U = "U")
+energyTypes <- c(Q="Q", X="X", U="U")
 @
@@
 
-<<Country Factors Graph, echo=FALSE>>=
-createCountryFactorsGraph <- function(countryName){
-  dataTable <- loadData(countryName)
-  graphType <- "l"
-  lineTypes <- c(1, 5, 2, 4, 6) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
-  lineWidths <- c(1, 1, 1, 1, 1) #line widths
-  colors <- c("black", "black", "black", "black", "black") #line and point colors
-  lineSpec <- list(lty=lineTypes, lwd=lineWidths, col=colors)
-  graph <- xyplot(iCapStk+iLabor+iQ+iX+iU ~ Year, data=dataTable,
-                  type=graphType,
-                  par.settings = list(superpose.line = lineSpec),
-                  key=list(text=list(c("k", "l", "q", "x", "u")),
-                           type=graphType,
-                           lines=lineSpec,
-                           columns=1, x=0.0, y=0.98),
-                  scales=list(cex=1.0, #controls text size on scales
-                              tck=scaleTickSize), #controls tick mark length
-                  ylab="Indexed (1980=1)")
-  return(graph)
-}
-@
 <<Factors_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.cap="GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$) for all economies.
@@
   graph <- xyplot(iGDP+iCapStk+iLabor+iQ+iX+iU ~ Year | Country, data=dataTable,
-                  type=graphType,
-                  index.cond=list(countryOrderForGraphs), #orders the panels.
-                  layout=layoutSpec, 
-                  as.table=TRUE, #indexing of panels starts in upper left and goes across rows.
+                  type = graphType,
+                  index.cond = list(countryOrderForGraphs), #orders the panels.
+                  layout = layoutSpec, 
+                  strip = strip.custom(factor.levels=countryNamesAlph, bg="white"),
+                  as.table = TRUE, #indexing of panels starts in upper left and goes across rows.
                   lty = lineTypes, lwd = lineWidths, col = colors, #Controls line parameters
@@
   model <- cobbDouglasModel(countryName)
-  coefs <- coef(usModel)
   pred <- predict(model) #See http://stackoverflow.com/questions/9918807/how-get-plot-from-nls-in-r
-  return(data.frame(pred))
+  df <- data.frame(pred)
+  # There are two countries which do not have labor data for 2011. Need to add a "NA" for 2011 for those countries.
+  if (countryName == "CN" || countryName == "ZA"){
+    dfNA <- data.frame(NA)
+    colnames(dfNA) <- "pred" #Need to give it the same name so that we can apply rbind
+    df <- rbind(df, dfNA)
+  }
+  return(df)
 }
@@
 cobbDouglasPredictionsColumn <- function(){
-  preds <- lapply(countries, cobbDouglasPredictions)
+  preds <- lapply(countryAbbrevs, cobbDouglasPredictions)
   out <- rbind(preds[["US"]], preds[["UK"]], preds[["JP"]], preds[["CN"]], preds[["ZA"]], preds[["SA"]], preds[["IR"]], preds[["TZ"]], preds[["ZM"]])
   colnames(out) <- c("predGDP")
-  print(out)
   return(out)
@@
                         " ", "$\\beta$",   " ")
-  rownames(dataCD) <- countries
+  rownames(dataCD) <- countryAbbrevs
   tableCD <- xtable(dataCD, 
@@
 
-<<US_CD_Graph>>=
-usModel <- cobbDouglasModel("US")
-# print(coef(usModel))
-usPred <- predict(usModel) #See http://stackoverflow.com/questions/9918807/how-get-plot-from-nls-in-r
-#print(usPred)
-data.frame(usPred)
-
-# allData <- loadData("All")
-# predictions <- cobbDouglasPredictionsColumn()
-# allData <- cbind(allData, predictions)
-# 
-# print(allData)
-@
-
-<<CD_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.cap="Cobb-Douglas model results.", echo=FALSE>>=
+<<CD_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.cap="Cobb-Douglas (without energy) results.", echo=FALSE>>=
 createCDLatticeGraph <- function(){
@@
                   layout=layoutSpec, #indicates a 3x3 arrangement of panels.
+                  strip = strip.custom(factor.levels=countryNamesAlph, bg="white"),
                   as.table=TRUE, #indexing of panels starts in upper left and goes across rows.
@@
                   pch = symbols, col.symbol = colors, #Controls symbol parameters
-                  key=list(text=list(c("y", "y_pred")),
+                  key=list(text=list(c("Actual", "Predicted")),
                            type=graphType,
@@
                               y=list(at=c(1,2,3,4,5,6,7,8,9,10))), #tick mark locations
-                  ylim=c(0.5,4.5), #y axis limits
-                  xlab="", ylab="Indexed (1980=1 or 1991=1)") #axis labels
+                  ylim=c(0.5,8), #y axis limits
+                  xlab="", ylab="Indexed GDP (1980=1 or 1991=1)") #axis labels
   return(graph)
@@
 # Note that the anlaysis of ZA is taking a long time here. Need to figure out why.
-CDqTables <- lapply(countries, cobbDouglasEnergyTable, energyType="Q")
+CDqTables <- lapply(countryAbbrevs, cobbDouglasEnergyTable, energyType="Q")
 @
@@
 # Note that the anlaysis of ZA is taking a long time here. Need to figure out why.
-CDxTables <- lapply(countries, cobbDouglasEnergyTable, energyType="X")
+CDxTables <- lapply(countryAbbrevs, cobbDouglasEnergyTable, energyType="X")
 @
@@
 <<CDu analysis, eval=FALSE>>=
-CDuTables <- lapply(countries, cobbDouglasEnergyTable, energyType="U")
+CDuTables <- lapply(countryAbbrevs, cobbDouglasEnergyTable, energyType="U")
 @
@@
 
-#CESqTables <- lapply(countries, cesTable, energyType="Q")
+#CESqTables <- lapply(countryAbbrevs, cesTable, energyType="Q")
 @

### 2013-02-01 EconGrowth.Rnw
Working on a plot that will show the parameters from the Cobb-Douglas curve fits (lambda, alpha, beta). Still not working yet.

@@
 require(lattice)
+require(latticeExtra)
 require(ggplot2)
@@
 <<Factors_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.cap="GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$) for all economies.
-(China's indexed GDP and indexed capital stock rise to $y = 7.3$ and $k = 9.2$ in 2011.)", echo=FALSE>>=
+(China's indexed GDP and indexed capital stock rise to $y = 7.3$ and $k = 9.2$ in 2011.)", echo=FALSE, eval=FALSE>>=
 createFactorsLatticeGraph <- function(){
@@
   lineWidths <- c(0, 2, 2, 1, 1, 1) #line widths. 0 means no line.
-  colors <- c("black", "black", "black", "red", "blue", "black") #line and symbol colors
+  colors <- c("black", "black", "black", "red", "blue", "darkorange") #line and symbol colors
   symbols <- c(1, NA, NA, NA, NA, NA)  #NA gives no symbol.
@@
                   layout = layoutSpec, 
-                  strip = strip.custom(factor.levels=countryNamesAlph, bg="white"),
+                  strip = strip.custom(factor.levels=countryNamesAlph, bg="white"), #Sets strip parameters
                   as.table = TRUE, #indexing of panels starts in upper left and goes across rows.
@@
 
+cobbDouglasCountryRowsForParamsGraph <- function(countryName){
+  dataCD <- cobbDouglasData(countryName)
+  #Create three rows, one for each parameter.
+  lambdaRow <- cbind(dataCD["- 95% CI", "lambda"], 
+                     dataCD["CD", "lambda"], 
+                     dataCD["+ 95% CI", "lambda"], 
+                     countryName, 
+                     "lambda")
+  alphaRow <- cbind(dataCD["- 95% CI", "alpha"],
+                    dataCD["CD", "alpha"],  
+                    dataCD["+ 95% CI", "alpha"],
+                    countryName,
+                    "alpha")
+  betaRow <- cbind(dataCD["- 95% CI", "beta"],   
+                   dataCD["CD", "beta"],   
+                   dataCD["+ 95% CI", "beta"],
+                   countryName,
+                   "beta")
+  #Now combine into a table
+  table <- rbind(lambdaRow, alphaRow, betaRow)
+  colnames(table) <- c("- 95% CI", "value", "+ 95% CI", "country", "parameter")
+  return(table)
+}
+
 ############################
@@
 
-<<CD Results, results='asis', echo=FALSE>>=
+<<CD Params Table, results='asis', echo=FALSE, eval=FALSE>>=
 print(cobbDouglasParamsTable(), caption.placement="top", sanitize.colnames.function = identity)
@@
 
-<<CD_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.cap="Cobb-Douglas (without energy) results.", echo=FALSE>>=
+<<CD_Params_Graph, fig.width=figWidth, fig.height=figHeight, fig.cap="Cobb-Douglas (without energy) model parameters.">>=
+createCDParamsGraph <- function(){
+  # Create the data table that we want. This table has the following columns
+  # -95% CI, value, +95% CI, country abbrev, parameter (lambda, alpha, or beta)
+  dataTable <- do.call("rbind", lapply(countryAbbrevs, cobbDouglasCountryRowsForParamsGraph))
+
+  print(dataTable)
+
+  graph <- segplot(value ~ country | parameter, centers=value, data=dataTable)  
+  return(graph)
+
+}
+
+createCDParamsGraph()
+
+@
+
+<<CD_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.cap="Cobb-Douglas (without energy) results.", echo=FALSE, eval=FALSE>>=
 createCDLatticeGraph <- function(){
@@
                   layout=layoutSpec, #indicates a 3x3 arrangement of panels.
-                  strip = strip.custom(factor.levels=countryNamesAlph, bg="white"),
+                  strip = strip.custom(factor.levels=countryNamesAlph, bg="white"), #Sets strip parameters
                   as.table=TRUE, #indexing of panels starts in upper left and goes across rows.
@@
 
-<<cobbDouglasEnergy function, include=TRUE, echo=FALSE>>=
+<<cobbDouglasEnergy function, include=TRUE, echo=FALSE, eval=FALSE>>=
 ###############################
@@
 \subsection{CES with $Q$}
-<<CESq analysisQ>>=
+<<CESq analysisQ, eval=FALSE>>=
 countryName <- "US"
@@
 
-<<CESq Results, results='asis'>>=
+<<CESq Results, results='asis', eval=FALSE>>=
 print(tableCESq, caption.placement="top")

### 2013-02-01 EconGrowth.Rnw
Attempting to draw a parameters graph for the CD model. Not working yet.

@@
 
+###########################################
+# Creates a number of rows in a data.frame that contain information 
+# about the coefficients of a Cobb-Douglas model for countryName.
+# Each parameter has its own row with confidence intervals.
+# The country name is in a column. Which parameter is involved is
+# also in a column.
+# 
+# The return type is a data.frame.
+##
 cobbDouglasCountryRowsForParamsGraph <- function(countryName){
@@
   #Create three rows, one for each parameter.
-  lambdaRow <- cbind(dataCD["- 95% CI", "lambda"], 
+  lambdaRow <- cbind(countryName,
+                     "lambda",
+                     dataCD["- 95% CI", "lambda"], 
                      dataCD["CD", "lambda"], 
-                     dataCD["+ 95% CI", "lambda"], 
-                     countryName, 
-                     "lambda")
-  alphaRow <- cbind(dataCD["- 95% CI", "alpha"],
+                     dataCD["+ 95% CI", "lambda"])
+  alphaRow <- cbind(countryName, 
+                    "alpha",
+                    dataCD["- 95% CI", "alpha"],
                     dataCD["CD", "alpha"],  
-                    dataCD["+ 95% CI", "alpha"],
-                    countryName,
-                    "alpha")
-  betaRow <- cbind(dataCD["- 95% CI", "beta"],   
+                    dataCD["+ 95% CI", "alpha"])
+  betaRow <- cbind(countryName, 
+                   "beta",
+                   dataCD["- 95% CI", "beta"],   
                    dataCD["CD", "beta"],   
-                   dataCD["+ 95% CI", "beta"],
-                   countryName,
-                   "beta")
-  #Now combine into a table
+                   dataCD["+ 95% CI", "beta"])
+  #Now combine into a table. table is a matrix, not a data.frame.
   table <- rbind(lambdaRow, alphaRow, betaRow)
-  colnames(table) <- c("- 95% CI", "value", "+ 95% CI", "country", "parameter")
-  return(table)
+  #Set names for the columns
+  colnames(table) <- c("country", "parameter", "lowerCI", "value", "upperCI")
+  #Convert the matrix to a data.frame and return it.
+  return(data.frame(table))
 }
@@
 cobbDouglasParamsTable <- function(){
-  dataCD <- rbind(cobbDouglasCountryRow("US"),
-                cobbDouglasCountryRow("UK"),
-                cobbDouglasCountryRow("JP"),
-                cobbDouglasCountryRow("CN"),
-                cobbDouglasCountryRow("ZA"),
-                cobbDouglasCountryRow("SA"),
-                cobbDouglasCountryRow("IR"),
-                cobbDouglasCountryRow("TZ"),
-                cobbDouglasCountryRow("ZM"))
+  #Do rbind on the results of creating a row in the table for every country abbreviation that we know.
+  dataCD <- do.call("rbind", lapply(countryAbbrevs, cobbDouglasCountryRow))
   colnames(dataCD) <- c(" ", "$\\lambda$", " ", 
@@
                     digit = c(1, 4,4,4, 2,2,2, 2,2,2),
-                    align = "r|ccc|ccc|ccc")
+                    align = "r|ccc|ccc|ccc") #Sets alignment of the numbers in the columns
   return(tableCD)
@@
 createCDParamsGraph <- function(){
-  # Create the data table that we want. This table has the following columns
-  # -95% CI, value, +95% CI, country abbrev, parameter (lambda, alpha, or beta)
-  dataTable <- do.call("rbind", lapply(countryAbbrevs, cobbDouglasCountryRowsForParamsGraph))
-
+  # Create a data table with the following columns:
+  # country abbrev, parameter (lambda, alpha, or beta), -95% CI, value, +95% CI
+  dataTable <- do.call("rbind", 
+                       lapply(countryAbbrevs, 
+                              cobbDouglasCountryRowsForParamsGraph))
+  print(class(dataTable))
   print(dataTable)
-
-  graph <- segplot(value ~ country | parameter, centers=value, data=dataTable)  
+  # Make a graph. I want the following:
+  ### two-letter country abbreviation on the horizontal axis
+  ### dots for the values of each parameter
+  ### error bars to the top and bottom of the dots representing the 95% CI
+  ### three panels, one for each parameter (lambda, alpha, and beta)
+  #
+  # Note that "segplot" is in the "latticeExtra" package.
+  # But, at this point, I obtain the following error:
+  # "Error:  range not meaningful for factors"
+  graph <- segplot(country ~ upperCI + lowerCI | parameter, 
+                   data = dataTable, 
+                   centers = value)
   return(graph)
-
 }
-
 createCDParamsGraph()
-
 @
@@
 
-<<CDq analysis, eval=FALSE>>=
+<<CDq analysis, echo=FALSE, eval=FALSE>>=
 # Note that the anlaysis of ZA is taking a long time here. Need to figure out why.
@@
 
-<<CDq Results, results='asis', echo=TRUE, eval=FALSE>>=
+<<CDq Results, results='asis', echo=FALSE, eval=FALSE>>=
 print(CDqTables[["US"]], caption.placement="top")
@@
 
-<<CDx analysis, eval=FALSE>>=
+<<CDx analysis, echo=FALSE, eval=FALSE>>=
 # Note that the anlaysis of ZA is taking a long time here. Need to figure out why.
@@
 
-<<CDx Results, results='asis', eval=FALSE>>=
+<<CDx Results, results='asis', echo=FALSE, eval=FALSE>>=
 print(CDxTables[["US"]], caption.placement="top")
@@
 
-<<CDu analysis, eval=FALSE>>=
+<<CDu analysis, echo=FALSE, eval=FALSE>>=
 CDuTables <- lapply(countryAbbrevs, cobbDouglasEnergyTable, energyType="U")
@@
 
-<<CDu Results, results='asis', eval=FALSE>>=
+<<CDu Results, results='asis', echo=FALSE, eval=FALSE>>=
 print(CDuTables[["US"]], caption.placement="top")
@@
 
-<<CES function>>=
+<<CES function, echo=FALSE, eval=FALSE>>=
 cesData <- function(countryName, energyType){
@@
 \subsection{CES with $Q$}
-<<CESq analysisQ, eval=FALSE>>=
+<<CESq analysisQ, echo=FALSE, eval=FALSE>>=
 countryName <- "US"
@@
 
-<<CESq Results, results='asis', eval=FALSE>>=
+<<CESq Results, results='asis', echo=FALSE, eval=FALSE>>=
 print(tableCESq, caption.placement="top")

### 2013-02-01 EconGrowth.Rnw
Now doing str(dataTable) to see what is going on inside the data.frame.

@@
   print(dataTable)
+  print(str(dataTable))
   # Make a graph. I want the following:
@@
                    centers = value)
+  segplot(reorder(factor(county), rate.male) ~ LCL95.male + UCL95.male, 
+          data = subset(USCancerRates, state == "Washington"), 
+          draw.bands = FALSE, 
+          centers = rate.male)
   return(graph)

### 2013-02-01 EconGrowth.Rnw
Now correctly creating data.frames for each country. This allows us to draw a graph of values and undertainties for each coefficient in the Cobb-Douglas model.

@@
   modelCD <- cobbDouglasModel(countryName)
-
   # Checks validity of the model. AIC stands for Akaike's Information Criterion.
   aicCD  <- AIC(modelCD, k=2)
-  #print(aicCD)
-
   summaryCD <- summary(modelCD) # Gives the nls summary table.
   #print(summaryCD)
-  ciCD <- confint(modelCD, level = ciLevel); ciCD # Displays confidence intervals for the CD model.
-
+  ciCD <- confint(modelCD, level = ciLevel); ciCD # Calculates confidence intervals for the CD model.
   # Calculate beta and its confidence interval and report it.
@@
   betaCICD <- with(beta.est, Estimate + c(-1.0, 1.0) * tvalCD * SE); betaCICD # Gives the confidence interval on beta.  
-
-  #print(coef(modelCD))
-
   # Combine all estimates and their confidence intervals into data frames with intelligent row names
@@
   lowerCD <- data.frame(lambda = ciCD["lambda","2.5%"], alpha = ciCD["alpha", "2.5%"], beta = betaCICD[1], gamma = NA) 
-  row.names(lowerCD) <- "- 95% CI"
+  row.names(lowerCD) <- "-95% CI"
   # The [2] subscripts pick off the lower confidence interval
   upperCD <- data.frame(lambda = ciCD["lambda","97.5%"], alpha = ciCD["alpha", "97.5%"], beta = betaCICD[2], gamma = NA)
-  row.names(upperCD) <- "+ 95% CI"
-
+  row.names(upperCD) <- "+95% CI"
   # Now create the data for a table.
   dataCD <- rbind(upperCD, estCD, lowerCD)
-  #print(dataCD)
   return(dataCD)
@@
   # Create CI ranges
-  out <- cbind(dataCD["- 95% CI", "lambda"], dataCD["CD", "lambda"], dataCD["+ 95% CI", "lambda"],
-               dataCD["- 95% CI", "alpha"],  dataCD["CD", "alpha"],  dataCD["+ 95% CI", "alpha"],
-               dataCD["- 95% CI", "beta"],   dataCD["CD", "beta"],   dataCD["+ 95% CI", "beta"])
+  out <- cbind(dataCD["-95% CI", "lambda"], dataCD["CD", "lambda"], dataCD["+95% CI", "lambda"],
+               dataCD["-95% CI", "alpha"],  dataCD["CD", "alpha"],  dataCD["+95% CI", "alpha"],
+               dataCD["-95% CI", "beta"],   dataCD["CD", "beta"],   dataCD["+95% CI", "beta"])
   return(out)
@@
   dataCD <- cobbDouglasData(countryName)
-  #Create three rows, one for each parameter.
-  lambdaRow <- cbind(countryName,
-                     "lambda",
-                     dataCD["- 95% CI", "lambda"], 
-                     dataCD["CD", "lambda"], 
-                     dataCD["+ 95% CI", "lambda"])
-  alphaRow <- cbind(countryName, 
-                    "alpha",
-                    dataCD["- 95% CI", "alpha"],
-                    dataCD["CD", "alpha"],  
-                    dataCD["+ 95% CI", "alpha"])
-  betaRow <- cbind(countryName, 
-                   "beta",
-                   dataCD["- 95% CI", "beta"],   
-                   dataCD["CD", "beta"],   
-                   dataCD["+ 95% CI", "beta"])
-  #Now combine into a table. table is a matrix, not a data.frame.
+  #Create three rows, one for each parameter. Each row is a data.frame so that it is plottable!
+  lambdaRow <- data.frame(country = countryName, 
+                          parameter = "lambda", 
+                          lowerCI = dataCD["-95% CI", "lambda"], 
+                          value = dataCD["CD", "lambda"], 
+                          upperCI = dataCD["+95% CI", "lambda"])
+  alphaRow <- data.frame(country = countryName, 
+                         parameter = "alpha",
+                         lowerCI = dataCD["-95% CI", "alpha"],
+                         value = dataCD["CD", "alpha"],  
+                         upperCI = dataCD["+95% CI", "alpha"])
+  betaRow <- data.frame(country = countryName, 
+                        parameter = "beta",
+                        lowerCI = dataCD["-95% CI", "beta"],
+                        value = dataCD["CD", "beta"], 
+                        upperCI = dataCD["+95% CI", "beta"])
   table <- rbind(lambdaRow, alphaRow, betaRow)
-  #Set names for the columns
-  colnames(table) <- c("country", "parameter", "lowerCI", "value", "upperCI")
-  #Convert the matrix to a data.frame and return it.
-  return(data.frame(table))
+  return(table)
 }

### 2013-02-01 EconGrowth.Rnw
No obtaining different scales for each sub-graph in the Cobb-Douglas parameters graph.

@@
 
-<<CD_Params_Graph, fig.width=figWidth, fig.height=figHeight, fig.cap="Cobb-Douglas (without energy) model parameters.">>=
+<<CD_Params_Graph, fig.width=figWidth, fig.height=3.0, fig.cap="Cobb-Douglas (without energy) model parameters.", echo=FALSE>>=
 createCDParamsGraph <- function(){
@@
   # country abbrev, parameter (lambda, alpha, or beta), -95% CI, value, +95% CI
-  dataTable <- do.call("rbind", 
-                       lapply(countryAbbrevs, 
-                              cobbDouglasCountryRowsForParamsGraph))
-  print(class(dataTable))
-  print(dataTable)
-  print(str(dataTable))
-  # Make a graph. I want the following:
-  ### two-letter country abbreviation on the horizontal axis
-  ### dots for the values of each parameter
-  ### error bars to the top and bottom of the dots representing the 95% CI
-  ### three panels, one for each parameter (lambda, alpha, and beta)
-  #
-  # Note that "segplot" is in the "latticeExtra" package.
-  # But, at this point, I obtain the following error:
-  # "Error:  range not meaningful for factors"
+  dataTable <- do.call("rbind", lapply(countryAbbrevs, cobbDouglasCountryRowsForParamsGraph))
+
   graph <- segplot(country ~ upperCI + lowerCI | parameter, 
                    data = dataTable, 
-                   centers = value)
-  segplot(reorder(factor(county), rate.male) ~ LCL95.male + UCL95.male, 
-          data = subset(USCancerRates, state == "Washington"), 
-          draw.bands = FALSE, 
-          centers = rate.male)
+                   centers = value, #identifies where the dots should be placed
+                   draw.bands = FALSE, #provides nicer error bars
+                   horizontal = FALSE, #makes error bars vertical
+                   layout = c(3,1), #3 column, 1 row
+                   strip = strip.custom(bg="white"), #Sets strip parameters
+                   scales=list(cex=scaleTextSize, #controls text size on scales.
+                               tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
+                               y=list(at=c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0), #tick mark locations on y axis
+                                      relation="free")), #allow free relations of axis limits?
+                   ylim=list(c(-0.1,0.2), c(-0.5, 1.5), c(-0.5, 1.5)) #y axis limits
+                   ) 
   return(graph)

### 2013-02-02 EconGrowth.Rnw
Formatting for the C-D fit parameters graph.

@@
 
-<<CD_Params_Graph, fig.width=figWidth, fig.height=3.0, fig.cap="Cobb-Douglas (without energy) model parameters.", echo=FALSE>>=
+<<CD_Params_Graph, fig.width=figWidth, fig.height=3.5, fig.cap="Cobb-Douglas (without energy) model parameters.", echo=FALSE>>=
 createCDParamsGraph <- function(){
@@
                    draw.bands = FALSE, #provides nicer error bars
-                   horizontal = FALSE, #makes error bars vertical
+                   horizontal = FALSE, #makes error bars vertical and puts the countries in the x axis
                    layout = c(3,1), #3 column, 1 row
                    strip = strip.custom(bg="white"), #Sets strip parameters
-                   scales=list(cex=scaleTextSize, #controls text size on scales.
+                   col = "black", #Sets line color to black
+                   lwd = 1, #Sets line width to 1.0
+                   ylim = list(c(-0.05, 0.1), c(-0.5, 1.5), c(-0.5, 1.5)), #y axis limits
+                   scales = list(cex=scaleTextSize, #controls text size on scales.
                                  tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
-                               y=list(at=c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0), #tick mark locations on y axis
-                                      relation="free")), #allow free relations of axis limits?
-                   ylim=list(c(-0.1,0.2), c(-0.5, 1.5), c(-0.5, 1.5)) #y axis limits
+                                 y=list(relation="free",                        #allow each axis to be different
+                                        at=list(c(0.0, 0.05, 0.1),   #tick mark locations on y axis
+                                                c(0.0, 0.5, 1.0), 
+                                                c(0.0, 0.5, 1.0)
+                                                )
+                                        )
+                                 )
                    )

### 2013-02-02 EconGrowth.Rnw
Cobb-Douglas graphs are all pretty much what I want.

@@
 
-<<setup, include=FALSE>>=
+<<setup, include=FALSE, echo=FALSE>>=
 require(knitr)
@@
   tidy=FALSE,
-  fig.width=6,
-  fig.height=4,
   comment=NA)
@@
 
-<<Load Data, include=FALSE>>=
+<<Load Data, include=FALSE, echo=FALSE>>=
 #################################
@@
 
-<<Factors_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.cap="GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$) for all economies.
-(China's indexed GDP and indexed capital stock rise to $y = 7.3$ and $k = 9.2$ in 2011.)", echo=FALSE, eval=FALSE>>=
+<<Factors_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.cap="Indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$) for all economies.
+(China's indexed GDP and indexed capital stock rise to $y = 7.3$ and $k = 9.2$ in 2011.)", echo=FALSE>>=
 createFactorsLatticeGraph <- function(){
@@
 
-####################################
-# Creates a LaTeX printable table from the Cobb Douglas data. This function first calls cobbDouglasData.
-#
-# countryName is a string containint the 2-letter abbreviation for the country, e.g. "US" or "CN"
-#
-# returns a printable LaTeX table from xtable.
-##
-cobbDouglasCountryTable <- function(countryName){
-  dataCD <- cobbDouglasData(countryName) 
-  colnames(dataCD) <- c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$")
-  tableCD <- xtable(dataCD, caption=paste(countryName, " Cobb-Douglas, 1980-2011", sep=""), digit = c(4, 4, 2, 2, 1))
-  #print(tableCD)
-  return(tableCD)  
-}
-
 ############
@@
   tableCD <- xtable(dataCD, 
-                    caption="Cobb-Douglas parameters for 1980-2011 (US, UK, JP) or 1991-2011 (others). (Parameter estimates beneath symbol. 95\\% confidence bounds to left and right.)", 
+                    caption="Cobb-Douglas parameters for 1980-2011 (US, UK, JP) or 1991-2011 (others). (Parameter estimates beneath symbol. 95\\% confidence interval bounds to left and right.)", 
                     digit = c(1, 4,4,4, 2,2,2, 2,2,2),
@@
 
-<<CD Params Table, results='asis', echo=FALSE, eval=FALSE>>=
+<<CD Params Table, results='asis', echo=FALSE>>=
 print(cobbDouglasParamsTable(), caption.placement="top", sanitize.colnames.function = identity)
@@
                    layout = c(3,1), #3 column, 1 row
-                   strip = strip.custom(bg="white"), #Sets strip parameters
+                   strip = strip.custom(factor.levels=c(expression(italic(lambda)), #sets labels in strip
+                                                        expression(italic(alpha)),
+                                                        expression(italic(beta))
+                                                        ), 
+                                        bg="white"), #sets background color in strip
                    col = "black", #Sets line color to black
@@
 
-<<CD_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.cap="Cobb-Douglas (without energy) results.", echo=FALSE, eval=FALSE>>=
+<<CD_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.cap="Cobb-Douglas (without energy) results.", echo=FALSE>>=
 createCDLatticeGraph <- function(){

### 2013-02-02 EconGrowth.Rnw
Cleaned up the code prior to beginning the process of adding energy terms to the Cobb-Douglas model.

@@
 cobbDouglasPredictionsColumn <- function(){
-  preds <- lapply(countryAbbrevs, cobbDouglasPredictions)
-  out <- rbind(preds[["US"]], preds[["UK"]], preds[["JP"]], preds[["CN"]], preds[["ZA"]], preds[["SA"]], preds[["IR"]], preds[["TZ"]], preds[["ZM"]])
+  out <- do.call("rbind", lapply(countryAbbrevs, cobbDouglasPredictions)) #rbinds all the predictions together
   colnames(out) <- c("predGDP")
@@
   summaryCD <- summary(modelCD) # Gives the nls summary table.
-  #print(summaryCD)
   ciCD <- confint(modelCD, level = ciLevel); ciCD # Calculates confidence intervals for the CD model.
@@
   estCD <- data.frame(lambda = coef(modelCD)["lambda"], alpha = coef(modelCD)["alpha"], beta = beta, gamma = 0)
-  #print(estCD)
   row.names(estCD) <- "CD"
-  #row.names(estCD) <- "Cobb-Douglas: $y = e^{\\lambda t}k^{\\alpha}l^{\\beta}$"
   # The [1] subscripts pick off the lower confidence interval
@@
 
-<<CD_Params_Graph, fig.width=figWidth, fig.height=3.5, fig.cap="Cobb-Douglas (without energy) model parameters.", echo=FALSE>>=
+<<CD_Params_Graph, fig.width=figWidth, fig.height=3.5, fig.cap="Cobb-Douglas (without energy) model parameters. Vertical bars indicate 95\\% confidence intervals.", echo=FALSE>>=
 createCDParamsGraph <- function(){

### 2013-02-02 EconGrowth.Rnw
More code cleanup prior to making graphs for CD with energy.

@@
 cobbDouglasModel <- function(countryName){
-  # Load the data that we need.
-  dataTable <- loadData(countryName)
-
+  dataTable <- loadData(countryName) #Load the data that we need.
   # Establish guess values for alpha and lambda.
-  lambdaGuess <- 0.0 # guessing lambda = 0 means there is no technological progress.
-  alphaGuess <- 0.3 # a typical value for alpha, the coefficient on capital stock
-
+  lambdaGuess <- 0.0 #guessing lambda = 0 means there is no technological progress.
+  alphaGuess <- 0.7 #0.7 gives good results for all countries.
   # Runs a non-linear least squares fit to the data. We've replaced beta with 1-alpha for simplicity.
   modelCD <- nls(iGDP ~ exp(lambda*iYear) * iCapStk^alpha * iLabor^(1 - alpha), 
-#                 algorithm = "port",
+                 data=dataTable, 
                  start = list(lambda=lambdaGuess, alpha=alphaGuess),
-#                 lower = list(lambda=-Inf, alpha=0),
-#                 upper = list(lambda=Inf, alpha=1),
-                 data=dataTable)
+                 algorithm = "port",
+                 lower = list(lambda=-Inf, alpha=0), #constraints on lambda and alpha
+                 upper = list(lambda=Inf, alpha=1)
+                 )
   return(modelCD)

### 2013-02-02 EconGrowth.Rnw
Trying to make a CD predictions column that accounts for energy, but failing so far.

@@
 # Returns an nls Cobb-Douglas model for the country specified
+# Give an energyType ("Q", "X", or "U") if you want to include an energy term
 ##
-cobbDouglasModel <- function(countryName){
-  dataTable <- loadData(countryName) #Load the data that we need.
+cobbDouglasModel <- function(countryAbbrev, energyType){
+  dataTable <- loadData(countryAbbrev) #Load the data that we need.
+
+  betaGuess <- 0.3 #if needed
+  #Run the non-linear least squares fit to the data.
+  if (missing(energyType)){
+    # No energy term
     # Establish guess values for alpha and lambda.
@@
                    data=dataTable, 
+                   algorithm = "port",
                    start = list(lambda=lambdaGuess, alpha=alphaGuess),
+                   lower = list(lambda=-Inf, alpha=0), #constraints on lambda and alpha
+                   upper = list(lambda=Inf, alpha=1))
+    return(modelCD)
+  } else {
+    energyColumnName <- paste("i", energyType, sep="")
+    iEnergy <- dataTable[energyColumnName] #grabs the desired energy column
+    # Reparameterize to ensure that we meet the constraints:
+    # * alpha + beta + gamma = 1.0.
+    # * alpha, beta, and gamma are all between 0.0 and 1.0.
+    # To do this, we reparameterize as
+    # * 0 < a < 1
+    # * 0 < b < 1
+    # * alpha = min(a, b)
+    # * beta = b - a
+    # * gamma = 1 - max(a, b)
+    # Establish guess values for lambda, alpha, and beta.
+    lambdaGuess <- 0.0 #guessing lambda = 0 means there is no technological progress.
+    alphaGuess <- 0.4 
+    betaGuess <- 1.0 - alphaGuess
+    aGuess <- alphaGuess
+    bGuess <- alphaGuess + betaGuess - 0.05
+    modelCDe <- nls(iGDP ~ exp(lambda*iYear) * iCapStk^min(a,b) * iLabor^abs(b-a) * iEnergy^(1.0 - max(a,b)), 
+                    data = dataTable,
                     algorithm = "port",
-                 lower = list(lambda=-Inf, alpha=0), #constraints on lambda and alpha
-                 upper = list(lambda=Inf, alpha=1)
-                 )
-  return(modelCD)
+                    start = list(lambda=lambdaGuess, a=aGuess, b=bGuess),
+                    lower = list(lambda=-Inf, a=0, b=0),
+                    upper = list(lambda= Inf, a=1, b=1),
+                    control = nls.control(maxiter = 200, 
+                                          tol = 1e-05, 
+                                          minFactor = 1/1024, 
+                                          printEval=TRUE, 
+                                          warnOnly=TRUE))
+    return(modelCDe)
   }
+}
+#print(lapply(countryAbbrevs, cobbDouglasModel, energyType="Q"))
+model <- cobbDouglasModel(countryAbbrev="ZM", energyType="Q")
+print(model)
+print(model$convInfo)
+#print(lapply(countryAbbrevs, cobbDouglasModel))
 
@@
 ##
-cobbDouglasPredictions <- function(countryName){
-  model <- cobbDouglasModel(countryName)
+cobbDouglasPredictions <- function(countryAbbrev, energyType){
+  model <- cobbDouglasModel(countryAbbrev, energyType)
   pred <- predict(model) #See http://stackoverflow.com/questions/9918807/how-get-plot-from-nls-in-r
@@
   # There are two countries which do not have labor data for 2011. Need to add a "NA" for 2011 for those countries.
-  if (countryName == "CN" || countryName == "ZA"){
+  if (countryAbbrev == "CN" || countryAbbrev == "ZA"){
     dfNA <- data.frame(NA)
@@
 ##
-cobbDouglasPredictionsColumn <- function(){
+cobbDouglasPredictionsColumn <- function(energyType){
+  if (missing(energyType)){
     out <- do.call("rbind", lapply(countryAbbrevs, cobbDouglasPredictions)) #rbinds all the predictions together
+  } else {
+    out <- do.call("rbind", lapply(countryAbbrevs, cobbDouglasPredictions, energyType=energyType))
+  }
   colnames(out) <- c("predGDP")

### 2013-02-02 EconGrowth.Rnw
Cleaned up chunk options in the code. Set all chunks to message=FALSE and echo=FALSE via defaults. That seems to have eliminated the "Waiting for profiling to be done..." from the final .pdf file.

@@
 
-<<setup, include=FALSE, echo=FALSE>>=
+<<setup, echo=FALSE, message=FALSE>>=
 require(knitr)
@@
   tidy=FALSE,
-  comment=NA)
+  comment=NA,
+  echo=FALSE,    #Turns off code echo for all chunks. Set TRUE on an individual chunk to see it.
+  message=FALSE) #Turns off messages for all chunks. Set TRUE on an individual chunk to see it.
 
@@
 countryAbbrevs <- c(US="US", UK="UK", JP="JP", CN="CN", ZA="ZA", SA="SA", IR="IR", TZ="TZ", ZM="ZM")
+countryAbbrevsU <- c(US="US", UK="UK", JP="JP") #Only these countries have useful work data
 countryNamesAlph <- c(CN="China", IR="Iran", JP="Japan", SA="Saudi Arabia", TZ="Tanzania", UK="United Kingdom", US="USA", ZA="South Africa", ZM="Zambia") #In alphabetical order.
-
+# List of energy types
+energyTypes <- c(Q="Q", X="X", U="U")
+########### Several global parameters for graphs. Set here and use below to ensure consistent appearance of graphs.
 # Set the order for presenting countries in 3x3 lattice graphs. Default is alphabetical. "1" means first alphabetically.
-# So, this list sets the order as US, UK, JP, CN, ZA, TZ, SA, IR, ZM.
+# The following list sets the order as US, UK, JP, CN, ZA, TZ, SA, IR, ZM.
 countryOrderForGraphs <- c(7,6,3,1,8,5,4,2,9)
@@
 scaleTickSize <- -0.5 #50% of normal size and pointing INWARD!
-# List of energy types
-energyTypes <- c(Q="Q", X="X", U="U")
 @
 
-<<Load Data, include=FALSE, echo=FALSE>>=
+<<Load Data>>=
 #################################
@@
 <<Factors_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.cap="Indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$) for all economies.
-(China's indexed GDP and indexed capital stock rise to $y = 7.3$ and $k = 9.2$ in 2011.)", echo=FALSE>>=
+(China's indexed GDP and indexed capital stock rise to $y = 7.3$ and $k = 9.2$ in 2011.)">>=
 createFactorsLatticeGraph <- function(){
@@
 
-<<cobb-douglas, echo=FALSE>>=
+<<cobb-douglas>>=
 ####################
@@
 
-<<CD Params Table, results='asis', echo=FALSE>>=
+<<CD Params Table, results='asis'>>=
 print(cobbDouglasParamsTable(), caption.placement="top", sanitize.colnames.function = identity)
@@
 
-<<CD_Params_Graph, fig.width=figWidth, fig.height=3.5, fig.cap="Cobb-Douglas (without energy) model parameters. Vertical bars indicate 95\\% confidence intervals.", echo=FALSE>>=
+<<CD_Params_Graph, fig.width=figWidth, fig.height=3.5, fig.cap="Cobb-Douglas (without energy) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
 createCDParamsGraph <- function(){
@@
 
-<<CD_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.cap="Cobb-Douglas (without energy) results.", echo=FALSE>>=
+<<CD_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.cap="Cobb-Douglas (without energy) results.">>=
 createCDLatticeGraph <- function(){
@@
 
-<<cobbDouglasEnergy function, include=TRUE, echo=FALSE, eval=FALSE>>=
+<<cobbDouglasEnergy function, eval=FALSE>>=
 ###############################
@@
 
-<<CDq analysis, echo=FALSE, eval=FALSE>>=
+<<CDq analysis, eval=FALSE>>=
 # Note that the anlaysis of ZA is taking a long time here. Need to figure out why.
@@
 
-<<CDq Results, results='asis', echo=FALSE, eval=FALSE>>=
+<<CDq Results, results='asis', eval=FALSE>>=
 print(CDqTables[["US"]], caption.placement="top")
@@
 
-<<CDx analysis, echo=FALSE, eval=FALSE>>=
+<<CDx analysis, eval=FALSE>>=
 # Note that the anlaysis of ZA is taking a long time here. Need to figure out why.
@@
 
-<<CDx Results, results='asis', echo=FALSE, eval=FALSE>>=
+<<CDx Results, results='asis', eval=FALSE>>=
 print(CDxTables[["US"]], caption.placement="top")
@@
 
-<<CDu analysis, echo=FALSE, eval=FALSE>>=
+<<CDu analysis, eval=FALSE>>=
 CDuTables <- lapply(countryAbbrevs, cobbDouglasEnergyTable, energyType="U")
@@
 
-<<CDu Results, results='asis', echo=FALSE, eval=FALSE>>=
+<<CDu Results, results='asis', eval=FALSE>>=
 print(CDuTables[["US"]], caption.placement="top")
@@
 
-<<CES function, echo=FALSE, eval=FALSE>>=
+<<CES function, eval=FALSE>>=
 cesData <- function(countryName, energyType){
@@
   return(dataCES)
-
-  #xyplot( resid(modelCESQ) ~ fitted(modelCESQ) )
-  #histogram( ~resid(modelCESQ) )
-  #qqmath( ~resid(modelCESQ) )
 }
@@
 \subsection{CES with $Q$}
-<<CESq analysisQ, echo=FALSE, eval=FALSE>>=
+<<CESq analysisQ, eval=FALSE>>=
 countryName <- "US"
@@
 
-<<CESq Results, results='asis', echo=FALSE, eval=FALSE>>=
+<<CESq Results, results='asis', eval=FALSE>>=
 print(tableCESq, caption.placement="top")

### 2013-02-04 EconGrowth.Rnw
Now creating Cobb-Douglas graph with all energy types.

@@
 require(xtable)
+require(tikzDevice) #See http://r-forge.r-project.org/R/?group_id=440 for instructions on installing tikzDevice.
 trellis.par.set(theme=theme.mosaic())
@@
 opts_chunk$set(
+  dev='tikz',    #Allows LaTeX code in graphical output. E.g., "$y$" for a variable name in the legend for a graph.
   tidy=FALSE,
@@
 keyYLoc <- 0.95 #y position of the key
-scaleTextSize <- 0.75 #75% of normal size
+scaleTextSize <- 1.0 #0.75 #75% of normal size
 scaleTickSize <- -0.5 #50% of normal size and pointing INWARD!
@@
 <<Factors_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.cap="Indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$) for all economies.
-(China's indexed GDP and indexed capital stock rise to $y = 7.3$ and $k = 9.2$ in 2011.)">>=
+(China's indexed GDP and indexed capital stock rise to $y = 7.3$ and $k = 9.2$ in 2011.)", eval=FALSE>>=
 createFactorsLatticeGraph <- function(){
@@
                   pch = symbols, col.symbol = colors, #Controls symbol parameters
-                  key=list(text=list(c("y", "k", "l", "q", "x", "u")),
+                  key=list(text=list(c("$y$", "$k$", "$l$", "$q$", "$x$", "$u$")),
                            type=graphType,
@@
   dataTable <- loadData(countryAbbrev) #Load the data that we need.
-
-  betaGuess <- 0.3 #if needed
-  #Run the non-linear least squares fit to the data.
+  #Run the non-linear least squares fit to the data based on whether we have an energy type or not.
   if (missing(energyType)){
-    # No energy term
+    # No energy term desired in the Cobb-Douglas equation.
     # Establish guess values for alpha and lambda.
@@
                    data=dataTable, 
-                   algorithm = "port",
                    start = list(lambda=lambdaGuess, alpha=alphaGuess),
-                   lower = list(lambda=-Inf, alpha=0), #constraints on lambda and alpha
-                   upper = list(lambda=Inf, alpha=1))
+                   #Include the next 3 lines to fit with constraints.
+                   #algorithm = "port",
+                   #lower = list(lambda=-Inf, alpha=0), #constraints on lambda and alpha
+                   #upper = list(lambda=Inf, alpha=1)
+                   )
     return(modelCD)
   } else {
-    energyColumnName <- paste("i", energyType, sep="")
-    iEnergy <- dataTable[energyColumnName] #grabs the desired energy column
+    # We need to do the Cobb-Douglas fit with the desired energy data.
+    # To achieve the correct fit, we'll change the name of the desired column
+    # to "iEToFit" and use "iEToFit" in the nls function. 
+    energyColumnName <- paste("i", energyType, sep="") #Energy term desired in the Cobb-Douglas equation.
+    eColIndex <- which(names(dataTable) %in% energyColumnName) #Find index of desired column
+    colnames(dataTable)[eColIndex] <- "iEToFit" #Change desired column name to "iEToFit"
     # Reparameterize to ensure that we meet the constraints:
@@
     lambdaGuess <- 0.0 #guessing lambda = 0 means there is no technological progress.
-    alphaGuess <- 0.4 
+    alphaGuess <- 0.9
     betaGuess <- 1.0 - alphaGuess
@@
     bGuess <- alphaGuess + betaGuess - 0.05
-    modelCDe <- nls(iGDP ~ exp(lambda*iYear) * iCapStk^min(a,b) * iLabor^abs(b-a) * iEnergy^(1.0 - max(a,b)), 
+    # Now actually do the fit, using the column name "iEToFit".
+    modelCDe <- nls(iGDP ~ exp(lambda*iYear) * iCapStk^min(a,b) * iLabor^abs(b-a) * iEToFit^(1.0 - max(a,b)), 
                     data = dataTable,
-                    algorithm = "port",
                     start = list(lambda=lambdaGuess, a=aGuess, b=bGuess),
-                    lower = list(lambda=-Inf, a=0, b=0),
-                    upper = list(lambda= Inf, a=1, b=1),
                     control = nls.control(maxiter = 200, 
                                           tol = 1e-05, 
-                                          minFactor = 1/1024, 
-                                          printEval=TRUE, 
-                                          warnOnly=TRUE))
+                                          minFactor = 1/4096, 
+                                          printEval=FALSE, #Tells whether to print details of curve fit process.
+                                          warnOnly=TRUE),
+                    #Include the next 3 lines to fit with constraints.
+                    #algorithm = "port",
+                    #lower = list(lambda=-Inf, a=0, b=0),
+                    #upper = list(lambda= Inf, a=1, b=1)
+                    )
     return(modelCDe)
@@
 }
-#print(lapply(countryAbbrevs, cobbDouglasModel, energyType="Q"))
-model <- cobbDouglasModel(countryAbbrev="ZM", energyType="Q")
-print(model)
-print(model$convInfo)
-#print(lapply(countryAbbrevs, cobbDouglasModel))
 
@@
 
+print("US"); print(cobbDouglasPredictions("US", "Q"))
+print("UK"); print(cobbDouglasPredictions("UK", "Q"))
+print("JP"); print(cobbDouglasPredictions("JP", "Q"))
+print("CN"); print(cobbDouglasPredictions("CN", "Q"))
+print("ZA"); print(cobbDouglasPredictions("ZA", "Q"))
+print("SA"); print(cobbDouglasPredictions("SA", "Q"))
+print("IR"); print(cobbDouglasPredictions("IR", "Q"))
+print("TZ"); print(cobbDouglasPredictions("TZ", "Q"))
+print("ZM"); print(cobbDouglasPredictions("ZM", "Q"))
+
 #########################
@@
     out <- do.call("rbind", lapply(countryAbbrevs, cobbDouglasPredictions)) #rbinds all the predictions together
+    colnames(out) <- c("predGDP")
   } else {
     out <- do.call("rbind", lapply(countryAbbrevs, cobbDouglasPredictions, energyType=energyType))
+    colnames(out) <- c(paste("predGDP", energyType, sep=""))
+    print(colnames(out))
   }
-  colnames(out) <- c("predGDP")
   return(out)
@@
 ##
-cobbDouglasParamsTable <- function(){
+cobbDouglasParamsTableNoEnergy <- function(){
   #Do rbind on the results of creating a row in the table for every country abbreviation that we know.
@@
   tableCD <- xtable(dataCD, 
-                    caption="Cobb-Douglas parameters for 1980-2011 (US, UK, JP) or 1991-2011 (others). (Parameter estimates beneath symbol. 95\\% confidence interval bounds to left and right.)", 
+                    caption="Cobb-Douglas (without energy) for 1980-2011 (US, UK, JP) or 1991-2011 (others).
+(Parameter estimates beneath symbol.
+95\\% confidence interval bounds to left and right.)",
                     digit = c(1, 4,4,4, 2,2,2, 2,2,2),
@@
 <<CD Params Table, results='asis'>>=
-print(cobbDouglasParamsTable(), caption.placement="top", sanitize.colnames.function = identity)
+print(cobbDouglasParamsTableNoEnergy(), caption.placement="top", sanitize.colnames.function = identity)
 @
 
-<<CD_Params_Graph, fig.width=figWidth, fig.height=3.5, fig.cap="Cobb-Douglas (without energy) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
+<<CD_Params_Graph, fig.width=figWidth, fig.height=3.5, fig.cap="Cobb-Douglas (without energy) model parameters. Vertical bars indicate 95\\% confidence intervals.", eval=FALSE>>=
 createCDParamsGraph <- function(){
@@
                    layout = c(3,1), #3 column, 1 row
-                   strip = strip.custom(factor.levels=c(expression(italic(lambda)), #sets labels in strip
-                                                        expression(italic(alpha)),
-                                                        expression(italic(beta))
-                                                        ), 
+                   strip = strip.custom(factor.levels=c("$\\lambda$", "$\\alpha$", "$\\beta$"),  #sets labels in strip 
                                         bg="white"), #sets background color in strip
@@
                                  tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
+                                 x=list(cex=0.75), #reduces text size so that country abbrevs are legible
                                  y=list(relation="free", #allow each axis to be different
-                                        at=list(c(0.0, 0.05, 0.1),   #tick mark locations on y axis
+                                        at=list(c(0.0, 0.05, 0.1),   #y tick mark for lambda
                                                 c(0.0, 0.5, 1.0), 
@@
 
-<<CD_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.cap="Cobb-Douglas (without energy) results.">>=
+<<CD_GDP_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.cap="Cobb-Douglas results.">>=
 createCDLatticeGraph <- function(){
   dataTable <- loadData("All") #Grab the raw data
-  predictions <- cobbDouglasPredictionsColumn() #Get the predictions from the models
-  dataTable <- cbind(dataTable, predictions) #Now add the predictions column to the data. Column name = "predGDP".
+  predictions <- cobbDouglasPredictionsColumn() #Get the predictions from the CD model without energy
+  predictionsQ <- cobbDouglasPredictionsColumn("Q") #Predictions with Q
+  predictionsX <- cobbDouglasPredictionsColumn("X") #Predictions with X
+  dataTable <- cbind(dataTable, predictions, predictionsQ, predictionsX) #Now add the predictions column to the data. Column name = "predGDP".
   graphType <- "b" #b is for both line and symbol
-  lineTypes <- c(0, 1) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
-  lineWidths <- c(0, 1) #line widths. 0 means no line.
-  colors <- c("black", "black") #line and symbol colors
-  symbols <- c(1, NA)  #NA gives no symbol.
-  graph <- xyplot(iGDP+predGDP ~ Year | Country, data=dataTable,
+  lineTypes <- c(0, 1, 5, 6) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
+  lineWidths <- c(0, 1, 1, 1) #line widths. 0 means no line.
+  colors <- c("black", "black", "red", "blue") #line and symbol colors
+  symbols <- c(1, NA, NA, NA)  #NA gives no symbol.
+  graph <- xyplot(iGDP+predGDP+predGDPQ+predGDPX ~ Year | Country, data=dataTable,
                   type=graphType,
@@
                   pch = symbols, col.symbol = colors, #Controls symbol parameters
-                  key=list(text=list(c("Actual", "Predicted")),
+                  key=list(text=list(c("Actual", "No energy", "With q", "With x")),
                            type=graphType,
@@
                               tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
-                              y=list(at=c(1,2,3,4,5,6,7,8,9,10))), #tick mark locations
-                  ylim=c(0.5,8), #y axis limits
+                              y=list(relation="free", #allow each axis to be different
+                                     at=c(1,2,3,4,5,6,7,8,9,10))), #tick mark locations
+#                  ylim=c(0.5,3), #y axis limits
+                  ylim=list(c(1,8), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3)),
+
                   xlab="", ylab="Indexed GDP (1980=1 or 1991=1)") #axis labels
@@
 
-  print(countryName)
+  #print(countryName)
   energyColumnName  <- paste("i", energyType, sep="")
@@
   summaryCDe <- summary(modelCDe) # Gives the nls summary table
-  print(summaryCDe)
+  #print(summaryCDe)
 
@@
   b <- as.numeric(coef(modelCDe)["b"])
-  print(a)
-  print(b)
+  #print(a)
+  #print(b)
   lambda <- as.numeric(coef(modelCDe)["lambda"])

### 2013-02-04 EconGrowth.Rnw
Now creating a table of parameters from Cobb-Douglas with energy fits.

@@
 
-print("US"); print(cobbDouglasPredictions("US", "Q"))
-print("UK"); print(cobbDouglasPredictions("UK", "Q"))
-print("JP"); print(cobbDouglasPredictions("JP", "Q"))
-print("CN"); print(cobbDouglasPredictions("CN", "Q"))
-print("ZA"); print(cobbDouglasPredictions("ZA", "Q"))
-print("SA"); print(cobbDouglasPredictions("SA", "Q"))
-print("IR"); print(cobbDouglasPredictions("IR", "Q"))
-print("TZ"); print(cobbDouglasPredictions("TZ", "Q"))
-print("ZM"); print(cobbDouglasPredictions("ZM", "Q"))
-
 #########################
@@
 # countryName is a string containing the 2-letter abbreviation for the country, e.g. "US" or "CN"
+# energyType is a string, one of "Q", "X", or "U"
 #
@@
 ##
-cobbDouglasData <- function(countryName){
-  modelCD <- cobbDouglasModel(countryName)
-  # Checks validity of the model. AIC stands for Akaike's Information Criterion.
-  aicCD  <- AIC(modelCD, k=2)
+cobbDouglasData <- function(countryName, energyType){
+  modelCD <- cobbDouglasModel(countryName, energyType)
   summaryCD <- summary(modelCD) # Gives the nls summary table.
   ciCD <- confint(modelCD, level = ciLevel); ciCD # Calculates confidence intervals for the CD model.
-  # Calculate beta and its confidence interval and report it.
+  dofCD <- summaryCD$df[2] # Gives the degrees of freedom for the model.
+  tvalCD <- qt(ciHalfLevel, df = dofCD)
+  if (missing(energyType)){
+    #Cobb-Douglas without energy
     alpha <- as.numeric(coef(modelCD)["alpha"])
     beta <- 1.0 - alpha
-  beta.est <- deltaMethod(modelCD, "1 - alpha"); beta.est # Estimates beta and its standard error (SE).
+    beta.est <- deltaMethod(modelCD, "1 - alpha") # Estimates beta and its standard error (SE).
+    # Calculate beta and its confidence interval and report it.
     # Now calculate a confidence interval on beta
-  dofCD <- summaryCD$df[2]; dofCD # Gives the degrees of freedom for the model.
-  tvalCD <- qt(ciHalfLevel, df = dofCD); tvalCD
     betaCICD <- with(beta.est, Estimate + c(-1.0, 1.0) * tvalCD * SE); betaCICD # Gives the confidence interval on beta.  
     # Combine all estimates and their confidence intervals into data frames with intelligent row names
-  estCD <- data.frame(lambda = coef(modelCD)["lambda"], alpha = coef(modelCD)["alpha"], beta = beta, gamma = 0)
+    estCD <- data.frame(lambda=coef(modelCD)["lambda"], alpha=coef(modelCD)["alpha"], beta=beta, gamma=0)
     row.names(estCD) <- "CD"
     # The [1] subscripts pick off the lower confidence interval
-  lowerCD <- data.frame(lambda = ciCD["lambda","2.5%"], alpha = ciCD["alpha", "2.5%"], beta = betaCICD[1], gamma = NA) 
+    lowerCD <- data.frame(lambda=ciCD["lambda","2.5%"], alpha=ciCD["alpha", "2.5%"], beta=betaCICD[1], gamma=NA) 
     row.names(lowerCD) <- "-95% CI"
     # The [2] subscripts pick off the lower confidence interval
-  upperCD <- data.frame(lambda = ciCD["lambda","97.5%"], alpha = ciCD["alpha", "97.5%"], beta = betaCICD[2], gamma = NA)
+    upperCD <- data.frame(lambda=ciCD["lambda","97.5%"], alpha=ciCD["alpha", "97.5%"], beta=betaCICD[2], gamma=NA)
     row.names(upperCD) <- "+95% CI"
+  } else {
+    #Cobb-Douglas with energy
+    a <- as.numeric(coef(modelCD)["a"])
+    b <- as.numeric(coef(modelCD)["b"])
+    print(a)
+    print(b)
+    lambda <- as.numeric(coef(modelCD)["lambda"])
+    alpha <- a
+    beta <- b - a
+    gamma <- 1.0 - b
+    # Report results with SE
+    beta.est <- deltaMethod(modelCD, "b-a") # Reports results for beta, because beta = b - a.
+    gamma.est <- deltaMethod(modelCD, "1-b") # Reports results for gamma, because gamma = 1 - b.
+    # Now calculate confidence intervals.
+    betaCICD <- with(beta.est, Estimate + c(-1.0, 1.0) * tvalCD * SE) # Gives the confidence interval on beta.
+    gammaCICD <- with(gamma.est, Estimate + c(-1.0, 1.0) * tvalCD * SE) # Gives the confidence interval on gamma.
+    # Combine all estimates and their confidence intervals into data frames with intelligent row names
+    estCD <- data.frame(lambda = lambda, alpha = alpha, beta = beta, gamma = gamma)
+    row.names(estCD) <- "CDe"
+    # The [1] subscripts pick off the lower confidence interval
+    lowerCD <- data.frame(lambda=ciCD["lambda","2.5%"], alpha=ciCD["a", "2.5%"], beta=betaCICD[1], gamma=gammaCICD[1])
+    row.names(lowerCD) <- "- 95% CI"
+    # The [2] subscripts pick off the lower confidence interval
+    upperCD <- data.frame(lambda=ciCD["lambda","97.5%"], alpha=ciCD["a", "97.5%"], beta=betaCICD[2], gamma=gammaCICD[2])
+    row.names(upperCD) <- "+ 95% CI"
+  }
   # Now create the data for a table.
@@
 ##
-cobbDouglasCountryRow <- function(countryName){
-  dataCD <- cobbDouglasData(countryName)
-  # Create CI ranges
+cobbDouglasCountryRow <- function(countryName, energyType){
+  dataCD <- cobbDouglasData(countryName, energyType)
+  if (missing(energyType)){
     out <- cbind(dataCD["-95% CI", "lambda"], dataCD["CD", "lambda"], dataCD["+95% CI", "lambda"],
@@
                  dataCD["-95% CI", "beta"],   dataCD["CD", "beta"],   dataCD["+95% CI", "beta"])
+  } else {
+    out <- cbind(dataCD["-95% CI", "lambda"], dataCD["CDe", "lambda"], dataCD["+95% CI", "lambda"],
+                 dataCD["-95% CI", "alpha"],  dataCD["CDe", "alpha"],  dataCD["+95% CI", "alpha"],
+                 dataCD["-95% CI", "beta"],   dataCD["CDe", "beta"],   dataCD["+95% CI", "beta"],
+                 dataCD["-95% CI", "gamma"],  dataCD["CDe", "gamma"],  dataCD["+95% CI", "gamma"])
+  }
   return(out)
@@
 ############################
-# Aggregates the Cobb-Douglas results into a big data table
+# Aggregates the Cobb-Douglas results into a big data table. No energy.
 ##
@@
 }
+
+############################
+# Aggregates the Cobb-Douglas results into a big data table. With energy.
+##
+cobbDouglasParamsTableWithEnergy <- function(energyType){
+  #Do rbind on the results of creating a row in the table for every country abbreviation that we know.
+  dataCD <- do.call("rbind", lapply(countryAbbrevs, cobbDouglasCountryRow, energyType=energyType))
+  colnames(dataCD) <- c(" ", "$\\lambda$", " ", 
+                        " ", "$\\alpha$",  " ",
+                        " ", "$\\beta$",   " ",
+                        " ", "$\\gamma$",  " ")
+  rownames(dataCD) <- countryAbbrevs
+  tableCD <- xtable(dataCD, 
+                    caption=paste("Cobb-Douglas (with ", energyType, ") for 1980-2011 (US, UK, JP) or 1991-2011 (others).
+(Parameter estimates beneath symbol.
+95\\% confidence interval bounds to left and right.)", sep=""),
+                    digit = c(1, 4,4,4, 2,2,2, 2,2,2, 2,2,2),
+                    align = "r|ccc|ccc|ccc|ccc") #Sets alignment of the numbers in the columns
+  return(tableCD)
+}
 @
 
-<<CD Params Table, results='asis'>>=
+<<CD_Params_Table_No_E, results='asis'>>=
 print(cobbDouglasParamsTableNoEnergy(), caption.placement="top", sanitize.colnames.function = identity)
@@
 
-<<CD_Params_Graph, fig.width=figWidth, fig.height=3.5, fig.cap="Cobb-Douglas (without energy) model parameters. Vertical bars indicate 95\\% confidence intervals.", eval=FALSE>>=
+<<CD_Params_Graph, fig.width=figWidth, fig.height=3.5, fig.cap="Cobb-Douglas (without energy) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
 createCDParamsGraph <- function(){
@@
 \[ a \in[0,1], b \in [0,1], \alpha=\min(a,b), \beta=|b-a|, \gamma = 1-\max(a,b) \]
+
+<<CD_Params_Table_Q, results='asis'>>=
+print(cobbDouglasParamsTableWithEnergy("Q"), caption.placement="top", sanitize.colnames.function = identity)
+@
 

### 2013-02-04 EconGrowth.Rnw
Now generating graphs and tables for CD with q.

--- 2013-02-04 EconGrowth.Rnw
@@
 <<Factors_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.cap="Indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$) for all economies.
-(China's indexed GDP and indexed capital stock rise to $y = 7.3$ and $k = 9.2$ in 2011.)", eval=FALSE>>=
+(China's indexed GDP and indexed capital stock rise to $y = 7.3$ and $k = 9.2$ in 2011.)">>=
 createFactorsLatticeGraph <- function(){
@@
 
-<<cobb-douglas>>=
+<<cobb-douglas functions>>=
 ####################
@@
     aGuess <- alphaGuess
-    bGuess <- alphaGuess + betaGuess - 0.05
+    bGuess <- alphaGuess + betaGuess
     # Now actually do the fit, using the column name "iEToFit".
@@
                                           tol = 1e-05, 
-                                          minFactor = 1/4096, 
+                                          minFactor = 1/1024, 
                                           printEval=FALSE, #Tells whether to print details of curve fit process.
@@
     colnames(out) <- c(paste("predGDP", energyType, sep=""))
-    print(colnames(out))
   }
@@
 ##
-cobbDouglasData <- function(countryName){
-  modelCD <- cobbDouglasModel(countryName)
-  # Checks validity of the model. AIC stands for Akaike's Information Criterion.
-  aicCD  <- AIC(modelCD, k=2)
+cobbDouglasData <- function(countryName, energyType){
+  modelCD <- cobbDouglasModel(countryName, energyType)
   summaryCD <- summary(modelCD) # Gives the nls summary table.
-  ciCD <- confint(modelCD, level = ciLevel); ciCD # Calculates confidence intervals for the CD model.
-  # Calculate beta and its confidence interval and report it.
+  ciCD <- confint(modelCD, level = ciLevel)  # Calculates confidence intervals for the CD model.
+  dofCD <- summaryCD$df[2] # Gives the degrees of freedom for the model.
+  tvalCD <- qt(ciHalfLevel, df = dofCD)
+  if (missing(energyType)){
+    #Cobb-Douglas without energy
     alpha <- as.numeric(coef(modelCD)["alpha"])
     beta <- 1.0 - alpha
-  beta.est <- deltaMethod(modelCD, "1 - alpha"); beta.est # Estimates beta and its standard error (SE).
+    beta.est <- deltaMethod(modelCD, "1 - alpha") # Estimates beta and its standard error (SE).
+    # Calculate beta and its confidence interval and report it.
     # Now calculate a confidence interval on beta
-  dofCD <- summaryCD$df[2]; dofCD # Gives the degrees of freedom for the model.
-  tvalCD <- qt(ciHalfLevel, df = dofCD); tvalCD
     betaCICD <- with(beta.est, Estimate + c(-1.0, 1.0) * tvalCD * SE); betaCICD # Gives the confidence interval on beta.  
     # Combine all estimates and their confidence intervals into data frames with intelligent row names
-  estCD <- data.frame(lambda = coef(modelCD)["lambda"], alpha = coef(modelCD)["alpha"], beta = beta, gamma = 0)
+    estCD <- data.frame(lambda=coef(modelCD)["lambda"], alpha=coef(modelCD)["alpha"], beta=beta, gamma=0)
     row.names(estCD) <- "CD"
     # The [1] subscripts pick off the lower confidence interval
-  lowerCD <- data.frame(lambda = ciCD["lambda","2.5%"], alpha = ciCD["alpha", "2.5%"], beta = betaCICD[1], gamma = NA) 
+    lowerCD <- data.frame(lambda=ciCD["lambda","2.5%"], alpha=ciCD["alpha", "2.5%"], beta=betaCICD[1], gamma=NA) 
     row.names(lowerCD) <- "-95% CI"
     # The [2] subscripts pick off the lower confidence interval
-  upperCD <- data.frame(lambda = ciCD["lambda","97.5%"], alpha = ciCD["alpha", "97.5%"], beta = betaCICD[2], gamma = NA)
+    upperCD <- data.frame(lambda=ciCD["lambda","97.5%"], alpha=ciCD["alpha", "97.5%"], beta=betaCICD[2], gamma=NA)
     row.names(upperCD) <- "+95% CI"
+  } else {
+#     print("")
+#     print(paste("In cobbDouglasData:", countryName, energyType))
+#     print("summaryCD:")
+#     print(paste("    df:", summaryCD$df))
+#     print(paste("    sigma:", summaryCD$sigma))
+#     print("    coeffs: ")
+#     print(summaryCD$coefficients)
+#     print("ciCD:")
+#     print(ciCD)
+    #Cobb-Douglas with energy
+    a <- as.numeric(coef(modelCD)["a"])
+    b <- as.numeric(coef(modelCD)["b"])
+#     print(paste("a =", a))
+#     print(paste("b =", b))
+    lambda <- as.numeric(coef(modelCD)["lambda"])
+    alpha <- a
+    beta <- b - a
+    gamma <- 1.0 - b
+    # Report results with SE
+    beta.est <- deltaMethod(modelCD, "b-a") # Reports results for beta, because beta = b - a.
+#     print("beta.est = b-a")
+#     print(beta.est)
+    gamma.est <- deltaMethod(modelCD, "1-b") # Reports results for gamma, because gamma = 1 - b.
+#     print("gamma.est = 1 - b")
+#     print(gamma.est)
+    # Now calculate confidence intervals.
+#     print(paste("dofCD =", dofCD))
+#     print(paste("tvalCD =", tvalCD))
+    betaCICD <- with(beta.est, Estimate + c(-1.0, 1.0) * tvalCD * SE) # Gives the confidence interval on beta.
+#     print("betaCICD:")
+#     print(betaCICD)
+    gammaCICD <- with(gamma.est, Estimate + c(-1.0, 1.0) * tvalCD * SE) # Gives the confidence interval on gamma.
+#     print("gammaCICD:")
+#     print(gammaCICD)
+    # Combine all estimates and their confidence intervals into data frames with intelligent row names
+    estCD <- data.frame(lambda = lambda, alpha = alpha, beta = beta, gamma = gamma)
+    row.names(estCD) <- "CDe"
+    # The [1] subscripts pick off the lower confidence interval
+    lowerCD <- data.frame(lambda=ciCD["lambda","2.5%"], alpha=ciCD["a", "2.5%"], beta=betaCICD[1], gamma=gammaCICD[1])
+    row.names(lowerCD) <- "-95% CI"
+    # The [2] subscripts pick off the lower confidence interval
+    upperCD <- data.frame(lambda=ciCD["lambda","97.5%"], alpha=ciCD["a", "97.5%"], beta=betaCICD[2], gamma=gammaCICD[2])
+    row.names(upperCD) <- "+95% CI"
+  }
   # Now create the data for a table.
@@
 ############
-# Creates a row for the Cobb Douglas parameters table
+# Creates a row for the Cobb Douglas parameters table for the given country (2-letter code) and energyType (Q, X, or U)
 ##
-cobbDouglasCountryRow <- function(countryName){
-  dataCD <- cobbDouglasData(countryName)
-  # Create CI ranges
+cobbDouglasCountryRow <- function(countryName, energyType){
+  dataCD <- cobbDouglasData(countryName, energyType)
+  if (missing(energyType)){
     out <- cbind(dataCD["-95% CI", "lambda"], dataCD["CD", "lambda"], dataCD["+95% CI", "lambda"],
@@
 ##
-cobbDouglasCountryRowsForParamsGraph <- function(countryName){
+cobbDouglasCountryRowsForParamsGraph <- function(countryName, energyType){
+  #Create three rows, one for each parameter. Each row is a data.frame so that it is plottable!
+  if (missing(energyType)){
+    valueRow <- "CD"
     dataCD <- cobbDouglasData(countryName)
-  #Create three rows, one for each parameter. Each row is a data.frame so that it is plottable!
+  } else {
+    valueRow <- "CDe"
+    dataCD <- cobbDouglasData(countryName, energyType)
+  }
+  # These rows are common to the "with" and "without" energy cases.
   lambdaRow <- data.frame(country = countryName, 
@@
                           lowerCI = dataCD["-95% CI", "lambda"], 
-                          value = dataCD["CD", "lambda"], 
+                          value = dataCD[valueRow, "lambda"], 
                           upperCI = dataCD["+95% CI", "lambda"])
@@
                          lowerCI = dataCD["-95% CI", "alpha"],
-                         value = dataCD["CD", "alpha"],  
+                         value = dataCD[valueRow, "alpha"],  
                          upperCI = dataCD["+95% CI", "alpha"])
@@
                         lowerCI = dataCD["-95% CI", "beta"],
-                        value = dataCD["CD", "beta"], 
+                        value = dataCD[valueRow, "beta"], 
                         upperCI = dataCD["+95% CI", "beta"])
+  if (missing(energyType)){
     table <- rbind(lambdaRow, alphaRow, betaRow)
+  } else {
+#     print("In not missing energyType")
+#     print(dataCD)
+    gammaRow <- data.frame(country = countryName, 
+                           parameter = "gamma",
+                           lowerCI = dataCD["-95% CI", "gamma"],
+                           value = dataCD[valueRow, "gamma"], 
+                           upperCI = dataCD["+95% CI", "gamma"])
+#     print(gammaRow)
+    table <- rbind(lambdaRow, alphaRow, betaRow, gammaRow)
+  }
   return(table)
@@
 }
-@
 
-<<CD Params Table, results='asis'>>=
-print(cobbDouglasParamsTableNoEnergy(), caption.placement="top", sanitize.colnames.function = identity)
-@
+############################
+# Aggregates the Cobb-Douglas results into a big data table for the given energyType.
+##
+cobbDouglasParamsTableWithEnergy <- function(energyType){
+  #Do rbind on the results of creating a row in the table for every country abbreviation that we know.
+  dataCD <- do.call("rbind", lapply(countryAbbrevs, cobbDouglasCountryRow, energyType=energyType))
+  colnames(dataCD) <- c(" ", "$\\lambda$", " ", 
+                        " ", "$\\alpha$",  " ",
+                        " ", "$\\beta$",   " ",
+                        " ", "$\\gamma$",  " ")
+  rownames(dataCD) <- countryAbbrevs
+  tableCD <- xtable(dataCD, 
+                    caption=paste("Cobb-Douglas (with $", tolower(energyType), "$) for 1980-2011 (US, UK, JP) or 1991-2011 (others).
+(Parameter estimates beneath symbol.
+95\\% confidence interval bounds to left and right.)", sep=""),
+                    digit = c(1, 4,4,4, 2,2,2, 2,2,2, 2,2,2),
+                    align = "r|ccc|ccc|ccc|ccc") #Sets alignment of the numbers in the columns
+  return(tableCD)
+}
 
-<<CD_Params_Graph, fig.width=figWidth, fig.height=3.5, fig.cap="Cobb-Douglas (without energy) model parameters. Vertical bars indicate 95\\% confidence intervals.", eval=FALSE>>=
-createCDParamsGraph <- function(){
+#############################
+# Creates a graph with confidene intervals for the Cobb-Douglas model for the given energyType
+##
+createCDParamsGraph <- function(energyType){
   # Create a data table with the following columns:
   # country abbrev, parameter (lambda, alpha, or beta), -95% CI, value, +95% CI
+  if (missing(energyType)){
     dataTable <- do.call("rbind", lapply(countryAbbrevs, cobbDouglasCountryRowsForParamsGraph))
-
     graph <- segplot(country ~ upperCI + lowerCI | parameter, 
@@
                      horizontal = FALSE, #makes error bars vertical and puts the countries in the x axis
-                   layout = c(3,1), #3 column, 1 row
+                     layout = c(2,2), #2 column, 2 row
+#                     index.cond = list(2,3,1), #orders the panels as alpha, beta, lambda, gamma
                      strip = strip.custom(factor.levels=c("$\\lambda$", "$\\alpha$", "$\\beta$"), #sets labels in strip 
@@
                      )
+   } else {
+     dataTable <- do.call("rbind", lapply(countryAbbrevs, cobbDouglasCountryRowsForParamsGraph, energyType=energyType))
+     graph <- segplot(country ~ upperCI + lowerCI | parameter, 
+                      data = dataTable, 
+                      centers = value, #identifies where the dots should be placed
+                      draw.bands = FALSE, #provides nicer error bars
+                      horizontal = FALSE, #makes error bars vertical and puts the countries in the x axis
+                      layout = c(2,2), #2 column, 2 row
+#                      index.cond = list(2,3,1,4), #orders the panels as alpha, beta, lambda, gamma
+                      #set labels and bg color in strip
+                      strip = strip.custom(factor.levels=c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$"),  
+                                           bg="white"),
+                      col = "black", #Sets line color to black
+                      lwd = 1, #Sets line width to 1.0
+                      ylim = list(c(-0.05, 0.1), c(-0.5, 1.5), c(-0.5, 1.5), c(-0.5, 1.5)), #y axis limits
+                      scales = list(cex=scaleTextSize, #controls text size on scales.
+                                    tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
+                                    x=list(cex=0.75), #reduces text size so that country abbrevs are legible
+                                    y=list(relation="free", #allow each axis to be different
+                                           at=list(c(0.0, 0.05, 0.1),   #y tick mark for lambda
+                                                   c(0.0, 0.5, 1.0), 
+                                                   c(0.0, 0.5, 1.0),
+                                                   c(0.0, 0.5, 1.0)
+                                                   )
+                                           )
+                                    )
+                      )
+   }
   return(graph)
 }
-createCDParamsGraph()
-@
 
-<<CD_GDP_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.cap="Cobb-Douglas results.">>=
+##############################
+# Creates a graph that plots predicted GDP as lines and GDP data as open circles.
+##
 createCDLatticeGraph <- function(){
@@
   predictionsX <- cobbDouglasPredictionsColumn("X") #Predictions with X
-  dataTable <- cbind(dataTable, predictions, predictionsQ, predictionsX) #Now add the predictions column to the data. Column name = "predGDP".
+  #Now add the predictions columns to the data.
+  dataTable <- cbind(dataTable, predictions, predictionsQ, predictionsX) 
   graphType <- "b" #b is for both line and symbol
@@
                               tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
-                              y=list(relation="free", #allow each axis to be different
-                                     at=c(1,2,3,4,5,6,7,8,9,10))), #tick mark locations
-#                  ylim=c(0.5,3), #y axis limits
+                              y=list(relation="free", #allows each axis to be different
+                                     at=c(1,2,3,4,5,6,7,8,9,10) #tick mark locations
+                                     )
+                              ), 
                   ylim=list(c(1,8), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3)),
-
                   xlab="", ylab="Indexed GDP (1980=1 or 1991=1)") #axis labels
@@
 }
+@
+
+<<CD_Params_Table, results='asis', eval=FALSE>>=
+print(cobbDouglasParamsTableNoEnergy(), caption.placement="top", sanitize.colnames.function = identity, size="\\tiny")
+@
+
+<<CD_Params_Graph, fig.width=figWidth, fig.height=5, fig.cap="Cobb-Douglas (without energy) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
+createCDParamsGraph()
+@
+
+<<CD_GDP_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.cap="Cobb-Douglas results.">>=
 createCDLatticeGraph()
@@
 
-<<cobbDouglasEnergy function, eval=FALSE>>=
-###############################
-# This function fits the Cobb Douglas production function including energy to historical data
-# The functional form is
-#
-# iGDP = exp(lambda * itime) * iCapStk^alpha * iLabor^beta * iEnergy^gamma
-# 
-# iYear: time indexed to 0.0 at the first year [years since beginning of data set]
-# iGDP = time series GDP data indexed to 1.0 at the first year [-]
-# iCapStk = time series capital stock data indexed to 1.0 at the first year [-]
-# iLabor = time series labor data indexed to 1.0 at the first year [-]
-# iEnergy = time series energy data indexed to 1.0 at the first year [-]. 
-#      This may be any of heat (iQ), exergy (iX), or useful work (iU).
-# 
-# returns a data object containing three rows and 5 columns.
-#   col 1: lambda
-#   col 2: alpha
-#   col 3: beta
-#   col 4: gamma
-#   row 1: -95% CI for each parameter
-#   row 2: estimate for each parameter
-#   row 3: +95% CI for each parameter
-#
-# countryName is a string containint the 2-letter abbreviation for the country, e.g. "US" or "CN"
-# energyType is a string to be used in table captions reprsenting the type of energy. Typically, "Q", "X", or "U"
-##
-cobbDouglasEnergyData <- function(countryName, energyType){
+\subsection{Cobb-Douglas with $Q$}
 
-  #print(countryName)
-  energyColumnName  <- paste("i", energyType, sep="")
-  #print(energyColumnName)
-
-  # Load the data that we need.
-  dataTable <- loadData(countryName)
-
-  # Reparameterize to ensure that we meet the constraints:
-  # * alpha + beta + gamma = 1.0.
-  # * alpha, beta, and gamma are all between 0.0 and 1.0.
-  # To do this, we reparameterize as
-  # * 0 < a < 1
-  # * 0 < b < 1
-  # * alpha = min(a, b)
-  # * beta = b - a
-  # * gamma = 1 - max(a, b)
-  iEnergy <- dataTable[energyColumnName] #grabs the desired energy column
-  lambdaGuess <- 0.0 # guessing lambda = 0 means there is no technological progress.
-  alphaGuess <- 0.3 # a typical value for alpha
-  betaGuess <- 0.7 # a typical value for beta
-  modelCDe <- nls(iGDP ~ exp(lambda*iYear) * 
-                    iCapStk^min(a,b) * iLabor^abs(b-a) * 
-                    iEnergy^(1.0 - max(a,b)), 
-                  algorithm = "port",
-                  start = list(lambda=lambdaGuess, a=alphaGuess, b=alphaGuess+betaGuess),
-                  lower = list(lambda=-Inf, a=0, b=0),
-                  upper = list(lambda=Inf, a=1, b=1),
-                  data = dataTable)
-  aicCDe <- AIC(modelCDe, k=2) # Checks validity of the model. AIC stands for Akaike's Information Criterion
-  #print(aicCDe)
-
-  summaryCDe <- summary(modelCDe) # Gives the nls summary table
-  #print(summaryCDe)
-
-  # Provides confidence intervals on lambda, a, and b. But, we need CIs on alpha and beta.
-  ciCDe <- confint(modelCDe, level = ciLevel)
-  #print(ciCDe)
-
-  a <- as.numeric(coef(modelCDe)["a"])
-  b <- as.numeric(coef(modelCDe)["b"])
-  #print(a)
-  #print(b)
-  lambda <- as.numeric(coef(modelCDe)["lambda"])
-  alpha <- a
-  beta <- b - a
-  gamma <- 1.0 - alpha - beta
-
-  # Report results with SE
-  beta.est <- deltaMethod(modelCDe, "b-a") # Reports results for beta, because beta = b - a.
-  gamma.est <- deltaMethod(modelCDe, "1-b") # Reports results for gamma, because gamma = 1 - b.
-
-  # Now calculate confidence intervals.
-  dofCDe <- summaryCDe$df[2] # Gives the degrees of freedom for the model.
-  #print(dofCDe)
-  tvalCDe <- qt(ciHalfLevel, df = dofCDe)
-  #print(tvalCDe)
-  betaCICDe <- with(beta.est, Estimate + c(-1.0, 1.0) * tvalCDe * SE) # Gives the confidence interval on beta.
-  #print(betaCICDe)
-  gammaCICDe <- with(gamma.est, Estimate + c(-1.0, 1.0) * tvalCDe * SE) # Gives the confidence interval on alpha.
-  #print(gammaCICDe)
-
-  # Combine all estimates and their confidence intervals into data frames with intelligent row names
-  estCDe <- data.frame(lambda = lambda, alpha = alpha, beta = beta, gamma = gamma)
-  #print(estCDe);
-  #row.names(estCDe) <- "Cobb-Douglas with e: $y = e^{\\lambda t}k^{\\alpha}l^{\\beta}e^{\\gamma}$"
-  row.names(estCDe) <- paste("C-D with ", energyType, sep="")
-  # The [1] subscripts pick off the lower confidence interval
-  lowerCDe <- data.frame(lambda = ciCDe["lambda","2.5%"], alpha = ciCDe["a", "2.5%"], beta = betaCICDe[1], gamma = gammaCICDe[1])
-  row.names(lowerCDe) <- "- 95% CI"
-  # The [2] subscripts pick off the lower confidence interval
-  upperCDe <- data.frame(lambda = ciCDe["lambda","97.5%"], alpha = ciCDe["a", "97.5%"], beta = betaCICDe[2], gamma = gammaCICDe[2])
-  row.names(upperCDe) <- "+ 95% CI"
-
-  # Now create the data for a table.
-  dataCDe <- rbind(upperCDe, estCDe, lowerCDe)
-  #print(dataCDe)
-  return(dataCDe)
-}
-
-####################################
-# Creates a LaTeX printable table from the CES data. This function first calls cobbDouglasEnergyData.
-#
-# countryName is a string containint the 2-letter abbreviation for the country, e.g. "US" or "CN"
-# energyType is a string to be used in table captions reprsenting the type of energy. Typically, "Q", "X", or "U"
-#
-# returns a printable LaTeX table from xtable.
-##
-cobbDouglasEnergyTable <- function(countryName, energyType){
-  dataCDe <- cobbDouglasEnergyData(countryName, energyType)
-  tableCDe <- xtable(dataCDe, caption=paste(countryName, ", 1980-2011.", sep=""), digit = c(4, 4, 2, 2, 3))
-  return(tableCDe)
-}
+<<CDq_Params_Table, results='asis'>>=
+print(cobbDouglasParamsTableWithEnergy("Q"), 
+      caption.placement="top", 
+      sanitize.colnames.function = identity, 
+      size="\\tiny")
 @
 
-\subsection{Cobb-Douglas with $Q$}
-
-<<CDq analysis, eval=FALSE>>=
-# Note that the anlaysis of ZA is taking a long time here. Need to figure out why.
-CDqTables <- lapply(countryAbbrevs, cobbDouglasEnergyTable, energyType="Q")
-@
-
-<<CDq Results, results='asis', eval=FALSE>>=
-print(CDqTables[["US"]], caption.placement="top")
-print(CDqTables[["ZA"]], caption.placement="top")
-# According to http://cran.r-project.org/web/packages/xtable/vignettes/xtableGallery.pdf, Section 3.1, I should 
-# be able to use the "sanitize.text.function" parameter to allow markup in column headers. But this next
-# line is not working at the present time. --MKH, 18 Jan 2012.
-# print(tableCDe, sanitize.text.function = function(x){x})
-
-#print(tableAll, caption.placement="top")
-@
-
-\subsection{Cobb-Douglas With $X$}
-
-<<CDx analysis, eval=FALSE>>=
-# Note that the anlaysis of ZA is taking a long time here. Need to figure out why.
-CDxTables <- lapply(countryAbbrevs, cobbDouglasEnergyTable, energyType="X")
-@
-
-<<CDx Results, results='asis', eval=FALSE>>=
-print(CDxTables[["US"]], caption.placement="top")
-print(CDxTables[["ZA"]], caption.placement="top")
-@
-
-\subsection{Cobb-Douglas With $U$}
-
-<<CDu analysis, eval=FALSE>>=
-CDuTables <- lapply(countryAbbrevs, cobbDouglasEnergyTable, energyType="U")
-@
-
-<<CDu Results, results='asis', eval=FALSE>>=
-print(CDuTables[["US"]], caption.placement="top")
-print(CDuTables[["ZA"]], caption.placement="top")
+<<CDq_Params_Graph, fig.width=figWidth, fig.height=5, fig.cap="Cobb-Douglas (with $q$) model parameters. Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
+createCDParamsGraph("Q")
 @

### 2013-02-04 EconGrowth.Rnw
Now creating CD graph and table for exergy versino of CD model.

@@
 
-<<Factors_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.cap="Indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$) for all economies.
-(China's indexed GDP and indexed capital stock rise to $y = 7.3$ and $k = 9.2$ in 2011.)">>=
+<<Factors_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.cap="The facts.
+Indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$) for all economies.">>=
 createFactorsLatticeGraph <- function(){
@@
                               tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
-                              y=list(at=c(1,2,3,4,5,6,7,8,9,10))), #tick mark locations
-                  ylim=c(0.5,4.5), #y axis limits
+                              y=list(relation="free", #allows each axis to be different
+                                     at=c(1,2,3,4,5,6,7,8,9,10) #tick mark locations
+                                     )
+                              ),
+                  ylim=list(c(1,10), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4)), #y axis limits
                   xlab="", ylab="Indexed (1980=1 or 1991=1)") #axis labels
@@
 createCDParamsGraph <- function(energyType){
+
+  if (missing(energyType)){
     # Create a data table with the following columns:
     # country abbrev, parameter (lambda, alpha, or beta), -95% CI, value, +95% CI
-  if (missing(energyType)){
     dataTable <- do.call("rbind", lapply(countryAbbrevs, cobbDouglasCountryRowsForParamsGraph))
@@
                      layout = c(2,2), #2 column, 2 row
-#                     index.cond = list(2,3,1), #orders the panels as alpha, beta, lambda, gamma
+                     index.cond = list(c(2,3,1)), #orders the panels as alpha, beta, lambda, gamma
                      strip = strip.custom(factor.levels=c("$\\lambda$", "$\\alpha$", "$\\beta$"), #sets labels in strip 
@@
    } else {
+     # Create a data table with the following columns:
+     # country abbrev, parameter (lambda, alpha, or beta), -95% CI, value, +95% CI
      dataTable <- do.call("rbind", lapply(countryAbbrevs, cobbDouglasCountryRowsForParamsGraph, energyType=energyType))
@@
                       layout = c(2,2), #2 column, 2 row
-#                      index.cond = list(2,3,1,4), #orders the panels as alpha, beta, lambda, gamma
+                      index.cond = list(c(2,3,1,4)), #orders the panels as alpha, beta, lambda, gamma
                       #set labels and bg color in strip
@@
 createCDParamsGraph("Q")
+@
+
+<<CDx_Params_Graph, fig.width=figWidth, fig.height=5, fig.cap="Cobb-Douglas (with $x$) model parameters. Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
+createCDParamsGraph("X")
+@
+
+<<CDx_Params_Table, results='asis'>>=
+print(cobbDouglasParamsTableWithEnergy("X"), 
+      caption.placement="top", 
+      sanitize.colnames.function = identity, 
+      size="\\tiny")
 @

### 2013-02-05 EconGrowth.Rnw
Now creating labels on figures and tables from knitr so that they can be referenced in the paper.

@@
   comment=NA,
-  echo=FALSE,    #Turns off code echo for all chunks. Set TRUE on an individual chunk to see it.
+  warning=FALSE, #Tells whether to show warnings.
+  #Tells whether to cache output from chunks are saved. Cacheing saves time. 
+  #However, references to LaTeX tables DO NOT WORK if cacheing is turned on (cache=TRUE).
+  cache=FALSE,
+  echo=FALSE,    #Tells whether to echo code for all chunks. Set TRUE on an individual chunk to see its code.
   message=FALSE) #Turns off messages for all chunks. Set TRUE on an individual chunk to see it.
@@
 
+Figure \ref{fig:Factors_Lattice_Graph} shows the ``facts'' as they are known.
+
 <<Factors_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.cap="The facts.
-Indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$) for all economies.">>=
+Indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$).">>=
 createFactorsLatticeGraph <- function(){
@@
   tableCD <- xtable(dataCD, 
-                    caption="Cobb-Douglas (without energy) for 1980-2011 (US, UK, JP) or 1991-2011 (others).
+                    caption="Cobb-Douglas (without energy) for 1980-2011 (US, UK, JP), 1991-2010 (CN and ZA), and 1991-2011 (SA, IR, TZ, and ZM).
 (Parameter estimates beneath symbol.
 95\\% confidence interval bounds to left and right.)",
+                    label="tab:CD_Parameters_No_Energy",
                     digit = c(1, 4,4,4, 2,2,2, 2,2,2),
@@
   tableCD <- xtable(dataCD, 
-                    caption=paste("Cobb-Douglas (with $", tolower(energyType), "$) for 1980-2011 (US, UK, JP) or 1991-2011 (others).
+                    caption=paste("Cobb-Douglas (with $", tolower(energyType), "$) for 1980-2011 (US, UK, JP), 1991-2010 (CN and ZA), and 1991-2011 (SA, IR, TZ, and ZM).
 (Parameter estimates beneath symbol.
 95\\% confidence interval bounds to left and right.)", sep=""),
+                    label=paste("tab:CD_Parameters_With_", energyType, sep=""),
                     digit = c(1, 4,4,4, 2,2,2, 2,2,2, 2,2,2),
@@
                   pch = symbols, col.symbol = colors, #Controls symbol parameters
-                  key=list(text=list(c("Actual", "No energy", "With q", "With x")),
+                  key=list(text=list(c("Actual", "No energy", "With $q$", "With $x$")),
                            type=graphType,
@@
 
-<<CD_Params_Table, results='asis', eval=FALSE>>=
+The Cobb-Douglas model without energy is given by
+
+\begin{equation} \label{eq:CD_No_Energy}
+  y = a^{\lambda (t-t_0)}k^{\alpha}l^{\beta}.
+\end{equation}
+
+Table \ref{tab:CD_Parameters_No_Energy} gives the parameters for the Cobb-Douglas model without energy.
+
+<<CD_Params_Table, results='asis'>>=
 print(cobbDouglasParamsTableNoEnergy(), caption.placement="top", sanitize.colnames.function = identity, size="\\tiny")
@@
 
+Figure \ref{fig:CD_Params_Graph} shows values and 95\% confidence intervals for the parameters for the Cobb-Douglas model (without energy).
+
 <<CD_Params_Graph, fig.width=figWidth, fig.height=5, fig.cap="Cobb-Douglas (without energy) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
 createCDParamsGraph()
-@
-
-<<CD_GDP_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.cap="Cobb-Douglas results.">>=
-createCDLatticeGraph()
 @
@@
 
-\subsection{Cobb-Douglas with $Q$}
+The Cobb-Douglas model with energy is given by
+
+\begin{equation} \label{eq:CD_With_Energy}
+  y = a^{\lambda (t-t_0)}k^{\alpha}l^{\beta}e^{\gamma},
+\end{equation}
+
+\noindent where $e$ can be any of thermal energy ($q$), exergy ($x$), or useful work ($u$).
+
+\subsection{Cobb-Douglas with $q$}
+
+The Cobb-Douglas (with thermal energy, $q$) parameters are given in Table \ref{tab:CD_Parameters_With_Q}.
 
@@
 
+Figure \ref{fig:CDq_Params_Graph} shows values and 95\% confidence intervals for the parameters for the Cobb-Douglas model (with $q$).
+
 <<CDq_Params_Graph, fig.width=figWidth, fig.height=5, fig.cap="Cobb-Douglas (with $q$) model parameters. Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
@@
 
+The Cobb-Douglas (with exergy) parameters are given in Table \ref{tab:CD_Parameters_With_X}.
+
 <<CDx_Params_Graph, fig.width=figWidth, fig.height=5, fig.cap="Cobb-Douglas (with $x$) model parameters. Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
@@
 @
+
+Figure \ref{fig:CDx_Params_Graph} shows values and 95\% confidence intervals for the parameters for the Cobb-Douglas model (with $x$).
 
@@
       size="\\tiny")
+@
+
+\subsection{Cobb-Douglas Comparisons}
+
+Figure \ref{fig:CD_GDP_Lattice_Graph} compares predictions from the Cobb-Douglas models (without energy, with $Q$, and with $x$) to historical data.
+
+<<CD_GDP_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.cap="Cobb-Douglas results.">>=
+createCDLatticeGraph()
 @
@@
 
+\subsection{CES with $X$}
+
+\subsection{CES with $U$}
+
+\section{LINEX}
+
+\subsection{LINEX with $Q$}
+
+\subsection{LINEX with $X$}
+
+\subsection{LINEX with $U$}
+
 %% The Appendices part is started with the command \appendix;

### 2013-02-05 EconGrowth.Rnw
Added a table of AIC values.

@@
 
+\usepackage{soul} %Provides strikethrough text
+
 %% The lineno packages adds line numbers. Start line numbering with
@@
 
-\title{Empirical Analysis of the Role of Energy in Economic Growth}
+\title{An Empirical Analysis of the Role of Energy in Economic Growth}
 
@@
 
+**************** To Do List ********************
+\begin{itemize}
+\item Reese: Add text from Word verson of paper to the LaTeX version.
+\item \st{Heun: Create a table of AIC values for each fit.}
+\item Heun: Add $u$ preductions for Cobb-Douglas
+\item Heun: Eliminate blanks in the coefficient tables for the 95\% CIs in the Cobb-Douglas with energy rows 
+      \begin{itemize}
+      \item ZA: lower bound on $\lambda$ and upper bound on $\alpha$
+      \item ZM: lower bound on $\lambda$
+      \end{itemize}
+\item Heun: Fix warnings of the form ``Warning:  step factor 0.000488281 reduced below ’minFactor’ of 0.000976562'' in the code that generates the Cobb-Douglas with energy fits.
+\item Heun: Add CES production function fits
+\item Heun: Add Linex production function fits
+\item Heun: Add $k$, $l$, $q$, $x$, and $u$ fits ONLY
+\end{itemize}
+*************************************************
+
 Caleb, put your LaTeX code here.
@@
   comment=NA,
-  warning=FALSE, #Tells whether to show warnings.
+  warning=TRUE, #Tells whether to show warnings.
   #Tells whether to cache output from chunks are saved. Cacheing saves time. 
   #However, references to LaTeX tables DO NOT WORK if cacheing is turned on (cache=TRUE).
-  cache=FALSE,
+  cache=TRUE,
   echo=FALSE,    #Tells whether to echo code for all chunks. Set TRUE on an individual chunk to see its code.
@@
 @
+
+\section{The Facts}
 
@@
                     label="tab:CD_Parameters_No_Energy",
-                    digit = c(1, 4,4,4, 2,2,2, 2,2,2),
+                    digits = c(1, 4,4,4, 2,2,2, 2,2,2),
                     align = "r|ccc|ccc|ccc") #Sets alignment of the numbers in the columns
@@
                     label=paste("tab:CD_Parameters_With_", energyType, sep=""),
-                    digit = c(1, 4,4,4, 2,2,2, 2,2,2, 2,2,2),
+                    digits = c(1, 4,4,4, 2,2,2, 2,2,2, 2,2,2),
                     align = "r|ccc|ccc|ccc|ccc") #Sets alignment of the numbers in the columns
@@
 
+\section{Goodness of Fit}
+
+<<AIC_Analysis>>=
+###############################
+# Creates a xtable object that holds the AIC values for each parameter estimation that we include.
+##
+createAICTable <- function(){
+  # Cobb-Douglas
+  models <- lapply(countryAbbrevs, cobbDouglasModel)
+  aicCD <- data.frame(lapply(models, AIC))
+  rownames(aicCD) <- "CD"
+  # Cobb-Douglas with Q
+  models <- lapply(countryAbbrevs, cobbDouglasModel, energyType="Q")
+  aicCDq <- data.frame(lapply(models, AIC))
+  rownames(aicCDq) <- "CD$q$"
+  # Cobb-Douglas with X
+  models <- lapply(countryAbbrevs, cobbDouglasModel, energyType="X")
+  aicCDx <- data.frame(lapply(models, AIC))
+  rownames(aicCDx) <- "CD$x$"
+  # Create the data.frame table
+  out <- rbind(aicCD, aicCDq, aicCDx) 
+  # Create the xtable with caption and label
+  out <- xtable(out, 
+                caption="AIC values for all models.", 
+                label="tab:AICTable", 
+                digits=1 #Only one number after the decimal place
+                )
+  return(out)
+}
+@
+
+We assess goodness of fit via the Akaike Information Criterion (AIC).
+AIC values for all models and all countries are shown in Table \ref{tab:AICTable}.
+Increasing goodness of fit is indicated by smaller (i.e., more negative) AIC values.
+AIC values can be compared per data set (i.e., per country) but not across data sets (i.e., not across countries).
+
+<<AIC_Table, results='asis', label="AIC_Table">>=
+print(createAICTable(), 
+      caption.placement="top", 
+      sanitize.rownames.function = identity)
+
+@
+
+The AIC results show *****************.
+
 %% The Appendices part is started with the command \appendix;

### 2013-02-05 EconGrowth.Rnw
Now doing U predictions.

@@
 \item \st{Heun: Create a table of AIC values for each fit.}
-\item Heun: Add $u$ preductions for Cobb-Douglas
-\item Heun: Eliminate blanks in the coefficient tables for the 95\% CIs in the Cobb-Douglas with energy rows 
+\item \st{Heun: Add $u$ predictions for Cobb-Douglas}
+\item Heun: Add covariance metrics.
+\item Heun: Eliminate blanks in the coefficient tables for the 95\% CIs in the Cobb-Douglas with energy rows. Asked Pruim about this via email but have not heard a response.
       \begin{itemize}
@@
 \item Heun: Add Linex production function fits
-\item Heun: Add $k$, $l$, $q$, $x$, and $u$ fits ONLY
+\item Heun: Add $k$, $l$, $q$, $x$, and $u$ ONLY fits
 \end{itemize}
@@
   #However, references to LaTeX tables DO NOT WORK if cacheing is turned on (cache=TRUE).
-  cache=TRUE,
+  cache=FALSE,
   echo=FALSE,    #Tells whether to echo code for all chunks. Set TRUE on an individual chunk to see its code.
@@
 cobbDouglasPredictions <- function(countryAbbrev, energyType){
+  # Can't make predictions for any of CN, ZA, SA, IR, TZ, or ZM if we're interested in U
+  if (!missing(energyType)){
+    # Consider this replacement only if energyType has been specified.
+    if (energyType == "U" && (countryAbbrev == "CN" || countryAbbrev == "ZA" || countryAbbrev == "SA" 
+                              || countryAbbrev == "IR" || countryAbbrev == "TZ" || countryAbbrev == "ZM")){
+      #Return a column of NAs if the above conditions have been met.
+      nRows <- 21 # All of these countries need 21 rows.
+      df <- as.data.frame(matrix(NA, ncol = 1, nrow = nRows))
+      colnames(df) <- "pred"
+      return(df)
+    }
+  }
   model <- cobbDouglasModel(countryAbbrev, energyType)
@@
   df <- data.frame(pred)
-  # There are two countries which do not have labor data for 2011. Need to add a "NA" for 2011 for those countries.
-  if (countryAbbrev == "CN" || countryAbbrev == "ZA"){
-    dfNA <- data.frame(NA)
-    colnames(dfNA) <- "pred" #Need to give it the same name so that we can apply rbind
-    df <- rbind(df, dfNA)
-  }
+  # Pad with rows as necessary
+  df <- padRows(countryAbbrev, df)
   return(df)
+}
+
+#####################
+# This function adds NA rows to a data.frame to ensure that the df is the same length as the country data set
+##
+padRows <- function(countryAbbrev, df){
+  nRowsData <- nrow(loadData(countryAbbrev)) #Gets number of rows in data set
+  nRowsDF <- nrow(df)
+  nRowsToAdd <- nRowsData - nRowsDF
+  nCol <- ncol(df)
+  dfToAppend <- as.data.frame(matrix(NA, ncol=nCol, nrow=nRowsToAdd))
+  colnames(dfToAppend) <- colnames(df)
+  return(rbind(df, dfToAppend))
 }
@@
   dataTable <- loadData("All") #Grab the raw data
-  predictions <- cobbDouglasPredictionsColumn() #Get the predictions from the CD model without energy
-  predictionsQ <- cobbDouglasPredictionsColumn("Q") #Predictions with Q
-  predictionsX <- cobbDouglasPredictionsColumn("X") #Predictions with X
+  predictions <- cobbDouglasPredictionsColumn()     #Predictions from CD without energy
+  predictionsQ <- cobbDouglasPredictionsColumn("Q") #Predictions from CD with Q
+  predictionsX <- cobbDouglasPredictionsColumn("X") #Predictions from CD with X
+  predictionsU <- cobbDouglasPredictionsColumn("U") #Predictions from CD with U
   #Now add the predictions columns to the data.
-  dataTable <- cbind(dataTable, predictions, predictionsQ, predictionsX) 
+  dataTable <- cbind(dataTable, predictions, predictionsQ, predictionsX, predictionsU) 
   graphType <- "b" #b is for both line and symbol
-  lineTypes <- c(0, 1, 5, 6) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
-  lineWidths <- c(0, 1, 1, 1) #line widths. 0 means no line.
-  colors <- c("black", "black", "red", "blue") #line and symbol colors
-  symbols <- c(1, NA, NA, NA)  #NA gives no symbol.
-  graph <- xyplot(iGDP+predGDP+predGDPQ+predGDPX ~ Year | Country, data=dataTable,
+  lineTypes <- c(0, 1, 2, 4, 1) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
+  lineWidths <- c(0, 2, 1, 1, 1) #line widths. 0 means no line.
+  colors <- c("black", "black", "red", "blue", "darkorange") #line and symbol colors
+  symbols <- c(1, NA, NA, NA, NA)  #NA gives no symbol.
+  graph <- xyplot(iGDP+predGDP+predGDPQ+predGDPX+predGDPU ~ Year | Country, data=dataTable,
                   type=graphType,
@@
                   pch = symbols, col.symbol = colors, #Controls symbol parameters
-                  key=list(text=list(c("Actual", "No energy", "With $q$", "With $x$")),
+                  key=list(text=list(c("Actual", "No energy", "With $q$", "With $x$", "With $u$")),
                            type=graphType,
@@
 
-\[ a \in[0,1], b \in [0,1], \alpha=\min(a,b), \beta=|b-a|, \gamma = 1-\max(a,b) \]
+$a \in[0,1], b \in [0,1], \alpha=\min(a,b), \beta=|b-a|, \gamma = 1-\max(a,b)$
 
@@
 ###############################
-# Creates a xtable object that holds the AIC values for each parameter estimation that we include.
+# Creates an xtable object that holds the AIC values for each parameter estimation that we include.
 ##
@@
   rownames(aicCDx) <- "CD$x$"
+  # Cobb-Douglas with U
+  models <- c(cobbDouglasModel("US", "U"), cobbDouglasModel("UK", "U"), cobbDouglasModel("JP", "U"))
+  aicCDu <- cbind(US=AIC(cobbDouglasModel("US", "U")), 
+                  UK=AIC(cobbDouglasModel("UK", "U")), 
+                  JP=AIC(cobbDouglasModel("JP", "U")),
+                  CN=NA, ZA=NA, SA=NA, IR=NA, TZ=NA, ZM=NA) #No U data for these countries.
+  rownames(aicCDu) <- "CD$u$"
   # Create the data.frame table
-  out <- rbind(aicCD, aicCDq, aicCDx) 
+  out <- rbind(aicCD, aicCDq, aicCDx, aicCDu) 
   # Create the xtable with caption and label
-  out <- xtable(out, 
-                caption="AIC values for all models.", 
-                label="tab:AICTable", 
-                digits=1 #Only one number after the decimal place
-                )
+  out <- xtable(out, caption="AIC values for all models.", label="tab:AICTable", digits=1)
   return(out)

### 2013-02-06 EconGrowth.Rnw
Added new "to-do" item about u table and graph.
Added Martin as an author.
Moved tables to an appendix. Added a function that tests whether data is available. Added a parameters table for Cobb-Douglas with U.

@@
 \usepackage{soul} %Provides strikethrough text
+\usepackage{float} %Allows precise positioning of tables and figures within the text
 
@@
 \author[Calvin]{Lucas Timmer}
+\author[Stellenbosch]{Martin de Wit}
 \author[Calvin]{Matthew Kuperus Heun\corref{cor1}}
@@
 \address[Calvin]{Engineering Department, Calvin College, Grand Rapids, MI 49546, USA}
+\address[Stellenbosch]{ Stellenbosch University, School of Public Leadership, P.O. Box 610, Bellville 7535, South Africa}
 
@@
 \item \st{Heun: Add $u$ predictions for Cobb-Douglas}
+\item Heun: Add $u$ parameter table and graph
 \item Heun: Add covariance metrics.
+\item Heun: Add acknowledgements (Dad, Pruim)
 \item Heun: Eliminate blanks in the coefficient tables for the 95\% CIs in the Cobb-Douglas with energy rows. Asked Pruim about this via email but have not heard a response.
+\item Heun: move tables to an appendix at the end.
       \begin{itemize}
@@
   comment=NA,
+  eval=TRUE,
   warning=TRUE, #Tells whether to show warnings.
@@
 
-<<Load Data>>=
+<<Data, eval=TRUE>>=
 #################################
-# This function loads data given a country name.
+# This function loads data given a country abbreviation.
 # The file name from which data will be loaded is assumed to be of the form 
-# "<countryName>Data.txt". The file is assumed to exist in a subfolder of this project called "data".
+# "<countryAbbrev>Data.txt". The file is assumed to exist in a subfolder of this project called "data".
 #
-# countryName is a string containing the 2-letter abbreviation for the country, e.g. "US" or "CN"
+# countryAbbrev is a string containing the 2-letter abbreviation for the country, e.g. "US" or "CN"
 #
-# returns a matrix with the data that has been loaded
-##
-loadData <- function(countryName){
+# returns a data.frame with the data that has been loaded
+##
+loadData <- function(countryAbbrev){
   # Read the data file as a table with a header.  
-  fileName <- paste("data/", countryName, "Data.txt", sep="")
+  fileName <- paste("data/", countryAbbrev, "Data.txt", sep="")
   dataTable <- read.table(fileName, header = TRUE)
@@
   return(dataTable)
+}
+
+###############################
+# Tells whether we have data for this combination of country and energy type.
+# a missing energyType or energyType == NA means that we want to develop a model without energy, if possible.
+#
+# returns logical value (TRUE or FALSE)
+##
+haveData <- function(countryAbbrev, energyType){
+  # The design here is to go through several cases where data is unavailable and
+  # return FALSE. If we make it through all of those cases, we'll return TRUE.
+  if (!(countryAbbrev %in% countryAbbrevs)){
+    # If we don't know the country, we don't have data
+    return(FALSE)
+  }
+  if (missing(energyType) || is.na(energyType)){
+    # If we don't want energy included, we have data for all known countries. We need to check this case
+    # first, BEFORE doing various checks on the energyType.
+    return(TRUE)
+  }
+  if (!(energyType %in% energyTypes)){
+    # If we want to include energy, we know only a few types. So, return false if we don't know the energy type.
+    return(FALSE)
+  }
+  if (energyType == "U" && (!(countryAbbrev %in% countryAbbrevsU))){
+    # We have U data for only a few countries.
+    return(FALSE)
+  }
+  return(TRUE)
 }
@@
 
-<<cobb-douglas functions>>=
+<<cobb-douglas functions, eval=TRUE>>=
 ####################
@@
     # Consider this replacement only if energyType has been specified.
-    if (energyType == "U" && (countryAbbrev == "CN" || countryAbbrev == "ZA" || countryAbbrev == "SA" 
-                              || countryAbbrev == "IR" || countryAbbrev == "TZ" || countryAbbrev == "ZM")){
-      #Return a column of NAs if the above conditions have been met.
+    if (!(haveData(countryAbbrev, energyType))){
+      #If we don't have data for this combination of countryAbbrev and energyType, 
+      # return a column of NAs if the above conditions have been met.
       nRows <- 21 # All of these countries need 21 rows.
@@
 #
-# returns a vector of data for the Cobb-Douglas model. 
-# First item is the +95% CI on all parameters
-# Second item contains the parameter estimates
-# Third item is the -95% CI on all parameters
-# Each row has names: lambda, alpha, beta, gamma, corresponding to the parameters in the model.
-##
-cobbDouglasData <- function(countryName, energyType){
-  modelCD <- cobbDouglasModel(countryName, energyType)
+# returns a data.frame of data for the Cobb-Douglas model. 
+# First row is the +95% CI on all parameters
+# Second row contains the parameter estimates
+# Third row is the -95% CI on all parameters
+# Each column has names: lambda, alpha, beta, gamma, corresponding to the parameters in the model.
+##
+cobbDouglasData <- function(countryAbbrev, energyType){
+  #First, check to see if we want useful work (U) AND one of the countries for which we don't have data.
+  if (!haveData(countryAbbrev, energyType)){
+    #Return a column of NAs if the above conditions have been met.
+    nRows <- 3 # +95% CI, CDe, and -95% CI.
+    nCols <- 4 # lambda, alpha, beta, and gamma
+    df <- as.data.frame(matrix(NA, ncol = nCols, nrow = nRows))
+    colnames(df) <- c("lambda", "alpha", "beta", "gamma")
+    rownames(df) <- c("+95% CI", "CDe", "-95% CI")
+    return(df)
+  }
+  # We have a combination of country and energy type for which we have data.
+  modelCD <- cobbDouglasModel(countryAbbrev, energyType)
   summaryCD <- summary(modelCD) # Gives the nls summary table.
@@
     # The [1] subscripts pick off the lower confidence interval
-    lowerCD <- data.frame(lambda=ciCD["lambda","2.5%"], alpha=ciCD["a", "2.5%"], beta=betaCICD[1], gamma=gammaCICD[1])
+    lowerCD <- data.frame(lambda=ciCD["lambda","2.5%"], 
+                          alpha=ciCD["a", "2.5%"], 
+                          beta=betaCICD[1], 
+                          gamma=gammaCICD[1])
     row.names(lowerCD) <- "-95% CI"
-    # The [2] subscripts pick off the lower confidence interval
-    upperCD <- data.frame(lambda=ciCD["lambda","97.5%"], alpha=ciCD["a", "97.5%"], beta=betaCICD[2], gamma=gammaCICD[2])
+    # The [2] subscripts pick off the upper confidence interval
+    upperCD <- data.frame(lambda=ciCD["lambda","97.5%"], 
+                          alpha=ciCD["a", "97.5%"], 
+                          beta=betaCICD[2], 
+                          gamma=gammaCICD[2])
     row.names(upperCD) <- "+95% CI"
   }
-  # Now create the data for a table.
+  # Now create the data for a table and return it
   dataCD <- rbind(upperCD, estCD, lowerCD)
@@
 
-Table \ref{tab:CD_Parameters_No_Energy} gives the parameters for the Cobb-Douglas model without energy.
-
-<<CD_Params_Table, results='asis'>>=
-print(cobbDouglasParamsTableNoEnergy(), caption.placement="top", sanitize.colnames.function = identity, size="\\tiny")
-@
-
 Figure \ref{fig:CD_Params_Graph} shows values and 95\% confidence intervals for the parameters for the Cobb-Douglas model (without energy).
@@
 
-The Cobb-Douglas (with thermal energy, $q$) parameters are given in Table \ref{tab:CD_Parameters_With_Q}.
-
-<<CDq_Params_Table, results='asis'>>=
-print(cobbDouglasParamsTableWithEnergy("Q"), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny")
-@
-
 Figure \ref{fig:CDq_Params_Graph} shows values and 95\% confidence intervals for the parameters for the Cobb-Douglas model (with $q$).
 
-<<CDq_Params_Graph, fig.width=figWidth, fig.height=5, fig.cap="Cobb-Douglas (with $q$) model parameters. Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
+<<CDq_Params_Graph, fig.width=figWidth, fig.height=5, fig.cap="Cobb-Douglas (with $q$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
 createCDParamsGraph("Q")
@@
 
-<<CDx_Params_Graph, fig.width=figWidth, fig.height=5, fig.cap="Cobb-Douglas (with $x$) model parameters. Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
+<<CDx_Params_Graph, fig.width=figWidth, fig.height=5, fig.cap="Cobb-Douglas (with $x$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
 createCDParamsGraph("X")
@@
 Figure \ref{fig:CDx_Params_Graph} shows values and 95\% confidence intervals for the parameters for the Cobb-Douglas model (with $x$).
-
-<<CDx_Params_Table, results='asis'>>=
-print(cobbDouglasParamsTableWithEnergy("X"), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny")
-@
 
@@
 
+\section{Conclusion}
+
+****************** Add conclusion here. *********************
+
+\section{Acknowledgements}
+
+The authors thank Randall Pruim (Calvin College) and Loren L. Heun (Western Michigan University) for their insightful comments on and assistance with the statistical analyses presented herein.
+
 %% The Appendices part is started with the command \appendix;
@@
 %% \appendix
-
 %% \section{}
 %% \label{}
+
+\appendix
+\section{Tabular Results}
+
+Table \ref{tab:CD_Parameters_No_Energy} gives the parameters for the Cobb-Douglas model without energy.
+
+<<CD_Params_Table, results='asis'>>=
+print(cobbDouglasParamsTableNoEnergy(), 
+      caption.placement="top", 
+      sanitize.colnames.function = identity, 
+      size="\\tiny", 
+      table.placement="H")
+@
+
+The Cobb-Douglas (with thermal energy, $q$) parameters are given in Table \ref{tab:CD_Parameters_With_Q}.
+
+<<CDq_Params_Table, results='asis'>>=
+print(cobbDouglasParamsTableWithEnergy("Q"), 
+      caption.placement="top", 
+      sanitize.colnames.function = identity, 
+      size="\\tiny",
+      table.placement="H")
+@
+
+Table \ref{tab:CD_Parameters_With_X} gives the parameters for the Cobb-Douglas model with exergy ($x$).
+
+<<CDx_Params_Table, results='asis'>>=
+print(cobbDouglasParamsTableWithEnergy("X"), 
+      caption.placement="top", 
+      sanitize.colnames.function = identity, 
+      size="\\tiny",
+      table.placement="H")
+@
+
+The Cobb-Douglas (with useful work, $u$) parameters are given in Table \ref{tab:CD_Parameters_With_U}.
+
+<<CDu_Params_Table, results='asis', eval=TRUE>>=
+print(cobbDouglasParamsTableWithEnergy("U"), 
+      caption.placement="top", 
+      sanitize.colnames.function = identity, 
+      size="\\tiny",
+      table.placement="H")
+@
 

### 2013-02-08 EconGrowth.Rnw
Now calculating covariance tables for all countries.

@@
 
-**************** To Do List ********************
+\section*{To-do List}
 \begin{itemize}
 \item Reese: Add text from Word verson of paper to the LaTeX version.
-\item \st{Heun: Create a table of AIC values for each fit.}
-\item \st{Heun: Add $u$ predictions for Cobb-Douglas}
-\item Heun: Add $u$ parameter table and graph
-\item Heun: Add covariance metrics.
-\item Heun: Add acknowledgements (Dad, Pruim)
+\item Heun: Deal with missing covariance numbers when columns have unequal length.
+\item Heun: Add $k$, $l$, $q$, $x$, and $u$ ONLY fits
+\item Heun: Add CES production function fits
+\item Heun: Add Linex production function fits
 \item Heun: Eliminate blanks in the coefficient tables for the 95\% CIs in the Cobb-Douglas with energy rows. Asked Pruim about this via email but have not heard a response.
-\item Heun: move tables to an appendix at the end.
       \begin{itemize}
@@
 \item Heun: Fix warnings of the form ``Warning:  step factor 0.000488281 reduced below ’minFactor’ of 0.000976562'' in the code that generates the Cobb-Douglas with energy fits.
-\item Heun: Add CES production function fits
-\item Heun: Add Linex production function fits
-\item Heun: Add $k$, $l$, $q$, $x$, and $u$ ONLY fits
+\item \st{Heun: Create a table of AIC values for each fit.}
+\item \st{Heun: Add $u$ predictions for Cobb-Douglas}
+\item \st{Heun: move tables to an appendix at the end.}
+\item \st{Heun: Add acknowledgements (Dad, Pruim)}
+\item \st{Heun: Add $u$ parameter table and graph}
+\item \st{Heun: Add covariance metrics.}
 \end{itemize}
-*************************************************
-
-Caleb, put your LaTeX code here.
+
+\section{Introduction}
+
+*********** Caleb, put your LaTeX code here. *************
 
@@
   eval=TRUE,
-  warning=TRUE, #Tells whether to show warnings.
+  warning=FALSE, #Tells whether to show warnings.
   #Tells whether to cache output from chunks are saved. Cacheing saves time. 
@@
   dataTable <- read.table(fileName, header = TRUE)
-  # Identifies the header names associated with dataTable
-  #print(names(dataTable))
   return(dataTable)
@@
   return(TRUE)
+}
+
+##############################
+# Returns an xtable of covariance information for the specified country.
+##
+covarianceTable <- function(countryAbbrev){
+  data <- loadData(countryAbbrev)
+  # Grab only the data we want.
+  dataForCovar <- cbind(data$iGDP, data$iCapStk, data$iLabor, data$iQ, data$iX)
+  names <- c("$y$", "$k$", "$l$", "$q$", "$x$")
+  if (countryAbbrev %in% countryAbbrevsU){
+    # Add U data only if we have it.
+    dataForCovar <- cbind(dataForCovar, data$iU)
+    names <- c("$y$", "$k$", "$l$", "$q$", "$x$", "$u$")
+  }
+  covarResults <- cor(dataForCovar)
+  colnames(covarResults) <- names
+  rownames(covarResults) <- names
+  covarXtable <- xtable(covarResults, 
+                      caption=paste("Covariance table for ", countryAbbrev, "economy."), 
+                      label=paste("tab:Covar_", countryAbbrev, sep=""))
+                      # digits = c(1, 4,4,4, 2,2,2, 2,2,2),
+                      # align = "r|ccc|ccc|ccc") #Sets alignment of the numbers in the columns)
+  return(covarXtable)
 }
@@
 @
+
+Figure \ref{Factors_Lattice_Graph} shows that GDP ($y$), capital stock ($k$), labor ($l$), and the various energy types ($q$, $x$, and $u$) track each other quite closely.
+Covariances among these variables are quite high as shown in Tables \ref{tab:Covar_US} through \ref{tab:Covar_ZM} show.
 
@@
 
-\subsection{Cobb-Douglas with $q$}
+\subsection{Cobb-Douglas with thermal energy ($q$)}
 
@@
 
+\subsection{Cobb-Douglas with exergy ($x$)}
+
 The Cobb-Douglas (with exergy) parameters are given in Table \ref{tab:CD_Parameters_With_X}.
+
+Figure \ref{fig:CDx_Params_Graph} shows values and 95\% confidence intervals for the parameters for the Cobb-Douglas model (with $x$).
 
@@
 
-Figure \ref{fig:CDx_Params_Graph} shows values and 95\% confidence intervals for the parameters for the Cobb-Douglas model (with $x$).
+\subsection{Cobb-Douglas with useful work ($u$)}
+
+Figure \ref{fig:CDu_Params_Graph} shows values and 95\% confidence intervals for the parameters for the Cobb-Douglas model (with $u$).
+
+<<CDu_Params_Graph, fig.width=figWidth, fig.height=5, fig.cap="Cobb-Douglas (with $u$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
+createCDParamsGraph("U")
+@
 
@@
 
-\section{Acknowledgements}
+\section*{Acknowledgements}
 
@@
 
+\subsection{Covariances}
+
+The following tables show covariances among GDP ($y$) and factors of production ($k$, $l$, $q$, $x$, and $u$).
+
+<<Covar_Table_US, results='asis'>>=
+print(covarianceTable("US"), 
+                      caption.placement="top", 
+                      sanitize.rownames.function = identity,
+                      sanitize.colnames.function = identity,
+                      table.placement="H")
+@
+
+<<Covar_Table_UK, results='asis'>>=
+print(covarianceTable("UK"), 
+                      caption.placement="top", 
+                      sanitize.rownames.function = identity,
+                      sanitize.colnames.function = identity,
+                      table.placement="H")
+@
+
+<<Covar_Table_JP, results='asis'>>=
+print(covarianceTable("JP"), 
+                      caption.placement="top", 
+                      sanitize.rownames.function = identity,
+                      sanitize.colnames.function = identity,
+                      table.placement="H")
+@
+
+<<Covar_Table_CN, results='asis'>>=
+print(covarianceTable("CN"), 
+                      caption.placement="top", 
+                      sanitize.rownames.function = identity,
+                      sanitize.colnames.function = identity,
+                      table.placement="H")
+@
+
+<<Covar_Table_ZA, results='asis'>>=
+print(covarianceTable("ZA"), 
+                      caption.placement="top", 
+                      sanitize.rownames.function = identity,
+                      sanitize.colnames.function = identity,
+                      table.placement="H")
+@
+
+<<Covar_Table_SA, results='asis'>>=
+print(covarianceTable("SA"), 
+                      caption.placement="top", 
+                      sanitize.rownames.function = identity,
+                      sanitize.colnames.function = identity,
+                      table.placement="H")
+@
+
+<<Covar_Table_IR, results='asis'>>=
+print(covarianceTable("IR"), 
+                      caption.placement="top", 
+                      sanitize.rownames.function = identity,
+                      sanitize.colnames.function = identity,
+                      table.placement="H")
+@
+
+<<Covar_Table_TZ, results='asis'>>=
+print(covarianceTable("TZ"), 
+                      caption.placement="top", 
+                      sanitize.rownames.function = identity,
+                      sanitize.colnames.function = identity,
+                      table.placement="H")
+@
+
+<<Covar_Table_ZM, results='asis'>>=
+print(covarianceTable("ZM"), 
+                      caption.placement="top", 
+                      sanitize.rownames.function = identity,
+                      sanitize.colnames.function = identity,
+                      table.placement="H")
+@
+
+\subsection{Model Parameters}
+
 Table \ref{tab:CD_Parameters_No_Energy} gives the parameters for the Cobb-Douglas model without energy.
@@
 
-<<CDu_Params_Table, results='asis', eval=TRUE>>=
+<<CDu_Params_Table, results='asis'>>=
 print(cobbDouglasParamsTableWithEnergy("U"), 

### 2013-02-10 EconGrowth.Rnw
Now forcing figure positions with "H". Began writing text for single-factor economic model analysis.

@@
 
-\section{The Facts}
-
-Figure \ref{fig:Factors_Lattice_Graph} shows the ``facts'' as they are known.
-
-<<Factors_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.cap="The facts.
+\section{Historical Data}
+
+Figure \ref{fig:Factors_Lattice_Graph} shows historical data.
+GDP ($y$), capital stock ($k$), labor ($l$), and the various energy types ($q$, $x$, and $u$) track each other closely.
+Covariances among these variables are rather high as shown in Tables \ref{tab:Covar_US} through \ref{tab:Covar_ZM}.
+
+<<Factors_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.pos="H", fig.cap="The facts.
 Indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$).">>=
@@
 
-Figure \ref{Factors_Lattice_Graph} shows that GDP ($y$), capital stock ($k$), labor ($l$), and the various energy types ($q$, $x$, and $u$) track each other quite closely.
-Covariances among these variables are quite high as shown in Tables \ref{tab:Covar_US} through \ref{tab:Covar_ZM} show.
+\section{Single-factor Models}
+
+<<single-factor functions, eval=TRUE>>=
+
+@
+
+We begin by fitting single-factor economic models of the form
+
+\begin{equation} \label{eq:Single_Factor_Generic}
+  y = a^{\lambda (t-t_0)}f^{m}
+\end{equation}
+
+\noindent to historical data where the factor of production ($f$) is any of $k$, $l$, $q$, $x$, or $u$ and the exponent ($m$) is $\alpha$ for $k$, $\beta$ for $l$, and $\gamma$ for $q$, $x$, or $u$.
 
@@
 
-<<CD_Params_Graph, fig.width=figWidth, fig.height=5, fig.cap="Cobb-Douglas (without energy) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
+<<CD_Params_Graph, fig.width=figWidth, fig.height=5, fig.pos="H", fig.cap="Cobb-Douglas (without energy) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
 createCDParamsGraph()
@@
 
-<<CDq_Params_Graph, fig.width=figWidth, fig.height=5, fig.cap="Cobb-Douglas (with $q$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
+<<CDq_Params_Graph, fig.width=figWidth, fig.height=5, fig.pos="H", fig.cap="Cobb-Douglas (with $q$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
 createCDParamsGraph("Q")
@@
 
-<<CDx_Params_Graph, fig.width=figWidth, fig.height=5, fig.cap="Cobb-Douglas (with $x$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
+<<CDx_Params_Graph, fig.width=figWidth, fig.height=5, fig.pos="H", fig.cap="Cobb-Douglas (with $x$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
 createCDParamsGraph("X")
@@
 
-<<CDu_Params_Graph, fig.width=figWidth, fig.height=5, fig.cap="Cobb-Douglas (with $u$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
+<<CDu_Params_Graph, fig.width=figWidth, fig.height=5, fig.pos="H", fig.cap="Cobb-Douglas (with $u$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
 createCDParamsGraph("U")
@@
 
-<<CD_GDP_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.cap="Cobb-Douglas results.">>=
+<<CD_GDP_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.pos="H", fig.cap="Cobb-Douglas results.">>=
 createCDLatticeGraph()

### 2013-02-10 EconGrowth.Rnw
Changed labels for covariance tables, spelling out "Covariance" in its entirety.

@@
                       caption=paste("Covariance table for ", countryAbbrev, "economy."), 
-                      label=paste("tab:Covar_", countryAbbrev, sep=""))
+                      label=paste("tab:Covariance_", countryAbbrev, sep=""))
                       # digits = c(1, 4,4,4, 2,2,2, 2,2,2),
@@
 GDP ($y$), capital stock ($k$), labor ($l$), and the various energy types ($q$, $x$, and $u$) track each other closely.
-Covariances among these variables are rather high as shown in Tables \ref{tab:Covar_US} through \ref{tab:Covar_ZM}.
+Covariances among these variables are rather high as shown in Tables \ref{tab:iance_US} through \ref{tab:Covariance_ZM}.
 
@@
 
-<<Covar_Table_US, results='asis'>>=
+<<Covariance_Table_US, results='asis'>>=
 print(covarianceTable("US"), 
@@
 
-<<Covar_Table_UK, results='asis'>>=
+<<Covariance_Table_UK, results='asis'>>=
 print(covarianceTable("UK"), 
@@
 
-<<Covar_Table_JP, results='asis'>>=
+<<Covariance_Table_JP, results='asis'>>=
 print(covarianceTable("JP"), 
@@
 
-<<Covar_Table_CN, results='asis'>>=
+<<Covariance_Table_CN, results='asis'>>=
 print(covarianceTable("CN"), 
@@
 
-<<Covar_Table_ZA, results='asis'>>=
+<<Covariance_Table_ZA, results='asis'>>=
 print(covarianceTable("ZA"), 
@@
 
-<<Covar_Table_SA, results='asis'>>=
+<<Covariance_Table_SA, results='asis'>>=
 print(covarianceTable("SA"), 
@@
 
-<<Covar_Table_IR, results='asis'>>=
+<<Covariance_Table_IR, results='asis'>>=
 print(covarianceTable("IR"), 
@@
 
-<<Covar_Table_TZ, results='asis'>>=
+<<Covariance_Table_TZ, results='asis'>>=
 print(covarianceTable("TZ"), 
@@
 
-<<Covar_Table_ZM, results='asis'>>=
+<<Covariance_Table_ZM, results='asis'>>=
 print(covarianceTable("ZM"), 

### 2013-02-10 EconGrowth.Rnw
Added new to-do item for variables for fighre height and width where not already implemented.
Now including a graph of single-factor models in the paper.

@@
 \item Reese: Add text from Word verson of paper to the LaTeX version.
+\item Heun: Add setup variables for figure height and width where not already included.
 \item Heun: Deal with missing covariance numbers when columns have unequal length.
@@
 opts_chunk$set(
+  # ********************************************************************************************************
+  eval=TRUE,
+  # ********************************************************************************************************
+  warning=FALSE, #Tells whether to show warnings.
   dev='tikz',    #Allows LaTeX code in graphical output. E.g., "$y$" for a variable name in the legend for a graph.
@@
   comment=NA,
-  eval=TRUE,
-  warning=FALSE, #Tells whether to show warnings.
   #Tells whether to cache output from chunks are saved. Cacheing saves time. 
@@
 
+#####################
+# This function adds NA rows to the end of a data.frame to ensure that the df is 
+# the same length as the country data set
+# returns a modified version of df that includes the padded rows filled with "NA".
+##
+padRows <- function(countryAbbrev, df){
+  nRowsData <- nrow(loadData(countryAbbrev)) #Gets number of rows in data set
+  nRowsDF <- nrow(df)
+  nRowsToAdd <- nRowsData - nRowsDF
+  nCol <- ncol(df)
+  dfToAppend <- as.data.frame(matrix(NA, ncol=nCol, nrow=nRowsToAdd))
+  colnames(dfToAppend) <- colnames(df)
+  return(rbind(df, dfToAppend))
+}
+
+##############################
+# Returns an integer representing the column index for some data
+# dataTable the data.frame in which you want to change column names
+# factor should be a string and one of Year, Y, K, L, Q, X, or U
+##
+columnIndex <- function(dataTable, factor){
+  if (factor == "Year"){
+    colName <- "iYear"
+  } else if (factor == "Y"){
+    colName <- "iGDP"
+  } else if (factor == "K"){
+    colName <- "iCapStk"
+  } else if (factor == "L"){
+    colName <- "iLabor"
+  } else if (factor == "Q"){
+    colName <- "iQ"
+  } else if (factor == "X"){
+    colName <- "iX"
+  } else if (factor == "U"){
+    colName <- "iU"
+  } else {
+    print(paste("Unknown factor:", factor, "in colIndex. Terminating execution."))
+    quit()
+  }
+  # Get the desired column index.
+  colIndex <- which(names(dataTable) %in% colName) #Find index of desired column
+  return(colIndex)  
+}
+
+##############################
+# Replaces a column name with the given string
+# dataTable the data.frame that you're working with
+# factor should be a string and one of Year, Y, K, L, Q, X, or U
+# newName should be a string and the desired new name of the column
+# returns dataTable with a new name for one of its factor column.
+##
+replaceColName <- function(dataTable, factor, newName){
+  colIndex <- columnIndex(dataTable, factor)
+  colnames(dataTable)[colIndex] <- newName #Change desired column name to newName
+  return(dataTable)
+}
+
 ##############################
@@
 
-Figure \ref{fig:Factors_Lattice_Graph} shows historical data.
-GDP ($y$), capital stock ($k$), labor ($l$), and the various energy types ($q$, $x$, and $u$) track each other closely.
-Covariances among these variables are rather high as shown in Tables \ref{tab:iance_US} through \ref{tab:Covariance_ZM}.
-
-<<Factors_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.pos="H", fig.cap="The facts.
+Figure \ref{fig:Factors_Lattice_Graph} shows historical data, including GDP ($y$), capital stock ($k$), labor ($l$), and the various energy types ($q$, $x$, and $u$).
+Facotrs of production track each other closely, and large covariances among these variables can be seen in Tables \ref{tab:Covariance_US} through \ref{tab:Covariance_ZM}.
+
+<<Factors_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.pos="H", fig.cap="Historical data.
 Indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$).">>=
@@
 <<single-factor functions, eval=TRUE>>=
+####################
+# Returns an nls single-factor model for the country and factor specified.
+# factor should be one of "K", "L", "Q", "X", or "U".
+##
+singleFactorModel <- function(countryAbbrev, factor){
+  dataTable <- loadData(countryAbbrev) #Load the data that we need.
+  # We'll change the name of the desired column to "f"
+  dataTable <- replaceColName(dataTable, factor, "f")
+  # Now do the fit.
+  lambdaGuess <- 0.0 #guessing lambda = 0 means there is no technological progress.
+  mGuess <- 0.5
+  # Runs a non-linear least squares fit to the data. We've replaced beta with 1-alpha for simplicity.
+  modelSF <- nls(iGDP ~ exp(lambda*iYear) * f^m, 
+                 data=dataTable, 
+                 start = list(lambda=lambdaGuess, m=mGuess)
+                 )
+  return(modelSF)
+}
+
+#########################
+# Takes the single-factor fitted models and creates per-country predictions for them.
+# Returns a data.frame with the predictions.
+##
+singleFactorPredictions <- function(countryAbbrev, factor){
+  # Can't make predictions for any of CN, ZA, SA, IR, TZ, or ZM if we're interested in U
+  if (factor == "U"){
+    if (!(haveData(countryAbbrev, factor))){
+      #If we don't have data for this combination of countryAbbrev and energyType, 
+      # return a column of NAs if the above conditions have been met.
+      nRows <- 21 # All of these countries need 21 rows.
+      df <- as.data.frame(matrix(NA, ncol = 1, nrow = nRows))
+      colnames(df) <- "pred"
+      return(df)
+    }
+  }
+  model <- singleFactorModel(countryAbbrev, factor)
+  pred <- predict(model) #See http://stackoverflow.com/questions/9918807/how-get-plot-from-nls-in-r
+  df <- data.frame(pred)
+  # Pad with rows as necessary
+  df <- padRows(countryAbbrev, df)
+  return(df)
+}
+
+#########################
+# Takes the single-factor fitted models and creates a single column of predicted GDP values
+# that corresponds, row for row, with the AllData.txt file.
+##
+singleFactorPredictionsColumn <- function(factor){
+  out <- do.call("rbind", lapply(countryAbbrevs, singleFactorPredictions, factor=factor))
+  colnames(out) <- c(paste("predGDP", factor, sep=""))
+  return(out)
+}
+
+##############################
+# Creates a graph that plots predicted GDP as lines, one for each single factor, and historical GDP 
+# data as open circles.
+##
+createSFLatticeGraph <- function(){
+  dataTable <- loadData("All") #Grab the raw data
+  predictionsK <- singleFactorPredictionsColumn("K") #Predictions from SF with K
+  predictionsL <- singleFactorPredictionsColumn("L") #Predictions from SF with L
+  predictionsQ <- singleFactorPredictionsColumn("Q") #Predictions from SF with Q
+  predictionsX <- singleFactorPredictionsColumn("X") #Predictions from SF with X
+  predictionsU <- singleFactorPredictionsColumn("U") #Predictions from SF with U
+  #Now add the predictions columns to the data.
+  dataTable <- cbind(dataTable, predictionsK, predictionsL, predictionsQ, predictionsX, predictionsU) 
+  graphType <- "b" #b is for both line and symbol
+  lineTypes <- c(0, 1, 2, 4, 1, 1) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
+  lineWidths <- c(0, 2, 1, 1, 1, 1) #line widths. 0 means no line.
+  colors <- c("black", "black", "red", "blue", "darkorange", "darkgreen") #line and symbol colors
+  symbols <- c(1, NA, NA, NA, NA, NA)  #NA gives no symbol.
+  graph <- xyplot(iGDP+predGDPK+predGDPL+predGDPQ+predGDPX+predGDPU ~ Year | Country, data=dataTable,
+                  type=graphType,
+                  index.cond=list(countryOrderForGraphs), #orders the panels.
+                  layout=layoutSpec, #indicates a 3x3 arrangement of panels.
+                  strip = strip.custom(factor.levels=countryNamesAlph, bg="white"), #Sets strip parameters
+                  as.table=TRUE, #indexing of panels starts in upper left and goes across rows.
+                  lty = lineTypes, lwd = lineWidths, col = colors, #Controls line parameters
+                  pch = symbols, col.symbol = colors, #Controls symbol parameters
+                  key=list(text=list(c("Actual", "With $k$", "With $l$", "With $q$", "With $x$", "With $u$")),
+                           type=graphType,
+                           cex=keyTextSize, #controls size of text in the key
+                           lines=list(lty=lineTypes, lwd=lineWidths), #controls line types
+                           pch=symbols, col=colors, #controls symbol (plot characters) types
+                           columns=keyColumns, x=keyXLoc, y=keyYLoc), #controls columns and position of the key
+                  scales=list(cex=scaleTextSize, #controls text size on scales.
+                              tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
+                              y=list(relation="free", #allows each axis to be different
+                                     at=c(1,2,3,4,5,6,7,8,9,10) #tick mark locations
+                                     )
+                              ), 
+                  ylim=list(c(1,8), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3)),
+                  xlab="", ylab="Indexed GDP (1980=1 or 1991=1)") #axis labels
+  return(graph)
+}
+
+# print(singleFactorPredictions("US", "K"))
+# print(singleFactorPredictionsColumn("K"))
+# print(singleFactorPredictionsColumn("L"))
+# print(singleFactorPredictionsColumn("Q"))
+# print(singleFactorPredictionsColumn("X"))
+# print(singleFactorPredictionsColumn("U"))
+# print(createSFLatticeGraph())
 
@@
 \noindent to historical data where the factor of production ($f$) is any of $k$, $l$, $q$, $x$, or $u$ and the exponent ($m$) is $\alpha$ for $k$, $\beta$ for $l$, and $\gamma$ for $q$, $x$, or $u$.
+
+<<SF_GDP_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.pos="H", fig.cap="Single-factor results.">>=
+createSFLatticeGraph()
+@
 
@@
     # to "iEToFit" and use "iEToFit" in the nls function. 
-    energyColumnName <- paste("i", energyType, sep="") #Energy term desired in the Cobb-Douglas equation.
-    eColIndex <- which(names(dataTable) %in% energyColumnName) #Find index of desired column
-    colnames(dataTable)[eColIndex] <- "iEToFit" #Change desired column name to "iEToFit"
+    dataTable <- replaceColName(dataTable, energyType, "iEToFit")
     # Reparameterize to ensure that we meet the constraints:
@@
   return(df)
-}
-
-#####################
-# This function adds NA rows to a data.frame to ensure that the df is the same length as the country data set
-##
-padRows <- function(countryAbbrev, df){
-  nRowsData <- nrow(loadData(countryAbbrev)) #Gets number of rows in data set
-  nRowsDF <- nrow(df)
-  nRowsToAdd <- nRowsData - nRowsDF
-  nCol <- ncol(df)
-  dfToAppend <- as.data.frame(matrix(NA, ncol=nCol, nrow=nRowsToAdd))
-  colnames(dfToAppend) <- colnames(df)
-  return(rbind(df, dfToAppend))
 }

### 2013-02-11 EconGrowth.Rnw
Now including single-factor models in the AIC table. Also, restarting table numbering in each appendix. Now using variables for figure height on all parameter tables.

@@
 \item Heun: Deal with missing covariance numbers when columns have unequal length.
-\item Heun: Add $k$, $l$, $q$, $x$, and $u$ ONLY fits
+\item Heun: Add single factor fits
+      \begin{itemize}
+      \item \st{GDP comparison graph}
+      \item parameter graphs ($\lambda$ and $m$) for each country
+      \item parameter tables for each country in the appendix
+      \item \st{AIC rows in the AIC table}
+      \end{itemize}
 \item Heun: Add CES production function fits
+      \begin{itemize}
+      \item GDP comparison graph
+      \item parameter graphs ($\lambda$ and $m$) for each country
+      \item parameter tables for each country in the appendix
+      \item AIC rows in the AIC table
+      \end{itemize}
 \item Heun: Add Linex production function fits
+      \begin{itemize}
+      \item GDP comparison graph
+      \item parameter graphs ($\lambda$ and $m$) for each country
+      \item parameter tables for each country in the appendix
+      \item AIC rows in the AIC table
+      \end{itemize}
 \item Heun: Eliminate blanks in the coefficient tables for the 95\% CIs in the Cobb-Douglas with energy rows. Asked Pruim about this via email but have not heard a response.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 # Full page lattice plot sizes and other parameters
-layoutSpec <- c(3,3) #indicates a 3x3 arrangement of panels.
+ninePanelLayoutSpec <- c(3,3) #indicates a 3x3 arrangement of panels.
 figWidth <- 6.5             #Inches
-figHeight <- 7.5 #Inches
+ninePanelGraphHeight <- 7.5 #Inches
+parameterGraphHeight <- 5   #Inches
 keyTextSize <- 0.85 #85% of normal size
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Historical Data}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-<<Factors_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.pos="H", fig.cap="Historical data.
+<<Factors_Lattice_Graph, fig.width=figWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="Historical data.
 Indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$).">>=
@@
                   index.cond = list(countryOrderForGraphs), #orders the panels.
-                  layout = layoutSpec, 
+                  layout = ninePanelLayoutSpec, 
                   strip = strip.custom(factor.levels=countryNamesAlph, bg="white"), #Sets strip parameters
@@
 
-\section{Single-factor Models}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Single-factor Models (SF)}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
   graphType <- "b" #b is for both line and symbol
-  lineTypes <- c(0, 1, 2, 4, 1, 1) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
-  lineWidths <- c(0, 2, 1, 1, 1, 1) #line widths. 0 means no line.
-  colors <- c("black", "black", "red", "blue", "darkorange", "darkgreen") #line and symbol colors
+  lineTypes <- c(0, 1, 5, 2, 4, 1) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
+  lineWidths <- c(0, 2, 2, 1, 1, 1) #line widths. 0 means no line.
+  colors <- c("black", "black", "black", "red", "blue", "darkorange") #line and symbol colors
   symbols <- c(1, NA, NA, NA, NA, NA)  #NA gives no symbol.
@@
                   index.cond=list(countryOrderForGraphs), #orders the panels.
-                  layout=layoutSpec, #indicates a 3x3 arrangement of panels.
+                  layout=ninePanelLayoutSpec, #indicates a 3x3 arrangement of panels.
                   strip = strip.custom(factor.levels=countryNamesAlph, bg="white"), #Sets strip parameters
@@
 }
-
-# print(singleFactorPredictions("US", "K"))
-# print(singleFactorPredictionsColumn("K"))
-# print(singleFactorPredictionsColumn("L"))
-# print(singleFactorPredictionsColumn("Q"))
-# print(singleFactorPredictionsColumn("X"))
-# print(singleFactorPredictionsColumn("U"))
-# print(createSFLatticeGraph())
-
 @
@@
 
-\noindent to historical data where the factor of production ($f$) is any of $k$, $l$, $q$, $x$, or $u$ and the exponent ($m$) is $\alpha$ for $k$, $\beta$ for $l$, and $\gamma$ for $q$, $x$, or $u$.
-
-<<SF_GDP_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.pos="H", fig.cap="Single-factor results.">>=
+\noindent to historical data where the factor of production ($f$) is any of $k$, $l$, $q$, $x$, or $u$, and the exponent ($m$) is $\alpha$ for $k$, $\beta$ for $l$, or $\gamma$ for $q$, $x$, or $u$.
+
+Figure \ref{fig:SF_GDP_Lattice_Graph} compares single-factor model predictions with historica data.
+
+<<SF_GDP_Lattice_Graph, fig.width=figWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="Single-factor results.">>=
 createSFLatticeGraph()
@@
 
-\section{Cobb-Douglas Without Energy}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Cobb-Douglas Models Without Energy (CD)}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 }
+
 @
@@
 
-<<CD_Params_Graph, fig.width=figWidth, fig.height=5, fig.pos="H", fig.cap="Cobb-Douglas (without energy) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
+<<CD_Params_Graph, fig.width=figWidth, fig.height=parameterGraphHeight, fig.pos="H", fig.cap="Cobb-Douglas (without energy) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
 createCDParamsGraph()
@@
 
-\section{Cobb-Douglas With Energy}
+\section{Cobb-Douglas Models With Energy (CDe)}
 
@@
 
-<<CDq_Params_Graph, fig.width=figWidth, fig.height=5, fig.pos="H", fig.cap="Cobb-Douglas (with $q$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
+<<CDq_Params_Graph, fig.width=figWidth, fig.height=parameterGraphHeight, fig.pos="H", fig.cap="Cobb-Douglas (with $q$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
 createCDParamsGraph("Q")
@@
 
-<<CDx_Params_Graph, fig.width=figWidth, fig.height=5, fig.pos="H", fig.cap="Cobb-Douglas (with $x$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
+<<CDx_Params_Graph, fig.width=figWidth, fig.height=parameterGraphHeight, fig.pos="H", fig.cap="Cobb-Douglas (with $x$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
 createCDParamsGraph("X")
@@
 
-<<CDu_Params_Graph, fig.width=figWidth, fig.height=5, fig.pos="H", fig.cap="Cobb-Douglas (with $u$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
+<<CDu_Params_Graph, fig.width=figWidth, fig.height=parameterGraphHeight, fig.pos="H", fig.cap="Cobb-Douglas (with $u$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
 createCDParamsGraph("U")
@@
 
-<<CD_GDP_Lattice_Graph, fig.width=figWidth, fig.height=figHeight, fig.pos="H", fig.cap="Cobb-Douglas results.">>=
+<<CD_GDP_Lattice_Graph, fig.width=figWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="Cobb-Douglas results.">>=
 createCDLatticeGraph()
@@
 
-\section{CES}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{CES Models}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \subsection{CES with $Q$}
+
 <<CESq analysisQ, eval=FALSE>>=
@@
 
-\section{LINEX}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{LINEX Models}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\section{Goodness of Fit}
-
-<<AIC_Analysis>>=
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusion}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+****************** Add conclusion here. *********************
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Acknowledgements}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Funding for Caleb Reese and Lucas Timmer was graciously supplied by the Jack and Lois Kuipers Applied Mathematics Endowment and the Calvin College Alumni Association.
+The authors thank Randall Pruim (Calvin College) and Loren L.
+Heun (Western Michigan University) for their insightful comments on and invaluable assistance with the statistical analyses presented herein.
+
+%% The Appendices part is started with the command \appendix;
+%% appendix sections are then done as normal sections
+%% \appendix
+%% \section{}
+%% \label{}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\appendix
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Covariance Tables}
+\setcounter{table}{0} % Restarts table number counter at 0 in this section.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The following tables show covariances among GDP ($y$) and factors of production ($k$, $l$, $q$, $x$, and $u$).
+
+<<Covariance_Table_US, results='asis'>>=
+print(covarianceTable("US"), 
+                      caption.placement="top", 
+                      sanitize.rownames.function = identity,
+                      sanitize.colnames.function = identity,
+                      table.placement="H")
+@
+
+<<Covariance_Table_UK, results='asis'>>=
+print(covarianceTable("UK"), 
+                      caption.placement="top", 
+                      sanitize.rownames.function = identity,
+                      sanitize.colnames.function = identity,
+                      table.placement="H")
+@
+
+<<Covariance_Table_JP, results='asis'>>=
+print(covarianceTable("JP"), 
+                      caption.placement="top", 
+                      sanitize.rownames.function = identity,
+                      sanitize.colnames.function = identity,
+                      table.placement="H")
+@
+
+<<Covariance_Table_CN, results='asis'>>=
+print(covarianceTable("CN"), 
+                      caption.placement="top", 
+                      sanitize.rownames.function = identity,
+                      sanitize.colnames.function = identity,
+                      table.placement="H")
+@
+
+<<Covariance_Table_ZA, results='asis'>>=
+print(covarianceTable("ZA"), 
+                      caption.placement="top", 
+                      sanitize.rownames.function = identity,
+                      sanitize.colnames.function = identity,
+                      table.placement="H")
+@
+
+<<Covariance_Table_SA, results='asis'>>=
+print(covarianceTable("SA"), 
+                      caption.placement="top", 
+                      sanitize.rownames.function = identity,
+                      sanitize.colnames.function = identity,
+                      table.placement="H")
+@
+
+<<Covariance_Table_IR, results='asis'>>=
+print(covarianceTable("IR"), 
+                      caption.placement="top", 
+                      sanitize.rownames.function = identity,
+                      sanitize.colnames.function = identity,
+                      table.placement="H")
+@
+
+<<Covariance_Table_TZ, results='asis'>>=
+print(covarianceTable("TZ"), 
+                      caption.placement="top", 
+                      sanitize.rownames.function = identity,
+                      sanitize.colnames.function = identity,
+                      table.placement="H")
+@
+
+<<Covariance_Table_ZM, results='asis'>>=
+print(covarianceTable("ZM"), 
+                      caption.placement="top", 
+                      sanitize.rownames.function = identity,
+                      sanitize.colnames.function = identity,
+                      table.placement="H")
+@
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Model Parameters}
+\setcounter{table}{0} % Restarts table number counter at 0 in this section.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Table \ref{tab:CD_Parameters_No_Energy} gives the parameters for the Cobb-Douglas model without energy.
+
+<<CD_Params_Table, results='asis'>>=
+print(cobbDouglasParamsTableNoEnergy(), 
+      caption.placement="top", 
+      sanitize.colnames.function = identity, 
+      size="\\tiny", 
+      table.placement="H")
+@
+
+The Cobb-Douglas (with thermal energy, $q$) parameters are given in Table \ref{tab:CD_Parameters_With_Q}.
+
+<<CDq_Params_Table, results='asis'>>=
+print(cobbDouglasParamsTableWithEnergy("Q"), 
+      caption.placement="top", 
+      sanitize.colnames.function = identity, 
+      size="\\tiny",
+      table.placement="H")
+@
+
+Table \ref{tab:CD_Parameters_With_X} gives the parameters for the Cobb-Douglas model with exergy ($x$).
+
+<<CDx_Params_Table, results='asis'>>=
+print(cobbDouglasParamsTableWithEnergy("X"), 
+      caption.placement="top", 
+      sanitize.colnames.function = identity, 
+      size="\\tiny",
+      table.placement="H")
+@
+
+The Cobb-Douglas (with useful work, $u$) parameters are given in Table \ref{tab:CD_Parameters_With_U}.
+
+<<CDu_Params_Table, results='asis'>>=
+print(cobbDouglasParamsTableWithEnergy("U"), 
+      caption.placement="top", 
+      sanitize.colnames.function = identity, 
+      size="\\tiny",
+      table.placement="H")
+@
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Goodness of fit}
+\setcounter{table}{0} % Restarts table number counter at 0 in this section.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+<<AIC_Table_Functions>>=
 ###############################
@@
 createAICTable <- function(){
-  # Cobb-Douglas
-  models <- lapply(countryAbbrevs, cobbDouglasModel)
-  aicCD <- data.frame(lapply(models, AIC))
+  # Single-factor with K
+  sfKModels <- lapply(countryAbbrevs, singleFactorModel, factor="K")
+  aicSFk <- data.frame(lapply(sfKModels, AIC))
+  rownames(aicSFk) <- "SF$k$"
+  # Single-factor with L
+  sfLModels <- lapply(countryAbbrevs, singleFactorModel, factor="L")
+  aicSFl <- data.frame(lapply(sfLModels, AIC))
+  rownames(aicSFl) <- "SF$l$"
+  # Single-factor with Q
+  sfQModels <- lapply(countryAbbrevs, singleFactorModel, factor="Q")
+  aicSFq <- data.frame(lapply(sfQModels, AIC))
+  rownames(aicSFq) <- "SF$q$"
+  # Single-factor with X
+  sfXModels <- lapply(countryAbbrevs, singleFactorModel, factor="X")
+  aicSFx <- data.frame(lapply(sfXModels, AIC))
+  rownames(aicSFx) <- "SF$x$"
+  # Single-factor with U
+  aicSFu <- cbind(US=AIC(singleFactorModel("US", "U")), 
+                  UK=AIC(singleFactorModel("UK", "U")), 
+                  JP=AIC(singleFactorModel("JP", "U")),
+                  CN=NA, ZA=NA, SA=NA, IR=NA, TZ=NA, ZM=NA) #No U data for these countries.
+  rownames(aicSFu) <- "SF$u$"
+  # Cobb-Douglas models
+  cdModels <- lapply(countryAbbrevs, cobbDouglasModel)
+  aicCD <- data.frame(lapply(cdModels, AIC))
   rownames(aicCD) <- "CD"
   # Cobb-Douglas with Q
-  models <- lapply(countryAbbrevs, cobbDouglasModel, energyType="Q")
-  aicCDq <- data.frame(lapply(models, AIC))
+  cdQModels <- lapply(countryAbbrevs, cobbDouglasModel, energyType="Q")
+  aicCDq <- data.frame(lapply(cdQModels, AIC))
   rownames(aicCDq) <- "CD$q$"
   # Cobb-Douglas with X
-  models <- lapply(countryAbbrevs, cobbDouglasModel, energyType="X")
-  aicCDx <- data.frame(lapply(models, AIC))
+  cdXModels <- lapply(countryAbbrevs, cobbDouglasModel, energyType="X")
+  aicCDx <- data.frame(lapply(cdXModels, AIC))
   rownames(aicCDx) <- "CD$x$"
   # Cobb-Douglas with U
-  models <- c(cobbDouglasModel("US", "U"), cobbDouglasModel("UK", "U"), cobbDouglasModel("JP", "U"))
+  cdUModels <- c(cobbDouglasModel("US", "U"), cobbDouglasModel("UK", "U"), cobbDouglasModel("JP", "U"))
   aicCDu <- cbind(US=AIC(cobbDouglasModel("US", "U")), 
@@
   # Create the data.frame table
-  out <- rbind(aicCD, aicCDq, aicCDx, aicCDu) 
+  out <- rbind(aicSFk, aicSFl, aicSFq, aicSFx, aicSFu, aicCD, aicCDq, aicCDx, aicCDu) 
   # Create the xtable with caption and label
@@
 
-<<AIC_Table, results='asis', label="AIC_Table">>=
+<<AIC_Table, results='asis', label="AIC_Table", eval=TRUE>>=
 print(createAICTable(), 
@@
       sanitize.rownames.function = identity)
-
-@
-
-The AIC results show *****************.
-
-\section{Conclusion}
-
-****************** Add conclusion here. *********************
-
-\section*{Acknowledgements}
-
-The authors thank Randall Pruim (Calvin College) and Loren L. Heun (Western Michigan University) for their insightful comments on and assistance with the statistical analyses presented herein.
-
-%% The Appendices part is started with the command \appendix;
-%% appendix sections are then done as normal sections
-%% \appendix
-%% \section{}
-%% \label{}
-
-\appendix
-\section{Tabular Results}
-
-\subsection{Covariances}
-
-The following tables show covariances among GDP ($y$) and factors of production ($k$, $l$, $q$, $x$, and $u$).
-
-<<Covariance_Table_US, results='asis'>>=
-print(covarianceTable("US"), 
-                      caption.placement="top", 
-                      sanitize.rownames.function = identity,
-                      sanitize.colnames.function = identity,
-                      table.placement="H")
-@
-
-<<Covariance_Table_UK, results='asis'>>=
-print(covarianceTable("UK"), 
-                      caption.placement="top", 
-                      sanitize.rownames.function = identity,
-                      sanitize.colnames.function = identity,
-                      table.placement="H")
-@
-
-<<Covariance_Table_JP, results='asis'>>=
-print(covarianceTable("JP"), 
-                      caption.placement="top", 
-                      sanitize.rownames.function = identity,
-                      sanitize.colnames.function = identity,
-                      table.placement="H")
-@
-
-<<Covariance_Table_CN, results='asis'>>=
-print(covarianceTable("CN"), 
-                      caption.placement="top", 
-                      sanitize.rownames.function = identity,
-                      sanitize.colnames.function = identity,
-                      table.placement="H")
-@
-
-<<Covariance_Table_ZA, results='asis'>>=
-print(covarianceTable("ZA"), 
-                      caption.placement="top", 
-                      sanitize.rownames.function = identity,
-                      sanitize.colnames.function = identity,
-                      table.placement="H")
-@
-
-<<Covariance_Table_SA, results='asis'>>=
-print(covarianceTable("SA"), 
-                      caption.placement="top", 
-                      sanitize.rownames.function = identity,
-                      sanitize.colnames.function = identity,
-                      table.placement="H")
-@
-
-<<Covariance_Table_IR, results='asis'>>=
-print(covarianceTable("IR"), 
-                      caption.placement="top", 
-                      sanitize.rownames.function = identity,
-                      sanitize.colnames.function = identity,
-                      table.placement="H")
-@
-
-<<Covariance_Table_TZ, results='asis'>>=
-print(covarianceTable("TZ"), 
-                      caption.placement="top", 
-                      sanitize.rownames.function = identity,
-                      sanitize.colnames.function = identity,
-                      table.placement="H")
-@
-
-<<Covariance_Table_ZM, results='asis'>>=
-print(covarianceTable("ZM"), 
-                      caption.placement="top", 
-                      sanitize.rownames.function = identity,
-                      sanitize.colnames.function = identity,
-                      table.placement="H")
-@
-
-\subsection{Model Parameters}
-
-Table \ref{tab:CD_Parameters_No_Energy} gives the parameters for the Cobb-Douglas model without energy.
-
-<<CD_Params_Table, results='asis'>>=
-print(cobbDouglasParamsTableNoEnergy(), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny", 
-      table.placement="H")
-@
-
-The Cobb-Douglas (with thermal energy, $q$) parameters are given in Table \ref{tab:CD_Parameters_With_Q}.
-
-<<CDq_Params_Table, results='asis'>>=
-print(cobbDouglasParamsTableWithEnergy("Q"), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-@
-
-Table \ref{tab:CD_Parameters_With_X} gives the parameters for the Cobb-Douglas model with exergy ($x$).
-
-<<CDx_Params_Table, results='asis'>>=
-print(cobbDouglasParamsTableWithEnergy("X"), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-@
-
-The Cobb-Douglas (with useful work, $u$) parameters are given in Table \ref{tab:CD_Parameters_With_U}.
-
-<<CDu_Params_Table, results='asis'>>=
-print(cobbDouglasParamsTableWithEnergy("U"), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
 @

### 2013-02-11 EconGrowth.Rnw
Significant code cleanup, including a single function that prints all of the covariance tables.

@@
       \end{itemize}
-\item Heun: Eliminate blanks in the coefficient tables for the 95\% CIs in the Cobb-Douglas with energy rows. Asked Pruim about this via email but have not heard a response.
+\item Heun: Eliminate blanks in the coefficient tables for the 95\% CIs in the Cobb-Douglas with energy rows. Asked Pruim about this via email on 4 Feb 2013 but have not heard a response.
       \begin{itemize}
@@
 \item Heun: Fix warnings of the form ``Warning:  step factor 0.000488281 reduced below ’minFactor’ of 0.000976562'' in the code that generates the Cobb-Douglas with energy fits.
+\item Heun: Ask Martin if he can supply an ``Economics'' affiliation. Will probably make a stronger paper.
 \item \st{Heun: Create a table of AIC values for each fit.}
@@
 require(xtable)
-require(tikzDevice) #See http://r-forge.r-project.org/R/?group_id=440 for instructions on installing tikzDevice.
+# tikz allows use of LaTeX formatting and font in graphs. Allows for a consistent look across the paper.
+# See http://r-forge.r-project.org/R/?group_id=440 for instructions on installing tikzDevice.
+require(tikzDevice) 
 trellis.par.set(theme=theme.mosaic())
@@
   # ********************************************************************************************************
-  warning=FALSE, #Tells whether to show warnings.
+  warning=FALSE, #Tells whether to show warnings in the output.
   dev='tikz',    #Allows LaTeX code in graphical output. E.g., "$y$" for a variable name in the legend for a graph.
@@
 keyYLoc <- 0.95 #y position of the key
-scaleTextSize <- 1.0 #0.75 #75% of normal size
+scaleTextSize <- 1.0  #Multiple of normal size
 scaleTickSize <- -0.5 #50% of normal size and pointing INWARD!
@@
 
-<<Data, eval=TRUE>>=
+<<Data Functions, eval=TRUE>>=
 #################################
@@
   covarXtable <- xtable(covarResults, 
-                      caption=paste("Covariance table for ", countryAbbrev, "economy."), 
+                      caption=paste("Covariance table for ", countryAbbrev, ".", sep=""), 
                       label=paste("tab:Covariance_", countryAbbrev, sep=""))
@@
 }
+
+###############################
+# Prints a covariance table for countryAbbrev
+##
+printCovarTable <- function(countryAbbrev){
+  print(covarianceTable(countryAbbrev), 
+                      caption.placement="top", 
+                      sanitize.rownames.function = identity,
+                      sanitize.colnames.function = identity,
+                      size="\\tiny",
+                      table.placement="H")
+}
 @
@@
 Figure \ref{fig:Factors_Lattice_Graph} shows historical data, including GDP ($y$), capital stock ($k$), labor ($l$), and the various energy types ($q$, $x$, and $u$).
-Facotrs of production track each other closely, and large covariances among these variables can be seen in Tables \ref{tab:Covariance_US} through \ref{tab:Covariance_ZM}.
+Factors of production track each other closely, and large covariances among these variables can be seen in Tables \ref{tab:Covariance_US} through \ref{tab:Covariance_ZM}.
 
@@
 <<Covariance_Table_US, results='asis'>>=
-print(covarianceTable("US"), 
-                      caption.placement="top", 
-                      sanitize.rownames.function = identity,
-                      sanitize.colnames.function = identity,
-                      table.placement="H")
+printCovarTable("US")
 @
@@
 <<Covariance_Table_UK, results='asis'>>=
-print(covarianceTable("UK"), 
-                      caption.placement="top", 
-                      sanitize.rownames.function = identity,
-                      sanitize.colnames.function = identity,
-                      table.placement="H")
+printCovarTable("UK")
 @
@@
 <<Covariance_Table_JP, results='asis'>>=
-print(covarianceTable("JP"), 
-                      caption.placement="top", 
-                      sanitize.rownames.function = identity,
-                      sanitize.colnames.function = identity,
-                      table.placement="H")
+printCovarTable("JP")
 @
@@
 <<Covariance_Table_CN, results='asis'>>=
-print(covarianceTable("CN"), 
-                      caption.placement="top", 
-                      sanitize.rownames.function = identity,
-                      sanitize.colnames.function = identity,
-                      table.placement="H")
+printCovarTable("CN")
 @
@@
 <<Covariance_Table_ZA, results='asis'>>=
-print(covarianceTable("ZA"), 
-                      caption.placement="top", 
-                      sanitize.rownames.function = identity,
-                      sanitize.colnames.function = identity,
-                      table.placement="H")
+printCovarTable("ZA")
 @
@@
 <<Covariance_Table_SA, results='asis'>>=
-print(covarianceTable("SA"), 
-                      caption.placement="top", 
-                      sanitize.rownames.function = identity,
-                      sanitize.colnames.function = identity,
-                      table.placement="H")
+printCovarTable("SA")
 @
@@
 <<Covariance_Table_IR, results='asis'>>=
-print(covarianceTable("IR"), 
-                      caption.placement="top", 
-                      sanitize.rownames.function = identity,
-                      sanitize.colnames.function = identity,
-                      table.placement="H")
+printCovarTable("IR")
 @
@@
 <<Covariance_Table_TZ, results='asis'>>=
-print(covarianceTable("TZ"), 
-                      caption.placement="top", 
-                      sanitize.rownames.function = identity,
-                      sanitize.colnames.function = identity,
-                      table.placement="H")
+printCovarTable("TZ")
 @
@@
 <<Covariance_Table_ZM, results='asis'>>=
-print(covarianceTable("ZM"), 
-                      caption.placement="top", 
-                      sanitize.rownames.function = identity,
-                      sanitize.colnames.function = identity,
-                      table.placement="H")
+printCovarTable("ZM")
 @
@@
 
-<<AIC_Table, results='asis', label="AIC_Table", eval=TRUE>>=
+<<AIC_Table, results='asis', label="AIC_Table">>=
 print(createAICTable(), 
       caption.placement="top", 
-      sanitize.rownames.function = identity)
+      sanitize.rownames.function = identity,
+      size="\\tiny",
+      table.placement="H")
 @

### 2013-02-11 EconGrowth.Rnw
Now doing all covariance tables in one knitr chunk.

@@
 
-<<Covariance_Table_US, results='asis'>>=
+<<Print_Covariance_Tables, results='asis'>>=
 printCovarTable("US")
-@
-
-<<Covariance_Table_UK, results='asis'>>=
 printCovarTable("UK")
-@
-
-<<Covariance_Table_JP, results='asis'>>=
 printCovarTable("JP")
-@
-
-<<Covariance_Table_CN, results='asis'>>=
 printCovarTable("CN")
-@
-
-<<Covariance_Table_ZA, results='asis'>>=
 printCovarTable("ZA")
-@
-
-<<Covariance_Table_SA, results='asis'>>=
 printCovarTable("SA")
-@
-
-<<Covariance_Table_IR, results='asis'>>=
 printCovarTable("IR")
-@
-
-<<Covariance_Table_TZ, results='asis'>>=
 printCovarTable("TZ")
-@
-
-<<Covariance_Table_ZM, results='asis'>>=
 printCovarTable("ZM")

### 2013-02-11 EconGrowth.Rnw
Now building parameter tables for single-factor models. Now quite debugged yet.

@@
       \begin{itemize}
-      \item \st{GDP comparison graph}
       \item parameter graphs ($\lambda$ and $m$) for each country
       \item parameter tables for each country in the appendix
+      \item \st{GDP comparison graph}
       \item \st{AIC rows in the AIC table}
@@
       \item GDP comparison graph
-      \item parameter graphs ($\lambda$ and $m$) for each country
+      \item parameter graphs for each country
       \item parameter tables for each country in the appendix
@@
   # ********************************************************************************************************
-  eval=TRUE,
+  eval=FALSE,
   # ********************************************************************************************************
@@
 countryNamesAlph <- c(CN="China", IR="Iran", JP="Japan", SA="Saudi Arabia", TZ="Tanzania", UK="United Kingdom", US="USA", ZA="South Africa", ZM="Zambia") #In alphabetical order.
-# List of energy types
-energyTypes <- c(Q="Q", X="X", U="U")
+energyTypes <- c(Q="Q", X="X", U="U") # List of energy types
+factors <- c(K="K", L="L", Q="Q", X="X", U="U") # List of factors of production
 ########### Several global parameters for graphs. Set here and use below to ensure consistent appearance of graphs.
-# Set the order for presenting countries in 3x3 lattice graphs. Default is alphabetical. "1" means first alphabetically.
-# The following list sets the order as US, UK, JP, CN, ZA, TZ, SA, IR, ZM.
-countryOrderForGraphs <- c(7,6,3,1,8,5,4,2,9)
+# Set the order for presenting countries in 3x3 lattice graphs. Default is alphabetical. 
+# "1" means first alphabetically.
+countryOrderForGraphs <- c(7,6,3,1,8,5,4,2,9) # Sets the order as US, UK, JP, CN, ZA, TZ, SA, IR, ZM.
 # Full page lattice plot sizes and other parameters
@@
 ###############################
-# Tells whether we have data for this combination of country and energy type.
+# Tells whether we have data for this combination of country and energy type for a single-factor curve fit.
+#
+# returns logical value (TRUE or FALSE)
+##
+haveDataSF <- function(countryAbbrev, factor){
+  # The design here is to go through several cases where data is unavailable and
+  # return FALSE. If we make it through all of those cases, we'll return TRUE.
+  if (!(countryAbbrev %in% countryAbbrevs)){
+    # If we don't know the country, we don't have data
+    return(FALSE)
+  }
+  if (missing(factor) || is.na(factor)){
+    # If we don't have a factor, we don't have data.
+    return(FALSE)
+  }
+  if (!(factor %in% factors)){
+    # If we don't know the factor, we don't have data
+    return(FALSE)
+  }
+  if (factor == "U" && (!(countryAbbrev %in% countryAbbrevsU))){
+    # We have U data for only a few countries.
+    return(FALSE)
+  }
+  return(TRUE)
+}
+
+###############################
+# Tells whether we have data for this combination of country and energy type for a Cobb-Douglas curve fit.
 # a missing energyType or energyType == NA means that we want to develop a model without energy, if possible.
@@
 ##
-haveData <- function(countryAbbrev, energyType){
+haveDataCD <- function(countryAbbrev, energyType){
   # The design here is to go through several cases where data is unavailable and
@@
   # Can't make predictions for any of CN, ZA, SA, IR, TZ, or ZM if we're interested in U
-  if (factor == "U"){
-    if (!(haveData(countryAbbrev, factor))){
+  if (!(haveDataSF(countryAbbrev, factor))){
     #If we don't have data for this combination of countryAbbrev and energyType, 
@@
     return(df)
-    }
   }
@@
   return(graph)
+}
+
+#################################################
+# Calculates parameter estimates and confidence intervals
+# for the single factor production function for a given a country.
+#
+# countryAbbrev is a string containing the 2-letter abbreviation for the country, e.g. "US" or "CN"
+# factor is a string, one of "K", "L", "Q", "X", or "U"
+#
+# returns a data.frame of data for the Cobb-Douglas model. 
+# First row is the +95% CI on all parameters
+# Second row contains the parameter estimates
+# Third row is the -95% CI on all parameters
+# Each column has names: lambda and m corresponding to the parameters in the model.
+##
+singleFactorData <- function(countryAbbrev, factor){
+  #First, check to see if we want useful work (U) AND one of the countries for which we don't have data.
+  if (!haveDataSF(countryAbbrev, factor)){
+    #Return a column of NAs if we don't have data for this factor
+    nRows <- 3 # +95% CI, SF, and -95% CI.
+    nCols <- 2 # lambda, m
+    df <- as.data.frame(matrix(NA, ncol = nCols, nrow = nRows))
+    colnames(df) <- c("lambda", "m")
+    rownames(df) <- c("+95% CI", "SF", "-95% CI")
+    return(df)
+  }
+  # We have a combination of country and factor for which we have data.
+  modelSF <- singleFactorModel(countryAbbrev, factor)
+  summarySF <- summary(modelSF) # Gives the nls summary table.
+  ciSF <- confint(modelSF, level = ciLevel)  # Calculates confidence intervals for the SF model.
+  dofSF <- summarySF$df[2] # Gives the degrees of freedom for the model.
+  tvalSF <- qt(ciHalfLevel, df = dofSF)
+#   print("")
+#   print(paste("In singleFactorData:", countryAbbrev, factor))
+#   print("summarySF:")
+#   print(paste("    df:", summarySF$df))
+#   print(paste("    sigma:", summarySF$sigma))
+#   print("    coeffs: ")
+#   print(summarySF$coefficients)
+#   print("ciSF:")
+#   print(ciSF)
+  #Single factor model
+  lambda <- as.numeric(coef(modelSF)["lambda"])
+  m <- as.numeric(coef(modelSF)["m"])
+  # Combine all estimates and their confidence intervals into data frames with intelligent row names
+  estSF <- data.frame(lambda = lambda, m = m)
+  row.names(estSF) <- "SF"
+  # The [1] subscripts pick off the lower confidence interval
+  lowerSF <- data.frame(lambda=ciSF["lambda","2.5%"], 
+                        m=ciSF["m", "2.5%"])
+  row.names(lowerSF) <- "-95% CI"
+  # The [2] subscripts pick off the upper confidence interval
+  upperSF <- data.frame(lambda=ciSF["lambda","97.5%"], 
+                        m=ciSF["m", "97.5%"])
+  row.names(upperSF) <- "+95% CI"
+  # Now create the data for a table and return it
+  dataSF <- rbind(upperSF, estSF, lowerSF)
+  return(dataSF)
+}
+
+############
+# Creates a row for the single factor parameters table for the given country (2-letter code) and factor.
+##
+singleFactorCountryRow <- function(countryAbbrev, factor){
+ dataSF <- singleFactorData(countryAbbrev, factor)
+ out <- cbind(dataSF["-95% CI", "lambda"], dataSF["SF", "lambda"], dataSF["+95% CI", "lambda"],
+              dataSF["-95% CI", "m"],  dataSF["SF", "m"],  dataSF["+95% CI", "m"])
+ return(out)
+}
+
+############################
+# Aggregates the single-factor results into a big data table for the given factor.
+##
+singleFactorParamsTable <- function(factor){
+  #Do rbind on the results of creating a row in the table for every country abbreviation that we know.
+  dataSF <- do.call("rbind", lapply(countryAbbrevs, singleFactorCountryRow, factor=factor))
+  if (factor == "K"){
+    factorString <- "$\\alpha$"
+  } else if (factor == "L"){
+    factorString <- "$\\beta$"
+  } else {
+    factorString <- "$\\gamma$"
+  }
+  colnames(dataSF) <- c(" ", "$\\lambda$", " ", 
+                        " ", factorString,  " ")
+  rownames(dataSF) <- countryAbbrevs
+  tableSF <- xtable(dataSF, 
+                    caption=paste("Single-factor model (with $", tolower(factor), "$) parameters for 1980-2011 (US, UK, JP), 1991-2010 (CN and ZA), and 1991-2011 (SA, IR, TZ, and ZM).
+(Parameter estimates beneath symbol.
+95\\% confidence interval bounds to left and right.)", sep=""),
+                    label=paste("tab:SF_Parameters_With_", factor, sep=""),
+                    digits = c(1, 4,4,4, 2,2,2),
+                    align = "r|ccc|ccc") #Sets alignment of the numbers in the columns
+  return(tableSF)
+}
+
+###############################
+# Prints a covariance table for countryAbbrev
+##
+printSingleFactorParamsTable <- function(factor){
+  print(singleFactorParamsTable(factor),
+      caption.placement="top", 
+      sanitize.colnames.function = identity, 
+      size="\\tiny", 
+      table.placement="H")
 }
@@
     # Consider this replacement only if energyType has been specified.
-    if (!(haveData(countryAbbrev, energyType))){
+    if (!(haveDataCD(countryAbbrev, energyType))){
       #If we don't have data for this combination of countryAbbrev and energyType, 
@@
 #
-# countryName is a string containing the 2-letter abbreviation for the country, e.g. "US" or "CN"
+# countryAbbrev is a string containing the 2-letter abbreviation for the country, e.g. "US" or "CN"
 # energyType is a string, one of "Q", "X", or "U"
@@
   #First, check to see if we want useful work (U) AND one of the countries for which we don't have data.
-  if (!haveData(countryAbbrev, energyType)){
+  if (!haveDataCD(countryAbbrev, energyType)){
     #Return a column of NAs if the above conditions have been met.
@@
 #     print("")
-#     print(paste("In cobbDouglasData:", countryName, energyType))
+#     print(paste("In cobbDouglasData:", countryAbbrev, energyType))
 #     print("summaryCD:")
@@
 ##
-cobbDouglasCountryRow <- function(countryName, energyType){
-  dataCD <- cobbDouglasData(countryName, energyType)
+cobbDouglasCountryRow <- function(countryAbbrev, energyType){
+  dataCD <- cobbDouglasData(countryAbbrev, energyType)
   if (missing(energyType)){
@@
   tableCD <- xtable(dataCD, 
-                    caption="Cobb-Douglas (without energy) for 1980-2011 (US, UK, JP), 1991-2010 (CN and ZA), and 1991-2011 (SA, IR, TZ, and ZM).
+                    caption="Cobb-Douglas model (without energy) parameters for 1980-2011 (US, UK, JP), 1991-2010 (CN and ZA), and 1991-2011 (SA, IR, TZ, and ZM).
 (Parameter estimates beneath symbol.
@@
   tableCD <- xtable(dataCD, 
-                    caption=paste("Cobb-Douglas (with $", tolower(energyType), "$) for 1980-2011 (US, UK, JP), 1991-2010 (CN and ZA), and 1991-2011 (SA, IR, TZ, and ZM).
+                    caption=paste("Cobb-Douglas model (with $", tolower(energyType), "$) parameters for 1980-2011 (US, UK, JP), 1991-2010 (CN and ZA), and 1991-2011 (SA, IR, TZ, and ZM).
 (Parameter estimates beneath symbol.
@@
 
-<<Print_Covariance_Tables, results='asis'>>=
+<<Print_Covariance_Tables, results='asis', eval=TRUE>>=
+#I wish I could say this, but I get bogus "$US" strings appearing in the LaTeX output.
+#lapply(countryAbbrevs, printCovarTable)
 printCovarTable("US")
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Single-factor Models}
+
+Tables \ref{} below provide tabular results for single-factor models.
+
+<<SF_Params_Tables, results='asis', eval=TRUE>>=
+# print(singleFactorParamsTable("Q"),
+#      caption.placement="top", 
+#      sanitize.colnames.function = identity, 
+#      size="\\tiny", 
+#      table.placement="H")
+#printSingleFactorParamsTable("Q")
+lapply(factors, printSingleFactorParamsTable)
+@
+
+\subsection{Cobb-Douglas Models}
 

### 2013-02-11 EconGrowth.Rnw
A commit before enhancing the .gitignore file.

@@
   # ********************************************************************************************************
-  eval=FALSE,
+  eval=TRUE,
   # ********************************************************************************************************

### 2013-02-12 EconGrowth.Rnw
Now adding more file types to .gitignore to make collaboration easier.
A few small changes.
Deleted some bogus lines of text.
Now including tables of parameters for single-factor model fits.

@@
   lambdaGuess <- 0.0 #guessing lambda = 0 means there is no technological progress.
+  # Some economies need different guesses
+  if (countryAbbrev == "IR" && factor == "X"){
+    mGuess <- 0.7
+  } else {
+    # This works for every other combination of country and factor.
     mGuess <- 0.5
+  }
   # Runs a non-linear least squares fit to the data. We've replaced beta with 1-alpha for simplicity.
@@
   tvalSF <- qt(ciHalfLevel, df = dofSF)
-#   print("")
-#   print(paste("In singleFactorData:", countryAbbrev, factor))
-#   print("summarySF:")
-#   print(paste("    df:", summarySF$df))
-#   print(paste("    sigma:", summarySF$sigma))
-#   print("    coeffs: ")
-#   print(summarySF$coefficients)
-#   print("ciSF:")
-#   print(ciSF)
   #Single factor model
@@
 
-Figure \ref{fig:CD_GDP_Lattice_Graph} compares predictions from the Cobb-Douglas models (without energy, with $Q$, and with $x$) to historical data.
+Figure \ref{fig:CD_GDP_Lattice_Graph} compares predictions from the Cobb-Douglas models (without energy, with $q$, with $x$, and with $u$) to historical data.
 
@@
 
-<<Print_Covariance_Tables, results='asis', eval=TRUE>>=
+<<Print_Covariance_Tables, results='asis'>>=
 #I wish I could say this, but I get bogus "$US" strings appearing in the LaTeX output.
@@
 
-Tables \ref{} below provide tabular results for single-factor models.
-
-<<SF_Params_Tables, results='asis', eval=TRUE>>=
-# print(singleFactorParamsTable("Q"),
-#      caption.placement="top", 
-#      sanitize.colnames.function = identity, 
-#      size="\\tiny", 
-#      table.placement="H")
-#printSingleFactorParamsTable("Q")
-lapply(factors, printSingleFactorParamsTable)
+The following tables provide tabular results for single-factor models.
+
+<<SF_Params_Tables, results='asis'>>=
+#I wish I could say this, but I get bogus K [1]” strings appearing in the LaTeX output.
+#lapply(factors, printSingleFactorParamsTable)
+printSingleFactorParamsTable("K")
+printSingleFactorParamsTable("L")
+printSingleFactorParamsTable("Q")
+printSingleFactorParamsTable("X")
+printSingleFactorParamsTable("U")
 @
@@
 
-The Cobb-Douglas (with thermal energy, $q$) parameters are given in Table \ref{tab:CD_Parameters_With_Q}.
+The following tables provide tabular results for Cobb-Douglas models with various energy terms.
 
@@
 
-Table \ref{tab:CD_Parameters_With_X} gives the parameters for the Cobb-Douglas model with exergy ($x$).
-
 <<CDx_Params_Table, results='asis'>>=
@@
 @
-
-The Cobb-Douglas (with useful work, $u$) parameters are given in Table \ref{tab:CD_Parameters_With_U}.
 

### 2013-02-12 EconGrowth.Rnw
Better formatting for the single factor graphs.

@@
       \item parameter graphs ($\lambda$ and $m$) for each country
-      \item parameter tables for each country in the appendix
+      \item \st{parameter tables for each country in the appendix}
       \item \st{GDP comparison graph}
@@
 
+###########################################
+# Creates a number of rows in a data.frame that contain information 
+# about the coefficients of a single factor model for countryAbbrev.
+# Each parameter has its own row with confidence intervals.
+# The country name is in a column. Which parameter is involved is
+# also in a column.
+# 
+# The return type is a data.frame.
+##
+singleFactorCountryRowsForParamsGraph <- function(countryAbbrev, factor){
+  #Create three rows, one for each parameter. Each row is a data.frame so that it is plottable!
+  dataSF <- singleFactorData(countryAbbrev, factor)
+  valueRow <- "SF"
+  # Create rows for each parameter
+  lambdaRow <- data.frame(country = countryAbbrev, 
+                          parameter = "lambda", 
+                          lowerCI = dataSF["-95% CI", "lambda"], 
+                          value = dataSF[valueRow, "lambda"], 
+                          upperCI = dataSF["+95% CI", "lambda"])
+  mRow <- data.frame(country = countryAbbrev, 
+                     parameter = "m",
+                     lowerCI = dataSF["-95% CI", "m"],
+                     value = dataSF[valueRow, "m"],  
+                     upperCI = dataSF["+95% CI", "m"])
+  table <- rbind(lambdaRow, mRow)
+  return(table)
+}
+
 ###############################
@@
 }
+
+#############################
+# Creates a graph with confidene intervals for the single-factor model for the given factor
+##
+createSFParamsGraph <- function(factor){
+  # Create a data table with the following columns:
+  # country abbrev, parameter (lambda or m), -95% CI, value, +95% CI
+  dataTable <- do.call("rbind", lapply(countryAbbrevs, singleFactorCountryRowsForParamsGraph, factor=factor))
+print(dataTable)
+#   graph <- segplot(country ~ upperCI + lowerCI | parameter, 
+#                    data = dataTable, 
+#                    centers = value, #identifies where the dots should be placed
+#                    draw.bands = FALSE, #provides nicer error bars
+#                    horizontal = FALSE, #makes error bars vertical and puts the countries in the x axis
+#                    layout = c(2,1), #2 column, 1 row
+#                    index.cond = list(c(1,2)), #orders the panels as lambda, m
+#                    #set labels and bg color in strip
+#                    strip = strip.custom(factor.levels=c("$\\lambda$", "$m"),  
+#                                         bg="white"),
+#                    col = "black", #Sets line color to black
+#                    lwd = 1, #Sets line width to 1.0
+#                    ylim = list(c(-0.05, 0.1), c(-0.5, 1.5)), #y axis limits
+#                    scales = list(cex=scaleTextSize, #controls text size on scales.
+#                                  tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
+#                                  x=list(cex=0.75), #reduces text size so that country abbrevs are legible
+#                                  y=list(relation="free", #allow each axis to be different
+#                                         at=list(c(0.0, 0.05, 0.1),   #y tick mark for lambda
+#                                                 c(0.0, 0.5, 1.0)
+#                                         )
+#                                  )
+#                    )
+#   )  
+  graph <- segplot(country ~ upperCI + lowerCI | parameter, 
+                   data = dataTable,
+                   centers = value, #identifies where the dots should be placed
+                   draw.bands = FALSE, #provides nicer error bars
+                   horizontal = FALSE, #makes error bars vertical and puts the countries in the x axis
+                   layout = c(2,1), #2 column, 1 row
+                   col = "black", #Sets line color to black
+                   lwd = 1, #Sets line width to 1.0
+                   strip = strip.custom(bg="white", factor.levels=c("$\\lambda$", "$m$")),
+                   ylim = list(c(-0.05, 0.1), c(-0.5, 1.5)), #y axis limits
+                   scales = list(cex=scaleTextSize, #controls text size on scales.
+                                 tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
+                                 x=list(cex=0.75), #reduces text size so that country abbrevs are legible
+                                 y=list(relation="free", #allow each axis to be different
+                                        at=list(c(0.0, 0.05, 0.1),   #y tick mark for lambda
+                                                c(0.0, 0.5, 1.0)
+                                                )
+                                        )
+                                 )
+                   )
+
+  return(graph)
+}
+
+createSFParamsGraph("L")
+
 @

### 2013-02-12 EconGrowth.Rnw
Now generating single-factor parameter graphs for all models within the text.

@@
   dataTable <- do.call("rbind", lapply(countryAbbrevs, singleFactorCountryRowsForParamsGraph, factor=factor))
-print(dataTable)
-#   graph <- segplot(country ~ upperCI + lowerCI | parameter, 
-#                    data = dataTable, 
-#                    centers = value, #identifies where the dots should be placed
-#                    draw.bands = FALSE, #provides nicer error bars
-#                    horizontal = FALSE, #makes error bars vertical and puts the countries in the x axis
-#                    layout = c(2,1), #2 column, 1 row
-#                    index.cond = list(c(1,2)), #orders the panels as lambda, m
-#                    #set labels and bg color in strip
-#                    strip = strip.custom(factor.levels=c("$\\lambda$", "$m"),  
-#                                         bg="white"),
-#                    col = "black", #Sets line color to black
-#                    lwd = 1, #Sets line width to 1.0
-#                    ylim = list(c(-0.05, 0.1), c(-0.5, 1.5)), #y axis limits
-#                    scales = list(cex=scaleTextSize, #controls text size on scales.
-#                                  tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
-#                                  x=list(cex=0.75), #reduces text size so that country abbrevs are legible
-#                                  y=list(relation="free", #allow each axis to be different
-#                                         at=list(c(0.0, 0.05, 0.1),   #y tick mark for lambda
-#                                                 c(0.0, 0.5, 1.0)
-#                                         )
-#                                  )
-#                    )
-#   )  
   graph <- segplot(country ~ upperCI + lowerCI | parameter, 
@@
 }
-
-createSFParamsGraph("L")
-
 @
@@
 \noindent to historical data where the factor of production ($f$) is any of $k$, $l$, $q$, $x$, or $u$, and the exponent ($m$) is $\alpha$ for $k$, $\beta$ for $l$, or $\gamma$ for $q$, $x$, or $u$.
+
+<<SFk_Params_Graph, fig.width=figWidth, fig.height=parameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $k$) model parameters.
+Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
+createSFParamsGraph("K")
+@
+
+<<SFl_Params_Graph, fig.width=figWidth, fig.height=parameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $l$) model parameters.
+Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
+createSFParamsGraph("L")
+@
+
+<<SFq_Params_Graph, fig.width=figWidth, fig.height=parameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $q$) model parameters.
+Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
+createSFParamsGraph("Q")
+@
+
+<<SFx_Params_Graph, fig.width=figWidth, fig.height=parameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $x$) model parameters.
+Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
+createSFParamsGraph("X")
+@
+
+<<SFu_Params_Graph, fig.width=figWidth, fig.height=parameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $u$) model parameters.
+Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
+createSFParamsGraph("U")
+@
 

### 2013-02-12 EconGrowth.Rnw
Added better variables for graph widths and heights in the setup chunk.

@@
 ninePanelLayoutSpec <- c(3,3) #indicates a 3x3 arrangement of panels.
-figWidth <- 6.5             #Inches
+ninePanelGraphWidth <- 6.5   #Inches
 ninePanelGraphHeight <- 7.5  #Inches
-parameterGraphHeight <- 5   #Inches
+sfParameterGraphWidth <- 4   #Inches
+sfParameterGraphHeight <- 3  #Inches
+cdParameterGraphWidth <- 6.5 #Inches
+cdParameterGraphHeight <- 5  #Inches
 keyTextSize <- 0.85 #85% of normal size
@@
 
-<<Factors_Lattice_Graph, fig.width=figWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="Historical data.
+<<Factors_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="Historical data.
 Indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$).">>=
@@
 
-<<SFk_Params_Graph, fig.width=figWidth, fig.height=parameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $k$) model parameters.
+<<SFk_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $k$) model parameters.
 Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
@@
 
-<<SFl_Params_Graph, fig.width=figWidth, fig.height=parameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $l$) model parameters.
+<<SFl_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $l$) model parameters.
 Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
@@
 
-<<SFq_Params_Graph, fig.width=figWidth, fig.height=parameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $q$) model parameters.
+<<SFq_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $q$) model parameters.
 Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
@@
 
-<<SFx_Params_Graph, fig.width=figWidth, fig.height=parameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $x$) model parameters.
+<<SFx_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $x$) model parameters.
 Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
@@
 
-<<SFu_Params_Graph, fig.width=figWidth, fig.height=parameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $u$) model parameters.
+<<SFu_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $u$) model parameters.
 Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
@@
 
-<<SF_GDP_Lattice_Graph, fig.width=figWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="Single-factor results.">>=
+<<SF_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="Single-factor results.">>=
 createSFLatticeGraph()
@@
 
-<<CD_Params_Graph, fig.width=figWidth, fig.height=parameterGraphHeight, fig.pos="H", fig.cap="Cobb-Douglas (without energy) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
+<<CD_Params_Graph, fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.pos="H", fig.cap="Cobb-Douglas (without energy) model parameters.
+Vertical bars indicate 95\\% confidence intervals.">>=
 createCDParamsGraph()
@@
 
-<<CDq_Params_Graph, fig.width=figWidth, fig.height=parameterGraphHeight, fig.pos="H", fig.cap="Cobb-Douglas (with $q$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
+<<CDq_Params_Graph, fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.pos="H", fig.cap="Cobb-Douglas (with $q$) model parameters.
+Vertical bars indicate 95\\% confidence intervals.">>=
 createCDParamsGraph("Q")
@@
 
-<<CDx_Params_Graph, fig.width=figWidth, fig.height=parameterGraphHeight, fig.pos="H", fig.cap="Cobb-Douglas (with $x$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
+<<CDx_Params_Graph, fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.pos="H", fig.cap="Cobb-Douglas (with $x$) model parameters.
+Vertical bars indicate 95\\% confidence intervals.">>=
 createCDParamsGraph("X")
@@
 
-<<CDu_Params_Graph, fig.width=figWidth, fig.height=parameterGraphHeight, fig.pos="H", fig.cap="Cobb-Douglas (with $u$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
+<<CDu_Params_Graph, fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.pos="H", fig.cap="Cobb-Douglas (with $u$) model parameters.
+Vertical bars indicate 95\\% confidence intervals.">>=
 createCDParamsGraph("U")
@@
 
-<<CD_GDP_Lattice_Graph, fig.width=figWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="Cobb-Douglas results.">>=
+<<CD_GDP_Lattice_Graph, fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="Cobb-Douglas results.">>=
 createCDLatticeGraph()

### 2013-02-12 EconGrowth.Rnw
Edited to-do list.
Now including econ affiliation for Martin. Now using better variables for graph sizes.

@@
 \address[Calvin]{Engineering Department, Calvin College, Grand Rapids, MI 49546, USA}
-\address[Stellenbosch]{ Stellenbosch University, School of Public Leadership, P.O. Box 610, Bellville 7535, South Africa}
+\address[Stellenbosch]{Stellenbosch University, Faculty of Economics and Management Sciences, School of Public Leadership, P.O. Box 610, Bellville 7535, South Africa}
 
@@
       \begin{itemize}
-      \item parameter graphs ($\lambda$ and $m$) for each country
+      \item correct sizes for parameter graphs for each country
+      \item \st{parameter graphs ($\lambda$ and $m$) for each country}
       \item \st{parameter tables for each country in the appendix}
@@
 \item Heun: Fix warnings of the form ``Warning:  step factor 0.000488281 reduced below ’minFactor’ of 0.000976562'' in the code that generates the Cobb-Douglas with energy fits.
-\item Heun: Ask Martin if he can supply an ``Economics'' affiliation. Will probably make a stronger paper.
+\item \st{Heun: Ask Martin if he can supply an ``Economics'' affiliation. Will probably make a stronger paper.}
 \item \st{Heun: Create a table of AIC values for each fit.}
@@
 countryOrderForGraphs <- c(7,6,3,1,8,5,4,2,9) # Sets the order as US, UK, JP, CN, ZA, TZ, SA, IR, ZM.
-# Full page lattice plot sizes and other parameters
+maxWidth <- 6.5 #Inches
+# Full page lattice plot sizes
 ninePanelLayoutSpec <- c(3,3) #indicates a 3x3 arrangement of panels.
-ninePanelGraphWidth <- 6.5   #Inches
+ninePanelGraphWidth <- maxWidth     
 ninePanelGraphHeight <- 7.5  #Inches
-sfParameterGraphWidth <- 4   #Inches
-sfParameterGraphHeight <- 3  #Inches
-cdParameterGraphWidth <- 6.5 #Inches
-cdParameterGraphHeight <- 5  #Inches
 keyTextSize <- 0.85 #85% of normal size
@@
 keyYLoc <- 0.95 #y position of the key
+# Parameter graphs are tricky to ensure same size. I've found that with height set to 5 in for the 
+# cd graphs and 2.93 in for the sf graphs, I get a nearly-exact match with graph size. From these settings I 
+# can set up 2 equations:
+#    5 in = 2*hgraph + haxis
+#    2.93 in = hgraph + haxis
+# to estimate that h_axis = 0.86 in and hgraph = 2.05 in.
+h_param_graph <- 2.07 # Inches for a single panel
+h_param_axis <- 0.86 # Inches (also includes whatever margin is applied)
+sfParameterGraphHeight <- h_param_graph + h_param_axis
+cdParameterGraphHeight <- 2*h_param_graph + h_param_axis
+sfParameterGraphWidth <- maxWidth
+cdParameterGraphWidth <- maxWidth
+# Other graph parameters that apply to all graphs
 scaleTextSize <- 1.0  #Multiple of normal size
 scaleTickSize <- -0.5 #50% of normal size and pointing INWARD!
+print(paste("sfParameterGraphHeight =", sfParameterGraphHeight))
+print(paste("cdParameterGraphHeight =", cdParameterGraphHeight))
 @

### 2013-02-12 EconGrowth.Rnw
Added a printCDParamsTable function and used it in the appendix. Cleaned up the appendix quite a bit. Added some further code cleanup.

@@
 \item Reese: Add text from Word verson of paper to the LaTeX version.
-\item Heun: Add setup variables for figure height and width where not already included.
-\item Heun: Deal with missing covariance numbers when columns have unequal length.
-\item Heun: Add single factor fits
-      \begin{itemize}
-      \item correct sizes for parameter graphs for each country
-      \item \st{parameter graphs ($\lambda$ and $m$) for each country}
-      \item \st{parameter tables for each country in the appendix}
-      \item \st{GDP comparison graph}
-      \item \st{AIC rows in the AIC table}
-      \end{itemize}
 \item Heun: Add CES production function fits
@@
       \end{itemize}
+\item Heun: Deal with missing covariance numbers when columns have unequal length.
 \item Heun: Eliminate blanks in the coefficient tables for the 95\% CIs in the Cobb-Douglas with energy rows. Asked Pruim about this via email on 4 Feb 2013 but have not heard a response.
@@
 \item \st{Heun: Add covariance metrics.}
+\item Heun: Add single factor fits
+      \begin{itemize}
+      \item \st{correct sizes for parameter graphs for each country}
+      \item \st{parameter graphs ($\lambda$ and $m$) for each country}
+      \item \st{parameter tables for each country in the appendix}
+      \item \st{GDP comparison graph}
+      \item \st{AIC rows in the AIC table}
+      \end{itemize}
+\item \st{Heun: Add setup variables for figure height and width where not already included.}
 \end{itemize}
@@
 }
-@
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Historical Data}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Figure \ref{fig:Factors_Lattice_Graph} shows historical data, including GDP ($y$), capital stock ($k$), labor ($l$), and the various energy types ($q$, $x$, and $u$).
-Factors of production track each other closely, and large covariances among these variables can be seen in Tables \ref{tab:Covariance_US} through \ref{tab:Covariance_ZM}.
-
-<<Factors_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="Historical data.
-Indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$).">>=
-createFactorsLatticeGraph <- function(){
+
+####################################
+# Creates a graph that displays all of the factors of production for all countries.
+##
+createHistoricalLatticeGraph <- function(){
   dataTable <- loadData("All")
@@
 }
-createFactorsLatticeGraph()
+@
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Historical Data}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Figure \ref{fig:Historical_Lattice_Graph} shows historical data, including GDP ($y$), capital stock ($k$), labor ($l$), and the various energy types ($q$, $x$, and $u$).
+Factors of production track each other closely, and large covariances among these variables can be seen in Tables \ref{tab:Covariance_US} through \ref{tab:Covariance_ZM}.
+
+<<HIstorical_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="Historical data.
+Indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$).">>=
+createHistoricalLatticeGraph()
 @
@@
 ###############################
-# Prints a covariance table for countryAbbrev
-##
-printSingleFactorParamsTable <- function(factor){
+# Prints a covariance table for the given factor of production
+##
+printSFParamsTable <- function(factor){
   print(singleFactorParamsTable(factor),
@@
 
+############################
+# Prints a table with parameters from a Cobb-Douglas model for the given energyType. 
+# Leave energyType blank to print a table for Cobb-Douglas without energy.
+printCDParamsTable <- function(energyType){
+  if (missing(energyType)){
+    print(cobbDouglasParamsTableNoEnergy(), 
+        caption.placement="top", 
+        sanitize.colnames.function = identity, 
+        size="\\tiny", 
+        table.placement="H")
+  } else {
+    print(cobbDouglasParamsTableWithEnergy(energyType), 
+      caption.placement="top", 
+      sanitize.colnames.function = identity, 
+      size="\\tiny",
+      table.placement="H")
+  }
+}
+
 #############################
@@
 
-<<CES function, eval=FALSE>>=
+<<CES functions, eval=FALSE>>=
 cesData <- function(countryName, energyType){
@@
 
-The following tables provide tabular results for single-factor models.
+The following tables provide results for parameters in single-factor models.
 
@@
 #lapply(factors, printSingleFactorParamsTable)
-printSingleFactorParamsTable("K")
-printSingleFactorParamsTable("L")
-printSingleFactorParamsTable("Q")
-printSingleFactorParamsTable("X")
-printSingleFactorParamsTable("U")
+printSFParamsTable("K")
+printSFParamsTable("L")
+printSFParamsTable("Q")
+printSFParamsTable("X")
+printSFParamsTable("U")
 @
@@
 
-Table \ref{tab:CD_Parameters_No_Energy} gives the parameters for the Cobb-Douglas model without energy.
+The following tables provide results for parameters in Cobb-Douglas models with and without energy terms.
 
 <<CD_Params_Table, results='asis'>>=
-print(cobbDouglasParamsTableNoEnergy(), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny", 
-      table.placement="H")
-@
-
-The following tables provide tabular results for Cobb-Douglas models with various energy terms.
-
-<<CDq_Params_Table, results='asis'>>=
-print(cobbDouglasParamsTableWithEnergy("Q"), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-@
-
-<<CDx_Params_Table, results='asis'>>=
-print(cobbDouglasParamsTableWithEnergy("X"), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-@
-
-<<CDu_Params_Table, results='asis'>>=
-print(cobbDouglasParamsTableWithEnergy("U"), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-@
+printCDParamsTable()    #Without energy
+printCDParamsTable("Q")
+printCDParamsTable("X")
+printCDParamsTable("U")
+@
+
+\subsection{CES Models}
+
+The following tables provide results for parameters in CES models.
+
+\subsection{LINEX Models}
+
+The following tables provide results for parameters in LINEX models.
 
@@
 createAICTable <- function(){
+  ######################
+  # Single-factor models
+  ######################
   # Single-factor with K
@@
   rownames(aicSFu) <- "SF$u$"
+  ######################
   # Cobb-Douglas models
+  ######################
   cdModels <- lapply(countryAbbrevs, cobbDouglasModel)
@@
   rownames(aicCDu) <- "CD$u$"
+  ######################
+  # CES models
+  ######################
+
+  ######################
+  # LINEX models
+  ######################
+
   # Create the data.frame table

### 2013-02-13 EconGrowth.Rnw
Beginning to add the CES production function. Can't get a solution yet.

@@
 
-<<HIstorical_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="Historical data.
+<<Historical_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="Historical data.
 Indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$).">>=
@@
 <<SFk_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $k$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
+Vertical bars indicate 95\\% confidence intervals.">>=
 createSFParamsGraph("K")
@@
 <<SFl_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $l$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
+Vertical bars indicate 95\\% confidence intervals.">>=
 createSFParamsGraph("L")
@@
 <<SFq_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $q$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
+Vertical bars indicate 95\\% confidence intervals.">>=
 createSFParamsGraph("Q")
@@
 <<SFx_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $x$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
+Vertical bars indicate 95\\% confidence intervals.">>=
 createSFParamsGraph("X")
@@
 <<SFu_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $u$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
+Vertical bars indicate 95\\% confidence intervals.">>=
 createSFParamsGraph("U")
@@
 
-<<CES functions, eval=FALSE>>=
+<<CES functions, eval=TRUE>>=
+####################
+# Returns an nls ces model for the country and energyType specified.
+# energyType should be one of Q", "X", or "U".
+##
+cesModel <- function(countryAbbrev, energyType){
+  # Load the data that we need.
+  dataTable <- loadData(countryAbbrev)
+  # We need to do the CES fit with the desired energyType.
+  # To achieve the correct fit, we'll change the name of the desired column
+  # to "iEToFit" and use "iEToFit" in the nls function.
+  dataTable <- replaceColName(dataTable, energyType, "iEToFit")
+print(dataTable)
+  # Establish guess values for phi beta, zeta, lambda_L and lambda_E.
+  phiGuess <- -20
+  betaGuess <- 0.5 # a typical value for beta (exponent on labor)
+  zetaGuess <- 0.0004 # a small value
+  lambda_LGuess <- 0.007 #assuming no technical progress on the labor-capital portion of the function
+  lambda_EGuess <- 0.008 #assuming no technical progress on the energy portion of the function
+  # Runs a non-linear least squares fit to the data with constraints
+  modelCES <- nls(iGDP ~ ((1-zeta) * (exp(lambda_L*iYear) * iCapStk^(1-beta) * iLabor^beta)^phi 
+                           + zeta*(exp(lambda_E*iYear) * iEToFit)^phi)^(1/phi), 
+                  data=dataTable,
+                  start=list(phi=phiGuess, beta=betaGuess, zeta=zetaGuess, lambda_L=lambda_LGuess, 
+                             lambda_E=lambda_EGuess),
+                  control=nls.control(maxiter=500, tol=1e-06, minFactor=1/1024, 
+                                      printEval=FALSE, warnOnly=TRUE),
+#                   algorithm = "port",
+#                   lower = list(phi=-Inf, beta=0, zeta=0, lambda_L=-Inf, lambda_E=-Inf),
+#                   upper = list(phi=0, beta=1, zeta=1, lambda_L=Inf, lambda_E=Inf),
+                   )
+  return(modelCES)
+}
+model <- cesModel("UK", "U")
+summary <- summary(model)
+print(summary)
+
 cesData <- function(countryName, energyType){

### 2013-02-14 EconGrowth.Rnw
Included CES modeling. But, it is not yet working.
Now including LINEX model fits.

@@
 options(width=75)
-options(show.signif.stars=FALSE)
+options(show.signif.stars=TRUE)
 opts_chunk$set(
@@
 
-<<CES functions, eval=TRUE>>=
+<<CES functions, eval=FALSE>>=
 ####################
@@
   # Establish guess values for phi beta, zeta, lambda_L and lambda_E.
-  phiGuess <- -20
-  betaGuess <- 0.5 # a typical value for beta (exponent on labor)
-  zetaGuess <- 0.0004 # a small value
-  lambda_LGuess <- 0.007 #assuming no technical progress on the labor-capital portion of the function
-  lambda_EGuess <- 0.008 #assuming no technical progress on the energy portion of the function
+  sigmaGuess <- 0.663 # 0.663 for Sweden
+  zetaGuess <- 0.147 # 0.147 for Sweden
+  betaGuess <- 0.7 # 0.7 for Sweden
+  lambda_LGuess <- 0.011 # 0.011 for Sweden
+  lambda_EGuess <- 0.018 # 0.018 for Sweden
   # Runs a non-linear least squares fit to the data with constraints
-  modelCES <- nls(iGDP ~ ((1-zeta) * (exp(lambda_L*iYear) * iCapStk^(1-beta) * iLabor^beta)^phi 
-                           + zeta*(exp(lambda_E*iYear) * iEToFit)^phi)^(1/phi), 
+  modelCES <- nls(iGDP ~ ((1-zeta)^(1.0/sigma) * ((exp(lambda_L*iYear))^beta 
+                                                  * iCapStk^(1-beta) 
+                                                  * iLabor^beta)^((sigma-1.0)/sigma) 
+                          + zeta^(1.0/sigma)*(exp(lambda_E*iYear) 
+                                                  * iEToFit)^((sigma-1.0)/sigma))^(sigma/(sigma-1.0)), 
                   data=dataTable,
-                  start=list(phi=phiGuess, beta=betaGuess, zeta=zetaGuess, lambda_L=lambda_LGuess, 
-                             lambda_E=lambda_EGuess),
-                  control=nls.control(maxiter=500, tol=1e-06, minFactor=1/1024, 
+                  start=list(sigma=sigmaGuess, zeta=zetaGuess, beta=betaGuess, 
+                             lambda_L=lambda_LGuess, lambda_E=lambda_EGuess),
+                  control=nls.control(maxiter=10000, tol=1e-06, minFactor=1/1024, 
                                       printEval=FALSE, warnOnly=TRUE),
-#                   algorithm = "port",
-#                   lower = list(phi=-Inf, beta=0, zeta=0, lambda_L=-Inf, lambda_E=-Inf),
-#                   upper = list(phi=0, beta=1, zeta=1, lambda_L=Inf, lambda_E=Inf),
+                  algorithm = "port",
+                  lower = list(sigma=-Inf, zeta=0, beta=0.0, lambda_L=0.0, lambda_E=0.0),
+                  upper = list(sigma= Inf, zeta=1, beta=1.0, lambda_L=0.1, lambda_E=0.1),
                   )
@@
 }
-model <- cesModel("UK", "U")
+model <- cesModel("US", "Q")
 summary <- summary(model)
@@
 
+<<LINEX functions, eval=TRUE>>=
+####################
+# Returns an nls linex model for the country and energyType specified.
+# energyType should be one of Q", "X", or "U".
+##
+linexModel <- function(countryAbbrev, energyType){
+  # Load the data that we need.
+  dataTable <- loadData(countryAbbrev)
+  # We need to do the CES fit with the desired energyType.
+  # To achieve the correct fit, we'll change the name of the desired column
+  # to "iEToFit" and use "iEToFit" in the nls function.
+  dataTable <- replaceColName(dataTable, energyType, "iEToFit")
+  a_0Guess <- 1.0
+  c_tGuess <- 1.0
+  # Runs a non-linear least squares fit to the data with constraints
+  modelLINEX <- nls(iGDP ~ iEToFit * exp(a_0*(2.0 - (iLabor+iEToFit)/iCapStk) + a_0 * c_t *(iLabor/iEToFit - 1.0)), 
+                  data=dataTable,
+                  start=list(a_0=a_0Guess, c_t=c_tGuess),
+                  control=nls.control(maxiter=50, tol=1e-06, minFactor=1/1024, 
+                                      printEval=FALSE, warnOnly=TRUE),
+#                   algorithm = "port",
+#                   lower = list(a_0=-INF, c_t=-INF),
+#                   upper = list(a_0= INF, c_t= INF)
+                  )
+  return(modelLINEX)
+}
+
+#########################
+# Takes the LINEX fitted models and creates per-country predictions for them.
+# Returns a data.frame with the predictions.
+##
+linexPredictions <- function(countryAbbrev, energyType){
+  # Can't make predictions for any of CN, ZA, SA, IR, TZ, or ZM if we're interested in U
+  if (!(haveDataSF(countryAbbrev, energyType))){
+    # If we don't have data for this combination of countryAbbrev and energyType, 
+    # return a column of NAs if the above conditions have been met.
+    nRows <- 21 # All of these countries need 21 rows.
+    df <- as.data.frame(matrix(NA, ncol = 1, nrow = nRows))
+    colnames(df) <- "pred"
+    return(df)
+  }
+  model <- linexModel(countryAbbrev, energyType)
+  pred <- predict(model) #See http://stackoverflow.com/questions/9918807/how-get-plot-from-nls-in-r
+  df <- data.frame(pred)
+  # Pad with rows as necessary
+  df <- padRows(countryAbbrev, df)
+  return(df)
+}
+
+#########################
+# Takes the LINEX fitted models and creates a single column of predicted GDP values
+# that corresponds, row for row, with the AllData.txt file.
+##
+linexPredictionsColumn <- function(energyType){
+  out <- do.call("rbind", lapply(countryAbbrevs, linexPredictions, energyType=energyType))
+  colnames(out) <- c(paste("predGDP", energyType, sep=""))
+  return(out)
+}
+
+##############################
+# Creates a graph that plots predicted GDP as lines, one for each single factor, and historical GDP 
+# data as open circles.
+##
+createLinexLatticeGraph <- function(){
+  dataTable <- loadData("All") #Grab the raw data
+  predictionsQ <- linexPredictionsColumn("Q") #Predictions from LINEX with Q
+  predictionsX <- linexPredictionsColumn("X") #Predictions from LINEX with X
+  predictionsU <- linexPredictionsColumn("U") #Predictions from LINEX with U
+  #Now add the predictions columns to the data.
+  dataTable <- cbind(dataTable, predictionsQ, predictionsX, predictionsU) 
+  graphType <- "b" #b is for both line and symbol
+  lineTypes <- c(0, 2, 4, 1) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
+  lineWidths <- c(0, 1, 1, 1) #line widths. 0 means no line.
+  colors <- c("black", "red", "blue", "darkorange") #line and symbol colors
+  symbols <- c(1, NA, NA, NA)  #NA gives no symbol.
+  graph <- xyplot(iGDP+predGDPQ+predGDPX+predGDPU ~ Year | Country, data=dataTable,
+                  type=graphType,
+                  index.cond=list(countryOrderForGraphs), #orders the panels.
+                  layout=ninePanelLayoutSpec, #indicates a 3x3 arrangement of panels.
+                  strip = strip.custom(factor.levels=countryNamesAlph, bg="white"), #Sets strip parameters
+                  as.table=TRUE, #indexing of panels starts in upper left and goes across rows.
+                  lty = lineTypes, lwd = lineWidths, col = colors, #Controls line parameters
+                  pch = symbols, col.symbol = colors, #Controls symbol parameters
+                  key=list(text=list(c("Actual", "With $q$", "With $x$", "With $u$")),
+                           type=graphType,
+                           cex=keyTextSize, #controls size of text in the key
+                           lines=list(lty=lineTypes, lwd=lineWidths), #controls line types
+                           pch=symbols, col=colors, #controls symbol (plot characters) types
+                           columns=keyColumns, x=keyXLoc, y=keyYLoc), #controls columns and position of the key
+                  scales=list(cex=scaleTextSize, #controls text size on scales.
+                              tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
+                              y=list(relation="free", #allows each axis to be different
+                                     at=c(1,2,3,4,5,6,7,8,9,10) #tick mark locations
+                                     )
+                              ), 
+                  ylim=list(c(1,8), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3)),
+                  xlab="", ylab="Indexed GDP (1980=1 or 1991=1)") #axis labels
+  return(graph)
+}
+
+@
+
 \subsection{LINEX with $Q$}
@@
 \subsection{LINEX with $U$}
+
+Figure \ref{fig:LINEX_GDP_Lattice_Graph} compares LINEX model predictions with historica data.
+
+<<LINEX_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="LINEX results.", eval=TRUE>>=
+createLinexLatticeGraph()
+@
 

### 2013-02-14 EconGrowth.Rnw
Changed to-do list to reflect fact that LINEX GDP comparison graphs are being generated.
Now including LINEX model in the AIC table.

@@
       \begin{itemize}
-      \item GDP comparison graph
       \item parameter graphs for each country
       \item parameter tables for each country in the appendix
-      \item AIC rows in the AIC table
+      \item \st{AIC rows in the AIC table}
+      \item \st{GDP comparison graph}
       \end{itemize}
@@
 
-<<LINEX_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="LINEX results.", eval=TRUE>>=
+<<LINEX_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="LINEX results.">>=
 createLinexLatticeGraph()
@@
 #lapply(countryAbbrevs, printCovarTable)
-printCovarTable("US")
-printCovarTable("UK")
-printCovarTable("JP")
-printCovarTable("CN")
-printCovarTable("ZA")
-printCovarTable("SA")
-printCovarTable("IR")
-printCovarTable("TZ")
-printCovarTable("ZM")
+printCovarTable("US"); printCovarTable("UK"); printCovarTable("JP")
+printCovarTable("CN"); printCovarTable("ZA")
+printCovarTable("SA"); printCovarTable("IR")
+printCovarTable("TZ"); printCovarTable("ZM")
 @
@@
 #lapply(factors, printSingleFactorParamsTable)
-printSFParamsTable("K")
-printSFParamsTable("L")
-printSFParamsTable("Q")
-printSFParamsTable("X")
-printSFParamsTable("U")
+printSFParamsTable("K"); printSFParamsTable("L")
+printSFParamsTable("Q"); printSFParamsTable("X"); printSFParamsTable("U")
 @
@@
 printCDParamsTable()    #Without energy
-printCDParamsTable("Q")
-printCDParamsTable("X")
-printCDParamsTable("U")
+printCDParamsTable("Q"); printCDParamsTable("X"); printCDParamsTable("U") #With energy
 @
@@
 
-<<AIC_Table_Functions>>=
+<<AIC_Table_Functions, eval=TRUE>>=
 ###############################
@@
   ######################
+  # Cobb-Douglas without energy
   cdModels <- lapply(countryAbbrevs, cobbDouglasModel)
@@
   # Cobb-Douglas with U
-  cdUModels <- c(cobbDouglasModel("US", "U"), cobbDouglasModel("UK", "U"), cobbDouglasModel("JP", "U"))
   aicCDu <- cbind(US=AIC(cobbDouglasModel("US", "U")), 
@@
   ######################
+  # LINEX with Q
+  linexQModels <- lapply(countryAbbrevs, linexModel, energyType="Q")
+  aicLINEXq <- data.frame(lapply(linexQModels, AIC))
+  rownames(aicLINEXq) <- "LINEX$q$"
+  # LINEX with X
+  linexXModels <- lapply(countryAbbrevs, linexModel, energyType="X")
+  aicLINEXx <- data.frame(lapply(linexXModels, AIC))
+  rownames(aicLINEXx) <- "LINEX$x$"  
+  # LINEX with U
+  aicLINEXu <- cbind(US=AIC(linexModel("US", "U")), 
+                  UK=AIC(linexModel("UK", "U")), 
+                  JP=AIC(linexModel("JP", "U")),
+                  CN=NA, ZA=NA, SA=NA, IR=NA, TZ=NA, ZM=NA) #No U data for these countries.
+  rownames(aicLINEXu) <- "LINEX$u$"
 
   # Create the data.frame table
-  out <- rbind(aicSFk, aicSFl, aicSFq, aicSFx, aicSFu, aicCD, aicCDq, aicCDx, aicCDu) 
+  out <- rbind(aicSFk, aicSFl, aicSFq, aicSFx, aicSFu, aicCD, aicCDq, aicCDx, aicCDu, aicLINEXq, aicLINEXx, aicLINEXu) 
   # Create the xtable with caption and label

### 2013-02-15 EconGrowth.Rnw
Changed the labels on the single-factor graphs to be k, l, q, x, or u rather than the generic "m".

@@
 scaleTickSize <- -0.5 #50% of normal size and pointing INWARD!
-print(paste("sfParameterGraphHeight =", sfParameterGraphHeight))
-print(paste("cdParameterGraphHeight =", cdParameterGraphHeight))
 @
@@
 createSFParamsGraph <- function(factor){
+  # Set the name of the 2nd graph (m)
+  factorLabel <- paste("$", tolower(factor), "$", sep="")
   # Create a data table with the following columns:
@@
                    lwd = 1, #Sets line width to 1.0
-                   strip = strip.custom(bg="white", factor.levels=c("$\\lambda$", "$m$")),
+                   strip = strip.custom(bg="white", factor.levels=c("$\\lambda$", factorLabel)),
                    ylim = list(c(-0.05, 0.1), c(-0.5, 1.5)), #y axis limits

### 2013-02-15 EconGrowth.Rnw
No generating tables of LINEX parameters in the appendix.

@@
 \item Heun: Fix warnings of the form ``Warning:  step factor 0.000488281 reduced below ’minFactor’ of 0.000976562'' in the code that generates the Cobb-Douglas with energy fits.
+\item Heun: x-axis labels only on bottom for 9-panel lattice graphs
 \item \st{Heun: Ask Martin if he can supply an ``Economics'' affiliation. Will probably make a stronger paper.}
@@
 <<Historical_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="Historical data.
-Indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$).">>=
+Indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$).", eval=TRUE>>=
 createHistoricalLatticeGraph()
@@
 # Leave energyType blank to print a table for Cobb-Douglas without energy.
+##
 printCDParamsTable <- function(energyType){
@@
   dataTable <- replaceColName(dataTable, energyType, "iEToFit")
-  a_0Guess <- 1.0
+  a_0Guess <- 0.5
   c_tGuess <- 1.0
+  if (countryAbbrev == "SA"){
+    # Need adjusted guess values, becasue k and l are above GDP for SA.
+    a_0Guess <- -1
+    c_tGuess <- -6
+
+  }
   # Runs a non-linear least squares fit to the data with constraints
@@
                   start=list(a_0=a_0Guess, c_t=c_tGuess),
-                  control=nls.control(maxiter=50, tol=1e-06, minFactor=1/1024, 
-                                      printEval=FALSE, warnOnly=TRUE),
+                  control=nls.control(maxiter=50, tol=1e-06, minFactor=1/1024, printEval=FALSE, warnOnly=TRUE),
 #                   algorithm = "port",
@@
 
-@
+#################################################
+# Calculates parameter estimates and confidence intervals
+# for the LINEX production function given a country and an energyType.
+#
+# countryAbbrev is a string containing the 2-letter abbreviation for the country, e.g. "US" or "CN"
+# energyType is a string, one of "Q", "X", or "U"
+#
+# returns a data.frame of data for the LINEX model.
+# First row is the +95% CI on all parameters
+# Second row contains the parameter estimates
+# Third row is the -95% CI on all parameters
+# Each column has names: a_0 and c_t, corresponding to the parameters in the model.
+##
+linexData <- function(countryAbbrev, energyType){
+  #First, check to see if we want useful work (U) AND one of the countries for which we don't have data.
+  if (!haveDataCD(countryAbbrev, energyType)){
+    #Return a column of NAs if the above conditions have been met.
+    nRows <- 3 # +95% CI, CDe, and -95% CI.
+    nCols <- 2 # a_0 and c_t
+    df <- as.data.frame(matrix(NA, ncol = nCols, nrow = nRows))
+    colnames(df) <- c("a_0", "c_t")
+    rownames(df) <- c("+95% CI", "CDe", "-95% CI")
+    return(df)
+  }
+  # We have a combination of country and energy type for which we have data.
+  modelLINEX <- linexModel(countryAbbrev, energyType)
+  summaryLINEX <- summary(modelLINEX) # Gives the nls summary table.
+  dofLINEX <- summaryLINEX$df[2] # Gives the degrees of freedom for the model.
+  tvalLINEX <- qt(ciHalfLevel, df = dofLINEX)
+  ciLINEX <- confint(modelLINEX, level = ciLevel)  # Calculates confidence intervals for the LINEX model.
+  # Report results with SE
+  a_0 <- as.numeric(coef(modelLINEX)["a_0"])
+  c_t <- as.numeric(coef(modelLINEX)["c_t"])
+  # Combine all estimates and their confidence intervals into data frames with intelligent row names
+  estLINEX <- data.frame(a_0 = a_0, c_t = c_t)
+  row.names(estLINEX) <- "LINEX"
+  # The [1] subscripts pick off the lower confidence interval
+  lowerLINEX <- data.frame(a_0=ciLINEX["a_0","2.5%"], c_t=ciLINEX["c_t", "2.5%"])
+  row.names(lowerLINEX) <- "-95% CI"
+  # The [2] subscripts pick off the upper confidence interval
+  upperLINEX <- data.frame(a_0=ciLINEX["a_0","97.5%"], c_t=ciLINEX["c_t", "97.5%"])
+  row.names(upperLINEX) <- "+95% CI"
+  # Now create the data for a table and return it
+  dataLINEX <- rbind(upperLINEX, estLINEX, lowerLINEX)
+  return(dataLINEX)
+}
+
+############
+# Creates a row for the LINEX parameters table for the given country (2-letter code) and energyType (Q, X, or U)
+##
+linexCountryRow <- function(countryAbbrev, energyType){
+  dataLINEX <- linexData(countryAbbrev, energyType)
+  out <- cbind(dataLINEX["-95% CI", "a_0"], dataLINEX["LINEX", "a_0"], dataLINEX["+95% CI", "a_0"],
+               dataLINEX["-95% CI", "c_t"], dataLINEX["LINEX", "c_t"], dataLINEX["+95% CI", "c_t"])
+  return(out)
+}
+
+############################
+# Aggregates the LINEX results into a big data table for the given energyType.
+##
+linexParamsTable <- function(energyType){
+  #Do rbind on the results of creating a row in the table for every country abbreviation that we know.
+  dataLINEX <- do.call("rbind", lapply(countryAbbrevs, linexCountryRow, energyType=energyType))
+  colnames(dataLINEX) <- c(" ", "$a_0$", " ", " ", "$c_t$",  " ")
+  rownames(dataLINEX) <- countryAbbrevs
+  tableLINEX <- xtable(dataLINEX, 
+                    caption=paste("LINEX model (with $", tolower(energyType), "$) parameters for 1980-2011 (US, UK, JP), 1991-2010 (CN and ZA), and 1991-2011 (SA, IR, TZ, and ZM).
+(Parameter estimates beneath symbol.
+95\\% confidence interval bounds to left and right.)", sep=""),
+                    label=paste("tab:LINEX_Parameters_With_", energyType, sep=""),
+                    digits = c(1, 2,2,2, 2,2,2),
+                    align = "r|ccc|ccc") #Sets alignment of the numbers in the columns
+  return(tableLINEX)
+}
+
+############################
+# Prints a table with parameters from a LINEX model for the given energyType. 
+##
+printLINEXParamsTable <- function(energyType){
+  print(linexParamsTable(energyType), 
+    caption.placement="top", 
+    sanitize.colnames.function = identity, 
+    size="\\tiny",
+    table.placement="H")
+}
+@
+
+The LINEX model is of the form
+
+\begin{equation} \label{eq:LINEX_model}
+  y = e \: \mathrm{exp} \left[a_0 \left(2 - \frac{l + e}{k} \right) + a_0 c_t \left(\frac{l}{e} - 1 \right)       \right]
+\end{equation}
+
+\noindent where $e$ is any of $q$, $x$, or $u$.
 
@@
 
-<<LINEX_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="LINEX results.">>=
+<<LINEX_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="LINEX results.", eval=TRUE>>=
 createLinexLatticeGraph()
@@
 The following tables provide results for parameters in LINEX models.
+
+<<LINEX_Params_Table, results='asis', eval=TRUE>>=
+printLINEXParamsTable("Q"); printLINEXParamsTable("X"); printLINEXParamsTable("U")
+@
 

### 2013-02-15 EconGrowth.Rnw
Now generating tables of LINEX parameers in the appendix.

@@
       \end{itemize}
-\item Heun: Add Linex production function fits
+\item Heun: Add LINEX production function fits
       \begin{itemize}
       \item parameter graphs for each country
-      \item parameter tables for each country in the appendix
+      \item \st{parameter tables for each country in the appendix}
       \item \st{AIC rows in the AIC table}
@@
 
-<<LINEX_Params_Table, results='asis', eval=TRUE>>=
+<<LINEX_Params_Table, results='asis'>>=
 printLINEXParamsTable("Q"); printLINEXParamsTable("X"); printLINEXParamsTable("U")

### 2013-02-15 EconGrowth.Rnw
Added a function that creates country rows for the parameters graphs for LINEX.

--- 2013-02-15 EconGrowth.Rnw
@@
 
+###########################################
+# Creates a number of rows in a data.frame that contain information 
+# about the coefficients of a LINEX model for countryName and energyType
+# Each parameter has its own row with confidence intervals.
+# The country name is in a column. Which parameter is involved is
+# also in a column.
+# 
+# The return type is a data.frame.
+##
+linexCountryRowsForParamsGraph <- function(countryName, energyType){
+  #Create three rows, one for each parameter. Each row is a data.frame so that it is plottable!
+  dataLINEX <- linexData(countryName, energyType)
+  a_0Row <- data.frame(country = countryName, 
+                          parameter = "a_0", 
+                          lowerCI = dataLINEX["-95% CI", "a_0"], 
+                          value = dataLINEX["LINEX", "a_0"], 
+                          upperCI = dataLINEX["+95% CI", "a_0"])
+  c_tRow <- data.frame(country = countryName, 
+                         parameter = "c_t",
+                         lowerCI = dataLINEX["-95% CI", "c_t"],
+                         value = dataLINEX["LINEX", "c_t"],  
+                         upperCI = dataLINEX["+95% CI", "c_t"])
+  table <- rbind(a_0Row, c_tRow)
+  return(table)
+}
+
 ############################
@@
 \begin{equation} \label{eq:LINEX_model}
-  y = e \: \mathrm{exp} \left[a_0 \left(2 - \frac{l + e}{k} \right) + a_0 c_t \left(\frac{l}{e} - 1 \right)       \right]
+  y = e \: \mathrm{exp} \left[a_0 \left(2 - \frac{l + e}{k} \right) + a_0 c_t \left(\frac{l}{e} - 1 \right) \right],
 \end{equation}
@@
 
-Figure \ref{fig:LINEX_GDP_Lattice_Graph} compares LINEX model predictions with historica data.
-
-<<LINEX_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="LINEX results.", eval=TRUE>>=
+Figure \ref{fig:LINEX_GDP_Lattice_Graph} compares LINEX model predictions with historical data.
+
+<<LINEX_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="LINEX results.">>=
 createLinexLatticeGraph()

### 2013-02-15 EconGrowth.Rnw
Now including all parameter graphs for LINEX fits.

@@
       \end{itemize}
-\item Heun: Add LINEX production function fits
-      \begin{itemize}
-      \item parameter graphs for each country
-      \item \st{parameter tables for each country in the appendix}
-      \item \st{AIC rows in the AIC table}
-      \item \st{GDP comparison graph}
-      \end{itemize}
 \item Heun: Deal with missing covariance numbers when columns have unequal length.
@@
       \end{itemize}
+\item Heun: Eliminate blanks in the coefficient tables for the 95\% CIs in the LINEX model
+      \begin{itemize}
+      \item Zambia, upper bound on $c_t$
+      \end{itemize}
 \item Heun: Fix warnings of the form ``Warning:  step factor 0.000488281 reduced below ’minFactor’ of 0.000976562'' in the code that generates the Cobb-Douglas with energy fits.
 \item Heun: x-axis labels only on bottom for 9-panel lattice graphs
+\item Heun: adjust y axis limits on $a_0$ and $c_t$ parameter graphs for the LINEX model AFTER we finish debugging the LINEX models.
 \item \st{Heun: Ask Martin if he can supply an ``Economics'' affiliation. Will probably make a stronger paper.}
@@
 \item \st{Heun: Add covariance metrics.}
-\item Heun: Add single factor fits
+\item \st{Heun: Add single factor fits}
       \begin{itemize}
@@
 \item \st{Heun: Add setup variables for figure height and width where not already included.}
+\item \st{Heun: Add LINEX production function fits}
+      \begin{itemize}
+      \item \st{parameter graphs for each country}
+      \item \st{parameter tables for each country in the appendix}
+      \item \st{AIC rows in the AIC table}
+      \item \st{GDP comparison graph}
+      \end{itemize}
 \end{itemize}
@@
 cdParameterGraphHeight <- 2*h_param_graph + h_param_axis
+linexParameterGraphHeight <- h_param_graph + h_param_axis
 sfParameterGraphWidth <- maxWidth
 cdParameterGraphWidth <- maxWidth
+cesParameterGraphWidth <- maxWidth
+linexParameterGraphWidth <- maxWidth
 # Other graph parameters that apply to all graphs
@@
   covarXtable <- xtable(covarResults, 
-                      caption=paste("Covariance table for ", countryAbbrev, ".", sep=""), 
+                      caption=paste(countryAbbrev, "covariance table."), 
                       label=paste("tab:Covariance_", countryAbbrev, sep=""))
-                      # digits = c(1, 4,4,4, 2,2,2, 2,2,2),
-                      # align = "r|ccc|ccc|ccc") #Sets alignment of the numbers in the columns)
   return(covarXtable)
@@
 <<Historical_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="Historical data.
-Indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$).", eval=TRUE>>=
+Indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$).">>=
 createHistoricalLatticeGraph()
@@
 #############################
-# Creates a graph with confidene intervals for the Cobb-Douglas model for the given energyType
+# Creates a graph with confidence intervals for the Cobb-Douglas model for the given energyType
 ##
@@
 
+#############################
+# Creates a graph with confidence intervals for the LINEX model for the given energyType
+##
+createLINEXParamsGraph <- function(energyType){
+  # Create a data table with the following columns:
+  # country abbrev, parameter (a_0, c_t), -95% CI, value, +95% CI
+  dataTable <- do.call("rbind", lapply(countryAbbrevs, linexCountryRowsForParamsGraph, energyType=energyType))
+  graph <- segplot(country ~ upperCI + lowerCI | parameter, 
+                   data = dataTable, 
+                   centers = value, #identifies where the dots should be placed
+                   draw.bands = FALSE, #provides nicer error bars
+                   horizontal = FALSE, #makes error bars vertical and puts the countries in the x axis
+                   layout = c(2,1), #2 column, 2 row
+                   index.cond = list(c(1,2)), #orders the panels as alpha, beta, lambda, gamma
+                   #set labels and bg color in strip
+                   strip = strip.custom(factor.levels=c("$a_0$", "$c_t$"), bg="white"),
+                   col = "black", #Sets line color to black
+                   lwd = 1, #Sets line width to 1.0
+                   ylim = list(c(-0.05, 1.0), c(-0.5, 5)), #y axis limits
+                   scales = list(cex=scaleTextSize, #controls text size on scales.
+                                 tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
+                                 x=list(cex=0.75), #reduces text size so that country abbrevs are legible
+                                 y=list(relation="free", #allow each axis to be different
+                                        at=list(c(0.0, 0.5, 1.0), c(0, 1, 2, 3, 4, 5))   #y tick marks
+                                 )
+                   )
+  )
+  return(graph)
+}
+
 ############################
@@
 
-\noindent where $e$ is any of $q$, $x$, or $u$.
+\noindent where $e$ is any of $q$, $x$, or $u$, and $a_0$ and $c_t$ are fitting parameters.
 
@@
 
+Figure \ref{fig:LINEXq_Params_Graph} shows values and 95\% confidence intervals for the parameters for the LINEX model (with $q$).
+
+<<LINEXq_Params_Graph, fig.width=linexParameterGraphWidth, fig.height=linexParameterGraphHeight, fig.pos="H", fig.cap="LINEX (with $q$) model parameters.
+Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
+createLINEXParamsGraph("Q")
+@
+
 \subsection{LINEX with $X$}
 
+Figure \ref{fig:LINEXx_Params_Graph} shows values and 95\% confidence intervals for the parameters for the LINEX model (with $x$).
+
+<<LINEXx_Params_Graph, fig.width=linexParameterGraphWidth, fig.height=linexParameterGraphHeight, fig.pos="H", fig.cap="LINEX (with $x$) model parameters.
+Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
+createLINEXParamsGraph("X")
+@
+
 \subsection{LINEX with $U$}
+
+Figure \ref{fig:LINEXu_Params_Graph} shows values and 95\% confidence intervals for the parameters for the LINEX model (with $u$).
+
+<<LINEXu_Params_Graph, fig.width=linexParameterGraphWidth, fig.height=linexParameterGraphHeight, fig.pos="H", fig.cap="LINEX (with $u$) model parameters.
+Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
+createLINEXParamsGraph("U")
+@
 
@@
 
-<<LINEX_Params_Table, results='asis'>>=
+<<LINEX_Params_Table, results='asis', eval=TRUE>>=
 printLINEXParamsTable("Q"); printLINEXParamsTable("X"); printLINEXParamsTable("U")

### 2013-02-16 EconGrowth.Rnw
Edited the CES and LINEX equations.

@@
 \begin{equation} \label{eq:Single_Factor_Generic}
-  y = a^{\lambda (t-t_0)}f^{m}
+  y = \mathrm{e}^{\lambda (t-t_0)}f^{m}
 \end{equation}
@@
 \begin{equation} \label{eq:CD_No_Energy}
-  y = a^{\lambda (t-t_0)}k^{\alpha}l^{\beta}.
+  y = \mathrm{e}^{\lambda (t-t_0)}k^{\alpha}l^{\beta}.
 \end{equation}
@@
 \begin{equation} \label{eq:CD_With_Energy}
-  y = a^{\lambda (t-t_0)}k^{\alpha}l^{\beta}e^{\gamma},
+  y = \mathrm{e}^{\lambda (t-t_0)}k^{\alpha}l^{\beta}e^{\gamma},
 \end{equation}
@@
 
-<<CES functions, eval=FALSE>>=
+<<CES functions, eval=TRUE>>=
 ####################
@@
   dataTable <- replaceColName(dataTable, energyType, "iEToFit")
-print(dataTable)
   # Establish guess values for phi beta, zeta, lambda_L and lambda_E.
   sigmaGuess <- 0.663 # 0.663 for Sweden
-  zetaGuess <- 0.147 # 0.147 for Sweden
+  # gamma_EGuess <- 0.147 # 0.147 for Sweden
+  gamma_EGuess <- 0.01
   betaGuess <- 0.7 # 0.7 for Sweden
@@
   # Runs a non-linear least squares fit to the data with constraints
-  modelCES <- nls(iGDP ~ ((1-zeta)^(1.0/sigma) * ((exp(lambda_L*iYear))^beta 
+  modelCES <- nls(iGDP ~ ((1-gamma_E)^(1.0/sigma) * ((exp(lambda_L*iYear))^beta 
                                                   * iCapStk^(1-beta) 
                                                   * iLabor^beta)^((sigma-1.0)/sigma) 
-                          + zeta^(1.0/sigma)*(exp(lambda_E*iYear) 
+                          + gamma_E^(1.0/sigma)*(exp(lambda_E*iYear) 
                                                   * iEToFit)^((sigma-1.0)/sigma))^(sigma/(sigma-1.0)), 
                   data=dataTable,
-                  start=list(sigma=sigmaGuess, zeta=zetaGuess, beta=betaGuess, 
+                  start=list(sigma=sigmaGuess, gamma_E=gamma_EGuess, beta=betaGuess, 
                              lambda_L=lambda_LGuess, lambda_E=lambda_EGuess),
@@
                   algorithm = "port",
-                  lower = list(sigma=-Inf, zeta=0, beta=0.0, lambda_L=0.0, lambda_E=0.0),
-                  upper = list(sigma= Inf, zeta=1, beta=1.0, lambda_L=0.1, lambda_E=0.1),
+                  lower = list(sigma=-Inf, gamma_E=0.0, beta=-Inf, lambda_L=-Inf, lambda_E=-Inf),
+                  upper = list(sigma= Inf, gamma_E=1.0, beta= Inf, lambda_L= Inf, lambda_E= Inf),
                   )
@@
 }
-model <- cesModel("US", "Q")
-summary <- summary(model)
-print(summary)
+print("US Q")
+print(summary(cesModel("US", "Q")))
+
+print("")
+print("UK Q")
+print(summary(cesModel("UK", "Q")))
+
+print("")
+print("JP Q")
+print(summary(cesModel("JP", "Q")))
+
+print("")
+print("CN Q")
+print(summary(cesModel("CN", "Q")))
+
+print("")
+print("ZA Q")
+print(summary(cesModel("ZA", "Q")))
+
+print("")
+print("SA Q")
+print(summary(cesModel("SA", "Q")))
+
+print("")
+print("IR Q")
+print(summary(cesModel("IR", "Q")))
+
+print("")
+print("TZ Q")
+print(summary(cesModel("TZ", "Q")))
+
+print("")
+print("ZM Q")
+print(summary(cesModel("ZM", "Q")))
 
@@
 @
+
+The CES model is of the form
+
+\begin{equation} \label{eq:CES_model}
+  y = \left\{ (1-\gamma_E)^{1/\sigma} \left[ k^{\alpha} \left( \mathrm{e}^{\lambda_L(t-t_0)} l \right)^{\beta} \right]^{\frac{\sigma-1}{\sigma}}   
+      + (\gamma_E)^{1/\sigma} \left[ \mathrm{e}^{\lambda_E(t-t_0)} e \right]^{\frac{\sigma - 1}{\sigma}}   \right\}
+      ^{\frac{\sigma}{\sigma - 1}},
+\end{equation}
+
+\noindent where $e$ is any of $q$, $x$, or $u$; $\gamma_E$, $\lambda_L$, $\lambda_E$, $\beta$, and $\sigma$ are fitting parameters; and $\mathrm{e}$ is the base of the natural logarithm.
+Ths sum $\alpha + \beta$ is constrained to unity.
 
@@
 \begin{equation} \label{eq:LINEX_model}
-  y = e \: \mathrm{exp} \left[a_0 \left(2 - \frac{l + e}{k} \right) + a_0 c_t \left(\frac{l}{e} - 1 \right) \right],
+  y = e \: \mathrm{e}^{\left[a_0 \left(2 - \frac{l + e}{k} \right) + a_0 c_t \left(\frac{l}{e} - 1 \right)\right]} ,
 \end{equation}
 
-\noindent where $e$ is any of $q$, $x$, or $u$, and $a_0$ and $c_t$ are fitting parameters.
+\noindent where $e$ is any of $q$, $x$, or $u$; $a_0$ and $c_t$ are fitting parameters; and $\mathrm{e}$ is the base of the natural logarithm.
 
@@
 <<LINEXq_Params_Graph, fig.width=linexParameterGraphWidth, fig.height=linexParameterGraphHeight, fig.pos="H", fig.cap="LINEX (with $q$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
+Vertical bars indicate 95\\% confidence intervals.">>=
 createLINEXParamsGraph("Q")
@@
 <<LINEXx_Params_Graph, fig.width=linexParameterGraphWidth, fig.height=linexParameterGraphHeight, fig.pos="H", fig.cap="LINEX (with $x$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
+Vertical bars indicate 95\\% confidence intervals.">>=
 createLINEXParamsGraph("X")
@@
 <<LINEXu_Params_Graph, fig.width=linexParameterGraphWidth, fig.height=linexParameterGraphHeight, fig.pos="H", fig.cap="LINEX (with $u$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
+Vertical bars indicate 95\\% confidence intervals.">>=
 createLINEXParamsGraph("U")
 @
+
+\subsection{LINEX comparisons}
 

### 2013-02-16 EconGrowth.Rnw
Now using nlmrt to do CES curve fits.

@@
 require(xtable)
+require(nlmrt)
 # tikz allows use of LaTeX formatting and font in graphs. Allows for a consistent look across the paper.
@@
   dataTable <- replaceColName(dataTable, energyType, "iEToFit")
-  # Establish guess values for phi beta, zeta, lambda_L and lambda_E.
+  # Establish default guesses for sigma, gamma_E, beta, lambda_L and lambda_E.
   sigmaGuess <- 0.663 # 0.663 for Sweden
-  # gamma_EGuess <- 0.147 # 0.147 for Sweden
-  gamma_EGuess <- 0.01
+  gamma_EGuess <- 0.01 # Minimum contribution by energy is the default.
   betaGuess <- 0.7 # 0.7 for Sweden
@@
   lambda_EGuess <- 0.018 # 0.018 for Sweden
+  lower = list(sigma=-Inf, gamma_E=0.0, beta=-Inf, lambda_L=-Inf, lambda_E=-Inf)
+  upper = list(sigma= Inf, gamma_E=1.0, beta= Inf, lambda_L= Inf, lambda_E= Inf)
+  if (countryAbbrev == "US"){
+    gamma_EGuess <- 0.147 # 0.147 for Sweden
+  }
+  if (countryAbbrev == "UK"){
+    sigmaGuess <- 0.5
+    gamma_EGuess <- 0.147 # 0.147 for Sweden
+    betaGuess <- 0.9
+    lambda_LGuess <- 0.0
+    lambda_EGuess <- 0.0
+    lower = list(sigma=-Inf, gamma_E=0.0, beta=-Inf, lambda_L=-0.3, lambda_E=-0.3)
+    upper = list(sigma= Inf, gamma_E=1.0, beta= Inf, lambda_L= 0.3, lambda_E= 0.3)
+  }
+  if (countryAbbrev == "CN"){
+
+  }
   # Runs a non-linear least squares fit to the data with constraints
-  modelCES <- nls(iGDP ~ ((1-gamma_E)^(1.0/sigma) * ((exp(lambda_L*iYear))^beta 
-                                                  * iCapStk^(1-beta) 
-                                                  * iLabor^beta)^((sigma-1.0)/sigma) 
+#   modelCES <- nls(iGDP ~ ((1-gamma_E)^(1.0/sigma) * ((exp(lambda_L*iYear))^beta 
+#                                                   * iLabor^beta
+#                                                   * iCapStk^(1-beta) )^((sigma-1.0)/sigma) 
+#                           + gamma_E^(1.0/sigma)*(exp(lambda_E*iYear) 
+#                                                   * iEToFit)^((sigma-1.0)/sigma))^(sigma/(sigma-1.0)), 
+#                   data=dataTable,
+#                   start=list(sigma=sigmaGuess, gamma_E=gamma_EGuess, beta=betaGuess, 
+#                              lambda_L=lambda_LGuess, lambda_E=lambda_EGuess),
+#                   control=nls.control(maxiter=10000, tol=1e-05, minFactor=1/1024, 
+#                                       printEval=TRUE, warnOnly=TRUE),
+#                   algorithm = "port",
+#                   lower = lower,
+#                   upper = upper
+#                   )
+  model <- iGDP ~ ((1-gamma_E)^(1.0/sigma) * ((exp(lambda_L*iYear))^beta 
+                                                  * iLabor^beta
+                                                  * iCapStk^(1-beta) )^((sigma-1.0)/sigma) 
                           + gamma_E^(1.0/sigma)*(exp(lambda_E*iYear) 
-                                                  * iEToFit)^((sigma-1.0)/sigma))^(sigma/(sigma-1.0)), 
+                                                  * iEToFit)^((sigma-1.0)/sigma))^(sigma/(sigma-1.0))
+  modelCES <- nlxb(model,
                    data=dataTable,
                    start=list(sigma=sigmaGuess, gamma_E=gamma_EGuess, beta=betaGuess, 
-                             lambda_L=lambda_LGuess, lambda_E=lambda_EGuess),
-                  control=nls.control(maxiter=10000, tol=1e-06, minFactor=1/1024, 
-                                      printEval=FALSE, warnOnly=TRUE),
-                  algorithm = "port",
-                  lower = list(sigma=-Inf, gamma_E=0.0, beta=-Inf, lambda_L=-Inf, lambda_E=-Inf),
-                  upper = list(sigma= Inf, gamma_E=1.0, beta= Inf, lambda_L= Inf, lambda_E= Inf),
-                  )
+                              lambda_L=lambda_LGuess, lambda_E=lambda_EGuess)
+                   )
+print(class(modelCES))
+print(modelCES)
+  modelCES <- wrapnls(modelCES)
+print(class(modelCES))
   return(modelCES)
@@
 
-The CES model is of the form
+The CES model has the form
 
@@
 
-\noindent where $e$ is any of $q$, $x$, or $u$; $\gamma_E$, $\lambda_L$, $\lambda_E$, $\beta$, and $\sigma$ are fitting parameters; and $\mathrm{e}$ is the base of the natural logarithm.
+\noindent where $e$ is any of $q$, $x$, or $u$; $\sigma$, $\gamma_E$, $\beta$, $\lambda_L$, and $\lambda_E$ are fitting parameters; and $\mathrm{e}$ is the base of the natural logarithm.
 Ths sum $\alpha + \beta$ is constrained to unity.
@@
 
-The LINEX model is of the form
+The LINEX model has the form
 

### 2013-02-16 EconGrowth.Rnw
Now trying nlxb for CES.

@@
                    )
-print(class(modelCES))
 print(modelCES)
-  modelCES <- wrapnls(modelCES)
-print(class(modelCES))
   return(modelCES)

### 2013-02-17 EconGrowth.Rnw
Now including a biblography file allowing citations. Used Stern and Kander as a first example.
Now includes a test for the nlmrt package from https://stat.ethz.ch/pipermail/r-help/2012-November/330554.html.

@@
 scaleTickSize <- -0.5 #50% of normal size and pointing INWARD!
+@
+
+<<nlmrt tests, eval=TRUE>>=
+# From https://stat.ethz.ch/pipermail/r-help/2012-November/330554.html
+Laptop_sale <- c(1405,1863,2027,2669,2938,5275,6595,6943,8621,10905,12420,22400,32380,31600,34900,43163,47838,47592)
+CuSale <- Laptop_sale
+time <- seq_along(Laptop_sale)
+Bass.Model <- Laptop_sale ~ m * ((p + q)^2/p) * (exp(-(p + q) * time)/((q /p) * exp(-(p + q) * time) + 1)^2)
+Bass.Fit <- nls(formula = Bass.Model, start = c(p = 0.03, q = 0.4, m = max(CuSale)), trace = FALSE)
+Bass.Fit
+library(nlmrt)
+xdata<-data.frame(Laptop_sale, time)
+Bass.Fitn <- nlxb(formula = Bass.Model, start = c(p = 0.03, q = 0.4, m = max(CuSale)), data=xdata,trace=FALSE)
+print("")
+print("After nlxb fit:")
+Bass.Fitn
+print(summary(Bass.Fitn))
+
+Bass.Fitn <- wrapnls(formula = Bass.Model, start = c(p = 0.03, q = 0.4, m = max(CuSale)), data=xdata,trace=FALSE)
+print("")
+print("After wrapnls fit:")
+print(summary(Bass.Fitn))
+
 @
@@
 
-<<CES functions, eval=TRUE>>=
+<<ces functions, eval=FALSE>>=
 ####################
@@
                    start=list(sigma=sigmaGuess, gamma_E=gamma_EGuess, beta=betaGuess, 
-                              lambda_L=lambda_LGuess, lambda_E=lambda_EGuess)
-                   )
-print(modelCES)
+                              lambda_L=lambda_LGuess, lambda_E=lambda_EGuess),
+                   trace=TRUE
+                  )
   return(modelCES)
@@
 
-The CES model has the form
+\citet{Stern:2012ey} developed a CES model of the following form
 
@@
 \bibliographystyle{model2-names}
-\bibliography{<your-bib-database>}
+%%\bibliography{<your-bib-database>}
+\bibliography{EconGrowth.bib}
 

### 2013-02-18 EconGrowth.Rnw
Added some CES information to the US and UK Excel workbooks. Added a footnote about Stern and Kander's equation being wrong in the text of their 2012 paper.

--- 2013-02-16 EconGrowth.Rnw
@@
 \usepackage{float} %Allows precise positioning of tables and figures within the text
+\usepackage{amsmath} %Allows \begin{equation*} for unnumbered equations
 
@@
   # ********************************************************************************************************
-  warning=FALSE, #Tells whether to show warnings in the output.
+  warning=TRUE, #Tells whether to show warnings in the output.
   dev='tikz',    #Allows LaTeX code in graphical output. E.g., "$y$" for a variable name in the legend for a graph.
@@
 
+<<nlmrt tests, eval=FALSE>>=
+# From https://stat.ethz.ch/pipermail/r-help/2012-November/330554.html
+Laptop_sale <- c(1405,1863,2027,2669,2938,5275,6595,6943,8621,10905,12420,22400,32380,31600,34900,43163,47838,47592)
+CuSale <- Laptop_sale
+time <- seq_along(Laptop_sale)
+Bass.Model <- Laptop_sale ~ m * ((p + q)^2/p) * (exp(-(p + q) * time)/((q /p) * exp(-(p + q) * time) + 1)^2)
+# Bass.Fit <- nls(formula = Bass.Model, start = c(p = 0.03, q = 0.4, m = max(CuSale)), trace = FALSE)
+# Bass.Fit
+library(nlmrt)
+xdata<-data.frame(Laptop_sale, time)
+Bass.Fitn <- nlxb(formula = Bass.Model, start = c(p = 0.03, q = 0.4, m = max(CuSale)), data=xdata,trace=TRUE)
+print("")
+print("After nlxb fit:")
+Bass.Fitn
+print(summary(Bass.Fitn))
+
+Bass.Fitn <- wrapnls(formula = Bass.Model, start = c(p = 0.03, q = 0.4, m = max(CuSale)), data=xdata,trace=FALSE)
+print("")
+print("After wrapnls fit:")
+print(summary(Bass.Fitn))
+@
+
 <<Data Functions, eval=TRUE>>=
@@
   }
+  start <- list(lambda=lambdaGuess, m=mGuess)
   # Runs a non-linear least squares fit to the data. We've replaced beta with 1-alpha for simplicity.
-  modelSF <- nls(iGDP ~ exp(lambda*iYear) * f^m, 
-                 data=dataTable, 
-                 start = list(lambda=lambdaGuess, m=mGuess)
-                 )
+  model <- iGDP ~ exp(lambda*iYear) * f^m
+  modelSF <- nls(formula=model, data=dataTable, start = start)
+#   model <- iGDP ~ exp(lambda*iYear) * f^m
+#   modelSF <- wrapnls(formula=model, data=dataTable, start=list(lambda=lambdaGuess, m=mGuess))
   return(modelSF)
@@
 
-\noindent to historical data where the factor of production ($f$) is any of $k$, $l$, $q$, $x$, or $u$, and the exponent ($m$) is $\alpha$ for $k$, $\beta$ for $l$, or $\gamma$ for $q$, $x$, or $u$.
+\noindent to historical data where the factor of production ($f$) is any of $k$, $l$, $q$, $x$, or $u$, and the exponent ($m$) is $\alpha$ for $k$, $\beta$ for $l$, or $\gamma$ for $q$, $x$, and $u$.
 
@@
     alphaGuess <- 0.7 #0.7 gives good results for all countries.  
+    start <- list(lambda=lambdaGuess, alpha=alphaGuess)
     # Runs a non-linear least squares fit to the data. We've replaced beta with 1-alpha for simplicity.
-    modelCD <- nls(iGDP ~ exp(lambda*iYear) * iCapStk^alpha * iLabor^(1 - alpha), 
-                   data=dataTable, 
-                   start = list(lambda=lambdaGuess, alpha=alphaGuess),
+    model <- iGDP ~ exp(lambda*iYear) * iCapStk^alpha * iLabor^(1 - alpha)
+    modelCD <- nls(formula=model, data=dataTable, start = start,
                    #Include the next 3 lines to fit with constraints.
@@
     bGuess <- alphaGuess + betaGuess
+    start <- list(lambda=lambdaGuess, a=aGuess, b=bGuess)
     # Now actually do the fit, using the column name "iEToFit".
-    modelCDe <- nls(iGDP ~ exp(lambda*iYear) * iCapStk^min(a,b) * iLabor^abs(b-a) * iEToFit^(1.0 - max(a,b)), 
-                    data = dataTable,
-                    start = list(lambda=lambdaGuess, a=aGuess, b=bGuess),
+    model <- iGDP ~ exp(lambda*iYear) * iCapStk^min(a,b) * iLabor^abs(b-a) * iEToFit^(1.0 - max(a,b))
+    modelCDe <- nls(formula=model, data = dataTable, start = start,
                     control = nls.control(maxiter = 200, 
@@
 
-<<CES functions, eval=TRUE>>=
+<<ces functions, eval=TRUE>>=
 ####################
@@
   # Establish default guesses for sigma, gamma_E, beta, lambda_L and lambda_E.
-  sigmaGuess <- 0.663 # 0.663 for Sweden
-  gamma_EGuess <- 0.01 # Minimum contribution by energy is the default.
-  betaGuess <- 0.7 # 0.7 for Sweden
-  lambda_LGuess <- 0.011 # 0.011 for Sweden
-  lambda_EGuess <- 0.018 # 0.018 for Sweden
+  start <- list(sigma=0.9, gamma_E=0.01, beta=0.7, lambda_L=0.011, lambda_E=0.018) #values for Sweden
+  # Establish bounds
   lower = list(sigma=-Inf, gamma_E=0.0, beta=-Inf, lambda_L=-Inf, lambda_E=-Inf)
   upper = list(sigma= Inf, gamma_E=1.0, beta= Inf, lambda_L= Inf, lambda_E= Inf)
+  # Now some country-specific values.
   if (countryAbbrev == "US"){
-    gamma_EGuess <- 0.147 # 0.147 for Sweden
+    start <- list(sigma=0.95, gamma_E=0.1, beta=0.7, lambda_L=0.015, lambda_E=0.015) #values for Sweden
   }
   if (countryAbbrev == "UK"){
-    sigmaGuess <- 0.5
-    gamma_EGuess <- 0.147 # 0.147 for Sweden
-    betaGuess <- 0.9
-    lambda_LGuess <- 0.0
-    lambda_EGuess <- 0.0
+    start <- list(sigma=0.95, gamma_E=0.2, beta=0.7, lambda_L=0.02, lambda_E=0.02) #values for Sweden
     lower = list(sigma=-Inf, gamma_E=0.0, beta=-Inf, lambda_L=-0.3, lambda_E=-0.3)
@@
   # Runs a non-linear least squares fit to the data with constraints
-#   modelCES <- nls(iGDP ~ ((1-gamma_E)^(1.0/sigma) * ((exp(lambda_L*iYear))^beta 
+#   model <- iGDP ~ ((1-gamma_E)^(1.0/sigma) * ((exp(lambda_L*iYear))^beta 
 #                                                   * iLabor^beta
 #                                                   * iCapStk^(1-beta) )^((sigma-1.0)/sigma) 
-#                           + gamma_E^(1.0/sigma)*(exp(lambda_E*iYear) 
-#                                                   * iEToFit)^((sigma-1.0)/sigma))^(sigma/(sigma-1.0)), 
+#                   + gamma_E^(1.0/sigma)*(exp(lambda_E*iYear) * iEToFit)^((sigma-1.0)/sigma))^(sigma/(sigma-1.0))
+  model <- iGDP ~ ((1-gamma_E) * ((exp(lambda_L*iYear))^beta * iLabor^beta * iCapStk^(1-beta) )^((sigma-1.0)/sigma) 
+                  + gamma_E * (exp(lambda_E*iYear) * iEToFit)^((sigma-1.0)/sigma))^(sigma/(sigma-1.0))
+  modelCES <- nls(formula=model, data=dataTable, start=start,
+                  control=nls.control(maxiter=10000, tol=1e-05, minFactor=1/1024, 
+                                      printEval=TRUE, warnOnly=TRUE),
+                  algorithm = "port",
+                  lower = lower,
+                  upper = upper,
+                  trace=TRUE
+                  )
+#   modelCES <- nlxb(model,
 #                    data=dataTable,
@@
 #                               lambda_L=lambda_LGuess, lambda_E=lambda_EGuess),
-#                   control=nls.control(maxiter=10000, tol=1e-05, minFactor=1/1024, 
-#                                       printEval=TRUE, warnOnly=TRUE),
-#                   algorithm = "port",
-#                   lower = lower,
-#                   upper = upper
+#                    trace=TRUE
 #                   )
-  model <- iGDP ~ ((1-gamma_E)^(1.0/sigma) * ((exp(lambda_L*iYear))^beta 
-                                                  * iLabor^beta
-                                                  * iCapStk^(1-beta) )^((sigma-1.0)/sigma) 
-                          + gamma_E^(1.0/sigma)*(exp(lambda_E*iYear) 
-                                                  * iEToFit)^((sigma-1.0)/sigma))^(sigma/(sigma-1.0))
-  modelCES <- nlxb(model,
-                   data=dataTable,
-                   start=list(sigma=sigmaGuess, gamma_E=gamma_EGuess, beta=betaGuess, 
-                              lambda_L=lambda_LGuess, lambda_E=lambda_EGuess)
-                   )
-print(modelCES)
   return(modelCES)
@@
 
-The CES model has the form
+\citet{Stern:2012ey} developed a CES model of the form
 
 \begin{equation} \label{eq:CES_model}
+  y = \left\{ (1-\gamma_E) \left[ k^{\alpha} \left( \mathrm{e}^{\lambda_L(t-t_0)} l \right)^{\beta} \right]^{\frac{\sigma-1}{\sigma}}   
+      + (\gamma_E) \left[ \mathrm{e}^{\lambda_E(t-t_0)} e \right]^{\frac{\sigma - 1}{\sigma}}   \right\}
+      ^{\frac{\sigma}{\sigma - 1}},
+\end{equation}
+
+\noindent where $e$ is any of $q$, $x$, or $u$; $\sigma$, $\gamma_E$, $\beta$, $\lambda_L$, and $\lambda_E$ are fitting parameters; $\mathrm{e}$ is the base of the natural logarithm; and the sum $\alpha + \beta$ is constrained to unity.\footnote{The CES equation in \citet{Stern:2012ey} appears as
+
+\begin{equation*} \label{eq:Stern_CES_model}
   y = \left\{ (1-\gamma_E)^{1/\sigma} \left[ k^{\alpha} \left( \mathrm{e}^{\lambda_L(t-t_0)} l \right)^{\beta} \right]^{\frac{\sigma-1}{\sigma}}   
@@
       ^{\frac{\sigma}{\sigma - 1}},
-\end{equation}
-
-\noindent where $e$ is any of $q$, $x$, or $u$; $\sigma$, $\gamma_E$, $\beta$, $\lambda_L$, and $\lambda_E$ are fitting parameters; and $\mathrm{e}$ is the base of the natural logarithm.
-Ths sum $\alpha + \beta$ is constrained to unity.
+\end{equation*}
+
+but the $1/\sigma$ exponent on the $(1-\gamma_E)$ and $\gamma_E$ terms seems erroneous due to $y(t_\mathrm{0}) \neq 1$.}
 

### 2013-02-21 EconGrowth.Rnw
Now including US, UK, JP, and CN for CES fits.

@@
 \usepackage{float} %Allows precise positioning of tables and figures within the text
-\usepackage{amsmath} %Allows \begin{equation*} for unnumbered equations
+\usepackage{amsmath} %Allows \begin{equation*} \end{equation*} for unnumbered equations
 
@@
 require(nlmrt)
+require(micEconCES)
 # tikz allows use of LaTeX formatting and font in graphs. Allows for a consistent look across the paper.
@@
 scaleTickSize <- -0.5 #50% of normal size and pointing INWARD!
-@
-
-<<nlmrt tests, eval=FALSE>>=
-# From https://stat.ethz.ch/pipermail/r-help/2012-November/330554.html
-Laptop_sale <- c(1405,1863,2027,2669,2938,5275,6595,6943,8621,10905,12420,22400,32380,31600,34900,43163,47838,47592)
-CuSale <- Laptop_sale
-time <- seq_along(Laptop_sale)
-Bass.Model <- Laptop_sale ~ m * ((p + q)^2/p) * (exp(-(p + q) * time)/((q /p) * exp(-(p + q) * time) + 1)^2)
-# Bass.Fit <- nls(formula = Bass.Model, start = c(p = 0.03, q = 0.4, m = max(CuSale)), trace = FALSE)
-# Bass.Fit
-library(nlmrt)
-xdata<-data.frame(Laptop_sale, time)
-Bass.Fitn <- nlxb(formula = Bass.Model, start = c(p = 0.03, q = 0.4, m = max(CuSale)), data=xdata,trace=TRUE)
-print("")
-print("After nlxb fit:")
-Bass.Fitn
-print(summary(Bass.Fitn))
-
-Bass.Fitn <- wrapnls(formula = Bass.Model, start = c(p = 0.03, q = 0.4, m = max(CuSale)), data=xdata,trace=FALSE)
-print("")
-print("After wrapnls fit:")
-print(summary(Bass.Fitn))
 @
@@
   dataTable <- loadData(countryAbbrev)
+  if (energyType == "U"){
+    # Trim the dataset to include only those years for which U is available.
+    dataTable <- subset(dataTable, !is.na(iU))
+  }
+  # Trim data from China and South Africa that is missing labor information for 2011.
+  dataTable <- subset(dataTable, !is.na(iLabor))
   # We need to do the CES fit with the desired energyType.
@@
   # Runs a non-linear least squares fit to the data with constraints
+  # This is the version of the function from the Stern and Kander (2012) paper. However, it includes a 
+  # 1/sigma exponent on the gamma_E terms, which, I believe, is bogus.
 #   model <- iGDP ~ ((1-gamma_E)^(1.0/sigma) * ((exp(lambda_L*iYear))^beta 
@@
 #                   + gamma_E^(1.0/sigma)*(exp(lambda_E*iYear) * iEToFit)^((sigma-1.0)/sigma))^(sigma/(sigma-1.0))
-  model <- iGDP ~ ((1-gamma_E) * ((exp(lambda_L*iYear))^beta * iLabor^beta * iCapStk^(1-beta) )^((sigma-1.0)/sigma) 
-                  + gamma_E * (exp(lambda_E*iYear) * iEToFit)^((sigma-1.0)/sigma))^(sigma/(sigma-1.0))
-  modelCES <- nls(formula=model, data=dataTable, start=start,
-                  control=nls.control(maxiter=10000, tol=1e-05, minFactor=1/1024, 
-                                      printEval=TRUE, warnOnly=TRUE),
-                  algorithm = "port",
-                  lower = lower,
-                  upper = upper,
-                  trace=TRUE
-                  )
+
+  # This is the corrected version of the Stern and Kander (2012) paper.
+#   model <- iGDP ~ ((1-gamma_E) * ((exp(lambda_L*iYear))^beta * iLabor^beta * iCapStk^(1-beta) )^((sigma-1.0)/sigma) 
+#                   + gamma_E * (exp(lambda_E*iYear) * iEToFit)^((sigma-1.0)/sigma))^(sigma/(sigma-1.0))
+
+  # This is the nls fit to the CES model  
+#   modelCES <- nls(formula=model, data=dataTable, start=start,
+#                   control=nls.control(maxiter=10000, tol=1e-05, minFactor=1/1024, 
+#                                       printEval=TRUE, warnOnly=TRUE),
+#                   algorithm = "port",
+#                   lower = lower,
+#                   upper = upper,
+#                   trace=TRUE
+#                   )
+
+  # An attempt with nlmrt function nlxb. Doesn't provide many good results.
 #   modelCES <- nlxb(model,
@@
 #                   )
+
+  # Try a fit to a nested CES function with the micEconCES package.  
+  # This approach is based on a white paper by Henningsen and Henningsen 
+  # http://okonomi.foi.dk/workingpapers/WPpdf/WP2011/WP_2011_9_econometric_estimation_CES.pdf.
+  # Set a few of the variables up front
+  yName = "iGDP"
+  xNames = c("iCapStk", "iLabor", "iEToFit")
+  tName = "iYear"
+  control=nls.lm.control(maxiter=1000, maxfev=2000)
+  if (countryAbbrev == "US") {
+    # With Q, The unconstrained optimization leads to rho1 = -0.72 and sigma1 = 3.57, which is not 
+    # economically meaningful.  So, a grid search was performed, and it confirmed that low values of 
+    # rho1 yield a better fit. In fact, the lower the value of rho1, the better. So, we'll set it 
+    # here at rho1=0.0, which makes the elasticity of substitution between k and l sigma1 = 1.0, 
+    # giving the Cobb-Douglas form for the k l portion of the CES function. Similar results are found
+    # for X and U.
+    rho1 = 0.0
+    # Unconstrained optimization leads to rho = 25.7 and sigma = 0.0374, indicating that (kl) and (e) are 
+    # complimentary.  We'll let the estCES function solve for the best value.
+    modelCES <- cesEst(data=dataTable, yName=yName, xNames=xNames, tName=tName, control=control,
+                       method="LM",
+                       rho1=rho1
+                       )
+  } else if (countryAbbrev == "UK") {
+    # The unconstrained optimization leads to rho1 = -2.4 and sigma1 = -0.71, which is not economically meaningful.
+    # So, a grid search was performed, and it confirmed that low values of rho1 yield a better fit. In fact, the 
+    # lower the value of rho1, the better. So, we'll set it here at rho1=0.0, which makes the elasticity of 
+    # substitution between k and l sigma1 = 1.0, giving the Cobb-Douglas form for the k l portion of the CES function.
+    # rho1 = c(0.00, 0.01, 0.02)
+    rho1 = 0.0
+    modelCES <- cesEst(data=dataTable, yName=yName, xNames=xNames, tName=tName, control=control,
+                       method="LM",
+                       rho1=rho1
+                       )
+  } else if (countryAbbrev == "JP") {
+    # The unconstrained optimization leads to rho1 = 7.99 and sigma1 = 0.11, indicating complementarity between k & l,
+    # but different from the results for the US and UK (where k & l were found to be substitutes).  However, the
+    # p value for rho1 is very high (0.3), indicating that rho1 is not making a significant contribution to the model. 
+    # The unconstrained fit gives R^ = 0.996 and sigma = 0.103, indicating complementarity between (kl) and (e).
+    # 
+    # In fact, we could force rho1 = 0.0 and achieve rho = 280 and sigma = 0.00356 with R^2 = 0.988, a very small
+    # decrease, indeed.  Note that both the constrained and unconstrained fits give small sigma, indicating
+    # that (kl) and (e) are complimentary.
+    modelCES <- cesEst(data=dataTable, yName=yName, xNames=xNames, tName=tName, control=control,
+                       method="LM"
+                       )
+  } else if (countryAbbrev == "CN"){
+    # Unconstrained optimization: rho1 < -0.2290, rho = 14.1651, R^2 = 0.9984. This corresponds to sigma1 = 1.297
+    # and sigma = 0.0659, indicating that (kl) and (e) are complements and k & l are substitutes.  However, none of the
+    # rho or sigma values are statistically significant.
+    # Now, sigma1 > 1 is not economically meaningful, so we'll set rho1 = 0 to force sigma1 = 1.0. When we do that, 
+    # we obtain sigma1 = 1.0 (so perfect substitution between k and l) and sigma = 7.19 (again, not economically
+    # meaningful) with R^2 = 0.9983.  Again, none of the rho or sigma values are statistically significant.
+    # Furthermore, the only significant varluable is gamma = 1.0731.
+    # So, for the final fit, I'll put rho1 = 0.0 and rho = 0.0. The final R^2 = 
+    rho1 = 0.0
+    rho = 0.0
+    modelCES <- cesEst(data=dataTable, yName=yName, xNames=xNames, tName=tName, control=control,
+                       method="LM",
+                       rho1=rho1,
+                       rho=rho                     
+                       )
+  }
+
   return(modelCES)
 }
-print("US Q")
-print(summary(cesModel("US", "Q")))
-
-print("")
-print("UK Q")
-print(summary(cesModel("UK", "Q")))
-
-print("")
-print("JP Q")
-print(summary(cesModel("JP", "Q")))
-
-print("")
+# print("US U")
+# print(summary(cesModel("US", "U")))
+# 
+# print("")
+# print("UK U")
+# print(summary(cesModel("UK", "U")))
+# 
+# print("")
+# print("JP U")
+# print(summary(cesModel("JP", "U")))
+
+# print("")
 print("CN Q")
 print(summary(cesModel("CN", "Q")))
-
-print("")
-print("ZA Q")
-print(summary(cesModel("ZA", "Q")))
-
-print("")
-print("SA Q")
-print(summary(cesModel("SA", "Q")))
-
-print("")
-print("IR Q")
-print(summary(cesModel("IR", "Q")))
-
-print("")
-print("TZ Q")
-print(summary(cesModel("TZ", "Q")))
-
-print("")
-print("ZM Q")
-print(summary(cesModel("ZM", "Q")))
+# 
+# print("")
+# print("ZA Q")
+# print(summary(cesModel("ZA", "Q")))
+# 
+# print("")
+# print("SA Q")
+# print(summary(cesModel("SA", "Q")))
+# 
+# print("")
+# print("IR Q")
+# print(summary(cesModel("IR", "Q")))
+# 
+# print("")
+# print("TZ Q")
+# print(summary(cesModel("TZ", "Q")))
+# 
+# print("")
+# print("ZM Q")
+# print(summary(cesModel("ZM", "Q")))
 
@@
 
-\citet{Stern:2012ey} developed a CES model of the form
-
-\begin{equation} \label{eq:CES_model}
-  y = \left\{ (1-\gamma_E) \left[ k^{\alpha} \left( \mathrm{e}^{\lambda_L(t-t_0)} l \right)^{\beta} \right]^{\frac{\sigma-1}{\sigma}}   
-      + (\gamma_E) \left[ \mathrm{e}^{\lambda_E(t-t_0)} e \right]^{\frac{\sigma - 1}{\sigma}}   \right\}
-      ^{\frac{\sigma}{\sigma - 1}},
-\end{equation}
-
-\noindent where $e$ is any of $q$, $x$, or $u$; $\sigma$, $\gamma_E$, $\beta$, $\lambda_L$, and $\lambda_E$ are fitting parameters; $\mathrm{e}$ is the base of the natural logarithm; and the sum $\alpha + \beta$ is constrained to unity.\footnote{The CES equation in \citet{Stern:2012ey} appears as
+\citet{Stern:2012ey} developed a CES model of the form\footnote{The CES equation in \citet{Stern:2012ey} appears as
 
@@
 
-but the $1/\sigma$ exponent on the $(1-\gamma_E)$ and $\gamma_E$ terms seems erroneous due to $y(t_\mathrm{0}) \neq 1$.}
+but the $1/\sigma$ exponent on the $(1-\gamma_E)$ and $\gamma_E$ terms is erroneous due to $y_{\mathrm{t_0}} \neq 1$.}
+
+\begin{equation} \label{eq:Stern_CES_model_in_print}
+  y = \left\{ (1-\gamma_E) \left[ k^{\alpha} \left( \mathrm{e}^{\lambda_L(t-t_0)} l \right)^{\beta} \right]^{\frac{\sigma-1}{\sigma}}   
+      + (\gamma_E) \left[ \mathrm{e}^{\lambda_E(t-t_0)} e \right]^{\frac{\sigma - 1}{\sigma}}   \right\}
+      ^{\frac{\sigma}{\sigma - 1}},
+\end{equation}
+
+\noindent where $e$ is any of $q$, $x$, or $u$; $\sigma$, $\gamma_E$, $\beta$, $\lambda_L$, and $\lambda_E$ are fitting parameters; $\mathrm{e}$ is the base of the natural logarithm; and the sum $\alpha + \beta$ is constrained to unity.
+
+The R package micEconCES (***** Need reference here *****) estimates CES production functions of the form
+
+\begin{equation} \label{eq:micEconCES_model}
+  y = something.
+\end{equation}
+
+\citet{Henningsen:2011td}, in their detailed analysis of \citet{Kemfert:1998vd}, found that
+
+\begin{quote}
+\ldots the Levenberg-Marquardt and the PORT algorithms are--at least in this study--most likely to find the coefficients that give the best fit to the model, where the PORT algorithm can be used to restrict the estimates to the economically meaningful region.
+\end{quote}
 

### 2013-02-21 EconGrowth.Rnw
Now also including ZA in the CES fits.

@@
     # Furthermore, the only significant varluable is gamma = 1.0731.
-    # So, for the final fit, I'll put rho1 = 0.0 and rho = 0.0. The final R^2 = 
+    # So, for the final fit, I'll put rho1 = 0.0 and rho = 0.0. The final R^2 = 0.9983.
     rho1 = 0.0
@@
                        )
+  } else if (countryAbbrev == "ZA"){
+    # An unconstrained fit works for South Africa.  Results are sigma1 = 0.05, signalling complementarity
+    # between k and l.  sigma = 0.03, indicating complementatity between (kl) and (e).
+    modelCES <- cesEst(data=dataTable, yName=yName, xNames=xNames, tName=tName, control=control,
+                       method="LM",
+                       )
+  } else if (countryAbbrev == "SA"){
+    modelCES <- cesEst(data=dataTable, yName=yName, xNames=xNames, tName=tName, control=control,
+                       method="LM",
+                       )
   }
@@
 # print("")
-print("CN Q")
-print(summary(cesModel("CN", "Q")))
+# print("CN Q")
+# print(summary(cesModel("CN", "Q")))
 # 
@@
 # print("")
-# print("SA Q")
-# print(summary(cesModel("SA", "Q")))
+print("SA Q")
+print(summary(cesModel("SA", "Q")))
 # 

### 2013-02-22 EconGrowth.Rnw
Now including a cesPredictions function with example using US data.

@@
 <<ces functions, eval=TRUE>>=
-####################
-# Returns an nls ces model for the country and energyType specified.
-# energyType should be one of Q", "X", or "U".
-##
-cesModel <- function(countryAbbrev, energyType){
-  # Load the data that we need.
+######################################
+# Loads data and trims rows where necessary.
+# Also, replaces the name of the desired energy column with "iEToFit".
+# Returns a data.frame with the loaded data.
+##
+loadAndPrepDataForCES <- function(countryAbbrev, energyType){
   dataTable <- loadData(countryAbbrev)
@@
   dataTable <- replaceColName(dataTable, energyType, "iEToFit")
-  # Establish default guesses for sigma, gamma_E, beta, lambda_L and lambda_E.
-  start <- list(sigma=0.9, gamma_E=0.01, beta=0.7, lambda_L=0.011, lambda_E=0.018) #values for Sweden
-  # Establish bounds
-  lower = list(sigma=-Inf, gamma_E=0.0, beta=-Inf, lambda_L=-Inf, lambda_E=-Inf)
-  upper = list(sigma= Inf, gamma_E=1.0, beta= Inf, lambda_L= Inf, lambda_E= Inf)
-  # Now some country-specific values.
-  if (countryAbbrev == "US"){
-    start <- list(sigma=0.95, gamma_E=0.1, beta=0.7, lambda_L=0.015, lambda_E=0.015) #values for Sweden
-  }
-  if (countryAbbrev == "UK"){
-    start <- list(sigma=0.95, gamma_E=0.2, beta=0.7, lambda_L=0.02, lambda_E=0.02) #values for Sweden
-    lower = list(sigma=-Inf, gamma_E=0.0, beta=-Inf, lambda_L=-0.3, lambda_E=-0.3)
-    upper = list(sigma= Inf, gamma_E=1.0, beta= Inf, lambda_L= 0.3, lambda_E= 0.3)
-  }
-  if (countryAbbrev == "CN"){
-
-  }
-  # Runs a non-linear least squares fit to the data with constraints
-  # This is the version of the function from the Stern and Kander (2012) paper. However, it includes a 
-  # 1/sigma exponent on the gamma_E terms, which, I believe, is bogus.
-#   model <- iGDP ~ ((1-gamma_E)^(1.0/sigma) * ((exp(lambda_L*iYear))^beta 
-#                                                   * iLabor^beta
-#                                                   * iCapStk^(1-beta) )^((sigma-1.0)/sigma) 
-#                   + gamma_E^(1.0/sigma)*(exp(lambda_E*iYear) * iEToFit)^((sigma-1.0)/sigma))^(sigma/(sigma-1.0))
-
-  # This is the corrected version of the Stern and Kander (2012) paper.
-#   model <- iGDP ~ ((1-gamma_E) * ((exp(lambda_L*iYear))^beta * iLabor^beta * iCapStk^(1-beta) )^((sigma-1.0)/sigma) 
-#                   + gamma_E * (exp(lambda_E*iYear) * iEToFit)^((sigma-1.0)/sigma))^(sigma/(sigma-1.0))
-
-  # This is the nls fit to the CES model  
-#   modelCES <- nls(formula=model, data=dataTable, start=start,
-#                   control=nls.control(maxiter=10000, tol=1e-05, minFactor=1/1024, 
-#                                       printEval=TRUE, warnOnly=TRUE),
-#                   algorithm = "port",
-#                   lower = lower,
-#                   upper = upper,
-#                   trace=TRUE
-#                   )
-
-  # An attempt with nlmrt function nlxb. Doesn't provide many good results.
-#   modelCES <- nlxb(model,
-#                    data=dataTable,
-#                    start=list(sigma=sigmaGuess, gamma_E=gamma_EGuess, beta=betaGuess, 
-#                               lambda_L=lambda_LGuess, lambda_E=lambda_EGuess),
-#                    trace=TRUE
-#                   )
+  return(dataTable)
+}
+
+####################
+# Returns an nls ces model for the country and energyType specified.
+# energyType should be one of Q", "X", or "U".
+##
+cesModel <- function(countryAbbrev, energyType){
+  # Load the data that we need.
+  dataTable <- loadAndPrepDataForCES(countryAbbrev, energyType)
+#   # Establish default guesses for sigma, gamma_E, beta, lambda_L and lambda_E.
+#   start <- list(sigma=0.9, gamma_E=0.01, beta=0.7, lambda_L=0.011, lambda_E=0.018) #values for Sweden
+#   # Establish bounds
+#   lower = list(sigma=-Inf, gamma_E=0.0, beta=-Inf, lambda_L=-Inf, lambda_E=-Inf)
+#   upper = list(sigma= Inf, gamma_E=1.0, beta= Inf, lambda_L= Inf, lambda_E= Inf)
+#   # Now some country-specific values.
+#   if (countryAbbrev == "US"){
+#     start <- list(sigma=0.95, gamma_E=0.1, beta=0.7, lambda_L=0.015, lambda_E=0.015) #values for Sweden
+#   }
+#   if (countryAbbrev == "UK"){
+#     start <- list(sigma=0.95, gamma_E=0.2, beta=0.7, lambda_L=0.02, lambda_E=0.02) #values for Sweden
+#     lower = list(sigma=-Inf, gamma_E=0.0, beta=-Inf, lambda_L=-0.3, lambda_E=-0.3)
+#     upper = list(sigma= Inf, gamma_E=1.0, beta= Inf, lambda_L= 0.3, lambda_E= 0.3)
+#   }
+#   if (countryAbbrev == "CN"){
+#     
+#   }
+#   # Runs a non-linear least squares fit to the data with constraints
+#   # This is the version of the function from the Stern and Kander (2012) paper. However, it includes a 
+#   # 1/sigma exponent on the gamma_E terms, which, I believe, is bogus.
+# #   model <- iGDP ~ ((1-gamma_E)^(1.0/sigma) * ((exp(lambda_L*iYear))^beta 
+# #                                                   * iLabor^beta
+# #                                                   * iCapStk^(1-beta) )^((sigma-1.0)/sigma) 
+# #                   + gamma_E^(1.0/sigma)*(exp(lambda_E*iYear) * iEToFit)^((sigma-1.0)/sigma))^(sigma/(sigma-1.0))
+#   
+#   # This is the corrected version of the Stern and Kander (2012) paper.
+# #   model <- iGDP ~ ((1-gamma_E) * ((exp(lambda_L*iYear))^beta * iLabor^beta * iCapStk^(1-beta) )^((sigma-1.0)/sigma) 
+# #                   + gamma_E * (exp(lambda_E*iYear) * iEToFit)^((sigma-1.0)/sigma))^(sigma/(sigma-1.0))
+#   
+#   # This is the nls fit to the CES model  
+# #   modelCES <- nls(formula=model, data=dataTable, start=start,
+# #                   control=nls.control(maxiter=10000, tol=1e-05, minFactor=1/1024, 
+# #                                       printEval=TRUE, warnOnly=TRUE),
+# #                   algorithm = "port",
+# #                   lower = lower,
+# #                   upper = upper,
+# #                   trace=TRUE
+# #                   )
+# 
+#   # An attempt with nlmrt function nlxb. Doesn't provide many good results.
+# #   modelCES <- nlxb(model,
+# #                    data=dataTable,
+# #                    start=list(sigma=sigmaGuess, gamma_E=gamma_EGuess, beta=betaGuess, 
+# #                               lambda_L=lambda_LGuess, lambda_E=lambda_EGuess),
+# #                    trace=TRUE
+# #                   )
 
@@
   } else if (countryAbbrev == "SA"){
+    # An unconstrained fit gives rho = -6.33, rho1 = 9.36 (sigma1 = 0.0965) and R^2 = 0.9892.  
+    # This result is not economically meaningful.
+    # Constraining rho = 0 gives rho1 = -582, again not economically meaningful.
+    # So, do a grid search over meaningful regions to see what is best.
+    # The result (to with +/- 0.1) is rho = 0.0 and rho1 = 5.7, with R^2 = 0.9885.
+    # However, neither the the rho or nor the sigma values are statistically significant.
+    rho1 = 5.7
+    rho = 0.0
     modelCES <- cesEst(data=dataTable, yName=yName, xNames=xNames, tName=tName, control=control,
                        method="LM",
-                       )
-  }
-
+                       rho1 = rho1,
+                       rho = rho
+                       )
+  } else if (countryAbbrev == "IR"){
+    # Iran works with an unconstrained fit.
+    modelCES <- cesEst(data=dataTable, yName=yName, xNames=xNames, tName=tName, control=control,
+                       method="LM",
+                       )
+  } else if (countryAbbrev == "TZ"){
+    # Using the PORT algorithm yields convergence and R^2 = 0.9974 with economically menaingful results.
+    # However, none of the rho or sigma values are statistically significant.
+    modelCES <- cesEst(data=dataTable, yName=yName, xNames=xNames, tName=tName, control=control,
+                       method="PORT",
+                       )
+  } else if (countryAbbrev == "ZM"){
+    # ZM works with the PORT algorithm, but not the LM algorithm.
+    modelCES <- cesEst(data=dataTable, yName=yName, xNames=xNames, tName=tName, control=control,
+                       method="PORT",
+                       rho=0.0
+                       )
+  }
   return(modelCES)
@@
 # print("")
-print("SA Q")
-print(summary(cesModel("SA", "Q")))
+# print("SA Q")
+# print(summary(cesModel("SA", "Q")))
 # 
@@
 # print(summary(cesModel("ZM", "Q")))
+
+#########################
+# Takes the CES fitted models and creates per-country predictions for them.
+# Returns a data.frame with the predictions.
+##
+cesPredictions <- function(countryAbbrev, energyType){
+  xNames = c("iCapStk", "iLabor", "iEToFit")
+  tName = "iYear"
+  dataTable <- loadAndPrepDataForCES(countryAbbrev, energyType)
+  # Can't make predictions for any of CN, ZA, SA, IR, TZ, or ZM if we're interested in U
+  if (!(haveDataSF(countryAbbrev, energyType))){
+    # If we don't have data for this combination of countryAbbrev and energyType, 
+    # return a column of NAs if the above conditions have been met.
+    nRows <- 21 # All of these countries need 21 rows.
+    df <- as.data.frame(matrix(NA, ncol = 1, nrow = nRows))
+    colnames(df) <- "pred"
+    return(df)
+  }
+  model <- cesModel(countryAbbrev, energyType)
+  print(model)
+  pred <- cesCalc(xNames=xNames, data=dataTable, coef=coef(model), tName="iYear", nested=TRUE)
+  df <- data.frame(pred)
+  # Pad with rows as necessary
+  df <- padRows(countryAbbrev, df)
+  return(df)
+}
+
+print(cesPredictions("US", "Q"))
 

### 2013-02-22 EconGrowth.Rnw
Now creating a CES comparison graph.

@@
 <<ces functions, eval=TRUE>>=
+# Set some common names for CES variables.
+xNames = c("iCapStk", "iLabor", "iEToFit")
+tName = "iYear"
+yName = "iGDP"
+
 ######################################
@@
   dataTable <- loadAndPrepDataForCES(countryAbbrev, energyType)
-#   # Establish default guesses for sigma, gamma_E, beta, lambda_L and lambda_E.
-#   start <- list(sigma=0.9, gamma_E=0.01, beta=0.7, lambda_L=0.011, lambda_E=0.018) #values for Sweden
-#   # Establish bounds
-#   lower = list(sigma=-Inf, gamma_E=0.0, beta=-Inf, lambda_L=-Inf, lambda_E=-Inf)
-#   upper = list(sigma= Inf, gamma_E=1.0, beta= Inf, lambda_L= Inf, lambda_E= Inf)
-#   # Now some country-specific values.
-#   if (countryAbbrev == "US"){
-#     start <- list(sigma=0.95, gamma_E=0.1, beta=0.7, lambda_L=0.015, lambda_E=0.015) #values for Sweden
-#   }
-#   if (countryAbbrev == "UK"){
-#     start <- list(sigma=0.95, gamma_E=0.2, beta=0.7, lambda_L=0.02, lambda_E=0.02) #values for Sweden
-#     lower = list(sigma=-Inf, gamma_E=0.0, beta=-Inf, lambda_L=-0.3, lambda_E=-0.3)
-#     upper = list(sigma= Inf, gamma_E=1.0, beta= Inf, lambda_L= 0.3, lambda_E= 0.3)
-#   }
-#   if (countryAbbrev == "CN"){
-#     
-#   }
-#   # Runs a non-linear least squares fit to the data with constraints
-#   # This is the version of the function from the Stern and Kander (2012) paper. However, it includes a 
-#   # 1/sigma exponent on the gamma_E terms, which, I believe, is bogus.
-# #   model <- iGDP ~ ((1-gamma_E)^(1.0/sigma) * ((exp(lambda_L*iYear))^beta 
-# #                                                   * iLabor^beta
-# #                                                   * iCapStk^(1-beta) )^((sigma-1.0)/sigma) 
-# #                   + gamma_E^(1.0/sigma)*(exp(lambda_E*iYear) * iEToFit)^((sigma-1.0)/sigma))^(sigma/(sigma-1.0))
-#   
-#   # This is the corrected version of the Stern and Kander (2012) paper.
-# #   model <- iGDP ~ ((1-gamma_E) * ((exp(lambda_L*iYear))^beta * iLabor^beta * iCapStk^(1-beta) )^((sigma-1.0)/sigma) 
-# #                   + gamma_E * (exp(lambda_E*iYear) * iEToFit)^((sigma-1.0)/sigma))^(sigma/(sigma-1.0))
-#   
-#   # This is the nls fit to the CES model  
-# #   modelCES <- nls(formula=model, data=dataTable, start=start,
-# #                   control=nls.control(maxiter=10000, tol=1e-05, minFactor=1/1024, 
-# #                                       printEval=TRUE, warnOnly=TRUE),
-# #                   algorithm = "port",
-# #                   lower = lower,
-# #                   upper = upper,
-# #                   trace=TRUE
-# #                   )
-# 
-#   # An attempt with nlmrt function nlxb. Doesn't provide many good results.
-# #   modelCES <- nlxb(model,
-# #                    data=dataTable,
-# #                    start=list(sigma=sigmaGuess, gamma_E=gamma_EGuess, beta=betaGuess, 
-# #                               lambda_L=lambda_LGuess, lambda_E=lambda_EGuess),
-# #                    trace=TRUE
-# #                   )
-
-  # Try a fit to a nested CES function with the micEconCES package.  
-  # This approach is based on a white paper by Henningsen and Henningsen 
-  # http://okonomi.foi.dk/workingpapers/WPpdf/WP2011/WP_2011_9_econometric_estimation_CES.pdf.
-  # Set a few of the variables up front
-  yName = "iGDP"
-  xNames = c("iCapStk", "iLabor", "iEToFit")
-  tName = "iYear"
   control=nls.lm.control(maxiter=1000, maxfev=2000)
@@
 }
-# print("US U")
-# print(summary(cesModel("US", "U")))
-# 
-# print("")
-# print("UK U")
-# print(summary(cesModel("UK", "U")))
-# 
-# print("")
-# print("JP U")
-# print(summary(cesModel("JP", "U")))
-
-# print("")
-# print("CN Q")
-# print(summary(cesModel("CN", "Q")))
-# 
-# print("")
-# print("ZA Q")
-# print(summary(cesModel("ZA", "Q")))
-# 
-# print("")
-# print("SA Q")
-# print(summary(cesModel("SA", "Q")))
-# 
-# print("")
-# print("IR Q")
-# print(summary(cesModel("IR", "Q")))
-# 
-# print("")
-# print("TZ Q")
-# print(summary(cesModel("TZ", "Q")))
-# 
-# print("")
-# print("ZM Q")
-# print(summary(cesModel("ZM", "Q")))
 
@@
 cesPredictions <- function(countryAbbrev, energyType){
-  xNames = c("iCapStk", "iLabor", "iEToFit")
-  tName = "iYear"
   dataTable <- loadAndPrepDataForCES(countryAbbrev, energyType)
@@
   model <- cesModel(countryAbbrev, energyType)
-  print(model)
   pred <- cesCalc(xNames=xNames, data=dataTable, coef=coef(model), tName="iYear", nested=TRUE)
@@
 
-print(cesPredictions("US", "Q"))
+#########################
+# Takes the CES fitted models and creates a single column of predicted GDP values
+# that corresponds, row for row, with the AllData.txt file.
+##
+cesPredictionsColumn <- function(energyType){
+  out <- do.call("rbind", lapply(countryAbbrevs, cesPredictions, energyType=energyType))
+  colnames(out) <- c(paste("predGDP", energyType, sep=""))
+  return(out)
+}
+
+##############################
+# Creates a graph that plots predicted GDP as lines, one for each single factor, and historical GDP 
+# data as open circles.
+##
+createCESLatticeGraph <- function(){
+  dataTable <- loadData("All") #Grab the raw data
+  predictionsQ <- cesPredictionsColumn("Q") #Predictions from CES with Q
+  predictionsX <- cesPredictionsColumn("X") #Predictions from CES with X
+  predictionsU <- cesPredictionsColumn("U") #Predictions from CES with U
+  #Now add the predictions columns to the data.
+  dataTable <- cbind(dataTable, predictionsQ, predictionsX, predictionsU) 
+  graphType <- "b" #b is for both line and symbol
+  lineTypes <- c(0, 2, 4, 1) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
+  lineWidths <- c(0, 1, 1, 1) #line widths. 0 means no line.
+  colors <- c("black", "red", "blue", "darkorange") #line and symbol colors
+  symbols <- c(1, NA, NA, NA)  #NA gives no symbol.
+  graph <- xyplot(iGDP+predGDPQ+predGDPX+predGDPU ~ Year | Country, data=dataTable,
+                  type=graphType,
+                  index.cond=list(countryOrderForGraphs), #orders the panels.
+                  layout=ninePanelLayoutSpec, #indicates a 3x3 arrangement of panels.
+                  strip = strip.custom(factor.levels=countryNamesAlph, bg="white"), #Sets strip parameters
+                  as.table=TRUE, #indexing of panels starts in upper left and goes across rows.
+                  lty = lineTypes, lwd = lineWidths, col = colors, #Controls line parameters
+                  pch = symbols, col.symbol = colors, #Controls symbol parameters
+                  key=list(text=list(c("Actual", "With $q$", "With $x$", "With $u$")),
+                           type=graphType,
+                           cex=keyTextSize, #controls size of text in the key
+                           lines=list(lty=lineTypes, lwd=lineWidths), #controls line types
+                           pch=symbols, col=colors, #controls symbol (plot characters) types
+                           columns=keyColumns, x=keyXLoc, y=keyYLoc), #controls columns and position of the key
+                  scales=list(cex=scaleTextSize, #controls text size on scales.
+                              tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
+                              y=list(relation="free", #allows each axis to be different
+                                     at=c(1,2,3,4,5,6,7,8,9,10) #tick mark locations
+                                     )
+                              ), 
+                  ylim=list(c(1,8), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3)),
+                  xlab="", ylab="Indexed GDP (1980=1 or 1991=1)") #axis labels
+  return(graph)
+}
 
@@
   dataCES <- rbind(upperCES, estCES, lowerCES)
-  print(dataCES)
   return(dataCES)
@@
 
-<<CESq analysisQ, eval=FALSE>>=
-countryName <- "US"
-energyType <- "Q"
-tableCESq <- cesTable(countryName, energyType)
-
-#CESqTables <- lapply(countryAbbrevs, cesTable, energyType="Q")
-@
-
-<<CESq Results, results='asis', eval=FALSE>>=
-print(tableCESq, caption.placement="top")
-
-#print(CESqTables[["US"]], caption.placement="top")
-#print(CESqTables[["ZA"]], caption.placement="top")
-@
-
 \subsection{CES with $X$}
@@
 \subsection{CES with $U$}
+
+\subsection{CES comparisons}
+
+Figure \ref{fig:CES_GDP_Lattice_Graph} compares CES model predictions to historical data.
+
+<<CES_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="CES results.", eval=TRUE>>=
+createCESLatticeGraph()
+@
 
@@
 
-Figure \ref{fig:LINEX_GDP_Lattice_Graph} compares LINEX model predictions with historical data.
+Figure \ref{fig:LINEX_GDP_Lattice_Graph} compares LINEX model predictions to historical data.
 

### 2013-02-22 EconGrowth.Rnw
Added a LaTeX equation for the CES production function.

@@
       \begin{itemize}
-      \item GDP comparison graph
+      \item \st{GDP comparison graph}
       \item parameter graphs for each country
@@
 \item Heun: adjust y axis limits on $a_0$ and $c_t$ parameter graphs for the LINEX model AFTER we finish debugging the LINEX models.
+\item de Wit: provide funding acknowledgement, if necessary.
+\item de Wit: review, critique, and contextualize.
 \item \st{Heun: Ask Martin if he can supply an ``Economics'' affiliation. Will probably make a stronger paper.}
@@
 \item \st{Heun: Add $u$ predictions for Cobb-Douglas}
-\item \st{Heun: move tables to an appendix at the end.}
+\item \st{Heun: Move tables to an appendix at the end.}
 \item \st{Heun: Add acknowledgements (Dad, Pruim)}
@@
       \begin{itemize}
-      \item \st{correct sizes for parameter graphs for each country}
-      \item \st{parameter graphs ($\lambda$ and $m$) for each country}
-      \item \st{parameter tables for each country in the appendix}
+      \item \st{Correct sizes for parameter graphs for each country}
+      \item \st{Parameter graphs ($\lambda$ and $m$) for each country}
+      \item \st{Parameter tables for each country in the appendix}
       \item \st{GDP comparison graph}
@@
       \begin{itemize}
-      \item \st{parameter graphs for each country}
-      \item \st{parameter tables for each country in the appendix}
+      \item \st{Parameter graphs for each country}
+      \item \st{Parameter tables for each country in the appendix}
       \item \st{AIC rows in the AIC table}
@@
   } else {
-#     print("")
-#     print(paste("In cobbDouglasData:", countryAbbrev, energyType))
-#     print("summaryCD:")
-#     print(paste("    df:", summaryCD$df))
-#     print(paste("    sigma:", summaryCD$sigma))
-#     print("    coeffs: ")
-#     print(summaryCD$coefficients)
-#     print("ciCD:")
-#     print(ciCD)
     #Cobb-Douglas with energy
@@
     b <- as.numeric(coef(modelCD)["b"])
-#     print(paste("a =", a))
-#     print(paste("b =", b))
     lambda <- as.numeric(coef(modelCD)["lambda"])
@@
     beta.est <- deltaMethod(modelCD, "b-a") # Reports results for beta, because beta = b - a.
-#     print("beta.est = b-a")
-#     print(beta.est)
     gamma.est <- deltaMethod(modelCD, "1-b") # Reports results for gamma, because gamma = 1 - b.
-#     print("gamma.est = 1 - b")
-#     print(gamma.est)
     # Now calculate confidence intervals.
-#     print(paste("dofCD =", dofCD))
-#     print(paste("tvalCD =", tvalCD))
     betaCICD <- with(beta.est, Estimate + c(-1.0, 1.0) * tvalCD * SE) # Gives the confidence interval on beta.
-#     print("betaCICD:")
-#     print(betaCICD)
     gammaCICD <- with(gamma.est, Estimate + c(-1.0, 1.0) * tvalCD * SE) # Gives the confidence interval on gamma.
-#     print("gammaCICD:")
-#     print(gammaCICD)
     # Combine all estimates and their confidence intervals into data frames with intelligent row names
@@
   } else {
-#     print("In not missing energyType")
-#     print(dataCD)
     gammaRow <- data.frame(country = countryName, 
@@
                            upperCI = dataCD["+95% CI", "gamma"])
-#     print(gammaRow)
     table <- rbind(lambdaRow, alphaRow, betaRow, gammaRow)
@@
 createCDParamsGraph <- function(energyType){
-
   if (missing(energyType)){
@@
 }
-
 @
@@
 ####################
-# Returns an nls ces model for the country and energyType specified.
+# Returns a cesEst model for the country and energyType specified.
 # energyType should be one of Q", "X", or "U".
@@
   model <- cesModel(countryAbbrev, energyType)
-  pred <- cesCalc(xNames=xNames, data=dataTable, coef=coef(model), tName="iYear", nested=TRUE)
+  pred <- fitted(model)
   df <- data.frame(pred)
@@
 
-The R package micEconCES (***** Need reference here *****) estimates CES production functions of the form
+The \texttt{R} \citep{R} package \texttt{micEconCES} \citep{Henningsen:2011td} estimates CES production functions of the form (among others)
 
 \begin{equation} \label{eq:micEconCES_model}
-  y = something.
+  y = \gamma \mathrm{e}^{\lambda(t-t_0)}  
+      \left\{\delta \left[\delta_1 k^{-\rho_1} + (1-\delta_1)l^{-\rho_1} \right] + (1-\delta) e^{-\rho} \right\}
+                                                                                                        ^{-1/\rho}.
 \end{equation}
@@
 \begin{quote}
-\ldots the Levenberg-Marquardt and the PORT algorithms are--at least in this study--most likely to find the coefficients that give the best fit to the model, where the PORT algorithm can be used to restrict the estimates to the economically meaningful region.
+\ldots the Levenberg-Marquardt and the PORT algorithms are---at least in this study---most likely to find the coefficients that give the best fit to the model, where the PORT algorithm can be used to restrict the estimates to the economically meaningful region.
 \end{quote}
@@
 
-<<CES_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="CES results.", eval=TRUE>>=
+<<CES_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="CES results.">>=
 createCESLatticeGraph()
@@
 
-Funding for Caleb Reese and Lucas Timmer was graciously supplied by the Jack and Lois Kuipers Applied Mathematics Endowment and the Calvin College Alumni Association.
+Funding for Caleb Reese and Lucas Timmer was generously supplied by the Jack and Lois Kuipers Applied Mathematics Endowment and the Calvin College Alumni Association.
+Funding for Martin de Wit was provided by *******.
 The authors thank Randall Pruim (Calvin College) and Loren L.
 Heun (Western Michigan University) for their insightful comments on and invaluable assistance with the statistical analyses presented herein.
-
 %% The Appendices part is started with the command \appendix;

### 2013-02-23 EconGrowth.Rnw
Added some to-do items.
Now including code to print CES parameter tables in the appendix. Not quite working yet, unfortunately. The values of the sigma parameters are messed up.

@@
       \item \st{GDP comparison graph}
+      \item Convert $\rho$ variables in the \citet{Henningsen:2011td} CES production function to $\sigma$ variables.
       \item parameter graphs for each country
@@
       \end{itemize}
-\item Heun: Deal with missing covariance numbers when columns have unequal length.
+\item Heun: Deal with missing covariance numbers when columns have unequal length. Use the \texttt{subset} command.
 \item Heun: Eliminate blanks in the coefficient tables for the 95\% CIs in the Cobb-Douglas with energy rows. Asked Pruim about this via email on 4 Feb 2013 but have not heard a response.
@@
 
-cesData <- function(countryName, energyType){
-  energyColumnName <- paste("i", energyType, sep="")
-  # Load the data that we need.
-  dataTable <- loadData(countryName)
-
-  # Establish guess values for phi beta, zeta, lambda_L and lambda_E.
-  phiGuess <- -20
-  betaGuess <- 0.5 # a typical value for beta (exponent on labor)
-  zetaGuess <- 0.0004 # a small value
-  lambda_LGuess <- 0.007 #assuming no technical progress on the labor-capital portion of the function
-  lambda_EGuess <- 0.008 #assuming no technical progress on the energy portion of the function
-
-  # Runs a non-linear least squares fit to the data with constraints
-  modelCES <- nls(iGDP ~ ((1-zeta) * (exp(lambda_L*iYear) * iCapStk^(1-beta) * iLabor^beta)^phi 
-                           + zeta*(exp(lambda_E*iYear) * iQ)^phi)^(1/phi), 
-                   algorithm = "port",
-                   control = nls.control(maxiter = 500, tol = 1e-06, minFactor = 1/1024, 
-                                         printEval = FALSE, warnOnly = FALSE),
-                   start = list(phi=phiGuess, beta=betaGuess, zeta=zetaGuess, lambda_L=lambda_LGuess, 
-                                lambda_E=lambda_EGuess),
-                   lower = list(phi=-Inf, beta=0, zeta=0, lambda_L=-Inf, lambda_E=-Inf),
-                   upper = list(phi=0, beta=1, zeta=1, lambda_L=Inf, lambda_E=Inf),
-                   data=dataTable)
-
-  aicCES <- AIC(modelCES, k=2) # Checks validity of the model. AIC stands for Akaike's Information Criterion
-  print(aicCES)
-
-  # Gives the nls summary table
-  summaryCES <- summary(modelCES) # Gives the nls summary table
-  print(summaryCES)
-
-  # Provides confidence intervals on phi, beta, zeta, lambda_L, and lambda_E. But, we need the CI on alpha.
-  ciCES <- confint(modelCES, level = ciLevel)
-  print(ciCES)
-
-  # Get the estimate for alpha
-  beta <- as.numeric(coef(modelCES)["beta"])
-  alpha <- 1.0 - beta
-  alpha.est <- deltaMethod(modelCES, "1 - beta") # Estimates alpha and its standard error (SE).
-  print(alpha.est)
-
-  # Now calculate a confidence interval on alpha
-  dofCES <- summaryCES$df[2]
-  print(dofCES) # Gives the degrees of freedom for the model.
-  tvalCES <- qt(ciHalfLevel, df = dofCES); tvalCES
-  # Get confidence intervals for each parameter in the model
-  alphaCICES <- with(alpha.est, Estimate + c(-1.0, 1.0) * tvalCES * SE) # CI on alpha.
-  print(alphaCICES)
-
-  # Assemble the data into data frames for the table.
-  estCES <- data.frame(phi = coef(modelCES)["phi"], alpha = alpha, 
-                       beta = coef(modelCES)["beta"], zeta = coef(modelCES)["zeta"], 
-                       lambda_L = coef(modelCES)["lambda_L"], lambda_E = coef(modelCES)["lambda_E"])
-  row.names(estCES) <- paste("CES with ", energyType, sep="")
+#################################################
+# Calculates parameter estimates and confidence intervals
+# for the CES production function given a country and an energyType.
+#
+# countryAbbrev is a string containing the 2-letter abbreviation for the country, e.g. "US" or "CN"
+# energyType is a string, one of "Q", "X", or "U"
+#
+# returns a data.frame of data for the LINEX model.
+# First row is the +95% CI on all parameters
+# Second row contains the parameter estimates
+# Third row is the -95% CI on all parameters
+# Each column has names: gamma, lambda, delta_1, delta, rho_1, rho
+##
+cesData <- function(countryAbbrev, energyType){
+  #First, check to see if we want useful work (U) AND one of the countries for which we don't have data.
+  if (!haveDataCD(countryAbbrev, energyType)){
+    #Return a column of NAs if the above conditions have been met.
+    nRows <- 3 # +95% CI, CDe, and -95% CI.
+    nCols <- 6 # gamma, lambda, delta_1, delta, sigma_1, and sigma
+    df <- as.data.frame(matrix(NA, ncol = nCols, nrow = nRows))
+    colnames(df) <- c("gamma", "lambda", "delta_1", "delta", "sigma_1", "sigma")
+    rownames(df) <- c("+95% CI", "CES", "-95% CI")
+    return(df)
+  }
+  # We have a combination of country and energy type for which we have data.
+  modelCES <- cesModel(countryAbbrev, energyType)
+  summaryCES <- summary(modelCES) # Gives a summary table.
+#print(summaryCES)
+  # Calculate the degrees of freedom as N_obs - N_params
+  dofCES <- nrow(loadAndPrepDataForCES(countryAbbrev, energyType)) - 6 # Gives the degrees of freedom for the model.
+#print(dofCES)
+  tvalCES <- qt(ciHalfLevel, df = dofCES)
+#print(tvalCES)
+  # Calculate confidence intervals for the parameters of the model
+  ciCES <- confint(modelCES, level = ciLevel)  # Calculates confidence intervals for the CES model.
+#print(ciCES)
+  # Get confidence intervals for the elasticities of substitution
+  sigma_1.est <- deltaMethod(modelCES, "1.0 / (1.0 + rho_1)") # Estimates sigma_1 and its standard error (SE).
+#print(sigma_1.est)
+  sigma_1CI <- with(sigma_1.est, Estimate + c(-1.0, 1.0) * tvalCES * SE)
+#print("sigma_1CI:")
+#print(sigma_1CI)
+  sigma.est <- deltaMethod(modelCES, "1.0 / (1.0 + rho)") # Estimates sigma and its standard error (SE)
+#print(sigma.est)
+  sigmaCI <- with(sigma.est, Estimate + c(-1.0, 1.0) * tvalCES * SE)
+#print("sigmaCI:")
+#print(sigmaCI)
+  # Report results with SE
+  gamma <- coef(modelCES)["gamma"] #as.numeric(coef(modelCES)["gamma"])
+  lambda <- coef(modelCES)["lambda"] #as.numeric(coef(modelCES)["lambda"])
+  delta_1 <- coef(modelCES)["delta_1"]
+  delta <- coef(modelCES)["delta"]
+  sigma_1 <- sigma_1.est$Estimate
+  sigma <- sigma.est$Estimate
+  # Combine all estimates and their confidence intervals into data frames with intelligent row names
+  estCES <- data.frame(gamma=gamma, lambda=lambda, delta_1=delta_1, delta=delta, sigma_1=sigma_1, sigma=sigma)
+  row.names(estCES) <- "CES"
 #print(estCES)
   # The [1] subscripts pick off the lower confidence interval
-  lowerCES <- data.frame(phi = ciCES["phi","2.5%"], alpha = alphaCICES[1], 
-                         beta = ciCES["beta", "2.5%"], zeta = ciCES["zeta", "2.5%"],
-                         lambda_L = ciCES["lambda_L", "2.5%"], lambda_E = ciCES["lambda_E", "2.5%"])
-  row.names(lowerCES) <- "- 95% CI"
-  # The [2] subscripts pick off the lower confidence interval
-  upperCES <- data.frame(phi = ciCES["phi","97.5%"], alpha = alphaCICES[2], 
-                         beta = ciCES["beta", "97.5%"], zeta = ciCES["zeta", "97.5%"],
-                         lambda_L = ciCES["lambda_L", "97.5%"], lambda_E = ciCES["lambda_E", "97.5%"])
-  row.names(upperCES) <- "+ 95% CI"
-
-  # Now create the data for a table.
+#print(ciCES["gamma","2.5 %"])
+  lowerCES <- data.frame(gamma=ciCES["gamma","2.5 %"], lambda=ciCES["lambda", "2.5 %"],
+                         delta_1=ciCES["delta_1", "2.5 %"], delta=ciCES["delta", "2.5 %"],
+                         sigma_1=sigma_1CI[1], sigma=sigmaCI[1])
+  row.names(lowerCES) <- "-95% CI"
+#print(lowerCES)
+  # The [2] subscripts pick off the upper confidence interval
+  upperCES <- data.frame(gamma=ciCES["gamma","97.5 %"], lambda=ciCES["lambda", "97.5 %"],
+                         delta_1=ciCES["delta_1", "97.5 %"], delta=ciCES["delta", "97.5 %"],
+                         sigma_1=sigma_1CI[2], sigma=sigmaCI[2])
+  row.names(upperCES) <- "+95% CI"
+#print(upperCES)
+  # Now create the data for a table and return it
   dataCES <- rbind(upperCES, estCES, lowerCES)
+#print("dataCES")
+#print(dataCES)
   return(dataCES)
@@
 
-####################################
-# Creates a LaTeX printable table from the CES data. This function first calls cesData.
+############
+# Creates a row for the CES parameters table for the given country (2-letter code) and energyType (Q, X, or U)
+##
+cesCountryRow <- function(countryAbbrev, energyType){
+  dataCES <- cesData(countryAbbrev, energyType)
+  out <- cbind(dataCES["-95% CI", "gamma"], dataCES["CES", "gamma"], dataCES["+95% CI", "gamma"],
+               dataCES["-95% CI", "lambda"], dataCES["CES", "lambda"], dataCES["+95% CI", "lambda"],
+               dataCES["-95% CI", "delta_1"], dataCES["CES", "delta_1"], dataCES["+95% CI", "delta_1"],
+               dataCES["-95% CI", "delta"], dataCES["CES", "delta"], dataCES["+95% CI", "delta"],
+               dataCES["-95% CI", "sigma_1"], dataCES["CES", "sigma_1"], dataCES["+95% CI", "sigma_1"],
+               dataCES["-95% CI", "sigma"], dataCES["CES", "sigma"], dataCES["+95% CI", "sigma"]
+               )
+  return(out)
+}
+
+###########################################
+# Creates a number of rows in a data.frame that contain information 
+# about the coefficients of a CES model for countryName and energyType
+# Each parameter has its own row with confidence intervals.
+# The country name is in a column. Which parameter is involved is
+# also in a column.
 # 
-# countryName is a string containint the 2-letter abbreviation for the country, e.g. "US" or "CN"
-# energyType is a string to be used in table captions reprsenting the type of energy. Typically, "Q", "X", or "U"
-#
-# returns a printable LaTeX table from xtable.
-##
-cesTable <- function(countryName, energyType){
-  dataCESe <- cesData(countryName, energyType)
-  tableCESq <- xtable(dataCESe, caption=paste(countryName, ", 1980-2011.", sep=""), digit = c(4, 1, 2, 2, 6, 5, 5))
+# The return type is a data.frame.
+##
+cesCountryRowsForParamsGraph <- function(countryName, energyType){
+  #Create six rows, one for each parameter. Each row is a data.frame so that it is plottable!
+  dataCES <- cesData(countryName, energyType)
+  gammaRow <- data.frame(country = countryName, 
+                          parameter = "gamma", 
+                          lowerCI = dataCES["-95% CI", "gamma"], 
+                          value = dataCES["CES", "gamma"], 
+                          upperCI = dataCES["+95% CI", "gamma"])
+  lambdaRow <- data.frame(country = countryName, 
+                         parameter = "lambda",
+                         lowerCI = dataCES["-95% CI", "lambda"],
+                         value = dataCES["CES", "lambda"],  
+                         upperCI = dataCES["+95% CI", "lambda"])
+  delta_1Row <- data.frame(country = countryName, 
+                         parameter = "delta_1",
+                         lowerCI = dataCES["-95% CI", "delta_1"],
+                         value = dataCES["CES", "delta_1"],  
+                         upperCI = dataCES["+95% CI", "delta_1"])
+  deltaRow <- data.frame(country = countryName, 
+                         parameter = "delta",
+                         lowerCI = dataCES["-95% CI", "delta"],
+                         value = dataCES["CES", "delta"],  
+                         upperCI = dataCES["+95% CI", "delta"])
+  sigma_1Row <- data.frame(country = countryName, 
+                         parameter = "sigma_1",
+                         lowerCI = dataCES["-95% CI", "sigma_1"],
+                         value = dataCES["CES", "sigma_1"],  
+                         upperCI = dataCES["+95% CI", "sigma_1"])
+  sigmaRow <- data.frame(country = countryName, 
+                         parameter = "sigma",
+                         lowerCI = dataCES["-95% CI", "sigma"],
+                         value = dataCES["CES", "sigma"],  
+                         upperCI = dataCES["+95% CI", "sigma"])
+  table <- rbind(gammaRow, lambdaRow, delta_1Row, deltaRow, sigma_1Row, sigmaRow)
+  return(table)
+}
+
+############################
+# Aggregates the CES results into a big data table for the given energyType.
+##
+cesParamsTable <- function(energyType){
+  #Do rbind on the results of creating a row in the table for every country abbreviation that we know.
+  dataCES <- do.call("rbind", lapply(countryAbbrevs, cesCountryRow, energyType=energyType))
+  colnames(dataCES) <- c(" ", "$\\gamma$",    " ", 
+                         " ", "$\\lambda$",   " ",
+                         " ", "$\\delta_1$",  " ",
+                         " ", "$\\delta$",    " ",
+                         " ", "$\\sigma_1$",  " ",
+                         " ", "$\\sigma$",    " ")
+  rownames(dataCES) <- countryAbbrevs
+  tableCES <- xtable(dataCES, 
+                    caption=paste("CES model (with $", tolower(energyType), "$) parameters for 1980-2011 (US, UK, JP), 1991-2010 (CN and ZA), and 1991-2011 (SA, IR, TZ, and ZM).
+(Parameter estimates beneath symbol.
+95\\% confidence interval bounds to left and right.)", sep=""),
+                    label=paste("tab:CES_Parameters_With_", energyType, sep=""),
+                    digits = c(1, 2,2,2, 2,2,2, 2,2,2, 2,2,2, 2,2,2, 2,2,2),
+                    align = "r|ccc|ccc|ccc|ccc|ccc|ccc") #Sets alignment of the numbers in the columns
+  return(tableCES)
+}
+
+############################
+# Prints a table with parameters from a CES model for the given energyType. 
+##
+printCESParamsTable <- function(energyType){
+  print(cesParamsTable(energyType), 
+    caption.placement="top", 
+    sanitize.colnames.function = identity, 
+    size="\\tiny",
+    table.placement="H")
 }
@@
 The following tables provide results for parameters in CES models.
+
+<<CES_Params_Table, results='asis', eval=TRUE>>=
+printCESParamsTable("Q"); printCESParamsTable("X"); printCESParamsTable("U")
+@
 

### 2013-02-23 EconGrowth.Rnw
Edited the to-do list slightly.
Now including parameter graphs for CES models. Need to adjust vertical axes and tic marks.

@@
       \item Convert $\rho$ variables in the \citet{Henningsen:2011td} CES production function to $\sigma$ variables.
-      \item parameter graphs for each country
-      \item parameter tables for each country in the appendix
+      \item Create parameter graphs for each country
+      \item \st{Parameter tables for each energy type in the appendix}
+      \item Fix the problems with $\sigma_1$ and $\sigma$ values in the CES parameter tables in the appendix
       \item AIC rows in the AIC table
@@
 cdParameterGraphHeight <- 2*h_param_graph + h_param_axis
+cesParameterGraphHeight <- 3*h_param_graph + h_param_axis
 linexParameterGraphHeight <- h_param_graph + h_param_axis
@@
 
+# print("cobbDouglasModel(US, Q) works fine:")
+# us <- cobbDouglasModel("US", "Q")
+# print(summary(us))
+# print(confint(us))
+# print("cobbDouglasModel(ZA, Q) has NA values:")
+# za <- cobbDouglasModel("ZA", "Q")
+# print(summary(za))
+# print(confint(za))
+# save(us, za, file="HeunModels.Rdata")
+
 #########################
@@
     if (!(haveDataCD(countryAbbrev, energyType))){
-      #If we don't have data for this combination of countryAbbrev and energyType, 
-      # return a column of NAs if the above conditions have been met.
+      # If we don't have data for this combination of countryAbbrev and energyType, 
+      # return a column of NAs when the above conditions have been met.
       nRows <- 21 # All of these countries need 21 rows.
@@
 
+#############################
+# Creates a graph with confidence intervals for the CES model for the given energyType
+##
+createCESParamsGraph <- function(energyType){
+  # Create a data table with the following columns:
+  # country abbrev, parameter (gamma, lambda, delta_1, delta, sigma_1, sigma), -95% CI, value, +95% CI
+  dataTable <- do.call("rbind", lapply(countryAbbrevs, cesCountryRowsForParamsGraph, energyType=energyType))
+  graph <- segplot(country ~ upperCI + lowerCI | parameter, 
+                   data = dataTable, 
+                   centers = value, #identifies where the dots should be placed
+                   as.table = TRUE, #indexing of panels starts in upper left and goes across rows.
+                   draw.bands = FALSE, #provides nicer error bars
+                   horizontal = FALSE, #makes error bars vertical and puts the countries in the x axis
+                   layout = c(2,3), #2 column, 3 row
+                   # Orders the panels as gamma, lambda, delta_1, delta, sigma_1, sigma
+                   index.cond = list(c(1,2,3,4,5,6)), 
+                   #set labels and bg color in strip
+                   strip = strip.custom(factor.levels=c("$\\gamma$", "$\\lambda$", "$\\delta_1$",
+                                                        "$\\delta$", "$\\sigma_1$", "$\\sigma$"), bg="white"),
+                   col = "black", #Sets line color to black
+                   lwd = 1, #Sets line width to 1.0
+                   ylim = list(c(-0.05, 1.0), c(-0.5, 5), c(0.0, 5.0),
+                               c(0.0, 1.0), c(0.0, 1.0), c(0.0, 1.0)), #y axis limits
+                   scales = list(cex=scaleTextSize, #controls text size on scales.
+                                 tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
+                                 x=list(cex=0.75), #reduces text size so that country abbrevs are legible
+                                 y=list(relation="free", #allow each axis to be different
+                                        at=list(c(0.0, 0.5, 1.0), c(0, 1, 2, 3, 4, 5), c(0.0, 0.5, 1.0),
+                                                c(0.0, 0.5, 1.0), c(0.0, 0.5, 1.0), c(0.0, 0.5, 1.0))   #y tick marks
+                                       )
+                   )
+  )
+  return(graph)
+}
+
 ############################
@@
 
+Figure \ref{fig:CESq_Params_Graph} shows values and 95\% confidence intervals for the parameters for the CES model (with $q$).
+
+<<CESq_Params_Graph, fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.pos="H", fig.cap="CES (with $q$) model parameters.
+Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
+createCESParamsGraph("Q")
+@
+
 \subsection{CES with $X$}
 
+Figure \ref{fig:CESx_Params_Graph} shows values and 95\% confidence intervals for the parameters for the CES model (with $x$).
+
+<<CESx_Params_Graph, fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.pos="H", fig.cap="CES (with $x$) model parameters.
+Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
+createCESParamsGraph("X")
+@
+
 \subsection{CES with $U$}
+
+Figure \ref{fig:CESu_Params_Graph} shows values and 95\% confidence intervals for the parameters for the CES model (with $u$).
+
+<<CESu_Params_Graph, fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.pos="H", fig.cap="CES (with $u$) model parameters.
+Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
+createCESParamsGraph("U")
+@
 
@@
 
-<<CES_Params_Table, results='asis', eval=TRUE>>=
+<<CES_Params_Table, results='asis'>>=
 printCESParamsTable("Q"); printCESParamsTable("X"); printCESParamsTable("U")

### 2013-02-25 EconGrowth.Rnw
Now including most information for the CES fits. Need to do the AIC table yet.

@@
       \item \st{GDP comparison graph}
-      \item Convert $\rho$ variables in the \citet{Henningsen:2011td} CES production function to $\sigma$ variables.
-      \item Create parameter graphs for each country
+      \item \st{Convert $\rho$ variables in the \citet{Henningsen:2011td} CES production function to $\sigma$ variables.}
+      \item \st{Create parameter graphs for each country}
       \item \st{Parameter tables for each energy type in the appendix}
-      \item Fix the problems with $\sigma_1$ and $\sigma$ values in the CES parameter tables in the appendix
+      \item \st{Fix the problems with $\sigma_1$ and $\sigma$ values in the CES parameter tables in the appendix}
       \item AIC rows in the AIC table
@@
     betaGuess <- 1.0 - alphaGuess
+    if (countryAbbrev == "ZA"){
+      # South Africa doesn't converge using the default guess values above. Try different values.
+      alphaGuess <- 0.597 # The alpha value when energy is not included
+      betaGuess <- 1.0 - alphaGuess
+#       alphaGuess <- 0.4
+#       gammaGuess <- 0.1
+#       betaGuess <- 1.0 - alphaGuess - gammaGuess
+#       alphaGuess <- 0.39
+#       betaGuess <- 0.41
+    }
     aGuess <- alphaGuess
@@
 
+# Some code that is helping to debug the Cobb-Douglas models. Randy Pruim is helping on this.
+
 # print("cobbDouglasModel(US, Q) works fine:")
@@
 # print(confint(us))
-# print("cobbDouglasModel(ZA, Q) has NA values:")
+
+# print("cobbDouglasModel(ZA) works fine")
+# za <- cobbDouglasModel("ZA")
+# print(summary(za))
+# print(confint(za))
+
+# print("cobbDouglasModel(ZA, Q) stops before convergence achieved,")
+# print("and confint gives NA values:")
 # za <- cobbDouglasModel("ZA", "Q")
@@
 # print(confint(za))
-# save(us, za, file="HeunModels.Rdata")
+# 
+# print("cobbDouglasModel(UK, Q) also stops before convergence achieved,")
+# print("but confint does not produce NA values:")
+# uk <- cobbDouglasModel("UK", "Q")
+# print(summary(uk))
+# print(confint(uk))
+
+# save(us, za, uk, file="HeunModels-US-ZA-UK.Rdata")
 
@@
   sigma_1CI <- with(sigma_1.est, Estimate + c(-1.0, 1.0) * tvalCES * SE)
+  # There are some cases where the confidence intervals for sigma_1 are huge. Set them to -Inf or Inf as appropriate
+  if (is.nan(sigma_1CI[1]) || (sigma_1CI[1] < -1.0e10)){
+    sigma_1CI[1] <- -Inf 
+  }
+  if (is.nan(sigma_1CI[2]) || (sigma_1CI[2] > 1.0e10)){
+    sigma_1CI[2] <- Inf
+  }
 #print("sigma_1CI:")
@@
 ############################
-# Aggregates the CES results into a big data table for the given energyType.
-##
-cesParamsTable <- function(energyType){
-  #Do rbind on the results of creating a row in the table for every country abbreviation that we know.
+# Aggregates the CES results for gamma, delta_1, and delta into a table for the given energyType.
+##
+cesParamsTableA <- function(energyType){
   dataCES <- do.call("rbind", lapply(countryAbbrevs, cesCountryRow, energyType=energyType))
@@
   rownames(dataCES) <- countryAbbrevs
-  tableCES <- xtable(dataCES, 
-                    caption=paste("CES model (with $", tolower(energyType), "$) parameters for 1980-2011 (US, UK, JP), 1991-2010 (CN and ZA), and 1991-2011 (SA, IR, TZ, and ZM).
+  tableCESa <- xtable(dataCES[,c(1,2,3, 7,8,9, 10,11,12)], #Picks up gamma, delta_1, and delta
+                      caption=paste("CES model (with $", tolower(energyType), "$).
+$\\gamma$, $\\delta_1$, and $\\delta$ parameters for 1980-2011 (US, UK, JP), 1991-2010 (CN and ZA), and 1991-2011 (SA, IR, TZ, and ZM).
 (Parameter estimates beneath symbol.
@@
                       label=paste("tab:CES_Parameters_With_", energyType, sep=""),
-                    digits = c(1, 2,2,2, 2,2,2, 2,2,2, 2,2,2, 2,2,2, 2,2,2),
-                    align = "r|ccc|ccc|ccc|ccc|ccc|ccc") #Sets alignment of the numbers in the columns
-  return(tableCES)
+                      digits = c(1, 2,2,2, 2,2,2, 2,2,2),
+                      align = "r|ccc|ccc|ccc" #Sets alignment of the numbers in the columns
+                      ) 
+  return(tableCESa)
+}
+
+############################
+# Aggregates the CES results for lambda, sigma_1, and sigma into a table for the given energyType.
+##
+cesParamsTableB <- function(energyType){
+  dataCES <- do.call("rbind", lapply(countryAbbrevs, cesCountryRow, energyType=energyType))
+  colnames(dataCES) <- c(" ", "$\\gamma$",    " ", 
+                         " ", "$\\lambda$",   " ",
+                         " ", "$\\delta_1$",  " ",
+                         " ", "$\\delta$",    " ",
+                         " ", "$\\sigma_1$",  " ",
+                         " ", "$\\sigma$",    " ")
+  rownames(dataCES) <- countryAbbrevs
+  tableCESb <- xtable(dataCES[,c(4,5,6, 13,14,15, 16,17,18)], #Picks up lambda, sigma_1, and sigma
+                      caption=paste("CES model (with $", tolower(energyType), "$).
+$\\lambda$, $\\sigma_1$, and $\\sigma$ parameters for 1980-2011 (US, UK, JP), 1991-2010 (CN and ZA), and 1991-2011 (SA, IR, TZ, and ZM).
+(Parameter estimates beneath symbol.
+95\\% confidence interval bounds to left and right.)", sep=""),
+                      label=paste("tab:CES_Parameters_With_", energyType, sep=""),
+                      digits = c(1, 4,4,4, 2,2,2, 2,2,2),
+                      align = "r|ccc|ccc|ccc"  #Sets alignment of the numbers in the columns
+                      )
+  return(tableCESb)
 }
@@
                    lwd = 1, #Sets line width to 1.0
-                   ylim = list(c(-0.05, 1.0), c(-0.5, 5), c(0.0, 5.0),
+                   ylim = list(c(0.9, 1.1), c(-0.05, 0.05), c(0.0, 1.0),
                                c(0.0, 1.0), c(0.0, 1.0), c(0.0, 1.0)), #y axis limits
@@
                                  y=list(relation="free", #allow each axis to be different
-                                        at=list(c(0.0, 0.5, 1.0), c(0, 1, 2, 3, 4, 5), c(0.0, 0.5, 1.0),
-                                                c(0.0, 0.5, 1.0), c(0.0, 0.5, 1.0), c(0.0, 0.5, 1.0))   #y tick marks
+                                        at=list(c(0.9, 1.0, 1.1), c(-0.05, 0.0, 0.05),
+                                                c(0.0, 0.5, 1.0), c(0.0, 0.5, 1.0), 
+                                                c(0.0, 0.5, 1.0), c(0.0, 0.5, 1.0))   #y tick marks
                                        )
@@
 ############################
-# Prints a table with parameters from a CES model for the given energyType. 
-##
-printCESParamsTable <- function(energyType){
-  print(cesParamsTable(energyType), 
+# Prints a table with gamma, delta_1, and delta parameters from a CES model for the given energyType. 
+##
+printCESParamsTableA <- function(energyType){
+  print(cesParamsTableA(energyType), 
+    caption.placement="top", 
+    sanitize.colnames.function = identity, 
+    size="\\tiny",
+    table.placement="H")
+}
+
+############################
+# Prints a table with lambda, sigma_1, and sigma parameters from a CES model for the given energyType. 
+##
+printCESParamsTableB <- function(energyType){
+  print(cesParamsTableB(energyType), 
     caption.placement="top", 
@@
 
-<<CESq_Params_Graph, fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.pos="H", fig.cap="CES (with $q$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
+<<CESq_Params_Graph, fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.pos="H", fig.cap="CES (with $q$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
 createCESParamsGraph("Q")
@@
 
-<<CESx_Params_Graph, fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.pos="H", fig.cap="CES (with $x$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
+<<CESx_Params_Graph, fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.pos="H", fig.cap="CES (with $x$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
 createCESParamsGraph("X")
@@
 
-<<CESu_Params_Graph, fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.pos="H", fig.cap="CES (with $u$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
+<<CESu_Params_Graph, fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.pos="H", fig.cap="CES (with $u$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
 createCESParamsGraph("U")
@@
 <<CES_Params_Table, results='asis'>>=
-printCESParamsTable("Q"); printCESParamsTable("X"); printCESParamsTable("U")
+#printCESParamsTable("Q"); printCESParamsTable("X"); printCESParamsTable("U")
+printCESParamsTableA("Q"); printCESParamsTableB("Q")
+printCESParamsTableA("X"); printCESParamsTableB("X")
+printCESParamsTableA("U"); printCESParamsTableB("U")
 @

### 2013-02-25 EconGrowth.Rnw
Edited the to-do list.

@@
       \item \st{GDP comparison graph}
-      \item \st{Convert $\rho$ variables in the \citet{Henningsen:2011td} CES production function to $\sigma$ variables.}
+      \item \st{Convert $\rho$ variables in the CES production function to $\sigma$}
+      \item Write up the decisions about parameter estimation for the CES production function fits
       \item \st{Create parameter graphs for each country}
       \item \st{Parameter tables for each energy type in the appendix}
-      \item \st{Fix the problems with $\sigma_1$ and $\sigma$ values in the CES parameter tables in the appendix}
+      \item Fix the problems with $\sigma_1$ and $\sigma$ values in the CES parameter tables in the appendix
       \item AIC rows in the AIC table

### 2013-02-25 EconGrowth.Rnw
Now including code to generate a graph of SE vs. gamma for the CD models. Trying to debug why the ZA model doesn't converge.

@@
 # Give an energyType ("Q", "X", or "U") if you want to include an energy term
-##
-cobbDouglasModel <- function(countryAbbrev, energyType){
+# by including the gamma parameter, a fit with fixed gamma will be provided.
+##
+cobbDouglasModel <- function(countryAbbrev, energyType, gamma){
   dataTable <- loadData(countryAbbrev) #Load the data that we need.
@@
                    #algorithm = "port",
-                   #lower = list(lambda=-Inf, alpha=0), #constraints on lambda and alpha
+                   #lower = list(lambda=-Inf, alpha=0),
                    #upper = list(lambda=Inf, alpha=1)
@@
     # Now actually do the fit, using the column name "iEToFit".
+    if (missing(gamma)){
+      # gamma is a free parameter that we want to estimate
       model <- iGDP ~ exp(lambda*iYear) * iCapStk^min(a,b) * iLabor^abs(b-a) * iEToFit^(1.0 - max(a,b))
@@
                       )
+    } else {
+      # We don't want to estimat the value of gamma
+      # Calculate a new column iEGamma = iEToFit^gamma
+      iEGamma <- with(dataTable, iEToFit^gamma)
+# print(iEGamma)
+      dataTable <- cbind(dataTable, iEGamma)
+# print(dataTable)
+      # Now fit the CD model with fixed gamma
+      # Establish guess values for alpha and lambda.
+      lambdaGuess <- 0.0 #guessing lambda = 0 means there is no technological progress.
+      alphaGuess <- 0.7 #0.7 gives good results for all countries.  
+      start <- list(lambda=lambdaGuess, alpha=alphaGuess)
+      model <- iGDP ~ exp(lambda*iYear) * iCapStk^alpha * iLabor^(1 - alpha) * iEGamma
+      modelCDe <- nls(formula=model, data = dataTable, start = start,
+                      control = nls.control(maxiter = 200, 
+                                            tol = 1e-05, 
+                                            minFactor = 1/1024, 
+                                            printEval=FALSE, #Tells whether to print details of curve fit process.
+                                            warnOnly=TRUE),
+                      #Include the next 3 lines to fit with constraints.
+                      #algorithm = "port",
+                      #lower = list(lambda=-Inf, alpha=0),
+                      #upper = list(lambda=Inf, alpha=1)
+                      )
+    }
+# print(summary(modelCDe))
     return(modelCDe)
@@
 }
+
+###############################
+# Does a grid search over values of gamma for a CD production function
+##
+cdGrid <- function(countryAbbrev, energyType, gammaGrid){
+  gamma <- c(0.1, 0.2)
+  gamma <- gammaGrid
+  models <- lapply(gamma, cobbDouglasModel, energyType=energyType, countryAbbrev=countryAbbrev)
+  return(models)
+}
+
+seFromNlsModel <- function(model) { 
+  return(summary(model)$sigma)
+}
+
+gammaGrid <- seq(0.0, 1.0, by=0.1)
+models <- cdGrid("US", "Q", gammaGrid)
+SSE <- lapply(models, function(model) summary(model)$sigma)
+data <- cbind(gammaGrid, SSE)
+print("US")
+plot(gammaGrid, SSE)
+print(coef(models[[2]]))
+
+models <- cdGrid("ZA", "Q", gammaGrid)
+SSE <- lapply(models, function(model) summary(model)$sigma)
+data <- cbind(gammaGrid, SSE)
+print("ZA")
+plot(gammaGrid, SSE)
+print(coef(models[[5]]))
 

### 2013-02-25 EconGrowth.Rnw
Now correctly including the effect of fixed gamma on the Cobb-Douglas with energy model for South Africa.

@@
       iEGamma <- with(dataTable, iEToFit^gamma)
-# print(iEGamma)
       dataTable <- cbind(dataTable, iEGamma)
-# print(dataTable)
-      # Now fit the CD model with fixed gamma
-      # Establish guess values for alpha and lambda.
+      # We already know the value of gamma. We don't want to estimate it.
+      # Establish guess values for lambda and alpha.
       lambdaGuess <- 0.0 #guessing lambda = 0 means there is no technological progress.
-      alphaGuess <- 0.7 #0.7 gives good results for all countries.  
+      alphaGuess <- 0.7*(1-gamma) #ensure a consistent starting point.
       start <- list(lambda=lambdaGuess, alpha=alphaGuess)
-      model <- iGDP ~ exp(lambda*iYear) * iCapStk^alpha * iLabor^(1 - alpha) * iEGamma
+      model <- iGDP ~ exp(lambda*iYear) * iCapStk^alpha * iLabor^((1-gamma) - alpha) * iEGamma
       modelCDe <- nls(formula=model, data = dataTable, start = start,
@@
 
-gammaGrid <- seq(0.0, 1.0, by=0.1)
+gammaGrid <- seq(0.05, 0.95, by=0.1)
 models <- cdGrid("US", "Q", gammaGrid)

### 2013-02-25 EconGrowth.Rnw
Now creating graphs of lambda and alpha as a function of gamma for ZA Cobb-Douglas wtih energy.

@@
 
-seFromNlsModel <- function(model) { 
-  return(summary(model)$sigma)
-}
-
+print("US")
 gammaGrid <- seq(0.05, 0.95, by=0.1)
@@
 data <- cbind(gammaGrid, SSE)
-print("US")
 plot(gammaGrid, SSE)
@@
 
+print("ZA")
 models <- cdGrid("ZA", "Q", gammaGrid)
 SSE <- lapply(models, function(model) summary(model)$sigma)
-data <- cbind(gammaGrid, SSE)
-print("ZA")
+print(str(coef(models[[5]])))
+lambda <- lapply(models, function(model) coef(model)["lambda"])
+alpha <- lapply(models, function(model) coef(model)["alpha"])
+data <- cbind(gammaGrid, lambda, alpha, SSE)
 plot(gammaGrid, SSE)
+plot(gammaGrid, lambda)
+plot(gammaGrid, alpha)
 print(coef(models[[5]]))

### 2013-02-25 EconGrowth.Rnw
Now including code that correctly handles constraints on alpha, beta, and gamma for CD with energy fits. This new code also creates graphs of variation of SE, lambda, alpha, (and therefore beta) for a grid search over gamma.

--- 2013-02-25 EconGrowth.Rnw
@@
       # South Africa doesn't converge using the default guess values above. Try different values.
+      gammaGuess <- 0.65 # Found via grid search over gamma
       alphaGuess <- 0.597 # The alpha value when energy is not included
-      betaGuess <- 1.0 - alphaGuess
+      betaGuess <- 1.0 - alphaGuess - gammaGuess
 #       alphaGuess <- 0.4
@@
     if (missing(gamma)){
-      # gamma is a free parameter that we want to estimate
+      # gamma is a free parameter. We need to estimate lambda, a, and b.
       model <- iGDP ~ exp(lambda*iYear) * iCapStk^min(a,b) * iLabor^abs(b-a) * iEToFit^(1.0 - max(a,b))
@@
     } else {
-      # We don't want to estimat the value of gamma
+      # We don't want to estimate the value of gamma
       # Calculate a new column iEGamma = iEToFit^gamma
@@
                       #Include the next 3 lines to fit with constraints.
-                      #algorithm = "port",
-                      #lower = list(lambda=-Inf, alpha=0),
-                      #upper = list(lambda=Inf, alpha=1)
+                      algorithm = "port",
+                      lower = list(lambda=-Inf, alpha=0),
+                      upper = list(lambda=Inf, alpha=1.0-gamma)
                       )
@@
 cdGrid <- function(countryAbbrev, energyType, gammaGrid){
-  gamma <- c(0.1, 0.2)
   gamma <- gammaGrid
@@
 
-seFromNlsModel <- function(model) { 
-  return(summary(model)$sigma)
-}
-
-gammaGrid <- seq(0.05, 0.95, by=0.1)
-models <- cdGrid("US", "Q", gammaGrid)
-SSE <- lapply(models, function(model) summary(model)$sigma)
-data <- cbind(gammaGrid, SSE)
-print("US")
-plot(gammaGrid, SSE)
-print(coef(models[[2]]))
-
+gammaGrid <- seq(0.0, 0.95, by=0.05)
+# print("US")
+# models <- cdGrid("US", "Q", gammaGrid)
+# SSE <- lapply(models, function(model) summary(model)$sigma)
+# data <- cbind(gammaGrid, SSE)
+# plot(gammaGrid, SSE)
+# print(coef(models[[2]]))
+# 
+print("ZA")
 models <- cdGrid("ZA", "Q", gammaGrid)
 SSE <- lapply(models, function(model) summary(model)$sigma)
-data <- cbind(gammaGrid, SSE)
-print("ZA")
+lambda <- lapply(models, function(model) coef(model)["lambda"])
+alpha <- lapply(models, function(model) coef(model)["alpha"])
+data <- cbind(lambda, alpha, gammaGrid, SSE)
+print(data)
 plot(gammaGrid, SSE)
-print(coef(models[[5]]))
-
-# Some code that is helping to debug the Cobb-Douglas models. Randy Pruim is helping on this.
+plot(gammaGrid, lambda)
+plot(gammaGrid, alpha)
+
+# Some code to debug the Cobb-Douglas models. Randy Pruim is helping on this.
 
@@
 # print(confint(us))
-
+# 
 # print("cobbDouglasModel(ZA) works fine")
@@
 # print(confint(za))
-
+# 
 # print("cobbDouglasModel(ZA, Q) stops before convergence achieved,")

### 2013-02-26 EconGrowth.Rnw
Doing some serious code cleanup. At this point, I have split the Cobb-Douglas functions apart, and everything is still working fine.

@@
 ####################
-# Returns an nls Cobb-Douglas model for the country specified
-# Give an energyType ("Q", "X", or "U") if you want to include an energy term
-# by including the gamma parameter, a fit with fixed gamma will be provided.
-##
-cobbDouglasModel <- function(countryAbbrev, energyType, gamma){
+# Returns an nls Cobb-Douglas model (without energy) for the country specified. 
+# No energy is included in the function to be fitted.
+##
+cdModel <- function(countryAbbrev){
   dataTable <- loadData(countryAbbrev) #Load the data that we need.
-  #Run the non-linear least squares fit to the data based on whether we have an energy type or not.
-  if (missing(energyType)){
-    # No energy term desired in the Cobb-Douglas equation.
+  # Run the non-linear least squares fit to the data. No energy term desired in the Cobb-Douglas equation.
   # Establish guess values for alpha and lambda.
@@
   return(modelCD)
-  } else {
+}
+
+####################
+# Returns an nls Cobb-Douglas model for the country specified
+# energyType is one of "Q", "X", or "U".
+##
+cdeModel <- function(countryAbbrev, energyType){
+  dataTable <- loadData(countryAbbrev) #Load the data that we need.
   # We need to do the Cobb-Douglas fit with the desired energy data.
@@
   dataTable <- replaceColName(dataTable, energyType, "iEToFit")
+  # Establish guess values for lambda, alpha, and beta.
+  lambdaGuess <- 0.0 #guessing lambda = 0 means there is no technological progress.
+  alphaGuess <- 0.9
+  betaGuess <- 1.0 - alphaGuess
+  aGuess <- alphaGuess
+  bGuess <- alphaGuess + betaGuess
+  start <- list(lambda=lambdaGuess, a=aGuess, b=bGuess)
+  # Now actually do the fit, using the column name "iEToFit".
+  # gamma is a free parameter.
   # Reparameterize to ensure that we meet the constraints:
@@
   # * gamma = 1 - max(a, b)
-    # Establish guess values for lambda, alpha, and beta.
-    lambdaGuess <- 0.0 #guessing lambda = 0 means there is no technological progress.
-    alphaGuess <- 0.9
-    betaGuess <- 1.0 - alphaGuess
-    if (countryAbbrev == "ZA"){
-      # South Africa doesn't converge using the default guess values above. Try different values.
-      gammaGuess <- 0.65 # Found via grid search over gamma
-      alphaGuess <- 0.597 # The alpha value when energy is not included
-      betaGuess <- 1.0 - alphaGuess - gammaGuess
-#       alphaGuess <- 0.4
-#       gammaGuess <- 0.1
-#       betaGuess <- 1.0 - alphaGuess - gammaGuess
-#       alphaGuess <- 0.39
-#       betaGuess <- 0.41
-    }
-    aGuess <- alphaGuess
-    bGuess <- alphaGuess + betaGuess
-    start <- list(lambda=lambdaGuess, a=aGuess, b=bGuess)
-    # Now actually do the fit, using the column name "iEToFit".
-    if (missing(gamma)){
-      # gamma is a free parameter. We need to estimate lambda, a, and b.
   model <- iGDP ~ exp(lambda*iYear) * iCapStk^min(a,b) * iLabor^abs(b-a) * iEToFit^(1.0 - max(a,b))
@@
                   )
-    } else {
-      # We don't want to estimate the value of gamma
+  return(modelCDe)
+}
+
+##############################
+# Returns a Cobb-Douglas model where gamma (the exponent on the energy term) has been fixed
+##
+cdeFixedGammaModel <- function(countryAbbrev, energyType, gamma){
+  dataTable <- loadData(countryAbbrev) #Load the data that we need.
+  # We need to do the Cobb-Douglas fit with the desired energy data.
+  # To achieve the correct fit, we'll change the name of the desired column
+  # to "iEToFit" and use "iEToFit" in the nls function. 
+  dataTable <- replaceColName(dataTable, energyType, "iEToFit")
+  # We're fixing the value of gamma.
   # Calculate a new column iEGamma = iEToFit^gamma
@@
                   )
-    }
-# print(summary(modelCDe))
   return(modelCDe)
+}
+
+####################
+# Returns an nls Cobb-Douglas model for the country specified
+# Give an energyType ("Q", "X", or "U") if you want to include an energy term
+# If you supply a value for the gamma argument, a fit with fixed gamma will be provided.
+# This function dispatches to cdModel, cdeModel, or cdFixedGammaModel as appropriate.
+##
+cobbDouglasModel <- function(countryAbbrev, energyType, gamma){
+  if (missing(energyType)){
+    # Fit the Cobb-Douglas model without energy.
+    return(cdModel(countryAbbrev))
+  } else {
+    if (missing(gamma)){
+      # Fit the Cobb-Douglas model with gamma as a free parameter
+      return(cdeModel(countryAbbrev, energyType))
+    }
+    # Fit the Cobb-Douglas model with fixed value of gamma
+    return(cdeFixedGammaModel(countryAbbrev, energyType, gamma))
   }

### 2013-03-03 EconGrowth.Rnw
Added a file for the Math seminar presentation.

@@
                  )
+# print("str(modelCD)")
+# print(str(modelCD))
+# print("")
+# print(modelCD$)
+#   # We estimated alpha with the above code, but we have beta = 1.0 - alpha. So, get 
+#   # an estimate for beta and add it to the model.
+#   summaryCD <- summary(modelCD)
+# print("summaryCD")
+# print(summaryCD)
+#   dofCD <- summaryCD$df[2] # Gives the degrees of freedom for the model.
+#   tvalCD <- qt(ciHalfLevel, df = dofCD)
+#   alpha <- coef(modelCD)["alpha"]
+#   betaEst <- deltaMethod(modelCD, "1 - alpha") # Estimates beta and its standard error (SE).
+# print("betaEst")
+# print(betaEst)
+#   # Calculate beta and its confidence interval and report it.
+#   # Now calculate a confidence interval on beta
+#   betaCICD <- with(betaEst, Estimate + c(-1.0, 1.0) * tvalCD * SE); betaCICD # Gives the confidence interval on beta.  
+# print("betaCICD")
+# print(betaCICD)
+
   return(modelCD)
 }
+
+cdModel("US")
 
@@
 # If you supply a value for the gamma argument, a fit with fixed gamma will be provided.
-# This function dispatches to cdModel, cdeModel, or cdFixedGammaModel as appropriate.
+# This function dispatches to cdModel, cdeModel, or cdFixedGammaModel based on which arguments are specified.
 ##
@@
     return(cdModel(countryAbbrev))
-  } else {
-    if (missing(gamma)){
+  }
+  if (!missing(gamma)){
+    # Fit the Cobb-Douglas model with fixed value of gamma
+    return(cdeFixedGammaModel(countryAbbrev, energyType, gamma))
+  }
   # Fit the Cobb-Douglas model with gamma as a free parameter
   return(cdeModel(countryAbbrev, energyType))
-    }
-    # Fit the Cobb-Douglas model with fixed value of gamma
-    return(cdeFixedGammaModel(countryAbbrev, energyType, gamma))
-  }
 }
@@
 data <- cbind(lambda, alpha, gammaGrid, SSE)
-print(data)
 plot(gammaGrid, SSE)

### 2013-03-03 EconGrowthSeminar.Rnw
Added a file for the Math seminar presentation.

\documentclass{beamer}

% This file is a solution template for:
% - Giving a talk on some subject.
% - The talk is between 15min and 45min long.
% - Style is ornate.

\mode<presentation>
{
  \usetheme{Berkeley}
  \usecolortheme{beaver}
  % or ...

  \setbeamercovered{transparent}
  % or whatever (possibly just delete it)

  \setbeamercolor{section number projected}{bg=red,fg=gray}
  \setbeamercolor{itemize item} {bg=red, fg=gray}
}

\usepackage[english]{babel}
% or whatever

\usepackage[latin1]{inputenc}
% or whatever

\usepackage{times}
\usepackage[T1]{fontenc}
% Or whatever. Note that the encoding and the font should match. If T1
% does not look nice, try deleting the line with the fontenc.

\title[Energy and Growth] % (optional, use only with long paper titles)
{An Empirical Analysis of the Role of Energy in Economic Growth}

%\subtitle
%{Presentation Subtitle} % (optional)

\author[Caleb Reese, Lucas Timmer, Matthew Heun] % (optional, use only with lots of authors)
%{F.~Author\inst{1} \and S.~Another\inst{2}}
{Caleb Reese, Lucas Timmer, Matthew Kuperus Heun}
% - Use the \inst{?} command only if the authors have different
%   affiliation.

\institute[Calvin College] % (optional, but mostly needed)
{
  %\inst{1}%
  Engineering Department\\
  Calvin College
}
% - Use the \inst command only if there are several affiliations.
% - Keep it simple, no one is interested in your street address.

\date[Short Occasion] % (optional)
{4 April 2013 / Mathematics Department Colloquium}

\subject{Talks}
% This is only inserted into the PDF information catalog. Can be left
% out.

% If you have a file called "university-logo-filename.xxx", where xxx
% is a graphic format that can be processed by latex or pdflatex,
% resp., then you can add a logo as follows:

% \pgfdeclareimage[height=0.5cm]{university-logo}{university-logo-filename}
% \logo{\pgfuseimage{university-logo}}

% Delete this, if you do not want the table of contents to pop up at
% the beginning of each subsection:
\AtBeginSubsection[]
{
  \begin{frame}<beamer>{Outline}
    \tableofcontents[currentsection,currentsubsection]
  \end{frame}
}

% If you wish to uncover everything in a step-wise fashion, uncomment
% the following command:

%\beamerdefaultoverlayspecification{<+->}

\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{Outline}
  \tableofcontents
  % You might wish to add the option [pausesections]
\end{frame}

% Since this a solution template for a generic talk, very little can
% be said about how it should be structured. However, the talk length
% of between 15min and 45min and the theme suggest that you stick to
% the following rules:

% - Exactly two or three sections (other than the summary).
% - At *most* three subsections per section.
% - Talk about 30s to 2min per frame. So there should be between about
%   15 and 30 frames, all told.

\section{Introduction}

\subsection[Short First Subsection Name]{First Subsection Name}

\begin{frame}{Make Titles Informative. Use Uppercase Letters.}{Subtitles are optional.}
  % - A title should summarize the slide in an understandable fashion
  %   for anyone how does not follow everything on the slide itself.

  \begin{itemize}
  \item
    Use \texttt{itemize} a lot.
  \item
    Use very short sentences or short phrases.
  \end{itemize}
\end{frame}

\begin{frame}{Make Titles Informative.}

  You can create overlays\dots
  \begin{itemize}
  \item using the \texttt{pause} command:
    \begin{itemize}
    \item
      First item.
      \pause
    \item    
      Second item.
    \end{itemize}
  \item
    using overlay specifications:
    \begin{itemize}
    \item<3->
      First item.
    \item<4->
      Second item.
    \end{itemize}
  \item
    using the general \texttt{uncover} command:
    \begin{itemize}
      \uncover<5->{\item
        First item.}
      \uncover<6->{\item
        Second item.}
    \end{itemize}
  \end{itemize}
\end{frame}

\subsection{Second Subsection}

\begin{frame}{Make Titles Informative.}
\end{frame}

\begin{frame}{Make Titles Informative.}
\end{frame}

\section*{Summary}

\begin{frame}{Summary}

  % Keep the summary *very short*.
  \begin{itemize}
  \item
    The \alert{first main message} of your talk in one or two lines.
  \item
    The \alert{second main message} of your talk in one or two lines.
  \item
    Perhaps a \alert{third message}, but not more than that.
  \end{itemize}

  % The following outlook is optional.
  \vskip0pt plus.5fill
  \begin{itemize}
  \item
    Outlook
    \begin{itemize}
    \item
      Something you haven't solved.
    \item
      Something else you haven't solved.
    \end{itemize}
  \end{itemize}
\end{frame}

\end{document}

### 2013-03-03 EconGrowthSeminar.Rnw
Starting to include the outline for the seminar. Added a Calvin heart-and-hand logo to the presentation.

@@
   % or ...
+  \setbeamercolor{section number projected}{bg=gray,fg=red}
+  \setbeamercolor{itemize item} {bg=gray, fg=red}
+  \setbeamercolor{itemize subitem} {bg=gray, fg=red}
+  \setbeamercolor{itemize subsubitem} {bg=gray, fg=red}
 
-  \setbeamercovered{transparent}
+  % \setbeamercovered{transparent}
   % or whatever (possibly just delete it)  
-
-  \setbeamercolor{section number projected}{bg=red,fg=gray}
-  \setbeamercolor{itemize item} {bg=red, fg=gray}
 }
@@
 
-\author[Caleb Reese, Lucas Timmer, Matthew Heun] % (optional, use only with lots of authors)
+\author[Reese, Timmer, Heun] % (optional, use only with lots of authors)
+{Caleb Reese, Lucas Timmer, Matthew Kuperus Heun}
 %{F.~Author\inst{1} \and S.~Another\inst{2}}
-{Caleb Reese, Lucas Timmer, Matthew Kuperus Heun}
 % - Use the \inst{?} command only if the authors have different
@@
 
-\date[Short Occasion] % (optional)
-{4 April 2013 / Mathematics Department Colloquium}
+\date[Math Seminar] % (optional)
+{Mathematics Colloquium\\
+4 April 2013
+}
 
-\subject{Talks}
+\subject{Energy and Economic Growth}
 % This is only inserted into the PDF information catalog. Can be left
@@
 % resp., then you can add a logo as follows:
-
 % \pgfdeclareimage[height=0.5cm]{university-logo}{university-logo-filename}
 % \logo{\pgfuseimage{university-logo}}
+
+\pgfdeclareimage[height=1.53cm]{university-logo}{CalvinLogo.png}
+\logo{\pgfuseimage{university-logo}}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\subsection[Short First Subsection Name]{First Subsection Name}
+\subsection[Growth Modeling]{Economic Growth Modeling} %+++++++++++++++++++++++++++++++++++++++
 
-\begin{frame}{Make Titles Informative. Use Uppercase Letters.}{Subtitles are optional.}
-  % - A title should summarize the slide in an understandable fashion
-  %   for anyone how does not follow everything on the slide itself.
+% \begin{frame}{Make Titles Informative. Use Uppercase Letters.} %----------------------------
+%   % - A title should summarize the slide in an understandable fashion
+%   %   for anyone how does not follow everything on the slide itself.
+% 
+%   \begin{itemize}
+%   \item
+%     Use \texttt{itemize} a lot.
+%   \item
+%     Use very short sentences or short phrases.
+%   \end{itemize}
+% \end{frame}
+% 
+% \begin{frame}{Make Titles Informative.} %----------------------------
+% 
+%   You can create overlays\dots
+%   \begin{itemize}
+%   \item using the \texttt{pause} command:
+%     \begin{itemize}
+%     \item
+%       First item.
+%       \pause
+%     \item    
+%       Second item.
+%     \end{itemize}
+%   \item
+%     using overlay specifications:
+%     \begin{itemize}
+%     \item<3->
+%       First item.
+%     \item<4->
+%       Second item.
+%     \end{itemize}
+%   \item
+%     using the general \texttt{uncover} command:
+%     \begin{itemize}
+%       \uncover<5->{\item
+%         First item.}
+%       \uncover<6->{\item
+%         Second item.}
+%     \end{itemize}
+%   \end{itemize}
+% \end{frame}
 
-  \begin{itemize}
-  \item
-    Use \texttt{itemize} a lot.
-  \item
-    Use very short sentences or short phrases.
-  \end{itemize}
+\subsection{Types of Energy} %+++++++++++++++++++++++++++++++++++++++
+
+\begin{frame}{Thermal Energy ($Q$)} %----------------------------
+
 \end{frame}
 
-\begin{frame}{Make Titles Informative.}
+\begin{frame}{Exergy ($X$)} %----------------------------
 
-  You can create overlays\dots
-  \begin{itemize}
-  \item using the \texttt{pause} command:
-    \begin{itemize}
-    \item
-      First item.
-      \pause
-    \item    
-      Second item.
-    \end{itemize}
-  \item
-    using overlay specifications:
-    \begin{itemize}
-    \item<3->
-      First item.
-    \item<4->
-      Second item.
-    \end{itemize}
-  \item
-    using the general \texttt{uncover} command:
-    \begin{itemize}
-      \uncover<5->{\item
-        First item.}
-      \uncover<6->{\item
-        Second item.}
-    \end{itemize}
-  \end{itemize}
 \end{frame}
 
-\subsection{Second Subsection}
+\begin{frame}{Useful Work ($W$)} %----------------------------
 
-\begin{frame}{Make Titles Informative.}
 \end{frame}
 
-\begin{frame}{Make Titles Informative.}
+\subsection{Economic Growth Models} %+++++++++++++++++++++++++++++++++++++++
+
+\begin{frame}{Single Factor} %----------------------------
+
 \end{frame}
 
+\begin{frame}{Cobb-Douglas} %----------------------------
+
+\end{frame}
+
+\begin{frame}{Constant Elasticity of Substitution (CES)} %----------------------------
+
+\end{frame}
+
+\begin{frame}{LINEX} %----------------------------
+
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Sources of Data}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection[Econ Data]{Sources of Economic Data} %+++++++++++++++++++++++++++++++++++++++
+
+\subsection[Energy Data]{Sources of Energy Data} %+++++++++++++++++++++++++++++++++++++++
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Examples}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection[US]{USA} %+++++++++++++++++++++++++++++++++++++++
+
+\subsection[ZA]{South Africa} %+++++++++++++++++++++++++++++++++++++++
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Summary}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\begin{frame}{Summary}
+\begin{frame}{Summary} %----------------------------
 

### 2013-03-04 EconGrowthSeminar.Rnw
Updates seminar slides. Now looking more like one of my Calvin talks.

@@
   % or ...
-  \setbeamercolor{section number projected}{bg=gray,fg=red}
-  \setbeamercolor{itemize item} {bg=gray, fg=red}
-  \setbeamercolor{itemize subitem} {bg=gray, fg=red}
-  \setbeamercolor{itemize subsubitem} {bg=gray, fg=red}
+  % Some Calvin colors. See:
+  % http://www.calvin.edu/admin/webmanager/color-palette.htm
+  % http://www.calvin.edu/admin/publishing/nameplat.html
+  \definecolor{CalvinMaroon}{RGB}{108, 1, 29} % Approximation of Pantone 202
+  \definecolor{CalvinTan}{RGB}{126, 25, 52}
+  \definecolor{CalvinLightTan}{RGB}{207, 212, 182} % Good for backgrounds
+  \definecolor{CalvinDarkBlueAccent}{RGB}{4, 27, 55}
+  \definecolor{CalvinLightBlueAccent}{RGB}{80, 111, 136}
+  \definecolor{CalvinGreenAccent}{RGB}{8, 59, 71}
+  \definecolor{CalvinGrayAccent}{RGB}{131, 154, 150}
+
+  % Now set colors of the on-screen elements
+  \setbeamercolor{frametitle}{fg=CalvinMaroon, bg=CalvinLightTan}
+  \setbeamercolor{title}{fg=CalvinMaroon, bg=CalvinLightTan!60!white}
+  \setbeamercolor{section in toc}{fg=CalvinMaroon, bg=CalvinLightTan!60!white}
+  \setbeamercolor{section in toc shaded}{fg=CalvinMaroon, bg=CalvinLightTan!60!white} 
+  \setbeamercolor{item}{fg=CalvinMaroon}
+  \setbeamercolor{subitem}{fg=CalvinMaroon}
+  \setbeamercolor{subsubitem}{fg=CalvinMaroon}
+  \setbeamercolor{description item}{fg=CalvinMaroon}
+  \setbeamercolor{caption}{fg=CalvinMaroon}
+  \setbeamercolor{caption name}{fg=CalvinMaroon}
+
+  \setbeamercolor{background canvas}{bg=CalvinLightTan!60!white}
+  \setbeamercolor{block title}{fg=CalvinMaroon, bg=CalvinLightTan!60!white}
+  \setbeamercolor{block body}{bg=CalvinLightTan!60!white}
+  \setbeamercolor{block title alerted}{bg=CalvinLightTan!60!white}
+  \setbeamercolor{block body alerted}{bg=CalvinLightTan!60!white}
+  \setbeamercolor{block title example}{bg=CalvinLightTan!60!white}
+  \setbeamercolor{block body example}{bg=CalvinLightTan!60!white}
+
+  \setbeamercolor{section number projected}{fg=CalvinMaroon, bg=CalvinLightTan!60!white}
+  \setbeamercolor{itemize item} {fg=CalvinMaroon}
+  \setbeamercolor{itemize subitem} {fg=CalvinMaroon}
+  \setbeamercolor{itemize subsubitem} {fg=CalvinMaroon}
+  \setbeamercolor{normal text}{fg=CalvinMaroon}
+
+  \setbeamercolor{palette sidebar primary}{fg=CalvinMaroon, bg=CalvinLightTan!60!white}
+  \setbeamercolor{palette sidebar secondary}{fg=CalvinMaroon, bg=CalvinLightTan!60!white}
+  \setbeamercolor{palette sidebar tertiary}{fg=CalvinMaroon, bg=CalvinLightTan!60!white}
+  \setbeamercolor{palette sidebar quaternary}{fg=CalvinMaroon, bg=CalvinLightTan!60!white}
+
+  % Remove navigation bar from bottom of slides.
+  \beamertemplatenavigationsymbolsempty
 
@@
 
-\pgfdeclareimage[height=1.53cm]{university-logo}{CalvinLogo.png}
+\pgfdeclareimage[height=1.56cm]{university-logo}{CalvinLogo.png}
 \logo{\pgfuseimage{university-logo}}
@@
 % the beginning of each subsection:
-\AtBeginSubsection[]
-{
-  \begin{frame}<beamer>{Outline}
-    \tableofcontents[currentsection,currentsubsection]
-  \end{frame}
-}
+% \AtBeginSubsection[]
+% {
+%   \begin{frame}<beamer>{Outline}
+%     \tableofcontents[currentsection,currentsubsection]
+%   \end{frame}
+% }
 
@@
 
+\begin{frame}{Example Frame from the Template}{Shows how to overlay stuff} %----------------------------
+
+  You can create overlays\dots
+  \begin{itemize}
+  \item using the \texttt{pause} command:
+    \begin{itemize}
+    \item
+      First item.
+      \pause
+    \item    
+      Second item.
+    \end{itemize}
+  \item
+    using overlay specifications:
+    \begin{itemize}
+    \item<3->
+      First item.
+    \item<4->
+      Second item.
+    \end{itemize}
+  \item
+    using the general \texttt{uncover} command:
+    \begin{itemize}
+      \uncover<5->{\item
+        First item.}
+      \uncover<6->{\item
+        Second item.}
+    \end{itemize}
+  \end{itemize}
+\end{frame}
+
 \subsection[Growth Modeling]{Economic Growth Modeling} %+++++++++++++++++++++++++++++++++++++++
 
-% \begin{frame}{Make Titles Informative. Use Uppercase Letters.} %----------------------------
-%   % - A title should summarize the slide in an understandable fashion
-%   %   for anyone how does not follow everything on the slide itself.
-% 
-%   \begin{itemize}
-%   \item
-%     Use \texttt{itemize} a lot.
-%   \item
-%     Use very short sentences or short phrases.
-%   \end{itemize}
-% \end{frame}
-% 
-% \begin{frame}{Make Titles Informative.} %----------------------------
-% 
-%   You can create overlays\dots
-%   \begin{itemize}
-%   \item using the \texttt{pause} command:
-%     \begin{itemize}
-%     \item
-%       First item.
-%       \pause
-%     \item    
-%       Second item.
-%     \end{itemize}
-%   \item
-%     using overlay specifications:
-%     \begin{itemize}
-%     \item<3->
-%       First item.
-%     \item<4->
-%       Second item.
-%     \end{itemize}
-%   \item
-%     using the general \texttt{uncover} command:
-%     \begin{itemize}
-%       \uncover<5->{\item
-%         First item.}
-%       \uncover<6->{\item
-%         Second item.}
-%     \end{itemize}
-%   \end{itemize}
-% \end{frame}
+\begin{frame}{Factors of Production: $K$ and $L$} %----------------------------
+  \begin{itemize}
+  \item
+    Capital Stock ($K$) <Definition here>
+  \item
+    Labor ($L$) <Definition here>
+  \item
+    Energy ($E$)
+  \end{itemize}
+\end{frame}
 

### 2013-03-04 EconGrowthSeminar.Rnw
Now including a figure for the seminar. Lots more of the seminar outline in beamer has been developed.

@@
 
-  \setbeamercolor{background canvas}{bg=CalvinLightTan!60!white}
+  \setbeamertemplate{background canvas}[vertical shading][top=CalvinLightTan, bottom=white]
   \setbeamercolor{block title}{fg=CalvinMaroon, bg=CalvinLightTan!60!white}
@@
   \setbeamercolor{palette sidebar quaternary}{fg=CalvinMaroon, bg=CalvinLightTan!60!white}
+  \setbeamercolor{sidebar}{bg=CalvinLightTan}
 
@@
 
-\begin{frame}{Example Frame from the Template}{Shows how to overlay stuff} %----------------------------
+\begin{frame}{Energy is Essential for Economic Activity} %----------------------------
+  What do you do that doesn't require energy?
+\end{frame}
 
-  You can create overlays\dots
-  \begin{itemize}
-  \item using the \texttt{pause} command:
+\begin{frame}{Cleveland, 1984} %----------------------------
+  Show Cleveland's graph and cover of \emph{Science} here.
+\end{frame}
+
+\begin{frame}{Problem: Energy Cost Share is Low} %----------------------------
+  Therefore, energy is considered to be economically unimportant.
+
+  Compare cost shares of capital stock, labor, and energy.
+\end{frame}
+
+\begin{frame}{Energy Cost Share and Economic Growth} %----------------------------
+  Show graphs of energy cost share and recessions
+\end{frame}
+
+\begin{frame}{The Big Questions} %----------------------------
+  How account for energy in economic models?
+
+  What happens when energy supplies become constrained?
+
+  Historical economic development paths are energy intensive. What happens when energy is constrained and prices rise? Will developing countries be able to expand their economies?
+\end{frame}
+
+\begin{frame}{Economic (Growth) Modeling} %----------------------------
+  \begin{center}
+    \includegraphics[height=2.5cm]{figure/Figure_Growth_Models.pdf}
+  \end{center}
   \begin{itemize}
   \item
-      First item.
-      \pause
+    Goal: predict economic output over time
   \item
-      Second item.
-    \end{itemize}
+    Economic output is a function of ``factors of production''
   \item
-    using overlay specifications:
-    \begin{itemize}
-    \item<3->
-      First item.
-    \item<4->
-      Second item.
-    \end{itemize}
+    Output defined as GDP ($Y$)
   \item
-    using the general \texttt{uncover} command:
-    \begin{itemize}
-      \uncover<5->{\item
-        First item.}
-      \uncover<6->{\item
-        Second item.}
-    \end{itemize}
+    All inputs and outputs normalized to initial year (0)
   \end{itemize}
@@
 
-\subsection[Growth Modeling]{Economic Growth Modeling} %+++++++++++++++++++++++++++++++++++++++
+\subsection[Factors of Production]{Factors of Production} %+++++++++++++++++++++++++++++++++++++++
 
-\begin{frame}{Factors of Production: $K$ and $L$} %----------------------------
+\begin{frame}{Capital Stock ($K$) and Labor ($L$)} %----------------------------
   \begin{itemize}
@@
     Labor ($L$) <Definition here>
-  \item
-    Energy ($E$)
   \end{itemize}
@@
 
-\subsection{Types of Energy} %+++++++++++++++++++++++++++++++++++++++
+\begin{frame}{Energy ($E$)} %----------------------------
+  Caleb complete
+\end{frame}
 
 \begin{frame}{Thermal Energy ($Q$)} %----------------------------
+  Caleb complete
+\end{frame}
+
+\begin{frame}{Exergy ($X$)} %----------------------------
+  Caleb complete
+\end{frame}
+
+\begin{frame}{Useful Work ($W$)} %----------------------------
+  Caleb complete
+\end{frame}
+
+\subsection[Growth Models]{Economic Growth Models} %+++++++++++++++++++++++++++++++++++++++
+
+\begin{frame}{Single Factor} %----------------------------
+
+  \begin{equation*} \label{eq:Single_Factor_Generic}
+    y = \mathrm{e}^{\lambda (t-t_0)}f^{m}
+  \end{equation*}
+
+  \begin{center}
+    \begin{tabular}{|c|l|}\hline
+      $y$   & $Y$/$Y_0$ \\
+      $t$   & year\\
+      $t_0$ & initial year\\
+      $f$   & $F$/$F_0$, a factor of production\\
+      \hline
+      $\lambda$   &   technological progress\\
+      $m$   &         ``strength'' of factor $f$\\
+      \hline
+    \end{tabular}
+  \end{center}
 
@@
 
-\begin{frame}{Exergy ($X$)} %----------------------------
-
-\end{frame}
-
-\begin{frame}{Useful Work ($W$)} %----------------------------
-
-\end{frame}
-
-\subsection{Economic Growth Models} %+++++++++++++++++++++++++++++++++++++++
-
-\begin{frame}{Single Factor} %----------------------------
-
+\begin{frame}{Example Single-Factor Fit} %----------------------------
+  Heun complete
 \end{frame}
@@
 
+  \begin{equation*} \label{eq:CD_With_Energy}
+    y = \mathrm{e}^{\lambda (t-t_0)}k^{\alpha}l^{\beta}e^{\gamma}
+  \end{equation*}
+
+  \begin{equation*} \label{eq:CD_Const_Returns_To_Scale}
+    \alpha + \beta + \gamma = 1
+  \end{equation*}
+
+  \begin{equation*} \label{eq:CD_Constraints}
+    0 \leq \alpha, \beta, \gamma \leq 1
+  \end{equation*}
+
+  \begin{center}
+    \begin{tabular}{|c|l|}\hline
+      $k$   & $K$/$K_0$, capital stock\\
+      $l$   & $L$/$L_0$, labor\\
+      $e$   & $E$/$E_0$, any of $q$, $x$, or $u$\\
+      \hline
+      $\lambda$   &   technological progress\\
+      $\alpha$   &    ``strength'' of capital\\
+      $\beta$   &    ``strength'' of labor\\
+      $\gamma$   &    ``strength'' of energy\\
+      \hline
+    \end{tabular}
+  \end{center}
+
+\end{frame}
+
+\begin{frame}{Example Cobb-Douglas Fit} %----------------------------
+  Heun complete
 \end{frame}
@@
 
+  \begin{equation*} \label{eq:micEconCES_model}
+    \begin{split}
+    y = & \gamma \mathrm{e}^{\lambda(t-t_0)} \\
+        & \cdot \left\{\delta \left[\delta_1 k^{-\rho_1} + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1} 
+                        + (1-\delta) e^{-\rho} \right\}^{-1/\rho}
+    \end{split}
+  \end{equation*}
+
+  \begin{center}
+    \begin{tabular}{|c|l|}\hline
+      $k$   & $K$/$K_0$, capital stock\\
+      $l$   & $L$/$L_0$, labor\\
+      $e$   & $E$/$E_0$, any of $q$, $x$, or $u$\\
+      \hline
+      $\gamma$   &   fitting coefficient\\
+      $\lambda$  &   technological progress\\
+      $\delta$   &   split between ($kl$) and ($e$)\\
+      $\rho$     &   ``strength'' of ($kl$) vs. ($e$)\\
+      $\delta_1$   &   split between ($k$) and ($l$)\\
+      $\rho_1$     &   ``strength'' of ($k$) vs. ($l$)\\
+      \hline
+    \end{tabular}
+  \end{center}
+
+\end{frame}
+
+\begin{frame}{Example CES Fit} %----------------------------
+  Heun complete
 \end{frame}
@@
 
+  \begin{equation*} \label{eq:LINEX_model}
+    y = e \: \mathrm{e}^{\left[a_0 \left(2 - \frac{l + e}{k} \right) + a_0 c_t \left(\frac{l}{e} - 1 \right)\right]}
+  \end{equation*}
+
+  \begin{center}
+    \begin{tabular}{|c|l|}\hline
+      $k$   & $K$/$K_0$, capital stock\\
+      $l$   & $L$/$L_0$, labor\\
+      $e$   & $E$/$E_0$, any of $q$, $x$, or $u$\\
+      \hline
+      $a_0$   &   fitting parameter\\
+      $c_t$   &   fitting parameter\\
+      \hline
+    \end{tabular}
+  \end{center}
+
+\end{frame}
+
+\begin{frame}{Example LINEX Fit} %----------------------------
+  Heun complete
 \end{frame}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Sources of Data}
+\section[Data Sources]{Sources of Data}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\subsection[Econ Data]{Sources of Economic Data} %+++++++++++++++++++++++++++++++++++++++
+\subsection[Economic Data]{Sources of Economic Data} %+++++++++++++++++++++++++++++++++++++++
+
+\begin{frame}{Economic Data}
+  Lucas complete
+\end{frame}
 
 \subsection[Energy Data]{Sources of Energy Data} %+++++++++++++++++++++++++++++++++++++++
+
+\begin{frame}{Energy Data}
+  Caleb complete
+\end{frame}
 
@@
 
+\begin{frame}{US Single Factor}
+  Heun complete
+\end{frame}
+
+\begin{frame}{US Cobb-Douglas}
+  Heun complete
+\end{frame}
+
+\begin{frame}{US CES}
+  Heun complete
+\end{frame}
+
+\begin{frame}{US LINEX}
+  Heun complete
+\end{frame}
+
 \subsection[ZA]{South Africa} %+++++++++++++++++++++++++++++++++++++++
+
+\begin{frame}{ZA Single Factor}
+  Heun complete
+\end{frame}
+
+\begin{frame}{ZA Cobb-Douglas}
+  Heun complete
+\end{frame}
+
+\begin{frame}{ZA CES}
+  Heun complete
+\end{frame}
+
+\begin{frame}{ZA LINEX}
+  Heun complete
+\end{frame}
 
@@
 
+\begin{frame}{Results}
+  Heun complete
+\end{frame}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\begin{frame}{Summary} %----------------------------
+\begin{frame}{Conclusions} %----------------------------
 
-  % Keep the summary *very short*.
   \begin{itemize}
   \item
-    The \alert{first main message} of your talk in one or two lines.
+    Including energy is unwarranted \\
+    \scriptsize
+    Little statistical evidence that including energy in production functions improves fit.
+    \normalsize
   \item
-    The \alert{second main message} of your talk in one or two lines.
+    Including energy is unnecessary \\
+    \scriptsize
+    Energy is always \emph{already} embedded in capital stock ($K$) and labor ($L$).
+    \normalsize
+  \vskip0pt plus.5fill
   \item
-    Perhaps a \alert{third message}, but not more than that.
+    Need a modeling method that captures energy's embeddedness \\
+    \scriptsize
+    System dynamics modeling
+    \normalsize
   \end{itemize}
 
-  % The following outlook is optional.
-  \vskip0pt plus.5fill
-  \begin{itemize}
-  \item
-    Outlook
-    \begin{itemize}
-    \item
-      Something you haven't solved.
-    \item
-      Something else you haven't solved.
-    \end{itemize}
-  \end{itemize}
 \end{frame}

### 2013-03-04 EconGrowth-R-Functions.Rnw
Have moved all functions to a special file.

--- 2013-03-03 EconGrowth.Rnw
@@
-% This article has been prepared for publication in Energy Economics in RStudio with knitr.
-% According to http://www.elsevier.com/author-schemas/the-elsarticle-latex-document-class, we should be using the
-% elsarticle.cls file.
-% According to http://cdn.elsevier.com/assets/pdf_file/0006/109392/journal_refstyles.pdf, we should be using
-% elsarticle-template-2-harv.tex as the template for the text.
-% Furthermore, we should be using model2-names.bst for the bibliographic references.
-% The approach here is to load the frontmatter and backmatter from elsarticle-template-2-harv.tex
-% both ahead of and behind the text for our paper.
-% -- Matthew Kuperus Heun, 2013-01-18
-
-%% This is file `elsarticle-template-2-harv.tex',
-%%
-%% Copyright 2009 Elsevier Ltd
-%%
-%% This file is part of the 'Elsarticle  Bundle'.
-%% ---------------------------------------------
-%%
-%% It may be distributed under the conditions of the LaTeX Project Public
-%% License, either version 1.2 of this license or (at your option) any
-%% later version.  The latest version of this license is in
-%%    http://www.latex-project.org/lppl.txt
-%% and version 1.2 or later is part of all distributions of LaTeX
-%% version 1999/12/01 or later.
-%%
-%% The list of all files belonging to the 'Elsarticle Bundle' is
-%% given in the file `manifest.txt'.
-%%
-%% Template article for Elsevier's document class `elsarticle'
-%% with harvard style bibliographic references
-%%
-%% $Id: elsarticle-template-2-harv.tex 155 2009-10-08 05:35:05Z rishi $
-%% $URL: http://lenova.river-valley.com/svn/elsbst/trunk/elsarticle-template-2-harv.tex $
-%%
-\documentclass[preprint,authoryear,12pt]{elsarticle}
-
-%% Use the option review to obtain double line spacing
-%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}
-
-%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
-%% for a journal layout:
-%% \documentclass[final,authoryear,1p,times]{elsarticle}
-%% \documentclass[final,authoryear,1p,times,twocolumn]{elsarticle}
-%% \documentclass[final,authoryear,3p,times]{elsarticle}
-%% \documentclass[final,authoryear,3p,times,twocolumn]{elsarticle}
-%% \documentclass[final,authoryear,5p,times]{elsarticle}
-%% \documentclass[final,authoryear,5p,times,twocolumn]{elsarticle}
-
-%% if you use PostScript figures in your article
-%% use the graphics package for simple commands
-%% \usepackage{graphics}
-%% or use the graphicx package for more complicated commands
-%% \usepackage{graphicx}
-%% or use the epsfig package if you prefer to use the old commands
-%% \usepackage{epsfig}
-
-%% The amssymb package provides various useful mathematical symbols
-\usepackage{amssymb}
-%% The amsthm package provides extended theorem environments
-%% \usepackage{amsthm}
-
-\usepackage{soul} %Provides strikethrough text
-\usepackage{float} %Allows precise positioning of tables and figures within the text
-\usepackage{amsmath} %Allows \begin{equation*} \end{equation*} for unnumbered equations
-
-%% The lineno packages adds line numbers. Start line numbering with
-%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
-%% for the whole article with \linenumbers after \end{frontmatter}.
-%% \usepackage{lineno}
-
-%% natbib.sty is loaded by default. However, natbib options can be
-%% provided with \biboptions{...} command. Following options are
-%% valid:
-
-%%   round  -  round parentheses are used (default)
-%%   square -  square brackets are used   [option]
-%%   curly  -  curly braces are used      {option}
-%%   angle  -  angle brackets are used    <option>
-%%   semicolon  -  multiple citations separated by semi-colon (default)
-%%   colon  - same as semicolon, an earlier confusion
-%%   comma  -  separated by comma
-%%   authoryear - selects author-year citations (default)
-%%   numbers-  selects numerical citations
-%%   super  -  numerical citations as superscripts
-%%   sort   -  sorts multiple citations according to order in ref. list
-%%   sort&compress   -  like sort, but also compresses numerical citations
-%%   compress - compresses without sorting
-%%   longnamesfirst  -  makes first citation full author list
-%%
-%% \biboptions{longnamesfirst,comma}
-
-% \biboptions{}
-
-\journal{Energy Economics}
-
-\begin{document}
-
-\begin{frontmatter}
-
-%% Title, authors and addresses
-
-%% use the tnoteref command within \title for footnotes;
-%% use the tnotetext command for the associated footnote;
-%% use the fnref command within \author or \address for footnotes;
-%% use the fntext command for the associated footnote;
-%% use the corref command within \author for corresponding author footnotes;
-%% use the cortext command for the associated footnote;
-%% use the ead command for the email address,
-%% and the form \ead[url] for the home page:
-%%
-%% \title{Title\tnoteref{label1}}
-%% \tnotetext[label1]{}
-%% \author{Name\corref{cor1}\fnref{label2}}
-%% \ead{email address}
-%% \ead[url]{home page}
-%% \fntext[label2]{}
-%% \cortext[cor1]{}
-%% \address{Address\fnref{label3}}
-%% \fntext[label3]{}
-
-\title{An Empirical Analysis of the Role of Energy in Economic Growth}
-
-%% use optional labels to link authors explicitly to addresses:
-%% \author[label1,label2]{<author name>}
-%% \address[label1]{<address>}
-%% \address[label2]{<address>}
-
-\author[Calvin]{Caleb Reese}
-\author[Calvin]{Lucas Timmer}
-\author[Stellenbosch]{Martin de Wit}
-\author[Calvin]{Matthew Kuperus Heun\corref{cor1}}
-\ead{mkh2@calvin.edu, tel: +1 (616) 526-6663, fax: +1 (616) 526-6501}
-
-\cortext[cor1]{Corresponding author}
-\address[Calvin]{Engineering Department, Calvin College, Grand Rapids, MI 49546, USA}
-\address[Stellenbosch]{Stellenbosch University, Faculty of Economics and Management Sciences, School of Public Leadership, P.O. Box 610, Bellville 7535, South Africa}
-
-\begin{abstract}
-%% Text of abstract
-*********** Add abstract ***********
-\end{abstract}
-
-\begin{keyword}
-%% keywords here, in the form: keyword \sep keyword
-economic growth \sep energy \sep cobb-douglas \sep CES \sep LINEX
-%% MSC codes here, in the form: \MSC code \sep code
-%% or \MSC[2008] code \sep code (2000 is the default)
-\end{keyword}
-
-\end{frontmatter}
-
-% \linenumbers
-%% main text
-
-\section*{To-do List}
-\begin{itemize}
-\item Reese: Add text from Word verson of paper to the LaTeX version.
-\item Heun: Add CES production function fits
-      \begin{itemize}
-      \item \st{GDP comparison graph}
-      \item \st{Convert $\rho$ variables in the CES production function to $\sigma$}
-      \item Write up the decisions about parameter estimation for the CES production function fits
-      \item \st{Create parameter graphs for each country}
-      \item \st{Parameter tables for each energy type in the appendix}
-      \item Fix the problems with $\sigma_1$ and $\sigma$ values in the CES parameter tables in the appendix
-      \item AIC rows in the AIC table
-      \end{itemize}
-\item Heun: Deal with missing covariance numbers when columns have unequal length. Use the \texttt{subset} command.
-\item Heun: Eliminate blanks in the coefficient tables for the 95\% CIs in the Cobb-Douglas with energy rows. Asked Pruim about this via email on 4 Feb 2013 but have not heard a response.
-      \begin{itemize}
-      \item ZA: lower bound on $\lambda$ and upper bound on $\alpha$
-      \item ZM: lower bound on $\lambda$
-      \end{itemize}
-\item Heun: Eliminate blanks in the coefficient tables for the 95\% CIs in the LINEX model
-      \begin{itemize}
-      \item Zambia, upper bound on $c_t$
-      \end{itemize}
-\item Heun: Fix warnings of the form ``Warning:  step factor 0.000488281 reduced below ’minFactor’ of 0.000976562'' in the code that generates the Cobb-Douglas with energy fits.
-\item Heun: x-axis labels only on bottom for 9-panel lattice graphs
-\item Heun: adjust y axis limits on $a_0$ and $c_t$ parameter graphs for the LINEX model AFTER we finish debugging the LINEX models.
-\item de Wit: provide funding acknowledgement, if necessary.
-\item de Wit: review, critique, and contextualize.
-\item \st{Heun: Ask Martin if he can supply an ``Economics'' affiliation. Will probably make a stronger paper.}
-\item \st{Heun: Create a table of AIC values for each fit.}
-\item \st{Heun: Add $u$ predictions for Cobb-Douglas}
-\item \st{Heun: Move tables to an appendix at the end.}
-\item \st{Heun: Add acknowledgements (Dad, Pruim)}
-\item \st{Heun: Add $u$ parameter table and graph}
-\item \st{Heun: Add covariance metrics.}
-\item \st{Heun: Add single factor fits}
-      \begin{itemize}
-      \item \st{Correct sizes for parameter graphs for each country}
-      \item \st{Parameter graphs ($\lambda$ and $m$) for each country}
-      \item \st{Parameter tables for each country in the appendix}
-      \item \st{GDP comparison graph}
-      \item \st{AIC rows in the AIC table}
-      \end{itemize}
-\item \st{Heun: Add setup variables for figure height and width where not already included.}
-\item \st{Heun: Add LINEX production function fits}
-      \begin{itemize}
-      \item \st{Parameter graphs for each country}
-      \item \st{Parameter tables for each country in the appendix}
-      \item \st{AIC rows in the AIC table}
-      \item \st{GDP comparison graph}
-      \end{itemize}
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-*********** Caleb, put your LaTeX code here. *************
-
-<<setup, echo=FALSE, message=FALSE>>=
+<<setup_parent, echo=FALSE, message=FALSE, eval=TRUE>>=
 require(knitr)
@@
 opts_chunk$set(
-  # ********************************************************************************************************
-  eval=TRUE,
-  # ********************************************************************************************************
-  warning=TRUE, #Tells whether to show warnings in the output.
   dev='tikz',    #Allows LaTeX code in graphical output. E.g., "$y$" for a variable name in the legend for a graph.
@@
   cache=FALSE,
-  echo=FALSE,    #Tells whether to echo code for all chunks. Set TRUE on an individual chunk to see its code.
-  message=FALSE) #Turns off messages for all chunks. Set TRUE on an individual chunk to see it.
+  warning=TRUE,  #Tells whether to show warnings in the output.
+  message=FALSE, #Turns off messages for all chunks. Set TRUE on an individual chunk to see it.
+  echo=FALSE     #Tells whether to echo code for all chunks. Set TRUE on an individual chunk to see its code.
+)
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Historical Data}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Figure \ref{fig:Historical_Lattice_Graph} shows historical data, including GDP ($y$), capital stock ($k$), labor ($l$), and the various energy types ($q$, $x$, and $u$).
-Factors of production track each other closely, and large covariances among these variables can be seen in Tables \ref{tab:Covariance_US} through \ref{tab:Covariance_ZM}.
-
-<<Historical_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="Historical data.
-Indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$).">>=
-createHistoricalLatticeGraph()
-@
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Single-factor Models (SF)}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 <<single-factor functions, eval=TRUE>>=
@@
 @
-
-We begin by fitting single-factor economic models of the form
-
-\begin{equation} \label{eq:Single_Factor_Generic}
-  y = \mathrm{e}^{\lambda (t-t_0)}f^{m}
-\end{equation}
-
-\noindent to historical data where the factor of production ($f$) is any of $k$, $l$, $q$, $x$, or $u$, and the exponent ($m$) is $\alpha$ for $k$, $\beta$ for $l$, or $\gamma$ for $q$, $x$, and $u$.
-
-<<SFk_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $k$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createSFParamsGraph("K")
-@
-
-<<SFl_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $l$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createSFParamsGraph("L")
-@
-
-<<SFq_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $q$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createSFParamsGraph("Q")
-@
-
-<<SFx_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $x$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createSFParamsGraph("X")
-@
-
-<<SFu_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $u$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createSFParamsGraph("U")
-@
-
-Figure \ref{fig:SF_GDP_Lattice_Graph} compares single-factor model predictions with historica data.
-
-<<SF_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="Single-factor results.">>=
-createSFLatticeGraph()
-@
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Cobb-Douglas Models Without Energy (CD)}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-The Cobb-Douglas model without energy is given by
-
-\begin{equation} \label{eq:CD_No_Energy}
-  y = \mathrm{e}^{\lambda (t-t_0)}k^{\alpha}l^{\beta}.
-\end{equation}
-
-Figure \ref{fig:CD_Params_Graph} shows values and 95\% confidence intervals for the parameters for the Cobb-Douglas model (without energy).
-
-<<CD_Params_Graph, fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.pos="H", fig.cap="Cobb-Douglas (without energy) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createCDParamsGraph()
-@
-
-\section{Cobb-Douglas Models With Energy (CDe)}
-
-We can force $\alpha$, $\beta$, and $\gamma$ to be in $[0,1]$ by a reparameterization:
-
-$a \in[0,1], b \in [0,1], \alpha=\min(a,b), \beta=|b-a|, \gamma = 1-\max(a,b)$
-
-The Cobb-Douglas model with energy is given by
-
-\begin{equation} \label{eq:CD_With_Energy}
-  y = \mathrm{e}^{\lambda (t-t_0)}k^{\alpha}l^{\beta}e^{\gamma},
-\end{equation}
-
-\noindent where $e$ can be any of thermal energy ($q$), exergy ($x$), or useful work ($u$).
-
-\subsection{Cobb-Douglas with thermal energy ($q$)}
-
-Figure \ref{fig:CDq_Params_Graph} shows values and 95\% confidence intervals for the parameters for the Cobb-Douglas model (with $q$).
-
-<<CDq_Params_Graph, fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.pos="H", fig.cap="Cobb-Douglas (with $q$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createCDParamsGraph("Q")
-@
-
-\subsection{Cobb-Douglas with exergy ($x$)}
-
-The Cobb-Douglas (with exergy) parameters are given in Table \ref{tab:CD_Parameters_With_X}.
-
-Figure \ref{fig:CDx_Params_Graph} shows values and 95\% confidence intervals for the parameters for the Cobb-Douglas model (with $x$).
-
-<<CDx_Params_Graph, fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.pos="H", fig.cap="Cobb-Douglas (with $x$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createCDParamsGraph("X")
-@
-
-\subsection{Cobb-Douglas with useful work ($u$)}
-
-Figure \ref{fig:CDu_Params_Graph} shows values and 95\% confidence intervals for the parameters for the Cobb-Douglas model (with $u$).
-
-<<CDu_Params_Graph, fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.pos="H", fig.cap="Cobb-Douglas (with $u$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createCDParamsGraph("U")
-@
-
-\subsection{Cobb-Douglas Comparisons}
-
-Figure \ref{fig:CD_GDP_Lattice_Graph} compares predictions from the Cobb-Douglas models (without energy, with $q$, with $x$, and with $u$) to historical data.
-
-<<CD_GDP_Lattice_Graph, fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="Cobb-Douglas results.">>=
-createCDLatticeGraph()
-@
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{CES Models}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 <<ces functions, eval=TRUE>>=
@@
 
-\citet{Stern:2012ey} developed a CES model of the form\footnote{The CES equation in \citet{Stern:2012ey} appears as
-
-\begin{equation*} \label{eq:Stern_CES_model}
-  y = \left\{ (1-\gamma_E)^{1/\sigma} \left[ k^{\alpha} \left( \mathrm{e}^{\lambda_L(t-t_0)} l \right)^{\beta} \right]^{\frac{\sigma-1}{\sigma}}   
-      + (\gamma_E)^{1/\sigma} \left[ \mathrm{e}^{\lambda_E(t-t_0)} e \right]^{\frac{\sigma - 1}{\sigma}}   \right\}
-      ^{\frac{\sigma}{\sigma - 1}},
-\end{equation*}
-
-but the $1/\sigma$ exponent on the $(1-\gamma_E)$ and $\gamma_E$ terms is erroneous due to $y_{\mathrm{t_0}} \neq 1$.}
-
-\begin{equation} \label{eq:Stern_CES_model_in_print}
-  y = \left\{ (1-\gamma_E) \left[ k^{\alpha} \left( \mathrm{e}^{\lambda_L(t-t_0)} l \right)^{\beta} \right]^{\frac{\sigma-1}{\sigma}}   
-      + (\gamma_E) \left[ \mathrm{e}^{\lambda_E(t-t_0)} e \right]^{\frac{\sigma - 1}{\sigma}}   \right\}
-      ^{\frac{\sigma}{\sigma - 1}},
-\end{equation}
-
-\noindent where $e$ is any of $q$, $x$, or $u$; $\sigma$, $\gamma_E$, $\beta$, $\lambda_L$, and $\lambda_E$ are fitting parameters; $\mathrm{e}$ is the base of the natural logarithm; and the sum $\alpha + \beta$ is constrained to unity.
-
-The \texttt{R} \citep{R} package \texttt{micEconCES} \citep{Henningsen:2011td} estimates CES production functions of the form (among others)
-
-\begin{equation} \label{eq:micEconCES_model}
-  y = \gamma \mathrm{e}^{\lambda(t-t_0)}  
-      \left\{\delta \left[\delta_1 k^{-\rho_1} + (1-\delta_1)l^{-\rho_1} \right] + (1-\delta) e^{-\rho} \right\}
-                                                                                                        ^{-1/\rho}.
-\end{equation}
-
-\citet{Henningsen:2011td}, in their detailed analysis of \citet{Kemfert:1998vd}, found that
-
-\begin{quote}
-\ldots the Levenberg-Marquardt and the PORT algorithms are---at least in this study---most likely to find the coefficients that give the best fit to the model, where the PORT algorithm can be used to restrict the estimates to the economically meaningful region.
-\end{quote}
-
-\subsection{CES with $Q$}
-
-Figure \ref{fig:CESq_Params_Graph} shows values and 95\% confidence intervals for the parameters for the CES model (with $q$).
-
-<<CESq_Params_Graph, fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.pos="H", fig.cap="CES (with $q$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
-createCESParamsGraph("Q")
-@
-
-\subsection{CES with $X$}
-
-Figure \ref{fig:CESx_Params_Graph} shows values and 95\% confidence intervals for the parameters for the CES model (with $x$).
-
-<<CESx_Params_Graph, fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.pos="H", fig.cap="CES (with $x$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
-createCESParamsGraph("X")
-@
-
-\subsection{CES with $U$}
-
-Figure \ref{fig:CESu_Params_Graph} shows values and 95\% confidence intervals for the parameters for the CES model (with $u$).
-
-<<CESu_Params_Graph, fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.pos="H", fig.cap="CES (with $u$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
-createCESParamsGraph("U")
-@
-
-\subsection{CES comparisons}
-
-Figure \ref{fig:CES_GDP_Lattice_Graph} compares CES model predictions to historical data.
-
-<<CES_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="CES results.">>=
-createCESLatticeGraph()
-@
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{LINEX Models}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 <<LINEX functions, eval=TRUE>>=
@@
 @
-
-The LINEX model has the form
-
-\begin{equation} \label{eq:LINEX_model}
-  y = e \: \mathrm{e}^{\left[a_0 \left(2 - \frac{l + e}{k} \right) + a_0 c_t \left(\frac{l}{e} - 1 \right)\right]} ,
-\end{equation}
-
-\noindent where $e$ is any of $q$, $x$, or $u$; $a_0$ and $c_t$ are fitting parameters; and $\mathrm{e}$ is the base of the natural logarithm.
-
-\subsection{LINEX with $Q$}
-
-Figure \ref{fig:LINEXq_Params_Graph} shows values and 95\% confidence intervals for the parameters for the LINEX model (with $q$).
-
-<<LINEXq_Params_Graph, fig.width=linexParameterGraphWidth, fig.height=linexParameterGraphHeight, fig.pos="H", fig.cap="LINEX (with $q$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createLINEXParamsGraph("Q")
-@
-
-\subsection{LINEX with $X$}
-
-Figure \ref{fig:LINEXx_Params_Graph} shows values and 95\% confidence intervals for the parameters for the LINEX model (with $x$).
-
-<<LINEXx_Params_Graph, fig.width=linexParameterGraphWidth, fig.height=linexParameterGraphHeight, fig.pos="H", fig.cap="LINEX (with $x$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createLINEXParamsGraph("X")
-@
-
-\subsection{LINEX with $U$}
-
-Figure \ref{fig:LINEXu_Params_Graph} shows values and 95\% confidence intervals for the parameters for the LINEX model (with $u$).
-
-<<LINEXu_Params_Graph, fig.width=linexParameterGraphWidth, fig.height=linexParameterGraphHeight, fig.pos="H", fig.cap="LINEX (with $u$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createLINEXParamsGraph("U")
-@
-
-\subsection{LINEX comparisons}
-
-Figure \ref{fig:LINEX_GDP_Lattice_Graph} compares LINEX model predictions to historical data.
-
-<<LINEX_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="LINEX results.">>=
-createLinexLatticeGraph()
-@
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusion}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-****************** Add conclusion here. *********************
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Acknowledgements}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Funding for Caleb Reese and Lucas Timmer was generously supplied by the Jack and Lois Kuipers Applied Mathematics Endowment and the Calvin College Alumni Association.
-Funding for Martin de Wit was provided by *******.
-The authors thank Randall Pruim (Calvin College) and Loren L.
-Heun (Western Michigan University) for their insightful comments on and invaluable assistance with the statistical analyses presented herein.
-%% The Appendices part is started with the command \appendix;
-%% appendix sections are then done as normal sections
-%% \appendix
-%% \section{}
-%% \label{}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\appendix
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Covariance Tables}
-\setcounter{table}{0} % Restarts table number counter at 0 in this section.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The following tables show covariances among GDP ($y$) and factors of production ($k$, $l$, $q$, $x$, and $u$).
-
-<<Print_Covariance_Tables, results='asis'>>=
-#I wish I could say this, but I get bogus "$US" strings appearing in the LaTeX output.
-#lapply(countryAbbrevs, printCovarTable)
-printCovarTable("US"); printCovarTable("UK"); printCovarTable("JP")
-printCovarTable("CN"); printCovarTable("ZA")
-printCovarTable("SA"); printCovarTable("IR")
-printCovarTable("TZ"); printCovarTable("ZM")
-@
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Model Parameters}
-\setcounter{table}{0} % Restarts table number counter at 0 in this section.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Single-factor Models}
-
-The following tables provide results for parameters in single-factor models.
-
-<<SF_Params_Tables, results='asis'>>=
-#I wish I could say this, but I get bogus K [1]” strings appearing in the LaTeX output.
-#lapply(factors, printSingleFactorParamsTable)
-printSFParamsTable("K"); printSFParamsTable("L")
-printSFParamsTable("Q"); printSFParamsTable("X"); printSFParamsTable("U")
-@
-
-\subsection{Cobb-Douglas Models}
-
-The following tables provide results for parameters in Cobb-Douglas models with and without energy terms.
-
-<<CD_Params_Table, results='asis'>>=
-printCDParamsTable()    #Without energy
-printCDParamsTable("Q"); printCDParamsTable("X"); printCDParamsTable("U") #With energy
-@
-
-\subsection{CES Models}
-
-The following tables provide results for parameters in CES models.
-
-<<CES_Params_Table, results='asis'>>=
-#printCESParamsTable("Q"); printCESParamsTable("X"); printCESParamsTable("U")
-printCESParamsTableA("Q"); printCESParamsTableB("Q")
-printCESParamsTableA("X"); printCESParamsTableB("X")
-printCESParamsTableA("U"); printCESParamsTableB("U")
-@
-
-\subsection{LINEX Models}
-
-The following tables provide results for parameters in LINEX models.
-
-<<LINEX_Params_Table, results='asis'>>=
-printLINEXParamsTable("Q"); printLINEXParamsTable("X"); printLINEXParamsTable("U")
-@
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Goodness of fit}
-\setcounter{table}{0} % Restarts table number counter at 0 in this section.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 @
-
-We assess goodness of fit via the Akaike Information Criterion (AIC).
-AIC values for all models and all countries are shown in Table \ref{tab:AICTable}.
-Increasing goodness of fit is indicated by smaller (i.e., more negative) AIC values.
-AIC values can be compared per data set (i.e., per country) but not across data sets (i.e., not across countries).
-
-<<AIC_Table, results='asis', label="AIC_Table">>=
-print(createAICTable(), 
-      caption.placement="top", 
-      sanitize.rownames.function = identity,
-      size="\\tiny",
-      table.placement="H")
-@
-
-%% References
-%%
-%% Following citation commands can be used in the body text:
-%%
-%%  \citet{key}  ==>>  Jones et al. (1990)
-%%  \citep{key}  ==>>  (Jones et al., 1990)
-%%
-%% Multiple citations as normal:
-%% \citep{key1,key2}         ==>> (Jones et al., 1990; Smith, 1989)
-%%                            or  (Jones et al., 1990, 1991)
-%%                            or  (Jones et al., 1990a,b)
-%% \cite{key} is the equivalent of \citet{key} in author-year mode
-%%
-%% Full author lists may be forced with \citet* or \citep*, e.g.
-%%   \citep*{key}            ==>> (Jones, Baker, and Williams, 1990)
-%%
-%% Optional notes as:
-%%   \citep[chap. 2]{key}    ==>> (Jones et al., 1990, chap. 2)
-%%   \citep[e.g.,][]{key}    ==>> (e.g., Jones et al., 1990)
-%%   \citep[see][pg. 34]{key}==>> (see Jones et al., 1990, pg. 34)
-%%  (Note: in standard LaTeX, only one note is allowed, after the ref.
-%%   Here, one note is like the standard, two make pre- and post-notes.)
-%%
-%%   \citealt{key}          ==>> Jones et al. 1990
-%%   \citealt*{key}         ==>> Jones, Baker, and Williams 1990
-%%   \citealp{key}          ==>> Jones et al., 1990
-%%   \citealp*{key}         ==>> Jones, Baker, and Williams, 1990
-%%
-%% Additional citation possibilities
-%%   \citeauthor{key}       ==>> Jones et al.
-%%   \citeauthor*{key}      ==>> Jones, Baker, and Williams
-%%   \citeyear{key}         ==>> 1990
-%%   \citeyearpar{key}      ==>> (1990)
-%%   \citetext{priv. comm.} ==>> (priv. comm.)
-%%   \citenum{key}          ==>> 11 [non-superscripted]
-%% Note: full author lists depends on whether the bib style supports them;
-%%       if not, the abbreviated list is printed even when full requested.
-%%
-%% For names like della Robbia at the start of a sentence, use
-%%   \Citet{dRob98}         ==>> Della Robbia (1998)
-%%   \Citep{dRob98}         ==>> (Della Robbia, 1998)
-%%   \Citeauthor{dRob98}    ==>> Della Robbia
-
-%% References with bibTeX database:
-
-\bibliographystyle{model2-names}
-%%\bibliography{<your-bib-database>}
-\bibliography{EconGrowth.bib}
-
-%% Authors are advised to submit their bibtex database files. They are
-%% requested to list a bibtex style file in the manuscript if they do
-%% not want to use model2-names.bst.
-
-%% References without bibTeX database:
-
-% \begin{thebibliography}{00}
-
-%% \bibitem must have one of the following forms:
-%%   \bibitem[Jones et al.(1990)]{key}...
-%%   \bibitem[Jones et al.(1990)Jones, Baker, and Williams]{key}...
-%%   \bibitem[Jones et al., 1990]{key}...
-%%   \bibitem[\protect\citeauthoryear{Jones, Baker, and Williams}{Jones
-%%       et al.}{1990}]{key}...
-%%   \bibitem[\protect\citeauthoryear{Jones et al.}{1990}]{key}...
-%%   \bibitem[\protect\astroncite{Jones et al.}{1990}]{key}...
-%%   \bibitem[\protect\citename{Jones et al., }1990]{key}...
-%%   \harvarditem[Jones et al.]{Jones, Baker, and Williams}{1990}{key}...
-%%
-
-% \bibitem[ ()]{}
-
-% \end{thebibliography}
-
-\end{document}
-
-%%
-%% End of file `elsarticle-template-2-harv.tex'.

### 2013-03-04 EconGrowth.Rnw
Now including a figure for the seminar. Lots more of the seminar outline in beamer has been developed.
Have moved all functions to a special file.

--- 2013-02-25 EconGrowth.Rnw
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-*********** Caleb, put your LaTeX code here. *************
-
-<<setup, echo=FALSE, message=FALSE>>=
-require(knitr)
-require(lattice)
-require(latticeExtra)
-require(ggplot2)
-require(car)
-require(mosaic)
-require(xtable)
-require(nlmrt)
-require(micEconCES)
-# tikz allows use of LaTeX formatting and font in graphs. Allows for a consistent look across the paper.
-# See http://r-forge.r-project.org/R/?group_id=440 for instructions on installing tikzDevice.
-require(tikzDevice) 
-trellis.par.set(theme=theme.mosaic())
-options(width=75)
-options(show.signif.stars=TRUE)
+<<setup_child, child='EconGrowth-R-Functions.Rnw', echo=FALSE, message=FALSE, eval=TRUE>>=
+# Includes the Functions.Rnw file that contains all of the functions for analyzing our economic data.
 opts_chunk$set(
   # ********************************************************************************************************
-  eval=FALSE,
+  eval=TRUE,
   # ********************************************************************************************************
   warning=TRUE,  #Tells whether to show warnings in the output.
-  dev='tikz',    #Allows LaTeX code in graphical output. E.g., "$y$" for a variable name in the legend for a graph.
-  tidy=FALSE,
-  comment=NA,
-  #Tells whether to cache output from chunks are saved. Cacheing saves time. 
-  #However, references to LaTeX tables DO NOT WORK if cacheing is turned on (cache=TRUE).
-  cache=FALSE,
-  echo=FALSE,    #Tells whether to echo code for all chunks. Set TRUE on an individual chunk to see its code.
-  message=FALSE) #Turns off messages for all chunks. Set TRUE on an individual chunk to see it.
-
-# Statistical significance levels. We'll work with 95% CIs
-ciLevel <- 0.95
-ciHalfLevel <- ciLevel + (1.0-ciLevel)/2.0
-# List of countries
-countryAbbrevs <- c(US="US", UK="UK", JP="JP", CN="CN", ZA="ZA", SA="SA", IR="IR", TZ="TZ", ZM="ZM")
-countryAbbrevsU <- c(US="US", UK="UK", JP="JP") #Only these countries have useful work data
-countryNamesAlph <- c(CN="China", IR="Iran", JP="Japan", SA="Saudi Arabia", TZ="Tanzania", UK="United Kingdom", US="USA", ZA="South Africa", ZM="Zambia") #In alphabetical order.
-energyTypes <- c(Q="Q", X="X", U="U") # List of energy types
-factors <- c(K="K", L="L", Q="Q", X="X", U="U") # List of factors of production
-########### Several global parameters for graphs. Set here and use below to ensure consistent appearance of graphs.
-# Set the order for presenting countries in 3x3 lattice graphs. Default is alphabetical. 
-# "1" means first alphabetically.
-countryOrderForGraphs <- c(7,6,3,1,8,5,4,2,9) # Sets the order as US, UK, JP, CN, ZA, TZ, SA, IR, ZM.
-maxWidth <- 6.5 #Inches
-# Full page lattice plot sizes
-ninePanelLayoutSpec <- c(3,3) #indicates a 3x3 arrangement of panels.
-ninePanelGraphWidth <- maxWidth     
-ninePanelGraphHeight <- 7.5  #Inches
-keyTextSize <- 0.85 #85% of normal size
-keyColumns <- 1 #Want only 1 column in the key for lattice graphs
-keyXLoc <- 0.01 #x position of the key
-keyYLoc <- 0.95 #y position of the key
-# Parameter graphs are tricky to ensure same size. I've found that with height set to 5 in for the 
-# cd graphs and 2.93 in for the sf graphs, I get a nearly-exact match with graph size. From these settings I 
-# can set up 2 equations:
-#    5 in = 2*hgraph + haxis
-#    2.93 in = hgraph + haxis
-# to estimate that h_axis = 0.86 in and hgraph = 2.05 in.
-h_param_graph <- 2.07 # Inches for a single panel
-h_param_axis <- 0.86 # Inches (also includes whatever margin is applied)
-sfParameterGraphHeight <- h_param_graph + h_param_axis
-cdParameterGraphHeight <- 2*h_param_graph + h_param_axis
-cesParameterGraphHeight <- 3*h_param_graph + h_param_axis
-linexParameterGraphHeight <- h_param_graph + h_param_axis
-sfParameterGraphWidth <- maxWidth
-cdParameterGraphWidth <- maxWidth
-cesParameterGraphWidth <- maxWidth
-linexParameterGraphWidth <- maxWidth
-# Other graph parameters that apply to all graphs
-scaleTextSize <- 1.0  #Multiple of normal size
-scaleTickSize <- -0.5 #50% of normal size and pointing INWARD!
-@
-
-<<Data Functions, eval=TRUE>>=
-#################################
-# This function loads data given a country abbreviation.
-# The file name from which data will be loaded is assumed to be of the form 
-# "<countryAbbrev>Data.txt". The file is assumed to exist in a subfolder of this project called "data".
-#
-# countryAbbrev is a string containing the 2-letter abbreviation for the country, e.g. "US" or "CN"
-#
-# returns a data.frame with the data that has been loaded
-##
-loadData <- function(countryAbbrev){
-  # Read the data file as a table with a header.  
-  fileName <- paste("data/", countryAbbrev, "Data.txt", sep="")
-  dataTable <- read.table(fileName, header = TRUE)
-  return(dataTable)
-}
-
-###############################
-# Tells whether we have data for this combination of country and energy type for a single-factor curve fit.
-#
-# returns logical value (TRUE or FALSE)
-##
-haveDataSF <- function(countryAbbrev, factor){
-  # The design here is to go through several cases where data is unavailable and
-  # return FALSE. If we make it through all of those cases, we'll return TRUE.
-  if (!(countryAbbrev %in% countryAbbrevs)){
-    # If we don't know the country, we don't have data
-    return(FALSE)
-  }
-  if (missing(factor) || is.na(factor)){
-    # If we don't have a factor, we don't have data.
-    return(FALSE)
-  }
-  if (!(factor %in% factors)){
-    # If we don't know the factor, we don't have data
-    return(FALSE)
-  }
-  if (factor == "U" && (!(countryAbbrev %in% countryAbbrevsU))){
-    # We have U data for only a few countries.
-    return(FALSE)
-  }
-  return(TRUE)
-}
-
-###############################
-# Tells whether we have data for this combination of country and energy type for a Cobb-Douglas curve fit.
-# a missing energyType or energyType == NA means that we want to develop a model without energy, if possible.
-#
-# returns logical value (TRUE or FALSE)
-##
-haveDataCD <- function(countryAbbrev, energyType){
-  # The design here is to go through several cases where data is unavailable and
-  # return FALSE. If we make it through all of those cases, we'll return TRUE.
-  if (!(countryAbbrev %in% countryAbbrevs)){
-    # If we don't know the country, we don't have data
-    return(FALSE)
-  }
-  if (missing(energyType) || is.na(energyType)){
-    # If we don't want energy included, we have data for all known countries. We need to check this case
-    # first, BEFORE doing various checks on the energyType.
-    return(TRUE)
-  }
-  if (!(energyType %in% energyTypes)){
-    # If we want to include energy, we know only a few types. So, return false if we don't know the energy type.
-    return(FALSE)
-  }
-  if (energyType == "U" && (!(countryAbbrev %in% countryAbbrevsU))){
-    # We have U data for only a few countries.
-    return(FALSE)
-  }
-  return(TRUE)
-}
-
-#####################
-# This function adds NA rows to the end of a data.frame to ensure that the df is 
-# the same length as the country data set
-# returns a modified version of df that includes the padded rows filled with "NA".
-##
-padRows <- function(countryAbbrev, df){
-  nRowsData <- nrow(loadData(countryAbbrev)) #Gets number of rows in data set
-  nRowsDF <- nrow(df)
-  nRowsToAdd <- nRowsData - nRowsDF
-  nCol <- ncol(df)
-  dfToAppend <- as.data.frame(matrix(NA, ncol=nCol, nrow=nRowsToAdd))
-  colnames(dfToAppend) <- colnames(df)
-  return(rbind(df, dfToAppend))
-}
-
-##############################
-# Returns an integer representing the column index for some data
-# dataTable the data.frame in which you want to change column names
-# factor should be a string and one of Year, Y, K, L, Q, X, or U
-##
-columnIndex <- function(dataTable, factor){
-  if (factor == "Year"){
-    colName <- "iYear"
-  } else if (factor == "Y"){
-    colName <- "iGDP"
-  } else if (factor == "K"){
-    colName <- "iCapStk"
-  } else if (factor == "L"){
-    colName <- "iLabor"
-  } else if (factor == "Q"){
-    colName <- "iQ"
-  } else if (factor == "X"){
-    colName <- "iX"
-  } else if (factor == "U"){
-    colName <- "iU"
-  } else {
-    print(paste("Unknown factor:", factor, "in colIndex. Terminating execution."))
-    quit()
-  }
-  # Get the desired column index.
-  colIndex <- which(names(dataTable) %in% colName) #Find index of desired column
-  return(colIndex)  
-}
-
-##############################
-# Replaces a column name with the given string
-# dataTable the data.frame that you're working with
-# factor should be a string and one of Year, Y, K, L, Q, X, or U
-# newName should be a string and the desired new name of the column
-# returns dataTable with a new name for one of its factor column.
-##
-replaceColName <- function(dataTable, factor, newName){
-  colIndex <- columnIndex(dataTable, factor)
-  colnames(dataTable)[colIndex] <- newName #Change desired column name to newName
-  return(dataTable)
-}
-
-##############################
-# Returns an xtable of covariance information for the specified country.
-##
-covarianceTable <- function(countryAbbrev){
-  data <- loadData(countryAbbrev)
-  # Grab only the data we want.
-  dataForCovar <- cbind(data$iGDP, data$iCapStk, data$iLabor, data$iQ, data$iX)
-  names <- c("$y$", "$k$", "$l$", "$q$", "$x$")
-  if (countryAbbrev %in% countryAbbrevsU){
-    # Add U data only if we have it.
-    dataForCovar <- cbind(dataForCovar, data$iU)
-    names <- c("$y$", "$k$", "$l$", "$q$", "$x$", "$u$")
-  }
-  covarResults <- cor(dataForCovar)
-  colnames(covarResults) <- names
-  rownames(covarResults) <- names
-  covarXtable <- xtable(covarResults, 
-                      caption=paste(countryAbbrev, "covariance table."), 
-                      label=paste("tab:Covariance_", countryAbbrev, sep=""))
-  return(covarXtable)
-}
-
-###############################
-# Prints a covariance table for countryAbbrev
-##
-printCovarTable <- function(countryAbbrev){
-  print(covarianceTable(countryAbbrev), 
-                      caption.placement="top", 
-                      sanitize.rownames.function = identity,
-                      sanitize.colnames.function = identity,
-                      size="\\tiny",
-                      table.placement="H")
-}
-
-####################################
-# Creates a graph that displays all of the factors of production for all countries.
-##
-createHistoricalLatticeGraph <- function(){
-  dataTable <- loadData("All")
-  graphType <- "b" #b is for both line and symbol
-  lineTypes <- c(0, 1, 5, 2, 4, 1) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
-  lineWidths <- c(0, 2, 2, 1, 1, 1) #line widths. 0 means no line.
-  colors <- c("black", "black", "black", "red", "blue", "darkorange") #line and symbol colors
-  symbols <- c(1, NA, NA, NA, NA, NA)  #NA gives no symbol.
-  graph <- xyplot(iGDP+iCapStk+iLabor+iQ+iX+iU ~ Year | Country, data=dataTable,
-                  type = graphType,
-                  index.cond = list(countryOrderForGraphs), #orders the panels.
-                  layout = ninePanelLayoutSpec, 
-                  strip = strip.custom(factor.levels=countryNamesAlph, bg="white"), #Sets strip parameters
-                  as.table = TRUE, #indexing of panels starts in upper left and goes across rows.
-                  lty = lineTypes, lwd = lineWidths, col = colors, #Controls line parameters
-                  pch = symbols, col.symbol = colors, #Controls symbol parameters
-                  key=list(text=list(c("$y$", "$k$", "$l$", "$q$", "$x$", "$u$")),
-                           type=graphType,
-                           cex=keyTextSize, #controls size of text in the key
-                           lines=list(lty=lineTypes, lwd=lineWidths), #controls line types
-                           pch=symbols, col=colors, #controls symbol (plot characters) types
-                           columns=keyColumns, x=keyXLoc, y=keyYLoc), #controls columns and position of the key
-                  scales=list(cex=scaleTextSize, #controls text size on scales.
-                              tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
-                              y=list(relation="free", #allows each axis to be different
-                                     at=c(1,2,3,4,5,6,7,8,9,10) #tick mark locations
+  message=FALSE, #Turns off messages for all chunks. Set TRUE on an individual chunk to see it.
+  echo=FALSE     #Tells whether to echo code for all chunks. Set TRUE on an individual chunk to see its code.
 ) 
-                              ),
-                  ylim=list(c(1,10), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4)), #y axis limits
-                  xlab="", ylab="Indexed (1980=1 or 1991=1)") #axis labels
-  return(graph)
-}
-@
+@
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Introduction}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+*********** Caleb, put your LaTeX code here. *************
 
@@
 
-<<single-factor functions, eval=TRUE>>=
-####################
-# Returns an nls single-factor model for the country and factor specified.
-# factor should be one of "K", "L", "Q", "X", or "U".
-##
-singleFactorModel <- function(countryAbbrev, factor){
-  dataTable <- loadData(countryAbbrev) #Load the data that we need.
-  # We'll change the name of the desired column to "f"
-  dataTable <- replaceColName(dataTable, factor, "f")
-  # Now do the fit.
-  lambdaGuess <- 0.0 #guessing lambda = 0 means there is no technological progress.
-  # Some economies need different guesses
-  if (countryAbbrev == "IR" && factor == "X"){
-    mGuess <- 0.7
-  } else {
-    # This works for every other combination of country and factor.
-    mGuess <- 0.5
-  }
-  start <- list(lambda=lambdaGuess, m=mGuess)
-  # Runs a non-linear least squares fit to the data. We've replaced beta with 1-alpha for simplicity.
-  model <- iGDP ~ exp(lambda*iYear) * f^m
-  modelSF <- nls(formula=model, data=dataTable, start = start)
-#   model <- iGDP ~ exp(lambda*iYear) * f^m
-#   modelSF <- wrapnls(formula=model, data=dataTable, start=list(lambda=lambdaGuess, m=mGuess))
-  return(modelSF)
-}
-
-#########################
-# Takes the single-factor fitted models and creates per-country predictions for them.
-# Returns a data.frame with the predictions.
-##
-singleFactorPredictions <- function(countryAbbrev, factor){
-  # Can't make predictions for any of CN, ZA, SA, IR, TZ, or ZM if we're interested in U
-  if (!(haveDataSF(countryAbbrev, factor))){
-    #If we don't have data for this combination of countryAbbrev and energyType, 
-    # return a column of NAs if the above conditions have been met.
-    nRows <- 21 # All of these countries need 21 rows.
-    df <- as.data.frame(matrix(NA, ncol = 1, nrow = nRows))
-    colnames(df) <- "pred"
-    return(df)
-  }
-  model <- singleFactorModel(countryAbbrev, factor)
-  pred <- predict(model) #See http://stackoverflow.com/questions/9918807/how-get-plot-from-nls-in-r
-  df <- data.frame(pred)
-  # Pad with rows as necessary
-  df <- padRows(countryAbbrev, df)
-  return(df)
-}
-
-#########################
-# Takes the single-factor fitted models and creates a single column of predicted GDP values
-# that corresponds, row for row, with the AllData.txt file.
-##
-singleFactorPredictionsColumn <- function(factor){
-  out <- do.call("rbind", lapply(countryAbbrevs, singleFactorPredictions, factor=factor))
-  colnames(out) <- c(paste("predGDP", factor, sep=""))
-  return(out)
-}
-
-##############################
-# Creates a graph that plots predicted GDP as lines, one for each single factor, and historical GDP 
-# data as open circles.
-##
-createSFLatticeGraph <- function(){
-  dataTable <- loadData("All") #Grab the raw data
-  predictionsK <- singleFactorPredictionsColumn("K") #Predictions from SF with K
-  predictionsL <- singleFactorPredictionsColumn("L") #Predictions from SF with L
-  predictionsQ <- singleFactorPredictionsColumn("Q") #Predictions from SF with Q
-  predictionsX <- singleFactorPredictionsColumn("X") #Predictions from SF with X
-  predictionsU <- singleFactorPredictionsColumn("U") #Predictions from SF with U
-  #Now add the predictions columns to the data.
-  dataTable <- cbind(dataTable, predictionsK, predictionsL, predictionsQ, predictionsX, predictionsU) 
-  graphType <- "b" #b is for both line and symbol
-  lineTypes <- c(0, 1, 5, 2, 4, 1) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
-  lineWidths <- c(0, 2, 2, 1, 1, 1) #line widths. 0 means no line.
-  colors <- c("black", "black", "black", "red", "blue", "darkorange") #line and symbol colors
-  symbols <- c(1, NA, NA, NA, NA, NA)  #NA gives no symbol.
-  graph <- xyplot(iGDP+predGDPK+predGDPL+predGDPQ+predGDPX+predGDPU ~ Year | Country, data=dataTable,
-                  type=graphType,
-                  index.cond=list(countryOrderForGraphs), #orders the panels.
-                  layout=ninePanelLayoutSpec, #indicates a 3x3 arrangement of panels.
-                  strip = strip.custom(factor.levels=countryNamesAlph, bg="white"), #Sets strip parameters
-                  as.table=TRUE, #indexing of panels starts in upper left and goes across rows.
-                  lty = lineTypes, lwd = lineWidths, col = colors, #Controls line parameters
-                  pch = symbols, col.symbol = colors, #Controls symbol parameters
-                  key=list(text=list(c("Actual", "With $k$", "With $l$", "With $q$", "With $x$", "With $u$")),
-                           type=graphType,
-                           cex=keyTextSize, #controls size of text in the key
-                           lines=list(lty=lineTypes, lwd=lineWidths), #controls line types
-                           pch=symbols, col=colors, #controls symbol (plot characters) types
-                           columns=keyColumns, x=keyXLoc, y=keyYLoc), #controls columns and position of the key
-                  scales=list(cex=scaleTextSize, #controls text size on scales.
-                              tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
-                              y=list(relation="free", #allows each axis to be different
-                                     at=c(1,2,3,4,5,6,7,8,9,10) #tick mark locations
-                                     )
-                              ), 
-                  ylim=list(c(1,8), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3)),
-                  xlab="", ylab="Indexed GDP (1980=1 or 1991=1)") #axis labels
-  return(graph)
-}
-
-#################################################
-# Calculates parameter estimates and confidence intervals
-# for the single factor production function for a given a country.
-#
-# countryAbbrev is a string containing the 2-letter abbreviation for the country, e.g. "US" or "CN"
-# factor is a string, one of "K", "L", "Q", "X", or "U"
-#
-# returns a data.frame of data for the Cobb-Douglas model. 
-# First row is the +95% CI on all parameters
-# Second row contains the parameter estimates
-# Third row is the -95% CI on all parameters
-# Each column has names: lambda and m corresponding to the parameters in the model.
-##
-singleFactorData <- function(countryAbbrev, factor){
-  #First, check to see if we want useful work (U) AND one of the countries for which we don't have data.
-  if (!haveDataSF(countryAbbrev, factor)){
-    #Return a column of NAs if we don't have data for this factor
-    nRows <- 3 # +95% CI, SF, and -95% CI.
-    nCols <- 2 # lambda, m
-    df <- as.data.frame(matrix(NA, ncol = nCols, nrow = nRows))
-    colnames(df) <- c("lambda", "m")
-    rownames(df) <- c("+95% CI", "SF", "-95% CI")
-    return(df)
-  }
-  # We have a combination of country and factor for which we have data.
-  modelSF <- singleFactorModel(countryAbbrev, factor)
-  summarySF <- summary(modelSF) # Gives the nls summary table.
-  ciSF <- confint(modelSF, level = ciLevel)  # Calculates confidence intervals for the SF model.
-  dofSF <- summarySF$df[2] # Gives the degrees of freedom for the model.
-  tvalSF <- qt(ciHalfLevel, df = dofSF)
-  #Single factor model
-  lambda <- as.numeric(coef(modelSF)["lambda"])
-  m <- as.numeric(coef(modelSF)["m"])
-  # Combine all estimates and their confidence intervals into data frames with intelligent row names
-  estSF <- data.frame(lambda = lambda, m = m)
-  row.names(estSF) <- "SF"
-  # The [1] subscripts pick off the lower confidence interval
-  lowerSF <- data.frame(lambda=ciSF["lambda","2.5%"], 
-                        m=ciSF["m", "2.5%"])
-  row.names(lowerSF) <- "-95% CI"
-  # The [2] subscripts pick off the upper confidence interval
-  upperSF <- data.frame(lambda=ciSF["lambda","97.5%"], 
-                        m=ciSF["m", "97.5%"])
-  row.names(upperSF) <- "+95% CI"
-  # Now create the data for a table and return it
-  dataSF <- rbind(upperSF, estSF, lowerSF)
-  return(dataSF)
-}
-
-############
-# Creates a row for the single factor parameters table for the given country (2-letter code) and factor.
-##
-singleFactorCountryRow <- function(countryAbbrev, factor){
- dataSF <- singleFactorData(countryAbbrev, factor)
- out <- cbind(dataSF["-95% CI", "lambda"], dataSF["SF", "lambda"], dataSF["+95% CI", "lambda"],
-              dataSF["-95% CI", "m"],  dataSF["SF", "m"],  dataSF["+95% CI", "m"])
- return(out)
-}
-
-############################
-# Aggregates the single-factor results into a big data table for the given factor.
-##
-singleFactorParamsTable <- function(factor){
-  #Do rbind on the results of creating a row in the table for every country abbreviation that we know.
-  dataSF <- do.call("rbind", lapply(countryAbbrevs, singleFactorCountryRow, factor=factor))
-  if (factor == "K"){
-    factorString <- "$\\alpha$"
-  } else if (factor == "L"){
-    factorString <- "$\\beta$"
-  } else {
-    factorString <- "$\\gamma$"
-  }
-  colnames(dataSF) <- c(" ", "$\\lambda$", " ", 
-                        " ", factorString,  " ")
-  rownames(dataSF) <- countryAbbrevs
-  tableSF <- xtable(dataSF, 
-                    caption=paste("Single-factor model (with $", tolower(factor), "$) parameters for 1980-2011 (US, UK, JP), 1991-2010 (CN and ZA), and 1991-2011 (SA, IR, TZ, and ZM).
-(Parameter estimates beneath symbol.
-95\\% confidence interval bounds to left and right.)", sep=""),
-                    label=paste("tab:SF_Parameters_With_", factor, sep=""),
-                    digits = c(1, 4,4,4, 2,2,2),
-                    align = "r|ccc|ccc") #Sets alignment of the numbers in the columns
-  return(tableSF)
-}
-
-###########################################
-# Creates a number of rows in a data.frame that contain information 
-# about the coefficients of a single factor model for countryAbbrev.
-# Each parameter has its own row with confidence intervals.
-# The country name is in a column. Which parameter is involved is
-# also in a column.
-# 
-# The return type is a data.frame.
-##
-singleFactorCountryRowsForParamsGraph <- function(countryAbbrev, factor){
-  #Create three rows, one for each parameter. Each row is a data.frame so that it is plottable!
-  dataSF <- singleFactorData(countryAbbrev, factor)
-  valueRow <- "SF"
-  # Create rows for each parameter
-  lambdaRow <- data.frame(country = countryAbbrev, 
-                          parameter = "lambda", 
-                          lowerCI = dataSF["-95% CI", "lambda"], 
-                          value = dataSF[valueRow, "lambda"], 
-                          upperCI = dataSF["+95% CI", "lambda"])
-  mRow <- data.frame(country = countryAbbrev, 
-                     parameter = "m",
-                     lowerCI = dataSF["-95% CI", "m"],
-                     value = dataSF[valueRow, "m"],  
-                     upperCI = dataSF["+95% CI", "m"])
-  table <- rbind(lambdaRow, mRow)
-  return(table)
-}
-
-###############################
-# Prints a covariance table for the given factor of production
-##
-printSFParamsTable <- function(factor){
-  print(singleFactorParamsTable(factor),
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny", 
-      table.placement="H")
-}
-
-#############################
-# Creates a graph with confidene intervals for the single-factor model for the given factor
-##
-createSFParamsGraph <- function(factor){
-  # Set the name of the 2nd graph (m)
-  factorLabel <- paste("$", tolower(factor), "$", sep="")
-  # Create a data table with the following columns:
-  # country abbrev, parameter (lambda or m), -95% CI, value, +95% CI
-  dataTable <- do.call("rbind", lapply(countryAbbrevs, singleFactorCountryRowsForParamsGraph, factor=factor))
-  graph <- segplot(country ~ upperCI + lowerCI | parameter, 
-                   data = dataTable,
-                   centers = value, #identifies where the dots should be placed
-                   draw.bands = FALSE, #provides nicer error bars
-                   horizontal = FALSE, #makes error bars vertical and puts the countries in the x axis
-                   layout = c(2,1), #2 column, 1 row
-                   col = "black", #Sets line color to black
-                   lwd = 1, #Sets line width to 1.0
-                   strip = strip.custom(bg="white", factor.levels=c("$\\lambda$", factorLabel)),
-                   ylim = list(c(-0.05, 0.1), c(-0.5, 1.5)), #y axis limits
-                   scales = list(cex=scaleTextSize, #controls text size on scales.
-                                 tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
-                                 x=list(cex=0.75), #reduces text size so that country abbrevs are legible
-                                 y=list(relation="free", #allow each axis to be different
-                                        at=list(c(0.0, 0.05, 0.1),   #y tick mark for lambda
-                                                c(0.0, 0.5, 1.0)
-                                                )
-                                        )
-                                 )
-                   )
-
-  return(graph)
-}
-@
-
 We begin by fitting single-factor economic models of the form
@@
 
-<<cobb-douglas functions, eval=TRUE>>=
-####################
-# Returns an nls Cobb-Douglas model for the country specified
-# Give an energyType ("Q", "X", or "U") if you want to include an energy term
-# by including the gamma parameter, a fit with fixed gamma will be provided.
-##
-cobbDouglasModel <- function(countryAbbrev, energyType, gamma){
-  dataTable <- loadData(countryAbbrev) #Load the data that we need.
-  #Run the non-linear least squares fit to the data based on whether we have an energy type or not.
-  if (missing(energyType)){
-    # No energy term desired in the Cobb-Douglas equation.
-    # Establish guess values for alpha and lambda.
-    lambdaGuess <- 0.0 #guessing lambda = 0 means there is no technological progress.
-    alphaGuess <- 0.7 #0.7 gives good results for all countries.  
-    start <- list(lambda=lambdaGuess, alpha=alphaGuess)
-    # Runs a non-linear least squares fit to the data. We've replaced beta with 1-alpha for simplicity.
-    model <- iGDP ~ exp(lambda*iYear) * iCapStk^alpha * iLabor^(1 - alpha)
-    modelCD <- nls(formula=model, data=dataTable, start = start,
-                   #Include the next 3 lines to fit with constraints.
-                   #algorithm = "port",
-                   #lower = list(lambda=-Inf, alpha=0),
-                   #upper = list(lambda=Inf, alpha=1)
-                   )
-    return(modelCD)
-  } else {
-    # We need to do the Cobb-Douglas fit with the desired energy data.
-    # To achieve the correct fit, we'll change the name of the desired column
-    # to "iEToFit" and use "iEToFit" in the nls function. 
-    dataTable <- replaceColName(dataTable, energyType, "iEToFit")
-    # Reparameterize to ensure that we meet the constraints:
-    # * alpha + beta + gamma = 1.0.
-    # * alpha, beta, and gamma are all between 0.0 and 1.0.
-    # To do this, we reparameterize as
-    # * 0 < a < 1
-    # * 0 < b < 1
-    # * alpha = min(a, b)
-    # * beta = b - a
-    # * gamma = 1 - max(a, b)
-    # Establish guess values for lambda, alpha, and beta.
-    lambdaGuess <- 0.0 #guessing lambda = 0 means there is no technological progress.
-    alphaGuess <- 0.9
-    betaGuess <- 1.0 - alphaGuess
-    if (countryAbbrev == "ZA"){
-      # South Africa doesn't converge using the default guess values above. Try different values.
-      gammaGuess <- 0.65 # Found via grid search over gamma
-      alphaGuess <- 0.597 # The alpha value when energy is not included
-      betaGuess <- 1.0 - alphaGuess - gammaGuess
-#       alphaGuess <- 0.4
-#       gammaGuess <- 0.1
-#       betaGuess <- 1.0 - alphaGuess - gammaGuess
-#       alphaGuess <- 0.39
-#       betaGuess <- 0.41
-    }
-    aGuess <- alphaGuess
-    bGuess <- alphaGuess + betaGuess
-    start <- list(lambda=lambdaGuess, a=aGuess, b=bGuess)
-    # Now actually do the fit, using the column name "iEToFit".
-    if (missing(gamma)){
-      # gamma is a free parameter. We need to estimate lambda, a, and b.
-      model <- iGDP ~ exp(lambda*iYear) * iCapStk^min(a,b) * iLabor^abs(b-a) * iEToFit^(1.0 - max(a,b))
-      modelCDe <- nls(formula=model, data = dataTable, start = start,
-                      control = nls.control(maxiter = 200, 
-                                            tol = 1e-05, 
-                                            minFactor = 1/1024, 
-                                            printEval=FALSE, #Tells whether to print details of curve fit process.
-                                            warnOnly=TRUE),
-                      #Include the next 3 lines to fit with constraints.
-                      #algorithm = "port",
-                      #lower = list(lambda=-Inf, a=0, b=0),
-                      #upper = list(lambda= Inf, a=1, b=1)
-                      )
-    } else {
-      # We don't want to estimate the value of gamma
-      # Calculate a new column iEGamma = iEToFit^gamma
-      iEGamma <- with(dataTable, iEToFit^gamma)
-      dataTable <- cbind(dataTable, iEGamma)
-      # We already know the value of gamma. We don't want to estimate it.
-      # Establish guess values for lambda and alpha.
-      lambdaGuess <- 0.0 #guessing lambda = 0 means there is no technological progress.
-      alphaGuess <- 0.7*(1-gamma) #ensure a consistent starting point.
-      start <- list(lambda=lambdaGuess, alpha=alphaGuess)
-      model <- iGDP ~ exp(lambda*iYear) * iCapStk^alpha * iLabor^((1-gamma) - alpha) * iEGamma
-      modelCDe <- nls(formula=model, data = dataTable, start = start,
-                      control = nls.control(maxiter = 200, 
-                                            tol = 1e-05, 
-                                            minFactor = 1/1024, 
-                                            printEval=FALSE, #Tells whether to print details of curve fit process.
-                                            warnOnly=TRUE),
-                      #Include the next 3 lines to fit with constraints.
-                      algorithm = "port",
-                      lower = list(lambda=-Inf, alpha=0),
-                      upper = list(lambda=Inf, alpha=1.0-gamma)
-                      )
-    }
-# print(summary(modelCDe))
-    return(modelCDe)
-  }
-}
-
-###############################
-# Does a grid search over values of gamma for a CD production function
-##
-cdGrid <- function(countryAbbrev, energyType, gammaGrid){
-  gamma <- gammaGrid
-  models <- lapply(gamma, cobbDouglasModel, energyType=energyType, countryAbbrev=countryAbbrev)
-  return(models)
-}
-
-gammaGrid <- seq(0.0, 0.95, by=0.05)
-# print("US")
-# models <- cdGrid("US", "Q", gammaGrid)
-# SSE <- lapply(models, function(model) summary(model)$sigma)
-# data <- cbind(gammaGrid, SSE)
-# plot(gammaGrid, SSE)
-# print(coef(models[[2]]))
-# 
-print("ZA")
-models <- cdGrid("ZA", "Q", gammaGrid)
-SSE <- lapply(models, function(model) summary(model)$sigma)
-lambda <- lapply(models, function(model) coef(model)["lambda"])
-alpha <- lapply(models, function(model) coef(model)["alpha"])
-data <- cbind(lambda, alpha, gammaGrid, SSE)
-print(data)
-plot(gammaGrid, SSE)
-plot(gammaGrid, lambda)
-plot(gammaGrid, alpha)
-
-# Some code to debug the Cobb-Douglas models. Randy Pruim is helping on this.
-
-# print("cobbDouglasModel(US, Q) works fine:")
-# us <- cobbDouglasModel("US", "Q")
-# print(summary(us))
-# print(confint(us))
-# 
-# print("cobbDouglasModel(ZA) works fine")
-# za <- cobbDouglasModel("ZA")
-# print(summary(za))
-# print(confint(za))
-# 
-# print("cobbDouglasModel(ZA, Q) stops before convergence achieved,")
-# print("and confint gives NA values:")
-# za <- cobbDouglasModel("ZA", "Q")
-# print(summary(za))
-# print(confint(za))
-# 
-# print("cobbDouglasModel(UK, Q) also stops before convergence achieved,")
-# print("but confint does not produce NA values:")
-# uk <- cobbDouglasModel("UK", "Q")
-# print(summary(uk))
-# print(confint(uk))
-
-# save(us, za, uk, file="HeunModels-US-ZA-UK.Rdata")
-
-#########################
-# Takes the Cobb-Douglas fitted models and creates per-country predictions for them.
-# Returns a data.frame with the predictions.
-##
-cobbDouglasPredictions <- function(countryAbbrev, energyType){
-  # Can't make predictions for any of CN, ZA, SA, IR, TZ, or ZM if we're interested in U
-  if (!missing(energyType)){
-    # Consider this replacement only if energyType has been specified.
-    if (!(haveDataCD(countryAbbrev, energyType))){
-      # If we don't have data for this combination of countryAbbrev and energyType, 
-      # return a column of NAs when the above conditions have been met.
-      nRows <- 21 # All of these countries need 21 rows.
-      df <- as.data.frame(matrix(NA, ncol = 1, nrow = nRows))
-      colnames(df) <- "pred"
-      return(df)
-    }
-  }
-  model <- cobbDouglasModel(countryAbbrev, energyType)
-  pred <- predict(model) #See http://stackoverflow.com/questions/9918807/how-get-plot-from-nls-in-r
-  df <- data.frame(pred)
-  # Pad with rows as necessary
-  df <- padRows(countryAbbrev, df)
-  return(df)
-}
-
-#########################
-# Takes the Cobb-Douglas fitted models and creates a single column of predicted GDP values
-# that corresponds, row for row, with the AllData.txt file.
-##
-cobbDouglasPredictionsColumn <- function(energyType){
-  if (missing(energyType)){
-    out <- do.call("rbind", lapply(countryAbbrevs, cobbDouglasPredictions)) #rbinds all the predictions together
-    colnames(out) <- c("predGDP")
-  } else {
-    out <- do.call("rbind", lapply(countryAbbrevs, cobbDouglasPredictions, energyType=energyType))
-    colnames(out) <- c(paste("predGDP", energyType, sep=""))
-  }
-  return(out)
-}
-
-#################################################
-# Calculates parameter estimates and confidence intervals
-# for the Cobb-Douglas production function given a country.
-#
-# countryAbbrev is a string containing the 2-letter abbreviation for the country, e.g. "US" or "CN"
-# energyType is a string, one of "Q", "X", or "U"
-#
-# returns a data.frame of data for the Cobb-Douglas model. 
-# First row is the +95% CI on all parameters
-# Second row contains the parameter estimates
-# Third row is the -95% CI on all parameters
-# Each column has names: lambda, alpha, beta, gamma, corresponding to the parameters in the model.
-##
-cobbDouglasData <- function(countryAbbrev, energyType){
-  #First, check to see if we want useful work (U) AND one of the countries for which we don't have data.
-  if (!haveDataCD(countryAbbrev, energyType)){
-    #Return a column of NAs if the above conditions have been met.
-    nRows <- 3 # +95% CI, CDe, and -95% CI.
-    nCols <- 4 # lambda, alpha, beta, and gamma
-    df <- as.data.frame(matrix(NA, ncol = nCols, nrow = nRows))
-    colnames(df) <- c("lambda", "alpha", "beta", "gamma")
-    rownames(df) <- c("+95% CI", "CDe", "-95% CI")
-    return(df)
-  }
-  # We have a combination of country and energy type for which we have data.
-  modelCD <- cobbDouglasModel(countryAbbrev, energyType)
-  summaryCD <- summary(modelCD) # Gives the nls summary table.
-  ciCD <- confint(modelCD, level = ciLevel)  # Calculates confidence intervals for the CD model.
-  dofCD <- summaryCD$df[2] # Gives the degrees of freedom for the model.
-  tvalCD <- qt(ciHalfLevel, df = dofCD)
-  if (missing(energyType)){
-    #Cobb-Douglas without energy
-    alpha <- as.numeric(coef(modelCD)["alpha"])
-    beta <- 1.0 - alpha
-    beta.est <- deltaMethod(modelCD, "1 - alpha") # Estimates beta and its standard error (SE).
-    # Calculate beta and its confidence interval and report it.
-    # Now calculate a confidence interval on beta
-    betaCICD <- with(beta.est, Estimate + c(-1.0, 1.0) * tvalCD * SE); betaCICD # Gives the confidence interval on beta.  
-    # Combine all estimates and their confidence intervals into data frames with intelligent row names
-    estCD <- data.frame(lambda=coef(modelCD)["lambda"], alpha=coef(modelCD)["alpha"], beta=beta, gamma=0)
-    row.names(estCD) <- "CD"
-    # The [1] subscripts pick off the lower confidence interval
-    lowerCD <- data.frame(lambda=ciCD["lambda","2.5%"], alpha=ciCD["alpha", "2.5%"], beta=betaCICD[1], gamma=NA) 
-    row.names(lowerCD) <- "-95% CI"
-    # The [2] subscripts pick off the lower confidence interval
-    upperCD <- data.frame(lambda=ciCD["lambda","97.5%"], alpha=ciCD["alpha", "97.5%"], beta=betaCICD[2], gamma=NA)
-    row.names(upperCD) <- "+95% CI"
-  } else {
-    #Cobb-Douglas with energy
-    a <- as.numeric(coef(modelCD)["a"])
-    b <- as.numeric(coef(modelCD)["b"])
-    lambda <- as.numeric(coef(modelCD)["lambda"])
-    alpha <- a
-    beta <- b - a
-    gamma <- 1.0 - b
-    # Report results with SE
-    beta.est <- deltaMethod(modelCD, "b-a") # Reports results for beta, because beta = b - a.
-    gamma.est <- deltaMethod(modelCD, "1-b") # Reports results for gamma, because gamma = 1 - b.
-    # Now calculate confidence intervals.
-    betaCICD <- with(beta.est, Estimate + c(-1.0, 1.0) * tvalCD * SE) # Gives the confidence interval on beta.
-    gammaCICD <- with(gamma.est, Estimate + c(-1.0, 1.0) * tvalCD * SE) # Gives the confidence interval on gamma.
-    # Combine all estimates and their confidence intervals into data frames with intelligent row names
-    estCD <- data.frame(lambda = lambda, alpha = alpha, beta = beta, gamma = gamma)
-    row.names(estCD) <- "CDe"
-    # The [1] subscripts pick off the lower confidence interval
-    lowerCD <- data.frame(lambda=ciCD["lambda","2.5%"], 
-                          alpha=ciCD["a", "2.5%"], 
-                          beta=betaCICD[1], 
-                          gamma=gammaCICD[1])
-    row.names(lowerCD) <- "-95% CI"
-    # The [2] subscripts pick off the upper confidence interval
-    upperCD <- data.frame(lambda=ciCD["lambda","97.5%"], 
-                          alpha=ciCD["a", "97.5%"], 
-                          beta=betaCICD[2], 
-                          gamma=gammaCICD[2])
-    row.names(upperCD) <- "+95% CI"
-  }
-  # Now create the data for a table and return it
-  dataCD <- rbind(upperCD, estCD, lowerCD)
-  return(dataCD)
-}
-
-############
-# Creates a row for the Cobb Douglas parameters table for the given country (2-letter code) and energyType (Q, X, or U)
-##
-cobbDouglasCountryRow <- function(countryAbbrev, energyType){
-  dataCD <- cobbDouglasData(countryAbbrev, energyType)
-  if (missing(energyType)){
-    out <- cbind(dataCD["-95% CI", "lambda"], dataCD["CD", "lambda"], dataCD["+95% CI", "lambda"],
-                 dataCD["-95% CI", "alpha"],  dataCD["CD", "alpha"],  dataCD["+95% CI", "alpha"],
-                 dataCD["-95% CI", "beta"],   dataCD["CD", "beta"],   dataCD["+95% CI", "beta"])
-  } else {
-    out <- cbind(dataCD["-95% CI", "lambda"], dataCD["CDe", "lambda"], dataCD["+95% CI", "lambda"],
-                 dataCD["-95% CI", "alpha"],  dataCD["CDe", "alpha"],  dataCD["+95% CI", "alpha"],
-                 dataCD["-95% CI", "beta"],   dataCD["CDe", "beta"],   dataCD["+95% CI", "beta"],
-                 dataCD["-95% CI", "gamma"],  dataCD["CDe", "gamma"],  dataCD["+95% CI", "gamma"])
-  }
-  return(out)
-}
-
-###########################################
-# Creates a number of rows in a data.frame that contain information 
-# about the coefficients of a Cobb-Douglas model for countryName.
-# Each parameter has its own row with confidence intervals.
-# The country name is in a column. Which parameter is involved is
-# also in a column.
-# 
-# The return type is a data.frame.
-##
-cobbDouglasCountryRowsForParamsGraph <- function(countryName, energyType){
-  #Create three rows, one for each parameter. Each row is a data.frame so that it is plottable!
-  if (missing(energyType)){
-    valueRow <- "CD"
-    dataCD <- cobbDouglasData(countryName)
-  } else {
-    valueRow <- "CDe"
-    dataCD <- cobbDouglasData(countryName, energyType)
-  }
-  # These rows are common to the "with" and "without" energy cases.
-  lambdaRow <- data.frame(country = countryName, 
-                          parameter = "lambda", 
-                          lowerCI = dataCD["-95% CI", "lambda"], 
-                          value = dataCD[valueRow, "lambda"], 
-                          upperCI = dataCD["+95% CI", "lambda"])
-  alphaRow <- data.frame(country = countryName, 
-                         parameter = "alpha",
-                         lowerCI = dataCD["-95% CI", "alpha"],
-                         value = dataCD[valueRow, "alpha"],  
-                         upperCI = dataCD["+95% CI", "alpha"])
-  betaRow <- data.frame(country = countryName, 
-                        parameter = "beta",
-                        lowerCI = dataCD["-95% CI", "beta"],
-                        value = dataCD[valueRow, "beta"], 
-                        upperCI = dataCD["+95% CI", "beta"])
-  if (missing(energyType)){
-    table <- rbind(lambdaRow, alphaRow, betaRow)
-  } else {
-    gammaRow <- data.frame(country = countryName, 
-                           parameter = "gamma",
-                           lowerCI = dataCD["-95% CI", "gamma"],
-                           value = dataCD[valueRow, "gamma"], 
-                           upperCI = dataCD["+95% CI", "gamma"])
-    table <- rbind(lambdaRow, alphaRow, betaRow, gammaRow)
-  }
-  return(table)
-}
-
-############################
-# Aggregates the Cobb-Douglas results into a big data table. No energy.
-##
-cobbDouglasParamsTableNoEnergy <- function(){
-  #Do rbind on the results of creating a row in the table for every country abbreviation that we know.
-  dataCD <- do.call("rbind", lapply(countryAbbrevs, cobbDouglasCountryRow))
-  colnames(dataCD) <- c(" ", "$\\lambda$", " ", 
-                        " ", "$\\alpha$",  " ",
-                        " ", "$\\beta$",   " ")
-  rownames(dataCD) <- countryAbbrevs
-  tableCD <- xtable(dataCD, 
-                    caption="Cobb-Douglas model (without energy) parameters for 1980-2011 (US, UK, JP), 1991-2010 (CN and ZA), and 1991-2011 (SA, IR, TZ, and ZM).
-(Parameter estimates beneath symbol.
-95\\% confidence interval bounds to left and right.)",
-                    label="tab:CD_Parameters_No_Energy",
-                    digits = c(1, 4,4,4, 2,2,2, 2,2,2),
-                    align = "r|ccc|ccc|ccc") #Sets alignment of the numbers in the columns
-  return(tableCD)
-}
-
-############################
-# Aggregates the Cobb-Douglas results into a big data table for the given energyType.
-##
-cobbDouglasParamsTableWithEnergy <- function(energyType){
-  #Do rbind on the results of creating a row in the table for every country abbreviation that we know.
-  dataCD <- do.call("rbind", lapply(countryAbbrevs, cobbDouglasCountryRow, energyType=energyType))
-  colnames(dataCD) <- c(" ", "$\\lambda$", " ", 
-                        " ", "$\\alpha$",  " ",
-                        " ", "$\\beta$",   " ",
-                        " ", "$\\gamma$",  " ")
-  rownames(dataCD) <- countryAbbrevs
-  tableCD <- xtable(dataCD, 
-                    caption=paste("Cobb-Douglas model (with $", tolower(energyType), "$) parameters for 1980-2011 (US, UK, JP), 1991-2010 (CN and ZA), and 1991-2011 (SA, IR, TZ, and ZM).
-(Parameter estimates beneath symbol.
-95\\% confidence interval bounds to left and right.)", sep=""),
-                    label=paste("tab:CD_Parameters_With_", energyType, sep=""),
-                    digits = c(1, 4,4,4, 2,2,2, 2,2,2, 2,2,2),
-                    align = "r|ccc|ccc|ccc|ccc") #Sets alignment of the numbers in the columns
-  return(tableCD)
-}
-
-############################
-# Prints a table with parameters from a Cobb-Douglas model for the given energyType. 
-# Leave energyType blank to print a table for Cobb-Douglas without energy.
-##
-printCDParamsTable <- function(energyType){
-  if (missing(energyType)){
-    print(cobbDouglasParamsTableNoEnergy(), 
-        caption.placement="top", 
-        sanitize.colnames.function = identity, 
-        size="\\tiny", 
-        table.placement="H")
-  } else {
-    print(cobbDouglasParamsTableWithEnergy(energyType), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-  }
-}
-
-#############################
-# Creates a graph with confidence intervals for the Cobb-Douglas model for the given energyType
-##
-createCDParamsGraph <- function(energyType){
-  if (missing(energyType)){
-    # Create a data table with the following columns:
-    # country abbrev, parameter (lambda, alpha, or beta), -95% CI, value, +95% CI
-    dataTable <- do.call("rbind", lapply(countryAbbrevs, cobbDouglasCountryRowsForParamsGraph))
-    graph <- segplot(country ~ upperCI + lowerCI | parameter, 
-                     data = dataTable, 
-                     centers = value, #identifies where the dots should be placed
-                     draw.bands = FALSE, #provides nicer error bars
-                     horizontal = FALSE, #makes error bars vertical and puts the countries in the x axis
-                     layout = c(2,2), #2 column, 2 row
-                     index.cond = list(c(2,3,1)), #orders the panels as alpha, beta, lambda, gamma
-                     strip = strip.custom(factor.levels=c("$\\lambda$", "$\\alpha$", "$\\beta$"), #sets labels in strip 
-                                          bg="white"), #sets background color in strip
-                     col = "black", #Sets line color to black
-                     lwd = 1, #Sets line width to 1.0
-                     ylim = list(c(-0.05, 0.1), c(-0.5, 1.5), c(-0.5, 1.5)), #y axis limits
-                     scales = list(cex=scaleTextSize, #controls text size on scales.
-                                   tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
-                                   x=list(cex=0.75), #reduces text size so that country abbrevs are legible
-                                   y=list(relation="free", #allow each axis to be different
-                                          at=list(c(0.0, 0.05, 0.1),   #y tick mark for lambda
-                                                  c(0.0, 0.5, 1.0), 
-                                                  c(0.0, 0.5, 1.0)
-                                                  )
-                                          )
-                                   )
-                     )
-   } else {
-    # Create a data table with the following columns:
-    # country abbrev, parameter (lambda, alpha, or beta), -95% CI, value, +95% CI
-    dataTable <- do.call("rbind", lapply(countryAbbrevs, cobbDouglasCountryRowsForParamsGraph, energyType=energyType))
-    graph <- segplot(country ~ upperCI + lowerCI | parameter, 
-                     data = dataTable, 
-                     centers = value, #identifies where the dots should be placed
-                     draw.bands = FALSE, #provides nicer error bars
-                     horizontal = FALSE, #makes error bars vertical and puts the countries in the x axis
-                     layout = c(2,2), #2 column, 2 row
-                     index.cond = list(c(2,3,1,4)), #orders the panels as alpha, beta, lambda, gamma
-                     #set labels and bg color in strip
-                     strip = strip.custom(factor.levels=c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$"),  
-                                          bg="white"),
-                     col = "black", #Sets line color to black
-                     lwd = 1, #Sets line width to 1.0
-                     ylim = list(c(-0.05, 0.1), c(-0.5, 1.5), c(-0.5, 1.5), c(-0.5, 1.5)), #y axis limits
-                     scales = list(cex=scaleTextSize, #controls text size on scales.
-                                   tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
-                                   x=list(cex=0.75), #reduces text size so that country abbrevs are legible
-                                   y=list(relation="free", #allow each axis to be different
-                                          at=list(c(0.0, 0.05, 0.1),   #y tick mark for lambda
-                                                  c(0.0, 0.5, 1.0), 
-                                                  c(0.0, 0.5, 1.0),
-                                                  c(0.0, 0.5, 1.0)
-                                                  )
-                                          )
-                                   )
-                     )
-   }
-   return(graph)
-}
-
-##############################
-# Creates a graph that plots predicted GDP as lines and GDP data as open circles.
-##
-createCDLatticeGraph <- function(){
-  dataTable <- loadData("All") #Grab the raw data
-  predictions <- cobbDouglasPredictionsColumn()     #Predictions from CD without energy
-  predictionsQ <- cobbDouglasPredictionsColumn("Q") #Predictions from CD with Q
-  predictionsX <- cobbDouglasPredictionsColumn("X") #Predictions from CD with X
-  predictionsU <- cobbDouglasPredictionsColumn("U") #Predictions from CD with U
-  #Now add the predictions columns to the data.
-  dataTable <- cbind(dataTable, predictions, predictionsQ, predictionsX, predictionsU) 
-  graphType <- "b" #b is for both line and symbol
-  lineTypes <- c(0, 1, 2, 4, 1) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
-  lineWidths <- c(0, 2, 1, 1, 1) #line widths. 0 means no line.
-  colors <- c("black", "black", "red", "blue", "darkorange") #line and symbol colors
-  symbols <- c(1, NA, NA, NA, NA)  #NA gives no symbol.
-  graph <- xyplot(iGDP+predGDP+predGDPQ+predGDPX+predGDPU ~ Year | Country, data=dataTable,
-                  type=graphType,
-                  index.cond=list(countryOrderForGraphs), #orders the panels.
-                  layout=ninePanelLayoutSpec, #indicates a 3x3 arrangement of panels.
-                  strip = strip.custom(factor.levels=countryNamesAlph, bg="white"), #Sets strip parameters
-                  as.table=TRUE, #indexing of panels starts in upper left and goes across rows.
-                  lty = lineTypes, lwd = lineWidths, col = colors, #Controls line parameters
-                  pch = symbols, col.symbol = colors, #Controls symbol parameters
-                  key=list(text=list(c("Actual", "No energy", "With $q$", "With $x$", "With $u$")),
-                           type=graphType,
-                           cex=keyTextSize, #controls size of text in the key
-                           lines=list(lty=lineTypes, lwd=lineWidths), #controls line types
-                           pch=symbols, col=colors, #controls symbol (plot characters) types
-                           columns=keyColumns, x=keyXLoc, y=keyYLoc), #controls columns and position of the key
-                  scales=list(cex=scaleTextSize, #controls text size on scales.
-                              tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
-                              y=list(relation="free", #allows each axis to be different
-                                     at=c(1,2,3,4,5,6,7,8,9,10) #tick mark locations
-                                     )
-                              ), 
-                  ylim=list(c(1,8), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3)),
-                  xlab="", ylab="Indexed GDP (1980=1 or 1991=1)") #axis labels
-  return(graph)
-}
-@
-
 The Cobb-Douglas model without energy is given by
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-<<ces functions, eval=TRUE>>=
-# Set some common names for CES variables.
-xNames = c("iCapStk", "iLabor", "iEToFit")
-tName = "iYear"
-yName = "iGDP"
-
-######################################
-# Loads data and trims rows where necessary.
-# Also, replaces the name of the desired energy column with "iEToFit".
-# Returns a data.frame with the loaded data.
-##
-loadAndPrepDataForCES <- function(countryAbbrev, energyType){
-  dataTable <- loadData(countryAbbrev)
-  if (energyType == "U"){
-    # Trim the dataset to include only those years for which U is available.
-    dataTable <- subset(dataTable, !is.na(iU))
-  }
-  # Trim data from China and South Africa that is missing labor information for 2011.
-  dataTable <- subset(dataTable, !is.na(iLabor))
-  # We need to do the CES fit with the desired energyType.
-  # To achieve the correct fit, we'll change the name of the desired column
-  # to "iEToFit" and use "iEToFit" in the nls function.
-  dataTable <- replaceColName(dataTable, energyType, "iEToFit")
-  return(dataTable)
-}
-
-####################
-# Returns a cesEst model for the country and energyType specified.
-# energyType should be one of Q", "X", or "U".
-##
-cesModel <- function(countryAbbrev, energyType){
-  # Load the data that we need.
-  dataTable <- loadAndPrepDataForCES(countryAbbrev, energyType)
-  control=nls.lm.control(maxiter=1000, maxfev=2000)
-  if (countryAbbrev == "US") {
-    # With Q, The unconstrained optimization leads to rho1 = -0.72 and sigma1 = 3.57, which is not 
-    # economically meaningful.  So, a grid search was performed, and it confirmed that low values of 
-    # rho1 yield a better fit. In fact, the lower the value of rho1, the better. So, we'll set it 
-    # here at rho1=0.0, which makes the elasticity of substitution between k and l sigma1 = 1.0, 
-    # giving the Cobb-Douglas form for the k l portion of the CES function. Similar results are found
-    # for X and U.
-    rho1 = 0.0
-    # Unconstrained optimization leads to rho = 25.7 and sigma = 0.0374, indicating that (kl) and (e) are 
-    # complimentary.  We'll let the estCES function solve for the best value.
-    modelCES <- cesEst(data=dataTable, yName=yName, xNames=xNames, tName=tName, control=control,
-                       method="LM",
-                       rho1=rho1
-                       )
-  } else if (countryAbbrev == "UK") {
-    # The unconstrained optimization leads to rho1 = -2.4 and sigma1 = -0.71, which is not economically meaningful.
-    # So, a grid search was performed, and it confirmed that low values of rho1 yield a better fit. In fact, the 
-    # lower the value of rho1, the better. So, we'll set it here at rho1=0.0, which makes the elasticity of 
-    # substitution between k and l sigma1 = 1.0, giving the Cobb-Douglas form for the k l portion of the CES function.
-    # rho1 = c(0.00, 0.01, 0.02)
-    rho1 = 0.0
-    modelCES <- cesEst(data=dataTable, yName=yName, xNames=xNames, tName=tName, control=control,
-                       method="LM",
-                       rho1=rho1
-                       )
-  } else if (countryAbbrev == "JP") {
-    # The unconstrained optimization leads to rho1 = 7.99 and sigma1 = 0.11, indicating complementarity between k & l,
-    # but different from the results for the US and UK (where k & l were found to be substitutes).  However, the
-    # p value for rho1 is very high (0.3), indicating that rho1 is not making a significant contribution to the model. 
-    # The unconstrained fit gives R^ = 0.996 and sigma = 0.103, indicating complementarity between (kl) and (e).
-    # 
-    # In fact, we could force rho1 = 0.0 and achieve rho = 280 and sigma = 0.00356 with R^2 = 0.988, a very small
-    # decrease, indeed.  Note that both the constrained and unconstrained fits give small sigma, indicating
-    # that (kl) and (e) are complimentary.
-    modelCES <- cesEst(data=dataTable, yName=yName, xNames=xNames, tName=tName, control=control,
-                       method="LM"
-                       )
-  } else if (countryAbbrev == "CN"){
-    # Unconstrained optimization: rho1 < -0.2290, rho = 14.1651, R^2 = 0.9984. This corresponds to sigma1 = 1.297
-    # and sigma = 0.0659, indicating that (kl) and (e) are complements and k & l are substitutes.  However, none of the
-    # rho or sigma values are statistically significant.
-    # Now, sigma1 > 1 is not economically meaningful, so we'll set rho1 = 0 to force sigma1 = 1.0. When we do that, 
-    # we obtain sigma1 = 1.0 (so perfect substitution between k and l) and sigma = 7.19 (again, not economically
-    # meaningful) with R^2 = 0.9983.  Again, none of the rho or sigma values are statistically significant.
-    # Furthermore, the only significant varluable is gamma = 1.0731.
-    # So, for the final fit, I'll put rho1 = 0.0 and rho = 0.0. The final R^2 = 0.9983.
-    rho1 = 0.0
-    rho = 0.0
-    modelCES <- cesEst(data=dataTable, yName=yName, xNames=xNames, tName=tName, control=control,
-                       method="LM",
-                       rho1=rho1,
-                       rho=rho                     
-                       )
-  } else if (countryAbbrev == "ZA"){
-    # An unconstrained fit works for South Africa.  Results are sigma1 = 0.05, signalling complementarity
-    # between k and l.  sigma = 0.03, indicating complementatity between (kl) and (e).
-    modelCES <- cesEst(data=dataTable, yName=yName, xNames=xNames, tName=tName, control=control,
-                       method="LM",
-                       )
-  } else if (countryAbbrev == "SA"){
-    # An unconstrained fit gives rho = -6.33, rho1 = 9.36 (sigma1 = 0.0965) and R^2 = 0.9892.  
-    # This result is not economically meaningful.
-    # Constraining rho = 0 gives rho1 = -582, again not economically meaningful.
-    # So, do a grid search over meaningful regions to see what is best.
-    # The result (to with +/- 0.1) is rho = 0.0 and rho1 = 5.7, with R^2 = 0.9885.
-    # However, neither the the rho or nor the sigma values are statistically significant.
-    rho1 = 5.7
-    rho = 0.0
-    modelCES <- cesEst(data=dataTable, yName=yName, xNames=xNames, tName=tName, control=control,
-                       method="LM",
-                       rho1 = rho1,
-                       rho = rho
-                       )
-  } else if (countryAbbrev == "IR"){
-    # Iran works with an unconstrained fit.
-    modelCES <- cesEst(data=dataTable, yName=yName, xNames=xNames, tName=tName, control=control,
-                       method="LM",
-                       )
-  } else if (countryAbbrev == "TZ"){
-    # Using the PORT algorithm yields convergence and R^2 = 0.9974 with economically menaingful results.
-    # However, none of the rho or sigma values are statistically significant.
-    modelCES <- cesEst(data=dataTable, yName=yName, xNames=xNames, tName=tName, control=control,
-                       method="PORT",
-                       )
-  } else if (countryAbbrev == "ZM"){
-    # ZM works with the PORT algorithm, but not the LM algorithm.
-    modelCES <- cesEst(data=dataTable, yName=yName, xNames=xNames, tName=tName, control=control,
-                       method="PORT",
-                       rho=0.0
-                       )
-  }
-  return(modelCES)
-}
-
-#########################
-# Takes the CES fitted models and creates per-country predictions for them.
-# Returns a data.frame with the predictions.
-##
-cesPredictions <- function(countryAbbrev, energyType){
-  dataTable <- loadAndPrepDataForCES(countryAbbrev, energyType)
-  # Can't make predictions for any of CN, ZA, SA, IR, TZ, or ZM if we're interested in U
-  if (!(haveDataSF(countryAbbrev, energyType))){
-    # If we don't have data for this combination of countryAbbrev and energyType, 
-    # return a column of NAs if the above conditions have been met.
-    nRows <- 21 # All of these countries need 21 rows.
-    df <- as.data.frame(matrix(NA, ncol = 1, nrow = nRows))
-    colnames(df) <- "pred"
-    return(df)
-  }
-  model <- cesModel(countryAbbrev, energyType)
-  pred <- fitted(model)
-  df <- data.frame(pred)
-  # Pad with rows as necessary
-  df <- padRows(countryAbbrev, df)
-  return(df)
-}
-
-#########################
-# Takes the CES fitted models and creates a single column of predicted GDP values
-# that corresponds, row for row, with the AllData.txt file.
-##
-cesPredictionsColumn <- function(energyType){
-  out <- do.call("rbind", lapply(countryAbbrevs, cesPredictions, energyType=energyType))
-  colnames(out) <- c(paste("predGDP", energyType, sep=""))
-  return(out)
-}
-
-##############################
-# Creates a graph that plots predicted GDP as lines, one for each single factor, and historical GDP 
-# data as open circles.
-##
-createCESLatticeGraph <- function(){
-  dataTable <- loadData("All") #Grab the raw data
-  predictionsQ <- cesPredictionsColumn("Q") #Predictions from CES with Q
-  predictionsX <- cesPredictionsColumn("X") #Predictions from CES with X
-  predictionsU <- cesPredictionsColumn("U") #Predictions from CES with U
-  #Now add the predictions columns to the data.
-  dataTable <- cbind(dataTable, predictionsQ, predictionsX, predictionsU) 
-  graphType <- "b" #b is for both line and symbol
-  lineTypes <- c(0, 2, 4, 1) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
-  lineWidths <- c(0, 1, 1, 1) #line widths. 0 means no line.
-  colors <- c("black", "red", "blue", "darkorange") #line and symbol colors
-  symbols <- c(1, NA, NA, NA)  #NA gives no symbol.
-  graph <- xyplot(iGDP+predGDPQ+predGDPX+predGDPU ~ Year | Country, data=dataTable,
-                  type=graphType,
-                  index.cond=list(countryOrderForGraphs), #orders the panels.
-                  layout=ninePanelLayoutSpec, #indicates a 3x3 arrangement of panels.
-                  strip = strip.custom(factor.levels=countryNamesAlph, bg="white"), #Sets strip parameters
-                  as.table=TRUE, #indexing of panels starts in upper left and goes across rows.
-                  lty = lineTypes, lwd = lineWidths, col = colors, #Controls line parameters
-                  pch = symbols, col.symbol = colors, #Controls symbol parameters
-                  key=list(text=list(c("Actual", "With $q$", "With $x$", "With $u$")),
-                           type=graphType,
-                           cex=keyTextSize, #controls size of text in the key
-                           lines=list(lty=lineTypes, lwd=lineWidths), #controls line types
-                           pch=symbols, col=colors, #controls symbol (plot characters) types
-                           columns=keyColumns, x=keyXLoc, y=keyYLoc), #controls columns and position of the key
-                  scales=list(cex=scaleTextSize, #controls text size on scales.
-                              tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
-                              y=list(relation="free", #allows each axis to be different
-                                     at=c(1,2,3,4,5,6,7,8,9,10) #tick mark locations
-                                     )
-                              ), 
-                  ylim=list(c(1,8), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3)),
-                  xlab="", ylab="Indexed GDP (1980=1 or 1991=1)") #axis labels
-  return(graph)
-}
-
-#################################################
-# Calculates parameter estimates and confidence intervals
-# for the CES production function given a country and an energyType.
-#
-# countryAbbrev is a string containing the 2-letter abbreviation for the country, e.g. "US" or "CN"
-# energyType is a string, one of "Q", "X", or "U"
-#
-# returns a data.frame of data for the LINEX model.
-# First row is the +95% CI on all parameters
-# Second row contains the parameter estimates
-# Third row is the -95% CI on all parameters
-# Each column has names: gamma, lambda, delta_1, delta, rho_1, rho
-##
-cesData <- function(countryAbbrev, energyType){
-  #First, check to see if we want useful work (U) AND one of the countries for which we don't have data.
-  if (!haveDataCD(countryAbbrev, energyType)){
-    #Return a column of NAs if the above conditions have been met.
-    nRows <- 3 # +95% CI, CDe, and -95% CI.
-    nCols <- 6 # gamma, lambda, delta_1, delta, sigma_1, and sigma
-    df <- as.data.frame(matrix(NA, ncol = nCols, nrow = nRows))
-    colnames(df) <- c("gamma", "lambda", "delta_1", "delta", "sigma_1", "sigma")
-    rownames(df) <- c("+95% CI", "CES", "-95% CI")
-    return(df)
-  }
-  # We have a combination of country and energy type for which we have data.
-  modelCES <- cesModel(countryAbbrev, energyType)
-  summaryCES <- summary(modelCES) # Gives a summary table.
-#print(summaryCES)
-  # Calculate the degrees of freedom as N_obs - N_params
-  dofCES <- nrow(loadAndPrepDataForCES(countryAbbrev, energyType)) - 6 # Gives the degrees of freedom for the model.
-#print(dofCES)
-  tvalCES <- qt(ciHalfLevel, df = dofCES)
-#print(tvalCES)
-  # Calculate confidence intervals for the parameters of the model
-  ciCES <- confint(modelCES, level = ciLevel)  # Calculates confidence intervals for the CES model.
-#print(ciCES)
-  # Get confidence intervals for the elasticities of substitution
-  sigma_1.est <- deltaMethod(modelCES, "1.0 / (1.0 + rho_1)") # Estimates sigma_1 and its standard error (SE).
-#print(sigma_1.est)
-  sigma_1CI <- with(sigma_1.est, Estimate + c(-1.0, 1.0) * tvalCES * SE)
-  # There are some cases where the confidence intervals for sigma_1 are huge. Set them to -Inf or Inf as appropriate
-  if (is.nan(sigma_1CI[1]) || (sigma_1CI[1] < -1.0e10)){
-    sigma_1CI[1] <- -Inf 
-  }
-  if (is.nan(sigma_1CI[2]) || (sigma_1CI[2] > 1.0e10)){
-    sigma_1CI[2] <- Inf
-  }
-#print("sigma_1CI:")
-#print(sigma_1CI)
-  sigma.est <- deltaMethod(modelCES, "1.0 / (1.0 + rho)") # Estimates sigma and its standard error (SE)
-#print(sigma.est)
-  sigmaCI <- with(sigma.est, Estimate + c(-1.0, 1.0) * tvalCES * SE)
-#print("sigmaCI:")
-#print(sigmaCI)
-  # Report results with SE
-  gamma <- coef(modelCES)["gamma"] #as.numeric(coef(modelCES)["gamma"])
-  lambda <- coef(modelCES)["lambda"] #as.numeric(coef(modelCES)["lambda"])
-  delta_1 <- coef(modelCES)["delta_1"]
-  delta <- coef(modelCES)["delta"]
-  sigma_1 <- sigma_1.est$Estimate
-  sigma <- sigma.est$Estimate
-  # Combine all estimates and their confidence intervals into data frames with intelligent row names
-  estCES <- data.frame(gamma=gamma, lambda=lambda, delta_1=delta_1, delta=delta, sigma_1=sigma_1, sigma=sigma)
-  row.names(estCES) <- "CES"
-#print(estCES)
-  # The [1] subscripts pick off the lower confidence interval
-#print(ciCES["gamma","2.5 %"])
-  lowerCES <- data.frame(gamma=ciCES["gamma","2.5 %"], lambda=ciCES["lambda", "2.5 %"],
-                         delta_1=ciCES["delta_1", "2.5 %"], delta=ciCES["delta", "2.5 %"],
-                         sigma_1=sigma_1CI[1], sigma=sigmaCI[1])
-  row.names(lowerCES) <- "-95% CI"
-#print(lowerCES)
-  # The [2] subscripts pick off the upper confidence interval
-  upperCES <- data.frame(gamma=ciCES["gamma","97.5 %"], lambda=ciCES["lambda", "97.5 %"],
-                         delta_1=ciCES["delta_1", "97.5 %"], delta=ciCES["delta", "97.5 %"],
-                         sigma_1=sigma_1CI[2], sigma=sigmaCI[2])
-  row.names(upperCES) <- "+95% CI"
-#print(upperCES)
-  # Now create the data for a table and return it
-  dataCES <- rbind(upperCES, estCES, lowerCES)
-#print("dataCES")
-#print(dataCES)
-  return(dataCES)
-}
-
-############
-# Creates a row for the CES parameters table for the given country (2-letter code) and energyType (Q, X, or U)
-##
-cesCountryRow <- function(countryAbbrev, energyType){
-  dataCES <- cesData(countryAbbrev, energyType)
-  out <- cbind(dataCES["-95% CI", "gamma"], dataCES["CES", "gamma"], dataCES["+95% CI", "gamma"],
-               dataCES["-95% CI", "lambda"], dataCES["CES", "lambda"], dataCES["+95% CI", "lambda"],
-               dataCES["-95% CI", "delta_1"], dataCES["CES", "delta_1"], dataCES["+95% CI", "delta_1"],
-               dataCES["-95% CI", "delta"], dataCES["CES", "delta"], dataCES["+95% CI", "delta"],
-               dataCES["-95% CI", "sigma_1"], dataCES["CES", "sigma_1"], dataCES["+95% CI", "sigma_1"],
-               dataCES["-95% CI", "sigma"], dataCES["CES", "sigma"], dataCES["+95% CI", "sigma"]
-               )
-  return(out)
-}
-
-###########################################
-# Creates a number of rows in a data.frame that contain information 
-# about the coefficients of a CES model for countryName and energyType
-# Each parameter has its own row with confidence intervals.
-# The country name is in a column. Which parameter is involved is
-# also in a column.
-# 
-# The return type is a data.frame.
-##
-cesCountryRowsForParamsGraph <- function(countryName, energyType){
-  #Create six rows, one for each parameter. Each row is a data.frame so that it is plottable!
-  dataCES <- cesData(countryName, energyType)
-  gammaRow <- data.frame(country = countryName, 
-                          parameter = "gamma", 
-                          lowerCI = dataCES["-95% CI", "gamma"], 
-                          value = dataCES["CES", "gamma"], 
-                          upperCI = dataCES["+95% CI", "gamma"])
-  lambdaRow <- data.frame(country = countryName, 
-                         parameter = "lambda",
-                         lowerCI = dataCES["-95% CI", "lambda"],
-                         value = dataCES["CES", "lambda"],  
-                         upperCI = dataCES["+95% CI", "lambda"])
-  delta_1Row <- data.frame(country = countryName, 
-                         parameter = "delta_1",
-                         lowerCI = dataCES["-95% CI", "delta_1"],
-                         value = dataCES["CES", "delta_1"],  
-                         upperCI = dataCES["+95% CI", "delta_1"])
-  deltaRow <- data.frame(country = countryName, 
-                         parameter = "delta",
-                         lowerCI = dataCES["-95% CI", "delta"],
-                         value = dataCES["CES", "delta"],  
-                         upperCI = dataCES["+95% CI", "delta"])
-  sigma_1Row <- data.frame(country = countryName, 
-                         parameter = "sigma_1",
-                         lowerCI = dataCES["-95% CI", "sigma_1"],
-                         value = dataCES["CES", "sigma_1"],  
-                         upperCI = dataCES["+95% CI", "sigma_1"])
-  sigmaRow <- data.frame(country = countryName, 
-                         parameter = "sigma",
-                         lowerCI = dataCES["-95% CI", "sigma"],
-                         value = dataCES["CES", "sigma"],  
-                         upperCI = dataCES["+95% CI", "sigma"])
-  table <- rbind(gammaRow, lambdaRow, delta_1Row, deltaRow, sigma_1Row, sigmaRow)
-  return(table)
-}
-
-############################
-# Aggregates the CES results for gamma, delta_1, and delta into a table for the given energyType.
-##
-cesParamsTableA <- function(energyType){
-  dataCES <- do.call("rbind", lapply(countryAbbrevs, cesCountryRow, energyType=energyType))
-  colnames(dataCES) <- c(" ", "$\\gamma$",    " ", 
-                         " ", "$\\lambda$",   " ",
-                         " ", "$\\delta_1$",  " ",
-                         " ", "$\\delta$",    " ",
-                         " ", "$\\sigma_1$",  " ",
-                         " ", "$\\sigma$",    " ")
-  rownames(dataCES) <- countryAbbrevs
-  tableCESa <- xtable(dataCES[,c(1,2,3, 7,8,9, 10,11,12)], #Picks up gamma, delta_1, and delta
-                      caption=paste("CES model (with $", tolower(energyType), "$).
-$\\gamma$, $\\delta_1$, and $\\delta$ parameters for 1980-2011 (US, UK, JP), 1991-2010 (CN and ZA), and 1991-2011 (SA, IR, TZ, and ZM).
-(Parameter estimates beneath symbol.
-95\\% confidence interval bounds to left and right.)", sep=""),
-                      label=paste("tab:CES_Parameters_With_", energyType, sep=""),
-                      digits = c(1, 2,2,2, 2,2,2, 2,2,2),
-                      align = "r|ccc|ccc|ccc" #Sets alignment of the numbers in the columns
-                      ) 
-  return(tableCESa)
-}
-
-############################
-# Aggregates the CES results for lambda, sigma_1, and sigma into a table for the given energyType.
-##
-cesParamsTableB <- function(energyType){
-  dataCES <- do.call("rbind", lapply(countryAbbrevs, cesCountryRow, energyType=energyType))
-  colnames(dataCES) <- c(" ", "$\\gamma$",    " ", 
-                         " ", "$\\lambda$",   " ",
-                         " ", "$\\delta_1$",  " ",
-                         " ", "$\\delta$",    " ",
-                         " ", "$\\sigma_1$",  " ",
-                         " ", "$\\sigma$",    " ")
-  rownames(dataCES) <- countryAbbrevs
-  tableCESb <- xtable(dataCES[,c(4,5,6, 13,14,15, 16,17,18)], #Picks up lambda, sigma_1, and sigma
-                      caption=paste("CES model (with $", tolower(energyType), "$).
-$\\lambda$, $\\sigma_1$, and $\\sigma$ parameters for 1980-2011 (US, UK, JP), 1991-2010 (CN and ZA), and 1991-2011 (SA, IR, TZ, and ZM).
-(Parameter estimates beneath symbol.
-95\\% confidence interval bounds to left and right.)", sep=""),
-                      label=paste("tab:CES_Parameters_With_", energyType, sep=""),
-                      digits = c(1, 4,4,4, 2,2,2, 2,2,2),
-                      align = "r|ccc|ccc|ccc"  #Sets alignment of the numbers in the columns
-                      )
-  return(tableCESb)
-}
-
-#############################
-# Creates a graph with confidence intervals for the CES model for the given energyType
-##
-createCESParamsGraph <- function(energyType){
-  # Create a data table with the following columns:
-  # country abbrev, parameter (gamma, lambda, delta_1, delta, sigma_1, sigma), -95% CI, value, +95% CI
-  dataTable <- do.call("rbind", lapply(countryAbbrevs, cesCountryRowsForParamsGraph, energyType=energyType))
-  graph <- segplot(country ~ upperCI + lowerCI | parameter, 
-                   data = dataTable, 
-                   centers = value, #identifies where the dots should be placed
-                   as.table = TRUE, #indexing of panels starts in upper left and goes across rows.
-                   draw.bands = FALSE, #provides nicer error bars
-                   horizontal = FALSE, #makes error bars vertical and puts the countries in the x axis
-                   layout = c(2,3), #2 column, 3 row
-                   # Orders the panels as gamma, lambda, delta_1, delta, sigma_1, sigma
-                   index.cond = list(c(1,2,3,4,5,6)), 
-                   #set labels and bg color in strip
-                   strip = strip.custom(factor.levels=c("$\\gamma$", "$\\lambda$", "$\\delta_1$",
-                                                        "$\\delta$", "$\\sigma_1$", "$\\sigma$"), bg="white"),
-                   col = "black", #Sets line color to black
-                   lwd = 1, #Sets line width to 1.0
-                   ylim = list(c(0.9, 1.1), c(-0.05, 0.05), c(0.0, 1.0),
-                               c(0.0, 1.0), c(0.0, 1.0), c(0.0, 1.0)), #y axis limits
-                   scales = list(cex=scaleTextSize, #controls text size on scales.
-                                 tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
-                                 x=list(cex=0.75), #reduces text size so that country abbrevs are legible
-                                 y=list(relation="free", #allow each axis to be different
-                                        at=list(c(0.9, 1.0, 1.1), c(-0.05, 0.0, 0.05),
-                                                c(0.0, 0.5, 1.0), c(0.0, 0.5, 1.0), 
-                                                c(0.0, 0.5, 1.0), c(0.0, 0.5, 1.0))   #y tick marks
-                                       )
-                   )
-  )
-  return(graph)
-}
-
-############################
-# Prints a table with gamma, delta_1, and delta parameters from a CES model for the given energyType. 
-##
-printCESParamsTableA <- function(energyType){
-  print(cesParamsTableA(energyType), 
-    caption.placement="top", 
-    sanitize.colnames.function = identity, 
-    size="\\tiny",
-    table.placement="H")
-}
-
-############################
-# Prints a table with lambda, sigma_1, and sigma parameters from a CES model for the given energyType. 
-##
-printCESParamsTableB <- function(energyType){
-  print(cesParamsTableB(energyType), 
-    caption.placement="top", 
-    sanitize.colnames.function = identity, 
-    size="\\tiny",
-    table.placement="H")
-}
-@
 
@@
   y = \gamma \mathrm{e}^{\lambda(t-t_0)}  
-      \left\{\delta \left[\delta_1 k^{-\rho_1} + (1-\delta_1)l^{-\rho_1} \right] + (1-\delta) e^{-\rho} \right\}
-                                                                                                        ^{-1/\rho}.
+      \left\{\delta \left[\delta_1 k^{-\rho_1} + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1} 
+              + (1-\delta) e^{-\rho} \right\}^{-1/\rho}.
 \end{equation}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-<<LINEX functions, eval=TRUE>>=
-####################
-# Returns an nls linex model for the country and energyType specified.
-# energyType should be one of Q", "X", or "U".
-##
-linexModel <- function(countryAbbrev, energyType){
-  # Load the data that we need.
-  dataTable <- loadData(countryAbbrev)
-  # We need to do the CES fit with the desired energyType.
-  # To achieve the correct fit, we'll change the name of the desired column
-  # to "iEToFit" and use "iEToFit" in the nls function.
-  dataTable <- replaceColName(dataTable, energyType, "iEToFit")
-  a_0Guess <- 0.5
-  c_tGuess <- 1.0
-  if (countryAbbrev == "SA"){
-    # Need adjusted guess values, becasue k and l are above GDP for SA.
-    a_0Guess <- -1
-    c_tGuess <- -6
-
-  }
-  # Runs a non-linear least squares fit to the data with constraints
-  modelLINEX <- nls(iGDP ~ iEToFit * exp(a_0*(2.0 - (iLabor+iEToFit)/iCapStk) + a_0 * c_t *(iLabor/iEToFit - 1.0)), 
-                  data=dataTable,
-                  start=list(a_0=a_0Guess, c_t=c_tGuess),
-                  control=nls.control(maxiter=50, tol=1e-06, minFactor=1/1024, printEval=FALSE, warnOnly=TRUE),
-#                   algorithm = "port",
-#                   lower = list(a_0=-INF, c_t=-INF),
-#                   upper = list(a_0= INF, c_t= INF)
-                  )
-  return(modelLINEX)
-}
-
-#########################
-# Takes the LINEX fitted models and creates per-country predictions for them.
-# Returns a data.frame with the predictions.
-##
-linexPredictions <- function(countryAbbrev, energyType){
-  # Can't make predictions for any of CN, ZA, SA, IR, TZ, or ZM if we're interested in U
-  if (!(haveDataSF(countryAbbrev, energyType))){
-    # If we don't have data for this combination of countryAbbrev and energyType, 
-    # return a column of NAs if the above conditions have been met.
-    nRows <- 21 # All of these countries need 21 rows.
-    df <- as.data.frame(matrix(NA, ncol = 1, nrow = nRows))
-    colnames(df) <- "pred"
-    return(df)
-  }
-  model <- linexModel(countryAbbrev, energyType)
-  pred <- predict(model) #See http://stackoverflow.com/questions/9918807/how-get-plot-from-nls-in-r
-  df <- data.frame(pred)
-  # Pad with rows as necessary
-  df <- padRows(countryAbbrev, df)
-  return(df)
-}
-
-#########################
-# Takes the LINEX fitted models and creates a single column of predicted GDP values
-# that corresponds, row for row, with the AllData.txt file.
-##
-linexPredictionsColumn <- function(energyType){
-  out <- do.call("rbind", lapply(countryAbbrevs, linexPredictions, energyType=energyType))
-  colnames(out) <- c(paste("predGDP", energyType, sep=""))
-  return(out)
-}
-
-##############################
-# Creates a graph that plots predicted GDP as lines, one for each single factor, and historical GDP 
-# data as open circles.
-##
-createLinexLatticeGraph <- function(){
-  dataTable <- loadData("All") #Grab the raw data
-  predictionsQ <- linexPredictionsColumn("Q") #Predictions from LINEX with Q
-  predictionsX <- linexPredictionsColumn("X") #Predictions from LINEX with X
-  predictionsU <- linexPredictionsColumn("U") #Predictions from LINEX with U
-  #Now add the predictions columns to the data.
-  dataTable <- cbind(dataTable, predictionsQ, predictionsX, predictionsU) 
-  graphType <- "b" #b is for both line and symbol
-  lineTypes <- c(0, 2, 4, 1) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
-  lineWidths <- c(0, 1, 1, 1) #line widths. 0 means no line.
-  colors <- c("black", "red", "blue", "darkorange") #line and symbol colors
-  symbols <- c(1, NA, NA, NA)  #NA gives no symbol.
-  graph <- xyplot(iGDP+predGDPQ+predGDPX+predGDPU ~ Year | Country, data=dataTable,
-                  type=graphType,
-                  index.cond=list(countryOrderForGraphs), #orders the panels.
-                  layout=ninePanelLayoutSpec, #indicates a 3x3 arrangement of panels.
-                  strip = strip.custom(factor.levels=countryNamesAlph, bg="white"), #Sets strip parameters
-                  as.table=TRUE, #indexing of panels starts in upper left and goes across rows.
-                  lty = lineTypes, lwd = lineWidths, col = colors, #Controls line parameters
-                  pch = symbols, col.symbol = colors, #Controls symbol parameters
-                  key=list(text=list(c("Actual", "With $q$", "With $x$", "With $u$")),
-                           type=graphType,
-                           cex=keyTextSize, #controls size of text in the key
-                           lines=list(lty=lineTypes, lwd=lineWidths), #controls line types
-                           pch=symbols, col=colors, #controls symbol (plot characters) types
-                           columns=keyColumns, x=keyXLoc, y=keyYLoc), #controls columns and position of the key
-                  scales=list(cex=scaleTextSize, #controls text size on scales.
-                              tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
-                              y=list(relation="free", #allows each axis to be different
-                                     at=c(1,2,3,4,5,6,7,8,9,10) #tick mark locations
-                                     )
-                              ), 
-                  ylim=list(c(1,8), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3)),
-                  xlab="", ylab="Indexed GDP (1980=1 or 1991=1)") #axis labels
-  return(graph)
-}
-
-#################################################
-# Calculates parameter estimates and confidence intervals
-# for the LINEX production function given a country and an energyType.
-#
-# countryAbbrev is a string containing the 2-letter abbreviation for the country, e.g. "US" or "CN"
-# energyType is a string, one of "Q", "X", or "U"
-#
-# returns a data.frame of data for the LINEX model.
-# First row is the +95% CI on all parameters
-# Second row contains the parameter estimates
-# Third row is the -95% CI on all parameters
-# Each column has names: a_0 and c_t, corresponding to the parameters in the model.
-##
-linexData <- function(countryAbbrev, energyType){
-  #First, check to see if we want useful work (U) AND one of the countries for which we don't have data.
-  if (!haveDataCD(countryAbbrev, energyType)){
-    #Return a column of NAs if the above conditions have been met.
-    nRows <- 3 # +95% CI, CDe, and -95% CI.
-    nCols <- 2 # a_0 and c_t
-    df <- as.data.frame(matrix(NA, ncol = nCols, nrow = nRows))
-    colnames(df) <- c("a_0", "c_t")
-    rownames(df) <- c("+95% CI", "CDe", "-95% CI")
-    return(df)
-  }
-  # We have a combination of country and energy type for which we have data.
-  modelLINEX <- linexModel(countryAbbrev, energyType)
-  summaryLINEX <- summary(modelLINEX) # Gives the nls summary table.
-  dofLINEX <- summaryLINEX$df[2] # Gives the degrees of freedom for the model.
-  tvalLINEX <- qt(ciHalfLevel, df = dofLINEX)
-  ciLINEX <- confint(modelLINEX, level = ciLevel)  # Calculates confidence intervals for the LINEX model.
-  # Report results with SE
-  a_0 <- as.numeric(coef(modelLINEX)["a_0"])
-  c_t <- as.numeric(coef(modelLINEX)["c_t"])
-  # Combine all estimates and their confidence intervals into data frames with intelligent row names
-  estLINEX <- data.frame(a_0 = a_0, c_t = c_t)
-  row.names(estLINEX) <- "LINEX"
-  # The [1] subscripts pick off the lower confidence interval
-  lowerLINEX <- data.frame(a_0=ciLINEX["a_0","2.5%"], c_t=ciLINEX["c_t", "2.5%"])
-  row.names(lowerLINEX) <- "-95% CI"
-  # The [2] subscripts pick off the upper confidence interval
-  upperLINEX <- data.frame(a_0=ciLINEX["a_0","97.5%"], c_t=ciLINEX["c_t", "97.5%"])
-  row.names(upperLINEX) <- "+95% CI"
-  # Now create the data for a table and return it
-  dataLINEX <- rbind(upperLINEX, estLINEX, lowerLINEX)
-  return(dataLINEX)
-}
-
-############
-# Creates a row for the LINEX parameters table for the given country (2-letter code) and energyType (Q, X, or U)
-##
-linexCountryRow <- function(countryAbbrev, energyType){
-  dataLINEX <- linexData(countryAbbrev, energyType)
-  out <- cbind(dataLINEX["-95% CI", "a_0"], dataLINEX["LINEX", "a_0"], dataLINEX["+95% CI", "a_0"],
-               dataLINEX["-95% CI", "c_t"], dataLINEX["LINEX", "c_t"], dataLINEX["+95% CI", "c_t"])
-  return(out)
-}
-
-###########################################
-# Creates a number of rows in a data.frame that contain information 
-# about the coefficients of a LINEX model for countryName and energyType
-# Each parameter has its own row with confidence intervals.
-# The country name is in a column. Which parameter is involved is
-# also in a column.
-# 
-# The return type is a data.frame.
-##
-linexCountryRowsForParamsGraph <- function(countryName, energyType){
-  #Create three rows, one for each parameter. Each row is a data.frame so that it is plottable!
-  dataLINEX <- linexData(countryName, energyType)
-  a_0Row <- data.frame(country = countryName, 
-                          parameter = "a_0", 
-                          lowerCI = dataLINEX["-95% CI", "a_0"], 
-                          value = dataLINEX["LINEX", "a_0"], 
-                          upperCI = dataLINEX["+95% CI", "a_0"])
-  c_tRow <- data.frame(country = countryName, 
-                         parameter = "c_t",
-                         lowerCI = dataLINEX["-95% CI", "c_t"],
-                         value = dataLINEX["LINEX", "c_t"],  
-                         upperCI = dataLINEX["+95% CI", "c_t"])
-  table <- rbind(a_0Row, c_tRow)
-  return(table)
-}
-
-#############################
-# Creates a graph with confidence intervals for the LINEX model for the given energyType
-##
-createLINEXParamsGraph <- function(energyType){
-  # Create a data table with the following columns:
-  # country abbrev, parameter (a_0, c_t), -95% CI, value, +95% CI
-  dataTable <- do.call("rbind", lapply(countryAbbrevs, linexCountryRowsForParamsGraph, energyType=energyType))
-  graph <- segplot(country ~ upperCI + lowerCI | parameter, 
-                   data = dataTable, 
-                   centers = value, #identifies where the dots should be placed
-                   draw.bands = FALSE, #provides nicer error bars
-                   horizontal = FALSE, #makes error bars vertical and puts the countries in the x axis
-                   layout = c(2,1), #2 column, 2 row
-                   index.cond = list(c(1,2)), #orders the panels as alpha, beta, lambda, gamma
-                   #set labels and bg color in strip
-                   strip = strip.custom(factor.levels=c("$a_0$", "$c_t$"), bg="white"),
-                   col = "black", #Sets line color to black
-                   lwd = 1, #Sets line width to 1.0
-                   ylim = list(c(-0.05, 1.0), c(-0.5, 5)), #y axis limits
-                   scales = list(cex=scaleTextSize, #controls text size on scales.
-                                 tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
-                                 x=list(cex=0.75), #reduces text size so that country abbrevs are legible
-                                 y=list(relation="free", #allow each axis to be different
-                                        at=list(c(0.0, 0.5, 1.0), c(0, 1, 2, 3, 4, 5))   #y tick marks
-                                 )
-                   )
-  )
-  return(graph)
-}
-
-############################
-# Aggregates the LINEX results into a big data table for the given energyType.
-##
-linexParamsTable <- function(energyType){
-  #Do rbind on the results of creating a row in the table for every country abbreviation that we know.
-  dataLINEX <- do.call("rbind", lapply(countryAbbrevs, linexCountryRow, energyType=energyType))
-  colnames(dataLINEX) <- c(" ", "$a_0$", " ", " ", "$c_t$",  " ")
-  rownames(dataLINEX) <- countryAbbrevs
-  tableLINEX <- xtable(dataLINEX, 
-                    caption=paste("LINEX model (with $", tolower(energyType), "$) parameters for 1980-2011 (US, UK, JP), 1991-2010 (CN and ZA), and 1991-2011 (SA, IR, TZ, and ZM).
-(Parameter estimates beneath symbol.
-95\\% confidence interval bounds to left and right.)", sep=""),
-                    label=paste("tab:LINEX_Parameters_With_", energyType, sep=""),
-                    digits = c(1, 2,2,2, 2,2,2),
-                    align = "r|ccc|ccc") #Sets alignment of the numbers in the columns
-  return(tableLINEX)
-}
-
-############################
-# Prints a table with parameters from a LINEX model for the given energyType. 
-##
-printLINEXParamsTable <- function(energyType){
-  print(linexParamsTable(energyType), 
-    caption.placement="top", 
-    sanitize.colnames.function = identity, 
-    size="\\tiny",
-    table.placement="H")
-}
-@
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-<<AIC_Table_Functions, eval=TRUE>>=
-###############################
-# Creates an xtable object that holds the AIC values for each parameter estimation that we include.
-##
-createAICTable <- function(){
-  ######################
-  # Single-factor models
-  ######################
-  # Single-factor with K
-  sfKModels <- lapply(countryAbbrevs, singleFactorModel, factor="K")
-  aicSFk <- data.frame(lapply(sfKModels, AIC))
-  rownames(aicSFk) <- "SF$k$"
-  # Single-factor with L
-  sfLModels <- lapply(countryAbbrevs, singleFactorModel, factor="L")
-  aicSFl <- data.frame(lapply(sfLModels, AIC))
-  rownames(aicSFl) <- "SF$l$"
-  # Single-factor with Q
-  sfQModels <- lapply(countryAbbrevs, singleFactorModel, factor="Q")
-  aicSFq <- data.frame(lapply(sfQModels, AIC))
-  rownames(aicSFq) <- "SF$q$"
-  # Single-factor with X
-  sfXModels <- lapply(countryAbbrevs, singleFactorModel, factor="X")
-  aicSFx <- data.frame(lapply(sfXModels, AIC))
-  rownames(aicSFx) <- "SF$x$"
-  # Single-factor with U
-  aicSFu <- cbind(US=AIC(singleFactorModel("US", "U")), 
-                  UK=AIC(singleFactorModel("UK", "U")), 
-                  JP=AIC(singleFactorModel("JP", "U")),
-                  CN=NA, ZA=NA, SA=NA, IR=NA, TZ=NA, ZM=NA) #No U data for these countries.
-  rownames(aicSFu) <- "SF$u$"
-  ######################
-  # Cobb-Douglas models
-  ######################
-  # Cobb-Douglas without energy
-  cdModels <- lapply(countryAbbrevs, cobbDouglasModel)
-  aicCD <- data.frame(lapply(cdModels, AIC))
-  rownames(aicCD) <- "CD"
-  # Cobb-Douglas with Q
-  cdQModels <- lapply(countryAbbrevs, cobbDouglasModel, energyType="Q")
-  aicCDq <- data.frame(lapply(cdQModels, AIC))
-  rownames(aicCDq) <- "CD$q$"
-  # Cobb-Douglas with X
-  cdXModels <- lapply(countryAbbrevs, cobbDouglasModel, energyType="X")
-  aicCDx <- data.frame(lapply(cdXModels, AIC))
-  rownames(aicCDx) <- "CD$x$"
-  # Cobb-Douglas with U
-  aicCDu <- cbind(US=AIC(cobbDouglasModel("US", "U")), 
-                  UK=AIC(cobbDouglasModel("UK", "U")), 
-                  JP=AIC(cobbDouglasModel("JP", "U")),
-                  CN=NA, ZA=NA, SA=NA, IR=NA, TZ=NA, ZM=NA) #No U data for these countries.
-  rownames(aicCDu) <- "CD$u$"
-  ######################
-  # CES models
-  ######################
-
-  ######################
-  # LINEX models
-  ######################
-  # LINEX with Q
-  linexQModels <- lapply(countryAbbrevs, linexModel, energyType="Q")
-  aicLINEXq <- data.frame(lapply(linexQModels, AIC))
-  rownames(aicLINEXq) <- "LINEX$q$"
-  # LINEX with X
-  linexXModels <- lapply(countryAbbrevs, linexModel, energyType="X")
-  aicLINEXx <- data.frame(lapply(linexXModels, AIC))
-  rownames(aicLINEXx) <- "LINEX$x$"  
-  # LINEX with U
-  aicLINEXu <- cbind(US=AIC(linexModel("US", "U")), 
-                  UK=AIC(linexModel("UK", "U")), 
-                  JP=AIC(linexModel("JP", "U")),
-                  CN=NA, ZA=NA, SA=NA, IR=NA, TZ=NA, ZM=NA) #No U data for these countries.
-  rownames(aicLINEXu) <- "LINEX$u$"
-
-  # Create the data.frame table
-  out <- rbind(aicSFk, aicSFl, aicSFq, aicSFx, aicSFu, aicCD, aicCDq, aicCDx, aicCDu, aicLINEXq, aicLINEXx, aicLINEXu) 
-  # Create the xtable with caption and label
-  out <- xtable(out, caption="AIC values for all models.", label="tab:AICTable", digits=1)
-  return(out)
-}
-@
 

### 2013-03-04 EconGrowth-R-Functions.Rnw
Now creating graphs for ZA in the presentation. But, they are too large.

@@
 opts_chunk$set(
+  # ********************************************************************************************************
+  eval=TRUE,
+  # ********************************************************************************************************
   dev='tikz',    #Allows LaTeX code in graphical output. E.g., "$y$" for a variable name in the legend for a graph.
@@
 
-cdModel("US")
-
 ####################
@@
 ##
-cdGrid <- function(countryAbbrev, energyType, gammaGrid){
+cdeGridData <- function(countryAbbrev, energyType, gammaGrid){
   gamma <- gammaGrid
@@
 
+#############################
+# This function creates a series of graphs for Cobb-Douglas with energy functions
+# showing various parameters as a function of gamma.
+##
+cdeGridGraphs <- function(countryAbbrev, energyType){
   gammaGrid <- seq(0.0, 0.95, by=0.05)
-# print("US")
-# models <- cdGrid("US", "Q", gammaGrid)
-# SSE <- lapply(models, function(model) summary(model)$sigma)
-# data <- cbind(gammaGrid, SSE)
-# plot(gammaGrid, SSE)
-# print(coef(models[[2]]))
-# 
-print("ZA")
-models <- cdGrid("ZA", "Q", gammaGrid)
+  #print(paste(countryAbbrev, energyType))
+  models <- cdeGridData(countryAbbrev, energyType, gammaGrid)
   SSE <- lapply(models, function(model) summary(model)$sigma)
@@
   plot(gammaGrid, alpha)
-
-# Some code to debug the Cobb-Douglas models. Randy Pruim is helping on this.
-
-# print("cobbDouglasModel(US, Q) works fine:")
-# us <- cobbDouglasModel("US", "Q")
-# print(summary(us))
-# print(confint(us))
-# 
-# print("cobbDouglasModel(ZA) works fine")
-# za <- cobbDouglasModel("ZA")
-# print(summary(za))
-# print(confint(za))
-# 
-# print("cobbDouglasModel(ZA, Q) stops before convergence achieved,")
-# print("and confint gives NA values:")
-# za <- cobbDouglasModel("ZA", "Q")
-# print(summary(za))
-# print(confint(za))
-# 
-# print("cobbDouglasModel(UK, Q) also stops before convergence achieved,")
-# print("but confint does not produce NA values:")
-# uk <- cobbDouglasModel("UK", "Q")
-# print(summary(uk))
-# print(confint(uk))
-
-# save(us, za, uk, file="HeunModels-US-ZA-UK.Rdata")
+}
 

### 2013-03-04 EconGrowth.Rnw
Now creating graphs for ZA in the presentation. But, they are too large.

@@
 # Includes the Functions.Rnw file that contains all of the functions for analyzing our economic data.
-opts_chunk$set(
-  # ********************************************************************************************************
-  eval=TRUE,
-  # ********************************************************************************************************
-  warning=TRUE,  #Tells whether to show warnings in the output.
-  message=FALSE, #Turns off messages for all chunks. Set TRUE on an individual chunk to see it.
-  echo=FALSE     #Tells whether to echo code for all chunks. Set TRUE on an individual chunk to see its code.
-) 
 @
@@
 \subsection{Cobb-Douglas with thermal energy ($q$)}
+
+The Cobb-Douglas with energy parameter estimation process is problematic. The following graphs show that the minimum of the squared-errors curve occurs at the point where $\beta$ --> 0.0.
+
+<<CDeGammaGraphsZA, eval=TRUE>>=
+  cdeGridGraphs("ZA", "Q")
+@
 

### 2013-03-04 EconGrowthSeminar.Rnw
Allowing .pdf graphics in the repository now. Also, clearing a lot of old files with .aux and .spl extensions.
Now creating graphs for ZA in the presentation. But, they are too large.

@@
 
-\begin{document}
+\begin{document} %**************************************************
 
-\begin{frame}
+\begin{frame} %----------------------------
   \titlepage
@@
 
-\begin{frame}{Outline}
+\begin{frame}{Outline} %----------------------------
   \tableofcontents
@@
 
-% Since this a solution template for a generic talk, very little can
-% be said about how it should be structured. However, the talk length
-% of between 15min and 45min and the theme suggest that you stick to
-% the following rules:
-
-% - Exactly two or three sections (other than the summary).
-% - At *most* three subsections per section.
-% - Talk about 30s to 2min per frame. So there should be between about
-%   15 and 30 frames, all told.
+<<setup_child, child='EconGrowth-R-Functions.Rnw', echo=FALSE, message=FALSE, eval=TRUE>>=
+# Includes the Functions.Rnw file that contains all of the functions for analyzing our economic data.
+@
 
@@
   \begin{center}
-    \includegraphics[height=2.5cm]{figure/Figure_Growth_Models.pdf}
+    \includegraphics[height=2.5cm]{figure_other/Figure_Growth_Models.pdf}
   \end{center}
@@
 \begin{frame}{Example Cobb-Douglas Fit} %----------------------------
-  Heun complete
+<<CDeGammaGraphsZA, eval=TRUE>>=
+  cdeGridGraphs("ZA", "Q")
+@
 \end{frame}
@@
 
-\end{document}
+\end{document} %**************************************************

### 2013-03-06 EconGrowth-R-Functions.Rnw
Now including the capability for the historical data graph function to create a graph with only 1 country in it. Still needs to be prettified for the seminar, but it is working!
Also, added several figures from papers.

@@
 countryAbbrevs <- c(US="US", UK="UK", JP="JP", CN="CN", ZA="ZA", SA="SA", IR="IR", TZ="TZ", ZM="ZM")
+countryAbbrevsAlph <- c(CN="CN", IR="IR", JP="JP", SA="SA", TZ="TZ", UK="UK", US="US", ZA="ZA", ZM="ZM")
 countryAbbrevsU <- c(US="US", UK="UK", JP="JP") #Only these countries have useful work data
@@
 ninePanelLayoutSpec <- c(3,3) #indicates a 3x3 arrangement of panels.
+onePanelLayoutSpec <- c(1,1) #indicates a 1x1 arrangement of panels.
 ninePanelGraphWidth <- maxWidth     
 ninePanelGraphHeight <- 7.5  #Inches
+presentationGraph1RowHeight <- 2 #Inches
+presentationGraph2ColWidth  <- 2 #Inches
 keyTextSize <- 0.85 #85% of normal size
@@
 ####################################
-# Creates a graph that displays all of the factors of production for all countries.
-##
-createHistoricalLatticeGraph <- function(){
-  dataTable <- loadData("All")
+# Creates a graph that displays all of the factors of production for all countries (if you leave off countryAbbrev)
+# or a specific country (if you supply a 2-letter abbreviation for a country that we know).
+##
+createHistoricalLatticeGraph <- function(countryAbbrev){
+  # Code for all graphs, regardless of whether we want to focus on a specific country
   graphType <- "b" #b is for both line and symbol
@@
   lineWidths <- c(0, 2, 2, 1, 1, 1) #line widths. 0 means no line.
+  yTics <- c(1,2,3,4,5,6,7,8,9,10) #y tic mark locations.
   colors <- c("black", "black", "black", "red", "blue", "darkorange") #line and symbol colors
   symbols <- c(1, NA, NA, NA, NA, NA)  #NA gives no symbol.
+  #y axis limits for countries in alphabetical order.
+  yLimits <- list(c(1,10), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4)) 
+  # Code that deals with items that are specific to whether we want all countries or a specific country.
+  if (missing(countryAbbrev)){
+    # We want a graph with panels for all countries
+    dataTable <- loadData("All")
+    factorLevels <- countryNamesAlph # We want all countries shown
+    indexCond <- list(countryOrderForGraphs) # We want all countries in this order
+    layout <- ninePanelLayoutSpec # Show all countries
+  } else {
+    # We want only a specific country
+    dataTable <- loadData(countryAbbrev)
+    # Select the correct y limits
+    index <- which(countryAbbrevsAlph %in% countryAbbrev)
+    yLimits <- yLimits[index:index]                   # Pick limits for the country we want.
+    factorLevels <- countryNamesAlph[index:index]     # Only show the country we have chosen.
+    indexCond <- list(c(1))                           # We want only one country.
+    layout <- onePanelLayoutSpec                      # We want only one panel in the graph.
+  }
   graph <- xyplot(iGDP+iCapStk+iLabor+iQ+iX+iU ~ Year | Country, data=dataTable,
                   type = graphType,
-                  index.cond = list(countryOrderForGraphs), #orders the panels.
-                  layout = ninePanelLayoutSpec, 
-                  strip = strip.custom(factor.levels=countryNamesAlph, bg="white"), #Sets strip parameters
+                  index.cond = indexCond, #orders the panels.
+                  layout = layout, 
+                  strip = strip.custom(factor.levels=factorLevels, bg="white"), #Sets strip parameters
                   as.table = TRUE, #indexing of panels starts in upper left and goes across rows.
@@
                               tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
-                              y=list(relation="free", #allows each axis to be different
-                                     at=c(1,2,3,4,5,6,7,8,9,10) #tick mark locations
-                                     )
-                              ),
-                  ylim=list(c(1,10), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4)), #y axis limits
-                  xlab="", ylab="Indexed (1980=1 or 1991=1)") #axis labels
+                              y=list(relation="free", at=yTics)), #allows each axis to be different
+                  ylim=yLimits, #y axis limits
+                  xlab="", 
+                  ylab="Indexed (1980=1 or 1991=1)") #axis labels
   return(graph)

### 2013-03-06 EconGrowth.Rnw
Now including the capability for the historical data graph function to create a graph with only 1 country in it. Still needs to be prettified for the seminar, but it is working!
Also, added several figures from papers.

@@
 
-The Cobb-Douglas with energy parameter estimation process is problematic. The following graphs show that the minimum of the squared-errors curve occurs at the point where $\beta$ --> 0.0.
+The Cobb-Douglas with energy parameter estimation process is problematic. The following graphs show that the minimum of the squared-errors curve occurs at the point where $\beta \rightarrow 0.0$.
 
-<<CDeGammaGraphsZA, eval=TRUE>>=
+<<CDeGammaGraphsZA>>=
   cdeGridGraphs("ZA", "Q")

### 2013-03-06 EconGrowthSeminar.Rnw
Now including the capability for the historical data graph function to create a graph with only 1 country in it. Still needs to be prettified for the seminar, but it is working!
Also, added several figures from papers.

@@
+<<setup_child, child='EconGrowth-R-Functions.Rnw', echo=FALSE, message=FALSE, eval=TRUE>>=
+# Includes the Functions.Rnw file that contains all of the functions for analyzing our economic data.
+@
+
 \documentclass{beamer}
@@
 }
+
+% Code to get a bibliography working. See notes at http://judsonsnotes.com/notes/index.php?option=com_content&view=article&id=641:bibliography-in-beamer&catid=60:latex&Itemid=84
+\def\newblock{\hskip .11em plus .33em minus .07em}
 
@@
 
-<<setup_child, child='EconGrowth-R-Functions.Rnw', echo=FALSE, message=FALSE, eval=TRUE>>=
-# Includes the Functions.Rnw file that contains all of the functions for analyzing our economic data.
-@
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\begin{frame}{Cleveland, 1984} %----------------------------
-  Show Cleveland's graph and cover of \emph{Science} here.
+\begin{frame}{Energy and GDP are Linked}%{\citet{Cleveland:1997p5055}} %----------------------------
+  \begin{columns}[c]
+    \column{2.0in}
+      \includegraphics[width=2.0in]{figure_other/Figure_Cleveland_1984.pdf}
+    \column{1.5in}
+      \includegraphics[width=1.5in]{figure_other/Figure_Cleveland_1984_Science_Cover.pdf}
+  \end{columns}
 \end{frame}
@@
 \begin{frame}{Energy Cost Share and Economic Growth} %----------------------------
-  Show graphs of energy cost share and recessions
+  \begin{center}
+    \includegraphics[height=6.3cm]{figure_other/Figure_Bashmakov_2007.pdf}
+  \end{center}
+%  \citet{Bashmakov:2007ek}
 \end{frame}
@@
 \begin{frame}{Example Cobb-Douglas Fit} %----------------------------
-<<CDeGammaGraphsZA, eval=TRUE>>=
+<<CDeGammaGraphsZA>>=
   cdeGridGraphs("ZA", "Q")
@@
   Caleb complete
+\end{frame}
+
+\begin{frame}[fragile]{Example Data}
+
+<<Historical_Data, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H", fig.cap="Historical data.
+Indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$).", eval=TRUE>>=
+createHistoricalLatticeGraph("US")
+@
+
 \end{frame}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Bibliography}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% See hints at http://judsonsnotes.com/notes/index.php?option=com_content&view=article&id=641:bibliography-in-beamer&catid=60:latex&Itemid=84
+\begin{frame}{Bibliography} %----------------------------
+\bibliographystyle{model2-names}
+\bibliography{EconGrowth.bib}
+\end{frame}
+
 \end{document} %**************************************************

### 2013-03-06 EconGrowth-R-Functions.Rnw
Now including a ZA graph for example data.

@@
     index <- which(countryAbbrevsAlph %in% countryAbbrev)
+    # The following lines use [index:index] as a convenient way of subsetting.
+    # This has the added benefit of maintaining the correct classes for things.
     yLimits <- yLimits[index:index]                   # Pick limits for the country we want.

### 2013-03-06 EconGrowthSeminar.Rnw
Now including a ZA graph for example data.

@@
 
-\begin{frame}[fragile]{Example Data}
-
-<<Historical_Data, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H", fig.cap="Historical data.
-Indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$).", eval=TRUE>>=
+\begin{frame}{Example Data}
+  \begin{columns}[c]
+    \column{2.0in}
+<<Historical_Data_US, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H", eval=TRUE>>=
 createHistoricalLatticeGraph("US")
 @    
+    \column{2.0in}
+<<Historical_Data_ZA, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H", eval=TRUE>>=
+createHistoricalLatticeGraph("ZA")
+@
+  \end{columns}
 

### 2013-03-06 EconGrowth-R-Functions.Rnw
Partially implemented a solution for scaling the text in a beamer graph. Working on the graph of the historical data.

@@
 ninePanelGraphHeight <- 7.5  #Inches
-presentationGraph1RowHeight <- 2 #Inches
+presentationGraph1RowHeight <- 3 #Inches
 presentationGraph2ColWidth  <- 2 #Inches
@@
 # or a specific country (if you supply a 2-letter abbreviation for a country that we know).
-##
-createHistoricalLatticeGraph <- function(countryAbbrev){
+# Provide a value for textScaling to scale the size of the text on the graph. This is expecially useful
+# for converting between graphs in a paper and graphs in a beamer presentation.
+# textScaling = 1.0 is good for a paper. textScaling = 0.6 is good for a beamer presentation.
+##
+createHistoricalLatticeGraph <- function(countryAbbrev, textScaling = 1.0){
   # Code for all graphs, regardless of whether we want to focus on a specific country
@@
                   layout = layout, 
-                  strip = strip.custom(factor.levels=factorLevels, bg="white"), #Sets strip parameters
+                  strip = strip.custom(factor.levels=factorLevels, 
+                                       bg="transparent"), #Sets strip parameters
                   as.table = TRUE, #indexing of panels starts in upper left and goes across rows.
@@
                            type=graphType,
-                           cex=keyTextSize, #controls size of text in the key
+                           cex=keyTextSize * textScaling, #controls size of text in the key
                            lines=list(lty=lineTypes, lwd=lineWidths), #controls line types
@@
                            columns=keyColumns, x=keyXLoc, y=keyYLoc), #controls columns and position of the key
-                  scales=list(cex=scaleTextSize, #controls text size on scales.
+                  scales=list(cex=scaleTextSize * textScaling, #controls text size on scales.
                               tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
-                              y=list(relation="free", at=yTics)), #allows each axis to be different
+                              y=list(relation="free",  #allows each axis to be different
+                                     at=yTics, #specifies location for tics
+                                     tck=scaleTickSize)), #scales text on the axis
                   ylim=yLimits, #y axis limits

### 2013-03-06 EconGrowthSeminar.Rnw
Partially implemented a solution for scaling the text in a beamer graph. Working on the graph of the historical data.

--- 2013-03-06 EconGrowthSeminar.Rnw
@@
 # Includes the Functions.Rnw file that contains all of the functions for analyzing our economic data.
+@
+
+<<global_params>>=
+textScaleForGraphs <- 0.6 # Controls text scaling in graphs
 @
@@
 
-\begin{frame}{Economic Data}
+\begin{frame}{Economic Data} %----------------------------
   Lucas complete
@@
 
-\begin{frame}{Energy Data}
+\begin{frame}{Energy Data} %----------------------------
   Caleb complete
@@
 
-\begin{frame}[fragile]{Example Data}
+\begin{frame}{Example Data} %----------------------------
 
-<<Historical_Data, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H", fig.cap="Historical data.
-Indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$).", eval=TRUE>>=
-createHistoricalLatticeGraph("US")
+  \begin{columns}[c]
+    \column{2.2in}
+<<Historical_Data_US, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H", eval=TRUE>>=
+createHistoricalLatticeGraph("US", textScaling=0.6)
 @    
+    \column{2.2in}
+<<Historical_Data_SA, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H", eval=TRUE>>=
+createHistoricalLatticeGraph("SA", textScaling=textScaleForGraphs)
+@
+  \end{columns}
 
@@
 
-\begin{frame}{US Single Factor}
+\begin{frame}{US Single Factor} %----------------------------
   Heun complete
@@
 
-\begin{frame}{US Cobb-Douglas}
+\begin{frame}{US Cobb-Douglas} %----------------------------
   Heun complete
@@
 
-\begin{frame}{US CES}
+\begin{frame}{US CES} %----------------------------
   Heun complete
@@
 
-\begin{frame}{US LINEX}
+\begin{frame}{US LINEX} %----------------------------
   Heun complete
@@
 
-\begin{frame}{ZA Single Factor}
+\begin{frame}{ZA Single Factor} %----------------------------
   Heun complete
@@
 
-\begin{frame}{ZA Cobb-Douglas}
+\begin{frame}{ZA Cobb-Douglas} %----------------------------
   Heun complete
@@
 
-\begin{frame}{ZA CES}
+\begin{frame}{ZA CES} %----------------------------
   Heun complete
@@
 
-\begin{frame}{ZA LINEX}
+\begin{frame}{ZA LINEX} %----------------------------
   Heun complete
@@
 
-\begin{frame}{Results}
+\begin{frame}{Results} %----------------------------
   Heun complete

### 2013-03-07 EconGrowth-R-Functions.Rnw
Now scaling the y axis label in the historical data graph.
Now the text in the Strip of the historical data graph is scaled appropriately.

@@
 # Other graph parameters that apply to all graphs
-scaleTextSize <- 1.0  #Multiple of normal size
+scaleTextSize <- 0.8  #Multiple of normal size
 scaleTickSize <- -0.5 #50% of normal size and pointing INWARD!
@@
                   strip = strip.custom(factor.levels=factorLevels, 
-                                       bg="transparent"), #Sets strip parameters
+                                       bg="transparent",
+                                       par.strip.text=list(cex=textScaling)
+                                       ), #Sets strip parameters
                   as.table = TRUE, #indexing of panels starts in upper left and goes across rows.
@@
                   xlab="", 
-                  ylab="Indexed (1980=1 or 1991=1)") #axis labels
+                  ylab=list(label="Indexed (1980=1 or 1991=1)", cex=textScaling)
+                  ) #axis labels
   return(graph)

### 2013-03-07 EconGrowth-R-Functions.Rnw
Now filling the background of the historical data plot with white.

@@
 ninePanelGraphHeight <- 7.5  #Inches
-presentationGraph1RowHeight <- 3 #Inches
+presentationGraph1RowHeight <- 2.8 #Inches
 presentationGraph2ColWidth  <- 2 #Inches
@@
                   layout = layout, 
-                  strip = strip.custom(factor.levels=factorLevels, 
-                                       bg="transparent",
-                                       par.strip.text=list(cex=textScaling)
-                                       ), #Sets strip parameters
+                  # This next code fills the background of the graph panels with white.
+                  panel = function(...) {
+                      panel.fill(col = "white")
+                      panel.xyplot(...)
+                  },
+                  # Sets strip parameters
+                  strip = strip.custom(factor.levels=factorLevels, # Sets text for factor levels
+                                       bg="white", # Sets background color to white
+                                       par.strip.text=list(cex=textScaling) # Scales text in the strip.
+                                       ),
                   as.table = TRUE, #indexing of panels starts in upper left and goes across rows.

### 2013-03-07 EconGrowth-R-Functions.Rnw
Added Caleb's text in the introduction.

@@
   #Tells whether to cache output from chunks are saved. Cacheing saves time. 
-  #However, references to LaTeX tables DO NOT WORK if cacheing is turned on (cache=TRUE).
+  #However, references to LaTeX tables DO NOT WORK if cacheing is turned on (i.e., cache=TRUE).
   cache=FALSE,
@@
 keyColumns <- 1 #Want only 1 column in the key for lattice graphs
-keyXLoc <- 0.01 #x position of the key
-keyYLoc <- 0.95 #y position of the key
+defaultKeyXLoc <- 0.01 #x position of the key. This default is good for 9-panel graphs.
+defaultKeyYLoc <- 0.95 #y position of the key. This default is good for 9-panel graphs.
 # Parameter graphs are tricky to ensure same size. I've found that with height set to 5 in for the 
@@
 # textScaling = 1.0 is good for a paper. textScaling = 0.6 is good for a beamer presentation.
-##
-createHistoricalLatticeGraph <- function(countryAbbrev, textScaling = 1.0){
+# keyXLoc and keyYLoc are locations for the graph's legend.
+##
+createHistoricalLatticeGraph <- function(countryAbbrev, textScaling = 1.0, keyXLoc = defaultKeyXLoc, keyYLoc = defaultKeyYLoc){
   # Code for all graphs, regardless of whether we want to focus on a specific country
@@
   lineWidths <- c(0, 2, 2, 1, 1, 1) #line widths. 0 means no line.
+  xTics <- c(1980, 1990, 2000, 2010)
   yTics <- c(1,2,3,4,5,6,7,8,9,10) #y tic mark locations.
@@
                   layout = layout, 
-                  # This next code fills the background of the graph panels with white.
-                  panel = function(...) {
-                      panel.fill(col = "white")
-                      panel.xyplot(...)
-                  },
                   # Sets strip parameters
                   strip = strip.custom(factor.levels=factorLevels, # Sets text for factor levels
-                                       bg="white", # Sets background color to white
+                                       bg="transparent", # Sets background transparent to match the graph itself.
                                        par.strip.text=list(cex=textScaling) # Scales text in the strip.
@@
                               tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
+                              x=list(at=xTics),
                               y=list(relation="free",  #allows each axis to be different
-                                     at=yTics, #specifies location for tics
-                                     tck=scaleTickSize)), #scales text on the axis
+                                     at=yTics)), #specifies location for tics
                   ylim=yLimits, #y axis limits
-                  xlab="", 
+                  #axis labels and scaling
+                  xlab=list(label="", cex=textScaling), 
                   ylab=list(label="Indexed (1980=1 or 1991=1)", cex=textScaling)
-                  ) #axis labels
+                  ) 
   return(graph)

### 2013-03-07 EconGrowth.Rnw
Added Caleb's text in the introduction.

@@
 
-*********** Caleb, put your LaTeX code here. *************
+\subsection{Background}
+
+Neoclassical economic growth theory attributes output growth to growth rates of factors of production: capital stock and labor.
+In 1928, Amherst Professors Charles Cobb and Paul Douglas created the Cobb-Douglas production function that predicted manufacturing output (\textit{y}) as a function of labor (\textit{l}) and capital (\textit{k}) (MISHRA, 2007).
+
+\begin{equation}
+  y_\mathrm{C-D} = A(t) k^\alpha l^\beta
+\end{equation}
+
+\begin{equation}
+  y \equiv Y/Y_\mathrm{0}
+\end{equation}
+
+\begin{equation}
+  k \equiv K/K_\mathrm{0}
+\end{equation}
+
+\begin{equation}
+  l \equiv L/L_\mathrm{0}
+\end{equation}
+
+In the Cobb-Douglas production function, capital and labor are related to output with an elasticity of unity, indicating constant returns to scale.
+
+\begin{equation}
+  \alpha + \beta = 1
+\end{equation}
+
+Using only labor and capital factors of production, neoclassical economic growth theory cannot predict the growth of the U.S. economy over the last 100 years.
+
+%Figure 1 goes here
+
+So, an exogenous "technological progress" term (\textit{A(t)}) is often included to better predict historical economic growth as a function of capital and labor factors of production.
+For the U.S., the \textit{A(t)} parameter is necessary: without it, the theory cannot accurately describe historical economic performance.
+
+Neoclassical economic growth theory makes no attempt to understand the mechanisms by which technological progress affects economic growth, nor does it attempt to say how technological progress might vary from one economy to the next.
+Mathematically, technological progress is nothing more than a fitting parameter that aligns the predictions of equation 1 with historical data.
+
+As shown in Equation 1 above, neoclassical economic theory neglects the role of energy input to the economy.
+However, (BASHMAKOV, 2007) and (MURPHY, 2011) indicate that the influence of energy on economic growth may far outweigh its cost share in the economy.
+That neoclassical economic growth theory ignores energy input is, therefore, cause for concern, and an inquiry into the proper approach to including energy as a factor of production in growth modeling is therefore, extremely relevant.
+
+Many energy economists include energy as a factor of production (along with capital stock and labor) to improve predictions of historical economic growth.
+But, there is little agreement on how this should be done.
+Neither the mathematical form of the production function, nor which type of energy should be considered (thermal energy, exergy, of useful work) are consistent in the literature.
+Furthermore, there has been little empirical work done to assess the predictive ability of various energy-including production functions for different types of economies.
+This paper attempts to contribute to our understanding in these important areas.
+
+\subsection{Mathematical Forms of the Production Function}
+Many energy-including production functions have been used to predict economic growth.
+Three prominent functions are the Cobb-Douglas production function with an energy input as used by (AYRES AND WARR, 2008), the Stern Constant Elasticity of Substitution (CES) production function (STERN, 2010), and K\"{u}mmel's Linear Exponential (LINEX) production function (KUMMEL, 1980).
+
+Similar to the Cobb-Douglas production function without an energy term, the Cobb-Douglas production function with energy (\textit{e}) includes constant returns to scale for the three factors of production.
+
+\begin{equation}
+  y_\mathrm{C-D} = A(t)k^\alpha l^\beta e^\gamma
+\end{equation}
+
+\begin{equation}
+  e \equiv E/E_\mathrm{0}
+\end{equation}
+
+\begin{equation}
+  \alpha + \beta + \gamma = 1
+\end{equation}
+
+(AYRES AND WARR, 2009) use this production function with useful work and exergy being the energy factors of production to descrive historic Japanese and American economies from 1900-2000.
+(FROLING, 2009) also uses a Cobb-Douglas production function with a thermal energy input to describe output for the global economy from 1800-1970.
+Fr\"{o}ling's Cobb-Douglas production function endogenizes labor with respect to fertility and mortality rates and separates the thermal energy factor of production into two types: biomass energy and coal energy.
+(SERRENHO, 2010) uses the Cobb-Douglas derivative with a thermal energy factor of production to describe output for the EU-15 countries.
+Serrenho divides the thermal energy factor into energy consumption from renewables, non-renewables, wastes, and imports.
+
+Other energy economists use the Constant Elasticity of Substitution (CES) production function to describe economic growth with an energy factor of production.
+(VAN DER WERF, 2007) models various nested CES production functions for 12 OECD (Organisation for Economic Co-operating and Development) countries with respect to climate change policy.
+van der Werf concludes that (KL)E nesting structure (capital and labor combined, then energy added) best fits the historic data.
+(LECCA, 2011) also models a variety of CES production functions using a KLEM structure to determine how the energy factor of production's location affects results stability.
+(STERN, 2011) uses a CES production function that has a Cobb-Douglas production function embedded into the CES production function, following the (KL)E format.
+
+\begin{equation}
+  y_\mathrm{CES} = \bigg{[} (1-\zeta)(A_\mathrm{L} l^\beta k^{1-\beta})^\phi + \zeta(A_\mathrm{E} e)^\phi \bigg{]} ^\frac{1}{\phi}
+\end{equation}
+
+\begin{equation}
+  \phi = \frac{\sigma-1}{\sigma}
+\end{equation}
+
+Where $A_\mathrm{L}$ is the augmentation indice for labor and capital, $A_\mathrm{E}$ is the augmentation indice for energy, $\sigma$ is the elasticity of substitution between energy and value added aggregate, and $\zeta$ is the relative importance of labor/capital and energy.
+The elasticity of substitution between the capital and labor term and the energy term is less than unity, reflecting a minimum energy requirement for economic output.
+Stern applies his CES function to the Swedish economy from 1800-2000, which reflects the significance in the transfer from wood to more energy-intensive fossil fuel sources in promoting economic growth.
+
+The final production function chosen for our comparison was the (KUMMEL, 1980, 1985, 2002) LINEX production function.
+
+\begin{equation}
+  y_\mathrm{LINEX} = e \textrm{exp} \bigg{[} a_\mathrm{0} \bigg{(} 2-\frac{l+e}{k} \bigg{)} + a_\mathrm{0} c_\mathrm{t} \bigg{(} \frac{l}{e} - 1 \bigg{)} \bigg{]}
+\end{equation}
+
+\begin{equation}
+  a = a_\mathrm{0} \frac{l + e}{k}
+\end{equation}
+
+\begin{equation}
+  \beta = a_\mathrm{0} \bigg{(} c_\mathrm{t} \frac{l}{e} - \frac{l}{k} \bigg{)}
+\end{equation}
+
+\begin{equation}
+  \gamma = 1 - \frac{a_\mathrm{0} e}{k} - a_\mathrm{0} c_\mathrm{t} \frac{l}{e}
+\end{equation}
+
+Where $a_\mathrm{0}$ is a parameter representing capital efficiency and $c_\mathrm{t}$ is a parameter representing energy demand.
+(KUMMEL, 1980) inserted an energy factor of production into the Cobb-Douglas derivative, then assumed constant elasticity for the energy, labor, and capital factors of production.
+(KUMMEL, 1985) then partially integrated the Cobb-Douglas derivative to form the LINEX production function.
+K\"{u}mmel uses his LINEX production function to describe economic output for the economies of the U.S., Japan, and Germany (KUMMEL, 2002).
+(AYRES AND WARR, 2010) compare the LINEX production function with the Cobb-Douglas production function to assess economic growth for Austria, the United Kingdom, the United States, and Japan.
+
+\subsection{Quantification of Energy}
+The literature shows three types of energy used in production functions: thermal energy, exergy, and useful work.
+Thermal energy ($e$) is the heat content of an energy carrier.
+Exergy ($x$) is the maximum useful work that can be extracted from an energy carrier by a process that brings the system into equilibrium with a heat reservoir (typically the surrounding environment).
+Useful work ($u$) includes the direct energy that goes into an economy, including work from machines, human muscles, and animals.
+Most energy economists have used thermal energy for the energy factor of production in the production function, including (STERN, 2011), (FROLING, 2009), (SERRENHO, 2010), and (KUMMEL, 1980, 1985, 2002).
+(AYRES AND WARR, 2009) introduced the idea of using exergy and useful work in a production function in order to include the importance of efficiency gains in energy production over the last century.
+Little work has been done comparing the predictive ability of each type of energy quantification in production functions.
+
+%Figure 2 goes here.
+
+(ADD FIG REF) exemplifies the importance of the quantification of energy's effect on growth modeling.
+The indexed values of $e$, $x$, and $u$ have very different growth rates.
+In particular, $u$ grows faster than either $e$ or $x$ due to efficiency gains in economies.
+The quantification of energy as $u$ suggests that perhaps technological progress $A(t)$ is a proxy for increasing energy efficiency in the U.S.
+economy.
+
+\subsection{Economy Types}
+
+In most economic growth literature, economists assess developed economies primarily from North America or Europe.
+Examples of developed economies being assessed include (KUMMEL, 1980) applying LINEX to describe the West German economy, (SERRENHO, 2010) applying Cobb-Douglas variants to EU-15 countries, (VAN DER WERF, 2007) applying CES nesting variants to the 12 OECD countries, (LECCA, 2011) applying CES nesting variants to the Scottish economy, (STERN, 2011) applying CES to describe the Swedish economy, and (AYRES AND WARR, 2010) using LINEX and Cobb-Douglas to describe the Austrian, American, British, and Japanese economies.
+There is a need to evaluate economies at all stages of growth.
+
+%Table 1 goes here.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Models and methodology}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Production function selection}
+The production functions chosen for comparison were the Cobb-Douglas production function, the CES production function, and the LINEX production function.
+These three production functions were all treated as exogenous, with inputs of capital, labor, and energy (or exergy in the case of this paper's analysis).
+All three of the production functions are derived from the fundamental growth equation.
+
+\begin{equation}
+  \frac{1}{y} \frac{dy}{dt} = \alpha \frac{1}{k} \frac{\partial k}{\partial t} + \beta \frac {1}{l} \frac{\partial l}{\partial t} + \gamma \frac{1}{e} \frac{\partial e}{\partial t}
+\end{equation}
+
+Integrating equation 1 with differing solutions of $\alpha$, $\beta$, and $\gamma$ yields the various production functions.
+In order to satisfy the condition of constant returns to scale, $\alpha + \beta +\gamma = 1$ in all cases.
+The bounds for the elasticities are: $0 \le \alpha \le 1$, $0 \le \beta \le 1$, and $0 \le \gamma \le 1$.
+
+The Cobb-Douglas production function was chosen because it is one of the most commonly used in econometric modeling.
+The Cobb-Douglas production function is the result of partially integrating equation 11 from ($y_\mathrm{0}$, 1, 1, 1) to ($y_\mathrm{final}$, k, l, e) and assuming trivial values of $\alpha$, $\beta$, and $\gamma$ ($\alpha_\mathrm{0}$, $\beta_\mathrm{0}$, $\gamma_\mathrm{0}$).
+The Cobb-Douglas function is most commonly written as a function of capital and labor.
+A modified form can also be used where energy is a third term.
+The technological progress term, $A(t)$, is a multiplier representing total factor productivity; to account for some portion of the output that is only dependent on time and unaccounted for by labor and capital.
+The other production functions were compared to the basic Cobb-Douglas function to gain an understanding of how energy is intertwined with capital and labor.
+A modified version of the Cobb-Douglas with energy was also modeled to see how adaptive the function is and to examine if the total factor productivity term could be partially explained by energy.
+
+The CES production functions are a family of production functions that are starting to become more widely used in economic modeling.
+(MISHRA, 2007) covers a wide variety of production functions that are members of the CES family.
+The CES form that we chose to use is from (STERN, 2011, 2012), which embeds a Cobb-Douglas function in a CES function (see equation 8).
+Since Stern's function is embedded with a Cobb-Douglas function, it reduces to the standard Cobb-Douglas form as $\sigma \rightarrow 1$ and $\gamma \rightarrow 0$.
+
+The LINEX production function was chosen because it approaches growth from a perspective that combines elements of thermodynamics and economics (see equation 10).
+The form of the LINEX function being used is taken from (KUMMEL, 1980, 1985, 2002), with a linear dependence on energy and an exponential dependence on capital and labor.
+The LINEX function is a result of using the simplest non-trivial solutions of $\alpha$, $\beta$, and $\gamma$ (see equation 11, 12, and 13).
+The variables $a_\mathrm{0}$ and $c_\mathrm{t}$ are constant over a given period of time.
+The greatest advantage of the LINEX function is the time dependent output elasticities.
+It seems more plausible that these values would change over time as a country nears the demographic transition and shifts from using physical labor to more energy for industrialization.
+
+The combination of these four types of production functions (Cobb-Douglas, Cobb-Douglas with energy, LINEX, and Stern-CES) allowed us to get a sense of the true effects of energy on economic growth modeling.
+
+\subsection{Country and economy type selection}
+In this paper we analyze economies at all stages of economic growth.
+We selected at least two economies from each of the following categories: the developed economies, which are economies that are technologically advanced with high standards of living; developing economies, which experience rapid economic growth but are still subject to low standards of living; the petrol economies, which depend on petroleum as a substantial source of GDP; and the Malthusian economies, which maintain living standards near subsistence levels.
+We analyzed the developed economies of the United States, the United Kingdom, and Japan for the period 1980-2011.
+We analyze two developing economies for 1991-2011: South Africa and China.
+The petrol economies analyzed for 1991-2011 are Iran and Saudi Arabia.
+Finally, the Malthusian economies analyzed from 1991-2011 are Tanzania and Zambia.
+
+\section{Data sources and data collection}
+\subsection{Output}
+We take real gross domestic product to be an appropriate, if imperfect proxy for output.
+Real gross domestic product data in real 2005 U.S.
+dollars for the United States, the United Kingdom, and Japan for 1980-2011 is from the World Bank's Global Economic Prospects (GEP) database (WORLD BANK, 2012).
+Real GDP data in real 2005 U.S.
+dollars for South Africa, China, Iran, Saudi Arabia, Tanzania, and Zambia for 1991-2011is from the World Bank's Global Economic Prospects database (WORLD BANK, 2012).
+
+\subsection{Capital stock}
+Gross capital stock for the United States, the United Kingdom, and Japan for 1980-2011 in real 2005 U.S.
+dollars is from the World Bank GEP database (WORLD BANK, 2012).
+Gross capital stock data in real 2005 U.S.
+dollars for South Africa, China, Iran, Saudi Arabia, Tanzania, and Zambia for 1991-2011 is from the World Bank GEP database (WORLD BANK, 2012).
+
+\subsection{Labor and employment}
+Total employment and average hours worked per year per worker for the United States, the United Kingdom, and Japan for 1980-2011 is from the United States Bureau of Labor Statistics (BLS, 2011).
+Total hours worked is calculated by multiplying total employment by average hours worked per worker.
+The World Bank's WDI database (WORLD BANK, 2012) provides an employment to population ratio of people fifteen and older, total population, and a percentage of people under fifteen for South Africa, China, Iran, Saudi Arabia, Tanzania, and Zambia for 1991-2011.
+The population of people fifteen and older was calculated by multiplying the percentage of people under fifteen by total population, and then subtracting this from the total population.
+Total employment could be calculated by multiplying the employment to population ratio of people fifteen and older by the population of people fifteen and older.
+The labor input for South Africa, China, Iran, Saudi Arabia, Tanzania, and Zambia is based on total employment, not on total hours worked per year.
+
+\subsection{Thermal energy, exergy, and useful work}
+We were interested in how the three different types of energy (thermal energy, exergy, and useful work) would affect our econometric growth modeling.
+The rationale being that exergy, and to a greater extent useful work, would take into account the energy that is being directly used to further economic growth.
+We examined typical sources of energy for an economy, including: coal; oil and petroleum products; dry natural gas and natural gas plant liquids; nuclear power generation; and renewable energy sources (solar, wind, geothermal, biomass/fuel wood,  hydroelectric generation).
+In the style of (AYRES AND WARR, 2002, 2005), energy available from human and animal muscle power are also considered.
+The time series data used for the United States, the United Kingdom, and Japan is from 1980-2011.
+Time series data used for South Africa, China, Saudi Arabia, Iran, Zambia, and Tanzania is from 1991-2011.
+
+\subsubsection{Thermal energy}
+
+Thermal energy ($e$) is evaluated in TJ/year for the production functions. In the case of fuels, thermal energy was calculated using equation \ref{eq:thermal_energy}.
+
+\begin{equation} \label{eq:thermal_energy}
+  e_\mathrm{fuel} = (consumption)(heat content)
+\end{equation}
+
+Yearly consumption data for all the countries was obtained from the International Energy Agency (IEA, 2012) for coal (in short tons/year); oil and petroleum (in barrels/year); and dry natural gas and natural gas plant liquids (in cubic feet/year).
+Yearly average heat content data (in kJ/kg) for coal, oil, and natural gas was also taken from the IEA (IEA, 2012) for all the countries.
+Yearly consumption (in cubic meters/year) and heat content data (in kJ/kg) for biomass/fuel wood was taken from the"Fuelwood" time series on the FAO Statistics Database (FAOSTAT, 2012).
+
+For the renewable and nuclear energy sources, data on yearly electricity generation (in BTU/year) was directly available from the IEA (IEA, 2012) for each of the countries, so the use of equation \ref{eq:thermal_energy} was not needed.
+
+Human and animal muscle power was calculated using a similar style to Ayres and Warr and Wirsenius (AYRES AND WARR (No reference?
+We used the worksheets he sent us.), WIRSENIUS (2000)).
+For animals, our analysis was restricted to draught animals; horses and mules in this case.
+Muscle work from animals was calculated using equation \ref{eq:animal_muscle}.
+
+\begin{equation} \label{eq:animal_muscle}
+  e_\mathrm{animals} = \bigg{[} (ME_\mathrm{horse}N_\mathrm{horses})+(ME_\mathrm{mules}N_\mathrm{mules}) \bigg{]}
+\end{equation}
+
+Where $ME$ is metabolizable energy (in kcal/day-animal) and $N$ is the number of horses or mules.
+Metabolizable energy values were taken from Warr (WARR SPREADSHEETS) for horses and mules, which represent the amount of energy used to the animals for a days work.
+It should be noted that the same $ME$ value was assumed constant across all years, and used for all countries.
+The number of horses and mules for all the countries was taken from the "Live Animals" time series on the FAO Statistics Database (FAOSTAT, 2012).
+The food-to-work conversion efficiency was taken from Warr (WARR SPREADSHEETS) and was assumed to be the same for all countries.
+
+Human muscle power was calculated in the same way, except the $ME$ value for people was taken from a time series of kcal/day-person for workers in the U.S.
+from 1980-2011 (WARR SPREADSHEETS).
+The value stays relatively constant over the time series and the same time series was used to all of the countries, although it should be noted that this value may vary some (especially for the Malthusian vs developed economies).
+The number of humans was taken to be only the working population, with the same data collected for employment and labor being used.
+Ultimately, human muscle work was calculated using equation \ref{eq:human_muscle}.
+
+\begin{equation} \label{eq:human_muscle}
+  e_\mathrm{humans} = (ME_\mathrm{humans})(N_\mathrm{humans,employed})
+\end{equation}
+
+\subsubsection{Exergy}
+
+Exergy ($x$) is also evaluated in TJ/year and based on the previously determined thermal energy values.
+For coal; oil and petroleum; dry natural gas and natural gas liquids; and biomass/fuel wood., the thermal energy value for the fuels was calculated using an exergy-to-energy allocation factor from Ayres and Warr (AYRES AND WARR, 2005).
+
+\begin{equation} \label{eq:exergy}
+  x_\mathrm{fuels} = (e_\mathrm{fuels})(f_\mathrm{exergy-allocation})
+\end{equation}
+
+This allocation factor is the ratio of each fuel source's chemical exergy to the higher heating value.
+The exergy allocation factor was assumed to be the same for each of the countries.
+For renewable and nuclear energy sources, the electricity generated is already pure exergy, so no further modification is needed.
+
+For calculating the exergy from animal and human muscle power, the food-to-energy conversion efficiency and the ratio of food-end-use to food-intake are considered (see equation \ref{eq:animal_muscle_exergy} and equation \ref{eq:human_muscle_exergy}).
+
+\begin{equation} \label{eq:animal_muscle_exergy}
+  x_\mathrm{animals} = (e_\mathrm{animals}) (\eta_\mathrm{food-to-work, animals})
+\end{equation}
+
+\begin{equation} \label{eq:human_muscle_exergy}
+  x_\mathrm{humans} = (e_\mathrm{humans}) (\eta_\mathrm{food-to-work, humans})( f_\mathrm{enduse-to-intake})
+\end{equation}
+
+Where $\eta_\mathrm{food-to-work, animals}$ and $\eta_\mathrm{food-to-work, humans}$ are the animal's and human's efficiency of converting food into energy respectively.
+For humans, an additional factor of the ratio of food-end-use to food-intake is also applied.
+This ratio looks at how much of a person's energy can actually be used for physical labor, or muscle work, by taking into account food that's used to simply sustain the body's normal function.
+The food-to-work efficiency values are taken from Ayres and Warr (AYRES AND WARR, THE ECONOMIC GROWTH ENGINE) and the end-use to intake ratio is taken from Wirsenius (WIRSENIUS, 2000).
+The same ratio could also be applied to animals, but Wirsenius did not contain any information on these values and the magnitude of the animal muscle exergy is quite small compared to the other fuel sources.
+
+\subsubsection{Useful work}
+Useful work is a concept first developed by (AYRES AND WARR, 2005).
+Useful work takes exergy analysis one step further and considers where the energy is going and how efficiencies come into play.
+To calculate useful work, exergy is broken down into several categories by usage type: high temperature heat, medium temperature heat, low temperature heat, mechanical drive, electricity, light, and muscle work.
+Each of these categories then has an efficiency applied, as opposed to using an overall effiency for the base exergy value.
+The rationale behind this is that the efficiency of various industries in an economy will be very different, e.g.
+the efficiency of a coal fired power plant (high temperature heat source) will be very different from that of a residential heating system (low temperature heat source).
+
+Useful work is evaluated in TJ/year, and is given be equation \ref{eq:useful_work}.
+
+\begin{equation} \label{eq:useful_work}
+  u = \sum{\phi_\mathrm{i} \epsilon_\mathrm{i} x}
+\end{equation}
+
+Where $\epsilon_\mathrm{i}$ is the efficiency of each useful work type and $\phi_\mathrm{i}$ is the allocation factor, where $0 \le \phi_\mathrm{i} \le 1$.
+
+Data on $\epsilon$ and $\phi$ values were taken from the REXS database compiled by Warr (WARR, REXS, 2012).
+These values are not constant over time, as power generation technologies change and become more efficient.
+Useful work was only analyzed for the developed economies (the United States, the United Kingdom, and Japan) from 1980-2011, because of the difficulty associated with determining $\phi$ and $\epsilon$ values.
+In order to determine these parameters, information is needed about the efficiency of different technologies and what industries/areas is consuming the most energy within an economy.
+This proved to be quite difficult for the developing, petrol, and Malthusian economies so we restricted this part of the analysis to using the data already compiled in the REXS database.
 

### 2013-03-07 EconGrowthSeminar.Rnw
Added Caleb's text in the introduction.

@@
-<<setup_child, child='EconGrowth-R-Functions.Rnw', echo=FALSE, message=FALSE, eval=TRUE>>=
+<<setup_functions, child='EconGrowth-R-Functions.Rnw', echo=FALSE, message=FALSE, eval=TRUE>>=
 # Includes the Functions.Rnw file that contains all of the functions for analyzing our economic data.
@@
 
-<<global_params>>=
+<<setup, echo=FALSE, message=FALSE, eval=TRUE>>=
 textScaleForGraphs <- 0.6 # Controls text scaling in graphs
+keyXLoc <- 0.013 # Location for the key in single-panel graphs.
+keyYLoc <- 0.87 # Location for the key in single-panel graphs.
 @
@@
 
-\begin{frame}{Energy and GDP are Linked}%{\citet{Cleveland:1997p5055}} %----------------------------
+\begin{frame}[fragile] %----------------------------
+  \frametitle{Energy and GDP are Linked} 
+%  \framesubtitle{\citet{Cleveland:1997p5055}}
   \begin{columns}[c]
@@
 
-\begin{frame}{Example Data} %----------------------------
+\subsection[Graphs]{Historical Data} %+++++++++++++++++++++++++++++++++++++++
 
+\begin{frame}{USA and China} %----------------------------
   \begin{columns}[c]
@@
 <<Historical_Data_US, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H", eval=TRUE>>=
-createHistoricalLatticeGraph("US", textScaling=0.6)
+createHistoricalLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@    
+    \column{2.2in}
+<<Historical_Data_CN, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H", eval=TRUE>>=
+createHistoricalLatticeGraph("CN", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
+\end{frame}
+
+\begin{frame}{South Africa and Saudi Arabia} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+<<Historical_Data_ZA, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H", eval=TRUE>>=
+createHistoricalLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
 @    
@@
 <<Historical_Data_SA, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H", eval=TRUE>>=
-createHistoricalLatticeGraph("SA", textScaling=textScaleForGraphs)
+createHistoricalLatticeGraph("SA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
 @
   \end{columns}
-
 \end{frame}

### 2013-03-07 EconGrowth.Rnw
Began editing introduction text.

@@
 Neoclassical economic growth theory attributes output growth to growth rates of factors of production: capital stock and labor.
-In 1928, Amherst Professors Charles Cobb and Paul Douglas created the Cobb-Douglas production function that predicted manufacturing output (\textit{y}) as a function of labor (\textit{l}) and capital (\textit{k}) (MISHRA, 2007).
+In 1928, Amherst Professors Charles Cobb and Paul Douglas created the Cobb-Douglas production function that predicted manufacturing output ($y$) as a function of labor ($l$), capital stock ($k$), and a technological progress term ($\mathmr{e}^(t-t_0)$) \citep{Mishra:2007tv}.
 
-\begin{equation}
-  y_\mathrm{C-D} = A(t) k^\alpha l^\beta
+\begin{equation} \label{eq:CD}
+  y_\mathrm{C-D} = \mathrm{e}^{(t-t_0)} k^\alpha l^\beta,
 \end{equation}
 
-\begin{equation}
-  y \equiv Y/Y_\mathrm{0}
+\noindent where
+
+\begin{equation} \label{eq:y_def}
+  y \equiv Y/Y_\mathrm{0},
 \end{equation}
 
-\begin{equation}
-  k \equiv K/K_\mathrm{0}
+\begin{equation} \label{eq:k_def}
+  k \equiv K/K_\mathrm{0},
 \end{equation}
 
-\begin{equation}
-  l \equiv L/L_\mathrm{0}
+\noindent and
+
+\begin{equation} \label{eq:l_def}
+  l \equiv L/L_\mathrm{0}; with
 \end{equation}
+
+\noindent $Y$ measured by GDP, $K$ measured in currency units, and $L$ measured in workers or work-hours.
 
@@
 
-\begin{equation}
+\begin{equation} \label{eq:CD_constant_returns_to_scale_constraint}
   \alpha + \beta = 1

### 2013-03-07 EconGrowth-R-Functions.Rnw
Now adding single-country SF graphs.

@@
 countryNamesAlph <- c(CN="China", IR="Iran", JP="Japan", SA="Saudi Arabia", TZ="Tanzania", UK="United Kingdom", US="USA", ZA="South Africa", ZM="Zambia") #In alphabetical order.
+yLimitsForGDPGraphs <- list(c(1,10), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4)) # Alph order
 energyTypes <- c(Q="Q", X="X", U="U") # List of energy types
@@
 countryOrderForGraphs <- c(7,6,3,1,8,5,4,2,9) # Sets the order as US, UK, JP, CN, ZA, TZ, SA, IR, ZM.
+timeTics <- c(1980, 1990, 2000, 2010)
+yTicsForIndexedGraphs <- c(1,2,3,4,5,6,7,8,9,10) #y tic mark locations.
+
 maxWidth <- 6.5 #Inches
@@
   lineWidths <- c(0, 2, 2, 1, 1, 1) #line widths. 0 means no line.
-  xTics <- c(1980, 1990, 2000, 2010)
-  yTics <- c(1,2,3,4,5,6,7,8,9,10) #y tic mark locations.
   colors <- c("black", "black", "black", "red", "blue", "darkorange") #line and symbol colors
   symbols <- c(1, NA, NA, NA, NA, NA)  #NA gives no symbol.
-  #y axis limits for countries in alphabetical order.
-  yLimits <- list(c(1,10), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4)) 
   # Code that deals with items that are specific to whether we want all countries or a specific country.
@@
     layout <- ninePanelLayoutSpec # Show all countries
+    yLimits <- yLimitsForGDPGraphs
   } else {
@@
     # This has the added benefit of maintaining the correct classes for things.
-    yLimits <- yLimits[index:index]                   # Pick limits for the country we want.
+    yLimits <- yLimitsForGDPGraphs[index:index]       # Pick limits for the country we want.
     factorLevels <- countryNamesAlph[index:index]     # Only show the country we have chosen.
@@
                               tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
-                              x=list(at=xTics),
+                              x=list(at=timeTics),
                               y=list(relation="free",  #allows each axis to be different
-                                     at=yTics)), #specifies location for tics
+                                     at=yTicsForIndexedGraphs)), #specifies location for tics
                   ylim=yLimits, #y axis limits
@@
 ##
-createSFLatticeGraph <- function(){
+createSFLatticeGraph <- function(countryAbbrev, textScaling = 1.0, keyXLoc = defaultKeyXLoc, keyYLoc = defaultKeyYLoc){
   dataTable <- loadData("All") #Grab the raw data
@@
   dataTable <- cbind(dataTable, predictionsK, predictionsL, predictionsQ, predictionsX, predictionsU)
+  # Code for all graphs, regardless of whether we want to focus on a specific country
+  graphType <- "b" #b is for both line and symbol
+  lineTypes <- c(0, 1, 5, 2, 4, 1) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
+  lineWidths <- c(0, 2, 2, 1, 1, 1) #line widths. 0 means no line.
+  colors <- c("black", "black", "black", "red", "blue", "darkorange") #line and symbol colors
+  symbols <- c(1, NA, NA, NA, NA, NA)  #NA gives no symbol.
+  # Code that deals with items that are specific to whether we want all countries or a specific country.  
+  if (missing (countryAbbrev)){
+    # We want a graph with panels for all countries
+    yLimits <- yLimitsForGDPGraphs
+    factorLevels <- countryNamesAlph # We want all countries shown
+    indexCond <- list(countryOrderForGraphs) # We want all countries in this order
+    layout <- ninePanelLayoutSpec # Show all countries
+  } else {
+    # We want only a specific country
+    dataTable <- subset(dataTable, Country == countryAbbrev)    
+    # Select the correct y limits
+    index <- which(countryAbbrevsAlph %in% countryAbbrev)
+    # The following lines use [index:index] as a convenient way of subsetting.
+    # This has the added benefit of maintaining the correct classes for things.
+    yLimits <- yLimitsForGDPGraphs[index:index]       # Pick limits for the country we want.
+    factorLevels <- countryNamesAlph[index:index]     # Only show the country we have chosen.
+    indexCond <- list(c(1))                           # We want only one country.
+    layout <- onePanelLayoutSpec                      # We want only one panel in the graph.
+  }  
   graphType <- "b" #b is for both line and symbol
@@
                   type=graphType,
-                  index.cond=list(countryOrderForGraphs), #orders the panels.
-                  layout=ninePanelLayoutSpec, #indicates a 3x3 arrangement of panels.
-                  strip = strip.custom(factor.levels=countryNamesAlph, bg="white"), #Sets strip parameters
+                  index.cond=indexCond, #orders the panels.
+                  layout=layout, #indicates a 3x3 arrangement of panels.
+                  strip = strip.custom(factor.levels=factorLevels, 
+                                       bg="transparent", # Sets background transparent to match the graph itself.
+                                       par.strip.text=list(cex=textScaling) # Scales text in the strip.
+                                       ),
                   as.table=TRUE, #indexing of panels starts in upper left and goes across rows.
@@
                            columns=keyColumns, x=keyXLoc, y=keyYLoc), #controls columns and position of the key
-                  scales=list(cex=scaleTextSize, #controls text size on scales.
+                  scales=list(cex=scaleTextSize * textScaling, #controls text size on scales.
                               tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
+                              x=list(at=timeTics),
                               y=list(relation="free",  #allows each axis to be different
-                                     at=c(1,2,3,4,5,6,7,8,9,10) #tick mark locations
-                                     )
-                              ), 
-                  ylim=list(c(1,8), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3), c(1,3)),
-                  xlab="", ylab="Indexed GDP (1980=1 or 1991=1)") #axis labels
+                                     at=yTicsForIndexedGraphs)), #specifies location for tics
+                  ylim=yLimits, #y axis limits
+                  #axis labels and scaling
+                  xlab=list(label="", cex=textScaling), 
+                  ylab=list(label="Indexed (1980=1 or 1991=1)", cex=textScaling)
+                  )
   return(graph)

### 2013-03-07 EconGrowth.Rnw
Now adding single-country SF graphs.

@@
 Neoclassical economic growth theory attributes output growth to growth rates of factors of production: capital stock and labor.
-In 1928, Amherst Professors Charles Cobb and Paul Douglas created the Cobb-Douglas production function that predicted manufacturing output ($y$) as a function of labor ($l$), capital stock ($k$), and a technological progress term ($\mathmr{e}^(t-t_0)$) \citep{Mishra:2007tv}.
+In 1928, Amherst Professors Charles Cobb and Paul Douglas created the Cobb-Douglas production function that predicted manufacturing output ($y$) as a function of labor ($l$), capital stock ($k$), and a technological progress term ($\mathrm{e}^{(t-t_0)}$) \citep{Mishra:2007tv}
 
 \begin{equation} \label{eq:CD}
-  y_\mathrm{C-D} = \mathrm{e}^{(t-t_0)} k^\alpha l^\beta,
+  y_\mathrm{CD} = \mathrm{e}^{(t-t_0)} k^\alpha l^\beta,
 \end{equation}
@@
 \begin{equation} \label{eq:l_def}
-  l \equiv L/L_\mathrm{0}; with
+  l \equiv L/L_\mathrm{0};
 \end{equation}
 
-\noindent $Y$ measured by GDP, $K$ measured in currency units, and $L$ measured in workers or work-hours.
+\noindent with $Y$ measured by GDP, $K$ measured in currency units, and $L$ measured in workers or work-hours.
 
@@
 
-<<SF_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="Single-factor results.">>=
+<<SF_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="Single-factor results.", eval=TRUE>>=
 createSFLatticeGraph()

### 2013-03-07 EconGrowthSeminar.Rnw
Now adding single-country SF graphs.

@@
     \column{2.2in}
-<<Historical_Data_US, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H", eval=TRUE>>=
+<<Historical_Data_US, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
 createHistoricalLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
@@
     \column{2.2in}
-<<Historical_Data_CN, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H", eval=TRUE>>=
+<<Historical_Data_CN, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
 createHistoricalLatticeGraph("CN", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
@@
     \column{2.2in}
-<<Historical_Data_ZA, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H", eval=TRUE>>=
+<<Historical_Data_ZA, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
 createHistoricalLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
@@
     \column{2.2in}
-<<Historical_Data_SA, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H", eval=TRUE>>=
+<<Historical_Data_SA, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
 createHistoricalLatticeGraph("SA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
@@
 
-\begin{frame}{US Single Factor} %----------------------------
-  Heun complete
-\end{frame}
-
-\begin{frame}{US Cobb-Douglas} %----------------------------
-  Heun complete
+\begin{frame}{US: Single Factor and Cobb-Douglas} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+<<Results_US_SF, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H", eval=TRUE>>=
+createSFLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@    
+    \column{2.2in}
+<<Results_US_CD, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H", eval=TRUE>>=
+#createCDLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
 \end{frame}

### 2013-03-07 EconGrowth-R-Functions.Rnw
Now including Cobb-Douglas single-country graphs.

@@
   cache=FALSE,
-  warning=TRUE,  #Tells whether to show warnings in the output.
+  warning=FALSE,  #Tells whether to show warnings in the output.
   message=FALSE, #Turns off messages for all chunks. Set TRUE on an individual chunk to see it.
@@
   }  
-  graphType <- "b" #b is for both line and symbol
-  lineTypes <- c(0, 1, 5, 2, 4, 1) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
-  lineWidths <- c(0, 2, 2, 1, 1, 1) #line widths. 0 means no line.
-  colors <- c("black", "black", "black", "red", "blue", "darkorange") #line and symbol colors
-  symbols <- c(1, NA, NA, NA, NA, NA)  #NA gives no symbol.
   graph <- xyplot(iGDP+predGDPK+predGDPL+predGDPQ+predGDPX+predGDPU ~ Year | Country, data=dataTable,
@@
 ##
-createCDLatticeGraph <- function(){
+createCDLatticeGraph <- function(countryAbbrev, textScaling = 1.0, keyXLoc = defaultKeyXLoc, keyYLoc = defaultKeyYLoc){
   dataTable <- loadData("All") #Grab the raw data
@@
   symbols <- c(1, NA, NA, NA, NA)  #NA gives no symbol.
+  # Code that deals with items that are specific to whether we want all countries or a specific country.  
+  if (missing (countryAbbrev)){
+    # We want a graph with panels for all countries
+    yLimits <- yLimitsForGDPGraphs
+    factorLevels <- countryNamesAlph # We want all countries shown
+    indexCond <- list(countryOrderForGraphs) # We want all countries in this order
+    layout <- ninePanelLayoutSpec # Show all countries
+  } else {
+    # We want only a specific country
+    dataTable <- subset(dataTable, Country == countryAbbrev)    
+    # Select the correct y limits
+    index <- which(countryAbbrevsAlph %in% countryAbbrev)
+    # The following lines use [index:index] as a convenient way of subsetting.
+    # This has the added benefit of maintaining the correct classes for things.
+    yLimits <- yLimitsForGDPGraphs[index:index]       # Pick limits for the country we want.
+    factorLevels <- countryNamesAlph[index:index]     # Only show the country we have chosen.
+    indexCond <- list(c(1))                           # We want only one country.
+    layout <- onePanelLayoutSpec                      # We want only one panel in the graph.
+  }  
   graph <- xyplot(iGDP+predGDP+predGDPQ+predGDPX+predGDPU ~ Year | Country, data=dataTable,
                   type=graphType,
-                  index.cond=list(countryOrderForGraphs), #orders the panels.
-                  layout=ninePanelLayoutSpec, #indicates a 3x3 arrangement of panels.
-                  strip = strip.custom(factor.levels=countryNamesAlph, bg="white"), #Sets strip parameters
+                  index.cond=indexCond, #orders the panels.
+                  layout=layout, #indicates a 3x3 arrangement of panels.
+                  strip = strip.custom(factor.levels=factorLevels, 
+                                       bg="transparent", # Sets background transparent to match the graph itself.
+                                       par.strip.text=list(cex=textScaling) # Scales text in the strip.
+                                       ),
                   as.table=TRUE, #indexing of panels starts in upper left and goes across rows.

### 2013-03-07 EconGrowth.Rnw
Now including Cobb-Douglas single-country graphs.

@@
 
-<<SF_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="Single-factor results.", eval=TRUE>>=
+<<SF_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="Single-factor results.">>=
 createSFLatticeGraph()

### 2013-03-07 EconGrowthSeminar.Rnw
Now including Cobb-Douglas single-country graphs.

@@
 <<Results_US_CD, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H", eval=TRUE>>=
-#createCDLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+createCDLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
 @

### 2013-03-08 EconGrowth-R-Functions.Rnw
Now including the capability to draw CES single-country graphs.

@@
 ##
-createCESLatticeGraph <- function(){
+createCESLatticeGraph <- function(countryAbbrev, textScaling = 1.0, keyXLoc = defaultKeyXLoc, keyYLoc = defaultKeyYLoc){
   dataTable <- loadData("All") #Grab the raw data
@@
   symbols <- c(1, NA, NA, NA)  #NA gives no symbol.
+  # Code that deals with items that are specific to whether we want all countries or a specific country.  
+  if (missing(countryAbbrev)){
+    # We want a graph with panels for all countries
+    yLimits <- yLimitsForGDPGraphs
+    factorLevels <- countryNamesAlph # We want all countries shown
+    indexCond <- list(countryOrderForGraphs) # We want all countries in this order
+    layout <- ninePanelLayoutSpec # Show all countries
+  } else {
+    # We want only a specific country
+    dataTable <- subset(dataTable, Country == countryAbbrev)    
+    # Select the correct y limits
+    index <- which(countryAbbrevsAlph %in% countryAbbrev)
+    # The following lines use [index:index] as a convenient way of subsetting.
+    # This has the added benefit of maintaining the correct classes for things.
+    yLimits <- yLimitsForGDPGraphs[index:index]       # Pick limits for the country we want.
+    factorLevels <- countryNamesAlph[index:index]     # Only show the country we have chosen.
+    indexCond <- list(c(1))                           # We want only one country.
+    layout <- onePanelLayoutSpec                      # We want only one panel in the graph.
+  }
   graph <- xyplot(iGDP+predGDPQ+predGDPX+predGDPU ~ Year | Country, data=dataTable,
                   type=graphType,
-                  index.cond=list(countryOrderForGraphs), #orders the panels.
-                  layout=ninePanelLayoutSpec, #indicates a 3x3 arrangement of panels.
-                  strip = strip.custom(factor.levels=countryNamesAlph, bg="white"), #Sets strip parameters
+                  index.cond=indexCond, #orders the panels.
+                  layout=layout,
+                  strip = strip.custom(factor.levels=factorLevels, 
+                                       bg="transparent", # Sets background transparent to match the graph itself.
+                                       par.strip.text=list(cex=textScaling) # Scales text in the strip.
+                                       ),
                   as.table=TRUE, #indexing of panels starts in upper left and goes across rows.

### 2013-03-08 EconGrowth.Rnw
Now including the capability to draw CES single-country graphs.

@@
 
-<<CES_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="CES results.">>=
+<<CES_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="CES results.", eval=TRUE>>=
 createCESLatticeGraph()

### 2013-03-08 EconGrowthSeminar.Rnw
Now including the capability to draw CES single-country graphs.

@@
 
-\begin{frame}{US CES} %----------------------------
-  Heun complete
-\end{frame}
-
-\begin{frame}{US LINEX} %----------------------------
-  Heun complete
+\begin{frame}{US: CES and LINEX} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+<<Results_US_CES, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H", eval=TRUE>>=
+createCESLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+    \column{2.2in}
+<<Results_US_LINEX, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H", eval=TRUE>>=
+#createLINEXLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
 \end{frame}

### 2013-03-08 EconGrowth.Rnw
Now including capability to generate single-country LINEX plots.

--- 2013-03-07 EconGrowth.Rnw
@@
 
-<<LINEX_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="LINEX results.">>=
-createLinexLatticeGraph()
+<<LINEX_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="LINEX results.", eval=TRUE>>=
+createLINEXLatticeGraph()
 @

### 2013-03-08 EconGrowthSeminar.Rnw
Now including capability to generate single-country LINEX plots.

@@
 <<Results_US_LINEX, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H", eval=TRUE>>=
-#createLINEXLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+createLINEXLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
 @

### 2013-03-08 EconGrowth-R-Functions.Rnw
Now including graphs for both US and ZA in the presentation.

@@
 ##
-createLinexLatticeGraph <- function(){
+createLINEXLatticeGraph <- function(countryAbbrev, textScaling = 1.0, keyXLoc = defaultKeyXLoc, keyYLoc = defaultKeyYLoc){
   dataTable <- loadData("All") #Grab the raw data
@@
   symbols <- c(1, NA, NA, NA)  #NA gives no symbol.
+  # Code that deals with items that are specific to whether we want all countries or a specific country.  
+  if (missing (countryAbbrev)){
+    # We want a graph with panels for all countries
+    yLimits <- yLimitsForGDPGraphs
+    factorLevels <- countryNamesAlph # We want all countries shown
+    indexCond <- list(countryOrderForGraphs) # We want all countries in this order
+    layout <- ninePanelLayoutSpec # Show all countries
+  } else {
+    # We want only a specific country
+    dataTable <- subset(dataTable, Country == countryAbbrev)    
+    # Select the correct y limits
+    index <- which(countryAbbrevsAlph %in% countryAbbrev)
+    # The following lines use [index:index] as a convenient way of subsetting.
+    # This has the added benefit of maintaining the correct classes for things.
+    yLimits <- yLimitsForGDPGraphs[index:index]       # Pick limits for the country we want.
+    factorLevels <- countryNamesAlph[index:index]     # Only show the country we have chosen.
+    indexCond <- list(c(1))                           # We want only one country.
+    layout <- onePanelLayoutSpec                      # We want only one panel in the graph.
+  }  
   graph <- xyplot(iGDP+predGDPQ+predGDPX+predGDPU ~ Year | Country, data=dataTable,
                   type=graphType,
-                  index.cond=list(countryOrderForGraphs), #orders the panels.
-                  layout=ninePanelLayoutSpec, #indicates a 3x3 arrangement of panels.
-                  strip = strip.custom(factor.levels=countryNamesAlph, bg="white"), #Sets strip parameters
+                  index.cond=indexCond, #orders the panels.
+                  layout=layout,
+                  strip = strip.custom(factor.levels=factorLevels, 
+                                       bg="transparent", # Sets background transparent to match the graph itself.
+                                       par.strip.text=list(cex=textScaling) # Scales text in the strip.
+                                       ),
                   as.table=TRUE, #indexing of panels starts in upper left and goes across rows.

### 2013-03-08 EconGrowthSeminar.Rnw
Now including graphs for both US and ZA in the presentation.

--- 2013-03-07 EconGrowthSeminar.Rnw
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Examples}
+\section{Results}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
     \column{2.2in}
-<<Results_US_SF, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H", eval=TRUE>>=
+<<Results_US_SF, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
 createSFLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
@@
     \column{2.2in}
-<<Results_US_CD, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H", eval=TRUE>>=
+<<Results_US_CD, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
 createCDLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
@@
 
-\begin{frame}{US CES} %----------------------------
-  Heun complete
-\end{frame}
-
-\begin{frame}{US LINEX} %----------------------------
-  Heun complete
+\begin{frame}{US: CES and LINEX} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+<<Results_US_CES, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+createCESLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+    \column{2.2in}
+<<Results_US_LINEX, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+createLINEXLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
 \end{frame}
@@
 
-\begin{frame}{ZA Single Factor} %----------------------------
-  Heun complete
+\begin{frame}{ZA: Single Factor and Cobb-Douglas} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+<<Results_ZA_SF, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+createSFLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+    \column{2.2in}
+<<Results_ZA_CD, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+createCDLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
 \end{frame}
 
-\begin{frame}{ZA Cobb-Douglas} %----------------------------
-  Heun complete
-\end{frame}
-
-\begin{frame}{ZA CES} %----------------------------
-  Heun complete
-\end{frame}
-
-\begin{frame}{ZA LINEX} %----------------------------
-  Heun complete
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{frame}{Results} %----------------------------
-  Heun complete
+\begin{frame}{ZA: CES and LINEX} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+<<Results_ZA_CES, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+createCESLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+    \column{2.2in}
+<<Results_ZA_LINEX, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+createLINEXLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
 \end{frame}

### 2013-03-08 EconGrowthSeminar.Rnw
Added figure from Tverberg on tightening oil supply. Got the bibliography to work, even if it is not in the format I would like, yet.

@@
 % does not look nice, try deleting the line with the fontenc.
+\usepackage{url} % To format URLs in the references section.
 
@@
 
-\begin{frame}[fragile] %----------------------------
-  \frametitle{Energy and GDP are Linked} 
-%  \framesubtitle{\citet{Cleveland:1997p5055}}
+\begin{frame}{Energy and GDP are Linked} %----------------------------
+  \tiny
+  \framesubtitle{\cite{Cleveland:1997p5055}}
+  \normalsize
   \begin{columns}[c]
@@
 
-\begin{frame}{Problem: Energy Cost Share is Low} %----------------------------
+\begin{frame}{World Oil Supply is Tightening} %----------------------------
+  \framesubtitle{\cite{Tverberg:2013}}
+  \includegraphics[width=4.0in]{figure_other/Figure_Tverberg_2013.png}
+\end{frame}
+
+\begin{frame}{Energy Cost Share is Low} %----------------------------
+  \begin{itemize}
+    \item
       Therefore, energy is considered to be economically unimportant.
-
+    \item
       Compare cost shares of capital stock, labor, and energy.
+  \end{itemize}
 \end{frame}
@@
 
-\begin{frame}{The Big Questions} %----------------------------
+\begin{frame}{Observations and Questions} %----------------------------
+  \begin{itemize}
+    \item
+      Historical economic development paths are energy intensive. 
+    \item
+      What happens when energy supplies are constrained and prices rise? 
+    \item
+      Will developing countries be able to expand their economies?
+    \item
       How account for energy in economic models?
-
-  What happens when energy supplies become constrained?
-
-  Historical economic development paths are energy intensive. What happens when energy is constrained and prices rise? Will developing countries be able to expand their economies?
+  \end{itemize}
 \end{frame}
@@
 % See hints at http://judsonsnotes.com/notes/index.php?option=com_content&view=article&id=641:bibliography-in-beamer&catid=60:latex&Itemid=84
-\begin{frame}{Bibliography} %----------------------------
+% \begin{frame}{Bibliography} %----------------------------
+% \bibliographystyle{model2-names}
+% \bibliography{EconGrowth.bib}
+% \end{frame}
+
+%-------------------------------------------------------------------
+
+\begin{frame}
+\frametitle{References}
+%\bibliographystyle{amsalpha}
 \bibliographystyle{model2-names}
+\renewcommand{\thepage}{\arabic{page}}
+\tiny
 \bibliography{EconGrowth.bib}
+\normalsize
 \end{frame}

### 2013-03-12 EconGrowth-R-Functions.Rnw
Now correctly calculating beta for cde models. Also, developing graphs of SSE, lambda, alpha, and beta vs. gamma to show that the minimum SSE occurs at the point where beta --> 0.0.

@@
 ###############################
-# Does a grid search over values of gamma for a CD production function
+# Does a grid search over values of gamma for a CD with energy production function.
+# Results are returned as a data.frame with columns of gamma, SSE, lambda, alpha, and beta
 ##
@@
   models <- lapply(gamma, cobbDouglasModel, energyType=energyType, countryAbbrev=countryAbbrev)
-  return(models)
+  SSE <- unlist(lapply(models, function(model){summary(model)$sigma}))
+  lambda <- unlist(lapply(models, function(model){coef(model)["lambda"]}))
+  alpha <- unlist(lapply(models, function(model){coef(model)["alpha"]}))
+  data <- as.data.frame(cbind(gammaGrid, lambda, alpha, SSE))
+  row.names(data) <- NULL #eliminates row names, leaving only numbered rows
+  colnames(data) <- c("gamma", "lambda", "alpha", "SSE")
+  data <- transform(data, beta = 1.0 - alpha - gamma)
+  return(data)
 }
@@
   gammaGrid <- seq(0.0, 0.95, by=0.05)
-  #print(paste(countryAbbrev, energyType))
-  models <- cdeGridData(countryAbbrev, energyType, gammaGrid)
-  SSE <- lapply(models, function(model) summary(model)$sigma)
-  lambda <- lapply(models, function(model) coef(model)["lambda"])
-  alpha <- lapply(models, function(model) coef(model)["alpha"])
-  data <- cbind(lambda, alpha, gammaGrid, SSE)
-  plot(gammaGrid, SSE)
-  plot(gammaGrid, lambda)
-  plot(gammaGrid, alpha)
+  data <- cdeGridData(countryAbbrev, energyType, gammaGrid)
+  with(data, plot(gamma, SSE))
+  with(data, plot(gamma, lambda))
+  with(data, plot(gamma, alpha))
+  with(data, plot(gamma, beta))
+  with(data, plot(beta, SSE))
 }
@@
     # Now calculate a confidence interval on beta
-    betaCICD <- with(beta.est, Estimate + c(-1.0, 1.0) * tvalCD * SE); betaCICD # Gives the confidence interval on beta.  
+    betaCICD <- with(beta.est, Estimate + c(-1.0, 1.0) * tvalCD * SE) # Gives the confidence interval on beta.  
     # Combine all estimates and their confidence intervals into data frames with intelligent row names

### 2013-03-12 EconGrowth.Rnw
Now correctly calculating beta for cde models. Also, developing graphs of SSE, lambda, alpha, and beta vs. gamma to show that the minimum SSE occurs at the point where beta --> 0.0.

--- 2013-03-07 EconGrowth.Rnw
@@
 
-<<CDeGammaGraphsZA>>=
+<<CDeGammaGraphsZA, eval=TRUE>>=
   cdeGridGraphs("ZA", "Q")
@@
 <<LINEX_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="LINEX results.">>=
-createLinexLatticeGraph()
+createLINEXLatticeGraph()
 @

### 2013-03-12 EconGrowthSeminar.Rnw
Added Bashmakov reference.
Now correctly calculating beta for cde models. Also, developing graphs of SSE, lambda, alpha, and beta vs. gamma to show that the minimum SSE occurs at the point where beta --> 0.0.

@@
 \usepackage{url} % To format URLs in the references section.
+\usepackage{natbib} % To format the bibliobraphy nicely
 
@@
   \tiny
-  \framesubtitle{\cite{Cleveland:1997p5055}}
+  \framesubtitle{\citep{Cleveland:1997p5055}}
   \normalsize
@@
 \begin{frame}{World Oil Supply is Tightening} %----------------------------
-  \framesubtitle{\cite{Tverberg:2013}}
+  \framesubtitle{\citep{Tverberg:2013}}
   \includegraphics[width=4.0in]{figure_other/Figure_Tverberg_2013.png}
@@
   \begin{itemize}
-    \item
-      Therefore, energy is considered to be economically unimportant.
-    \item
-      Compare cost shares of capital stock, labor, and energy.
+    \item{Energy is considered to be economically unimportant.}
+    \item{Compare cost shares of capital stock, labor, and energy.}
   \end{itemize}
@@
 \begin{frame}{Energy Cost Share and Economic Growth} %----------------------------
+  \framesubtitle{\citep{Bashmakov:2007ek}}
   \begin{center}
@@
   \begin{itemize}
-    \item
-      Historical economic development paths are energy intensive. 
-    \item
-      What happens when energy supplies are constrained and prices rise? 
-    \item
-      Will developing countries be able to expand their economies?
-    \item
-      How account for energy in economic models?
+    \item{Historical economic development paths (US, Western Europe) are energy intensive.}
+    \item{What happens when energy supplies are constrained and prices rise?}
+    \item{Will developing countries be able to expand their economies?}
+    \item{How account for energy in economic models?}
   \end{itemize}
@@
   \begin{itemize}
-  \item
-    Goal: predict economic output over time
-  \item
-    Economic output is a function of ``factors of production''
-  \item
-    Output defined as GDP ($Y$)
-  \item
-    All inputs and outputs normalized to initial year (0)
+  \item{Goal: predict economic output over time}
+  \item{Economic output is a function of ``factors of production''}
+  \item{Output defined as GDP ($Y$)}
+  \item{All inputs and outputs normalized to initial year (0)}
   \end{itemize}
@@
   \begin{itemize}
-  \item
-    Capital Stock ($K$) <Definition here>
-  \item
-    Labor ($L$) <Definition here>
+  \item{Capital Stock ($K$) <Definition here>}
+  \item{Labor ($L$) <Definition here>}
   \end{itemize}
@@
 \begin{frame}{Single Factor} %----------------------------
-
   \begin{equation*} \label{eq:Single_Factor_Generic}
@@
   \end{equation*}
-
   \begin{center}
@@
   \end{center}
-
 \end{frame}
@@
 \begin{frame}{Cobb-Douglas} %----------------------------
-
   \begin{equation*} \label{eq:CD_With_Energy}
@@
   \end{equation*}
-
   \begin{equation*} \label{eq:CD_Const_Returns_To_Scale}
@@
   \end{equation*}
-
   \begin{equation*} \label{eq:CD_Constraints}
@@
 \begin{frame}{Constant Elasticity of Substitution (CES)} %----------------------------
-
   \begin{equation*} \label{eq:micEconCES_model}
@@
 \begin{frame}{LINEX} %----------------------------
-
   \begin{equation*} \label{eq:LINEX_model}
@@
 
+\begin{frame}{Next Steps (Summer 2013)} %----------------------------
+  \begin{itemize}
+    \item{Estimate statistical properties for \emph{all} fitting parameters}
+    \item{Complete paper}
+  \end{itemize}  
+\end{frame}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-% See hints at http://judsonsnotes.com/notes/index.php?option=com_content&view=article&id=641:bibliography-in-beamer&catid=60:latex&Itemid=84
-% \begin{frame}{Bibliography} %----------------------------
-% \bibliographystyle{model2-names}
-% \bibliography{EconGrowth.bib}
-% \end{frame}
-
-%-------------------------------------------------------------------
-
-\begin{frame}
-\frametitle{References}
-%\bibliographystyle{amsalpha}
-\bibliographystyle{model2-names}
+\begin{frame}{References} %----------------------------
+  \bibliographystyle{plainnat}
   \renewcommand{\thepage}{\arabic{page}}

### 2013-03-14 EconGrowth-R-Functions.Rnw
Now using melt to reshape the data for graphs of lambda, alpha, beta, and SSE vs. gamma for CDe parameter estimation. Creating a lattice graph of the same variables.

@@
 require(micEconCES)
+require(reshape2) # Provides access to data melting. See http://cran.r-project.org/web/packages/reshape2/reshape2.pdf
 # tikz allows use of LaTeX formatting and font in graphs. Allows for a consistent look across the paper.
@@
   data <- cdeGridData(countryAbbrev, energyType, gammaGrid)
-  with(data, plot(gamma, SSE))
-  with(data, plot(gamma, lambda))
-  with(data, plot(gamma, alpha))
-  with(data, plot(gamma, beta))
+  # Now melt the data so that it is in the correct form.
+
+#   with(data, plot(gamma, SSE))
+#   with(data, plot(gamma, lambda))
+#   with(data, plot(gamma, alpha))
+#   with(data, plot(gamma, beta))
   with(data, plot(beta, SSE))
+
+  data_molten <- melt(data, id="gamma")
+print(data_molten)
+
+  graph <- xyplot(value ~ gamma | variable, data=data_molten,
+#                 type=graphType,
+#                 index.cond=indexCond, #orders the panels.
+#                 layout=layout, #indicates a 3x3 arrangement of panels.
+#                 strip = strip.custom(factor.levels=factorLevels, 
+#                                      bg="transparent", # Sets background transparent to match the graph itself.
+#                                      par.strip.text=list(cex=textScaling) # Scales text in the strip.
+#                                      ),
+#                 as.table=TRUE, #indexing of panels starts in upper left and goes across rows.
+#                 lty = lineTypes, lwd = lineWidths, col = colors, #Controls line parameters
+#                 pch = symbols, col.symbol = colors, #Controls symbol parameters
+#                 key=list(text=list(c("Actual", "No energy", "With $q$", "With $x$", "With $u$")),
+#                          type=graphType,
+#                          cex=keyTextSize * textScaling, #controls size of text in the key
+#                          lines=list(lty=lineTypes, lwd=lineWidths), #controls line types
+#                          pch=symbols, col=colors, #controls symbol (plot characters) types
+#                          columns=keyColumns, x=keyXLoc, y=keyYLoc), #controls columns and position of the key
+#                 scales=list(cex=scaleTextSize * textScaling, #controls text size on scales.
+#                             tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
+#                             x=list(at=timeTics),
+#                             y=list(relation="free",  #allows each axis to be different
+#                                    at=yTicsForIndexedGraphs)), #specifies location for tics
+#                 ylim=yLimits, #y axis limits
+#                 #axis labels and scaling
+#                 xlab=list(label="", cex=textScaling), 
+#                 ylab=list(label="Indexed (1980=1 or 1991=1)", cex=textScaling)
+                )
+  return(graph)
 }

### 2013-03-14 EconGrowth-R-Functions.Rnw
Now creating CDe grid graphs in both paper and presentation. Need to fix size of presentation graphs and scaling of presentation graph text.

--- 2013-03-12 EconGrowth-R-Functions.Rnw
@@
 # showing various parameters as a function of gamma.
-##
-cdeGridGraphs <- function(countryAbbrev, energyType){
+# countryAbbrev tells which country you want to view
+# energyType tells which type of energy you want
+# textScaling tells how you want to scale the text on the axes and other places.
+##
+cdeGridGraphs <- function(countryAbbrev, energyType, textScaling=1.0){
   gammaGrid <- seq(0.0, 0.95, by=0.05)
   data <- cdeGridData(countryAbbrev, energyType, gammaGrid)
-  with(data, plot(gamma, SSE))
-  with(data, plot(gamma, lambda))
-  with(data, plot(gamma, alpha))
-  with(data, plot(gamma, beta))
-  with(data, plot(beta, SSE))
+  # Now melt the data so that it is in the correct form.
+  data_molten <- melt(data, id="gamma")
+  alphaBetaGammaRange <- c(0.0, 1.0)
+  alphaBetaGammaTics <- c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0)
+  lambdaRange <- c(0.0, 0.004)
+  lambdaTics <- c(0.0, 0.001, 0.002, 0.003, 0.004)
+  sseRange <- c(0.0, 0.08)
+  sseTics <- c(0.0, 0.02, 0.04, 0.06, 0.08)
+  # Create a lattice graph that shows the four variables (lambda, alpha, beta, and SSE) vs. gamma.
+  graph <- xyplot(value ~ gamma | variable, data=data_molten,
+                  # 1=lambda, 2=alpha, 3=SSE, 4=beta
+                  index.cond=list(c(3,1,2,4)), #orders the panels as SSE, lambda, alpha, beta.
+                  strip = strip.custom(factor.levels=c("$\\lambda$", "$\\alpha$", "$SSE$", "$\\beta$"), 
+                                       bg="transparent", # Sets background transparent to match the graph itself.
+                                       par.strip.text=list(cex=textScaling) # Scales text in the strip.
+                                       ),
+                  as.table=TRUE, #indexing of panels starts in upper left and goes across rows.
+                  pch = c(1), col.symbol = c("black"), #Controls symbol parameters
+                  scales=list(cex=scaleTextSize * textScaling, #controls text size on scales.
+                              tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
+                              x=list(relation="free",
+                                     at=alphaBetaGammaTics),
+                              y=list(relation="free",  #allows each axis to be different
+                                     #specifies location for tics
+                                     at=list(lambdaTics, alphaBetaGammaTics, sseTics, alphaBetaGammaTics))
+                              ), 
+                  ylim=list(lambdaRange, alphaBetaGammaRange, sseRange, alphaBetaGammaRange), #y axis limits
+                  #axis labels and scaling
+                  xlab=list(label="$\\gamma$", cex=textScaling), 
+                  ylab=list(label="")
+                  )
+  return(graph)
 }

### 2013-03-14 EconGrowth.Rnw
Now using melt to reshape the data for graphs of lambda, alpha, beta, and SSE vs. gamma for CDe parameter estimation. Creating a lattice graph of the same variables.
Now creating CDe grid graphs in both paper and presentation. Need to fix size of presentation graphs and scaling of presentation graph text.

@@
 
-The Cobb-Douglas with energy parameter estimation process is problematic. The following graphs show that the minimum of the squared-errors curve occurs at the point where $\beta \rightarrow 0.0$.
+The Cobb-Douglas with energy parameter estimation process is challenging.
+To demonstrate the characteristics of the parameter estimation process, we performed a grid search over values of $\gamma$, wherein we re-estimated values of $\lambda$, $\alpha$, and $\beta$ at each value of $\gamma$.
+Figure \ref{fig:CDeGammaGraphsZA} shows the sum of squared errors ($SSE$), $\lambda$, $\alpha$, and $\beta$ as a function of the fixed value of $\gamma$ for South Africa with thermal energy ($q$).
+The minimum $SSE$ occurs at a discontinuity caused by the constraint $\beta \geq 0.0$.
+The parameter estimation algorithm has difficulty recognizing the values of $\gamma$, $\alpha$, $\beta$, and $\lambda$ that produce minimum $SSE$, because the constrained model behaves very differently on either side of the discontinuity.
 
-<<CDeGammaGraphsZA, eval=TRUE>>=
+<<CDeGammaGraphsZA, fig.cap="Cobb-Douglas with thermal energy ($q$) grid search for minimum $SSE$ for South Africa.", fig.pos="H", eval=TRUE>>=
 cdeGridGraphs("ZA", "Q")

### 2013-03-14 EconGrowth-R-Functions.Rnw
Working on appearance of graphs for seminar presentation.

@@
 presentationGraph2ColWidth <- 2 #Inches
+presentationGraph1ColWidth <- 2*presentationGraph2ColWidth
 keyTextSize <- 0.85 #85% of normal size

### 2013-03-14 EconGrowthSeminar.Rnw
Now creating CDe grid graphs in both paper and presentation. Need to fix size of presentation graphs and scaling of presentation graph text.
Working on appearance of graphs for seminar presentation.

@@
 \begin{frame}{Example Cobb-Douglas Fit} %----------------------------
-<<CDeGammaGraphsZA>>=
-  cdeGridGraphs("ZA", "Q")
+<<CDeGammaGraphsZA, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight, eval=TRUE>>=
+  cdeGridGraphs("ZA", "Q", textScaling=0.3)
 @

### 2013-03-14 EconGrowth-R-Functions.Rnw
Now doing a double-y graph for the gamma plots.

@@
 #############################
-# This function creates a series of graphs for Cobb-Douglas with energy functions
-# showing various parameters as a function of gamma.
+# This function creates a graph for Cobb-Douglas with energy functions. The graph has 
+# a double Y axis. The first Y axis has alpha, beta, and gamma vs. gamma. The second Y axis
+# has SSE vs. gamma.
 # countryAbbrev tells which country you want to view
@@
 # textScaling tells how you want to scale the text on the axes and other places.
+# This 
 ##
@@
   # Create a lattice graph that shows the four variables (lambda, alpha, beta, and SSE) vs. gamma.
-  graph <- xyplot(value ~ gamma | variable, data=data_molten,
-                  # 1=lambda, 2=alpha, 3=SSE, 4=beta
-                  index.cond=list(c(3,1,2,4)), #orders the panels as SSE, lambda, alpha, beta.
-                  strip = strip.custom(factor.levels=c("$\\lambda$", "$\\alpha$", "$SSE$", "$\\beta$"), 
-                                       bg="transparent", # Sets background transparent to match the graph itself.
-                                       par.strip.text=list(cex=textScaling) # Scales text in the strip.
+#   graph <- xyplot(value ~ gamma | variable, data=data_molten,
+#                   # 1=lambda, 2=alpha, 3=SSE, 4=beta
+#                   index.cond=list(c(3,1,2,4)), #orders the panels as SSE, lambda, alpha, beta.
+#                   strip = strip.custom(factor.levels=c("$\\lambda$", "$\\alpha$", "$SSE$", "$\\beta$"), 
+#                                        bg="transparent", # Sets background transparent to match the graph itself.
+#                                        par.strip.text=list(cex=textScaling) # Scales text in the strip.
+#                                        ),
+#                   as.table=TRUE, #indexing of panels starts in upper left and goes across rows.
+#                   pch = c(1), col.symbol = c("black"), #Controls symbol parameters
+#                   scales=list(cex=scaleTextSize * textScaling, #controls text size on scales.
+#                               tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
+#                               x=list(relation="free",
+#                                      at=alphaBetaGammaTics),
+#                               y=list(relation="free",  #allows each axis to be different
+#                                      #specifies location for tics
+#                                      at=list(lambdaTics, alphaBetaGammaTics, sseTics, alphaBetaGammaTics))
+#                               ), 
+#                   ylim=list(lambdaRange, alphaBetaGammaRange, sseRange, alphaBetaGammaRange), #y axis limits
+#                   #axis labels and scaling
+#                   xlab=list(label="$\\gamma$", cex=textScaling), 
+#                   ylab=list(label="")
+#                   )
+#   return(graph)
+  abgGraph <- xyplot(alpha+beta+gamma ~ gamma, data=data,
+#                    pch = c(1), col.symbol = c("black"), #Controls symbol parameters
+                     scales=list(cex=scaleTextSize * textScaling, #controls text size on scales.
+                                 tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
+                                 x=list(at=c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0)), #location for x tics
+                                 y=list(at=c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0))  #location for y tics
                      ), 
-                  as.table=TRUE, #indexing of panels starts in upper left and goes across rows.
+                     ylim=c(0.0, 1.5), #y axis limits
+                     #axis labels and scaling
+                     xlab=list(label="$\\gamma$", cex=textScaling), 
+                     ylab=list(label="$\\lambda$, $\\alpha$, $\\beta$")
+  )
+  sseGraph <- xyplot(SSE ~ gamma, data=data,
                      pch = c(1), col.symbol = c("black"), #Controls symbol parameters
@@
                                  tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
-                              x=list(relation="free",
-                                     at=alphaBetaGammaTics),
-                              y=list(relation="free",  #allows each axis to be different
-                                     #specifies location for tics
-                                     at=list(lambdaTics, alphaBetaGammaTics, sseTics, alphaBetaGammaTics))
+                                 y=list(at=c(0.0, 0.02, 0.04, 0.06, 0.08))  #location for y tics
                      ), 
-                  ylim=list(lambdaRange, alphaBetaGammaRange, sseRange, alphaBetaGammaRange), #y axis limits
-                  #axis labels and scaling
-                  xlab=list(label="$\\gamma$", cex=textScaling), 
-                  ylab=list(label="")
-                  )
-  return(graph)
+                     ylim=c(0.0, 0.08),
+                     ylab=list(label="$SSE$")
+                     )
+  doubleYGraph <- doubleYScale(abgGraph, sseGraph, add.ylab2=TRUE)
+  return(doubleYGraph)
 }

### 2013-03-15 EconGrowth.Rnw
Now creating a graph of alpha, beta, gamma, and SSE vs. gamma. Looks good except for the text scaling for the axis labels and scales.

@@
 To demonstrate the characteristics of the parameter estimation process, we performed a grid search over values of $\gamma$, wherein we re-estimated values of $\lambda$, $\alpha$, and $\beta$ at each value of $\gamma$.
-Figure \ref{fig:CDeGammaGraphsZA} shows the sum of squared errors ($SSE$), $\lambda$, $\alpha$, and $\beta$ as a function of the fixed value of $\gamma$ for South Africa with thermal energy ($q$).
+Figure \ref{fig:CDeGammaGraphsZA} shows the sum of squared errors ($SSE$), $\alpha$, and $\beta$ as a function of the fixed value of $\gamma$ for South Africa with thermal energy ($q$).
 The minimum $SSE$ occurs at a discontinuity caused by the constraint $\beta \geq 0.0$.
@@
 
-<<CDeGammaGraphsZA, fig.cap="Cobb-Douglas with thermal energy ($q$) grid search for minimum $SSE$ for South Africa.", fig.pos="H", eval=TRUE>>=
-cdeGridGraphs("ZA", "Q")
+******** Fix the right y axis label. SSE should be italicized. *************
+
+<<CDeGammaGraphsZA, fig.width=5, fig.height=3, fig.align="center", fig.cap="Cobb-Douglas with thermal energy ($q$) grid search for minimum $SSE$ for South Africa.", fig.pos="H", eval=TRUE>>=
+cdeGridGraph("ZA", "Q")
 @

### 2013-03-15 EconGrowthSeminar.Rnw
Now creating a graph of alpha, beta, gamma, and SSE vs. gamma. Looks good except for the text scaling for the axis labels and scales.

--- 2013-03-12 EconGrowthSeminar.Rnw
@@
 
-\begin{frame}{Example Cobb-Douglas Fit} %----------------------------
-<<CDeGammaGraphsZA>>=
-  cdeGridGraphs("ZA", "Q")
+\begin{frame}{Example Cobb-Douglas With Energy Fit} %----------------------------
+<<CDeGammaGraphsZA, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight, eval=TRUE>>=
+  cdeGridGraph("ZA", "Q", textScaling=0.8)
 @

### 2013-03-15 EconGrowthSeminar.Rnw
Some changes to the seminar presentation.

--- 2013-03-12 EconGrowthSeminar.Rnw
@@
 
-\begin{frame}{Example Cobb-Douglas Fit} %----------------------------
-<<CDeGammaGraphsZA>>=
-  cdeGridGraphs("ZA", "Q")
+\begin{frame}{Parameter Estimation for Cobb-Douglas With Energy} %----------------------------
+  \begin{equation*} \label{eq:CD_With_Energy}
+    y = \mathrm{e}^{\lambda (t-t_0)}k^{\alpha}l^{\beta}e^{\gamma}
+  \end{equation*}
+  \begin{itemize}
+    \item{Objective: determine $\lambda$, $\alpha$, $\beta$, and $\gamma$ that best fits data}
+    \item{Almost identical to Cobb-Douglas without energy}
+    \item{Perform grid search over $\gamma$}
+    \item{Re-estimate $\lambda$, $\alpha$, and $\beta$ at each value of $\gamma$}
+    \item{Respect sum constraint ($\alpha + \beta + \gamma = 1$)}
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Grid Search Over $\gamma$}{South Africa Cobb-Douglas With Energy} %----------------------------
+<<CDeGammaGraphsZA, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight, eval=TRUE>>=
+  cdeGridGraph("ZA", "Q", textScaling=0.8)
 @

### 2013-03-15 EconGrowth-R-Functions.Rnw
Now including Dave Murphy's energy cost share graph. Re-organized the sections of the presentation to make more sense.

--- 2013-03-14 EconGrowth-R-Functions.Rnw
@@
 # textScaling tells how you want to scale the text on the axes and other places.
-##
-cdeGridGraphs <- function(countryAbbrev, energyType, textScaling=1.0){
+# This 
+##
+cdeGridGraph <- function(countryAbbrev, energyType, keyXLoc = defaultKeyXLoc, keyYLoc = defaultKeyYLoc, textScaling = 1.0){
   gammaGrid <- seq(0.0, 0.95, by=0.05)
@@
   # Create a lattice graph that shows the four variables (lambda, alpha, beta, and SSE) vs. gamma.
-  graph <- xyplot(value ~ gamma | variable, data=data_molten,
-                  # 1=lambda, 2=alpha, 3=SSE, 4=beta
-                  index.cond=list(c(3,1,2,4)), #orders the panels as SSE, lambda, alpha, beta.
-                  strip = strip.custom(factor.levels=c("$\\lambda$", "$\\alpha$", "$SSE$", "$\\beta$"), 
-                                       bg="transparent", # Sets background transparent to match the graph itself.
-                                       par.strip.text=list(cex=textScaling) # Scales text in the strip.
+  graphType <- "b" #b is for both symbls and lines. Necessary so that the key looks right.
+  lineTypes <- c(2, 1, 3, 0) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
+  lineWidths <- c(1, 3, 1, 0) #line widths. 0 means no line.
+  symbols <- c(NA, NA, NA, 1)
+  colors <- c("black", "black", "black", "black") #line and symbol colors
+  abgGraph <- xyplot(alpha+beta+gamma ~ gamma, data=data,
+                     type=graphType,
+                     lty = lineTypes, lwd = lineWidths, col = colors, #Controls line parameters
+                     pch = symbols, col.symbol = colors, #Controls symbol parameters
+                     key=list(text=list(c("$\\alpha$", "$\\beta$", "$\\gamma$", "$SSE$")),
+                              type=graphType,
+                              cex=keyTextSize * textScaling, #controls size of text in the key
+                              lines=list(lty=lineTypes, lwd=lineWidths), #controls line types
+                              pch=symbols, col=colors, #controls symbol (plot characters) types
+                              columns=keyColumns, x=keyXLoc, y=keyYLoc), #controls columns and position of the key
+                     scales=list(cex=scaleTextSize * textScaling, #controls text size on scales.
+                                 tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
+                                 x=list(at=c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0)), #location for x tics
+                                 y=list(at=c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0))  #location for y tics
                      ), 
-                  as.table=TRUE, #indexing of panels starts in upper left and goes across rows.
+                     ylim=c(0.0, 1.5), #y axis limits
+                     #axis labels and scaling
+                     xlab=list(label="$\\gamma$", cex=textScaling), 
+                     ylab=list(label="$\\lambda$, $\\alpha$, $\\beta$", cex=textScaling)
+  )
+  sseGraph <- xyplot(SSE ~ gamma, data=data,
                      pch = c(1), col.symbol = c("black"), #Controls symbol parameters
@@
                                  tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
-                              x=list(relation="free",
-                                     at=alphaBetaGammaTics),
-                              y=list(relation="free",  #allows each axis to be different
-                                     #specifies location for tics
-                                     at=list(lambdaTics, alphaBetaGammaTics, sseTics, alphaBetaGammaTics))
+                                 y=list(at=c(0.0, 0.02, 0.04, 0.06, 0.08)) #location for y tics                                          
                                  ), 
-                  ylim=list(lambdaRange, alphaBetaGammaRange, sseRange, alphaBetaGammaRange), #y axis limits
-                  #axis labels and scaling
-                  xlab=list(label="$\\gamma$", cex=textScaling), 
-                  ylab=list(label="")
-                  )
-  return(graph)
+                     ylim=c(0.0, 0.08),
+                     xlab=list(label="$\\gamma$", cex=textScaling), #Not used by the double-Y graph.
+                     ylab=list(label="$SSE$", cex=textScaling)
+                     )
+  # Combine the two graphs into a double-Y graph.
+  doubleYGraph <- doubleYScale(abgGraph, sseGraph, add.ylab2=TRUE, use.style=FALSE)
+  return(doubleYGraph)
 }

### 2013-03-15 EconGrowthSeminar.Rnw
Now including Dave Murphy's energy cost share graph. Re-organized the sections of the presentation to make more sense.

@@
 \title[Energy and Growth] % (optional, use only with long paper titles)
-{An Empirical Analysis of the Role of Energy in Economic Growth}
-
-%\subtitle
-%{Presentation Subtitle} % (optional)
+{The Role of Energy in Economic Growth}
+\subtitle
+{An Empirical Analysis} % (optional)
 
@@
 % the beginning of each subsection:
-% \AtBeginSubsection[]
-% {
-%   \begin{frame}<beamer>{Outline}
-%     \tableofcontents[currentsection,currentsubsection]
-%   \end{frame}
-% }
+\AtBeginSubsection[]
+{
+  \begin{frame}<beamer>{Outline}
+    \tableofcontents[currentsection,currentsubsection]
+  \end{frame}
+}
 
@@
 
-\begin{frame}{World Oil Supply is Tightening} %----------------------------
-  \framesubtitle{\citep{Tverberg:2013}}
+\begin{frame}{World Oil Supply is Tightening}{\citep{Tverberg:2013}} %----------------------------
   \includegraphics[width=4.0in]{figure_other/Figure_Tverberg_2013.png}
@@
   \begin{itemize}
-    \item{Energy is considered to be economically unimportant.}
-    \item{Compare cost shares of capital stock, labor, and energy.}
+    \item{$\sim$10\%}
+    \pause
+    \item{Energy unimportant for classical economists}
+    \vspace{\baselineskip}
+    \item{Energy usually ignored}
+    \pause
+    \vspace{\baselineskip}
+    \item{But \dots}
   \end{itemize}
@@
 
-\begin{frame}{Energy Cost Share and Economic Growth} %----------------------------
-  \framesubtitle{\citep{Bashmakov:2007ek}}
+\begin{frame}{Energy Cost Share and Economic Growth}{\citep{Bashmakov:2007ek}} %----------------------------
   \begin{center}
@@
   \end{center}
-%  \citet{Bashmakov:2007ek}
 \end{frame}
 
-\begin{frame}{Observations and Questions} %----------------------------
+\begin{frame}{Energy Cost Share and Economic Growth}{\citep{Murphy:2011jh}}  %----------------------------
+  \begin{center}
+    \includegraphics[height=6.3cm]{figure_other/Figure_Murphy_2011.png}
+  \end{center}  
+\end{frame}
+
+\begin{frame}{Observation and Questions} %----------------------------
   \begin{itemize}
     \item{Historical economic development paths (US, Western Europe) are energy intensive.}
+    \vspace{\baselineskip}
+    \pause
     \item{What happens when energy supplies are constrained and prices rise?}
     \item{Will developing countries be able to expand their economies?}
+    \vspace{\baselineskip}
+    \pause
     \item{How account for energy in economic models?}
@@
     \item{Goal: predict economic output over time}
-    \item{Economic output is a function of ``factors of production''}
-    \item{Output defined as GDP ($Y$)}
+    \item{Economic output ($Y$) is a function of ``factors of production''}
+    \item{Output ($Y$) defined as GDP}
     \item{All inputs and outputs normalized to initial year (0)}
@@
 \begin{frame}{Energy ($E$)} %----------------------------
+  \begin{itemize}
+    \item{Thermal energy ($Q$)}
+    \item{Exergy ($X$)}
+    \item{Useful work ($W$)}
+  \end{itemize}
+\end{frame}
+
+\subsection[Growth Models]{Economic Growth Models} %+++++++++++++++++++++++++++++++++++++++
+
+\begin{frame}{No Shortage of Economic Growth Models} %----------------------------
+  Single Factor: $y = \mathrm{e}^{\lambda (t-t_0)}f^{m}$
+  \vspace{\baselineskip}
+  \pause
+
+  Cobb-Douglas: $y = \mathrm{e}^{\lambda (t-t_0)}k^{\alpha}l^{\beta}$
+  \vspace{\baselineskip}
+  \pause
+
+  Cobb-Douglas with Energy: $y = \mathrm{e}^{\lambda (t-t_0)}k^{\alpha}l^{\beta}e^{\gamma}$
+  \vspace{\baselineskip}
+  \pause
+
+  Constant Elasticity of Substitution:
+  \small
+  $y = \gamma \mathrm{e}^{\lambda(t-t_0)} \left\{\delta \left[\delta_1 k^{-\rho_1} + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1} + (1-\delta) e^{-\rho} \right\}^{-1/\rho}$
+  \normalsize
+  \vspace{\baselineskip}
+  \pause
+
+  LINEX: $y = e \: \mathrm{e}^{\left[a_0 \left(2 - \frac{l + e}{k} \right) + a_0 c_t \left(\frac{l}{e} - 1 \right)\right]}$
+  \vspace{\baselineskip}
+  \pause
+
+  System Dynamics Models
+\end{frame}
+
+\begin{frame}{The Question} %----------------------------
+  Which economic growth model best describes (statistically) the role of energy in economic growth for different types of economies?
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section[Data Sources]{Sources of Data}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection[Economic Data]{Sources of Economic Data} %+++++++++++++++++++++++++++++++++++++++
+
+\begin{frame}{Economic Data} %----------------------------
+  Lucas complete
+\end{frame}
+
+\subsection[Energy Data]{Sources of Energy Data} %+++++++++++++++++++++++++++++++++++++++
+
+\begin{frame}{Energy Data} %----------------------------
   Caleb complete
@@
 
-\begin{frame}{Thermal Energy ($Q$)} %----------------------------
-  Caleb complete
+\subsection[Graphs]{Historical Data} %+++++++++++++++++++++++++++++++++++++++
+
+\begin{frame}{USA and China} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+<<Historical_Data_US, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+createHistoricalLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@    
+    \column{2.2in}
+<<Historical_Data_CN, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+createHistoricalLatticeGraph("CN", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
 \end{frame}
 
-\begin{frame}{Exergy ($X$)} %----------------------------
-  Caleb complete
+\begin{frame}{South Africa and Saudi Arabia} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+<<Historical_Data_ZA, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+createHistoricalLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@    
+    \column{2.2in}
+<<Historical_Data_SA, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+createHistoricalLatticeGraph("SA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
 \end{frame}
 
-\begin{frame}{Useful Work ($W$)} %----------------------------
-  Caleb complete
-\end{frame}
-
-\subsection[Growth Models]{Economic Growth Models} %+++++++++++++++++++++++++++++++++++++++
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section[Analysis]{Analysis of Growth Models}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \begin{frame}{Cobb-Douglas} %----------------------------
-  \begin{equation*} \label{eq:CD_With_Energy}
+  \begin{equation*} \label{eq:CD_Without_Energy}
+    y = \mathrm{e}^{\lambda (t-t_0)}k^{\alpha}l^{\beta}
+  \end{equation*}
+  \begin{equation*} \label{eq:CD_Const_Returns_To_Scale}
+    \alpha + \beta = 1
+  \end{equation*}
+  \begin{equation*} \label{eq:CD_Constraints}
+    0 \leq \alpha, \beta \leq 1
+  \end{equation*}
+  \begin{center}
+    \begin{tabular}{|c|l|}\hline
+      $k$   & $K$/$K_0$, capital stock\\
+      $l$   & $L$/$L_0$, labor\\
+      \hline
+      $\lambda$   &   technological progress\\
+      $\alpha$   &    ``strength'' of capital\\
+      $\beta$   &    ``strength'' of labor\\
+      \hline
+    \end{tabular}
+  \end{center}
+\end{frame}
+
+\begin{frame}{Example Cobb-Douglas Fits}
+
+Heun complete.
+
+\end{frame}
+
+\begin{frame}{Cobb-Douglas With Energy} %----------------------------
+  \begin{equation*} \label{eq:CDe_With_Energy}
     y = \mathrm{e}^{\lambda (t-t_0)}k^{\alpha}l^{\beta}e^{\gamma}
   \end{equation*}
-  \begin{equation*} \label{eq:CD_Const_Returns_To_Scale}
+  \begin{equation*} \label{eq:CDe_Const_Returns_To_Scale}
     \alpha + \beta + \gamma = 1
   \end{equation*}
-  \begin{equation*} \label{eq:CD_Constraints}
+  \begin{equation*} \label{eq:CDe_Constraints}
     0 \leq \alpha, \beta, \gamma \leq 1
@@
 \begin{frame}{Parameter Estimation for Cobb-Douglas With Energy} %----------------------------
-  \begin{equation*} \label{eq:CD_With_Energy}
+  \begin{equation*}
+    y = \mathrm{e}^{\lambda (t-t_0)}k^{\alpha}l^{\beta}e^{\gamma}
+  \end{equation*}
+  \begin{itemize}
+    \item{Objective: determine $\lambda$, $\alpha$, $\beta$, and $\gamma$ that best fits historical data}
+    \item{Almost identical to Cobb-Douglas without energy}
+    \item{Perform grid search over $\gamma$}
+    \item{Re-estimate $\lambda$, $\alpha$, and $\beta$ at each value of $\gamma$}
+    \item{Respect sum constraint ($\alpha + \beta + \gamma = 1$)}
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Parameter Estimation for Cobb-Douglas With Energy} %----------------------------
+  \begin{equation*}
     y = \mathrm{e}^{\lambda (t-t_0)}k^{\alpha}l^{\beta}e^{\gamma}
@@
 \begin{frame}{Grid Search Over $\gamma$}{South Africa Cobb-Douglas With Energy} %----------------------------
-<<CDeGammaGraphsZA, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight, eval=TRUE>>=
+<<CDeGammaGraphsZA, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
   cdeGridGraph("ZA", "Q", textScaling=0.8)
@@
   Heun complete
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section[Data Sources]{Sources of Data}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection[Economic Data]{Sources of Economic Data} %+++++++++++++++++++++++++++++++++++++++
-
-\begin{frame}{Economic Data} %----------------------------
-  Lucas complete
-\end{frame}
-
-\subsection[Energy Data]{Sources of Energy Data} %+++++++++++++++++++++++++++++++++++++++
-
-\begin{frame}{Energy Data} %----------------------------
-  Caleb complete
-\end{frame}
-
-\subsection[Graphs]{Historical Data} %+++++++++++++++++++++++++++++++++++++++
-
-\begin{frame}{USA and China} %----------------------------
-  \begin{columns}[c]
-    \column{2.2in}
-<<Historical_Data_US, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-createHistoricalLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
-@    
-    \column{2.2in}
-<<Historical_Data_CN, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-createHistoricalLatticeGraph("CN", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
-@
-  \end{columns}
-\end{frame}
-
-\begin{frame}{South Africa and Saudi Arabia} %----------------------------
-  \begin{columns}[c]
-    \column{2.2in}
-<<Historical_Data_ZA, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-createHistoricalLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
-@    
-    \column{2.2in}
-<<Historical_Data_SA, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-createHistoricalLatticeGraph("SA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
-@
-  \end{columns}
 \end{frame}
@@
 \begin{frame}{Conclusions} %----------------------------
-
   \begin{itemize}
@@
   \end{itemize}
-
 \end{frame}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Bibliography}
+\section*{References}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2013-03-17 EconGrowthSeminar.Rnw
Now including separator pages in presentation.

@@
 
-\pgfdeclareimage[height=1.56cm]{university-logo}{CalvinLogo.png}
+\pgfdeclareimage[height=1.56cm]{university-logo}{figure_other/CalvinLogo.png}
 \logo{\pgfuseimage{university-logo}}
@@
 % the following command: 
-
 %\beamerdefaultoverlayspecification{<+->}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{frame} %----------------------------
+  \begin{center} \huge
+    INTRODUCTION
+  \normalsize \end{center}
+\end{frame}
 
@@
     \item{$\sim$10\%}
+    \vspace{\baselineskip}
     \pause
-    \item{Energy unimportant for classical economists}
+    \item{Energy (relatively) unimportant for classical economists}
+    \item{Usually ignored}
     \vspace{\baselineskip}
-    \item{Energy usually ignored}
     \pause
-    \vspace{\baselineskip}
     \item{But \dots}
@@
     \pause
-    \item{How account for energy in economic models?}
+    \item{How should we account for energy in economic models?}
   \end{itemize}
@@
 
+\begin{frame} %----------------------------
+  \begin{center} \Large
+    Factors of Production
+  \normalsize \end{center}
+\end{frame}
+
 \begin{frame}{Capital Stock ($K$) and Labor ($L$)} %----------------------------
@@
 \subsection[Growth Models]{Economic Growth Models} %+++++++++++++++++++++++++++++++++++++++
+
+\begin{frame} %----------------------------
+  \begin{center} \Large
+    Economic Growth Models
+  \normalsize \end{center}
+\end{frame}
 
@@
 
-\begin{frame}{The Question} %----------------------------
+\subsection[The Question]{The Question} %+++++++++++++++++++++++++++++++++++++++
+
+\begin{frame} %----------------------------
+  \begin{center} \Large
+    The Question
+  \normalsize \end{center}
   Which economic growth model best describes (statistically) the role of energy in economic growth for different types of economies?
@@
 
+\begin{frame} %----------------------------
+  \begin{center} \huge
+    SOURCES OF DATA
+  \normalsize \end{center}
+\end{frame}
+
 \subsection[Economic Data]{Sources of Economic Data} %+++++++++++++++++++++++++++++++++++++++
+
+\begin{frame} %----------------------------
+  \begin{center} \Large
+    Economic Data
+  \normalsize \end{center}
+\end{frame}
 
@@
 
+\begin{frame} %----------------------------
+  \begin{center} \Large
+    Energy Data
+  \normalsize \end{center}
+\end{frame}
+
 \begin{frame}{Energy Data} %----------------------------
@@
 \subsection[Graphs]{Historical Data} %+++++++++++++++++++++++++++++++++++++++
+
+\begin{frame} %----------------------------
+  \begin{center} \Large
+    Historical Data
+  \normalsize \end{center}
+\end{frame}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{frame} %----------------------------
+  \begin{center} \huge
+    ANALYSIS OF GROWTH MODELS
+  \normalsize \end{center}
+\end{frame}
 
@@
 
-\begin{frame}{Example Cobb-Douglas Fits}
-
-Heun complete.
-
+\begin{frame}{Example Cobb-Douglas Fit} %----------------------------
+  Heun complete
 \end{frame}
@@
 
-\begin{frame}{Parameter Estimation for Cobb-Douglas With Energy} %----------------------------
-  \begin{equation*}
-    y = \mathrm{e}^{\lambda (t-t_0)}k^{\alpha}l^{\beta}e^{\gamma}
-  \end{equation*}
-  \begin{itemize}
-    \item{Objective: determine $\lambda$, $\alpha$, $\beta$, and $\gamma$ that best fits data}
-    \item{Almost identical to Cobb-Douglas without energy}
-    \item{Perform grid search over $\gamma$}
-    \item{Re-estimate $\lambda$, $\alpha$, and $\beta$ at each value of $\gamma$}
-    \item{Respect sum constraint ($\alpha + \beta + \gamma = 1$)}
-  \end{itemize}
-\end{frame}
-
 \begin{frame}{Grid Search Over $\gamma$}{South Africa Cobb-Douglas With Energy} %----------------------------
@@
 @
+\end{frame}
+
+\begin{frame}{Cobb-Douglas with Energy Example Fit} %----------------------------
+  Heun complete
 \end{frame}
@@
       $\lambda$  &   technological progress\\
+      $\delta_1$   &   split between ($k$) and ($l$)\\
+      $\rho_1$     &   ``strength'' of ($k$) vs. ($l$)\\
       $\delta$   &   split between ($kl$) and ($e$)\\
       $\rho$     &   ``strength'' of ($kl$) vs. ($e$)\\
-      $\delta_1$   &   split between ($k$) and ($l$)\\
-      $\rho_1$     &   ``strength'' of ($k$) vs. ($l$)\\
       \hline
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{frame} %----------------------------
+  \begin{center} \huge
+    RESULTS
+  \normalsize \end{center}
+\end{frame}
 
@@
 
-\begin{frame}{Conclusions} %----------------------------
+\begin{frame} %----------------------------
+  \begin{center} \huge
+    SUMMARY
+  \normalsize \end{center}
+\end{frame}
+
+\begin{frame}{Tentative Conclusions} %----------------------------
   \begin{itemize}
-  \item
-    Including energy is unwarranted \\
+  \item{Including energy is unwarranted \\
         \scriptsize
-    Little statistical evidence that including energy in production functions improves fit.
-    \normalsize
-  \item
-    Including energy is unnecessary \\
+        Little statistical evidence that including energy in production functions improves stastical properties of fitting parameters.
+        \normalsize}
+  \item{Including energy is unnecessary \\
         \scriptsize
-    Energy is always \emph{already} embedded in capital stock ($K$) and labor ($L$).
-    \normalsize
-  \vskip0pt plus.5fill
-  \item
-    Need a modeling method that captures energy's embeddedness \\
+        Energy is \emph{always already} embedded in capital stock ($K$) and labor ($L$).
+        \normalsize}
+  \vspace{\baselineskip}
+  \item{Need a modeling method that captures energy's embeddedness \\
         \scriptsize
         System dynamics modeling
-    \normalsize
+        \normalsize}
   \end{itemize}
@@
     \item{Estimate statistical properties for \emph{all} fitting parameters}
+    \vspace{\baselineskip}
+    \vspace{\baselineskip}
     \item{Complete paper}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{References}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \begin{frame}{References} %----------------------------
   \bibliographystyle{plainnat}
-  \renewcommand{\thepage}{\arabic{page}}
   \tiny

### 2013-03-17 EconGrowth-R-Functions.Rnw
Now including ZA flag. Now including data from US Single Factor fits. ZA single factor fits not yet working.

--- 2013-03-15 EconGrowth-R-Functions.Rnw
@@
 createSFParamsGraph <- function(factor){
-  # Set the name of the 2nd graph (m)
-  factorLabel <- paste("$", tolower(factor), "$", sep="")
+  # Figure out the exponent for the desired factor
+  if (factor == "K"){
+    exponentParameter <- "$\\alpha$"
+  } else if (factor == "L"){
+    exponentParameter <- "$\\beta$"
+  } else if ((factor == "Q") || (factor == "X") || (factor == "U")){
+    exponentParameter <- "$\\gamma$"
+  }
   # Create a data table with the following columns:
@@
                    lwd = 1, #Sets line width to 1.0
-                   strip = strip.custom(bg="white", factor.levels=c("$\\lambda$", factorLabel)),
+                   strip = strip.custom(bg="white", factor.levels=c("$\\lambda$", exponentParameter)),
                    ylim = list(c(-0.05, 0.1), c(-0.5, 1.5)), #y axis limits

### 2013-03-17 EconGrowthSeminar.Rnw
Now including ZA flag. Now including data from US Single Factor fits. ZA single factor fits not yet working.

@@
 
-\begin{frame}{Energy Cost Share and Economic Growth}{\citep{Bashmakov:2007ek}} %----------------------------
+\begin{frame}{Energy Cost Share}{\citep{Bashmakov:2007ek}} %----------------------------
   \begin{center}
@@
   \begin{center}
-    \includegraphics[height=6.3cm]{figure_other/Figure_Murphy_2011.png}
+    \includegraphics[height=6.0cm]{figure_other/Figure_Murphy_2011.png}
   \end{center}  
@@
   \begin{center} \huge
-    SOURCES OF DATA
+    DATA SOURCES
   \normalsize \end{center}
@@
   \begin{center} \huge
-    ANALYSIS OF GROWTH MODELS
+    ANALYSIS OF\\
+    \vspace{\baselineskip}
+    GROWTH MODELS
   \normalsize \end{center}
@@
 
-\begin{frame}{Example Single-Factor Fit} %----------------------------
-  Heun complete
+\begin{frame}{\includegraphics[height=0.25in]{figure_other/flag_us.pdf} Single-Factor Fit} %----------------------------
+<<Results_Table_US_SF, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+sfUSK <- singleFactorModel("US", "K")
+sfUSL <- singleFactorModel("US", "L")
+sfUSQ <- singleFactorModel("US", "Q")
+sfUSX <- singleFactorModel("US", "X")
+sfUSU <- singleFactorModel("US", "U")
+@
+  \begin{columns}[c]
+    \column{2.2in}
+      \begin{center}
+        $y = \mathrm{e}^{\lambda (t-t_0)}f^{m}$
+        \vspace{\baselineskip}
+
+        \tiny
+          \begin{tabular}{|c|c|c|}\hline
+            $f$   & $\lambda$                      & $m$\\
+            \hline
+            $k$   & \Sexpr{coef(sfUSK)["lambda"]}  & \Sexpr{coef(sfUSK)["m"]}\\
+            \hline
+            $l$   & \Sexpr{coef(sfUSL)["lambda"]}  & \Sexpr{coef(sfUSL)["m"]}\\
+            \hline
+            $q$   & \Sexpr{coef(sfUSQ)["lambda"]}  & \Sexpr{coef(sfUSQ)["m"]}\\
+            \hline
+            $x$   & \Sexpr{coef(sfUSX)["lambda"]}  & \Sexpr{coef(sfUSX)["m"]}\\
+            \hline
+            $u$   & \Sexpr{coef(sfUSU)["lambda"]}  & \Sexpr{coef(sfUSU)["m"]}\\
+            \hline
+          \end{tabular}
+        \normalsize
+      \end{center}
+    \column{2.2in}
+<<Results_Graph_US_SF, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+createSFLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
+\end{frame}
+
+\begin{frame}{\includegraphics[height=0.25in]{figure_other/flag_za.png} Single-Factor Fit} %----------------------------
+<<Results_Table_ZA_SF, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+sfZAK <- singleFactorModel("ZA", "K")
+sfZAL <- singleFactorModel("ZA", "L")
+sfZAQ <- singleFactorModel("ZA", "Q")
+sfZAX <- singleFactorModel("ZA", "X")
+sfZAU <- singleFactorModel("ZA", "U")
+@
+  \begin{columns}[c]
+    \column{2.2in}
+%       \begin{center}
+%         $y = \mathrm{e}^{\lambda (t-t_0)}f^{m}$
+%         \vspace{\baselineskip}
+%         
+%         \tiny
+%           \begin{tabular}{|c|c|c|}\hline
+%             $f$   & $\lambda$                      & $m$\\
+%             \hline
+%             $k$   & \Sexpr{coef(sfZAK)["lambda"]}  & \Sexpr{coef(sfZAK)["m"]}\\
+%             \hline
+%             $l$   & \Sexpr{coef(sfZAL)["lambda"]}  & \Sexpr{coef(sfZAL)["m"]}\\
+%             \hline
+%             $q$   & \Sexpr{coef(sfZAQ)["lambda"]}  & \Sexpr{coef(sfZAQ)["m"]}\\
+%             \hline
+%             $x$   & \Sexpr{coef(sfZAX)["lambda"]}  & \Sexpr{coef(sfZAX)["m"]}\\
+%             \hline
+%             $u$   & \Sexpr{coef(sfZAU)["lambda"]}  & \Sexpr{coef(sfZAU)["m"]}\\
+%             \hline
+%           \end{tabular}
+%         \normalsize
+%       \end{center}
+    \column{2.2in}
+<<Results_Graph_ZA_SF, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+createSFLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
 \end{frame}
@@
     \column{2.2in}
-<<Results_US_SF, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-createSFLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
-@
+% <<Results_US_SF, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+% createSFLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+% @
     \column{2.2in}
@@
 
+\begin{frame}{Acknowledgements} %----------------------------
+  \begin{itemize}
+    \item{Martin de Wit, Stellenbosch University}
+    \item{Randall Pruim, Calvin College}
+    \item{Loren L. Heun, Western Michigan University}
+    \vspace{\baselineskip}
+    \item{Jack and Lois Kuipers Applied Mathematics Endowment\\(Reese and Timmer Summer 2012 funding)}
+    \item{Calvin College Alumni Association\\(Reese Fall 2012 funding)}
+  \end{itemize}  
+\end{frame}
+
 \begin{frame}{References} %----------------------------

### 2013-03-18 EconGrowthSeminar.Rnw
Now using \newcommand for repeated text in the presentation, such as production functions and rows in variable tables.

@@
 
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
+% A bunch of useful commands for this presentation
+% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
+
+% The equation for a single-factor model
+\newcommand{\sfEqn}{$y = \mathrm{e}^{\lambda (t-t_0)}f^{m}$}
+% The equation for a cobb-douglas without energy model
+\newcommand{\cdEqn}{$y = \mathrm{e}^{\lambda (t-t_0)}k^{\alpha}l^{\beta}$}
+% The equation for a cobb-douglas with energy model
+\newcommand{\cdeEqn}{$y = \mathrm{e}^{\lambda (t-t_0)}k^{\alpha}l^{\beta}e^{\gamma}$}
+% The equation for a ces model
+\newcommand{\cesEqn}{$y = \gamma \mathrm{e}^{\lambda(t-t_0)} \left\{\delta \left[\delta_1 k^{-\rho_1} + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1} + (1-\delta) e^{-\rho} \right\}^{-1/\rho}$}
+% The equation for a linex model
+\newcommand{\linexEqn}{$y = e \: \mathrm{e}^{\left[a_0 \left(2 - \frac{l + e}{k} \right) + a_0 c_t \left(\frac{l}{e} - 1 \right)\right]}$}
+
+% Some commands for parameter tables in slides
+\newcommand{\yRow}{$y$ & $Y/Y_0$, output}
+\newcommand{\timeRow}{$t$ & year}
+\newcommand{\initialTimeRow}{$t_0$ & initial year}
+\newcommand{\kRow}{$k$ & $K/K_0$, capital stock}
+\newcommand{\lRow}{$l$ & $L/L_0$, labor}
+\newcommand{\eRow}{$e$ & $E/E_0$, any of $q$, $x$, or $u$}
+\newcommand{\lambdaRow}{$\lambda$ & technological progress}
+\newcommand{\alphaRow}{$\alpha$ & ``strength'' of capital}
+\newcommand{\betaRow}{$\beta$ & ``strength'' of labor}
+\newcommand{\gammaRow}{$\gamma$ & ``strength'' of energy}
+
 \begin{document} %**************************************************
@@
 \begin{frame}{No Shortage of Economic Growth Models} %----------------------------
-  Single Factor: $y = \mathrm{e}^{\lambda (t-t_0)}f^{m}$
+  Single Factor: \sfEqn
   \vspace{\baselineskip}
@@
 
-  Cobb-Douglas: $y = \mathrm{e}^{\lambda (t-t_0)}k^{\alpha}l^{\beta}$
+  Cobb-Douglas: \cdEqn
   \vspace{\baselineskip}
@@
 
-  Cobb-Douglas with Energy: $y = \mathrm{e}^{\lambda (t-t_0)}k^{\alpha}l^{\beta}e^{\gamma}$
+  Cobb-Douglas with Energy: \cdeEqn
   \vspace{\baselineskip}
@@
   \small
-  $y = \gamma \mathrm{e}^{\lambda(t-t_0)} \left\{\delta \left[\delta_1 k^{-\rho_1} + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1} + (1-\delta) e^{-\rho} \right\}^{-1/\rho}$
+  \cesEqn
   \normalsize
@@
 
-  LINEX: $y = e \: \mathrm{e}^{\left[a_0 \left(2 - \frac{l + e}{k} \right) + a_0 c_t \left(\frac{l}{e} - 1 \right)\right]}$
+  LINEX: \linexEqn
   \vspace{\baselineskip}
@@
 \begin{frame}{Single Factor} %----------------------------
-  \begin{equation*} \label{eq:Single_Factor_Generic}
-    y = \mathrm{e}^{\lambda (t-t_0)}f^{m}
-  \end{equation*}
   \begin{center}
+    \sfEqn
+    \vspace{\baselineskip}
+
     \begin{tabular}{|c|l|}\hline
-      $y$   & $Y$/$Y_0$ \\
-      $t$   & year\\
-      $t_0$ & initial year\\
+      \yRow\\
+      \timeRow\\
+      \initialTimeRow\\
       $f$ & $F$/$F_0$, a factor of production\\
       \hline
-      $\lambda$   &   technological progress\\
+      \lambdaRow\\
       $m$ & ``strength'' of factor $f$\\
@@
       \begin{center}
-        $y = \mathrm{e}^{\lambda (t-t_0)}f^{m}$
+        \sfEqn
         \vspace{\baselineskip}
@@
 
-\begin{frame}{\includegraphics[height=0.25in]{figure_other/flag_za.png} Single-Factor Fit} %----------------------------
-<<Results_Table_ZA_SF, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-sfZAK <- singleFactorModel("ZA", "K")
-sfZAL <- singleFactorModel("ZA", "L")
-sfZAQ <- singleFactorModel("ZA", "Q")
-sfZAX <- singleFactorModel("ZA", "X")
-sfZAU <- singleFactorModel("ZA", "U")
-@
-  \begin{columns}[c]
-    \column{2.2in}
+% \begin{frame}{\includegraphics[height=0.25in]{figure_other/flag_za.png} Single-Factor Fit} %----------------------------
+% <<Results_Table_ZA_SF, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+% sfZAK <- singleFactorModel("ZA", "K")
+% sfZAL <- singleFactorModel("ZA", "L")
+% sfZAQ <- singleFactorModel("ZA", "Q")
+% sfZAX <- singleFactorModel("ZA", "X")
+% sfZAU <- singleFactorModel("ZA", "U")
+% @
+%   \begin{columns}[c]
+%     \column{2.2in}
 %       \begin{center}
@@
 %       \end{center}
-    \column{2.2in}
-<<Results_Graph_ZA_SF, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-createSFLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
-@
-  \end{columns}
-\end{frame}
+%     \column{2.2in}
+% <<Results_Graph_ZA_SF, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+% createSFLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+% @
+%   \end{columns}
+% \end{frame}
 
 \begin{frame}{Cobb-Douglas} %----------------------------
-  \begin{equation*} \label{eq:CD_Without_Energy}
-    y = \mathrm{e}^{\lambda (t-t_0)}k^{\alpha}l^{\beta}
-  \end{equation*}
-  \begin{equation*} \label{eq:CD_Const_Returns_To_Scale}
-    \alpha + \beta = 1
-  \end{equation*}
-  \begin{equation*} \label{eq:CD_Constraints}
-    0 \leq \alpha, \beta \leq 1
-  \end{equation*}
   \begin{center}
+    \cdEqn\\
+    $\alpha + \beta = 1$\\
+    $0 \leq \alpha, \beta \leq 1$
+    \vspace{\baselineskip}
+
     \begin{tabular}{|c|l|}\hline
-      $k$   & $K$/$K_0$, capital stock\\
-      $l$   & $L$/$L_0$, labor\\
+      \yRow\\
+      \timeRow\\
+      \initialTimeRow\\
+      \kRow\\
+      \lRow\\
       \hline
-      $\lambda$   &   technological progress\\
-      $\alpha$   &    ``strength'' of capital\\
-      $\beta$   &    ``strength'' of labor\\
+      \lambdaRow\\
+      \alphaRow\\
+      \betaRow\\
       \hline
@@
 \begin{frame}{Cobb-Douglas With Energy} %----------------------------
-  \begin{equation*} \label{eq:CDe_With_Energy}
-    y = \mathrm{e}^{\lambda (t-t_0)}k^{\alpha}l^{\beta}e^{\gamma}
-  \end{equation*}
-  \begin{equation*} \label{eq:CDe_Const_Returns_To_Scale}
-    \alpha + \beta + \gamma = 1
-  \end{equation*}
-  \begin{equation*} \label{eq:CDe_Constraints}
-    0 \leq \alpha, \beta, \gamma \leq 1
-  \end{equation*}
   \begin{center}
+    \cdeEqn\\
+    $\alpha + \beta + \gamma = 1$\\
+    $0 \leq \alpha, \beta, \gamma \leq 1$
+    \vspace{\baselineskip}
+
     \begin{tabular}{|c|l|}\hline
-      $k$   & $K$/$K_0$, capital stock\\
-      $l$   & $L$/$L_0$, labor\\
-      $e$   & $E$/$E_0$, any of $q$, $x$, or $u$\\
+      \yRow\\
+      \timeRow\\
+      \initialTimeRow\\
+      \kRow\\
+      \lRow\\
+      \eRow\\
       \hline
-      $\lambda$   &   technological progress\\
-      $\alpha$   &    ``strength'' of capital\\
-      $\beta$   &    ``strength'' of labor\\
-      $\gamma$   &    ``strength'' of energy\\
+      \lambdaRow\\
+      \alphaRow\\
+      \betaRow\\
+      \gammaRow\\
       \hline
@@
 \begin{frame}{Parameter Estimation for Cobb-Douglas With Energy} %----------------------------
-  \begin{equation*}
-    y = \mathrm{e}^{\lambda (t-t_0)}k^{\alpha}l^{\beta}e^{\gamma}
-  \end{equation*}
+  \begin{center}
+    \cdeEqn
+  \end{center}
   \begin{itemize}
@@
 \begin{frame}{Constant Elasticity of Substitution (CES)} %----------------------------
-  \begin{equation*} \label{eq:micEconCES_model}
-    \begin{split}
-    y = & \gamma \mathrm{e}^{\lambda(t-t_0)} \\
-        & \cdot \left\{\delta \left[\delta_1 k^{-\rho_1} + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1} 
-                        + (1-\delta) e^{-\rho} \right\}^{-1/\rho}
-    \end{split}
-  \end{equation*}
   \begin{center}
+    \small
+      \cesEqn
+    \normalsize
+    \vspace{\baselineskip}
+
     \begin{tabular}{|c|l|}\hline
-      $k$   & $K$/$K_0$, capital stock\\
-      $l$   & $L$/$L_0$, labor\\
-      $e$   & $E$/$E_0$, any of $q$, $x$, or $u$\\
+      \yRow\\
+      \timeRow\\
+      \initialTimeRow\\
+      \kRow\\
+      \lRow\\
+      \eRow\\
       \hline
       $\gamma$   &   fitting coefficient\\
-      $\lambda$  &   technological progress\\
+      \lambdaRow\\
       $\delta_1$   &   split between ($k$) and ($l$)\\
@@
 \begin{frame}{LINEX} %----------------------------
-  \begin{equation*} \label{eq:LINEX_model}
-    y = e \: \mathrm{e}^{\left[a_0 \left(2 - \frac{l + e}{k} \right) + a_0 c_t \left(\frac{l}{e} - 1 \right)\right]}
-  \end{equation*}
   \begin{center}
+    \linexEqn
+    \vspace{\baselineskip}
+
     \begin{tabular}{|c|l|}\hline
-      $k$   & $K$/$K_0$, capital stock\\
-      $l$   & $L$/$L_0$, labor\\
-      $e$   & $E$/$E_0$, any of $q$, $x$, or $u$\\
+      \kRow\\
+      \lRow\\
+      \eRow\\
       \hline

### 2013-03-18 EconGrowthSeminar.Rnw
Now have a macro for placing scaled graphics at a specific location on the page. Using that macro for placing a US flag on pages that include US data in the presentation.

@@
 
+\usepackage{tikz} % To use the tikzpicture environment.
+
 \title[Energy and Growth] % (optional, use only with long paper titles)
@@
 \newcommand{\gammaRow}{$\gamma$ & ``strength'' of energy}
+
+% Places an image (with scaling) at a position on the page
+% Arguments:
+%  #1 image path
+%  #2 image scaling (1.0 = same size as original image, 2.0 = double size)
+%  #3 x offset from center of the frame (include units, if desired. e.g. "1.0in")
+%  #4 y offset from center of the frame (include units, if desired. e.g. "1.0in")
+\newcommand{\putat}[4]{
+  \begin{tikzpicture}[remember picture,overlay] 
+    \node [xshift=#3, yshift=#4] at (current page.center){
+      \includegraphics[scale=#2]{#1}
+    };             
+  \end{tikzpicture}
+}
 
@@
 
-\begin{frame}{\includegraphics[height=0.25in]{figure_other/flag_us.pdf} Single-Factor Fit} %----------------------------
+\begin{frame}{Single-Factor $y$ Predictions} %----------------------------
+
 <<Results_Table_US_SF, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
@@
   \end{columns}
+  % Including at bottom of frame so as not to push other material downward on the frame.
+  \putat{figure_other/flag_us.pdf}{0.055}{2.14in}{1.59in}
 \end{frame}

### 2013-03-19 EconGrowth-R-Functions.Rnw
Now including details of CDe parameter estimation for US and ZA.

--- 2013-03-17 EconGrowth-R-Functions.Rnw
@@
                  )
-# print("str(modelCD)")
-# print(str(modelCD))
-# print("")
-# print(modelCD$)
-#   # We estimated alpha with the above code, but we have beta = 1.0 - alpha. So, get 
-#   # an estimate for beta and add it to the model.
-#   summaryCD <- summary(modelCD)
-# print("summaryCD")
-# print(summaryCD)
-#   dofCD <- summaryCD$df[2] # Gives the degrees of freedom for the model.
-#   tvalCD <- qt(ciHalfLevel, df = dofCD)
-#   alpha <- coef(modelCD)["alpha"]
-#   betaEst <- deltaMethod(modelCD, "1 - alpha") # Estimates beta and its standard error (SE).
-# print("betaEst")
-# print(betaEst)
-#   # Calculate beta and its confidence interval and report it.
-#   # Now calculate a confidence interval on beta
-#   betaCICD <- with(betaEst, Estimate + c(-1.0, 1.0) * tvalCD * SE); betaCICD # Gives the confidence interval on beta.  
-# print("betaCICD")
-# print(betaCICD)
-
   return(modelCD)

### 2013-03-19 EconGrowthSeminar.Rnw
Now including details of CDe parameter estimation for US and ZA.

@@
 
+<<Coefs_US_SF>>=
+sfUSK <- coef(singleFactorModel("US", "K"))
+sfUSL <- coef(singleFactorModel("US", "L"))
+sfUSQ <- coef(singleFactorModel("US", "Q"))
+sfUSX <- coef(singleFactorModel("US", "X"))
+sfUSU <- coef(singleFactorModel("US", "U"))
+@
 \begin{frame}{Single-Factor $y$ Predictions} %----------------------------
-
-<<Results_Table_US_SF, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-sfUSK <- singleFactorModel("US", "K")
-sfUSL <- singleFactorModel("US", "L")
-sfUSQ <- singleFactorModel("US", "Q")
-sfUSX <- singleFactorModel("US", "X")
-sfUSU <- singleFactorModel("US", "U")
-@
   \begin{columns}[c]
@@
             \hline
-            $k$   & \Sexpr{coef(sfUSK)["lambda"]}  & \Sexpr{coef(sfUSK)["m"]}\\
+            $k$   & \Sexpr{sfUSK["lambda"]}  & \Sexpr{sfUSK["m"]}\\
             \hline
-            $l$   & \Sexpr{coef(sfUSL)["lambda"]}  & \Sexpr{coef(sfUSL)["m"]}\\
+            $l$   & \Sexpr{sfUSL["lambda"]}  & \Sexpr{sfUSL["m"]}\\
             \hline
-            $q$   & \Sexpr{coef(sfUSQ)["lambda"]}  & \Sexpr{coef(sfUSQ)["m"]}\\
+            $q$   & \Sexpr{sfUSQ["lambda"]}  & \Sexpr{sfUSQ["m"]}\\
             \hline
-            $x$   & \Sexpr{coef(sfUSX)["lambda"]}  & \Sexpr{coef(sfUSX)["m"]}\\
+            $x$   & \Sexpr{sfUSX["lambda"]}  & \Sexpr{sfUSX["m"]}\\
             \hline
-            $u$   & \Sexpr{coef(sfUSU)["lambda"]}  & \Sexpr{coef(sfUSU)["m"]}\\
+            $u$   & \Sexpr{sfUSU["lambda"]}  & \Sexpr{sfUSU["m"]}\\
             \hline
@@
   \end{columns}
-  % Including at bottom of frame so as not to push other material downward on the frame.
+  % Including at bottom of frame so as not to push other material downward in the frame.
   \putat{figure_other/flag_us.pdf}{0.055}{2.14in}{1.59in}
@@
 
-% \begin{frame}{\includegraphics[height=0.25in]{figure_other/flag_za.png} Single-Factor Fit} %----------------------------
-% <<Results_Table_ZA_SF, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-% sfZAK <- singleFactorModel("ZA", "K")
-% sfZAL <- singleFactorModel("ZA", "L")
-% sfZAQ <- singleFactorModel("ZA", "Q")
-% sfZAX <- singleFactorModel("ZA", "X")
-% sfZAU <- singleFactorModel("ZA", "U")
-% @
-%   \begin{columns}[c]
-%     \column{2.2in}
-%       \begin{center}
-%         $y = \mathrm{e}^{\lambda (t-t_0)}f^{m}$
-%         \vspace{\baselineskip}
-%         
-%         \tiny
-%           \begin{tabular}{|c|c|c|}\hline
-%             $f$   & $\lambda$                      & $m$\\
-%             \hline
-%             $k$   & \Sexpr{coef(sfZAK)["lambda"]}  & \Sexpr{coef(sfZAK)["m"]}\\
-%             \hline
-%             $l$   & \Sexpr{coef(sfZAL)["lambda"]}  & \Sexpr{coef(sfZAL)["m"]}\\
-%             \hline
-%             $q$   & \Sexpr{coef(sfZAQ)["lambda"]}  & \Sexpr{coef(sfZAQ)["m"]}\\
-%             \hline
-%             $x$   & \Sexpr{coef(sfZAX)["lambda"]}  & \Sexpr{coef(sfZAX)["m"]}\\
-%             \hline
-%             $u$   & \Sexpr{coef(sfZAU)["lambda"]}  & \Sexpr{coef(sfZAU)["m"]}\\
-%             \hline
-%           \end{tabular}
-%         \normalsize
-%       \end{center}
-%     \column{2.2in}
-% <<Results_Graph_ZA_SF, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-% createSFLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
-% @
-%   \end{columns}
-% \end{frame}
-
-\begin{frame}{Cobb-Douglas} %----------------------------
+\begin{frame}{Cobb-Douglas (without Energy)} %----------------------------
   \begin{center}
@@
 
-\begin{frame}{Example Cobb-Douglas Fit} %----------------------------
-  Heun complete
-\end{frame}
-
-\begin{frame}{Cobb-Douglas With Energy} %----------------------------
+\begin{frame}{Cobb-Douglas (with Energy)} %----------------------------
   \begin{center}
@@
     \item{Re-estimate $\lambda$, $\alpha$, and $\beta$ at each value of $\gamma$}
-    \item{Respect sum constraint ($\alpha + \beta + \gamma = 1$)}
+    \item{Respect sum constraint: $\alpha + \beta + \gamma = 1$}
+    \item{Respect absolute constraints: $0 \leq \alpha, \beta, \gamma \leq 1$}
   \end{itemize}
@@
 
-\begin{frame}{Grid Search Over $\gamma$}{South Africa Cobb-Douglas With Energy} %----------------------------
+\begin{frame}{Grid Search Over $\gamma$}{US Cobb-Douglas With $q$} %----------------------------
+<<CDeGammaGraphsUS, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
+  cdeGridGraph("US", "Q", textScaling=0.8)
+@
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putat{figure_other/flag_us.pdf}{0.055}{2.14in}{1.59in}
+\end{frame}
+
+<<Coefs_US_CD>>=
+cdUS <- cobbDouglasData("US")
+cdqUS <- cobbDouglasData("US", "Q")
+cdxUS <- cobbDouglasData("US", "X")
+cduUS <- cobbDouglasData("US", "U")
+@
+\begin{frame}{Cobb-Douglas $y$ Predictions} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+      \begin{center}
+        \cdeEqn
+        \vspace{\baselineskip}
+
+        \tiny
+          \begin{tabular}{|c|c|c|c|c|}\hline
+            $e$ & $\lambda$ & $\alpha$ & $\beta$ & $\gamma$\\
+            \hline
+                  & \Sexpr{cdUS["CD", "lambda"]} & \Sexpr{cdUS["CD", "alpha"]} & \Sexpr{cdUS["CD", "beta"]} & \Sexpr{cdUS["CD", "gamma"]}\\
+            \hline
+            $q$   & \Sexpr{cdqUS["CD", "lambda"]} & \Sexpr{cdxUS["CD", "alpha"]} & \Sexpr{cdqUS["CD", "beta"]} & \Sexpr{cdqUS["CD", "gamma"]}\\
+            \hline
+            $x$   & \Sexpr{cdxUS["CD", "lambda"]} & \Sexpr{cdxUS["CD", "alpha"]} & \Sexpr{cdxUS["CD", "beta"]} & \Sexpr{cdxUS["CD", "gamma"]}\\
+            \hline
+            $u$   & \Sexpr{cduUS["CD", "lambda"]} & \Sexpr{cduUS["CD", "alpha"]} & \Sexpr{cduUS["CD", "beta"]} & \Sexpr{cduUS["CD", "gamma"]}\\
+            \hline
+          \end{tabular}
+        \normalsize
+      \end{center}
+    \column{2.2in}
+<<Results_Graph_US_CD, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+createCDLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putat{figure_other/flag_us.pdf}{0.055}{2.14in}{1.59in}
+\end{frame}
+
+\begin{frame}{Grid Search Over $\gamma$}{ZA Cobb-Douglas With $q$} %----------------------------
 <<CDeGammaGraphsZA, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
@@
 @
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putat{figure_other/flag_za.png}{0.055}{2.14in}{1.59in}
 \end{frame}
 
-\begin{frame}{Cobb-Douglas with Energy Example Fit} %----------------------------
-  Heun complete
+<<Coefs_ZA_CD>>=
+cdZA <- cobbDouglasData("ZA")
+cdqZA <- cobbDouglasData("ZA", "Q")
+cdxZA <- cobbDouglasData("ZA", "X")
+@
+\begin{frame}{Cobb-Douglas $y$ Predictions} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+      \begin{center}
+        \cdeEqn
+        \vspace{\baselineskip}
+
+        \tiny
+          \begin{tabular}{|c|c|c|c|c|}\hline
+            $e$ & $\lambda$ & $\alpha$ & $\beta$ & $\gamma$\\
+            \hline
+                  & \Sexpr{cdZA["CD", "lambda"]} & \Sexpr{cdZA["CD", "alpha"]} & \Sexpr{cdZA["CD", "beta"]} & \Sexpr{cdZA["CD", "gamma"]}\\
+            \hline
+            $q$   & \Sexpr{cdqZA["CD", "lambda"]} & \Sexpr{cdxZA["CD", "alpha"]} & \Sexpr{cdqZA["CD", "beta"]} & \Sexpr{cdqZA["CD", "gamma"]}\\
+            \hline
+            $x$   & \Sexpr{cdxZA["CD", "lambda"]} & \Sexpr{cdxZA["CD", "alpha"]} & \Sexpr{cdxZA["CD", "beta"]} & \Sexpr{cdxZA["CD", "gamma"]}\\
+            \hline
+          \end{tabular}
+        \normalsize
+      \end{center}
+    \column{2.2in}
+<<Results_Graph_US_ZA, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+createCDLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putat{figure_other/flag_za.png}{0.055}{2.14in}{1.59in}
 \end{frame}

### 2013-03-19 EconGrowth.Rnw
Some changes to the seminar presentation.
Now including additional slides and graphs for TZ and UK cde models.

@@
 
-******** Fix the right y axis label. SSE should be italicized. *************
+******** Fix the right y axis label. SSE should be italicized. Also, scaling on the axis labels and scales is not being picked up. *************
 
-<<CDeGammaGraphsZA, fig.width=5, fig.height=3, fig.align="center", fig.cap="Cobb-Douglas with thermal energy ($q$) grid search for minimum $SSE$ for South Africa.", fig.pos="H", eval=TRUE>>=
+<<CDeGammaGraphsZA, fig.width=5, fig.height=3, fig.align="center", fig.cap="Cobb-Douglas with thermal energy ($q$) grid search for minimum $SSE$ for South Africa.", fig.pos="H">>=
 cdeGridGraph("ZA", "Q")

### 2013-03-19 EconGrowthSeminar.Rnw
Now including additional slides and graphs for TZ and UK cde models.

@@
 
+\begin{frame}{Grid Search Over $\gamma$}{UK Cobb-Douglas With $q$} %----------------------------
+<<CDeGammaGraphsUK, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
+  cdeGridGraph("UK", "Q", textScaling=0.8)
+@
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putat{figure_other/flag_uk.png}{0.048}{2.14in}{1.59in}
+\end{frame}
+
 \begin{frame}{Grid Search Over $\gamma$}{ZA Cobb-Douglas With $q$} %----------------------------
@@
             \hline
-            $q$   & \Sexpr{cdqZA["CD", "lambda"]} & \Sexpr{cdxZA["CD", "alpha"]} & \Sexpr{cdqZA["CD", "beta"]} & \Sexpr{cdqZA["CD", "gamma"]}\\
+            $q$   & \Sexpr{cdqZA["CD", "lambda"]} & \Sexpr{cdxZA["CD", "alpha"]} & \Sexpr{round(cdqZA["CD", "beta"], digits=4)} & \Sexpr{cdqZA["CD", "gamma"]}\\
             \hline
-            $x$   & \Sexpr{cdxZA["CD", "lambda"]} & \Sexpr{cdxZA["CD", "alpha"]} & \Sexpr{cdxZA["CD", "beta"]} & \Sexpr{cdxZA["CD", "gamma"]}\\
+            $x$   & \Sexpr{cdxZA["CD", "lambda"]} & \Sexpr{cdxZA["CD", "alpha"]} & \Sexpr{round(cdxZA["CD", "beta"], digits=4)} & \Sexpr{cdxZA["CD", "gamma"]}\\
             \hline
@@
   \putat{figure_other/flag_za.png}{0.055}{2.14in}{1.59in}
+\end{frame}
+
+\begin{frame}{Grid Search Over $\gamma$}{TZ Cobb-Douglas With $q$} %----------------------------
+<<CDeGammaGraphsTZ, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
+  cdeGridGraph("TZ", "Q", textScaling=0.8)
+@
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putat{figure_other/flag_tz.png}{0.055}{2.14in}{1.59in}
 \end{frame}

### 2013-03-19 EconGrowthSeminar.Rnw
Fixed size of UK flag.
Added several additional flags. Added SSE vs. gamma graphs for all countries.

@@
   % Including at bottom of frame so as not to push other material downward in the frame.
-  \putat{figure_other/flag_us.pdf}{0.055}{2.14in}{1.59in}
+  \putat{figure_other/flag_us.png}{0.055}{2.14in}{1.59in}
 \end{frame}
@@
   % Including at bottom of frame so as not to push other material downward in the frame.
-  \putat{figure_other/flag_us.pdf}{0.055}{2.14in}{1.59in}
+  \putat{figure_other/flag_us.png}{0.055}{2.14in}{1.59in}
+\end{frame}
+
+\begin{frame}{Grid Search Over $\gamma$}{UK Cobb-Douglas With $q$} %----------------------------
+<<CDeGammaGraphsUK, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
+  cdeGridGraph("UK", "Q", textScaling=0.8)
+@
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putat{figure_other/flag_uk.png}{0.045}{2.14in}{1.59in}
+\end{frame}
+
+\begin{frame}{Grid Search Over $\gamma$}{JP Cobb-Douglas With $q$} %----------------------------
+<<CDeGammaGraphsJP, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
+  cdeGridGraph("JP", "Q", textScaling=0.8)
+@
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putat{figure_other/flag_jp.png}{0.045}{2.14in}{1.59in}
+\end{frame}
+
+\begin{frame}{Grid Search Over $\gamma$}{CN Cobb-Douglas With $q$} %----------------------------
+<<CDeGammaGraphsCN, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
+  cdeGridGraph("CN", "Q", textScaling=0.8)
+@
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putat{figure_other/flag_jp.png}{0.045}{2.14in}{1.59in}
+\end{frame}
+
+\begin{frame}{Grid Search Over $\gamma$}{ZA Cobb-Douglas With $q$} %----------------------------
+<<CDeGammaGraphsZA, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
+  cdeGridGraph("ZA", "Q", textScaling=0.8)
+@
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putat{figure_other/flag_za.png}{0.055}{2.14in}{1.59in}
+\end{frame}
+
+\begin{frame}{Grid Search Over $\gamma$}{SA Cobb-Douglas With $q$} %----------------------------
+<<CDeGammaGraphsSA, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
+  cdeGridGraph("SA", "Q", textScaling=0.8)
+@
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putat{figure_other/flag_sa.png}{0.055}{2.14in}{1.59in}
+\end{frame}
+
+\begin{frame}{Grid Search Over $\gamma$}{IR Cobb-Douglas With $q$} %----------------------------
+<<CDeGammaGraphsIR, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
+  cdeGridGraph("IR", "Q", textScaling=0.8)
+@
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putat{figure_other/flag_ir.png}{0.055}{2.14in}{1.59in}
+\end{frame}
+
+\begin{frame}{Grid Search Over $\gamma$}{TZ Cobb-Douglas With $q$} %----------------------------
+<<CDeGammaGraphsTZ, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
+  cdeGridGraph("TZ", "Q", textScaling=0.8)
+@
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putat{figure_other/flag_tz.png}{0.055}{2.14in}{1.59in}
+\end{frame}
+
+\begin{frame}{Grid Search Over $\gamma$}{ZM Cobb-Douglas With $q$} %----------------------------
+<<CDeGammaGraphsZM, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
+  cdeGridGraph("ZM", "Q", textScaling=0.8)
+@
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putat{figure_other/flag_zm.png}{0.055}{2.14in}{1.59in}
 \end{frame}
@@
   % Including at bottom of frame so as not to push other material downward in the frame.
-  \putat{figure_other/flag_us.pdf}{0.055}{2.14in}{1.59in}
-\end{frame}
-
-\begin{frame}{Grid Search Over $\gamma$}{UK Cobb-Douglas With $q$} %----------------------------
-<<CDeGammaGraphsUK, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
-  cdeGridGraph("UK", "Q", textScaling=0.8)
-@
-  % Including at bottom of frame so as not to push other material downward in the frame.
-  \putat{figure_other/flag_uk.png}{0.048}{2.14in}{1.59in}
-\end{frame}
-
-\begin{frame}{Grid Search Over $\gamma$}{ZA Cobb-Douglas With $q$} %----------------------------
-<<CDeGammaGraphsZA, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
-  cdeGridGraph("ZA", "Q", textScaling=0.8)
-@
-  % Including at bottom of frame so as not to push other material downward in the frame.
-  \putat{figure_other/flag_za.png}{0.055}{2.14in}{1.59in}
+  \putat{figure_other/flag_us.png}{0.055}{2.14in}{1.59in}
 \end{frame}
@@
 cdxZA <- cobbDouglasData("ZA", "X")
+pprint <- function(num, digits = 4){
+  out <- formatC(num, digit=digits, format="f")
+  return(out)
+}
 @
@@
             \hline
-                  & \Sexpr{cdZA["CD", "lambda"]} & \Sexpr{cdZA["CD", "alpha"]} & \Sexpr{cdZA["CD", "beta"]} & \Sexpr{cdZA["CD", "gamma"]}\\
+                  & \Sexpr{pprint(cdZA["CD", "lambda"])} & \Sexpr{cdZA["CD", "alpha"]} & \Sexpr{cdZA["CD", "beta"]} & \Sexpr{pprint(cdZA["CD", "gamma"])}\\
             \hline
-            $q$   & \Sexpr{cdqZA["CD", "lambda"]} & \Sexpr{cdxZA["CD", "alpha"]} & \Sexpr{round(cdqZA["CD", "beta"], digits=4)} & \Sexpr{cdqZA["CD", "gamma"]}\\
+            $q$   & \Sexpr{cdqZA["CD", "lambda"]} & \Sexpr{cdxZA["CD", "alpha"]} & \Sexpr{pprint(cdqZA["CD", "beta"])} & \Sexpr{cdqZA["CD", "gamma"]}\\
             \hline
-            $x$   & \Sexpr{cdxZA["CD", "lambda"]} & \Sexpr{cdxZA["CD", "alpha"]} & \Sexpr{round(cdxZA["CD", "beta"], digits=4)} & \Sexpr{cdxZA["CD", "gamma"]}\\
+            $x$   & \Sexpr{cdxZA["CD", "lambda"]} & \Sexpr{cdxZA["CD", "alpha"]} & \Sexpr{pprint(cdxZA["CD", "beta"])} & \Sexpr{cdxZA["CD", "gamma"]}\\
             \hline
@@
   \putat{figure_other/flag_za.png}{0.055}{2.14in}{1.59in}
-\end{frame}
-
-\begin{frame}{Grid Search Over $\gamma$}{TZ Cobb-Douglas With $q$} %----------------------------
-<<CDeGammaGraphsTZ, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
-  cdeGridGraph("TZ", "Q", textScaling=0.8)
-@
-  % Including at bottom of frame so as not to push other material downward in the frame.
-  \putat{figure_other/flag_tz.png}{0.055}{2.14in}{1.59in}
 \end{frame}

### 2013-03-19 EconGrowthSeminar.Rnw
Added Japan CD parameters.

@@
 
+<<Coefs_JP_CD>>=
+cdJP <- cobbDouglasData("JP")
+cdqJP <- cobbDouglasData("JP", "Q")
+cdxJP <- cobbDouglasData("JP", "X")
+cduJP <- cobbDouglasData("JP", "U")
+@
+\begin{frame}{Cobb-Douglas $y$ Predictions} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+      \begin{center}
+        \cdeEqn
+        \vspace{\baselineskip}
+
+        \tiny
+          \begin{tabular}{|c|c|c|c|c|}\hline
+            $e$ & $\lambda$ & $\alpha$ & $\beta$ & $\gamma$\\
+            \hline
+                  & \Sexpr{cdJP["CD", "lambda"]} & \Sexpr{cdJP["CD", "alpha"]} & \Sexpr{cdJP["CD", "beta"]} & \Sexpr{cdJP["CD", "gamma"]}\\
+            \hline
+            $q$   & \Sexpr{cdqJP["CD", "lambda"]} & \Sexpr{cdxJP["CD", "alpha"]} & \Sexpr{cdqJP["CD", "beta"]} & \Sexpr{cdqJP["CD", "gamma"]}\\
+            \hline
+            $x$   & \Sexpr{cdxJP["CD", "lambda"]} & \Sexpr{cdxJP["CD", "alpha"]} & \Sexpr{cdxJP["CD", "beta"]} & \Sexpr{cdxJP["CD", "gamma"]}\\
+            \hline
+            $u$   & \Sexpr{cduJP["CD", "lambda"]} & \Sexpr{cduJP["CD", "alpha"]} & \Sexpr{cduJP["CD", "beta"]} & \Sexpr{cduJP["CD", "gamma"]}\\
+            \hline
+          \end{tabular}
+        \normalsize
+      \end{center}
+    \column{2.2in}
+<<Results_Graph_JP_CD, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+createCDLatticeGraph("JP", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putat{figure_other/flag_jp.png}{0.055}{2.14in}{1.59in}
+\end{frame}
+
 <<Coefs_ZA_CD>>=

### 2013-03-20 EconGrowthSeminar.Rnw
Added a macro to place flag images in the upper-right corner of slides.

@@
 
-% Places an image (with scaling) at a position on the page
+% Provides the upper-right location on a page useful for positioning flags on frames
+\newcommand{\upperRightFlagLocation}{\{2.14in\}\{1.59in\}}
+
+% Places an image (with scaling) at a position on the page. The origin (0, 0) is 
+% assumed to be at the center of the frame.
 % Arguments:
@@
   \end{tikzpicture}
+}
+
+% Places a flag image in the upper-right portion of the slide. Assumes that the flag
+% file is called flag_<country_abbreviation>.png and is located in 
+% a directory called figure_other. This macro calls the \putat macro with location
+% x = 2.14 and y = 1.59in.
+% Arguments:
+%  #1 2-letter country code (lower case)
+%  #2 scale factor
+\newcommand{\putFlagUpperRight}[2]{
+  \putat{figure_other/flag_#1.png}{#2}{2.14in}{1.59in}
 }
@@
   % Including at bottom of frame so as not to push other material downward in the frame.
-  \putat{figure_other/flag_us.png}{0.055}{2.14in}{1.59in}
+  \putFlagUpperRight{us}{0.055}
 \end{frame}
@@
   % Including at bottom of frame so as not to push other material downward in the frame.
-  \putat{figure_other/flag_uk.png}{0.045}{2.14in}{1.59in}
+  \putFlagUpperRight{uk}{0.045}
 \end{frame}
@@
   % Including at bottom of frame so as not to push other material downward in the frame.
-  \putat{figure_other/flag_jp.png}{0.045}{2.14in}{1.59in}
+  \putFlagUpperRight{jp}{0.045}
 \end{frame}
@@
   % Including at bottom of frame so as not to push other material downward in the frame.
-  \putat{figure_other/flag_jp.png}{0.045}{2.14in}{1.59in}
+  \putFlagUpperRight{cn}{0.045}
 \end{frame}
@@
   % Including at bottom of frame so as not to push other material downward in the frame.
-  \putat{figure_other/flag_za.png}{0.055}{2.14in}{1.59in}
+  \putFlagUpperRight{za}{0.055}
 \end{frame}
@@
   % Including at bottom of frame so as not to push other material downward in the frame.
-  \putat{figure_other/flag_sa.png}{0.055}{2.14in}{1.59in}
+  \putFlagUpperRight{sa}{0.055}
 \end{frame}
@@
   % Including at bottom of frame so as not to push other material downward in the frame.
-  \putat{figure_other/flag_ir.png}{0.055}{2.14in}{1.59in}
+  \putFlagUpperRight{ir}{0.055}
 \end{frame}
@@
   % Including at bottom of frame so as not to push other material downward in the frame.
-  \putat{figure_other/flag_tz.png}{0.055}{2.14in}{1.59in}
+  \putFlagUpperRight{tz}{0.07}
 \end{frame}
@@
   % Including at bottom of frame so as not to push other material downward in the frame.
-  \putat{figure_other/flag_zm.png}{0.055}{2.14in}{1.59in}
+  \putFlagUpperRight{zm}{0.055}
 \end{frame}
@@
   % Including at bottom of frame so as not to push other material downward in the frame.
-  \putat{figure_other/flag_jp.png}{0.055}{2.14in}{1.59in}
+  \putFlagUpperRight{jp}{0.055}
 \end{frame}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Appendix}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{frame} %----------------------------
+  \begin{center} \huge
+    APPENDIX
+  \normalsize \end{center}
+\end{frame}
+
 \end{document} %**************************************************

### 2013-03-21 EconGrowth-R-Functions.Rnw
Now creating a 3-D graph of SSE vs. lambda and gamma for SF US Q.

@@
   return(graph)
+}
+
+#########################
+# Creates a 3-D wireframe graph with SSE on the vertical axis and 
+# lambda and m on the horizontal axes.
+# params: 
+#   countryAbbrev: 2-letter country code (upper case)
+#   factor: the factor of production you want to use in the single-factor model.
+##
+sf3DSSEGraph <- function(countryAbbrev, factor){
+  # Generate the data in the form of a matrix with gamma in columns, lambda in rows, and SSE in the middle
+  # First, make a data.frame with which we want to make predictions
+  lambdaSeq <- seq(0.0, 0.05, by=0.01)
+  mSeq <- seq(0.0, 1.0, by=0.1)
+
+  lambdaSeq <- data.frame(lambdaSeq)
+  nRowLambda <- nrow(lambdaSeq)
+  colnames(lambdaSeq) <- "lambda"
+
+  mSeq <- data.frame(mSeq)
+  nRowM <- nrow(mSeq)
+  colnames(mSeq) <- "m"
+
+  # Make a sequence of lambda values based on the number of m values you have.
+  lambda <- rep(lambdaSeq[1,1], nRowM)
+  lambda <- data.frame(lambda)
+  colnames(lambda) <- "lambda"
+  for (i in 2:nRowLambda){
+    lambdaTemp <- rep(lambdaSeq[i, 1], nRowM)
+    lambdaTemp <- data.frame(lambdaTemp)
+    colnames(lambdaTemp) <- "lambda"
+    lambda <- rbind(lambda, lambdaTemp)
+  }
+
+  # Make repeats of the m data frame as we have number of lambda rows
+  m <- mSeq
+  for (i in 2:nRowLambda){
+    m <- rbind(m, mSeq)
+  }
+
+  # Now create the data.frame of new observation locations
+  newX <- cbind(lambda, m)
+
+  # Get the actual data
+  data <- loadData(countryAbbrev)
+  y_act <- data[ ,"iGDP"] # Pick off the GDP column
+  y_act <- data.frame(y_act)
+
+  # Make predictions
+  # Get the model
+  model <- singleFactorModel(countryAbbrev, factor)
+
+  sse <- c(1:(nRowLambda*nRowM)) # Build a bogus vector at the start
+
+  # Loop over all the different combinations of lambda and m that are of interest for us.
+  #i = 1
+  for (i in 1:(nRowLambda*nRowM)){
+    y_pred <- predict(model, newX[i,]) # Get lambda and m for this particular row.
+    y_pred <- data.frame(y_pred)
+
+    compareDF <- cbind(y_pred, y_act)
+    se <- with(compareDF, (y_pred-y_act)^2) # Makes a column of squared errors at each year
+    compareDF <- cbind(compareDF, se) # Bind it to the data frame as an additional column
+
+    # Now get the sse
+    sums <- colSums(compareDF)
+    sse[i] <- sums[3] # squared error (se) is the 3rd column
+  }
+  ssedf <- data.frame(sse)
+  colnames(ssedf) <- "sse"
+
+  # Now merge the sse column and the newX data to form a data.frame fit for 3-D plotting
+  dataFor3DGraph <- cbind(newX, ssedf)
+
+  # Create the lattice graph
+  fig <- wireframe(sse ~ lambda * m,
+                   data = dataFor3DGraph,
+                   xlab = "$\\lambda$",
+                   ylab = "$\\gamma$",
+                   zlab = "$SSE$")
+  return(fig)    
 }

### 2013-03-21 EconGrowthSeminar.Rnw
Added new slides to better explain the curve-fit process as optimization.
Now creating a 3-D graph of SSE vs. lambda and gamma for SF US Q.

@@
   \begin{center} \huge
-    ANALYSIS OF\\
+    ANALYSIS OF
+    \vspace{\baselineskip}
     \vspace{\baselineskip}
@@
 
-<<Coefs_US_SF>>=
+\begin{frame}{Curve-fitting As Optimization} %----------------------------
+  \begin{itemize}
+    \item{Select values of parameters to minimize errors ($SSE$) between predicted and historical economic output $y$}
+    \vspace{\baselineskip}
+
+    \item{Example: Single-factor Model with $q$}
+    \begin{itemize}
+      \item{$y = \mathrm{e}^{\lambda (t-t_0)}q^{\gamma}$}
+      \item{Select $\lambda$ and $\gamma$ to minimize\\
+            $SSE = \sum\limits_{t=1980}^{2011}(y_{pred} - y_{act})^2$}
+    \end{itemize}
+  \end{itemize}
+\end{frame}
+
+<<Coefs_US_SF, eval=TRUE>>=
 sfUSK <- coef(singleFactorModel("US", "K"))
@@
 @
+
+\begin{frame}{$SSE$ Minimization} %---------------------------- 
+<<3D_Graph_US_SF_Q, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight, eval=TRUE>>=
+sf3DSSEGraph("US", "Q")
+@
+  \begin{center}
+    $y = \mathrm{e}^{\lambda (t-t_0)}q^{\gamma}$
+  \end{center}
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{us}{0.055}  
+\end{frame}
+
 \begin{frame}{Single-Factor $y$ Predictions} %----------------------------

### 2013-03-21 EconGrowth-R-Functions.Rnw
Many edits on the 3-D wireframe graph.

@@
 
+  # Adjust settings for a nicer graph
+  #trellis.par.set("axis.line", list(col="transparent"))
+
   # Create the lattice graph
@@
                    data = dataFor3DGraph,
+                   screen = list(z = -20, x = -65),
                    xlab = "$\\lambda$",
                    ylab = "$\\gamma$",
-                   zlab = "$SSE$")
+                   zlab = list(label="$SSE$", rot=90),
+                   scales = list(arrows=FALSE, 
+                                 cex=0.45, 
+                                 col="black", 
+                                 tck=0.8,
+                                 x=list(at=c(0.00, 0.01, 0.02, 0.03)),
+                                 y=list(at=c(0.0, 0.5, 1.0)),
+                                 z=list(at=c(10, 20, 30))
+                                 ),
+                   xlim = c(0.0, 0.04), # lambda axis
+                   ylim = c(0.0, 1.0), # gamma axis
+                   zlim = c(0, 30) # sse axis
+                   )
   return(fig)    

### 2013-03-21 EconGrowthSeminar.Rnw
Many edits on the 3-D wireframe graph.

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section[Analysis]{Analysis of Growth Models}
+\section[Evaluation]{Evaluation of Growth Models}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \begin{center} \huge
-    ANALYSIS OF
-    \vspace{\baselineskip}
+    EVALUATION OF
     \vspace{\baselineskip}
@@
 
-\begin{frame}{$SSE$ Minimization} %---------------------------- 
-<<3D_Graph_US_SF_Q, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight, eval=TRUE>>=
+\begin{frame}{$SSE$ Minimization}{US Single-factor with $q$} %---------------------------- 
+<<3D_Graph_US_SF_Q, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3, eval=TRUE>>=
 sf3DSSEGraph("US", "Q")
 @
-  \begin{center}
-    $y = \mathrm{e}^{\lambda (t-t_0)}q^{\gamma}$
-  \end{center}
   % Including at bottom of frame so as not to push other material downward in the frame.
@@
 
-\begin{frame}{Grid Search Over $\gamma$}{US Cobb-Douglas With $q$} %----------------------------
+\begin{frame}{Grid Search Over $\gamma$}{US Cobb-Douglas with $q$} %----------------------------
 <<CDeGammaGraphsUS, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
@@
 
-\begin{frame}{Grid Search Over $\gamma$}{UK Cobb-Douglas With $q$} %----------------------------
+\begin{frame}{Grid Search Over $\gamma$}{UK Cobb-Douglas with $q$} %----------------------------
 <<CDeGammaGraphsUK, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
@@
 
-\begin{frame}{Grid Search Over $\gamma$}{JP Cobb-Douglas With $q$} %----------------------------
+\begin{frame}{Grid Search Over $\gamma$}{JP Cobb-Douglas with $q$} %----------------------------
 <<CDeGammaGraphsJP, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
@@
 
-\begin{frame}{Grid Search Over $\gamma$}{CN Cobb-Douglas With $q$} %----------------------------
+\begin{frame}{Grid Search Over $\gamma$}{CN Cobb-Douglas with $q$} %----------------------------
 <<CDeGammaGraphsCN, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
@@
 
-\begin{frame}{Grid Search Over $\gamma$}{ZA Cobb-Douglas With $q$} %----------------------------
+\begin{frame}{Grid Search Over $\gamma$}{ZA Cobb-Douglas with $q$} %----------------------------
 <<CDeGammaGraphsZA, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
@@
 
-\begin{frame}{Grid Search Over $\gamma$}{SA Cobb-Douglas With $q$} %----------------------------
+\begin{frame}{Grid Search Over $\gamma$}{SA Cobb-Douglas with $q$} %----------------------------
 <<CDeGammaGraphsSA, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
@@
 
-\begin{frame}{Grid Search Over $\gamma$}{IR Cobb-Douglas With $q$} %----------------------------
+\begin{frame}{Grid Search Over $\gamma$}{IR Cobb-Douglas with $q$} %----------------------------
 <<CDeGammaGraphsIR, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
@@
 
-\begin{frame}{Grid Search Over $\gamma$}{TZ Cobb-Douglas With $q$} %----------------------------
+\begin{frame}{Grid Search Over $\gamma$}{TZ Cobb-Douglas with $q$} %----------------------------
 <<CDeGammaGraphsTZ, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
@@
 
-\begin{frame}{Grid Search Over $\gamma$}{ZM Cobb-Douglas With $q$} %----------------------------
+\begin{frame}{Grid Search Over $\gamma$}{ZM Cobb-Douglas with $q$} %----------------------------
 <<CDeGammaGraphsZM, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=

### 2013-03-21 EconGrowth-R-Functions.Rnw
Now using nice macros for major and minor separator slides in the presentation. Also added a graph for the statistical parameters of the Sf models.

@@
                    lwd = 1, #Sets line width to 1.0
-                   strip = strip.custom(bg="white", factor.levels=c("$\\lambda$", exponentParameter)),
+                   strip = strip.custom(bg="transparent", factor.levels=c("$\\lambda$", exponentParameter)),
                    ylim = list(c(-0.05, 0.1), c(-0.5, 1.5)), #y axis limits

### 2013-03-21 EconGrowthSeminar.Rnw
Now using nice macros for major and minor separator slides in the presentation. Also added a graph for the statistical parameters of the Sf models.

@@
 
+% Creates a major separator frame with specified text in ALL CAPS.
+\newcommand{\majorSeparator}[1]{
+\begin{frame} %----------------------------
+  \begin{center} \huge
+    \MakeUppercase{#1}
+  \normalsize \end{center}
+\end{frame}
+}
+
+% Creates a minor separator frame with specified text.
+\newcommand{\minorSeparator}[1]{
+\begin{frame} %----------------------------
+  \begin{center} \Large
+    #1
+  \normalsize \end{center}
+\end{frame}
+}
+
 \begin{document} %**************************************************
@@
 
-\begin{frame} %----------------------------
-  \begin{center} \huge
-    INTRODUCTION
-  \normalsize \end{center}
-\end{frame}
+\majorSeparator{Introduction} %----------------------------
 
@@
 
-\begin{frame} %----------------------------
-  \begin{center} \Large
-    Factors of Production
-  \normalsize \end{center}
-\end{frame}
+\minorSeparator{Factors of Production} %----------------------------
 
@@
 
-\begin{frame} %----------------------------
-  \begin{center} \Large
-    Economic Growth Models
-  \normalsize \end{center}
-\end{frame}
+\minorSeparator{Economic Growth Models} %----------------------------
 
@@
 
-\begin{frame} %----------------------------
-  \begin{center} \Large
-    The Question
-  \normalsize \end{center}
-  Which economic growth model best describes (statistically) the role of energy in economic growth for different types of economies?
-\end{frame}
+\minorSeparator{The Question\\ \normalsize     
+\vspace{\baselineskip} 
+Which economic growth model best describes (statistically) the role of energy in economic growth for different types of economies?} %----------------------------
 
@@
 
-\begin{frame} %----------------------------
-  \begin{center} \huge
-    DATA SOURCES
-  \normalsize \end{center}
-\end{frame}
+\majorSeparator{Data Sources}
 
@@
 
-\begin{frame} %----------------------------
-  \begin{center} \Large
-    Economic Data
-  \normalsize \end{center}
-\end{frame}
+\minorSeparator{Economic Data}
 
@@
 
-\begin{frame} %----------------------------
-  \begin{center} \Large
-    Energy Data
-  \normalsize \end{center}
-\end{frame}
+\minorSeparator{Energy Data}
 
@@
 
-\begin{frame} %----------------------------
-  \begin{center} \Large
-    Historical Data
-  \normalsize \end{center}
-\end{frame}
+\minorSeparator{Historical Data}
 
@@
 
-\begin{frame} %----------------------------
-  \begin{center} \huge
-    EVALUATION OF
-    \vspace{\baselineskip}
-    GROWTH MODELS
-  \normalsize \end{center}
-\end{frame}
+\majorSeparator{Evaluation of \vspace{\baselineskip} Growth Models}
+
+\minorSeparator{Single-factor Models}
 
@@
 
-\begin{frame}{Curve-fitting As Optimization} %----------------------------
+\begin{frame}{Curve-fitting as Optimization} %----------------------------
   \begin{itemize}
-    \item{Select values of parameters to minimize errors ($SSE$) between predicted and historical economic output $y$}
+    \item{Select values of parameters to minimize errors ($SSE$) between predicted and historical economic output ($y$)}
     \vspace{\baselineskip}
 
-    \item{Example: Single-factor Model with $q$}
+    \item{Example: Single-factor Model with $Q$}
     \begin{itemize}
@@
 
-\begin{frame}{$SSE$ Minimization}{US Single-factor with $q$} %---------------------------- 
+\begin{frame}{$SSE$ Minimization}{US Single-factor with $Q$} %---------------------------- 
 <<3D_Graph_US_SF_Q, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3, eval=TRUE>>=
@@
 
+\begin{frame}{Statistical Properties}{US Single-factor ($Q$)} %----------------------------
+<<SF_Params_Graph_Q, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3, eval=TRUE>>=
+createSFParamsGraph("Q")
+@  
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{us}{0.055}
+\end{frame}
+
+\minorSeparator{Cobb-Douglas (without Energy)}
+
 \begin{frame}{Cobb-Douglas (without Energy)} %----------------------------
@@
 \end{frame}
+
+\minorSeparator{Cobb-Douglas (with Energy)}
 
@@
 
-\begin{frame}{Grid Search Over $\gamma$}{US Cobb-Douglas with $q$} %----------------------------
+\begin{frame}{Grid Search Over $\gamma$}{US Cobb-Douglas with $Q$} %----------------------------
 <<CDeGammaGraphsUS, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
@@
 
-\begin{frame}{Grid Search Over $\gamma$}{UK Cobb-Douglas with $q$} %----------------------------
+\begin{frame}{Grid Search Over $\gamma$}{UK Cobb-Douglas with $Q$} %----------------------------
 <<CDeGammaGraphsUK, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
@@
 
-\begin{frame}{Grid Search Over $\gamma$}{JP Cobb-Douglas with $q$} %----------------------------
+\begin{frame}{Grid Search Over $\gamma$}{JP Cobb-Douglas with $Q$} %----------------------------
 <<CDeGammaGraphsJP, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
@@
 
-\begin{frame}{Grid Search Over $\gamma$}{CN Cobb-Douglas with $q$} %----------------------------
+\begin{frame}{Grid Search Over $\gamma$}{CN Cobb-Douglas with $Q$} %----------------------------
 <<CDeGammaGraphsCN, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
@@
 
-\begin{frame}{Grid Search Over $\gamma$}{ZA Cobb-Douglas with $q$} %----------------------------
+\begin{frame}{Grid Search Over $\gamma$}{ZA Cobb-Douglas with $Q$} %----------------------------
 <<CDeGammaGraphsZA, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
@@
 
-\begin{frame}{Grid Search Over $\gamma$}{SA Cobb-Douglas with $q$} %----------------------------
+\begin{frame}{Grid Search Over $\gamma$}{SA Cobb-Douglas with $Q$} %----------------------------
 <<CDeGammaGraphsSA, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
@@
 
-\begin{frame}{Grid Search Over $\gamma$}{IR Cobb-Douglas with $q$} %----------------------------
+\begin{frame}{Grid Search Over $\gamma$}{IR Cobb-Douglas with $Q$} %----------------------------
 <<CDeGammaGraphsIR, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
@@
 
-\begin{frame}{Grid Search Over $\gamma$}{TZ Cobb-Douglas with $q$} %----------------------------
+\begin{frame}{Grid Search Over $\gamma$}{TZ Cobb-Douglas with $Q$} %----------------------------
 <<CDeGammaGraphsTZ, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
@@
 
-\begin{frame}{Grid Search Over $\gamma$}{ZM Cobb-Douglas with $q$} %----------------------------
+\begin{frame}{Grid Search Over $\gamma$}{ZM Cobb-Douglas with $Q$} %----------------------------
 <<CDeGammaGraphsZM, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
@@
             \hline
-            $q$   & \Sexpr{cdqUS["CD", "lambda"]} & \Sexpr{cdxUS["CD", "alpha"]} & \Sexpr{cdqUS["CD", "beta"]} & \Sexpr{cdqUS["CD", "gamma"]}\\
+            $Q$   & \Sexpr{cdqUS["CD", "lambda"]} & \Sexpr{cdxUS["CD", "alpha"]} & \Sexpr{cdqUS["CD", "beta"]} & \Sexpr{cdqUS["CD", "gamma"]}\\
             \hline
@@
             \hline
-            $q$   & \Sexpr{cdqJP["CD", "lambda"]} & \Sexpr{cdxJP["CD", "alpha"]} & \Sexpr{cdqJP["CD", "beta"]} & \Sexpr{cdqJP["CD", "gamma"]}\\
+            $Q$   & \Sexpr{cdqJP["CD", "lambda"]} & \Sexpr{cdxJP["CD", "alpha"]} & \Sexpr{cdqJP["CD", "beta"]} & \Sexpr{cdqJP["CD", "gamma"]}\\
             \hline
@@
             \hline
-            $q$   & \Sexpr{cdqZA["CD", "lambda"]} & \Sexpr{cdxZA["CD", "alpha"]} & \Sexpr{pprint(cdqZA["CD", "beta"])} & \Sexpr{cdqZA["CD", "gamma"]}\\
+            $Q$   & \Sexpr{cdqZA["CD", "lambda"]} & \Sexpr{cdxZA["CD", "alpha"]} & \Sexpr{pprint(cdqZA["CD", "beta"])} & \Sexpr{cdqZA["CD", "gamma"]}\\
             \hline
@@
 \end{frame}
+
+\minorSeparator{Constant Elasticity of Substituion (CES)}
 
@@
 
+\minorSeparator{LINEX}
+
 \begin{frame}{LINEX} %----------------------------
@@
 
-\begin{frame} %----------------------------
-  \begin{center} \huge
-    RESULTS
-  \normalsize \end{center}
-\end{frame}
+\majorSeparator{Results}
 
@@
 
-\begin{frame} %----------------------------
-  \begin{center} \huge
-    SUMMARY
-  \normalsize \end{center}
-\end{frame}
+\majorSeparator{Summary}
 
@@
 
-\begin{frame} %----------------------------
-  \begin{center} \huge
-    APPENDIX
-  \normalsize \end{center}
-\end{frame}
+\majorSeparator{Appendix}
 

### 2013-03-21 EconGrowth-R-Functions.Rnw
Moved flags into their own directory. Now including CES parameters and fits in the presentation.

@@
                    data = dataFor3DGraph,
-                   screen = list(z = -20, x = -65),
+                   screen = list(z = -20, x = -55),
                    xlab = "$\\lambda$",
@@
                      strip = strip.custom(factor.levels=c("$\\lambda$", "$\\alpha$", "$\\beta$"), #sets labels in strip 
-                                          bg="white"), #sets background color in strip
+                                          bg="transparent"), #sets background color in strip
                      col = "black", #Sets line color to black
@@
                      strip = strip.custom(factor.levels=c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$"),  
-                                          bg="white"),
+                                          bg="transparent"),
                      col = "black", #Sets line color to black
@@
                    strip = strip.custom(factor.levels=c("$\\gamma$", "$\\lambda$", "$\\delta_1$",
-                                                        "$\\delta$", "$\\sigma_1$", "$\\sigma$"), bg="white"),
+                                                        "$\\delta$", "$\\sigma_1$", "$\\sigma$"), bg="transparent"),
                    col = "black", #Sets line color to black
@@
                    #set labels and bg color in strip
-                   strip = strip.custom(factor.levels=c("$a_0$", "$c_t$"), bg="white"),
+                   strip = strip.custom(factor.levels=c("$a_0$", "$c_t$"), bg="transparent"),
                    col = "black", #Sets line color to black

### 2013-03-21 EconGrowthSeminar.Rnw
Moved flags into their own directory. Now including CES parameters and fits in the presentation.

@@
 \newcommand{\lRow}{$l$ & $L/L_0$, labor}
-\newcommand{\eRow}{$e$ & $E/E_0$, any of $q$, $x$, or $u$}
+\newcommand{\eRow}{$e$ & $E/E_0$, one of $q$, $x$, or $u$}
 \newcommand{\lambdaRow}{$\lambda$ & technological progress}
@@
 \newcommand{\putFlagUpperRight}[2]{
-  \putat{figure_other/flag_#1.png}{#2}{2.14in}{1.59in}
+  \putat{flag/flag_#1.png}{#2}{2.14in}{1.59in}
 }
@@
 
-\subsection[Economic Data]{Sources of Economic Data} %+++++++++++++++++++++++++++++++++++++++
+\subsection[Economic]{Sources of Economic Data} %+++++++++++++++++++++++++++++++++++++++
 
@@
 
-\subsection[Energy Data]{Sources of Energy Data} %+++++++++++++++++++++++++++++++++++++++
+\subsection[Energy]{Sources of Energy Data} %+++++++++++++++++++++++++++++++++++++++
 
@@
 
-\subsection[Graphs]{Historical Data} %+++++++++++++++++++++++++++++++++++++++
+\subsection[Historical Data]{Historical Data} %+++++++++++++++++++++++++++++++++++++++
 
@@
     \end{itemize}
+    \vspace{\baselineskip}
+
+    \item{``Curve-fitting,'' ``parameter estimation,''  ``optimization,'' and ``minimization'' are used interchangeably}
   \end{itemize}
@@
 
-<<Coefs_US_SF, eval=TRUE>>=
+\begin{frame}{$SSE$ Minimization}{US single-factor with $Q$} %---------------------------- 
+<<3D_Graph_US_SF_Q, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
+sf3DSSEGraph("US", "Q")
+@
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{US}{0.055}  
+\end{frame}
+
+<<Coefs_US_SF>>=
 sfUSK <- coef(singleFactorModel("US", "K"))
@@
 @
-
-\begin{frame}{$SSE$ Minimization}{US Single-factor with $Q$} %---------------------------- 
-<<3D_Graph_US_SF_Q, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3, eval=TRUE>>=
-sf3DSSEGraph("US", "Q")
-@
-  % Including at bottom of frame so as not to push other material downward in the frame.
-  \putFlagUpperRight{us}{0.055}  
-\end{frame}
-
 \begin{frame}{Single-Factor $y$ Predictions} %----------------------------
@@
   % Including at bottom of frame so as not to push other material downward in the frame.
-  \putFlagUpperRight{us}{0.055}
+  \putFlagUpperRight{US}{0.055}
 \end{frame}
 
-\begin{frame}{Statistical Properties}{US Single-factor ($Q$)} %----------------------------
+\begin{frame}{95\% Confidence Intervals}{Single-factor with $Q$} %----------------------------
 <<SF_Params_Graph_Q, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3, eval=TRUE>>=
@@
 @  
-  % Including at bottom of frame so as not to push other material downward in the frame.
-  \putFlagUpperRight{us}{0.055}
 \end{frame}
 
-\minorSeparator{Cobb-Douglas (without Energy)}
+\minorSeparator{Cobb-Douglas (without Energy)} %----------------------------
 
@@
 
-\minorSeparator{Cobb-Douglas (with Energy)}
+\minorSeparator{Cobb-Douglas (with Energy)} %----------------------------
 
@@
   % Including at bottom of frame so as not to push other material downward in the frame.
-  \putFlagUpperRight{us}{0.055}
+  \putFlagUpperRight{US}{0.055}
 \end{frame}
@@
   % Including at bottom of frame so as not to push other material downward in the frame.
-  \putFlagUpperRight{uk}{0.045}
-\end{frame}
-
-\begin{frame}{Grid Search Over $\gamma$}{JP Cobb-Douglas with $Q$} %----------------------------
-<<CDeGammaGraphsJP, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
-  cdeGridGraph("JP", "Q", textScaling=0.8)
-@
-  % Including at bottom of frame so as not to push other material downward in the frame.
-  \putFlagUpperRight{jp}{0.045}
-\end{frame}
-
-\begin{frame}{Grid Search Over $\gamma$}{CN Cobb-Douglas with $Q$} %----------------------------
-<<CDeGammaGraphsCN, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
-  cdeGridGraph("CN", "Q", textScaling=0.8)
-@
-  % Including at bottom of frame so as not to push other material downward in the frame.
-  \putFlagUpperRight{cn}{0.045}
+  \putFlagUpperRight{UK}{0.045}
 \end{frame}
@@
   % Including at bottom of frame so as not to push other material downward in the frame.
-  \putFlagUpperRight{za}{0.055}
+  \putFlagUpperRight{ZA}{0.055}
 \end{frame}
@@
   % Including at bottom of frame so as not to push other material downward in the frame.
-  \putFlagUpperRight{sa}{0.055}
-\end{frame}
-
-\begin{frame}{Grid Search Over $\gamma$}{IR Cobb-Douglas with $Q$} %----------------------------
-<<CDeGammaGraphsIR, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
-  cdeGridGraph("IR", "Q", textScaling=0.8)
-@
-  % Including at bottom of frame so as not to push other material downward in the frame.
-  \putFlagUpperRight{ir}{0.055}
-\end{frame}
-
-\begin{frame}{Grid Search Over $\gamma$}{TZ Cobb-Douglas with $Q$} %----------------------------
-<<CDeGammaGraphsTZ, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
-  cdeGridGraph("TZ", "Q", textScaling=0.8)
-@
-  % Including at bottom of frame so as not to push other material downward in the frame.
-  \putFlagUpperRight{tz}{0.07}
-\end{frame}
-
-\begin{frame}{Grid Search Over $\gamma$}{ZM Cobb-Douglas with $Q$} %----------------------------
-<<CDeGammaGraphsZM, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
-  cdeGridGraph("ZM", "Q", textScaling=0.8)
-@
-  % Including at bottom of frame so as not to push other material downward in the frame.
-  \putFlagUpperRight{zm}{0.055}
+  \putFlagUpperRight{SA}{0.055}
 \end{frame}
@@
             \hline
-            $Q$   & \Sexpr{cdqUS["CD", "lambda"]} & \Sexpr{cdxUS["CD", "alpha"]} & \Sexpr{cdqUS["CD", "beta"]} & \Sexpr{cdqUS["CD", "gamma"]}\\
+            $q$   & \Sexpr{cdqUS["CD", "lambda"]} & \Sexpr{cdqUS["CD", "alpha"]} & \Sexpr{cdqUS["CD", "beta"]} & \Sexpr{cdqUS["CD", "gamma"]}\\
             \hline
@@
   % Including at bottom of frame so as not to push other material downward in the frame.
-  \putFlagUpperRight{us}{0.055}
-\end{frame}
-
-<<Coefs_JP_CD>>=
-cdJP <- cobbDouglasData("JP")
-cdqJP <- cobbDouglasData("JP", "Q")
-cdxJP <- cobbDouglasData("JP", "X")
-cduJP <- cobbDouglasData("JP", "U")
-@
-\begin{frame}{Cobb-Douglas $y$ Predictions} %----------------------------
-  \begin{columns}[c]
-    \column{2.2in}
-      \begin{center}
-        \cdeEqn
-        \vspace{\baselineskip}
-
-        \tiny
-          \begin{tabular}{|c|c|c|c|c|}\hline
-            $e$ & $\lambda$ & $\alpha$ & $\beta$ & $\gamma$\\
-            \hline
-                  & \Sexpr{cdJP["CD", "lambda"]} & \Sexpr{cdJP["CD", "alpha"]} & \Sexpr{cdJP["CD", "beta"]} & \Sexpr{cdJP["CD", "gamma"]}\\
-            \hline
-            $Q$   & \Sexpr{cdqJP["CD", "lambda"]} & \Sexpr{cdxJP["CD", "alpha"]} & \Sexpr{cdqJP["CD", "beta"]} & \Sexpr{cdqJP["CD", "gamma"]}\\
-            \hline
-            $x$   & \Sexpr{cdxJP["CD", "lambda"]} & \Sexpr{cdxJP["CD", "alpha"]} & \Sexpr{cdxJP["CD", "beta"]} & \Sexpr{cdxJP["CD", "gamma"]}\\
-            \hline
-            $u$   & \Sexpr{cduJP["CD", "lambda"]} & \Sexpr{cduJP["CD", "alpha"]} & \Sexpr{cduJP["CD", "beta"]} & \Sexpr{cduJP["CD", "gamma"]}\\
-            \hline
-          \end{tabular}
-        \normalsize
-      \end{center}
-    \column{2.2in}
-<<Results_Graph_JP_CD, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-createCDLatticeGraph("JP", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
-@
-  \end{columns}
-  % Including at bottom of frame so as not to push other material downward in the frame.
-  \putFlagUpperRight{jp}{0.055}
+  \putFlagUpperRight{US}{0.055}
 \end{frame}
@@
             \hline
-            $Q$   & \Sexpr{cdqZA["CD", "lambda"]} & \Sexpr{cdxZA["CD", "alpha"]} & \Sexpr{pprint(cdqZA["CD", "beta"])} & \Sexpr{cdqZA["CD", "gamma"]}\\
+            $q$   & \Sexpr{cdqZA["CD", "lambda"]} & \Sexpr{cdxZA["CD", "alpha"]} & \Sexpr{pprint(cdqZA["CD", "beta"])} & \Sexpr{cdqZA["CD", "gamma"]}\\
             \hline
@@
   % Including at bottom of frame so as not to push other material downward in the frame.
-  \putFlagUpperRight{za}{0.055}
+  \putFlagUpperRight{ZA}{0.055}
+\end{frame}
+
+\begin{frame}{95\% Confidence Intervals}{Cobb-Douglas (without energy)} %----------------------------
+<<CD_Params_Graph, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3, eval=TRUE>>=
+createCDParamsGraph()
+@  
+\end{frame}
+
+\begin{frame}{95\% Confidence Intervals}{Cobb-Douglas with $q$} %----------------------------
+<<CDq_Params_Graph, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3, eval=TRUE>>=
+createCDParamsGraph("Q")
+@  
 \end{frame}
@@
 
-\begin{frame}{Example CES Fit} %----------------------------
-  Heun complete
+<<Coefs_US_CES>>=
+cesqUS <- cesData("US", "Q")
+cesxUS <- cesData("US", "X")
+cesuUS <- cesData("US", "U")
+@
+\begin{frame}{CES $y$ Predictions} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+      \begin{center}
+        \tiny \cesEqn \normalsize
+
+        \vspace{\baselineskip}
+
+        \tiny
+          \begin{tabular}{|c|c|c|c|}\hline
+            $e$ & $\gamma$ & $\lambda$ & $\delta_1$\\
+            \hline
+            $q$ & \Sexpr{cesqUS["CES", "gamma"]} & \Sexpr{cesqUS["CES", "lambda"]} & \Sexpr{cesqUS["CES", "delta_1"]}\\
+            \hline
+            $x$ & \Sexpr{cesxUS["CES", "gamma"]} & \Sexpr{cesxUS["CES", "lambda"]} & \Sexpr{cesxUS["CES", "delta_1"]}\\
+            \hline
+            $u$ & \Sexpr{cesuUS["CES", "gamma"]} & \Sexpr{cesuUS["CES", "lambda"]} & \Sexpr{cesuUS["CES", "delta_1"]}\\
+            \hline
+          \end{tabular}
+          \vspace{\baselineskip}
+
+          \begin{tabular}{|c|c|c|c|}\hline
+            $e$ & $\sigma_1$ & $\delta$ & $\sigma$\\
+            \hline
+            $q$ & \Sexpr{cesqUS["CES", "sigma_1"]} & \Sexpr{cesqUS["CES", "delta"]} & \Sexpr{cesqUS["CES", "sigma"]}\\
+            \hline
+            $x$ & \Sexpr{cesxUS["CES", "sigma_1"]} & \Sexpr{cesxUS["CES", "delta"]} & \Sexpr{cesxUS["CES", "sigma"]}\\
+            \hline
+            $u$ & \Sexpr{cesuUS["CES", "sigma_1"]} & \Sexpr{cesuUS["CES", "delta"]} & \Sexpr{cesuUS["CES", "sigma"]}\\
+            \hline
+          \end{tabular}
+        \normalsize
+      \end{center}
+    \column{2.2in}
+<<Results_Graph_US_CES, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+createCESLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{US}{0.055}
+\end{frame}
+
+<<Coefs_ZA_CES>>=
+cesqZA <- cesData("ZA", "Q")
+cesxZA <- cesData("ZA", "X")
+@
+\begin{frame}{CES $y$ Predictions} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+      \begin{center}
+        \tiny \cesEqn \normalsize
+
+        \vspace{\baselineskip}
+
+        \tiny
+          \begin{tabular}{|c|c|c|c|}\hline
+            $e$ & $\gamma$ & $\lambda$ & $\delta_1$\\
+            \hline
+            $q$ & \Sexpr{cesqZA["CES", "gamma"]} & \Sexpr{cesqZA["CES", "lambda"]} & \Sexpr{cesqZA["CES", "delta_1"]}\\
+            \hline
+            $x$ & \Sexpr{cesxZA["CES", "gamma"]} & \Sexpr{cesxZA["CES", "lambda"]} & \Sexpr{cesxZA["CES", "delta_1"]}\\
+            \hline
+          \end{tabular}
+          \vspace{\baselineskip}
+
+          \begin{tabular}{|c|c|c|c|}\hline
+            $e$ & $\sigma_1$ & $\delta$ & $\sigma$\\
+            \hline
+            $q$ & \Sexpr{cesqZA["CES", "sigma_1"]} & \Sexpr{cesqZA["CES", "delta"]} & \Sexpr{cesqZA["CES", "sigma"]}\\
+            \hline
+            $x$ & \Sexpr{cesxZA["CES", "sigma_1"]} & \Sexpr{cesxZA["CES", "delta"]} & \Sexpr{cesxZA["CES", "sigma"]}\\
+            \hline
+          \end{tabular}
+        \normalsize
+      \end{center}
+    \column{2.2in}
+<<Results_Graph_ZA_CES, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+createCESLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{ZA}{0.055}
 \end{frame}
@@
   Heun complete
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\majorSeparator{Results}
-
-\subsection[US]{USA} %+++++++++++++++++++++++++++++++++++++++
-
-\begin{frame}{US: Single Factor and Cobb-Douglas} %----------------------------
-  \begin{columns}[c]
-    \column{2.2in}
-% <<Results_US_SF, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-% createSFLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
-% @
-    \column{2.2in}
-<<Results_US_CD, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-createCDLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
-@
-  \end{columns}
-\end{frame}
-
-\begin{frame}{US: CES and LINEX} %----------------------------
-  \begin{columns}[c]
-    \column{2.2in}
-<<Results_US_CES, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-createCESLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
-@
-    \column{2.2in}
-<<Results_US_LINEX, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-createLINEXLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
-@
-  \end{columns}
-\end{frame}
-
-\subsection[ZA]{South Africa} %+++++++++++++++++++++++++++++++++++++++
-
-\begin{frame}{ZA: Single Factor and Cobb-Douglas} %----------------------------
-  \begin{columns}[c]
-    \column{2.2in}
-<<Results_ZA_SF, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-createSFLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
-@
-    \column{2.2in}
-<<Results_ZA_CD, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-createCDLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
-@
-  \end{columns}
-\end{frame}
-
-\begin{frame}{ZA: CES and LINEX} %----------------------------
-  \begin{columns}[c]
-    \column{2.2in}
-<<Results_ZA_CES, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-createCESLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
-@
-    \column{2.2in}
-<<Results_ZA_LINEX, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-createLINEXLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
-@
-  \end{columns}
 \end{frame}
@@
 
+\begin{frame}{Grid Search Over $\gamma$}{JP Cobb-Douglas with $Q$} %----------------------------
+<<CDeGammaGraphsJP, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
+  cdeGridGraph("JP", "Q", textScaling=0.8)
+@
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{JP}{0.045}
+\end{frame}
+
+\begin{frame}{Grid Search Over $\gamma$}{CN Cobb-Douglas with $Q$} %----------------------------
+<<CDeGammaGraphsCN, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
+  cdeGridGraph("CN", "Q", textScaling=0.8)
+@
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{CN}{0.045}
+\end{frame}
+
+\begin{frame}{Grid Search Over $\gamma$}{IR Cobb-Douglas with $Q$} %----------------------------
+<<CDeGammaGraphsIR, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
+  cdeGridGraph("IR", "Q", textScaling=0.8)
+@
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{IR}{0.055}
+\end{frame}
+
+\begin{frame}{Grid Search Over $\gamma$}{TZ Cobb-Douglas with $Q$} %----------------------------
+<<CDeGammaGraphsTZ, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
+  cdeGridGraph("TZ", "Q", textScaling=0.8)
+@
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{TZ}{0.07}
+\end{frame}
+
+\begin{frame}{Grid Search Over $\gamma$}{ZM Cobb-Douglas with $Q$} %----------------------------
+<<CDeGammaGraphsZM, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
+  cdeGridGraph("ZM", "Q", textScaling=0.8)
+@
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{ZM}{0.055}
+\end{frame}
+
+<<Coefs_JP_CD>>=
+cdJP <- cobbDouglasData("JP")
+cdqJP <- cobbDouglasData("JP", "Q")
+cdxJP <- cobbDouglasData("JP", "X")
+cduJP <- cobbDouglasData("JP", "U")
+@
+\begin{frame}{Cobb-Douglas $y$ Predictions} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+      \begin{center}
+        \cdeEqn
+        \vspace{\baselineskip}
+
+        \tiny
+          \begin{tabular}{|c|c|c|c|c|}\hline
+            $e$ & $\lambda$ & $\alpha$ & $\beta$ & $\gamma$\\
+            \hline
+                  & \Sexpr{cdJP["CD", "lambda"]} & \Sexpr{cdJP["CD", "alpha"]} & \Sexpr{cdJP["CD", "beta"]} & \Sexpr{cdJP["CD", "gamma"]}\\
+            \hline
+            $Q$   & \Sexpr{cdqJP["CD", "lambda"]} & \Sexpr{cdxJP["CD", "alpha"]} & \Sexpr{cdqJP["CD", "beta"]} & \Sexpr{cdqJP["CD", "gamma"]}\\
+            \hline
+            $x$   & \Sexpr{cdxJP["CD", "lambda"]} & \Sexpr{cdxJP["CD", "alpha"]} & \Sexpr{cdxJP["CD", "beta"]} & \Sexpr{cdxJP["CD", "gamma"]}\\
+            \hline
+            $u$   & \Sexpr{cduJP["CD", "lambda"]} & \Sexpr{cduJP["CD", "alpha"]} & \Sexpr{cduJP["CD", "beta"]} & \Sexpr{cduJP["CD", "gamma"]}\\
+            \hline
+          \end{tabular}
+        \normalsize
+      \end{center}
+    \column{2.2in}
+<<Results_Graph_JP_CD, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+createCDLatticeGraph("JP", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{JP}{0.055}
+\end{frame}
+
 \end{document} %**************************************************

### 2013-03-22 EconGrowthSeminar.Rnw
Now including a multiline CES equation for 2-column slides in the presentation.

@@
 \newcommand{\cesEqn}{$y = \gamma \mathrm{e}^{\lambda(t-t_0)} \left\{\delta \left[\delta_1 k^{-\rho_1} + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1} + (1-\delta) e^{-\rho} \right\}^{-1/\rho}$}
+
+\newcommand{\cesEqnNarrow}{\begin{align*} y = \, &\gamma \: \mathrm{e}^{\lambda(t-t_0)}\\&\times \left\{\delta \left[\delta_1 k^{-\rho_1} + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1} \right.
+\\ &\left.+ \; (1-\delta) e^{-\rho} \right\}^{-1/\rho} \end{align*}}
+
 % The equation for a linex model
@@
 \begin{frame}{95\% Confidence Intervals}{Single-factor with $Q$} %----------------------------
-<<SF_Params_Graph_Q, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3, eval=TRUE>>=
+<<SF_Params_Graph_Q, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
 createSFParamsGraph("Q")
@@
 \begin{frame}{95\% Confidence Intervals}{Cobb-Douglas (without energy)} %----------------------------
-<<CD_Params_Graph, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3, eval=TRUE>>=
+<<CD_Params_Graph, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
 createCDParamsGraph()
@@
 \begin{frame}{95\% Confidence Intervals}{Cobb-Douglas with $q$} %----------------------------
-<<CDq_Params_Graph, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3, eval=TRUE>>=
+<<CDq_Params_Graph, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
 createCDParamsGraph("Q")
@@
 
-\minorSeparator{Constant Elasticity of Substituion (CES)}
+\minorSeparator{Constant Elasticity of Substitution (CES)}
 
@@
       \begin{center}
-        \tiny \cesEqn \normalsize
+        \tiny \cesEqnNarrow \normalsize
 
@@
       \begin{center}
-        \tiny \cesEqn \normalsize
-
+        \tiny \cesEqnNarrow \normalsize
         \vspace{\baselineskip}
@@
 
-\minorSeparator{LINEX}
+\begin{frame}{95\% Confidence Intervals}{CES with $q$} %----------------------------
+<<CESq_Params_Graph, fig.width=presentationGraph1ColWidth*1.8, fig.height=presentationGraph1RowHeight*1.8>>=
+createCESParamsGraph("Q")
+@  
+\end{frame}
+
+\minorSeparator{LINEX} %----------------------------
 

### 2013-03-22 EconGrowthSeminar.Rnw
Added a frame for Saudi Arabia CD coefficients and curve fit.

@@
 \begin{frame}{Energy is Essential for Economic Activity} %----------------------------
-  What do you do that doesn't require energy?
+  \begin{center}What do you do that doesn't require energy?\end{center}
 \end{frame}
@@
             \hline
-            $q$   & \Sexpr{cdqZA["CD", "lambda"]} & \Sexpr{cdxZA["CD", "alpha"]} & \Sexpr{pprint(cdqZA["CD", "beta"])} & \Sexpr{cdqZA["CD", "gamma"]}\\
+            $q$   & \Sexpr{cdqZA["CD", "lambda"]} & \Sexpr{cdqZA["CD", "alpha"]} & \Sexpr{pprint(cdqZA["CD", "beta"])} & \Sexpr{cdqZA["CD", "gamma"]}\\
             \hline
@@
     \column{2.2in}
-<<Results_Graph_US_ZA, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+<<Results_Graph_ZA_CD, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
 createCDLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
@@
   \putFlagUpperRight{ZA}{0.055}
+\end{frame}
+
+<<Coefs_SA_CD>>=
+cdSA <- cobbDouglasData("SA")
+cdqSA <- cobbDouglasData("SA", "Q")
+cdxSA <- cobbDouglasData("SA", "X")
+@
+\begin{frame}{Cobb-Douglas $y$ Predictions} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+      \begin{center}
+        \cdeEqn
+        \vspace{\baselineskip}
+
+        \tiny
+          \begin{tabular}{|c|c|c|c|c|}\hline
+            $e$ & $\lambda$ & $\alpha$ & $\beta$ & $\gamma$\\
+            \hline
+                  & \Sexpr{cdSA["CD", "lambda"]} & \Sexpr{cdSA["CD", "alpha"]} & \Sexpr{cdSA["CD", "beta"]} & \Sexpr{cdSA["CD", "gamma"]}\\
+            \hline
+            $q$   & \Sexpr{cdqSA["CD", "lambda"]} & \Sexpr{cdqSA["CD", "alpha"]} & \Sexpr{cdqSA["CD", "beta"]} & \Sexpr{cdqSA["CD", "gamma"]}\\
+            \hline
+            $x$   & \Sexpr{cdxSA["CD", "lambda"]} & \Sexpr{cdxSA["CD", "alpha"]} & \Sexpr{cdxSA["CD", "beta"]} & \Sexpr{cdxSA["CD", "gamma"]}\\
+            \hline
+          \end{tabular}
+        \normalsize
+      \end{center}
+    \column{2.2in}
+<<Results_Graph_SA_CD, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+createCDLatticeGraph("SA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{SA}{0.055}
 \end{frame}

### 2013-03-22 EconGrowth-R-Functions.Rnw
Last commit before a big reorg of the presentation.

@@
                    lwd = 1, #Sets line width to 1.0
-                   ylim = list(c(0.9, 1.1), c(-0.05, 0.05), c(0.0, 1.0),
+                   ylim = list(c(0.5, 1.5), c(-0.05, 0.05), c(0.0, 1.0),
                                c(0.0, 1.0), c(0.0, 1.0), c(0.0, 1.0)), #y axis limits
@@
                                  y=list(relation="free", #allow each axis to be different
-                                        at=list(c(0.9, 1.0, 1.1), c(-0.05, 0.0, 0.05),
+                                        at=list(c(0.5, 1.0, 1.5), c(-0.05, 0.0, 0.05),
                                                 c(0.0, 0.5, 1.0), c(0.0, 0.5, 1.0), 

### 2013-03-22 EconGrowthSeminar.Rnw
Added extra space in CES equation.
Last commit before a big reorg of the presentation.

@@
 % The equation for a ces model
-\newcommand{\cesEqn}{$y = \gamma \mathrm{e}^{\lambda(t-t_0)} \left\{\delta \left[\delta_1 k^{-\rho_1} + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1} + (1-\delta) e^{-\rho} \right\}^{-1/\rho}$}
+\newcommand{\cesEqn}{$y = \gamma \: \mathrm{e}^{\lambda(t-t_0)} \left\{\delta \left[\delta_1 k^{-\rho_1} + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1} + (1-\delta) e^{-\rho} \right\}^{-1/\rho}$}
 
@@
 
-\begin{frame}{Energy and GDP are Linked} %----------------------------
-  \tiny
-  \framesubtitle{\citep{Cleveland:1997p5055}}
-  \normalsize
+\begin{frame}{Energy and GDP are Linked}{\citep{Cleveland:1997p5055}} %----------------------------
   \begin{columns}[c]
@@
 
+\begin{frame}{Oil and Recessions}{\citep{Hamilton:2011fo}} %----------------------------
+  \begin{center}
+    10 of last 11 US recessions preceeded by oil price shocks
+  \end{center}
+\end{frame}
+
 \begin{frame}{Energy Cost Share}{\citep{Bashmakov:2007ek}} %----------------------------
@@
 
-\minorSeparator{The Question\\ \normalsize     
-\vspace{\baselineskip} 
-Which economic growth model best describes (statistically) the role of energy in economic growth for different types of economies?} %----------------------------
+\minorSeparator{The Question\\ \normalsize      %----------------------------
+\vspace{\baselineskip} 
+Which economic growth model best describes (statistically) the role of energy in economic growth for different types of economies?}
 
@@
 \majorSeparator{Evaluation of \vspace{\baselineskip} Growth Models}
+
+\begin{frame}{Coordinates of Analysis} %----------------------------
+  \begin{itemize}
+    \item{Country/Economy: 9 \\US, UK, JP, CN, ZA, SA, IR, TZ, ZM}
+    \item{Economic Growth Model: 4 \\SF, CD, CES, LINEX}
+    \item{Type of Energy: 3 \\Q, X, U}
+  \end{itemize}
+  Simplification: 1 country (US), 1 type of energy (Q)
+\end{frame}
 
@@
   \putFlagUpperRight{US}{0.055}
+\end{frame}
+
+\begin{frame}{95\% Confidence Intervals}{Single-factor with $K$} %----------------------------
+<<SF_Params_Graph_K, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
+createSFParamsGraph("K")
+@  
+\end{frame}
+
+\begin{frame}{95\% Confidence Intervals}{Single-factor with $L$} %----------------------------
+<<SF_Params_Graph_L, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
+createSFParamsGraph("L")
+@  
 \end{frame}
@@
 \begin{frame}{95\% Confidence Intervals}{CES with $q$} %----------------------------
-<<CESq_Params_Graph, fig.width=presentationGraph1ColWidth*1.8, fig.height=presentationGraph1RowHeight*1.8>>=
+<<CESq_Params_Graph, fig.width=presentationGraph1ColWidth*1.8, fig.height=presentationGraph1RowHeight*1.8, eval=TRUE>>=
 createCESParamsGraph("Q")

### 2013-03-22 EconGrowthSeminar.Rnw
Massive rearrangement of the seminar, including CI vs. parameter graphs.

@@
   \end{itemize}
-  Simplification: 1 country (US), 1 type of energy (Q)
-\end{frame}
-
-\minorSeparator{Single-factor Models}
-
-\begin{frame}{Single Factor} %----------------------------
+  Simplification: 1 type of energy (Q)
+\end{frame}
+
+\minorSeparator{Curve-fitting as Optimization}
+
+\begin{frame}{Example: Single-factor Model} %----------------------------
   \begin{center}
@@
   \putFlagUpperRight{US}{0.055}  
-\end{frame}
-
-<<Coefs_US_SF>>=
-sfUSK <- coef(singleFactorModel("US", "K"))
-sfUSL <- coef(singleFactorModel("US", "L"))
-sfUSQ <- coef(singleFactorModel("US", "Q"))
-sfUSX <- coef(singleFactorModel("US", "X"))
-sfUSU <- coef(singleFactorModel("US", "U"))
-@
-\begin{frame}{Single-Factor $y$ Predictions} %----------------------------
-  \begin{columns}[c]
-    \column{2.2in}
-      \begin{center}
-        \sfEqn
-        \vspace{\baselineskip}
-
-        \tiny
-          \begin{tabular}{|c|c|c|}\hline
-            $f$   & $\lambda$                & $m$\\
-            \hline
-            $k$   & \Sexpr{sfUSK["lambda"]}  & \Sexpr{sfUSK["m"]}\\
-            \hline
-            $l$   & \Sexpr{sfUSL["lambda"]}  & \Sexpr{sfUSL["m"]}\\
-            \hline
-            $q$   & \Sexpr{sfUSQ["lambda"]}  & \Sexpr{sfUSQ["m"]}\\
-            \hline
-            $x$   & \Sexpr{sfUSX["lambda"]}  & \Sexpr{sfUSX["m"]}\\
-            \hline
-            $u$   & \Sexpr{sfUSU["lambda"]}  & \Sexpr{sfUSU["m"]}\\
-            \hline
-          \end{tabular}
-        \normalsize
-      \end{center}
-    \column{2.2in}
-<<Results_Graph_US_SF, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-createSFLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
-@
-  \end{columns}
-  % Including at bottom of frame so as not to push other material downward in the frame.
-  \putFlagUpperRight{US}{0.055}
-\end{frame}
-
-\begin{frame}{95\% Confidence Intervals}{Single-factor with $K$} %----------------------------
-<<SF_Params_Graph_K, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
-createSFParamsGraph("K")
-@  
-\end{frame}
-
-\begin{frame}{95\% Confidence Intervals}{Single-factor with $L$} %----------------------------
-<<SF_Params_Graph_L, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
-createSFParamsGraph("L")
-@  
-\end{frame}
-
-\begin{frame}{95\% Confidence Intervals}{Single-factor with $Q$} %----------------------------
-<<SF_Params_Graph_Q, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
-createSFParamsGraph("Q")
-@  
-\end{frame}
-
-\minorSeparator{Cobb-Douglas (without Energy)} %----------------------------
-
-\begin{frame}{Cobb-Douglas (without Energy)} %----------------------------
-  \begin{center}
-    \cdEqn\\
-    $\alpha + \beta = 1$\\
-    $0 \leq \alpha, \beta \leq 1$
-    \vspace{\baselineskip}
-
-    \begin{tabular}{|c|l|}\hline
-      \yRow\\
-      \timeRow\\
-      \initialTimeRow\\
-      \kRow\\
-      \lRow\\
-      \hline
-      \lambdaRow\\
-      \alphaRow\\
-      \betaRow\\
-      \hline
-    \end{tabular}
-  \end{center}
 \end{frame}
@@
 \begin{frame}{Parameter Estimation for Cobb-Douglas With Energy} %----------------------------
-  \begin{center}
-    \cdeEqn
-  \end{center}
+  \begin{center}\cdeEqn\end{center}
   \begin{itemize}
@@
 
-\begin{frame}{Grid Search Over $\gamma$}{UK Cobb-Douglas with $Q$} %----------------------------
-<<CDeGammaGraphsUK, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
-  cdeGridGraph("UK", "Q", textScaling=0.8)
-@
-  % Including at bottom of frame so as not to push other material downward in the frame.
-  \putFlagUpperRight{UK}{0.045}
-\end{frame}
-
-\begin{frame}{Grid Search Over $\gamma$}{ZA Cobb-Douglas with $Q$} %----------------------------
-<<CDeGammaGraphsZA, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
-  cdeGridGraph("ZA", "Q", textScaling=0.8)
-@
-  % Including at bottom of frame so as not to push other material downward in the frame.
-  \putFlagUpperRight{ZA}{0.055}
-\end{frame}
-
 \begin{frame}{Grid Search Over $\gamma$}{SA Cobb-Douglas with $Q$} %----------------------------
@@
 \end{frame}
+
+\begin{frame}{95\% Confidence Intervals}{Cobb-Douglas with $q$} %----------------------------
+<<CDq_Params_Graph, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
+createCDParamsGraph("Q")
+@  
+\end{frame}
+
+\begin{frame}{$CI_{\gamma}$ and $\gamma$ in Cobb-Douglas} %----------------------------
+  \begin{center}
+    \cdeEqn\\
+    \includegraphics<1>[height=2.5in]{figure_other/CI-gamma-1.pdf}
+    \includegraphics<2>[height=2.5in]{figure_other/CI-gamma-2.pdf}
+    \includegraphics<3>[height=2.5in]{figure_other/CI-gamma-3.pdf}
+    \includegraphics<4>[height=2.5in]{figure_other/CI-gamma-4.pdf}
+  \end{center}
+\end{frame}
+
+\begin{frame}{CI and $\gamma$ in Cobb-Douglas} %----------------------------
+  Graph here of CI vs. $\gamma$ where each country abbreviation is plotted.
+\end{frame}
+
+\begin{frame}{Implications from Cobb-Douglas} %----------------------------
+  \begin{center}\cdeEqn\end{center}
+  \vspace{\baselineskip}
+
+  \begin{itemize}
+    \item{Energy parameter ($\gamma$) is either}
+      \begin{itemize}
+        \item{Small (US, JP, CN, SA, IR)}
+        \item{Large CI (ZA, TZ, ZM)}
+        \item{Exception: UK}
+      \end{itemize}
+    \vspace{\baselineskip}
+
+    \pause
+    \item{Direct energy input to economy ($q$)is unimportant as a Cobb-Douglas predictor of economic output ($y$)}
+  \end{itemize}
+\end{frame}
+
+\minorSeparator{Constant Elasticity of Substitution (CES)}
+
+\begin{frame}{Constant Elasticity of Substitution (CES)} %----------------------------
+  \begin{center}
+    \small
+      \cesEqn
+    \normalsize
+    \vspace{\baselineskip}
+
+    \begin{tabular}{|c|l|}\hline
+      \yRow\\
+      \timeRow\\
+      \initialTimeRow\\
+      \kRow\\
+      \lRow\\
+      \eRow\\
+      \hline
+      $\gamma$   &   fitting coefficient\\
+      \lambdaRow\\
+      $\delta_1$   &   split between ($k$) and ($l$)\\
+      $\rho_1$     &   ``strength'' of ($k$) vs. ($l$)\\
+      $\delta$   &   split between ($kl$) and ($e$)\\
+      $\rho$     &   ``strength'' of ($kl$) vs. ($e$)\\
+      \hline
+    \end{tabular}
+  \end{center}
+\end{frame}
+
+<<Coefs_US_CES>>=
+cesqUS <- cesData("US", "Q")
+cesxUS <- cesData("US", "X")
+cesuUS <- cesData("US", "U")
+@
+\begin{frame}{CES $y$ Predictions} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+      \begin{center}
+        \tiny \cesEqnNarrow \normalsize
+
+        \vspace{\baselineskip}
+
+        \tiny
+          \begin{tabular}{|c|c|c|c|}\hline
+            $e$ & $\gamma$ & $\lambda$ & $\delta_1$\\
+            \hline
+            $q$ & \Sexpr{cesqUS["CES", "gamma"]} & \Sexpr{cesqUS["CES", "lambda"]} & \Sexpr{cesqUS["CES", "delta_1"]}\\
+            \hline
+            $x$ & \Sexpr{cesxUS["CES", "gamma"]} & \Sexpr{cesxUS["CES", "lambda"]} & \Sexpr{cesxUS["CES", "delta_1"]}\\
+            \hline
+            $u$ & \Sexpr{cesuUS["CES", "gamma"]} & \Sexpr{cesuUS["CES", "lambda"]} & \Sexpr{cesuUS["CES", "delta_1"]}\\
+            \hline
+          \end{tabular}
+          \vspace{\baselineskip}
+
+          \begin{tabular}{|c|c|c|c|}\hline
+            $e$ & $\sigma_1$ & $\delta$ & $\sigma$\\
+            \hline
+            $q$ & \Sexpr{cesqUS["CES", "sigma_1"]} & \Sexpr{cesqUS["CES", "delta"]} & \Sexpr{cesqUS["CES", "sigma"]}\\
+            \hline
+            $x$ & \Sexpr{cesxUS["CES", "sigma_1"]} & \Sexpr{cesxUS["CES", "delta"]} & \Sexpr{cesxUS["CES", "sigma"]}\\
+            \hline
+            $u$ & \Sexpr{cesuUS["CES", "sigma_1"]} & \Sexpr{cesuUS["CES", "delta"]} & \Sexpr{cesuUS["CES", "sigma"]}\\
+            \hline
+          \end{tabular}
+        \normalsize
+      \end{center}
+    \column{2.2in}
+<<Results_Graph_US_CES, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+createCESLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{US}{0.055}
+\end{frame}
+
+<<Coefs_ZA_CES>>=
+cesqZA <- cesData("ZA", "Q")
+cesxZA <- cesData("ZA", "X")
+@
+\begin{frame}{CES $y$ Predictions} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+      \begin{center}
+        \tiny \cesEqnNarrow \normalsize
+        \vspace{\baselineskip}
+
+        \tiny
+          \begin{tabular}{|c|c|c|c|}\hline
+            $e$ & $\gamma$ & $\lambda$ & $\delta_1$\\
+            \hline
+            $q$ & \Sexpr{cesqZA["CES", "gamma"]} & \Sexpr{cesqZA["CES", "lambda"]} & \Sexpr{cesqZA["CES", "delta_1"]}\\
+            \hline
+            $x$ & \Sexpr{cesxZA["CES", "gamma"]} & \Sexpr{cesxZA["CES", "lambda"]} & \Sexpr{cesxZA["CES", "delta_1"]}\\
+            \hline
+          \end{tabular}
+          \vspace{\baselineskip}
+
+          \begin{tabular}{|c|c|c|c|}\hline
+            $e$ & $\sigma_1$ & $\delta$ & $\sigma$\\
+            \hline
+            $q$ & \Sexpr{cesqZA["CES", "sigma_1"]} & \Sexpr{cesqZA["CES", "delta"]} & \Sexpr{cesqZA["CES", "sigma"]}\\
+            \hline
+            $x$ & \Sexpr{cesxZA["CES", "sigma_1"]} & \Sexpr{cesxZA["CES", "delta"]} & \Sexpr{cesxZA["CES", "sigma"]}\\
+            \hline
+          \end{tabular}
+        \normalsize
+      \end{center}
+    \column{2.2in}
+<<Results_Graph_ZA_CES, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+createCESLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{ZA}{0.055}
+\end{frame}
+
+\begin{frame}{95\% Confidence Intervals}{CES with $q$} %----------------------------
+<<CESq_Params_Graph, fig.width=presentationGraph1ColWidth*1.8, fig.height=presentationGraph1RowHeight*1.8, eval=TRUE>>=
+createCESParamsGraph("Q")
+@  
+\end{frame}
+
+\begin{frame}{$CI_{\delta}$ and $\delta$ in CES} %----------------------------
+  \begin{center}
+    \cdeEqn\\
+    \includegraphics<1>[height=2.5in]{figure_other/CI-delta-1.pdf}
+    \includegraphics<2>[height=2.5in]{figure_other/CI-delta-2.pdf}
+    \includegraphics<3>[height=2.5in]{figure_other/CI-delta-3.pdf}
+    \includegraphics<4>[height=2.5in]{figure_other/CI-delta-4.pdf}
+  \end{center}
+\end{frame}
+
+\begin{frame}{$CI_{\delta}$ and $\delta$ in CES} %----------------------------
+  Graph here of $CI_{\delta}$ vs. $\delta$ where each country abbreviation is plotted.
+\end{frame}
+
+\begin{frame}{$CI_{\sigma}$ and $\sigma$ in CES} %----------------------------
+  \begin{center}
+    \cdeEqn\\
+    \includegraphics<1>[height=2.5in]{figure_other/CI-sigma-1.pdf}
+    \includegraphics<2>[height=2.5in]{figure_other/CI-sigma-2.pdf}
+    \includegraphics<3>[height=2.5in]{figure_other/CI-sigma-3.pdf}
+    \includegraphics<4>[height=2.5in]{figure_other/CI-sigma-4.pdf}
+  \end{center}
+\end{frame}
+
+\begin{frame}{$CI_{\sigma}$ and $\sigma$ in CES} %----------------------------
+  Graph here of $CI_{\sigma}$ vs. $\sigma$ where each country abbreviation is plotted.
+\end{frame}
+
+\begin{frame}{Implications from CES} %----------------------------
+  \begin{center}\cesEqn\end{center}
+  \vspace{\baselineskip}
+
+  \begin{itemize}
+    \item{kl and e are complements, sigma small where it is distinguishable.}
+    \item{Direct energy input to economy ($q$)is unimportant as a CES predictor of economic output ($y$), because delta is close to 1.0}
+  \end{itemize}
+\end{frame}
+
+\minorSeparator{LINEX} %----------------------------
+
+\begin{frame}{LINEX} %----------------------------
+  \begin{center}
+    \linexEqn
+    \vspace{\baselineskip}
+
+    \begin{tabular}{|c|l|}\hline
+      \kRow\\
+      \lRow\\
+      \eRow\\
+      \hline
+      $a_0$ & fitting parameter\\
+      $c_t$ & fitting parameter\\
+      \hline
+    \end{tabular}
+  \end{center}
+\end{frame}
+
+\begin{frame}{Example LINEX Fit} %----------------------------
+  Heun complete
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Summary}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\majorSeparator{Summary}
+
+\begin{frame}{Tentative Conclusions} %----------------------------
+  \begin{itemize}
+  \item{Including energy is unwarranted \\
+        \scriptsize
+        Little statistical evidence that including energy in production functions improves stastical properties of fitting parameters.
+        \normalsize}
+  \item{Including energy is unnecessary \\
+        \scriptsize
+        Energy is \emph{always already} embedded in capital stock ($K$) and labor ($L$).
+        \normalsize}
+  \vspace{\baselineskip}
+  \item{Need a modeling method that captures energy's embeddedness \\
+        \scriptsize
+        System dynamics modeling
+        \normalsize}
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Next Steps (Summer 2013)} %----------------------------
+  \begin{itemize}
+    \item{Estimate statistical properties for \emph{all} fitting parameters}
+    \vspace{\baselineskip}
+    \vspace{\baselineskip}
+    \item{Complete paper}
+  \end{itemize}  
+\end{frame}
+
+\begin{frame}{Acknowledgements} %----------------------------
+  \begin{itemize}
+    \item{Martin de Wit, Stellenbosch University}
+    \item{Randall Pruim, Calvin College}
+    \item{Loren L. Heun, Western Michigan University}
+    \vspace{\baselineskip}
+    \item{Jack and Lois Kuipers Applied Mathematics Endowment\\(Reese and Timmer Summer 2012 funding)}
+    \item{Calvin College Alumni Association\\(Reese Fall 2012 funding)}
+  \end{itemize}  
+\end{frame}
+
+\begin{frame}{References} %----------------------------
+  \bibliographystyle{plainnat}
+  \tiny
+    \bibliography{EconGrowth.bib}
+  \normalsize
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Appendix}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\majorSeparator{Appendix}
+
+\minorSeparator{Single-factor Model}
+
+<<Coefs_US_SF>>=
+sfUSK <- coef(singleFactorModel("US", "K"))
+sfUSL <- coef(singleFactorModel("US", "L"))
+sfUSQ <- coef(singleFactorModel("US", "Q"))
+sfUSX <- coef(singleFactorModel("US", "X"))
+sfUSU <- coef(singleFactorModel("US", "U"))
+@
+\begin{frame}{Single-Factor $y$ Predictions} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+      \begin{center}
+        \sfEqn
+        \vspace{\baselineskip}
+
+        \tiny
+          \begin{tabular}{|c|c|c|}\hline
+            $f$   & $\lambda$                & $m$\\
+            \hline
+            $k$   & \Sexpr{sfUSK["lambda"]}  & \Sexpr{sfUSK["m"]}\\
+            \hline
+            $l$   & \Sexpr{sfUSL["lambda"]}  & \Sexpr{sfUSL["m"]}\\
+            \hline
+            $q$   & \Sexpr{sfUSQ["lambda"]}  & \Sexpr{sfUSQ["m"]}\\
+            \hline
+            $x$   & \Sexpr{sfUSX["lambda"]}  & \Sexpr{sfUSX["m"]}\\
+            \hline
+            $u$   & \Sexpr{sfUSU["lambda"]}  & \Sexpr{sfUSU["m"]}\\
+            \hline
+          \end{tabular}
+        \normalsize
+      \end{center}
+    \column{2.2in}
+<<Results_Graph_US_SF, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+createSFLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{US}{0.055}
+\end{frame}
+
+\begin{frame}{Cobb-Douglas (without Energy)} %----------------------------
+  \begin{center}
+    \cdEqn\\
+    $\alpha + \beta = 1$\\
+    $0 \leq \alpha, \beta \leq 1$
+    \vspace{\baselineskip}
+
+    \begin{tabular}{|c|l|}\hline
+      \yRow\\
+      \timeRow\\
+      \initialTimeRow\\
+      \kRow\\
+      \lRow\\
+      \hline
+      \lambdaRow\\
+      \alphaRow\\
+      \betaRow\\
+      \hline
+    \end{tabular}
+  \end{center}
+\end{frame}
+
+\begin{frame}{95\% Confidence Intervals}{Single-factor with $K$} %----------------------------
+<<SF_Params_Graph_K, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
+createSFParamsGraph("K")
+@  
+\end{frame}
+
+\begin{frame}{95\% Confidence Intervals}{Single-factor with $L$} %----------------------------
+<<SF_Params_Graph_L, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
+createSFParamsGraph("L")
+@  
+\end{frame}
+
+\begin{frame}{95\% Confidence Intervals}{Single-factor with $Q$} %----------------------------
+<<SF_Params_Graph_Q, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
+createSFParamsGraph("Q")
+@  
+\end{frame}
+
+\minorSeparator{Cobb-Douglas Model}
 
@@
 
-\begin{frame}{95\% Confidence Intervals}{Cobb-Douglas (without energy)} %----------------------------
-<<CD_Params_Graph, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
-createCDParamsGraph()
-@  
-\end{frame}
-
-\begin{frame}{95\% Confidence Intervals}{Cobb-Douglas with $q$} %----------------------------
-<<CDq_Params_Graph, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
-createCDParamsGraph("Q")
-@  
-\end{frame}
-
-\minorSeparator{Constant Elasticity of Substitution (CES)}
-
-\begin{frame}{Constant Elasticity of Substitution (CES)} %----------------------------
-  \begin{center}
-    \small
-      \cesEqn
-    \normalsize
-    \vspace{\baselineskip}
-
-    \begin{tabular}{|c|l|}\hline
-      \yRow\\
-      \timeRow\\
-      \initialTimeRow\\
-      \kRow\\
-      \lRow\\
-      \eRow\\
-      \hline
-      $\gamma$   &   fitting coefficient\\
-      \lambdaRow\\
-      $\delta_1$   &   split between ($k$) and ($l$)\\
-      $\rho_1$     &   ``strength'' of ($k$) vs. ($l$)\\
-      $\delta$   &   split between ($kl$) and ($e$)\\
-      $\rho$     &   ``strength'' of ($kl$) vs. ($e$)\\
-      \hline
-    \end{tabular}
-  \end{center}
-\end{frame}
-
-<<Coefs_US_CES>>=
-cesqUS <- cesData("US", "Q")
-cesxUS <- cesData("US", "X")
-cesuUS <- cesData("US", "U")
-@
-\begin{frame}{CES $y$ Predictions} %----------------------------
-  \begin{columns}[c]
-    \column{2.2in}
-      \begin{center}
-        \tiny \cesEqnNarrow \normalsize
-
-        \vspace{\baselineskip}
-
-        \tiny
-          \begin{tabular}{|c|c|c|c|}\hline
-            $e$ & $\gamma$ & $\lambda$ & $\delta_1$\\
-            \hline
-            $q$ & \Sexpr{cesqUS["CES", "gamma"]} & \Sexpr{cesqUS["CES", "lambda"]} & \Sexpr{cesqUS["CES", "delta_1"]}\\
-            \hline
-            $x$ & \Sexpr{cesxUS["CES", "gamma"]} & \Sexpr{cesxUS["CES", "lambda"]} & \Sexpr{cesxUS["CES", "delta_1"]}\\
-            \hline
-            $u$ & \Sexpr{cesuUS["CES", "gamma"]} & \Sexpr{cesuUS["CES", "lambda"]} & \Sexpr{cesuUS["CES", "delta_1"]}\\
-            \hline
-          \end{tabular}
-          \vspace{\baselineskip}
-
-          \begin{tabular}{|c|c|c|c|}\hline
-            $e$ & $\sigma_1$ & $\delta$ & $\sigma$\\
-            \hline
-            $q$ & \Sexpr{cesqUS["CES", "sigma_1"]} & \Sexpr{cesqUS["CES", "delta"]} & \Sexpr{cesqUS["CES", "sigma"]}\\
-            \hline
-            $x$ & \Sexpr{cesxUS["CES", "sigma_1"]} & \Sexpr{cesxUS["CES", "delta"]} & \Sexpr{cesxUS["CES", "sigma"]}\\
-            \hline
-            $u$ & \Sexpr{cesuUS["CES", "sigma_1"]} & \Sexpr{cesuUS["CES", "delta"]} & \Sexpr{cesuUS["CES", "sigma"]}\\
-            \hline
-          \end{tabular}
-        \normalsize
-      \end{center}
-    \column{2.2in}
-<<Results_Graph_US_CES, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-createCESLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
-@
-  \end{columns}
-  % Including at bottom of frame so as not to push other material downward in the frame.
-  \putFlagUpperRight{US}{0.055}
-\end{frame}
-
-<<Coefs_ZA_CES>>=
-cesqZA <- cesData("ZA", "Q")
-cesxZA <- cesData("ZA", "X")
-@
-\begin{frame}{CES $y$ Predictions} %----------------------------
-  \begin{columns}[c]
-    \column{2.2in}
-      \begin{center}
-        \tiny \cesEqnNarrow \normalsize
-        \vspace{\baselineskip}
-
-        \tiny
-          \begin{tabular}{|c|c|c|c|}\hline
-            $e$ & $\gamma$ & $\lambda$ & $\delta_1$\\
-            \hline
-            $q$ & \Sexpr{cesqZA["CES", "gamma"]} & \Sexpr{cesqZA["CES", "lambda"]} & \Sexpr{cesqZA["CES", "delta_1"]}\\
-            \hline
-            $x$ & \Sexpr{cesxZA["CES", "gamma"]} & \Sexpr{cesxZA["CES", "lambda"]} & \Sexpr{cesxZA["CES", "delta_1"]}\\
-            \hline
-          \end{tabular}
-          \vspace{\baselineskip}
-
-          \begin{tabular}{|c|c|c|c|}\hline
-            $e$ & $\sigma_1$ & $\delta$ & $\sigma$\\
-            \hline
-            $q$ & \Sexpr{cesqZA["CES", "sigma_1"]} & \Sexpr{cesqZA["CES", "delta"]} & \Sexpr{cesqZA["CES", "sigma"]}\\
-            \hline
-            $x$ & \Sexpr{cesxZA["CES", "sigma_1"]} & \Sexpr{cesxZA["CES", "delta"]} & \Sexpr{cesxZA["CES", "sigma"]}\\
-            \hline
-          \end{tabular}
-        \normalsize
-      \end{center}
-    \column{2.2in}
-<<Results_Graph_ZA_CES, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-createCESLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
-@
-  \end{columns}
-  % Including at bottom of frame so as not to push other material downward in the frame.
-  \putFlagUpperRight{ZA}{0.055}
-\end{frame}
-
-\begin{frame}{95\% Confidence Intervals}{CES with $q$} %----------------------------
-<<CESq_Params_Graph, fig.width=presentationGraph1ColWidth*1.8, fig.height=presentationGraph1RowHeight*1.8, eval=TRUE>>=
-createCESParamsGraph("Q")
-@  
-\end{frame}
-
-\minorSeparator{LINEX} %----------------------------
-
-\begin{frame}{LINEX} %----------------------------
-  \begin{center}
-    \linexEqn
-    \vspace{\baselineskip}
-
-    \begin{tabular}{|c|l|}\hline
-      \kRow\\
-      \lRow\\
-      \eRow\\
-      \hline
-      $a_0$ & fitting parameter\\
-      $c_t$ & fitting parameter\\
-      \hline
-    \end{tabular}
-  \end{center}
-\end{frame}
-
-\begin{frame}{Example LINEX Fit} %----------------------------
-  Heun complete
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Summary}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\majorSeparator{Summary}
-
-\begin{frame}{Tentative Conclusions} %----------------------------
-  \begin{itemize}
-  \item{Including energy is unwarranted \\
-        \scriptsize
-        Little statistical evidence that including energy in production functions improves stastical properties of fitting parameters.
-        \normalsize}
-  \item{Including energy is unnecessary \\
-        \scriptsize
-        Energy is \emph{always already} embedded in capital stock ($K$) and labor ($L$).
-        \normalsize}
-  \vspace{\baselineskip}
-  \item{Need a modeling method that captures energy's embeddedness \\
-        \scriptsize
-        System dynamics modeling
-        \normalsize}
-  \end{itemize}
-\end{frame}
-
-\begin{frame}{Next Steps (Summer 2013)} %----------------------------
-  \begin{itemize}
-    \item{Estimate statistical properties for \emph{all} fitting parameters}
-    \vspace{\baselineskip}
-    \vspace{\baselineskip}
-    \item{Complete paper}
-  \end{itemize}  
-\end{frame}
-
-\begin{frame}{Acknowledgements} %----------------------------
-  \begin{itemize}
-    \item{Martin de Wit, Stellenbosch University}
-    \item{Randall Pruim, Calvin College}
-    \item{Loren L. Heun, Western Michigan University}
-    \vspace{\baselineskip}
-    \item{Jack and Lois Kuipers Applied Mathematics Endowment\\(Reese and Timmer Summer 2012 funding)}
-    \item{Calvin College Alumni Association\\(Reese Fall 2012 funding)}
-  \end{itemize}  
-\end{frame}
-
-\begin{frame}{References} %----------------------------
-  \bibliographystyle{plainnat}
-  \tiny
-    \bibliography{EconGrowth.bib}
-  \normalsize
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Appendix}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\majorSeparator{Appendix}
-
 \begin{frame}{Grid Search Over $\gamma$}{JP Cobb-Douglas with $Q$} %----------------------------
@@
   \putFlagUpperRight{CN}{0.045}
+\end{frame}
+
+\begin{frame}{Grid Search Over $\gamma$}{UK Cobb-Douglas with $Q$} %----------------------------
+<<CDeGammaGraphsUK, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
+  cdeGridGraph("UK", "Q", textScaling=0.8)
+@
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{UK}{0.045}
+\end{frame}
+
+\begin{frame}{Grid Search Over $\gamma$}{ZA Cobb-Douglas with $Q$} %----------------------------
+<<CDeGammaGraphsZA, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
+  cdeGridGraph("ZA", "Q", textScaling=0.8)
+@
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{ZA}{0.055}
 \end{frame}
@@
 
+\begin{frame}{95\% Confidence Intervals}{Cobb-Douglas (without energy)} %---------------------------- 
+<<CD_Params_Graph, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
+createCDParamsGraph()
+@  
+\end{frame}
+
 \end{document} %**************************************************

### 2013-03-23 EconGrowth-R-Functions.Rnw
Beginning the process of making graphs of CI vs. parameters. Have now implemented graphs for SF model.

@@
 
+########################
+# Aggregates the single-factor results intoa a big data frame for the given factor
+##
+singleFactorParamsDF <- function(factor){
+  #Do rbind on the results of creating a row in the table for every country abbreviation that we know.
+  dataSF <- do.call("rbind", lapply(countryAbbrevs, singleFactorCountryRow, factor=factor))
+  #Add names to the rows and columns
+  colnames(dataSF) <- list("lowerCI_lambda", "lambda", "upperCI_lambda", "lowerCI_m", "m", "upperCI_m")
+  rownames(dataSF) <- countryAbbrevs
+  return(dataSF)
+}
+
 ############################
@@
 singleFactorParamsTable <- function(factor){
-  #Do rbind on the results of creating a row in the table for every country abbreviation that we know.
-  dataSF <- do.call("rbind", lapply(countryAbbrevs, singleFactorCountryRow, factor=factor))
+  dataSF <- singleFactorParamsDF(factor)
   if (factor == "K"){

### 2013-03-23 EconGrowth.Rnw
Beginning the process of making graphs of CI vs. parameters. Have now implemented graphs for SF model.

@@
 \subsection{Background}
+
+<<CIvsParam_Graph, eval=TRUE>>=
+# plot(1:9, rep(1, 9), pch=LETTERS)
+# xyplot(rep(1:9) ~ 1:9, pch=LETTERS)
+# xyplot(rep(1:9) ~ 1:9, pch="US")
+# states <- data.frame(state.x77, 
+#                           state.name = dimnames(state.x77)[[1]], 
+#                           state.region = state.region) 
+#      xyplot(Murder ~ Population | state.region, data = states, 
+#             groups = state.name, 
+#             panel = function(x, y, subscripts, groups) { 
+#                 ltext(x = x, y = y, labels = groups[subscripts], cex=1, 
+#                       fontfamily = "HersheySans") 
+#             }) 
+# print(states)
+
+#######################
+# Creates a plot of confidence interval vs. value of a parameter with symbols being the 2-letter abbreviation
+# for each country.
+# 
+# model the model function you want to use. One of SF, CD, CDe, CES, or LINEX.
+# param the parameter you want to plot. The options depend upon the model you want:
+#       SF: lambda or m
+#       CD: lambda, alpha, or beta
+#      CDe: lambda, alpha, beta, or gamma
+#      CES: gamma, lambda, delta_1, sigma_1, delta, or sigma
+#    LINEX: a_0 or c_t
+# energyType the energy type you want. One of Q, X, or U
+# factor the factor you want to use in a single-factor model, if needed. One of K, L, Q, X, or U.
+##
+CIvsParamPlot <- function(model, param, energyType=NA, factor=NA){
+print("inside CIvsParamPlot")
+  if (model == "SF"){
+    data <- singleFactorParamsDF(factor)
+    if (param == "lambda"){
+      # Want lambda
+      x <- subset(data, select=lambda) # The column of lambdas
+      colnames(x) <- "lambda"
+      xLabel <- "$\\lambda$"
+      y <- subset(data, select=upperCI_lambda) - subset(data, select=lowerCI_lambda) # A column of CI values
+      colnames(y) <- "CI"
+      yLabel <- paste("95\\% CI on", xLabel)
+      data <- cbind(x, y)
+      data <- data.frame(data)
+    } else if (param == "m"){
+      # Want m
+      x <- subset(data, select=m) # The column of lambdas
+      colnames(x) <- "m"
+      if (factor == "K"){xLabel <- "$\\alpha$"}
+      else if (factor == "L"){xLabel <- "$\\beta$"}
+      else if ((factor == "Q") || (factor == "X") || (factor == "U")){xLabel <- "$\\gamma$"}
+      y <- subset(data, select=upperCI_m) - subset(data, select=lowerCI_m) # A column of CI values
+      colnames(y) <- "CI"
+      yLabel <- paste("95\\% CI on", xLabel)
+      data <- cbind(x, y)
+      data <- data.frame(data)
+    }
+  }
+  if (model == "CD"){
+
+  }
+  if (model == "CDe"){
+
+  }
+  if (model == "CES"){
+
+  }
+  if (model == "LINEX"){
+
+  }
+#   plot <- xyplot(rep(1:9) ~ 1:9,
+#                  panel = function(x, y){
+# print(x)
+# print(y)
+#                    ltext(x = x, y = y, labels=countryAbbrevsAlph)
+#                  })
+print(data)
+print(xLabel)
+print(yLabel)
+  # data[ , 1] is the column that contains the value of the parameter
+  # data[ , 2] is the column that contains confidence intervals
+  plot <- xyplot(data[ , 2] ~ data[ , 1],
+                 xlab=list(label=xLabel),
+                 ylab=list(label=yLabel),
+                 panel = function(x, y){
+                   ltext(x=x, y=y, labels=rownames(data))
+                 })
+  return(plot)
+}
+CIvsParamPlot(model="SF", param="m", factor="U")
+@
 
@@
 
-\noindent to historical data where the factor of production ($f$) is any of $k$, $l$, $q$, $x$, or $u$, and the exponent ($m$) is $\alpha$ for $k$, $\beta$ for $l$, or $\gamma$ for $q$, $x$, and $u$.
+\noindent to historical data where the factor of production ($f$) is one of $k$, $l$, $q$, $x$, or $u$, and the exponent ($m$) is $\alpha$ for $k$, $\beta$ for $l$, or $\gamma$ for $q$, $x$, and $u$.
 
@@
 
-\noindent where $e$ can be any of thermal energy ($q$), exergy ($x$), or useful work ($u$).
+\noindent where $e$ can be one of thermal energy ($q$), exergy ($x$), or useful work ($u$).
 
@@
 
-\noindent where $e$ is any of $q$, $x$, or $u$; $\sigma$, $\gamma_E$, $\beta$, $\lambda_L$, and $\lambda_E$ are fitting parameters; $\mathrm{e}$ is the base of the natural logarithm; and the sum $\alpha + \beta$ is constrained to unity.
+\noindent where $e$ is one of $q$, $x$, or $u$; $\sigma$, $\gamma_E$, $\beta$, $\lambda_L$, and $\lambda_E$ are fitting parameters; $\mathrm{e}$ is the base of the natural logarithm; and the sum $\alpha + \beta$ is constrained to unity.
 
@@
 
-\noindent where $e$ is any of $q$, $x$, or $u$; $a_0$ and $c_t$ are fitting parameters; and $\mathrm{e}$ is the base of the natural logarithm.
+\noindent where $e$ is one of $q$, $x$, or $u$; $a_0$ and $c_t$ are fitting parameters; and $\mathrm{e}$ is the base of the natural logarithm.
 

### 2013-03-23 EconGrowth-R-Functions.Rnw
Now all models, factors, and energy types have been included in the CI vs. parameter graph function.

@@
   #Add names to the rows and columns
-  colnames(dataSF) <- list("lowerCI_lambda", "lambda", "upperCI_lambda", "lowerCI_m", "m", "upperCI_m")
+  colnames(dataSF) <- c("lowerCI_lambda", "lambda", "upperCI_lambda", "lowerCI_m", "m", "upperCI_m")
   rownames(dataSF) <- countryAbbrevs
+  dataSF <- data.frame(dataSF)
   return(dataSF)
@@
 
+######################
+# Makes a data.frame with the parameters for the Cobb-Douglas model without energy.
+##
+cobbDouglasParamsTableNoEnergyDF <- function(){
+  #Do rbind on the results of creating a row in the table for every country abbreviation that we know.
+  dataCD <- do.call("rbind", lapply(countryAbbrevs, cobbDouglasCountryRow))
+  rownames(dataCD) <- countryAbbrevs
+  colnames(dataCD) <- c("lowerCI_lambda", "lambda", "upperCI_lambda", 
+                        "lowerCI_alpha", "alpha", "upperCI_alpha",
+                        "lowerCI_beta", "beta", "upperCI_beta")
+  dataCD <- data.frame(dataCD)
+  return(dataCD)
+}
+
 ############################
@@
 cobbDouglasParamsTableNoEnergy <- function(){
-  #Do rbind on the results of creating a row in the table for every country abbreviation that we know.
-  dataCD <- do.call("rbind", lapply(countryAbbrevs, cobbDouglasCountryRow))
+  dataCD <- cobbDouglasParamsTableNoEnergyDF()
   colnames(dataCD) <- c(" ", "$\\lambda$", " ", 
@@
 
+######################
+# Makes a data.frame with the parameters for the Cobb-Douglas model with energy.
+##
+cobbDouglasParamsTableWithEnergyDF <- function(energyType){
+  #Do rbind on the results of creating a row in the table for every country abbreviation that we know.
+  dataCD <- do.call("rbind", lapply(countryAbbrevs, cobbDouglasCountryRow, energyType=energyType))
+  rownames(dataCD) <- countryAbbrevs
+  colnames(dataCD) <- c("lowerCI_lambda", "lambda", "upperCI_lambda", 
+                        "lowerCI_alpha", "alpha", "upperCI_alpha",
+                        "lowerCI_beta", "beta", "upperCI_beta",
+                        "lowerCI_gamma", "gamma", "upperCI_gamma")
+  dataCD <- data.frame(dataCD)
+  return(dataCD)
+}
+
 ############################
@@
   #Do rbind on the results of creating a row in the table for every country abbreviation that we know.
-  dataCD <- do.call("rbind", lapply(countryAbbrevs, cobbDouglasCountryRow, energyType=energyType))
+  dataCD <- cobbDouglasParamsTableWithEnergyDF(energyType)
   colnames(dataCD) <- c(" ", "$\\lambda$", " ", 
@@
 
+######################
+# Creates a data.frame for CES parameters
+cesParamsTableDF <- function(energyType){
+  dataCES <- do.call("rbind", lapply(countryAbbrevs, cesCountryRow, energyType=energyType))
+  colnames(dataCES) <- c("lowerCI_gamma", "gamma", "upperCI_gamma",
+                         "lowerCI_lambda", "lambda", "upperCI_lambda",
+                         "lowerCI_delta_1", "delta_1", "upperCI_delta_1",
+                         "lowerCI_delta", "delta", "upperCI_delta",
+                         "lowerCI_sigma_1", "sigma_1", "upperCI_sigma_1",
+                         "lowerCI_sigma", "sigma", "upperCI_sigma")
+  rownames(dataCES) <- countryAbbrevs
+  return(dataCES)
+}
+
 ############################
@@
 
+#####################
+# Creates a data.frame containing all parameters and their confidence intervals 
+##
+linexParamsTableDF <- function(energyType){
+  #Do rbind on the results of creating a row in the table for every country abbreviation that we know.
+  dataLINEX <- do.call("rbind", lapply(countryAbbrevs, linexCountryRow, energyType=energyType))
+  colnames(dataLINEX) <- c("lowerCI_a_0", "a_0", "upperCI_a_0",
+                           "lowerCI_c_t", "c_t", "upperCI_c_t")
+  rownames(dataLINEX) <- countryAbbrevs
+  return(dataLINEX)
+}
+
 ############################
@@
 linexParamsTable <- function(energyType){
-  #Do rbind on the results of creating a row in the table for every country abbreviation that we know.
-  dataLINEX <- do.call("rbind", lapply(countryAbbrevs, linexCountryRow, energyType=energyType))
+  linexParamsTableDF(energyType)
   colnames(dataLINEX) <- c(" ", "$a_0$", " ", " ", "$c_t$",  " ")

### 2013-03-23 EconGrowth.Rnw
Now all models, factors, and energy types have been included in the CI vs. parameter graph function.

--- 2013-03-19 EconGrowth.Rnw
@@
 
+<<CIvsParam_Graph, eval=TRUE>>=
+# plot(1:9, rep(1, 9), pch=LETTERS)
+# xyplot(rep(1:9) ~ 1:9, pch=LETTERS)
+# xyplot(rep(1:9) ~ 1:9, pch="US")
+# states <- data.frame(state.x77, 
+#                           state.name = dimnames(state.x77)[[1]], 
+#                           state.region = state.region) 
+#      xyplot(Murder ~ Population | state.region, data = states, 
+#             groups = state.name, 
+#             panel = function(x, y, subscripts, groups) { 
+#                 ltext(x = x, y = y, labels = groups[subscripts], cex=1, 
+#                       fontfamily = "HersheySans") 
+#             }) 
+# print(states)
+
+#######################
+# Creates a plot of confidence interval vs. value of a parameter with symbols being the 2-letter abbreviation
+# for each country.
+# 
+# model the model function you want to use. One of SF, CD, CDe, CES, or LINEX.
+# param the parameter you want to plot. The options depend upon the model you want:
+#       SF: lambda or m
+#       CD: lambda, alpha, or beta
+#      CDe: lambda, alpha, beta, or gamma
+#      CES: gamma, lambda, delta_1, sigma_1, delta, or sigma
+#    LINEX: a_0 or c_t
+# energyType the energy type you want. One of Q, X, or U
+# factor the factor you want to use in a single-factor model, if needed. One of K, L, Q, X, or U.
+##
+CIvsParamPlot <- function(model, param, energyType=NA, factor=NA){
+print("inside CIvsParamPlot")
+  # Get the data from the requested model
+  if (model == "SF"){data <- singleFactorParamsDF(factor)} 
+  else if (model == "CD"){data <- cobbDouglasParamsTableNoEnergyDF()}
+  else if (model == "CDe"){data <- cobbDouglasParamsTableWithEnergyDF(energyType)}
+  else if (model == "CES"){data <- cesParamsTableDF(energyType)}
+  else if (model == "LINEX"){data <- linexParamsTableDF(energyType)}
+print(data)
+  # Now get the data for the parameter requested
+  if (param == "lambda"){
+    x <- subset(data, select=lambda) # The column of lambdas
+    xLabel <- "$\\lambda$"
+    y <- subset(data, select=upperCI_lambda) - subset(data, select=lowerCI_lambda) # A column of CI values
+  } else if (param == "m"){
+    x <- subset(data, select=m) # The column of ms
+    colnames(x) <- "m"
+    if (factor == "K"){xLabel <- "$\\alpha$"}
+    else if (factor == "L"){xLabel <- "$\\beta$"}
+    else if ((factor == "Q") || (factor == "X") || (factor == "U")){xLabel <- "$\\gamma$"}
+    y <- subset(data, select=upperCI_m) - subset(data, select=lowerCI_m) # A column of CI values
+  } else if (param == "alpha"){
+    x <- subset(data, select=alpha) # The column of alphas
+    xLabel <- "$\\alpha$"
+    y <- subset(data, select=upperCI_alpha) - subset(data, select=lowerCI_alpha) # A column of CI values
+  } else if (param == "beta"){
+    x <- subset(data, select=beta) # The column of betas
+    xLabel <- "$\\beta$"
+    y <- subset(data, select=upperCI_beta) - subset(data, select=lowerCI_beta) # A column of CI values
+  } else if (param == "gamma"){
+    x <- subset(data, select=gamma) # The column of gammas
+    xLabel <- "$\\gamma$"
+    y <- subset(data, select=upperCI_gamma) - subset(data, select=lowerCI_gamma) # A column of CI values
+  } else if (param == "delta_1"){
+    x <- subset(data, select=delta_1) # The column of delta_1
+    xLabel <- "$\\delta_1$"
+    y <- subset(data, select=upperCI_delta_1) - subset(data, select=lowerCI_delta_1) # A column of CI values
+  } else if (param == "sigma_1"){
+    x <- subset(data, select=sigma_1) # The column of sigma_1
+    xLabel <- "$\\sigma_1$"
+    y <- subset(data, select=upperCI_sigma_1) - subset(data, select=lowerCI_sigma_1) # A column of CI values
+  } else if (param == "delta"){
+    x <- subset(data, select=delta) # The column of delta
+    xLabel <- "$\\delta$"
+    y <- subset(data, select=upperCI_delta) - subset(data, select=lowerCI_delta) # A column of CI values
+  } else if (param == "sigma"){
+    x <- subset(data, select=sigma) # The column of sigma
+    xLabel <- "$\\sigma$"
+    y <- subset(data, select=upperCI_sigma) - subset(data, select=lowerCI_sigma) # A column of CI values
+  } else if (param == "a_0"){
+    x <- subset(data, select=a_0) # The column of a_0s
+    xLabel <- "$a_0$"
+    y <- subset(data, select=upperCI_a_0) - subset(data, select=lowerCI_a_0) # A column of CI values
+  } else if (param == "c_t"){
+    x <- subset(data, select=c_t) # The column of c_ts
+    xLabel <- "$c_t$"
+    y <- subset(data, select=upperCI_c_t) - subset(data, select=lowerCI_c_t) # A column of CI values
+  }
+  colnames(y) <- "CI"
+  yLabel <- paste("95\\% CI on", xLabel)
+  data <- cbind(x, y)
+  data <- data.frame(data)
+print(data)
+print(xLabel)
+print(yLabel)
+  plot <- xyplot(data[ , 2] ~ data[ , 1], # data[ , 1] contains the the parameter; data[ , 2] contains the CIs
+                 xlab=list(label=xLabel),
+                 ylab=list(label=yLabel),
+                 panel = function(x, y){
+                   ltext(x=x, y=y, labels=rownames(data))
+                 })
+  return(plot)
+}
+#CIvsParamPlot(model="SF", param="lambda", factor="Q")
+#CIvsParamPlot(model="CD", param="alpha")
+#CIvsParamPlot(model="CDe", param="gamma", energyType="Q")
+#CIvsParamPlot(model="CES", param="delta", energyType="Q")
+CIvsParamPlot(model="LINEX", param="c_t", energyType="Q")
+@
+
 Neoclassical economic growth theory attributes output growth to growth rates of factors of production: capital stock and labor.

### 2013-03-23 EconGrowth-R-Functions.Rnw
Now making a CI_delta vs. delta graph for CES in the presentation.

@@
 @
+
+<<CIvsParam_Graph, eval=TRUE>>=
+#######################
+# Creates a plot of confidence interval vs. value of a parameter with symbols being the 2-letter abbreviation
+# for each country.
+# 
+# model the model function you want to use. One of SF, CD, CDe, CES, or LINEX.
+# param the parameter you want to plot. The options depend upon the model you want:
+#       SF: lambda or m
+#       CD: lambda, alpha, or beta
+#      CDe: lambda, alpha, beta, or gamma
+#      CES: gamma, lambda, delta_1, sigma_1, delta, or sigma
+#    LINEX: a_0 or c_t
+# energyType the energy type you want. One of Q, X, or U
+# factor the factor you want to use in a single-factor model, if needed. One of K, L, Q, X, or U.
+# textScaling the scale factor for labels on the graph
+##
+CIvsParamPlot <- function(model, param, energyType=NA, factor=NA, textScaling=1.0){
+  # Get the data from the requested model
+  if (model == "SF"){data <- singleFactorParamsDF(factor)} 
+  else if (model == "CD"){data <- cobbDouglasParamsTableNoEnergyDF()}
+  else if (model == "CDe"){data <- cobbDouglasParamsTableWithEnergyDF(energyType)}
+  else if (model == "CES"){data <- cesParamsTableDF(energyType)}
+  else if (model == "LINEX"){data <- linexParamsTableDF(energyType)}
+  # Now get the data for the parameter requested
+  if (param == "lambda"){
+    x <- subset(data, select=lambda) # The column of lambdas
+    xLabel <- "$\\lambda$"
+    y <- subset(data, select=upperCI_lambda) - subset(data, select=lowerCI_lambda) # A column of CI values
+  } else if (param == "m"){
+    x <- subset(data, select=m) # The column of ms
+    colnames(x) <- "m"
+    if (factor == "K"){xLabel <- "$\\alpha$"}
+    else if (factor == "L"){xLabel <- "$\\beta$"}
+    else if ((factor == "Q") || (factor == "X") || (factor == "U")){xLabel <- "$\\gamma$"}
+    y <- subset(data, select=upperCI_m) - subset(data, select=lowerCI_m) # A column of CI values
+  } else if (param == "alpha"){
+    x <- subset(data, select=alpha) # The column of alphas
+    xLabel <- "$\\alpha$"
+    y <- subset(data, select=upperCI_alpha) - subset(data, select=lowerCI_alpha) # A column of CI values
+  } else if (param == "beta"){
+    x <- subset(data, select=beta) # The column of betas
+    xLabel <- "$\\beta$"
+    y <- subset(data, select=upperCI_beta) - subset(data, select=lowerCI_beta) # A column of CI values
+  } else if (param == "gamma"){
+    x <- subset(data, select=gamma) # The column of gammas
+    xLabel <- "$\\gamma$"
+    y <- subset(data, select=upperCI_gamma) - subset(data, select=lowerCI_gamma) # A column of CI values
+  } else if (param == "delta_1"){
+    x <- subset(data, select=delta_1) # The column of delta_1
+    xLabel <- "$\\delta_1$"
+    y <- subset(data, select=upperCI_delta_1) - subset(data, select=lowerCI_delta_1) # A column of CI values
+  } else if (param == "sigma_1"){
+    x <- subset(data, select=sigma_1) # The column of sigma_1
+    xLabel <- "$\\sigma_1$"
+    y <- subset(data, select=upperCI_sigma_1) - subset(data, select=lowerCI_sigma_1) # A column of CI values
+  } else if (param == "delta"){
+    x <- subset(data, select=delta) # The column of delta
+    xLabel <- "$\\delta$"
+    y <- subset(data, select=upperCI_delta) - subset(data, select=lowerCI_delta) # A column of CI values
+  } else if (param == "sigma"){
+    x <- subset(data, select=sigma) # The column of sigma
+    xLabel <- "$\\sigma$"
+    y <- subset(data, select=upperCI_sigma) - subset(data, select=lowerCI_sigma) # A column of CI values
+  } else if (param == "a_0"){
+    x <- subset(data, select=a_0) # The column of a_0s
+    xLabel <- "$a_0$"
+    y <- subset(data, select=upperCI_a_0) - subset(data, select=lowerCI_a_0) # A column of CI values
+  } else if (param == "c_t"){
+    x <- subset(data, select=c_t) # The column of c_ts
+    xLabel <- "$c_t$"
+    y <- subset(data, select=upperCI_c_t) - subset(data, select=lowerCI_c_t) # A column of CI values
+  }
+  colnames(y) <- "CI"
+  yLabel <- paste("95\\% CI on", xLabel)
+  data <- cbind(x, y)
+  plot <- xyplot(data[ , 2] ~ data[ , 1], # data[ , 1] contains the the parameter; data[ , 2] contains the CIs
+                 xlab=list(label=xLabel),
+                 ylab=list(label=yLabel),
+                 scales=list(cex=scaleTextSize * textScaling, #controls text size on scales.
+                             tck=scaleTickSize), #controls tick mark length. < 0 for inside the graph.
+                 panel = function(x, y){
+                   ltext(x=x, y=y, labels=rownames(data))
+                 })
+  return(plot)
+}
+#CIvsParamPlot(model="SF", param="lambda", factor="Q")
+#CIvsParamPlot(model="CD", param="alpha")
+#CIvsParamPlot(model="CDe", param="gamma", energyType="Q")
+#CIvsParamPlot(model="CES", param="delta", energyType="Q")
+#CIvsParamPlot(model="LINEX", param="c_t", energyType="Q")
+@

### 2013-03-23 EconGrowthSeminar.Rnw
Now making a CI_delta vs. delta graph for CES in the presentation.

@@
 \begin{frame}{$CI_{\delta}$ and $\delta$ in CES} %----------------------------
-  Graph here of $CI_{\delta}$ vs. $\delta$ where each country abbreviation is plotted.
+<<CI_delta_vs_delta_Graph, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight, eval=TRUE>>=
+CIvsParamPlot(model="CES", param="delta", energyType="Q")
+@
 \end{frame}

### 2013-03-24 EconGrowthSeminar.Rnw
Now including graphs of CI size vs. parameter value for all of the fits I had been considering.

--- 2013-03-22 EconGrowthSeminar.Rnw
@@
 \begin{frame}{CI and $\gamma$ in Cobb-Douglas} %----------------------------
-  Graph here of CI vs. $\gamma$ where each country abbreviation is plotted.
+<<CI_gamma_vs_gamma_Graph, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
+CIvsParamPlot(model="CDe", param="gamma", energyType="Q")
+@
 \end{frame}
@@
     \pause
-    \item{Direct energy input to economy ($q$)is unimportant as a Cobb-Douglas predictor of economic output ($y$)}
+    \item{Direct energy input to economy ($q$) is unimportant as a Cobb-Douglas predictor of economic output ($y$)}
   \end{itemize}
@@
   \begin{center}
-    \cdeEqn\\
+    \small\cesEqn\normalsize\\
     \includegraphics<1>[height=2.5in]{figure_other/CI-delta-1.pdf}
@@
 \begin{frame}{$CI_{\delta}$ and $\delta$ in CES} %----------------------------
-  Graph here of $CI_{\delta}$ vs. $\delta$ where each country abbreviation is plotted.
+<<CI_delta_vs_delta_Graph, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
+CIvsParamPlot(model="CES", param="delta", energyType="Q")
+@
 \end{frame}
@@
   \begin{center}
-    \cdeEqn\\
+    \small\cesEqn\normalsize\\
     \includegraphics<1>[height=2.5in]{figure_other/CI-sigma-1.pdf}
@@
 \begin{frame}{$CI_{\sigma}$ and $\sigma$ in CES} %----------------------------
-  Graph here of $CI_{\sigma}$ vs. $\sigma$ where each country abbreviation is plotted.
+<<CI_sigma_vs_sigma_Graph, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
+CIvsParamPlot(model="CES", param="sigma", energyType="Q")
+@
 \end{frame}
@@
 \begin{frame}{Implications from CES} %----------------------------
-  \begin{center}\cesEqn\end{center}
+  \begin{center}\small\cesEqn\normalsize\end{center}
   \vspace{\baselineskip}
@@
     \item{kl and e are complements, sigma small where it is distinguishable.}
-    \item{Direct energy input to economy ($q$)is unimportant as a CES predictor of economic output ($y$), because delta is close to 1.0}
+    \item{Direct energy input to economy ($q$) is unimportant as a CES predictor of economic output ($y$), because delta is close to 1.0}
   \end{itemize}

### 2013-03-25 EconGrowthSeminar.Rnw
Changed a few limits to the CI vs. parameter graphs.

@@
 
-\begin{frame}{World Oil Supply is Tightening}{\citep{Tverberg:2013}} %----------------------------
-  \includegraphics[width=4.0in]{figure_other/Figure_Tverberg_2013.png}
+\begin{frame}{World Oil Supply is Tightening}{\citep{Tverberg:2013b}} %----------------------------
+  \includegraphics[width=4.0in]{figure_other/Figure_Tverberg_2013b.png}
 \end{frame}
@@
 
-\minorSeparator{The Question\\ \normalsize      %----------------------------
-\vspace{\baselineskip} 
-Which economic growth model best describes (statistically) the role of energy in economic growth for different types of economies?}
+\minorSeparator{The Question} %----------------------------
+
+\begin{frame}{The Question} %----------------------------
+  \begin{center}
+    Which economic growth model best describes (statistically) the role of energy in economic growth for different types of economies?
+
+    \pause
+
+    No known studies of comparing economic growth models for various types of economies on a rigorous statistical basis.
+  \end{center}
+\end{frame}
 
@@
 
-\begin{frame}{CI and $\gamma$ in Cobb-Douglas} %----------------------------
-<<CI_gamma_vs_gamma_Graph, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
+\begin{frame}{$CI_{\gamma}$ vs. $\gamma$ for Cobb-Douglas with Energy} %----------------------------
+<<CI_gamma_vs_gamma_Graph, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5, eval=TRUE>>=
 CIvsParamPlot(model="CDe", param="gamma", energyType="Q")
@@
 
-\begin{frame}{$CI_{\delta}$ and $\delta$ in CES} %----------------------------
-<<CI_delta_vs_delta_Graph, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
+\begin{frame}{$CI_{\delta}$ vs. $\delta$ for CES} %----------------------------
+<<CI_delta_vs_delta_Graph, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5, eval=TRUE>>=
 CIvsParamPlot(model="CES", param="delta", energyType="Q")
@@
 
-\begin{frame}{$CI_{\sigma}$ and $\sigma$ in CES} %----------------------------
-<<CI_sigma_vs_sigma_Graph, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
+\begin{frame}{$CI_{\sigma}$ vs. $\sigma$ for CES} %----------------------------
+<<CI_sigma_vs_sigma_Graph, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5, eval=TRUE>>=
 CIvsParamPlot(model="CES", param="sigma", energyType="Q")
@@
 
+\minorSeparator{Introduction} %----------------------------
+
+\begin{frame}{Energy Cost Share}{\citep{Tverberg:2013a}} %----------------------------
+  \begin{center}
+    \includegraphics[height=6.3cm]{figure_other/Figure_Tverberg_2013a.png}
+  \end{center}
+\end{frame}
+
 \minorSeparator{Single-factor Model}

### 2013-03-26 EconGrowth-R-Functions.Rnw
Changed a few limits to the CI vs. parameter graphs.
Added a new function in the CD functions section to make a partial residuals plot: residuals vs. e for the Cobb-Douglas without energy model.

--- 2013-03-23 EconGrowth-R-Functions.Rnw
@@
                   #Include the next 3 lines to fit with constraints.
-                  #algorithm = "port",
-                  #lower = list(lambda=-Inf, a=0, b=0),
-                  #upper = list(lambda= Inf, a=1, b=1)
+#                   algorithm = "port",
+#                   lower = list(lambda=-Inf, a=0, b=0),
+#                   upper = list(lambda= Inf, a=1, b=1)
                   )
@@
 }
+
+#################
+# Creates a plot with y residuals vs. energy (e). The y residuals are from a Cobb-Douglas model without energy.
+# The energy term on the x axis is whatever type is specified in the calling funciton
+partialResidualPlot <- function(countryAbbrev, energyType, textScaling=1.0){
+  # Get the model
+  cdModel <- cdModel(countryAbbrev)
+  # Get the residuals
+  cdResid <- resid(cdModel)
+  cdResid <- data.frame(cdResid)
+  cdResid <- padRows(countryAbbrev=countryAbbrev, df=cdResid)
+  # Load data
+  data <- loadData(countryAbbrev)
+  data <- cbind(data, cdResid)
+  data <- replaceColName(dataTable=data, factor=energyType, newName="iEToFit")
+  plot <- xyplot(cdResid ~ iEToFit, data=data,
+                 type=c('p','smooth'),
+                 scales=list(cex=scaleTextSize*textScaling, #controls text size on scales.
+                             tck=scaleTickSize), #controls tick mark length. < 0 for inside the graph.
+                 xlab=list(label=paste("$", tolower(energyType), "$", sep=""), cex=textScaling),
+                 ylab=list(label="$y$ residuals", cex=textScaling)
+                 )
+  return(plot)  
+}
 @
@@
   # Now get the data for the parameter requested
+  # Also, set limits on the x and y axes if needed
   if (param == "lambda"){
@@
     y <- subset(data, select=upperCI_lambda) - subset(data, select=lowerCI_lambda) # A column of CI values
+    xLimits <- c(0.0, 0.1); atX=c(0.0, 0.05, 0.1)
+    yLimits <- c(0.0, 0.2); atY-c(0.0, 0.1, 0.2)
   } else if (param == "m"){
@@
     y <- subset(data, select=upperCI_m) - subset(data, select=lowerCI_m) # A column of CI values
+    xLimits <- c(-0.1, 1.5); atX <- c(0.0, 0.5, 1.0, 1.5)
+    yLimits <- c(0.0, 1.5); atY <- c(0.0, 0.5, 1.0, 1.5)
   } else if (param == "alpha"){
@@
     y <- subset(data, select=upperCI_alpha) - subset(data, select=lowerCI_alpha) # A column of CI values
+    xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
+    yLimits <- c(0.0, 1.5); atY <- c(0.0, 0.5, 1.0, 1.5)
   } else if (param == "beta"){
@@
     y <- subset(data, select=upperCI_beta) - subset(data, select=lowerCI_beta) # A column of CI values
+    xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
+    yLimits <- c(-0.1, 1.5); atY <- c(0.0, 0.5, 1.0, 1.5)
   } else if (param == "gamma"){
@@
     y <- subset(data, select=upperCI_gamma) - subset(data, select=lowerCI_gamma) # A column of CI values
+    xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
+    yLimits <- c(-0.1, 1.5); atY <- c(0.0, 0.5, 1.0, 1.5)
   } else if (param == "delta_1"){
@@
     y <- subset(data, select=upperCI_delta_1) - subset(data, select=lowerCI_delta_1) # A column of CI values
+    xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
+    yLimits <- c(0.0, 1.5); atY <- c(0.0, 0.5, 1.0, 1.5)
   } else if (param == "sigma_1"){
@@
     y <- subset(data, select=upperCI_sigma_1) - subset(data, select=lowerCI_sigma_1) # A column of CI values
+    xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
+    yLimits <- c(0.0, 1.5); atY <- c(0.0, 0.5, 1.0, 1.5)
   } else if (param == "delta"){
@@
     y <- subset(data, select=upperCI_delta) - subset(data, select=lowerCI_delta) # A column of CI values
+    xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
+    yLimits <- c(-0.1, 2.0); atY <- c(0.0, 1.0, 2.0)
   } else if (param == "sigma"){
@@
     y <- subset(data, select=upperCI_sigma) - subset(data, select=lowerCI_sigma) # A column of CI values
+    xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
+    yLimits <- c(-0.1, 2.0); atY <- c(0.0, 1.0, 2.0)
   } else if (param == "a_0"){
@@
     y <- subset(data, select=upperCI_a_0) - subset(data, select=lowerCI_a_0) # A column of CI values
+    xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
+    yLimits <- c(0.0, 1.5); atY <- c(0.0, 0.5, 1.0, 1.5)
   } else if (param == "c_t"){
@@
     y <- subset(data, select=upperCI_c_t) - subset(data, select=lowerCI_c_t) # A column of CI values
+    xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
+    yLimits <- c(0.0, 1.5); atY <- c(0.0, 0.5, 1.0, 1.5)
   }
@@
                  scales=list(cex=scaleTextSize * textScaling, #controls text size on scales.
-                             tck=scaleTickSize), #controls tick mark length. < 0 for inside the graph.
+                             tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
+                             x=list(at=atX),
+                             y=list(at=atY)
+                             ), 
+                 xlim=xLimits, #x axis limits
+                 ylim=yLimits, #y axis limits
                  panel = function(x, y){

### 2013-03-26 EconGrowthSeminar.Rnw
Added a new function in the CD functions section to make a partial residuals plot: residuals vs. e for the Cobb-Douglas without energy model.

@@
     Which economic growth model best describes (statistically) the role of energy in economic growth for different types of economies?
-
+    \vspace{\baselineskip}
     \pause
 
-    No known studies of comparing economic growth models for various types of economies on a rigorous statistical basis.
+    No known comparative studies of economic growth models for various types of economies on a rigorous statistical basis.
   \end{center}
@@
   \end{itemize}
-  Simplification: 1 type of energy (Q)
+  \vspace{\baselineskip}
+  \pause
+
+  \begin{center}Simplification: 1 type of energy ($Q$) for this presentation\end{center}
 \end{frame}
@@
     \item{Respect sum constraint: $\alpha + \beta + \gamma = 1$}
-    \item{Respect absolute constraints: $0 \leq \alpha, \beta, \gamma \leq 1$}
+    \item{Respect absolute constraints: $0 \leq \alpha, \beta, \gamma \leq 1$} (not yet)
   \end{itemize}
@@
 
-\begin{frame}{$CI_{\gamma}$ vs. $\gamma$ for Cobb-Douglas with Energy} %----------------------------
+\begin{frame}{$CI_{\gamma}$ vs. $\gamma$ for Cobb-Douglas with $Q$} %----------------------------
 <<CI_gamma_vs_gamma_Graph, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5, eval=TRUE>>=
@@
 \begin{frame}{95\% Confidence Intervals}{CES with $q$} %----------------------------
-<<CESq_Params_Graph, fig.width=presentationGraph1ColWidth*1.8, fig.height=presentationGraph1RowHeight*1.8, eval=TRUE>>=
+<<CESq_Params_Graph, fig.width=presentationGraph1ColWidth*1.8, fig.height=presentationGraph1RowHeight*1.8>>=
 createCESParamsGraph("Q")
@@
 
-\begin{frame}{$CI_{\delta}$ vs. $\delta$ for CES} %----------------------------
+\begin{frame}{$CI_{\delta}$ vs. $\delta$ for CES with $Q$} %----------------------------
 <<CI_delta_vs_delta_Graph, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5, eval=TRUE>>=
@@
 
-\begin{frame}{$CI_{\sigma}$ vs. $\sigma$ for CES} %----------------------------
+\begin{frame}{$CI_{\sigma}$ vs. $\sigma$ for CES with $Q$} %----------------------------
 <<CI_sigma_vs_sigma_Graph, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5, eval=TRUE>>=
@@
     \vspace{\baselineskip}
+    \item{Incorporate all constraints for Cobb-Douglas model}
     \vspace{\baselineskip}

### 2013-03-26 EconGrowth-R-Functions.Rnw
Made triangular figures for CI vs. gamma graph. Need to do the same for delta and sigma graphs.

@@
                  type=c('p','smooth'),
+                 col="black",
                  scales=list(cex=scaleTextSize*textScaling, #controls text size on scales.
@@
     xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
-    yLimits <- c(-0.1, 1.5); atY <- c(0.0, 0.5, 1.0, 1.5)
+    yLimits <- c(-0.1, 2.0); atY <- c(0.0, 1.0, 2.0)
   } else if (param == "delta_1"){
@@
     xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
-    yLimits <- c(0.0, 1.5); atY <- c(0.0, 0.5, 1.0, 1.5)
+    yLimits <- c(0.0, 2.0); atY <- c(0.0, 1.0, 2.0)
   } else if (param == "delta"){
@@
   colnames(y) <- "CI"
-  yLabel <- paste("95\\% CI on", xLabel)
+  yLabel <- paste("Width of 95\\% CI on", xLabel)
   data <- cbind(x, y)

### 2013-03-26 EconGrowthSeminar.Rnw
Made triangular figures for CI vs. gamma graph. Need to do the same for delta and sigma graphs.

@@
 
+\begin{frame}{Benefit to Including Energy?}  %----------------------------
+<<US_Partial_Residuals_Plot, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H", eval=TRUE>>=
+partialResidualPlot("US", "Q", textScaling=textScaleForGraphs)
+@
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{US}{0.055}
+\end{frame}
+
 \begin{frame}{95\% Confidence Intervals}{Cobb-Douglas with $q$} %----------------------------
@@
 \begin{frame}{$CI_{\gamma}$ vs. $\gamma$ for Cobb-Douglas with $Q$} %----------------------------
-<<CI_gamma_vs_gamma_Graph, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5, eval=TRUE>>=
+<<CI_gamma_vs_gamma_Graph, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5>>=
 CIvsParamPlot(model="CDe", param="gamma", energyType="Q")
@@
 \begin{frame}{$CI_{\delta}$ vs. $\delta$ for CES with $Q$} %----------------------------
-<<CI_delta_vs_delta_Graph, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5, eval=TRUE>>=
+<<CI_delta_vs_delta_Graph, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5>>=
 CIvsParamPlot(model="CES", param="delta", energyType="Q")
@@
 \begin{frame}{$CI_{\sigma}$ vs. $\sigma$ for CES with $Q$} %----------------------------
-<<CI_sigma_vs_sigma_Graph, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5, eval=TRUE>>=
+<<CI_sigma_vs_sigma_Graph, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5>>=
 CIvsParamPlot(model="CES", param="sigma", energyType="Q")
@@
   \begin{center}
-    \includegraphics[height=6.3cm]{figure_other/Figure_Tverberg_2013a.png}
+    \includegraphics[height=6.0cm]{figure_other/Figure_Tverberg_2013a.png}
   \end{center}

### 2013-03-26 EconGrowthSeminar.Rnw
Added a placeholder slide for Types of Economies.
Significantly re-organized the seminar presentation.

@@
 
+\usepackage{multirow} % To create multirow tables.
+
 \title[Energy and Growth] % (optional, use only with long paper titles)
@@
 
+\subsection[Interactions]{Energy-Economy Interactions} %+++++++++++++++++++++++++++++++++++++++
+
+\minorSeparator{Energy-Economy Interactions} %----------------------------
+
 \begin{frame}{Energy is Essential for Economic Activity} %----------------------------
@@
   \begin{center}
-    \includegraphics[height=2.5cm]{figure_other/Figure_Growth_Models.pdf}
+    \includegraphics[height=2.5cm]{figure_other/Growth_Models.pdf}
   \end{center}
@@
 
-\subsection[Factors of Production]{Factors of Production} %+++++++++++++++++++++++++++++++++++++++
-
-\minorSeparator{Factors of Production} %----------------------------
-
-\begin{frame}{Capital Stock ($K$) and Labor ($L$)} %----------------------------
-  \begin{itemize}
-    \item{Capital Stock ($K$) <Definition here>}
-    \item{Labor ($L$) <Definition here>}
-  \end{itemize}
-\end{frame}
-
-\begin{frame}{Energy ($E$)} %----------------------------
+\subsection[The Question]{The Question} %+++++++++++++++++++++++++++++++++++++++
+
+\minorSeparator{The Question} %----------------------------
+
+\begin{frame}{The Question} %----------------------------
+  \begin{center}
+    Which economic growth model best describes (statistically) the role of energy in economic growth for different types of economies?
+    \vspace{\baselineskip}
+    \pause
+    \footnotesize
+    \\ No known rigorous, statistical comparative studies of economic growth models for various types of economies. 
+    \normalsize
+  \end{center}
+\end{frame}
+
+\subsection[Coordinates]{Coordinates of Analysis}
+
+\minorSeparator{Coordinates of Analysis} %----------------------------
+
+\begin{frame}{Coordinates of Analysis} %----------------------------
+  \begin{itemize}
+    \item{Type of Economy}
+    \vspace{\baselineskip}
+    \item{Type of Energy}
+    \vspace{\baselineskip}
+    \item{Economic Growth Model}
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Type of Economy} %----------------------------
+  \begin{center}
+    \begin{tabular}{r c c l}
+      \multirow{3}{*}{Developed}  & \includegraphics[height=0.11in]{flag/flag_US.png} & US & USA           \\
+                                  & \includegraphics[height=0.11in]{flag/flag_UK.png} & UK & United Kingdom\\
+                                  & \includegraphics[height=0.11in]{flag/flag_JP.png} & JP & Japan         \\
+      \hline
+      \multirow{2}{*}{Developing} & \includegraphics[height=0.11in]{flag/flag_CN.png} & CN & China         \\
+                                  & \includegraphics[height=0.11in]{flag/flag_ZA.png} & ZA & South Africa  \\
+      \hline
+      \multirow{2}{*}{Petrol}     & \includegraphics[height=0.11in]{flag/flag_SA.png} & SA & Saudo Arabia  \\
+                                  & \includegraphics[height=0.11in]{flag/flag_IR.png} & IR & Iran          \\
+      \hline
+      \multirow{2}{*}{Malthusian} & \includegraphics[height=0.11in]{flag/flag_TZ.png} & TZ & Tanzania      \\
+                                  & \includegraphics[height=0.11in]{flag/flag_ZM.png} & ZM & Zambia        \\
+    \end{tabular}
+  \end{center}
+\end{frame}
+
+\begin{frame}{Type of Energy ($E$)} %----------------------------
   \begin{itemize}
     \item{Thermal energy ($Q$)}
+    \vspace{\baselineskip}  
     \item{Exergy ($X$)}
-    \item{Useful work ($W$)}
-  \end{itemize}
-\end{frame}
-
-\subsection[Growth Models]{Economic Growth Models} %+++++++++++++++++++++++++++++++++++++++
-
-\minorSeparator{Economic Growth Models} %----------------------------
-
-\begin{frame}{No Shortage of Economic Growth Models} %----------------------------
+    \vspace{\baselineskip}
+    \item{Useful work ($U$)}
+  \end{itemize}
+  \vspace{\baselineskip}
+  \pause
+  \begin{center}Simplification: 1 type of energy ($Q$) for this presentation\end{center}
+\end{frame}
+
+\begin{frame}{Economic Growth Model} %----------------------------
   Single Factor: \sfEqn
@@
 
-\subsection[The Question]{The Question} %+++++++++++++++++++++++++++++++++++++++
-
-\minorSeparator{The Question} %----------------------------
-
-\begin{frame}{The Question} %----------------------------
-  \begin{center}
-    Which economic growth model best describes (statistically) the role of energy in economic growth for different types of economies?
-    \vspace{\baselineskip}
-    \pause
-
-    No known comparative studies of economic growth models for various types of economies on a rigorous statistical basis.
-  \end{center}
-\end{frame}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\majorSeparator{Evaluation of \vspace{\baselineskip} Growth Models}
-
-\begin{frame}{Coordinates of Analysis} %----------------------------
-  \begin{itemize}
-    \item{Country/Economy: 9 \\US, UK, JP, CN, ZA, SA, IR, TZ, ZM}
-    \item{Economic Growth Model: 4 \\SF, CD, CES, LINEX}
-    \item{Type of Energy: 3 \\Q, X, U}
-  \end{itemize}
-  \vspace{\baselineskip}
-  \pause
-
-  \begin{center}Simplification: 1 type of energy ($Q$) for this presentation\end{center}
-\end{frame}
+\majorSeparator{Evaluation of Growth Models}
 
@@
 
+<<pprint>>=
+pprint <- function(num, digits = 2){
+  out <- formatC(num, digit=digits, format="f")
+  return(out)
+}
+@
+
 <<Coefs_US_CD>>=
@@
         \tiny
-          \begin{tabular}{|c|c|c|c|c|}\hline
+          \begin{tabular}{c|c c c c}
             $e$ & $\lambda$ & $\alpha$ & $\beta$ & $\gamma$\\
             \hline
-                  & \Sexpr{cdUS["CD", "lambda"]} & \Sexpr{cdUS["CD", "alpha"]} & \Sexpr{cdUS["CD", "beta"]} & \Sexpr{cdUS["CD", "gamma"]}\\
-            \hline
-            $q$   & \Sexpr{cdqUS["CD", "lambda"]} & \Sexpr{cdqUS["CD", "alpha"]} & \Sexpr{cdqUS["CD", "beta"]} & \Sexpr{cdqUS["CD", "gamma"]}\\
-            \hline
-            $x$   & \Sexpr{cdxUS["CD", "lambda"]} & \Sexpr{cdxUS["CD", "alpha"]} & \Sexpr{cdxUS["CD", "beta"]} & \Sexpr{cdxUS["CD", "gamma"]}\\
-            \hline
-            $u$   & \Sexpr{cduUS["CD", "lambda"]} & \Sexpr{cduUS["CD", "alpha"]} & \Sexpr{cduUS["CD", "beta"]} & \Sexpr{cduUS["CD", "gamma"]}\\
-            \hline
+                  & \Sexpr{pprint(cdUS["CD", "lambda"], digits=4)} & \Sexpr{pprint(cdUS["CD", "alpha"])} & \Sexpr{pprint(cdUS["CD", "beta"])} & \Sexpr{pprint(cdUS["CD", "gamma"])}\\
+            \hline
+            $q$   & \Sexpr{pprint(cdqUS["CD", "lambda"], digits=4)} & \Sexpr{pprint(cdqUS["CD", "alpha"])} & \Sexpr{pprint(cdqUS["CD", "beta"])} & \Sexpr{pprint(cdqUS["CD", "gamma"])}\\
+            \hline
+            $x$   & \Sexpr{pprint(cdxUS["CD", "lambda"], digits=4)} & \Sexpr{pprint(cdxUS["CD", "alpha"])} & \Sexpr{pprint(cdxUS["CD", "beta"])} & \Sexpr{pprint(cdxUS["CD", "gamma"])}\\
+            \hline
+            $u$   & \Sexpr{pprint(cduUS["CD", "lambda"], digits=4)} & \Sexpr{pprint(cduUS["CD", "alpha"])} & \Sexpr{pprint(cduUS["CD", "beta"])} & \Sexpr{pprint(cduUS["CD", "gamma"])}\\
           \end{tabular}
@@
     \column{2.2in}
-<<Results_Graph_US_CD, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+<<Results_Graph_US_CD, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight>>=
 createCDLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
@@
 \begin{frame}{Benefit to Including Energy?}  %----------------------------
-<<US_Partial_Residuals_Plot, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H", eval=TRUE>>=
+<<US_Partial_Residuals_Plot, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
 partialResidualPlot("US", "Q", textScaling=textScaleForGraphs)
@@
 
-\begin{frame}{Implications from Cobb-Douglas} %----------------------------
+\begin{frame}{Implications from Cobb-Douglas with $Q$} %----------------------------
   \begin{center}\cdeEqn\end{center}
@@
         \tiny
-          \begin{tabular}{|c|c|c|c|}\hline
+          \begin{tabular}{c|c c c}
             $e$ & $\gamma$ & $\lambda$ & $\delta_1$\\
             \hline
-            $q$ & \Sexpr{cesqUS["CES", "gamma"]} & \Sexpr{cesqUS["CES", "lambda"]} & \Sexpr{cesqUS["CES", "delta_1"]}\\
-            \hline
-            $x$ & \Sexpr{cesxUS["CES", "gamma"]} & \Sexpr{cesxUS["CES", "lambda"]} & \Sexpr{cesxUS["CES", "delta_1"]}\\
-            \hline
-            $u$ & \Sexpr{cesuUS["CES", "gamma"]} & \Sexpr{cesuUS["CES", "lambda"]} & \Sexpr{cesuUS["CES", "delta_1"]}\\
-            \hline
-          \end{tabular}
-          \vspace{\baselineskip}
-
-          \begin{tabular}{|c|c|c|c|}\hline
+            $q$ & \Sexpr{pprint(cesqUS["CES", "gamma"])} & \Sexpr{pprint(cesqUS["CES", "lambda"], digits=4)} & \Sexpr{pprint(cesqUS["CES", "delta_1"])}\\
+            \hline
+            $x$ & \Sexpr{pprint(cesxUS["CES", "gamma"])} & \Sexpr{pprint(cesxUS["CES", "lambda"], digits=4)} & \Sexpr{pprint(cesxUS["CES", "delta_1"])}\\
+            \hline
+            $u$ & \Sexpr{pprint(cesuUS["CES", "gamma"])} & \Sexpr{pprint(cesuUS["CES", "lambda"], digits=4)} & \Sexpr{pprint(cesuUS["CES", "delta_1"])}\\
+          \end{tabular}
+          \vspace{\baselineskip}
+
+          \begin{tabular}{c|c c c}
             $e$ & $\sigma_1$ & $\delta$ & $\sigma$\\
             \hline
-            $q$ & \Sexpr{cesqUS["CES", "sigma_1"]} & \Sexpr{cesqUS["CES", "delta"]} & \Sexpr{cesqUS["CES", "sigma"]}\\
-            \hline
-            $x$ & \Sexpr{cesxUS["CES", "sigma_1"]} & \Sexpr{cesxUS["CES", "delta"]} & \Sexpr{cesxUS["CES", "sigma"]}\\
-            \hline
-            $u$ & \Sexpr{cesuUS["CES", "sigma_1"]} & \Sexpr{cesuUS["CES", "delta"]} & \Sexpr{cesuUS["CES", "sigma"]}\\
-            \hline
+            $q$ & \Sexpr{pprint(cesqUS["CES", "sigma_1"])} & \Sexpr{pprint(cesqUS["CES", "delta"])} & \Sexpr{pprint(cesqUS["CES", "sigma"])}\\
+            \hline
+            $x$ & \Sexpr{pprint(cesxUS["CES", "sigma_1"])} & \Sexpr{pprint(cesxUS["CES", "delta"])} & \Sexpr{pprint(cesxUS["CES", "sigma"])}\\
+            \hline
+            $u$ & \Sexpr{pprint(cesuUS["CES", "sigma_1"])} & \Sexpr{pprint(cesuUS["CES", "delta"])} & \Sexpr{pprint(cesuUS["CES", "sigma"])}\\
           \end{tabular}
@@
   \putFlagUpperRight{US}{0.055}
-\end{frame}
-
-<<Coefs_ZA_CES>>=
-cesqZA <- cesData("ZA", "Q")
-cesxZA <- cesData("ZA", "X")
-@
-\begin{frame}{CES $y$ Predictions} %----------------------------
-  \begin{columns}[c]
-    \column{2.2in}
-      \begin{center}
-        \tiny \cesEqnNarrow \normalsize
-        \vspace{\baselineskip}
-
-        \tiny
-          \begin{tabular}{|c|c|c|c|}\hline
-            $e$ & $\gamma$ & $\lambda$ & $\delta_1$\\
-            \hline
-            $q$ & \Sexpr{cesqZA["CES", "gamma"]} & \Sexpr{cesqZA["CES", "lambda"]} & \Sexpr{cesqZA["CES", "delta_1"]}\\
-            \hline
-            $x$ & \Sexpr{cesxZA["CES", "gamma"]} & \Sexpr{cesxZA["CES", "lambda"]} & \Sexpr{cesxZA["CES", "delta_1"]}\\
-            \hline
-          \end{tabular}
-          \vspace{\baselineskip}
-
-          \begin{tabular}{|c|c|c|c|}\hline
-            $e$ & $\sigma_1$ & $\delta$ & $\sigma$\\
-            \hline
-            $q$ & \Sexpr{cesqZA["CES", "sigma_1"]} & \Sexpr{cesqZA["CES", "delta"]} & \Sexpr{cesqZA["CES", "sigma"]}\\
-            \hline
-            $x$ & \Sexpr{cesxZA["CES", "sigma_1"]} & \Sexpr{cesxZA["CES", "delta"]} & \Sexpr{cesxZA["CES", "sigma"]}\\
-            \hline
-          \end{tabular}
-        \normalsize
-      \end{center}
-    \column{2.2in}
-<<Results_Graph_ZA_CES, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-createCESLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
-@
-  \end{columns}
-  % Including at bottom of frame so as not to push other material downward in the frame.
-  \putFlagUpperRight{ZA}{0.055}
 \end{frame}
@@
     \small\cesEqn\normalsize\\
-    \includegraphics<1>[height=2.5in]{figure_other/CI-delta-1.pdf}
-    \includegraphics<2>[height=2.5in]{figure_other/CI-delta-2.pdf}
-    \includegraphics<3>[height=2.5in]{figure_other/CI-delta-3.pdf}
-    \includegraphics<4>[height=2.5in]{figure_other/CI-delta-4.pdf}
+    \includegraphics[height=2.5in]{figure_other/CI-delta.pdf}
   \end{center}
@@
 
-\begin{frame}{$CI_{\sigma}$ and $\sigma$ in CES} %----------------------------
-  \begin{center}
-    \small\cesEqn\normalsize\\
-    \includegraphics<1>[height=2.5in]{figure_other/CI-sigma-1.pdf}
-    \includegraphics<2>[height=2.5in]{figure_other/CI-sigma-2.pdf}
-    \includegraphics<3>[height=2.5in]{figure_other/CI-sigma-3.pdf}
-    \includegraphics<4>[height=2.5in]{figure_other/CI-sigma-4.pdf}
-  \end{center}
-\end{frame}
-
-\begin{frame}{$CI_{\sigma}$ vs. $\sigma$ for CES with $Q$} %----------------------------
-<<CI_sigma_vs_sigma_Graph, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5>>=
-CIvsParamPlot(model="CES", param="sigma", energyType="Q")
-@
-\end{frame}
-
 \begin{frame}{Implications from CES} %----------------------------
@@
   \begin{itemize}
-    \item{kl and e are complements, sigma small where it is distinguishable.}
-    \item{Direct energy input to economy ($q$) is unimportant as a CES predictor of economic output ($y$), because delta is close to 1.0}
+    \item{Where significant, $\delta$ is close to 1.0}
+    \item{Direct energy input to economy ($q$) is unimportant as a CES predictor of economic output ($y$)}
   \end{itemize}
@@
 cdxZA <- cobbDouglasData("ZA", "X")
-pprint <- function(num, digits = 4){
-  out <- formatC(num, digit=digits, format="f")
-  return(out)
-}
 @
@@
             \hline
-                  & \Sexpr{pprint(cdZA["CD", "lambda"])} & \Sexpr{cdZA["CD", "alpha"]} & \Sexpr{cdZA["CD", "beta"]} & \Sexpr{pprint(cdZA["CD", "gamma"])}\\
-            \hline
-            $q$   & \Sexpr{cdqZA["CD", "lambda"]} & \Sexpr{cdqZA["CD", "alpha"]} & \Sexpr{pprint(cdqZA["CD", "beta"])} & \Sexpr{cdqZA["CD", "gamma"]}\\
-            \hline
-            $x$   & \Sexpr{cdxZA["CD", "lambda"]} & \Sexpr{cdxZA["CD", "alpha"]} & \Sexpr{pprint(cdxZA["CD", "beta"])} & \Sexpr{cdxZA["CD", "gamma"]}\\
+                  & \Sexpr{pprint(cdZA["CD", "lambda"], digits=4)} & \Sexpr{pprint(cdZA["CD", "alpha"])} & \Sexpr{pprint(cdZA["CD", "beta"])} & \Sexpr{pprint(cdZA["CD", "gamma"])}\\
+            \hline
+            $q$   & \Sexpr{pprint(cdqZA["CD", "lambda"], digits=4)} & \Sexpr{pprint(cdqZA["CD", "alpha"])} & \Sexpr{pprint(cdqZA["CD", "beta"])} & \Sexpr{pprint(cdqZA["CD", "gamma"])}\\
+            \hline
+            $x$   & \Sexpr{pprint(cdxZA["CD", "lambda"], digits=4)} & \Sexpr{pprint(cdxZA["CD", "alpha"])} & \Sexpr{pprint(cdxZA["CD", "beta"])} & \Sexpr{pprint(cdxZA["CD", "gamma"])}\\
             \hline
@@
 
+<<Coefs_ZA_CES>>=
+cesqZA <- cesData("ZA", "Q")
+cesxZA <- cesData("ZA", "X")
+@
+\begin{frame}{CES $y$ Predictions} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+      \begin{center}
+        \tiny \cesEqnNarrow \normalsize
+        \vspace{\baselineskip}
+
+        \tiny
+          \begin{tabular}{|c|c|c|c|}\hline
+            $e$ & $\gamma$ & $\lambda$ & $\delta_1$\\
+            \hline
+            $q$ & \Sexpr{pprint(cesqZA["CES", "gamma"])} & \Sexpr{pprint(cesqZA["CES", "lambda"], digits=4)} & \Sexpr{pprint(cesqZA["CES", "delta_1"])}\\
+            \hline
+            $x$ & \Sexpr{pprint(cesxZA["CES", "gamma"])} & \Sexpr{pprint(cesxZA["CES", "lambda"], digits=4)} & \Sexpr{pprint(cesxZA["CES", "delta_1"])}\\
+            \hline
+          \end{tabular}
+          \vspace{\baselineskip}
+
+          \begin{tabular}{|c|c|c|c|}\hline
+            $e$ & $\sigma_1$ & $\delta$ & $\sigma$\\
+            \hline
+            $q$ & \Sexpr{pprint(cesqZA["CES", "sigma_1"])} & \Sexpr{pprint(cesqZA["CES", "delta"])} & \Sexpr{pprint(cesqZA["CES", "sigma"])}\\
+            \hline
+            $x$ & \Sexpr{pprint(cesxZA["CES", "sigma_1"])} & \Sexpr{pprint(cesxZA["CES", "delta"])} & \Sexpr{pprint(cesxZA["CES", "sigma"])}\\
+            \hline
+          \end{tabular}
+        \normalsize
+      \end{center}
+    \column{2.2in}
+<<Results_Graph_ZA_CES, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+createCESLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{ZA}{0.055}
+\end{frame}
+
+\begin{frame}{$CI_{\sigma}$ and $\sigma$ in CES} %----------------------------
+  \begin{center}
+    \small\cesEqn\normalsize\\
+    \includegraphics[height=2.5in]{figure_other/CI-sigma.pdf}
+  \end{center}
+\end{frame}
+
+\begin{frame}{$CI_{\sigma}$ vs. $\sigma$ for CES with $Q$} %----------------------------
+<<CI_sigma_vs_sigma_Graph, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5>>=
+CIvsParamPlot(model="CES", param="sigma", energyType="Q")
+@
+\end{frame}
+
 \end{document} %**************************************************

### 2013-03-26 EconGrowth-R-Functions.Rnw
Now added LINEX predictions.

@@
                    ylab = "$\\gamma$",
-                   zlab = list(label="$SSE$", rot=90),
+                   zlab = list(label="$SSE_y$", rot=90),
                    scales = list(arrows=FALSE, 
@@
     colnames(df) <- c("a_0", "c_t")
-    rownames(df) <- c("+95% CI", "CDe", "-95% CI")
+    rownames(df) <- c("+95% CI", "LINEX", "-95% CI")
     return(df)

### 2013-03-26 EconGrowthSeminar.Rnw
Now added LINEX predictions.

@@
       \hline
-      \multirow{2}{*}{Petrol}     & \includegraphics[height=0.11in]{flag/flag_SA.png} & SA & Saudo Arabia  \\
+      \multirow{2}{*}{Petrol}     & \includegraphics[height=0.11in]{flag/flag_SA.png} & SA & Saudi Arabia  \\
                                   & \includegraphics[height=0.11in]{flag/flag_IR.png} & IR & Iran          \\
@@
   \end{columns}
+  \putat{flag/flag_US.png}{0.055}{-0.73in}{1.0in} % US flag
+  \putat{flag/flag_CN.png}{0.055}{ 1.50in}{1.0in} % CN flag
 \end{frame}
@@
   \end{columns}
+  \putat{flag/flag_ZA.png}{0.055}{-0.73in}{1.0in} % US flag
+  \putat{flag/flag_SA.png}{0.055}{ 1.50in}{1.0in} % CN flag
 \end{frame}
@@
 @
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{US}{0.055}  
+\end{frame}
+
+<<Coefs_US_SF>>=
+sfUSK <- coef(singleFactorModel("US", "K"))
+sfUSL <- coef(singleFactorModel("US", "L"))
+sfUSQ <- coef(singleFactorModel("US", "Q"))
+sfUSX <- coef(singleFactorModel("US", "X"))
+sfUSU <- coef(singleFactorModel("US", "U"))
+@
+\begin{frame}{Single-Factor $y$ Predictions} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+      \begin{center}
+        \sfEqn
+        \vspace{\baselineskip}
+
+        \tiny
+          \begin{tabular}{|c|c|c|}\hline
+            $f$   & $\lambda$                & $m$\\
+            \hline
+            $k$   & \Sexpr{sfUSK["lambda"]}  & \Sexpr{sfUSK["m"]}\\
+            \hline
+            $l$   & \Sexpr{sfUSL["lambda"]}  & \Sexpr{sfUSL["m"]}\\
+            \hline
+            $q$   & \Sexpr{sfUSQ["lambda"]}  & \Sexpr{sfUSQ["m"]}\\
+            \hline
+            $x$   & \Sexpr{sfUSX["lambda"]}  & \Sexpr{sfUSX["m"]}\\
+            \hline
+            $u$   & \Sexpr{sfUSU["lambda"]}  & \Sexpr{sfUSU["m"]}\\
+            \hline
+          \end{tabular}
+        \normalsize
+      \end{center}
+    \column{2.2in}
+<<Results_Graph_US_SF, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+createSFLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
   % Including at bottom of frame so as not to push other material downward in the frame.
@@
 
-\begin{frame}{Grid Search Over $\gamma$}{SA Cobb-Douglas with $Q$} %----------------------------
-<<CDeGammaGraphsSA, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
-  cdeGridGraph("SA", "Q", textScaling=0.8)
-@
-  % Including at bottom of frame so as not to push other material downward in the frame.
-  \putFlagUpperRight{SA}{0.055}
+\begin{frame}{Grid Search Over $\gamma$}{UK Cobb-Douglas with $Q$} %----------------------------
+<<CDeGammaGraphsUK, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
+  cdeGridGraph("UK", "Q", textScaling=0.8)
+@
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{UK}{0.045}
 \end{frame}
@@
 
+<<Coefs_UK_CD>>=
+cdUK <- cobbDouglasData("UK")
+cdqUK <- cobbDouglasData("UK", "Q")
+cdxUK <- cobbDouglasData("UK", "X")
+cduUK <- cobbDouglasData("UK", "U")
+@
+\begin{frame}{Cobb-Douglas $y$ Predictions} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+      \begin{center}
+        \cdeEqn
+        \vspace{\baselineskip}
+
+        \tiny
+          \begin{tabular}{c|c c c c}
+            $e$ & $\lambda$ & $\alpha$ & $\beta$ & $\gamma$\\
+            \hline
+                  & \Sexpr{pprint(cdUK["CD", "lambda"], digits=4)} & \Sexpr{pprint(cdUK["CD", "alpha"])} & \Sexpr{pprint(cdUK["CD", "beta"])} & \Sexpr{pprint(cdUK["CD", "gamma"])}\\
+            \hline
+            $q$   & \Sexpr{pprint(cdqUK["CD", "lambda"], digits=4)} & \Sexpr{pprint(cdqUK["CD", "alpha"])} & \Sexpr{pprint(cdqUK["CD", "beta"])} & \Sexpr{pprint(cdqUK["CD", "gamma"])}\\
+            \hline
+            $x$   & \Sexpr{pprint(cdxUK["CD", "lambda"], digits=4)} & \Sexpr{pprint(cdxUK["CD", "alpha"])} & \Sexpr{pprint(cdxUK["CD", "beta"])} & \Sexpr{pprint(cdxUK["CD", "gamma"])}\\
+            \hline
+            $u$   & \Sexpr{pprint(cduUK["CD", "lambda"], digits=4)} & \Sexpr{pprint(cduUK["CD", "alpha"])} & \Sexpr{pprint(cduUK["CD", "beta"])} & \Sexpr{pprint(cduUK["CD", "gamma"])}\\
+          \end{tabular}
+        \normalsize
+      \end{center}
+    \column{2.2in}
+<<Results_Graph_UK_CD, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight>>=
+createCDLatticeGraph("UK", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{UK}{0.055}
+\end{frame}
+
 \begin{frame}{Benefit to Including Energy?}  %----------------------------
@@
   \putFlagUpperRight{US}{0.055}
+\end{frame}
+
+\begin{frame}{Benefit to Including Energy?}  %----------------------------
+<<UK_Partial_Residuals_Plot, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
+partialResidualPlot("UK", "Q", textScaling=textScaleForGraphs)
+@
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{UK}{0.055}
 \end{frame}
@@
   \end{center}
+\end{frame}
+
+<<Coefs_US_LINEX>>=
+linexqUS <- linexData("US", "Q")
+linexxUS <- linexData("US", "X")
+linexuUS <- linexData("US", "U")
+@
+\begin{frame}{LINEX $y$ Predictions} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+      \begin{center}
+        \linexEqn
+
+        \vspace{\baselineskip}
+
+        \tiny
+          \begin{tabular}{c|c c}
+            $e$ & $a_0$ & $c_t$\\
+            \hline
+            $q$ & \Sexpr{pprint(linexqUS["LINEX", "a_0"])} & \Sexpr{pprint(linexqUS["LINEX", "c_t"])}\\
+            \hline
+            $x$ & \Sexpr{pprint(linexxUS["LINEX", "a_0"])} & \Sexpr{pprint(linexxUS["LINEX", "c_t"])}\\
+            \hline
+            $u$ & \Sexpr{pprint(linexuUS["LINEX", "a_0"])} & \Sexpr{pprint(linexuUS["LINEX", "c_t"])}\\
+          \end{tabular}
+        \normalsize
+      \end{center}
+    \column{2.2in}
+<<Results_Graph_US_LINEX, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight>>=
+createLINEXLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{US}{0.055}
 \end{frame}
@@
 
-<<Coefs_US_SF>>=
-sfUSK <- coef(singleFactorModel("US", "K"))
-sfUSL <- coef(singleFactorModel("US", "L"))
-sfUSQ <- coef(singleFactorModel("US", "Q"))
-sfUSX <- coef(singleFactorModel("US", "X"))
-sfUSU <- coef(singleFactorModel("US", "U"))
-@
-\begin{frame}{Single-Factor $y$ Predictions} %----------------------------
-  \begin{columns}[c]
-    \column{2.2in}
-      \begin{center}
-        \sfEqn
-        \vspace{\baselineskip}
-
-        \tiny
-          \begin{tabular}{|c|c|c|}\hline
-            $f$   & $\lambda$                & $m$\\
-            \hline
-            $k$   & \Sexpr{sfUSK["lambda"]}  & \Sexpr{sfUSK["m"]}\\
-            \hline
-            $l$   & \Sexpr{sfUSL["lambda"]}  & \Sexpr{sfUSL["m"]}\\
-            \hline
-            $q$   & \Sexpr{sfUSQ["lambda"]}  & \Sexpr{sfUSQ["m"]}\\
-            \hline
-            $x$   & \Sexpr{sfUSX["lambda"]}  & \Sexpr{sfUSX["m"]}\\
-            \hline
-            $u$   & \Sexpr{sfUSU["lambda"]}  & \Sexpr{sfUSU["m"]}\\
-            \hline
-          \end{tabular}
-        \normalsize
-      \end{center}
-    \column{2.2in}
-<<Results_Graph_US_SF, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-createSFLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
-@
-  \end{columns}
-  % Including at bottom of frame so as not to push other material downward in the frame.
-  \putFlagUpperRight{US}{0.055}
-\end{frame}
-
 \begin{frame}{Cobb-Douglas (without Energy)} %----------------------------
@@
 
-\begin{frame}{Grid Search Over $\gamma$}{UK Cobb-Douglas with $Q$} %----------------------------
-<<CDeGammaGraphsUK, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
-  cdeGridGraph("UK", "Q", textScaling=0.8)
-@
-  % Including at bottom of frame so as not to push other material downward in the frame.
-  \putFlagUpperRight{UK}{0.045}
-\end{frame}
-
 \begin{frame}{Grid Search Over $\gamma$}{ZA Cobb-Douglas with $Q$} %----------------------------
@@
   \putFlagUpperRight{ZA}{0.055}
+\end{frame}
+
+\begin{frame}{Grid Search Over $\gamma$}{SA Cobb-Douglas with $Q$} %----------------------------
+<<CDeGammaGraphsSA, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
+  cdeGridGraph("SA", "Q", textScaling=0.8)
+@
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{SA}{0.055}
 \end{frame}

### 2013-03-26 EconGrowthSeminar.Rnw
Now including "comments" frames about each model.

@@
 
+\begin{frame}{Comments on Single-factor Model Equation} %----------------------------
+    \begin{center} \sfEqn \end{center}
+    \vspace{\baselineskip}
+
+    \begin{itemize}
+      \item{Time-dependent technology term: $\mathrm{e}^{\lambda(t-t_0)}$}
+      \begin{itemize}
+        \item{Represents the irrepressible ``progress'' of technology}
+        \item{Is independent of factor of production ($f$)}
+      \end{itemize}
+      \item{Use for illustration purposes here}
+      \item{Example: \citet{Nel:2009wq} use $f$ = $q$}
+      \item{Parameters estimated by \texttt{nls} function in \texttt{R}}
+    \end{itemize}
+\end{frame}
+
 \begin{frame}{Curve-fitting as Optimization} %----------------------------
@@
 \end{frame}
+
+\subsection[Cobb-Douglas]{Evaluation of Cobb-Douglas} %+++++++++++++++++++++++++++++++++++++++
 
@@
 
+\begin{frame}{Comments on Cobb-Douglas Model Equation} %----------------------------
+  \begin{center} \cdeEqn \end{center}
+  \begin{itemize}
+    \item{Time-dependent technology term: $\mathrm{e}^{\lambda(t-t_0)}$}
+    \begin{itemize}
+      \item{Represents the irrepressible ``progress'' of technology}
+      \item{Is independent of factors of production ($k$, $l$, and $e$)}
+    \end{itemize}
+    \item{$k$, $l$, and $e$ factors of production ``blend'' with $\alpha + \beta + \gamma = 1$}
+    \item{Example: \citet{Froling:2009vo}}
+  \end{itemize}
+\end{frame}
+
 \begin{frame}{Parameter Estimation for Cobb-Douglas With Energy} %----------------------------
@@
     \item{Objective: determine $\lambda$, $\alpha$, $\beta$, and $\gamma$ that best fits historical data}
-    \item{Almost identical to Cobb-Douglas without energy}
-    \item{Perform grid search over $\gamma$}
-    \item{Re-estimate $\lambda$, $\alpha$, and $\beta$ at each value of $\gamma$}
+    \item{Perform grid search over $\gamma$: Re-estimate $\lambda$, $\alpha$, and $\beta$ at each value of $\gamma$}
     \item{Respect sum constraint: $\alpha + \beta + \gamma = 1$}
     \item{Respect absolute constraints: $0 \leq \alpha, \beta, \gamma \leq 1$} (not yet)
+    \item{Parameters estimated by \texttt{nls} function in \texttt{R}}
   \end{itemize}
@@
 \end{frame}
+
+\subsection[CES]{Evaluation of CES} %+++++++++++++++++++++++++++++++++++++++
 
@@
 
+\begin{frame}{Comments on CES Model Equation} %----------------------------
+  \begin{center} \small \cesEqn \normalsize \end{center}
+  \begin{itemize}
+    \item{Time-dependent technology term: $\mathrm{e}^{\lambda(t-t_0)}$}
+    \begin{itemize}
+      \item{Represents the irrepressible ``progress'' of technology}
+      \item{Is independent of factors of production ($k$, $l$, and $e$)}
+    \end{itemize}
+    \item{$\delta$: split between ($kl$) and ($e$)}
+    \item{$\sigma$: elasticity of substitution ($0.0 \leq \sigma \leq 1.0$)}
+    \begin{itemize}
+      \item{$\sigma$ ******* rightarrow******* 0: ($kl$) and ($e$) are complementary}
+      \item{$\sigma$ ******* rightarrow******* 1: ($kl$) and ($e$) are substitutes}
+    \end{itemize}
+    \item{Example: \citet{Stern:2012ey}}
+    \item{Parameters estimated by \texttt{cesEst} function in \texttt{R}'s \texttt{micEcon} package}
+  \end{itemize}
+\end{frame}
+
 <<Coefs_US_CES>>=
@@
 
+\subsection[LINEX]{Evaluation of LINEX} %+++++++++++++++++++++++++++++++++++++++
+
 \minorSeparator{LINEX} %----------------------------
@@
 
+\begin{frame}{Comments on LINEX Model Equation} %----------------------------
+  \begin{center} \linexEqn \end{center}
+  \begin{itemize}
+    \item{Derived from thermodynamic considerations}
+    \item{Foundation is energy ($e$)}
+    \item{No time-dependent technology term}
+    \item{Ratios among $k$, $l$, and $e$ ``trim'' energy}
+    \item{Example: \citet{Warr:2006hc}}
+    \item{Parameters estimated by \texttt{nls} function in \texttt{R}}
+  \end{itemize}
+\end{frame}
+
 <<Coefs_US_LINEX>>=
@@
 
-\begin{frame}{Example LINEX Fit} %----------------------------
-  Heun complete
+<<Coefs_UK_LINEX>>=
+linexqUK <- linexData("UK", "Q")
+linexxUK <- linexData("UK", "X")
+linexuUK <- linexData("UK", "U")
+@
+\begin{frame}{LINEX $y$ Predictions} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+      \begin{center}
+        \linexEqn
+
+        \vspace{\baselineskip}
+
+        \tiny
+          \begin{tabular}{c|c c}
+            $e$ & $a_0$ & $c_t$\\
+            \hline
+            $q$ & \Sexpr{pprint(linexqUK["LINEX", "a_0"])} & \Sexpr{pprint(linexqUK["LINEX", "c_t"])}\\
+            \hline
+            $x$ & \Sexpr{pprint(linexxUK["LINEX", "a_0"])} & \Sexpr{pprint(linexxUK["LINEX", "c_t"])}\\
+            \hline
+            $u$ & \Sexpr{pprint(linexuUK["LINEX", "a_0"])} & \Sexpr{pprint(linexuUK["LINEX", "c_t"])}\\
+          \end{tabular}
+        \normalsize
+      \end{center}
+    \column{2.2in}
+<<Results_Graph_UK_LINEX, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight>>=
+createLINEXLatticeGraph("UK", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{UK}{0.055}
+\end{frame}
+
+<<Coefs_ZA_LINEX>>=
+linexqZA <- linexData("ZA", "Q")
+linexxZA <- linexData("ZA", "X")
+@
+\begin{frame}{LINEX $y$ Predictions} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+      \begin{center}
+        \linexEqn
+
+        \vspace{\baselineskip}
+
+        \tiny
+          \begin{tabular}{c|c c}
+            $e$ & $a_0$ & $c_t$\\
+            \hline
+            $q$ & \Sexpr{pprint(linexqZA["LINEX", "a_0"])} & \Sexpr{pprint(linexqZA["LINEX", "c_t"])}\\
+            \hline
+            $x$ & \Sexpr{pprint(linexxZA["LINEX", "a_0"])} & \Sexpr{pprint(linexxZA["LINEX", "c_t"])}\\
+          \end{tabular}
+        \normalsize
+      \end{center}
+    \column{2.2in}
+<<Results_Graph_ZA_LINEX, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight>>=
+createLINEXLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{ZA}{0.055}
+\end{frame}
+
+<<Coefs_SA_LINEX>>=
+linexqSA <- linexData("SA", "Q")
+linexxSA <- linexData("SA", "X")
+@
+\begin{frame}{LINEX $y$ Predictions} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+      \begin{center}
+        \linexEqn
+
+        \vspace{\baselineskip}
+
+        \tiny
+          \begin{tabular}{c|c c}
+            $e$ & $a_0$ & $c_t$\\
+            \hline
+            $q$ & \Sexpr{pprint(linexqSA["LINEX", "a_0"])} & \Sexpr{pprint(linexqSA["LINEX", "c_t"])}\\
+            \hline
+            $x$ & \Sexpr{pprint(linexxSA["LINEX", "a_0"])} & \Sexpr{pprint(linexxSA["LINEX", "c_t"])}\\
+          \end{tabular}
+        \normalsize
+      \end{center}
+    \column{2.2in}
+<<Results_Graph_SA_LINEX, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight>>=
+createLINEXLatticeGraph("SA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{SA}{0.055}
+\end{frame}
+
+\begin{frame}{95\% Confidence Intervals}{LINEX with $q$} %----------------------------
+<<LINEXq_Params_Graph, fig.width=presentationGraph1ColWidth*1.8, fig.height=presentationGraph1RowHeight*1.8>>=
+createLINEXParamsGraph("Q")
+@  
+\end{frame}
+
+\begin{frame}{Implications from LINEX} %----------------------------
+  \begin{center}\linexEqn\end{center}
+  \vspace{\baselineskip}
+
+  \begin{itemize}
+    \item{LINEX parameters $a_0$ and $c_t$ are significant (different from 0.0) for most countries}
+    \item{Direct energy input to economy ($q$) is important as a LINEX predictor of economic output ($y$)}
+  \end{itemize}
 \end{frame}
@@
   \begin{itemize}
-  \item{Including energy is unwarranted \\
+  \item{Including energy in Cobb-Douglas and CES production functions is unwarranted \\
         \scriptsize
-        Little statistical evidence that including energy in production functions improves stastical properties of fitting parameters.
+        Statistical evidence indicates that energy parameters are not significant for most countries \\
+        Why? Energy is \emph{always already} embedded in capital stock ($K$) and labor ($L$), so including energy is unnecessary.
         \normalsize}
-  \item{Including energy is unnecessary \\
+  \item{Including energy in LINEX production function is required \\
         \scriptsize
-        Energy is \emph{always already} embedded in capital stock ($K$) and labor ($L$).
+        The foundation of LINEX is an energy term.\\
+        Statistical evidence indicates that LINEX parameters $a_0$ and $c_t$ are significant for most countries. \\
+        LINEX fits overall are worse than Cobb-Douglas or CES.
         \normalsize}
   \vspace{\baselineskip}
-  \item{Need a modeling method that captures energy's embeddedness \\
+  \pause
+
+  \item{Need a modeling method (that is better than LINEX) that captures energy's embeddedness \\
         \scriptsize
-        System dynamics modeling
+        System dynamics modeling?
         \normalsize}
@@
     \vspace{\baselineskip}
-    \item{Complete paper}
+    \item{Complete paper for \emph{Energy Economics}}
   \end{itemize}  

### 2013-03-28 EconGrowth-R-Functions.Rnw
Added a 2-questions slide after the CD model in the presentation. Also trying (unsuccessfully) to add a point to the 3-D SF graph.

@@
 #   countryAbbrev: 2-letter country code (upper case)
-#   factor: the factor of production you want to use in the single-factor model.
+#   factor: the factor of production you want to use in the single-factor model. One of K, L, Q, X, or U
 ##
@@
 
+  # Get information about the optimum point, the point where SSE is minimized
+  coefs <- coef(model)
+  lambda_opt <- coefs["lambda"]
+  gamma_opt <- coefs["gamma"]
+  #sse_opt <- ???????
+
   sse <- c(1:(nRowLambda*nRowM)) # Build a bogus vector at the start
@@
   # Create the lattice graph
+#   fig <- wireframe(sse ~ lambda * m,
+#                    data = dataFor3DGraph,
+#                    screen = list(z = -20, x = -55),
+#                    xlab = "$\\lambda$",
+#                    ylab = "$\\gamma$",
+#                    zlab = list(label="$SSE_y$", rot=90),
+#                    scales = list(arrows=FALSE, 
+#                                  cex=0.45, 
+#                                  col="black", 
+#                                  tck=0.8,
+#                                  x=list(at=c(0.00, 0.01, 0.02, 0.03)),
+#                                  y=list(at=c(0.0, 0.5, 1.0)),
+#                                  z=list(at=c(10, 20, 30))
+#                                  ),
+#                    xlim = c(0.0, 0.04), # lambda axis
+#                    ylim = c(0.0, 1.0), # gamma axis
+#                    zlim = c(0, 30) # sse axis
+#                    )
+
   fig <- wireframe(sse ~ lambda * m,

### 2013-03-28 EconGrowth.Rnw
Added a 2-questions slide after the CD model in the presentation. Also trying (unsuccessfully) to add a point to the 3-D SF graph.

--- 2013-03-19 EconGrowth.Rnw
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+<<test3dPlot, eval=TRUE>>=
+sf3DSSEGraph("US", "Q")
+@
 

### 2013-03-28 EconGrowthSeminar.Rnw
Added a 2-questions slide after the CD model in the presentation. Also trying (unsuccessfully) to add a point to the 3-D SF graph.

@@
 \newcommand{\lambdaRow}{$\lambda$ & technological progress}
-\newcommand{\alphaRow}{$\alpha$ & ``strength'' of capital}
-\newcommand{\betaRow}{$\beta$ & ``strength'' of labor}
-\newcommand{\gammaRow}{$\gamma$ & ``strength'' of energy}
+\newcommand{\alphaRow}{$\alpha$ & ``influence'' of capital}
+\newcommand{\betaRow}{$\beta$ & ``influence'' of labor}
+\newcommand{\gammaRow}{$\gamma$ & ``influence'' of energy}
 
@@
   \pause
-  \begin{center}Simplification: 1 type of energy ($Q$) for this presentation\end{center}
+  \begin{center}Simplification: One type of energy ($Q$) for this presentation\end{center}
 \end{frame}
@@
       \lambdaRow\\
-      $m$ & ``strength'' of factor $f$\\
+      $m$ & ``influence'' of factor $f$\\
       \hline
@@
     \begin{itemize}
-      \item{Time-dependent technology term: $\mathrm{e}^{\lambda(t-t_0)}$}
+      \item{$\mathrm{e}^{\lambda(t-t_0)}$: Time-dependent technology term}
       \begin{itemize}
@@
       \end{itemize}
-      \item{Use for illustration purposes here}
+      \item{Used for illustration purposes here}
       \item{Example: \citet{Nel:2009wq} use $f$ = $q$}
@@
 \begin{frame}{$SSE$ Minimization}{US single-factor with $Q$} %---------------------------- 
-<<3D_Graph_US_SF_Q, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
+<<3D_Graph_US_SF_Q, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3, eval=TRUE>>=
 sf3DSSEGraph("US", "Q")
@@
 @
-\begin{frame}{Single-Factor $y$ Predictions} %----------------------------
+\begin{frame}{Single-factor (with $q$) Predictions for $y$} %----------------------------
   \begin{columns}[c]
@@
   \putFlagUpperRight{US}{0.055}
+\end{frame}
+
+\begin{frame}{95\% Confidence Intervals}{Single-factor with $Q$} %----------------------------
+<<SF_Params_Graph_Q, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
+createSFParamsGraph("Q")
+@  
 \end{frame}
@@
   \begin{itemize}
-    \item{Time-dependent technology term: $\mathrm{e}^{\lambda(t-t_0)}$}
-    \begin{itemize}
-      \item{Represents the irrepressible ``progress'' of technology}
+    \item{$\mathrm{e}^{\lambda(t-t_0)}$: Time-dependent technology term}
+    \begin{itemize}
+      \item{Represents the ``irrepressible'' ``progress'' of technology}
       \item{Is independent of factors of production ($k$, $l$, and $e$)}
@@
 @  
+\end{frame}
+
+\begin{frame}{Two Important Questions for\\Cobb-Douglas Model} %----------------------------
+  \begin{center}
+    \cdeEqn
+  \end{center}
+  \begin{itemize}
+    \item{Is energy important for this economy?\\Yes, if $\gamma$ not small.}
+    \vspace{\baselineskip}
+
+    \item{Are we sure? (Is energy statistically significant?)\\Yes, if $CI_{\gamma}$ doesn't cross 0.0.}
+  \end{itemize}
 \end{frame}
@@
       $\delta_1$   &   split between ($k$) and ($l$)\\
-      $\rho_1$     &   ``strength'' of ($k$) vs. ($l$)\\
+      $\rho_1$     &   ``influence'' of ($k$) vs. ($l$)\\
       $\delta$   &   split between ($kl$) and ($e$)\\
-      $\rho$     &   ``strength'' of ($kl$) vs. ($e$)\\
+      $\rho$     &   ``influence'' of ($kl$) vs. ($e$)\\
       \hline
@@
   \begin{itemize}
-    \item{Time-dependent technology term: $\mathrm{e}^{\lambda(t-t_0)}$}
-    \begin{itemize}
-      \item{Represents the irrepressible ``progress'' of technology}
-      \item{Is independent of factors of production ($k$, $l$, and $e$)}
-    \end{itemize}
+    \item{$\mathrm{e}^{\lambda(t-t_0)}$: Time-dependent technology term}
     \item{$\delta$: split between ($kl$) and ($e$)}
-    \item{$\sigma$: elasticity of substitution ($0.0 \leq \sigma \leq 1.0$)}
-    \begin{itemize}
-      \item{$\sigma$ ******* rightarrow******* 0: ($kl$) and ($e$) are complementary}
-      \item{$\sigma$ ******* rightarrow******* 1: ($kl$) and ($e$) are substitutes}
+    \item{$\sigma \equiv \frac{1}{1+\rho}$: elasticity of substitution ($0 \leq \sigma \leq 1$)}
+    \begin{itemize}
+      \item{$\sigma \rightarrow 0$: ($kl$) and ($e$) are complementary}
+      \item{$\sigma \rightarrow 1$: ($kl$) and ($e$) are substitutes}
     \end{itemize}
@@
 
+\begin{frame}{95\% Confidence Intervals}{Single-factor with $K$} %----------------------------
+<<SF_Params_Graph_K, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
+createSFParamsGraph("K")
+@  
+\end{frame}
+
+\begin{frame}{95\% Confidence Intervals}{Single-factor with $L$} %----------------------------
+<<SF_Params_Graph_L, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
+createSFParamsGraph("L")
+@  
+\end{frame}
+
+\minorSeparator{Cobb-Douglas Model}
+
 \begin{frame}{Cobb-Douglas (without Energy)} %----------------------------
@@
 
-\begin{frame}{95\% Confidence Intervals}{Single-factor with $K$} %----------------------------
-<<SF_Params_Graph_K, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
-createSFParamsGraph("K")
-@  
-\end{frame}
-
-\begin{frame}{95\% Confidence Intervals}{Single-factor with $L$} %----------------------------
-<<SF_Params_Graph_L, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
-createSFParamsGraph("L")
-@  
-\end{frame}
-
-\begin{frame}{95\% Confidence Intervals}{Single-factor with $Q$} %----------------------------
-<<SF_Params_Graph_Q, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
-createSFParamsGraph("Q")
-@  
-\end{frame}
-
-\minorSeparator{Cobb-Douglas Model}
-
 <<Coefs_ZA_CD>>=

### 2013-03-29 EconGrowthSeminar.Rnw
Now including tables and frames for sources of economic data. Also including graphics for world bank and BLS.

@@
     \pause
-    \item{But \dots}
+    \item{And yet \dots}
   \end{itemize}
@@
     \item{Economic output ($Y$) is a function of ``factors of production''}
-    \item{Output ($Y$) defined as GDP}
-    \item{All inputs and outputs normalized to initial year (0)}
+    \item{Output ($Y$) measured by GDP}
+    \item{All inputs and outputs normalized to initial year: $y = Y/Y_0, e = E/E_0$, etc.}
   \end{itemize}
@@
     \pause
+
+    Extra credit: reflect dynamics of energy cost share and prices spikes.
+    \vspace{\baselineskip}
+    \pause
+
     \footnotesize
-    \\ No known rigorous, statistical comparative studies of economic growth models for various types of economies. 
+    No known rigorous, statistical comparative studies of economic growth models for various types of economies. 
     \normalsize
@@
 
-\minorSeparator{Economic Data}
-
-\begin{frame}{Economic Data} %----------------------------
-  Lucas complete
+\minorSeparator{Sources of Economic Data}
+
+\begin{frame}{Economic Data: Definitions} %----------------------------
+  \begin{itemize}
+    \item{Output ($Y$): the real market value of the total amount of produced goods in an economy (GDP).}
+    \item{Capital Stock ($K$): the real market value of the total amount of goods in an economy used in the production process of output (machines, tools, infrastructure, etc.).}
+    \item{Labor: the number of workers in an economy that produce output.
+Labor can be treated as either the total number of workers in an economy or the total number of hours worked per year in an economy.}
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Sources of Economic Data} %----------------------------
+  \begin{center}
+    \tiny
+    \begin{tabular}{r c|c l}
+      \multirow{3}{*}{WB GEP} & \multirow{3}{*}{\includegraphics[scale=0.07]{figure_other/Figure_World_Bank.png}} & $Y$, $K$ for all countries & \multirow{3}{*}{Real 2005\$} \\
+                              &                          & (1980-2011: US, UK, JP; & \\
+                              &                          & 1991-2011: CN, ZA, SA, IR, TZ, ZM) & \\
+      \hline
+      \multirow{4}{*}{WB WDI} & \multirow{4}{*}{\includegraphics[scale=0.07]{figure_other/Figure_World_Bank.png}} & Pop, Pop < 15 yo,    & \multirow{4}{*}{Total Employment} \\
+                              &                          & Emp/Pop ratio > 15 yo, &                                \\
+                              &                          & used to find $L$, (1991-2011: &                         \\
+                              &                          & CN, ZA, SA, IR, TZ, ZM) &                         \\
+      \hline
+      \multirow{2}{*}{US BLS} & \multirow{2}{*}{\includegraphics[scale=0.07]{figure_other/Figure_BLS.png}} & $L$ for developed countries & Labor hours \\
+                              &                          & (1980-2011: US, UK, JP)     & per year \\ 
+    \end{tabular}
+  \normalsize
+  \end{center}
 \end{frame}
@@
 @  
+\end{frame}
+
+\begin{frame}{Comments on Single-factor Model with $Q$} %----------------------------
+  \begin{itemize}
+    \item{Not typically used for economic modeling. Illustrates confidence intervals.}
+    \vspace{\baselineskip}
+
+    \item{$CI_{\lambda}$ smaller than $CI_{\gamma}$ for all countries}
+  \end{itemize}
 \end{frame}
@@
 
-\begin{frame}{Two Important Questions for\\Cobb-Douglas Model} %----------------------------
+\begin{frame}{Two Important Questions for the\\Cobb-Douglas Model} %----------------------------
   \begin{center}
@@
 
+\begin{frame}{Two Important Questions for\\CES Model} %----------------------------
+  \begin{center}
+    \small \cesEqn \normalsize
+  \end{center}
+  \begin{itemize}
+    \item{Is energy important for this economy?\\Yes, if $\delta$ is not large.}
+    \vspace{\baselineskip}
+
+    \item{Are we sure? (Is energy statistically significant?)\\Yes, if $CI_{\delta}$ doesn't cross 0.0.}
+  \end{itemize}
+\end{frame}
+
 \begin{frame}{$CI_{\delta}$ and $\delta$ in CES} %----------------------------
@@
 
+\begin{frame}{Two Important Questions for\\LINEX Model} %----------------------------
+  \begin{center}
+    \linexEqn
+  \end{center}
+  \begin{itemize}
+    \item{Is energy important for this economy?\\Yes, by definition!}
+    \vspace{\baselineskip}
+
+    \item{Are we sure? Yes, by definition!}
+  \end{itemize}
+\end{frame}
+
 \begin{frame}{95\% Confidence Intervals}{LINEX with $q$} %----------------------------
@@
         \scriptsize
-        Statistical evidence indicates that energy parameters are not significant for most countries \\
-        Why? Energy is \emph{always already} embedded in capital stock ($K$) and labor ($L$), so including energy is unnecessary.
+        Statistical evidence indicates that energy parameters are not significant for most countries \\Why?
+Energy is \emph{always already} embedded in capital stock ($K$) and labor ($L$), so including energy is unnecessary.
         \normalsize}
@@
         \scriptsize
-        The foundation of LINEX is an energy term.\\
-        Statistical evidence indicates that LINEX parameters $a_0$ and $c_t$ are significant for most countries. \\
-        LINEX fits overall are worse than Cobb-Douglas or CES.
+        The foundation of LINEX is an energy term.\\Statistical evidence indicates that LINEX parameters $a_0$ and $c_t$ are significant for most countries.\\LINEX fits overall are worse than Cobb-Douglas or CES.
         \normalsize}

### 2013-03-29 EconGrowthSeminar.Rnw
Changed nomenclature on country groups. Now including slides for Caleb's energy information.

@@
       \hline
-      \multirow{2}{*}{Developing} & \includegraphics[height=0.11in]{flag/flag_CN.png} & CN & China         \\
+      \multirow{2}{*}{BRICS}      & \includegraphics[height=0.11in]{flag/flag_CN.png} & CN & China         \\
                                   & \includegraphics[height=0.11in]{flag/flag_ZA.png} & ZA & South Africa  \\
@@
       \hline
-      \multirow{2}{*}{Malthusian} & \includegraphics[height=0.11in]{flag/flag_TZ.png} & TZ & Tanzania      \\
+      \multirow{2}{*}{LDCs}       & \includegraphics[height=0.11in]{flag/flag_TZ.png} & TZ & Tanzania      \\
                                   & \includegraphics[height=0.11in]{flag/flag_ZM.png} & ZM & Zambia        \\
@@
     \item{Capital Stock ($K$): the real market value of the total amount of goods in an economy used in the production process of output (machines, tools, infrastructure, etc.).}
-    \item{Labor: the number of workers in an economy that produce output.
+    \item{Labor ($L$): the number of workers in an economy that produce output.
 Labor can be treated as either the total number of workers in an economy or the total number of hours worked per year in an economy.}
@@
   \begin{center}
-    \tiny
+    \scriptsize
     \begin{tabular}{r c|c l}
@@
 
-\begin{frame}{Energy Data} %----------------------------
-  Caleb complete
+\begin{frame}{Energy Data: Definitions} %----------------------------
+  \begin{itemize}
+    \item{Thermal Energy ($Q$): The heat content of an energy carrier.}
+    \item{Exergy ($X$): The maximum work that can be extracted from a heat carrier by a process that brings the system into equillibrium with a thermal reservoir (typically the surrounding environment).}
+    \item{Useful Work ($U$): Energy that directly generates economic activity.}
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Energy Flows} %----------------------------
+  Caleb's diagram here
+\end{frame}
+
+\begin{frame}{Sources of Energy Data} %----------------------------
+  Table here.
 \end{frame}

### 2013-03-29 EconGrowthSeminar.Rnw
Now including Caleb's inputs.

@@
     \item{Output ($Y$) measured by GDP}
-    \item{All inputs and outputs normalized to initial year: $y = Y/Y_0, e = E/E_0$, etc.}
+    \item{All factors and outputs indexed to initial year: $y = Y/Y_0, e = E/E_0$, etc.}
   \end{itemize}
@@
 
-\begin{frame}{Economic Data: Definitions} %----------------------------
+\begin{frame}{Economic Definitions} %----------------------------
   \begin{itemize}
@@
     \scriptsize
-    \begin{tabular}{r c|c l}
+    \begin{tabular}{r c c l}
       \multirow{3}{*}{WB GEP} & \multirow{3}{*}{\includegraphics[scale=0.07]{figure_other/Figure_World_Bank.png}} & $Y$, $K$ for all countries & \multirow{3}{*}{Real 2005\$} \\
-                              &                          & (1980-2011: US, UK, JP; & \\
-                              &                          & 1991-2011: CN, ZA, SA, IR, TZ, ZM) & \\
+                              &                          & (1980-2011: Developed; & \\
+                              &                          & 1991-2011: Other) & \\
       \hline
@@
 
-\begin{frame}{Energy Data: Definitions} %----------------------------
+\begin{frame}{Energy Definitions} %----------------------------
   \begin{itemize}
@@
   \end{itemize}
+  \begin{center}Note: indexed $Q$ and $X$ are identical unless energy mix changes significantly. \end{center}
 \end{frame}
@@
 \begin{frame}{Energy Flows} %----------------------------
-  Caleb's diagram here
+  \begin{center}
+    \includegraphics[scale=0.4]{figure_other/Figure_Energy_Sankey.pdf}
+  \end{center}
 \end{frame}
@@
 \begin{frame}{Sources of Energy Data} %----------------------------
-  Table here.
+  \begin{center}
+    \scriptsize
+    \begin{tabular}{r c c l}
+      \multirow{3}{*}{IEA} & \multirow{3}{*}{\includegraphics[scale=0.20]{figure_other/Figure_IEA.png}} & Coal, Oil, Petroleum, & \multirow{3}{*}{GJ/year} \\
+                              &                          & Nat. gas, Nuclear, & \\
+                              &                          & Renewables & \\
+      \hline
+      \multirow{4}{*}{FAOStat} & \multirow{4}{*}{\includegraphics[scale=0.07]{figure_other/Figure_FAOStat.png}} & Fuel wood,    & \multirow{4}{*}{GJ/year} \\
+                              &                          & Available livestock &                                \\
+                              &                          & (1980-2011: Developed; &                         \\
+                              &                          & 1991-2011: Other) &                         \\
+      \hline
+      \multirow{2}{*}{REXS} & \multirow{2}{*}{\includegraphics[scale=0.05]{figure_other/Figure_Warr.png}} & Energy allocation factors. &  \\
+                              &                          & (1980-2000: Developed)     & \\ 
+    \end{tabular}
+    \normalsize
+  \end{center}
 \end{frame}
@@
 \begin{frame}{$SSE$ Minimization}{US single-factor with $Q$} %---------------------------- 
-<<3D_Graph_US_SF_Q, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3, eval=TRUE>>=
+<<3D_Graph_US_SF_Q, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
 sf3DSSEGraph("US", "Q")
@@
 
-\begin{frame}{Benefit to Including Energy?}  %----------------------------
+\begin{frame}{Beneficial to Include Energy?}  %----------------------------
 <<US_Partial_Residuals_Plot, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
@@
 
-\begin{frame}{Benefit to Including Energy?}  %----------------------------
+\begin{frame}{Beneficial to Include Energy?}  %----------------------------
 <<UK_Partial_Residuals_Plot, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=

### 2013-03-29 EconGrowthSeminar.Rnw
Many minor edits. Now including better understanding of LINEX model.

@@
 % The equation for a linex model
-\newcommand{\linexEqn}{$y = e \: \mathrm{e}^{\left[a_0 \left(2 - \frac{l + e}{k} \right) + a_0 c_t \left(\frac{l}{e} - 1 \right)\right]}$}
+% \newcommand{\linexEqn}{$y = e \: \mathrm{e}^{\left[a_0 \left(2 - \frac{l + e}{k} \right) + a_0 c_t \left(\frac{l}{e} - 1 \right)\right]}$}
+
+\newcommand{\linexEqn}{$y = \mathrm{e}^{\left[a_0 \left(2 - \frac{l + e}{k} \right) + a_0 c_t \left(\frac{l}{e} - 1 \right)\right]} \times e$}
 
@@
     10 of last 11 US recessions preceeded by oil price shocks
+    \vspace{\baselineskip}
+
+    \pause
+    \small Exception: mild recession of 1960-1961 \normalsize
   \end{center}
@@
     Which economic growth model best describes (statistically) the role of energy in economic growth for different types of economies?
-    \vspace{\baselineskip}
-    \pause
-
-    Extra credit: reflect dynamics of energy cost share and prices spikes.
-    \vspace{\baselineskip}
-    \pause
+    \pause
+    \vspace{\baselineskip}
 
@@
     \normalsize
+    \pause
+    \vspace{\baselineskip}
+
+    Extra credit: reflect dynamics of energy cost share and prices spikes.
   \end{center}
@@
   \begin{itemize}
-    \item{Output ($Y$): the real market value of the total amount of produced goods in an economy (GDP).}
-    \item{Capital Stock ($K$): the real market value of the total amount of goods in an economy used in the production process of output (machines, tools, infrastructure, etc.).}
-    \item{Labor ($L$): the number of workers in an economy that produce output.
-Labor can be treated as either the total number of workers in an economy or the total number of hours worked per year in an economy.}
+    \item{Output ($Y$): total value (\$) of goods produced (GDP)}
+    \item{Capital Stock ($K$): market value of productive goods (machines, tools, infrastructure).}
+    \item{Labor ($L$): workers in an economy (people or hours)}
   \end{itemize}
@@
 
-\minorSeparator{Energy Data}
+\minorSeparator{Energy Data} %----------------------------
 
@@
   \begin{itemize}
-    \item{Thermal Energy ($Q$): The heat content of an energy carrier.}
-    \item{Exergy ($X$): The maximum work that can be extracted from a heat carrier by a process that brings the system into equillibrium with a thermal reservoir (typically the surrounding environment).}
-    \item{Useful Work ($U$): Energy that directly generates economic activity.}
+    \item{Thermal energy ($Q$): heat content of an energy carrier}
+    \item{Exergy ($X$): maximum work from a heat carrier}
+    \item{Useful work ($U$): energy that generates economic activity directly}
   \end{itemize}
@@
       \hline
-      \multirow{2}{*}{REXS} & \multirow{2}{*}{\includegraphics[scale=0.05]{figure_other/Figure_Warr.png}} & Energy allocation factors. &  \\
+      \multirow{2}{*}{REXS} & \multirow{2}{*}{\includegraphics[scale=0.05]{figure_other/Figure_Warr.png}} & Energy allocation factors. &  \multirow{2}{*}{\citet{Warr:2006hc}}\\
                               &                          & (1980-2000: Developed)     & \\ 
@@
       \item{Example: \citet{Nel:2009wq} use $f$ = $q$}
-      \item{Parameters estimated by \texttt{nls} function in \texttt{R}}
+      \item{$\lambda$ and $m$ estimated by \texttt{nls} function in \texttt{R}}
     \end{itemize}
@@
     \item{Respect absolute constraints: $0 \leq \alpha, \beta, \gamma \leq 1$} (not yet)
-    \item{Parameters estimated by \texttt{nls} function in \texttt{R}}
+    \item{$\lambda$, $\alpha$, $\beta$, and $\gamma$ estimated by \texttt{nls} function in \texttt{R}}
   \end{itemize}
@@
 
-    \item{Are we sure? (Is energy statistically significant?)\\Yes, if $CI_{\gamma}$ doesn't cross 0.0.}
+    \item{Are we sure? (Is energy statistically significant?)\\Yes, if $CI_{\gamma}$ (95\%) doesn't cross 0.0.}
   \end{itemize}
@@
   \begin{itemize}
-    \item{Energy parameter ($\gamma$) is either}
-      \begin{itemize}
-        \item{Small (US, JP, CN, SA, IR)}
+    \item{Energy parameter ($\gamma$) has either}
+      \begin{itemize}
+        \item{Small magnitude (US, JP, CN, SA, IR)}
         \item{Large CI (ZA, TZ, ZM)}
@@
     \item{Example: \citet{Stern:2012ey}}
-    \item{Parameters estimated by \texttt{cesEst} function in \texttt{R}'s \texttt{micEcon} package}
+    \item{$\gamma$, $\lambda$, $\delta_1$, $\rho_1$, $\delta$, $\rho$ estimated by \texttt{cesEst} function in \texttt{R}'s \texttt{micEcon} package}
   \end{itemize}
@@
 
-    \item{Are we sure? (Is energy statistically significant?)\\Yes, if $CI_{\delta}$ doesn't cross 0.0.}
+    \item{Are we sure? (Is energy statistically significant?)\\Yes, if $CI_{\delta}$ (95\%) doesn't cross 0.0.}
   \end{itemize}
@@
   \begin{itemize}
-    \item{Where significant, $\delta$ is close to 1.0}
+    \item{Energy parameter ($\delta$) has either}
+      \begin{itemize}
+        \item{Large magnitude (US, UK, JP, SA, IR)}
+        \item{Large CI (CN, TZ, ZA, ZM)}
+      \end{itemize}
+      \vspace{\baselineskip}          
+      \pause
+
     \item{Direct energy input to economy ($q$) is unimportant as a CES predictor of economic output ($y$)}
@@
   \begin{itemize}
-    \item{Derived from thermodynamic considerations}
-    \item{Foundation is energy ($e$)}
-    \item{No time-dependent technology term}
-    \item{Ratios among $k$, $l$, and $e$ ``trim'' energy}
+    \item{Derived from thermodynamics \citep{Kummel:1980wx}}
+    \item{Time-dependent technology $\rightarrow$ efficiency ratios}
+    \item{Productivity $\uparrow$ if}
+    \begin{itemize}
+      \item{Efficiency of producing capital stock increases ($k$ > $l + e$)}
+      \item{Energy efficiency of labor increases ($l$ > $e$)}
+    \end{itemize}
     \item{Example: \citet{Warr:2006hc}}
-    \item{Parameters estimated by \texttt{nls} function in \texttt{R}}
+    \item{$a_0$ and $c_t$ estimated by \texttt{nls} function in \texttt{R}}
   \end{itemize}
@@
 
-    \item{Are we sure? Yes, by definition!}
+    \item{Are we sure?\\Yes, by definition!}
   \end{itemize}
@@
   \begin{itemize}
-    \item{LINEX parameters $a_0$ and $c_t$ are significant (different from 0.0) for most countries}
+    \item{LINEX parameters $a_0$ and $c_t$ are significant (different from 0) for most countries}
     \item{Direct energy input to economy ($q$) is important as a LINEX predictor of economic output ($y$)}
@@
 
+\begin{frame}{The Question} %----------------------------
+  \begin{center}
+    Which economic growth model best describes (statistically) the role of energy in economic growth for different types of economies?
+  \end{center}
+\end{frame}
+
 \begin{frame}{Tentative Conclusions} %----------------------------
@@
         \scriptsize
-        Statistical evidence indicates that energy parameters are not significant for most countries \\Why?
+        Preliminary statistical evidence indicates that energy parameters are not significant for most countries \\Why?
 Energy is \emph{always already} embedded in capital stock ($K$) and labor ($L$), so including energy is unnecessary.
@@
         \scriptsize
-        The foundation of LINEX is an energy term.\\Statistical evidence indicates that LINEX parameters $a_0$ and $c_t$ are significant for most countries.\\LINEX fits overall are worse than Cobb-Douglas or CES.
+        The foundation of LINEX is an energy term.\\Statistical evidence indicates that LINEX parameters $a_0$ and $c_t$ are significant for most countries.\\However, LINEX fits are worse overall than Cobb-Douglas or CES.
         \normalsize}
-  \vspace{\baselineskip}
-  \pause
-
-  \item{Need a modeling method (that is better than LINEX) that captures energy's embeddedness \\
-        \scriptsize
-        System dynamics modeling?
-        \normalsize}
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{The ``Answer''} %----------------------------
+  \begin{center}
+    Which economic growth model best describes (statistically) the role of energy in economic growth for different types of economies?
+    \vspace{\baselineskip}
+
+    \pause
+    Answer: Cobb-Douglas without energy or CES 
+  \end{center}
+\end{frame}
+
+\begin{frame}{Extra Credit?} %----------------------------
+  \begin{itemize}
+    \item{Price, cost share exogenous to all models}
+    \pause
+    \item{Models (CD without energy, CES) could be \emph{included within} a model that endogenizes price and cost share}
+    \pause
+    \item{Still searching for a modeling approach that captures price and cost share dynamics \\
+      \scriptsize System dynamics modeling? \normalsize}
+    \pause
+    \item{No extra credit!}
   \end{itemize}

### 2013-03-30 EconGrowth-R-Functions.Rnw
Now possible to include the optimum point on the SSE vs. lambda and gamma graph.

--- 2013-03-26 EconGrowth-R-Functions.Rnw
@@
 
+###############################
+# Creates a panel for use with a mixed wireframe and cloud.
+# See http://stackoverflow.com/questions/1406202/plotting-a-wireframe-and-a-cloud-with-lattice-in-r
+# 
+# x: x variable to be used in the wireframe plot. This will be the x variable from the wireframe plot.
+# y: y variable to be used in the wireframe plot. This will be the y variable from the wireframe plot.
+# z: z variable to be used in the wireframe plot. This will be the z variable from the wireframe plot.
+# points: a data.frame containing columns named x, y, and z.
+# showPoints: a boolean saying whether you want the points to be shown.
+##
+wireCloudPanel <- function(x, y, z, points, showPoints=TRUE, ...) {
+  panel.wireframe(x, y, z, ...)
+  if (showPoints){
+    panel.cloud(points$x, points$y, points$z, ...)
+  }
+}
+
 #########################
@@
 #   countryAbbrev: 2-letter country code (upper case)
-#   factor: the factor of production you want to use in the single-factor model.
-##
-sf3DSSEGraph <- function(countryAbbrev, factor){
-  # Generate the data in the form of a matrix with gamma in columns, lambda in rows, and SSE in the middle
+#   factor: the factor of production you want to use in the single-factor model. One of K, L, Q, X, or U
+#   showOpt: tells whether or not to show a dot at the optimium point.
+##
+sf3DSSEGraph <- function(countryAbbrev, factor, showOpt=TRUE){
   # First, make a data.frame with which we want to make predictions
@@
   mSeq <- seq(0.0, 1.0, by=0.1)
-
-  lambdaSeq <- data.frame(lambdaSeq)
-  nRowLambda <- nrow(lambdaSeq)
-  colnames(lambdaSeq) <- "lambda"
-
-  mSeq <- data.frame(mSeq)
-  nRowM <- nrow(mSeq)
-  colnames(mSeq) <- "m"
-
-  # Make a sequence of lambda values based on the number of m values you have.
-  lambda <- rep(lambdaSeq[1,1], nRowM)
-  lambda <- data.frame(lambda)
-  colnames(lambda) <- "lambda"
-  for (i in 2:nRowLambda){
-    lambdaTemp <- rep(lambdaSeq[i, 1], nRowM)
-    lambdaTemp <- data.frame(lambdaTemp)
-    colnames(lambdaTemp) <- "lambda"
-    lambda <- rbind(lambda, lambdaTemp)
-  }
-
-  # Make repeats of the m data frame as we have number of lambda rows
-  m <- mSeq
-  for (i in 2:nRowLambda){
-    m <- rbind(m, mSeq)
-  }
-
-  # Now create the data.frame of new observation locations
-  newX <- cbind(lambda, m)
-
-  # Get the actual data
+  newX <- data.frame(expand.grid(lambdaSeq, mSeq))
+  colnames(newX) <- c("lambda", "m")
+  # Get the actual GDP data
   data <- loadData(countryAbbrev)
@@
   y_act <- data.frame(y_act)
-
-  # Make predictions
-  # Get the model
+  # Need the model to make predictions
   model <- singleFactorModel(countryAbbrev, factor)
-
-  sse <- c(1:(nRowLambda*nRowM)) # Build a bogus vector at the start
-
+  # Get information about the optimum point, the point where SSE is minimized
+  coefs <- coef(model)
+  lambda_opt <- coefs["lambda"]
+  gamma_opt <- coefs["m"]
+  xOpt <- data.frame(lambda=lambda_opt, m=gamma_opt)
+  y_opt_pred <- predict(model, xOpt)
+  y_opt_pred <- data.frame(y_opt_pred)
+  compareDF_opt <- cbind(y_opt_pred, y_act)
+  se_opt <- with(compareDF_opt, (y_opt_pred-y_act)^2)
+  compareDF_opt <- cbind(compareDF_opt, se_opt)
+  sums_opt <- colSums(compareDF_opt)
+  sse_opt <- sums_opt[3]
+  # Need to name these x, y, and z so that the custom panel will pick them up.
+  optPoint <- data.frame(x=lambda_opt, y=gamma_opt, z=sse_opt)
+  rownames(optPoint) <- NULL
+
+  # Now gather all the points we need for the surface.
+  nObs <- nrow(newX)
+  sse <- c(1:nObs) # Build a bogus vector at the start
   # Loop over all the different combinations of lambda and m that are of interest for us.
-  #i = 1
-  for (i in 1:(nRowLambda*nRowM)){
+  for (i in 1:nObs){
     y_pred <- predict(model, newX[i,]) # Get lambda and m for this particular row.
     y_pred <- data.frame(y_pred)
-
     compareDF <- cbind(y_pred, y_act)
@@
     compareDF <- cbind(compareDF, se) # Bind it to the data frame as an additional column
-
     # Now get the sse
@@
   colnames(ssedf) <- "sse"
-
   # Now merge the sse column and the newX data to form a data.frame fit for 3-D plotting
-  dataFor3DGraph <- cbind(newX, ssedf)
-
-  # Adjust settings for a nicer graph
-  #trellis.par.set("axis.line", list(col="transparent"))
-
-  # Create the lattice graph
+  dataFor3DSurface <- cbind(newX, ssedf)
+  # Create the figure
   fig <- wireframe(sse ~ lambda * m,
-                   data = dataFor3DGraph,
+                   data = dataFor3DSurface,
+                   panel = wireCloudPanel,
+                   points = optPoint,
+                   showPoints = showOpt,
                    screen = list(z = -20, x = -55),

### 2013-03-30 EconGrowth.Rnw
Now including tables and frames for sources of economic data. Also including graphics for world bank and BLS.
Now possible to include the optimum point on the SSE vs. lambda and gamma graph.

@@
 
-<<test3dPlot, eval=TRUE>>=
-sf3DSSEGraph("US", "Q")
+<<TestWireframeCloud, eval=TRUE>>=
+
+sf3DSSEGraph("US", "Q", showOpt=TRUE)
+
+# point <- data.frame(x=0.0, y=0.0, z=1.0)
+# 
+# x <- seq(-.8, .8, .1)
+# y <- seq(-.8, .8, .1)
+# myGrid <- data.frame(expand.grid(x,y))
+# colnames(myGrid) <- c("x","y")
+# myGrid$z <- myGrid$x + myGrid$y
+# noise <- rnorm(length(myGrid$z),.3,.2)
+# myGrid$z2 <- myGrid$x + myGrid$y + noise
+# mypanel <- function(x, y, z, points, showPoints=TRUE, ...) {
+#   panel.wireframe(x, y, z, ...)
+#   if (showPoints){
+#     panel.cloud(points$x, points$y, points$z, ...)
+#   }
+# }
+# wireframe(z ~ x * y, data=myGrid, xlab="X", ylab="Y", zlab="Z",
+#           panel=mypanel, points=point, showPoints=FALSE)
+
+# x <- seq(-.8, .8, .1)
+# y <- seq(-.8, .8, .1)
+# myGrid <- data.frame(expand.grid(x,y))
+# colnames(myGrid) <- c("x","y")
+# myGrid$z <- myGrid$x + myGrid$y
+# noise <- rnorm(length(myGrid$z),.3,.2)
+# myGrid$z2 <- myGrid$x + myGrid$y + noise
+# mypanel <- function(x,y,z,z2,...) {
+#   panel.wireframe(x,y,z,...)
+#   panel.cloud(x,y,z2,...)
+# }
+# wireframe(z ~ x * y, data=myGrid, xlab="X", ylab="Y", zlab="Z",
+#           panel=mypanel, z2=myGrid$z2)
+
 @

### 2013-03-30 EconGrowthSeminar.Rnw
Now possible to include the optimum point on the SSE vs. lambda and gamma graph.

@@
 {Mathematics Colloquium\\
-4 April 2013
+Thursday, 4 April 2013
 }
@@
 
-\subsection[Economic]{Sources of Economic Data} %+++++++++++++++++++++++++++++++++++++++
+\subsection[Economic]{Economic} %+++++++++++++++++++++++++++++++++++++++
 
@@
     \item{Output ($Y$): total value (\$) of goods produced (GDP)}
-    \item{Capital Stock ($K$): market value of productive goods (machines, tools, infrastructure).}
+    \vspace{\baselineskip}
+
+    \item{Capital stock ($K$): market value of productive goods (e.g., machines, tools, infrastructure)}
+    \vspace{\baselineskip}
+
     \item{Labor ($L$): workers in an economy (people or hours)}
@@
       \hline
-      \multirow{4}{*}{WB WDI} & \multirow{4}{*}{\includegraphics[scale=0.07]{figure_other/Figure_World_Bank.png}} & Pop, Pop < 15 yo,    & \multirow{4}{*}{Total Employment} \\
+      \multirow{4}{*}{WB WDI} & \multirow{4}{*}{\includegraphics[scale=0.07]{figure_other/Figure_World_Bank.png}} & Pop, Pop < 15 yo,    & \multirow{4}{*}{Total employment} \\
                               &                          & Emp/Pop ratio > 15 yo, &                                \\
@@
 
-\subsection[Energy]{Sources of Energy Data} %+++++++++++++++++++++++++++++++++++++++
+\subsection[Energy]{Energy} %+++++++++++++++++++++++++++++++++++++++
 
@@
     \item{Thermal energy ($Q$): heat content of an energy carrier}
+    \vspace{\baselineskip}
+
     \item{Exergy ($X$): maximum work from a heat carrier}
+    \vspace{\baselineskip}
+
     \item{Useful work ($U$): energy that generates economic activity directly}
   \end{itemize}
-  \begin{center}Note: indexed $Q$ and $X$ are identical unless energy mix changes significantly. \end{center}
+  \begin{center}Note: indexed $Q$ and $X$ are identical unless energy mix changes significantly \end{center}
 \end{frame}
@@
 
-\subsection[Historical Data]{Historical Data} %+++++++++++++++++++++++++++++++++++++++
-
-\minorSeparator{Historical Data}
+\subsection[Visualization]{Visualization} %+++++++++++++++++++++++++++++++++++++++
+
+\minorSeparator{Visualization of Historical Data}
 
@@
     \begin{itemize}
+      \item{Illustrative}
       \item{$\mathrm{e}^{\lambda(t-t_0)}$: Time-dependent technology term}
       \begin{itemize}
-        \item{Represents the irrepressible ``progress'' of technology}
-        \item{Is independent of factor of production ($f$)}
-      \end{itemize}
-      \item{Used for illustration purposes here}
+        \item{Irrepressible ``progress'' of technology}
+        \item{Independent of factor of production ($f$)}
+      \end{itemize}
       \item{Example: \citet{Nel:2009wq} use $f$ = $q$}
@@
 
-\begin{frame}{Curve-fitting as Optimization} %----------------------------
-  \begin{itemize}
-    \item{Select values of parameters to minimize errors ($SSE$) between predicted and historical economic output ($y$)}
-    \vspace{\baselineskip}
-
-    \item{Example: Single-factor Model with $Q$}
-    \begin{itemize}
-      \item{$y = \mathrm{e}^{\lambda (t-t_0)}q^{\gamma}$}
-      \item{Select $\lambda$ and $\gamma$ to minimize\\
-            $SSE = \sum\limits_{t=1980}^{2011}(y_{pred} - y_{act})^2$}
-    \end{itemize}
-    \vspace{\baselineskip}
-
-    \item{``Curve-fitting,'' ``parameter estimation,''  ``optimization,'' and ``minimization'' are used interchangeably}
+\begin{frame}{Example: Single-factor model with $q$} %----------------------------
+  \begin{center}$y = \mathrm{e}^{\lambda (t-t_0)}q^{\gamma}$\end{center}
+  \begin{itemize}
+    \item{Select $\lambda$, $\gamma$}
+    \item{To minimize \\ $SSE = \sum\limits_{t=1980}^{2011}(y_{pred} - y_{act})^2$}
   \end{itemize}
@@
   \begin{itemize}
-    \item{Not typically used for economic modeling. Illustrates confidence intervals.}
+    \item{Not typically used for economic modeling: illustrates confidence intervals}
     \vspace{\baselineskip}
@@
 
-\subsection[Cobb-Douglas]{Evaluation of Cobb-Douglas} %+++++++++++++++++++++++++++++++++++++++
+\subsection[Cobb-Douglas]{Cobb-Douglas} %+++++++++++++++++++++++++++++++++++++++
 
@@
 
-\subsection[CES]{Evaluation of CES} %+++++++++++++++++++++++++++++++++++++++
+\subsection[CES]{CES} %+++++++++++++++++++++++++++++++++++++++
 
@@
     \item{$\delta$: split between ($kl$) and ($e$)}
-    \item{$\sigma \equiv \frac{1}{1+\rho}$: elasticity of substitution ($0 \leq \sigma \leq 1$)}
-    \begin{itemize}
-      \item{$\sigma \rightarrow 0$: ($kl$) and ($e$) are complementary}
-      \item{$\sigma \rightarrow 1$: ($kl$) and ($e$) are substitutes}
-    \end{itemize}
     \item{Example: \citet{Stern:2012ey}}
@@
 
-\subsection[LINEX]{Evaluation of LINEX} %+++++++++++++++++++++++++++++++++++++++
+\subsection[LINEX]{LINEX} %+++++++++++++++++++++++++++++++++++++++
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Summary}
+\section{Summary}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
     \pause
-    \item{Still searching for a modeling approach that captures price and cost share dynamics \\
-      \scriptsize System dynamics modeling? \normalsize}
+    \item{Still searching for a modeling approach that captures price and cost share dynamics \\ \scriptsize System dynamics modeling? \normalsize}
     \pause
@@
 
+\begin{frame}{95\% Confidence Intervals}{Cobb-Douglas (without energy)} %---------------------------- 
+<<CD_Params_Graph, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
+createCDParamsGraph()
+@  
+\end{frame}
+
 <<Coefs_ZA_CD>>=
@@
 
-\begin{frame}{95\% Confidence Intervals}{Cobb-Douglas (without energy)} %---------------------------- 
-<<CD_Params_Graph, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
-createCDParamsGraph()
-@  
+\minorSeparator{CES Model}
+
+\begin{frame}{CES Elasticity of Substitution} %----------------------------
+  \begin{center} \small \cesEqn \normalsize \end{center}
+  \begin{itemize}
+    \item{$\sigma \equiv \frac{1}{1+\rho}$: elasticity of substitution ($0 \leq \sigma \leq 1$)}
+    \begin{itemize}
+      \item{$\sigma \rightarrow 0$: ($kl$) and ($e$) are complementary}
+      \item{$\sigma \rightarrow 1$: ($kl$) and ($e$) are substitutes}
+    \end{itemize}
+  \end{itemize}
 \end{frame}

### 2013-03-30 EconGrowth-R-Functions.Rnw
Now including a 3-D graph with optimum point in the presentation.

@@
   if (showPoints){
-    panel.cloud(points$x, points$y, points$z, ...)
+    #pch=16 gives filled circle plot symbol, cex!=1 makes it a different size.
+    panel.cloud(points$x, points$y, points$z, col="red", pch=16, cex=1.5, ...)
   }

### 2013-03-30 EconGrowthSeminar.Rnw
Now including a 3-D graph with optimum point in the presentation.

@@
 
+% This is a sequence of two slides with 3-D graphs. 
+% The first just shows the surface. The second also shows the optimum point in the surface.
 \begin{frame}{$SSE$ Minimization}{US single-factor with $Q$} %---------------------------- 
-<<3D_Graph_US_SF_Q, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
-sf3DSSEGraph("US", "Q")
+<<3D_Graph_US_SF_Q, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3, eval=TRUE>>=
+sf3DSSEGraph("US", "Q", showOpt=FALSE)
+@
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{US}{0.055}  
+\end{frame}
+
+\begin{frame}{$SSE$ Minimization}{US single-factor with $Q$} %---------------------------- 
+<<3D_Graph_US_SF_Q_With_Opt_Point, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3, eval=TRUE>>=
+sf3DSSEGraph("US", "Q", showOpt=TRUE)
 @

### 2013-03-30 EconGrowthSeminar.Rnw
A few small edits on the seminar presentation.

@@
     \footnotesize
-    No known rigorous, statistical comparative studies of economic growth models for various types of economies. 
-    \normalsize
-    \pause
-    \vspace{\baselineskip}
-
-    Extra credit: reflect dynamics of energy cost share and prices spikes.
+    No known statistically-rigorous comparative studies of economic growth models for various types of economies. 
+    \normalsize
+    \pause
+    \vspace{\baselineskip}
+
+    Extra credit: reflect dynamics of energy cost share and price spikes.
   \end{center}
@@
 
-    \item{Labor ($L$): workers in an economy (people or hours)}
+    \item{Labor ($L$): human work in an economy (people or hours)}
   \end{itemize}
@@
     \item{$\mathrm{e}^{\lambda(t-t_0)}$: Time-dependent technology term}
-    \begin{itemize}
-      \item{Represents the ``irrepressible'' ``progress'' of technology}
-      \item{Is independent of factors of production ($k$, $l$, and $e$)}
-    \end{itemize}
     \item{$k$, $l$, and $e$ factors of production ``blend'' with $\alpha + \beta + \gamma = 1$}
@@
 
-\begin{frame}{The Question} %----------------------------
-  \begin{center}
-    Which economic growth model best describes (statistically) the role of energy in economic growth for different types of economies?
-  \end{center}
-\end{frame}
-
 \begin{frame}{Tentative Conclusions} %----------------------------
@@
         \scriptsize
-        Preliminary statistical evidence indicates that energy parameters are not significant for most countries \\Why?
-Energy is \emph{always already} embedded in capital stock ($K$) and labor ($L$), so including energy is unnecessary.
+        Preliminary statistical evidence indicates that energy parameters are not significant for most countries \\Why? Energy is \emph{always already} embedded in capital stock ($K$) and labor ($L$).
         \normalsize}
@@
 
+\begin{frame}{The Question} %----------------------------
+  \begin{center}
+    Which economic growth model best describes (statistically) the role of energy in economic growth for different types of economies?
+  \end{center}
+\end{frame}
+
 \begin{frame}{The ``Answer''} %----------------------------
@@
     \pause
-    Answer: Cobb-Douglas without energy or CES 
+    Answer: Cobb-Douglas or CES without energy
   \end{center}
@@
 \begin{frame}{Extra Credit?} %----------------------------
+  \begin{center} Reflect dynamics of energy cost share and price spikes \end{center}
+    \vspace{\baselineskip}
+
+    \pause
   \begin{itemize}
@@
     \pause
-    \item{Models (CD without energy, CES) could be \emph{included within} a model that endogenizes price and cost share}
+    \item{Models (CD and CES without energy) could be \emph{included within} a model that endogenizes price and cost share}
     \pause

### 2013-03-30 EconGrowthSeminar.Rnw
Several small changes and edits in preparation for the seminar.

@@
 \begin{frame}{$SSE$ Minimization}{US single-factor with $Q$} %---------------------------- 
-<<3D_Graph_US_SF_Q, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3, eval=TRUE>>=
+<<3D_Graph_US_SF_Q, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
 sf3DSSEGraph("US", "Q", showOpt=FALSE)
@@
 \begin{frame}{$SSE$ Minimization}{US single-factor with $Q$} %---------------------------- 
-<<3D_Graph_US_SF_Q_With_Opt_Point, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3, eval=TRUE>>=
+<<3D_Graph_US_SF_Q_With_Opt_Point, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
 sf3DSSEGraph("US", "Q", showOpt=TRUE)
@@
 
-    \item{$CI_{\lambda}$ smaller than $CI_{\gamma}$ for all countries}
+    \item{$CI_{\lambda}$ smaller than $CI_{\gamma}$ for all countries\footnote{\tiny as percentage of $0.0 < \lambda < 0.1$ and $0 < \gamma < 1$ \normalsize}}
   \end{itemize}
@@
 
-\begin{frame}{Tentative Conclusions} %----------------------------
-  \begin{itemize}
-  \item{Including energy in Cobb-Douglas and CES production functions is unwarranted \\
+\begin{frame}{Summary of Analysis} %----------------------------
+  \begin{itemize}
+  \item{Including energy ($E$) in Cobb-Douglas and CES production functions appears to be unwarranted}
+  \pause
+    \begin{itemize}
       \scriptsize
-        Preliminary statistical evidence indicates that energy parameters are not significant for most countries \\Why? Energy is \emph{always already} embedded in capital stock ($K$) and labor ($L$).
-        \normalsize}
-  \item{Including energy in LINEX production function is required \\
+      \item{Energy parameters less significant than others for most countries}
+      \pause
+      \item{Why? Energy is \emph{always already} embedded in capital stock ($K$) and labor ($L$)}
+      \normalsize
+    \end{itemize}
+  \vspace{\baselineskip}
+  \pause
+  \item{Including energy ($E$) in LINEX production function is required}
+  \pause
+    \begin{itemize}
       \scriptsize
-        The foundation of LINEX is an energy term.\\Statistical evidence indicates that LINEX parameters $a_0$ and $c_t$ are significant for most countries.\\However, LINEX fits are worse overall than Cobb-Douglas or CES.
-        \normalsize}
+      \item{One factor of production: energy}
+      \pause
+      \item{Statistical evidence indicates that LINEX parameters $a_0$ and $c_t$ are significant for most countries}
+      \pause
+      \item{Unfortunately, LINEX fits are worse overall than Cobb-Douglas or CES}
+      \normalsize
+    \end{itemize}
   \end{itemize}
@@
   \end{center}
+  \vspace{\baselineskip}
+
+  \vspace{\baselineskip}
+
 \end{frame}
@@
 
-    \pause
     Answer: Cobb-Douglas or CES without energy
@@
 \begin{frame}{Extra Credit?} %----------------------------
-  \begin{center} Reflect dynamics of energy cost share and price spikes \end{center}
+  \begin{center} Reflect dynamics of energy cost share and price spikes? \end{center}
     \vspace{\baselineskip}
@@
     \pause
+    \item{No extra credit!}
+    \pause
+    \vspace{\baselineskip}
+
     \item{Models (CD and CES without energy) could be \emph{included within} a model that endogenizes price and cost share}
@@
     \item{Still searching for a modeling approach that captures price and cost share dynamics \\ \scriptsize System dynamics modeling? \normalsize}
-    \pause
-    \item{No extra credit!}
   \end{itemize}
@@
   \begin{itemize}
-    \item{Estimate statistical properties for \emph{all} fitting parameters}
+    \item{Verify and improve estimates of statistical properties for \emph{all} fitting parameters}
     \vspace{\baselineskip}

### 2013-04-03 EconGrowth-R-Functions.Rnw
Now including several mods to the presentation based on feedback from Caleb and Lucas.

@@
   plot <- xyplot(cdResid ~ iEToFit, data=data,
-                 type=c('p','smooth'),
+#                 type=c("p",:smooth"),
+                 type=c("p"),
                  col="black",
@@
                  xlab=list(label=paste("$", tolower(energyType), "$", sep=""), cex=textScaling),
-                 ylab=list(label="$y$ residuals", cex=textScaling)
+                 ylab=list(label="$y$ residuals (CD without energy)", cex=textScaling)
                  )

### 2013-04-03 EconGrowthSeminar.Rnw
Now including several mods to the presentation based on feedback from Caleb and Lucas.

@@
 
-  \setbeamertemplate{background canvas}[vertical shading][top=CalvinLightTan, bottom=white]
+  \setbeamertemplate{background canvas}[vertical shading][top=CalvinLightTan!40!white, bottom=white]
   \setbeamercolor{block title}{fg=CalvinMaroon, bg=CalvinLightTan!60!white}
@@
 % The equation for a single-factor model
-\newcommand{\sfEqn}{$y = \mathrm{e}^{\lambda (t-t_0)}f^{m}$}
+\newcommand{\sfEqn}{$y = A \: f^{m}$; $A \equiv \mathrm{e}^{\lambda (t-t_0)}$}
 % The equation for a cobb-douglas without energy model
-\newcommand{\cdEqn}{$y = \mathrm{e}^{\lambda (t-t_0)}k^{\alpha}l^{\beta}$}
+\newcommand{\cdEqn}{$y = A \: k^{\alpha}l^{\beta}$; $A \equiv \mathrm{e}^{\lambda (t-t_0)}$}
 % The equation for a cobb-douglas with energy model
-\newcommand{\cdeEqn}{$y = \mathrm{e}^{\lambda (t-t_0)}k^{\alpha}l^{\beta}e^{\gamma}$}
+\newcommand{\cdeEqn}{$y = A\: k^{\alpha}l^{\beta}e^{\gamma}$; $A \equiv \mathrm{e}^{\lambda (t-t_0)}$}
 % The equation for a ces model
-\newcommand{\cesEqn}{$y = \gamma \: \mathrm{e}^{\lambda(t-t_0)} \left\{\delta \left[\delta_1 k^{-\rho_1} + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1} + (1-\delta) e^{-\rho} \right\}^{-1/\rho}$}
-
-\newcommand{\cesEqnNarrow}{\begin{align*} y = \, &\gamma \: \mathrm{e}^{\lambda(t-t_0)}\\&\times \left\{\delta \left[\delta_1 k^{-\rho_1} + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1} \right.
+\newcommand{\cesEqn}{\scriptsize $y = \gamma \: A \: \left\{\delta \left[\delta_1 k^{-\rho_1} + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1} + (1-\delta) e^{-\rho} \right\}^{-1/\rho}$; \tiny $A \equiv \mathrm{e}^{\lambda (t-t_0)}$ \normalsize}
+% The narrow equation for a ces model
+\newcommand{\cesEqnNarrow}{\begin{align*} y = \, &\gamma \: A \\&\times \left\{\delta \left[\delta_1 k^{-\rho_1} + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1} \right.
 \\ &\left.+ \; (1-\delta) e^{-\rho} \right\}^{-1/\rho} \end{align*}}
-
 % The equation for a linex model
-% \newcommand{\linexEqn}{$y = e \: \mathrm{e}^{\left[a_0 \left(2 - \frac{l + e}{k} \right) + a_0 c_t \left(\frac{l}{e} - 1 \right)\right]}$}
-
-\newcommand{\linexEqn}{$y = \mathrm{e}^{\left[a_0 \left(2 - \frac{l + e}{k} \right) + a_0 c_t \left(\frac{l}{e} - 1 \right)\right]} \times e$}
+\newcommand{\linexEqn}{$y =  A \: e$; $A \equiv \mathrm{e}^{\left[a_0 \left(2 - \frac{l + e}{k} \right) + a_0 c_t \left(\frac{l}{e} - 1 \right)\right]}$}
 
@@
 
-\begin{frame}{Energy Cost Share}{\citep{Bashmakov:2007ek}} %----------------------------
-  \begin{center}
-    \includegraphics[height=6.3cm]{figure_other/Figure_Bashmakov_2007.pdf}
-  \end{center}
-\end{frame}
-
 \begin{frame}{Energy Cost Share and Economic Growth}{\citep{Murphy:2011jh}}  %----------------------------
@@
   \begin{itemize}
-    \item{Historical economic development paths (US, Western Europe) are energy intensive.}
+    \item{Historical economic development paths (US, Western Europe) are energy intensive}
     \vspace{\baselineskip}
@@
     \item{Goal: predict economic output over time}
-    \item{Economic output ($Y$) is a function of ``factors of production''}
-    \item{Output ($Y$) measured by GDP}
     \item{All factors and outputs indexed to initial year: $y = Y/Y_0, e = E/E_0$, etc.}
+    \vspace{\baselineskip}
+    \pause
+
+    \item{Set aside debates about growth and its measure}
   \end{itemize}
@@
     Which economic growth model best describes (statistically) the role of energy in economic growth for different types of economies?
-    \pause
-    \vspace{\baselineskip}
-
-    \footnotesize
-    No known statistically-rigorous comparative studies of economic growth models for various types of economies. 
-    \normalsize
     \pause
@@
   \vspace{\baselineskip}
-  \pause
 
@@
   \vspace{\baselineskip}
-  \pause
 
   Constant Elasticity of Substitution:
-  \small
   \cesEqn
-  \normalsize
-  \vspace{\baselineskip}
-  \pause
+  \vspace{\baselineskip}
 
   LINEX: \linexEqn
-  \vspace{\baselineskip}
-  \pause
-
-  System Dynamics Models
+\end{frame}
+
+\begin{frame}{Single-factor Model} %----------------------------
+  \begin{center}
+    \sfEqn
+    \vspace{\baselineskip}
+
+    \begin{tabular}{|c|l|}\hline
+      \yRow\\
+      \timeRow\\
+      \initialTimeRow\\
+      $f$ & $F$/$F_0$, factor of production ($k$, $l$, $q$, $x$, or $u$)\\
+      \hline
+      \lambdaRow\\
+      $m$ & ``influence'' of factor $f$ ($\alpha$, $\beta$, or $\gamma$)\\
+      \hline
+    \end{tabular}
+  \end{center}
+\end{frame}
+
+\begin{frame}{Cobb-Douglas (with Energy)} %----------------------------
+  \begin{center}
+    \cdeEqn\\
+    $\alpha + \beta + \gamma = 1$\\
+    $0 \leq \alpha, \beta, \gamma \leq 1$
+    \vspace{\baselineskip}
+
+    \begin{tabular}{|c|l|}\hline
+      \lambdaRow\\
+      \alphaRow\\
+      \betaRow\\
+      \gammaRow\\
+      \hline
+    \end{tabular}
+  \end{center}
+\end{frame}
+
+\begin{frame}{Constant Elasticity of Substitution (CES)} %----------------------------
+  \begin{center}
+    \cesEqn
+    \vspace{\baselineskip}
+
+    \begin{tabular}{|c|l|}\hline
+      $\gamma$   &   fitting coefficient\\
+      \lambdaRow\\
+      $\delta_1$   &   split between ($k$) and ($l$)\\
+      $\rho_1$     &   ``influence'' of ($k$) vs. ($l$)\\
+      $\delta$   &   split between ($kl$) and ($e$)\\
+      $\rho$     &   ``influence'' of ($kl$) vs. ($e$)\\
+      \hline
+    \end{tabular}
+  \end{center}
+\end{frame}
+
+\begin{frame}{LINEX} %----------------------------
+  \begin{center}
+    \linexEqn
+    \vspace{\baselineskip}
+
+    \begin{tabular}{|c|l|}\hline
+      $a_0$ & fitting parameter\\
+      $c_t$ & fitting parameter\\
+      \hline
+    \end{tabular}
+  \end{center}
 \end{frame}
@@
   \begin{itemize}
-    \item{Output ($Y$): total value (\$) of goods produced (GDP)}
+    \item{Output ($Y$): total value (real 2005\$) of goods produced (GDP)}
     \vspace{\baselineskip}
@@
   \end{itemize}
-  \begin{center}Note: indexed $Q$ and $X$ are identical unless energy mix changes significantly \end{center}
-\end{frame}
-
-\begin{frame}{Energy Flows} %----------------------------
+  \begin{center}Note: $q$ and $x$ are identical unless energy mix changes significantly \end{center}
+\end{frame}
+
+\begin{frame}{Energy Flows (Sankey Diagram)} %----------------------------
   \begin{center}
@@
 
-\begin{frame}{USA and China} %----------------------------
+\begin{frame}{USA and United Kingdom} %----------------------------
   \begin{columns}[c]
@@
     \column{2.2in}
-<<Historical_Data_CN, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-createHistoricalLatticeGraph("CN", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
-@
-  \end{columns}
-  \putat{flag/flag_US.png}{0.055}{-0.73in}{1.0in} % US flag
-  \putat{flag/flag_CN.png}{0.055}{ 1.50in}{1.0in} % CN flag
+<<Historical_Data_UK, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+createHistoricalLatticeGraph("UK", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
+  \putat{flag/flag_US.png}{0.055}{-0.73in}{1.0in}
+  \putat{flag/flag_UK.png}{0.055}{ 1.50in}{1.0in}
 \end{frame}
@@
   \end{columns}
-  \putat{flag/flag_ZA.png}{0.055}{-0.73in}{1.0in} % US flag
-  \putat{flag/flag_SA.png}{0.055}{ 1.50in}{1.0in} % CN flag
+  \putat{flag/flag_ZA.png}{0.055}{-0.73in}{1.0in}
+  \putat{flag/flag_SA.png}{0.055}{ 1.50in}{1.0in}
 \end{frame}
@@
 \minorSeparator{Curve-fitting as Optimization}
-
-\begin{frame}{Example: Single-factor Model} %----------------------------
-  \begin{center}
-    \sfEqn
-    \vspace{\baselineskip}
-
-    \begin{tabular}{|c|l|}\hline
-      \yRow\\
-      \timeRow\\
-      \initialTimeRow\\
-      $f$ & $F$/$F_0$, a factor of production\\
-      \hline
-      \lambdaRow\\
-      $m$ & ``influence'' of factor $f$\\
-      \hline
-    \end{tabular}
-  \end{center}
-\end{frame}
 
@@
 
-    \item{$CI_{\lambda}$ smaller than $CI_{\gamma}$ for all countries\footnote{\tiny as percentage of $0.0 < \lambda < 0.1$ and $0 < \gamma < 1$ \normalsize}}
+    \item{$CI_{\gamma}$ > $CI_{\lambda}$ for all countries\footnote{\tiny as percentage of $0.0 < \lambda < 0.1$ and $0 < \gamma < 1$ \normalsize}}
   \end{itemize}
@@
 
-\begin{frame}{Cobb-Douglas (with Energy)} %----------------------------
+\begin{frame}{Comments on Cobb-Douglas Model Equation} %----------------------------
+  \begin{center} \cdeEqn \end{center}
+  \begin{itemize}
+    \item{$\mathrm{e}^{\lambda(t-t_0)}$: Time-dependent technology term}
+    \item{$k$, $l$, and $e$ factors of production ``blend'' with $\alpha + \beta + \gamma = 1$}
+    \item{Example: \citet{Froling:2009vo}}
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Parameter Estimation for Cobb-Douglas With Energy} %----------------------------
+  \begin{center}\cdeEqn\end{center}
+  \begin{itemize}
+    \item{Objective: determine $\lambda$, $\alpha$, $\beta$, and $\gamma$ that best fits historical data}
+    \item{Perform grid search over $\gamma$: Re-estimate $\lambda$, $\alpha$, and $\beta$ at each value of $\gamma$}
+    \item{Respect sum constraint: $\alpha + \beta + \gamma = 1$}
+    \item{Respect absolute constraints: $0 \leq \alpha, \beta, \gamma \leq 1$} (not yet)
+    \item{$\lambda$, $\alpha$, $\beta$, and $\gamma$ estimated by \texttt{nls} function in \texttt{R}}
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Grid Search Over $\gamma$}{US Cobb-Douglas with $Q$} %----------------------------
+<<CDeGammaGraphsUS, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
+  cdeGridGraph("US", "Q", textScaling=0.8)
+@
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{US}{0.055}
+\end{frame}
+
+\begin{frame}{Grid Search Over $\gamma$}{UK Cobb-Douglas with $Q$} %----------------------------
+<<CDeGammaGraphsUK, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
+  cdeGridGraph("UK", "Q", textScaling=0.8)
+@
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{UK}{0.045}
+\end{frame}
+
+<<pprint>>=
+pprint <- function(num, digits = 2){
+  out <- formatC(num, digit=digits, format="f")
+  return(out)
+}
+@
+
+<<Coefs_US_CD>>=
+cdUS <- cobbDouglasData("US")
+cdqUS <- cobbDouglasData("US", "Q")
+cdxUS <- cobbDouglasData("US", "X")
+cduUS <- cobbDouglasData("US", "U")
+@
+\begin{frame}{Cobb-Douglas $y$ Predictions} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+      \begin{center}
+        \cdeEqn
+        \vspace{\baselineskip}
+
+        \tiny
+          \begin{tabular}{c|c c c c}
+            $e$ & $\lambda$ & $\alpha$ & $\beta$ & $\gamma$\\
+            \hline
+            $-$   & \Sexpr{pprint(cdUS["CD", "lambda"], digits=4)} & \Sexpr{pprint(cdUS["CD", "alpha"])} & \Sexpr{pprint(cdUS["CD", "beta"])} & \Sexpr{pprint(cdUS["CD", "gamma"])}\\
+            \hline
+            $q$   & \Sexpr{pprint(cdqUS["CD", "lambda"], digits=4)} & \Sexpr{pprint(cdqUS["CD", "alpha"])} & \Sexpr{pprint(cdqUS["CD", "beta"])} & \Sexpr{pprint(cdqUS["CD", "gamma"])}\\
+            \hline
+            $x$   & \Sexpr{pprint(cdxUS["CD", "lambda"], digits=4)} & \Sexpr{pprint(cdxUS["CD", "alpha"])} & \Sexpr{pprint(cdxUS["CD", "beta"])} & \Sexpr{pprint(cdxUS["CD", "gamma"])}\\
+            \hline
+            $u$   & \Sexpr{pprint(cduUS["CD", "lambda"], digits=4)} & \Sexpr{pprint(cduUS["CD", "alpha"])} & \Sexpr{pprint(cduUS["CD", "beta"])} & \Sexpr{pprint(cduUS["CD", "gamma"])}\\
+          \end{tabular}
+        \normalsize
+      \end{center}
+    \column{2.2in}
+<<Results_Graph_US_CD, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight>>=
+createCDLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{US}{0.055}
+\end{frame}
+
+<<Coefs_UK_CD>>=
+cdUK <- cobbDouglasData("UK")
+cdqUK <- cobbDouglasData("UK", "Q")
+cdxUK <- cobbDouglasData("UK", "X")
+cduUK <- cobbDouglasData("UK", "U")
+@
+\begin{frame}{Cobb-Douglas $y$ Predictions} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+      \begin{center}
+        \cdeEqn
+        \vspace{\baselineskip}
+
+        \tiny
+          \begin{tabular}{c|c c c c}
+            $e$ & $\lambda$ & $\alpha$ & $\beta$ & $\gamma$\\
+            \hline
+            $-$   & \Sexpr{pprint(cdUK["CD", "lambda"], digits=4)} & \Sexpr{pprint(cdUK["CD", "alpha"])} & \Sexpr{pprint(cdUK["CD", "beta"])} & \Sexpr{pprint(cdUK["CD", "gamma"])}\\
+            \hline
+            $q$   & \Sexpr{pprint(cdqUK["CD", "lambda"], digits=4)} & \Sexpr{pprint(cdqUK["CD", "alpha"])} & \Sexpr{pprint(cdqUK["CD", "beta"])} & \Sexpr{pprint(cdqUK["CD", "gamma"])}\\
+            \hline
+            $x$   & \Sexpr{pprint(cdxUK["CD", "lambda"], digits=4)} & \Sexpr{pprint(cdxUK["CD", "alpha"])} & \Sexpr{pprint(cdxUK["CD", "beta"])} & \Sexpr{pprint(cdxUK["CD", "gamma"])}\\
+            \hline
+            $u$   & \Sexpr{pprint(cduUK["CD", "lambda"], digits=4)} & \Sexpr{pprint(cduUK["CD", "alpha"])} & \Sexpr{pprint(cduUK["CD", "beta"])} & \Sexpr{pprint(cduUK["CD", "gamma"])}\\
+          \end{tabular}
+        \normalsize
+      \end{center}
+    \column{2.2in}
+<<Results_Graph_UK_CD, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight>>=
+createCDLatticeGraph("UK", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{UK}{0.055}
+\end{frame}
+
+<<Coefs_ZA_CD>>=
+cdZA <- cobbDouglasData("ZA")
+cdqZA <- cobbDouglasData("ZA", "Q")
+cdxZA <- cobbDouglasData("ZA", "X")
+@
+\begin{frame}{Cobb-Douglas $y$ Predictions} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+      \begin{center}
+        \cdeEqn
+        \vspace{\baselineskip}
+
+        \tiny
+          \begin{tabular}{|c|c|c|c|c|}\hline
+            $e$ & $\lambda$ & $\alpha$ & $\beta$ & $\gamma$\\
+            \hline
+            $-$   & \Sexpr{pprint(cdZA["CD", "lambda"], digits=4)} & \Sexpr{pprint(cdZA["CD", "alpha"])} & \Sexpr{pprint(cdZA["CD", "beta"])} & \Sexpr{pprint(cdZA["CD", "gamma"])}\\
+            \hline
+            $q$   & \Sexpr{pprint(cdqZA["CD", "lambda"], digits=4)} & \Sexpr{pprint(cdqZA["CD", "alpha"])} & \Sexpr{pprint(cdqZA["CD", "beta"])} & \Sexpr{pprint(cdqZA["CD", "gamma"])}\\
+            \hline
+            $x$   & \Sexpr{pprint(cdxZA["CD", "lambda"], digits=4)} & \Sexpr{pprint(cdxZA["CD", "alpha"])} & \Sexpr{pprint(cdxZA["CD", "beta"])} & \Sexpr{pprint(cdxZA["CD", "gamma"])}\\
+            \hline
+          \end{tabular}
+        \normalsize
+      \end{center}
+    \column{2.2in}
+<<Results_Graph_ZA_CD, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+createCDLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{ZA}{0.055}
+\end{frame}
+
+<<Coefs_SA_CD>>=
+cdSA <- cobbDouglasData("SA")
+cdqSA <- cobbDouglasData("SA", "Q")
+cdxSA <- cobbDouglasData("SA", "X")
+@
+\begin{frame}{Cobb-Douglas $y$ Predictions} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+      \begin{center}
+        \cdeEqn
+        \vspace{\baselineskip}
+
+        \tiny
+          \begin{tabular}{|c|c|c|c|c|}\hline
+            $e$ & $\lambda$ & $\alpha$ & $\beta$ & $\gamma$\\
+            \hline
+            $-$   & \Sexpr{cdSA["CD", "lambda"]} & \Sexpr{cdSA["CD", "alpha"]} & \Sexpr{cdSA["CD", "beta"]} & \Sexpr{cdSA["CD", "gamma"]}\\
+            \hline
+            $q$   & \Sexpr{cdqSA["CD", "lambda"]} & \Sexpr{cdqSA["CD", "alpha"]} & \Sexpr{cdqSA["CD", "beta"]} & \Sexpr{cdqSA["CD", "gamma"]}\\
+            \hline
+            $x$   & \Sexpr{cdxSA["CD", "lambda"]} & \Sexpr{cdxSA["CD", "alpha"]} & \Sexpr{cdxSA["CD", "beta"]} & \Sexpr{cdxSA["CD", "gamma"]}\\
+            \hline
+          \end{tabular}
+        \normalsize
+      \end{center}
+    \column{2.2in}
+<<Results_Graph_SA_CD, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+createCDLatticeGraph("SA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{SA}{0.055}
+\end{frame}
+
+\begin{frame}{Beneficial to Include Energy?}  %----------------------------
+<<US_Partial_Residuals_Plot, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
+partialResidualPlot("US", "Q", textScaling=textScaleForGraphs)
+@
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{US}{0.055}
+\end{frame}
+
+\begin{frame}{Beneficial to Include Energy?}  %----------------------------
+<<UK_Partial_Residuals_Plot, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
+partialResidualPlot("UK", "Q", textScaling=textScaleForGraphs)
+@
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{UK}{0.055}
+\end{frame}
+
+\begin{frame}{95\% Confidence Intervals}{Cobb-Douglas with $q$} %----------------------------
+<<CDq_Params_Graph, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
+createCDParamsGraph("Q")
+@  
+\end{frame}
+
+\begin{frame}{Two Important Questions for the\\Cobb-Douglas Model} %----------------------------
+  \begin{center}
+    \cdeEqn
+  \end{center}
+  \begin{itemize}
+    \item{Is energy important for this economy?\\Yes, if $\gamma$ not small.}
+    \vspace{\baselineskip}
+
+    \item{Are we sure? (Is energy statistically significant?)\\Yes, if $CI_{\gamma}$ (95\%) doesn't cross 0.0.}
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{$CI_{\gamma}$ and $\gamma$ in Cobb-Douglas} %----------------------------
   \begin{center}
     \cdeEqn\\
-    $\alpha + \beta + \gamma = 1$\\
-    $0 \leq \alpha, \beta, \gamma \leq 1$
+    \includegraphics<1>[height=2.5in]{figure_other/CI-gamma-1.pdf}
+    \includegraphics<2>[height=2.5in]{figure_other/CI-gamma-2.pdf}
+    \includegraphics<3>[height=2.5in]{figure_other/CI-gamma-3.pdf}
+    \includegraphics<4>[height=2.5in]{figure_other/CI-gamma-4.pdf}
+  \end{center}
+\end{frame}
+
+\begin{frame}{$CI_{\gamma}$ vs. $\gamma$ for Cobb-Douglas with $Q$} %----------------------------
+<<CI_gamma_vs_gamma_Graph, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5>>=
+CIvsParamPlot(model="CDe", param="gamma", energyType="Q")
+@
+\end{frame}
+
+\begin{frame}{Implications from Cobb-Douglas with $Q$} %----------------------------
+  \begin{center}\cdeEqn\end{center}
+  \vspace{\baselineskip}
+
+  \begin{itemize}
+    \item{Energy parameter ($\gamma$) has either}
+      \begin{itemize}
+        \item{Small magnitude (US, JP, CN, SA, IR)}
+        \item{Large CI (ZA, TZ, ZM)}
+        \item{Exception: UK}
+      \end{itemize}
+    \vspace{\baselineskip}
+
+    \pause
+    \item{Direct energy input to economy ($q$) is unimportant as a Cobb-Douglas predictor of economic output ($y$)}
+  \end{itemize}
+\end{frame}
+
+\subsection[CES]{CES} %+++++++++++++++++++++++++++++++++++++++
+
+\minorSeparator{Constant Elasticity of Substitution (CES)}
+
+\begin{frame}{Comments on CES Model Equation} %----------------------------
+  \begin{center} \cesEqn \end{center}
+  \begin{itemize}
+    \item{$\mathrm{e}^{\lambda(t-t_0)}$: Time-dependent technology term}
+    \item{$\delta$: split between ($kl$) and ($e$)}
+    \item{Example: \citet{Stern:2012ey}}
+    \item{$\gamma$, $\lambda$, $\delta_1$, $\rho_1$, $\delta$, $\rho$ estimated by \texttt{cesEst} function in \texttt{R}'s \texttt{micEcon} package}
+  \end{itemize}
+\end{frame}
+
+<<Coefs_US_CES>>=
+cesqUS <- cesData("US", "Q")
+cesxUS <- cesData("US", "X")
+cesuUS <- cesData("US", "U")
+@
+\begin{frame}{CES $y$ Predictions} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+      \begin{center}
+        \tiny \cesEqnNarrow \normalsize
+
+        \vspace{\baselineskip}
+
+        \tiny
+          \begin{tabular}{c|c c c}
+            $e$ & $\gamma$ & $\lambda$ & $\delta_1$\\
+            \hline
+            $q$ & \Sexpr{pprint(cesqUS["CES", "gamma"])} & \Sexpr{pprint(cesqUS["CES", "lambda"], digits=4)} & \Sexpr{pprint(cesqUS["CES", "delta_1"])}\\
+            \hline
+            $x$ & \Sexpr{pprint(cesxUS["CES", "gamma"])} & \Sexpr{pprint(cesxUS["CES", "lambda"], digits=4)} & \Sexpr{pprint(cesxUS["CES", "delta_1"])}\\
+            \hline
+            $u$ & \Sexpr{pprint(cesuUS["CES", "gamma"])} & \Sexpr{pprint(cesuUS["CES", "lambda"], digits=4)} & \Sexpr{pprint(cesuUS["CES", "delta_1"])}\\
+          \end{tabular}
+          \vspace{\baselineskip}
+
+          \begin{tabular}{c|c c c}
+            $e$ & $\sigma_1$ & $\delta$ & $\sigma$\\
+            \hline
+            $q$ & \Sexpr{pprint(cesqUS["CES", "sigma_1"])} & \Sexpr{pprint(cesqUS["CES", "delta"])} & \Sexpr{pprint(cesqUS["CES", "sigma"])}\\
+            \hline
+            $x$ & \Sexpr{pprint(cesxUS["CES", "sigma_1"])} & \Sexpr{pprint(cesxUS["CES", "delta"])} & \Sexpr{pprint(cesxUS["CES", "sigma"])}\\
+            \hline
+            $u$ & \Sexpr{pprint(cesuUS["CES", "sigma_1"])} & \Sexpr{pprint(cesuUS["CES", "delta"])} & \Sexpr{pprint(cesuUS["CES", "sigma"])}\\
+          \end{tabular}
+        \normalsize
+      \end{center}
+    \column{2.2in}
+<<Results_Graph_US_CES, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+createCESLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{US}{0.055}
+\end{frame}
+
+<<Coefs_UK_CES>>=
+cesqUK <- cesData("UK", "Q")
+cesxUK <- cesData("UK", "X")
+cesuUK <- cesData("UK", "U")
+@
+\begin{frame}{CES $y$ Predictions} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+      \begin{center}
+        \tiny \cesEqnNarrow \normalsize
+
+        \vspace{\baselineskip}
+
+        \tiny
+          \begin{tabular}{c|c c c}
+            $e$ & $\gamma$ & $\lambda$ & $\delta_1$\\
+            \hline
+            $q$ & \Sexpr{pprint(cesqUK["CES", "gamma"])} & \Sexpr{pprint(cesqUK["CES", "lambda"], digits=4)} & \Sexpr{pprint(cesqUK["CES", "delta_1"])}\\
+            \hline
+            $x$ & \Sexpr{pprint(cesxUK["CES", "gamma"])} & \Sexpr{pprint(cesxUK["CES", "lambda"], digits=4)} & \Sexpr{pprint(cesxUK["CES", "delta_1"])}\\
+            \hline
+            $u$ & \Sexpr{pprint(cesuUK["CES", "gamma"])} & \Sexpr{pprint(cesuUK["CES", "lambda"], digits=4)} & \Sexpr{pprint(cesuUK["CES", "delta_1"])}\\
+          \end{tabular}
+          \vspace{\baselineskip}
+
+          \begin{tabular}{c|c c c}
+            $e$ & $\sigma_1$ & $\delta$ & $\sigma$\\
+            \hline
+            $q$ & \Sexpr{pprint(cesqUK["CES", "sigma_1"])} & \Sexpr{pprint(cesqUK["CES", "delta"])} & \Sexpr{pprint(cesqUK["CES", "sigma"])}\\
+            \hline
+            $x$ & \Sexpr{pprint(cesxUK["CES", "sigma_1"])} & \Sexpr{pprint(cesxUK["CES", "delta"])} & \Sexpr{pprint(cesxUK["CES", "sigma"])}\\
+            \hline
+            $u$ & \Sexpr{pprint(cesuUK["CES", "sigma_1"])} & \Sexpr{pprint(cesuUK["CES", "delta"])} & \Sexpr{pprint(cesuUK["CES", "sigma"])}\\
+          \end{tabular}
+        \normalsize
+      \end{center}
+    \column{2.2in}
+<<Results_Graph_UK_CES, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+createCESLatticeGraph("UK", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{UK}{0.055}
+\end{frame}
+
+<<Coefs_ZA_CES>>=
+cesqZA <- cesData("ZA", "Q")
+cesxZA <- cesData("ZA", "X")
+@
+\begin{frame}{CES $y$ Predictions} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+      \begin{center}
+        \tiny \cesEqnNarrow \normalsize
+        \vspace{\baselineskip}
+
+        \tiny
+          \begin{tabular}{|c|c|c|c|}\hline
+            $e$ & $\gamma$ & $\lambda$ & $\delta_1$\\
+            \hline
+            $q$ & \Sexpr{pprint(cesqZA["CES", "gamma"])} & \Sexpr{pprint(cesqZA["CES", "lambda"], digits=4)} & \Sexpr{pprint(cesqZA["CES", "delta_1"])}\\
+            \hline
+            $x$ & \Sexpr{pprint(cesxZA["CES", "gamma"])} & \Sexpr{pprint(cesxZA["CES", "lambda"], digits=4)} & \Sexpr{pprint(cesxZA["CES", "delta_1"])}\\
+            \hline
+          \end{tabular}
+          \vspace{\baselineskip}
+
+          \begin{tabular}{|c|c|c|c|}\hline
+            $e$ & $\sigma_1$ & $\delta$ & $\sigma$\\
+            \hline
+            $q$ & \Sexpr{pprint(cesqZA["CES", "sigma_1"])} & \Sexpr{pprint(cesqZA["CES", "delta"])} & \Sexpr{pprint(cesqZA["CES", "sigma"])}\\
+            \hline
+            $x$ & \Sexpr{pprint(cesxZA["CES", "sigma_1"])} & \Sexpr{pprint(cesxZA["CES", "delta"])} & \Sexpr{pprint(cesxZA["CES", "sigma"])}\\
+            \hline
+          \end{tabular}
+        \normalsize
+      \end{center}
+    \column{2.2in}
+<<Results_Graph_ZA_CES, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+createCESLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{ZA}{0.055}
+\end{frame}
+
+<<Coefs_SA_CES>>=
+cesqSA <- cesData("SA", "Q")
+cesxSA <- cesData("SA", "X")
+@
+\begin{frame}{CES $y$ Predictions} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+      \begin{center}
+        \tiny \cesEqnNarrow \normalsize
+        \vspace{\baselineskip}
+
+        \tiny
+          \begin{tabular}{|c|c|c|c|}\hline
+            $e$ & $\gamma$ & $\lambda$ & $\delta_1$\\
+            \hline
+            $q$ & \Sexpr{pprint(cesqSA["CES", "gamma"])} & \Sexpr{pprint(cesqSA["CES", "lambda"], digits=4)} & \Sexpr{pprint(cesqSA["CES", "delta_1"])}\\
+            \hline
+            $x$ & \Sexpr{pprint(cesxSA["CES", "gamma"])} & \Sexpr{pprint(cesxSA["CES", "lambda"], digits=4)} & \Sexpr{pprint(cesxSA["CES", "delta_1"])}\\
+            \hline
+          \end{tabular}
+          \vspace{\baselineskip}
+
+          \begin{tabular}{|c|c|c|c|}\hline
+            $e$ & $\sigma_1$ & $\delta$ & $\sigma$\\
+            \hline
+            $q$ & \Sexpr{pprint(cesqSA["CES", "sigma_1"])} & \Sexpr{pprint(cesqSA["CES", "delta"])} & \Sexpr{pprint(cesqSA["CES", "sigma"])}\\
+            \hline
+            $x$ & \Sexpr{pprint(cesxSA["CES", "sigma_1"])} & \Sexpr{pprint(cesxSA["CES", "delta"])} & \Sexpr{pprint(cesxSA["CES", "sigma"])}\\
+            \hline
+          \end{tabular}
+        \normalsize
+      \end{center}
+    \column{2.2in}
+<<Results_Graph_SA_CES, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+createCESLatticeGraph("SA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{SA}{0.055}
+\end{frame}
+
+\begin{frame}{95\% Confidence Intervals}{CES with $q$} %----------------------------
+<<CESq_Params_Graph, fig.width=presentationGraph1ColWidth*1.8, fig.height=presentationGraph1RowHeight*1.8>>=
+createCESParamsGraph("Q")
+@  
+\end{frame}
+
+\begin{frame}{Two Important Questions for\\CES Model} %----------------------------
+  \begin{center}
+    \cesEqn
+  \end{center}
+  \begin{itemize}
+    \item{Is energy important for this economy?\\Yes, if $\delta$ is not large.}
+    \vspace{\baselineskip}
+
+    \item{Are we sure? (Is energy statistically significant?)\\Yes, if $CI_{\delta}$ (95\%) doesn't cross 1.0.}
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{$CI_{\delta}$ and $\delta$ in CES} %----------------------------
+  \begin{center}
+    \cesEqn\\
+    \includegraphics[height=2.5in]{figure_other/CI-delta.pdf}
+  \end{center}
+\end{frame}
+
+\begin{frame}{$CI_{\delta}$ vs. $\delta$ for CES with $Q$} %----------------------------
+<<CI_delta_vs_delta_Graph, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5>>=
+CIvsParamPlot(model="CES", param="delta", energyType="Q")
+@
+\end{frame}
+
+\begin{frame}{Implications from CES} %----------------------------
+  \begin{center} \cesEqn \end{center}
+  \vspace{\baselineskip}
+
+  \begin{itemize}
+    \item{Energy parameter ($\delta$) has either}
+      \begin{itemize}
+        \item{Large magnitude (US, UK, JP, SA, IR)}
+        \item{Large CI (CN, TZ, ZA, ZM)}
+      \end{itemize}
+      \vspace{\baselineskip}          
+      \pause
+
+    \item{Direct energy input to economy ($q$) is unimportant as a CES predictor of economic output ($y$)}
+  \end{itemize}
+\end{frame}
+
+\subsection[LINEX]{LINEX} %+++++++++++++++++++++++++++++++++++++++
+
+\minorSeparator{LINEX} %----------------------------
+
+\begin{frame}{Comments on LINEX Model Equation} %----------------------------
+  \begin{center} \linexEqn \end{center}
+  \begin{itemize}
+    \item{Derived from thermodynamics \citep{Kummel:1980wx}}
+    \item{Time-dependent technology $\rightarrow$ efficiency ratios}
+    \item{Productivity $\uparrow$ if}
+    \begin{itemize}
+      \item{Efficiency of producing capital stock increases ($k$ > $l + e$)}
+      \item{Energy efficiency of labor increases ($l$ > $e$)}
+    \end{itemize}
+    \item{Example: \citet{Warr:2006hc}}
+    \item{$a_0$ and $c_t$ estimated by \texttt{nls} function in \texttt{R}}
+  \end{itemize}
+\end{frame}
+
+<<Coefs_US_LINEX>>=
+linexqUS <- linexData("US", "Q")
+linexxUS <- linexData("US", "X")
+linexuUS <- linexData("US", "U")
+@
+\begin{frame}{LINEX $y$ Predictions} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+      \begin{center}
+        \linexEqn
+
+        \vspace{\baselineskip}
+
+        \tiny
+          \begin{tabular}{c|c c}
+            $e$ & $a_0$ & $c_t$\\
+            \hline
+            $q$ & \Sexpr{pprint(linexqUS["LINEX", "a_0"])} & \Sexpr{pprint(linexqUS["LINEX", "c_t"])}\\
+            \hline
+            $x$ & \Sexpr{pprint(linexxUS["LINEX", "a_0"])} & \Sexpr{pprint(linexxUS["LINEX", "c_t"])}\\
+            \hline
+            $u$ & \Sexpr{pprint(linexuUS["LINEX", "a_0"])} & \Sexpr{pprint(linexuUS["LINEX", "c_t"])}\\
+          \end{tabular}
+        \normalsize
+      \end{center}
+    \column{2.2in}
+<<Results_Graph_US_LINEX, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight>>=
+createLINEXLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{US}{0.055}
+\end{frame}
+
+<<Coefs_UK_LINEX>>=
+linexqUK <- linexData("UK", "Q")
+linexxUK <- linexData("UK", "X")
+linexuUK <- linexData("UK", "U")
+@
+\begin{frame}{LINEX $y$ Predictions} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+      \begin{center}
+        \linexEqn
+
+        \vspace{\baselineskip}
+
+        \tiny
+          \begin{tabular}{c|c c}
+            $e$ & $a_0$ & $c_t$\\
+            \hline
+            $q$ & \Sexpr{pprint(linexqUK["LINEX", "a_0"])} & \Sexpr{pprint(linexqUK["LINEX", "c_t"])}\\
+            \hline
+            $x$ & \Sexpr{pprint(linexxUK["LINEX", "a_0"])} & \Sexpr{pprint(linexxUK["LINEX", "c_t"])}\\
+            \hline
+            $u$ & \Sexpr{pprint(linexuUK["LINEX", "a_0"])} & \Sexpr{pprint(linexuUK["LINEX", "c_t"])}\\
+          \end{tabular}
+        \normalsize
+      \end{center}
+    \column{2.2in}
+<<Results_Graph_UK_LINEX, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight>>=
+createLINEXLatticeGraph("UK", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{UK}{0.055}
+\end{frame}
+
+<<Coefs_ZA_LINEX>>=
+linexqZA <- linexData("ZA", "Q")
+linexxZA <- linexData("ZA", "X")
+@
+\begin{frame}{LINEX $y$ Predictions} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+      \begin{center}
+        \linexEqn
+
+        \vspace{\baselineskip}
+
+        \tiny
+          \begin{tabular}{c|c c}
+            $e$ & $a_0$ & $c_t$\\
+            \hline
+            $q$ & \Sexpr{pprint(linexqZA["LINEX", "a_0"])} & \Sexpr{pprint(linexqZA["LINEX", "c_t"])}\\
+            \hline
+            $x$ & \Sexpr{pprint(linexxZA["LINEX", "a_0"])} & \Sexpr{pprint(linexxZA["LINEX", "c_t"])}\\
+          \end{tabular}
+        \normalsize
+      \end{center}
+    \column{2.2in}
+<<Results_Graph_ZA_LINEX, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight>>=
+createLINEXLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{ZA}{0.055}
+\end{frame}
+
+<<Coefs_SA_LINEX>>=
+linexqSA <- linexData("SA", "Q")
+linexxSA <- linexData("SA", "X")
+@
+\begin{frame}{LINEX $y$ Predictions} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+      \begin{center}
+        \linexEqn
+
+        \vspace{\baselineskip}
+
+        \tiny
+          \begin{tabular}{c|c c}
+            $e$ & $a_0$ & $c_t$\\
+            \hline
+            $q$ & \Sexpr{pprint(linexqSA["LINEX", "a_0"])} & \Sexpr{pprint(linexqSA["LINEX", "c_t"])}\\
+            \hline
+            $x$ & \Sexpr{pprint(linexxSA["LINEX", "a_0"])} & \Sexpr{pprint(linexxSA["LINEX", "c_t"])}\\
+          \end{tabular}
+        \normalsize
+      \end{center}
+    \column{2.2in}
+<<Results_Graph_SA_LINEX, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight>>=
+createLINEXLatticeGraph("SA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
+  % Including at bottom of frame so as not to push other material downward in the frame.
+  \putFlagUpperRight{SA}{0.055}
+\end{frame}
+
+\begin{frame}{Two Important Questions for\\LINEX Model} %----------------------------
+  \begin{center}
+    \linexEqn
+  \end{center}
+  \begin{itemize}
+    \item{Is energy important for this economy?\\Yes, by definition!}
+    \vspace{\baselineskip}
+
+    \item{Are we sure?\\Yes, by definition!}
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{95\% Confidence Intervals}{LINEX with $q$} %----------------------------
+<<LINEXq_Params_Graph, fig.width=presentationGraph1ColWidth*1.8, fig.height=presentationGraph1RowHeight*1.8>>=
+createLINEXParamsGraph("Q")
+@  
+\end{frame}
+
+\begin{frame}{Implications from LINEX} %----------------------------
+  \begin{center}\linexEqn\end{center}
+  \vspace{\baselineskip}
+
+  \begin{itemize}
+    \item{LINEX parameters $a_0$ and $c_t$ are significant (different from 0) for most countries}
+    \item{Direct energy input to economy ($q$) is important as a LINEX predictor of economic output ($y$)}
+    \item{LINEX fits are poorer quality than other model}
+  \end{itemize}
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Summary}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\majorSeparator{Summary}
+
+\begin{frame}{Summary of Analysis} %----------------------------
+  \begin{itemize}
+  \item{Including energy ($E$) in Cobb-Douglas and CES production functions appears to be unwarranted}
+  \pause
+    \begin{itemize}
+      \scriptsize
+      \item{Energy parameters ($\gamma$, $\delta$) less important than others ($\lambda$, $\alpha$, $\beta$) for nearly all countries}
+      \pause
+      \item{Why? Energy is \emph{always already} embedded in capital stock ($K$) and labor ($L$)}
+      \normalsize
+    \end{itemize}
+  \vspace{\baselineskip}
+  \pause
+  \item{Including energy ($E$) in LINEX production function is required}
+  \pause
+    \begin{itemize}
+      \scriptsize
+      \item{One factor of production: energy}
+      \pause
+      \item{$a_0$ and $c_t$ are significant for most countries}
+      \pause
+      \item{Unfortunately, LINEX fits are poorer quality than Cobb-Douglas or CES}
+      \normalsize
+    \end{itemize}
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{The Question} %----------------------------
+  \begin{center}
+    Which economic growth model best describes (statistically) the role of energy in economic growth for different types of economies?
+  \end{center}
+  \vspace{\baselineskip}
+
+  \vspace{\baselineskip}
+
+\end{frame}
+
+\begin{frame}{The ``Answer''} %----------------------------
+  \begin{center}
+    Which economic growth model best describes (statistically) the role of energy in economic growth for different types of economies?
+    \vspace{\baselineskip}
+
+    Answer: Cobb-Douglas or CES without energy
+  \end{center}
+\end{frame}
+
+\begin{frame}{Extra Credit?} %----------------------------
+  \begin{center} Reflect dynamics of energy cost share and price spikes? \end{center}
+    \vspace{\baselineskip}
+
+    \pause
+  \begin{itemize}
+    \item{Price, cost share exogenous to all models}
+    \pause
+    \item{No extra credit!}
+    \pause
+    \vspace{\baselineskip}
+
+    \item{Models (CD and CES without energy) could be \emph{included within} a model that endogenizes price and cost share}
+    \pause
+    \item{Still searching for a modeling approach that captures price and cost share dynamics \\ \scriptsize System dynamics modeling? \normalsize}
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Next Steps (Summer 2013)} %----------------------------
+  \begin{itemize}
+    \item{Verify and improve estimates of statistical properties for \emph{all} fitting parameters}
+    \vspace{\baselineskip}
+    \item{Incorporate all constraints for Cobb-Douglas model}
+    \vspace{\baselineskip}
+    \item{Submit paper}
+  \end{itemize}  
+\end{frame}
+
+\begin{frame}{Acknowledgements} %----------------------------
+  \begin{itemize}
+    \item{Martin de Wit, Stellenbosch University}
+    \item{Randall Pruim, Calvin College}
+    \item{Loren L. Heun, Western Michigan University}
+    \vspace{\baselineskip}
+    \item{Jack and Lois Kuipers Applied Mathematics Endowment\\(Reese and Timmer Summer 2012 funding)}
+    \item{Calvin College Alumni Association\\(Reese Fall 2012 funding)}
+  \end{itemize}  
+\end{frame}
+
+\begin{frame}{References} %----------------------------
+  \bibliographystyle{plainnat}
+  \tiny
+    \bibliography{EconGrowth.bib}
+  \normalsize
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Appendix}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\majorSeparator{Appendix}
+
+\minorSeparator{Introduction} %----------------------------
+
+\begin{frame}{Energy Cost Share}{\citep{Bashmakov:2007ek}} %----------------------------
+  \begin{center}
+    \includegraphics[height=6.3cm]{figure_other/Figure_Bashmakov_2007.pdf}
+  \end{center}
+\end{frame}
+
+\begin{frame}{Energy Cost Share}{\citep{Tverberg:2013a}} %----------------------------
+  \begin{center}
+    \includegraphics[height=6.0cm]{figure_other/Figure_Tverberg_2013a.png}
+  \end{center}
+\end{frame}
+
+\begin{frame}{Japan and China} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+<<Historical_Data_JP, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+createHistoricalLatticeGraph("JP", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@    
+    \column{2.2in}
+<<Historical_Data_CN, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+createHistoricalLatticeGraph("CN", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
+  \putat{flag/flag_JP.png}{0.055}{-0.73in}{1.0in}
+  \putat{flag/flag_CN.png}{0.055}{ 1.50in}{1.0in}
+\end{frame}
+
+\begin{frame}{Saudi Arabia and Iran} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+<<Historical_Data_SA_Appendix, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+createHistoricalLatticeGraph("SA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@    
+    \column{2.2in}
+<<Historical_Data_IR, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+createHistoricalLatticeGraph("IR", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
+  \putat{flag/flag_SA.png}{0.055}{-0.73in}{1.0in}
+  \putat{flag/flag_IR.png}{0.055}{ 1.50in}{1.0in}
+\end{frame}
+
+\begin{frame}{Tanzania and Zambia} %----------------------------
+  \begin{columns}[c]
+    \column{2.2in}
+<<Historical_Data_TZ, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+createHistoricalLatticeGraph("TZ", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@    
+    \column{2.2in}
+<<Historical_Data_ZM, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
+createHistoricalLatticeGraph("ZM", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+@
+  \end{columns}
+  \putat{flag/flag_TZ.png}{0.055}{-0.73in}{1.0in}
+  \putat{flag/flag_ZM.png}{0.055}{ 1.50in}{1.0in}
+\end{frame}
+
+\minorSeparator{Single-factor Model}
+
+\begin{frame}{95\% Confidence Intervals}{Single-factor with $K$} %----------------------------
+<<SF_Params_Graph_K, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
+createSFParamsGraph("K")
+@  
+\end{frame}
+
+\begin{frame}{95\% Confidence Intervals}{Single-factor with $L$} %----------------------------
+<<SF_Params_Graph_L, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
+createSFParamsGraph("L")
+@  
+\end{frame}
+
+\minorSeparator{Cobb-Douglas Model}
+
+\begin{frame}{Cobb-Douglas (without Energy)} %----------------------------
+  \begin{center}
+    \cdEqn\\
+    $\alpha + \beta = 1$\\
+    $0 \leq \alpha, \beta \leq 1$
     \vspace{\baselineskip}
@@
       \lRow\\
-      \eRow\\
       \hline
@@
       \betaRow\\
-      \gammaRow\\
-      \hline
-    \end{tabular}
-  \end{center}
-\end{frame}
-
-\begin{frame}{Comments on Cobb-Douglas Model Equation} %----------------------------
-  \begin{center} \cdeEqn \end{center}
-  \begin{itemize}
-    \item{$\mathrm{e}^{\lambda(t-t_0)}$: Time-dependent technology term}
-    \item{$k$, $l$, and $e$ factors of production ``blend'' with $\alpha + \beta + \gamma = 1$}
-    \item{Example: \citet{Froling:2009vo}}
-  \end{itemize}
-\end{frame}
-
-\begin{frame}{Parameter Estimation for Cobb-Douglas With Energy} %----------------------------
-  \begin{center}\cdeEqn\end{center}
-  \begin{itemize}
-    \item{Objective: determine $\lambda$, $\alpha$, $\beta$, and $\gamma$ that best fits historical data}
-    \item{Perform grid search over $\gamma$: Re-estimate $\lambda$, $\alpha$, and $\beta$ at each value of $\gamma$}
-    \item{Respect sum constraint: $\alpha + \beta + \gamma = 1$}
-    \item{Respect absolute constraints: $0 \leq \alpha, \beta, \gamma \leq 1$} (not yet)
-    \item{$\lambda$, $\alpha$, $\beta$, and $\gamma$ estimated by \texttt{nls} function in \texttt{R}}
-  \end{itemize}
-\end{frame}
-
-\begin{frame}{Grid Search Over $\gamma$}{US Cobb-Douglas with $Q$} %----------------------------
-<<CDeGammaGraphsUS, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
-  cdeGridGraph("US", "Q", textScaling=0.8)
-@
-  % Including at bottom of frame so as not to push other material downward in the frame.
-  \putFlagUpperRight{US}{0.055}
-\end{frame}
-
-\begin{frame}{Grid Search Over $\gamma$}{UK Cobb-Douglas with $Q$} %----------------------------
-<<CDeGammaGraphsUK, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
-  cdeGridGraph("UK", "Q", textScaling=0.8)
-@
-  % Including at bottom of frame so as not to push other material downward in the frame.
-  \putFlagUpperRight{UK}{0.045}
-\end{frame}
-
-<<pprint>>=
-pprint <- function(num, digits = 2){
-  out <- formatC(num, digit=digits, format="f")
-  return(out)
-}
-@
-
-<<Coefs_US_CD>>=
-cdUS <- cobbDouglasData("US")
-cdqUS <- cobbDouglasData("US", "Q")
-cdxUS <- cobbDouglasData("US", "X")
-cduUS <- cobbDouglasData("US", "U")
-@
-\begin{frame}{Cobb-Douglas $y$ Predictions} %----------------------------
-  \begin{columns}[c]
-    \column{2.2in}
-      \begin{center}
-        \cdeEqn
-        \vspace{\baselineskip}
-
-        \tiny
-          \begin{tabular}{c|c c c c}
-            $e$ & $\lambda$ & $\alpha$ & $\beta$ & $\gamma$\\
-            \hline
-                  & \Sexpr{pprint(cdUS["CD", "lambda"], digits=4)} & \Sexpr{pprint(cdUS["CD", "alpha"])} & \Sexpr{pprint(cdUS["CD", "beta"])} & \Sexpr{pprint(cdUS["CD", "gamma"])}\\
-            \hline
-            $q$   & \Sexpr{pprint(cdqUS["CD", "lambda"], digits=4)} & \Sexpr{pprint(cdqUS["CD", "alpha"])} & \Sexpr{pprint(cdqUS["CD", "beta"])} & \Sexpr{pprint(cdqUS["CD", "gamma"])}\\
-            \hline
-            $x$   & \Sexpr{pprint(cdxUS["CD", "lambda"], digits=4)} & \Sexpr{pprint(cdxUS["CD", "alpha"])} & \Sexpr{pprint(cdxUS["CD", "beta"])} & \Sexpr{pprint(cdxUS["CD", "gamma"])}\\
-            \hline
-            $u$   & \Sexpr{pprint(cduUS["CD", "lambda"], digits=4)} & \Sexpr{pprint(cduUS["CD", "alpha"])} & \Sexpr{pprint(cduUS["CD", "beta"])} & \Sexpr{pprint(cduUS["CD", "gamma"])}\\
-          \end{tabular}
-        \normalsize
-      \end{center}
-    \column{2.2in}
-<<Results_Graph_US_CD, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight>>=
-createCDLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
-@
-  \end{columns}
-  % Including at bottom of frame so as not to push other material downward in the frame.
-  \putFlagUpperRight{US}{0.055}
-\end{frame}
-
-<<Coefs_UK_CD>>=
-cdUK <- cobbDouglasData("UK")
-cdqUK <- cobbDouglasData("UK", "Q")
-cdxUK <- cobbDouglasData("UK", "X")
-cduUK <- cobbDouglasData("UK", "U")
-@
-\begin{frame}{Cobb-Douglas $y$ Predictions} %----------------------------
-  \begin{columns}[c]
-    \column{2.2in}
-      \begin{center}
-        \cdeEqn
-        \vspace{\baselineskip}
-
-        \tiny
-          \begin{tabular}{c|c c c c}
-            $e$ & $\lambda$ & $\alpha$ & $\beta$ & $\gamma$\\
-            \hline
-                  & \Sexpr{pprint(cdUK["CD", "lambda"], digits=4)} & \Sexpr{pprint(cdUK["CD", "alpha"])} & \Sexpr{pprint(cdUK["CD", "beta"])} & \Sexpr{pprint(cdUK["CD", "gamma"])}\\
-            \hline
-            $q$   & \Sexpr{pprint(cdqUK["CD", "lambda"], digits=4)} & \Sexpr{pprint(cdqUK["CD", "alpha"])} & \Sexpr{pprint(cdqUK["CD", "beta"])} & \Sexpr{pprint(cdqUK["CD", "gamma"])}\\
-            \hline
-            $x$   & \Sexpr{pprint(cdxUK["CD", "lambda"], digits=4)} & \Sexpr{pprint(cdxUK["CD", "alpha"])} & \Sexpr{pprint(cdxUK["CD", "beta"])} & \Sexpr{pprint(cdxUK["CD", "gamma"])}\\
-            \hline
-            $u$   & \Sexpr{pprint(cduUK["CD", "lambda"], digits=4)} & \Sexpr{pprint(cduUK["CD", "alpha"])} & \Sexpr{pprint(cduUK["CD", "beta"])} & \Sexpr{pprint(cduUK["CD", "gamma"])}\\
-          \end{tabular}
-        \normalsize
-      \end{center}
-    \column{2.2in}
-<<Results_Graph_UK_CD, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight>>=
-createCDLatticeGraph("UK", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
-@
-  \end{columns}
-  % Including at bottom of frame so as not to push other material downward in the frame.
-  \putFlagUpperRight{UK}{0.055}
-\end{frame}
-
-\begin{frame}{Beneficial to Include Energy?}  %----------------------------
-<<US_Partial_Residuals_Plot, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
-partialResidualPlot("US", "Q", textScaling=textScaleForGraphs)
-@
-  % Including at bottom of frame so as not to push other material downward in the frame.
-  \putFlagUpperRight{US}{0.055}
-\end{frame}
-
-\begin{frame}{Beneficial to Include Energy?}  %----------------------------
-<<UK_Partial_Residuals_Plot, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
-partialResidualPlot("UK", "Q", textScaling=textScaleForGraphs)
-@
-  % Including at bottom of frame so as not to push other material downward in the frame.
-  \putFlagUpperRight{UK}{0.055}
-\end{frame}
-
-\begin{frame}{95\% Confidence Intervals}{Cobb-Douglas with $q$} %----------------------------
-<<CDq_Params_Graph, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
-createCDParamsGraph("Q")
-@  
-\end{frame}
-
-\begin{frame}{Two Important Questions for the\\Cobb-Douglas Model} %----------------------------
-  \begin{center}
-    \cdeEqn
-  \end{center}
-  \begin{itemize}
-    \item{Is energy important for this economy?\\Yes, if $\gamma$ not small.}
-    \vspace{\baselineskip}
-
-    \item{Are we sure? (Is energy statistically significant?)\\Yes, if $CI_{\gamma}$ (95\%) doesn't cross 0.0.}
-  \end{itemize}
-\end{frame}
-
-\begin{frame}{$CI_{\gamma}$ and $\gamma$ in Cobb-Douglas} %----------------------------
-  \begin{center}
-    \cdeEqn\\
-    \includegraphics<1>[height=2.5in]{figure_other/CI-gamma-1.pdf}
-    \includegraphics<2>[height=2.5in]{figure_other/CI-gamma-2.pdf}
-    \includegraphics<3>[height=2.5in]{figure_other/CI-gamma-3.pdf}
-    \includegraphics<4>[height=2.5in]{figure_other/CI-gamma-4.pdf}
-  \end{center}
-\end{frame}
-
-\begin{frame}{$CI_{\gamma}$ vs. $\gamma$ for Cobb-Douglas with $Q$} %----------------------------
-<<CI_gamma_vs_gamma_Graph, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5>>=
-CIvsParamPlot(model="CDe", param="gamma", energyType="Q")
-@
-\end{frame}
-
-\begin{frame}{Implications from Cobb-Douglas with $Q$} %----------------------------
-  \begin{center}\cdeEqn\end{center}
-  \vspace{\baselineskip}
-
-  \begin{itemize}
-    \item{Energy parameter ($\gamma$) has either}
-      \begin{itemize}
-        \item{Small magnitude (US, JP, CN, SA, IR)}
-        \item{Large CI (ZA, TZ, ZM)}
-        \item{Exception: UK}
-      \end{itemize}
-    \vspace{\baselineskip}
-
-    \pause
-    \item{Direct energy input to economy ($q$) is unimportant as a Cobb-Douglas predictor of economic output ($y$)}
-  \end{itemize}
-\end{frame}
-
-\subsection[CES]{CES} %+++++++++++++++++++++++++++++++++++++++
-
-\minorSeparator{Constant Elasticity of Substitution (CES)}
-
-\begin{frame}{Constant Elasticity of Substitution (CES)} %----------------------------
-  \begin{center}
-    \small
-      \cesEqn
-    \normalsize
-    \vspace{\baselineskip}
-
-    \begin{tabular}{|c|l|}\hline
-      \yRow\\
-      \timeRow\\
-      \initialTimeRow\\
-      \kRow\\
-      \lRow\\
-      \eRow\\
-      \hline
-      $\gamma$   &   fitting coefficient\\
-      \lambdaRow\\
-      $\delta_1$   &   split between ($k$) and ($l$)\\
-      $\rho_1$     &   ``influence'' of ($k$) vs. ($l$)\\
-      $\delta$   &   split between ($kl$) and ($e$)\\
-      $\rho$     &   ``influence'' of ($kl$) vs. ($e$)\\
-      \hline
-    \end{tabular}
-  \end{center}
-\end{frame}
-
-\begin{frame}{Comments on CES Model Equation} %----------------------------
-  \begin{center} \small \cesEqn \normalsize \end{center}
-  \begin{itemize}
-    \item{$\mathrm{e}^{\lambda(t-t_0)}$: Time-dependent technology term}
-    \item{$\delta$: split between ($kl$) and ($e$)}
-    \item{Example: \citet{Stern:2012ey}}
-    \item{$\gamma$, $\lambda$, $\delta_1$, $\rho_1$, $\delta$, $\rho$ estimated by \texttt{cesEst} function in \texttt{R}'s \texttt{micEcon} package}
-  \end{itemize}
-\end{frame}
-
-<<Coefs_US_CES>>=
-cesqUS <- cesData("US", "Q")
-cesxUS <- cesData("US", "X")
-cesuUS <- cesData("US", "U")
-@
-\begin{frame}{CES $y$ Predictions} %----------------------------
-  \begin{columns}[c]
-    \column{2.2in}
-      \begin{center}
-        \tiny \cesEqnNarrow \normalsize
-
-        \vspace{\baselineskip}
-
-        \tiny
-          \begin{tabular}{c|c c c}
-            $e$ & $\gamma$ & $\lambda$ & $\delta_1$\\
-            \hline
-            $q$ & \Sexpr{pprint(cesqUS["CES", "gamma"])} & \Sexpr{pprint(cesqUS["CES", "lambda"], digits=4)} & \Sexpr{pprint(cesqUS["CES", "delta_1"])}\\
-            \hline
-            $x$ & \Sexpr{pprint(cesxUS["CES", "gamma"])} & \Sexpr{pprint(cesxUS["CES", "lambda"], digits=4)} & \Sexpr{pprint(cesxUS["CES", "delta_1"])}\\
-            \hline
-            $u$ & \Sexpr{pprint(cesuUS["CES", "gamma"])} & \Sexpr{pprint(cesuUS["CES", "lambda"], digits=4)} & \Sexpr{pprint(cesuUS["CES", "delta_1"])}\\
-          \end{tabular}
-          \vspace{\baselineskip}
-
-          \begin{tabular}{c|c c c}
-            $e$ & $\sigma_1$ & $\delta$ & $\sigma$\\
-            \hline
-            $q$ & \Sexpr{pprint(cesqUS["CES", "sigma_1"])} & \Sexpr{pprint(cesqUS["CES", "delta"])} & \Sexpr{pprint(cesqUS["CES", "sigma"])}\\
-            \hline
-            $x$ & \Sexpr{pprint(cesxUS["CES", "sigma_1"])} & \Sexpr{pprint(cesxUS["CES", "delta"])} & \Sexpr{pprint(cesxUS["CES", "sigma"])}\\
-            \hline
-            $u$ & \Sexpr{pprint(cesuUS["CES", "sigma_1"])} & \Sexpr{pprint(cesuUS["CES", "delta"])} & \Sexpr{pprint(cesuUS["CES", "sigma"])}\\
-          \end{tabular}
-        \normalsize
-      \end{center}
-    \column{2.2in}
-<<Results_Graph_US_CES, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-createCESLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
-@
-  \end{columns}
-  % Including at bottom of frame so as not to push other material downward in the frame.
-  \putFlagUpperRight{US}{0.055}
-\end{frame}
-
-\begin{frame}{95\% Confidence Intervals}{CES with $q$} %----------------------------
-<<CESq_Params_Graph, fig.width=presentationGraph1ColWidth*1.8, fig.height=presentationGraph1RowHeight*1.8>>=
-createCESParamsGraph("Q")
-@  
-\end{frame}
-
-\begin{frame}{Two Important Questions for\\CES Model} %----------------------------
-  \begin{center}
-    \small \cesEqn \normalsize
-  \end{center}
-  \begin{itemize}
-    \item{Is energy important for this economy?\\Yes, if $\delta$ is not large.}
-    \vspace{\baselineskip}
-
-    \item{Are we sure? (Is energy statistically significant?)\\Yes, if $CI_{\delta}$ (95\%) doesn't cross 0.0.}
-  \end{itemize}
-\end{frame}
-
-\begin{frame}{$CI_{\delta}$ and $\delta$ in CES} %----------------------------
-  \begin{center}
-    \small\cesEqn\normalsize\\
-    \includegraphics[height=2.5in]{figure_other/CI-delta.pdf}
-  \end{center}
-\end{frame}
-
-\begin{frame}{$CI_{\delta}$ vs. $\delta$ for CES with $Q$} %----------------------------
-<<CI_delta_vs_delta_Graph, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5>>=
-CIvsParamPlot(model="CES", param="delta", energyType="Q")
-@
-\end{frame}
-
-\begin{frame}{Implications from CES} %----------------------------
-  \begin{center}\small\cesEqn\normalsize\end{center}
-  \vspace{\baselineskip}
-
-  \begin{itemize}
-    \item{Energy parameter ($\delta$) has either}
-      \begin{itemize}
-        \item{Large magnitude (US, UK, JP, SA, IR)}
-        \item{Large CI (CN, TZ, ZA, ZM)}
-      \end{itemize}
-      \vspace{\baselineskip}          
-      \pause
-
-    \item{Direct energy input to economy ($q$) is unimportant as a CES predictor of economic output ($y$)}
-  \end{itemize}
-\end{frame}
-
-\subsection[LINEX]{LINEX} %+++++++++++++++++++++++++++++++++++++++
-
-\minorSeparator{LINEX} %----------------------------
-
-\begin{frame}{LINEX} %----------------------------
-  \begin{center}
-    \linexEqn
-    \vspace{\baselineskip}
-
-    \begin{tabular}{|c|l|}\hline
-      \kRow\\
-      \lRow\\
-      \eRow\\
-      \hline
-      $a_0$ & fitting parameter\\
-      $c_t$ & fitting parameter\\
-      \hline
-    \end{tabular}
-  \end{center}
-\end{frame}
-
-\begin{frame}{Comments on LINEX Model Equation} %----------------------------
-  \begin{center} \linexEqn \end{center}
-  \begin{itemize}
-    \item{Derived from thermodynamics \citep{Kummel:1980wx}}
-    \item{Time-dependent technology $\rightarrow$ efficiency ratios}
-    \item{Productivity $\uparrow$ if}
-    \begin{itemize}
-      \item{Efficiency of producing capital stock increases ($k$ > $l + e$)}
-      \item{Energy efficiency of labor increases ($l$ > $e$)}
-    \end{itemize}
-    \item{Example: \citet{Warr:2006hc}}
-    \item{$a_0$ and $c_t$ estimated by \texttt{nls} function in \texttt{R}}
-  \end{itemize}
-\end{frame}
-
-<<Coefs_US_LINEX>>=
-linexqUS <- linexData("US", "Q")
-linexxUS <- linexData("US", "X")
-linexuUS <- linexData("US", "U")
-@
-\begin{frame}{LINEX $y$ Predictions} %----------------------------
-  \begin{columns}[c]
-    \column{2.2in}
-      \begin{center}
-        \linexEqn
-
-        \vspace{\baselineskip}
-
-        \tiny
-          \begin{tabular}{c|c c}
-            $e$ & $a_0$ & $c_t$\\
-            \hline
-            $q$ & \Sexpr{pprint(linexqUS["LINEX", "a_0"])} & \Sexpr{pprint(linexqUS["LINEX", "c_t"])}\\
-            \hline
-            $x$ & \Sexpr{pprint(linexxUS["LINEX", "a_0"])} & \Sexpr{pprint(linexxUS["LINEX", "c_t"])}\\
-            \hline
-            $u$ & \Sexpr{pprint(linexuUS["LINEX", "a_0"])} & \Sexpr{pprint(linexuUS["LINEX", "c_t"])}\\
-          \end{tabular}
-        \normalsize
-      \end{center}
-    \column{2.2in}
-<<Results_Graph_US_LINEX, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight>>=
-createLINEXLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
-@
-  \end{columns}
-  % Including at bottom of frame so as not to push other material downward in the frame.
-  \putFlagUpperRight{US}{0.055}
-\end{frame}
-
-<<Coefs_UK_LINEX>>=
-linexqUK <- linexData("UK", "Q")
-linexxUK <- linexData("UK", "X")
-linexuUK <- linexData("UK", "U")
-@
-\begin{frame}{LINEX $y$ Predictions} %----------------------------
-  \begin{columns}[c]
-    \column{2.2in}
-      \begin{center}
-        \linexEqn
-
-        \vspace{\baselineskip}
-
-        \tiny
-          \begin{tabular}{c|c c}
-            $e$ & $a_0$ & $c_t$\\
-            \hline
-            $q$ & \Sexpr{pprint(linexqUK["LINEX", "a_0"])} & \Sexpr{pprint(linexqUK["LINEX", "c_t"])}\\
-            \hline
-            $x$ & \Sexpr{pprint(linexxUK["LINEX", "a_0"])} & \Sexpr{pprint(linexxUK["LINEX", "c_t"])}\\
-            \hline
-            $u$ & \Sexpr{pprint(linexuUK["LINEX", "a_0"])} & \Sexpr{pprint(linexuUK["LINEX", "c_t"])}\\
-          \end{tabular}
-        \normalsize
-      \end{center}
-    \column{2.2in}
-<<Results_Graph_UK_LINEX, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight>>=
-createLINEXLatticeGraph("UK", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
-@
-  \end{columns}
-  % Including at bottom of frame so as not to push other material downward in the frame.
-  \putFlagUpperRight{UK}{0.055}
-\end{frame}
-
-<<Coefs_ZA_LINEX>>=
-linexqZA <- linexData("ZA", "Q")
-linexxZA <- linexData("ZA", "X")
-@
-\begin{frame}{LINEX $y$ Predictions} %----------------------------
-  \begin{columns}[c]
-    \column{2.2in}
-      \begin{center}
-        \linexEqn
-
-        \vspace{\baselineskip}
-
-        \tiny
-          \begin{tabular}{c|c c}
-            $e$ & $a_0$ & $c_t$\\
-            \hline
-            $q$ & \Sexpr{pprint(linexqZA["LINEX", "a_0"])} & \Sexpr{pprint(linexqZA["LINEX", "c_t"])}\\
-            \hline
-            $x$ & \Sexpr{pprint(linexxZA["LINEX", "a_0"])} & \Sexpr{pprint(linexxZA["LINEX", "c_t"])}\\
-          \end{tabular}
-        \normalsize
-      \end{center}
-    \column{2.2in}
-<<Results_Graph_ZA_LINEX, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight>>=
-createLINEXLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
-@
-  \end{columns}
-  % Including at bottom of frame so as not to push other material downward in the frame.
-  \putFlagUpperRight{ZA}{0.055}
-\end{frame}
-
-<<Coefs_SA_LINEX>>=
-linexqSA <- linexData("SA", "Q")
-linexxSA <- linexData("SA", "X")
-@
-\begin{frame}{LINEX $y$ Predictions} %----------------------------
-  \begin{columns}[c]
-    \column{2.2in}
-      \begin{center}
-        \linexEqn
-
-        \vspace{\baselineskip}
-
-        \tiny
-          \begin{tabular}{c|c c}
-            $e$ & $a_0$ & $c_t$\\
-            \hline
-            $q$ & \Sexpr{pprint(linexqSA["LINEX", "a_0"])} & \Sexpr{pprint(linexqSA["LINEX", "c_t"])}\\
-            \hline
-            $x$ & \Sexpr{pprint(linexxSA["LINEX", "a_0"])} & \Sexpr{pprint(linexxSA["LINEX", "c_t"])}\\
-          \end{tabular}
-        \normalsize
-      \end{center}
-    \column{2.2in}
-<<Results_Graph_SA_LINEX, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight>>=
-createLINEXLatticeGraph("SA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
-@
-  \end{columns}
-  % Including at bottom of frame so as not to push other material downward in the frame.
-  \putFlagUpperRight{SA}{0.055}
-\end{frame}
-
-\begin{frame}{Two Important Questions for\\LINEX Model} %----------------------------
-  \begin{center}
-    \linexEqn
-  \end{center}
-  \begin{itemize}
-    \item{Is energy important for this economy?\\Yes, by definition!}
-    \vspace{\baselineskip}
-
-    \item{Are we sure?\\Yes, by definition!}
-  \end{itemize}
-\end{frame}
-
-\begin{frame}{95\% Confidence Intervals}{LINEX with $q$} %----------------------------
-<<LINEXq_Params_Graph, fig.width=presentationGraph1ColWidth*1.8, fig.height=presentationGraph1RowHeight*1.8>>=
-createLINEXParamsGraph("Q")
-@  
-\end{frame}
-
-\begin{frame}{Implications from LINEX} %----------------------------
-  \begin{center}\linexEqn\end{center}
-  \vspace{\baselineskip}
-
-  \begin{itemize}
-    \item{LINEX parameters $a_0$ and $c_t$ are significant (different from 0) for most countries}
-    \item{Direct energy input to economy ($q$) is important as a LINEX predictor of economic output ($y$)}
-  \end{itemize}
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Summary}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\majorSeparator{Summary}
-
-\begin{frame}{Summary of Analysis} %----------------------------
-  \begin{itemize}
-  \item{Including energy ($E$) in Cobb-Douglas and CES production functions appears to be unwarranted}
-  \pause
-    \begin{itemize}
-      \scriptsize
-      \item{Energy parameters less significant than others for most countries}
-      \pause
-      \item{Why? Energy is \emph{always already} embedded in capital stock ($K$) and labor ($L$)}
-      \normalsize
-    \end{itemize}
-  \vspace{\baselineskip}
-  \pause
-  \item{Including energy ($E$) in LINEX production function is required}
-  \pause
-    \begin{itemize}
-      \scriptsize
-      \item{One factor of production: energy}
-      \pause
-      \item{Statistical evidence indicates that LINEX parameters $a_0$ and $c_t$ are significant for most countries}
-      \pause
-      \item{Unfortunately, LINEX fits are worse overall than Cobb-Douglas or CES}
-      \normalsize
-    \end{itemize}
-  \end{itemize}
-\end{frame}
-
-\begin{frame}{The Question} %----------------------------
-  \begin{center}
-    Which economic growth model best describes (statistically) the role of energy in economic growth for different types of economies?
-  \end{center}
-  \vspace{\baselineskip}
-
-  \vspace{\baselineskip}
-
-\end{frame}
-
-\begin{frame}{The ``Answer''} %----------------------------
-  \begin{center}
-    Which economic growth model best describes (statistically) the role of energy in economic growth for different types of economies?
-    \vspace{\baselineskip}
-
-    Answer: Cobb-Douglas or CES without energy
-  \end{center}
-\end{frame}
-
-\begin{frame}{Extra Credit?} %----------------------------
-  \begin{center} Reflect dynamics of energy cost share and price spikes? \end{center}
-    \vspace{\baselineskip}
-
-    \pause
-  \begin{itemize}
-    \item{Price, cost share exogenous to all models}
-    \pause
-    \item{No extra credit!}
-    \pause
-    \vspace{\baselineskip}
-
-    \item{Models (CD and CES without energy) could be \emph{included within} a model that endogenizes price and cost share}
-    \pause
-    \item{Still searching for a modeling approach that captures price and cost share dynamics \\ \scriptsize System dynamics modeling? \normalsize}
-  \end{itemize}
-\end{frame}
-
-\begin{frame}{Next Steps (Summer 2013)} %----------------------------
-  \begin{itemize}
-    \item{Verify and improve estimates of statistical properties for \emph{all} fitting parameters}
-    \vspace{\baselineskip}
-    \item{Incorporate all constraints for Cobb-Douglas model}
-    \vspace{\baselineskip}
-    \item{Complete paper for \emph{Energy Economics}}
-  \end{itemize}  
-\end{frame}
-
-\begin{frame}{Acknowledgements} %----------------------------
-  \begin{itemize}
-    \item{Martin de Wit, Stellenbosch University}
-    \item{Randall Pruim, Calvin College}
-    \item{Loren L. Heun, Western Michigan University}
-    \vspace{\baselineskip}
-    \item{Jack and Lois Kuipers Applied Mathematics Endowment\\(Reese and Timmer Summer 2012 funding)}
-    \item{Calvin College Alumni Association\\(Reese Fall 2012 funding)}
-  \end{itemize}  
-\end{frame}
-
-\begin{frame}{References} %----------------------------
-  \bibliographystyle{plainnat}
-  \tiny
-    \bibliography{EconGrowth.bib}
-  \normalsize
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Appendix}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\majorSeparator{Appendix}
-
-\minorSeparator{Introduction} %----------------------------
-
-\begin{frame}{Energy Cost Share}{\citep{Tverberg:2013a}} %----------------------------
-  \begin{center}
-    \includegraphics[height=6.0cm]{figure_other/Figure_Tverberg_2013a.png}
-  \end{center}
-\end{frame}
-
-\minorSeparator{Single-factor Model}
-
-\begin{frame}{95\% Confidence Intervals}{Single-factor with $K$} %----------------------------
-<<SF_Params_Graph_K, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
-createSFParamsGraph("K")
-@  
-\end{frame}
-
-\begin{frame}{95\% Confidence Intervals}{Single-factor with $L$} %----------------------------
-<<SF_Params_Graph_L, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
-createSFParamsGraph("L")
-@  
-\end{frame}
-
-\minorSeparator{Cobb-Douglas Model}
-
-\begin{frame}{Cobb-Douglas (without Energy)} %----------------------------
-  \begin{center}
-    \cdEqn\\
-    $\alpha + \beta = 1$\\
-    $0 \leq \alpha, \beta \leq 1$
-    \vspace{\baselineskip}
-
-    \begin{tabular}{|c|l|}\hline
-      \yRow\\
-      \timeRow\\
-      \initialTimeRow\\
-      \kRow\\
-      \lRow\\
-      \hline
-      \lambdaRow\\
-      \alphaRow\\
-      \betaRow\\
       \hline
@@
 @  
-\end{frame}
-
-<<Coefs_ZA_CD>>=
-cdZA <- cobbDouglasData("ZA")
-cdqZA <- cobbDouglasData("ZA", "Q")
-cdxZA <- cobbDouglasData("ZA", "X")
-@
-\begin{frame}{Cobb-Douglas $y$ Predictions} %----------------------------
-  \begin{columns}[c]
-    \column{2.2in}
-      \begin{center}
-        \cdeEqn
-        \vspace{\baselineskip}
-
-        \tiny
-          \begin{tabular}{|c|c|c|c|c|}\hline
-            $e$ & $\lambda$ & $\alpha$ & $\beta$ & $\gamma$\\
-            \hline
-                  & \Sexpr{pprint(cdZA["CD", "lambda"], digits=4)} & \Sexpr{pprint(cdZA["CD", "alpha"])} & \Sexpr{pprint(cdZA["CD", "beta"])} & \Sexpr{pprint(cdZA["CD", "gamma"])}\\
-            \hline
-            $q$   & \Sexpr{pprint(cdqZA["CD", "lambda"], digits=4)} & \Sexpr{pprint(cdqZA["CD", "alpha"])} & \Sexpr{pprint(cdqZA["CD", "beta"])} & \Sexpr{pprint(cdqZA["CD", "gamma"])}\\
-            \hline
-            $x$   & \Sexpr{pprint(cdxZA["CD", "lambda"], digits=4)} & \Sexpr{pprint(cdxZA["CD", "alpha"])} & \Sexpr{pprint(cdxZA["CD", "beta"])} & \Sexpr{pprint(cdxZA["CD", "gamma"])}\\
-            \hline
-          \end{tabular}
-        \normalsize
-      \end{center}
-    \column{2.2in}
-<<Results_Graph_ZA_CD, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-createCDLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
-@
-  \end{columns}
-  % Including at bottom of frame so as not to push other material downward in the frame.
-  \putFlagUpperRight{ZA}{0.055}
-\end{frame}
-
-<<Coefs_SA_CD>>=
-cdSA <- cobbDouglasData("SA")
-cdqSA <- cobbDouglasData("SA", "Q")
-cdxSA <- cobbDouglasData("SA", "X")
-@
-\begin{frame}{Cobb-Douglas $y$ Predictions} %----------------------------
-  \begin{columns}[c]
-    \column{2.2in}
-      \begin{center}
-        \cdeEqn
-        \vspace{\baselineskip}
-
-        \tiny
-          \begin{tabular}{|c|c|c|c|c|}\hline
-            $e$ & $\lambda$ & $\alpha$ & $\beta$ & $\gamma$\\
-            \hline
-                  & \Sexpr{cdSA["CD", "lambda"]} & \Sexpr{cdSA["CD", "alpha"]} & \Sexpr{cdSA["CD", "beta"]} & \Sexpr{cdSA["CD", "gamma"]}\\
-            \hline
-            $q$   & \Sexpr{cdqSA["CD", "lambda"]} & \Sexpr{cdqSA["CD", "alpha"]} & \Sexpr{cdqSA["CD", "beta"]} & \Sexpr{cdqSA["CD", "gamma"]}\\
-            \hline
-            $x$   & \Sexpr{cdxSA["CD", "lambda"]} & \Sexpr{cdxSA["CD", "alpha"]} & \Sexpr{cdxSA["CD", "beta"]} & \Sexpr{cdxSA["CD", "gamma"]}\\
-            \hline
-          \end{tabular}
-        \normalsize
-      \end{center}
-    \column{2.2in}
-<<Results_Graph_SA_CD, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-createCDLatticeGraph("SA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
-@
-  \end{columns}
-  % Including at bottom of frame so as not to push other material downward in the frame.
-  \putFlagUpperRight{SA}{0.055}
 \end{frame}
@@
 \begin{frame}{CES Elasticity of Substitution} %----------------------------
-  \begin{center} \small \cesEqn \normalsize \end{center}
+  \begin{center} \cesEqn \end{center}
   \begin{itemize}
@@
 
-<<Coefs_ZA_CES>>=
-cesqZA <- cesData("ZA", "Q")
-cesxZA <- cesData("ZA", "X")
-@
-\begin{frame}{CES $y$ Predictions} %----------------------------
-  \begin{columns}[c]
-    \column{2.2in}
-      \begin{center}
-        \tiny \cesEqnNarrow \normalsize
-        \vspace{\baselineskip}
-
-        \tiny
-          \begin{tabular}{|c|c|c|c|}\hline
-            $e$ & $\gamma$ & $\lambda$ & $\delta_1$\\
-            \hline
-            $q$ & \Sexpr{pprint(cesqZA["CES", "gamma"])} & \Sexpr{pprint(cesqZA["CES", "lambda"], digits=4)} & \Sexpr{pprint(cesqZA["CES", "delta_1"])}\\
-            \hline
-            $x$ & \Sexpr{pprint(cesxZA["CES", "gamma"])} & \Sexpr{pprint(cesxZA["CES", "lambda"], digits=4)} & \Sexpr{pprint(cesxZA["CES", "delta_1"])}\\
-            \hline
-          \end{tabular}
-          \vspace{\baselineskip}
-
-          \begin{tabular}{|c|c|c|c|}\hline
-            $e$ & $\sigma_1$ & $\delta$ & $\sigma$\\
-            \hline
-            $q$ & \Sexpr{pprint(cesqZA["CES", "sigma_1"])} & \Sexpr{pprint(cesqZA["CES", "delta"])} & \Sexpr{pprint(cesqZA["CES", "sigma"])}\\
-            \hline
-            $x$ & \Sexpr{pprint(cesxZA["CES", "sigma_1"])} & \Sexpr{pprint(cesxZA["CES", "delta"])} & \Sexpr{pprint(cesxZA["CES", "sigma"])}\\
-            \hline
-          \end{tabular}
-        \normalsize
-      \end{center}
-    \column{2.2in}
-<<Results_Graph_ZA_CES, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-createCESLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
-@
-  \end{columns}
-  % Including at bottom of frame so as not to push other material downward in the frame.
-  \putFlagUpperRight{ZA}{0.055}
-\end{frame}
-
 \begin{frame}{$CI_{\sigma}$ and $\sigma$ in CES} %----------------------------
   \begin{center}
-    \small\cesEqn\normalsize\\
+    \cesEqn\\
     \includegraphics[height=2.5in]{figure_other/CI-sigma.pdf}

### 2013-04-03 EconGrowthSeminar.Rnw
Many editing changes in preparation for seminar on 4 April 2013.

@@
 
-  Cobb-Douglas: \cdEqn
-  \vspace{\baselineskip}
-
-  Cobb-Douglas with Energy: \cdeEqn
-  \vspace{\baselineskip}
-
-  Constant Elasticity of Substitution:
+  Cobb-Douglas (CD): \cdEqn
+  \vspace{\baselineskip}
+
+  Cobb-Douglas (CD) with Energy: \cdeEqn
+  \vspace{\baselineskip}
+
+  Constant Elasticity of Substitution (CES):
   \cesEqn
@@
     \end{tabular}
+    \vspace{\baselineskip}
+
+    Example: \citet{Nel:2009wq} use $f$ = $q$
   \end{center}
@@
     \end{tabular}
+    \vspace{\baselineskip}
+
+    Example: \citet{Froling:2009vo}
   \end{center}
@@
     \end{tabular}
+    \vspace{\baselineskip}
+
+    Example: \citet{Stern:2012ey}
   \end{center}
@@
     \end{tabular}
+    \vspace{\baselineskip}
+
+    Example: \citet{Warr:2006hc}
   \end{center}
@@
 
-    \item{Capital stock ($K$): market value of productive goods (e.g., machines, tools, infrastructure)}
-    \vspace{\baselineskip}
-
-    \item{Labor ($L$): human work in an economy (people or hours)}
+    \item{Capital stock ($K$): market value (real 2005\$) of productive goods (e.g., machines, tools, infrastructure)}
+    \vspace{\baselineskip}
+
+    \item{Labor ($L$): human work in an economy (persons or hours)}
   \end{itemize}
@@
       \hline
-      \multirow{4}{*}{WB WDI} & \multirow{4}{*}{\includegraphics[scale=0.07]{figure_other/Figure_World_Bank.png}} & Pop, Pop < 15 yo,    & \multirow{4}{*}{Total employment} \\
+      \multirow{4}{*}{WB WDI} & \multirow{4}{*}{\includegraphics[scale=0.07]{figure_other/Figure_World_Bank.png}} & Pop, Pop < 15 yo,    & \multirow{4}{*}{Total employment (persons)} \\
                               &                          & Emp/Pop ratio > 15 yo, &                                \\
@@
 
-    \item{Useful work ($U$): energy that generates economic activity directly}
+    \item{Useful work ($U$): energy that generates economic activity directly \citep{Warr:2006hc}}
   \end{itemize}
@@
       \multirow{3}{*}{IEA} & \multirow{3}{*}{\includegraphics[scale=0.20]{figure_other/Figure_IEA.png}} & Coal, Oil, Petroleum, & \multirow{3}{*}{GJ/year} \\
-                              &                          & Nat. gas, Nuclear, & \\
+                              &                          & Natural gas, Nuclear, & \\
                               &                          & Renewables & \\
       \hline
-      \multirow{4}{*}{FAOStat} & \multirow{4}{*}{\includegraphics[scale=0.07]{figure_other/Figure_FAOStat.png}} & Fuel wood,    & \multirow{4}{*}{GJ/year} \\
+      \multirow{2}{*}{FAOStat} & \multirow{2}{*}{\includegraphics[scale=0.06]{figure_other/Figure_FAOStat.png}} & Fuel wood,    & \multirow{2}{*}{GJ/year} \\
                               &                          & Available livestock &                                \\
-                              &                          & (1980-2011: Developed; &                         \\
-                              &                          & 1991-2011: Other) &                         \\
       \hline
@@
 
-\begin{frame}{Comments on Single-factor Model Equation} %----------------------------
-    \begin{center} \sfEqn \end{center}
-    \vspace{\baselineskip}
-
-    \begin{itemize}
-      \item{Illustrative}
-      \item{$\mathrm{e}^{\lambda(t-t_0)}$: Time-dependent technology term}
-      \begin{itemize}
-        \item{Irrepressible ``progress'' of technology}
-        \item{Independent of factor of production ($f$)}
-      \end{itemize}
-      \item{Example: \citet{Nel:2009wq} use $f$ = $q$}
+\begin{frame}{Example: Single-factor model with $q$} %----------------------------
+  \begin{center}$y = A \: q^{\gamma}; A \equiv \mathrm{e}^{\lambda (t-t_0)}$\end{center}
+  \begin{itemize}
+    \item{Select $\lambda$, $\gamma$ to minimize \\ $SSE_y = \sum\limits_{t=1980}^{2011}(y_{pred} - y_{act})^2$}
+    \pause
+    \vspace{\baselineskip}
+
     \item{$\lambda$ and $m$ estimated by \texttt{nls} function in \texttt{R}}
-    \end{itemize}
-\end{frame}
-
-\begin{frame}{Example: Single-factor model with $q$} %----------------------------
-  \begin{center}$y = \mathrm{e}^{\lambda (t-t_0)}q^{\gamma}$\end{center}
-  \begin{itemize}
-    \item{Select $\lambda$, $\gamma$}
-    \item{To minimize \\ $SSE = \sum\limits_{t=1980}^{2011}(y_{pred} - y_{act})^2$}
   \end{itemize}
@@
 
-\begin{frame}{Comments on Cobb-Douglas Model Equation} %----------------------------
-  \begin{center} \cdeEqn \end{center}
-  \begin{itemize}
-    \item{$\mathrm{e}^{\lambda(t-t_0)}$: Time-dependent technology term}
-    \item{$k$, $l$, and $e$ factors of production ``blend'' with $\alpha + \beta + \gamma = 1$}
-    \item{Example: \citet{Froling:2009vo}}
-  \end{itemize}
-\end{frame}
-
 \begin{frame}{Parameter Estimation for Cobb-Douglas With Energy} %----------------------------
@@
 
-\begin{frame}{Comments on CES Model Equation} %----------------------------
+\begin{frame}{Parameter Estimation for CES Model Equation} %----------------------------
   \begin{center} \cesEqn \end{center}
   \begin{itemize}
-    \item{$\mathrm{e}^{\lambda(t-t_0)}$: Time-dependent technology term}
     \item{$\delta$: split between ($kl$) and ($e$)}
-    \item{Example: \citet{Stern:2012ey}}
+    \vspace{\baselineskip}
+
     \item{$\gamma$, $\lambda$, $\delta_1$, $\rho_1$, $\delta$, $\rho$ estimated by \texttt{cesEst} function in \texttt{R}'s \texttt{micEcon} package}
@@
 
-\begin{frame}{Comments on LINEX Model Equation} %----------------------------
+\begin{frame}{Parameter Estimatino for LINEX Model Equation} %----------------------------
   \begin{center} \linexEqn \end{center}
@@
     \item{Time-dependent technology $\rightarrow$ efficiency ratios}
-    \item{Productivity $\uparrow$ if}
+    \item{Productivity ($A$) $\uparrow$ if}
     \begin{itemize}
@@
     \end{itemize}
-    \item{Example: \citet{Warr:2006hc}}
     \item{$a_0$ and $c_t$ estimated by \texttt{nls} function in \texttt{R}}

### 2013-04-03 EconGrowth-R-Functions.Rnw
Edited the notional graph for delta to correctly identify regions where we see significance. Many other edits to the presentation.

--- 2013-04-03 EconGrowth-R-Functions.Rnw
@@
                    lwd = 1, #Sets line width to 1.0
-                   strip = strip.custom(bg="transparent", factor.levels=c("$\\lambda$", exponentParameter)),
+                   strip = strip.custom(bg="transparent", factor.levels=c("$\\lambda$ [1/year]", exponentParameter)),
                    ylim = list(c(-0.05, 0.1), c(-0.5, 1.5)), #y axis limits
@@
                    screen = list(z = -20, x = -55),
-                   xlab = "$\\lambda$",
+                   xlab = "$\\lambda$ [1/year]",
                    ylab = "$\\gamma$",
@@
                      pch = symbols, col.symbol = colors, #Controls symbol parameters
-                     key=list(text=list(c("$\\alpha$", "$\\beta$", "$\\gamma$", "$SSE$")),
+                     key=list(text=list(c("$\\alpha$", "$\\beta$", "$\\gamma$", "$SSE_y$")),
                               type=graphType,
@@
                      xlab=list(label="$\\gamma$", cex=textScaling), 
-                     ylab=list(label="$\\lambda$, $\\alpha$, $\\beta$", cex=textScaling)
+                     ylab=list(label="$\\alpha$, $\\beta$, $\\gamma$", cex=textScaling)
   )
@@
                      index.cond = list(c(2,3,1)), #orders the panels as alpha, beta, lambda, gamma
-                     strip = strip.custom(factor.levels=c("$\\lambda$", "$\\alpha$", "$\\beta$"), #sets labels in strip 
+                     strip = strip.custom(factor.levels=c("$\\lambda$ [1/year]", "$\\alpha$", "$\\beta$"), #sets labels in strip 
                                           bg="transparent"), #sets background color in strip
@@
                      #set labels and bg color in strip
-                     strip = strip.custom(factor.levels=c("$\\lambda$", "$\\alpha$", "$\\beta$", "$\\gamma$"),  
+                     strip = strip.custom(factor.levels=c("$\\lambda$ [1/year]", "$\\alpha$", "$\\beta$", "$\\gamma$"),  
                                           bg="transparent"),
@@
                    #set labels and bg color in strip
-                   strip = strip.custom(factor.levels=c("$\\gamma$", "$\\lambda$", "$\\delta_1$",
+                   strip = strip.custom(factor.levels=c("$\\gamma$", "$\\lambda$ [1/year]", "$\\delta_1$",
                                                         "$\\delta$", "$\\sigma_1$", "$\\sigma$"), bg="transparent"),
@@
     x <- subset(data, select=lambda) # The column of lambdas
-    xLabel <- "$\\lambda$"
+    xLabel <- "$\\lambda$ [1/year]"
     y <- subset(data, select=upperCI_lambda) - subset(data, select=lowerCI_lambda) # A column of CI values
@@
 }
-#CIvsParamPlot(model="SF", param="lambda", factor="Q")
-#CIvsParamPlot(model="CD", param="alpha")
-#CIvsParamPlot(model="CDe", param="gamma", energyType="Q")
-#CIvsParamPlot(model="CES", param="delta", energyType="Q")
-#CIvsParamPlot(model="LINEX", param="c_t", energyType="Q")
 @

### 2013-04-03 EconGrowthSeminar.Rnw
Edited the notional graph for delta to correctly identify regions where we see significance. Many other edits to the presentation.

@@
 % The equation for a single-factor model
-\newcommand{\sfEqn}{$y = A \: f^{m}$; $A \equiv \mathrm{e}^{\lambda (t-t_0)}$}
+\newcommand{\sfEqn}{$y = A \: f^{m}$; \small $A \equiv \mathrm{e}^{\lambda (t-t_0)}$ \normalsize}
 % The equation for a cobb-douglas without energy model
-\newcommand{\cdEqn}{$y = A \: k^{\alpha}l^{\beta}$; $A \equiv \mathrm{e}^{\lambda (t-t_0)}$}
+\newcommand{\cdEqn}{$y = A \: k^{\alpha}l^{\beta}$; \small $A \equiv \mathrm{e}^{\lambda (t-t_0)}$ \normalsize}
 % The equation for a cobb-douglas with energy model
-\newcommand{\cdeEqn}{$y = A\: k^{\alpha}l^{\beta}e^{\gamma}$; $A \equiv \mathrm{e}^{\lambda (t-t_0)}$}
+\newcommand{\cdeEqn}{$y = A\: k^{\alpha}l^{\beta}e^{\gamma}$; \small $A \equiv \mathrm{e}^{\lambda (t-t_0)}$ \normalsize}
 % The equation for a ces model
@@
 % The equation for a linex model
-\newcommand{\linexEqn}{$y =  A \: e$; $A \equiv \mathrm{e}^{\left[a_0 \left(2 - \frac{l + e}{k} \right) + a_0 c_t \left(\frac{l}{e} - 1 \right)\right]}$}
+\newcommand{\linexEqn}{$y =  A \: e$; \small $A \equiv \mathrm{e}^{\left[a_0 \left(2 - \frac{l + e}{k} \right) + a_0 c_t \left(\frac{l}{e} - 1 \right)\right]}$ \normalsize}
 
@@
 
-\begin{frame}{Outline} %----------------------------
-  \tableofcontents
-  % You might wish to add the option [pausesections]
-\end{frame}
+% \begin{frame}{Outline} %----------------------------
+%   \tableofcontents
+%   % You might wish to add the option [pausesections]
+% \end{frame}
 
@@
 
-\subsection[Visualization]{Visualization} %+++++++++++++++++++++++++++++++++++++++
-
-\minorSeparator{Visualization of Historical Data}
+\subsection[Historical Data]{Historical Data} %+++++++++++++++++++++++++++++++++++++++
+
+\minorSeparator{Historical Data}
 
@@
 % The first just shows the surface. The second also shows the optimum point in the surface.
-\begin{frame}{$SSE$ Minimization}{US single-factor with $Q$} %---------------------------- 
+\begin{frame}{$SSE$ Minimization}{US single-factor with $q$} %---------------------------- 
 <<3D_Graph_US_SF_Q, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
@@
 
-\begin{frame}{$SSE$ Minimization}{US single-factor with $Q$} %---------------------------- 
+\begin{frame}{$SSE$ Minimization}{US single-factor with $q$} %---------------------------- 
 <<3D_Graph_US_SF_Q_With_Opt_Point, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
@@
           \begin{tabular}{|c|c|c|}\hline
-            $f$   & $\lambda$                & $m$\\
+            $f$   & $\lambda$ [1/year]       & $m$\\
             \hline
@@
 
-\begin{frame}{95\% Confidence Intervals}{Single-factor with $Q$} %----------------------------
+\begin{frame}{95\% Confidence Intervals}{Single-factor with $q$} %----------------------------
 <<SF_Params_Graph_Q, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
@@
 
-\begin{frame}{Comments on Single-factor Model with $Q$} %----------------------------
+\begin{frame}{Comments on Single-factor Model with $q$} %----------------------------
   \begin{itemize}
@@
 
-\begin{frame}{Grid Search Over $\gamma$}{US Cobb-Douglas with $Q$} %----------------------------
+\begin{frame}{Grid Search Over $\gamma$}{US Cobb-Douglas with $q$} %----------------------------
 <<CDeGammaGraphsUS, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
@@
 
-\begin{frame}{Grid Search Over $\gamma$}{UK Cobb-Douglas with $Q$} %----------------------------
+\begin{frame}{Grid Search Over $\gamma$}{UK Cobb-Douglas with $q$} %----------------------------
 <<CDeGammaGraphsUK, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
@@
           \begin{tabular}{c|c c c c}
-            $e$ & $\lambda$ & $\alpha$ & $\beta$ & $\gamma$\\
+            $e$ & $\lambda$ [1/year] & $\alpha$ & $\beta$ & $\gamma$\\
             \hline
@@
           \begin{tabular}{|c|c|c|c|c|}\hline
-            $e$ & $\lambda$ & $\alpha$ & $\beta$ & $\gamma$\\
+            $e$ & $\lambda$ [1/year] & $\alpha$ & $\beta$ & $\gamma$\\
             \hline
@@
 
-\begin{frame}{$CI_{\gamma}$ vs. $\gamma$ for Cobb-Douglas with $Q$} %----------------------------
+\begin{frame}{$CI_{\gamma}$ vs. $\gamma$ for Cobb-Douglas with $q$} %----------------------------
 <<CI_gamma_vs_gamma_Graph, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5>>=
@@
 
-\begin{frame}{Implications from Cobb-Douglas with $Q$} %----------------------------
+\begin{frame}{Implications from Cobb-Douglas with $q$} %----------------------------
   \begin{center}\cdeEqn\end{center}
@@
           \begin{tabular}{c|c c c}
-            $e$ & $\gamma$ & $\lambda$ & $\delta_1$\\
+            $e$ & $\gamma$ & $\lambda$ [1/year] & $\delta_1$\\
             \hline
@@
           \begin{tabular}{c|c c c}
-            $e$ & $\gamma$ & $\lambda$ & $\delta_1$\\
+            $e$ & $\gamma$ & $\lambda$ [1year] & $\delta_1$\\
             \hline
@@
           \begin{tabular}{|c|c|c|c|}\hline
-            $e$ & $\gamma$ & $\lambda$ & $\delta_1$\\
+            $e$ & $\gamma$ & $\lambda$ [1/year] & $\delta_1$\\
             \hline
@@
 
-\begin{frame}{$CI_{\delta}$ vs. $\delta$ for CES with $Q$} %----------------------------
+\begin{frame}{$CI_{\delta}$ vs. $\delta$ for CES with $q$} %----------------------------
 <<CI_delta_vs_delta_Graph, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5>>=
@@
 
-\begin{frame}{Parameter Estimatino for LINEX Model Equation} %----------------------------
+\begin{frame}{Parameter Estimation for LINEX Model Equation} %----------------------------
   \begin{center} \linexEqn \end{center}
@@
     \begin{itemize}
-      \item{Efficiency of producing capital stock increases ($k$ > $l + e$)}
-      \item{Energy efficiency of labor increases ($l$ > $e$)}
+      \item{Efficiency of producing capital stock increases \\ ($k$ > $l + e$)}
+      \item{Energy efficiency of labor increases \\ ($l$ > $e$)}
     \end{itemize}
@@
     \item{Direct energy input to economy ($q$) is important as a LINEX predictor of economic output ($y$)}
-    \item{LINEX fits are poorer quality than other model}
+    \item{LINEX fits are poorer quality than other models}
   \end{itemize}
@@
       \pause
-      \item{Unfortunately, LINEX fits are poorer quality than Cobb-Douglas or CES}
+      \item{Unfortunately, LINEX fits are poorer quality than CD or CES}
       \normalsize
@@
 
-\begin{frame}{The ``Answer''} %----------------------------
+\begin{frame}{The (Tentative) ``Answer''} %----------------------------
   \begin{center}
@@
 
-\begin{frame}{Grid Search Over $\gamma$}{JP Cobb-Douglas with $Q$} %----------------------------
+\begin{frame}{Grid Search Over $\gamma$}{JP Cobb-Douglas with $q$} %----------------------------
 <<CDeGammaGraphsJP, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
@@
 
-\begin{frame}{Grid Search Over $\gamma$}{CN Cobb-Douglas with $Q$} %----------------------------
+\begin{frame}{Grid Search Over $\gamma$}{CN Cobb-Douglas with $q$} %----------------------------
 <<CDeGammaGraphsCN, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
@@
 
-\begin{frame}{Grid Search Over $\gamma$}{ZA Cobb-Douglas with $Q$} %----------------------------
+\begin{frame}{Grid Search Over $\gamma$}{ZA Cobb-Douglas with $q$} %----------------------------
 <<CDeGammaGraphsZA, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
@@
 
-\begin{frame}{Grid Search Over $\gamma$}{SA Cobb-Douglas with $Q$} %----------------------------
+\begin{frame}{Grid Search Over $\gamma$}{SA Cobb-Douglas with $q$} %----------------------------
 <<CDeGammaGraphsSA, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
@@
 
-\begin{frame}{Grid Search Over $\gamma$}{IR Cobb-Douglas with $Q$} %----------------------------
+\begin{frame}{Grid Search Over $\gamma$}{IR Cobb-Douglas with $q$} %----------------------------
 <<CDeGammaGraphsIR, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
@@
 
-\begin{frame}{Grid Search Over $\gamma$}{TZ Cobb-Douglas with $Q$} %----------------------------
+\begin{frame}{Grid Search Over $\gamma$}{TZ Cobb-Douglas with $q$} %----------------------------
 <<CDeGammaGraphsTZ, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
@@
 
-\begin{frame}{Grid Search Over $\gamma$}{ZM Cobb-Douglas with $Q$} %----------------------------
+\begin{frame}{Grid Search Over $\gamma$}{ZM Cobb-Douglas with $q$} %----------------------------
 <<CDeGammaGraphsZM, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
@@
 
-\begin{frame}{$CI_{\sigma}$ vs. $\sigma$ for CES with $Q$} %----------------------------
+\begin{frame}{$CI_{\sigma}$ vs. $\sigma$ for CES with $q$} %----------------------------
 <<CI_sigma_vs_sigma_Graph, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5>>=

### 2013-04-03 EconGrowthSeminar.Rnw
Changes to the presentation before the seminar.

@@
 
-\begin{frame}{Energy is Essential for Economic Activity} %----------------------------
+\begin{frame} %----------------------------
   \begin{center}What do you do that doesn't require energy?\end{center}
@@
     \item{Goal: predict economic output over time}
+    \item{Set aside debates about growth and its measure}
     \item{All factors and outputs indexed to initial year: $y = Y/Y_0, e = E/E_0$, etc.}
@@
 
-    \item{Set aside debates about growth and its measure}
+    \item{Uncritical use of energy-augmented growth models in the literature}
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{What's Needed?} %----------------------------
+  \begin{itemize}
+    \item{Go beyond developed economies}
+    \pause
+    \vspace{\baselineskip}
+
+    \item{Rigorous, statistical evaluation of energy-augmented growth models with $Q$, $X$, and $U$}
+    \pause
+    \vspace{\baselineskip}
+
+    \item{Comparative analysis of growth models}
   \end{itemize}
@@
 
-    Extra credit: reflect dynamics of energy cost share and price spikes.
+    Extra credit: reflect dynamics of energy cost share and price spikes
   \end{center}
@@
   \begin{itemize}
-    \item{Type of Economy}
-    \vspace{\baselineskip}
-    \item{Type of Energy}
-    \vspace{\baselineskip}
-    \item{Economic Growth Model}
+    \item{Type of economy}
+    \vspace{\baselineskip}
+    \item{Type of energy}
+    \vspace{\baselineskip}
+    \item{Type of economic growth model}
   \end{itemize}
@@
       \hline
-      \multirow{2}{*}{LDCs}       & \includegraphics[height=0.11in]{flag/flag_TZ.png} & TZ & Tanzania      \\
+      \multirow{2}{*}{LDC}       & \includegraphics[height=0.11in]{flag/flag_TZ.png} & TZ & Tanzania      \\
                                   & \includegraphics[height=0.11in]{flag/flag_ZM.png} & ZM & Zambia        \\
@@
 
-\begin{frame}{Economic Growth Model} %----------------------------
+\begin{frame}{Type of Economic Growth Model} %----------------------------
   Single Factor: \sfEqn
@@
       \yRow\\
+      $A$ & productivity of factors of production\\
       \timeRow\\
@@
     Example: \citet{Nel:2009wq} use $f$ = $q$
+  \end{center}
+\end{frame}
+
+\begin{frame}{Cobb-Douglas} %----------------------------
+  \begin{center}
+    \cdEqn\\
+    $\alpha + \beta = 1$\\
+    $0 \leq \alpha, \beta \leq 1$
+    \vspace{\baselineskip}
+
+    \begin{tabular}{|c|l|}\hline
+      \lambdaRow\\
+      \alphaRow\\
+      \betaRow\\
+      \hline
+    \end{tabular}
+    \vspace{\baselineskip}
+
+    Example: \citet{Warr:2006hc}
   \end{center}
@@
 
+\begin{frame}{LINEX}
+    \begin{center} \linexEqn \end{center}
+    \vspace{\baselineskip}
+
+  \begin{itemize}
+    \item{Derived from thermodynamics \citep{Kummel:1980wx}}
+    \item{Productivity ($A$) based on efficiency ratios}
+    \item{$A$ $\uparrow$ if}
+    \begin{itemize}
+      \item{Efficiency of producing capital stock increases \\ ($k$ > $l + e$)}
+      \item{Energy efficiency of labor increases \\ ($l$ > $e$)}
+    \end{itemize}
+  \end{itemize}
+\end{frame}
+
 \begin{frame}{LINEX} %----------------------------
@@
 
-    \item{Labor ($L$): human work in an economy (persons or hours)}
+    \item{Labor ($L$): human work in an economy (persons or work hours)}
   \end{itemize}
@@
       \hline
-      \multirow{2}{*}{US BLS} & \multirow{2}{*}{\includegraphics[scale=0.07]{figure_other/Figure_BLS.png}} & $L$ for developed countries & Labor hours \\
+      \multirow{2}{*}{US BLS} & \multirow{2}{*}{\includegraphics[scale=0.07]{figure_other/Figure_BLS.png}} & $L$ for developed countries & Work hours \\
                               &                          & (1980-2011: US, UK, JP)     & per year \\ 
@@
       \hline
-      \multirow{2}{*}{REXS} & \multirow{2}{*}{\includegraphics[scale=0.05]{figure_other/Figure_Warr.png}} & Energy allocation factors. &  \multirow{2}{*}{\citet{Warr:2006hc}}\\
+      \multirow{2}{*}{REXS} & \multirow{2}{*}{\includegraphics[scale=0.05]{figure_other/Figure_Warr.png}} & Energy allocation factors  &  \multirow{2}{*}{\citet{Warr:2006hc}}\\
                               &                          & (1980-2000: Developed)     & \\ 
@@
 \begin{frame}{Example: Single-factor model with $q$} %----------------------------
-  \begin{center}$y = A \: q^{\gamma}; A \equiv \mathrm{e}^{\lambda (t-t_0)}$\end{center}
+  \begin{center}$y = A \: q^{\gamma}$; \small $A \equiv \mathrm{e}^{\lambda (t-t_0)}$ \normalsize \end{center}
   \begin{itemize}
@@
 
-    \item{$\lambda$ and $m$ estimated by \texttt{nls} function in \texttt{R}}
+    \item{$\lambda$ and $\gamma$ estimated by \texttt{nls} function in \texttt{R}}
   \end{itemize}
@@
   \begin{itemize}
-    \item{Not typically used for economic modeling: illustrates confidence intervals}
-    \vspace{\baselineskip}
-
-    \item{$CI_{\gamma}$ > $CI_{\lambda}$ for all countries\footnote{\tiny as percentage of $0.0 < \lambda < 0.1$ and $0 < \gamma < 1$ \normalsize}}
+    \item{Single-factor not typically used for economic modeling: illustrates confidence intervals}
+    \vspace{\baselineskip}
+
+    \item{$CI_{\gamma}$ > $CI_{\lambda}$ for all countries\footnote{\tiny as percentage of 0.0 1/year < $\lambda$ < 0.1 1/year and $0 < \gamma < 1$ \normalsize}}
   \end{itemize}
@@
   \begin{itemize}
-    \item{Is energy important for this economy?\\Yes, if $\gamma$ not small.}
+    \item{Is energy important for this economy?\\Yes, if $\gamma$ not near 0.0.}
     \vspace{\baselineskip}
@@
   \begin{itemize}
-    \item{Is energy important for this economy?\\Yes, if $\delta$ is not large.}
+    \item{Is energy important for this economy?\\Yes, if $\delta$ is not near 1.0.}
     \vspace{\baselineskip}
@@
 \begin{frame}{$CI_{\delta}$ vs. $\delta$ for CES with $q$} %----------------------------
-<<CI_delta_vs_delta_Graph, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5>>=
+<<CI_delta_vs_delta_Graph_Q, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5>>=
 CIvsParamPlot(model="CES", param="delta", energyType="Q")
@@
   \begin{itemize}
-    \item{Derived from thermodynamics \citep{Kummel:1980wx}}
-    \item{Time-dependent technology $\rightarrow$ efficiency ratios}
-    \item{Productivity ($A$) $\uparrow$ if}
-    \begin{itemize}
-      \item{Efficiency of producing capital stock increases \\ ($k$ > $l + e$)}
-      \item{Energy efficiency of labor increases \\ ($l$ > $e$)}
-    \end{itemize}
+    \item{Select $a_0$ and $c_t$ to best fit historical data}
+    \vspace{\baselineskip}
+
     \item{$a_0$ and $c_t$ estimated by \texttt{nls} function in \texttt{R}}
@@
     \end{itemize}
+  \item{Uncritical use of energy-augmented growth models is problematic}
   \end{itemize}
@@
 
+  \vspace{\baselineskip}
+
 \end{frame}
@@
 
-    Answer: Cobb-Douglas or CES without energy
+    Answer: Cobb-Douglas without energy (possibly CES without energy)
   \end{center}
@@
 
-    \item{Models (CD and CES without energy) could be \emph{included within} a model that endogenizes price and cost share}
+    \item{Models (CD, or CES, without energy) could be \emph{included within} a model that endogenizes price and cost share}
     \pause
@@
   \begin{itemize}
+    \item{Evaluate CES without energy}
     \item{Verify and improve estimates of statistical properties for \emph{all} fitting parameters}
     \vspace{\baselineskip}
-    \item{Incorporate all constraints for Cobb-Douglas model}
+    \item{Incorporate all constraints for all models}
     \vspace{\baselineskip}
@@
 
+\begin{frame}{$CI_{\delta}$ and $\delta$ in CES} %----------------------------
+  \begin{center}
+    \cesEqn\\
+    \includegraphics[height=2.5in]{figure_other/CI-delta.pdf}
+  \end{center}
+\end{frame}
+
+\begin{frame}{$CI_{\delta}$ vs. $\delta$ for CES with $x$} %----------------------------
+<<CI_delta_vs_delta_Graph_X, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5>>=
+CIvsParamPlot(model="CES", param="delta", energyType="X")
+@
+\end{frame}
+
+\begin{frame}{$CI_{\delta}$ vs. $\delta$ for CES with $u$} %----------------------------
+<<CI_delta_vs_delta_Graph_U, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5>>=
+CIvsParamPlot(model="CES", param="delta", energyType="U")
+@
+\end{frame}
+
 \begin{frame}{CES Elasticity of Substitution} %----------------------------

### 2013-04-04 EconGrowthSeminar.Rnw
Fixed several small things on the seminar in preparation for the seminar.

@@
 \date[Math Seminar] % (optional)
-{Mathematics Colloquium\\
-Thursday, 4 April 2013
+{Calvin College Mathematics Colloquium\\
+3:30 PM, Thursday, 4 April 2013
 }
@@
     \pause
-    \item{Energy (relatively) unimportant for classical economists}
+    \item{Energy (relatively) unimportant for neoclassical economists}
     \item{Usually ignored}
@@
     \pause
-    \item{And yet \dots}
+    \item{And yet\dots}
   \end{itemize}
@@
   \begin{center}
-    10 of last 11 US recessions preceeded by oil price shocks
+    10 of last 11 US recessions preceded by oil price shocks
     \vspace{\baselineskip}
@@
   \begin{itemize}
-    \item{Goal: predict economic output over time}
+    \item{Goal: predict economic output ($Y$) over time}
     \item{Set aside debates about growth and its measure}
@@
 
-    \item{Uncritical use of energy-augmented growth models in the literature}
+    \item{Uncritical use of energy-augmented growth models for developed economies in the literature}
   \end{itemize}
@@
   \begin{itemize}
-    \item{Go beyond developed economies}
-    \pause
-    \vspace{\baselineskip}
-
-    \item{Rigorous, statistical evaluation of energy-augmented growth models with $Q$, $X$, and $U$}
-    \pause
-    \vspace{\baselineskip}
-
-    \item{Comparative analysis of growth models}
+    \item{Move beyond developed economies}
+    \pause
+    \vspace{\baselineskip}
+
+    \item{Statistically rigorous evaluation of energy types $Q$, $X$, and $U$}
+    \pause
+    \vspace{\baselineskip}
+
+    \item{Comparative analysis of energy-augmented growth models}
   \end{itemize}
@@
   \begin{center}
-    Which economic growth model best describes (statistically) the role of energy in economic growth for different types of economies?
+    Which model best describes (statistically) the role of energy in economic growth for different types of economies?
     \pause
@@
   \pause
-  \begin{center}Simplification: One type of energy ($Q$) for this presentation\end{center}
+  \begin{center} Simplification: One type of energy ($Q$) for this presentation \end{center}
 \end{frame}
@@
 
-\begin{frame}{LINEX}
+\begin{frame}{LINEX} %----------------------------
     \begin{center} \linexEqn \end{center}
@@
 
-\majorSeparator{Data Sources}
+\majorSeparator{Data Sources} %----------------------------
 
@@
 @
-\begin{frame}{Single-factor (with $q$) Predictions for $y$} %----------------------------
+\begin{frame}{Single-factor Predictions for $y$} %----------------------------
   \begin{columns}[c]
@@
   \begin{itemize}
-    \item{Single-factor not typically used for economic modeling: illustrates confidence intervals}
-    \vspace{\baselineskip}
-
-    \item{$CI_{\gamma}$ > $CI_{\lambda}$ for all countries\footnote{\tiny as percentage of 0.0 1/year < $\lambda$ < 0.1 1/year and $0 < \gamma < 1$ \normalsize}}
+    \item{Single-factor model not typically used for economic modeling: illustrates confidence intervals}
+    \vspace{\baselineskip}
+
+    \item{$CI_{\gamma}$ > $CI_{\lambda}$ for all countries\footnote{\tiny as percentage of 0.0 yr$^{-1}$ < $\lambda$ < 0.1 yr$^{-1}$ and $0 < \gamma < 1$ \normalsize}}
   \end{itemize}
@@
             \hline
-            $-$   & \Sexpr{cdSA["CD", "lambda"]} & \Sexpr{cdSA["CD", "alpha"]} & \Sexpr{cdSA["CD", "beta"]} & \Sexpr{cdSA["CD", "gamma"]}\\
-            \hline
-            $q$   & \Sexpr{cdqSA["CD", "lambda"]} & \Sexpr{cdqSA["CD", "alpha"]} & \Sexpr{cdqSA["CD", "beta"]} & \Sexpr{cdqSA["CD", "gamma"]}\\
-            \hline
-            $x$   & \Sexpr{cdxSA["CD", "lambda"]} & \Sexpr{cdxSA["CD", "alpha"]} & \Sexpr{cdxSA["CD", "beta"]} & \Sexpr{cdxSA["CD", "gamma"]}\\
+            $-$   & \Sexpr{pprint(cdSA["CD", "lambda"], digits=4)} & \Sexpr{pprint(cdSA["CD", "alpha"])} & \Sexpr{pprint(cdSA["CD", "beta"])} & \Sexpr{pprint(cdSA["CD", "gamma"])}\\
+            \hline
+            $q$   & \Sexpr{pprint(cdqSA["CD", "lambda"], digits=4)} & \Sexpr{pprint(cdqSA["CD", "alpha"])} & \Sexpr{pprint(cdqSA["CD", "beta"])} & \Sexpr{pprint(cdqSA["CD", "gamma"])}\\
+            \hline
+            $x$   & \Sexpr{pprint(cdxSA["CD", "lambda"], digits=4)} & \Sexpr{pprint(cdxSA["CD", "alpha"])} & \Sexpr{pprint(cdxSA["CD", "beta"])} & \Sexpr{pprint(cdxSA["CD", "gamma"])}\\
             \hline
@@
 \begin{frame}{$CI_{\gamma}$ vs. $\gamma$ for Cobb-Douglas with $q$} %----------------------------
-<<CI_gamma_vs_gamma_Graph, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5>>=
+<<CI_gamma_vs_gamma_Graph_Q, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5>>=
 CIvsParamPlot(model="CDe", param="gamma", energyType="Q")
@@
 
-\begin{frame}{Implications from Cobb-Douglas with $q$} %----------------------------
+\begin{frame}{Summary of Cobb-Douglas with $q$} %----------------------------
   \begin{center}\cdeEqn\end{center}
@@
 
-\begin{frame}{Implications from CES} %----------------------------
+\begin{frame}{Summary of CES with $q$} %----------------------------
   \begin{center} \cesEqn \end{center}
@@
 
-\begin{frame}{Implications from LINEX} %----------------------------
+\begin{frame}{Summary of LINEX with $q$} %----------------------------
   \begin{center}\linexEqn\end{center}
@@
   \begin{itemize}
-  \item{Including energy ($E$) in Cobb-Douglas and CES production functions appears to be unwarranted}
+  \item{Augmenting Cobb-Douglas and CES production functions with energy ($E$) appears to be unwarranted}
   \pause
@@
       \scriptsize
-      \item{Energy parameters ($\gamma$, $\delta$) less important than others ($\lambda$, $\alpha$, $\beta$) for nearly all countries}
+      \item{Energy parameters ($\gamma$, $\delta$) less important than others for nearly all countries}
       \pause
@@
     \end{itemize}
+  \pause
+  \item{Uncritical use of energy-augmented CD and CES growth models is problematic}
   \vspace{\baselineskip}
@@
       \pause
-      \item{Unfortunately, LINEX fits are poorer quality than CD or CES}
-      \normalsize
-    \end{itemize}
-  \item{Uncritical use of energy-augmented growth models is problematic}
+      \item{LINEX fits are poorer quality than CD or CES}
+      \normalsize
+    \end{itemize}
   \end{itemize}
@@
   \begin{center}
-    Which economic growth model best describes (statistically) the role of energy in economic growth for different types of economies?
-  \end{center}
-  \vspace{\baselineskip}
-
-  \vspace{\baselineskip}
-
-  \vspace{\baselineskip}
-
+    Which model best describes (statistically) the role of energy in economic growth for different types of economies?
+  \end{center}
 \end{frame}
@@
   \begin{center}
-    Which economic growth model best describes (statistically) the role of energy in economic growth for different types of economies?
-    \vspace{\baselineskip}
-
-    Answer: Cobb-Douglas without energy (possibly CES without energy)
+    Cobb-Douglas without energy\\(possibly CES without energy)
   \end{center}
@@
 
-    \item{Models (CD, or CES, without energy) could be \emph{included within} a model that endogenizes price and cost share}
-    \pause
-    \item{Still searching for a modeling approach that captures price and cost share dynamics \\ \scriptsize System dynamics modeling? \normalsize}
+    \item{Models (CD, or CES, without energy) could be \emph{included within} a system dynamics model that endogenizes price and cost share}
+    \pause
+    \item{System dynamics modeling}
   \end{itemize}
@@
     \item{Evaluate CES without energy}
+    \vspace{\baselineskip}
     \item{Verify and improve estimates of statistical properties for \emph{all} fitting parameters}
@@
     \item{Submit paper}
+    \vspace{\baselineskip}
+    \item{Develop system dynamics model}
   \end{itemize}  
@@
     \item{Martin de Wit, Stellenbosch University}
+    \item{Loren L. Heun, Western Michigan University}
     \item{Randall Pruim, Calvin College}
-    \item{Loren L. Heun, Western Michigan University}
     \vspace{\baselineskip}
@@
 
-\minorSeparator{CES Model}
+\begin{frame}{$CI_{\gamma}$ and $\gamma$ in Cobb-Douglas} %----------------------------
+  \begin{center}
+    \cdeEqn\\
+    \includegraphics[height=2.5in]{figure_other/CI-gamma-4.pdf}
+  \end{center}
+\end{frame}
+
+\begin{frame}{$CI_{\gamma}$ vs. $\gamma$ for Cobb-Douglas with $x$} %----------------------------
+<<CI_gamma_vs_gamma_Graph_X, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5>>=
+CIvsParamPlot(model="CDe", param="gamma", energyType="X")
+@
+\end{frame}
+
+\begin{frame}{$CI_{\gamma}$ vs. $\gamma$ for Cobb-Douglas with $u$} %----------------------------
+<<CI_gamma_vs_gamma_Graph_U, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5>>=
+CIvsParamPlot(model="CDe", param="gamma", energyType="U")
+@
+\end{frame}
+
+\minorSeparator{CES Model} %----------------------------
 

### 2013-04-04 EconGrowthSeminar.Rnw
Clarified wording on some slides.

@@
 
-    \item{Statistically rigorous evaluation of energy types $Q$, $X$, and $U$}
+    \item{Statistically rigorous evaluation of energy quantifications $Q$, $X$, and $U$}
     \pause
@@
     \vspace{\baselineskip}
-    \item{Type of energy}
+    \item{Energy quantification}
     \vspace{\baselineskip}
@@
 
-\begin{frame}{Type of Energy ($E$)} %----------------------------
+\begin{frame}{Energy ($E$) Quantification} %----------------------------
   \begin{itemize}
@@
   \pause
-  \begin{center} Simplification: One type of energy ($Q$) for this presentation \end{center}
+  \begin{center} Simplification: Focus on $Q$ for this presentation \end{center}
 \end{frame}
@@
   \begin{itemize}
-    \item{Output ($Y$): total value (real 2005\$) of goods produced (GDP)}
+    \item{Output ($Y$): total value (real 2005\$/year) of goods produced (GDP)}
     \vspace{\baselineskip}
@@
 
-    \item{Labor ($L$): human work in an economy (persons or work hours)}
+    \item{Labor ($L$): human work in an economy (persons/year or work hours/year)}
   \end{itemize}
@@
     \item{Models (CD, or CES, without energy) could be \emph{included within} a system dynamics model that endogenizes price and cost share}
-    \pause
-    \item{System dynamics modeling}
   \end{itemize}

### 2013-04-10 EconGrowth-R-Functions.Rnw
Fixed a bug that caused LINEX model parameters to not show up in tables in the appendix.

@@
 linexParamsTable <- function(energyType){
-  linexParamsTableDF(energyType)
+  dataLINEX <- linexParamsTableDF(energyType)
   colnames(dataLINEX) <- c(" ", "$a_0$", " ", " ", "$c_t$",  " ")

### 2013-04-11 EconGrowth-R-Functions.Rnw
Re-arranged the CES parameter tables in the appendix of the paper.

@@
 
+# ############################
+# # Aggregates the CES results for gamma, delta_1, and delta into a table for the given energyType.
+# ##
+# cesParamsTableA <- function(energyType){
+#   dataCES <- do.call("rbind", lapply(countryAbbrevs, cesCountryRow, energyType=energyType))
+#   colnames(dataCES) <- c(" ", "$\\gamma$",    " ", 
+#                          " ", "$\\lambda$",   " ",
+#                          " ", "$\\delta_1$",  " ",
+#                          " ", "$\\delta$",    " ",
+#                          " ", "$\\sigma_1$",  " ",
+#                          " ", "$\\sigma$",    " ")
+#   rownames(dataCES) <- countryAbbrevs
+#   tableCESa <- xtable(dataCES[,c(1,2,3, 7,8,9, 10,11,12)], #Picks up gamma, delta_1, and delta
+#                       caption=paste("CES model (with $", tolower(energyType), "$).
+$\\gamma$, $\\delta_1$, and $\\delta$ parameters for 1980-2011 (US, UK, JP), 1991-2010 (CN and ZA), and 1991-2011 (SA, IR, TZ, and ZM).
+(Parameter estimates beneath symbol.
+95\\% confidence interval bounds to left and right.)", sep=""),
+#                       label=paste("tab:CES_Parameters_With_", energyType, sep=""),
+#                       digits = c(1, 2,2,2, 2,2,2, 2,2,2),
+#                       align = "r|ccc|ccc|ccc" #Sets alignment of the numbers in the columns
+#                       ) 
+#   return(tableCESa)
+# }
+# 
+# ############################
+# # Aggregates the CES results for lambda, sigma_1, and sigma into a table for the given energyType.
+# ##
+# cesParamsTableB <- function(energyType){
+#   dataCES <- do.call("rbind", lapply(countryAbbrevs, cesCountryRow, energyType=energyType))
+#   colnames(dataCES) <- c(" ", "$\\gamma$",    " ", 
+#                          " ", "$\\lambda$",   " ",
+#                          " ", "$\\delta_1$",  " ",
+#                          " ", "$\\delta$",    " ",
+#                          " ", "$\\sigma_1$",  " ",
+#                          " ", "$\\sigma$",    " ")
+#   rownames(dataCES) <- countryAbbrevs
+#   tableCESb <- xtable(dataCES[,c(4,5,6, 13,14,15, 16,17,18)], #Picks up lambda, sigma_1, and sigma
+#                       caption=paste("CES model (with $", tolower(energyType), "$).
+$\\lambda$, $\\sigma_1$, and $\\sigma$ parameters for 1980-2011 (US, UK, JP), 1991-2010 (CN and ZA), and 1991-2011 (SA, IR, TZ, and ZM).
+(Parameter estimates beneath symbol.
+95\\% confidence interval bounds to left and right.)", sep=""),
+#                       label=paste("tab:CES_Parameters_With_", energyType, sep=""),
+#                       digits = c(1, 4,4,4, 2,2,2, 2,2,2),
+#                       align = "r|ccc|ccc|ccc"  #Sets alignment of the numbers in the columns
+#                       )
+#   return(tableCESb)
+# }
+#
+
 ############################
@@
   rownames(dataCES) <- countryAbbrevs
-  tableCESa <- xtable(dataCES[,c(1,2,3, 7,8,9, 10,11,12)], #Picks up gamma, delta_1, and delta
+  tableCESa <- xtable(dataCES[,c(4,5,6, 10,11,12, 16,17,18)], #Picks up lambda, delta, sigma
                       caption=paste("CES model (with $", tolower(energyType), "$).
-$\\gamma$, $\\delta_1$, and $\\delta$ parameters for 1980-2011 (US, UK, JP), 1991-2010 (CN and ZA), and 1991-2011 (SA, IR, TZ, and ZM).
+$\\lambda$, $\\delta$, and $\\sigma$ parameters for 1980-2011 (US, UK, JP), 1991-2010 (CN and ZA), and 1991-2011 (SA, IR, TZ, and ZM).
 (Parameter estimates beneath symbol.
 95\\% confidence interval bounds to left and right.)", sep=""),
-                      label=paste("tab:CES_Parameters_With_", energyType, sep=""),
-                      digits = c(1, 2,2,2, 2,2,2, 2,2,2),
+                      label=paste("tab:CES_Parameters_A_With_", energyType, sep=""),
+                      digits = c(1, 4,4,4, 2,2,2, 2,2,2),
                       align = "r|ccc|ccc|ccc" #Sets alignment of the numbers in the columns
@@
   rownames(dataCES) <- countryAbbrevs
-  tableCESb <- xtable(dataCES[,c(4,5,6, 13,14,15, 16,17,18)], #Picks up lambda, sigma_1, and sigma
+  tableCESb <- xtable(dataCES[,c(1,2,3, 7,8,9, 13,14,15)], #Picks up gamma, delta_1, and sigma_1
                       caption=paste("CES model (with $", tolower(energyType), "$).
-$\\lambda$, $\\sigma_1$, and $\\sigma$ parameters for 1980-2011 (US, UK, JP), 1991-2010 (CN and ZA), and 1991-2011 (SA, IR, TZ, and ZM).
+$\\gamma$, $\\delta_1$, and $\\sigma_1$ parameters for 1980-2011 (US, UK, JP), 1991-2010 (CN and ZA), and 1991-2011 (SA, IR, TZ, and ZM).
 (Parameter estimates beneath symbol.
 95\\% confidence interval bounds to left and right.)", sep=""),
-                      label=paste("tab:CES_Parameters_With_", energyType, sep=""),
-                      digits = c(1, 4,4,4, 2,2,2, 2,2,2),
+                      label=paste("tab:CES_Parameters_B_With_", energyType, sep=""),
+                      digits = c(1, 2,2,2, 2,2,2, 2,2,2),
                       align = "r|ccc|ccc|ccc"  #Sets alignment of the numbers in the columns
@@
   ######################
+  cesQModels <- lapply(countryAbbrevs, cesModel, energyType="Q")
+  aicCESq <- data.frame(lapply(cesQModels, AIC))
+  rownames(aicCESq)
 

### 2013-04-11 EconGrowth.Rnw
Re-arranged the CES parameter tables in the appendix of the paper.

--- 2013-03-28 EconGrowth.Rnw
@@
       \item AIC rows in the AIC table
+      \item \st{Re-organize CES tables into (a) $\lambda$, $\delta$, $\sigma$ and (b) $\gamma$, $\delta_1$, $\sigma_1$}
       \end{itemize}
-\item Heun: Deal with missing covariance numbers when columns have unequal length. Use the \texttt{subset} command.
+\item Heun: Deal with missing covariance numbers when columns have unequal length. Use the \texttt{subset} command?
 \item Heun: Eliminate blanks in the coefficient tables for the 95\% CIs in the Cobb-Douglas with energy rows. Asked Pruim about this via email on 4 Feb 2013 but have not heard a response.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-<<test3dPlot, eval=TRUE>>=
-sf3DSSEGraph("US", "Q")
-@
 
@@
 <<CES_Params_Table, results='asis'>>=
-#printCESParamsTable("Q"); printCESParamsTable("X"); printCESParamsTable("U")
 printCESParamsTableA("Q"); printCESParamsTableB("Q")

### 2013-04-11 EconGrowth-R-Functions.Rnw
Added code to calculate AIC values for the CES production function. However, it doesn't work at the present time, so it is commented out.

@@
 
-# ############################
-# # Aggregates the CES results for gamma, delta_1, and delta into a table for the given energyType.
-# ##
-# cesParamsTableA <- function(energyType){
-#   dataCES <- do.call("rbind", lapply(countryAbbrevs, cesCountryRow, energyType=energyType))
-#   colnames(dataCES) <- c(" ", "$\\gamma$",    " ", 
-#                          " ", "$\\lambda$",   " ",
-#                          " ", "$\\delta_1$",  " ",
-#                          " ", "$\\delta$",    " ",
-#                          " ", "$\\sigma_1$",  " ",
-#                          " ", "$\\sigma$",    " ")
-#   rownames(dataCES) <- countryAbbrevs
-#   tableCESa <- xtable(dataCES[,c(1,2,3, 7,8,9, 10,11,12)], #Picks up gamma, delta_1, and delta
-#                       caption=paste("CES model (with $", tolower(energyType), "$).
-$\\gamma$, $\\delta_1$, and $\\delta$ parameters for 1980-2011 (US, UK, JP), 1991-2010 (CN and ZA), and 1991-2011 (SA, IR, TZ, and ZM).
-(Parameter estimates beneath symbol.
-95\\% confidence interval bounds to left and right.)", sep=""),
-#                       label=paste("tab:CES_Parameters_With_", energyType, sep=""),
-#                       digits = c(1, 2,2,2, 2,2,2, 2,2,2),
-#                       align = "r|ccc|ccc|ccc" #Sets alignment of the numbers in the columns
-#                       ) 
-#   return(tableCESa)
-# }
-# 
-# ############################
-# # Aggregates the CES results for lambda, sigma_1, and sigma into a table for the given energyType.
-# ##
-# cesParamsTableB <- function(energyType){
-#   dataCES <- do.call("rbind", lapply(countryAbbrevs, cesCountryRow, energyType=energyType))
-#   colnames(dataCES) <- c(" ", "$\\gamma$",    " ", 
-#                          " ", "$\\lambda$",   " ",
-#                          " ", "$\\delta_1$",  " ",
-#                          " ", "$\\delta$",    " ",
-#                          " ", "$\\sigma_1$",  " ",
-#                          " ", "$\\sigma$",    " ")
-#   rownames(dataCES) <- countryAbbrevs
-#   tableCESb <- xtable(dataCES[,c(4,5,6, 13,14,15, 16,17,18)], #Picks up lambda, sigma_1, and sigma
-#                       caption=paste("CES model (with $", tolower(energyType), "$).
-$\\lambda$, $\\sigma_1$, and $\\sigma$ parameters for 1980-2011 (US, UK, JP), 1991-2010 (CN and ZA), and 1991-2011 (SA, IR, TZ, and ZM).
-(Parameter estimates beneath symbol.
-95\\% confidence interval bounds to left and right.)", sep=""),
-#                       label=paste("tab:CES_Parameters_With_", energyType, sep=""),
-#                       digits = c(1, 4,4,4, 2,2,2, 2,2,2),
-#                       align = "r|ccc|ccc|ccc"  #Sets alignment of the numbers in the columns
-#                       )
-#   return(tableCESb)
-# }
-#
-
 ############################
@@
   ######################
-  cesQModels <- lapply(countryAbbrevs, cesModel, energyType="Q")
-  aicCESq <- data.frame(lapply(cesQModels, AIC))
-  rownames(aicCESq)
-
+# At present, this AIC for CES code is not working. Perhaps because the CES model from the cesEst function
+# in the micEcon package does not provide its data in the correct format for the AIC function?
+# --Matthew Kuperus Heun, 10 April 2013.
+#   # CES with Q
+#   cesQModels <- lapply(countryAbbrevs, cesModel, energyType="Q")
+#   aicCESq <- data.frame(lapply(cesQModels, AIC))
+#   rownames(aicCESq) <- "CES$q$"
+#   # CES with X
+#   cesXModels <- lapply(countryAbbrevs, cesModel, energyType="X")
+#   aicDEXx <- data.frame(lapply(cesXModels, AIC))
+#   rownames(aicCESx) <- "CES$x$"
+#   # CES with U
+#   aicCESu <- cbind(US=AIC(cesModel("US", "U")), 
+#                   UK=AIC(cesModel("UK", "U")), 
+#                   JP=AIC(cesModel("JP", "U")),
+#                   CN=NA, ZA=NA, SA=NA, IR=NA, TZ=NA, ZM=NA) #No U data for these countries.
+#   rownames(aicCESu) <- "CES$u$"
   ######################
@@
   # Create the data.frame table
-  out <- rbind(aicSFk, aicSFl, aicSFq, aicSFx, aicSFu, aicCD, aicCDq, aicCDx, aicCDu, aicLINEXq, aicLINEXx, aicLINEXu) 
+  out <- rbind(aicSFk, aicSFl, aicSFq, aicSFx, aicSFu, 
+               aicCD, aicCDq, aicCDx, aicCDu, 
+               aicLINEXq, aicLINEXx, aicLINEXu) 
+#   out <- rbind(aicSFk, aicSFl, aicSFq, aicSFx, aicSFu, 
+#                aicCD, aicCDq, aicCDx, aicCDu, 
+#                aicCESq, aicCESx, aicCESu, 
+#                aicLINEXq, aicLINEXx, aicLINEXu) 
   # Create the xtable with caption and label

### 2013-04-11 EconGrowth.Rnw
Added code to calculate AIC values for the CES production function. However, it doesn't work at the present time, so it is commented out.
Added a comment on the status of the AIC code for CES in the to-do list of the paper.
Rearranged authors and acknowledgements.

@@
 
-\author[Calvin]{Caleb Reese}
-\author[Calvin]{Lucas Timmer}
+\author[CalvinEngr]{Caleb Reese}
+\author[CalvinEngr]{Lucas Timmer}
+\author[CalvinEngr]{Matthew Kuperus Heun\corref{cor1}}
 \author[Stellenbosch]{Martin de Wit}
-\author[Calvin]{Matthew Kuperus Heun\corref{cor1}}
+\author[CalvinMath]{Randall J. Pruim}
 \ead{mkh2@calvin.edu, tel: +1 (616) 526-6663, fax: +1 (616) 526-6501}
@@
 \cortext[cor1]{Corresponding author}
-\address[Calvin]{Engineering Department, Calvin College, Grand Rapids, MI 49546, USA}
+\address[CalvinEngr]{Engineering Department, Calvin College, Grand Rapids, MI 49546, USA}
 \address[Stellenbosch]{Stellenbosch University, Faculty of Economics and Management Sciences, School of Public Leadership, P.O. Box 610, Bellville 7535, South Africa}
+\address[CalvinMath]{Mathematics \& Statistics Department, Calvin College, Grand Rapids, MI 49546, USA}
 
@@
 \begin{itemize}
-\item Reese: Add text from Word verson of paper to the LaTeX version.
+\item Heun: Add 9-panel lattice graph for min($SSE_y$) graphs for the CD model.
+\item Heun: Add CI vs. params plots for all model types. Maybe as a lattice graph where each model type is a panel.
 \item Heun: Add CES production function fits
@@
       \item Fix the problems with $\sigma_1$ and $\sigma$ values in the CES parameter tables in the appendix
-      \item AIC rows in the AIC table
+      \item AIC rows in the AIC table (Code is in the createAICTable function, but it is not yet working)
       \item \st{Re-organize CES tables into (a) $\lambda$, $\delta$, $\sigma$ and (b) $\gamma$, $\delta_1$, $\sigma_1$}
+      \item Add a CES model without energy option (unspecified energyType parameters means CES without energy)
       \end{itemize}
@@
 \item de Wit: review, critique, and contextualize.
+\item \st{Reese: Add text from Word verson of paper to the LaTeX version.}
 \item \st{Heun: Ask Martin if he can supply an ``Economics'' affiliation. Will probably make a stronger paper.}
@@
 Funding for Caleb Reese and Lucas Timmer was generously supplied by the Jack and Lois Kuipers Applied Mathematics Endowment and the Calvin College Alumni Association.
+A Calvin Research Fellowship provided funding for Matthew Kuperus Heun.
 Funding for Martin de Wit was provided by *******.
-The authors thank Randall Pruim (Calvin College) and Loren L.
-Heun (Western Michigan University) for their insightful comments on and invaluable assistance with the statistical analyses presented herein.
+The authors thank Loren L.
+Heun (Western Michigan University) for insightful critique of the statistical analyses presented herein.
 %% The Appendices part is started with the command \appendix;

### 2013-04-11 EconGrowth-R-Functions.Rnw
Beginning the process of including a CES model without energy. Can now call the cesModel function without an energyType term and get a model back.

@@
 # Set some common names for CES variables.
-xNames = c("iCapStk", "iLabor", "iEToFit")
+xNamesWithoutEnergy = c("iCapStk", "iLabor")
+xNamesWithEnergy = c("iCapStk", "iLabor", "iEToFit")
 tName = "iYear"
@@
 loadAndPrepDataForCES <- function(countryAbbrev, energyType){
+print(paste("Inside loadAndPrepDataForCES. countryAbbrev =", countryAbbrev))
+print(paste("missing(energyType) =", missing(energyType)))
   dataTable <- loadData(countryAbbrev)
+print("loaded data")
+  # Trim data from China and South Africa that is missing labor information for 2011.
+  dataTable <- subset(dataTable, !is.na(iLabor))
+print("Trimmed data")
+  if (!missing(energyType)){
+print("Inside if not missing energy type")
     if (energyType == "U"){
@@
     }
-  # Trim data from China and South Africa that is missing labor information for 2011.
-  dataTable <- subset(dataTable, !is.na(iLabor))
     # We need to do the CES fit with the desired energyType.
@@
     dataTable <- replaceColName(dataTable, energyType, "iEToFit")
+  }
+print("right before return.")
   return(dataTable)
+}
+
+########################
+# Returns a cesEst model (without energy) for the country specified.
+##
+cesModelNoEnergy <- function(countryAbbrev){
+print(paste("Inside cesModelNoEnergy. countryAbbrev =", countryAbbrev))
+  # Load the data that we need.
+  dataTable <- loadAndPrepDataForCES(countryAbbrev)
+  control=nls.lm.control(maxiter=1000, maxfev=2000)
+  modelCES <- cesEst(data=dataTable, yName=yName, xNames=xNamesWithoutEnergy, tName=tName, control=control)
+  return(modelCES)
 }
@@
 # energyType should be one of Q", "X", or "U".
+# If energyType is not specified, this method dispatches to the function cesModelNoEnergy(countryAbbrev)
 ##
 cesModel <- function(countryAbbrev, energyType){
+  if (missing(energyType)){
+print(paste("Inside cesModel. energyType is missing. countryAbbrev =", countryAbbrev))
+    return(cesModelNoEnergy(countryAbbrev))
+  }
+  # We need to include energy in the production function.
   # Load the data that we need.
@@
   control=nls.lm.control(maxiter=1000, maxfev=2000)
+  # Decide which independent variables we want to use
+  xNamesToUse <- xNamesWithEnergy    
+  # Now estimate the parameters for the CES production function.
   if (countryAbbrev == "US") {
@@
     # complimentary.  We'll let the estCES function solve for the best value.
-    modelCES <- cesEst(data=dataTable, yName=yName, xNames=xNames, tName=tName, control=control,
+    modelCES <- cesEst(data=dataTable, yName=yName, xNames=xNamesToUse, tName=tName, control=control,
                        method="LM",
@@
     rho1 = 0.0
-    modelCES <- cesEst(data=dataTable, yName=yName, xNames=xNames, tName=tName, control=control,
+    modelCES <- cesEst(data=dataTable, yName=yName, xNames=xNamesToUse, tName=tName, control=control,
                        method="LM",
@@
     # that (kl) and (e) are complimentary.
-    modelCES <- cesEst(data=dataTable, yName=yName, xNames=xNames, tName=tName, control=control,
+    modelCES <- cesEst(data=dataTable, yName=yName, xNames=xNamesToUse, tName=tName, control=control,
                        method="LM"
@@
     rho = 0.0
-    modelCES <- cesEst(data=dataTable, yName=yName, xNames=xNames, tName=tName, control=control,
+    modelCES <- cesEst(data=dataTable, yName=yName, xNames=xNamesToUse, tName=tName, control=control,
                        method="LM",
@@
     # An unconstrained fit works for South Africa.  Results are sigma1 = 0.05, signalling complementarity
-    # between k and l.  sigma = 0.03, indicating complementatity between (kl) and (e).
-    modelCES <- cesEst(data=dataTable, yName=yName, xNames=xNames, tName=tName, control=control,
+    # between k and l.  sigma = 0.03, indicating complementarity between (kl) and (e).
+    modelCES <- cesEst(data=dataTable, yName=yName, xNames=xNamesToUse, tName=tName, control=control,
                        method="LM",
@@
     # Iran works with an unconstrained fit.
-    modelCES <- cesEst(data=dataTable, yName=yName, xNames=xNames, tName=tName, control=control,
+    modelCES <- cesEst(data=dataTable, yName=yName, xNames=xNamesToUse, tName=tName, control=control,
                        method="LM",
@@
     # However, none of the rho or sigma values are statistically significant.
-    modelCES <- cesEst(data=dataTable, yName=yName, xNames=xNames, tName=tName, control=control,
+    modelCES <- cesEst(data=dataTable, yName=yName, xNames=xNamesToUse, tName=tName, control=control,
                        method="PORT",
@@
     # ZM works with the PORT algorithm, but not the LM algorithm.
-    modelCES <- cesEst(data=dataTable, yName=yName, xNames=xNames, tName=tName, control=control,
+    modelCES <- cesEst(data=dataTable, yName=yName, xNames=xNamesToUse, tName=tName, control=control,
                        method="PORT",

### 2013-04-11 EconGrowth.Rnw
Fixed a bug with the email address for MKH.
Beginning the process of including a CES model without energy. Can now call the cesModel function without an energyType term and get a model back.

@@
 \author[CalvinEngr]{Matthew Kuperus Heun\corref{cor1}}
+\ead{mkh2@calvin.edu, tel: +1 (616) 526-6663, fax: +1 (616) 526-6501}
 \author[Stellenbosch]{Martin de Wit}
 \author[CalvinMath]{Randall J. Pruim}
-\ead{mkh2@calvin.edu, tel: +1 (616) 526-6663, fax: +1 (616) 526-6501}
 
@@
       \item Add a CES model without energy option (unspecified energyType parameters means CES without energy)
+      \item Revisit my assumptions for the CES production function (with energy) for each country.
       \end{itemize}
+\item Heun: \st{Investigate use of the micEcon package transLogEst function for CD parameter estimation. Doesn't look like it will work, because it doesn't do the CD form of interest to us.}
 \item Heun: Deal with missing covariance numbers when columns have unequal length. Use the \texttt{subset} command?
@@
 
+\subsection{CES without energy}
+
+<<CES_Params_Graph, fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.pos="H", fig.cap="CES (without energy) model parameters.
+Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
+
+modelUS <- cesModel("US")
+print(summary(modelUS))
+
+@
+
 \subsection{CES with $Q$}
@@
 Funding for Caleb Reese and Lucas Timmer was generously supplied by the Jack and Lois Kuipers Applied Mathematics Endowment and the Calvin College Alumni Association.
-A Calvin Research Fellowship provided funding for Matthew Kuperus Heun.
+Support for Matthew Kuperus Heun was provided by a Calvin College Research Followship.
 Funding for Martin de Wit was provided by *******.

### 2013-04-11 EconGrowth-R-Functions.Rnw
Improved documentation.

@@
 # Also, replaces the name of the desired energy column with "iEToFit".
+# If you omit the energyType parameter, "iEToFit" will not appear in the column names, because
+# it is assumed that you want a CES fit without an energy term.
 # Returns a data.frame with the loaded data.
@@
 loadAndPrepDataForCES <- function(countryAbbrev, energyType){
-print(paste("Inside loadAndPrepDataForCES. countryAbbrev =", countryAbbrev))
-print(paste("missing(energyType) =", missing(energyType)))
   dataTable <- loadData(countryAbbrev)
-print("loaded data")
   # Trim data from China and South Africa that is missing labor information for 2011.
   dataTable <- subset(dataTable, !is.na(iLabor))
-print("Trimmed data")
   if (!missing(energyType)){
-print("Inside if not missing energy type")
     if (energyType == "U"){
@@
   }
-print("right before return.")
   return(dataTable)
@@
 cesModelNoEnergy <- function(countryAbbrev){
-print(paste("Inside cesModelNoEnergy. countryAbbrev =", countryAbbrev))
   # Load the data that we need.
@@
   if (missing(energyType)){
-print(paste("Inside cesModel. energyType is missing. countryAbbrev =", countryAbbrev))
     return(cesModelNoEnergy(countryAbbrev))

### 2013-04-11 EconGrowth.Rnw
Added non-energy CES models for all countries.

@@
 
-modelUS <- cesModel("US")
-print(summary(modelUS))
+print("US")
+print(summary(cesModel("US")))
+print("UK")
+print(summary(cesModel("UK")))
+print("JP")
+print(summary(cesModel("JP")))
+print("CN")
+print(summary(cesModel("CN")))
+print("ZA")
+print(summary(cesModel("ZA")))
+print("SA")
+print(summary(cesModel("SA")))
+print("IR")
+print(summary(cesModel("IR")))
+print("TZ")
+print(summary(cesModel("TZ")))
+print("ZM")
+print(summary(cesModel("ZM")))
 

### 2013-04-11 EconGrowth-R-Functions.Rnw
Now including CES without energy predictions in the CES lattice graph.

@@
 # Returns a data.frame with the predictions.
+# If energyType is not specified, the CES model without energy will be used.
 ##
 cesPredictions <- function(countryAbbrev, energyType){
-  dataTable <- loadAndPrepDataForCES(countryAbbrev, energyType)
+  if (missing(energyType)){
+    model <- cesModel(countryAbbrev)
+  } else {
     # Can't make predictions for any of CN, ZA, SA, IR, TZ, or ZM if we're interested in U
@@
     model <- cesModel(countryAbbrev, energyType)
+  }
   pred <- fitted(model)
@@
 # that corresponds, row for row, with the AllData.txt file.
+# If energyType is not specified, the CES model without energy will be used for the predictions.
 ##
 cesPredictionsColumn <- function(energyType){
+  if (missing(energyType)){
+    out <- do.call("rbind", lapply(countryAbbrevs, cesPredictions))      
+    colnames(out) <- "predGDP"
+  } else {
     out <- do.call("rbind", lapply(countryAbbrevs, cesPredictions, energyType=energyType))  
     colnames(out) <- c(paste("predGDP", energyType, sep=""))
+  }
   return(out)
@@
   dataTable <- loadData("All") #Grab the raw data
+  predictions <- cesPredictionsColumn() #Predictions from CES without energy
   predictionsQ <- cesPredictionsColumn("Q") #Predictions from CES with Q
@@
   #Now add the predictions columns to the data.
-  dataTable <- cbind(dataTable, predictionsQ, predictionsX, predictionsU) 
+  dataTable <- cbind(dataTable, predictions, predictionsQ, predictionsX, predictionsU) 
   graphType <- "b" #b is for both line and symbol
-  lineTypes <- c(0, 2, 4, 1) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
-  lineWidths <- c(0, 1, 1, 1) #line widths. 0 means no line.
-  colors <- c("black", "red", "blue", "darkorange") #line and symbol colors
-  symbols <- c(1, NA, NA, NA)  #NA gives no symbol.
+  lineTypes <- c(0, 1, 2, 4, 1) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
+  lineWidths <- c(0, 2, 1, 1, 1) #line widths. 0 means no line.
+  colors <- c("black", "black", "red", "blue", "darkorange") #line and symbol colors
+  symbols <- c(1, NA, NA, NA, NA)  #NA gives no symbol.
   # Code that deals with items that are specific to whether we want all countries or a specific country.  
@@
   }
-  graph <- xyplot(iGDP+predGDPQ+predGDPX+predGDPU ~ Year | Country, data=dataTable,
+  graph <- xyplot(iGDP+predGDP+predGDPQ+predGDPX+predGDPU ~ Year | Country, data=dataTable,
                   type=graphType,
@@
                   pch = symbols, col.symbol = colors, #Controls symbol parameters
-                  key=list(text=list(c("Actual", "With $q$", "With $x$", "With $u$")),
+                  key=list(text=list(c("Actual", "No energy", "With $q$", "With $x$", "With $u$")),
                            type=graphType,

### 2013-04-11 EconGrowth.Rnw
Now including CES without energy predictions in the CES lattice graph.

--- 2013-04-11 EconGrowth.Rnw
@@
 
-modelUS <- cesModel("US")
-print(summary(modelUS))
+# print("US")
+# print(summary(cesModel("US")))
+# print("UK")
+# print(summary(cesModel("UK")))
+# print("JP")
+# print(summary(cesModel("JP")))
+# print("CN")
+# print(summary(cesModel("CN")))
+# print("ZA")
+# print(summary(cesModel("ZA")))
+# print("SA")
+# print(summary(cesModel("SA")))
+# print("IR")
+# print(summary(cesModel("IR")))
+# print("TZ")
+# print(summary(cesModel("TZ")))
+# print("ZM")
+# print(summary(cesModel("ZM")))
+
+# print(cesPredictionsColumn("Q"))
+# print(cesPredictionsColumn())
+
+# createCESLatticeGraph()
 

### 2013-04-11 EconGrowth.Rnw
Updated the to-do list.

@@
 \author[CalvinEngr]{Matthew Kuperus Heun\corref{cor1}}
-\ead{mkh2@calvin.edu, tel: +1 (616) 526-6663, fax: +1 (616) 526-6501}
+\ead{mkh2@calvin.edu}
 \author[Stellenbosch]{Martin de Wit}
@@
 \address[CalvinEngr]{Engineering Department, Calvin College, Grand Rapids, MI 49546, USA}
-\address[Stellenbosch]{Stellenbosch University, Faculty of Economics and Management Sciences, School of Public Leadership, P.O. Box 610, Bellville 7535, South Africa}
+\address[Stellenbosch]{Faculty of Economics and Management Sciences, School of Public Leadership, Stellenbosch University, P.O. Box 610, Bellville 7535, South Africa}
 \address[CalvinMath]{Mathematics \& Statistics Department, Calvin College, Grand Rapids, MI 49546, USA}
@@
 \item Heun: Add 9-panel lattice graph for min($SSE_y$) graphs for the CD model.
-\item Heun: Add CI vs. params plots for all model types. Maybe as a lattice graph where each model type is a panel.
+\item Heun: Add CI vs. params plots for all model types (the triangle plots from the seminar). Maybe as a lattice graph where each model type is a panel.
 \item Heun: Add CES production function fits
@@
       \item AIC rows in the AIC table (Code is in the createAICTable function, but it is not yet working)
-      \item \st{Re-organize CES tables into (a) $\lambda$, $\delta$, $\sigma$ and (b) $\gamma$, $\delta_1$, $\sigma_1$}
       \item Add a CES model without energy option (unspecified energyType parameters means CES without energy)
+        \begin{itemize}
+          \item{Extract CES without energy parameters from the ``without energy'' models and correctly name them: $\sigma \rightarrow \sigma_1$, $\rho \rightarrow \rho_1$, $\delta \rightarrow \delta_1$}
+          \item{Add CES without energy parameters to tables of results in the appendix}
+          \item{Create a CES without energy parameters graphs (with CIs) in the paper}
+          \item{\st{Add CES without energy lines to the CES lattice graph}}
+        \end{itemize}
       \item Revisit my assumptions for the CES production function (with energy) for each country.
       \end{itemize}
-\item Heun: \st{Investigate use of the micEcon package transLogEst function for CD parameter estimation. Doesn't look like it will work, because it doesn't do the CD form of interest to us.}
 \item Heun: Deal with missing covariance numbers when columns have unequal length. Use the \texttt{subset} command?
-\item Heun: Eliminate blanks in the coefficient tables for the 95\% CIs in the Cobb-Douglas with energy rows. Asked Pruim about this via email on 4 Feb 2013 but have not heard a response.
+\item Heun: Eliminate blanks in the coefficient tables for the 95\% CIs in the Cobb-Douglas with energy rows
       \begin{itemize}
@@
 \item \st{Reese: Add text from Word verson of paper to the LaTeX version.}
+\item{\st{Heun: Investigate use of the micEcon package transLogEst function for CD parameter estimation. Doesn't look like it will work, because it doesn't do the CD form of interest to us.}}
+\item \st{Heun: Re-organize CES tables into (a) $\lambda$, $\delta$, $\sigma$ and (b) $\gamma$, $\delta_1$, $\sigma_1$}
 \item \st{Heun: Ask Martin if he can supply an ``Economics'' affiliation. Will probably make a stronger paper.}

### 2013-04-12 EconGrowth-R-Functions.Rnw
Now doing CES without energy in the cesData function.

@@
   }
-  if (missing(energyType) || is.na(energyType)){
+  if (missing(energyType) || is.na(energyType) || is.null(energyType)){
     # If we don't want energy included, we have data for all known countries. We need to check this case
@@
   return(TRUE)
+}
+
+###############################
+# Tells whether we have data for this combination of country and energy type for a CES curve fit.
+# a missing energyType or energyType == NA means that we want to develop a model without energy, if possible.
+# This function re-routes to haveDataCD, because the logic is identical.
+#
+# returns logical value (TRUE or FALSE)
+##
+haveDataCES <- function(countryAbbrev, energyType){
+  return(haveDataCD(countryAbbrev, energyType))
+}
+
+###############################
+# Tells whether we have data for this combination of country and energy type for a LINEX curve fit.
+# a missing energyType or energyType == NA means that we want to develop a model without energy, if possible.
+# This function re-routes to haveDataCD, because the logic is identical.
+#
+# returns logical value (TRUE or FALSE)
+##
+haveDataLINEX <- function(countryAbbrev, energyType){
+  return(haveDataCD(countryAbbrev, energyType))
 }
@@
 ##
-loadAndPrepDataForCES <- function(countryAbbrev, energyType){
+loadAndPrepDataForCES <- function(countryAbbrev, energyType = NULL){
   dataTable <- loadData(countryAbbrev)
@@
   dataTable <- subset(dataTable, !is.na(iLabor))
-  if (!missing(energyType)){
+  if (missing(energyType) || is.na(energyType) || is.null(energyType) || energyType == ""){
+    # We're done. Don't have to deal with special issues with energyType.
+    return(dataTable)
+  }
+  # We have an energyType argument. Do some additional checking.
   if (energyType == "U"){
@@
   dataTable <- replaceColName(dataTable, energyType, "iEToFit")
-  }
   return(dataTable)
@@
 cesModel <- function(countryAbbrev, energyType){
-  if (missing(energyType)){
+  if (missing(energyType) || is.null(energyType) || is.na(energyType) || energyType == ""){
     return(cesModelNoEnergy(countryAbbrev))
@@
 # countryAbbrev is a string containing the 2-letter abbreviation for the country, e.g. "US" or "CN"
-# energyType is a string, one of "Q", "X", or "U"
+# energyType is a string, one of "Q", "X", or "U". Not specifying an energy type means we're interested
+# in a CES function without energy.
 #
-# returns a data.frame of data for the LINEX model.
+# returns a data.frame of data for the CES model.
 # First row is the +95% CI on all parameters
@@
 ##
-cesData <- function(countryAbbrev, energyType){
+cesData <- function(countryAbbrev, energyType=NULL){
   #First, check to see if we want useful work (U) AND one of the countries for which we don't have data.
-  if (!haveDataCD(countryAbbrev, energyType)){
-    #Return a column of NAs if the above conditions have been met.
+  if (!haveDataCES(countryAbbrev, energyType)){
+    #Return a column of NAs if we don't have data available for this combination of country and energy type.
     nRows <- 3 # +95% CI, CDe, and -95% CI.
@@
   summaryCES <- summary(modelCES) # Gives a summary table.
-#print(summaryCES)
   # Calculate the degrees of freedom as N_obs - N_params
+  if (is.null(energyType)){
+    # For a CES model without energy, we have 4 parameters: gamma, lambda, delta, and rho
+    dofCES <- nrow(loadAndPrepDataForCES(countryAbbrev)) - 4 #    
+  } else {
+    # For a CES model with energy, we have 6 parameters: gamma, lambda, delta, rho, delta_1, and rho_1
     dofCES <- nrow(loadAndPrepDataForCES(countryAbbrev, energyType)) - 6 # Gives the degrees of freedom for the model.
-#print(dofCES)
+  }
   tvalCES <- qt(ciHalfLevel, df = dofCES)
-#print(tvalCES)
   # Calculate confidence intervals for the parameters of the model
   ciCES <- confint(modelCES, level = ciLevel)  # Calculates confidence intervals for the CES model.
-#print(ciCES)
-  # Get confidence intervals for the elasticities of substitution
-  sigma_1.est <- deltaMethod(modelCES, "1.0 / (1.0 + rho_1)") # Estimates sigma_1 and its standard error (SE).
-#print(sigma_1.est)
+  # Get confidence intervals for the elasticities of substitution.
+  #######################
+  # Note: I would rather get the value of sigma and its standard error directly from the cesModel object.
+  # The information is all in there. You can see it as the E terms at the bottom of the
+  # print(summaryCES) results.
+  #######################
+  sigma.est <- deltaMethod(modelCES, "1.0 / (1.0 + rho)") # Estimates sigma and its standard error (SE)
+  sigmaCI <- with(sigma.est, Estimate + c(-1.0, 1.0) * tvalCES * SE)
+  if (!is.null(energyType)){
+    sigma_1.est <- deltaMethod(modelCES, "1.0 / (1.0 + rho_1)") # Estimates sigma_1 and its standard error (SE)
     sigma_1CI <- with(sigma_1.est, Estimate + c(-1.0, 1.0) * tvalCES * SE)
-  # There are some cases where the confidence intervals for sigma_1 are huge. Set them to -Inf or Inf as appropriate
-  if (is.nan(sigma_1CI[1]) || (sigma_1CI[1] < -1.0e10)){
-    sigma_1CI[1] <- -Inf 
-  }
-  if (is.nan(sigma_1CI[2]) || (sigma_1CI[2] > 1.0e10)){
-    sigma_1CI[2] <- Inf
-  }
-#print("sigma_1CI:")
-#print(sigma_1CI)
-  sigma.est <- deltaMethod(modelCES, "1.0 / (1.0 + rho)") # Estimates sigma and its standard error (SE)
-#print(sigma.est)
-  sigmaCI <- with(sigma.est, Estimate + c(-1.0, 1.0) * tvalCES * SE)
-#print("sigmaCI:")
-#print(sigmaCI)
-  # Report results with SE
-  gamma <- coef(modelCES)["gamma"] #as.numeric(coef(modelCES)["gamma"])
-  lambda <- coef(modelCES)["lambda"] #as.numeric(coef(modelCES)["lambda"])
+  }
+  if (is.null(energyType)){
+    # We're not using energy in this fit.
+    gamma <- coef(modelCES)["gamma"]
+    lambda <- coef(modelCES)["lambda"]
+    # Without energy, we get the delta coefficient that means the split between 
+    # capital and labor.
+    # With energy, delta_1 means the split between energy and labor.
+    # To be consistent, we map the delta from the "without energy" model to variable name "delta_1"
+    delta_1 <- coef(modelCES)["delta"]
+    # The without energy model can be obtained with delta = 1.0. So, we set it here.
+    delta <- 1.0
+    # The without energy model has a sigma (elasticity of substitution between k and l) that is 
+    # equivalent to the sigma_1 parameter from the "with energy" model. So, we map the names 
+    # here.
+    sigma_1 <- sigma.est$Estimate
+    # With delta = 1.0, rho has no meaning (there is no energy term). Therefore, sigma has no meaning.
+    # So, set sigma to NA
+    sigma <- NA
+    # Combine all estimates and their confidence intervals into data frames with intelligent row names
+    estCES <- data.frame(gamma=gamma, lambda=lambda, delta_1=delta_1, delta=delta, sigma_1=sigma_1, sigma=sigma)
+    row.names(estCES) <- "CES"
+    # The [1] subscripts pick off the lower confidence interval
+    # The size of the CI on delta is 0.0 for the CES model without energy, so we set the upper and lower bounds to 1.0
+    # The CI on delta_1 shows up with the variable delta for the CES model without energy.
+    lowerCES <- data.frame(gamma=ciCES["gamma","2.5 %"], lambda=ciCES["lambda", "2.5 %"],
+                           delta_1=ciCES["delta", "2.5 %"], delta=1.0,
+                           sigma_1=sigmaCI[1], sigma=NA)
+    row.names(lowerCES) <- "-95% CI"
+    # The [2] subscripts pick off the upper confidence interval
+    upperCES <- data.frame(gamma=ciCES["gamma","97.5 %"], lambda=ciCES["lambda", "97.5 %"],
+                           delta_1=ciCES["delta", "97.5 %"], delta=1.0,
+                           sigma_1=sigmaCI[2], sigma=NA)
+    row.names(upperCES) <- "+95% CI"
+  } else {
+    # We're using energy in this fit.
+    gamma <- coef(modelCES)["gamma"]
+    lambda <- coef(modelCES)["lambda"]
     delta_1 <- coef(modelCES)["delta_1"]
@@
     row.names(estCES) <- "CES"
-#print(estCES)
     # The [1] subscripts pick off the lower confidence interval
-#print(ciCES["gamma","2.5 %"])
     lowerCES <- data.frame(gamma=ciCES["gamma","2.5 %"], lambda=ciCES["lambda", "2.5 %"],
@@
     row.names(lowerCES) <- "-95% CI"
-#print(lowerCES)
     # The [2] subscripts pick off the upper confidence interval
@@
     row.names(upperCES) <- "+95% CI"
-#print(upperCES)
+  }
   # Now create the data for a table and return it
   dataCES <- rbind(upperCES, estCES, lowerCES)
-#print("dataCES")
-#print(dataCES)
   return(dataCES)

### 2013-04-12 EconGrowth.Rnw
Now doing CES without energy in the cesData function.

@@
       \begin{itemize}
-      \item \st{GDP comparison graph}
-      \item \st{Convert $\rho$ variables in the CES production function to $\sigma$}
+      \item{Get values and se for $\sigma$s directly from the \texttt{cesModel} object in the \texttt{cesData} function}
       \item Write up the decisions about parameter estimation for the CES production function fits
-      \item \st{Create parameter graphs for each country}
-      \item \st{Parameter tables for each energy type in the appendix}
       \item Fix the problems with $\sigma_1$ and $\sigma$ values in the CES parameter tables in the appendix
@@
       \item Revisit my assumptions for the CES production function (with energy) for each country.
+      \item \st{Create parameter graphs for each country}
+      \item \st{Parameter tables for each energy type in the appendix}
+      \item \st{GDP comparison graph}
+      \item \st{Convert $\rho$ variables in the CES production function to $\sigma$}
       \end{itemize}
@@
 
-# print("US")
-# print(summary(cesModel("US")))
-# print("UK")
-# print(summary(cesModel("UK")))
-# print("JP")
-# print(summary(cesModel("JP")))
-# print("CN")
-# print(summary(cesModel("CN")))
-# print("ZA")
-# print(summary(cesModel("ZA")))
-# print("SA")
-# print(summary(cesModel("SA")))
-# print("IR")
-# print(summary(cesModel("IR")))
-# print("TZ")
-# print(summary(cesModel("TZ")))
-# print("ZM")
-# print(summary(cesModel("ZM")))
-
-# print(cesPredictionsColumn("Q"))
-# print(cesPredictionsColumn())
-
-# createCESLatticeGraph()
+print(cesData("US"))
 

### 2013-04-13 EconGrowth-R-Functions.Rnw
cesCountryRow now working for situations where we do not want energy in the CES function.
Moved the entire paper and all functions over to using energyType=NA for models where you don't want energy.

@@
   }
-  if (missing(energyType) || is.na(energyType) || is.null(energyType)){
+  if (is.na(energyType)){
     # If we don't want energy included, we have data for all known countries. We need to check this case
@@
 # Returns an nls Cobb-Douglas model for the country specified
-# Give an energyType ("Q", "X", or "U") if you want to include an energy term
+# Give an energyType ("Q", "X", or "U") if you want to include an energy term. Supply energyType=NA 
+# for a model without energy.
 # If you supply a value for the gamma argument, a fit with fixed gamma will be provided.
@@
 cobbDouglasModel <- function(countryAbbrev, energyType, gamma){
-  if (missing(energyType)){
+  if (is.na(energyType)){
     # Fit the Cobb-Douglas model without energy.
-    return(cdModel(countryAbbrev))
+    return(cdModel(countryAbbrev=countryAbbrev))
   }
@@
     # Fit the Cobb-Douglas model with fixed value of gamma
-    return(cdeFixedGammaModel(countryAbbrev, energyType, gamma))
+    return(cdeFixedGammaModel(countryAbbrev=countryAbbrev, energyType=energyType, gamma=gamma))
   }
   # Fit the Cobb-Douglas model with gamma as a free parameter
-  return(cdeModel(countryAbbrev, energyType))
+  return(cdeModel(countryAbbrev=countryAbbrev, energyType=energyType))
 }
@@
   # Can't make predictions for any of CN, ZA, SA, IR, TZ, or ZM if we're interested in U
-  if (!missing(energyType)){
+  if (!is.na(energyType)){
     # Consider this replacement only if energyType has been specified.
@@
 cobbDouglasPredictionsColumn <- function(energyType){
-  if (missing(energyType)){
-    out <- do.call("rbind", lapply(countryAbbrevs, cobbDouglasPredictions)) #rbinds all the predictions together
+  out <- do.call("rbind", lapply(countryAbbrevs, cobbDouglasPredictions, energyType=energyType))
+  if (is.na(energyType)){
     colnames(out) <- c("predGDP")
   } else {
-    out <- do.call("rbind", lapply(countryAbbrevs, cobbDouglasPredictions, energyType=energyType))
     colnames(out) <- c(paste("predGDP", energyType, sep=""))
@@
 # countryAbbrev is a string containing the 2-letter abbreviation for the country, e.g. "US" or "CN"
-# energyType is a string, one of "Q", "X", or "U"
+# energyType is a string, one of "Q", "X", "U", or NA. NA means you want a CD model without energy.
 #
@@
 cobbDouglasData <- function(countryAbbrev, energyType){
+print("Inside cobbDouglasData")
+print(paste("energyType =", energyType))
   #First, check to see if we want useful work (U) AND one of the countries for which we don't have data.
@@
   }
+print("After if ! haveDataCD")
   # We have a combination of country and energy type for which we have data.
-  modelCD <- cobbDouglasModel(countryAbbrev, energyType)
+  modelCD <- cobbDouglasModel(countryAbbrev=countryAbbrev, energyType=energyType)
+print("After cobbDouglasModel")
   summaryCD <- summary(modelCD) # Gives the nls summary table.
@@
   tvalCD <- qt(ciHalfLevel, df = dofCD)
-  if (missing(energyType)){
+  if (is.na(energyType)){
+print("Inside if is.na(energyType)")
     #Cobb-Douglas without energy
@@
   dataCD <- cobbDouglasData(countryAbbrev, energyType)
-  if (missing(energyType)){
+  if (is.na(energyType)){
     out <- cbind(dataCD["-95% CI", "lambda"], dataCD["CD", "lambda"], dataCD["+95% CI", "lambda"],
@@
 # Creates a number of rows in a data.frame that contain information 
-# about the coefficients of a Cobb-Douglas model for countryName.
+# about the coefficients of a Cobb-Douglas model for countryAbbrev.
 # Each parameter has its own row with confidence intervals.
@@
 ##
-cobbDouglasCountryRowsForParamsGraph <- function(countryName, energyType){
+cobbDouglasCountryRowsForParamsGraph <- function(countryAbbrev, energyType){
+print("Inside cobbDouglasCountryRowsForParamsGraph")
   #Create three rows, one for each parameter. Each row is a data.frame so that it is plottable!
-  if (missing(energyType)){
+  if (is.na(energyType)){
+print("Inside is.na(energyType)")
     valueRow <- "CD"
-    dataCD <- cobbDouglasData(countryName)
+    dataCD <- cobbDouglasData(countryAbbrev=countryAbbrev, energyType=NA)
+print("After cobbDouglasData")
   } else {
     valueRow <- "CDe"
-    dataCD <- cobbDouglasData(countryName, energyType)
+    dataCD <- cobbDouglasData(countryAbbrev=countryAbbrev, energyType=energyType)
   }
   # These rows are common to the "with" and "without" energy cases.
-  lambdaRow <- data.frame(country = countryName, 
+  lambdaRow <- data.frame(country = countryAbbrev, 
                           parameter = "lambda", 
@@
                           upperCI = dataCD["+95% CI", "lambda"])
-  alphaRow <- data.frame(country = countryName, 
+  alphaRow <- data.frame(country = countryAbbrev, 
                          parameter = "alpha",
@@
                          upperCI = dataCD["+95% CI", "alpha"])
-  betaRow <- data.frame(country = countryName, 
+  betaRow <- data.frame(country = countryAbbrev, 
                         parameter = "beta",
@@
                         upperCI = dataCD["+95% CI", "beta"])
-  if (missing(energyType)){
+  if (is.na(energyType)){
     table <- rbind(lambdaRow, alphaRow, betaRow)
   } else {
-    gammaRow <- data.frame(country = countryName, 
+    gammaRow <- data.frame(country = countryAbbrev, 
                            parameter = "gamma",
@@
   #Do rbind on the results of creating a row in the table for every country abbreviation that we know.
-  dataCD <- do.call("rbind", lapply(countryAbbrevs, cobbDouglasCountryRow))
+  dataCD <- do.call("rbind", lapply(countryAbbrevs, cobbDouglasCountryRow, energyType=NA))
   rownames(dataCD) <- countryAbbrevs
@@
 # Prints a table with parameters from a Cobb-Douglas model for the given energyType. 
-# Leave energyType blank to print a table for Cobb-Douglas without energy.
+# Set energyType=NA to print a table for Cobb-Douglas without energy.
 ##
 printCDParamsTable <- function(energyType){
-  if (missing(energyType)){
+  if (is.na(energyType)){
     print(cobbDouglasParamsTableNoEnergy(), 
@@
 #############################
-# Creates a graph with confidence intervals for the Cobb-Douglas model for the given energyType
+# Creates a graph with confidence intervals for the Cobb-Douglas model for the given energyType. If you 
+# want the Cobb-Douglas model without energy, supply energyType=NA.
 ##
 createCDParamsGraph <- function(energyType){
-  if (missing(energyType)){
+print("Inside createCDParamsGraph")
+  if (is.na(energyType)){
     # Create a data table with the following columns:
     # country abbrev, parameter (lambda, alpha, or beta), -95% CI, value, +95% CI
-    dataTable <- do.call("rbind", lapply(countryAbbrevs, cobbDouglasCountryRowsForParamsGraph))
+    dataTable <- do.call("rbind", lapply(countryAbbrevs, cobbDouglasCountryRowsForParamsGraph, energyType=NA))
+print("After lapply(cobbDouglasCountryRowsForParamsGraph")
     graph <- segplot(country ~ upperCI + lowerCI | parameter, 
@@
                      index.cond = list(c(2,3,1)), #orders the panels as alpha, beta, lambda, gamma
-                     strip = strip.custom(factor.levels=c("$\\lambda$ [1/year]", "$\\alpha$", "$\\beta$"), #sets labels in strip 
-                                          bg="transparent"), #sets background color in strip
+                     #sets labels in strip and background color.
+                     strip = strip.custom(factor.levels=c("$\\lambda$ [1/year]", "$\\alpha$", "$\\beta$"), 
+                                          bg="transparent"),
                      col = "black", #Sets line color to black
@@
   dataTable <- loadData("All") #Grab the raw data
-  predictions <- cobbDouglasPredictionsColumn()     #Predictions from CD without energy
-  predictionsQ <- cobbDouglasPredictionsColumn("Q") #Predictions from CD with Q
-  predictionsX <- cobbDouglasPredictionsColumn("X") #Predictions from CD with X
-  predictionsU <- cobbDouglasPredictionsColumn("U") #Predictions from CD with U
+  predictions  <- cobbDouglasPredictionsColumn(energyType=NA)  #Predictions from CD without energy
+print("After cobbDouglasPredictionsColumn(energyType=NA)")
+  predictionsQ <- cobbDouglasPredictionsColumn(energyType="Q") #Predictions from CD with Q
+  predictionsX <- cobbDouglasPredictionsColumn(energyType="X") #Predictions from CD with X
+  predictionsU <- cobbDouglasPredictionsColumn(energyType="U") #Predictions from CD with U
   #Now add the predictions columns to the data.
@@
   }  
+print("Before xyplot")
   graph <- xyplot(iGDP+predGDP+predGDPQ+predGDPX+predGDPU ~ Year | Country, data=dataTable,
@@
                   )
+print("After xyplot")
   return(graph)
@@
 # Also, replaces the name of the desired energy column with "iEToFit".
-# If you omit the energyType parameter, "iEToFit" will not appear in the column names, because
+# If you set energyType=NA, "iEToFit" will not appear in the column names, because
 # it is assumed that you want a CES fit without an energy term.
@@
 ##
-loadAndPrepDataForCES <- function(countryAbbrev, energyType = NULL){
+loadAndPrepDataForCES <- function(countryAbbrev, energyType){
+print(paste("Inside loadAndPrepDataForCES. energyType =", energyType))
   dataTable <- loadData(countryAbbrev)
@@
   dataTable <- subset(dataTable, !is.na(iLabor))
-  if (missing(energyType) || is.na(energyType) || is.null(energyType) || energyType == ""){
+  if (is.na(energyType)){
+print("Inside is.na(energyType) in loadAndPrepDataForCES")
     # We're done. Don't have to deal with special issues with energyType.
@@
   }
+print("After is.na(energyType) block")
   # We have an energyType argument. Do some additional checking.
@@
   # Load the data that we need.
-  dataTable <- loadAndPrepDataForCES(countryAbbrev)
+  dataTable <- loadAndPrepDataForCES(countryAbbrev, energyType=NA)
   control=nls.lm.control(maxiter=1000, maxfev=2000)
@@
 # Returns a cesEst model for the country and energyType specified.
-# energyType should be one of Q", "X", or "U".
-# If energyType is not specified, this method dispatches to the function cesModelNoEnergy(countryAbbrev)
+# energyType should be one of Q", "X", "U", or NA.
+# If energyType=NA, this method dispatches to the function cesModelNoEnergy(countryAbbrev)
 ##
 cesModel <- function(countryAbbrev, energyType){
-  if (missing(energyType) || is.null(energyType) || is.na(energyType) || energyType == ""){
+print(paste("Inside cesModel. energyType =", energyType))
+  if (is.na(energyType)){
+print("Inside is.na(energyType)")
     return(cesModelNoEnergy(countryAbbrev))
@@
 # Returns a data.frame with the predictions.
-# If energyType is not specified, the CES model without energy will be used.
+# If energyType=NA, the CES model without energy will be used.
 ##
 cesPredictions <- function(countryAbbrev, energyType){
-  if (missing(energyType)){
-    model <- cesModel(countryAbbrev)
-  } else {
+print(paste("Inside cesPredictions. energyType =", energyType))
   # Can't make predictions for any of CN, ZA, SA, IR, TZ, or ZM if we're interested in U
-    if (!(haveDataSF(countryAbbrev, energyType))){
+  if (!(haveDataCES(countryAbbrev, energyType))){
     # If we don't have data for this combination of countryAbbrev and energyType, 
@@
   }
-    model <- cesModel(countryAbbrev, energyType)
-  }
+  model <- cesModel(countryAbbrev=countryAbbrev, energyType=energyType)
   pred <- fitted(model)
@@
 # that corresponds, row for row, with the AllData.txt file.
-# If energyType is not specified, the CES model without energy will be used for the predictions.
+# If energyType=NA is specified, the CES model without energy will be used for the predictions.
 ##
 cesPredictionsColumn <- function(energyType){
-  if (missing(energyType)){
-    out <- do.call("rbind", lapply(countryAbbrevs, cesPredictions))      
+print(paste("Inside cesPredictionsColumn. energyType =", energyType))
+  out <- do.call("rbind", lapply(countryAbbrevs, cesPredictions, energyType=energyType))  
+print("After do.call(rbind, etc.)")
+  if (is.na(energyType)){
     colnames(out) <- "predGDP"
   } else {
-    out <- do.call("rbind", lapply(countryAbbrevs, cesPredictions, energyType=energyType))  
     colnames(out) <- c(paste("predGDP", energyType, sep=""))
@@
 ##
-createCESLatticeGraph <- function(countryAbbrev, textScaling = 1.0, keyXLoc = defaultKeyXLoc, keyYLoc = defaultKeyYLoc){
+createCESLatticeGraph <- function(countryAbbrev, textScaling=1.0, keyXLoc=defaultKeyXLoc, keyYLoc=defaultKeyYLoc){
+print("Inside createCESLatticeGraph.")
   dataTable <- loadData("All") #Grab the raw data
-  predictions <- cesPredictionsColumn() #Predictions from CES without energy
-  predictionsQ <- cesPredictionsColumn("Q") #Predictions from CES with Q
-  predictionsX <- cesPredictionsColumn("X") #Predictions from CES with X
-  predictionsU <- cesPredictionsColumn("U") #Predictions from CES with U
+  predictions  <- cesPredictionsColumn(energyType=NA)  #Predictions from CES without energy
+  predictionsQ <- cesPredictionsColumn(energyType="Q") #Predictions from CES with Q
+  predictionsX <- cesPredictionsColumn(energyType="X") #Predictions from CES with X
+  predictionsU <- cesPredictionsColumn(energyType="U") #Predictions from CES with U
+print("Made it to after collecting all the predictions.")
   #Now add the predictions columns to the data.
@@
 # countryAbbrev is a string containing the 2-letter abbreviation for the country, e.g. "US" or "CN"
-# energyType is a string, one of "Q", "X", or "U". Not specifying an energy type means we're interested
+# energyType is a string, one of "Q", "X", "U", or NA. energyType=NA means we're interested
 # in a CES function without energy.
@@
 ##
-cesData <- function(countryAbbrev, energyType=NULL){
+cesData <- function(countryAbbrev, energyType){
+print("Inside cesData")
+print(paste("is.na(energyType) =", is.na(energyType)))
+  # Determine whether we want an energy term or not
+  if (is.na(energyType)){
+    wantEnergyTerm <- FALSE
+  } else {
+    wantEnergyTerm <- TRUE
+  }
+print(paste("wantEnergyTerm =", wantEnergyTerm))
   #First, check to see if we want useful work (U) AND one of the countries for which we don't have data.
@@
   # Calculate the degrees of freedom as N_obs - N_params
-  if (is.null(energyType)){
+  nRows <- nrow(loadAndPrepDataForCES(countryAbbrev, energyType))
+  if (wantEnergyTerm){
+    # For a CES model with energy, we have 6 parameters: gamma, lambda, delta, rho, delta_1, and rho_1
+    dofCES <- nRows - 6 # Gives the degrees of freedom for the model.
+  } else {
     # For a CES model without energy, we have 4 parameters: gamma, lambda, delta, and rho
-    dofCES <- nrow(loadAndPrepDataForCES(countryAbbrev)) - 4 #    
-  } else {
-    # For a CES model with energy, we have 6 parameters: gamma, lambda, delta, rho, delta_1, and rho_1
-    dofCES <- nrow(loadAndPrepDataForCES(countryAbbrev, energyType)) - 6 # Gives the degrees of freedom for the model.
+    dofCES <- nRows - 4 # Gives the degrees of freedom for the model.   
   }
@@
   sigmaCI <- with(sigma.est, Estimate + c(-1.0, 1.0) * tvalCES * SE)
-  if (!is.null(energyType)){
+  if (wantEnergyTerm){
     sigma_1.est <- deltaMethod(modelCES, "1.0 / (1.0 + rho_1)") # Estimates sigma_1 and its standard error (SE)
@@
   }
-  if (is.null(energyType)){
+  if (!wantEnergyTerm){
     # We're not using energy in this fit.
@@
 ############
-# Creates a row for the CES parameters table for the given country (2-letter code) and energyType (Q, X, or U)
+# Creates a row for the CES parameters table for the given country (2-letter code) and energyType (Q, X, U, or NA)
 ##
@@
 # Creates a number of rows in a data.frame that contain information 
-# about the coefficients of a CES model for countryName and energyType
+# about the coefficients of a CES model for countryAbbrev and energyType
 # Each parameter has its own row with confidence intervals.
@@
 # also in a column.
+# Set energyType=NA for the CES model without energy.
 # 
@@
 ##
-cesCountryRowsForParamsGraph <- function(countryName, energyType){
+cesCountryRowsForParamsGraph <- function(countryAbbrev, energyType){
   #Create six rows, one for each parameter. Each row is a data.frame so that it is plottable!
-  dataCES <- cesData(countryName, energyType)
-  gammaRow <- data.frame(country = countryName, 
+  dataCES <- cesData(countryAbbrev, energyType)
+  gammaRow <- data.frame(country = countryAbbrev, 
                           parameter = "gamma", 
@@
                           upperCI = dataCES["+95% CI", "gamma"])
-  lambdaRow <- data.frame(country = countryName, 
+  lambdaRow <- data.frame(country = countryAbbrev, 
                          parameter = "lambda",
@@
                          upperCI = dataCES["+95% CI", "lambda"])
-  delta_1Row <- data.frame(country = countryName, 
+  delta_1Row <- data.frame(country = countryAbbrev, 
                          parameter = "delta_1",
@@
                          upperCI = dataCES["+95% CI", "delta_1"])
-  deltaRow <- data.frame(country = countryName, 
+  deltaRow <- data.frame(country = countryAbbrev, 
                          parameter = "delta",
@@
                          upperCI = dataCES["+95% CI", "delta"])
-  sigma_1Row <- data.frame(country = countryName, 
+  sigma_1Row <- data.frame(country = countryAbbrev, 
                          parameter = "sigma_1",
@@
                          upperCI = dataCES["+95% CI", "sigma_1"])
-  sigmaRow <- data.frame(country = countryName, 
+  sigmaRow <- data.frame(country = countryAbbrev, 
                          parameter = "sigma",
@@
 ############################
-# Aggregates the CES results for gamma, delta_1, and delta into a table for the given energyType.
+# Aggregates the CES results for lambda, delta, and sigma into a table for the given energyType.
 ##
@@
   rownames(dataCES) <- countryAbbrevs
+  if (is.na(energyType)){
+    energyStringCaption <- "(without energy)"
+    energyStringLabel <- ""
+  } else {
+    energyStringCaption <- paste("(with $", tolower(energyType), "$)")
+    energyStringLabel <- paste("_With_", energyType, sep="")
+  }
   tableCESa <- xtable(dataCES[,c(4,5,6, 10,11,12, 16,17,18)], #Picks up lambda, delta, sigma
-                      caption=paste("CES model (with $", tolower(energyType), "$).
+                      caption=paste("CES model ", energyStringCaption, ".
 $\\lambda$, $\\delta$, and $\\sigma$ parameters for 1980-2011 (US, UK, JP), 1991-2010 (CN and ZA), and 1991-2011 (SA, IR, TZ, and ZM).
@@
 95\\% confidence interval bounds to left and right.)", sep=""),
-                      label=paste("tab:CES_Parameters_A_With_", energyType, sep=""),
+                      label=paste("tab:CES_Parameters_A", energyStringLabel, sep=""),
                       digits = c(1, 4,4,4, 2,2,2, 2,2,2),
@@
 ############################
-# Aggregates the CES results for lambda, sigma_1, and sigma into a table for the given energyType.
+# Aggregates the CES results for gamma, delta_1, and sigma_1 into a table for the given energyType.
 ##
@@
   rownames(dataCES) <- countryAbbrevs
+  if (is.na(energyType)){
+    energyStringCaption <- "(without energy)"
+    energyStringLabel <- ""
+  } else {
+    energyStringCaption <- paste("(with $", tolower(energyType), "$)")
+    energyStringLabel <- paste("_With_", energyType, sep="")
+  }
   tableCESb <- xtable(dataCES[,c(1,2,3, 7,8,9, 13,14,15)], #Picks up gamma, delta_1, and sigma_1
-                      caption=paste("CES model (with $", tolower(energyType), "$).
+                      caption=paste("CES model ", energyStringCaption, ".
 $\\gamma$, $\\delta_1$, and $\\sigma_1$ parameters for 1980-2011 (US, UK, JP), 1991-2010 (CN and ZA), and 1991-2011 (SA, IR, TZ, and ZM).
@@
 95\\% confidence interval bounds to left and right.)", sep=""),
-                      label=paste("tab:CES_Parameters_B_With_", energyType, sep=""),
+                      label=paste("tab:CES_Parameters_B", energyStringLabel, sep=""),
                       digits = c(1, 2,2,2, 2,2,2, 2,2,2),
@@
 ############################
-# Prints a table with gamma, delta_1, and delta parameters from a CES model for the given energyType. 
+# Prints a table with lambda, delta, and sigma parameters from a CES model for the given energyType. 
 ##
 printCESParamsTableA <- function(energyType){
-  print(cesParamsTableA(energyType), 
+  print(cesParamsTableA(energyType=energyType), 
     caption.placement="top", 
@@
 ############################
-# Prints a table with lambda, sigma_1, and sigma parameters from a CES model for the given energyType. 
+# Prints a table with gamma, delta_1, and sigma_1 parameters from a CES model for the given energyType. 
 ##
 printCESParamsTableB <- function(energyType){
-  print(cesParamsTableB(energyType), 
+  print(cesParamsTableB(energyType=energyType), 
     caption.placement="top", 
@@
 # Creates a number of rows in a data.frame that contain information 
-# about the coefficients of a LINEX model for countryName and energyType
+# about the coefficients of a LINEX model for countryAbbrev and energyType
 # Each parameter has its own row with confidence intervals.
@@
 ##
-linexCountryRowsForParamsGraph <- function(countryName, energyType){
+linexCountryRowsForParamsGraph <- function(countryAbbrev, energyType){
   #Create three rows, one for each parameter. Each row is a data.frame so that it is plottable!
-  dataLINEX <- linexData(countryName, energyType)
-  a_0Row <- data.frame(country = countryName, 
+  dataLINEX <- linexData(countryAbbrev, energyType)
+  a_0Row <- data.frame(country = countryAbbrev, 
                           parameter = "a_0", 
@@
                           upperCI = dataLINEX["+95% CI", "a_0"])
-  c_tRow <- data.frame(country = countryName, 
+  c_tRow <- data.frame(country = countryAbbrev, 
                          parameter = "c_t",

### 2013-04-13 EconGrowth.Rnw
cesCountryRow now working for situations where we do not want energy in the CES function.
Moved the entire paper and all functions over to using energyType=NA for models where you don't want energy.

@@
 \item Heun: Add CI vs. params plots for all model types (the triangle plots from the seminar). Maybe as a lattice graph where each model type is a panel.
+\item{Heun: Convert to using NA everywhere for models without energy}
 \item Heun: Add CES production function fits
@@
 Vertical bars indicate 95\\% confidence intervals.">>=
-createSFParamsGraph("K")
+createSFParamsGraph(factor="K")
 @
@@
 Vertical bars indicate 95\\% confidence intervals.">>=
-createSFParamsGraph("L")
+createSFParamsGraph(factor="L")
 @
@@
 Vertical bars indicate 95\\% confidence intervals.">>=
-createSFParamsGraph("Q")
+createSFParamsGraph(factor="Q")
 @
@@
 Vertical bars indicate 95\\% confidence intervals.">>=
-createSFParamsGraph("X")
+createSFParamsGraph(factor="X")
 @
@@
 Vertical bars indicate 95\\% confidence intervals.">>=
-createSFParamsGraph("U")
+createSFParamsGraph(factor="U")
 @
 
-Figure \ref{fig:SF_GDP_Lattice_Graph} compares single-factor model predictions with historica data.
+Figure \ref{fig:SF_GDP_Lattice_Graph} compares single-factor model predictions with historical data.
 
@@
 Vertical bars indicate 95\\% confidence intervals.">>=
-createCDParamsGraph()
+createCDParamsGraph(energyType=NA)
 @
@@
 <<CDeGammaGraphsZA, fig.width=5, fig.height=3, fig.align="center", fig.cap="Cobb-Douglas with thermal energy ($q$) grid search for minimum $SSE$ for South Africa.", fig.pos="H">>=
-cdeGridGraph("ZA", "Q")
+cdeGridGraph(countryAbbrev="ZA", energyType="Q")
 @
@@
 Vertical bars indicate 95\\% confidence intervals.">>=
-createCDParamsGraph("Q")
+createCDParamsGraph(energyType="Q")
 @
@@
 Vertical bars indicate 95\\% confidence intervals.">>=
-createCDParamsGraph("X")
+createCDParamsGraph(energyType="X")
 @
@@
 Vertical bars indicate 95\\% confidence intervals.">>=
-createCDParamsGraph("U")
+createCDParamsGraph(energyType="U")
 @
@@
 
-print(cesData("US"))
+# print(cesData("US"))
+# print(cesCountryRow("US"))
+# print(cesCountryRowsForParamsGraph("US"))
+# print(cesParamsTableDF())
+
+# Testing null and missing
+
+testMissing <- function(param){
+  print(paste("missing(param) =", missing(param)))
+  print(paste("is.na(param) =", is.na(param)))
+  print(paste("is.null(param) =", is.null(param)))
+  print(paste("param =", param))
+}
+
+# testMissing()
+# testMissing(NA)
+# testMissing(NULL)
+# testMissing("")
 
@@
 <<CESq_Params_Graph, fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.pos="H", fig.cap="CES (with $q$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
-createCESParamsGraph("Q")
+createCESParamsGraph(energyType="Q")
 @
@@
 <<CESx_Params_Graph, fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.pos="H", fig.cap="CES (with $x$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
-createCESParamsGraph("X")
+createCESParamsGraph(energyType="X")
 @
@@
 <<CESu_Params_Graph, fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.pos="H", fig.cap="CES (with $u$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
-createCESParamsGraph("U")
+createCESParamsGraph(energyType="U")
 @
@@
 Vertical bars indicate 95\\% confidence intervals.">>=
-createLINEXParamsGraph("Q")
+createLINEXParamsGraph(energyType="Q")
 @
@@
 Vertical bars indicate 95\\% confidence intervals.">>=
-createLINEXParamsGraph("X")
+createLINEXParamsGraph(energyType="X")
 @
@@
 Vertical bars indicate 95\\% confidence intervals.">>=
-createLINEXParamsGraph("U")
+createLINEXParamsGraph(energyType="U")
 @
@@
 <<Print_Covariance_Tables, results='asis'>>=
-#I wish I could say this, but I get bogus "$US" strings appearing in the LaTeX output.
+#I wish I could say the following, but I get bogus "$US" strings appearing in the LaTeX output.
 #lapply(countryAbbrevs, printCovarTable)
-printCovarTable("US"); printCovarTable("UK"); printCovarTable("JP")
-printCovarTable("CN"); printCovarTable("ZA")
-printCovarTable("SA"); printCovarTable("IR")
-printCovarTable("TZ"); printCovarTable("ZM")
+printCovarTable(countryAbbrev="US"); printCovarTable(countryAbbrev="UK"); printCovarTable(countryAbbrev="JP")
+printCovarTable(countryAbbrev="CN"); printCovarTable(countryAbbrev="ZA")
+printCovarTable(countryAbbrev="SA"); printCovarTable(countryAbbrev="IR")
+printCovarTable(countryAbbrev="TZ"); printCovarTable(countryAbbrev="ZM")
 @
@@
 #lapply(factors, printSingleFactorParamsTable)
-printSFParamsTable("K"); printSFParamsTable("L")
-printSFParamsTable("Q"); printSFParamsTable("X"); printSFParamsTable("U")
+printSFParamsTable(factor="K"); printSFParamsTable(factor="L")
+printSFParamsTable(factor="Q"); printSFParamsTable(factor="X"); printSFParamsTable(factor="U")
 @
@@
 
-<<CD_Params_Table, results='asis'>>=
-printCDParamsTable()    #Without energy
-printCDParamsTable("Q"); printCDParamsTable("X"); printCDParamsTable("U") #With energy
+<<CD_Params_Table, results='asis', eval=TRUE>>=
+printCDParamsTable(energyType=NA)    #Without energy
+printCDParamsTable(energyType="Q"); printCDParamsTable(energyType="X"); printCDParamsTable(energyType="U") #With energy
 @
@@
 
-<<CES_Params_Table, results='asis'>>=
-printCESParamsTableA("Q"); printCESParamsTableB("Q")
-printCESParamsTableA("X"); printCESParamsTableB("X")
-printCESParamsTableA("U"); printCESParamsTableB("U")
+<<CES_Params_Table, results='asis', eval=TRUE>>=
+printCESParamsTableA(energyType=NA);  printCESParamsTableB(energyType=NA)
+printCESParamsTableA(energyType="Q"); printCESParamsTableB(energyType="Q")
+printCESParamsTableA(energyType="X"); printCESParamsTableB(energyType="X")
+printCESParamsTableA(energyType="U"); printCESParamsTableB(energyType="U")
 @
@@
 <<LINEX_Params_Table, results='asis'>>=
-printLINEXParamsTable("Q"); printLINEXParamsTable("X"); printLINEXParamsTable("U")
+printLINEXParamsTable(energyType="Q"); printLINEXParamsTable(energyType="X"); printLINEXParamsTable(energyType="U")
 @

### 2013-04-13 EconGrowth-R-Functions.Rnw
Removed many debugging print statements in the functions.

@@
 cobbDouglasData <- function(countryAbbrev, energyType){
-print("Inside cobbDouglasData")
-print(paste("energyType =", energyType))
   #First, check to see if we want useful work (U) AND one of the countries for which we don't have data.
@@
   }
-print("After if ! haveDataCD")
   # We have a combination of country and energy type for which we have data.
   modelCD <- cobbDouglasModel(countryAbbrev=countryAbbrev, energyType=energyType)
-print("After cobbDouglasModel")
   summaryCD <- summary(modelCD) # Gives the nls summary table.
@@
   if (is.na(energyType)){
-print("Inside if is.na(energyType)")
     #Cobb-Douglas without energy
@@
 cobbDouglasCountryRowsForParamsGraph <- function(countryAbbrev, energyType){
-print("Inside cobbDouglasCountryRowsForParamsGraph")
   #Create three rows, one for each parameter. Each row is a data.frame so that it is plottable!
   if (is.na(energyType)){
-print("Inside is.na(energyType)")
     valueRow <- "CD"
     dataCD <- cobbDouglasData(countryAbbrev=countryAbbrev, energyType=NA)
-print("After cobbDouglasData")
   } else {
@@
 createCDParamsGraph <- function(energyType){
-print("Inside createCDParamsGraph")
   if (is.na(energyType)){
@@
     dataTable <- do.call("rbind", lapply(countryAbbrevs, cobbDouglasCountryRowsForParamsGraph, energyType=NA))
-print("After lapply(cobbDouglasCountryRowsForParamsGraph")
     graph <- segplot(country ~ upperCI + lowerCI | parameter, 
@@
   predictions  <- cobbDouglasPredictionsColumn(energyType=NA)  #Predictions from CD without energy
-print("After cobbDouglasPredictionsColumn(energyType=NA)")
   predictionsQ <- cobbDouglasPredictionsColumn(energyType="Q") #Predictions from CD with Q
@@
   }
-print("Before xyplot")
   graph <- xyplot(iGDP+predGDP+predGDPQ+predGDPX+predGDPU ~ Year | Country, data=dataTable,
@@
                   )
-print("After xyplot")
   return(graph)
@@
 loadAndPrepDataForCES <- function(countryAbbrev, energyType){
-print(paste("Inside loadAndPrepDataForCES. energyType =", energyType))
   dataTable <- loadData(countryAbbrev)
@@
   if (is.na(energyType)){
-print("Inside is.na(energyType) in loadAndPrepDataForCES")
     # We're done. Don't have to deal with special issues with energyType.
@@
   }
-print("After is.na(energyType) block")
   # We have an energyType argument. Do some additional checking.
@@
 cesModel <- function(countryAbbrev, energyType){
-print(paste("Inside cesModel. energyType =", energyType))
   if (is.na(energyType)){
-print("Inside is.na(energyType)")
     return(cesModelNoEnergy(countryAbbrev))
@@
 cesPredictions <- function(countryAbbrev, energyType){
-print(paste("Inside cesPredictions. energyType =", energyType))
   # Can't make predictions for any of CN, ZA, SA, IR, TZ, or ZM if we're interested in U
@@
 cesPredictionsColumn <- function(energyType){
-print(paste("Inside cesPredictionsColumn. energyType =", energyType))
   out <- do.call("rbind", lapply(countryAbbrevs, cesPredictions, energyType=energyType))  
-print("After do.call(rbind, etc.)")
   if (is.na(energyType)){
@@
 createCESLatticeGraph <- function(countryAbbrev, textScaling=1.0, keyXLoc=defaultKeyXLoc, keyYLoc=defaultKeyYLoc){
-print("Inside createCESLatticeGraph.")
   dataTable <- loadData("All") #Grab the raw data
@@
   predictionsU <- cesPredictionsColumn(energyType="U") #Predictions from CES with U
-print("Made it to after collecting all the predictions.")
   #Now add the predictions columns to the data.
@@
 cesData <- function(countryAbbrev, energyType){
-print("Inside cesData")
-print(paste("is.na(energyType) =", is.na(energyType)))
   # Determine whether we want an energy term or not
@@
   }
-print(paste("wantEnergyTerm =", wantEnergyTerm))
   #First, check to see if we want useful work (U) AND one of the countries for which we don't have data.

### 2013-04-13 EconGrowth.Rnw
Removed many debugging print statements in the functions.

@@
 \item Heun: Add CI vs. params plots for all model types (the triangle plots from the seminar). Maybe as a lattice graph where each model type is a panel.
-\item{Heun: Convert to using NA everywhere for models without energy}
+\item{Heun: Convert the presentation to use energyType=NA for models without energy}
 \item Heun: Add CES production function fits
@@
 \item \st{Reese: Add text from Word verson of paper to the LaTeX version.}
+\item{\st{Heun: Convert to using NA everywhere for models without energy}}
 \item{\st{Heun: Investigate use of the micEcon package transLogEst function for CD parameter estimation. Doesn't look like it will work, because it doesn't do the CD form of interest to us.}}
-\item \st{Heun: Re-organize CES tables into (a) $\lambda$, $\delta$, $\sigma$ and (b) $\gamma$, $\delta_1$, $\sigma_1$}
+\item{\st{Heun: Re-organize CES tables into (a) $\lambda$, $\delta$, $\sigma$ and (b) $\gamma$, $\delta_1$, $\sigma_1$}}
 \item \st{Heun: Ask Martin if he can supply an ``Economics'' affiliation. Will probably make a stronger paper.}

### 2013-04-13 EconGrowth-R-Functions.Rnw
Fixed a small bug with the AIC tables.

@@
   # Cobb-Douglas without energy
-  cdModels <- lapply(countryAbbrevs, cobbDouglasModel)
+  cdModels <- lapply(countryAbbrevs, cobbDouglasModel, energyType=NA)
   aicCD <- data.frame(lapply(cdModels, AIC))

### 2013-04-13 EconGrowth.Rnw
Fixed a small bug with the AIC tables.

@@
 <<CES_Params_Graph, fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.pos="H", fig.cap="CES (without energy) model parameters.
-Vertical bars indicate 95\\% confidence intervals.", eval=TRUE>>=
+Vertical bars indicate 95\\% confidence intervals.">>=
 
@@
 
-<<CD_Params_Table, results='asis', eval=TRUE>>=
+<<CD_Params_Table, results='asis'>>=
 printCDParamsTable(energyType=NA)    #Without energy
@@
 
-<<CES_Params_Table, results='asis', eval=TRUE>>=
+<<CES_Params_Table, results='asis'>>=
 printCESParamsTableA(energyType=NA);  printCESParamsTableB(energyType=NA)

### 2013-04-13 EconGrowthSeminar.Rnw
Rearranged debates slide.
Nearly have the presentation also working after changing all of the code for signifying that you want a model without energy to use energyType=NA.

@@
     \item{Goal: predict economic output ($Y$) over time}
+    \item{All factors and outputs indexed to initial year: $y = Y/Y_0, e = E/E_0$, etc.}
+    \pause
+    \vspace{\baselineskip}
+
     \item{Set aside debates about growth and its measure}
-    \item{All factors and outputs indexed to initial year: $y = Y/Y_0, e = E/E_0$, etc.}
-    \vspace{\baselineskip}
-    \pause
-
+    \pause
     \item{Uncritical use of energy-augmented growth models for developed economies in the literature}
@@
 <<Coefs_US_CD>>=
-cdUS <- cobbDouglasData("US")
-cdqUS <- cobbDouglasData("US", "Q")
-cdxUS <- cobbDouglasData("US", "X")
-cduUS <- cobbDouglasData("US", "U")
+cdUS  <- cobbDouglasData(countryAbbrev="US", energyType=NA)
+cdqUS <- cobbDouglasData(countryAbbrev="US", energyType="Q")
+cdxUS <- cobbDouglasData(countryAbbrev="US", energyType="X")
+cduUS <- cobbDouglasData(countryAbbrev="US", energyType="U")
 @
@@
 <<Results_Graph_US_CD, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight>>=
-createCDLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+createCDLatticeGraph(countryAbbrev="US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
 @
@@
 <<Coefs_UK_CD>>=
-cdUK <- cobbDouglasData("UK")
-cdqUK <- cobbDouglasData("UK", "Q")
-cdxUK <- cobbDouglasData("UK", "X")
-cduUK <- cobbDouglasData("UK", "U")
+cdUK  <- cobbDouglasData(countryAbbrev="UK", energyType=NA)
+cdqUK <- cobbDouglasData(countryAbbrev="UK", energyType="Q")
+cdxUK <- cobbDouglasData(countryAbbrev="UK", energyType="X")
+cduUK <- cobbDouglasData(countryAbbrev="UK", energyType="U")
 @
@@
 <<Results_Graph_UK_CD, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight>>=
-createCDLatticeGraph("UK", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+createCDLatticeGraph(countryAbbrev="UK", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
 @
@@
 <<Coefs_ZA_CD>>=
-cdZA <- cobbDouglasData("ZA")
-cdqZA <- cobbDouglasData("ZA", "Q")
-cdxZA <- cobbDouglasData("ZA", "X")
+cdZA  <- cobbDouglasData(countryAbbrev="ZA", energyType=NA)
+cdqZA <- cobbDouglasData(countryAbbrev="ZA", energyType="Q")
+cdxZA <- cobbDouglasData(countryAbbrev="ZA", energyType="X")
 @
@@
 <<Results_Graph_ZA_CD, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-createCDLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+createCDLatticeGraph(countryAbbrev="ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
 @
@@
 <<Coefs_SA_CD>>=
-cdSA <- cobbDouglasData("SA")
-cdqSA <- cobbDouglasData("SA", "Q")
-cdxSA <- cobbDouglasData("SA", "X")
+cdSA  <- cobbDouglasData(countryAbbrev="SA", energyType=NA)
+cdqSA <- cobbDouglasData(countryAbbrev="SA", energyType="Q")
+cdxSA <- cobbDouglasData(countryAbbrev="SA", energyType="X")
 @
@@
 <<Results_Graph_SA_CD, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-createCDLatticeGraph("SA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+createCDLatticeGraph(countryAbbrev="SA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
 @
@@
 <<US_Partial_Residuals_Plot, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
-partialResidualPlot("US", "Q", textScaling=textScaleForGraphs)
+partialResidualPlot(countryAbbrev="US", energyType="Q", textScaling=textScaleForGraphs)
 @
@@
 <<UK_Partial_Residuals_Plot, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
-partialResidualPlot("UK", "Q", textScaling=textScaleForGraphs)
+partialResidualPlot(countryAbbrev="UK", energyType="Q", textScaling=textScaleForGraphs)
 @
@@
 <<CDq_Params_Graph, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
-createCDParamsGraph("Q")
+createCDParamsGraph(energyType="Q")
 @  
@@
 <<Coefs_US_CES>>=
-cesqUS <- cesData("US", "Q")
-cesxUS <- cesData("US", "X")
-cesuUS <- cesData("US", "U")
+cesqUS <- cesData(countryAbbrev="US", energyType="Q")
+cesxUS <- cesData(countryAbbrev="US", energyType="X")
+cesuUS <- cesData(countryAbbrev="US", energyType="U")
 @
@@
 <<Results_Graph_US_CES, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-createCESLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+createCESLatticeGraph(countryAbbrev="US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
 @
@@
 <<Coefs_UK_CES>>=
-cesqUK <- cesData("UK", "Q")
-cesxUK <- cesData("UK", "X")
-cesuUK <- cesData("UK", "U")
+cesqUK <- cesData(countryAbbrev="UK", energyType="Q")
+cesxUK <- cesData(countryAbbrev="UK", energyType="X")
+cesuUK <- cesData(countryAbbrev="UK", energyType="U")
 @
@@
 <<Results_Graph_UK_CES, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-createCESLatticeGraph("UK", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+createCESLatticeGraph(countryAbbrev="UK", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
 @
@@
 <<Coefs_ZA_CES>>=
-cesqZA <- cesData("ZA", "Q")
-cesxZA <- cesData("ZA", "X")
+cesqZA <- cesData(countryAbbrev="ZA", energyType="Q")
+cesxZA <- cesData(countryAbbrev="ZA", energyType="X")
 @
@@
 <<Results_Graph_ZA_CES, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-createCESLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+createCESLatticeGraph(countryAbbrev="ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
 @
@@
 <<Coefs_SA_CES>>=
-cesqSA <- cesData("SA", "Q")
-cesxSA <- cesData("SA", "X")
+cesqSA <- cesData(countryAbbrev="SA", energyType="Q")
+cesxSA <- cesData(countryAbbrev="SA", energyType="X")
 @
@@
 <<Results_Graph_SA_CES, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-createCESLatticeGraph("SA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+createCESLatticeGraph(countryAbbrev="SA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
 @
@@
 <<CESq_Params_Graph, fig.width=presentationGraph1ColWidth*1.8, fig.height=presentationGraph1RowHeight*1.8>>=
-createCESParamsGraph("Q")
+createCESParamsGraph(energyType="Q")
 @  
@@
 <<Coefs_US_LINEX>>=
-linexqUS <- linexData("US", "Q")
-linexxUS <- linexData("US", "X")
-linexuUS <- linexData("US", "U")
+linexqUS <- linexData(countryAbbrev="US", energyType="Q")
+linexxUS <- linexData(countryAbbrev="US", energyType="X")
+linexuUS <- linexData(countryAbbrev="US", energyType="U")
 @
@@
 <<Results_Graph_US_LINEX, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight>>=
-createLINEXLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+createLINEXLatticeGraph(countryAbbrev="US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
 @
@@
 <<Coefs_UK_LINEX>>=
-linexqUK <- linexData("UK", "Q")
-linexxUK <- linexData("UK", "X")
-linexuUK <- linexData("UK", "U")
+linexqUK <- linexData(countryAbbrev="UK", energyType="Q")
+linexxUK <- linexData(countryAbbrev="UK", energyType="X")
+linexuUK <- linexData(countryAbbrev="UK", energyType="U")
 @
@@
 <<Results_Graph_UK_LINEX, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight>>=
-createLINEXLatticeGraph("UK", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+createLINEXLatticeGraph(countryAbbrev="UK", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
 @
@@
 <<Coefs_ZA_LINEX>>=
-linexqZA <- linexData("ZA", "Q")
-linexxZA <- linexData("ZA", "X")
+linexqZA <- linexData(countryAbbrev="ZA", energyType="Q")
+linexxZA <- linexData(countryAbbrev="ZA", energyType="X")
 @
@@
 <<Results_Graph_ZA_LINEX, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight>>=
-createLINEXLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+createLINEXLatticeGraph(countryAbbrev="ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
 @
@@
 <<Coefs_SA_LINEX>>=
-linexqSA <- linexData("SA", "Q")
-linexxSA <- linexData("SA", "X")
+linexqSA <- linexData(countryAbbrev="SA", energyType="Q")
+linexxSA <- linexData(countryAbbrev="SA", energyType="X")
 @
@@
 <<Results_Graph_SA_LINEX, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight>>=
-createLINEXLatticeGraph("SA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+createLINEXLatticeGraph(countryAbbrev="SA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
 @
@@
 <<LINEXq_Params_Graph, fig.width=presentationGraph1ColWidth*1.8, fig.height=presentationGraph1RowHeight*1.8>>=
-createLINEXParamsGraph("Q")
+createLINEXParamsGraph(energyType="Q")
 @  
@@
 <<Historical_Data_JP, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-createHistoricalLatticeGraph("JP", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+createHistoricalLatticeGraph(countryAbbrev="JP", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
 @    
@@
 <<Historical_Data_CN, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-createHistoricalLatticeGraph("CN", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+createHistoricalLatticeGraph(countryAbbrev="CN", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
 @
@@
 <<Historical_Data_SA_Appendix, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-createHistoricalLatticeGraph("SA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+createHistoricalLatticeGraph(countryAbbrev="SA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
 @    
@@
 <<Historical_Data_IR, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-createHistoricalLatticeGraph("IR", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+createHistoricalLatticeGraph(countryAbbrev="IR", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
 @
@@
 <<Historical_Data_TZ, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-createHistoricalLatticeGraph("TZ", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+createHistoricalLatticeGraph(countryAbbrev="TZ", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
 @    
@@
 <<Historical_Data_ZM, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-createHistoricalLatticeGraph("ZM", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+createHistoricalLatticeGraph(countryAbbrev="ZM", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
 @
@@
 <<SF_Params_Graph_K, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
-createSFParamsGraph("K")
+createSFParamsGraph(factor="K")
 @  
@@
 <<SF_Params_Graph_L, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
-createSFParamsGraph("L")
+createSFParamsGraph(factor="L")
 @  
@@
 <<CDeGammaGraphsJP, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
-  cdeGridGraph("JP", "Q", textScaling=0.8)
+  cdeGridGraph(countryAbbrev="JP", energyType="Q", textScaling=0.8)
 @
@@
 <<CDeGammaGraphsCN, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
-  cdeGridGraph("CN", "Q", textScaling=0.8)
+  cdeGridGraph(countryAbbrev="CN", energyType="Q", textScaling=0.8)
 @
@@
 <<CDeGammaGraphsZA, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
-  cdeGridGraph("ZA", "Q", textScaling=0.8)
+  cdeGridGraph(countryAbbrev="ZA", energyType="Q", textScaling=0.8)
 @
@@
 <<CDeGammaGraphsSA, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
-  cdeGridGraph("SA", "Q", textScaling=0.8)
+  cdeGridGraph(countryAbbrev="SA", energyType="Q", textScaling=0.8)
 @
@@
 <<CDeGammaGraphsIR, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
-  cdeGridGraph("IR", "Q", textScaling=0.8)
+  cdeGridGraph(countryAbbrev="IR", energyType="Q", textScaling=0.8)
 @
@@
 <<CDeGammaGraphsTZ, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
-  cdeGridGraph("TZ", "Q", textScaling=0.8)
+  cdeGridGraph(countryAbbrev="TZ", energyType="Q", textScaling=0.8)
 @
@@
 <<CDeGammaGraphsZM, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
-  cdeGridGraph("ZM", "Q", textScaling=0.8)
+  cdeGridGraph(countryAbbrev="ZM", energyType="Q", textScaling=0.8)
 @
@@
 <<Coefs_JP_CD>>=
-cdJP <- cobbDouglasData("JP")
-cdqJP <- cobbDouglasData("JP", "Q")
-cdxJP <- cobbDouglasData("JP", "X")
-cduJP <- cobbDouglasData("JP", "U")
+cdJP  <- cobbDouglasData(countryAbbrev="JP", energyType=NA)
+cdqJP <- cobbDouglasData(countryAbbrev="JP", energyType="Q")
+cdxJP <- cobbDouglasData(countryAbbrev="JP", energyType="X")
+cduJP <- cobbDouglasData(countryAbbrev="JP", energyType="U")
 @
@@
 <<Results_Graph_JP_CD, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
-createCDLatticeGraph("JP", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
+createCDLatticeGraph(countryAbbrev="JP", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
 @

### 2013-04-13 EconGrowthSeminar.Rnw
Fixed one remaining bug with the presentation after switching to energyType=NA signifying that a model without energy is desired.

@@
 <<CD_Params_Graph, fig.width=presentationGraph1ColWidth*1.3, fig.height=presentationGraph1RowHeight*1.3>>=
-createCDParamsGraph()
+createCDParamsGraph(energyType=NA)
 @  

### 2013-04-14 EconGrowth-R-Functions.Rnw
Now including a parameters graph for CES without energy.

--- 2013-04-13 EconGrowth-R-Functions.Rnw
@@
 #   rownames(aicCESu) <- "CES$u$"
+  aicCES  <- data.frame(US=NA, UK=NA, JP=NA, CN=NA, ZA=NA, SA=NA, IR=NA, TZ=NA, ZM=NA)
+  rownames(aicCES) <- "CES"
+  aicCESq <- data.frame(US=NA, UK=NA, JP=NA, CN=NA, ZA=NA, SA=NA, IR=NA, TZ=NA, ZM=NA)
+  rownames(aicCESq) <- "CES$q$"
+  aicCESx <- data.frame(US=NA, UK=NA, JP=NA, CN=NA, ZA=NA, SA=NA, IR=NA, TZ=NA, ZM=NA)
+  rownames(aicCESx) <- "CES$x$"
+  aicCESu <- data.frame(US=NA, UK=NA, JP=NA, CN=NA, ZA=NA, SA=NA, IR=NA, TZ=NA, ZM=NA)
+  rownames(aicCESu) <- "CES$u$"
   ######################
@@
                aicCD, aicCDq, aicCDx, aicCDu, 
+               aicCES, aicCESq, aicCESx, aicCESu, 
                aicLINEXq, aicLINEXx, aicLINEXu) 
-#   out <- rbind(aicSFk, aicSFl, aicSFq, aicSFx, aicSFu, 
-#                aicCD, aicCDq, aicCDx, aicCDu, 
-#                aicCESq, aicCESx, aicCESu, 
-#                aicLINEXq, aicLINEXx, aicLINEXu) 
   # Create the xtable with caption and label

### 2013-04-14 EconGrowth.Rnw
Nearly have the presentation also working after changing all of the code for signifying that you want a model without energy to use energyType=NA.
Now including a parameters graph for CES without energy.

@@
 \item Heun: Add CI vs. params plots for all model types (the triangle plots from the seminar). Maybe as a lattice graph where each model type is a panel.
-\item{Heun: Convert the presentation to use energyType=NA for models without energy}
 \item Heun: Add CES production function fits
@@
       \item AIC rows in the AIC table (Code is in the createAICTable function, but it is not yet working)
-      \item Add a CES model without energy option (unspecified energyType parameters means CES without energy)
-        \begin{itemize}
-          \item{Extract CES without energy parameters from the ``without energy'' models and correctly name them: $\sigma \rightarrow \sigma_1$, $\rho \rightarrow \rho_1$, $\delta \rightarrow \delta_1$}
-          \item{Add CES without energy parameters to tables of results in the appendix}
-          \item{Create a CES without energy parameters graphs (with CIs) in the paper}
-          \item{\st{Add CES without energy lines to the CES lattice graph}}
-        \end{itemize}
       \item Revisit my assumptions for the CES production function (with energy) for each country.
@@
       \item \st{Convert $\rho$ variables in the CES production function to $\sigma$}
+      \item{\st{Add a CES model without energy option (energyType=NA means CES without energy)}}
+        \begin{itemize}
+          \item{\st{Create a CES without energy parameters graphs (with CIs) in the paper}}
+          \item{\st{Extract CES without energy parameters from the ``without energy'' models and correctly name them: $\sigma \rightarrow \sigma_1$, $\rho \rightarrow \rho_1$, $\delta \rightarrow \delta_1$}}
+          \item{\st{Add CES without energy parameters to tables of results in the appendix}}
+          \item{\st{Add CES without energy lines to the CES lattice graph}}
+        \end{itemize}
       \end{itemize}
@@
 \item \st{Reese: Add text from Word verson of paper to the LaTeX version.}
+\item{\st{Heun: Convert the presentation to use energyType=NA for models without energy}}
 \item{\st{Heun: Convert to using NA everywhere for models without energy}}
@@
 
+Figure \ref{fig:CES_Params_Graph} shows values and 95\% confidence intervals for the parameters for the CES model (without energy).
+
 <<CES_Params_Graph, fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.pos="H", fig.cap="CES (without energy) model parameters.
 Vertical bars indicate 95\\% confidence intervals.">>=
-
-# print(cesData("US"))
-# print(cesCountryRow("US"))
-# print(cesCountryRowsForParamsGraph("US"))
-# print(cesParamsTableDF())
-
-# Testing null and missing
-
-testMissing <- function(param){
-  print(paste("missing(param) =", missing(param)))
-  print(paste("is.na(param) =", is.na(param)))
-  print(paste("is.null(param) =", is.null(param)))
-  print(paste("param =", param))
-}
-
-# testMissing()
-# testMissing(NA)
-# testMissing(NULL)
-# testMissing("")
-
+createCESParamsGraph(energyType=NA)
 @
@@
 
-The following tables provide results for parameters in CES models.
+The following tables provide results for parameters in CES models with and without energy terms.
 

### 2013-04-14 EconGrowth-R-Functions.Rnw
Added the ability of CIvsParamPlot to use the CES model without energy and retrofitted the presentation to handle this correctly.

@@
 #      CDe: lambda, alpha, beta, or gamma
-#      CES: gamma, lambda, delta_1, sigma_1, delta, or sigma
+#      CES: gamma, lambda, delta_1, sigma_1, or delta
+#     CESe: gamma, lambda, delta_1, sigma_1, delta, or sigma
 #    LINEX: a_0 or c_t
@@
   else if (model == "CDe"){data <- cobbDouglasParamsTableWithEnergyDF(energyType)}
-  else if (model == "CES"){data <- cesParamsTableDF(energyType)}
+  else if (model == "CES"){data <- cesParamsTableDF(energyType=NA)}
+  else if (model == "CESe"){data <- cesParamsTableDF(energyType)}
   else if (model == "LINEX"){data <- linexParamsTableDF(energyType)}

### 2013-04-14 EconGrowth.Rnw
Added the ability of CIvsParamPlot to use the CES model without energy and retrofitted the presentation to handle this correctly.

@@
       \item Fix the problems with $\sigma_1$ and $\sigma$ values in the CES parameter tables in the appendix
-      \item AIC rows in the AIC table (Code is in the createAICTable function, but it is not yet working)
+      \item{AIC rows in the AIC table.
+Code is in the createAICTable function, but it is not yet working.
+Need to find a way to calculate AIC from the object that is returned from the cesEst function.}
       \item Revisit my assumptions for the CES production function (with energy) for each country.
@@
       \end{itemize}
-\item Heun: Deal with missing covariance numbers when columns have unequal length. Use the \texttt{subset} command?
+\item{Heun: Deal with missing covariance numbers when columns have unequal length. Use the \texttt{subset} command?}
+\item{Heun: Add data from 2011 and, possibly, 2012 to the models}
 \item Heun: Eliminate blanks in the coefficient tables for the 95\% CIs in the Cobb-Douglas with energy rows

### 2013-04-14 EconGrowthSeminar.Rnw
Added the ability of CIvsParamPlot to use the CES model without energy and retrofitted the presentation to handle this correctly.

@@
 <<CI_delta_vs_delta_Graph_Q, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5>>=
-CIvsParamPlot(model="CES", param="delta", energyType="Q")
+CIvsParamPlot(model="CESe", param="delta", energyType="Q")
 @
@@
 <<CI_delta_vs_delta_Graph_X, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5>>=
-CIvsParamPlot(model="CES", param="delta", energyType="X")
+CIvsParamPlot(model="CESe", param="delta", energyType="X")
 @
@@
 <<CI_delta_vs_delta_Graph_U, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5>>=
-CIvsParamPlot(model="CES", param="delta", energyType="U")
+CIvsParamPlot(model="CESe", param="delta", energyType="U")
 @
@@
 <<CI_sigma_vs_sigma_Graph, fig.width=presentationGraph1ColWidth*1.5, fig.height=presentationGraph1RowHeight*1.5>>=
-CIvsParamPlot(model="CES", param="sigma", energyType="Q")
+CIvsParamPlot(model="CESe", param="sigma", energyType="Q")
 @

### 2013-04-14 EconGrowth-R-Functions.Rnw
Added the option to include CES models in partialResidualPlots.

@@
 # a double Y axis. The first Y axis has alpha, beta, and gamma vs. gamma. The second Y axis
-# has SSE vs. gamma.
+# has SSE_y vs. gamma.
 # countryAbbrev tells which country you want to view
@@
 # textScaling tells how you want to scale the text on the axes and other places.
-# This 
 ##
@@
   return(graph)
-}
-
-#################
-# Creates a plot with y residuals vs. energy (e). The y residuals are from a Cobb-Douglas model without energy.
-# The energy term on the x axis is whatever type is specified in the calling funciton
-partialResidualPlot <- function(countryAbbrev, energyType, textScaling=1.0){
-  # Get the model
-  cdModel <- cdModel(countryAbbrev)
-  # Get the residuals
-  cdResid <- resid(cdModel)
-  cdResid <- data.frame(cdResid)
-  cdResid <- padRows(countryAbbrev=countryAbbrev, df=cdResid)
-  # Load data
-  data <- loadData(countryAbbrev)
-  data <- cbind(data, cdResid)
-  data <- replaceColName(dataTable=data, factor=energyType, newName="iEToFit")
-  plot <- xyplot(cdResid ~ iEToFit, data=data,
-#                 type=c("p",:smooth"),
-                 type=c("p"),
-                 col="black",
-                 scales=list(cex=scaleTextSize*textScaling, #controls text size on scales.
-                             tck=scaleTickSize), #controls tick mark length. < 0 for inside the graph.
-                 xlab=list(label=paste("$", tolower(energyType), "$", sep=""), cex=textScaling),
-                 ylab=list(label="$y$ residuals (CD without energy)", cex=textScaling)
-                 )
-  return(plot)  
 }
@@
 @
+
+<<PartialResidualPlots, eval=TRUE>>=
+#################
+# Creates a plot with y residuals vs. energy (e). The y residuals are from the specified modelType without energy.
+# modelType: one of "CD" or "CES"
+# energyType: one of "Q", "X", or "U"
+# The energy term on the x axis is whatever type is specified in the calling funciton
+# 
+partialResidualPlot <- function(modelType, countryAbbrev, energyType, textScaling=1.0){
+  if (modelType == "CD"){
+    model <- cdModel(countryAbbrev)  
+  } else if (modelType == "CES"){
+    model <- cesModelNoEnergy(countryAbbrev)
+  } else {
+    print(paste("Unknown modelType:", modelType, "in partialResidualPlot."))
+  }
+  # Get the model
+  # Get the residuals
+  resid <- resid(model)
+  resid <- data.frame(resid)
+  resid <- padRows(countryAbbrev=countryAbbrev, df=resid)
+  # Load data
+  data <- loadData(countryAbbrev)
+  data <- cbind(data, resid)
+  data <- replaceColName(dataTable=data, factor=energyType, newName="iEToFit")
+  plot <- xyplot(resid ~ iEToFit, data=data,
+                 type=c("p"),
+                 col="black",
+                 scales=list(cex=scaleTextSize*textScaling, #controls text size on scales.
+                             tck=scaleTickSize), #controls tick mark length. < 0 for inside the graph.
+                 xlab=list(label=paste("$", tolower(energyType), "$", sep=""), cex=textScaling),
+                 ylab=list(label="$y$ residuals (CD without energy)", cex=textScaling)
+                 )
+  return(plot)  
+}
+
+partialResidualLattice <- function(modelType, energyType){
+
+}
+@

### 2013-04-14 EconGrowth.Rnw
Added the option to include CES models in partialResidualPlots.

@@
 
-\section{Cobb-Douglas Models With Energy (CDe)}
+\section{Cobb-Douglas Models With Energy (CD$e$)}
 
@@
 
+<<CDPartialResidualsQ, fig.width=5, fig.height=3, fig.align="center", fig.cap="Cobb-Douglas partial residuals plot for thermal energy ($q$).", fig.pos="H", eval=TRUE>>=
+partialResidualPlot(modelType="CES", countryAbbrev="US", energyType="Q")
+@
+
 The Cobb-Douglas with energy parameter estimation process is challenging.
@@
 cdeGridGraph(countryAbbrev="ZA", energyType="Q")
+@
+
+<<CDGridSearchGraphs, fig.width=5, fig.height=3, fig.align='center', fig.cap="Cobb-Douglas with thermal energy ($q$) grid search for minimum $SSEy$.", fig.pos="H">>=
+cdeGridGraph(countryAbbrev=NA, energyType="Q")
 @
@@
 
-\subsection{CES without energy}
+\subsection{CES without energy (CES)}
 
@@
 
-\subsection{CES with $Q$}
+\subsection{CES with $Q$ (CES$q$)}
 
@@
 
-\subsection{CES with $X$}
+\subsection{CES with $X$ (CES$x$)}
 
@@
 
-\subsection{CES with $U$}
+\subsection{CES with $U$ (CES$u$)}
 

### 2013-04-14 EconGrowthSeminar.Rnw
Added the option to include CES models in partialResidualPlots.

@@
 \begin{frame}{Beneficial to Include Energy?}  %----------------------------
-<<US_Partial_Residuals_Plot, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
-partialResidualPlot(countryAbbrev="US", energyType="Q", textScaling=textScaleForGraphs)
+<<US_Partial_Residuals_Plot, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight, eval=TRUE>>=
+partialResidualPlot(modelType="CD", countryAbbrev="US", energyType="Q", textScaling=textScaleForGraphs)
 @
@@
 <<UK_Partial_Residuals_Plot, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
-partialResidualPlot(countryAbbrev="UK", energyType="Q", textScaling=textScaleForGraphs)
+partialResidualPlot(modelType="CD", countryAbbrev="UK", energyType="Q", textScaling=textScaleForGraphs)
 @

### 2013-04-14 EconGrowth-R-Functions.Rnw
Now creating lattice partial residual plots for all countries. Need to format them a bit better, but they are working at least.

@@
 <<PartialResidualPlots, eval=TRUE>>=
+#############################
+# Creates a data.frame containing raw data and residuals for given arguments.
+# modelType: one of "CD" or "CES"
+# countryAbbrev: the country of interest to you
+# energyType: one of "Q", "X", or "U"
+##
+calcResiduals <- function(countryAbbrev, modelType, energyType){
+  # Get the model
+  if (modelType == "CD"){
+    model <- cdModel(countryAbbrev)  
+  } else if (modelType == "CES"){
+    model <- cesModelNoEnergy(countryAbbrev)
+  } else {
+    print(paste("Unknown modelType:", modelType, "in partialResidualPlot."))
+    return(NULL)
+  }
+  # Get the residuals
+  resid <- resid(model)
+  resid <- data.frame(resid)
+  resid <- padRows(countryAbbrev=countryAbbrev, df=resid)
+  # Load data
+  data <- loadData(countryAbbrev)
+  data <- cbind(data, resid)
+  # Replace name of column we want with the name "iEToFit"
+  data <- replaceColName(dataTable=data, factor=energyType, newName="iEToFit")
+  return(data)
+}
+
 #################
@@
 partialResidualPlot <- function(modelType, countryAbbrev, energyType, textScaling=1.0){
-  if (modelType == "CD"){
-    model <- cdModel(countryAbbrev)  
-  } else if (modelType == "CES"){
-    model <- cesModelNoEnergy(countryAbbrev)
-  } else {
-    print(paste("Unknown modelType:", modelType, "in partialResidualPlot."))
-  }
-  # Get the model
-  # Get the residuals
-  resid <- resid(model)
-  resid <- data.frame(resid)
-  resid <- padRows(countryAbbrev=countryAbbrev, df=resid)
-  # Load data
-  data <- loadData(countryAbbrev)
-  data <- cbind(data, resid)
-  data <- replaceColName(dataTable=data, factor=energyType, newName="iEToFit")
+  data <- calcResiduals(modelType=modelType, countryAbbrev=countryAbbrev, energyType=energyType)
   plot <- xyplot(resid ~ iEToFit, data=data,
@@
 
-partialResidualLattice <- function(modelType, energyType){
-
-}
+partialResidualLattice <- function(modelType, energyType, textScaling=1.0){
+  data <- do.call("rbind", lapply(countryAbbrevs, calcResiduals, modelType=modelType, energyType=energyType))
+print(data)
+  plot <- xyplot(resid ~ iEToFit | Country, data=data,
+                 type=c("p"),
+                 col="black",
+                 scales=list(cex=scaleTextSize*textScaling, #controls text size on scales.
+                             tck=scaleTickSize), #controls tick mark length. < 0 for inside the graph.
+                 xlab=list(label=paste("$", tolower(energyType), "$", sep=""), cex=textScaling),
+                 ylab=list(label="$y$ residuals (CD without energy)", cex=textScaling)
+                 )
+  return(plot)
+}
+
 @

### 2013-04-14 EconGrowth.Rnw
Now creating lattice partial residual plots for all countries. Need to format them a bit better, but they are working at least.

@@
 <<CDPartialResidualsQ, fig.width=5, fig.height=3, fig.align="center", fig.cap="Cobb-Douglas partial residuals plot for thermal energy ($q$).", fig.pos="H", eval=TRUE>>=
-partialResidualPlot(modelType="CES", countryAbbrev="US", energyType="Q")
+partialResidualPlot(modelType="CD", countryAbbrev="US", energyType="Q")
+partialResidualLattice(modelType="CD", energyType="Q")
 @

### 2013-04-14 EconGrowth-R-Functions.Rnw
Now including partial residual plots for all countries, all energy types as lattice graphs in the paper.

@@
 # modelType: one of "CD" or "CES"
-# energyType: one of "Q", "X", or "U"
-# The energy term on the x axis is whatever type is specified in the calling funciton
-# 
-partialResidualPlot <- function(modelType, countryAbbrev, energyType, textScaling=1.0){
+# energyType: one of "Q", "X", or "U" to serve as the ordinate of the graph
+# countryAbbrev: set to NA (the default) if you want a lattice graph with all countries shown. Set to one of
+#                US, UK, JP, CN, ZA, SA, IR, TZ, ZM for an individual graph.
+## 
+createPartialResidualPlot <- function(modelType, energyType, countryAbbrev=NA, textScaling=1.0){
+  xLabelString <- paste("$", tolower(energyType), "$", sep="")
+  yLabelString <- paste("$y$ residuals (", modelType, " without energy)", sep="")
+  if (! is.na(countryAbbrev)){
+    # An individual graph for a single country is desired.
     data <- calcResiduals(modelType=modelType, countryAbbrev=countryAbbrev, energyType=energyType)
@@
                                tck=scaleTickSize), #controls tick mark length. < 0 for inside the graph.
-                 xlab=list(label=paste("$", tolower(energyType), "$", sep=""), cex=textScaling),
-                 ylab=list(label="$y$ residuals (CD without energy)", cex=textScaling)
-                 )
+                   xlab=list(label=xLabelString, cex=textScaling),
+                   ylab=list(label=yLabelString, cex=textScaling)
+                   )
+  } else {
+    # Lattice graph will all countries is desired.
+    factorLevels <- countryNamesAlph # We want all countries shown
+    layout <- ninePanelLayoutSpec
+    indexCond <- list(countryOrderForGraphs) # We want all countries in this order
+    data <- do.call("rbind", lapply(countryAbbrevsAlph, calcResiduals, modelType=modelType, energyType=energyType))
+    plot <- xyplot(resid ~ iEToFit | Country, data=data,
+                   type = c("p"),
+                   index.cond = indexCond, #orders the panels.
+                   layout = layout,
+                   strip = strip.custom(factor.levels=factorLevels, 
+                                        bg="transparent", # Sets background transparent to match the graph itself.
+                                        par.strip.text=list(cex=textScaling) # Scales text in the strip.
+                                        ),
+                   as.table = TRUE, #indexing of panels starts in upper left and goes across rows.
+                   col = "black",
+                   scales = list(cex=scaleTextSize*textScaling, #controls text size on scales.
+                                 tck=scaleTickSize), #controls tick mark length. < 0 for inside the graph.
+                   xlab = list(label=xLabelString, cex=textScaling),
+                   ylab = list(label=yLabelString, cex=textScaling)
+                   )
+  }
   return(plot)
@@
 
-partialResidualLattice <- function(modelType, energyType, textScaling=1.0){
-  data <- do.call("rbind", lapply(countryAbbrevs, calcResiduals, modelType=modelType, energyType=energyType))
-print(data)
-  plot <- xyplot(resid ~ iEToFit | Country, data=data,
-                 type=c("p"),
-                 col="black",
-                 scales=list(cex=scaleTextSize*textScaling, #controls text size on scales.
-                             tck=scaleTickSize), #controls tick mark length. < 0 for inside the graph.
-                 xlab=list(label=paste("$", tolower(energyType), "$", sep=""), cex=textScaling),
-                 ylab=list(label="$y$ residuals (CD without energy)", cex=textScaling)
-                 )
-  return(plot)
-}
-
 @

### 2013-04-14 EconGrowth.Rnw
Now including partial residual plots for all countries, all energy types as lattice graphs in the paper.

--- 2013-04-14 EconGrowth.Rnw
@@
 
-<<CDPartialResidualsQ, fig.width=5, fig.height=3, fig.align="center", fig.cap="Cobb-Douglas partial residuals plot for thermal energy ($q$).", fig.pos="H", eval=TRUE>>=
-partialResidualPlot(modelType="CES", countryAbbrev="US", energyType="Q")
+<<CDPartialResidualsQ, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="Cobb-Douglas partial residuals plot for thermal energy ($q$).", fig.pos="H", eval=TRUE>>=
+createPartialResidualPlot(modelType="CD", energyType="Q", countryAbbrev=NA)
+@
+
+<<CESPartialResidualsQ, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="CES partial residuals plot for thermal energy ($q$).", fig.pos="H", eval=TRUE>>=
+createPartialResidualPlot(modelType="CES", energyType="Q", countryAbbrev=NA)
+@
+
+<<CDPartialResidualsX, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="Cobb-Douglas partial residuals plot for exergy ($x$).", fig.pos="H", eval=TRUE>>=
+createPartialResidualPlot(modelType="CD", energyType="X", countryAbbrev=NA)
+@
+
+<<CESPartialResidualsX, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="CES partial residuals plot for exergy ($x$).", fig.pos="H", eval=TRUE>>=
+createPartialResidualPlot(modelType="CES", energyType="X", countryAbbrev=NA)
+@
+
+<<CDPartialResidualsU, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="Cobb-Douglas partial residuals plot for useful work ($u$).", fig.pos="H", eval=TRUE>>=
+createPartialResidualPlot(modelType="CD", energyType="U", countryAbbrev=NA)
+@
+
+<<CESPartialResidualsU, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="CES partial residuals plot for useful work ($u$).", fig.pos="H", eval=TRUE>>=
+createPartialResidualPlot(modelType="CES", energyType="U", countryAbbrev=NA)
 @

### 2013-04-14 EconGrowthSeminar.Rnw
Now including partial residual plots for all countries, all energy types as lattice graphs in the paper.

--- 2013-04-14 EconGrowthSeminar.Rnw
@@
 <<US_Partial_Residuals_Plot, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
-partialResidualPlot(countryAbbrev="US", energyType="Q", textScaling=textScaleForGraphs)
+createPartialResidualPlot(modelType="CD", countryAbbrev="US", energyType="Q", textScaling=textScaleForGraphs)
 @
@@
 <<UK_Partial_Residuals_Plot, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
-partialResidualPlot(countryAbbrev="UK", energyType="Q", textScaling=textScaleForGraphs)
+createPartialResidualPlot(modelType="CD", countryAbbrev="UK", energyType="Q", textScaling=textScaleForGraphs)
 @

### 2013-04-14 EconGrowth.Rnw
Moved the partial residual plots to a reasonable place in the paper.

@@
 
+To qualitatively assess whether augmenting the Cobb-Douglas model with energy will be beneficial, we create partial residual plots as shown in Figures \ref{fig:CDPartialResidualsQ} - \ref{fig:CDPartialResidualsU} below.
+If a monotonic trend is observed on the graphs, we expect that energy augmentation will be beneficial.
+However, no strong monotonic tends are observed for any country, suggesting that energy augmentation of the Cobb-Douglas production function will not be beneficial.
+
+<<CDPartialResidualsQ, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="Cobb-Douglas partial residuals plot for thermal energy ($q$).", fig.pos="H", eval=TRUE>>=
+createPartialResidualPlot(modelType="CD", energyType="Q", countryAbbrev=NA)
+@
+
+<<CDPartialResidualsX, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="Cobb-Douglas partial residuals plot for exergy ($x$).", fig.pos="H", eval=TRUE>>=
+createPartialResidualPlot(modelType="CD", energyType="X", countryAbbrev=NA)
+@
+
+<<CDPartialResidualsU, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="Cobb-Douglas partial residuals plot for useful work ($u$).", fig.pos="H", eval=TRUE>>=
+createPartialResidualPlot(modelType="CD", energyType="U", countryAbbrev=NA)
+@
+
 \section{Cobb-Douglas Models With Energy (CD$e$)}
@@
 \subsection{Cobb-Douglas with thermal energy ($q$)}
-
-<<CDPartialResidualsQ, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="Cobb-Douglas partial residuals plot for thermal energy ($q$).", fig.pos="H", eval=TRUE>>=
-createPartialResidualPlot(modelType="CD", energyType="Q", countryAbbrev=NA)
-@
-
-<<CESPartialResidualsQ, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="CES partial residuals plot for thermal energy ($q$).", fig.pos="H", eval=TRUE>>=
-createPartialResidualPlot(modelType="CES", energyType="Q", countryAbbrev=NA)
-@
-
-<<CDPartialResidualsX, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="Cobb-Douglas partial residuals plot for exergy ($x$).", fig.pos="H", eval=TRUE>>=
-createPartialResidualPlot(modelType="CD", energyType="X", countryAbbrev=NA)
-@
-
-<<CESPartialResidualsX, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="CES partial residuals plot for exergy ($x$).", fig.pos="H", eval=TRUE>>=
-createPartialResidualPlot(modelType="CES", energyType="X", countryAbbrev=NA)
-@
-
-<<CDPartialResidualsU, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="Cobb-Douglas partial residuals plot for useful work ($u$).", fig.pos="H", eval=TRUE>>=
-createPartialResidualPlot(modelType="CD", energyType="U", countryAbbrev=NA)
-@
-
-<<CESPartialResidualsU, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="CES partial residuals plot for useful work ($u$).", fig.pos="H", eval=TRUE>>=
-createPartialResidualPlot(modelType="CES", energyType="U", countryAbbrev=NA)
-@
 
@@
 createCESParamsGraph(energyType=NA)
+@
+
+Similar to the analysis of the Cobb-Douglas model above, we make partial residual plots for the CES model in Figures \ref{fig:CESPartialResidualsQ} - \ref{fig:CESPartialResidualsU} below.
+Again, no strong monotonic trend is observed, suggesting the energy-augmentation of the CES model will not significantly improve the model.
+
+<<CESPartialResidualsQ, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="CES partial residuals plot for thermal energy ($q$).", fig.pos="H", eval=TRUE>>=
+createPartialResidualPlot(modelType="CES", energyType="Q", countryAbbrev=NA)
+@
+
+<<CESPartialResidualsX, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="CES partial residuals plot for exergy ($x$).", fig.pos="H", eval=TRUE>>=
+createPartialResidualPlot(modelType="CES", energyType="X", countryAbbrev=NA)
+@
+
+<<CESPartialResidualsU, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="CES partial residuals plot for useful work ($u$).", fig.pos="H", eval=TRUE>>=
+createPartialResidualPlot(modelType="CES", energyType="U", countryAbbrev=NA)
 @

### 2013-04-14 EconGrowth-R-Functions.Rnw
Eliminated the alternating (left-right, top-bot) axis labels on lattice graphs.

@@
                               tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
+                              alternating=FALSE, # eliminates left-right, top-bot alternating of axes
                               x=list(at=timeTics),
@@
                                  tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
+                                 alternating=FALSE, # eliminates left-right, top-bot alternating of axes
                                  x=list(at=c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0)), #location for x tics
@@
                    scales = list(cex=scaleTextSize*textScaling, #controls text size on scales.
-                                 tck=scaleTickSize), #controls tick mark length. < 0 for inside the graph.
+                                 tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
+                                 alternating=FALSE), # prevents left/right, top/bot alternating
                    xlab = list(label=xLabelString, cex=textScaling),

### 2013-04-14 EconGrowth.Rnw
Removed code for a graph which isn't yet implemented in the paper.
Eliminated the alternating (left-right, top-bot) axis labels on lattice graphs.

--- 2013-04-14 EconGrowth.Rnw
@@
       \item Write up the decisions about parameter estimation for the CES production function fits
+      \item Revisit my assumptions for the CES production function (with energy) for each country.
       \item Fix the problems with $\sigma_1$ and $\sigma$ values in the CES parameter tables in the appendix
-      \item{AIC rows in the AIC table.
+      \item{Add CES rows to the AIC table.
 Code is in the createAICTable function, but it is not yet working.
-Need to find a way to calculate AIC from the object that is returned from the cesEst function.}
-      \item Revisit my assumptions for the CES production function (with energy) for each country.
+Need to find a way to calculate AIC for the object that is returned from the cesEst function.}
       \item \st{Create parameter graphs for each country}
@@
       \begin{itemize}
-      \item Zambia, upper bound on $c_t$
+      \item ZM: upper bound on $c_t$
       \end{itemize}
 \item Heun: Fix warnings of the form ``Warning:  step factor 0.000488281 reduced below ’minFactor’ of 0.000976562'' in the code that generates the Cobb-Douglas with energy fits.
-\item Heun: x-axis labels only on bottom for 9-panel lattice graphs
 \item Heun: adjust y axis limits on $a_0$ and $c_t$ parameter graphs for the LINEX model AFTER we finish debugging the LINEX models.
@@
 \item \st{Reese: Add text from Word verson of paper to the LaTeX version.}
+\item{\st{Heun: x-axis labels only on bottom for 9-panel lattice graphs}}
 \item{\st{Heun: Convert the presentation to use energyType=NA for models without energy}}
@@
 
+To qualitatively assess whether augmenting the Cobb-Douglas model with energy will be beneficial, we create partial residual plots as shown in Figures \ref{fig:CDPartialResidualsQ} - \ref{fig:CDPartialResidualsU} below.
+If a monotonic trend is observed on the graphs, we expect that energy augmentation will be beneficial.
+However, no strong monotonic tends are observed for any country, suggesting that energy augmentation of the Cobb-Douglas production function will not be beneficial.
+
+<<CDPartialResidualsQ, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="Cobb-Douglas partial residuals plot for thermal energy ($q$).", fig.pos="H">>=
+createPartialResidualPlot(modelType="CD", energyType="Q", countryAbbrev=NA)
+@
+
+<<CDPartialResidualsX, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="Cobb-Douglas partial residuals plot for exergy ($x$).", fig.pos="H">>=
+createPartialResidualPlot(modelType="CD", energyType="X", countryAbbrev=NA)
+@
+
+<<CDPartialResidualsU, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="Cobb-Douglas partial residuals plot for useful work ($u$).", fig.pos="H">>=
+createPartialResidualPlot(modelType="CD", energyType="U", countryAbbrev=NA)
+@
+
 \section{Cobb-Douglas Models With Energy (CD$e$)}
@@
 \subsection{Cobb-Douglas with thermal energy ($q$)}
-
-<<CDPartialResidualsQ, fig.width=5, fig.height=3, fig.align="center", fig.cap="Cobb-Douglas partial residuals plot for thermal energy ($q$).", fig.pos="H", eval=TRUE>>=
-partialResidualPlot(modelType="CD", countryAbbrev="US", energyType="Q")
-partialResidualLattice(modelType="CD", energyType="Q")
-@
 
@@
 
-<<CDGridSearchGraphs, fig.width=5, fig.height=3, fig.align='center', fig.cap="Cobb-Douglas with thermal energy ($q$) grid search for minimum $SSEy$.", fig.pos="H">>=
-cdeGridGraph(countryAbbrev=NA, energyType="Q")
-@
-
 Figure \ref{fig:CDq_Params_Graph} shows values and 95\% confidence intervals for the parameters for the Cobb-Douglas model (with $q$).
@@
 createCESParamsGraph(energyType=NA)
+@
+
+Similar to the analysis of the Cobb-Douglas model above, we make partial residual plots for the CES model in Figures \ref{fig:CESPartialResidualsQ} - \ref{fig:CESPartialResidualsU} below.
+Again, no strong monotonic trend is observed, suggesting the energy-augmentation of the CES model will not significantly improve the model.
+
+<<CESPartialResidualsQ, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="CES partial residuals plot for thermal energy ($q$).", fig.pos="H">>=
+createPartialResidualPlot(modelType="CES", energyType="Q", countryAbbrev=NA)
+@
+
+<<CESPartialResidualsX, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="CES partial residuals plot for exergy ($x$).", fig.pos="H">>=
+createPartialResidualPlot(modelType="CES", energyType="X", countryAbbrev=NA)
+@
+
+<<CESPartialResidualsU, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="CES partial residuals plot for useful work ($u$).", fig.pos="H">>=
+createPartialResidualPlot(modelType="CES", energyType="U", countryAbbrev=NA)
 @
@@
 
-<<AIC_Table, results='asis', label="AIC_Table", eval=TRUE>>=
+<<AIC_Table, results='asis', label="AIC_Table">>=
 print(createAICTable(), 

### 2013-04-15 EconGrowth-R-Functions.Rnw
Cleaning up the gamma grid graph.

@@
   data <- transform(data, beta = 1.0 - alpha - gamma)
+  # Now make a column that has the country abbreviation
+  nRowsData <- nrow(data) #Gets number of rows in data set
+  dfOfCountryAbbrevs <- as.data.frame(matrix(countryAbbrev, ncol=1, nrow=nRowsData))
+  colnames(dfOfCountryAbbrevs) <- "Country"
+  data <- cbind(data, dfOfCountryAbbrevs) 
   return(data)
@@
   # Combine the two graphs into a double-Y graph.
+  doubleYGraph <- doubleYScale(abgGraph, sseGraph, add.ylab2=TRUE, use.style=FALSE)
+  return(doubleYGraph)
+}
+
+#######################
+# Creates a single graph or a multi-panel lattice plot showing grid search over gamma for Cobb-Douglas models with 
+# the given quantification for energy.
+# countryAbbrev: one of "US", "UK", "JP", "CN", "ZA", "SA", "IR", "TZ", or "ZM". Set to NA if you want a lattice
+# plot for all countries
+# energyType: one of "Q", "X", or "U"
+##
+cdeGridLattice <- function(energyType, countryAbbrev=NA, keyXLoc = defaultKeyXLoc, keyYLoc = defaultKeyYLoc, textScaling = 1.0){
+  gammaGrid <- seq(0.0, 0.95, by=0.05) # Establishes the grid in which we're interested.
+  if (is.na(countryAbbrev)){
+    # All countries are wanted.
+    data <- do.call("rbind", lapply(countryAbbrevsAlph, cdeGridData, energyType=energyType, gammaGrid=gammaGrid))
+  } else {
+    # Only one specific country is wanted.
+    data <- cdeGridData(countryAbbrev=countryAbbrev, energyType=energyType, gammaGrid=gammaGrid)
+  }
+  alphaBetaGammaRange <- c(0.0, 1.0)
+  alphaBetaGammaTics <- c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0)
+  lambdaRange <- c(0.0, 0.004)
+  lambdaTics <- c(0.0, 0.001, 0.002, 0.003, 0.004)
+  sseRange <- c(0.0, 0.1)
+  sseTics <- c(0.0, 0.02, 0.04, 0.06, 0.08, 0.10)
+  # Create a lattice graph that shows the four variables (lambda, alpha, beta, and SSE) vs. gamma.
+  graphType <- "b" #b is for both symbls and lines. Necessary so that the key looks right.
+  lineTypes <- c(2, 1, 3, 0) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
+  lineWidths <- c(1, 3, 1, 0) #line widths. 0 means no line.
+  symbols <- c(NA, NA, NA, 1)
+  colors <- c("black", "black", "black", "black") #line and symbol colors
+  abgGraph <- xyplot(alpha+beta+gamma ~ gamma | Country, data=data,
+                     type=graphType,
+                     lty = lineTypes, lwd = lineWidths, col = colors, #Controls line parameters
+                     pch = symbols, col.symbol = colors, #Controls symbol parameters
+                     key=list(text=list(c("$\\alpha$", "$\\beta$", "$\\gamma$", "$SSE_y$")),
+                              type=graphType,
+                              cex=keyTextSize * textScaling, #controls size of text in the key
+                              lines=list(lty=lineTypes, lwd=lineWidths), #controls line types
+                              pch=symbols, col=colors, #controls symbol (plot characters) types
+                              columns=keyColumns, x=keyXLoc, y=keyYLoc), #controls columns and position of the key
+                     scales=list(cex=scaleTextSize * textScaling, #controls text size on scales.
+                                 tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
+                                 alternating=FALSE, # eliminates left-right, top-bot alternating of axes
+                                 x=list(at=c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0)), #location for x tics
+                                 y=list(at=c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0))  #location for y tics
+                     ), 
+                     ylim=c(0.0, 1.5), #y axis limits
+                     #axis labels and scaling
+                     xlab=list(label="$\\gamma$", cex=textScaling), 
+                     ylab=list(label="$\\alpha$, $\\beta$, $\\gamma$", cex=textScaling)
+                     )
+  sseGraph <- xyplot(SSE ~ gamma | Country, data=data,
+                     pch = c(1), col.symbol = c("black"), #Controls symbol parameters
+                     scales=list(cex=scaleTextSize * textScaling, #controls text size on scales.
+                                 tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
+                                 y=list(at=sseTics) #location for y tics                                          
+                                 ), 
+                     ylim=sseRange,
+                     xlab=list(label="$\\gamma$", cex=textScaling), #Not used by the double-Y graph.
+                     ylab=list(label="$SSE$", cex=textScaling)
+                     )
   doubleYGraph <- doubleYScale(abgGraph, sseGraph, add.ylab2=TRUE, use.style=FALSE)

### 2013-04-15 EconGrowth.Rnw
Cleaning up the gamma grid graph.

@@
 \item Heun: Add 9-panel lattice graph for min($SSE_y$) graphs for the CD model.
-\item Heun: Add CI vs. params plots for all model types (the triangle plots from the seminar). Maybe as a lattice graph where each model type is a panel.
+\item{Heun: Add CI vs.
+params plots for all model types (the triangle plots from the seminar).
+Maybe as a lattice graph where each model type is a panel.
+But, wait until we know if we have symmetric confidence intervals before doing this.
+These graphs won't work if we have asymmetric CIs.}
 \item Heun: Add CES production function fits
@@
 
-<<CDeGammaGraphsZA, fig.width=5, fig.height=3, fig.align="center", fig.cap="Cobb-Douglas with thermal energy ($q$) grid search for minimum $SSE$ for South Africa.", fig.pos="H">>=
+<<CDeGammaGraphsZA, fig.width=5, fig.height=3, fig.align="center", fig.cap="Cobb-Douglas with thermal energy ($q$) grid search for minimum $SSE$ for South Africa.", fig.pos="H", eval=TRUE>>=
 cdeGridGraph(countryAbbrev="ZA", energyType="Q")
+@
+
+<<CDeGridLattice, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Grid search over $\\gamma$ for Cobb-Douglas with energy model.", fig.pos="H", eval=TRUE>>=
+cdeGridLattice(energyType="Q")
 @

### 2013-04-15 EconGrowth.Rnw
Updated to-do list on the paper.

@@
 \begin{itemize}
-\item Heun: Add 9-panel lattice graph for min($SSE_y$) graphs for the CD model.
+\item{Heun: Rearrange the panels on the CD gamma grid search graph}
+\item{Heun: Change the strip to transparent on the CD gamma grid search graph}
+\item{Heun: Get full country names into the CD gamma grid search graph}
+\item{Heun: Fix weirdnesses with China on the CD gamma grid search graph}
+\item{Heun: Change the presentation to use the cdeGridLattice function instead of cdeGridGraph}
+\item{Heun: Remove cdeGridGraph function}
 \item{Heun: Add CI vs.
@@
 \item \st{Reese: Add text from Word verson of paper to the LaTeX version.}
+\item{\st{Heun: Add 9-panel lattice graph for min($SSE_y$) graphs for the CD model}}
 \item{\st{Heun: x-axis labels only on bottom for 9-panel lattice graphs}}
@@
 
-<<CDeGammaGraphsZA, fig.width=5, fig.height=3, fig.align="center", fig.cap="Cobb-Douglas with thermal energy ($q$) grid search for minimum $SSE$ for South Africa.", fig.pos="H", eval=TRUE>>=
-cdeGridGraph(countryAbbrev="ZA", energyType="Q")
-@
-
 <<CDeGridLattice, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Grid search over $\\gamma$ for Cobb-Douglas with energy model.", fig.pos="H", eval=TRUE>>=

### 2013-04-15 EconGrowth-R-Functions.Rnw
Updated to-do list on the paper.
CD gamma grid search panels now in correct order. Strip is now transparent. Full country names are included. Unified the "Graph" and "Lattice" versions of the cdeGrid functions. Presentation is now using the lattice version of the function. Eliminated the "Graph" version of the function.

@@
 
-#############################
-# This function creates a graph for Cobb-Douglas with energy functions. The graph has 
-# a double Y axis. The first Y axis has alpha, beta, and gamma vs. gamma. The second Y axis
-# has SSE_y vs. gamma.
-# countryAbbrev tells which country you want to view
-# energyType tells which type of energy you want
-# textScaling tells how you want to scale the text on the axes and other places.
-##
-cdeGridGraph <- function(countryAbbrev, energyType, keyXLoc = defaultKeyXLoc, keyYLoc = defaultKeyYLoc, textScaling = 1.0){
-  gammaGrid <- seq(0.0, 0.95, by=0.05)
-  data <- cdeGridData(countryAbbrev, energyType, gammaGrid)
-  # Now melt the data so that it is in the correct form.
-  data_molten <- melt(data, id="gamma")
-  alphaBetaGammaRange <- c(0.0, 1.0)
-  alphaBetaGammaTics <- c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0)
-  lambdaRange <- c(0.0, 0.004)
-  lambdaTics <- c(0.0, 0.001, 0.002, 0.003, 0.004)
-  sseRange <- c(0.0, 0.08)
-  sseTics <- c(0.0, 0.02, 0.04, 0.06, 0.08)
-  # Create a lattice graph that shows the four variables (lambda, alpha, beta, and SSE) vs. gamma.
-  graphType <- "b" #b is for both symbls and lines. Necessary so that the key looks right.
-  lineTypes <- c(2, 1, 3, 0) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
-  lineWidths <- c(1, 3, 1, 0) #line widths. 0 means no line.
-  symbols <- c(NA, NA, NA, 1)
-  colors <- c("black", "black", "black", "black") #line and symbol colors
-  abgGraph <- xyplot(alpha+beta+gamma ~ gamma, data=data,
-                     type=graphType,
-                     lty = lineTypes, lwd = lineWidths, col = colors, #Controls line parameters
-                     pch = symbols, col.symbol = colors, #Controls symbol parameters
-                     key=list(text=list(c("$\\alpha$", "$\\beta$", "$\\gamma$", "$SSE_y$")),
-                              type=graphType,
-                              cex=keyTextSize * textScaling, #controls size of text in the key
-                              lines=list(lty=lineTypes, lwd=lineWidths), #controls line types
-                              pch=symbols, col=colors, #controls symbol (plot characters) types
-                              columns=keyColumns, x=keyXLoc, y=keyYLoc), #controls columns and position of the key
-                     scales=list(cex=scaleTextSize * textScaling, #controls text size on scales.
-                                 tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
-                                 alternating=FALSE, # eliminates left-right, top-bot alternating of axes
-                                 x=list(at=c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0)), #location for x tics
-                                 y=list(at=c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0))  #location for y tics
-                     ), 
-                     ylim=c(0.0, 1.5), #y axis limits
-                     #axis labels and scaling
-                     xlab=list(label="$\\gamma$", cex=textScaling), 
-                     ylab=list(label="$\\alpha$, $\\beta$, $\\gamma$", cex=textScaling)
-  )
-  sseGraph <- xyplot(SSE ~ gamma, data=data,
-                     pch = c(1), col.symbol = c("black"), #Controls symbol parameters
-                     scales=list(cex=scaleTextSize * textScaling, #controls text size on scales.
-                                 tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
-                                 y=list(at=c(0.0, 0.02, 0.04, 0.06, 0.08)) #location for y tics                                          
-                                 ), 
-                     ylim=c(0.0, 0.08),
-                     xlab=list(label="$\\gamma$", cex=textScaling), #Not used by the double-Y graph.
-                     ylab=list(label="$SSE$", cex=textScaling)
-                     )
-  # Combine the two graphs into a double-Y graph.
-  doubleYGraph <- doubleYScale(abgGraph, sseGraph, add.ylab2=TRUE, use.style=FALSE)
-  return(doubleYGraph)
-}
-
 #######################
@@
     data <- do.call("rbind", lapply(countryAbbrevsAlph, cdeGridData, energyType=energyType, gammaGrid=gammaGrid))
+    # Establish some formatting parameters
+    factorLevels <- countryNamesAlph # We want all countries shown
+    indexCond <- list(countryOrderForGraphs) # We want all countries in this order
+    layout <- ninePanelLayoutSpec # Show all countries
+    stripSpec <- strip.custom(factor.levels=factorLevels, # Sets text for factor levels
+                              bg="transparent", # Sets background transparent to match the graph itself.
+                              par.strip.text=list(cex=textScaling) # Scales text in the strip.
+                              )
   } else {
@@
     data <- cdeGridData(countryAbbrev=countryAbbrev, energyType=energyType, gammaGrid=gammaGrid)
-  }
-  alphaBetaGammaRange <- c(0.0, 1.0)
+    # Select the correct y limits
+    index <- which(countryAbbrevsAlph %in% countryAbbrev)
+    # The following lines use [index:index] as a convenient way of subsetting.
+    # This has the added benefit of maintaining the correct classes for things.
+    factorLevels <- countryNamesAlph[index:index]     # Only show the country we have chosen.
+    indexCond <- list(c(1))                           # We want only one country.
+    layout <- onePanelLayoutSpec                      # We want only one panel in the graph.
+    stripSpec <- FALSE # No strip needed.
+  }
+  alphaBetaGammaRange <- c(-0.1, 1.5)
   alphaBetaGammaTics <- c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0)
@@
   sseRange <- c(0.0, 0.1)
-  sseTics <- c(0.0, 0.02, 0.04, 0.06, 0.08, 0.10)
+  sseTics <- c(0.02, 0.04, 0.06, 0.08, 0.10)
+  gammaRange <- c(-0.1, 1.1)
+  gammaTics <- c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0)
   # Create a lattice graph that shows the four variables (lambda, alpha, beta, and SSE) vs. gamma.
@@
                      pch = symbols, col.symbol = colors, #Controls symbol parameters
+                     index.cond = indexCond, #orders the panels.
+                     layout = layout,                     
+                     strip = stripSpec,
+                     as.table = TRUE, #indexing of panels starts in upper left and goes across rows.
                      key=list(text=list(c("$\\alpha$", "$\\beta$", "$\\gamma$", "$SSE_y$")),
@@
                                  alternating=FALSE, # eliminates left-right, top-bot alternating of axes
-                                 x=list(at=c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0)), #location for x tics
-                                 y=list(at=c(0.0, 0.2, 0.4, 0.6, 0.8, 1.0))  #location for y tics
+                                 x=list(at=gammaTics), #location for x tics
+                                 y=list(at=alphaBetaGammaTics)  #location for y tics
                      ), 
-                     ylim=c(0.0, 1.5), #y axis limits
+                     xlim=gammaRange, #x axis limits
+                     ylim=alphaBetaGammaRange, #y axis limits
                      #axis labels and scaling
@@
                      pch = c(1), col.symbol = c("black"), #Controls symbol parameters
+                     index.cond = indexCond, #orders the panels.
+                     layout = layout,                     
+                     strip = stripSpec,
+                     as.table = TRUE, #indexing of panels starts in upper left and goes across rows.
                      scales=list(cex=scaleTextSize * textScaling, #controls text size on scales.
@@
                                  ), 
+                     xlim=gammaRange,
                      ylim=sseRange,

### 2013-04-15 EconGrowthSeminar.Rnw
CD gamma grid search panels now in correct order. Strip is now transparent. Full country names are included. Unified the "Graph" and "Lattice" versions of the cdeGrid functions. Presentation is now using the lattice version of the function. Eliminated the "Graph" version of the function.

@@
 \begin{frame}{Grid Search Over $\gamma$}{US Cobb-Douglas with $q$} %----------------------------
-<<CDeGammaGraphsUS, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
-  cdeGridGraph("US", "Q", textScaling=0.8)
+<<CDeGammaGraphsUS, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight, eval=TRUE>>=
+  cdeGridLattice(countryAbbrev="US", energyType="Q", textScaling=0.8)
 @
@@
 \begin{frame}{Grid Search Over $\gamma$}{UK Cobb-Douglas with $q$} %----------------------------
-<<CDeGammaGraphsUK, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
-  cdeGridGraph("UK", "Q", textScaling=0.8)
+<<CDeGammaGraphsUK, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight, eval=TRUE>>=
+  cdeGridLattice(countryAbbrev="UK", energyType="Q", textScaling=0.8)
 @

### 2013-04-15 EconGrowth.Rnw
Adjusted to-do list.

@@
 \begin{itemize}
-\item{Heun: Rearrange the panels on the CD gamma grid search graph}
-\item{Heun: Change the strip to transparent on the CD gamma grid search graph}
-\item{Heun: Get full country names into the CD gamma grid search graph}
 \item{Heun: Fix weirdnesses with China on the CD gamma grid search graph}
-\item{Heun: Change the presentation to use the cdeGridLattice function instead of cdeGridGraph}
-\item{Heun: Remove cdeGridGraph function}
 \item{Heun: Add CI vs.
@@
 \item \st{Reese: Add text from Word verson of paper to the LaTeX version.}
+\item{\st{Heun: Rearrange the panels on the CD gamma grid search graph}}
+\item{\st{Heun: Change the strip to transparent on the CD gamma grid search graph}}
+\item{\st{Heun: Get full country names into the CD gamma grid search graph}}
+\item{\st{Heun: Change the presentation to use the cdeGridLattice function instead of cdeGridGraph}}
+\item{\st{Heun: Remove cdeGridGraph function}}
 \item{\st{Heun: Add 9-panel lattice graph for min($SSE_y$) graphs for the CD model}}
@@
 
-<<Historical_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="Historical data.
-Indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$).">>=
+<<Historical_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="Historical data: Indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$).">>=
 createHistoricalLatticeGraph()

### 2013-04-16 EconGrowth-R-Functions.Rnw
In the process of building 9-panel graphs for CI vs. param plots.

@@
 countryAbbrevsU <- c(US="US", UK="UK", JP="JP") #Only these countries have useful work data
+countryAbbrevsAlphU <- c(JP="JP", UK="UK", US="US")
 countryNamesAlph <- c(CN="China", IR="Iran", JP="Japan", SA="Saudi Arabia", TZ="Tanzania", UK="United Kingdom", US="USA", ZA="South Africa", ZM="Zambia") #In alphabetical order.
@@
 <<CIvsParam_Graph, eval=TRUE>>=
+############################
+# Creates a data.frame that contains the following information:
+# row name: 2-letter country abbreviation
+# 1st col: parameter value. The name of this column is the name of the parameter, "sigma", "delta", etc. 
+#          as appropriate for the model generating the data
+# 2nd col: width of the confidence interval. The name of this column is "CI"
+# 3rd col: an identifier for parameter, model, and (factor or energy type). 
+#          For example, if you want the sigma parameter for the CES model with Q, you would get "sigmaCESeq".
+#          If you want the m parameter for the single-factor mdoel with k, you would get "mSFk".
+#          If you want the alpha parameter for the Cobb-Douglas model without energy, you would get "alphaCD".
+#          The name of the column is "factor"
+##
+CIvsParamDF <- function(model, param, energyType=NA, factor=NA){
+  # Get the data from the requested model
+  if (model == "SF"){data <- singleFactorParamsDF(factor)} 
+  else if (model == "CD"){data <- cobbDouglasParamsTableNoEnergyDF()}
+  else if (model == "CDe"){data <- cobbDouglasParamsTableWithEnergyDF(energyType)}
+  else if (model == "CES"){data <- cesParamsTableDF(energyType=NA)}
+  else if (model == "CESe"){data <- cesParamsTableDF(energyType)}
+  else if (model == "LINEX"){data <- linexParamsTableDF(energyType)}
+  # Now get the data for the parameter requested
+  # Also, set limits on the x and y axes if needed
+  if (param == "lambda"){
+    x <- subset(data, select=lambda) # The column of lambdas
+    y <- subset(data, select=upperCI_lambda) - subset(data, select=lowerCI_lambda) # A column of CI values
+  } else if (param == "m"){
+    x <- subset(data, select=m) # The column of m's
+    colnames(x) <- "m"
+    y <- subset(data, select=upperCI_m) - subset(data, select=lowerCI_m) # A column of CI values
+  } else if (param == "alpha"){
+    x <- subset(data, select=alpha) # The column of alphas
+    y <- subset(data, select=upperCI_alpha) - subset(data, select=lowerCI_alpha) # A column of CI values
+  } else if (param == "beta"){
+    x <- subset(data, select=beta) # The column of betas
+    y <- subset(data, select=upperCI_beta) - subset(data, select=lowerCI_beta) # A column of CI values
+  } else if (param == "gamma"){
+    x <- subset(data, select=gamma) # The column of gammas
+    y <- subset(data, select=upperCI_gamma) - subset(data, select=lowerCI_gamma) # A column of CI values
+  } else if (param == "delta_1"){
+    x <- subset(data, select=delta_1) # The column of delta_1's
+    y <- subset(data, select=upperCI_delta_1) - subset(data, select=lowerCI_delta_1) # A column of CI values
+  } else if (param == "sigma_1"){
+    x <- subset(data, select=sigma_1) # The column of sigma_1's
+    y <- subset(data, select=upperCI_sigma_1) - subset(data, select=lowerCI_sigma_1) # A column of CI values
+  } else if (param == "delta"){
+    x <- subset(data, select=delta) # The column of deltas
+    y <- subset(data, select=upperCI_delta) - subset(data, select=lowerCI_delta) # A column of CI values
+  } else if (param == "sigma"){
+    x <- subset(data, select=sigma) # The column of sigmas
+    y <- subset(data, select=upperCI_sigma) - subset(data, select=lowerCI_sigma) # A column of CI values
+  } else if (param == "a_0"){
+    x <- subset(data, select=a_0) # The column of a_0's
+    y <- subset(data, select=upperCI_a_0) - subset(data, select=lowerCI_a_0) # A column of CI values
+  } else if (param == "c_t"){
+    x <- subset(data, select=c_t) # The column of c_t's
+    y <- subset(data, select=upperCI_c_t) - subset(data, select=lowerCI_c_t) # A column of CI values
+  }
+  colnames(y) <- "CI"
+  # Create the factor string. We are guaranteed to have a value for the param and model arguments.
+  # However, we might have NA for either energyType or factor. But, we will not have values for both 
+  # energyType and factor at the same time! So, we can simply paste everything together here and 
+  # obtain the desired result.
+  if (is.na(factor)){
+    factorString <- paste(param, model, energyType, sep="")
+  } else if (is.na(energyType)){
+    factorString <- paste(param, model, factor, sep="")
+  } else {
+    print("Neither energyType nor factor were NA in CIvsParamDF. But one should be.")
+    return(NULL)
+  }
+  nRows <- nrow(x)
+  factor <- as.data.frame(matrix(factorString, ncol=1, nrow=nRows))
+  colnames(factor) <- "factor"
+  data <- cbind(x, y, factor)
+  return(data)
+}
+
 #######################
@@
   # Get the data from the requested model
-  if (model == "SF"){data <- singleFactorParamsDF(factor)} 
-  else if (model == "CD"){data <- cobbDouglasParamsTableNoEnergyDF()}
-  else if (model == "CDe"){data <- cobbDouglasParamsTableWithEnergyDF(energyType)}
-  else if (model == "CES"){data <- cesParamsTableDF(energyType=NA)}
-  else if (model == "CESe"){data <- cesParamsTableDF(energyType)}
-  else if (model == "LINEX"){data <- linexParamsTableDF(energyType)}
-  # Now get the data for the parameter requested
+  data <- CIvsParamDF(model=model, param=param, energyType=energyType, factor=factor)
+#   if (model == "SF"){data <- singleFactorParamsDF(factor)} 
+#   else if (model == "CD"){data <- cobbDouglasParamsTableNoEnergyDF()}
+#   else if (model == "CDe"){data <- cobbDouglasParamsTableWithEnergyDF(energyType)}
+#   else if (model == "CES"){data <- cesParamsTableDF(energyType=NA)}
+#   else if (model == "CESe"){data <- cesParamsTableDF(energyType)}
+#   else if (model == "LINEX"){data <- linexParamsTableDF(energyType)}
+#   # Now get the data for the parameter requested
   # Also, set limits on the x and y axes if needed
   if (param == "lambda"){
-    x <- subset(data, select=lambda) # The column of lambdas
+#     x <- subset(data, select=lambda) # The column of lambdas
     xLabel <- "$\\lambda$ [1/year]"
-    y <- subset(data, select=upperCI_lambda) - subset(data, select=lowerCI_lambda) # A column of CI values
+#     y <- subset(data, select=upperCI_lambda) - subset(data, select=lowerCI_lambda) # A column of CI values
     xLimits <- c(0.0, 0.1); atX=c(0.0, 0.05, 0.1)
@@
   } else if (param == "m"){
-    x <- subset(data, select=m) # The column of ms
-    colnames(x) <- "m"
+#     x <- subset(data, select=m) # The column of ms
+#     colnames(x) <- "m"
     if (factor == "K"){xLabel <- "$\\alpha$"}
@@
     else if ((factor == "Q") || (factor == "X") || (factor == "U")){xLabel <- "$\\gamma$"}
-    y <- subset(data, select=upperCI_m) - subset(data, select=lowerCI_m) # A column of CI values
+#     y <- subset(data, select=upperCI_m) - subset(data, select=lowerCI_m) # A column of CI values
     xLimits <- c(-0.1, 1.5); atX <- c(0.0, 0.5, 1.0, 1.5)
@@
   } else if (param == "alpha"){
-    x <- subset(data, select=alpha) # The column of alphas
+#     x <- subset(data, select=alpha) # The column of alphas
     xLabel <- "$\\alpha$"
-    y <- subset(data, select=upperCI_alpha) - subset(data, select=lowerCI_alpha) # A column of CI values
+#     y <- subset(data, select=upperCI_alpha) - subset(data, select=lowerCI_alpha) # A column of CI values
     xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
@@
   } else if (param == "beta"){
-    x <- subset(data, select=beta) # The column of betas
+#     x <- subset(data, select=beta) # The column of betas
     xLabel <- "$\\beta$"
-    y <- subset(data, select=upperCI_beta) - subset(data, select=lowerCI_beta) # A column of CI values
+#     y <- subset(data, select=upperCI_beta) - subset(data, select=lowerCI_beta) # A column of CI values
     xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
@@
   } else if (param == "gamma"){
-    x <- subset(data, select=gamma) # The column of gammas
+#     x <- subset(data, select=gamma) # The column of gammas
     xLabel <- "$\\gamma$"
-    y <- subset(data, select=upperCI_gamma) - subset(data, select=lowerCI_gamma) # A column of CI values
+#     y <- subset(data, select=upperCI_gamma) - subset(data, select=lowerCI_gamma) # A column of CI values
     xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
@@
   } else if (param == "delta_1"){
-    x <- subset(data, select=delta_1) # The column of delta_1
+#     x <- subset(data, select=delta_1) # The column of delta_1
     xLabel <- "$\\delta_1$"
-    y <- subset(data, select=upperCI_delta_1) - subset(data, select=lowerCI_delta_1) # A column of CI values
+#     y <- subset(data, select=upperCI_delta_1) - subset(data, select=lowerCI_delta_1) # A column of CI values
     xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
@@
   } else if (param == "sigma_1"){
-    x <- subset(data, select=sigma_1) # The column of sigma_1
+#     x <- subset(data, select=sigma_1) # The column of sigma_1
     xLabel <- "$\\sigma_1$"
-    y <- subset(data, select=upperCI_sigma_1) - subset(data, select=lowerCI_sigma_1) # A column of CI values
+#     y <- subset(data, select=upperCI_sigma_1) - subset(data, select=lowerCI_sigma_1) # A column of CI values
     xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
@@
   } else if (param == "delta"){
-    x <- subset(data, select=delta) # The column of delta
+#     x <- subset(data, select=delta) # The column of delta
     xLabel <- "$\\delta$"
-    y <- subset(data, select=upperCI_delta) - subset(data, select=lowerCI_delta) # A column of CI values
+#     y <- subset(data, select=upperCI_delta) - subset(data, select=lowerCI_delta) # A column of CI values
     xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
@@
   } else if (param == "sigma"){
-    x <- subset(data, select=sigma) # The column of sigma
+#     x <- subset(data, select=sigma) # The column of sigma
     xLabel <- "$\\sigma$"
-    y <- subset(data, select=upperCI_sigma) - subset(data, select=lowerCI_sigma) # A column of CI values
+#     y <- subset(data, select=upperCI_sigma) - subset(data, select=lowerCI_sigma) # A column of CI values
     xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
@@
   } else if (param == "a_0"){
-    x <- subset(data, select=a_0) # The column of a_0s
+#     x <- subset(data, select=a_0) # The column of a_0s
     xLabel <- "$a_0$"
-    y <- subset(data, select=upperCI_a_0) - subset(data, select=lowerCI_a_0) # A column of CI values
+#     y <- subset(data, select=upperCI_a_0) - subset(data, select=lowerCI_a_0) # A column of CI values
     xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
@@
   } else if (param == "c_t"){
-    x <- subset(data, select=c_t) # The column of c_ts
+#     x <- subset(data, select=c_t) # The column of c_ts
     xLabel <- "$c_t$"
-    y <- subset(data, select=upperCI_c_t) - subset(data, select=lowerCI_c_t) # A column of CI values
+#     y <- subset(data, select=upperCI_c_t) - subset(data, select=lowerCI_c_t) # A column of CI values
     xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
@@
   }
-  colnames(y) <- "CI"
+#   colnames(y) <- "CI"
   yLabel <- paste("Width of 95\\% CI on", xLabel)
-  data <- cbind(x, y)
-  plot <- xyplot(data[ , 2] ~ data[ , 1], # data[ , 1] contains the the parameter; data[ , 2] contains the CIs
+#   data <- cbind(x, y)
+  # Need to use the indices in the following code, because the column labels will be different for each type
+  # of model. In other words, if we're doing CESe with Q and plotting sigma, the data.frame will come 
+  # back with column names of "sigma" and "CI" on the first and second column, respectively. 
+  # plot <-  xyplot(data$CI ~ data$sigma, ...)
+  # would break if we, instead, wanted CESe with Q and plotting delta.
+  # So, instead, we use the column indices to pick off the correct variables.
+  plot <- xyplot(data[ , 2] ~ data[ , 1], # data[ , 1] contains the the parameter; data[ , 2] contains the CI width
                  xlab=list(label=xLabel),

### 2013-04-16 EconGrowth.Rnw
In the process of building 9-panel graphs for CI vs. param plots.

@@
 These graphs won't work if we have asymmetric CIs.}
+\item{Heun: Eliminate non-developed countries from partial residual plots.}
 \item Heun: Add CES production function fits
@@
 
+<<Test, eval=TRUE>>=
+CIvsParamDF(model="CESe", param="sigma", energyType="Q")
+CIvsParamPlot(model="CESe", param="sigma", energyType="Q")
+
+@
+
 \subsection{Background}
@@
 
-<<CDeGridLattice, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Grid search over $\\gamma$ for Cobb-Douglas with energy model.", fig.pos="H", eval=TRUE>>=
+<<CDeGridLattice, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Grid search over $\\gamma$ for Cobb-Douglas with energy model.", fig.pos="H">>=
 cdeGridLattice(energyType="Q")

### 2013-04-16 EconGrowthSeminar.Rnw
In the process of building 9-panel graphs for CI vs. param plots.

@@
 <<CDeGammaGraphsJP, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
-  cdeGridGraph(countryAbbrev="JP", energyType="Q", textScaling=0.8)
+  cdeGridLattice(countryAbbrev="JP", energyType="Q", textScaling=0.8)
 @
@@
 <<CDeGammaGraphsCN, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
-  cdeGridGraph(countryAbbrev="CN", energyType="Q", textScaling=0.8)
+  cdeGridLattice(countryAbbrev="CN", energyType="Q", textScaling=0.8)
 @
@@
 <<CDeGammaGraphsZA, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
-  cdeGridGraph(countryAbbrev="ZA", energyType="Q", textScaling=0.8)
+  cdeGridLattice(countryAbbrev="ZA", energyType="Q", textScaling=0.8)
 @
@@
 <<CDeGammaGraphsSA, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
-  cdeGridGraph(countryAbbrev="SA", energyType="Q", textScaling=0.8)
+  cdeGridLattice(countryAbbrev="SA", energyType="Q", textScaling=0.8)
 @
@@
 <<CDeGammaGraphsIR, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
-  cdeGridGraph(countryAbbrev="IR", energyType="Q", textScaling=0.8)
+  cdeGridLattice(countryAbbrev="IR", energyType="Q", textScaling=0.8)
 @
@@
 <<CDeGammaGraphsTZ, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
-  cdeGridGraph(countryAbbrev="TZ", energyType="Q", textScaling=0.8)
+  cdeGridLattice(countryAbbrev="TZ", energyType="Q", textScaling=0.8)
 @
@@
 <<CDeGammaGraphsZM, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
-  cdeGridGraph(countryAbbrev="ZM", energyType="Q", textScaling=0.8)
+  cdeGridLattice(countryAbbrev="ZM", energyType="Q", textScaling=0.8)
 @

### 2013-04-16 EconGrowth-R-Functions.Rnw
Removed a lot of code from CIvsParamPlot, because a new method called CIvsParamDF is now being used to generate the data.frame that contains the data.

@@
   data <- CIvsParamDF(model=model, param=param, energyType=energyType, factor=factor)
-#   if (model == "SF"){data <- singleFactorParamsDF(factor)} 
-#   else if (model == "CD"){data <- cobbDouglasParamsTableNoEnergyDF()}
-#   else if (model == "CDe"){data <- cobbDouglasParamsTableWithEnergyDF(energyType)}
-#   else if (model == "CES"){data <- cesParamsTableDF(energyType=NA)}
-#   else if (model == "CESe"){data <- cesParamsTableDF(energyType)}
-#   else if (model == "LINEX"){data <- linexParamsTableDF(energyType)}
-#   # Now get the data for the parameter requested
   # Also, set limits on the x and y axes if needed
   if (param == "lambda"){
-#     x <- subset(data, select=lambda) # The column of lambdas
     xLabel <- "$\\lambda$ [1/year]"
-#     y <- subset(data, select=upperCI_lambda) - subset(data, select=lowerCI_lambda) # A column of CI values
     xLimits <- c(0.0, 0.1); atX=c(0.0, 0.05, 0.1)
@@
   } else if (param == "m"){
-#     x <- subset(data, select=m) # The column of ms
-#     colnames(x) <- "m"
     if (factor == "K"){xLabel <- "$\\alpha$"}
@@
     else if ((factor == "Q") || (factor == "X") || (factor == "U")){xLabel <- "$\\gamma$"}
-#     y <- subset(data, select=upperCI_m) - subset(data, select=lowerCI_m) # A column of CI values
     xLimits <- c(-0.1, 1.5); atX <- c(0.0, 0.5, 1.0, 1.5)
@@
   } else if (param == "alpha"){
-#     x <- subset(data, select=alpha) # The column of alphas
     xLabel <- "$\\alpha$"
-#     y <- subset(data, select=upperCI_alpha) - subset(data, select=lowerCI_alpha) # A column of CI values
     xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
@@
   } else if (param == "beta"){
-#     x <- subset(data, select=beta) # The column of betas
     xLabel <- "$\\beta$"
-#     y <- subset(data, select=upperCI_beta) - subset(data, select=lowerCI_beta) # A column of CI values
     xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
@@
   } else if (param == "gamma"){
-#     x <- subset(data, select=gamma) # The column of gammas
     xLabel <- "$\\gamma$"
-#     y <- subset(data, select=upperCI_gamma) - subset(data, select=lowerCI_gamma) # A column of CI values
     xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
@@
   } else if (param == "delta_1"){
-#     x <- subset(data, select=delta_1) # The column of delta_1
     xLabel <- "$\\delta_1$"
-#     y <- subset(data, select=upperCI_delta_1) - subset(data, select=lowerCI_delta_1) # A column of CI values
     xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
@@
   } else if (param == "sigma_1"){
-#     x <- subset(data, select=sigma_1) # The column of sigma_1
     xLabel <- "$\\sigma_1$"
-#     y <- subset(data, select=upperCI_sigma_1) - subset(data, select=lowerCI_sigma_1) # A column of CI values
     xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
@@
   } else if (param == "delta"){
-#     x <- subset(data, select=delta) # The column of delta
     xLabel <- "$\\delta$"
-#     y <- subset(data, select=upperCI_delta) - subset(data, select=lowerCI_delta) # A column of CI values
     xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
@@
   } else if (param == "sigma"){
-#     x <- subset(data, select=sigma) # The column of sigma
     xLabel <- "$\\sigma$"
-#     y <- subset(data, select=upperCI_sigma) - subset(data, select=lowerCI_sigma) # A column of CI values
     xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
@@
   } else if (param == "a_0"){
-#     x <- subset(data, select=a_0) # The column of a_0s
     xLabel <- "$a_0$"
-#     y <- subset(data, select=upperCI_a_0) - subset(data, select=lowerCI_a_0) # A column of CI values
     xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
@@
   } else if (param == "c_t"){
-#     x <- subset(data, select=c_t) # The column of c_ts
     xLabel <- "$c_t$"
-#     y <- subset(data, select=upperCI_c_t) - subset(data, select=lowerCI_c_t) # A column of CI values
     xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
@@
   }
-#   colnames(y) <- "CI"
   yLabel <- paste("Width of 95\\% CI on", xLabel)
-#   data <- cbind(x, y)
   # Need to use the indices in the following code, because the column labels will be different for each type

### 2013-04-20 EconGrowth-R-Functions.Rnw
Beginning the work on the lattice version of the triangle plot that contains (a) all the relevant energy parameters and their confidence intervals (on the y axis) and (b) the values of the parameters (on the x axis).

@@
   else if (model == "CD"){data <- cobbDouglasParamsTableNoEnergyDF()}
-  else if (model == "CDe"){data <- cobbDouglasParamsTableWithEnergyDF(energyType)}
+  else if (model == "CDe"){data <- cobbDouglasParamsTableWithEnergyDF(energyType=energyType)}
   else if (model == "CES"){data <- cesParamsTableDF(energyType=NA)}
-  else if (model == "CESe"){data <- cesParamsTableDF(energyType)}
+  else if (model == "CESe"){data <- cesParamsTableDF(energyType=energyType)}
   else if (model == "LINEX"){data <- linexParamsTableDF(energyType)}
@@
   } else {
-    print("Neither energyType nor factor were NA in CIvsParamDF. But one should be.")
+    print("Neither energyType nor factor were NA in CIvsParamDF. But one should be!")
     return(NULL)
@@
   yLabel <- paste("Width of 95\\% CI on", xLabel)
+
   # Need to use the indices in the following code, because the column labels will be different for each type
@@
   return(plot)
+}
+
+########################
+# Creates a lattice plot that has the size of confidence intervals on the vertical axis and parameter
+# values on the horizontal axis.
+# At this point, this function is NOT a general-purpose function, as the number of permutations
+# of model, parameter, energy type, and factor is too varied to be able to turn into a general-purpose 
+# graph with little time investment at this point.
+# This function makes a lattice plot with the following panels (in the arrangement shown)
+#
+# gammaCDeq   gammaCDex    gammaCDeu
+# deltaCESeq  deltaCESex   deltaCESeu
+# sigmaCESeq  sigmaCESex   sigmaCESeu
+#
+# Parameters and models (gamma for CDe and delta and sigma for CESe) are in rows and energyTypes (q, x, and u) 
+# are in columns.
+##
+CIvsParamLattice <- function(descriptors){
+  # Build a data.frame that has all the necessary models
+  gammaCDeqDF  <- CIvsParamDF(model="CDe",  param="gamma", energyType="Q")
+  gammaCDexDF  <- CIvsParamDF(model="CDe",  param="gamma", energyType="X")
+  gammaCDeuDF  <- CIvsParamDF(model="CDe",  param="gamma", energyType="U")
+  deltaCESeqDF <- CIvsParamDF(model="CESe", param="delta", energyType="Q")
+  deltaCESexDF <- CIvsParamDF(model="CESe", param="delta", energyType="X")
+  deltaCESeuDF <- CIvsParamDF(model="CESe", param="delta", energyType="U")
+  sigmaCESeqDF <- CIvsParamDF(model="CESe", param="sigma", energyType="Q")
+  sigmaCESexDF <- CIvsParamDF(model="CESe", param="sigma", energyType="X")
+  sigmaCESeuDF <- CIvsParamDF(model="CESe", param="sigma", energyType="U")
+  # Change the name of the first columns (the ones that contain the parameter of interest to us) to "param".
+  # Doing this allows us to combine the individual data frames into one large data frame.
+  colnames(gammaCDeqDF)[1]  <- "param"
+  colnames(gammaCDexDF)[1]  <- "param"
+  colnames(gammaCDeuDF)[1]  <- "param"
+  colnames(deltaCESeqDF)[1] <- "param"
+  colnames(deltaCESexDF)[1] <- "param"
+  colnames(deltaCESeuDF)[1] <- "param"
+  colnames(sigmaCESeqDF)[1] <- "param"
+  colnames(sigmaCESexDF)[1] <- "param"
+  colnames(sigmaCESeuDF)[1] <- "param"
+  # Create one big data.frame with all of the data.
+  data <- rbind(gammaCDeqDF,  gammaCDexDF,  gammaCDeuDF, 
+                deltaCESeqDF, deltaCESexDF, deltaCESeuDF, 
+                sigmaCESeqDF, sigmaCESexDF, sigmaCESeuDF)
+  # Now make the graph.
 }

### 2013-04-20 EconGrowth-R-Functions.Rnw
Now adding a column of Country abbreviations for the triangle plots.

@@
   colnames(factor) <- "factor"
-  data <- cbind(x, y, factor)
+  # Now make a column containing the country abbreviations.
+  Country <- data.frame(countryAbbrevs)
+  data <- cbind(x, y, factor, Country)
   return(data)
@@
                  panel = function(x, y){
-                   ltext(x=x, y=y, labels=rownames(data))
+                   ltext(x=x, y=y, labels=data[ , 4]) # Picks up the 4th column containing the country abbreviations.
                  })
@@
                 sigmaCESeqDF, sigmaCESexDF, sigmaCESeuDF)
+print(data)
   # Now make the graph.

### 2013-04-20 EconGrowth-R-Functions.Rnw
Implemented a 9-panel lattice graph for the triangle plots with function CIvsParamLattice. Need to work on the formatting of the graphs, but this is now in there.

@@
                 sigmaCESeqDF, sigmaCESexDF, sigmaCESeuDF)
-print(data)
   # Now make the graph.
+  # Need to use the indices in the following code, because the column labels will be different for each type
+  # of model. In other words, if we're doing CESe with Q and plotting sigma, the data.frame will come 
+  # back with column names of "sigma" and "CI" on the first and second column, respectively. 
+  # plot <-  xyplot(data$CI ~ data$sigma, ...)
+  # would break if we, instead, wanted CESe with Q and plotting delta.
+  # So, instead, we use the column indices to pick off the correct variables.
+  # data[ , 1] contains the the parameter; 
+  # data[ , 2] contains the CI width; 
+  # data[ , 3] contains the descriptor for the type of graph it is.
+  plot <- xyplot(data[ , 2] ~ data[ , 1] | data[ , 3], 
+#                  xlab=list(label=xLabel),
+#                  ylab=list(label=yLabel),
+#                  scales=list(cex=scaleTextSize * textScaling, #controls text size on scales.
+#                              tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
+#                              x=list(at=atX),
+#                              y=list(at=atY)
+#                              ), 
+#                  xlim=xLimits, #x axis limits
+#                  ylim=yLimits, #y axis limits
+                 panel = function(x, y){
+                   ltext(x=x, y=y, labels=data[ , 4]) # Picks up the 4th column containing the country abbreviations.
+                 })
+  return(plot)
 }

### 2013-04-21 EconGrowth-R-Functions.Rnw
Triangle graph has much better format. Scales are reasonable. Strip is transparent, tics are inside the graph, ordering is table order, etc.

--- 2013-04-20 EconGrowth-R-Functions.Rnw
@@
 # are in columns.
-##
-CIvsParamLattice <- function(descriptors){
+#
+# textScaling: the amount by which you want to scale the text on the graph.
+##
+CIvsParamLattice <- function(textScaling=1.0){
   # Build a data.frame that has all the necessary models
@@
                 sigmaCESeqDF, sigmaCESexDF, sigmaCESeuDF)
-print(data)
   # Now make the graph.
+  # Need to use the indices in the following code, because the column labels will be different for each type
+  # of model. In other words, if we're doing CESe with Q and plotting sigma, the data.frame will come 
+  # back with column names of "sigma" and "CI" on the first and second column, respectively. 
+  # plot <-  xyplot(data$CI ~ data$sigma, ...)
+  # would break if we, instead, wanted CESe with Q and plotting delta.
+  # So, instead, we use the column indices to pick off the correct variables.
+  # data[ , 1] contains the the parameter; 
+  # data[ , 2] contains the CI width; 
+  # data[ , 3] contains the descriptor for the type of graph it is.
+  plot <- xyplot(data[ , 2] ~ data[ , 1] | data[ , 3], 
+                 scales=list(cex=scaleTextSize * textScaling, #controls text size on scales.
+                             tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
+                             alternating=FALSE, # eliminates left-right, top-bot alternating of axes
+                             x=list(at=c(0.0, 0.5, 1.0)),
+                             y=list(at=c(0.0, 1.0, 2.0))
+                             ), 
+                 xlim=c(-0.2, 1.2), #x axis limits
+                 ylim=c(-0.4, 2.4), #y axis limits
+                 xlab=list(label=""),
+                 ylab=list(label="Width of 95\\% Confidence Interval"),
+                 # Set text for factor levels
+                 strip = strip.custom(factor.levels=c("$\\gamma$ (CD with $q$)",  
+                                                      "$\\gamma$ (CD with $x$)",  
+                                                      "$\\gamma$ (CD with $u$)",
+                                                      "$\\delta$ (CES with $q$)", 
+                                                      "$\\delta$ (CES with $x$)", 
+                                                      "$\\delta$ (CES with $u$)",
+                                                      "$\\sigma$ (CES with $q$)", 
+                                                      "$\\sigma$ (CES with $x$)", 
+                                                      "$\\sigma$ (CES with $u$)"), 
+                                      bg="transparent", # Sets background transparent to match the graph itself.
+                                      par.strip.text=list(cex=textScaling) # Scales text in the strip.
+                                      ),
+                 as.table = TRUE, #indexing of panels starts in upper left and goes across rows.
+                 panel = function(x, y){
+                   ltext(x=x, y=y, labels=data[ , 4]) # Picks up the 4th column containing the country abbreviations.
+                 })
+  return(plot)
 }

### 2013-04-21 EconGrowth.Rnw
Beginning the work on the lattice version of the triangle plot that contains (a) all the relevant energy parameters and their confidence intervals (on the y axis) and (b) the values of the parameters (on the x axis).
Edited the to-do list in the paper.

@@
 \item{Heun: Fix weirdnesses with China on the CD gamma grid search graph}
-\item{Heun: Add CI vs.
-params plots for all model types (the triangle plots from the seminar).
-Maybe as a lattice graph where each model type is a panel.
-But, wait until we know if we have symmetric confidence intervals before doing this.
-These graphs won't work if we have asymmetric CIs.}
 \item{Heun: Eliminate non-developed countries from partial residual plots.}
@@
 \item de Wit: review, critique, and contextualize.
-\item \st{Reese: Add text from Word verson of paper to the LaTeX version.}
+\item{\st{Reese: Add text from Word verson of paper to the LaTeX version.}}
+\item{\st{Heun: Add CI vs.
+params plots for all model types (the triangle plots from the seminar).
+Maybe as a lattice graph where each model type is a panel.
+But, wait until we know if we have symmetric confidence intervals before doing this.
+These graphs won't work if we have asymmetric CIs.}}
 \item{\st{Heun: Rearrange the panels on the CD gamma grid search graph}}
@@
 
-<<Test, eval=TRUE>>=
-CIvsParamDF(model="CESe", param="sigma", energyType="Q")
-CIvsParamPlot(model="CESe", param="sigma", energyType="Q")
-
-@
-
 \subsection{Background}
@@
 createCESLatticeGraph()
+@
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Confidence Intervals for Cobb-Douglas and CES Models}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The key energy parameters for the Cobb-Douglas and CES models are $\gamma$, $\delta$, and $\sigma$.
+When the 95\% confidence interval for $\gamma$ and $\delta$ extends to 0.0 and 1.0, respectively, we cannot say whether including energy in the production function is helpful.
+If the value of $\gamma$ is close to 0.0, and the 95\% confidence interval does not extend to 0.0, we know that energy does not play an important role in producing economic output for the Cobb-Douglas model.
+If the value of $\delta$ is close to 1.0 and the 95\% confidence intervale does not extend to 1.0, we know that energy does not play an important role in producing economic output for the CES model.
+
+The following figure shows these relationships.
+
+<<CIvsParam_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="95\\% Confidence interval width vs.
+parameter value for key energy parameters ($\\gamma$, $\\delta$, and $\\sigma$) of the Cobb-Douglas and CES models.">>=
+CIvsParamLattice(countryAbbrevScaling=0.6)
 @

### 2013-04-21 EconGrowth.Rnw
Edited the to-do list.

@@
 \item{Heun: Fix weirdnesses with China on the CD gamma grid search graph}
-\item{Heun: Eliminate non-developed countries from partial residual plots.}
+\item{Heun: Eliminate non-developed countries from 9-panel partial residual plots.}
 \item Heun: Add CES production function fits
@@
       \item{Get values and se for $\sigma$s directly from the \texttt{cesModel} object in the \texttt{cesData} function}
-      \item Write up the decisions about parameter estimation for the CES production function fits
-      \item Revisit my assumptions for the CES production function (with energy) for each country.
-      \item Fix the problems with $\sigma_1$ and $\sigma$ values in the CES parameter tables in the appendix
+      \item{Write up the decisions about parameter estimation for the CES production function fits}
+      \item{Revisit my assumptions for the CES production function (with energy) for each country.}
+      \item{Fix the problems with $\sigma_1$ and $\sigma$ values in the CES parameter tables in the appendix}
       \item{Add CES rows to the AIC table.
-Code is in the createAICTable function, but it is not yet working.
+Code is in the \texttt{createAICTable} function, but it is not yet working.
 Need to find a way to calculate AIC for the object that is returned from the cesEst function.}
-      \item \st{Create parameter graphs for each country}
-      \item \st{Parameter tables for each energy type in the appendix}
-      \item \st{GDP comparison graph}
-      \item \st{Convert $\rho$ variables in the CES production function to $\sigma$}
+      \item{\st{Create parameter graphs for each country}}
+      \item{\st{Parameter tables for each energy type in the appendix}}
+      \item{\st{GDP comparison graph}}
+      \item{\st{Convert $\rho$ variables in the CES production function to $\sigma$}}
       \item{\st{Add a CES model without energy option (energyType=NA means CES without energy)}}
@@
 \item{Heun: Deal with missing covariance numbers when columns have unequal length. Use the \texttt{subset} command?}
-\item{Heun: Add data from 2011 and, possibly, 2012 to the models}
-\item Heun: Eliminate blanks in the coefficient tables for the 95\% CIs in the Cobb-Douglas with energy rows
+\item{Heun: Add data from 2011 to the models}
+\item{Heun: Eliminate blanks in the coefficient tables for the 95\% CIs in the Cobb-Douglas with energy rows}
       \begin{itemize}
-      \item ZA: lower bound on $\lambda$ and upper bound on $\alpha$
-      \item ZM: lower bound on $\lambda$
+      \item{ZA: lower bound on $\lambda$ and upper bound on $\alpha$}
+      \item{ZM: lower bound on $\lambda$}
       \end{itemize}
-\item Heun: Eliminate blanks in the coefficient tables for the 95\% CIs in the LINEX model
+\item{Heun: Eliminate blanks in the coefficient tables for the 95\% CIs in the LINEX model}
       \begin{itemize}
-      \item ZM: upper bound on $c_t$
+      \item{ZM: upper bound on $c_t$}
       \end{itemize}
-\item Heun: Fix warnings of the form ``Warning:  step factor 0.000488281 reduced below ’minFactor’ of 0.000976562'' in the code that generates the Cobb-Douglas with energy fits.
-\item Heun: adjust y axis limits on $a_0$ and $c_t$ parameter graphs for the LINEX model AFTER we finish debugging the LINEX models.
-\item de Wit: provide funding acknowledgement, if necessary.
-\item de Wit: review, critique, and contextualize.
+\item{Heun: Fix warnings of the form ``Warning:  step factor 0.000488281 reduced below ’minFactor’ of 0.000976562'' in the code that generates the Cobb-Douglas with energy fits.}
+\item{Heun: adjust y axis limits on $a_0$ and $c_t$ parameter graphs for the LINEX model AFTER we finish debugging the LINEX models.}
+\item{de Wit: provide funding acknowledgement, if necessary.}
+\item{de Wit: review, critique, and contextualize.}
 \item{\st{Reese: Add text from Word verson of paper to the LaTeX version.}}
@@
       \begin{itemize}
-      \item \st{Correct sizes for parameter graphs for each country}
-      \item \st{Parameter graphs ($\lambda$ and $m$) for each country}
-      \item \st{Parameter tables for each country in the appendix}
-      \item \st{GDP comparison graph}
-      \item \st{AIC rows in the AIC table}
+      \item{\st{Correct sizes for parameter graphs for each country}}
+      \item{\st{Parameter graphs ($\lambda$ and $m$) for each country}}
+      \item{\st{Parameter tables for each country in the appendix}}
+      \item{\st{GDP comparison graph}}
+      \item{\st{AIC rows in the AIC table}}
       \end{itemize}
-\item \st{Heun: Add setup variables for figure height and width where not already included.}
-\item \st{Heun: Add LINEX production function fits}
+\item{\st{Heun: Add setup variables for figure height and width where not already included.}}
+\item{\st{Heun: Add LINEX production function fits}}
       \begin{itemize}
-      \item \st{Parameter graphs for each country}
-      \item \st{Parameter tables for each country in the appendix}
-      \item \st{AIC rows in the AIC table}
-      \item \st{GDP comparison graph}
+      \item{\st{Parameter graphs for each country}}
+      \item{\st{Parameter tables for each country in the appendix}}
+      \item{\st{AIC rows in the AIC table}}
+      \item{\st{GDP comparison graph}}
       \end{itemize}

### 2013-04-22 EconGrowth.Rnw
Converted the triangle plots to have a columnar structure rather than a row structure. This allows the x-axis parameter to be the same for any column of panels. This, in turn, allows x axis labels to be moved out of the strip and onto the x axis!

@@
       \end{itemize}
-\item{Heun: Fix warnings of the form ``Warning:  step factor 0.000488281 reduced below ’minFactor’ of 0.000976562'' in the code that generates the Cobb-Douglas with energy fits.}
+\item{Heun: Fix warnings of the form \texttt{Warning:  step factor 0.000488281 reduced below ’minFactor’ of 0.000976562} in the code that generates the Cobb-Douglas with energy fits.}
 \item{Heun: adjust y axis limits on $a_0$ and $c_t$ parameter graphs for the LINEX model AFTER we finish debugging the LINEX models.}
@@
 The key energy parameters for the Cobb-Douglas and CES models are $\gamma$, $\delta$, and $\sigma$.
-When the 95\% confidence interval for $\gamma$ and $\delta$ extends to 0.0 and 1.0, respectively, we cannot say whether including energy in the production function is helpful.
-If the value of $\gamma$ is close to 0.0, and the 95\% confidence interval does not extend to 0.0, we know that energy does not play an important role in producing economic output for the Cobb-Douglas model.
-If the value of $\delta$ is close to 1.0 and the 95\% confidence intervale does not extend to 1.0, we know that energy does not play an important role in producing economic output for the CES model.
-
-The following figure shows these relationships.
+The parameter $\gamma$ in the Cobb-Douglas model (Equation \ref{eq:CD_With_Energy}) represents the importance of energy for economic growth.
+When $\gamma$ is small (close to 0), energy is not a significant contributor to economic growth for an economy.
+Conversely, when $\gamma$ is large (close to 1), energy is the primary contributor to economic growth.
+However, if the 95\% confidence interval for $\gamma$ for any given economy extends to 0.0, we cannot say with high confidence that energy makes a meaningful contribution to economic growth for that economy.
+On a graph of the width of the 95\% confidence interval for 95\% confidence interval on $\gamma$ ($CI_{95\%,\gamma}$) vs.
+$\gamma$, where each economy is represented by a point, the region where the 95\% confidence interval on $\gamma$ crosses 0 is an upper-left triangle, above and to the left of a line that connects points (0, 0) and (1, 2) on the graph.
+If $\gamma$ for a given economy is below and to the right of the line connecting (0, 0) and (1, 2), we have high confidence that we can say whether or not energy is a significant contributor to economic growth.
+Thus, only when $\gamma$ is below the line and small (i.e., close to 0) for an economy, can we say with confidence that energy is an insignificant contributor to economic growth.
+Only when $\gamma$ is below the line and large (i.e., close to 1) for an economy can we say that energy is a significant contributor to economic growth, according to the Cobb-Douglas model.
+
+The left column of graphs in Figure \ref{fig:CIvsParam_Lattice_Graph} shows $CI_{95\%,\gamma}$ vs.
+$\gamma$ for the three quantifications of energy (thermal energy, $q$, exergy, $x$, and useful work, $u$).
+We note that most countries are above and to the left of the line, while only a few are below and to the right.
+
+For the CES model (Equation \ref{eq:micEconCES_model}), the parameter $\delta$ indicates that importance of energy for economic growth.
+When $\delta$ is close to 1, energy is an insignificant contributor to economic growth, and when $\delta$ is close to 0, energy is the primary contributor to economic growth for an economy.
+However, if the 95\% confidence interval for $\delta$ extends to 1, we cannot say with high confidence that energy makes a meaningful contribution to economic growth for that economy.
+On a graph of $\delta$ confidence interval width ($CI_{95\%,\delta}$) vs.
+$\delta$, where each economy is represented by a point, the region where the 95\% confidence interval for $\delta$ crosses 1 is an upper-right triangle, above and to the right of a line that connects points (1, 0) and (0, 2) on the graph.
+If $\delta$ for a given economy is below and to the left of the line connecting (1, 0) and (0, 2), we have high confidence that we can say whether or not energy is a significant contributor to economic growth.
+Thus, only when $\delta$ is below the line and large (i.e., close to 1) for an economy, can we say with confidence that energy is an insignificant contributor to economic growth.
+Only when $\delta$ is below the line and small (i.e., close to 0) for an economy can we say that energy is a significant contributor to economic growth, according to the CES model.
+
+The middle column of graphs in Figure \ref{fig:CIvsParam_Lattice_Graph} shows $CI_{95\%,\delta}$ vs.
+$\delta$ for the three quantifications of energy (thermal energy, $q$, exergy, $x$, and useful work, $u$).
+We note that most countries are above and to the right of the line, while only a few are below and to the left.
+
+For the CES model (Equation \ref{eq:micEconCES_model}), the parameter $\sigma$ indicates whether capital stock and labor ($kl$) and energy ($e$) are substitutes ($\sigma >$ 1) or complements ($\sigma <$ 1).
+For countries whose value of $\sigma$ is below and to the right of a line connecting (0, 0) and (2, 1) on a graph of $CI_{95\%,\sigma}$ vs.
+$\sigma$, we can tell (with 95\% confidence) whether ($kl$) and ($e$) are substitutes or complements.
+For economies whose value of $\sigma$ is above and to the left of a line connecting (0, 0) and (2, 1), we cannot say with 95\% confidence whether ($kl$) and ($e$) are substitues or complements.
+Conversely, for economies whose value of $\sigma$ is below and to the right of a line connecting (0, 0) and (2, 1), we are able to say with 95\% confidence whether ($kl$) and ($e$) are substitues or complements.
+
+The right column of graphs in Figure \ref{fig:CIvsParam_Lattice_Graph} shows $CI_{95\%,\sigma}$ vs.
+$\sigma$ for the three quantifications of energy (thermal energy, $q$, exergy, $x$, and useful work, $u$).
+We note that where we can tell one way or another, energy ($e$) appears to complement capital stock and labor ($kl$).
 
 <<CIvsParam_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="95\\% Confidence interval width vs.
-parameter value for key energy parameters ($\\gamma$, $\\delta$, and $\\sigma$) of the Cobb-Douglas and CES models.">>=
+parameter value for key energy parameters ($\\gamma$, $\\delta$, and $\\sigma$) of the Cobb-Douglas and CES models.", eval=TRUE>>=
 CIvsParamLattice(countryAbbrevScaling=0.6)
 @
+
+*********** Martin: Need interpretation here. *******************
 

### 2013-04-22 EconGrowth-R-Functions.Rnw
Edited the to-do list in the paper.
Converted the triangle plots to have a columnar structure rather than a row structure. This allows the x-axis parameter to be the same for any column of panels. This, in turn, allows x axis labels to be moved out of the strip and onto the x axis!
Edited the text. Switched around the LINEX function to put the exponential term first.

@@
 ##
-CIvsParamLattice <- function(textScaling=1.0){
+CIvsParamLattice <- function(textScaling=1.0, countryAbbrevScaling=1.0){
   # Build a data.frame that has all the necessary models
   gammaCDeqDF  <- CIvsParamDF(model="CDe",  param="gamma", energyType="Q")
+  deltaCESeqDF <- CIvsParamDF(model="CESe", param="delta", energyType="Q")
+  sigmaCESeqDF <- CIvsParamDF(model="CESe", param="sigma", energyType="Q")
   gammaCDexDF  <- CIvsParamDF(model="CDe",  param="gamma", energyType="X")
+  deltaCESexDF <- CIvsParamDF(model="CESe", param="delta", energyType="X")
+  sigmaCESexDF <- CIvsParamDF(model="CESe", param="sigma", energyType="X")
   gammaCDeuDF  <- CIvsParamDF(model="CDe",  param="gamma", energyType="U")
-  deltaCESeqDF <- CIvsParamDF(model="CESe", param="delta", energyType="Q")
-  deltaCESexDF <- CIvsParamDF(model="CESe", param="delta", energyType="X")
   deltaCESeuDF <- CIvsParamDF(model="CESe", param="delta", energyType="U")
-  sigmaCESeqDF <- CIvsParamDF(model="CESe", param="sigma", energyType="Q")
-  sigmaCESexDF <- CIvsParamDF(model="CESe", param="sigma", energyType="X")
   sigmaCESeuDF <- CIvsParamDF(model="CESe", param="sigma", energyType="U")
@@
   colnames(gammaCDeqDF)[1]  <- "param"
+  colnames(deltaCESeqDF)[1] <- "param"
+  colnames(sigmaCESeqDF)[1] <- "param"
   colnames(gammaCDexDF)[1]  <- "param"
+  colnames(deltaCESexDF)[1] <- "param"
+  colnames(sigmaCESexDF)[1] <- "param"
   colnames(gammaCDeuDF)[1]  <- "param"
-  colnames(deltaCESeqDF)[1] <- "param"
-  colnames(deltaCESexDF)[1] <- "param"
   colnames(deltaCESeuDF)[1] <- "param"
-  colnames(sigmaCESeqDF)[1] <- "param"
-  colnames(sigmaCESexDF)[1] <- "param"
   colnames(sigmaCESeuDF)[1] <- "param"
   # Create one big data.frame with all of the data.
-  data <- rbind(gammaCDeqDF,  gammaCDexDF,  gammaCDeuDF, 
-                deltaCESeqDF, deltaCESexDF, deltaCESeuDF, 
-                sigmaCESeqDF, sigmaCESexDF, sigmaCESeuDF)
+  data <- rbind(gammaCDeqDF, deltaCESeqDF, sigmaCESeqDF, 
+                gammaCDexDF, deltaCESexDF, sigmaCESexDF,
+                gammaCDeuDF, deltaCESeuDF, sigmaCESeuDF)
   # Now make the graph.
@@
                  ylim=c(-0.4, 2.4), #y axis limits
-                 xlab=list(label=""),
+                 xlab=list(label=c("$\\gamma$", "$\\delta$", "$\\sigma$")),
                  ylab=list(label="Width of 95\\% Confidence Interval"),
                  # Set text for factor levels
-                 strip = strip.custom(factor.levels=c("$\\gamma$ (CD with $q$)",  
-                                                      "$\\gamma$ (CD with $x$)",  
-                                                      "$\\gamma$ (CD with $u$)",
-                                                      "$\\delta$ (CES with $q$)", 
-                                                      "$\\delta$ (CES with $x$)", 
-                                                      "$\\delta$ (CES with $u$)",
-                                                      "$\\sigma$ (CES with $q$)", 
-                                                      "$\\sigma$ (CES with $x$)", 
-                                                      "$\\sigma$ (CES with $u$)"), 
+                 strip = strip.custom(factor.levels=c("CD with $q$",
+                                                      "CES with $q$", 
+                                                      "CES with $q$",
+                                                      "CD with $x$",  
+                                                      "CES with $x$", 
+                                                      "CES with $x$", 
+                                                      "CD with $u$",
+                                                      "CES with $u$",
+                                                      "CES with $u$"), 
                                       bg="transparent", # Sets background transparent to match the graph itself.
@@
                  panel = function(x, y){
-                   ltext(x=x, y=y, labels=data[ , 4]) # Picks up the 4th column containing the country abbreviations.
+                   # Picks up the 4th column containing the country abbreviations.
+                   ltext(x=x, y=y, labels=data[ , 4], cex=countryAbbrevScaling) 
                  })

### 2013-04-22 EconGrowth.Rnw
Edited the text. Switched around the LINEX function to put the exponential term first.

@@
 \begin{itemize}
+\item{Heun: Add diagonal lines to triangle plots via the doubleY graph idea.
+Make a simple data.frame that contains the coordinates of the line and add it to the graph as a second Y axis, but don't show the second Y axis.}
 \item{Heun: Fix weirdnesses with China on the CD gamma grid search graph}
@@
 \item{\st{Heun: Convert to using NA everywhere for models without energy}}
-\item{\st{Heun: Investigate use of the micEcon package transLogEst function for CD parameter estimation. Doesn't look like it will work, because it doesn't do the CD form of interest to us.}}
+\item{\st{Heun: Investigate use of the micEcon package transLogEst function for CD parameter estimation. Result: doesn't look like it will work, because it doesn't do the CD form of interest to us.}}
 \item{\st{Heun: Re-organize CES tables into (a) $\lambda$, $\delta$, $\sigma$ and (b) $\gamma$, $\delta_1$, $\sigma_1$}}
-\item \st{Heun: Ask Martin if he can supply an ``Economics'' affiliation. Will probably make a stronger paper.}
-\item \st{Heun: Create a table of AIC values for each fit.}
-\item \st{Heun: Add $u$ predictions for Cobb-Douglas}
-\item \st{Heun: Move tables to an appendix at the end.}
-\item \st{Heun: Add acknowledgements (Dad, Pruim)}
-\item \st{Heun: Add $u$ parameter table and graph}
-\item \st{Heun: Add covariance metrics.}
-\item \st{Heun: Add single factor fits}
+\item{\st{Heun: Ask Martin if he can supply an ``Economics'' affiliation. Will probably make a stronger paper.}}
+\item{\st{Heun: Create a table of AIC values for each fit.}}
+\item{\st{Heun: Add $u$ predictions for Cobb-Douglas}}
+\item{\st{Heun: Move tables to an appendix at the end.}}
+\item{\st{Heun: Add acknowledgements (Dad, Pruim)}}
+\item{\st{Heun: Add $u$ parameter table and graph}}
+\item{\st{Heun: Add covariance metrics.}}
+\item{\st{Heun: Add single factor fits}}
       \begin{itemize}
@@
 To demonstrate the characteristics of the parameter estimation process, we performed a grid search over values of $\gamma$, wherein we re-estimated values of $\lambda$, $\alpha$, and $\beta$ at each value of $\gamma$.
-Figure \ref{fig:CDeGammaGraphsZA} shows the sum of squared errors ($SSE$), $\alpha$, and $\beta$ as a function of the fixed value of $\gamma$ for South Africa with thermal energy ($q$).
-The minimum $SSE$ occurs at a discontinuity caused by the constraint $\beta \geq 0.0$.
-The parameter estimation algorithm has difficulty recognizing the values of $\gamma$, $\alpha$, $\beta$, and $\lambda$ that produce minimum $SSE$, because the constrained model behaves very differently on either side of the discontinuity.
+Figure \ref{fig:CDeGridLattice} shows the sum of squared errors ($SSE$), $\alpha$, and $\beta$ as a function of the fixed value of $\gamma$ with thermal energy ($q$).
+For most economies, the minimum $SSE$ occurs at a boundary of $\alpha$, $\beta$, or $\gamma$.
+The parameter estimation algorithm has difficulty assessing confidence intervals for $\alpha$, $\beta$, and $\gamma$, because the constrained model behaves very differently on either side of the constraint.
 
@@
 The parameter $\gamma$ in the Cobb-Douglas model (Equation \ref{eq:CD_With_Energy}) represents the importance of energy for economic growth.
-When $\gamma$ is small (close to 0), energy is not a significant contributor to economic growth for an economy.
-Conversely, when $\gamma$ is large (close to 1), energy is the primary contributor to economic growth.
+When $\gamma \rightarrow 0$, energy is not a significant contributor to economic growth for an economy.
+Conversely, when $\gamma \rightarrow 1$, energy is the primary contributor to economic growth.
 However, if the 95\% confidence interval for $\gamma$ for any given economy extends to 0.0, we cannot say with high confidence that energy makes a meaningful contribution to economic growth for that economy.
@@
 For the CES model (Equation \ref{eq:micEconCES_model}), the parameter $\delta$ indicates that importance of energy for economic growth.
-When $\delta$ is close to 1, energy is an insignificant contributor to economic growth, and when $\delta$ is close to 0, energy is the primary contributor to economic growth for an economy.
+When $\delta \rightarrow 1$, energy is an insignificant contributor to economic growth, and when $\delta \rightarrow 0$, energy is the primary contributor to economic growth for an economy.
 However, if the 95\% confidence interval for $\delta$ extends to 1, we cannot say with high confidence that energy makes a meaningful contribution to economic growth for that economy.
@@
 \begin{equation} \label{eq:LINEX_model}
-  y = e \: \mathrm{e}^{\left[a_0 \left(2 - \frac{l + e}{k} \right) + a_0 c_t \left(\frac{l}{e} - 1 \right)\right]} ,
+  y = \mathrm{e}^{\left[a_0 \left(2 - \frac{l + e}{k} \right) + a_0 c_t \left(\frac{l}{e} - 1 \right)\right]} \: e ,
 \end{equation}

### 2013-04-22 EconGrowth-R-Functions.Rnw
Working toward a second graph to be used as a doubleY to show diagonal lines on the triangle plots.

--- 2013-04-20 EconGrowth-R-Functions.Rnw
@@
 # are in columns.
-##
-CIvsParamLattice <- function(descriptors){
-  # Build a data.frame that has all the necessary models
+#
+# textScaling: the amount by which you want to scale the text on the graph.
+##
+CIvsParamLattice <- function(textScaling=1.0, countryAbbrevScaling=1.0){
+  # Set up plotting parameters that are common to both graphs.
+  xTics <- c(0.0, 0.5, 1.0) #x axis tic locations
+  yTics <- c(0.0, 1.0, 2.0) #y axis tic locations
+  xLimits <- c(-0.2, 1.2) #x axis limits
+  yLimits <- c(-0.4, 2.4) #y axis limits
+  xLabels <- c("$\\gamma$", "$\\delta$", "$\\sigma$") #x axis labels
+  yLabel <- "Width of 95\\% Confidence Interval"
+  stripLabels <- c("CD with $q$", "CES with $q$", "CES with $q$",
+                   "CD with $x$", "CES with $x$", "CES with $x$", 
+                   "CD with $u$", "CES with $u$", "CES with $u$")
+  stripBG <- "transparent"
+
+  # Build a data.frame that contains coordinates for diagonal lines on the various graphs.
+  # Columns are "param", "CI", and "factor" to match the column names later in this function.
+  # Diagonal line for the gamma-CD-Q panel
+  param <- c(0.0, 1.0)
+  CI <- c(0.0, 2.0)
+  factor <- c("gammaCDeQ", "gammaCDeQ")
+  diagLineGammaCDeQDF <- data.frame(param, CI, factor)
+  # Diagonal line for the gamma-CD-X panel
+  factor <- c("gammaCDeX", "gammaCDeX")
+  diagLineGammaCDeXDF <- data.frame(param, CI, factor)
+  # Diagonal line for the gamma-CD-U panel
+  factor <- c("gammaCDeU", "gammaCDeU")
+  diagLineGammaCDeUDF <- data.frame(param, CI, factor)
+
+  # Diagonal line for the delta-CES-Q panel  
+  param <- c(1.0, 0.0)
+  CI <- c(0.0, 2.0)
+  factor <- c("deltaCESeQ", "deltaCESeQ")
+  diagLineDeltaCESeQDF <- data.frame(param, CI, factor)
+  # Diagonal line for the delta-CES-X panel  
+  factor <- c("deltaCESeX", "deltaCESeX")
+  diagLineDeltaCESeXDF <- data.frame(param, CI, factor)
+  # Diagonal line for the delta-CES-U panel  
+  factor <- c("deltaCESeU", "deltaCESeU")
+  diagLineDeltaCESeUDF <- data.frame(param, CI, factor)
+
+  # Diagonal line for the sigma-CES-Q panel  
+  param <- c(0.0, 1.0)
+  CI <- c(0.0, 2.0)
+  factor <- c("sigmaCESeQ", "sigmaCESeQ")
+  diagLineSigmaCESeQDF <- data.frame(param, CI, factor)
+  # Diagonal line for the sigma-CES-X panel  
+  factor <- c("sigmaCESeX", "sigmaCESeX")
+  diagLineSigmaCESeXDF <- data.frame(param, CI, factor)
+  # Diagonal line for the sigma-CES-U panel  
+  factor <- c("sigmaCESeU", "sigmaCESeU")
+  diagLineSigmaCESeUDF <- data.frame(param, CI, factor)
+
+  # Now combine all data.frames in the correct order.
+  diagLinesDF <- rbind(diagLineGammaCDeQDF, diagLineDeltaCESeQDF, diagLineSigmaCESeQDF,
+                       diagLineGammaCDeXDF, diagLineDeltaCESeXDF, diagLineSigmaCESeXDF,
+                       diagLineGammaCDeUDF, diagLineDeltaCESeUDF, diagLineSigmaCESeUDF)
+
+  # Make an xyplot that contains the diagonal lines.
+  diagLinesLattice <- xyplot(CI ~ param | factor, data=diagLinesDF,
+                             scales=list(cex=scaleTextSize * textScaling, #controls text size on scales.
+                             tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
+                             alternating=FALSE, # eliminates left-right, top-bot alternating of axes
+                             x=list(at=xTics),
+                             y=list(at=yTics)
+                             ), 
+                             xlim=xLimits, 
+                             ylim=yLimits, 
+                             xlab=list(label=xLabels),
+                             ylab=list(label=yLabel),
+                             strip = strip.custom(factor.levels=stripLabels, # Set text for factor levels
+                                                  bg=stripBG,
+                                                  par.strip.text=list(cex=textScaling) # Scales text in the strip.
+                                                  ),
+                             as.table = TRUE, #indexing of panels starts in upper left and goes across rows.
+                             )
+
+  # Build a data.frame that has all the necessary data from the models.
   gammaCDeqDF  <- CIvsParamDF(model="CDe",  param="gamma", energyType="Q")
+  deltaCESeqDF <- CIvsParamDF(model="CESe", param="delta", energyType="Q")
+  sigmaCESeqDF <- CIvsParamDF(model="CESe", param="sigma", energyType="Q")
   gammaCDexDF  <- CIvsParamDF(model="CDe",  param="gamma", energyType="X")
+  deltaCESexDF <- CIvsParamDF(model="CESe", param="delta", energyType="X")
+  sigmaCESexDF <- CIvsParamDF(model="CESe", param="sigma", energyType="X")
   gammaCDeuDF  <- CIvsParamDF(model="CDe",  param="gamma", energyType="U")
-  deltaCESeqDF <- CIvsParamDF(model="CESe", param="delta", energyType="Q")
-  deltaCESexDF <- CIvsParamDF(model="CESe", param="delta", energyType="X")
   deltaCESeuDF <- CIvsParamDF(model="CESe", param="delta", energyType="U")
-  sigmaCESeqDF <- CIvsParamDF(model="CESe", param="sigma", energyType="Q")
-  sigmaCESexDF <- CIvsParamDF(model="CESe", param="sigma", energyType="X")
   sigmaCESeuDF <- CIvsParamDF(model="CESe", param="sigma", energyType="U")
@@
   colnames(gammaCDeqDF)[1]  <- "param"
+  colnames(deltaCESeqDF)[1] <- "param"
+  colnames(sigmaCESeqDF)[1] <- "param"
   colnames(gammaCDexDF)[1]  <- "param"
+  colnames(deltaCESexDF)[1] <- "param"
+  colnames(sigmaCESexDF)[1] <- "param"
   colnames(gammaCDeuDF)[1]  <- "param"
-  colnames(deltaCESeqDF)[1] <- "param"
-  colnames(deltaCESexDF)[1] <- "param"
   colnames(deltaCESeuDF)[1] <- "param"
-  colnames(sigmaCESeqDF)[1] <- "param"
-  colnames(sigmaCESexDF)[1] <- "param"
   colnames(sigmaCESeuDF)[1] <- "param"
   # Create one big data.frame with all of the data.
-  data <- rbind(gammaCDeqDF,  gammaCDexDF,  gammaCDeuDF, 
-                deltaCESeqDF, deltaCESexDF, deltaCESeuDF, 
-                sigmaCESeqDF, sigmaCESexDF, sigmaCESeuDF)
+  data <- rbind(gammaCDeqDF, deltaCESeqDF, sigmaCESeqDF, 
+                gammaCDexDF, deltaCESexDF, sigmaCESexDF,
+                gammaCDeuDF, deltaCESeuDF, sigmaCESeuDF)
+print(data)
   # Now make the graph.
@@
   # data[ , 3] contains the descriptor for the type of graph it is.
-  plot <- xyplot(data[ , 2] ~ data[ , 1] | data[ , 3], 
-#                  xlab=list(label=xLabel),
-#                  ylab=list(label=yLabel),
-#                  scales=list(cex=scaleTextSize * textScaling, #controls text size on scales.
-#                              tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
-#                              x=list(at=atX),
-#                              y=list(at=atY)
-#                              ), 
-#                  xlim=xLimits, #x axis limits
-#                  ylim=yLimits, #y axis limits
+  plot <- xyplot(CI ~ param | factor, data=data,
+                 scales=list(cex=scaleTextSize * textScaling, #controls text size on scales.
+                             tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
+                             alternating=FALSE, # eliminates left-right, top-bot alternating of axes
+                             x=list(at=xTics),
+                             y=list(at=yTics)
+                             ), 
+                 xlim=xLimits, 
+                 ylim=yLimits, 
+                 xlab=list(label=xLabels),
+                 ylab=list(label=yLabel),
+                 # Set text for factor levels
+                 strip = strip.custom(factor.levels=stripLabels, 
+                                      bg=stripBG, # Sets background transparent to match the graph itself.
+                                      par.strip.text=list(cex=textScaling) # Scales text in the strip.
+                                      ),
+                 as.table = TRUE, #indexing of panels starts in upper left and goes across rows.
                  panel = function(x, y){
-                   ltext(x=x, y=y, labels=data[ , 4]) # Picks up the 4th column containing the country abbreviations.
+                   # Picks up the 4th column containing the country abbreviations.
+                   ltext(x=x, y=y, labels=data[ , 4], cex=countryAbbrevScaling) 
                  })
-  return(plot)
+  #return(plot)
+  return(diagLinesLattice)
 }

### 2013-04-22 EconGrowth.Rnw
Now including diagonal lines on triangle graphs.

@@
 
-For the CES model (Equation \ref{eq:micEconCES_model}), the parameter $\sigma$ indicates whether capital stock and labor ($kl$) and energy ($e$) are substitutes ($\sigma >$ 1) or complements ($\sigma <$ 1).
-For countries whose value of $\sigma$ is below and to the right of a line connecting (0, 0) and (2, 1) on a graph of $CI_{95\%,\sigma}$ vs.
-$\sigma$, we can tell (with 95\% confidence) whether ($kl$) and ($e$) are substitutes or complements.
-For economies whose value of $\sigma$ is above and to the left of a line connecting (0, 0) and (2, 1), we cannot say with 95\% confidence whether ($kl$) and ($e$) are substitues or complements.
-Conversely, for economies whose value of $\sigma$ is below and to the right of a line connecting (0, 0) and (2, 1), we are able to say with 95\% confidence whether ($kl$) and ($e$) are substitues or complements.
+For the CES model (Equation \ref{eq:micEconCES_model}), the parameter $\sigma$ indicates whether capital stock and labor ($kl$) and energy ($e$) are complements ($\sigma <$ 1) or substitutes ($\sigma >$ 1).
+For countries whose value of $\sigma$ is below and to the left of a line connecting (0, 2) and (1, 0) on a graph of $CI_{95\%,\sigma}$ vs.
+$\sigma$, we can say (with 95\% confidence) that ($kl$) and ($e$) are complements.
+For economies whose value of $\sigma$ is below and to the right of a line connecting (1, 0) and (2, 2), we can say (with 95\% confidence) that ($kl$) and ($e$) are substitutes.
+For economies whose value of $\sigma$ is above those lines, we cannot say with 95\% confidence whether ($kl$) and ($e$) are substitues or complements.
 
@@
 $\sigma$ for the three quantifications of energy (thermal energy, $q$, exergy, $x$, and useful work, $u$).
-We note that where we can tell one way or another, energy ($e$) appears to complement capital stock and labor ($kl$).
-
-<<CIvsParam_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="95\\% Confidence interval width vs.
-parameter value for key energy parameters ($\\gamma$, $\\delta$, and $\\sigma$) of the Cobb-Douglas and CES models.", eval=TRUE>>=
+We note that energy ($e$) unambiguously complements capital stock and labor ($kl$) for most economies.
+
+<<CIvsParam_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="95\\% Confidence interval widths vs.
+parameter values for key energy parameters ($\\gamma$, $\\delta$, and $\\sigma$) of the Cobb-Douglas and CES models.
+If an economy appears in the region above a dashed line, the 95\\% confidence interval for the parameter extends to or beyond $\\gamma \\le$ 0 (cannot say with 95\\% confidence that energy is important for the Cobb-Douglas model), $\\delta \\ge$ 1 (cannot say with 95\\% confidence that energy is important for the CES model), or $\\sigma$ = 0 (cannot say with 95\\% confidence whether ($kl$) and ($e$) are complements or substitutes in the CES model).", eval=TRUE>>=
 CIvsParamLattice(countryAbbrevScaling=0.6)

### 2013-04-23 EconGrowth.Rnw
Edited the background section.

@@
 \begin{itemize}
-\item{Heun: Add diagonal lines to triangle plots via the doubleY graph idea.
-Make a simple data.frame that contains the coordinates of the line and add it to the graph as a second Y axis, but don't show the second Y axis.}
 \item{Heun: Fix weirdnesses with China on the CD gamma grid search graph}
@@
 \item{de Wit: review, critique, and contextualize.}
+\item{\st{Heun: Add diagonal lines to triangle plots via the doubleY graph idea.
+Make a simple data.frame that contains the coordinates of the line and add it to the graph as a second Y axis, but don't show the second Y axis.}}
 \item{\st{Reese: Add text from Word verson of paper to the LaTeX version.}}
@@
 
-Neoclassical economic growth theory attributes output growth to growth rates of factors of production: capital stock and labor.
-In 1928, Amherst Professors Charles Cobb and Paul Douglas created the Cobb-Douglas production function that predicted manufacturing output ($y$) as a function of labor ($l$), capital stock ($k$), and a technological progress term ($\mathrm{e}^{(t-t_0)}$) \citep{Mishra:2007tv}
+Neoclassical economic growth theory attributes output ($Y$) to factors of production: capital stock ($K$) and labor ($L$).
+The Cobb-Douglas production function is the canonical representation of indexed economic output ($y$) as a function of indexed labor ($l$), indexed capital stock ($k$), and an exogenous, time-dependent technological progress term ($\mathrm{e}^{\lambda(t-t_0)}$):
 
 \begin{equation} \label{eq:CD}
-  y_\mathrm{CD} = \mathrm{e}^{(t-t_0)} k^\alpha l^\beta,
-\end{equation}
-
-\noindent where
-
-\begin{equation} \label{eq:y_def}
-  y \equiv Y/Y_\mathrm{0},
-\end{equation}
-
-\begin{equation} \label{eq:k_def}
-  k \equiv K/K_\mathrm{0},
-\end{equation}
-
-\noindent and
-
-\begin{equation} \label{eq:l_def}
-  l \equiv L/L_\mathrm{0};
-\end{equation}
-
-\noindent with $Y$ measured by GDP, $K$ measured in currency units, and $L$ measured in workers or work-hours.
-
-In the Cobb-Douglas production function, capital and labor are related to output with an elasticity of unity, indicating constant returns to scale.
-
-\begin{equation} \label{eq:CD_constant_returns_to_scale_constraint}
-  \alpha + \beta = 1
-\end{equation}
-
-Using only labor and capital factors of production, neoclassical economic growth theory cannot predict the growth of the U.S. economy over the last 100 years.
-
-%Figure 1 goes here
-
-So, an exogenous "technological progress" term (\textit{A(t)}) is often included to better predict historical economic growth as a function of capital and labor factors of production.
-For the U.S., the \textit{A(t)} parameter is necessary: without it, the theory cannot accurately describe historical economic performance.
-
-Neoclassical economic growth theory makes no attempt to understand the mechanisms by which technological progress affects economic growth, nor does it attempt to say how technological progress might vary from one economy to the next.
-Mathematically, technological progress is nothing more than a fitting parameter that aligns the predictions of equation 1 with historical data.
-
-As shown in Equation 1 above, neoclassical economic theory neglects the role of energy input to the economy.
-However, (BASHMAKOV, 2007) and (MURPHY, 2011) indicate that the influence of energy on economic growth may far outweigh its cost share in the economy.
-That neoclassical economic growth theory ignores energy input is, therefore, cause for concern, and an inquiry into the proper approach to including energy as a factor of production in growth modeling is therefore, extremely relevant.
-
-Many energy economists include energy as a factor of production (along with capital stock and labor) to improve predictions of historical economic growth.
-But, there is little agreement on how this should be done.
-Neither the mathematical form of the production function, nor which type of energy should be considered (thermal energy, exergy, of useful work) are consistent in the literature.
-Furthermore, there has been little empirical work done to assess the predictive ability of various energy-including production functions for different types of economies.
-This paper attempts to contribute to our understanding in these important areas.
+  y = \mathrm{e}^{\lambda(t-t_0)} k^\alpha l^\beta,
+\end{equation}
+
+\noindent where $y \equiv Y/Y_\mathrm{0}$, $k \equiv K/K_\mathrm{0}$, and $l \equiv L/L_\mathrm{0}$; with $Y$ measured by GDP, $K$ measured in currency units, $L$ measured in workers/year or work-hours/year, and subscripts ``0'' indicating values at an initial year.
+Time ($t$) is measured in years, and $\lambda$ indicates the pace of technological progress (in units of year$^{-1}$).
+Neoclassical economic growth theory makes no attempt to understand the mechanisms by which technological progress affects economic growth, nor does it attempt to describe how technological progress might vary from one economy to the next.
+Mathematically, technological progress is a fitting parameter that aligns the predictions of Equation \ref{eq:CD} with historical data.
+Typically, an elasticity of unity is assumed ($\alpha + \beta = 1$), indicating constant returns to scale.
+
+As shown in Equation \ref{eq:CD} above, neoclassical economic theory neglects the role of energy input to the economy.
+However, \citet{Bashmakov:2007ek} and \citet{Murphy:2011jh} indicate that the influence of energy on economic growth may far outweigh its cost share in the economy.
+That neoclassical economic growth theory ignores energy is, therefore, cause for concern, and an inquiry into the proper approach for including energy as a factor of production in economic growth modeling is both relevant and important.
+
+Some energy economists augment economic growth models with energy as an additional (or the only) factor of production.
+However, there is little agreement on how this should be done.
+Neither the mathematical form of the production function (Cobb-Douglas, CD; Constant Elasticity of Substitution, CES; or Linear Exponential, LINEX) nor which quantification of energy should be included (thermal energy, $q$; exergy, $x$; or useful work, $u$) are consistent in the literature.
+Furthermore, there has been little empirical work done to assess the predictive ability of energy-augmented production functions for different types of economies (e.g., developed, BRICS,\footnote{Brazil, China, India, South Africa} petrol, or developing).
+This paper attempts to contribute to the literature in these important areas.
+
+************* Matt ended here. ****************
 
 \subsection{Mathematical Forms of the Production Function}
-Many energy-including production functions have been used to predict economic growth.
+
+Many energy-augmented production functions have been used to predict economic growth.
 Three prominent functions are the Cobb-Douglas production function with an energy input as used by (AYRES AND WARR, 2008), the Stern Constant Elasticity of Substitution (CES) production function (STERN, 2010), and K\"{u}mmel's Linear Exponential (LINEX) production function (KUMMEL, 1980).
@@
 The key energy parameters for the Cobb-Douglas and CES models are $\gamma$, $\delta$, and $\sigma$.
-The parameter $\gamma$ in the Cobb-Douglas model (Equation \ref{eq:CD_With_Energy}) represents the importance of energy for economic growth.
+The parameter $\gamma$ in the Cobb-Douglas model (Equation \ref{eq:CD_With_Energy}) indicates the importance of energy for economic growth.
 When $\gamma \rightarrow 0$, energy is not a significant contributor to economic growth for an economy.
 Conversely, when $\gamma \rightarrow 1$, energy is the primary contributor to economic growth.
-However, if the 95\% confidence interval for $\gamma$ for any given economy extends to 0.0, we cannot say with high confidence that energy makes a meaningful contribution to economic growth for that economy.
-On a graph of the width of the 95\% confidence interval for 95\% confidence interval on $\gamma$ ($CI_{95\%,\gamma}$) vs.
-$\gamma$, where each economy is represented by a point, the region where the 95\% confidence interval on $\gamma$ crosses 0 is an upper-left triangle, above and to the left of a line that connects points (0, 0) and (1, 2) on the graph.
-If $\gamma$ for a given economy is below and to the right of the line connecting (0, 0) and (1, 2), we have high confidence that we can say whether or not energy is a significant contributor to economic growth.
+However, if the 95\% confidence interval for $\gamma$ for any given economy extends to 0.0, we cannot say with high confidence whether or not energy makes a meaningful contribution to economic growth for that economy.
+On a graph of the width of the 95\% confidence interval for $\gamma$ ($CI_{95\%,\gamma}$) vs.
+$\gamma$, where each economy is represented by a point, the locus of points where the 95\% confidence interval on $\gamma$ crosses 0 is a diagonal line.
+If the combination of $\gamma$ and its confidence interval for a given economy is below and to the right of the line, we have high confidence that we can say whether or not energy is a significant contributor to economic growth.
 Thus, only when $\gamma$ is below the line and small (i.e., close to 0) for an economy, can we say with confidence that energy is an insignificant contributor to economic growth.
@@
 $\gamma$ for the three quantifications of energy (thermal energy, $q$, exergy, $x$, and useful work, $u$).
-We note that most countries are above and to the left of the line, while only a few are below and to the right.
-
-For the CES model (Equation \ref{eq:micEconCES_model}), the parameter $\delta$ indicates that importance of energy for economic growth.
+We note that most economies are above and to the left of the line, while only a few are below and to the right.
+
+For the CES model (Equation \ref{eq:micEconCES_model}), the parameter $\delta$ indicates the importance of energy for economic growth.
 When $\delta \rightarrow 1$, energy is an insignificant contributor to economic growth, and when $\delta \rightarrow 0$, energy is the primary contributor to economic growth for an economy.
-However, if the 95\% confidence interval for $\delta$ extends to 1, we cannot say with high confidence that energy makes a meaningful contribution to economic growth for that economy.
-On a graph of $\delta$ confidence interval width ($CI_{95\%,\delta}$) vs.
-$\delta$, where each economy is represented by a point, the region where the 95\% confidence interval for $\delta$ crosses 1 is an upper-right triangle, above and to the right of a line that connects points (1, 0) and (0, 2) on the graph.
-If $\delta$ for a given economy is below and to the left of the line connecting (1, 0) and (0, 2), we have high confidence that we can say whether or not energy is a significant contributor to economic growth.
+However, if the 95\% confidence interval for $\delta$ extends to 1, we cannot say with high confidence whether or not energy makes a meaningful contribution to economic growth for that economy.
+In a manner similar to $\gamma$ for the Cobb-Douglas model, we note that if the combination of $\delta$ and its confidence interval for a given economy is below and to the left of the line, we have high confidence that we can say whether or not energy is a significant contributor to economic growth.
 Thus, only when $\delta$ is below the line and large (i.e., close to 1) for an economy, can we say with confidence that energy is an insignificant contributor to economic growth.
@@
 $\delta$ for the three quantifications of energy (thermal energy, $q$, exergy, $x$, and useful work, $u$).
-We note that most countries are above and to the right of the line, while only a few are below and to the left.
+We note that most economies are above and to the right of the line, while only a few are below and to the left.
 
 For the CES model (Equation \ref{eq:micEconCES_model}), the parameter $\sigma$ indicates whether capital stock and labor ($kl$) and energy ($e$) are complements ($\sigma <$ 1) or substitutes ($\sigma >$ 1).
-For countries whose value of $\sigma$ is below and to the left of a line connecting (0, 2) and (1, 0) on a graph of $CI_{95\%,\sigma}$ vs.
-$\sigma$, we can say (with 95\% confidence) that ($kl$) and ($e$) are complements.
-For economies whose value of $\sigma$ is below and to the right of a line connecting (1, 0) and (2, 2), we can say (with 95\% confidence) that ($kl$) and ($e$) are substitutes.
+For countries whose combination of  $\sigma$ and its confidence interval is below and to the left of the lines in the rightmost graphs of Figure \ref{fig:CIvsParam_Lattice_Graph} we can say (with 95\% confidence) that ($kl$) and ($e$) are complements.
+For economies whose value of $\sigma$ is below and to the right of the line, we can say (with 95\% confidence) that ($kl$) and ($e$) are substitutes.
 For economies whose value of $\sigma$ is above those lines, we cannot say with 95\% confidence whether ($kl$) and ($e$) are substitues or complements.
@@
 <<CIvsParam_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="95\\% Confidence interval widths vs.
-parameter values for key energy parameters ($\\gamma$, $\\delta$, and $\\sigma$) of the Cobb-Douglas and CES models.
-If an economy appears in the region above a dashed line, the 95\\% confidence interval for the parameter extends to or beyond $\\gamma \\le$ 0 (cannot say with 95\\% confidence that energy is important for the Cobb-Douglas model), $\\delta \\ge$ 1 (cannot say with 95\\% confidence that energy is important for the CES model), or $\\sigma$ = 0 (cannot say with 95\\% confidence whether ($kl$) and ($e$) are complements or substitutes in the CES model).", eval=TRUE>>=
+parameter values for key energy parameters ($\\gamma$, $\\delta$, and $\\sigma$) of the Cobb-Douglas and CES models with energy.
+If an economy appears in the region above a dashed line, the 95\\% confidence interval for the parameter extends to or beyond $\\gamma \\le$ 0 (cannot say with 95\\% confidence that energy is important for the Cobb-Douglas model), $\\delta \\ge$ 1 (cannot say with 95\\% confidence that energy is important for the CES model), or $\\sigma$ = 1 (cannot say with 95\\% confidence whether ($kl$) and ($e$) are complements or substitutes in the CES model).">>=
 CIvsParamLattice(countryAbbrevScaling=0.6)
@@
 
-*********** Martin: Need interpretation here. *******************
+Regardless of model (Cobb-Douglas or CES) or energy quantification ($q$, $x$, or $u$), there are few economies for which we can say with high confidence (at the 95\% level) that energy plays a significant role in economic growth.
+However, in seeming contradiction, results for the CES model indicate that energy complements capital stock and labor.
+That is, energy is essential for capital stock and labor to generate economic growth.
+One possible explanation for this apparent contradiction is to consider energy as embedded within capital stock and labor: it takes energy to make both captial stock and labor available to generate economic growth.
+
+*********** Martin: Need additional interpretation here. *******************
 

### 2013-04-23 EconGrowth.Rnw
Further editing of the introduction text. Added several references, too.

@@
 
-\subsection{Background}
-
 Neoclassical economic growth theory attributes output ($Y$) to factors of production: capital stock ($K$) and labor ($L$).
@@
 \begin{equation} \label{eq:CD}
-  y = \mathrm{e}^{\lambda(t-t_0)} k^\alpha l^\beta,
-\end{equation}
-
-\noindent where $y \equiv Y/Y_\mathrm{0}$, $k \equiv K/K_\mathrm{0}$, and $l \equiv L/L_\mathrm{0}$; with $Y$ measured by GDP, $K$ measured in currency units, $L$ measured in workers/year or work-hours/year, and subscripts ``0'' indicating values at an initial year.
-Time ($t$) is measured in years, and $\lambda$ indicates the pace of technological progress (in units of year$^{-1}$).
+  y = A k^\alpha l^\beta; A = \mathrm{e}^{\lambda(t-t_0)}
+\end{equation}
+
+\noindent where $y \equiv Y/Y_\mathrm{0}$, $k \equiv K/K_\mathrm{0}$, and $l \equiv L/L_\mathrm{0}$; with $Y$ represented by GDP, $K$ expressed in currency units, $L$ expressed in workers/year or work-hours/year, e being the base of the natural logarithm, and subscripts ``0'' indicating values at an initial year.
+Time ($t$) is measured in years, $A$ is a technological progress term with $\lambda$ indicating the pace of technological progress (in units of year$^{-1}$).
 Neoclassical economic growth theory makes no attempt to understand the mechanisms by which technological progress affects economic growth, nor does it attempt to describe how technological progress might vary from one economy to the next.
 Mathematically, technological progress is a fitting parameter that aligns the predictions of Equation \ref{eq:CD} with historical data.
-Typically, an elasticity of unity is assumed ($\alpha + \beta = 1$), indicating constant returns to scale.
-
-As shown in Equation \ref{eq:CD} above, neoclassical economic theory neglects the role of energy input to the economy.
-However, \citet{Bashmakov:2007ek} and \citet{Murphy:2011jh} indicate that the influence of energy on economic growth may far outweigh its cost share in the economy.
-That neoclassical economic growth theory ignores energy is, therefore, cause for concern, and an inquiry into the proper approach for including energy as a factor of production in economic growth modeling is both relevant and important.
-
-Some energy economists augment economic growth models with energy as an additional (or the only) factor of production.
-However, there is little agreement on how this should be done.
-Neither the mathematical form of the production function (Cobb-Douglas, CD; Constant Elasticity of Substitution, CES; or Linear Exponential, LINEX) nor which quantification of energy should be included (thermal energy, $q$; exergy, $x$; or useful work, $u$) are consistent in the literature.
-Furthermore, there has been little empirical work done to assess the predictive ability of energy-augmented production functions for different types of economies (e.g., developed, BRICS,\footnote{Brazil, China, India, South Africa} petrol, or developing).
-This paper attempts to contribute to the literature in these important areas.
+Typically, the constraint $\alpha + \beta = 1$ is assumed, indicating constant returns to scale.
+
+As shown in Equation \ref{eq:CD} above, neoclassical economic theory does not include an explicit term for the role of energy in economic growth.
+However, \citet{Bashmakov:2007ek} and \citet{Murphy:2011jh} indicate that the importance of energy may far outweigh its cost share in the economy.
+That neoclassical economic growth theory ignores energy is, therefore, cause for concern, and inquiry into the proper approach for including energy as a factor of production in economic growth modeling is both relevant and important.
+
+Some energy economists augment economic growth models with energy being an additional (or the only) factor of production.
+However, there is little agreement in the literature on how this should be done.
+Neither the mathematical form of the energy-augmented production function nor the quantification of energy are consistent in the literature.
+Furthermore, there has been little empirical work done to assess the predictive ability of energy-augmented production functions for different types of economies.
+In addition, very few studies of the importance of energy in economic growth include rigorous statistical assessments of energy-related parameters.
+This paper attempts to contribute to the literature with statistically rigorous methods along three coordinates of analysis: form of the energy augmented production function, energy quantification, and type of economy.
+
+\subsection{Mathematical Forms of the Energy-augmented Production Function}
+
+Three prominent energy-augmented production functions appear in the literature: Cobb-Douglas, CDe \citep{Ayres:2008cl}, Constant Elasticity of Substitution, CESe \citep{Stern:2012ey}, and LINear EXponential, LINEX \citep{Kummel:1980wx}.
+
+Similar to Equation \ref{eq:CD}, the energy-augmented Cobb-Douglas production function is
+
+\begin{equation} \label{eq:CDe}
+  y = A k^\alpha l^\beta e^\gamma; A = \mathrm{e}^{\lambda(t-t_0)}
+\end{equation}
+
+\noindent where $e \equiv E/E_0$, and $E$ is in units of energy per time.
+The energy-augmented Cobb-Douglas production function is often assumed to have constant returns to scale for the three factors of production: $\alpha + \beta + \gamma = 1$.
+
+\citet{Ayres:2008cl} uses Equation \ref{eq:CDe} with exergy ($x$) and useful work ($u$) energy quantifications to describe historic Japanese and American economies from 1900-2000.
+\citet{Froling:2009vo} uses an energy-augmented Cobb-Douglas production function with a thermal energy ($q$) to describe output for the global economy from 1800-1970.
+Fr\"{o}ling's model endogenizes labor with respect to fertility and mortality rates and separates thermal energy into two types: biomass energy and coal energy.
+\citet{Serrenho:2010vq} use the log transform of the energy-augmented Cobb-Douglas function with thermal energy quantification ($q$) to describe output for the EU-15 countries.
+Serrenho divides thermal energy into renewables, non-renewables, wastes, and imports.
 
 ************* Matt ended here. ****************
-
-\subsection{Mathematical Forms of the Production Function}
-
-Many energy-augmented production functions have been used to predict economic growth.
-Three prominent functions are the Cobb-Douglas production function with an energy input as used by (AYRES AND WARR, 2008), the Stern Constant Elasticity of Substitution (CES) production function (STERN, 2010), and K\"{u}mmel's Linear Exponential (LINEX) production function (KUMMEL, 1980).
-
-Similar to the Cobb-Douglas production function without an energy term, the Cobb-Douglas production function with energy (\textit{e}) includes constant returns to scale for the three factors of production.
-
-\begin{equation}
-  y_\mathrm{C-D} = A(t)k^\alpha l^\beta e^\gamma
-\end{equation}
-
-\begin{equation}
-  e \equiv E/E_\mathrm{0}
-\end{equation}
-
-\begin{equation}
-  \alpha + \beta + \gamma = 1
-\end{equation}
-
-(AYRES AND WARR, 2009) use this production function with useful work and exergy being the energy factors of production to descrive historic Japanese and American economies from 1900-2000.
-(FROLING, 2009) also uses a Cobb-Douglas production function with a thermal energy input to describe output for the global economy from 1800-1970.
-Fr\"{o}ling's Cobb-Douglas production function endogenizes labor with respect to fertility and mortality rates and separates the thermal energy factor of production into two types: biomass energy and coal energy.
-(SERRENHO, 2010) uses the Cobb-Douglas derivative with a thermal energy factor of production to describe output for the EU-15 countries.
-Serrenho divides the thermal energy factor into energy consumption from renewables, non-renewables, wastes, and imports.
 
@@
 \subsection{Quantification of Energy}
+
 The literature shows three types of energy used in production functions: thermal energy, exergy, and useful work.

### 2013-04-24 EconGrowth.Rnw
Editing the LINEX section of the paper.

@@
 
-Three prominent energy-augmented production functions appear in the literature: Cobb-Douglas, CDe \citep{Ayres:2008cl}, Constant Elasticity of Substitution, CESe \citep{Stern:2012ey}, and LINear EXponential, LINEX \citep{Kummel:1980wx}.
+Three prominent energy-augmented production functions appear in the literature: Cobb-Douglas (CDe), Constant Elasticity of Substitution (CESe), and LINear EXponential (LINEX).
+
+\subsubsection{Energy-augmented Cobb-Douglas Production Function (CDe)}
 
@@
 
+**************** Martin: add more here about the conclusions of each paper regarding the role of energy in economic growth?
+Especially, are there any confidence interals or statistical evaluation in each of these studies?
+********************
+
+\subsubsection{Energy-augmented CES Production Function (CESe)}
+
+Other energy economists use an energy-augmented Constant Elasticity of Substitution (CESe) production function to describe economic growth.
+The \texttt{R} \citep{R} package \texttt{micEconCES} \citep{Henningsen:2011td} estimates CES production functions of the form (among others)
+
+\begin{equation} \label{eq:CESe}
+  y = \gamma \: A \: \left\{\delta \left[\delta_1 k^{-\rho_1} + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1} + (1-\delta) e^{-\rho} \right\}^{-1/\rho}; A = \mathrm{e}^{\lambda (t-t_0)}
+\end{equation}
+
+\noindent where the elasticity of substitution between capital ($k$) and labor ($l$) is given by $\sigma_1 = \frac{1}{1+\rho_1}$, the elasticity of substitution between ($kl$) and ($e$) is given by $\sigma = \frac{1}{1+\rho}$, $\delta$ describes the importance of ($kl$) relative to ($e$), and $\gamma$ is a fitting parameter, expected to be close to unity.
+
+\citet{VanderWerf:2008tc} evalutes various nested CES production functions for 12 OECD countries with respect to climate change policy.
+van der Werf concludes that ($kl$)($e$) nesting structure (capital and labor combined, then energy added) best fits the historic data.
+******** Any confidence intervals in this study?
+********* \citet{Lecca:2011kr} also evaluate a variety of CES production functions using a KLEM structure to determine how the energy factor of production's location affects results stability.
+\citet{Stern:2012ey} use a CES production function of the form ($kl$)($e$) that has a Cobb-Douglas production function embedded within the CES production function as shown below.
+
+\begin{equation} \label{eq:CES_Stern}
+  y = \left\{ (1-\gamma_E)^{1/\sigma} \left[ k^{\alpha} \left( \mathrm{e}^{\lambda_L(t-t_0)} l \right)^{\beta} \right]^{\frac{\sigma-1}{\sigma}}   
+      + (\gamma_E)^{1/\sigma} \left[ \mathrm{e}^{\lambda_E(t-t_0)} e \right]^{\frac{\sigma - 1}{\sigma}}   \right\}
+      ^{\frac{\sigma}{\sigma - 1}}
+\end{equation}
+
+\citeauthor{Stern:2012ey} apply their CES function to the Swedish economy from 1800-2000 and demonstrate the importance of the transition from wood to fossil fuels for economic growth.
+
+\subsubsection{LINEX Production Function}
+
+A third production function often cited in the literature is the LINear EXponential (LINEX) function \citep{Kummel:1980wx,Kummel:1982vy,Kummel:1985vz,Kummel:1989tf,Kummel:2002tx,Kummel:2010vz}:
+
+\begin{equation} \label{eq:LINEX}
+  y = Ae; A = \mathrm{e}^{a_0\left[2 \left(1 - \frac{1}{\rho_k} \right) + c_t \left(\rho_l - 1 \right)\right]},
+\end{equation}
+
+\noindent where $e$ is indexed energy and e is the base of the natural logarithm.
+The LINEX model assumes energy ($e$) is the only factor of production.
+$\rho_k \equiv \frac{k}{(1/2)(l+e)}$ and represents the rate at which capital stock increases relative to the average of labor and energy.
+$\rho_l \equiv \frac{l}{e}$ and represents the rate at which labor ($l$) increases relative to energy ($e$).
+Energy ($e$) as a factor of production is enhanced by $A$ if either
+
+\begin{itemize}
+\item{capital stock ($k$) increases faster than the average of energy ($e$) and labor ($l$), i.e. if $\rho_k >$ 1, or}
+\item{labor ($l$) increases faster than energy ($e$), i.e. if $\rho_l >$ 1.}
+\end{itemize}
+
+\noindent According to the LINEX model, an economy that can increase capital stock without a commensurate increase in labor and energy will experience increasing output.
+Similarly, an economy benefits by increasing labor without a commensurate increase in energy.
+Thus, $\rho_k$ is a kind of efficiency of using labor and energy to make capital available to the economy, and $\rho_l$ is a kind of efficiency of using energy to make labor available to the economy.
+The parameter $a_0$ represents the overall importance of these efficiencies, and $c_t$ represents the relative importance of the labor efficiency compared to the capital stock efficiency.
+
 ************* Matt ended here. ****************
-
-Other energy economists use the Constant Elasticity of Substitution (CES) production function to describe economic growth with an energy factor of production.
-(VAN DER WERF, 2007) models various nested CES production functions for 12 OECD (Organisation for Economic Co-operating and Development) countries with respect to climate change policy.
-van der Werf concludes that (KL)E nesting structure (capital and labor combined, then energy added) best fits the historic data.
-(LECCA, 2011) also models a variety of CES production functions using a KLEM structure to determine how the energy factor of production's location affects results stability.
-(STERN, 2011) uses a CES production function that has a Cobb-Douglas production function embedded into the CES production function, following the (KL)E format.
-
-\begin{equation}
-  y_\mathrm{CES} = \bigg{[} (1-\zeta)(A_\mathrm{L} l^\beta k^{1-\beta})^\phi + \zeta(A_\mathrm{E} e)^\phi \bigg{]} ^\frac{1}{\phi}
-\end{equation}
-
-\begin{equation}
-  \phi = \frac{\sigma-1}{\sigma}
-\end{equation}
-
-Where $A_\mathrm{L}$ is the augmentation indice for labor and capital, $A_\mathrm{E}$ is the augmentation indice for energy, $\sigma$ is the elasticity of substitution between energy and value added aggregate, and $\zeta$ is the relative importance of labor/capital and energy.
-The elasticity of substitution between the capital and labor term and the energy term is less than unity, reflecting a minimum energy requirement for economic output.
-Stern applies his CES function to the Swedish economy from 1800-2000, which reflects the significance in the transfer from wood to more energy-intensive fossil fuel sources in promoting economic growth.
-
-The final production function chosen for our comparison was the (KUMMEL, 1980, 1985, 2002) LINEX production function.
-
-\begin{equation}
-  y_\mathrm{LINEX} = e \textrm{exp} \bigg{[} a_\mathrm{0} \bigg{(} 2-\frac{l+e}{k} \bigg{)} + a_\mathrm{0} c_\mathrm{t} \bigg{(} \frac{l}{e} - 1 \bigg{)} \bigg{]}
-\end{equation}
-
-\begin{equation}
-  a = a_\mathrm{0} \frac{l + e}{k}
-\end{equation}
-
-\begin{equation}
-  \beta = a_\mathrm{0} \bigg{(} c_\mathrm{t} \frac{l}{e} - \frac{l}{k} \bigg{)}
-\end{equation}
-
-\begin{equation}
-  \gamma = 1 - \frac{a_\mathrm{0} e}{k} - a_\mathrm{0} c_\mathrm{t} \frac{l}{e}
-\end{equation}
 

### 2013-04-25 EconGrowth.Rnw
Edits for the introductory text of the paper, including many new references.

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
+\section{Introduction} \label{sec:Introduction}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Neoclassical economic growth theory attributes output ($Y$) to factors of production: capital stock ($K$) and labor ($L$).
-The Cobb-Douglas production function is the canonical representation of indexed economic output ($y$) as a function of indexed labor ($l$), indexed capital stock ($k$), and an exogenous, time-dependent technological progress term ($\mathrm{e}^{\lambda(t-t_0)}$):
+The Cobb-Douglas production function is the canonical representation of indexed economic output ($y$) as a function of indexed labor ($l$), indexed capital stock ($k$), and an exogenous, time-dependent technological progress term ($A$):
 
@@
 
-\noindent where $y \equiv Y/Y_\mathrm{0}$, $k \equiv K/K_\mathrm{0}$, and $l \equiv L/L_\mathrm{0}$; with $Y$ represented by GDP, $K$ expressed in currency units, $L$ expressed in workers/year or work-hours/year, e being the base of the natural logarithm, and subscripts ``0'' indicating values at an initial year.
-Time ($t$) is measured in years, $A$ is a technological progress term with $\lambda$ indicating the pace of technological progress (in units of year$^{-1}$).
-Neoclassical economic growth theory makes no attempt to understand the mechanisms by which technological progress affects economic growth, nor does it attempt to describe how technological progress might vary from one economy to the next.
-Mathematically, technological progress is a fitting parameter that aligns the predictions of Equation \ref{eq:CD} with historical data.
+\noindent where $y \equiv Y/Y_\mathrm{0}$, $k \equiv K/K_\mathrm{0}$, and $l \equiv L/L_\mathrm{0}$; with $Y$ represented by GDP, $K$ expressed in currency units, $L$ expressed in workers/year or work-hours/year, time ($t$) measured in years, e being the base of the natural logarithm, and subscripts ``0'' indicating values at an initial year.
+$A$ is a technological progress term, with $\lambda$ indicating the pace of technological progress (in units of year$^{-1}$).
+Neoclassical economic growth theory makes no attempt to understand the mechanisms by which technological progress ($A$) affects economic growth, nor does it attempt to describe how technological progress ($A$) might vary from one economy to the next.
+Mathematically, $A$ is a fitting parameter that aligns the predictions of Equation \ref{eq:CD} with historical data.
 Typically, the constraint $\alpha + \beta = 1$ is assumed, indicating constant returns to scale.
@@
 In addition, very few studies of the importance of energy in economic growth include rigorous statistical assessments of energy-related parameters.
-This paper attempts to contribute to the literature with statistically rigorous methods along three coordinates of analysis: form of the energy augmented production function, energy quantification, and type of economy.
-
-\subsection{Mathematical Forms of the Energy-augmented Production Function}
+This paper attempts to contribute to the literature by applying statistically rigorous methods along three coordinates of analysis: form of the energy augmented production function, energy quantification, and type of economy.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Coordinates of Analysis} \label{sec:Coordinates}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+This section describes the three coordinates of analysis and reviews studies in the literature related to each.
+
+%++++++++++++++++++++++++++++++
+\subsection{Mathematical Forms of the Energy-augmented Production Function} \label{sec:Prod_Func_Forms}
+%++++++++++++++++++++++++++++++
 
 Three prominent energy-augmented production functions appear in the literature: Cobb-Douglas (CDe), Constant Elasticity of Substitution (CESe), and LINear EXponential (LINEX).
-
+In this paper, we assess all three, and the following sections describe each.
+
+%------------------------------
 \subsubsection{Energy-augmented Cobb-Douglas Production Function (CDe)}
+%------------------------------
 
@@
 \citet{Ayres:2008cl} uses Equation \ref{eq:CDe} with exergy ($x$) and useful work ($u$) energy quantifications to describe historic Japanese and American economies from 1900-2000.
-\citet{Froling:2009vo} uses an energy-augmented Cobb-Douglas production function with a thermal energy ($q$) to describe output for the global economy from 1800-1970.
+\citet{Froling:2009vo} uses an energy-augmented Cobb-Douglas production function with thermal energy quantification ($q$) to describe output for the global economy from 1800-1970.
 Fr\"{o}ling's model endogenizes labor with respect to fertility and mortality rates and separates thermal energy into two types: biomass energy and coal energy.
@@
 **************** Martin: add more here about the conclusions of each paper regarding the role of energy in economic growth?
-Especially, are there any confidence interals or statistical evaluation in each of these studies?
+Especially, are there any confidence intervals or statistical evaluation in each of these studies?
 ********************
 
+%------------------------------
 \subsubsection{Energy-augmented CES Production Function (CESe)}
+%------------------------------
 
@@
 \citet{VanderWerf:2008tc} evalutes various nested CES production functions for 12 OECD countries with respect to climate change policy.
-van der Werf concludes that ($kl$)($e$) nesting structure (capital and labor combined, then energy added) best fits the historic data.
+\citeauthor{VanderWerf:2008tc} concludes that ($kl$)($e$) nesting structure best fits historical data.
 ******** Any confidence intervals in this study?
-********* \citet{Lecca:2011kr} also evaluate a variety of CES production functions using a KLEM structure to determine how the energy factor of production's location affects results stability.
-\citet{Stern:2012ey} use a CES production function of the form ($kl$)($e$) that has a Cobb-Douglas production function embedded within the CES production function as shown below.
-
-\begin{equation} \label{eq:CES_Stern}
-  y = \left\{ (1-\gamma_E)^{1/\sigma} \left[ k^{\alpha} \left( \mathrm{e}^{\lambda_L(t-t_0)} l \right)^{\beta} \right]^{\frac{\sigma-1}{\sigma}}   
-      + (\gamma_E)^{1/\sigma} \left[ \mathrm{e}^{\lambda_E(t-t_0)} e \right]^{\frac{\sigma - 1}{\sigma}}   \right\}
-      ^{\frac{\sigma}{\sigma - 1}}
-\end{equation}
-
+********* \citet{Lecca:2011kr} also evaluate a variety of CES production functions using a KLEM structure to determine how the various options for nesting the energy factor of production affect predictive ability.
+\citet{Stern:2012ey} also use a CES production function of the form ($kl$)($e$).
 \citeauthor{Stern:2012ey} apply their CES function to the Swedish economy from 1800-2000 and demonstrate the importance of the transition from wood to fossil fuels for economic growth.
 
+%------------------------------
 \subsubsection{LINEX Production Function}
+%------------------------------
 
@@
 
-\noindent According to the LINEX model, an economy that can increase capital stock without a commensurate increase in labor and energy will experience increasing output.
-Similarly, an economy benefits by increasing labor without a commensurate increase in energy.
-Thus, $\rho_k$ is a kind of efficiency of using labor and energy to make capital available to the economy, and $\rho_l$ is a kind of efficiency of using energy to make labor available to the economy.
-The parameter $a_0$ represents the overall importance of these efficiencies, and $c_t$ represents the relative importance of the labor efficiency compared to the capital stock efficiency.
-
-************* Matt ended here. ****************
-
-Where $a_\mathrm{0}$ is a parameter representing capital efficiency and $c_\mathrm{t}$ is a parameter representing energy demand.
-(KUMMEL, 1980) inserted an energy factor of production into the Cobb-Douglas derivative, then assumed constant elasticity for the energy, labor, and capital factors of production.
-(KUMMEL, 1985) then partially integrated the Cobb-Douglas derivative to form the LINEX production function.
-K\"{u}mmel uses his LINEX production function to describe economic output for the economies of the U.S., Japan, and Germany (KUMMEL, 2002).
-(AYRES AND WARR, 2010) compare the LINEX production function with the Cobb-Douglas production function to assess economic growth for Austria, the United Kingdom, the United States, and Japan.
-
+\noindent According to the LINEX model, an economy that can increase capital stock ($k$) without a commensurate increase in labor ($l$) and energy ($e$) will experience an increase in output ($y$) in excess of its increase of energy consumption ($e$).
+Similarly, an economy benefits by increasing labor ($l$) without a commensurate increase in energy ($e$).
+Thus, $\rho_k$ is an efficiency of using labor and energy to make capital available to the economy, and $\rho_l$ is an efficiency of using energy to make labor available to the economy.
+The parameter $a_0$ represents the overall importance of these efficiencies, and $c_t$ represents the relative importance of the labor efficiency term compared to the capital stock efficiency term.
+In contrast to the Cobb-Douglas model (Equations \ref{eq:CD} and \ref{eq:CDe}) and the CES model (Equation \ref{eq:CESe}), the LINEX model (Equation \ref{eq:LINEX}) accounts for efficiencies directly and, therefore, does not employ a time-dependent technical progress term.
+\citet{Kummel:2002tx} use the LINEX production function to describe economic output for the economies of the U.S., Japan, and Germany.
+\citet{Warr:2010ga} compare the LINEX production function with the Cobb-Douglas production function to assess economic growth for Austria, the United Kingdom, the United States, and Japan.
+
+**************** Martin: More on the conclusions of the papers above. ***************
+
+%++++++++++++++++++++++++++++++
 \subsection{Quantification of Energy}
-
-The literature shows three types of energy used in production functions: thermal energy, exergy, and useful work.
-Thermal energy ($e$) is the heat content of an energy carrier.
+%++++++++++++++++++++++++++++++
+
+The literature shows three quantifications of energy ($e$) used in production functions: thermal energy ($q$), exergy ($x$), and useful work ($u$).
+Thermal energy ($q$) is the heat content of an energy carrier.
 Exergy ($x$) is the maximum useful work that can be extracted from an energy carrier by a process that brings the system into equilibrium with a heat reservoir (typically the surrounding environment).
 Useful work ($u$) includes the direct energy that goes into an economy, including work from machines, human muscles, and animals.
-Most energy economists have used thermal energy for the energy factor of production in the production function, including (STERN, 2011), (FROLING, 2009), (SERRENHO, 2010), and (KUMMEL, 1980, 1985, 2002).
-(AYRES AND WARR, 2009) introduced the idea of using exergy and useful work in a production function in order to include the importance of efficiency gains in energy production over the last century.
-Little work has been done comparing the predictive ability of each type of energy quantification in production functions.
-
-%Figure 2 goes here.
-
-(ADD FIG REF) exemplifies the importance of the quantification of energy's effect on growth modeling.
-The indexed values of $e$, $x$, and $u$ have very different growth rates.
-In particular, $u$ grows faster than either $e$ or $x$ due to efficiency gains in economies.
-The quantification of energy as $u$ suggests that perhaps technological progress $A(t)$ is a proxy for increasing energy efficiency in the U.S.
-economy.
-
+Most energy economists have used thermal energy ($q$) for the energy factor of production ($e$) in energy-augmented production functions, including \citet{Stern:2012ey}, \citet{Froling:2009vo}, \citet{Serrenho:2010vq}, and \citet{Kummel:1980wx,Kummel:1982vy,Kummel:1985vz,Kummel:1989tf,Kummel:2002tx,Kummel:2010vz}.
+\citet{Warr:2010ga} introduced the idea of using exergy ($x$) and useful work ($u$) in a production function to account for efficiency gains in energy production and consumption over the last century.
+We know of no statistically-rigorous comparisons of the predictive ability of each type of energy quantification in the various types of production functions discussed in Section \ref{sec:Prod_Func_Forms}.
+
+%++++++++++++++++++++++++++++++
 \subsection{Economy Types}
-
-In most economic growth literature, economists assess developed economies primarily from North America or Europe.
-Examples of developed economies being assessed include (KUMMEL, 1980) applying LINEX to describe the West German economy, (SERRENHO, 2010) applying Cobb-Douglas variants to EU-15 countries, (VAN DER WERF, 2007) applying CES nesting variants to the 12 OECD countries, (LECCA, 2011) applying CES nesting variants to the Scottish economy, (STERN, 2011) applying CES to describe the Swedish economy, and (AYRES AND WARR, 2010) using LINEX and Cobb-Douglas to describe the Austrian, American, British, and Japanese economies.
-There is a need to evaluate economies at all stages of growth.
-
-%Table 1 goes here.
+%++++++++++++++++++++++++++++++
+
+In most energy-economic growth literature, economists assess developed economies from North America or Europe.
+Examples include \citet{Kummel:1980wx} applying LINEX to describe the West German economy, \citet{Serrenho:2010vq} applying Cobb-Douglas variants to EU-15 countries, \citet{VanderWerf:2008tc} applying CES nesting variants to the 12 OECD countries, \citet{Lecca:2011kr} applying CES nesting variants to the Scottish economy, \citet{Stern:2012ey} applying CES to describe the Swedish economy, and \citet{Warr:2012cg} using LINEX and Cobb-Douglas to describe the Austrian, American, British, and Japanese economies.
+
+************* Matt ended here. ****************
+
+In this paper, we evaluate
 
@@
 
+%++++++++++++++++++++++++++++++
 \subsection{Production function selection}
+%++++++++++++++++++++++++++++++
+
 The production functions chosen for comparison were the Cobb-Douglas production function, the CES production function, and the LINEX production function.
@@
 
+%++++++++++++++++++++++++++++++
 \subsection{Country and economy type selection}
+%++++++++++++++++++++++++++++++
+
 In this paper we analyze economies at all stages of economic growth.
@@
 \section{Data sources and data collection}
+
+%++++++++++++++++++++++++++++++
 \subsection{Output}
+%++++++++++++++++++++++++++++++
+
 We take real gross domestic product to be an appropriate, if imperfect proxy for output.
@@
 
+%++++++++++++++++++++++++++++++
 \subsection{Capital stock}
+%++++++++++++++++++++++++++++++
+
 Gross capital stock for the United States, the United Kingdom, and Japan for 1980-2011 in real 2005 U.S.
@@
 
+%++++++++++++++++++++++++++++++
 \subsection{Labor and employment}
+%++++++++++++++++++++++++++++++
+
 Total employment and average hours worked per year per worker for the United States, the United Kingdom, and Japan for 1980-2011 is from the United States Bureau of Labor Statistics (BLS, 2011).
@@
 
+%++++++++++++++++++++++++++++++
 \subsection{Thermal energy, exergy, and useful work}
+%++++++++++++++++++++++++++++++
+
 We were interested in how the three different types of energy (thermal energy, exergy, and useful work) would affect our econometric growth modeling.
@@
 
+%++++++++++++++++++++++++++++++
 \subsubsection{Thermal energy}
-
-Thermal energy ($e$) is evaluated in TJ/year for the production functions. In the case of fuels, thermal energy was calculated using equation \ref{eq:thermal_energy}.
+%++++++++++++++++++++++++++++++
+
+Thermal energy ($q$) is evaluated in TJ/year for the production functions. In the case of fuels, thermal energy was calculated using equation \ref{eq:thermal_energy}.
 
@@
 
+%++++++++++++++++++++++++++++++
 \subsubsection{Exergy}
+%++++++++++++++++++++++++++++++
 
@@
 
+%------------------------------
 \subsubsection{Useful work}
+%------------------------------
+
 Useful work is a concept first developed by (AYRES AND WARR, 2005).
@@
 
-Figure \ref{fig:Historical_Lattice_Graph} shows historical data, including GDP ($y$), capital stock ($k$), labor ($l$), and the various energy types ($q$, $x$, and $u$).
+Figure \ref{fig:Historical_Lattice_Graph} shows historical data, including GDP ($y$), capital stock ($k$), labor ($l$), and the various energy quantifications ($q$, $x$, and $u$) for 1980-2011 (developed economies) and 1991-2011 (other economies).
 Factors of production track each other closely, and large covariances among these variables can be seen in Tables \ref{tab:Covariance_US} through \ref{tab:Covariance_ZM}.
 
-<<Historical_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="Historical data: Indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$).">>=
+<<Historical_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="Historical data: Indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$).", eval=TRUE>>=
 createHistoricalLatticeGraph()
 @
+
+Figure \ref{fig:Historical_Lattice_Graph} indicates the importance of energy quantification for economic growth modeling.
+Thermal energy ($q$) and exergy ($x$) grow at similar rates, unless there is a significant raw energy carrier substitution (such as China's substitution of ***** for ***** over the last 2 decades).
+The growth rate of $u$ is significantly different from $q$ and $x$, however.
+\citet{Warr:2012cg} show that from 1950-1990, useful work ($u$) grew much faster than $q$, $x$, $k$, or $l$ due to efficiency gains in the U.S.
+economy.
+The results of \citeauthor{Warr:2012cg} suggest that the time-dependent technological progress term ($A$) in the Cobb-Douglas and CES production functions (Equations \ref{eq:CD}, \ref{eq:CDe}, and \ref{eq:CESe}) may be a proxy for increasing energy efficiency in the U.S.
+economy.
 

### 2013-04-25 EconGrowth.Rnw
Now including years of analysis in the countries table.

@@
 \usepackage{amsmath} %Allows \begin{equation*} \end{equation*} for unnumbered equations
+\usepackage{multirow} % To create multirow tables.
 
@@
 
-The literature shows three quantifications of energy ($e$) used in production functions: thermal energy ($q$), exergy ($x$), and useful work ($u$).
+The literature shows three quantifications of energy ($e$) used in energy-augmented production functions: thermal energy ($q$), exergy ($x$), and useful work ($u$).
 Thermal energy ($q$) is the heat content of an energy carrier.
@@
 
+In this paper, we evaluate example economies from four significant groups: Developed, BRICS, Petrol, and LDCs.\footnote{Lesser-Developed Countries}
+
+In this paper we analyze at least two economies from each of the following categories: developed economies (technologically advanced with high standards of living), BRICS\footnote{Brazil, Russia, India, China, and South Africa} economies (rapid economic growth with standards of living below the developed economies), petrol economies (petroleum is a substantial source of GDP); and LDCs\footnote{Lesser Developed Countries} (living standards near subsistence levels).
+Table \ref{tab:Economy_Types} shows the example countries, their ISO 3166-1 alpha-2 codes, and the years of analysis for each economy.
+
+\begin{table} \caption{Economy types and examples evaluated in this paper.} \label{tab:Economy_Types} 
+  \begin{center}
+    \begin{tabular}{r c c l l} 
+      \multirow{3}{*}{Developed} & \includegraphics[height=0.11in]{flag/flag_US.png} & US & USA & \multirow{3}{*}{1980-2011}\\
+                                 & \includegraphics[height=0.11in]{flag/flag_UK.png} & UK & United Kingdom & \\
+                                 & \includegraphics[height=0.11in]{flag/flag_JP.png} & JP & Japan          & \\
+      \hline
+      \multirow{2}{*}{BRICS}     & \includegraphics[height=0.11in]{flag/flag_CN.png} & CN & China & \multirow{2}{*}{1990-2011}        \\
+                                 & \includegraphics[height=0.11in]{flag/flag_ZA.png} & ZA & South Africa & \\
+      \hline
+      \multirow{2}{*}{Petrol}    & \includegraphics[height=0.11in]{flag/flag_SA.png} & SA & Saudi Arabia & \multirow{2}{*}{1990-2011} \\
+                                 & \includegraphics[height=0.11in]{flag/flag_IR.png} & IR & Iran         &  \\
+      \hline
+      \multirow{2}{*}{LDC}       & \includegraphics[height=0.11in]{flag/flag_TZ.png} & TZ & Tanzania & \multirow{2}{*}{1990-2011}     \\
+                                 & \includegraphics[height=0.11in]{flag/flag_ZM.png} & ZM & Zambia      & \\
+    \end{tabular}
+  \end{center}
+\end{table}
+
 ************* Matt ended here. ****************
-
-In this paper, we evaluate
 
@@
 
-In this paper we analyze economies at all stages of economic growth.
-We selected at least two economies from each of the following categories: the developed economies, which are economies that are technologically advanced with high standards of living; developing economies, which experience rapid economic growth but are still subject to low standards of living; the petrol economies, which depend on petroleum as a substantial source of GDP; and the Malthusian economies, which maintain living standards near subsistence levels.
-We analyzed the developed economies of the United States, the United Kingdom, and Japan for the period 1980-2011.
-We analyze two developing economies for 1991-2011: South Africa and China.
-The petrol economies analyzed for 1991-2011 are Iran and Saudi Arabia.
-Finally, the Malthusian economies analyzed from 1991-2011 are Tanzania and Zambia.
-
 \section{Data sources and data collection}
@@
 
-<<Historical_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="Historical data: Indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$).", eval=TRUE>>=
+<<Historical_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="Historical data: Indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$).">>=
 createHistoricalLatticeGraph()

### 2013-04-25 EconGrowth.Rnw
Now finished editing the coordinates of anlaysis section.

@@
 
-Three prominent energy-augmented production functions appear in the literature: Cobb-Douglas (CDe), Constant Elasticity of Substitution (CESe), and LINear EXponential (LINEX).
-In this paper, we assess all three, and the following sections describe each.
+In this paper, we assess three prominent energy-augmented production functions appear in the literature: Cobb-Douglas (CDe), Constant Elasticity of Substitution (CESe), and LINear EXponential (LINEX).
+The following sections describe each.
 
@@
 Other energy economists use an energy-augmented Constant Elasticity of Substitution (CESe) production function to describe economic growth.
-The \texttt{R} \citep{R} package \texttt{micEconCES} \citep{Henningsen:2011td} estimates CES production functions of the form (among others)
+The \texttt{R} \citep{R} package \texttt{micEconCES} \citep{Henningsen:2011td} estimates CES production functions of the following forms (among others):
+
+\begin{equation} \label{eq:CES}
+  y = \gamma \: A \: \left[\delta_1 k^{-\rho_1} + (1-\delta_1)l^{-\rho_1} \right]^{-1/\rho_1}; A = \mathrm{e}^{\lambda (t-t_0)}
+\end{equation}
 
@@
 
-\noindent where the elasticity of substitution between capital ($k$) and labor ($l$) is given by $\sigma_1 = \frac{1}{1+\rho_1}$, the elasticity of substitution between ($kl$) and ($e$) is given by $\sigma = \frac{1}{1+\rho}$, $\delta$ describes the importance of ($kl$) relative to ($e$), and $\gamma$ is a fitting parameter, expected to be close to unity.
+\noindent where the elasticity of substitution between capital ($k$) and labor ($l$) is given by $\sigma_1 = \frac{1}{1+\rho_1}$, the elasticity of substitution between ($kl$) and ($e$) is given by $\sigma = \frac{1}{1+\rho}$, $\delta \in [0, 1]$ describes the importance of ($kl$) relative to ($e$), and $\gamma$ is a fitting parameter, expected to be close to unity.
+Equation \ref{eq:CESe} augments a standard CES production function (Equation \ref{eq:CES}) with energy using a ($kl$)($e$) nesting arrangement, as is typical in the literature.
+Equation \ref{eq:CES} is a degenerate form of Equation \ref{eq:CESe} where $\delta = 1$.
 
@@
 
-A third production function often cited in the literature is the LINear EXponential (LINEX) function \citep{Kummel:1980wx,Kummel:1982vy,Kummel:1985vz,Kummel:1989tf,Kummel:2002tx,Kummel:2010vz}:
+A third production function, the LINear EXponential (LINEX) function \citep{Kummel:1980wx,Kummel:1982vy,Kummel:1985vz,Kummel:1989tf,Kummel:2002tx,Kummel:2010vz}, was derived from thermodynamic considerations:
 
@@
 The parameter $a_0$ represents the overall importance of these efficiencies, and $c_t$ represents the relative importance of the labor efficiency term compared to the capital stock efficiency term.
-In contrast to the Cobb-Douglas model (Equations \ref{eq:CD} and \ref{eq:CDe}) and the CES model (Equation \ref{eq:CESe}), the LINEX model (Equation \ref{eq:LINEX}) accounts for efficiencies directly and, therefore, does not employ a time-dependent technical progress term.
+Both $a_0$ and $c_t$ are constant with respect to time.
+
+In contrast to the Cobb-Douglas model (Equations \ref{eq:CD} and \ref{eq:CDe}) and the CES model (Equations \ref{eq:CES} and \ref{eq:CESe}), the LINEX model (Equation \ref{eq:LINEX}) accounts for efficiencies among capital, labor, and energy directly and, therefore, does not employ a time-dependent technical progress term ($A$).
 \citet{Kummel:2002tx} use the LINEX production function to describe economic output for the economies of the U.S., Japan, and Germany.
@@
 
-**************** Martin: More on the conclusions of the papers above. ***************
+**************** Martin: More on the results of the above papers. ***************
 
@@
 \citet{Warr:2010ga} introduced the idea of using exergy ($x$) and useful work ($u$) in a production function to account for efficiency gains in energy production and consumption over the last century.
+
 We know of no statistically-rigorous comparisons of the predictive ability of each type of energy quantification in the various types of production functions discussed in Section \ref{sec:Prod_Func_Forms}.
+We analyze all three quantifications of energy ($q$, $x$, and $u$) for developed economies and thermal energy ($q$) and exergy ($x$) for all other economies.
 
@@
 
-In this paper, we evaluate example economies from four significant groups: Developed, BRICS, Petrol, and LDCs.\footnote{Lesser-Developed Countries}
-
-In this paper we analyze at least two economies from each of the following categories: developed economies (technologically advanced with high standards of living), BRICS\footnote{Brazil, Russia, India, China, and South Africa} economies (rapid economic growth with standards of living below the developed economies), petrol economies (petroleum is a substantial source of GDP); and LDCs\footnote{Lesser Developed Countries} (living standards near subsistence levels).
-Table \ref{tab:Economy_Types} shows the example countries, their ISO 3166-1 alpha-2 codes, and the years of analysis for each economy.
-
-\begin{table} \caption{Economy types and examples evaluated in this paper.} \label{tab:Economy_Types} 
+In this paper we analyze at least two economies from each of the following categories: developed (technologically advanced with high standards of living), BRICS\footnote{Brazil, Russia, India, China, and South Africa} (rapid economic growth with standards of living below that of developed economies), petrol (petroleum is a substantial source of GDP); and LDCs\footnote{Lesser Developed Countries} (living standards near subsistence levels).
+(See Table \ref{tab:Economy_Examples}.)
+
+\begin{table} \caption{Example economies and years of evaluation.} \label{tab:Economy_Examples} 
   \begin{center}
@@
 
-%++++++++++++++++++++++++++++++
-\subsection{Production function selection}
-%++++++++++++++++++++++++++++++
-
-The production functions chosen for comparison were the Cobb-Douglas production function, the CES production function, and the LINEX production function.
-These three production functions were all treated as exogenous, with inputs of capital, labor, and energy (or exergy in the case of this paper's analysis).
-All three of the production functions are derived from the fundamental growth equation.
-
-\begin{equation}
-  \frac{1}{y} \frac{dy}{dt} = \alpha \frac{1}{k} \frac{\partial k}{\partial t} + \beta \frac {1}{l} \frac{\partial l}{\partial t} + \gamma \frac{1}{e} \frac{\partial e}{\partial t}
-\end{equation}
-
-Integrating equation 1 with differing solutions of $\alpha$, $\beta$, and $\gamma$ yields the various production functions.
-In order to satisfy the condition of constant returns to scale, $\alpha + \beta +\gamma = 1$ in all cases.
-The bounds for the elasticities are: $0 \le \alpha \le 1$, $0 \le \beta \le 1$, and $0 \le \gamma \le 1$.
-
-The Cobb-Douglas production function was chosen because it is one of the most commonly used in econometric modeling.
-The Cobb-Douglas production function is the result of partially integrating equation 11 from ($y_\mathrm{0}$, 1, 1, 1) to ($y_\mathrm{final}$, k, l, e) and assuming trivial values of $\alpha$, $\beta$, and $\gamma$ ($\alpha_\mathrm{0}$, $\beta_\mathrm{0}$, $\gamma_\mathrm{0}$).
-The Cobb-Douglas function is most commonly written as a function of capital and labor.
-A modified form can also be used where energy is a third term.
-The technological progress term, $A(t)$, is a multiplier representing total factor productivity; to account for some portion of the output that is only dependent on time and unaccounted for by labor and capital.
-The other production functions were compared to the basic Cobb-Douglas function to gain an understanding of how energy is intertwined with capital and labor.
-A modified version of the Cobb-Douglas with energy was also modeled to see how adaptive the function is and to examine if the total factor productivity term could be partially explained by energy.
-
-The CES production functions are a family of production functions that are starting to become more widely used in economic modeling.
-(MISHRA, 2007) covers a wide variety of production functions that are members of the CES family.
-The CES form that we chose to use is from (STERN, 2011, 2012), which embeds a Cobb-Douglas function in a CES function (see equation 8).
-Since Stern's function is embedded with a Cobb-Douglas function, it reduces to the standard Cobb-Douglas form as $\sigma \rightarrow 1$ and $\gamma \rightarrow 0$.
-
-The LINEX production function was chosen because it approaches growth from a perspective that combines elements of thermodynamics and economics (see equation 10).
-The form of the LINEX function being used is taken from (KUMMEL, 1980, 1985, 2002), with a linear dependence on energy and an exponential dependence on capital and labor.
-The LINEX function is a result of using the simplest non-trivial solutions of $\alpha$, $\beta$, and $\gamma$ (see equation 11, 12, and 13).
-The variables $a_\mathrm{0}$ and $c_\mathrm{t}$ are constant over a given period of time.
-The greatest advantage of the LINEX function is the time dependent output elasticities.
-It seems more plausible that these values would change over time as a country nears the demographic transition and shifts from using physical labor to more energy for industrialization.
-
-The combination of these four types of production functions (Cobb-Douglas, Cobb-Douglas with energy, LINEX, and Stern-CES) allowed us to get a sense of the true effects of energy on economic growth modeling.
-
-%++++++++++++++++++++++++++++++
-\subsection{Country and economy type selection}
-%++++++++++++++++++++++++++++++
-
 \section{Data sources and data collection}

### 2013-04-25 EconGrowth.Rnw
Additional editing changes.

@@
 
-\noindent where $y \equiv Y/Y_\mathrm{0}$, $k \equiv K/K_\mathrm{0}$, and $l \equiv L/L_\mathrm{0}$; with $Y$ represented by GDP, $K$ expressed in currency units, $L$ expressed in workers/year or work-hours/year, time ($t$) measured in years, e being the base of the natural logarithm, and subscripts ``0'' indicating values at an initial year.
-$A$ is a technological progress term, with $\lambda$ indicating the pace of technological progress (in units of year$^{-1}$).
+\noindent where $y \equiv Y/Y_\mathrm{0}$, $k \equiv K/K_\mathrm{0}$, and $l \equiv L/L_\mathrm{0}$; with $Y$ represented by GDP, $K$ expressed in currency units, $L$ expressed in workers/year or work-hours/year, time ($t$) measured in years, e being the base of the natural logarithm, and subscripts ``0'' indicating values at an initial year.\footnote{Indexed quantities are represented by lower-case symbols ($y$, $k$, $l$, $e$, $q$, $x$, and $u$) and dimensional quantities are represented by upper-case symbols ($Y$, $K$, $L$, $E$, $Q$, $X$, and $U$).} $A$ is a technological progress term, with $\lambda$ indicating the pace of technological progress (in units of year$^{-1}$).
 Neoclassical economic growth theory makes no attempt to understand the mechanisms by which technological progress ($A$) affects economic growth, nor does it attempt to describe how technological progress ($A$) might vary from one economy to the next.
@@
 
-This section describes the three coordinates of analysis and reviews studies in the literature related to each.
+This section describes the three coordinates of analysis and briefly reviews literature related to each.
 
@@
 %------------------------------
-\subsubsection{Energy-augmented Cobb-Douglas Production Function (CDe)}
+\subsubsection{Energy-augmented Cobb-Douglas Production Function (CDe)} \label{sec:CDe}
 %------------------------------
@@
 
-\citet{Ayres:2008cl} uses Equation \ref{eq:CDe} with exergy ($x$) and useful work ($u$) energy quantifications to describe historic Japanese and American economies from 1900-2000.
+\citet{Ayres:2008cl} uses Equation \ref{eq:CDe} with exergy ($x$) and useful work ($u$) quantifications for $e$ to describe historic Japanese and American economies from 1900-2000.
 \citet{Froling:2009vo} uses an energy-augmented Cobb-Douglas production function with thermal energy quantification ($q$) to describe output for the global economy from 1800-1970.
@@
 %------------------------------
-\subsubsection{Energy-augmented CES Production Function (CESe)}
+\subsubsection{Energy-augmented CES Production Function (CESe)} \label{sec:CES}
 %------------------------------
@@
 %------------------------------
-\subsubsection{LINEX Production Function}
+\subsubsection{LINEX Production Function} \label{sec:LINEX}
 %------------------------------
@@
 %++++++++++++++++++++++++++++++
-\subsection{Quantification of Energy}
-%++++++++++++++++++++++++++++++
-
-The literature shows three quantifications of energy ($e$) used in energy-augmented production functions: thermal energy ($q$), exergy ($x$), and useful work ($u$).
-Thermal energy ($q$) is the heat content of an energy carrier.
-Exergy ($x$) is the maximum useful work that can be extracted from an energy carrier by a process that brings the system into equilibrium with a heat reservoir (typically the surrounding environment).
-Useful work ($u$) includes the direct energy that goes into an economy, including work from machines, human muscles, and animals.
-Most energy economists have used thermal energy ($q$) for the energy factor of production ($e$) in energy-augmented production functions, including \citet{Stern:2012ey}, \citet{Froling:2009vo}, \citet{Serrenho:2010vq}, and \citet{Kummel:1980wx,Kummel:1982vy,Kummel:1985vz,Kummel:1989tf,Kummel:2002tx,Kummel:2010vz}.
-\citet{Warr:2010ga} introduced the idea of using exergy ($x$) and useful work ($u$) in a production function to account for efficiency gains in energy production and consumption over the last century.
+\subsection{Quantification of Energy} \label{sec:Quantification_Of_Energy}
+%++++++++++++++++++++++++++++++
+
+The literature shows three quantifications of energy ($E$) used in energy-augmented production functions: thermal energy ($Q$), exergy ($X$), and useful work ($U$).
+Thermal energy ($Q$) is the heat content of an energy carrier.
+Exergy ($X$) is the maximum useful work that can be extracted from an energy carrier by a process that brings the system into equilibrium with a heat reservoir (typically the surrounding environment).
+Useful work ($U$) includes the direct energy that goes into an economy, including work from machines, human muscles, and animals.
+Most energy economists have used thermal energy ($Q$) for the energy factor of production ($E$) in energy-augmented production functions, including \citet{Stern:2012ey}, \citet{Froling:2009vo}, \citet{Serrenho:2010vq}, and \citet{Kummel:1980wx,Kummel:1982vy,Kummel:1985vz,Kummel:1989tf,Kummel:2002tx,Kummel:2010vz}.
+\citet{Warr:2010ga} introduced the idea of using exergy ($X$) and useful work ($U$) in a production function to account for efficiency gains in energy production and consumption over the last century.
 
 We know of no statistically-rigorous comparisons of the predictive ability of each type of energy quantification in the various types of production functions discussed in Section \ref{sec:Prod_Func_Forms}.
-We analyze all three quantifications of energy ($q$, $x$, and $u$) for developed economies and thermal energy ($q$) and exergy ($x$) for all other economies.
-
-%++++++++++++++++++++++++++++++
-\subsection{Economy Types}
+We analyze all three quantifications of energy ($Q$, $X$, and $U$) for developed economies and thermal energy ($Q$) and exergy ($X$) for all other economies.
+
+%++++++++++++++++++++++++++++++
+\subsection{Economy Types} \label{sec:Economy_Types}
 %++++++++++++++++++++++++++++++
@@
       \hline
-      \multirow{2}{*}{BRICS}     & \includegraphics[height=0.11in]{flag/flag_CN.png} & CN & China & \multirow{2}{*}{1990-2011}        \\
+      \multirow{2}{*}{BRICS}     & \includegraphics[height=0.11in]{flag/flag_CN.png} & CN & China & \multirow{2}{*}{1991-2011}        \\
                                  & \includegraphics[height=0.11in]{flag/flag_ZA.png} & ZA & South Africa & \\
       \hline
-      \multirow{2}{*}{Petrol}    & \includegraphics[height=0.11in]{flag/flag_SA.png} & SA & Saudi Arabia & \multirow{2}{*}{1990-2011} \\
+      \multirow{2}{*}{Petrol}    & \includegraphics[height=0.11in]{flag/flag_SA.png} & SA & Saudi Arabia & \multirow{2}{*}{1991-2011} \\
                                  & \includegraphics[height=0.11in]{flag/flag_IR.png} & IR & Iran         &  \\
       \hline
-      \multirow{2}{*}{LDC}       & \includegraphics[height=0.11in]{flag/flag_TZ.png} & TZ & Tanzania & \multirow{2}{*}{1990-2011}     \\
+      \multirow{2}{*}{LDC}       & \includegraphics[height=0.11in]{flag/flag_TZ.png} & TZ & Tanzania & \multirow{2}{*}{1991-2011}     \\
                                  & \includegraphics[height=0.11in]{flag/flag_ZM.png} & ZM & Zambia      & \\
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Data Sources} \label{sec:Data_Sources}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+To assess energy-augmented models of economic growth along the coordinates of analysis outlined in Section \ref{sec:Coordinates}, historical data for economic output ($Y$), capital stock ($K$), labor ($L$), thermal energy ($Q$), exergy ($X$), and useful work ($U$) is required.
+Subsections below describe sources for and calculations to obtain historical data.
+A final subsection presents the data in graphical form.
+
 ************* Matt ended here. ****************
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Models and methodology}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Data sources and data collection}
-
-%++++++++++++++++++++++++++++++
-\subsection{Output}
-%++++++++++++++++++++++++++++++
-
-We take real gross domestic product to be an appropriate, if imperfect proxy for output.
-Real gross domestic product data in real 2005 U.S.
+%++++++++++++++++++++++++++++++
+\subsection{Output ($Y$)} \label{sec:Output_Data}
+%++++++++++++++++++++++++++++++
+
+We take real gross domestic product to be an appropriate, if imperfect, proxy for output ($Y$).
+Gross domestic product data in real 2005 U.S.
 dollars for the United States, the United Kingdom, and Japan for 1980-2011 is from the World Bank's Global Economic Prospects (GEP) database (WORLD BANK, 2012).
-Real GDP data in real 2005 U.S.
-dollars for South Africa, China, Iran, Saudi Arabia, Tanzania, and Zambia for 1991-2011is from the World Bank's Global Economic Prospects database (WORLD BANK, 2012).
-
-%++++++++++++++++++++++++++++++
-\subsection{Capital stock}
+GDP data in real 2005 U.S.
+dollars for South Africa, China, Iran, Saudi Arabia, Tanzania, and Zambia for 1991-2011 is from the World Bank's Global Economic Prospects database (WORLD BANK, 2012).
+
+%++++++++++++++++++++++++++++++
+\subsection{Capital stock ($K$)} \label{sec:Capital_Stock_Data}
 %++++++++++++++++++++++++++++++
@@
 %++++++++++++++++++++++++++++++
-\subsection{Labor and employment}
+\subsection{Labor and employment ($L$)} \label{sec:Labor_Data}
 %++++++++++++++++++++++++++++++
@@
 %++++++++++++++++++++++++++++++
-\subsection{Thermal energy, exergy, and useful work}
+\subsection{Thermal energy, exergy, and useful work ($E$)} \label{sec:Energy_Data}
 %++++++++++++++++++++++++++++++
@@
 
-%++++++++++++++++++++++++++++++
-\subsubsection{Thermal energy}
-%++++++++++++++++++++++++++++++
+%------------------------------
+\subsubsection{Thermal energy ($Q$)} \label{sec:Q_Data}
+%------------------------------
 
@@
 
-%++++++++++++++++++++++++++++++
-\subsubsection{Exergy}
-%++++++++++++++++++++++++++++++
+%------------------------------
+\subsubsection{Exergy ($X$)} \label{sec:X_Data}
+%------------------------------
 
@@
 %------------------------------
-\subsubsection{Useful work}
+\subsubsection{Useful work ($U$)} \label{sec:U_Data}
 %------------------------------
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Historical Data}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Figure \ref{fig:Historical_Lattice_Graph} shows historical data, including GDP ($y$), capital stock ($k$), labor ($l$), and the various energy quantifications ($q$, $x$, and $u$) for 1980-2011 (developed economies) and 1991-2011 (other economies).
+%++++++++++++++++++++++++++++++
+\subsection{Historical Data} \label{sec:Historical_Data}
+%++++++++++++++++++++++++++++++
+
+Figure \ref{fig:Historical_Lattice_Graph} presents historical data, including indexed values for output ($y$), capital stock ($k$), labor ($l$), and the various energy quantifications ($q$, $x$, and $u$) for 1980-2011 (developed economies) and 1991-2011 (other economies).
 Factors of production track each other closely, and large covariances among these variables can be seen in Tables \ref{tab:Covariance_US} through \ref{tab:Covariance_ZM}.

### 2013-04-26 EconGrowth.Rnw
Further edits on the data section. Also adding several additional papers to the bibliography file.

@@
 
-\usepackage{soul} %Provides strikethrough text
-\usepackage{float} %Allows precise positioning of tables and figures within the text
-\usepackage{amsmath} %Allows \begin{equation*} \end{equation*} for unnumbered equations
-\usepackage{multirow} % To create multirow tables.
+\usepackage{soul} % Provides strikethrough text
+\usepackage{float} % Allows precise positioning of tables and figures within the text
+\usepackage{amsmath} % Allows \begin{equation*} \end{equation*} for unnumbered equations
+\usepackage{multirow} % To create multirow tables
+\usepackage{hyperref} % To create hyperlinks in the paper
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction} \label{sec:Introduction}
+\section{Introduction} 
+\label{sec:Introduction}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Coordinates of Analysis} \label{sec:Coordinates}
+\section{Coordinates of Analysis} 
+\label{sec:Coordinates}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %------------------------------
-\subsubsection{Energy-augmented Cobb-Douglas Production Function (CDe)} \label{sec:CDe}
+\subsubsection{Energy-augmented Cobb-Douglas Production Function (CDe)} 
+\label{sec:CDe}
 %------------------------------
@@
 %------------------------------
-\subsubsection{Energy-augmented CES Production Function (CESe)} \label{sec:CES}
+\subsubsection{Energy-augmented CES Production Function (CESe)} 
+\label{sec:CES}
 %------------------------------
@@
 %------------------------------
-\subsubsection{LINEX Production Function} \label{sec:LINEX}
+\subsubsection{LINEX Production Function} 
+\label{sec:LINEX}
 %------------------------------
@@
 %++++++++++++++++++++++++++++++
-\subsection{Quantification of Energy} \label{sec:Quantification_Of_Energy}
+\subsection{Quantification of Energy} 
+\label{sec:Quantification_of_Energy}
 %++++++++++++++++++++++++++++++
@@
 %++++++++++++++++++++++++++++++
-\subsection{Economy Types} \label{sec:Economy_Types}
+\subsection{Economy Types} 
+\label{sec:Economy_Types}
 %++++++++++++++++++++++++++++++
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Data Sources} \label{sec:Data_Sources}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-To assess energy-augmented models of economic growth along the coordinates of analysis outlined in Section \ref{sec:Coordinates}, historical data for economic output ($Y$), capital stock ($K$), labor ($L$), thermal energy ($Q$), exergy ($X$), and useful work ($U$) is required.
+\section{Historical Data}
+\label{sec:Historical_Data}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+To assess energy-augmented models of economic growth along the coordinates of analysis outlined in Section \ref{sec:Coordinates}, historical data for economic output ($Y$), capital stock ($K$), labor ($L$), thermal energy ($Q$), exergy ($X$), and useful work ($U$) are required.
 Subsections below describe sources for and calculations to obtain historical data.
-A final subsection presents the data in graphical form.
-
-************* Matt ended here. ****************
-
-%++++++++++++++++++++++++++++++
-\subsection{Output ($Y$)} \label{sec:Output_Data}
-%++++++++++++++++++++++++++++++
-
-We take real gross domestic product to be an appropriate, if imperfect, proxy for output ($Y$).
-Gross domestic product data in real 2005 U.S.
-dollars for the United States, the United Kingdom, and Japan for 1980-2011 is from the World Bank's Global Economic Prospects (GEP) database (WORLD BANK, 2012).
+A final subsection presents the historical data in graphical form.
+
+%++++++++++++++++++++++++++++++
+\subsection{Output ($Y$)} 
+\label{sec:Output_Data}
+%++++++++++++++++++++++++++++++
+
+We measure economic output ($Y$) by real gross domestic product (GDP).
 GDP data in real 2005 U.S.
-dollars for South Africa, China, Iran, Saudi Arabia, Tanzania, and Zambia for 1991-2011 is from the World Bank's Global Economic Prospects database (WORLD BANK, 2012).
-
-%++++++++++++++++++++++++++++++
-\subsection{Capital stock ($K$)} \label{sec:Capital_Stock_Data}
-%++++++++++++++++++++++++++++++
-
-Gross capital stock for the United States, the United Kingdom, and Japan for 1980-2011 in real 2005 U.S.
-dollars is from the World Bank GEP database (WORLD BANK, 2012).
-Gross capital stock data in real 2005 U.S.
-dollars for South Africa, China, Iran, Saudi Arabia, Tanzania, and Zambia for 1991-2011 is from the World Bank GEP database (WORLD BANK, 2012).
-
-%++++++++++++++++++++++++++++++
-\subsection{Labor and employment ($L$)} \label{sec:Labor_Data}
-%++++++++++++++++++++++++++++++
-
-Total employment and average hours worked per year per worker for the United States, the United Kingdom, and Japan for 1980-2011 is from the United States Bureau of Labor Statistics (BLS, 2011).
-Total hours worked is calculated by multiplying total employment by average hours worked per worker.
-The World Bank's WDI database (WORLD BANK, 2012) provides an employment to population ratio of people fifteen and older, total population, and a percentage of people under fifteen for South Africa, China, Iran, Saudi Arabia, Tanzania, and Zambia for 1991-2011.
+dollars for developed countries (1980-2011) and all other countries (1991-2011) was obtained from the World Bank's Global Economic Prospects (GEP) database \citep{WorldBankGEP:2013a}.
+
+%++++++++++++++++++++++++++++++
+\subsection{Capital Stock ($K$)} 
+\label{sec:Capital_Stock_Data}
+%++++++++++++++++++++++++++++++
+
+Gross capital stock in real 2005 U.S.
+dollars for developed countries (1980-2011) and all other countries (1991-2011) was obtained from the World Bank's Global Economic Prospects (GEP) database \citep{WorldBankGEP:2013a}.
+
+%++++++++++++++++++++++++++++++
+\subsection{Labor and Employment ($L$)} 
+\label{sec:Labor_Data}
+%++++++++++++++++++++++++++++++
+
+Total employment and average hours worked per year per worker for the United States, the United Kingdom, and Japan for 1980-2011 was obtained from the United States \citet{BLS:2011a}.
+Total hours worked was calculated by multiplying total employment by average hours worked per worker.
+************* Matt ended here.
+**************** The World Bank's WDI database (WORLD BANK, 2012) provides an employment to population ratio of people fifteen and older, total population, and a percentage of people under fifteen for South Africa, China, Iran, Saudi Arabia, Tanzania, and Zambia for 1991-2011.
 The population of people fifteen and older was calculated by multiplying the percentage of people under fifteen by total population, and then subtracting this from the total population.
@@
 %++++++++++++++++++++++++++++++
-\subsection{Thermal energy, exergy, and useful work ($E$)} \label{sec:Energy_Data}
+\subsection{Thermal Energy, Exergy, and Useful Work ($E$)} 
+\label{sec:Energy_Data}
 %++++++++++++++++++++++++++++++
@@
 %------------------------------
-\subsubsection{Thermal energy ($Q$)} \label{sec:Q_Data}
+\subsubsection{Thermal Energy ($Q$)} 
+\label{sec:Q_Data}
 %------------------------------
@@
 %------------------------------
-\subsubsection{Exergy ($X$)} \label{sec:X_Data}
+\subsubsection{Exergy ($X$)} 
+\label{sec:X_Data}
 %------------------------------
@@
 %------------------------------
-\subsubsection{Useful work ($U$)} \label{sec:U_Data}
+\subsubsection{Useful Work ($U$)} 
+\label{sec:U_Data}
 %------------------------------
@@
 economy.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Single-factor Models (SF)}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-We begin by fitting single-factor economic models of the form
-
-\begin{equation} \label{eq:Single_Factor_Generic}
-  y = \mathrm{e}^{\lambda (t-t_0)}f^{m}
-\end{equation}
-
-\noindent to historical data where the factor of production ($f$) is one of $k$, $l$, $q$, $x$, or $u$, and the exponent ($m$) is $\alpha$ for $k$, $\beta$ for $l$, or $\gamma$ for $q$, $x$, and $u$.
-
-<<SFk_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $k$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createSFParamsGraph(factor="K")
-@
-
-<<SFl_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $l$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createSFParamsGraph(factor="L")
-@
-
-<<SFq_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $q$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createSFParamsGraph(factor="Q")
-@
-
-<<SFx_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $x$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createSFParamsGraph(factor="X")
-@
-
-<<SFu_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $u$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createSFParamsGraph(factor="U")
-@
-
-Figure \ref{fig:SF_GDP_Lattice_Graph} compares single-factor model predictions with historical data.
-
-<<SF_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="Single-factor results.">>=
-createSFLatticeGraph()
-@
 
@@
 Heun (Western Michigan University) for insightful critique of the statistical analyses presented herein.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Reproducible Research}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In the spirit of Reproducible Research \citep{Gandrud:2013vx}, all data, spreadsheets, \texttt{R} code \citep{R}, and other materials associated with this paper can be found at \url{https://github.com/MatthewHeun/Econ-Growth-R-Analysis}.
+
 %% The Appendices part is started with the command \appendix;
@@
 \section{Covariance Tables}
+\label{sec:Covariance_Tables}
 \setcounter{table}{0} % Restarts table number counter at 0 in this section.
@@
 \subsection{Single-factor Models}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Single-factor Models (SF)}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We begin by fitting single-factor economic models of the form
+
+\begin{equation} \label{eq:Single_Factor_Generic}
+  y = \mathrm{e}^{\lambda (t-t_0)}f^{m}
+\end{equation}
+
+\noindent to historical data where the factor of production ($f$) is one of $k$, $l$, $q$, $x$, or $u$, and the exponent ($m$) is $\alpha$ for $k$, $\beta$ for $l$, or $\gamma$ for $q$, $x$, and $u$.
+
+<<SFk_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $k$) model parameters.
+Vertical bars indicate 95\\% confidence intervals.">>=
+createSFParamsGraph(factor="K")
+@
+
+<<SFl_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $l$) model parameters.
+Vertical bars indicate 95\\% confidence intervals.">>=
+createSFParamsGraph(factor="L")
+@
+
+<<SFq_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $q$) model parameters.
+Vertical bars indicate 95\\% confidence intervals.">>=
+createSFParamsGraph(factor="Q")
+@
+
+<<SFx_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $x$) model parameters.
+Vertical bars indicate 95\\% confidence intervals.">>=
+createSFParamsGraph(factor="X")
+@
+
+<<SFu_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $u$) model parameters.
+Vertical bars indicate 95\\% confidence intervals.">>=
+createSFParamsGraph(factor="U")
+@
+
+Figure \ref{fig:SF_GDP_Lattice_Graph} compares single-factor model predictions with historical data.
+
+<<SF_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="Single-factor results.">>=
+createSFLatticeGraph()
+@
 

### 2013-04-26 EconGrowth.Rnw
Additional edits to remove math formatting in section titles.

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Historical Data}
-\label{sec:Historical_Data}
+\section{Sources of Data}
+\label{sec:Sources_of_Data}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %++++++++++++++++++++++++++++++
-\subsection{Output ($Y$)} 
-\label{sec:Output_Data}
+\subsection{Economic Output} 
+\label{sec:Economic_Output_Data}
 %++++++++++++++++++++++++++++++
@@
 %++++++++++++++++++++++++++++++
-\subsection{Capital Stock ($K$)} 
+\subsection{Capital Stock} 
 \label{sec:Capital_Stock_Data}
@@
 %++++++++++++++++++++++++++++++
-\subsection{Labor and Employment ($L$)} 
+\subsection{Labor and Employment}
 \label{sec:Labor_Data}
@@
 %++++++++++++++++++++++++++++++
-\subsection{Thermal Energy, Exergy, and Useful Work ($E$)} 
+\subsection{Thermal Energy, Exergy, and Useful Work} 
 \label{sec:Energy_Data}
@@
 %------------------------------
-\subsubsection{Thermal Energy ($Q$)} 
+\subsubsection{Thermal Energy} 
 \label{sec:Q_Data}
@@
 %------------------------------
-\subsubsection{Exergy ($X$)} 
+\subsubsection{Exergy} 
 \label{sec:X_Data}
@@
 %------------------------------
-\subsubsection{Useful Work ($U$)} 
+\subsubsection{Useful Work} 
 \label{sec:U_Data}
@@
 %++++++++++++++++++++++++++++++
-\subsection{Historical Data} \label{sec:Historical_Data}
+\subsection{Historical Data} 
+\label{sec:Historical_Data}
 %++++++++++++++++++++++++++++++
@@
 Figure \ref{fig:Historical_Lattice_Graph} presents historical data, including indexed values for output ($y$), capital stock ($k$), labor ($l$), and the various energy quantifications ($q$, $x$, and $u$) for 1980-2011 (developed economies) and 1991-2011 (other economies).
-Factors of production track each other closely, and large covariances among these variables can be seen in Tables \ref{tab:Covariance_US} through \ref{tab:Covariance_ZM}.
+Factors of production track each other closely, and high covariances among these variables can be seen in Tables \ref{tab:Covariance_US} through \ref{tab:Covariance_ZM}.
 
@@
 
-\section{Cobb-Douglas Models With Energy (CD$e$)}
+\section{Cobb-Douglas Models With Energy}
 
@@
 
-\subsection{Cobb-Douglas with thermal energy ($q$)}
+\subsection{Cobb-Douglas with thermal energy}
 
@@
 
-\subsection{Cobb-Douglas with exergy ($x$)}
+\subsection{Cobb-Douglas with exergy}
 
@@
 
-\subsection{Cobb-Douglas with useful work ($u$)}
+\subsection{Cobb-Douglas with useful work}
 
@@
 
-\subsection{CES with $Q$ (CES$q$)}
+\subsection{CES with Thermal Energy}
 
@@
 
-\subsection{CES with $X$ (CES$x$)}
+\subsection{CES with Exergy}
 
@@
 
-\subsection{CES with $U$ (CES$u$)}
+\subsection{CES with Useful Work}
 
@@
 
-\subsection{LINEX with $Q$}
+\subsection{LINEX with Thermal Energy}
 
@@
 
-\subsection{LINEX with $X$}
+\subsection{LINEX with Exergy}
 
@@
 
-\subsection{LINEX with $U$}
+\subsection{LINEX with Useful Work}
 
@@
 
-In the spirit of Reproducible Research \citep{Gandrud:2013vx}, all data, spreadsheets, \texttt{R} code \citep{R}, and other materials associated with this paper can be found at \url{https://github.com/MatthewHeun/Econ-Growth-R-Analysis}.
+In the spirit of Reproducible Research \citep{Gandrud:2013vx}, all data, spreadsheets, \texttt{R} code \citep{R}, and other materials associated with this paper can be found at \protect\url{https://github.com/MatthewHeun/Econ-Growth-R-Analysis}.
 

### 2013-04-26 EconGrowth.Rnw
Further edits on the preliminary sections.

@@
 
-\noindent where $y \equiv Y/Y_\mathrm{0}$, $k \equiv K/K_\mathrm{0}$, and $l \equiv L/L_\mathrm{0}$; with $Y$ represented by GDP, $K$ expressed in currency units, $L$ expressed in workers/year or work-hours/year, time ($t$) measured in years, e being the base of the natural logarithm, and subscripts ``0'' indicating values at an initial year.\footnote{Indexed quantities are represented by lower-case symbols ($y$, $k$, $l$, $e$, $q$, $x$, and $u$) and dimensional quantities are represented by upper-case symbols ($Y$, $K$, $L$, $E$, $Q$, $X$, and $U$).} $A$ is a technological progress term, with $\lambda$ indicating the pace of technological progress (in units of year$^{-1}$).
+\noindent where $y \equiv Y/Y_\mathrm{0}$, $k \equiv K/K_\mathrm{0}$, and $l \equiv L/L_\mathrm{0}$; with $Y$ represented by GDP, $K$ expressed in currency units, $L$ expressed in workers/year or work-hours/year, time ($t$) measured in years, e being the base of the natural logarithm, and subscripts ``0'' indicating values at an initial year.\footnote{In this paper, indexed quantities are represented by lower-case symbols ($y$, $k$, $l$, $e$, $q$, $x$, and $u$) and dimensional quantities are represented by upper-case symbols ($Y$, $K$, $L$, $E$, $Q$, $X$, and $U$).} $A$ is a technological progress term, with $\lambda$ indicating the pace of technological progress (in units of year$^{-1}$).
 Neoclassical economic growth theory makes no attempt to understand the mechanisms by which technological progress ($A$) affects economic growth, nor does it attempt to describe how technological progress ($A$) might vary from one economy to the next.
@@
 Some energy economists augment economic growth models with energy being an additional (or the only) factor of production.
-However, there is little agreement in the literature on how this should be done.
+However, there is little agreement on how this should be done.
 Neither the mathematical form of the energy-augmented production function nor the quantification of energy are consistent in the literature.
-Furthermore, there has been little empirical work done to assess the predictive ability of energy-augmented production functions for different types of economies.
-In addition, very few studies of the importance of energy in economic growth include rigorous statistical assessments of energy-related parameters.
+Furthermore, there has been little empirical work done to assess the predictive ability of various energy-augmented production functions for different types of economies.
+In addition, very few studies of the importance of energy in economic growth include rigorous statistical assessments of energy-related fitting parameters.
 This paper attempts to contribute to the literature by applying statistically rigorous methods along three coordinates of analysis: form of the energy augmented production function, energy quantification, and type of economy.
@@
 The LINEX model assumes energy ($e$) is the only factor of production.
-$\rho_k \equiv \frac{k}{(1/2)(l+e)}$ and represents the rate at which capital stock increases relative to the average of labor and energy.
-$\rho_l \equiv \frac{l}{e}$ and represents the rate at which labor ($l$) increases relative to energy ($e$).
-Energy ($e$) as a factor of production is enhanced by $A$ if either
+The parameters $\rho_k$ and $\rho_l$ are defined as
+
+\begin{equation} \label{eq:rho_k}
+  \rho_k \equiv \frac{k}{(1/2)(l+e)}
+\end{equation}
+
+\noindent and
+
+\begin{equation} \label{eq:rho_l}
+  \rho_l \equiv \frac{l}{e}
+\end{equation}
+
+\noindent and represent (a) capital stock increase relative to the average of labor and energy and (b) the increase of labor ($l$) relative to energy ($e$), respectively.
+Energy ($e$) as a the only factor of production is enhanced by $A$ if either
 
 \begin{itemize}
-\item{capital stock ($k$) increases faster than the average of energy ($e$) and labor ($l$), i.e. if $\rho_k >$ 1, or}
-\item{labor ($l$) increases faster than energy ($e$), i.e. if $\rho_l >$ 1.}
+\item{capital stock ($k$) has increased more than the average of energy ($e$) and labor ($l$), i.e. if $\rho_k >$ 1, or}
+\item{labor ($l$) has increased more than energy ($e$), i.e. if $\rho_l >$ 1.}
 \end{itemize}
 
-\noindent According to the LINEX model, an economy that can increase capital stock ($k$) without a commensurate increase in labor ($l$) and energy ($e$) will experience an increase in output ($y$) in excess of its increase of energy consumption ($e$).
+\noindent According to the LINEX model, an economy that can increase capital stock ($k$) without a commensurate increase in labor ($l$) and energy ($e$) will experience an increase in output ($y$) in excess of its increase of energy consumption ($e$), because $A$ will be greater than 1.
 Similarly, an economy benefits by increasing labor ($l$) without a commensurate increase in energy ($e$).
 Thus, $\rho_k$ is an efficiency of using labor and energy to make capital available to the economy, and $\rho_l$ is an efficiency of using energy to make labor available to the economy.
-The parameter $a_0$ represents the overall importance of these efficiencies, and $c_t$ represents the relative importance of the labor efficiency term compared to the capital stock efficiency term.
-Both $a_0$ and $c_t$ are constant with respect to time.
-
-In contrast to the Cobb-Douglas model (Equations \ref{eq:CD} and \ref{eq:CDe}) and the CES model (Equations \ref{eq:CES} and \ref{eq:CESe}), the LINEX model (Equation \ref{eq:LINEX}) accounts for efficiencies among capital, labor, and energy directly and, therefore, does not employ a time-dependent technical progress term ($A$).
+$a_0$ represents the overall importance of these efficiencies, and $c_t$ represents the relative importance of the labor efficiency term compared to the capital stock efficiency term.
+We treat $a_0$ and $c_t$ as fitting parameters; both are assumed constant with respect to time.
+
+In contrast to both the Cobb-Douglas model (Equations \ref{eq:CD} and \ref{eq:CDe}) and the CES model (Equations \ref{eq:CES} and \ref{eq:CESe}), the LINEX model (Equation \ref{eq:LINEX}) accounts for efficiencies among capital, labor, and energy directly and, therefore, does not employ a time-dependent technical progress term ($A$).
 \citet{Kummel:2002tx} use the LINEX production function to describe economic output for the economies of the U.S., Japan, and Germany.
@@
 Useful work ($U$) includes the direct energy that goes into an economy, including work from machines, human muscles, and animals.
-Most energy economists have used thermal energy ($Q$) for the energy factor of production ($E$) in energy-augmented production functions, including \citet{Stern:2012ey}, \citet{Froling:2009vo}, \citet{Serrenho:2010vq}, and \citet{Kummel:1980wx,Kummel:1982vy,Kummel:1985vz,Kummel:1989tf,Kummel:2002tx,Kummel:2010vz}.
-\citet{Warr:2010ga} introduced the idea of using exergy ($X$) and useful work ($U$) in a production function to account for efficiency gains in energy production and consumption over the last century.
-
-We know of no statistically-rigorous comparisons of the predictive ability of each type of energy quantification in the various types of production functions discussed in Section \ref{sec:Prod_Func_Forms}.
+Firms pay for thermal energy ($Q$), but useful work ($U$) alters the size and shape of materials, keeps the lights on, and transports goods to consumers.
+Not all forms of energy are created equal in terms of ability to generate economic activity \citep{Cleveland:2000vl}.
+Exergy ($X$), and to a greater extent, useful work ($U$) account for the useful energy that goes into generating economic activity, thereby reflecting the ``quality'' of each energy type and the efficiency of machines and devices typically used to convert thermal energy ($Q$) into useful work ($U$).
+
+Most energy economists use thermal energy ($q$) for the energy factor of production ($e$) in energy-augmented production functions, including \citet{Stern:2012ey}, \citet{Froling:2009vo}, \citet{Serrenho:2010vq}, and \citet{Kummel:1980wx,Kummel:1982vy,Kummel:1985vz,Kummel:1989tf,Kummel:2002tx,Kummel:2010vz}.
+\citet{Warr:2010ga} introduced the idea of using exergy ($x$) and useful work ($u$) in energy-augmentd production functions to account for efficiency gains in energy production and consumption over the last century.
+
+We know of no statistically-rigorous comparisons of the predictive ability of each energy quantification in the various types of production functions discussed in Section \ref{sec:Prod_Func_Forms}.
 We analyze all three quantifications of energy ($Q$, $X$, and $U$) for developed economies and thermal energy ($Q$) and exergy ($X$) for all other economies.
@@
 
-In most energy-economic growth literature, economists assess developed economies from North America or Europe.
+In the energy-economic growth literature, the focus is almost exclusively on developed economies from North America or Europe.
 Examples include \citet{Kummel:1980wx} applying LINEX to describe the West German economy, \citet{Serrenho:2010vq} applying Cobb-Douglas variants to EU-15 countries, \citet{VanderWerf:2008tc} applying CES nesting variants to the 12 OECD countries, \citet{Lecca:2011kr} applying CES nesting variants to the Scottish economy, \citet{Stern:2012ey} applying CES to describe the Swedish economy, and \citet{Warr:2012cg} using LINEX and Cobb-Douglas to describe the Austrian, American, British, and Japanese economies.
 
+But, the nearly-complete focus on developed economies misses the role that energy plays in the development process.
 In this paper we analyze at least two economies from each of the following categories: developed (technologically advanced with high standards of living), BRICS\footnote{Brazil, Russia, India, China, and South Africa} (rapid economic growth with standards of living below that of developed economies), petrol (petroleum is a substantial source of GDP); and LDCs\footnote{Lesser Developed Countries} (living standards near subsistence levels).
@@
 
-Total employment and average hours worked per year per worker for the United States, the United Kingdom, and Japan for 1980-2011 was obtained from the United States \citet{BLS:2011a}.
-Total hours worked was calculated by multiplying total employment by average hours worked per worker.
-************* Matt ended here.
-**************** The World Bank's WDI database (WORLD BANK, 2012) provides an employment to population ratio of people fifteen and older, total population, and a percentage of people under fifteen for South Africa, China, Iran, Saudi Arabia, Tanzania, and Zambia for 1991-2011.
-The population of people fifteen and older was calculated by multiplying the percentage of people under fifteen by total population, and then subtracting this from the total population.
-Total employment could be calculated by multiplying the employment to population ratio of people fifteen and older by the population of people fifteen and older.
-The labor input for South Africa, China, Iran, Saudi Arabia, Tanzania, and Zambia is based on total employment, not on total hours worked per year.
+Total employment and average hours worked per worker per year for the developed nations (United States, United Kingdom, and Japan) for 1980-2011 were obtained from the United States \citet{BLS:2011a}.
+Total hours worked per year was calculated by multiplying total employment by average hours worked per worker per year.
+
+The World Bank's World Development Indicators database \citep{WorldBankWDI:2013a} provides the employment to population ratio for people fifteen and older, total population, and a percentage of people under fifteen for other nations (South Africa, China, Iran, Saudi Arabia, Tanzania, and Zambia) for 1991-2011.
+The population of people under fifteen was subtracted from total population to calculate the population of people fifteen and older.
+Total employment was calculated by multiplying the employment to population ratio of people fifteen and older by the population of people fifteen and older.
 
@@
 
-We were interested in how the three different types of energy (thermal energy, exergy, and useful work) would affect our econometric growth modeling.
-The rationale being that exergy, and to a greater extent useful work, would take into account the energy that is being directly used to further economic growth.
-We examined typical sources of energy for an economy, including: coal; oil and petroleum products; dry natural gas and natural gas plant liquids; nuclear power generation; and renewable energy sources (solar, wind, geothermal, biomass/fuel wood,  hydroelectric generation).
+************* Matt ended here. ****************
+
+To account for all energy input to an economy, we summed consumption data for many energy sources for each economy, including: coal; oil and petroleum products; dry natural gas and natural gas plant liquids; nuclear power generation; and renewable energy sources (solar, wind, geothermal, biomass/fuel wood,  hydroelectric generation).
 In the style of (AYRES AND WARR, 2002, 2005), energy available from human and animal muscle power are also considered.
@@
 Figure \ref{fig:Historical_Lattice_Graph} indicates the importance of energy quantification for economic growth modeling.
-Thermal energy ($q$) and exergy ($x$) grow at similar rates, unless there is a significant raw energy carrier substitution (such as China's substitution of ***** for ***** over the last 2 decades).
-The growth rate of $u$ is significantly different from $q$ and $x$, however.
+Thermal energy ($q$) and exergy ($x$) grow at similar rates, unless there is a significant raw energy carrier substitution in the economy (such as China's rapid increase of coal consumption relative to petroleum since 2000).
+The growth rate of $u$ is significantly different from $q$ and $x$ for most countries, however.
 \citet{Warr:2012cg} show that from 1950-1990, useful work ($u$) grew much faster than $q$, $x$, $k$, or $l$ due to efficiency gains in the U.S.

### 2013-04-26 EconGrowth.Rnw
More editing into energy section.

@@
 Firms pay for thermal energy ($Q$), but useful work ($U$) alters the size and shape of materials, keeps the lights on, and transports goods to consumers.
-Not all forms of energy are created equal in terms of ability to generate economic activity \citep{Cleveland:2000vl}.
+Not all forms of energy are created equal in terms of ability to generate economic activity \citep{Cleveland:2000vl, Warr:2010ht}.
 Exergy ($X$), and to a greater extent, useful work ($U$) account for the useful energy that goes into generating economic activity, thereby reflecting the ``quality'' of each energy type and the efficiency of machines and devices typically used to convert thermal energy ($Q$) into useful work ($U$).
@@
 But, the nearly-complete focus on developed economies misses the role that energy plays in the development process.
-In this paper we analyze at least two economies from each of the following categories: developed (technologically advanced with high standards of living), BRICS\footnote{Brazil, Russia, India, China, and South Africa} (rapid economic growth with standards of living below that of developed economies), petrol (petroleum is a substantial source of GDP); and LDCs\footnote{Lesser Developed Countries} (living standards near subsistence levels).
+In this paper we analyze at least two economies in each of the following four categories: Developed (technologically advanced with high standards of living), BRICS\footnote{Brazil, Russia, India, China, and South Africa} (rapid economic growth with standards of living below that of developed economies), Petrol (petroleum is a substantial source of GDP); and LDCs\footnote{Lesser Developed Countries} (living standards near subsistence levels).
 (See Table \ref{tab:Economy_Examples}.)
@@
     \begin{tabular}{r c c l l} 
-      \multirow{3}{*}{Developed} & \includegraphics[height=0.11in]{flag/flag_US.png} & US & USA & \multirow{3}{*}{1980-2011}\\
+      \multirow{3}{*}{Developed} & \includegraphics[height=0.11in]{flag/flag_US.png} & US & USA & \multirow{3}{*}{1980--2011}\\
                                  & \includegraphics[height=0.11in]{flag/flag_UK.png} & UK & United Kingdom & \\
@@
       \hline
-      \multirow{2}{*}{BRICS}     & \includegraphics[height=0.11in]{flag/flag_CN.png} & CN & China & \multirow{2}{*}{1991-2011}        \\
+      \multirow{2}{*}{BRICS}     & \includegraphics[height=0.11in]{flag/flag_CN.png} & CN & China & \multirow{2}{*}{1991--2011}        \\
                                  & \includegraphics[height=0.11in]{flag/flag_ZA.png} & ZA & South Africa & \\
       \hline
-      \multirow{2}{*}{Petrol}    & \includegraphics[height=0.11in]{flag/flag_SA.png} & SA & Saudi Arabia & \multirow{2}{*}{1991-2011} \\
+      \multirow{2}{*}{Petrol}    & \includegraphics[height=0.11in]{flag/flag_SA.png} & SA & Saudi Arabia & \multirow{2}{*}{1991--2011} \\
                                  & \includegraphics[height=0.11in]{flag/flag_IR.png} & IR & Iran         &  \\
       \hline
-      \multirow{2}{*}{LDC}       & \includegraphics[height=0.11in]{flag/flag_TZ.png} & TZ & Tanzania & \multirow{2}{*}{1991-2011}     \\
+      \multirow{2}{*}{LDC}       & \includegraphics[height=0.11in]{flag/flag_TZ.png} & TZ & Tanzania & \multirow{2}{*}{1991--2011}     \\
                                  & \includegraphics[height=0.11in]{flag/flag_ZM.png} & ZM & Zambia      & \\
@@
 GDP data in real 2005 U.S.
-dollars for developed countries (1980-2011) and all other countries (1991-2011) was obtained from the World Bank's Global Economic Prospects (GEP) database \citep{WorldBankGEP:2013a}.
+dollars for developed countries (1980--2011) and all other countries (1991--2011) was obtained from the World Bank's Global Economic Prospects (GEP) database \citep{WorldBankGEP:2013a}.
 
@@
 Gross capital stock in real 2005 U.S.
-dollars for developed countries (1980-2011) and all other countries (1991-2011) was obtained from the World Bank's Global Economic Prospects (GEP) database \citep{WorldBankGEP:2013a}.
+dollars for developed countries (1980--2011) and all other countries (1991--2011) was obtained from the World Bank's Global Economic Prospects (GEP) database \citep{WorldBankGEP:2013a}.
 
@@
 
-Total employment and average hours worked per worker per year for the developed nations (United States, United Kingdom, and Japan) for 1980-2011 were obtained from the United States \citet{BLS:2011a}.
+Total employment and average hours worked per worker per year for the developed nations (United States, United Kingdom, and Japan) for 1980--2011 were obtained from the United States \citet{BLS:2011a}.
 Total hours worked per year was calculated by multiplying total employment by average hours worked per worker per year.
 
-The World Bank's World Development Indicators database \citep{WorldBankWDI:2013a} provides the employment to population ratio for people fifteen and older, total population, and a percentage of people under fifteen for other nations (South Africa, China, Iran, Saudi Arabia, Tanzania, and Zambia) for 1991-2011.
+The World Bank's World Development Indicators database \citep{WorldBankWDI:2013a} provides the employment to population ratio for people fifteen and older, total population, and a percentage of people under fifteen for other nations (South Africa, China, Iran, Saudi Arabia, Tanzania, and Zambia) for 1991--2011.
 The population of people under fifteen was subtracted from total population to calculate the population of people fifteen and older.
@@
 
+To account for all energy input to an economy, we summed consumption data for many energy sources, including: coal, oil and petroleum products, dry natural gas and natural gas plant liquids, nuclear power generation, and renewable energy sources (solar, wind, geothermal, biomass/fuel wood,  hydroelectric generation).
+In the style of \citet{Ayres:2005kn, Warr:2010ht, Warr:2010ga, Warr:2012cg}, energy from human and animal muscle power are also included.
+Similar to the economic data discussed in Sections \ref{sec:Economic_Output_Data}--\ref{sec:Labor_Data}, we generated energy data for developed countries from 1980--2011.
+For all other countries, we generated energy data for 1991--2011.
+
 ************* Matt ended here. ****************
-
-To account for all energy input to an economy, we summed consumption data for many energy sources for each economy, including: coal; oil and petroleum products; dry natural gas and natural gas plant liquids; nuclear power generation; and renewable energy sources (solar, wind, geothermal, biomass/fuel wood,  hydroelectric generation).
-In the style of (AYRES AND WARR, 2002, 2005), energy available from human and animal muscle power are also considered.
-The time series data used for the United States, the United Kingdom, and Japan is from 1980-2011.
-Time series data used for South Africa, China, Saudi Arabia, Iran, Zambia, and Tanzania is from 1991-2011.
 
@@
 
-Thermal energy ($q$) is evaluated in TJ/year for the production functions. In the case of fuels, thermal energy was calculated using equation \ref{eq:thermal_energy}.
+Thermal energy ($Q$) is evaluated in TJ/year for the production functions. In the case of fuels, thermal energy was calculated using equation \ref{eq:thermal_energy}.
 
@@
 Human muscle power was calculated in the same way, except the $ME$ value for people was taken from a time series of kcal/day-person for workers in the U.S.
-from 1980-2011 (WARR SPREADSHEETS).
+from 1980--2011 (WARR SPREADSHEETS).
 The value stays relatively constant over the time series and the same time series was used to all of the countries, although it should be noted that this value may vary some (especially for the Malthusian vs developed economies).
@@
 These values are not constant over time, as power generation technologies change and become more efficient.
-Useful work was only analyzed for the developed economies (the United States, the United Kingdom, and Japan) from 1980-2011, because of the difficulty associated with determining $\phi$ and $\epsilon$ values.
+Useful work was only analyzed for the developed economies (the United States, the United Kingdom, and Japan) from 1980--2011, because of the difficulty associated with determining $\phi$ and $\epsilon$ values.
 In order to determine these parameters, information is needed about the efficiency of different technologies and what industries/areas is consuming the most energy within an economy.
@@
 
-Figure \ref{fig:Historical_Lattice_Graph} presents historical data, including indexed values for output ($y$), capital stock ($k$), labor ($l$), and the various energy quantifications ($q$, $x$, and $u$) for 1980-2011 (developed economies) and 1991-2011 (other economies).
+Figure \ref{fig:Historical_Lattice_Graph} presents historical data, including indexed values for output ($y$), capital stock ($k$), labor ($l$), and the various energy quantifications ($q$, $x$, and $u$) for 1980--2011 (developed economies) and 1991--2011 (other economies).
 Factors of production track each other closely, and high covariances among these variables can be seen in Tables \ref{tab:Covariance_US} through \ref{tab:Covariance_ZM}.

### 2013-04-27 EconGrowth.Rnw
Added additional references and edited text in the thermal energy section.

@@
 For all other countries, we generated energy data for 1991--2011.
-
-************* Matt ended here. ****************
+Details on each of the quantifications of energy are given in subsections below.
 
@@
 
-Thermal energy ($Q$) is evaluated in TJ/year for the production functions. In the case of fuels, thermal energy was calculated using equation \ref{eq:thermal_energy}.
+Thermal energy ($Q$) for fuels (in units of TJ/year) was calculated by
 
 \begin{equation} \label{eq:thermal_energy}
-  e_\mathrm{fuel} = (consumption)(heat content)
-\end{equation}
-
-Yearly consumption data for all the countries was obtained from the International Energy Agency (IEA, 2012) for coal (in short tons/year); oil and petroleum (in barrels/year); and dry natural gas and natural gas plant liquids (in cubic feet/year).
-Yearly average heat content data (in kJ/kg) for coal, oil, and natural gas was also taken from the IEA (IEA, 2012) for all the countries.
-Yearly consumption (in cubic meters/year) and heat content data (in kJ/kg) for biomass/fuel wood was taken from the"Fuelwood" time series on the FAO Statistics Database (FAOSTAT, 2012).
-
-For the renewable and nuclear energy sources, data on yearly electricity generation (in BTU/year) was directly available from the IEA (IEA, 2012) for each of the countries, so the use of equation \ref{eq:thermal_energy} was not needed.
-
-Human and animal muscle power was calculated using a similar style to Ayres and Warr and Wirsenius (AYRES AND WARR (No reference?
+  Q_{fuel} = C_{fuel}h_{fuel},
+\end{equation}
+
+\noindent where $C_{fuel}$ is the consumption rate of the fuel (in units of short tons/year for coal, barrels/year for oil and petroleum, ft$^3$/year for dry natural gas and natural gas plant liquids, and m$^3$/year for biomass/fuel wood) and $h_{{fuel}}$ is the heat content of the fuel (in kJ/short ton for coal, kJ/barrel for oil, kJ/ft$^3$ for dry natural gas and natural gas plant liquids, and kJ/kg for biomass/fuel wood).
+******* Need a fuelwood density to convert between m3/year and kJ/kg.
+*******
+
+Yearly consumption rates ($C_{fuel}$) for all economies were obtained from the International Energy Agency \citep{IEA:2013a} for coal, oil and petroleum, and dry natural gas and natural gas plant liquids.
+Yearly average heat content data  for coal, oil, and natural gas was obtained from the IEA for all economies.
+Yearly consumption and heat content data for biomass/fuel wood was obtained from the ``Fuelwood'' time series of the FAO Statistics Database \citep{FAO:2013a}.
+
+For renewable and nuclear energy sources, data on yearly electricity generation (in BTU/year) was directly available from the IEA \citep{IEA:2013a} for all economies, so Equation \ref{eq:thermal_energy} was not needed.
+
+************* Matt ended here. ****************
+
+Human and animal muscle power was calculated using a similar approach to Ayres and Warr and Wirsenius (AYRES AND WARR (No reference?
 We used the worksheets he sent us.), WIRSENIUS (2000)).

### 2013-04-28 EconGrowth.Rnw
Editing the thermal energy and exergy sections.

@@
 
-\noindent where $y \equiv Y/Y_\mathrm{0}$, $k \equiv K/K_\mathrm{0}$, and $l \equiv L/L_\mathrm{0}$; with $Y$ represented by GDP, $K$ expressed in currency units, $L$ expressed in workers/year or work-hours/year, time ($t$) measured in years, e being the base of the natural logarithm, and subscripts ``0'' indicating values at an initial year.\footnote{In this paper, indexed quantities are represented by lower-case symbols ($y$, $k$, $l$, $e$, $q$, $x$, and $u$) and dimensional quantities are represented by upper-case symbols ($Y$, $K$, $L$, $E$, $Q$, $X$, and $U$).} $A$ is a technological progress term, with $\lambda$ indicating the pace of technological progress (in units of year$^{-1}$).
-Neoclassical economic growth theory makes no attempt to understand the mechanisms by which technological progress ($A$) affects economic growth, nor does it attempt to describe how technological progress ($A$) might vary from one economy to the next.
+\noindent where $y \equiv Y/Y_\mathrm{0}$, $k \equiv K/K_\mathrm{0}$, and $l \equiv L/L_\mathrm{0}$; with $Y$ represented by GDP, $K$ expressed in currency units, $L$ expressed in workers/year or work-hours/year, time ($t$) measured in years, e being the base of the natural logarithm, and subscripts ``0'' indicating values at an initial year.
+$A$ is a unitless technological progress term, with $\lambda$ indicating the pace of technological progress (in units of year$^{-1}$).\footnote{Dimensionless, indexed quantities are represented by lower-case symbols ($y$, $k$, $l$, $e$, $q$, $x$, and $u$), and dimensional quantities are represented by upper-case symbols ($Y$, $K$, $L$, $E$, $Q$, $X$, and $U$).
+One exception is the technolgical progress term $A$, which is dimensionless but written in upper-case by convention.} Neoclassical economic growth theory makes no attempt to understand the mechanisms by which technological progress ($A$) affects economic growth, nor does it attempt to describe how technological progress ($A$) might vary from one economy to the next.
 Mathematically, $A$ is a fitting parameter that aligns the predictions of Equation \ref{eq:CD} with historical data.
@@
 
-To account for all energy input to an economy, we summed consumption data for many energy sources, including: coal, oil and petroleum products, dry natural gas and natural gas plant liquids, nuclear power generation, and renewable energy sources (solar, wind, geothermal, biomass/fuel wood,  hydroelectric generation).
-In the style of \citet{Ayres:2005kn, Warr:2010ht, Warr:2010ga, Warr:2012cg}, energy from human and animal muscle power are also included.
+To account for all energy input to an economy, we summed consumption data for many energy sources, including coal, oil and petroleum products, dry natural gas and natural gas plant liquids, nuclear power generation, and renewable energy sources (solar, wind, geothermal, biomass/fuel wood, and hydro).
+In the style of work by Warr and Ayres \citep{Ayres:2005kn, Warr:2010ht, Warr:2010ga, Warr:2012cg}, energy from human and animal muscle power were also included.
 Similar to the economic data discussed in Sections \ref{sec:Economic_Output_Data}--\ref{sec:Labor_Data}, we generated energy data for developed countries from 1980--2011.
 For all other countries, we generated energy data for 1991--2011.
-Details on each of the quantifications of energy are given in subsections below.
+Details on each of the energy quantifications are given in subsections below.
 
@@
 Yearly consumption rates ($C_{fuel}$) for all economies were obtained from the International Energy Agency \citep{IEA:2013a} for coal, oil and petroleum, and dry natural gas and natural gas plant liquids.
-Yearly average heat content data  for coal, oil, and natural gas was obtained from the IEA for all economies.
+Yearly average heat content data  for coal, oil, and natural gas and natural gas plant liquids was obtained from the IEA for all economies.
 Yearly consumption and heat content data for biomass/fuel wood was obtained from the ``Fuelwood'' time series of the FAO Statistics Database \citep{FAO:2013a}.
 
-For renewable and nuclear energy sources, data on yearly electricity generation (in BTU/year) was directly available from the IEA \citep{IEA:2013a} for all economies, so Equation \ref{eq:thermal_energy} was not needed.
-
-************* Matt ended here. ****************
-
-Human and animal muscle power was calculated using a similar approach to Ayres and Warr and Wirsenius (AYRES AND WARR (No reference?
-We used the worksheets he sent us.), WIRSENIUS (2000)).
-For animals, our analysis was restricted to draught animals; horses and mules in this case.
-Muscle work from animals was calculated using equation \ref{eq:animal_muscle}.
+For renewable and nuclear energies, yearly electricity generation (in BTU/year) was available directly from the IEA \citep{IEA:2013a} for all economies, so Equation \ref{eq:thermal_energy} was not necessary.
+
+************** Should all of the following calculations have $Q_m$ instead of $E_m$, because we're talking specifically about thermal energy here. Or, is $E_m$ correct? *************
+
+Animal and human muscle work was estimated using an approach similar to \citet{Ayres:2010ug}, using some data from Warr's REXS database \citep{Warr:2012a} and results from \citet{Wirsenius:2000vi}.
+For animal work, our analysis was restricted to draught animals (horses and mules).
+Muscle work from animals ($E_{animals}$) was calculated using
 
 \begin{equation} \label{eq:animal_muscle}
-  e_\mathrm{animals} = \bigg{[} (ME_\mathrm{horse}N_\mathrm{horses})+(ME_\mathrm{mules}N_\mathrm{mules}) \bigg{]}
-\end{equation}
-
-Where $ME$ is metabolizable energy (in kcal/day-animal) and $N$ is the number of horses or mules.
-Metabolizable energy values were taken from Warr (WARR SPREADSHEETS) for horses and mules, which represent the amount of energy used to the animals for a days work.
-It should be noted that the same $ME$ value was assumed constant across all years, and used for all countries.
-The number of horses and mules for all the countries was taken from the "Live Animals" time series on the FAO Statistics Database (FAOSTAT, 2012).
-The food-to-work conversion efficiency was taken from Warr (WARR SPREADSHEETS) and was assumed to be the same for all countries.
-
-Human muscle power was calculated in the same way, except the $ME$ value for people was taken from a time series of kcal/day-person for workers in the U.S.
-from 1980--2011 (WARR SPREADSHEETS).
-The value stays relatively constant over the time series and the same time series was used to all of the countries, although it should be noted that this value may vary some (especially for the Malthusian vs developed economies).
-The number of humans was taken to be only the working population, with the same data collected for employment and labor being used.
-Ultimately, human muscle work was calculated using equation \ref{eq:human_muscle}.
+  E_{animals} = E_{m,horse}N_{horses} + E_{m,mule}N_{mules}
+\end{equation}
+
+\noindent where $E_m$ is metabolizable energy (in kcal/day-animal) and $N$ is the number of animals.
+Metabolizable energy values were taken from \citet{Warr:2012a} for horses and mules and represent the amount of energy used to ****** feed?
+****** the animals for a days work.
+The value of $E_m$ was assumed constant for all economies and years.
+***** What was the value?
+******* The number of horses and mules for each economy was taken from the ``Live Animals'' time series on the FAO Statistics Database \citep{FAO:2013a}.
+The animal feed-to-work conversion efficiency was taken from \citet{Warr:2012a} and assumed equal across all economies.
+******** Why is this important here?
+Should the feed-to-work conversion efficiency be employed in the sections below?
+Or, was the feed-to-work effiency used to calculate $E_m$?
+In any case, what was the value of the feed-to-work efficiency?
+**********
+
+Human muscle power was calculated in a similar manner.
 
 \begin{equation} \label{eq:human_muscle}
-  e_\mathrm{humans} = (ME_\mathrm{humans})(N_\mathrm{humans,employed})
-\end{equation}
+  E_{workers} = (E_{m,workers})(N_{workers})
+\end{equation}
+
+\noindent The value of $E_{m,workers}$ was taken from a time series of kcal/day-person for workers in the U.S.
+from 1980--2011 \citep{Warr:2012a}.
+$E_{m,workers}$ is relatively constant over the period 1980--2011 at about ****** What is the value?
+*******, and the U.S.
+time series was assumed to apply to all economies.\footnote{The assumption that U.S.
+per-worker food intake applies to all economies introduces minor errors in human muscle work estimates for the various economies.
+However, human muscle work is never more than ****** \% of total energy consumption for any of the economies in this study, and we estimate that the error caused by this assumption is always less than ***** \% of total energy consumption for all economies.} The value for $N_{workers}$ was obtained from the labor time series for each economy as discussed in Section \ref{sec:Labor_Data}.
 
@@
 
-Exergy ($x$) is also evaluated in TJ/year and based on the previously determined thermal energy values.
-For coal; oil and petroleum; dry natural gas and natural gas liquids; and biomass/fuel wood., the thermal energy value for the fuels was calculated using an exergy-to-energy allocation factor from Ayres and Warr (AYRES AND WARR, 2005).
+Exergy ($X$), expressed in TJ/year, was calculated from the thermal energy ($Q$) values discussed in Section \ref{sec:Q_Data}.
+For fuels, exergy was calculated using a unitless exergy-to-energy allocation factor ($f_{exergy-allocation}$) from \citet{Ayres:2005kn} and shown in Table \ref{tab:Exergy_Allocation}.
 
 \begin{equation} \label{eq:exergy}
-  x_\mathrm{fuels} = (e_\mathrm{fuels})(f_\mathrm{exergy-allocation})
-\end{equation}
-
-This allocation factor is the ratio of each fuel source's chemical exergy to the higher heating value.
-The exergy allocation factor was assumed to be the same for each of the countries.
-For renewable and nuclear energy sources, the electricity generated is already pure exergy, so no further modification is needed.
-
-For calculating the exergy from animal and human muscle power, the food-to-energy conversion efficiency and the ratio of food-end-use to food-intake are considered (see equation \ref{eq:animal_muscle_exergy} and equation \ref{eq:human_muscle_exergy}).
+  X_{fuel} = f_{exergy-allocation} Q_{fuel}
+\end{equation}
+
+\begin{table} \caption{Exergy allocation factors.} \label{tab:Exergy_Allocation} 
+  \begin{center}
+    \begin{tabular}{r l} 
+      Fuel                                    & $f_{exergy-allocation}$ \\
+      \hline
+      Coal                                    & ****    \\
+      Oil and petroleum                       & *****   \\      
+      Dry natural gas and                     & \multirow{2}{*}{******}    \\
+      natural gas liquids                     &         \\
+      Biomass/fuel wood                       & *****   \\
+      Nuclear                                 & 1.0     \\
+      Renewables                              & 1.0     \\
+    \end{tabular}
+  \end{center}
+\end{table}
+
+$f_{exergy-allocation}$ is the ratio of chemical exergy to the higher heating value for each fuel.
+***** Is this right?
+Are the $X$ values larger than the $Q$ values?
+The exergy allocation factor for each fuel was assumed to be constant across all economiess.
+For renewable and nuclear energy sources, the electricity generated is already pure exergy, so $f_{exergy-allocation}$ is unity.
+
+************* Matt ended here. ****************
+
+For calculating the exergy of animal and human muscle power, the food-to-energy conversion efficiency and the ratio of food-end-use to food-intake are considered (see equation \ref{eq:animal_muscle_exergy} and equation \ref{eq:human_muscle_exergy}).
 
 \begin{equation} \label{eq:animal_muscle_exergy}
-  x_\mathrm{animals} = (e_\mathrm{animals}) (\eta_\mathrm{food-to-work, animals})
+  X_{animals} = E_{animals} \eta_{food \rightarrow work,animals}
 \end{equation}
@@
 \begin{equation} \label{eq:human_muscle_exergy}
-  x_\mathrm{humans} = (e_\mathrm{humans}) (\eta_\mathrm{food-to-work, humans})( f_\mathrm{enduse-to-intake})
+  X_{workers} = E_{humans} \eta_{food \rightarrow work,workers} f_{enduse-to-intake}
 \end{equation}

### 2013-04-29 EconGrowth.Rnw
Minor change to a formula.
Edited to-do list.

@@
 \begin{itemize}
-\item{Heun: Fix weirdnesses with China on the CD gamma grid search graph}
 \item{Heun: Eliminate non-developed countries from 9-panel partial residual plots.}
-\item Heun: Add CES production function fits
+\item{Heun: Fix the ordering of references in the bibliography by setting the alphabetical order of the keys to match the temporal order of the references.}
+\item{Heun: Obtain answers to questions for Caleb.}
+\item{Heun: Add references from Lucas.}
+\item{Heun: Add CES production function fits}
       \begin{itemize}
@@
       \end{itemize}
-\item{Heun: Deal with missing covariance numbers when columns have unequal length. Use the \texttt{subset} command?}
-\item{Heun: Add data from 2011 to the models}
+\item{Heun: Deal with missing covariance numbers when columns have unequal length. Use the \texttt{subset} command? Partially complete: need to work on the $u$ data only.}
 \item{Heun: Eliminate blanks in the coefficient tables for the 95\% CIs in the Cobb-Douglas with energy rows}
@@
 \item{de Wit: review, critique, and contextualize.}
+\item{\st{Heun: Add data from 2011 to the models}}
+\item{\st{Heun: Fix weirdnesses with China on the CD gamma grid search graph.}}
 \item{\st{Heun: Add diagonal lines to triangle plots via the doubleY graph idea.
@@
 Useful work ($U$) includes the direct energy that goes into an economy, including work from machines, human muscles, and animals.
-Firms pay for thermal energy ($Q$), but useful work ($U$) alters the size and shape of materials, keeps the lights on, and transports goods to consumers.
+Firms pay for thermal energy ($Q$), but useful work ($U$) alters the size and shape of materials, keeps lights on, and transports goods to consumers.
 Not all forms of energy are created equal in terms of ability to generate economic activity \citep{Cleveland:2000vl, Warr:2010ht}.
@@
 \begin{equation} \label{eq:human_muscle}
-  E_{workers} = (E_{m,workers})(N_{workers})
+  E_{workers} = E_{m,workers} N_{workers}
 \end{equation}

### 2013-04-29 EconGrowth-R-Functions.Rnw
Went through all of Caleb's text. Lots of questions remain.

@@
   yLabel <- "Width of 95\\% Confidence Interval"
-  stripLabels <- c("CD with $q$", "CES with $q$", "CES with $q$",
-                   "CD with $x$", "CES with $x$", "CES with $x$", 
-                   "CD with $u$", "CES with $u$", "CES with $u$")
+  stripLabels <- c("Cobb-Douglas with $q$", "CES with $q$", "CES with $q$",
+                   "Cobb-Douglas with $x$", "CES with $x$", "CES with $x$", 
+                   "Cobb-Douglas with $u$", "CES with $u$", "CES with $u$")
   stripBG <- "transparent"
@@
 
-  # Diagonal line for the sigma-CES-Q panel  
-  param <- c(0.0, 1.0)
-  CI <- c(0.0, 2.0)
-  factor <- c("sigmaCESeQ", "sigmaCESeQ")
+  # Diagonal lines for the sigma-CES-Q panel  
+  param <- c(0.0, 1.0, 2.0)
+  CI <- c(2.0, 0.0, 2.0)
+  factor <- c("sigmaCESeQ", "sigmaCESeQ", "sigmaCESeQ")
   diagLineSigmaCESeQDF <- data.frame(param, CI, factor)
   # Diagonal line for the sigma-CES-X panel  
-  factor <- c("sigmaCESeX", "sigmaCESeX")
+  factor <- c("sigmaCESeX", "sigmaCESeX", "sigmaCESeX")
   diagLineSigmaCESeXDF <- data.frame(param, CI, factor)
   # Diagonal line for the sigma-CES-U panel  
-  factor <- c("sigmaCESeU", "sigmaCESeU")
+  factor <- c("sigmaCESeU", "sigmaCESeU", "sigmaCESeU")
   diagLineSigmaCESeUDF <- data.frame(param, CI, factor)
@@
   diagLinesLattice <- xyplot(CI ~ param | factor, data=diagLinesDF,
+                             type="l", col = "black", lty=2, #controls line parameters
                              scales=list(cex=scaleTextSize * textScaling, #controls text size on scales.
@@
                 gammaCDeuDF, deltaCESeuDF, sigmaCESeuDF)
-print(data)
   # Now make the graph.
-  # Need to use the indices in the following code, because the column labels will be different for each type
-  # of model. In other words, if we're doing CESe with Q and plotting sigma, the data.frame will come 
-  # back with column names of "sigma" and "CI" on the first and second column, respectively. 
-  # plot <-  xyplot(data$CI ~ data$sigma, ...)
-  # would break if we, instead, wanted CESe with Q and plotting delta.
-  # So, instead, we use the column indices to pick off the correct variables.
-  # data[ , 1] contains the the parameter; 
-  # data[ , 2] contains the CI width; 
-  # data[ , 3] contains the descriptor for the type of graph it is.
-  plot <- xyplot(CI ~ param | factor, data=data,
+  dataPlot <- xyplot(CI ~ param | factor, data=data,
                      scales=list(cex=scaleTextSize * textScaling, #controls text size on scales.
@@
                      })
+  doubleYPlot <- doubleYScale(diagLinesLattice, dataPlot, add.ylab2=FALSE, use.style=FALSE)
   #return(plot)
-  return(diagLinesLattice)
+  #return(diagLinesLattice)
+  return(doubleYPlot)
 }

### 2013-04-29 EconGrowth.Rnw
Went through all of Caleb's text. Lots of questions remain.

@@
 \usepackage{hyperref} % To create hyperlinks in the paper
+
+% From http://economics.utoronto.ca/osborne/latex/BIBTEX.HTM
+\def\citeapos#1{\citeauthor{#1}'s (\citeyear{#1})} % Posessive citations.
 
@@
 \noindent where the elasticity of substitution between capital ($k$) and labor ($l$) is given by $\sigma_1 = \frac{1}{1+\rho_1}$, the elasticity of substitution between ($kl$) and ($e$) is given by $\sigma = \frac{1}{1+\rho}$, $\delta \in [0, 1]$ describes the importance of ($kl$) relative to ($e$), and $\gamma$ is a fitting parameter, expected to be close to unity.
-Equation \ref{eq:CESe} augments a standard CES production function (Equation \ref{eq:CES}) with energy using a ($kl$)($e$) nesting arrangement, as is typical in the literature.
+Equation \ref{eq:CESe} augments a standard CES production function (Equation \ref{eq:CES}) with energy using a ($kl$)($e$) nesting structure, as is typical in the literature.
 Equation \ref{eq:CES} is a degenerate form of Equation \ref{eq:CESe} where $\delta = 1$.
@@
 
-Total employment and average hours worked per worker per year for the developed nations (United States, United Kingdom, and Japan) for 1980--2011 were obtained from the United States \citet{BLS:2011a}.
+Total employment and average hours worked per worker per year for the developed nations (United States, United Kingdom, and Japan) for 1980--2011 were obtained from the United States \citet{BLS:2013a}.
 Total hours worked per year was calculated by multiplying total employment by average hours worked per worker per year.
@@
 Exergy ($X$), expressed in TJ/year, was calculated from the thermal energy ($Q$) values discussed in Section \ref{sec:Q_Data}.
-For fuels, exergy was calculated using a unitless exergy-to-energy allocation factor ($f_{exergy-allocation}$) from \citet{Ayres:2005kn} and shown in Table \ref{tab:Exergy_Allocation}.
+For fuels, exergy was calculated by a unitless exergy-to-energy allocation factor ($f_{exergy-allocation}$) from \citet{Ayres:2005kn} and shown in Table \ref{tab:Exergy_Allocation}.
+$f_{exergy-allocation}$ is the ratio of chemical exergy to the higher heating value for each fuel.
+***** Is this right?
+Are the $X$ values larger than the $Q$ values?
+******* $f_{exergy-allocation}$ for each fuel was assumed to be constant through time across all economies.
+For renewable and nuclear energy sources, the electricity generated is already pure exergy, so $f_{exergy-allocation}$ is unity.
 
@@
 
-$f_{exergy-allocation}$ is the ratio of chemical exergy to the higher heating value for each fuel.
-***** Is this right?
-Are the $X$ values larger than the $Q$ values?
-The exergy allocation factor for each fuel was assumed to be constant across all economiess.
-For renewable and nuclear energy sources, the electricity generated is already pure exergy, so $f_{exergy-allocation}$ is unity.
-
-************* Matt ended here. ****************
-
-For calculating the exergy of animal and human muscle power, the food-to-energy conversion efficiency and the ratio of food-end-use to food-intake are considered (see equation \ref{eq:animal_muscle_exergy} and equation \ref{eq:human_muscle_exergy}).
+To calculate the exergy of animal and human muscle power, the food-to-work conversion efficiency ($\eta_{food \rightarrow work}$) and the ratio of food end-use to food intake ($f_{enduse \rightarrow intake}$) were included.
+$\eta_{food \rightarrow work, animals}$ and $\eta_{food \rightarrow work, workers}$ are animal and worker efficiency of converting food into energy respectively.
+The values for $\eta_{food \rightarrow work, animals}$ = ***** and $\eta_{food \rightarrow work, workers}$ = ***** were taken from \citet{Ayres:2010ug}.
+For workers, an additional factor ($f_{enduse \rightarrow intake}$ = ********), which accounts for food energy that is used to sustain the body's normal function as opposed to providing energy for physical labor \citep{Wirsenius:2000vi}.
+A similar ratio could also be applied to animal work, but it was unavailable from \citet{Wirsenius:2000vi}.\footnote{The error in neglecting $f_{enduse \rightarrow intake}$ for animals is very small, because animal muscle exergy is a small fraction of the total energy supply to any economy, with a maximum of **** \% for ****** in ****** year ******.}
 
 \begin{equation} \label{eq:animal_muscle_exergy}
-  X_{animals} = E_{animals} \eta_{food \rightarrow work,animals}
+  X_{animals} = \eta_{food \rightarrow work,animals} E_{animals}
 \end{equation}
@@
 \begin{equation} \label{eq:human_muscle_exergy}
-  X_{workers} = E_{humans} \eta_{food \rightarrow work,workers} f_{enduse-to-intake}
-\end{equation}
-
-Where $\eta_\mathrm{food-to-work, animals}$ and $\eta_\mathrm{food-to-work, humans}$ are the animal's and human's efficiency of converting food into energy respectively.
-For humans, an additional factor of the ratio of food-end-use to food-intake is also applied.
-This ratio looks at how much of a person's energy can actually be used for physical labor, or muscle work, by taking into account food that's used to simply sustain the body's normal function.
-The food-to-work efficiency values are taken from Ayres and Warr (AYRES AND WARR, THE ECONOMIC GROWTH ENGINE) and the end-use to intake ratio is taken from Wirsenius (WIRSENIUS, 2000).
-The same ratio could also be applied to animals, but Wirsenius did not contain any information on these values and the magnitude of the animal muscle exergy is quite small compared to the other fuel sources.
+  X_{workers} = \eta_{food \rightarrow work,workers} f_{enduse \rightarrow intake} E_{workers}
+\end{equation}
+
+\noindent
 
@@
 
-Useful work is a concept first developed by (AYRES AND WARR, 2005).
-Useful work takes exergy analysis one step further and considers where the energy is going and how efficiencies come into play.
-To calculate useful work, exergy is broken down into several categories by usage type: high temperature heat, medium temperature heat, low temperature heat, mechanical drive, electricity, light, and muscle work.
-Each of these categories then has an efficiency applied, as opposed to using an overall effiency for the base exergy value.
-The rationale behind this is that the efficiency of various industries in an economy will be very different, e.g.
-the efficiency of a coal fired power plant (high temperature heat source) will be very different from that of a residential heating system (low temperature heat source).
-
-Useful work is evaluated in TJ/year, and is given be equation \ref{eq:useful_work}.
+The conversion of a raw energy carrier (e.g., coal) into productive energy for an economy (e.g., electricity) necessarily involves inefficiencies.
+In the case of coal consumption, only about one-third ****** Is this the number we want to use?
+****** of the heat content of coal is converted to useful electricity, the rest is waste heat.
+The concept of ``useful work,'' pioneered by \citet{Ayres:2005kn}, takes exergy one step further to consider efficiencies of both energy production and end use.
+To calculate useful work ($U$), each source of exergy (coal, oil and petroleum products, dry natural gas and natural gas plant liquids, biomass/fuel wood, nuclear, solar, wind, and human and animal muscle work) is decomposed into several end uses: high temperature heat (for electricity production **** anything else?
+****), medium temperature heat (**** for ????
+****), low temperature heat (for residential heating **** anything else?
+****), mechanical drive (**** for ????
+****), electricity (**** for ????
+****), light, and muscle work.
+The efficiency of each combination of energy source and end use in an economy can be very different, e.g.
+the efficiency of a coal fired power plant (high temperature heat source, $\sim$30\%) will be very different from a residential heating system (low temperature heat source, $\sim$****\%).
+Efficiencies specific to each combination of energy source and end use were applied to exergy values to obtain useful work ($U$) input to an economy with the following equation:
 
 \begin{equation} \label{eq:useful_work}
-  u = \sum{\phi_\mathrm{i} \epsilon_\mathrm{i} x}
-\end{equation}
-
-Where $\epsilon_\mathrm{i}$ is the efficiency of each useful work type and $\phi_\mathrm{i}$ is the allocation factor, where $0 \le \phi_\mathrm{i} \le 1$.
-
-Data on $\epsilon$ and $\phi$ values were taken from the REXS database compiled by Warr (WARR, REXS, 2012).
-These values are not constant over time, as power generation technologies change and become more efficient.
-Useful work was only analyzed for the developed economies (the United States, the United Kingdom, and Japan) from 1980--2011, because of the difficulty associated with determining $\phi$ and $\epsilon$ values.
-In order to determine these parameters, information is needed about the efficiency of different technologies and what industries/areas is consuming the most energy within an economy.
-This proved to be quite difficult for the developing, petrol, and Malthusian economies so we restricted this part of the analysis to using the data already compiled in the REXS database.
+  U = \sum{\phi_i \varepsilon_i X}
+\end{equation}
+
+***** Shouldn't this be a double-sum?
+In other words, shouldn't $X$ have a subscript, too?
+We sum the U's for all energy sources to get the total useful work for an economy, right?
+Also, the allocation factor should be specific to the COMBINATION of energy source and end use, right?
+*****
+
+\noindent where the subscript $i$ indicates the energy end use, $\varepsilon_i$ is the efficiency of each end use, and $\phi_i$ gives the fraction of each energy source that goes to the end use, where $0 \le \phi_i \le 1$.
+****** Can we list the raw energy sources and the end uses?
+*****
+
+Values of $\varepsilon_i$ and $\phi_i$ were calculated from the REXS database supplied by \citet{Warr:2012a}.
+Values of $X$ were calculated by methods discussed in Section \ref{sec:X_Data}.
+Most $\varepsilon$ values increase over time **** Are there any that don't?
+****, as power generation technologies improve.
+**** Are there any values of $\varepsilon_i$ that are not increasing with time?
+**** For most countries, values of $\phi_i$ are not constant with time, as economic sectors with different distributions of raw energy inputs grow at different rates.
+\citeapos{Warr:2012a} REXS database contains information for developed economies (United States, United Kingdom, and Japan) from 1980--2011 ****** Up to 2011?
+Isn't this 2000?
+******.
+Extending the REXS database to the BRICS, petrol, and LDC economies is beyond the scope of this work, because longitudinal data for the efficiency of different end uses ($\varepsilon_i$) and the distribution of energy sources to end uses ($\phi_i$) are extremely difficult to find.
+
+**** Do we want to graph the $\varepsilon_i$ and $\phi_i$ values over time?
+
+************* Matt ended here. ****************
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Cobb-Douglas Models Without Energy (CD)}
+\section{Cobb-Douglas Model Without Energy (CD)}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2013-04-29 EconGrowth.Rnw
Fixed heights on LINEX production function.

@@
 \item{Heun: Fix the ordering of references in the bibliography by setting the alphabetical order of the keys to match the temporal order of the references.}
-\item{Heun: Obtain answers to questions for Caleb.}
+\item{Heun: Obtain answers to questions I put to Caleb.}
 \item{Heun: Add references from Lucas.}
@@
 \item{de Wit: review, critique, and contextualize.}
+\item{\st{Heun: Fix parentheses heights in LINEX production function equation.}}
 \item{\st{Heun: Add data from 2011 to the models}}
@@
 \begin{equation} \label{eq:LINEX}
-  y = Ae; A = \mathrm{e}^{a_0\left[2 \left(1 - \frac{1}{\rho_k} \right) + c_t \left(\rho_l - 1 \right)\right]},
+  y = Ae; A = \mathrm{e}^{a_0\left[2 \left(1 - \frac{1}{\rho_k} \right) + c_t \left(\vphantom{\frac{1}{\rho_k}}\rho_l - 1 \right)\right]},
 \end{equation}
@@
 economy.
-The results of \citeauthor{Warr:2012cg} suggest that the time-dependent technological progress term ($A$) in the Cobb-Douglas and CES production functions (Equations \ref{eq:CD}, \ref{eq:CDe}, and \ref{eq:CESe}) may be a proxy for increasing energy efficiency in the U.S.
+The results of \citeauthor{Warr:2012cg} suggest that the time-dependent technological progress term ($A$) in the Cobb-Douglas and CES production functions (Equations \ref{eq:CD} -- \ref{eq:CESe}) may be a proxy for increasing energy efficiency in the U.S.
 economy.
@@
 Regardless of model (Cobb-Douglas or CES) or energy quantification ($q$, $x$, or $u$), there are few economies for which we can say with high confidence (at the 95\% level) that energy plays a significant role in economic growth.
-However, in seeming contradiction, results for the CES model indicate that energy complements capital stock and labor.
-That is, energy is essential for capital stock and labor to generate economic growth.
+However, in seeming contradiction, results for the CES model indicate that energy complements capital stock and labor, indicating that energy ($e$) is essential for capital stock ($k$) and labor ($l$) to generate economic growth.
 One possible explanation for this apparent contradiction is to consider energy as embedded within capital stock and labor: it takes energy to make both captial stock and labor available to generate economic growth.
@@
 \setcounter{table}{0} % Restarts table number counter at 0 in this section.
+\setcounter{figure}{0} % Restarts figure number counter at 0 in this section.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Single-factor Models}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Single-factor Models (SF)}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2013-04-29 EconGrowth.Rnw
Minor changes. But, did note that the bibliography is probably OK.

@@
 % From http://economics.utoronto.ca/osborne/latex/BIBTEX.HTM
-\def\citeapos#1{\citeauthor{#1}'s (\citeyear{#1})} % Posessive citations.
+\newcommand{\citeapos}[1]{\citeauthor{#1}'s (\citeyear{#1})} % Posessive citations.
 
@@
 \item{Heun: Eliminate non-developed countries from 9-panel partial residual plots.}
-\item{Heun: Fix the ordering of references in the bibliography by setting the alphabetical order of the keys to match the temporal order of the references.}
 \item{Heun: Obtain answers to questions I put to Caleb.}
@@
 \item{de Wit: review, critique, and contextualize.}
+\item{\st{Heun: Fix the ordering of references in the bibliography by setting the alphabetical order of the keys to match the temporal order of the references. I think the bibliography is OK.}}
 \item{\st{Heun: Fix parentheses heights in LINEX production function equation.}}
@@
 In the style of work by Warr and Ayres \citep{Ayres:2005kn, Warr:2010ht, Warr:2010ga, Warr:2012cg}, energy from human and animal muscle power were also included.
-Similar to the economic data discussed in Sections \ref{sec:Economic_Output_Data}--\ref{sec:Labor_Data}, we generated energy data for developed countries from 1980--2011.
+Similar to the economic data discussed in Sections \ref{sec:Economic_Output_Data}--\ref{sec:Labor_Data}, we generated energy data for developed countries from 1980--2011 (except for useful work which is limited to the years 1980--2000 **** is this date range correct?
+****).
 For all other countries, we generated energy data for 1991--2011.
@@
 \noindent The value of $E_{m,workers}$ was taken from a time series of kcal/day-person for workers in the U.S.
-from 1980--2011 \citep{Warr:2012a}.
-$E_{m,workers}$ is relatively constant over the period 1980--2011 at about ****** What is the value?
+from 1980--2011 ***** Should this be 1980--2000 ???
+******  \citep{Warr:2012a}.
+$E_{m,workers}$ is relatively constant over the period 1980--2011 ***** Should this be 1980--2000 ????
+**** at about ****** What is the value?
 *******, and the U.S.

### 2013-04-29 EconGrowthSeminar.Rnw
Adjusted spacing in one row of a table.
Switched to using EIA instead of IEA.

@@
     \begin{tabular}{r c c l}
-      \multirow{3}{*}{IEA} & \multirow{3}{*}{\includegraphics[scale=0.20]{figure_other/Figure_IEA.png}} & Coal, Oil, Petroleum, & \multirow{3}{*}{GJ/year} \\
+      \multirow{3}{*}{EIA} & \multirow{3}{*}{\includegraphics[scale=0.20]{figure_other/Figure_EIA.png}} & Coal, Oil, Petroleum, & \multirow{3}{*}{GJ/year} \\
                               &                          & Natural gas, Nuclear, & \\

### 2013-04-29 EconGrowth-R-Functions.Rnw
Detailed edits on the energy sections with Caleb.

--- 2013-04-29 EconGrowth-R-Functions.Rnw
@@
 ninePanelLayoutSpec <- c(3,3) #indicates a 3x3 arrangement of panels.
+threePanelLayoutSpec <- c(1,3) #indicates a 1 row x 3 column arangement of panels
 onePanelLayoutSpec <- c(1,1) #indicates a 1x1 arrangement of panels.
@@
     # Lattice graph will all countries is desired.
+    data <- do.call("rbind", lapply(countryAbbrevsAlph, calcResiduals, modelType=modelType, energyType=energyType))
+    # If useful work is desired, need to trim the data set.
+    if (energyType == "U"){
+print(data)
+      data <- subset(data, !is.na(iEToFit))
+print(data)
+      layout <- threePanelLayoutSpec
+      factorLevels <- countryAbbrevsAlphU # Want only those countries for which U is known
+    } else {
       factorLevels <- countryNamesAlph # We want all countries shown
       layout <- ninePanelLayoutSpec
+    }
     indexCond <- list(countryOrderForGraphs) # We want all countries in this order
-    data <- do.call("rbind", lapply(countryAbbrevsAlph, calcResiduals, modelType=modelType, energyType=energyType))
     plot <- xyplot(resid ~ iEToFit | Country, data=data,

### 2013-04-29 EconGrowth.Rnw
Detailed edits on the energy sections with Caleb.

@@
 \begin{itemize}
+\item{Reese: Review EIA IES database for any revisions to historical data.}
+\item{Reese: Add food energy intake for all countries from FAO.}
+\item{Reese: Fix the energy sankey diagram from the seminar.}
+\item{Heun: Include the adjusted sankey diagram in the seminar.}
 \item{Heun: Eliminate non-developed countries from 9-panel partial residual plots.}
@@
 \item{de Wit: review, critique, and contextualize.}
+\item{\st{Reese: Send URL reference for FAO food data.}}
 \item{\st{Heun: Fix the ordering of references in the bibliography by setting the alphabetical order of the keys to match the temporal order of the references. I think the bibliography is OK.}}
@@
 To account for all energy input to an economy, we summed consumption data for many energy sources, including coal, oil and petroleum products, dry natural gas and natural gas plant liquids, nuclear power generation, and renewable energy sources (solar, wind, geothermal, biomass/fuel wood, and hydro).
-In the style of work by Warr and Ayres \citep{Ayres:2005kn, Warr:2010ht, Warr:2010ga, Warr:2012cg}, energy from human and animal muscle power were also included.
-Similar to the economic data discussed in Sections \ref{sec:Economic_Output_Data}--\ref{sec:Labor_Data}, we generated energy data for developed countries from 1980--2011 (except for useful work which is limited to the years 1980--2000 **** is this date range correct?
-****).
+In the style of work by Warr and Ayres \citep{Ayres:2005kn, Warr:2010ht, Warr:2010ga, Warr:2012cg}, energy from human and animal muscle power was also included.
+Similar to the economic data discussed in Sections \ref{sec:Economic_Output_Data}--\ref{sec:Labor_Data}, we generated energy data for developed countries from 1980--2000.
 For all other countries, we generated energy data for 1991--2011.
@@
 \noindent where $C_{fuel}$ is the consumption rate of the fuel (in units of short tons/year for coal, barrels/year for oil and petroleum, ft$^3$/year for dry natural gas and natural gas plant liquids, and m$^3$/year for biomass/fuel wood) and $h_{{fuel}}$ is the heat content of the fuel (in kJ/short ton for coal, kJ/barrel for oil, kJ/ft$^3$ for dry natural gas and natural gas plant liquids, and kJ/kg for biomass/fuel wood).
-******* Need a fuelwood density to convert between m3/year and kJ/kg.
-*******
-
-Yearly consumption rates ($C_{fuel}$) for all economies were obtained from the International Energy Agency \citep{IEA:2013a} for coal, oil and petroleum, and dry natural gas and natural gas plant liquids.
-Yearly average heat content data  for coal, oil, and natural gas and natural gas plant liquids was obtained from the IEA for all economies.
+The fuel wood density of 166.67 kg/m$^3$ was obtained from the \citet{FAO:2013a} **** Caleb: verify this number and source ****.
+
+Yearly consumption rates ($C_{fuel}$) for all economies were obtained from the Energy Information Agency \citep{EIA:2013a} for coal, oil and petroleum, and dry natural gas and natural gas plant liquids.
+Yearly average heat content data  for coal, oil, and natural gas and natural gas plant liquids was obtained from the EIA for all economies.
 Yearly consumption and heat content data for biomass/fuel wood was obtained from the ``Fuelwood'' time series of the FAO Statistics Database \citep{FAO:2013a}.
 
-For renewable and nuclear energies, yearly electricity generation (in BTU/year) was available directly from the IEA \citep{IEA:2013a} for all economies, so Equation \ref{eq:thermal_energy} was not necessary.
-
-************** Should all of the following calculations have $Q_m$ instead of $E_m$, because we're talking specifically about thermal energy here. Or, is $E_m$ correct? *************
+For renewable and nuclear energies, yearly electricity generation (in BTU/year) was available directly from the \citet{EIA:2013a} for all economies, so Equation \ref{eq:thermal_energy} was not necessary.
 
@@
 \begin{equation} \label{eq:animal_muscle}
-  E_{animals} = E_{m,horse}N_{horses} + E_{m,mule}N_{mules}
-\end{equation}
-
-\noindent where $E_m$ is metabolizable energy (in kcal/day-animal) and $N$ is the number of animals.
-Metabolizable energy values were taken from \citet{Warr:2012a} for horses and mules and represent the amount of energy used to ****** feed?
-****** the animals for a days work.
-The value of $E_m$ was assumed constant for all economies and years.
-***** What was the value?
-******* The number of horses and mules for each economy was taken from the ``Live Animals'' time series on the FAO Statistics Database \citep{FAO:2013a}.
-The animal feed-to-work conversion efficiency was taken from \citet{Warr:2012a} and assumed equal across all economies.
-******** Why is this important here?
-Should the feed-to-work conversion efficiency be employed in the sections below?
-Or, was the feed-to-work effiency used to calculate $E_m$?
-In any case, what was the value of the feed-to-work efficiency?
-**********
-
-Human muscle power was calculated in a similar manner.
+  Q_{animals} = Q_{m,horse}N_{horses} + Q_{m,mule}N_{mules}
+\end{equation}
+
+\noindent where $Q_m$ is metabolizable energy (in kcal/day-animal) and $N$ is the number of animals.
+Metabolizable energy values ($Q_{m,horses}$ = 19,110 kcal/day-horse and $Q_{m,mules}$ = 7,215 kcal/day-mule) were taken from \citet{Warr:2012a} for horses and mules and represent the amount of energy used by animals for a day of work.
+The $Q_m$ values are assumed constant for all countries and years.
+The number of horses and mules for each economy was taken from the ``Live Animals'' time series in the FAO Statistics Database \citep{FAO:2013a}.
+
+Human muscle power was calculated in a similar manner
 
 \begin{equation} \label{eq:human_muscle}
-  E_{workers} = E_{m,workers} N_{workers}
-\end{equation}
-
-\noindent The value of $E_{m,workers}$ was taken from a time series of kcal/day-person for workers in the U.S.
-from 1980--2011 ***** Should this be 1980--2000 ???
-******  \citep{Warr:2012a}.
-$E_{m,workers}$ is relatively constant over the period 1980--2011 ***** Should this be 1980--2000 ????
-**** at about ****** What is the value?
-*******, and the U.S.
-time series was assumed to apply to all economies.\footnote{The assumption that U.S.
-per-worker food intake applies to all economies introduces minor errors in human muscle work estimates for the various economies.
-However, human muscle work is never more than ****** \% of total energy consumption for any of the economies in this study, and we estimate that the error caused by this assumption is always less than ***** \% of total energy consumption for all economies.} The value for $N_{workers}$ was obtained from the labor time series for each economy as discussed in Section \ref{sec:Labor_Data}.
+  Q_{workers} = Q_{m,workers} N_{workers}
+\end{equation}
+
+\noindent where the value of $Q_{m,workers}$ for the U.S.
+was taken from a time series of kcal/day-person for workers for 1980--2011 \citep{Warr:2012a} ($\sim$ 4200 kcal/day-worker).
+$Q_{m,workers}$ for other countries was taken from the \citet{FAO:2013b}.
+The value for $N_{workers}$ was obtained from the labor time series for each economy as discussed in Section \ref{sec:Labor_Data}.
 
@@
 $f_{exergy-allocation}$ is the ratio of chemical exergy to the higher heating value for each fuel.
-***** Is this right?
-Are the $X$ values larger than the $Q$ values?
-******* $f_{exergy-allocation}$ for each fuel was assumed to be constant through time across all economies.
+$f_{exergy-allocation}$ for each fuel was assumed to be constant through time across all economies.
 For renewable and nuclear energy sources, the electricity generated is already pure exergy, so $f_{exergy-allocation}$ is unity.
@@
       \hline
-      Coal                                    & ****    \\
-      Oil and petroleum                       & *****   \\      
-      Dry natural gas and                     & \multirow{2}{*}{******}    \\
+      Coal                                    & 1.088    \\
+      Oil and petroleum                       & 1.073   \\      
+      Dry natural gas and                     & \multirow{2}{*}{1.040}    \\
       natural gas liquids                     &         \\
-      Biomass/fuel wood                       & *****   \\
-      Nuclear                                 & 1.0     \\
-      Renewables                              & 1.0     \\
+      Biomass/fuel wood                       & 1.150   \\
+      Nuclear                                 & 1.000   \\
+      Renewables                              & 1.000   \\
     \end{tabular}
@@
 
-To calculate the exergy of animal and human muscle power, the food-to-work conversion efficiency ($\eta_{food \rightarrow work}$) and the ratio of food end-use to food intake ($f_{enduse \rightarrow intake}$) were included.
+To calculate the exergy of animal and human muscle power, the food-to-work conversion efficiency ($\eta_{food \rightarrow work}$) and the ratio of food end-use to food intake ($f_{enduse/intake}$) were included.
 $\eta_{food \rightarrow work, animals}$ and $\eta_{food \rightarrow work, workers}$ are animal and worker efficiency of converting food into energy respectively.
-The values for $\eta_{food \rightarrow work, animals}$ = ***** and $\eta_{food \rightarrow work, workers}$ = ***** were taken from \citet{Ayres:2010ug}.
-For workers, an additional factor ($f_{enduse \rightarrow intake}$ = ********), which accounts for food energy that is used to sustain the body's normal function as opposed to providing energy for physical labor \citep{Wirsenius:2000vi}.
-A similar ratio could also be applied to animal work, but it was unavailable from \citet{Wirsenius:2000vi}.\footnote{The error in neglecting $f_{enduse \rightarrow intake}$ for animals is very small, because animal muscle exergy is a small fraction of the total energy supply to any economy, with a maximum of **** \% for ****** in ****** year ******.}
+The animal feed-to-work conversion efficiency ($\eta_{food \rightarrow work, animals}$ = 0.4) was taken from \citet{Warr:2012a} and assumed equal across all economies.
+The worker food-to-work efficiency ($\eta_{food \rightarrow work, workers}$ = 0.2) was taken from \citet{Ayres:2010ug}.
+Following \citet[p.~315]{Ayres:2010ug}, an additional factor ($f_{enduse/intake}$) was included to account for workers' food energy that sustains the body's normal function as opposed to providing energy for physical labor \citep{Wirsenius:2000vi}.
+$f_{enduse/intake}$ varies by country.
+A similar enduse-to-intake ratio could also be applied to animal work, but it was unavailable from \citet{Wirsenius:2000vi}.\footnote{The error in exergy caused by neglecting $f_{enduse/intake}$ for animals is very small, because animal muscle exergy is a small fraction of the total energy supply to any economy, with a maximum of 4.1\% for China in 1992.}
+
+\begin{table} \caption{Food end use to intake ratios for all countries.} \label{tab:f_enduse_intake}
+  \begin{center}
+    \begin{tabular}{r c c c c c c c c c}
+      Country & US & UK & JP & CN & ZA & SA & IR & TZ & ZM \\
+      \hline
+      $f_{enduse/intake}$ & 0.62 & 0.65 & 0.76 & 0.76 & 0.87 & 0.72 & 0.72 & 0.72 & 0.72\\
+    \end{tabular}
+  \end{center}
+\end{table}
 
 \begin{equation} \label{eq:animal_muscle_exergy}
-  X_{animals} = \eta_{food \rightarrow work,animals} E_{animals}
+  X_{animals} = \eta_{food \rightarrow work,animals} Q_{animals}
 \end{equation}
@@
 \begin{equation} \label{eq:human_muscle_exergy}
-  X_{workers} = \eta_{food \rightarrow work,workers} f_{enduse \rightarrow intake} E_{workers}
+  X_{workers} = \eta_{food \rightarrow work,workers} f_{enduse/intake} Q_{workers}
 \end{equation}
@@
 The conversion of a raw energy carrier (e.g., coal) into productive energy for an economy (e.g., electricity) necessarily involves inefficiencies.
-In the case of coal consumption, only about one-third ****** Is this the number we want to use?
-****** of the heat content of coal is converted to useful electricity, the rest is waste heat.
-The concept of ``useful work,'' pioneered by \citet{Ayres:2005kn}, takes exergy one step further to consider efficiencies of both energy production and end use.
-To calculate useful work ($U$), each source of exergy (coal, oil and petroleum products, dry natural gas and natural gas plant liquids, biomass/fuel wood, nuclear, solar, wind, and human and animal muscle work) is decomposed into several end uses: high temperature heat (for electricity production **** anything else?
-****), medium temperature heat (**** for ????
-****), low temperature heat (for residential heating **** anything else?
-****), mechanical drive (**** for ????
-****), electricity (**** for ????
-****), light, and muscle work.
-The efficiency of each combination of energy source and end use in an economy can be very different, e.g.
-the efficiency of a coal fired power plant (high temperature heat source, $\sim$30\%) will be very different from a residential heating system (low temperature heat source, $\sim$****\%).
-Efficiencies specific to each combination of energy source and end use were applied to exergy values to obtain useful work ($U$) input to an economy with the following equation:
+In the case of coal consumption, only about one-third of the coal exergy is converted to useful electricity, the rest is waste heat.
+The concept of ``useful work,'' pioneered by Ayres and Warr \citep{Ayres:2003ec, Ayres:2005kn}, takes exergy one step further to consider efficiencies of both energy production and end use.
+To calculate useful work ($U$), each source of exergy (coal, oil and petroleum products, dry natural gas and natural gas plant liquids, biomass/fuel wood, nuclear, solar, wind, and human and animal muscle work) is decomposed into several end uses: high temperature industrial heat (e.g., steel production), medium temperature heat (e.g., steam production), low temperature space heat (for residential heating), mechanical drive (energy used for prime mover engines of all types except electric motors), electricity (excluding lighting), light (from both electricity and fuels), and muscle work (from animals and workers).
+The efficiency ($\varepsilon$) of convering exergy into useful work can be very different, depending upon the end use of the exergy.
+Efficiencies specific to each end use ($\varepsilon_i$) were applied to exergy values to obtain useful work ($U$) input to an economy with the following equation:
 
 \begin{equation} \label{eq:useful_work}
-  U = \sum{\phi_i \varepsilon_i X}
-\end{equation}
-
-***** Shouldn't this be a double-sum?
-In other words, shouldn't $X$ have a subscript, too?
-We sum the U's for all energy sources to get the total useful work for an economy, right?
-Also, the allocation factor should be specific to the COMBINATION of energy source and end use, right?
-*****
-
-\noindent where the subscript $i$ indicates the energy end use, $\varepsilon_i$ is the efficiency of each end use, and $\phi_i$ gives the fraction of each energy source that goes to the end use, where $0 \le \phi_i \le 1$.
-****** Can we list the raw energy sources and the end uses?
-*****
+  U = \sum_i{\varepsilon_i \phi_i X}
+\end{equation}
+
+\noindent where the subscript $i$ indicates the energy end use, $\varepsilon_i$ is the efficiency of converting exergy into useful energy for each end use, and $\phi_i$ gives the fraction of exergy input to an economy that goes toward the i$^\mathrm{th}$ end use.
 
@@
 Values of $X$ were calculated by methods discussed in Section \ref{sec:X_Data}.
-Most $\varepsilon$ values increase over time **** Are there any that don't?
-****, as power generation technologies improve.
-**** Are there any values of $\varepsilon_i$ that are not increasing with time?
-**** For most countries, values of $\phi_i$ are not constant with time, as economic sectors with different distributions of raw energy inputs grow at different rates.
-\citeapos{Warr:2012a} REXS database contains information for developed economies (United States, United Kingdom, and Japan) from 1980--2011 ****** Up to 2011?
-Isn't this 2000?
-******.
-Extending the REXS database to the BRICS, petrol, and LDC economies is beyond the scope of this work, because longitudinal data for the efficiency of different end uses ($\varepsilon_i$) and the distribution of energy sources to end uses ($\phi_i$) are extremely difficult to find.
-
-**** Do we want to graph the $\varepsilon_i$ and $\phi_i$ values over time?
+For most countries, values of $\phi_i$ are not constant with time, as economic sectors with different distributions of raw exergy inputs grow at different rates.
+\citeapos{Warr:2012a} REXS database contains information for developed economies (United States, United Kingdom, and Japan) from 1900--2000, but we are using data in the 1980--2000 timeframe.
+Extending the REXS database to the BRICS, petrol, and LDC economies is beyond the scope of this work, because longitudinal data for the efficiency of different end uses ($\varepsilon_i$) and the distribution of exergy sources to end uses ($\phi_i$) are extremely difficult to find.
 

### 2013-04-30 EconGrowthSeminar.Rnw
Now includeing an EIA graphic for the seminar.

@@
     \begin{tabular}{r c c l}
-      \multirow{3}{*}{EIA} & \multirow{3}{*}{\includegraphics[scale=0.20]{figure_other/Figure_EIA.png}} & Coal, Oil, Petroleum, & \multirow{3}{*}{GJ/year} \\
+      \multirow{3}{*}{EIA} & \multirow{3}{*}{\includegraphics[scale=0.07]{figure_other/Figure_EIA.png}} & Coal, Oil, Petroleum, & \multirow{3}{*}{GJ/year} \\
                               &                          & Natural gas, Nuclear, & \\
@@
       \hline
-      \multirow{2}{*}{FAOStat} & \multirow{2}{*}{\includegraphics[scale=0.06]{figure_other/Figure_FAOStat.png}} & Fuel wood,    & \multirow{2}{*}{GJ/year} \\
+      \multirow{2}{*}{FAOStat} & \multirow{2}{*}{\includegraphics[scale=0.065]{figure_other/Figure_FAOStat.png}} & Fuel wood,    & \multirow{2}{*}{GJ/year} \\
                               &                          & Available livestock &                                \\

### 2013-04-30 EconGrowth.Rnw
Updated references.

@@
 \begin{itemize}
-\item{Reese: Review EIA IES database for any revisions to historical data.}
-\item{Reese: Add food energy intake for all countries from FAO.}
-\item{Reese: Fix the energy sankey diagram from the seminar.}
-\item{Heun: Include the adjusted sankey diagram in the seminar.}
-\item{Heun: Eliminate non-developed countries from 9-panel partial residual plots.}
-\item{Heun: Obtain answers to questions I put to Caleb.}
-\item{Heun: Add references from Lucas.}
+\item{Reese: Review EIA IES database for any revisions to historical data}
+\item{Reese: Add food energy intake for all countries from FAO}
+\item{Reese: Fix the energy sankey diagram from the seminar}
+\item{Heun: Include the adjusted sankey diagram in the seminar}
+\item{Heun: Eliminate non-developed countries from 9-panel partial residual plots}
+\item{Heun: Add references from Lucas}
 \item{Heun: Add CES production function fits}
@@
 \item{de Wit: review, critique, and contextualize.}
+\item{\st{Heun: Obtain answers to questions I put to Caleb about the energy section}}
+\item{\st{Heun: Add Warr to acknowledgements}}
+\item{\st{Heun: Include EIA graphic (instead of IEA graphic) in the seminar}}
 \item{\st{Reese: Send URL reference for FAO food data.}}
@@
 
-Total employment and average hours worked per worker per year for the developed nations (United States, United Kingdom, and Japan) for 1980--2011 were obtained from the United States \citet{BLS:2013a}.
+Total employment and average hours worked per worker per year for the developed nations (United States, United Kingdom, and Japan) for 1980--2011 were obtained from the United States \citet[Tables 6 and 7]{BLS:2013a}.
 Total hours worked per year was calculated by multiplying total employment by average hours worked per worker per year.
@@
 Heun (Western Michigan University) for insightful critique of the statistical analyses presented herein.
+The authors are grateful to Benjamin S.
+Warr (INSEAD) for providing the REXS database \citep{Warr:2012a}.
 

### 2013-04-30 EconGrowth-R-Functions.Rnw
Partial residual plots for U now include only US, UK, and JP, the countries for which U data is available.

--- 2013-04-29 EconGrowth-R-Functions.Rnw
@@
 countryOrderForGraphs <- c(7,6,3,1,8,5,4,2,9) # Sets the order as US, UK, JP, CN, ZA, TZ, SA, IR, ZM.
+countryOrderForGraphsU <- c(3, 2, 1) # Sets the order as US, UK, JP when we're looking only at energyType=U.
 timeTics <- c(1980, 1990, 2000, 2010)
@@
 ninePanelLayoutSpec <- c(3,3) #indicates a 3x3 arrangement of panels.
+threePanelLayoutSpec <- c(3,1) #indicates a 1 row x 3 column arangement of panels
 onePanelLayoutSpec <- c(1,1) #indicates a 1x1 arrangement of panels.
@@
     # Lattice graph will all countries is desired.
+    data <- do.call("rbind", lapply(countryAbbrevsAlph, calcResiduals, modelType=modelType, energyType=energyType))
+    # If useful work is desired, need to trim the data set.
+    if (energyType == "U"){
+      # Use data from only those countries that have U defined.
+      data <- subset(data, !is.na(iEToFit))
+print(data)
+      layout <- threePanelLayoutSpec
+      factorLevels <- countryAbbrevsAlphU # Want only those countries for which U is known
+print(factorLevels)
+      indexCond <- list(countryOrderForGraphsU) # Orders as US, UK, JP
+    } else {
+      # Use data from all countries, because all countries have Q and X data.
       factorLevels <- countryNamesAlph # We want all countries shown
       layout <- ninePanelLayoutSpec
-    indexCond <- list(countryOrderForGraphs) # We want all countries in this order
-    data <- do.call("rbind", lapply(countryAbbrevsAlph, calcResiduals, modelType=modelType, energyType=energyType))
+      indexCond <- list(countryOrderForGraphs) # Orders as US, UK, JP, CN, ZA, SA, IR, TZ, ZM
+    }
     plot <- xyplot(resid ~ iEToFit | Country, data=data,

### 2013-04-30 EconGrowth.Rnw
Partial residual plots for U now include only US, UK, and JP, the countries for which U data is available.

@@
 \item{Heun: Eliminate non-developed countries from 9-panel partial residual plots}
-\item{Heun: Add references from Lucas}
 \item{Heun: Add CES production function fits}
@@
 \item{Heun: adjust y axis limits on $a_0$ and $c_t$ parameter graphs for the LINEX model AFTER we finish debugging the LINEX models.}
-\item{de Wit: provide funding acknowledgement, if necessary.}
 \item{de Wit: review, critique, and contextualize.}
+\item{\st{Heun: Add references from Lucas}}
 \item{\st{Heun: Obtain answers to questions I put to Caleb about the energy section}}
@@
       \end{itemize}
+\item{\st{de Wit: provide funding acknowledgement, if necessary}}
 \end{itemize}
@@
 In this paper, we assess three prominent energy-augmented production functions appear in the literature: Cobb-Douglas (CDe), Constant Elasticity of Substitution (CESe), and LINear EXponential (LINEX).
-The following sections describe each.
+The following subsections describe each.
 
@@
 
-\begin{table} \caption{Food end use to intake ratios for all countries.} \label{tab:f_enduse_intake}
+\begin{table} \caption{Food enduse-to-intake ratios for all countries.} \label{tab:f_enduse_intake}
   \begin{center}
@@
 
-<<CDPartialResidualsU, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="Cobb-Douglas partial residuals plot for useful work ($u$).", fig.pos="H">>=
+<<CDPartialResidualsU, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="Cobb-Douglas partial residuals plot for useful work ($u$).", fig.pos="H", eval=TRUE>>=
 createPartialResidualPlot(modelType="CD", energyType="U", countryAbbrev=NA)
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Cobb-Douglas Models With Energy}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%++++++++++++++++++++++++++++++
 \subsection{CES without energy (CES)}
+%++++++++++++++++++++++++++++++
 
@@
 
+%++++++++++++++++++++++++++++++
 \subsection{CES with Thermal Energy}
+%++++++++++++++++++++++++++++++
 
@@
 
+%++++++++++++++++++++++++++++++
 \subsection{CES with Exergy}
+%++++++++++++++++++++++++++++++
 
@@
 
+%++++++++++++++++++++++++++++++
 \subsection{CES with Useful Work}
+%++++++++++++++++++++++++++++++
 
@@
 
+%++++++++++++++++++++++++++++++
 \subsection{CES comparisons}
+%++++++++++++++++++++++++++++++
 
@@
 
+%++++++++++++++++++++++++++++++
 \subsection{LINEX with Thermal Energy}
+%++++++++++++++++++++++++++++++
 
@@
 
+%++++++++++++++++++++++++++++++
 \subsection{LINEX with Exergy}
+%++++++++++++++++++++++++++++++
 
@@
 
+%++++++++++++++++++++++++++++++
 \subsection{LINEX with Useful Work}
+%++++++++++++++++++++++++++++++
 
@@
 
+%++++++++++++++++++++++++++++++
 \subsection{LINEX comparisons}
+%++++++++++++++++++++++++++++++
 
@@
 Support for Matthew Kuperus Heun was provided by a Calvin College Research Followship.
-Funding for Martin de Wit was provided by *******.
+Partial funding for Martin de Wit was provided by the South African National Research Foundation (NRF).\footnote{Any opinion, findings, and conclusions or recommendations expressed herein are those of the authors, and, therefore, NRF does not accept any liability in regard thereto.} The authors are grateful to Benjamin S.
+Warr (INSEAD) for providing the REXS database \citep{Warr:2012a}.
 The authors thank Loren L.
 Heun (Western Michigan University) for insightful critique of the statistical analyses presented herein.
-The authors are grateful to Benjamin S.
-Warr (INSEAD) for providing the REXS database \citep{Warr:2012a}.
 
@@
 \section{Model Parameters}
+\label{sec:Model_Parameters}
 \setcounter{table}{0} % Restarts table number counter at 0 in this section.
 \setcounter{figure}{0} % Restarts figure number counter at 0 in this section.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+\setcounter{equation}{0} % Restarts equation counter to 0 in this section.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%++++++++++++++++++++++++++++++
 \subsection{Single-factor Models}
-
-We begin by fitting single-factor economic models of the form
-
-\begin{equation} \label{eq:Single_Factor_Generic}
-  y = \mathrm{e}^{\lambda (t-t_0)}f^{m}
-\end{equation}
-
-\noindent to historical data where the factor of production ($f$) is one of $k$, $l$, $q$, $x$, or $u$, and the exponent ($m$) is $\alpha$ for $k$, $\beta$ for $l$, or $\gamma$ for $q$, $x$, and $u$.
-
-<<SFk_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $k$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createSFParamsGraph(factor="K")
-@
-
-<<SFl_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $l$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createSFParamsGraph(factor="L")
-@
-
-<<SFq_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $q$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createSFParamsGraph(factor="Q")
-@
-
-<<SFx_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $x$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createSFParamsGraph(factor="X")
-@
-
-<<SFu_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $u$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createSFParamsGraph(factor="U")
-@
-
-Figure \ref{fig:SF_GDP_Lattice_Graph} compares single-factor model predictions with historical data.
-
-<<SF_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="Single-factor results.">>=
-createSFLatticeGraph()
-@
+%++++++++++++++++++++++++++++++
+
+****** This subsection should be either (a) deleted or (b) moved into the main body of the paper.
+I would prefer to delete it on the grounds that single-factor models are not often used in the literature.
+However, I want to talk with Martin about this before making the decision.
+So, I'm parking it here for now.
+--Matt.
+********
 
@@
 
+%++++++++++++++++++++++++++++++
 \subsection{Cobb-Douglas Models}
+%++++++++++++++++++++++++++++++
 
@@
 
+%++++++++++++++++++++++++++++++
 \subsection{CES Models}
+%++++++++++++++++++++++++++++++
 
@@
 
+%++++++++++++++++++++++++++++++
 \subsection{LINEX Models}
+%++++++++++++++++++++++++++++++
 
@@
 \section{Goodness of fit}
+\label{sec:Goodness_of_Fit}
 \setcounter{table}{0} % Restarts table number counter at 0 in this section.
 \setcounter{figure}{0} % Restarts figure number counter at 0 in this section.
+\setcounter{equation}{0} % Restarts equation counter to 0 in this section.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
       table.placement="H")
+@
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Single-factor Models}
+\label{sec:Single-factor_Models}
+\setcounter{table}{0} % Restarts table number counter at 0 in this section.
+\setcounter{figure}{0} % Restarts figure number counter at 0 in this section.
+\setcounter{equation}{0} % Restarts equation counter to 0 in this section.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+****** This section should be either (a) deleted or (b) moved into the main body of the paper.
+I would prefer to delete it on the grounds that single-factor models are not often used in the literature.
+However, I want to talk with Martin about this before making the decision.
+So, I'm parking it here for now.
+--Matt.
+********
+
+We begin by fitting single-factor economic models of the form
+
+\begin{equation} \label{eq:Single_Factor_Generic}
+  y = \mathrm{e}^{\lambda (t-t_0)}f^{m}
+\end{equation}
+
+\noindent to historical data where the factor of production ($f$) is one of $k$, $l$, $q$, $x$, or $u$, and the exponent ($m$) is $\alpha$ for $k$, $\beta$ for $l$, or $\gamma$ for $q$, $x$, and $u$.
+
+<<SFk_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $k$) model parameters.
+Vertical bars indicate 95\\% confidence intervals.">>=
+createSFParamsGraph(factor="K")
+@
+
+<<SFl_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $l$) model parameters.
+Vertical bars indicate 95\\% confidence intervals.">>=
+createSFParamsGraph(factor="L")
+@
+
+<<SFq_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $q$) model parameters.
+Vertical bars indicate 95\\% confidence intervals.">>=
+createSFParamsGraph(factor="Q")
+@
+
+<<SFx_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $x$) model parameters.
+Vertical bars indicate 95\\% confidence intervals.">>=
+createSFParamsGraph(factor="X")
+@
+
+<<SFu_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $u$) model parameters.
+Vertical bars indicate 95\\% confidence intervals.">>=
+createSFParamsGraph(factor="U")
+@
+
+Figure \ref{fig:SF_GDP_Lattice_Graph} compares single-factor model predictions with historical data.
+
+<<SF_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="Single-factor results.">>=
+createSFLatticeGraph()
 @

### 2013-04-30 EconGrowth-R-Functions.Rnw
Now 3-panel partial residual plots for U are nearly same height as panels in the 9-panel partial residual plots.

@@
 onePanelLayoutSpec <- c(1,1) #indicates a 1x1 arrangement of panels.
+threePanelGraphWidth <- maxWidth
+threePanelGraphHeight <- 3.3 #Inches
 ninePanelGraphWidth <- maxWidth     
@@
       data <- subset(data, !is.na(iEToFit))
-print(data)
       layout <- threePanelLayoutSpec
       factorLevels <- countryAbbrevsAlphU # Want only those countries for which U is known
-print(factorLevels)
       indexCond <- list(countryOrderForGraphsU) # Orders as US, UK, JP

### 2013-04-30 EconGrowth.Rnw
Now 3-panel partial residual plots for U are nearly same height as panels in the 9-panel partial residual plots.

@@
 \item{Heun: Include the adjusted sankey diagram in the seminar}
-\item{Heun: Eliminate non-developed countries from 9-panel partial residual plots}
+\item{Heun: Adjust variable threePanelGraphHeight in the Functions file to produce U partial residual plots that are exactly the same size as the graphs in the 9-panel plots.}
 \item{Heun: Add CES production function fits}
@@
 \item{de Wit: review, critique, and contextualize.}
+\item{\st{Heun: Eliminate non-developed countries from 9-panel partial residual plots}}
 \item{\st{Heun: Add references from Lucas}}
@@
 
-<<CDPartialResidualsU, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="Cobb-Douglas partial residuals plot for useful work ($u$).", fig.pos="H", eval=TRUE>>=
+<<CDPartialResidualsU, fig.width=threePanelGraphWidth, fig.height=threePanelGraphHeight, fig.align="center", fig.cap="Cobb-Douglas partial residuals plot for useful work ($u$).", fig.pos="H">>=
 createPartialResidualPlot(modelType="CD", energyType="U", countryAbbrev=NA)

### 2013-04-30 EconGrowth.Rnw
Did an extensive edit of the first three sections of the paper.

@@
 
-\noindent where $y \equiv Y/Y_\mathrm{0}$, $k \equiv K/K_\mathrm{0}$, and $l \equiv L/L_\mathrm{0}$; with $Y$ represented by GDP, $K$ expressed in currency units, $L$ expressed in workers/year or work-hours/year, time ($t$) measured in years, e being the base of the natural logarithm, and subscripts ``0'' indicating values at an initial year.
+\noindent where $y \equiv Y/Y_\mathrm{0}$, $k \equiv K/K_\mathrm{0}$, and $l \equiv L/L_\mathrm{0}$; with $Y$ represented by GDP, $K$ expressed in currency units, $L$ expressed in workers/year or work-hours/year, time ($t$) measured in years, with e being the base of the natural logarithm, and subscripts ``0'' indicating values at an initial year.
 $A$ is a unitless technological progress term, with $\lambda$ indicating the pace of technological progress (in units of year$^{-1}$).\footnote{Dimensionless, indexed quantities are represented by lower-case symbols ($y$, $k$, $l$, $e$, $q$, $x$, and $u$), and dimensional quantities are represented by upper-case symbols ($Y$, $K$, $L$, $E$, $Q$, $X$, and $U$).
-One exception is the technolgical progress term $A$, which is dimensionless but written in upper-case by convention.} Neoclassical economic growth theory makes no attempt to understand the mechanisms by which technological progress ($A$) affects economic growth, nor does it attempt to describe how technological progress ($A$) might vary from one economy to the next.
+One exception is the technolgical progress term $A$, which is dimensionless but written in upper-case by convention.} Neoclassical economic growth theory as expressed in the Cobb-Douglas production function makes no attempt to describe the mechanisms by which technological progress ($A$) affects economic growth, nor does it attempt to describe how technological progress ($A$) might vary from one economy to the next.
 Mathematically, $A$ is a fitting parameter that aligns the predictions of Equation \ref{eq:CD} with historical data.
@@
 As shown in Equation \ref{eq:CD} above, neoclassical economic theory does not include an explicit term for the role of energy in economic growth.
-However, \citet{Bashmakov:2007ek} and \citet{Murphy:2011jh} indicate that the importance of energy may far outweigh its cost share in the economy.
+However, \citet{Bashmakov:2007ek}, \citet{Hamilton:2009ui}, \citet{Murphy:2011jh}, \citet{Benes:2012tm}, \citet{Kumhof:2012ua}, and others indicate that the importance of energy for economic growth may far outweigh its cost share in the economy.
 That neoclassical economic growth theory ignores energy is, therefore, cause for concern, and inquiry into the proper approach for including energy as a factor of production in economic growth modeling is both relevant and important.
 
-Some energy economists augment economic growth models with energy being an additional (or the only) factor of production.
+Some energy economists augment economic growth models by including energy as an additional (or the only) factor of production.
 However, there is little agreement on how this should be done.
 Neither the mathematical form of the energy-augmented production function nor the quantification of energy are consistent in the literature.
-Furthermore, there has been little empirical work done to assess the predictive ability of various energy-augmented production functions for different types of economies.
-In addition, very few studies of the importance of energy in economic growth include rigorous statistical assessments of energy-related fitting parameters.
+There has been little empirical work assessing the predictive ability of various energy-augmented production functions for different types of economies.
+And, very few studies of the importance of energy in economic growth include rigorous statistical assessments of energy-related fitting parameters.
 This paper attempts to contribute to the literature by applying statistically rigorous methods along three coordinates of analysis: form of the energy augmented production function, energy quantification, and type of economy.
@@
 
-\noindent where $e \equiv E/E_0$, and $E$ is in units of energy per time.
+\noindent where $e \equiv E/E_0$, and $E$ is in units of energy per time, typically TJ/year.
 The energy-augmented Cobb-Douglas production function is often assumed to have constant returns to scale for the three factors of production: $\alpha + \beta + \gamma = 1$.
@@
 **************** Martin: add more here about the conclusions of each paper regarding the role of energy in economic growth?
+Add additional literature?
+Or, adjust as you see fit.
 Especially, are there any confidence intervals or statistical evaluation in each of these studies?
@@
 
-\noindent where the elasticity of substitution between capital ($k$) and labor ($l$) is given by $\sigma_1 = \frac{1}{1+\rho_1}$, the elasticity of substitution between ($kl$) and ($e$) is given by $\sigma = \frac{1}{1+\rho}$, $\delta \in [0, 1]$ describes the importance of ($kl$) relative to ($e$), and $\gamma$ is a fitting parameter, expected to be close to unity.
-Equation \ref{eq:CESe} augments a standard CES production function (Equation \ref{eq:CES}) with energy using a ($kl$)($e$) nesting structure, as is typical in the literature.
+\noindent Equation \ref{eq:CESe} augments a standard CES production function (Equation \ref{eq:CES}) with energy using a ($kl$)($e$) nesting structure, as is typical in the literature.
 Equation \ref{eq:CES} is a degenerate form of Equation \ref{eq:CESe} where $\delta = 1$.
+The elasticity of substitution between capital ($k$) and labor ($l$) is given by $\sigma_1 = \frac{1}{1+\rho_1}$, the elasticity of substitution between ($kl$) and ($e$) is given by $\sigma = \frac{1}{1+\rho}$, $\delta \in [0, 1]$ describes the importance of ($kl$) relative to ($e$), and $\gamma$ is a fitting parameter, expected to be close to unity.
 
@@
 \citeauthor{VanderWerf:2008tc} concludes that ($kl$)($e$) nesting structure best fits historical data.
-******** Any confidence intervals in this study?
-********* \citet{Lecca:2011kr} also evaluate a variety of CES production functions using a KLEM structure to determine how the various options for nesting the energy factor of production affect predictive ability.
+\citet{Lecca:2011kr} also evaluate a variety of CES production functions using a KLEM structure to determine how the various options for nesting the energy factor of production affect predictive ability.
 \citet{Stern:2012ey} also use a CES production function of the form ($kl$)($e$).
 \citeauthor{Stern:2012ey} apply their CES function to the Swedish economy from 1800-2000 and demonstrate the importance of the transition from wood to fossil fuels for economic growth.
+
+**************** Martin: add more here about the conclusions of each paper regarding the role of energy in economic growth?
+Add additional literature?
+Or, adjust as you see fit.
+Especially, are there any confidence intervals or statistical evaluation in each of these studies?
+********************
 
@@
 
-\noindent and represent (a) capital stock increase relative to the average of labor and energy and (b) the increase of labor ($l$) relative to energy ($e$), respectively.
-Energy ($e$) as a the only factor of production is enhanced by $A$ if either
+\noindent and represent (a) capital stock increase relative to the average of labor and energy and (b) labor increase relative to energy, respectively.
+Energy ($e$), as the only factor of production, is enhanced by $A$ if either
 
@@
 
-In contrast to both the Cobb-Douglas model (Equations \ref{eq:CD} and \ref{eq:CDe}) and the CES model (Equations \ref{eq:CES} and \ref{eq:CESe}), the LINEX model (Equation \ref{eq:LINEX}) accounts for efficiencies among capital, labor, and energy directly and, therefore, does not employ a time-dependent technical progress term ($A$).
+In contrast to both the Cobb-Douglas model (Equations \ref{eq:CD} and \ref{eq:CDe}) and the CES model (Equations \ref{eq:CES} and \ref{eq:CESe}), the LINEX model (Equation \ref{eq:LINEX}) accounts for efficiencies among capital, labor, and energy directly and, therefore, does not employ a time-dependent technological progress term ($A$).
 \citet{Kummel:2002tx} use the LINEX production function to describe economic output for the economies of the U.S., Japan, and Germany.
@@
 
-**************** Martin: More on the results of the above papers. ***************
+**************** Martin: add more here about the conclusions of each paper regarding the role of energy in economic growth?
+Add additional literature?
+Or, adjust as you see fit.
+Especially, are there any confidence intervals or statistical evaluation in each of these studies?
+********************
 
@@
 Thermal energy ($Q$) is the heat content of an energy carrier.
-Exergy ($X$) is the maximum useful work that can be extracted from an energy carrier by a process that brings the system into equilibrium with a heat reservoir (typically the surrounding environment).
-Useful work ($U$) includes the direct energy that goes into an economy, including work from machines, human muscles, and animals.
-Firms pay for thermal energy ($Q$), but useful work ($U$) alters the size and shape of materials, keeps lights on, and transports goods to consumers.
-Not all forms of energy are created equal in terms of ability to generate economic activity \citep{Cleveland:2000vl, Warr:2010ht}.
-Exergy ($X$), and to a greater extent, useful work ($U$) account for the useful energy that goes into generating economic activity, thereby reflecting the ``quality'' of each energy type and the efficiency of machines and devices typically used to convert thermal energy ($Q$) into useful work ($U$).
+Exergy ($X$) is the maximum useful work that could be extracted from an energy carrier by a process that brings the system into equilibrium with a heat reservoir (typically the surrounding environment).
+******** Caleb: Is this how Ayres and Warr use the term ``exergy''?
+************ Useful work ($U$) includes the direct energy that goes into an economy, including work from machines, human muscles, and animals.
+Firms pay for thermal energy ($Q$), but useful work ($U$) alters the size and shape of materials, keeps the lights on, and transports goods to consumers.
+Not all forms of energy are created equal in terms of their ability to generate economic activity \citep{Cleveland:2000vl, Warr:2010ht}.
+Both exergy ($X$), and to a greater extent, useful work ($U$) quantifications of energy are intended to account for the usefulness of energy for generating economic activity, thereby reflecting the ``quality'' of each energy type and the efficiency of machines and devices typically used in energy conversion processes.
 
 Most energy economists use thermal energy ($q$) for the energy factor of production ($e$) in energy-augmented production functions, including \citet{Stern:2012ey}, \citet{Froling:2009vo}, \citet{Serrenho:2010vq}, and \citet{Kummel:1980wx,Kummel:1982vy,Kummel:1985vz,Kummel:1989tf,Kummel:2002tx,Kummel:2010vz}.
-\citet{Warr:2010ga} introduced the idea of using exergy ($x$) and useful work ($u$) in energy-augmentd production functions to account for efficiency gains in energy production and consumption over the last century.
+\citet{Ayres:2003ec} introduced the idea that exergy ($x$) and useful work ($u$) were important factors of production.
+
+**************** Martin: add more here about the conclusions of each paper regarding the role of energy in economic growth?
+Add additional literature?
+Or, adjust as you see fit.
+Especially, are there any confidence intervals or statistical evaluation in each of these studies?
+********************
 
@@
 
-But, the nearly-complete focus on developed economies misses the role that energy plays in the development process.
-In this paper we analyze at least two economies in each of the following four categories: Developed (technologically advanced with high standards of living), BRICS\footnote{Brazil, Russia, India, China, and South Africa} (rapid economic growth with standards of living below that of developed economies), Petrol (petroleum is a substantial source of GDP); and LDCs\footnote{Lesser Developed Countries} (living standards near subsistence levels).
+But, the nearly-complete focus on developed economies closes off the possibility of discovering any role that energy plays in the development process.
+In this paper we analyze at least two economies in each of the following four categories: Developed (technologically advanced with high standards of living), BRICS\footnote{Brazil, Russia, India, China, and South Africa} (rapid economic growth with standards of living below that of developed economies), Petrol (petroleum is a substantial source of GDP ******* Martin: Is this the right way to describe the petrol economies?
+*********); and LDCs\footnote{Lesser Developed Countries} (living standards near subsistence levels ******* Martin: Is this the right way to describe the LDC economies?
+*********).
 (See Table \ref{tab:Economy_Examples}.)
@@
 
-We measure economic output ($Y$) by real gross domestic product (GDP).
+We measure economic output ($Y$) by gross domestic product (GDP).
 GDP data in real 2005 U.S.
@@
 
-The World Bank's World Development Indicators database \citep{WorldBankWDI:2013a} provides the employment to population ratio for people fifteen and older, total population, and a percentage of people under fifteen for other nations (South Africa, China, Iran, Saudi Arabia, Tanzania, and Zambia) for 1991--2011.
-The population of people under fifteen was subtracted from total population to calculate the population of people fifteen and older.
+The World Bank's World Development Indicators database \citep{WorldBankWDI:2013a} provides the employment to population ratio for people fifteen and older, total population, and a percentage of people under fifteen for other economies (South Africa, China, Iran, Saudi Arabia, Tanzania, and Zambia) for 1991--2011.
+The population of people under fifteen years of age was subtracted from total population to calculate the population of people fifteen and older.
 Total employment was calculated by multiplying the employment to population ratio of people fifteen and older by the population of people fifteen and older.
@@
 To account for all energy input to an economy, we summed consumption data for many energy sources, including coal, oil and petroleum products, dry natural gas and natural gas plant liquids, nuclear power generation, and renewable energy sources (solar, wind, geothermal, biomass/fuel wood, and hydro).
-In the style of work by Warr and Ayres \citep{Ayres:2005kn, Warr:2010ht, Warr:2010ga, Warr:2012cg}, energy from human and animal muscle power was also included.
-Similar to the economic data discussed in Sections \ref{sec:Economic_Output_Data}--\ref{sec:Labor_Data}, we generated energy data for developed countries from 1980--2000.
-For all other countries, we generated energy data for 1991--2011.
-Details on each of the energy quantifications are given in subsections below.
+In the style of work by Warr and Ayres \citep{Ayres:2003ec, Ayres:2005kn, Warr:2010ht, Warr:2010ga, Warr:2012cg}, energy from human and animal muscle power was also included.
+Similar to the economic data discussed in Sections \ref{sec:Economic_Output_Data}--\ref{sec:Labor_Data}, we generated energy data for developed countries from 1980--2011, with the exception of useful work data (1980--2000).
+For all other countries, we generated thermal energy and exergy data for 1991--2011.
+Details on each energy quantifications are given in subsections below.
 
@@
 \begin{equation} \label{eq:thermal_energy}
-  Q_{fuel} = C_{fuel}h_{fuel},
+  Q_{fuel} = C_{fuel}h_{fuel}
 \end{equation}
@@
 \noindent where $C_{fuel}$ is the consumption rate of the fuel (in units of short tons/year for coal, barrels/year for oil and petroleum, ft$^3$/year for dry natural gas and natural gas plant liquids, and m$^3$/year for biomass/fuel wood) and $h_{{fuel}}$ is the heat content of the fuel (in kJ/short ton for coal, kJ/barrel for oil, kJ/ft$^3$ for dry natural gas and natural gas plant liquids, and kJ/kg for biomass/fuel wood).
-The fuel wood density of 166.67 kg/m$^3$ was obtained from the \citet{FAO:2013a} **** Caleb: verify this number and source ****.
-
-Yearly consumption rates ($C_{fuel}$) for all economies were obtained from the Energy Information Agency \citep{EIA:2013a} for coal, oil and petroleum, and dry natural gas and natural gas plant liquids.
+Fuel wood density (166.67 kg/m$^3$ **** Caleb: verify this number and source ****) was obtained from the \citet{FAO:2013a}.
+
+Yearly consumption rates ($C_{fuel}$) for all economies were obtained from the \citet{EIA:2013a} for coal, oil and petroleum, and dry natural gas and natural gas plant liquids.
 Yearly average heat content data for coal, oil, and natural gas and natural gas plant liquids was obtained from the EIA for all economies.
@@
 
-For renewable and nuclear energies, yearly electricity generation (in BTU/year) was available directly from the \citet{EIA:2013a} for all economies, so Equation \ref{eq:thermal_energy} was not necessary.
+For renewable and nuclear energy sources, yearly electricity generation (in BTU/year) was available directly from the \citet{EIA:2013a} for all economies, so Equation \ref{eq:thermal_energy} was unnecessary.
 
@@
 For animal work, our analysis was restricted to draught animals (horses and mules).
-Muscle work from animals ($E_{animals}$) was calculated using
+Muscle work from animals ($Q_{animals}$) was calculated using
 
@@
 Metabolizable energy values ($Q_{m,horses}$ = 19,110 kcal/day-horse and $Q_{m,mules}$ = 7,215 kcal/day-mule) were taken from \citet{Warr:2012a} for horses and mules and represent the amount of energy used by animals for a day of work.
-The $Q_m$ values are assumed constant for all countries and years.
-The number of horses and mules for each economy was taken from the ``Live Animals'' time series in the FAO Statistics Database \citep{FAO:2013a}.
-
-Human muscle power was calculated in a similar manner
+(******** Caleb: Perhaps this should be ``represent the amount of energy in the feed consumed by animals for a day of work.'' *********) The $Q_m$ values are assumed constant for all countries and years.
+The number of horses and mules for each economy was taken from the ``Live Animals'' time series in the FAO Statistics Database \citep{FAO:2013a} ******** Get a table number from Caleb.
+*************.
+
+Human muscle power was calculated in a similar manner:
 
@@
 \noindent where the value of $Q_{m,workers}$ for the U.S.
-was taken from a time series of kcal/day-person for workers for 1980--2011 \citep{Warr:2012a} ($\sim$ 4200 kcal/day-worker).
+($\sim$ 4200 kcal/day-worker) was taken from a time series of kcal/day-person for workers for 1980--2011 \citep{Warr:2012a}.
 $Q_{m,workers}$ for other countries was taken from the \citet{FAO:2013b}.
@@
 Exergy ($X$), expressed in TJ/year, was calculated from the thermal energy ($Q$) values discussed in Section \ref{sec:Q_Data}.
-For fuels, exergy was calculated by a unitless exergy-to-energy allocation factor ($f_{exergy-allocation}$) from \citet{Ayres:2005kn} and shown in Table \ref{tab:Exergy_Allocation}.
-$f_{exergy-allocation}$ is the ratio of chemical exergy to the higher heating value for each fuel.
-$f_{exergy-allocation}$ for each fuel was assumed to be constant through time across all economies.
-For renewable and nuclear energy sources, the electricity generated is already pure exergy, so $f_{exergy-allocation}$ is unity.
+For fuels, exergy was calculated by a unitless exergy-to-energy allocation factor ($f_{exergy-allocation}$) from \citet[Table~A-2]{Ayres:2003ec} and shown in Table \ref{tab:Exergy_Allocation}.
 
@@
       Oil and petroleum                       & 1.073   \\      
-      Dry natural gas and                     & \multirow{2}{*}{1.040}    \\
+      Dry natural gas and                     & \multirow{2}{*}{1.04}    \\
       natural gas liquids                     &         \\
-      Biomass/fuel wood                       & 1.150   \\
-      Nuclear                                 & 1.000   \\
-      Renewables                              & 1.000   \\
+      Biomass/fuel wood                       & 1.15   \\
+      Nuclear                                 & 1.0   \\
+      Renewables                              & 1.0   \\
     \end{tabular}
@@
 
-To calculate the exergy of animal and human muscle power, the food-to-work conversion efficiency ($\eta_{food \rightarrow work}$) and the ratio of food end-use to food intake ($f_{enduse/intake}$) were included.
-$\eta_{food \rightarrow work, animals}$ and $\eta_{food \rightarrow work, workers}$ are animal and worker efficiency of converting food into energy respectively.
+\noindent $f_{exergy-allocation}$ is the ratio of chemical exergy to the higher heating value for each fuel.
+$f_{exergy-allocation}$ for each fuel was assumed to be constant through time across all economies.
+For renewable and nuclear energy sources, the electricity generated is already pure exergy, so $f_{exergy-allocation}$ is unity.
+
+To calculate the exergy of animal and human muscle power, the food-to-work conversion efficiency ($\eta_{food \rightarrow work}$) and the ratio of food enduse to food intake ($f_{enduse/intake}$) were included.
+
+\begin{equation} \label{eq:animal_muscle_exergy}
+  X_{animals} = \eta_{food \rightarrow work,animals} Q_{animals}
+\end{equation}
+
+\begin{equation} \label{eq:human_muscle_exergy}
+  X_{workers} = \eta_{food \rightarrow work,workers} f_{enduse/intake} Q_{workers}
+\end{equation}
+
+\noindent $\eta_{food \rightarrow work, animals}$ and $\eta_{food \rightarrow work, workers}$ are animal and worker efficiency of converting food into energy respectively.
 The animal feed-to-work conversion efficiency ($\eta_{food \rightarrow work, animals}$ = 0.4) was taken from \citet{Warr:2012a} and assumed equal across all economies.
-The worker food-to-work efficiency ($\eta_{food \rightarrow work, workers}$ = 0.2) was taken from \citet{Ayres:2010ug}.
+The food-to-work efficiency for workers ($\eta_{food \rightarrow work, workers}$ = 0.2) was taken from \citet{Ayres:2010ug}.
 Following \citet[p.~315]{Ayres:2010ug}, an additional factor ($f_{enduse/intake}$) was included to account for workers' food energy that sustains the body's normal function as opposed to providing energy for physical labor \citep{Wirsenius:2000vi}.
-$f_{enduse/intake}$ varies by country.
+$f_{enduse/intake}$ varies by country (Table \ref{tab:f_enduse_intake}).
 A similar enduse-to-intake ratio could also be applied to animal work, but it was unavailable from \citet{Wirsenius:2000vi}.\footnote{The error in exergy caused by neglecting $f_{enduse/intake}$ for animals is very small, because animal muscle exergy is a small fraction of the total energy supply to any economy, with a maximum of 4.1\% for China in 1992.}
@@
 
-\begin{equation} \label{eq:animal_muscle_exergy}
-  X_{animals} = \eta_{food \rightarrow work,animals} Q_{animals}
-\end{equation}
-
-\begin{equation} \label{eq:human_muscle_exergy}
-  X_{workers} = \eta_{food \rightarrow work,workers} f_{enduse/intake} Q_{workers}
-\end{equation}
-
-\noindent
-
 %------------------------------
@@
 The conversion of a raw energy carrier (e.g., coal) into productive energy for an economy (e.g., electricity) necessarily involves inefficiencies.
-In the case of coal consumption, only about one-third of the coal exergy is converted to useful electricity, the rest is waste heat.
-The concept of ``useful work,'' pioneered by Ayres and Warr \citep{Ayres:2003ec, Ayres:2005kn}, takes exergy one step further to consider efficiencies of both energy production and end use.
-To calculate useful work ($U$), each source of exergy (coal, oil and petroleum products, dry natural gas and natural gas plant liquids, biomass/fuel wood, nuclear, solar, wind, and human and animal muscle work) is decomposed into several end uses: high temperature industrial heat (e.g., steel production), medium temperature heat (e.g., steam production), low temperature space heat (for residential heating), mechanical drive (energy used for prime mover engines of all types except electric motors), electricity (excluding lighting), light (from both electricity and fuels), and muscle work (from animals and workers).
-The efficiency ($\varepsilon$) of convering exergy into useful work can be very different, depending upon the end use of the exergy.
-Efficiencies specific to each end use ($\varepsilon_i$) were applied to exergy values to obtain useful work ($U$) input to an economy with the following equation:
+In the case of coal consumption, only about one-third of the coal exergy is converted to useful electricity: the rest is waste heat.
+The concept of ``useful work,'' pioneered by Ayres and Warr \citep{Ayres:2003ec, Ayres:2005kn}, build upon exergy analysis to consider efficiencies of both energy production and end use.
+To calculate useful work ($U$), the total exergy input to an economy ($X$) is decomposed into several end uses: high temperature industrial heat (e.g., steel production), medium temperature heat (e.g., steam production), low temperature space heat (for residential heating), mechanical drive (energy used for prime mover engines of all types except electric motors), electricity (excluding lighting), lighting (from both electricity and fuels), and muscle work (from animals and workers) as shown in the following equation:
 
@@
 For most countries, values of $\phi_i$ are not constant with time, as economic sectors with different distributions of raw exergy inputs grow at different rates.
-\citeapos{Warr:2012a} REXS database contains information for developed economies (United States, United Kingdom, and Japan) from 1900--2000, but we are using data in the 1980--2000 timeframe.
+\citeapos{Warr:2012a} REXS database contains information for developed economies (United States, United Kingdom, and Japan) from 1900--2000, and we used data from the 1980--2000 timeframe.
 Extending the REXS database to the BRICS, petrol, and LDC economies is beyond the scope of this work, because longitudinal data for the efficiency of different end uses ($\varepsilon_i$) and the distribution of exergy sources to end uses ($\phi_i$) are extremely difficult to find.

### 2013-04-30 EconGrowth.Rnw
More editing and fixing the graphs. Still have a problem with stars appearing in the gamma grid graph key.

@@
 %++++++++++++++++++++++++++++++
-\subsection{Mathematical Forms of the Energy-augmented Production Function} \label{sec:Prod_Func_Forms}
+\subsection{Mathematical Forms of the Energy-augmented Production Function} 
+\label{sec:Prod_Func_Forms}
 %++++++++++++++++++++++++++++++
@@
 
-************* Matt ended here. ****************
-
 %++++++++++++++++++++++++++++++
@@
 
-<<Historical_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="Historical data: Indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$).">>=
+% You can add fig.pos="H" to force the figure position to be this exact place.
+
+<<Historical_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Historical data: Indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$).">>=
 createHistoricalLatticeGraph()
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Cobb-Douglas Model Without Energy (CD)}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The Cobb-Douglas model without energy is given by
-
-\begin{equation} \label{eq:CD_No_Energy}
-  y = \mathrm{e}^{\lambda (t-t_0)}k^{\alpha}l^{\beta}.
-\end{equation}
-
-Figure \ref{fig:CD_Params_Graph} shows values and 95\% confidence intervals for the parameters for the Cobb-Douglas model (without energy).
-
-<<CD_Params_Graph, fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.pos="H", fig.cap="Cobb-Douglas (without energy) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
+\section{Parameter Estimation}
+\label{sec:Parameter_Estimation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Each of the economic growth models discussed in Section \ref{sec:Prod_Func_Forms} has parameters which must be estimated for each economy (see Section \ref{sec:Economy_Types}) and each energy quantification (see Section \ref{sec:Quantification_of_Energy}) via least-squares methods.
+The following subsections discuss parameter estimation methods interpret the results.
+
+%++++++++++++++++++++++++++++++
+\subsection{Cobb-Douglas Models}
+%++++++++++++++++++++++++++++++
+
+The Cobb-Douglas model without energy is given by Equation \ref{eq:CD}. The Cobb-Douglas production function was reparameterized as
+
+\begin{equation} \label{eq:CD_reparam}
+  y = A k^{\alpha} l^{1-\alpha}; A = \mathrm{e}^{\lambda (t-t_0)}
+\end{equation}
+
+\noindent from which $\beta = 1 - \alpha$ can be found.
+The above reparameterization ensures the $\alpha + \beta = 1$ for constant returns to scale.
+****** Say something here about constraints when we get them figured out.
+*********** $\lambda$ and $\alpha$ were estimated for all countries with the \citet{R} function \texttt{nls}.
+Figure \ref{fig:CD_Params_Graph} shows values of and 95\% confidence intervals for $\lambda$ and $\alpha$.
+Appendix \ref{sec:Model_Parameters} contains tables with numerical values of model parameters and confidence intervals.
+
+<<CD_Params_Graph, fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.cap="Cobb-Douglas (without energy) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
 createCDParamsGraph(energyType=NA)
@@
 
-To qualitatively assess whether augmenting the Cobb-Douglas model with energy will be beneficial, we create partial residual plots as shown in Figures \ref{fig:CDPartialResidualsQ} - \ref{fig:CDPartialResidualsU} below.
+To qualitatively assess whether augmenting the Cobb-Douglas model with energy will be beneficial, we created partial residual plots as shown in Figures \ref{fig:CDPartialResidualsQ}--\ref{fig:CDPartialResidualsU} below.
 If a monotonic trend is observed on the graphs, we expect that energy augmentation will be beneficial.
-However, no strong monotonic tends are observed for any country, suggesting that energy augmentation of the Cobb-Douglas production function will not be beneficial.
-
-<<CDPartialResidualsQ, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="Cobb-Douglas partial residuals plot for thermal energy ($q$).", fig.pos="H">>=
+However, no strong monotonic tends are observed for any country, with the exception, perhaps, of the United Kingdom, whose residuals are, on average, above 0.
+
+<<CDPartialResidualsQ, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="Cobb-Douglas partial residuals plot for thermal energy ($q$).">>=
 createPartialResidualPlot(modelType="CD", energyType="Q", countryAbbrev=NA)
@@
 
-<<CDPartialResidualsX, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="Cobb-Douglas partial residuals plot for exergy ($x$).", fig.pos="H">>=
+<<CDPartialResidualsX, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="Cobb-Douglas partial residuals plot for exergy ($x$).">>=
 createPartialResidualPlot(modelType="CD", energyType="X", countryAbbrev=NA)
@@
 
-<<CDPartialResidualsU, fig.width=threePanelGraphWidth, fig.height=threePanelGraphHeight, fig.align="center", fig.cap="Cobb-Douglas partial residuals plot for useful work ($u$).", fig.pos="H">>=
+<<CDPartialResidualsU, fig.width=threePanelGraphWidth, fig.height=threePanelGraphHeight, fig.align="center", fig.cap="Cobb-Douglas partial residuals plot for useful work ($u$).">>=
 createPartialResidualPlot(modelType="CD", energyType="U", countryAbbrev=NA)
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Cobb-Douglas Models With Energy}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-We can force $\alpha$, $\beta$, and $\gamma$ to be in $[0,1]$ by a reparameterization:
-
-$a \in[0,1], b \in [0,1], \alpha=\min(a,b), \beta=|b-a|, \gamma = 1-\max(a,b)$
-
-The Cobb-Douglas model with energy is given by
-
-\begin{equation} \label{eq:CD_With_Energy}
-  y = \mathrm{e}^{\lambda (t-t_0)}k^{\alpha}l^{\beta}e^{\gamma},
-\end{equation}
-
-\noindent where $e$ can be one of thermal energy ($q$), exergy ($x$), or useful work ($u$).
-
-\subsection{Cobb-Douglas with thermal energy}
+To estimate the parameters $\lambda$, $\alpha$, $\beta$, and $\gamma$ in the energy-augmented Cobb-Douglas model, we reparameterized Equation \ref{eq:CDe} as
+
+\begin{equation} \label{eq:CDe_reparam}
+  y = A k^{\min(a,b)}l^{|b-a|}e^{1 - \max(a,b)}; A = \mathrm{e}^{\lambda (t-t_0)}
+\end{equation}
+
+\noindent from which $\alpha = \min(a,b)$, $\beta = |b-a|$, and $\gamma = \max(a,b)$ can be calculated.
+By constraining $a \in [0,1]$ and $b \in [0,1]$, we ensure that $\alpha \in [0,1]$, $\beta \in [0,1]$, and $\gamma \in [0,1]$.
+The \citet{R} function \texttt{nls} was used to estimate values for $\lambda$, $a$, and $b$.
 
@@
 
-<<CDeGridLattice, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Grid search over $\\gamma$ for Cobb-Douglas with energy model.", fig.pos="H">>=
+<<CDeGridLattice, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Grid search over $\\gamma$ for Cobb-Douglas with energy model.", eval=TRUE>>=
 cdeGridLattice(energyType="Q")
@@
 
-<<CDq_Params_Graph, fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.pos="H", fig.cap="Cobb-Douglas (with $q$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
+<<CDq_Params_Graph, fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.cap="Cobb-Douglas (with $q$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
 createCDParamsGraph(energyType="Q")
@@
 
-\subsection{Cobb-Douglas with exergy}
-
 The Cobb-Douglas (with exergy) parameters are given in Table \ref{tab:CD_Parameters_With_X}.
@@
 
-<<CDx_Params_Graph, fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.pos="H", fig.cap="Cobb-Douglas (with $x$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
+<<CDx_Params_Graph, fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.cap="Cobb-Douglas (with $x$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
 createCDParamsGraph(energyType="X")
@@
 
-\subsection{Cobb-Douglas with useful work}
-
 Figure \ref{fig:CDu_Params_Graph} shows values and 95\% confidence intervals for the parameters for the Cobb-Douglas model (with $u$).
 
-<<CDu_Params_Graph, fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.pos="H", fig.cap="Cobb-Douglas (with $u$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
+<<CDu_Params_Graph, fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.cap="Cobb-Douglas (with $u$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
 createCDParamsGraph(energyType="U")
@@
 
-\subsection{Cobb-Douglas Comparisons}
-
-Figure \ref{fig:CD_GDP_Lattice_Graph} compares predictions from the Cobb-Douglas models (without energy, with $q$, with $x$, and with $u$) to historical data.
-
-<<CD_GDP_Lattice_Graph, fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="Cobb-Douglas results.">>=
+Figure \ref{fig:CD_GDP_Lattice_Graph} compares predictions from the Cobb-Douglas models (without energy, with $e=q$, with $e=x$, and with $e=u$) to historical data.
+
+<<CD_GDP_Lattice_Graph, fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas results.">>=
 createCDLatticeGraph()
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{CES Models}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+************* Matt ended here. ****************
+
+%++++++++++++++++++++++++++++++
+\subsection{CES Models}
+%++++++++++++++++++++++++++++++
 
@@
 
-%++++++++++++++++++++++++++++++
-\subsection{CES without energy (CES)}
-%++++++++++++++++++++++++++++++
-
 Figure \ref{fig:CES_Params_Graph} shows values and 95\% confidence intervals for the parameters for the CES model (without energy).
 
-<<CES_Params_Graph, fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.pos="H", fig.cap="CES (without energy) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
+<<CES_Params_Graph, fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (without energy) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
 createCESParamsGraph(energyType=NA)
@@
 
-<<CESPartialResidualsQ, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="CES partial residuals plot for thermal energy ($q$).", fig.pos="H">>=
+<<CESPartialResidualsQ, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="CES partial residuals plot for thermal energy ($q$).">>=
 createPartialResidualPlot(modelType="CES", energyType="Q", countryAbbrev=NA)
@@
 
-<<CESPartialResidualsX, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="CES partial residuals plot for exergy ($x$).", fig.pos="H">>=
+<<CESPartialResidualsX, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="CES partial residuals plot for exergy ($x$).">>=
 createPartialResidualPlot(modelType="CES", energyType="X", countryAbbrev=NA)
@@
 
-<<CESPartialResidualsU, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="CES partial residuals plot for useful work ($u$).", fig.pos="H">>=
+<<CESPartialResidualsU, fig.width=threePanelGraphWidth, fig.height=threePanelGraphHeight, fig.align="center", fig.cap="CES partial residuals plot for useful work ($u$).">>=
 createPartialResidualPlot(modelType="CES", energyType="U", countryAbbrev=NA)
@@
 
-%++++++++++++++++++++++++++++++
-\subsection{CES with Thermal Energy}
-%++++++++++++++++++++++++++++++
-
 Figure \ref{fig:CESq_Params_Graph} shows values and 95\% confidence intervals for the parameters for the CES model (with $q$).
 
-<<CESq_Params_Graph, fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.pos="H", fig.cap="CES (with $q$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
+<<CESq_Params_Graph, fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with $q$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
 createCESParamsGraph(energyType="Q")
@@
 
-%++++++++++++++++++++++++++++++
-\subsection{CES with Exergy}
-%++++++++++++++++++++++++++++++
-
 Figure \ref{fig:CESx_Params_Graph} shows values and 95\% confidence intervals for the parameters for the CES model (with $x$).
 
-<<CESx_Params_Graph, fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.pos="H", fig.cap="CES (with $x$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
+<<CESx_Params_Graph, fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with $x$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
 createCESParamsGraph(energyType="X")
@@
 
-%++++++++++++++++++++++++++++++
-\subsection{CES with Useful Work}
-%++++++++++++++++++++++++++++++
-
 Figure \ref{fig:CESu_Params_Graph} shows values and 95\% confidence intervals for the parameters for the CES model (with $u$).
 
-<<CESu_Params_Graph, fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.pos="H", fig.cap="CES (with $u$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
+<<CESu_Params_Graph, fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with $u$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
 createCESParamsGraph(energyType="U")
@@
 
-%++++++++++++++++++++++++++++++
-\subsection{CES comparisons}
-%++++++++++++++++++++++++++++++
-
 Figure \ref{fig:CES_GDP_Lattice_Graph} compares CES model predictions to historical data.
 
-<<CES_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="CES results.">>=
+<<CES_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES results.">>=
 createCESLatticeGraph()
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Confidence Intervals for Cobb-Douglas and CES Models}
+\subsection{Confidence Intervals for Cobb-Douglas and CES Models}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-<<CIvsParam_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="95\\% Confidence interval widths vs.
+<<CIvsParam_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="95\\% Confidence interval widths vs.
 parameter values for key energy parameters ($\\gamma$, $\\delta$, and $\\sigma$) of the Cobb-Douglas and CES models with energy.
@@
 
-%++++++++++++++++++++++++++++++
-\subsection{LINEX with Thermal Energy}
-%++++++++++++++++++++++++++++++
-
 Figure \ref{fig:LINEXq_Params_Graph} shows values and 95\% confidence intervals for the parameters for the LINEX model (with $q$).
 
-<<LINEXq_Params_Graph, fig.width=linexParameterGraphWidth, fig.height=linexParameterGraphHeight, fig.pos="H", fig.cap="LINEX (with $q$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
+<<LINEXq_Params_Graph, fig.width=linexParameterGraphWidth, fig.height=linexParameterGraphHeight, fig.cap="LINEX (with $q$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
 createLINEXParamsGraph(energyType="Q")
@@
 
-%++++++++++++++++++++++++++++++
-\subsection{LINEX with Exergy}
-%++++++++++++++++++++++++++++++
-
 Figure \ref{fig:LINEXx_Params_Graph} shows values and 95\% confidence intervals for the parameters for the LINEX model (with $x$).
 
-<<LINEXx_Params_Graph, fig.width=linexParameterGraphWidth, fig.height=linexParameterGraphHeight, fig.pos="H", fig.cap="LINEX (with $x$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
+<<LINEXx_Params_Graph, fig.width=linexParameterGraphWidth, fig.height=linexParameterGraphHeight, fig.cap="LINEX (with $x$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
 createLINEXParamsGraph(energyType="X")
@@
 
-%++++++++++++++++++++++++++++++
-\subsection{LINEX with Useful Work}
-%++++++++++++++++++++++++++++++
-
 Figure \ref{fig:LINEXu_Params_Graph} shows values and 95\% confidence intervals for the parameters for the LINEX model (with $u$).
 
-<<LINEXu_Params_Graph, fig.width=linexParameterGraphWidth, fig.height=linexParameterGraphHeight, fig.pos="H", fig.cap="LINEX (with $u$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
+<<LINEXu_Params_Graph, fig.width=linexParameterGraphWidth, fig.height=linexParameterGraphHeight, fig.cap="LINEX (with $u$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
 createLINEXParamsGraph(energyType="U")
@@
 
-%++++++++++++++++++++++++++++++
-\subsection{LINEX comparisons}
-%++++++++++++++++++++++++++++++
-
 Figure \ref{fig:LINEX_GDP_Lattice_Graph} compares LINEX model predictions to historical data.
 
-<<LINEX_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="LINEX results.">>=
+<<LINEX_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX results.">>=
 createLINEXLatticeGraph()
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Implications}
+\label{sec:Implications}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+************* Do we need this? **************
+
+************* Martin needs to write this. **************
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusion}
+\label{sec:Conclusion}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-In the spirit of Reproducible Research \citep{Gandrud:2013vx}, all data, spreadsheets, \texttt{R} code \citep{R}, and other materials associated with this paper can be found at \protect\url{https://github.com/MatthewHeun/Econ-Growth-R-Analysis}.
+In the spirit of Reproducible Research \citep{Gandrud:2013vx}, all data, spreadsheets, \texttt{R} code \citep{R}, and other materials associated with this paper can be found at \protect\url{https://github.com/MatthewHeun/Econ-Growth- R-Analysis}.
 
@@
 
-<<SFk_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $k$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
+<<SFk_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.cap="Single-factor (with $k$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
 createSFParamsGraph(factor="K")
@@
 
-<<SFl_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $l$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
+<<SFl_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.cap="Single-factor (with $l$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
 createSFParamsGraph(factor="L")
@@
 
-<<SFq_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $q$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
+<<SFq_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.cap="Single-factor (with $q$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
 createSFParamsGraph(factor="Q")
@@
 
-<<SFx_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $x$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
+<<SFx_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.cap="Single-factor (with $x$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
 createSFParamsGraph(factor="X")
@@
 
-<<SFu_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.pos="H", fig.cap="Single-factor (with $u$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
+<<SFu_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.cap="Single-factor (with $u$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
 createSFParamsGraph(factor="U")
@@
 
-<<SF_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.pos="H", fig.cap="Single-factor results.">>=
+<<SF_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single-factor results.">>=
 createSFLatticeGraph()

### 2013-04-30 EconGrowth-R-Functions.Rnw
More editing and fixing the graphs. Still have a problem with stars appearing in the gamma grid graph key.
Changed the size of symbols in the gamma grid search 9-panel lattice graph.
Now using country names (instead of abbreviations) in partial residual plots.

--- 2013-04-30 EconGrowth-R-Functions.Rnw
@@
 countryNamesAlph <- c(CN="China", IR="Iran", JP="Japan", SA="Saudi Arabia", TZ="Tanzania", UK="United Kingdom", US="USA", ZA="South Africa", ZM="Zambia") #In alphabetical order.
+countryNamesAlphU <- c(JP="Japan", UK="United Kingdom", US="USA") #In alphabetical order.
 yLimitsForGDPGraphs <- list(c(1,10), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4)) # Alph order
@@
 onePanelLayoutSpec <- c(1,1) #indicates a 1x1 arrangement of panels.
+threePanelGraphWidth <- maxWidth
+threePanelGraphHeight <- 3.17 #Inches
 ninePanelGraphWidth <- maxWidth     
@@
   gammaGrid <- seq(0.0, 0.95, by=0.05) # Establishes the grid in which we're interested.
-  if (is.na(countryAbbrev)){
-    # All countries are wanted.
-    data <- do.call("rbind", lapply(countryAbbrevsAlph, cdeGridData, energyType=energyType, gammaGrid=gammaGrid))
-    # Establish some formatting parameters
-    factorLevels <- countryNamesAlph # We want all countries shown
-    indexCond <- list(countryOrderForGraphs) # We want all countries in this order
-    layout <- ninePanelLayoutSpec # Show all countries
-    stripSpec <- strip.custom(factor.levels=factorLevels, # Sets text for factor levels
-                              bg="transparent", # Sets background transparent to match the graph itself.
-                              par.strip.text=list(cex=textScaling) # Scales text in the strip.
-                              )
-  } else {
-    # Only one specific country is wanted.
-    data <- cdeGridData(countryAbbrev=countryAbbrev, energyType=energyType, gammaGrid=gammaGrid)
-    # Select the correct y limits
-    index <- which(countryAbbrevsAlph %in% countryAbbrev)
-    # The following lines use [index:index] as a convenient way of subsetting.
-    # This has the added benefit of maintaining the correct classes for things.
-    factorLevels <- countryNamesAlph[index:index]     # Only show the country we have chosen.
-    indexCond <- list(c(1))                           # We want only one country.
-    layout <- onePanelLayoutSpec                      # We want only one panel in the graph.
-    stripSpec <- FALSE # No strip needed.
-  }
   alphaBetaGammaRange <- c(-0.1, 1.5)
@@
   lineWidths <- c(1, 3, 1, 0) #line widths. 0 means no line.
-  symbols <- c(NA, NA, NA, 1)
   colors <- c("black", "black", "black", "black") #line and symbol colors  
+  symbolSize <- 0.5
+  symbolType <- 0 #for an open square
+  symbols <- c(NA, NA, NA, symbolType)
+  if (is.na(countryAbbrev)){
+    # All countries are wanted.
+    data <- do.call("rbind", lapply(countryAbbrevsAlph, cdeGridData, energyType=energyType, gammaGrid=gammaGrid))
+    # Establish some formatting parameters
+    factorLevels <- countryNamesAlph # We want all countries shown
+    indexCond <- list(countryOrderForGraphs) # We want all countries in this order
+    layout <- ninePanelLayoutSpec # Show all countries
+    stripSpec <- strip.custom(factor.levels=factorLevels, # Sets text for factor levels
+                              bg="transparent", # Sets background transparent to match the graph itself.
+                              par.strip.text=list(cex=textScaling) # Scales text in the strip.
+                              )
+  } else {
+    # Only one specific country is wanted.
+    data <- cdeGridData(countryAbbrev=countryAbbrev, energyType=energyType, gammaGrid=gammaGrid)
+    # Select the correct y limits
+    index <- which(countryAbbrevsAlph %in% countryAbbrev)
+    # The following lines use [index:index] as a convenient way of subsetting.
+    # This has the added benefit of maintaining the correct classes for things.
+    factorLevels <- countryNamesAlph[index:index]     # Only show the country we have chosen.
+    indexCond <- list(c(1))                           # We want only one country.
+    layout <- onePanelLayoutSpec                      # We want only one panel in the graph.
+    stripSpec <- FALSE # No strip needed.
+  }
   abgGraph <- xyplot(alpha+beta+gamma ~ gamma | Country, data=data,
@@
                               cex=keyTextSize * textScaling, #controls size of text in the key
-                              lines=list(lty=lineTypes, lwd=lineWidths), #controls line types
-                              pch=symbols, col=colors, #controls symbol (plot characters) types
+                              lines=list(lty=lineTypes, lwd=lineWidths, pch=symbols, cex=symbolSize), #controls lines
+                              col=colors,
                               columns=keyColumns, x=keyXLoc, y=keyYLoc), #controls columns and position of the key
@@
   sseGraph <- xyplot(SSE ~ gamma | Country, data=data,
-                     pch = c(1), col.symbol = c("black"), #Controls symbol parameters
+                     pch = c(symbolType), col.symbol = c("black"), cex = symbolSize, #Controls symbol parameters
                      index.cond = indexCond, #orders the panels.
@@
       data <- subset(data, !is.na(iEToFit))
-print(data)
       layout <- threePanelLayoutSpec
-      factorLevels <- countryAbbrevsAlphU # Want only those countries for which U is known
-print(factorLevels)
+      factorLevels <- countryNamesAlphU # Want only those countries for which U is known
       indexCond <- list(countryOrderForGraphsU) # Orders as US, UK, JP

### 2013-04-30 EconGrowth.Rnw
Now using country names (instead of abbreviations) in partial residual plots.

@@
 \item{Heun: Include the adjusted sankey diagram in the seminar}
-\item{Heun: Adjust variable threePanelGraphHeight in the Functions file to produce U partial residual plots that are exactly the same size as the graphs in the 9-panel plots.}
+\item{Heun: Ensure consistent x and y axis limits in partial residual plots}
 \item{Heun: Add CES production function fits}
@@
 \item{de Wit: review, critique, and contextualize.}
+\item{\st{Heun: Use full country names instead of 2-letter abbreviations in partial residual plots}}
+\item{\st{Heun: Adjust variable threePanelGraphHeight in the Functions file to produce U partial residual plots that are exactly the same size as the graphs in the 9-panel plots.}}
 \item{\st{Heun: Eliminate non-developed countries from 9-panel partial residual plots}}
@@
 
-<<CDeGridLattice, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Grid search over $\\gamma$ for Cobb-Douglas with energy model.", eval=TRUE>>=
+<<CDeGridLattice, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Grid search over $\\gamma$ for Cobb-Douglas with energy model.">>=
 cdeGridLattice(energyType="Q")
@@
 
-<<CESPartialResidualsX, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="CES partial residuals plot for exergy ($x$).">>=
+<<CESPartialResidualsX, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="CES partial residuals plot for exergy ($x$).", eval=TRUE>>=
 createPartialResidualPlot(modelType="CES", energyType="X", countryAbbrev=NA)
@@
 
-<<CESPartialResidualsU, fig.width=threePanelGraphWidth, fig.height=threePanelGraphHeight, fig.align="center", fig.cap="CES partial residuals plot for useful work ($u$).">>=
+<<CESPartialResidualsU, fig.width=threePanelGraphWidth, fig.height=threePanelGraphHeight, fig.align="center", fig.cap="CES partial residuals plot for useful work ($u$).", eval=TRUE>>=
 createPartialResidualPlot(modelType="CES", energyType="U", countryAbbrev=NA)

### 2013-04-30 EconGrowth-R-Functions.Rnw
Edited the text for the CD and CDe parameter estimation section.

@@
     }
+    xLimits <- c(0.5, 4.5) # Maintain consistent x-axis limits across all graphs
+    yLimits <- c(-0.2, 0.2) # Maintain consistent y-axis limits across all graphs
     plot <- xyplot(resid ~ iEToFit | Country, data=data,
@@
                    col = "black",
+                   xlim=xLimits, 
+                   ylim=yLimits, 
                    scales = list(cex=scaleTextSize*textScaling, #controls text size on scales.

### 2013-04-30 EconGrowth.Rnw
Edited the text for the CD and CDe parameter estimation section.

--- 2013-04-30 EconGrowth.Rnw
@@
 \item{Heun: Include the adjusted sankey diagram in the seminar}
-\item{Heun: Adjust variable threePanelGraphHeight in the Functions file to produce U partial residual plots that are exactly the same size as the graphs in the 9-panel plots.}
 \item{Heun: Add CES production function fits}
@@
 \item{de Wit: review, critique, and contextualize.}
+\item{\st{Heun: Ensure consistent x and y axis limits in partial residual plots}}
+\item{\st{Heun: Use full country names instead of 2-letter abbreviations in partial residual plots}}
+\item{\st{Heun: Adjust variable threePanelGraphHeight in the EconGrowth-R-Functions.Rnw file to produce U partial residual plots that are exactly the same size as the graphs in the 9-panel plots.}}
 \item{\st{Heun: Eliminate non-developed countries from 9-panel partial residual plots}}
@@
 
-\noindent from which $\beta = 1 - \alpha$ can be found.
-The above reparameterization ensures the $\alpha + \beta = 1$ for constant returns to scale.
-****** Say something here about constraints when we get them figured out.
-*********** $\lambda$ and $\alpha$ were estimated for all countries with the \citet{R} function \texttt{nls}.
+\noindent to ensure $\alpha + \beta = 1$ for constant returns to scale.
+$\lambda$ and $\alpha$ were estimated for all countries in Equation \ref{eq:CD_reparam} by the \citet{R} function \texttt{nls}.
+By constraining $\alpha \in [0,1]$ during the fitting process, we ensure that $\beta \in [0,1]$ also.
+****** Is this truly how we implemented the constraints?
+Finish after we actually implement the constraints.
+*********** The value of $\beta$ can be found with $\beta = 1 - \alpha$.
 Figure \ref{fig:CD_Params_Graph} shows values of and 95\% confidence intervals for $\lambda$ and $\alpha$.
@@
 
-To estimate the parameters $\lambda$, $\alpha$, $\beta$, and $\gamma$ in the energy-augmented Cobb-Douglas model, we reparameterized Equation \ref{eq:CDe} as
+To estimate the parameters $\lambda$, $\alpha$, $\beta$, and $\gamma$ in the energy-augmented Cobb-Douglas model, Equation \ref{eq:CDe} was reparameterized as
 
@@
 
-\noindent from which $\alpha = \min(a,b)$, $\beta = |b-a|$, and $\gamma = \max(a,b)$ can be calculated.
+\noindent to ensure that $\alpha + \beta + \gamma = 1$.
 By constraining $a \in [0,1]$ and $b \in [0,1]$, we ensure that $\alpha \in [0,1]$, $\beta \in [0,1]$, and $\gamma \in [0,1]$.
-The \citet{R} function \texttt{nls} was used to estimate values for $\lambda$, $a$, and $b$.
+Given values of $a$ and $b$ that represent the least-squares parameter optimization for a given economy, $\alpha = \min(a,b)$, $\beta = |b-a|$, and $\gamma = \max(a,b)$ can be calculated.
+The \citet{R} function \texttt{nls} was used to estimate the least-squares values of $\lambda$, $a$, and $b$.
 

### 2013-05-02 EconGrowth.Rnw
Edits to the parameter estimation sections.

@@
 \item{Heun: Include the adjusted sankey diagram in the seminar}
+\item{Heun: Add the insight that for indexed factors of production $q$ and $x$, there is small difference in absolute magnitude and even smaller difference in indexed values unless $f_{exergy-allocation}$ is significantly different from 1.0 \emph{and} there is a shift in energy input to the economy.}
 \item{Heun: Add CES production function fits}
@@
 Figure \ref{fig:Historical_Lattice_Graph} indicates the importance of energy quantification for economic growth modeling.
-Thermal energy ($q$) and exergy ($x$) grow at similar rates, unless there is a significant raw energy carrier substitution in the economy (such as China's rapid increase of coal consumption relative to petroleum since 2000).
+Thermal energy ($q$) and exergy ($x$) grow at similar rates, unless there is a significant raw energy carrier substitution in the economy (such as China's rapid increase of natural gas and coal consumption relative to petroleum since 2000).
 The growth rate of $u$ is significantly different from $q$ and $x$ for most countries, however.
@@
 \subsection{Cobb-Douglas Models}
+\label{sec:CD_Parameter_Estimation}
 %++++++++++++++++++++++++++++++
@@
 \noindent to ensure $\alpha + \beta = 1$ for constant returns to scale.
-$\lambda$ and $\alpha$ were estimated for all countries in Equation \ref{eq:CD_reparam} by the \citet{R} function \texttt{nls}.
-By constraining $\alpha \in [0,1]$ during the fitting process, we ensure that $\beta \in [0,1]$ also.
+By constraining $\alpha \in [0,1]$, we ensure that $\beta \in [0,1]$ also.
 ****** Is this truly how we implemented the constraints?
 Finish after we actually implement the constraints.
-*********** The value of $\beta$ can be found with $\beta = 1 - \alpha$.
+*********** $\lambda$ and $\alpha$ were estimated by the \citet{R} function \texttt{nls}.
+The value of $\beta$ can be found with $\beta = 1 - \alpha$.
 Figure \ref{fig:CD_Params_Graph} shows values of and 95\% confidence intervals for $\lambda$ and $\alpha$.
@@
 
-************* Matt ended here. ****************
-
 %++++++++++++++++++++++++++++++
 \subsection{CES Models}
-%++++++++++++++++++++++++++++++
-
-\citet{Stern:2012ey} developed a CES model of the form\footnote{The CES equation in \citet{Stern:2012ey} appears as
-
-\begin{equation*} \label{eq:Stern_CES_model}
-  y = \left\{ (1-\gamma_E)^{1/\sigma} \left[ k^{\alpha} \left( \mathrm{e}^{\lambda_L(t-t_0)} l \right)^{\beta} \right]^{\frac{\sigma-1}{\sigma}}   
-      + (\gamma_E)^{1/\sigma} \left[ \mathrm{e}^{\lambda_E(t-t_0)} e \right]^{\frac{\sigma - 1}{\sigma}}   \right\}
-      ^{\frac{\sigma}{\sigma - 1}},
-\end{equation*}
-
-but the $1/\sigma$ exponent on the $(1-\gamma_E)$ and $\gamma_E$ terms is erroneous due to $y_{\mathrm{t_0}} \neq 1$.}
-
-\begin{equation} \label{eq:Stern_CES_model_in_print}
-  y = \left\{ (1-\gamma_E) \left[ k^{\alpha} \left( \mathrm{e}^{\lambda_L(t-t_0)} l \right)^{\beta} \right]^{\frac{\sigma-1}{\sigma}}   
-      + (\gamma_E) \left[ \mathrm{e}^{\lambda_E(t-t_0)} e \right]^{\frac{\sigma - 1}{\sigma}}   \right\}
-      ^{\frac{\sigma}{\sigma - 1}},
-\end{equation}
-
-\noindent where $e$ is one of $q$, $x$, or $u$; $\sigma$, $\gamma_E$, $\beta$, $\lambda_L$, and $\lambda_E$ are fitting parameters; $\mathrm{e}$ is the base of the natural logarithm; and the sum $\alpha + \beta$ is constrained to unity.
-
-The \texttt{R} \citep{R} package \texttt{micEconCES} \citep{Henningsen:2011td} estimates CES production functions of the form (among others)
-
-\begin{equation} \label{eq:micEconCES_model}
-  y = \gamma \mathrm{e}^{\lambda(t-t_0)}  
-      \left\{\delta \left[\delta_1 k^{-\rho_1} + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1} 
-              + (1-\delta) e^{-\rho} \right\}^{-1/\rho}.
-\end{equation}
-
-\citet{Henningsen:2011td}, in their detailed analysis of \citet{Kemfert:1998vd}, found that
-
-\begin{quote}
-\ldots the Levenberg-Marquardt and the PORT algorithms are---at least in this study---most likely to find the coefficients that give the best fit to the model, where the PORT algorithm can be used to restrict the estimates to the economically meaningful region.
-\end{quote}
+\label{sec:CES_Parameter_Estimation}
+%++++++++++++++++++++++++++++++
+
+% This bit about the Stern model is commented out for now. I'm leaving it in the paper in case we decide to use it later.
+% \citet{Stern:2012ey} developed a CES model of the form\footnote{The CES equation in \citet{Stern:2012ey} appears as
+% 
+% \begin{equation*} \label{eq:Stern_CES_model}
+%   y = \left\{ (1-\gamma_E)^{1/\sigma} \left[ k^{\alpha} \left( \mathrm{e}^{\lambda_L(t-t_0)} l \right)^{\beta} \right]^{\frac{\sigma-1}{\sigma}}   
+%       + (\gamma_E)^{1/\sigma} \left[ \mathrm{e}^{\lambda_E(t-t_0)} e \right]^{\frac{\sigma - 1}{\sigma}}   \right\}
+%       ^{\frac{\sigma}{\sigma - 1}},
+% \end{equation*}
+% 
+% but the $1/\sigma$ exponent on the $(1-\gamma_E)$ and $\gamma_E$ terms is erroneous due to $y_{\mathrm{t_0}} \neq 1$.} 
+% 
+% 
+% \begin{equation} \label{eq:Stern_CES_model_in_print}
+%   y = \left\{ (1-\gamma_E) \left[ k^{\alpha} \left( \mathrm{e}^{\lambda_L(t-t_0)} l \right)^{\beta} \right]^{\frac{\sigma-1}{\sigma}}   
+%       + (\gamma_E) \left[ \mathrm{e}^{\lambda_E(t-t_0)} e \right]^{\frac{\sigma - 1}{\sigma}}   \right\}
+%       ^{\frac{\sigma}{\sigma - 1}},
+% \end{equation}
+% 
+% \noindent where $e$ is one of $q$, $x$, or $u$; $\sigma$, $\gamma_E$, $\beta$, $\lambda_L$, and $\lambda_E$ are fitting parameters; $\mathrm{e}$ is the base of the natural logarithm; and the sum $\alpha + \beta$ is constrained to unity.
+
+The CES model without and with energy is given by Equations \ref{eq:CES} and \ref{eq:CESe}, respectively.
+The \texttt{R} \citep{R} package \texttt{micEconCES} \citep{Henningsen:2011td} was used to estimate parameters $\gamma$, $\lambda$, $\delta_1$, $\rho_1$, $\delta$, and $\rho$.
+********* More details here about which algorithms were used, etc.
+Complete after our work this summer.
+******* Elasticities of substitution $\sigma_1$ and $\sigma$ (see Section \ref{sec:CES}) were estimated by the delta method (****** is this correct?
+Ask Pruim.
+******).
+
+% \citet{Henningsen:2011td}, in their detailed analysis of \citet{Kemfert:1998vd}, found that 
+% 
+% \begin{quote}
+% \ldots the Levenberg-Marquardt and the PORT algorithms are---at least in this study---most likely to find the coefficients that give the best fit to the model, where the PORT algorithm can be used to restrict the estimates to the economically meaningful region.
+% \end{quote}
 
@@
 
-Similar to the analysis of the Cobb-Douglas model above, we make partial residual plots for the CES model in Figures \ref{fig:CESPartialResidualsQ} - \ref{fig:CESPartialResidualsU} below.
+Similar to the analysis of the Cobb-Douglas model in Section \ref{sec:CD_Parameter_Estimation}, we make partial residual plots for the CES model (without energy) in Figures \ref{fig:CESPartialResidualsQ} - \ref{fig:CESPartialResidualsU} below.
 Again, no strong monotonic trend is observed, suggesting the energy-augmentation of the CES model will not significantly improve the model.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Confidence Intervals for Cobb-Douglas and CES Models}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%++++++++++++++++++++++++++++++
+\subsection{Confidence Intervals for Cobb-Douglas and CES Energy Parameters}
+\label{sec:CI_for_CD_and_CES}
+%++++++++++++++++++++++++++++++
 
 The key energy parameters for the Cobb-Douglas and CES models are $\gamma$, $\delta$, and $\sigma$.
-The parameter $\gamma$ in the Cobb-Douglas model (Equation \ref{eq:CD_With_Energy}) indicates the importance of energy for economic growth.
+The parameter $\gamma$ in the Cobb-Douglas model (Equation \ref{eq:CDe}) indicates the importance of energy for economic growth.
 When $\gamma \rightarrow 0$, energy is not a significant contributor to economic growth for an economy.
@@
 On a graph of the width of the 95\% confidence interval for $\gamma$ ($CI_{95\%,\gamma}$) vs.
-$\gamma$, where each economy is represented by a point, the locus of points where the 95\% confidence interval on $\gamma$ crosses 0 is a diagonal line.
+$\gamma$, where each economy is represented by a point (its two-letter abbreviation; see Table \ref{tab:Economy_Examples}), the locus of points where the 95\% confidence interval for $\gamma$ crosses 0 is a diagonal line.
 If the combination of $\gamma$ and its confidence interval for a given economy is below and to the right of the line, we have high confidence that we can say whether or not energy is a significant contributor to economic growth.
@@
 
-For the CES model (Equation \ref{eq:micEconCES_model}), the parameter $\delta$ indicates the importance of energy for economic growth.
+For the CES model (Equation \ref{eq:CESe}), the parameter $\delta$ indicates the importance of energy for economic growth.
 When $\delta \rightarrow 1$, energy is an insignificant contributor to economic growth, and when $\delta \rightarrow 0$, energy is the primary contributor to economic growth for an economy.
@@
 
-For the CES model (Equation \ref{eq:micEconCES_model}), the parameter $\sigma$ indicates whether capital stock and labor ($kl$) and energy ($e$) are complements ($\sigma <$ 1) or substitutes ($\sigma >$ 1).
+For the CES model (Equation \ref{eq:CESe}), the parameter $\sigma$ indicates whether capital stock and labor ($kl$) and energy ($e$) are complements ($\sigma <$ 1) or substitutes ($\sigma >$ 1).
 For countries whose combination of  $\sigma$ and its confidence interval is below and to the left of the lines in the rightmost graphs of Figure \ref{fig:CIvsParam_Lattice_Graph} we can say (with 95\% confidence) that ($kl$) and ($e$) are complements.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{LINEX Models}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+************* Matt ended here. ****************
+
+%++++++++++++++++++++++++++++++
+\subsection{LINEX Models}
+\label{sec:LINEX_Parameter_Estimation}
+%++++++++++++++++++++++++++++++
 

### 2013-05-02 EconGrowth.Rnw
Adjusted the LINEX section text slightly.

@@
 
-The LINEX model has the form
-
-\begin{equation} \label{eq:LINEX_model}
-  y = \mathrm{e}^{\left[a_0 \left(2 - \frac{l + e}{k} \right) + a_0 c_t \left(\frac{l}{e} - 1 \right)\right]} \: e ,
-\end{equation}
-
-\noindent where $e$ is one of $q$, $x$, or $u$; $a_0$ and $c_t$ are fitting parameters; and $\mathrm{e}$ is the base of the natural logarithm.
-
+The LINEX model is given in Equation \ref{eq:LINEX}.
+Parameters $a_0$ and $c_t$ were estimated using the \texttt{nls} function in \texttt{R} \citep{R}.
 Figure \ref{fig:LINEXq_Params_Graph} shows values and 95\% confidence intervals for the parameters for the LINEX model (with $q$).
@@
 @
+
+************* Matt ended here. ****************
 

### 2013-05-03 EconGrowth.Rnw
Edits on the implications section.

@@
 Figure \ref{fig:Historical_Lattice_Graph} indicates the importance of energy quantification for economic growth modeling.
-Thermal energy ($q$) and exergy ($x$) grow at similar rates, unless there is a significant raw energy carrier substitution in the economy (such as China's rapid increase of natural gas and coal consumption relative to petroleum since 2000).
+Thermal energy ($q$) and exergy ($x$) grow at similar rates, unless there is a significant raw energy carrier substitution in the economy (such as China's rapid increase of coal and natural gas consumption relative to petroleum since 2000).
 The growth rate of $u$ is significantly different from $q$ and $x$ for most countries, however.
@@
 
-<<CDeGridLattice, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Grid search over $\\gamma$ for Cobb-Douglas with energy model.">>=
+<<CDeGridLattice, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Grid search over $\\gamma$ for Cobb-Douglas model with thermal energy ($q$).">>=
 cdeGridLattice(energyType="Q")
@@
 
-************* Matt ended here. ****************
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-************* Do we need this? **************
-
-************* Martin needs to write this. **************
+The above analysis points to several implications.
+
+\begin{itemize}
+  \item{The use of exergy, as opposed to thermal energy, in economic growth models is probably unnecessary.
+The exergy allocation factors are all close to unity (Table \ref{tab:Exergy_Allocation}).
+In the absence of very large changes in energy mix for an economy, indexed exergy ($x$) and thermal energy ($q$) are very similar.
+Figure \ref{fig:Historical_Lattice_Graph} shows that $q$ and $x$ lines lie atop one another for almost every economy.}
+  \item{Figure \ref{fig:CDeGridLattice} shows that the set of parameters ($\lambda$, $\alpha$, $\beta$, and $\gamma$) that minimizes $SSE$ for the energy-augmented Cobb-Douglas production function always (with the exception of Saudi Arabia) has $\beta = 0$ or $\gamma = 0$.
+This result implies that it is unnecessary to include both labor ($l$) and energy ($e$) in the Cobb-Douglas production function.}
+  \item{Partial residual plots for both the Cobb-Douglas model (Figures \ref{fig:CDPartialResidualsQ}--\ref{fig:CDPartialResidualsU} and CES model (Figures \ref{fig:CESPartialResidualsQ}--\ref{fig:CESPartialResidualsU}) indicate that augmenting the Cobb-Douglas and CES production functions with energy is not beneficial.}
+  \item{Figure \ref{fig:CIvsParam_Lattice_Graph} shows that important energy parameters for both the energy-augmented Cobb-Douglas ($\gamma$) and CES ($\delta$) production functions have large confidence intervals such that we are unable to say (at the 95\% confidence level) that energy is an important factor for economic growth, vis-\`{a}-vis capital stock ($k$) or labor ($l$) for most economies.}
+  \item{Figure \ref{fig:CIvsParam_Lattice_Graph} indicates that energy (in all quantifications, $q$, $x$, and $u$) is complementary to capital stock ($k$) and labor ($l$) for producing economic growth.}
+  \item{Figures \ref{fig:LINEXq_Params_Graph}--\ref{fig:LINEXu_Params_Graph} indicate that LINEX model fitting parameters $a_0$ and $c_t$ are significant (at the 95\% confidence level) for nearly all countries.
+The LINEX production function provides reasonable good fits to historical data.
+This evidence indicates that the LINEX production function (with energy ($e$) as its only factor of production) is a reasonable replacement for capital stock ($k$) and labor ($l$) in the Cobb-Douglas and CES production functions.}
+  \item{The concept of useful work ($u$) has potential and should be explored beyond developed economies.
+Figure \ref{fig:Historical_Lattice_Graph} shows that $u$ grows at very different rates from $k$ or $l$ for the developed economies.
+The covariance values in Section \ref{sec:Covariance_Tables} show that $u$ has much lower covariances with $k$ and $l$ than $q$ or $x$ has with $k$ and $l$.
+Thus, $u$ may contain more information relative to $k$ and $l$ than $q$ or $x$ and may, therefore, be more useful in economic growth modeling than $q$ or $x$.
+******* Check this assumption after we obtain covariance values for $u$.
+}
+\end{itemize}
+
+The evidence above leads to a re-conceptualization of the relationship among energy, capital stock, and labor: energy is \emph{embedded} in capital stock and labor, and, therefore, it is unwarranted and unnecessary to include \emph{both} energy and the capital stock/labor pair in production functions.
+The empirical evidence indicates that an energy-only production function (LINEX) also provides a reasonable model for economic growth.
+
+************* The above section needs to be re-evaluated after the statistical work is tightened up. ****************
+
+************* Martin needs to flesh out the above section. **************
+
+************* Matt ended here. ****************
 
@@
 
-Funding for Caleb Reese and Lucas Timmer was generously supplied by the Jack and Lois Kuipers Applied Mathematics Endowment and the Calvin College Alumni Association.
+Funding for Caleb Reese and Lucas Timmer was provided by the Jack and Lois Kuipers Applied Mathematics Endowment and the Calvin College Alumni Association.
 Support for Matthew Kuperus Heun was provided by a Calvin College Research Followship.
@@
 
-In the spirit of Reproducible Research \citep{Gandrud:2013vx}, all data, spreadsheets, \texttt{R} code \citep{R}, and other materials associated with this paper can be found at \protect\url{https://github.com/MatthewHeun/Econ-Growth- R-Analysis}.
+In the spirit of Reproducible Research \citep{Gandrud:2013vx}, all data, spreadsheets, \texttt{R} code \citep{R}, and other materials associated with this paper can be found at \protect\url{https://github.com/MatthewHeun/Econ-Growth-R-Analysis}.
 

### 2013-05-06 EconGrowth-R-Functions.Rnw
Fixed covariance tables to be complete, even for U columns and rows.

--- 2013-04-30 EconGrowth-R-Functions.Rnw
@@
   data <- loadData(countryAbbrev)
-  # Grab only the data we want.
+  if (countryAbbrev %in% countryAbbrevsU){
+    # Calculate covariances among the typical variables.
+    dataForCovar <- cbind(data$iGDP, data$iCapStk, data$iLabor, data$iQ, data$iX, data$iU)
+    # Calculates the covariances among y, k. l, q, x, and u using all available data, namely,
+    # 1980-2011 for covariances among y, k, l, q, and x for developed economies
+    # 1980-2000 for covariances involving u for developed economies
+    # 1991-2011 for covariances among y, k, l, q, and x for developing economies
+    covarResults <- data.frame(cor(x=dataForCovar, use="pairwise.complete.obs"))
+    names <- c("$y$", "$k$", "$l$", "$q$", "$x$", "$u$")
+  } else {
     dataForCovar <- cbind(data$iGDP, data$iCapStk, data$iLabor, data$iQ, data$iX)
+    covarResults <- cor(dataForCovar)
     names <- c("$y$", "$k$", "$l$", "$q$", "$x$")
-  if (countryAbbrev %in% countryAbbrevsU){
-    # Add U data only if we have it.
-    dataForCovar <- cbind(dataForCovar, data$iU)
-    names <- c("$y$", "$k$", "$l$", "$q$", "$x$", "$u$")
-  }
-  covarResults <- cor(dataForCovar)
+  }
   colnames(covarResults) <- names
   rownames(covarResults) <- names
+  # Now make an xtable so it displays nicely
   covarXtable <- xtable(covarResults, 

### 2013-05-06 EconGrowth.Rnw
Fixed covariance tables to be complete, even for U columns and rows.

@@
       \end{itemize}
-\item{Heun: Deal with missing covariance numbers when columns have unequal length. Use the \texttt{subset} command? Partially complete: need to work on the $u$ data only.}
 \item{Heun: Eliminate blanks in the coefficient tables for the 95\% CIs in the Cobb-Douglas with energy rows}
@@
 \item{de Wit: review, critique, and contextualize.}
+\item{\st{Heun: Deal with missing covariance numbers when columns have unequal length. Use the \texttt{subset} command? Partially complete: need to work on the $u$ data only.}}
 \item{\st{Heun: Ensure consistent x and y axis limits in partial residual plots}}
@@
 Factors of production track each other closely, and high covariances among these variables can be seen in Tables \ref{tab:Covariance_US} through \ref{tab:Covariance_ZM}.
-
-% You can add fig.pos="H" to force the figure position to be this exact place.
-
-<<Historical_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Historical data: Indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$).">>=
+**************** Discuss the covariances in more detail after we finalize the covariances for U.
+*******************
+
+<<Historical_Lattice_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Historical data: Indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$).">>=
 createHistoricalLatticeGraph()
@@
 
-<<CD_Params_Graph, fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.cap="Cobb-Douglas (without energy) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
+<<CD_Params_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.cap="Cobb-Douglas (without energy) model parameters.
+Vertical bars indicate 95\\% confidence intervals.">>=
 createCDParamsGraph(energyType=NA)
@@
 
-<<CDPartialResidualsQ, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="Cobb-Douglas partial residuals plot for thermal energy ($q$).">>=
+<<CDPartialResidualsQ, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="Cobb-Douglas partial residuals plot for thermal energy ($q$).">>=
 createPartialResidualPlot(modelType="CD", energyType="Q", countryAbbrev=NA)
@@
 
-<<CDPartialResidualsX, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="Cobb-Douglas partial residuals plot for exergy ($x$).">>=
+<<CDPartialResidualsX, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="Cobb-Douglas partial residuals plot for exergy ($x$).">>=
 createPartialResidualPlot(modelType="CD", energyType="X", countryAbbrev=NA)
@@
 
-<<CDPartialResidualsU, fig.width=threePanelGraphWidth, fig.height=threePanelGraphHeight, fig.align="center", fig.cap="Cobb-Douglas partial residuals plot for useful work ($u$).">>=
+<<CDPartialResidualsU, fig.pos="H", fig.width=threePanelGraphWidth, fig.height=threePanelGraphHeight, fig.align="center", fig.cap="Cobb-Douglas partial residuals plot for useful work ($u$).">>=
 createPartialResidualPlot(modelType="CD", energyType="U", countryAbbrev=NA)
@@
 
-<<CDeGridLattice, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Grid search over $\\gamma$ for Cobb-Douglas model with thermal energy ($q$).">>=
+<<CDeGridLattice, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Grid search over $\\gamma$ for Cobb-Douglas model with thermal energy ($q$).">>=
 cdeGridLattice(energyType="Q")
@@
 
-<<CDq_Params_Graph, fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.cap="Cobb-Douglas (with $q$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
+<<CDq_Params_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.cap="Cobb-Douglas (with $q$) model parameters.
+Vertical bars indicate 95\\% confidence intervals.">>=
 createCDParamsGraph(energyType="Q")
@@
 
-<<CDx_Params_Graph, fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.cap="Cobb-Douglas (with $x$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
+<<CDx_Params_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.cap="Cobb-Douglas (with $x$) model parameters.
+Vertical bars indicate 95\\% confidence intervals.">>=
 createCDParamsGraph(energyType="X")
@@
 
-<<CDu_Params_Graph, fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.cap="Cobb-Douglas (with $u$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
+<<CDu_Params_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.cap="Cobb-Douglas (with $u$) model parameters.
+Vertical bars indicate 95\\% confidence intervals.">>=
 createCDParamsGraph(energyType="U")
@@
 
-<<CD_GDP_Lattice_Graph, fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas results.">>=
+<<CD_GDP_Lattice_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas results.">>=
 createCDLatticeGraph()
@@
 
-<<CES_Params_Graph, fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (without energy) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
+<<CES_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (without energy) model parameters.
+Vertical bars indicate 95\\% confidence intervals.">>=
 createCESParamsGraph(energyType=NA)
@@
 
-<<CESPartialResidualsQ, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="CES partial residuals plot for thermal energy ($q$).">>=
+<<CESPartialResidualsQ, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="CES partial residuals plot for thermal energy ($q$).">>=
 createPartialResidualPlot(modelType="CES", energyType="Q", countryAbbrev=NA)
@@
 
-<<CESPartialResidualsX, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="CES partial residuals plot for exergy ($x$).">>=
+<<CESPartialResidualsX, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="CES partial residuals plot for exergy ($x$).">>=
 createPartialResidualPlot(modelType="CES", energyType="X", countryAbbrev=NA)
@@
 
-<<CESPartialResidualsU, fig.width=threePanelGraphWidth, fig.height=threePanelGraphHeight, fig.align="center", fig.cap="CES partial residuals plot for useful work ($u$).">>=
+<<CESPartialResidualsU, fig.pos="H", fig.width=threePanelGraphWidth, fig.height=threePanelGraphHeight, fig.align="center", fig.cap="CES partial residuals plot for useful work ($u$).">>=
 createPartialResidualPlot(modelType="CES", energyType="U", countryAbbrev=NA)
@@
 
-<<CESq_Params_Graph, fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with $q$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
+<<CESq_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with $q$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
 createCESParamsGraph(energyType="Q")
@@
 
-<<CESx_Params_Graph, fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with $x$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
+<<CESx_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with $x$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
 createCESParamsGraph(energyType="X")
@@
 
-<<CESu_Params_Graph, fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with $u$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
+<<CESu_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with $u$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
 createCESParamsGraph(energyType="U")
@@
 
-<<CES_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES results.">>=
+<<CES_GDP_Lattice_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES results.">>=
 createCESLatticeGraph()
@@
 
-<<CIvsParam_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="95\\% Confidence interval widths vs.
+<<CIvsParam_Lattice_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="95\\% Confidence interval widths vs.
 parameter values for key energy parameters ($\\gamma$, $\\delta$, and $\\sigma$) of the Cobb-Douglas and CES models with energy.
@@
 
-<<LINEXq_Params_Graph, fig.width=linexParameterGraphWidth, fig.height=linexParameterGraphHeight, fig.cap="LINEX (with $q$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
+<<LINEXq_Params_Graph, fig.pos="H", fig.width=linexParameterGraphWidth, fig.height=linexParameterGraphHeight, fig.cap="LINEX (with $q$) model parameters.
+Vertical bars indicate 95\\% confidence intervals.">>=
 createLINEXParamsGraph(energyType="Q")
@@
 
-<<LINEXx_Params_Graph, fig.width=linexParameterGraphWidth, fig.height=linexParameterGraphHeight, fig.cap="LINEX (with $x$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
+<<LINEXx_Params_Graph, fig.pos="H", fig.width=linexParameterGraphWidth, fig.height=linexParameterGraphHeight, fig.cap="LINEX (with $x$) model parameters.
+Vertical bars indicate 95\\% confidence intervals.">>=
 createLINEXParamsGraph(energyType="X")
@@
 
-<<LINEXu_Params_Graph, fig.width=linexParameterGraphWidth, fig.height=linexParameterGraphHeight, fig.cap="LINEX (with $u$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
+<<LINEXu_Params_Graph, fig.pos="H", fig.width=linexParameterGraphWidth, fig.height=linexParameterGraphHeight, fig.cap="LINEX (with $u$) model parameters.
+Vertical bars indicate 95\\% confidence intervals.">>=
 createLINEXParamsGraph(energyType="U")
@@
 
-<<LINEX_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX results.">>=
+<<LINEX_GDP_Lattice_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX results.">>=
 createLINEXLatticeGraph()
@@
 
+****** This section needs to be re-evaluated after the statistical work is tightened up during Summer 2013. ******
+
 The above analysis points to several implications.
@@
 \begin{itemize}
-  \item{The use of exergy, as opposed to thermal energy, in economic growth models is probably unnecessary.
-The exergy allocation factors are all close to unity (Table \ref{tab:Exergy_Allocation}).
-In the absence of very large changes in energy mix for an economy, indexed exergy ($x$) and thermal energy ($q$) are very similar.
-Figure \ref{fig:Historical_Lattice_Graph} shows that $q$ and $x$ lines lie atop one another for almost every economy.}
+  \item{The use of chemical exergy, as opposed to thermal energy, in economic growth models is probably unnecessary.
+Table \ref{tab:Exergy_Allocation} shows that exergy allocation factors are all close to unity.
+In the absence of very large changes in energy mix for an economy, indexed chemical exergy ($x$) and thermal energy ($q$) are very similar, and Figure \ref{fig:Historical_Lattice_Graph} shows that $q$ and $x$ lines lie atop one another for almost every economy.}
   \item{Figure \ref{fig:CDeGridLattice} shows that the set of parameters ($\lambda$, $\alpha$, $\beta$, and $\gamma$) that minimizes $SSE$ for the energy-augmented Cobb-Douglas production function always (with the exception of Saudi Arabia) has $\beta = 0$ or $\gamma = 0$.
@@
   \item{Partial residual plots for both the Cobb-Douglas model (Figures \ref{fig:CDPartialResidualsQ}--\ref{fig:CDPartialResidualsU} and CES model (Figures \ref{fig:CESPartialResidualsQ}--\ref{fig:CESPartialResidualsU}) indicate that augmenting the Cobb-Douglas and CES production functions with energy is not beneficial.}
-  \item{Figure \ref{fig:CIvsParam_Lattice_Graph} shows that important energy parameters for both the energy-augmented Cobb-Douglas ($\gamma$) and CES ($\delta$) production functions have large confidence intervals such that we are unable to say (at the 95\% confidence level) that energy is an important factor for economic growth, vis-\`{a}-vis capital stock ($k$) or labor ($l$) for most economies.}
-  \item{Figure \ref{fig:CIvsParam_Lattice_Graph} indicates that energy (in all quantifications, $q$, $x$, and $u$) is complementary to capital stock ($k$) and labor ($l$) for producing economic growth.}
+  \item{Figure \ref{fig:CIvsParam_Lattice_Graph} shows that important energy parameters for both the energy-augmented Cobb-Douglas and CES production functions ($\gamma$ and $\delta$, respectively) have large confidence intervals such that we are unable to say (at the 95\% confidence level) that energy is an important factor for economic growth, vis-\`{a}-vis capital stock ($k$) or labor ($l$) for most economies.}
+  \item{Figure \ref{fig:CIvsParam_Lattice_Graph} indicates that energy (in all quantifications: $q$, $x$, and $u$) is complementary to capital stock ($k$) and labor ($l$) for producing economic growth, according to the CES model.}
   \item{Figures \ref{fig:LINEXq_Params_Graph}--\ref{fig:LINEXu_Params_Graph} indicate that LINEX model fitting parameters $a_0$ and $c_t$ are significant (at the 95\% confidence level) for nearly all countries.
-The LINEX production function provides reasonable good fits to historical data.
-This evidence indicates that the LINEX production function (with energy ($e$) as its only factor of production) is a reasonable replacement for capital stock ($k$) and labor ($l$) in the Cobb-Douglas and CES production functions.}
+Figure \ref{fig:LINEX_GDP_Lattice_Graph} shows that the LINEX production function provides reasonably good fits to historical data.
+This evidence indicates that the LINEX production function (with energy ($e$) as its only factor of production) is a reasonable replacement the Cobb-Douglas and CES production functions which have capital stock ($k$) and labor ($l$) as factors of production.}
+  \item{****** Discuss the AIC values for each of the model types.
+It could happen that the LINEX models have a higher AIC value than the CD or CES models.
+If so, that would mean that the LINEX model is actually preferred to the CD or CES models, primarily because it does a good-enough job of predicting economic output with fewer adjustable parameters (2) compared to CD (2), CDe (3), CES (4), CESe (6).
+Discuss with Randy Pruim during Summer 2013.}
   \item{The concept of useful work ($u$) has potential and should be explored beyond developed economies.
 Figure \ref{fig:Historical_Lattice_Graph} shows that $u$ grows at very different rates from $k$ or $l$ for the developed economies.
-The covariance values in Section \ref{sec:Covariance_Tables} show that $u$ has much lower covariances with $k$ and $l$ than $q$ or $x$ has with $k$ and $l$.
+The covariance values in Tables \ref{tab:Covariance_US}--\ref{tab:Covariance_ZM} show that $u$ has much lower covariances with $k$ and $l$ than $q$ or $x$ has with $k$ and $l$.
 Thus, $u$ may contain more information relative to $k$ and $l$ than $q$ or $x$ and may, therefore, be more useful in economic growth modeling than $q$ or $x$.
-******* Check this assumption after we obtain covariance values for $u$.
-}
+******* Check this assumption after we obtain covariance values for $u$.**********}
 \end{itemize}
 
-The evidence above leads to a re-conceptualization of the relationship among energy, capital stock, and labor: energy is \emph{embedded} in capital stock and labor, and, therefore, it is unwarranted and unnecessary to include \emph{both} energy and the capital stock/labor pair in production functions.
-The empirical evidence indicates that an energy-only production function (LINEX) also provides a reasonable model for economic growth.
-
-************* The above section needs to be re-evaluated after the statistical work is tightened up. ****************
+The evidence above leads to a re-conceptualization of the relationships among energy, capital stock, and labor: energy is \emph{embedded within} capital stock and labor, and, therefore, it is both unwarranted and unnecessary to include \emph{both} energy ($e$) and the capital stock/labor pair ($kl$) in a production function.
+The empirical evidence indicates that \emph{both} (a) capital stock/labor production functions (Cobb-Douglas and CES without energy) and (b) an energy-only production function (LINEX) provide a reasonable models for economic growth.
 
 ************* Martin needs to flesh out the above section. **************
-
-************* Matt ended here. ****************
 
@@
 \setcounter{figure}{0} % Restarts figure number counter at 0 in this section.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The following tables show covariances among GDP ($y$) and factors of production ($k$, $l$, $q$, $x$, and $u$).
-
-<<Print_Covariance_Tables, results='asis'>>=
+\setcounter{equation}{0} % Restarts equation counter to 0 in this section.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The following tables show covariances among GDP ($y$) and factors of production ($k$, $l$, $q$, $x$, and $u$). Covariances are calculated for the following years: 
+\begin{itemize}
+  \item{1980-2011 for covariances among $y$, $k$, $l$, $q$, and $x$ for developed economies;}
+  \item{1980-2000 for covariances involving $u$ for developed economies; and}
+  \item{1991-2011 for covariances among $y$, $k$, $l$, $q$, and $x$ for developing economies.}
+\end{itemize}
+
+<<Print_Covariance_Tables, results='asis', eval=TRUE>>=
 #I wish I could say the following, but I get bogus "$US" strings appearing in the LaTeX output.
@@
 
-<<SFk_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.cap="Single-factor (with $k$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
+<<SFk_Params_Graph, fig.pos="H", fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.cap="Single-factor (with $k$) model parameters.
+Vertical bars indicate 95\\% confidence intervals.">>=
 createSFParamsGraph(factor="K")
@@
 
-<<SFl_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.cap="Single-factor (with $l$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
+<<SFl_Params_Graph, fig.pos="H", fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.cap="Single-factor (with $l$) model parameters.
+Vertical bars indicate 95\\% confidence intervals.">>=
 createSFParamsGraph(factor="L")
@@
 
-<<SFq_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.cap="Single-factor (with $q$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
+<<SFq_Params_Graph, fig.pos="H", fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.cap="Single-factor (with $q$) model parameters.
+Vertical bars indicate 95\\% confidence intervals.">>=
 createSFParamsGraph(factor="Q")
@@
 
-<<SFx_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.cap="Single-factor (with $x$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
+<<SFx_Params_Graph, fig.pos="H", fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.cap="Single-factor (with $x$) model parameters.
+Vertical bars indicate 95\\% confidence intervals.">>=
 createSFParamsGraph(factor="X")
@@
 
-<<SFu_Params_Graph, fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.cap="Single-factor (with $u$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
+<<SFu_Params_Graph, fig.pos="H", fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.cap="Single-factor (with $u$) model parameters.
+Vertical bars indicate 95\\% confidence intervals.">>=
 createSFParamsGraph(factor="U")
@@
 
-<<SF_GDP_Lattice_Graph, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single-factor results.">>=
+<<SF_GDP_Lattice_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single-factor results.">>=
 createSFLatticeGraph()

### 2013-05-06 EconGrowth-R-Functions.Rnw
Added a better comment about covariance calculations.

@@
     # 1991-2011 for covariances among y, k, l, q, and x for developing economies
+    # The key here is the use="pairwise.complete.obs" argument.
     covarResults <- data.frame(cor(x=dataForCovar, use="pairwise.complete.obs"))

### 2013-05-06 EconGrowth.Rnw
Changes to to-do list and other small adjustments.

@@
 \item{Reese: Fix the energy sankey diagram from the seminar}
-\item{Heun: Include the adjusted sankey diagram in the seminar}
-\item{Heun: Add the insight that for indexed factors of production $q$ and $x$, there is small difference in absolute magnitude and even smaller difference in indexed values unless $f_{exergy-allocation}$ is significantly different from 1.0 \emph{and} there is a shift in energy input to the economy.}
+\item{Heun: Include Caleb's adjusted sankey diagram in the seminar}
 \item{Heun: Add CES production function fits}
@@
 \item{de Wit: review, critique, and contextualize.}
+\item{\st{Heun: Add the insight that for indexed factors of production $q$ and $x$, there is small difference in absolute magnitude and even smaller difference in indexed values unless $f_{exergy-allocation}$ is significantly different from 1.0 \emph{and} there is a shift in energy input to the economy.}}
 \item{\st{Heun: Deal with missing covariance numbers when columns have unequal length. Use the \texttt{subset} command? Partially complete: need to work on the $u$ data only.}}
@@
 Table \ref{tab:Exergy_Allocation} shows that exergy allocation factors are all close to unity.
-In the absence of very large changes in energy mix for an economy, indexed chemical exergy ($x$) and thermal energy ($q$) are very similar, and Figure \ref{fig:Historical_Lattice_Graph} shows that $q$ and $x$ lines lie atop one another for almost every economy.}
+Therefore, there is a small difference in absolute magnitude between $Q$ and $X$.
+However, there is no difference in indexed magnitude between $q$ and $x$, unless there are large changes in energy mix for an economy.
+Figure \ref{fig:Historical_Lattice_Graph} shows that $q$ and $x$ lines lie atop one another for almost every economy.}
+  \item{The concept of useful work ($u$) is potentially useful and should be explored beyond developed economies.
+Figure \ref{fig:Historical_Lattice_Graph} shows that $u$ grows at very different rates from thermal energy ($q$) or exergy ($x$).
+Useful work may contain different information from thermal energy and exergy.}
   \item{Figure \ref{fig:CDeGridLattice} shows that the set of parameters ($\lambda$, $\alpha$, $\beta$, and $\gamma$) that minimizes $SSE$ for the energy-augmented Cobb-Douglas production function always (with the exception of Saudi Arabia) has $\beta = 0$ or $\gamma = 0$.
@@
 Discuss with Randy Pruim during Summer 2013.}
-  \item{The concept of useful work ($u$) has potential and should be explored beyond developed economies.
-Figure \ref{fig:Historical_Lattice_Graph} shows that $u$ grows at very different rates from $k$ or $l$ for the developed economies.
-The covariance values in Tables \ref{tab:Covariance_US}--\ref{tab:Covariance_ZM} show that $u$ has much lower covariances with $k$ and $l$ than $q$ or $x$ has with $k$ and $l$.
-Thus, $u$ may contain more information relative to $k$ and $l$ than $q$ or $x$ and may, therefore, be more useful in economic growth modeling than $q$ or $x$.
-******* Check this assumption after we obtain covariance values for $u$.**********}
 \end{itemize}

### 2013-05-06 EconGrowth.Rnw
Added a draft conclusion section.

@@
 
-\noindent Equation \ref{eq:CESe} augments a standard CES production function (Equation \ref{eq:CES}) with energy using a ($kl$)($e$) nesting structure, as is typical in the literature.
+\noindent Equation \ref{eq:CES} is a CES production function with capital stock ($k$) and labor ($l$) factors of production.
+Equation \ref{eq:CESe} augments Equation \ref{eq:CES} with energy using a ($kl$)($e$) nesting structure, as is typical in the literature.
 Equation \ref{eq:CES} is a degenerate form of Equation \ref{eq:CESe} where $\delta = 1$.
@@
 
-****************** Add conclusion here. *********************
+****************** Edit conclusion after we finish the statistical studies. *********************
+
+We found that statistical properties of historical economic data (e.g., covariances) and statistical properties of fitting parameters in production functions (e.g., confidence intervals) are extremely useful for interpreting historical economic data and growth model results.
+We know of no previous energy-economic studies that presented these statistical properties, and we presume that energy-augmentation of production functions has been done in the literature without regard to whether it is statistically meaningful to do so.
+That different authors can find good correlation between model predictions and historical data with very different growth model coefficients is a result of the heretofore unseen large confidence intervals on the fitting parameters.
+As a consequence, economic growth models that assume very different relationships among capital stock, labor, and energy can all be successful in matching historical data.
+The production function is a canvas upon which investigators can paint their preconceived vision of the importance (or not) of energy for ecnomic growth.
+
+To break free of this problem, a new way of conceptualizing the relationships among capital stock, labor, and energy is required.
+Our analysis above indicates that energy is unequivocally complementary to the capital stock/labor pair for many types of economies.
+We agree with K\"{u}mmel that energy is required to form and maintain capital stock, and that energy is required to sustain labor.
+(And, for that matter, that labor is required to operate capital stock.) I.e., energy is already always \emph{embedded within} capital stock and labor.
+We posit that the complementarity between ($kl$) and ($e$) shown by the energy-augmented CES production function is due to the embeddedness of energy within the traditional factors of production, capital stock and labor.
+
+As a consequence, production functions that use only energy and production functions that use the capital stock/labor pair are both successful in predicting economic growth.
+The augmentation of capital stock/labor production functions with energy is both unwarranted and unnecessary.
 

### 2013-05-07 EconGrowth.Rnw
Small adjustment to conclusion.

@@
 Code is in the \texttt{createAICTable} function, but it is not yet working.
-Need to find a way to calculate AIC for the object that is returned from the cesEst function.}
+Need to find a way to calculate AIC for the object that is returned from the \texttt{cesEst} function.}
       \item{\st{Create parameter graphs for each country}}
@@
 
-We found that statistical properties of historical economic data (e.g., covariances) and statistical properties of fitting parameters in production functions (e.g., confidence intervals) are extremely useful for interpreting historical economic data and growth model results.
-We know of no previous energy-economic studies that presented these statistical properties, and we presume that energy-augmentation of production functions has been done in the literature without regard to whether it is statistically meaningful to do so.
+We claim that statistical properties (e.g., covariances) of historical economic data and statistical properties (e.g., confidence intervals) of production function fitting parameters are extremely useful for interpreting historical economic data and growth model results.
+We know of no previous studies on the role of energy in the economy that presented these statistical properties, and we presume that energy-augmentation of production functions has been done in the literature without regard to whether it is statistically meaningful to do so.
 That different authors can find good correlation between model predictions and historical data with very different growth model coefficients is a result of the heretofore unseen large confidence intervals on the fitting parameters.
 As a consequence, economic growth models that assume very different relationships among capital stock, labor, and energy can all be successful in matching historical data.
-The production function is a canvas upon which investigators can paint their preconceived vision of the importance (or not) of energy for ecnomic growth.
-
-To break free of this problem, a new way of conceptualizing the relationships among capital stock, labor, and energy is required.
+In short, the production function is a canvas upon which investigators can paint their preconceived vision of the importance (or not) of energy for economic growth.
+
+To break free from this problem, a new way of conceptualizing the relationships among capital stock, labor, and energy is required.
 Our analysis above indicates that energy is unequivocally complementary to the capital stock/labor pair for many types of economies.
 We agree with K\"{u}mmel that energy is required to form and maintain capital stock, and that energy is required to sustain labor.
-(And, for that matter, that labor is required to operate capital stock.) I.e., energy is already always \emph{embedded within} capital stock and labor.
+(And, for that matter, we agree that labor is required to operate capital stock.) In other words, energy is already, always \emph{embedded within} capital stock and labor.
 We posit that the complementarity between ($kl$) and ($e$) shown by the energy-augmented CES production function is due to the embeddedness of energy within the traditional factors of production, capital stock and labor.
 
-As a consequence, production functions that use only energy and production functions that use the capital stock/labor pair are both successful in predicting economic growth.
-The augmentation of capital stock/labor production functions with energy is both unwarranted and unnecessary.
+The foregoing discussion means that production functions with either (a) energy only (such as the LINEX model) or (b) capital stock/labor only (such as the Cobb-Douglas and CES models without energy) can both be successful in predicting economic growth.
+But, the embedded nature of energy in capital stock and labor means that augmenting a capital stock/labor only production function with energy is redundant and unnecessary, and, therefore, unwarranted.
 
@@
 
-In the spirit of Reproducible Research \citep{Gandrud:2013vx}, all data, spreadsheets, \texttt{R} code \citep{R}, and other materials associated with this paper can be found at \protect\url{https://github.com/MatthewHeun/Econ-Growth-R-Analysis}.
+In the spirit of Reproducible Research \citep{Gandrud:2013vx}, all data, spreadsheets, \texttt{R} code \citep{R}, and other materials associated with this paper can be found at\\*
+\protect\url{https://github.com/MatthewHeun/Econ-Growth-R-Analysis}.
 

### 2013-05-08 EconGrowth.Rnw
Edits to take care of some remaining issues in the text that Caleb wrote.

@@
 \item{Reese: Review EIA IES database for any revisions to historical data}
-\item{Reese: Add food energy intake for all countries from FAO}
+\item{Reese: Add food energy intake for all countries from FAO. We won't assume that the US caloric intake applies to all coutries.}
 \item{Reese: Fix the energy sankey diagram from the seminar}
@@
 \item{Heun: Fix warnings of the form \texttt{Warning:  step factor 0.000488281 reduced below ’minFactor’ of 0.000976562} in the code that generates the Cobb-Douglas with energy fits.}
-\item{Heun: adjust y axis limits on $a_0$ and $c_t$ parameter graphs for the LINEX model AFTER we finish debugging the LINEX models.}
 \item{de Wit: review, critique, and contextualize.}
+\item{\st{Heun: adjust y axis limits on $a_0$ and $c_t$ parameter graphs for the LINEX model AFTER we finish debugging the LINEX models.}}
 \item{\st{Heun: Add the insight that for indexed factors of production $q$ and $x$, there is small difference in absolute magnitude and even smaller difference in indexed values unless $f_{exergy-allocation}$ is significantly different from 1.0 \emph{and} there is a shift in energy input to the economy.}}
@@
 Thermal energy ($Q$) is the heat content of an energy carrier.
-Exergy ($X$) is the maximum useful work that could be extracted from an energy carrier by a process that brings the system into equilibrium with a heat reservoir (typically the surrounding environment).
-******** Caleb: Is this how Ayres and Warr use the term ``exergy''?
-************ Useful work ($U$) includes the direct energy that goes into an economy, including work from machines, human muscles, and animals.
+Exergy ($X$) is the maximum useful work that could be extracted from an energy carrier by a process that brings the system into equilibrium with a heat reservoir, typically the surrounding environment \citep[p.~78]{Ayres:2010ug}.
+Like \citeauthor{Ayres:2010ug}, we use chemical exergy (as opposed to thermal exergy or mechanical exergy) as our quantification for exergy ($x$).
+Useful work ($U$) includes the direct energy that goes into an economy, including work from machines, human muscles, and animals.
 Firms pay for thermal energy ($Q$), but useful work ($U$) alters the size and shape of materials, keeps the lights on, and transports goods to consumers.
@@
 \noindent where $C_{fuel}$ is the consumption rate of the fuel (in units of short tons/year for coal, barrels/year for oil and petroleum, ft$^3$/year for dry natural gas and natural gas plant liquids, and m$^3$/year for biomass/fuel wood) and $h_{{fuel}}$ is the heat content of the fuel (in kJ/short ton for coal, kJ/barrel for oil, kJ/ft$^3$ for dry natural gas and natural gas plant liquids, and kJ/kg for biomass/fuel wood).
-Fuel wood density (166.67 kg/m$^3$ **** Caleb: verify this number and source ****) was obtained from the \citet{FAO:2013a}.
-
-Yearly consumption rates ($C_{fuel}$) for all economies were obtained from the \citet{EIA:2013a} for coal, oil and petroleum, and dry natural gas and natural gas plant liquids.
+Fuel wood density (166.67~kg/m$^3$ **** Caleb: verify this number and source ****) was obtained from the \citet{FAO:2013a}.
+
+Yearly consumption rates ($C_{fuel}$) of coal, oil and petroleum, dry natural gas and natural gas plant liquids, and biofuels (ethanol and biodiesel) were obtained from the \citet{EIA:2013a} for all economies.
 Yearly average heat content data for coal, oil, and natural gas and natural gas plant liquids was obtained from the EIA for all economies.
+We used 26.8~MJ/kg \citep[Table~A-27]{Cengel:2011ww} and 37.8~MJ/kg \citep[Table~7.3]{Gupta:2010vg} for the heat content of ethanol and corn-based biodiesel, respectively.
 Yearly consumption and heat content data for biomass/fuel wood was obtained from the ``Fuelwood'' time series of the FAO Statistics Database \citep{FAO:2013a}.
@@
 \noindent where $Q_m$ is metabolizable energy (in kcal/day-animal) and $N$ is the number of animals.
-Metabolizable energy values ($Q_{m,horses}$ = 19,110 kcal/day-horse and $Q_{m,mules}$ = 7,215 kcal/day-mule) were taken from \citet{Warr:2012a} for horses and mules and represent the amount of energy used by animals for a day of work.
-(******** Caleb: Perhaps this should be ``represent the amount of energy in the feed consumed by animals for a day of work.'' *********) The $Q_m$ values are assumed constant for all countries and years.
-The number of horses and mules for each economy was taken from the ``Live Animals'' time series in the FAO Statistics Database \citep{FAO:2013a} ******** Get a table number from Caleb.
-*************.
+Metabolizable energy values ($Q_{m,horses}$ = 19,110 kcal/day-horse and $Q_{m,mules}$ = 7,215 kcal/day-mule) were taken from \citet{Warr:2012a}.
+$Q_m$ represents the amount of energy in the feed consumed by animals for a day of work, and they are assumed constant for all countries and years.
+The number of horses and mules for each economy was taken from the ``Live Animals'' section of the FAO Statistics online database \citep{FAO:2013a}.
 

### 2013-05-08 EconGrowth.Rnw
Minor edits.

@@
 ($\sim$ 4200 kcal/day-worker) was taken from a time series of kcal/day-person for workers for 1980--2011 \citep{Warr:2012a}.
-$Q_{m,workers}$ for other countries was taken from the \citet{FAO:2013b}.
+$Q_{m,workers}$ for other countries was taken from the \citet[``\texttt{Dietary Energy Cons.~Countries}'' tab]{FAO:2013b}.
 The value for $N_{workers}$ was obtained from the labor time series for each economy as discussed in Section \ref{sec:Labor_Data}.
@@
 
-\noindent $\eta_{food \rightarrow work, animals}$ and $\eta_{food \rightarrow work, workers}$ are animal and worker efficiency of converting food into energy respectively.
-The animal feed-to-work conversion efficiency ($\eta_{food \rightarrow work, animals}$ = 0.4) was taken from \citet{Warr:2012a} and assumed equal across all economies.
-The food-to-work efficiency for workers ($\eta_{food \rightarrow work, workers}$ = 0.2) was taken from \citet{Ayres:2010ug}.
-Following \citet[p.~315]{Ayres:2010ug}, an additional factor ($f_{enduse/intake}$) was included to account for workers' food energy that sustains the body's normal function as opposed to providing energy for physical labor \citep{Wirsenius:2000vi}.
+\noindent $\eta_{food \rightarrow work, animals}$ and $\eta_{food \rightarrow work, workers}$ are animal and worker efficiency of converting food into energy, respectively.
+The animal feed-to-work conversion efficiency ($\eta_{feed \rightarrow work, animals}$ = 0.4) was taken from \citet{Warr:2012a} and assumed equal across all economies.
+The food-to-work efficiency for workers ($\eta_{food \rightarrow work, workers}$ = 0.2) was taken from \citet[Table~B.1]{Ayres:2010ug}.
+Following \citet[p.~315]{Ayres:2010ug}, an additional factor ($f_{enduse/intake}$) was included to account for workers' food energy that sustains the body's normal function as opposed to providing energy for physical labor \citep{Wirsenius:2000vi} **** Caleb needs to find a detailed source (table, equation, number, page number) in Wirsenius for this approach *****.
 $f_{enduse/intake}$ varies by country (Table \ref{tab:f_enduse_intake}).
@@
 
-\begin{table} \caption{Food enduse-to-intake ratios for all countries.} \label{tab:f_enduse_intake}
+\begin{table} \caption{Food enduse-to-intake ratios ($f_{enduse/intake}$) for all countries.} \label{tab:f_enduse_intake}
   \begin{center}
@@
 In the case of coal consumption, only about one-third of the coal exergy is converted to useful electricity: the rest is waste heat.
-The concept of ``useful work,'' pioneered by Ayres and Warr \citep{Ayres:2003ec, Ayres:2005kn}, build upon exergy analysis to consider efficiencies of both energy production and end use.
+The concept of ``useful work,'' pioneered by Ayres and Warr \citep{Ayres:2003ec, Ayres:2005kn}, builds upon exergy analysis to consider efficiencies of both energy production and enduse.
 To calculate useful work ($U$), the total exergy input to an economy ($X$) is decomposed into several end uses: high temperature industrial heat (e.g., steel production), medium temperature heat (e.g., steam production), low temperature space heat (for residential heating), mechanical drive (energy used for prime mover engines of all types except electric motors), electricity (excluding lighting), lighting (from both electricity and fuels), and muscle work (from animals and workers) as shown in the following equation:
@@
 
-\noindent where the subscript $i$ indicates the energy end use, $\varepsilon_i$ is the efficiency of converting exergy into useful energy for each end use, and $\phi_i$ gives the fraction of exergy input to an economy that goes toward the i$^\mathrm{th}$ end use.
+\noindent where the subscript $i$ indicates the energy enduse, $\varepsilon_i$ is the efficiency of converting exergy into useful energy for each enduse, and $\phi_i$ gives the fraction of exergy input to an economy that goes toward the i$^\mathrm{th}$ enduse.
 

### 2013-05-10 EconGrowth.Rnw
Added details to energy analysis. Added a paragraph on organization of the paper. Added references.

@@
 
+The remainder of this paper is organized as follows.
+Section \ref{sec:Coordinates} discusses the coordinates of analysis described above.
+Section \ref{sec:Sources_of_Data} details sources of data and calculations to generate time series for economic output and factors of production.
+The procedures for and results from parameter estimation for the various production functions are discussed in Section \ref{sec:Parameter_Estimation}.
+Section \ref{sec:Implications} discusses implications of the parameter estimation results, and Section \ref{sec:Conclusion} concludes.
+An appendix provides details of all statistical results.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \noindent where $C_{fuel}$ is the consumption rate of the fuel (in units of short tons/year for coal, barrels/year for oil and petroleum, ft$^3$/year for dry natural gas and natural gas plant liquids, and m$^3$/year for biomass/fuel wood) and $h_{{fuel}}$ is the heat content of the fuel (in kJ/short ton for coal, kJ/barrel for oil, kJ/ft$^3$ for dry natural gas and natural gas plant liquids, and kJ/kg for biomass/fuel wood).
-Fuel wood density (166.67~kg/m$^3$ **** Caleb: verify this number and source ****) was obtained from the \citet{FAO:2013a}.
+Fuel wood density (166.67~kg/m$^3$ **** Caleb: verify this number and source ****) was calculated from ***** and *****, both obtained from the \citet{FAO:2013c}.
 
@@
 Yearly average heat content data for coal, oil, and natural gas and natural gas plant liquids was obtained from the EIA for all economies.
-We used 26.8~MJ/kg \citep[Table~A-27]{Cengel:2011ww} and 37.8~MJ/kg \citep[Table~7.3]{Gupta:2010vg} for the heat content of ethanol and corn-based biodiesel, respectively.
+We used lower (net) heating values of 26.8~MJ/kg \citep[Table~A-27]{Cengel:2011ww} and 37.8~MJ/kg \citep[Table~7.3]{Gupta:2010vg} for the heat content of ethanol and corn-based biodiesel, respectively.
 Yearly consumption and heat content data for biomass/fuel wood was obtained from the ``Fuelwood'' time series of the FAO Statistics Database \citep{FAO:2013a}.
@@
 
-Exergy ($X$), expressed in TJ/year, was calculated from the thermal energy ($Q$) values discussed in Section \ref{sec:Q_Data}.
-For fuels, exergy was calculated by a unitless exergy-to-energy allocation factor ($f_{exergy-allocation}$) from \citet[Table~A-2]{Ayres:2003ec} and shown in Table \ref{tab:Exergy_Allocation}.
+Exergy ($X$), expressed in TJ/year, was calculated by multiplying the thermal energy ($Q$) values discussed in Section \ref{sec:Q_Data} by a unitless exergy-to-thermal-energy allocation factor ($f_{exergy-allocation}$) shown in Table \ref{tab:Exergy_Allocation}.
 
@@
       natural gas liquids                     &         \\
+      Corn-based biodiesel                    & 1.07  \\
       Biomass/fuel wood                       & 1.15   \\
-      Nuclear                                 & 1.0   \\
-      Renewables                              & 1.0   \\
+      Ethanol biofuel                         & 1.099 \\
+      Nuclear, wind,                          & \multirow{2}{*}{1.0}   \\
+      solar PV, and hydro                     &                        \\
     \end{tabular}
@@
 
-\noindent $f_{exergy-allocation}$ is the ratio of chemical exergy to the higher heating value for each fuel.
+\noindent For carbon-based energy sources, $f_{exergy-allocation}$ is the ratio of chemical exergy to lower (net) heating value.
+The exergy allocation factors for coal, oil, natural gas, biodiesel, and biomass/fuel wood were obtained from \citet[Table~A-2]{Ayres:2003ec}.
+The exergy allocation ratio for liquid ethanol was calculated from the standard molar chemical exergy of 1357.7~kJ/mol \citep[Table~II]{Szargut:1988wv} and its lower (net) heating value of 26.8~MJ/kg \citep[Table~A-27]{Cengel:2011ww}.
 $f_{exergy-allocation}$ for each fuel was assumed to be constant through time across all economies.
-For renewable and nuclear energy sources, the electricity generated is already pure exergy, so $f_{exergy-allocation}$ is unity.
+For nuclear, wind, solar photovoltaic, and hydro energy sources, the electricity generated is already pure exergy, so $f_{exergy-allocation}$ is unity.
 

### 2013-05-13 EconGrowth.Rnw
Change China footnote from 4.1% to 0.41%, as requested by Caleb.

@@
 $f_{enduse/intake}$ varies by country (Table \ref{tab:f_enduse_intake}).
-A similar enduse-to-intake ratio could also be applied to animal work, but it was unavailable from \citet{Wirsenius:2000vi}.\footnote{The error in exergy caused by neglecting $f_{enduse/intake}$ for animals is very small, because animal muscle exergy is a small fraction of the total energy supply to any economy, with a maximum of 4.1\% for China in 1992.}
+A similar enduse-to-intake ratio could also be applied to animal work, but it was unavailable from \citet{Wirsenius:2000vi}.\footnote{The error in exergy caused by neglecting $f_{enduse/intake}$ for animals is very small, because animal muscle exergy is a small fraction of the total energy supply to any economy, with a maximum of 0.41\% for China in 1992.}
 

### 2013-05-24 EconGrowth-R-Functions.Rnw
Changed multiple *** comments in the paper to only 4 stars to avoid underfull and overfull boxes.

@@
   fileName <- paste("data/", countryAbbrev, "Data.txt", sep="")
-  dataTable <- read.table(fileName, header = TRUE)
+  dataTable <- read.table(file=fileName, header=TRUE)
   return(dataTable)
@@
   # Now make an xtable so it displays nicely
-  covarXtable <- xtable(covarResults, 
+  covarXtable <- xtable(x=covarResults, 
                       caption=paste(countryAbbrev, "covariance table."), 

### 2013-05-24 EconGrowth.Rnw
Changed multiple *** comments in the paper to only 4 stars to avoid underfull and overfull boxes.

@@
 %% Text of abstract
-*********** Add abstract ***********
+**** Add abstract ****
 \end{abstract}
@@
 
-**************** Martin: add more here about the conclusions of each paper regarding the role of energy in economic growth?
+**** Martin: add more here about the conclusions of each paper regarding the role of energy in economic growth?
 Add additional literature?
@@
 Especially, are there any confidence intervals or statistical evaluation in each of these studies?
-********************
+****
 
@@
 But, the nearly-complete focus on developed economies closes off the possibility of discovering any role that energy plays in the development process.
-In this paper we analyze at least two economies in each of the following four categories: Developed (technologically advanced with high standards of living), BRICS\footnote{Brazil, Russia, India, China, and South Africa} (rapid economic growth with standards of living below that of developed economies), Petrol (petroleum is a substantial source of GDP ******* Martin: Is this the right way to describe the petrol economies?
-*********); and LDCs\footnote{Lesser Developed Countries} (living standards near subsistence levels ******* Martin: Is this the right way to describe the LDC economies?
-*********).
+In this paper we analyze at least two economies in each of the following four categories: Developed (technologically advanced with high standards of living), BRICS\footnote{Brazil, Russia, India, China, and South Africa} (rapid economic growth with standards of living below that of developed economies), Petrol (petroleum is a substantial source of GDP **** Martin: Is this the right way to describe the petrol economies?
+****); and LDCs\footnote{Lesser Developed Countries} (living standards near subsistence levels **** Martin: Is this the right way to describe the LDC economies?
+****).
 (See Table \ref{tab:Economy_Examples}.)
@@
 \noindent where $C_{fuel}$ is the consumption rate of the fuel (in units of short tons/year for coal, barrels/year for oil and petroleum, ft$^3$/year for dry natural gas and natural gas plant liquids, and m$^3$/year for biomass/fuel wood) and $h_{{fuel}}$ is the heat content of the fuel (in kJ/short ton for coal, kJ/barrel for oil, kJ/ft$^3$ for dry natural gas and natural gas plant liquids, and kJ/kg for biomass/fuel wood).
-Fuel wood density (166.67~kg/m$^3$ **** Caleb: verify this number and source ****) was calculated from ***** and *****, both obtained from the \citet{FAO:2013c}.
+Fuel wood density (166.67~kg/m$^3$ **** Caleb: verify this number and source ****) was calculated from **** and ****, both obtained from the \citet{FAO:2013c}.
 
@@
 The food-to-work efficiency for workers ($\eta_{food \rightarrow work, workers}$ = 0.2) was taken from \citet[Table~B.1]{Ayres:2010ug}.
-Following \citet[p.~315]{Ayres:2010ug}, an additional factor ($f_{enduse/intake}$) was included to account for workers' food energy that sustains the body's normal function as opposed to providing energy for physical labor \citep{Wirsenius:2000vi} **** Caleb needs to find a detailed source (table, equation, number, page number) in Wirsenius for this approach *****.
+Following \citet[p.~315]{Ayres:2010ug}, an additional factor ($f_{enduse/intake}$) was included to account for workers' food energy that sustains the body's normal function as opposed to providing energy for physical labor \citep{Wirsenius:2000vi} **** Caleb needs to find a detailed source (table, equation, number, page number) in Wirsenius for this approach ****.
 $f_{enduse/intake}$ varies by country (Table \ref{tab:f_enduse_intake}).
@@
 Factors of production track each other closely, and high covariances among these variables can be seen in Tables \ref{tab:Covariance_US} through \ref{tab:Covariance_ZM}.
-**************** Discuss the covariances in more detail after we finalize the covariances for U.
-*******************
+**** Discuss the covariances in more detail after we finalize the covariances for U.
+****
 
@@
 By constraining $\alpha \in [0,1]$, we ensure that $\beta \in [0,1]$ also.
-****** Is this truly how we implemented the constraints?
+**** Is this truly how we implemented the constraints?
 Finish after we actually implement the constraints.
-*********** $\lambda$ and $\alpha$ were estimated by the \citet{R} function \texttt{nls}.
+**** $\lambda$ and $\alpha$ were estimated by the \citet{R} function \texttt{nls}.
 The value of $\beta$ can be found with $\beta = 1 - \alpha$.
@@
 
-******** Fix the right y axis label. SSE should be italicized. Also, scaling on the axis labels and scales is not being picked up. *************
+**** Fix the right y axis label. SSE should be italicized. Also, scaling on the axis labels and scales is not being picked up. ****
 
@@
 The \texttt{R} \citep{R} package \texttt{micEconCES} \citep{Henningsen:2011td} was used to estimate parameters $\gamma$, $\lambda$, $\delta_1$, $\rho_1$, $\delta$, and $\rho$.
-********* More details here about which algorithms were used, etc.
+**** More details here about which algorithms were used, etc.
 Complete after our work this summer.
-******* Elasticities of substitution $\sigma_1$ and $\sigma$ (see Section \ref{sec:CES}) were estimated by the delta method (****** is this correct?
+**** Elasticities of substitution $\sigma_1$ and $\sigma$ (see Section \ref{sec:CES}) were estimated by the delta method (**** is this correct?
 Ask Pruim.
-******).
+****).
 
@@
 
-*********** Martin: Need additional interpretation here. *******************
+**** Martin: Need additional interpretation here. ****
 
@@
 
-****** This section needs to be re-evaluated after the statistical work is tightened up during Summer 2013. ******
+**** This section needs to be re-evaluated after the statistical work is tightened up during Summer 2013. ****
 
@@
 This evidence indicates that the LINEX production function (with energy ($e$) as its only factor of production) is a reasonable replacement the Cobb-Douglas and CES production functions which have capital stock ($k$) and labor ($l$) as factors of production.}
-  \item{****** Discuss the AIC values for each of the model types.
+  \item{**** Discuss the AIC values for each of the model types.
 It could happen that the LINEX models have a higher AIC value than the CD or CES models.
@@
 
-************* Martin needs to flesh out the above section. **************
+**** Martin needs to flesh out the above section. ****
 
@@
 
-****************** Edit conclusion after we finish the statistical studies. *********************
+**** Edit conclusion after we finish the statistical studies. ****
 
@@
 Funding for Caleb Reese and Lucas Timmer was provided by the Jack and Lois Kuipers Applied Mathematics Endowment and the Calvin College Alumni Association.
-Support for Matthew Kuperus Heun was provided by a Calvin College Research Followship.
+Partial support for Matthew Kuperus Heun was provided by a Calvin College Research Followship.
 Partial funding for Martin de Wit was provided by the South African National Research Foundation (NRF).\footnote{Any opinion, findings, and conclusions or recommendations expressed herein are those of the authors, and, therefore, NRF does not accept any liability in regard thereto.} The authors are grateful to Benjamin S.
@@
 \begin{itemize}
-  \item{1980-2011 for covariances among $y$, $k$, $l$, $q$, and $x$ for developed economies;}
+  \item{1980-2011 for covariances among $y$, $k$, $l$, $q$, and $x$ for\\*developed economies;}
   \item{1980-2000 for covariances involving $u$ for developed economies; and}
-  \item{1991-2011 for covariances among $y$, $k$, $l$, $q$, and $x$ for developing economies.}
+  \item{1991-2011 for covariances among $y$, $k$, $l$, $q$, and $x$ for\\*developing economies.}
 \end{itemize}
@@
 
-****** This subsection should be either (a) deleted or (b) moved into the main body of the paper.
+**** This subsection should be either (a) deleted or (b) moved into the main body of the paper.
 I would prefer to delete it on the grounds that single-factor models are not often used in the literature.
@@
 --Matt.
-********
+****
 
@@
 
-****** This section should be either (a) deleted or (b) moved into the main body of the paper.
+**** This section should be either (a) deleted or (b) moved into the main body of the paper.
 I would prefer to delete it on the grounds that single-factor models are not often used in the literature.

### 2013-05-24 EconGrowth.Rnw
Improved spacing in a bullet list.

@@
 \begin{itemize}
-  \item{1980-2011 for covariances among $y$, $k$, $l$, $q$, and $x$ for\\*developed economies;}
+  \item{1980-2011 for covariances among $y$, $k$, $l$, $q$, and $x$ for developed\\*economies;}
   \item{1980-2000 for covariances involving $u$ for developed economies; and}
-  \item{1991-2011 for covariances among $y$, $k$, $l$, $q$, and $x$ for\\*developing economies.}
+  \item{1991-2011 for covariances among $y$, $k$, $l$, $q$, and $x$ for developing\\*economies.}
 \end{itemize}

### 2013-05-24 EconGrowth.Rnw
Fixed the f enduse-to-intake information. Changed to f_intake/wholesale.

@@
 \noindent where $C_{fuel}$ is the consumption rate of the fuel (in units of short tons/year for coal, barrels/year for oil and petroleum, ft$^3$/year for dry natural gas and natural gas plant liquids, and m$^3$/year for biomass/fuel wood) and $h_{{fuel}}$ is the heat content of the fuel (in kJ/short ton for coal, kJ/barrel for oil, kJ/ft$^3$ for dry natural gas and natural gas plant liquids, and kJ/kg for biomass/fuel wood).
-Fuel wood density (166.67~kg/m$^3$ **** Caleb: verify this number and source ****) was calculated from **** and ****, both obtained from the \citet{FAO:2013c}.
+Fuel wood density of 300~kg/m$^3$ was taken from \citet{Ragland:2013wp} at the low end of the range of density of dry wood and bark.
 
@@
 
-\noindent where the value of $Q_{m,workers}$ for the U.S.
-($\sim$ 4200 kcal/day-worker) was taken from a time series of kcal/day-person for workers for 1980--2011 \citep{Warr:2012a}.
-$Q_{m,workers}$ for other countries was taken from the \citet[``\texttt{Dietary Energy Cons.~Countries}'' tab]{FAO:2013b}.
-The value for $N_{workers}$ was obtained from the labor time series for each economy as discussed in Section \ref{sec:Labor_Data}.
+\noindent where the value of $Q_{m,workers}$ is the ``the amount of food available for human consumption'' (i.e., at the wholesale level) taken from the \citet[``\texttt{Dietary~Energy~Cons.~Countries}'' tab]{FAO:2013b}.
+The value for $N_{workers}$ was obtained from the labor time series for each economy as discussed in Section~\ref{sec:Labor_Data}.
 
@@
 The food-to-work efficiency for workers ($\eta_{food \rightarrow work, workers}$ = 0.2) was taken from \citet[Table~B.1]{Ayres:2010ug}.
-Following \citet[p.~315]{Ayres:2010ug}, an additional factor ($f_{enduse/intake}$) was included to account for workers' food energy that sustains the body's normal function as opposed to providing energy for physical labor \citep{Wirsenius:2000vi} **** Caleb needs to find a detailed source (table, equation, number, page number) in Wirsenius for this approach ****.
-$f_{enduse/intake}$ varies by country (Table \ref{tab:f_enduse_intake}).
-A similar enduse-to-intake ratio could also be applied to animal work, but it was unavailable from \citet{Wirsenius:2000vi}.\footnote{The error in exergy caused by neglecting $f_{enduse/intake}$ for animals is very small, because animal muscle exergy is a small fraction of the total energy supply to any economy, with a maximum of 0.41\% for China in 1992.}
-
-\begin{table} \caption{Food enduse-to-intake ratios ($f_{enduse/intake}$) for all countries.} \label{tab:f_enduse_intake}
+Following \citet[p.~315]{Ayres:2010ug} and methodology from \citet{Warr:2012a}, an additional factor ($f_{intake/wholesale}$) was included to account for ``wastage and losses of food in the household, e.g.
+during storage, in preparation and cooking, as plate-waste, or quantities fed to domestic animals and pets'' \citep{FAO:2013b}.
+Values of $f_{intake/wholesale}$ were calculated from \citet[Table~3.3 for wholesale and Table~3.4 for intake]{Wirsenius:2000vi}.
+$f_{intake/wholesale}$ varies by country (Table \ref{tab:f_intake_wholesale}).
+A similar intake-to-wholesale ratio could also be applied to animal work, but data to calculate the ratio was unavailable from \citet{Wirsenius:2000vi}.\footnote{The error in exergy caused by neglecting $f_{intake/wholesale}$ for animals is very small, because animal muscle exergy is a small fraction of the total energy supply to any economy, with a maximum of 0.41\% for China in 1992.
+It could be argued that $f_{intake/wholesale}$ for animals is likely to be closer to 1.0 than $f_{intake/wholesale}$ for humans.}
+
+\begin{table} \caption{Food intake-to-wholesale ratios ($f_{intake/wholesale}$) for all countries.} \label{tab:f_intake_wholesale}
   \begin{center}

### 2013-05-24 EconGrowth.Rnw
More changes related to f_enduse/intake moving to f_intake/wholesale.

@@
 
-To calculate the exergy of animal and human muscle power, the food-to-work conversion efficiency ($\eta_{food \rightarrow work}$) and the ratio of food enduse to food intake ($f_{enduse/intake}$) were included.
+To calculate the exergy of animal and human muscle power, the food-to-work conversion efficiency ($\eta_{food \rightarrow work}$) and the ratio of food intake to food available at wholesale ($f_{intake/wholesale}$) were included.
 
@@
 \begin{equation} \label{eq:human_muscle_exergy}
-  X_{workers} = \eta_{food \rightarrow work,workers} f_{enduse/intake} Q_{workers}
+  X_{workers} = \eta_{food \rightarrow work,workers} f_{intake/wholesale} Q_{workers}
 \end{equation}
@@
       \hline
-      $f_{enduse/intake}$ & 0.62 & 0.65 & 0.76 & 0.76 & 0.87 & 0.72 & 0.72 & 0.72 & 0.72\\
+      $f_{intake/wholesale}$ & 0.62 & 0.65 & 0.76 & 0.76 & 0.87 & 0.72 & 0.72 & 0.72 & 0.72\\
     \end{tabular}

### 2013-05-24 EconGrowth.Rnw
Added nonbreaking spaces between Equation, Figure, Table, Section and the \ref{} reference.

@@
 One exception is the technolgical progress term $A$, which is dimensionless but written in upper-case by convention.} Neoclassical economic growth theory as expressed in the Cobb-Douglas production function makes no attempt to describe the mechanisms by which technological progress ($A$) affects economic growth, nor does it attempt to describe how technological progress ($A$) might vary from one economy to the next.
-Mathematically, $A$ is a fitting parameter that aligns the predictions of Equation \ref{eq:CD} with historical data.
+Mathematically, $A$ is a fitting parameter that aligns the predictions of Equation~\ref{eq:CD} with historical data.
 Typically, the constraint $\alpha + \beta = 1$ is assumed, indicating constant returns to scale.
 
-As shown in Equation \ref{eq:CD} above, neoclassical economic theory does not include an explicit term for the role of energy in economic growth.
+As shown in Equation~\ref{eq:CD} above, neoclassical economic theory does not include an explicit term for the role of energy in economic growth.
 However, \citet{Bashmakov:2007ek}, \citet{Hamilton:2009ui}, \citet{Murphy:2011jh}, \citet{Benes:2012tm}, \citet{Kumhof:2012ua}, and others indicate that the importance of energy for economic growth may far outweigh its cost share in the economy.
@@
 The remainder of this paper is organized as follows.
-Section \ref{sec:Coordinates} discusses the coordinates of analysis described above.
-Section \ref{sec:Sources_of_Data} details sources of data and calculations to generate time series for economic output and factors of production.
-The procedures for and results from parameter estimation for the various production functions are discussed in Section \ref{sec:Parameter_Estimation}.
-Section \ref{sec:Implications} discusses implications of the parameter estimation results, and Section \ref{sec:Conclusion} concludes.
+Section~\ref{sec:Coordinates} discusses the coordinates of analysis described above.
+Section~\ref{sec:Sources_of_Data} details sources of data and calculations to generate time series for economic output and factors of production.
+The procedures for and results from parameter estimation for the various production functions are discussed in Section~\ref{sec:Parameter_Estimation}.
+Section~\ref{sec:Implications} discusses implications of the parameter estimation results, and Section~\ref{sec:Conclusion} concludes.
 An appendix provides details of all statistical results.
@@
 
-Similar to Equation \ref{eq:CD}, the energy-augmented Cobb-Douglas production function is
+Similar to Equation~\ref{eq:CD}, the energy-augmented Cobb-Douglas production function is
 
@@
 
-\citet{Ayres:2008cl} uses Equation \ref{eq:CDe} with exergy ($x$) and useful work ($u$) quantifications for $e$ to describe historic Japanese and American economies from 1900-2000.
+\citet{Ayres:2008cl} uses Equation~\ref{eq:CDe} with exergy ($x$) and useful work ($u$) quantifications for $e$ to describe historic Japanese and American economies from 1900-2000.
 \citet{Froling:2009vo} uses an energy-augmented Cobb-Douglas production function with thermal energy quantification ($q$) to describe output for the global economy from 1800-1970.
@@
 
-\noindent Equation \ref{eq:CES} is a CES production function with capital stock ($k$) and labor ($l$) factors of production.
-Equation \ref{eq:CESe} augments Equation \ref{eq:CES} with energy using a ($kl$)($e$) nesting structure, as is typical in the literature.
-Equation \ref{eq:CES} is a degenerate form of Equation \ref{eq:CESe} where $\delta = 1$.
+\noindent Equation~\ref{eq:CES} is a CES production function with capital stock ($k$) and labor ($l$) factors of production.
+Equation~\ref{eq:CESe} augments Equation~\ref{eq:CES} with energy using a ($kl$)($e$) nesting structure, as is typical in the literature.
+Equation~\ref{eq:CES} is a degenerate form of Equation~\ref{eq:CESe} where $\delta = 1$.
 The elasticity of substitution between capital ($k$) and labor ($l$) is given by $\sigma_1 = \frac{1}{1+\rho_1}$, the elasticity of substitution between ($kl$) and ($e$) is given by $\sigma = \frac{1}{1+\rho}$, $\delta \in [0, 1]$ describes the importance of ($kl$) relative to ($e$), and $\gamma$ is a fitting parameter, expected to be close to unity.
@@
 
-In contrast to both the Cobb-Douglas model (Equations \ref{eq:CD} and \ref{eq:CDe}) and the CES model (Equations \ref{eq:CES} and \ref{eq:CESe}), the LINEX model (Equation \ref{eq:LINEX}) accounts for efficiencies among capital, labor, and energy directly and, therefore, does not employ a time-dependent technological progress term ($A$).
+In contrast to both the Cobb-Douglas model (Equations~\ref{eq:CD} and \ref{eq:CDe}) and the CES model (Equations~\ref{eq:CES} and \ref{eq:CESe}), the LINEX model (Equation~\ref{eq:LINEX}) accounts for efficiencies among capital, labor, and energy directly and, therefore, does not employ a time-dependent technological progress term ($A$).
 \citet{Kummel:2002tx} use the LINEX production function to describe economic output for the economies of the U.S., Japan, and Germany.
@@
 
-We know of no statistically-rigorous comparisons of the predictive ability of each energy quantification in the various types of production functions discussed in Section \ref{sec:Prod_Func_Forms}.
+We know of no statistically-rigorous comparisons of the predictive ability of each energy quantification in the various types of production functions discussed in Section~\ref{sec:Prod_Func_Forms}.
 We analyze all three quantifications of energy ($Q$, $X$, and $U$) for developed economies and thermal energy ($Q$) and exergy ($X$) for all other economies.
@@
 ****).
-(See Table \ref{tab:Economy_Examples}.)
+(See Table~\ref{tab:Economy_Examples}.)
 
@@
 
-To assess energy-augmented models of economic growth along the coordinates of analysis outlined in Section \ref{sec:Coordinates}, historical data for economic output ($Y$), capital stock ($K$), labor ($L$), thermal energy ($Q$), exergy ($X$), and useful work ($U$) are required.
+To assess energy-augmented models of economic growth along the coordinates of analysis outlined in Section~\ref{sec:Coordinates}, historical data for economic output ($Y$), capital stock ($K$), labor ($L$), thermal energy ($Q$), exergy ($X$), and useful work ($U$) are required.
 Subsections below describe sources for and calculations to obtain historical data.
@@
 In the style of work by Warr and Ayres \citep{Ayres:2003ec, Ayres:2005kn, Warr:2010ht, Warr:2010ga, Warr:2012cg}, energy from human and animal muscle power was also included.
-Similar to the economic data discussed in Sections \ref{sec:Economic_Output_Data}--\ref{sec:Labor_Data}, we generated energy data for developed countries from 1980--2011, with the exception of useful work data (1980--2000).
+Similar to the economic data discussed in Sections~\ref{sec:Economic_Output_Data}--\ref{sec:Labor_Data}, we generated energy data for developed countries from 1980--2011, with the exception of useful work data (1980--2000).
 For all other countries, we generated thermal energy and exergy data for 1991--2011.
@@
 
-For renewable and nuclear energy sources, yearly electricity generation (in BTU/year) was available directly from the \citet{EIA:2013a} for all economies, so Equation \ref{eq:thermal_energy} was unnecessary.
+For renewable and nuclear energy sources, yearly electricity generation (in BTU/year) was available directly from the \citet{EIA:2013a} for all economies, so Equation~\ref{eq:thermal_energy} was unnecessary.
 
@@
 
-Exergy ($X$), expressed in TJ/year, was calculated by multiplying the thermal energy ($Q$) values discussed in Section \ref{sec:Q_Data} by a unitless exergy-to-thermal-energy allocation factor ($f_{exergy-allocation}$) shown in Table \ref{tab:Exergy_Allocation}.
+Exergy ($X$), expressed in TJ/year, was calculated by multiplying the thermal energy ($Q$) values discussed in Section~\ref{sec:Q_Data} by a unitless exergy-to-thermal-energy allocation factor ($f_{exergy-allocation}$) shown in Table~\ref{tab:Exergy_Allocation}.
 
@@
 Following \citet[p.~315]{Ayres:2010ug} and methodology from \citet{Warr:2012a}, an additional factor ($f_{intake/wholesale}$) was included to account for ``wastage and losses of food in the household, e.g.
-during storage, in preparation and cooking, as plate-waste, or quantities fed to domestic animals and pets'' \citep{FAO:2013b}.
+during storage, in preparation and cooking, as plate-waste, or quantities fed to domestic animals and pets'' \citep[\texttt{notes} tab]{FAO:2013b}.
 Values of $f_{intake/wholesale}$ were calculated from \citet[Table~3.3 for wholesale and Table~3.4 for intake]{Wirsenius:2000vi}.
-$f_{intake/wholesale}$ varies by country (Table \ref{tab:f_intake_wholesale}).
-A similar intake-to-wholesale ratio could also be applied to animal work, but data to calculate the ratio was unavailable from \citet{Wirsenius:2000vi}.\footnote{The error in exergy caused by neglecting $f_{intake/wholesale}$ for animals is very small, because animal muscle exergy is a small fraction of the total energy supply to any economy, with a maximum of 0.41\% for China in 1992.
-It could be argued that $f_{intake/wholesale}$ for animals is likely to be closer to 1.0 than $f_{intake/wholesale}$ for humans.}
+$f_{intake/wholesale}$ varies by country as shown in Table~\ref{tab:f_intake_wholesale}.
+A similar intake-to-wholesale ratio could also be applied to animal work, but data to calculate the ratio was unavailable from \citet{Wirsenius:2000vi}, and $f_{intake/wholesale,animals}$ is assumed to be unity.\footnote{The error in total exergy input to any economy caused by assuming $f_{intake/wholesale,animals} = 1.0$ is very small, because animal muscle exergy is a small fraction of the total exergy supply to any economy, with a maximum of 0.41\% for China in 1992.
+It could also be argued that $f_{intake/wholesale, animals}$ is likely to be closer to unity than $f_{intake/wholesale, workers}$.}
 
@@
 
-\noindent where the subscript $i$ indicates the energy enduse, $\varepsilon_i$ is the efficiency of converting exergy into useful energy for each enduse, and $\phi_i$ gives the fraction of exergy input to an economy that goes toward the i$^\mathrm{th}$ enduse.
+\noindent where the subscript $i$ indicates the energy enduse, $\varepsilon_i$ is the efficiency of converting exergy into useful energy for each enduse, and $\phi_i$ gives the fraction of exergy input to an economy that goes toward the $i^\mathrm{th}$ enduse.
 
 Values of $\varepsilon_i$ and $\phi_i$ were calculated from the REXS database supplied by \citet{Warr:2012a}.
-Values of $X$ were calculated by methods discussed in Section \ref{sec:X_Data}.
+Values of $X$ were calculated by methods discussed in Section~\ref{sec:X_Data}.
 For most countries, values of $\phi_i$ are not constant with time, as economic sectors with different distributions of raw exergy inputs grow at different rates.
@@
 
-Figure \ref{fig:Historical_Lattice_Graph} presents historical data, including indexed values for output ($y$), capital stock ($k$), labor ($l$), and the various energy quantifications ($q$, $x$, and $u$) for 1980--2011 (developed economies) and 1991--2011 (other economies).
-Factors of production track each other closely, and high covariances among these variables can be seen in Tables \ref{tab:Covariance_US} through \ref{tab:Covariance_ZM}.
+Figure~\ref{fig:Historical_Lattice_Graph} presents historical data, including indexed values for output ($y$), capital stock ($k$), labor ($l$), and the various energy quantifications ($q$, $x$, and $u$) for 1980--2011 (developed economies) and 1991--2011 (other economies).
+Factors of production track each other closely, and high covariances among these variables can be seen in Tables~\ref{tab:Covariance_US}--\ref{tab:Covariance_ZM}.
 **** Discuss the covariances in more detail after we finalize the covariances for U.
@@
 
-Figure \ref{fig:Historical_Lattice_Graph} indicates the importance of energy quantification for economic growth modeling.
+Figure~\ref{fig:Historical_Lattice_Graph} indicates the importance of energy quantification for economic growth modeling.
 Thermal energy ($q$) and exergy ($x$) grow at similar rates, unless there is a significant raw energy carrier substitution in the economy (such as China's rapid increase of coal and natural gas consumption relative to petroleum since 2000).
@@
 economy.
-The results of \citeauthor{Warr:2012cg} suggest that the time-dependent technological progress term ($A$) in the Cobb-Douglas and CES production functions (Equations \ref{eq:CD} -- \ref{eq:CESe}) may be a proxy for increasing energy efficiency in the U.S.
+The results of \citeauthor{Warr:2012cg} suggest that the time-dependent technological progress term ($A$) in the Cobb-Douglas and CES production functions (Equations~\ref{eq:CD}--\ref{eq:CESe}) may be a proxy for increasing energy efficiency in the U.S.
 economy.
@@
 
-Each of the economic growth models discussed in Section \ref{sec:Prod_Func_Forms} has parameters which must be estimated for each economy (see Section \ref{sec:Economy_Types}) and each energy quantification (see Section \ref{sec:Quantification_of_Energy}) via least-squares methods.
+Each of the economic growth models discussed in Section~\ref{sec:Prod_Func_Forms} has parameters which must be estimated for each economy (see Section~\ref{sec:Economy_Types}) and each energy quantification (see Section~\ref{sec:Quantification_of_Energy}) via least-squares methods.
 The following subsections discuss parameter estimation methods interpret the results.
@@
 
-The Cobb-Douglas model without energy is given by Equation \ref{eq:CD}. The Cobb-Douglas production function was reparameterized as
+The Cobb-Douglas model without energy is given by Equation~\ref{eq:CD}. The Cobb-Douglas production function was reparameterized as
 
@@
 The value of $\beta$ can be found with $\beta = 1 - \alpha$.
-Figure \ref{fig:CD_Params_Graph} shows values of and 95\% confidence intervals for $\lambda$ and $\alpha$.
-Appendix \ref{sec:Model_Parameters} contains tables with numerical values of model parameters and confidence intervals.
+Figure~\ref{fig:CD_Params_Graph} shows values of and 95\% confidence intervals for $\lambda$ and $\alpha$.
+Appendix~\ref{sec:Model_Parameters} contains tables with numerical values of model parameters and confidence intervals.
 
@@
 
-To qualitatively assess whether augmenting the Cobb-Douglas model with energy will be beneficial, we created partial residual plots as shown in Figures \ref{fig:CDPartialResidualsQ}--\ref{fig:CDPartialResidualsU} below.
+To qualitatively assess whether augmenting the Cobb-Douglas model with energy will be beneficial, we created partial residual plots as shown in Figures~\ref{fig:CDPartialResidualsQ}--\ref{fig:CDPartialResidualsU} below.
 If a monotonic trend is observed on the graphs, we expect that energy augmentation will be beneficial.
@@
 
-To estimate the parameters $\lambda$, $\alpha$, $\beta$, and $\gamma$ in the energy-augmented Cobb-Douglas model, Equation \ref{eq:CDe} was reparameterized as
+To estimate the parameters $\lambda$, $\alpha$, $\beta$, and $\gamma$ in the energy-augmented Cobb-Douglas model, Equation~\ref{eq:CDe} was reparameterized as
 
@@
 To demonstrate the characteristics of the parameter estimation process, we performed a grid search over values of $\gamma$, wherein we re-estimated values of $\lambda$, $\alpha$, and $\beta$ at each value of $\gamma$.
-Figure \ref{fig:CDeGridLattice} shows the sum of squared errors ($SSE$), $\alpha$, and $\beta$ as a function of the fixed value of $\gamma$ with thermal energy ($q$).
+Figure~\ref{fig:CDeGridLattice} shows the sum of squared errors ($SSE$), $\alpha$, and $\beta$ as a function of the fixed value of $\gamma$ with thermal energy ($q$).
 For most economies, the minimum $SSE$ occurs at a boundary of $\alpha$, $\beta$, or $\gamma$.
@@
 
-Figure \ref{fig:CDq_Params_Graph} shows values and 95\% confidence intervals for the parameters for the Cobb-Douglas model (with $q$).
+Figure~\ref{fig:CDq_Params_Graph} shows values and 95\% confidence intervals for the parameters for the Cobb-Douglas model (with $q$).
 
@@
 
-The Cobb-Douglas (with exergy) parameters are given in Table \ref{tab:CD_Parameters_With_X}.
-
-Figure \ref{fig:CDx_Params_Graph} shows values and 95\% confidence intervals for the parameters for the Cobb-Douglas model (with $x$).
+The Cobb-Douglas (with exergy) parameters are given in Table~\ref{tab:CD_Parameters_With_X}.
+
+Figure~\ref{fig:CDx_Params_Graph} shows values and 95\% confidence intervals for the parameters for the Cobb-Douglas model (with $x$).
 
@@
 
-Figure \ref{fig:CDu_Params_Graph} shows values and 95\% confidence intervals for the parameters for the Cobb-Douglas model (with $u$).
+Figure~\ref{fig:CDu_Params_Graph} shows values and 95\% confidence intervals for the parameters for the Cobb-Douglas model (with $u$).
 
@@
 
-Figure \ref{fig:CD_GDP_Lattice_Graph} compares predictions from the Cobb-Douglas models (without energy, with $e=q$, with $e=x$, and with $e=u$) to historical data.
+Figure~\ref{fig:CD_GDP_Lattice_Graph} compares predictions from the Cobb-Douglas models (without energy, with $e=q$, with $e=x$, and with $e=u$) to historical data.
 
@@
 
-The CES model without and with energy is given by Equations \ref{eq:CES} and \ref{eq:CESe}, respectively.
+The CES model without and with energy is given by Equations~\ref{eq:CES} and \ref{eq:CESe}, respectively.
 The \texttt{R} \citep{R} package \texttt{micEconCES} \citep{Henningsen:2011td} was used to estimate parameters $\gamma$, $\lambda$, $\delta_1$, $\rho_1$, $\delta$, and $\rho$.
@@
 Complete after our work this summer.
-**** Elasticities of substitution $\sigma_1$ and $\sigma$ (see Section \ref{sec:CES}) were estimated by the delta method (**** is this correct?
+**** Elasticities of substitution $\sigma_1$ and $\sigma$ (see Section~\ref{sec:CES}) were estimated by the delta method (**** is this correct?
 Ask Pruim.
@@
 
-Figure \ref{fig:CES_Params_Graph} shows values and 95\% confidence intervals for the parameters for the CES model (without energy).
+Figure~\ref{fig:CES_Params_Graph} shows values and 95\% confidence intervals for the parameters for the CES model (without energy).
 
@@
 
-Similar to the analysis of the Cobb-Douglas model in Section \ref{sec:CD_Parameter_Estimation}, we make partial residual plots for the CES model (without energy) in Figures \ref{fig:CESPartialResidualsQ} - \ref{fig:CESPartialResidualsU} below.
+Similar to the analysis of the Cobb-Douglas model in Section~\ref{sec:CD_Parameter_Estimation}, we make partial residual plots for the CES model (without energy) in Figures~\ref{fig:CESPartialResidualsQ}--\ref{fig:CESPartialResidualsU} below.
 Again, no strong monotonic trend is observed, suggesting the energy-augmentation of the CES model will not significantly improve the model.
@@
 
-Figure \ref{fig:CESq_Params_Graph} shows values and 95\% confidence intervals for the parameters for the CES model (with $q$).
+Figure~\ref{fig:CESq_Params_Graph} shows values and 95\% confidence intervals for the parameters for the CES model (with $q$).
 
@@
 
-Figure \ref{fig:CESx_Params_Graph} shows values and 95\% confidence intervals for the parameters for the CES model (with $x$).
+Figure~\ref{fig:CESx_Params_Graph} shows values and 95\% confidence intervals for the parameters for the CES model (with $x$).
 
@@
 
-Figure \ref{fig:CESu_Params_Graph} shows values and 95\% confidence intervals for the parameters for the CES model (with $u$).
+Figure~\ref{fig:CESu_Params_Graph} shows values and 95\% confidence intervals for the parameters for the CES model (with $u$).
 
@@
 
-Figure \ref{fig:CES_GDP_Lattice_Graph} compares CES model predictions to historical data.
+Figure~\ref{fig:CES_GDP_Lattice_Graph} compares CES model predictions to historical data.
 
@@
 The key energy parameters for the Cobb-Douglas and CES models are $\gamma$, $\delta$, and $\sigma$.
-The parameter $\gamma$ in the Cobb-Douglas model (Equation \ref{eq:CDe}) indicates the importance of energy for economic growth.
+The parameter $\gamma$ in the Cobb-Douglas model (Equation~\ref{eq:CDe}) indicates the importance of energy for economic growth.
 When $\gamma \rightarrow 0$, energy is not a significant contributor to economic growth for an economy.
@@
 On a graph of the width of the 95\% confidence interval for $\gamma$ ($CI_{95\%,\gamma}$) vs.
-$\gamma$, where each economy is represented by a point (its two-letter abbreviation; see Table \ref{tab:Economy_Examples}), the locus of points where the 95\% confidence interval for $\gamma$ crosses 0 is a diagonal line.
+$\gamma$, where each economy is represented by a point (its two-letter abbreviation; see Table~\ref{tab:Economy_Examples}), the locus of points where the 95\% confidence interval for $\gamma$ crosses 0 is a diagonal line.
 If the combination of $\gamma$ and its confidence interval for a given economy is below and to the right of the line, we have high confidence that we can say whether or not energy is a significant contributor to economic growth.
@@
 
-The left column of graphs in Figure \ref{fig:CIvsParam_Lattice_Graph} shows $CI_{95\%,\gamma}$ vs.
+The left column of graphs in Figure~\ref{fig:CIvsParam_Lattice_Graph} shows $CI_{95\%,\gamma}$ vs.
 $\gamma$ for the three quantifications of energy (thermal energy, $q$, exergy, $x$, and useful work, $u$).
@@
 
-For the CES model (Equation \ref{eq:CESe}), the parameter $\delta$ indicates the importance of energy for economic growth.
+For the CES model (Equation~\ref{eq:CESe}), the parameter $\delta$ indicates the importance of energy for economic growth.
 When $\delta \rightarrow 1$, energy is an insignificant contributor to economic growth, and when $\delta \rightarrow 0$, energy is the primary contributor to economic growth for an economy.
@@
 
-The middle column of graphs in Figure \ref{fig:CIvsParam_Lattice_Graph} shows $CI_{95\%,\delta}$ vs.
+The middle column of graphs in Figure~\ref{fig:CIvsParam_Lattice_Graph} shows $CI_{95\%,\delta}$ vs.
 $\delta$ for the three quantifications of energy (thermal energy, $q$, exergy, $x$, and useful work, $u$).
@@
 
-For the CES model (Equation \ref{eq:CESe}), the parameter $\sigma$ indicates whether capital stock and labor ($kl$) and energy ($e$) are complements ($\sigma <$ 1) or substitutes ($\sigma >$ 1).
-For countries whose combination of  $\sigma$ and its confidence interval is below and to the left of the lines in the rightmost graphs of Figure \ref{fig:CIvsParam_Lattice_Graph} we can say (with 95\% confidence) that ($kl$) and ($e$) are complements.
+For the CES model (Equation~\ref{eq:CESe}), the parameter $\sigma$ indicates whether capital stock and labor ($kl$) and energy ($e$) are complements ($\sigma <$ 1) or substitutes ($\sigma >$ 1).
+For countries whose combination of  $\sigma$ and its confidence interval is below and to the left of the lines in the rightmost graphs of Figure~\ref{fig:CIvsParam_Lattice_Graph} we can say (with 95\% confidence) that ($kl$) and ($e$) are complements.
 For economies whose value of $\sigma$ is below and to the right of the line, we can say (with 95\% confidence) that ($kl$) and ($e$) are substitutes.
@@
 
-The right column of graphs in Figure \ref{fig:CIvsParam_Lattice_Graph} shows $CI_{95\%,\sigma}$ vs.
+The right column of graphs in Figure~\ref{fig:CIvsParam_Lattice_Graph} shows $CI_{95\%,\sigma}$ vs.
 $\sigma$ for the three quantifications of energy (thermal energy, $q$, exergy, $x$, and useful work, $u$).
@@
 
-The LINEX model is given in Equation \ref{eq:LINEX}.
+The LINEX model is given in Equation~\ref{eq:LINEX}.
 Parameters $a_0$ and $c_t$ were estimated using the \texttt{nls} function in \texttt{R} \citep{R}.
-Figure \ref{fig:LINEXq_Params_Graph} shows values and 95\% confidence intervals for the parameters for the LINEX model (with $q$).
+Figure~\ref{fig:LINEXq_Params_Graph} shows values and 95\% confidence intervals for the parameters for the LINEX model (with $q$).
 
@@
 
-Figure \ref{fig:LINEXx_Params_Graph} shows values and 95\% confidence intervals for the parameters for the LINEX model (with $x$).
+Figure~\ref{fig:LINEXx_Params_Graph} shows values and 95\% confidence intervals for the parameters for the LINEX model (with $x$).
 
@@
 
-Figure \ref{fig:LINEXu_Params_Graph} shows values and 95\% confidence intervals for the parameters for the LINEX model (with $u$).
+Figure~\ref{fig:LINEXu_Params_Graph} shows values and 95\% confidence intervals for the parameters for the LINEX model (with $u$).
 
@@
 
-Figure \ref{fig:LINEX_GDP_Lattice_Graph} compares LINEX model predictions to historical data.
+Figure~\ref{fig:LINEX_GDP_Lattice_Graph} compares LINEX model predictions to historical data.
 
@@
   \item{The use of chemical exergy, as opposed to thermal energy, in economic growth models is probably unnecessary.
-Table \ref{tab:Exergy_Allocation} shows that exergy allocation factors are all close to unity.
+Table~\ref{tab:Exergy_Allocation} shows that exergy allocation factors are all close to unity.
 Therefore, there is a small difference in absolute magnitude between $Q$ and $X$.
 However, there is no difference in indexed magnitude between $q$ and $x$, unless there are large changes in energy mix for an economy.
-Figure \ref{fig:Historical_Lattice_Graph} shows that $q$ and $x$ lines lie atop one another for almost every economy.}
+Figure~\ref{fig:Historical_Lattice_Graph} shows that $q$ and $x$ lines lie atop one another for almost every economy.}
   \item{The concept of useful work ($u$) is potentially useful and should be explored beyond developed economies.
-Figure \ref{fig:Historical_Lattice_Graph} shows that $u$ grows at very different rates from thermal energy ($q$) or exergy ($x$).
+Figure~\ref{fig:Historical_Lattice_Graph} shows that $u$ grows at very different rates from thermal energy ($q$) or exergy ($x$).
 Useful work may contain different information from thermal energy and exergy.}
-  \item{Figure \ref{fig:CDeGridLattice} shows that the set of parameters ($\lambda$, $\alpha$, $\beta$, and $\gamma$) that minimizes $SSE$ for the energy-augmented Cobb-Douglas production function always (with the exception of Saudi Arabia) has $\beta = 0$ or $\gamma = 0$.
+  \item{Figure~\ref{fig:CDeGridLattice} shows that the set of parameters ($\lambda$, $\alpha$, $\beta$, and $\gamma$) that minimizes $SSE$ for the energy-augmented Cobb-Douglas production function always (with the exception of Saudi Arabia) has $\beta = 0$ or $\gamma = 0$.
 This result implies that it is unnecessary to include both labor ($l$) and energy ($e$) in the Cobb-Douglas production function.}
-  \item{Partial residual plots for both the Cobb-Douglas model (Figures \ref{fig:CDPartialResidualsQ}--\ref{fig:CDPartialResidualsU} and CES model (Figures \ref{fig:CESPartialResidualsQ}--\ref{fig:CESPartialResidualsU}) indicate that augmenting the Cobb-Douglas and CES production functions with energy is not beneficial.}
-  \item{Figure \ref{fig:CIvsParam_Lattice_Graph} shows that important energy parameters for both the energy-augmented Cobb-Douglas and CES production functions ($\gamma$ and $\delta$, respectively) have large confidence intervals such that we are unable to say (at the 95\% confidence level) that energy is an important factor for economic growth, vis-\`{a}-vis capital stock ($k$) or labor ($l$) for most economies.}
-  \item{Figure \ref{fig:CIvsParam_Lattice_Graph} indicates that energy (in all quantifications: $q$, $x$, and $u$) is complementary to capital stock ($k$) and labor ($l$) for producing economic growth, according to the CES model.}
-  \item{Figures \ref{fig:LINEXq_Params_Graph}--\ref{fig:LINEXu_Params_Graph} indicate that LINEX model fitting parameters $a_0$ and $c_t$ are significant (at the 95\% confidence level) for nearly all countries.
-Figure \ref{fig:LINEX_GDP_Lattice_Graph} shows that the LINEX production function provides reasonably good fits to historical data.
+  \item{Partial residual plots for both the Cobb-Douglas model (Figures~\ref{fig:CDPartialResidualsQ}--\ref{fig:CDPartialResidualsU} and CES model (Figures~\ref{fig:CESPartialResidualsQ}--\ref{fig:CESPartialResidualsU}) indicate that augmenting the Cobb-Douglas and CES production functions with energy is not beneficial.}
+  \item{Figure~\ref{fig:CIvsParam_Lattice_Graph} shows that important energy parameters for both the energy-augmented Cobb-Douglas and CES production functions ($\gamma$ and $\delta$, respectively) have large confidence intervals such that we are unable to say (at the 95\% confidence level) that energy is an important factor for economic growth, vis-\`{a}-vis capital stock ($k$) or labor ($l$) for most economies.}
+  \item{Figure~\ref{fig:CIvsParam_Lattice_Graph} indicates that energy (in all quantifications: $q$, $x$, and $u$) is complementary to capital stock ($k$) and labor ($l$) for producing economic growth, according to the CES model.}
+  \item{Figures~\ref{fig:LINEXq_Params_Graph}--\ref{fig:LINEXu_Params_Graph} indicate that LINEX model fitting parameters $a_0$ and $c_t$ are significant (at the 95\% confidence level) for nearly all countries.
+Figure~\ref{fig:LINEX_GDP_Lattice_Graph} shows that the LINEX production function provides reasonably good fits to historical data.
 This evidence indicates that the LINEX production function (with energy ($e$) as its only factor of production) is a reasonable replacement the Cobb-Douglas and CES production functions which have capital stock ($k$) and labor ($l$) as factors of production.}
@@
 We assess goodness of fit via the Akaike Information Criterion (AIC).
-AIC values for all models and all countries are shown in Table \ref{tab:AICTable}.
+AIC values for all models and all countries are shown in Table~\ref{tab:AICTable}.
 Increasing goodness of fit is indicated by smaller (i.e., more negative) AIC values.
@@
 
-Figure \ref{fig:SF_GDP_Lattice_Graph} compares single-factor model predictions with historical data.
+Figure~\ref{fig:SF_GDP_Lattice_Graph} compares single-factor model predictions with historical data.
 

### 2013-05-24 EconGrowth.Rnw
Trying to fix error where CD with X fails for TZ.

@@
 \item{Reese: Fix the energy sankey diagram from the seminar}
+\item{Heun: Fix error when calculating confidence intervals for Cobb-Douglas model for TZ with X.
+The problem occurs in function \texttt{cobbDouglasData}.
+To repeat the problem, call \texttt{cobbDouglasData(countryAbbrev="TZ", energyType="X")}}
 \item{Heun: Include Caleb's adjusted sankey diagram in the seminar}
@@
 
+<<FindError, eval=TRUE>>=
+# print(cobbDouglasCountryRow(countryAbbrev="US", energyType="X"))
+# print(cobbDouglasCountryRow(countryAbbrev="UK", energyType="X"))
+# print(cobbDouglasCountryRow(countryAbbrev="JP", energyType="X"))
+# print(cobbDouglasCountryRow(countryAbbrev="CN", energyType="X"))
+# print(cobbDouglasCountryRow(countryAbbrev="ZA", energyType="X"))
+# print(cobbDouglasCountryRow(countryAbbrev="SA", energyType="X"))
+# print(cobbDouglasCountryRow(countryAbbrev="IR", energyType="X"))
+# print(cobbDouglasCountryRow(countryAbbrev="TZ", energyType="X"))
+
+print(cobbDouglasData(countryAbbrev="TZ", energyType="X"))
+
+# print(cobbDouglasModel(countryAbbrev="TZ", energyType="X"))
+# print(cdeModel(countryAbbrev="TZ", energyType="X"))
+# print(cobbDouglasCountryRow(countryAbbrev="ZM", energyType="X"))
+@
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2013-05-28 EconGrowth.Rnw
Adding details about error in CD with X for TZ.
Removed completed items from the to-do list to shorten and simplify the paper.

@@
 \begin{itemize}
-\item{Reese: Review EIA IES database for any revisions to historical data}
-\item{Reese: Add food energy intake for all countries from FAO. We won't assume that the US caloric intake applies to all coutries.}
-\item{Reese: Fix the energy sankey diagram from the seminar}
 \item{Heun: Fix error when calculating confidence intervals for Cobb-Douglas model for TZ with X.
 The problem occurs in function \texttt{cobbDouglasData}.
-To repeat the problem, call \texttt{cobbDouglasData(countryAbbrev="TZ", energyType="X")}}
-\item{Heun: Include Caleb's adjusted sankey diagram in the seminar}
+To repeat the problem, call \texttt{cobbDouglasData(countryAbbrev="TZ", energyType="X")}.
+The code fails on the line \\* \texttt{  ciCD <- confint(object=modelCD, level=ciLevel)}.
+\\* There is code after the to-do list in this file that exposes the problem.}
+\item{Heun: Get function \texttt{cdeModel} working with constraints.
+Note that the unconstrained solutions are sometimes within the constraints.
+But, sometimes they aren't.
+All solutions need to be within constraints.
+We may need to run with warnings turned off to get this to work properly.}
+\item{Heun: Investigate possible conflicting use of exergy by Warr and Ayres.}
+\item{Heun: Fix the energy sankey diagram from the seminar}
+\item{Heun: Include adjusted sankey diagram in the seminar}
 \item{Heun: Add CES production function fits}
@@
 Need to find a way to calculate AIC for the object that is returned from the \texttt{cesEst} function.}
-      \item{\st{Create parameter graphs for each country}}
-      \item{\st{Parameter tables for each energy type in the appendix}}
-      \item{\st{GDP comparison graph}}
-      \item{\st{Convert $\rho$ variables in the CES production function to $\sigma$}}
-      \item{\st{Add a CES model without energy option (energyType=NA means CES without energy)}}
-        \begin{itemize}
-          \item{\st{Create a CES without energy parameters graphs (with CIs) in the paper}}
-          \item{\st{Extract CES without energy parameters from the ``without energy'' models and correctly name them: $\sigma \rightarrow \sigma_1$, $\rho \rightarrow \rho_1$, $\delta \rightarrow \delta_1$}}
-          \item{\st{Add CES without energy parameters to tables of results in the appendix}}
-          \item{\st{Add CES without energy lines to the CES lattice graph}}
-        \end{itemize}
       \end{itemize}
@@
 \item{de Wit: review, critique, and contextualize.}
-\item{\st{Heun: adjust y axis limits on $a_0$ and $c_t$ parameter graphs for the LINEX model AFTER we finish debugging the LINEX models.}}
-\item{\st{Heun: Add the insight that for indexed factors of production $q$ and $x$, there is small difference in absolute magnitude and even smaller difference in indexed values unless $f_{exergy-allocation}$ is significantly different from 1.0 \emph{and} there is a shift in energy input to the economy.}}
-\item{\st{Heun: Deal with missing covariance numbers when columns have unequal length. Use the \texttt{subset} command? Partially complete: need to work on the $u$ data only.}}
-\item{\st{Heun: Ensure consistent x and y axis limits in partial residual plots}}
-\item{\st{Heun: Use full country names instead of 2-letter abbreviations in partial residual plots}}
-\item{\st{Heun: Adjust variable threePanelGraphHeight in the EconGrowth-R-Functions.Rnw file to produce U partial residual plots that are exactly the same size as the graphs in the 9-panel plots.}}
-\item{\st{Heun: Eliminate non-developed countries from 9-panel partial residual plots}}
-\item{\st{Heun: Add references from Lucas}}
-\item{\st{Heun: Obtain answers to questions I put to Caleb about the energy section}}
-\item{\st{Heun: Add Warr to acknowledgements}}
-\item{\st{Heun: Include EIA graphic (instead of IEA graphic) in the seminar}}
-\item{\st{Reese: Send URL reference for FAO food data.}}
-\item{\st{Heun: Fix the ordering of references in the bibliography by setting the alphabetical order of the keys to match the temporal order of the references. I think the bibliography is OK.}}
-\item{\st{Heun: Fix parentheses heights in LINEX production function equation.}}
-\item{\st{Heun: Add data from 2011 to the models}}
-\item{\st{Heun: Fix weirdnesses with China on the CD gamma grid search graph.}}
-\item{\st{Heun: Add diagonal lines to triangle plots via the doubleY graph idea.
-Make a simple data.frame that contains the coordinates of the line and add it to the graph as a second Y axis, but don't show the second Y axis.}}
-\item{\st{Reese: Add text from Word verson of paper to the LaTeX version.}}
-\item{\st{Heun: Add CI vs.
-params plots for all model types (the triangle plots from the seminar).
-Maybe as a lattice graph where each model type is a panel.
-But, wait until we know if we have symmetric confidence intervals before doing this.
-These graphs won't work if we have asymmetric CIs.}}
-\item{\st{Heun: Rearrange the panels on the CD gamma grid search graph}}
-\item{\st{Heun: Change the strip to transparent on the CD gamma grid search graph}}
-\item{\st{Heun: Get full country names into the CD gamma grid search graph}}
-\item{\st{Heun: Change the presentation to use the cdeGridLattice function instead of cdeGridGraph}}
-\item{\st{Heun: Remove cdeGridGraph function}}
-\item{\st{Heun: Add 9-panel lattice graph for min($SSE_y$) graphs for the CD model}}
-\item{\st{Heun: x-axis labels only on bottom for 9-panel lattice graphs}}
-\item{\st{Heun: Convert the presentation to use energyType=NA for models without energy}}
-\item{\st{Heun: Convert to using NA everywhere for models without energy}}
-\item{\st{Heun: Investigate use of the micEcon package transLogEst function for CD parameter estimation. Result: doesn't look like it will work, because it doesn't do the CD form of interest to us.}}
-\item{\st{Heun: Re-organize CES tables into (a) $\lambda$, $\delta$, $\sigma$ and (b) $\gamma$, $\delta_1$, $\sigma_1$}}
-\item{\st{Heun: Ask Martin if he can supply an ``Economics'' affiliation. Will probably make a stronger paper.}}
-\item{\st{Heun: Create a table of AIC values for each fit.}}
-\item{\st{Heun: Add $u$ predictions for Cobb-Douglas}}
-\item{\st{Heun: Move tables to an appendix at the end.}}
-\item{\st{Heun: Add acknowledgements (Dad, Pruim)}}
-\item{\st{Heun: Add $u$ parameter table and graph}}
-\item{\st{Heun: Add covariance metrics.}}
-\item{\st{Heun: Add single factor fits}}
-      \begin{itemize}
-      \item{\st{Correct sizes for parameter graphs for each country}}
-      \item{\st{Parameter graphs ($\lambda$ and $m$) for each country}}
-      \item{\st{Parameter tables for each country in the appendix}}
-      \item{\st{GDP comparison graph}}
-      \item{\st{AIC rows in the AIC table}}
-      \end{itemize}
-\item{\st{Heun: Add setup variables for figure height and width where not already included.}}
-\item{\st{Heun: Add LINEX production function fits}}
-      \begin{itemize}
-      \item{\st{Parameter graphs for each country}}
-      \item{\st{Parameter tables for each country in the appendix}}
-      \item{\st{AIC rows in the AIC table}}
-      \item{\st{GDP comparison graph}}
-      \end{itemize}
-\item{\st{de Wit: provide funding acknowledgement, if necessary}}
 \end{itemize}

### 2013-05-28 EconGrowth-R-Functions.Rnw
Trying to fix error where CD with X fails for TZ.
Added some to-do items in preparation for meeting Randy Pruim. Some small edits on the paper.

--- 2013-05-24 EconGrowth-R-Functions.Rnw
@@
   model <- iGDP ~ exp(lambda*iYear) * iCapStk^alpha * iLabor^(1 - alpha)
-  modelCD <- nls(formula=model, data=dataTable, start = start,
+  modelCD <- nls(formula=model, data=dataTable, start=start,
                  #Include the next 3 lines to fit with constraints.
@@
 cobbDouglasData <- function(countryAbbrev, energyType){
-  #First, check to see if we want useful work (U) AND one of the countries for which we don't have data.
+  # First, check to see if we want useful work (U) AND one of the countries for which we don't have data.
   if (!haveDataCD(countryAbbrev, energyType)){
@@
   modelCD <- cobbDouglasModel(countryAbbrev=countryAbbrev, energyType=energyType)
+print(str(modelCD))
   summaryCD <- summary(modelCD) # Gives the nls summary table.
-  ciCD <- confint(modelCD, level = ciLevel)  # Calculates confidence intervals for the CD model.
+print(summaryCD)
+print("Before CI calculation")
+  ciCD <- confint(object=modelCD, level=ciLevel)  # Calculates confidence intervals for the CD model.
+print("After CI calculation")
+print(ciCD)
   dofCD <- summaryCD$df[2] # Gives the degrees of freedom for the model.

### 2013-05-28 EconGrowth.Rnw
Added some to-do items in preparation for meeting Randy Pruim. Some small edits on the paper.

@@
 \\* There is code after the to-do list in this file that exposes the problem.}
+\item{Heun: Get function \texttt{cdModel} working with constraints.
+Note that the unconstrained solutions are sometimes within the constraints.
+But, sometimes they aren't.
+All solutions need to be within constraints.
+We may need to run with warnings turned off to get this to work properly.}
 \item{Heun: Get function \texttt{cdeModel} working with constraints.
@@
 
-\noindent where $y \equiv Y/Y_\mathrm{0}$, $k \equiv K/K_\mathrm{0}$, and $l \equiv L/L_\mathrm{0}$; with $Y$ represented by GDP, $K$ expressed in currency units, $L$ expressed in workers/year or work-hours/year, time ($t$) measured in years, with e being the base of the natural logarithm, and subscripts ``0'' indicating values at an initial year.
+\noindent where $y \equiv Y/Y_\mathrm{0}$, $k \equiv K/K_\mathrm{0}$, and $l \equiv L/L_\mathrm{0}$; with $Y$ represented by GDP, $K$ expressed in currency units, $L$ expressed in workers or work-hours/year, time ($t$) measured in years, with e being the base of the natural logarithm, and subscripts ``0'' indicating values at an initial year.
 $A$ is a unitless technological progress term, with $\lambda$ indicating the pace of technological progress (in units of year$^{-1}$).\footnote{Dimensionless, indexed quantities are represented by lower-case symbols ($y$, $k$, $l$, $e$, $q$, $x$, and $u$), and dimensional quantities are represented by upper-case symbols ($Y$, $K$, $L$, $E$, $Q$, $X$, and $U$).
-One exception is the technolgical progress term $A$, which is dimensionless but written in upper-case by convention.} Neoclassical economic growth theory as expressed in the Cobb-Douglas production function makes no attempt to describe the mechanisms by which technological progress ($A$) affects economic growth, nor does it attempt to describe how technological progress ($A$) might vary from one economy to the next.
+One exception is the technolgical progress term $A$, which is dimensionless but written upper-case by convention.} Neoclassical economic growth theory as expressed in the Cobb-Douglas production function makes no attempt to describe the mechanisms by which technological progress ($A$) affects economic growth, nor does it attempt to describe how technological progress ($A$) might vary from one economy to the next.
 Mathematically, $A$ is a fitting parameter that aligns the predictions of Equation~\ref{eq:CD} with historical data.
@@
 
-<<Historical_Lattice_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Historical data: Indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$).">>=
+<<Historical_Lattice_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$).">>=
 createHistoricalLatticeGraph()

### 2013-05-28 EconGrowth.Rnw
Edited the to-do list

@@
 The problem occurs in function \texttt{cobbDouglasData}.
-To repeat the problem, call \texttt{cobbDouglasData(countryAbbrev="TZ", energyType="X")}.
+To repeat the problem, call \\* \texttt{cobbDouglasData(countryAbbrev="TZ", energyType="X")}.
 The code fails on the line \\* \texttt{  ciCD <- confint(object=modelCD, level=ciLevel)}.
@@
 All solutions need to be within constraints.
-We may need to run with warnings turned off to get this to work properly.}
+We may need to run with warnings turned off to view the problems.}
 \item{Heun: Get function \texttt{cdeModel} working with constraints.
@@
 All solutions need to be within constraints.
-We may need to run with warnings turned off to get this to work properly.}
+We may need to run with warnings turned off to view the problems.}
 \item{Heun: Investigate possible conflicting use of exergy by Warr and Ayres.}

### 2013-05-28 EconGrowth.Rnw
Additional to-do list enhancements.
Edited to-do list.
Shortening lines.

@@
 \begin{itemize}
+\item{\st{Heun: Get Pruim set up on the GitHub repository.}}
 \item{Heun: Fix error when calculating confidence intervals for Cobb-Douglas model for TZ with X.
@@
 To repeat the problem, call \\* \texttt{cobbDouglasData(countryAbbrev="TZ", energyType="X")}.
-The code fails on the line \\* \texttt{  ciCD <- confint(object=modelCD, level=ciLevel)}.
+\\* The code fails on the line \\* \texttt{  ciCD <- confint(object=modelCD, level=ciLevel)}.
 \\* There is code after the to-do list in this file that exposes the problem.}
@@
 
-Neoclassical economic growth theory attributes output ($Y$) to factors of production: capital stock ($K$) and labor ($L$).
-The Cobb-Douglas production function is the canonical representation of indexed economic output ($y$) as a function of indexed labor ($l$), indexed capital stock ($k$), and an exogenous, time-dependent technological progress term ($A$):
+Neoclassical economic growth theory attributes output ($Y$) to factors of production:
+capital stock ($K$) and labor ($L$). The Cobb-Douglas production function is the 
+canonical representation of indexed economic output ($y$) as a function of indexed 
+labor ($l$), indexed capital stock ($k$), and an exogenous, time-dependent 
+technological progress term ($A$):
 
@@
 
-\noindent where $y \equiv Y/Y_\mathrm{0}$, $k \equiv K/K_\mathrm{0}$, and $l \equiv L/L_\mathrm{0}$; with $Y$ represented by GDP, $K$ expressed in currency units, $L$ expressed in workers or work-hours/year, time ($t$) measured in years, with e being the base of the natural logarithm, and subscripts ``0'' indicating values at an initial year.
-$A$ is a unitless technological progress term, with $\lambda$ indicating the pace of technological progress (in units of year$^{-1}$).\footnote{Dimensionless, indexed quantities are represented by lower-case symbols ($y$, $k$, $l$, $e$, $q$, $x$, and $u$), and dimensional quantities are represented by upper-case symbols ($Y$, $K$, $L$, $E$, $Q$, $X$, and $U$).
-One exception is the technolgical progress term $A$, which is dimensionless but written upper-case by convention.} Neoclassical economic growth theory as expressed in the Cobb-Douglas production function makes no attempt to describe the mechanisms by which technological progress ($A$) affects economic growth, nor does it attempt to describe how technological progress ($A$) might vary from one economy to the next.
-Mathematically, $A$ is a fitting parameter that aligns the predictions of Equation~\ref{eq:CD} with historical data.
-Typically, the constraint $\alpha + \beta = 1$ is assumed, indicating constant returns to scale.
-
-As shown in Equation~\ref{eq:CD} above, neoclassical economic theory does not include an explicit term for the role of energy in economic growth.
-However, \citet{Bashmakov:2007ek}, \citet{Hamilton:2009ui}, \citet{Murphy:2011jh}, \citet{Benes:2012tm}, \citet{Kumhof:2012ua}, and others indicate that the importance of energy for economic growth may far outweigh its cost share in the economy.
-That neoclassical economic growth theory ignores energy is, therefore, cause for concern, and inquiry into the proper approach for including energy as a factor of production in economic growth modeling is both relevant and important.
-
-Some energy economists augment economic growth models by including energy as an additional (or the only) factor of production.
-However, there is little agreement on how this should be done.
-Neither the mathematical form of the energy-augmented production function nor the quantification of energy are consistent in the literature.
-There has been little empirical work assessing the predictive ability of various energy-augmented production functions for different types of economies.
-And, very few studies of the importance of energy in economic growth include rigorous statistical assessments of energy-related fitting parameters.
-This paper attempts to contribute to the literature by applying statistically rigorous methods along three coordinates of analysis: form of the energy augmented production function, energy quantification, and type of economy.
-
-The remainder of this paper is organized as follows.
-Section~\ref{sec:Coordinates} discusses the coordinates of analysis described above.
-Section~\ref{sec:Sources_of_Data} details sources of data and calculations to generate time series for economic output and factors of production.
-The procedures for and results from parameter estimation for the various production functions are discussed in Section~\ref{sec:Parameter_Estimation}.
-Section~\ref{sec:Implications} discusses implications of the parameter estimation results, and Section~\ref{sec:Conclusion} concludes.
-An appendix provides details of all statistical results.
+\noindent where $y \equiv Y/Y_\mathrm{0}$, $k \equiv K/K_\mathrm{0}$, and 
+$l \equiv L/L_\mathrm{0}$; with $Y$ represented by GDP, $K$ expressed in 
+currency units, $L$ expressed in workers or work-hours/year, time ($t$) measured in years, 
+with e being the base of the natural logarithm, and subscripts ``0'' indicating values 
+at an initial year. $A$ is a unitless technological progress term, with $\lambda$ 
+indicating the pace of technological progress (in units of 
+year$^{-1}$).\footnote{Dimensionless, indexed quantities are represented by 
+lower-case symbols 
+($y$, $k$, $l$, $e$, $q$, $x$, and $u$), and dimensional 
+quantities are represented by upper-case symbols 
+($Y$, $K$, $L$, $E$, $Q$, $X$, and $U$). One exception is the technolgical 
+progress term $A$, which is dimensionless but written upper-case by convention.} 
+Neoclassical economic growth theory as expressed in the Cobb-Douglas production 
+function makes no attempt to describe the mechanisms by which technological 
+progress ($A$) affects economic growth, nor does it attempt to describe how 
+technological progress ($A$) might vary from one economy to the next. Mathematically, 
+$A$ is a fitting parameter that aligns the predictions of Equation~\ref{eq:CD} 
+with historical data. Typically, the constraint $\alpha + \beta = 1$ is assumed, 
+indicating constant returns to scale.
+
+As shown in Equation~\ref{eq:CD} above, neoclassical economic theory does not 
+include an explicit term for the role of energy in economic growth. However, 
+\citet{Bashmakov:2007ek}, \citet{Hamilton:2009ui}, \citet{Murphy:2011jh}, 
+\citet{Benes:2012tm}, \citet{Kumhof:2012ua}, and others indicate that the 
+importance of energy for economic growth may far outweigh its cost share in the 
+economy. That neoclassical economic growth theory ignores energy is, therefore, 
+cause for concern, and inquiry into the proper approach for including energy 
+as a factor of production in economic growth modeling is both relevant and important.
+
+Some energy economists augment economic growth models by including energy as an 
+additional (or the only) factor of production. However, there is little agreement 
+on how this should be done. Neither the mathematical form of the energy-augmented 
+production function nor the quantification of energy are consistent in the 
+literature. There has been little empirical work assessing the predictive ability 
+of various energy-augmented production functions for different types of economies. 
+And, very few studies of the importance of energy in economic growth include 
+rigorous statistical assessments of energy-related fitting parameters. This paper 
+attempts to contribute to the literature by applying statistically rigorous 
+methods along three coordinates of analysis: form of the energy augmented 
+production function, energy quantification, and type of economy.
+
+The remainder of this paper is organized as follows. Section~\ref{sec:Coordinates} 
+discusses the coordinates of analysis described above. 
+Section~\ref{sec:Sources_of_Data} details sources of data and calculations to 
+generate time series for economic output and factors of production. The procedures 
+for and results from parameter estimation for the various production functions 
+are discussed in Section~\ref{sec:Parameter_Estimation}. 
+Section~\ref{sec:Implications} discusses implications of the parameter estimation 
+results, and Section~\ref{sec:Conclusion} concludes. An appendix provides details 
+of all statistical results.
 

### 2013-05-28 EconGrowth.Rnw
Now using the .R file instead of the .Rnw file for the paper.

@@
 \begin{document}
+
+<<setup_child, echo=FALSE, message=FALSE, eval=TRUE>>=
+# Includes the Functions.Rnw file that contains all of the functions for analyzing our economic data.
+require(lattice)
+require(latticeExtra)
+require(ggplot2)
+require(car)
+require(mosaic)
+require(xtable)
+require(nlmrt)
+require(micEconCES)
+require(reshape2) # Provides access to data melting. See http://cran.r-project.org/web/packages/reshape2/reshape2.pdf
+# tikz allows use of LaTeX formatting and font in graphs. Allows for a consistent look across the paper.
+# See http://r-forge.r-project.org/R/?group_id=440 for instructions on installing tikzDevice.
+# require(tikzDevice) 
+trellis.par.set(theme=theme.mosaic())
+options(width=75)
+options(show.signif.stars=TRUE)
+opts_chunk$set(
+  # ********************************************************************************************************
+  eval=FALSE,
+  # ********************************************************************************************************
+  dev='tikz',    #Allows LaTeX code in graphical output. E.g., "$y$" for a variable name in the legend for a graph.
+  tidy=FALSE,
+  comment=NA,
+  #Tells whether to cache output from chunks are saved. Cacheing saves time. 
+  #However, references to LaTeX tables DO NOT WORK if cacheing is turned on (i.e., cache=TRUE).
+  cache=FALSE,
+  warning=FALSE,  #Tells whether to show warnings in the output.
+  message=FALSE, #Turns off messages for all chunks. Set TRUE on an individual chunk to see it.
+  echo=FALSE     #Tells whether to echo code for all chunks. Set TRUE on an individual chunk to see its code.
+)
+source("Econ-Growth-Functions.R")
+@
 
@@
 
-<<setup_child, child='EconGrowth-R-Functions.Rnw', echo=FALSE, message=FALSE, eval=TRUE>>=
-# Includes the Functions.Rnw file that contains all of the functions for analyzing our economic data.
-@
-
 <<FindError, eval=TRUE>>=
@@
 
-This section describes the three coordinates of analysis and briefly reviews literature related to each.
+This section describes the three coordinates of analysis and briefly reviews 
+literature related to each.
 
@@
 
-In this paper, we assess three prominent energy-augmented production functions appear in the literature: Cobb-Douglas (CDe), Constant Elasticity of Substitution (CESe), and LINear EXponential (LINEX).
-The following subsections describe each.
+In this paper, we assess three prominent energy-augmented production functions 
+appear in the literature: Cobb-Douglas (CDe), Constant Elasticity of 
+Substitution (CESe), and LINear EXponential (LINEX). The following subsections 
+describe each.
 
@@
 
-Similar to Equation~\ref{eq:CD}, the energy-augmented Cobb-Douglas production function is
+Similar to Equation~\ref{eq:CD}, the energy-augmented Cobb-Douglas 
+production function is
 
@@
 
-\noindent where $e \equiv E/E_0$, and $E$ is in units of energy per time, typically TJ/year.
-The energy-augmented Cobb-Douglas production function is often assumed to have constant returns to scale for the three factors of production: $\alpha + \beta + \gamma = 1$.
-
-\citet{Ayres:2008cl} uses Equation~\ref{eq:CDe} with exergy ($x$) and useful work ($u$) quantifications for $e$ to describe historic Japanese and American economies from 1900-2000.
-\citet{Froling:2009vo} uses an energy-augmented Cobb-Douglas production function with thermal energy quantification ($q$) to describe output for the global economy from 1800-1970.
-Fr\"{o}ling's model endogenizes labor with respect to fertility and mortality rates and separates thermal energy into two types: biomass energy and coal energy.
-\citet{Serrenho:2010vq} use the log transform of the energy-augmented Cobb-Douglas function with thermal energy quantification ($q$) to describe output for the EU-15 countries.
-Serrenho divides thermal energy into renewables, non-renewables, wastes, and imports.
-
-**** Martin: add more here about the conclusions of each paper regarding the role of energy in economic growth?
-Add additional literature?
-Or, adjust as you see fit.
-Especially, are there any confidence intervals or statistical evaluation in each of these studies?
-****
+\noindent where $e \equiv E/E_0$, and $E$ is in units of energy per time, 
+typically TJ/year. The energy-augmented Cobb-Douglas production function 
+is often assumed to have constant returns to scale for the three factors 
+of production: $\alpha + \beta + \gamma = 1$.
+
+\citet{Ayres:2008cl} uses Equation~\ref{eq:CDe} with exergy ($x$) and 
+useful work ($u$) quantifications for $e$ to describe historic Japanese 
+and American economies from 1900-2000. \citet{Froling:2009vo} uses an 
+energy-augmented Cobb-Douglas production function with thermal energy 
+quantification ($q$) to describe output for the global economy from 
+1800--1970. Fr\"{o}ling's model endogenizes labor with respect to fertility 
+and mortality rates and separates thermal energy into two types: biomass 
+energy and coal energy. \citet{Serrenho:2010vq} use the log transform of 
+the energy-augmented Cobb-Douglas function with thermal energy 
+quantification ($q$) to describe output for the EU-15 countries. 
+Serrenho divides thermal energy into renewables, non-renewables, 
+wastes, and imports.
+
+**** Martin: add more here about the conclusions of each paper regarding 
+the role of energy in economic growth? Add additional literature? 
+Or, adjust as you see fit. Especially, are there any confidence intervals 
+or statistical evaluation in each of these studies? ****
 
@@
 
-Other energy economists use an energy-augmented Constant Elasticity of Substitution (CESe) production function to describe economic growth.
-The \texttt{R} \citep{R} package \texttt{micEconCES} \citep{Henningsen:2011td} estimates CES production functions of the following forms (among others):
+Other energy economists use an energy-augmented 
+Constant Elasticity of Substitution (CESe) production function to 
+describe economic growth. The \texttt{R} \citep{R} package 
+\texttt{micEconCES} \citep{Henningsen:2011td} estimates CES production 
+functions of the following forms (among others):
 

### 2013-05-28 Econ-Growth-Functions.R

@@ -1,5 +1,4 @@
 ## <<setup_parent, echo=FALSE, message=FALSE, eval=TRUE>>=
-require(knitr)
 require(lattice)
 require(latticeExtra)
 require(ggplot2)
@@ -12,23 +11,23 @@ require(reshape2) # Provides access to data melting. See http://cran.r-project.o
 # tikz allows use of LaTeX formatting and font in graphs. Allows for a consistent look across the paper.
 # See http://r-forge.r-project.org/R/?group_id=440 for instructions on installing tikzDevice.
 # require(tikzDevice) 
-trellis.par.set(theme=theme.mosaic())
-options(width=75)
-options(show.signif.stars=TRUE)
-opts_chunk$set(
-  # ********************************************************************************************************
-  eval=TRUE,
-  # ********************************************************************************************************
-  dev='tikz',    #Allows LaTeX code in graphical output. E.g., "$y$" for a variable name in the legend for a graph.
-  tidy=FALSE,
-  comment=NA,
-  #Tells whether to cache output from chunks are saved. Cacheing saves time. 
-  #However, references to LaTeX tables DO NOT WORK if cacheing is turned on (i.e., cache=TRUE).
-  cache=FALSE,
-  warning=FALSE,  #Tells whether to show warnings in the output.
-  message=FALSE, #Turns off messages for all chunks. Set TRUE on an individual chunk to see it.
-  echo=FALSE     #Tells whether to echo code for all chunks. Set TRUE on an individual chunk to see its code.
-)
+# trellis.par.set(theme=theme.mosaic())
+# options(width=75)
+# options(show.signif.stars=TRUE)
+# opts_chunk$set(
+#   # ********************************************************************************************************
+#   eval=TRUE,
+#   # ********************************************************************************************************
+#   dev='tikz',    #Allows LaTeX code in graphical output. E.g., "$y$" for a variable name in the legend for a graph.
+#   tidy=FALSE,
+#   comment=NA,
+#   #Tells whether to cache output from chunks are saved. Cacheing saves time. 
+#   #However, references to LaTeX tables DO NOT WORK if cacheing is turned on (i.e., cache=TRUE).
+#   cache=FALSE,
+#   warning=FALSE,  #Tells whether to show warnings in the output.
+#   message=FALSE, #Turns off messages for all chunks. Set TRUE on an individual chunk to see it.
[…]

### 2013-05-29 EconGrowth.Rnw
removed print()
Changed name of chunk setup_child to setup.

@@
 
-<<setup_child, echo=FALSE, message=FALSE, eval=TRUE>>=
+<<setup, echo=FALSE, message=FALSE, eval=TRUE>>=
 # Includes the Functions.Rnw file that contains all of the functions for analyzing our economic data.
@@
 
-print(cobbDouglasData(countryAbbrev="TZ", energyType="X"))
+cobbDouglasData(countryAbbrev="TZ", energyType="X")
 

### 2013-05-30 EconGrowth.Rnw
Added a couple to-do items regarding CIs.

@@
 \begin{itemize}
-\item{\st{Heun: Get Pruim set up on the GitHub repository.}}
+\item{Pruim: At present, we are doing simple ± t-value * std. dev. for
+      confidence intervals of, e.g., $1-\alpha-\beta$ in some places. 
+      Is that still correct if we move to a different approach for 
+      estimating confidence intervals?}
+\item{Pruim: At present, we are doing \texttt{deltaMethod} for determining CIs on 
+      $1-\alpha-\beta$ terms. Is that OK if we move to a different approach
+      for estimating confidence intervals?}
 \item{Heun: Fix error when calculating confidence intervals for Cobb-Douglas model for TZ with X.
@@
 \item{de Wit: review, critique, and contextualize.}
+\item{\st{Heun: Get Pruim set up on the GitHub repository.}}
 \end{itemize}

### 2013-05-30 EconGrowth.Rnw
Shortlining.

@@
 <<setup, echo=FALSE, message=FALSE, eval=TRUE>>=
-# Includes the Functions.Rnw file that contains all of the functions for analyzing our economic data.
 require(lattice)
@@
 require(micEconCES)
-require(reshape2) # Provides access to data melting. See http://cran.r-project.org/web/packages/reshape2/reshape2.pdf
-# tikz allows use of LaTeX formatting and font in graphs. Allows for a consistent look across the paper.
-# See http://r-forge.r-project.org/R/?group_id=440 for instructions on installing tikzDevice.
-# require(tikzDevice) 
+# Provides access to data melting. 
+# See http://cran.r-project.org/web/packages/reshape2/reshape2.pdf
+require(reshape2) 
+# tikz allows use of LaTeX formatting and font in graphs. 
+# Allows for a consistent look across the paper.
+# See http://r-forge.r-project.org/R/?group_id=440 for instructions 
+# on installing tikzDevice.
+require(tikzDevice) 
 trellis.par.set(theme=theme.mosaic())
@@
 opts_chunk$set(
-  # ********************************************************************************************************
+  # ********************************************************
   eval=FALSE,
-  # ********************************************************************************************************
-  dev='tikz',    #Allows LaTeX code in graphical output. E.g., "$y$" for a variable name in the legend for a graph.
+  # ********************************************************
+  # Allows LaTeX code in graphical output. 
+  # E.g., "$y$" for a variable name in the legend for a graph.  
+  dev='tikz',    
   tidy=FALSE,
   comment=NA,
-  #Tells whether to cache output from chunks are saved. Cacheing saves time. 
-  #However, references to LaTeX tables DO NOT WORK if cacheing is turned on (i.e., cache=TRUE).
+  # Tells whether to cache output from chunks are saved. Cacheing saves time. 
+  # However, references to LaTeX tables DO NOT WORK if cacheing is turned on.
   cache=FALSE,
   warning=FALSE,  #Tells whether to show warnings in the output.
-  message=FALSE, #Turns off messages for all chunks. Set TRUE on an individual chunk to see it.
-  echo=FALSE     #Tells whether to echo code for all chunks. Set TRUE on an individual chunk to see its code.
+  # Turns off messages for all chunks. 
+  # Set TRUE on an individual chunk to see it.
+  message=FALSE, 
+  # Tells whether to echo code for all chunks. 
+  # Set TRUE on an individual chunk to see its code.
+  echo=FALSE     
 )
@@
 \begin{equation} \label{eq:CES}
-  y = \gamma \: A \: \left[\delta_1 k^{-\rho_1} + (1-\delta_1)l^{-\rho_1} \right]^{-1/\rho_1}; A = \mathrm{e}^{\lambda (t-t_0)}
+  y = \gamma \: A \: \left[\delta_1 k^{-\rho_1} 
+      + (1-\delta_1)l^{-\rho_1} \right]^{-1/\rho_1}; 
+      A = \mathrm{e}^{\lambda (t-t_0)}
 \end{equation}
@@
 \begin{equation} \label{eq:CESe}
-  y = \gamma \: A \: \left\{\delta \left[\delta_1 k^{-\rho_1} + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1} + (1-\delta) e^{-\rho} \right\}^{-1/\rho}; A = \mathrm{e}^{\lambda (t-t_0)}
+  y = \gamma \: A \: \left\{\delta \left[\delta_1 k^{-\rho_1} 
+      + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1} 
+      + (1-\delta) e^{-\rho} \right\}^{-1/\rho}; 
+      A = \mathrm{e}^{\lambda (t-t_0)}
 \end{equation}

### 2013-05-30 EconGrowth.Rnw
Shortening lines.
Line shortening.

@@
   # ********************************************************
-  eval=FALSE,
+  eval=TRUE,
   # ********************************************************
@@
 )
-source("Econ-Growth-Functions.R")
+source("Econ-Growth-Functions2.R")
 @
@@
       for estimating confidence intervals?}
-\item{Heun: Fix error when calculating confidence intervals for Cobb-Douglas model for TZ with X.
-The problem occurs in function \texttt{cobbDouglasData}.
-To repeat the problem, call \\* \texttt{cobbDouglasData(countryAbbrev="TZ", energyType="X")}.
-\\* The code fails on the line \\* \texttt{  ciCD <- confint(object=modelCD, level=ciLevel)}.
-\\* There is code after the to-do list in this file that exposes the problem.}
+\item{Heun: Fix error when calculating confidence intervals for 
+Cobb-Douglas model for TZ with X. The problem occurs in function 
+\texttt{cobbDouglasData}. To repeat the problem, call \\* 
+\texttt{cobbDouglasData(countryAbbrev="TZ", energyType="X")}. \\* 
+The code fails on the line \\* 
+\texttt{  ciCD <- confint(object=modelCD, level=ciLevel)}. \\* 
+There is code after the to-do list in this file that exposes the problem.}
 \item{Heun: Get function \texttt{cdModel} working with constraints. 
 Note that the unconstrained solutions are sometimes within the constraints. 
-But, sometimes they aren't.
-All solutions need to be within constraints.
+But, sometimes they aren't. All solutions need to be within constraints. 
 We may need to run with warnings turned off to view the problems.}
@@
 Note that the unconstrained solutions are sometimes within the constraints. 
-But, sometimes they aren't.
-All solutions need to be within constraints.
+But, sometimes they aren't. All solutions need to be within constraints. 
 We may need to run with warnings turned off to view the problems.}
@@
       \begin{itemize}
-      \item{Get values and se for $\sigma$s directly from the \texttt{cesModel} object in the \texttt{cesData} function}
-      \item{Write up the decisions about parameter estimation for the CES production function fits}
-      \item{Revisit my assumptions for the CES production function (with energy) for each country.}
-      \item{Fix the problems with $\sigma_1$ and $\sigma$ values in the CES parameter tables in the appendix}
-      \item{Add CES rows to the AIC table.
-Code is in the \texttt{createAICTable} function, but it is not yet working.
-Need to find a way to calculate AIC for the object that is returned from the \texttt{cesEst} function.}
+      \item{Get values and se for $\sigma$s directly from the 
+            \texttt{cesModel} object in the \texttt{cesData} function}
+      \item{Write up the decisions about parameter estimation for the 
+            CES production function fits}
+      \item{Revisit my assumptions for the CES production function 
+            (with energy) for each country.}
+      \item{Fix the problems with $\sigma_1$ and $\sigma$ values in 
+            the CES parameter tables in the appendix}
+      \item{Add CES rows to the AIC table. Code is in the 
+            \texttt{createAICTable} function, but it is not yet working. Need to find a way to calculate AIC for the object that is returned from the \texttt{cesEst} function.}
       \end{itemize}
@@
 
-\noindent Equation~\ref{eq:CES} is a CES production function with capital stock ($k$) and labor ($l$) factors of production.
-Equation~\ref{eq:CESe} augments Equation~\ref{eq:CES} with energy using a ($kl$)($e$) nesting structure, as is typical in the literature.
-Equation~\ref{eq:CES} is a degenerate form of Equation~\ref{eq:CESe} where $\delta = 1$.
-The elasticity of substitution between capital ($k$) and labor ($l$) is given by $\sigma_1 = \frac{1}{1+\rho_1}$, the elasticity of substitution between ($kl$) and ($e$) is given by $\sigma = \frac{1}{1+\rho}$, $\delta \in [0, 1]$ describes the importance of ($kl$) relative to ($e$), and $\gamma$ is a fitting parameter, expected to be close to unity.
-
-\citet{VanderWerf:2008tc} evalutes various nested CES production functions for 12 OECD countries with respect to climate change policy.
-\citeauthor{VanderWerf:2008tc} concludes that ($kl$)($e$) nesting structure best fits historical data.
-\citet{Lecca:2011kr} also evaluate a variety of CES production functions using a KLEM structure to determine how the various options for nesting the energy factor of production affect predictive ability.
+\noindent Equation~\ref{eq:CES} is a CES production function with 
+capital stock ($k$) and labor ($l$) factors of production. 
+Equation~\ref{eq:CESe} augments Equation~\ref{eq:CES} with energy 
+using a ($kl$)($e$) nesting structure, as is typical in the literature. 
+Equation~\ref{eq:CES} is a degenerate form of Equation~\ref{eq:CESe} 
+where $\delta = 1$. The elasticity of substitution between capital ($k$) 
+and labor ($l$) is given by $\sigma_1 = \frac{1}{1+\rho_1}$, 
+the elasticity of substitution between ($kl$) and ($e$) is given by 
+$\sigma = \frac{1}{1+\rho}$, $\delta \in [0, 1]$ describes the importance 
+of ($kl$) relative to ($e$), and $\gamma$ is a fitting parameter, 
+expected to be close to unity.
+
+\citet{VanderWerf:2008tc} evalutes various nested CES production 
+functions for 12 OECD countries with respect to climate change policy. 
+\citeauthor{VanderWerf:2008tc} concludes that ($kl$)($e$) nesting structure 
+best fits historical data. \citet{Lecca:2011kr} also evaluate a variety of 
+CES production functions using a KLEM structure to determine how the various 
+options for nesting the energy factor of production affect predictive ability. 
 \citet{Stern:2012ey} also use a CES production function of the form ($kl$)($e$). 
-\citeauthor{Stern:2012ey} apply their CES function to the Swedish economy from 1800-2000 and demonstrate the importance of the transition from wood to fossil fuels for economic growth.
-
-**** Martin: add more here about the conclusions of each paper regarding the role of energy in economic growth?
-Add additional literature?
-Or, adjust as you see fit.
-Especially, are there any confidence intervals or statistical evaluation in each of these studies?
-****
+\citeauthor{Stern:2012ey} apply their CES function to the Swedish economy 
+from 1800-2000 and demonstrate the importance of the transition from wood to 
+fossil fuels for economic growth.
+
+**** Martin: add more here about the conclusions of each paper regarding 
+the role of energy in economic growth? Add additional literature? 
+Or, adjust as you see fit. Especially, are there any confidence 
+intervals or statistical evaluation in each of these studies? ****
 
@@
 
-A third production function, the LINear EXponential (LINEX) function \citep{Kummel:1980wx,Kummel:1982vy,Kummel:1985vz,Kummel:1989tf,Kummel:2002tx,Kummel:2010vz}, was derived from thermodynamic considerations:
+A third production function, the LINear EXponential (LINEX) function 
+\citep{Kummel:1980wx,Kummel:1982vy,Kummel:1985vz,Kummel:1989tf,Kummel:2002tx,Kummel:2010vz}, 
+was derived from thermodynamic considerations:
 
 \begin{equation} \label{eq:LINEX}
-  y = Ae; A = \mathrm{e}^{a_0\left[2 \left(1 - \frac{1}{\rho_k} \right) + c_t \left(\vphantom{\frac{1}{\rho_k}}\rho_l - 1 \right)\right]},
-\end{equation}
-
-\noindent where $e$ is indexed energy and e is the base of the natural logarithm.
-The LINEX model assumes energy ($e$) is the only factor of production.
+  y = Ae; 
+  A = \mathrm{e}^{a_0\left[2 \left(1 - \frac{1}{\rho_k} \right) 
+    + c_t \left(\vphantom{\frac{1}{\rho_k}}\rho_l - 1 \right)\right]},
+\end{equation}
+
+\noindent where $e$ is indexed energy and e is the base of 
+the natural logarithm. The LINEX model assumes energy ($e$) 
+is the only factor of production. 
 The parameters $\rho_k$ and $\rho_l$ are defined as
@@
 
-\noindent and represent (a) capital stock increase relative to the average of labor and energy and (b) labor increase relative to energy, respectively.
+\noindent and represent 
+(a) capital stock increase relative to the average of labor and energy and 
+(b) labor increase relative to energy, respectively. 
 Energy ($e$), as the only factor of production, is enhanced by $A$ if either
@@
 \begin{itemize}
-\item{capital stock ($k$) has increased more than the average of energy ($e$) and labor ($l$), i.e. if $\rho_k >$ 1, or}
+\item{capital stock ($k$) has increased more than the average 
+      of energy ($e$) and labor ($l$), i.e. if $\rho_k >$ 1, or}
 \item{labor ($l$) has increased more than energy ($e$), i.e. if $\rho_l >$ 1.}
@@
 
-\noindent According to the LINEX model, an economy that can increase capital stock ($k$) without a commensurate increase in labor ($l$) and energy ($e$) will experience an increase in output ($y$) in excess of its increase of energy consumption ($e$), because $A$ will be greater than 1.
-Similarly, an economy benefits by increasing labor ($l$) without a commensurate increase in energy ($e$).
-Thus, $\rho_k$ is an efficiency of using labor and energy to make capital available to the economy, and $\rho_l$ is an efficiency of using energy to make labor available to the economy.
-$a_0$ represents the overall importance of these efficiencies, and $c_t$ represents the relative importance of the labor efficiency term compared to the capital stock efficiency term.
-We treat $a_0$ and $c_t$ as fitting parameters; both are assumed constant with respect to time.
-
-In contrast to both the Cobb-Douglas model (Equations~\ref{eq:CD} and \ref{eq:CDe}) and the CES model (Equations~\ref{eq:CES} and \ref{eq:CESe}), the LINEX model (Equation~\ref{eq:LINEX}) accounts for efficiencies among capital, labor, and energy directly and, therefore, does not employ a time-dependent technological progress term ($A$).
-\citet{Kummel:2002tx} use the LINEX production function to describe economic output for the economies of the U.S., Japan, and Germany.
-\citet{Warr:2010ga} compare the LINEX production function with the Cobb-Douglas production function to assess economic growth for Austria, the United Kingdom, the United States, and Japan.
-
-**** Martin: add more here about the conclusions of each paper regarding the role of energy in economic growth?
-Add additional literature?
-Or, adjust as you see fit.
-Especially, are there any confidence intervals or statistical evaluation in each of these studies?
-****
+\noindent According to the LINEX model, an economy that can increase 
+capital stock ($k$) without a commensurate increase in labor ($l$) 
+and energy ($e$) will experience an increase in output ($y$) in excess 
+of its increase of energy consumption ($e$), because $A$ will be 
+greater than 1. Similarly, an economy benefits by increasing labor ($l$) 
+without a commensurate increase in energy ($e$). Thus, $\rho_k$ is an 
+efficiency of using labor and energy to make capital available to the 
+economy, and $\rho_l$ is an efficiency of using energy to make labor 
+available to the economy. $a_0$ represents the overall importance 
+of these efficiencies, and $c_t$ represents the relative importance 
+of the labor efficiency term compared to the capital stock efficiency term. 
+We treat $a_0$ and $c_t$ as fitting parameters; 
+both are assumed constant with respect to time.
+
+In contrast to both the Cobb-Douglas model (Equations~\ref{eq:CD} and 
+\ref{eq:CDe}) and the CES model (Equations~\ref{eq:CES} and 
+\ref{eq:CESe}), the LINEX model (Equation~\ref{eq:LINEX}) accounts 
+for efficiencies among capital, labor, and energy directly and, 
+therefore, does not employ a time-dependent 
+technological progress term ($A$). \citet{Kummel:2002tx} use the 
+LINEX production function to describe economic output 
+for the economies of the U.S., Japan, and Germany. 
+\citet{Warr:2010ga} compare the LINEX production function with 
+the Cobb-Douglas production function to assess economic growth 
+for Austria, the United Kingdom, the United States, and Japan.
+
+**** Martin: add more here about the conclusions of each paper 
+regarding the role of energy in economic growth? Add additional literature? 
+Or, adjust as you see fit. Especially, are there any confidence intervals 
+or statistical evaluation in each of these studies? ****
 
@@
 
-The literature shows three quantifications of energy ($E$) used in energy-augmented production functions: thermal energy ($Q$), exergy ($X$), and useful work ($U$).
-Thermal energy ($Q$) is the heat content of an energy carrier.
-Exergy ($X$) is the maximum useful work that could be extracted from an energy carrier by a process that brings the system into equilibrium with a heat reservoir, typically the surrounding environment \citep[p.~78]{Ayres:2010ug}.
-Like \citeauthor{Ayres:2010ug}, we use chemical exergy (as opposed to thermal exergy or mechanical exergy) as our quantification for exergy ($x$).
-Useful work ($U$) includes the direct energy that goes into an economy, including work from machines, human muscles, and animals.
-Firms pay for thermal energy ($Q$), but useful work ($U$) alters the size and shape of materials, keeps the lights on, and transports goods to consumers.
-Not all forms of energy are created equal in terms of their ability to generate economic activity \citep{Cleveland:2000vl, Warr:2010ht}.
-Both exergy ($X$), and to a greater extent, useful work ($U$) quantifications of energy are intended to account for the usefulness of energy for generating economic activity, thereby reflecting the ``quality'' of each energy type and the efficiency of machines and devices typically used in energy conversion processes.
-
-Most energy economists use thermal energy ($q$) for the energy factor of production ($e$) in energy-augmented production functions, including \citet{Stern:2012ey}, \citet{Froling:2009vo}, \citet{Serrenho:2010vq}, and \citet{Kummel:1980wx,Kummel:1982vy,Kummel:1985vz,Kummel:1989tf,Kummel:2002tx,Kummel:2010vz}.
-\citet{Ayres:2003ec} introduced the idea that exergy ($x$) and useful work ($u$) were important factors of production.
-
-**** Martin: add more here about the conclusions of each paper regarding the role of energy in economic growth?
-Add additional literature?
-Or, adjust as you see fit.
-Especially, are there any confidence intervals or statistical evaluation in each of these studies?
-****
-
-We know of no statistically-rigorous comparisons of the predictive ability of each energy quantification in the various types of production functions discussed in Section~\ref{sec:Prod_Func_Forms}.
-We analyze all three quantifications of energy ($Q$, $X$, and $U$) for developed economies and thermal energy ($Q$) and exergy ($X$) for all other economies.
+The literature shows three quantifications of energy ($E$) used in 
+energy-augmented production functions: thermal energy ($Q$), 
+exergy ($X$), and useful work ($U$). Thermal energy ($Q$) 
+is the heat content of an energy carrier. Exergy ($X$) is 
+the maximum useful work that could be extracted from an energy carrier 
+by a process that brings the system into equilibrium with 
+a heat reservoir, typically the surrounding environment 
+\citep[p.~78]{Ayres:2010ug}. Like \citeauthor{Ayres:2010ug}, 
+we use chemical exergy (as opposed to thermal exergy or mechanical exergy) 
+as our quantification for exergy ($x$). Useful work ($U$) 
+includes the direct energy that goes into an economy, including work 
+from machines, human muscles, and animals. Firms pay for thermal energy ($Q$), 
+but useful work ($U$) alters the size and shape of materials, 
+keeps the lights on, and transports goods to consumers. 
+Not all forms of energy are created equal in terms of their ability 
+to generate economic activity \citep{Cleveland:2000vl, Warr:2010ht}. 
+Both exergy ($X$), and to a greater extent, useful work ($U$) 
+quantifications of energy are intended to account for the usefulness 
+of energy for generating economic activity, thereby reflecting 
+the ``quality'' of each energy type and the efficiency of machines 
+and devices typically used in energy conversion processes.
+
+Most energy economists use thermal energy ($q$) 
+for the energy factor of production ($e$) in energy-augmented 
+production functions, including \citet{Stern:2012ey}, 
+\citet{Froling:2009vo}, \citet{Serrenho:2010vq}, and 
+\citet{Kummel:1980wx,Kummel:1982vy,Kummel:1985vz,Kummel:1989tf,Kummel:2002tx,Kummel:2010vz}. 
+\citet{Ayres:2003ec} introduced the idea that exergy ($x$) and 
+useful work ($u$) were important factors of production.
+
+**** Martin: add more here about the conclusions of each paper 
+regarding the role of energy in economic growth? 
+Add additional literature? Or, adjust as you see fit. 
+Especially, are there any confidence intervals or 
+statistical evaluation in each of these studies? ****
+
+We know of no statistically-rigorous comparisons of the 
+predictive ability of each energy quantification in the 
+various types of production functions discussed in 
+Section~\ref{sec:Prod_Func_Forms}. We analyze all 
+three quantifications of energy ($Q$, $X$, and $U$) 
+for developed economies and thermal energy ($Q$) and 
+exergy ($X$) for all other economies.
 
@@
 
-In the energy-economic growth literature, the focus is almost exclusively on developed economies from North America or Europe.
-Examples include \citet{Kummel:1980wx} applying LINEX to describe the West German economy, \citet{Serrenho:2010vq} applying Cobb-Douglas variants to EU-15 countries, \citet{VanderWerf:2008tc} applying CES nesting variants to the 12 OECD countries, \citet{Lecca:2011kr} applying CES nesting variants to the Scottish economy, \citet{Stern:2012ey} applying CES to describe the Swedish economy, and \citet{Warr:2012cg} using LINEX and Cobb-Douglas to describe the Austrian, American, British, and Japanese economies.
-
-But, the nearly-complete focus on developed economies closes off the possibility of discovering any role that energy plays in the development process.
-In this paper we analyze at least two economies in each of the following four categories: Developed (technologically advanced with high standards of living), BRICS\footnote{Brazil, Russia, India, China, and South Africa} (rapid economic growth with standards of living below that of developed economies), Petrol (petroleum is a substantial source of GDP **** Martin: Is this the right way to describe the petrol economies?
-****); and LDCs\footnote{Lesser Developed Countries} (living standards near subsistence levels **** Martin: Is this the right way to describe the LDC economies?
-****).
+In the energy-economic growth literature, the focus is 
+almost exclusively on developed economies from North America 
+or Europe. Examples include \citet{Kummel:1980wx} applying 
+LINEX to describe the West German economy, \citet{Serrenho:2010vq} 
+applying Cobb-Douglas variants to EU-15 countries, 
+\citet{VanderWerf:2008tc} applying CES nesting variants 
+to the 12 OECD countries, \citet{Lecca:2011kr} applying 
+CES nesting variants to the Scottish economy, \citet{Stern:2012ey} 
+applying CES to describe the Swedish economy, and \citet{Warr:2012cg} 
+using LINEX and Cobb-Douglas to describe the Austrian, 
+American, British, and Japanese economies.
+
+But, the nearly-complete focus on developed economies closes off 
+the possibility of discovering any role that energy plays 
+in the development process. In this paper we analyze at least 
+two economies in each of the following four categories: 
+Developed (technologically advanced with high standards of living), 
+BRICS\footnote{Brazil, Russia, India, China, and South Africa} 
+(rapid economic growth with standards of living below that of 
+developed economies), 
+Petrol (petroleum is a substantial source of GDP 
+**** Martin: Is this the right way to describe the 
+petrol economies? ****); and 
+LDCs\footnote{Lesser Developed Countries} 
+(living standards near subsistence levels 
+**** Martin: Is this the right way to describe the LDC economies? ****). 
 (See Table~\ref{tab:Economy_Examples}.)
@@
 
-To assess energy-augmented models of economic growth along the coordinates of analysis outlined in Section~\ref{sec:Coordinates}, historical data for economic output ($Y$), capital stock ($K$), labor ($L$), thermal energy ($Q$), exergy ($X$), and useful work ($U$) are required.
-Subsections below describe sources for and calculations to obtain historical data.
-A final subsection presents the historical data in graphical form.
+To assess energy-augmented models of economic growth along the 
+coordinates of analysis outlined in Section~\ref{sec:Coordinates}, 
+historical data for economic output ($Y$), capital stock ($K$), 
+labor ($L$), thermal energy ($Q$), exergy ($X$), and useful work ($U$) 
+are required. Subsections below describe sources for and calculations 
+to obtain historical data. A final subsection presents the historical 
+data in graphical form.
 
@@
 We measure economic output ($Y$) by gross domestic product (GDP). 
-GDP data in real 2005 U.S.
-dollars for developed countries (1980--2011) and all other countries (1991--2011) was obtained from the World Bank's Global Economic Prospects (GEP) database \citep{WorldBankGEP:2013a}.
+GDP data in real 2005 U.S. dollars for developed countries (1980--2011) 
+and all other countries (1991--2011) was obtained from 
+the World Bank's Global Economic Prospects (GEP) database 
+\citep{WorldBankGEP:2013a}.
 
@@
 
-Gross capital stock in real 2005 U.S.
-dollars for developed countries (1980--2011) and all other countries (1991--2011) was obtained from the World Bank's Global Economic Prospects (GEP) database \citep{WorldBankGEP:2013a}.
+Gross capital stock in real 2005 U.S. dollars 
+for developed countries (1980--2011) and 
+all other countries (1991--2011) was obtained from 
+the World Bank's Global Economic Prospects (GEP) database 
+\citep{WorldBankGEP:2013a}.
 
@@
 
-Total employment and average hours worked per worker per year for the developed nations (United States, United Kingdom, and Japan) for 1980--2011 were obtained from the United States \citet[Tables 6 and 7]{BLS:2013a}.
-Total hours worked per year was calculated by multiplying total employment by average hours worked per worker per year.
-
-The World Bank's World Development Indicators database \citep{WorldBankWDI:2013a} provides the employment to population ratio for people fifteen and older, total population, and a percentage of people under fifteen for other economies (South Africa, China, Iran, Saudi Arabia, Tanzania, and Zambia) for 1991--2011.
-The population of people under fifteen years of age was subtracted from total population to calculate the population of people fifteen and older.
-Total employment was calculated by multiplying the employment to population ratio of people fifteen and older by the population of people fifteen and older.
+Total employment and average hours worked per worker per year 
+for the developed nations (United States, United Kingdom, and Japan) 
+for 1980--2011 were obtained from the United States 
+\citet[Tables 6 and 7]{BLS:2013a}. Total hours worked per year was 
+calculated by multiplying total employment by average hours worked 
+per worker per year.
+
+The World Bank's World Development Indicators database 
+\citep{WorldBankWDI:2013a} provides the employment to population 
+ratio for people fifteen and older, total population, and a percentage 
+of people under fifteen for other economies (South Africa, China, Iran, 
+Saudi Arabia, Tanzania, and Zambia) for 1991--2011. The population 
+of people under fifteen years of age was subtracted from total population 
+to calculate the population of people fifteen and older. 
+Total employment was calculated by multiplying the employment to 
+population ratio of people fifteen and older by the population 
+of people fifteen and older.
 
@@
 
-To account for all energy input to an economy, we summed consumption data for many energy sources, including coal, oil and petroleum products, dry natural gas and natural gas plant liquids, nuclear power generation, and renewable energy sources (solar, wind, geothermal, biomass/fuel wood, and hydro).
-In the style of work by Warr and Ayres \citep{Ayres:2003ec, Ayres:2005kn, Warr:2010ht, Warr:2010ga, Warr:2012cg}, energy from human and animal muscle power was also included.
-Similar to the economic data discussed in Sections~\ref{sec:Economic_Output_Data}--\ref{sec:Labor_Data}, we generated energy data for developed countries from 1980--2011, with the exception of useful work data (1980--2000).
-For all other countries, we generated thermal energy and exergy data for 1991--2011.
+To account for all energy input to an economy, we summed consumption data 
+for many energy sources, including coal, oil and petroleum products, 
+dry natural gas and natural gas plant liquids, nuclear power generation, 
+and renewable energy sources (solar, wind, geothermal, biomass/fuel wood, 
+and hydro). In the style of work by Warr and Ayres 
+\citep{Ayres:2003ec, Ayres:2005kn, Warr:2010ht, Warr:2010ga, Warr:2012cg}, 
+energy from human and animal muscle power was also included. 
+Similar to the economic data discussed in 
+Sections~\ref{sec:Economic_Output_Data}--\ref{sec:Labor_Data}, 
+we generated energy data for developed countries from 1980--2011, 
+with the exception of useful work data (1980--2000). For all other countries, 
+we generated thermal energy and exergy data for 1991--2011. 
 Details on each energy quantifications are given in subsections below.
@@
 
-\noindent where $C_{fuel}$ is the consumption rate of the fuel (in units of short tons/year for coal, barrels/year for oil and petroleum, ft$^3$/year for dry natural gas and natural gas plant liquids, and m$^3$/year for biomass/fuel wood) and $h_{{fuel}}$ is the heat content of the fuel (in kJ/short ton for coal, kJ/barrel for oil, kJ/ft$^3$ for dry natural gas and natural gas plant liquids, and kJ/kg for biomass/fuel wood).
-Fuel wood density of 300~kg/m$^3$ was taken from \citet{Ragland:2013wp} at the low end of the range of density of dry wood and bark.
-
-Yearly consumption rates ($C_{fuel}$) of coal, oil and petroleum, dry natural gas and natural gas plant liquids, and biofuels (ethanol and biodiesel) were obtained from the \citet{EIA:2013a} for all economies.
-Yearly average heat content data for coal, oil, and natural gas and natural gas plant liquids was obtained from the EIA for all economies.
-We used lower (net) heating values of 26.8~MJ/kg \citep[Table~A-27]{Cengel:2011ww} and 37.8~MJ/kg \citep[Table~7.3]{Gupta:2010vg} for the heat content of ethanol and corn-based biodiesel, respectively.
-Yearly consumption and heat content data for biomass/fuel wood was obtained from the ``Fuelwood'' time series of the FAO Statistics Database \citep{FAO:2013a}.
-
-For renewable and nuclear energy sources, yearly electricity generation (in BTU/year) was available directly from the \citet{EIA:2013a} for all economies, so Equation~\ref{eq:thermal_energy} was unnecessary.
-
-Animal and human muscle work was estimated using an approach similar to \citet{Ayres:2010ug}, using some data from Warr's REXS database \citep{Warr:2012a} and results from \citet{Wirsenius:2000vi}.
-For animal work, our analysis was restricted to draught animals (horses and mules).
-Muscle work from animals ($Q_{animals}$) was calculated using
+\noindent where $C_{fuel}$ is the consumption rate of the fuel 
+(in units of short tons/year for coal, barrels/year for oil and petroleum, 
+ft$^3$/year for dry natural gas and natural gas plant liquids, 
+and m$^3$/year for biomass/fuel wood) and $h_{{fuel}}$ is 
+the heat content of the fuel (in kJ/short ton for coal, kJ/barrel for oil, 
+kJ/ft$^3$ for dry natural gas and natural gas plant liquids, 
+and kJ/kg for biomass/fuel wood). Fuel wood density of 300~kg/m$^3$ 
+was taken from \citet{Ragland:2013wp} at the low end of the range 
+of density of dry wood and bark.
+
+Yearly consumption rates ($C_{fuel}$) of coal, oil and petroleum, 
+dry natural gas and natural gas plant liquids, and biofuels 
+(ethanol and biodiesel) were obtained from the \citet{EIA:2013a} 
+for all economies. Yearly average heat content data for coal, oil, 
+and natural gas and natural gas plant liquids was obtained from the 
+EIA for all economies. We used lower (net) heating values of 
+26.8~MJ/kg \citep[Table~A-27]{Cengel:2011ww} and 37.8~MJ/kg 
+\citep[Table~7.3]{Gupta:2010vg} for the heat content of ethanol 
+and corn-based biodiesel, respectively. Yearly consumption and 
+heat content data for biomass/fuel wood was obtained from the 
+``Fuelwood'' time series of the FAO Statistics Database 
+\citep{FAO:2013a}.
+
+For renewable and nuclear energy sources, yearly electricity 
+generation (in BTU/year) was available directly from 
+the \citet{EIA:2013a} for all economies, so 
+Equation~\ref{eq:thermal_energy} was unnecessary.
+
+Animal and human muscle work was estimated using an approach 
+similar to \citet{Ayres:2010ug}, using some data from Warr's 
+REXS database \citep{Warr:2012a} and results from 
+\citet{Wirsenius:2000vi}. For animal work, our analysis was 
+restricted to draught animals (horses and mules). Muscle work 
+from animals ($Q_{animals}$) was calculated using
 

### 2013-06-07 EconGrowth.Rnw
Added details to the to-do note about estimating CIs.
Line shortening.

@@
       Is that still correct if we move to a different approach for 
-      estimating confidence intervals?}
+      estimating confidence intervals? See especially \texttt{cesData} 
+      and possibly other places.}
 \item{Pruim: At present, we are doing \texttt{deltaMethod} for determining CIs on 
@@
       \item{Add CES rows to the AIC table. Code is in the 
-            \texttt{createAICTable} function, but it is not yet working. Need to find a way to calculate AIC for the object that is returned from the \texttt{cesEst} function.}
+            \texttt{createAICTable} function, but it is not yet working. 
+            Need to find a way to calculate AIC for the object that is 
+            returned from the \texttt{cesEst} function.}
       \end{itemize}
-\item{Heun: Eliminate blanks in the coefficient tables for the 95\% CIs in the Cobb-Douglas with energy rows}
+\item{Heun: Eliminate blanks in the coefficient tables for the 
+      95\% CIs in the Cobb-Douglas with energy rows}
       \begin{itemize}
@@
 
-\noindent where $Q_m$ is metabolizable energy (in kcal/day-animal) and $N$ is the number of animals.
-Metabolizable energy values ($Q_{m,horses}$ = 19,110 kcal/day-horse and $Q_{m,mules}$ = 7,215 kcal/day-mule) were taken from \citet{Warr:2012a}.
-$Q_m$ represents the amount of energy in the feed consumed by animals for a day of work, and they are assumed constant for all countries and years.
-The number of horses and mules for each economy was taken from the ``Live Animals'' section of the FAO Statistics online database \citep{FAO:2013a}.
+\noindent where $Q_m$ is metabolizable energy (in kcal/day-animal) 
+and $N$ is the number of animals. Metabolizable energy values 
+($Q_{m,horses}$ = 19,110 kcal/day-horse and $Q_{m,mules}$ = 
+7,215 kcal/day-mule) were taken from \citet{Warr:2012a}. 
+$Q_m$ represents the amount of energy in the feed consumed by 
+animals for a day of work, and they are assumed constant for 
+all countries and years. The number of horses and mules for 
+each economy was taken from the ``Live Animals'' section of the 
+FAO Statistics online database \citep{FAO:2013a}.
 
@@
 
-\noindent where the value of $Q_{m,workers}$ is the ``the amount of food available for human consumption'' (i.e., at the wholesale level) taken from the \citet[``\texttt{Dietary~Energy~Cons.~Countries}'' tab]{FAO:2013b}.
-The value for $N_{workers}$ was obtained from the labor time series for each economy as discussed in Section~\ref{sec:Labor_Data}.
+\noindent where the value of $Q_{m,workers}$ is the ``the amount 
+of food available for human consumption'' (i.e., at the wholesale level) 
+taken from the 
+\citet[``\texttt{Dietary~Energy~Cons.~Countries}'' tab]{FAO:2013b}. 
+The value for $N_{workers}$ was obtained from the labor time series 
+for each economy as discussed in Section~\ref{sec:Labor_Data}.
 
@@
 
-Exergy ($X$), expressed in TJ/year, was calculated by multiplying the thermal energy ($Q$) values discussed in Section~\ref{sec:Q_Data} by a unitless exergy-to-thermal-energy allocation factor ($f_{exergy-allocation}$) shown in Table~\ref{tab:Exergy_Allocation}.
+Exergy ($X$), expressed in TJ/year, was calculated by multiplying 
+the thermal energy ($Q$) values discussed in Section~\ref{sec:Q_Data} 
+by a unitless exergy-to-thermal-energy allocation factor 
+($f_{exergy-allocation}$) shown in Table~\ref{tab:Exergy_Allocation}.
 
@@
 
-\noindent For carbon-based energy sources, $f_{exergy-allocation}$ is the ratio of chemical exergy to lower (net) heating value.
-The exergy allocation factors for coal, oil, natural gas, biodiesel, and biomass/fuel wood were obtained from \citet[Table~A-2]{Ayres:2003ec}.
-The exergy allocation ratio for liquid ethanol was calculated from the standard molar chemical exergy of 1357.7~kJ/mol \citep[Table~II]{Szargut:1988wv} and its lower (net) heating value of 26.8~MJ/kg \citep[Table~A-27]{Cengel:2011ww}.
-$f_{exergy-allocation}$ for each fuel was assumed to be constant through time across all economies.
-For nuclear, wind, solar photovoltaic, and hydro energy sources, the electricity generated is already pure exergy, so $f_{exergy-allocation}$ is unity.
-
-To calculate the exergy of animal and human muscle power, the food-to-work conversion efficiency ($\eta_{food \rightarrow work}$) and the ratio of food intake to food available at wholesale ($f_{intake/wholesale}$) were included.
+\noindent For carbon-based energy sources, $f_{exergy-allocation}$ 
+is the ratio of chemical exergy to lower (net) heating value. 
+The exergy allocation factors for coal, oil, natural gas, 
+biodiesel, and biomass/fuel wood were obtained from 
+\citet[Table~A-2]{Ayres:2003ec}. The exergy allocation ratio for 
+liquid ethanol was calculated from the standard molar chemical exergy 
+of 1357.7~kJ/mol \citep[Table~II]{Szargut:1988wv} and its lower 
+(net) heating value of 26.8~MJ/kg \citep[Table~A-27]{Cengel:2011ww}. 
+$f_{exergy-allocation}$ for each fuel was assumed to be constant 
+through time across all economies. For nuclear, wind, 
+solar photovoltaic, and hydro energy sources, the electricity generated 
+is already pure exergy, so $f_{exergy-allocation}$ is unity.
+
+To calculate the exergy of animal and human muscle power, 
+the food-to-work conversion efficiency ($\eta_{food \rightarrow work}$) 
+and the ratio of food intake to food available at wholesale 
+($f_{intake/wholesale}$) were included.
 
@@
 
-\noindent $\eta_{food \rightarrow work, animals}$ and $\eta_{food \rightarrow work, workers}$ are animal and worker efficiency of converting food into energy, respectively.
-The animal feed-to-work conversion efficiency ($\eta_{feed \rightarrow work, animals}$ = 0.4) was taken from \citet{Warr:2012a} and assumed equal across all economies.
-The food-to-work efficiency for workers ($\eta_{food \rightarrow work, workers}$ = 0.2) was taken from \citet[Table~B.1]{Ayres:2010ug}.
-Following \citet[p.~315]{Ayres:2010ug} and methodology from \citet{Warr:2012a}, an additional factor ($f_{intake/wholesale}$) was included to account for ``wastage and losses of food in the household, e.g.
-during storage, in preparation and cooking, as plate-waste, or quantities fed to domestic animals and pets'' \citep[\texttt{notes} tab]{FAO:2013b}.
-Values of $f_{intake/wholesale}$ were calculated from \citet[Table~3.3 for wholesale and Table~3.4 for intake]{Wirsenius:2000vi}.
-$f_{intake/wholesale}$ varies by country as shown in Table~\ref{tab:f_intake_wholesale}.
-A similar intake-to-wholesale ratio could also be applied to animal work, but data to calculate the ratio was unavailable from \citet{Wirsenius:2000vi}, and $f_{intake/wholesale,animals}$ is assumed to be unity.\footnote{The error in total exergy input to any economy caused by assuming $f_{intake/wholesale,animals} = 1.0$ is very small, because animal muscle exergy is a small fraction of the total exergy supply to any economy, with a maximum of 0.41\% for China in 1992.
-It could also be argued that $f_{intake/wholesale, animals}$ is likely to be closer to unity than $f_{intake/wholesale, workers}$.}
-
-\begin{table} \caption{Food intake-to-wholesale ratios ($f_{intake/wholesale}$) for all countries.} \label{tab:f_intake_wholesale}
+\noindent $\eta_{food \rightarrow work, animals}$ and 
+$\eta_{food \rightarrow work, workers}$ are animal and worker efficiency 
+of converting food into energy, respectively. The animal feed-to-work 
+conversion efficiency ($\eta_{feed \rightarrow work, animals}$ = 0.4) 
+was taken from \citet{Warr:2012a} and assumed equal across all economies. 
+The food-to-work efficiency for workers 
+($\eta_{food \rightarrow work, workers}$ = 0.2) was taken from 
+\citet[Table~B.1]{Ayres:2010ug}. Following \citet[p.~315]{Ayres:2010ug} 
+and methodology from \citet{Warr:2012a}, an additional factor 
+($f_{intake/wholesale}$) was included to account for ``wastage and 
+losses of food in the household, e.g. during storage, in preparation 
+and cooking, as plate-waste, or quantities fed to domestic animals 
+and pets'' \citep[\texttt{notes} tab]{FAO:2013b}. 
+Values of $f_{intake/wholesale}$ were calculated from 
+\citet[Table~3.3 for wholesale and Table~3.4 for intake]{Wirsenius:2000vi}. 
+$f_{intake/wholesale}$ varies by country as shown in 
+Table~\ref{tab:f_intake_wholesale}. A similar intake-to-wholesale ratio 
+could also be applied to animal work, but data to calculate the ratio was 
+unavailable from \citet{Wirsenius:2000vi}, and $f_{intake/wholesale,animals}$ 
+is assumed to be unity.\footnote{The error in total exergy input to 
+any economy caused by assuming $f_{intake/wholesale,animals} = 1.0$ 
+is very small, because animal muscle exergy is a small fraction of the 
+total exergy supply to any economy, with a maximum of 0.41\% for China in 1992. 
+It could also be argued that $f_{intake/wholesale, animals}$ is likely 
+to be closer to unity than $f_{intake/wholesale, workers}$.}
+
+\begin{table} \caption{Food intake-to-wholesale ratios 
+                        ($f_{intake/wholesale}$) for all countries.} 
+                        \label{tab:f_intake_wholesale}
   \begin{center}
@@
 
-The conversion of a raw energy carrier (e.g., coal) into productive energy for an economy (e.g., electricity) necessarily involves inefficiencies.
-In the case of coal consumption, only about one-third of the coal exergy is converted to useful electricity: the rest is waste heat.
-The concept of ``useful work,'' pioneered by Ayres and Warr \citep{Ayres:2003ec, Ayres:2005kn}, builds upon exergy analysis to consider efficiencies of both energy production and enduse.
-To calculate useful work ($U$), the total exergy input to an economy ($X$) is decomposed into several end uses: high temperature industrial heat (e.g., steel production), medium temperature heat (e.g., steam production), low temperature space heat (for residential heating), mechanical drive (energy used for prime mover engines of all types except electric motors), electricity (excluding lighting), lighting (from both electricity and fuels), and muscle work (from animals and workers) as shown in the following equation:
+The conversion of a raw energy carrier (e.g., coal) into 
+productive energy for an economy (e.g., electricity) necessarily 
+involves inefficiencies. In the case of coal consumption, 
+only about one-third of the coal exergy is converted to useful electricity: 
+the rest is waste heat. The concept of ``useful work,'' pioneered by 
+Ayres and Warr \citep{Ayres:2003ec, Ayres:2005kn}, builds upon 
+exergy analysis to consider efficiencies of both energy production and enduse. 
+To calculate useful work ($U$), the total exergy input to an 
+economy ($X$) is decomposed into several end uses: 
+high temperature industrial heat (e.g., steel production), 
+medium temperature heat (e.g., steam production), 
+low temperature space heat (for residential heating), 
+mechanical drive (energy used for prime mover engines of all types except electric motors), 
+electricity (excluding lighting), 
+lighting (from both electricity and fuels), and 
+muscle work (from animals and workers) as shown in the following equation:
 

### 2013-06-07 EconGrowth.Rnw
Line shortening.

@@
 
-\noindent where the subscript $i$ indicates the energy enduse, $\varepsilon_i$ is the efficiency of converting exergy into useful energy for each enduse, and $\phi_i$ gives the fraction of exergy input to an economy that goes toward the $i^\mathrm{th}$ enduse.
-
-Values of $\varepsilon_i$ and $\phi_i$ were calculated from the REXS database supplied by \citet{Warr:2012a}.
-Values of $X$ were calculated by methods discussed in Section~\ref{sec:X_Data}.
-For most countries, values of $\phi_i$ are not constant with time, as economic sectors with different distributions of raw exergy inputs grow at different rates.
-\citeapos{Warr:2012a} REXS database contains information for developed economies (United States, United Kingdom, and Japan) from 1900--2000, and we used data from the 1980--2000 timeframe.
-Extending the REXS database to the BRICS, petrol, and LDC economies is beyond the scope of this work, because longitudinal data for the efficiency of different end uses ($\varepsilon_i$) and the distribution of exergy sources to end uses ($\phi_i$) are extremely difficult to find.
+\noindent where the subscript $i$ indicates the energy enduse, 
+$\varepsilon_i$ is the efficiency of converting exergy into 
+useful energy for each enduse, and $\phi_i$ gives 
+the fraction of exergy input to an economy that goes toward 
+the $i^\mathrm{th}$ enduse.
+
+Values of $\varepsilon_i$ and $\phi_i$ were calculated from 
+the REXS database supplied by \citet{Warr:2012a}. 
+Values of $X$ were calculated by methods discussed in 
+Section~\ref{sec:X_Data}. For most countries, values of 
+$\phi_i$ are not constant with time, as economic sectors with 
+different distributions of raw exergy inputs grow at different rates. 
+\citeapos{Warr:2012a} REXS database contains information for 
+developed economies (United States, United Kingdom, and Japan) 
+from 1900--2000, and we used data from the 1980--2000 timeframe. 
+Extending the REXS database to the BRICS, petrol, and LDC economies 
+is beyond the scope of this work, because longitudinal data for 
+the efficiency of different end uses ($\varepsilon_i$) and 
+the distribution of exergy sources to end uses 
+($\phi_i$) are extremely difficult to obtain.
 
@@
 
-Figure~\ref{fig:Historical_Lattice_Graph} presents historical data, including indexed values for output ($y$), capital stock ($k$), labor ($l$), and the various energy quantifications ($q$, $x$, and $u$) for 1980--2011 (developed economies) and 1991--2011 (other economies).
-Factors of production track each other closely, and high covariances among these variables can be seen in Tables~\ref{tab:Covariance_US}--\ref{tab:Covariance_ZM}.
-**** Discuss the covariances in more detail after we finalize the covariances for U.
-****
+Figure~\ref{fig:Historical_Lattice_Graph} presents historical data, 
+including indexed values for 
+output ($y$), 
+capital stock ($k$), 
+labor ($l$), and 
+the various energy quantifications ($q$, $x$, and $u$) 
+for 1980--2011 (developed economies) and 1991--2011 (other economies). 
+Factors of production track each other closely, 
+and high covariances among these variables can be seen in 
+Tables~\ref{tab:Covariance_US}--\ref{tab:Covariance_ZM}. 
+**** Discuss the covariances in more detail after we 
+finalize the covariances for U. ****
 
@@
 
-Figure~\ref{fig:Historical_Lattice_Graph} indicates the importance of energy quantification for economic growth modeling.
-Thermal energy ($q$) and exergy ($x$) grow at similar rates, unless there is a significant raw energy carrier substitution in the economy (such as China's rapid increase of coal and natural gas consumption relative to petroleum since 2000).
-The growth rate of $u$ is significantly different from $q$ and $x$ for most countries, however.
-\citet{Warr:2012cg} show that from 1950-1990, useful work ($u$) grew much faster than $q$, $x$, $k$, or $l$ due to efficiency gains in the U.S.
-economy.
-The results of \citeauthor{Warr:2012cg} suggest that the time-dependent technological progress term ($A$) in the Cobb-Douglas and CES production functions (Equations~\ref{eq:CD}--\ref{eq:CESe}) may be a proxy for increasing energy efficiency in the U.S.
-economy.
+Figure~\ref{fig:Historical_Lattice_Graph} indicates the importance 
+of energy quantification for economic growth modeling. 
+Thermal energy ($q$) and exergy ($x$) grow at similar rates, 
+unless there is a significant raw energy carrier substitution in the economy 
+(such as China's rapid increase of coal and natural gas consumption 
+relative to petroleum since 2000). The growth rate of $u$ is 
+significantly different from $q$ and $x$ for most countries, however. 
+\citet{Warr:2012cg} show that from 1950-1990, useful work ($u$) 
+grew much faster than $q$, $x$, $k$, or $l$ due to efficiency gains 
+in the U.S. economy. The results of \citeauthor{Warr:2012cg} suggest 
+that the time-dependent technological progress term ($A$) 
+in the Cobb-Douglas and CES production functions 
+(Equations~\ref{eq:CD}--\ref{eq:CESe}) may be a proxy for 
+increasing energy efficiency in the U.S. economy.
 
@@
 
-Each of the economic growth models discussed in Section~\ref{sec:Prod_Func_Forms} has parameters which must be estimated for each economy (see Section~\ref{sec:Economy_Types}) and each energy quantification (see Section~\ref{sec:Quantification_of_Energy}) via least-squares methods.
-The following subsections discuss parameter estimation methods interpret the results.
+Each of the economic growth models discussed in 
+Section~\ref{sec:Prod_Func_Forms} has parameters which must be estimated 
+for each economy (see Section~\ref{sec:Economy_Types}) and 
+each energy quantification (see Section~\ref{sec:Quantification_of_Energy}) 
+via least-squares methods. The following subsections discuss 
+parameter estimation methods and interpret the results.
 
@@
 
-The Cobb-Douglas model without energy is given by Equation~\ref{eq:CD}. The Cobb-Douglas production function was reparameterized as
+The Cobb-Douglas model without energy is given by 
+Equation~\ref{eq:CD}. The Cobb-Douglas production function was 
+reparameterized as
 
@@
 **** Is this truly how we implemented the constraints? 
-Finish after we actually implement the constraints.
-**** $\lambda$ and $\alpha$ were estimated by the \citet{R} function \texttt{nls}.
+Finish after we actually implement the constraints. **** 
+$\lambda$ and $\alpha$ were estimated by the \citet{R} function \texttt{nls}. 
 The value of $\beta$ can be found with $\beta = 1 - \alpha$. 
-Figure~\ref{fig:CD_Params_Graph} shows values of and 95\% confidence intervals for $\lambda$ and $\alpha$.
-Appendix~\ref{sec:Model_Parameters} contains tables with numerical values of model parameters and confidence intervals.
+Figure~\ref{fig:CD_Params_Graph} shows values of and 95\% confidence intervals 
+for $\lambda$ and $\alpha$. Appendix~\ref{sec:Model_Parameters} 
+contains tables with numerical values of model parameters and confidence intervals.
 
@@
 
-To qualitatively assess whether augmenting the Cobb-Douglas model with energy will be beneficial, we created partial residual plots as shown in Figures~\ref{fig:CDPartialResidualsQ}--\ref{fig:CDPartialResidualsU} below.
-If a monotonic trend is observed on the graphs, we expect that energy augmentation will be beneficial.
-However, no strong monotonic tends are observed for any country, with the exception, perhaps, of the United Kingdom, whose residuals are, on average, above 0.
+To qualitatively assess whether augmenting the Cobb-Douglas model with energy 
+will be beneficial, we created partial residual plots as shown in 
+Figures~\ref{fig:CDPartialResidualsQ}--\ref{fig:CDPartialResidualsU} below. 
+If a monotonic trend is observed on the graphs, we expect that 
+energy augmentation will be beneficial. 
+However, no strong monotonic tends are observed for any country, 
+with the exception, perhaps, of the United Kingdom, whose residuals are, 
+on average, above 0.
 
@@
 
-To estimate the parameters $\lambda$, $\alpha$, $\beta$, and $\gamma$ in the energy-augmented Cobb-Douglas model, Equation~\ref{eq:CDe} was reparameterized as
+To estimate the parameters $\lambda$, $\alpha$, $\beta$, and $\gamma$ 
+in the energy-augmented Cobb-Douglas model, Equation~\ref{eq:CDe} 
+was reparameterized as
 
@@
 \noindent to ensure that $\alpha + \beta + \gamma = 1$. 
-By constraining $a \in [0,1]$ and $b \in [0,1]$, we ensure that $\alpha \in [0,1]$, $\beta \in [0,1]$, and $\gamma \in [0,1]$.
-Given values of $a$ and $b$ that represent the least-squares parameter optimization for a given economy, $\alpha = \min(a,b)$, $\beta = |b-a|$, and $\gamma = \max(a,b)$ can be calculated.
-The \citet{R} function \texttt{nls} was used to estimate the least-squares values of $\lambda$, $a$, and $b$.
+By constraining $a \in [0,1]$ and $b \in [0,1]$, 
+we ensure that $\alpha \in [0,1]$, $\beta \in [0,1]$, and $\gamma \in [0,1]$. 
+Given values of $a$ and $b$ that represent the least-squares parameter 
+optimization for a given economy, 
+$\alpha = \min(a,b)$, 
+$\beta = |b-a|$, and 
+$\gamma = \max(a,b)$ 
+can be calculated. 
+The \citet{R} function \texttt{nls} was used to estimate the 
+least-squares values of $\lambda$, $a$, and $b$.
 
 The Cobb-Douglas with energy parameter estimation process is challenging. 
-To demonstrate the characteristics of the parameter estimation process, we performed a grid search over values of $\gamma$, wherein we re-estimated values of $\lambda$, $\alpha$, and $\beta$ at each value of $\gamma$.
-Figure~\ref{fig:CDeGridLattice} shows the sum of squared errors ($SSE$), $\alpha$, and $\beta$ as a function of the fixed value of $\gamma$ with thermal energy ($q$).
-For most economies, the minimum $SSE$ occurs at a boundary of $\alpha$, $\beta$, or $\gamma$.
-The parameter estimation algorithm has difficulty assessing confidence intervals for $\alpha$, $\beta$, and $\gamma$, because the constrained model behaves very differently on either side of the constraint.
-
-**** Fix the right y axis label. SSE should be italicized. Also, scaling on the axis labels and scales is not being picked up. ****
+To demonstrate the characteristics of the parameter estimation process, 
+we performed a grid search over values of $\gamma$, 
+wherein we re-estimated values of $\lambda$, $\alpha$, and 
+$\beta$ at each value of $\gamma$. 
+Figure~\ref{fig:CDeGridLattice} shows the sum of squared errors ($SSE$), 
+$\alpha$, and $\beta$ as a function of the fixed value of 
+$\gamma$ with thermal energy ($q$). 
+For most economies, the minimum $SSE$ occurs at a boundary of $\alpha$, 
+$\beta$, or $\gamma$. 
+The parameter estimation algorithm has difficulty assessing confidence 
+intervals for $\alpha$, $\beta$, and $\gamma$, because the constrained 
+model behaves very differently on either side of the constraint.
+
+**** Fix the right y axis label. SSE should be italicized. 
+Also, scaling on the axis labels and scales is not being picked up. ****
 
@@
 
-Figure~\ref{fig:CDq_Params_Graph} shows values and 95\% confidence intervals for the parameters for the Cobb-Douglas model (with $q$).
+Figure~\ref{fig:CDq_Params_Graph} shows values and 95\% confidence intervals 
+for the parameters for the Cobb-Douglas model (with $q$).
 
@@
 
-The Cobb-Douglas (with exergy) parameters are given in Table~\ref{tab:CD_Parameters_With_X}.
-
-Figure~\ref{fig:CDx_Params_Graph} shows values and 95\% confidence intervals for the parameters for the Cobb-Douglas model (with $x$).
+The Cobb-Douglas (with exergy) parameters are given in 
+Table~\ref{tab:CD_Parameters_With_X}.
+
+Figure~\ref{fig:CDx_Params_Graph} shows values and 95\% confidence intervals 
+for the parameters for the Cobb-Douglas model (with $x$).
 
@@
 
-Figure~\ref{fig:CDu_Params_Graph} shows values and 95\% confidence intervals for the parameters for the Cobb-Douglas model (with $u$).
+Figure~\ref{fig:CDu_Params_Graph} shows values and 95\% confidence intervals 
+for the parameters for the Cobb-Douglas model (with $u$).
 
@@
 
-Figure~\ref{fig:CD_GDP_Lattice_Graph} compares predictions from the Cobb-Douglas models (without energy, with $e=q$, with $e=x$, and with $e=u$) to historical data.
+Figure~\ref{fig:CD_GDP_Lattice_Graph} compares predictions 
+from the Cobb-Douglas models 
+(without energy, with $e=q$, with $e=x$, and with $e=u$) to historical data.
 
@@
 
-The CES model without and with energy is given by Equations~\ref{eq:CES} and \ref{eq:CESe}, respectively.
-The \texttt{R} \citep{R} package \texttt{micEconCES} \citep{Henningsen:2011td} was used to estimate parameters $\gamma$, $\lambda$, $\delta_1$, $\rho_1$, $\delta$, and $\rho$.
+The CES model without and with energy is given by 
+Equations~\ref{eq:CES} and \ref{eq:CESe}, respectively. 
+The \texttt{R} \citep{R} package \texttt{micEconCES} 
+\citep{Henningsen:2011td} was used to estimate parameters 
+$\gamma$, $\lambda$, $\delta_1$, $\rho_1$, $\delta$, and $\rho$. 
 **** More details here about which algorithms were used, etc. 
-Complete after our work this summer.
-**** Elasticities of substitution $\sigma_1$ and $\sigma$ (see Section~\ref{sec:CES}) were estimated by the delta method (**** is this correct?
-Ask Pruim.
-****).
-
-% \citet{Henningsen:2011td}, in their detailed analysis of \citet{Kemfert:1998vd}, found that 
+Complete after our work this summer. **** 
+Elasticities of substitution $\sigma_1$ and $\sigma$ 
+(see Section~\ref{sec:CES}) were estimated by the delta method 
+(**** is this correct? Ask Pruim. ****).
+
+% \citet{Henningsen:2011td}, in their detailed analysis of 
+% \citet{Kemfert:1998vd}, found that 
 % 
 % \begin{quote}
-% \ldots the Levenberg-Marquardt and the PORT algorithms are---at least in this study---most likely to find the coefficients that give the best fit to the model, where the PORT algorithm can be used to restrict the estimates to the economically meaningful region.
+% \ldots the Levenberg-Marquardt and the PORT algorithms 
+% are---at least in this study---most likely to find the 
+% coefficients that give the best fit to the model, 
+% where the PORT algorithm can be used to restrict the estimates 
+% to the economically meaningful region.
 % \end{quote}
 
-Figure~\ref{fig:CES_Params_Graph} shows values and 95\% confidence intervals for the parameters for the CES model (without energy).
+Figure~\ref{fig:CES_Params_Graph} shows values and 95\% confidence intervals 
+for the parameters for the CES model (without energy).
 
@@
 
-Similar to the analysis of the Cobb-Douglas model in Section~\ref{sec:CD_Parameter_Estimation}, we make partial residual plots for the CES model (without energy) in Figures~\ref{fig:CESPartialResidualsQ}--\ref{fig:CESPartialResidualsU} below.
-Again, no strong monotonic trend is observed, suggesting the energy-augmentation of the CES model will not significantly improve the model.
+Similar to the analysis of the Cobb-Douglas model in 
+Section~\ref{sec:CD_Parameter_Estimation}, 
+we make partial residual plots for the CES model (without energy) in 
+Figures~\ref{fig:CESPartialResidualsQ}--\ref{fig:CESPartialResidualsU} below. 
+Again, no strong monotonic trend is observed, suggesting the 
+energy-augmentation of the CES model will not significantly improve the model.
 
@@
 
-Figure~\ref{fig:CESq_Params_Graph} shows values and 95\% confidence intervals for the parameters for the CES model (with $q$).
+Figure~\ref{fig:CESq_Params_Graph} shows values and 95\% confidence intervals 
+for the parameters for the CES model (with $q$).
 
@@
 
-Figure~\ref{fig:CESx_Params_Graph} shows values and 95\% confidence intervals for the parameters for the CES model (with $x$).
+Figure~\ref{fig:CESx_Params_Graph} shows values and 95\% confidence intervals 
+for the parameters for the CES model (with $x$).
 
@@
 
-Figure~\ref{fig:CESu_Params_Graph} shows values and 95\% confidence intervals for the parameters for the CES model (with $u$).
+Figure~\ref{fig:CESu_Params_Graph} shows values and 95\% confidence intervals 
+for the parameters for the CES model (with $u$).
 
@@
 
-Figure~\ref{fig:CES_GDP_Lattice_Graph} compares CES model predictions to historical data.
+Figure~\ref{fig:CES_GDP_Lattice_Graph} compares CES model predictions 
+to historical data.
 
@@
 
-The key energy parameters for the Cobb-Douglas and CES models are $\gamma$, $\delta$, and $\sigma$.
-The parameter $\gamma$ in the Cobb-Douglas model (Equation~\ref{eq:CDe}) indicates the importance of energy for economic growth.
-When $\gamma \rightarrow 0$, energy is not a significant contributor to economic growth for an economy.
-Conversely, when $\gamma \rightarrow 1$, energy is the primary contributor to economic growth.
-However, if the 95\% confidence interval for $\gamma$ for any given economy extends to 0.0, we cannot say with high confidence whether or not energy makes a meaningful contribution to economic growth for that economy.
-On a graph of the width of the 95\% confidence interval for $\gamma$ ($CI_{95\%,\gamma}$) vs.
-$\gamma$, where each economy is represented by a point (its two-letter abbreviation; see Table~\ref{tab:Economy_Examples}), the locus of points where the 95\% confidence interval for $\gamma$ crosses 0 is a diagonal line.
-If the combination of $\gamma$ and its confidence interval for a given economy is below and to the right of the line, we have high confidence that we can say whether or not energy is a significant contributor to economic growth.
-Thus, only when $\gamma$ is below the line and small (i.e., close to 0) for an economy, can we say with confidence that energy is an insignificant contributor to economic growth.
-Only when $\gamma$ is below the line and large (i.e., close to 1) for an economy can we say that energy is a significant contributor to economic growth, according to the Cobb-Douglas model.
-
-The left column of graphs in Figure~\ref{fig:CIvsParam_Lattice_Graph} shows $CI_{95\%,\gamma}$ vs.
-$\gamma$ for the three quantifications of energy (thermal energy, $q$, exergy, $x$, and useful work, $u$).
-We note that most economies are above and to the left of the line, while only a few are below and to the right.
-
-For the CES model (Equation~\ref{eq:CESe}), the parameter $\delta$ indicates the importance of energy for economic growth.
-When $\delta \rightarrow 1$, energy is an insignificant contributor to economic growth, and when $\delta \rightarrow 0$, energy is the primary contributor to economic growth for an economy.
-However, if the 95\% confidence interval for $\delta$ extends to 1, we cannot say with high confidence whether or not energy makes a meaningful contribution to economic growth for that economy.
-In a manner similar to $\gamma$ for the Cobb-Douglas model, we note that if the combination of $\delta$ and its confidence interval for a given economy is below and to the left of the line, we have high confidence that we can say whether or not energy is a significant contributor to economic growth.
-Thus, only when $\delta$ is below the line and large (i.e., close to 1) for an economy, can we say with confidence that energy is an insignificant contributor to economic growth.
-Only when $\delta$ is below the line and small (i.e., close to 0) for an economy can we say that energy is a significant contributor to economic growth, according to the CES model.
-
-The middle column of graphs in Figure~\ref{fig:CIvsParam_Lattice_Graph} shows $CI_{95\%,\delta}$ vs.
-$\delta$ for the three quantifications of energy (thermal energy, $q$, exergy, $x$, and useful work, $u$).
-We note that most economies are above and to the right of the line, while only a few are below and to the left.
-
-For the CES model (Equation~\ref{eq:CESe}), the parameter $\sigma$ indicates whether capital stock and labor ($kl$) and energy ($e$) are complements ($\sigma <$ 1) or substitutes ($\sigma >$ 1).
-For countries whose combination of  $\sigma$ and its confidence interval is below and to the left of the lines in the rightmost graphs of Figure~\ref{fig:CIvsParam_Lattice_Graph} we can say (with 95\% confidence) that ($kl$) and ($e$) are complements.
-For economies whose value of $\sigma$ is below and to the right of the line, we can say (with 95\% confidence) that ($kl$) and ($e$) are substitutes.
-For economies whose value of $\sigma$ is above those lines, we cannot say with 95\% confidence whether ($kl$) and ($e$) are substitues or complements.
-
-The right column of graphs in Figure~\ref{fig:CIvsParam_Lattice_Graph} shows $CI_{95\%,\sigma}$ vs.
-$\sigma$ for the three quantifications of energy (thermal energy, $q$, exergy, $x$, and useful work, $u$).
-We note that energy ($e$) unambiguously complements capital stock and labor ($kl$) for most economies.
+The key energy parameters for the Cobb-Douglas and CES models are 
+$\gamma$, $\delta$, and $\sigma$. 
+The parameter $\gamma$ in the Cobb-Douglas model (Equation~\ref{eq:CDe}) 
+indicates the importance of energy for economic growth. 
+When $\gamma \rightarrow 0$, energy is not a significant contributor 
+to economic growth for an economy. 
+Conversely, when $\gamma \rightarrow 1$, energy is the primary contributor 
+to economic growth. 
+However, if the 95\% confidence interval for $\gamma$ for any given economy 
+extends to 0.0, we cannot say with high confidence whether or not energy 
+makes a meaningful contribution to economic growth for that economy. 
+On a graph of the width of the 95\% confidence interval for 
+$\gamma$ ($CI_{95\%,\gamma}$) vs. $\gamma$, where each economy is represented 
+by a point (its two-letter abbreviation; see Table~\ref{tab:Economy_Examples}), 
+the locus of points where the 95\% confidence interval for 
+$\gamma$ crosses 0 is a diagonal line. 
+If the combination of $\gamma$ and its confidence interval 
+for a given economy is below and to the right of the line, 
+we have high confidence that we can say whether or not energy 
+is a significant contributor to economic growth. 
+Thus, only when $\gamma$ is below the line and small (i.e., close to 0) 
+for an economy, can we say with confidence that energy is 
+an insignificant contributor to economic growth. 
+Only when $\gamma$ is below the line and large (i.e., close to 1) 
+for an economy can we say that energy is a significant contributor 
+to economic growth, according to the Cobb-Douglas model.
+
+The left column of graphs in Figure~\ref{fig:CIvsParam_Lattice_Graph} shows 
+$CI_{95\%,\gamma}$ vs. $\gamma$ for the three quantifications of energy 
+(thermal energy, $q$, exergy, $x$, and useful work, $u$). 
+We note that most economies are above and to the left of the line, 
+while only a few are below and to the right.
+
+For the CES model (Equation~\ref{eq:CESe}), the parameter $\delta$ 
+indicates the importance of energy for economic growth. 
+When $\delta \rightarrow 1$, energy is an insignificant contributor 
+to economic growth, and when $\delta \rightarrow 0$, 
+energy is the primary contributor to economic growth for an economy. 
+However, if the 95\% confidence interval for $\delta$ extends to 1, 
+we cannot say with high confidence whether or not energy makes 
+a meaningful contribution to economic growth for that economy. 
+In a manner similar to $\gamma$ for the Cobb-Douglas model, 
+we note that if the combination of $\delta$ and its confidence interval 
+for a given economy is below and to the left of the line, 
+we have high confidence that we can say whether or not energy is 
+a significant contributor to economic growth. 
+Thus, only when $\delta$ is below the line and large (i.e., close to 1) 
+for an economy, can we say with confidence that energy is 
+an insignificant contributor to economic growth. 
+Only when $\delta$ is below the line and small (i.e., close to 0) 
+for an economy can we say that energy is a significant contributor 
+to economic growth, according to the CES model.
+
+The middle column of graphs in Figure~\ref{fig:CIvsParam_Lattice_Graph} shows 
+$CI_{95\%,\delta}$ vs. $\delta$ for the three quantifications of energy 
+(thermal energy, $q$, exergy, $x$, and useful work, $u$). 
+We note that most economies are above and to the right of the line, 
+while only a few are below and to the left.
+
+For the CES model (Equation~\ref{eq:CESe}), the parameter $\sigma$ indicates 
+whether capital stock and labor ($kl$) and energy ($e$) are 
+complements ($\sigma <$ 1) or substitutes ($\sigma >$ 1). 
+For countries whose combination of  $\sigma$ and its confidence interval is 
+below and to the left of the lines in the rightmost graphs 
+of Figure~\ref{fig:CIvsParam_Lattice_Graph} we can say (with 95\% confidence) 
+that ($kl$) and ($e$) are complements. 
+For economies whose value of $\sigma$ is below and to the right of the line, 
+we can say (with 95\% confidence) that ($kl$) and ($e$) are substitutes. 
+For economies whose value of $\sigma$ is above those lines, 
+we cannot say with 95\% confidence whether ($kl$) and ($e$) are substitues or complements.
+
+The right column of graphs in Figure~\ref{fig:CIvsParam_Lattice_Graph} shows 
+$CI_{95\%,\sigma}$ vs. $\sigma$ for the three quantifications of energy 
+(thermal energy, $q$, exergy, $x$, and useful work, $u$). 
+We note that energy ($e$) unambiguously complements 
+capital stock and labor ($kl$) for most economies.
 
@@
 
-Regardless of model (Cobb-Douglas or CES) or energy quantification ($q$, $x$, or $u$), there are few economies for which we can say with high confidence (at the 95\% level) that energy plays a significant role in economic growth.
-However, in seeming contradiction, results for the CES model indicate that energy complements capital stock and labor, indicating that energy ($e$) is essential for capital stock ($k$) and labor ($l$) to generate economic growth.
-One possible explanation for this apparent contradiction is to consider energy as embedded within capital stock and labor: it takes energy to make both captial stock and labor available to generate economic growth.
+Regardless of model (Cobb-Douglas or CES) or energy quantification 
+($q$, $x$, or $u$), there are few economies for which we can say 
+with high confidence (at the 95\% level) that energy plays 
+a significant role in economic growth. 
+However, in seeming contradiction, results for the CES model indicate 
+that energy complements capital stock and labor, 
+indicating that energy ($e$) is essential for capital stock ($k$) and 
+labor ($l$) to generate economic growth. 
+One possible explanation for this apparent contradiction is 
+to consider energy as embedded within capital stock and labor: 
+it takes energy to make both captial stock and labor available to generate economic growth.
 
@@
 The LINEX model is given in Equation~\ref{eq:LINEX}. 
-Parameters $a_0$ and $c_t$ were estimated using the \texttt{nls} function in \texttt{R} \citep{R}.
-Figure~\ref{fig:LINEXq_Params_Graph} shows values and 95\% confidence intervals for the parameters for the LINEX model (with $q$).
+Parameters $a_0$ and $c_t$ were estimated using the \texttt{nls} function 
+in \texttt{R} \citep{R}. 
+Figure~\ref{fig:LINEXq_Params_Graph} shows values and 95\% confidence intervals 
+for the parameters for the LINEX model (with $q$).
 
@@
 
-Figure~\ref{fig:LINEXx_Params_Graph} shows values and 95\% confidence intervals for the parameters for the LINEX model (with $x$).
+Figure~\ref{fig:LINEXx_Params_Graph} shows values and 
+95\% confidence intervals for the parameters for the LINEX model (with $x$).
 
@@
 
-Figure~\ref{fig:LINEXu_Params_Graph} shows values and 95\% confidence intervals for the parameters for the LINEX model (with $u$).
+Figure~\ref{fig:LINEXu_Params_Graph} shows values and 
+95\% confidence intervals for the parameters for the LINEX model (with $u$).
 
@@
 
-**** This section needs to be re-evaluated after the statistical work is tightened up during Summer 2013. ****
+**** This section needs to be re-evaluated after the statistical work is 
+tightened up during Summer 2013. ****
 
@@
 \begin{itemize}
-  \item{The use of chemical exergy, as opposed to thermal energy, in economic growth models is probably unnecessary.
-Table~\ref{tab:Exergy_Allocation} shows that exergy allocation factors are all close to unity.
-Therefore, there is a small difference in absolute magnitude between $Q$ and $X$.
-However, there is no difference in indexed magnitude between $q$ and $x$, unless there are large changes in energy mix for an economy.
-Figure~\ref{fig:Historical_Lattice_Graph} shows that $q$ and $x$ lines lie atop one another for almost every economy.}
-  \item{The concept of useful work ($u$) is potentially useful and should be explored beyond developed economies.
-Figure~\ref{fig:Historical_Lattice_Graph} shows that $u$ grows at very different rates from thermal energy ($q$) or exergy ($x$).
+  \item{The use of chemical exergy, as opposed to thermal energy, 
+        in economic growth models is probably unnecessary. 
+        Table~\ref{tab:Exergy_Allocation} shows that exergy allocation factors are 
+        all close to unity. 
+        Therefore, there is a small difference in absolute magnitude 
+        between $Q$ and $X$. 
+        However, there is no difference in indexed magnitude 
+        between $q$ and $x$, unless there are large changes 
+        in energy mix for an economy. 
+        Figure~\ref{fig:Historical_Lattice_Graph} shows that 
+        $q$ and $x$ lines lie atop one another for almost every economy.}
+  \item{The concept of useful work ($u$) is potentially useful and 
+        should be explored beyond developed economies. 
+        Figure~\ref{fig:Historical_Lattice_Graph} shows that $u$ grows 
+        at very different rates from thermal energy ($q$) or exergy ($x$). 
         Useful work may contain different information from thermal energy and exergy.}
-  \item{Figure~\ref{fig:CDeGridLattice} shows that the set of parameters ($\lambda$, $\alpha$, $\beta$, and $\gamma$) that minimizes $SSE$ for the energy-augmented Cobb-Douglas production function always (with the exception of Saudi Arabia) has $\beta = 0$ or $\gamma = 0$.
-This result implies that it is unnecessary to include both labor ($l$) and energy ($e$) in the Cobb-Douglas production function.}
-  \item{Partial residual plots for both the Cobb-Douglas model (Figures~\ref{fig:CDPartialResidualsQ}--\ref{fig:CDPartialResidualsU} and CES model (Figures~\ref{fig:CESPartialResidualsQ}--\ref{fig:CESPartialResidualsU}) indicate that augmenting the Cobb-Douglas and CES production functions with energy is not beneficial.}
-  \item{Figure~\ref{fig:CIvsParam_Lattice_Graph} shows that important energy parameters for both the energy-augmented Cobb-Douglas and CES production functions ($\gamma$ and $\delta$, respectively) have large confidence intervals such that we are unable to say (at the 95\% confidence level) that energy is an important factor for economic growth, vis-\`{a}-vis capital stock ($k$) or labor ($l$) for most economies.}
-  \item{Figure~\ref{fig:CIvsParam_Lattice_Graph} indicates that energy (in all quantifications: $q$, $x$, and $u$) is complementary to capital stock ($k$) and labor ($l$) for producing economic growth, according to the CES model.}
-  \item{Figures~\ref{fig:LINEXq_Params_Graph}--\ref{fig:LINEXu_Params_Graph} indicate that LINEX model fitting parameters $a_0$ and $c_t$ are significant (at the 95\% confidence level) for nearly all countries.
-Figure~\ref{fig:LINEX_GDP_Lattice_Graph} shows that the LINEX production function provides reasonably good fits to historical data.
-This evidence indicates that the LINEX production function (with energy ($e$) as its only factor of production) is a reasonable replacement the Cobb-Douglas and CES production functions which have capital stock ($k$) and labor ($l$) as factors of production.}
+  \item{Figure~\ref{fig:CDeGridLattice} shows that the set 
+        of parameters ($\lambda$, $\alpha$, $\beta$, and $\gamma$) that 
+        minimizes $SSE$ for the energy-augmented Cobb-Douglas production function 
+        always (with the exception of Saudi Arabia) has 
+        $\beta = 0$ or $\gamma = 0$. 
+        This result implies that it is unnecessary to include both labor ($l$) 
+        and energy ($e$) in the Cobb-Douglas production function.}
+  \item{Partial residual plots for both the Cobb-Douglas model 
+        (Figures~\ref{fig:CDPartialResidualsQ}--\ref{fig:CDPartialResidualsU} and 
+        CES model (Figures~\ref{fig:CESPartialResidualsQ}--\ref{fig:CESPartialResidualsU}) 
+        indicate that augmenting the Cobb-Douglas and CES production functions 
+        with energy is not beneficial.}
+  \item{Figure~\ref{fig:CIvsParam_Lattice_Graph} shows that important energy parameters 
+        for both the energy-augmented Cobb-Douglas and CES production functions 
+        ($\gamma$ and $\delta$, respectively) have large confidence intervals such that 
+        we are unable to say (at the 95\% confidence level) that energy is 
+        an important factor for economic growth, 
+        vis-\`{a}-vis capital stock ($k$) or labor ($l$) for most economies.}
+  \item{Figure~\ref{fig:CIvsParam_Lattice_Graph} indicates that 
+        energy (in all quantifications: $q$, $x$, and $u$) is complementary 
+        to capital stock ($k$) and labor ($l$) for producing economic growth, 
+        according to the CES model.}
+  \item{Figures~\ref{fig:LINEXq_Params_Graph}--\ref{fig:LINEXu_Params_Graph} 
+        indicate that LINEX model fitting parameters $a_0$ and $c_t$ are 
+        significant (at the 95\% confidence level) for nearly all countries. 
+        Figure~\ref{fig:LINEX_GDP_Lattice_Graph} shows that 
+        the LINEX production function provides reasonably good fits 
+        to historical data. 
+        This evidence indicates that the LINEX production function 
+        (with energy ($e$) as its only factor of production) is 
+        a reasonable replacement for the Cobb-Douglas and CES production functions 
+        which have capital stock ($k$) and labor ($l$) as factors of production.}
   \item{**** Discuss the AIC values for each of the model types. 
-It could happen that the LINEX models have a higher AIC value than the CD or CES models.
-If so, that would mean that the LINEX model is actually preferred to the CD or CES models, primarily because it does a good-enough job of predicting economic output with fewer adjustable parameters (2) compared to CD (2), CDe (3), CES (4), CESe (6).
-Discuss with Randy Pruim during Summer 2013.}
+        It could happen that the LINEX models have a higher AIC value than 
+        the CD or CES models. 
+        If so, that would mean that the LINEX model is actually preferred 
+        to the CD or CES models, primarily because it does a good-enough job 
+        of predicting economic output with fewer adjustable parameters (2) 
+        compared to CD (2), CDe (3), CES (4), CESe (6). 
+        Discuss with Randy Pruim during Summer 2013. ****}
 \end{itemize}
 
-The evidence above leads to a re-conceptualization of the relationships among energy, capital stock, and labor: energy is \emph{embedded within} capital stock and labor, and, therefore, it is both unwarranted and unnecessary to include \emph{both} energy ($e$) and the capital stock/labor pair ($kl$) in a production function.
-The empirical evidence indicates that \emph{both} (a) capital stock/labor production functions (Cobb-Douglas and CES without energy) and (b) an energy-only production function (LINEX) provide a reasonable models for economic growth.
+The evidence above leads to a re-conceptualization of the relationships 
+among energy, capital stock, and labor: energy is \emph{embedded within} 
+capital stock and labor, and, therefore, it is both 
+unwarranted and unnecessary to include \emph{both} energy ($e$) 
+and the capital stock/labor pair ($kl$) in a production function. 
+The empirical evidence indicates that \emph{both} 
+(a) capital stock/labor production functions (Cobb-Douglas and CES without energy) and 
+(b) an energy-only production function (LINEX) provide a reasonable models for economic growth.
 
@@
 
-We claim that statistical properties (e.g., covariances) of historical economic data and statistical properties (e.g., confidence intervals) of production function fitting parameters are extremely useful for interpreting historical economic data and growth model results.
-We know of no previous studies on the role of energy in the economy that presented these statistical properties, and we presume that energy-augmentation of production functions has been done in the literature without regard to whether it is statistically meaningful to do so.
-That different authors can find good correlation between model predictions and historical data with very different growth model coefficients is a result of the heretofore unseen large confidence intervals on the fitting parameters.
-As a consequence, economic growth models that assume very different relationships among capital stock, labor, and energy can all be successful in matching historical data.
-In short, the production function is a canvas upon which investigators can paint their preconceived vision of the importance (or not) of energy for economic growth.
-
-To break free from this problem, a new way of conceptualizing the relationships among capital stock, labor, and energy is required.
-Our analysis above indicates that energy is unequivocally complementary to the capital stock/labor pair for many types of economies.
-We agree with K\"{u}mmel that energy is required to form and maintain capital stock, and that energy is required to sustain labor.
-(And, for that matter, we agree that labor is required to operate capital stock.) In other words, energy is already, always \emph{embedded within} capital stock and labor.
-We posit that the complementarity between ($kl$) and ($e$) shown by the energy-augmented CES production function is due to the embeddedness of energy within the traditional factors of production, capital stock and labor.
-
-The foregoing discussion means that production functions with either (a) energy only (such as the LINEX model) or (b) capital stock/labor only (such as the Cobb-Douglas and CES models without energy) can both be successful in predicting economic growth.
-But, the embedded nature of energy in capital stock and labor means that augmenting a capital stock/labor only production function with energy is redundant and unnecessary, and, therefore, unwarranted.
+We claim that statistical properties (e.g., covariances) 
+of historical economic data and statistical properties 
+(e.g., confidence intervals) of production function fitting parameters are 
+extremely useful for interpreting historical economic data and growth model results. 
+We know of no previous studies on the role of energy in the economy that 
+presented these statistical properties, 
+and we presume that energy-augmentation of production functions has been done 
+in the literature without regard to whether it is statistically meaningful to do so. 
+That different authors can find good correlation 
+between model predictions and historical data 
+with very different growth model coefficients is 
+a result of the heretofore unseen large confidence intervals 
+on the fitting parameters. 
+As a consequence, economic growth models that assume very different relationships 
+among capital stock, labor, and energy can all be successful in matching historical data. 
+In short, the production function becomes a canvas upon which 
+investigators can paint their preconceived vision of the importance 
+(or not) of energy for economic growth.
+
+To break free from this problem, a new way of conceptualizing 
+the relationships among capital stock, labor, and energy is required. 
+Our analysis above indicates that energy is unequivocally complementary 
+to the capital stock/labor pair for many types of economies. 
+We agree with K\"{u}mmel that energy is required 
+to form and maintain capital stock, and that energy is required to sustain labor. 
+(And, for that matter, we agree that labor is required to operate capital stock.) 
+In other words, energy is already, always \emph{embedded within} capital stock and labor. 
+We posit that the complementarity between ($kl$) and ($e$) shown 
+by the energy-augmented CES production function is due 
+to the embeddedness of energy within the traditional factors of production, 
+capital stock and labor.
+
+The foregoing discussion means that production functions with either 
+(a) energy only (such as the LINEX model) or 
+(b) capital stock/labor only (such as the Cobb-Douglas and CES models without energy) 
+can both be successful in predicting economic growth. 
+But, the embedded nature of energy in capital stock and labor means that 
+augmenting a capital stock/labor only production function 
+with energy is redundant and unnecessary, and, therefore, unwarranted.
 
@@
 
-Funding for Caleb Reese and Lucas Timmer was provided by the Jack and Lois Kuipers Applied Mathematics Endowment and the Calvin College Alumni Association.
-Partial support for Matthew Kuperus Heun was provided by a Calvin College Research Followship.
-Partial funding for Martin de Wit was provided by the South African National Research Foundation (NRF).\footnote{Any opinion, findings, and conclusions or recommendations expressed herein are those of the authors, and, therefore, NRF does not accept any liability in regard thereto.} The authors are grateful to Benjamin S.
-Warr (INSEAD) for providing the REXS database \citep{Warr:2012a}.
-The authors thank Loren L.
-Heun (Western Michigan University) for insightful critique of the statistical analyses presented herein.
+Funding for Caleb Reese and Lucas Timmer was provided 
+by the Jack and Lois Kuipers Applied Mathematics Endowment and 
+the Calvin College Alumni Association. 
+Partial support for Matthew Kuperus Heun was 
+provided by a Calvin College Research Followship. 
+Partial funding for Martin de Wit was provided 
+by the South African National Research Foundation (NRF).\footnote{Any opinion, 
+findings, and conclusions or recommendations expressed herein are those 
+of the authors, and, therefore, NRF does not accept any liability in regard thereto.} 
+The authors are grateful to Benjamin S. Warr (INSEAD) for providing 
+the REXS database \citep{Warr:2012a}. 
+The authors thank Loren L. Heun (Western Michigan University) 
+for insightful critique of the statistical analyses presented herein.
 
@@
 
-In the spirit of Reproducible Research \citep{Gandrud:2013vx}, all data, spreadsheets, \texttt{R} code \citep{R}, and other materials associated with this paper can be found at\\*
+In the spirit of Reproducible Research \citep{Gandrud:2013vx}, 
+all data, spreadsheets, \texttt{R} code \citep{R}, and other materials 
+associated with this paper can be found at\\*
 \protect\url{https://github.com/MatthewHeun/Econ-Growth-R-Analysis}.
@@
 
-The following tables show covariances among GDP ($y$) and factors of production ($k$, $l$, $q$, $x$, and $u$). Covariances are calculated for the following years: 
+The following tables show covariances among GDP ($y$) and 
+factors of production ($k$, $l$, $q$, $x$, and $u$). 
+Covariances are calculated for the following years: 
 \begin{itemize}
-  \item{1980-2011 for covariances among $y$, $k$, $l$, $q$, and $x$ for developed\\*economies;}
-  \item{1980-2000 for covariances involving $u$ for developed economies; and}
-  \item{1991-2011 for covariances among $y$, $k$, $l$, $q$, and $x$ for developing\\*economies.}
+  \item{1980-2011 for covariances among 
+        $y$, $k$, $l$, $q$, and $x$ for developed\\*economies;}
+  \item{1980-2000 for covariances involving 
+        $u$ for developed economies; and}
+  \item{1991-2011 for covariances among 
+        $y$, $k$, $l$, $q$, and $x$ for developing\\*economies.}
 \end{itemize}
@@
 #lapply(countryAbbrevs, printCovarTable)
-printCovarTable(countryAbbrev="US"); printCovarTable(countryAbbrev="UK"); printCovarTable(countryAbbrev="JP")
+printCovarTable(countryAbbrev="US"); printCovarTable(countryAbbrev="UK")
+printCovarTable(countryAbbrev="JP")
 printCovarTable(countryAbbrev="CN"); printCovarTable(countryAbbrev="ZA")
@@
 
-**** This subsection should be either (a) deleted or (b) moved into the main body of the paper.
-I would prefer to delete it on the grounds that single-factor models are not often used in the literature.
+**** This subsection should be either 
+(a) deleted or 
+(b) moved into the main body of the paper. 
+I would prefer to delete it on the grounds that single-factor models are 
+not often used in the literature. 
 However, I want to talk with Martin about this before making the decision. 
-So, I'm parking it here for now.
---Matt.
-****
+So, I'm parking it here for now. --Matt. ****
 
@@
 
-The following tables provide results for parameters in Cobb-Douglas models with and without energy terms.
+The following tables provide results for parameters 
+in Cobb-Douglas models with and without energy terms.
 
@@
 
-The following tables provide results for parameters in CES models with and without energy terms.
+The following tables provide results for parameters 
+in CES models with and without energy terms.
 
@@
 
-The following tables provide results for parameters in LINEX models.
+The following tables provide results for parameters 
+in LINEX models.
 
@@
 AIC values for all models and all countries are shown in Table~\ref{tab:AICTable}. 
-Increasing goodness of fit is indicated by smaller (i.e., more negative) AIC values.
-AIC values can be compared per data set (i.e., per country) but not across data sets (i.e., not across countries).
+Increasing goodness of fit is indicated by smaller 
+(i.e., more negative) AIC values. 
+AIC values can be compared per data set (i.e., per country) but 
+not across data sets (i.e., not across countries).
 
@@
 
-**** This section should be either (a) deleted or (b) moved into the main body of the paper.
-I would prefer to delete it on the grounds that single-factor models are not often used in the literature.
+**** This section should be either 
+(a) deleted or 
+(b) moved into the main body of the paper. 
+I would prefer to delete it on the grounds that single-factor models are 
+not often used in the literature. 
 However, I want to talk with Martin about this before making the decision.  
-So, I'm parking it here for now.
---Matt.
-****
+So, I'm parking it here for now. --Matt. ****
 
@@
 
-\noindent to historical data where the factor of production ($f$) is one of $k$, $l$, $q$, $x$, or $u$, and the exponent ($m$) is $\alpha$ for $k$, $\beta$ for $l$, or $\gamma$ for $q$, $x$, and $u$.
+\noindent to historical data where the factor of production ($f$) is 
+one of $k$, $l$, $q$, $x$, or $u$, and 
+the exponent ($m$) is $\alpha$ for $k$, $\beta$ for $l$, 
+or $\gamma$ for $q$, $x$, and $u$.
 
@@
 
-Figure~\ref{fig:SF_GDP_Lattice_Graph} compares single-factor model predictions with historical data.
+Figure~\ref{fig:SF_GDP_Lattice_Graph} compares single-factor model predictions 
+with historical data.
 

### 2013-06-25 EconGrowth.Rnw
Now including the triangle cloud graph for cde with q in the paper.

@@
   # ********************************************************
-  eval=TRUE,
+  eval=FALSE,
   # ********************************************************
@@
 @
+
+Figure~\ref{fig:CDq_Cloud_Graph} shows $\alpha$, $\beta$, and $\gamma$ parameter values for resample models for the Cobb-Douglas model (with $q$).
+**** Need to add the sloped triangle lines if we decide to use graphs like this.
+****
+
+<<CDq_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.cap="Cobb-Douglas (with $q$) resample model parameters.", eval=TRUE>>=
+cdeResampleTrianglePlot(energyType="Q")
+@
+
+**** Add triangle cloud plots for $x$ and $u$ if we decide to use these plots. ****
 

### 2013-06-25 Econ-Growth-Functions2.R

@@ -1911,28 +1911,45 @@ abgTriangleTransform <- function(alpha, beta, gamma){
   return(data.frame(x=x, y=y))
 }
 
-triangleCloudPlot <- function(resampleCoeffs, ...){
+triangleCloudPlot <- function(resampleCoeffs, textScaling = 1.0, ...){
   ########################
   # This function makes a triangle cloud plot from 
   # resample data. The resample data should be in the form of a 
   # data.frame containing columns named x, y, and countryAbbrev.
   # This function makes a lattice plot from the information.
   ##
+  factorLevels <- countryNamesAlph # We want all countries shown
   # Attach the xy data to the original resample data so that we retain the country information
   graph <- xyplot(y ~ x | countryAbbrev, data=resampleCoeffs, 
                   pch=16, 
                   alpha=0.1, 
                   cex=1,
+                  col.symbol = "black", #Controls symbol parameters
+                  as.table = TRUE, #indexing of panels starts in upper left and goes across rows.
+                  index.cond = list(countryOrderForGraphs), #orders the panels.
+                  scales=list(cex=scaleTextSize * textScaling, #controls text size on scales.
+                              tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
+                              alternating=FALSE # eliminates left-right, top-bot alternating of axes
+                  ), 
+                  strip=strip.custom(factor.levels=factorLevels, # Sets text for factor levels
+                                     bg="transparent", # Sets background transparent to match the graph itself.
+                                     par.strip.text=list(cex=textScaling) # Scales text in the strip.
+                  ),
                   xlim=c(0,1), 
-                  ylim=c(0,1)
+                  ylim=c(0,1),
+                  xlab=list(label="$\\alpha$", cex=textScaling), 
+                  ylab=list(label="$\\gamma$", cex=textScaling)
   )
-  ladd(panel.xyplot(c(0.0, 1.0, 0.5, 0.0) , c(0.0 ,0.0 ,1.0 ,0.0), type="l"))
+  # This next line causes the plot to fail in the paper. Need 
+  # to find a way to add the sloped lines ot hte plot.
+  # ladd(panel.xyplot(c(0.0, 1.0, 0.5, 0.0) , c(0.0 ,0.0 ,1.0 ,0.0), type="l"))
   return(graph)
 }
 
 cdeResampleTrianglePlot <- function(energyType, ...){
   ##################
[…]

### 2013-06-25 EconGrowth.Rnw
Changed height of clooud graph.

--- 2013-06-07 EconGrowth.Rnw
@@
 @
+
+Figure~\ref{fig:CDq_Cloud_Graph} shows $\alpha$, $\beta$, and $\gamma$ parameter values for resample models for the Cobb-Douglas model (with $q$).
+**** Need to add the sloped triangle lines if we decide to use graphs like this.
+****
+
+<<CDq_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (with $q$) resample model parameters.", eval=TRUE>>=
+cdeResampleTrianglePlot(energyType="Q")
+@
+
+**** Add triangle cloud plots for $x$ and $u$ if we decide to use these plots. ****
 

### 2013-06-26 EconGrowth.Rnw
prepping for residual resampling

@@
 
-<<setup, echo=FALSE, message=FALSE, eval=TRUE>>=
+<<setup, echo=FALSE, message=FALSE, eval=FALSE>>=
 require(lattice)

### 2013-06-27 EconGrowth.Rnw
Moving back to 100 samples for the CDe resampling.

--- 2013-06-25 EconGrowth.Rnw
@@
 
-<<FindError, eval=TRUE>>=
-# print(cobbDouglasCountryRow(countryAbbrev="US", energyType="X"))
-# print(cobbDouglasCountryRow(countryAbbrev="UK", energyType="X"))
-# print(cobbDouglasCountryRow(countryAbbrev="JP", energyType="X"))
-# print(cobbDouglasCountryRow(countryAbbrev="CN", energyType="X"))
-# print(cobbDouglasCountryRow(countryAbbrev="ZA", energyType="X"))
-# print(cobbDouglasCountryRow(countryAbbrev="SA", energyType="X"))
-# print(cobbDouglasCountryRow(countryAbbrev="IR", energyType="X"))
-# print(cobbDouglasCountryRow(countryAbbrev="TZ", energyType="X"))
-
-cobbDouglasData(countryAbbrev="TZ", energyType="X")
-
-# print(cobbDouglasModel(countryAbbrev="TZ", energyType="X"))
-# print(cdeModel(countryAbbrev="TZ", energyType="X"))
-# print(cobbDouglasCountryRow(countryAbbrev="ZM", energyType="X"))
-@
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-But, the nearly-complete focus on developed economies closes off 
+But, the near-exclusive focus on developed economies closes off 
 the possibility of discovering any role that energy plays 
-in the development process. In this paper we analyze at least 
+in the economic development process. In this paper we analyze at least 
 two economies in each of the following four categories: 
-Developed (technologically advanced with high standards of living), 
-BRICS\footnote{Brazil, Russia, India, China, and South Africa} 
-(rapid economic growth with standards of living below that of 
-developed economies), 
-Petrol (petroleum is a substantial source of GDP 
-**** Martin: Is this the right way to describe the 
-petrol economies? ****); and 
-LDCs\footnote{Lesser Developed Countries} 
-(living standards near subsistence levels 
-**** Martin: Is this the right way to describe the LDC economies? ****). 
+Developed, 
+NICs,\footnote{Newly Industrialized Countries}
+OPEC, and 
+LDCs.\footnote{Lesser Developed Countries} 
 (See Table~\ref{tab:Economy_Examples}.)
@@
       \hline
-      \multirow{2}{*}{BRICS}     & \includegraphics[height=0.11in]{flag/flag_CN.png} & CN & China & \multirow{2}{*}{1991--2011}        \\
+      \multirow{2}{*}{NICs}      & \includegraphics[height=0.11in]{flag/flag_CN.png} & CN & China & \multirow{2}{*}{1991--2011}        \\
                                  & \includegraphics[height=0.11in]{flag/flag_ZA.png} & ZA & South Africa & \\
       \hline
-      \multirow{2}{*}{Petrol}    & \includegraphics[height=0.11in]{flag/flag_SA.png} & SA & Saudi Arabia & \multirow{2}{*}{1991--2011} \\
+      \multirow{2}{*}{OPEC}      & \includegraphics[height=0.11in]{flag/flag_SA.png} & SA & Saudi Arabia & \multirow{2}{*}{1991--2011} \\
                                  & \includegraphics[height=0.11in]{flag/flag_IR.png} & IR & Iran         &  \\
       \hline
-      \multirow{2}{*}{LDC}       & \includegraphics[height=0.11in]{flag/flag_TZ.png} & TZ & Tanzania & \multirow{2}{*}{1991--2011}     \\
+      \multirow{2}{*}{LDCs}      & \includegraphics[height=0.11in]{flag/flag_TZ.png} & TZ & Tanzania & \multirow{2}{*}{1991--2011}     \\
                                  & \includegraphics[height=0.11in]{flag/flag_ZM.png} & ZM & Zambia      & \\
@@
 
-<<CDq_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (with $q$) resample model parameters.", eval=TRUE>>=
+<<CDq_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (with $q$) resample model parameters.">>=
 cdeResampleTrianglePlot(energyType="Q")

### 2013-06-27 Econ-Growth-CDe-Resampling.R

@@ -30,7 +30,7 @@ genAllCDeResampleData <- function(){
   # and saves to disk.
   ##
   t_0 <- proc.time()
-  n=1000 # 10,000 samples are probably sufficient
+  n=100 # 10,000 samples are probably sufficient
   energyType <- "Q"
   lapply(countryAbbrevs, genCDeResampleData, energyType=energyType, n=n)
   energyType <- "X"

### 2013-06-28 EconGrowth.Rnw
Changed to -- from - in LaTeX code.

--- 2013-06-27 EconGrowth.Rnw
@@
 \begin{itemize}
-  \item{1980-2011 for covariances among 
+  \item{1980--2011 for covariances among 
         $y$, $k$, $l$, $q$, and $x$ for developed\\*economies;}
-  \item{1980-2000 for covariances involving 
+  \item{1980--2000 for covariances involving 
         $u$ for developed economies; and}
-  \item{1991-2011 for covariances among 
+  \item{1991--2011 for covariances among 
         $y$, $k$, $l$, $q$, and $x$ for developing\\*economies.}

### 2013-07-01 EconGrowth.Rnw
Not evaluating any R code except for the triangle plots.

@@
 
-<<CDq_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (with $q$) resample model parameters.">>=
+<<CDq_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (with $q$) resample model parameters.", eval=TRUE>>=
 cdeResampleTrianglePlot(energyType="Q")

### 2013-07-06 EconGrowth.Rnw
Now evaluating all chunks.

@@
   # ********************************************************
-  # Allows LaTeX code in graphical output. 
+  # tikz allows LaTeX code in graphical output. 
   # E.g., "$y$" for a variable name in the legend for a graph.  

### 2013-07-07 EconGrowth.Rnw
Cleaned up several to-do items.

@@
 \begin{itemize}
-\item{Pruim: At present, we are doing simple ± t-value * std. dev. for
-      confidence intervals of, e.g., $1-\alpha-\beta$ in some places. 
-      Is that still correct if we move to a different approach for 
-      estimating confidence intervals? See especially \texttt{cesData} 
-      and possibly other places.}
-\item{Pruim: At present, we are doing \texttt{deltaMethod} for determining CIs on 
-      $1-\alpha-\beta$ terms. Is that OK if we move to a different approach
-      for estimating confidence intervals?}
-\item{Heun: Fix error when calculating confidence intervals for 
-Cobb-Douglas model for TZ with X. The problem occurs in function 
-\texttt{cobbDouglasData}. To repeat the problem, call \\* 
-\texttt{cobbDouglasData(countryAbbrev="TZ", energyType="X")}. \\* 
-The code fails on the line \\* 
-\texttt{  ciCD <- confint(object=modelCD, level=ciLevel)}. \\* 
-There is code after the to-do list in this file that exposes the problem.}
-\item{Heun: Get function \texttt{cdModel} working with constraints. 
-Note that the unconstrained solutions are sometimes within the constraints. 
-But, sometimes they aren't. All solutions need to be within constraints. 
-We may need to run with warnings turned off to view the problems.}
-\item{Heun: Get function \texttt{cdeModel} working with constraints. 
-Note that the unconstrained solutions are sometimes within the constraints. 
-But, sometimes they aren't. All solutions need to be within constraints. 
-We may need to run with warnings turned off to view the problems.}
+\item{Heun: Figure out why CESe for ZA with X fails during resampling.}
+\item{Heun: Review all assumptions for CES with energy models. 
+There are several assumptions for rho and rho1 for various countries. 
+When we are resampling, we probably don't want to specify those values.}
+\item{Heun: Implement confidence interval calculations for 
+all resampling methods.}
+\item{Heun: Decide if the single factor models should include constraints
+on $\alpha$, $\beta$, and $\gamma$. At present, the single-factor model allows
+values outside the ranges $\alpha \in (0,1)$, $\beta \in (0,1)$, and $\gamma \in (0,1)$.}
+\item{Heun: Make smaller cloud plots for resample coefficients for those 
+countries where $u$ is involved.}
 \item{Heun: Investigate possible conflicting use of exergy by Warr and Ayres.}
+\item{Heun: Get AIC calculations working again.}
 \item{Heun: Fix the energy sankey diagram from the seminar}
@@
       \begin{itemize}
-      \item{Get values and se for $\sigma$s directly from the 
-            \texttt{cesModel} object in the \texttt{cesData} function}
       \item{Write up the decisions about parameter estimation for the 
@@
       \end{itemize}
-\item{Heun: Eliminate blanks in the coefficient tables for the 
-      95\% CIs in the Cobb-Douglas with energy rows}
-      \begin{itemize}
-      \item{ZA: lower bound on $\lambda$ and upper bound on $\alpha$}
-      \item{ZM: lower bound on $\lambda$}
-      \end{itemize}
-\item{Heun: Eliminate blanks in the coefficient tables for the 95\% CIs in the LINEX model}
-      \begin{itemize}
-      \item{ZM: upper bound on $c_t$}
-      \end{itemize}
 \item{Heun: Fix warnings of the form \texttt{Warning:  step factor 0.000488281 reduced below ’minFactor’ of 0.000976562} in the code that generates the Cobb-Douglas with energy fits.}
 \item{de Wit: review, critique, and contextualize.}
-\item{\st{Heun: Get Pruim set up on the GitHub repository.}}
 \end{itemize}

### 2013-07-08 Workflow.Rnw
adding workflow and documentation document

\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{language}
\usepackage{underscore}

\title{Workflow and Software Documentation}
\author{Heun/Pruim}
\begin{document}

\maketitle

\section{Resampling Workflow}

Because it takes significant time to generate all the resampling data,
this data is cached to save model coefficients generated 
from resampled data into files for each country and each model. 
The files are stored in a directory called \texttt{data_resample}.

A reasonable workflow is this:
\begin{enumerate}
\item 
<<message=FALSE>>=
source("Econ-Growth-Resampling.R")
@
\item
Execute the function called \function{genAllResampleData()} in this file 
from the Console. A typical call would be 
<<eval=FALSE>>=
genAllResampleData(method="wild", n=100)
@
\item Reload the data using one of the various "load" functions
from file \texttt{Econ-Growth-Functions2.R}:

<<eval=FALSE>>=
loadResampleData <- function(modelType, countryAbbrev, energyType, factor)
loadAllResampleData <- function(modelType, energyType, factor)
loadResampleDataRefitsOnly <- function(modelType, countryAbbrev, energyType,  factor)
loadResampleDataBaseFitOnly <- function(modelType, countryAbbrev, energyType, factor)
@

\begin{enumerate}
\item
A typical call for loadAllResampleData would be
<<eval=FALSE>>=
loadAllResampleData(modelType="cde", energyType="Q")
@
\item
Another example:
<<>>=
head(loadAllResampleData(model="sf", factor="K"), n=5)
@
\end{enumerate}
\end{enumerate}
\end{document}

### 2013-07-08 Workflow.Rnw
added plotting example

@@
 \begin{document}
+
+<<setup, include=FALSE>>=
+require(knitr)
+opts_chunk$set(
+  tidy=FALSE
+)
+@
 
@@
 \item
-Execute the function called \function{genAllResampleData()} in this file 
-from the Console. A typical call would be 
+Execute the function called \function{genAllResampleData()}.
+
+A typical call would be 
 <<eval=FALSE>>=
@@
 \end{enumerate}
+\item
+Plots of resampling distributions can be made with \function{triPlot()}.
+<<>>=
+source("Graphics.R")
+resData <- loadAllResampleData(modelType="cde", energyType="Q")
+triPlot( subset(resData, method=="wild"), 
+         gamma, alpha, beta,
+         labels=c("gamma", "alpha", "beta"),
+         n.grid=5,  aes_string="color=lambda", 
+         size=3, alpha=.5 ) + 
+     geom_point( data=subset(resData, method=="orig"), 
+                 color="red", alpha=1, size=3) +
+     facet_wrap( ~ countryAbbrev )
+@
+Eventually, we can build a wrapper that loads the data and builds the plot with our favorite settings.
 \end{enumerate}

### 2013-07-08 Workflow.Rnw
Minor edits.

@@
 \usepackage[margin=1in]{geometry}
-\usepackage{language}
-\usepackage{underscore}
+\usepackage{language} % Obtain language.sty from https://github.com/rpruim/latex
+\usepackage{underscore} % Should be part of any LaTeX distribution.
 
@@
 )
+require(tikzDevice)
 @
@@
 Because it takes significant time to generate all the resampling data,
-this data is cached to save model coefficients generated 
-from resampled data into files for each country and each model. 
+resample data is cached on disk. Model coefficients generated 
+from resampled data are stored in files for each country and each model. 
 The files are stored in a directory called \texttt{data_resample}.
@@
 @
+which, in turn, sources the file named \texttt{Econ-Growth_Functions2.R}.
+
 \item
@@
 @
-\item Reload the data using one of the various "load" functions
+\item Reload the data using one of the various ``load'' functions
 from file \texttt{Econ-Growth-Functions2.R}:
@@
 \item
-Plots of resampling distributions can be made with \function{triPlot()}.
+Plots of distributions of coefficients for the Cobb-Douglas 
+with energy model can be made with \function{triPlot()} in 
+file \texttt{Graphics.R}.
 <<>>=

### 2013-07-08 Workflow.Rnw
Didn't want to force Randy to require(tikzDevice)
Added a new section for Ternary Plots.
Several small updates.

@@
 )
-require(tikzDevice)
 @
@@
 
-A reasonable workflow is this:
+A reasonable workflow is:
 \begin{enumerate}
@@
 \end{enumerate}
+\end{enumerate}
+
+\section{Ternary Plots}
+\begin{enumerate}
 \item
@@
 resData <- loadAllResampleData(modelType="cde", energyType="Q")
-triPlot( subset(resData, method=="wild"), 
+triPlot(subset(resData, method!="orig"), 
         gamma, alpha, beta,
@@
         size=3, alpha=.5 ) + 
-     geom_point( data=subset(resData, method=="orig"), 
+     geom_point(data=subset(resData, method=="orig"), 
                 color="red", alpha=1, size=3) +
@@
 \end{enumerate}
+
 \end{document}

### 2013-07-08 EconGrowth.Rnw
Now using the Graphics.R file to generate ternary plots.

@@
 source("Econ-Growth-Functions2.R")
+source("Graphics.R")
 @
@@
 Figure~\ref{fig:CDq_Cloud_Graph} shows $\alpha$, $\beta$, and $\gamma$ parameter values for resample models for the Cobb-Douglas model (with $q$).
-**** Need to add the sloped triangle lines if we decide to use graphs like this.
-****
 
@@
 cdeResampleTrianglePlot(energyType="Q")
+@
+
+Figure~\ref{fig:CDx_Cloud_Graph} shows $\alpha$, $\beta$, and $\gamma$ parameter values for resample models for the Cobb-Douglas model (with $x$).
+
+<<CDx_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (with $x$) resample model parameters.", eval=TRUE>>=
+cdeResampleTrianglePlot(energyType="X")
 @

### 2013-07-09 EconGrowth.Rnw
Turned off tikz device for now. The new ternary plots don't work with tikz.

@@
 # on installing tikzDevice.
-require(tikzDevice) 
+# require(tikzDevice) 
 trellis.par.set(theme=theme.mosaic())
@@
   # E.g., "$y$" for a variable name in the legend for a graph.  
-  dev='tikz',    
+  # dev='tikz',    
   tidy=FALSE,

### 2013-07-09 Workflow.Rnw
demo of subscripts, sqrt in lables

@@
 with energy model can be made with \function{triPlot()} in 
-file \texttt{Graphics.R}.
+file \texttt{Graphics.R}.  (Goofy labels here just to demonstrate what is possible.)
 <<>>=
@@
         gamma, alpha, beta,
-        labels=c("gamma", "alpha", "beta"),
+        labels=c("gamma[1]", "alpha[2]", "sqrt(beta[3])"),
         n.grid=5,  aes_string="color=lambda", 

### 2013-07-09 EconGrowth.Rnw
Turned off tikz.
Now using ternary plots for resample data for CD and CDe models in the paper.

@@
 
+Figure~\ref{fig:CD_Cloud_Graph} shows $\alpha$, $\beta$, and $\gamma$ parameter values for resample models for the Cobb-Douglas model (without energy).
+$\gamma$ is always 0.0, because energy is not included in this model.
+
+<<CD_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (without energy) resample model parameters.">>=
+cdResampleTrianglePlot(energyType=NA)
+@
+
 To qualitatively assess whether augmenting the Cobb-Douglas model with energy 
@@
 
-<<CDq_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (with $q$) resample model parameters.", eval=TRUE>>=
-cdeResampleTrianglePlot(energyType="Q")
+<<CDq_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (with $q$) resample model parameters.">>=
+cdResampleTrianglePlot(energyType="Q")
 @
@@
 
-<<CDx_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (with $x$) resample model parameters.", eval=TRUE>>=
-cdeResampleTrianglePlot(energyType="X")
-@
-
-**** Add triangle cloud plots for $x$ and $u$ if we decide to use these plots. ****
+<<CDx_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (with $x$) resample model parameters.">>=
+cdResampleTrianglePlot(energyType="X")
+@
+
+Figure~\ref{fig:CDu_Cloud_Graph} shows $\alpha$, $\beta$, and $\gamma$ parameter values for resample models for the Cobb-Douglas model (with $u$).
+
+<<CDu_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=threePanelGraphHeight, fig.cap="Cobb-Douglas (with $u$) resample model parameters.">>=
+cdResampleTrianglePlot(energyType="U")
+@
 

### 2013-07-09 Workflow.Rnw

--- 2013-07-08 Workflow.Rnw
@@
         gamma, alpha, beta,
-        labels=c("gamma", "alpha", "beta"),
+        labels=c("gamma[1]", "alpha[2]", "sqrt(beta[3])"),
         n.grid=5,  aes_string="color=lambda", 
-        size=3, alpha=.5 ) + 
+        size=1.7, alpha=.5 ) + 
      geom_point(data=subset(resData, method=="orig"), 
                 color="red", alpha=1, size=3) +
-     facet_wrap( ~ countryAbbrev )
+     facet_wrap( ~ countryAbbrev ) +
+     scale_colour_gradient(expression(lambda), high="navy", low="skyblue")
 @

### 2013-07-09 EconGrowth.Rnw
Now generating SF cloud graphs in the paper.

@@
 \begin{itemize}
-\item{Heun: Figure out why CESe for ZA with X fails during resampling.}
+\item{Heun: Add option for $m = 1$ in single-factor models.}
+\item{Heun: Figure out why CESe for ZA with $x$ fails during resampling.}
 \item{Heun: Review all assumptions for CES with energy models. 
@@
 When we are resampling, we probably don't want to specify those values.}
-\item{Heun: Implement confidence interval calculations for 
-all resampling methods.}
-\item{Heun: Decide if the single factor models should include constraints
+\item{Heun: Re-implement confidence interval calculations to use
+resampling methods.}
+      \begin{itemize}
+      \item{SF}
+      \item{CD}
+      \item{\st{CDe}}
+      \item{CES}
+      \item{CESe}
+      \item{LINEX}
+      \end{itemize}
+\item{Heun: Include cloud graphs for model parameters 
+estimated by resampling methods.}
+      \begin{itemize}
+      \item{\st{SF}}
+      \item{CD}
+      \item{\st{CDe}}
+      \item{CES}
+      \item{CESe}
+      \item{LINEX}
+      \end{itemize}
+\item{\st{Heun: Decide if the single factor models should include constraints
 on $\alpha$, $\beta$, and $\gamma$. At present, the single-factor model allows
-values outside the ranges $\alpha \in (0,1)$, $\beta \in (0,1)$, and $\gamma \in (0,1)$.}
-\item{Heun: Make smaller cloud plots for resample coefficients for those 
-countries where $u$ is involved.}
+values outside the ranges $\alpha \in (0,1)$, $\beta \in (0,1)$, and $\gamma \in (0,1)$.}}
+\item{\st{Heun: Make smaller cloud plots for resample coefficients for those 
+countries where $u$ is involved.}}
 \item{Heun: Investigate possible conflicting use of exergy by Warr and Ayres.}
@@
 
+Coefficients derived from resampling are shown in 
+Figures~\ref{fig:SFk_Resample_Graph}--\ref{fig:SFu_Resample_Graph}. 
+In each case, the exponent on the factor of production is assumed to be $m = 1$.
+
+<<SFk_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single factor model (with $f = k$ and $m = \\alpha$) resampling results.">>=
+sfResamplePlot(factor="K")
+@
+
+<<SFl_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single factor model (with $f = l$ and $m = \\beta$) resampling results.">>=
+sfResamplePlot(factor="L")
+@
+
+<<SFq_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single factor model (with $f = q$ and $m = \\gamma$) resampling results.">>=
+sfResamplePlot(factor="Q")
+@
+
+<<SFx_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single factor model (with $f = x$ and $m = \\gamma$) resampling results.">>=
+sfResamplePlot(factor="X")
+@
+
+<<SFu_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="Single factor model (with $f = u$ and $m = \\gamma$) resampling results.">>=
+sfResamplePlot(factor="U")
+@
+
 Figure~\ref{fig:SF_GDP_Lattice_Graph} compares single-factor model predictions 

### 2013-07-09 Econ-Growth-Functions2.R
CD model now uses resampling information for confidence intervals.

@@ -1303,14 +1303,15 @@ cobbDouglasModel <- function(countryAbbrev, energyType=NA, gamma, data=loadData(
   return(cdeModel(data=data, energyType=energyType, ...))
 }
 
-cdeResampleCoeffProps <- function(cdeResampleFits, ...){
+cdResampleCoeffProps <- function(cdResampleFits, ...){
   ####### 
-  # This function creates a table of confidence intervals for the cde model
+  # This function creates a table of confidence intervals for the cd and cde models
+  # from the data supplied
   ##
   # Grab the original curve fit
-  baseFitCoeffs <- cdeResampleFits[cdeResampleFits[["method"]]=="orig", ]
+  baseFitCoeffs <- cdResampleFits[cdResampleFits[["method"]]=="orig", ]
   # Grab the resample curve fits
-  resampleFitCoeffs <- cdeResampleFits[cdeResampleFits[["method"]] != "orig", ]
+  resampleFitCoeffs <- cdResampleFits[cdResampleFits[["method"]] != "orig", ]
   lambdaCI <- qdata(p=ciVals, vals=lambda, data=resampleFitCoeffs)
   alphaCI <- qdata(p=ciVals, vals=alpha, data=resampleFitCoeffs)
   betaCI <- qdata(p=ciVals, vals=beta, data=resampleFitCoeffs)
@@ -1512,141 +1513,21 @@ cobbDouglasData <- function(countryAbbrev, energyType=NA, ...){
     colnames(df) <- c("lambda", "alpha", "beta", "gamma")
     rownames(df) <- c("+95% CI", "CDe", "-95% CI")
     return(df)
-  }
-  # We have a combination of country and energy type for which we have data.
-  if (! is.na(energyType)){
+  } else if (is.na(energyType)){
+    # We want Cobb-Douglas without energy
+    resampledData <- loadResampleData(modelType="cd", countryAbbrev=countryAbbrev)
+  } else {
     # We want Cobb-Douglas with energy
     resampledData <- loadResampleData(modelType="cde", countryAbbrev=countryAbbrev, energyType=energyType)
-    statisticalProperties <- cdeResampleCoeffProps(resampledData)
-    return(statisticalProperties)
   }
-  # Well, we want Cobb-Douglas without energy
-  modelCD <- cobbDouglasModel(countryAbbrev=countryAbbrev, energyType=energyType)
-  summaryCD <- summary(modelCD) # Gives the nls summary table.
[…]

### 2013-07-10 EconGrowth.Rnw
CD model now uses resampling information for confidence intervals.
Added notes about elasticity of substitution.
Edited the to-do list to reflect fact that we're now using resampled data to calculate SF confidence intervals.
Now including CES resampling graphs.

@@
       \begin{itemize}
-      \item{SF}
-      \item{CD}
+      \item{\st{SF}}
+      \item{\st{CD}}
       \item{\st{CDe}}
-      \item{CES}
-      \item{CESe}
+      \item{\st{CES}}
+      \item{\st{CESe}}
       \item{LINEX}
@@
       \item{\st{SF}}
-      \item{CD}
+      \item{\st{CD}}
       \item{\st{CDe}}
@@
 of ($kl$) relative to ($e$), and $\gamma$ is a fitting parameter, 
-expected to be close to unity.
+expected to be close to unity. As $\sigma \rightarrow \infty$, 
+($kl$) and ($e$) are perfect substitutes. As $\sigma \rightarrow 0$, 
+($kl$) and ($e$) are perfect complements: no substitution is possible.
 
@@
 
+Figure~\ref{fig:CD_Cloud_Graph} shows $\alpha$, $\beta$, and $\gamma$ parameter values for resample models for the Cobb-Douglas model (without energy).
+$\gamma$ is always 0.0, because energy is not included in this model.
+
+<<CD_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (without energy) resample model parameters.">>=
+cdResampleTrianglePlot(energyType=NA)
+@
+
+Converting the resample data into 95\% confidence intervls 
+provides data for Figure~\ref{fig:CD_Params_Graph}.
+
 <<CD_Params_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.cap="Cobb-Douglas (without energy) model parameters.
@@
 createCDParamsGraph(energyType=NA)
-@
-
-Figure~\ref{fig:CD_Cloud_Graph} shows $\alpha$, $\beta$, and $\gamma$ parameter values for resample models for the Cobb-Douglas model (without energy).
-$\gamma$ is always 0.0, because energy is not included in this model.
-
-<<CD_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (without energy) resample model parameters.">>=
-cdResampleTrianglePlot(energyType=NA)
 @
@@
 
+Figure~\ref{fig:CDq_Cloud_Graph} shows $\alpha$, $\beta$, and $\gamma$ parameter values for resample models for the Cobb-Douglas model (with $q$).
+
+<<CDq_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (with $q$) resample model parameters.">>=
+cdResampleTrianglePlot(energyType="Q")
+@
+
+Figure~\ref{fig:CDx_Cloud_Graph} shows $\alpha$, $\beta$, and $\gamma$ parameter values for resample models for the Cobb-Douglas model (with $x$).
+
+<<CDx_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (with $x$) resample model parameters.">>=
+cdResampleTrianglePlot(energyType="X")
+@
+
+Figure~\ref{fig:CDu_Cloud_Graph} shows $\alpha$, $\beta$, and $\gamma$ parameter values for resample models for the Cobb-Douglas model (with $u$).
+
+<<CDu_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=threePanelGraphHeight, fig.cap="Cobb-Douglas (with $u$) resample model parameters.">>=
+cdResampleTrianglePlot(energyType="U")
+@
+
 Figure~\ref{fig:CDq_Params_Graph} shows values and 95\% confidence intervals 
@@
 createCDParamsGraph(energyType="U")
-@
-
-Figure~\ref{fig:CDq_Cloud_Graph} shows $\alpha$, $\beta$, and $\gamma$ parameter values for resample models for the Cobb-Douglas model (with $q$).
-
-<<CDq_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (with $q$) resample model parameters.">>=
-cdResampleTrianglePlot(energyType="Q")
-@
-
-Figure~\ref{fig:CDx_Cloud_Graph} shows $\alpha$, $\beta$, and $\gamma$ parameter values for resample models for the Cobb-Douglas model (with $x$).
-
-<<CDx_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (with $x$) resample model parameters.">>=
-cdResampleTrianglePlot(energyType="X")
-@
-
-Figure~\ref{fig:CDu_Cloud_Graph} shows $\alpha$, $\beta$, and $\gamma$ parameter values for resample models for the Cobb-Douglas model (with $u$).
-
-<<CDu_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=threePanelGraphHeight, fig.cap="Cobb-Douglas (with $u$) resample model parameters.">>=
-cdResampleTrianglePlot(energyType="U")
 @
@@
 Complete after our work this summer. ****
-Elasticities of substitution $\sigma_1$ and $\sigma$ 
-(see Section~\ref{sec:CES}) were estimated by the delta method 
-(**** is this correct? Ask Pruim. ****).
 
@@
 % \end{quote}
+
+Coefficients for each resampled CES model (without energy)
+are shown in Figures~\ref{fig:CES_lambda_gamma_Cloud_Graph} 
+and \ref{fig:CES_sigma_1_delta_1_Cloud_Graph}.
+
+<<CES_lambda_gamma_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\lambda$ and $\\gamma$.", eval=TRUE>>=
+cesLambdaGammaResamplePlot(energyType=NA)
+@
+
+<<CES_sigma_1_delta_1_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\sigma_1$ and $\\delta_1$.", eval=TRUE>>=
+cesSigma_1Delta_1ResamplePlot(energyType=NA)
+@
+
+Coefficients for each resampled CES model (with $q$)
+are shown in 
+Figures~\ref{fig:CESq_lambda_gamma_Cloud_Graph}--\ref{fig:CESq_sigma_delta_Cloud_Graph}.
+
+<<CESq_lambda_gamma_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$) resample model parameters $\\lambda$ and $\\gamma$.", eval=TRUE>>=
+cesLambdaGammaResamplePlot(energyType="Q")
+@
+
+<<CESq_sigma_1_delta_1_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$) resample model parameters $\\sigma_1$ and $\\delta_1$.", eval=TRUE>>=
+cesSigma_1Delta_1ResamplePlot(energyType="Q")
+@
+
+<<CESq_sigma_delta_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$) resample model parameters $\\sigma$ and $\\delta$.", eval=TRUE>>=
+cesSigmaDeltaResamplePlot(energyType="Q")
+@
+
+Coefficients for each resampled CES model (with $x$)
+are shown in 
+Figures~\ref{fig:CESx_lambda_gamma_Cloud_Graph}--\ref{fig:CESx_sigma_delta_Cloud_Graph}.
+
+<<CESx_lambda_gamma_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$) resample model parameters $\\lambda$ and $\\gamma$.", eval=TRUE>>=
+cesLambdaGammaResamplePlot(energyType="X")
+@
+
+<<CESx_sigma_1_delta_1_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$) resample model parameters $\\sigma_1$ and $\\delta_1$.", eval=TRUE>>=
+cesSigma_1Delta_1ResamplePlot(energyType="X")
+@
+
+<<CESx_sigma_delta_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$) resample model parameters $\\sigma$ and $\\delta$.", eval=TRUE>>=
+cesSigmaDeltaResamplePlot(energyType="X")
+@
+
+Coefficients for each resampled CES model (with $u$)
+are shown in 
+Figures~\ref{fig:CESu_lambda_gamma_Cloud_Graph}--\ref{fig:CESu_sigma_delta_Cloud_Graph}.
+
+<<CESu_lambda_gamma_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$) resample model parameters $\\lambda$ and $\\gamma$.", eval=TRUE>>=
+cesLambdaGammaResamplePlot(energyType="U")
+@
+
+<<CESu_sigma_1_delta_1_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$) resample model parameters $\\sigma_1$ and $\\delta_1$.", eval=TRUE>>=
+cesSigma_1Delta_1ResamplePlot(energyType="U")
+@
+
+<<CESu_sigma_delta_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$) resample model parameters $\\sigma$ and $\\delta$.", eval=TRUE>>=
+cesSigmaDeltaResamplePlot(energyType="U")
+@
 
@@
 
+Coefficients derived from resampling are shown in 
+Figures~\ref{fig:SFk_Resample_Graph}--\ref{fig:SFu_Resample_Graph}. 
+In each case, the exponent on the factor of production is assumed to be $m = 1$.
+
+<<SFk_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single factor model (with $f = k$ and $m = \\alpha$) resampling results.">>=
+sfResamplePlot(factor="K")
+@
+
+<<SFl_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single factor model (with $f = l$ and $m = \\beta$) resampling results.">>=
+sfResamplePlot(factor="L")
+@
+
+<<SFq_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single factor model (with $f = q$ and $m = \\gamma$) resampling results.">>=
+sfResamplePlot(factor="Q")
+@
+
+<<SFx_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single factor model (with $f = x$ and $m = \\gamma$) resampling results.">>=
+sfResamplePlot(factor="X")
+@
+
+<<SFu_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="Single factor model (with $f = u$ and $m = \\gamma$) resampling results.">>=
+sfResamplePlot(factor="U")
+@
+
+Converting the resampling data to 95\% confidence intervals
+provides results shown in 
+Figures~\ref{fig:SFk_Params_Graph}--\ref{fig:SFu_Params_Graph}.
+
 <<SFk_Params_Graph, fig.pos="H", fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.cap="Single-factor (with $k$) model parameters.
@@
 createSFParamsGraph(factor="U")
-@
-
-Coefficients derived from resampling are shown in 
-Figures~\ref{fig:SFk_Resample_Graph}--\ref{fig:SFu_Resample_Graph}. 
-In each case, the exponent on the factor of production is assumed to be $m = 1$.
-
-<<SFk_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single factor model (with $f = k$ and $m = \\alpha$) resampling results.">>=
-sfResamplePlot(factor="K")
-@
-
-<<SFl_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single factor model (with $f = l$ and $m = \\beta$) resampling results.">>=
-sfResamplePlot(factor="L")
-@
-
-<<SFq_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single factor model (with $f = q$ and $m = \\gamma$) resampling results.">>=
-sfResamplePlot(factor="Q")
-@
-
-<<SFx_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single factor model (with $f = x$ and $m = \\gamma$) resampling results.">>=
-sfResamplePlot(factor="X")
-@
-
-<<SFu_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="Single factor model (with $f = u$ and $m = \\gamma$) resampling results.">>=
-sfResamplePlot(factor="U")
 @

### 2013-07-10 EconGrowth.Rnw
Removed eval=TRUE from several graphs.

--- 2013-07-09 EconGrowth.Rnw
@@
       \item{\st{SF}}
-      \item{CD}
+      \item{\st{CD}}
       \item{\st{CDe}}
-      \item{CES}
-      \item{CESe}
+      \item{\st{CES}}
+      \item{\st{CESe}}
       \item{LINEX}
@@
 % \end{quote}
+
+Coefficients for each resampled CES model (without energy)
+are shown in Figures~\ref{fig:CES_lambda_gamma_Cloud_Graph} 
+and \ref{fig:CES_sigma_1_delta_1_Cloud_Graph}.
+
+<<CES_lambda_gamma_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\lambda$ and $\\gamma$.">>=
+cesLambdaGammaResamplePlot(energyType=NA)
+@
+
+<<CES_sigma_1_delta_1_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
+cesSigma_1Delta_1ResamplePlot(energyType=NA)
+@
+
+Coefficients for each resampled CES model (with $q$)
+are shown in 
+Figures~\ref{fig:CESq_lambda_gamma_Cloud_Graph}--\ref{fig:CESq_sigma_delta_Cloud_Graph}.
+
+<<CESq_lambda_gamma_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$) resample model parameters $\\lambda$ and $\\gamma$.">>=
+cesLambdaGammaResamplePlot(energyType="Q")
+@
+
+<<CESq_sigma_1_delta_1_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
+cesSigma_1Delta_1ResamplePlot(energyType="Q")
+@
+
+<<CESq_sigma_delta_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$) resample model parameters $\\sigma$ and $\\delta$.">>=
+cesSigmaDeltaResamplePlot(energyType="Q")
+@
+
+Coefficients for each resampled CES model (with $x$)
+are shown in 
+Figures~\ref{fig:CESx_lambda_gamma_Cloud_Graph}--\ref{fig:CESx_sigma_delta_Cloud_Graph}.
+
+<<CESx_lambda_gamma_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$) resample model parameters $\\lambda$ and $\\gamma$.">>=
+cesLambdaGammaResamplePlot(energyType="X")
+@
+
+<<CESx_sigma_1_delta_1_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
+cesSigma_1Delta_1ResamplePlot(energyType="X")
+@
+
+<<CESx_sigma_delta_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$) resample model parameters $\\sigma$ and $\\delta$.">>=
+cesSigmaDeltaResamplePlot(energyType="X")
+@
+
+Coefficients for each resampled CES model (with $u$)
+are shown in 
+Figures~\ref{fig:CESu_lambda_gamma_Cloud_Graph}--\ref{fig:CESu_sigma_delta_Cloud_Graph}.
+
+<<CESu_lambda_gamma_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$) resample model parameters $\\lambda$ and $\\gamma$.">>=
+cesLambdaGammaResamplePlot(energyType="U")
+@
+
+<<CESu_sigma_1_delta_1_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
+cesSigma_1Delta_1ResamplePlot(energyType="U")
+@
+
+<<CESu_sigma_delta_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$) resample model parameters $\\sigma$ and $\\delta$.">>=
+cesSigmaDeltaResamplePlot(energyType="U")
+@
 

### 2013-07-10 EconGrowth.Rnw
Now including LINEX resample plots in the paper.

@@
 in \texttt{R} \citep{R}.
+
+Figures~\ref{fig:LINEXq_Resample_Graph}--\ref{fig:LINEXu_Resample_Graph}
+show the coefficients estimated from resampled data.
+
+<<LINEXq_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX model (with $q$) resampling results.", eval=TRUE>>=
+linexResamplePlot(energyType="Q")
+@
+
+<<LINEXx_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX model (with $x$) resampling results.", eval=TRUE>>=
+linexResamplePlot(energyType="X")
+@
+
+<<LINEXu_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="LINEX model (with $u$) resampling results.", eval=TRUE>>=
+linexResamplePlot(energyType="U")
+@
+
 Figure~\ref{fig:LINEXq_Params_Graph} shows values and 95\% confidence intervals 

### 2013-07-10 EconGrowth.Rnw
Edited to-do list.

--- 2013-07-10 EconGrowth.Rnw
@@
 \begin{itemize}
-\item{Heun: Add option for $m = 1$ in single-factor models.}
+\item{Heun: Add base fit red dots to all cloud plots.}
+      \begin{itemize}
+      \item{SF}
+      \item{CES}
+      \item{CESe}
+      \item{LINEX}
+      \end{itemize}
 \item{Heun: Figure out why CESe for ZA with $x$ fails during resampling.}
@@
 When we are resampling, we probably don't want to specify those values.}
-\item{Heun: Re-implement confidence interval calculations to use
-resampling methods.}
-      \begin{itemize}
-      \item{\st{SF}}
-      \item{\st{CD}}
-      \item{\st{CDe}}
-      \item{\st{CES}}
-      \item{\st{CESe}}
-      \item{LINEX}
-      \end{itemize}
-\item{Heun: Include cloud graphs for model parameters 
-estimated by resampling methods.}
-      \begin{itemize}
-      \item{\st{SF}}
-      \item{\st{CD}}
-      \item{\st{CDe}}
-      \item{\st{CES}}
-      \item{\st{CESe}}
-      \item{LINEX}
-      \end{itemize}
-\item{\st{Heun: Decide if the single factor models should include constraints
-on $\alpha$, $\beta$, and $\gamma$. At present, the single-factor model allows
-values outside the ranges $\alpha \in (0,1)$, $\beta \in (0,1)$, and $\gamma \in (0,1)$.}}
-\item{\st{Heun: Make smaller cloud plots for resample coefficients for those 
-countries where $u$ is involved.}}
 \item{Heun: Investigate possible conflicting use of exergy by Warr and Ayres.}
@@
 \item{de Wit: review, critique, and contextualize.}
+\item{\st{Heun: Add option for $m = 1$ in single-factor models.}}
+\item{\st{Heun: Re-implement confidence interval calculations to use
+resampling methods.}}
+      \begin{itemize}
+      \item{\st{SF}}
+      \item{\st{CD}}
+      \item{\st{CDe}}
+      \item{\st{CES}}
+      \item{\st{CESe}}
+      \item{\st{LINEX}}
+      \end{itemize}
+\item{\st{Heun: Include cloud graphs for model parameters 
+estimated by resampling methods.}}
+      \begin{itemize}
+      \item{\st{SF}}
+      \item{\st{CD}}
+      \item{\st{CDe}}
+      \item{\st{CES}}
+      \item{\st{CESe}}
+      \item{\st{LINEX}}
+      \end{itemize}
+\item{\st{Heun: Decide if the single factor models should include constraints
+on $\alpha$, $\beta$, and $\gamma$. At present, the single-factor model allows
+values outside the ranges $\alpha \in (0,1)$, $\beta \in (0,1)$, and $\gamma \in (0,1)$.}}
+\item{\st{Heun: Make smaller cloud plots for resample coefficients for those 
+countries where $u$ is involved.}}
 \end{itemize}
@@
 in \texttt{R} \citep{R}.
+
+Figures~\ref{fig:LINEXq_Resample_Graph}--\ref{fig:LINEXu_Resample_Graph}
+show the coefficients estimated from resampled data.
+
+<<LINEXq_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX model (with $q$) resampling results." >>=
+linexResamplePlot(energyType="Q")
+@
+
+<<LINEXx_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX model (with $x$) resampling results.">>=
+linexResamplePlot(energyType="X")
+@
+
+<<LINEXu_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="LINEX model (with $u$) resampling results.">>=
+linexResamplePlot(energyType="U")
+@
+
 Figure~\ref{fig:LINEXq_Params_Graph} shows values and 95\% confidence intervals 

### 2013-07-10 EconGrowth.Rnw
Now including graph of rho (sigma) vs. delta for CES without energy. Not a very exciting graph, but drawing it all the same.

@@
 Coefficients for each resampled CES model (without energy)
-are shown in Figures~\ref{fig:CES_lambda_gamma_Cloud_Graph} 
-and \ref{fig:CES_sigma_1_delta_1_Cloud_Graph}.
+are shown in 
+Figures~\ref{fig:CES_lambda_gamma_Cloud_Graph}--\ref{fig:CES_sigma_delta_Cloud_Graph}.
 
@@
 cesSigma_1Delta_1ResamplePlot(energyType=NA)
+@
+
+The next graph is not particularly interesting, 
+because $\delta \rightarrow 1.0$, 
+$\rho \rightarrow -1$, and 
+$\sigma \rightarrow \infty$
+for the CES without energy model.
+
+<<CES_sigma_delta_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\rho$ and $\\delta$.">>=
+cesSigmaDeltaResamplePlot(energyType=NA)
 @

### 2013-07-11 Workflow.Rnw
example of 2d plot similar to triPlot

@@
 Eventually, we can build a wrapper that loads the data and builds the plot with our favorite settings.
+
+\section*{Scatterplots with two variables}
+
+<<>>=
+ggplot(data=subset(resData, method!="orig"), 
+        aes(x=alpha, y=beta, color=lambda)) +
+  geom_point() +
+  xlab(expression(alpha)) +
+  ylab(expression(beta)) +
+  geom_point(data=subset(resData, method=="orig"), 
+                color="red", alpha=1, size=3) +
+  facet_wrap( ~ countryAbbrev ) +
+  scale_colour_gradient(expression(lambda), high="navy", low="skyblue")
+@
 \end{enumerate}

### 2013-07-11 EconGrowth.Rnw
Now including a table of the number of unconverged resample fits in the paper.

@@
 
-<<Print_Covariance_Tables, results='asis', eval=TRUE>>=
+<<Print_Covariance_Tables, results='asis'>>=
 #I wish I could say the following, but I get bogus "$US" strings appearing in the LaTeX output.
@@
       table.placement="H")
+@
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Convergence of Resample Models}
+\label{sec:Convergence_Resample_Models}
+\setcounter{table}{0} % Restarts table number counter at 0 in this section.
+\setcounter{figure}{0} % Restarts figure number counter at 0 in this section.
+\setcounter{equation}{0} % Restarts equation counter to 0 in this section.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The following table shows the fraction of resample models 
+that did not achieve convergence when estimating model parameters.
+
+<<Unconverged_Frac_Table, results='asis', eval=TRUE>>=
+printFracUnconvergedXtable()
 @

### 2013-07-11 EconGrowth.Rnw
Edited to-do list.

@@
       \end{itemize}
-\item{\st{Heun: Include cloud graphs for model parameters 
+\item{\st{Heun: Include scatter graphs for model parameters 
 estimated by resampling methods.}}
@@
 values outside the ranges $\alpha \in (0,1)$, $\beta \in (0,1)$, and $\gamma \in (0,1)$.}}
-\item{\st{Heun: Make smaller cloud plots for resample coefficients for those 
+\item{\st{Heun: Make smaller scatter plots for resample coefficients for those 
 countries where $u$ is involved.}}
+\item{\st{Heun: Add a table that shows the fraction of unconverged resample fits
+for each model, energy type, and factor.}}
 \end{itemize}

### 2013-07-12 EconGrowth.Rnw
Edited to-do list.
Changed vertical dimension of ternary plots to provide equilateral triangle.

@@
 %% keywords here, in the form: keyword \sep keyword
-economic growth \sep energy \sep cobb-douglas \sep CES \sep LINEX
+economic growth \sep energy \sep Cobb-Douglas \sep CES \sep LINEX
 %% MSC codes here, in the form: \MSC code \sep code
@@
       \item{SF}
+      \item{\st{CD}}
+      \item{\st{CDe}}
       \item{CES}
@@
 \item{Heun: Investigate possible conflicting use of exergy by Warr and Ayres.}
-\item{Heun: Get AIC calculations working again.}
 \item{Heun: Fix the energy sankey diagram from the seminar}
@@
 for each model, energy type, and factor.}}
+\item{\st{Heun: Get AIC calculations working again.}}
 \end{itemize}
@@
 
-<<CD_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (without energy) resample model parameters.">>=
+<<CD_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (without energy) resample model parameters.">>=
 cdResampleTrianglePlot(energyType=NA)
@@
 
-Converting the resample data into 95\% confidence intervls 
+Converting the resample data into 95\% confidence intervals 
 provides data for Figure~\ref{fig:CD_Params_Graph}.
@@
 
-<<CDq_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (with $q$) resample model parameters.">>=
+<<CDq_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (with $q$) resample model parameters.">>=
 cdResampleTrianglePlot(energyType="Q")
@@
 
-<<CDx_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (with $x$) resample model parameters.">>=
+<<CDx_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (with $x$) resample model parameters.">>=
 cdResampleTrianglePlot(energyType="X")
@@
 
-<<CDu_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=threePanelGraphHeight, fig.cap="Cobb-Douglas (with $u$) resample model parameters.">>=
+<<CDu_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=threePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (with $u$) resample model parameters.">>=
 cdResampleTrianglePlot(energyType="U")

### 2013-07-12 EconGrowth.Rnw
Minor edits on the paper.

@@
 \begin{itemize}
-\item{Heun: Add base fit red dots to all cloud plots.}
+\item{Pruim: Add base fit red dots to all cloud plots.}
       \begin{itemize}
@@
 \item{capital stock ($k$) has increased more than the average 
-      of energy ($e$) and labor ($l$), i.e. if $\rho_k >$ 1, or}
+      of labor ($l$) and energy ($e$), i.e. if $\rho_k >$ 1, or}
 \item{labor ($l$) has increased more than energy ($e$), i.e. if $\rho_l >$ 1.}
@@
 without a commensurate increase in energy ($e$). Thus, $\rho_k$ is an 
-efficiency of using labor and energy to make capital available to the 
-economy, and $\rho_l$ is an efficiency of using energy to make labor 
-available to the economy. $a_0$ represents the overall importance 
-of these efficiencies, and $c_t$ represents the relative importance 
+efficiency of using additional labor and energy to make 
+additional capital stock available to the economy, 
+and $\rho_l$ is an efficiency of using additional energy to make 
+additional labor available to the economy. 
+$a_0$ represents the overall importance of these efficiencies, 
+and $c_t$ represents the relative importance 
 of the labor efficiency term compared to the capital stock efficiency term. 

### 2013-07-13 Workflow.Rnw
Scatterplot with two variables now a numbered section.
first draft of plot wrappers

--- 2013-07-09 Workflow.Rnw
@@
 which, in turn, sources the file named \texttt{Econ-Growth_Functions2.R}.
+\item
+<<>>=
+source("Graphics.R")
+@
 
 \item
-Execute the function called \function{genAllResampleData()}.
+Execute the function called \function{genAllResampleData()} to cache the resampling data.
 
@@
 @
+
 \item Reload the data using one of the various ``load'' functions
@@
 A typical call for loadAllResampleData would be
-<<eval=FALSE>>=
-loadAllResampleData(modelType="cde", energyType="Q")
+
+<<>>=
+head( loadAllResampleData(modelType="cde", energyType="Q"), n=3 )
 @
+
 \item
-Another example:
+Other examples:
 <<>>=
-head(loadAllResampleData(model="sf", factor="K"), n=5)
+head( loadAllResampleData(model="sf", factor="K"), n=3 )
+head( loadAllResampleData(model="linex", energyType = "Q"), n=3 )
+head( loadAllResampleData(model="cese", energyType = "Q"), n=3 )
 @
@@
 \section{Ternary Plots}
-\begin{enumerate}
-\item
-Plots of distributions of coefficients for the Cobb-Douglas 
-with energy model can be made with \function{triPlot()} in 
-file \texttt{Graphics.R}.  (Goofy labels here just to demonstrate what is possible.)
+Plots of distributions of coefficients for the Cobb-Douglas-Energy
+model can be made with \function{standardTriPlot()} in 
+file \texttt{Graphics.R}.  
 <<>>=
-source("Graphics.R")
-resData <- loadAllResampleData(modelType="cde", energyType="Q")
-triPlot(subset(resData, method!="orig"), 
-        gamma, alpha, beta,
-        labels=c("gamma[1]", "alpha[2]", "sqrt(beta[3])"),
-        n.grid=5,  aes_string="color=lambda", 
-        size=3, alpha=.5 ) + 
-     geom_point(data=subset(resData, method=="orig"), 
-                color="red", alpha=1, size=3) +
-     facet_wrap( ~ countryAbbrev )
+standardTriPlot( loadAllResampleData(modelType="cde", energyType="Q") ) +
+  labs(title="Model = CDE; energy=Q")
 @
-Eventually, we can build a wrapper that loads the data and builds the plot with our favorite settings.
-\end{enumerate}
 
+\section{Scatterplots with two variables}
+
+<<>>=
+standardScatterPlot( loadAllResampleData(model="sf", factor="K"), 
+                     aes(lambda, m) ) +
+  labs(title="Model = sf; factor=K", x=expression(lambda))
+@
+
+<<>>=
+standardScatterPlot( loadAllResampleData(model="linex", energyType = "Q"), 
+                     aes(a_0, c_t) ) +
+  labs(title="Model = linex; energy=Q", x=expression(a[0]), y=expression(c[t]))
+@
+
+<<>>=
+standardScatterPlot( loadAllResampleData(model="cese", energyType = "Q"), 
+                     aes(delta, rho) ) +
+  labs(title="Model = cese; energy=Q", x=expression(delta), y=expression(rho))
+@
 \end{document}

### 2013-07-13 Graphics.R

@@ -24,9 +24,19 @@ tri_theme <- function(base_size=12, base_family = "", base_theme=theme_bw) {
             )
   }  
 
+
+xy_theme <- function(base_size=12, base_family = "", base_theme=theme_bw) {
+  base_theme(base_size = base_size, base_family = base_family) %+replace% 
+    theme(panel.border = element_blank(), 
+          panel.grid.major = element_blank(), 
+          panel.grid.minor = element_blank(),
+          plot.background = element_blank(),
+          strip.background =  element_rect(fill = NA, colour = "gray50")
+    )
+}  
 triPlot <- function(data, x, y, z, labels=c("gamma", "alpha", "beta"), 
-                    parse=TRUE, n.grid=4, aes_string="", ...) {
-  h <- seq(0, 1, by=1/n.grid)
+                    parse=TRUE, grid_lines=4, aes_string="", ...) {
+  h <- seq(0, 1, by=1/grid_lines)
   points <- data.frame( h=h )
   if ( nchar(aes_string) > 0 ) aes_string <- paste(",", aes_string)
   
@@ -64,40 +74,32 @@ triPlot <- function(data, x, y, z, labels=c("gamma", "alpha", "beta"),
     geom_point(...)
 }
 
-# an example use
-
-# first we create some fake data with four "countries"
-ddd <- data.frame( x=runif(80) ) 
-ddd <- transform(ddd, y = runif(80, 0, 1-x))
-ddd <- transform(ddd, z = runif(80, 0, 1-x-y))
-ddd <- transform(ddd, country=resample(toupper(letters[1:4]), 80))
-
-# Now we plot the data by providing a data frame, the x, y, and z coordinates
-# computed in that data frame, and any optional arguments (like size and alpha).
-# The order of x, y, and z is top, lower left, lower right.
-# The guidelines are at fixed values of one of the three.  n.grid determines the 
-# number of gridlines to use.
-#
-# This is probably still a bit brittle and may not look good at extreme sizes, but
-# this will get us started.
-
-if(FALSE) {  # examples moved to workflow document on 2013-07-08
-triPlot( ddd, x,y,z, labels=c('x','y','z'), size=3, alpha=.5 ) + 
-  facet_wrap( ~ country )
-
-exampleData <- rbind(
-  resampleFits( "cde", "TZ", "X", method="wild", n=100),
-  resampleFits( "cde", "US", "X", method="wild", n=100),
[…]

### 2013-07-13 EconGrowth.Rnw
Using the new standardScatterPlot code for the first single-factor resampling graph.

@@
 
-<<Unconverged_Frac_Table, results='asis', eval=TRUE>>=
+<<Unconverged_Frac_Table, results='asis'>>=
 printFracUnconvergedXtable()
@@
 
-<<SFk_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single factor model (with $f = k$ and $m = \\alpha$) resampling results.">>=
-sfResamplePlot(factor="K")
+<<SFk_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single factor model (with $f = k$ and $m = \\alpha$) resampling results.", eval=TRUE>>=
+standardScatterPlot(loadAllResampleData(model="sf", factor="K", 
+                                        countryAbbrevsOrder=countryAbbrevsForGraph,
+                                        countryAbbrevsOrderU=countryAbbrevsForGraphU), 
+                    aes(m, lambda)) + 
+  labs(x=expression(alpha), y=expression(lambda))
 @
@@
 
-Converting the resampling data to 95\% confidence intervals
-provides results shown in 
+Converting the resample model coefficient data to 95\% confidence intervals
+gives the results shown in 
 Figures~\ref{fig:SFk_Params_Graph}--\ref{fig:SFu_Params_Graph}.

### 2013-07-13 Workflow.Rnw
Added example of finding fraction of unconverged resample fits.
Added a demonstration of specifying the country order for a graph.

@@
 \end{enumerate}
+
+\item To find the fraction of resample models that do not converge, say
+<<>>=
+fracUnconvergedResampleFitsAll()
+@
+
 \end{enumerate}
@@
 <<>>=
-standardScatterPlot( loadAllResampleData(model="linex", energyType = "Q"), 
+standardScatterPlot( loadAllResampleData(model="linex", energyType = "Q", 
+                                         countryAbbrevsOrder=c("US", "UK", "JP", "CN", 
+                                                               "ZA", "TZ", "SA", "IR", "ZM")), 
                      aes(a_0, c_t) ) +

### 2013-07-13 Workflow.Rnw
Explanation of changing the order of countries on a graph.

@@
 )
+source("Econ-Growth-Functions2.R")
 @
@@
 
+You can change the order of the countries on the graph 
+with the \texttt{countryAbbrevsOrder} argument 
+to \texttt{loadAllResampleData}. 
+The default order is 
+<<>>=
+countryAbbrevs
+@
+However, for the 9-panel graphs, 
+I like to plot in the order shown below, 
+so that the SA/IR and TZ/ZM pairs 
+are adjacent and atop one another, respectively.
+The variable 
+<<>>=
+countryAbbrevsForGraph
+@
+\noindent in file \texttt{Econ-Growth-Functions2.R} contains the preferred
+order for 9-panel graphs, as demonstrated below.
 <<>>=
 standardScatterPlot( loadAllResampleData(model="linex", energyType = "Q", 
-                                         countryAbbrevsOrder=c("US", "UK", "JP", "CN", 
-                                                               "ZA", "TZ", "SA", "IR", "ZM")), 
+                                         countryAbbrevsOrder=countryAbbrevsForGraph), 
                      aes(a_0, c_t) ) +

### 2013-07-13 EconGrowth.Rnw
Now using Randy's graph function for all SF scatter plots.

@@
 standardScatterPlot(loadAllResampleData(model="sf", factor="K", 
-                                        countryAbbrevsOrder=countryAbbrevsForGraph,
-                                        countryAbbrevsOrderU=countryAbbrevsForGraphU), 
+                                        countryAbbrevsOrder=countryAbbrevsForGraph), 
                     aes(m, lambda)) + 
@@
 
-<<SFl_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single factor model (with $f = l$ and $m = \\beta$) resampling results.">>=
-sfResamplePlot(factor="L")
-@
-
-<<SFq_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single factor model (with $f = q$ and $m = \\gamma$) resampling results.">>=
-sfResamplePlot(factor="Q")
-@
-
-<<SFx_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single factor model (with $f = x$ and $m = \\gamma$) resampling results.">>=
-sfResamplePlot(factor="X")
-@
-
-<<SFu_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="Single factor model (with $f = u$ and $m = \\gamma$) resampling results.">>=
-sfResamplePlot(factor="U")
+<<SFl_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single factor model (with $f = l$ and $m = \\beta$) resampling results.", eval=TRUE>>=
+standardScatterPlot(loadAllResampleData(model="sf", factor="L", 
+                                        countryAbbrevsOrder=countryAbbrevsForGraph), 
+                    aes(m, lambda)) + 
+  labs(x=expression(beta), y=expression(lambda))
+@
+
+<<SFq_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single factor model (with $f = q$ and $m = \\gamma$) resampling results.", eval=TRUE>>=
+standardScatterPlot(loadAllResampleData(model="sf", factor="Q", 
+                                        countryAbbrevsOrder=countryAbbrevsForGraph), 
+                    aes(m, lambda)) + 
+  labs(x=expression(gamma), y=expression(lambda))
+@
+
+<<SFx_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single factor model (with $f = x$ and $m = \\gamma$) resampling results.", eval=TRUE>>=
+standardScatterPlot(loadAllResampleData(model="sf", factor="X", 
+                                        countryAbbrevsOrder=countryAbbrevsForGraph), 
+                    aes(m, lambda)) + 
+  labs(x=expression(gamma), y=expression(lambda))
+@
+
+<<SFu_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="Single factor model (with $f = u$ and $m = \\gamma$) resampling results.", eval=TRUE>>=
+standardScatterPlot(loadAllResampleData(model="sf", factor="U", 
+                                        countryAbbrevsOrder=countryAbbrevsForGraphU), 
+                    aes(m, lambda)) + 
+  labs(x=expression(gamma), y=expression(lambda))
 @

### 2013-07-13 Econ-Growth-Functions2.R

@@ -3384,9 +3384,7 @@ loadResampleData <- function(modelType, countryAbbrev, energyType, factor){
   return(resampleData)
 }
 
-loadAllResampleData <- function(modelType, energyType, factor, 
-                                countryAbbrevsOrder=countryAbbrevs,
-                                countryAbbrevsOrderU=countryAbbrevsU){
+loadAllResampleData <- function(modelType, energyType, factor, countryAbbrevsOrder=countryAbbrevs){
   ##################
   # Loads resample data for all countries for the given modelType and energyType or factor
   ##
@@ -3396,13 +3394,13 @@ loadAllResampleData <- function(modelType, energyType, factor,
   }
   if (!missing(energyType)){
     if (energyType == "U"){
-      data <- do.call("rbind", lapply(countryAbbrevsOrderU, loadResampleData, modelType=modelType, energyType=energyType))
+      data <- do.call("rbind", lapply(countryAbbrevsOrder, loadResampleData, modelType=modelType, energyType=energyType))
     } else {
       data <- do.call("rbind", lapply(countryAbbrevsOrder, loadResampleData, modelType=modelType, energyType=energyType))
     }
   } else if (!missing(factor)){
     if (factor == "U"){
-      data <- do.call("rbind", lapply(countryAbbrevsOrderU, loadResampleData, modelType=modelType, factor=factor))
+      data <- do.call("rbind", lapply(countryAbbrevsOrder, loadResampleData, modelType=modelType, factor=factor))
     } else {
       data <- do.call("rbind", lapply(countryAbbrevsOrder, loadResampleData, modelType=modelType, factor=factor))
     }

### 2013-07-13 EconGrowth.Rnw
Now using rewritten sfResamplePlot for all SF resample graphs.

--- 2013-07-12 EconGrowth.Rnw
@@
 
-<<LINEXq_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX model (with $q$) resampling results." >>=
+<<LINEXq_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX model (with $q$) resampling results.">>=
+# linexResamplePlot(energyType="Q")
 linexResamplePlot(energyType="Q")

### 2013-07-15 EconGrowth.Rnw
Moved the location of the scatter plots for CES models with energy to be AFTER the partial residual plots.
Edited the text of the CDe section. Edited the to-do list. Changed names of resample plots for CES to be consistent with SF, CD, and LINEX.

@@
 \begin{itemize}
-\item{Pruim: Add base fit red dots to all cloud plots.}
-      \begin{itemize}
-      \item{SF}
-      \item{\st{CD}}
-      \item{\st{CDe}}
-      \item{CES}
-      \item{CESe}
-      \item{LINEX}
-      \end{itemize}
+\itme{Heun: Look into constraining $\delta \in [0,1]$
+and $\delta_1 \in [0,1]$}
+\item{Pruim: Respond to Heun's wish list for graphs.}
 \item{Heun: Figure out why CESe for ZA with $x$ fails during resampling.}
@@
 \item{\st{Heun: Get AIC calculations working again.}}
+\item{\st{Pruim: Add base fit red dots to all cloud plots.}}
+      \begin{itemize}
+      \item{\st{SF}}
+      \item{\st{CD}}
+      \item{\st{CDe}}
+      \item{\st{CES}}
+      \item{\st{CESe}}
+      \item{\st{LINEX}}
+      \end{itemize}
 \end{itemize}
@@
 Equation~\ref{eq:CES} is a degenerate form of Equation~\ref{eq:CESe} 
-where $\delta = 1$. The elasticity of substitution between capital ($k$) 
-and labor ($l$) is given by $\sigma_1 = \frac{1}{1+\rho_1}$, 
+where $\delta = 1$ and $\rho = -1$. The elasticity of substitution 
+between capital ($k$) and labor ($l$) is given by 
+$\sigma_1 = \frac{1}{1+\rho_1}$, 
 the elasticity of substitution between ($kl$) and ($e$) is given by 
-$\sigma = \frac{1}{1+\rho}$, $\delta \in [0, 1]$ describes the importance 
-of ($kl$) relative to ($e$), and $\gamma$ is a fitting parameter, 
-expected to be close to unity. As $\sigma \rightarrow \infty$, 
-($kl$) and ($e$) are perfect substitutes. As $\sigma \rightarrow 0$, 
-($kl$) and ($e$) are perfect complements: no substitution is possible.
+$\sigma = \frac{1}{1+\rho}$, 
+$\delta_1 \in [0, 1]$ describes the relative importance of capital ($k$)
+and labor ($l$), 
+$\delta \in [0, 1]$ describes the importance 
+of ($kl$) relative to ($e$), 
+and $\gamma$ is a fitting parameter, 
+expected to be close to unity. 
+As $\sigma \rightarrow \infty$ ($\rho \rightarrow -1$), 
+($kl$) and ($e$) are perfect substitutes. 
+As $\sigma \rightarrow 0$ ($\rho \rightarrow \infty$), 
+($kl$) and ($e$) are perfect complements: 
+no substitution is possible. Similarly,
 
@@
 
-\noindent According to the LINEX model, an economy that can increase 
+\noindent According to the LINEX model, an economy that increases 
 capital stock ($k$) without a commensurate increase in labor ($l$) 
@@
 \noindent to ensure $\alpha + \beta = 1$ for constant returns to scale. 
-By constraining $\alpha \in [0,1]$, we ensure that $\beta \in [0,1]$ also. 
-**** Is this truly how we implemented the constraints? 
-Finish after we actually implement the constraints. **** 
-$\lambda$ and $\alpha$ were estimated by the \citet{R} function \texttt{nls}. 
-The value of $\beta$ can be found with $\beta = 1 - \alpha$. 
-Figure~\ref{fig:CD_Params_Graph} shows values of and 95\% confidence intervals 
-for $\lambda$ and $\alpha$. Appendix~\ref{sec:Model_Parameters} 
-contains tables with numerical values of model parameters and confidence intervals.
+$\lambda$ and $\alpha$ were estimated by the 
+\texttt{R} \citep{R} function \texttt{nls}. 
+If the estimated value for $\alpha$ was found outside the interval $[0,1]$, 
+we set $\alpha$ to its boundary value and re-estimated $\lambda$. 
+The value of $\beta$ was found with $\beta = 1 - \alpha$.
 
@@
 provides data for Figure~\ref{fig:CD_Params_Graph}.
+Appendix~\ref{sec:Model_Parameters} 
+contains tables with numerical values of 
+Cobb-Douglas model parameters and 95\% confidence intervals.
 
@@
 
-\begin{equation} \label{eq:CDe_reparam}
-  y = A k^{\min(a,b)}l^{|b-a|}e^{1 - \max(a,b)}; A = \mathrm{e}^{\lambda (t-t_0)}
+\begin{equation} \label{eq:CDe_AB_reparam}
+  y = A k^{\min(a,b)} l^{|b-a|} e^{1 - \max(a,b)}; A = \mathrm{e}^{\lambda (t-t_0)}
 \end{equation}
 
-\noindent to ensure that $\alpha + \beta + \gamma = 1$. 
-By constraining $a \in [0,1]$ and $b \in [0,1]$, 
-we ensure that $\alpha \in [0,1]$, $\beta \in [0,1]$, and $\gamma \in [0,1]$. 
-Given values of $a$ and $b$ that represent the least-squares parameter 
-optimization for a given economy, 
+\noindent with 
 $\alpha = \min(a,b)$, 
 $\beta = |b-a|$, and 
-$\gamma = \max(a,b)$ 
-can be calculated. 
-The \citet{R} function \texttt{nls} was used to estimate the 
-least-squares values of $\lambda$, $a$, and $b$.
-
-The Cobb-Douglas with energy parameter estimation process is challenging. 
+$\gamma = 1 - \max(a,b)$.
+The reparameterization ensures that $\alpha + \beta + \gamma = 1$. 
+The \texttt{R} \citep{R} function \texttt{nls} was used to estimate 
+values of $\lambda$, $a$, and $b$.
+If the fitted value for $a$ ($b$) fell outside $[0,1]$, it was 
+set equal to its boundary value and $\lambda$ and $b$ ($a$) 
+were re-estimated.
+
 To demonstrate the characteristics of the parameter estimation process, 
@@
 $\gamma$ with thermal energy ($q$).
-For most economies, the minimum $SSE$ occurs at a boundary of $\alpha$, 
-$\beta$, or $\gamma$. 
-The parameter estimation algorithm has difficulty assessing confidence 
-intervals for $\alpha$, $\beta$, and $\gamma$, because the constrained 
-model behaves very differently on either side of the constraint.
-
-**** Fix the right y axis label. SSE should be italicized. 
+
+**** Fix the right y axis label. SSE should be italicized ($SSE$). 
 Also, scaling on the axis labels and scales is not being picked up. ****
@@
 
-Figure~\ref{fig:CDq_Cloud_Graph} shows $\alpha$, $\beta$, and $\gamma$ parameter values for resample models for the Cobb-Douglas model (with $q$).
+Figure~\ref{fig:CDeGridLattice} shows that, for most economies,
+the minimum $SSE$ occurs at or near a boundary of 
+$\alpha$, $\beta$, or $\gamma$. 
+The parameter estimation algorithm (\texttt{nls}) had difficulty converging when
+the optimal value for the parameter represented by the absolute value function 
+(in Equation~\ref{eq:CDe_AB_reparam}, $\beta$) 
+was near a boundary. If the absolute value caused non-convergence of the 
+\texttt{nls} function, second and, if necessary, third reparameterizations 
+were attempted:
+
+\begin{equation} \label{eq:CDe_CD_reparam}
+  y = A k^{1 - \max(c,d)} l^{\min(c,d)} e^{|d-c|}; A = \mathrm{e}^{\lambda (t-t_0)}
+\end{equation}
+
+\begin{equation} \label{eq:CDe_FG_reparam}
+  y = A k^{|g-f|} l^{1 - \max(f,g)} e^{\min(f,g)}; A = \mathrm{e}^{\lambda (t-t_0)}
+\end{equation}
+
+\noindent If none of the three reparameterizations converged, 
+the parameterization with the smallest $SSE$
+was used. \ref{sec:Convergence_Resample_Models} shows the 
+fraction of unconverged models for each model type. The above approach
+resulted in very few unconverged resample models, 
+even with \Sexpr{numResamples()} resamples.
+
+Figure~\ref{fig:CDq_Cloud_Graph} shows $\alpha$, $\beta$, and $\gamma$ 
+parameter values for Cobb-Douglas (with $q$) resample models.
 
@@
 <<CES_lambda_gamma_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\lambda$ and $\\gamma$.">>=
-cesLambdaGammaResamplePlot(energyType=NA)
+cesResamplePlotLambdaGamma(energyType=NA)
 @
@@
 <<CES_sigma_1_delta_1_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
-cesSigma_1Delta_1ResamplePlot(energyType=NA)
+cesResamplePlotSigma_1Delta_1(energyType=NA)
 @
@@
 <<CES_sigma_delta_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\rho$ and $\\delta$.">>=
-cesSigmaDeltaResamplePlot(energyType=NA)
-@
-
-Coefficients for each resampled CES model (with $q$)
-are shown in 
-Figures~\ref{fig:CESq_lambda_gamma_Cloud_Graph}--\ref{fig:CESq_sigma_delta_Cloud_Graph}.
-
-<<CESq_lambda_gamma_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$) resample model parameters $\\lambda$ and $\\gamma$.">>=
-cesLambdaGammaResamplePlot(energyType="Q")
-@
-
-<<CESq_sigma_1_delta_1_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
-cesSigma_1Delta_1ResamplePlot(energyType="Q")
-@
-
-<<CESq_sigma_delta_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$) resample model parameters $\\sigma$ and $\\delta$.">>=
-cesSigmaDeltaResamplePlot(energyType="Q")
-@
-
-Coefficients for each resampled CES model (with $x$)
-are shown in 
-Figures~\ref{fig:CESx_lambda_gamma_Cloud_Graph}--\ref{fig:CESx_sigma_delta_Cloud_Graph}.
-
-<<CESx_lambda_gamma_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$) resample model parameters $\\lambda$ and $\\gamma$.">>=
-cesLambdaGammaResamplePlot(energyType="X")
-@
-
-<<CESx_sigma_1_delta_1_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
-cesSigma_1Delta_1ResamplePlot(energyType="X")
-@
-
-<<CESx_sigma_delta_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$) resample model parameters $\\sigma$ and $\\delta$.">>=
-cesSigmaDeltaResamplePlot(energyType="X")
-@
-
-Coefficients for each resampled CES model (with $u$)
-are shown in 
-Figures~\ref{fig:CESu_lambda_gamma_Cloud_Graph}--\ref{fig:CESu_sigma_delta_Cloud_Graph}.
-
-<<CESu_lambda_gamma_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$) resample model parameters $\\lambda$ and $\\gamma$.">>=
-cesLambdaGammaResamplePlot(energyType="U")
-@
-
-<<CESu_sigma_1_delta_1_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
-cesSigma_1Delta_1ResamplePlot(energyType="U")
-@
-
-<<CESu_sigma_delta_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$) resample model parameters $\\sigma$ and $\\delta$.">>=
-cesSigmaDeltaResamplePlot(energyType="U")
+cesResamplePlotSigmaDelta(energyType=NA)
 @
@@
 createPartialResidualPlot(modelType="CES", energyType="U", countryAbbrev=NA)
+@
+
+Coefficients for each resampled CES model (with $q$)
+are shown in 
+Figures~\ref{fig:CESq_lambda_gamma_Cloud_Graph}--\ref{fig:CESq_sigma_delta_Cloud_Graph}.
+
+<<CESq_lambda_gamma_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$) resample model parameters $\\lambda$ and $\\gamma$.">>=
+cesResamplePlotLambdaGamma(energyType="Q")
+@
+
+<<CESq_sigma_1_delta_1_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
+cesResamplePlotSigma_1Delta_1(energyType="Q")
+@
+
+<<CESq_sigma_delta_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$) resample model parameters $\\sigma$ and $\\delta$.">>=
+cesResamplePlotSigmaDelta(energyType="Q")
+@
+
+Coefficients for each resampled CES model (with $x$)
+are shown in 
+Figures~\ref{fig:CESx_lambda_gamma_Cloud_Graph}--\ref{fig:CESx_sigma_delta_Cloud_Graph}.
+
+<<CESx_lambda_gamma_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$) resample model parameters $\\lambda$ and $\\gamma$.">>=
+cesResamplePlotLambdaGamma(energyType="X")
+@
+
+<<CESx_sigma_1_delta_1_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
+cesResamplePlotSigma_1Delta_1(energyType="X")
+@
+
+<<CESx_sigma_delta_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$) resample model parameters $\\sigma$ and $\\delta$.">>=
+cesResamplePlotSigmaDelta(energyType="X")
+@
+
+Coefficients for each resampled CES model (with $u$)
+are shown in 
+Figures~\ref{fig:CESu_lambda_gamma_Cloud_Graph}--\ref{fig:CESu_sigma_delta_Cloud_Graph}.
+
+<<CESu_lambda_gamma_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$) resample model parameters $\\lambda$ and $\\gamma$.">>=
+cesResamplePlotLambdaGamma(energyType="U")
+@
+
+<<CESu_sigma_1_delta_1_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
+cesResamplePlotSigma_1Delta_1(energyType="U")
+@
+
+<<CESu_sigma_delta_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$) resample model parameters $\\sigma$ and $\\delta$.">>=
+cesResamplePlotSigmaDelta(energyType="U")
 @

### 2013-07-15 Econ-Growth-Functions2.R

@@ -2465,7 +2465,7 @@ printCESParamsTableB <- function(energyType){
         table.placement="H")
 }
 
-cesLambdaGammaResamplePlot <- function(energyType=NA, ...){
+cesResamplePlotLambdaGamma <- function(energyType=NA, ...){
   ##################
   # A wrapper function for twoVarCloudPlot that binds data for all countries
   # and sends to the graphing function.
@@ -2481,7 +2481,7 @@ cesLambdaGammaResamplePlot <- function(energyType=NA, ...){
   return(graph)
 }
 
-cesSigma_1Delta_1ResamplePlot <- function(energyType=NA, ...){
+cesResamplePlotSigma_1Delta_1 <- function(energyType=NA, ...){
   ##################
   # A wrapper function for twoVarCloudPlot that binds data for all countries
   # and sends to the graphing function.
@@ -2497,7 +2497,7 @@ cesSigma_1Delta_1ResamplePlot <- function(energyType=NA, ...){
   return(graph)
 }
 
-cesSigmaDeltaResamplePlot <- function(energyType=NA, ...){
+cesResamplePlotSigmaDelta <- function(energyType=NA, ...){
   ##################
   # A wrapper function for twoVarCloudPlot that binds data for all countries
   # and sends to the graphing function.
@@ -3585,4 +3585,8 @@ printFracUnconvergedXtable <- function(){
         size="\\tiny",
         table.placement="H",
         include.rownames=FALSE)
+}
+
+numResamples <- function(){
+  return(1000)
 }

### 2013-07-15 Econ-Growth-Resampling.R

@@ -12,7 +12,7 @@ source('Econ-Growth-Functions2.R')
 # We do this multiple times and save a file that contains 
 # the results for later investigation
 
-genAllResampleData <- function(method="wild", n=100){
+genAllResampleData <- function(method="wild", n=numResamples()){
   #######################
   # Generates all resampling data for all models using the method specified
   ##

### 2013-07-15 EconGrowth.Rnw
Edited to-do list.
Improved description of CES production function.

@@
 \begin{itemize}
-\itme{Heun: Look into constraining $\delta \in [0,1]$
-and $\delta_1 \in [0,1]$}
+\item{Heun: Look into constraining $\delta \in [0,1]$
+and $\delta_1 \in [0,1]$ in the CES and CES$e$ models.}
 \item{Pruim: Respond to Heun's wish list for graphs.}
@@
 Other energy economists use an energy-augmented 
-Constant Elasticity of Substitution (CESe) production function to 
+Constant Elasticity of Substitution (CES$e$) production function to 
 describe economic growth. The \texttt{R} \citep{R} package 
@@
 Equation~\ref{eq:CES} is a degenerate form of Equation~\ref{eq:CESe} 
-where $\delta = 1$ and $\rho = -1$. The elasticity of substitution 
+where $\delta \rightarrow 1$ and $\rho \rightarrow -1$.
+
+Constraints on the fitting parameters include 
+$\delta_1 \in (0,1)$,
+$\delta \in (0,1)$,
+$\rho_1 \in (-1,0) \cup (0,\infty)$, and
+$\rho \in (-1,0) \cup (0,\infty)$.
+The elasticity of substitution 
 between capital ($k$) and labor ($l$) is given by 
@@
 of ($kl$) relative to ($e$), 
-and $\gamma$ is a fitting parameter, 
-expected to be close to unity. 
+and $\gamma$ is a fitting parameter that represents productivity. 
 As $\sigma \rightarrow \infty$ ($\rho \rightarrow -1$), 
@@
 no substitution is possible. Similarly, 
+as $\sigma_1 \rightarrow 0$ ($\rho_1 \rightarrow \infty$),
+$k$ and $l$ are perfect complements.
 

### 2013-07-15 EconGrowth.Rnw
Improved description of CES production function.

@@
 and $\delta_1 \in [0,1]$ in the CES and CES$e$ models.}
+\item{Heun: Investigate why wew obtain $\rho_1 < -1$ 
+for some US CES$e$ resample models.}
 \item{Pruim: Respond to Heun's wish list for graphs.}
@@
 
-Constraints on the fitting parameters include 
-$\delta_1 \in (0,1)$,
-$\delta \in (0,1)$,
-$\rho_1 \in (-1,0) \cup (0,\infty)$, and
-$\rho \in (-1,0) \cup (0,\infty)$.
+$\gamma$ is a fitting parameter that represents productivity. 
+The fitting parameters $\rho_1$ and $\rho$ indicate elasticities 
+of substitution ($\sigma_1$ and $\sigma$).
 The elasticity of substitution 
 between capital ($k$) and labor ($l$) is given by 
-$\sigma_1 = \frac{1}{1+\rho_1}$, 
+$\sigma_1 = \frac{1}{1+\rho_1}$, and
 the elasticity of substitution between ($kl$) and ($e$) is given by 
-$\sigma = \frac{1}{1+\rho}$, 
-$\delta_1 \in [0, 1]$ describes the relative importance of capital ($k$)
-and labor ($l$), 
-$\delta \in [0, 1]$ describes the importance 
-of ($kl$) relative to ($e$), 
-and $\gamma$ is a fitting parameter that represents productivity. 
+$\sigma = \frac{1}{1+\rho}$. 
+As $\rho_1 \rightarrow 0$, $\sigma_1 \rightarrow 1$,
+and the embedded CES production function for $k$ and $l$ degenerates 
+to the Cobb-Douglas production function.
+Similarly, as $\rho \rightarrow 0$, $\sigma \rightarrow 1$,
+and the CES production function for $(kl)$ and $(e)$ degenerates 
+to the Cobb-Douglas production function.
 As $\sigma \rightarrow \infty$ ($\rho \rightarrow -1$), 
@@
 $k$ and $l$ are perfect complements.
+$\delta_1$ describes the relative importance of capital ($k$)
+and labor ($l$), and
+$\delta$ describes the importance of ($kl$) relative to ($e$).
+
+Constraints on the fitting parameters include 
+$\delta_1 \in (0,1)$,
+$\delta \in (0,1)$,
+$\rho_1 \in (-1,0) \cup (0,\infty)$, and
+$\rho \in (-1,0) \cup (0,\infty)$. **** Describe here how 
+we implemented the constraints. ****
 

### 2013-07-19 EconGrowth.Rnw
Edited to-do list.

@@
 \begin{itemize}
-\item{Heun: Look into constraining $\delta \in [0,1]$
-and $\delta_1 \in [0,1]$ in the CES and CES$e$ models.}
+\item{Heun: Figure out why CES$q$ model fails to converge with original data for JP and CN.}
 \item{Heun: Investigate why wew obtain $\rho_1 < -1$ 
@@
       \end{itemize}
+\item{\st{Heun: Look into constraining $\delta \in [0,1]$
+and $\delta_1 \in [0,1]$ in the CES and CES$e$ models.}}
 \end{itemize}

### 2013-07-19 CES.Rnw
Created a new file (CES.Rnw) to describe the travails of fitting the CES model. This will, hopefully, document the details for Randy's review and thoughts.

\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{language} % Obtain language.sty from https://github.com/rpruim/latex
\usepackage{underscore} % Should be part of any LaTeX distribution.

\title{Parameter Estimation for the CES Model}
\author{Matthew Kuperus Heun}
\begin{document}

<<setup, include=FALSE>>=
require(knitr)
opts_chunk$set(
  tidy=FALSE
)
source("Econ-Growth-Functions2.R")
@

\maketitle

%------------------------------
\section{Energy-augmented CES Production Function (CESe)} 
\label{sec:CES}
%------------------------------

The CES model without energy is

\begin{equation} \label{eq:CES}
  y = \gamma \: A \: \left[\delta_1 k^{-\rho_1} 
      + (1-\delta_1)l^{-\rho_1} \right]^{-1/\rho_1}; 
      A = \mathrm{e}^{\lambda (t-t_0)}
\end{equation}

\begin{itemize}
\item
Equation~\ref{eq:CES} is a CES production function with 
capital stock ($k$) and labor ($l$) factors of production. 
\item
$\gamma$ is a fitting parameter that represents productivity. 
\item
$\delta_1$ describes the importance of ($k$) relative to ($l$).
\item
The fitting parameter $\rho_1$ indicates elasticity
of substitution ($\sigma_1$) between capital ($k$) 
and labor ($l$). $\sigma_1 = \frac{1}{1+\rho_1}$.
\item
As $\rho_1 \rightarrow 0$, $\sigma_1 \rightarrow 1$,
and the embedded CES production function for $k$ and $l$ degenerates 
to the Cobb-Douglas production function.
\item
As $\sigma_1 \rightarrow 0$ ($\rho_1 \rightarrow \infty$),
$k$ and $l$ are perfect complements.
\item
As $\sigma_1 \rightarrow \infty$ ($\rho_1 \rightarrow -1$),
$k$ and $l$ are perfect substitutes.
\item
Constraints on the fitting parameters include 
  \begin{itemize}
  \item $\delta_1 \in (0,1)$
  \item $\rho_1 \in (-1,0) \cup (0,\infty)$
  \item $\sigma_1 \in (0,1) \cup (1,\infty)$
  \end{itemize}

\end{itemize}

The CES model with energy is

\begin{equation} \label{eq:CESe}
  y = \gamma \: A \: \left\{\delta \left[\delta_1 k^{-\rho_1} 
      + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1} 
      + (1-\delta) e^{-\rho} \right\}^{-1/\rho}; 
      A = \mathrm{e}^{\lambda (t-t_0)}
\end{equation}

\begin{itemize}
\item
Equation~\ref{eq:CESe} augments Equation~\ref{eq:CES} with energy 
using a ($kl$)($e$) nesting structure, as is typical in the literature. 
\item
$\delta$ describes the importance of the capital/labor pair ($kl$) relative to ($e$).
\item
The fitting parameter $\rho$ indicates elasticity
of substitution ($\sigma$) between the capital/labor pair ($kl$) 
and energy ($e$). $\sigma = \frac{1}{1+\rho}$.
\item
As $\rho \rightarrow 0$, $\sigma \rightarrow 1$,
and the CES production function for $(kl)$ and $(e)$ degenerates 
to the Cobb-Douglas production function.
\item
As $\sigma \rightarrow \infty$ ($\rho \rightarrow -1$), 
($kl$) and ($e$) are perfect substitutes. 
\item
As $\sigma \rightarrow 0$ ($\rho \rightarrow \infty$), 
($kl$) and ($e$) are perfect complements: 
no substitution is possible. 
\item 
Constraints on the fitting parameters include 
  \begin{itemize}
  \item $\delta \in (0,1)$,
  \item $\rho \in (-1,0) \cup (0,\infty)$.
  \item $\sigma \in (0,1) \cup (1,\infty)$
  \end{itemize}
\item
Equation~\ref{eq:CES} is a degenerate form of Equation~\ref{eq:CESe} 
where $\delta \rightarrow 1$ and $\rho \rightarrow -1$ 
($\sigma \rightarrow \infty$). 
\end{itemize}

The \texttt{R} package \texttt{micEcon} provide function 
\texttt{cesEst} for estimating the parameters of the CES model.
If we use cesEst ``out of the box,'' which uses the
Levenberg-Marquardt (\texttt{LM}) optimization method, 
we often obtain parameter
estimates that violate the constraints above.

<<>>=
dataUK <- loadData(countryAbbrev="UK")
modelUKQ_LM <- cesEst(data=dataUK, yName="iGDP", xNames=c("iCapStk", "iLabor", "iQ"), tName="iYear")
summary(modelUKQ_LM)
@

In the above example, we obtain $\rho_1 = $ \Sexpr{coef(modelUKQ_LM)["rho_1"]} 
which violates the constraint $\rho_1 \in (-1,0) \cup (0,\infty)$.

\end{document}

### 2013-07-19 CES.Rnw
Adding the L-BFGS-B and grid search to CES.Rnw.

@@
 dataUK <- loadData(countryAbbrev="UK")
-modelUKQ_LM <- cesEst(data=dataUK, yName="iGDP", xNames=c("iCapStk", "iLabor", "iQ"), tName="iYear")
+modelUKQ_LM <- cesEst(data=dataUK, 
+                      yName="iGDP", 
+                      xNames=c("iCapStk", "iLabor", "iQ"), 
+                      tName="iYear")
 summary(modelUKQ_LM)
@@
 
-In the above example, we obtain $\rho_1 = $ \Sexpr{coef(modelUKQ_LM)["rho_1"]} 
-which violates the constraint $\rho_1 \in (-1,0) \cup (0,\infty)$.
+In the above example, we obtain convergence of the curve-fitting routine.
+But, we also obtain an estimate of $\rho_1 = $ \Sexpr{coef(modelUKQ_LM)["rho_1"]} 
+that violates the constraint $\rho_1 \in (-1,0) \cup (0,\infty)$. 
+This violation leads to $\sigma_1$ (\texttt{E_1_2 (HM)}) being undefined (\texttt{NA})
+in the model summary.
+
+To respect the constraints, we can use the \texttt{L-BFGS-B} optimization
+method. The default guess parameters are
+
+<<>>=
+modelUKQ_LBFGSB <- cesEst(data=dataUK, 
+                          yName="iGDP", 
+                          xNames=c("iCapStk", "iLabor", "iQ"), 
+                          tName="iYear",
+                          method="L-BFGS-B")
+summary(modelUKQ_LBFGSB)
+@
+
+This approach correctly respects the constraints, 
+but the \texttt{LM} algorithm does not converge.
+
+To assess what is happening, we can use the built-in grid search
+capability of \texttt{cesEst}. Grid search is accessed by specifying
+rho or rho1 arguments and a range of values.
+
+<<>>=
+modelUKQ_grid <- cesEst(data=dataUK, yName="iGDP", xNames=c("iCapStk", "iLabor", "iQ"), tName="iYear")
+modelUKQ_grid <- cesEst(data=dataUK, 
+                        yName="iGDP", 
+                        xNames=c("iCapStk", "iLabor", "iQ"), 
+                        tName="iYear",
+                        method="L-BFGS-B",
+                        rho=seq(from=1, to=20, by=2), 
+                        rho1=seq(from=1, to=2, by=0.2))
+summary(modelUKQ_grid)
+@
+
+<<>>=
+plot(modelUKQ_grid)
+@
 

### 2013-07-19 CES.Rnw
Adjusted bounds on the graph.

@@
                         rho=seq(from=1, to=20, by=2), 
-                        rho1=seq(from=1, to=2, by=0.2))
+                        rho1=seq(from=-0.5, to=2, by=0.5))
 summary(modelUKQ_grid)

### 2013-07-19 CES.Rnw
Now creating graphs of SSE vs. rho and rho_1 for UK CES with q.

--- 2013-07-19 CES.Rnw
@@
 \usepackage{underscore} % Should be part of any LaTeX distribution.
+\usepackage{float} % For precise figure positioning.
 
@@
 
-This approach correctly respects the constraints, 
+The above approach correctly respects the constraints, 
 but the \texttt{LM} algorithm does not converge.
@@
 <<>>=
-modelUKQ_grid <- cesEst(data=dataUK, yName="iGDP", xNames=c("iCapStk", "iLabor", "iQ"), tName="iYear")
 modelUKQ_grid <- cesEst(data=dataUK, 
@@
                         method="L-BFGS-B",
-                        rho=seq(from=1, to=20, by=2), 
-                        rho1=seq(from=1, to=2, by=0.2))
+                        rho=seq(from=5, to=30, by=5), 
+                        rho1=seq(from=-0.5, to=1.5, by=0.5))
 summary(modelUKQ_grid)
@@
 
-<<>>=
+The negative of the $SSE$ values from the grid search can be plotted as a function of 
+$\rho$ and $\rho_1$ quite easily, as shown in Figure~\ref{fig:UKQ-grid-coarse}.
+The \texttt{plot} function puts the negative of $SSE$ on the $z$ axis, 
+so better curve fits appear as higher on the $z$ axis of this plot.
+
+<<UKQ-grid-coarse, fig.pos="H", fig.cap="$-SSE$ vs. $\\rho$ and $\\rho_1$. Coarse grid.">>=
 plot(modelUKQ_grid)
@@
 
+To explore the details at high values of $\rho$ and values of 
+$\rho_1 \rightarrow -1$, we can do a detailed analysis\dots
+
+<<>>=
+modelUKQ_grid_detail <- cesEst(data=dataUK, 
+                        yName="iGDP", 
+                        xNames=c("iCapStk", "iLabor", "iQ"), 
+                        tName="iYear",
+                        method="L-BFGS-B",
+                        rho=seq(from=14, to=20, by=1), 
+                        rho1=seq(from=-0.95, to=-0.5, by=0.05))
+summary(modelUKQ_grid_detail)
+@
+
+{\dots}and build a graph as shown in Figure~\ref{fig:UKQ-grid-fine}.
+
+<<UKQ-grid-fine, fig.pos="H", fig.cap="$-SSE$ vs. $\\rho$ and $\\rho_1$. Fine grid.">>=
+plot(modelUKQ_grid_detail)
+@
+
+The best fit for the UK appears to be $\rho_1 \rightarrow -1$ ($\sigma_1 \rightarrow \infty$, meaning perfect subsitutibility between $k$ and $l$).
+It is unclear why there is a sudden dropoff in $-SSE$ at larger values of $\rho$.
+
 \end{document}

### 2013-07-19 CES.Rnw
Added additional comments at the end of the document.

@@
 
-The best fit for the UK appears to be $\rho_1 \rightarrow -1$ ($\sigma_1 \rightarrow \infty$, meaning perfect subsitutibility between $k$ and $l$).
-It is unclear why there is a sudden dropoff in $-SSE$ at larger values of $\rho$.
+The best fit for the UK appears to be $\rho_1 \rightarrow -1$ 
+($\sigma_1 \rightarrow \infty$, 
+meaning perfect subsitutibility between $k$ and $l$). 
+The sudden dropoff in $-SSE$ at larger values of $\rho$ 
+should be investigated.
+
+Figure~\ref{fig:UKQ-grid-fine} makes it clear 
+that it will be difficult to achieve convergence 
+for the UK CES model with $q$ unless the cause of the steep
+dropoff can be understood.
 

### 2013-07-19 CES.Rnw
Added a suggestion for how we could fit CES with constraints.

@@
 
+It is possible to set $\rho_1$ to a specific number 
+(in this case, we could choose $\rho_1 = -0.99$; $-1.0$ would 
+blow up)
+and have \texttt{cesEst} fit the remaining parameters.
+If we went this route, we would be going in a direction that
+is similar to our approach to the constraints
+on the Cobb-Douglas model, wherein we fit the unconstrained 
+model first. If the unconstrained fit violates any constraints, 
+we set the offending parameter at the constraint 
+and re-fit the remaining the parameters.
+
 \end{document}

### 2013-07-20 CES.Rnw
Lots of updates dealing with alternatives to the standard CES fit.

--- 2013-07-19 CES.Rnw
@@
 %------------------------------
-\section{Energy-augmented CES Production Function (CESe)} 
+\section{CES Production Function} 
 \label{sec:CES}
@@
 \item
+As $\delta \rightarrow 1$, the energy term ($e$) 
+becomes increasingly unimportant for the model.
+\item
 The fitting parameter $\rho$ indicates elasticity
@@
 
+%------------------------------
+\section{Fitting Without Constraints} 
+\label{sec:CES-without-constraints}
+%------------------------------
+
 The \texttt{R} package \texttt{micEcon} provide function 
 \texttt{cesEst} for estimating the parameters of the CES model.
-If we use cesEst ``out of the box,'' which uses the
+If we use \texttt{cesEst} ``out of the box,'' which uses the
 Levenberg-Marquardt (\texttt{LM}) optimization method, 
@@
 estimates that violate the constraints above. 
+The default starting values for the fitting parameters are 
+\begin{itemize}
+\item $\lambda = 0.015$
+\item $\gamma = $ a value that makes the mean of the residuals is zero under certain assumptions
+\item $\delta = 0.5$
+\item $\delta_1 = 0.5$
+\item $\rho = 0.25$ (implying that $\sigma = 0.8$) (if not otherwise specified)
+\item $\rho_1 = 0.25$ (implying that $\sigma_1 = 0.8$) (if not otherwise specified)
+\end{itemize}
+
+We can perform unconstrained parameter estimation with the following code.
 
@@
 In the above example, we obtain convergence of the curve-fitting routine. 
-But, we also obtain an estimate of $\rho_1 = $ \Sexpr{coef(modelUKQ_LM)["rho_1"]} 
-that violates the constraint $\rho_1 \in (-1,0) \cup (0,\infty)$. 
+However, there are two problems.
+
+\begin{enumerate}
+\item The estimate of $\rho_1 = $ \Sexpr{coef(modelUKQ_LM)["rho_1"]}
+violates the constraint $\rho_1 \in (-1,0) \cup (0,\infty)$. 
 This violation leads to $\sigma_1$ (\texttt{E_1_2 (HM)}) being undefined (\texttt{NA})
 in the model summary.
+\item $\delta \rightarrow 1$, meaning that the energy term
+is unnecessary.
+\end{enumerate}
 
-To respect the constraints, we can use the \texttt{L-BFGS-B} optimization
-method. The default guess parameters are
+%------------------------------
+\section{Fitting With Constraints} 
+\label{sec:CES-with-constraints}
+%------------------------------
+
+To fit while respecting the constraints, we can use the \texttt{L-BFGS-B} optimization
+method.
 
@@
 
-The above approach correctly respects the constraints, 
+\noindent The above approach correctly respects the constraints, 
 but the \texttt{LM} algorithm does not converge.
@@
 capability of \texttt{cesEst}. Grid search is accessed by specifying
-rho or rho1 arguments and a range of values.
+\texttt{rho} and/or \texttt{rho1} arguments and a range of values. 
+Note that specifying a range of values for $\rho$ or $\rho_1$ that 
+contains values less than $-1$ results in an error. 
+The model with lowest $SSE$ will be returned from the grid search.
 
@@
 The \texttt{plot} function puts the negative of $SSE$ on the $z$ axis, 
-so better curve fits appear as higher on the $z$ axis of this plot.
+so better curve fits appear higher on the $z$ axis of this plot.
 
@@
 
+The best fit occurs when $\rho_1 \rightarrow -1$ (its boundary) and $\rho$ is large, 
+but not so large that you fall over the cliff. In Figure~\ref{fig:UKQ-grid-coarse},
+that is at $\rho = 15$ and $\rho_1 = -0.5$ (the lowest value of $\rho_1$ in the grid search).
+Although, it should be noted that $\frac{\partial^2 SSE}{\partial \rho_1^2}$
+is very small.
+
 To explore the details at high values of $\rho$ and values of 
-$\rho_1 \rightarrow -1$, we can do a detailed analysis\dots
+$\rho_1 \rightarrow -1$, we can do a detailed analysis with 
+a finer grid.
 
@@
 
-{\dots}and build a graph as shown in Figure~\ref{fig:UKQ-grid-fine}.
+We can build a graph as shown in Figure~\ref{fig:UKQ-grid-fine}.
 
@@
 
-The best fit for the UK appears to be $\rho_1 \rightarrow -1$ ($\sigma_1 \rightarrow \infty$, meaning perfect subsitutibility between $k$ and $l$).
-It is unclear why there is a sudden dropoff in $-SSE$ at larger values of $\rho$.
+The best fit occurs when $\rho_1 \rightarrow -1$ (at its boundary
+and indicating perfect substitutibility between $k$ and $l$)
+and $\delta \rightarrow 1$ (indicating that energy is unnecessary
+in this production function). Interestingly, the Cobb-Douglas
+model with $q$ for the UK indicates that energy is important
+($\gamma \approx 0.5$). Are the Cobb-Douglas and CES models
+indicating different things?
+
+The sudden dropoff in $-SSE$ at larger values of $\rho$ 
+should be investigated.
+
+%------------------------------
+\section{Fitting Without Energy} 
+\label{sec:CES-without-energy}
+%------------------------------
+
+Based on the fact that the best fit constrained model gives
+$\delta \rightarrow 1$, we can try a no-energy CES model 
+with the following code. 
+(Note that the value of \texttt{rho} below 
+corresponds to the parameter $\rho_1$ in Equation~\ref{eq:CES}.)
+
+<<>>=
+modelUK <- cesEst(data=dataUK, 
+                        yName="iGDP", 
+                        xNames=c("iCapStk", "iLabor"), 
+                        tName="iYear",
+                        method="L-BFGS-B")
+summary(modelUK)
+@
+
+With the no-energy model, we have achieved reasonable values for
+all parameters. And, the parameter estimation algorithm converges.
+However, we may be in a situation where Cobb-Douglas and CES
+are in conflict regarding the role of energy in economic growth.
+
+%------------------------------
+\section{Possible Ways Forward} 
+\label{sec:CES-way-forward}
+%------------------------------
+
+Here are some brainstorm-y ideas on how to proceed.
+
+\begin{enumerate}
+\item I think we need to understand the cause of the 
+steep dropoff in Figures~\ref{fig:UKQ-grid-coarse} and
+\ref{fig:UKQ-grid-fine}.
+
+\item We may want to consider an algorithm to detect when
+$\delta \rightarrow 1$ and switch to a no-energy
+model as shown above.
+
+\item Perhaps there is a degenerate form of the model that is 
+easier to fit if we detect that $\rho_1 \rightarrow -1$.
+
+\item It is possible to set $\rho_1$ to a specific number 
+(in this case, we could choose $\rho_1 = -0.99$; $-1.0$ would 
+blow up)
+and have \texttt{cesEst} fit the remaining parameters.
+(This is accomplished by supplying \texttt{rho} and/or
+\texttt{rho1} parameters as single values, not 
+ranges.)
+A possible algorithm using this mechanism would be
+similar to our algorithm for respecting the constraints
+on the Cobb-Douglas model.
+  \begin{enumerate}
+  \item{Fit the unconstrained model}
+  \item{If the unconstrained fit violates any constraints, 
+  set the offending parameter at the constraint}
+  \item{Re-fit the remaining the parameters}
+  \end{enumerate}
+\end{enumerate}
 

### 2013-07-20 CES.Rnw
Small updates to the file.

@@
 Equation~\ref{eq:CES} is a degenerate form of Equation~\ref{eq:CESe} 
-where $\delta \rightarrow 1$ and $\rho \rightarrow -1$ 
-($\sigma \rightarrow \infty$). 
+where $\delta \rightarrow 1$ and $\rho$ is undefined in 
+the sense that energy ($e$) is unimportant regardless of the 
+value of $\rho$.
 \end{itemize}

### 2013-07-22 CES.Rnw
Added (le)(k) nesting.

@@
 
-%------------------------------
+%++++++++++++++++++++++++++++++
 \section{CES Production Function} 
 \label{sec:CES}
-%------------------------------
+%++++++++++++++++++++++++++++++
 
-The CES model without energy is
+The Constant Elasticity of Substitution (CES) model without energy is
 
@@
 
-%------------------------------
+%++++++++++++++++++++++++++++++
 \section{Fitting Without Constraints} 
 \label{sec:CES-without-constraints}
+%++++++++++++++++++++++++++++++
+
+%------------------------------
+\subsection{Standard Energy Nesting ($kl$)($e$)}
 %------------------------------
@@
 \item $\delta \rightarrow 1$, meaning that the energy term
-is unnecessary.
+is unnecessary. The Cobb-Douglas model indicated that the 
+capital stock term was unnecessary ($\alpha = 0$). So, the 
+Cobb-Douglas and CES models seem to be in conflict.
 \end{enumerate}
@@
 %------------------------------
+\subsection{Alternative Energy Nesting ($le$)($k$)}
+%------------------------------
+
+A second option is to use a different nesting structure
+for the CES model, namely ($le$)($k$), as shown in Equation~\ref{eq:CESe2}.
+
+\begin{equation} \label{eq:CESe2}
+  y = \gamma \: A \: \left\{\delta \left[\delta_1 l^{-\rho_1} 
+      + (1-\delta_1) e^{-\rho_1} \right]^{\rho/\rho_1} 
+      + (1-\delta) k^{-\rho} \right\}^{-1/\rho}; 
+      A = \mathrm{e}^{\lambda (t-t_0)}
+\end{equation}
+
+In Equation~\ref{eq:CESe2}, $\delta \rightarrow 1$ indicates that capital stock ($k$)
+is unnecessary.
+
+<<>>=
+modelUKQ_LM2 <- cesEst(data=dataUK, 
+                      yName="iGDP", 
+                      xNames=c("iLabor", "iQ", "iCapStk"), 
+                      tName="iYear")
+summary(modelUKQ_LM2)
+@
+
+With ($le$)($k$) nesting, the fitting routine converges, and we find that 
+$\delta = $ \Sexpr{coef(modelUKQ_LM2)["delta"]}, 
+which violates the constraint $\delta \in (0,1)$. This result might indicate 
+that capital stock ($k$) is unnecessary.
+
+So, the indications about relative importance of different factors 
+of production may be a function of nesting method in the CES model.
+
+%++++++++++++++++++++++++++++++
 \section{Fitting With Constraints} 
 \label{sec:CES-with-constraints}
-%------------------------------
+%++++++++++++++++++++++++++++++
 
@@
 
-%------------------------------
+%++++++++++++++++++++++++++++++
 \section{Fitting Without Energy} 
 \label{sec:CES-without-energy}
-%------------------------------
+%++++++++++++++++++++++++++++++
 
@@
 
-%------------------------------
+%++++++++++++++++++++++++++++++
 \section{Possible Ways Forward} 
 \label{sec:CES-way-forward}
-%------------------------------
+%++++++++++++++++++++++++++++++
 
-Here are some brainstorm-y ideas on how to proceed.
+Here are some brainstorm-y ideas on how to proceed, in no particular order.
 
@@
 \ref{fig:UKQ-grid-fine}.
+
+\item We need to understand why the nesting structure appears
+to affect the indications of which parameters are important.
+This may involve a little bit of literature searching by Martin.
 

### 2013-07-22 EconGrowth.Rnw
Added several references and some text suggested by Martin.

--- 2013-07-15 EconGrowth.Rnw
@@
 
+**** Additional references requested by Martin. Incorporate into paper? ****
+
+\citet{Lindenberger:2011dx}
+
+\citet{Stresing:2008cq}
+
 The remainder of this paper is organized as follows. Section~\ref{sec:Coordinates} 
@@
 Serrenho divides thermal energy into renewables, non-renewables, 
-wastes, and imports.
+wastes, and imports. The main argument of these papers is that 
+energy is an important driver of growth and needs to be included
+as an essential factor of production.
 
@@
 from 1800-2000 and demonstrate the importance of the transition from wood to 
-fossil fuels for economic growth.
+fossil fuels for economic growth. \citet{Shen:2013vp} included energy 
+in nested aggregated CES production functions 
+for China and found that the best nesting structure is ($le$)($k$).
 
@@
 for Austria, the United Kingdom, the United States, and Japan. 
+\citet{Ayres:2005kn} argued that introducing energy inputs 
+in traditional production functions does not improve its explanatory power, 
+but including useful work in a LINEX function does.
 

### 2013-07-23 CES.Rnw
Adding a way to do CES fits for all countries with all 3 possible nesting structures.

@@
 opts_chunk$set(
-  tidy=FALSE
+  tidy=FALSE,
+  eval=FALSE
 )
@@
 Equation~\ref{eq:CESe} augments Equation~\ref{eq:CES} with energy 
-using a ($kl$)($e$) nesting structure, as is typical in the literature. 
+using a ($kl$)$e$ nesting structure, as is typical in the literature. 
 \item
-$\delta$ describes the importance of the capital/labor pair ($kl$) relative to ($e$).
+$\delta$ describes the importance of the capital/labor pair ($kl$) relative to energy ($e$).
 \item
@@
 As $\sigma \rightarrow \infty$ ($\rho \rightarrow -1$), 
-($kl$) and ($e$) are perfect substitutes. 
+($kl$) and $e$ are perfect substitutes. 
 \item
 As $\sigma \rightarrow 0$ ($\rho \rightarrow \infty$), 
-($kl$) and ($e$) are perfect complements: 
+($kl$) and $e$ are perfect complements: 
 no substitution is possible. 
@@
 %------------------------------
-\subsection{Standard Energy Nesting ($kl$)($e$)}
+\subsection{Standard Energy Nesting ($kl$)$e$}
+\label{sec:kle-nesting}
 %------------------------------
@@
 %------------------------------
-\subsection{Alternative Energy Nesting ($le$)($k$)}
+\subsection{Alternative Energy Nesting ($le$)$k$}
+\label{sec:lek-nesting}
 %------------------------------
@@
 for the CES model, namely ($le$)($k$), as shown in Equation~\ref{eq:CESe2}.
+
+\begin{equation} \label{eq:CESe}
+  y = \gamma \: A \: \left\{\delta \left[\delta_1 k^{-\rho_1} 
+      + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1} 
+      + (1-\delta) e^{-\rho} \right\}^{-1/\rho}; 
+      A = \mathrm{e}^{\lambda (t-t_0)}
+\end{equation}
 
@@
 %++++++++++++++++++++++++++++++
+\section{Effect of Nesting} 
+\label{sec:effect-of-nesting}
+%++++++++++++++++++++++++++++++
+In Section~\ref{sec:lek-nesting}, we found that different results were
+obtained with standard nesting ($kl$)$e$ vs. a differnet nesting
+($le$)$k$. To explore that further, we run all 9 countries with 
+all three nesting options 
+\begin{itemize}
+\item{($kl$)$e$} 
+\item{($le$)$k$}
+\item{($ek$)$l$}
+\end{itemize}
+
+<<eval=TRUE>>=
+nestingOptions <- c(kle="(kl)e", lek="(le)k", ekl="(ek)l")
+fitCES <- function(countryAbbrev, nest, energyType="Q", method="L-BFGS-B"){
+  data <- loadData(countryAbbrev=countryAbbrev)
+  data <- replaceColName(data, energyType, "iEToFit")
+  if (nest == "(kl)e"){
+    xNames <- c("iCapStk", "iLabor", "iEToFit")
+  } else if (nest == "(le)k"){
+    xNames <- c("iLabor", "iEToFit", "iCapStk")
+  } else if (nest == "(ek)l"){
+    xNames <- c("iEToFit", "iCapStk", "iLabor")
+  } else {
+    stop(paste("Unknown nesting option", nest, "in fitCES."))
+  }
+  model <- cesEst(data=data, 
+                  yName="iGDP", 
+                  xNames=xNames, 
+                  tName="iYear",
+                  method=method)
+}
+
+# Make all the models
+kleModels <- lapply(countryAbbrevs, fitCES, nest="(kl)e")
+lekModels <- lapply(countryAbbrevs, fitCES, nest="(le)k")
+eklModels <- lapply(countryAbbrevs, fitCES, nest="(ek)l")
+
+# Now, extract coefficients to make a table
+coef(kleModels["US"])
+@
+
+%++++++++++++++++++++++++++++++
 \section{Possible Ways Forward} 

### 2013-07-23 CES.Rnw
Created a modelMatrix. Added template of code to extract coefficients from modelMatrix.

@@
 
-# Now, extract coefficients to make a table
-coef(kleModels["US"])
+modelMatrix <- cbind(kleModels, lekModels, eklModels)
+colnames(modelTable) <- nestingOptions
+
+# Now, extract coefficients from each model in the matrix
+# to make data.frames of coefficients. Each data.frame has 
+# countries in rows and nesting options in columns 
+# (same structure) as modelMatrix
+
+# gamma
+
+# lambda
+
+# delta
+
+# delta1
+
+# rho
+
+# rho1
+
 @

### 2013-07-23 CES.Rnw
Added a return statement to the fitCES function.

@@
                   method=method)
+  return(model)
 }

### 2013-07-23 CES.Rnw
Added a comma.
collect data into data frame

--- 2013-07-23 CES.Rnw
@@
 <<eval=TRUE>>=
+require(plyr)
 nestingOptions <- c(kle="(kl)e", lek="(le)k", ekl="(ek)l")
@@
                   method=method)
+  return(c(coef( model ), c(country=countryAbbrev, nest=nest)) )
 }
@@
 # Make all the models
-kleModels <- lapply(countryAbbrevs, fitCES, nest="(kl)e")
-lekModels <- lapply(countryAbbrevs, fitCES, nest="(le)k")
-eklModels <- lapply(countryAbbrevs, fitCES, nest="(ek)l")
-
-modelMatrix <- cbind(kleModels, lekModels, eklModels)
-colnames(modelTable) <- nestingOptions
+kleModels <- ldply(countryAbbrevs, fitCES, nest="(kl)e")
+lekModels <- ldply(countryAbbrevs, fitCES, nest="(le)k")
+eklModels <- ldply(countryAbbrevs, fitCES, nest="(ek)l")
+allModels <- rbind(kleModels, lekModels, eklModels)
+#modelMatrix <- cbind(kleModels, lekModels, eklModels)
+#colnames(modelTable) <- nestingOptions
 
@@
 # to make data.frames of coefficients. Each data.frame has 
-# countries in rows and nesting options in columns 
+# countries in rows and nesting options in columns, 
 # (same structure) as modelMatrix

### 2013-07-23 CES.Rnw
better preservation of type s

@@
                   method=method)
-  return(c(coef( model ), c(country=countryAbbrev, nest=nest)) )
+  res <- as.data.frame( coef( model ) )
+  res <- transform( res, country=countryAbbrev, nest=nest ) 
+  return(res)
 }

### 2013-07-23 CES.Rnw
better preservation of type s

--- 2013-07-23 CES.Rnw
@@
                   method=method)
-  return(c(coef( model ), c(country=countryAbbrev, nest=nest)) )
+  res <- do(1) * coef( model ) 
+  res <- transform( res, country=countryAbbrev, nest=nest ) 
+  return(res)
 }

### 2013-07-24 CES.Rnw
add convergence indicator

--- 2013-07-23 CES.Rnw
@@
                   method=method)
-  return(c(coef( model ), c(country=countryAbbrev, nest=nest)) )
+  res <- do(1) * coef( model ) 
+  res <- transform( res, country=countryAbbrev, nest=nest, converge=model$convergence )
+
+  return(res)
 }

### 2013-07-24 CES.Rnw
Trying to get xtable to work.

--- 2013-07-23 CES.Rnw
@@
 allModels <- rbind(kleModels, lekModels, eklModels)
+
+CESTable <- xtable(allModels, caption="CES coefficients.", label="tab:CES-coeffs-table")
+
 #modelMatrix <- cbind(kleModels, lekModels, eklModels)
@@
 
+@
+
+<<Print_CES_Tables, results='asis'>>=
+CESTable
 @

### 2013-07-24 CES.Rnw
Now creating table of all countries and CES nesting options.

--- 2013-07-24 CES.Rnw
@@
 require(knitr)
+require(plyr)
 opts_chunk$set(
   tidy=FALSE,
-  eval=FALSE
+  eval=TRUE
 )
@@
 \maketitle
+
+% Add an argument if you want a label. Example: "\label{eq:CES}"
+\newcommand{\ceskl}[1]{\begin{equation} #1
+  y = \gamma \: A \: \left[\delta_1 k^{-\rho_1} 
+      + (1-\delta_1)l^{-\rho_1} \right]^{-1/\rho_1}; 
+      A = \mathrm{e}^{\lambda (t-t_0)}
+\end{equation}}
+
+\newcommand{\ceskle}[1]{\begin{equation} #1
+  y = \gamma \: A \: \left\{\delta \left[\delta_1 k^{-\rho_1} 
+      + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1} 
+      + (1-\delta) e^{-\rho} \right\}^{-1/\rho}; 
+      A = \mathrm{e}^{\lambda (t-t_0)}
+\end{equation}
+}
+
+\newcommand{\ceslek}[1]{\begin{equation} #1
+  y = \gamma \: A \: \left\{\delta \left[\delta_1 l^{-\rho_1} 
+      + (1-\delta_1) e^{-\rho_1} \right]^{\rho/\rho_1} 
+      + (1-\delta) k^{-\rho} \right\}^{-1/\rho}; 
+      A = \mathrm{e}^{\lambda (t-t_0)}
+\end{equation}
+}
+
+\newcommand{\cesekl}[1]{\begin{equation} #1
+  y = \gamma \: A \: \left\{\delta \left[\delta_1 e^{-\rho_1} 
+      + (1-\delta_1) k^{-\rho_1} \right]^{\rho/\rho_1} 
+      + (1-\delta) l^{-\rho} \right\}^{-1/\rho}; 
+      A = \mathrm{e}^{\lambda (t-t_0)}
+\end{equation}
+}
 
@@
 
-\begin{equation} \label{eq:CES}
-  y = \gamma \: A \: \left[\delta_1 k^{-\rho_1} 
-      + (1-\delta_1)l^{-\rho_1} \right]^{-1/\rho_1}; 
-      A = \mathrm{e}^{\lambda (t-t_0)}
-\end{equation}
+\ceskl{\label{eq:CES}}
 
@@
 
-\begin{equation} \label{eq:CESe}
-  y = \gamma \: A \: \left\{\delta \left[\delta_1 k^{-\rho_1} 
-      + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1} 
-      + (1-\delta) e^{-\rho} \right\}^{-1/\rho}; 
-      A = \mathrm{e}^{\lambda (t-t_0)}
-\end{equation}
+\ceskle{\label{eq:CESe}}
+% \begin{equation} \label{eq:CESe}
+%   y = \gamma \: A \: \left\{\delta \left[\delta_1 k^{-\rho_1} 
+%       + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1} 
+%       + (1-\delta) e^{-\rho} \right\}^{-1/\rho}; 
+%       A = \mathrm{e}^{\lambda (t-t_0)}
+% \end{equation}
 
@@
 A second option is to use a different nesting structure
-for the CES model, namely ($le$)($k$), as shown in Equation~\ref{eq:CESe2}.
+for the CES model, namely ($le$)($k$), as shown in Equation~\ref{eq:ceslek}.
 
-\begin{equation} \label{eq:CESe}
-  y = \gamma \: A \: \left\{\delta \left[\delta_1 k^{-\rho_1} 
-      + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1} 
-      + (1-\delta) e^{-\rho} \right\}^{-1/\rho}; 
-      A = \mathrm{e}^{\lambda (t-t_0)}
-\end{equation}
+\ceskle{}
 
-\begin{equation} \label{eq:CESe2}
-  y = \gamma \: A \: \left\{\delta \left[\delta_1 l^{-\rho_1} 
-      + (1-\delta_1) e^{-\rho_1} \right]^{\rho/\rho_1} 
-      + (1-\delta) k^{-\rho} \right\}^{-1/\rho}; 
-      A = \mathrm{e}^{\lambda (t-t_0)}
-\end{equation}
+\ceslek{\label{eq:ceslek}}
 
-In Equation~\ref{eq:CESe2}, $\delta \rightarrow 1$ indicates that capital stock ($k$)
+% \begin{equation} \label{eq:CESe2}
+%   y = \gamma \: A \: \left\{\delta \left[\delta_1 l^{-\rho_1} 
+%       + (1-\delta_1) e^{-\rho_1} \right]^{\rho/\rho_1} 
+%       + (1-\delta) k^{-\rho} \right\}^{-1/\rho}; 
+%       A = \mathrm{e}^{\lambda (t-t_0)}
+% \end{equation}
+
+In Equation~\ref{eq:ceslek}, $\delta \rightarrow 1$ indicates that capital stock ($k$)
 is unnecessary.
@@
 In Section~\ref{sec:lek-nesting}, we found that different results were
-obtained with standard nesting ($kl$)$e$ vs. a differnet nesting
-($le$)$k$. To explore that further, we run all 9 countries with 
-all three nesting options 
+obtained with standard nesting ($kl$)$e$ vs. a differnet nesting, namely
+($le$)$k$. To explore that further, we fit all 9 countries with 
+all three nesting options:
 \begin{itemize}
 \item{($kl$)$e$} 
+\end{itemize}
+\ceskle{}
+\begin{itemize}
 \item{($le$)$k$}
+\end{itemize}
+\ceslek{}
+\begin{itemize}
 \item{($ek$)$l$}
 \end{itemize}
+\cesekl{\label{eq:cesekl}}
 
-<<eval=TRUE>>=
-require(plyr)
+<<>>=
 nestingOptions <- c(kle="(kl)e", lek="(le)k", ekl="(ek)l")
@@
 allModels <- rbind(kleModels, lekModels, eklModels)
-#modelMatrix <- cbind(kleModels, lekModels, eklModels)
-#colnames(modelTable) <- nestingOptions
+# Ignore the leading .id column
+allModels <- allModels[ , 2:10] 
+# Sort based on country
+allModels_ordered <- allModels[order(allModels$country) , ] 
+# Reorder the columns
+allModels_ordered <- allModels_ordered[c("country", "nest", "converge", "gamma", "lambda", 
+                                         "delta_1", "delta", "rho_1", "rho")]
 
-# Now, extract coefficients from each model in the matrix
-# to make data.frames of coefficients. Each data.frame has 
-# countries in rows and nesting options in columns, 
-# (same structure) as modelMatrix
+CESTable <- xtable(allModels_ordered, caption="CES coefficients for three nesting options.", 
+                   label="tab:CES-coeffs-table",
+                   table.placement="")
+@
 
-# gamma
-
-# lambda
-
-# delta
-
-# delta1
-
-# rho
-
-# rho1
-
+<<Print_CES_Tables, results='asis'>>=
+print(CESTable,
+      caption.placement="top", 
+      table.placement="H",
+      include.rownames=FALSE,
+      hline.after=c(-1,0,3,6,9,12,15,18,21,24,nrow(CESTable)))
 @

### 2013-07-24 CES.Rnw
Minor format changes.

@@
 
+We use the \texttt{L-BFGS-B} method (as shown in Section~\ref{sec:CES-with-constraints}),
+which respects constraints on the model parameters.
+
 <<>>=
@@
   res <- transform( res, country=countryAbbrev, nest=nest, converge=model$convergence ) 
-
   return(res)
@@
 allModels <- allModels[ , 2:10] 
-# Sort based on country
+# Sort rows based on country
 allModels_ordered <- allModels[order(allModels$country) , ] 
-# Reorder the columns
+# Reorder the columns to put the meta information first
 allModels_ordered <- allModels_ordered[c("country", "nest", "converge", "gamma", "lambda", 
                                          "delta_1", "delta", "rho_1", "rho")]
-
+# Create the LaTeX table
 CESTable <- xtable(allModels_ordered, caption="CES coefficients for three nesting options.", 
                    label="tab:CES-coeffs-table",
-                   table.placement="")
+                   table.placement="H")
 @

### 2013-07-24 CES.Rnw
Added a nice comparison table between CD and CES models.

@@
 \usepackage{float} % For precise figure positioning.
+\usepackage{multirow} % To create multirow tables
+\usepackage{amssymb} % To provide check marks
 
@@
 
+However, we should note that we are not respecting the constraints here. 
+To assess whether the models are actually telling us 
+something different, we need to be sure to respect constraints
+with the CES model.
+
 %------------------------------
@@
 which violates the constraint $\delta \in (0,1)$. This result might indicate 
-that capital stock ($k$) is unnecessary.
+that capital stock ($k$) is unnecessary, thereby agreeing with 
+results from the Cobb-Douglas model.
 
@@
 of production may be a function of nesting method in the CES model.
+However, we need to be careful about convergence and respecting 
+constraints.
 
@@
 We use the \texttt{L-BFGS-B} method (as shown in Section~\ref{sec:CES-with-constraints}),
-which respects constraints on the model parameters.
+which respects constraints on the model parameters, and thermal energy ($q$) is 
+used for the energy quantification.
 
@@
 
-<<Print_CES_Tables, results='asis'>>=
+<<CESResultsTable, results='asis'>>=
 print(CESTable,
@@
 @
+
+One way to assess the data in Table~\ref{tab:CES-coeffs-table} is to compare indications 
+from the Cobb-Douglas and CES models. 
+Table~\ref{tab:cd-ces-comparison} does so.
+
+\begin{table}[H] \caption{Comparison of indications from Cobb-Douglas and CES models with energy.} \label{tab:cd-ces-comparison} 
+  \begin{center}
+    \begin{tabular}{c|l|l|c}
+Country & CD                                     & CES                                            & Agree? \\
+\hline
+US      & $\gamma = 0 \rightarrow e$ unnecessary & ($kl$)$e$, ($le$)$k \rightarrow e$ unnecessary & \checkmark \\
+\hline
+UK      & $\alpha = 0 \rightarrow k$ unnecessary & ($kl$)$e$, ($le$)$k \rightarrow k$ unnecessary & \checkmark \\
+\hline
+JP      & $\gamma = 0 \rightarrow e$ unnecessary & ($ek$)$l \rightarrow e$ unnecessary            & \checkmark $\:$ but no CES convergence\\
+\hline
+CN      & $\gamma = 0 \rightarrow e$ unnecessary & No indications                                 & Note: no CES convergence\\
+\hline
+ZA      & $\beta  = 0 \rightarrow l$ unnecessary & No indications                                 &      \\
+\hline
+SA      & No indications                         & No indications                                 & \checkmark \\
+\hline
+IR      & $\gamma = 0 \rightarrow e$ unnecessary & All nestings $\rightarrow e$ unnecessary       & \checkmark \\
+\hline
+TZ      & $\beta  = 0 \rightarrow l$ unnecessary & No indications                                 &      \\
+\hline
+\multirow{2}{*}{ZM} & $\beta  = 0 \rightarrow l$ unnecessary & \multirow{2}{*}{All nestings $\rightarrow l$ unnecessary} & \multirow{2}{*}{-- (partial)}\\
+        & $\gamma = 0 \rightarrow e$ unnecessary &                                                &        \\
+
+    \end{tabular}
+  \end{center}
+\end{table}
+
+Table~\ref{tab:cd-ces-comparison} looks better than I was expecting. 
+Note that in Section~\ref{sec:CES-without-constraints},
+I was not assessing the indications from the CES model 
+\emph{while also respecting the constraints}. 
+When the constraints are respected, both Cobb-Douglas and CES
+give similar indications for most economies.
+
+I suspect that clearing up the non-convergence issues 
+for the UK, JP, and CN will provide additional insights.
+Martin may be able to provide additional insight on the South African (ZA)
+and Tanzanian (TZ) situations, as ZA and TZ are the only countries with both 
+(a) dissimilar indications from Cobb-Douglas and CES and 
+(b) convergence of the CES models for all nestings.
 

### 2013-07-29 CES.Rnw
added extractRSSdata(); levelplot()

@@
 source("Econ-Growth-Functions2.R")
+@
+
+<<>>=
+extractRSSdata <- function(object, ...) {
+  res <- expand.grid( object$rho1Values, object$rhoValues )
+  names(res) <- c('rho1', 'rho')
+  res <- transform(res, RSS = as.vector(object$rssArray))
+  res
+}
 @
@@
 plot(modelUKQ_grid)
+print(class(modelUKQ_grid))
 @
@@
                         method="L-BFGS-B",
-                        rho=seq(from=14, to=20, by=1), 
-                        rho1=seq(from=-0.95, to=-0.5, by=0.05))
+                        rho=seq(from=100, to=120, length.out=20), 
+                        rho1=seq(from=1, to=2, length.out=20))
 summary(modelUKQ_grid_detail)
+levelplot( RSS ~ rho1 + rho, data=extractRSSdata(modelUKQ_grid_detail), 
+           region=TRUE, 
+           col.regions=terrain.colors)
 @

### 2013-07-29 EconGrowth.Rnw
Added notes from Martin to the introduction.

@@
 
+**** Notes from Martin ****
+
+To be included somewhere.
+
+Big picture
+Why do we do this? Want to link energy and economics on national level 
+and in a modeled approach,informing energy policy during energy transitions.
+Usually macro energy economic models rely on PF with energy included. 
+Key papers using CES in energy economics incl high impact such as 
+Stern, Gerlagh, Tol etc. 
+Cite in introduction met energy economists using PF approaches, specially CES.
+But, which form to choose and using which parameters? 
+Literature is inconclusive, very little actual empirical testing of such functions. 
+Mostly CES in CGE models used by Wbank and others. 
+CD adviced to be used by CBO. 
+How do we select a functional form and what are the parameters to be used? On what basis do we select?
+
+We aim. to search for empirically robust solution, one that stands up to statistical testing.
+
+What we find is counterintuitive for many cases: dropping energy from the PF has little impact, 
+but some notable exceptions. 
+On other hand, only including energy in a PF of LINEX form also yields good results and stats tests. 
+Is not a simple case for dropping energy, but acknowledging its key role. 
+Do we support the call for better bottom-up understanding? 
+What do we say on the limitations of macroeconomic modelling approaches altogether? 
+(Note such limitations are well known in ME literature, for example capital controversy Robinson).
+We speculate on implications for choosing PF in energy economic models that inform growth policy.
+
+Points on paper so far
+1. Does the relative small differences in fit between different production functions warrant 
+such a large debate on validity of one vs other? Clearly not. 
+CD been used by economists for ease of use and extreme flexibility (Miller).  
+PF generally used on instrumentalist grounds if give reasonable good description of data. 
+NK econ theory provide poor causal explanation of observed data, 
+but yet CD shows very good fit (miller, p17). 
+CES is  more general, but is a liability in forecasting because difficult 
+to get estimate of EoS that is consistent across studies (Miller, p26). 
+Aggregation is problem of both CD and CES functional forms, 
+so being careful when making strong inferences that cannot be justified.
+
+2. We think we can contribute by emphasising the need 
+for proper stats testing or inconsistent reporting on use of preferred functions. 
+Problems with empirical testing presented by Shen, Serrenho.
+What are our issues with multivariate OLS (Serrenho)?
+
+3. Are we joining the forced choice between production functions or 
+acknowledge the similar problems with aggregate prod functions in general? 
+Do we see this as sufficient evidence to doubt the top-down approach to econ growth altogether?
+
+4. R2 is a very crude measure and only very minor improvements 
+are achieved when others factors such as energy is added in a CD. 
+We concur. Puzzling is conclusion that such minor improvements 
+does prove the need to include energy in PF (Serrenho).
+
+5. We do think it is a choice between CD and CES (Miller) as 
+both have serious deficiencies after stats tests.
+
+6. One central issue within PF is elasticity of subs (EoS). 
+That is the \%ch in factor proportions ( k,l, etc) 
+because of one unit ch in MRTS. 
+MRTS is rate at which one factor can be substituted for another holding output constant. 
+EoS is low in Leontief cases, L shaped isoquants.
+
+7. Miller makes the point that even if parameters in model are stats artifacts, 
+they are still useful for forecasting. Do we agree?
+
+8. Is Ockham's razor relevant to what we are doing?
+
+9. Assumptions of CD are strongly rejected by empirical work, Miller still makes case for using CD.
+
+11. What about energy augmented
+
+10. TZ case
+CDno e: almost 80\% l
+CD with e: 25\% energy, rest c,importance of l drops to 0
+CES no e: 20\% c (sigma), 80\% l, but large range
+CES with e: fig 35 e may be NB
+LINEX: one of lowest ct parameters (low relative importance of labour eff compared to cap eff)
+Does this mean that relative small increases in cap eff can really lift the economy?
+
+11. ZA case
+CD no e: roughly half c, l
+CD with e: roughly half, c, e, importance of l drops to 0
+CES no e: 10% c, 25% l ??
+CES with e: fig 35 e may be NB
+LINEX: one of highest ct parameters (high relative importance of labour eff compared to cap eff)
+Does this mean that relative small increases in labour eff can really lift the economy?
+
+12. Capital starved Zambia. Very high importance. Understand CES param better.
+
+Discussion: What is Next?
+
+a. A comparative analysis between diff PF reveal interesting 
+enough information to warrant a more diffused approach to countries. 
+Thus, we have a case for doing this for  all countries in the world 
+(or at least those representative of countries in different groups 80/20)
+
+b. If c is relatively more important than labour or energy 
+for growth and if capital stock is low, a situation one would expect in LDCs, 
+a relative small addition of capital stock can give relatively large returns in terms of growth.
+
+c. Now it becomes interesting, in a 'stages of growth' approach, 
+using LT econ data it may be the case that the importance 
+of factors are different across growth stages. 
+It would need a composite type of analysis - both stock and importance.
+
+d. Is it possible to have evidence of diff stocks and diff importances across phases of growth? 
+Maybe test this for a data rich nation that has worked through these stages, 
+we try to identify them and do partial analysis on time periods coinciding with these stages.
+
+Discussions:
+
+Counterfactuals: energy, cap, labour what ifs for future.
+
+interpretation of type of economies, what does the data presentation say 
+on relative change in each input and change in GDP?
+
+Forcing const elast of subs in CES thru nested structures violates 
+observation that more than two factor will not be const. elasticities Uzawa 1962.
+
+R programming dealt with nested CES see paper discussion on Kemfert.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2013-07-30 CES.Rnw
bug fixes in running multiple CES models

@@
 dataUK <- loadData(countryAbbrev="UK")
-modelUKQ_LM <- cesEst(data=dataUK, 
+modelUKQ_LM <- cesEstPlus(data=dataUK, 
                       yName="iGDP", 
@@
 <<>>=
-modelUKQ_LM2 <- cesEst(data=dataUK, 
+modelUKQ_LM2 <- cesEstPlus(data=dataUK, 
                       yName="iGDP", 
@@
 <<>>=
-modelUKQ_LBFGSB <- cesEst(data=dataUK, 
+modelUKQ_LBFGSB <- cesEstPlus(data=dataUK, 
                           yName="iGDP", 
@@
 To assess what is happening, we can use the built-in grid search
-capability of \texttt{cesEst}. Grid search is accessed by specifying
+capability of \texttt{cesEstPlus}. Grid search is accessed by specifying
 \texttt{rho} and/or \texttt{rho1} arguments and a range of values. 
@@
 <<>>=
-modelUKQ_grid <- cesEst(data=dataUK, 
+modelUKQ_grid <- cesEstPlus(data=dataUK, 
                         yName="iGDP", 
@@
 <<>>=
-modelUKQ_grid_detail <- cesEst(data=dataUK, 
+modelUKQ_grid_detail <- cesEstPlus(data=dataUK, 
                         yName="iGDP", 
@@
 <<>>=
-modelUK <- cesEst(data=dataUK, 
+modelUK <- cesEstPlus(data=dataUK, 
                         yName="iGDP", 
@@
 nestingOptions <- c(kle="(kl)e", lek="(le)k", ekl="(ek)l")
-fitCES <- function(countryAbbrev, nest, energyType="Q", method="L-BFGS-B"){
+fitCES <- function(countryAbbrev, nest, energyType="Q", method=c("PORT","L-BFGS-B")){
   data <- loadData(countryAbbrev=countryAbbrev)
@@
   }
-  model <- cesEst(data=data, 
-                  yName="iGDP", 
+  model <- cesModel(data=data, energyType=energyType, 
+                  # yName="iGDP", 
                   xNames=xNames, 
-                  tName="iYear",
+                  # tName="iYear",
                   method=method)
-  res <- do(1) * coef( model ) 
-  res <- transform( res, country=countryAbbrev, nest=nest, converge=model$convergence ) 
+  res <- naturalCoef( model ) 
+  res <- transform( res, nest=nest, country=countryAbbrev, nest=nest, converge=model$convergence ) 
   return(res)
@@
 # Ignore the leading .id column
-allModels <- allModels[ , 2:10] 
+allModels <- subset( allModels, select= -.id )
+allModels <- transform( allModels, max.sse = pmax(sse.PORT, sse.L.BFGS.B))
 # Sort rows based on country
@@
 allModels_ordered <- allModels_ordered[c("country", "nest", "converge", "gamma", "lambda", 
-                                         "delta_1", "delta", "rho_1", "rho")]
+                                         "delta_1", "delta", "rho_1", "rho", "method", "sse","max.sse")]
 # Create the LaTeX table
 CESTable <- xtable(allModels_ordered, caption="CES coefficients for three nesting options.", 
-                   label="tab:CES-coeffs-table",
+                   label="tab:CES-coeffs-table", digits=3,
                    table.placement="H")
@@
       include.rownames=FALSE,
-      hline.after=c(-1,0,3,6,9,12,15,18,21,24,nrow(CESTable)))
+      hline.after=c(-1,0,3,6,9,12,15,18,21,24,nrow(CESTable)),
+      digits=3
+      )
 @

### 2013-07-30 CES.Rnw
clean up output for resampling of cese models

@@
                           tName="iYear",
-                          method="L-BFGS-B")
+                          algorithm="L-BFGS-B")
 summary(modelUKQ_LBFGSB)
@@
                         tName="iYear",
-                        method="L-BFGS-B",
+                        algorithm="L-BFGS-B",
                         rho=seq(from=5, to=30, by=5), 
@@
                         tName="iYear",
-                        method="L-BFGS-B",
+                        algorithm="L-BFGS-B",
                         rho=seq(from=100, to=120, length.out=20), 
@@
                         tName="iYear",
-                        method="L-BFGS-B")
+                        algorithm="L-BFGS-B")
 summary(modelUK)
@@
 nestingOptions <- c(kle="(kl)e", lek="(le)k", ekl="(ek)l")
-fitCES <- function(countryAbbrev, nest, energyType="Q", method=c("PORT","L-BFGS-B")){
+fitCES <- function(countryAbbrev, nest, energyType="Q", algorithm=c("PORT","L-BFGS-B")){
   data <- loadData(countryAbbrev=countryAbbrev)
@@
                   # tName="iYear",
-                  method=method)
+                  algorithm=algorithm)
   res <- naturalCoef( model ) 
@@
 allModels_ordered <- allModels_ordered[c("country", "nest", "converge", "gamma", "lambda", 
-                                         "delta_1", "delta", "rho_1", "rho", "method", "sse","max.sse")]
+                                         "delta_1", "delta", "rho_1", "rho", "algorithm", "sse","max.sse")]
 # Create the LaTeX table

### 2013-07-30 EconGrowth.Rnw
Added note about stages of growth.
Added note about possibly eliminating q.

@@
 
+Should we eliminate $u$ data? Only 3 countries. Only 20 years. Doesn't add much insight. 
+Too bad, but perhaps necessary to simplify paper.
+
 Discussions:
@@
 R programming dealt with nested CES see paper discussion on Kemfert.
+
+Next steps:
+
+Stages of growth crowd implicitly assumes countries at similar stage of growth will
+have similar values for $\alpha$, $\beta$, $\gamma$. However, our results show
+that not to be true. Needs further exploration to cover more (all?) countries.
 
@@
 @
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Interpretation of Results}
+\label{sec:Interpretation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+**** Notes for interpretation of results ****
+
+Country interpretation
+Comparison Cobb Douglas and CES results.
+US: 
+CD: Energy is unnecessary
+CES (kl)e: energy is unnec (delta is 1); also (el)k energy is unnec. (delta_1 is 0); (le)k no indication
+Relative consistent signal that energy is unnec.
+Sigma:
+capital and energy are complements
+labour and energy are subsitutable
+
+UK:
+CD: Capital is unnec.
+CES (kl)e: energy is unnec (delat is 1); (le)k capital is unnec. (delta is 1); (ek)l (delta_1 is 0) energy is unnec,
+Thus, inconsistent results, possibly look at different time series as massive changes in economic policy in Uk economic history
+Sigma:
+energy is not substitutable with capital or labour, totally complementary
+
+JP:
+CD: energy is unnec.
+CES: (kl)e; (le)k; (ek)l: no indications, all are important. weak signal that labour is less necessary (kl(e) delta_1 =0.86 and (ek)l delta =0.89)
+Thus, inconsistent results.
+Sigma:
+labour and energy are complements
+capital and energy complements
+
+CN:
+CD: energy not necessary, capital less necessary
+CES: (kl)e: energy is unnec. (delta is 1); (le)k labour is unnnec (delta_1 is 0); (ek)l energy is unnec. (delta_1 close to 0)
+Strong signal that energy is unnec, but the labour and capital signals are conflicting
+Sigma:
+capital and energy is complementary, but labour and energy more substitutable
+
+ZA:
+CD: Labour is unnec.
+CES: (kl)e: labour is unnec. (delta_1 is 1); (le)k labour is unnec. (delta_1 is 0); (ek)l labour is unnec. (delta is 1)
+Consistent signal that labour is unnec.
+Sigma:
+capital and energy is complementary
+labour and energy is substitutable
+
+SA:
+CD: no indications
+CES: no indications, but weak signal that labour is unnec in (ek)l (delta is 0.93) 
+Almost consistent signal that no indocations.
+Sigma:
+labour and energy are complements
+capital and energy are substitutes
+
+IR:
+CD: energy is unnec.
+CES: (kl)e: energy is unnec (delta=1); (le)k: energy is unnec. (delta_1=1); (ek)l: labour is unnec. (delta=1)
+sigma:
+labour and energy still complements, but not as strong
+capital and energy complements
+
+TZ:
+CD: labour in unnec.
+CES: (kl)e: labour is unnec (delta_1=0.97); (le)k: weak signal that energy is unnec. (delta_1=0.92); very weal signal capital is unnec (delta=0.84); (ek)l: labour is unnec. delta=0.96 
+Consistent signal that labour is unnec, with exception of one nesting.
+Sigma:
+labour and energy complements
+capital and energy perfect substitutes
+
+ZM:
+CD: labour is unnec; energy is unnec.
+CES: (kl)e: labour is unnec. (delta_1=1); labour is unnec (le)k: (delta_1=0); (ek)l: labour is unnec. (delta=1)
+Consistent signal that labour is unnec.
+Sigma:
+labour and energy complements, not as strong
+capital and energy perfect substitutes.
+
+Discussion of results: How to get better consistent signals?
+- Use CD as starting points and do CES convergence on that basis.
+- Do scatterplots to get range of uncertainty inputs, then re-interpret. delta against sigma plots, as well as delta_1 and sigma_1 plots.
+
+Thus, to do the fitting well we need to understand:
+- nesting
+- algorithm
+- starting values
+esp. for CES. 
+(Maybe illustrate with one case study such as China what implications are).
+
+How do we compare witj LINEX results?
+CES is a broader specification of CD, LINEX is not.
+In LINEX no delta's nor sigmas are generated.
+Only efficiency terms are generated in LINEX, thus in other words economic growth is only possible by increased efficiency.
+The efficiency of using energy is driven by capital stock.
+The objective/growth engine is to increase capital at a rate that is faster then growth in labour and energy.
+Increasing labour relative to energy gives a muted benefit.
+LINEX derived for Germany: only really applicable when energy and capital are complements.
+
+Discussion in relation to other papers. 
+Problems with other papers:
+- If not giving you all parameters
+- Not explain nesting approach 
+- No CI on data
+
+Economic interpretation (revisit after scatterplot information)
+Developed economies: Capital and energy is complementary (US: labour and energy substitutable)
+NICs: Capital and energy complementary, but labour and energy more substitutable
+OPEC: Labour and energy complementary (mixed results on capital and energy)
+LDCs: Labour and energy complementary, Capital and energy perfect substitutes.
 

### 2013-07-30 EconGrowth2.Rnw
New file for the actual paper.

--- 2013-07-29 EconGrowth.Rnw
@@
 
-\section*{To-do List}
-\begin{itemize}
-\item{Heun: Figure out why CES$q$ model fails to converge with original data for JP and CN.}
-\item{Heun: Investigate why wew obtain $\rho_1 < -1$ 
-for some US CES$e$ resample models.}
-\item{Pruim: Respond to Heun's wish list for graphs.}
-\item{Heun: Figure out why CESe for ZA with $x$ fails during resampling.}
-\item{Heun: Review all assumptions for CES with energy models. 
-There are several assumptions for rho and rho1 for various countries. 
-When we are resampling, we probably don't want to specify those values.}
-\item{Heun: Investigate possible conflicting use of exergy by Warr and Ayres.}
-\item{Heun: Fix the energy sankey diagram from the seminar}
-\item{Heun: Include adjusted sankey diagram in the seminar}
-\item{Heun: Add CES production function fits}
-      \begin{itemize}
-      \item{Write up the decisions about parameter estimation for the 
-            CES production function fits}
-      \item{Revisit my assumptions for the CES production function 
-            (with energy) for each country.}
-      \item{Fix the problems with $\sigma_1$ and $\sigma$ values in 
-            the CES parameter tables in the appendix}
-      \item{Add CES rows to the AIC table. Code is in the 
-            \texttt{createAICTable} function, but it is not yet working. 
-            Need to find a way to calculate AIC for the object that is 
-            returned from the \texttt{cesEst} function.}
-      \end{itemize}
-\item{Heun: Fix warnings of the form \texttt{Warning:  step factor 0.000488281 reduced below ’minFactor’ of 0.000976562} in the code that generates the Cobb-Douglas with energy fits.}
-\item{de Wit: review, critique, and contextualize.}
-\item{\st{Heun: Add option for $m = 1$ in single-factor models.}}
-\item{\st{Heun: Re-implement confidence interval calculations to use
-resampling methods.}}
-      \begin{itemize}
-      \item{\st{SF}}
-      \item{\st{CD}}
-      \item{\st{CDe}}
-      \item{\st{CES}}
-      \item{\st{CESe}}
-      \item{\st{LINEX}}
-      \end{itemize}
-\item{\st{Heun: Include scatter graphs for model parameters 
-estimated by resampling methods.}}
-      \begin{itemize}
-      \item{\st{SF}}
-      \item{\st{CD}}
-      \item{\st{CDe}}
-      \item{\st{CES}}
-      \item{\st{CESe}}
-      \item{\st{LINEX}}
-      \end{itemize}
-\item{\st{Heun: Decide if the single factor models should include constraints
-on $\alpha$, $\beta$, and $\gamma$. At present, the single-factor model allows
-values outside the ranges $\alpha \in (0,1)$, $\beta \in (0,1)$, and $\gamma \in (0,1)$.}}
-\item{\st{Heun: Make smaller scatter plots for resample coefficients for those 
-countries where $u$ is involved.}}
-\item{\st{Heun: Add a table that shows the fraction of unconverged resample fits
-for each model, energy type, and factor.}}
-\item{\st{Heun: Get AIC calculations working again.}}
-\item{\st{Pruim: Add base fit red dots to all cloud plots.}}
-      \begin{itemize}
-      \item{\st{SF}}
-      \item{\st{CD}}
-      \item{\st{CDe}}
-      \item{\st{CES}}
-      \item{\st{CESe}}
-      \item{\st{LINEX}}
-      \end{itemize}
-\item{\st{Heun: Look into constraining $\delta \in [0,1]$
-and $\delta_1 \in [0,1]$ in the CES and CES$e$ models.}}
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction} 
-\label{sec:Introduction}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Neoclassical economic growth theory attributes output ($Y$) to factors of production:
-capital stock ($K$) and labor ($L$). The Cobb-Douglas production function is the 
-canonical representation of indexed economic output ($y$) as a function of indexed 
-labor ($l$), indexed capital stock ($k$), and an exogenous, time-dependent 
-technological progress term ($A$):
-
-\begin{equation} \label{eq:CD}
-  y = A k^\alpha l^\beta; A = \mathrm{e}^{\lambda(t-t_0)}
-\end{equation}
-
-\noindent where $y \equiv Y/Y_\mathrm{0}$, $k \equiv K/K_\mathrm{0}$, and 
-$l \equiv L/L_\mathrm{0}$; with $Y$ represented by GDP, $K$ expressed in 
-currency units, $L$ expressed in workers or work-hours/year, time ($t$) measured in years, 
-with e being the base of the natural logarithm, and subscripts ``0'' indicating values 
-at an initial year. $A$ is a unitless technological progress term, with $\lambda$ 
-indicating the pace of technological progress (in units of 
-year$^{-1}$).\footnote{Dimensionless, indexed quantities are represented by 
-lower-case symbols 
-($y$, $k$, $l$, $e$, $q$, $x$, and $u$), and dimensional 
-quantities are represented by upper-case symbols 
-($Y$, $K$, $L$, $E$, $Q$, $X$, and $U$). One exception is the technolgical 
-progress term $A$, which is dimensionless but written upper-case by convention.} 
-Neoclassical economic growth theory as expressed in the Cobb-Douglas production 
-function makes no attempt to describe the mechanisms by which technological 
-progress ($A$) affects economic growth, nor does it attempt to describe how 
-technological progress ($A$) might vary from one economy to the next. Mathematically, 
-$A$ is a fitting parameter that aligns the predictions of Equation~\ref{eq:CD} 
-with historical data. Typically, the constraint $\alpha + \beta = 1$ is assumed, 
-indicating constant returns to scale.
-
-As shown in Equation~\ref{eq:CD} above, neoclassical economic theory does not 
-include an explicit term for the role of energy in economic growth. However, 
-\citet{Bashmakov:2007ek}, \citet{Hamilton:2009ui}, \citet{Murphy:2011jh}, 
-\citet{Benes:2012tm}, \citet{Kumhof:2012ua}, and others indicate that the 
-importance of energy for economic growth may far outweigh its cost share in the 
-economy. That neoclassical economic growth theory ignores energy is, therefore, 
-cause for concern, and inquiry into the proper approach for including energy 
-as a factor of production in economic growth modeling is both relevant and important.
-
-Some energy economists augment economic growth models by including energy as an 
-additional (or the only) factor of production. However, there is little agreement 
-on how this should be done. Neither the mathematical form of the energy-augmented 
-production function nor the quantification of energy are consistent in the 
-literature. There has been little empirical work assessing the predictive ability 
-of various energy-augmented production functions for different types of economies. 
-And, very few studies of the importance of energy in economic growth include 
-rigorous statistical assessments of energy-related fitting parameters. This paper 
-attempts to contribute to the literature by applying statistically rigorous 
-methods along three coordinates of analysis: form of the energy augmented 
-production function, energy quantification, and type of economy.
+\section*{Notes from Martin}
 
@@
 R programming dealt with nested CES see paper discussion on Kemfert.
+
+Next steps:
+
+Stages of growth crowd implicitly assumes countries at similar stage of growth will
+have similar values for $\alpha$, $\beta$, $\gamma$. However, our results show
+that not to be true. Needs further exploration to cover more (all?) countries.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Introduction} 
+\label{sec:Introduction}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+1. Set scene through energy economic modelling papers. 
+Point out that PF approaches are alive and well (Stern, Tol, Gerlagh, World Bank, IMF), 
+short lit review as part of a longer introduction.  
+Mention competing PF approaches and parameter choice. 
+On what basis selection and how estimate parameters?
+
+2. Point out the need for adequate statistical testing and economic interpretation, 
+citing some earlier critical papers on PF limitations. Take issue with
+
+3. Spell out the contribution we will be making in this paper, 
+we are taking the approach that all models are wrong but some are useful. 
+We are after generating insights even after deeper assumptions of econ growth theory are very limiting.
+
+4. Introduce coordinates of analysis.
+
+The remainder of this paper is organized as follows: **** complete this sentence ****.
 
@@
 \section{Parameter Estimation}
-\label{sec:Parameter_Estimation}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Each of the economic growth models discussed in 
-Section~\ref{sec:Prod_Func_Forms} has parameters which must be estimated 
-for each economy (see Section~\ref{sec:Economy_Types}) and 
-each energy quantification (see Section~\ref{sec:Quantification_of_Energy}) 
-via least-squares methods. The following subsections discuss 
-parameter estimation methods and interpret the results.
-
-%++++++++++++++++++++++++++++++
-\subsection{Cobb-Douglas Models}
-\label{sec:CD_Parameter_Estimation}
-%++++++++++++++++++++++++++++++
-
-The Cobb-Douglas model without energy is given by 
-Equation~\ref{eq:CD}. The Cobb-Douglas production function was
-reparameterized as
-
-\begin{equation} \label{eq:CD_reparam}
-  y = A k^{\alpha} l^{1-\alpha}; A = \mathrm{e}^{\lambda (t-t_0)}
-\end{equation}
-
-\noindent to ensure $\alpha + \beta = 1$ for constant returns to scale. 
-$\lambda$ and $\alpha$ were estimated by the 
-\texttt{R} \citep{R} function \texttt{nls}. 
-If the estimated value for $\alpha$ was found outside the interval $[0,1]$, 
-we set $\alpha$ to its boundary value and re-estimated $\lambda$. 
-The value of $\beta$ was found with $\beta = 1 - \alpha$.
-
-Figure~\ref{fig:CD_Cloud_Graph} shows $\alpha$, $\beta$, and $\gamma$ parameter values for resample models for the Cobb-Douglas model (without energy).
-$\gamma$ is always 0.0, because energy is not included in this model.
-
-<<CD_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (without energy) resample model parameters.">>=
-cdResampleTrianglePlot(energyType=NA)
-@
-
-Converting the resample data into 95\% confidence intervals 
-provides data for Figure~\ref{fig:CD_Params_Graph}.
-Appendix~\ref{sec:Model_Parameters} 
-contains tables with numerical values of 
-Cobb-Douglas model parameters and 95\% confidence intervals.
-
-<<CD_Params_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.cap="Cobb-Douglas (without energy) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createCDParamsGraph(energyType=NA)
-@
-
-To qualitatively assess whether augmenting the Cobb-Douglas model with energy 
-will be beneficial, we created partial residual plots as shown in 
-Figures~\ref{fig:CDPartialResidualsQ}--\ref{fig:CDPartialResidualsU} below. 
-If a monotonic trend is observed on the graphs, we expect that 
-energy augmentation will be beneficial. 
-However, no strong monotonic tends are observed for any country, 
-with the exception, perhaps, of the United Kingdom, whose residuals are, 
-on average, above 0.
-
-<<CDPartialResidualsQ, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="Cobb-Douglas partial residuals plot for thermal energy ($q$).">>=
-createPartialResidualPlot(modelType="CD", energyType="Q", countryAbbrev=NA)
-@
-
-<<CDPartialResidualsX, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="Cobb-Douglas partial residuals plot for exergy ($x$).">>=
-createPartialResidualPlot(modelType="CD", energyType="X", countryAbbrev=NA)
-@
-
-<<CDPartialResidualsU, fig.pos="H", fig.width=threePanelGraphWidth, fig.height=threePanelGraphHeight, fig.align="center", fig.cap="Cobb-Douglas partial residuals plot for useful work ($u$).">>=
-createPartialResidualPlot(modelType="CD", energyType="U", countryAbbrev=NA)
-@
-
-To estimate the parameters $\lambda$, $\alpha$, $\beta$, and $\gamma$ 
-in the energy-augmented Cobb-Douglas model, Equation~\ref{eq:CDe} 
-was reparameterized as
-
-\begin{equation} \label{eq:CDe_AB_reparam}
-  y = A k^{\min(a,b)} l^{|b-a|} e^{1 - \max(a,b)}; A = \mathrm{e}^{\lambda (t-t_0)}
-\end{equation}
-
-\noindent with 
-$\alpha = \min(a,b)$, 
-$\beta = |b-a|$, and 
-$\gamma = 1 - \max(a,b)$.
-The reparameterization ensures that $\alpha + \beta + \gamma = 1$. 
-The \texttt{R} \citep{R} function \texttt{nls} was used to estimate 
-values of $\lambda$, $a$, and $b$.
-If the fitted value for $a$ ($b$) fell outside $[0,1]$, it was 
-set equal to its boundary value and $\lambda$ and $b$ ($a$) 
-were re-estimated.
-
-To demonstrate the characteristics of the parameter estimation process, 
-we performed a grid search over values of $\gamma$, 
-wherein we re-estimated values of $\lambda$, $\alpha$, and 
-$\beta$ at each value of $\gamma$. 
-Figure~\ref{fig:CDeGridLattice} shows the sum of squared errors ($SSE$), 
-$\alpha$, and $\beta$ as a function of the fixed value of 
-$\gamma$ with thermal energy ($q$).
-
-**** Fix the right y axis label. SSE should be italicized ($SSE$). 
-Also, scaling on the axis labels and scales is not being picked up. ****
-
-<<CDeGridLattice, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Grid search over $\\gamma$ for Cobb-Douglas model with thermal energy ($q$).">>=
-cdeGridLattice(energyType="Q")
-@
-
-Figure~\ref{fig:CDeGridLattice} shows that, for most economies,
-the minimum $SSE$ occurs at or near a boundary of 
-$\alpha$, $\beta$, or $\gamma$. 
-The parameter estimation algorithm (\texttt{nls}) had difficulty converging when
-the optimal value for the parameter represented by the absolute value function 
-(in Equation~\ref{eq:CDe_AB_reparam}, $\beta$) 
-was near a boundary. If the absolute value caused non-convergence of the 
-\texttt{nls} function, second and, if necessary, third reparameterizations 
-were attempted:
-
-\begin{equation} \label{eq:CDe_CD_reparam}
-  y = A k^{1 - \max(c,d)} l^{\min(c,d)} e^{|d-c|}; A = \mathrm{e}^{\lambda (t-t_0)}
-\end{equation}
-
-\begin{equation} \label{eq:CDe_FG_reparam}
-  y = A k^{|g-f|} l^{1 - \max(f,g)} e^{\min(f,g)}; A = \mathrm{e}^{\lambda (t-t_0)}
-\end{equation}
-
-\noindent If none of the three reparameterizations converged, 
-the parameterization with the smallest $SSE$
-was used. \ref{sec:Convergence_Resample_Models} shows the 
-fraction of unconverged models for each model type. The above approach
-resulted in very few unconverged resample models, 
-even with \Sexpr{numResamples()} resamples.
-
-Figure~\ref{fig:CDq_Cloud_Graph} shows $\alpha$, $\beta$, and $\gamma$ 
-parameter values for Cobb-Douglas (with $q$) resample models.
-
-<<CDq_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (with $q$) resample model parameters.">>=
-cdResampleTrianglePlot(energyType="Q")
-@
-
-Figure~\ref{fig:CDx_Cloud_Graph} shows $\alpha$, $\beta$, and $\gamma$ parameter values for resample models for the Cobb-Douglas model (with $x$).
-
-<<CDx_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (with $x$) resample model parameters.">>=
-cdResampleTrianglePlot(energyType="X")
-@
-
-Figure~\ref{fig:CDu_Cloud_Graph} shows $\alpha$, $\beta$, and $\gamma$ parameter values for resample models for the Cobb-Douglas model (with $u$).
-
-<<CDu_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=threePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (with $u$) resample model parameters.">>=
-cdResampleTrianglePlot(energyType="U")
-@
-
-Figure~\ref{fig:CDq_Params_Graph} shows values and 95\% confidence intervals 
-for the parameters for the Cobb-Douglas model (with $q$).
-
-<<CDq_Params_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.cap="Cobb-Douglas (with $q$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createCDParamsGraph(energyType="Q")
-@
-
-The Cobb-Douglas (with exergy) parameters are given in 
-Table~\ref{tab:CD_Parameters_With_X}.
-
-Figure~\ref{fig:CDx_Params_Graph} shows values and 95\% confidence intervals 
-for the parameters for the Cobb-Douglas model (with $x$).
-
-<<CDx_Params_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.cap="Cobb-Douglas (with $x$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createCDParamsGraph(energyType="X")
-@
-
-Figure~\ref{fig:CDu_Params_Graph} shows values and 95\% confidence intervals 
-for the parameters for the Cobb-Douglas model (with $u$).
-
-<<CDu_Params_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.cap="Cobb-Douglas (with $u$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createCDParamsGraph(energyType="U")
-@
-
-Figure~\ref{fig:CD_GDP_Lattice_Graph} compares predictions 
-from the Cobb-Douglas models 
-(without energy, with $e=q$, with $e=x$, and with $e=u$) to historical data.
-
-<<CD_GDP_Lattice_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas results.">>=
-createCDLatticeGraph()
-@
-
-%++++++++++++++++++++++++++++++
-\subsection{CES Models}
-\label{sec:CES_Parameter_Estimation}
-%++++++++++++++++++++++++++++++
-
-% This bit about the Stern model is commented out for now. I'm leaving it in the paper in case we decide to use it later.
-% \citet{Stern:2012ey} developed a CES model of the form\footnote{The CES equation in \citet{Stern:2012ey} appears as
-% 
-% \begin{equation*} \label{eq:Stern_CES_model}
-%   y = \left\{ (1-\gamma_E)^{1/\sigma} \left[ k^{\alpha} \left( \mathrm{e}^{\lambda_L(t-t_0)} l \right)^{\beta} \right]^{\frac{\sigma-1}{\sigma}}   
-%       + (\gamma_E)^{1/\sigma} \left[ \mathrm{e}^{\lambda_E(t-t_0)} e \right]^{\frac{\sigma - 1}{\sigma}}   \right\}
-%       ^{\frac{\sigma}{\sigma - 1}},
-% \end{equation*}
-% 
-% but the $1/\sigma$ exponent on the $(1-\gamma_E)$ and $\gamma_E$ terms is erroneous due to $y_{\mathrm{t_0}} \neq 1$.} 
-% 
-% 
-% \begin{equation} \label{eq:Stern_CES_model_in_print}
-%   y = \left\{ (1-\gamma_E) \left[ k^{\alpha} \left( \mathrm{e}^{\lambda_L(t-t_0)} l \right)^{\beta} \right]^{\frac{\sigma-1}{\sigma}}   
-%       + (\gamma_E) \left[ \mathrm{e}^{\lambda_E(t-t_0)} e \right]^{\frac{\sigma - 1}{\sigma}}   \right\}
-%       ^{\frac{\sigma}{\sigma - 1}},
-% \end{equation}
-% 
-% \noindent where $e$ is one of $q$, $x$, or $u$; $\sigma$, $\gamma_E$, $\beta$, $\lambda_L$, and $\lambda_E$ are fitting parameters; $\mathrm{e}$ is the base of the natural logarithm; and the sum $\alpha + \beta$ is constrained to unity.
-
-The CES model without and with energy is given by 
-Equations~\ref{eq:CES} and \ref{eq:CESe}, respectively. 
-The \texttt{R} \citep{R} package \texttt{micEconCES} 
-\citep{Henningsen:2011td} was used to estimate parameters 
-$\gamma$, $\lambda$, $\delta_1$, $\rho_1$, $\delta$, and $\rho$. 
-**** More details here about which algorithms were used, etc. 
-Complete after our work this summer. ****
-
-% \citet{Henningsen:2011td}, in their detailed analysis of 
-% \citet{Kemfert:1998vd}, found that 
-% 
-% \begin{quote}
-% \ldots the Levenberg-Marquardt and the PORT algorithms 
-% are---at least in this study---most likely to find the 
-% coefficients that give the best fit to the model, 
-% where the PORT algorithm can be used to restrict the estimates 
-% to the economically meaningful region.
-% \end{quote}
-
-Coefficients for each resampled CES model (without energy)
-are shown in 
-Figures~\ref{fig:CES_lambda_gamma_Cloud_Graph}--\ref{fig:CES_sigma_delta_Cloud_Graph}.
-
-<<CES_lambda_gamma_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\lambda$ and $\\gamma$.">>=
-cesResamplePlotLambdaGamma(energyType=NA)
-@
-
-<<CES_sigma_1_delta_1_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
-cesResamplePlotSigma_1Delta_1(energyType=NA)
-@
-
-The next graph is not particularly interesting, 
-because $\delta \rightarrow 1.0$, 
-$\rho \rightarrow -1$, and 
-$\sigma \rightarrow \infty$
-for the CES without energy model.
-
-<<CES_sigma_delta_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\rho$ and $\\delta$.">>=
-cesResamplePlotSigmaDelta(energyType=NA)
-@
-
-Figure~\ref{fig:CES_Params_Graph} shows values and 95\% confidence intervals 
-for the parameters for the CES model (without energy).
-
-<<CES_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (without energy) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createCESParamsGraph(energyType=NA)
-@
-
-Similar to the analysis of the Cobb-Douglas model in 
-Section~\ref{sec:CD_Parameter_Estimation}, 
-we make partial residual plots for the CES model (without energy) in 
-Figures~\ref{fig:CESPartialResidualsQ}--\ref{fig:CESPartialResidualsU} below. 
-Again, no strong monotonic trend is observed, suggesting the 
-energy-augmentation of the CES model will not significantly improve the model.
-
-<<CESPartialResidualsQ, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="CES partial residuals plot for thermal energy ($q$).">>=
-createPartialResidualPlot(modelType="CES", energyType="Q", countryAbbrev=NA)
-@
-
-<<CESPartialResidualsX, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.align="center", fig.cap="CES partial residuals plot for exergy ($x$).">>=
-createPartialResidualPlot(modelType="CES", energyType="X", countryAbbrev=NA)
-@
-
-<<CESPartialResidualsU, fig.pos="H", fig.width=threePanelGraphWidth, fig.height=threePanelGraphHeight, fig.align="center", fig.cap="CES partial residuals plot for useful work ($u$).">>=
-createPartialResidualPlot(modelType="CES", energyType="U", countryAbbrev=NA)
-@
-
-Coefficients for each resampled CES model (with $q$)
-are shown in 
-Figures~\ref{fig:CESq_lambda_gamma_Cloud_Graph}--\ref{fig:CESq_sigma_delta_Cloud_Graph}.
-
-<<CESq_lambda_gamma_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$) resample model parameters $\\lambda$ and $\\gamma$.">>=
-cesResamplePlotLambdaGamma(energyType="Q")
-@
-
-<<CESq_sigma_1_delta_1_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
-cesResamplePlotSigma_1Delta_1(energyType="Q")
-@
-
-<<CESq_sigma_delta_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$) resample model parameters $\\sigma$ and $\\delta$.">>=
-cesResamplePlotSigmaDelta(energyType="Q")
-@
-
-Coefficients for each resampled CES model (with $x$)
-are shown in 
-Figures~\ref{fig:CESx_lambda_gamma_Cloud_Graph}--\ref{fig:CESx_sigma_delta_Cloud_Graph}.
-
-<<CESx_lambda_gamma_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$) resample model parameters $\\lambda$ and $\\gamma$.">>=
-cesResamplePlotLambdaGamma(energyType="X")
-@
-
-<<CESx_sigma_1_delta_1_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
-cesResamplePlotSigma_1Delta_1(energyType="X")
-@
-
-<<CESx_sigma_delta_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$) resample model parameters $\\sigma$ and $\\delta$.">>=
-cesResamplePlotSigmaDelta(energyType="X")
-@
-
-Coefficients for each resampled CES model (with $u$)
-are shown in 
-Figures~\ref{fig:CESu_lambda_gamma_Cloud_Graph}--\ref{fig:CESu_sigma_delta_Cloud_Graph}.
-
-<<CESu_lambda_gamma_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$) resample model parameters $\\lambda$ and $\\gamma$.">>=
-cesResamplePlotLambdaGamma(energyType="U")
-@
-
-<<CESu_sigma_1_delta_1_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
-cesResamplePlotSigma_1Delta_1(energyType="U")
-@
-
-<<CESu_sigma_delta_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$) resample model parameters $\\sigma$ and $\\delta$.">>=
-cesResamplePlotSigmaDelta(energyType="U")
-@
-
-Figure~\ref{fig:CESq_Params_Graph} shows values and 95\% confidence intervals 
-for the parameters for the CES model (with $q$).
-
-<<CESq_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with $q$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
-createCESParamsGraph(energyType="Q")
-@
-
-Figure~\ref{fig:CESx_Params_Graph} shows values and 95\% confidence intervals 
-for the parameters for the CES model (with $x$).
-
-<<CESx_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with $x$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
-createCESParamsGraph(energyType="X")
-@
-
-Figure~\ref{fig:CESu_Params_Graph} shows values and 95\% confidence intervals 
-for the parameters for the CES model (with $u$).
-
-<<CESu_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with $u$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
-createCESParamsGraph(energyType="U")
-@
-
-Figure~\ref{fig:CES_GDP_Lattice_Graph} compares CES model predictions 
-to historical data.
-
-<<CES_GDP_Lattice_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES results.">>=
-createCESLatticeGraph()
-@
-
-%++++++++++++++++++++++++++++++
-\subsection{Confidence Intervals for Cobb-Douglas and CES Energy Parameters}
-\label{sec:CI_for_CD_and_CES}
-%++++++++++++++++++++++++++++++
-
-The key energy parameters for the Cobb-Douglas and CES models are 
-$\gamma$, $\delta$, and $\sigma$. 
-The parameter $\gamma$ in the Cobb-Douglas model (Equation~\ref{eq:CDe}) 
-indicates the importance of energy for economic growth. 
-When $\gamma \rightarrow 0$, energy is not a significant contributor 
-to economic growth for an economy. 
-Conversely, when $\gamma \rightarrow 1$, energy is the primary contributor 
-to economic growth. 
-However, if the 95\% confidence interval for $\gamma$ for any given economy 
-extends to 0.0, we cannot say with high confidence whether or not energy 
-makes a meaningful contribution to economic growth for that economy. 
-On a graph of the width of the 95\% confidence interval for 
-$\gamma$ ($CI_{95\%,\gamma}$) vs. $\gamma$, where each economy is represented 
-by a point (its two-letter abbreviation; see Table~\ref{tab:Economy_Examples}), 
-the locus of points where the 95\% confidence interval for 
-$\gamma$ crosses 0 is a diagonal line. 
-If the combination of $\gamma$ and its confidence interval 
-for a given economy is below and to the right of the line, 
-we have high confidence that we can say whether or not energy 
-is a significant contributor to economic growth. 
-Thus, only when $\gamma$ is below the line and small (i.e., close to 0) 
-for an economy, can we say with confidence that energy is 
-an insignificant contributor to economic growth. 
-Only when $\gamma$ is below the line and large (i.e., close to 1) 
-for an economy can we say that energy is a significant contributor 
-to economic growth, according to the Cobb-Douglas model.
-
-The left column of graphs in Figure~\ref{fig:CIvsParam_Lattice_Graph} shows 
-$CI_{95\%,\gamma}$ vs. $\gamma$ for the three quantifications of energy 
-(thermal energy, $q$, exergy, $x$, and useful work, $u$). 
-We note that most economies are above and to the left of the line, 
-while only a few are below and to the right.
-
-For the CES model (Equation~\ref{eq:CESe}), the parameter $\delta$ 
-indicates the importance of energy for economic growth. 
-When $\delta \rightarrow 1$, energy is an insignificant contributor 
-to economic growth, and when $\delta \rightarrow 0$, 
-energy is the primary contributor to economic growth for an economy. 
-However, if the 95\% confidence interval for $\delta$ extends to 1, 
-we cannot say with high confidence whether or not energy makes 
-a meaningful contribution to economic growth for that economy. 
-In a manner similar to $\gamma$ for the Cobb-Douglas model, 
-we note that if the combination of $\delta$ and its confidence interval 
-for a given economy is below and to the left of the line, 
-we have high confidence that we can say whether or not energy is 
-a significant contributor to economic growth. 
-Thus, only when $\delta$ is below the line and large (i.e., close to 1) 
-for an economy, can we say with confidence that energy is 
-an insignificant contributor to economic growth. 
-Only when $\delta$ is below the line and small (i.e., close to 0) 
-for an economy can we say that energy is a significant contributor 
-to economic growth, according to the CES model.
-
-The middle column of graphs in Figure~\ref{fig:CIvsParam_Lattice_Graph} shows 
-$CI_{95\%,\delta}$ vs. $\delta$ for the three quantifications of energy 
-(thermal energy, $q$, exergy, $x$, and useful work, $u$). 
-We note that most economies are above and to the right of the line, 
-while only a few are below and to the left.
-
-For the CES model (Equation~\ref{eq:CESe}), the parameter $\sigma$ indicates 
-whether capital stock and labor ($kl$) and energy ($e$) are 
-complements ($\sigma <$ 1) or substitutes ($\sigma >$ 1). 
-For countries whose combination of  $\sigma$ and its confidence interval is 
-below and to the left of the lines in the rightmost graphs 
-of Figure~\ref{fig:CIvsParam_Lattice_Graph} we can say (with 95\% confidence) 
-that ($kl$) and ($e$) are complements. 
-For economies whose value of $\sigma$ is below and to the right of the line, 
-we can say (with 95\% confidence) that ($kl$) and ($e$) are substitutes. 
-For economies whose value of $\sigma$ is above those lines, 
-we cannot say with 95\% confidence whether ($kl$) and ($e$) are substitues or complements.
-
-The right column of graphs in Figure~\ref{fig:CIvsParam_Lattice_Graph} shows 
-$CI_{95\%,\sigma}$ vs. $\sigma$ for the three quantifications of energy 
-(thermal energy, $q$, exergy, $x$, and useful work, $u$). 
-We note that energy ($e$) unambiguously complements 
-capital stock and labor ($kl$) for most economies.
-
-<<CIvsParam_Lattice_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="95\\% Confidence interval widths vs.
-parameter values for key energy parameters ($\\gamma$, $\\delta$, and $\\sigma$) of the Cobb-Douglas and CES models with energy.
-If an economy appears in the region above a dashed line, the 95\\% confidence interval for the parameter extends to or beyond $\\gamma \\le$ 0 (cannot say with 95\\% confidence that energy is important for the Cobb-Douglas model), $\\delta \\ge$ 1 (cannot say with 95\\% confidence that energy is important for the CES model), or $\\sigma$ = 1 (cannot say with 95\\% confidence whether ($kl$) and ($e$) are complements or substitutes in the CES model).">>=
-CIvsParamLattice(countryAbbrevScaling=0.6)
-@
-
-Regardless of model (Cobb-Douglas or CES) or energy quantification 
-($q$, $x$, or $u$), there are few economies for which we can say 
-with high confidence (at the 95\% level) that energy plays 
-a significant role in economic growth. 
-However, in seeming contradiction, results for the CES model indicate 
-that energy complements capital stock and labor, 
-indicating that energy ($e$) is essential for capital stock ($k$) and 
-labor ($l$) to generate economic growth. 
-One possible explanation for this apparent contradiction is 
-to consider energy as embedded within capital stock and labor: 
-it takes energy to make both captial stock and labor available to generate economic growth.
-
-**** Martin: Need additional interpretation here. ****
-
-%++++++++++++++++++++++++++++++
-\subsection{LINEX Models}
-\label{sec:LINEX_Parameter_Estimation}
-%++++++++++++++++++++++++++++++
-
-The LINEX model is given in Equation~\ref{eq:LINEX}. 
-Parameters $a_0$ and $c_t$ were estimated using the \texttt{nls} function 
-in \texttt{R} \citep{R}.
-
-Figures~\ref{fig:LINEXq_Resample_Graph}--\ref{fig:LINEXu_Resample_Graph}
-show the coefficients estimated from resampled data.
-
-<<LINEXq_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX model (with $q$) resampling results.">>=
-# linexResamplePlot(energyType="Q")
-linexResamplePlot(energyType="Q")
-@
-
-<<LINEXx_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX model (with $x$) resampling results.">>=
-linexResamplePlot(energyType="X")
-@
-
-<<LINEXu_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="LINEX model (with $u$) resampling results.">>=
-linexResamplePlot(energyType="U")
-@
-
-Figure~\ref{fig:LINEXq_Params_Graph} shows values and 95\% confidence intervals 
-for the parameters for the LINEX model (with $q$).
-
-<<LINEXq_Params_Graph, fig.pos="H", fig.width=linexParameterGraphWidth, fig.height=linexParameterGraphHeight, fig.cap="LINEX (with $q$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createLINEXParamsGraph(energyType="Q")
-@
-
-Figure~\ref{fig:LINEXx_Params_Graph} shows values and 
-95\% confidence intervals for the parameters for the LINEX model (with $x$).
-
-<<LINEXx_Params_Graph, fig.pos="H", fig.width=linexParameterGraphWidth, fig.height=linexParameterGraphHeight, fig.cap="LINEX (with $x$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createLINEXParamsGraph(energyType="X")
-@
-
-Figure~\ref{fig:LINEXu_Params_Graph} shows values and 
-95\% confidence intervals for the parameters for the LINEX model (with $u$).
-
-<<LINEXu_Params_Graph, fig.pos="H", fig.width=linexParameterGraphWidth, fig.height=linexParameterGraphHeight, fig.cap="LINEX (with $u$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createLINEXParamsGraph(energyType="U")
-@
-
-Figure~\ref{fig:LINEX_GDP_Lattice_Graph} compares LINEX model predictions to historical data.
-
-<<LINEX_GDP_Lattice_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX results.">>=
-createLINEXLatticeGraph()
-@
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Implications}
-\label{sec:Implications}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-**** This section needs to be re-evaluated after the statistical work is 
-tightened up during Summer 2013. ****
-
-The above analysis points to several implications.
-
-\begin{itemize}
-  \item{The use of chemical exergy, as opposed to thermal energy, 
-        in economic growth models is probably unnecessary. 
-        Table~\ref{tab:Exergy_Allocation} shows that exergy allocation factors are 
-        all close to unity. 
-        Therefore, there is a small difference in absolute magnitude 
-        between $Q$ and $X$. 
-        However, there is no difference in indexed magnitude 
-        between $q$ and $x$, unless there are large changes 
-        in energy mix for an economy. 
-        Figure~\ref{fig:Historical_Lattice_Graph} shows that 
-        $q$ and $x$ lines lie atop one another for almost every economy.}
-  \item{The concept of useful work ($u$) is potentially useful and 
-        should be explored beyond developed economies. 
-        Figure~\ref{fig:Historical_Lattice_Graph} shows that $u$ grows 
-        at very different rates from thermal energy ($q$) or exergy ($x$). 
-        Useful work may contain different information from thermal energy and exergy.}
-  \item{Figure~\ref{fig:CDeGridLattice} shows that the set 
-        of parameters ($\lambda$, $\alpha$, $\beta$, and $\gamma$) that 
-        minimizes $SSE$ for the energy-augmented Cobb-Douglas production function 
-        always (with the exception of Saudi Arabia) has 
-        $\beta = 0$ or $\gamma = 0$. 
-        This result implies that it is unnecessary to include both labor ($l$) 
-        and energy ($e$) in the Cobb-Douglas production function.}
-  \item{Partial residual plots for both the Cobb-Douglas model 
-        (Figures~\ref{fig:CDPartialResidualsQ}--\ref{fig:CDPartialResidualsU} and 
-        CES model (Figures~\ref{fig:CESPartialResidualsQ}--\ref{fig:CESPartialResidualsU}) 
-        indicate that augmenting the Cobb-Douglas and CES production functions 
-        with energy is not beneficial.}
-  \item{Figure~\ref{fig:CIvsParam_Lattice_Graph} shows that important energy parameters 
-        for both the energy-augmented Cobb-Douglas and CES production functions 
-        ($\gamma$ and $\delta$, respectively) have large confidence intervals such that 
-        we are unable to say (at the 95\% confidence level) that energy is 
-        an important factor for economic growth, 
-        vis-\`{a}-vis capital stock ($k$) or labor ($l$) for most economies.}
-  \item{Figure~\ref{fig:CIvsParam_Lattice_Graph} indicates that 
-        energy (in all quantifications: $q$, $x$, and $u$) is complementary 
-        to capital stock ($k$) and labor ($l$) for producing economic growth, 
-        according to the CES model.}
-  \item{Figures~\ref{fig:LINEXq_Params_Graph}--\ref{fig:LINEXu_Params_Graph} 
-        indicate that LINEX model fitting parameters $a_0$ and $c_t$ are 
-        significant (at the 95\% confidence level) for nearly all countries. 
-        Figure~\ref{fig:LINEX_GDP_Lattice_Graph} shows that 
-        the LINEX production function provides reasonably good fits 
-        to historical data. 
-        This evidence indicates that the LINEX production function 
-        (with energy ($e$) as its only factor of production) is 
-        a reasonable replacement for the Cobb-Douglas and CES production functions 
-        which have capital stock ($k$) and labor ($l$) as factors of production.}
-  \item{**** Discuss the AIC values for each of the model types. 
-        It could happen that the LINEX models have a higher AIC value than 
-        the CD or CES models. 
-        If so, that would mean that the LINEX model is actually preferred 
-        to the CD or CES models, primarily because it does a good-enough job 
-        of predicting economic output with fewer adjustable parameters (2) 
-        compared to CD (2), CDe (3), CES (4), CESe (6). 
-        Discuss with Randy Pruim during Summer 2013. ****}
-\end{itemize}
-
-The evidence above leads to a re-conceptualization of the relationships 
-among energy, capital stock, and labor: energy is \emph{embedded within} 
-capital stock and labor, and, therefore, it is both 
-unwarranted and unnecessary to include \emph{both} energy ($e$) 
-and the capital stock/labor pair ($kl$) in a production function. 
-The empirical evidence indicates that \emph{both} 
-(a) capital stock/labor production functions (Cobb-Douglas and CES without energy) and 
-(b) an energy-only production function (LINEX) provide a reasonable models for economic growth.
-
-**** Martin needs to flesh out the above section. ****
+\label{sec:ParameterEstimation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+This section should cover both technique and results. 
+Organize along coordinates of analysis.
+
+1. Discuss parameter estimation for each model here.
+
+2. Show scatter plot results.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Discussion of Results}
+\label{sec:DiscussionOfResults}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Drive towards new insights from our stats tested comparative approach
 
@@
 
-**** Edit conclusion after we finish the statistical studies. ****
-
-We claim that statistical properties (e.g., covariances) 
-of historical economic data and statistical properties 
-(e.g., confidence intervals) of production function fitting parameters are 
-extremely useful for interpreting historical economic data and growth model results. 
-We know of no previous studies on the role of energy in the economy that 
-presented these statistical properties, 
-and we presume that energy-augmentation of production functions has been done 
-in the literature without regard to whether it is statistically meaningful to do so. 
-That different authors can find good correlation 
-between model predictions and historical data 
-with very different growth model coefficients is 
-a result of the heretofore unseen large confidence intervals 
-on the fitting parameters. 
-As a consequence, economic growth models that assume very different relationships 
-among capital stock, labor, and energy can all be successful in matching historical data. 
-In short, the production function becomes a canvas upon which 
-investigators can paint their preconceived vision of the importance 
-(or not) of energy for economic growth.
-
-To break free from this problem, a new way of conceptualizing 
-the relationships among capital stock, labor, and energy is required. 
-Our analysis above indicates that energy is unequivocally complementary 
-to the capital stock/labor pair for many types of economies. 
-We agree with K\"{u}mmel that energy is required 
-to form and maintain capital stock, and that energy is required to sustain labor. 
-(And, for that matter, we agree that labor is required to operate capital stock.) 
-In other words, energy is already, always \emph{embedded within} capital stock and labor. 
-We posit that the complementarity between ($kl$) and ($e$) shown 
-by the energy-augmented CES production function is due 
-to the embeddedness of energy within the traditional factors of production, 
-capital stock and labor.
-
-The foregoing discussion means that production functions with either 
-(a) energy only (such as the LINEX model) or 
-(b) capital stock/labor only (such as the Cobb-Douglas and CES models without energy) 
-can both be successful in predicting economic growth. 
-But, the embedded nature of energy in capital stock and labor means that 
-augmenting a capital stock/labor only production function 
-with energy is redundant and unnecessary, and, therefore, unwarranted.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Future Work}
+\label{sec:FutureWork}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \section*{Acknowledgements}
+\label{sec:Acknowledgements}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-The following tables show covariances among GDP ($y$) and 
-factors of production ($k$, $l$, $q$, $x$, and $u$). 
-Covariances are calculated for the following years: 
-\begin{itemize}
-  \item{1980--2011 for covariances among 
-        $y$, $k$, $l$, $q$, and $x$ for developed\\*economies;}
-  \item{1980--2000 for covariances involving 
-        $u$ for developed economies; and}
-  \item{1991--2011 for covariances among 
-        $y$, $k$, $l$, $q$, and $x$ for developing\\*economies.}
-\end{itemize}
-
-<<Print_Covariance_Tables, results='asis'>>=
-#I wish I could say the following, but I get bogus "$US" strings appearing in the LaTeX output.
-#lapply(countryAbbrevs, printCovarTable)
-printCovarTable(countryAbbrev="US"); printCovarTable(countryAbbrev="UK")
-printCovarTable(countryAbbrev="JP")
-printCovarTable(countryAbbrev="CN"); printCovarTable(countryAbbrev="ZA")
-printCovarTable(countryAbbrev="SA"); printCovarTable(countryAbbrev="IR")
-printCovarTable(countryAbbrev="TZ"); printCovarTable(countryAbbrev="ZM")
-@
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Model Parameters}
-\label{sec:Model_Parameters}
-\setcounter{table}{0} % Restarts table number counter at 0 in this section.
-\setcounter{figure}{0} % Restarts figure number counter at 0 in this section.
-\setcounter{equation}{0} % Restarts equation counter to 0 in this section.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%++++++++++++++++++++++++++++++
-\subsection{Single-factor Models}
-%++++++++++++++++++++++++++++++
-
-**** This subsection should be either 
-(a) deleted or 
-(b) moved into the main body of the paper. 
-I would prefer to delete it on the grounds that single-factor models are 
-not often used in the literature. 
-However, I want to talk with Martin about this before making the decision. 
-So, I'm parking it here for now. --Matt. ****
-
-The following tables provide results for parameters in single-factor models.
-
-<<SF_Params_Tables, results='asis'>>=
-#I wish I could say this, but I get bogus K [1]” strings appearing in the LaTeX output.
-#lapply(factors, printSingleFactorParamsTable)
-printSFParamsTable(factor="K"); printSFParamsTable(factor="L")
-printSFParamsTable(factor="Q"); printSFParamsTable(factor="X"); printSFParamsTable(factor="U")
-@
-
-%++++++++++++++++++++++++++++++
-\subsection{Cobb-Douglas Models}
-%++++++++++++++++++++++++++++++
-
-The following tables provide results for parameters 
-in Cobb-Douglas models with and without energy terms.
-
-<<CD_Params_Table, results='asis'>>=
-printCDParamsTable(energyType=NA)    #Without energy
-printCDParamsTable(energyType="Q"); printCDParamsTable(energyType="X"); printCDParamsTable(energyType="U") #With energy
-@
-
-%++++++++++++++++++++++++++++++
-\subsection{CES Models}
-%++++++++++++++++++++++++++++++
-
-The following tables provide results for parameters 
-in CES models with and without energy terms.
-
-<<CES_Params_Table, results='asis'>>=
-printCESParamsTableA(energyType=NA);  printCESParamsTableB(energyType=NA)
-printCESParamsTableA(energyType="Q"); printCESParamsTableB(energyType="Q")
-printCESParamsTableA(energyType="X"); printCESParamsTableB(energyType="X")
-printCESParamsTableA(energyType="U"); printCESParamsTableB(energyType="U")
-@
-
-%++++++++++++++++++++++++++++++
-\subsection{LINEX Models}
-%++++++++++++++++++++++++++++++
-
-The following tables provide results for parameters 
-in LINEX models.
-
-<<LINEX_Params_Table, results='asis'>>=
-printLINEXParamsTable(energyType="Q"); printLINEXParamsTable(energyType="X"); printLINEXParamsTable(energyType="U")
-@
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Goodness of fit}
-\label{sec:Goodness_of_Fit}
-\setcounter{table}{0} % Restarts table number counter at 0 in this section.
-\setcounter{figure}{0} % Restarts figure number counter at 0 in this section.
-\setcounter{equation}{0} % Restarts equation counter to 0 in this section.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-We assess goodness of fit via the Akaike Information Criterion (AIC). 
-AIC values for all models and all countries are shown in Table~\ref{tab:AICTable}. 
-Increasing goodness of fit is indicated by smaller 
-(i.e., more negative) AIC values. 
-AIC values can be compared per data set (i.e., per country) but 
-not across data sets (i.e., not across countries).
-
-<<AIC_Table, results='asis', label="AIC_Table">>=
-print(createAICTable(), 
-      caption.placement="top", 
-      sanitize.rownames.function = identity,
-      size="\\tiny",
-      table.placement="H")
-@
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Convergence of Resample Models}
-\label{sec:Convergence_Resample_Models}
-\setcounter{table}{0} % Restarts table number counter at 0 in this section.
-\setcounter{figure}{0} % Restarts figure number counter at 0 in this section.
-\setcounter{equation}{0} % Restarts equation counter to 0 in this section.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The following table shows the fraction of resample models 
-that did not achieve convergence when estimating model parameters.
-
-<<Unconverged_Frac_Table, results='asis'>>=
-printFracUnconvergedXtable()
-@
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Single-factor Models}
-\label{sec:Single-factor_Models}
-\setcounter{table}{0} % Restarts table number counter at 0 in this section.
-\setcounter{figure}{0} % Restarts figure number counter at 0 in this section.
-\setcounter{equation}{0} % Restarts equation counter to 0 in this section.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-**** This section should be either 
-(a) deleted or 
-(b) moved into the main body of the paper. 
-I would prefer to delete it on the grounds that single-factor models are 
-not often used in the literature. 
-However, I want to talk with Martin about this before making the decision.  
-So, I'm parking it here for now. --Matt. ****
-
-We begin by fitting single-factor economic models of the form
-
-\begin{equation} \label{eq:Single_Factor_Generic}
-  y = \mathrm{e}^{\lambda (t-t_0)}f^{m}
-\end{equation}
-
-\noindent to historical data where the factor of production ($f$) is 
-one of $k$, $l$, $q$, $x$, or $u$, and 
-the exponent ($m$) is $\alpha$ for $k$, $\beta$ for $l$, 
-or $\gamma$ for $q$, $x$, and $u$.
-
-Coefficients derived from resampling are shown in 
-Figures~\ref{fig:SFk_Resample_Graph}--\ref{fig:SFu_Resample_Graph}. 
-In each case, the exponent on the factor of production is assumed to be $m = 1$.
-
-<<SFk_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single factor model (with $f = k$ and $m = \\alpha$) resampling results.">>=
-sfResamplePlot(factor="K")
-@
-
-<<SFl_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single factor model (with $f = l$ and $m = \\beta$) resampling results.">>=
-sfResamplePlot(factor="L")
-@
-
-<<SFq_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single factor model (with $f = q$ and $m = \\gamma$) resampling results.">>=
-sfResamplePlot(factor="Q")
-@
-
-<<SFx_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single factor model (with $f = x$ and $m = \\gamma$) resampling results.">>=
-sfResamplePlot(factor="X")
-@
-
-<<SFu_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="Single factor model (with $f = u$ and $m = \\gamma$) resampling results.">>=
-sfResamplePlot(factor="U")
-@
-
-Converting the resample model coefficient data to 95\% confidence intervals
-gives the results shown in 
-Figures~\ref{fig:SFk_Params_Graph}--\ref{fig:SFu_Params_Graph}.
-
-<<SFk_Params_Graph, fig.pos="H", fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.cap="Single-factor (with $k$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createSFParamsGraph(factor="K")
-@
-
-<<SFl_Params_Graph, fig.pos="H", fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.cap="Single-factor (with $l$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createSFParamsGraph(factor="L")
-@
-
-<<SFq_Params_Graph, fig.pos="H", fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.cap="Single-factor (with $q$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createSFParamsGraph(factor="Q")
-@
-
-<<SFx_Params_Graph, fig.pos="H", fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.cap="Single-factor (with $x$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createSFParamsGraph(factor="X")
-@
-
-<<SFu_Params_Graph, fig.pos="H", fig.width=sfParameterGraphWidth, fig.height=sfParameterGraphHeight, fig.cap="Single-factor (with $u$) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createSFParamsGraph(factor="U")
-@
-
-Figure~\ref{fig:SF_GDP_Lattice_Graph} compares single-factor model predictions 
-with historical data.
-
-<<SF_GDP_Lattice_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single-factor results.">>=
-createSFLatticeGraph()
-@
-
 %% References

### 2013-07-31 EconGrowth2.Rnw
Added Martin's notes about interpretation of results.

@@
 CD with e: roughly half, c, e, importance of l drops to 0
-CES no e: 10% c, 25% l ??
+CES no e: 10\% c, 25\% l ??
 CES with e: fig 35 e may be NB
@@
 
-Drive towards new insights from our stats tested comparative approach
+Drive towards new insights from our stats tested comparative approach..
+
+**** Notes for interpretation of results ****
+
+Country interpretation
+
+Comparison Cobb Douglas and CES results.
+
+%++++++++++++++++++++++++++++++
+\subsection{United States} 
+\label{sec:InterpUS}
+%++++++++++++++++++++++++++++++
+
+CD: Energy is unnecessary
+
+CES:
+
+($kl$)$e$: energy is unnec ($\delta$ is 1); also ($el$)$k$ energy is unnec. 
+($\delta_1$ is 0);
+
+($le$)$k$ no indication
+Relative consistent signal that energy is unnec.
+
+$\sigma$:
+capital and energy are complements
+labour and energy are subsitutable
+
+%++++++++++++++++++++++++++++++
+\subsection{United Kingdom} 
+\label{sec:InterpUK}
+%++++++++++++++++++++++++++++++
+
+CD: Capital is unnec.
+
+CES:
+
+($kl$)$e$: energy is unnec ($\delta =1$);
+
+($le$)$k$ capital is unnec. ($\delta = 1$);
+
+($ek$)$l$ ($\delta_1 = 0$) energy is unnec.
+
+Thus, inconsistent results, possibly look at different time series 
+as massive changes in economic policy in Uk economic history
+
+$\sigma$: energy is not substitutable with capital or labour, totally complementary
+
+%++++++++++++++++++++++++++++++
+\subsection{Japan} 
+\label{sec:InterpJP}
+%++++++++++++++++++++++++++++++
+
+CD: energy is unnec.
+
+CES:
+
+($kl$)$e$; ($le$)$k$; ($ek$)$l$: no indications, all are important.
+
+weak signal that labour is less necessary 
+(($kl$)$e$ $delta_1 = 0.86$ and ($ek$)$l$ $\delta = 0.89$)
+
+Thus, inconsistent results.
+
+$\sigma$: labour and energy are complements, capital and energy complements
+
+%++++++++++++++++++++++++++++++
+\subsection{China} 
+\label{sec:InterpCN}
+%++++++++++++++++++++++++++++++
+
+CD: energy not necessary, capital less necessary
+
+CES:
+
+($kl$)$e$: energy is unnec. ($\delta = 1$);
+
+($le$)$k$: labour is unnnec ($\delta_1 = 0$);
+
+($ek$)$l$ energy is unnec. ($\delta_1 \rightarrow 0$)
+
+Strong signal that energy is unnec, but the labour and capital signals are conflicting
+
+$\sigma$: capital and energy is complementary, but labour and energy more substitutable
+
+%++++++++++++++++++++++++++++++
+\subsection{South Africa} 
+\label{sec:InterpZA}
+%++++++++++++++++++++++++++++++
+
+CD: Labour is unnec.
+
+CES:
+
+($kl$)$e$: labour is unnec. ($\delta_1 = 1$);
+
+($le$)$k$ labour is unnec. ($\delta_1 = 0$);
+
+($ek$)$l$ labour is unnec. ($\delta = 1$)
+
+Consistent signal that labour is unnec.
+
+$\sigma$: capital and energy is complementary, labour and energy is substitutable
+
+%++++++++++++++++++++++++++++++
+\subsection{Saudi Arabia} 
+\label{sec:InterpSA}
+%++++++++++++++++++++++++++++++
+
+CD: no indications
+
+CES: no indications, but weak signal that labour is unnec in ($ek$)$l$ ($\delta = 0.93$)
+
+Almost consistent signal that no indocations.
+
+$\sigma$: labour and energy are complements, capital and energy are substitutes
+
+%++++++++++++++++++++++++++++++
+\subsection{Iran} 
+\label{sec:InterpIR}
+%++++++++++++++++++++++++++++++
+
+CD: energy is unnec.
+
+CES:
+
+($kl$)$e$: energy is unnec ($\delta=1$);
+
+($le$)$k$: energy is unnec. ($\delta_1=1$);
+
+($ek$)$l$: labour is unnec. ($\delta=1$)
+
+$\sigma$: labour and energy still complements, 
+but not as strong capital and energy complements
+
+%++++++++++++++++++++++++++++++
+\subsection{Tanzania} 
+\label{sec:InterpTZ}
+%++++++++++++++++++++++++++++++
+
+CD: labour in unnec.
+
+CES:
+
+($kl$)$e$: labour is unnec ($\delta_1=0.97$);
+
+($le$)$k$: weak signal that energy is unnec. ($\delta_1=0.92$); 
+very weal signal capital is unnec ($\delta=0.84$);
+
+($ek$)$l$: labour is unnec. $\delta=0.96$
+
+Consistent signal that labour is unnec, with exception of one nesting.
+
+$\sigma$: labour and energy complements, capital and energy perfect substitutes
+
+%++++++++++++++++++++++++++++++
+\subsection{Zambia} 
+\label{sec:InterpZM}
+%++++++++++++++++++++++++++++++
+
+CD: labour is unnec; energy is unnec.
+
+CES:
+
+($kl$)$e$: labour is unnec. ($\delta_1=1$); labour is unnec
+
+($le$)$k$: ($\delta_1=0$);
+
+($ek$)$l$: labour is unnec. ($\delta=1$)
+
+Consistent signal that labour is unnec.
+
+$\sigma$: labour and energy complements, not as strong. 
+Capital and energy perfect substitutes.
+
+% 
+% 
+% Discussion of results: How to get better consistent signals?
+% - Use CD as starting points and do CES convergence on that basis.
+% - Do scatterplots to get range of uncertainty inputs, then re-interpret. delta against sigma plots, as well as delta_1 and sigma_1 plots.
+% 
+% Thus, to do the fitting well we need to understand:
+% - nesting
+% - algorithm
+% - starting values
+% esp. for CES. 
+% (Maybe illustrate with one case study such as China what implications are).
+% 
+% How do we compare witj LINEX results?
+% CES is a broader specification of CD, LINEX is not.
+In LINEX no delta's nor sigmas are generated.
+Only efficiency terms are generated in LINEX, thus in other words economic growth is only possible by increased efficiency.
+% The efficiency of using energy is driven by capital stock.
+The objective/growth engine is to increase capital at a rate that is faster then growth in labour and energy.
+Increasing labour relative to energy gives a muted benefit.
+% LINEX derived for Germany: only really applicable when energy and capital are complements.
+% 
+% Discussion in relation to other papers. 
+% Problems with other papers:
+% - If not giving you all parameters
+% - Not explain nesting approach 
+% - No CI on data
+% 
+% 
+% Economic interpretation (revisit after scatterplot information)
+% Developed economies: Capital and energy is complementary (US: labour and energy substitutable)
+% NICs: Capital and energy complementary, but labour and energy more substitutable
+% OPEC: Labour and energy complementary (mixed results on capital and energy)
+% LDCs: Labour and energy complementary, Capital and energy perfect substitutes.
+%
 

### 2013-07-31 EconGrowth.Rnw
Removed country interpretation section.

--- 2013-07-29 EconGrowth.Rnw
@@
 @
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Interpretation of Results}
+\label{sec:Interpretation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+**** Notes for interpretation of results ****
+
+Discussion of results: How to get better consistent signals?
+- Use CD as starting points and do CES convergence on that basis.
+- Do scatterplots to get range of uncertainty inputs, then re-interpret. delta against sigma plots, as well as delta_1 and sigma_1 plots.
+
+Thus, to do the fitting well we need to understand:
+- nesting
+- algorithm
+- starting values
+esp. for CES. 
+(Maybe illustrate with one case study such as China what implications are).
+
+How do we compare witj LINEX results?
+CES is a broader specification of CD, LINEX is not.
+In LINEX no delta's nor sigmas are generated.
+Only efficiency terms are generated in LINEX, thus in other words economic growth is only possible by increased efficiency.
+The efficiency of using energy is driven by capital stock.
+The objective/growth engine is to increase capital at a rate that is faster then growth in labour and energy.
+Increasing labour relative to energy gives a muted benefit.
+LINEX derived for Germany: only really applicable when energy and capital are complements.
+
+Discussion in relation to other papers. 
+Problems with other papers:
+- If not giving you all parameters
+- Not explain nesting approach 
+- No CI on data
+
+Economic interpretation (revisit after scatterplot information)
+Developed economies: Capital and energy is complementary (US: labour and energy substitutable)
+NICs: Capital and energy complementary, but labour and energy more substitutable
+OPEC: Labour and energy complementary (mixed results on capital and energy)
+LDCs: Labour and energy complementary, Capital and energy perfect substitutes.
 

### 2013-07-31 EconGrowth2.Rnw

@@
 
-The remainder of this paper is organized as follows. Section~\ref{sec:Coordinates} 
-discusses the coordinates of analysis described above. 
-Section~\ref{sec:Sources_of_Data} details sources of data and calculations to 
-generate time series for economic output and factors of production. The procedures 
-for and results from parameter estimation for the various production functions 
-are discussed in Section~\ref{sec:Parameter_Estimation}. 
-Section~\ref{sec:Implications} discusses implications of the parameter estimation 
-results, and Section~\ref{sec:Conclusion} concludes. An appendix provides details 
-of all statistical results.
-
 **** Notes from Martin ****
@@
 
-The remainder of this paper is organized as follows: **** complete this sentence ****.
+Neoclassical economic growth theory attributes output ($Y$) to factors of production:
+capital stock ($K$) and labor ($L$). The Cobb-Douglas production function is the 
+canonical representation of indexed economic output ($y$) as a function of indexed 
+labor ($l$), indexed capital stock ($k$), and an exogenous, time-dependent 
+technological progress term ($A$):
+
+\begin{equation} \label{eq:CD}
+  y = A k^\alpha l^\beta; A = \mathrm{e}^{\lambda(t-t_0)}
+\end{equation}
+
+\noindent where $y \equiv Y/Y_\mathrm{0}$, $k \equiv K/K_\mathrm{0}$, and 
+$l \equiv L/L_\mathrm{0}$; with $Y$ represented by GDP, $K$ expressed in 
+currency units, $L$ expressed in workers or work-hours/year, time ($t$) measured in years, 
+with e being the base of the natural logarithm, and subscripts ``0'' indicating values 
+at an initial year. $A$ is a unitless technological progress term, with $\lambda$ 
+indicating the pace of technological progress (in units of 
+year$^{-1}$).\footnote{Dimensionless, indexed quantities are represented by 
+lower-case symbols 
+($y$, $k$, $l$, $e$, $q$, $x$, and $u$), and dimensional 
+quantities are represented by upper-case symbols 
+($Y$, $K$, $L$, $E$, $Q$, $X$, and $U$). One exception is the technolgical 
+progress term $A$, which is dimensionless but written upper-case by convention.} 
+Neoclassical economic growth theory as expressed in the Cobb-Douglas production 
+function makes no attempt to describe the mechanisms by which technological 
+progress ($A$) affects economic growth, nor does it attempt to describe how 
+technological progress ($A$) might vary from one economy to the next. Mathematically, 
+$A$ is a fitting parameter that aligns the predictions of Equation~\ref{eq:CD} 
+with historical data. Typically, the constraint $\alpha + \beta = 1$ is assumed, 
+indicating constant returns to scale.
+
+As shown in Equation~\ref{eq:CD} above, neoclassical economic theory does not 
+include an explicit term for the role of energy in economic growth. However, 
+\citet{Bashmakov:2007ek}, \citet{Hamilton:2009ui}, \citet{Murphy:2011jh}, 
+\citet{Benes:2012tm}, \citet{Kumhof:2012ua}, and others indicate that the 
+importance of energy for economic growth may far outweigh its cost share in the 
+economy. That neoclassical economic growth theory ignores energy is, therefore, 
+cause for concern, and inquiry into the proper approach for including energy 
+as a factor of production in economic growth modeling is both relevant and important.
+
+Some energy economists augment economic growth models by including energy as an 
+additional (or the only) factor of production. However, there is little agreement 
+on how this should be done. Neither the mathematical form of the energy-augmented 
+production function nor the quantification of energy are consistent in the 
+literature. There has been little empirical work assessing the predictive ability 
+of various energy-augmented production functions for different types of economies. 
+And, very few studies of the importance of energy in economic growth include 
+rigorous statistical assessments of energy-related fitting parameters. This paper 
+attempts to contribute to the literature by applying statistically rigorous 
+methods along three coordinates of analysis: form of the energy augmented 
+production function, energy quantification, and type of economy.
+
+The remainder of this paper is organized as follows. Section~\ref{sec:Coordinates} 
+discusses the coordinates of analysis described above. 
+Section~\ref{sec:Sources_of_Data} details sources of data and calculations to 
+generate time series for economic output and factors of production. The procedures 
+for and results from parameter estimation for the various production functions 
+are discussed in Section~\ref{sec:Parameter_Estimation}. 
+Section~\ref{sec:Discussion_of_Results} discusses implications of the parameter estimation 
+results, and Section~\ref{sec:Conclusion} concludes. An appendix provides details 
+of all statistical results.
 
@@
 \section{Parameter Estimation}
-\label{sec:ParameterEstimation}
+\label{sec:Parameter_Estimation}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+CES Model: It is possible for L-BFGS-B to report convergence and PORT to report non-convergence 
+but nevertheless reach a better solution (smaller sse).
+
 2. Show scatter plot results.
@@
 \section{Discussion of Results}
-\label{sec:DiscussionOfResults}
+\label{sec:Discussion_of_Results}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2013-07-31 EconGrowth2.Rnw
Added introduction material from Martin.

@@
 
+Thoughts on literature review and contextualisation of our work
+
+Imagine ourselves walking into a conversation on the role of energy in the economy.
+
+1. Listen to what others say
+
+Identify key issues and important voices
+
+\begin{itemize}
+\item{energy has become an important strategic issue, shocks in 1970s, spikes in energy prices generated renewed interest (IEA, IMF), supported by analysis on more structural depletion and technology race over time (Hamilton), cite reviews on energy and economics (Stern,...), cite articles that show close correlations energy use and economic growth (Cleveland etc)}
+\item{economic theoretical frameworks adjusted: energy theory of value; Energy fundamental in biophysical economics (Cleveland, Hall), energy as one cost in production set; energy plays a role in production (extended Solow-Swan or CES (who introduced CES first) framework)}
+\item{how to account for energy on a macro economic level?
+taken up in economic growth theory by (1) including energy in PF (stern, froling, tahvonen, Gerlagh, Tol, Kemfert, FEEM crowd, Cooper, Nel) or (2) new thermodynamically rooted Function (kümmel, lindenberger, ayres, warr).
+Mention energy in endogenous growth theory models (smulders, Mulder, vd Bergh) in SD modelling}
+\item{countries are going through different stages in their development, and the role of energy in such phases is now started to be explored (frohling, tahvonen, dalgaard)}
+\item{some have started to do work on empirical testing of PF with energy (Shen, walley, Serrenho,) and some have started doing comparative analysis of PF CD vs CES (miller)}
+\end{itemize}
+
+2. Find our own voice
+
+What is our own argument?
+
+We argue that macroeconomic modelling is real, but needs to be used in a very careful way.
+Throughout decades, there are Enough signals that macroeconomic growth theory has serious limitations.
+Not revisiting but refer to reviews (mishra, others).
+
+We argue that the basis on which a choice between ME and energy models and parameters are made, needs more detailed work, specifically detailed statistical testing.
+
+We also argue that different types of countries may need different PF parameters to be used in modelling approaches, leave possibility open for different explanations of growth in different countries and at different stages of their development.
+
+We present a comparative analysis between countries and of commonly used approaches in PF and LINEX, focussing on the insights one may drawn on a detailed comparative analysis, rather then run with one selected PF or LINEX.
+
+What is general tone of conversation? Controversial, established? Cross-disciplinary?
+
+We provide insights from cross-disciplinary work between statistics, engineering and environmental economics. This is not established work, and possibly controversial.
+
+We are taking issue with untested applications of PF, incl energy.
+Also taking issue with idea that importance of energy in growth also means it is necessary to include it as a factor in PF.
+Opens up a argument for the need of richer than just aggregate modelling approaches.
+
+Who makes arguments we want to amplify?
+
+Amplify need to account for energy in understanding growth in economies (Stern, Tol, Gerlagh)
+
+Amplify those who call for caution in applying aggregate PF and just adding energy to it.
+
+Amplify those who call for testing what value of adding energy really is.
+
+Amplify comparative analysis of role of energy between countries.
+
+What established sources we build on? Question? Contradict? In our writing.
+
+Build on articles using R to test econ growth PF, question what is reported when doing these tests.
+Contradict literature that calls for incl.
+energy in all PF, without testing whether that make sense at all.
+
+What methods apply to what we do?
+
+R software, makes detailed testing possible. R2 not a good measure, limited insights t and p values (confirm?)
+Grid search etc. (Matt, Randy to populate)
+
+Does analysis differ from others in the conversation?
+
+Yes, differs as follows:
+\begin{itemize}
+\item{if one do these test, report on all delta, sigma values as well as sse. Best fits not evidence of best values, must report uncertainties as well.}
+\item{What motivates nesting of CES? Not well behaved rho results, driving sigmas.
+Different type of CES with parsimonious factors, sigmas can be generated but not that easy (idea Randy)}
+\item{different factors in PF for countries in diff. development status}
+\end{itemize}
+
+What do we add to the conversation?
+\begin{itemize}
+\item{Richer insights from detailed testing across all functional relationships.}
+\item{Energy is not necessary to be included in all PF.}
+\item{What does that mean? Energy remains important for growth, 
+but its function in economies need deeper understanding}
+\item{Also signals that different types of countries likely to react differently to energy constraints. Interpret $\sigma$ here, substitution possibilities.}
+\end{itemize}
+
+More work?
+
+**** Notes on the introduction from Martin ****
+
 1. Set scene through energy economic modelling papers. 
@@
 4. Introduce coordinates of analysis.
+
+**** Orignial introduction that MKH wrote ****
 
@@
 Tables~\ref{tab:Covariance_US}--\ref{tab:Covariance_ZM}. 
-**** Discuss the covariances in more detail after we 
-finalize the covariances for U. ****
+**** Do we want to discuss the covariances? ****
 
@@
 
+CD assumes $\sigma_1 = 1$. CES doesn't assume a value for $\sigma_1$. 
+The $\sigma_1$ vs. $\delta_1$ graphs for CES without energy often have 
+two frequent values for $\sigma_1$.  One of those frequent values is
+nearer to $\sigma_1 = 1$. When CD and CES without energy do not agree on 
+share values (CD: $\alpha$ compared to $\beta$, CES: $\delta_1$) for the 
+base curve fit (red dot), they do agree for the data that clusters near 
+$\sigma_1 = 1$ for the CES fits.
+
 Country interpretation
@@
 
-% 
-% 
-% Discussion of results: How to get better consistent signals?
-% - Use CD as starting points and do CES convergence on that basis.
-% - Do scatterplots to get range of uncertainty inputs, then re-interpret. delta against sigma plots, as well as delta_1 and sigma_1 plots.
-% 
-% Thus, to do the fitting well we need to understand:
-% - nesting
-% - algorithm
-% - starting values
-% esp. for CES. 
-% (Maybe illustrate with one case study such as China what implications are).
-% 
-% How do we compare witj LINEX results?
-% CES is a broader specification of CD, LINEX is not.
+Discussion of results:
+
+How to get better consistent signals?
+
+\begin{itemize}
+\item{Use CD as starting points and do CES convergence on that basis.}
+\item{Do scatterplots to get range of uncertainty inputs, then re-interpret. delta against sigma plots, as well as $\delta_1$ and $\sigma_1$ plots.}
+\end{itemize}
+
+Thus, to do the fitting well we need to understand:
+\begin{itemize}
+\item{nesting}
+\item{algorithm}
+\item{starting values}
+\end{itemize}
+esp. for CES.
+
+(Maybe illustrate with one case study such as China what implications are).
+
+How do we compare with LINEX results?
+
+CES is a broader specification of CD, LINEX is not.
 In LINEX no delta's nor sigmas are generated.
 Only efficiency terms are generated in LINEX, thus in other words economic growth is only possible by increased efficiency.
-% The efficiency of using energy is driven by capital stock.
+The efficiency of using energy is driven by capital stock.
 The objective/growth engine is to increase capital at a rate that is faster then growth in labour and energy.
 Increasing labour relative to energy gives a muted benefit.
-% LINEX derived for Germany: only really applicable when energy and capital are complements.
-% 
-% Discussion in relation to other papers. 
-% Problems with other papers:
-% - If not giving you all parameters
-% - Not explain nesting approach 
-% - No CI on data
-% 
-% 
-% Economic interpretation (revisit after scatterplot information)
-% Developed economies: Capital and energy is complementary (US: labour and energy substitutable)
-% NICs: Capital and energy complementary, but labour and energy more substitutable
-% OPEC: Labour and energy complementary (mixed results on capital and energy)
-% LDCs: Labour and energy complementary, Capital and energy perfect substitutes.
-%
+LINEX derived for Germany: only really applicable when energy and capital are complements.
+
+Discussion in relation to other papers. 
+Problems with other papers:
+\begin{itemize}
+\item{If not giving you all parameters}
+\item{Not explain nesting approach}
+\item{No CI on data}
+\end{itemize}
+
+Economic interpretation (revisit after scatterplot information)
+Developed economies: Capital and energy is complementary (US: labour and energy substitutable)
+NICs: Capital and energy complementary, but labour and energy more substitutable
+OPEC: Labour and energy complementary (mixed results on capital and energy)
+LDCs: Labour and energy complementary, Capital and energy perfect substitutes.
 

### 2013-07-31 EconGrowth.Rnw

--- 2013-07-29 EconGrowth.Rnw
@@
 <<CES_sigma_1_delta_1_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
-cesResamplePlotSigma_1Delta_1(energyType=NA)
+cesResamplePlotSigma_1Delta_1(energyType=NA) + ylim(0, 2)
 @
@@
 @
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Interpretation of Results}
+\label{sec:Interpretation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+**** Need to complete this ****
 

### 2013-07-31 EconGrowth2.Rnw

@@
 \begin{itemize}
-\item{energy has become an important strategic issue, shocks in 1970s, spikes in energy prices generated renewed interest (IEA, IMF), supported by analysis on more structural depletion and technology race over time (Hamilton), cite reviews on energy and economics (Stern,...), cite articles that show close correlations energy use and economic growth (Cleveland etc)}
+
+\item{energy has become an important strategic issue for economic growth, shocks in 1970s, spikes in energy prices generated renewed interest (IEA, IMF), supported by analysis on more structural depletion and technology race over time (Hamilton), cite reviews on energy and economics (Stern,...), cite articles that show close correlations energy use and economic growth (Cleveland etc)}
+
 \item{economic theoretical frameworks adjusted: energy theory of value; Energy fundamental in biophysical economics (Cleveland, Hall), energy as one cost in production set; energy plays a role in production (extended Solow-Swan or CES (who introduced CES first) framework)}
-\item{how to account for energy on a macro economic level?
+
+\item{how to account for energy on a macro economic modeling?
 taken up in economic growth theory by (1) including energy in PF (stern, froling, tahvonen, Gerlagh, Tol, Kemfert, FEEM crowd, Cooper, Nel) or (2) new thermodynamically rooted Function (kümmel, lindenberger, ayres, warr).
 Mention energy in endogenous growth theory models (smulders, Mulder, vd Bergh) in SD modelling}
+
 \item{countries are going through different stages in their development, and the role of energy in such phases is now started to be explored (frohling, tahvonen, dalgaard)}
-\item{some have started to do work on empirical testing of PF with energy (Shen, walley, Serrenho,) and some have started doing comparative analysis of PF CD vs CES (miller)}
+
+\item{some have started to do work on empirical/statistical testing of PF with energy (Shen, walley, Serrenho,) and some have started doing comparative analysis of PF CD vs CES (miller)}
+
 \end{itemize}
@@
 
-We argue that macroeconomic modelling is real, but needs to be used in a very careful way.
-Throughout decades, there are Enough signals that macroeconomic growth theory has serious limitations.
+We argue that macroeconomic modelling is a reality (being used for policy analysis), 
+but needs to be used in a very careful way. 
+Throughout decades, there are enough signals that 
+macroeconomic growth theory has serious limitations. 
 Not revisiting but refer to reviews (mishra, others).
 
-We argue that the basis on which a choice between ME and energy models and parameters are made, needs more detailed work, specifically detailed statistical testing.
-
-We also argue that different types of countries may need different PF parameters to be used in modelling approaches, leave possibility open for different explanations of growth in different countries and at different stages of their development.
-
-We present a comparative analysis between countries and of commonly used approaches in PF and LINEX, focussing on the insights one may drawn on a detailed comparative analysis, rather then run with one selected PF or LINEX.
+We argue that the basis on which choice version of energy-augmented macroeconomic model 
+and parameters are made, needs more detailed work, 
+specifically detailed statistical testing and/or data analysis, including
+the quantification of energy ($q$, $x$, or $u$).
+
+We also argue that different types of countries may need different PF parameters 
+to be used in modelling approaches, 
+leave possibility open for different explanations of growth 
+in different countries and at different stages of their development.
+
+We present a comparative analysis among countries and of commonly used approaches in PF, 
+focussing on the insights one may drawn on a detailed comparative analysis, 
+rather then run with one selected PF.
 
 What is general tone of conversation? Controversial, established? Cross-disciplinary?
-
-We provide insights from cross-disciplinary work between statistics, engineering and environmental economics. This is not established work, and possibly controversial.
-
-We are taking issue with untested applications of PF, incl energy.
-Also taking issue with idea that importance of energy in growth also means it is necessary to include it as a factor in PF.
+We provide insights from cross-disciplinary work among statistics, engineering,
+and environmental economics. This is a new approach to issues that have been 
+discussed in recent years in the literature.
+
+We are taking issue with untested (statistically) applications of functional forms 
+of energy-augmented PF across different countries, with different energy quantifications. 
+Also taking issue with idea that importance of energy in growth 
+also means it is necessary to include it as a factor in PF (unnecessary vs. unimportant). 
 Opens up a argument for the need of richer than just aggregate modelling approaches.
@@
 
-Amplify need to account for energy in understanding growth in economies (Stern, Tol, Gerlagh)
-
-Amplify those who call for caution in applying aggregate PF and just adding energy to it.
-
-Amplify those who call for testing what value of adding energy really is.
-
-Amplify comparative analysis of role of energy between countries.
+Amplify voices who claim energy is important in understanding growth in economies (Stern, Tol, Gerlagh)
+
+Amplify those who call for caution in applying aggregate PF by just adding energy to it. (who?)
+
+Amplify those who call for testing (statistically) the benefit of energy-augmentation. (shen/whalley)
+
+Amplify comparative analysis of role of energy between countries indifferent stages of development. (who?)
 
@@
 
-Build on articles using R to test econ growth PF, question what is reported when doing these tests.
-Contradict literature that calls for incl.
-energy in all PF, without testing whether that make sense at all.
-
-What methods apply to what we do?
-
-R software, makes detailed testing possible. R2 not a good measure, limited insights t and p values (confirm?)
-Grid search etc. (Matt, Randy to populate)
+Build on articles using R to test econ growth PF, 
+question what is reported when doing these tests (shen/whalley and others who have used micEconCES). 
+Critique literature that calls for uncritical energy-augmentation of PF, 
+without testing whether that make sense at all.
 
@@
 \begin{itemize}
-\item{if one do these test, report on all delta, sigma values as well as sse. Best fits not evidence of best values, must report uncertainties as well.}
-\item{What motivates nesting of CES? Not well behaved rho results, driving sigmas.
-Different type of CES with parsimonious factors, sigmas can be generated but not that easy (idea Randy)}
-\item{different factors in PF for countries in diff. development status}
+\item{if one do these test, report on all $\delta$, $\sigma$, $\gamma$, and $\lambda$ 
+values as well as sse. 
+Good fits not evidence of best values, must report uncertainties as well.}
+\item{What motivates nesting of CES? Not well behaved $\rho$ results, driving $\sigma$s.
+Different type of CES with parsimonious factors, sigmas can be generated but not that easy (idea Randy).
+If you run all 3 nesting options, you can identify elasticities of all three factors in relation to each 
+other. Furthermore, you can determine which two factors are driving overall behavior in the aggregate function.}
+\item{necessary of different factors in PF to explain growth for countries in diff. development status}
 \end{itemize}
@@
 What do we add to the conversation?
+
 \begin{itemize}
-\item{Richer insights from detailed testing across all functional relationships.}
-\item{Energy is not necessary to be included in all PF.}
-\item{What does that mean? Energy remains important for growth, 
-but its function in economies need deeper understanding}
-\item{Also signals that different types of countries likely to react differently to energy constraints. Interpret $\sigma$ here, substitution possibilities.}
+
+\item{We are able to gain rich insights 
+on what really drives growth from detailed analysis (including uncertainties) 
+by testing all functional forms across many different 
+economy types.}
+
+\item{We were unable to gain new insights from the various energy quantifications that we tried.}
+
+\item{We find, surprisingly, that energy is not necessary 
+to be included alongside $k$ and $l$ in all PF. Models with energy and models without energy
+all perform well on an R$^2$ basis.}
+
+\item{We also find that
+
+(1) covariance of energy($e$) with both $k$ and $l$ is very high, with few exceptions (UK?).
+
+(2) with few exceptions, $\sigma_{(kl)e}$, $\sigma_{ke}$, and $\sigma_{le}$ 
+are all very low (indicating complementarity) (verify!!!!), and
+
+(3) energy-only models (SF$e$ and LINEX) achieve very good fits, just like CD$e$ and CES$e$.
+(should we make this point or not?)}
+
+\item{What does that mean? 
+It is a fallacy to think that saying energy is unnecessary 
+to include in an equation means energy is unimportant for economic growth. How to support this argument?
+
+If you find that energy is unnecessary to include alongside capital and labor 
+to explain growth in one economy at the macro, aggregated level, 
+you should not assume that energy is unimportant as a driver for economic growth for all economies.
+For developed economies, energy is captial intensive: you need to have large capital to make use 
+of energy. In developing economies, you don't need capital to make use of energy. 
+Rather, you need labor.
+
+We need to verify the above by comparison with our results.}
+
+\item{Also signals that different types of countries likely 
+to react differently to energy constraints. 
+Interpret $\sigma$ here, substitution possibilities.}
+
 \end{itemize}
@@
 
+\texttt{R} software, makes detailed testing possible. R$^2$ not a good measure, 
+limited insights t and p values, especially on PFs that have parameters with constraints
+
+We found that we are able to maintain good fits while respecting theoretical foundations
+of the models (i.e., respect parameter constraints). No need to relax parameter constraints
+and, thereby, contradict micro foundations.
+
+Grid search etc. (Matt, Randy to populate)
+
 This section should cover both technique and results. 

### 2013-08-01 EconGrowth.Rnw
Narrowed limits on CES resample plots with sigmas to the range (0, 2.5).

@@
 <<CES_sigma_1_delta_1_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
-cesResamplePlotSigma_1Delta_1(energyType=NA) + ylim(0, 2)
+cesResamplePlotSigma_1Delta_1(energyType=NA) + ylim(0, 2.5)
 @
@@
 
-Coefficients for each resampled CES model (with $q$)
+Coefficients for each resampled CES model (with $q$) for the ($kl$)$e$ nesting
 are shown in 
-Figures~\ref{fig:CESq_lambda_gamma_Cloud_Graph}--\ref{fig:CESq_sigma_delta_Cloud_Graph}.
-
-<<CESq_lambda_gamma_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$) resample model parameters $\\lambda$ and $\\gamma$.">>=
-cesResamplePlotLambdaGamma(energyType="Q")
-@
-
-<<CESq_sigma_1_delta_1_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
-cesResamplePlotSigma_1Delta_1(energyType="Q")
-@
-
-<<CESq_sigma_delta_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$) resample model parameters $\\sigma$ and $\\delta$.">>=
-cesResamplePlotSigmaDelta(energyType="Q")
-@
-
-Coefficients for each resampled CES model (with $x$)
+Figures~\ref{fig:CESq_lambda_gamma_Cloud_Graph_kle}--\ref{fig:CESq_sigma_delta_Cloud_Graph_kle}.
+
+<<CESq_lambda_gamma_Cloud_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($kl$)$e$ nesting) resample model parameters $\\lambda$ and $\\gamma$.">>=
+cesResamplePlotLambdaGamma(energyType="Q", nest="(kl)e")
+@
+
+<<CESq_sigma_1_delta_1_Cloud_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($kl$)$e$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
+cesResamplePlotSigma_1Delta_1(energyType="Q", nest="(kl)e") + ylim(0, 2.5)
+@
+
+<<CESq_sigma_delta_Cloud_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($kl$)$e$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
+cesResamplePlotSigmaDelta(energyType="Q", nest="(kl)e") + ylim(0, 2.5)
+@
+
+Coefficients for each resampled CES model (with $x$, ($kl$)$e$ nesting)
 are shown in 
-Figures~\ref{fig:CESx_lambda_gamma_Cloud_Graph}--\ref{fig:CESx_sigma_delta_Cloud_Graph}.
-
-<<CESx_lambda_gamma_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$) resample model parameters $\\lambda$ and $\\gamma$.">>=
-cesResamplePlotLambdaGamma(energyType="X")
-@
-
-<<CESx_sigma_1_delta_1_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
-cesResamplePlotSigma_1Delta_1(energyType="X")
-@
-
-<<CESx_sigma_delta_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$) resample model parameters $\\sigma$ and $\\delta$.">>=
-cesResamplePlotSigmaDelta(energyType="X")
+Figures~\ref{fig:CESx_lambda_gamma_Cloud_Graph_kle}--\ref{fig:CESx_sigma_delta_Cloud_Graph}.
+
+<<CESx_lambda_gamma_Cloud_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$, ($kl$)$e$ nesting) resample model parameters $\\lambda$ and $\\gamma$.">>=
+cesResamplePlotLambdaGamma(energyType="X", nest="(kl)e")
+@
+
+<<CESx_sigma_1_delta_1_Cloud_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$, ($kl$)$e$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
+cesResamplePlotSigma_1Delta_1(energyType="X", nest="(kl)e") + ylim(0, 2.5)
+@
+
+<<CESx_sigma_delta_Cloud_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$, ($kl$)$e$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
+cesResamplePlotSigmaDelta(energyType="X", nest="(kl)e") + ylim(0, 2.5)
 @
@@
 are shown in 
-Figures~\ref{fig:CESu_lambda_gamma_Cloud_Graph}--\ref{fig:CESu_sigma_delta_Cloud_Graph}.
-
-<<CESu_lambda_gamma_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$) resample model parameters $\\lambda$ and $\\gamma$.">>=
-cesResamplePlotLambdaGamma(energyType="U")
-@
-
-<<CESu_sigma_1_delta_1_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
-cesResamplePlotSigma_1Delta_1(energyType="U")
-@
-
-<<CESu_sigma_delta_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$) resample model parameters $\\sigma$ and $\\delta$.">>=
-cesResamplePlotSigmaDelta(energyType="U")
+Figures~\ref{fig:CESu_lambda_gamma_Cloud_Graph_kle}--\ref{fig:CESu_sigma_delta_Cloud_Graph_kle}.
+
+<<CESu_lambda_gamma_Cloud_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$, ($kl$)$e$ nesting) resample model parameters $\\lambda$ and $\\gamma$.">>=
+cesResamplePlotLambdaGamma(energyType="U", nest="(kl)e")
+@
+
+<<CESu_sigma_1_delta_1_Cloud_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$, ($kl$)$e$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
+cesResamplePlotSigma_1Delta_1(energyType="U", nest="(kl)e") + ylim(0, 2.5)
+@
+
+<<CESu_sigma_delta_Cloud_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$, ($kl$)$e$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
+cesResamplePlotSigmaDelta(energyType="U", nest="(kl)e") + ylim(0, 2.5)
+@
+
+Coefficients for each resampled CES model (with $q$) for the ($le$)$k$ nesting
+are shown in 
+Figures~\ref{fig:CESq_lambda_gamma_Cloud_Graph_lek}--\ref{fig:CESq_sigma_delta_Cloud_Graph_lek}.
+
+<<CESq_lambda_gamma_Cloud_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($le$)$k$ nesting) resample model parameters $\\lambda$ and $\\gamma$.">>=
+cesResamplePlotLambdaGamma(energyType="Q", nest="(le)k")
+@
+
+<<CESq_sigma_1_delta_1_Cloud_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($le$)$k$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
+cesResamplePlotSigma_1Delta_1(energyType="Q", nest="(le)k") + ylim(0, 2.5)
+@
+
+<<CESq_sigma_delta_Cloud_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($le$)$k$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
+cesResamplePlotSigmaDelta(energyType="Q", nest="(le)k") + ylim(0, 2.5)
+@
+
+Coefficients for each resampled CES model (with $x$ and ($le$)$k$ nesting)
+are shown in 
+Figures~\ref{fig:CESx_lambda_gamma_Cloud_Graph_lek}--\ref{fig:CESx_sigma_delta_Cloud_Graph_lek}.
+
+<<CESx_lambda_gamma_Cloud_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$, ($le$)$k$ nesting) resample model parameters $\\lambda$ and $\\gamma$.">>=
+cesResamplePlotLambdaGamma(energyType="X", nest="(le)k")
+@
+
+<<CESx_sigma_1_delta_1_Cloud_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$, ($le$)$k$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
+cesResamplePlotSigma_1Delta_1(energyType="X", nest="(le)k") + ylim(0, 2.5)
+@
+
+<<CESx_sigma_delta_Cloud_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$, ($le$)$k$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
+cesResamplePlotSigmaDelta(energyType="X", nest="(le)k") + ylim(0, 2.5)
+@
+
+Coefficients for each resampled CES model (with $u$ and ($le$)$k$ nesting)
+are shown in 
+Figures~\ref{fig:CESu_lambda_gamma_Cloud_Graph_lek}--\ref{fig:CESu_sigma_delta_Cloud_Graph_lek}.
+
+<<CESu_lambda_gamma_Cloud_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$, ($le$)$k$ nesting) resample model parameters $\\lambda$ and $\\gamma$.">>=
+cesResamplePlotLambdaGamma(energyType="U", nest="(le)k")
+@
+
+<<CESu_sigma_1_delta_1_Cloud_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$, ($le$)$k$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
+cesResamplePlotSigma_1Delta_1(energyType="U", nest="(le)k") + ylim(0, 2.5)
+@
+
+<<CESu_sigma_delta_Cloud_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$, ($le$)$k$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
+cesResamplePlotSigmaDelta(energyType="U", nest="(le)k") + ylim(0, 2.5)
+@
+
+Coefficients for each resampled CES model (with $q$) for the ($ek$)$l$ nesting
+are shown in 
+Figures~\ref{fig:CESq_lambda_gamma_Cloud_Graph_ekl}--\ref{fig:CESq_sigma_delta_Cloud_Graph_ekl}.
+
+<<CESq_lambda_gamma_Cloud_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($ek$)$l$ nesting) resample model parameters $\\lambda$ and $\\gamma$.">>=
+cesResamplePlotLambdaGamma(energyType="Q", nest="(ek)l")
+@
+
+<<CESq_sigma_1_delta_1_Cloud_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($ek$)$l$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
+cesResamplePlotSigma_1Delta_1(energyType="Q", nest="(ek)l") + ylim(0, 2.5)
+@
+
+<<CESq_sigma_delta_Cloud_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($ek$)$l$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
+cesResamplePlotSigmaDelta(energyType="Q", nest="(ek)l") + ylim(0, 2.5)
+@
+
+Coefficients for each resampled CES model (with $x$ and ($ek$)$l$ nesting)
+are shown in 
+Figures~\ref{fig:CESx_lambda_gamma_Cloud_Graph_ekl}--\ref{fig:CESx_sigma_delta_Cloud_Graph_ekl}.
+
+<<CESx_lambda_gamma_Cloud_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$, ($ek$)$l$ nesting) resample model parameters $\\lambda$ and $\\gamma$.">>=
+cesResamplePlotLambdaGamma(energyType="X", nest="(ek)l")
+@
+
+<<CESx_sigma_1_delta_1_Cloud_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$, ($ek$)$l$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
+cesResamplePlotSigma_1Delta_1(energyType="X", nest="(ek)l") + ylim(0, 2.5)
+@
+
+<<CESx_sigma_delta_Cloud_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$, ($ek$)$l$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
+cesResamplePlotSigmaDelta(energyType="X", nest="(ek)l") + ylim(0, 2.5)
+@
+
+Coefficients for each resampled CES model (with $u$ and ($ek$)$l$ nesting)
+are shown in 
+Figures~\ref{fig:CESu_lambda_gamma_Cloud_Graph_ekl}--\ref{fig:CESu_sigma_delta_Cloud_Graph_ekl}.
+
+<<CESu_lambda_gamma_Cloud_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$, ($ek$)$l$ nesting) resample model parameters $\\lambda$ and $\\gamma$.">>=
+cesResamplePlotLambdaGamma(energyType="U", nest="(ek)l")
+@
+
+<<CESu_sigma_1_delta_1_Cloud_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$, ($ek$)$l$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
+cesResamplePlotSigma_1Delta_1(energyType="U", nest="(ek)l") + ylim(0, 2.5)
+@
+
+<<CESu_sigma_delta_Cloud_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$, ($ek$)$l$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
+cesResamplePlotSigmaDelta(energyType="U", nest="(ek)l") + ylim(0, 2.5)
 @
@@
 Figure~\ref{fig:CESq_Params_Graph} shows values and 95\% confidence intervals 
-for the parameters for the CES model (with $q$).
-
-<<CESq_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with $q$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
+for the parameters for the CES model (with $q$, ($kl$)$e$ nesting).
+
+<<CESq_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with $q$, ($kl$)$e$ nesting) model parameters.
+Vertical bars indicate 95\\% confidence intervals.">>=
 createCESParamsGraph(energyType="Q")
@@
 
-<<CESx_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with $x$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
+<<CESx_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with $x$, ($kl$)$e$ nesting) model parameters.
+Vertical bars indicate 95\\% confidence intervals.">>=
 createCESParamsGraph(energyType="X")
@@
 
-<<CESu_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with $u$) model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
+<<CESu_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with $u$, ($kl$)$e$ nesting) model parameters.
+Vertical bars indicate 95\\% confidence intervals.">>=
 createCESParamsGraph(energyType="U")
@@
 
-<<CES_GDP_Lattice_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES results.">>=
+<<CES_GDP_Lattice_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES results (($kl$)$e$ nesting).">>=
 createCESLatticeGraph()
@@
 # linexResamplePlot(energyType="Q")
-linexResamplePlot(energyType="Q")
+linexResamplePlot(energyType="Q") + ylim(-20, 10)
 @
@@
 <<LINEXx_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX model (with $x$) resampling results.">>=
-linexResamplePlot(energyType="X")
+linexResamplePlot(energyType="X") + ylim(-20, 10)
 @

### 2013-08-01 EconGrowth2.Rnw
Added resample scatter plots for (le)k and (ek)l nestings for CES.

@@
 
-<<Historical_Lattice_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$).">>=
+<<Historical_Lattice_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$).", eval=FALSE>>=
 createHistoricalLatticeGraph()
@@
 
-CES:
-
-($kl$)$e$: energy is unnec ($\delta$ is 1); also ($el$)$k$ energy is unnec. 
-($\delta_1$ is 0);
+CES with $q$:
+
+($kl$): $\delta_1 = 0.3, \sigma_1 = 0.8$. $k$ is less necessary. Complements, but close to substitutes.
+signal of substitutability in the spread.
+
+($kl$)$e$: energy is unnec ($\delta = 1$). $\delta_1 = 0.45$: $k$ and $l$ are about equally necessary.
+$\sigma_1 = 0.8$: $k$ and $l$ are slight complements. Spread on $0.25 < \sigma_1 < \infty$, signalling 
+possibilities of substitution.
+
+($el$)$k$: energy is unnec. ($\delta_1$ is 0);
 
@@
 
-$\sigma$:
-capital and energy are complements
-labour and energy are subsitutable
+CES with $u$:
+
+($kl$)$e$: $\delta = 1$, signalling $e$ unnecessary. $\sigma = 0.8$, indicating clost to substitutability,
+but still complementary. 
+$\delta_1 = 0.25$, with large spread. not strong for $k$.
+$\sigma_1 \rightarrow \infty$, but with large spread from 0.2 upward. Signals complementarity
+between $k$ and $l$.
 
@@
 
-CES:
-
-($kl$)$e$: energy is unnec ($\delta =1$);
+CES with $q$:
+
+($kl$): $\delta_1 = 0.7, \sigma_1 = 0.35$. $kl$ complementary, $k$ is more important, because $\delta_1 > 0.5$. Large spread on $\delta_1$. Complementary signal is consistent, however.
+
+($kl$)$e$: energy is unnec ($\delta = 1$). $\delta_1 = 0.25$, $k$ is less necessary. 
+$\sigma_1 \rightarrow \infty$, giving strong $kl$ substitutability signal.
 
@@
 
-$\sigma$: energy is not substitutable with capital or labour, totally complementary
+CES with $u$:
+
+($kl$)$e$: $\delta = 1$, $u$ is unnecessary. $\sigma = 0.8$, approache complementarity between $kl$ and $e$.
+$\delta_1 = 0.1$. $\sigma_1 \rightarrow \infty$, indicating substitutability between $k$ and $l$.
 
@@
 
-CES:
-
-($kl$)$e$; ($le$)$k$; ($ek$)$l$: no indications, all are important.
+CES with $q$:
+
+($kl$): $\delta_1 = 0.7, \sigma_1 = 0.25$. Very little scatter. Both are well-known. 
+$l$ is close to unnecessary. $k$ and $l$ are complements.
+
+($kl$)$e$: no indications, all are important. $\delta = 0.6$, both $kl$ and $e$ are necessary.
+$0.5 < \delta < 1$.
+$\sigma=0.1$ signalling complementarity betwen $kl$ and $e$.
+$\delta_1 = 0.8$ signalling $l$ is almost unnecessary. $\sigma_1 = 0.1$, signalling complementarity 
+between $k$ and $l$.
+
+($le$)$k$: no indications, all are important.
+
+($ek$)$l$: no indications, all are important.
 
@@
 
-$\sigma$: labour and energy are complements, capital and energy complements
+CES with $u$:
+
+($kl$)$e$: $\delta = 0.6, \sigma = 0.4$. Complementarity between $kl$ and $e$.
+$\delta_1 = 1$, indicating $l$ unnecessary. $\sigma_1 = 0.1$, indicating complementarity
+between $k$ and $l$. Need only one of $k$ or $l$ in your equation, but they are
+complemetary! You need one to have the other.
 
@@
 
-CES:
-
-($kl$)$e$: energy is unnec. ($\delta = 1$);
+CES with $q$:
+
+($kl$): $\delta_1 = 0.3$, so $k$ is getting close to unnecessary. $\sigma_1 = 1.25$.
+$k$ and $l$ are substitutes. Large spread in $\delta_1$ from 0.1 to 1.0. Large spread in
+$\sigma_1$, but most points have $\sigma_1 > 1$.
+
+($kl$)$e$: $\delta = 0.8$. however, strong signal at $0.8 < \delta < 1$, 
+signalling that energy is less necessary. $0.5 < \delta < 1$. $\sigma = 0.5$, 
+signalling complementarity between $kl$ and $e$. 
+$\delta_1 = 1$, signalling that $l$ is unnecessary. $\sigma_1 = 0.1$, signalling
+that $k$ and $l$ are complementary. Both $\delta_1$ and $\sigma_1$ have large spreads, 
+so our confidence in these results is low.
 
@@
 Strong signal that energy is unnec, but the labour and capital signals are conflicting
-
-$\sigma$: capital and energy is complementary, but labour and energy more substitutable
 
@@
 
-CES:
-
-($kl$)$e$: labour is unnec. ($\delta_1 = 1$);
+CES with $q$:
+
+($kl$): $\delta_1 = 0.35, \sigma_1 = 0.8$. $k$ is relatively less necessary. $k$ and $l$ 
+are complements but relatively close to being substitutes. Spread is tight between 
+$0.25 < \delta_1 < 0.5$ and $\sigma_1$ is consistently complementary 
+between $0.1 < \sigma_1 < 0.8$.
+
+($kl$)$e$: labour is unnec. ($\delta_1 = 1$). $\delta = 0.25$, signalling complemtarity 
+between $kl$ and $e$, but large spread from 0 to 1. $\sigma$ and $\sigma_1$ are both 0, 
+indicating perfect complements betwen $kl$ and $e$ and between $k$ and $l$.
 
@@
 Consistent signal that labour is unnec.
-
-$\sigma$: capital and energy is complementary, labour and energy is substitutable
 
@@
 
-CES: no indications, but weak signal that labour is unnec in ($ek$)$l$ ($\delta = 0.93$)
+CES with $q$:
+
+($kl$): $\delta_1 = 0.85$. $l$ is unnecessary. $\sigma_1 = 0.1$ indicating strong complementarity between 
+$k$ and $l$. Spread of $0.15 < \delta_1 < 1$. $0 < \sigma_1 < 0.8$, signalling complementarity.
+
+($kl$)$e$: $\delta = 0.6$, $e$ is less necessary (weak signal). Big spread on $\delta$ between 0 and 0.8.
+$\sigma = 0.1$ indicating complementarity between $kl$ and $e$. $\delta_1 = 0.8$ 
+(with large spread between 0.3 and 1), labor is less necessary.
+$\sigma_1 = 0.1$: very complementary between $k$ and $l$.
+
+($le$)$k$:
+
+($ek$)$l$: weak signal that labour is unnec ($\delta = 0.93$)
 
 Almost consistent signal that no indocations.
-
-$\sigma$: labour and energy are complements, capital and energy are substitutes
 
@@
 
-CES:
-
-($kl$)$e$: energy is unnec ($\delta=1$);
+CES with $q$:
+
+($kl$): $\delta_1 = 0.3$. Spread $0 < \delta_1 < 0.7$. $0 < \sigma_1 < 0.8$. $\sigma_1 = 0$. 
+Strong complementarity. $k$ is less necessary compared to $l$.
+
+($kl$)$e$: energy is unnec ($\delta=1$). $\sigma = 0.75$ indicating complementarity between $kl$ and $e$, approaching substitutibility.
+$\delta_1 = 0.3, \sigma_1 = 0$ indicating strong perfect complementarity between $k$ and $l$.
 
@@
 ($ek$)$l$: labour is unnec. ($\delta=1$)
-
-$\sigma$: labour and energy still complements, 
-but not as strong capital and energy complements
 
@@
 
-CES:
-
-($kl$)$e$: labour is unnec ($\delta_1=0.97$);
+CES with $q$:
+
+($kl$): $\delta_1 = 0.8$ $0.3 < \delta_1 < 1$ signalling labor is less necessary.
+$\sigma_1 = 0.1$ $0 < \sigma_1 < 0.8$, signalling complementary $k$ and $l$.
+
+($kl$)$e$: labour is unnec ($\delta_1=0.97$). $\delta = 0.45$, so $kl$ and $e$ both necessary, but 
+$\sigma \rightarrow \infty$, so $kl$ and $e$ has perfect substitutibility.
+$\sigma_1 = 0.1$, so $k$ and $l$ are perfect complements. Spread on $\delta$ is large (0.2 to 1).
+So, we are unsure about the value of $\delta$.
 
@@
 
-$\sigma$: labour and energy complements, capital and energy perfect substitutes
-
 %++++++++++++++++++++++++++++++
@@
 
-CES:
-
-($kl$)$e$: labour is unnec. ($\delta_1=1$); labour is unnec
+CES with $q$:
+
+($kl$): $\delta_1 = 1$: $l$ is unnecessary. $0.5 < \delta_1 < 1$. $\sigma_1 = 0.8$ without any 
+noticeable spread indicating complemetary.
+
+($kl$)$e$: labour is unnec. ($\delta_1=1$). $\delta = 0.6$, $kl$ and $e$ are both necessary. 
+$\sigma \rightarrow \infty$, signalling substitutability between $kl$ and $e$. $\sigma_1 = 0.8$ with very
+large spread between 0 and 2. Approaching substitutability between $k$ and $l$ and perfect substitutibility
+between $kl$ and $e$. Very little certainty here.
 
@@
 Consistent signal that labour is unnec.
-
-$\sigma$: labour and energy complements, not as strong. 
-Capital and energy perfect substitutes.
 

### 2013-08-01 EconGrowth2.Rnw
Added additional descriptions for parameter estimation. Added additional nestings for CES model.

@@
 
+% Add an argument if you want a label. Example: "\label{eq:CES}"
+\newcommand{\ceskl}[1]{\begin{equation} #1
+  y = \gamma \: A \: \left[\delta_1 k^{-\rho_1} 
+      + (1-\delta_1)l^{-\rho_1} \right]^{-1/\rho_1}; 
+      A = \mathrm{e}^{\lambda (t-t_0)}
+\end{equation}}
+
+\newcommand{\ceskle}[1]{\begin{equation} #1
+  y = \gamma \: A \: \left\{\delta \left[\delta_1 k^{-\rho_1} 
+      + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1} 
+      + (1-\delta) e^{-\rho} \right\}^{-1/\rho}; 
+      A = \mathrm{e}^{\lambda (t-t_0)}
+\end{equation}
+}
+
+\newcommand{\ceslek}[1]{\begin{equation} #1
+  y = \gamma \: A \: \left\{\delta \left[\delta_1 l^{-\rho_1} 
+      + (1-\delta_1) e^{-\rho_1} \right]^{\rho/\rho_1} 
+      + (1-\delta) k^{-\rho} \right\}^{-1/\rho}; 
+      A = \mathrm{e}^{\lambda (t-t_0)}
+\end{equation}
+}
+
+\newcommand{\cesekl}[1]{\begin{equation} #1
+  y = \gamma \: A \: \left\{\delta \left[\delta_1 e^{-\rho_1} 
+      + (1-\delta_1) k^{-\rho_1} \right]^{\rho/\rho_1} 
+      + (1-\delta) l^{-\rho} \right\}^{-1/\rho}; 
+      A = \mathrm{e}^{\lambda (t-t_0)}
+\end{equation}
+}
+
 \begin{frontmatter}
@@
 CD with e: 25\% energy, rest c,importance of l drops to 0
-CES no e: 20\% c (sigma), 80\% l, but large range
+CES no e: 20\% c ($\sigma$), 80\% l, but large range
 CES with e: fig 35 e may be NB
@@
 
-Similar to Equation~\ref{eq:CD}, the energy-augmented Cobb-Douglas 
-production function is
+The capital-labor Cobb-Douglas production function is shown in Equation~\ref{eq:CD}.
+Similarly, the energy-augmented Cobb-Douglasproduction function is
 
@@
 
-\begin{equation} \label{eq:CES}
-  y = \gamma \: A \: \left[\delta_1 k^{-\rho_1} 
-      + (1-\delta_1)l^{-\rho_1} \right]^{-1/\rho_1}; 
-      A = \mathrm{e}^{\lambda (t-t_0)}
-\end{equation}
-
-\begin{equation} \label{eq:CESe}
-  y = \gamma \: A \: \left\{\delta \left[\delta_1 k^{-\rho_1} 
-      + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1} 
-      + (1-\delta) e^{-\rho} \right\}^{-1/\rho}; 
-      A = \mathrm{e}^{\lambda (t-t_0)}
-\end{equation}
+\ceskl{\label{eq:CES}}
+
+\ceskle{\label{eq:CESkle}}
 
@@
 capital stock ($k$) and labor ($l$) factors of production. 
-Equation~\ref{eq:CESe} augments Equation~\ref{eq:CES} with energy 
+Equation~\ref{eq:CESkle} augments Equation~\ref{eq:CES} with energy 
 using a ($kl$)($e$) nesting structure, as is typical in the literature. 
-Equation~\ref{eq:CES} is a degenerate form of Equation~\ref{eq:CESe} 
+Equation~\ref{eq:CES} is a degenerate form of Equation~\ref{eq:CESkle} 
 where $\delta \rightarrow 1$ and $\rho \rightarrow -1$.
@@
 $\rho_1 \in (-1,0) \cup (0,\infty)$, and
-$\rho \in (-1,0) \cup (0,\infty)$. **** Describe here how 
+$\rho \in (-1,0) \cup (0,\infty)$.
+
+Two other nestings of the factors of production ($k$, $l$, and $e$)
+are possible with the CES model.
+
+\ceslek{\label{eq:CESlek}}
+
+\cesekl{\label{eq:CESekl}}
+
+\noindent Note that the $\rho$ ($\sigma$) and $\delta$ parameters have different
+meanings that depend upon the nesting of the factors of production.
+**** Do we want to define different variables that indicate meaning, 
+such as $\sigma_{kl}, \sigma_{(kl)e}, \delta_{(ek)l}$, and the like? If so, we'll 
+need to translate from $\rho$ and $\sigma$ in \texttt{cesEst} to the correct
+variable names in the paper. ****
+
+**** Describe here how 
 we implemented the constraints. ****
@@
 In contrast to both the Cobb-Douglas model (Equations~\ref{eq:CD} and 
-\ref{eq:CDe}) and the CES model (Equations~\ref{eq:CES} and 
+\ref{eq:CDe}) and the CES model (Equations~\ref{eq:CESkle} and 
 \ref{eq:CESe}), the LINEX model (Equation~\ref{eq:LINEX}) accounts 
@@
 
-<<Historical_Lattice_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$).", eval=FALSE>>=
+<<Historical_Lattice_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$).">>=
 createHistoricalLatticeGraph()
@@
 
-\texttt{R} software, makes detailed testing possible. R$^2$ not a good measure, 
-limited insights t and p values, especially on PFs that have parameters with constraints
+Each of the economic growth models discussed in 
+Section~\ref{sec:Prod_Func_Forms} has parameters which must be estimated (fitted)
+for each economy (see Section~\ref{sec:Economy_Types}) and 
+each energy quantification (see Section~\ref{sec:Quantification_of_Energy}) 
+via least-squares methods. We used \texttt{R} \citep{R}, specifically the \texttt{nls} and 
+\texttt{cesEst} \citep{Henningsen:2011td} functions for the parameter estimation process.
+
+The following subsections discuss 
+parameter estimation methods and results.
+
+%++++++++++++++++++++++++++++++
+\subsection{Resampling}
+\label{sec:Resampling}
+%++++++++++++++++++++++++++++++
+
+**** To be completed by Randy Prium ****
+
+Discuss resampling theory.
+
+Discuss our resampling approach.
+
+Be sure to include references on resampling. 
+Resampling will be new territory for the readers of \emph{Energy Economics}
+
+%++++++++++++++++++++++++++++++
+\subsection{Cobb-Douglas Models}
+\label{sec:CD_Parameter_Estimation}
+%++++++++++++++++++++++++++++++
+
+The Cobb-Douglas model without energy is given by 
+Equation~\ref{eq:CD}. The Cobb-Douglas (without energy) production function was
+reparameterized as
+
+\begin{equation} \label{eq:CD_reparam}
+  y = A k^{\alpha} l^{1-\alpha}; A = \mathrm{e}^{\lambda (t-t_0)}
+\end{equation}
+
+\noindent to ensure $\alpha + \beta = 1$ for constant returns to scale. 
+$\lambda$ and $\alpha$ were estimated by the 
+\texttt{R} \citep{R} function \texttt{nls}. 
+If the estimated value for $\alpha$ was found outside the interval $[0,1]$, 
+we set $\alpha$ to its boundary value and re-estimated $\lambda$. 
+The value of $\beta$ was found with $\beta = 1 - \alpha$.
+
+**** CD without energy results here. Scatter plots? CIs? 
+Partial residual plots? TBD which to include. ****
+
+To estimate the parameters $\lambda$, $\alpha$, $\beta$, and $\gamma$ 
+in the energy-augmented Cobb-Douglas model, Equation~\ref{eq:CDe} 
+was reparameterized as
+
+\begin{equation} \label{eq:CDe_AB_reparam}
+  y = A k^{\min(a,b)} l^{|b-a|} e^{1 - \max(a,b)}; A = \mathrm{e}^{\lambda (t-t_0)}
+\end{equation}
+
+\noindent with 
+$\alpha = \min(a,b)$, 
+$\beta = |b-a|$, and 
+$\gamma = 1 - \max(a,b)$.
+The reparameterization ensures that $\alpha + \beta + \gamma = 1$,
+thereby providing constant returns to scale.
+The \texttt{R} \citep{R} function \texttt{nls} was used to estimate 
+values of $\lambda$, $a$, and $b$.
+If the fitted value for $a$ ($b$) fell outside $[0,1]$, it was 
+set equal to its boundary value and $\lambda$ and $b$ ($a$) 
+were re-estimated.
+
+The \texttt{nls} parameter estimation algorithm can encounter convergence difficulty 
+when the optimal value for the parameter represented by the absolute value function 
+(in Equation~\ref{eq:CDe_AB_reparam}, $\beta$) 
+lies near a boundary. If the absolute value exponent caused non-convergence of the 
+\texttt{nls} function, second and, if necessary, third reparameterizations 
+were attempted:
+
+\begin{equation} \label{eq:CDe_CD_reparam}
+  y = A k^{1 - \max(c,d)} l^{\min(c,d)} e^{|d-c|}; A = \mathrm{e}^{\lambda (t-t_0)}
+\end{equation}
+
+\begin{equation} \label{eq:CDe_FG_reparam}
+  y = A k^{|g-f|} l^{1 - \max(f,g)} e^{\min(f,g)}; A = \mathrm{e}^{\lambda (t-t_0)}
+\end{equation}
+
+\noindent If none of the three reparameterizations converged, 
+the parameterization with the smallest sum of square errors ($SSE$)
+was used. \ref{sec:Convergence_Resample_Models} shows the 
+fraction of unconverged models for each model type. 
+The above approach resulted in very few unconverged
+Cobb-Douglas resample models, even with \Sexpr{numResamples()} resamples.
+
+**** Include CD$e$ graphs here. Ternary plots? CIs? TBD which to include. ****
+
+Figure~\ref{fig:CD_GDP_Lattice_Graph} compares predictions 
+from the Cobb-Douglas models 
+(without energy, with $e=q$, with $e=x$, and with $e=u$) to historical data.
+
+<<CD_GDP_Lattice_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas fitted models.">>=
+createCDLatticeGraph()
+@
+
+%++++++++++++++++++++++++++++++
+\subsection{Parameter Estimation Summary}
+\label{sec:Parameter_Estimation_Summary}
+%++++++++++++++++++++++++++++++
+
+**** Include a table here of important values. 
+Include a table of convergence? (In appendix?)
+Martin to suggest the form of this table after working 
+on the interpretation for a while. ****
+
+Grid search etc. (Matt, Randy to populate)
+
+This section should cover both technique and results. 
+Organize along coordinates of analysis.
+
+1. Discuss parameter estimation for each model here.
+
+CES Model: It is possible for L-BFGS-B to report convergence and PORT to report non-convergence 
+but nevertheless reach a better solution (smaller sse).
+
+2. Show scatter plot results.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Discussion of Results}
+\label{sec:Discussion_of_Results}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Drive towards new insights from our stats tested comparative approach.
+
+**** Notes for interpretation of results ****
+
+R$^2$ not a good measure. 
+Limited insights are obtained from $t$ and $p$ values, 
+especially on PFs that have parameters with constraints (CD, CES).
 
@@
 and, thereby, contradict micro foundations.
-
-Grid search etc. (Matt, Randy to populate)
-
-This section should cover both technique and results. 
-Organize along coordinates of analysis.
-
-1. Discuss parameter estimation for each model here.
-
-CES Model: It is possible for L-BFGS-B to report convergence and PORT to report non-convergence 
-but nevertheless reach a better solution (smaller sse).
-
-2. Show scatter plot results.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion of Results}
-\label{sec:Discussion_of_Results}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Drive towards new insights from our stats tested comparative approach..
-
-**** Notes for interpretation of results ****
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Convergence of Resample Models}
+\label{sec:Convergence_Resample_Models}
+\setcounter{table}{0} % Restarts table number counter at 0 in this section.
+\setcounter{figure}{0} % Restarts figure number counter at 0 in this section.
+\setcounter{equation}{0} % Restarts equation counter to 0 in this section.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The following table shows the fraction of resample models 
+that did not achieve convergence when estimating model parameters.
+
+<<Unconverged_Frac_Table, results='asis'>>=
+printFracUnconvergedXtable()
+@
 

### 2013-08-02 EconGrowth2.Rnw
Added subsection on CES parameter estimation.

@@
 %++++++++++++++++++++++++++++++
+\subsection{CES Models}
+\label{sec:CES_Parameter_Estimation}
+%++++++++++++++++++++++++++++++
+
+The CES model without and with energy is given by 
+Equations~\ref{eq:CES}--\ref{eq:CESekl}. 
+The \texttt{R} \citep{R} package \texttt{micEconCES} 
+\citep{Henningsen:2011td} was used to estimate parameters 
+$\gamma$, $\lambda$, $\delta_1$, $\rho_1$, $\delta$, and $\rho$. 
+**** Adjust these parameter names if we decide to 
+change them. **** The \texttt{cesEst} function of \texttt{micEconCES} provides 
+several algorithm options for parameter estimation.
+The default algorithm (Levenberg-Marquardt) does not respect
+parameter constraints (see Section~\ref{sec:CES}) and, 
+in our testing, nearly always violated them, often returning
+negative values for elasticity of substitution ($\sigma$) parameters.
+
+Two algorithms available in \texttt{cesEst} 
+(\texttt{PORT} and \texttt{L-BFGS-B}) respect coefficient constraints. 
+Our CES parameter estimation algorithm tries both
+with default starting values and selects the
+result with lowest $sse$, regardless
+of convergence status. If one algorithm
+fails during the fitting process 
+(due to division by zero or another numerical error), 
+we use coefficients from the algorithm that didn't.
+In event that both algorithms fail, 
+we skip that resampled data point.
+
+\citet{Henningsen:2011td}, 
+in their detailed analysis of \citet{Kemfert:1998vd}, found that
+
+\begin{quote}
+\ldots the Levenberg-Marquardt and the PORT algorithms 
+are---at least in this study---most likely to find the 
+coefficients that give the best fit to the model, 
+where the PORT algorithm can be used to restrict the estimates 
+to the economically meaningful region.
+\end{quote}
+
+In our testing, we found that to be mostly true. 
+\texttt{PORT} nearly always provided lower
+$sse$ than \texttt{L-BFGS-B}, despite the fact that 
+\texttt{L-BFGS-B} often reports convergence
+and \texttt{PORT} does not for the same economic data.
+
+**** Include CES graphs here. Need to cover
+all options: without energy and the three nesting
+options. CIs? TBD which to include. ****
+
+Figure~\ref{fig:CES_GDP_Lattice_Graph_kle} compares CES model predictions 
+to historical data for the $(kl)e$ nesting.
+
+<<CES_GDP_Lattice_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES fitted models with ($kl$)$e$ nesting.">>=
+createCESLatticeGraph()
+@
+
+**** Include other nestings here? ****
+
+%++++++++++++++++++++++++++++++
 \subsection{Parameter Estimation Summary}

### 2013-08-02 EconGrowth2.Rnw
Fixed two table references.

@@
 In contrast to both the Cobb-Douglas model (Equations~\ref{eq:CD} and 
-\ref{eq:CDe}) and the CES model (Equations~\ref{eq:CESkle} and 
-\ref{eq:CESe}), the LINEX model (Equation~\ref{eq:LINEX}) accounts 
+\ref{eq:CDe}) and the CES model (Equations~\ref{eq:CES}--\ref{eq:CESekl}), 
+the LINEX model (Equation~\ref{eq:LINEX}) accounts 
 for efficiencies among capital, labor, and energy directly and, 
@@
 in the Cobb-Douglas and CES production functions 
-(Equations~\ref{eq:CD}--\ref{eq:CESe}) may be a proxy for 
+(Equations~\ref{eq:CD}--\ref{eq:CESekl}) may be a proxy for 
 increasing energy efficiency in the U.S. economy.

### 2013-08-02 EconGrowth2.Rnw
Added section on LINEX parameter estimation.

@@
 each energy quantification (see Section~\ref{sec:Quantification_of_Energy}) 
-via least-squares methods. We used \texttt{R} \citep{R}, specifically the \texttt{nls} and 
-\texttt{cesEst} \citep{Henningsen:2011td} functions for the parameter estimation process.
-
-The following subsections discuss 
+via least-squares methods. We used \texttt{R} \citep{R} functions
+\texttt{nls} and \texttt{cesEst} \citep{Henningsen:2011td} 
+for that purpose. The following subsections discuss 
 parameter estimation methods and results.
@@
 \noindent If none of the three reparameterizations converged, 
-the parameterization with the smallest sum of square errors ($SSE$)
+the parameterization with the smallest sum of square errors ($sse$)
 was used. \ref{sec:Convergence_Resample_Models} shows the 
@@
 \begin{quote}
-\ldots the Levenberg-Marquardt and the PORT algorithms 
+\ldots the Levenberg-Marquardt and the \texttt{PORT} algorithms 
 are---at least in this study---most likely to find the 
@@
 \texttt{L-BFGS-B} often reports convergence
-and \texttt{PORT} does not for the same economic data.
+and \texttt{PORT} does not for the same data
+(i.e., for the same $y$, $k$, $l$, and $e$ data).
 
@@
 **** Include other nestings here? ****
+
+%++++++++++++++++++++++++++++++
+\subsection{LINEX Models}
+\label{sec:LINEX_Parameter_Estimation}
+%++++++++++++++++++++++++++++++
+
+The LINEX model is given in Equation~\ref{eq:LINEX}. 
+If the fitting algorithm drives $a_0 \rightarrow 0$, 
+any changes to $c_t$ have no effect on $sse$, 
+leading the fitting algorithm to report non-convergence. 
+To avoid this problem, we transformed the LINEX model into
+
+\begin{equation} \label{eq:LINEX_transformed}
+  y = Ae; 
+  A = \mathrm{e}^{\left[2 a_0 \left(1 - \frac{1}{\rho_k} \right) 
+    + a_1 \left(\vphantom{\frac{1}{\rho_k}}\rho_l - 1 \right)\right]},
+\end{equation}
+
+\noindent where $a_1 \equiv a_0 c_t$. 
+We used the \texttt{nls} function in \texttt{R}
+\citep{R} to estimate least-squares values for $a_0$ and $a_1$ in 
+Equation~\ref{eq:LINEX_transformed}. We recovered
+a value for $c_t$ with $c_t = a_1 / a_0$. The reparameterization
+of Equation~\ref{eq:LINEX_transformed} reduced the number of 
+unconverged resample fits to nearly zero.
+
+**** Include LINEX scatter graphs here. Cover all 
+quantifications of energy? CIs? TBD which to include. ****
+
+Figure~\ref{fig:LINEX_GDP_Lattice_Graph} compares LINEX model predictions to historical data.
+
+<<LINEX_GDP_Lattice_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX results.">>=
+createLINEXLatticeGraph()
+@
 
@@
 on the interpretation for a while. ****
-
-Grid search etc. (Matt, Randy to populate)
-
-This section should cover both technique and results. 
-Organize along coordinates of analysis.
-
-1. Discuss parameter estimation for each model here.
-
-CES Model: It is possible for L-BFGS-B to report convergence and PORT to report non-convergence 
-but nevertheless reach a better solution (smaller sse).
-
-2. Show scatter plot results.
 

### 2013-08-02 EconGrowth2.Rnw
Edited the interpretation text from Martin.
Added a description of the resampling process.

@@
 
-**** To be completed by Randy Prium ****
-
-Discuss resampling theory.
-
-Discuss our resampling approach.
-
-Be sure to include references on resampling. 
-Resampling will be new territory for the readers of \emph{Energy Economics}
+Resampling is a statistical technique for estimating the 
+precision of coefficient estimates. We implemented
+residual resampling in our parameter estimation processes.
+
+When resampling, the modeler assumes that the residuals ($r_t$) between 
+observed data (in our case historical GDP values, $y_{act,t}$) and
+model predictions (in our case, $y_{pred,t}$) at
+time $t$ are representative 
+of the uncertainty and random scatter in the observed historical data.
+
+\begin{equation} \label{eq:residual}
+  r_t = y_{pred,t} - y_{act,t}
+\end{equation}
+
+Under that assumption, it would not be surprising if the residual from 
+any one year had been observed on a different year. 
+By applying randomly selected residuals (with randomly selected signs)
+to model predictions at each year of the GDP time series, we create a resampled
+GDP time series ($y_{resample,t}$) that can be re-fitted using the techniques
+described below.
+
+\begin{equation} \label{eq:resample_y}
+  y_{resample,t} = y_{pred,t} + \mathrm{rand}(-1, 1) \cdot \mathrm{abs}(\mathrm{rand}(r_t))
+\end{equation}
+
+We repeated the resampling process \Sexpr{numResamples()} times for each
+combination of growth model, energy quantification, and country.
+
+The coefficients from the fit to the resampled time series
+(the ``resample coefficients'') will be different from the coefficients 
+obtained from the fit to historical data (the ``base coefficients'').
+Large residuals in the base fit
+are expected to produce large variation in resample coefficients, 
+indicating less certainty in the knowledge
+of those coefficients. 
+Similarly, small base fit residuals are expected to produce small
+variation in resample coefficients, indicating better knowledge
+of the model coefficients.
+
+It is important to note that large residuals can arise from 
+(a) poor quality historical time series data ($y_{act}$) or 
+(b) a mathematical model that does not describe the underlying phenomena well.
+In either case, we would not want to claim precise knowledge of the 
+fitted coefficients for a model. The resampling technique that we employed
+provides looser coefficient distributions when either of the above
+is true. After discussing the fitting technique for each 
+growth model, we show scatter plots of fitted coefficients
+to provide visual indication of the uncertainty 
+of the coefficients for each model.
+
+**** Randy Pruim review the above text and supply some text and references. ****
 
@@
 
-($kl$): $\delta_1 = 0.3, \sigma_1 = 0.8$. $k$ is less necessary. Complements, but close to substitutes.
+($kl$): $\delta_1 = 0.3, \sigma_1 = 0.8$. $k$ is less necessary. 
+Complements, but close to substitutes.
 signal of substitutability in the spread.
 
-($kl$)$e$: energy is unnec ($\delta = 1$). $\delta_1 = 0.45$: $k$ and $l$ are about equally necessary.
-$\sigma_1 = 0.8$: $k$ and $l$ are slight complements. Spread on $0.25 < \sigma_1 < \infty$, signalling 
+($kl$)$e$: energy is unnec ($\delta = 1$). 
+$\delta_1 = 0.45$: $k$ and $l$ are about equally necessary.
+$\sigma_1 = 0.8$: $k$ and $l$ are slight complements. 
+Spread on $0.25 < \sigma_1 < \infty$, signalling 
 possibilities of substitution.
@@
 
-($kl$)$e$: $\delta = 1$, signalling $e$ unnecessary. $\sigma = 0.8$, indicating clost to substitutability,
+($kl$)$e$: $\delta = 1$, signalling $e$ unnecessary. 
+$\sigma = 0.8$, indicating clost to substitutability,
 but still complementary. 
 $\delta_1 = 0.25$, with large spread. not strong for $k$.
-$\sigma_1 \rightarrow \infty$, but with large spread from 0.2 upward. Signals complementarity
-between $k$ and $l$.
+$\sigma_1 \rightarrow \infty$, but with large spread from 0.2 upward. 
+Signals complementarity between $k$ and $l$.
 
@@
 
-($kl$): $\delta_1 = 0.7, \sigma_1 = 0.35$. $kl$ complementary, $k$ is more important, because $\delta_1 > 0.5$. Large spread on $\delta_1$. Complementary signal is consistent, however.
-
-($kl$)$e$: energy is unnec ($\delta = 1$). $\delta_1 = 0.25$, $k$ is less necessary. 
+($kl$): $\delta_1 = 0.7, \sigma_1 = 0.35$. 
+$kl$ complementary, $k$ is more important, because $\delta_1 > 0.5$. 
+Large spread on $\delta_1$. 
+Complementary signal is consistent, however.
+
+($kl$)$e$: energy is unnec ($\delta = 1$). 
+$\delta_1 = 0.25$, $k$ is less necessary. 
 $\sigma_1 \rightarrow \infty$, giving strong $kl$ substitutability signal.
@@
 
-($kl$)$e$: $\delta = 1$, $u$ is unnecessary. $\sigma = 0.8$, approache complementarity between $kl$ and $e$.
-$\delta_1 = 0.1$. $\sigma_1 \rightarrow \infty$, indicating substitutability between $k$ and $l$.
+($kl$)$e$: $\delta = 1$, $u$ is unnecessary. 
+$\sigma = 0.8$, approache complementarity between $kl$ and $e$.
+$\delta_1 = 0.1$. 
+$\sigma_1 \rightarrow \infty$, indicating substitutability between $k$ and $l$.
 
@@
 $\sigma=0.1$ signalling complementarity betwen $kl$ and $e$.
-$\delta_1 = 0.8$ signalling $l$ is almost unnecessary. $\sigma_1 = 0.1$, signalling complementarity 
+$\delta_1 = 0.8$ signalling $l$ is almost unnecessary. 
+$\sigma_1 = 0.1$, signalling complementarity 
 between $k$ and $l$.
@@
 
-($kl$): $\delta_1 = 0.85$. $l$ is unnecessary. $\sigma_1 = 0.1$ indicating strong complementarity between 
-$k$ and $l$. Spread of $0.15 < \delta_1 < 1$. $0 < \sigma_1 < 0.8$, signalling complementarity.
-
-($kl$)$e$: $\delta = 0.6$, $e$ is less necessary (weak signal). Big spread on $\delta$ between 0 and 0.8.
+($kl$): $\delta_1 = 0.85$. $l$ is unnecessary. 
+$\sigma_1 = 0.1$ indicating strong complementarity between 
+$k$ and $l$. Spread of $0.15 < \delta_1 < 1$. 
+$0 < \sigma_1 < 0.8$, signalling complementarity.
+
+($kl$)$e$: $\delta = 0.6$, $e$ is less necessary (weak signal). 
+Big spread on $\delta$ between 0 and 0.8.
 $\sigma = 0.1$ indicating complementarity between $kl$ and $e$. $\delta_1 = 0.8$ 
@@
 
-($kl$)$e$: energy is unnec ($\delta=1$). $\sigma = 0.75$ indicating complementarity between $kl$ and $e$, approaching substitutibility.
+($kl$)$e$: energy is unnec ($\delta=1$). 
+$\sigma = 0.75$ indicating complementarity between $kl$ and $e$, approaching substitutibility.
 $\delta_1 = 0.3, \sigma_1 = 0$ indicating strong perfect complementarity between $k$ and $l$.
@@
 
-($kl$)$e$: labour is unnec ($\delta_1=0.97$). $\delta = 0.45$, so $kl$ and $e$ both necessary, but 
+($kl$)$e$: labour is unnec ($\delta_1=0.97$). 
+$\delta = 0.45$, so $kl$ and $e$ both necessary, but 
 $\sigma \rightarrow \infty$, so $kl$ and $e$ has perfect substitutibility.
-$\sigma_1 = 0.1$, so $k$ and $l$ are perfect complements. Spread on $\delta$ is large (0.2 to 1).
+$\sigma_1 = 0.1$, so $k$ and $l$ are perfect complements. 
+Spread on $\delta$ is large (0.2 to 1).
 So, we are unsure about the value of $\delta$.
@@
 
-($kl$): $\delta_1 = 1$: $l$ is unnecessary. $0.5 < \delta_1 < 1$. $\sigma_1 = 0.8$ without any 
+($kl$): $\delta_1 = 1$: $l$ is unnecessary. 
+$0.5 < \delta_1 < 1$. $\sigma_1 = 0.8$ without any 
 noticeable spread indicating complemetary.
 
-($kl$)$e$: labour is unnec. ($\delta_1=1$). $\delta = 0.6$, $kl$ and $e$ are both necessary. 
-$\sigma \rightarrow \infty$, signalling substitutability between $kl$ and $e$. $\sigma_1 = 0.8$ with very
-large spread between 0 and 2. Approaching substitutability between $k$ and $l$ and perfect substitutibility
+($kl$)$e$: labour is unnec. ($\delta_1=1$). 
+$\delta = 0.6$, $kl$ and $e$ are both necessary. 
+$\sigma \rightarrow \infty$, signalling substitutability between $kl$ and $e$. 
+$\sigma_1 = 0.8$ with very large spread between 0 and 2. 
+Approaching substitutability between $k$ and $l$ and perfect substitutibility
 between $kl$ and $e$. Very little certainty here.
@@
 \item{Use CD as starting points and do CES convergence on that basis.}
-\item{Do scatterplots to get range of uncertainty inputs, then re-interpret. delta against sigma plots, as well as $\delta_1$ and $\sigma_1$ plots.}
+\item{Do scatterplots to get range of uncertainty inputs, then re-interpret. 
+$\delta$ against $\sigma$ plots, as well as $\delta_1$ and $\sigma_1$ plots.}
 \end{itemize}
@@
 CES is a broader specification of CD, LINEX is not. 
-In LINEX no delta's nor sigmas are generated.
-Only efficiency terms are generated in LINEX, thus in other words economic growth is only possible by increased efficiency.
+In LINEX neither $\delta$s nor $\sigma$s are generated. 
+Only efficiency terms are generated in LINEX, 
+thus in other words economic growth is only possible by increased efficiency. 
 The efficiency of using energy is driven by capital stock. 
-The objective/growth engine is to increase capital at a rate that is faster then growth in labour and energy.
+The objective/growth engine is to increase capital 
+at a rate that is faster then growth in labour and energy.  
 Increasing labour relative to energy gives a muted benefit. 

### 2013-08-05 EconGrowth2.Rnw
Edits to the paper.

@@
 Section~\ref{sec:Prod_Func_Forms} has parameters which must be estimated (fitted)
-for each economy (see Section~\ref{sec:Economy_Types}) and 
-each energy quantification (see Section~\ref{sec:Quantification_of_Energy}) 
+for each energy quantification (see Section~\ref{sec:Quantification_of_Energy}) 
+and each economy (see Section~\ref{sec:Economy_Types})
 via least-squares methods. We used \texttt{R} \citep{R} functions
@@
 
-When resampling, the modeler assumes that the residuals ($r_t$) between 
+When employing resampling techniques, 
+the modeler assumes that the residuals ($r_t$) between 
 observed data (in our case historical GDP values, $y_{act,t}$) and
@@
 time $t$ are representative 
-of the uncertainty and random scatter in the observed historical data.
+of the uncertainty of and random scatter in the observed historical data.
 
 \begin{equation} \label{eq:residual}
-  r_t = y_{pred,t} - y_{act,t}
+  r_t = y_{act,t} - y_{pred,t}
 \end{equation}
@@
 to model predictions at each year of the GDP time series, we create a resampled
-GDP time series ($y_{resample,t}$) that can be re-fitted using the techniques
+GDP time series ($y_{resample,t}$) that can be fitted using the techniques
 described below.
@@
 obtained from the fit to historical data (the ``base coefficients'').
-Large residuals in the base fit
-are expected to produce large variation in resample coefficients, 
-indicating less certainty in the knowledge
+Large residuals in the fit to historical data (the ``base fit'')
+are expected to produce large variation in resample coefficient values
+(when the resampling is repeated \Sexpr{numResamples()} times),
+indicating less certainty in the value
 of those coefficients. 
 Similarly, small base fit residuals are expected to produce small
-variation in resample coefficients, indicating better knowledge
+variation in resample coefficient values, indicating more-precise knowledge
 of the model coefficients.
@@
 In either case, we would not want to claim precise knowledge of the 
-fitted coefficients for a model. The resampling technique that we employed
+fitted coefficients for an economic growth model. 
+The resampling technique that we employed
 provides looser coefficient distributions when either of the above
 is true. After discussing the fitting technique for each 
-growth model, we show scatter plots of fitted coefficients
-to provide visual indication of the uncertainty 
+growth model below, we show scatter plots of fitted coefficients,
+thereby providing visual indication of the uncertainty 
 of the coefficients for each model.

### 2013-08-05 EconGrowth2.Rnw
Added details about how many unconverged LINEX models are present to the text using \Sexpr.

@@
 a value for $c_t$ with $c_t = a_1 / a_0$. The reparameterization
-of Equation~\ref{eq:LINEX_transformed} reduced the number of 
-unconverged resample fits to nearly zero.
+shown in Equation~\ref{eq:LINEX_transformed} reduced the number of 
+unconverged resample fits to nearly zero: 
+The largest fraction of unconverged resample fits is found 
+for Zambia (ZM) with thermal energy ($q$), where
+\Sexpr{fracUnconvergedResampleFits(modelType="linex", countryAbbrev="ZM", energyType="Q")*100}\%
+of the resample fits did not converge. 
+(See Table~\ref{tab:frac_unconverged_models}.)
 

### 2013-08-22 EconGrowth2.Rnw
Added notes about non-convergence.
Insert TEST text
Testing
Intro and Refs
Added Introduction, incl Lit Review as well as References at end.

@@
 
+Introduction
+
+[1. Listen to what others say
+Identify key issues and important voices]
+
+The available of adequate energy at affordable costs has become an important strategic issue in recent years.
+Despite a slowdown in economic growth worldwide, longer-term trends in energy use remain strongly upwards, as the dynamics of energy markets are increasingly determined by emerging markets, notably China, India and the Middle East (IEA, 2012).
+A large body of literature points towards the fact that economic growth and energy consumption are closely correlated and for a diverse set of countries such as the United States (Stern, 2000; Cleveland et al 1984), India (Paul & Bhattacharya 2004), China (Wang et al 2011), South Africa (Menyah & Wolde-Rufael, 2010; Odhiambo, 2009) and sixteen Asian countries (Lee & Chang, 2008) to name a few, although the causal relationship between energy consumption and economic growth is still controversial (Chen et al 2012; Ozturk, 2009).
+Ozturk (2009:347) in a survey of the literature on the topic, concluded that there is “… no consensus neither on the existence nor on the direction of causality between these variables in the literature”, but do point out that “…causality is running from electricity consumption to economic growth in the most of these studies [surveyed]”.
+
+Those that have accepted that energy use is closely correlated to economic performance in one form or another, have expressed further concerns on the negative effects of rising energy prices and energy depletion effects on current and future economic growth.
+Benes et al (2012), incorporating both views on geological physical constraints and technological solutions to oil production, suggest a near doubling of the real price of over the next decade.
+Kumhof & Muir (2012) point out that for larger oil supply shocks, assuming production functions where oil plays a prominent role as well as reduced possibilities for substitution away from oil, significant impacts on GDP growth could occur.
+Nel and Van Zyl (2010) argue for the “…vital importance of energy security…” on the basis of a model based on an explicit energy-based formulation of economic growth.
+Hamilton (2012:30) argues that “[c]oping with a final peak in world oil production…have much in common with previous historical episodes that resulted from temporary geopolitical conflict, being associated with significant declines in employment and output.
+If the future decades look like the last 5 years, we are in for a rough time.”
+
+The current trends in energy production and consumption and the possible dire impacts on the world economy as argued by above-mentioned scholars have further raised the question whether and how to including appropriate energy indicators in economic growth modeling.
+Stern (2011) provided a useful overview on how energy is dealt with in mainstream economic, resource economic and ecological economic models of growth.
+Stern points out that energy is usually not included as a factor of production in mainstream economic growth models, that energy is seen as the central driver of growth in ecological economic (incl.
+biophysical economic) models, and that energy is included in resource economic models, but remain isolated within this sub-discipline (2011:26).
+To break through this theoretical impasse, Stern proposed a synthesized CES production function where the constraints or abundance of energy determines whether to include energy explicitly as a factor of production or not.
+On the basis of this model, Stern (2011:45) points out that energy availability plays “…a key role in enabling growth” even given the evidence of decreasing energy used per unit of output.
+He concludes that, based on theory and time-series results the inclusion of energy in the production function approach to economic growth is warranted, and that further clarification is needed on the role of energy in economic growth.
+The inclusion of energy as a factor of production in CES and Cobb-Douglas production functions, is generally accepted by most resource and energy economists and economic growth modelers (see Smulders & De Nooij 2003; Van der Zwaan et al 2002; Kemfert, 1998).
+Researchers interested in explaining long-term economic growth and possible constraints on growth have started to include energy as an explicit production factor (Fröling, 2011; Tahvonen & Salo, 2001).
+One alternative approach, attempting to be “…more consistent with physical laws…” (Ayres, 2001), and classified by Stern as an ecological economic model of growth is the LINEX production function approach, combining capital (non ICT and ICT), labour and useful work, but with the difference that technological change only affects the amount of useful work done per joule of exergy (Ayres & Warr 2005).
+
+The unsatisfactorily situation is that the choice of a production function and the parameters used to populate these functions in economic growth modeling will affect the results in a significant way.
+This leaves far too much scope to misuse model specifications and the selective choice of parameters to support certain theories rather then empirically test these theories.
+For example, Lecca et al (2010) pointed out that the modellers’ choice on the structure of a production function reflects different views on the elasticity between different inputs and “…the point at which energy enters the [nested CES] production function has a significant impact on CGE [computable general equilibrium] model results.” [brackets added].
+Duffy and Papageorgiou (2000) rejected the Cobb-Douglas specification altogether finding that capital and labour are more substitutable in richer countries and less substitutable in poorer countries then what a Cobb-Douglas specification would imply.
+Miller (2008), however, points to the “…reasonably accurate long-term economic forecasts”, achieved with the use of Cobb-Douglas production functions in economic models.
+Shen and Whalley (2013) is one recent example where empirical analysis on the estimated substitution elasticities is actually done before choosing any particular nested CES production function structure and as a result propose a different structure to the Chinese economy to the one usually used in macro-economic growth modeling.
+Both the choice of a production function structure and the value of the parameters chosen drive model results and empirical and statistical testing of such approaches appear more and more prudent.
+
+[2. Find our own voice
+What is our own argument?]
+
+We agree with those who have a serious concern with the reliability of the results from economic growth models which are often used to inform policy choices (Lecca et al 2010) and would like to add that the inclusion of energy would only further complicate issues.
+We do except, however, that macroeconomic policymaking is needed and are increasingly informed by integrated energy-economic models, in a world where energy constraints are possible (Beckman et al 2011; Benes et al, 2010; Nel and van Zyl, 2010).
+We support the call from Shen and Walley (2013) that the basis on which a modelling choice is made on the structure of the production function and the parameters used to populate this function, needs empirical testing, and we would like to add; including for the quantification of energy in various measures ($q$, $x$, or $u$).
+Building on the argument of Stern (2011) that energy may or may not be required in production functions depending on its abundance or scarcity, we will further argue in this paper that different types of countries may need different factors of production to explain their respective growth paths.
+This further leaves the possibility open for different explanations of growth in different countries and at different stages of their development, a central point by contributions made in long-wave economic growth modeling (Fröling, 2011; Jones, 2001; Galor and Weil, 2000).
+To gain insights from different countries across different stages of development, we present a comparative analysis among the World Bank’s main categories of countries, namely Developed Countries (DCs), Newly Industrialized Countries (NICs), OPEC countries, and Least Developed Countries (LDCs).
+
+Approach
+Build on articles using R to test econ growth PF, 
+question what is reported when doing these tests (shen/whalley and others who have used micEconCES).
+
+Discussion and Insights
+
+Does analysis differ from others in the conversation?
+Yes, differs as follows:
+\begin{itemize}
+\item{if one do these test, report on all $\delta$, $\sigma$, $\gamma$, and $\lambda$ 
+values as well as sse. 
+Good fits not evidence of best values, must report uncertainties as well.}
+\item{What motivates nesting of CES? Not well behaved $\rho$ results, driving $\sigma$s.
+Different type of CES with parsimonious factors, sigmas can be generated but not that easy (idea Randy).
+If you run all 3 nesting options, you can identify elasticities of all three factors in relation to each 
+other. Furthermore, you can determine which two factors are driving overall behavior in the aggregate function.}
+\item{necessary of different factors in PF to explain growth for countries in diff. development status}
+\end{itemize}
+
+What do we add to the conversation?
+
+\begin{itemize}
+
+\item{We are able to gain rich insights 
+on what really drives growth from detailed analysis (including uncertainties) 
+by testing all functional forms across many different 
+economy types.}
+
+\item{We were unable to gain new insights from the various energy quantifications that we tried.}
+
+\item{We find, surprisingly, that energy is not necessary 
+to be included alongside $k$ and $l$ in all PF. Models with energy and models without energy
+all perform well on an R$^2$ basis.}
+
+\item{We also find that
+
+(1) covariance of energy($e$) with both $k$ and $l$ is very high, with few exceptions (UK?).
+
+(2) with few exceptions, $\sigma_{(kl)e}$, $\sigma_{ke}$, and $\sigma_{le}$ 
+are all very low (indicating complementarity) (verify!!!!), and
+
+(3) energy-only models (SF$e$ and LINEX) achieve very good fits, just like CD$e$ and CES$e$.
+(should we make this point or not?)}
+
+\item{What does that mean? 
+It is a fallacy to think that saying energy is unnecessary 
+to include in an equation means energy is unimportant for economic growth. How to support this argument?
+
+If you find that energy is unnecessary to include alongside capital and labor 
+to explain growth in one economy at the macro, aggregated level, 
+you should not assume that energy is unimportant as a driver for economic growth for all economies.
+For developed economies, energy is captial intensive: you need to have large capital to make use 
+of energy. In developing economies, you don't need capital to make use of energy. 
+Rather, you need labor.
+
+We need to verify the above by comparison with our results.}
+
+\item{Also signals that different types of countries likely 
+to react differently to energy constraints. 
+Interpret $\sigma$ here, substitution possibilities.}
+
+\end{itemize}
+
+More work?
+
 Big picture
+[insert test test]
+
 Why do we do this? Want to link energy and economics on national level 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Thoughts on literature review and contextualisation of our work
-
-Imagine ourselves walking into a conversation on the role of energy in the economy.
-
-1. Listen to what others say
-
-Identify key issues and important voices
-
-\begin{itemize}
-
-\item{energy has become an important strategic issue for economic growth, shocks in 1970s, spikes in energy prices generated renewed interest (IEA, IMF), supported by analysis on more structural depletion and technology race over time (Hamilton), cite reviews on energy and economics (Stern,...), cite articles that show close correlations energy use and economic growth (Cleveland etc)}
-
-\item{economic theoretical frameworks adjusted: energy theory of value; Energy fundamental in biophysical economics (Cleveland, Hall), energy as one cost in production set; energy plays a role in production (extended Solow-Swan or CES (who introduced CES first) framework)}
-
-\item{how to account for energy on a macro economic modeling?
-taken up in economic growth theory by (1) including energy in PF (stern, froling, tahvonen, Gerlagh, Tol, Kemfert, FEEM crowd, Cooper, Nel) or (2) new thermodynamically rooted Function (kümmel, lindenberger, ayres, warr).
-Mention energy in endogenous growth theory models (smulders, Mulder, vd Bergh) in SD modelling}
-
-\item{countries are going through different stages in their development, and the role of energy in such phases is now started to be explored (frohling, tahvonen, dalgaard)}
-
-\item{some have started to do work on empirical/statistical testing of PF with energy (Shen, walley, Serrenho,) and some have started doing comparative analysis of PF CD vs CES (miller)}
-
-\end{itemize}
-
-2. Find our own voice
-
-What is our own argument?
-
-We argue that macroeconomic modelling is a reality (being used for policy analysis), 
-but needs to be used in a very careful way. 
-Throughout decades, there are enough signals that 
-macroeconomic growth theory has serious limitations. 
-Not revisiting but refer to reviews (mishra, others).
-
-We argue that the basis on which choice version of energy-augmented macroeconomic model 
-and parameters are made, needs more detailed work, 
-specifically detailed statistical testing and/or data analysis, including
-the quantification of energy ($q$, $x$, or $u$).
-
-We also argue that different types of countries may need different PF parameters 
-to be used in modelling approaches, 
-leave possibility open for different explanations of growth 
-in different countries and at different stages of their development.
-
-We present a comparative analysis among countries and of commonly used approaches in PF, 
-focussing on the insights one may drawn on a detailed comparative analysis, 
-rather then run with one selected PF.
-
-What is general tone of conversation? Controversial, established? Cross-disciplinary?
-We provide insights from cross-disciplinary work among statistics, engineering,
-and environmental economics. This is a new approach to issues that have been 
-discussed in recent years in the literature.
-
-We are taking issue with untested (statistically) applications of functional forms 
-of energy-augmented PF across different countries, with different energy quantifications. 
-Also taking issue with idea that importance of energy in growth 
-also means it is necessary to include it as a factor in PF (unnecessary vs. unimportant). 
-Opens up a argument for the need of richer than just aggregate modelling approaches.
-
-Who makes arguments we want to amplify?
-
-Amplify voices who claim energy is important in understanding growth in economies (Stern, Tol, Gerlagh)
-
-Amplify those who call for caution in applying aggregate PF by just adding energy to it. (who?)
-
-Amplify those who call for testing (statistically) the benefit of energy-augmentation. (shen/whalley)
-
-Amplify comparative analysis of role of energy between countries indifferent stages of development. (who?)
-
-What established sources we build on? Question? Contradict? In our writing.
-
-Build on articles using R to test econ growth PF, 
-question what is reported when doing these tests (shen/whalley and others who have used micEconCES). 
-Critique literature that calls for uncritical energy-augmentation of PF, 
-without testing whether that make sense at all.
-
-Does analysis differ from others in the conversation?
-
-Yes, differs as follows:
-\begin{itemize}
-\item{if one do these test, report on all $\delta$, $\sigma$, $\gamma$, and $\lambda$ 
-values as well as sse. 
-Good fits not evidence of best values, must report uncertainties as well.}
-\item{What motivates nesting of CES? Not well behaved $\rho$ results, driving $\sigma$s.
-Different type of CES with parsimonious factors, sigmas can be generated but not that easy (idea Randy).
-If you run all 3 nesting options, you can identify elasticities of all three factors in relation to each 
-other. Furthermore, you can determine which two factors are driving overall behavior in the aggregate function.}
-\item{necessary of different factors in PF to explain growth for countries in diff. development status}
-\end{itemize}
-
-What do we add to the conversation?
-
-\begin{itemize}
-
-\item{We are able to gain rich insights 
-on what really drives growth from detailed analysis (including uncertainties) 
-by testing all functional forms across many different 
-economy types.}
-
-\item{We were unable to gain new insights from the various energy quantifications that we tried.}
-
-\item{We find, surprisingly, that energy is not necessary 
-to be included alongside $k$ and $l$ in all PF. Models with energy and models without energy
-all perform well on an R$^2$ basis.}
-
-\item{We also find that
-
-(1) covariance of energy($e$) with both $k$ and $l$ is very high, with few exceptions (UK?).
-
-(2) with few exceptions, $\sigma_{(kl)e}$, $\sigma_{ke}$, and $\sigma_{le}$ 
-are all very low (indicating complementarity) (verify!!!!), and
-
-(3) energy-only models (SF$e$ and LINEX) achieve very good fits, just like CD$e$ and CES$e$.
-(should we make this point or not?)}
-
-\item{What does that mean? 
-It is a fallacy to think that saying energy is unnecessary 
-to include in an equation means energy is unimportant for economic growth. How to support this argument?
-
-If you find that energy is unnecessary to include alongside capital and labor 
-to explain growth in one economy at the macro, aggregated level, 
-you should not assume that energy is unimportant as a driver for economic growth for all economies.
-For developed economies, energy is captial intensive: you need to have large capital to make use 
-of energy. In developing economies, you don't need capital to make use of energy. 
-Rather, you need labor.
-
-We need to verify the above by comparison with our results.}
-
-\item{Also signals that different types of countries likely 
-to react differently to energy constraints. 
-Interpret $\sigma$ here, substitution possibilities.}
-
-\end{itemize}
-
-More work?
 
@@
 
+**** Do we want to report on the fraction of non-convergence
+reported? Maybe we should write a function that 
+searches all the countries to find which 
+country reports least convergence for a given model. ****
+
 **** Include CES graphs here. Need to cover
@@
 @
+
+[manually added]
+References
+
+Benes, J., Chauvet, M., Kamenik, O., Kumhof, M., Laxton, D., Mursula, S., & Selody, J. (2012). The Future of Oil: Geology versus Technology. IMF Working Papers, I12/109, 1–33.
+
+Chen, P-Y., Chen, S-T., Chen, C-C. 2012. Energy consumption and economic growth – New evidence from meta analysis. Energy Policy, 44: 245-255. http://dx.doi.org/10.1016/j.enpol.2012.01.048
+
+Cleveland, C., Costanza, R., Hall, C., & Kaufmann, R. (1984). Energy and the US economy: a biophysical perspective. INTERNATIONAL LIBRARY OF CRITICAL WRITINGS IN ECONOMICS, 75, 295–302.
+
+Duffy, J., & Papageorgiou, C. (2000). A Cross-Country Empirical Investigation of the Aggregate Production Function Specification. Journal of Economic Growth, 5(1), 87–120. doi:10.1023/A:1009830421147
+
+Fröling, M. (2011). Energy use, population and growth, 1800–1970. Journal of Population Economics, 24(3), 1133–1163.
+
+Galor, O., & Weil, D. N. (2000). Population,Technology, and Growth: From Malthusian Stagnation to the Demographic Transition and Beyond. American Economic Review, 90(4), 806–828.
+
+Hamilton, J. (2012). Oil Prices, exhaustible resources, and economic growth.  Handbook of Energy and Climate Change
+
+International Energy Agency (IEA), 2012. World Energy Outlook 2012. IEA: Paris, France.
+
+Jones, C. (2001). Was an industrial revolution inevitable? Economic growth over the very long run. Advances in Macroeconomics, 1(2), 1–43.
+
+Kemfert, C. (1998). Estimated substitution elasticities of a nested CES production function approach for Germany. Energy Economics, 20(3), 249–264.
+
+Kumhof, M., & Muir, D. (2012). Oil and the World Economy: Some Possible Futures. IMF Working Papers, 12/256(October, 1), 1–31.
+
+Lee, C-C. & Chang, C-P. Energy consumption and economic growth in Asian economies: A more comprehensive analysis using panel data. Resource and Energy Economics, 30(1): 50-65.
+
+Lecca, P., Swales, K., & Turner, K. (2011). An investigation of issues relating to where energy should enter the production function. Economic Modelling, 28(6), 2832–2841.
 

### 2013-08-28 EconGrowth2.Rnw
Edited Martin's initial GitHub contribution for LaTeX formatting and references.

--- 2013-08-05 EconGrowth2.Rnw
@@
 
+Introduction
+
+[1. Listen to what others say
+Identify key issues and important voices]
+
+The availability of adequate energy at affordable costs 
+has become an important strategic issue in recent years.
+Despite a slowdown in economic growth worldwide, 
+longer-term trends in energy use remain strongly upwards, 
+as the dynamics of energy markets are increasingly determined by emerging markets, 
+notably China, India, and the Middle East \citep{IEA:2012ty}. 
+A large body of literature points towards the fact that 
+economic growth and energy consumption are closely correlated 
+and for a diverse set of countries such as 
+the United States \citep{Stern2000, Cleveland:1984p5055}, 
+India (Paul and Bhattacharya 2004), 
+China (Wang et al 2011), 
+South Africa (Menyah and Wolde-Rufael, 2010; Odhiambo, 2009) and 
+sixteen Asian countries (Lee and Chang, 2008) 
+to name a few, 
+although the causal relationship between energy consumption 
+and economic growth is still controversial \citep{Chen2012, Ozturk:2010kb}. 
+\citet[p. 347]{Ozturk:2010kb} in a survey of the literature on the topic, 
+concluded that there is 
+``\dots no consensus neither on the existence nor on the direction of 
+causality between these variables in the literature,'' 
+but does point out that ``\dots causality is running from 
+electricity consumption to economic growth 
+in the most of these studies [surveyed].''
+
+Those that have accepted that energy use is closely correlated with
+economic performance in one form or another
+have expressed further concerns on the negative effects of 
+rising energy prices and fossil fuel depletion 
+on current and future economic growth.
+\citet{Benes:2012tm}, incorporating views on both
+geological physical constraints and 
+technological solutions to oil production, 
+suggest a near doubling of the real price of over the next decade.  
+\citet{Kumhof:2012ua} point out that 
+significant impacts on GDP growth could occur
+for larger oil supply shocks, 
+assuming production functions where oil plays a prominent role 
+and reduced possibilities for substitution away from oil.  
+\citet{Nel:2010fv} argue for the 
+``\dots vital importance of energy security \dots'' 
+on the basis of a model based on an explicit 
+energy-based formulation of economic growth.  
+\citet{Hamilton:2013vc} argues that 
+``[c]oping with a final peak in world oil production \dots 
+[will] have much in common with previous historical episodes that resulted from 
+temporary geopolitical conflict, 
+being associated with significant declines in employment and output. 
+If the future decades look like the last 5 years, we are in for a rough time.''
+
+The current trends in energy production and consumption and 
+the possible dire impacts on the world economy 
+as argued by above-mentioned scholars 
+have further raised the question 
+whether and how to include appropriate energy indicators 
+in economic growth modeling.  
+\citet[p. 26]{Stern:2011bq} provides an overview of how energy is included 
+in mainstream economic, resource economic, and ecological economic models of growth.  
+\citeauthor{Stern:2011bq} points out that energy is usually \emph{not included} 
+as a factor of production in mainstream economic growth models, 
+that energy is seen as the \emph{central driver of growth} 
+in ecological economic (incl. biophysical economic) models, 
+and that energy \emph{is included} in resource economic models, 
+but \emph{remains isolated} within this sub-discipline.  
+To break through this theoretical impasse, 
+Stern proposes a synthesized CES production function 
+where the constraints or abundance of energy 
+determines whether to include energy explicitly 
+as a factor of production.  
+On the basis of this model, 
+\citet[p. 45]{Stern:2011bq} points out that 
+energy availability plays
+``\dots a key role in enabling growth''
+despite the evidence of decreasing energy used per unit of output.  
+He concludes, based on theory and time-series results, 
+that including energy in the production function is warranted, 
+and that further clarification is needed 
+on the role of energy in economic growth.  
+The inclusion of energy as a factor of production 
+in CES and Cobb-Douglas production functions 
+is generally accepted by most 
+resource and energy economists and economic growth modelers 
+\citep{Smulders:2003wc, VanderZwaan2002, Kemfert:1998vd}.
+Researchers interested in explaining long-term economic growth 
+and possible constraints on growth 
+have started to include energy as an explicit factor of production
+\citep{Froling:2009vo, Tahvonen:2001tz}.  
+One alternative approach, attempting to be 
+``\dots more consistent with physical laws \dots'' \citep{Ayres:2001tx}
+and classified by \citeauthor{Stern:2011bq} as an ecological economic model of growth, 
+is the LINEX production function, 
+combining capital (non-ICT and ICT), 
+labour, and useful work. In the LINEX model, 
+technological change affects only 
+the amount of useful work done per joule of exergy \citep{Ayres:2005kn}.
+
+Unsatisfactorily, the choice of a production function 
+and the parameters used to populate these functions 
+affects results significantly.
+This situation leaves far too much latitude 
+for misuse of model specifications 
+and selection of parameters 
+to support certain theories (rather than empirically testing the theories
+and parameters \emph{before} they are employed).  
+For example, \citet{Lecca:2011kr} pointed out that 
+the modellers' choice for the structure of a production function 
+reflects his or her assumptions about
+the elasticities among inputs, and 
+``\dots the point at which energy enters the [nested CES] production function 
+has a significant impact on CGE [computable general equilibrium] model results.''
+\citet{Duffy:2000ty} rejected the Cobb-Douglas production function altogether, 
+finding that capital and labour are more substitutable 
+in richer countries and less substitutable in poorer countries 
+than what a Cobb-Douglas specification would imply.  
+**** Miller (2008) ****, however, points to the 
+``\dots reasonably accurate long-term economic forecasts,'' 
+achieved with the use of Cobb-Douglas production functions in economic models.  
+\citet{Shen:2013vp} provide a recent example 
+wherein empirical analysis on the estimated substitution elasticities 
+is performed before choosing any particular 
+nested CES production function structure. 
+As a result, \citeauthor{Shen:2013vp} propose an atypical structure 
+for the Chinese economy. **** More detail here about nesting? ****  
+Both the choice of production function structure 
+and the value of the model parameters 
+drive model results, and empirical and statistical testing 
+of such approaches is prudent.
+
+[2. Find our own voice
+What is our own argument?]
+
+These are not idle debates. 
+Economic growth models are often used to inform economic policy,
+and the paths of economies worldwide are determined by
+such policy choices. 
+Therefore, we agree with those who have serious concerns 
+about the reliability of the results from economic growth models \citep{Lecca:2011kr}. 
+\citet{Lecca:2011kr} and **** and what? **** would like to add
+**** ``would like to add'' or ``add''?**** that the inclusion of energy 
+would only further complicate issues.  **** Prev. sentence is unclear. ****
+We do except **** do you mean ``accept'' or ``expect'' here? ****, however, 
+that macroeconomic policymaking is needed 
+and is increasingly informed by integrated energy-economic models, 
+in a world where energy constraints are possible 
+\citep{Beckmanetal2011, Benes:2012tm, Nel:2010fv}.  
+We support the call from \citet{Shen:2013vp} that both
+the structure of the production function 
+and the parameters used to populate this function
+need empirical testing. 
+Furthermore, the quantification of energy ($q$, $x$, or $u$) 
+needs to be empirically assessed.  **** Need more on topic of energy quantification above. ****
+Building on the argument of \citet{Stern:2011bq} 
+that energy may or may not be required in production functions 
+depending on its abundance or scarcity, 
+we will further argue in this paper that different types of countries 
+may need different factors of production to explain their respective growth paths.  
+This further leaves open the possibility for 
+different explanations of growth in various countries
+at different stages of their development, 
+a central point of long-wave economic growth modeling 
+\citep{Froling:2009vo, Jones:2001wn, Galor:2000up}. 
+**** Should we discuss the longwave literature above? ****
+To gain insights from different countries across different stages of development, 
+we present a comparative analysis among 
+the World Bank’s main categories of countries, 
+namely Developed Countries (DCs), 
+Newly Industrialized Countries (NICs), 
+OPEC countries, and 
+Least Developed Countries (LDCs). 
+**** Move the previous sentence to the ``approach'' section below? ****
+
+Approach
+Build on articles using R to test econ growth PF, 
+question what is reported when doing these tests (shen/whalley and others who have used micEconCES).
+
+Discussion and Insights
+
+Does analysis differ from others in the conversation?
+Yes, differs as follows:
+\begin{itemize}
+\item{if one do these test, report on all $\delta$, $\sigma$, $\gamma$, and $\lambda$ 
+values as well as sse. 
+Good fits not evidence of best values, must report uncertainties as well.}
+\item{What motivates nesting of CES? Not well behaved $\rho$ results, driving $\sigma$s.
+Different type of CES with parsimonious factors, sigmas can be generated but not that easy (idea Randy).
+If you run all 3 nesting options, you can identify elasticities of all three factors in relation to each 
+other. Furthermore, you can determine which two factors are driving overall behavior in the aggregate function.}
+\item{necessary of different factors in PF to explain growth for countries in diff. development status}
+\end{itemize}
+
+What do we add to the conversation?
+
+\begin{itemize}
+
+\item{We are able to gain rich insights 
+on what really drives growth from detailed analysis (including uncertainties) 
+by testing all functional forms across many different 
+economy types.}
+
+\item{We were unable to gain new insights from the various energy quantifications that we tried.}
+
+\item{We find, surprisingly, that energy is not necessary 
+to be included alongside $k$ and $l$ in all PF. Models with energy and models without energy
+all perform well on an R$^2$ basis.}
+
+\item{We also find that
+
+(1) covariance of energy($e$) with both $k$ and $l$ is very high, with few exceptions (UK?).
+
+(2) with few exceptions, $\sigma_{(kl)e}$, $\sigma_{ke}$, and $\sigma_{le}$ 
+are all very low (indicating complementarity) (verify!!!!), and
+
+(3) energy-only models (SF$e$ and LINEX) achieve very good fits, just like CD$e$ and CES$e$.
+(should we make this point or not?)}
+
+\item{What does that mean? 
+It is a fallacy to think that saying energy is unnecessary 
+to include in an equation means energy is unimportant for economic growth. How to support this argument?
+
+If you find that energy is unnecessary to include alongside capital and labor 
+to explain growth in one economy at the macro, aggregated level, 
+you should not assume that energy is unimportant as a driver for economic growth for all economies.
+For developed economies, energy is captial intensive: you need to have large capital to make use 
+of energy. In developing economies, you don't need capital to make use of energy. 
+Rather, you need labor.
+
+We need to verify the above by comparison with our results.}
+
+\item{Also signals that different types of countries likely 
+to react differently to energy constraints. 
+Interpret $\sigma$ here, substitution possibilities.}
+
+\end{itemize}
+
+More work?
+
 Big picture
+[insert test test]
+
 Why do we do this? Want to link energy and economics on national level 
@@
 @
+
+[manually added]
+References
+
+Benes, J., Chauvet, M., Kamenik, O., Kumhof, M., Laxton, D., Mursula, S., and Selody, J. (2012). The Future of Oil: Geology versus Technology. IMF Working Papers, I12/109, 1–33.
+
+Chen, P-Y., Chen, S-T., Chen, C-C. 2012. Energy consumption and economic growth – New evidence from meta analysis. Energy Policy, 44: 245-255. http://dx.doi.org/10.1016/j.enpol.2012.01.048
+
+Duffy, J., and Papageorgiou, C.
+(2000).
+A Cross-Country Empirical Investigation of the Aggregate Production Function Specification.
+Journal of Economic Growth, 5(1), 87–120.
+doi:10.1023/A:1009830421147
+
+Fröling, M. (2011). Energy use, population and growth, 1800–1970. Journal of Population Economics, 24(3), 1133–1163.
+
+Galor, O., and Weil, D. N. (2000). Population,Technology, and Growth: From Malthusian Stagnation to the Demographic Transition and Beyond. American Economic Review, 90(4), 806–828.
+
+Jones, C. (2001). Was an industrial revolution inevitable? Economic growth over the very long run. Advances in Macroeconomics, 1(2), 1–43.
+
+Kemfert, C. (1998). Estimated substitution elasticities of a nested CES production function approach for Germany. Energy Economics, 20(3), 249–264.
+
+Lee, C-C. and Chang, C-P. Energy consumption and economic growth in Asian economies: A more comprehensive analysis using panel data. Resource and Energy Economics, 30(1): 50-65.
+
+Lecca, P., Swales, K., and Turner, K. (2011). An investigation of issues relating to where energy should enter the production function. Economic Modelling, 28(6), 2832–2841.
 

### 2013-09-01 EconGrowth2.Rnw
Example text for GitHub testing.

@@
 To be included somewhere.
+
+Matt added this text to debug his GitHub account.
 
@@
 
-Benes, J., Chauvet, M., Kamenik, O., Kumhof, M., Laxton, D., Mursula, S., and Selody, J. (2012). The Future of Oil: Geology versus Technology. IMF Working Papers, I12/109, 1–33.
-
 Chen, P-Y., Chen, S-T., Chen, C-C. 2012. Energy consumption and economic growth – New evidence from meta analysis. Energy Policy, 44: 245-255. http://dx.doi.org/10.1016/j.enpol.2012.01.048
 
-Duffy, J., and Papageorgiou, C.
-(2000).
-A Cross-Country Empirical Investigation of the Aggregate Production Function Specification.
-Journal of Economic Growth, 5(1), 87–120.
-doi:10.1023/A:1009830421147
-
-Fröling, M. (2011). Energy use, population and growth, 1800–1970. Journal of Population Economics, 24(3), 1133–1163.
-
-Galor, O., and Weil, D. N. (2000). Population,Technology, and Growth: From Malthusian Stagnation to the Demographic Transition and Beyond. American Economic Review, 90(4), 806–828.
-
-Jones, C. (2001). Was an industrial revolution inevitable? Economic growth over the very long run. Advances in Macroeconomics, 1(2), 1–43.
-
-Kemfert, C. (1998). Estimated substitution elasticities of a nested CES production function approach for Germany. Energy Economics, 20(3), 249–264.
-
 Lee, C-C. and Chang, C-P. Energy consumption and economic growth in Asian economies: A more comprehensive analysis using panel data. Resource and Energy Economics, 30(1): 50-65.
-
-Lecca, P., Swales, K., and Turner, K. (2011). An investigation of issues relating to where energy should enter the production function. Economic Modelling, 28(6), 2832–2841.
 

### 2013-09-01 EconGrowth.Rnw
Deleted several blank lines.
Added a section about sigma^{\prime} transform.
Testing GitHub.

@@
+% small change to test GitHub.
+
 % This article has been prepared for publication in Energy Economics in RStudio with knitr.
@@
 Figures~\ref{fig:CES_lambda_gamma_Cloud_Graph}--\ref{fig:CES_sigma_delta_Cloud_Graph}. 
+Note that transformed $\sigma$ and $\sigma_1$ values 
+($\sigma^{\prime}$ and $\sigma_1^{\prime}$) are plotted to compress 
+$2 < \sigma < \infty$ into $2 < \sigma^{\prime} \le 2.5$
+($2 < \sigma_1 < \infty$ into $2 < \sigma_1^{\prime} \le 2.5$):
+
+\begin{equation} \label{eq:sigma_transform}
+  \sigma^{\prime} = 
+    \begin{cases}
+      \sigma,   & 0 \le \sigma \le 2\\
+      1.5-\rho, & \sigma > 2
+    \end{cases}
+\end{equation}
+
+\begin{equation} \label{eq:sigma_1_transform}
+  \sigma_1^{\prime} = 
+    \begin{cases}
+      \sigma_1,   & 0 \le \sigma_1 \le 2\\
+      1.5-\rho_1, & \sigma_1 > 2
+    \end{cases}
+\end{equation}
 
@@
 are shown in 
-Figures~\ref{fig:CESx_lambda_gamma_Cloud_Graph_kle}--\ref{fig:CESx_sigma_delta_Cloud_Graph}.
+Figures~\ref{fig:CESx_lambda_gamma_Cloud_Graph_kle}--\ref{fig:CESx_sigma_delta_Cloud_Graph_kle}.
 

### 2013-09-03 EconGrowth2.Rnw
Removed recently added text.
Added several references from Martin.

@@
 
-Matt added this text to debug his GitHub account.
-
 Introduction
@@
 and for a diverse set of countries such as 
-the United States \citep{Stern2000, Cleveland:1984p5055}, 
+the United States \citep{Stern:2000wq, Cleveland:1984p5055}, 
 India (Paul and Bhattacharya 2004), 
@@
 resource and energy economists and economic growth modelers 
-\citep{Smulders:2003wc, VanderZwaan2002, Kemfert:1998vd}.
+\citep{Smulders:2003wc, vanderZwaan:2002wn, Kemfert:1998vd}.
 Researchers interested in explaining long-term economic growth 
@@
 than what a Cobb-Douglas specification would imply.  
-**** Miller (2008) ****, however, points to the 
+However, \citet{Miller:2008vd} points to the 
 ``\dots reasonably accurate long-term economic forecasts,'' 
@@
 in a world where energy constraints are possible 
-\citep{Beckmanetal2011, Benes:2012tm, Nel:2010fv}.  
+\citep{Beckman:2011gb, Benes:2012tm, Nel:2010fv}.  
 We support the call from \citet{Shen:2013vp} that both

### 2013-09-03 EconGrowth2.Rnw
Incorporated more of Martin's references. Edited the introduction section.

@@
 longer-term trends in energy use remain strongly upwards, 
-as the dynamics of energy markets are increasingly determined by emerging markets, 
+as the dynamics of energy markets are increasingly determined by emerging economies, 
 notably China, India, and the Middle East \citep{IEA:2012ty}. 
-A large body of literature points towards the fact that 
+A large body of literature points to the fact that 
 economic growth and energy consumption are closely correlated 
@@
 the United States \citep{Stern:2000wq, Cleveland:1984p5055}, 
-India (Paul and Bhattacharya 2004), 
-China (Wang et al 2011), 
-South Africa (Menyah and Wolde-Rufael, 2010; Odhiambo, 2009) and 
-sixteen Asian countries (Lee and Chang, 2008) 
+India \citep{Paul:2004jl}, 
+China \citep{Wang:2011fe}, 
+South Africa \citep{Menyah:2010hl, Odhiambo:2009hj} and 
+sixteen Asian countries \citep{Lee:2008dm}
 to name a few, 
-although the causal relationship between energy consumption 
-and economic growth is still controversial \citep{Chen2012, Ozturk:2010kb}. 
+although the causal relationship from energy consumption 
+to economic growth remains controversial \citep{Chen:2012fs, Ozturk:2010kb}. 
 \citet[p. 347]{Ozturk:2010kb} in a survey of the literature on the topic, 
@@
 as argued by above-mentioned scholars 
-have further raised the question 
+have further raised the question of
 whether and how to include appropriate energy indicators 
@@
 that energy is seen as the \emph{central driver of growth} 
-in ecological economic (incl. biophysical economic) models, 
+in ecological economic (including biophysical economic) models, 
 and that energy \emph{is included} in resource economic models, 
@@
 energy availability plays
-``\dots a key role in enabling growth''
-despite the evidence of decreasing energy used per unit of output.  
+``\dots a key role in enabling growth,''
+despite the evidence of decreasing energy consumed per unit of output.  
 He concludes, based on theory and time-series results, 
@@
 on the role of energy in economic growth.
+
 The inclusion of energy as a factor of production 
@@
 \citep{Froling:2009vo, Tahvonen:2001tz}.  
-One alternative approach, attempting to be 
+An alternative approach, attempting to be 
 ``\dots more consistent with physical laws \dots'' \citep{Ayres:2001tx}
-and classified by \citeauthor{Stern:2011bq} as an ecological economic model of growth, 
+and classified by \citet{Stern:2011bq} as an ecological economic model of growth, 
 is the LINEX production function, 
@@
 in richer countries and less substitutable in poorer countries 
-than what a Cobb-Douglas specification would imply.  
+than Cobb-Douglas implies.  
 However, \citet{Miller:2008vd} points to the 
@@
 drive model results, and empirical and statistical testing 
-of such approaches is prudent.
+of such approaches is prudent, but rarely conducted.
 
@@
 **** Should we discuss the longwave literature above? ****
+
 To gain insights from different countries across different stages of development, 
@@
 Approach
+
 Build on articles using R to test econ growth PF, 
@@
 @
-
-[manually added]
-References
-
-Chen, P-Y., Chen, S-T., Chen, C-C. 2012. Energy consumption and economic growth – New evidence from meta analysis. Energy Policy, 44: 245-255. http://dx.doi.org/10.1016/j.enpol.2012.01.048
-
-Lee, C-C. and Chang, C-P. Energy consumption and economic growth in Asian economies: A more comprehensive analysis using panel data. Resource and Energy Economics, 30(1): 50-65.
 

### 2013-09-15 EconGrowth.Rnw
Deleted test text.
Reran Iran cases with the full algorithm for all resampling.
Completed fixing the rbind.fill bug.

@@
-% small change to test GitHub.
-
 % This article has been prepared for publication in Energy Economics in RStudio with knitr.
@@
 require(micEconCES)
+require(plyr)
 # Provides access to data melting. 
@@
 Points on paper so far
+
 1. Does the relative small differences in fit between different production functions warrant 

### 2013-10-03 EconGrowth.Rnw
plot improvements

@@
 require(plyr)
+require(knitr)
 # Provides access to data melting. 

### 2013-10-03 Econ-Growth-Functions2.R

@@ -2615,7 +2615,8 @@ cesResamplePlotLambdaGamma <- function(energyType=NA, nest="(kl)e", ...){
     data <- loadAllResampleData(modelType="cese-(kl)e", energyType=energyType, 
                                 countryAbbrevsOrder=countryAbbrevsForGraph)
   }
-  graph <- standardScatterPlot(data, aes(gamma, lambda)) +
+  data$hist <- gsub("[^LPg]", "", data$history)
+  graph <- standardScatterPlot(data, aes(gamma, lambda, colour=hist)) +
     labs(x=expression(gamma), y=expression(lambda))
   return(graph)
 }
@@ -2632,7 +2633,8 @@ cesResamplePlotSigma_1Delta_1 <- function(energyType=NA, nest="(kl)e", ...){
     data <- loadAllResampleData(modelType=modelType, energyType=energyType, 
                                 countryAbbrevsOrder=countryAbbrevsForGraph)
   }
-  graph <- standardScatterPlot(data, aes(delta_1, sigmaTrans_1)) +
+  data$hist <- gsub("[^LPg]", "", data$history)
+  graph <- standardScatterPlot(data, aes(delta_1, sigmaTrans_1, colour=hist)) +
     labs(x=expression(delta_1), y=expression(sigma_1))
   return(graph)
 }
@@ -2651,7 +2653,8 @@ cesResamplePlotSigmaDelta <- function(energyType=NA, nest="(kl)e", ...){
     data <- loadAllResampleData(modelType="cese-(kl)e", energyType=energyType, 
                                 countryAbbrevsOrder=countryAbbrevsForGraph)
   }
-  graph <- standardScatterPlot(data, aes(delta, sigmaTrans)) +
+  data$hist <- gsub("[^LPg]", "", data$history)
+  graph <- standardScatterPlot(data, aes(delta, sigmaTrans, colour=hist)) +
     labs(x=expression(delta), y=expression(sigma))
   return(graph)
 }

### 2013-10-28 EconGrowth.Rnw
Removed ylim adjustments.

@@
 <<CES_sigma_1_delta_1_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
-cesResamplePlotSigma_1Delta_1(energyType=NA) + ylim(0, 2.5)
+cesResamplePlotSigma_1Delta_1(energyType=NA)
 @
@@
 <<CESq_sigma_1_delta_1_Cloud_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($kl$)$e$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
-cesResamplePlotSigma_1Delta_1(energyType="Q", nest="(kl)e") + ylim(0, 2.5)
+cesResamplePlotSigma_1Delta_1(energyType="Q", nest="(kl)e")
 @
@@
 <<CESq_sigma_delta_Cloud_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($kl$)$e$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
-cesResamplePlotSigmaDelta(energyType="Q", nest="(kl)e") + ylim(0, 2.5)
+cesResamplePlotSigmaDelta(energyType="Q", nest="(kl)e")
 @
@@
 <<CESx_sigma_1_delta_1_Cloud_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$, ($kl$)$e$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
-cesResamplePlotSigma_1Delta_1(energyType="X", nest="(kl)e") + ylim(0, 2.5)
+cesResamplePlotSigma_1Delta_1(energyType="X", nest="(kl)e")
 @
@@
 <<CESx_sigma_delta_Cloud_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$, ($kl$)$e$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
-cesResamplePlotSigmaDelta(energyType="X", nest="(kl)e") + ylim(0, 2.5)
+cesResamplePlotSigmaDelta(energyType="X", nest="(kl)e")
 @
@@
 <<CESu_sigma_1_delta_1_Cloud_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$, ($kl$)$e$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
-cesResamplePlotSigma_1Delta_1(energyType="U", nest="(kl)e") + ylim(0, 2.5)
+cesResamplePlotSigma_1Delta_1(energyType="U", nest="(kl)e")
 @
@@
 <<CESu_sigma_delta_Cloud_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$, ($kl$)$e$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
-cesResamplePlotSigmaDelta(energyType="U", nest="(kl)e") + ylim(0, 2.5)
+cesResamplePlotSigmaDelta(energyType="U", nest="(kl)e")
 @
@@
 <<CESq_sigma_1_delta_1_Cloud_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($le$)$k$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
-cesResamplePlotSigma_1Delta_1(energyType="Q", nest="(le)k") + ylim(0, 2.5)
+cesResamplePlotSigma_1Delta_1(energyType="Q", nest="(le)k")
 @
@@
 <<CESq_sigma_delta_Cloud_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($le$)$k$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
-cesResamplePlotSigmaDelta(energyType="Q", nest="(le)k") + ylim(0, 2.5)
+cesResamplePlotSigmaDelta(energyType="Q", nest="(le)k")
 @
@@
 <<CESx_sigma_1_delta_1_Cloud_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$, ($le$)$k$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
-cesResamplePlotSigma_1Delta_1(energyType="X", nest="(le)k") + ylim(0, 2.5)
+cesResamplePlotSigma_1Delta_1(energyType="X", nest="(le)k")
 @
@@
 <<CESx_sigma_delta_Cloud_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$, ($le$)$k$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
-cesResamplePlotSigmaDelta(energyType="X", nest="(le)k") + ylim(0, 2.5)
+cesResamplePlotSigmaDelta(energyType="X", nest="(le)k")
 @
@@
 <<CESu_sigma_1_delta_1_Cloud_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$, ($le$)$k$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
-cesResamplePlotSigma_1Delta_1(energyType="U", nest="(le)k") + ylim(0, 2.5)
+cesResamplePlotSigma_1Delta_1(energyType="U", nest="(le)k")
 @
@@
 <<CESu_sigma_delta_Cloud_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$, ($le$)$k$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
-cesResamplePlotSigmaDelta(energyType="U", nest="(le)k") + ylim(0, 2.5)
+cesResamplePlotSigmaDelta(energyType="U", nest="(le)k")
 @
@@
 <<CESq_sigma_1_delta_1_Cloud_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($ek$)$l$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
-cesResamplePlotSigma_1Delta_1(energyType="Q", nest="(ek)l") + ylim(0, 2.5)
+cesResamplePlotSigma_1Delta_1(energyType="Q", nest="(ek)l")
 @
@@
 <<CESq_sigma_delta_Cloud_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($ek$)$l$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
-cesResamplePlotSigmaDelta(energyType="Q", nest="(ek)l") + ylim(0, 2.5)
+cesResamplePlotSigmaDelta(energyType="Q", nest="(ek)l")
 @
@@
 <<CESx_sigma_1_delta_1_Cloud_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$, ($ek$)$l$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
-cesResamplePlotSigma_1Delta_1(energyType="X", nest="(ek)l") + ylim(0, 2.5)
+cesResamplePlotSigma_1Delta_1(energyType="X", nest="(ek)l")
 @
@@
 <<CESx_sigma_delta_Cloud_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $x$, ($ek$)$l$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
-cesResamplePlotSigmaDelta(energyType="X", nest="(ek)l") + ylim(0, 2.5)
+cesResamplePlotSigmaDelta(energyType="X", nest="(ek)l")
 @
@@
 <<CESu_sigma_1_delta_1_Cloud_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$, ($ek$)$l$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
-cesResamplePlotSigma_1Delta_1(energyType="U", nest="(ek)l") + ylim(0, 2.5)
+cesResamplePlotSigma_1Delta_1(energyType="U", nest="(ek)l")
 @
@@
 <<CESu_sigma_delta_Cloud_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="CES (with $u$, ($ek$)$l$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
-cesResamplePlotSigmaDelta(energyType="U", nest="(ek)l") + ylim(0, 2.5)
+cesResamplePlotSigmaDelta(energyType="U", nest="(ek)l")
 @
@@
 # linexResamplePlot(energyType="Q")
-linexResamplePlot(energyType="Q") + ylim(-20, 10)
+linexResamplePlot(energyType="Q")
 @
@@
 <<LINEXx_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX model (with $x$) resampling results.">>=
-linexResamplePlot(energyType="X") + ylim(-20, 10)
+linexResamplePlot(energyType="X")
 @

### 2013-10-29 EconGrowth2.Rnw
Initial trimming of exergy and useful work from the paper.

@@
 
-This section describes the three coordinates of analysis and briefly reviews 
+This section describes the two coordinates of analysis and briefly reviews 
 literature related to each.
@@
 %++++++++++++++++++++++++++++++
-\subsection{Quantification of Energy} 
-\label{sec:Quantification_of_Energy}
-%++++++++++++++++++++++++++++++
-
-The literature shows three quantifications of energy ($E$) used in 
-energy-augmented production functions: thermal energy ($Q$), 
-exergy ($X$), and useful work ($U$). Thermal energy ($Q$) 
-is the heat content of an energy carrier. Exergy ($X$) is 
-the maximum useful work that could be extracted from an energy carrier 
-by a process that brings the system into equilibrium with 
-a heat reservoir, typically the surrounding environment 
-\citep[p.~78]{Ayres:2010ug}. Like \citeauthor{Ayres:2010ug}, 
-we use chemical exergy (as opposed to thermal exergy or mechanical exergy) 
-as our quantification for exergy ($x$). Useful work ($U$) 
-includes the direct energy that goes into an economy, including work 
-from machines, human muscles, and animals. Firms pay for thermal energy ($Q$), 
-but useful work ($U$) alters the size and shape of materials, 
-keeps the lights on, and transports goods to consumers. 
-Not all forms of energy are created equal in terms of their ability 
-to generate economic activity \citep{Cleveland:2000vl, Warr:2010ht}. 
-Both exergy ($X$), and to a greater extent, useful work ($U$) 
-quantifications of energy are intended to account for the usefulness 
-of energy for generating economic activity, thereby reflecting 
-the ``quality'' of each energy type and the efficiency of machines 
-and devices typically used in energy conversion processes.
-
-Most energy economists use thermal energy ($q$) 
-for the energy factor of production ($e$) in energy-augmented 
-production functions, including \citet{Stern:2012ey}, 
-\citet{Froling:2009vo}, \citet{Serrenho:2010vq}, and 
-\citet{Kummel:1980wx,Kummel:1982vy,Kummel:1985vz,Kummel:1989tf,Kummel:2002tx,Kummel:2010vz}. 
-\citet{Ayres:2003ec} introduced the idea that exergy ($x$) and 
-useful work ($u$) were important factors of production.
-
-**** Martin: add more here about the conclusions of each paper 
-regarding the role of energy in economic growth? 
-Add additional literature? Or, adjust as you see fit. 
-Especially, are there any confidence intervals or 
-statistical evaluation in each of these studies? ****
-
-We know of no statistically-rigorous comparisons of the 
-predictive ability of each energy quantification in the 
-various types of production functions discussed in 
-Section~\ref{sec:Prod_Func_Forms}. We analyze all 
-three quantifications of energy ($Q$, $X$, and $U$) 
-for developed economies and thermal energy ($Q$) and 
-exergy ($X$) for all other economies.
-
-%++++++++++++++++++++++++++++++
 \subsection{Economy Types} 
@@
 %++++++++++++++++++++++++++++++
-\subsection{Thermal Energy, Exergy, and Useful Work} 
+\subsection{Thermal Energy} 
 \label{sec:Energy_Data}
@@
 and renewable energy sources (solar, wind, geothermal, biomass/fuel wood, 
-and hydro). In the style of work by Warr and Ayres 
-\citep{Ayres:2003ec, Ayres:2005kn, Warr:2010ht, Warr:2010ga, Warr:2012cg}, 
-energy from human and animal muscle power was also included. 
-Similar to the economic data discussed in 
+and hydro). Similar to the economic data discussed in 
 Sections~\ref{sec:Economic_Output_Data}--\ref{sec:Labor_Data}, 
-we generated energy data for developed countries from 1980--2011, 
-with the exception of useful work data (1980--2000). For all other countries, 
-we generated thermal energy and exergy data for 1991--2011. 
-Details on each energy quantifications are given in subsections below.
+we obtained energy data for developed countries from 1980--2011. 
+For all other countries, 
+we obtained thermal energy data for 1991--2011.
 
@@
 
+******* Maybe remove these paragraphs on animal and human muscle
+work, pending a response from Caleb. ****
+
 Animal and human muscle work was estimated using an approach 
@@
 
-%------------------------------
-\subsubsection{Exergy} 
-\label{sec:X_Data}
-%------------------------------
-
-Exergy ($X$), expressed in TJ/year, was calculated by multiplying 
-the thermal energy ($Q$) values discussed in Section~\ref{sec:Q_Data} 
-by a unitless exergy-to-thermal-energy allocation factor 
-($f_{exergy-allocation}$) shown in Table~\ref{tab:Exergy_Allocation}.
-
-\begin{equation} \label{eq:exergy}
-  X_{fuel} = f_{exergy-allocation} Q_{fuel}
-\end{equation}
-
-\begin{table} \caption{Exergy allocation factors.} \label{tab:Exergy_Allocation} 
-  \begin{center}
-    \begin{tabular}{r l} 
-      Fuel                                    & $f_{exergy-allocation}$ \\
-      \hline
-      Coal                                    & 1.088    \\
-      Oil and petroleum                       & 1.073   \\      
-      Dry natural gas and                     & \multirow{2}{*}{1.04}    \\
-      natural gas liquids                     &         \\
-      Corn-based biodiesel                    & 1.07  \\
-      Biomass/fuel wood                       & 1.15   \\
-      Ethanol biofuel                         & 1.099 \\
-      Nuclear, wind,                          & \multirow{2}{*}{1.0}   \\
-      solar PV, and hydro                     &                        \\
-    \end{tabular}
-  \end{center}
-\end{table}
-
-\noindent For carbon-based energy sources, $f_{exergy-allocation}$ 
-is the ratio of chemical exergy to lower (net) heating value. 
-The exergy allocation factors for coal, oil, natural gas, 
-biodiesel, and biomass/fuel wood were obtained from 
-\citet[Table~A-2]{Ayres:2003ec}. The exergy allocation ratio for 
-liquid ethanol was calculated from the standard molar chemical exergy 
-of 1357.7~kJ/mol \citep[Table~II]{Szargut:1988wv} and its lower 
-(net) heating value of 26.8~MJ/kg \citep[Table~A-27]{Cengel:2011ww}. 
-$f_{exergy-allocation}$ for each fuel was assumed to be constant 
-through time across all economies. For nuclear, wind, 
-solar photovoltaic, and hydro energy sources, the electricity generated 
-is already pure exergy, so $f_{exergy-allocation}$ is unity.
-
-To calculate the exergy of animal and human muscle power, 
-the food-to-work conversion efficiency ($\eta_{food \rightarrow work}$) 
-and the ratio of food intake to food available at wholesale 
-($f_{intake/wholesale}$) were included.
-
-\begin{equation} \label{eq:animal_muscle_exergy}
-  X_{animals} = \eta_{food \rightarrow work,animals} Q_{animals}
-\end{equation}
-
-\begin{equation} \label{eq:human_muscle_exergy}
-  X_{workers} = \eta_{food \rightarrow work,workers} f_{intake/wholesale} Q_{workers}
-\end{equation}
-
-\noindent $\eta_{food \rightarrow work, animals}$ and 
-$\eta_{food \rightarrow work, workers}$ are animal and worker efficiency 
-of converting food into energy, respectively. The animal feed-to-work 
-conversion efficiency ($\eta_{feed \rightarrow work, animals}$ = 0.4) 
-was taken from \citet{Warr:2012a} and assumed equal across all economies. 
-The food-to-work efficiency for workers 
-($\eta_{food \rightarrow work, workers}$ = 0.2) was taken from 
-\citet[Table~B.1]{Ayres:2010ug}. Following \citet[p.~315]{Ayres:2010ug} 
-and methodology from \citet{Warr:2012a}, an additional factor 
-($f_{intake/wholesale}$) was included to account for ``wastage and 
-losses of food in the household, e.g. during storage, in preparation 
-and cooking, as plate-waste, or quantities fed to domestic animals 
-and pets'' \citep[\texttt{notes} tab]{FAO:2013b}. 
-Values of $f_{intake/wholesale}$ were calculated from 
-\citet[Table~3.3 for wholesale and Table~3.4 for intake]{Wirsenius:2000vi}. 
-$f_{intake/wholesale}$ varies by country as shown in 
-Table~\ref{tab:f_intake_wholesale}. A similar intake-to-wholesale ratio 
-could also be applied to animal work, but data to calculate the ratio was 
-unavailable from \citet{Wirsenius:2000vi}, and $f_{intake/wholesale,animals}$ 
-is assumed to be unity.\footnote{The error in total exergy input to 
-any economy caused by assuming $f_{intake/wholesale,animals} = 1.0$ 
-is very small, because animal muscle exergy is a small fraction of the 
-total exergy supply to any economy, with a maximum of 0.41\% for China in 1992. 
-It could also be argued that $f_{intake/wholesale, animals}$ is likely 
-to be closer to unity than $f_{intake/wholesale, workers}$.}
-
-\begin{table} \caption{Food intake-to-wholesale ratios 
-                        ($f_{intake/wholesale}$) for all countries.} 
-                        \label{tab:f_intake_wholesale}
-  \begin{center}
-    \begin{tabular}{r c c c c c c c c c}
-      Country & US & UK & JP & CN & ZA & SA & IR & TZ & ZM \\
-      \hline
-      $f_{intake/wholesale}$ & 0.62 & 0.65 & 0.76 & 0.76 & 0.87 & 0.72 & 0.72 & 0.72 & 0.72\\
-    \end{tabular}
-  \end{center}
-\end{table}
-
-%------------------------------
-\subsubsection{Useful Work} 
-\label{sec:U_Data}
-%------------------------------
-
-The conversion of a raw energy carrier (e.g., coal) into 
-productive energy for an economy (e.g., electricity) necessarily 
-involves inefficiencies. In the case of coal consumption, 
-only about one-third of the coal exergy is converted to useful electricity: 
-the rest is waste heat. The concept of ``useful work,'' pioneered by 
-Ayres and Warr \citep{Ayres:2003ec, Ayres:2005kn}, builds upon 
-exergy analysis to consider efficiencies of both energy production and enduse. 
-To calculate useful work ($U$), the total exergy input to an 
-economy ($X$) is decomposed into several end uses: 
-high temperature industrial heat (e.g., steel production), 
-medium temperature heat (e.g., steam production), 
-low temperature space heat (for residential heating), 
-mechanical drive (energy used for prime mover engines of all types except electric motors), 
-electricity (excluding lighting), 
-lighting (from both electricity and fuels), and 
-muscle work (from animals and workers) as shown in the following equation:
-
-\begin{equation} \label{eq:useful_work}
-  U = \sum_i{\varepsilon_i \phi_i X}
-\end{equation}
-
-\noindent where the subscript $i$ indicates the energy enduse, 
-$\varepsilon_i$ is the efficiency of converting exergy into 
-useful energy for each enduse, and $\phi_i$ gives 
-the fraction of exergy input to an economy that goes toward 
-the $i^\mathrm{th}$ enduse.
-
-Values of $\varepsilon_i$ and $\phi_i$ were calculated from 
-the REXS database supplied by \citet{Warr:2012a}. 
-Values of $X$ were calculated by methods discussed in 
-Section~\ref{sec:X_Data}. For most countries, values of 
-$\phi_i$ are not constant with time, as economic sectors with 
-different distributions of raw exergy inputs grow at different rates. 
-\citeapos{Warr:2012a} REXS database contains information for 
-developed economies (United States, United Kingdom, and Japan) 
-from 1900--2000, and we used data from the 1980--2000 timeframe. 
-Extending the REXS database to the BRICS, petrol, and LDC economies 
-is beyond the scope of this work, because longitudinal data for 
-the efficiency of different end uses ($\varepsilon_i$) and 
-the distribution of exergy sources to end uses 
-($\phi_i$) are extremely difficult to obtain.
-
 %++++++++++++++++++++++++++++++
@@
 labor ($l$), and 
-the various energy quantifications ($q$, $x$, and $u$) 
+energy ($q$) 
 for 1980--2011 (developed economies) and 1991--2011 (other economies). 
@@
 
-Figure~\ref{fig:Historical_Lattice_Graph} indicates the importance 
-of energy quantification for economic growth modeling. 
-Thermal energy ($q$) and exergy ($x$) grow at similar rates, 
-unless there is a significant raw energy carrier substitution in the economy 
-(such as China's rapid increase of coal and natural gas consumption 
-relative to petroleum since 2000). The growth rate of $u$ is 
-significantly different from $q$ and $x$ for most countries, however. 
-\citet{Warr:2012cg} show that from 1950-1990, useful work ($u$) 
-grew much faster than $q$, $x$, $k$, or $l$ due to efficiency gains 
-in the U.S. economy. The results of \citeauthor{Warr:2012cg} suggest 
-that the time-dependent technological progress term ($A$) 
-in the Cobb-Douglas and CES production functions 
-(Equations~\ref{eq:CD}--\ref{eq:CESekl}) may be a proxy for 
-increasing energy efficiency in the U.S. economy.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Section~\ref{sec:Prod_Func_Forms} has parameters which must be estimated (fitted)
-for each energy quantification (see Section~\ref{sec:Quantification_of_Energy}) 
-and each economy (see Section~\ref{sec:Economy_Types})
+for each economy (see Section~\ref{sec:Economy_Types})
 via least-squares methods. We used \texttt{R} \citep{R} functions
@@
 model predictions (in our case, $y_{pred,t}$) at
-time $t$ are representative 
-of the uncertainty of and random scatter in the observed historical data.
+time $t$ are representative of the uncertainty of 
+and random scatter in the observed historical data.
 
@@
 from the Cobb-Douglas models 
-(without energy, with $e=q$, with $e=x$, and with $e=u$) to historical data.
+(with and without energy) to historical data.
+
+**** Need to strip out $x$ and $u$ predictions ****
 
@@
 $\gamma$, $\lambda$, $\delta_1$, $\rho_1$, $\delta$, and $\rho$. 
-**** Adjust these parameter names if we decide to 
-change them. **** The \texttt{cesEst} function of \texttt{micEconCES} provides 
+The \texttt{cesEst} function of \texttt{micEconCES} provides 
 several algorithm options for parameter estimation.
@@
 negative values for elasticity of substitution ($\sigma$) parameters.
+
+**** MKH: Rewrite to reflect final algorithm ****
 

### 2013-10-29 EconGrowth2.Rnw
Renamed Thermal Energy to Energy. Removed a comment about needing input from Caleb.

@@
 %++++++++++++++++++++++++++++++
-\subsection{Thermal Energy} 
+\subsection{Energy} 
 \label{sec:Energy_Data}
@@
 and renewable energy sources (solar, wind, geothermal, biomass/fuel wood, 
-and hydro). Similar to the economic data discussed in 
+and hydro). We also added human and animal muscle work. 
+Similar to the economic data discussed in 
 Sections~\ref{sec:Economic_Output_Data}--\ref{sec:Labor_Data}, 
@@
 For all other countries, 
-we obtained thermal energy data for 1991--2011.
-
-%------------------------------
-\subsubsection{Thermal Energy} 
-\label{sec:Q_Data}
-%------------------------------
+we obtained energy data for 1991--2011.
 
@@
 
-******* Maybe remove these paragraphs on animal and human muscle
-work, pending a response from Caleb. ****
-
 Animal and human muscle work was estimated using an approach 
-similar to \citet{Ayres:2010ug}, using some data from Warr's 
+similar to \citet{Ayres:2010ug}, using data from Warr's 
 REXS database \citep{Warr:2012a} and results from 

### 2013-11-04 EconGrowth2.Rnw
Added CD ternary plots.

@@
 Under that assumption, it would not be surprising if the residual from 
-any one year had been observed on a different year. 
+any one year had been observed in a different year. 
 By applying randomly selected residuals (with randomly selected signs)
@@
 The Cobb-Douglas model without energy is given by 
-Equation~\ref{eq:CD}. The Cobb-Douglas (without energy) production function was
+Equation~\ref{eq:CD}. Equation~\ref{eq:CD} was
 reparameterized as
@@
 
-**** CD without energy results here. Scatter plots? CIs? 
-Partial residual plots? TBD which to include. ****
+Figure~\ref{fig:CD_Scatter_Graph} shows a ternary plot 
+of $\alpha$, $\beta$, and $\gamma$ parameter values 
+for resample models for the Cobb-Douglas model (without energy). 
+In Figure~\ref{fig:CD_Scatter_Graph}, 
+$\gamma$ is always 0.0, because energy is not included in this model.
+
+<<CD_Scatter_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (without energy) resample model parameters.">>=
+cdResampleTrianglePlot(energyType=NA)
+@
+
+Converting the resample data into 95\% confidence intervals 
+provides data for Figure~\ref{fig:CD_Params_Graph}.
+Appendix~\ref{sec:Model_Parameters} 
+contains tables with numerical values of 
+Cobb-Douglas model parameters and 95\% confidence intervals.
+
+<<CD_Params_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.cap="Cobb-Douglas (without energy) model parameters.
+Vertical bars indicate 95\\% confidence intervals.">>=
+createCDParamsGraph(energyType=NA)
+@
 
@@
 
-**** Include CD$e$ graphs here. Ternary plots? CIs? TBD which to include. ****
+Figure~\ref{fig:CDq_Cloud_Graph} shows ternary plots 
+for $\alpha$, $\beta$, and $\gamma$ parameter values 
+for Cobb-Douglas (with energy) resample models.
+
+<<CDq_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (with energy) resample model parameters.">>=
+cdResampleTrianglePlot(energyType="Q")
+@
 
@@
 
-<<CES_GDP_Lattice_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES fitted models with ($kl$)$e$ nesting.">>=
+<<CES_GDP_Lattice_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES fitted models with ($kl$)$e$ nesting.", eval=FALSE>>=
 createCESLatticeGraph()

### 2013-11-04 EconGrowth2.Rnw
Moved resample coefficient tables and 95% CI graphs to appendix.

@@
 
-Converting the resample data into 95\% confidence intervals 
-provides data for Figure~\ref{fig:CD_Params_Graph}.
-Appendix~\ref{sec:Model_Parameters} 
-contains tables with numerical values of 
-Cobb-Douglas model parameters and 95\% confidence intervals.
-
-<<CD_Params_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.cap="Cobb-Douglas (without energy) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createCDParamsGraph(energyType=NA)
-@
-
 To estimate the parameters $\lambda$, $\alpha$, $\beta$, and $\gamma$ 
@@
 
-Figure~\ref{fig:CDq_Cloud_Graph} shows ternary plots 
+Figure~\ref{fig:CDq_Scatter_Graph} shows ternary plots 
 for $\alpha$, $\beta$, and $\gamma$ parameter values 
@@
 
-<<CDq_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (with energy) resample model parameters.">>=
+<<CDq_Scatter_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (with energy) resample model parameters.">>=
 cdResampleTrianglePlot(energyType="Q")
@@
 
-**** Include CES graphs here. Need to cover
-all options: without energy and the three nesting
-options. CIs? TBD which to include. ****
+Coefficients for each resampled CES model (without energy)
+are shown in 
+Figures~\ref{fig:CES_lambda_gamma_Scatter_Graph} and
+\ref{fig:CES_sigma_1_delta_1_Scatter_Graph}. 
+Note that the bottom of the vertical axis represents $\sigma = 0$.
+The top of the vertical axis represents $\sigma = \infty$.
+The crosshair on each graph shows the location 
+of the fit to historical data. 
+Dots are colored by whether or not the fitting routine
+reports model convergence.
+
+<<CES_lambda_gamma_Scatter_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\lambda$ and $\\gamma$.">>=
+cesResamplePlotLambdaGamma(energyType=NA)
+@
+
+<<CES_sigma_1_delta_1_Scatter_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
+cesResamplePlotSigma_1Delta_1(energyType=NA)
+@
 
@@
 to historical data for the $(kl)e$ nesting.
+
+**** Matt: Remove $x$ and $u$ lines. Replace with lines for each nesting. ****
 
@@
 printFracUnconvergedXtable()
+@
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{95\% Confidence Intervals}
+\label{sec:Confidence_Intervals}
+\setcounter{table}{0} % Restarts table number counter at 0 in this section.
+\setcounter{figure}{0} % Restarts figure number counter at 0 in this section.
+\setcounter{equation}{0} % Restarts equation counter to 0 in this section.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Resample coefficients in the scatter plots 
+can be represented as 95\% confidence intervals 
+by finding the parameter values associated with 
+the middle 95\% of the data for each model parameter.
+This appendix provides tables and graphs of the 95\% confidence
+intervals on fitted model parameters.
+
+%++++++++++++++++++++++++++++++
+\subsection{Cobb-Douglas Models}
+%++++++++++++++++++++++++++++++
+
+The 95\% confidence intervals associated with Figure~\ref{fig:CD_Scatter_Graph} 
+are shown in Table~\ref{tab:CD_Params_Table}.
+
+<<CD_Params_Table, results='asis'>>=
+printCDParamsTable(energyType=NA)    #Without energy
+@
+
+The data in Table~\ref{tab:CD_Params_Table} is plotted in
+Figure~\ref{CD_Params_Graph}.
+
+<<CD_Params_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.cap="Cobb-Douglas (without energy) model parameters.
+Vertical bars indicate 95\\% confidence intervals.">>=
+createCDParamsGraph(energyType=NA)
+@
+
+The 95\% confidence intervals associated with Figure~\ref{fig:CDq_Scatter_Graph} 
+are shown in Table~\ref{tab:CDq_Params_Table}
+and Figure~\ref{CDq_Params_Graph}.
+
+<<CDq_Params_Table, results='asis'>>=
+printCDParamsTable(energyType="Q")   #With energy
+@
+
+<<CDq_Params_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.cap="Cobb-Douglas (with energy) model parameters.
+Vertical bars indicate 95\\% confidence intervals.">>=
+createCDParamsGraph(energyType="Q")
+@
+
+%++++++++++++++++++++++++++++++
+\subsection{CES Models}
+%++++++++++++++++++++++++++++++
+
+The 95\% confidence intervals associated with Figure~\ref{fig:}
+are shown in Table~\ref{tab:} and Figure~\ref{fig:}
+**** Ensure that we have tables for all nestings. ****
+
+<<CES_Params_Table, results='asis'>>=
+printCESParamsTableA(energyType=NA)
+printCESParamsTableB(energyType=NA)
+@
+
+The 95\% confidence intervals associated with Figure~\ref{fig:}
+are shown in Table~\ref{tab:} and Figure~\ref{fig:}
+**** Ensure that we have figures for all nestings. ****
+
+<<CES_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (without energy) model parameters.
+Vertical bars indicate 95\\% confidence intervals.">>=
+createCESParamsGraph(energyType=NA)
+@
+
+The 95\% confidence intervals associated with Figure~\ref{fig:}
+are shown in Table~\ref{tab:} and Figure~\ref{fig:}
+**** Ensure that we have tables for all nestings. ****
+
+<<CESq_Params_Table, results='asis'>>=
+printCESParamsTableA(energyType="Q")
+printCESParamsTableB(energyType="Q")
+@
+
+The 95\% confidence intervals associated with Figure~\ref{fig:}
+are shown in Table~\ref{tab:} and Figure~\ref{fig:}
+**** Ensure that we have figures for all nestings. ****
+
+<<CESq_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with energy, ($kl$)$e$ nesting) model parameters.
+Vertical bars indicate 95\\% confidence intervals.">>=
+createCESParamsGraph(energyType="Q")
+@
+
+%++++++++++++++++++++++++++++++
+\subsection{LINEX Model}
+%++++++++++++++++++++++++++++++
+
+The 95\% confidence intervals associated with Figure~\ref{fig:}
+are shown in Table~\ref{tab:} and Figure~\ref{fig:}
+**** Ensure that we have figures for all nestings. ****
+
+<<LINEX_Params_Table, results='asis'>>=
+printLINEXParamsTable(energyType="Q")
+@
+
+<<LINEXq_Params_Graph, fig.pos="H", fig.width=linexParameterGraphWidth, fig.height=linexParameterGraphHeight, fig.cap="LINEX model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
+createLINEXParamsGraph(energyType="Q")
 @

### 2013-11-04 EconGrowth2.Rnw
Resample scatter plots for all CES nestings now included.

@@
 
+**** Include other nestings here ****
+
+Coefficients for each resampled CES model (with energy)
+are shown in 
+Figures~\ref{fig:CESq_lambda_gamma_Scatter_Graph_kle}--\ref{fig:CESq_sigma_delta_Scatter_Graph_ekl}. 
+Note that each nesting of the factors of production
+is included in the graphs.
+
+<<CESq_lambda_gamma_Scatter_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($kl$)$e$ nesting) resample model parameters $\\lambda$ and $\\gamma$.">>=
+cesResamplePlotLambdaGamma(energyType="Q", nest="(kl)e")
+@
+
+<<CESq_sigma_1_delta_1_Scatter_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($kl$)$e$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
+cesResamplePlotSigma_1Delta_1(energyType="Q", nest="(kl)e")
+@
+
+<<CESq_sigma_delta_Scatter_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($kl$)$e$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
+cesResamplePlotSigmaDelta(energyType="Q", nest="(kl)e")
+@
+
+<<CESq_lambda_gamma_Scatter_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($le$)$k$ nesting) resample model parameters $\\lambda$ and $\\gamma$.">>=
+cesResamplePlotLambdaGamma(energyType="Q", nest="(le)k")
+@
+
+<<CESq_sigma_1_delta_1_Scatter_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($le$)$k$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
+cesResamplePlotSigma_1Delta_1(energyType="Q", nest="(le)k")
+@
+
+<<CESq_sigma_delta_Scatter_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($le$)$k$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
+cesResamplePlotSigmaDelta(energyType="Q", nest="(le)k")
+@
+
+<<CESq_lambda_gamma_Scatter_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($ek$)$l$ nesting) resample model parameters $\\lambda$ and $\\gamma$.">>=
+cesResamplePlotLambdaGamma(energyType="Q", nest="(ek)l")
+@
+
+<<CESq_sigma_1_delta_1_Scatter_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($ek$)$l$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
+cesResamplePlotSigma_1Delta_1(energyType="Q", nest="(ek)l")
+@
+
+<<CESq_sigma_delta_Scatter_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($ek$)$l$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
+cesResamplePlotSigmaDelta(energyType="Q", nest="(ek)l")
+@
+
 Figure~\ref{fig:CES_GDP_Lattice_Graph_kle} compares CES model predictions 
@@
 @
-
-**** Include other nestings here? ****
 

### 2013-11-04 EconGrowth2.Rnw
Added description of final CES fitting algorithm.

@@
 \citep{Henningsen:2011td} was used to estimate parameters 
-$\gamma$, $\lambda$, $\delta_1$, $\rho_1$, $\delta$, and $\rho$. 
+$\lambda$, $\gamma$, $\delta$, $\delta_1$, $\rho$, and $\rho_1$. 
 The \texttt{cesEst} function of \texttt{micEconCES} provides 
@@
 negative values for elasticity of substitution ($\sigma$) parameters.
-
-**** MKH: Rewrite to reflect final algorithm ****
-
-Two algorithms available in \texttt{cesEst} 
-(\texttt{PORT} and \texttt{L-BFGS-B}) respect coefficient constraints. 
-Our CES parameter estimation algorithm tries both
-with default starting values and selects the
-result with lowest $sse$, regardless
-of convergence status. If one algorithm
-fails during the fitting process 
-(due to division by zero or another numerical error), 
-we use coefficients from the algorithm that didn't.
-In event that both algorithms fail, 
-we skip that resampled data point.
+Thus, we used the two fitting algorithms available in \texttt{cesEst} that
+respect coefficient constraints: \texttt{PORT} and \texttt{L-BFGS-B}.
+
+Our CES parameter estimation algorithm starts with an eleven-value grid search
+in $\rho$ and $\rho_1$ (9, 2, 1, 0.43, 0.25, 0.1, -0.1, -0.5, -0.75, -0.9, -0.99),
+which corresponds to $\sigma$ and $\sigma_1$ values of
+0.1, 0.33, 0.5, 0.7, 0.8, 0.9, 1.11, 2, 4, 10, and 100, respectively.
+During the grid search, values of $\rho$ and $\rho_1$ are fixed,
+and values of $\lambda$, $\gamma$, $\delta$, and $\delta_1$ are estimated 
+by gradient search with the \texttt{PORT} and \texttt{L-BFGS-B} algorithms.
+In all, 121 gradient searches in $\lambda$, $\gamma$, $\delta$, and $\delta_1$
+at grid points representing all combinations of $\rho$ and $\rho_1$ are attempted.
+During the grid search portion of our algorithm, starting values for the free parameters
+are $\lambda$ = 0.015/year, $\delta$ = 0.5, $\delta_1$ = 0.5, 
+and $\gamma$ is set to a value such that the mean of the residuals is zero.
+
+Next, a gradient search (using both \texttt{PORT} and \texttt{L-BFGS-B}) 
+is attempted wherein all fitting parameters 
+($\lambda$, $\gamma$, $\delta$, $\delta_1$, $\rho$, and $\rho_1$)
+are allowed to float. 
+The start values for fitting parameters are taken from 
+the grid search fit that provided the lowest $sse$.
+
+If resampled data are being fitted, a prior fit to historical data is available.
+In the final step of our algorithm, 
+a gradient search (using both \texttt{PORT} and \texttt{L-BFGS-B})
+uses coefficients from the best 
+fit to historical data as its starting point. 
+In this final gradient search, all model parameters 
+($\lambda$, $\gamma$, $\delta$, $\delta_1$, $\rho$, and $\rho_1$)
+are considered free parameters.
+
+The fit with lowest $sse$ of all the above trials is deemed the winner,
+and its fitting parameters are used as the model.
 
@@
 (i.e., for the same $y$, $k$, $l$, and $e$ data).
-
-**** Do we want to report on the fraction of non-convergence
-reported? Maybe we should write a function that 
-searches all the countries to find which 
-country reports least convergence for a given model. ****
 

### 2013-11-04 EconGrowth2.Rnw
Added LINEX resample plot.

@@
 
-**** Include LINEX scatter graphs here. Cover all 
-quantifications of energy? CIs? TBD which to include. ****
+Figure~\ref{fig:LINEXq_Resample_Graph}
+shows the coefficients estimated from resampled data.
+
+<<LINEXq_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX model (with energy) resampling results.">>=
+# linexResamplePlot(energyType="Q")
+linexResamplePlot(energyType="Q")
+@
 

### 2013-11-04 EconGrowth2.Rnw
Fixed Table and Figure references in the Appendix.

@@
 Figure~\ref{fig:LINEX_GDP_Lattice_Graph} compares LINEX model predictions to historical data.
+**** Remove $x$ and $u$ lines. ****
 
@@
 The 95\% confidence intervals associated with Figure~\ref{fig:CD_Scatter_Graph} 
-are shown in Table~\ref{tab:CD_Params_Table}.
+are shown in Table~\ref{tab:CD_Parameters_No_Energy}.
 
@@
 
-The data in Table~\ref{tab:CD_Params_Table} is plotted in
-Figure~\ref{CD_Params_Graph}.
+The data in Table~\ref{tab:CD_Parameters_No_Energy} is plotted in
+Figure~\ref{fig:CD_Params_Graph}.
 
@@
 The 95\% confidence intervals associated with Figure~\ref{fig:CDq_Scatter_Graph} 
-are shown in Table~\ref{tab:CDq_Params_Table}
-and Figure~\ref{CDq_Params_Graph}.
+are shown in Table~\ref{tab:CD_Parameters_With_Q}
+and Figure~\ref{fig:CDq_Params_Graph}.
 

### 2013-11-05 EconGrowth2.Rnw
Edited text to create 95% CI graphs and tables for different CES nestings.

@@
 
-The 95\% confidence intervals associated with Figure~\ref{fig:}
-are shown in Table~\ref{tab:} and Figure~\ref{fig:}
-**** Ensure that we have tables for all nestings. ****
+The 95\% confidence intervals associated 
+with Figures~\ref{fig:CES_lambda_gamma_Scatter_Graph} 
+and \ref{fig:CES_sigma_1_delta_1_Scatter_Graph}
+are shown in Tables~\ref{tab:CES_Parameters_A} 
+and \ref{tab:CES_Parameters_B} and Figure~\ref{fig:CES_Params_Graph}.
 
@@
 
-The 95\% confidence intervals associated with Figure~\ref{fig:}
-are shown in Table~\ref{tab:} and Figure~\ref{fig:}
-**** Ensure that we have figures for all nestings. ****
-
 <<CES_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (without energy) model parameters.
@@
 
-The 95\% confidence intervals associated with Figure~\ref{fig:}
-are shown in Table~\ref{tab:} and Figure~\ref{fig:}
-**** Ensure that we have tables for all nestings. ****
+The 95\% confidence intervals associated 
+with Figures~\ref{fig:CESq_lambda_gamma_Scatter_Graph_kle}--\ref{fig:CESq_sigma_delta_Scatter_Graph_kle}
+are shown in Tables~\ref{tab:CES_Parameters_A_With_Q_(kl)e} and 
+\ref{tab:CES_Parameters_B_With_Q_(kl)e} and Figure~\ref{fig:CESq_Params_Graph_kle}.
+**** Ensure that we have figures for all nestings. ****
 
 <<CESq_Params_Table, results='asis'>>=
-printCESParamsTableA(energyType="Q")
-printCESParamsTableB(energyType="Q")
-@
-
-The 95\% confidence intervals associated with Figure~\ref{fig:}
-are shown in Table~\ref{tab:} and Figure~\ref{fig:}
-**** Ensure that we have figures for all nestings. ****
-
-<<CESq_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with energy, ($kl$)$e$ nesting) model parameters.
+printCESParamsTableA(energyType="Q", nest="(kl)e")
+printCESParamsTableB(energyType="Q", nest="(kl)e")
+@
+
+<<CESq_Params_Graph_kle, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with energy, ($kl$)$e$ nesting) model parameters.
 Vertical bars indicate 95\\% confidence intervals.">>=
-createCESParamsGraph(energyType="Q")
+createCESParamsGraph(energyType="Q", nest="(kl)e")
 @

### 2013-11-05 EconGrowth2.Rnw
Changed name of one code block to include nesting.
Added graphs and tables for (le)k and (ek)l nestings.

@@
 
-The 95\% confidence intervals associated 
+The 95\% confidence intervals for the ($kl$)$e$ nesting associated 
 with Figures~\ref{fig:CESq_lambda_gamma_Scatter_Graph_kle}--\ref{fig:CESq_sigma_delta_Scatter_Graph_kle}
@@
 \ref{tab:CES_Parameters_B_With_Q_(kl)e} and Figure~\ref{fig:CESq_Params_Graph_kle}.
-**** Ensure that we have figures for all nestings. ****
-
-<<CESq_Params_Table, results='asis'>>=
+
+<<CESq_Params_Table_kle, results='asis'>>=
 printCESParamsTableA(energyType="Q", nest="(kl)e")
@@
 createCESParamsGraph(energyType="Q", nest="(kl)e")
+@
+
+The 95\% confidence intervals for the ($le$)$k$ nesting associated 
+with Figures~\ref{fig:CESq_lambda_gamma_Scatter_Graph_lek}--\ref{fig:CESq_sigma_delta_Scatter_Graph_lek}
+are shown in Tables~\ref{tab:CES_Parameters_A_With_Q_(le)k} and 
+\ref{tab:CES_Parameters_B_With_Q_(le)k} and Figure~\ref{fig:CESq_Params_Graph_lek}.
+
+<<CESq_Params_Table_lek, results='asis'>>=
+printCESParamsTableA(energyType="Q", nest="(le)k")
+printCESParamsTableB(energyType="Q", nest="(le)k")
+@
+
+<<CESq_Params_Graph_lek, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with energy, ($le$)$k$ nesting) model parameters.
+Vertical bars indicate 95\\% confidence intervals.">>=
+createCESParamsGraph(energyType="Q", nest="(le)k")
+@
+
+The 95\% confidence intervals for the ($ek$)$l$ nesting associated 
+with Figures~\ref{fig:CESq_lambda_gamma_Scatter_Graph_ekl}--\ref{fig:CESq_sigma_delta_Scatter_Graph_ekl}
+are shown in Tables~\ref{tab:CES_Parameters_A_With_Q_(ek)l} and 
+\ref{tab:CES_Parameters_B_With_Q_(ek)l} and Figure~\ref{fig:CESq_Params_Graph_ekl}.
+
+<<CESq_Params_Table_ekl, results='asis'>>=
+printCESParamsTableA(energyType="Q", nest="(ek)l")
+printCESParamsTableB(energyType="Q", nest="(ek)l")
+@
+
+<<CESq_Params_Graph_ekl, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with energy, ($ek$)$l$ nesting) model parameters.
+Vertical bars indicate 95\\% confidence intervals.">>=
+createCESParamsGraph(energyType="Q", nest="(ek)l")
 @

### 2013-11-05 EconGrowth2.Rnw
Now including LINEX parameter tables and candlestick graphs in appendix.

@@
 
-The 95\% confidence intervals associated with Figure~\ref{fig:}
-are shown in Table~\ref{tab:} and Figure~\ref{fig:}
-**** Ensure that we have figures for all nestings. ****
+The 95\% confidence intervals associated with Figure~\ref{fig:LINEXq_Resample_Graph}
+are shown in Table~\ref{tab:LINEX_Parameters_With_Q} and Figure~\ref{fig:LINEXq_Params_Graph}.
 

### 2013-11-10 EconGrowth2.Rnw
Added CES prediction graphs for (le)k and (ek)l nestings.

@@
 
-<<CES_GDP_Lattice_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES fitted models with ($kl$)$e$ nesting.", eval=FALSE>>=
-createCESLatticeGraph()
+<<CES_GDP_Lattice_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES fitted models with ($kl$)$e$ nesting.">>=
+createCESLatticeGraph(nest="(kl)e")
+@
+
+Figure~\ref{fig:CES_GDP_Lattice_Graph_lek} compares CES model predictions 
+to historical data for the $(le)k$ nesting.
+
+<<CES_GDP_Lattice_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES fitted models with ($le$)$k$ nesting.">>=
+createCESLatticeGraph(nest="(le)k")
+@
+
+Figure~\ref{fig:CES_GDP_Lattice_Graph_ekl} compares CES model predictions 
+to historical data for the $(ek)l$ nesting.
+
+<<CES_GDP_Lattice_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES fitted models with ($ek$)$l$ nesting.">>=
+createCESLatticeGraph(nest="(ek)l")
 @

### 2013-11-11 EconGrowth2.Rnw
Added a table for CES alpha, beta, and gamma calculations.

@@
 
-**** Include other nestings here ****
-
 Coefficients for each resampled CES model (with energy)
@@
 @
+
+We can develop pseudo $\alpha$, $\beta$, and $\gamma$ parameters 
+for the CES model, based on values of $\delta$ and $\delta_1$.
+The following table shows the permuted equations for each CES nesting.
+
+\begin{table} \caption{Equations for $\alpha$, $\beta$, and $\gamma$ for the various CES nestings.} 
+\label{tab:CES_abg_equations} 
+  \begin{center}
+    \begin{tabular}{c c c c c} 
+      Nesting    & Equation        & $\alpha$                & $\beta$                 & $\gamma$                \\
+      \hline
+      ($kl$)     & \ref{eq:CES}    & $\delta_1$              & $1 - \delta_1$          & 0                       \\
+      ($kl$)$e$  & \ref{eq:CESkle} & $\delta \delta_1$       & $\delta (1 - \delta_1)$ & $1 - \delta$            \\   
+      ($le$)$k$  & \ref{eq:CESlek} & $1 - \delta$            & $\delta \delta_1$       & $\delta (1 - \delta_1)$ \\
+      ($ek$)$l$  & \ref{eq:CESekl} & $\delta (1 - \delta_1)$ & $1 - \delta$            & $\delta \delta_1$       \\
+    \end{tabular}
+  \end{center}
+\end{table}
 

### 2013-11-12 EconGrowth2.Rnw
Added ternary plots for CES models with different nestings.

@@
 
+Figure~\ref{fig:CESq_ternary_graph_kl} shows 
+$\alpha$, $\beta$, and $\gamma$ parameters from the CES model without energy.
+
+<<CESq_ternary_graph_kl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="CES (without energy) resample model $\\alpha$, $\\beta$, and $\\gamma$ values.">>=
+cesResampleTrianglePlot(energyType=NA)
+@
+
+Figure~\ref{fig:CESq_ternary_graph_kle} shows 
+$\alpha$, $\beta$, and $\gamma$ parameters from the CES model with ($kl$)$e$ nesting.
+
+<<CESq_ternary_graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="CES (with energy) resample model $\\alpha$, $\\beta$, and $\\gamma$ values, ($kl$)$e$ nesting.">>=
+cesResampleTrianglePlot(energyType="Q", nest="(kl)e")
+@
+
+Figure~\ref{fig:CESq_ternary_graph_lek} shows 
+$\alpha$, $\beta$, and $\gamma$ parameters from the CES model with ($kl$)$e$ nesting.
+
+<<CESq_ternary_graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="CES (with energy) resample model $\\alpha$, $\\beta$, and $\\gamma$ values, ($le$)$k$ nesting.">>=
+cesResampleTrianglePlot(energyType="Q", nest="(kl)e")
+@
+
+Figure~\ref{fig:CESq_ternary_graph_ekl} shows 
+$\alpha$, $\beta$, and $\gamma$ parameters from the CES model with ($kl$)$e$ nesting.
+
+<<CESq_ternary_graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="CES (with energy) resample model $\\alpha$, $\\beta$, and $\\gamma$ values, ($ek$)$l$ nesting.">>=
+cesResampleTrianglePlot(energyType="Q", nest="(ek)l")
+@
+
 Figure~\ref{fig:CES_GDP_Lattice_Graph_kle} compares CES model predictions 

### 2013-11-12 EconGrowth2.Rnw
Deleted two lines.
Lattice graphs contain only Q predictions. CES lattice graph contains all nestings.

@@
 
-**** Need to strip out $x$ and $u$ predictions ****
-
 <<CD_GDP_Lattice_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas fitted models.">>=
-createCDLatticeGraph()
+createCDLatticeGraph(energyType="Q")
 @
@@
 <<CESq_ternary_graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="CES (with energy) resample model $\\alpha$, $\\beta$, and $\\gamma$ values, ($le$)$k$ nesting.">>=
-cesResampleTrianglePlot(energyType="Q", nest="(kl)e")
+cesResampleTrianglePlot(energyType="Q", nest="(le)k")
 @
@@
 
-Figure~\ref{fig:CES_GDP_Lattice_Graph_kle} compares CES model predictions 
-to historical data for the $(kl)e$ nesting.
-
-**** Matt: Remove $x$ and $u$ lines. Replace with lines for each nesting. ****
-
-<<CES_GDP_Lattice_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES fitted models with ($kl$)$e$ nesting.">>=
-createCESLatticeGraph(nest="(kl)e")
-@
-
-Figure~\ref{fig:CES_GDP_Lattice_Graph_lek} compares CES model predictions 
-to historical data for the $(le)k$ nesting.
-
-<<CES_GDP_Lattice_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES fitted models with ($le$)$k$ nesting.">>=
-createCESLatticeGraph(nest="(le)k")
-@
-
-Figure~\ref{fig:CES_GDP_Lattice_Graph_ekl} compares CES model predictions 
-to historical data for the $(ek)l$ nesting.
-
-<<CES_GDP_Lattice_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES fitted models with ($ek$)$l$ nesting.">>=
-createCESLatticeGraph(nest="(ek)l")
+Figure~\ref{fig:CES_GDP_Lattice_Graph} compares CES model predictions 
+to historical data for all nestings.
+
+<<CES_GDP_Lattice_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES fitted models.">>=
+createCESLatticeGraph(energyType="Q")
 @
@@
 Figure~\ref{fig:LINEX_GDP_Lattice_Graph} compares LINEX model predictions to historical data.
-**** Remove $x$ and $u$ lines. ****
 
 <<LINEX_GDP_Lattice_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX results.">>=
-createLINEXLatticeGraph()
+createLINEXLatticeGraph(energyType="Q")
 @

### 2013-11-13 EconGrowth2.Rnw
Changed wording on one sentence.
Changed brackets on constraints.

@@
 Equation~\ref{eq:CES} is a degenerate form of Equation~\ref{eq:CESkle} 
-where $\delta \rightarrow 1$ and $\rho \rightarrow -1$.
+where $\delta \rightarrow 1$.
 
@@
 Constraints on the fitting parameters include 
-$\delta_1 \in (0,1)$,
-$\delta \in (0,1)$,
-$\rho_1 \in (-1,0) \cup (0,\infty)$, and
-$\rho \in (-1,0) \cup (0,\infty)$.
+$\delta_1 \in [0,1]$,
+$\delta \in [0,1]$,
+$\rho_1 \in [-1,0] \cup [0,\infty)$, and
+$\rho \in [-1,0] \cup [0,\infty)$.
 

### 2013-11-13 EconGrowth2.Rnw

@@
 $\delta \in [0,1]$,
-$\rho_1 \in [-1,0] \cup [0,\infty)$, and
-$\rho \in [-1,0] \cup [0,\infty)$.
+$\rho_1 \in [-1,0) \cup (0,\infty)$, and
+$\rho \in [-1,0) \cup (0,\infty)$.
 

### 2013-11-17 EconGrowth2.Rnw
Fixed functions to correctly handle energyType=NA.

@@
 for resample models for the Cobb-Douglas model (without energy).
-In Figure~\ref{fig:CD_Scatter_Graph}, 
-$\gamma$ is always 0.0, because energy is not included in this model.
-
-<<CD_Scatter_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (without energy) resample model parameters.">>=
+
+<<CD_Scatter_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (without energy) resample model parameters.
+$\\gamma$ is always 0.0, because energy is not included in this model.">>=
 cdResampleTrianglePlot(energyType=NA)

### 2013-11-17 Econ-Growth-Functions2.R

@@ -1568,7 +1568,7 @@ cobbDouglasData <- function(countryAbbrev, energyType=NA, ...){
     return(df)
   } else if (is.na(energyType)){
     # We want Cobb-Douglas without energy
-    resampledData <- loadResampleData(modelType="cd", countryAbbrev=countryAbbrev)
+    resampledData <- loadResampleData(modelType="cd", countryAbbrev=countryAbbrev, energyType=NA)
   } else {
     # We want Cobb-Douglas with energy
     resampledData <- loadResampleData(modelType="cde", countryAbbrev=countryAbbrev, energyType=energyType)
@@ -2278,7 +2278,7 @@ cesResampleTrianglePlot <- function(energyType, nest, ...){
   # and sends to the graphing function.
   ##
   if (is.na(energyType)){
-    data <- loadAllResampleData(modelType="ces", countryAbbrevsOrder=countryAbbrevsForGraph)
+    data <- loadAllResampleData(modelType="ces", countryAbbrevsOrder=countryAbbrevsForGraph, energyType=NA)
   } else if (energyType == "U"){
     modelType <- paste("cese-", nest, sep="")
     data <- loadAllResampleData(modelType=modelType, 
@@ -2536,7 +2536,7 @@ cesData <- function(countryAbbrev, energyType=NA, nest="(kl)e"){
     return(df)
   } else if (is.na(energyType)){
     # We want CES without energy
-    resampleData <- loadResampleData(modelType="ces", countryAbbrev=countryAbbrev)
+    resampleData <- loadResampleData(modelType="ces", countryAbbrev=countryAbbrev, energyType=NA)
   } else {
     # We want CES with energy  -- might want all three for this later.
     modelType <- paste("cese-", nest, sep="")
@@ -2769,7 +2769,7 @@ cesResamplePlotLambdaGamma <- function(energyType=NA, nest, ...){
   # and sends to the graphing function.
   ##
   if (is.na(energyType)){
-    data <- loadAllResampleData(modelType="ces", countryAbbrevsOrder=countryAbbrevsForGraph)
+    data <- loadAllResampleData(modelType="ces", countryAbbrevsOrder=countryAbbrevsForGraph, energyType=NA)
   } else {
     modelType <- paste("cese-", nest, sep="")
     data <- loadAllResampleData(modelType=modelType, energyType=energyType, 
[…]

### 2013-11-18 EconGrowth2.Rnw
Added graphs of sigma vs. sigma_1 to the paper.

@@
 for the CES model, based on values of $\delta$ and $\delta_1$.
-The following table shows the permuted equations for each CES nesting.
+Table~\ref{tab:CES_abg_equations} shows the permuted equations for each CES nesting.
 
@@
 
-Figure~\ref{fig:CESq_ternary_graph_kl} shows 
+**** Replace Figures~\ref{fig:CES_ternary_graph_kl}--\ref{fig:CESq_ternary_graph_ekl}
+with one plot that shows all 4 nestings. ****
+
+Figure~\ref{fig:CES_ternary_graph_kl} shows 
 $\alpha$, $\beta$, and $\gamma$ parameters from the CES model without energy.
 
-<<CESq_ternary_graph_kl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="CES (without energy) resample model $\\alpha$, $\\beta$, and $\\gamma$ values.">>=
+<<CES_ternary_graph_kl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="CES (without energy) resample model $\\alpha$, $\\beta$, and $\\gamma$ values.">>=
 cesResampleTrianglePlot(energyType=NA)
@@
 
+**** Fix $x$-axis on Figures~\ref{fig:CESq_Sigma_Sigma_1_kle}--\ref{fig:CESq_Sigma_Sigma_1_ekl}.
+Or, consider a better way to show resampled $\sigma$ and $\sigma_1$ values. ****
+
+Figure~\ref{fig:CESq_Sigma_Sigma_1_kle} shows 
+$\sigma$ and $\sigma_1$ values from the CES model with ($kl$)$e$ nesting.
+
+<<CESq_Sigma_Sigma_1_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="CES (with energy) resample model $\\sigma$ and $\\sigma_1$ values, ($kl$)$e$ nesting.">>=
+cesResamplePlotSigmaSigma_1(energyType="Q", nest="(kl)e")
+@
+
+Figure~\ref{fig:CESq_Sigma_Sigma_1_lek} shows 
+$\sigma$ and $\sigma_1$ values from the CES model with ($le$)$k$ nesting.
+
+<<CESq_Sigma_Sigma_1_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="CES (with energy) resample model $\\sigma$ and $\\sigma_1$ values, ($le$)$k$ nesting.">>=
+cesResamplePlotSigmaSigma_1(energyType="Q", nest="(le)k")
+@
+
+Figure~\ref{fig:CESq_Sigma_Sigma_1_ekl} shows 
+$\sigma$ and $\sigma_1$ values from the CES model with ($ek$)$l$ nesting.
+
+<<CESq_Sigma_Sigma_1_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="CES (with energy) resample model $\\sigma$ and $\\sigma_1$ values, ($ek$)$l$ nesting.">>=
+cesResamplePlotSigmaSigma_1(energyType="Q", nest="(ek)l")
+@
+
 Figure~\ref{fig:CES_GDP_Lattice_Graph} compares CES model predictions 
 to historical data for all nestings.
+
+**** Replace Figure~\ref{fig:CES_GDP_Lattice_Graph} with four graphs that show
+the range of predictions from resamples with each nesting. ****
 

### 2013-11-22 EconGrowth2.Rnw
Added CES spaghetti graphs.

@@
 
-**** Replace Figure~\ref{fig:CES_GDP_Lattice_Graph} with four graphs that show
-the range of predictions from resamples with each nesting. ****
-
 <<CES_GDP_Lattice_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES fitted models.">>=
 createCESLatticeGraph(energyType="Q")
+@
+
+The resample model predictions for each nesting 
+in Figure~\ref{fig:CES_GDP_Lattice_Graph} can be shown as gray lines 
+beneath superimposed on the historical data as shown
+in Figures~\ref{fig:CES_Spaghetti_Graph_kl}--\ref{fig:CES_Spaghetti_Graph_ekl}. 
+Figure~\ref{fig:CES_Spaghetti_Graph_kl} shows CES model resample predictions
+for the ($kl$) nesting (without energy).
+
+<<CES_Spaghetti_Graph_kl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Graph of CES resample model indexed GDP predictions for the ($kl$) nesting (without energy).
+Only 50 resample models are shown.
+**** Need to change the order of the countries to correspond to countryAbbrevsForGraph.
+Need to plot historical data as open circles instead of red lines.
+****">>=
+createCESSpaghettiGraph(energyType=NA)
+@
+
+Figure~\ref{fig:CES_Spaghetti_Graph_kle} shows CES model 
+resample predictions for the ($kl$)$e$ nesting.
+
+<<CES_Spaghetti_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Graph of CES resample model indexed GDP predictions for the ($kl$)$e$ nesting (with energy).
+Only 50 resample models are shown.
+**** Need to change the order of the countries to correspond to countryAbbrevsForGraph.
+Need to plot historical data as open circles instead of red lines.
+****">>=
+createCESSpaghettiGraph(energyType="Q", nest="(kl)e")
+@
+
+<<CES_Spaghetti_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Graph of CES resample model indexed GDP predictions for the ($le$)$k$ nesting (with energy).
+Only 50 resample models are shown.
+**** Need to change the order of the countries to correspond to countryAbbrevsForGraph.
+Need to plot historical data as open circles instead of red lines.
+****">>=
+createCESSpaghettiGraph(energyType="Q", nest="(le)k")
+@
+
+<<CES_Spaghetti_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Graph of CES resample model indexed GDP predictions for the ($ek$)$l$ nesting (with energy).
+Only 50 resample models are shown.
+**** Need to change the order of the countries to correspond to countryAbbrevsForGraph.
+Need to plot historical data as open circles instead of red lines.
+****">>=
+createCESSpaghettiGraph(energyType="Q", nest="(ek)l")
+
 @

### 2013-11-26 EconGrowth2.Rnw
Added commented lines for creating the CES Spaghetti graphs from archive data.

--- 2013-11-18 EconGrowth2.Rnw
@@
 
-**** Replace Figure~\ref{fig:CES_GDP_Lattice_Graph} with four graphs that show
-the range of predictions from resamples with each nesting. ****
-
 <<CES_GDP_Lattice_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES fitted models.">>=
 createCESLatticeGraph(energyType="Q")
+@
+
+The resample model predictions for each nesting 
+in Figure~\ref{fig:CES_GDP_Lattice_Graph} can be shown as gray lines 
+beneath superimposed on the historical data as shown
+in Figures~\ref{fig:CES_Spaghetti_Graph_kl}--\ref{fig:CES_Spaghetti_Graph_ekl}. 
+Figure~\ref{fig:CES_Spaghetti_Graph_kl} shows CES model resample predictions
+for the ($kl$) nesting (without energy).
+
+<<CES_Spaghetti_Graph_kl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Indexed GDP predictions for 1000 CES resample models for the ($kl$) nesting (without energy).
+**** Need to change the order of the countries to correspond to countryAbbrevsForGraph.
+Need to plot historical data as open circles instead of red lines.
+****">>=
+# createCESSpaghettiGraph(energyType=NA, archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
+# createCESSpaghettiGraph(energyType=NA, archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
+createCESSpaghettiGraph(energyType=NA)
+@
+
+Figure~\ref{fig:CES_Spaghetti_Graph_kle} shows CES model 
+resample predictions for the ($kl$)$e$ nesting.
+
+<<CES_Spaghetti_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Indexed GDP predictions for 1000 CES resample models for the ($kl$)$e$ nesting (with energy).
+Only 50 resample models are shown.
+**** Need to change the order of the countries to correspond to countryAbbrevsForGraph.
+Need to plot historical data as open circles instead of red lines.
+****">>=
+# createCESSpaghettiGraph(energyType="Q", nest="(kl)e", archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
+# createCESSpaghettiGraph(energyType="Q", nest="(kl)e", archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
+createCESSpaghettiGraph(energyType="Q", nest="(kl)e")
+@
+
+<<CES_Spaghetti_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Indexed GDP predictions for 1000 CES resample models for the ($le$)$k$ nesting (with energy).
+**** Need to change the order of the countries to correspond to countryAbbrevsForGraph.
+Need to plot historical data as open circles instead of red lines.
+****">>=
+# createCESSpaghettiGraph(energyType="Q", nest="(le)k", archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
+# createCESSpaghettiGraph(energyType="Q", nest="(le)k", archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
+createCESSpaghettiGraph(energyType="Q", nest="(le)k")
+@
+
+<<CES_Spaghetti_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Indexed GDP predictions for 1000 CES resample models for the ($ek$)$l$ nesting (with energy).
+**** Need to change the order of the countries to correspond to countryAbbrevsForGraph.
+Need to plot historical data as open circles instead of red lines.
+****">>=
+# createCESSpaghettiGraph(energyType="Q", nest="(ek)Le", archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
+# createCESSpaghettiGraph(energyType="Q", nest="(ek)l", archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
+createCESSpaghettiGraph(energyType="Q", nest="(ek)l")
 @

### 2013-11-26 EconGrowth2.Rnw
Added commented options for gathering CES spaghetti data from different archives.

@@
 Need to plot historical data as open circles instead of red lines.
+Need to plot fit to historical data as a red line.
 ****">>=
-# createCESSpaghettiGraph(energyType=NA, archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
+createCESSpaghettiGraph(energyType=NA, archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
 # createCESSpaghettiGraph(energyType=NA, archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
-createCESSpaghettiGraph(energyType=NA)
+# createCESSpaghettiGraph(energyType=NA)
 @
@@
 <<CES_Spaghetti_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Indexed GDP predictions for 1000 CES resample models for the ($kl$)$e$ nesting (with energy).
-Only 50 resample models are shown.
 **** Need to change the order of the countries to correspond to countryAbbrevsForGraph.
 Need to plot historical data as open circles instead of red lines.
+Need to plot fit to historical data as a red line.
 ****">>=
-# createCESSpaghettiGraph(energyType="Q", nest="(kl)e", archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
+createCESSpaghettiGraph(energyType="Q", nest="(kl)e", archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
 # createCESSpaghettiGraph(energyType="Q", nest="(kl)e", archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
-createCESSpaghettiGraph(energyType="Q", nest="(kl)e")
+# createCESSpaghettiGraph(energyType="Q", nest="(kl)e")
 @
@@
 Need to plot historical data as open circles instead of red lines.
+Need to plot fit to historical data as a red line.
 ****">>=
-# createCESSpaghettiGraph(energyType="Q", nest="(le)k", archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
+createCESSpaghettiGraph(energyType="Q", nest="(le)k", archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
 # createCESSpaghettiGraph(energyType="Q", nest="(le)k", archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
-createCESSpaghettiGraph(energyType="Q", nest="(le)k")
+# createCESSpaghettiGraph(energyType="Q", nest="(le)k")
 @
@@
 Need to plot historical data as open circles instead of red lines.
+Need to plot fit to historical data as a red line.
 ****">>=
-# createCESSpaghettiGraph(energyType="Q", nest="(ek)Le", archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
+createCESSpaghettiGraph(energyType="Q", nest="(ek)Le", archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
 # createCESSpaghettiGraph(energyType="Q", nest="(ek)l", archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
-createCESSpaghettiGraph(energyType="Q", nest="(ek)l")
+# createCESSpaghettiGraph(energyType="Q", nest="(ek)l")
 @

### 2013-11-26 EconGrowth2.Rnw
CES spaghetti graph sections now use the data argument instead of the energy and nest arguments.

@@
 Need to plot fit to historical data as a red line.
+Change vertical axis limits: China 1-10, all others 1-4.
 ****">>=
-createCESSpaghettiGraph(energyType=NA, archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
-# createCESSpaghettiGraph(energyType=NA, archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
-# createCESSpaghettiGraph(energyType=NA)
+# For the data currently in the data_resample directory:
+# data <- loadCESSpaghettiGraphData(energyType=NA)
+# For the data in the n=50 archive:
+data <- loadCESSpaghettiGraphData(energyType=NA, 
+                                  archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
+# For the data in the n=1000 archive:
+# data <- loadCESSpaghettiGraphData(energyType=NA, 
+#               archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
+createCESSpaghettiGraph(data=data)
 @
@@
 Need to plot fit to historical data as a red line.
+Change vertical axis limits: China 1-10, all others 1-4.
 ****">>=
-createCESSpaghettiGraph(energyType="Q", nest="(kl)e", archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
-# createCESSpaghettiGraph(energyType="Q", nest="(kl)e", archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
-# createCESSpaghettiGraph(energyType="Q", nest="(kl)e")
+# For the data currently in the data_resample directory:
+# data <- loadCESSpaghettiGraphData(energyType="Q", nest="(kl)e")
+# For the data in the n=50 archive:
+data <- loadCESSpaghettiGraphData(energyType="Q", nest="(kl)e", 
+                                  archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
+# For the data in the n=1000 archive:
+# data <- loadCESSpaghettiGraphData(energyType="Q", nest="(kl)e",
+#               archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
+createCESSpaghettiGraph(data=data)
 @
@@
 Need to plot fit to historical data as a red line.
+Change vertical axis limits: China 1-10, all others 1-4.
 ****">>=
-createCESSpaghettiGraph(energyType="Q", nest="(le)k", archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
-# createCESSpaghettiGraph(energyType="Q", nest="(le)k", archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
-# createCESSpaghettiGraph(energyType="Q", nest="(le)k")
+# For the data currently in the data_resample directory:
+# data <- loadCESSpaghettiGraphData(energyType="Q", nest="(le)k")
+# For the data in the n=50 archive:
+data <- loadCESSpaghettiGraphData(energyType="Q", nest="(le)k", 
+                                  archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
+# For the data in the n=1000 archive:
+# data <- loadCESSpaghettiGraphData(energyType="Q", nest="(le)k",
+#               archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
+createCESSpaghettiGraph(data=data)
 @
@@
 Need to plot fit to historical data as a red line.
+Change vertical axis limits: China 1-10, all others 1-4.
 ****">>=
-createCESSpaghettiGraph(energyType="Q", nest="(ek)Le", archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
-# createCESSpaghettiGraph(energyType="Q", nest="(ek)l", archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
-# createCESSpaghettiGraph(energyType="Q", nest="(ek)l")
+# For the data currently in the data_resample directory:
+# data <- loadCESSpaghettiGraphData(energyType="Q", nest="(ek)l")
+# For the data in the n=50 archive:
+data <- loadCESSpaghettiGraphData(energyType="Q", nest="(ek)l", 
+                                  archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
+# For the data in the n=1000 archive:
+# data <- loadCESSpaghettiGraphData(energyType="Q", nest="(ek)l",
+#               archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
+createCESSpaghettiGraph(data=data)
 @

### 2013-12-07 EconGrowth2.Rnw
createCESSpaghettiGraph renamed to cesSpaghettiGraph

--- 2013-11-26 EconGrowth2.Rnw
@@
 Need to plot fit to historical data as a red line.
+Change vertical axis limits: China 1-10, all others 1-4.
 ****">>=
-createCESSpaghettiGraph(energyType=NA, archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
-# createCESSpaghettiGraph(energyType=NA, archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
-# createCESSpaghettiGraph(energyType=NA)
+# For the data currently in the data_resample directory:
+# data <- loadCESSpaghettiGraphData(energyType=NA)
+# For the data in the n=50 archive:
+data <- loadCESSpaghettiGraphData(energyType=NA, 
+                                  archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
+# For the data in the n=1000 archive:
+# data <- loadCESSpaghettiGraphData(energyType=NA, 
+#               archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
+cesSpaghettiGraph(data=data)
 @
@@
 Need to plot fit to historical data as a red line.
+Change vertical axis limits: China 1-10, all others 1-4.
 ****">>=
-createCESSpaghettiGraph(energyType="Q", nest="(kl)e", archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
-# createCESSpaghettiGraph(energyType="Q", nest="(kl)e", archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
-# createCESSpaghettiGraph(energyType="Q", nest="(kl)e")
+# For the data currently in the data_resample directory:
+# data <- loadCESSpaghettiGraphData(energyType="Q", nest="(kl)e")
+# For the data in the n=50 archive:
+data <- loadCESSpaghettiGraphData(energyType="Q", nest="(kl)e", 
+                                  archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
+# For the data in the n=1000 archive:
+# data <- loadCESSpaghettiGraphData(energyType="Q", nest="(kl)e",
+#               archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
+cesSpaghettiGraph(data=data)
 @
@@
 Need to plot fit to historical data as a red line.
+Change vertical axis limits: China 1-10, all others 1-4.
 ****">>=
-createCESSpaghettiGraph(energyType="Q", nest="(le)k", archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
-# createCESSpaghettiGraph(energyType="Q", nest="(le)k", archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
-# createCESSpaghettiGraph(energyType="Q", nest="(le)k")
+# For the data currently in the data_resample directory:
+# data <- loadCESSpaghettiGraphData(energyType="Q", nest="(le)k")
+# For the data in the n=50 archive:
+data <- loadCESSpaghettiGraphData(energyType="Q", nest="(le)k", 
+                                  archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
+# For the data in the n=1000 archive:
+# data <- loadCESSpaghettiGraphData(energyType="Q", nest="(le)k",
+#               archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
+cesSpaghettiGraph(data=data)
 @
@@
 Need to plot fit to historical data as a red line.
+Change vertical axis limits: China 1-10, all others 1-4.
 ****">>=
-createCESSpaghettiGraph(energyType="Q", nest="(ek)Le", archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
-# createCESSpaghettiGraph(energyType="Q", nest="(ek)l", archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
-# createCESSpaghettiGraph(energyType="Q", nest="(ek)l")
+# For the data currently in the data_resample directory:
+# data <- loadCESSpaghettiGraphData(energyType="Q", nest="(ek)l")
+# For the data in the n=50 archive:
+data <- loadCESSpaghettiGraphData(energyType="Q", nest="(ek)l", 
+                                  archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
+# For the data in the n=1000 archive:
+# data <- loadCESSpaghettiGraphData(energyType="Q", nest="(ek)l",
+#               archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
+cesSpaghettiGraph(data=data)
 @

### 2013-12-07 Econ-Growth-Functions2.R

@@ -2822,7 +2822,7 @@ cesResamplePlotSigmaSigma_1 <- function(energyType="Q", nest="(kl)e", ...){
   return(graph)
 }
 
-createCESSpaghettiGraph <- function(energyType, 
+cesSpaghettiGraph <- function(energyType, 
                                     nest, 
                                     data=loadCESSpaghettiGraphData(energyType=energyType, 
                                                                    nest=nest, ...), 
@@ -2835,7 +2835,7 @@ createCESSpaghettiGraph <- function(energyType,
   # For example:
   # data <- loadCESSpaghettiGraphData(energyType="Q", nest="(kl)e", 
   #         archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
-  # createCESSpaghettiGraph(data=data)
+  # cesSpaghettiGraph(data=data)
   ##
   
   #

### 2013-12-12 EconGrowth2.Rnw
Now using 36-panel graph for CES alpha, beta, and gamma.

@@
 
-Figure~\ref{fig:CES_ternary_graph_kl} shows 
-$\alpha$, $\beta$, and $\gamma$ parameters from the CES model without energy.
-
-<<CES_ternary_graph_kl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="CES (without energy) resample model $\\alpha$, $\\beta$, and $\\gamma$ values.">>=
-cesResampleTrianglePlot(energyType=NA)
-@
-
-Figure~\ref{fig:CESq_ternary_graph_kle} shows 
-$\alpha$, $\beta$, and $\gamma$ parameters from the CES model with ($kl$)$e$ nesting.
-
-<<CESq_ternary_graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="CES (with energy) resample model $\\alpha$, $\\beta$, and $\\gamma$ values, ($kl$)$e$ nesting.">>=
-cesResampleTrianglePlot(energyType="Q", nest="(kl)e")
-@
-
-Figure~\ref{fig:CESq_ternary_graph_lek} shows 
-$\alpha$, $\beta$, and $\gamma$ parameters from the CES model with ($kl$)$e$ nesting.
-
-<<CESq_ternary_graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="CES (with energy) resample model $\\alpha$, $\\beta$, and $\\gamma$ values, ($le$)$k$ nesting.">>=
-cesResampleTrianglePlot(energyType="Q", nest="(le)k")
-@
-
-Figure~\ref{fig:CESq_ternary_graph_ekl} shows 
-$\alpha$, $\beta$, and $\gamma$ parameters from the CES model with ($kl$)$e$ nesting.
-
-<<CESq_ternary_graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="CES (with energy) resample model $\\alpha$, $\\beta$, and $\\gamma$ values, ($ek$)$l$ nesting.">>=
-cesResampleTrianglePlot(energyType="Q", nest="(ek)l")
+Figure~\ref{fig:CES_ternary_graph} shows 
+$\alpha$, $\beta$, and $\gamma$ parameters for the CES model for all nests and countries.
+
+<<CES_ternary_graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelTernaryGraphHeight, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models.">>=
+cesResampleTrianglePlot(energyType="Q", nest="all")
 @

### 2013-12-12 EconGrowth2.Rnw
Now incorporating the CES spaghetti graph in the paper.

@@
 
-Figure~\ref{fig:CES_GDP_Lattice_Graph} compares CES model predictions 
+Figure~\ref{fig:CES_Spaghetti_Graph} compares CES model predictions 
 to historical data for all nestings. 
-
-<<CES_GDP_Lattice_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES fitted models.">>=
-createCESLatticeGraph(energyType="Q")
-@
-
-The resample model predictions for each nesting 
-in Figure~\ref{fig:CES_GDP_Lattice_Graph} can be shown as gray lines 
-beneath superimposed on the historical data as shown
-in Figures~\ref{fig:CES_Spaghetti_Graph_kl}--\ref{fig:CES_Spaghetti_Graph_ekl}. 
-Figure~\ref{fig:CES_Spaghetti_Graph_kl} shows CES model resample predictions
-for the ($kl$) nesting (without energy).
-
-<<CES_Spaghetti_Graph_kl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Indexed GDP predictions for 1000 CES resample models for the ($kl$) nesting (without energy).
-**** Need to change the order of the countries to correspond to countryAbbrevsForGraph.
-Need to plot historical data as open circles instead of red lines.
-Need to plot fit to historical data as a red line.
-Change vertical axis limits: China 1-10, all others 1-4.
-****">>=
-# For the data currently in the data_resample directory:
-# data <- loadCESSpaghettiGraphData(energyType=NA)
-# For the data in the n=50 archive:
-data <- loadCESSpaghettiGraphData(energyType=NA, 
-                                  archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
-# For the data in the n=1000 archive:
-# data <- loadCESSpaghettiGraphData(energyType=NA, 
-#               archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
-cesSpaghettiGraph(data=data)
-@
-
-Figure~\ref{fig:CES_Spaghetti_Graph_kle} shows CES model 
-resample predictions for the ($kl$)$e$ nesting.
-
-<<CES_Spaghetti_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Indexed GDP predictions for 1000 CES resample models for the ($kl$)$e$ nesting (with energy).
-**** Need to change the order of the countries to correspond to countryAbbrevsForGraph.
-Need to plot historical data as open circles instead of red lines.
-Need to plot fit to historical data as a red line.
-Change vertical axis limits: China 1-10, all others 1-4.
-****">>=
-# For the data currently in the data_resample directory:
-# data <- loadCESSpaghettiGraphData(energyType="Q", nest="(kl)e")
-# For the data in the n=50 archive:
-data <- loadCESSpaghettiGraphData(energyType="Q", nest="(kl)e", 
-                                  archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
-# For the data in the n=1000 archive:
-# data <- loadCESSpaghettiGraphData(energyType="Q", nest="(kl)e",
-#               archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
-cesSpaghettiGraph(data=data)
-@
-
-<<CES_Spaghetti_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Indexed GDP predictions for 1000 CES resample models for the ($le$)$k$ nesting (with energy).
-**** Need to change the order of the countries to correspond to countryAbbrevsForGraph.
-Need to plot historical data as open circles instead of red lines.
-Need to plot fit to historical data as a red line.
-Change vertical axis limits: China 1-10, all others 1-4.
-****">>=
-# For the data currently in the data_resample directory:
-# data <- loadCESSpaghettiGraphData(energyType="Q", nest="(le)k")
-# For the data in the n=50 archive:
-data <- loadCESSpaghettiGraphData(energyType="Q", nest="(le)k", 
-                                  archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
-# For the data in the n=1000 archive:
-# data <- loadCESSpaghettiGraphData(energyType="Q", nest="(le)k",
-#               archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
-cesSpaghettiGraph(data=data)
-@
-
-<<CES_Spaghetti_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Indexed GDP predictions for 1000 CES resample models for the ($ek$)$l$ nesting (with energy).
-**** Need to change the order of the countries to correspond to countryAbbrevsForGraph.
-Need to plot historical data as open circles instead of red lines.
-Need to plot fit to historical data as a red line.
-Change vertical axis limits: China 1-10, all others 1-4.
-****">>=
-# For the data currently in the data_resample directory:
-# data <- loadCESSpaghettiGraphData(energyType="Q", nest="(ek)l")
-# For the data in the n=50 archive:
-data <- loadCESSpaghettiGraphData(energyType="Q", nest="(ek)l", 
-                                  archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
-# For the data in the n=1000 archive:
-# data <- loadCESSpaghettiGraphData(energyType="Q", nest="(ek)l",
-#               archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
-cesSpaghettiGraph(data=data)
+Historical data are shown as open circles. 
+The fit to historical data is shown as a dashed line. 
+The gray band beneath the historical data shows the spread of predictions for 1000 resamples.
+
+<<CES_Spaghetti_Graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelSpaghettiGraphHeight, fig.cap="CES fitted models.">>=
+cesSpaghettiGraph(nest="all", energyType="Q")
 @

### 2013-12-12 EconGrowth2.Rnw
Now including a single Zambia CES spaghetti graph in the paper.

@@
 <<CES_Spaghetti_Graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelSpaghettiGraphHeight, fig.cap="CES fitted models.">>=
-cesSpaghettiGraph(nest="all", energyType="Q")
+spagData <- loadCESSpaghettiGraphData(energyType="Q", nest="all")
+cesSpaghettiGraph(data=spagData, level=1)
+@
+
+Figure~\ref{fig:CES_Spaghetti_Graph_ZM} shows details of the resample fits for Zambia with the (kl)e nesting.
+
+<<CES_Spaghetti_Graph_ZM, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES fitted models for Zambia with the (kl)e nesting.">>=
+cesSpaghettiGraph(data=subset(spagData, Country=="ZM" & nest=="(kl)e"), level=1)
 @

### 2013-12-15 EconGrowth2.Rnw
Removed notes about x and u.

@@
 
-<<Historical_Lattice_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$).">>=
+<<Historical_Lattice_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), and thermal energy ($q$).">>=
 createHistoricalLatticeGraph()

### 2013-12-15 EconGrowth2.Rnw
energyType=NA is no longer accepted. Use energyType="none".

@@
 $\\gamma$ is always 0.0, because energy is not included in this model.">>=
-cdResampleTrianglePlot(energyType=NA)
+cdResampleTrianglePlot(energyType="none")
 @
@@
 <<CES_lambda_gamma_Scatter_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\lambda$ and $\\gamma$.">>=
-cesResamplePlotLambdaGamma(energyType=NA)
+cesResamplePlotLambdaGamma(energyType="none")
 @
@@
 <<CES_sigma_1_delta_1_Scatter_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
-cesResamplePlotSigma_1Delta_1(energyType=NA)
+cesResamplePlotSigma_1Delta_1(energyType="none")
 @
@@
 <<CD_Params_Table, results='asis'>>=
-printCDParamsTable(energyType=NA)    #Without energy
+printCDParamsTable(energyType="none")    #Without energy
 @
@@
 Vertical bars indicate 95\\% confidence intervals.">>=
-createCDParamsGraph(energyType=NA)
+createCDParamsGraph(energyType="none")
 @
@@
 <<CES_Params_Table, results='asis'>>=
-printCESParamsTableA(energyType=NA)
-printCESParamsTableB(energyType=NA)
+printCESParamsTableA(energyType="none")
+printCESParamsTableB(energyType="none")
 @
@@
 Vertical bars indicate 95\\% confidence intervals.">>=
-createCESParamsGraph(energyType=NA)
+createCESParamsGraph(energyType="none")
 @

### 2013-12-15 Econ-Growth-Functions2.R

@@ -157,7 +157,7 @@ haveDataCD <- function(countryAbbrev, energyType){
     # If we don't know the country, we don't have data
     return(FALSE)
   }
-  if (is.na(energyType)){
+  if (energyType == "none"){
     # If we don't want energy included, we have data for all known countries. We need to check this case
     # first, BEFORE doing various checks on the energyType.
     return(TRUE)
@@ -1579,7 +1579,7 @@ cobbDouglasData <- function(countryAbbrev, energyType="none", ...){
   }
   statisticalProperties <- cdResampleCoeffProps(resampledData)
   # Set the correct label in the row that shows the base values.
-  if (is.na(energyType)){
+  if (energyType == "none"){
     rownames(statisticalProperties) <- c("+95% CI", "CD", "-95% CI")
   } else {
     rownames(statisticalProperties) <- c("+95% CI", "CDe", "-95% CI")
@@ -1689,7 +1689,7 @@ cobbDouglasCountryRow <- function(countryAbbrev, energyType){
   # Creates a row for the Cobb Douglas parameters table for the given country (2-letter code) and energyType (Q, X, or U)
   ##
   dataCD <- cobbDouglasData(countryAbbrev, energyType)
-  if (is.na(energyType)){
+  if (energyType == "none"){
     out <- cbind(dataCD["-95% CI", "lambda"], dataCD["CD", "lambda"], dataCD["+95% CI", "lambda"],
                  dataCD["-95% CI", "alpha"],  dataCD["CD", "alpha"],  dataCD["+95% CI", "alpha"],
                  dataCD["-95% CI", "beta"],   dataCD["CD", "beta"],   dataCD["+95% CI", "beta"])
@@ -1736,7 +1736,7 @@ cobbDouglasCountryRowsForParamsGraph <- function(countryAbbrev, energyType){
                         lowerCI = dataCD["-95% CI", "beta"],
                         value = dataCD[valueRow, "beta"], 
                         upperCI = dataCD["+95% CI", "beta"])
-  if (is.na(energyType)){
+  if (energyType == "none"){
     table <- rbind(lambdaRow, alphaRow, betaRow)
   } else {
     gammaRow <- data.frame(country = countryAbbrev, 
@@ -1989,7 +1989,7 @@ cdResampleTrianglePlot <- function(energyType, ...){
 }
 
 cesModel2 <- function(countryAbbrev, 
-                      energyType=NA, 
+                      energyType="none", 
[…]

### 2013-12-29 EconGrowth2.Rnw
Edited description of resample to include reindexing.

@@
 Under that assumption, it would not be surprising if the residual from 
-any one year had been observed in a different year. 
-By applying randomly selected residuals (with randomly selected signs)
-to model predictions at each year of the GDP time series, we create a resampled
-GDP time series ($y_{resample,t}$) that can be fitted using the techniques
+any particular year had been observed in a different year. 
+By applying randomly selected residuals [$\mathrm{abs}(\mathrm{rand}(r_t))$]
+with randomly selected signs [$\mathrm{rand}(-1, 1)$]
+to model predictions, we create a 
+preliminary resampled GDP time series ($y_{prelim,resample,t}$):
+
+\begin{equation} \label{eq:resample_y_prelim}
+  y_{prelim,resample,t} = y_{pred,t} + \mathrm{rand}(-1, 1) \cdot \mathrm{abs}(\mathrm{rand}(r_t)).
+\end{equation}
+
+\noindent{}The preliminary resample time series
+can have non-unity first-year GDP ($y_{prelim,resample,0} \ne 1$).
+If we had actually obtained the resampled GDP data series,
+we would have indexed to a different first-year GDP value, 
+such that \emph{every} resampled GDP time series starts with $y_{resample,0} = 1$.
+We use
+
+\begin{equation} \label{eq:resample_y}
+  y_{resample,t} = \frac{y_{prelim,resample,t}}{y_{prelim,resample,0}}
+\end{equation}
+
+\noindent{}to obtain a resampled indexed GDP time series that can be fitted using the techniques
 described below. 
-
-\begin{equation} \label{eq:resample_y}
-  y_{resample,t} = y_{pred,t} + \mathrm{rand}(-1, 1) \cdot \mathrm{abs}(\mathrm{rand}(r_t))
-\end{equation}
-
 We repeated the resampling process \Sexpr{numResamples()} times for each
-combination of growth model, energy quantification, and country.
+combination of growth model and country, both with and without energy when appropriate.
 
@@
 
-It is important to note that large residuals can arise from 
+It is important to note that large residuals can arise from either
 (a) poor quality historical time series data ($y_{act}$) or 
 (b) a mathematical model that does not describe the underlying phenomena well.
-In either case, we would not want to claim precise knowledge of the 
+In both cases, we would not want to claim precise knowledge of the 
 fitted coefficients for an economic growth model. 
-The resampling technique that we employed
-provides looser coefficient distributions when either of the above
-is true. After discussing the fitting technique for each 
+So, it is appropriate that the resampling technique that we employed
+provides looser coefficient distributions when either (a) or (b) above
+is true. 
+After discussing the fitting technique for each 
 growth model below, we show scatter plots of fitted coefficients,
@@
 If the fitted value for $a$ ($b$) fell outside $[0,1]$, it was 
-set equal to its boundary value and $\lambda$ and $b$ ($a$) 
+set equal to its boundary value and both $\lambda$ and $b$ ($a$) 
 were re-estimated.
@@
 (with and without energy) to historical data.
+
+**** Replace with a spaghetti graph? Countries in rows. Without energy and with energy in columns. ****
 

### 2013-12-30 EconGrowth.Rnw
dealing with CD triplots and related issues

@@
 <<CD_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (without energy) resample model parameters.">>=
-cdResampleTrianglePlot(energyType=NA)
+cdResampleTrianglePlot(energyType=NA, facet_formula = ~ countryAbbrev)
 @
@@
 <<CDq_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (with $q$) resample model parameters.">>=
-cdResampleTrianglePlot(energyType="Q")
+cdResampleTrianglePlot(energyType="Q", facet_formula = NULL) + facet_wrap( ~ countryAbbrev )
 @
@@
 <<CDx_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (with $x$) resample model parameters.">>=
-cdResampleTrianglePlot(energyType="X")
+cdResampleTrianglePlot(energyType="X", facet_formula=NULL) + facet_wrap( ~ countryAbbrev )
 @
@@
 <<CDu_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=threePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (with $u$) resample model parameters.">>=
-cdResampleTrianglePlot(energyType="U")
+cdResampleTrianglePlot(energyType="U", facet_formula=NULL) + facet_wrap( ~ countryAbbrev )
 @

### 2013-12-30 EconGrowth2.Rnw
Deleted a non-applicable note about the faceted ternary graphs.
dealing with CD triplots and related issues

@@
 options(show.signif.stars=TRUE)
+require(knitr)
 opts_chunk$set(
@@
 $\\gamma$ is always 0.0, because energy is not included in this model.">>=
-cdResampleTrianglePlot(energyType="none")
+cdResampleTrianglePlot(energyType="none", facet_formula= ~countryAbbrev )
 @
@@
 <<CDq_Scatter_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (with energy) resample model parameters.">>=
-cdResampleTrianglePlot(energyType="Q")
+cdResampleTrianglePlot(energyType="Q", facet_formala=~countryAbbrev)
 @
@@
 \end{table}
-
-**** Replace Figures~\ref{fig:CES_ternary_graph_kl}--\ref{fig:CESq_ternary_graph_ekl}
-with one plot that shows all 4 nestings. ****
 

### 2013-12-30 Econ-Growth-Functions2.R

@@ -144,7 +144,7 @@ haveDataSF <- function(countryAbbrev, factor){
   return(TRUE)
 }
 
-haveDataCD <- function(countryAbbrev, energyType){
+haveDataCD <- function(countryAbbrev, energyType="none"){
   ###############################
   # Tells whether we have data for this combination of country and energy type for a Cobb-Douglas curve fit.
   # a missing energyType or energyType == NA means that we want to develop a model without energy, if possible.
@@ -173,7 +173,7 @@ haveDataCD <- function(countryAbbrev, energyType){
   return(TRUE)
 }
 
-haveDataCES <- function(countryAbbrev, energyType){
+haveDataCES <- function(countryAbbrev, energyType="none"){
   ###############################
   # Tells whether we have data for this combination of country and energy type for a CES curve fit.
   # a missing energyType or energyType == NA means that we want to develop a model without energy, if possible.
@@ -184,7 +184,7 @@ haveDataCES <- function(countryAbbrev, energyType){
   return(haveDataCD(countryAbbrev, energyType))
 }
 
-haveDataLINEX <- function(countryAbbrev, energyType){
+haveDataLINEX <- function(countryAbbrev, energyType="none"){
   ###############################
   # Tells whether we have data for this combination of country and energy type for a LINEX curve fit.
   # a missing energyType or energyType == NA means that we want to develop a model without energy, if possible.
@@ -1533,7 +1533,7 @@ cobbDouglasPredictions <- function(countryAbbrev, energyType){
   return(df)
 }
 
-cobbDouglasPredictionsColumn <- function(energyType){
+cobbDouglasPredictionsColumn <- function(energyType="none"){
   #########################
   # Takes the Cobb-Douglas fitted models and creates a single column of predicted GDP values
   # that corresponds, row for row, with the AllData.txt file.
@@ -1587,7 +1587,7 @@ cobbDouglasData <- function(countryAbbrev, energyType="none", ...){
   return(statisticalProperties)
 }
 
-loadCDSpaghettiGraphData <- function(energyType, archive=NULL){
+loadCDSpaghettiGraphData <- function(energyType="none", archive=NULL){
   ################################
   # Creates a data frame containing historical data, the fit to historical data, and 
   # resample predictions for Cobb-Douglas models.
@@ -1684,7 +1684,7 @@ loadCDSpaghettiGraphData <- function(energyType, archive=NULL){
[…]

### 2013-12-30 EconGrowth2.Rnw
typo fix

@@
 $\\gamma$ is always 0.0, because energy is not included in this model.">>=
-cdResampleTrianglePlot(energyType="none", facet_formula= ~countryAbbrev )
+cdResampleTrianglePlot(energyType="none", facet_formula=~countryAbbrev )
 @
@@
 <<CDq_Scatter_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (with energy) resample model parameters.">>=
-cdResampleTrianglePlot(energyType="Q", facet_formala=~countryAbbrev)
+cdResampleTrianglePlot(energyType="Q", facet_formula=~countryAbbrev)
 @

### 2013-12-30 EconGrowth.Rnw
energyType:  NA -> "none"

@@
 <<CD_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (without energy) resample model parameters.">>=
-cdResampleTrianglePlot(energyType=NA, facet_formula = ~ countryAbbrev)
+cdResampleTrianglePlot(energyType="none", facet_formula = ~countryAbbrev)
 @
@@
 <<CES_lambda_gamma_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\lambda$ and $\\gamma$.">>=
-cesResamplePlotLambdaGamma(energyType=NA)
+cesResamplePlotLambdaGamma(energyType="none")
 @
@@
 <<CES_sigma_1_delta_1_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
-cesResamplePlotSigma_1Delta_1(energyType=NA)
+cesResamplePlotSigma_1Delta_1(energyType="none")
 @
@@
 <<CES_sigma_delta_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\rho$ and $\\delta$.">>=
-cesResamplePlotSigmaDelta(energyType=NA)
+cesResamplePlotSigmaDelta(energyType="none")
 @
@@
 <<CD_Params_Table, results='asis'>>=
-printCDParamsTable(energyType=NA)    #Without energy
+printCDParamsTable(energyType="none")    #Without energy
 printCDParamsTable(energyType="Q"); printCDParamsTable(energyType="X"); printCDParamsTable(energyType="U") #With energy
@@
 <<CES_Params_Table, results='asis'>>=
-printCESParamsTableA(energyType=NA);  printCESParamsTableB(energyType=NA)
+printCESParamsTableA(energyType="none");  printCESParamsTableB(energyType="none")
 printCESParamsTableA(energyType="Q"); printCESParamsTableB(energyType="Q")

### 2013-12-31 EconGrowth2.Rnw
Now using the spaghetti graph function to plot the CD results.

@@
 
-Figure~\ref{fig:CD_GDP_Lattice_Graph} compares predictions 
+Figure~\ref{fig:CD_GDP_Spaghetti_Graph} compares predictions 
 from the Cobb-Douglas models 
@@
 
-**** Replace with a spaghetti graph? Countries in rows. Without energy and with energy in columns. ****
-
-<<CD_GDP_Lattice_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas fitted models.">>=
-createCDLatticeGraph(energyType="Q")
+<<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas fitted models.">>=
+cdData <- loadCDSpaghettiGraphData(energyType="none")
+cdQData <- loadCDSpaghettiGraphData(energyType="Q")
+cdData <- rbind(cdData, cdQData)
+cesSpaghettiGraph(data=cdData, facet_formula=Country~Energy)
+# createCDLatticeGraph(energyType="Q")
 @

### 2013-12-31 EconGrowth2.Rnw
Now using faceted ternary plots for CD coefficients (without and with energy).

@@
 
-Figure~\ref{fig:CD_Scatter_Graph} shows a ternary plot 
-of $\alpha$, $\beta$, and $\gamma$ parameter values 
-for resample models for the Cobb-Douglas model (without energy).
-
-<<CD_Scatter_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (without energy) resample model parameters.
-$\\gamma$ is always 0.0, because energy is not included in this model.">>=
-cdResampleTrianglePlot(energyType="none", facet_formula=~countryAbbrev )
-@
-
 To estimate the parameters $\lambda$, $\alpha$, $\beta$, and $\gamma$ 
@@
 
-Figure~\ref{fig:CDq_Scatter_Graph} shows ternary plots 
+% Figure~\ref{fig:CDq_Scatter_Graph} shows ternary plots 
+% for $\alpha$, $\beta$, and $\gamma$ parameter values 
+% for Cobb-Douglas (with energy) resample models.
+% 
+% Figure~\ref{fig:CD_Scatter_Graph} shows a ternary plot 
+% of $\alpha$, $\beta$, and $\gamma$ parameter values 
+% for resample models for the Cobb-Douglas model (without energy).
+
+% <<CD_Scatter_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (without energy) resample model parameters.
+$\\gamma$ is always 0.0, because energy is not included in this model.">>=
+% cdResampleTrianglePlot(energyType="none", facet_formula=~countryAbbrev )
+% @
+% 
+% <<CDq_Scatter_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (with energy) resample model parameters.">>=
+% cdResampleTrianglePlot(energyType="Q", facet_formula=~countryAbbrev)
+% @
+
+Figure~\ref{fig:CD_Ternary_Scatter_Graph} shows ternary plots 
 for $\alpha$, $\beta$, and $\gamma$ parameter values 
-for Cobb-Douglas (with energy) resample models.
-
-<<CDq_Scatter_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (with energy) resample model parameters.">>=
-cdResampleTrianglePlot(energyType="Q", facet_formula=~countryAbbrev)
+for Cobb-Douglas (without and with energy) resample models.
+
+<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (without and with energy) resample model parameters.">>=
+  dataCD <- loadAllResampleData(modelType="cd", countryAbbrevsOrder=countryAbbrevsForGraph, energyType="none")
+  dataCDQ <- loadAllResampleData(modelType="cde", energyType="Q", countryAbbrevsOrder=countryAbbrevsForGraph)
+  data <- rbind.fill(dataCD, dataCDQ)
+  standardTriPlot(data=data, facet_formula=countryAbbrev~energy)
 @
@@
 from the Cobb-Douglas models 
-(with and without energy) to historical data.
+(without and with energy) to historical data.
 
@@
 
-The fit with lowest $sse$ of all the above trials is deemed the winner,
+The fit with lowest $sse$ of all above trials is deemed the winner,
 and its fitting parameters are used as the model.

### 2013-12-31 EconGrowth2.Rnw
Now correctly referring to China for zoomed spaghetti graph.

@@
 
-Figure~\ref{fig:CES_Spaghetti_Graph_ZM} shows details of the resample fits for Zambia with the (kl)e nesting.
-
-<<CES_Spaghetti_Graph_ZM, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES fitted models for Zambia with the (kl)e nesting.">>=
-cesSpaghettiGraph(data=subset(spagData, Country=="ZM" & nest=="(kl)e"), level=1)
+Figure~\ref{fig:CES_Spaghetti_Graph_CN} shows details of the resample fits for China with the (kl)e nesting.
+
+<<CES_Spaghetti_Graph_CN, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES fitted models for China with the (kl)e nesting.">>=
+cesSpaghettiGraph(data=subset(spagData, Country=="CN" & nest=="(kl)e"), level=1)
 @

### 2013-12-31 EconGrowth2.Rnw
Changed name of loadCESResampleTrianglePlotData to loadCESResampleData

@@
 
+<<CES_lambda_gamma_graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelTernaryGraphHeight, fig.cap="$\\lambda$ and $\\sigma$ values for CES resample models.">>=
+cesQResampleData <- loadCESResampleData(nest="all", energyType="Q")
+# standardScatterPlot(data=data, mapping=aes(gamma_coef, lambda, colour=isConv), facet_formula=countryAbbrev~nest)
+standardScatterPlot(data=cesQResampleData, mapping=aes(gamma_coef, lambda), facet_formula=countryAbbrev~nest, alpha=0.1)
+@
+
 **** Fix $x$-axis on Figures~\ref{fig:CESq_Sigma_Sigma_1_kle}--\ref{fig:CESq_Sigma_Sigma_1_ekl}.

### 2013-12-31 EconGrowth2.Rnw
Deleted much old text dealing with no-longer-used graphs. Replaced by faceted graphs for CES resampling parameters.

--- 2013-12-31 EconGrowth2.Rnw
@@
 
-Coefficients for each resampled CES model (without energy)
+Coefficients for each resampled CES model for all countries and all nests
 are shown in 
-Figures~\ref{fig:CES_lambda_gamma_Scatter_Graph} and
-\ref{fig:CES_sigma_1_delta_1_Scatter_Graph}. 
-Note that the bottom of the vertical axis represents $\sigma = 0$.
-The top of the vertical axis represents $\sigma = \infty$.
+Figures~\ref{fig:CES_lambda_gamma_graph}--\ref{fig:CES_sigma_delta_graph}. 
 The crosshair on each graph shows the location 
 of the fit to historical data. 
-Dots are colored by whether or not the fitting routine
-reports model convergence.
-
-<<CES_lambda_gamma_Scatter_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\lambda$ and $\\gamma$.">>=
-cesResamplePlotLambdaGamma(energyType="none")
-@
-
-<<CES_sigma_1_delta_1_Scatter_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
-cesResamplePlotSigma_1Delta_1(energyType="none")
-@
-
-Coefficients for each resampled CES model (with energy)
-are shown in 
-Figures~\ref{fig:CESq_lambda_gamma_Scatter_Graph_kle}--\ref{fig:CESq_sigma_delta_Scatter_Graph_ekl}. 
-Note that each nesting of the factors of production
-is included in the graphs.
-
-<<CESq_lambda_gamma_Scatter_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($kl$)$e$ nesting) resample model parameters $\\lambda$ and $\\gamma$.">>=
-cesResamplePlotLambdaGamma(energyType="Q", nest="(kl)e")
-@
-
-<<CESq_sigma_1_delta_1_Scatter_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($kl$)$e$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
-cesResamplePlotSigma_1Delta_1(energyType="Q", nest="(kl)e")
-@
-
-<<CESq_sigma_delta_Scatter_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($kl$)$e$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
-cesResamplePlotSigmaDelta(energyType="Q", nest="(kl)e")
-@
-
-<<CESq_lambda_gamma_Scatter_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($le$)$k$ nesting) resample model parameters $\\lambda$ and $\\gamma$.">>=
-cesResamplePlotLambdaGamma(energyType="Q", nest="(le)k")
-@
-
-<<CESq_sigma_1_delta_1_Scatter_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($le$)$k$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
-cesResamplePlotSigma_1Delta_1(energyType="Q", nest="(le)k")
-@
-
-<<CESq_sigma_delta_Scatter_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($le$)$k$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
-cesResamplePlotSigmaDelta(energyType="Q", nest="(le)k")
-@
-
-<<CESq_lambda_gamma_Scatter_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($ek$)$l$ nesting) resample model parameters $\\lambda$ and $\\gamma$.">>=
-cesResamplePlotLambdaGamma(energyType="Q", nest="(ek)l")
-@
-
-<<CESq_sigma_1_delta_1_Scatter_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($ek$)$l$ nesting) resample model parameters $\\sigma_1$ and $\\delta_1$.">>=
-cesResamplePlotSigma_1Delta_1(energyType="Q", nest="(ek)l")
-@
-
-<<CESq_sigma_delta_Scatter_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (with $q$, ($ek$)$l$ nesting) resample model parameters $\\sigma$ and $\\delta$.">>=
-cesResamplePlotSigmaDelta(energyType="Q", nest="(ek)l")
+In Figures~\ref{fig:CES_sigma1_delta1_graph} and~\ref{fig:CES_sigma_delta_graph},
+the bottom of the vertical axis represents $\sigma = 0$.
+The top of the vertical axis represents $\sigma = \infty$.
+
+<<CES_lambda_gamma_graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelTernaryGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models.">>=
+cesQResampleData <- loadCESResampleData(nest="all", energyType="Q")
+standardScatterPlot(data=cesQResampleData, mapping=aes(gamma_coef, lambda), facet_formula=countryAbbrev~nest, alpha=0.05) +
+    scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
+    scale_y_continuous(breaks=c(0, 0.025, 0.05, 0.075)) +    
+    labs(x=expression(gamma), y=expression(lambda))
+@
+
+<<CES_sigma1_delta1_graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelTernaryGraphHeight, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models.">>=
+standardScatterPlot(data=cesQResampleData, mapping=aes(delta_1, sigma_1), facet_formula=countryAbbrev~nest, alpha=0.05) +
+    coord_trans(y="sigma") +
+    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
+    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
+    labs(x=expression(delta[1]), y=expression(sigma[1]))
+@
+
+<<CES_sigma_delta_graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelTernaryGraphHeight, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models.">>=
+standardScatterPlot(data=subset(cesQResampleData, nest!="(kl)"), 
+                                mapping=aes(delta, sigma), 
+                                facet_formula=countryAbbrev~nest, 
+                                alpha=0.05) +
+    coord_trans(y="sigma") +
+    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
+    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
+    labs(x=expression(delta), y=expression(sigma))
 @
@@
 cesResampleTrianglePlot(energyType="Q", nest="all")
-@
-
-**** Fix $x$-axis on Figures~\ref{fig:CESq_Sigma_Sigma_1_kle}--\ref{fig:CESq_Sigma_Sigma_1_ekl}.
-Or, consider a better way to show resampled $\sigma$ and $\sigma_1$ values. ****
-
-Figure~\ref{fig:CESq_Sigma_Sigma_1_kle} shows 
-$\sigma$ and $\sigma_1$ values from the CES model with ($kl$)$e$ nesting.
-
-<<CESq_Sigma_Sigma_1_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="CES (with energy) resample model $\\sigma$ and $\\sigma_1$ values, ($kl$)$e$ nesting.">>=
-cesResamplePlotSigmaSigma_1(energyType="Q", nest="(kl)e")
-@
-
-Figure~\ref{fig:CESq_Sigma_Sigma_1_lek} shows 
-$\sigma$ and $\sigma_1$ values from the CES model with ($le$)$k$ nesting.
-
-<<CESq_Sigma_Sigma_1_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="CES (with energy) resample model $\\sigma$ and $\\sigma_1$ values, ($le$)$k$ nesting.">>=
-cesResamplePlotSigmaSigma_1(energyType="Q", nest="(le)k")
-@
-
-Figure~\ref{fig:CESq_Sigma_Sigma_1_ekl} shows 
-$\sigma$ and $\sigma_1$ values from the CES model with ($ek$)$l$ nesting.
-
-<<CESq_Sigma_Sigma_1_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="CES (with energy) resample model $\\sigma$ and $\\sigma_1$ values, ($ek$)$l$ nesting.">>=
-cesResamplePlotSigmaSigma_1(energyType="Q", nest="(ek)l")
 @

### 2013-12-31 EconGrowth2.Rnw
Rewrote section of paper that builds the LINEX resample plot.

@@
 <<LINEXq_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX model (with energy) resampling results.">>=
-# linexResamplePlot(energyType="Q")
-linexResamplePlot(energyType="Q")
+  linexResampleData <- loadAllResampleData(model="linex", energyType="Q", countryAbbrevsOrder=countryAbbrevsForGraph)
+  standardScatterPlot(data=linexResampleData, aes(a_0, c_t), facet_formula= ~ countryAbbrev, alpha=0.05) +
+      labs(x=expression(a[0]), y=expression(c[t])) +
+       scale_x_continuous(limits=c(-1, 2), breaks=c(-1, 0, 1.0, 2.0)) +
+       scale_y_continuous(limits=c(0, 10), breaks=c(0, 5, 10))
 @

### 2013-12-31 EconGrowth2.Rnw
Added LINEX spaghetti graph to the paper.

@@
 
-Figure~\ref{fig:LINEX_GDP_Lattice_Graph} compares LINEX model predictions to historical data.
-
-<<LINEX_GDP_Lattice_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX results.">>=
-createLINEXLatticeGraph(energyType="Q")
+Figure~\ref{fig:LINEX_Spaghetti_Graph} compares LINEX model predictions to historical data.
+
+<<LINEX_Spaghetti_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX results.">>=
+spagDataLinex <- loadLinexSpaghettiGraphData(energyType="Q")
+cesSpaghettiGraph(data=spagDataLinex, facet_formula= ~ Country)
 @

### 2013-12-31 EconGrowth2.Rnw
Deleted a commented line.

@@
 cesSpaghettiGraph(data=cdData, facet_formula=Country~Energy)
-# createCDLatticeGraph(energyType="Q")
 @

### 2013-12-31 EconGrowth2.Rnw
No longer using the cesResampleTrianglePlot function.

@@
 <<CES_ternary_graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelTernaryGraphHeight, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models.">>=
-cesResampleTrianglePlot(energyType="Q", nest="all")
+cesTriPlotData=loadCESResampleData(energyType="Q", nest="all")
+standardTriPlot(data=cesTriPlotData)
 @

### 2013-12-31 EconGrowth2.Rnw
Fixed width of ternary plots. Closes issue #19.

@@
 
-% Figure~\ref{fig:CDq_Scatter_Graph} shows ternary plots 
-% for $\alpha$, $\beta$, and $\gamma$ parameter values 
-% for Cobb-Douglas (with energy) resample models.
-% 
-% Figure~\ref{fig:CD_Scatter_Graph} shows a ternary plot 
-% of $\alpha$, $\beta$, and $\gamma$ parameter values 
-% for resample models for the Cobb-Douglas model (without energy).
-
-% <<CD_Scatter_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (without energy) resample model parameters.
-$\\gamma$ is always 0.0, because energy is not included in this model.">>=
-% cdResampleTrianglePlot(energyType="none", facet_formula=~countryAbbrev )
-% @
-% 
-% <<CDq_Scatter_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="Cobb-Douglas (with energy) resample model parameters.">>=
-% cdResampleTrianglePlot(energyType="Q", facet_formula=~countryAbbrev)
-% @
-
 Figure~\ref{fig:CD_Ternary_Scatter_Graph} shows ternary plots 
@@
 
-<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (without and with energy) resample model parameters.">>=
+<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=cdTernaryGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (without and with energy) resample model parameters.">>=
   dataCD <- loadAllResampleData(modelType="cd", countryAbbrevsOrder=countryAbbrevsForGraph, energyType="none")
@@
 (without and with energy) to historical data.
-
-<<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas fitted models.">>=
+Historical data are shown as a black line. 
+The fit to historical data is shown as a white line.
+The gray band encompasses 95\% of the fits to resampled data.
+
+<<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=cdSpaghettiGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas fitted models.">>=
 cdData <- loadCDSpaghettiGraphData(energyType="none")
@@
 cdData <- rbind(cdData, cdQData)
-cesSpaghettiGraph(data=cdData, facet_formula=Country~Energy)
+cesSpaghettiGraph(data=cdData, facet_formula=Country~Energy, level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1980 = 1 or 1991 = 1")
 @
@@
 to historical data for all nestings. 
-Historical data are shown as open circles. 
-The fit to historical data is shown as a dashed line. 
-The gray band beneath the historical data shows the spread of predictions for 1000 resamples.
+Historical data are shown as a black line. 
+The fit to historical data is shown as a white line.
+The gray band encompasses 95\% of the fits to resampled data.
 
@@
 Figure~\ref{fig:CES_Spaghetti_Graph_CN} shows details of the resample fits for China with the (kl)e nesting.
+Again, historical data are shown as a black line. 
+The fit to historical data is shown as a white line.
+The gray band encompasses 95\% of the fits to resampled data.
 
 <<CES_Spaghetti_Graph_CN, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES fitted models for China with the (kl)e nesting.">>=
-cesSpaghettiGraph(data=subset(spagData, Country=="CN" & nest=="(kl)e"), level=1)
+cesSpaghettiGraph(data=subset(spagData, Country=="CN" & nest=="(kl)e"), level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1980 = 1 or 1991 = 1")
 @
@@
 Figure~\ref{fig:LINEX_Spaghetti_Graph} compares LINEX model predictions to historical data.
+Historical data are shown as a black line. 
+The fit to historical data is shown as a white line.
+The gray band encompasses 95\% of the fits to resampled data.
 
@@
 spagDataLinex <- loadLinexSpaghettiGraphData(energyType="Q")
-cesSpaghettiGraph(data=spagDataLinex, facet_formula= ~ Country)
+cesSpaghettiGraph(data=spagDataLinex, facet_formula= ~ Country, level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1980 = 1 or 1991 = 1")
 @

### 2013-12-31 EconGrowth2.Rnw
Reduced the vertical size of the resample scatter plots, thereby eliminating blank pages. Closes Issue #16.

@@
 cesSpaghettiGraph(data=cdData, facet_formula=Country~Energy, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1980 = 1 or 1991 = 1")
+    labs(y="Indexed GDP (1980=1 or 1991=1)")
 @
@@
 
-<<CES_lambda_gamma_graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelTernaryGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models.">>=
+<<CES_lambda_gamma_graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models.">>=
 cesQResampleData <- loadCESResampleData(nest="all", energyType="Q")
@@
 
-<<CES_sigma1_delta1_graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelTernaryGraphHeight, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models.">>=
+<<CES_sigma1_delta1_graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelScatterGraphHeight, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models.">>=
 standardScatterPlot(data=cesQResampleData, mapping=aes(delta_1, sigma_1), facet_formula=countryAbbrev~nest, alpha=0.05) +
@@
 
-<<CES_sigma_delta_graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelTernaryGraphHeight, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models.">>=
+<<CES_sigma_delta_graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelScatterGraphHeight, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models.">>=
 standardScatterPlot(data=subset(cesQResampleData, nest!="(kl)"), 
-                                mapping=aes(delta, sigma), 
-                                facet_formula=countryAbbrev~nest, 
-                                alpha=0.05) +
+                    mapping=aes(delta, sigma), facet_formula=countryAbbrev~nest, alpha=0.05) +
     coord_trans(y="sigma") +
@@
 spagData <- loadCESSpaghettiGraphData(energyType="Q", nest="all")
-cesSpaghettiGraph(data=spagData, level=1)
+cesSpaghettiGraph(data=spagData, facet_formula=Country~nest, level=spaghettiGraphLevel)+
+    labs(y="Indexed GDP (1980=1 or 1991=1)")
 @
@@
 cesSpaghettiGraph(data=spagDataLinex, facet_formula= ~ Country, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1980 = 1 or 1991 = 1")
+    labs(y="Indexed GDP (1980=1 or 1991=1)")
 @

### 2013-12-31 EconGrowth2.Rnw
Added two-column format for CD and LINEX scatter plots and spaghetti graphs. This is an enhancement on Issue #16.

--- 2013-12-31 EconGrowth2.Rnw
@@
 
-<<Historical_Lattice_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), and thermal energy ($q$).">>=
+<<Historical_Lattice_Graph, fig.pos="H", fig.width=maxWidth, fig.height=maxHeight, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), and thermal energy ($q$).">>=
 createHistoricalLatticeGraph()
@@
 for Cobb-Douglas (without and with energy) resample models.
-
-<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=cdTernaryGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (without and with energy) resample model parameters.">>=
-  dataCD <- loadAllResampleData(modelType="cd", countryAbbrevsOrder=countryAbbrevsForGraph, energyType="none")
-  dataCDQ <- loadAllResampleData(modelType="cde", energyType="Q", countryAbbrevsOrder=countryAbbrevsForGraph)
-  data <- rbind.fill(dataCD, dataCDQ)
-  standardTriPlot(data=data, facet_formula=countryAbbrev~energy)
-@
+Each reample is shown as a gray dot on the graph. 
+The fit to historical data is shown as a gray circle.
 
@@
 
-<<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=cdSpaghettiGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas fitted models.">>=
+\twocolumn{}
+<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=7.5, fig.cap="Cobb-Douglas resample model parameters.">>=
+  dataCD <- loadAllResampleData(modelType="cd", countryAbbrevsOrder=countryAbbrevsForGraph, energyType="none")
+  dataCDQ <- loadAllResampleData(modelType="cde", energyType="Q", countryAbbrevsOrder=countryAbbrevsForGraph)
+  data <- rbind.fill(dataCD, dataCDQ)
+  standardTriPlot(data=data, facet_formula=countryAbbrev~energy)
+@
+
+<<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=7.75, fig.cap="Cobb-Douglas fitted models.">>=
 cdData <- loadCDSpaghettiGraphData(energyType="none")
@@
 cesSpaghettiGraph(data=cdData, facet_formula=Country~Energy, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1980 = 1 or 1991 = 1")
-@
+    labs(y="Indexed GDP (1980=1 or 1991=1)")
+@
+\onecolumn{}
 
@@
 
-<<CES_lambda_gamma_graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelTernaryGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models.">>=
+<<CES_lambda_gamma_graph, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models.">>=
 cesQResampleData <- loadCESResampleData(nest="all", energyType="Q")
@@
 
-<<CES_sigma1_delta1_graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelTernaryGraphHeight, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models.">>=
+<<CES_sigma1_delta1_graph, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models.">>=
 standardScatterPlot(data=cesQResampleData, mapping=aes(delta_1, sigma_1), facet_formula=countryAbbrev~nest, alpha=0.05) +
@@
 
-<<CES_sigma_delta_graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelTernaryGraphHeight, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models.">>=
+<<CES_sigma_delta_graph, fig.pos="H", fig.align='center', fig.width=4.5, fig.height=7, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models.">>=
 standardScatterPlot(data=subset(cesQResampleData, nest!="(kl)"), 
-                                mapping=aes(delta, sigma), 
-                                facet_formula=countryAbbrev~nest, 
-                                alpha=0.05) +
+                    mapping=aes(delta, sigma), facet_formula=countryAbbrev~nest, alpha=0.05) +
     coord_trans(y="sigma") +
@@
 
-<<CES_ternary_graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelTernaryGraphHeight, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models.">>=
+<<CES_ternary_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models.">>=
 cesTriPlotData=loadCESResampleData(energyType="Q", nest="all")
@@
 
-<<CES_Spaghetti_Graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelSpaghettiGraphHeight, fig.cap="CES fitted models.">>=
+<<CES_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8, fig.cap="CES fitted models.">>=
 spagData <- loadCESSpaghettiGraphData(energyType="Q", nest="all")
-cesSpaghettiGraph(data=spagData, level=1)
+cesSpaghettiGraph(data=spagData, facet_formula=Country~nest, level=spaghettiGraphLevel)+
+    labs(y="Indexed GDP (1980=1 or 1991=1)")
 @
@@
 
-<<CES_Spaghetti_Graph_CN, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES fitted models for China with the (kl)e nesting.">>=
+<<CES_Spaghetti_Graph_CN, fig.pos="H", fig.align='center', fig.width=maxWidth, fig.height=maxHeight, fig.cap="CES fitted models for China with the (kl)e nesting.">>=
 cesSpaghettiGraph(data=subset(spagData, Country=="CN" & nest=="(kl)e"), level=spaghettiGraphLevel) +
@@
 
-<<LINEXq_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX model (with energy) resampling results.">>=
-  linexResampleData <- loadAllResampleData(model="linex", energyType="Q", countryAbbrevsOrder=countryAbbrevsForGraph)
-  standardScatterPlot(data=linexResampleData, aes(a_0, c_t), facet_formula= ~ countryAbbrev, alpha=0.05) +
-      labs(x=expression(a[0]), y=expression(c[t])) +
-       scale_x_continuous(limits=c(-1, 2), breaks=c(-1, 0, 1.0, 2.0)) +
-       scale_y_continuous(limits=c(0, 10), breaks=c(0, 5, 10))
-@
-
 Figure~\ref{fig:LINEX_Spaghetti_Graph} compares LINEX model predictions to historical data.
@@
 
-<<LINEX_Spaghetti_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX results.">>=
+\twocolumn{}
+<<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7, fig.cap="LINEX model (with energy) resampling results.">>=
+  linexResampleData <- loadAllResampleData(model="linex", energyType="Q", countryAbbrevsOrder=countryAbbrevsForGraph)
+  standardScatterPlot(data=linexResampleData, aes(a_0, c_t), facet_formula=countryAbbrev~energy, alpha=0.05) +
+      labs(x=expression(a[0]), y=expression(c[t])) +
+       scale_x_continuous(limits=c(-1, 2), breaks=c(-1, 0, 1.0, 2.0)) +
+       scale_y_continuous(limits=c(0, 10), breaks=c(0, 5, 10))
+@
+
+<<LINEX_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7.1, fig.cap="LINEX fitted models.">>=
 spagDataLinex <- loadLinexSpaghettiGraphData(energyType="Q")
-cesSpaghettiGraph(data=spagDataLinex, facet_formula= ~ Country, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1980 = 1 or 1991 = 1")
-@
+cesSpaghettiGraph(data=spagDataLinex, facet_formula=Country ~ Energy, level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1980=1 or 1991=1)")
+@
+\onecolumn{}
 

### 2013-12-31 Econ-Growth-Functions2.R

@@ -53,21 +53,28 @@ countryOrderForGraphsU <- c(3, 2, 1) # Sets the order as US, UK, JP when we're l
 timeTics <- c(1980, 1990, 2000, 2010)
 yTicsForIndexedGraphs <- c(1,2,3,4,5,6,7,8,9,10) #y tic mark locations.
 
-maxWidth <- 6.5 #Inches
+
 # Full page lattice plot sizes
 ninePanelLayoutSpec <- c(3,3) #indicates a 3x3 arrangement of panels.
 threePanelLayoutSpec <- c(3,1) #indicates a 1 row x 3 column arangement of panels
 onePanelLayoutSpec <- c(1,1) #indicates a 1x1 arrangement of panels.
-threePanelGraphWidth <- maxWidth
-threePanelGraphHeight <- 3.17 #Inches
-threePanelTernaryGraphHeight <- 2.0 #Inches
-ninePanelGraphWidth <- maxWidth     
-ninePanelGraphHeight <- 7.5  #Inches
-ninePanelTernaryGraphHeight <- 5.1 #Inches
-thirtySixPanelGraphWidth <- maxWidth
-thirtySixPanelTernaryGraphHeight <- 9.0-0.5 #Inches
-thirtySixPanelSpaghettiGraphHeight <- thirtySixPanelTernaryGraphHeight #Inches
-thirtySixPanelScatterGraphHeight <- thirtySixPanelTernaryGraphHeight #Inches
+
+# Graph Heights
+maxHeight <- 8.5 #Inches
+ninePanelScatterGraphHeight <- maxHeight #Inches
+ninePanelTernaryGraphHeight <- 7 #Inches
+ninePanelSpaghettiGraphHeight <- 7 #Inches
+
+# Graph Widths
+maxWidth <- 6.5 #Inches
+fourPanelScatterGraphWidth <- maxWidth #Inches
+threePanelScatterGraphWidth <- maxWidth*0.75 #Inches
+onePanelScatterGraphWidth <- maxWidth*0.25
+fourPanelTernaryGraphWidth <- maxWidth
+twoPanelTernaryGraphWidth <- maxWidth*0.45
+fourPanelSpaghettiGraphWidth <- maxWidth
+twoPanelSpaghettiGraphWidth <- maxWidth*0.55
+onePanelSpaghettiGraphWidth <- maxWidth*0.4
 
 presentationGraph1RowHeight <- 2.8 #Inches
 presentationGraph2ColWidth <- 2 #Inches

### 2014-01-01 EconGrowth2.Rnw
Fixed height of one figure.

@@
 
-<<CES_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8, fig.cap="CES fitted models.">>=
+<<CES_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models.">>=
 spagData <- loadCESSpaghettiGraphData(energyType="Q", nest="all")

### 2014-01-01 EconGrowth2.Rnw
Fixed some wording in the paper.

@@
 
-The 95\% confidence intervals associated with Figure~\ref{fig:CD_Scatter_Graph} 
+The 95\% confidence intervals associated with 
+the without-energy column of Figure~\ref{fig:CD_Ternary_Scatter_Graph} 
 are shown in Table~\ref{tab:CD_Parameters_No_Energy}.
@@
 
-The 95\% confidence intervals associated with Figure~\ref{fig:CDq_Scatter_Graph} 
+The 95\% confidence intervals associated with 
+the with-energy column of Figure~\ref{fig:CD_Ternary_Scatter_Graph} 
 are shown in Table~\ref{tab:CD_Parameters_With_Q}
@@
 The 95\% confidence intervals associated 
-with Figures~\ref{fig:CES_lambda_gamma_Scatter_Graph} 
-and \ref{fig:CES_sigma_1_delta_1_Scatter_Graph}
+with ($kl$) nest columns of 
+Figures~\ref{fig:CES_lambda_gamma_graph}--\ref{fig:CES_ternary_graph}
 are shown in Tables~\ref{tab:CES_Parameters_A} 
@@
 
-<<CES_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (without energy) model parameters.
+<<CES_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (without energy, ($kl$) nesting) model parameters.
 Vertical bars indicate 95\\% confidence intervals.">>=
@@
 
-The 95\% confidence intervals for the ($kl$)$e$ nesting associated 
-with Figures~\ref{fig:CESq_lambda_gamma_Scatter_Graph_kle}--\ref{fig:CESq_sigma_delta_Scatter_Graph_kle}
+The 95\% confidence intervals associated 
+with ($kl$)$e$ nest columns of 
+Figures~\ref{fig:CES_lambda_gamma_graph}--\ref{fig:CES_ternary_graph}
 are shown in Tables~\ref{tab:CES_Parameters_A_With_Q_(kl)e} and 
@@
 
-The 95\% confidence intervals for the ($le$)$k$ nesting associated 
-with Figures~\ref{fig:CESq_lambda_gamma_Scatter_Graph_lek}--\ref{fig:CESq_sigma_delta_Scatter_Graph_lek}
+The 95\% confidence intervals associated 
+with ($le$)$k$ nest columns of 
+Figures~\ref{fig:CES_lambda_gamma_graph}--\ref{fig:CES_ternary_graph}
 are shown in Tables~\ref{tab:CES_Parameters_A_With_Q_(le)k} and 
@@
 
-The 95\% confidence intervals for the ($ek$)$l$ nesting associated 
-with Figures~\ref{fig:CESq_lambda_gamma_Scatter_Graph_ekl}--\ref{fig:CESq_sigma_delta_Scatter_Graph_ekl}
+The 95\% confidence intervals associated 
+with ($ek$)$l$ nest columns of 
+Figures~\ref{fig:CES_lambda_gamma_graph}--\ref{fig:CES_ternary_graph}
 are shown in Tables~\ref{tab:CES_Parameters_A_With_Q_(ek)l} and 

### 2014-01-01 Econ-Growth-Functions2.R

@@ -2464,7 +2464,7 @@ cesParamsTableA <- function(energyType="none", nest="(kl)e"){
                          " ", "$\\sigma$",    " ")
   rownames(dataCES) <- countryAbbrevs
   if (energyType == "none"){
-    energyStringCaption <- "(without energy)"
+    energyStringCaption <- "(without energy, ($kl$) nesting)"
     energyStringLabel <- ""
   } else {
     if (nest == "(kl)e"){
@@ -2503,7 +2503,7 @@ cesParamsTableB <- function(energyType="none", nest="(kl)e"){
                          " ", "$\\sigma$",    " ")
   rownames(dataCES) <- countryAbbrevs
   if (energyType == "none"){
-    energyStringCaption <- "(without energy)"
+    energyStringCaption <- "(without energy, ($kl$) nesting)"
     energyStringLabel <- ""
   } else {
     if (nest == "(kl)e"){
@@ -2518,7 +2518,7 @@ cesParamsTableB <- function(energyType="none", nest="(kl)e"){
     energyStringLabel <- paste("_With_", energyType, "_", nest, sep="")
   }
   tableCESb <- xtable(dataCES[,c(1,2,3, 7,8,9, 13,14,15)], #Picks up gamma, delta_1, and sigma_1
-                      caption=paste("CES model ", energyStringCaption, ". $\\gamma$, $\\delta_1$, and $\\sigma_1$ parameters for 1980--2011 (US, UK, JP) and 1991--2011 (CN, ZA, SA, IR, TZ, and ZM). (Parameter estimates beneath symbol. 95\\% confidence interval bounds to left and right.)", sep=""), 
+                      caption=paste("CES model parameters ", energyStringCaption, ". $\\gamma$, $\\delta_1$, and $\\sigma_1$ parameters for 1980--2011 (US, UK, JP) and 1991--2011 (CN, ZA, SA, IR, TZ, and ZM). (Parameter estimates beneath symbol. 95\\% confidence interval bounds to left and right.)", sep=""), 
                       label=paste("tab:CES_Parameters_B", energyStringLabel, sep=""),
                       digits = c(1, 2,2,2, 2,2,2, 2,2,2),
                       align = "r|ccc|ccc|ccc"  #Sets alignment of the numbers in the columns

### 2014-01-01 EconGrowth2.Rnw
Added a note about comparing ternary plots from CD and CES models.
Changed country order. Fixes Issue #23.

@@
 <<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=7.5, fig.cap="Cobb-Douglas resample model parameters.">>=
-  dataCD <- loadAllResampleData(modelType="cd", countryAbbrevsOrder=countryAbbrevsForGraph, energyType="none")
-  dataCDQ <- loadAllResampleData(modelType="cde", energyType="Q", countryAbbrevsOrder=countryAbbrevsForGraph)
+  dataCD <- loadAllResampleData(modelType="cd", countryAbbrevsOrder=countryAbbrevs, energyType="none")
+  dataCDQ <- loadAllResampleData(modelType="cde", energyType="Q", countryAbbrevsOrder=countryAbbrevs)
   data <- rbind.fill(dataCD, dataCDQ)
@@
 $\alpha$, $\beta$, and $\gamma$ parameters for the CES model for all nests and countries.
+Figure~\ref{fig:CES_ternary_graph} is comparable to
+the ternary graph for the Cobb-Douglas models, 
+Figure~\ref{fig:CD_Ternary_Scatter_Graph}.
 
@@
 <<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7, fig.cap="LINEX model (with energy) resampling results.">>=
-  linexResampleData <- loadAllResampleData(model="linex", energyType="Q", countryAbbrevsOrder=countryAbbrevsForGraph)
+  linexResampleData <- loadAllResampleData(model="linex", energyType="Q", countryAbbrevsOrder=countryAbbrevs)
   standardScatterPlot(data=linexResampleData, aes(a_0, c_t), facet_formula=countryAbbrev~energy, alpha=0.05) +

### 2014-01-10 EconGrowth2.Rnw
createHistoricalLatticeGraph -> historicalPlot

@@
 <<Historical_Lattice_Graph, fig.pos="H", fig.width=maxWidth, fig.height=maxHeight, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), and thermal energy ($q$).">>=
-createHistoricalLatticeGraph()
+historicalPlot()
 @

### 2014-01-10 EconGrowth2.Rnw
cesSpaghettiGraph -> spaghettiPlot

@@
 cdData <- rbind(cdData, cdQData)
-cesSpaghettiGraph(data=cdData, facet_formula=Country~Energy, level=spaghettiGraphLevel) +
+spaghettiPlot(data=cdData, facet_formula=Country~Energy, level=spaghettiGraphLevel) +
     labs(y="Indexed GDP (1980=1 or 1991=1)")
@@
 spagData <- loadCESSpaghettiGraphData(energyType="Q", nest="all")
-cesSpaghettiGraph(data=spagData, facet_formula=Country~nest, level=spaghettiGraphLevel)+
+spghettiPlot(data=spagData, facet_formula=Country~nest, level=spaghettiGraphLevel)+
     labs(y="Indexed GDP (1980=1 or 1991=1)")
@@
 <<CES_Spaghetti_Graph_CN, fig.pos="H", fig.align='center', fig.width=maxWidth, fig.height=maxHeight, fig.cap="CES fitted models for China with the (kl)e nesting.">>=
-cesSpaghettiGraph(data=subset(spagData, Country=="CN" & nest=="(kl)e"), level=spaghettiGraphLevel) +
+spghettiPlot(data=subset(spagData, Country=="CN" & nest=="(kl)e"), level=spaghettiGraphLevel) +
     labs(y="Indexed GDP (1980 = 1 or 1991 = 1")
@@
 spagDataLinex <- loadLinexSpaghettiGraphData(energyType="Q")
-cesSpaghettiGraph(data=spagDataLinex, facet_formula=Country ~ Energy, level=spaghettiGraphLevel) +
+spghettiPlot(data=spagDataLinex, facet_formula=Country ~ Energy, level=spaghettiGraphLevel) +
     labs(y="Indexed GDP (1980=1 or 1991=1)")

### 2014-01-10 Graphics.R

@@ -148,7 +148,7 @@ standardScatterPlot <- function(data, mapping, orig_color="gray70", size=2.0, al
   p + xy_theme()
 }
 
-cesSpaghettiGraph <- function(energyType='none', 
+spaghettiPlot <- function(energyType='none', 
                               nest, 
                               data=loadCESSpaghettiGraphData(energyType=energyType, 
                                                              nest=nest, ...), 

### 2014-01-11 EconGrowth2.Rnw
Changed size of historical graph to be significantly narrower.

@@
 
-<<Historical_Lattice_Graph, fig.pos="H", fig.width=maxWidth, fig.height=maxHeight, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), and thermal energy ($q$).">>=
+<<Historical_Lattice_Graph, fig.pos="H", fig.width=3, fig.height=7.0, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), and thermal energy ($q$).">>=
 historicalPlot()
@@
 spagData <- loadCESSpaghettiGraphData(energyType="Q", nest="all")
-spghettiPlot(data=spagData, facet_formula=Country~nest, level=spaghettiGraphLevel)+
+spaghettiPlot(data=spagData, facet_formula=Country~nest, level=spaghettiGraphLevel)+
     labs(y="Indexed GDP (1980=1 or 1991=1)")
@@
 <<CES_Spaghetti_Graph_CN, fig.pos="H", fig.align='center', fig.width=maxWidth, fig.height=maxHeight, fig.cap="CES fitted models for China with the (kl)e nesting.">>=
-spghettiPlot(data=subset(spagData, Country=="CN" & nest=="(kl)e"), level=spaghettiGraphLevel) +
+spaghettiPlot(data=subset(spagData, Country=="CN" & nest=="(kl)e"), level=spaghettiGraphLevel) +
     labs(y="Indexed GDP (1980 = 1 or 1991 = 1")
@@
 spagDataLinex <- loadLinexSpaghettiGraphData(energyType="Q")
-spghettiPlot(data=spagDataLinex, facet_formula=Country ~ Energy, level=spaghettiGraphLevel) +
+spaghettiPlot(data=spagDataLinex, facet_formula=Country ~ Energy, level=spaghettiGraphLevel) +
     labs(y="Indexed GDP (1980=1 or 1991=1)")

### 2014-01-11 EconGrowth2.Rnw
Adjusted sizes of ternary plots.

@@
 \twocolumn{}
-<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=7.5, fig.cap="Cobb-Douglas resample model parameters.">>=
+<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=2.9, fig.height=7.7, fig.cap="Cobb-Douglas resample model parameters.">>=
   dataCD <- loadAllResampleData(modelType="cd", countryAbbrevsOrder=countryAbbrevs, energyType="none")
@@
 
-<<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=7.75, fig.cap="Cobb-Douglas fitted models.">>=
+<<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=8.2, fig.cap="Cobb-Douglas fitted models.">>=
 cdData <- loadCDSpaghettiGraphData(energyType="none")
@@
 
-<<CES_ternary_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models.">>=
+<<CES_ternary_graph, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models.">>=
 cesTriPlotData=loadCESResampleData(energyType="Q", nest="all")

### 2014-01-11 EconGrowth2.Rnw
Now using \twocolumn for the historical data graph.

@@
 
+\usepackage{wrapfig}  % Allows wrapping of text around figures
 \usepackage{soul}     % Provides strikethrough text
@@
 
+\twocolumn{}
+<<Historical_Lattice_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=7.5, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), and thermal energy ($q$).">>=
+historicalPlot()
+@
+
 %++++++++++++++++++++++++++++++
@@
 
-<<Historical_Lattice_Graph, fig.pos="H", fig.width=3, fig.height=7.0, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), and thermal energy ($q$).">>=
-historicalPlot()
-@
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 residual resampling in our parameter estimation processes.
+
+\onecolumn{}
 

### 2014-01-12 EconGrowth2.Rnw
Added NSF acknowledgement.
Changed wording of the resampling section.

@@
 
-Under that assumption, it would not be surprising if the residual from 
+Under that assumption, it would be unsurprising if the residual from 
 any particular year had been observed in a different year. 
-By applying randomly selected residuals [$\mathrm{abs}(\mathrm{rand}(r_t))$]
-with randomly selected signs [$\mathrm{rand}(-1, 1)$]
-to model predictions, we create a 
-preliminary resampled GDP time series ($y_{prelim,resample,t}$):
+To obtain a 
+preliminary resampled GDP time series ($y_{prelim,resample,t}$),
+we add
+the absolute value of residuals 
+from randomly-selected times $\left( \left| r_{\mathrm{rand}(t)} \right| \right)$
+with randomly-selected signs [$\mathrm{rand}(-1, 1)$]
+to model predictions.
 
 \begin{equation} \label{eq:resample_y_prelim}
-  y_{prelim,resample,t} = y_{pred,t} + \mathrm{rand}(-1, 1) \cdot \mathrm{abs}(\mathrm{rand}(r_t)).
+  y_{prelim,resample,t} = y_{pred,t} + \mathrm{rand}(-1, 1) \cdot \left| r_{\mathrm{rand}(t)} \right|.
 \end{equation}
 
-\noindent{}The preliminary resample time series
+\noindent{}We note that the preliminary resample time series
 can have non-unity first-year GDP ($y_{prelim,resample,0} \ne 1$).
@@
 we would have indexed to a different first-year GDP value, 
-such that \emph{every} resampled GDP time series starts with $y_{resample,0} = 1$.
+such that \emph{every} resampled GDP time series has $y_{resample,0} = 1$.
 We use
@@
 for insightful critique of the statistical analyses presented herein.
+The computations in this paper were accomplished using dahl.calvin.edu, 
+a Beowulf cluster built with support from the National Science Foundation's 
+Major Research Instrumentation and Cyber Infrastructure programs, 
+grant no. OCI-0722819.
 

### 2014-01-19 EconGrowth2.Rnw
Added quotes from Solow and Abramowitz.

@@
 labor ($l$), indexed capital stock ($k$), and an exogenous, time-dependent 
-technological progress term ($A$):
+residual\footnote{The $A$ term in production functions is often linked
+to ``technological progress,'' but that is a very narrow reading of Solow's original intent:
+\begin{quote}
+  It will be seen that I am using the phrase ``technical change''
+  as a short-hand expression for any kind of shift 
+  in the production function. 
+  Thus slowdowns, speed-ups, improvements in the education of the labor force, 
+  and all sorts of things will appear as ``technical change.''~\citep{solow1957technical}
+\end{quote}
+Thus, we refer to $A$ as a ``residual.''} 
+term ($A$):
 
@@
 with e being the base of the natural logarithm, and subscripts ``0'' indicating values 
-at an initial year. $A$ is a unitless technological progress term, with $\lambda$ 
-indicating the pace of technological progress (in units of 
+at an initial year. $A$ is the residual term, with $\lambda$ 
+indicating the change of the residual over time (in units of 
 year$^{-1}$).\footnote{Dimensionless, indexed quantities are represented by 
@@
 quantities are represented by upper-case symbols 
-($Y$, $K$, $L$, $E$, $Q$, $X$, and $U$). One exception is the technolgical 
-progress term $A$, which is dimensionless but written upper-case by convention.} 
+($Y$, $K$, $L$, $E$, $Q$, $X$, and $U$). One exception is the 
+residual term $A$, which is dimensionless but written upper-case by convention.} 
 Neoclassical economic growth theory as expressed in the Cobb-Douglas production 
-function makes no attempt to describe the mechanisms by which technological 
-progress ($A$) affects economic growth, nor does it attempt to describe how 
-technological progress ($A$) might vary from one economy to the next. Mathematically, 
-$A$ is a fitting parameter that aligns the predictions of Equation~\ref{eq:CD} 
+function makes no attempt to describe the mechanisms that affect
+economic growth, nor does it attempt to describe how such things as
+slowdowns, speedups, and improvements of the education of the labor force
+($A$) might vary from one economy to the next. Mathematically, 
+$A$ is the residual, a fitting parameter that aligns the predictions of Equation~\ref{eq:CD} 
 with historical data. Typically, the constraint $\alpha + \beta = 1$ is assumed, 
@@
 
+\citet{Abramovitz:1956aa} wrote:
+
+\begin{quote}
+  This result [that ``technological progress, $A$'' explained
+  175\% of the growth of the US economy since 1870] is surprising in the lopsided
+  importance which it appears to give to productivity increase,
+  and it should be, in a sense, sobering, if not discouraging,
+  to students of economic growth.
+  Since we know little about the causes of productivity increase,
+  the indicated importance of this element may be taken to be some sort of measure
+  of our ignorance about the causes of economic growth in the United States
+  and some sort of indication of where
+  we need to concentrate our atention.
+\end{quote}
+
 In contrast to both the Cobb-Douglas model (Equations~\ref{eq:CD} and 
 \ref{eq:CDe}) and the CES model (Equations~\ref{eq:CES}--\ref{eq:CESekl}), 
-the LINEX model (Equation~\ref{eq:LINEX}) accounts 
-for efficiencies among capital, labor, and energy directly and, 
-therefore, does not employ a time-dependent 
-technological progress term ($A$). \citet{Kummel:2002tx} use the 
+the LINEX model (Equation~\ref{eq:LINEX}) attempts to explain the residual ($A$)
+with physical factors,
+efficiencies among capital, labor, and energy.
+Therefore, LINEX does not employ a time-dependent 
+residual term ($A$).
+
+\citet{Kummel:2002tx} use the 
 LINEX production function to describe economic output 

### 2014-01-19 EconGrowth2.Rnw
Small punctuation change.

@@
 the LINEX model (Equation~\ref{eq:LINEX}) attempts to explain the residual ($A$)
-with physical factors,
+with physical factors:
 efficiencies among capital, labor, and energy.

### 2014-01-19 EconGrowth2.Rnw
Spelling correction. Turned on knitr chunks.

@@
   and some sort of indication of where
-  we need to concentrate our atention.
+  we need to concentrate our attention.
 \end{quote}

### 2014-01-24 EconGrowth2.Rnw
Minor edits.

@@
 \end{quote}
-Thus, we refer to $A$ as a ``residual.''} 
+Mathematically, $A$ is nothing more than a fitting parameter 
+that aligns the predictions of Equation~\ref{eq:CD} 
+with historical data. 
+Thus, we refer to $A$ as the ``residual'' in this paper.} 
 term ($A$):
@@
 slowdowns, speedups, and improvements of the education of the labor force
-($A$) might vary from one economy to the next. Mathematically, 
-$A$ is the residual, a fitting parameter that aligns the predictions of Equation~\ref{eq:CD} 
-with historical data. Typically, the constraint $\alpha + \beta = 1$ is assumed, 
+($A$) might vary from one economy to the next. 
+Typically, the constraint $\alpha + \beta = 1$ is assumed, 
 indicating constant returns to scale.

### 2014-02-10 EconGrowth2.Rnw
Removed last vestiges of X and U. Closes Issue #32.

@@
 historical data for economic output ($Y$), capital stock ($K$), 
-labor ($L$), thermal energy ($Q$), exergy ($X$), and useful work ($U$) 
+labor ($L$), and thermal energy ($Q$)   %, exergy ($X$), and useful work ($U$) 
 are required. Subsections below describe sources for and calculations 

### 2014-03-01 Article/EconGrowth2.Rnw
house cleaning and reorg

--- 2014-02-10 EconGrowth2.Rnw
@@
 <<setup, echo=FALSE, message=FALSE, eval=TRUE>>=
+require(EconModels)
 require(lattice)
@@
 )
-source("Econ-Growth-Functions2.R")
-source("Graphics.R")
+#source("Econ-Growth-Functions2.R")
+#source("Graphics.R")
 @

### 2014-03-01 Scrap/CES.Rnw
house cleaning and reorg

--- 2013-07-30 CES.Rnw
@@
 nestingOptions <- c(kle="(kl)e", lek="(le)k", ekl="(ek)l")
-fitCES <- function(countryAbbrev, nest, energyType="Q", algorithm=c("PORT","L-BFGS-B")){
-  data <- loadData(countryAbbrev=countryAbbrev)
-  data <- replaceColName(data, energyType, "iEToFit")
-  if (nest == "(kl)e"){
-    xNames <- c("iCapStk", "iLabor", "iEToFit")
-  } else if (nest == "(le)k"){
-    xNames <- c("iLabor", "iEToFit", "iCapStk")
-  } else if (nest == "(ek)l"){
-    xNames <- c("iEToFit", "iCapStk", "iLabor")
-  } else {
-    stop(paste("Unknown nesting option", nest, "in fitCES."))
-  }
-  model <- cesModel(data=data, energyType=energyType, 
-                  # yName="iGDP", 
-                  xNames=xNames, 
-                  # tName="iYear",
-                  algorithm=algorithm)
-  res <- naturalCoef( model ) 
-  res <- transform( res, nest=nest, country=countryAbbrev, nest=nest, converge=model$convergence ) 
-  return(res)
-}
 

### 2014-03-01 Seminar/EconGrowthSeminar.Rnw
house cleaning and reorg

--- 2013-04-30 EconGrowthSeminar.Rnw
@@
-<<setup_functions, child='EconGrowth-R-Functions.Rnw', echo=FALSE, message=FALSE, eval=TRUE>>=
+<<setup_child, echo=FALSE, message=FALSE, eval=TRUE>>=
 # Includes the Functions.Rnw file that contains all of the functions for analyzing our economic data.
+require(lattice)
+require(latticeExtra)
+require(ggplot2)
+require(car)
+require(mosaic)
+require(xtable)
+require(nlmrt)
+require(micEconCES)
+require(reshape2) # Provides access to data melting. See http://cran.r-project.org/web/packages/reshape2/reshape2.pdf
+# tikz allows use of LaTeX formatting and font in graphs. Allows for a consistent look across the paper.
+# See http://r-forge.r-project.org/R/?group_id=440 for instructions on installing tikzDevice.
+# require(tikzDevice) 
+trellis.par.set(theme=theme.mosaic())
+options(width=75)
+options(show.signif.stars=TRUE)
+opts_chunk$set(
+  # ********************************************************************************************************
+  eval=TRUE,
+  # ********************************************************************************************************
+  dev='tikz',    #Allows LaTeX code in graphical output. E.g., "$y$" for a variable name in the legend for a graph.
+  tidy=FALSE,
+  comment=NA,
+  #Tells whether to cache output from chunks are saved. Cacheing saves time. 
+  #However, references to LaTeX tables DO NOT WORK if cacheing is turned on (i.e., cache=TRUE).
+  cache=FALSE,
+  warning=FALSE,  #Tells whether to show warnings in the output.
+  message=FALSE, #Turns off messages for all chunks. Set TRUE on an individual chunk to see it.
+  echo=FALSE     #Tells whether to echo code for all chunks. Set TRUE on an individual chunk to see its code.
+)
+source("Econ-Growth-Functions.R")
 @

### 2014-03-03 Article/EconGrowth2.Rnw
updating presentation of the models

@@
 Neoclassical economic growth theory attributes output ($Y$) to factors of production:
-capital stock ($K$) and labor ($L$). The Cobb-Douglas production function is the 
+capital stock ($K$) and labor ($L$). The Cobb-Douglas production function 
+is the 
 canonical representation of indexed economic output ($y$) as a function of indexed 
-labor ($l$), indexed capital stock ($k$), and an exogenous, time-dependent 
-residual\footnote{The $A$ term in production functions is often linked
+labor ($l$), indexed capital stock ($k$), and an additional exogenous, time-dependent 
+term.%
+\footnote{The time-dependent term in production functions is often linked
 to ``technological progress,'' but that is a very narrow reading of Solow's original intent:
@@
 \end{quote}
-Mathematically, $A$ is nothing more than a fitting parameter 
-that aligns the predictions of Equation~\ref{eq:CD} 
-with historical data. 
-Thus, we refer to $A$ as the ``residual'' in this paper.} 
-term ($A$):
-
+}
+This production function can be expressed as
 \begin{equation} \label{eq:CD}
-  y = A k^\alpha l^\beta; A = \mathrm{e}^{\lambda(t-t_0)}
+  y = \theta \mathrm{e}^{\lambda(t-t_0)} k^\alpha l^\beta \;,
 \end{equation}
-
-\noindent where $y \equiv Y/Y_\mathrm{0}$, $k \equiv K/K_\mathrm{0}$, and 
-$l \equiv L/L_\mathrm{0}$; with $Y$ represented by GDP, $K$ expressed in 
-currency units, $L$ expressed in workers or work-hours/year, time ($t$) measured in years, 
-with e being the base of the natural logarithm, and subscripts ``0'' indicating values 
-at an initial year. $A$ is the residual term, with $\lambda$ 
-indicating the change of the residual over time (in units of 
-year$^{-1}$).\footnote{Dimensionless, indexed quantities are represented by 
+where 
+\begin{itemize}
+	\item $y \equiv Y/Y_{0}$,  % why was 0 typeset as mathrm??
+	\item $k \equiv K/K_{0}$, 
+	\item $l \equiv L/L_{0}$, 
+	\item $Y$ represented by GDP, 
+	\item $K$ expressed in currency units, 
+	\item $L$ expressed in workers or work-hours/year, 
+	\item $t$ (time) is measured in years, 
+	\item e is the base of the natural logarithm, and 
+	\item 0 subscripts indicate values at an initial year.%
+\footnote{Dimensionless, indexed quantities are represented by 
 lower-case symbols 
@@
 quantities are represented by upper-case symbols 
-($Y$, $K$, $L$, $E$, $Q$, $X$, and $U$). One exception is the 
-residual term $A$, which is dimensionless but written upper-case by convention.} 
+($Y$, $K$, $L$, $E$, $Q$, $X$, and $U$). 
+Model parameters are represented by Greek letters
+($\alpha$, $\beta$, $\lambda$, $\theta$).} 
+\end{itemize}
+%Mathematically, $A$ is nothing more than a fitting parameter 
+%that aligns the predictions of Equation~\ref{eq:CD} 
+%with historical data. 
+%Thus, we refer to $A$ as the ``residual'' in this paper.} 
+%term ($A$):
+
+% $A$ is the residual term, 
+% with $\lambda$ 
+% indicating the change of the residual over time (in units of 
+% year$^{-1}$).
 Neoclassical economic growth theory as expressed in the Cobb-Douglas production 
@@
 slowdowns, speedups, and improvements of the education of the labor force
-($A$) might vary from one economy to the next. 
+($\lambda$) might vary from one economy to the next. 
+The parameters $\alpha$ and $\beta$ indicate the relative roles 
+of capital and labor in the economy.
 Typically, the constraint $\alpha + \beta = 1$ is assumed, 
@@
 
-The capital-labor Cobb-Douglas production function is shown in Equation~\ref{eq:CD}.
-Similarly, the energy-augmented Cobb-Douglasproduction function is
+The capital-labor Cobb-Douglas production function shown in Equation~\ref{eq:CD}
+can be augmented to include an energy term:
+%Similarly, the energy-augmented Cobb-Douglas production function is
 
 \begin{equation} \label{eq:CDe}
-  y = A k^\alpha l^\beta e^\gamma; A = \mathrm{e}^{\lambda(t-t_0)}
+  y = \theta \mathrm{e}^{\lambda(t-t_0)}  k^\alpha l^\beta e^\gamma \;,
 \end{equation}
-
-\noindent where $e \equiv E/E_0$, and $E$ is in units of energy per time, 
+where $e \equiv E/E_0$, and $E$ is in units of energy per time, 
 typically TJ/year. The energy-augmented Cobb-Douglas production function 
@@
 A third production function, the LINear EXponential (LINEX) function
-\citep{Kummel:1980wx,Kummel:1982vy,Kummel:1985vz,Kummel:1989tf,Kummel:2002tx,Kummel:2010vz}, 
-was derived from thermodynamic considerations:
-
 \begin{equation} \label{eq:LINEX}
-  y = Ae; 
-  A = \mathrm{e}^{a_0\left[2 \left(1 - \frac{1}{\rho_k} \right) 
-    + c_t \left(\vphantom{\frac{1}{\rho_k}}\rho_l - 1 \right)\right]},
+  y = \theta \; \mathrm{e}^{a_0\left[2 \left(1 - \frac{1}{\rho_k} \right) 
+    + c_t \left(\vphantom{\frac{1}{\rho_k}}\rho_l - 1 \right)\right]} \; e \;,
 \end{equation}
-
-\noindent where $e$ is indexed energy and e is the base of 
-the natural logarithm. The LINEX model assumes energy ($e$) 
-is the only factor of production. 
-The parameters $\rho_k$ and $\rho_l$ are defined as
+was derived from thermodynamic considerations
+\citep{Kummel:1980wx,Kummel:1982vy,Kummel:1985vz,Kummel:1989tf,Kummel:2002tx,Kummel:2010vz}. 
+%\noindent where $e$ is indexed energy and e is the base of 
+%the natural logarithm. 
+The LINEX model assumes energy ($e$) 
+is the only factor of production and defines
+the quantities $\rho_k$ and $\rho_l$ by
 
@@
 \end{equation}
-
-\noindent and
-
+and
 \begin{equation} \label{eq:rho_l}
@@
 \end{equation}
-
-\noindent and represent 
+and represent 
 (a) capital stock increase relative to the average of labor and energy and 
 (b) labor increase relative to energy, respectively. 
-Energy ($e$), as the only factor of production, is enhanced by $A$ if either
+Energy ($e$), as the only factor of production, is enhanced if either
 
@@
 and energy ($e$) will experience an increase in output ($y$) in excess 
-of its increase of energy consumption ($e$), because $A$ will be 
-greater than 1. Similarly, an economy benefits by increasing labor ($l$) 
+of its increase of energy consumption ($e$), because in that case
+\(
+A \equiv \mathrm{e}^{a_0\left[2 \left(1 - \frac{1}{\rho_k} \right) 
+    + c_t \left(\vphantom{\frac{1}{\rho_k}}\rho_l - 1 \right)\right]}
+	> 1 \;.
+\) 
+Similarly, an economy benefits by increasing labor ($l$) 
 without a commensurate increase in energy ($e$). Thus, $\rho_k$ is an 
@@
 
-\citet{Abramovitz:1956aa} wrote:
+\citet{Abramovitz:1956aa} wrote (but it unclear why this is here since the paper
+predates the definition of the model):
 
@@
 \ref{eq:CDe}) and the CES model (Equations~\ref{eq:CES}--\ref{eq:CESekl}), 
-the LINEX model (Equation~\ref{eq:LINEX}) attempts to explain the residual ($A$)
-with physical factors:
+the LINEX model (Equation~\ref{eq:LINEX}) does not include a generic time-dependent
+term but instead includes terms that represent % physical factors:
 efficiencies among capital, labor, and energy.
-Therefore, LINEX does not employ a time-dependent 
-residual term ($A$).
 

### 2014-03-03 Article/EconGrowth2.Rnw
Beginning rewrite of modeling and resamping discussion

@@
 % \biboptions{}
+
+\usepackage[shownotes]{authNote}
 
@@
 %the natural logarithm. 
-The LINEX model assumes energy ($e$) 
-is the only factor of production and defines
-the quantities $\rho_k$ and $\rho_l$ by
-
+In contrast to both the Cobb-Douglas model (Equations~\ref{eq:CD} and 
+\ref{eq:CDe}) and the CES model (Equations~\ref{eq:CES}--\ref{eq:CESekl}), 
+the LINEX model (Equation~\ref{eq:LINEX}) does not include a generic time-dependent
+term but assumes energy ($e$) is the only factor of production.
+
+This model does, however, 
+instead includes terms that represent % physical factors:
+efficiencies among capital, labor, and energy, which are included
+in the model in the form of 
+the quantities $\rho_k$ and $\rho_l$ which are defined by\footnote{The notation
+for the LINEX model breaks from the conventions used in the previous
+models:  $a_0$ and $c_t$ are parameters and $\rho_k$ and $\rho_l$ are not.}
+%
 \begin{equation} \label{eq:rho_k}
@@
 and represent 
-(a) capital stock increase relative to the average of labor and energy and 
-(b) labor increase relative to energy, respectively. 
-Energy ($e$), as the only factor of production, is enhanced if either
+(\ref{eq:rho_k}) capital stock increase relative to the average of labor and energy and 
+(\ref{eq:rho_l}) labor increase relative to energy.
+The effect of energy ($e$) on production is enhanced if either
 
@@
 \end{itemize}
-
-\noindent According to the LINEX model, an economy that increases 
+%
+According to the LINEX model, an economy that increases 
 capital stock ($k$) without a commensurate increase in labor ($l$) 
@@
 \(
-A \equiv \mathrm{e}^{a_0\left[2 \left(1 - \frac{1}{\rho_k} \right) 
+\mathrm{e}^{a_0\left[2 \left(1 - \frac{1}{\rho_k} \right) 
     + c_t \left(\vphantom{\frac{1}{\rho_k}}\rho_l - 1 \right)\right]}
@@
 of the labor efficiency term compared to the capital stock efficiency term. 
-We treat $a_0$ and $c_t$ as fitting parameters; 
-both are assumed constant with respect to time.
-
-\citet{Abramovitz:1956aa} wrote (but it unclear why this is here since the paper
-predates the definition of the model):
+% We treat $a_0$ and $c_t$ as fitting parameters; 
+% both are assumed constant with respect to time.
+
+\citet{Kummel:2002tx} use the 
+LINEX production function to describe economic output 
+for the economies of the U.S., Japan, and Germany. 
+\citet{Warr:2010ga} compare the LINEX production function with 
+the Cobb-Douglas production function to assess economic growth 
+for Austria, the United Kingdom, the United States, and Japan. 
+\citet{Ayres:2005kn} argued that introducing energy inputs 
+in traditional production functions does not improve its explanatory power, 
+but including useful work in a LINEX function does.
+
+\authNote{Martin: add more here about the conclusions of each paper 
+regarding the role of energy in economic growth? Add additional literature? 
+Or, adjust as you see fit. Especially, are there any confidence intervals 
+or statistical evaluation in each of these studies?}
+
+\authNote{If we want to keep this quote, it should be clearer what point we are trying to
+make with it. ---rjp}
+\citet{Abramovitz:1956aa} wrote:
 
 \begin{quote}
-  This result [that ``technological progress, $A$'' explained
+  This result [that ``technological progress'' explained
   175\% of the growth of the US economy since 1870] is surprising in the lopsided
@@
 \end{quote}
-
-In contrast to both the Cobb-Douglas model (Equations~\ref{eq:CD} and 
-\ref{eq:CDe}) and the CES model (Equations~\ref{eq:CES}--\ref{eq:CESekl}), 
-the LINEX model (Equation~\ref{eq:LINEX}) does not include a generic time-dependent
-term but instead includes terms that represent % physical factors:
-efficiencies among capital, labor, and energy.
-
-\citet{Kummel:2002tx} use the 
-LINEX production function to describe economic output 
-for the economies of the U.S., Japan, and Germany. 
-\citet{Warr:2010ga} compare the LINEX production function with 
-the Cobb-Douglas production function to assess economic growth 
-for Austria, the United Kingdom, the United States, and Japan. 
-\citet{Ayres:2005kn} argued that introducing energy inputs 
-in traditional production functions does not improve its explanatory power, 
-but including useful work in a LINEX function does.
-
-**** Martin: add more here about the conclusions of each paper 
-regarding the role of energy in economic growth? Add additional literature? 
-Or, adjust as you see fit. Especially, are there any confidence intervals 
-or statistical evaluation in each of these studies? ****
 
@@
 Tables~\ref{tab:Covariance_US}--\ref{tab:Covariance_ZM}. 
-**** Do we want to discuss the covariances? ****
-
+\authNote{Do we want to discuss the covariances?}
+
+\onecolumn{}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+\subsection{Point Estimates}
 Each of the economic growth models discussed in 
 Section~\ref{sec:Prod_Func_Forms} has parameters which must be estimated (fitted)
-for each economy (see Section~\ref{sec:Economy_Types})
-via least-squares methods. We used \texttt{R} \citep{R} functions
-\texttt{nls} and \texttt{cesEst} \citep{Henningsen:2011td} 
-for that purpose. The following subsections discuss 
-parameter estimation methods and results.
-
-%++++++++++++++++++++++++++++++
-\subsection{Resampling}
+from data for each economy (see Section~\ref{sec:Economy_Types}).
+We obtained parameter estimates by applying the method of least-squares to (potentially
+log-transformed) data using the \texttt{R} \citep{R} functions
+\texttt{lm} (for Cobb-Douglas and LINEX models) 
+and \texttt{cesEst} \citep{Henningsen:2011td} (for CES models). 
+\authNote{Need to check how CES is being fit and adjust this accordingly.}%
+
+Although the details vary from model to model, each of our three models has the general form
+\[
+y = f(t,k,l,e; \theta) + \mathrm{error} \;,
+\]
+where $\theta$ is a vector of parameters for the function $f$.
+\authNote{if we use $\theta$ this way, we need a new scaling parameter. --rjp}%
+In least squares models, parameter estimates are chosen to minimize
+\[
+\sum_{i} (y_i - f(t,k,l,e; \theta) )^2 \;.
+\]
+For the optimal parameter values $\hat \theta$, we define the 
+fitted response by
+\[
+\hat y_i = f(t_i, k_i, l_i, e_i; \hat \theta)
+\]
+and the residuals
+as the difference between the observed response and the fitted response
+\begin{equation} \label{eq:residual}
+  r_i 
+  = y_i - \hat y_i
+  = y_i - f(t,k,l,e; \hat\theta)
+\end{equation}
+The details for each of the models (including the effects of using 
+log transformations) are discussed below.
+
+%After back transforming to the natural scale of the data, the 
+%residuals have a multiplicative rather than additive affect.
+%The reflects an assumption that variability in GDP is roughly 
+%proportion to GDP rather than constant.
+
+%++++++++++++++++++++++++++++++
+\subsection{Resampling Methods}
 \label{sec:Resampling}
@@
 
-Resampling is a statistical technique for estimating the 
-precision of coefficient estimates. We implemented
-residual resampling in our parameter estimation processes.
-
-\onecolumn{}
-
-When employing resampling techniques, 
-the modeler assumes that the residuals ($r_t$) between 
-observed data (in our case historical GDP values, $y_{act,t}$) and
-model predictions (in our case, $y_{pred,t}$) at
-time $t$ are representative of the uncertainty of 
-and random scatter in the observed historical data.
-
-\begin{equation} \label{eq:residual}
-  r_t = y_{act,t} - y_{pred,t}
+Bootstrappng is a statistical resampling technique for assigning
+measures of accuracy and precision to sample estimates by measuring
+properties of an estimator when sampling from a resampling
+distribution.  Resampling distributions can be formed in a number of 
+ways in accordance with the type of data, experimental design,
+and modeling assumptions involved.  In each case, many new resamples 
+are created, each of which is a randomized version of the original sample data to 
+which the desired analysis method can be applied.  By investigating, for example,
+the variability of a parameter estimate from one resample to another,
+one can learn about the precision of the estimation method.
+\authNote{Add some references here. --rjp}
+
+In the context of linear models (regression), resamples are generally created
+by residual resampling.  In our case, we formed resamples by adding to the fitted 
+response (GDP) the product of a residual from the original model fit and 
+and random sign ($-1$ or $1$, each with probability $0.5$).  For the case of 
+Cobb-Douglas and LINEX models, this residual resampling occurs on the 
+log-transformed data.
+
+Intuitively, this method assumes that the residuals are indicative of 
+the variability (from many potential sources) inherent in the data so that
+it would be unsurprising if the residual from 
+any particular year had been observed in a different year. 
+Thus, a resampled response $\tilde Y$ can be computed as 
+\[
+\tilde Y_i' = \hat y_i \pm r_j
+\]
+where 
+\[
+r_i = y_i - \hat y_i
+\]
+both the sign ($\pm$) and the index of the residual ($j$, typically different from $i$) 
+are chosen at random (with replacement). 
+Resampling in this way has the consequence 
+that a resampled time series could have non-unity first-year GDP ($\tilde Y_1 \neq 1$),
+so a renormalization takes place using the initial GDP from the
+resampled data as the new baseline, not the observed GDP in year 1.
+
+\begin{equation} \label{eq:resample_y}
+	\tilde y_i  = \frac{\tilde Y_i'}{\tilde Y_1'}
 \end{equation}
-
-Under that assumption, it would be unsurprising if the residual from 
-any particular year had been observed in a different year. 
-To obtain a 
-preliminary resampled GDP time series ($y_{prelim,resample,t}$),
-we add
-the absolute value of residuals 
-from randomly-selected times $\left( \left| r_{\mathrm{rand}(t)} \right| \right)$
-with randomly-selected signs [$\mathrm{rand}(-1, 1)$]
-to model predictions.
-
-\begin{equation} \label{eq:resample_y_prelim}
-  y_{prelim,resample,t} = y_{pred,t} + \mathrm{rand}(-1, 1) \cdot \left| r_{\mathrm{rand}(t)} \right|.
-\end{equation}
-
-\noindent{}We note that the preliminary resample time series
-can have non-unity first-year GDP ($y_{prelim,resample,0} \ne 1$).
-If we had actually obtained the resampled GDP data series,
-we would have indexed to a different first-year GDP value, 
-such that \emph{every} resampled GDP time series has $y_{resample,0} = 1$.
-We use
-
-\begin{equation} \label{eq:resample_y}
-  y_{resample,t} = \frac{y_{prelim,resample,t}}{y_{prelim,resample,0}}
-\end{equation}
-
-\noindent{}to obtain a resampled indexed GDP time series that can be fitted using the techniques
-described below. 
+to obtain a resampled indexed GDP time series.
 We repeated the resampling process \Sexpr{numResamples()} times for each
@@
 
-The coefficients from the fit to the resampled time series
+The coefficients from the fit to a resampled time series
 (the ``resample coefficients'') will be different from the coefficients 
 obtained from the fit to historical data (the ``base coefficients'').
+When these resample coefficients are highly variable, it is an indication
+that the data do not determine the parameter estimates very precisely.
+Lack of imprecision can stem from a number of factors, most obviously
+a poor model fit, low model sensitivity to one or more parameters, 
+or correlations between parameter estimates.
+\authNote{This is not precisely true:
 Large residuals in the fit to historical data (the ``base fit'')
@@
 of the model coefficients.
+--rjp}
 
 It is important to note that large residuals can arise from either
-(a) poor quality historical time series data ($y_{act}$) or 
+(a) poor quality historical time series data, or 
 (b) a mathematical model that does not describe the underlying phenomena well.
-In both cases, we would not want to claim precise knowledge of the 
-fitted coefficients for an economic growth model. 
-So, it is appropriate that the resampling technique that we employed
-provides looser coefficient distributions when either (a) or (b) above
-is true. 
-After discussing the fitting technique for each 
-growth model below, we show scatter plots of fitted coefficients,
-thereby providing visual indication of the uncertainty 
-of the coefficients for each model.
-
-**** Randy Pruim review the above text and supply some text and references. ****
+It is also important to note that (c) even when the residuals are small and the 
+model produces fitted values that track the observed data closely, it may
+still be difficult to estimate some or all of the model parameters precisely.
+The resampling method employed reflects all three of these potential 
+sources of uncertainty in parameter estimates.
+
+\authNote{Should the description of model fitting come before or after 
+the description of resampling?}
 

### 2014-03-04 Article/EconGrowth2.Rnw
moving constants from pacakge to Rnw file

@@
 
+<<constants, include=FALSE>>=
+# Graph Heights
+#' @export
+maxHeight <- 8.5 # Inches
+#' @export
+ninePanelScatterGraphHeight <- maxHeight # Inches
+#' @export
+ninePanelTernaryGraphHeight <- 7 # Inches
+#' @export
+ninePanelSpaghettiGraphHeight <- 7 # Inches
+
+# Graph Widths
+#' @export
+maxWidth <- 6.5 # Inches
+#' @export
+fourPanelScatterGraphWidth <- maxWidth # Inches
+#' @export
+threePanelScatterGraphWidth <- maxWidth*0.75 # Inches
+#' @export
+onePanelScatterGraphWidth <- maxWidth*0.25
+#' @export
+fourPanelTernaryGraphWidth <- maxWidth
+#' @export
+twoPanelTernaryGraphWidth <- maxWidth*0.45
+#' @export
+fourPanelSpaghettiGraphWidth <- maxWidth
+#' @export
+twoPanelSpaghettiGraphWidth <- maxWidth*0.55
+#' @export
+onePanelSpaghettiGraphWidth <- maxWidth*0.4
+
+#' @export
+presentationGraph1RowHeight <- 2.8 # Inches
+#' @export
+presentationGraph2ColWidth <- 2 # Inches
+#' @export
+presentationGraph1ColWidth <- 2*presentationGraph2ColWidth
+#' @export
+keyTextSize <- 0.85 # 85% of normal size
+#' @export
+keyColumns <- 1 # Want only 1 column in the key for lattice graphs
+#' @export
+defaultKeyXLoc <- 0.01 # x position of the key. This default is good for 9-panel graphs.
+#' @export
+defaultKeyYLoc <- 0.95 # y position of the key. This default is good for 9-panel graphs.
+# Parameter graphs are tricky to ensure same size. I've found that with height set to 5 in for the 
+# cd graphs and 2.93 in for the sf graphs, I get a nearly-exact match with graph size. From these settings I 
+# can set up 2 equations:
+#    5 in = 2*hgraph + haxis
+#    2.93 in = hgraph + haxis
+# to estimate that h_axis = 0.86 in and hgraph = 2.05 in.
+#' @export
+h_param_graph <- 2.07 # Inches for a single panel
+#' @export
+h_param_axis <- 0.86 # Inches (also includes whatever margin is applied)
+#' @export
+sfParameterGraphHeight <- h_param_graph + h_param_axis
+#' @export
+cdParameterGraphHeight <- 2*h_param_graph + h_param_axis
+#' @export
+cesParameterGraphHeight <- 3*h_param_graph + h_param_axis
+#' @export
+linexParameterGraphHeight <- h_param_graph + h_param_axis
+#' @export
+sfParameterGraphWidth <- maxWidth
+#' @export
+cdParameterGraphWidth <- maxWidth
+#' @export
+cdTernaryGraphWidth <- maxWidth/2.2
+#' @export
+cdSpaghettiGraphWidth <- maxWidth/2.2
+#' @export
+cesParameterGraphWidth <- maxWidth
+#' @export
+linexParameterGraphWidth <- maxWidth
+# Other graph parameters that apply to all graphs
+#' @export
+scaleTextSize <- 0.8  # Multiple of normal size
+#' @export
+scaleTickSize <- -0.5 # 50% of normal size and pointing INWARD!
+
+@
+
 % Add an argument if you want a label. Example: "\label{eq:CES}"

### 2014-03-27 Article/EconGrowth2.Rnw
Added definition of spaghettiGraphLevel to the EconGrowth2.Rnw file.
Removed #' @export from spaghettiGraphLevel.

--- 2014-03-03 Article/EconGrowth2.Rnw
@@
 
+<<constants, include=FALSE>>=
+# Graph Heights
+# #' @export
+maxHeight <- 8.5 # Inches
+# #' @export
+ninePanelScatterGraphHeight <- maxHeight # Inches
+# #' @export
+# ninePanelTernaryGraphHeight <- 7 # Inches
+# #' @export
+# ninePanelSpaghettiGraphHeight <- 7 # Inches
+
+# Graph Widths
+# #' @export
+maxWidth <- 6.5 # Inches
+# #' @export
+fourPanelScatterGraphWidth <- maxWidth # Inches
+# #' @export
+# threePanelScatterGraphWidth <- maxWidth*0.75 # Inches
+# #' @export
+# onePanelScatterGraphWidth <- maxWidth*0.25
+# #' @export
+# fourPanelTernaryGraphWidth <- maxWidth
+# #' @export
+# twoPanelTernaryGraphWidth <- maxWidth*0.45
+# #' @export
+# fourPanelSpaghettiGraphWidth <- maxWidth
+# #' @export
+# twoPanelSpaghettiGraphWidth <- maxWidth*0.55
+# #' @export
+# onePanelSpaghettiGraphWidth <- maxWidth*0.4
+
+#' @export
+presentationGraph1RowHeight <- 2.8 # Inches
+#' @export
+presentationGraph2ColWidth <- 2 # Inches
+#' @export
+presentationGraph1ColWidth <- 2*presentationGraph2ColWidth
+# #' @export
+# keyTextSize <- 0.85 # 85% of normal size
+# #' @export
+# keyColumns <- 1 # Want only 1 column in the key for lattice graphs
+# #' @export
+# defaultKeyXLoc <- 0.01 # x position of the key. This default is good for 9-panel graphs.
+# #' @export
+# defaultKeyYLoc <- 0.95 # y position of the key. This default is good for 9-panel graphs.
+# Parameter graphs are tricky to ensure same size. I've found that with height set to 5 in for the 
+# cd graphs and 2.93 in for the sf graphs, I get a nearly-exact match with graph size. From these settings I 
+# can set up 2 equations:
+#    5 in = 2*hgraph + haxis
+#    2.93 in = hgraph + haxis
+# to estimate that h_axis = 0.86 in and hgraph = 2.05 in.
+# #' @export
+h_param_graph <- 2.07 # Inches for a single panel
+# #' @export
+h_param_axis <- 0.86 # Inches (also includes whatever margin is applied)
+# #' @export
+# sfParameterGraphHeight <- h_param_graph + h_param_axis
+# #' @export
+cdParameterGraphHeight <- 2*h_param_graph + h_param_axis
+# #' @export
+cesParameterGraphHeight <- 3*h_param_graph + h_param_axis
+# #' @export
+linexParameterGraphHeight <- h_param_graph + h_param_axis
+# #' @export
+sfParameterGraphWidth <- maxWidth
+# #' @export
+cdParameterGraphWidth <- maxWidth
+# #' @export
+# cdTernaryGraphWidth <- maxWidth/2.2
+# #' @export
+# cdSpaghettiGraphWidth <- maxWidth/2.2
+# #' @export
+cesParameterGraphWidth <- maxWidth
+# #' @export
+linexParameterGraphWidth <- maxWidth
+# Other graph parameters that apply to all graphs
+# #' @export
+scaleTextSize <- 0.8  # Multiple of normal size
+# #' @export
+scaleTickSize <- -0.5 # 50% of normal size and pointing INWARD!
+
+spaghettiGraphLevel <- 0.95 # Spaghetti graph bands will encompass 95% of the data.
+@
+
+% These equations are used in several locations in the paper.
+% By defining commands for them, we ensure consistent appearance
+% of the equations when they are used.
+
 % Add an argument if you want a label. Example: "\label{eq:CES}"

### 2014-03-29 Article/EconGrowth2.Rnw
Now using baseHistorical and baseResample paths to data.

@@
 )
-#source("Econ-Growth-Functions2.R")
-#source("Graphics.R")
 @
@@
 spaghettiGraphLevel <- 0.95 # Spaghetti graph bands will encompass 95% of the data.
+
+# In Rstudio, this paper is generated from it's directory, which is "Article".
+# We need to define paths relative to the location of the paper. 
+# Relative path to historical data from Article
+baseHistorical <- file.path("..", "data")
+# We also need to define a directory path to the resample data results from "Article"
+baseResample <- file.path("..", "data_resample")
 @
@@
 <<Historical_Lattice_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=7.5, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), and thermal energy ($q$).">>=
-historicalPlot()
+historicalPlot(baseHistorical=baseHistorical)
 @
@@
 <<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=2.9, fig.height=7.7, fig.cap="Cobb-Douglas resample model parameters.">>=
-  dataCD <- loadAllResampleData(modelType="cd", countryAbbrevsOrder=countryAbbrevs, energyType="none")
-  dataCDQ <- loadAllResampleData(modelType="cde", energyType="Q", countryAbbrevsOrder=countryAbbrevs)
+  dataCD <- loadAllResampleData(modelType="cd", countryAbbrevsOrder=countryAbbrevs, energyType="none", baseResample=baseResample)
+  dataCDQ <- loadAllResampleData(modelType="cde", countryAbbrevsOrder=countryAbbrevs, energyType="Q", baseResample=baseResample)
   data <- rbind.fill(dataCD, dataCDQ)
@@
 <<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=8.2, fig.cap="Cobb-Douglas fitted models.">>=
-cdData <- loadCDSpaghettiGraphData(energyType="none")
-cdQData <- loadCDSpaghettiGraphData(energyType="Q")
+cdData <- loadCDSpaghettiGraphData(energyType="none", baseHistorical=baseHistorical, baseResample=baseResample)
+cdQData <- loadCDSpaghettiGraphData(energyType="Q", baseHistorical=baseHistorical, baseResample=baseResample)
 cdData <- rbind(cdData, cdQData)
@@
 <<CES_lambda_gamma_graph, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models.">>=
-cesQResampleData <- loadCESResampleData(nest="all", energyType="Q")
+cesQResampleData <- loadCESResampleData(nest="all", energyType="Q", baseResample=baseResample)
 standardScatterPlot(data=cesQResampleData, mapping=aes(gamma_coef, lambda), facet_formula=countryAbbrev~nest, alpha=0.05) +
@@
 <<CES_ternary_graph, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models.">>=
-cesTriPlotData=loadCESResampleData(energyType="Q", nest="all")
+cesTriPlotData=loadCESResampleData(energyType="Q", nest="all", baseResample=baseResample)
 standardTriPlot(data=cesTriPlotData)
@@
 <<CES_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models.">>=
-spagData <- loadCESSpaghettiGraphData(energyType="Q", nest="all")
+spagData <- loadCESSpaghettiGraphData(energyType="Q", nest="all", baseHistorical=baseHistorical, baseResample=baseResample)
 spaghettiPlot(data=spagData, facet_formula=Country~nest, level=spaghettiGraphLevel)+
@@
 for Zambia (ZM) with thermal energy ($q$), where
-\Sexpr{fracUnconvergedResampleFits(modelType="linex", countryAbbrev="ZM", energyType="Q")*100}\%
+\Sexpr{fracUnconvergedResampleFits(modelType="linex", countryAbbrev="ZM", energyType="Q", baseResample=baseResample)*100}\%
 of the resample fits did not converge. 
@@
 <<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7, fig.cap="LINEX model (with energy) resampling results.">>=
-  linexResampleData <- loadAllResampleData(model="linex", energyType="Q", countryAbbrevsOrder=countryAbbrevs)
+  linexResampleData <- loadAllResampleData(model="linex", energyType="Q", countryAbbrevsOrder=countryAbbrevs, 
+                                           baseResample=baseResample)
   standardScatterPlot(data=linexResampleData, aes(a_0, c_t), facet_formula=countryAbbrev~energy, alpha=0.05) +
@@
 <<LINEX_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7.1, fig.cap="LINEX fitted models.">>=
-spagDataLinex <- loadLinexSpaghettiGraphData(energyType="Q")
+spagDataLinex <- loadLinexSpaghettiGraphData(energyType="Q", baseHistorical=baseHistorical, baseResample=baseResample)
 spaghettiPlot(data=spagDataLinex, facet_formula=Country ~ Energy, level=spaghettiGraphLevel) +
@@
 <<Unconverged_Frac_Table, results='asis'>>=
-printFracUnconvergedXtable()
+# printFracUnconvergedXtable()
+  data <- fracUnconvergedResampleFitsAll(baseResample=baseResample)
+  dataXtable <- xtable(x=data, 
+                       caption="Fraction of unconverged resample models", 
+                       label="tab:frac_unconverged_models",
+                       digits = 3,
+                       align = "rl|cc|ccccccccc") #Sets alignment of the numbers in the columns)
+  print(dataXtable, 
+        caption.placement="top", 
+        size="\\tiny",
+        table.placement="H",
+        include.rownames=FALSE)
 @
@@
 <<CD_Params_Table, results='asis'>>=
-printCDParamsTable(energyType="none")    #Without energy
-@
-
-The data in Table~\ref{tab:CD_Parameters_No_Energy} is plotted in
+printCDParamsTable(energyType="none", baseResample=baseResample)    #Without energy
+@
+
+The data in Table~\ref{tab:CD_Parameters_No_Energy} are plotted in
 Figure~\ref{fig:CD_Params_Graph}.
@@
 Vertical bars indicate 95\\% confidence intervals.">>=
-createCDParamsGraph(energyType="none")
+createCDParamsGraph(energyType="none", baseResample=baseResample)
 @
@@
 <<CDq_Params_Table, results='asis'>>=
-printCDParamsTable(energyType="Q")   #With energy
+printCDParamsTable(energyType="Q", baseResample=baseResample)   #With energy
 @
@@
 Vertical bars indicate 95\\% confidence intervals.">>=
-createCDParamsGraph(energyType="Q")
+createCDParamsGraph(energyType="Q", baseResample=baseResample)
 @
@@
 <<CES_Params_Table, results='asis'>>=
-printCESParamsTableA(energyType="none")
-printCESParamsTableB(energyType="none")
+print(cesParamsTableA(energyType="none", nest="(kl)", baseResample=baseResample), 
+      caption.placement="top", 
+      sanitize.colnames.function = identity, 
+      size="\\tiny",
+      table.placement="H")
+print(cesParamsTableB(energyType="none", nest="(kl)", baseResample=baseResample), 
+      caption.placement="top", 
+      sanitize.colnames.function = identity, 
+      size="\\tiny",
+      table.placement="H")
 @
@@
 Vertical bars indicate 95\\% confidence intervals.">>=
-createCESParamsGraph(energyType="none")
+createCESParamsGraph(energyType="none", nest="(kl)", baseResample=baseResample)
 @
@@
 <<CESq_Params_Table_kle, results='asis'>>=
-printCESParamsTableA(energyType="Q", nest="(kl)e")
-printCESParamsTableB(energyType="Q", nest="(kl)e")
+print(cesParamsTableA(energyType="Q", nest="(kl)e", baseResample=baseResample), 
+      caption.placement="top", 
+      sanitize.colnames.function = identity, 
+      size="\\tiny",
+      table.placement="H")
+print(cesParamsTableB(energyType="Q", nest="(kl)e", baseResample=baseResample), 
+      caption.placement="top", 
+      sanitize.colnames.function = identity, 
+      size="\\tiny",
+      table.placement="H")
+
 @
@@
 Vertical bars indicate 95\\% confidence intervals.">>=
-createCESParamsGraph(energyType="Q", nest="(kl)e")
+createCESParamsGraph(energyType="Q", nest="(kl)e", baseResample=baseResample)
 @
@@
 <<CESq_Params_Table_lek, results='asis'>>=
-printCESParamsTableA(energyType="Q", nest="(le)k")
-printCESParamsTableB(energyType="Q", nest="(le)k")
+print(cesParamsTableA(energyType="Q", nest="(le)k", baseResample=baseResample), 
+      caption.placement="top", 
+      sanitize.colnames.function = identity, 
+      size="\\tiny",
+      table.placement="H")
+print(cesParamsTableB(energyType="Q", nest="(le)k", baseResample=baseResample), 
+      caption.placement="top", 
+      sanitize.colnames.function = identity, 
+      size="\\tiny",
+      table.placement="H")
+
 @
@@
 Vertical bars indicate 95\\% confidence intervals.">>=
-createCESParamsGraph(energyType="Q", nest="(le)k")
+createCESParamsGraph(energyType="Q", nest="(le)k", baseResample=baseResample)
 @
@@
 <<CESq_Params_Table_ekl, results='asis'>>=
-printCESParamsTableA(energyType="Q", nest="(ek)l")
-printCESParamsTableB(energyType="Q", nest="(ek)l")
+print(cesParamsTableA(energyType="Q", nest="(ek)l", baseResample=baseResample), 
+      caption.placement="top", 
+      sanitize.colnames.function = identity, 
+      size="\\tiny",
+      table.placement="H")
+print(cesParamsTableB(energyType="Q", nest="(ek)l", baseResample=baseResample), 
+      caption.placement="top", 
+      sanitize.colnames.function = identity, 
+      size="\\tiny",
+      table.placement="H")
+
 @
@@
 Vertical bars indicate 95\\% confidence intervals.">>=
-createCESParamsGraph(energyType="Q", nest="(ek)l")
+createCESParamsGraph(energyType="Q", nest="(ek)l", baseResample=baseResample)
 @
@@
 <<LINEX_Params_Table, results='asis'>>=
-printLINEXParamsTable(energyType="Q")
+print(linexParamsTable(energyType="Q", baseResample=baseResample), 
+      caption.placement="top", 
+      sanitize.colnames.function = identity, 
+      size="\\tiny",
+      table.placement="H")
 @
@@
 <<LINEXq_Params_Graph, fig.pos="H", fig.width=linexParameterGraphWidth, fig.height=linexParameterGraphHeight, fig.cap="LINEX model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
-createLINEXParamsGraph(energyType="Q")
+createLINEXParamsGraph(energyType="Q", baseResample=baseResample)
 @

### 2014-03-29 batchEcon.R

@@ -1,14 +1,14 @@
 #!/usr/bin/Rscript  --default-packages=utils,stats,lattice,grid,mosaic,methods,graphics,foreach,doParallel,plyr,xtable,nlmrt,micEconCES,systemfit,Matrix,lmtest,zoo,miscTools,micEcon,minpack.lm,DEoptim,iterators,parallel,latticeExtra,RColorBrewer,ggplot2,reshape2,scales
 
 # Example usage:
-# Move into a subdirectory (such as "Article")
-# for US, exergy, linex model, 10 resamples, clobbering previous results, and wild resampling:
-# ../batchEcon.R -c US -e X -m linex -n 10 -C -M wild
-# for all countries, all energy types, all models, 1000 resamples, clobber previous results, wild resampling:
-# ../batchEcon.R -c all -e all -m all -n 1000 -C -M wild
 
-print(sort(.packages()))
-# source('Econ-Growth-Resampling.R',echo=FALSE,verbose=FALSE)
+# Move into the top level directory that contains this file
+# for US, exergy, linex model, 10 resamples, clobbering previous results, and wild resampling:
+# ./batchEcon.R -c US -e X -m linex -n 10 -C -M wild -H data -R data_resample
+# for all countries, all energy types, all models, 1000 resamples, clobber previous results, wild resampling:
+# ./batchEcon.R -c all -e all -m all -n 1000 -C -M wild -H data -R data_resample
+
+# print(sort(.packages()))
 require(EconModels)
 suppressPackageStartupMessages(library("optparse"))
 
@@ -28,10 +28,15 @@ option_list <- list(
   make_option(c("-d", "--debug"), default=FALSE, action="store_true",
               help="runs without executing the resampling [default=%default]"),
   make_option(c("-M", "--method"), default="wild", 
-              help="resampling method [default=%default]")
+              help="resampling method [default=%default]"),
+  make_option(c("-H", "--baseHistorical"), # default="data", 
+              help="relative path to directory for historical data"),
+  make_option(c("-R", "--baseResample"), # default="data_resample", 
+              help="relative path to directory for resample data")
 )
 
 opts <- parse_args(OptionParser(option_list=option_list))
+# print(opts)
 
 if(opts$model == "all") {
   opts$model <- modelTypes
@@ -64,7 +69,6 @@ if(opts$factor== "all") {
 }
 
 print(str(opts))
-print(sort(.packages()))
 
 startTime <- proc.time()
 cat("\n\nStart @ ")
[…]

### 2014-04-21 Article/EconGrowth2.Rnw
Added microtype package.
Now the article (EconGrowth2.Rnw) loads the original models.

@@
 \usepackage{hyperref}   % To create hyperlinks in the paper
+\usepackage{microtype}  % produces hanging punctuation and beautiful type
 
@@
 baseResample <- file.path("..", "data_resample")
+
+# Load the fits to the original historical data
+# This object should be passed in to functions that need specific fits.
+oModels <- readRDS(file=file.path(baseResample, "oModels.Rdata"))
 @

### 2014-04-22 Scrap/CES.Rnw
Now using iK, iL, iY for data columns. batchEcon2.R now working.

@@
 modelUKQ_LM <- cesEstPlus(data=dataUK, 
-                      yName="iGDP", 
-                      xNames=c("iCapStk", "iLabor", "iQ"), 
+                      yName="iY", 
+                      xNames=c("iK", "iL", "iQ"), 
                       tName="iYear")
@@
 modelUKQ_LM2 <- cesEstPlus(data=dataUK, 
-                      yName="iGDP", 
-                      xNames=c("iLabor", "iQ", "iCapStk"), 
+                      yName="iY", 
+                      xNames=c("iL", "iQ", "iK"), 
                       tName="iYear")
@@
 modelUKQ_LBFGSB <- cesEstPlus(data=dataUK, 
-                          yName="iGDP", 
-                          xNames=c("iCapStk", "iLabor", "iQ"), 
+                          yName="iY", 
+                          xNames=c("iK", "iL", "iQ"), 
                           tName="iYear",
@@
 modelUKQ_grid <- cesEstPlus(data=dataUK, 
-                        yName="iGDP", 
-                        xNames=c("iCapStk", "iLabor", "iQ"), 
+                        yName="iY", 
+                        xNames=c("iK", "iL", "iQ"), 
                         tName="iYear",
@@
 modelUKQ_grid_detail <- cesEstPlus(data=dataUK, 
-                        yName="iGDP", 
-                        xNames=c("iCapStk", "iLabor", "iQ"), 
+                        yName="iY", 
+                        xNames=c("iK", "iL", "iQ"), 
                         tName="iYear",
@@
 modelUK <- cesEstPlus(data=dataUK, 
-                        yName="iGDP", 
-                        xNames=c("iCapStk", "iLabor"), 
+                        yName="iY", 
+                        xNames=c("iK", "iL"), 
                         tName="iYear",

### 2014-04-22 Scrap/EconGrowth-R-Functions.Rnw
Now using iK, iL, iY for data columns. batchEcon2.R now working.

--- 2013-05-28 EconGrowth-R-Functions.Rnw
@@
   } else if (factor == "Y"){
-    colName <- "iGDP"
+    colName <- "iY"
   } else if (factor == "K"){
-    colName <- "iCapStk"
+    colName <- "iK"
   } else if (factor == "L"){
-    colName <- "iLabor"
+    colName <- "iL"
   } else if (factor == "Q"){
@@
     # Calculate covariances among the typical variables.
-    dataForCovar <- cbind(data$iGDP, data$iCapStk, data$iLabor, data$iQ, data$iX, data$iU)
+    dataForCovar <- cbind(data$iY, data$iK, data$iL, data$iQ, data$iX, data$iU)
     # Calculates the covariances among y, k. l, q, x, and u using all available data, namely,
@@
   } else {
-    dataForCovar <- cbind(data$iGDP, data$iCapStk, data$iLabor, data$iQ, data$iX)
+    dataForCovar <- cbind(data$iY, data$iK, data$iL, data$iQ, data$iX)
     covarResults <- cor(dataForCovar)
@@
   }
-  graph <- xyplot(iGDP+iCapStk+iLabor+iQ+iX+iU ~ Year | Country, data=dataTable,
+  graph <- xyplot(iY+iK+iL+iQ+iX+iU ~ Year | Country, data=dataTable,
                   type = graphType,
@@
   # Runs a non-linear least squares fit to the data. We've replaced beta with 1-alpha for simplicity.
-  model <- iGDP ~ exp(lambda*iYear) * f^m
+  model <- iY ~ exp(lambda*iYear) * f^m
   modelSF <- nls(formula=model, data=dataTable, start = start)
-#   model <- iGDP ~ exp(lambda*iYear) * f^m
+#   model <- iY ~ exp(lambda*iYear) * f^m
 #   modelSF <- wrapnls(formula=model, data=dataTable, start=list(lambda=lambdaGuess, m=mGuess))
@@
   }  
-  graph <- xyplot(iGDP+predGDPK+predGDPL+predGDPQ+predGDPX+predGDPU ~ Year | Country, data=dataTable,
+  graph <- xyplot(iY+predGDPK+predGDPL+predGDPQ+predGDPX+predGDPU ~ Year | Country, data=dataTable,
                   type=graphType,
@@
   data <- loadData(countryAbbrev)
-  y_act <- data[ ,"iGDP"] # Pick off the GDP column
+  y_act <- data[ ,"iY"] # Pick off the GDP column
   y_act <- data.frame(y_act)
@@
   # Runs a non-linear least squares fit to the data. We've replaced beta with 1-alpha for simplicity.
-  model <- iGDP ~ exp(lambda*iYear) * iCapStk^alpha * iLabor^(1 - alpha)
+  model <- iY ~ exp(lambda*iYear) * iK^alpha * iL^(1 - alpha)
   modelCD <- nls(formula=model, data=dataTable, start=start,
@@
   # * gamma = 1 - max(a, b)
-  model <- iGDP ~ exp(lambda*iYear) * iCapStk^min(a,b) * iLabor^abs(b-a) * iEToFit^(1.0 - max(a,b))
+  model <- iY ~ exp(lambda*iYear) * iK^min(a,b) * iL^abs(b-a) * iEToFit^(1.0 - max(a,b))
   modelCDe <- nls(formula=model, data = dataTable, start = start,
@@
   start <- list(lambda=lambdaGuess, alpha=alphaGuess)
-  model <- iGDP ~ exp(lambda*iYear) * iCapStk^alpha * iLabor^((1-gamma) - alpha) * iEGamma
+  model <- iY ~ exp(lambda*iYear) * iK^alpha * iL^((1-gamma) - alpha) * iEGamma
   modelCDe <- nls(formula=model, data = dataTable, start = start,
@@
   }
-  graph <- xyplot(iGDP+predGDP+predGDPQ+predGDPX+predGDPU ~ Year | Country, data=dataTable,
+  graph <- xyplot(iY+predGDP+predGDPQ+predGDPX+predGDPU ~ Year | Country, data=dataTable,
                   type=graphType,
@@
 # Set some common names for CES variables.
-xNamesWithoutEnergy = c("iCapStk", "iLabor")
-xNamesWithEnergy = c("iCapStk", "iLabor", "iEToFit")
+xNamesWithoutEnergy = c("iK", "iL")
+xNamesWithEnergy = c("iK", "iL", "iEToFit")
 tName = "iYear"
-yName = "iGDP"
+yName = "iY"
 
@@
   # Trim data from China and South Africa that is missing labor information for 2011.
-  dataTable <- subset(dataTable, !is.na(iLabor))
+  dataTable <- subset(dataTable, !is.na(iL))
   if (is.na(energyType)){
@@
   # Runs a non-linear least squares fit to the data with constraints
-  modelLINEX <- nls(iGDP ~ iEToFit * exp(a_0*(2.0 - (iLabor+iEToFit)/iCapStk) + a_0 * c_t *(iLabor/iEToFit - 1.0)), 
+  modelLINEX <- nls(iY ~ iEToFit * exp(a_0*(2.0 - (iL+iEToFit)/iK) + a_0 * c_t *(iL/iEToFit - 1.0)), 
                   data=dataTable,
@@
   }  
-  graph <- xyplot(iGDP+predGDPQ+predGDPX+predGDPU ~ Year | Country, data=dataTable,
+  graph <- xyplot(iY+predGDPQ+predGDPX+predGDPU ~ Year | Country, data=dataTable,
                   type=graphType,

### 2014-04-22 Testing/ExperimentingWithPlots.Rnw
Now using iK, iL, iY for data columns. batchEcon2.R now working.

\documentclass{article}

\begin{document}

<<message=FALSE>>=
require(knitr)
opts_chunk$set(
  dev="pdf",
  tidy=FALSE
)
require(ggplot2)
require(plyr)
source('Econ-Growth-Functions2.R')
@

<<plot1>>=
for (nest in c("(kl)e", "(le)k", "(ek)l") ) {
  nestData <- loadCESSpaghettiGraphData("Q", nest= nest, 
                archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
  print( 
    qplot( Year, iY, group=ResampleNumber, 
           data=nestData, # subset(foo, Country=="US"), 
           facets = ~Country, geom="line", alpha=I(0.15) ) + 
      geom_line(data=subset(nestData, Type=="actual"), 
                colour="red") +
      labs(title=nest) +
      theme_minimal()
  )
}
@

\end{document}

### 2014-04-22 Scrap/Econ-Growth-Functions2.R

@@ -249,11 +249,11 @@ columnIndex <- function(data, factor){
   if (factor == "Year"){
     colName <- "iYear"
   } else if (factor == "Y"){
-    colName <- "iGDP"
+    colName <- "iY"
   } else if (factor == "K"){
-    colName <- "iCapStk"
+    colName <- "iK"
   } else if (factor == "L"){
-    colName <- "iLabor"
+    colName <- "iL"
   } else if (factor == "Q"){
     colName <- "iQ"
   } else if (factor == "X"){
@@ -290,7 +290,7 @@ covarianceTable <- function(countryAbbrev){
   data <- loadData(countryAbbrev)
   if (countryAbbrev %in% countryAbbrevsU){
     # Calculate covariances among the typical variables.
-    dataForCovar <- cbind(data$iGDP, data$iCapStk, data$iLabor, data$iQ, data$iX, data$iU)
+    dataForCovar <- cbind(data$iY, data$iK, data$iL, data$iQ, data$iX, data$iU)
     # Calculates the covariances among y, k. l, q, x, and u using all available data, namely,
     # 1980-2011 for covariances among y, k, l, q, and x for developed economies
     # 1980-2000 for covariances involving u for developed economies
@@ -299,7 +299,7 @@ covarianceTable <- function(countryAbbrev){
     covarResults <- data.frame(cor(x=dataForCovar, use="pairwise.complete.obs"))
     names <- c("$y$", "$k$", "$l$", "$q$", "$x$", "$u$")
   } else {
-    dataForCovar <- cbind(data$iGDP, data$iCapStk, data$iLabor, data$iQ, data$iX)
+    dataForCovar <- cbind(data$iY, data$iK, data$iL, data$iQ, data$iX)
     covarResults <- cor(dataForCovar)
     names <- c("$y$", "$k$", "$l$", "$q$", "$x$")
   }
@@ -361,9 +361,9 @@ createHistoricalLatticeGraphOld <- function(countryAbbrev, textScaling = 1.0, ke
     layout <- onePanelLayoutSpec                      # We want only one panel in the graph.
   }
   graph <- ggplot(aes(x=Year), data=data) +
-    geom_line(aes(y=iGDP, lty="iGPD")) +
-    geom_line(aes(y=iCapStk, lty="iCapStk")) +
-    geom_line(aes(y=iLabor, lty="iLabor")) +
[…]

### 2014-04-22 Scrap/Graphics.R

@@ -173,15 +173,15 @@ spaghettiPlot <- function(energyType='none',
   data$alph = alph
   split <- intersect( split, names(data) )
   seData <- ddply( subset(data, Type=="fitted"), split, summarise, 
-                   n = length(iGDP),
-                   lower= quantile(iGDP, alph[1]),
-                   upper= quantile(iGDP, 1-alph[1]),
-                   iGDP = iGDP[1]
+                   n = length(iY),
+                   lower= quantile(iY, alph[1]),
+                   upper= quantile(iY, 1-alph[1]),
+                   iY = iY[1]
   ) 
   # return(seData)
   # return(names(data))
-  # graph <- qplot(Year, iGDP, group=ResampleNumber, data=data, facets = ~Country, geom="line", alpha=I(alpha))
-  graph <- ggplot( data=subset(data, Type=="actual"), aes(Year, iGDP)) 
+  # graph <- qplot(Year, iY, group=ResampleNumber, data=data, facets = ~Country, geom="line", alpha=I(alpha))
+  graph <- ggplot( data=subset(data, Type=="actual"), aes(Year, iY)) 
   graph <- graph + geom_smooth(aes(ymin=lower, ymax=upper), col=NA, fill="gray10", 
                                lty=1, size=.5, data=seData, stat="identity")
 #  graph <- graph + geom_area(fill="black", shape=1, alpha=0.05)
@@ -216,9 +216,9 @@ historicalPlot <- function(countryAbbrev){
     data <- loadData(countryAbbrev)
   }
   graph <- ggplot(aes(x=Year), data=data) +
-    geom_line(aes(y=iGDP, lty="y")) +
-    geom_line(aes(y=iCapStk, lty="k")) +
-    geom_line(aes(y=iLabor, lty="l")) +
+    geom_line(aes(y=iY, lty="y")) +
+    geom_line(aes(y=iK, lty="k")) +
+    geom_line(aes(y=iL, lty="l")) +
     geom_line(aes(y=iQ, lty="q")) +
     facet_grid( Country ~ ., scales="free_y" ) +
     ylab("Indexed (1980=1 or 1991=1)") +

### 2014-04-22 Scripts/BaseModels.R

@@ -19,28 +19,28 @@ Countries <- unique(All$Country)
 Energies <- c("iQ", "iX", "iU")
 
 ModelInfos <- list(
-  list( formulaStr = c("iGDP ~ iCapStk + iYear", 
-                       "iGDP ~ iLabor + iYear",
-                       "iGDP ~ energy + iYear"),
+  list( formulaStr = c("iY ~ iK + iYear", 
+                       "iY ~ iL + iYear",
+                       "iY ~ energy + iYear"),
         fun = "singleFactorModel",
         dots = list()),
-  list( formulaStr = c("iGDP ~ iCapStk + iLabor + iYear",
-                       "iGDP ~ iCapStk + iLabor + energy + iYear"),
+  list( formulaStr = c("iY ~ iK + iL + iYear",
+                       "iY ~ iK + iL + energy + iYear"),
         fun = "cobbDouglasModel",
         dots = list()),
-  list( formulaStr = "iGDP ~ iCapStk + iLabor + energy + iYear",
+  list( formulaStr = "iY ~ iK + iL + energy + iYear",
         fun = "linexModel",
         dots = list()),
-  list( formulaStr = "iGDP ~ iCapStk + iLabor + iYear",
+  list( formulaStr = "iY ~ iK + iL + iYear",
         fun = "cesModel",
         dots = list(nest=1:2)),
-  list( formulaStr = "iGDP ~ iCapStk + iLabor + energy + iYear",
+  list( formulaStr = "iY ~ iK + iL + energy + iYear",
         fun = "cesModel",
         dots = list(nest=1:3)),
-  list( formulaStr = "iGDP ~ iCapStk + iLabor + energy + iYear",
+  list( formulaStr = "iY ~ iK + iL + energy + iYear",
         fun = "cesModel",
         dots = list(nest=c(2,3,1))),
-  list( formulaStr = "iGDP ~ iCapStk + iLabor + energy + iYear",
+  list( formulaStr = "iY ~ iK + iL + energy + iYear",
         fun = "cesModel",
         dots = list(nest=c(1,3,2)))
 )
@@ -59,7 +59,7 @@ for (country in Countries) {
       for (energy in if (grepl("energy", f))  Energies else 'noEnergy') {
         formulaStr <- sub( "energy", energy, f ) 
         formula <- eval( parse( text= formulaStr ) )
-        # formula <- substitute( iGDP ~ iCapStk + iLabor + e + iYear, list(e = energy))
[…]

### 2014-04-22 Testing/RefactorTesting.R

@@ -2,36 +2,36 @@ require(EconModels2)
 
 All <- read.table("data/AllData.txt", header=TRUE)
 
-model.cd1 <-  cdModel( response = iGDP, capital=iCapStk, labor=iLabor, time=iYear, data=subset(All, Country=="US") )
+model.cd1 <-  cdModel( response = iY, capital=iK, labor=iL, time=iYear, data=subset(All, Country=="US") )
 naturalCoef( model.cd1 )
 
-model.cd2 <- cdModel( iGDP ~ iCapStk + iLabor + iYear, data=subset(All, Country=="US") )
+model.cd2 <- cdModel( iY ~ iK + iL + iYear, data=subset(All, Country=="US") )
 naturalCoef( model.cd2 )
 
-model.cde1 <- cdeModel( response = iGDP, capital=iCapStk, labor=iLabor, energy=iU, time=iYear, data=subset(All, Country=="US") )
+model.cde1 <- cdeModel( response = iY, capital=iK, labor=iL, energy=iU, time=iYear, data=subset(All, Country=="US") )
 naturalCoef( model.cde1)
 
-model.cde2 <- cdeModel( iGDP ~ iCapStk + iLabor + iU + iYear, data=subset(All, Country=="US") )
+model.cde2 <- cdeModel( iY ~ iK + iL + iU + iYear, data=subset(All, Country=="US") )
 naturalCoef( model.cde2 )
 
-model.linex1 <- linexModel( iGDP ~ iCapStk + iLabor + iU + iYear, data=subset(All, Country=="US") )
+model.linex1 <- linexModel( iY ~ iK + iL + iU + iYear, data=subset(All, Country=="US") )
 naturalCoef( model.linex1 )
 
-model.linex2 <-  linexModel( response=iGDP, capital= iCapStk, labor=iLabor, energy=iU, time= iYear, 
+model.linex2 <-  linexModel( response=iY, capital= iK, labor=iL, energy=iU, time= iYear, 
                data=subset(All, Country=="US") )
 naturalCoef( model.linex2 )
 
-model.sf1 <-  singleFactorModel( iGDP ~ iCapStk + iYear, data=subset(All, Country=="US") )
+model.sf1 <-  singleFactorModel( iY ~ iK + iYear, data=subset(All, Country=="US") )
 naturalCoef( model.sf1 )
 
[…]

### 2014-04-22 batchEcon2.R

@@ -24,7 +24,7 @@ nestString <- function( formula, nest ) {
     ")"
   )
 }
-# print(sort(.packages()))
+
 require(EconModels2)
 suppressPackageStartupMessages(library("optparse"))
 
@@ -32,7 +32,7 @@ suppressPackageStartupMessages(library("optparse"))
 countryAbbrevs <- c(US="US", UK="UK", JP="JP", CN="CN", ZA="ZA", SA="SA", IR="IR", TZ="TZ", ZM="ZM")
 modelTypes <- c('sf', 'cd', 'cde', 'ces', 'cese-(kl)e', 'cese-(le)k', 'cese-(ek)l', 'linex')
 energyTypes <- c(Q="iQ", X="iX", U="iU") 
-factors <- c(K="iCapStk", L="iLabor", energyTypes)
+factors <- c(K="iK", L="iL", energyTypes)
 
 baseResample <- file.path("data_resample")
 
@@ -82,14 +82,18 @@ getPathForResampleModels <- function(modelType, countryAbbrev, energyType="none"
 #' \code{"cese-(kl)e"}, \code{"cese-(le)k"}, \code{"cese-(kl)e"}, or \code{"linex"}.
 #' @param countryAbbrev, a character string naming the country, 
 #' if you want to use original data.
-#' @param energyType one of \code{"Q"} (for thermal energy), \code{"X"} (for exergy), or \code{"U"} (for useful work).
-#' @param factor one of \code{"K"} (for capital stock), \code{"L"} (for labor), \code{"Q"} (for thermal energy), 
-#' \code{"X"} (for exergy), or \code{"U"} (for useful work).
+#' @param energyType the name of the energy type as it appeared in the original data file.
+#' For example, "iQ".
+#' @param factor the name of the factor as it appeared in the original data file.
+#' For example, "iK".
 #' @param baseResample the relative path of the top-level directory containing the resample data.
 #' @return the relative path of the file containing the data for the requested resample data.
-doGetPath <- function(prefix, modelType, countryAbbrev, energyType="Q", factor="K", baseResample){
-  if (energyType == "none"){
-    energyType="NA"
+doGetPath <- function(prefix, modelType, countryAbbrev, energyType="iQ", factor="iK", baseResample){
+  if (missing(energyType) || is.na(energyType) || (energyType == "none")){
+    energyType <- "NA"
+  }
+  if (missing(factor) || is.na(factor) || (factor == "none")){
[…]

### 2014-04-22 package/R/Graphics.R

@@ -185,15 +185,15 @@ spaghettiPlot <- function(energyType='none',
   data$alph = alph
   split <- intersect( split, names(data) )
   seData <- ddply( subset(data, Type=="fitted"), split, summarise, 
-                   n = length(iGDP),
-                   lower= quantile(iGDP, alph[1]),
-                   upper= quantile(iGDP, 1-alph[1]),
-                   iGDP = iGDP[1]
+                   n = length(iY),
+                   lower= quantile(iY, alph[1]),
+                   upper= quantile(iY, 1-alph[1]),
+                   iY = iY[1]
   ) 
   # return(seData)
   # return(names(data))
-  # graph <- qplot(Year, iGDP, group=ResampleNumber, data=data, facets = ~Country, geom="line", alpha=I(alpha))
-  graph <- ggplot( data=subset(data, Type=="actual"), aes(Year, iGDP)) 
+  # graph <- qplot(Year, iY, group=ResampleNumber, data=data, facets = ~Country, geom="line", alpha=I(alpha))
+  graph <- ggplot( data=subset(data, Type=="actual"), aes(Year, iY)) 
   graph <- graph + geom_smooth(aes(ymin=lower, ymax=upper), col=NA, fill="gray10", 
                                lty=1, size=.5, data=seData, stat="identity")
 #  graph <- graph + geom_area(fill="black", shape=1, alpha=0.05)
@@ -230,9 +230,9 @@ historicalPlot <- function(countryAbbrev, baseHistorical){
     data <- loadData(countryAbbrev=countryAbbrev, baseHistorical=baseHistorical)
   }
   graph <- ggplot(aes(x=Year), data=data) +
-    geom_line(aes(y=iGDP, lty="y")) +
-    geom_line(aes(y=iCapStk, lty="k")) +
-    geom_line(aes(y=iLabor, lty="l")) +
+    geom_line(aes(y=iY, lty="y")) +
+    geom_line(aes(y=iK, lty="k")) +
+    geom_line(aes(y=iL, lty="l")) +
     geom_line(aes(y=iQ, lty="q")) +
     facet_grid( Country ~ ., scales="free_y" ) +
     ylab("Indexed (1980=1 or 1991=1)") +

### 2014-04-22 package/R/Resampling.R

@@ -431,20 +431,20 @@ doResample <- function(data, origModel, method=resampleMethods, reindexGDP=TRUE)
   #         residual:  resamples the residuals and applies them to the data. All years are present.
   #         wild:      same as residuals but randomly select sign of resampled residuals
   # reindexGDP:
-  #         TRUE (default) will rescale iGDP values so that the observation in the first year (row) is 1.0
-  #         FALSE leaves iGDP values untouched.
+  #         TRUE (default) will rescale iY values so that the observation in the first year (row) is 1.0
+  #         FALSE leaves iY values untouched.
   ##
   method <- match.arg(method)
   if(method == "resample") {
     out <- resample(data)
   } else {
     out <- data    
-    out[ , "iGDP"] <- NA
-    out[ , "iGDP"] <- resampledResponse(origModel, method=method)
+    out[ , "iY"] <- NA
+    out[ , "iY"] <- resampledResponse(origModel, method=method)
   }
   if (reindexGDP){
-    # Divide all the values in the iGDP column by the first value in the column
-    out[ , "iGDP"] <- out[ , "iGDP"] / out[1, "iGDP"]
+    # Divide all the values in the iY column by the first value in the column
+    out[ , "iY"] <- out[ , "iY"] / out[1, "iY"]
   }
   return(out)
 }

### 2014-04-22 package/R/huh.R

@@ -39,11 +39,11 @@ columnIndex <- function(data, factor){
   if (factor == "Year"){
     colName <- "iYear"
   } else if (factor == "Y"){
-    colName <- "iGDP"
+    colName <- "iY"
   } else if (factor == "K"){
-    colName <- "iCapStk"
+    colName <- "iK"
   } else if (factor == "L"){
-    colName <- "iLabor"
+    colName <- "iL"
   } else if (factor == "Q"){
     colName <- "iQ"
   } else if (factor == "X"){

### 2014-04-22 package/R/load.R

@@ -67,7 +67,7 @@ loadCESSpaghettiGraphData <- function(nest="(kl)", energyType="none", archive=NU
   # We apply the nest argument as given to the data frame. 
   # Doing so assists with graphing later.
   actual <- loadData(baseHistorical=baseHistorical)
-  actual <- actual[c("Year", "iGDP", "Country")]
+  actual <- actual[c("Year", "iY", "Country")]
   actual$ResampleNumber <- NA
   actual$Type <- "actual"
   actual$Resampled <- FALSE
@@ -81,7 +81,7 @@ loadCESSpaghettiGraphData <- function(nest="(kl)", energyType="none", archive=NU
   prediction <- cesPredictionsColumn(energyType=energyType, nest=nest, baseHistorical=baseHistorical, baseResample=baseResample)
   pred <- actual
   # Replace the historical GDP data with the predicted GDP data, which is in column 1.
-  pred$iGDP <- prediction[,1]
+  pred$iY <- prediction[,1]
   pred$ResampleNumber <- NA
   pred$Type <- "fitted"
   pred$Resampled <- FALSE
@@ -89,7 +89,7 @@ loadCESSpaghettiGraphData <- function(nest="(kl)", energyType="none", archive=NU
   pred$nest <- nest
   
   # Remove rows where predicted GDP is NA, i.e., those rows where we don't have a prediction.
-  pred <- subset(pred, !is.na(iGDP))
+  pred <- subset(pred, !is.na(iY))
   
   # Remove rows where we don't need historical data or predictions, 
   # specifically those times when we won't have a prediction.
@@ -146,7 +146,7 @@ loadCESSpaghettiGraphData <- function(nest="(kl)", energyType="none", archive=NU
     nYears <- length(fitted(resampleModels[[1]]))
     dfList[[countryAbbrev]] <- data.frame(
       Year = rep(historical$Year, nResamples),
-      iGDP = unlist(lapply( resampleModels, fitted )),
+      iY = unlist(lapply( resampleModels, fitted )),
       Country = countryAbbrev,
       ResampleNumber = rep( 1:nResamples, each=nYears ),
       Type = "fitted",

### 2014-04-22 package/R/tables.R

@@ -6,7 +6,7 @@ covarianceTable <- function(countryAbbrev, baseHistorical){
   data <- loadData(countryAbbrev=countryAbbrev, baseHistorical=baseHistorical)
   if (countryAbbrev %in% countryAbbrevsU){
     # Calculate covariances among the typical variables.
-    dataForCovar <- cbind(data$iGDP, data$iCapStk, data$iLabor, data$iQ, data$iX, data$iU)
+    dataForCovar <- cbind(data$iY, data$iK, data$iL, data$iQ, data$iX, data$iU)
     # Calculates the covariances among y, k. l, q, x, and u using all available data, namely,
     # 1980-2011 for covariances among y, k, l, q, and x for developed economies
     # 1980-2000 for covariances involving u for developed economies
@@ -15,7 +15,7 @@ covarianceTable <- function(countryAbbrev, baseHistorical){
     covarResults <- data.frame(cor(x=dataForCovar, use="pairwise.complete.obs"))
     names <- c("$y$", "$k$", "$l$", "$q$", "$x$", "$u$")
   } else {
-    dataForCovar <- cbind(data$iGDP, data$iCapStk, data$iLabor, data$iQ, data$iX)
+    dataForCovar <- cbind(data$iY, data$iK, data$iL, data$iQ, data$iX)
     covarResults <- cor(dataForCovar)
     names <- c("$y$", "$k$", "$l$", "$q$", "$x$")
   }

### 2014-04-22 package2/R/Graphics.R

@@ -185,15 +185,15 @@ spaghettiPlot <- function(energyType='none',
   data$alph = alph
   split <- intersect( split, names(data) )
   seData <- ddply( subset(data, Type=="fitted"), split, summarise, 
-                   n = length(iGDP),
-                   lower= quantile(iGDP, alph[1]),
-                   upper= quantile(iGDP, 1-alph[1]),
-                   iGDP = iGDP[1]
+                   n = length(iY),
+                   lower= quantile(iY, alph[1]),
+                   upper= quantile(iY, 1-alph[1]),
+                   iY = iY[1]
   ) 
   # return(seData)
   # return(names(data))
-  # graph <- qplot(Year, iGDP, group=ResampleNumber, data=data, facets = ~Country, geom="line", alpha=I(alpha))
-  graph <- ggplot( data=subset(data, Type=="actual"), aes(Year, iGDP)) 
+  # graph <- qplot(Year, iY, group=ResampleNumber, data=data, facets = ~Country, geom="line", alpha=I(alpha))
+  graph <- ggplot( data=subset(data, Type=="actual"), aes(Year, iY)) 
   graph <- graph + geom_smooth(aes(ymin=lower, ymax=upper), col=NA, fill="gray10", 
                                lty=1, size=.5, data=seData, stat="identity")
 #  graph <- graph + geom_area(fill="black", shape=1, alpha=0.05)
@@ -230,9 +230,9 @@ historicalPlot <- function(countryAbbrev){
     data <- loadData(countryAbbrev)
   }
   graph <- ggplot(aes(x=Year), data=data) +
-    geom_line(aes(y=iGDP, lty="y")) +
-    geom_line(aes(y=iCapStk, lty="k")) +
-    geom_line(aes(y=iLabor, lty="l")) +
+    geom_line(aes(y=iY, lty="y")) +
+    geom_line(aes(y=iK, lty="k")) +
+    geom_line(aes(y=iL, lty="l")) +
     geom_line(aes(y=iQ, lty="q")) +
     facet_grid( Country ~ ., scales="free_y" ) +
     ylab("Indexed (1980=1 or 1991=1)") +

### 2014-04-24 Article/EconGrowth2.Rnw
The article now uses the modified historicalPlot function.

--- 2014-03-29 Article/EconGrowth2.Rnw
@@
 <<setup, echo=FALSE, message=FALSE, eval=TRUE>>=
-require(EconModels)
+require(EconModels2)
 require(lattice)
@@
 require(knitr)
+
+# Pull in some constants and other important functions
+source("Scripts/files.R")
+
+# ********************************************************
+# We need to define a directory path to the resample data results from "Article"
+archive <- file.path("..", "data_resample_2014-04-24_Refactored-Code_n=1000.zip")
+baseResample <- "data_resample" # Define the directory within the archive wherein we can find the data.
+# ********************************************************
+# Load the fits to the original historical data out of the archive we're using.
+# This object should be passed in to functions that need specific fits.
+f <- gzcon(unz(archive, file.path(baseResample, "oModels.Rdata")))
+oModels <- readRDS(f)
+close(f)
+# In Rstudio, this paper is generated from it's directory, which is "Article".
+# We need to define paths relative to the location of the paper. 
+# Relative path to historical data from Article
+baseHistorical <- file.path("..", "data")
+
 opts_chunk$set(
@@
 <<constants, include=FALSE>>=
+source(file.path("..", "Scripts", "Constants.R"))
+
 # Graph Heights
-# #' @export
 maxHeight <- 8.5 # Inches
-# #' @export
 ninePanelScatterGraphHeight <- maxHeight # Inches
-# #' @export
 # ninePanelTernaryGraphHeight <- 7 # Inches
-# #' @export
 # ninePanelSpaghettiGraphHeight <- 7 # Inches
@@
 # Graph Widths
-# #' @export
 maxWidth <- 6.5 # Inches
-# #' @export
 fourPanelScatterGraphWidth <- maxWidth # Inches
-# #' @export
 # threePanelScatterGraphWidth <- maxWidth*0.75 # Inches
-# #' @export
 # onePanelScatterGraphWidth <- maxWidth*0.25
-# #' @export
 # fourPanelTernaryGraphWidth <- maxWidth
-# #' @export
 # twoPanelTernaryGraphWidth <- maxWidth*0.45
-# #' @export
 # fourPanelSpaghettiGraphWidth <- maxWidth
-# #' @export
 # twoPanelSpaghettiGraphWidth <- maxWidth*0.55
-# #' @export
 # onePanelSpaghettiGraphWidth <- maxWidth*0.4
 
-#' @export
 presentationGraph1RowHeight <- 2.8 # Inches
-#' @export
 presentationGraph2ColWidth <- 2 # Inches
-#' @export
 presentationGraph1ColWidth <- 2*presentationGraph2ColWidth
-# #' @export
 # keyTextSize <- 0.85 # 85% of normal size
-# #' @export
 # keyColumns <- 1 # Want only 1 column in the key for lattice graphs
-# #' @export
 # defaultKeyXLoc <- 0.01 # x position of the key. This default is good for 9-panel graphs.
-# #' @export
 # defaultKeyYLoc <- 0.95 # y position of the key. This default is good for 9-panel graphs.
@@
 # to estimate that h_axis = 0.86 in and hgraph = 2.05 in.
-# #' @export
 h_param_graph <- 2.07 # Inches for a single panel
-# #' @export
 h_param_axis <- 0.86 # Inches (also includes whatever margin is applied)
-# #' @export
 # sfParameterGraphHeight <- h_param_graph + h_param_axis
-# #' @export
 cdParameterGraphHeight <- 2*h_param_graph + h_param_axis
-# #' @export
 cesParameterGraphHeight <- 3*h_param_graph + h_param_axis
-# #' @export
 linexParameterGraphHeight <- h_param_graph + h_param_axis
-# #' @export
 sfParameterGraphWidth <- maxWidth
-# #' @export
 cdParameterGraphWidth <- maxWidth
-# #' @export
-# cdTernaryGraphWidth <- maxWidth/2.2
-# #' @export
-# cdSpaghettiGraphWidth <- maxWidth/2.2
-# #' @export
 cesParameterGraphWidth <- maxWidth
-# #' @export
 linexParameterGraphWidth <- maxWidth
 # Other graph parameters that apply to all graphs
-# #' @export
 scaleTextSize <- 0.8  # Multiple of normal size
-# #' @export
 scaleTickSize <- -0.5 # 50% of normal size and pointing INWARD!
@@
 spaghettiGraphLevel <- 0.95 # Spaghetti graph bands will encompass 95% of the data.
-
-# In Rstudio, this paper is generated from it's directory, which is "Article".
-# We need to define paths relative to the location of the paper. 
-# Relative path to historical data from Article
-baseHistorical <- file.path("..", "data")
-# We also need to define a directory path to the resample data results from "Article"
-baseResample <- file.path("..", "data_resample")
 @
@@
 
-\author[CalvinEngr]{Caleb Reese}
-\author[CalvinEngr]{Lucas Timmer}
 \author[CalvinEngr]{Matthew Kuperus Heun\corref{cor1}}
@@
 \author[CalvinMath]{Randall J. Pruim}
+\author[CalvinEngr]{Caleb Reese}
+\author[CalvinEngr]{Lucas Timmer}
 
@@
 \twocolumn{}
-<<Historical_Lattice_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=7.5, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), and thermal energy ($q$).">>=
-historicalPlot(baseHistorical=baseHistorical)
+<<Historical_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=7.5, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), and thermal energy ($q$).">>=
+historicalData <- read.table(file=file.path(baseHistorical, "AllData.txt"), header=TRUE)
+levels(historicalData$Country) <- countryAbbrevs
+historicalPlot(historicalData)
 @
@@
 
-Figure~\ref{fig:Historical_Lattice_Graph} presents historical data, 
+Figure~\ref{fig:Historical_Graph} presents historical data, 
 including indexed values for 

### 2014-04-24 Article/EconGrowth2.Rnw
Now correctly setting levels (with relevel) for the Country column of historical data. Fixes Issue #101.

@@
 source("Scripts/files.R")
-
-# ********************************************************
-# We need to define a directory path to the resample data results from "Article"
-archive <- file.path("..", "data_resample_2014-04-24_Refactored-Code_n=1000.zip")
-baseResample <- "data_resample" # Define the directory within the archive wherein we can find the data.
-# ********************************************************
-# Load the fits to the original historical data out of the archive we're using.
-# This object should be passed in to functions that need specific fits.
-f <- gzcon(unz(archive, file.path(baseResample, "oModels.Rdata")))
-oModels <- readRDS(f)
-close(f)
+source(file.path("..", "Scripts", "Constants.R"))
+
+# Load historical data
 # In Rstudio, this paper is generated from it's directory, which is "Article".
@@
 baseHistorical <- file.path("..", "data")
+historicalData <- read.table(file=file.path(baseHistorical, "AllData.txt"), header=TRUE)
+# Adjust the levels of historicalData so that the levels are in the same order as countryAbbrevs.
+for (lev in rev(countryAbbrevs)){
+  historicalData$Country <- relevel(historicalData$Country, ref=lev)
+}
+
+# Set up for loading resample results
+# We need to define a directory path from "Article" to the resample data results
+archive <- file.path("..", "data_resample_2014-04-24_Refactored-Code_n=1000.zip")
+baseResample <- "data_resample" # Define the directory within the archive wherein we can find the data.
+# Load the fits to the original historical data out of the archive we're using.
+# This object (oModels) should be passed in to functions that need information from orig fits.
+f <- gzcon(unz(archive, file.path(baseResample, "oModels.Rdata")))
+oModels <- readRDS(f)
+close(f)
 
@@
 <<constants, include=FALSE>>=
-source(file.path("..", "Scripts", "Constants.R"))
-
 # Graph Heights
@@
 <<Historical_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=7.5, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), and thermal energy ($q$).">>=
-historicalData <- read.table(file=file.path(baseHistorical, "AllData.txt"), header=TRUE)
-levels(historicalData$Country) <- countryAbbrevs
 historicalPlot(historicalData)

### 2014-04-25 Article/EconGrowth2.Rnw
moving to EconModels and EconData

@@
 <<setup, echo=FALSE, message=FALSE, eval=TRUE>>=
-require(EconModels2)
+require(EconModels)
+require(EconData)
 require(lattice)
@@
 # Pull in some constants and other important functions
-source("Scripts/files.R")
-source(file.path("..", "Scripts", "Constants.R"))
+#source("Scripts/files.R")
+#source(file.path("..", "Scripts", "Constants.R"))
 
@@
 baseHistorical <- file.path("..", "data")
-historicalData <- read.table(file=file.path(baseHistorical, "AllData.txt"), header=TRUE)
-# Adjust the levels of historicalData so that the levels are in the same order as countryAbbrevs.
-for (lev in rev(countryAbbrevs)){
-  historicalData$Country <- relevel(historicalData$Country, ref=lev)
-}
+historicalData <- Econ2011
 

### 2014-04-25 Article/EconGrowth2.Rnw
CD tri plot now works in the paper. But, graphs are squished horizontally.

@@
 baseHistorical <- file.path("..", "data")
-historicalData <- Econ2011
+historicalData <- Econ2011 # From the EconData package
 
@@
 <<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=2.9, fig.height=7.7, fig.cap="Cobb-Douglas resample model parameters.">>=
-  dataCD <- loadAllResampleData(modelType="cd", countryAbbrevsOrder=countryAbbrevs, energyType="none", baseResample=baseResample)
-  dataCDQ <- loadAllResampleData(modelType="cde", countryAbbrevsOrder=countryAbbrevs, energyType="Q", baseResample=baseResample)
+  dataCD <- loadAllResampleData(modelType="cd", 
+                                countryAbbrevs=countryAbbrevs, 
+                                energyType="none", 
+                                archive=archive,
+                                baseResample=baseResample)
+  dataCDQ <- loadAllResampleData(modelType="cde", 
+                                 countryAbbrevs=countryAbbrevs, 
+                                 energyType="iQ", 
+                                 archive=archive,
+                                 baseResample=baseResample)
   data <- rbind.fill(dataCD, dataCDQ)
-  standardTriPlot(data=data, facet_formula=countryAbbrev~energy)
+  standardTriPlot(data=data, facet_formula=countryAbbrev~energyType)
 @

### 2014-04-28 Scrap/EconGrowth-R-Functions.Rnw
sfModel, cdModel now in place.

@@
 ##
-singleFactorModel <- function(countryAbbrev, factor){
+sfModel <- function(countryAbbrev, factor){
   dataTable <- loadData(countryAbbrev) #Load the data that we need.
@@
   }
-  model <- singleFactorModel(countryAbbrev, factor)
+  model <- sfModel(countryAbbrev, factor)
   pred <- predict(model) #See http://stackoverflow.com/questions/9918807/how-get-plot-from-nls-in-r
@@
   # We have a combination of country and factor for which we have data.
-  modelSF <- singleFactorModel(countryAbbrev, factor)
+  modelSF <- sfModel(countryAbbrev, factor)
   summarySF <- summary(modelSF) # Gives the nls summary table.
@@
   # Need the model to make predictions
-  model <- singleFactorModel(countryAbbrev, factor)
+  model <- sfModel(countryAbbrev, factor)
   # Get information about the optimum point, the point where SSE is minimized
@@
 ##
-cdModel <- function(countryAbbrev){
+cdwoeModel <- function(countryAbbrev){
   dataTable <- loadData(countryAbbrev) #Load the data that we need.
@@
 # If you supply a value for the gamma argument, a fit with fixed gamma will be provided.
-# This function dispatches to cdModel, cdeModel, or cdFixedGammaModel based on which arguments are specified.
-##
-cobbDouglasModel <- function(countryAbbrev, energyType, gamma){
+# This function dispatches to cdwoeModel, cdeModel, or cdFixedGammaModel based on which arguments are specified.
+##
+cdModel <- function(countryAbbrev, energyType, gamma){
   if (is.na(energyType)){
     # Fit the Cobb-Douglas model without energy.
-    return(cdModel(countryAbbrev=countryAbbrev))
+    return(cdwoeModel(countryAbbrev=countryAbbrev))
   }
@@
   gamma <- gammaGrid
-  models <- lapply(gamma, cobbDouglasModel, energyType=energyType, countryAbbrev=countryAbbrev)
+  models <- lapply(gamma, cdModel, energyType=energyType, countryAbbrev=countryAbbrev)
   SSE <- unlist(lapply(models, function(model){summary(model)$sigma}))
@@
   }
-  model <- cobbDouglasModel(countryAbbrev, energyType)
+  model <- cdModel(countryAbbrev, energyType)
   pred <- predict(model) #See http://stackoverflow.com/questions/9918807/how-get-plot-from-nls-in-r
@@
   # We have a combination of country and energy type for which we have data.
-  modelCD <- cobbDouglasModel(countryAbbrev=countryAbbrev, energyType=energyType)
+  modelCD <- cdModel(countryAbbrev=countryAbbrev, energyType=energyType)
 print(str(modelCD))
@@
   # Single-factor with K
-  sfKModels <- lapply(countryAbbrevs, singleFactorModel, factor="K")
+  sfKModels <- lapply(countryAbbrevs, sfModel, factor="K")
   aicSFk <- data.frame(lapply(sfKModels, AIC))
@@
   # Single-factor with L
-  sfLModels <- lapply(countryAbbrevs, singleFactorModel, factor="L")
+  sfLModels <- lapply(countryAbbrevs, sfModel, factor="L")
   aicSFl <- data.frame(lapply(sfLModels, AIC))
@@
   # Single-factor with Q
-  sfQModels <- lapply(countryAbbrevs, singleFactorModel, factor="Q")
+  sfQModels <- lapply(countryAbbrevs, sfModel, factor="Q")
   aicSFq <- data.frame(lapply(sfQModels, AIC))
@@
   # Single-factor with X
-  sfXModels <- lapply(countryAbbrevs, singleFactorModel, factor="X")
+  sfXModels <- lapply(countryAbbrevs, sfModel, factor="X")
   aicSFx <- data.frame(lapply(sfXModels, AIC))
@@
   # Single-factor with U
-  aicSFu <- cbind(US=AIC(singleFactorModel("US", "U")), 
-                  UK=AIC(singleFactorModel("UK", "U")), 
-                  JP=AIC(singleFactorModel("JP", "U")),
+  aicSFu <- cbind(US=AIC(sfModel("US", "U")), 
+                  UK=AIC(sfModel("UK", "U")), 
+                  JP=AIC(sfModel("JP", "U")),
                   CN=NA, ZA=NA, SA=NA, IR=NA, TZ=NA, ZM=NA) #No U data for these countries.
@@
   # Cobb-Douglas without energy
-  cdModels <- lapply(countryAbbrevs, cobbDouglasModel, energyType=NA)
-  aicCD <- data.frame(lapply(cdModels, AIC))
+  cdwoeModels <- lapply(countryAbbrevs, cdModel, energyType=NA)
+  aicCD <- data.frame(lapply(cdwoeModels, AIC))
   rownames(aicCD) <- "CD"
   # Cobb-Douglas with Q
-  cdQModels <- lapply(countryAbbrevs, cobbDouglasModel, energyType="Q")
+  cdQModels <- lapply(countryAbbrevs, cdModel, energyType="Q")
   aicCDq <- data.frame(lapply(cdQModels, AIC))
@@
   # Cobb-Douglas with X
-  cdXModels <- lapply(countryAbbrevs, cobbDouglasModel, energyType="X")
+  cdXModels <- lapply(countryAbbrevs, cdModel, energyType="X")
   aicCDx <- data.frame(lapply(cdXModels, AIC))
@@
   # Cobb-Douglas with U
-  aicCDu <- cbind(US=AIC(cobbDouglasModel("US", "U")), 
-                  UK=AIC(cobbDouglasModel("UK", "U")), 
-                  JP=AIC(cobbDouglasModel("JP", "U")),
+  aicCDu <- cbind(US=AIC(cdModel("US", "U")), 
+                  UK=AIC(cdModel("UK", "U")), 
+                  JP=AIC(cdModel("JP", "U")),
                   CN=NA, ZA=NA, SA=NA, IR=NA, TZ=NA, ZM=NA) #No U data for these countries.
@@
   if (modelType == "CD"){
-    model <- cdModel(countryAbbrev)  
+    model <- cdwoeModel(countryAbbrev)  
   } else if (modelType == "CES"){

### 2014-04-28 Seminar/EconGrowthSeminar.Rnw
sfModel, cdModel now in place.

@@
 <<Coefs_US_SF>>=
-sfUSK <- coef(singleFactorModel("US", "K"))
-sfUSL <- coef(singleFactorModel("US", "L"))
-sfUSQ <- coef(singleFactorModel("US", "Q"))
-sfUSX <- coef(singleFactorModel("US", "X"))
-sfUSU <- coef(singleFactorModel("US", "U"))
+sfUSK <- coef(sfModel("US", "K"))
+sfUSL <- coef(sfModel("US", "L"))
+sfUSQ <- coef(sfModel("US", "Q"))
+sfUSX <- coef(sfModel("US", "X"))
+sfUSU <- coef(sfModel("US", "U"))
 @

### 2014-04-28 Packages/EconData/R/files.R

@@ -50,12 +50,26 @@ fittingID <- function(fun, countryAbbrev, formula, nest=NULL, nestStr=nestString
   return(id)
 }
 
+#' Calculate a file name for given parameters
+#' 
+#' @param fun the function used for fitting
+#' @param countryAbbrev the country being fitted
+#' @param formula the formula used for the fitting
+#' @param nest if used, the nest employed for this fit. A 2- or 3-vector of integers.
+#' @param nestStr if used, the string for the nesting
+#' @param n the number of resamples being attempted
+#' @param sep the separator used to create the id string. Default is " : ".
+#' @return a string to be used as the id for this resample
+resampleFileName <- function(fun, countryAbbrev, formula, nest=NULL, nestStr=nestString(nest), sep="_"){
+  
+}
+
 #' Extracts a factor from a formula
 #' 
 #' @param formulaStr a string representing the formula that was fitted
 #' @param formula the formula that was fitted
 #' @return a string representing the factor that was used for the fitting. 
-#' NA if the singleFactorModel was not used.
+#' NA if the sfModel was not used.
 factorFromFormula <- function(formulaStr, formula=eval(parse(text=formulaStr))){
   vars <- all.vars(formula)
   if (length(vars) == 3){
@@ -79,7 +93,7 @@ factorFromFormula <- function(formulaStr, formula=eval(parse(text=formulaStr))){
 #' @param formulaStr a string representing the formula that was fitted
 #' @param formula the formula that was fitted
 #' @return a string representing the energyType that was used for the fitting. 
-#' NA if the singleFactorModel was used.
+#' NA if the sfModel was used.
 energyTypeFromFormula <- function(formulaStr, formula=eval(parse(text=formulaStr))){
   vars <- all.vars(formula)
   if (length(vars) == 3){
@@ -151,10 +165,10 @@ parseID <- function(id, sep=" : "){
   # Now add some additional useful information
   factor <- factorFromFormula(formula=formula)
   energyType <- energyTypeFromFormula(formula=formula)
-  if (func == "singleFactorModel"){
+  if (func == "sfModel"){
     modelType <- "sf"
     nest <- NA
-  } else if (func == "cobbDouglasModel"){
+  } else if (func == "cdModel"){
     if (is.na(energyType)){
       modelType <- "cd"
     } else {

### 2014-04-28 Packages/EconModels/R/Fitting.R

@@ -114,7 +114,7 @@ predict.LINEXmodel <- function( object, ... ) {
 #' @param constrained a logical indicating whether the model parameters are constrained
 #' @return an lm object with some additional attributes
 #' @export
-singleFactorModel <- function(formula, data, response, factor, time, constrained=FALSE,
+sfModel <- function(formula, data, response, factor, time, constrained=FALSE,
                               save.data=TRUE) {
   
   if ( missing(formula) ) {
@@ -191,7 +191,7 @@ singleFactorModel <- function(formula, data, response, factor, time, constrained
 #' @param constrained a logical indicating whether the parameters are constrained
 #' @return a CDEmodel object, which is an lm object with some additioanl attributes.
 #' @export
-cobbDouglasModel <- function(formula, data, response, capital, labor, energy, time, 
+cdModel <- function(formula, data, response, capital, labor, energy, time, 
                              constrained=FALSE, save.data=TRUE, ...) {
   if (missing(formula)) {
     if (missing(energy)) {
@@ -206,7 +206,7 @@ cobbDouglasModel <- function(formula, data, response, capital, labor, energy, ti
   
   if (ncol( attr(terms(formula),"factors") ) == 3 ) {
     # formula contains response, capital, and labor
-    cdModel( formula=formula, data=data, constrained = constrained, save.data=save.data, ... )
+    cdwoeModel( formula=formula, data=data, constrained = constrained, save.data=save.data, ... )
   } else {
     # formula contains response, capital, labor, and energy
     cdeModel( formula=formula, data=data, constrained = constrained, save.data=save.data, ... )
@@ -226,9 +226,8 @@ cobbDouglasModel <- function(formula, data, response, capital, labor, energy, ti
 #' @param time instead of specifying a formula, expressions for
 #' the components can be specified individually.
 #' @param contrained a logical indicating whether the parameters are contrained
-#' @return a CDEmodel object, which is an lm object with some additioanl attributes.
-
-cdModel <- function(formula, data, response, capital, labor, time, constrained=FALSE, 
+#' @return a CDEmodel object, which is an lm object with some additional attributes.
+cdwoeModel <- function(formula, data, response, capital, labor, time, constrained=FALSE, 
                     save.data=TRUE, ...) {
   if ( missing(formula) ) {
     formula <- substitute( response ~ capital + labor + time,

### 2014-04-28 Packages/EconModels/R/Resampling.R

@@ -49,8 +49,8 @@ resampledResponse.default <- function( object, method=c("residual", "wild", "deb
 #' 
 #' This function returns a list containing models and coefficients from the resample fits.
 #' 
-#' @param model a model returned from \code{linexModel}, \code{cobbDouglasModel}, 
-#' \code{cesModel}, or \code{singleFactorModel}.  \code{model} must
+#' @param model a model returned from \code{linexModel}, \code{cdModel}, 
+#' \code{cesModel}, or \code{sfModel}.  \code{model} must
 #' have been fit with \code{save.data = TRUE}.
 #' @param method one of \code{"resample"}, \code{"residual"}, \code{"wild"}, or \code{"debug"}
 #' @param n the number of resamples you want to perform
@@ -72,9 +72,9 @@ resampledFits <- function(model,
                           ...) {
   
   fitfun <- switch(class(model)[1],
-                   "sfModel" = "singleFactorModel",
+                   "sfModel" = "sfModel",
                    "LINEXmodel" = "linexModel",
-                   "CDEmodel" = "cobbDouglasModel",
+                   "CDEmodel" = "cdModel",
                    "cesEst" = "cesModel"
   )
   
@@ -123,8 +123,8 @@ resampledFits <- function(model,
 
 #' Create resampled data
 #' 
-#' @param model a model returned from \code{linexModel}, \code{cobbDouglasModel},
-#' \code{cesModel}, or \code{singleFactorModel}.  \code{model} must
+#' @param model a model returned from \code{linexModel}, \code{cdModel},
+#' \code{cesModel}, or \code{sfModel}.  \code{model} must
 #' have been fit with \code{save.data = TRUE}.
 #' @param method One of 
 #'      resample:  resample rows from data. Can result in repeated years.

### 2014-04-28 Packages/EconModels0/R/Fitting.R

@@ -385,7 +385,7 @@ addMetaData <- function(model, nest, history=""){
 }
 
 #' @export
-singleFactorModel <- function(countryAbbrev, baseHistorical, data=loadData(countryAbbrev, baseHistorical), 
+sfModel <- function(countryAbbrev, baseHistorical, data=loadData(countryAbbrev, baseHistorical), 
                               factor, respectRangeConstraints=FALSE){
   ####################
   # Returns an nls single-factor model for the country and factor specified.
@@ -420,7 +420,7 @@ singleFactorModel <- function(countryAbbrev, baseHistorical, data=loadData(count
 
 
 #' @export
-cdModel <- function(countryAbbrev, baseHistorical, data=loadData(countryAbbrev, baseHistorical), 
+cdwoeModel <- function(countryAbbrev, baseHistorical, data=loadData(countryAbbrev, baseHistorical), 
                     respectRangeConstraints=FALSE, ...){
   ## <<cobb-douglas functions, eval=TRUE>>=
   ####################

### 2014-04-28 Packages/EconModels0/R/singleFactor.R

@@ -13,7 +13,7 @@ singleFactorPredictions <- function(countryAbbrev, factor, baseHistorical, baseR
     colnames(df) <- "pred"
     return(df)
   }
-#   model <- singleFactorModel(countryAbbrev=countryAbbrev, factor=factor)
+#   model <- sfModel(countryAbbrev=countryAbbrev, factor=factor)
   model <- loadResampleModelsBaseModelOnly(modelType="sf", countryAbbrev=countryAbbrev, factor=factor, 
                                            baseResample=baseResample, archive=archive)
   pred <- predict(model) #See http://stackoverflow.com/questions/9918807/how-get-plot-from-nls-in-r

### 2014-04-28 Packages/EconModels0/R/tables.R

@@ -474,7 +474,7 @@ createAICTable <- function(baseHistorical){
   ######################
   # Single-factor with K
   # At present, this function re-fits all models with lines like the following.
-  sfKModels <- lapply(countryAbbrevs, singleFactorModel, factor="K", respectRangeConstraints=TRUE, baseHistorical=baseHistorical)
+  sfKModels <- lapply(countryAbbrevs, sfModel, factor="K", respectRangeConstraints=TRUE, baseHistorical=baseHistorical)
   # The above approach will be painfully slow for the CES models, because they take soooo long to run.
   # If we want to load from disk instead of re-running the model, we should use code that looks like the line below
   # But, at present, the next line of code is slooooow, because loadResampleModelsBaseModelOnly 
@@ -484,42 +484,42 @@ createAICTable <- function(baseHistorical){
   aicSFk <- data.frame(lapply(sfKModels, AIC))
   rownames(aicSFk) <- "SF$k$"
   # Single-factor with L
-  sfLModels <- lapply(countryAbbrevs, singleFactorModel, factor="L", respectRangeConstraints=TRUE, baseHistorical=baseHistorical)
+  sfLModels <- lapply(countryAbbrevs, sfModel, factor="L", respectRangeConstraints=TRUE, baseHistorical=baseHistorical)
   aicSFl <- data.frame(lapply(sfLModels, AIC))
   rownames(aicSFl) <- "SF$l$"
   # Single-factor with Q
-  sfQModels <- lapply(countryAbbrevs, singleFactorModel, factor="Q", respectRangeConstraints=TRUE, baseHistorical=baseHistorical)
+  sfQModels <- lapply(countryAbbrevs, sfModel, factor="Q", respectRangeConstraints=TRUE, baseHistorical=baseHistorical)
   aicSFq <- data.frame(lapply(sfQModels, AIC))
   rownames(aicSFq) <- "SF$q$"
   # Single-factor with X
-  sfXModels <- lapply(countryAbbrevs, singleFactorModel, factor="X", respectRangeConstraints=TRUE, baseHistorical=baseHistorical)
+  sfXModels <- lapply(countryAbbrevs, sfModel, factor="X", respectRangeConstraints=TRUE, baseHistorical=baseHistorical)
   aicSFx <- data.frame(lapply(sfXModels, AIC))
[…]

### 2014-04-28 Scrap/BaseModels.R

@@ -21,35 +21,35 @@ names(countryAbbrevsU) <- countryAbbrevsU
 # Single Factor models
 #
 modelsSFK <- lapply(countryAbbrevs, function(countryAbbrev){
-  singleFactorModel(formula=iY ~ iK + iYear, data=subset(data, Country==countryAbbrev))
+  sfModel(formula=iY ~ iK + iYear, data=subset(data, Country==countryAbbrev))
 })
 modelsSFL <- lapply(countryAbbrevs, function(countryAbbrev){
-  singleFactorModel(formula=iY ~ iL + iYear, data=subset(data, Country==countryAbbrev))
+  sfModel(formula=iY ~ iL + iYear, data=subset(data, Country==countryAbbrev))
 })
 modelsSFQ <- lapply(countryAbbrevs, function(countryAbbrev){
-  singleFactorModel(formula=iY ~ iQ + iYear, data=subset(data, Country==countryAbbrev))
+  sfModel(formula=iY ~ iQ + iYear, data=subset(data, Country==countryAbbrev))
 })
 modelsSFX <- lapply(countryAbbrevs, function(countryAbbrev){
-  singleFactorModel(formula=iY ~ iX + iYear, data=subset(data, Country==countryAbbrev))
+  sfModel(formula=iY ~ iX + iYear, data=subset(data, Country==countryAbbrev))
 })
 modelsSFU <- lapply(countryAbbrevsU, function(countryAbbrev){
-  singleFactorModel(formula=iY ~ iU + iYear, data=subset(data, Country==countryAbbrev))
+  sfModel(formula=iY ~ iU + iYear, data=subset(data, Country==countryAbbrev))
 })
 
 #
 # Cobb-Douglas models
 #
 modelsCD <- lapply(countryAbbrevs, function(countryAbbrev){
-  cdModel(formula=iY ~ iK + iL + iYear, data=subset(data, Country==countryAbbrev))
+  cdwoeModel(formula=iY ~ iK + iL + iYear, data=subset(data, Country==countryAbbrev))
 })
 modelsCDQ <- lapply(countryAbbrevs, function(countryAbbrev){
-  cdModel(formula=iY ~ iK + iL + iQ + iYear, data=subset(data, Country==countryAbbrev))
+  cdwoeModel(formula=iY ~ iK + iL + iQ + iYear, data=subset(data, Country==countryAbbrev))
 })
[…]

### 2014-04-28 Scrap/Econ-Growth-Functions.R

@@ -329,7 +329,7 @@ createHistoricalLatticeGraph <- function(countryAbbrev, textScaling = 1.0, keyXL
 }
 
 ## <<single-factor functions, eval=TRUE>>=
-singleFactorModel <- function(countryAbbrev, factor){
+sfModel <- function(countryAbbrev, factor){
   ####################
   # Returns an nls single-factor model for the country and factor specified.
   # factor should be one of "K", "L", "Q", "X", or "U".
@@ -369,7 +369,7 @@ singleFactorPredictions <- function(countryAbbrev, factor){
     colnames(df) <- "pred"
     return(df)
   }
-  model <- singleFactorModel(countryAbbrev, factor)
+  model <- sfModel(countryAbbrev, factor)
   pred <- predict(model) #See http://stackoverflow.com/questions/9918807/how-get-plot-from-nls-in-r
   df <- data.frame(pred)
   # Pad with rows as necessary
@@ -481,7 +481,7 @@ singleFactorData <- function(countryAbbrev, factor){
     return(df)
   }
   # We have a combination of country and factor for which we have data.
-  modelSF <- singleFactorModel(countryAbbrev, factor)
+  modelSF <- sfModel(countryAbbrev, factor)
   summarySF <- summary(modelSF) # Gives the nls summary table.
   ciSF <- confint(modelSF, level = ciLevel)  # Calculates confidence intervals for the SF model.
   dofSF <- summarySF$df[2] # Gives the degrees of freedom for the model.
@@ -666,7 +666,7 @@ sf3DSSEGraph <- function(countryAbbrev, factor, showOpt=TRUE){
   y_act <- data[ ,"iY"] # Pick off the GDP column
   y_act <- data.frame(y_act)
   # Need the model to make predictions
-  model <- singleFactorModel(countryAbbrev, factor)
+  model <- sfModel(countryAbbrev, factor)
   # Get information about the optimum point, the point where SSE is minimized
   coefs <- coef(model)
   lambda_opt <- coefs["lambda"]
@@ -726,7 +726,7 @@ sf3DSSEGraph <- function(countryAbbrev, factor, showOpt=TRUE){
   return(fig)    
 }
 
-cdModel <- function(countryAbbrev,...){
+cdwoeModel <- function(countryAbbrev,...){
   ## <<cobb-douglas functions, eval=TRUE>>=
[…]

### 2014-04-28 Scrap/Econ-Growth-Functions2.R

@@ -432,7 +432,7 @@ safeDF <- function(object, nrow=1, ncol=0){
 }
 
 ## <<single-factor functions, eval=TRUE>>=
-singleFactorModel <- function(countryAbbrev, data=loadData(countryAbbrev), factor, respectRangeConstraints=FALSE){
+sfModel <- function(countryAbbrev, data=loadData(countryAbbrev), factor, respectRangeConstraints=FALSE){
   ####################
   # Returns an nls single-factor model for the country and factor specified.
   # factor should be one of "K", "L", "Q", "X", or "U".
@@ -478,7 +478,7 @@ singleFactorPredictions <- function(countryAbbrev, factor){
     colnames(df) <- "pred"
     return(df)
   }
-  model <- singleFactorModel(countryAbbrev=countryAbbrev, factor=factor)
+  model <- sfModel(countryAbbrev=countryAbbrev, factor=factor)
   pred <- predict(model) #See http://stackoverflow.com/questions/9918807/how-get-plot-from-nls-in-r
   df <- data.frame(pred)
   # Pad with rows as necessary
@@ -713,7 +713,7 @@ sf3DSSEGraph <- function(countryAbbrev, factor, showOpt=TRUE){
   y_act <- data[ ,"iY"] # Pick off the GDP column
   y_act <- data.frame(y_act)
   # Need the model to make predictions
-  model <- singleFactorModel(countryAbbrev=countryAbbrev, factor=factor)
+  model <- sfModel(countryAbbrev=countryAbbrev, factor=factor)
   # Get information about the optimum point, the point where SSE is minimized
   coefs <- coef(model)
   lambda_opt <- coefs["lambda"]
@@ -899,7 +899,7 @@ predict.LINEXmodel <- function( object, ... ) {
 #  return( switch(type, response=E, log=e))
 #}
 
-cdModel <- function(countryAbbrev, data=loadData(countryAbbrev), respectRangeConstraints=FALSE, ...){
+cdwoeModel <- function(countryAbbrev, data=loadData(countryAbbrev), respectRangeConstraints=FALSE, ...){
   ## <<cobb-douglas functions, eval=TRUE>>=
   ####################
   # Returns an nls Cobb-Douglas model (without energy) for the country specified. 
@@ -1050,16 +1050,16 @@ cdeModel <- function(countryAbbrev,
   return(res)
 }
 
[…]

### 2014-04-28 Scrap/Econ-Growth-Resampling.R

@@ -228,8 +228,8 @@ resampleFits <- function(
   }
   # First do a fit without resampling and get these coefficients
   origModel <- switch(modelType,
-                      "sf"          = singleFactorModel(data=data, factor=factor, respectRangeConstraints=TRUE),
-                      "cd"          = cdModel(data=data, respectRangeConstraints=TRUE),
+                      "sf"          = sfModel(data=data, factor=factor, respectRangeConstraints=TRUE),
+                      "cd"          = cdwoeModel(data=data, respectRangeConstraints=TRUE),
                       "cde"         = cdeModel(data=data, energyType=energyType, respectRangeConstraints=TRUE),
                       "ces"         = cesModel2(data=data),
                       "cese-(kl)e"  = cesModel2(countryAbbrev=countryAbbrev, nest="(kl)e", energyType=energyType),
@@ -256,7 +256,7 @@ resampleFits <- function(
   resampleFitCoeffs <- switch(modelType,
                               "sf"    = for (i in 1:n){
                                 resampleData <- doResample(data=data, origModel=origModel, method=method)
-                                model <- singleFactorModel(data=resampleData, factor=factor, respectRangeConstraints=TRUE)
+                                model <- sfModel(data=resampleData, factor=factor, respectRangeConstraints=TRUE)
                                 resampleCoeffs <- attr(x=model, which="naturalCoeffs")
                                 resampleCoeffs$method <- method
                                 coeffs <- rbind.fill(coeffs, resampleCoeffs)
@@ -265,7 +265,7 @@ resampleFits <- function(
                               },
                               "cd"    = for (i in 1:n){
                                 resampleData <- doResample(data=data, origModel=origModel, method=method)
-                                model <- cdModel(data=resampleData, factor=factor, respectRangeConstraints=TRUE)
+                                model <- cdwoeModel(data=resampleData, factor=factor, respectRangeConstraints=TRUE)
                                 resampleCoeffs <- attr(x=model, which="naturalCoeffs")
                                 resampleCoeffs$method <- method
                                 coeffs <- rbind.fill(coeffs, resampleCoeffs)

### 2014-04-28 Scripts/BaseModels.R

@@ -24,11 +24,11 @@ ModelInfos <- list(
   list( formulaStr = c("iY ~ iK + iYear", 
                        "iY ~ iL + iYear",
                        "iY ~ energy + iYear"),
-        fun = "singleFactorModel",
+        fun = "sfModel",
         dots = list()),
   list( formulaStr = c("iY ~ iK + iL + iYear",
                        "iY ~ iK + iL + energy + iYear"),
-        fun = "cobbDouglasModel",
+        fun = "cdModel",
         dots = list()),
   list( formulaStr = "iY ~ iK + iL + energy + iYear",
         fun = "linexModel",

### 2014-04-28 Testing/RefactorTesting.R

@@ -2,10 +2,10 @@ require(EconModels2)
 
 All <- read.table("data/AllData.txt", header=TRUE)
 
-model.cd1 <-  cdModel( response = iY, capital=iK, labor=iL, time=iYear, data=subset(All, Country=="US") )
+model.cd1 <-  cdwoeModel( response = iY, capital=iK, labor=iL, time=iYear, data=subset(All, Country=="US") )
 naturalCoef( model.cd1 )
 
-model.cd2 <- cdModel( iY ~ iK + iL + iYear, data=subset(All, Country=="US") )
+model.cd2 <- cdwoeModel( iY ~ iK + iL + iYear, data=subset(All, Country=="US") )
 naturalCoef( model.cd2 )
 
 model.cde1 <- cdeModel( response = iY, capital=iK, labor=iL, energy=iU, time=iYear, data=subset(All, Country=="US") )
@@ -21,13 +21,13 @@ model.linex2 <-  linexModel( response=iY, capital= iK, labor=iL, energy=iU, time
                data=subset(All, Country=="US") )
 naturalCoef( model.linex2 )
 
-model.sf1 <-  singleFactorModel( iY ~ iK + iYear, data=subset(All, Country=="US") )
+model.sf1 <-  sfModel( iY ~ iK + iYear, data=subset(All, Country=="US") )
 naturalCoef( model.sf1 )
 
-model.sf2 <- singleFactorModel( response=iY, factor=iK, time=iYear, data=subset(All, Country=="US") )
+model.sf2 <- sfModel( response=iY, factor=iK, time=iYear, data=subset(All, Country=="US") )
 naturalCoef( model.sf2 )
 
-model.sf3 <- singleFactorModel( iY ~ iK + iYear, data=subset(All, Country=="US"), constrained=TRUE )
+model.sf3 <- sfModel( iY ~ iK + iYear, data=subset(All, Country=="US"), constrained=TRUE )
 naturalCoef( model.sf3 ) 
 
 model.ces1 <- cesModel( iY ~ iK + iL + iQ + iYear, data=subset(All, Country=="US"))

### 2014-04-28 Testing/ResamplingTesting.R

@@ -15,12 +15,12 @@ ModelInfos <- list(
   list( formulaStr = c("iY ~ iK + iYear", 
                        "iY ~ iL + iYear",
                        "iY ~ energy + iYear"),
-        fun = "singleFactorModel",
+        fun = "sfModel",
         n=lots,
         dots = list()),
   list( formulaStr = c("iY ~ iK + iL + iYear",
                        "iY ~ iK + iL + energy + iYear"),
-        fun = "cobbDouglasModel",
+        fun = "cdModel",
         n=lots,
         dots = list()),
   list( formulaStr = "iY ~ iK + iL + energy + iYear",

### 2014-04-28 Scrap/CES.Rnw
Changed to iGDP everywhere (from iY).

@@
 modelUKQ_LM <- cesEstPlus(data=dataUK, 
-                      yName="iY", 
+                      yName="iGDP", 
                       xNames=c("iK", "iL", "iQ"), 
@@
 modelUKQ_LM2 <- cesEstPlus(data=dataUK, 
-                      yName="iY", 
+                      yName="iGDP", 
                       xNames=c("iL", "iQ", "iK"), 
@@
 modelUKQ_LBFGSB <- cesEstPlus(data=dataUK, 
-                          yName="iY", 
+                          yName="iGDP", 
                           xNames=c("iK", "iL", "iQ"), 
@@
 modelUKQ_grid <- cesEstPlus(data=dataUK, 
-                        yName="iY", 
+                        yName="iGDP", 
                         xNames=c("iK", "iL", "iQ"), 
@@
 modelUKQ_grid_detail <- cesEstPlus(data=dataUK, 
-                        yName="iY", 
+                        yName="iGDP", 
                         xNames=c("iK", "iL", "iQ"), 
@@
 modelUK <- cesEstPlus(data=dataUK, 
-                        yName="iY", 
+                        yName="iGDP", 
                         xNames=c("iK", "iL"), 

### 2014-04-28 Scrap/EconGrowth-R-Functions.Rnw
Changed to iGDP everywhere (from iY).

@@
   } else if (factor == "Y"){
-    colName <- "iY"
+    colName <- "iGDP"
   } else if (factor == "K"){
@@
     # Calculate covariances among the typical variables.
-    dataForCovar <- cbind(data$iY, data$iK, data$iL, data$iQ, data$iX, data$iU)
+    dataForCovar <- cbind(data$iGDP, data$iK, data$iL, data$iQ, data$iX, data$iU)
     # Calculates the covariances among y, k. l, q, x, and u using all available data, namely,
@@
   } else {
-    dataForCovar <- cbind(data$iY, data$iK, data$iL, data$iQ, data$iX)
+    dataForCovar <- cbind(data$iGDP, data$iK, data$iL, data$iQ, data$iX)
     covarResults <- cor(dataForCovar)
@@
   }
-  graph <- xyplot(iY+iK+iL+iQ+iX+iU ~ Year | Country, data=dataTable,
+  graph <- xyplot(iGDP+iK+iL+iQ+iX+iU ~ Year | Country, data=dataTable,
                   type = graphType,
@@
   # Runs a non-linear least squares fit to the data. We've replaced beta with 1-alpha for simplicity.
-  model <- iY ~ exp(lambda*iYear) * f^m
+  model <- iGDP ~ exp(lambda*iYear) * f^m
   modelSF <- nls(formula=model, data=dataTable, start = start)
-#   model <- iY ~ exp(lambda*iYear) * f^m
+#   model <- iGDP ~ exp(lambda*iYear) * f^m
 #   modelSF <- wrapnls(formula=model, data=dataTable, start=list(lambda=lambdaGuess, m=mGuess))
@@
   }  
-  graph <- xyplot(iY+predGDPK+predGDPL+predGDPQ+predGDPX+predGDPU ~ Year | Country, data=dataTable,
+  graph <- xyplot(iGDP+predGDPK+predGDPL+predGDPQ+predGDPX+predGDPU ~ Year | Country, data=dataTable,
                   type=graphType,
@@
   data <- loadData(countryAbbrev)
-  y_act <- data[ ,"iY"] # Pick off the GDP column
+  y_act <- data[ ,"iGDP"] # Pick off the GDP column
   y_act <- data.frame(y_act)
@@
   # Runs a non-linear least squares fit to the data. We've replaced beta with 1-alpha for simplicity.
-  model <- iY ~ exp(lambda*iYear) * iK^alpha * iL^(1 - alpha)
+  model <- iGDP ~ exp(lambda*iYear) * iK^alpha * iL^(1 - alpha)
   modelCD <- nls(formula=model, data=dataTable, start=start,
@@
   # * gamma = 1 - max(a, b)
-  model <- iY ~ exp(lambda*iYear) * iK^min(a,b) * iL^abs(b-a) * iEToFit^(1.0 - max(a,b))
+  model <- iGDP ~ exp(lambda*iYear) * iK^min(a,b) * iL^abs(b-a) * iEToFit^(1.0 - max(a,b))
   modelCDe <- nls(formula=model, data = dataTable, start = start,
@@
   start <- list(lambda=lambdaGuess, alpha=alphaGuess)
-  model <- iY ~ exp(lambda*iYear) * iK^alpha * iL^((1-gamma) - alpha) * iEGamma
+  model <- iGDP ~ exp(lambda*iYear) * iK^alpha * iL^((1-gamma) - alpha) * iEGamma
   modelCDe <- nls(formula=model, data = dataTable, start = start,
@@
   }
-  graph <- xyplot(iY+predGDP+predGDPQ+predGDPX+predGDPU ~ Year | Country, data=dataTable,
+  graph <- xyplot(iGDP+predGDP+predGDPQ+predGDPX+predGDPU ~ Year | Country, data=dataTable,
                   type=graphType,
@@
 tName = "iYear"
-yName = "iY"
+yName = "iGDP"
 
@@
   # Runs a non-linear least squares fit to the data with constraints
-  modelLINEX <- nls(iY ~ iEToFit * exp(a_0*(2.0 - (iL+iEToFit)/iK) + a_0 * c_t *(iL/iEToFit - 1.0)), 
+  modelLINEX <- nls(iGDP ~ iEToFit * exp(a_0*(2.0 - (iL+iEToFit)/iK) + a_0 * c_t *(iL/iEToFit - 1.0)), 
                   data=dataTable,
@@
   }  
-  graph <- xyplot(iY+predGDPQ+predGDPX+predGDPU ~ Year | Country, data=dataTable,
+  graph <- xyplot(iGDP+predGDPQ+predGDPX+predGDPU ~ Year | Country, data=dataTable,
                   type=graphType,

### 2014-04-28 Testing/ExperimentingWithPlots.Rnw
Changed to iGDP everywhere (from iY).

@@
   print( 
-    qplot( Year, iY, group=ResampleNumber, 
+    qplot( Year, iGDP, group=ResampleNumber, 
            data=nestData, # subset(foo, Country=="US"), 

### 2014-04-28 Packages/EconData/R/files.R

@@ -370,7 +370,7 @@ loadCESSpaghettiGraphData <- function(nest="(kl)", energyType="none", archive=NU
   # We apply the nest argument as given to the data frame. 
   # Doing so assists with graphing later.
   actual <- loadData(baseHistorical=baseHistorical)
-  actual <- actual[c("Year", "iY", "Country")]
+  actual <- actual[c("Year", "iGDP", "Country")]
   actual$ResampleNumber <- NA
   actual$Type <- "actual"
   actual$Resampled <- FALSE
@@ -384,7 +384,7 @@ loadCESSpaghettiGraphData <- function(nest="(kl)", energyType="none", archive=NU
   prediction <- cesPredictionsColumn(energyType=energyType, nest=nest, baseHistorical=baseHistorical, baseResample=baseResample)
   pred <- actual
   # Replace the historical GDP data with the predicted GDP data, which is in column 1.
-  pred$iY <- prediction[,1]
+  pred$iGDP <- prediction[,1]
   pred$ResampleNumber <- NA
   pred$Type <- "fitted"
   pred$Resampled <- FALSE
@@ -392,7 +392,7 @@ loadCESSpaghettiGraphData <- function(nest="(kl)", energyType="none", archive=NU
   pred$nest <- nest
   
   # Remove rows where predicted GDP is NA, i.e., those rows where we don't have a prediction.
-  pred <- subset(pred, !is.na(iY))
+  pred <- subset(pred, !is.na(iGDP))
   
   # Remove rows where we don't need historical data or predictions, 
   # specifically those times when we won't have a prediction.
@@ -449,7 +449,7 @@ loadCESSpaghettiGraphData <- function(nest="(kl)", energyType="none", archive=NU
     nYears <- length(fitted(resampleModels[[1]]))
     dfList[[countryAbbrev]] <- data.frame(
       Year = rep(historical$Year, nResamples),
-      iY = unlist(lapply( resampleModels, fitted )),
+      iGDP = unlist(lapply( resampleModels, fitted )),
       Country = countryAbbrev,
       ResampleNumber = rep( 1:nResamples, each=nYears ),
       Type = "fitted",

### 2014-04-28 Packages/EconModels/R/Fitting.R

@@ -241,8 +241,8 @@ cdwoeModel <- function(formula, data, response, capital, labor, time, constraine
   
   formulas <- list(
     log(y) - log(labor) ~ time + I(log(capital) - log(labor)),
-    log(iY) - log(iK) ~ iYear,  
-    log(iY) - log(iL) ~ iYear 
+    log(iGDP) - log(iK) ~ iYear,  
+    log(iGDP) - log(iL) ~ iYear 
   )
   
   formulas <- lapply( formulas,
@@ -858,7 +858,7 @@ linexModel <- function(formula, data, response, capital, labor, energy, time, sa
   )
   attr(res, "naturalCoeffs") <- naturalCoeffs
   #  sdata <- subset(data, 
-  #                  select= c( "iY","iEToFit","iK","iL","rho_k","rho_l"))
+  #                  select= c( "iGDP","iEToFit","iK","iL","rho_k","rho_l"))
   sdata <- subset(data, select = all.vars(res$terms))
   sdata <- data[complete.cases(sdata), unique(c(all.vars(res$terms), names(data)))]
   if (save.data) {

### 2014-04-28 Packages/EconModels/R/Graphics.R

@@ -185,15 +185,15 @@ spaghettiPlot <- function(energyType='none',
   data$alph = alph
   split <- intersect( split, names(data) )
   seData <- ddply( subset(data, Type=="fitted"), split, summarise, 
-                   n = length(iY),
-                   lower= quantile(iY, alph[1]),
-                   upper= quantile(iY, 1-alph[1]),
-                   iY = iY[1]
+                   n = length(iGDP),
+                   lower= quantile(iGDP, alph[1]),
+                   upper= quantile(iGDP, 1-alph[1]),
+                   iGDP = iGDP[1]
   ) 
   # return(seData)
   # return(names(data))
-  # graph <- qplot(Year, iY, group=ResampleNumber, data=data, facets = ~Country, geom="line", alpha=I(alpha))
-  graph <- ggplot( data=subset(data, Type=="actual"), aes(Year, iY)) 
+  # graph <- qplot(Year, iGDP, group=ResampleNumber, data=data, facets = ~Country, geom="line", alpha=I(alpha))
+  graph <- ggplot( data=subset(data, Type=="actual"), aes(Year, iGDP)) 
   graph <- graph + geom_smooth(aes(ymin=lower, ymax=upper), col=NA, fill="gray10", 
                                lty=1, size=.5, data=seData, stat="identity")
 #  graph <- graph + geom_area(fill="black", shape=1, alpha=0.05)
@@ -219,7 +219,7 @@ spaghettiPlot <- function(energyType='none',
 #' in \code{data}. The graphs are arranged vertically by country with year on the horizontal axis.
 #' You can change the vertical order of the graphs with \code{levels(data$Country)}. 
 #' \code{data} is assumed to contain the following columns: 
-#' \code{iY} (indexed GDP), 
+#' \code{iGDP} (indexed GDP), 
 #' \code{Year} (the year for each row in the table), 
 #' \code{iK} (indexed capital stock), 
 #' \code{iL} (indexed labor), 
@@ -231,7 +231,7 @@ spaghettiPlot <- function(energyType='none',
 #' @export
 historicalPlot <- function(data){
   graph <- ggplot(aes(x=Year), data=data) +
-    geom_line(aes(y=iY, lty="y")) +
+    geom_line(aes(y=iGDP, lty="y")) +
     geom_line(aes(y=iK, lty="k")) +
     geom_line(aes(y=iL, lty="l")) +
     geom_line(aes(y=iQ, lty="q")) +

### 2014-04-28 Packages/EconModels0/R/Fitting.R

@@ -78,7 +78,7 @@ predict.LINEXmodel <- function( object, ... ) {
 #  e <- NextMethod()
 #  return( exp(e) )
 #  # model has form:
-#  # log(iY) - log(iEToFit) ~ I(2 * (1 - 1/rho_k)) +  I(rho_l - 1)
+#  # log(iGDP) - log(iEToFit) ~ I(2 * (1 - 1/rho_k)) +  I(rho_l - 1)
 #  lx0 <- eval( parse( text = gsub( ".* - ", "", names(object$model)[1]) ), attr(object,'data'))
 #  ly <- eval( parse( text = gsub( " - .*", "", names(object$model)[1]) ), attr(object,'data'))
 #  y <- exp(ly)
@@ -174,7 +174,7 @@ cesModel2 <- function(countryAbbrev,
   }
   # Establish key variable names  
   tName <- "iYear"
-  yName <- "iY"
+  yName <- "iGDP"
   models <- list()
   for (algorithm in algorithms) {
     #
@@ -403,7 +403,7 @@ sfModel <- function(countryAbbrev, baseHistorical, data=loadData(countryAbbrev, 
     start <- list(lambda=lambdaGuess, m=mGuess)
   }
   # Runs a non-linear least squares fit to the data. We've replaced beta with 1-alpha for simplicity.
-  model <- iY ~ exp(lambda*iYear) * f^m
+  model <- iGDP ~ exp(lambda*iYear) * f^m
   modelSF <- nls(formula=model, data=data, start = start, control=nlsControl)
   # Build the additional object to add as an atrribute to the output
   if (!respectRangeConstraints){
@@ -435,9 +435,9 @@ cdwoeModel <- function(countryAbbrev, baseHistorical, data=loadData(countryAbbre
   # alphaGuess <- 0.7 # 0.7 gives good results for all countries.  
   # start <- list(lambda=lambdaGuess, alpha=alphaGuess)
   # Runs a non-linear least squares fit to the data. We've replaced beta with 1-alpha for simplicity.
-  # model <- iY ~ exp(lambda*iYear) * iK^alpha * iL^(1.0 - alpha)
+  # model <- iGDP ~ exp(lambda*iYear) * iK^alpha * iL^(1.0 - alpha)
   # modelCD <- nls(formula=model, data=data, start=start, control=nlsControl)
[…]

### 2014-04-28 Packages/EconModels0/R/Graphics.R

@@ -185,15 +185,15 @@ spaghettiPlot <- function(energyType='none',
   data$alph = alph
   split <- intersect( split, names(data) )
   seData <- ddply( subset(data, Type=="fitted"), split, summarise, 
-                   n = length(iY),
-                   lower= quantile(iY, alph[1]),
-                   upper= quantile(iY, 1-alph[1]),
-                   iY = iY[1]
+                   n = length(iGDP),
+                   lower= quantile(iGDP, alph[1]),
+                   upper= quantile(iGDP, 1-alph[1]),
+                   iGDP = iGDP[1]
   ) 
   # return(seData)
   # return(names(data))
-  # graph <- qplot(Year, iY, group=ResampleNumber, data=data, facets = ~Country, geom="line", alpha=I(alpha))
-  graph <- ggplot( data=subset(data, Type=="actual"), aes(Year, iY)) 
+  # graph <- qplot(Year, iGDP, group=ResampleNumber, data=data, facets = ~Country, geom="line", alpha=I(alpha))
+  graph <- ggplot( data=subset(data, Type=="actual"), aes(Year, iGDP)) 
   graph <- graph + geom_smooth(aes(ymin=lower, ymax=upper), col=NA, fill="gray10", 
                                lty=1, size=.5, data=seData, stat="identity")
 #  graph <- graph + geom_area(fill="black", shape=1, alpha=0.05)
@@ -230,7 +230,7 @@ historicalPlot <- function(countryAbbrev, baseHistorical){
     data <- loadData(countryAbbrev=countryAbbrev, baseHistorical=baseHistorical)
   }
   graph <- ggplot(aes(x=Year), data=data) +
-    geom_line(aes(y=iY, lty="y")) +
+    geom_line(aes(y=iGDP, lty="y")) +
     geom_line(aes(y=iK, lty="k")) +
     geom_line(aes(y=iL, lty="l")) +
     geom_line(aes(y=iQ, lty="q")) +

### 2014-04-28 Packages/EconModels0/R/Resampling.R

@@ -431,20 +431,20 @@ doResample <- function(data, origModel, method=resampleMethods, reindexGDP=TRUE)
   #         residual:  resamples the residuals and applies them to the data. All years are present.
   #         wild:      same as residuals but randomly select sign of resampled residuals
   # reindexGDP:
-  #         TRUE (default) will rescale iY values so that the observation in the first year (row) is 1.0
-  #         FALSE leaves iY values untouched.
+  #         TRUE (default) will rescale iGDP values so that the observation in the first year (row) is 1.0
+  #         FALSE leaves GDP values untouched.
   ##
   method <- match.arg(method)
   if(method == "resample") {
     out <- resample(data)
   } else {
     out <- data    
-    out[ , "iY"] <- NA
-    out[ , "iY"] <- resampledResponse(origModel, method=method)
+    out[ , "iGDP"] <- NA
+    out[ , "iGDP"] <- resampledResponse(origModel, method=method)
   }
   if (reindexGDP){
-    # Divide all the values in the iY column by the first value in the column
-    out[ , "iY"] <- out[ , "iY"] / out[1, "iY"]
+    # Divide all the values in the iGDP column by the first value in the column
+    out[ , "iGDP"] <- out[ , "iGDP"] / out[1, "iGDP"]
   }
   return(out)
 }

### 2014-04-28 Packages/EconModels0/R/load.R

@@ -67,7 +67,7 @@ loadCESSpaghettiGraphData <- function(nest="(kl)", energyType="none", archive=NU
   # We apply the nest argument as given to the data frame. 
   # Doing so assists with graphing later.
   actual <- loadData(baseHistorical=baseHistorical)
-  actual <- actual[c("Year", "iY", "Country")]
+  actual <- actual[c("Year", "iGDP", "Country")]
   actual$ResampleNumber <- NA
   actual$Type <- "actual"
   actual$Resampled <- FALSE
@@ -81,7 +81,7 @@ loadCESSpaghettiGraphData <- function(nest="(kl)", energyType="none", archive=NU
   prediction <- cesPredictionsColumn(energyType=energyType, nest=nest, baseHistorical=baseHistorical, baseResample=baseResample)
   pred <- actual
   # Replace the historical GDP data with the predicted GDP data, which is in column 1.
-  pred$iY <- prediction[,1]
+  pred$iGDP <- prediction[,1]
   pred$ResampleNumber <- NA
   pred$Type <- "fitted"
   pred$Resampled <- FALSE
@@ -89,7 +89,7 @@ loadCESSpaghettiGraphData <- function(nest="(kl)", energyType="none", archive=NU
   pred$nest <- nest
   
   # Remove rows where predicted GDP is NA, i.e., those rows where we don't have a prediction.
-  pred <- subset(pred, !is.na(iY))
+  pred <- subset(pred, !is.na(iGDP))
   
   # Remove rows where we don't need historical data or predictions, 
   # specifically those times when we won't have a prediction.
@@ -146,7 +146,7 @@ loadCESSpaghettiGraphData <- function(nest="(kl)", energyType="none", archive=NU
     nYears <- length(fitted(resampleModels[[1]]))
     dfList[[countryAbbrev]] <- data.frame(
       Year = rep(historical$Year, nResamples),
-      iY = unlist(lapply( resampleModels, fitted )),
+      iGDP = unlist(lapply( resampleModels, fitted )),
       Country = countryAbbrev,
       ResampleNumber = rep( 1:nResamples, each=nYears ),
       Type = "fitted",

### 2014-04-28 Packages/EconModels0/R/plotting.R

@@ -104,7 +104,7 @@ sf3DSSEGraph <- function(countryAbbrev, factor, showOpt=TRUE, baseHistorical, ba
   colnames(newX) <- c("lambda", "m")
   # Get the actual GDP data
   data <- loadData(countryAbbrev=countryAbbrev, baseHistorical=baseHistorical)
-  y_act <- data[ ,"iY"] # Pick off the GDP column
+  y_act <- data[ ,"iGDP"] # Pick off the GDP column
   y_act <- data.frame(y_act)
   # Need the model to make predictions
 #   model <- sfModel(countryAbbrev=countryAbbrev, factor=factor, baseHistorical=baseHistorical)
@@ -274,7 +274,7 @@ loadCDSpaghettiGraphData <- function(energyType="none", archive=NULL, baseHistor
   
   # Put the historical data in a data.frame. 
   actual <- loadData(baseHistorical=baseHistorical)
-  actual <- actual[c("Year", "iY", "Country")]
+  actual <- actual[c("Year", "iGDP", "Country")]
   actual$ResampleNumber <- NA
   actual$Type <- "actual"
   actual$Resampled <- FALSE
@@ -284,14 +284,14 @@ loadCDSpaghettiGraphData <- function(energyType="none", archive=NULL, baseHistor
   prediction <- cobbDouglasPredictionsColumn(energyType=energyType, baseHistorical=baseHistorical)
   pred <- actual
   # Replace the historical GDP data with the predicted GDP data, which is in column 1.
-  pred$iY <- prediction[,1]
+  pred$iGDP <- prediction[,1]
   pred$ResampleNumber <- NA
   pred$Type <- "fitted"
   pred$Resampled <- FALSE
   pred$Energy <- energyType
   
   # Remove rows where predicted GDP is NA, i.e., those rows where we don't have a prediction.
-  pred <- subset(pred, !is.na(iY))
+  pred <- subset(pred, !is.na(iGDP))
   
   # Figure out which countries we need to loop over.
   if (energyType == "U"){
@@ -326,7 +326,7 @@ loadCDSpaghettiGraphData <- function(energyType="none", archive=NULL, baseHistor
     nYears <- length(fitted(resampleModels[[1]]))
     dfList[[countryAbbrev]] <- data.frame(
       Year = rep(historical$Year, nResamples),
-      iY = unlist(lapply( resampleModels, yhat)),
+      iGDP = unlist(lapply( resampleModels, yhat)),
[…]

### 2014-04-28 Packages/EconModels0/R/tables.R

@@ -6,7 +6,7 @@ covarianceTable <- function(countryAbbrev, baseHistorical){
   data <- loadData(countryAbbrev=countryAbbrev, baseHistorical=baseHistorical)
   if (countryAbbrev %in% countryAbbrevsU){
     # Calculate covariances among the typical variables.
-    dataForCovar <- cbind(data$iY, data$iK, data$iL, data$iQ, data$iX, data$iU)
+    dataForCovar <- cbind(data$iGDP, data$iK, data$iL, data$iQ, data$iX, data$iU)
     # Calculates the covariances among y, k. l, q, x, and u using all available data, namely,
     # 1980-2011 for covariances among y, k, l, q, and x for developed economies
     # 1980-2000 for covariances involving u for developed economies
@@ -15,7 +15,7 @@ covarianceTable <- function(countryAbbrev, baseHistorical){
     covarResults <- data.frame(cor(x=dataForCovar, use="pairwise.complete.obs"))
     names <- c("$y$", "$k$", "$l$", "$q$", "$x$", "$u$")
   } else {
-    dataForCovar <- cbind(data$iY, data$iK, data$iL, data$iQ, data$iX)
+    dataForCovar <- cbind(data$iGDP, data$iK, data$iL, data$iQ, data$iX)
     covarResults <- cor(dataForCovar)
     names <- c("$y$", "$k$", "$l$", "$q$", "$x$")
   }

### 2014-04-28 Scrap/BaseModels.R

@@ -21,35 +21,35 @@ names(countryAbbrevsU) <- countryAbbrevsU
 # Single Factor models
 #
 modelsSFK <- lapply(countryAbbrevs, function(countryAbbrev){
-  sfModel(formula=iY ~ iK + iYear, data=subset(data, Country==countryAbbrev))
+  sfModel(formula=iGDP ~ iK + iYear, data=subset(data, Country==countryAbbrev))
 })
 modelsSFL <- lapply(countryAbbrevs, function(countryAbbrev){
-  sfModel(formula=iY ~ iL + iYear, data=subset(data, Country==countryAbbrev))
+  sfModel(formula=iGDP ~ iL + iYear, data=subset(data, Country==countryAbbrev))
 })
 modelsSFQ <- lapply(countryAbbrevs, function(countryAbbrev){
-  sfModel(formula=iY ~ iQ + iYear, data=subset(data, Country==countryAbbrev))
+  sfModel(formula=iGDP ~ iQ + iYear, data=subset(data, Country==countryAbbrev))
 })
 modelsSFX <- lapply(countryAbbrevs, function(countryAbbrev){
-  sfModel(formula=iY ~ iX + iYear, data=subset(data, Country==countryAbbrev))
+  sfModel(formula=iGDP ~ iX + iYear, data=subset(data, Country==countryAbbrev))
 })
 modelsSFU <- lapply(countryAbbrevsU, function(countryAbbrev){
-  sfModel(formula=iY ~ iU + iYear, data=subset(data, Country==countryAbbrev))
+  sfModel(formula=iGDP ~ iU + iYear, data=subset(data, Country==countryAbbrev))
 })
 
 #
 # Cobb-Douglas models
 #
 modelsCD <- lapply(countryAbbrevs, function(countryAbbrev){
-  cdwoeModel(formula=iY ~ iK + iL + iYear, data=subset(data, Country==countryAbbrev))
+  cdwoeModel(formula=iGDP ~ iK + iL + iYear, data=subset(data, Country==countryAbbrev))
 })
 modelsCDQ <- lapply(countryAbbrevs, function(countryAbbrev){
-  cdwoeModel(formula=iY ~ iK + iL + iQ + iYear, data=subset(data, Country==countryAbbrev))
+  cdwoeModel(formula=iGDP ~ iK + iL + iQ + iYear, data=subset(data, Country==countryAbbrev))
 })
[…]

### 2014-04-28 Scrap/Econ-Growth-Functions.R

@@ -187,7 +187,7 @@ columnIndex <- function(dataTable, factor){
   if (factor == "Year"){
     colName <- "iYear"
   } else if (factor == "Y"){
-    colName <- "iY"
+    colName <- "iGDP"
   } else if (factor == "K"){
     colName <- "iK"
   } else if (factor == "L"){
@@ -227,7 +227,7 @@ covarianceTable <- function(countryAbbrev){
   data <- loadData(countryAbbrev)
   if (countryAbbrev %in% countryAbbrevsU){
     # Calculate covariances among the typical variables.
-    dataForCovar <- cbind(data$iY, data$iK, data$iL, data$iQ, data$iX, data$iU)
+    dataForCovar <- cbind(data$iGDP, data$iK, data$iL, data$iQ, data$iX, data$iU)
     # Calculates the covariances among y, k. l, q, x, and u using all available data, namely,
     # 1980-2011 for covariances among y, k, l, q, and x for developed economies
     # 1980-2000 for covariances involving u for developed economies
@@ -236,7 +236,7 @@ covarianceTable <- function(countryAbbrev){
     covarResults <- data.frame(cor(x=dataForCovar, use="pairwise.complete.obs"))
     names <- c("$y$", "$k$", "$l$", "$q$", "$x$", "$u$")
   } else {
-    dataForCovar <- cbind(data$iY, data$iK, data$iL, data$iQ, data$iX)
+    dataForCovar <- cbind(data$iGDP, data$iK, data$iL, data$iQ, data$iX)
     covarResults <- cor(dataForCovar)
     names <- c("$y$", "$k$", "$l$", "$q$", "$x$")
   }
@@ -296,7 +296,7 @@ createHistoricalLatticeGraph <- function(countryAbbrev, textScaling = 1.0, keyXL
     indexCond <- list(c(1))                           # We want only one country.
     layout <- onePanelLayoutSpec                      # We want only one panel in the graph.
   }
-  graph <- xyplot(iY+iK+iL+iQ+iX+iU ~ Year | Country, data=dataTable,
+  graph <- xyplot(iGDP+iK+iL+iQ+iX+iU ~ Year | Country, data=dataTable,
                   type = graphType,
                   index.cond = indexCond, #orders the panels.
                   layout = layout, 
@@ -348,9 +348,9 @@ sfModel <- function(countryAbbrev, factor){
   }
[…]

### 2014-04-28 Scrap/Econ-Growth-Functions2.R

@@ -249,7 +249,7 @@ columnIndex <- function(data, factor){
   if (factor == "Year"){
     colName <- "iYear"
   } else if (factor == "Y"){
-    colName <- "iY"
+    colName <- "iGDP"
   } else if (factor == "K"){
     colName <- "iK"
   } else if (factor == "L"){
@@ -290,7 +290,7 @@ covarianceTable <- function(countryAbbrev){
   data <- loadData(countryAbbrev)
   if (countryAbbrev %in% countryAbbrevsU){
     # Calculate covariances among the typical variables.
-    dataForCovar <- cbind(data$iY, data$iK, data$iL, data$iQ, data$iX, data$iU)
+    dataForCovar <- cbind(data$iGDP, data$iK, data$iL, data$iQ, data$iX, data$iU)
     # Calculates the covariances among y, k. l, q, x, and u using all available data, namely,
     # 1980-2011 for covariances among y, k, l, q, and x for developed economies
     # 1980-2000 for covariances involving u for developed economies
@@ -299,7 +299,7 @@ covarianceTable <- function(countryAbbrev){
     covarResults <- data.frame(cor(x=dataForCovar, use="pairwise.complete.obs"))
     names <- c("$y$", "$k$", "$l$", "$q$", "$x$", "$u$")
   } else {
-    dataForCovar <- cbind(data$iY, data$iK, data$iL, data$iQ, data$iX)
+    dataForCovar <- cbind(data$iGDP, data$iK, data$iL, data$iQ, data$iX)
     covarResults <- cor(dataForCovar)
     names <- c("$y$", "$k$", "$l$", "$q$", "$x$")
   }
@@ -361,7 +361,7 @@ createHistoricalLatticeGraphOld <- function(countryAbbrev, textScaling = 1.0, ke
     layout <- onePanelLayoutSpec                      # We want only one panel in the graph.
   }
   graph <- ggplot(aes(x=Year), data=data) +
-    geom_line(aes(y=iY, lty="iGPD")) +
+    geom_line(aes(y=iGDP, lty="iGPD")) +
     geom_line(aes(y=iK, lty="iK")) +
     geom_line(aes(y=iL, lty="iL")) +
     geom_line(aes(y=iQ, lty="iQ")) +
@@ -371,7 +371,7 @@ createHistoricalLatticeGraphOld <- function(countryAbbrev, textScaling = 1.0, ke
     theme_minimal()
   return(graph)
   
[…]

### 2014-04-28 Scrap/Graphics.R

@@ -173,15 +173,15 @@ spaghettiPlot <- function(energyType='none',
   data$alph = alph
   split <- intersect( split, names(data) )
   seData <- ddply( subset(data, Type=="fitted"), split, summarise, 
-                   n = length(iY),
-                   lower= quantile(iY, alph[1]),
-                   upper= quantile(iY, 1-alph[1]),
-                   iY = iY[1]
+                   n = length(iGDP),
+                   lower= quantile(iGDP, alph[1]),
+                   upper= quantile(iGDP, 1-alph[1]),
+                   iGDP = iGDP[1]
   ) 
   # return(seData)
   # return(names(data))
-  # graph <- qplot(Year, iY, group=ResampleNumber, data=data, facets = ~Country, geom="line", alpha=I(alpha))
-  graph <- ggplot( data=subset(data, Type=="actual"), aes(Year, iY)) 
+  # graph <- qplot(Year, iGDP, group=ResampleNumber, data=data, facets = ~Country, geom="line", alpha=I(alpha))
+  graph <- ggplot( data=subset(data, Type=="actual"), aes(Year, iGDP)) 
   graph <- graph + geom_smooth(aes(ymin=lower, ymax=upper), col=NA, fill="gray10", 
                                lty=1, size=.5, data=seData, stat="identity")
 #  graph <- graph + geom_area(fill="black", shape=1, alpha=0.05)
@@ -216,7 +216,7 @@ historicalPlot <- function(countryAbbrev){
     data <- loadData(countryAbbrev)
   }
   graph <- ggplot(aes(x=Year), data=data) +
-    geom_line(aes(y=iY, lty="y")) +
+    geom_line(aes(y=iGDP, lty="y")) +
     geom_line(aes(y=iK, lty="k")) +
     geom_line(aes(y=iL, lty="l")) +
     geom_line(aes(y=iQ, lty="q")) +

### 2014-04-30 Article/EconGrowth2.Rnw
EconGrowth2.Rnw now uses loadResampledData function for the CD ternary plot.

--- 2014-04-25 Article/EconGrowth2.Rnw
@@
 # Relative path to historical data from Article
-baseHistorical <- file.path("..", "data")
-historicalData <- Econ2011
+# baseHistorical <- file.path("..", "data")
+historicalData <- Econ2011 # From the EconData package
 
@@
 # We need to define a directory path from "Article" to the resample data results
-archive <- file.path("..", "data_resample_2014-04-24_Refactored-Code_n=1000.zip")
-baseResample <- "data_resample" # Define the directory within the archive wherein we can find the data.
+archive <- file.path("..", "data_resample_2014-04-29_Refactored-EconData_n=2.zip")
+# baseResample <- "data_resample" # Define the directory within the archive wherein we can find the data.
 # Load the fits to the original historical data out of the archive we're using.
 # This object (oModels) should be passed in to functions that need information from orig fits.
-f <- gzcon(unz(archive, file.path(baseResample, "oModels.Rdata")))
+f <- gzcon(unz(archive, file.path("oModels.Rdata")))
 oModels <- readRDS(f)
@@
 <<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=2.9, fig.height=7.7, fig.cap="Cobb-Douglas resample model parameters.">>=
-  dataCD <- loadAllResampleData(modelType="cd", countryAbbrevsOrder=countryAbbrevs, energyType="none", baseResample=baseResample)
-  dataCDQ <- loadAllResampleData(modelType="cde", countryAbbrevsOrder=countryAbbrevs, energyType="Q", baseResample=baseResample)
-  data <- rbind.fill(dataCD, dataCDQ)
-  standardTriPlot(data=data, facet_formula=countryAbbrev~energy)
+data <- loadResampledData(archive=archive, 
+                          country=countryAbbrevs, 
+                          model="cd", 
+                          factors=c("iK+iL", "iK+iL+iQ"), 
+                          prefix="coeffs")
+# Rearrange the factors to obtain our preferred ordering of countries.
+for (l in rev(countryAbbrevs)) { data$countryAbbrev <- relevel(data$countryAbbrev, ref=l) }
+# Replace all NA's in energyType with "none"
+
+# Rearrange the factors to obtain our preferred ordering of countries.
+
+for (l in rev(energyTypes)) { data$energyType <- relevel(data$energyType, ref=l) }
+standardTriPlot(data=data, facet_formula=countryAbbrev~energyType)
 @

### 2014-05-02 Article/EconGrowth2.Rnw
Added argument names to unz function.
Beginning the process of getting the paper to build after refactoring EconData.

@@
 # We need to define a directory path from "Article" to the resample data results
-archive <- file.path("..", "data_resample_2014-04-29_Refactored-EconData_n=2.zip")
+archive <- file.path("..", "data_resample_2014-05-01_Refactored-EconData_n=1000.zip")
 # baseResample <- "data_resample" # Define the directory within the archive wherein we can find the data.
@@
 # This object (oModels) should be passed in to functions that need information from orig fits.
-f <- gzcon(unz(archive, file.path("oModels.Rdata")))
+f <- gzcon(unz(description=archive, filename=file.path("oModels.Rdata")))
 oModels <- readRDS(f)
@@
                           factors=c("iK+iL", "iK+iL+iQ"), 
-                          prefix="coeffs")
+                          kind="coeffs")
 # Rearrange the factors to obtain our preferred ordering of countries.
-for (l in rev(countryAbbrevs)) { data$countryAbbrev <- relevel(data$countryAbbrev, ref=l) }
+# for (lev in rev(countryAbbrevs)) { data$country <- relevel(data$country, ref=lev) }
 # Replace all NA's in energyType with "none"
 
-# Rearrange the factors to obtain our preferred ordering of countries.
-
-for (l in rev(energyTypes)) { data$energyType <- relevel(data$energyType, ref=l) }
-standardTriPlot(data=data, facet_formula=countryAbbrev~energyType)
+# Rearrange the factors to obtain our preferred ordering of energy types.
+# for (lev in rev(energyTypes)) { data$energy <- relevel(data$energy, ref=lev) }
+standardTriPlot(data=data, facet_formula=country~energy)
 @
@@
 <<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=8.2, fig.cap="Cobb-Douglas fitted models.">>=
-cdData <- loadCDSpaghettiGraphData(energyType="none", baseHistorical=baseHistorical, baseResample=baseResample)
-cdQData <- loadCDSpaghettiGraphData(energyType="Q", baseHistorical=baseHistorical, baseResample=baseResample)
-cdData <- rbind(cdData, cdQData)
+# cdData <- loadCDSpaghettiGraphData(energyType="none", baseHistorical=baseHistorical, baseResample=baseResample)
+# cdQData <- loadCDSpaghettiGraphData(energyType="Q", baseHistorical=baseHistorical, baseResample=baseResample)
+# cdData <- rbind(cdData, cdQData)
+cdData <- loadResampledData(archive=archive, country=countryAbbrevs, model="cd", factors=c("iK+iL", "iK+iL+iQ"), kind="fitted")
 spaghettiPlot(data=cdData, facet_formula=Country~Energy, level=spaghettiGraphLevel) +

### 2014-05-03 Article/EconGrowth2.Rnw
Changing levels of factors on graphs in the article.

@@
 <<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=2.9, fig.height=7.7, fig.cap="Cobb-Douglas resample model parameters.">>=
-data <- loadResampledData(archive=archive, 
+cdCoeffsData <- loadResampledData(archive=archive, 
                                   country=countryAbbrevs, 
@@
                                   kind="coeffs")
-# Rearrange the factors to obtain our preferred ordering of countries.
-# for (lev in rev(countryAbbrevs)) { data$country <- relevel(data$country, ref=lev) }
-# Replace all NA's in energyType with "none"
-
-# Rearrange the factors to obtain our preferred ordering of energy types.
-# for (lev in rev(energyTypes)) { data$energy <- relevel(data$energy, ref=lev) }
-standardTriPlot(data=data, facet_formula=country~energy)
+# Rearrange the country factors to obtain our preferred ordering.
+cdCoeffsData$country <- as.factor(cdCoeffsData$country)
+for (lev in rev(countryAbbrevs)) { cdCoeffsData$country <- relevel(cdCoeffsData$country, ref=lev) }
+# Rearrange the energy factors to obtain our preferred ordering.
+cdCoeffsData$energy <- replace(cdCoeffsData$energy, which(is.na(cdCoeffsData$energy)), "none")
+cdCoeffsData$energy <- as.factor(cdCoeffsData$energy)
+energyLevels <- c(none="none", Q="iQ")
+for (lev in rev(energyLevels)) { cdCoeffsData$energy <- relevel(cdCoeffsData$energy, ref=lev) }
+standardTriPlot(data=cdCoeffsData, facet_formula=country~energy)
 @
@@
 # cdData <- rbind(cdData, cdQData)
-cdData <- loadResampledData(archive=archive, country=countryAbbrevs, model="cd", factors=c("iK+iL", "iK+iL+iQ"), kind="fitted")
-spaghettiPlot(data=cdData, facet_formula=Country~Energy, level=spaghettiGraphLevel) +
+cdFittedData <- loadResampledData(archive=archive, 
+                                  country=countryAbbrevs, 
+                                  model="cd", 
+                                  factors=c("iK+iL", "iK+iL+iQ"), 
+                                  kind="fitted")
+spaghettiPlot(data=cdSpagData, facet_formula=Country~Energy, level=spaghettiGraphLevel) +
     labs(y="Indexed GDP (1980=1 or 1991=1)")
@@
 <<CES_lambda_gamma_graph, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models.">>=
-cesQResampleData <- loadCESResampleData(nest="all", energyType="Q", baseResample=baseResample)
-standardScatterPlot(data=cesQResampleData, mapping=aes(gamma_coef, lambda), facet_formula=countryAbbrev~nest, alpha=0.05) +
+cesCoeffsData <- loadResampledData(archive=archive, 
+                                   country=countryAbbrevs, 
+                                   model="ces", 
+                                   factors=c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"), 
+                                   kind="coeffs")
+standardScatterPlot(data=cesCoeffsData, mapping=aes(gamma_coef, lambda), facet_formula=country~nestStr, alpha=0.05) +
     scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
@@
 <<CES_sigma1_delta1_graph, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models.">>=
-standardScatterPlot(data=cesQResampleData, mapping=aes(delta_1, sigma_1), facet_formula=countryAbbrev~nest, alpha=0.05) +
+standardScatterPlot(data=cesCoeffsData, mapping=aes(delta_1, sigma_1), facet_formula=country~nestStr, alpha=0.05) +
     coord_trans(y="sigma") +
@@
 <<CES_sigma_delta_graph, fig.pos="H", fig.align='center', fig.width=4.5, fig.height=7, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models.">>=
-standardScatterPlot(data=subset(cesQResampleData, nest!="(kl)"), 
-                    mapping=aes(delta, sigma), facet_formula=countryAbbrev~nest, alpha=0.05) +
+standardScatterPlot(data=subset(cesCoeffsData, nestStr != "iK+iL"),
+                    mapping=aes(delta, sigma), facet_formula=country~nestStr, alpha=0.05) +
     coord_trans(y="sigma") +
@@
 <<CES_ternary_graph, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models.">>=
-cesTriPlotData=loadCESResampleData(energyType="Q", nest="all", baseResample=baseResample)
-standardTriPlot(data=cesTriPlotData)
+# cesTriPlotData=loadCESResampleData(energyType="Q", nest="all", baseResample=baseResample)
+# standardTriPlot(data=cesTriPlotData)
+standardTriPlot(data=cesCoeffsData, facet_formula=country~nestStr)
 @
@@
 <<CES_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models.">>=
-spagData <- loadCESSpaghettiGraphData(energyType="Q", nest="all", baseHistorical=baseHistorical, baseResample=baseResample)
-spaghettiPlot(data=spagData, facet_formula=Country~nest, level=spaghettiGraphLevel)+
+cesFittedData <- loadResampledData(archive=archive, 
+                                   country=countryAbbrevs, 
+                                   model="ces",
+                                   factors=c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"), 
+                                   kind="fitted")
+spaghettiPlot(data=cesFittedData, facet_formula=Country~nestStr, level=spaghettiGraphLevel) +
     labs(y="Indexed GDP (1980=1 or 1991=1)")
@@
 <<CES_Spaghetti_Graph_CN, fig.pos="H", fig.align='center', fig.width=maxWidth, fig.height=maxHeight, fig.cap="CES fitted models for China with the (kl)e nesting.">>=
-spaghettiPlot(data=subset(spagData, Country=="CN" & nest=="(kl)e"), level=spaghettiGraphLevel) +
+spaghettiPlot(data=subset(cesFittedData, Country=="CN" & nest=="iK+iL+iQ"), level=spaghettiGraphLevel) +
     labs(y="Indexed GDP (1980 = 1 or 1991 = 1")
@@
 <<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7, fig.cap="LINEX model (with energy) resampling results.">>=
-  linexResampleData <- loadAllResampleData(model="linex", energyType="Q", countryAbbrevsOrder=countryAbbrevs, 
-                                           baseResample=baseResample)
-  standardScatterPlot(data=linexResampleData, aes(a_0, c_t), facet_formula=countryAbbrev~energy, alpha=0.05) +
+linexCoeffsData <- loadResampledData(archive=archive, 
+                                     country=countryAbbrevs, 
+                                     model="linex", 
+                                     factors=c("iK+iL+iQ"), 
+                                     kind="coeffs")
+
+standardScatterPlot(data=linexCoeffsData, aes(a_0, c_t), facet_formula=country~energy, alpha=0.05) +
     labs(x=expression(a[0]), y=expression(c[t])) +
@@
 <<LINEX_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7.1, fig.cap="LINEX fitted models.">>=
-spagDataLinex <- loadLinexSpaghettiGraphData(energyType="Q", baseHistorical=baseHistorical, baseResample=baseResample)
-spaghettiPlot(data=spagDataLinex, facet_formula=Country ~ Energy, level=spaghettiGraphLevel) +
+linexFittedData <- loadResampledData(archive=archive, 
+                                     country=countryAbbrevs, 
+                                     model="linex",
+                                     factors=c("iK+iL+iQ"), 
+                                     kind="fitted")
+
+spaghettiPlot(data=linexFittedData, facet_formula=Country ~ Energy, level=spaghettiGraphLevel) +
     labs(y="Indexed GDP (1980=1 or 1991=1)")

### 2014-05-03 Article/EconGrowth2.Rnw
Changed country and energy levels on all scatter plots.

@@
                                    kind="coeffs")
+# Rearrange the country factors to obtain our preferred ordering.
+cesCoeffsData$country <- as.factor(cesCoeffsData$country)
+for (lev in rev(countryAbbrevs)) { cesCoeffsData$country <- relevel(cesCoeffsData$country, ref=lev) }
 standardScatterPlot(data=cesCoeffsData, mapping=aes(gamma_coef, lambda), facet_formula=country~nestStr, alpha=0.05) +
@@
                                      kind="coeffs")
+# Rearrange the country factors to obtain our preferred ordering.
+linexCoeffsData$country <- as.factor(linexCoeffsData$country)
+for (lev in rev(countryAbbrevs)) { linexCoeffsData$country <- relevel(linexCoeffsData$country, ref=lev) }
 

### 2014-05-04 Article/EconGrowth2.Rnw
Made a few changes to the description of the capital stock and labor efficiency terms for the Linex model.

@@
 # We need to define a directory path from "Article" to the resample data results
-archive <- file.path("..", "data_resample_2014-05-01_Refactored-EconData_n=1000.zip")
+archive <- file.path("..", "data_resample_2014-05-02_Refactored-EconData_n=1000.zip")
 # baseResample <- "data_resample" # Define the directory within the archive wherein we can find the data.
@@
 
-<<constants, include=FALSE>>=
+<<constants, include=FALSE, eval=TRUE>>=
 # Graph Heights
@@
 This model does, however, 
-instead includes terms that represent % physical factors:
+instead includes terms that represent
 efficiencies among capital, labor, and energy, which are included
 in the model in the form of 
-the quantities $\rho_k$ and $\rho_l$ which are defined by\footnote{The notation
+the ratios $\rho_k$ and $\rho_l$ which are defined by\footnote{The notation
 for the LINEX model breaks from the conventions used in the previous
@@
 and energy ($e$) will experience an increase in output ($y$) in excess 
-of its increase of energy consumption ($e$), because in that case
+of its increase of energy consumption ($e$), because
 \(
@@
     + c_t \left(\vphantom{\frac{1}{\rho_k}}\rho_l - 1 \right)\right]}
-	> 1 \;.
+	> 1.
 \) 
@@
 additional labor available to the economy. 
-$a_0$ represents the overall importance of these efficiencies, 
-and $c_t$ represents the relative importance 
-of the labor efficiency term compared to the capital stock efficiency term. 
+The parameter $a_0$ represents the overall importance of efficiencies $\rho_k$ and $\rho_l$, 
+and the parameter $c_t$ represents the relative importance 
+of the labor efficiency term ($\rho_l$) compared to the capital stock efficiency term ($\rho_k$). 
 % We treat $a_0$ and $c_t$ as fitting parameters; 

### 2014-05-04 Article/EconGrowth2.Rnw
Additional clarification on the LINEX model.

@@
 \ref{eq:CDe}) and the CES model (Equations~\ref{eq:CES}--\ref{eq:CESekl}), 
-the LINEX model (Equation~\ref{eq:LINEX}) does not include a generic time-dependent
-term but assumes energy ($e$) is the only factor of production.
-
-This model does, however, 
-instead includes terms that represent
-efficiencies among capital, labor, and energy, which are included
-in the model in the form of 
+the LINEX model (Equation~\ref{eq:LINEX}) does not include a generic, 
+time-dependent augmentation term ($A$).
+The LINEX models assumes energy ($e$) is the only factor of production.
+
+The LINEX model does, however, include terms that represent
+efficiencies among capital, labor, and energy, in the form of 
 the ratios $\rho_k$ and $\rho_l$ which are defined by\footnote{The notation
-for the LINEX model breaks from the conventions used in the previous
+for the LINEX model breaks from the conventions used in the Cobb-Douglas and CES
 models:  $a_0$ and $c_t$ are parameters and $\rho_k$ and $\rho_l$ are not.}
@@
 %
+An economy that increases 
+capital stock ($k$) and labor ($l$) at the same rate as energy will have
+capital and labor efficiency ratios ($\rho_k$ and $\rho_l$, respectively) of unity.
+In that case, economic output ($y$) increases at the same rate as energy consumption ($e$).
 According to the LINEX model, an economy that increases 
@@
 Similarly, an economy benefits by increasing labor ($l$) 
-without a commensurate increase in energy ($e$). Thus, $\rho_k$ is an 
+without a commensurate increase in energy ($e$). 
+Thus, $\rho_k$ is an 
 efficiency of using additional labor and energy to make 
@@
 additional labor available to the economy. 
+Increases in $\rho_k$ and $\rho_l$ provide upward pressure on economic output ($y$),
+as the only factor of production ($e$) is used more efficiently.
+
 The parameter $a_0$ represents the overall importance of efficiencies $\rho_k$ and $\rho_l$, 
@@
 of the labor efficiency term ($\rho_l$) compared to the capital stock efficiency term ($\rho_k$). 
-% We treat $a_0$ and $c_t$ as fitting parameters; 
-% both are assumed constant with respect to time.
+Both $a_0$ and $c_t$ are assumed constant with respect to time.
 

### 2014-05-04 Article/EconGrowth2.Rnw
Converting EconGrowth2.Rnw to use the new AllCoef.rda and AllFitted.rda files.

@@
 require(plyr)
+require(dplyr)
 # Provides access to data melting. 
@@
 
-# Pull in some constants and other important functions
-#source("Scripts/files.R")
-#source(file.path("..", "Scripts", "Constants.R"))
-
 # Load historical data
@@
 # Relative path to historical data from Article
-# baseHistorical <- file.path("..", "data")
 historicalData <- Econ2011 # From the EconData package
+
+# Load coefficients from all models in one large data frame
+coef_df<- tbl_df( readRDS("../AllCoef.rda") )
+fitted_df <- tbl_df( readRDS("../AllFitted.rda") )
 
@@
 # We need to define a directory path from "Article" to the resample data results
-archive <- file.path("..", "data_resample_2014-05-02_Refactored-EconData_n=1000.zip")
+# archive <- file.path("..", "data_resample_2014-05-02_Refactored-EconData_n=1000.zip")
 # baseResample <- "data_resample" # Define the directory within the archive wherein we can find the data.
 # Load the fits to the original historical data out of the archive we're using.
-# This object (oModels) should be passed in to functions that need information from orig fits.
-f <- gzcon(unz(description=archive, filename=file.path("oModels.Rdata")))
-oModels <- readRDS(f)
+
+# Load the original models.
+# f <- gzcon(unz(description=archive, filename=file.path("../oModels.Rdata")))
+oModels <- readRDS(file=file.path("..", "oModels.Rdata"))
 close(f)
@@
 <<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=2.9, fig.height=7.7, fig.cap="Cobb-Douglas resample model parameters.">>=
-cdCoeffsData <- loadResampledData(archive=archive, 
-                                  country=countryAbbrevs, 
-                                  model="cd", 
-                                  factors=c("iK+iL", "iK+iL+iQ"), 
-                                  kind="coeffs")
+cdCoeffsData <- filter(coef_df, model=="cd", nestStr==c("iK+iL", "iK+iL+iQ"))
+
 # Rearrange the country factors to obtain our preferred ordering.
@@
 cdCoeffsData$energy <- replace(cdCoeffsData$energy, which(is.na(cdCoeffsData$energy)), "none")
+cdCoeffsData$energy <- replace(cdCoeffsData$energy, which(cdCoeffsData$energy=="iQ"), "q")
 cdCoeffsData$energy <- as.factor(cdCoeffsData$energy)
-energyLevels <- c(none="none", Q="iQ")
+energyLevels <- c(none="none", q="q")
 for (lev in rev(energyLevels)) { cdCoeffsData$energy <- relevel(cdCoeffsData$energy, ref=lev) }
@@
 <<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=8.2, fig.cap="Cobb-Douglas fitted models.">>=
-# cdData <- loadCDSpaghettiGraphData(energyType="none", baseHistorical=baseHistorical, baseResample=baseResample)
-# cdQData <- loadCDSpaghettiGraphData(energyType="Q", baseHistorical=baseHistorical, baseResample=baseResample)
-# cdData <- rbind(cdData, cdQData)
-cdFittedData <- loadResampledData(archive=archive, 
-                                  country=countryAbbrevs, 
-                                  model="cd", 
-                                  factors=c("iK+iL", "iK+iL+iQ"), 
-                                  kind="fitted")
-spaghettiPlot(data=cdSpagData, facet_formula=Country~Energy, level=spaghettiGraphLevel) +
+cdFittedData <- filter(fitted_df, model=="cd", nest==c("iK+iL", "iK+iL+iQ"))
+# Rearrange the energy factors to obtain our preferred ordering.
+cdFittedData$energy <- replace(cdFittedData$energy, which(is.na(cdFittedData$energy)), "none")
+cdFittedData$energy <- replace(cdFittedData$energy, which(cdFittedData$energy=="iQ"), "q")
+cdFittedData$energy <- as.factor(cdFittedData$energy)
+energyLevels <- c(none="none", q="q")
+for (lev in rev(energyLevels)) { cdFittedData$energy <- relevel(cdFittedData$energy, ref=lev) }
+spaghettiPlot(data=cdFittedData, facet_formula=Country~energy, level=spaghettiGraphLevel) +
     labs(y="Indexed GDP (1980=1 or 1991=1)")
@@
 <<CES_lambda_gamma_graph, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models.">>=
-cesCoeffsData <- loadResampledData(archive=archive, 
-                                   country=countryAbbrevs, 
-                                   model="ces", 
-                                   factors=c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"), 
-                                   kind="coeffs")
+cesCoeffsData <- filter(coef_df, model=="ces", nestStr==c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"))
 # Rearrange the country factors to obtain our preferred ordering.
@@
 for (lev in rev(countryAbbrevs)) { cesCoeffsData$country <- relevel(cesCoeffsData$country, ref=lev) }
-standardScatterPlot(data=cesCoeffsData, mapping=aes(gamma_coef, lambda), facet_formula=country~nestStr, alpha=0.05) +
+standardScatterPlot(data=cesCoeffsData, mapping=aes(gamma_coef, lambda), facet_formula=country~nest, alpha=0.05) +
     scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
@@
 <<CES_sigma1_delta1_graph, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models.">>=
-standardScatterPlot(data=cesCoeffsData, mapping=aes(delta_1, sigma_1), facet_formula=country~nestStr, alpha=0.05) +
+standardScatterPlot(data=cesCoeffsData, mapping=aes(delta_1, sigma_1), facet_formula=country~nest, alpha=0.05) +
     coord_trans(y="sigma") +
@@
 standardScatterPlot(data=subset(cesCoeffsData, nestStr != "iK+iL"),
-                    mapping=aes(delta, sigma), facet_formula=country~nestStr, alpha=0.05) +
+                    mapping=aes(delta, sigma), facet_formula=country~nest, alpha=0.05) +
     coord_trans(y="sigma") +
@@
 # standardTriPlot(data=cesTriPlotData)
-standardTriPlot(data=cesCoeffsData, facet_formula=country~nestStr)
+standardTriPlot(data=cesCoeffsData, facet_formula=country~nest)
 @
@@
 <<CES_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models.">>=
-cesFittedData <- loadResampledData(archive=archive, 
-                                   country=countryAbbrevs, 
-                                   model="ces",
-                                   factors=c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"), 
-                                   kind="fitted")
-spaghettiPlot(data=cesFittedData, facet_formula=Country~nestStr, level=spaghettiGraphLevel) +
+cesFittedData <- filter(fitted_df, model=="ces", nest==c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"))
+spaghettiPlot(data=cesFittedData, facet_formula=Country~nest, level=spaghettiGraphLevel) +
     labs(y="Indexed GDP (1980=1 or 1991=1)")

### 2014-05-04 Article/EconGrowth2.Rnw
Linex graphs now working in the paper.

@@
 <<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7, fig.cap="LINEX model (with energy) resampling results.">>=
-linexCoeffsData <- loadResampledData(archive=archive, 
-                                     country=countryAbbrevs, 
-                                     model="linex", 
-                                     factors=c("iK+iL+iQ"), 
-                                     kind="coeffs")
+linexCoeffsData <- filter(coef_df, model=="linex", energy=="iQ")
 # Rearrange the country factors to obtain our preferred ordering.
@@
 for (lev in rev(countryAbbrevs)) { linexCoeffsData$country <- relevel(linexCoeffsData$country, ref=lev) }
-
 standardScatterPlot(data=linexCoeffsData, aes(a_0, c_t), facet_formula=country~energy, alpha=0.05) +
@@
 <<LINEX_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7.1, fig.cap="LINEX fitted models.">>=
-linexFittedData <- loadResampledData(archive=archive, 
-                                     country=countryAbbrevs, 
-                                     model="linex",
-                                     factors=c("iK+iL+iQ"), 
-                                     kind="fitted")
-
-spaghettiPlot(data=linexFittedData, facet_formula=Country ~ Energy, level=spaghettiGraphLevel) +
+# linexFittedData <- loadResampledData(archive=archive, 
+#                                      country=countryAbbrevs, 
+#                                      model="linex",
+#                                      factors=c("iK+iL+iQ"), 
+#                                      kind="fitted")
+
+linexFittedData <- filter(fitted_df, model=="linex", energy=="iQ")
+spaghettiPlot(data=linexFittedData, facet_formula=Country~energy, level=spaghettiGraphLevel) +
     labs(y="Indexed GDP (1980=1 or 1991=1)")

### 2014-05-05 Article/EconGrowth2.Rnw
EconGrowth2.Rnw now uses AllCoef.rda dna AllFitted.rda. Using %in% for all filtering.

--- 2014-05-04 Article/EconGrowth2.Rnw
@@
 # Load coefficients from all models in one large data frame
-coef_df<- tbl_df( readRDS("../AllCoef.rda") )
+coef_df <- tbl_df( readRDS("../AllCoef.rda") )
+# Rearrange the country factors to obtain our preferred ordering.
+coef_df$country <- as.factor(coef_df$country)
+for (lev in rev(countryAbbrevs)) { coef_df$country <- relevel(coef_df$country, ref=lev) }
+# Change the names of the energy factors to the names for the graph
+coef_df$energy <- replace(coef_df$energy, which(is.na(coef_df$energy)), "none")
+coef_df$energy <- replace(coef_df$energy, which(coef_df$energy=="iQ"), "q")
+coef_df$energy <- replace(coef_df$energy, which(coef_df$energy=="iX"), "x")
+coef_df$energy <- replace(coef_df$energy, which(coef_df$energy=="iU"), "u")
+# Rearrange the energy factors to obtain our preferred ordering.
+coef_df$energy <- as.factor(coef_df$energy)
+energyLevels <- c(none="none", q="q", x="x", u="u")
+for (lev in rev(energyLevels)) { coef_df$energy <- relevel(coef_df$energy, ref=lev) }
+
+# Load fitted data from all models in one large data frame
 fitted_df <- tbl_df( readRDS("../AllFitted.rda") )
-
-# Set up for loading resample results
-# We need to define a directory path from "Article" to the resample data results
-# archive <- file.path("..", "data_resample_2014-05-02_Refactored-EconData_n=1000.zip")
-# baseResample <- "data_resample" # Define the directory within the archive wherein we can find the data.
-# Load the fits to the original historical data out of the archive we're using.
+# Rearrange the energy factors to obtain our preferred ordering.
+fitted_df$energy <- replace(fitted_df$energy, which(is.na(fitted_df$energy)), "none")
+fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iQ"), "q")
+fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iX"), "x")
+fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iU"), "u")
+fitted_df$energy <- as.factor(fitted_df$energy)
+for (lev in rev(energyLevels)) { fitted_df$energy <- relevel(fitted_df$energy, ref=lev) }
 
 # Load the original models.
-# f <- gzcon(unz(description=archive, filename=file.path("../oModels.Rdata")))
 oModels <- readRDS(file=file.path("..", "oModels.Rdata"))
@@
 <<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=2.9, fig.height=7.7, fig.cap="Cobb-Douglas resample model parameters.">>=
-cdCoeffsData <- filter(coef_df, model=="cd", nestStr==c("iK+iL", "iK+iL+iQ"))
-
-# Rearrange the country factors to obtain our preferred ordering.
-cdCoeffsData$country <- as.factor(cdCoeffsData$country)
-for (lev in rev(countryAbbrevs)) { cdCoeffsData$country <- relevel(cdCoeffsData$country, ref=lev) }
-# Rearrange the energy factors to obtain our preferred ordering.
-cdCoeffsData$energy <- replace(cdCoeffsData$energy, which(is.na(cdCoeffsData$energy)), "none")
-cdCoeffsData$energy <- replace(cdCoeffsData$energy, which(cdCoeffsData$energy=="iQ"), "q")
-cdCoeffsData$energy <- as.factor(cdCoeffsData$energy)
-energyLevels <- c(none="none", q="q")
-for (lev in rev(energyLevels)) { cdCoeffsData$energy <- relevel(cdCoeffsData$energy, ref=lev) }
+cdCoeffsData <- filter(coef_df, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iQ"))
 standardTriPlot(data=cdCoeffsData, facet_formula=country~energy)
@@
 <<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=8.2, fig.cap="Cobb-Douglas fitted models.">>=
-cdFittedData <- filter(fitted_df, model=="cd", nest==c("iK+iL", "iK+iL+iQ"))
-# Rearrange the energy factors to obtain our preferred ordering.
-cdFittedData$energy <- replace(cdFittedData$energy, which(is.na(cdFittedData$energy)), "none")
-cdFittedData$energy <- replace(cdFittedData$energy, which(cdFittedData$energy=="iQ"), "q")
-cdFittedData$energy <- as.factor(cdFittedData$energy)
-energyLevels <- c(none="none", q="q")
-for (lev in rev(energyLevels)) { cdFittedData$energy <- relevel(cdFittedData$energy, ref=lev) }
+cdFittedData <- filter(fitted_df, model=="cd", nest %in% c("iK+iL", "iK+iL+iQ"))
 spaghettiPlot(data=cdFittedData, facet_formula=Country~energy, level=spaghettiGraphLevel) +
@@
 <<CES_lambda_gamma_graph, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models.">>=
-cesCoeffsData <- filter(coef_df, model=="ces", nestStr==c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"))
-# Rearrange the country factors to obtain our preferred ordering.
-cesCoeffsData$country <- as.factor(cesCoeffsData$country)
-for (lev in rev(countryAbbrevs)) { cesCoeffsData$country <- relevel(cesCoeffsData$country, ref=lev) }
+cesCoeffsData <- filter(coef_df, model=="ces", nestStr %in% c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"))
 standardScatterPlot(data=cesCoeffsData, mapping=aes(gamma_coef, lambda), facet_formula=country~nest, alpha=0.05) +
@@
 <<CES_ternary_graph, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models.">>=
-# cesTriPlotData=loadCESResampleData(energyType="Q", nest="all", baseResample=baseResample)
-# standardTriPlot(data=cesTriPlotData)
 standardTriPlot(data=cesCoeffsData, facet_formula=country~nest)
@@
 <<CES_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models.">>=
-cesFittedData <- filter(fitted_df, model=="ces", nest==c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"))
+cesFittedData <- filter(fitted_df, model=="ces", nest %in% c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"))
 spaghettiPlot(data=cesFittedData, facet_formula=Country~nest, level=spaghettiGraphLevel) +
@@
 <<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7, fig.cap="LINEX model (with energy) resampling results.">>=
-linexCoeffsData <- loadResampledData(archive=archive, 
-                                     country=countryAbbrevs, 
-                                     model="linex", 
-                                     factors=c("iK+iL+iQ"), 
-                                     kind="coeffs")
-# Rearrange the country factors to obtain our preferred ordering.
-linexCoeffsData$country <- as.factor(linexCoeffsData$country)
-for (lev in rev(countryAbbrevs)) { linexCoeffsData$country <- relevel(linexCoeffsData$country, ref=lev) }
-
+linexCoeffsData <- filter(coef_df, model=="linex", energy=="q")
 standardScatterPlot(data=linexCoeffsData, aes(a_0, c_t), facet_formula=country~energy, alpha=0.05) +
@@
 <<LINEX_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7.1, fig.cap="LINEX fitted models.">>=
-linexFittedData <- loadResampledData(archive=archive, 
-                                     country=countryAbbrevs, 
-                                     model="linex",
-                                     factors=c("iK+iL+iQ"), 
-                                     kind="fitted")
-
-spaghettiPlot(data=linexFittedData, facet_formula=Country ~ Energy, level=spaghettiGraphLevel) +
+linexFittedData <- filter(fitted_df, model=="linex", energy=="q")
+spaghettiPlot(data=linexFittedData, facet_formula=Country~energy, level=spaghettiGraphLevel) +
     labs(y="Indexed GDP (1980=1 or 1991=1)")

### 2014-05-14 Article/EconGrowth2.Rnw
Eliminated the unneeded close statement.
Updated version of Article that uses new style of loading Coef data within the package.

@@
 require(nlmrt)
-require(micEconCES)
+# require(micEconCES)
 require(plyr)
@@
 # Load coefficients from all models in one large data frame
-coef_df <- tbl_df( readRDS("../AllCoef.rda") )
+# coeffs_df <- tbl_df( readRDS("../AllCoef.rda") )
+coeffs_df <- tbl_df(AllCoef)
 # Rearrange the country factors to obtain our preferred ordering.
-coef_df$country <- as.factor(coef_df$country)
-for (lev in rev(countryAbbrevs)) { coef_df$country <- relevel(coef_df$country, ref=lev) }
+coeffs_df$country <- as.factor(coeffs_df$country)
+for (lev in rev(countryAbbrevs)) { coeffs_df$country <- relevel(coeffs_df$country, ref=lev) }
 # Change the names of the energy factors to the names for the graph
-coef_df$energy <- replace(coef_df$energy, which(is.na(coef_df$energy)), "none")
-coef_df$energy <- replace(coef_df$energy, which(coef_df$energy=="iQ"), "q")
-coef_df$energy <- replace(coef_df$energy, which(coef_df$energy=="iX"), "x")
-coef_df$energy <- replace(coef_df$energy, which(coef_df$energy=="iU"), "u")
+coeffs_df$energy <- replace(coeffs_df$energy, which(is.na(coeffs_df$energy)), "none")
+coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iQ"), "q")
+coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iX"), "x")
+coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iU"), "u")
 # Rearrange the energy factors to obtain our preferred ordering.
-coef_df$energy <- as.factor(coef_df$energy)
+coeffs_df$energy <- as.factor(coeffs_df$energy)
 energyLevels <- c(none="none", q="q", x="x", u="u")
-for (lev in rev(energyLevels)) { coef_df$energy <- relevel(coef_df$energy, ref=lev) }
+for (lev in rev(energyLevels)) { coeffs_df$energy <- relevel(coeffs_df$energy, ref=lev) }
 
 # Load fitted data from all models in one large data frame
-fitted_df <- tbl_df( readRDS("../AllFitted.rda") )
+# fitted_df <- tbl_df( readRDS("../AllFitted.rda") )
+fitted_df <- tbl_df(AllFitted)
 # Rearrange the energy factors to obtain our preferred ordering.
@@
 # Load the original models.
-oModels <- readRDS(file=file.path("..", "oModels.Rdata"))
-close(f)
+# oModels <- readRDS(file=file.path("..", "oModels.Rdata"))
+oModels <- OrigModels
 
@@
 <<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=2.9, fig.height=7.7, fig.cap="Cobb-Douglas resample model parameters.">>=
-cdCoeffsData <- filter(coef_df, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iQ"))
+cdCoeffsData <- filter(coeffs_df, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iQ"))
 standardTriPlot(data=cdCoeffsData, facet_formula=country~energy)
@@
 <<CES_lambda_gamma_graph, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models.">>=
-cesCoeffsData <- filter(coef_df, model=="ces", nestStr %in% c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"))
+cesCoeffsData <- filter(coeffs_df, model=="ces", nestStr %in% c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"))
 standardScatterPlot(data=cesCoeffsData, mapping=aes(gamma_coef, lambda), facet_formula=country~nest, alpha=0.05) +
@@
 <<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7, fig.cap="LINEX model (with energy) resampling results.">>=
-linexCoeffsData <- filter(coef_df, model=="linex", energy=="q")
+linexCoeffsData <- filter(coeffs_df, model=="linex", energy=="q")
 standardScatterPlot(data=linexCoeffsData, aes(a_0, c_t), facet_formula=country~energy, alpha=0.05) +
@@
 for insightful critique of the statistical analyses presented herein.
-The computations in this paper were accomplished using dahl.calvin.edu, 
+The computations in this paper were accomplished using \url{http://dahl.calvin.edu}, 
 a Beowulf cluster built with support from the National Science Foundation's 
 Major Research Instrumentation and Cyber Infrastructure programs, 
-grant no. OCI-0722819.
+grant number OCI-0722819.
 

### 2014-05-16 Article/EconGrowth2-GraphsOnly.Rnw
New file that has only graphs in it.

--- 2014-05-14 Article/EconGrowth2.Rnw
@@
 
-\section*{Notes from Martin}
-
-**** Additional references requested by Martin. Incorporate into paper? ****
-
-\citet{Lindenberger:2011dx}
-
-\citet{Stresing:2008cq}
-
-**** Notes from Martin ****
-
-To be included somewhere.
-
-Introduction
-
-[1. Listen to what others say
-Identify key issues and important voices]
-
-The availability of adequate energy at affordable costs 
-has become an important strategic issue in recent years.
-Despite a slowdown in economic growth worldwide, 
-longer-term trends in energy use remain strongly upwards, 
-as the dynamics of energy markets are increasingly determined by emerging economies, 
-notably China, India, and the Middle East \citep{IEA:2012ty}. 
-A large body of literature points to the fact that 
-economic growth and energy consumption are closely correlated 
-and for a diverse set of countries such as 
-the United States \citep{Stern:2000wq, Cleveland:1984p5055}, 
-India \citep{Paul:2004jl}, 
-China \citep{Wang:2011fe}, 
-South Africa \citep{Menyah:2010hl, Odhiambo:2009hj} and 
-sixteen Asian countries \citep{Lee:2008dm}
-to name a few, 
-although the causal relationship from energy consumption 
-to economic growth remains controversial \citep{Chen:2012fs, Ozturk:2010kb}. 
-\citet[p. 347]{Ozturk:2010kb} in a survey of the literature on the topic, 
-concluded that there is 
-``\dots no consensus neither on the existence nor on the direction of 
-causality between these variables in the literature,'' 
-but does point out that ``\dots causality is running from 
-electricity consumption to economic growth 
-in the most of these studies [surveyed].''
-
-Those that have accepted that energy use is closely correlated with
-economic performance in one form or another
-have expressed further concerns on the negative effects of 
-rising energy prices and fossil fuel depletion 
-on current and future economic growth.
-\citet{Benes:2012tm}, incorporating views on both
-geological physical constraints and 
-technological solutions to oil production, 
-suggest a near doubling of the real price of over the next decade.  
-\citet{Kumhof:2012ua} point out that 
-significant impacts on GDP growth could occur
-for larger oil supply shocks, 
-assuming production functions where oil plays a prominent role 
-and reduced possibilities for substitution away from oil.  
-\citet{Nel:2010fv} argue for the 
-``\dots vital importance of energy security \dots'' 
-on the basis of a model based on an explicit 
-energy-based formulation of economic growth.  
-\citet{Hamilton:2013vc} argues that 
-``[c]oping with a final peak in world oil production \dots 
-[will] have much in common with previous historical episodes that resulted from 
-temporary geopolitical conflict, 
-being associated with significant declines in employment and output. 
-If the future decades look like the last 5 years, we are in for a rough time.''
-
-The current trends in energy production and consumption and 
-the possible dire impacts on the world economy 
-as argued by above-mentioned scholars 
-have further raised the question of
-whether and how to include appropriate energy indicators 
-in economic growth modeling.  
-\citet[p. 26]{Stern:2011bq} provides an overview of how energy is included 
-in mainstream economic, resource economic, and ecological economic models of growth.  
-\citeauthor{Stern:2011bq} points out that energy is usually \emph{not included} 
-as a factor of production in mainstream economic growth models, 
-that energy is seen as the \emph{central driver of growth} 
-in ecological economic (including biophysical economic) models, 
-and that energy \emph{is included} in resource economic models, 
-but \emph{remains isolated} within this sub-discipline.  
-To break through this theoretical impasse, 
-Stern proposes a synthesized CES production function 
-where the constraints or abundance of energy 
-determines whether to include energy explicitly 
-as a factor of production.  
-On the basis of this model, 
-\citet[p. 45]{Stern:2011bq} points out that 
-energy availability plays
-``\dots a key role in enabling growth,''
-despite the evidence of decreasing energy consumed per unit of output.  
-He concludes, based on theory and time-series results, 
-that including energy in the production function is warranted, 
-and that further clarification is needed 
-on the role of energy in economic growth.
-
-The inclusion of energy as a factor of production 
-in CES and Cobb-Douglas production functions 
-is generally accepted by most 
-resource and energy economists and economic growth modelers 
-\citep{Smulders:2003wc, vanderZwaan:2002wn, Kemfert:1998vd}.
-Researchers interested in explaining long-term economic growth 
-and possible constraints on growth 
-have started to include energy as an explicit factor of production
-\citep{Froling:2009vo, Tahvonen:2001tz}.  
-An alternative approach, attempting to be 
-``\dots more consistent with physical laws \dots'' \citep{Ayres:2001tx}
-and classified by \citet{Stern:2011bq} as an ecological economic model of growth, 
-is the LINEX production function, 
-combining capital (non-ICT and ICT), 
-labour, and useful work. In the LINEX model, 
-technological change affects only 
-the amount of useful work done per joule of exergy \citep{Ayres:2005kn}.
-
-Unsatisfactorily, the choice of a production function 
-and the parameters used to populate these functions 
-affects results significantly.
-This situation leaves far too much latitude 
-for misuse of model specifications 
-and selection of parameters 
-to support certain theories (rather than empirically testing the theories
-and parameters \emph{before} they are employed).  
-For example, \citet{Lecca:2011kr} pointed out that 
-the modellers' choice for the structure of a production function 
-reflects his or her assumptions about
-the elasticities among inputs, and 
-``\dots the point at which energy enters the [nested CES] production function 
-has a significant impact on CGE [computable general equilibrium] model results.''
-\citet{Duffy:2000ty} rejected the Cobb-Douglas production function altogether, 
-finding that capital and labour are more substitutable 
-in richer countries and less substitutable in poorer countries 
-than Cobb-Douglas implies.  
-However, \citet{Miller:2008vd} points to the 
-``\dots reasonably accurate long-term economic forecasts,'' 
-achieved with the use of Cobb-Douglas production functions in economic models.  
-\citet{Shen:2013vp} provide a recent example 
-wherein empirical analysis on the estimated substitution elasticities 
-is performed before choosing any particular 
-nested CES production function structure. 
-As a result, \citeauthor{Shen:2013vp} propose an atypical structure 
-for the Chinese economy. **** More detail here about nesting? ****  
-Both the choice of production function structure 
-and the value of the model parameters 
-drive model results, and empirical and statistical testing 
-of such approaches is prudent, but rarely conducted.
-
-[2. Find our own voice
-What is our own argument?]
-
-These are not idle debates. 
-Economic growth models are often used to inform economic policy,
-and the paths of economies worldwide are determined by
-such policy choices. 
-Therefore, we agree with those who have serious concerns 
-about the reliability of the results from economic growth models \citep{Lecca:2011kr}. 
-\citet{Lecca:2011kr} and **** and what? **** would like to add
-**** ``would like to add'' or ``add''?**** that the inclusion of energy 
-would only further complicate issues.  **** Prev. sentence is unclear. ****
-We do except **** do you mean ``accept'' or ``expect'' here? ****, however, 
-that macroeconomic policymaking is needed 
-and is increasingly informed by integrated energy-economic models, 
-in a world where energy constraints are possible 
-\citep{Beckman:2011gb, Benes:2012tm, Nel:2010fv}.  
-We support the call from \citet{Shen:2013vp} that both
-the structure of the production function 
-and the parameters used to populate this function
-need empirical testing. 
-Furthermore, the quantification of energy ($q$, $x$, or $u$) 
-needs to be empirically assessed.  **** Need more on topic of energy quantification above. ****
-Building on the argument of \citet{Stern:2011bq} 
-that energy may or may not be required in production functions 
-depending on its abundance or scarcity, 
-we will further argue in this paper that different types of countries 
-may need different factors of production to explain their respective growth paths.  
-This further leaves open the possibility for 
-different explanations of growth in various countries
-at different stages of their development, 
-a central point of long-wave economic growth modeling 
-\citep{Froling:2009vo, Jones:2001wn, Galor:2000up}. 
-**** Should we discuss the longwave literature above? ****
-
-To gain insights from different countries across different stages of development, 
-we present a comparative analysis among 
-the World Bank’s main categories of countries, 
-namely Developed Countries (DCs), 
-Newly Industrialized Countries (NICs), 
-OPEC countries, and 
-Least Developed Countries (LDCs). 
-**** Move the previous sentence to the ``approach'' section below? ****
-
-Approach
-
-Build on articles using R to test econ growth PF, 
-question what is reported when doing these tests (shen/whalley and others who have used micEconCES).
-
-Discussion and Insights
-
-Does analysis differ from others in the conversation?
-Yes, differs as follows:
-\begin{itemize}
-\item{if one do these test, report on all $\delta$, $\sigma$, $\gamma$, and $\lambda$ 
-values as well as sse. 
-Good fits not evidence of best values, must report uncertainties as well.}
-\item{What motivates nesting of CES? Not well behaved $\rho$ results, driving $\sigma$s.
-Different type of CES with parsimonious factors, sigmas can be generated but not that easy (idea Randy).
-If you run all 3 nesting options, you can identify elasticities of all three factors in relation to each 
-other. Furthermore, you can determine which two factors are driving overall behavior in the aggregate function.}
-\item{necessary of different factors in PF to explain growth for countries in diff. development status}
-\end{itemize}
-
-What do we add to the conversation?
-
-\begin{itemize}
-
-\item{We are able to gain rich insights 
-on what really drives growth from detailed analysis (including uncertainties) 
-by testing all functional forms across many different 
-economy types.}
-
-\item{We were unable to gain new insights from the various energy quantifications that we tried.}
-
-\item{We find, surprisingly, that energy is not necessary 
-to be included alongside $k$ and $l$ in all PF. Models with energy and models without energy
-all perform well on an R$^2$ basis.}
-
-\item{We also find that
-
-(1) covariance of energy($e$) with both $k$ and $l$ is very high, with few exceptions (UK?).
-
-(2) with few exceptions, $\sigma_{(kl)e}$, $\sigma_{ke}$, and $\sigma_{le}$ 
-are all very low (indicating complementarity) (verify!!!!), and
-
-(3) energy-only models (SF$e$ and LINEX) achieve very good fits, just like CD$e$ and CES$e$.
-(should we make this point or not?)}
-
-\item{What does that mean? 
-It is a fallacy to think that saying energy is unnecessary 
-to include in an equation means energy is unimportant for economic growth. How to support this argument?
-
-If you find that energy is unnecessary to include alongside capital and labor 
-to explain growth in one economy at the macro, aggregated level, 
-you should not assume that energy is unimportant as a driver for economic growth for all economies.
-For developed economies, energy is captial intensive: you need to have large capital to make use 
-of energy. In developing economies, you don't need capital to make use of energy. 
-Rather, you need labor.
-
-We need to verify the above by comparison with our results.}
-
-\item{Also signals that different types of countries likely 
-to react differently to energy constraints. 
-Interpret $\sigma$ here, substitution possibilities.}
-
-\end{itemize}
-
-More work?
-
-Big picture
-[insert test test]
-
-Why do we do this? Want to link energy and economics on national level 
-and in a modeled approach,informing energy policy during energy transitions.
-Usually macro energy economic models rely on PF with energy included. 
-Key papers using CES in energy economics incl high impact such as 
-Stern, Gerlagh, Tol etc. 
-Cite in introduction met energy economists using PF approaches, specially CES.
-But, which form to choose and using which parameters? 
-Literature is inconclusive, very little actual empirical testing of such functions. 
-Mostly CES in CGE models used by Wbank and others. 
-CD adviced to be used by CBO. 
-How do we select a functional form and what are the parameters to be used? On what basis do we select?
-
-We aim. to search for empirically robust solution, one that stands up to statistical testing.
-
-What we find is counterintuitive for many cases: dropping energy from the PF has little impact, 
-but some notable exceptions. 
-On other hand, only including energy in a PF of LINEX form also yields good results and stats tests. 
-Is not a simple case for dropping energy, but acknowledging its key role. 
-Do we support the call for better bottom-up understanding? 
-What do we say on the limitations of macroeconomic modelling approaches altogether? 
-(Note such limitations are well known in ME literature, for example capital controversy Robinson).
-We speculate on implications for choosing PF in energy economic models that inform growth policy.
-
-Points on paper so far
-1. Does the relative small differences in fit between different production functions warrant 
-such a large debate on validity of one vs other? Clearly not. 
-CD been used by economists for ease of use and extreme flexibility (Miller).  
-PF generally used on instrumentalist grounds if give reasonable good description of data. 
-NK econ theory provide poor causal explanation of observed data, 
-but yet CD shows very good fit (miller, p17). 
-CES is  more general, but is a liability in forecasting because difficult 
-to get estimate of EoS that is consistent across studies (Miller, p26). 
-Aggregation is problem of both CD and CES functional forms, 
-so being careful when making strong inferences that cannot be justified.
-
-2. We think we can contribute by emphasising the need 
-for proper stats testing or inconsistent reporting on use of preferred functions. 
-Problems with empirical testing presented by Shen, Serrenho.
-What are our issues with multivariate OLS (Serrenho)?
-
-3. Are we joining the forced choice between production functions or 
-acknowledge the similar problems with aggregate prod functions in general? 
-Do we see this as sufficient evidence to doubt the top-down approach to econ growth altogether?
-
-4. R2 is a very crude measure and only very minor improvements 
-are achieved when others factors such as energy is added in a CD. 
-We concur. Puzzling is conclusion that such minor improvements 
-does prove the need to include energy in PF (Serrenho).
-
-5. We do think it is a choice between CD and CES (Miller) as 
-both have serious deficiencies after stats tests.
-
-6. One central issue within PF is elasticity of subs (EoS). 
-That is the \%ch in factor proportions ( k,l, etc) 
-because of one unit ch in MRTS. 
-MRTS is rate at which one factor can be substituted for another holding output constant. 
-EoS is low in Leontief cases, L shaped isoquants.
-
-7. Miller makes the point that even if parameters in model are stats artifacts, 
-they are still useful for forecasting. Do we agree?
-
-8. Is Ockham's razor relevant to what we are doing?
-
-9. Assumptions of CD are strongly rejected by empirical work, Miller still makes case for using CD.
-
-11. What about energy augmented
-
-10. TZ case
-CDno e: almost 80\% l
-CD with e: 25\% energy, rest c,importance of l drops to 0
-CES no e: 20\% c ($\sigma$), 80\% l, but large range
-CES with e: fig 35 e may be NB
-LINEX: one of lowest ct parameters (low relative importance of labour eff compared to cap eff)
-Does this mean that relative small increases in cap eff can really lift the economy?
-
-11. ZA case
-CD no e: roughly half c, l
-CD with e: roughly half, c, e, importance of l drops to 0
-CES no e: 10\% c, 25\% l ??
-CES with e: fig 35 e may be NB
-LINEX: one of highest ct parameters (high relative importance of labour eff compared to cap eff)
-Does this mean that relative small increases in labour eff can really lift the economy?
-
-12. Capital starved Zambia. Very high importance. Understand CES param better.
-
-Discussion: What is Next?
-
-a. A comparative analysis between diff PF reveal interesting 
-enough information to warrant a more diffused approach to countries. 
-Thus, we have a case for doing this for  all countries in the world 
-(or at least those representative of countries in different groups 80/20)
-
-b. If c is relatively more important than labour or energy 
-for growth and if capital stock is low, a situation one would expect in LDCs, 
-a relative small addition of capital stock can give relatively large returns in terms of growth.
-
-c. Now it becomes interesting, in a 'stages of growth' approach, 
-using LT econ data it may be the case that the importance 
-of factors are different across growth stages. 
-It would need a composite type of analysis - both stock and importance.
-
-d. Is it possible to have evidence of diff stocks and diff importances across phases of growth? 
-Maybe test this for a data rich nation that has worked through these stages, 
-we try to identify them and do partial analysis on time periods coinciding with these stages.
-
-Should we eliminate $u$ data? Only 3 countries. Only 20 years. Doesn't add much insight. 
-Too bad, but perhaps necessary to simplify paper.
-
-Discussions:
-
-Counterfactuals: energy, cap, labour what ifs for future.
-
-interpretation of type of economies, what does the data presentation say 
-on relative change in each input and change in GDP?
-
-Forcing const elast of subs in CES thru nested structures violates 
-observation that more than two factor will not be const. elasticities Uzawa 1962.
-
-R programming dealt with nested CES see paper discussion on Kemfert.
-
-Next steps:
-
-Stages of growth crowd implicitly assumes countries at similar stage of growth will
-have similar values for $\alpha$, $\beta$, $\gamma$. However, our results show
-that not to be true. Needs further exploration to cover more (all?) countries.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-**** Notes on the introduction from Martin ****
-
-1. Set scene through energy economic modelling papers. 
-Point out that PF approaches are alive and well (Stern, Tol, Gerlagh, World Bank, IMF), 
-short lit review as part of a longer introduction.  
-Mention competing PF approaches and parameter choice. 
-On what basis selection and how estimate parameters?
-
-2. Point out the need for adequate statistical testing and economic interpretation, 
-citing some earlier critical papers on PF limitations. Take issue with
-
-3. Spell out the contribution we will be making in this paper, 
-we are taking the approach that all models are wrong but some are useful. 
-We are after generating insights even after deeper assumptions of econ growth theory are very limiting.
-
-4. Introduce coordinates of analysis.
-
-**** Orignial introduction that MKH wrote ****
-
-Neoclassical economic growth theory attributes output ($Y$) to factors of production:
-capital stock ($K$) and labor ($L$). The Cobb-Douglas production function 
-is the 
-canonical representation of indexed economic output ($y$) as a function of indexed 
-labor ($l$), indexed capital stock ($k$), and an additional exogenous, time-dependent 
-term.%
-\footnote{The time-dependent term in production functions is often linked
-to ``technological progress,'' but that is a very narrow reading of Solow's original intent:
-\begin{quote}
-  It will be seen that I am using the phrase ``technical change''
-  as a short-hand expression for any kind of shift 
-  in the production function. 
-  Thus slowdowns, speed-ups, improvements in the education of the labor force, 
-  and all sorts of things will appear as ``technical change.''~\citep{solow1957technical}
-\end{quote}
-}
-This production function can be expressed as
 \begin{equation} \label{eq:CD}
@@
 \end{itemize}
-%Mathematically, $A$ is nothing more than a fitting parameter 
-%that aligns the predictions of Equation~\ref{eq:CD} 
-%with historical data. 
-%Thus, we refer to $A$ as the ``residual'' in this paper.} 
-%term ($A$):
-
-% $A$ is the residual term, 
-% with $\lambda$ 
-% indicating the change of the residual over time (in units of 
-% year$^{-1}$).
-Neoclassical economic growth theory as expressed in the Cobb-Douglas production 
-function makes no attempt to describe the mechanisms that affect
-economic growth, nor does it attempt to describe how such things as
-slowdowns, speedups, and improvements of the education of the labor force
-($\lambda$) might vary from one economy to the next. 
-The parameters $\alpha$ and $\beta$ indicate the relative roles 
-of capital and labor in the economy.
-Typically, the constraint $\alpha + \beta = 1$ is assumed, 
-indicating constant returns to scale.
-
-As shown in Equation~\ref{eq:CD} above, neoclassical economic theory does not 
-include an explicit term for the role of energy in economic growth. However, 
-\citet{Bashmakov:2007ek}, \citet{Hamilton:2009ui}, \citet{Murphy:2011jh}, 
-\citet{Benes:2012tm}, \citet{Kumhof:2012ua}, and others indicate that the 
-importance of energy for economic growth may far outweigh its cost share in the 
-economy. That neoclassical economic growth theory ignores energy is, therefore, 
-cause for concern, and inquiry into the proper approach for including energy 
-as a factor of production in economic growth modeling is both relevant and important.
-
-Some energy economists augment economic growth models by including energy as an 
-additional (or the only) factor of production. However, there is little agreement 
-on how this should be done. Neither the mathematical form of the energy-augmented 
-production function nor the quantification of energy are consistent in the 
-literature. There has been little empirical work assessing the predictive ability 
-of various energy-augmented production functions for different types of economies. 
-And, very few studies of the importance of energy in economic growth include 
-rigorous statistical assessments of energy-related fitting parameters. This paper 
-attempts to contribute to the literature by applying statistically rigorous 
-methods along three coordinates of analysis: form of the energy augmented 
-production function, energy quantification, and type of economy.
-
-The remainder of this paper is organized as follows. Section~\ref{sec:Coordinates} 
-discusses the coordinates of analysis described above. 
-Section~\ref{sec:Sources_of_Data} details sources of data and calculations to 
-generate time series for economic output and factors of production. The procedures 
-for and results from parameter estimation for the various production functions 
-are discussed in Section~\ref{sec:Parameter_Estimation}. 
-Section~\ref{sec:Discussion_of_Results} discusses implications of the parameter estimation 
-results, and Section~\ref{sec:Conclusion} concludes. An appendix provides details 
-of all statistical results.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Coordinates of Analysis} 
-\label{sec:Coordinates}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-This section describes the two coordinates of analysis and briefly reviews 
-literature related to each.
-
-%++++++++++++++++++++++++++++++
-\subsection{Mathematical Forms of the Energy-augmented Production Function} 
-\label{sec:Prod_Func_Forms}
-%++++++++++++++++++++++++++++++
-
-In this paper, we assess three prominent energy-augmented production functions 
-appear in the literature: Cobb-Douglas (CDe), Constant Elasticity of 
-Substitution (CESe), and LINear EXponential (LINEX). The following subsections 
-describe each.
-
-%------------------------------
-\subsubsection{Energy-augmented Cobb-Douglas Production Function (CDe)} 
-\label{sec:CDe}
-%------------------------------
-
-The capital-labor Cobb-Douglas production function shown in Equation~\ref{eq:CD}
-can be augmented to include an energy term:
-%Similarly, the energy-augmented Cobb-Douglas production function is
 
@@
 
-\citet{Ayres:2008cl} uses Equation~\ref{eq:CDe} with exergy ($x$) and 
-useful work ($u$) quantifications for $e$ to describe historic Japanese 
-and American economies from 1900-2000. \citet{Froling:2009vo} uses an 
-energy-augmented Cobb-Douglas production function with thermal energy 
-quantification ($q$) to describe output for the global economy from 
-1800--1970. Fr\"{o}ling's model endogenizes labor with respect to fertility 
-and mortality rates and separates thermal energy into two types: biomass 
-energy and coal energy. \citet{Serrenho:2010vq} use the log transform of 
-the energy-augmented Cobb-Douglas function with thermal energy 
-quantification ($q$) to describe output for the EU-15 countries. 
-Serrenho divides thermal energy into renewables, non-renewables, 
-wastes, and imports. The main argument of these papers is that 
-energy is an important driver of growth and needs to be included
-as an essential factor of production.
-
-**** Martin: add more here about the conclusions of each paper regarding 
-the role of energy in economic growth? Add additional literature? 
-Or, adjust as you see fit. Especially, are there any confidence intervals 
-or statistical evaluation in each of these studies? ****
-
-%------------------------------
-\subsubsection{Energy-augmented CES Production Function (CESe)} 
-\label{sec:CES}
-%------------------------------
-
-Other energy economists use an energy-augmented 
-Constant Elasticity of Substitution (CES$e$) production function to 
-describe economic growth. The \texttt{R} \citep{R} package 
-\texttt{micEconCES} \citep{Henningsen:2011td} estimates CES production 
-functions of the following forms (among others):
-
 \ceskl{\label{eq:CES}}
@@
 \ceskle{\label{eq:CESkle}}
-
-\noindent Equation~\ref{eq:CES} is a CES production function with 
-capital stock ($k$) and labor ($l$) factors of production. 
-Equation~\ref{eq:CESkle} augments Equation~\ref{eq:CES} with energy 
-using a ($kl$)($e$) nesting structure, as is typical in the literature. 
-Equation~\ref{eq:CES} is a degenerate form of Equation~\ref{eq:CESkle} 
-where $\delta \rightarrow 1$.
-
-$\gamma$ is a fitting parameter that represents productivity. 
-The fitting parameters $\rho_1$ and $\rho$ indicate elasticities 
-of substitution ($\sigma_1$ and $\sigma$).
-The elasticity of substitution 
-between capital ($k$) and labor ($l$) is given by 
-$\sigma_1 = \frac{1}{1+\rho_1}$, and
-the elasticity of substitution between ($kl$) and ($e$) is given by 
-$\sigma = \frac{1}{1+\rho}$. 
-As $\rho_1 \rightarrow 0$, $\sigma_1 \rightarrow 1$,
-and the embedded CES production function for $k$ and $l$ degenerates 
-to the Cobb-Douglas production function.
-Similarly, as $\rho \rightarrow 0$, $\sigma \rightarrow 1$,
-and the CES production function for $(kl)$ and $(e)$ degenerates 
-to the Cobb-Douglas production function.
-As $\sigma \rightarrow \infty$ ($\rho \rightarrow -1$), 
-($kl$) and ($e$) are perfect substitutes. 
-As $\sigma \rightarrow 0$ ($\rho \rightarrow \infty$), 
-($kl$) and ($e$) are perfect complements: 
-no substitution is possible. Similarly, 
-as $\sigma_1 \rightarrow 0$ ($\rho_1 \rightarrow \infty$),
-$k$ and $l$ are perfect complements.
-$\delta_1$ describes the relative importance of capital ($k$)
-and labor ($l$), and
-$\delta$ describes the importance of ($kl$) relative to ($e$).
 
@@
 
-Two other nestings of the factors of production ($k$, $l$, and $e$)
-are possible with the CES model.
-
 \ceslek{\label{eq:CESlek}}
@@
 \cesekl{\label{eq:CESekl}}
-
-\noindent Note that the $\rho$ ($\sigma$) and $\delta$ parameters have different
-meanings that depend upon the nesting of the factors of production.
-**** Do we want to define different variables that indicate meaning, 
-such as $\sigma_{kl}, \sigma_{(kl)e}, \delta_{(ek)l}$, and the like? If so, we'll 
-need to translate from $\rho$ and $\sigma$ in \texttt{cesEst} to the correct
-variable names in the paper. ****
-
-**** Describe here how 
-we implemented the constraints. ****
-
-\citet{VanderWerf:2008tc} evalutes various nested CES production 
-functions for 12 OECD countries with respect to climate change policy. 
-\citeauthor{VanderWerf:2008tc} concludes that ($kl$)($e$) nesting structure 
-best fits historical data. \citet{Lecca:2011kr} also evaluate a variety of 
-CES production functions using a KLEM structure to determine how the various 
-options for nesting the energy factor of production affect predictive ability. 
-\citet{Stern:2012ey} also use a CES production function of the form ($kl$)($e$). 
-\citeauthor{Stern:2012ey} apply their CES function to the Swedish economy 
-from 1800-2000 and demonstrate the importance of the transition from wood to 
-fossil fuels for economic growth. \citet{Shen:2013vp} included energy 
-in nested aggregated CES production functions 
-for China and found that the best nesting structure is ($le$)($k$).
-
-**** Martin: add more here about the conclusions of each paper regarding 
-the role of energy in economic growth? Add additional literature? 
-Or, adjust as you see fit. Especially, are there any confidence 
-intervals or statistical evaluation in each of these studies? ****
-
-%------------------------------
-\subsubsection{LINEX Production Function} 
-\label{sec:LINEX}
-%------------------------------
 
@@
 \end{equation}
-was derived from thermodynamic considerations
-\citep{Kummel:1980wx,Kummel:1982vy,Kummel:1985vz,Kummel:1989tf,Kummel:2002tx,Kummel:2010vz}. 
-%\noindent where $e$ is indexed energy and e is the base of 
-%the natural logarithm. 
-In contrast to both the Cobb-Douglas model (Equations~\ref{eq:CD} and 
-\ref{eq:CDe}) and the CES model (Equations~\ref{eq:CES}--\ref{eq:CESekl}), 
-the LINEX model (Equation~\ref{eq:LINEX}) does not include a generic, 
-time-dependent augmentation term ($A$).
-The LINEX models assumes energy ($e$) is the only factor of production.
-
-The LINEX model does, however, include terms that represent
-efficiencies among capital, labor, and energy, in the form of 
-the ratios $\rho_k$ and $\rho_l$ which are defined by\footnote{The notation
-for the LINEX model breaks from the conventions used in the Cobb-Douglas and CES
-models:  $a_0$ and $c_t$ are parameters and $\rho_k$ and $\rho_l$ are not.}
-%
+
 \begin{equation} \label{eq:rho_k}
@@
 
-\citet{Kummel:2002tx} use the 
-LINEX production function to describe economic output 
-for the economies of the U.S., Japan, and Germany. 
-\citet{Warr:2010ga} compare the LINEX production function with 
-the Cobb-Douglas production function to assess economic growth 
-for Austria, the United Kingdom, the United States, and Japan. 
-\citet{Ayres:2005kn} argued that introducing energy inputs 
-in traditional production functions does not improve its explanatory power, 
-but including useful work in a LINEX function does.
-
-\authNote{Martin: add more here about the conclusions of each paper 
-regarding the role of energy in economic growth? Add additional literature? 
-Or, adjust as you see fit. Especially, are there any confidence intervals 
-or statistical evaluation in each of these studies?}
-
-\authNote{If we want to keep this quote, it should be clearer what point we are trying to
-make with it. ---rjp}
-\citet{Abramovitz:1956aa} wrote:
-
-\begin{quote}
-  This result [that ``technological progress'' explained
-  175\% of the growth of the US economy since 1870] is surprising in the lopsided
-  importance which it appears to give to productivity increase,
-  and it should be, in a sense, sobering, if not discouraging,
-  to students of economic growth.
-  Since we know little about the causes of productivity increase,
-  the indicated importance of this element may be taken to be some sort of measure
-  of our ignorance about the causes of economic growth in the United States
-  and some sort of indication of where
-  we need to concentrate our attention.
-\end{quote}
-
-%++++++++++++++++++++++++++++++
-\subsection{Economy Types} 
-\label{sec:Economy_Types}
-%++++++++++++++++++++++++++++++
-
-In the energy-economic growth literature, the focus is 
-almost exclusively on developed economies from North America 
-or Europe. Examples include \citet{Kummel:1980wx} applying 
-LINEX to describe the West German economy, \citet{Serrenho:2010vq} 
-applying Cobb-Douglas variants to EU-15 countries, 
-\citet{VanderWerf:2008tc} applying CES nesting variants 
-to the 12 OECD countries, \citet{Lecca:2011kr} applying 
-CES nesting variants to the Scottish economy, \citet{Stern:2012ey} 
-applying CES to describe the Swedish economy, and \citet{Warr:2012cg} 
-using LINEX and Cobb-Douglas to describe the Austrian, 
-American, British, and Japanese economies.
-
-But, the near-exclusive focus on developed economies closes off 
-the possibility of discovering any role that energy plays 
-in the economic development process. In this paper we analyze at least 
+In this paper we analyze at least 
 two economies in each of the following four categories: 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Sources of Data}
-\label{sec:Sources_of_Data}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-To assess energy-augmented models of economic growth along the 
-coordinates of analysis outlined in Section~\ref{sec:Coordinates}, 
-historical data for economic output ($Y$), capital stock ($K$), 
-labor ($L$), and thermal energy ($Q$)   %, exergy ($X$), and useful work ($U$) 
-are required. Subsections below describe sources for and calculations 
-to obtain historical data. A final subsection presents the historical 
-data in graphical form.
-
-%++++++++++++++++++++++++++++++
-\subsection{Economic Output} 
-\label{sec:Economic_Output_Data}
-%++++++++++++++++++++++++++++++
-
-We measure economic output ($Y$) by gross domestic product (GDP). 
-GDP data in real 2005 U.S. dollars for developed countries (1980--2011) 
-and all other countries (1991--2011) was obtained from 
-the World Bank's Global Economic Prospects (GEP) database 
-\citep{WorldBankGEP:2013a}.
-
-%++++++++++++++++++++++++++++++
-\subsection{Capital Stock} 
-\label{sec:Capital_Stock_Data}
-%++++++++++++++++++++++++++++++
-
-Gross capital stock in real 2005 U.S. dollars 
-for developed countries (1980--2011) and 
-all other countries (1991--2011) was obtained from 
-the World Bank's Global Economic Prospects (GEP) database 
-\citep{WorldBankGEP:2013a}.
-
-%++++++++++++++++++++++++++++++
-\subsection{Labor and Employment}
-\label{sec:Labor_Data}
-%++++++++++++++++++++++++++++++
-
-Total employment and average hours worked per worker per year 
-for the developed nations (United States, United Kingdom, and Japan) 
-for 1980--2011 were obtained from the United States 
-\citet[Tables 6 and 7]{BLS:2013a}. Total hours worked per year was 
-calculated by multiplying total employment by average hours worked 
-per worker per year.
-
-The World Bank's World Development Indicators database 
-\citep{WorldBankWDI:2013a} provides the employment to population 
-ratio for people fifteen and older, total population, and a percentage 
-of people under fifteen for other economies (South Africa, China, Iran, 
-Saudi Arabia, Tanzania, and Zambia) for 1991--2011. The population 
-of people under fifteen years of age was subtracted from total population 
-to calculate the population of people fifteen and older. 
-Total employment was calculated by multiplying the employment to 
-population ratio of people fifteen and older by the population 
-of people fifteen and older.
-
-%++++++++++++++++++++++++++++++
-\subsection{Energy} 
-\label{sec:Energy_Data}
-%++++++++++++++++++++++++++++++
-
-To account for all energy input to an economy, we summed consumption data 
-for many energy sources, including coal, oil and petroleum products, 
-dry natural gas and natural gas plant liquids, nuclear power generation, 
-and renewable energy sources (solar, wind, geothermal, biomass/fuel wood, 
-and hydro). We also added human and animal muscle work. 
-Similar to the economic data discussed in 
-Sections~\ref{sec:Economic_Output_Data}--\ref{sec:Labor_Data}, 
-we obtained energy data for developed countries from 1980--2011. 
-For all other countries, 
-we obtained energy data for 1991--2011.
-
-Thermal energy ($Q$) for fuels (in units of TJ/year) was calculated by
-
-\begin{equation} \label{eq:thermal_energy}
-  Q_{fuel} = C_{fuel}h_{fuel}
-\end{equation}
-
-\noindent where $C_{fuel}$ is the consumption rate of the fuel 
-(in units of short tons/year for coal, barrels/year for oil and petroleum, 
-ft$^3$/year for dry natural gas and natural gas plant liquids, 
-and m$^3$/year for biomass/fuel wood) and $h_{{fuel}}$ is 
-the heat content of the fuel (in kJ/short ton for coal, kJ/barrel for oil, 
-kJ/ft$^3$ for dry natural gas and natural gas plant liquids, 
-and kJ/kg for biomass/fuel wood). Fuel wood density of 300~kg/m$^3$ 
-was taken from \citet{Ragland:2013wp} at the low end of the range 
-of density of dry wood and bark.
-
-Yearly consumption rates ($C_{fuel}$) of coal, oil and petroleum, 
-dry natural gas and natural gas plant liquids, and biofuels 
-(ethanol and biodiesel) were obtained from the \citet{EIA:2013a} 
-for all economies. Yearly average heat content data for coal, oil, 
-and natural gas and natural gas plant liquids was obtained from the 
-EIA for all economies. We used lower (net) heating values of 
-26.8~MJ/kg \citep[Table~A-27]{Cengel:2011ww} and 37.8~MJ/kg 
-\citep[Table~7.3]{Gupta:2010vg} for the heat content of ethanol 
-and corn-based biodiesel, respectively. Yearly consumption and 
-heat content data for biomass/fuel wood was obtained from the 
-``Fuelwood'' time series of the FAO Statistics Database 
-\citep{FAO:2013a}.
-
-For renewable and nuclear energy sources, yearly electricity 
-generation (in BTU/year) was available directly from 
-the \citet{EIA:2013a} for all economies, so 
-Equation~\ref{eq:thermal_energy} was unnecessary.
-
-Animal and human muscle work was estimated using an approach 
-similar to \citet{Ayres:2010ug}, using data from Warr's 
-REXS database \citep{Warr:2012a} and results from 
-\citet{Wirsenius:2000vi}. For animal work, our analysis was 
-restricted to draught animals (horses and mules). Muscle work 
-from animals ($Q_{animals}$) was calculated using
-
-\begin{equation} \label{eq:animal_muscle}
-  Q_{animals} = Q_{m,horse}N_{horses} + Q_{m,mule}N_{mules}
-\end{equation}
-
-\noindent where $Q_m$ is metabolizable energy (in kcal/day-animal) 
-and $N$ is the number of animals. Metabolizable energy values 
-($Q_{m,horses}$ = 19,110 kcal/day-horse and $Q_{m,mules}$ = 
-7,215 kcal/day-mule) were taken from \citet{Warr:2012a}. 
-$Q_m$ represents the amount of energy in the feed consumed by 
-animals for a day of work, and they are assumed constant for 
-all countries and years. The number of horses and mules for 
-each economy was taken from the ``Live Animals'' section of the 
-FAO Statistics online database \citep{FAO:2013a}.
-
-Human muscle power was calculated in a similar manner:
-
-\begin{equation} \label{eq:human_muscle}
-  Q_{workers} = Q_{m,workers} N_{workers}
-\end{equation}
-
-\noindent where the value of $Q_{m,workers}$ is the ``the amount 
-of food available for human consumption'' (i.e., at the wholesale level) 
-taken from the 
-\citet[``\texttt{Dietary~Energy~Cons.~Countries}'' tab]{FAO:2013b}. 
-The value for $N_{workers}$ was obtained from the labor time series 
-for each economy as discussed in Section~\ref{sec:Labor_Data}.
-
-\twocolumn{}
 <<Historical_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=7.5, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), and thermal energy ($q$).">>=
@@
 
-%++++++++++++++++++++++++++++++
-\subsection{Historical Data} 
-\label{sec:Historical_Data}
-%++++++++++++++++++++++++++++++
-
-Figure~\ref{fig:Historical_Graph} presents historical data, 
-including indexed values for 
-output ($y$), 
-capital stock ($k$), 
-labor ($l$), and 
-energy ($q$) 
-for 1980--2011 (developed economies) and 1991--2011 (other economies). 
-Factors of production track each other closely, 
-and high covariances among these variables can be seen in 
-Tables~\ref{tab:Covariance_US}--\ref{tab:Covariance_ZM}. 
-\authNote{Do we want to discuss the covariances?}
-
-\onecolumn{}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Parameter Estimation}
-\label{sec:Parameter_Estimation}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Point Estimates}
-Each of the economic growth models discussed in 
-Section~\ref{sec:Prod_Func_Forms} has parameters which must be estimated (fitted)
-from data for each economy (see Section~\ref{sec:Economy_Types}).
-We obtained parameter estimates by applying the method of least-squares to (potentially
-log-transformed) data using the \texttt{R} \citep{R} functions
-\texttt{lm} (for Cobb-Douglas and LINEX models) 
-and \texttt{cesEst} \citep{Henningsen:2011td} (for CES models). 
-\authNote{Need to check how CES is being fit and adjust this accordingly.}%
-
-Although the details vary from model to model, each of our three models has the general form
-\[
-y = f(t,k,l,e; \theta) + \mathrm{error} \;,
-\]
-where $\theta$ is a vector of parameters for the function $f$.
-\authNote{if we use $\theta$ this way, we need a new scaling parameter. --rjp}%
-In least squares models, parameter estimates are chosen to minimize
-\[
-\sum_{i} (y_i - f(t,k,l,e; \theta) )^2 \;.
-\]
-For the optimal parameter values $\hat \theta$, we define the 
-fitted response by
-\[
-\hat y_i = f(t_i, k_i, l_i, e_i; \hat \theta)
-\]
-and the residuals
-as the difference between the observed response and the fitted response
-\begin{equation} \label{eq:residual}
-  r_i 
-  = y_i - \hat y_i
-  = y_i - f(t,k,l,e; \hat\theta)
-\end{equation}
-The details for each of the models (including the effects of using 
-log transformations) are discussed below.
-
-%After back transforming to the natural scale of the data, the 
-%residuals have a multiplicative rather than additive affect.
-%The reflects an assumption that variability in GDP is roughly 
-%proportion to GDP rather than constant.
-
-%++++++++++++++++++++++++++++++
-\subsection{Resampling Methods}
-\label{sec:Resampling}
-%++++++++++++++++++++++++++++++
-
-Bootstrappng is a statistical resampling technique for assigning
-measures of accuracy and precision to sample estimates by measuring
-properties of an estimator when sampling from a resampling
-distribution.  Resampling distributions can be formed in a number of 
-ways in accordance with the type of data, experimental design,
-and modeling assumptions involved.  In each case, many new resamples 
-are created, each of which is a randomized version of the original sample data to 
-which the desired analysis method can be applied.  By investigating, for example,
-the variability of a parameter estimate from one resample to another,
-one can learn about the precision of the estimation method.
-\authNote{Add some references here. --rjp}
-
-In the context of linear models (regression), resamples are generally created
-by residual resampling.  In our case, we formed resamples by adding to the fitted 
-response (GDP) the product of a residual from the original model fit and 
-and random sign ($-1$ or $1$, each with probability $0.5$).  For the case of 
-Cobb-Douglas and LINEX models, this residual resampling occurs on the 
-log-transformed data.
-
-Intuitively, this method assumes that the residuals are indicative of 
-the variability (from many potential sources) inherent in the data so that
-it would be unsurprising if the residual from 
-any particular year had been observed in a different year. 
-Thus, a resampled response $\tilde Y$ can be computed as 
-\[
-\tilde Y_i' = \hat y_i \pm r_j
-\]
-where 
-\[
-r_i = y_i - \hat y_i
-\]
-both the sign ($\pm$) and the index of the residual ($j$, typically different from $i$) 
-are chosen at random (with replacement). 
-Resampling in this way has the consequence 
-that a resampled time series could have non-unity first-year GDP ($\tilde Y_1 \neq 1$),
-so a renormalization takes place using the initial GDP from the
-resampled data as the new baseline, not the observed GDP in year 1.
-
-\begin{equation} \label{eq:resample_y}
-	\tilde y_i  = \frac{\tilde Y_i'}{\tilde Y_1'}
-\end{equation}
-to obtain a resampled indexed GDP time series.
-We repeated the resampling process \Sexpr{numResamples()} times for each
-combination of growth model and country, both with and without energy when appropriate.
-
-The coefficients from the fit to a resampled time series
-(the ``resample coefficients'') will be different from the coefficients 
-obtained from the fit to historical data (the ``base coefficients'').
-When these resample coefficients are highly variable, it is an indication
-that the data do not determine the parameter estimates very precisely.
-Lack of imprecision can stem from a number of factors, most obviously
-a poor model fit, low model sensitivity to one or more parameters, 
-or correlations between parameter estimates.
-\authNote{This is not precisely true:
-Large residuals in the fit to historical data (the ``base fit'')
-are expected to produce large variation in resample coefficient values
-(when the resampling is repeated \Sexpr{numResamples()} times),
-indicating less certainty in the value
-of those coefficients. 
-Similarly, small base fit residuals are expected to produce small
-variation in resample coefficient values, indicating more-precise knowledge
-of the model coefficients.
---rjp}
-
-It is important to note that large residuals can arise from either
-(a) poor quality historical time series data, or 
-(b) a mathematical model that does not describe the underlying phenomena well.
-It is also important to note that (c) even when the residuals are small and the 
-model produces fitted values that track the observed data closely, it may
-still be difficult to estimate some or all of the model parameters precisely.
-The resampling method employed reflects all three of these potential 
-sources of uncertainty in parameter estimates.
-
-\authNote{Should the description of model fitting come before or after 
-the description of resampling?}
-
-%++++++++++++++++++++++++++++++
-\subsection{Cobb-Douglas Models}
-\label{sec:CD_Parameter_Estimation}
-%++++++++++++++++++++++++++++++
-
-The Cobb-Douglas model without energy is given by 
-Equation~\ref{eq:CD}. Equation~\ref{eq:CD} was
-reparameterized as
-
-\begin{equation} \label{eq:CD_reparam}
-  y = A k^{\alpha} l^{1-\alpha}; A = \mathrm{e}^{\lambda (t-t_0)}
-\end{equation}
-
-\noindent to ensure $\alpha + \beta = 1$ for constant returns to scale. 
-$\lambda$ and $\alpha$ were estimated by the 
-\texttt{R} \citep{R} function \texttt{nls}. 
-If the estimated value for $\alpha$ was found outside the interval $[0,1]$, 
-we set $\alpha$ to its boundary value and re-estimated $\lambda$. 
-The value of $\beta$ was found with $\beta = 1 - \alpha$.
-
-To estimate the parameters $\lambda$, $\alpha$, $\beta$, and $\gamma$ 
-in the energy-augmented Cobb-Douglas model, Equation~\ref{eq:CDe} 
-was reparameterized as
-
-\begin{equation} \label{eq:CDe_AB_reparam}
-  y = A k^{\min(a,b)} l^{|b-a|} e^{1 - \max(a,b)}; A = \mathrm{e}^{\lambda (t-t_0)}
-\end{equation}
-
-\noindent with 
-$\alpha = \min(a,b)$, 
-$\beta = |b-a|$, and 
-$\gamma = 1 - \max(a,b)$.
-The reparameterization ensures that $\alpha + \beta + \gamma = 1$,
-thereby providing constant returns to scale.
-The \texttt{R} \citep{R} function \texttt{nls} was used to estimate 
-values of $\lambda$, $a$, and $b$.
-If the fitted value for $a$ ($b$) fell outside $[0,1]$, it was 
-set equal to its boundary value and both $\lambda$ and $b$ ($a$) 
-were re-estimated.
-
-The \texttt{nls} parameter estimation algorithm can encounter convergence difficulty 
-when the optimal value for the parameter represented by the absolute value function 
-(in Equation~\ref{eq:CDe_AB_reparam}, $\beta$) 
-lies near a boundary. If the absolute value exponent caused non-convergence of the 
-\texttt{nls} function, second and, if necessary, third reparameterizations 
-were attempted:
-
-\begin{equation} \label{eq:CDe_CD_reparam}
-  y = A k^{1 - \max(c,d)} l^{\min(c,d)} e^{|d-c|}; A = \mathrm{e}^{\lambda (t-t_0)}
-\end{equation}
-
-\begin{equation} \label{eq:CDe_FG_reparam}
-  y = A k^{|g-f|} l^{1 - \max(f,g)} e^{\min(f,g)}; A = \mathrm{e}^{\lambda (t-t_0)}
-\end{equation}
-
-\noindent If none of the three reparameterizations converged, 
-the parameterization with the smallest sum of square errors ($sse$)
-was used. \ref{sec:Convergence_Resample_Models} shows the 
-fraction of unconverged models for each model type. 
-The above approach resulted in very few unconverged
-Cobb-Douglas resample models, even with \Sexpr{numResamples()} resamples.
-
-Figure~\ref{fig:CD_Ternary_Scatter_Graph} shows ternary plots 
-for $\alpha$, $\beta$, and $\gamma$ parameter values 
-for Cobb-Douglas (without and with energy) resample models.
-Each reample is shown as a gray dot on the graph. 
-The fit to historical data is shown as a gray circle.
-
-Figure~\ref{fig:CD_GDP_Spaghetti_Graph} compares predictions 
-from the Cobb-Douglas models 
-(without and with energy) to historical data.
-Historical data are shown as a black line. 
-The fit to historical data is shown as a white line.
-The gray band encompasses 95\% of the fits to resampled data.
-
-\twocolumn{}
-<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=2.9, fig.height=7.7, fig.cap="Cobb-Douglas resample model parameters.">>=
-cdCoeffsData <- filter(coeffs_df, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iQ"))
+<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=5.8, fig.height=7.7, fig.cap="Cobb-Douglas resample model parameters.">>=
+cdCoeffsData <- filter(coeffs_df, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iQ", "iK+iL+iX", "iK+iL+iU"))
 standardTriPlot(data=cdCoeffsData, facet_formula=country~energy)
@@
 
-<<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=8.2, fig.cap="Cobb-Douglas fitted models.">>=
-cdFittedData <- filter(fitted_df, model=="cd", nest %in% c("iK+iL", "iK+iL+iQ"))
+<<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=6, fig.height=8.2, fig.cap="Cobb-Douglas fitted models.">>=
+cdFittedData <- filter(fitted_df, model=="cd", nest %in% c("iK+iL", "iK+iL+iQ", "iK+iL+iX", "iK+iL+iU"))
 spaghettiPlot(data=cdFittedData, facet_formula=Country~energy, level=spaghettiGraphLevel) +
@@
 @
-\onecolumn{}
-
-%++++++++++++++++++++++++++++++
-\subsection{CES Models}
-\label{sec:CES_Parameter_Estimation}
-%++++++++++++++++++++++++++++++
-
-The CES model without and with energy is given by 
-Equations~\ref{eq:CES}--\ref{eq:CESekl}. 
-The \texttt{R} \citep{R} package \texttt{micEconCES} 
-\citep{Henningsen:2011td} was used to estimate parameters 
-$\lambda$, $\gamma$, $\delta$, $\delta_1$, $\rho$, and $\rho_1$. 
-The \texttt{cesEst} function of \texttt{micEconCES} provides 
-several algorithm options for parameter estimation.
-The default algorithm (Levenberg-Marquardt) does not respect
-parameter constraints (see Section~\ref{sec:CES}) and, 
-in our testing, nearly always violated them, often returning
-negative values for elasticity of substitution ($\sigma$) parameters.
-Thus, we used the two fitting algorithms available in \texttt{cesEst} that
-respect coefficient constraints: \texttt{PORT} and \texttt{L-BFGS-B}.
-
-Our CES parameter estimation algorithm starts with an eleven-value grid search
-in $\rho$ and $\rho_1$ (9, 2, 1, 0.43, 0.25, 0.1, -0.1, -0.5, -0.75, -0.9, -0.99),
-which corresponds to $\sigma$ and $\sigma_1$ values of
-0.1, 0.33, 0.5, 0.7, 0.8, 0.9, 1.11, 2, 4, 10, and 100, respectively.
-During the grid search, values of $\rho$ and $\rho_1$ are fixed,
-and values of $\lambda$, $\gamma$, $\delta$, and $\delta_1$ are estimated 
-by gradient search with the \texttt{PORT} and \texttt{L-BFGS-B} algorithms.
-In all, 121 gradient searches in $\lambda$, $\gamma$, $\delta$, and $\delta_1$
-at grid points representing all combinations of $\rho$ and $\rho_1$ are attempted.
-During the grid search portion of our algorithm, starting values for the free parameters
-are $\lambda$ = 0.015/year, $\delta$ = 0.5, $\delta_1$ = 0.5, 
-and $\gamma$ is set to a value such that the mean of the residuals is zero.
-
-Next, a gradient search (using both \texttt{PORT} and \texttt{L-BFGS-B}) 
-is attempted wherein all fitting parameters 
-($\lambda$, $\gamma$, $\delta$, $\delta_1$, $\rho$, and $\rho_1$)
-are allowed to float. 
-The start values for fitting parameters are taken from 
-the grid search fit that provided the lowest $sse$.
-
-If resampled data are being fitted, a prior fit to historical data is available.
-In the final step of our algorithm, 
-a gradient search (using both \texttt{PORT} and \texttt{L-BFGS-B})
-uses coefficients from the best 
-fit to historical data as its starting point. 
-In this final gradient search, all model parameters 
-($\lambda$, $\gamma$, $\delta$, $\delta_1$, $\rho$, and $\rho_1$)
-are considered free parameters.
-
-The fit with lowest $sse$ of all above trials is deemed the winner,
-and its fitting parameters are used as the model.
-
-\citet{Henningsen:2011td}, 
-in their detailed analysis of \citet{Kemfert:1998vd}, found that
-
-\begin{quote}
-\ldots the Levenberg-Marquardt and the \texttt{PORT} algorithms 
-are---at least in this study---most likely to find the 
-coefficients that give the best fit to the model, 
-where the PORT algorithm can be used to restrict the estimates 
-to the economically meaningful region.
-\end{quote}
-
-In our testing, we found that to be mostly true. 
-\texttt{PORT} nearly always provided lower
-$sse$ than \texttt{L-BFGS-B}, despite the fact that 
-\texttt{L-BFGS-B} often reports convergence
-and \texttt{PORT} does not for the same data
-(i.e., for the same $y$, $k$, $l$, and $e$ data).
-
-Coefficients for each resampled CES model for all countries and all nests
-are shown in 
-Figures~\ref{fig:CES_lambda_gamma_graph}--\ref{fig:CES_sigma_delta_graph}. 
-The crosshair on each graph shows the location 
-of the fit to historical data. 
-In Figures~\ref{fig:CES_sigma1_delta1_graph} and~\ref{fig:CES_sigma_delta_graph},
-the bottom of the vertical axis represents $\sigma = 0$.
-The top of the vertical axis represents $\sigma = \infty$.
 
@@
 
-Figure~\ref{fig:CES_Spaghetti_Graph} compares CES model predictions 
-to historical data for all nestings. 
-Historical data are shown as a black line. 
-The fit to historical data is shown as a white line.
-The gray band encompasses 95\% of the fits to resampled data.
-
 <<CES_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models.">>=
@@
 
-Figure~\ref{fig:CES_Spaghetti_Graph_CN} shows details of the resample fits for China with the (kl)e nesting.
-Again, historical data are shown as a black line. 
-The fit to historical data is shown as a white line.
-The gray band encompasses 95\% of the fits to resampled data.
-
-<<CES_Spaghetti_Graph_CN, fig.pos="H", fig.align='center', fig.width=maxWidth, fig.height=maxHeight, fig.cap="CES fitted models for China with the (kl)e nesting.">>=
-spaghettiPlot(data=subset(cesFittedData, Country=="CN" & nest=="iK+iL+iQ"), level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1980 = 1 or 1991 = 1")
-@
-
-%++++++++++++++++++++++++++++++
-\subsection{LINEX Models}
-\label{sec:LINEX_Parameter_Estimation}
-%++++++++++++++++++++++++++++++
-
-The LINEX model is given in Equation~\ref{eq:LINEX}. 
-If the fitting algorithm drives $a_0 \rightarrow 0$, 
-any changes to $c_t$ have no effect on $sse$, 
-leading the fitting algorithm to report non-convergence. 
-To avoid this problem, we transformed the LINEX model into
-
-\begin{equation} \label{eq:LINEX_transformed}
-  y = Ae; 
-  A = \mathrm{e}^{\left[2 a_0 \left(1 - \frac{1}{\rho_k} \right) 
-    + a_1 \left(\vphantom{\frac{1}{\rho_k}}\rho_l - 1 \right)\right]},
-\end{equation}
-
-\noindent where $a_1 \equiv a_0 c_t$. 
-We used the \texttt{nls} function in \texttt{R}
-\citep{R} to estimate least-squares values for $a_0$ and $a_1$ in 
-Equation~\ref{eq:LINEX_transformed}. We recovered
-a value for $c_t$ with $c_t = a_1 / a_0$. The reparameterization
-shown in Equation~\ref{eq:LINEX_transformed} reduced the number of 
-unconverged resample fits to nearly zero: 
-The largest fraction of unconverged resample fits is found 
-for Zambia (ZM) with thermal energy ($q$), where
-\Sexpr{fracUnconvergedResampleFits(modelType="linex", countryAbbrev="ZM", energyType="Q", baseResample=baseResample)*100}\%
-of the resample fits did not converge. 
-(See Table~\ref{tab:frac_unconverged_models}.)
-
-Figure~\ref{fig:LINEXq_Resample_Graph}
-shows the coefficients estimated from resampled data.
-
-Figure~\ref{fig:LINEX_Spaghetti_Graph} compares LINEX model predictions to historical data.
-Historical data are shown as a black line. 
-The fit to historical data is shown as a white line.
-The gray band encompasses 95\% of the fits to resampled data.
+% <<CES_Spaghetti_Graph_CN, fig.pos="H", fig.align='center', fig.width=maxWidth, fig.height=maxHeight, fig.cap="CES fitted models for China with the (kl)e nesting.">>=
+% spaghettiPlot(data=subset(cesFittedData, Country=="CN" & nest=="iK+iL+iQ"), level=spaghettiGraphLevel) +
+%     labs(y="Indexed GDP (1980 = 1 or 1991 = 1")
+% @
 
@@
 \onecolumn{}
-
-%++++++++++++++++++++++++++++++
-\subsection{Parameter Estimation Summary}
-\label{sec:Parameter_Estimation_Summary}
-%++++++++++++++++++++++++++++++
-
-**** Include a table here of important values. 
-Include a table of convergence? (In appendix?)
-Martin to suggest the form of this table after working 
-on the interpretation for a while. ****
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion of Results}
-\label{sec:Discussion_of_Results}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Drive towards new insights from our stats tested comparative approach.
-
-**** Notes for interpretation of results ****
-
-R$^2$ not a good measure. 
-Limited insights are obtained from $t$ and $p$ values, 
-especially on PFs that have parameters with constraints (CD, CES).
-
-We found that we are able to maintain good fits while respecting theoretical foundations
-of the models (i.e., respect parameter constraints). No need to relax parameter constraints
-and, thereby, contradict micro foundations.
-
-CD assumes $\sigma_1 = 1$. CES doesn't assume a value for $\sigma_1$. 
-The $\sigma_1$ vs. $\delta_1$ graphs for CES without energy often have 
-two frequent values for $\sigma_1$.  One of those frequent values is
-nearer to $\sigma_1 = 1$. When CD and CES without energy do not agree on 
-share values (CD: $\alpha$ compared to $\beta$, CES: $\delta_1$) for the 
-base curve fit (red dot), they do agree for the data that clusters near 
-$\sigma_1 = 1$ for the CES fits.
-
-Country interpretation
-
-Comparison Cobb Douglas and CES results.
-
-%++++++++++++++++++++++++++++++
-\subsection{United States} 
-\label{sec:InterpUS}
-%++++++++++++++++++++++++++++++
-
-CD: Energy is unnecessary
-
-CES with $q$:
-
-($kl$): $\delta_1 = 0.3, \sigma_1 = 0.8$. $k$ is less necessary. 
-Complements, but close to substitutes.
-signal of substitutability in the spread.
-
-($kl$)$e$: energy is unnec ($\delta = 1$). 
-$\delta_1 = 0.45$: $k$ and $l$ are about equally necessary.
-$\sigma_1 = 0.8$: $k$ and $l$ are slight complements. 
-Spread on $0.25 < \sigma_1 < \infty$, signalling 
-possibilities of substitution.
-
-($el$)$k$: energy is unnec. ($\delta_1$ is 0);
-
-($le$)$k$ no indication
-Relative consistent signal that energy is unnec.
-
-CES with $u$:
-
-($kl$)$e$: $\delta = 1$, signalling $e$ unnecessary. 
-$\sigma = 0.8$, indicating clost to substitutability,
-but still complementary. 
-$\delta_1 = 0.25$, with large spread. not strong for $k$.
-$\sigma_1 \rightarrow \infty$, but with large spread from 0.2 upward. 
-Signals complementarity between $k$ and $l$.
-
-%++++++++++++++++++++++++++++++
-\subsection{United Kingdom} 
-\label{sec:InterpUK}
-%++++++++++++++++++++++++++++++
-
-CD: Capital is unnec.
-
-CES with $q$:
-
-($kl$): $\delta_1 = 0.7, \sigma_1 = 0.35$. 
-$kl$ complementary, $k$ is more important, because $\delta_1 > 0.5$. 
-Large spread on $\delta_1$. 
-Complementary signal is consistent, however.
-
-($kl$)$e$: energy is unnec ($\delta = 1$). 
-$\delta_1 = 0.25$, $k$ is less necessary. 
-$\sigma_1 \rightarrow \infty$, giving strong $kl$ substitutability signal.
-
-($le$)$k$ capital is unnec. ($\delta = 1$);
-
-($ek$)$l$ ($\delta_1 = 0$) energy is unnec.
-
-Thus, inconsistent results, possibly look at different time series 
-as massive changes in economic policy in Uk economic history
-
-CES with $u$:
-
-($kl$)$e$: $\delta = 1$, $u$ is unnecessary. 
-$\sigma = 0.8$, approache complementarity between $kl$ and $e$.
-$\delta_1 = 0.1$. 
-$\sigma_1 \rightarrow \infty$, indicating substitutability between $k$ and $l$.
-
-%++++++++++++++++++++++++++++++
-\subsection{Japan} 
-\label{sec:InterpJP}
-%++++++++++++++++++++++++++++++
-
-CD: energy is unnec.
-
-CES with $q$:
-
-($kl$): $\delta_1 = 0.7, \sigma_1 = 0.25$. Very little scatter. Both are well-known. 
-$l$ is close to unnecessary. $k$ and $l$ are complements.
-
-($kl$)$e$: no indications, all are important. $\delta = 0.6$, both $kl$ and $e$ are necessary.
-$0.5 < \delta < 1$.
-$\sigma=0.1$ signalling complementarity betwen $kl$ and $e$.
-$\delta_1 = 0.8$ signalling $l$ is almost unnecessary. 
-$\sigma_1 = 0.1$, signalling complementarity 
-between $k$ and $l$.
-
-($le$)$k$: no indications, all are important.
-
-($ek$)$l$: no indications, all are important.
-
-weak signal that labour is less necessary 
-(($kl$)$e$ $delta_1 = 0.86$ and ($ek$)$l$ $\delta = 0.89$)
-
-Thus, inconsistent results.
-
-CES with $u$:
-
-($kl$)$e$: $\delta = 0.6, \sigma = 0.4$. Complementarity between $kl$ and $e$.
-$\delta_1 = 1$, indicating $l$ unnecessary. $\sigma_1 = 0.1$, indicating complementarity
-between $k$ and $l$. Need only one of $k$ or $l$ in your equation, but they are
-complemetary! You need one to have the other.
-
-%++++++++++++++++++++++++++++++
-\subsection{China} 
-\label{sec:InterpCN}
-%++++++++++++++++++++++++++++++
-
-CD: energy not necessary, capital less necessary
-
-CES with $q$:
-
-($kl$): $\delta_1 = 0.3$, so $k$ is getting close to unnecessary. $\sigma_1 = 1.25$.
-$k$ and $l$ are substitutes. Large spread in $\delta_1$ from 0.1 to 1.0. Large spread in
-$\sigma_1$, but most points have $\sigma_1 > 1$.
-
-($kl$)$e$: $\delta = 0.8$. however, strong signal at $0.8 < \delta < 1$, 
-signalling that energy is less necessary. $0.5 < \delta < 1$. $\sigma = 0.5$, 
-signalling complementarity between $kl$ and $e$. 
-$\delta_1 = 1$, signalling that $l$ is unnecessary. $\sigma_1 = 0.1$, signalling
-that $k$ and $l$ are complementary. Both $\delta_1$ and $\sigma_1$ have large spreads, 
-so our confidence in these results is low.
-
-($le$)$k$: labour is unnnec ($\delta_1 = 0$);
-
-($ek$)$l$ energy is unnec. ($\delta_1 \rightarrow 0$)
-
-Strong signal that energy is unnec, but the labour and capital signals are conflicting
-
-%++++++++++++++++++++++++++++++
-\subsection{South Africa} 
-\label{sec:InterpZA}
-%++++++++++++++++++++++++++++++
-
-CD: Labour is unnec.
-
-CES with $q$:
-
-($kl$): $\delta_1 = 0.35, \sigma_1 = 0.8$. $k$ is relatively less necessary. $k$ and $l$ 
-are complements but relatively close to being substitutes. Spread is tight between 
-$0.25 < \delta_1 < 0.5$ and $\sigma_1$ is consistently complementary 
-between $0.1 < \sigma_1 < 0.8$.
-
-($kl$)$e$: labour is unnec. ($\delta_1 = 1$). $\delta = 0.25$, signalling complemtarity 
-between $kl$ and $e$, but large spread from 0 to 1. $\sigma$ and $\sigma_1$ are both 0, 
-indicating perfect complements betwen $kl$ and $e$ and between $k$ and $l$.
-
-($le$)$k$ labour is unnec. ($\delta_1 = 0$);
-
-($ek$)$l$ labour is unnec. ($\delta = 1$)
-
-Consistent signal that labour is unnec.
-
-%++++++++++++++++++++++++++++++
-\subsection{Saudi Arabia} 
-\label{sec:InterpSA}
-%++++++++++++++++++++++++++++++
-
-CD: no indications
-
-CES with $q$:
-
-($kl$): $\delta_1 = 0.85$. $l$ is unnecessary. 
-$\sigma_1 = 0.1$ indicating strong complementarity between 
-$k$ and $l$. Spread of $0.15 < \delta_1 < 1$. 
-$0 < \sigma_1 < 0.8$, signalling complementarity.
-
-($kl$)$e$: $\delta = 0.6$, $e$ is less necessary (weak signal). 
-Big spread on $\delta$ between 0 and 0.8.
-$\sigma = 0.1$ indicating complementarity between $kl$ and $e$. $\delta_1 = 0.8$ 
-(with large spread between 0.3 and 1), labor is less necessary.
-$\sigma_1 = 0.1$: very complementary between $k$ and $l$.
-
-($le$)$k$:
-
-($ek$)$l$: weak signal that labour is unnec ($\delta = 0.93$)
-
-Almost consistent signal that no indocations.
-
-%++++++++++++++++++++++++++++++
-\subsection{Iran} 
-\label{sec:InterpIR}
-%++++++++++++++++++++++++++++++
-
-CD: energy is unnec.
-
-CES with $q$:
-
-($kl$): $\delta_1 = 0.3$. Spread $0 < \delta_1 < 0.7$. $0 < \sigma_1 < 0.8$. $\sigma_1 = 0$. 
-Strong complementarity. $k$ is less necessary compared to $l$.
-
-($kl$)$e$: energy is unnec ($\delta=1$). 
-$\sigma = 0.75$ indicating complementarity between $kl$ and $e$, approaching substitutibility.
-$\delta_1 = 0.3, \sigma_1 = 0$ indicating strong perfect complementarity between $k$ and $l$.
-
-($le$)$k$: energy is unnec. ($\delta_1=1$);
-
-($ek$)$l$: labour is unnec. ($\delta=1$)
-
-%++++++++++++++++++++++++++++++
-\subsection{Tanzania} 
-\label{sec:InterpTZ}
-%++++++++++++++++++++++++++++++
-
-CD: labour in unnec.
-
-CES with $q$:
-
-($kl$): $\delta_1 = 0.8$ $0.3 < \delta_1 < 1$ signalling labor is less necessary.
-$\sigma_1 = 0.1$ $0 < \sigma_1 < 0.8$, signalling complementary $k$ and $l$.
-
-($kl$)$e$: labour is unnec ($\delta_1=0.97$). 
-$\delta = 0.45$, so $kl$ and $e$ both necessary, but 
-$\sigma \rightarrow \infty$, so $kl$ and $e$ has perfect substitutibility.
-$\sigma_1 = 0.1$, so $k$ and $l$ are perfect complements. 
-Spread on $\delta$ is large (0.2 to 1).
-So, we are unsure about the value of $\delta$.
-
-($le$)$k$: weak signal that energy is unnec. ($\delta_1=0.92$); 
-very weal signal capital is unnec ($\delta=0.84$);
-
-($ek$)$l$: labour is unnec. $\delta=0.96$
-
-Consistent signal that labour is unnec, with exception of one nesting.
-
-%++++++++++++++++++++++++++++++
-\subsection{Zambia} 
-\label{sec:InterpZM}
-%++++++++++++++++++++++++++++++
-
-CD: labour is unnec; energy is unnec.
-
-CES with $q$:
-
-($kl$): $\delta_1 = 1$: $l$ is unnecessary. 
-$0.5 < \delta_1 < 1$. $\sigma_1 = 0.8$ without any 
-noticeable spread indicating complemetary.
-
-($kl$)$e$: labour is unnec. ($\delta_1=1$). 
-$\delta = 0.6$, $kl$ and $e$ are both necessary. 
-$\sigma \rightarrow \infty$, signalling substitutability between $kl$ and $e$. 
-$\sigma_1 = 0.8$ with very large spread between 0 and 2. 
-Approaching substitutability between $k$ and $l$ and perfect substitutibility
-between $kl$ and $e$. Very little certainty here.
-
-($le$)$k$: ($\delta_1=0$);
-
-($ek$)$l$: labour is unnec. ($\delta=1$)
-
-Consistent signal that labour is unnec.
-
-Discussion of results:
-
-How to get better consistent signals?
-
-\begin{itemize}
-\item{Use CD as starting points and do CES convergence on that basis.}
-\item{Do scatterplots to get range of uncertainty inputs, then re-interpret. 
-$\delta$ against $\sigma$ plots, as well as $\delta_1$ and $\sigma_1$ plots.}
-\end{itemize}
-
-Thus, to do the fitting well we need to understand:
-\begin{itemize}
-\item{nesting}
-\item{algorithm}
-\item{starting values}
-\end{itemize}
-esp. for CES.
-
-(Maybe illustrate with one case study such as China what implications are).
-
-How do we compare with LINEX results?
-
-CES is a broader specification of CD, LINEX is not. 
-In LINEX neither $\delta$s nor $\sigma$s are generated. 
-Only efficiency terms are generated in LINEX, 
-thus in other words economic growth is only possible by increased efficiency. 
-The efficiency of using energy is driven by capital stock. 
-The objective/growth engine is to increase capital 
-at a rate that is faster then growth in labour and energy.  
-Increasing labour relative to energy gives a muted benefit. 
-LINEX derived for Germany: only really applicable when energy and capital are complements.
-
-Discussion in relation to other papers. 
-Problems with other papers:
-\begin{itemize}
-\item{If not giving you all parameters}
-\item{Not explain nesting approach}
-\item{No CI on data}
-\end{itemize}
-
-Economic interpretation (revisit after scatterplot information)
-Developed economies: Capital and energy is complementary (US: labour and energy substitutable)
-NICs: Capital and energy complementary, but labour and energy more substitutable
-OPEC: Labour and energy complementary (mixed results on capital and energy)
-LDCs: Labour and energy complementary, Capital and energy perfect substitutes.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusion}
-\label{sec:Conclusion}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Future Work}
-\label{sec:FutureWork}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Reproducible Research}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-In the spirit of Reproducible Research \citep{Gandrud:2013vx}, 
-all data, spreadsheets, \texttt{R} code \citep{R}, and other materials 
-associated with this paper can be found at\\*
-\protect\url{https://github.com/MatthewHeun/Econ-Growth-R-Analysis}.
-
-%% The Appendices part is started with the command \appendix;
-%% appendix sections are then done as normal sections
-%% \appendix
-%% \section{}
-%% \label{}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\appendix
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Covariance Tables}
-\label{sec:Covariance_Tables}
-\setcounter{table}{0} % Restarts table number counter at 0 in this section.
-\setcounter{figure}{0} % Restarts figure number counter at 0 in this section.
-\setcounter{equation}{0} % Restarts equation counter to 0 in this section.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Convergence of Resample Models}
-\label{sec:Convergence_Resample_Models}
-\setcounter{table}{0} % Restarts table number counter at 0 in this section.
-\setcounter{figure}{0} % Restarts figure number counter at 0 in this section.
-\setcounter{equation}{0} % Restarts equation counter to 0 in this section.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The following table shows the fraction of resample models 
-that did not achieve convergence when estimating model parameters.
-
-<<Unconverged_Frac_Table, results='asis'>>=
-# printFracUnconvergedXtable()
-  data <- fracUnconvergedResampleFitsAll(baseResample=baseResample)
-  dataXtable <- xtable(x=data, 
-                       caption="Fraction of unconverged resample models", 
-                       label="tab:frac_unconverged_models",
-                       digits = 3,
-                       align = "rl|cc|ccccccccc") #Sets alignment of the numbers in the columns)
-  print(dataXtable, 
-        caption.placement="top", 
-        size="\\tiny",
-        table.placement="H",
-        include.rownames=FALSE)
-@
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{95\% Confidence Intervals}
-\label{sec:Confidence_Intervals}
-\setcounter{table}{0} % Restarts table number counter at 0 in this section.
-\setcounter{figure}{0} % Restarts figure number counter at 0 in this section.
-\setcounter{equation}{0} % Restarts equation counter to 0 in this section.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Resample coefficients in the scatter plots 
-can be represented as 95\% confidence intervals 
-by finding the parameter values associated with 
-the middle 95\% of the data for each model parameter.
-This appendix provides tables and graphs of the 95\% confidence
-intervals on fitted model parameters.
-
-%++++++++++++++++++++++++++++++
-\subsection{Cobb-Douglas Models}
-%++++++++++++++++++++++++++++++
-
-The 95\% confidence intervals associated with 
-the without-energy column of Figure~\ref{fig:CD_Ternary_Scatter_Graph} 
-are shown in Table~\ref{tab:CD_Parameters_No_Energy}.
-
-<<CD_Params_Table, results='asis'>>=
-printCDParamsTable(energyType="none", baseResample=baseResample)    #Without energy
-@
-
-The data in Table~\ref{tab:CD_Parameters_No_Energy} are plotted in
-Figure~\ref{fig:CD_Params_Graph}.
-
-<<CD_Params_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.cap="Cobb-Douglas (without energy) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createCDParamsGraph(energyType="none", baseResample=baseResample)
-@
-
-The 95\% confidence intervals associated with 
-the with-energy column of Figure~\ref{fig:CD_Ternary_Scatter_Graph} 
-are shown in Table~\ref{tab:CD_Parameters_With_Q}
-and Figure~\ref{fig:CDq_Params_Graph}.
-
-<<CDq_Params_Table, results='asis'>>=
-printCDParamsTable(energyType="Q", baseResample=baseResample)   #With energy
-@
-
-<<CDq_Params_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.cap="Cobb-Douglas (with energy) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createCDParamsGraph(energyType="Q", baseResample=baseResample)
-@
-
-%++++++++++++++++++++++++++++++
-\subsection{CES Models}
-%++++++++++++++++++++++++++++++
-
-The 95\% confidence intervals associated 
-with ($kl$) nest columns of 
-Figures~\ref{fig:CES_lambda_gamma_graph}--\ref{fig:CES_ternary_graph}
-are shown in Tables~\ref{tab:CES_Parameters_A} 
-and \ref{tab:CES_Parameters_B} and Figure~\ref{fig:CES_Params_Graph}.
-
-<<CES_Params_Table, results='asis'>>=
-print(cesParamsTableA(energyType="none", nest="(kl)", baseResample=baseResample), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-print(cesParamsTableB(energyType="none", nest="(kl)", baseResample=baseResample), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-@
-
-<<CES_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (without energy, ($kl$) nesting) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createCESParamsGraph(energyType="none", nest="(kl)", baseResample=baseResample)
-@
-
-The 95\% confidence intervals associated 
-with ($kl$)$e$ nest columns of 
-Figures~\ref{fig:CES_lambda_gamma_graph}--\ref{fig:CES_ternary_graph}
-are shown in Tables~\ref{tab:CES_Parameters_A_With_Q_(kl)e} and 
-\ref{tab:CES_Parameters_B_With_Q_(kl)e} and Figure~\ref{fig:CESq_Params_Graph_kle}.
-
-<<CESq_Params_Table_kle, results='asis'>>=
-print(cesParamsTableA(energyType="Q", nest="(kl)e", baseResample=baseResample), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-print(cesParamsTableB(energyType="Q", nest="(kl)e", baseResample=baseResample), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-
-@
-
-<<CESq_Params_Graph_kle, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with energy, ($kl$)$e$ nesting) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createCESParamsGraph(energyType="Q", nest="(kl)e", baseResample=baseResample)
-@
-
-The 95\% confidence intervals associated 
-with ($le$)$k$ nest columns of 
-Figures~\ref{fig:CES_lambda_gamma_graph}--\ref{fig:CES_ternary_graph}
-are shown in Tables~\ref{tab:CES_Parameters_A_With_Q_(le)k} and 
-\ref{tab:CES_Parameters_B_With_Q_(le)k} and Figure~\ref{fig:CESq_Params_Graph_lek}.
-
-<<CESq_Params_Table_lek, results='asis'>>=
-print(cesParamsTableA(energyType="Q", nest="(le)k", baseResample=baseResample), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-print(cesParamsTableB(energyType="Q", nest="(le)k", baseResample=baseResample), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-
-@
-
-<<CESq_Params_Graph_lek, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with energy, ($le$)$k$ nesting) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createCESParamsGraph(energyType="Q", nest="(le)k", baseResample=baseResample)
-@
-
-The 95\% confidence intervals associated 
-with ($ek$)$l$ nest columns of 
-Figures~\ref{fig:CES_lambda_gamma_graph}--\ref{fig:CES_ternary_graph}
-are shown in Tables~\ref{tab:CES_Parameters_A_With_Q_(ek)l} and 
-\ref{tab:CES_Parameters_B_With_Q_(ek)l} and Figure~\ref{fig:CESq_Params_Graph_ekl}.
-
-<<CESq_Params_Table_ekl, results='asis'>>=
-print(cesParamsTableA(energyType="Q", nest="(ek)l", baseResample=baseResample), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-print(cesParamsTableB(energyType="Q", nest="(ek)l", baseResample=baseResample), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-
-@
-
-<<CESq_Params_Graph_ekl, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with energy, ($ek$)$l$ nesting) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createCESParamsGraph(energyType="Q", nest="(ek)l", baseResample=baseResample)
-@
-
-%++++++++++++++++++++++++++++++
-\subsection{LINEX Model}
-%++++++++++++++++++++++++++++++
-
-The 95\% confidence intervals associated with Figure~\ref{fig:LINEXq_Resample_Graph}
-are shown in Table~\ref{tab:LINEX_Parameters_With_Q} and Figure~\ref{fig:LINEXq_Params_Graph}.
-
-<<LINEX_Params_Table, results='asis'>>=
-print(linexParamsTable(energyType="Q", baseResample=baseResample), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-@
-
-<<LINEXq_Params_Graph, fig.pos="H", fig.width=linexParameterGraphWidth, fig.height=linexParameterGraphHeight, fig.cap="LINEX model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
-createLINEXParamsGraph(energyType="Q", baseResample=baseResample)
-@
-
 %% References

### 2014-05-16 Article/EconGrowth2-GraphsOnly.Rnw
Edits to the Graphs-Only version of the article.

@@
 
+\clearpage
+
 <<Historical_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=7.5, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), and thermal energy ($q$).">>=
@@
 
-<<CES_lambda_gamma_graph, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models.">>=
-cesCoeffsData <- filter(coeffs_df, model=="ces", nestStr %in% c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"))
-standardScatterPlot(data=cesCoeffsData, mapping=aes(gamma_coef, lambda), facet_formula=country~nest, alpha=0.05) +
+% <<CES_lambda_gamma_graph, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models.">>=
+% cesCoeffsData <- filter(coeffs_df, model=="ces", nestStr %in% c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"))
+% standardScatterPlot(data=cesCoeffsData, mapping=aes(gamma_coef, lambda), facet_formula=country~nest, alpha=0.05) +
+%     scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
+%     scale_y_continuous(breaks=c(0, 0.025, 0.05, 0.075)) +    
+%     labs(x=expression(gamma), y=expression(lambda))
+% @
+
+<<CES_lambda_gamma_graph_kle, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with (kl)e nesting.">>=
+cesCoeffsData_kle <- filter(coeffs_df, model=="ces", nestStr %in% c("iK+iL", "iK+iL+iQ", "iK+iL+iX", "iK+iL+iU"))
+standardScatterPlot(data=cesCoeffsData_kle, mapping=aes(gamma_coef, lambda), facet_formula=country~nest, alpha=0.05) +
     scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
@@
 
-<<CES_sigma1_delta1_graph, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models.">>=
-standardScatterPlot(data=cesCoeffsData, mapping=aes(delta_1, sigma_1), facet_formula=country~nest, alpha=0.05) +
+<<CES_lambda_gamma_graph_lek, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with (le)k nesting.">>=
+cesCoeffsData_lek <- filter(coeffs_df, model=="ces", nestStr %in% c("iK+iL", "iL+iQ+iK", "iL+iX+iK", "iL+iU+iK"))
+standardScatterPlot(data=cesCoeffsData_lek, mapping=aes(gamma_coef, lambda), facet_formula=country~nest, alpha=0.05) +
+    scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
+    scale_y_continuous(breaks=c(0, 0.025, 0.05, 0.075)) +    
+    labs(x=expression(gamma), y=expression(lambda))
+@
+
+<<CES_lambda_gamma_graph_ekl, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with (ek)l nesting.">>=
+cesCoeffsData_ekl <- filter(coeffs_df, model=="ces", nestStr %in% c("iK+iL", "iQ+iK+iL", "iX+iK+iL", "iU+iK+iL"))
+standardScatterPlot(data=cesCoeffsData_ekl, mapping=aes(gamma_coef, lambda), facet_formula=country~nest, alpha=0.05) +
+    scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
+    scale_y_continuous(breaks=c(0, 0.025, 0.05, 0.075)) +    
+    labs(x=expression(gamma), y=expression(lambda))
+@
+
+% <<CES_sigma1_delta1_graph, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models.">>=
+% standardScatterPlot(data=cesCoeffsData, mapping=aes(delta_1, sigma_1), facet_formula=country~nest, alpha=0.05) +
+%     coord_trans(y="sigma") +
+%     scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
+%     scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
+%     labs(x=expression(delta[1]), y=expression(sigma[1]))
+% @
+
+<<CES_sigma1_delta1_graph_kle, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with (kl)e nesting.">>=
+standardScatterPlot(data=cesCoeffsData_kle, mapping=aes(delta_1, sigma_1), facet_formula=country~nest, alpha=0.05) +
     coord_trans(y="sigma") +
@@
 
-<<CES_sigma_delta_graph, fig.pos="H", fig.align='center', fig.width=4.5, fig.height=7, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models.">>=
-standardScatterPlot(data=subset(cesCoeffsData, nestStr != "iK+iL"),
+<<CES_sigma1_delta1_graph_lek, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with (le)k nesting.">>=
+standardScatterPlot(data=cesCoeffsData_lek, mapping=aes(delta_1, sigma_1), facet_formula=country~nest, alpha=0.05) +
+    coord_trans(y="sigma") +
+    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
+    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
+    labs(x=expression(delta[1]), y=expression(sigma[1]))
+@
+
+<<CES_sigma1_delta1_graph_ekl, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with (ek)l nesting.">>=
+standardScatterPlot(data=cesCoeffsData_ekl, mapping=aes(delta_1, sigma_1), facet_formula=country~nest, alpha=0.05) +
+    coord_trans(y="sigma") +
+    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
+    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
+    labs(x=expression(delta[1]), y=expression(sigma[1]))
+@
+
+% # <<CES_sigma_delta_graph, fig.pos="H", fig.align='center', fig.width=4.5, fig.height=7, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models.">>=
+% #  standardScatterPlot(data=subset(cesCoeffsData, nestStr != "iK+iL"),
+% #                      mapping=aes(delta, sigma), facet_formula=country~nest, alpha=0.05) +
+% #      coord_trans(y="sigma") +
+% #      scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
+% #      scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
+% #      labs(x=expression(delta), y=expression(sigma))
+% #  @
+
+<<CES_sigma_delta_graph_kle, fig.pos="H", fig.align='center', fig.width=4.5, fig.height=7, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models with (kl)e nesting.">>=
+standardScatterPlot(data=subset(cesCoeffsData_kle, nestStr != "iK+iL"),
+                    mapping=aes(delta, sigma), facet_formula=country~nest, alpha=0.05) +
+    coord_trans(y="sigma") +
+    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
+    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
+    labs(x=expression(delta), y=expression(sigma))
+@
+
+<<CES_sigma_delta_graph_lek, fig.pos="H", fig.align='center', fig.width=4.5, fig.height=7, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models with (le)k nesting.">>=
+standardScatterPlot(data=subset(cesCoeffsData_lek, nestStr != "iK+iL"),
+                    mapping=aes(delta, sigma), facet_formula=country~nest, alpha=0.05) +
+    coord_trans(y="sigma") +
+    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
+    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
+    labs(x=expression(delta), y=expression(sigma))
+@
+
+<<CES_sigma_delta_graph_ekl, fig.pos="H", fig.align='center', fig.width=4.5, fig.height=7, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models with (ek)l nesting.">>=
+standardScatterPlot(data=subset(cesCoeffsData_ekl, nestStr != "iK+iL"),
                     mapping=aes(delta, sigma), facet_formula=country~nest, alpha=0.05) +
@@
 
-<<CES_ternary_graph, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models.">>=
-standardTriPlot(data=cesCoeffsData, facet_formula=country~nest)
+% <<CES_ternary_graph, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models.">>=
+% standardTriPlot(data=cesCoeffsData, facet_formula=country~nest)
+% @
+
+<<CES_ternary_graph_kle, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models with (kl)e nesting.">>=
+standardTriPlot(data=cesCoeffsData_kle, facet_formula=country~nest)
 @
 
-<<CES_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models.">>=
-cesFittedData <- filter(fitted_df, model=="ces", nest %in% c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"))
+<<CES_ternary_graph_lek, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models with (le)k nesting.">>=
+standardTriPlot(data=cesCoeffsData_lek, facet_formula=country~nest)
+@
+
+<<CES_ternary_graph_ekl, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models with (ek)l nesting.">>=
+standardTriPlot(data=cesCoeffsData_ekl, facet_formula=country~nest)
+@
+
+% <<CES_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models.">>=
+% cesFittedData <- filter(fitted_df, model=="ces", nest %in% c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"))
+% spaghettiPlot(data=cesFittedData, facet_formula=Country~nest, level=spaghettiGraphLevel) +
+%     labs(y="Indexed GDP (1980=1 or 1991=1)")
+% @
+
+<<CES_Spaghetti_Graph_kle, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models with (kl)e nesting.">>=
+cesFittedData <- filter(fitted_df, model=="ces", nest %in% c("iK+iL", "iK+iL+iQ", "iK+iL+iX", "iK+iL+iU"))
+spaghettiPlot(data=cesFittedData, facet_formula=Country~nest, level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1980=1 or 1991=1)")
+@
+
+<<CES_Spaghetti_Graph_lek, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models with (le)k nesting.">>=
+cesFittedData <- filter(fitted_df, model=="ces", nest %in% c("iK+iL", "iL+iQ+iK", "iL+iX+iK", "iL+iU+iK"))
+spaghettiPlot(data=cesFittedData, facet_formula=Country~nest, level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1980=1 or 1991=1)")
+@
+
+<<CES_Spaghetti_Graph_ekl, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models with (ek)l nesting.">>=
+cesFittedData <- filter(fitted_df, model=="ces", nest %in% c("iK+iL", "iQ+iK+iL", "iX+iK+iL", "iU+iK+iL"))
 spaghettiPlot(data=cesFittedData, facet_formula=Country~nest, level=spaghettiGraphLevel) +
@@
 
-\twocolumn{}
-<<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7, fig.cap="LINEX model (with energy) resampling results.">>=
-linexCoeffsData <- filter(coeffs_df, model=="linex", energy=="q")
+% <<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7, fig.cap="LINEX model (with energy) resampling results.">>=
+% linexCoeffsData <- filter(coeffs_df, model=="linex", energy=="q")
+% standardScatterPlot(data=linexCoeffsData, aes(a_0, c_t), facet_formula=country~energy, alpha=0.05) +
+%     labs(x=expression(a[0]), y=expression(c[t])) +
+%      scale_x_continuous(limits=c(-1, 2), breaks=c(-1, 0, 1.0, 2.0)) +
+%      scale_y_continuous(limits=c(0, 10), breaks=c(0, 5, 10))
+% @
+
+<<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=4.5, fig.height=7, fig.cap="LINEX model (with energy) resampling results.">>=
+linexCoeffsData <- filter(coeffs_df, model=="linex")
 standardScatterPlot(data=linexCoeffsData, aes(a_0, c_t), facet_formula=country~energy, alpha=0.05) +
@@
 
-<<LINEX_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7.1, fig.cap="LINEX fitted models.">>=
-linexFittedData <- filter(fitted_df, model=="linex", energy=="q")
+% <<LINEX_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7.1, fig.cap="LINEX fitted models.">>=
+% linexFittedData <- filter(fitted_df, model=="linex", energy=="q")
+% spaghettiPlot(data=linexFittedData, facet_formula=Country~energy, level=spaghettiGraphLevel) +
+%     labs(y="Indexed GDP (1980=1 or 1991=1)")
+% @
+
+<<LINEX_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=4.5, fig.height=7.1, fig.cap="LINEX fitted models.">>=
+linexFittedData <- filter(fitted_df, model=="linex")
 spaghettiPlot(data=linexFittedData, facet_formula=Country~energy, level=spaghettiGraphLevel) +
@@
 @
-\onecolumn{}
 

### 2014-05-18 Article/EconGrowth2-GraphsOnly.Rnw
Moved all loading first.

@@
 # Load coefficients from all models in one large data frame
-# coeffs_df <- tbl_df( readRDS("../AllCoef.rda") )
 coeffs_df <- tbl_df(AllCoef)
+# Load fitted data from all models in one large data frame
+fitted_df <- tbl_df(AllFitted)
+
 # Rearrange the country factors to obtain our preferred ordering.
@@
 
-# Load fitted data from all models in one large data frame
-# fitted_df <- tbl_df( readRDS("../AllFitted.rda") )
-fitted_df <- tbl_df(AllFitted)
 # Rearrange the energy factors to obtain our preferred ordering.

### 2014-05-18 Article/EconGrowth2-GraphsOnly.Rnw
Article now relies on re-leveling of factors by PostProcess.R

@@
 # Rearrange the country factors to obtain our preferred ordering.
-coeffs_df$country <- as.factor(coeffs_df$country)
-for (lev in rev(countryAbbrevs)) { coeffs_df$country <- relevel(coeffs_df$country, ref=lev) }
-# Change the names of the energy factors to the names for the graph
-coeffs_df$energy <- replace(coeffs_df$energy, which(is.na(coeffs_df$energy)), "none")
-coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iQ"), "q")
-coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iX"), "x")
-coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iU"), "u")
+# coeffs_df$country <- as.factor(coeffs_df$country)
+# for (lev in rev(countryAbbrevs)) { coeffs_df$country <- relevel(coeffs_df$country, ref=lev) }
+# Change the names of the energy factors to the desired names for the graph
+# coeffs_df$energy <- replace(coeffs_df$energy, which(is.na(coeffs_df$energy)), "none")
+# coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iQ"), "q")
+# coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iX"), "x")
+# coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iU"), "u")
 # Rearrange the energy factors to obtain our preferred ordering.
-coeffs_df$energy <- as.factor(coeffs_df$energy)
-energyLevels <- c(none="none", q="q", x="x", u="u")
-for (lev in rev(energyLevels)) { coeffs_df$energy <- relevel(coeffs_df$energy, ref=lev) }
+# coeffs_df$energy <- as.factor(coeffs_df$energy)
+# energyLevels <- c(none="none", q="q", x="x", u="u")
+# for (lev in rev(energyLevels)) { coeffs_df$energy <- relevel(coeffs_df$energy, ref=lev) }
 
 # Rearrange the energy factors to obtain our preferred ordering.
-fitted_df$energy <- replace(fitted_df$energy, which(is.na(fitted_df$energy)), "none")
-fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iQ"), "q")
-fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iX"), "x")
-fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iU"), "u")
-fitted_df$energy <- as.factor(fitted_df$energy)
-for (lev in rev(energyLevels)) { fitted_df$energy <- relevel(fitted_df$energy, ref=lev) }
+# fitted_df$energy <- replace(fitted_df$energy, which(is.na(fitted_df$energy)), "none")
+# fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iQ"), "q")
+# fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iX"), "x")
+# fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iU"), "u")
+# fitted_df$energy <- as.factor(fitted_df$energy)
+# for (lev in rev(energyLevels)) { fitted_df$energy <- relevel(fitted_df$energy, ref=lev) }
 

### 2014-05-18 Article/EconGrowth2.Rnw
Article now relies on re-leveling of factors by PostProcess.R

@@
 # Load coefficients from all models in one large data frame
-# coeffs_df <- tbl_df( readRDS("../AllCoef.rda") )
 coeffs_df <- tbl_df(AllCoef)
+# Load fitted data from all models in one large data frame
+fitted_df <- tbl_df(AllFitted)
+
 # Rearrange the country factors to obtain our preferred ordering.
-coeffs_df$country <- as.factor(coeffs_df$country)
-for (lev in rev(countryAbbrevs)) { coeffs_df$country <- relevel(coeffs_df$country, ref=lev) }
+# coeffs_df$country <- as.factor(coeffs_df$country)
+# for (lev in rev(countryAbbrevs)) { coeffs_df$country <- relevel(coeffs_df$country, ref=lev) }
 # Change the names of the energy factors to the names for the graph
-coeffs_df$energy <- replace(coeffs_df$energy, which(is.na(coeffs_df$energy)), "none")
-coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iQ"), "q")
-coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iX"), "x")
-coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iU"), "u")
+# coeffs_df$energy <- replace(coeffs_df$energy, which(is.na(coeffs_df$energy)), "none")
+# coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iQ"), "q")
+# coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iX"), "x")
+# coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iU"), "u")
 # Rearrange the energy factors to obtain our preferred ordering.
-coeffs_df$energy <- as.factor(coeffs_df$energy)
-energyLevels <- c(none="none", q="q", x="x", u="u")
-for (lev in rev(energyLevels)) { coeffs_df$energy <- relevel(coeffs_df$energy, ref=lev) }
-
-# Load fitted data from all models in one large data frame
-# fitted_df <- tbl_df( readRDS("../AllFitted.rda") )
-fitted_df <- tbl_df(AllFitted)
+# coeffs_df$energy <- as.factor(coeffs_df$energy)
+# energyLevels <- c(none="none", q="q", x="x", u="u")
+# for (lev in rev(energyLevels)) { coeffs_df$energy <- relevel(coeffs_df$energy, ref=lev) }
+
 # Rearrange the energy factors to obtain our preferred ordering.
-fitted_df$energy <- replace(fitted_df$energy, which(is.na(fitted_df$energy)), "none")
-fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iQ"), "q")
-fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iX"), "x")
-fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iU"), "u")
-fitted_df$energy <- as.factor(fitted_df$energy)
-for (lev in rev(energyLevels)) { fitted_df$energy <- relevel(fitted_df$energy, ref=lev) }
+# fitted_df$energy <- replace(fitted_df$energy, which(is.na(fitted_df$energy)), "none")
+# fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iQ"), "q")
+# fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iX"), "x")
+# fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iU"), "u")
+# fitted_df$energy <- as.factor(fitted_df$energy)
+# for (lev in rev(energyLevels)) { fitted_df$energy <- relevel(fitted_df$energy, ref=lev) }
 
@@
 <<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7, fig.cap="LINEX model (with energy) resampling results.">>=
-linexCoeffsData <- filter(coeffs_df, model=="linex", energy=="q")
+linexCoeffsData <- filter(coeffs_df, model=="linex", energy=="iQ")
 standardScatterPlot(data=linexCoeffsData, aes(a_0, c_t), facet_formula=country~energy, alpha=0.05) +
@@
 <<LINEX_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7.1, fig.cap="LINEX fitted models.">>=
-linexFittedData <- filter(fitted_df, model=="linex", energy=="q")
+linexFittedData <- filter(fitted_df, model=="linex", energy=="iQ")
 spaghettiPlot(data=linexFittedData, facet_formula=Country~energy, level=spaghettiGraphLevel) +

### 2014-05-18 Article/EconGrowth2-GraphsOnly.Rnw
Deleted releveling code. Now in PostProcess.R.

--- 2014-05-18 Article/EconGrowth2-GraphsOnly.Rnw
@@
 
-# Rearrange the country factors to obtain our preferred ordering.
-coeffs_df$country <- as.factor(coeffs_df$country)
-for (lev in rev(countryAbbrevs)) { coeffs_df$country <- relevel(coeffs_df$country, ref=lev) }
-# Change the names of the energy factors to the names for the graph
-coeffs_df$energy <- replace(coeffs_df$energy, which(is.na(coeffs_df$energy)), "none")
-coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iQ"), "q")
-coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iX"), "x")
-coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iU"), "u")
-# Rearrange the energy factors to obtain our preferred ordering.
-coeffs_df$energy <- as.factor(coeffs_df$energy)
-energyLevels <- c(none="none", q="q", x="x", u="u")
-for (lev in rev(energyLevels)) { coeffs_df$energy <- relevel(coeffs_df$energy, ref=lev) }
-
-# Rearrange the energy factors to obtain our preferred ordering.
-fitted_df$energy <- replace(fitted_df$energy, which(is.na(fitted_df$energy)), "none")
-fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iQ"), "q")
-fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iX"), "x")
-fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iU"), "u")
-fitted_df$energy <- as.factor(fitted_df$energy)
-for (lev in rev(energyLevels)) { fitted_df$energy <- relevel(fitted_df$energy, ref=lev) }
-
 # Load the original models.
-# oModels <- readRDS(file=file.path("..", "oModels.Rdata"))
 oModels <- OrigModels

### 2014-05-18 Article/EconGrowth2.Rnw
Deleted releveling code. Now in PostProcess.R.

@@
 
-# Rearrange the country factors to obtain our preferred ordering.
-# coeffs_df$country <- as.factor(coeffs_df$country)
-# for (lev in rev(countryAbbrevs)) { coeffs_df$country <- relevel(coeffs_df$country, ref=lev) }
-# Change the names of the energy factors to the names for the graph
-# coeffs_df$energy <- replace(coeffs_df$energy, which(is.na(coeffs_df$energy)), "none")
-# coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iQ"), "q")
-# coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iX"), "x")
-# coeffs_df$energy <- replace(coeffs_df$energy, which(coeffs_df$energy=="iU"), "u")
-# Rearrange the energy factors to obtain our preferred ordering.
-# coeffs_df$energy <- as.factor(coeffs_df$energy)
-# energyLevels <- c(none="none", q="q", x="x", u="u")
-# for (lev in rev(energyLevels)) { coeffs_df$energy <- relevel(coeffs_df$energy, ref=lev) }
-
-# Rearrange the energy factors to obtain our preferred ordering.
-# fitted_df$energy <- replace(fitted_df$energy, which(is.na(fitted_df$energy)), "none")
-# fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iQ"), "q")
-# fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iX"), "x")
-# fitted_df$energy <- replace(fitted_df$energy, which(fitted_df$energy=="iU"), "u")
-# fitted_df$energy <- as.factor(fitted_df$energy)
-# for (lev in rev(energyLevels)) { fitted_df$energy <- relevel(fitted_df$energy, ref=lev) }
-
 # Load the original models.
-# oModels <- readRDS(file=file.path("..", "oModels.Rdata"))
 oModels <- OrigModels

### 2014-05-29 Article/EconGrowth2-GraphsOnly.Rnw
Added a scatter graph for CD lambda and theta.

@@
 
+<<CD_lambda_theta_graph, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\theta$ values for CD resample models.">>=
+cdCoeffsData <- filter(coeffs_df, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iQ", "iK+iL+iX", "iK+iL+iU"))
+standardScatterPlot(data=cdCoeffsData, mapping=aes(scale, lambda), facet_formula=country~energy, alpha=0.05) +
+    scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
+    scale_y_continuous(breaks=c(0, 0.025, 0.05, 0.075)) +    
+    labs(x=expression(theta), y=expression(lambda))
+@
+
 <<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=5.8, fig.height=7.7, fig.cap="Cobb-Douglas resample model parameters.">>=
-cdCoeffsData <- filter(coeffs_df, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iQ", "iK+iL+iX", "iK+iL+iU"))
 standardTriPlot(data=cdCoeffsData, facet_formula=country~energy)

### 2014-05-30 Article/EconGrowth2.Rnw
Added "that".

@@
 In this paper, we assess three prominent energy-augmented production functions 
-appear in the literature: Cobb-Douglas (CDe), Constant Elasticity of 
+that appear in the literature: Cobb-Douglas (CDe), Constant Elasticity of 
 Substitution (CESe), and LINear EXponential (LINEX). The following subsections 

### 2014-05-30 Article_JAE_2014/ZAGrowth_JAE.Rnw
Adding a directory for Journal of African Economics paper.

--- 2014-05-18 Article/EconGrowth2.Rnw
@@
-% This article has been prepared for publication in Energy Economics in RStudio with knitr.
-% According to http://www.elsevier.com/author-schemas/the-elsarticle-latex-document-class, we should be using the
-% elsarticle.cls file.
-% According to http://cdn.elsevier.com/assets/pdf_file/0006/109392/journal_refstyles.pdf, we should be using
-% elsarticle-template-2-harv.tex as the template for the text.
-% Furthermore, we should be using model2-names.bst for the bibliographic references.
-% The approach here is to load the frontmatter and backmatter from elsarticle-template-2-harv.tex
-% both ahead of and behind the text for our paper.
-% -- Matthew Kuperus Heun, 2013-01-18
+% This article has been prepared for publication in the Journal of African Economies in RStudio with knitr.
+% -- Matthew Kuperus Heun, 2014-05-30
 
-%% This is file `elsarticle-template-2-harv.tex',
-%%
-%% Copyright 2009 Elsevier Ltd
-%%
-%% This file is part of the 'Elsarticle  Bundle'.
-%% ---------------------------------------------
-%%
-%% It may be distributed under the conditions of the LaTeX Project Public
-%% License, either version 1.2 of this license or (at your option) any
-%% later version.  The latest version of this license is in
-%%    http://www.latex-project.org/lppl.txt
-%% and version 1.2 or later is part of all distributions of LaTeX
-%% version 1999/12/01 or later.
-%%
-%% The list of all files belonging to the 'Elsarticle Bundle' is
-%% given in the file `manifest.txt'.
-%%
-%% Template article for Elsevier's document class `elsarticle'
-%% with harvard style bibliographic references
-%%
-%% $Id: elsarticle-template-2-harv.tex 155 2009-10-08 05:35:05Z rishi $
-%% $URL: http://lenova.river-valley.com/svn/elsbst/trunk/elsarticle-template-2-harv.tex $
-%%
-\documentclass[preprint,authoryear,12pt]{elsarticle}
+\documentclass[a4paper]{article}
 
-%% Use the option review to obtain double line spacing
-%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}
-
-%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
-%% for a journal layout:
-%% \documentclass[final,authoryear,1p,times]{elsarticle}
-%% \documentclass[final,authoryear,1p,times,twocolumn]{elsarticle}
-%% \documentclass[final,authoryear,3p,times]{elsarticle}
-%% \documentclass[final,authoryear,3p,times,twocolumn]{elsarticle}
-%% \documentclass[final,authoryear,5p,times]{elsarticle}
-%% \documentclass[final,authoryear,5p,times,twocolumn]{elsarticle}
-
-%% if you use PostScript figures in your article
-%% use the graphics package for simple commands
-%% \usepackage{graphics}
-%% or use the graphicx package for more complicated commands
-%% \usepackage{graphicx}
-%% or use the epsfig package if you prefer to use the old commands
-%% \usepackage{epsfig}
-
-%% The amssymb package provides various useful mathematical symbols
-\usepackage{amssymb}
-%% The amsthm package provides extended theorem environments
-%% \usepackage{amsthm}
-
-\usepackage{wrapfig}    % Allows wrapping of text around figures
-\usepackage{soul}       % Provides strikethrough text
-\usepackage{float}      % Allows precise positioning of tables and figures within the text
-\usepackage{amsmath}    % Allows \begin{equation*} \end{equation*} for unnumbered equations
-\usepackage{multirow}   % To create multirow tables
-\usepackage{hyperref}   % To create hyperlinks in the paper
 \usepackage{microtype}  % produces hanging punctuation and beautiful type
-
-% From http://economics.utoronto.ca/osborne/latex/BIBTEX.HTM
-\newcommand{\citeapos}[1]{\citeauthor{#1}'s (\citeyear{#1})} % Posessive citations.
-
-%% The lineno packages adds line numbers. Start line numbering with
-%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
-%% for the whole article with \linenumbers after \end{frontmatter}.
-%% \usepackage{lineno}
-
-%% natbib.sty is loaded by default. However, natbib options can be
-%% provided with \biboptions{...} command. Following options are
-%% valid:
-
-%%   round  -  round parentheses are used (default)
-%%   square -  square brackets are used   [option]
-%%   curly  -  curly braces are used      {option}
-%%   angle  -  angle brackets are used    <option>
-%%   semicolon  -  multiple citations separated by semi-colon (default)
-%%   colon  - same as semicolon, an earlier confusion
-%%   comma  -  separated by comma
-%%   authoryear - selects author-year citations (default)
-%%   numbers-  selects numerical citations
-%%   super  -  numerical citations as superscripts
-%%   sort   -  sorts multiple citations according to order in ref. list
-%%   sort&compress   -  like sort, but also compresses numerical citations
-%%   compress - compresses without sorting
-%%   longnamesfirst  -  makes first citation full author list
-%%
-%% \biboptions{longnamesfirst,comma}
-
-% \biboptions{}
-
+\usepackage[compress]{natbib}
 \usepackage[shownotes]{authNote}
 
-\journal{Energy Economics}
-
-\begin{document}
+\title{Growth of the South African Economy:\\An Empirical Evaluation}
+\author{Matthew Kuperus Heun, Martin de Wit, Randall Pruim,\\Stan du Plessis, Ben Smit}
+\date{\today}
+% \date{}
 
@@
 require(EconData)
-require(lattice)
-require(latticeExtra)
+require(knitr)
+require(dplyr)
 require(ggplot2)
-require(car)
-require(mosaic)
-require(xtable)
-require(nlmrt)
-# require(micEconCES)
-require(plyr)
-require(dplyr)
-# Provides access to data melting. 
-# See http://cran.r-project.org/web/packages/reshape2/reshape2.pdf
-require(reshape2) 
-# tikz allows use of LaTeX formatting and font in graphs. 
-# Allows for a consistent look across the paper.
-# See http://r-forge.r-project.org/R/?group_id=440 for instructions 
-# on installing tikzDevice.
-# require(tikzDevice) 
-trellis.par.set(theme=theme.mosaic())
-options(width=75)
-options(show.signif.stars=TRUE)
-require(knitr)
-
-# Load historical data
-# In Rstudio, this paper is generated from it's directory, which is "Article".
-# We need to define paths relative to the location of the paper. 
-# Relative path to historical data from Article
-historicalData <- Econ2011 # From the EconData package
-
-# Load coefficients from all models in one large data frame
-coeffs_df <- tbl_df(AllCoef)
-# Load fitted data from all models in one large data frame
-fitted_df <- tbl_df(AllFitted)
-
-# Load the original models.
-oModels <- OrigModels
-
 opts_chunk$set(
@@
   # Tells whether to echo code for all chunks. 
-  # Set TRUE on an individual chunk to see its code.
+  # Set echo=TRUE on an individual chunk to see its code.
   echo=FALSE     
 )
-@
-
-<<constants, include=FALSE, eval=TRUE>>=
-# Graph Heights
-maxHeight <- 8.5 # Inches
-ninePanelScatterGraphHeight <- maxHeight # Inches
-# ninePanelTernaryGraphHeight <- 7 # Inches
-# ninePanelSpaghettiGraphHeight <- 7 # Inches
-
-# Graph Widths
-maxWidth <- 6.5 # Inches
-fourPanelScatterGraphWidth <- maxWidth # Inches
-# threePanelScatterGraphWidth <- maxWidth*0.75 # Inches
-# onePanelScatterGraphWidth <- maxWidth*0.25
-# fourPanelTernaryGraphWidth <- maxWidth
-# twoPanelTernaryGraphWidth <- maxWidth*0.45
-# fourPanelSpaghettiGraphWidth <- maxWidth
-# twoPanelSpaghettiGraphWidth <- maxWidth*0.55
-# onePanelSpaghettiGraphWidth <- maxWidth*0.4
-
-presentationGraph1RowHeight <- 2.8 # Inches
-presentationGraph2ColWidth <- 2 # Inches
-presentationGraph1ColWidth <- 2*presentationGraph2ColWidth
-# keyTextSize <- 0.85 # 85% of normal size
-# keyColumns <- 1 # Want only 1 column in the key for lattice graphs
-# defaultKeyXLoc <- 0.01 # x position of the key. This default is good for 9-panel graphs.
-# defaultKeyYLoc <- 0.95 # y position of the key. This default is good for 9-panel graphs.
-# Parameter graphs are tricky to ensure same size. I've found that with height set to 5 in for the 
-# cd graphs and 2.93 in for the sf graphs, I get a nearly-exact match with graph size. From these settings I 
-# can set up 2 equations:
-#    5 in = 2*hgraph + haxis
-#    2.93 in = hgraph + haxis
-# to estimate that h_axis = 0.86 in and hgraph = 2.05 in.
-h_param_graph <- 2.07 # Inches for a single panel
-h_param_axis <- 0.86 # Inches (also includes whatever margin is applied)
-# sfParameterGraphHeight <- h_param_graph + h_param_axis
-cdParameterGraphHeight <- 2*h_param_graph + h_param_axis
-cesParameterGraphHeight <- 3*h_param_graph + h_param_axis
-linexParameterGraphHeight <- h_param_graph + h_param_axis
-sfParameterGraphWidth <- maxWidth
-cdParameterGraphWidth <- maxWidth
-cesParameterGraphWidth <- maxWidth
-linexParameterGraphWidth <- maxWidth
-# Other graph parameters that apply to all graphs
-scaleTextSize <- 0.8  # Multiple of normal size
-scaleTickSize <- -0.5 # 50% of normal size and pointing INWARD!
-
 spaghettiGraphLevel <- 0.95 # Spaghetti graph bands will encompass 95% of the data.
@@
 \newcommand{\ceskl}[1]{\begin{equation} #1
-  y = \gamma \: A \: \left[\delta_1 k^{-\rho_1} 
+  y = \theta \: A \: \left[\delta_1 k^{-\rho_1} 
       + (1-\delta_1)l^{-\rho_1} \right]^{-1/\rho_1}; 
@@
 \newcommand{\ceskle}[1]{\begin{equation} #1
-  y = \gamma \: A \: \left\{\delta \left[\delta_1 k^{-\rho_1} 
+  y = \theta \: A \: \left\{\delta \left[\delta_1 k^{-\rho_1} 
       + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1} 
@@
 \newcommand{\ceslek}[1]{\begin{equation} #1
-  y = \gamma \: A \: \left\{\delta \left[\delta_1 l^{-\rho_1} 
+  y = \theta \: A \: \left\{\delta \left[\delta_1 l^{-\rho_1} 
       + (1-\delta_1) e^{-\rho_1} \right]^{\rho/\rho_1} 
@@
 \newcommand{\cesekl}[1]{\begin{equation} #1
-  y = \gamma \: A \: \left\{\delta \left[\delta_1 e^{-\rho_1} 
+  y = \theta \: A \: \left\{\delta \left[\delta_1 e^{-\rho_1} 
       + (1-\delta_1) k^{-\rho_1} \right]^{\rho/\rho_1} 
@@
 
-\begin{frontmatter}
+\begin{document}
 
-%% Title, authors and addresses
-
-%% use the tnoteref command within \title for footnotes;
-%% use the tnotetext command for the associated footnote;
-%% use the fnref command within \author or \address for footnotes;
-%% use the fntext command for the associated footnote;
-%% use the corref command within \author for corresponding author footnotes;
-%% use the cortext command for the associated footnote;
-%% use the ead command for the email address,
-%% and the form \ead[url] for the home page:
-%%
-%% \title{Title\tnoteref{label1}}
-%% \tnotetext[label1]{}
-%% \author{Name\corref{cor1}\fnref{label2}}
-%% \ead{email address}
-%% \ead[url]{home page}
-%% \fntext[label2]{}
-%% \cortext[cor1]{}
-%% \address{Address\fnref{label3}}
-%% \fntext[label3]{}
-
-\title{An Empirical Analysis of the Role of Energy in Economic Growth}
-
-%% use optional labels to link authors explicitly to addresses:
-%% \author[label1,label2]{<author name>}
-%% \address[label1]{<address>}
-%% \address[label2]{<address>}
-
-\author[CalvinEngr]{Matthew Kuperus Heun\corref{cor1}}
-\ead{mkh2@calvin.edu}
-\author[Stellenbosch]{Martin de Wit}
-\author[CalvinMath]{Randall J. Pruim}
-\author[CalvinEngr]{Caleb Reese}
-\author[CalvinEngr]{Lucas Timmer}
-
-\cortext[cor1]{Corresponding author}
-\address[CalvinEngr]{Engineering Department, Calvin College, Grand Rapids, MI 49546, USA}
-\address[Stellenbosch]{Faculty of Economics and Management Sciences, School of Public Leadership, Stellenbosch University, P.O. Box 610, Bellville 7535, South Africa}
-\address[CalvinMath]{Mathematics \& Statistics Department, Calvin College, Grand Rapids, MI 49546, USA}
+\maketitle
 
 \begin{abstract}
-%% Text of abstract
-**** Add abstract ****
+Abstract goes here.
 \end{abstract}
 
-\begin{keyword}
-%% keywords here, in the form: keyword \sep keyword
-economic growth \sep energy \sep Cobb-Douglas \sep CES \sep LINEX
-%% MSC codes here, in the form: \MSC code \sep code
-%% or \MSC[2008] code \sep code (2000 is the default)
-\end{keyword}
+%++++++++++++++++++++++++++++++
+\section{Introduction}
+\label{sec:Intro}
+%++++++++++++++++++++++++++++++
 
-\end{frontmatter}
+Intro goes here.
 
-% \linenumbers
-%% main text
+%++++++++++++++++++++++++++++++
+\section{Mathematical Forms of the Energy-augmented Production Functions} 
+\label{sec:Prod_Func_Forms}
+%++++++++++++++++++++++++++++++
 
-\section*{Notes from Martin}
+In this paper, we assess three prominent energy-augmented production functions that
+appear in the literature: Cobb-Douglas (CD), Constant Elasticity of 
+Substitution (CES), and LINear EXponential (LINEX). The following subsections 
+describe each.
 
-**** Additional references requested by Martin. Incorporate into paper? ****
+%------------------------------
+\subsection{Energy-augmented Cobb-Douglas Production Function} 
+\label{sec:CDe}
+%------------------------------
 
-\citet{Lindenberger:2011dx}
-
-\citet{Stresing:2008cq}
-
-**** Notes from Martin ****
-
-To be included somewhere.
-
-Introduction
-
-[1. Listen to what others say
-Identify key issues and important voices]
-
-The availability of adequate energy at affordable costs 
-has become an important strategic issue in recent years.
-Despite a slowdown in economic growth worldwide, 
-longer-term trends in energy use remain strongly upwards, 
-as the dynamics of energy markets are increasingly determined by emerging economies, 
-notably China, India, and the Middle East \citep{IEA:2012ty}. 
-A large body of literature points to the fact that 
-economic growth and energy consumption are closely correlated 
-and for a diverse set of countries such as 
-the United States \citep{Stern:2000wq, Cleveland:1984p5055}, 
-India \citep{Paul:2004jl}, 
-China \citep{Wang:2011fe}, 
-South Africa \citep{Menyah:2010hl, Odhiambo:2009hj} and 
-sixteen Asian countries \citep{Lee:2008dm}
-to name a few, 
-although the causal relationship from energy consumption 
-to economic growth remains controversial \citep{Chen:2012fs, Ozturk:2010kb}. 
-\citet[p. 347]{Ozturk:2010kb} in a survey of the literature on the topic, 
-concluded that there is 
-``\dots no consensus neither on the existence nor on the direction of 
-causality between these variables in the literature,'' 
-but does point out that ``\dots causality is running from 
-electricity consumption to economic growth 
-in the most of these studies [surveyed].''
-
-Those that have accepted that energy use is closely correlated with
-economic performance in one form or another
-have expressed further concerns on the negative effects of 
-rising energy prices and fossil fuel depletion 
-on current and future economic growth.
-\citet{Benes:2012tm}, incorporating views on both
-geological physical constraints and 
-technological solutions to oil production, 
-suggest a near doubling of the real price of over the next decade.  
-\citet{Kumhof:2012ua} point out that 
-significant impacts on GDP growth could occur
-for larger oil supply shocks, 
-assuming production functions where oil plays a prominent role 
-and reduced possibilities for substitution away from oil.  
-\citet{Nel:2010fv} argue for the 
-``\dots vital importance of energy security \dots'' 
-on the basis of a model based on an explicit 
-energy-based formulation of economic growth.  
-\citet{Hamilton:2013vc} argues that 
-``[c]oping with a final peak in world oil production \dots 
-[will] have much in common with previous historical episodes that resulted from 
-temporary geopolitical conflict, 
-being associated with significant declines in employment and output. 
-If the future decades look like the last 5 years, we are in for a rough time.''
-
-The current trends in energy production and consumption and 
-the possible dire impacts on the world economy 
-as argued by above-mentioned scholars 
-have further raised the question of
-whether and how to include appropriate energy indicators 
-in economic growth modeling.  
-\citet[p. 26]{Stern:2011bq} provides an overview of how energy is included 
-in mainstream economic, resource economic, and ecological economic models of growth.  
-\citeauthor{Stern:2011bq} points out that energy is usually \emph{not included} 
-as a factor of production in mainstream economic growth models, 
-that energy is seen as the \emph{central driver of growth} 
-in ecological economic (including biophysical economic) models, 
-and that energy \emph{is included} in resource economic models, 
-but \emph{remains isolated} within this sub-discipline.  
-To break through this theoretical impasse, 
-Stern proposes a synthesized CES production function 
-where the constraints or abundance of energy 
-determines whether to include energy explicitly 
-as a factor of production.  
-On the basis of this model, 
-\citet[p. 45]{Stern:2011bq} points out that 
-energy availability plays
-``\dots a key role in enabling growth,''
-despite the evidence of decreasing energy consumed per unit of output.  
-He concludes, based on theory and time-series results, 
-that including energy in the production function is warranted, 
-and that further clarification is needed 
-on the role of energy in economic growth.
-
-The inclusion of energy as a factor of production 
-in CES and Cobb-Douglas production functions 
-is generally accepted by most 
-resource and energy economists and economic growth modelers 
-\citep{Smulders:2003wc, vanderZwaan:2002wn, Kemfert:1998vd}.
-Researchers interested in explaining long-term economic growth 
-and possible constraints on growth 
-have started to include energy as an explicit factor of production
-\citep{Froling:2009vo, Tahvonen:2001tz}.  
-An alternative approach, attempting to be 
-``\dots more consistent with physical laws \dots'' \citep{Ayres:2001tx}
-and classified by \citet{Stern:2011bq} as an ecological economic model of growth, 
-is the LINEX production function, 
-combining capital (non-ICT and ICT), 
-labour, and useful work. In the LINEX model, 
-technological change affects only 
-the amount of useful work done per joule of exergy \citep{Ayres:2005kn}.
-
-Unsatisfactorily, the choice of a production function 
-and the parameters used to populate these functions 
-affects results significantly.
-This situation leaves far too much latitude 
-for misuse of model specifications 
-and selection of parameters 
-to support certain theories (rather than empirically testing the theories
-and parameters \emph{before} they are employed).  
-For example, \citet{Lecca:2011kr} pointed out that 
-the modellers' choice for the structure of a production function 
-reflects his or her assumptions about
-the elasticities among inputs, and 
-``\dots the point at which energy enters the [nested CES] production function 
-has a significant impact on CGE [computable general equilibrium] model results.''
-\citet{Duffy:2000ty} rejected the Cobb-Douglas production function altogether, 
-finding that capital and labour are more substitutable 
-in richer countries and less substitutable in poorer countries 
-than Cobb-Douglas implies.  
-However, \citet{Miller:2008vd} points to the 
-``\dots reasonably accurate long-term economic forecasts,'' 
-achieved with the use of Cobb-Douglas production functions in economic models.  
-\citet{Shen:2013vp} provide a recent example 
-wherein empirical analysis on the estimated substitution elasticities 
-is performed before choosing any particular 
-nested CES production function structure. 
-As a result, \citeauthor{Shen:2013vp} propose an atypical structure 
-for the Chinese economy. **** More detail here about nesting? ****  
-Both the choice of production function structure 
-and the value of the model parameters 
-drive model results, and empirical and statistical testing 
-of such approaches is prudent, but rarely conducted.
-
-[2. Find our own voice
-What is our own argument?]
-
-These are not idle debates. 
-Economic growth models are often used to inform economic policy,
-and the paths of economies worldwide are determined by
-such policy choices. 
-Therefore, we agree with those who have serious concerns 
-about the reliability of the results from economic growth models \citep{Lecca:2011kr}. 
-\citet{Lecca:2011kr} and **** and what? **** would like to add
-**** ``would like to add'' or ``add''?**** that the inclusion of energy 
-would only further complicate issues.  **** Prev. sentence is unclear. ****
-We do except **** do you mean ``accept'' or ``expect'' here? ****, however, 
-that macroeconomic policymaking is needed 
-and is increasingly informed by integrated energy-economic models, 
-in a world where energy constraints are possible 
-\citep{Beckman:2011gb, Benes:2012tm, Nel:2010fv}.  
-We support the call from \citet{Shen:2013vp} that both
-the structure of the production function 
-and the parameters used to populate this function
-need empirical testing. 
-Furthermore, the quantification of energy ($q$, $x$, or $u$) 
-needs to be empirically assessed.  **** Need more on topic of energy quantification above. ****
-Building on the argument of \citet{Stern:2011bq} 
-that energy may or may not be required in production functions 
-depending on its abundance or scarcity, 
-we will further argue in this paper that different types of countries 
-may need different factors of production to explain their respective growth paths.  
-This further leaves open the possibility for 
-different explanations of growth in various countries
-at different stages of their development, 
-a central point of long-wave economic growth modeling 
-\citep{Froling:2009vo, Jones:2001wn, Galor:2000up}. 
-**** Should we discuss the longwave literature above? ****
-
-To gain insights from different countries across different stages of development, 
-we present a comparative analysis among 
-the World Bank’s main categories of countries, 
-namely Developed Countries (DCs), 
-Newly Industrialized Countries (NICs), 
-OPEC countries, and 
-Least Developed Countries (LDCs). 
-**** Move the previous sentence to the ``approach'' section below? ****
-
-Approach
-
-Build on articles using R to test econ growth PF, 
-question what is reported when doing these tests (shen/whalley and others who have used micEconCES).
-
-Discussion and Insights
-
-Does analysis differ from others in the conversation?
-Yes, differs as follows:
-\begin{itemize}
-\item{if one do these test, report on all $\delta$, $\sigma$, $\gamma$, and $\lambda$ 
-values as well as sse. 
-Good fits not evidence of best values, must report uncertainties as well.}
-\item{What motivates nesting of CES? Not well behaved $\rho$ results, driving $\sigma$s.
-Different type of CES with parsimonious factors, sigmas can be generated but not that easy (idea Randy).
-If you run all 3 nesting options, you can identify elasticities of all three factors in relation to each 
-other. Furthermore, you can determine which two factors are driving overall behavior in the aggregate function.}
-\item{necessary of different factors in PF to explain growth for countries in diff. development status}
-\end{itemize}
-
-What do we add to the conversation?
-
-\begin{itemize}
-
-\item{We are able to gain rich insights 
-on what really drives growth from detailed analysis (including uncertainties) 
-by testing all functional forms across many different 
-economy types.}
-
-\item{We were unable to gain new insights from the various energy quantifications that we tried.}
-
-\item{We find, surprisingly, that energy is not necessary 
-to be included alongside $k$ and $l$ in all PF. Models with energy and models without energy
-all perform well on an R$^2$ basis.}
-
-\item{We also find that
-
-(1) covariance of energy($e$) with both $k$ and $l$ is very high, with few exceptions (UK?).
-
-(2) with few exceptions, $\sigma_{(kl)e}$, $\sigma_{ke}$, and $\sigma_{le}$ 
-are all very low (indicating complementarity) (verify!!!!), and
-
-(3) energy-only models (SF$e$ and LINEX) achieve very good fits, just like CD$e$ and CES$e$.
-(should we make this point or not?)}
-
-\item{What does that mean? 
-It is a fallacy to think that saying energy is unnecessary 
-to include in an equation means energy is unimportant for economic growth. How to support this argument?
-
-If you find that energy is unnecessary to include alongside capital and labor 
-to explain growth in one economy at the macro, aggregated level, 
-you should not assume that energy is unimportant as a driver for economic growth for all economies.
-For developed economies, energy is captial intensive: you need to have large capital to make use 
-of energy. In developing economies, you don't need capital to make use of energy. 
-Rather, you need labor.
-
-We need to verify the above by comparison with our results.}
-
-\item{Also signals that different types of countries likely 
-to react differently to energy constraints. 
-Interpret $\sigma$ here, substitution possibilities.}
-
-\end{itemize}
-
-More work?
-
-Big picture
-[insert test test]
-
-Why do we do this? Want to link energy and economics on national level 
-and in a modeled approach,informing energy policy during energy transitions.
-Usually macro energy economic models rely on PF with energy included. 
-Key papers using CES in energy economics incl high impact such as 
-Stern, Gerlagh, Tol etc. 
-Cite in introduction met energy economists using PF approaches, specially CES.
-But, which form to choose and using which parameters? 
-Literature is inconclusive, very little actual empirical testing of such functions. 
-Mostly CES in CGE models used by Wbank and others. 
-CD adviced to be used by CBO. 
-How do we select a functional form and what are the parameters to be used? On what basis do we select?
-
-We aim. to search for empirically robust solution, one that stands up to statistical testing.
-
-What we find is counterintuitive for many cases: dropping energy from the PF has little impact, 
-but some notable exceptions. 
-On other hand, only including energy in a PF of LINEX form also yields good results and stats tests. 
-Is not a simple case for dropping energy, but acknowledging its key role. 
-Do we support the call for better bottom-up understanding? 
-What do we say on the limitations of macroeconomic modelling approaches altogether? 
-(Note such limitations are well known in ME literature, for example capital controversy Robinson).
-We speculate on implications for choosing PF in energy economic models that inform growth policy.
-
-Points on paper so far
-1. Does the relative small differences in fit between different production functions warrant 
-such a large debate on validity of one vs other? Clearly not. 
-CD been used by economists for ease of use and extreme flexibility (Miller).  
-PF generally used on instrumentalist grounds if give reasonable good description of data. 
-NK econ theory provide poor causal explanation of observed data, 
-but yet CD shows very good fit (miller, p17). 
-CES is  more general, but is a liability in forecasting because difficult 
-to get estimate of EoS that is consistent across studies (Miller, p26). 
-Aggregation is problem of both CD and CES functional forms, 
-so being careful when making strong inferences that cannot be justified.
-
-2. We think we can contribute by emphasising the need 
-for proper stats testing or inconsistent reporting on use of preferred functions. 
-Problems with empirical testing presented by Shen, Serrenho.
-What are our issues with multivariate OLS (Serrenho)?
-
-3. Are we joining the forced choice between production functions or 
-acknowledge the similar problems with aggregate prod functions in general? 
-Do we see this as sufficient evidence to doubt the top-down approach to econ growth altogether?
-
-4. R2 is a very crude measure and only very minor improvements 
-are achieved when others factors such as energy is added in a CD. 
-We concur. Puzzling is conclusion that such minor improvements 
-does prove the need to include energy in PF (Serrenho).
-
-5. We do think it is a choice between CD and CES (Miller) as 
-both have serious deficiencies after stats tests.
-
-6. One central issue within PF is elasticity of subs (EoS). 
-That is the \%ch in factor proportions ( k,l, etc) 
-because of one unit ch in MRTS. 
-MRTS is rate at which one factor can be substituted for another holding output constant. 
-EoS is low in Leontief cases, L shaped isoquants.
-
-7. Miller makes the point that even if parameters in model are stats artifacts, 
-they are still useful for forecasting. Do we agree?
-
-8. Is Ockham's razor relevant to what we are doing?
-
-9. Assumptions of CD are strongly rejected by empirical work, Miller still makes case for using CD.
-
-11. What about energy augmented
-
-10. TZ case
-CDno e: almost 80\% l
-CD with e: 25\% energy, rest c,importance of l drops to 0
-CES no e: 20\% c ($\sigma$), 80\% l, but large range
-CES with e: fig 35 e may be NB
-LINEX: one of lowest ct parameters (low relative importance of labour eff compared to cap eff)
-Does this mean that relative small increases in cap eff can really lift the economy?
-
-11. ZA case
-CD no e: roughly half c, l
-CD with e: roughly half, c, e, importance of l drops to 0
-CES no e: 10\% c, 25\% l ??
-CES with e: fig 35 e may be NB
-LINEX: one of highest ct parameters (high relative importance of labour eff compared to cap eff)
-Does this mean that relative small increases in labour eff can really lift the economy?
-
-12. Capital starved Zambia. Very high importance. Understand CES param better.
-
-Discussion: What is Next?
-
-a. A comparative analysis between diff PF reveal interesting 
-enough information to warrant a more diffused approach to countries. 
-Thus, we have a case for doing this for  all countries in the world 
-(or at least those representative of countries in different groups 80/20)
-
-b. If c is relatively more important than labour or energy 
-for growth and if capital stock is low, a situation one would expect in LDCs, 
-a relative small addition of capital stock can give relatively large returns in terms of growth.
-
-c. Now it becomes interesting, in a 'stages of growth' approach, 
-using LT econ data it may be the case that the importance 
-of factors are different across growth stages. 
-It would need a composite type of analysis - both stock and importance.
-
-d. Is it possible to have evidence of diff stocks and diff importances across phases of growth? 
-Maybe test this for a data rich nation that has worked through these stages, 
-we try to identify them and do partial analysis on time periods coinciding with these stages.
-
-Should we eliminate $u$ data? Only 3 countries. Only 20 years. Doesn't add much insight. 
-Too bad, but perhaps necessary to simplify paper.
-
-Discussions:
-
-Counterfactuals: energy, cap, labour what ifs for future.
-
-interpretation of type of economies, what does the data presentation say 
-on relative change in each input and change in GDP?
-
-Forcing const elast of subs in CES thru nested structures violates 
-observation that more than two factor will not be const. elasticities Uzawa 1962.
-
-R programming dealt with nested CES see paper discussion on Kemfert.
-
-Next steps:
-
-Stages of growth crowd implicitly assumes countries at similar stage of growth will
-have similar values for $\alpha$, $\beta$, $\gamma$. However, our results show
-that not to be true. Needs further exploration to cover more (all?) countries.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction} 
-\label{sec:Introduction}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-**** Notes on the introduction from Martin ****
-
-1. Set scene through energy economic modelling papers. 
-Point out that PF approaches are alive and well (Stern, Tol, Gerlagh, World Bank, IMF), 
-short lit review as part of a longer introduction.  
-Mention competing PF approaches and parameter choice. 
-On what basis selection and how estimate parameters?
-
-2. Point out the need for adequate statistical testing and economic interpretation, 
-citing some earlier critical papers on PF limitations. Take issue with
-
-3. Spell out the contribution we will be making in this paper, 
-we are taking the approach that all models are wrong but some are useful. 
-We are after generating insights even after deeper assumptions of econ growth theory are very limiting.
-
-4. Introduce coordinates of analysis.
-
-**** Orignial introduction that MKH wrote ****
-
-Neoclassical economic growth theory attributes output ($Y$) to factors of production:
-capital stock ($K$) and labor ($L$). The Cobb-Douglas production function 
-is the 
-canonical representation of indexed economic output ($y$) as a function of indexed 
-labor ($l$), indexed capital stock ($k$), and an additional exogenous, time-dependent 
-term.%
-\footnote{The time-dependent term in production functions is often linked
-to ``technological progress,'' but that is a very narrow reading of Solow's original intent:
-\begin{quote}
-  It will be seen that I am using the phrase ``technical change''
-  as a short-hand expression for any kind of shift 
-  in the production function. 
-  Thus slowdowns, speed-ups, improvements in the education of the labor force, 
-  and all sorts of things will appear as ``technical change.''~\citep{solow1957technical}
-\end{quote}
-}
-This production function can be expressed as
+The Cobb-Douglas production function without energy can be expressed as
 \begin{equation} \label{eq:CD}
@@
 	\item $l \equiv L/L_{0}$, 
-	\item $Y$ represented by GDP, 
-	\item $K$ expressed in currency units, 
-	\item $L$ expressed in workers or work-hours/year, 
-	\item $t$ (time) is measured in years, 
-	\item e is the base of the natural logarithm, and 
-	\item 0 subscripts indicate values at an initial year.%
+	\item $Y$ economic output, measured by GDP, 
+	\item $K$ capital stock, expressed in currency units, 
+	\item $L$ labor, expressed in workers or work-hours/year, 
+	\item $t$ time, measured in years, 
+	\item e the base of the natural logarithm, and 
+	\item 0 subscripts indicate values at an initial year.
 \footnote{Dimensionless, indexed quantities are represented by 
@@
 \end{itemize}
-%Mathematically, $A$ is nothing more than a fitting parameter 
-%that aligns the predictions of Equation~\ref{eq:CD} 
-%with historical data. 
-%Thus, we refer to $A$ as the ``residual'' in this paper.} 
-%term ($A$):
-
-% $A$ is the residual term, 
-% with $\lambda$ 
-% indicating the change of the residual over time (in units of 
-% year$^{-1}$).
-Neoclassical economic growth theory as expressed in the Cobb-Douglas production 
-function makes no attempt to describe the mechanisms that affect
-economic growth, nor does it attempt to describe how such things as
-slowdowns, speedups, and improvements of the education of the labor force
-($\lambda$) might vary from one economy to the next. 
-The parameters $\alpha$ and $\beta$ indicate the relative roles 
-of capital and labor in the economy.
-Typically, the constraint $\alpha + \beta = 1$ is assumed, 
-indicating constant returns to scale.
-
-As shown in Equation~\ref{eq:CD} above, neoclassical economic theory does not 
-include an explicit term for the role of energy in economic growth. However, 
-\citet{Bashmakov:2007ek}, \citet{Hamilton:2009ui}, \citet{Murphy:2011jh}, 
-\citet{Benes:2012tm}, \citet{Kumhof:2012ua}, and others indicate that the 
-importance of energy for economic growth may far outweigh its cost share in the 
-economy. That neoclassical economic growth theory ignores energy is, therefore, 
-cause for concern, and inquiry into the proper approach for including energy 
-as a factor of production in economic growth modeling is both relevant and important.
-
-Some energy economists augment economic growth models by including energy as an 
-additional (or the only) factor of production. However, there is little agreement 
-on how this should be done. Neither the mathematical form of the energy-augmented 
-production function nor the quantification of energy are consistent in the 
-literature. There has been little empirical work assessing the predictive ability 
-of various energy-augmented production functions for different types of economies. 
-And, very few studies of the importance of energy in economic growth include 
-rigorous statistical assessments of energy-related fitting parameters. This paper 
-attempts to contribute to the literature by applying statistically rigorous 
-methods along three coordinates of analysis: form of the energy augmented 
-production function, energy quantification, and type of economy.
-
-The remainder of this paper is organized as follows. Section~\ref{sec:Coordinates} 
-discusses the coordinates of analysis described above. 
-Section~\ref{sec:Sources_of_Data} details sources of data and calculations to 
-generate time series for economic output and factors of production. The procedures 
-for and results from parameter estimation for the various production functions 
-are discussed in Section~\ref{sec:Parameter_Estimation}. 
-Section~\ref{sec:Discussion_of_Results} discusses implications of the parameter estimation 
-results, and Section~\ref{sec:Conclusion} concludes. An appendix provides details 
-of all statistical results.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Coordinates of Analysis} 
-\label{sec:Coordinates}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-This section describes the two coordinates of analysis and briefly reviews 
-literature related to each.
-
-%++++++++++++++++++++++++++++++
-\subsection{Mathematical Forms of the Energy-augmented Production Function} 
-\label{sec:Prod_Func_Forms}
-%++++++++++++++++++++++++++++++
-
-In this paper, we assess three prominent energy-augmented production functions 
-appear in the literature: Cobb-Douglas (CDe), Constant Elasticity of 
-Substitution (CESe), and LINear EXponential (LINEX). The following subsections 
-describe each.
-
-%------------------------------
-\subsubsection{Energy-augmented Cobb-Douglas Production Function (CDe)} 
-\label{sec:CDe}
-%------------------------------
 
@@
 can be augmented to include an energy term:
-%Similarly, the energy-augmented Cobb-Douglas production function is
 
@@
 
-\citet{Ayres:2008cl} uses Equation~\ref{eq:CDe} with exergy ($x$) and 
-useful work ($u$) quantifications for $e$ to describe historic Japanese 
-and American economies from 1900-2000. \citet{Froling:2009vo} uses an 
-energy-augmented Cobb-Douglas production function with thermal energy 
-quantification ($q$) to describe output for the global economy from 
-1800--1970. Fr\"{o}ling's model endogenizes labor with respect to fertility 
-and mortality rates and separates thermal energy into two types: biomass 
-energy and coal energy. \citet{Serrenho:2010vq} use the log transform of 
-the energy-augmented Cobb-Douglas function with thermal energy 
-quantification ($q$) to describe output for the EU-15 countries. 
-Serrenho divides thermal energy into renewables, non-renewables, 
-wastes, and imports. The main argument of these papers is that 
-energy is an important driver of growth and needs to be included
-as an essential factor of production.
-
-**** Martin: add more here about the conclusions of each paper regarding 
-the role of energy in economic growth? Add additional literature? 
-Or, adjust as you see fit. Especially, are there any confidence intervals 
-or statistical evaluation in each of these studies? ****
-
 %------------------------------
-\subsubsection{Energy-augmented CES Production Function (CESe)} 
+\subsection{Energy-augmented CES Production Function (CESe)} 
 \label{sec:CES}
@@
 
-Other energy economists use an energy-augmented 
-Constant Elasticity of Substitution (CES$e$) production function to 
-describe economic growth. The \texttt{R} \citep{R} package 
+The \texttt{R} \citep{R} package 
 \texttt{micEconCES} \citep{Henningsen:2011td} estimates CES production 
@@
 
-$\gamma$ is a fitting parameter that represents productivity. 
+$\theta$ is a fitting parameter that represents productivity. 
 The fitting parameters $\rho_1$ and $\rho$ indicate elasticities 
@@
 \noindent Note that the $\rho$ ($\sigma$) and $\delta$ parameters have different
-meanings that depend upon the nesting of the factors of production.
-**** Do we want to define different variables that indicate meaning, 
-such as $\sigma_{kl}, \sigma_{(kl)e}, \delta_{(ek)l}$, and the like? If so, we'll 
-need to translate from $\rho$ and $\sigma$ in \texttt{cesEst} to the correct
-variable names in the paper. ****
+meanings depending upon the nesting of the factors of production.
 
@@
 
-\citet{VanderWerf:2008tc} evalutes various nested CES production 
-functions for 12 OECD countries with respect to climate change policy. 
-\citeauthor{VanderWerf:2008tc} concludes that ($kl$)($e$) nesting structure 
-best fits historical data. \citet{Lecca:2011kr} also evaluate a variety of 
-CES production functions using a KLEM structure to determine how the various 
-options for nesting the energy factor of production affect predictive ability. 
-\citet{Stern:2012ey} also use a CES production function of the form ($kl$)($e$). 
-\citeauthor{Stern:2012ey} apply their CES function to the Swedish economy 
-from 1800-2000 and demonstrate the importance of the transition from wood to 
-fossil fuels for economic growth. \citet{Shen:2013vp} included energy 
-in nested aggregated CES production functions 
-for China and found that the best nesting structure is ($le$)($k$).
-
-**** Martin: add more here about the conclusions of each paper regarding 
-the role of energy in economic growth? Add additional literature? 
-Or, adjust as you see fit. Especially, are there any confidence 
-intervals or statistical evaluation in each of these studies? ****
-
 %------------------------------
-\subsubsection{LINEX Production Function} 
+\subsection{LINEX Production Function} 
 \label{sec:LINEX}
@@
 %++++++++++++++++++++++++++++++
-\subsection{Economy Types} 
-\label{sec:Economy_Types}
+\section{Data}
 %++++++++++++++++++++++++++++++
 
-In the energy-economic growth literature, the focus is 
-almost exclusively on developed economies from North America 
-or Europe. Examples include \citet{Kummel:1980wx} applying 
-LINEX to describe the West German economy, \citet{Serrenho:2010vq} 
-applying Cobb-Douglas variants to EU-15 countries, 
-\citet{VanderWerf:2008tc} applying CES nesting variants 
-to the 12 OECD countries, \citet{Lecca:2011kr} applying 
-CES nesting variants to the Scottish economy, \citet{Stern:2012ey} 
-applying CES to describe the Swedish economy, and \citet{Warr:2012cg} 
-using LINEX and Cobb-Douglas to describe the Austrian, 
-American, British, and Japanese economies.
+<<data, echo=FALSE, message=FALSE>>=
+# Load historical data
+historicalData <- Econ2011 # From the EconData package
+historicalData <- subset(historicalData, subset=Country=="ZA")
 
-But, the near-exclusive focus on developed economies closes off 
-the possibility of discovering any role that energy plays 
-in the economic development process. In this paper we analyze at least 
-two economies in each of the following four categories: 
-Developed, 
-NICs,\footnote{Newly Industrialized Countries}
-OPEC, and 
-LDCs.\footnote{Lesser Developed Countries} 
-(See Table~\ref{tab:Economy_Examples}.)
+# Load coefficients from all models in one large data frame
+coeffs_df <- tbl_df(AllCoef)
+coeffs_df <- subset(coeffs_df, subset=country=="ZA")
+# Load fitted data from all models in one large data frame
+fitted_df <- tbl_df(AllFitted)
+fitted_df <- subset(fitted_df, subset=Country=="ZA")
+# Load the original models.
+oModels <- OrigModels$ZA
+@
 
-\begin{table} \caption{Example economies and years of evaluation.} \label{tab:Economy_Examples} 
-  \begin{center}
-    \begin{tabular}{r c c l l} 
-      \multirow{3}{*}{Developed} & \includegraphics[height=0.11in]{flag/flag_US.png} & US & USA & \multirow{3}{*}{1980--2011}\\
-                                 & \includegraphics[height=0.11in]{flag/flag_UK.png} & UK & United Kingdom & \\
-                                 & \includegraphics[height=0.11in]{flag/flag_JP.png} & JP & Japan          & \\
-      \hline
-      \multirow{2}{*}{NICs}      & \includegraphics[height=0.11in]{flag/flag_CN.png} & CN & China & \multirow{2}{*}{1991--2011}        \\
-                                 & \includegraphics[height=0.11in]{flag/flag_ZA.png} & ZA & South Africa & \\
-      \hline
-      \multirow{2}{*}{OPEC}      & \includegraphics[height=0.11in]{flag/flag_SA.png} & SA & Saudi Arabia & \multirow{2}{*}{1991--2011} \\
-                                 & \includegraphics[height=0.11in]{flag/flag_IR.png} & IR & Iran         &  \\
-      \hline
-      \multirow{2}{*}{LDCs}      & \includegraphics[height=0.11in]{flag/flag_TZ.png} & TZ & Tanzania & \multirow{2}{*}{1991--2011}     \\
-                                 & \includegraphics[height=0.11in]{flag/flag_ZM.png} & ZM & Zambia      & \\
-    \end{tabular}
-  \end{center}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Sources of Data}
-\label{sec:Sources_of_Data}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-To assess energy-augmented models of economic growth along the 
-coordinates of analysis outlined in Section~\ref{sec:Coordinates}, 
-historical data for economic output ($Y$), capital stock ($K$), 
-labor ($L$), and thermal energy ($Q$)   %, exergy ($X$), and useful work ($U$) 
-are required. Subsections below describe sources for and calculations 
-to obtain historical data. A final subsection presents the historical 
-data in graphical form.
-
-%++++++++++++++++++++++++++++++
-\subsection{Economic Output} 
-\label{sec:Economic_Output_Data}
-%++++++++++++++++++++++++++++++
-
-We measure economic output ($Y$) by gross domestic product (GDP). 
-GDP data in real 2005 U.S. dollars for developed countries (1980--2011) 
-and all other countries (1991--2011) was obtained from 
-the World Bank's Global Economic Prospects (GEP) database 
-\citep{WorldBankGEP:2013a}.
-
-%++++++++++++++++++++++++++++++
-\subsection{Capital Stock} 
-\label{sec:Capital_Stock_Data}
-%++++++++++++++++++++++++++++++
-
-Gross capital stock in real 2005 U.S. dollars 
-for developed countries (1980--2011) and 
-all other countries (1991--2011) was obtained from 
-the World Bank's Global Economic Prospects (GEP) database 
-\citep{WorldBankGEP:2013a}.
-
-%++++++++++++++++++++++++++++++
-\subsection{Labor and Employment}
-\label{sec:Labor_Data}
-%++++++++++++++++++++++++++++++
-
-Total employment and average hours worked per worker per year 
-for the developed nations (United States, United Kingdom, and Japan) 
-for 1980--2011 were obtained from the United States 
-\citet[Tables 6 and 7]{BLS:2013a}. Total hours worked per year was 
-calculated by multiplying total employment by average hours worked 
-per worker per year.
-
-The World Bank's World Development Indicators database 
-\citep{WorldBankWDI:2013a} provides the employment to population 
-ratio for people fifteen and older, total population, and a percentage 
-of people under fifteen for other economies (South Africa, China, Iran, 
-Saudi Arabia, Tanzania, and Zambia) for 1991--2011. The population 
-of people under fifteen years of age was subtracted from total population 
-to calculate the population of people fifteen and older. 
-Total employment was calculated by multiplying the employment to 
-population ratio of people fifteen and older by the population 
-of people fifteen and older.
-
-%++++++++++++++++++++++++++++++
-\subsection{Energy} 
-\label{sec:Energy_Data}
-%++++++++++++++++++++++++++++++
-
-To account for all energy input to an economy, we summed consumption data 
-for many energy sources, including coal, oil and petroleum products, 
-dry natural gas and natural gas plant liquids, nuclear power generation, 
-and renewable energy sources (solar, wind, geothermal, biomass/fuel wood, 
-and hydro). We also added human and animal muscle work. 
-Similar to the economic data discussed in 
-Sections~\ref{sec:Economic_Output_Data}--\ref{sec:Labor_Data}, 
-we obtained energy data for developed countries from 1980--2011. 
-For all other countries, 
-we obtained energy data for 1991--2011.
-
-Thermal energy ($Q$) for fuels (in units of TJ/year) was calculated by
-
-\begin{equation} \label{eq:thermal_energy}
-  Q_{fuel} = C_{fuel}h_{fuel}
-\end{equation}
-
-\noindent where $C_{fuel}$ is the consumption rate of the fuel 
-(in units of short tons/year for coal, barrels/year for oil and petroleum, 
-ft$^3$/year for dry natural gas and natural gas plant liquids, 
-and m$^3$/year for biomass/fuel wood) and $h_{{fuel}}$ is 
-the heat content of the fuel (in kJ/short ton for coal, kJ/barrel for oil, 
-kJ/ft$^3$ for dry natural gas and natural gas plant liquids, 
-and kJ/kg for biomass/fuel wood). Fuel wood density of 300~kg/m$^3$ 
-was taken from \citet{Ragland:2013wp} at the low end of the range 
-of density of dry wood and bark.
-
-Yearly consumption rates ($C_{fuel}$) of coal, oil and petroleum, 
-dry natural gas and natural gas plant liquids, and biofuels 
-(ethanol and biodiesel) were obtained from the \citet{EIA:2013a} 
-for all economies. Yearly average heat content data for coal, oil, 
-and natural gas and natural gas plant liquids was obtained from the 
-EIA for all economies. We used lower (net) heating values of 
-26.8~MJ/kg \citep[Table~A-27]{Cengel:2011ww} and 37.8~MJ/kg 
-\citep[Table~7.3]{Gupta:2010vg} for the heat content of ethanol 
-and corn-based biodiesel, respectively. Yearly consumption and 
-heat content data for biomass/fuel wood was obtained from the 
-``Fuelwood'' time series of the FAO Statistics Database 
-\citep{FAO:2013a}.
-
-For renewable and nuclear energy sources, yearly electricity 
-generation (in BTU/year) was available directly from 
-the \citet{EIA:2013a} for all economies, so 
-Equation~\ref{eq:thermal_energy} was unnecessary.
-
-Animal and human muscle work was estimated using an approach 
-similar to \citet{Ayres:2010ug}, using data from Warr's 
-REXS database \citep{Warr:2012a} and results from 
-\citet{Wirsenius:2000vi}. For animal work, our analysis was 
-restricted to draught animals (horses and mules). Muscle work 
-from animals ($Q_{animals}$) was calculated using
-
-\begin{equation} \label{eq:animal_muscle}
-  Q_{animals} = Q_{m,horse}N_{horses} + Q_{m,mule}N_{mules}
-\end{equation}
-
-\noindent where $Q_m$ is metabolizable energy (in kcal/day-animal) 
-and $N$ is the number of animals. Metabolizable energy values 
-($Q_{m,horses}$ = 19,110 kcal/day-horse and $Q_{m,mules}$ = 
-7,215 kcal/day-mule) were taken from \citet{Warr:2012a}. 
-$Q_m$ represents the amount of energy in the feed consumed by 
-animals for a day of work, and they are assumed constant for 
-all countries and years. The number of horses and mules for 
-each economy was taken from the ``Live Animals'' section of the 
-FAO Statistics online database \citep{FAO:2013a}.
-
-Human muscle power was calculated in a similar manner:
-
-\begin{equation} \label{eq:human_muscle}
-  Q_{workers} = Q_{m,workers} N_{workers}
-\end{equation}
-
-\noindent where the value of $Q_{m,workers}$ is the ``the amount 
-of food available for human consumption'' (i.e., at the wholesale level) 
-taken from the 
-\citet[``\texttt{Dietary~Energy~Cons.~Countries}'' tab]{FAO:2013b}. 
-The value for $N_{workers}$ was obtained from the labor time series 
-for each economy as discussed in Section~\ref{sec:Labor_Data}.
-
-\twocolumn{}
-<<Historical_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=7.5, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), and thermal energy ($q$).">>=
+<<Historical_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=3, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), and thermal energy ($q$).">>=
 historicalPlot(historicalData)
@@
 %++++++++++++++++++++++++++++++
-\subsection{Historical Data} 
-\label{sec:Historical_Data}
+\section{Results}
 %++++++++++++++++++++++++++++++
 
-Figure~\ref{fig:Historical_Graph} presents historical data, 
-including indexed values for 
-output ($y$), 
-capital stock ($k$), 
-labor ($l$), and 
-energy ($q$) 
-for 1980--2011 (developed economies) and 1991--2011 (other economies). 
-Factors of production track each other closely, 
-and high covariances among these variables can be seen in 
-Tables~\ref{tab:Covariance_US}--\ref{tab:Covariance_ZM}. 
-\authNote{Do we want to discuss the covariances?}
-
-\onecolumn{}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Parameter Estimation}
-\label{sec:Parameter_Estimation}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Point Estimates}
-Each of the economic growth models discussed in 
-Section~\ref{sec:Prod_Func_Forms} has parameters which must be estimated (fitted)
-from data for each economy (see Section~\ref{sec:Economy_Types}).
-We obtained parameter estimates by applying the method of least-squares to (potentially
-log-transformed) data using the \texttt{R} \citep{R} functions
-\texttt{lm} (for Cobb-Douglas and LINEX models) 
-and \texttt{cesEst} \citep{Henningsen:2011td} (for CES models). 
-\authNote{Need to check how CES is being fit and adjust this accordingly.}%
-
-Although the details vary from model to model, each of our three models has the general form
-\[
-y = f(t,k,l,e; \theta) + \mathrm{error} \;,
-\]
-where $\theta$ is a vector of parameters for the function $f$.
-\authNote{if we use $\theta$ this way, we need a new scaling parameter. --rjp}%
-In least squares models, parameter estimates are chosen to minimize
-\[
-\sum_{i} (y_i - f(t,k,l,e; \theta) )^2 \;.
-\]
-For the optimal parameter values $\hat \theta$, we define the 
-fitted response by
-\[
-\hat y_i = f(t_i, k_i, l_i, e_i; \hat \theta)
-\]
-and the residuals
-as the difference between the observed response and the fitted response
-\begin{equation} \label{eq:residual}
-  r_i 
-  = y_i - \hat y_i
-  = y_i - f(t,k,l,e; \hat\theta)
-\end{equation}
-The details for each of the models (including the effects of using 
-log transformations) are discussed below.
-
-%After back transforming to the natural scale of the data, the 
-%residuals have a multiplicative rather than additive affect.
-%The reflects an assumption that variability in GDP is roughly 
-%proportion to GDP rather than constant.
-
 %++++++++++++++++++++++++++++++
-\subsection{Resampling Methods}
-\label{sec:Resampling}
-%++++++++++++++++++++++++++++++
-
-Bootstrappng is a statistical resampling technique for assigning
-measures of accuracy and precision to sample estimates by measuring
-properties of an estimator when sampling from a resampling
-distribution.  Resampling distributions can be formed in a number of 
-ways in accordance with the type of data, experimental design,
-and modeling assumptions involved.  In each case, many new resamples 
-are created, each of which is a randomized version of the original sample data to 
-which the desired analysis method can be applied.  By investigating, for example,
-the variability of a parameter estimate from one resample to another,
-one can learn about the precision of the estimation method.
-\authNote{Add some references here. --rjp}
-
-In the context of linear models (regression), resamples are generally created
-by residual resampling.  In our case, we formed resamples by adding to the fitted 
-response (GDP) the product of a residual from the original model fit and 
-and random sign ($-1$ or $1$, each with probability $0.5$).  For the case of 
-Cobb-Douglas and LINEX models, this residual resampling occurs on the 
-log-transformed data.
-
-Intuitively, this method assumes that the residuals are indicative of 
-the variability (from many potential sources) inherent in the data so that
-it would be unsurprising if the residual from 
-any particular year had been observed in a different year. 
-Thus, a resampled response $\tilde Y$ can be computed as 
-\[
-\tilde Y_i' = \hat y_i \pm r_j
-\]
-where 
-\[
-r_i = y_i - \hat y_i
-\]
-both the sign ($\pm$) and the index of the residual ($j$, typically different from $i$) 
-are chosen at random (with replacement). 
-Resampling in this way has the consequence 
-that a resampled time series could have non-unity first-year GDP ($\tilde Y_1 \neq 1$),
-so a renormalization takes place using the initial GDP from the
-resampled data as the new baseline, not the observed GDP in year 1.
-
-\begin{equation} \label{eq:resample_y}
-	\tilde y_i  = \frac{\tilde Y_i'}{\tilde Y_1'}
-\end{equation}
-to obtain a resampled indexed GDP time series.
-We repeated the resampling process \Sexpr{numResamples()} times for each
-combination of growth model and country, both with and without energy when appropriate.
-
-The coefficients from the fit to a resampled time series
-(the ``resample coefficients'') will be different from the coefficients 
-obtained from the fit to historical data (the ``base coefficients'').
-When these resample coefficients are highly variable, it is an indication
-that the data do not determine the parameter estimates very precisely.
-Lack of imprecision can stem from a number of factors, most obviously
-a poor model fit, low model sensitivity to one or more parameters, 
-or correlations between parameter estimates.
-\authNote{This is not precisely true:
-Large residuals in the fit to historical data (the ``base fit'')
-are expected to produce large variation in resample coefficient values
-(when the resampling is repeated \Sexpr{numResamples()} times),
-indicating less certainty in the value
-of those coefficients. 
-Similarly, small base fit residuals are expected to produce small
-variation in resample coefficient values, indicating more-precise knowledge
-of the model coefficients.
---rjp}
-
-It is important to note that large residuals can arise from either
-(a) poor quality historical time series data, or 
-(b) a mathematical model that does not describe the underlying phenomena well.
-It is also important to note that (c) even when the residuals are small and the 
-model produces fitted values that track the observed data closely, it may
-still be difficult to estimate some or all of the model parameters precisely.
-The resampling method employed reflects all three of these potential 
-sources of uncertainty in parameter estimates.
-
-\authNote{Should the description of model fitting come before or after 
-the description of resampling?}
-
-%++++++++++++++++++++++++++++++
-\subsection{Cobb-Douglas Models}
+\subsection{Cobb-Douglas Model}
 \label{sec:CD_Parameter_Estimation}
@@
 
-The Cobb-Douglas model without energy is given by 
-Equation~\ref{eq:CD}. Equation~\ref{eq:CD} was
-reparameterized as
-
-\begin{equation} \label{eq:CD_reparam}
-  y = A k^{\alpha} l^{1-\alpha}; A = \mathrm{e}^{\lambda (t-t_0)}
-\end{equation}
-
-\noindent to ensure $\alpha + \beta = 1$ for constant returns to scale. 
-$\lambda$ and $\alpha$ were estimated by the 
-\texttt{R} \citep{R} function \texttt{nls}. 
-If the estimated value for $\alpha$ was found outside the interval $[0,1]$, 
-we set $\alpha$ to its boundary value and re-estimated $\lambda$. 
-The value of $\beta$ was found with $\beta = 1 - \alpha$.
-
-To estimate the parameters $\lambda$, $\alpha$, $\beta$, and $\gamma$ 
-in the energy-augmented Cobb-Douglas model, Equation~\ref{eq:CDe} 
-was reparameterized as
-
-\begin{equation} \label{eq:CDe_AB_reparam}
-  y = A k^{\min(a,b)} l^{|b-a|} e^{1 - \max(a,b)}; A = \mathrm{e}^{\lambda (t-t_0)}
-\end{equation}
-
-\noindent with 
-$\alpha = \min(a,b)$, 
-$\beta = |b-a|$, and 
-$\gamma = 1 - \max(a,b)$.
-The reparameterization ensures that $\alpha + \beta + \gamma = 1$,
-thereby providing constant returns to scale.
-The \texttt{R} \citep{R} function \texttt{nls} was used to estimate 
-values of $\lambda$, $a$, and $b$.
-If the fitted value for $a$ ($b$) fell outside $[0,1]$, it was 
-set equal to its boundary value and both $\lambda$ and $b$ ($a$) 
-were re-estimated.
-
-The \texttt{nls} parameter estimation algorithm can encounter convergence difficulty 
-when the optimal value for the parameter represented by the absolute value function 
-(in Equation~\ref{eq:CDe_AB_reparam}, $\beta$) 
-lies near a boundary. If the absolute value exponent caused non-convergence of the 
-\texttt{nls} function, second and, if necessary, third reparameterizations 
-were attempted:
-
-\begin{equation} \label{eq:CDe_CD_reparam}
-  y = A k^{1 - \max(c,d)} l^{\min(c,d)} e^{|d-c|}; A = \mathrm{e}^{\lambda (t-t_0)}
-\end{equation}
-
-\begin{equation} \label{eq:CDe_FG_reparam}
-  y = A k^{|g-f|} l^{1 - \max(f,g)} e^{\min(f,g)}; A = \mathrm{e}^{\lambda (t-t_0)}
-\end{equation}
-
-\noindent If none of the three reparameterizations converged, 
-the parameterization with the smallest sum of square errors ($sse$)
-was used. \ref{sec:Convergence_Resample_Models} shows the 
-fraction of unconverged models for each model type. 
-The above approach resulted in very few unconverged
-Cobb-Douglas resample models, even with \Sexpr{numResamples()} resamples.
-
-Figure~\ref{fig:CD_Ternary_Scatter_Graph} shows ternary plots 
-for $\alpha$, $\beta$, and $\gamma$ parameter values 
-for Cobb-Douglas (without and with energy) resample models.
-Each reample is shown as a gray dot on the graph. 
-The fit to historical data is shown as a gray circle.
-
-Figure~\ref{fig:CD_GDP_Spaghetti_Graph} compares predictions 
-from the Cobb-Douglas models 
-(without and with energy) to historical data.
-Historical data are shown as a black line. 
-The fit to historical data is shown as a white line.
-The gray band encompasses 95\% of the fits to resampled data.
-
-\twocolumn{}
-<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=2.9, fig.height=7.7, fig.cap="Cobb-Douglas resample model parameters.">>=
+<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=4.5, fig.height=3, fig.cap="Cobb-Douglas resample model parameters.">>=
 cdCoeffsData <- filter(coeffs_df, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iQ"))
@@
 
-<<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=8.2, fig.cap="Cobb-Douglas fitted models.">>=
+<<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=4.5, fig.height=3, fig.cap="Cobb-Douglas fitted models.">>=
 cdFittedData <- filter(fitted_df, model=="cd", nest %in% c("iK+iL", "iK+iL+iQ"))
@@
 @
-\onecolumn{}
 
-%++++++++++++++++++++++++++++++
-\subsection{CES Models}
-\label{sec:CES_Parameter_Estimation}
-%++++++++++++++++++++++++++++++
-
-The CES model without and with energy is given by 
-Equations~\ref{eq:CES}--\ref{eq:CESekl}. 
-The \texttt{R} \citep{R} package \texttt{micEconCES} 
-\citep{Henningsen:2011td} was used to estimate parameters 
-$\lambda$, $\gamma$, $\delta$, $\delta_1$, $\rho$, and $\rho_1$. 
-The \texttt{cesEst} function of \texttt{micEconCES} provides 
-several algorithm options for parameter estimation.
-The default algorithm (Levenberg-Marquardt) does not respect
-parameter constraints (see Section~\ref{sec:CES}) and, 
-in our testing, nearly always violated them, often returning
-negative values for elasticity of substitution ($\sigma$) parameters.
-Thus, we used the two fitting algorithms available in \texttt{cesEst} that
-respect coefficient constraints: \texttt{PORT} and \texttt{L-BFGS-B}.
-
-Our CES parameter estimation algorithm starts with an eleven-value grid search
-in $\rho$ and $\rho_1$ (9, 2, 1, 0.43, 0.25, 0.1, -0.1, -0.5, -0.75, -0.9, -0.99),
-which corresponds to $\sigma$ and $\sigma_1$ values of
-0.1, 0.33, 0.5, 0.7, 0.8, 0.9, 1.11, 2, 4, 10, and 100, respectively.
-During the grid search, values of $\rho$ and $\rho_1$ are fixed,
-and values of $\lambda$, $\gamma$, $\delta$, and $\delta_1$ are estimated 
-by gradient search with the \texttt{PORT} and \texttt{L-BFGS-B} algorithms.
-In all, 121 gradient searches in $\lambda$, $\gamma$, $\delta$, and $\delta_1$
-at grid points representing all combinations of $\rho$ and $\rho_1$ are attempted.
-During the grid search portion of our algorithm, starting values for the free parameters
-are $\lambda$ = 0.015/year, $\delta$ = 0.5, $\delta_1$ = 0.5, 
-and $\gamma$ is set to a value such that the mean of the residuals is zero.
-
-Next, a gradient search (using both \texttt{PORT} and \texttt{L-BFGS-B}) 
-is attempted wherein all fitting parameters 
-($\lambda$, $\gamma$, $\delta$, $\delta_1$, $\rho$, and $\rho_1$)
-are allowed to float. 
-The start values for fitting parameters are taken from 
-the grid search fit that provided the lowest $sse$.
-
-If resampled data are being fitted, a prior fit to historical data is available.
-In the final step of our algorithm, 
-a gradient search (using both \texttt{PORT} and \texttt{L-BFGS-B})
-uses coefficients from the best 
-fit to historical data as its starting point. 
-In this final gradient search, all model parameters 
-($\lambda$, $\gamma$, $\delta$, $\delta_1$, $\rho$, and $\rho_1$)
-are considered free parameters.
-
-The fit with lowest $sse$ of all above trials is deemed the winner,
-and its fitting parameters are used as the model.
-
-\citet{Henningsen:2011td}, 
-in their detailed analysis of \citet{Kemfert:1998vd}, found that
-
-\begin{quote}
-\ldots the Levenberg-Marquardt and the \texttt{PORT} algorithms 
-are---at least in this study---most likely to find the 
-coefficients that give the best fit to the model, 
-where the PORT algorithm can be used to restrict the estimates 
-to the economically meaningful region.
-\end{quote}
-
-In our testing, we found that to be mostly true. 
-\texttt{PORT} nearly always provided lower
-$sse$ than \texttt{L-BFGS-B}, despite the fact that 
-\texttt{L-BFGS-B} often reports convergence
-and \texttt{PORT} does not for the same data
-(i.e., for the same $y$, $k$, $l$, and $e$ data).
-
-Coefficients for each resampled CES model for all countries and all nests
-are shown in 
-Figures~\ref{fig:CES_lambda_gamma_graph}--\ref{fig:CES_sigma_delta_graph}. 
-The crosshair on each graph shows the location 
-of the fit to historical data. 
-In Figures~\ref{fig:CES_sigma1_delta1_graph} and~\ref{fig:CES_sigma_delta_graph},
-the bottom of the vertical axis represents $\sigma = 0$.
-The top of the vertical axis represents $\sigma = \infty$.
-
-<<CES_lambda_gamma_graph, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models.">>=
-cesCoeffsData <- filter(coeffs_df, model=="ces", nestStr %in% c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"))
-standardScatterPlot(data=cesCoeffsData, mapping=aes(gamma_coef, lambda), facet_formula=country~nest, alpha=0.05) +
-    scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
-    scale_y_continuous(breaks=c(0, 0.025, 0.05, 0.075)) +    
-    labs(x=expression(gamma), y=expression(lambda))
-@
-
-<<CES_sigma1_delta1_graph, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models.">>=
-standardScatterPlot(data=cesCoeffsData, mapping=aes(delta_1, sigma_1), facet_formula=country~nest, alpha=0.05) +
-    coord_trans(y="sigma") +
-    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-    labs(x=expression(delta[1]), y=expression(sigma[1]))
-@
-
-<<CES_sigma_delta_graph, fig.pos="H", fig.align='center', fig.width=4.5, fig.height=7, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models.">>=
-standardScatterPlot(data=subset(cesCoeffsData, nestStr != "iK+iL"),
-                    mapping=aes(delta, sigma), facet_formula=country~nest, alpha=0.05) +
-    coord_trans(y="sigma") +
-    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-    labs(x=expression(delta), y=expression(sigma))
-@
-
-We can develop pseudo $\alpha$, $\beta$, and $\gamma$ parameters 
-for the CES model, based on values of $\delta$ and $\delta_1$.
-Table~\ref{tab:CES_abg_equations} shows the permuted equations for each CES nesting.
-
-\begin{table} \caption{Equations for $\alpha$, $\beta$, and $\gamma$ for the various CES nestings.} 
-\label{tab:CES_abg_equations} 
-  \begin{center}
-    \begin{tabular}{c c c c c} 
-      Nesting    & Equation        & $\alpha$                & $\beta$                 & $\gamma$                \\
-      \hline
-      ($kl$)     & \ref{eq:CES}    & $\delta_1$              & $1 - \delta_1$          & 0                       \\
-      ($kl$)$e$  & \ref{eq:CESkle} & $\delta \delta_1$       & $\delta (1 - \delta_1)$ & $1 - \delta$            \\   
-      ($le$)$k$  & \ref{eq:CESlek} & $1 - \delta$            & $\delta \delta_1$       & $\delta (1 - \delta_1)$ \\
-      ($ek$)$l$  & \ref{eq:CESekl} & $\delta (1 - \delta_1)$ & $1 - \delta$            & $\delta \delta_1$       \\
-    \end{tabular}
-  \end{center}
-\end{table}
-
-Figure~\ref{fig:CES_ternary_graph} shows 
-$\alpha$, $\beta$, and $\gamma$ parameters for the CES model for all nests and countries.
-Figure~\ref{fig:CES_ternary_graph} is comparable to
-the ternary graph for the Cobb-Douglas models, 
-Figure~\ref{fig:CD_Ternary_Scatter_Graph}.
-
-<<CES_ternary_graph, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models.">>=
-standardTriPlot(data=cesCoeffsData, facet_formula=country~nest)
-@
-
-Figure~\ref{fig:CES_Spaghetti_Graph} compares CES model predictions 
-to historical data for all nestings. 
-Historical data are shown as a black line. 
-The fit to historical data is shown as a white line.
-The gray band encompasses 95\% of the fits to resampled data.
-
-<<CES_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models.">>=
-cesFittedData <- filter(fitted_df, model=="ces", nest %in% c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"))
-spaghettiPlot(data=cesFittedData, facet_formula=Country~nest, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1980=1 or 1991=1)")
-@
-
-Figure~\ref{fig:CES_Spaghetti_Graph_CN} shows details of the resample fits for China with the (kl)e nesting.
-Again, historical data are shown as a black line. 
-The fit to historical data is shown as a white line.
-The gray band encompasses 95\% of the fits to resampled data.
-
-<<CES_Spaghetti_Graph_CN, fig.pos="H", fig.align='center', fig.width=maxWidth, fig.height=maxHeight, fig.cap="CES fitted models for China with the (kl)e nesting.">>=
-spaghettiPlot(data=subset(cesFittedData, Country=="CN" & nest=="iK+iL+iQ"), level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1980 = 1 or 1991 = 1")
-@
-
-%++++++++++++++++++++++++++++++
-\subsection{LINEX Models}
-\label{sec:LINEX_Parameter_Estimation}
-%++++++++++++++++++++++++++++++
-
-The LINEX model is given in Equation~\ref{eq:LINEX}. 
-If the fitting algorithm drives $a_0 \rightarrow 0$, 
-any changes to $c_t$ have no effect on $sse$, 
-leading the fitting algorithm to report non-convergence. 
-To avoid this problem, we transformed the LINEX model into
-
-\begin{equation} \label{eq:LINEX_transformed}
-  y = Ae; 
-  A = \mathrm{e}^{\left[2 a_0 \left(1 - \frac{1}{\rho_k} \right) 
-    + a_1 \left(\vphantom{\frac{1}{\rho_k}}\rho_l - 1 \right)\right]},
-\end{equation}
-
-\noindent where $a_1 \equiv a_0 c_t$. 
-We used the \texttt{nls} function in \texttt{R}
-\citep{R} to estimate least-squares values for $a_0$ and $a_1$ in 
-Equation~\ref{eq:LINEX_transformed}. We recovered
-a value for $c_t$ with $c_t = a_1 / a_0$. The reparameterization
-shown in Equation~\ref{eq:LINEX_transformed} reduced the number of 
-unconverged resample fits to nearly zero: 
-The largest fraction of unconverged resample fits is found 
-for Zambia (ZM) with thermal energy ($q$), where
-\Sexpr{fracUnconvergedResampleFits(modelType="linex", countryAbbrev="ZM", energyType="Q", baseResample=baseResample)*100}\%
-of the resample fits did not converge. 
-(See Table~\ref{tab:frac_unconverged_models}.)
-
-Figure~\ref{fig:LINEXq_Resample_Graph}
-shows the coefficients estimated from resampled data.
-
-Figure~\ref{fig:LINEX_Spaghetti_Graph} compares LINEX model predictions to historical data.
-Historical data are shown as a black line. 
-The fit to historical data is shown as a white line.
-The gray band encompasses 95\% of the fits to resampled data.
-
-\twocolumn{}
-<<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7, fig.cap="LINEX model (with energy) resampling results.">>=
-linexCoeffsData <- filter(coeffs_df, model=="linex", energy=="iQ")
-standardScatterPlot(data=linexCoeffsData, aes(a_0, c_t), facet_formula=country~energy, alpha=0.05) +
-    labs(x=expression(a[0]), y=expression(c[t])) +
-     scale_x_continuous(limits=c(-1, 2), breaks=c(-1, 0, 1.0, 2.0)) +
-     scale_y_continuous(limits=c(0, 10), breaks=c(0, 5, 10))
-@
-
-<<LINEX_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7.1, fig.cap="LINEX fitted models.">>=
-linexFittedData <- filter(fitted_df, model=="linex", energy=="iQ")
-spaghettiPlot(data=linexFittedData, facet_formula=Country~energy, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1980=1 or 1991=1)")
-@
-\onecolumn{}
-
-%++++++++++++++++++++++++++++++
-\subsection{Parameter Estimation Summary}
-\label{sec:Parameter_Estimation_Summary}
-%++++++++++++++++++++++++++++++
-
-**** Include a table here of important values. 
-Include a table of convergence? (In appendix?)
-Martin to suggest the form of this table after working 
-on the interpretation for a while. ****
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion of Results}
-\label{sec:Discussion_of_Results}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Drive towards new insights from our stats tested comparative approach.
-
-**** Notes for interpretation of results ****
-
-R$^2$ not a good measure. 
-Limited insights are obtained from $t$ and $p$ values, 
-especially on PFs that have parameters with constraints (CD, CES).
-
-We found that we are able to maintain good fits while respecting theoretical foundations
-of the models (i.e., respect parameter constraints). No need to relax parameter constraints
-and, thereby, contradict micro foundations.
-
-CD assumes $\sigma_1 = 1$. CES doesn't assume a value for $\sigma_1$. 
-The $\sigma_1$ vs. $\delta_1$ graphs for CES without energy often have 
-two frequent values for $\sigma_1$.  One of those frequent values is
-nearer to $\sigma_1 = 1$. When CD and CES without energy do not agree on 
-share values (CD: $\alpha$ compared to $\beta$, CES: $\delta_1$) for the 
-base curve fit (red dot), they do agree for the data that clusters near 
-$\sigma_1 = 1$ for the CES fits.
-
-Country interpretation
-
-Comparison Cobb Douglas and CES results.
-
-%++++++++++++++++++++++++++++++
-\subsection{United States} 
-\label{sec:InterpUS}
-%++++++++++++++++++++++++++++++
-
-CD: Energy is unnecessary
-
-CES with $q$:
-
-($kl$): $\delta_1 = 0.3, \sigma_1 = 0.8$. $k$ is less necessary. 
-Complements, but close to substitutes.
-signal of substitutability in the spread.
-
-($kl$)$e$: energy is unnec ($\delta = 1$). 
-$\delta_1 = 0.45$: $k$ and $l$ are about equally necessary.
-$\sigma_1 = 0.8$: $k$ and $l$ are slight complements. 
-Spread on $0.25 < \sigma_1 < \infty$, signalling 
-possibilities of substitution.
-
-($el$)$k$: energy is unnec. ($\delta_1$ is 0);
-
-($le$)$k$ no indication
-Relative consistent signal that energy is unnec.
-
-CES with $u$:
-
-($kl$)$e$: $\delta = 1$, signalling $e$ unnecessary. 
-$\sigma = 0.8$, indicating clost to substitutability,
-but still complementary. 
-$\delta_1 = 0.25$, with large spread. not strong for $k$.
-$\sigma_1 \rightarrow \infty$, but with large spread from 0.2 upward. 
-Signals complementarity between $k$ and $l$.
-
-%++++++++++++++++++++++++++++++
-\subsection{United Kingdom} 
-\label{sec:InterpUK}
-%++++++++++++++++++++++++++++++
-
-CD: Capital is unnec.
-
-CES with $q$:
-
-($kl$): $\delta_1 = 0.7, \sigma_1 = 0.35$. 
-$kl$ complementary, $k$ is more important, because $\delta_1 > 0.5$. 
-Large spread on $\delta_1$. 
-Complementary signal is consistent, however.
-
-($kl$)$e$: energy is unnec ($\delta = 1$). 
-$\delta_1 = 0.25$, $k$ is less necessary. 
-$\sigma_1 \rightarrow \infty$, giving strong $kl$ substitutability signal.
-
-($le$)$k$ capital is unnec. ($\delta = 1$);
-
-($ek$)$l$ ($\delta_1 = 0$) energy is unnec.
-
-Thus, inconsistent results, possibly look at different time series 
-as massive changes in economic policy in Uk economic history
-
-CES with $u$:
-
-($kl$)$e$: $\delta = 1$, $u$ is unnecessary. 
-$\sigma = 0.8$, approache complementarity between $kl$ and $e$.
-$\delta_1 = 0.1$. 
-$\sigma_1 \rightarrow \infty$, indicating substitutability between $k$ and $l$.
-
-%++++++++++++++++++++++++++++++
-\subsection{Japan} 
-\label{sec:InterpJP}
-%++++++++++++++++++++++++++++++
-
-CD: energy is unnec.
-
-CES with $q$:
-
-($kl$): $\delta_1 = 0.7, \sigma_1 = 0.25$. Very little scatter. Both are well-known. 
-$l$ is close to unnecessary. $k$ and $l$ are complements.
-
-($kl$)$e$: no indications, all are important. $\delta = 0.6$, both $kl$ and $e$ are necessary.
-$0.5 < \delta < 1$.
-$\sigma=0.1$ signalling complementarity betwen $kl$ and $e$.
-$\delta_1 = 0.8$ signalling $l$ is almost unnecessary. 
-$\sigma_1 = 0.1$, signalling complementarity 
-between $k$ and $l$.
-
-($le$)$k$: no indications, all are important.
-
-($ek$)$l$: no indications, all are important.
-
-weak signal that labour is less necessary 
-(($kl$)$e$ $delta_1 = 0.86$ and ($ek$)$l$ $\delta = 0.89$)
-
-Thus, inconsistent results.
-
-CES with $u$:
-
-($kl$)$e$: $\delta = 0.6, \sigma = 0.4$. Complementarity between $kl$ and $e$.
-$\delta_1 = 1$, indicating $l$ unnecessary. $\sigma_1 = 0.1$, indicating complementarity
-between $k$ and $l$. Need only one of $k$ or $l$ in your equation, but they are
-complemetary! You need one to have the other.
-
-%++++++++++++++++++++++++++++++
-\subsection{China} 
-\label{sec:InterpCN}
-%++++++++++++++++++++++++++++++
-
-CD: energy not necessary, capital less necessary
-
-CES with $q$:
-
-($kl$): $\delta_1 = 0.3$, so $k$ is getting close to unnecessary. $\sigma_1 = 1.25$.
-$k$ and $l$ are substitutes. Large spread in $\delta_1$ from 0.1 to 1.0. Large spread in
-$\sigma_1$, but most points have $\sigma_1 > 1$.
-
-($kl$)$e$: $\delta = 0.8$. however, strong signal at $0.8 < \delta < 1$, 
-signalling that energy is less necessary. $0.5 < \delta < 1$. $\sigma = 0.5$, 
-signalling complementarity between $kl$ and $e$. 
-$\delta_1 = 1$, signalling that $l$ is unnecessary. $\sigma_1 = 0.1$, signalling
-that $k$ and $l$ are complementary. Both $\delta_1$ and $\sigma_1$ have large spreads, 
-so our confidence in these results is low.
-
-($le$)$k$: labour is unnnec ($\delta_1 = 0$);
-
-($ek$)$l$ energy is unnec. ($\delta_1 \rightarrow 0$)
-
-Strong signal that energy is unnec, but the labour and capital signals are conflicting
-
-%++++++++++++++++++++++++++++++
-\subsection{South Africa} 
-\label{sec:InterpZA}
-%++++++++++++++++++++++++++++++
-
-CD: Labour is unnec.
-
-CES with $q$:
-
-($kl$): $\delta_1 = 0.35, \sigma_1 = 0.8$. $k$ is relatively less necessary. $k$ and $l$ 
-are complements but relatively close to being substitutes. Spread is tight between 
-$0.25 < \delta_1 < 0.5$ and $\sigma_1$ is consistently complementary 
-between $0.1 < \sigma_1 < 0.8$.
-
-($kl$)$e$: labour is unnec. ($\delta_1 = 1$). $\delta = 0.25$, signalling complemtarity 
-between $kl$ and $e$, but large spread from 0 to 1. $\sigma$ and $\sigma_1$ are both 0, 
-indicating perfect complements betwen $kl$ and $e$ and between $k$ and $l$.
-
-($le$)$k$ labour is unnec. ($\delta_1 = 0$);
-
-($ek$)$l$ labour is unnec. ($\delta = 1$)
-
-Consistent signal that labour is unnec.
-
-%++++++++++++++++++++++++++++++
-\subsection{Saudi Arabia} 
-\label{sec:InterpSA}
-%++++++++++++++++++++++++++++++
-
-CD: no indications
-
-CES with $q$:
-
-($kl$): $\delta_1 = 0.85$. $l$ is unnecessary. 
-$\sigma_1 = 0.1$ indicating strong complementarity between 
-$k$ and $l$. Spread of $0.15 < \delta_1 < 1$. 
-$0 < \sigma_1 < 0.8$, signalling complementarity.
-
-($kl$)$e$: $\delta = 0.6$, $e$ is less necessary (weak signal). 
-Big spread on $\delta$ between 0 and 0.8.
-$\sigma = 0.1$ indicating complementarity between $kl$ and $e$. $\delta_1 = 0.8$ 
-(with large spread between 0.3 and 1), labor is less necessary.
-$\sigma_1 = 0.1$: very complementary between $k$ and $l$.
-
-($le$)$k$:
-
-($ek$)$l$: weak signal that labour is unnec ($\delta = 0.93$)
-
-Almost consistent signal that no indocations.
-
-%++++++++++++++++++++++++++++++
-\subsection{Iran} 
-\label{sec:InterpIR}
-%++++++++++++++++++++++++++++++
-
-CD: energy is unnec.
-
-CES with $q$:
-
-($kl$): $\delta_1 = 0.3$. Spread $0 < \delta_1 < 0.7$. $0 < \sigma_1 < 0.8$. $\sigma_1 = 0$. 
-Strong complementarity. $k$ is less necessary compared to $l$.
-
-($kl$)$e$: energy is unnec ($\delta=1$). 
-$\sigma = 0.75$ indicating complementarity between $kl$ and $e$, approaching substitutibility.
-$\delta_1 = 0.3, \sigma_1 = 0$ indicating strong perfect complementarity between $k$ and $l$.
-
-($le$)$k$: energy is unnec. ($\delta_1=1$);
-
-($ek$)$l$: labour is unnec. ($\delta=1$)
-
-%++++++++++++++++++++++++++++++
-\subsection{Tanzania} 
-\label{sec:InterpTZ}
-%++++++++++++++++++++++++++++++
-
-CD: labour in unnec.
-
-CES with $q$:
-
-($kl$): $\delta_1 = 0.8$ $0.3 < \delta_1 < 1$ signalling labor is less necessary.
-$\sigma_1 = 0.1$ $0 < \sigma_1 < 0.8$, signalling complementary $k$ and $l$.
-
-($kl$)$e$: labour is unnec ($\delta_1=0.97$). 
-$\delta = 0.45$, so $kl$ and $e$ both necessary, but 
-$\sigma \rightarrow \infty$, so $kl$ and $e$ has perfect substitutibility.
-$\sigma_1 = 0.1$, so $k$ and $l$ are perfect complements. 
-Spread on $\delta$ is large (0.2 to 1).
-So, we are unsure about the value of $\delta$.
-
-($le$)$k$: weak signal that energy is unnec. ($\delta_1=0.92$); 
-very weal signal capital is unnec ($\delta=0.84$);
-
-($ek$)$l$: labour is unnec. $\delta=0.96$
-
-Consistent signal that labour is unnec, with exception of one nesting.
-
-%++++++++++++++++++++++++++++++
-\subsection{Zambia} 
-\label{sec:InterpZM}
-%++++++++++++++++++++++++++++++
-
-CD: labour is unnec; energy is unnec.
-
-CES with $q$:
-
-($kl$): $\delta_1 = 1$: $l$ is unnecessary. 
-$0.5 < \delta_1 < 1$. $\sigma_1 = 0.8$ without any 
-noticeable spread indicating complemetary.
-
-($kl$)$e$: labour is unnec. ($\delta_1=1$). 
-$\delta = 0.6$, $kl$ and $e$ are both necessary. 
-$\sigma \rightarrow \infty$, signalling substitutability between $kl$ and $e$. 
-$\sigma_1 = 0.8$ with very large spread between 0 and 2. 
-Approaching substitutability between $k$ and $l$ and perfect substitutibility
-between $kl$ and $e$. Very little certainty here.
-
-($le$)$k$: ($\delta_1=0$);
-
-($ek$)$l$: labour is unnec. ($\delta=1$)
-
-Consistent signal that labour is unnec.
-
-Discussion of results:
-
-How to get better consistent signals?
-
-\begin{itemize}
-\item{Use CD as starting points and do CES convergence on that basis.}
-\item{Do scatterplots to get range of uncertainty inputs, then re-interpret. 
-$\delta$ against $\sigma$ plots, as well as $\delta_1$ and $\sigma_1$ plots.}
-\end{itemize}
-
-Thus, to do the fitting well we need to understand:
-\begin{itemize}
-\item{nesting}
-\item{algorithm}
-\item{starting values}
-\end{itemize}
-esp. for CES.
-
-(Maybe illustrate with one case study such as China what implications are).
-
-How do we compare with LINEX results?
-
-CES is a broader specification of CD, LINEX is not. 
-In LINEX neither $\delta$s nor $\sigma$s are generated. 
-Only efficiency terms are generated in LINEX, 
-thus in other words economic growth is only possible by increased efficiency. 
-The efficiency of using energy is driven by capital stock. 
-The objective/growth engine is to increase capital 
-at a rate that is faster then growth in labour and energy.  
-Increasing labour relative to energy gives a muted benefit. 
-LINEX derived for Germany: only really applicable when energy and capital are complements.
-
-Discussion in relation to other papers. 
-Problems with other papers:
-\begin{itemize}
-\item{If not giving you all parameters}
-\item{Not explain nesting approach}
-\item{No CI on data}
-\end{itemize}
-
-Economic interpretation (revisit after scatterplot information)
-Developed economies: Capital and energy is complementary (US: labour and energy substitutable)
-NICs: Capital and energy complementary, but labour and energy more substitutable
-OPEC: Labour and energy complementary (mixed results on capital and energy)
-LDCs: Labour and energy complementary, Capital and energy perfect substitutes.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusion}
-\label{sec:Conclusion}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Future Work}
-\label{sec:FutureWork}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Acknowledgements}
-\label{sec:Acknowledgements}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Funding for Caleb Reese and Lucas Timmer was provided 
-by the Jack and Lois Kuipers Applied Mathematics Endowment and 
-the Calvin College Alumni Association. 
-Partial support for Matthew Kuperus Heun was 
-provided by a Calvin College Research Followship. 
-Partial funding for Martin de Wit was provided 
-by the South African National Research Foundation (NRF).\footnote{Any opinion, 
-findings, and conclusions or recommendations expressed herein are those 
-of the authors, and, therefore, NRF does not accept any liability in regard thereto.} 
-The authors are grateful to Benjamin S. Warr (INSEAD) for providing 
-the REXS database \citep{Warr:2012a}. 
-The authors thank Loren L. Heun (Western Michigan University) 
-for insightful critique of the statistical analyses presented herein.
-The computations in this paper were accomplished using \url{http://dahl.calvin.edu}, 
-a Beowulf cluster built with support from the National Science Foundation's 
-Major Research Instrumentation and Cyber Infrastructure programs, 
-grant number OCI-0722819.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Reproducible Research}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-In the spirit of Reproducible Research \citep{Gandrud:2013vx}, 
-all data, spreadsheets, \texttt{R} code \citep{R}, and other materials 
-associated with this paper can be found at\\*
-\protect\url{https://github.com/MatthewHeun/Econ-Growth-R-Analysis}.
-
-%% The Appendices part is started with the command \appendix;
-%% appendix sections are then done as normal sections
-%% \appendix
-%% \section{}
-%% \label{}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\appendix
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Covariance Tables}
-\label{sec:Covariance_Tables}
-\setcounter{table}{0} % Restarts table number counter at 0 in this section.
-\setcounter{figure}{0} % Restarts figure number counter at 0 in this section.
-\setcounter{equation}{0} % Restarts equation counter to 0 in this section.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Convergence of Resample Models}
-\label{sec:Convergence_Resample_Models}
-\setcounter{table}{0} % Restarts table number counter at 0 in this section.
-\setcounter{figure}{0} % Restarts figure number counter at 0 in this section.
-\setcounter{equation}{0} % Restarts equation counter to 0 in this section.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The following table shows the fraction of resample models 
-that did not achieve convergence when estimating model parameters.
-
-<<Unconverged_Frac_Table, results='asis'>>=
-# printFracUnconvergedXtable()
-  data <- fracUnconvergedResampleFitsAll(baseResample=baseResample)
-  dataXtable <- xtable(x=data, 
-                       caption="Fraction of unconverged resample models", 
-                       label="tab:frac_unconverged_models",
-                       digits = 3,
-                       align = "rl|cc|ccccccccc") #Sets alignment of the numbers in the columns)
-  print(dataXtable, 
-        caption.placement="top", 
-        size="\\tiny",
-        table.placement="H",
-        include.rownames=FALSE)
-@
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{95\% Confidence Intervals}
-\label{sec:Confidence_Intervals}
-\setcounter{table}{0} % Restarts table number counter at 0 in this section.
-\setcounter{figure}{0} % Restarts figure number counter at 0 in this section.
-\setcounter{equation}{0} % Restarts equation counter to 0 in this section.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Resample coefficients in the scatter plots 
-can be represented as 95\% confidence intervals 
-by finding the parameter values associated with 
-the middle 95\% of the data for each model parameter.
-This appendix provides tables and graphs of the 95\% confidence
-intervals on fitted model parameters.
-
-%++++++++++++++++++++++++++++++
-\subsection{Cobb-Douglas Models}
-%++++++++++++++++++++++++++++++
-
-The 95\% confidence intervals associated with 
-the without-energy column of Figure~\ref{fig:CD_Ternary_Scatter_Graph} 
-are shown in Table~\ref{tab:CD_Parameters_No_Energy}.
-
-<<CD_Params_Table, results='asis'>>=
-printCDParamsTable(energyType="none", baseResample=baseResample)    #Without energy
-@
-
-The data in Table~\ref{tab:CD_Parameters_No_Energy} are plotted in
-Figure~\ref{fig:CD_Params_Graph}.
-
-<<CD_Params_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.cap="Cobb-Douglas (without energy) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createCDParamsGraph(energyType="none", baseResample=baseResample)
-@
-
-The 95\% confidence intervals associated with 
-the with-energy column of Figure~\ref{fig:CD_Ternary_Scatter_Graph} 
-are shown in Table~\ref{tab:CD_Parameters_With_Q}
-and Figure~\ref{fig:CDq_Params_Graph}.
-
-<<CDq_Params_Table, results='asis'>>=
-printCDParamsTable(energyType="Q", baseResample=baseResample)   #With energy
-@
-
-<<CDq_Params_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.cap="Cobb-Douglas (with energy) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createCDParamsGraph(energyType="Q", baseResample=baseResample)
-@
-
-%++++++++++++++++++++++++++++++
-\subsection{CES Models}
-%++++++++++++++++++++++++++++++
-
-The 95\% confidence intervals associated 
-with ($kl$) nest columns of 
-Figures~\ref{fig:CES_lambda_gamma_graph}--\ref{fig:CES_ternary_graph}
-are shown in Tables~\ref{tab:CES_Parameters_A} 
-and \ref{tab:CES_Parameters_B} and Figure~\ref{fig:CES_Params_Graph}.
-
-<<CES_Params_Table, results='asis'>>=
-print(cesParamsTableA(energyType="none", nest="(kl)", baseResample=baseResample), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-print(cesParamsTableB(energyType="none", nest="(kl)", baseResample=baseResample), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-@
-
-<<CES_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (without energy, ($kl$) nesting) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createCESParamsGraph(energyType="none", nest="(kl)", baseResample=baseResample)
-@
-
-The 95\% confidence intervals associated 
-with ($kl$)$e$ nest columns of 
-Figures~\ref{fig:CES_lambda_gamma_graph}--\ref{fig:CES_ternary_graph}
-are shown in Tables~\ref{tab:CES_Parameters_A_With_Q_(kl)e} and 
-\ref{tab:CES_Parameters_B_With_Q_(kl)e} and Figure~\ref{fig:CESq_Params_Graph_kle}.
-
-<<CESq_Params_Table_kle, results='asis'>>=
-print(cesParamsTableA(energyType="Q", nest="(kl)e", baseResample=baseResample), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-print(cesParamsTableB(energyType="Q", nest="(kl)e", baseResample=baseResample), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-
-@
-
-<<CESq_Params_Graph_kle, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with energy, ($kl$)$e$ nesting) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createCESParamsGraph(energyType="Q", nest="(kl)e", baseResample=baseResample)
-@
-
-The 95\% confidence intervals associated 
-with ($le$)$k$ nest columns of 
-Figures~\ref{fig:CES_lambda_gamma_graph}--\ref{fig:CES_ternary_graph}
-are shown in Tables~\ref{tab:CES_Parameters_A_With_Q_(le)k} and 
-\ref{tab:CES_Parameters_B_With_Q_(le)k} and Figure~\ref{fig:CESq_Params_Graph_lek}.
-
-<<CESq_Params_Table_lek, results='asis'>>=
-print(cesParamsTableA(energyType="Q", nest="(le)k", baseResample=baseResample), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-print(cesParamsTableB(energyType="Q", nest="(le)k", baseResample=baseResample), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-
-@
-
-<<CESq_Params_Graph_lek, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with energy, ($le$)$k$ nesting) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createCESParamsGraph(energyType="Q", nest="(le)k", baseResample=baseResample)
-@
-
-The 95\% confidence intervals associated 
-with ($ek$)$l$ nest columns of 
-Figures~\ref{fig:CES_lambda_gamma_graph}--\ref{fig:CES_ternary_graph}
-are shown in Tables~\ref{tab:CES_Parameters_A_With_Q_(ek)l} and 
-\ref{tab:CES_Parameters_B_With_Q_(ek)l} and Figure~\ref{fig:CESq_Params_Graph_ekl}.
-
-<<CESq_Params_Table_ekl, results='asis'>>=
-print(cesParamsTableA(energyType="Q", nest="(ek)l", baseResample=baseResample), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-print(cesParamsTableB(energyType="Q", nest="(ek)l", baseResample=baseResample), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-
-@
-
-<<CESq_Params_Graph_ekl, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with energy, ($ek$)$l$ nesting) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createCESParamsGraph(energyType="Q", nest="(ek)l", baseResample=baseResample)
-@
-
-%++++++++++++++++++++++++++++++
-\subsection{LINEX Model}
-%++++++++++++++++++++++++++++++
-
-The 95\% confidence intervals associated with Figure~\ref{fig:LINEXq_Resample_Graph}
-are shown in Table~\ref{tab:LINEX_Parameters_With_Q} and Figure~\ref{fig:LINEXq_Params_Graph}.
-
-<<LINEX_Params_Table, results='asis'>>=
-print(linexParamsTable(energyType="Q", baseResample=baseResample), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-@
-
-<<LINEXq_Params_Graph, fig.pos="H", fig.width=linexParameterGraphWidth, fig.height=linexParameterGraphHeight, fig.cap="LINEX model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
-createLINEXParamsGraph(energyType="Q", baseResample=baseResample)
-@
-
-%% References
-%%
-%% Following citation commands can be used in the body text:
-%%
-%%  \citet{key}  ==>>  Jones et al. (1990)
-%%  \citep{key}  ==>>  (Jones et al., 1990)
-%%
-%% Multiple citations as normal:
-%% \citep{key1,key2}         ==>> (Jones et al., 1990; Smith, 1989)
-%%                            or  (Jones et al., 1990, 1991)
-%%                            or  (Jones et al., 1990a,b)
-%% \cite{key} is the equivalent of \citet{key} in author-year mode
-%%
-%% Full author lists may be forced with \citet* or \citep*, e.g.
-%%   \citep*{key}            ==>> (Jones, Baker, and Williams, 1990)
-%%
-%% Optional notes as:
-%%   \citep[chap. 2]{key}    ==>> (Jones et al., 1990, chap. 2)
-%%   \citep[e.g.,][]{key}    ==>> (e.g., Jones et al., 1990)
-%%   \citep[see][pg. 34]{key}==>> (see Jones et al., 1990, pg. 34)
-%%  (Note: in standard LaTeX, only one note is allowed, after the ref.
-%%   Here, one note is like the standard, two make pre- and post-notes.)
-%%
-%%   \citealt{key}          ==>> Jones et al. 1990
-%%   \citealt*{key}         ==>> Jones, Baker, and Williams 1990
-%%   \citealp{key}          ==>> Jones et al., 1990
-%%   \citealp*{key}         ==>> Jones, Baker, and Williams, 1990
-%%
-%% Additional citation possibilities
-%%   \citeauthor{key}       ==>> Jones et al.
-%%   \citeauthor*{key}      ==>> Jones, Baker, and Williams
-%%   \citeyear{key}         ==>> 1990
-%%   \citeyearpar{key}      ==>> (1990)
-%%   \citetext{priv. comm.} ==>> (priv. comm.)
-%%   \citenum{key}          ==>> 11 [non-superscripted]
-%% Note: full author lists depends on whether the bib style supports them;
-%%       if not, the abbreviated list is printed even when full requested.
-%%
-%% For names like della Robbia at the start of a sentence, use
-%%   \Citet{dRob98}         ==>> Della Robbia (1998)
-%%   \Citep{dRob98}         ==>> (Della Robbia, 1998)
-%%   \Citeauthor{dRob98}    ==>> Della Robbia
-
-%% References with bibTeX database:
-
-\bibliographystyle{model2-names}
-%%\bibliography{<your-bib-database>}
-\bibliography{EconGrowth.bib}
-
-%% Authors are advised to submit their bibtex database files. They are
-%% requested to list a bibtex style file in the manuscript if they do
-%% not want to use model2-names.bst.
-
-%% References without bibTeX database:
-
-% \begin{thebibliography}{00}
-
-%% \bibitem must have one of the following forms:
-%%   \bibitem[Jones et al.(1990)]{key}...
-%%   \bibitem[Jones et al.(1990)Jones, Baker, and Williams]{key}...
-%%   \bibitem[Jones et al., 1990]{key}...
-%%   \bibitem[\protect\citeauthoryear{Jones, Baker, and Williams}{Jones
-%%       et al.}{1990}]{key}...
-%%   \bibitem[\protect\citeauthoryear{Jones et al.}{1990}]{key}...
-%%   \bibitem[\protect\astroncite{Jones et al.}{1990}]{key}...
-%%   \bibitem[\protect\citename{Jones et al., }1990]{key}...
-%%   \harvarditem[Jones et al.]{Jones, Baker, and Williams}{1990}{key}...
-%%
-
-% \bibitem[ ()]{}
-
-% \end{thebibliography}
+% \bibliographystyle{model2-names}
+\bibliographystyle{plainnat}
+\bibliography{ZAGrowth_JAE.bib}
 
 \end{document}
-
-%%
-%% End of file `elsarticle-template-2-harv.tex'.

### 2014-05-31 Article_JAE_2014/ZAGrowth_JAE.Rnw
Added additional graphs to the ZA JAE paper.

@@
 \usepackage[shownotes]{authNote}
+\usepackage{float}      % Allows precise positioning of tables and figures within the text
 
@@
 
-\citet{Kummel:2002tx} use the 
-LINEX production function to describe economic output 
-for the economies of the U.S., Japan, and Germany. 
-\citet{Warr:2010ga} compare the LINEX production function with 
-the Cobb-Douglas production function to assess economic growth 
-for Austria, the United Kingdom, the United States, and Japan. 
-\citet{Ayres:2005kn} argued that introducing energy inputs 
-in traditional production functions does not improve its explanatory power, 
-but including useful work in a LINEX function does.
-
-\authNote{Martin: add more here about the conclusions of each paper 
-regarding the role of energy in economic growth? Add additional literature? 
-Or, adjust as you see fit. Especially, are there any confidence intervals 
-or statistical evaluation in each of these studies?}
-
-\authNote{If we want to keep this quote, it should be clearer what point we are trying to
-make with it. ---rjp}
-\citet{Abramovitz:1956aa} wrote:
-
-\begin{quote}
-  This result [that ``technological progress'' explained
-  175\% of the growth of the US economy since 1870] is surprising in the lopsided
-  importance which it appears to give to productivity increase,
-  and it should be, in a sense, sobering, if not discouraging,
-  to students of economic growth.
-  Since we know little about the causes of productivity increase,
-  the indicated importance of this element may be taken to be some sort of measure
-  of our ignorance about the causes of economic growth in the United States
-  and some sort of indication of where
-  we need to concentrate our attention.
-\end{quote}
-
 %++++++++++++++++++++++++++++++
@@
 coeffs_df <- tbl_df(AllCoef)
-coeffs_df <- subset(coeffs_df, subset=country=="ZA")
+coeffs_df_ZA <- subset(coeffs_df, subset=country=="ZA")
 # Load fitted data from all models in one large data frame
 fitted_df <- tbl_df(AllFitted)
-fitted_df <- subset(fitted_df, subset=Country=="ZA")
+fitted_df_ZA <- subset(fitted_df, subset=Country=="ZA")
 # Load the original models.
-oModels <- OrigModels$ZA
+oModels_ZA <- OrigModels$ZA
 @
 
-<<Historical_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=3, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), and thermal energy ($q$).">>=
+<<Historical_Graph, fig.pos="H", fig.align='center', fig.width=5, fig.height=3, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), and thermal energy ($q$).">>=
 historicalPlot(historicalData)
@@
 
-<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=4.5, fig.height=3, fig.cap="Cobb-Douglas resample model parameters.">>=
-cdCoeffsData <- filter(coeffs_df, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iQ"))
-standardTriPlot(data=cdCoeffsData, facet_formula=country~energy)
+<<CD_lambda_theta_graph, fig.pos="H", fig.align='center', fig.width=5, fig.height=3, fig.cap="$\\lambda$ and $\\theta$ values for CD resample models.">>=
+cdCoeffsData_ZA <- filter(coeffs_df_ZA, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iQ"))
+standardScatterPlot(data=cdCoeffsData_ZA, mapping=aes(scale, lambda), facet_formula=country~energy, alpha=0.05) +
+    scale_x_continuous(breaks=c(0.95, 1.0, 1.05)) +
+    scale_y_continuous(breaks=c(0, 0.002, 0.004, 0.006, 0.008)) +    
+    labs(x=expression(theta), y=expression(lambda))
 @
 
-<<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=4.5, fig.height=3, fig.cap="Cobb-Douglas fitted models.">>=
-cdFittedData <- filter(fitted_df, model=="cd", nest %in% c("iK+iL", "iK+iL+iQ"))
-spaghettiPlot(data=cdFittedData, facet_formula=Country~energy, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1980=1 or 1991=1)")
+<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=5, fig.height=3, fig.cap="Cobb-Douglas resample model parameters.">>=
+cdCoeffsData_ZA <- filter(coeffs_df_ZA, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iQ"))
+standardTriPlot(data=cdCoeffsData_ZA, facet_formula=country~energy)
+@
+
+<<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=5, fig.height=3, fig.cap="Cobb-Douglas fitted models.">>=
+cdFittedData_ZA <- filter(fitted_df_ZA, model=="cd", nest %in% c("iK+iL", "iK+iL+iQ"))
+spaghettiPlot(data=cdFittedData_ZA, facet_formula=Country~energy, level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1991=1)")
+@
+
+%++++++++++++++++++++++++++++++
+\subsection{CES Model}
+\label{sec:CES_Parameter_Estimation}
+%++++++++++++++++++++++++++++++
+
+<<CES_lambda_theta_graph, fig.pos="H", fig.align='center', fig.width=5, fig.height=3, fig.cap="$\\lambda$ and $\\theta$ values for CES resample models with various nestings.">>=
+cesCoeffsData_ZA <- filter(coeffs_df_ZA, model=="ces", nestStr %in% c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"))
+standardScatterPlot(data=cesCoeffsData_ZA, mapping=aes(gamma_coef, lambda), facet_formula=country~nest, alpha=0.05) +
+    scale_x_continuous(breaks=c(0.95, 1.0, 1.05)) +
+    scale_y_continuous(breaks=c(0, 0.002, 0.004, 0.006, 0.008)) +    
+    labs(x=expression(theta), y=expression(lambda))
+@
+
+<<CES_sigma1_delta1_graph, fig.pos="H", fig.align='center', fig.width=5, fig.height=3, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with various nestings.">>=
+standardScatterPlot(data=cesCoeffsData_ZA, mapping=aes(delta_1, sigma_1), facet_formula=country~nest, alpha=0.05) +
+    coord_trans(y="sigma") +
+    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
+    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
+    labs(x=expression(delta[1]), y=expression(sigma[1]))
+@
+
+<<CES_sigma_delta_graph, fig.pos="H", fig.align='center', fig.width=5, fig.height=3, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models with various nestings.">>=
+standardScatterPlot(data=subset(cesCoeffsData_ZA, nestStr != "iK+iL"),
+                    mapping=aes(delta, sigma), facet_formula=country~nest, alpha=0.05) +
+    coord_trans(y="sigma") +
+    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
+    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
+    labs(x=expression(delta), y=expression(sigma))
+@
+
+We can develop pseudo $\alpha$, $\beta$, and $\gamma$ parameters 
+for the CES model, based on values of $\delta$ and $\delta_1$.
+Table~\ref{tab:CES_abg_equations} shows the permuted equations for each CES nesting.
+
+\begin{table} \caption{Equations for $\alpha$, $\beta$, and $\gamma$ for the various CES nestings.} 
+\label{tab:CES_abg_equations} 
+  \begin{center}
+    \begin{tabular}{c c c c c} 
+      Nesting    & Equation        & $\alpha$                & $\beta$                 & $\gamma$                \\
+      \hline
+      ($kl$)     & \ref{eq:CES}    & $\delta_1$              & $1 - \delta_1$          & 0                       \\
+      ($kl$)$e$  & \ref{eq:CESkle} & $\delta \delta_1$       & $\delta (1 - \delta_1)$ & $1 - \delta$            \\   
+      ($le$)$k$  & \ref{eq:CESlek} & $1 - \delta$            & $\delta \delta_1$       & $\delta (1 - \delta_1)$ \\
+      ($ek$)$l$  & \ref{eq:CESekl} & $\delta (1 - \delta_1)$ & $1 - \delta$            & $\delta \delta_1$       \\
+    \end{tabular}
+  \end{center}
+\end{table}
+
+<<CES_ternary_graph, fig.pos="H", fig.align='center', fig.width=5, fig.height=3, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models with various nestings.">>=
+standardTriPlot(data=cesCoeffsData_ZA, facet_formula=country~nest)
+@
+
+<<CES_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=5, fig.height=3, fig.cap="CES fitted models with various nestings.">>=
+cesFittedData_ZA <- filter(fitted_df_ZA, model=="ces", nest %in% c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"))
+spaghettiPlot(data=cesFittedData_ZA, facet_formula=Country~nest, level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1991=1)")
+@
+
+%++++++++++++++++++++++++++++++
+\subsection{LINEX Model}
+\label{sec:LINEX_Parameter_Estimation}
+%++++++++++++++++++++++++++++++
+
+<<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=5, fig.height=3, fig.cap="LINEX model (with energy) resampling results.">>=
+linexCoeffsData_ZA <- filter(coeffs_df_ZA, model=="linex", energy=="iQ")
+standardScatterPlot(data=linexCoeffsData_ZA, aes(a_0, c_t), facet_formula=country~energy, alpha=0.05) +
+    labs(x=expression(a[0]), y=expression(c[t])) +
+     scale_x_continuous(limits=c(-1, 2), breaks=c(-1, 0, 1.0, 2.0)) +
+     scale_y_continuous(limits=c(0, 10), breaks=c(0, 5, 10))
+@
+
+<<LINEX_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=5, fig.height=3, fig.cap="LINEX fitted models.">>=
+linexFittedData_ZA <- filter(fitted_df_ZA, model=="linex", energy=="iQ")
+spaghettiPlot(data=linexFittedData_ZA, facet_formula=Country~energy, level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1991=1)")
 @

### 2014-06-09 Article_JAE_2014/ZAGrowth_JAE.Rnw
Added a note about reampled theta values for LINEX.
Added a note about ternary graph trajectories.
Removed unneeded comment.

@@
   # ********************************************************
-  # tikz allows LaTeX code in graphical output. 
-  # E.g., "$y$" for a variable name in the legend for a graph.  
-  # dev='tikz',
   tidy=FALSE,
@@
 
+**** Need to graph resampled $\theta$ values. ****
+
+**** Need to graph $\alpha$, $\beta$, and $\gamma$ as a trajectory on a ternary graph. ****
+
 <<LINEX_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=5, fig.height=3, fig.cap="LINEX fitted models.">>=

### 2014-06-09 Article/EconGrowth2.Rnw
Now conforms to nest, nestStr, nestStrParen.

@@
 <<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=8.2, fig.cap="Cobb-Douglas fitted models.">>=
-cdFittedData <- filter(fitted_df, model=="cd", nest %in% c("iK+iL", "iK+iL+iQ"))
+cdFittedData <- filter(fitted_df, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iQ"))
 spaghettiPlot(data=cdFittedData, facet_formula=Country~energy, level=spaghettiGraphLevel) +

### 2014-06-09 Scripts/PostProcess.R

@@ -81,7 +81,7 @@ AllFitted$Country <- as.factor(AllFitted$Country)
 for (lev in rev(countryAbbrevs)) { AllFitted$Country <- relevel(AllFitted$Country, ref=lev) }
 # Relevel nest
 AllFitted$nestStr <- as.factor(AllFitted$nestStr)
-for (lev in rev(nestStrLevels)) { AllFitted$nest <- relevel(AllFitted$nest, ref=lev) }
+for (lev in rev(nestStrLevels)) { AllFitted$nestStr <- relevel(AllFitted$nestStr, ref=lev) }
 # Relevel nestStrParen
 AllCoef$nestStrParen <- as.factor(AllCoef$nestStrParen)
 for (lev in rev(nestStrParenLevels)) { AllCoef$nestStrParen <- relevel(AllCoef$nestStrParen, ref=lev) }

### 2014-06-09 Article/EconGrowth2.Rnw
Now conforming to nest, nestStr, nestStrParen.

@@
 <<CES_lambda_gamma_graph, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models.">>=
-cesCoeffsData <- filter(coeffs_df, model=="ces", nestStr %in% c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"))
-standardScatterPlot(data=cesCoeffsData, mapping=aes(gamma_coef, lambda), facet_formula=country~nest, alpha=0.05) +
+cesCoeffsData <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
+                                                                     "(iK + iL) + (iQ)", 
+                                                                     "(iL + iQ) + (iK)", 
+                                                                     "(iQ + iK) + (iL)"))
+standardScatterPlot(data=cesCoeffsData, mapping=aes(gamma_coef, lambda), facet_formula=country~nestStrParen, alpha=0.05) +
     scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
@@
 <<CES_sigma1_delta1_graph, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models.">>=
-standardScatterPlot(data=cesCoeffsData, mapping=aes(delta_1, sigma_1), facet_formula=country~nest, alpha=0.05) +
+standardScatterPlot(data=cesCoeffsData, mapping=aes(delta_1, sigma_1), facet_formula=country~nestStrParen, alpha=0.05) +
     coord_trans(y="sigma") +
@@
 <<CES_sigma_delta_graph, fig.pos="H", fig.align='center', fig.width=4.5, fig.height=7, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models.">>=
-standardScatterPlot(data=subset(cesCoeffsData, nestStr != "iK+iL"),
-                    mapping=aes(delta, sigma), facet_formula=country~nest, alpha=0.05) +
+standardScatterPlot(data=subset(cesCoeffsData, nestStrParen != "(iK + iL) + ()"),
+                    mapping=aes(delta, sigma), facet_formula=country~nestStrParen, alpha=0.05) +
     coord_trans(y="sigma") +
@@
 <<CES_ternary_graph, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models.">>=
-standardTriPlot(data=cesCoeffsData, facet_formula=country~nest)
+standardTriPlot(data=cesCoeffsData, facet_formula=country~nestStrParen)
 @
@@
 <<CES_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models.">>=
-cesFittedData <- filter(fitted_df, model=="ces", nest %in% c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"))
-spaghettiPlot(data=cesFittedData, facet_formula=Country~nest, level=spaghettiGraphLevel) +
+cesFittedData <- filter(fitted_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
+                                                                     "(iK + iL) + (iQ)", 
+                                                                     "(iL + iQ) + (iK)", 
+                                                                     "(iQ + iK) + (iL)"))
+spaghettiPlot(data=cesFittedData, facet_formula=Country~nestStrParen, level=spaghettiGraphLevel) +
     labs(y="Indexed GDP (1980=1 or 1991=1)")
@@
 <<CES_Spaghetti_Graph_CN, fig.pos="H", fig.align='center', fig.width=maxWidth, fig.height=maxHeight, fig.cap="CES fitted models for China with the (kl)e nesting.">>=
-spaghettiPlot(data=subset(cesFittedData, Country=="CN" & nest=="iK+iL+iQ"), level=spaghettiGraphLevel) +
+spaghettiPlot(data=subset(cesFittedData, Country=="CN" & nestStrParen=="(iK + iL) + (iQ)"), level=spaghettiGraphLevel) +
     labs(y="Indexed GDP (1980 = 1 or 1991 = 1")

### 2014-06-16 Article/EconGrowth2-GraphsOnly.Rnw
Now building all graphs. In the Graphs-Only version of the paper, we weren't using the new versions of nestStr and nestStrParen.

@@
 <<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=6, fig.height=8.2, fig.cap="Cobb-Douglas fitted models.">>=
-cdFittedData <- filter(fitted_df, model=="cd", nest %in% c("iK+iL", "iK+iL+iQ", "iK+iL+iX", "iK+iL+iU"))
+cdFittedData <- filter(fitted_df, model=="cd")
 spaghettiPlot(data=cdFittedData, facet_formula=Country~energy, level=spaghettiGraphLevel) +
@@
 
-% <<CES_lambda_gamma_graph, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models.">>=
-% cesCoeffsData <- filter(coeffs_df, model=="ces", nestStr %in% c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"))
-% standardScatterPlot(data=cesCoeffsData, mapping=aes(gamma_coef, lambda), facet_formula=country~nest, alpha=0.05) +
-%     scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
-%     scale_y_continuous(breaks=c(0, 0.025, 0.05, 0.075)) +    
-%     labs(x=expression(gamma), y=expression(lambda))
-% @
-
 <<CES_lambda_gamma_graph_kle, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with (kl)e nesting.">>=
-cesCoeffsData_kle <- filter(coeffs_df, model=="ces", nestStr %in% c("iK+iL", "iK+iL+iQ", "iK+iL+iX", "iK+iL+iU"))
-standardScatterPlot(data=cesCoeffsData_kle, mapping=aes(gamma_coef, lambda), facet_formula=country~nest, alpha=0.05) +
+cesCoeffsData_kle <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", "(iK + iL) + (iQ)", "(iK + iL) + (iX)", "(iK + iL) + (iU)"))
+standardScatterPlot(data=cesCoeffsData_kle, mapping=aes(gamma_coef, lambda), facet_formula=country~nestStrParen, alpha=0.05) +
     scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
@@
 <<CES_lambda_gamma_graph_lek, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with (le)k nesting.">>=
-cesCoeffsData_lek <- filter(coeffs_df, model=="ces", nestStr %in% c("iK+iL", "iL+iQ+iK", "iL+iX+iK", "iL+iU+iK"))
-standardScatterPlot(data=cesCoeffsData_lek, mapping=aes(gamma_coef, lambda), facet_formula=country~nest, alpha=0.05) +
+cesCoeffsData_lek <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", "(iL + iQ) + (iK)", "(iL + iX) + (iK)", "(iL + iU) + (iK)"))
+standardScatterPlot(data=cesCoeffsData_lek, mapping=aes(gamma_coef, lambda), facet_formula=country~nestStrParen, alpha=0.05) +
     scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
@@
 <<CES_lambda_gamma_graph_ekl, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with (ek)l nesting.">>=
-cesCoeffsData_ekl <- filter(coeffs_df, model=="ces", nestStr %in% c("iK+iL", "iQ+iK+iL", "iX+iK+iL", "iU+iK+iL"))
-standardScatterPlot(data=cesCoeffsData_ekl, mapping=aes(gamma_coef, lambda), facet_formula=country~nest, alpha=0.05) +
+cesCoeffsData_ekl <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", "(iQ + iK) + (iL)", "(iX + iK) + (iL)", "(iU + iK) + (iL)"))
+standardScatterPlot(data=cesCoeffsData_ekl, mapping=aes(gamma_coef, lambda), facet_formula=country~nestStrParen, alpha=0.05) +
     scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
@@
 
-% <<CES_sigma1_delta1_graph, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models.">>=
-% standardScatterPlot(data=cesCoeffsData, mapping=aes(delta_1, sigma_1), facet_formula=country~nest, alpha=0.05) +
-%     coord_trans(y="sigma") +
-%     scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-%     scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-%     labs(x=expression(delta[1]), y=expression(sigma[1]))
-% @
-
 <<CES_sigma1_delta1_graph_kle, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with (kl)e nesting.">>=
-standardScatterPlot(data=cesCoeffsData_kle, mapping=aes(delta_1, sigma_1), facet_formula=country~nest, alpha=0.05) +
+standardScatterPlot(data=cesCoeffsData_kle, mapping=aes(delta_1, sigma_1), facet_formula=country~nestStrParen, alpha=0.05) +
     coord_trans(y="sigma") +
@@
 <<CES_sigma1_delta1_graph_lek, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with (le)k nesting.">>=
-standardScatterPlot(data=cesCoeffsData_lek, mapping=aes(delta_1, sigma_1), facet_formula=country~nest, alpha=0.05) +
+standardScatterPlot(data=cesCoeffsData_lek, mapping=aes(delta_1, sigma_1), facet_formula=country~nestStrParen, alpha=0.05) +
     coord_trans(y="sigma") +
@@
 <<CES_sigma1_delta1_graph_ekl, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with (ek)l nesting.">>=
-standardScatterPlot(data=cesCoeffsData_ekl, mapping=aes(delta_1, sigma_1), facet_formula=country~nest, alpha=0.05) +
+standardScatterPlot(data=cesCoeffsData_ekl, mapping=aes(delta_1, sigma_1), facet_formula=country~nestStrParen, alpha=0.05) +
     coord_trans(y="sigma") +
@@
 
-% # <<CES_sigma_delta_graph, fig.pos="H", fig.align='center', fig.width=4.5, fig.height=7, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models.">>=
-% #  standardScatterPlot(data=subset(cesCoeffsData, nestStr != "iK+iL"),
-% #                      mapping=aes(delta, sigma), facet_formula=country~nest, alpha=0.05) +
-% #      coord_trans(y="sigma") +
-% #      scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-% #      scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-% #      labs(x=expression(delta), y=expression(sigma))
-% #  @
-
 <<CES_sigma_delta_graph_kle, fig.pos="H", fig.align='center', fig.width=4.5, fig.height=7, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models with (kl)e nesting.">>=
-standardScatterPlot(data=subset(cesCoeffsData_kle, nestStr != "iK+iL"),
-                    mapping=aes(delta, sigma), facet_formula=country~nest, alpha=0.05) +
+standardScatterPlot(data=subset(cesCoeffsData_kle, nestStrParen != "(iK + iL) + ()"),
+                    mapping=aes(delta, sigma), facet_formula=country~nestStrParen, alpha=0.05) +
     coord_trans(y="sigma") +
@@
 <<CES_sigma_delta_graph_lek, fig.pos="H", fig.align='center', fig.width=4.5, fig.height=7, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models with (le)k nesting.">>=
-standardScatterPlot(data=subset(cesCoeffsData_lek, nestStr != "iK+iL"),
-                    mapping=aes(delta, sigma), facet_formula=country~nest, alpha=0.05) +
+standardScatterPlot(data=subset(cesCoeffsData_lek, nestStrParen != "(iK + iL) + ()"),
+                    mapping=aes(delta, sigma), facet_formula=country~nestStrParen, alpha=0.05) +
     coord_trans(y="sigma") +
@@
 <<CES_sigma_delta_graph_ekl, fig.pos="H", fig.align='center', fig.width=4.5, fig.height=7, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models with (ek)l nesting.">>=
-standardScatterPlot(data=subset(cesCoeffsData_ekl, nestStr != "iK+iL"),
-                    mapping=aes(delta, sigma), facet_formula=country~nest, alpha=0.05) +
+standardScatterPlot(data=subset(cesCoeffsData_ekl, nestStrParen != "(iK + iL) + ()"),
+                    mapping=aes(delta, sigma), facet_formula=country~nestStrParen, alpha=0.05) +
     coord_trans(y="sigma") +
@@
 <<CES_ternary_graph_kle, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models with (kl)e nesting.">>=
-standardTriPlot(data=cesCoeffsData_kle, facet_formula=country~nest)
+standardTriPlot(data=cesCoeffsData_kle, facet_formula=country~nestStrParen)
 @
@@
 <<CES_ternary_graph_lek, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models with (le)k nesting.">>=
-standardTriPlot(data=cesCoeffsData_lek, facet_formula=country~nest)
+standardTriPlot(data=cesCoeffsData_lek, facet_formula=country~nestStrParen)
 @
@@
 <<CES_ternary_graph_ekl, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models with (ek)l nesting.">>=
-standardTriPlot(data=cesCoeffsData_ekl, facet_formula=country~nest)
+standardTriPlot(data=cesCoeffsData_ekl, facet_formula=country~nestStrParen)
 @
 
-% <<CES_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models.">>=
-% cesFittedData <- filter(fitted_df, model=="ces", nest %in% c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"))
-% spaghettiPlot(data=cesFittedData, facet_formula=Country~nest, level=spaghettiGraphLevel) +
-%     labs(y="Indexed GDP (1980=1 or 1991=1)")
-% @
-
 <<CES_Spaghetti_Graph_kle, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models with (kl)e nesting.">>=
-cesFittedData <- filter(fitted_df, model=="ces", nest %in% c("iK+iL", "iK+iL+iQ", "iK+iL+iX", "iK+iL+iU"))
-spaghettiPlot(data=cesFittedData, facet_formula=Country~nest, level=spaghettiGraphLevel) +
+cesFittedData <- filter(fitted_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", "(iK + iL) + (iQ)", "(iK + iL) + (iX)", "(iK + iL) + (iU)"))
+spaghettiPlot(data=cesFittedData, facet_formula=Country~nestStrParen, level=spaghettiGraphLevel) +
     labs(y="Indexed GDP (1980=1 or 1991=1)")
@@
 <<CES_Spaghetti_Graph_lek, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models with (le)k nesting.">>=
-cesFittedData <- filter(fitted_df, model=="ces", nest %in% c("iK+iL", "iL+iQ+iK", "iL+iX+iK", "iL+iU+iK"))
-spaghettiPlot(data=cesFittedData, facet_formula=Country~nest, level=spaghettiGraphLevel) +
+cesFittedData <- filter(fitted_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", "(iL + iQ) + (iK)", "(iL + iX) + (iK)", "(iL + iU) + (iK)"))
+spaghettiPlot(data=cesFittedData, facet_formula=Country~nestStrParen, level=spaghettiGraphLevel) +
     labs(y="Indexed GDP (1980=1 or 1991=1)")
@@
 <<CES_Spaghetti_Graph_ekl, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models with (ek)l nesting.">>=
-cesFittedData <- filter(fitted_df, model=="ces", nest %in% c("iK+iL", "iQ+iK+iL", "iX+iK+iL", "iU+iK+iL"))
-spaghettiPlot(data=cesFittedData, facet_formula=Country~nest, level=spaghettiGraphLevel) +
+cesFittedData <- filter(fitted_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", "(iQ + iK) + (iL)", "(iX + iK) + (iL)", "(iU + iK) + (iL)"))
+spaghettiPlot(data=cesFittedData, facet_formula=Country~nestStrParen, level=spaghettiGraphLevel) +
     labs(y="Indexed GDP (1980=1 or 1991=1)")
 @
-
-% <<CES_Spaghetti_Graph_CN, fig.pos="H", fig.align='center', fig.width=maxWidth, fig.height=maxHeight, fig.cap="CES fitted models for China with the (kl)e nesting.">>=
-% spaghettiPlot(data=subset(cesFittedData, Country=="CN" & nest=="iK+iL+iQ"), level=spaghettiGraphLevel) +
-%     labs(y="Indexed GDP (1980 = 1 or 1991 = 1")
-% @
-
-% <<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7, fig.cap="LINEX model (with energy) resampling results.">>=
-% linexCoeffsData <- filter(coeffs_df, model=="linex", energy=="q")
-% standardScatterPlot(data=linexCoeffsData, aes(a_0, c_t), facet_formula=country~energy, alpha=0.05) +
-%     labs(x=expression(a[0]), y=expression(c[t])) +
-%      scale_x_continuous(limits=c(-1, 2), breaks=c(-1, 0, 1.0, 2.0)) +
-%      scale_y_continuous(limits=c(0, 10), breaks=c(0, 5, 10))
-% @
 
@@
 @
-
-% <<LINEX_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7.1, fig.cap="LINEX fitted models.">>=
-% linexFittedData <- filter(fitted_df, model=="linex", energy=="q")
-% spaghettiPlot(data=linexFittedData, facet_formula=Country~energy, level=spaghettiGraphLevel) +
-%     labs(y="Indexed GDP (1980=1 or 1991=1)")
-% @
 

### 2014-06-16 Article/EconGrowth2.Rnw
Minor changes to the EE article.

@@
 \noindent where $a_1 \equiv a_0 c_t$. 
-We used the \texttt{nls} function in \texttt{R}
+We used the \texttt{lm} function in \texttt{R}
 \citep{R} to estimate least-squares values for $a_0$ and $a_1$ in 
-Equation~\ref{eq:LINEX_transformed}. We recovered
-a value for $c_t$ with $c_t = a_1 / a_0$. The reparameterization
+Equation~\ref{eq:LINEX_transformed}. 
+We recovered a value for $c_t$ with $c_t = a_1 / a_0$. 
+The reparameterization
 shown in Equation~\ref{eq:LINEX_transformed} reduced the number of 
-unconverged resample fits to nearly zero: 
-The largest fraction of unconverged resample fits is found 
-for Zambia (ZM) with thermal energy ($q$), where
-\Sexpr{fracUnconvergedResampleFits(modelType="linex", countryAbbrev="ZM", energyType="Q", baseResample=baseResample)*100}\%
-of the resample fits did not converge. 
-(See Table~\ref{tab:frac_unconverged_models}.)
+unconverged resample fits to zero:
 

### 2014-06-19 Article/EconGrowth2-GraphsOnly.Rnw
Added text about alpha, beta, gamma, for the LINEX model.

@@
 
+In the LINEX model, values of $a_0$ and $c_t$ imply values of $\alpha$, $\beta$, and $\gamma$ 
+according to the following equations:
+
+\begin{equation} \label{eq:LINEX_alpha}
+  \alpha = a_0 \left( \frac{l + e}{k} \right) \;,
+\end{equation}
+
+\begin{equation} \label{eq:LINEX_beta}
+  \beta = a_0 \left[ c_t \left( \frac{l}{e}\right) - \frac{l}{k} \right] \;,
+\end{equation}
+
+\noindent{}and
+
+\begin{equation} \label{eq:LINEX_beta}
+  \gamma = 1 - \alpha - \beta \;.
+\end{equation}
+
+Each curve fit implies a trajectory of $\alpha$, $\beta$, and $\gamma$ values as time proceeds.
+The following graph shows China's trajectory for thermal energy ($q$):
+
+<<LINEX_abg_traj_graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="LINEX trajectory for China with thermal energy $q$.">>=
+data <- fortify(OrigModels$CN$linex$`iK+iL+iQ`)
+triPlot(data=data, grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear")
+@
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2014-06-19 Article/EconGrowth2.Rnw
Move data loading to its own chunk. Allows faster generation of paper with eval=FALSE.
Line break changes.

@@
 require(knitr)
-
-# Load historical data
-# In Rstudio, this paper is generated from it's directory, which is "Article".
-# We need to define paths relative to the location of the paper. 
-# Relative path to historical data from Article
-historicalData <- Econ2011 # From the EconData package
-
-# Load coefficients from all models in one large data frame
-coeffs_df <- tbl_df(AllCoef)
-# Load fitted data from all models in one large data frame
-fitted_df <- tbl_df(AllFitted)
-
-# Load the original models.
-oModels <- OrigModels
 
@@
 spaghettiGraphLevel <- 0.95 # Spaghetti graph bands will encompass 95% of the data.
+@
+
+<<data, include=FALSE>>=
+# Load historical data
+# In Rstudio, this paper is generated from it's directory, which is "Article".
+# We need to define paths relative to the location of the paper. 
+# Relative path to historical data from Article
+historicalData <- Econ2011 # From the EconData package
+
+# Load coefficients from all models in one large data frame
+coeffs_df <- tbl_df(AllCoef)
+# Load fitted data from all models in one large data frame
+fitted_df <- tbl_df(AllFitted)
+
+# Load the original models.
+oModels <- OrigModels
 @
@@
 rigorous statistical assessments of energy-related fitting parameters. This paper 
-attempts to contribute to the literature by applying statistically rigorous 
-methods along three coordinates of analysis: form of the energy augmented 
-production function, energy quantification, and type of economy.
+contributes to the literature by applying statistically rigorous 
+methods along two coordinates of analysis: form of the energy augmented 
+production function and type of economy.
 
@@
 Section~\ref{sec:Sources_of_Data} details sources of data and calculations to 
-generate time series for economic output and factors of production. The procedures 
-for and results from parameter estimation for the various production functions 
+generate time series for economic output and factors of production. 
+The procedures for and results from parameter estimation for the various production functions 
 are discussed in Section~\ref{sec:Parameter_Estimation}. 
 Section~\ref{sec:Discussion_of_Results} discusses implications of the parameter estimation 
-results, and Section~\ref{sec:Conclusion} concludes. An appendix provides details 
-of all statistical results.
+results, and Section~\ref{sec:Conclusion} concludes. 
+An appendix provides details of all statistical results.
 
@@
 In this paper, we assess three prominent energy-augmented production functions 
-that appear in the literature: Cobb-Douglas (CDe), Constant Elasticity of 
-Substitution (CESe), and LINear EXponential (LINEX). The following subsections 
-describe each.
+that appear in the literature: 
+Cobb-Douglas (CD), 
+Constant Elasticity of Substitution (CES), and 
+LINear EXponential (LINEX). 
+The following subsections describe each.
 
 %------------------------------
-\subsubsection{Energy-augmented Cobb-Douglas Production Function (CDe)} 
+\subsubsection{Cobb-Douglas (CD) Production Function} 
 \label{sec:CDe}
@@
 \end{equation}
-where $e \equiv E/E_0$, and $E$ is in units of energy per time, 
-typically TJ/year. The energy-augmented Cobb-Douglas production function 
+where $e \equiv E/E_0$, and $E$ is in units of energy per time, typically TJ/year. 
+The energy-augmented Cobb-Douglas production function 
 is often assumed to have constant returns to scale for the three factors 
@@
 energy-augmented Cobb-Douglas production function with thermal energy 
-quantification ($q$) to describe output for the global economy from 
-1800--1970. Fr\"{o}ling's model endogenizes labor with respect to fertility 
+quantification ($q$) to describe output for the global economy from 1800--1970. 
+Fr\"{o}ling's model endogenizes labor with respect to fertility 
 and mortality rates and separates thermal energy into two types: biomass 
-energy and coal energy. \citet{Serrenho:2010vq} use the log transform of 
+energy and coal energy. 
+\citet{Serrenho:2010vq} use the log transform of 
 the energy-augmented Cobb-Douglas function with thermal energy 
@@
 Serrenho divides thermal energy into renewables, non-renewables, 
-wastes, and imports. The main argument of these papers is that 
+wastes, and imports. 
+The main argument of these papers is that 
 energy is an important driver of growth and needs to be included
@@
 %------------------------------
-\subsubsection{Energy-augmented CES Production Function (CESe)} 
+\subsubsection{Constant Elasticity of Substitution Production Function (CES)} 
 \label{sec:CES}
@@
 Other energy economists use an energy-augmented 
-Constant Elasticity of Substitution (CES$e$) production function to 
+Constant Elasticity of Substitution (CES) production function to 
 describe economic growth. The \texttt{R} \citep{R} package 

### 2014-06-19 Article/EconGrowth2.Rnw
Minor changes.

@@
 \citep{Kummel:1980wx,Kummel:1982vy,Kummel:1985vz,Kummel:1989tf,Kummel:2002tx,Kummel:2010vz}. 
-%\noindent where $e$ is indexed energy and e is the base of 
-%the natural logarithm. 
 In contrast to both the Cobb-Douglas model (Equations~\ref{eq:CD} and 
@@
 
-\twocolumn{}
 <<Historical_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=7.5, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), and thermal energy ($q$).">>=
@@
 
-\onecolumn{}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+%++++++++++++++++++++++++++++++
 \subsection{Point Estimates}
+%++++++++++++++++++++++++++++++
+
 Each of the economic growth models discussed in 
 Section~\ref{sec:Prod_Func_Forms} has parameters which must be estimated (fitted)
-from data for each economy (see Section~\ref{sec:Economy_Types}).
-We obtained parameter estimates by applying the method of least-squares to (potentially
-log-transformed) data using the \texttt{R} \citep{R} functions
+using data for each economy (see Section~\ref{sec:Economy_Types}).
+We obtained parameter estimates by applying the method of least-squares to 
+log-transformed data using the \texttt{R} \citep{R} functions
 \texttt{lm} (for Cobb-Douglas and LINEX models) 
@@
 \authNote{if we use $\theta$ this way, we need a new scaling parameter. --rjp}%
-In least squares models, parameter estimates are chosen to minimize
+Parameter estimates are chosen to minimize
 \[
-\sum_{i} (y_i - f(t,k,l,e; \theta) )^2 \;.
+\sum_{i} (y_i - f(t,k,l,e; \theta) )^2
 \]
+within constraints.
 For the optimal parameter values $\hat \theta$, we define the 

### 2014-06-19 Article/EconGrowth2.Rnw
Line break changes. Made discussion of fitting processes more accurate.

@@
 properties of an estimator when sampling from a resampling
-distribution.  Resampling distributions can be formed in a number of 
+distribution.  
+Resampling distributions can be formed in a number of 
 ways in accordance with the type of data, experimental design,
-and modeling assumptions involved.  In each case, many new resamples 
+and modeling assumptions involved.  
+In each case, many new resamples 
 are created, each of which is a randomized version of the original sample data to 
-which the desired analysis method can be applied.  By investigating, for example,
+which the desired analysis method can be applied.  
+By investigating, for example,
 the variability of a parameter estimate from one resample to another,
@@
 by residual resampling.  In our case, we formed resamples by adding to the fitted 
-response (GDP) the product of a residual from the original model fit and 
-and random sign ($-1$ or $1$, each with probability $0.5$).  For the case of 
-Cobb-Douglas and LINEX models, this residual resampling occurs on the 
+response ($\hat{y}$) the product of a residual from the original model fit and 
+random sign ($-1$ or $1$, each with probability $0.5$).  
+For the case of Cobb-Douglas and LINEX models, 
+this residual resampling occurs on the 
 log-transformed data.
@@
 any particular year had been observed in a different year. 
-Thus, a resampled response $\tilde Y$ can be computed as 
+Thus, a resampled response $\tilde Y'$ can be computed as 
 \[
@@
 are chosen at random (with replacement). 
-Resampling in this way has the consequence 
-that a resampled time series could have non-unity first-year GDP ($\tilde Y_1 \neq 1$),
-so a renormalization takes place using the initial GDP from the
-resampled data as the new baseline, not the observed GDP in year 1.
-
-\begin{equation} \label{eq:resample_y}
-	\tilde y_i  = \frac{\tilde Y_i'}{\tilde Y_1'}
-\end{equation}
-to obtain a resampled indexed GDP time series.
-We repeated the resampling process \Sexpr{numResamples()} times for each
-combination of growth model and country, both with and without energy when appropriate.
+% Resampling in this way has the consequence 
+% that a resampled time series could have non-unity first-year GDP ($\tilde Y_1 \neq 1$),
+% so a renormalization takes place using the initial GDP from the
+% resampled data as the new baseline, not the observed GDP in year 1.
+% \begin{equation} \label{eq:resample_y}
+% 	\tilde y_i  = \frac{\tilde Y_i'}{\tilde Y_1'}
+% \end{equation}
+% to obtain a resampled indexed GDP time series.
+We repeated the resampling process 1000 times for each
+combination of growth model and country, 
+both with and without energy as appropriate.
 
@@
 obtained from the fit to historical data (the ``base coefficients'').
-When these resample coefficients are highly variable, it is an indication
+When these resample coefficients are highly variable, 
+it is an indication
 that the data do not determine the parameter estimates very precisely.
-Lack of imprecision can stem from a number of factors, most obviously
+Lack of precision can stem from a number of factors, most obviously
 a poor model fit, low model sensitivity to one or more parameters, 
@@
 are expected to produce large variation in resample coefficient values
-(when the resampling is repeated \Sexpr{numResamples()} times),
+(when the resampling is repeated 1000 times),
 indicating less certainty in the value

### 2014-06-19 Article/EconGrowth2.Rnw
Small changes.

@@
 model produces fitted values that track the observed data closely, it may
-still be difficult to estimate some or all of the model parameters precisely.
-The resampling method employed reflects all three of these potential 
+yet be difficult to estimate some or all of the model parameters precisely.
+The resampling method employed herein reflects all three of these potential 
 sources of uncertainty in parameter estimates.
@@
 \begin{equation} \label{eq:CD_reparam}
-  y = A k^{\alpha} l^{1-\alpha}; A = \mathrm{e}^{\lambda (t-t_0)}
+  y = \theta \mathrm{e}^{\lambda (t-t_0)} k^{\alpha} l^{1-\alpha}
 \end{equation}
@@
 $\lambda$ and $\alpha$ were estimated by the 
-\texttt{R} \citep{R} function \texttt{nls}. 
+\texttt{R} \citep{R} function \texttt{lm} in log-transform space. 
 If the estimated value for $\alpha$ was found outside the interval $[0,1]$, 
@@
 \begin{equation} \label{eq:CDe_AB_reparam}
-  y = A k^{\min(a,b)} l^{|b-a|} e^{1 - \max(a,b)}; A = \mathrm{e}^{\lambda (t-t_0)}
+  y = \theta \mathrm{e}^{\lambda (t-t_0)} k^{\min(a,b)} l^{|b-a|} e^{1 - \max(a,b)}
 \end{equation}
@@
 thereby providing constant returns to scale.
-The \texttt{R} \citep{R} function \texttt{nls} was used to estimate 
-values of $\lambda$, $a$, and $b$.
-If the fitted value for $a$ ($b$) fell outside $[0,1]$, it was 
+The \texttt{R} \citep{R} function \texttt{lm} was used to estimate 
+values of $\lambda$, $a$, and $b$ in log-transform space.
+If the fitted value for $a$ ($b$) fell outside the range $[0,1]$, it was 
 set equal to its boundary value and both $\lambda$ and $b$ ($a$) 
@@
 
-The \texttt{nls} parameter estimation algorithm can encounter convergence difficulty 
-when the optimal value for the parameter represented by the absolute value function 
-(in Equation~\ref{eq:CDe_AB_reparam}, $\beta$) 
-lies near a boundary. If the absolute value exponent caused non-convergence of the 
-\texttt{nls} function, second and, if necessary, third reparameterizations 
-were attempted:
-
-\begin{equation} \label{eq:CDe_CD_reparam}
-  y = A k^{1 - \max(c,d)} l^{\min(c,d)} e^{|d-c|}; A = \mathrm{e}^{\lambda (t-t_0)}
-\end{equation}
-
-\begin{equation} \label{eq:CDe_FG_reparam}
-  y = A k^{|g-f|} l^{1 - \max(f,g)} e^{\min(f,g)}; A = \mathrm{e}^{\lambda (t-t_0)}
-\end{equation}
-
-\noindent If none of the three reparameterizations converged, 
-the parameterization with the smallest sum of square errors ($sse$)
-was used. \ref{sec:Convergence_Resample_Models} shows the 
-fraction of unconverged models for each model type. 
-The above approach resulted in very few unconverged
-Cobb-Douglas resample models, even with \Sexpr{numResamples()} resamples.
+% The \texttt{nls} parameter estimation algorithm can encounter convergence difficulty 
+% when the optimal value for the parameter represented by the absolute value function 
+% (in Equation~\ref{eq:CDe_AB_reparam}, $\beta$) 
+% lies near a boundary. If the absolute value exponent caused non-convergence of the 
+% \texttt{nls} function, second and, if necessary, third reparameterizations 
+% were attempted:
+% 
+% \begin{equation} \label{eq:CDe_CD_reparam}
+%   y = A k^{1 - \max(c,d)} l^{\min(c,d)} e^{|d-c|}; A = \mathrm{e}^{\lambda (t-t_0)}
+% \end{equation}
+% 
+% \begin{equation} \label{eq:CDe_FG_reparam}
+%   y = A k^{|g-f|} l^{1 - \max(f,g)} e^{\min(f,g)}; A = \mathrm{e}^{\lambda (t-t_0)}
+% \end{equation}
+% 
+% \noindent If none of the three reparameterizations converged, 
+% the parameterization with the smallest sum of square errors ($sse$)
+% was used. \ref{sec:Convergence_Resample_Models} shows the 
+% fraction of unconverged models for each model type. 
+% The above approach resulted in very few unconverged
+% Cobb-Douglas resample models, even with \Sexpr{numResamples()} resamples.
 
@@
 Each reample is shown as a gray dot on the graph. 
-The fit to historical data is shown as a gray circle.
+The fit to historical data is shown as a gray crosshairs.
 
@@
 are $\lambda$ = 0.015/year, $\delta$ = 0.5, $\delta_1$ = 0.5, 
-and $\gamma$ is set to a value such that the mean of the residuals is zero.
+and $\gamma$ is set to a value such that the mean of the residuals is zero
+by the \texttt{cesEst} function.
 
@@
 coefficients that give the best fit to the model, 
-where the PORT algorithm can be used to restrict the estimates 
+where the \texttt{PORT} algorithm can be used to restrict the estimates 
 to the economically meaningful region.

### 2014-06-19 Article/EconGrowth2.Rnw
Added paragraph about left and right sides of graphs being equal.

@@
 Figures~\ref{fig:CES_lambda_gamma_graph}--\ref{fig:CES_sigma_delta_graph}. 
-The crosshair on each graph shows the location 
+The white crosshair on each graph shows the location 
 of the fit to historical data. 
@@
 The top of the vertical axis represents $\sigma = \infty$.
+
+Note that as $\delta$ or $\delta_1$ approaches 0 (1) 
+in Equations~\ref{eq:CES}--\ref{eq:CESekl},
+the corresponding value of $\sigma$ or $\sigma_1$ becomes irrelevant, and
+resample points along the left (right) edge of
+Figures \ref{fig:CES_sigma1_delta1_graph} and \ref{fig:CES_sigma_delta_graph}
+are equivalent.
+That is, all points along the left (right) edge of
+Figures \ref{fig:CES_sigma1_delta1_graph} and \ref{fig:CES_sigma_delta_graph}
+have the same $sse$. 
+As a consequence, 
+the \texttt{cesEst} fitting algorithm has no way 
+to discriminate among points along the left (right) edge of
+Figures \ref{fig:CES_sigma1_delta1_graph} and \ref{fig:CES_sigma_delta_graph}. 
+Thus, resample point estimates where $\delta$ or $\delta_1$ approaches 0 (1)
+tend to cluster at the locations of the initial grid search in 
+$\sigma$ or $\sigma_1$
+(0.1, 0.33, 0.5, 0.7, 0.8, 0.9, 1.11, 2, 4, 10, and 100).
 

### 2014-06-19 Article/EconGrowth2.Rnw
Minor changes.

@@
 to historical data for all nestings. 
-Historical data are shown as a black line. 
-The fit to historical data is shown as a white line.
-The gray band encompasses 95\% of the fits to resampled data.
+As with the Cobb-Douglas results, 
+historical data are shown as a black line, 
+the fit to historical data is shown as a white line, and 
+the gray band encompasses 95\% of the fits to resampled data.
 
@@
 If the fitting algorithm drives $a_0 \rightarrow 0$, 
-any changes to $c_t$ have no effect on $sse$, 
-leading the fitting algorithm to report non-convergence. 
-To avoid this problem, we transformed the LINEX model into
+any changes to $c_t$ have no effect on $sse$. 
+Therefore, we transformed the LINEX model into
 
@@
 \citep{R} to estimate least-squares values for $a_0$ and $a_1$ in 
-Equation~\ref{eq:LINEX_transformed}. 
+Equation~\ref{eq:LINEX_transformed} in log-transformed space. 
 We recovered a value for $c_t$ with $c_t = a_1 / a_0$. 
-The reparameterization
-shown in Equation~\ref{eq:LINEX_transformed} reduced the number of 
-unconverged resample fits to zero:
-
 Figure~\ref{fig:LINEXq_Resample_Graph}
@@
 Figure~\ref{fig:LINEX_Spaghetti_Graph} compares LINEX model predictions to historical data.
-Historical data are shown as a black line. 
-The fit to historical data is shown as a white line.
-The gray band encompasses 95\% of the fits to resampled data.
+Again, historical data are shown as a black line, 
+the fit to historical data is shown as a white linem and 
+the gray band encompasses 95\% of the fits to resampled data.
 

### 2014-06-19 Article/EconGrowth2.Rnw
Adding section on future work.
Added paragraph on energy quantifications.

@@
 
+In the future, we intend add an additional coordinate of analysis 
+(Section~\ref{sec:Coordinates}):
+energy quantification.
+We wish to include exergy ($X$) and useful work ($U$) energy quantifications
+in the economic models.
+Doing so will provide an opportunity to engage the 
+literature around useful work as a driver 
+of economic growth.\citep{Ayres:2003ec, Ayres:2005kn, Ayres:2010ug, 
+Warr:2006hc, Warr:2010ga, Warr:2010ht, Warr:2012cg}
+And, we will be able to assess whether any models provide better 
+descriptions of economic growth with a given energy quantification.
+We intend to look at additional countries as data becomes available
+for the various enegy quantifications.
+And, we wish to look over longer time scales.
+In particular, we wish to investigate the effects of significant 
+processes (such as industrialization) and events (world wars)
+using the resampling techniques presented herein.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2014-06-19 Article/EconGrowth2.Rnw
Edits to Future Work section.

--- 2014-06-19 Article/EconGrowth2.Rnw
@@
 
+In the future, we intend add an additional coordinate of analysis 
+(Section~\ref{sec:Coordinates}):
+energy quantification.
+Specifically, we with to analyze exergy ($X$) and useful work ($U$)
+energy quantifications within the framework established in this paper.
+Doing so will provide an opportunity to engage the 
+literature around useful work as a driver 
+of economic growth.\citep{Ayres:2003ec, Ayres:2005kn, Ayres:2010ug, 
+Warr:2006hc, Warr:2010ga, Warr:2010ht, Warr:2012cg}
+And, we will be able to assess the interaction between economic models
+and energy quantification: 
+are there combinations of economic models and energy quantifications
+that provide significantly better descriptions of growth?
+We intend to evaluate additional countries as data become available.
+And, we wish to perform analyses over longer time scales.
+In particular, we wish to investigate the effects of significant 
+economic processes (such as industrialization) and political events (world wars)
+using the resampling techniques presented herein.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2014-06-19 Article/EconGrowth2.Rnw
Added a section on LINEX trajectories. Also discussed alpha, beta, and gamma constraints.

@@
 
+The LINEX model coefficients $a_0$ and $c_t$ imply time-dependent
+values of $\alpha$, $\beta$, and $\gamma$ as given by the following equations~\citep{Warr:2012cg}:
+
+\begin{equation} \label{eq:LINEX_alpha}
+  \alpha = \frac{k}{y}\frac{\partial y}{\partial k} = a_0 \left( \frac{l + e}{k} \right) \;,
+\end{equation}
+
+\begin{equation} \label{eq:LINEX_beta}
+  \beta = \frac{l}{y} \frac{\partial y}{\partial l} = a_0 \left[ c_t \left( \frac{l}{e}\right) - \frac{l}{k} \right] \;,
+\end{equation}
+
+\noindent{}and
+
+\begin{equation} \label{eq:LINEX_beta}
+  \gamma = \frac{e}{y} \frac{\partial y}{\partial e} 
+         = 1 - a_0 \left[ \frac{e}{k} + c_t \frac{l}{e} \right] 
+         = 1 - \alpha - \beta \;.
+\end{equation}
+
+\noindent Thus, each fitted model implies a trajectory of $\alpha$, $\beta$, and $\gamma$ values as time proceeds.
+If the trajectory stays within the triangle, 
+the constraints of $\alpha > 0$, $\beta > 0$, and $\gamma > 0$ are respected.  
+Conversely, if the trajectory goes outside the triangle, one of the constraints has been violated.
+
+The following graphs shows trajectories for China and Iran.
+
+<<LINEX_abg_traj_graph_CN, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="LINEX trajectory for China.">>=
+dataCN <- fortify(OrigModels$CN$linex$`iK+iL+iQ`)
+triPlot(data=dataCN, grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1990")
+@
+
+<<LINEX_abg_traj_graph_IR, fig.pos="H", fig.align='center', fig.width=3, fig.height=2, fig.cap="LINEX trajectory for Iran.">>=
+dataIR <- fortify(OrigModels$IR$linex$`iK+iL+iQ`)
+triPlot(data=dataIR, grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1990")
+@
+
+Iran is the only country for which the trajecotry stays within the triangle for the 
+entire time period.
+Thus, in our fitted models, the LINEX model is, for the most part, 
+violating constraints on $\alpha$, $\beta$, and $\gamma$.
+If the LINEX model were made to respect the constraints on $\alpha$, $\beta$, and $\gamma$,
+it would fit worse than it already does for those countries where
+the constraints are violated (that is, for every country except Iran).
+We did nothing to correct this situation, because it is not clear what could be done.
+Constraining $\alpha = 0$ in the case of China would imply that either
+$a_0$ or $c_t$ or both varied with time.
+At that point, $a_0$ and $c_t$ are no longer fitted parameters of the model, 
+and we have a different model: it is no longer LINEX.
+
 %++++++++++++++++++++++++++++++

### 2014-06-19 Article/EconGrowth2.Rnw
Changed height of Iran graph.

@@
 
-<<LINEX_abg_traj_graph_IR, fig.pos="H", fig.align='center', fig.width=3, fig.height=2, fig.cap="LINEX trajectory for Iran.">>=
+<<LINEX_abg_traj_graph_IR, fig.pos="H", fig.align='center', fig.width=3, fig.height=1.7, fig.cap="LINEX trajectory for Iran.">>=
 dataIR <- fortify(OrigModels$IR$linex$`iK+iL+iQ`)

### 2014-06-20 Article/EconGrowth2.Rnw
Different size of trajectory graph.

--- 2014-06-19 Article/EconGrowth2.Rnw
@@
 
-<<LINEX_abg_traj_graph_IR, fig.pos="H", fig.align='center', fig.width=3, fig.height=2, fig.cap="LINEX trajectory for Iran.">>=
+<<LINEX_abg_traj_graph_IR, fig.pos="H", fig.align='center', fig.width=3, fig.height=1.5, fig.cap="LINEX trajectory for Iran.">>=
 dataIR <- fortify(OrigModels$IR$linex$`iK+iL+iQ`)

### 2014-07-09 Article_JAE_2014/ZAGrowth_JAE.Rnw
Now using nestStr and nestStrParen where appropriate.

@@
 <<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=5, fig.height=3, fig.cap="Cobb-Douglas fitted models.">>=
-cdFittedData_ZA <- filter(fitted_df_ZA, model=="cd", nest %in% c("iK+iL", "iK+iL+iQ"))
+cdFittedData_ZA <- filter(fitted_df_ZA, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iQ"))
 spaghettiPlot(data=cdFittedData_ZA, facet_formula=Country~energy, level=spaghettiGraphLevel) +
@@
 cesCoeffsData_ZA <- filter(coeffs_df_ZA, model=="ces", nestStr %in% c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"))
-standardScatterPlot(data=cesCoeffsData_ZA, mapping=aes(gamma_coef, lambda), facet_formula=country~nest, alpha=0.05) +
+standardScatterPlot(data=cesCoeffsData_ZA, mapping=aes(gamma_coef, lambda), 
+    facet_formula=country~nestStrParen, alpha=0.05) +
     scale_x_continuous(breaks=c(0.95, 1.0, 1.05)) +
@@
 <<CES_sigma1_delta1_graph, fig.pos="H", fig.align='center', fig.width=5, fig.height=3, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with various nestings.">>=
-standardScatterPlot(data=cesCoeffsData_ZA, mapping=aes(delta_1, sigma_1), facet_formula=country~nest, alpha=0.05) +
+standardScatterPlot(data=cesCoeffsData_ZA, mapping=aes(delta_1, sigma_1), 
+    facet_formula=country~nestStrParen, alpha=0.05) +
     coord_trans(y="sigma") +
@@
 standardScatterPlot(data=subset(cesCoeffsData_ZA, nestStr != "iK+iL"),
-                    mapping=aes(delta, sigma), facet_formula=country~nest, alpha=0.05) +
+                    mapping=aes(delta, sigma), facet_formula=country~nestStrParen, alpha=0.05) +
     coord_trans(y="sigma") +
@@
 <<CES_ternary_graph, fig.pos="H", fig.align='center', fig.width=5, fig.height=3, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models with various nestings.">>=
-standardTriPlot(data=cesCoeffsData_ZA, facet_formula=country~nest)
+standardTriPlot(data=cesCoeffsData_ZA, facet_formula=country~nestStrParen)
 @
@@
 <<CES_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=5, fig.height=3, fig.cap="CES fitted models with various nestings.">>=
-cesFittedData_ZA <- filter(fitted_df_ZA, model=="ces", nest %in% c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"))
-spaghettiPlot(data=cesFittedData_ZA, facet_formula=Country~nest, level=spaghettiGraphLevel) +
+cesFittedData_ZA <- filter(fitted_df_ZA, model=="ces", nestStr %in% c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"))
+spaghettiPlot(data=cesFittedData_ZA, facet_formula=Country~nestStrParen, level=spaghettiGraphLevel) +
     labs(y="Indexed GDP (1991=1)")

### 2014-07-10 Article_JAE_2014/ZAGrowth_JAE.Rnw
Changed Econ2011 to Calvin2011 everywhere in our code.

@@
 # Load historical data
-historicalData <- Econ2011 # From the EconData package
+historicalData <- Calvin2011 # From the EconData package
 historicalData <- subset(historicalData, subset=Country=="ZA")

### 2014-07-10 Scripts/BaseModels.R

@@ -19,8 +19,8 @@ require(plyr)  # for rbind.fill()
 
 nestStr <- function(nest) paste(nest, collapse="")
 
-All <- Econ2011
-# All <- rbind(Econ2011, Warr2000)
+All <- Calvin2011
+# All <- rbind(Calvin2011, Warr2000)
 # All <- AllHistData
 Countries <- levels(All$Country)
 Databases <- levels(All$Database)

### 2014-07-10 Testing/RefactorTesting.R

@@ -1,8 +1,8 @@
-require(EconModels2)
+require(EconModels)
 require(EconData)
 
-data(Econ2011)
-All <- Econ2011
+data(Calvin2011)
+All <- Calvin2011
 
 model.cd1 <-  cdwoeModel( response = iY, capital=iK, labor=iL, time=iYear, data=subset(All, Country=="US") )
 naturalCoef( model.cd1 )

### 2014-07-10 batchEcon.R

@@ -162,7 +162,7 @@ cat('\n')
 
 # load historical data
 # All <- read.table(file="data/AllData.txt", header=TRUE)
-All <- Econ2011
+All <- Calvin2011
 
 registerDoParallel()
 # print(ModelInfos)

### 2014-07-10 Scripts/BaseModels.R
Econ2011 (Calvin2011) and Warr2000 are gone. We are how using an AllHistData object that has both.

@@ -19,11 +19,10 @@ require(plyr)  # for rbind.fill()
 
 nestStr <- function(nest) paste(nest, collapse="")
 
-All <- Calvin2011
-# All <- rbind(Calvin2011, Warr2000)
+All <- subset(AllHistData, subset=Source=="Calvin2011")
 # All <- AllHistData
 Countries <- levels(All$Country)
-Databases <- levels(All$Database)
+Sources <- levels(All$Source)
 Energies <- c("iQ", "iX", "iU")
 
 ModelInfos <- list(

### 2014-07-10 Scripts/PreProcess.R

@@ -25,21 +25,6 @@ datadir <- file.path("Packages", "EconData", "data")
 # Load historical data sets and save the data frames.
 #
 cat("Loading and saving historical data..."); cat("\n")
-# I would like to do the following. 
-# But, the data frames get stored with the name "data", and, 
-# thus, collide with each other.
-# databases <- c("Calvin2011", "Warr2000")
-# for (file in databases){
-#   cat("  "); cat(file); cat("\n")
-#   infile <- paste0(file, ".txt")
-#   outfile <- paste0(file, ".rda")
-#   data <- read.table(file.path("data", infile), header=TRUE)
-#   # Get the countries that are in this database, in the order we'd like the levels
-#   CountryLevels <- countryAbbrevs[countryAbbrevs %in% levels(data$Country)]
-#   # Releve the country column
-#   for (lev in rev(CountryLevels)) { data$Country <- relevel(data$Country, ref=lev) }
-#   save(data, file=file.path(datadir, outfile), compress="gzip")
-# }
 
 Calvin2011 <- read.table(file.path("data", "Calvin2011.txt"), header=TRUE)
 Warr2000 <- read.table(file.path("data", "Warr2000.txt"), header=TRUE)
@@ -51,8 +36,6 @@ for (data in sources){
   for (lev in rev(CountryLevels)) { data$Country <- relevel(data$Country, ref=lev) }
 }
 AllHistData <- rbind(Calvin2011, Warr2000)
-save(Calvin2011,    file=file.path(datadir, "Calvin2011.rda"),    compress="gzip")
-save(Warr2000,    file=file.path(datadir, "Warr2000.rda"),    compress="gzip")
 save(AllHistData, file=file.path(datadir, "AllHistData.rda"), compress="gzip")
 
 #

### 2014-07-11 Article/EconGrowth2.Rnw
Changed Econ2011 to Calvin2011 everywhere in our code.
Econ2011 (Calvin2011) and Warr2000 are gone. We are how using an AllHistData object that has both.
Updated discussion of dealing with constraints. The article still contained a description of our previous method of dealing with constraints.

--- 2014-06-19 Article/EconGrowth2.Rnw
@@
 ninePanelScatterGraphHeight <- maxHeight # Inches
-# ninePanelTernaryGraphHeight <- 7 # Inches
-# ninePanelSpaghettiGraphHeight <- 7 # Inches
 
@@
 fourPanelScatterGraphWidth <- maxWidth # Inches
-# threePanelScatterGraphWidth <- maxWidth*0.75 # Inches
-# onePanelScatterGraphWidth <- maxWidth*0.25
-# fourPanelTernaryGraphWidth <- maxWidth
-# twoPanelTernaryGraphWidth <- maxWidth*0.45
-# fourPanelSpaghettiGraphWidth <- maxWidth
-# twoPanelSpaghettiGraphWidth <- maxWidth*0.55
-# onePanelSpaghettiGraphWidth <- maxWidth*0.4
 
@@
 presentationGraph1ColWidth <- 2*presentationGraph2ColWidth
-# keyTextSize <- 0.85 # 85% of normal size
-# keyColumns <- 1 # Want only 1 column in the key for lattice graphs
-# defaultKeyXLoc <- 0.01 # x position of the key. This default is good for 9-panel graphs.
-# defaultKeyYLoc <- 0.95 # y position of the key. This default is good for 9-panel graphs.
-# Parameter graphs are tricky to ensure same size. I've found that with height set to 5 in for the 
-# cd graphs and 2.93 in for the sf graphs, I get a nearly-exact match with graph size. From these settings I 
-# can set up 2 equations:
-#    5 in = 2*hgraph + haxis
-#    2.93 in = hgraph + haxis
-# to estimate that h_axis = 0.86 in and hgraph = 2.05 in.
 h_param_graph <- 2.07 # Inches for a single panel
@@
 # Relative path to historical data from Article
-historicalData <- Econ2011 # From the EconData package
+historicalData <- subset(AllHistData, subset=Source=="Calvin2011") # From the EconData package
 
@@
 
-**** Orignial introduction that MKH wrote ****
+**** Original introduction that MKH wrote ****
 
@@
 This production function can be expressed as
+%
 \begin{equation} \label{eq:CD}
@@
 \end{equation}
-where 
-\begin{itemize}
-	\item $y \equiv Y/Y_{0}$,  % why was 0 typeset as mathrm??
-	\item $k \equiv K/K_{0}$, 
-	\item $l \equiv L/L_{0}$, 
-	\item $Y$ represented by GDP, 
-	\item $K$ expressed in currency units, 
-	\item $L$ expressed in workers or work-hours/year, 
-	\item $t$ (time) is measured in years, 
-	\item e is the base of the natural logarithm, and 
-	\item 0 subscripts indicate values at an initial year.%
+%
+\noindent where 
+$y \equiv Y/Y_{0}$,
+$\theta$ is a scale parameter,
+e is the base of the natural logarithm, 
+$\lambda$ is represents the pace of technological progress,
+$t$ (time) is measured in years,
+$k \equiv K/K_{0}$, 
+$l \equiv L/L_{0}$, 
+$Y$ is represented by GDP, 
+$K$ is expressed in currency units, 
+$L$ is expressed in workers or work-hours/year, and
+0 subscripts indicate values at an initial year.%
 \footnote{Dimensionless, indexed quantities are represented by 
@@
 ($\alpha$, $\beta$, $\lambda$, $\theta$).}
-\end{itemize}
+
 %Mathematically, $A$ is nothing more than a fitting parameter 
@@
 can be augmented to include an energy term:
-
+%
 \begin{equation} \label{eq:CDe}
@@
 \end{equation}
+%
 where $e \equiv E/E_0$, and $E$ is in units of energy per time, typically TJ/year. 
@@
 functions of the following forms (among others):
-
+%
 \ceskl{\label{eq:CES}}
-
+%
 \ceskle{\label{eq:CESkle}}
-
+%
 \noindent Equation~\ref{eq:CES} is a CES production function with 
@@
 are possible with the CES model.
-
+%
 \ceslek{\label{eq:CESlek}}
-
+%
 \cesekl{\label{eq:CESekl}}
-
+%
 \noindent Note that the $\rho$ ($\sigma$) and $\delta$ parameters have different
 meanings that depend upon the nesting of the factors of production.
-**** Do we want to define different variables that indicate meaning, 
-such as $\sigma_{kl}, \sigma_{(kl)e}, \delta_{(ek)l}$, and the like? If so, we'll 
-need to translate from $\rho$ and $\sigma$ in \texttt{cesEst} to the correct
-variable names in the paper. ****
+% **** Do we want to define different variables that indicate meaning, 
+% such as $\sigma_{kl}, \sigma_{(kl)e}, \delta_{(ek)l}$, and the like? If so, we'll 
+% need to translate from $\rho$ and $\sigma$ in \texttt{cesEst} to the correct
+% variable names in the paper. ****
 
@@
 A third production function, the LINear EXponential (LINEX) function
+%
 \begin{equation} \label{eq:LINEX}
@@
 \end{equation}
+%
 was derived from thermodynamic considerations
@@
 \end{equation}
+%
 and
+%
 \begin{equation} \label{eq:rho_l}
@@
 \end{equation}
+%
 and represent 
+%
 (\ref{eq:rho_k}) capital stock increase relative to the average of labor and energy and 
@@
 The effect of energy ($e$) on production is enhanced if either
-
+%
 \begin{itemize}
@@
 ratio for people fifteen and older, total population, and a percentage 
-of people under fifteen for other economies (South Africa, China, Iran, 
-Saudi Arabia, Tanzania, and Zambia) for 1991--2011. The population 
+of people under fifteen for other economies 
+(China, South Africa, 
+Saudi Arabia, Iran, 
+Tanzania, and Zambia) 
+for 1991--2011. 
+The population 
 of people under fifteen years of age was subtracted from total population 
@@
 and renewable energy sources (solar, wind, geothermal, biomass/fuel wood, 
-and hydro). We also added human and animal muscle work. 
+and hydro). 
+We also added animal muscle work. 
+Following \citet{Ayres:2010ug}, 
+human muscle work is excluded from the energy time series,
+because it is counted as labor.
 Similar to the economic data discussed in 
@@
 Thermal energy ($Q$) for fuels (in units of TJ/year) was calculated by
-
+%
 \begin{equation} \label{eq:thermal_energy}
@@
 \end{equation}
-
+%
 \noindent where $C_{fuel}$ is the consumption rate of the fuel 
@@
 ft$^3$/year for dry natural gas and natural gas plant liquids, 
-and m$^3$/year for biomass/fuel wood) and $h_{{fuel}}$ is 
+and m$^3$/year for biomass and fuel wood) and $h_{{fuel}}$ is 
 the heat content of the fuel (in kJ/short ton for coal, kJ/barrel for oil, 
 kJ/ft$^3$ for dry natural gas and natural gas plant liquids, 
-and kJ/kg for biomass/fuel wood). Fuel wood density of 300~kg/m$^3$ 
+and kJ/kg for biomass and fuel wood). 
+Fuel wood density of 300~kg/m$^3$ 
 was taken from \citet{Ragland:2013wp} at the low end of the range 
@@
 (ethanol and biodiesel) were obtained from the \citet{EIA:2013a} 
-for all economies. Yearly average heat content data for coal, oil, 
+for all economies. 
+Yearly average heat content data for coal, oil, 
 and natural gas and natural gas plant liquids was obtained from the 
-EIA for all economies. We used lower (net) heating values of 
+\citet{EIA:2013a} for all economies. 
+We used lower (net) heating values of 
 26.8~MJ/kg \citep[Table~A-27]{Cengel:2011ww} and 37.8~MJ/kg 
 \citep[Table~7.3]{Gupta:2010vg} for the heat content of ethanol 
-and corn-based biodiesel, respectively. Yearly consumption and 
+and corn-based biodiesel, respectively. 
+Yearly consumption and 
 heat content data for biomass/fuel wood was obtained from the 
@@
 from animals ($Q_{animals}$) was calculated using
-
+%
 \begin{equation} \label{eq:animal_muscle}
@@
 \end{equation}
-
+%
 \noindent where $Q_m$ is metabolizable energy (in kcal/day-animal) 
@@
 
-Human muscle power was calculated in a similar manner:
-
-\begin{equation} \label{eq:human_muscle}
-  Q_{workers} = Q_{m,workers} N_{workers}
-\end{equation}
-
-\noindent where the value of $Q_{m,workers}$ is the ``the amount 
-of food available for human consumption'' (i.e., at the wholesale level) 
-taken from the 
-\citet[``\texttt{Dietary~Energy~Cons.~Countries}'' tab]{FAO:2013b}. 
-The value for $N_{workers}$ was obtained from the labor time series 
-for each economy as discussed in Section~\ref{sec:Labor_Data}.
-
-<<Historical_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=7.5, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), and thermal energy ($q$).">>=
-historicalPlot(historicalData)
-@
+% Human muscle power was calculated in a similar manner:
+% 
+% \begin{equation} \label{eq:human_muscle}
+%   Q_{workers} = Q_{m,workers} N_{workers}
+% \end{equation}
+% 
+% \noindent where the value of $Q_{m,workers}$ is the ``the amount 
+% of food available for human consumption'' (i.e., at the wholesale level) 
+% taken from the 
+% \citet[``\texttt{Dietary~Energy~Cons.~Countries}'' tab]{FAO:2013b}. 
+% The value for $N_{workers}$ was obtained from the labor time series 
+% for each economy as discussed in Section~\ref{sec:Labor_Data}.
 
@@
 \authNote{Do we want to discuss the covariances?}
+%
+<<Historical_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=7.5, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), and thermal energy ($q$).">>=
+historicalPlot(historicalData)
+@
 
@@
 Section~\ref{sec:Prod_Func_Forms} has parameters which must be estimated (fitted)
-using data for each economy (see Section~\ref{sec:Economy_Types}).
+using data for each economy (see Sections~\ref{sec:Economy_Types} and~\ref{sec:Sources_of_Data}).
 We obtained parameter estimates by applying the method of least-squares to 
@@
 Parameter estimates are chosen to minimize
-\[
-\sum_{i} (y_i - f(t,k,l,e; \theta) )^2
-\]
+%
+\begin{equation} \label{eq:sse}
+  sse = \sum_{i} (y_i - f(t,k,l,e; \theta) )^2
+\end{equation}
+%
 within constraints.
@@
 \]
-and the residuals
+and the residuals ($r_i$)
 as the difference between the observed response and the fitted response
+%
 \begin{equation} \label{eq:residual}
@@
 \end{equation}
-The details for each of the models (including the effects of using 
-log transformations) are discussed below.
-
-%After back transforming to the natural scale of the data, the 
-%residuals have a multiplicative rather than additive affect.
-%The reflects an assumption that variability in GDP is roughly 
-%proportion to GDP rather than constant.
+%
+The details for each of the models are discussed in 
+Sections~\ref{sec:CD_Parameter_Estimation}--\ref{sec:LINEX_Parameter_Estimation} below.
 
@@
 
-Bootstrappng is a statistical resampling technique for assigning
+Bootstrapping is a statistical resampling technique for assigning
 measures of accuracy and precision to sample estimates by measuring
@@
 In the context of linear models (regression), resamples are generally created
-by residual resampling.  In our case, we formed resamples by adding to the fitted 
+by residual resampling.  
+In our case, we formed resamples by adding to the fitted 
 response ($\hat{y}$) the product of a residual from the original model fit and 
@@
 Intuitively, this method assumes that the residuals are indicative of 
-the variability (from many potential sources) inherent in the data so that
+the variability (from many potential sources) inherent in the data such that
 it would be unsurprising if the residual from 
@@
 \]
-both the sign ($\pm$) and the index of the residual ($j$, typically different from $i$) 
+both the sign ($\pm$) and the index of the residual 
+($j$,~typically different from $i$) 
 are chosen at random (with replacement). 
-% Resampling in this way has the consequence 
-% that a resampled time series could have non-unity first-year GDP ($\tilde Y_1 \neq 1$),
-% so a renormalization takes place using the initial GDP from the
-% resampled data as the new baseline, not the observed GDP in year 1.
-% \begin{equation} \label{eq:resample_y}
-% 	\tilde y_i  = \frac{\tilde Y_i'}{\tilde Y_1'}
-% \end{equation}
-% to obtain a resampled indexed GDP time series.
 We repeated the resampling process 1000 times for each
@@
 or correlations between parameter estimates.
-\authNote{This is not precisely true:
-Large residuals in the fit to historical data (the ``base fit'')
-are expected to produce large variation in resample coefficient values
-(when the resampling is repeated 1000 times),
-indicating less certainty in the value
-of those coefficients. 
-Similarly, small base fit residuals are expected to produce small
-variation in resample coefficient values, indicating more-precise knowledge
-of the model coefficients.
---rjp}
 
@@
 
-\authNote{Should the description of model fitting come before or after 
-the description of resampling?}
-
 %++++++++++++++++++++++++++++++
@@
 reparameterized as
-
+%
 \begin{equation} \label{eq:CD_reparam}
@@
 \end{equation}
-
+%
 \noindent to ensure $\alpha + \beta = 1$ for constant returns to scale. 
-$\lambda$ and $\alpha$ were estimated by the 
+$\theta$, $\lambda$, and $\alpha$ were estimated by the 
 \texttt{R} \citep{R} function \texttt{lm} in log-transform space. 
@@
 
-To estimate the parameters $\lambda$, $\alpha$, $\beta$, and $\gamma$ 
+To estimate the parameters $\theta$, $\lambda$, $\alpha$, $\beta$, and $\gamma$ 
 in the energy-augmented Cobb-Douglas model, Equation~\ref{eq:CDe} 
 was reparameterized as
-
+%
 \begin{equation} \label{eq:CDe_AB_reparam}
-  y = \theta \mathrm{e}^{\lambda (t-t_0)} k^{\min(a,b)} l^{|b-a|} e^{1 - \max(a,b)}
+  y = \theta \mathrm{e}^{\lambda (t-t_0)} k^{\alpha} l^{\beta} e^{1 - \alpha - \beta}
 \end{equation}
-
-\noindent with 
-$\alpha = \min(a,b)$, 
-$\beta = |b-a|$, and 
-$\gamma = 1 - \max(a,b)$.
-The reparameterization ensures that $\alpha + \beta + \gamma = 1$,
+%
+\noindent ensuring that $\alpha + \beta + \gamma = 1$,
 thereby providing constant returns to scale.
 The \texttt{R} \citep{R} function \texttt{lm} was used to estimate 
-values of $\lambda$, $a$, and $b$ in log-transform space.
-If the fitted value for $a$ ($b$) fell outside the range $[0,1]$, it was 
-set equal to its boundary value and both $\lambda$ and $b$ ($a$) 
-were re-estimated.
-
-% The \texttt{nls} parameter estimation algorithm can encounter convergence difficulty 
-% when the optimal value for the parameter represented by the absolute value function 
-% (in Equation~\ref{eq:CDe_AB_reparam}, $\beta$) 
-% lies near a boundary. If the absolute value exponent caused non-convergence of the 
-% \texttt{nls} function, second and, if necessary, third reparameterizations 
-% were attempted:
-% 
-% \begin{equation} \label{eq:CDe_CD_reparam}
-%   y = A k^{1 - \max(c,d)} l^{\min(c,d)} e^{|d-c|}; A = \mathrm{e}^{\lambda (t-t_0)}
-% \end{equation}
-% 
-% \begin{equation} \label{eq:CDe_FG_reparam}
-%   y = A k^{|g-f|} l^{1 - \max(f,g)} e^{\min(f,g)}; A = \mathrm{e}^{\lambda (t-t_0)}
-% \end{equation}
-% 
-% \noindent If none of the three reparameterizations converged, 
-% the parameterization with the smallest sum of square errors ($sse$)
-% was used. \ref{sec:Convergence_Resample_Models} shows the 
-% fraction of unconverged models for each model type. 
-% The above approach resulted in very few unconverged
-% Cobb-Douglas resample models, even with \Sexpr{numResamples()} resamples.
+values of $\lambda$, $\theta$, $\alpha$, and $\beta$ in log-transform space.
+If the fitted value for $\alpha$ or $\beta$ fell outside the interval $[0,1]$,
+we fit along all boundaries 
+($\alpha = 1$,
+$\beta = 1$,
+$\gamma = 1$,
+$\alpha = 0$,
+$\beta = 0$, and
+$\gamma = 0$)
+and chose the boundary fit with
+minimum $sse$ (Equation~\ref{eq:sse}) as the winner.
+$\gamma$ was recovered with $\gamma = 1 - \alpha - \beta$.
 
@@
 in our testing, nearly always violated them, often returning
-negative values for elasticity of substitution ($\sigma$) parameters.
+negative values for elasticity of substitution~($\sigma$) parameters.
 Thus, we used the two fitting algorithms available in \texttt{cesEst} that
@@
 The start values for fitting parameters are taken from 
-the grid search fit that provided the lowest $sse$.
+the grid search fit that provided the lowest $sse$ (Equation~\ref{eq:sse}).
 
@@
 Therefore, we transformed the LINEX model into
-
+%
 \begin{equation} \label{eq:LINEX_transformed}
-  y = Ae; 
+  y = \theta A e; 
   A = \mathrm{e}^{\left[2 a_0 \left(1 - \frac{1}{\rho_k} \right) 
@@
 \end{equation}
-
+%
 \noindent where $a_1 \equiv a_0 c_t$. 
@@
 If the trajectory stays within the triangle, 
-the constraints of $\alpha > 0$, $\beta > 0$, and $\gamma > 0$ are respected.  
+the constraints on $\alpha$, $\beta$, and $\gamma$ are respected.
 Conversely, if the trajectory goes outside the triangle, one of the constraints has been violated.
 
-The following graphs shows trajectories for China and Iran.
+Figures~\ref{fig:LINEX_abg_traj_graph_CN} and~\ref{fig:LINEX_abg_traj_graph_IR} 
+show trajectories for China and Iran, respectively.
+**** Can we make a figure that has all 9 graphs in it? --MKH ****
 
 <<LINEX_abg_traj_graph_CN, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="LINEX trajectory for China.">>=
-dataCN <- fortify(OrigModels$CN$linex$`iK+iL+iQ`)
+dataCN <- fortify(OrigModels$Calvin2011$CN$linex$`iK+iL+iQ`)
 triPlot(data=dataCN, grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1990")
@@
 
-<<LINEX_abg_traj_graph_IR, fig.pos="H", fig.align='center', fig.width=3, fig.height=2, fig.cap="LINEX trajectory for Iran.">>=
-dataIR <- fortify(OrigModels$IR$linex$`iK+iL+iQ`)
+<<LINEX_abg_traj_graph_IR, fig.pos="H", fig.align='center', fig.width=3, fig.height=1.5, fig.cap="LINEX trajectory for Iran.">>=
+dataIR <- fortify(OrigModels$Calvin2011$IR$linex$`iK+iL+iQ`)
 triPlot(data=dataIR, grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1990")
@@
 
-Iran is the only country for which the trajecotry stays within the triangle for the 
-entire time period.
-Thus, in our fitted models, the LINEX model is, for the most part, 
+In our testing, Iran is the only country for which the trajectory stays within 
+the constraint triangle for the entire time period.
+Thus, in our fitted models, the LINEX model is nearly always
 violating constraints on $\alpha$, $\beta$, and $\gamma$.
-If the LINEX model were made to respect the constraints on $\alpha$, $\beta$, and $\gamma$,
+If the LINEX model were made to respect the constraints,
 it would fit worse than it already does for those countries where
 the constraints are violated (that is, for every country except Iran).
-We did nothing to correct this situation, because it is not clear what could be done.
-Constraining $\alpha = 0$ in the case of China would imply that either
-$a_0$ or $c_t$ or both varied with time.
-At that point, $a_0$ and $c_t$ are no longer fitted parameters of the model, 
-and we have a different model: it is no longer LINEX.
+We did nothing to correct this situation, because it is not clear what should be done.
+\citet{Warr:2012cg} constrained the values of $a_0$ and $c_t$, while still holding them constant
+for the entire time series, such that the constraints on $\alpha$, $\beta$, and $\gamma$
+were respected.
+But, Warr's approach necessarily leads to larger $sse$ values than unconstrained fitting.
+Because unconstrained LINEX models already fit worse than 
+constrained Cobb-Douglas and CES models,
+we chose to report the unconstrained LINEX model fits in this paper.
+% Constraining $\alpha = 0$ in the case of China would imply that either
+% $a_0$ or $c_t$ or both varied with time.
+% At that point, $a_0$ and $c_t$ are no longer fitted parameters of the model, 
+% and we have a different model: it is no longer LINEX.
 
@@
 **** Include a table here of important values. 
-Include a table of convergence? (In appendix?)
 Martin to suggest the form of this table after working 

### 2014-07-22 Article_JAE_2014/ZAGrowth_JAE.Rnw

--- 2014-07-09 Article_JAE_2014/ZAGrowth_JAE.Rnw
@@
 # Load historical data
-historicalData <- Econ2011 # From the EconData package
-historicalData <- subset(historicalData, subset=Country=="ZA")
+historicalData <- subset(AllHistData, subset=Source=="Calvin2011" & Country=="ZA") # From the EconData package
+# historicalData <- subset(historicalData, subset=Country=="ZA")
 

### 2014-07-23 Article/EconGrowth2.Rnw
Papers now use Calvin data frame from the EconData package.

@@
 # Load historical data
-# In Rstudio, this paper is generated from it's directory, which is "Article".
-# We need to define paths relative to the location of the paper. 
-# Relative path to historical data from Article
-historicalData <- subset(AllHistData, subset=Source=="Calvin2011") # From the EconData package
-
+historicalData <- Calvin # From the EconData package
 # Load coefficients from all models in one large data frame

### 2014-07-25 Workflow/Workflow.Rmd
Now using .Rmd for Workflow file.

---
title: "Workflow"
author: "Matthew Kuperus Heun"
date: "July 25, 2014"
output: html_document
---

This file contains information about the workflow for analyses.

### Add new data
Add the file named `<Source>.txt` in the data directory.   
Edit the `Packages/EconData/R/Constants.R` file to include `<Source>` in the `dataSource` variable.   
Add any Excel workbooks or other metadata in `data/Excel Workbooks/<Source>`.

### Create historical data frame
Run `Scripts/PreProcess.R -S <Source>` to create the historical data frame for `<Source>`.    
The file will be stored at `Packages/EconData/data/<Source>.rda`.    
This command can be run on a laptop, because it is fast.    
Build and reload the EconData package.    
Push the changes to GitHub.   
On acc, Pull from GitHub.     
On dahl (node-00), say `install_github("MatthewHeun/Econ-Growth-R-Analysis/Packages/EconData")`.

### Create the batch script
Create the file `Scripts/<Source>_batch.bash` file.     
It is probably best to modify an existing `<Source>_batch.bash file.`      
Be sure to edit the `OUTDIR` variable to be `OUTDIR="$LOC_PATH/data_resample/<Source>"`     
Change the final line (the one that runs the `OrigModels.R script`) to be
`ssh node-xx "cd $LOC_PATH; Scripts/OrigModels.R -S <Source> &> $OUTDIR/node-xx.txt" &`        
Distribute the work over the nodes in a way that makes sense.
Push the file to GitHub.      
On dahl, pull from GitHub.

### Submit the job to dahl
Run `Scripts/<Source>_batch.bash` on dahl.

### Post-process the results
Run `PostProcess.R -R data_resample/<Source>` on dahl to create
`Packages/EconData/data/<Source>_Coeffs.rda` and
`Packages/EconData/data/<Source>_Fitted.rda`.
Note that this command will need to be issued from a node of the cluster, not from `fs1.calvin.edu`.

### Add to EconData package
From acc, push the changes to GitHub to make the new files available.
Pull from GitHub on a local laptop, and rebuild the `EconData` package.
At this point, all new results should be available in the `EconData` package.

### 2014-07-25 Workflow/Workflow.Rmd
Improved Workflow.Rmd file. Added bulleted lists.

@@
 ### Add new data
-Add the file named `<Source>.txt` in the data directory.   
-Edit the `Packages/EconData/R/Constants.R` file to include `<Source>` in the `dataSource` variable.   
-Add any Excel workbooks or other metadata in `data/Excel Workbooks/<Source>`.
+* Add the file named `<Source>.txt` in the data directory.   
+* Edit the `Packages/EconData/R/Constants.R` file to include `<Source>` in the `dataSource` variable.   
+* Add any Excel workbooks or other metadata in `data/Excel Workbooks/<Source>`.
 
 ### Create historical data frame
-Run `Scripts/PreProcess.R -S <Source>` to create the historical data frame for `<Source>`.    
+* Run `Scripts/PreProcess.R -S <Source>` to create the historical data frame for `<Source>`.
 The file will be stored at `Packages/EconData/data/<Source>.rda`.
 This command can be run on a laptop, because it is fast.    
-Build and reload the EconData package.    
-Push the changes to GitHub.   
-On acc, Pull from GitHub.     
-On dahl (node-00), say `install_github("MatthewHeun/Econ-Growth-R-Analysis/Packages/EconData")`.
+* Build and reload the EconData package.    
+* Push the changes to GitHub.   
+* On acc, Pull from GitHub.     
+* On dahl (node-00), say `install_github("MatthewHeun/Econ-Growth-R-Analysis/Packages/EconData")`.
 
 ### Create the batch script
-Create the file `Scripts/<Source>_batch.bash` file.     
-It is probably best to modify an existing `<Source>_batch.bash file.`      
-Be sure to edit the `OUTDIR` variable to be `OUTDIR="$LOC_PATH/data_resample/<Source>"`     
-Change the final line (the one that runs the `OrigModels.R script`) to be
+* Create the file `Scripts/<Source>_batch.bash` file.
+  + It is probably best to modify an existing `<Source>_batch.bash file.`      
+  + Be sure to edit the `OUTDIR` variable to be `OUTDIR="$LOC_PATH/data_resample/<Source>"`     
+  + Change the final line (the one that runs the `OrigModels.R script`) to be
 `ssh node-xx "cd $LOC_PATH; Scripts/OrigModels.R -S <Source> &> $OUTDIR/node-xx.txt" &`        
-Distribute the work over the nodes in a way that makes sense.
-Push the file to GitHub.      
-On dahl, pull from GitHub.
+  + Distribute the work over the nodes in a way that makes sense.
+* Push the file to GitHub.      
+* On dahl, pull from GitHub.
 
 ### Submit the job to dahl
-Run `Scripts/<Source>_batch.bash` on dahl.
+* Start with `Scripts/<Source>_batch.bash "-n 2 -C"`.
+* Then do `Scripts/<Source>_batch.bash "-n 1000 -C"`.
 
 ### Post-process the results
-Run `PostProcess.R -R data_resample/<Source>` on dahl to create
+* Run `PostProcess.R -R data_resample/<Source>` on dahl to create
 `Packages/EconData/data/<Source>_Coeffs.rda` and
 `Packages/EconData/data/<Source>_Fitted.rda`.
-Note that this command will need to be issued from a node of the cluster, not from `fs1.calvin.edu`.
+Note that this command will need to be issued from a node of the cluster (e.g., node-00), not from `fs1.calvin.edu`.
 
 ### Add to EconData package
-From acc, push the changes to GitHub to make the new files available.
-Pull from GitHub on a local laptop, and rebuild the `EconData` package.
+* From acc, push the changes to GitHub to make the new files available.
+* Pull from GitHub on a local laptop, and rebuild the `EconData` package.
+
 At this point, all new results should be available in the `EconData` package.

### 2014-07-26 Workflow/Workflow.Rmd
Updates to Workflow.Rmd.

@@
 ### Add new data
-* Add the file named `<Source>.txt` in the data directory.   
+* Add a file named `<Source>.txt` in the data directory.   
 * Edit the `Packages/EconData/R/Constants.R` file to include `<Source>` in the `dataSource` variable.   
@@
 The file will be stored at `Packages/EconData/data/<Source>.rda`.
-This command can be run on a laptop, because it is fast.    
-* Build and reload the EconData package.    
+This command is fast; it can be run on a laptop.    
+* Build and reload the `EconData` package.    
 * Push the changes to GitHub.   
@@
 * On dahl (node-00), say `install_github("MatthewHeun/Econ-Growth-R-Analysis/Packages/EconData")`.   
+This command doesn't work on fs1 or any of the nodes (node-01 through node-42).
 
@@
 * Create the file `Scripts/<Source>_batch.bash` file.
-  + It is probably best to modify an existing `<Source>_batch.bash file.`      
-  + Be sure to edit the `OUTDIR` variable to be `OUTDIR="$LOC_PATH/data_resample/<Source>"`     
-  + Change the final line (the one that runs the `OrigModels.R script`) to be
-`ssh node-xx "cd $LOC_PATH; Scripts/OrigModels.R -S <Source> &> $OUTDIR/node-xx.txt" &`        
+    + It is probably best to modify an existing `<Source>_batch.bash` file.      
+    + Be sure to edit the `OUTDIR` variable to be `OUTDIR="$LOC_PATH/data_resample/<Source>"`.
+    + Change the final line (the one that runs the `OrigModels.R script`) to be `ssh node-xx "cd $LOC_PATH; Scripts/OrigModels.R -S <Source> &> $OUTDIR/node-xx.txt" &`.   
     + Distribute the work over the nodes in a way that makes sense.
-* Push the file to GitHub.      
-* On dahl, pull from GitHub.
+* Push the `<Source>_batch.bash` file to GitHub.
+* On acc, Pull from GitHub.
 
 ### Submit the job to dahl
-* Start with `Scripts/<Source>_batch.bash "-n 2 -C"`.
-* Then do `Scripts/<Source>_batch.bash "-n 1000 -C"`.
+* `cd` to the `Econ-Growth-R-Analysis` directory from fs1.calvin.edu.
+* Run `Scripts/<Source>_batch.bash "-n 2 -C"` to test that things work as expected.
+* Then do `Scripts/<Source>_batch.bash "-n 1000 -C"` to do a complete run.
+* Check dahl's status at (http://fs1.calvin.edu/ganglia/?m=load_one&r=hour&s=by%2520name&c=dahl&h=&sh=1&hc=4&z=small).
+* Check progress with `more data_resample/<Source>/node-*.txt`.
 
 ### Post-process the results
-* Run `PostProcess.R -R data_resample/<Source>` on dahl to create
-`Packages/EconData/data/<Source>_Coeffs.rda` and
-`Packages/EconData/data/<Source>_Fitted.rda`.
+* Run `PostProcess.R -R data_resample/<Source>` on dahl to create:       
+    + `Packages/EconData/data/<Source>_Coeffs.rda` and
+    + `Packages/EconData/data/<Source>_Fitted.rda`.
+
 Note that this command will need to be issued from a node of the cluster (e.g., node-00), not from `fs1.calvin.edu`.
 
-### Add to EconData package
+### Add processed results to the EconData package
 * From acc, push the changes to GitHub to make the new files available.
-* Pull from GitHub on a local laptop, and rebuild the `EconData` package.
+* Pull from GitHub on a local laptop, and build and reload the `EconData` package.
 
 At this point, all new results should be available in the `EconData` package.
+Objects will be named:
+
+* `<Source>_Coeffs` (from the file `Packages/EconData/data/<Source>_Coeffs.rda`)  
+* `<Source>_Fitted` (from the file `Packages/EconData/data/<Source>_Fitted.rda`)  
+* `<Source>_OrigModels` (from the file `Packages/EconData/data/<Source>_OrigModels.rda`)

### 2014-07-26 Workflow/Workflow.Rmd
More improvements to Workflow.Rmd.

@@
 ### Post-process the results
-* Run `PostProcess.R -R data_resample/<Source>` on dahl to create:       
+* Run `PostProcess.R -R data_resample/<Source>` on a node of dahl to create:       
     + `Packages/EconData/data/<Source>_Coeffs.rda` and
@@
 Note that this command will need to be issued from a node of the cluster (e.g., node-00), not from `fs1.calvin.edu`.
+`fs1` does not have a full install of R.
 

### 2014-07-29 Workflow/Workflow.Rmd
Added Scripts/ to PostProcess.R call.

@@
 ### Post-process the results
-* Run `PostProcess.R -R data_resample/<Source>` on a node of dahl to create:       
+* Run `Scripts/PostProcess.R -R data_resample/<Source>` on a node of dahl to create:       
     + `Packages/EconData/data/<Source>_Coeffs.rda` and

### 2014-07-29 Workflow/Workflow.Rmd
Workflow now accounts for DownloadResults.R

@@
 author: "Matthew Kuperus Heun"
-date: "July 25, 2014"
+date: "29 July 2014"
 output: html_document
@@
 ### Add new data
-* Add a file named `<Source>.txt` in the data directory.   
-* Edit the `Packages/EconData/R/Constants.R` file to include `<Source>` in the `dataSource` variable.   
+* Add a file that contains the historical data from `<Source>` (name should be `<Source>.txt`) 
+in the `data` directory at the top level of the repository.   
 * Add any Excel workbooks or other metadata in `data/Excel Workbooks/<Source>`.
@@
 * On acc, Pull from GitHub.     
-* On dahl (node-00), say `install_github("MatthewHeun/Econ-Growth-R-Analysis/Packages/EconData")`.   
-This command doesn't work on fs1 or any of the nodes (node-01 through node-42).
+* On node-00, say `install_github("MatthewHeun/Econ-Growth-R-Analysis/Packages/EconData")`.
+This makes the historical data available to the nodes of dahl.
+This command doesn't work from fs1 or any of the other nodes of dahl (node-01 through node-42).
 
@@
 
+### Download post-processed results to local machine
+* From a local computer, say `Scripts/DownloadResults.R -u <user> -S <Source> -d`, where `<user>` is 
+a username on dahl, `<Source>` is the data source of interest, and `-d` will 
+print the files to be transferred to the local machine, rather than transfer them.
+* Verify that the list of files to be transferred looks right.
+* From a local computer, say `Scripts/DownloadResults.R -u <user> -S <Source>` to download the files.
+
 ### Add processed results to the EconData package
-* From acc, push the changes to GitHub to make the new files available.
-* Pull from GitHub on a local laptop, and build and reload the `EconData` package.
+* On the local machine, build and reload the `EconData` package.
 
-At this point, all new results should be available in the `EconData` package.
+At this point, all new results should be available in the `EconData` package on the local machine.
 Objects will be named:
@@
 * `<Source>_Fitted` (from the file `Packages/EconData/data/<Source>_Fitted.rda`)  
-* `<Source>_OrigModels` (from the file `Packages/EconData/data/<Source>_OrigModels.rda`)
+* `<Source>_Models` (from the file `Packages/EconData/data/<Source>_OrigModels.rda`)

### 2014-07-29 Article/EconGrowth2-GraphsOnly.Rnw
Changed Econ2011 to Calvin2011 everywhere in our code.
Econ2011 (Calvin2011) and Warr2000 are gone. We are how using an AllHistData object that has both.
Papers now use Calvin data frame from the EconData package.
Articles now use the new results structure.

@@
 # Relative path to historical data from Article
-historicalData <- Econ2011 # From the EconData package
+historicalData <- Calvin # From the EconData package
 
 # Load coefficients from all models in one large data frame
-coeffs_df <- tbl_df(AllCoef)
+coeffs_df <- tbl_df(Calvin_Coeffs)
 # Load fitted data from all models in one large data frame
-fitted_df <- tbl_df(AllFitted)
+fitted_df <- tbl_df(Calvin_Fitted)
 
 # Load the original models.
-oModels <- OrigModels
+oModels <- Calvin_Models
 
@@
 <<LINEX_abg_traj_graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="LINEX trajectory for China with thermal energy $q$.">>=
-data <- fortify(OrigModels$CN$linex$`iK+iL+iQ`)
+data <- fortify(oModels$Calvin$CN$linex$`iK+iL+iQ`)
 triPlot(data=data, grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear")

### 2014-07-29 Articles/Article_EnerEcon_2014/EconGrowth2.Rnw
Articles now in "Articles" directory.

--- 2014-07-23 Article/EconGrowth2.Rnw
@@
 # Load coefficients from all models in one large data frame
-coeffs_df <- tbl_df(AllCoef)
+coeffs_df <- tbl_df(Calvin_Coeffs)
 # Load fitted data from all models in one large data frame
-fitted_df <- tbl_df(AllFitted)
+fitted_df <- tbl_df(Calvin_Fitted)
 
 # Load the original models.
-oModels <- OrigModels
+oModels <- Calvin_Models
 @
@@
 <<LINEX_abg_traj_graph_CN, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="LINEX trajectory for China.">>=
-dataCN <- fortify(OrigModels$Calvin2011$CN$linex$`iK+iL+iQ`)
+dataCN <- fortify(oModels$Calvin$CN$linex$`iK+iL+iQ`)
 triPlot(data=dataCN, grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1990")
@@
 <<LINEX_abg_traj_graph_IR, fig.pos="H", fig.align='center', fig.width=3, fig.height=1.5, fig.cap="LINEX trajectory for Iran.">>=
-dataIR <- fortify(OrigModels$Calvin2011$IR$linex$`iK+iL+iQ`)
+dataIR <- fortify(oModels$Calvin$IR$linex$`iK+iL+iQ`)
 triPlot(data=dataIR, grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1990")

### 2014-07-29 Articles/Article_JAE_2014/ZAGrowth_JAE.Rnw
Articles now in "Articles" directory.

--- 2014-07-09 Article_JAE_2014/ZAGrowth_JAE.Rnw
@@
 # Load historical data
-historicalData <- Econ2011 # From the EconData package
-historicalData <- subset(historicalData, subset=Country=="ZA")
+historicalData <- Calvin # From the EconData package
 
 # Load coefficients from all models in one large data frame
-coeffs_df <- tbl_df(AllCoef)
+coeffs_df <- tbl_df(Calvin_Coeffs)
 coeffs_df_ZA <- subset(coeffs_df, subset=country=="ZA")
 # Load fitted data from all models in one large data frame
-fitted_df <- tbl_df(AllFitted)
+fitted_df <- tbl_df(Calvin_Fitted)
 fitted_df_ZA <- subset(fitted_df, subset=Country=="ZA")
 # Load the original models.
-oModels_ZA <- OrigModels$ZA
+oModels_ZA <- Calvin_Models$ZA
 @

### 2014-07-29 Articles/Article_Heun_Warr_2014/EcolEcon_HeunWarr.Rnw
First draft of an article with REXS data.

--- 2014-07-29 Articles/Article_EnerEcon_2014/EconGrowth2.Rnw
@@
-% This article has been prepared for publication in Energy Economics in RStudio with knitr.
+% This article has been prepared for publication in **** in RStudio with knitr.
 % According to http://www.elsevier.com/author-schemas/the-elsarticle-latex-document-class, we should be using the
@@
 
-\usepackage[shownotes]{authNote}
-
-\journal{Energy Economics}
+\journal{Ecological Economics}
 
@@
 
-<<data, include=FALSE>>=
+<<data, include=FALSE, eval=TRUE>>=
 # Load historical data
-historicalData <- Calvin # From the EconData package
+historicalData <- REXS # From the EconData package
 # Load coefficients from all models in one large data frame
-coeffs_df <- tbl_df(Calvin_Coeffs)
+coeffs_df <- tbl_df(REXS_Coeffs)
 # Load fitted data from all models in one large data frame
-fitted_df <- tbl_df(Calvin_Fitted)
+fitted_df <- tbl_df(REXS_Fitted)
 
 # Load the original models.
-oModels <- Calvin_Models
+oModels <- REXS_Models
 @
@@
 
-\title{An Empirical Analysis of the Role of Energy in Economic Growth}
+\title{Application of Bootstrap Resampling to REXS Data}
 
@@
 \ead{mkh2@calvin.edu}
+\author[BenWarr]{Benjamin Warr}
 \author[Stellenbosch]{Martin de Wit}
 \author[CalvinMath]{Randall J. Pruim}
-\author[CalvinEngr]{Caleb Reese}
-\author[CalvinEngr]{Lucas Timmer}
 
@@
 \address[CalvinMath]{Mathematics \& Statistics Department, Calvin College, Grand Rapids, MI 49546, USA}
+\address[BenWarr]{Ben Warr's address, Zambia}
 
@@
 
-**** Notes on the introduction from Martin ****
-
-1. Set scene through energy economic modelling papers. 
-Point out that PF approaches are alive and well (Stern, Tol, Gerlagh, World Bank, IMF), 
-short lit review as part of a longer introduction.  
-Mention competing PF approaches and parameter choice. 
-On what basis selection and how estimate parameters?
-
-2. Point out the need for adequate statistical testing and economic interpretation, 
-citing some earlier critical papers on PF limitations. Take issue with
-
-3. Spell out the contribution we will be making in this paper, 
-we are taking the approach that all models are wrong but some are useful. 
-We are after generating insights even after deeper assumptions of econ growth theory are very limiting.
-
-4. Introduce coordinates of analysis.
-
-**** Original introduction that MKH wrote ****
-
-Neoclassical economic growth theory attributes output ($Y$) to factors of production:
-capital stock ($K$) and labor ($L$). The Cobb-Douglas production function 
-is the 
-canonical representation of indexed economic output ($y$) as a function of indexed 
-labor ($l$), indexed capital stock ($k$), and an additional exogenous, time-dependent 
-term.%
-\footnote{The time-dependent term in production functions is often linked
-to ``technological progress,'' but that is a very narrow reading of Solow's original intent:
-\begin{quote}
-  It will be seen that I am using the phrase ``technical change''
-  as a short-hand expression for any kind of shift 
-  in the production function. 
-  Thus slowdowns, speed-ups, improvements in the education of the labor force, 
-  and all sorts of things will appear as ``technical change.''~\citep{solow1957technical}
-\end{quote}
-}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Coordinates of Analysis} 
+\label{sec:Coordinates}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+This section describes the coordinates of analysis and briefly reviews 
+literature related to each.
+
+%++++++++++++++++++++++++++++++
+\subsection{Mathematical Forms of the Energy-augmented Production Function} 
+\label{sec:Prod_Func_Forms}
+%++++++++++++++++++++++++++++++
+
+In this paper, we assess three prominent energy-augmented production functions 
+that appear in the literature: 
+Cobb-Douglas (CD), 
+Constant Elasticity of Substitution (CES), and 
+LINear EXponential (LINEX). 
+The following subsections describe each.
+
+%------------------------------
+\subsubsection{Cobb-Douglas (CD) Production Function} 
+\label{sec:CDe}
+%------------------------------
+
 This production function can be expressed as
@@
 
-%Mathematically, $A$ is nothing more than a fitting parameter 
-%that aligns the predictions of Equation~\ref{eq:CD} 
-%with historical data. 
-%Thus, we refer to $A$ as the ``residual'' in this paper.} 
-%term ($A$):
-
-% $A$ is the residual term, 
-% with $\lambda$ 
-% indicating the change of the residual over time (in units of 
-% year$^{-1}$).
-Neoclassical economic growth theory as expressed in the Cobb-Douglas production 
-function makes no attempt to describe the mechanisms that affect
-economic growth, nor does it attempt to describe how such things as
-slowdowns, speedups, and improvements of the education of the labor force
-($\lambda$) might vary from one economy to the next. 
-The parameters $\alpha$ and $\beta$ indicate the relative roles 
-of capital and labor in the economy.
-Typically, the constraint $\alpha + \beta = 1$ is assumed, 
-indicating constant returns to scale.
-
-As shown in Equation~\ref{eq:CD} above, neoclassical economic theory does not 
-include an explicit term for the role of energy in economic growth. However, 
-\citet{Bashmakov:2007ek}, \citet{Hamilton:2009ui}, \citet{Murphy:2011jh}, 
-\citet{Benes:2012tm}, \citet{Kumhof:2012ua}, and others indicate that the 
-importance of energy for economic growth may far outweigh its cost share in the 
-economy. That neoclassical economic growth theory ignores energy is, therefore, 
-cause for concern, and inquiry into the proper approach for including energy 
-as a factor of production in economic growth modeling is both relevant and important.
-
-Some energy economists augment economic growth models by including energy as an 
-additional (or the only) factor of production. However, there is little agreement 
-on how this should be done. Neither the mathematical form of the energy-augmented 
-production function nor the quantification of energy are consistent in the 
-literature. There has been little empirical work assessing the predictive ability 
-of various energy-augmented production functions for different types of economies. 
-And, very few studies of the importance of energy in economic growth include 
-rigorous statistical assessments of energy-related fitting parameters. This paper 
-contributes to the literature by applying statistically rigorous 
-methods along two coordinates of analysis: form of the energy augmented 
-production function and type of economy.
-
-The remainder of this paper is organized as follows. Section~\ref{sec:Coordinates} 
-discusses the coordinates of analysis described above. 
-Section~\ref{sec:Sources_of_Data} details sources of data and calculations to 
-generate time series for economic output and factors of production. 
-The procedures for and results from parameter estimation for the various production functions 
-are discussed in Section~\ref{sec:Parameter_Estimation}. 
-Section~\ref{sec:Discussion_of_Results} discusses implications of the parameter estimation 
-results, and Section~\ref{sec:Conclusion} concludes. 
-An appendix provides details of all statistical results.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Coordinates of Analysis} 
-\label{sec:Coordinates}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-This section describes the two coordinates of analysis and briefly reviews 
-literature related to each.
-
-%++++++++++++++++++++++++++++++
-\subsection{Mathematical Forms of the Energy-augmented Production Function} 
-\label{sec:Prod_Func_Forms}
-%++++++++++++++++++++++++++++++
-
-In this paper, we assess three prominent energy-augmented production functions 
-that appear in the literature: 
-Cobb-Douglas (CD), 
-Constant Elasticity of Substitution (CES), and 
-LINear EXponential (LINEX). 
-The following subsections describe each.
-
-%------------------------------
-\subsubsection{Cobb-Douglas (CD) Production Function} 
-\label{sec:CDe}
-%------------------------------
-
 The capital-labor Cobb-Douglas production function shown in Equation~\ref{eq:CD}
@@
 of production: $\alpha + \beta + \gamma = 1$.
-
-\citet{Ayres:2008cl} uses Equation~\ref{eq:CDe} with exergy ($x$) and 
-useful work ($u$) quantifications for $e$ to describe historic Japanese 
-and American economies from 1900-2000. \citet{Froling:2009vo} uses an 
-energy-augmented Cobb-Douglas production function with thermal energy 
-quantification ($q$) to describe output for the global economy from 1800--1970. 
-Fr\"{o}ling's model endogenizes labor with respect to fertility 
-and mortality rates and separates thermal energy into two types: biomass 
-energy and coal energy. 
-\citet{Serrenho:2010vq} use the log transform of 
-the energy-augmented Cobb-Douglas function with thermal energy 
-quantification ($q$) to describe output for the EU-15 countries. 
-Serrenho divides thermal energy into renewables, non-renewables, 
-wastes, and imports. 
-The main argument of these papers is that 
-energy is an important driver of growth and needs to be included
-as an essential factor of production.
-
-**** Martin: add more here about the conclusions of each paper regarding 
-the role of energy in economic growth? Add additional literature? 
-Or, adjust as you see fit. Especially, are there any confidence intervals 
-or statistical evaluation in each of these studies? ****
 
@@
 meanings that depend upon the nesting of the factors of production.
-% **** Do we want to define different variables that indicate meaning, 
-% such as $\sigma_{kl}, \sigma_{(kl)e}, \delta_{(ek)l}$, and the like? If so, we'll 
-% need to translate from $\rho$ and $\sigma$ in \texttt{cesEst} to the correct
-% variable names in the paper. ****
-
-**** Describe here how 
-we implemented the constraints. ****
-
-\citet{VanderWerf:2008tc} evalutes various nested CES production 
-functions for 12 OECD countries with respect to climate change policy. 
-\citeauthor{VanderWerf:2008tc} concludes that ($kl$)($e$) nesting structure 
-best fits historical data. \citet{Lecca:2011kr} also evaluate a variety of 
-CES production functions using a KLEM structure to determine how the various 
-options for nesting the energy factor of production affect predictive ability. 
-\citet{Stern:2012ey} also use a CES production function of the form ($kl$)($e$). 
-\citeauthor{Stern:2012ey} apply their CES function to the Swedish economy 
-from 1800-2000 and demonstrate the importance of the transition from wood to 
-fossil fuels for economic growth. \citet{Shen:2013vp} included energy 
-in nested aggregated CES production functions 
-for China and found that the best nesting structure is ($le$)($k$).
-
-**** Martin: add more here about the conclusions of each paper regarding 
-the role of energy in economic growth? Add additional literature? 
-Or, adjust as you see fit. Especially, are there any confidence 
-intervals or statistical evaluation in each of these studies? ****
 
@@
 
-In the energy-economic growth literature, the focus is 
-almost exclusively on developed economies from North America 
-or Europe. Examples include \citet{Kummel:1980wx} applying 
-LINEX to describe the West German economy, \citet{Serrenho:2010vq} 
-applying Cobb-Douglas variants to EU-15 countries, 
-\citet{VanderWerf:2008tc} applying CES nesting variants 
-to the 12 OECD countries, \citet{Lecca:2011kr} applying 
-CES nesting variants to the Scottish economy, \citet{Stern:2012ey} 
-applying CES to describe the Swedish economy, and \citet{Warr:2012cg} 
-using LINEX and Cobb-Douglas to describe the Austrian, 
-American, British, and Japanese economies.
-
-But, the near-exclusive focus on developed economies closes off 
-the possibility of discovering any role that energy plays 
-in the economic development process. In this paper we analyze at least 
-two economies in each of the following four categories: 
-Developed, 
-NICs,\footnote{Newly Industrialized Countries}
-OPEC, and 
-LDCs.\footnote{Lesser Developed Countries} 
+The REXS data set include US, UK, JP, and AT.
 (See Table~\ref{tab:Economy_Examples}.)
 
-\begin{table} \caption{Example economies and years of evaluation.} \label{tab:Economy_Examples} 
+\begin{table} \caption{REXS economies and years of evaluation.} \label{tab:Economy_Examples} 
   \begin{center}
-    \begin{tabular}{r c c l l} 
-      \multirow{3}{*}{Developed} & \includegraphics[height=0.11in]{flag/flag_US.png} & US & USA & \multirow{3}{*}{1980--2011}\\
-                                 & \includegraphics[height=0.11in]{flag/flag_UK.png} & UK & United Kingdom & \\
-                                 & \includegraphics[height=0.11in]{flag/flag_JP.png} & JP & Japan          & \\
+%     \begin{tabular}{r c c l l} 
+%       \multirow{3}{*}{Developed} & \includegraphics[height=0.11in]{flag/flag_US.png} & US & USA & \multirow{3}{*}{1900--2000}\\
+%                                  & \includegraphics[height=0.11in]{flag/flag_UK.png} & UK & United Kingdom & \\
+%                                  & \includegraphics[height=0.11in]{flag/flag_JP.png} & JP & Japan          & \\
+%                                  & \includegraphics[height=0.11in]{flag/flag_AT.png} & AT & Austria        & \\1950--2000
+%     \end{tabular}
+    \begin{tabular}{c c l l} 
+      \includegraphics[height=0.11in]{flag/flag_US.png} & US & USA            & \multirow{3}{*}{1900--2000}\\
+      \includegraphics[height=0.11in]{flag/flag_UK.png} & UK & United Kingdom & \\
+      \includegraphics[height=0.11in]{flag/flag_JP.png} & JP & Japan          & \\
       \hline
-      \multirow{2}{*}{NICs}      & \includegraphics[height=0.11in]{flag/flag_CN.png} & CN & China & \multirow{2}{*}{1991--2011}        \\
-                                 & \includegraphics[height=0.11in]{flag/flag_ZA.png} & ZA & South Africa & \\
-      \hline
-      \multirow{2}{*}{OPEC}      & \includegraphics[height=0.11in]{flag/flag_SA.png} & SA & Saudi Arabia & \multirow{2}{*}{1991--2011} \\
-                                 & \includegraphics[height=0.11in]{flag/flag_IR.png} & IR & Iran         &  \\
-      \hline
-      \multirow{2}{*}{LDCs}      & \includegraphics[height=0.11in]{flag/flag_TZ.png} & TZ & Tanzania & \multirow{2}{*}{1991--2011}     \\
-                                 & \includegraphics[height=0.11in]{flag/flag_ZM.png} & ZM & Zambia      & \\
+      \includegraphics[height=0.11in]{flag/flag_AT.png} & AT & Austria        & 1950--2000
     \end{tabular}
@@
 
-To assess energy-augmented models of economic growth along the 
-coordinates of analysis outlined in Section~\ref{sec:Coordinates}, 
-historical data for economic output ($Y$), capital stock ($K$), 
-labor ($L$), and thermal energy ($Q$)   %, exergy ($X$), and useful work ($U$) 
-are required. Subsections below describe sources for and calculations 
-to obtain historical data. A final subsection presents the historical 
-data in graphical form.
-
-%++++++++++++++++++++++++++++++
-\subsection{Economic Output} 
-\label{sec:Economic_Output_Data}
-%++++++++++++++++++++++++++++++
-
-We measure economic output ($Y$) by gross domestic product (GDP). 
-GDP data in real 2005 U.S. dollars for developed countries (1980--2011) 
-and all other countries (1991--2011) was obtained from 
-the World Bank's Global Economic Prospects (GEP) database 
-\citep{WorldBankGEP:2013a}.
-
-%++++++++++++++++++++++++++++++
-\subsection{Capital Stock} 
-\label{sec:Capital_Stock_Data}
-%++++++++++++++++++++++++++++++
-
-Gross capital stock in real 2005 U.S. dollars 
-for developed countries (1980--2011) and 
-all other countries (1991--2011) was obtained from 
-the World Bank's Global Economic Prospects (GEP) database 
-\citep{WorldBankGEP:2013a}.
-
-%++++++++++++++++++++++++++++++
-\subsection{Labor and Employment}
-\label{sec:Labor_Data}
-%++++++++++++++++++++++++++++++
-
-Total employment and average hours worked per worker per year 
-for the developed nations (United States, United Kingdom, and Japan) 
-for 1980--2011 were obtained from the United States 
-\citet[Tables 6 and 7]{BLS:2013a}. Total hours worked per year was 
-calculated by multiplying total employment by average hours worked 
-per worker per year.
-
-The World Bank's World Development Indicators database 
-\citep{WorldBankWDI:2013a} provides the employment to population 
-ratio for people fifteen and older, total population, and a percentage 
-of people under fifteen for other economies 
-(China, South Africa, 
-Saudi Arabia, Iran, 
-Tanzania, and Zambia) 
-for 1991--2011. 
-The population 
-of people under fifteen years of age was subtracted from total population 
-to calculate the population of people fifteen and older. 
-Total employment was calculated by multiplying the employment to 
-population ratio of people fifteen and older by the population 
-of people fifteen and older.
-
-%++++++++++++++++++++++++++++++
-\subsection{Energy} 
-\label{sec:Energy_Data}
-%++++++++++++++++++++++++++++++
-
-To account for all energy input to an economy, we summed consumption data 
-for many energy sources, including coal, oil and petroleum products, 
-dry natural gas and natural gas plant liquids, nuclear power generation, 
-and renewable energy sources (solar, wind, geothermal, biomass/fuel wood, 
-and hydro). 
-We also added animal muscle work. 
-Following \citet{Ayres:2010ug}, 
-human muscle work is excluded from the energy time series,
-because it is counted as labor.
-Similar to the economic data discussed in 
-Sections~\ref{sec:Economic_Output_Data}--\ref{sec:Labor_Data}, 
-we obtained energy data for developed countries from 1980--2011. 
-For all other countries, 
-we obtained energy data for 1991--2011.
-
-Thermal energy ($Q$) for fuels (in units of TJ/year) was calculated by
-%
-\begin{equation} \label{eq:thermal_energy}
-  Q_{fuel} = C_{fuel}h_{fuel}
-\end{equation}
-%
-\noindent where $C_{fuel}$ is the consumption rate of the fuel 
-(in units of short tons/year for coal, barrels/year for oil and petroleum, 
-ft$^3$/year for dry natural gas and natural gas plant liquids, 
-and m$^3$/year for biomass and fuel wood) and $h_{{fuel}}$ is 
-the heat content of the fuel (in kJ/short ton for coal, kJ/barrel for oil, 
-kJ/ft$^3$ for dry natural gas and natural gas plant liquids, 
-and kJ/kg for biomass and fuel wood). 
-Fuel wood density of 300~kg/m$^3$ 
-was taken from \citet{Ragland:2013wp} at the low end of the range 
-of density of dry wood and bark.
-
-Yearly consumption rates ($C_{fuel}$) of coal, oil and petroleum, 
-dry natural gas and natural gas plant liquids, and biofuels 
-(ethanol and biodiesel) were obtained from the \citet{EIA:2013a} 
-for all economies. 
-Yearly average heat content data for coal, oil, 
-and natural gas and natural gas plant liquids was obtained from the 
-\citet{EIA:2013a} for all economies. 
-We used lower (net) heating values of 
-26.8~MJ/kg \citep[Table~A-27]{Cengel:2011ww} and 37.8~MJ/kg 
-\citep[Table~7.3]{Gupta:2010vg} for the heat content of ethanol 
-and corn-based biodiesel, respectively. 
-Yearly consumption and 
-heat content data for biomass/fuel wood was obtained from the 
-``Fuelwood'' time series of the FAO Statistics Database 
-\citep{FAO:2013a}.
-
-For renewable and nuclear energy sources, yearly electricity 
-generation (in BTU/year) was available directly from 
-the \citet{EIA:2013a} for all economies, so 
-Equation~\ref{eq:thermal_energy} was unnecessary.
-
-Animal and human muscle work was estimated using an approach 
-similar to \citet{Ayres:2010ug}, using data from Warr's 
-REXS database \citep{Warr:2012a} and results from 
-\citet{Wirsenius:2000vi}. For animal work, our analysis was 
-restricted to draught animals (horses and mules). Muscle work 
-from animals ($Q_{animals}$) was calculated using
-%
-\begin{equation} \label{eq:animal_muscle}
-  Q_{animals} = Q_{m,horse}N_{horses} + Q_{m,mule}N_{mules}
-\end{equation}
-%
-\noindent where $Q_m$ is metabolizable energy (in kcal/day-animal) 
-and $N$ is the number of animals. Metabolizable energy values 
-($Q_{m,horses}$ = 19,110 kcal/day-horse and $Q_{m,mules}$ = 
-7,215 kcal/day-mule) were taken from \citet{Warr:2012a}. 
-$Q_m$ represents the amount of energy in the feed consumed by 
-animals for a day of work, and they are assumed constant for 
-all countries and years. The number of horses and mules for 
-each economy was taken from the ``Live Animals'' section of the 
-FAO Statistics online database \citep{FAO:2013a}.
-
-% Human muscle power was calculated in a similar manner:
-% 
-% \begin{equation} \label{eq:human_muscle}
-%   Q_{workers} = Q_{m,workers} N_{workers}
-% \end{equation}
-% 
-% \noindent where the value of $Q_{m,workers}$ is the ``the amount 
-% of food available for human consumption'' (i.e., at the wholesale level) 
-% taken from the 
-% \citet[``\texttt{Dietary~Energy~Cons.~Countries}'' tab]{FAO:2013b}. 
-% The value for $N_{workers}$ was obtained from the labor time series 
-% for each economy as discussed in Section~\ref{sec:Labor_Data}.
+REXS.
 
@@
 energy ($q$) 
-for 1980--2011 (developed economies) and 1991--2011 (other economies). 
-Factors of production track each other closely, 
-and high covariances among these variables can be seen in 
-Tables~\ref{tab:Covariance_US}--\ref{tab:Covariance_ZM}. 
-\authNote{Do we want to discuss the covariances?}
+for 1900--2000 (US, UK, JP) and 1950--2000 (AT). 
 %
@@
 and \texttt{cesEst} \citep{Henningsen:2011td} (for CES models).
-\authNote{Need to check how CES is being fit and adjust this accordingly.}%
 
@@
 where $\theta$ is a vector of parameters for the function $f$.
-\authNote{if we use $\theta$ this way, we need a new scaling parameter. --rjp}%
 Parameter estimates are chosen to minimize
@@
 one can learn about the precision of the estimation method.
-\authNote{Add some references here. --rjp}
 
@@
 
-\twocolumn{}
-<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=2.9, fig.height=7.7, fig.cap="Cobb-Douglas resample model parameters.">>=
-cdCoeffsData <- filter(coeffs_df, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iQ"))
+<<CD_lambda_theta_graph, fig.pos="H", fig.align='center', fig.width=4, fig.height=4.5, fig.cap="$\\lambda$ and $\\theta$ values for Cobb-Douglas resample models.">>=
+cdCoeffsData <- filter(coeffs_df, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iX", "iK+iL+iU"))
+standardScatterPlot(data=cdCoeffsData, mapping=aes(scale, lambda), facet_formula=country~energy, alpha=0.05) +
+#     scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
+#     scale_y_continuous(breaks=c(0, 0.025, 0.05, 0.075)) +    
+    labs(x=expression(theta), y=expression(lambda))
+@
+
+<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=3.9, fig.height=4, fig.cap="Cobb-Douglas resample model parameters.">>=
+cdCoeffsData <- filter(coeffs_df, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iX", "iK+iL+iU"))
 standardTriPlot(data=cdCoeffsData, facet_formula=country~energy)
@@
 
-<<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=8.2, fig.cap="Cobb-Douglas fitted models.">>=
-cdFittedData <- filter(fitted_df, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iQ"))
+<<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=4, fig.height=4.5, fig.cap="Cobb-Douglas fitted models.">>=
+cdFittedData <- filter(fitted_df, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iX", "iK+iL+iU"))
 spaghettiPlot(data=cdFittedData, facet_formula=Country~energy, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1980=1 or 1991=1)")
-@
-\onecolumn{}
+    labs(y="Indexed GDP (1900=1 or 1950=1)")
+@
 
@@
 are shown in 
-Figures~\ref{fig:CES_lambda_gamma_graph}--\ref{fig:CES_sigma_delta_graph}. 
+Figures~\ref{fig:CES_lambda_gamma_graph_X}--\ref{fig:CES_sigma_delta_graph_X}. 
 The white crosshair on each graph shows the location 
 of the fit to historical data. 
-In Figures~\ref{fig:CES_sigma1_delta1_graph} and~\ref{fig:CES_sigma_delta_graph},
+In Figures~\ref{fig:CES_sigma1_delta1_graph_X} and~\ref{fig:CES_sigma_delta_graph_X},
 the bottom of the vertical axis represents $\sigma = 0$.
@@
 resample points along the left (right) edge of
-Figures \ref{fig:CES_sigma1_delta1_graph} and \ref{fig:CES_sigma_delta_graph}
+Figures \ref{fig:CES_sigma1_delta1_graph_X} and \ref{fig:CES_sigma_delta_graph_X}
 are equivalent.
 That is, all points along the left (right) edge of
-Figures \ref{fig:CES_sigma1_delta1_graph} and \ref{fig:CES_sigma_delta_graph}
+Figures \ref{fig:CES_sigma1_delta1_graph_X} and \ref{fig:CES_sigma_delta_graph_X}
 have the same $sse$. 
@@
 to discriminate among points along the left (right) edge of
-Figures \ref{fig:CES_sigma1_delta1_graph} and \ref{fig:CES_sigma_delta_graph}. 
+Figures \ref{fig:CES_sigma1_delta1_graph_X} and \ref{fig:CES_sigma_delta_graph_X}. 
 Thus, resample point estimates where $\delta$ or $\delta_1$ approaches 0 (1)
@@
 
-<<CES_lambda_gamma_graph, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models.">>=
+<<CES_lambda_gamma_graph_X, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with exergy ($x$).", eval=TRUE>>=
 cesCoeffsData <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
-                                                                     "(iK + iL) + (iQ)", 
-                                                                     "(iL + iQ) + (iK)", 
-                                                                     "(iQ + iK) + (iL)"))
+                                                                     "(iK + iL) + (iX)", 
+                                                                     "(iL + iX) + (iK)", 
+                                                                     "(iX + iK) + (iL)"))
 standardScatterPlot(data=cesCoeffsData, mapping=aes(gamma_coef, lambda), facet_formula=country~nestStrParen, alpha=0.05) +
     scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
-    scale_y_continuous(breaks=c(0, 0.025, 0.05, 0.075)) +    
     labs(x=expression(gamma), y=expression(lambda))
@@
 
-<<CES_sigma1_delta1_graph, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models.">>=
+<<CES_sigma1_delta1_graph_X, fig.pos="H", fig.align='center', fig.width=5, fig.height=5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with exergy ($x$).", eval=TRUE>>=
 standardScatterPlot(data=cesCoeffsData, mapping=aes(delta_1, sigma_1), facet_formula=country~nestStrParen, alpha=0.05) +
@@
 
-<<CES_sigma_delta_graph, fig.pos="H", fig.align='center', fig.width=4.5, fig.height=7, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models.">>=
+<<CES_sigma_delta_graph_X, fig.pos="H", fig.align='center', fig.width=4.4, fig.height=5, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models using exergy ($x$).">>=
 standardScatterPlot(data=subset(cesCoeffsData, nestStrParen != "(iK + iL) + ()"),
@@
 
+<<CES_lambda_gamma_graph_U, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with useful work ($u$).", eval=TRUE>>=
+cesCoeffsData <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
+                                                                     "(iK + iL) + (iU)", 
+                                                                     "(iL + iU) + (iK)", 
+                                                                     "(iU + iK) + (iL)"))
+standardScatterPlot(data=cesCoeffsData, mapping=aes(gamma_coef, lambda), facet_formula=country~nestStrParen, alpha=0.05) +
+    scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
+    labs(x=expression(gamma), y=expression(lambda))
+@
+
+<<CES_sigma1_delta1_graph_U, fig.pos="H", fig.align='center', fig.width=5, fig.height=5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with useful work ($u$).">>=
+standardScatterPlot(data=cesCoeffsData, mapping=aes(delta_1, sigma_1), facet_formula=country~nestStrParen, alpha=0.05) +
+    coord_trans(y="sigma") +
+    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
+    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
+    labs(x=expression(delta[1]), y=expression(sigma[1]))
+@
+
+<<CES_sigma_delta_graph_U, fig.pos="H", fig.align='center', fig.width=4.4, fig.height=5, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models with useful work ($u$).">>=
+standardScatterPlot(data=subset(cesCoeffsData, nestStrParen != "(iK + iL) + ()"),
+                    mapping=aes(delta, sigma), facet_formula=country~nestStrParen, alpha=0.05) +
+    coord_trans(y="sigma") +
+    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
+    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
+    labs(x=expression(delta), y=expression(sigma))
+@
+
 Figure~\ref{fig:CES_Spaghetti_Graph_CN} shows details of the resample fits for China with the (kl)e nesting.
@@
 
-\begin{equation} \label{eq:LINEX_beta}
+\begin{equation} \label{eq:LINEX_beta_2}
   \gamma = \frac{e}{y} \frac{\partial y}{\partial e} 
@@
 
-**** Include a table here of important values. 
-Martin to suggest the form of this table after working 
-on the interpretation for a while. ****
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Drive towards new insights from our stats tested comparative approach.
-
-**** Notes for interpretation of results ****
-
-R$^2$ not a good measure. 
-Limited insights are obtained from $t$ and $p$ values, 
-especially on PFs that have parameters with constraints (CD, CES).
-
-We found that we are able to maintain good fits while respecting theoretical foundations
-of the models (i.e., respect parameter constraints). No need to relax parameter constraints
-and, thereby, contradict micro foundations.
-
-CD assumes $\sigma_1 = 1$. CES doesn't assume a value for $\sigma_1$. 
-The $\sigma_1$ vs. $\delta_1$ graphs for CES without energy often have 
-two frequent values for $\sigma_1$.  One of those frequent values is
-nearer to $\sigma_1 = 1$. When CD and CES without energy do not agree on 
-share values (CD: $\alpha$ compared to $\beta$, CES: $\delta_1$) for the 
-base curve fit (red dot), they do agree for the data that clusters near 
-$\sigma_1 = 1$ for the CES fits.
-
-Country interpretation
-
-Comparison Cobb Douglas and CES results.
-
-%++++++++++++++++++++++++++++++
-\subsection{United States} 
-\label{sec:InterpUS}
-%++++++++++++++++++++++++++++++
-
-CD: Energy is unnecessary
-
-CES with $q$:
-
-($kl$): $\delta_1 = 0.3, \sigma_1 = 0.8$. $k$ is less necessary. 
-Complements, but close to substitutes.
-signal of substitutability in the spread.
-
-($kl$)$e$: energy is unnec ($\delta = 1$). 
-$\delta_1 = 0.45$: $k$ and $l$ are about equally necessary.
-$\sigma_1 = 0.8$: $k$ and $l$ are slight complements. 
-Spread on $0.25 < \sigma_1 < \infty$, signalling 
-possibilities of substitution.
-
-($el$)$k$: energy is unnec. ($\delta_1$ is 0);
-
-($le$)$k$ no indication
-Relative consistent signal that energy is unnec.
-
-CES with $u$:
-
-($kl$)$e$: $\delta = 1$, signalling $e$ unnecessary. 
-$\sigma = 0.8$, indicating clost to substitutability,
-but still complementary. 
-$\delta_1 = 0.25$, with large spread. not strong for $k$.
-$\sigma_1 \rightarrow \infty$, but with large spread from 0.2 upward. 
-Signals complementarity between $k$ and $l$.
-
-%++++++++++++++++++++++++++++++
-\subsection{United Kingdom} 
-\label{sec:InterpUK}
-%++++++++++++++++++++++++++++++
-
-CD: Capital is unnec.
-
-CES with $q$:
-
-($kl$): $\delta_1 = 0.7, \sigma_1 = 0.35$. 
-$kl$ complementary, $k$ is more important, because $\delta_1 > 0.5$. 
-Large spread on $\delta_1$. 
-Complementary signal is consistent, however.
-
-($kl$)$e$: energy is unnec ($\delta = 1$). 
-$\delta_1 = 0.25$, $k$ is less necessary. 
-$\sigma_1 \rightarrow \infty$, giving strong $kl$ substitutability signal.
-
-($le$)$k$ capital is unnec. ($\delta = 1$);
-
-($ek$)$l$ ($\delta_1 = 0$) energy is unnec.
-
-Thus, inconsistent results, possibly look at different time series 
-as massive changes in economic policy in Uk economic history
-
-CES with $u$:
-
-($kl$)$e$: $\delta = 1$, $u$ is unnecessary. 
-$\sigma = 0.8$, approache complementarity between $kl$ and $e$.
-$\delta_1 = 0.1$. 
-$\sigma_1 \rightarrow \infty$, indicating substitutability between $k$ and $l$.
-
-%++++++++++++++++++++++++++++++
-\subsection{Japan} 
-\label{sec:InterpJP}
-%++++++++++++++++++++++++++++++
-
-CD: energy is unnec.
-
-CES with $q$:
-
-($kl$): $\delta_1 = 0.7, \sigma_1 = 0.25$. Very little scatter. Both are well-known. 
-$l$ is close to unnecessary. $k$ and $l$ are complements.
-
-($kl$)$e$: no indications, all are important. $\delta = 0.6$, both $kl$ and $e$ are necessary.
-$0.5 < \delta < 1$.
-$\sigma=0.1$ signalling complementarity betwen $kl$ and $e$.
-$\delta_1 = 0.8$ signalling $l$ is almost unnecessary. 
-$\sigma_1 = 0.1$, signalling complementarity 
-between $k$ and $l$.
-
-($le$)$k$: no indications, all are important.
-
-($ek$)$l$: no indications, all are important.
-
-weak signal that labour is less necessary 
-(($kl$)$e$ $delta_1 = 0.86$ and ($ek$)$l$ $\delta = 0.89$)
-
-Thus, inconsistent results.
-
-CES with $u$:
-
-($kl$)$e$: $\delta = 0.6, \sigma = 0.4$. Complementarity between $kl$ and $e$.
-$\delta_1 = 1$, indicating $l$ unnecessary. $\sigma_1 = 0.1$, indicating complementarity
-between $k$ and $l$. Need only one of $k$ or $l$ in your equation, but they are
-complemetary! You need one to have the other.
-
-%++++++++++++++++++++++++++++++
-\subsection{China} 
-\label{sec:InterpCN}
-%++++++++++++++++++++++++++++++
-
-CD: energy not necessary, capital less necessary
-
-CES with $q$:
-
-($kl$): $\delta_1 = 0.3$, so $k$ is getting close to unnecessary. $\sigma_1 = 1.25$.
-$k$ and $l$ are substitutes. Large spread in $\delta_1$ from 0.1 to 1.0. Large spread in
-$\sigma_1$, but most points have $\sigma_1 > 1$.
-
-($kl$)$e$: $\delta = 0.8$. however, strong signal at $0.8 < \delta < 1$, 
-signalling that energy is less necessary. $0.5 < \delta < 1$. $\sigma = 0.5$, 
-signalling complementarity between $kl$ and $e$. 
-$\delta_1 = 1$, signalling that $l$ is unnecessary. $\sigma_1 = 0.1$, signalling
-that $k$ and $l$ are complementary. Both $\delta_1$ and $\sigma_1$ have large spreads, 
-so our confidence in these results is low.
-
-($le$)$k$: labour is unnnec ($\delta_1 = 0$);
-
-($ek$)$l$ energy is unnec. ($\delta_1 \rightarrow 0$)
-
-Strong signal that energy is unnec, but the labour and capital signals are conflicting
-
-%++++++++++++++++++++++++++++++
-\subsection{South Africa} 
-\label{sec:InterpZA}
-%++++++++++++++++++++++++++++++
-
-CD: Labour is unnec.
-
-CES with $q$:
-
-($kl$): $\delta_1 = 0.35, \sigma_1 = 0.8$. $k$ is relatively less necessary. $k$ and $l$ 
-are complements but relatively close to being substitutes. Spread is tight between 
-$0.25 < \delta_1 < 0.5$ and $\sigma_1$ is consistently complementary 
-between $0.1 < \sigma_1 < 0.8$.
-
-($kl$)$e$: labour is unnec. ($\delta_1 = 1$). $\delta = 0.25$, signalling complemtarity 
-between $kl$ and $e$, but large spread from 0 to 1. $\sigma$ and $\sigma_1$ are both 0, 
-indicating perfect complements betwen $kl$ and $e$ and between $k$ and $l$.
-
-($le$)$k$ labour is unnec. ($\delta_1 = 0$);
-
-($ek$)$l$ labour is unnec. ($\delta = 1$)
-
-Consistent signal that labour is unnec.
-
-%++++++++++++++++++++++++++++++
-\subsection{Saudi Arabia} 
-\label{sec:InterpSA}
-%++++++++++++++++++++++++++++++
-
-CD: no indications
-
-CES with $q$:
-
-($kl$): $\delta_1 = 0.85$. $l$ is unnecessary. 
-$\sigma_1 = 0.1$ indicating strong complementarity between 
-$k$ and $l$. Spread of $0.15 < \delta_1 < 1$. 
-$0 < \sigma_1 < 0.8$, signalling complementarity.
-
-($kl$)$e$: $\delta = 0.6$, $e$ is less necessary (weak signal). 
-Big spread on $\delta$ between 0 and 0.8.
-$\sigma = 0.1$ indicating complementarity between $kl$ and $e$. $\delta_1 = 0.8$ 
-(with large spread between 0.3 and 1), labor is less necessary.
-$\sigma_1 = 0.1$: very complementary between $k$ and $l$.
-
-($le$)$k$:
-
-($ek$)$l$: weak signal that labour is unnec ($\delta = 0.93$)
-
-Almost consistent signal that no indocations.
-
-%++++++++++++++++++++++++++++++
-\subsection{Iran} 
-\label{sec:InterpIR}
-%++++++++++++++++++++++++++++++
-
-CD: energy is unnec.
-
-CES with $q$:
-
-($kl$): $\delta_1 = 0.3$. Spread $0 < \delta_1 < 0.7$. $0 < \sigma_1 < 0.8$. $\sigma_1 = 0$. 
-Strong complementarity. $k$ is less necessary compared to $l$.
-
-($kl$)$e$: energy is unnec ($\delta=1$). 
-$\sigma = 0.75$ indicating complementarity between $kl$ and $e$, approaching substitutibility.
-$\delta_1 = 0.3, \sigma_1 = 0$ indicating strong perfect complementarity between $k$ and $l$.
-
-($le$)$k$: energy is unnec. ($\delta_1=1$);
-
-($ek$)$l$: labour is unnec. ($\delta=1$)
-
-%++++++++++++++++++++++++++++++
-\subsection{Tanzania} 
-\label{sec:InterpTZ}
-%++++++++++++++++++++++++++++++
-
-CD: labour in unnec.
-
-CES with $q$:
-
-($kl$): $\delta_1 = 0.8$ $0.3 < \delta_1 < 1$ signalling labor is less necessary.
-$\sigma_1 = 0.1$ $0 < \sigma_1 < 0.8$, signalling complementary $k$ and $l$.
-
-($kl$)$e$: labour is unnec ($\delta_1=0.97$). 
-$\delta = 0.45$, so $kl$ and $e$ both necessary, but 
-$\sigma \rightarrow \infty$, so $kl$ and $e$ has perfect substitutibility.
-$\sigma_1 = 0.1$, so $k$ and $l$ are perfect complements. 
-Spread on $\delta$ is large (0.2 to 1).
-So, we are unsure about the value of $\delta$.
-
-($le$)$k$: weak signal that energy is unnec. ($\delta_1=0.92$); 
-very weal signal capital is unnec ($\delta=0.84$);
-
-($ek$)$l$: labour is unnec. $\delta=0.96$
-
-Consistent signal that labour is unnec, with exception of one nesting.
-
-%++++++++++++++++++++++++++++++
-\subsection{Zambia} 
-\label{sec:InterpZM}
-%++++++++++++++++++++++++++++++
-
-CD: labour is unnec; energy is unnec.
-
-CES with $q$:
-
-($kl$): $\delta_1 = 1$: $l$ is unnecessary. 
-$0.5 < \delta_1 < 1$. $\sigma_1 = 0.8$ without any 
-noticeable spread indicating complemetary.
-
-($kl$)$e$: labour is unnec. ($\delta_1=1$). 
-$\delta = 0.6$, $kl$ and $e$ are both necessary. 
-$\sigma \rightarrow \infty$, signalling substitutability between $kl$ and $e$. 
-$\sigma_1 = 0.8$ with very large spread between 0 and 2. 
-Approaching substitutability between $k$ and $l$ and perfect substitutibility
-between $kl$ and $e$. Very little certainty here.
-
-($le$)$k$: ($\delta_1=0$);
-
-($ek$)$l$: labour is unnec. ($\delta=1$)
-
-Consistent signal that labour is unnec.
-
-Discussion of results:
-
-How to get better consistent signals?
-
-\begin{itemize}
-\item{Use CD as starting points and do CES convergence on that basis.}
-\item{Do scatterplots to get range of uncertainty inputs, then re-interpret. 
-$\delta$ against $\sigma$ plots, as well as $\delta_1$ and $\sigma_1$ plots.}
-\end{itemize}
-
-Thus, to do the fitting well we need to understand:
-\begin{itemize}
-\item{nesting}
-\item{algorithm}
-\item{starting values}
-\end{itemize}
-esp. for CES.
-
-(Maybe illustrate with one case study such as China what implications are).
-
-How do we compare with LINEX results?
-
-CES is a broader specification of CD, LINEX is not. 
-In LINEX neither $\delta$s nor $\sigma$s are generated. 
-Only efficiency terms are generated in LINEX, 
-thus in other words economic growth is only possible by increased efficiency. 
-The efficiency of using energy is driven by capital stock. 
-The objective/growth engine is to increase capital 
-at a rate that is faster then growth in labour and energy.  
-Increasing labour relative to energy gives a muted benefit. 
-LINEX derived for Germany: only really applicable when energy and capital are complements.
-
-Discussion in relation to other papers. 
-Problems with other papers:
-\begin{itemize}
-\item{If not giving you all parameters}
-\item{Not explain nesting approach}
-\item{No CI on data}
-\end{itemize}
-
-Economic interpretation (revisit after scatterplot information)
-Developed economies: Capital and energy is complementary (US: labour and energy substitutable)
-NICs: Capital and energy complementary, but labour and energy more substitutable
-OPEC: Labour and energy complementary (mixed results on capital and energy)
-LDCs: Labour and energy complementary, Capital and energy perfect substitutes.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-In the future, we intend add an additional coordinate of analysis 
-(Section~\ref{sec:Coordinates}):
-energy quantification.
-Specifically, we with to analyze exergy ($X$) and useful work ($U$)
-energy quantifications within the framework established in this paper.
-Doing so will provide an opportunity to engage the 
-literature around useful work as a driver 
-of economic growth.\citep{Ayres:2003ec, Ayres:2005kn, Ayres:2010ug, 
-Warr:2006hc, Warr:2010ga, Warr:2010ht, Warr:2012cg}
-And, we will be able to assess the interaction between economic models
-and energy quantification: 
-are there combinations of economic models and energy quantifications
-that provide significantly better descriptions of growth?
-We intend to evaluate additional countries as data become available.
-And, we wish to perform analyses over longer time scales.
-In particular, we wish to investigate the effects of significant 
-economic processes (such as industrialization) and political events (world wars)
-using the resampling techniques presented herein.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Funding for Caleb Reese and Lucas Timmer was provided 
-by the Jack and Lois Kuipers Applied Mathematics Endowment and 
-the Calvin College Alumni Association. 
-Partial support for Matthew Kuperus Heun was 
-provided by a Calvin College Research Followship. 
-Partial funding for Martin de Wit was provided 
-by the South African National Research Foundation (NRF).\footnote{Any opinion, 
-findings, and conclusions or recommendations expressed herein are those 
-of the authors, and, therefore, NRF does not accept any liability in regard thereto.} 
-The authors are grateful to Benjamin S. Warr (INSEAD) for providing 
-the REXS database \citep{Warr:2012a}. 
-The authors thank Loren L. Heun (Western Michigan University) 
-for insightful critique of the statistical analyses presented herein.
-The computations in this paper were accomplished using \url{http://dahl.calvin.edu}, 
-a Beowulf cluster built with support from the National Science Foundation's 
-Major Research Instrumentation and Cyber Infrastructure programs, 
-grant number OCI-0722819.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-In the spirit of Reproducible Research \citep{Gandrud:2013vx}, 
-all data, spreadsheets, \texttt{R} code \citep{R}, and other materials 
-associated with this paper can be found at\\*
-\protect\url{https://github.com/MatthewHeun/Econ-Growth-R-Analysis}.
+% In the spirit of Reproducible Research \citep{Gandrud:2013vx}, 
+% all data, spreadsheets, \texttt{R} code \citep{R}, and other materials 
+% associated with this paper can be found at\\*
+% \protect\url{https://github.com/MatthewHeun/Econ-Growth-R-Analysis}.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Covariance Tables}
-\label{sec:Covariance_Tables}
-\setcounter{table}{0} % Restarts table number counter at 0 in this section.
-\setcounter{figure}{0} % Restarts figure number counter at 0 in this section.
-\setcounter{equation}{0} % Restarts equation counter to 0 in this section.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Convergence of Resample Models}
-\label{sec:Convergence_Resample_Models}
-\setcounter{table}{0} % Restarts table number counter at 0 in this section.
-\setcounter{figure}{0} % Restarts figure number counter at 0 in this section.
-\setcounter{equation}{0} % Restarts equation counter to 0 in this section.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The following table shows the fraction of resample models 
-that did not achieve convergence when estimating model parameters.
-
-<<Unconverged_Frac_Table, results='asis'>>=
-# printFracUnconvergedXtable()
-  data <- fracUnconvergedResampleFitsAll(baseResample=baseResample)
-  dataXtable <- xtable(x=data, 
-                       caption="Fraction of unconverged resample models", 
-                       label="tab:frac_unconverged_models",
-                       digits = 3,
-                       align = "rl|cc|ccccccccc") #Sets alignment of the numbers in the columns)
-  print(dataXtable, 
-        caption.placement="top", 
-        size="\\tiny",
-        table.placement="H",
-        include.rownames=FALSE)
-@
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{95\% Confidence Intervals}
-\label{sec:Confidence_Intervals}
-\setcounter{table}{0} % Restarts table number counter at 0 in this section.
-\setcounter{figure}{0} % Restarts figure number counter at 0 in this section.
-\setcounter{equation}{0} % Restarts equation counter to 0 in this section.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Resample coefficients in the scatter plots 
-can be represented as 95\% confidence intervals 
-by finding the parameter values associated with 
-the middle 95\% of the data for each model parameter.
-This appendix provides tables and graphs of the 95\% confidence
-intervals on fitted model parameters.
-
-%++++++++++++++++++++++++++++++
-\subsection{Cobb-Douglas Models}
-%++++++++++++++++++++++++++++++
-
-The 95\% confidence intervals associated with 
-the without-energy column of Figure~\ref{fig:CD_Ternary_Scatter_Graph} 
-are shown in Table~\ref{tab:CD_Parameters_No_Energy}.
-
-<<CD_Params_Table, results='asis'>>=
-printCDParamsTable(energyType="none", baseResample=baseResample)    #Without energy
-@
-
-The data in Table~\ref{tab:CD_Parameters_No_Energy} are plotted in
-Figure~\ref{fig:CD_Params_Graph}.
-
-<<CD_Params_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.cap="Cobb-Douglas (without energy) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createCDParamsGraph(energyType="none", baseResample=baseResample)
-@
-
-The 95\% confidence intervals associated with 
-the with-energy column of Figure~\ref{fig:CD_Ternary_Scatter_Graph} 
-are shown in Table~\ref{tab:CD_Parameters_With_Q}
-and Figure~\ref{fig:CDq_Params_Graph}.
-
-<<CDq_Params_Table, results='asis'>>=
-printCDParamsTable(energyType="Q", baseResample=baseResample)   #With energy
-@
-
-<<CDq_Params_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.cap="Cobb-Douglas (with energy) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createCDParamsGraph(energyType="Q", baseResample=baseResample)
-@
-
-%++++++++++++++++++++++++++++++
-\subsection{CES Models}
-%++++++++++++++++++++++++++++++
-
-The 95\% confidence intervals associated 
-with ($kl$) nest columns of 
-Figures~\ref{fig:CES_lambda_gamma_graph}--\ref{fig:CES_ternary_graph}
-are shown in Tables~\ref{tab:CES_Parameters_A} 
-and \ref{tab:CES_Parameters_B} and Figure~\ref{fig:CES_Params_Graph}.
-
-<<CES_Params_Table, results='asis'>>=
-print(cesParamsTableA(energyType="none", nest="(kl)", baseResample=baseResample), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-print(cesParamsTableB(energyType="none", nest="(kl)", baseResample=baseResample), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-@
-
-<<CES_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (without energy, ($kl$) nesting) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createCESParamsGraph(energyType="none", nest="(kl)", baseResample=baseResample)
-@
-
-The 95\% confidence intervals associated 
-with ($kl$)$e$ nest columns of 
-Figures~\ref{fig:CES_lambda_gamma_graph}--\ref{fig:CES_ternary_graph}
-are shown in Tables~\ref{tab:CES_Parameters_A_With_Q_(kl)e} and 
-\ref{tab:CES_Parameters_B_With_Q_(kl)e} and Figure~\ref{fig:CESq_Params_Graph_kle}.
-
-<<CESq_Params_Table_kle, results='asis'>>=
-print(cesParamsTableA(energyType="Q", nest="(kl)e", baseResample=baseResample), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-print(cesParamsTableB(energyType="Q", nest="(kl)e", baseResample=baseResample), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-
-@
-
-<<CESq_Params_Graph_kle, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with energy, ($kl$)$e$ nesting) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createCESParamsGraph(energyType="Q", nest="(kl)e", baseResample=baseResample)
-@
-
-The 95\% confidence intervals associated 
-with ($le$)$k$ nest columns of 
-Figures~\ref{fig:CES_lambda_gamma_graph}--\ref{fig:CES_ternary_graph}
-are shown in Tables~\ref{tab:CES_Parameters_A_With_Q_(le)k} and 
-\ref{tab:CES_Parameters_B_With_Q_(le)k} and Figure~\ref{fig:CESq_Params_Graph_lek}.
-
-<<CESq_Params_Table_lek, results='asis'>>=
-print(cesParamsTableA(energyType="Q", nest="(le)k", baseResample=baseResample), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-print(cesParamsTableB(energyType="Q", nest="(le)k", baseResample=baseResample), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-
-@
-
-<<CESq_Params_Graph_lek, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with energy, ($le$)$k$ nesting) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createCESParamsGraph(energyType="Q", nest="(le)k", baseResample=baseResample)
-@
-
-The 95\% confidence intervals associated 
-with ($ek$)$l$ nest columns of 
-Figures~\ref{fig:CES_lambda_gamma_graph}--\ref{fig:CES_ternary_graph}
-are shown in Tables~\ref{tab:CES_Parameters_A_With_Q_(ek)l} and 
-\ref{tab:CES_Parameters_B_With_Q_(ek)l} and Figure~\ref{fig:CESq_Params_Graph_ekl}.
-
-<<CESq_Params_Table_ekl, results='asis'>>=
-print(cesParamsTableA(energyType="Q", nest="(ek)l", baseResample=baseResample), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-print(cesParamsTableB(energyType="Q", nest="(ek)l", baseResample=baseResample), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-
-@
-
-<<CESq_Params_Graph_ekl, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with energy, ($ek$)$l$ nesting) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createCESParamsGraph(energyType="Q", nest="(ek)l", baseResample=baseResample)
-@
-
-%++++++++++++++++++++++++++++++
-\subsection{LINEX Model}
-%++++++++++++++++++++++++++++++
-
-The 95\% confidence intervals associated with Figure~\ref{fig:LINEXq_Resample_Graph}
-are shown in Table~\ref{tab:LINEX_Parameters_With_Q} and Figure~\ref{fig:LINEXq_Params_Graph}.
-
-<<LINEX_Params_Table, results='asis'>>=
-print(linexParamsTable(energyType="Q", baseResample=baseResample), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-@
-
-<<LINEXq_Params_Graph, fig.pos="H", fig.width=linexParameterGraphWidth, fig.height=linexParameterGraphHeight, fig.cap="LINEX model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
-createLINEXParamsGraph(energyType="Q", baseResample=baseResample)
-@
+\section{Appendix}
+
+Include data tables here?
 
@@
 %%\bibliography{<your-bib-database>}
-\bibliography{EconGrowth.bib}
+\bibliography{HeunWarr.bib}
 

### 2014-07-30 Articles/Article_Heun_Warr_2014/EcolEcon_HeunWarr.Rnw
Updates to HeunWarr paper.

@@
 
-<<CES_lambda_gamma_graph_X, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with exergy ($x$).", eval=TRUE>>=
-cesCoeffsData <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
+<<CES_lambda_gamma_graph_X, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with exergy ($x$).">>=
+cesCoeffsDataX <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
                                                                       "(iK + iL) + (iX)", 
@@
                                                                       "(iX + iK) + (iL)"))
-standardScatterPlot(data=cesCoeffsData, mapping=aes(gamma_coef, lambda), facet_formula=country~nestStrParen, alpha=0.05) +
+standardScatterPlot(data=cesCoeffsDataX, mapping=aes(gamma_coef, lambda), facet_formula=country~nestStrParen, alpha=0.05) +
     scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
@@
 
-<<CES_sigma1_delta1_graph_X, fig.pos="H", fig.align='center', fig.width=5, fig.height=5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with exergy ($x$).", eval=TRUE>>=
-standardScatterPlot(data=cesCoeffsData, mapping=aes(delta_1, sigma_1), facet_formula=country~nestStrParen, alpha=0.05) +
+<<CES_sigma1_delta1_graph_X, fig.pos="H", fig.align='center', fig.width=5, fig.height=5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with exergy ($x$).">>=
+standardScatterPlot(data=cesCoeffsDataX, mapping=aes(delta_1, sigma_1), facet_formula=country~nestStrParen, alpha=0.05) +
     coord_trans(y="sigma") +
@@
 <<CES_sigma_delta_graph_X, fig.pos="H", fig.align='center', fig.width=4.4, fig.height=5, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models using exergy ($x$).">>=
-standardScatterPlot(data=subset(cesCoeffsData, nestStrParen != "(iK + iL) + ()"),
+standardScatterPlot(data=subset(cesCoeffsDataX, nestStrParen != "(iK + iL) + ()"),
                     mapping=aes(delta, sigma), facet_formula=country~nestStrParen, alpha=0.05) +
@@
 
-<<CES_ternary_graph, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models.">>=
-standardTriPlot(data=cesCoeffsData, facet_formula=country~nestStrParen)
+<<CES_ternary_graphX, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models with exergy ($x$).">>=
+standardTriPlot(data=cesCoeffsDataX, facet_formula=country~nestStrParen)
 @
@@
 
-<<CES_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models.">>=
-cesFittedData <- filter(fitted_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
-                                                                     "(iK + iL) + (iQ)", 
-                                                                     "(iL + iQ) + (iK)", 
-                                                                     "(iQ + iK) + (iL)"))
-spaghettiPlot(data=cesFittedData, facet_formula=Country~nestStrParen, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1980=1 or 1991=1)")
-@
-
-<<CES_lambda_gamma_graph_U, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with useful work ($u$).", eval=TRUE>>=
-cesCoeffsData <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
+<<CES_Spaghetti_Graph_X, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models with exergy ($x$).">>=
+cesFittedDataX <- filter(fitted_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
+                                                                      "(iK + iL) + (iX)", 
+                                                                      "(iL + iX) + (iK)", 
+                                                                      "(iX + iK) + (iL)"))
+spaghettiPlot(data=cesFittedDataX, facet_formula=Country~nestStrParen, level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1900=1 or 1950=1)")
+@
+
+<<CES_lambda_gamma_graph_U, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with useful work ($u$).">>=
+cesCoeffsDataU <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
                                                                       "(iK + iL) + (iU)", 
@@
                                                                       "(iU + iK) + (iL)"))
-standardScatterPlot(data=cesCoeffsData, mapping=aes(gamma_coef, lambda), facet_formula=country~nestStrParen, alpha=0.05) +
+standardScatterPlot(data=cesCoeffsDataU, mapping=aes(gamma_coef, lambda), facet_formula=country~nestStrParen, alpha=0.05) +
     scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
@@
 <<CES_sigma1_delta1_graph_U, fig.pos="H", fig.align='center', fig.width=5, fig.height=5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with useful work ($u$).">>=
-standardScatterPlot(data=cesCoeffsData, mapping=aes(delta_1, sigma_1), facet_formula=country~nestStrParen, alpha=0.05) +
+standardScatterPlot(data=cesCoeffsDataU, mapping=aes(delta_1, sigma_1), facet_formula=country~nestStrParen, alpha=0.05) +
     coord_trans(y="sigma") +
@@
 <<CES_sigma_delta_graph_U, fig.pos="H", fig.align='center', fig.width=4.4, fig.height=5, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models with useful work ($u$).">>=
-standardScatterPlot(data=subset(cesCoeffsData, nestStrParen != "(iK + iL) + ()"),
+standardScatterPlot(data=subset(cesCoeffsDataU, nestStrParen != "(iK + iL) + ()"),
                     mapping=aes(delta, sigma), facet_formula=country~nestStrParen, alpha=0.05) +
@@
 
-Figure~\ref{fig:CES_Spaghetti_Graph_CN} shows details of the resample fits for China with the (kl)e nesting.
-Again, historical data are shown as a black line. 
-The fit to historical data is shown as a white line.
-The gray band encompasses 95\% of the fits to resampled data.
-
-<<CES_Spaghetti_Graph_CN, fig.pos="H", fig.align='center', fig.width=maxWidth, fig.height=maxHeight, fig.cap="CES fitted models for China with the (kl)e nesting.">>=
-spaghettiPlot(data=subset(cesFittedData, Country=="CN" & nestStrParen=="(iK + iL) + (iQ)"), level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1980 = 1 or 1991 = 1")
+<<CES_Spaghetti_Graph_U, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models with useful work ($u$).">>=
+cesFittedDataU <- filter(fitted_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
+                                                                      "(iK + iL) + (iU)", 
+                                                                      "(iL + iU) + (iK)", 
+                                                                      "(iU + iK) + (iL)"))
+spaghettiPlot(data=cesFittedDataU, facet_formula=Country~nestStrParen, level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1900=1 or 1950=1)")
 @
@@
 
-\twocolumn{}
 <<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7, fig.cap="LINEX model (with energy) resampling results.">>=
-linexCoeffsData <- filter(coeffs_df, model=="linex", energy=="iQ")
+linexCoeffsData <- filter(coeffs_df, model=="linex", energy %in% c("iX", "iU"))
 standardScatterPlot(data=linexCoeffsData, aes(a_0, c_t), facet_formula=country~energy, alpha=0.05) +
@@
 <<LINEX_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7.1, fig.cap="LINEX fitted models.">>=
-linexFittedData <- filter(fitted_df, model=="linex", energy=="iQ")
+linexFittedData <- filter(fitted_df, model=="linex", energy %in% c("iX", "iU"))
 spaghettiPlot(data=linexFittedData, facet_formula=Country~energy, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1980=1 or 1991=1)")
-@
-\onecolumn{}
+    labs(y="Indexed GDP (1900=1 or 1950=1)")
+@
 

### 2014-08-01 Workflow/Workflow.Rmd
Updates to Workflow file.

@@
 This command is fast; it can be run on a laptop.    
-* Build and reload the `EconData` package.    
+* Build and reload the `EconData` package on a local machine.    
 * Push the changes to GitHub.   
 * On acc, Pull from GitHub.     
-* On node-00, say `install_github("MatthewHeun/Econ-Growth-R-Analysis/Packages/EconData")`.
+* Install the `EconData` package from GitHub to dahl
+    + `ssh` to node-00 on dahl.   
+    + Open an R shell by saying `R` at the command prompt.    
+    + Say `require(devtools)`.
+    + Say `install_github("MatthewHeun/Econ-Growth-R-Analysis/Packages/EconData")`.
+
 This makes the historical data available to the nodes of dahl.

### 2014-08-01 Workflow/Workflow.Rmd
Workflow updated to include $SRC.
REXS1960 now UK only.

@@
     + It is probably best to modify an existing `<Source>_batch.bash` file.      
-    + Be sure to edit the `OUTDIR` variable to be `OUTDIR="$LOC_PATH/data_resample/<Source>"`.
-    + Change the final line (the one that runs the `OrigModels.R script`) to be `ssh node-xx "cd $LOC_PATH; Scripts/OrigModels.R -S <Source> &> $OUTDIR/node-xx.txt" &`.   
+    + Be sure to edit the `$SRC` variable.
     + Distribute the work over the nodes in a way that makes sense.
@@
 * `cd` to the `Econ-Growth-R-Analysis` directory from fs1.calvin.edu.
+* Run `Scripts/<Source>_batch.bash "-n 2 -C -d"` followed by `more data_resample/<SOURCE>/node*.txt` to obtain a printout of what will be executed.    
 * Run `Scripts/<Source>_batch.bash "-n 2 -C"` to test that things work as expected.

### 2014-08-01 Workflow/Workflow.Rmd
Improved Workflow.Rmd.
Now discussed tmp_big_data.

@@
 * Install the `EconData` package from GitHub to dahl
-    + `ssh` to node-00 on dahl.   
+    + `ssh` to node-00 on dahl. (For some reason, this doesn't work from `fs1` or any other node.)   
     + Open an R shell by saying `R` at the command prompt.    
@@
 * From a local computer, say `Scripts/DownloadResults.R -u <user> -S <Source>` to download the files.
+* The files are downloaded to the `Packages/EconData/tmp_big_data` directory on the local machine.
+* Manually move the files to `Packages/EconData/data` if you want them to be available in the `EconData` package.
+This manual step avoids large data files automatically included in the `EconData` package, 
+thereby slowing everything down.
 

### 2014-08-01 Workflow/Workflow.Rmd
PostProcess uses -S instead of -R. -R is still an option.

@@
 ### Post-process the results
-* Run `Scripts/PostProcess.R -R data_resample/<Source>` on a node of dahl to create:       
+* Run `Scripts/PostProcess.R -S <Source>` on a node of dahl to create:       
     + `Packages/EconData/data/<Source>_Coeffs.rda` and

### 2014-08-01 Scripts/PostProcess.R

@@ -21,12 +21,20 @@ cat('\n')
 
 # Provide a way to specify directory of resampled data
 option_list <- list(
-  make_option(c("-R", "--resamplePath"), default="data_resample/Calvin",
-              help="path to resampled data [default=%default]")
+  make_option(c("-S", "--Source"), default="Calvin", 
+              help="data source [default=%default]"),
+  make_option(c("-R", "--resamplePath"),
+              help="relative path to directory in which to store resample data. [default=data_resample/<Source>]")
 )
 # Parse the option list
 opts <- parse_args(OptionParser(option_list=option_list))
 print(opts)
+
+if (is.null(opts$resamplePath)){
+  # Didn't specify a resample path. 
+  # Use data_resample/<Source>
+  opts$resamplePath <- file.path("data_resample", opts$Source)
+}
 
 # Get the data Source from the resamplePath.
 dir_pieces <- strsplit(opts$resamplePath, split=.Platform$file.sep)[[1]]
@@ -71,9 +79,6 @@ cat(paste("Loading and saving", Source, "fitted models...")); cat("\n")
 Fitted <- foreach(country=countryAbbrevs, .combine=rbind, .errorhandling="remove") %dopar% {
   loadResampledData(path=opts$resamplePath, country=country, kind="fitted")
 }
-# system.time(Fitted2 <- loadResampledData(path="data_resample", kind="fitted"))
-# Add the Source to the data frame.
-Fitted$Source <- Source
 # Relevel the country abbreviations, nestStr, nestStrParen, and energy in Fitted
 Fitted$Country <- relevelFactor(as.factor(Fitted$Country), levs=countryAbbrevs)
 Fitted$nestStr <- relevelFactor(as.factor(Fitted$nestStr), levs=nestStrLevels)

### 2014-08-01 Articles/Article_EcolEcon_2014/Paper2.Rnw
Added Paper2.pdf to .gitignore.

--- 2014-07-30 Articles/Article_Heun_Warr_2014/EcolEcon_HeunWarr.Rnw
@@
-% This article has been prepared for publication in **** in RStudio with knitr.
+% This article has been prepared for publication in Ecological Economics in RStudio with knitr.
 % According to http://www.elsevier.com/author-schemas/the-elsarticle-latex-document-class, we should be using the
@@
 % both ahead of and behind the text for our paper.
-% -- Matthew Kuperus Heun, 2013-01-18
+% -- Matthew Kuperus Heun, 2014-08-01
 
@@
 require(EconData)
-require(lattice)
-require(latticeExtra)
+# require(lattice)
+# require(latticeExtra)
 require(ggplot2)
-require(car)
-require(mosaic)
-require(xtable)
-require(nlmrt)
+# require(car)
+# require(mosaic)
+# require(xtable)
+# require(nlmrt)
 # require(micEconCES)
 require(plyr)
-require(dplyr)
+# require(dplyr)
 # Provides access to data melting. 
 # See http://cran.r-project.org/web/packages/reshape2/reshape2.pdf
-require(reshape2) 
+# require(reshape2) 
 # tikz allows use of LaTeX formatting and font in graphs. 
@@
 # require(tikzDevice) 
-trellis.par.set(theme=theme.mosaic())
-options(width=75)
-options(show.signif.stars=TRUE)
+# trellis.par.set(theme=theme.mosaic())
+# options(width=75)
+# options(show.signif.stars=TRUE)
 require(knitr)
@@
 # Graph Heights
-maxHeight <- 8.5 # Inches
-ninePanelScatterGraphHeight <- maxHeight # Inches
+# maxHeight <- 8.5 # Inches
+# ninePanelScatterGraphHeight <- maxHeight # Inches
 
 # Graph Widths
-maxWidth <- 6.5 # Inches
-fourPanelScatterGraphWidth <- maxWidth # Inches
-
-presentationGraph1RowHeight <- 2.8 # Inches
-presentationGraph2ColWidth <- 2 # Inches
-presentationGraph1ColWidth <- 2*presentationGraph2ColWidth
-h_param_graph <- 2.07 # Inches for a single panel
-h_param_axis <- 0.86 # Inches (also includes whatever margin is applied)
+# maxWidth <- 6.5 # Inches
+# fourPanelScatterGraphWidth <- maxWidth # Inches
+# 
+# presentationGraph1RowHeight <- 2.8 # Inches
+# presentationGraph2ColWidth <- 2 # Inches
+# presentationGraph1ColWidth <- 2*presentationGraph2ColWidth
+# h_param_graph <- 2.07 # Inches for a single panel
+# h_param_axis <- 0.86 # Inches (also includes whatever margin is applied)
 # sfParameterGraphHeight <- h_param_graph + h_param_axis
-cdParameterGraphHeight <- 2*h_param_graph + h_param_axis
-cesParameterGraphHeight <- 3*h_param_graph + h_param_axis
-linexParameterGraphHeight <- h_param_graph + h_param_axis
-sfParameterGraphWidth <- maxWidth
-cdParameterGraphWidth <- maxWidth
-cesParameterGraphWidth <- maxWidth
-linexParameterGraphWidth <- maxWidth
+# cdParameterGraphHeight <- 2*h_param_graph + h_param_axis
+# cesParameterGraphHeight <- 3*h_param_graph + h_param_axis
+# linexParameterGraphHeight <- h_param_graph + h_param_axis
+# sfParameterGraphWidth <- maxWidth
+# cdParameterGraphWidth <- maxWidth
+# cesParameterGraphWidth <- maxWidth
+# linexParameterGraphWidth <- maxWidth
 # Other graph parameters that apply to all graphs
-scaleTextSize <- 0.8  # Multiple of normal size
-scaleTickSize <- -0.5 # 50% of normal size and pointing INWARD!
+# scaleTextSize <- 0.8  # Multiple of normal size
+# scaleTickSize <- -0.5 # 50% of normal size and pointing INWARD!
 
@@
 # Load historical data
-historicalData <- REXS # From the EconData package
+historicalData <- rbind.fill(REXS1960, IST, Leeds) # From the EconData package
 # Load coefficients from all models in one large data frame
-coeffs_df <- tbl_df(REXS_Coeffs)
+AllCoeffs <- rbind(REXS1960_Coeffs, IST_Coeffs, Leeds_Coeffs)
+AllCoeffs$Source <- as.factor(replace(AllCoeffs$Source, which(AllCoeffs$Source=="REXS1960"), "REXS"))
+AllCoeffs$Source <- relevelFactor(AllCoeffs$Source, levs = c("REXS", "IST", "Leeds"))
+AllCoeffs$energy <- relevelFactor(AllCoeffs$energy, levs = energyLevels)
 # Load fitted data from all models in one large data frame
-fitted_df <- tbl_df(REXS_Fitted)
-
-# Load the original models.
-oModels <- REXS_Models
+AllFitted <- rbind(REXS1960_Fitted, IST_Fitted, Leeds_Fitted)
+AllFitted$Source <- replace(AllFitted$Source, which(AllFitted$Source=="REXS1960"), "REXS")
+AllFitted$Source <- relevelFactor(as.factor(AllFitted$Source), levs = c("REXS", "IST", "Leeds"))
+AllFitted$energy <- relevelFactor(AllFitted$energy, levs=energyLevels)
 @
@@
 
+\author[BenWarr]{Benjamin Warr}
+\author[IST]{Tiago Domingos}
+\author[Leeds]{Paul Brockway}
+\author[Leeds]{Julia Steinberger}
 \author[CalvinEngr]{Matthew Kuperus Heun\corref{cor1}}
 \ead{mkh2@calvin.edu}
-\author[BenWarr]{Benjamin Warr}
-\author[Stellenbosch]{Martin de Wit}
-\author[CalvinMath]{Randall J. Pruim}
-
+
+\address[BenWarr]{Ben Warr's address, Zambia}
+\address[IST]{IST, Lisbon, Portugal}
+\address[Leeds]{Leeds University, Leeds, UK}
 \cortext[cor1]{Corresponding author}
 \address[CalvinEngr]{Engineering Department, Calvin College, Grand Rapids, MI 49546, USA}
-\address[Stellenbosch]{Faculty of Economics and Management Sciences, School of Public Leadership, Stellenbosch University, P.O. Box 610, Bellville 7535, South Africa}
-\address[CalvinMath]{Mathematics \& Statistics Department, Calvin College, Grand Rapids, MI 49546, USA}
-\address[BenWarr]{Ben Warr's address, Zambia}
 
@@
 %% keywords here, in the form: keyword \sep keyword
-economic growth \sep energy \sep Cobb-Douglas \sep CES \sep LINEX
+economic growth \sep exergy \sep energy \sep Cobb-Douglas \sep CES \sep LINEX
 %% MSC codes here, in the form: \MSC code \sep code
@@
 %++++++++++++++++++++++++++++++
-\subsection{Economy Types} 
-\label{sec:Economy_Types}
-%++++++++++++++++++++++++++++++
-
-The REXS data set include US, UK, JP, and AT.
-(See Table~\ref{tab:Economy_Examples}.)
-
-\begin{table} \caption{REXS economies and years of evaluation.} \label{tab:Economy_Examples} 
-  \begin{center}
-%     \begin{tabular}{r c c l l} 
-%       \multirow{3}{*}{Developed} & \includegraphics[height=0.11in]{flag/flag_US.png} & US & USA & \multirow{3}{*}{1900--2000}\\
-%                                  & \includegraphics[height=0.11in]{flag/flag_UK.png} & UK & United Kingdom & \\
-%                                  & \includegraphics[height=0.11in]{flag/flag_JP.png} & JP & Japan          & \\
-%                                  & \includegraphics[height=0.11in]{flag/flag_AT.png} & AT & Austria        & \\1950--2000
-%     \end{tabular}
-    \begin{tabular}{c c l l} 
-      \includegraphics[height=0.11in]{flag/flag_US.png} & US & USA            & \multirow{3}{*}{1900--2000}\\
-      \includegraphics[height=0.11in]{flag/flag_UK.png} & UK & United Kingdom & \\
-      \includegraphics[height=0.11in]{flag/flag_JP.png} & JP & Japan          & \\
-      \hline
-      \includegraphics[height=0.11in]{flag/flag_AT.png} & AT & Austria        & 1950--2000
-    \end{tabular}
-  \end{center}
-\end{table}
+\subsection{Economies} 
+\label{sec:Economies}
+%++++++++++++++++++++++++++++++
+
+Discuss economies here.
 
@@
 
-REXS.
+Discuss data sources here.
 
@@
 
-Figure~\ref{fig:Historical_Graph} presents historical data, 
-including indexed values for 
-output ($y$), 
-capital stock ($k$), 
-labor ($l$), and 
-energy ($q$) 
-for 1900--2000 (US, UK, JP) and 1950--2000 (AT). 
-%
-<<Historical_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=7.5, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), and thermal energy ($q$).">>=
-historicalPlot(historicalData)
-@
+Graph(s) of historical data here.
 
@@
 
-<<CD_lambda_theta_graph, fig.pos="H", fig.align='center', fig.width=4, fig.height=4.5, fig.cap="$\\lambda$ and $\\theta$ values for Cobb-Douglas resample models.">>=
-cdCoeffsData <- filter(coeffs_df, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iX", "iK+iL+iU"))
-standardScatterPlot(data=cdCoeffsData, mapping=aes(scale, lambda), facet_formula=country~energy, alpha=0.05) +
+<<CD_lambda_theta_graph, fig.pos="H", fig.align='center', fig.width=4, fig.height=4.5, fig.cap="$\\lambda$ and $\\theta$ values for UK Cobb-Douglas resample models.">>=
+cdCoeffsData <- subset(AllCoeffs, subset = model=="cd")
+standardScatterPlot(data=cdCoeffsData, mapping=aes(scale, lambda), facet_formula=energy~Source, alpha=0.05) +
 #     scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
@@
 
-<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=3.9, fig.height=4, fig.cap="Cobb-Douglas resample model parameters.">>=
-cdCoeffsData <- filter(coeffs_df, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iX", "iK+iL+iU"))
-standardTriPlot(data=cdCoeffsData, facet_formula=country~energy)
+<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=3.9, fig.height=4, fig.cap="UK Cobb-Douglas resample model parameters.">>=
+standardTriPlot(data=cdCoeffsData, facet_formula=energy~Source)
 @
@@
 <<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=4, fig.height=4.5, fig.cap="Cobb-Douglas fitted models.">>=
-cdFittedData <- filter(fitted_df, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iX", "iK+iL+iU"))
-spaghettiPlot(data=cdFittedData, facet_formula=Country~energy, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1900=1 or 1950=1)")
+cdFittedData <- subset(AllFitted, subset = model=="cd")
+spaghettiPlot(data=cdFittedData, facet_formula=energy~Source, level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1960=1)")
 @
@@
 
-<<CES_lambda_gamma_graph_X, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with exergy ($x$).">>=
+<<CES_lambda_gamma_graph_X, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with exergy ($x$).", eval=FALSE>>=
 cesCoeffsDataX <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
@@
     labs(x=expression(gamma), y=expression(lambda))
-@
-
-<<CES_sigma1_delta1_graph_X, fig.pos="H", fig.align='center', fig.width=5, fig.height=5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with exergy ($x$).">>=
+
+@
+
+<<CES_sigma1_delta1_graph_X, fig.pos="H", fig.align='center', fig.width=5, fig.height=5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with exergy ($x$).", eval=FALSE>>=
 standardScatterPlot(data=cesCoeffsDataX, mapping=aes(delta_1, sigma_1), facet_formula=country~nestStrParen, alpha=0.05) +
@@
 
-<<CES_sigma_delta_graph_X, fig.pos="H", fig.align='center', fig.width=4.4, fig.height=5, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models using exergy ($x$).">>=
+<<CES_sigma_delta_graph_X, fig.pos="H", fig.align='center', fig.width=4.4, fig.height=5, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models using exergy ($x$).", eval=FALSE>>=
 standardScatterPlot(data=subset(cesCoeffsDataX, nestStrParen != "(iK + iL) + ()"),
@@
 
-<<CES_ternary_graphX, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models with exergy ($x$).">>=
+<<CES_ternary_graphX, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models with exergy ($x$).", eval=FALSE>>=
 standardTriPlot(data=cesCoeffsDataX, facet_formula=country~nestStrParen)
@@
 
-<<CES_Spaghetti_Graph_X, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models with exergy ($x$).">>=
+<<CES_Spaghetti_Graph_X, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models with exergy ($x$).", eval=FALSE>>=
 cesFittedDataX <- filter(fitted_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
@@
 
-<<CES_lambda_gamma_graph_U, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with useful work ($u$).">>=
+<<CES_lambda_gamma_graph_U, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with useful work ($u$).", eval=FALSE>>=
 cesCoeffsDataU <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
@@
 
-<<CES_sigma1_delta1_graph_U, fig.pos="H", fig.align='center', fig.width=5, fig.height=5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with useful work ($u$).">>=
+<<CES_sigma1_delta1_graph_U, fig.pos="H", fig.align='center', fig.width=5, fig.height=5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with useful work ($u$).", eval=FALSE>>=
 standardScatterPlot(data=cesCoeffsDataU, mapping=aes(delta_1, sigma_1), facet_formula=country~nestStrParen, alpha=0.05) +
@@
 
-<<CES_sigma_delta_graph_U, fig.pos="H", fig.align='center', fig.width=4.4, fig.height=5, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models with useful work ($u$).">>=
+<<CES_sigma_delta_graph_U, fig.pos="H", fig.align='center', fig.width=4.4, fig.height=5, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models with useful work ($u$).", eval=FALSE>>=
 standardScatterPlot(data=subset(cesCoeffsDataU, nestStrParen != "(iK + iL) + ()"),
@@
 
-<<CES_Spaghetti_Graph_U, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models with useful work ($u$).">>=
+<<CES_Spaghetti_Graph_U, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models with useful work ($u$).", eval=FALSE>>=
 cesFittedDataU <- filter(fitted_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
@@
 Again, historical data are shown as a black line, 
-the fit to historical data is shown as a white linem and 
+the fit to historical data is shown as a white line and 
 the gray band encompasses 95\% of the fits to resampled data.
 
-<<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7, fig.cap="LINEX model (with energy) resampling results.">>=
-linexCoeffsData <- filter(coeffs_df, model=="linex", energy %in% c("iX", "iU"))
-standardScatterPlot(data=linexCoeffsData, aes(a_0, c_t), facet_formula=country~energy, alpha=0.05) +
-    labs(x=expression(a[0]), y=expression(c[t])) +
-     scale_x_continuous(limits=c(-1, 2), breaks=c(-1, 0, 1.0, 2.0)) +
-     scale_y_continuous(limits=c(0, 10), breaks=c(0, 5, 10))
-@
-
-<<LINEX_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7.1, fig.cap="LINEX fitted models.">>=
-linexFittedData <- filter(fitted_df, model=="linex", energy %in% c("iX", "iU"))
-spaghettiPlot(data=linexFittedData, facet_formula=Country~energy, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1900=1 or 1950=1)")
+<<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=4, fig.height=4, fig.cap="LINEX model (with energy) resampling results.">>=
+linexCoeffsData <- subset(AllCoeffs, subset = model=="linex")
+standardScatterPlot(data=linexCoeffsData, aes(a_0, c_t), facet_formula=energy~Source, alpha=0.05) +
+    labs(x=expression(a[0]), y=expression(c[t]))
+@
+
+<<LINEX_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=4, fig.height=4, fig.cap="LINEX fitted models.">>=
+linexFittedData <- subset(AllFitted, subset = model=="linex")
+spaghettiPlot(data=linexFittedData, facet_formula=energy~Source, level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1960=1)")
 @
@@
 
-Figures~\ref{fig:LINEX_abg_traj_graph_CN} and~\ref{fig:LINEX_abg_traj_graph_IR} 
-show trajectories for China and Iran, respectively.
-**** Can we make a figure that has all 9 graphs in it? --MKH ****
-
-<<LINEX_abg_traj_graph_CN, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="LINEX trajectory for China.">>=
-dataCN <- fortify(oModels$Calvin$CN$linex$`iK+iL+iQ`)
-triPlot(data=dataCN, grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1990")
-@
-
-<<LINEX_abg_traj_graph_IR, fig.pos="H", fig.align='center', fig.width=3, fig.height=1.5, fig.cap="LINEX trajectory for Iran.">>=
-dataIR <- fortify(oModels$Calvin$IR$linex$`iK+iL+iQ`)
-triPlot(data=dataIR, grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1990")
-@
-
-In our testing, Iran is the only country for which the trajectory stays within 
-the constraint triangle for the entire time period.
-Thus, in our fitted models, the LINEX model is nearly always
-violating constraints on $\alpha$, $\beta$, and $\gamma$.
-If the LINEX model were made to respect the constraints,
-it would fit worse than it already does for those countries where
-the constraints are violated (that is, for every country except Iran).
-We did nothing to correct this situation, because it is not clear what should be done.
-\citet{Warr:2012cg} constrained the values of $a_0$ and $c_t$, while still holding them constant
-for the entire time series, such that the constraints on $\alpha$, $\beta$, and $\gamma$
-were respected.
-But, Warr's approach necessarily leads to larger $sse$ values than unconstrained fitting.
-Because unconstrained LINEX models already fit worse than 
-constrained Cobb-Douglas and CES models,
-we chose to report the unconstrained LINEX model fits in this paper.
+Figure~\ref{fig:LINEX_abg_traj_graph_UK}
+show trajectories for the UK and useful work ($u$) from the Leeds data set.
+
+<<LINEX_abg_traj_graph_REXS_UK_U, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="LINEX trajectory for REXS, UK, $u$.">>=
+triPlot(data=fortify(REXS1960_Models$REXS1960$UK$linex$`iK+iL+iU`), grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1960")
+@
+
+<<LINEX_abg_traj_graph_IST_UK_U, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="LINEX trajectory for IST, UK, $u$.">>=
+triPlot(data=fortify(IST_Models$IST$UK$linex$`iK+iL+iU`), grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1960")
+@
+
+<<LINEX_abg_traj_graph_Leeds_UK_U, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="LINEX trajectory for Leeds, UK, $u$.">>=
+triPlot(data=fortify(Leeds_Models$Leeds$UK$linex$`iK+iL+iU`), grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1960")
+@
+
+% In our testing, Iran is the only country for which the trajectory stays within 
+% the constraint triangle for the entire time period.
+% Thus, in our fitted models, the LINEX model is nearly always
+% violating constraints on $\alpha$, $\beta$, and $\gamma$.
+% If the LINEX model were made to respect the constraints,
+% it would fit worse than it already does for those countries where
+% the constraints are violated (that is, for every country except Iran).
+% We did nothing to correct this situation, because it is not clear what should be done.
+% \citet{Warr:2012cg} constrained the values of $a_0$ and $c_t$, while still holding them constant
+% for the entire time series, such that the constraints on $\alpha$, $\beta$, and $\gamma$
+% were respected.
+% But, Warr's approach necessarily leads to larger $sse$ values than unconstrained fitting.
+% Because unconstrained LINEX models already fit worse than 
+% constrained Cobb-Douglas and CES models,
+% we chose to report the unconstrained LINEX model fits in this paper.
 % Constraining $\alpha = 0$ in the case of China would imply that either

### 2014-08-02 Workflow/Workflow.Rmd
Minor changes.

@@
 This makes the historical data available to the nodes of dahl.
-This command doesn't work from fs1 or any of the other nodes of dahl (node-01 through node-42).
+This command doesn't work from `fs1` or any of the other nodes of dahl (node-01 through node-42).
 
@@
 ### Submit the job to dahl
-* `cd` to the `Econ-Growth-R-Analysis` directory from fs1.calvin.edu.
+* `cd` to the `Econ-Growth-R-Analysis` directory from `fs1.calvin.edu`.
 * Run `Scripts/<Source>_batch.bash "-n 2 -C -d"` followed by `more data_resample/<SOURCE>/node*.txt` to obtain a printout of what will be executed.    
@@
 * Manually move the files to `Packages/EconData/data` if you want them to be available in the `EconData` package.
-This manual step avoids large data files automatically included in the `EconData` package, 
+This manual step prevents large data files from being automatically included in the `EconData` package, 
 thereby slowing everything down.

### 2014-08-02 Articles/Article_EcolEcon_2014/Paper2.Rnw
Made a Paper2.Rnw file.
Commented the CES section. Other minor changes to the text.

@@
 
-spaghettiGraphLevel <- 0.95 # Spaghetti graph bands will encompass 95% of the data.
+spaghettiGraphLevel <- 1.0 # Spaghetti graph bands will encompass 95% of the data.
 @
@@
 
-\title{Application of Bootstrap Resampling to REXS Data}
+\title{Paper 2 !DRAFT! Do not circulate!}
 
@@
 
-\author[BenWarr]{Benjamin Warr}
-\author[IST]{Tiago Domingos}
-\author[Leeds]{Paul Brockway}
-\author[Leeds]{Julia Steinberger}
-\author[CalvinEngr]{Matthew Kuperus Heun\corref{cor1}}
-\ead{mkh2@calvin.edu}
-
-\address[BenWarr]{Ben Warr's address, Zambia}
-\address[IST]{IST, Lisbon, Portugal}
-\address[Leeds]{Leeds University, Leeds, UK}
-\cortext[cor1]{Corresponding author}
-\address[CalvinEngr]{Engineering Department, Calvin College, Grand Rapids, MI 49546, USA}
+% \author[BenWarr]{Benjamin Warr}
+% \author[IST]{Tiago Domingos}
+% \author[Leeds]{Paul Brockway}
+% \author[Leeds]{Julia Steinberger}
+% \author[CalvinEngr]{Matthew Kuperus Heun\corref{cor1}}
+% \ead{mkh2@calvin.edu}
+
+% \address[BenWarr]{Ben Warr's address, Zambia}
+% \address[IST]{IST, Lisbon, Portugal}
+% \address[Leeds]{Leeds University, Leeds, UK}
+% \cortext[cor1]{Corresponding author}
+% \address[CalvinEngr]{Engineering Department, Calvin College, Grand Rapids, MI 49546, USA}
 
@@
 %------------------------------
-\subsubsection{Cobb-Douglas (CD) Production Function} 
+\subsubsection{Cobb-Douglas Production Function} 
 \label{sec:CDe}
@@
 
-This production function can be expressed as
+The Cobb-Douglas production function can be expressed as
 %
@@
 $l \equiv L/L_{0}$, 
-$Y$ is represented by GDP, 
-$K$ is expressed in currency units, 
-$L$ is expressed in workers or work-hours/year, and
-0 subscripts indicate values at an initial year.%
+$Y$ (economic output) is represented by GDP, 
+$K$ (capital) is expressed in currency units, 
+$L$ (labor) is expressed in workers or work-hours/year, and
+the 0 subscript indicates values at an initial year.%
   \footnote{Dimensionless, indexed quantities are represented by 
@@
   Model parameters are represented by Greek letters
-($\alpha$, $\beta$, $\lambda$, $\theta$).}
+  ($\alpha$, $\beta$, $\lambda$, $\theta$).
+  }
+Constant returns to scale are represented by the constraint
+$\alpha + \beta = 1$.
 
@@
 time-dependent augmentation term ($A$).
-The LINEX models assumes energy ($e$) is the only factor of production.
+The LINEX model assumes energy ($e$) is the only factor of production.
 
@@
 %
-(\ref{eq:rho_k}) capital stock increase relative to the average of labor and energy and 
+(\ref{eq:rho_k}) capital stock increase relative to the average of labor and energy (capital deepening) and 
 (\ref{eq:rho_l}) labor increase relative to energy.
-The effect of energy ($e$) on production is enhanced if either
+The effect of energy ($e$) on output ($y$) is enhanced if either
 %
@@
 
-Discuss economies here.
+Discuss economies here. EU15 and MX?
 
@@
 Although the details vary from model to model, each of our three models has the general form
-\[
+%
+\begin{equation}
   y = f(t,k,l,e; \theta) + \mathrm{error} \;,
-\]
+\end{equation}
+%
 where $\theta$ is a vector of parameters for the function $f$.
@@
 Thus, a resampled response $\tilde Y'$ can be computed as 
-\[
-\tilde Y_i' = \hat y_i \pm r_j
-\]
+%
+\begin{equation} \label{eq:Y_tilde}
+  \tilde Y_i' = \hat y_i \pm r_j \; ,
+\end{equation}
+%
 where 
-\[
-r_i = y_i - \hat y_i
-\]
-both the sign ($\pm$) and the index of the residual 
-($j$,~typically different from $i$) 
+%
+\begin{equation}
+  r_i = y_i - \hat y_i \; .
+\end{equation}
+%
+In Equation~\ref{eq:Y_tilde}, both the sign ($\pm$) 
+and the index ($j$,~typically different from $i$) 
+of the residual ($r$) 
 are chosen at random (with replacement). 
 We repeated the resampling process 1000 times for each
-combination of growth model and country, 
+combination of growth model, country, and data source, 
 both with and without energy as appropriate.
@@
 The fit to historical data is shown as a white line.
-The gray band encompasses 95\% of the fits to resampled data.
+The gray band encompasses \Sexpr{spaghettiGraphLevel*100}\% of the fits to resampled data.
 
@@
 standardScatterPlot(data=cdCoeffsData, mapping=aes(scale, lambda), facet_formula=energy~Source, alpha=0.05) +
-#     scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
-#     scale_y_continuous(breaks=c(0, 0.025, 0.05, 0.075)) +    
+    scale_x_continuous(limits=c(0.95, 1.05), breaks=c(0.95, 1.0)) +
+    scale_y_continuous(breaks=c(0.01, 0.015, 0.02)) +    
     labs(x=expression(theta), y=expression(lambda))
@@
 
-<<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=4, fig.height=4.5, fig.cap="Cobb-Douglas fitted models.">>=
+<<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=4, fig.height=4.5, fig.cap="UK Cobb-Douglas fitted models.">>=
 cdFittedData <- subset(AllFitted, subset = model=="cd")
 spaghettiPlot(data=cdFittedData, facet_formula=energy~Source, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)")
+    labs(y="Indexed GDP (1960=1)") +
+  scale_x_continuous(breaks=c(1960, 1980, 2000))
 @
@@
 
-The CES model without and with energy is given by 
-Equations~\ref{eq:CES}--\ref{eq:CESekl}. 
-The \texttt{R} \citep{R} package \texttt{micEconCES} 
-\citep{Henningsen:2011td} was used to estimate parameters 
-$\lambda$, $\gamma$, $\delta$, $\delta_1$, $\rho$, and $\rho_1$. 
-The \texttt{cesEst} function of \texttt{micEconCES} provides 
-several algorithm options for parameter estimation.
-The default algorithm (Levenberg-Marquardt) does not respect
-parameter constraints (see Section~\ref{sec:CES}) and, 
-in our testing, nearly always violated them, often returning
-negative values for elasticity of substitution~($\sigma$) parameters.
-Thus, we used the two fitting algorithms available in \texttt{cesEst} that
-respect coefficient constraints: \texttt{PORT} and \texttt{L-BFGS-B}.
-
-Our CES parameter estimation algorithm starts with an eleven-value grid search
-in $\rho$ and $\rho_1$ (9, 2, 1, 0.43, 0.25, 0.1, -0.1, -0.5, -0.75, -0.9, -0.99),
-which corresponds to $\sigma$ and $\sigma_1$ values of
-0.1, 0.33, 0.5, 0.7, 0.8, 0.9, 1.11, 2, 4, 10, and 100, respectively.
-During the grid search, values of $\rho$ and $\rho_1$ are fixed,
-and values of $\lambda$, $\gamma$, $\delta$, and $\delta_1$ are estimated 
-by gradient search with the \texttt{PORT} and \texttt{L-BFGS-B} algorithms.
-In all, 121 gradient searches in $\lambda$, $\gamma$, $\delta$, and $\delta_1$
-at grid points representing all combinations of $\rho$ and $\rho_1$ are attempted.
-During the grid search portion of our algorithm, starting values for the free parameters
-are $\lambda$ = 0.015/year, $\delta$ = 0.5, $\delta_1$ = 0.5, 
-and $\gamma$ is set to a value such that the mean of the residuals is zero
-by the \texttt{cesEst} function.
-
-Next, a gradient search (using both \texttt{PORT} and \texttt{L-BFGS-B}) 
-is attempted wherein all fitting parameters 
-($\lambda$, $\gamma$, $\delta$, $\delta_1$, $\rho$, and $\rho_1$)
-are allowed to float. 
-The start values for fitting parameters are taken from 
-the grid search fit that provided the lowest $sse$ (Equation~\ref{eq:sse}).
-
-If resampled data are being fitted, a prior fit to historical data is available.
-In the final step of our algorithm, 
-a gradient search (using both \texttt{PORT} and \texttt{L-BFGS-B})
-uses coefficients from the best 
-fit to historical data as its starting point. 
-In this final gradient search, all model parameters 
-($\lambda$, $\gamma$, $\delta$, $\delta_1$, $\rho$, and $\rho_1$)
-are considered free parameters.
-
-The fit with lowest $sse$ of all above trials is deemed the winner,
-and its fitting parameters are used as the model.
-
-\citet{Henningsen:2011td}, 
-in their detailed analysis of \citet{Kemfert:1998vd}, found that
-
-\begin{quote}
-\ldots the Levenberg-Marquardt and the \texttt{PORT} algorithms 
-are---at least in this study---most likely to find the 
-coefficients that give the best fit to the model, 
-where the \texttt{PORT} algorithm can be used to restrict the estimates 
-to the economically meaningful region.
-\end{quote}
-
-In our testing, we found that to be mostly true. 
-\texttt{PORT} nearly always provided lower
-$sse$ than \texttt{L-BFGS-B}, despite the fact that 
-\texttt{L-BFGS-B} often reports convergence
-and \texttt{PORT} does not for the same data
-(i.e., for the same $y$, $k$, $l$, and $e$ data).
-
-Coefficients for each resampled CES model for all countries and all nests
-are shown in 
-Figures~\ref{fig:CES_lambda_gamma_graph_X}--\ref{fig:CES_sigma_delta_graph_X}. 
-The white crosshair on each graph shows the location 
-of the fit to historical data. 
-In Figures~\ref{fig:CES_sigma1_delta1_graph_X} and~\ref{fig:CES_sigma_delta_graph_X},
-the bottom of the vertical axis represents $\sigma = 0$.
-The top of the vertical axis represents $\sigma = \infty$.
-
-Note that as $\delta$ or $\delta_1$ approaches 0 (1) 
-in Equations~\ref{eq:CES}--\ref{eq:CESekl},
-the corresponding value of $\sigma$ or $\sigma_1$ becomes irrelevant, and
-resample points along the left (right) edge of
-Figures \ref{fig:CES_sigma1_delta1_graph_X} and \ref{fig:CES_sigma_delta_graph_X}
-are equivalent.
-That is, all points along the left (right) edge of
-Figures \ref{fig:CES_sigma1_delta1_graph_X} and \ref{fig:CES_sigma_delta_graph_X}
-have the same $sse$. 
-As a consequence, 
-the \texttt{cesEst} fitting algorithm has no way 
-to discriminate among points along the left (right) edge of
-Figures \ref{fig:CES_sigma1_delta1_graph_X} and \ref{fig:CES_sigma_delta_graph_X}. 
-Thus, resample point estimates where $\delta$ or $\delta_1$ approaches 0 (1)
-tend to cluster at the locations of the initial grid search in 
-$\sigma$ or $\sigma_1$
-(0.1, 0.33, 0.5, 0.7, 0.8, 0.9, 1.11, 2, 4, 10, and 100).
-
-<<CES_lambda_gamma_graph_X, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with exergy ($x$).", eval=FALSE>>=
-cesCoeffsDataX <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
-                                                                      "(iK + iL) + (iX)", 
-                                                                      "(iL + iX) + (iK)", 
-                                                                      "(iX + iK) + (iL)"))
-standardScatterPlot(data=cesCoeffsDataX, mapping=aes(gamma_coef, lambda), facet_formula=country~nestStrParen, alpha=0.05) +
-    scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
-    labs(x=expression(gamma), y=expression(lambda))
-
-@
-
-<<CES_sigma1_delta1_graph_X, fig.pos="H", fig.align='center', fig.width=5, fig.height=5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with exergy ($x$).", eval=FALSE>>=
-standardScatterPlot(data=cesCoeffsDataX, mapping=aes(delta_1, sigma_1), facet_formula=country~nestStrParen, alpha=0.05) +
-    coord_trans(y="sigma") +
-    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-    labs(x=expression(delta[1]), y=expression(sigma[1]))
-@
-
-<<CES_sigma_delta_graph_X, fig.pos="H", fig.align='center', fig.width=4.4, fig.height=5, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models using exergy ($x$).", eval=FALSE>>=
-standardScatterPlot(data=subset(cesCoeffsDataX, nestStrParen != "(iK + iL) + ()"),
-                    mapping=aes(delta, sigma), facet_formula=country~nestStrParen, alpha=0.05) +
-    coord_trans(y="sigma") +
-    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-    labs(x=expression(delta), y=expression(sigma))
-@
-
-We can develop pseudo $\alpha$, $\beta$, and $\gamma$ parameters 
-for the CES model, based on values of $\delta$ and $\delta_1$.
-Table~\ref{tab:CES_abg_equations} shows the permuted equations for each CES nesting.
-
-\begin{table} \caption{Equations for $\alpha$, $\beta$, and $\gamma$ for the various CES nestings.} 
-\label{tab:CES_abg_equations} 
-  \begin{center}
-    \begin{tabular}{c c c c c} 
-      Nesting    & Equation        & $\alpha$                & $\beta$                 & $\gamma$                \\
-      \hline
-      ($kl$)     & \ref{eq:CES}    & $\delta_1$              & $1 - \delta_1$          & 0                       \\
-      ($kl$)$e$  & \ref{eq:CESkle} & $\delta \delta_1$       & $\delta (1 - \delta_1)$ & $1 - \delta$            \\   
-      ($le$)$k$  & \ref{eq:CESlek} & $1 - \delta$            & $\delta \delta_1$       & $\delta (1 - \delta_1)$ \\
-      ($ek$)$l$  & \ref{eq:CESekl} & $\delta (1 - \delta_1)$ & $1 - \delta$            & $\delta \delta_1$       \\
-    \end{tabular}
-  \end{center}
-\end{table}
-
-Figure~\ref{fig:CES_ternary_graph} shows 
-$\alpha$, $\beta$, and $\gamma$ parameters for the CES model for all nests and countries.
-Figure~\ref{fig:CES_ternary_graph} is comparable to
-the ternary graph for the Cobb-Douglas models, 
-Figure~\ref{fig:CD_Ternary_Scatter_Graph}.
-
-<<CES_ternary_graphX, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models with exergy ($x$).", eval=FALSE>>=
-standardTriPlot(data=cesCoeffsDataX, facet_formula=country~nestStrParen)
-@
-
-Figure~\ref{fig:CES_Spaghetti_Graph} compares CES model predictions 
-to historical data for all nestings. 
-As with the Cobb-Douglas results, 
-historical data are shown as a black line, 
-the fit to historical data is shown as a white line, and 
-the gray band encompasses 95\% of the fits to resampled data.
-
-<<CES_Spaghetti_Graph_X, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models with exergy ($x$).", eval=FALSE>>=
-cesFittedDataX <- filter(fitted_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
-                                                                      "(iK + iL) + (iX)", 
-                                                                      "(iL + iX) + (iK)", 
-                                                                      "(iX + iK) + (iL)"))
-spaghettiPlot(data=cesFittedDataX, facet_formula=Country~nestStrParen, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1900=1 or 1950=1)")
-@
-
-<<CES_lambda_gamma_graph_U, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with useful work ($u$).", eval=FALSE>>=
-cesCoeffsDataU <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
-                                                                      "(iK + iL) + (iU)", 
-                                                                      "(iL + iU) + (iK)", 
-                                                                      "(iU + iK) + (iL)"))
-standardScatterPlot(data=cesCoeffsDataU, mapping=aes(gamma_coef, lambda), facet_formula=country~nestStrParen, alpha=0.05) +
-    scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
-    labs(x=expression(gamma), y=expression(lambda))
-@
-
-<<CES_sigma1_delta1_graph_U, fig.pos="H", fig.align='center', fig.width=5, fig.height=5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with useful work ($u$).", eval=FALSE>>=
-standardScatterPlot(data=cesCoeffsDataU, mapping=aes(delta_1, sigma_1), facet_formula=country~nestStrParen, alpha=0.05) +
-    coord_trans(y="sigma") +
-    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-    labs(x=expression(delta[1]), y=expression(sigma[1]))
-@
-
-<<CES_sigma_delta_graph_U, fig.pos="H", fig.align='center', fig.width=4.4, fig.height=5, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models with useful work ($u$).", eval=FALSE>>=
-standardScatterPlot(data=subset(cesCoeffsDataU, nestStrParen != "(iK + iL) + ()"),
-                    mapping=aes(delta, sigma), facet_formula=country~nestStrParen, alpha=0.05) +
-    coord_trans(y="sigma") +
-    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-    labs(x=expression(delta), y=expression(sigma))
-@
-
-<<CES_Spaghetti_Graph_U, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models with useful work ($u$).", eval=FALSE>>=
-cesFittedDataU <- filter(fitted_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
-                                                                      "(iK + iL) + (iU)", 
-                                                                      "(iL + iU) + (iK)", 
-                                                                      "(iU + iK) + (iL)"))
-spaghettiPlot(data=cesFittedDataU, facet_formula=Country~nestStrParen, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1900=1 or 1950=1)")
-@
+Information on CES models goes here.
+
+% The CES model without and with energy is given by 
+% Equations~\ref{eq:CES}--\ref{eq:CESekl}. 
+% The \texttt{R} \citep{R} package \texttt{micEconCES} 
+% \citep{Henningsen:2011td} was used to estimate parameters 
+% $\lambda$, $\gamma$, $\delta$, $\delta_1$, $\rho$, and $\rho_1$. 
+% The \texttt{cesEst} function of \texttt{micEconCES} provides 
+% several algorithm options for parameter estimation.
+% The default algorithm (Levenberg-Marquardt) does not respect
+% parameter constraints (see Section~\ref{sec:CES}) and, 
+% in our testing, nearly always violated them, often returning
+% negative values for elasticity of substitution~($\sigma$) parameters.
+% Thus, we used the two fitting algorithms available in \texttt{cesEst} that
+% respect coefficient constraints: \texttt{PORT} and \texttt{L-BFGS-B}. 
+% 
+% Our CES parameter estimation algorithm starts with an eleven-value grid search
+% in $\rho$ and $\rho_1$ (9, 2, 1, 0.43, 0.25, 0.1, -0.1, -0.5, -0.75, -0.9, -0.99),
+% which corresponds to $\sigma$ and $\sigma_1$ values of
+% 0.1, 0.33, 0.5, 0.7, 0.8, 0.9, 1.11, 2, 4, 10, and 100, respectively.
+% During the grid search, values of $\rho$ and $\rho_1$ are fixed,
+% and values of $\lambda$, $\gamma$, $\delta$, and $\delta_1$ are estimated 
+% by gradient search with the \texttt{PORT} and \texttt{L-BFGS-B} algorithms.
+% In all, 121 gradient searches in $\lambda$, $\gamma$, $\delta$, and $\delta_1$
+% at grid points representing all combinations of $\rho$ and $\rho_1$ are attempted.
+% During the grid search portion of our algorithm, starting values for the free parameters
+% are $\lambda$ = 0.015/year, $\delta$ = 0.5, $\delta_1$ = 0.5, 
+% and $\gamma$ is set to a value such that the mean of the residuals is zero
+% by the \texttt{cesEst} function.
+% 
+% Next, a gradient search (using both \texttt{PORT} and \texttt{L-BFGS-B}) 
+% is attempted wherein all fitting parameters 
+% ($\lambda$, $\gamma$, $\delta$, $\delta_1$, $\rho$, and $\rho_1$)
+% are allowed to float. 
+% The start values for fitting parameters are taken from 
+% the grid search fit that provided the lowest $sse$ (Equation~\ref{eq:sse}).
+% 
+% If resampled data are being fitted, a prior fit to historical data is available.
+% In the final step of our algorithm, 
+% a gradient search (using both \texttt{PORT} and \texttt{L-BFGS-B})
+% uses coefficients from the best 
+% fit to historical data as its starting point. 
+% In this final gradient search, all model parameters 
+% ($\lambda$, $\gamma$, $\delta$, $\delta_1$, $\rho$, and $\rho_1$)
+% are considered free parameters.
+% 
+% The fit with lowest $sse$ of all above trials is deemed the winner,
+% and its fitting parameters are used as the model.
+% 
+% \citet{Henningsen:2011td}, 
+% in their detailed analysis of \citet{Kemfert:1998vd}, found that 
+% 
+% \begin{quote}
+% \ldots the Levenberg-Marquardt and the \texttt{PORT} algorithms 
+% are---at least in this study---most likely to find the 
+% coefficients that give the best fit to the model, 
+% where the \texttt{PORT} algorithm can be used to restrict the estimates 
+% to the economically meaningful region.
+% \end{quote}
+% 
+% In our testing, we found that to be mostly true. 
+% \texttt{PORT} nearly always provided lower
+% $sse$ than \texttt{L-BFGS-B}, despite the fact that 
+% \texttt{L-BFGS-B} often reports convergence
+% and \texttt{PORT} does not for the same data
+% (i.e., for the same $y$, $k$, $l$, and $e$ data).
+% 
+% Coefficients for each resampled CES model for all countries and all nests
+% are shown in 
+% Figures~\ref{fig:CES_lambda_gamma_graph_X}--\ref{fig:CES_sigma_delta_graph_X}. 
+% The white crosshair on each graph shows the location 
+% of the fit to historical data. 
+% In Figures~\ref{fig:CES_sigma1_delta1_graph_X} and~\ref{fig:CES_sigma_delta_graph_X},
+% the bottom of the vertical axis represents $\sigma = 0$.
+% The top of the vertical axis represents $\sigma = \infty$.
+% 
+% Note that as $\delta$ or $\delta_1$ approaches 0 (1) 
+% in Equations~\ref{eq:CES}--\ref{eq:CESekl},
+% the corresponding value of $\sigma$ or $\sigma_1$ becomes irrelevant, and
+% resample points along the left (right) edge of
+% Figures \ref{fig:CES_sigma1_delta1_graph_X} and \ref{fig:CES_sigma_delta_graph_X}
+% are equivalent.
+% That is, all points along the left (right) edge of
+% Figures \ref{fig:CES_sigma1_delta1_graph_X} and \ref{fig:CES_sigma_delta_graph_X}
+% have the same $sse$. 
+% As a consequence, 
+% the \texttt{cesEst} fitting algorithm has no way 
+% to discriminate among points along the left (right) edge of
+% Figures \ref{fig:CES_sigma1_delta1_graph_X} and \ref{fig:CES_sigma_delta_graph_X}. 
+% Thus, resample point estimates where $\delta$ or $\delta_1$ approaches 0 (1)
+% tend to cluster at the locations of the initial grid search in 
+% $\sigma$ or $\sigma_1$
+% (0.1, 0.33, 0.5, 0.7, 0.8, 0.9, 1.11, 2, 4, 10, and 100).
+% 
+% <<CES_lambda_gamma_graph_X, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with exergy ($x$).", eval=FALSE>>=
+% cesCoeffsDataX <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
+%                                                                       "(iK + iL) + (iX)", 
+%                                                                       "(iL + iX) + (iK)", 
+%                                                                       "(iX + iK) + (iL)"))
+% standardScatterPlot(data=cesCoeffsDataX, mapping=aes(gamma_coef, lambda), 
+%                     facet_formula=country~nestStrParen, alpha=0.05) +
+%     scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
+%     labs(x=expression(gamma), y=expression(lambda))
+% 
+% @
+% 
+% <<CES_sigma1_delta1_graph_X, fig.pos="H", fig.align='center', fig.width=5, fig.height=5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with exergy ($x$).", eval=FALSE>>=
+% standardScatterPlot(data=cesCoeffsDataX, mapping=aes(delta_1, sigma_1), facet_formula=country~nestStrParen, alpha=0.05) +
+%     coord_trans(y="sigma") +
+%     scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
+%     scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
+%     labs(x=expression(delta[1]), y=expression(sigma[1]))
+% @
+% 
+% <<CES_sigma_delta_graph_X, fig.pos="H", fig.align='center', fig.width=4.4, fig.height=5, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models using exergy ($x$).", eval=FALSE>>=
+% standardScatterPlot(data=subset(cesCoeffsDataX, nestStrParen != "(iK + iL) + ()"),
+%                     mapping=aes(delta, sigma), facet_formula=country~nestStrParen, alpha=0.05) +
+%     coord_trans(y="sigma") +
+%     scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
+%     scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
+%     labs(x=expression(delta), y=expression(sigma))
+% @
+% 
+% We can develop pseudo $\alpha$, $\beta$, and $\gamma$ parameters 
+% for the CES model, based on values of $\delta$ and $\delta_1$.
+% Table~\ref{tab:CES_abg_equations} shows the permuted equations for each CES nesting.
+% 
+% \begin{table} \caption{Equations for $\alpha$, $\beta$, and $\gamma$ for the various CES nestings.} 
+% \label{tab:CES_abg_equations} 
+%   \begin{center}
+%     \begin{tabular}{c c c c c} 
+%       Nesting    & Equation        & $\alpha$                & $\beta$                 & $\gamma$                \\
+%       \hline
+%       ($kl$)     & \ref{eq:CES}    & $\delta_1$              & $1 - \delta_1$          & 0                       \\
+%       ($kl$)$e$  & \ref{eq:CESkle} & $\delta \delta_1$       & $\delta (1 - \delta_1)$ & $1 - \delta$            \\   
+%       ($le$)$k$  & \ref{eq:CESlek} & $1 - \delta$            & $\delta \delta_1$       & $\delta (1 - \delta_1)$ \\
+%       ($ek$)$l$  & \ref{eq:CESekl} & $\delta (1 - \delta_1)$ & $1 - \delta$            & $\delta \delta_1$       \\
+%     \end{tabular}
+%   \end{center}
+% \end{table}
+% 
+% Figure~\ref{fig:CES_ternary_graph} shows 
+% $\alpha$, $\beta$, and $\gamma$ parameters for the CES model for all nests and countries.
+% Figure~\ref{fig:CES_ternary_graph} is comparable to
+% the ternary graph for the Cobb-Douglas models, 
+% Figure~\ref{fig:CD_Ternary_Scatter_Graph}.
+% 
+% <<CES_ternary_graphX, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models with exergy ($x$).", eval=FALSE>>=
+% standardTriPlot(data=cesCoeffsDataX, facet_formula=country~nestStrParen)
+% @
+% 
+% Figure~\ref{fig:CES_Spaghetti_Graph} compares CES model predictions 
+% to historical data for all nestings. 
+% As with the Cobb-Douglas results, 
+% historical data are shown as a black line, 
+% the fit to historical data is shown as a white line, and 
+% the gray band encompasses \Sexpr{spaghettiGraphLevel*100}\% of the fits to resampled data.
+% 
+% <<CES_Spaghetti_Graph_X, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models with exergy ($x$).", eval=FALSE>>=
+% cesFittedDataX <- filter(fitted_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
+%                                                                       "(iK + iL) + (iX)", 
+%                                                                       "(iL + iX) + (iK)", 
+%                                                                       "(iX + iK) + (iL)"))
+% spaghettiPlot(data=cesFittedDataX, facet_formula=Country~nestStrParen, level=spaghettiGraphLevel) +
+%     labs(y="Indexed GDP (1900=1 or 1950=1)")
+% @
+% 
+% <<CES_lambda_gamma_graph_U, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with useful work ($u$).", eval=FALSE>>=
+% cesCoeffsDataU <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
+%                                                                       "(iK + iL) + (iU)", 
+%                                                                       "(iL + iU) + (iK)", 
+%                                                                       "(iU + iK) + (iL)"))
+% standardScatterPlot(data=cesCoeffsDataU, mapping=aes(gamma_coef, lambda), facet_formula=country~nestStrParen, alpha=0.05) +
+%     scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
+%     labs(x=expression(gamma), y=expression(lambda))
+% @
+% 
+% <<CES_sigma1_delta1_graph_U, fig.pos="H", fig.align='center', fig.width=5, fig.height=5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with useful work ($u$).", eval=FALSE>>=
+% standardScatterPlot(data=cesCoeffsDataU, mapping=aes(delta_1, sigma_1), facet_formula=country~nestStrParen, alpha=0.05) +
+%     coord_trans(y="sigma") +
+%     scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
+%     scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
+%     labs(x=expression(delta[1]), y=expression(sigma[1]))
+% @
+% 
+% <<CES_sigma_delta_graph_U, fig.pos="H", fig.align='center', fig.width=4.4, fig.height=5, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models with useful work ($u$).", eval=FALSE>>=
+% standardScatterPlot(data=subset(cesCoeffsDataU, nestStrParen != "(iK + iL) + ()"),
+%                     mapping=aes(delta, sigma), facet_formula=country~nestStrParen, alpha=0.05) +
+%     coord_trans(y="sigma") +
+%     scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
+%     scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
+%     labs(x=expression(delta), y=expression(sigma))
+% @
+% 
+% <<CES_Spaghetti_Graph_U, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models with useful work ($u$).", eval=FALSE>>=
+% cesFittedDataU <- filter(fitted_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
+%                                                                       "(iK + iL) + (iU)", 
+%                                                                       "(iL + iU) + (iK)", 
+%                                                                       "(iU + iK) + (iL)"))
+% spaghettiPlot(data=cesFittedDataU, facet_formula=Country~nestStrParen, level=spaghettiGraphLevel) +
+%     labs(y="Indexed GDP (1900=1 or 1950=1)")
+% @
 
@@
 the fit to historical data is shown as a white line and 
-the gray band encompasses 95\% of the fits to resampled data.
-
-<<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=4, fig.height=4, fig.cap="LINEX model (with energy) resampling results.">>=
+the gray band encompasses \Sexpr{spaghettiGraphLevel*100}\% of the fits to resampled data.
+
+<<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=4, fig.height=4, fig.cap="UK LINEX model (with energy) resampling results.">>=
 linexCoeffsData <- subset(AllCoeffs, subset = model=="linex")
 standardScatterPlot(data=linexCoeffsData, aes(a_0, c_t), facet_formula=energy~Source, alpha=0.05) +
+    scale_x_continuous(breaks=c(0.6, 0.8, 1.0)) +
     labs(x=expression(a[0]), y=expression(c[t]))
@@
 
-<<LINEX_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=4, fig.height=4, fig.cap="LINEX fitted models.">>=
+<<LINEX_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=4, fig.height=4, fig.cap="UK LINEX fitted models.">>=
 linexFittedData <- subset(AllFitted, subset = model=="linex")
 spaghettiPlot(data=linexFittedData, facet_formula=energy~Source, level=spaghettiGraphLevel) +
+    scale_x_continuous(breaks=c(1960, 1980, 2000)) + 
     labs(y="Indexed GDP (1960=1)")
@@
 \begin{equation} \label{eq:LINEX_alpha}
-  \alpha = \frac{k}{y}\frac{\partial y}{\partial k} = a_0 \left( \frac{l + e}{k} \right) \;,
+  \alpha \equiv \frac{k}{y}\frac{\partial y}{\partial k} = a_0 \left( \frac{l + e}{k} \right) \;,
 \end{equation}
@@
 \begin{equation} \label{eq:LINEX_beta}
-  \beta = \frac{l}{y} \frac{\partial y}{\partial l} = a_0 \left[ c_t \left( \frac{l}{e}\right) - \frac{l}{k} \right] \;,
+  \beta \equiv \frac{l}{y} \frac{\partial y}{\partial l} = a_0 \left[ c_t \left( \frac{l}{e}\right) - \frac{l}{k} \right] \;,
 \end{equation}
@@
 \begin{equation} \label{eq:LINEX_beta_2}
-  \gamma = \frac{e}{y} \frac{\partial y}{\partial e} 
+  \gamma \equiv \frac{e}{y} \frac{\partial y}{\partial e} 
          = 1 - a_0 \left[ \frac{e}{k} + c_t \frac{l}{e} \right] 
@@
 the constraints on $\alpha$, $\beta$, and $\gamma$ are respected.
-Conversely, if the trajectory goes outside the triangle, one of the constraints has been violated.
-
-Figure~\ref{fig:LINEX_abg_traj_graph_UK}
-show trajectories for the UK and useful work ($u$) from the Leeds data set.
-
-<<LINEX_abg_traj_graph_REXS_UK_U, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="LINEX trajectory for REXS, UK, $u$.">>=
+Conversely, if the trajectory goes outside the triangle, the constraints have been violated.
+
+Figure~\ref{fig:LINEX_abg_traj_graph_REXS_UK_U}
+shows trajectories for the UK and useful work ($u$) from the REXS data set.
+
+<<LINEX_abg_traj_graph_REXS_UK_U, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="UK LINEX trajectory for REXS with $u$.">>=
 triPlot(data=fortify(REXS1960_Models$REXS1960$UK$linex$`iK+iL+iU`), grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1960")
@@
 
-<<LINEX_abg_traj_graph_IST_UK_U, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="LINEX trajectory for IST, UK, $u$.">>=
+Figure~\ref{fig:LINEX_abg_traj_graph_IST_UK_U}
+shows trajectories for the UK and useful work ($u$) from the IST data set.
+
+<<LINEX_abg_traj_graph_IST_UK_U, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="UK LINEX trajectory for IST with $u$.">>=
 triPlot(data=fortify(IST_Models$IST$UK$linex$`iK+iL+iU`), grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1960")
@@
 
-<<LINEX_abg_traj_graph_Leeds_UK_U, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="LINEX trajectory for Leeds, UK, $u$.">>=
+Figure~\ref{fig:LINEX_abg_traj_graph_Leeds_UK_U}
+shows trajectories for the UK and useful work ($u$) from the Leeds data set.
+
+<<LINEX_abg_traj_graph_Leeds_UK_U, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="UK LINEX trajectory for Leeds with $u$.">>=
 triPlot(data=fortify(Leeds_Models$Leeds$UK$linex$`iK+iL+iU`), grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1960")
@@
 %%\bibliography{<your-bib-database>}
-\bibliography{HeunWarr.bib}
+\bibliography{Paper2.bib}
 

### 2014-08-04 Articles/Article_EcolEcon_2014/Paper2.Rnw
Now including a historical graph.

@@
 require(EconData)
-# require(lattice)
-# require(latticeExtra)
 require(ggplot2)
-# require(car)
-# require(mosaic)
-# require(xtable)
-# require(nlmrt)
-# require(micEconCES)
 require(plyr)
-# require(dplyr)
 # Provides access to data melting. 
 # See http://cran.r-project.org/web/packages/reshape2/reshape2.pdf
-# require(reshape2) 
-# tikz allows use of LaTeX formatting and font in graphs. 
-# Allows for a consistent look across the paper.
-# See http://r-forge.r-project.org/R/?group_id=440 for instructions 
-# on installing tikzDevice.
-# require(tikzDevice) 
-# trellis.par.set(theme=theme.mosaic())
-# options(width=75)
-# options(show.signif.stars=TRUE)
+require(reshape2) 
 require(knitr)
@@
 
-Graph(s) of historical data here.
+Figure~\ref{fig:Historical_Data} shows a graph of historical data.
+
+<<Historical_Data, fig.pos="H", fig.align='center', fig.width=6.6, fig.height=3, fig.cap="Historical data.">>=
+historicalPlot(historicalData, 
+               facet_formula = Country ~ Source, 
+               lines_formula = iGDP + iK + iL + iXp + iXf + iU ~ Year, 
+               line_types = c(1,2,3,4,5,6)) + 
+  xlab("") + 
+  ylab("Indexed (1960=1)")
+@
 

### 2014-08-04 Articles/Article_EcolEcon_2014/Paper2.Rnw
Paper2 now includes a second graph of historical data. New graph has different faceting, thereby allowing more-direct comparison of different sources.

@@
 
-Figure~\ref{fig:Historical_Data} shows a graph of historical data.
-
-<<Historical_Data, fig.pos="H", fig.align='center', fig.width=6.6, fig.height=3, fig.cap="Historical data.">>=
-historicalPlot(historicalData, 
+Figure~\ref{fig:Historical_Data_1} shows a graph of historical data.
+
+<<Historical_Data_1, fig.pos="H", fig.align='center', fig.width=6.6, fig.height=3, fig.cap="Historical data.", eval=TRUE>>=
+mdata <- melt(historicalData, 
+              measure.vars = c("iGDP", "iK", "iL", "iXp", "iXf", "iU"), 
+              variable.name = "variable",
+              value.name = "value")
+historicalPlot(mdata, 
                facet_formula = Country ~ Source, 
-               lines_formula = iGDP + iK + iL + iXp + iXf + iU ~ Year, 
+               lines_formula = variable + value ~ Year, 
                line_types = c(1,2,3,4,5,6)) + 
+  xlab("") + 
+  ylab("Indexed (1960=1)")
+@
+
+Figure~\ref{fig:Historical_Data_2} shows the same data in a different form.
+
+<<Historical_Data_2, fig.pos="H", fig.align='center', fig.width=8, fig.height=3, fig.cap="Historical data.", eval=TRUE>>=
+historicalPlot(mdata, 
+               facet_formula=Country~variable, 
+               lines_formula=Source+value~Year, 
+               line_types=c(1,2,3)) +  
   xlab("") + 

### 2014-08-05 Articles/Article_EcolEcon_2014/Paper2.Rnw
Deleted unneeded constants.

@@
 <<constants, include=FALSE, eval=TRUE>>=
-# Graph Heights
-# maxHeight <- 8.5 # Inches
-# ninePanelScatterGraphHeight <- maxHeight # Inches
-
-# Graph Widths
-# maxWidth <- 6.5 # Inches
-# fourPanelScatterGraphWidth <- maxWidth # Inches
-# 
-# presentationGraph1RowHeight <- 2.8 # Inches
-# presentationGraph2ColWidth <- 2 # Inches
-# presentationGraph1ColWidth <- 2*presentationGraph2ColWidth
-# h_param_graph <- 2.07 # Inches for a single panel
-# h_param_axis <- 0.86 # Inches (also includes whatever margin is applied)
-# sfParameterGraphHeight <- h_param_graph + h_param_axis
-# cdParameterGraphHeight <- 2*h_param_graph + h_param_axis
-# cesParameterGraphHeight <- 3*h_param_graph + h_param_axis
-# linexParameterGraphHeight <- h_param_graph + h_param_axis
-# sfParameterGraphWidth <- maxWidth
-# cdParameterGraphWidth <- maxWidth
-# cesParameterGraphWidth <- maxWidth
-# linexParameterGraphWidth <- maxWidth
-# Other graph parameters that apply to all graphs
-# scaleTextSize <- 0.8  # Multiple of normal size
-# scaleTickSize <- -0.5 # 50% of normal size and pointing INWARD!
-
 spaghettiGraphLevel <- 1.0 # Spaghetti graph bands will encompass 95% of the data.

### 2014-08-05 Articles/Article_EnerEcon_2014/EconGrowth2.Rnw
new bit in file after upgrading RStudio.
Now using upgraded historicalPlot function.

@@
 \begin{document}
+\SweaveOpts{concordance=TRUE}
 
@@
 <<Historical_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=7.5, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), and thermal energy ($q$).">>=
-historicalPlot(historicalData)
+mdata <- melt(historicalData, 
+              measure.vars = c("iGDP", "iK", "iL", "iQp"), 
+              value.name = "value", 
+              variable.name = "variable") 
+historicalPlot(mdata, 
+               facet_formula = Country ~ Source, 
+               lines_formula = variable + value ~ Year, 
+               line_types = c(1,2,3,4)) +
+  xlab("") +
+  ylab("Indexed (1980-1 or 1991=1")
 @

### 2014-08-05 Articles/Article_EcolEcon_2014/Paper2.Rnw
Now uses loadPostProcessedData function.

@@
 # Load coefficients from all models in one large data frame
+REXS1960_Coeffs <- loadPostProcessedData(Source = "REXS1960", kind = "coeffs")
+IST_Coeffs <- loadPostProcessedData(Source = "IST", kind = "coeffs")
+Leeds_Coeffs <- loadPostProcessedData(Source = "Leeds", kind = "coeffs")
 AllCoeffs <- rbind(REXS1960_Coeffs, IST_Coeffs, Leeds_Coeffs)
@@
 # Load fitted data from all models in one large data frame
+REXS1960_Fitted <- loadPostProcessedData(Source = "REXS1960", kind = "fitted")
+IST_Fitted <- loadPostProcessedData(Source = "IST", kind = "fitted")
+Leeds_Fitted <- loadPostProcessedData(Source = "Leeds", kind = "fitted")
 AllFitted <- rbind(REXS1960_Fitted, IST_Fitted, Leeds_Fitted)

### 2014-08-05 Articles/Article_EcolEcon_2014/Paper2.Rnw
Added or 1978=1 to graphs.

@@
   xlab("") + 
-  ylab("Indexed (1960=1)")
+  ylab("Indexed (1960=1 or 1978=1)")
 @

### 2014-08-06 Articles/Article_EcolEcon_2014/Paper2.Rnw
All articles now use the new loadPostProcessedData function.

@@
 <<LINEX_abg_traj_graph_REXS_UK_U, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="UK LINEX trajectory for REXS with $u$.">>=
+REXS1960_Models <- loadPostProcessedData(Source = "REXS1960", kind = "models")
 triPlot(data=fortify(REXS1960_Models$REXS1960$UK$linex$`iK+iL+iU`), grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1960")
@@
 <<LINEX_abg_traj_graph_IST_UK_U, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="UK LINEX trajectory for IST with $u$.">>=
+IST_Models <- loadPostProcessedData(Source = "IST", kind = "models")
 triPlot(data=fortify(IST_Models$IST$UK$linex$`iK+iL+iU`), grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1960")
@@
 <<LINEX_abg_traj_graph_Leeds_UK_U, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="UK LINEX trajectory for Leeds with $u$.">>=
+Leeds_Models <- loadPostProcessedData(Source = "Leeds", kind = "models")
 triPlot(data=fortify(Leeds_Models$Leeds$UK$linex$`iK+iL+iU`), grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1960")

### 2014-08-06 Articles/Article_EnerEcon_2014/EconGrowth2-GraphsOnly.Rnw
All articles now use the new loadPostProcessedData function.

--- 2014-07-29 Article/EconGrowth2-GraphsOnly.Rnw
@@
 # Load historical data
-# In Rstudio, this paper is generated from it's directory, which is "Article".
-# We need to define paths relative to the location of the paper. 
-# Relative path to historical data from Article
 historicalData <- Calvin # From the EconData package
-
 # Load coefficients from all models in one large data frame
-coeffs_df <- tbl_df(Calvin_Coeffs)
+coeffs_df <- loadPostProcessedData(Source = "Calvin", kind = "coeffs")
 # Load fitted data from all models in one large data frame
-fitted_df <- tbl_df(Calvin_Fitted)
-
+fitted_df <- loadPostProcessedData(Source = "Calvin", kind = "fitted")
 # Load the original models.
-oModels <- Calvin_Models
+oModels <- loadPostProcessedData(Source = "Calvin", kind = "models")
 

### 2014-08-06 Articles/Article_EnerEcon_2014/EconGrowth2.Rnw
All articles now use the new loadPostProcessedData function.

@@
 # Load coefficients from all models in one large data frame
-coeffs_df <- tbl_df(Calvin_Coeffs)
+coeffs_df <- loadPostProcessedData(Source = "Calvin", kind = "coeffs")
 # Load fitted data from all models in one large data frame
-fitted_df <- tbl_df(Calvin_Fitted)
-
+fitted_df <- loadPostProcessedData(Source = "Calvin", kind = "fitted")
 # Load the original models.
-oModels <- Calvin_Models
+oModels <- loadPostProcessedData(Source = "Calvin", kind = "models")
 @

### 2014-08-06 Articles/Article_Heun_Warr_2014/EcolEcon_HeunWarr.Rnw
All articles now use the new loadPostProcessedData function.

@@
 # Load coefficients from all models in one large data frame
-coeffs_df <- tbl_df(REXS_Coeffs)
+coeffs_df <- loadPostProcessedData(Source = "REXS", kind = "coeffs")
 # Load fitted data from all models in one large data frame
-fitted_df <- tbl_df(REXS_Fitted)
-
+fitted_df <- loadPostProcessedData(Source = "REXS", kind = "fitted")
 # Load the original models.
-oModels <- REXS_Models
+oModels <- loadPostProcessedData(Source = "REXS", kind = "models")
 @

### 2014-08-06 Articles/Article_JAE_2014/ZAGrowth_JAE.Rnw
All articles now use the new loadPostProcessedData function.

@@
 # Load coefficients from all models in one large data frame
-coeffs_df <- tbl_df(Calvin_Coeffs)
+coeffs_df <- loadPostProcessedData(Source = "Calvin", kind = "coeffs")
 coeffs_df_ZA <- subset(coeffs_df, subset=country=="ZA")
 # Load fitted data from all models in one large data frame
-fitted_df <- tbl_df(Calvin_Fitted)
+fitted_df <- loadPostProcessedData(Source = "Calvin", kind = "fitted")
 fitted_df_ZA <- subset(fitted_df, subset=Country=="ZA")
 # Load the original models.
-oModels_ZA <- Calvin_Models$ZA
+oModels <- loadPostProcessedData(Source = "Calvin", kind = "models")
+oModels_ZA <- oModels$Calvin$ZA
 @

### 2014-08-06 Workflow/Workflow.Rmd
Added a note about countryAbbrevs variable.
Improvements to the Workflow.Rmd document.

@@
 author: "Matthew Kuperus Heun"
-date: "29 July 2014"
+date: "6 August 2014"
 output: html_document
@@
 
-This file contains information about the workflow for analyses.
+This file contains information about the workflow for resampling analyses of a data source.
 
@@
 * Add any Excel workbooks or other metadata in `data/Excel Workbooks/<Source>`.
+* Add any new countries to the `countryAbbrevs` variable in `Packages/EconData/R/Constants.R`.
 
@@
 The file will be stored at `Packages/EconData/data/<Source>.rda`.
-This command is fast; it can be run on a laptop.    
+This command is fast; it can be run on a local machine.    
 * Build and reload the `EconData` package on a local machine.    
 * Push the changes to GitHub.   
-* On acc, Pull from GitHub.     
+* On `acc`, pull from GitHub.     
 * Install the `EconData` package from GitHub to dahl
@@
 
-This makes the historical data available to the nodes of dahl.
-This command doesn't work from `fs1` or any of the other nodes of dahl (node-01 through node-42).
+`install_github` makes the historical data available to the nodes of `dahl`.
+This command doesn't work from `fs1` or any of the other nodes of `dahl` (`node-01` through `node-42`).
 
@@
 * Push the `<Source>_batch.bash` file to GitHub.
-* On acc, Pull from GitHub.
+* On `acc`, pull from GitHub.
 
@@
 * Then do `Scripts/<Source>_batch.bash "-n 1000 -C"` to do a complete run.
-* Check dahl's status at (http://fs1.calvin.edu/ganglia/?m=load_one&r=hour&s=by%2520name&c=dahl&h=&sh=1&hc=4&z=small).
-* Check progress with `more data_resample/<Source>/node-*.txt`.
+* Check `dahl`'s status at (http://fs1.calvin.edu/ganglia/?m=load_one&r=hour&s=by%2520name&c=dahl&h=&sh=1&hc=4&z=small).
+* Check progress with `more data_resample/<Source>/node*.txt`.
 
 ### Post-process the results
-* Run `Scripts/PostProcess.R -S <Source>` on a node of dahl to create:       
-    + `Packages/EconData/data/<Source>_Coeffs.rda` and
-    + `Packages/EconData/data/<Source>_Fitted.rda`.
-
-Note that this command will need to be issued from a node of the cluster (e.g., node-00), not from `fs1.calvin.edu`.
-`fs1` does not have a full install of R.
+* Run `Scripts/PostProcess.R -S <Source>` on a node of `dahl` to create:       
+    + `data_postprocessed/<Source>_Coeffs.rda` and
+    + `data_postprocessed/<Source>_Fitted.rda`.         
+* Note that this command must be issued from a node of the cluster (e.g., `node-00`), not from `fs1.calvin.edu`.
+`fs1` does not have a full install of `R`.
 
 ### Download post-processed results to local machine
-* From a local computer, say `Scripts/DownloadResults.R -u <user> -S <Source> -d`, where `<user>` is 
-a username on dahl, `<Source>` is the data source of interest, and `-d` will 
-print the files to be transferred to the local machine, rather than transfer them.
+* From a local machine, say `Scripts/DownloadPostProcessed.bash -u <user> -S <Source> -d`, where `<user>` is 
+a username on `dahl`, `<Source>` is the data source of interest, and `-d` (debug) will 
+show the files to be transferred to the local machine, without actually transferring them.
 * Verify that the list of files to be transferred looks right.
-* From a local computer, say `Scripts/DownloadResults.R -u <user> -S <Source>` to download the files.
-* The files are downloaded to the `Packages/EconData/tmp_big_data` directory on the local machine.
-* Manually move the files to `Packages/EconData/data` if you want them to be available in the `EconData` package.
-This manual step prevents large data files from being automatically included in the `EconData` package, 
-thereby slowing everything down.
+* From a local computer, say `Scripts/DownloadPostProcessed.bash -u <user> -S <Source>` to download the files.
+* The files are downloaded to the `data_postprocessed` directory on the local machine.
+* Use the function `loadPostProcessedData` in the `EconData` package to load the downloaded data into
+the environment.
 
-### Add processed results to the EconData package
-* On the local machine, build and reload the `EconData` package.
-
-At this point, all new results should be available in the `EconData` package on the local machine.
-Objects will be named:
-
-* `<Source>_Coeffs` (from the file `Packages/EconData/data/<Source>_Coeffs.rda`)  
-* `<Source>_Fitted` (from the file `Packages/EconData/data/<Source>_Fitted.rda`)  
-* `<Source>_Models` (from the file `Packages/EconData/data/<Source>_OrigModels.rda`)
+The data files are saved with `saveRDS` by `PostProcess.R`, so `loadPostProcessedData` uses `readRDS` to 
+load the data into memory. 
+As a consequence, `loadPostProcessedData` returns an object which must be assigned to a variable in `R`.

### 2014-08-06 Articles/Article_EnerEcon_2014/EconGrowth2-GraphsOnly.Rnw
EconGrowth papers now build with new variable names.

@@
 # Load coefficients from all models in one large data frame
-coeffs_df <- loadPostProcessedData(Source = "Calvin", kind = "coeffs")
+coeffs_df <- loadPostProcessedData(Source = "Calvin", kind = "coeffs", dir = "../../data_postprocessed")
 # Load fitted data from all models in one large data frame
-fitted_df <- loadPostProcessedData(Source = "Calvin", kind = "fitted")
+fitted_df <- loadPostProcessedData(Source = "Calvin", kind = "fitted", dir = "../../data_postprocessed")
 # Load the original models.
-oModels <- loadPostProcessedData(Source = "Calvin", kind = "models")
+oModels <- loadPostProcessedData(Source = "Calvin", kind = "models", dir = "../../data_postprocessed")
 
@@
 <<CD_lambda_theta_graph, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\theta$ values for CD resample models.">>=
-cdCoeffsData <- filter(coeffs_df, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iQ", "iK+iL+iX", "iK+iL+iU"))
+cdCoeffsData <- filter(coeffs_df, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iQp", "iK+iL+iXp", "iK+iL+iU"))
 standardScatterPlot(data=cdCoeffsData, mapping=aes(scale, lambda), facet_formula=country~energy, alpha=0.05) +
@@
 <<CES_lambda_gamma_graph_kle, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with (kl)e nesting.">>=
-cesCoeffsData_kle <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", "(iK + iL) + (iQ)", "(iK + iL) + (iX)", "(iK + iL) + (iU)"))
+cesCoeffsData_kle <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", "(iK + iL) + (iQp)", "(iK + iL) + (iXp)", "(iK + iL) + (iU)"))
 standardScatterPlot(data=cesCoeffsData_kle, mapping=aes(gamma_coef, lambda), facet_formula=country~nestStrParen, alpha=0.05) +
@@
 <<CES_lambda_gamma_graph_lek, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with (le)k nesting.">>=
-cesCoeffsData_lek <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", "(iL + iQ) + (iK)", "(iL + iX) + (iK)", "(iL + iU) + (iK)"))
+cesCoeffsData_lek <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", "(iL + iQp) + (iK)", "(iL + iXp) + (iK)", "(iL + iU) + (iK)"))
 standardScatterPlot(data=cesCoeffsData_lek, mapping=aes(gamma_coef, lambda), facet_formula=country~nestStrParen, alpha=0.05) +
@@
 <<CES_lambda_gamma_graph_ekl, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with (ek)l nesting.">>=
-cesCoeffsData_ekl <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", "(iQ + iK) + (iL)", "(iX + iK) + (iL)", "(iU + iK) + (iL)"))
+cesCoeffsData_ekl <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", "(iQp + iK) + (iL)", "(iXp + iK) + (iL)", "(iU + iK) + (iL)"))
 standardScatterPlot(data=cesCoeffsData_ekl, mapping=aes(gamma_coef, lambda), facet_formula=country~nestStrParen, alpha=0.05) +
@@
 <<CES_Spaghetti_Graph_kle, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models with (kl)e nesting.">>=
-cesFittedData <- filter(fitted_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", "(iK + iL) + (iQ)", "(iK + iL) + (iX)", "(iK + iL) + (iU)"))
+cesFittedData <- filter(fitted_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", "(iK + iL) + (iQp)", "(iK + iL) + (iXp)", "(iK + iL) + (iU)"))
 spaghettiPlot(data=cesFittedData, facet_formula=Country~nestStrParen, level=spaghettiGraphLevel) +
@@
 <<CES_Spaghetti_Graph_lek, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models with (le)k nesting.">>=
-cesFittedData <- filter(fitted_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", "(iL + iQ) + (iK)", "(iL + iX) + (iK)", "(iL + iU) + (iK)"))
+cesFittedData <- filter(fitted_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", "(iL + iQp) + (iK)", "(iL + iXp) + (iK)", "(iL + iU) + (iK)"))
 spaghettiPlot(data=cesFittedData, facet_formula=Country~nestStrParen, level=spaghettiGraphLevel) +
@@
 <<CES_Spaghetti_Graph_ekl, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models with (ek)l nesting.">>=
-cesFittedData <- filter(fitted_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", "(iQ + iK) + (iL)", "(iX + iK) + (iL)", "(iU + iK) + (iL)"))
+cesFittedData <- filter(fitted_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", "(iQp + iK) + (iL)", "(iXp + iK) + (iL)", "(iU + iK) + (iL)"))
 spaghettiPlot(data=cesFittedData, facet_formula=Country~nestStrParen, level=spaghettiGraphLevel) +
@@
 <<LINEX_abg_traj_graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="LINEX trajectory for China with thermal energy $q$.">>=
-data <- fortify(oModels$Calvin$CN$linex$`iK+iL+iQ`)
+data <- fortify(oModels$Calvin$CN$linex$`iK+iL+iQp`)
 triPlot(data=data, grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear")

### 2014-08-06 Articles/Article_EnerEcon_2014/EconGrowth2.Rnw
EconGrowth papers now build with new variable names.

--- 2014-08-05 Articles/Article_EnerEcon_2014/EconGrowth2.Rnw
@@
 \begin{document}
-\SweaveOpts{concordance=TRUE}
 
@@
 
-<<data, include=FALSE>>=
+<<data, include=TRUE, echo=TRUE>>=
 # Load historical data
@@
 # Load coefficients from all models in one large data frame
-coeffs_df <- tbl_df(Calvin_Coeffs)
+print(getwd())
+print(file.exists("data_postprocessed/Calvin_Coeffs.Rdata"))
+coeffs_df <- loadPostProcessedData(Source = "Calvin", kind = "coeffs", dir = "../../data_postprocessed")
 # Load fitted data from all models in one large data frame
-fitted_df <- tbl_df(Calvin_Fitted)
-
+fitted_df <- loadPostProcessedData(Source = "Calvin", kind = "fitted", dir = "../../data_postprocessed")
 # Load the original models.
-oModels <- Calvin_Models
+oModels <- loadPostProcessedData(Source = "Calvin", kind = "models", dir = "../../data_postprocessed")
 @
@@
 <<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=2.9, fig.height=7.7, fig.cap="Cobb-Douglas resample model parameters.">>=
-cdCoeffsData <- filter(coeffs_df, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iQ"))
+cdCoeffsData <- filter(coeffs_df, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iQp"))
 standardTriPlot(data=cdCoeffsData, facet_formula=country~energy)
@@
 <<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=8.2, fig.cap="Cobb-Douglas fitted models.">>=
-cdFittedData <- filter(fitted_df, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iQ"))
+cdFittedData <- filter(fitted_df, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iQp"))
 spaghettiPlot(data=cdFittedData, facet_formula=Country~energy, level=spaghettiGraphLevel) +
@@
 cesCoeffsData <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
-                                                                     "(iK + iL) + (iQ)", 
-                                                                     "(iL + iQ) + (iK)", 
-                                                                     "(iQ + iK) + (iL)"))
+                                                                     "(iK + iL) + (iQp)", 
+                                                                     "(iL + iQp) + (iK)", 
+                                                                     "(iQp + iK) + (iL)"))
 standardScatterPlot(data=cesCoeffsData, mapping=aes(gamma_coef, lambda), facet_formula=country~nestStrParen, alpha=0.05) +
@@
 cesFittedData <- filter(fitted_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
-                                                                     "(iK + iL) + (iQ)", 
-                                                                     "(iL + iQ) + (iK)", 
-                                                                     "(iQ + iK) + (iL)"))
+                                                                     "(iK + iL) + (iQp)", 
+                                                                     "(iL + iQp) + (iK)", 
+                                                                     "(iQp + iK) + (iL)"))
 spaghettiPlot(data=cesFittedData, facet_formula=Country~nestStrParen, level=spaghettiGraphLevel) +
@@
 <<CES_Spaghetti_Graph_CN, fig.pos="H", fig.align='center', fig.width=maxWidth, fig.height=maxHeight, fig.cap="CES fitted models for China with the (kl)e nesting.">>=
-spaghettiPlot(data=subset(cesFittedData, Country=="CN" & nestStrParen=="(iK + iL) + (iQ)"), level=spaghettiGraphLevel) +
+spaghettiPlot(data=subset(cesFittedData, Country=="CN" & nestStrParen=="(iK + iL) + (iQp)"), level=spaghettiGraphLevel) +
     labs(y="Indexed GDP (1980 = 1 or 1991 = 1")
@@
 <<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7, fig.cap="LINEX model (with energy) resampling results.">>=
-linexCoeffsData <- filter(coeffs_df, model=="linex", energy=="iQ")
+linexCoeffsData <- filter(coeffs_df, model=="linex", energy=="iQp")
 standardScatterPlot(data=linexCoeffsData, aes(a_0, c_t), facet_formula=country~energy, alpha=0.05) +
@@
 <<LINEX_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7.1, fig.cap="LINEX fitted models.">>=
-linexFittedData <- filter(fitted_df, model=="linex", energy=="iQ")
+linexFittedData <- filter(fitted_df, model=="linex", energy=="iQp")
 spaghettiPlot(data=linexFittedData, facet_formula=Country~energy, level=spaghettiGraphLevel) +
@@
 <<LINEX_abg_traj_graph_CN, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="LINEX trajectory for China.">>=
-dataCN <- fortify(oModels$Calvin$CN$linex$`iK+iL+iQ`)
+dataCN <- fortify(oModels$Calvin$CN$linex$`iK+iL+iQp`)
 triPlot(data=dataCN, grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1990")
@@
 <<LINEX_abg_traj_graph_IR, fig.pos="H", fig.align='center', fig.width=3, fig.height=1.5, fig.cap="LINEX trajectory for Iran.">>=
-dataIR <- fortify(oModels$Calvin$IR$linex$`iK+iL+iQ`)
+dataIR <- fortify(oModels$Calvin$IR$linex$`iK+iL+iQp`)
 triPlot(data=dataIR, grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1990")

### 2014-08-06 Articles/Article_JAE_2014/ZAGrowth_JAE.Rnw
Works with new var names.

--- 2014-07-29 Articles/Article_JAE_2014/ZAGrowth_JAE.Rnw
@@
 require(ggplot2)
+require(reshape2)
 opts_chunk$set(
@@
 # Load coefficients from all models in one large data frame
-coeffs_df <- tbl_df(Calvin_Coeffs)
+coeffs_df <- loadPostProcessedData(Source = "Calvin", kind = "coeffs", dir = "../../data_postprocessed")
 coeffs_df_ZA <- subset(coeffs_df, subset=country=="ZA")
 # Load fitted data from all models in one large data frame
-fitted_df <- tbl_df(Calvin_Fitted)
+fitted_df <- loadPostProcessedData(Source = "Calvin", kind = "fitted", dir = "../../data_postprocessed")
 fitted_df_ZA <- subset(fitted_df, subset=Country=="ZA")
 # Load the original models.
-oModels_ZA <- Calvin_Models$ZA
+oModels <- loadPostProcessedData(Source = "Calvin", kind = "models", dir = "../../data_postprocessed")
+oModels_ZA <- oModels$Calvin$ZA
 @
@@
 <<Historical_Graph, fig.pos="H", fig.align='center', fig.width=5, fig.height=3, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), and thermal energy ($q$).">>=
-historicalPlot(historicalData)
+mdata <- melt(historicalData, 
+              measure.vars = c("iGDP", "iK", "iL", "iQp"), 
+              value.name = "value", 
+              variable.name = "variable") 
+historicalPlot(mdata, 
+               facet_formula = Country ~ Source, 
+               lines_formula = variable + value ~ Year, 
+               line_types = c(1,2,3,4)) +
+  xlab("") +
+  ylab("Indexed (1980-1 or 1991=1")
 @
@@
 <<CD_lambda_theta_graph, fig.pos="H", fig.align='center', fig.width=5, fig.height=3, fig.cap="$\\lambda$ and $\\theta$ values for CD resample models.">>=
-cdCoeffsData_ZA <- filter(coeffs_df_ZA, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iQ"))
+cdCoeffsData_ZA <- filter(coeffs_df_ZA, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iQp"))
 standardScatterPlot(data=cdCoeffsData_ZA, mapping=aes(scale, lambda), facet_formula=country~energy, alpha=0.05) +
@@
 <<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=5, fig.height=3, fig.cap="Cobb-Douglas resample model parameters.">>=
-cdCoeffsData_ZA <- filter(coeffs_df_ZA, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iQ"))
+cdCoeffsData_ZA <- filter(coeffs_df_ZA, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iQp"))
 standardTriPlot(data=cdCoeffsData_ZA, facet_formula=country~energy)
@@
 <<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=5, fig.height=3, fig.cap="Cobb-Douglas fitted models.">>=
-cdFittedData_ZA <- filter(fitted_df_ZA, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iQ"))
+cdFittedData_ZA <- filter(fitted_df_ZA, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iQp"))
 spaghettiPlot(data=cdFittedData_ZA, facet_formula=Country~energy, level=spaghettiGraphLevel) +
@@
 <<CES_lambda_theta_graph, fig.pos="H", fig.align='center', fig.width=5, fig.height=3, fig.cap="$\\lambda$ and $\\theta$ values for CES resample models with various nestings.">>=
-cesCoeffsData_ZA <- filter(coeffs_df_ZA, model=="ces", nestStr %in% c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"))
+cesCoeffsData_ZA <- filter(coeffs_df_ZA, model=="ces", nestStr %in% c("iK+iL", "iK+iL+iQp", "iL+iQp+iK", "iQp+iK+iL"))
 standardScatterPlot(data=cesCoeffsData_ZA, mapping=aes(gamma_coef, lambda), 
@@
 <<CES_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=5, fig.height=3, fig.cap="CES fitted models with various nestings.">>=
-cesFittedData_ZA <- filter(fitted_df_ZA, model=="ces", nestStr %in% c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"))
+cesFittedData_ZA <- filter(fitted_df_ZA, model=="ces", nestStr %in% c("iK+iL", "iK+iL+iQp", "iL+iQp+iK", "iQp+iK+iL"))
 spaghettiPlot(data=cesFittedData_ZA, facet_formula=Country~nestStrParen, level=spaghettiGraphLevel) +
@@
 <<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=5, fig.height=3, fig.cap="LINEX model (with energy) resampling results.">>=
-linexCoeffsData_ZA <- filter(coeffs_df_ZA, model=="linex", energy=="iQ")
+linexCoeffsData_ZA <- filter(coeffs_df_ZA, model=="linex", energy=="iQp")
 standardScatterPlot(data=linexCoeffsData_ZA, aes(a_0, c_t), facet_formula=country~energy, alpha=0.05) +
@@
 <<LINEX_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=5, fig.height=3, fig.cap="LINEX fitted models.">>=
-linexFittedData_ZA <- filter(fitted_df_ZA, model=="linex", energy=="iQ")
+linexFittedData_ZA <- filter(fitted_df_ZA, model=="linex", energy=="iQp")
 spaghettiPlot(data=linexFittedData_ZA, facet_formula=Country~energy, level=spaghettiGraphLevel) +

### 2014-08-06 Articles/Article_EnerEcon_2014/EconGrowth3.Rnw
v3 of EconGrowth paper.

--- 2014-08-06 Articles/Article_EnerEcon_2014/EconGrowth2.Rnw
@@
 
-<<data, include=TRUE, echo=TRUE>>=
+<<data>>=
 # Load historical data
@@
 # Load coefficients from all models in one large data frame
-print(getwd())
-print(file.exists("data_postprocessed/Calvin_Coeffs.Rdata"))
 coeffs_df <- loadPostProcessedData(Source = "Calvin", kind = "coeffs", dir = "../../data_postprocessed")
@@
 
-\section*{Notes from Martin}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Introduction} 
+\label{sec:Introduction}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \citet{Stresing:2008cq}
-
-**** Notes from Martin ****
-
-To be included somewhere.
-
-Introduction
-
-[1. Listen to what others say
-Identify key issues and important voices]
 
@@
 in economic growth modeling.  
-\citet[p. 26]{Stern:2011bq} provides an overview of how energy is included 
-in mainstream economic, resource economic, and ecological economic models of growth.  
-\citeauthor{Stern:2011bq} points out that energy is usually \emph{not included} 
-as a factor of production in mainstream economic growth models, 
-that energy is seen as the \emph{central driver of growth} 
+Neoclassical economic growth theory attributes output ($Y$) to factors of production:
+capital stock ($K$) and labor ($L$). 
+The Cobb-Douglas production function 
+is the canonical representation of indexed economic output ($y$) as a function of indexed 
+labor ($l$), indexed capital stock ($k$), and an additional exogenous, time-dependent 
+term.%
+  \footnote{The time-dependent term in production functions is often linked
+  to ``technological progress,'' but that is a very narrow reading of Solow's original intent:
+  \begin{quote}
+    It will be seen that I am using the phrase ``technical change''
+    as a short-hand expression for any kind of shift 
+    in the production function. 
+    Thus slowdowns, speed-ups, improvements in the education of the labor force, 
+    and all sorts of things will appear as ``technical change.''~\citep{solow1957technical}
+  \end{quote}
+  }
+This production function can be expressed as
+%
+\begin{equation} \label{eq:CD}
+  y = \theta \mathrm{e}^{\lambda(t-t_0)} k^\alpha l^\beta \;,
+\end{equation}
+%
+\noindent where 
+$y \equiv Y/Y_{0}$,
+$\theta$ is a scale parameter,
+e is the base of the natural logarithm, 
+$\lambda$ is represents the pace of technological progress,
+$t$ (time) is measured in years,
+$k \equiv K/K_{0}$, 
+$l \equiv L/L_{0}$, 
+$Y$ is represented by GDP, 
+$K$ is expressed in currency units, 
+$L$ is expressed in workers or work-hours/year, and
+0 subscripts indicate values at an initial year.%
+\footnote{Dimensionless, indexed quantities are represented by 
+lower-case symbols 
+($y$, $k$, $l$, $e$, $q$, $x$, and $u$), and dimensional 
+quantities are represented by upper-case symbols 
+($Y$, $K$, $L$, $E$, $Q$, $X$, and $U$). 
+Model parameters are represented by Greek letters
+($\alpha$, $\beta$, $\lambda$, $\theta$).}
+
+Neoclassical economic growth theory as expressed in the Cobb-Douglas production 
+function makes no attempt to describe the mechanisms that affect
+economic growth, nor does it attempt to describe how such things as
+slowdowns, speedups, and improvements of the education of the labor force
+($\lambda$) might vary from one economy to the next. 
+The parameters $\alpha$ and $\beta$ indicate the relative roles 
+of capital and labor in the economy.
+Typically, the constraint $\alpha + \beta = 1$ is assumed, 
+indicating constant returns to scale.
+
+As shown in Equation~\ref{eq:CD} above, neoclassical economic theory does not 
+include an explicit term for the role of energy in economic growth. 
+However, \citet{Bashmakov:2007ek}, \citet{Hamilton:2009ui}, \citet{Murphy:2011jh}, 
+\citet{Benes:2012tm}, \citet{Kumhof:2012ua}, and others indicate that the 
+importance of energy for economic growth may far outweigh its cost share in the 
+economy. 
+That neoclassical economic growth theory ignores energy is, therefore, 
+cause for concern, and inquiry into the proper approach for including energy 
+as a factor of production in economic growth modeling is both relevant and important.
+
+Some energy economists augment economic growth models by including energy as an 
+additional (or the only) factor of production. 
+However, there is little agreement on how this should be done. 
+Neither the mathematical form of the energy-augmented 
+production function nor the quantification of energy is consistent in the 
+literature. 
+Furthermore, there has been little empirical work assessing the predictive ability 
+of various energy-augmented production functions for different types of economies. 
+And, very few studies of the importance of energy in economic growth include 
+rigorous statistical assessments of energy-related fitting parameters. 
+This paper contributes to the literature by applying statistically rigorous 
+methods along two coordinates of analysis: form of the energy augmented 
+production function and type of economy.
+
+The remainder of this paper is organized as follows. 
+Section~\ref{sec:lit_review} provides a necessarily brief overview of relevant literature.
+Section~\ref{sec:Coordinates} discusses the coordinates of analysis for the present study. 
+Section~\ref{sec:Sources_of_Data} details sources of data and calculations to 
+generate time series for economic output and factors of production. 
+The procedures for and results from parameter estimation for the various production functions 
+are discussed in Section~\ref{sec:Parameter_Estimation}. 
+Section~\ref{sec:Discussion_of_Results} discusses implications of the parameter estimation 
+results, and Section~\ref{sec:Conclusion} concludes. 
+An appendix provides details of all statistical results.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Literature Review} 
+\label{sec:lit_review}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\citet[p. 26]{Stern:2011bq} provides an overview of approaches to including energy 
+in ecological economic and resource economic models of growth.  
+\citeauthor{Stern:2011bq} points out that 
+energy is seen as the \emph{central driver of growth} 
 in ecological economic (including biophysical economic) models, 
@@
 To break through this theoretical impasse, 
-Stern proposes a synthesized CES production function 
+Stern proposes a synthesized Constant Elasticity of Substitution (CES) 
+production function 
 where the constraints or abundance of energy 
@@
 The inclusion of energy as a factor of production 
-in CES and Cobb-Douglas production functions 
+in Cobb-Douglas and CES production functions 
 is generally accepted by most 
-resource and energy economists and economic growth modelers 
+resource and energy economists
 \citep{Smulders:2003wc, vanderZwaan:2002wn, Kemfert:1998vd}.
@@
 
-[2. Find our own voice
-What is our own argument?]
-
-These are not idle debates. 
-Economic growth models are often used to inform economic policy,
+These are not idle academic debates. 
+Macroeconomic growth models are used often to inform economic policy,
 and the paths of economies worldwide are determined by
@@
 need empirical testing. 
-Furthermore, the quantification of energy ($q$, $x$, or $u$) 
-needs to be empirically assessed.  **** Need more on topic of energy quantification above. ****
 Building on the argument of \citet{Stern:2011bq} 
@@
 
-To gain insights from different countries across different stages of development, 
-we present a comparative analysis among 
-the World Bank’s main categories of countries, 
-namely Developed Countries (DCs), 
-Newly Industrialized Countries (NICs), 
-OPEC countries, and 
-Least Developed Countries (LDCs). 
-**** Move the previous sentence to the ``approach'' section below? ****
-
-Approach
-
-Build on articles using R to test econ growth PF, 
-question what is reported when doing these tests (shen/whalley and others who have used micEconCES).
-
-Discussion and Insights
-
-Does analysis differ from others in the conversation?
-Yes, differs as follows:
-\begin{itemize}
-\item{if one do these test, report on all $\delta$, $\sigma$, $\gamma$, and $\lambda$ 
-values as well as sse. 
-Good fits not evidence of best values, must report uncertainties as well.}
-\item{What motivates nesting of CES? Not well behaved $\rho$ results, driving $\sigma$s.
-Different type of CES with parsimonious factors, sigmas can be generated but not that easy (idea Randy).
-If you run all 3 nesting options, you can identify elasticities of all three factors in relation to each 
-other. Furthermore, you can determine which two factors are driving overall behavior in the aggregate function.}
-\item{necessary of different factors in PF to explain growth for countries in diff. development status}
-\end{itemize}
-
-What do we add to the conversation?
-
-\begin{itemize}
-
-\item{We are able to gain rich insights 
-on what really drives growth from detailed analysis (including uncertainties) 
-by testing all functional forms across many different 
-economy types.}
-
-\item{We were unable to gain new insights from the various energy quantifications that we tried.}
-
-\item{We find, surprisingly, that energy is not necessary 
-to be included alongside $k$ and $l$ in all PF. Models with energy and models without energy
-all perform well on an R$^2$ basis.}
-
-\item{We also find that
-
-(1) covariance of energy($e$) with both $k$ and $l$ is very high, with few exceptions (UK?).
-
-(2) with few exceptions, $\sigma_{(kl)e}$, $\sigma_{ke}$, and $\sigma_{le}$ 
-are all very low (indicating complementarity) (verify!!!!), and
-
-(3) energy-only models (SF$e$ and LINEX) achieve very good fits, just like CD$e$ and CES$e$.
-(should we make this point or not?)}
-
-\item{What does that mean? 
-It is a fallacy to think that saying energy is unnecessary 
-to include in an equation means energy is unimportant for economic growth. How to support this argument?
-
-If you find that energy is unnecessary to include alongside capital and labor 
-to explain growth in one economy at the macro, aggregated level, 
-you should not assume that energy is unimportant as a driver for economic growth for all economies.
-For developed economies, energy is captial intensive: you need to have large capital to make use 
-of energy. In developing economies, you don't need capital to make use of energy. 
-Rather, you need labor.
-
-We need to verify the above by comparison with our results.}
-
-\item{Also signals that different types of countries likely 
-to react differently to energy constraints. 
-Interpret $\sigma$ here, substitution possibilities.}
-
-\end{itemize}
-
-More work?
-
-Big picture
-[insert test test]
-
-Why do we do this? Want to link energy and economics on national level 
-and in a modeled approach,informing energy policy during energy transitions.
-Usually macro energy economic models rely on PF with energy included. 
-Key papers using CES in energy economics incl high impact such as 
-Stern, Gerlagh, Tol etc. 
-Cite in introduction met energy economists using PF approaches, specially CES.
-But, which form to choose and using which parameters? 
-Literature is inconclusive, very little actual empirical testing of such functions. 
-Mostly CES in CGE models used by Wbank and others. 
-CD adviced to be used by CBO. 
-How do we select a functional form and what are the parameters to be used? On what basis do we select?
-
-We aim. to search for empirically robust solution, one that stands up to statistical testing.
-
-What we find is counterintuitive for many cases: dropping energy from the PF has little impact, 
-but some notable exceptions. 
-On other hand, only including energy in a PF of LINEX form also yields good results and stats tests. 
-Is not a simple case for dropping energy, but acknowledging its key role. 
-Do we support the call for better bottom-up understanding? 
-What do we say on the limitations of macroeconomic modelling approaches altogether? 
-(Note such limitations are well known in ME literature, for example capital controversy Robinson).
-We speculate on implications for choosing PF in energy economic models that inform growth policy.
-
-Points on paper so far
-1. Does the relative small differences in fit between different production functions warrant 
-such a large debate on validity of one vs other? Clearly not. 
-CD been used by economists for ease of use and extreme flexibility (Miller).  
-PF generally used on instrumentalist grounds if give reasonable good description of data. 
-NK econ theory provide poor causal explanation of observed data, 
-but yet CD shows very good fit (miller, p17). 
-CES is  more general, but is a liability in forecasting because difficult 
-to get estimate of EoS that is consistent across studies (Miller, p26). 
-Aggregation is problem of both CD and CES functional forms, 
-so being careful when making strong inferences that cannot be justified.
-
-2. We think we can contribute by emphasising the need 
-for proper stats testing or inconsistent reporting on use of preferred functions. 
-Problems with empirical testing presented by Shen, Serrenho.
-What are our issues with multivariate OLS (Serrenho)?
-
-3. Are we joining the forced choice between production functions or 
-acknowledge the similar problems with aggregate prod functions in general? 
-Do we see this as sufficient evidence to doubt the top-down approach to econ growth altogether?
-
-4. R2 is a very crude measure and only very minor improvements 
-are achieved when others factors such as energy is added in a CD. 
-We concur. Puzzling is conclusion that such minor improvements 
-does prove the need to include energy in PF (Serrenho).
-
-5. We do think it is a choice between CD and CES (Miller) as 
-both have serious deficiencies after stats tests.
-
-6. One central issue within PF is elasticity of subs (EoS). 
-That is the \%ch in factor proportions ( k,l, etc) 
-because of one unit ch in MRTS. 
-MRTS is rate at which one factor can be substituted for another holding output constant. 
-EoS is low in Leontief cases, L shaped isoquants.
-
-7. Miller makes the point that even if parameters in model are stats artifacts, 
-they are still useful for forecasting. Do we agree?
-
-8. Is Ockham's razor relevant to what we are doing?
-
-9. Assumptions of CD are strongly rejected by empirical work, Miller still makes case for using CD.
-
-11. What about energy augmented
-
-10. TZ case
-CDno e: almost 80\% l
-CD with e: 25\% energy, rest c,importance of l drops to 0
-CES no e: 20\% c ($\sigma$), 80\% l, but large range
-CES with e: fig 35 e may be NB
-LINEX: one of lowest ct parameters (low relative importance of labour eff compared to cap eff)
-Does this mean that relative small increases in cap eff can really lift the economy?
-
-11. ZA case
-CD no e: roughly half c, l
-CD with e: roughly half, c, e, importance of l drops to 0
-CES no e: 10\% c, 25\% l ??
-CES with e: fig 35 e may be NB
-LINEX: one of highest ct parameters (high relative importance of labour eff compared to cap eff)
-Does this mean that relative small increases in labour eff can really lift the economy?
-
-12. Capital starved Zambia. Very high importance. Understand CES param better.
-
-Discussion: What is Next?
-
-a. A comparative analysis between diff PF reveal interesting 
-enough information to warrant a more diffused approach to countries. 
-Thus, we have a case for doing this for  all countries in the world 
-(or at least those representative of countries in different groups 80/20)
-
-b. If c is relatively more important than labour or energy 
-for growth and if capital stock is low, a situation one would expect in LDCs, 
-a relative small addition of capital stock can give relatively large returns in terms of growth.
-
-c. Now it becomes interesting, in a 'stages of growth' approach, 
-using LT econ data it may be the case that the importance 
-of factors are different across growth stages. 
-It would need a composite type of analysis - both stock and importance.
-
-d. Is it possible to have evidence of diff stocks and diff importances across phases of growth? 
-Maybe test this for a data rich nation that has worked through these stages, 
-we try to identify them and do partial analysis on time periods coinciding with these stages.
-
-Should we eliminate $u$ data? Only 3 countries. Only 20 years. Doesn't add much insight. 
-Too bad, but perhaps necessary to simplify paper.
-
-Discussions:
-
-Counterfactuals: energy, cap, labour what ifs for future.
-
-interpretation of type of economies, what does the data presentation say 
-on relative change in each input and change in GDP?
-
-Forcing const elast of subs in CES thru nested structures violates 
-observation that more than two factor will not be const. elasticities Uzawa 1962.
-
-R programming dealt with nested CES see paper discussion on Kemfert.
-
-Next steps:
-
-Stages of growth crowd implicitly assumes countries at similar stage of growth will
-have similar values for $\alpha$, $\beta$, $\gamma$. However, our results show
-that not to be true. Needs further exploration to cover more (all?) countries.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction} 
-\label{sec:Introduction}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-**** Notes on the introduction from Martin ****
-
-1. Set scene through energy economic modelling papers. 
-Point out that PF approaches are alive and well (Stern, Tol, Gerlagh, World Bank, IMF), 
-short lit review as part of a longer introduction.  
-Mention competing PF approaches and parameter choice. 
-On what basis selection and how estimate parameters?
-
-2. Point out the need for adequate statistical testing and economic interpretation, 
-citing some earlier critical papers on PF limitations. Take issue with
-
-3. Spell out the contribution we will be making in this paper, 
-we are taking the approach that all models are wrong but some are useful. 
-We are after generating insights even after deeper assumptions of econ growth theory are very limiting.
-
-4. Introduce coordinates of analysis.
-
-**** Original introduction that MKH wrote ****
-
-Neoclassical economic growth theory attributes output ($Y$) to factors of production:
-capital stock ($K$) and labor ($L$). The Cobb-Douglas production function 
-is the 
-canonical representation of indexed economic output ($y$) as a function of indexed 
-labor ($l$), indexed capital stock ($k$), and an additional exogenous, time-dependent 
-term.%
-\footnote{The time-dependent term in production functions is often linked
-to ``technological progress,'' but that is a very narrow reading of Solow's original intent:
-\begin{quote}
-  It will be seen that I am using the phrase ``technical change''
-  as a short-hand expression for any kind of shift 
-  in the production function. 
-  Thus slowdowns, speed-ups, improvements in the education of the labor force, 
-  and all sorts of things will appear as ``technical change.''~\citep{solow1957technical}
-\end{quote}
-}
-This production function can be expressed as
-%
-\begin{equation} \label{eq:CD}
-  y = \theta \mathrm{e}^{\lambda(t-t_0)} k^\alpha l^\beta \;,
-\end{equation}
-%
-\noindent where 
-$y \equiv Y/Y_{0}$,
-$\theta$ is a scale parameter,
-e is the base of the natural logarithm, 
-$\lambda$ is represents the pace of technological progress,
-$t$ (time) is measured in years,
-$k \equiv K/K_{0}$, 
-$l \equiv L/L_{0}$, 
-$Y$ is represented by GDP, 
-$K$ is expressed in currency units, 
-$L$ is expressed in workers or work-hours/year, and
-0 subscripts indicate values at an initial year.%
-\footnote{Dimensionless, indexed quantities are represented by 
-lower-case symbols 
-($y$, $k$, $l$, $e$, $q$, $x$, and $u$), and dimensional 
-quantities are represented by upper-case symbols 
-($Y$, $K$, $L$, $E$, $Q$, $X$, and $U$). 
-Model parameters are represented by Greek letters
-($\alpha$, $\beta$, $\lambda$, $\theta$).}
-
-%Mathematically, $A$ is nothing more than a fitting parameter 
-%that aligns the predictions of Equation~\ref{eq:CD} 
-%with historical data. 
-%Thus, we refer to $A$ as the ``residual'' in this paper.} 
-%term ($A$):
-
-% $A$ is the residual term, 
-% with $\lambda$ 
-% indicating the change of the residual over time (in units of 
-% year$^{-1}$).
-Neoclassical economic growth theory as expressed in the Cobb-Douglas production 
-function makes no attempt to describe the mechanisms that affect
-economic growth, nor does it attempt to describe how such things as
-slowdowns, speedups, and improvements of the education of the labor force
-($\lambda$) might vary from one economy to the next. 
-The parameters $\alpha$ and $\beta$ indicate the relative roles 
-of capital and labor in the economy.
-Typically, the constraint $\alpha + \beta = 1$ is assumed, 
-indicating constant returns to scale.
-
-As shown in Equation~\ref{eq:CD} above, neoclassical economic theory does not 
-include an explicit term for the role of energy in economic growth. However, 
-\citet{Bashmakov:2007ek}, \citet{Hamilton:2009ui}, \citet{Murphy:2011jh}, 
-\citet{Benes:2012tm}, \citet{Kumhof:2012ua}, and others indicate that the 
-importance of energy for economic growth may far outweigh its cost share in the 
-economy. That neoclassical economic growth theory ignores energy is, therefore, 
-cause for concern, and inquiry into the proper approach for including energy 
-as a factor of production in economic growth modeling is both relevant and important.
-
-Some energy economists augment economic growth models by including energy as an 
-additional (or the only) factor of production. However, there is little agreement 
-on how this should be done. Neither the mathematical form of the energy-augmented 
-production function nor the quantification of energy are consistent in the 
-literature. There has been little empirical work assessing the predictive ability 
-of various energy-augmented production functions for different types of economies. 
-And, very few studies of the importance of energy in economic growth include 
-rigorous statistical assessments of energy-related fitting parameters. This paper 
-contributes to the literature by applying statistically rigorous 
-methods along two coordinates of analysis: form of the energy augmented 
-production function and type of economy.
-
-The remainder of this paper is organized as follows. Section~\ref{sec:Coordinates} 
-discusses the coordinates of analysis described above. 
-Section~\ref{sec:Sources_of_Data} details sources of data and calculations to 
-generate time series for economic output and factors of production. 
-The procedures for and results from parameter estimation for the various production functions 
-are discussed in Section~\ref{sec:Parameter_Estimation}. 
-Section~\ref{sec:Discussion_of_Results} discusses implications of the parameter estimation 
-results, and Section~\ref{sec:Conclusion} concludes. 
-An appendix provides details of all statistical results.
+% Approach
+% 
+% Build on articles using R to test econ growth PF, 
+% question what is reported when doing these tests (shen/whalley and others who have used micEconCES). 
+% 
+% 
+% Discussion and Insights
+% 
+% Does analysis differ from others in the conversation?
+% Yes, differs as follows:
+% \begin{itemize}
+% \item{if one do these test, report on all $\delta$, $\sigma$, $\gamma$, and $\lambda$ 
+% values as well as sse. 
+% Good fits not evidence of best values, must report uncertainties as well.}
+% \item{What motivates nesting of CES? Not well behaved $\rho$ results, driving $\sigma$s.
+% Different type of CES with parsimonious factors, sigmas can be generated but not that easy (idea Randy).
+% If you run all 3 nesting options, you can identify elasticities of all three factors in relation to each 
+% other. Furthermore, you can determine which two factors are driving overall behavior in the aggregate function.}
+% \item{necessary of different factors in PF to explain growth for countries in diff. development status}
+% \end{itemize}
+% 
+% What do we add to the conversation?
+% 
+% \begin{itemize}
+% 
+% \item{We are able to gain rich insights 
+% on what really drives growth from detailed analysis (including uncertainties) 
+% by testing all functional forms across many different 
+% economy types.}
+% 
+% \item{We were unable to gain new insights from the various energy quantifications that we tried.}
+% 
+% \item{We find, surprisingly, that energy is not necessary 
+% to be included alongside $k$ and $l$ in all PF. Models with energy and models without energy
+% all perform well on an R$^2$ basis.}
+% 
+% \item{We also find that 
+% 
+% (1) covariance of energy($e$) with both $k$ and $l$ is very high, with few exceptions (UK?).
+% 
+% (2) with few exceptions, $\sigma_{(kl)e}$, $\sigma_{ke}$, and $\sigma_{le}$ 
+% are all very low (indicating complementarity) (verify!!!!), and 
+% 
+% (3) energy-only models (SF$e$ and LINEX) achieve very good fits, just like CD$e$ and CES$e$.
+% (should we make this point or not?)}
+% 
+% \item{What does that mean? 
+% It is a fallacy to think that saying energy is unnecessary 
+% to include in an equation means energy is unimportant for economic growth. How to support this argument?
+% 
+% If you find that energy is unnecessary to include alongside capital and labor 
+% to explain growth in one economy at the macro, aggregated level, 
+% you should not assume that energy is unimportant as a driver for economic growth for all economies.
+% For developed economies, energy is captial intensive: you need to have large capital to make use 
+% of energy. In developing economies, you don't need capital to make use of energy. 
+% Rather, you need labor.
+% 
+% We need to verify the above by comparison with our results.}
+% 
+% \item{Also signals that different types of countries likely 
+% to react differently to energy constraints. 
+% Interpret $\sigma$ here, substitution possibilities.}
+% 
+% \end{itemize}
+% 
+% More work?
+% 
+% 
+% 
+% 
+% Big picture
+% [insert test test]
+% 
+% Why do we do this? Want to link energy and economics on national level 
+% and in a modeled approach,informing energy policy during energy transitions.
+% Usually macro energy economic models rely on PF with energy included. 
+% Key papers using CES in energy economics incl high impact such as 
+% Stern, Gerlagh, Tol etc. 
+% Cite in introduction met energy economists using PF approaches, specially CES.
+% But, which form to choose and using which parameters? 
+% Literature is inconclusive, very little actual empirical testing of such functions. 
+% Mostly CES in CGE models used by Wbank and others. 
+% CD adviced to be used by CBO. 
+% How do we select a functional form and what are the parameters to be used? On what basis do we select?
+% 
+% We aim. to search for empirically robust solution, one that stands up to statistical testing.
+% 
+% What we find is counterintuitive for many cases: dropping energy from the PF has little impact, 
+% but some notable exceptions. 
+% On other hand, only including energy in a PF of LINEX form also yields good results and stats tests. 
+% Is not a simple case for dropping energy, but acknowledging its key role. 
+% Do we support the call for better bottom-up understanding? 
+% What do we say on the limitations of macroeconomic modelling approaches altogether? 
+% (Note such limitations are well known in ME literature, for example capital controversy Robinson).
+% We speculate on implications for choosing PF in energy economic models that inform growth policy.
+% 
+% Points on paper so far
+% 1. Does the relative small differences in fit between different production functions warrant 
+% such a large debate on validity of one vs other? Clearly not. 
+% CD been used by economists for ease of use and extreme flexibility (Miller).  
+% PF generally used on instrumentalist grounds if give reasonable good description of data. 
+% NK econ theory provide poor causal explanation of observed data, 
+% but yet CD shows very good fit (miller, p17). 
+% CES is  more general, but is a liability in forecasting because difficult 
+% to get estimate of EoS that is consistent across studies (Miller, p26). 
+% Aggregation is problem of both CD and CES functional forms, 
+% so being careful when making strong inferences that cannot be justified.
+% 
+% 2. We think we can contribute by emphasising the need 
+% for proper stats testing or inconsistent reporting on use of preferred functions. 
+% Problems with empirical testing presented by Shen, Serrenho.
+% What are our issues with multivariate OLS (Serrenho)?
+% 
+% 3. Are we joining the forced choice between production functions or 
+% acknowledge the similar problems with aggregate prod functions in general? 
+% Do we see this as sufficient evidence to doubt the top-down approach to econ growth altogether?
+% 
+% 4. R2 is a very crude measure and only very minor improvements 
+% are achieved when others factors such as energy is added in a CD. 
+% We concur. Puzzling is conclusion that such minor improvements 
+% does prove the need to include energy in PF (Serrenho).
+% 
+% 5. We do think it is a choice between CD and CES (Miller) as 
+% both have serious deficiencies after stats tests.
+% 
+% 6. One central issue within PF is elasticity of subs (EoS). 
+% That is the \%ch in factor proportions ( k,l, etc) 
+% because of one unit ch in MRTS. 
+% MRTS is rate at which one factor can be substituted for another holding output constant. 
+% EoS is low in Leontief cases, L shaped isoquants.
+% 
+% 7. Miller makes the point that even if parameters in model are stats artifacts, 
+% they are still useful for forecasting. Do we agree?
+% 
+% 8. Is Ockham's razor relevant to what we are doing?
+% 
+% 9. Assumptions of CD are strongly rejected by empirical work, Miller still makes case for using CD.
+% 
+% 11. What about energy augmented 
+% 
+% 10. TZ case
+% CDno e: almost 80\% l
+% CD with e: 25\% energy, rest c,importance of l drops to 0
+% CES no e: 20\% c ($\sigma$), 80\% l, but large range
+% CES with e: fig 35 e may be NB
+% LINEX: one of lowest ct parameters (low relative importance of labour eff compared to cap eff)
+% Does this mean that relative small increases in cap eff can really lift the economy?
+% 
+% 11. ZA case
+% CD no e: roughly half c, l
+% CD with e: roughly half, c, e, importance of l drops to 0
+% CES no e: 10\% c, 25\% l ??
+% CES with e: fig 35 e may be NB
+% LINEX: one of highest ct parameters (high relative importance of labour eff compared to cap eff)
+% Does this mean that relative small increases in labour eff can really lift the economy?
+% 
+% 12. Capital starved Zambia. Very high importance. Understand CES param better.
+% 
+% Discussion: What is Next?
+% 
+% a. A comparative analysis between diff PF reveal interesting 
+% enough information to warrant a more diffused approach to countries. 
+% Thus, we have a case for doing this for  all countries in the world 
+% (or at least those representative of countries in different groups 80/20)
+% 
+% b. If c is relatively more important than labour or energy 
+% for growth and if capital stock is low, a situation one would expect in LDCs, 
+% a relative small addition of capital stock can give relatively large returns in terms of growth.
+% 
+% c. Now it becomes interesting, in a 'stages of growth' approach, 
+% using LT econ data it may be the case that the importance 
+% of factors are different across growth stages. 
+% It would need a composite type of analysis - both stock and importance.
+% 
+% d. Is it possible to have evidence of diff stocks and diff importances across phases of growth? 
+% Maybe test this for a data rich nation that has worked through these stages, 
+% we try to identify them and do partial analysis on time periods coinciding with these stages.
+% 
+% Should we eliminate $u$ data? Only 3 countries. Only 20 years. Doesn't add much insight. 
+% Too bad, but perhaps necessary to simplify paper.
+% 
+% Discussions:
+% 
+% Counterfactuals: energy, cap, labour what ifs for future.
+% 
+% interpretation of type of economies, what does the data presentation say 
+% on relative change in each input and change in GDP?
+% 
+% Forcing const elast of subs in CES thru nested structures violates 
+% observation that more than two factor will not be const. elasticities Uzawa 1962.
+% 
+% R programming dealt with nested CES see paper discussion on Kemfert.
+% 
+% Next steps:
+% 
+% Stages of growth crowd implicitly assumes countries at similar stage of growth will
+% have similar values for $\alpha$, $\beta$, $\gamma$. However, our results show
+% that not to be true. Needs further exploration to cover more (all?) countries.
+% 
+% 
+% 
+% 
+% **** Notes on the introduction from Martin ****
+% 
+% 1. Set scene through energy economic modelling papers. 
+% Point out that PF approaches are alive and well (Stern, Tol, Gerlagh, World Bank, IMF), 
+% short lit review as part of a longer introduction.  
+% Mention competing PF approaches and parameter choice. 
+% On what basis selection and how estimate parameters? 
+% 
+% 2. Point out the need for adequate statistical testing and economic interpretation, 
+% citing some earlier critical papers on PF limitations. Take issue with 
+% 
+% 3. Spell out the contribution we will be making in this paper, 
+% we are taking the approach that all models are wrong but some are useful. 
+% We are after generating insights even after deeper assumptions of econ growth theory are very limiting.
+% 
+% 4. Introduce coordinates of analysis.
+% 
+% 
+% 
+% 
+% 
+% **** Original introduction that MKH wrote ****
 
@@
 the possibility of discovering any role that energy plays 
-in the economic development process. In this paper we analyze at least 
-two economies in each of the following four categories: 
-Developed, 
-NICs,\footnote{Newly Industrialized Countries}
-OPEC, and 
-LDCs.\footnote{Lesser Developed Countries} 
-(See Table~\ref{tab:Economy_Examples}.)
+in the economic development process. 
+To gain insights from different countries 
+across different stages of development, 
+we present a comparative analysis among representatives of
+the World Bank’s main categories of countries, 
+namely Developed Countries (DCs), 
+Newly Industrialized Countries (NICs), 
+OPEC countries, and 
+Least Developed Countries (LDCs).
 

### 2014-08-08 Articles/Article_EnerEcon_2014/EconGrowth3.Rnw
Added an Ayres reference.

@@
 
-The availability of adequate energy at affordable costs 
+The availability of adequate energy at affordable prices 
 has become an important strategic issue in recent years.
@@
 economic growth and energy consumption are closely correlated 
-and for a diverse set of countries such as 
+for a diverse set of countries such as 
 the United States \citep{Stern:2000wq, Cleveland:1984p5055}, 
@@
 China \citep{Wang:2011fe}, 
-South Africa \citep{Menyah:2010hl, Odhiambo:2009hj} and 
+South Africa \citep{Menyah:2010hl, Odhiambo:2009hj}, and 
 sixteen Asian countries \citep{Lee:2008dm}
@@
 although the causal relationship from energy consumption 
-to economic growth remains controversial \citep{Chen:2012fs, Ozturk:2010kb}. 
+to economic growth remains controversial \citep{Chen:2012fs, Ozturk:2010kb, Stern:2013aa}. 
 \citet[p. 347]{Ozturk:2010kb} in a survey of the literature on the topic, 
@@
 in the most of these studies [surveyed].''
-
-Those that have accepted that energy use is closely correlated with
-economic performance in one form or another
-have expressed further concerns on the negative effects of 
+\citet{Stern:2013aa} found similar results,
+noting that the direction of causality may change over time.
+
+Many who accept that energy use is closely correlated with
+economic performance, regardless of the direction of causality,
+express concern regarding the negative effects of 
 rising energy prices and fossil fuel depletion 
@@
 the possible dire impacts on the world economy 
-as argued by above-mentioned scholars 
-have further raised the question of
+as argued by the above-mentioned scholars 
+raise the question of
 whether and how to include appropriate energy indicators 
 in economic growth modeling.  
-Neoclassical economic growth theory attributes output ($Y$) to factors of production:
-capital stock ($K$) and labor ($L$). 
+Neoclassical economic growth theory attributes output~($Y$) to factors of production:
+capital stock~($K$) and labor~($L$). 
 The Cobb-Douglas production function 
 is the canonical representation of indexed economic output ($y$) as a function of indexed 
-labor ($l$), indexed capital stock ($k$), and an additional exogenous, time-dependent 
+labor~($l$), indexed capital stock~($k$), and an additional exogenous, time-dependent 
 term.%
@@
 Neoclassical economic growth theory as expressed in the Cobb-Douglas production 
-function makes no attempt to describe the mechanisms that affect
-economic growth, nor does it attempt to describe how such things as
+function makes no attempt, beyond growth in capital~($k$) and labor~($l$), 
+to describe the mechanisms that affect economic growth, 
+nor does it attempt, beyond different fitting parameters,
+to describe how such phenomena as
 slowdowns, speedups, and improvements of the education of the labor force
-($\lambda$) might vary from one economy to the next. 
+might vary from one economy to the next. 
 The parameters $\alpha$ and $\beta$ indicate the relative roles 
@@
 However, \citet{Bashmakov:2007ek}, \citet{Hamilton:2009ui}, \citet{Murphy:2011jh}, 
-\citet{Benes:2012tm}, \citet{Kumhof:2012ua}, and others indicate that the 
+\citet{Benes:2012tm}, \citet{Kumhof:2012ua}, \citet{Ayres:2013aa} and others indicate that the 
 importance of energy for economic growth may far outweigh its cost share in the 
@@
 Neither the mathematical form of the energy-augmented 
-production function nor the quantification of energy is consistent in the 
+production function nor the quantification%
+  \footnote{
+  Various energy quantifications have been used in economic growth modeling: 
+  thermal energy (primary and final), 
+  exergy (primary and final), and useful work.
+  }
+of energy is consistent in the 
 literature. 
@@
 rigorous statistical assessments of energy-related fitting parameters. 
-This paper contributes to the literature by applying statistically rigorous 
-methods along two coordinates of analysis: form of the energy augmented 
-production function and type of economy.
+This paper contributes to the literature on the role of energy in economic growth
+by applying statistically rigorous 
+methods along two coordinates of analysis: 
+form of the energy augmented production function 
+and type of economy.
 
@@
 
-\citet[p. 26]{Stern:2011bq} provides an overview of approaches to including energy 
+\citet[p.~26]{Stern:2011bq} provides an overview of approaches to including energy 
 in ecological economic and resource economic models of growth.  
@@
 energy is seen as the \emph{central driver of growth} 
-in ecological economic (including biophysical economic) models, 
+in ecological economic (including biophysical economic) models
 and that energy \emph{is included} in resource economic models, 
-but \emph{remains isolated} within this sub-discipline.  
+but \emph{remains isolated} within the sub-discipline.  
 To break through this theoretical impasse, 
@@
 and classified by \citet{Stern:2011bq} as an ecological economic model of growth, 
-is the LINEX production function, 
-combining capital (non-ICT and ICT), 
-labour, and useful work. In the LINEX model, 
-technological change affects only 
-the amount of useful work done per joule of exergy \citep{Ayres:2005kn}.
+is the LINEX model, 
+wherein energy is the only factor of production,
+and capital~($k$), labor~($l$), and energy~($e$)
+combine to provide efficiencies that augment energy.
+Technological change is manifest in these efficiencies,
+as more useful work is done per joule of exergy \citep{Ayres:2005kn}.
 
@@
 about the reliability of the results from economic growth models \citep{Lecca:2011kr}. 
-\citet{Lecca:2011kr} and **** and what? **** would like to add
-**** ``would like to add'' or ``add''?**** that the inclusion of energy 
-would only further complicate issues.  **** Prev. sentence is unclear. ****
-We do except **** do you mean ``accept'' or ``expect'' here? ****, however, 
+We understand, however, 
 that macroeconomic policymaking is needed 
@@
 \citep{Froling:2009vo, Jones:2001wn, Galor:2000up}.
-**** Should we discuss the longwave literature above? ****
 
@@
 
-This section describes the two coordinates of analysis and briefly reviews 
-literature related to each.
+This section describes our two coordinates of analysis.
 
@@
 
-\citet{Ayres:2008cl} uses Equation~\ref{eq:CDe} with exergy ($x$) and 
-useful work ($u$) quantifications for $e$ to describe historic Japanese 
-and American economies from 1900-2000. \citet{Froling:2009vo} uses an 
-energy-augmented Cobb-Douglas production function with thermal energy 
-quantification ($q$) to describe output for the global economy from 1800--1970. 
-Fr\"{o}ling's model endogenizes labor with respect to fertility 
-and mortality rates and separates thermal energy into two types: biomass 
-energy and coal energy. 
-\citet{Serrenho:2010vq} use the log transform of 
-the energy-augmented Cobb-Douglas function with thermal energy 
-quantification ($q$) to describe output for the EU-15 countries. 
-Serrenho divides thermal energy into renewables, non-renewables, 
-wastes, and imports. 
-The main argument of these papers is that 
-energy is an important driver of growth and needs to be included
-as an essential factor of production.
-
-**** Martin: add more here about the conclusions of each paper regarding 
-the role of energy in economic growth? Add additional literature? 
-Or, adjust as you see fit. Especially, are there any confidence intervals 
-or statistical evaluation in each of these studies? ****
+% \citet{Ayres:2008cl} uses Equation~\ref{eq:CDe} with exergy ($x$) and 
+% useful work ($u$) quantifications for $e$ to describe historic Japanese 
+% and American economies from 1900-2000. \citet{Froling:2009vo} uses an 
+% energy-augmented Cobb-Douglas production function with thermal energy 
+% quantification ($q$) to describe output for the global economy from 1800--1970. 
+% Fr\"{o}ling's model endogenizes labor with respect to fertility 
+% and mortality rates and separates thermal energy into two types: biomass 
+% energy and coal energy. 
+% \citet{Serrenho:2010vq} use the log transform of 
+% the energy-augmented Cobb-Douglas function with thermal energy 
+% quantification ($q$) to describe output for the EU-15 countries. 
+% Serrenho divides thermal energy into renewables, non-renewables, 
+% wastes, and imports. 
+% The main argument of these papers is that 
+% energy is an important driver of growth and needs to be included
+% as an essential factor of production.
+% 
+% **** Martin: add more here about the conclusions of each paper regarding 
+% the role of energy in economic growth? Add additional literature? 
+% Or, adjust as you see fit. Especially, are there any confidence intervals 
+% or statistical evaluation in each of these studies? ****
 
@@
 Equation~\ref{eq:CESkle} augments Equation~\ref{eq:CES} with energy 
-using a ($kl$)($e$) nesting structure, as is typical in the literature. 
+using a ($kl$) + ($e$) nesting structure, as is typical in the literature. 
 Equation~\ref{eq:CES} is a degenerate form of Equation~\ref{eq:CESkle} 
@@
 
-$\gamma$ is a fitting parameter that represents productivity. 
+$\gamma$ is a scale factor.
 The fitting parameters $\rho_1$ and $\rho$ indicate elasticities 
@@
 meanings that depend upon the nesting of the factors of production.
-% **** Do we want to define different variables that indicate meaning, 
-% such as $\sigma_{kl}, \sigma_{(kl)e}, \delta_{(ek)l}$, and the like? If so, we'll 
-% need to translate from $\rho$ and $\sigma$ in \texttt{cesEst} to the correct
-% variable names in the paper. ****
-
-**** Describe here how 
-we implemented the constraints. ****
-
-\citet{VanderWerf:2008tc} evalutes various nested CES production 
-functions for 12 OECD countries with respect to climate change policy. 
-\citeauthor{VanderWerf:2008tc} concludes that ($kl$)($e$) nesting structure 
-best fits historical data. \citet{Lecca:2011kr} also evaluate a variety of 
-CES production functions using a KLEM structure to determine how the various 
-options for nesting the energy factor of production affect predictive ability. 
-\citet{Stern:2012ey} also use a CES production function of the form ($kl$)($e$). 
-\citeauthor{Stern:2012ey} apply their CES function to the Swedish economy 
-from 1800-2000 and demonstrate the importance of the transition from wood to 
-fossil fuels for economic growth. \citet{Shen:2013vp} included energy 
-in nested aggregated CES production functions 
-for China and found that the best nesting structure is ($le$)($k$).
-
-**** Martin: add more here about the conclusions of each paper regarding 
-the role of energy in economic growth? Add additional literature? 
-Or, adjust as you see fit. Especially, are there any confidence 
-intervals or statistical evaluation in each of these studies? ****
+
+% \citet{VanderWerf:2008tc} evalutes various nested CES production 
+% functions for 12 OECD countries with respect to climate change policy. 
+% \citeauthor{VanderWerf:2008tc} concludes that ($kl$)($e$) nesting structure 
+% best fits historical data. \citet{Lecca:2011kr} also evaluate a variety of 
+% CES production functions using a KLEM structure to determine how the various 
+% options for nesting the energy factor of production affect predictive ability. 
+% \citet{Stern:2012ey} also use a CES production function of the form ($kl$)($e$). 
+% \citeauthor{Stern:2012ey} apply their CES function to the Swedish economy 
+% from 1800-2000 and demonstrate the importance of the transition from wood to 
+% fossil fuels for economic growth. \citet{Shen:2013vp} included energy 
+% in nested aggregated CES production functions 
+% for China and found that the best nesting structure is ($le$)($k$).
+% 
+% 
+% **** Martin: add more here about the conclusions of each paper regarding 
+% the role of energy in economic growth? Add additional literature? 
+% Or, adjust as you see fit. Especially, are there any confidence 
+% intervals or statistical evaluation in each of these studies? ****
 
@@
 of its increase of energy consumption ($e$), because
-\(
+%
+\begin{equation*}
   \mathrm{e}^{a_0\left[2 \left(1 - \frac{1}{\rho_k} \right) 
@@
   	> 1.
-\) 
+\end{equation*}
+%
 Similarly, an economy benefits by increasing labor ($l$) 
@@
 
-\citet{Kummel:2002tx} use the 
-LINEX production function to describe economic output 
-for the economies of the U.S., Japan, and Germany. 
-\citet{Warr:2010ga} compare the LINEX production function with 
-the Cobb-Douglas production function to assess economic growth 
-for Austria, the United Kingdom, the United States, and Japan. 
-\citet{Ayres:2005kn} argued that introducing energy inputs 
-in traditional production functions does not improve its explanatory power, 
-but including useful work in a LINEX function does.
-
-\authNote{Martin: add more here about the conclusions of each paper 
-regarding the role of energy in economic growth? Add additional literature? 
-Or, adjust as you see fit. Especially, are there any confidence intervals 
-or statistical evaluation in each of these studies?}
-
-\authNote{If we want to keep this quote, it should be clearer what point we are trying to
-make with it. ---rjp}
-\citet{Abramovitz:1956aa} wrote:
-
-\begin{quote}
-  This result [that ``technological progress'' explained
-  175\% of the growth of the US economy since 1870] is surprising in the lopsided
-  importance which it appears to give to productivity increase,
-  and it should be, in a sense, sobering, if not discouraging,
-  to students of economic growth.
-  Since we know little about the causes of productivity increase,
-  the indicated importance of this element may be taken to be some sort of measure
-  of our ignorance about the causes of economic growth in the United States
-  and some sort of indication of where
-  we need to concentrate our attention.
-\end{quote}
+% \citet{Kummel:2002tx} use the 
+% LINEX production function to describe economic output 
+% for the economies of the U.S., Japan, and Germany. 
+% \citet{Warr:2010ga} compare the LINEX production function with 
+% the Cobb-Douglas production function to assess economic growth 
+% for Austria, the United Kingdom, the United States, and Japan. 
+% \citet{Ayres:2005kn} argued that introducing energy inputs 
+% in traditional production functions does not improve its explanatory power, 
+% but including useful work in a LINEX function does. 
+% 
+% \authNote{Martin: add more here about the conclusions of each paper 
+% regarding the role of energy in economic growth? Add additional literature? 
+% Or, adjust as you see fit. Especially, are there any confidence intervals 
+% or statistical evaluation in each of these studies?}
+% 
+% \authNote{If we want to keep this quote, it should be clearer what point we are trying to
+% make with it. ---rjp}
+% \citet{Abramovitz:1956aa} wrote:
+% 
+% \begin{quote}
+%   This result [that ``technological progress'' explained
+%   175\% of the growth of the US economy since 1870] is surprising in the lopsided
+%   importance which it appears to give to productivity increase,
+%   and it should be, in a sense, sobering, if not discouraging,
+%   to students of economic growth.
+%   Since we know little about the causes of productivity increase,
+%   the indicated importance of this element may be taken to be some sort of measure
+%   of our ignorance about the causes of economic growth in the United States
+%   and some sort of indication of where
+%   we need to concentrate our attention.
+% \end{quote}
 
@@
 almost exclusively on developed economies from North America 
-or Europe. Examples include \citet{Kummel:1980wx} applying 
-LINEX to describe the West German economy, \citet{Serrenho:2010vq} 
-applying Cobb-Douglas variants to EU-15 countries, 
+and Europe. 
+Examples include \citet{Kummel:1980wx} applying 
+LINEX to describe the West German economy, 
+\citet{Serrenho:2010vq} applying Cobb-Douglas variants to EU-15 countries, 
 \citet{VanderWerf:2008tc} applying CES nesting variants 
-to the 12 OECD countries, \citet{Lecca:2011kr} applying 
-CES nesting variants to the Scottish economy, \citet{Stern:2012ey} 
-applying CES to describe the Swedish economy, and \citet{Warr:2012cg} 
-using LINEX and Cobb-Douglas to describe the Austrian, 
+to the 12 OECD countries, 
+\citet{Lecca:2011kr} applying CES nesting variants to the Scottish economy, 
+\citet{Stern:2012ey} applying CES to describe the Swedish economy, 
+and \citet{Warr:2012cg} using LINEX and Cobb-Douglas to describe the Austrian, 
 American, British, and Japanese economies.
@@
 Least Developed Countries (LDCs). 
+Table~\ref{tab:Economy_Examples} shows our example countries.
 
@@
 coordinates of analysis outlined in Section~\ref{sec:Coordinates}, 
-historical data for economic output ($Y$), capital stock ($K$), 
-labor ($L$), and thermal energy ($Q$)   %, exergy ($X$), and useful work ($U$) 
-are required. Subsections below describe sources for and calculations 
-to obtain historical data. A final subsection presents the historical 
-data in graphical form.
+historical data for 
+economic output~($Y$), 
+capital stock~($K$), 
+labor~($L$), and 
+thermal energy~($Q$)
+are required. 
+Subsections below describe sources for and calculations to obtain historical data. 
+A final subsection presents the historical data in graphical form.
 
@@
 
-Animal and human muscle work was estimated using an approach 
+Animal muscle work was estimated using an approach 
 similar to \citet{Ayres:2010ug}, using data from Warr's 
 REXS database \citep{Warr:2012a} and results from 
-\citet{Wirsenius:2000vi}. For animal work, our analysis was 
+\citet{Wirsenius:2000vi}. 
+Similar to Warr, we excluded human muscle work from the energy term
+on the grounds that labor terms are
+already present in all production functions.
+For animal work, our analysis was 
 restricted to draught animals (horses and mules). Muscle work 
@@
 
-% Human muscle power was calculated in a similar manner:
-% 
-% \begin{equation} \label{eq:human_muscle}
-%   Q_{workers} = Q_{m,workers} N_{workers}
-% \end{equation}
-% 
-% \noindent where the value of $Q_{m,workers}$ is the ``the amount 
-% of food available for human consumption'' (i.e., at the wholesale level) 
-% taken from the 
-% \citet[``\texttt{Dietary~Energy~Cons.~Countries}'' tab]{FAO:2013b}. 
-% The value for $N_{workers}$ was obtained from the labor time series 
-% for each economy as discussed in Section~\ref{sec:Labor_Data}.
-
 %++++++++++++++++++++++++++++++
@@
 for 1980--2011 (developed economies) and 1991--2011 (other economies). 
-Factors of production track each other closely, 
-and high covariances among these variables can be seen in 
-Tables~\ref{tab:Covariance_US}--\ref{tab:Covariance_ZM}. 
-\authNote{Do we want to discuss the covariances?}
+% Factors of production track each other closely, 
+% and high covariances among these variables can be seen in 
+% Tables~\ref{tab:Covariance_US}--\ref{tab:Covariance_ZM}. 
+% \authNote{Do we want to discuss the covariances?}
 %
@@
 and \texttt{cesEst} \citep{Henningsen:2011td} (for CES models).
-\authNote{Need to check how CES is being fit and adjust this accordingly.}%
 
 Although the details vary from model to model, each of our three models has the general form
-\[
+%
+\begin{equation}
   y = f(t,k,l,e; \theta) + \mathrm{error} \;,
-\]
+\end{equation}
+%
 where $\theta$ is a vector of parameters for the function $f$.
@@
 fitted response by
-\[
+%
+\begin{equation}
   \hat y_i = f(t_i, k_i, l_i, e_i; \hat \theta)
-\]
+\end{equation}
+%
 and the residuals ($r_i$)
@@
 Thus, a resampled response $\tilde Y'$ can be computed as 
-\[
+%
+\begin{equation}
   \tilde Y_i' = \hat y_i \pm r_j
-\]
+\end{equation}
+%
 where 
-\[
+%
+\begin{equation}
   r_i = y_i - \hat y_i
-\]
+\end{equation}
+%
 both the sign ($\pm$) and the index of the residual 
@@
 %
-\noindent ensuring that $\alpha + \beta + \gamma = 1$,
+ensuring that $\alpha + \beta + \gamma = 1$,
 thereby providing constant returns to scale.
@@
       \hline
-      ($kl$)     & \ref{eq:CES}    & $\delta_1$              & $1 - \delta_1$          & 0                       \\
-      ($kl$)$e$  & \ref{eq:CESkle} & $\delta \delta_1$       & $\delta (1 - \delta_1)$ & $1 - \delta$            \\   
-      ($le$)$k$  & \ref{eq:CESlek} & $1 - \delta$            & $\delta \delta_1$       & $\delta (1 - \delta_1)$ \\
-      ($ek$)$l$  & \ref{eq:CESekl} & $\delta (1 - \delta_1)$ & $1 - \delta$            & $\delta \delta_1$       \\
+      ($kl$) + ()     & \ref{eq:CES}    & $\delta_1$              & $1 - \delta_1$          & 0                       \\
+      ($kl$) + ($e$)  & \ref{eq:CESkle} & $\delta \delta_1$       & $\delta (1 - \delta_1)$ & $1 - \delta$            \\   
+      ($le$) + ($k$)  & \ref{eq:CESlek} & $1 - \delta$            & $\delta \delta_1$       & $\delta (1 - \delta_1)$ \\
+      ($ek$) + ($l$)  & \ref{eq:CESekl} & $\delta (1 - \delta_1)$ & $1 - \delta$            & $\delta \delta_1$       \\
     \end{tabular}
@@
 
-Figure~\ref{fig:CES_Spaghetti_Graph_CN} shows details of the resample fits for China with the (kl)e nesting.
-Again, historical data are shown as a black line. 
-The fit to historical data is shown as a white line.
-The gray band encompasses 95\% of the fits to resampled data.
-
-<<CES_Spaghetti_Graph_CN, fig.pos="H", fig.align='center', fig.width=maxWidth, fig.height=maxHeight, fig.cap="CES fitted models for China with the (kl)e nesting.">>=
-spaghettiPlot(data=subset(cesFittedData, Country=="CN" & nestStrParen=="(iK + iL) + (iQp)"), level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1980 = 1 or 1991 = 1")
-@
+% Figure~\ref{fig:CES_Spaghetti_Graph_CN} shows details of the resample fits for China with the (kl)e nesting.
+% Again, historical data are shown as a black line. 
+% The fit to historical data is shown as a white line.
+% The gray band encompasses 95\% of the fits to resampled data.
+% 
+% <<CES_Spaghetti_Graph_CN, fig.pos="H", fig.align='center', fig.width=maxWidth, fig.height=maxHeight, fig.cap="CES fitted models for China with the (kl)e nesting.">>=
+% spaghettiPlot(data=subset(cesFittedData, Country=="CN" & nestStrParen=="(iK + iL) + (iQp)"), level=spaghettiGraphLevel) +
+%     labs(y="Indexed GDP (1980 = 1 or 1991 = 1")
+% @
 
@@
 shows the coefficients estimated from resampled data.
+We fit $a_0$ and $c_t$ unconstrained.
 
@@
 
-The LINEX model coefficients $a_0$ and $c_t$ imply time-dependent
-values of $\alpha$, $\beta$, and $\gamma$ as given by the following equations~\citep{Warr:2012cg}:
-
-\begin{equation} \label{eq:LINEX_alpha}
-  \alpha = \frac{k}{y}\frac{\partial y}{\partial k} = a_0 \left( \frac{l + e}{k} \right) \;,
-\end{equation}
-
-\begin{equation} \label{eq:LINEX_beta}
-  \beta = \frac{l}{y} \frac{\partial y}{\partial l} = a_0 \left[ c_t \left( \frac{l}{e}\right) - \frac{l}{k} \right] \;,
-\end{equation}
-
-\noindent{}and
-
-\begin{equation} \label{eq:LINEX_beta}
-  \gamma = \frac{e}{y} \frac{\partial y}{\partial e} 
-         = 1 - a_0 \left[ \frac{e}{k} + c_t \frac{l}{e} \right] 
-         = 1 - \alpha - \beta \;.
-\end{equation}
-
-\noindent Thus, each fitted model implies a trajectory of $\alpha$, $\beta$, and $\gamma$ values as time proceeds.
-If the trajectory stays within the triangle, 
-the constraints on $\alpha$, $\beta$, and $\gamma$ are respected.
-Conversely, if the trajectory goes outside the triangle, one of the constraints has been violated.
-
-Figures~\ref{fig:LINEX_abg_traj_graph_CN} and~\ref{fig:LINEX_abg_traj_graph_IR} 
-show trajectories for China and Iran, respectively.
-**** Can we make a figure that has all 9 graphs in it? --MKH ****
-
-<<LINEX_abg_traj_graph_CN, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="LINEX trajectory for China.">>=
-dataCN <- fortify(oModels$Calvin$CN$linex$`iK+iL+iQp`)
-triPlot(data=dataCN, grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1990")
-@
-
-<<LINEX_abg_traj_graph_IR, fig.pos="H", fig.align='center', fig.width=3, fig.height=1.5, fig.cap="LINEX trajectory for Iran.">>=
-dataIR <- fortify(oModels$Calvin$IR$linex$`iK+iL+iQp`)
-triPlot(data=dataIR, grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1990")
-@
-
-In our testing, Iran is the only country for which the trajectory stays within 
-the constraint triangle for the entire time period.
-Thus, in our fitted models, the LINEX model is nearly always
-violating constraints on $\alpha$, $\beta$, and $\gamma$.
-If the LINEX model were made to respect the constraints,
+The LINEX model coefficients $a_0$ and $c_t$ imply time-varying
+values of $\alpha$, $\beta$, and $\gamma$ as shown by \citet[Equations~7]{Warr:2012cg}.
+Thus, each fitted model implies a trajectory of $\alpha$, $\beta$, and $\gamma$ values as time proceeds.
+We found unconstrained fitting produced $\alpha$,$\beta$,$\gamma$ trajectories
+that violated parameter constraints ($[0,1]$) for all countries, with the exception of Iran.
+If the LINEX model were forced to respect the constraints,
 it would fit worse than it already does for those countries where
 the constraints are violated (that is, for every country except Iran).
-We did nothing to correct this situation, because it is not clear what should be done.
-\citet{Warr:2012cg} constrained the values of $a_0$ and $c_t$, while still holding them constant
+\citet{Warr:2012cg} selected values of $a_0$ and $c_t$, while still holding them constant
 for the entire time series, such that the constraints on $\alpha$, $\beta$, and $\gamma$
-were respected.
+were respected throughout their time series.
 But, Warr's approach necessarily leads to larger $sse$ values than unconstrained fitting.
-Because unconstrained LINEX models already fit worse than 
+Because in our results unconstrained LINEX models already fit worse than 
 constrained Cobb-Douglas and CES models,
-we chose to report the unconstrained LINEX model fits in this paper.
-% Constraining $\alpha = 0$ in the case of China would imply that either
-% $a_0$ or $c_t$ or both varied with time.
-% At that point, $a_0$ and $c_t$ are no longer fitted parameters of the model, 
-% and we have a different model: it is no longer LINEX.
-
-%++++++++++++++++++++++++++++++
-\subsection{Parameter Estimation Summary}
-\label{sec:Parameter_Estimation_Summary}
-%++++++++++++++++++++++++++++++
-
-**** Include a table here of important values. 
-Martin to suggest the form of this table after working 
-on the interpretation for a while. ****
+we chose to report unconstrained LINEX model fits in this paper.
 
@@
 
-Drive towards new insights from our stats tested comparative approach.
-
-**** Notes for interpretation of results ****
-
-R$^2$ not a good measure. 
-Limited insights are obtained from $t$ and $p$ values, 
-especially on PFs that have parameters with constraints (CD, CES).
-
-We found that we are able to maintain good fits while respecting theoretical foundations
-of the models (i.e., respect parameter constraints). No need to relax parameter constraints
-and, thereby, contradict micro foundations.
-
-CD assumes $\sigma_1 = 1$. CES doesn't assume a value for $\sigma_1$. 
-The $\sigma_1$ vs. $\delta_1$ graphs for CES without energy often have 
-two frequent values for $\sigma_1$.  One of those frequent values is
-nearer to $\sigma_1 = 1$. When CD and CES without energy do not agree on 
-share values (CD: $\alpha$ compared to $\beta$, CES: $\delta_1$) for the 
-base curve fit (red dot), they do agree for the data that clusters near 
-$\sigma_1 = 1$ for the CES fits.
-
-Country interpretation
-
-Comparison Cobb Douglas and CES results.
-
-%++++++++++++++++++++++++++++++
-\subsection{United States} 
-\label{sec:InterpUS}
-%++++++++++++++++++++++++++++++
-
-CD: Energy is unnecessary
-
-CES with $q$:
-
-($kl$): $\delta_1 = 0.3, \sigma_1 = 0.8$. $k$ is less necessary. 
-Complements, but close to substitutes.
-signal of substitutability in the spread.
-
-($kl$)$e$: energy is unnec ($\delta = 1$). 
-$\delta_1 = 0.45$: $k$ and $l$ are about equally necessary.
-$\sigma_1 = 0.8$: $k$ and $l$ are slight complements. 
-Spread on $0.25 < \sigma_1 < \infty$, signalling 
-possibilities of substitution.
-
-($el$)$k$: energy is unnec. ($\delta_1$ is 0);
-
-($le$)$k$ no indication
-Relative consistent signal that energy is unnec.
-
-CES with $u$:
-
-($kl$)$e$: $\delta = 1$, signalling $e$ unnecessary. 
-$\sigma = 0.8$, indicating clost to substitutability,
-but still complementary. 
-$\delta_1 = 0.25$, with large spread. not strong for $k$.
-$\sigma_1 \rightarrow \infty$, but with large spread from 0.2 upward. 
-Signals complementarity between $k$ and $l$.
-
-%++++++++++++++++++++++++++++++
-\subsection{United Kingdom} 
-\label{sec:InterpUK}
-%++++++++++++++++++++++++++++++
-
-CD: Capital is unnec.
-
-CES with $q$:
-
-($kl$): $\delta_1 = 0.7, \sigma_1 = 0.35$. 
-$kl$ complementary, $k$ is more important, because $\delta_1 > 0.5$. 
-Large spread on $\delta_1$. 
-Complementary signal is consistent, however.
-
-($kl$)$e$: energy is unnec ($\delta = 1$). 
-$\delta_1 = 0.25$, $k$ is less necessary. 
-$\sigma_1 \rightarrow \infty$, giving strong $kl$ substitutability signal.
-
-($le$)$k$ capital is unnec. ($\delta = 1$);
-
-($ek$)$l$ ($\delta_1 = 0$) energy is unnec.
-
-Thus, inconsistent results, possibly look at different time series 
-as massive changes in economic policy in Uk economic history
-
-CES with $u$:
-
-($kl$)$e$: $\delta = 1$, $u$ is unnecessary. 
-$\sigma = 0.8$, approache complementarity between $kl$ and $e$.
-$\delta_1 = 0.1$. 
-$\sigma_1 \rightarrow \infty$, indicating substitutability between $k$ and $l$.
-
-%++++++++++++++++++++++++++++++
-\subsection{Japan} 
-\label{sec:InterpJP}
-%++++++++++++++++++++++++++++++
-
-CD: energy is unnec.
-
-CES with $q$:
-
-($kl$): $\delta_1 = 0.7, \sigma_1 = 0.25$. Very little scatter. Both are well-known. 
-$l$ is close to unnecessary. $k$ and $l$ are complements.
-
-($kl$)$e$: no indications, all are important. $\delta = 0.6$, both $kl$ and $e$ are necessary.
-$0.5 < \delta < 1$.
-$\sigma=0.1$ signalling complementarity betwen $kl$ and $e$.
-$\delta_1 = 0.8$ signalling $l$ is almost unnecessary. 
-$\sigma_1 = 0.1$, signalling complementarity 
-between $k$ and $l$.
-
-($le$)$k$: no indications, all are important.
-
-($ek$)$l$: no indications, all are important.
-
-weak signal that labour is less necessary 
-(($kl$)$e$ $delta_1 = 0.86$ and ($ek$)$l$ $\delta = 0.89$)
-
-Thus, inconsistent results.
-
-CES with $u$:
-
-($kl$)$e$: $\delta = 0.6, \sigma = 0.4$. Complementarity between $kl$ and $e$.
-$\delta_1 = 1$, indicating $l$ unnecessary. $\sigma_1 = 0.1$, indicating complementarity
-between $k$ and $l$. Need only one of $k$ or $l$ in your equation, but they are
-complemetary! You need one to have the other.
-
-%++++++++++++++++++++++++++++++
-\subsection{China} 
-\label{sec:InterpCN}
-%++++++++++++++++++++++++++++++
-
-CD: energy not necessary, capital less necessary
-
-CES with $q$:
-
-($kl$): $\delta_1 = 0.3$, so $k$ is getting close to unnecessary. $\sigma_1 = 1.25$.
-$k$ and $l$ are substitutes. Large spread in $\delta_1$ from 0.1 to 1.0. Large spread in
-$\sigma_1$, but most points have $\sigma_1 > 1$.
-
-($kl$)$e$: $\delta = 0.8$. however, strong signal at $0.8 < \delta < 1$, 
-signalling that energy is less necessary. $0.5 < \delta < 1$. $\sigma = 0.5$, 
-signalling complementarity between $kl$ and $e$. 
-$\delta_1 = 1$, signalling that $l$ is unnecessary. $\sigma_1 = 0.1$, signalling
-that $k$ and $l$ are complementary. Both $\delta_1$ and $\sigma_1$ have large spreads, 
-so our confidence in these results is low.
-
-($le$)$k$: labour is unnnec ($\delta_1 = 0$);
-
-($ek$)$l$ energy is unnec. ($\delta_1 \rightarrow 0$)
-
-Strong signal that energy is unnec, but the labour and capital signals are conflicting
-
-%++++++++++++++++++++++++++++++
-\subsection{South Africa} 
-\label{sec:InterpZA}
-%++++++++++++++++++++++++++++++
-
-CD: Labour is unnec.
-
-CES with $q$:
-
-($kl$): $\delta_1 = 0.35, \sigma_1 = 0.8$. $k$ is relatively less necessary. $k$ and $l$ 
-are complements but relatively close to being substitutes. Spread is tight between 
-$0.25 < \delta_1 < 0.5$ and $\sigma_1$ is consistently complementary 
-between $0.1 < \sigma_1 < 0.8$.
-
-($kl$)$e$: labour is unnec. ($\delta_1 = 1$). $\delta = 0.25$, signalling complemtarity 
-between $kl$ and $e$, but large spread from 0 to 1. $\sigma$ and $\sigma_1$ are both 0, 
-indicating perfect complements betwen $kl$ and $e$ and between $k$ and $l$.
-
-($le$)$k$ labour is unnec. ($\delta_1 = 0$);
-
-($ek$)$l$ labour is unnec. ($\delta = 1$)
-
-Consistent signal that labour is unnec.
-
-%++++++++++++++++++++++++++++++
-\subsection{Saudi Arabia} 
-\label{sec:InterpSA}
-%++++++++++++++++++++++++++++++
-
-CD: no indications
-
-CES with $q$:
-
-($kl$): $\delta_1 = 0.85$. $l$ is unnecessary. 
-$\sigma_1 = 0.1$ indicating strong complementarity between 
-$k$ and $l$. Spread of $0.15 < \delta_1 < 1$. 
-$0 < \sigma_1 < 0.8$, signalling complementarity.
-
-($kl$)$e$: $\delta = 0.6$, $e$ is less necessary (weak signal). 
-Big spread on $\delta$ between 0 and 0.8.
-$\sigma = 0.1$ indicating complementarity between $kl$ and $e$. $\delta_1 = 0.8$ 
-(with large spread between 0.3 and 1), labor is less necessary.
-$\sigma_1 = 0.1$: very complementary between $k$ and $l$.
-
-($le$)$k$:
-
-($ek$)$l$: weak signal that labour is unnec ($\delta = 0.93$)
-
-Almost consistent signal that no indocations.
-
-%++++++++++++++++++++++++++++++
-\subsection{Iran} 
-\label{sec:InterpIR}
-%++++++++++++++++++++++++++++++
-
-CD: energy is unnec.
-
-CES with $q$:
-
-($kl$): $\delta_1 = 0.3$. Spread $0 < \delta_1 < 0.7$. $0 < \sigma_1 < 0.8$. $\sigma_1 = 0$. 
-Strong complementarity. $k$ is less necessary compared to $l$.
-
-($kl$)$e$: energy is unnec ($\delta=1$). 
-$\sigma = 0.75$ indicating complementarity between $kl$ and $e$, approaching substitutibility.
-$\delta_1 = 0.3, \sigma_1 = 0$ indicating strong perfect complementarity between $k$ and $l$.
-
-($le$)$k$: energy is unnec. ($\delta_1=1$);
-
-($ek$)$l$: labour is unnec. ($\delta=1$)
-
-%++++++++++++++++++++++++++++++
-\subsection{Tanzania} 
-\label{sec:InterpTZ}
-%++++++++++++++++++++++++++++++
-
-CD: labour in unnec.
-
-CES with $q$:
-
-($kl$): $\delta_1 = 0.8$ $0.3 < \delta_1 < 1$ signalling labor is less necessary.
-$\sigma_1 = 0.1$ $0 < \sigma_1 < 0.8$, signalling complementary $k$ and $l$.
-
-($kl$)$e$: labour is unnec ($\delta_1=0.97$). 
-$\delta = 0.45$, so $kl$ and $e$ both necessary, but 
-$\sigma \rightarrow \infty$, so $kl$ and $e$ has perfect substitutibility.
-$\sigma_1 = 0.1$, so $k$ and $l$ are perfect complements. 
-Spread on $\delta$ is large (0.2 to 1).
-So, we are unsure about the value of $\delta$.
-
-($le$)$k$: weak signal that energy is unnec. ($\delta_1=0.92$); 
-very weal signal capital is unnec ($\delta=0.84$);
-
-($ek$)$l$: labour is unnec. $\delta=0.96$
-
-Consistent signal that labour is unnec, with exception of one nesting.
-
-%++++++++++++++++++++++++++++++
-\subsection{Zambia} 
-\label{sec:InterpZM}
-%++++++++++++++++++++++++++++++
-
-CD: labour is unnec; energy is unnec.
-
-CES with $q$:
-
-($kl$): $\delta_1 = 1$: $l$ is unnecessary. 
-$0.5 < \delta_1 < 1$. $\sigma_1 = 0.8$ without any 
-noticeable spread indicating complemetary.
-
-($kl$)$e$: labour is unnec. ($\delta_1=1$). 
-$\delta = 0.6$, $kl$ and $e$ are both necessary. 
-$\sigma \rightarrow \infty$, signalling substitutability between $kl$ and $e$. 
-$\sigma_1 = 0.8$ with very large spread between 0 and 2. 
-Approaching substitutability between $k$ and $l$ and perfect substitutibility
-between $kl$ and $e$. Very little certainty here.
-
-($le$)$k$: ($\delta_1=0$);
-
-($ek$)$l$: labour is unnec. ($\delta=1$)
-
-Consistent signal that labour is unnec.
-
-Discussion of results:
-
-How to get better consistent signals?
-
-\begin{itemize}
-\item{Use CD as starting points and do CES convergence on that basis.}
-\item{Do scatterplots to get range of uncertainty inputs, then re-interpret. 
-$\delta$ against $\sigma$ plots, as well as $\delta_1$ and $\sigma_1$ plots.}
-\end{itemize}
-
-Thus, to do the fitting well we need to understand:
-\begin{itemize}
-\item{nesting}
-\item{algorithm}
-\item{starting values}
-\end{itemize}
-esp. for CES.
-
-(Maybe illustrate with one case study such as China what implications are).
-
-How do we compare with LINEX results?
-
-CES is a broader specification of CD, LINEX is not. 
-In LINEX neither $\delta$s nor $\sigma$s are generated. 
-Only efficiency terms are generated in LINEX, 
-thus in other words economic growth is only possible by increased efficiency. 
-The efficiency of using energy is driven by capital stock. 
-The objective/growth engine is to increase capital 
-at a rate that is faster then growth in labour and energy.  
-Increasing labour relative to energy gives a muted benefit. 
-LINEX derived for Germany: only really applicable when energy and capital are complements.
-
-Discussion in relation to other papers. 
-Problems with other papers:
-\begin{itemize}
-\item{If not giving you all parameters}
-\item{Not explain nesting approach}
-\item{No CI on data}
-\end{itemize}
-
-Economic interpretation (revisit after scatterplot information)
-Developed economies: Capital and energy is complementary (US: labour and energy substitutable)
-NICs: Capital and energy complementary, but labour and energy more substitutable
-OPEC: Labour and energy complementary (mixed results on capital and energy)
-LDCs: Labour and energy complementary, Capital and energy perfect substitutes.
+Interpretation goes here.
+
+*** One item from previous version of paper led me to a question that could be answered by our approach:
+Is it true that economies at similar stages of development will have similar
+$\alpha$, $\beta$, and $\gamma$ values? ****
+
+**** Another question to address: Would better data reduce the uncertainty in parameter estimates?
+Probably not. The US, presumably the best data in the world, still shows very high uncertainty. ****
 
@@
 
+Conclusion goes here.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+**** Revisit this section when we finish writing the paper. ****
 
@@
 energy quantification.
-Specifically, we with to analyze exergy ($X$) and useful work ($U$)
+Specifically, we want to analyze exergy ($X$) and useful work ($U$)
 energy quantifications within the framework established in this paper.
@@
 %% \label{}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\appendix
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Covariance Tables}
-\label{sec:Covariance_Tables}
-\setcounter{table}{0} % Restarts table number counter at 0 in this section.
-\setcounter{figure}{0} % Restarts figure number counter at 0 in this section.
-\setcounter{equation}{0} % Restarts equation counter to 0 in this section.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Convergence of Resample Models}
-\label{sec:Convergence_Resample_Models}
-\setcounter{table}{0} % Restarts table number counter at 0 in this section.
-\setcounter{figure}{0} % Restarts figure number counter at 0 in this section.
-\setcounter{equation}{0} % Restarts equation counter to 0 in this section.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The following table shows the fraction of resample models 
-that did not achieve convergence when estimating model parameters.
-
-<<Unconverged_Frac_Table, results='asis'>>=
-# printFracUnconvergedXtable()
-  data <- fracUnconvergedResampleFitsAll(baseResample=baseResample)
-  dataXtable <- xtable(x=data, 
-                       caption="Fraction of unconverged resample models", 
-                       label="tab:frac_unconverged_models",
-                       digits = 3,
-                       align = "rl|cc|ccccccccc") #Sets alignment of the numbers in the columns)
-  print(dataXtable, 
-        caption.placement="top", 
-        size="\\tiny",
-        table.placement="H",
-        include.rownames=FALSE)
-@
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{95\% Confidence Intervals}
-\label{sec:Confidence_Intervals}
-\setcounter{table}{0} % Restarts table number counter at 0 in this section.
-\setcounter{figure}{0} % Restarts figure number counter at 0 in this section.
-\setcounter{equation}{0} % Restarts equation counter to 0 in this section.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Resample coefficients in the scatter plots 
-can be represented as 95\% confidence intervals 
-by finding the parameter values associated with 
-the middle 95\% of the data for each model parameter.
-This appendix provides tables and graphs of the 95\% confidence
-intervals on fitted model parameters.
-
-%++++++++++++++++++++++++++++++
-\subsection{Cobb-Douglas Models}
-%++++++++++++++++++++++++++++++
-
-The 95\% confidence intervals associated with 
-the without-energy column of Figure~\ref{fig:CD_Ternary_Scatter_Graph} 
-are shown in Table~\ref{tab:CD_Parameters_No_Energy}.
-
-<<CD_Params_Table, results='asis'>>=
-printCDParamsTable(energyType="none", baseResample=baseResample)    #Without energy
-@
-
-The data in Table~\ref{tab:CD_Parameters_No_Energy} are plotted in
-Figure~\ref{fig:CD_Params_Graph}.
-
-<<CD_Params_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.cap="Cobb-Douglas (without energy) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createCDParamsGraph(energyType="none", baseResample=baseResample)
-@
-
-The 95\% confidence intervals associated with 
-the with-energy column of Figure~\ref{fig:CD_Ternary_Scatter_Graph} 
-are shown in Table~\ref{tab:CD_Parameters_With_Q}
-and Figure~\ref{fig:CDq_Params_Graph}.
-
-<<CDq_Params_Table, results='asis'>>=
-printCDParamsTable(energyType="Q", baseResample=baseResample)   #With energy
-@
-
-<<CDq_Params_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=cdParameterGraphHeight, fig.cap="Cobb-Douglas (with energy) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createCDParamsGraph(energyType="Q", baseResample=baseResample)
-@
-
-%++++++++++++++++++++++++++++++
-\subsection{CES Models}
-%++++++++++++++++++++++++++++++
-
-The 95\% confidence intervals associated 
-with ($kl$) nest columns of 
-Figures~\ref{fig:CES_lambda_gamma_graph}--\ref{fig:CES_ternary_graph}
-are shown in Tables~\ref{tab:CES_Parameters_A} 
-and \ref{tab:CES_Parameters_B} and Figure~\ref{fig:CES_Params_Graph}.
-
-<<CES_Params_Table, results='asis'>>=
-print(cesParamsTableA(energyType="none", nest="(kl)", baseResample=baseResample), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-print(cesParamsTableB(energyType="none", nest="(kl)", baseResample=baseResample), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-@
-
-<<CES_Params_Graph, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (without energy, ($kl$) nesting) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createCESParamsGraph(energyType="none", nest="(kl)", baseResample=baseResample)
-@
-
-The 95\% confidence intervals associated 
-with ($kl$)$e$ nest columns of 
-Figures~\ref{fig:CES_lambda_gamma_graph}--\ref{fig:CES_ternary_graph}
-are shown in Tables~\ref{tab:CES_Parameters_A_With_Q_(kl)e} and 
-\ref{tab:CES_Parameters_B_With_Q_(kl)e} and Figure~\ref{fig:CESq_Params_Graph_kle}.
-
-<<CESq_Params_Table_kle, results='asis'>>=
-print(cesParamsTableA(energyType="Q", nest="(kl)e", baseResample=baseResample), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-print(cesParamsTableB(energyType="Q", nest="(kl)e", baseResample=baseResample), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-
-@
-
-<<CESq_Params_Graph_kle, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with energy, ($kl$)$e$ nesting) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createCESParamsGraph(energyType="Q", nest="(kl)e", baseResample=baseResample)
-@
-
-The 95\% confidence intervals associated 
-with ($le$)$k$ nest columns of 
-Figures~\ref{fig:CES_lambda_gamma_graph}--\ref{fig:CES_ternary_graph}
-are shown in Tables~\ref{tab:CES_Parameters_A_With_Q_(le)k} and 
-\ref{tab:CES_Parameters_B_With_Q_(le)k} and Figure~\ref{fig:CESq_Params_Graph_lek}.
-
-<<CESq_Params_Table_lek, results='asis'>>=
-print(cesParamsTableA(energyType="Q", nest="(le)k", baseResample=baseResample), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-print(cesParamsTableB(energyType="Q", nest="(le)k", baseResample=baseResample), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-
-@
-
-<<CESq_Params_Graph_lek, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with energy, ($le$)$k$ nesting) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createCESParamsGraph(energyType="Q", nest="(le)k", baseResample=baseResample)
-@
-
-The 95\% confidence intervals associated 
-with ($ek$)$l$ nest columns of 
-Figures~\ref{fig:CES_lambda_gamma_graph}--\ref{fig:CES_ternary_graph}
-are shown in Tables~\ref{tab:CES_Parameters_A_With_Q_(ek)l} and 
-\ref{tab:CES_Parameters_B_With_Q_(ek)l} and Figure~\ref{fig:CESq_Params_Graph_ekl}.
-
-<<CESq_Params_Table_ekl, results='asis'>>=
-print(cesParamsTableA(energyType="Q", nest="(ek)l", baseResample=baseResample), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-print(cesParamsTableB(energyType="Q", nest="(ek)l", baseResample=baseResample), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-
-@
-
-<<CESq_Params_Graph_ekl, fig.pos="H", fig.width=cesParameterGraphWidth, fig.height=cesParameterGraphHeight, fig.cap="CES (with energy, ($ek$)$l$ nesting) model parameters.
-Vertical bars indicate 95\\% confidence intervals.">>=
-createCESParamsGraph(energyType="Q", nest="(ek)l", baseResample=baseResample)
-@
-
-%++++++++++++++++++++++++++++++
-\subsection{LINEX Model}
-%++++++++++++++++++++++++++++++
-
-The 95\% confidence intervals associated with Figure~\ref{fig:LINEXq_Resample_Graph}
-are shown in Table~\ref{tab:LINEX_Parameters_With_Q} and Figure~\ref{fig:LINEXq_Params_Graph}.
-
-<<LINEX_Params_Table, results='asis'>>=
-print(linexParamsTable(energyType="Q", baseResample=baseResample), 
-      caption.placement="top", 
-      sanitize.colnames.function = identity, 
-      size="\\tiny",
-      table.placement="H")
-@
-
-<<LINEXq_Params_Graph, fig.pos="H", fig.width=linexParameterGraphWidth, fig.height=linexParameterGraphHeight, fig.cap="LINEX model parameters. Vertical bars indicate 95\\% confidence intervals.">>=
-createLINEXParamsGraph(energyType="Q", baseResample=baseResample)
-@
 

### 2014-08-09 Articles/Article_EnerEcon_2014/EconGrowth3.Rnw
Now using \Sexpr for % of data on spaghetti graphs.

@@
 
-% Approach
-% 
-% Build on articles using R to test econ growth PF, 
-% question what is reported when doing these tests (shen/whalley and others who have used micEconCES). 
-% 
-% 
-% Discussion and Insights
-% 
-% Does analysis differ from others in the conversation?
-% Yes, differs as follows:
-% \begin{itemize}
-% \item{if one do these test, report on all $\delta$, $\sigma$, $\gamma$, and $\lambda$ 
-% values as well as sse. 
-% Good fits not evidence of best values, must report uncertainties as well.}
-% \item{What motivates nesting of CES? Not well behaved $\rho$ results, driving $\sigma$s.
-% Different type of CES with parsimonious factors, sigmas can be generated but not that easy (idea Randy).
-% If you run all 3 nesting options, you can identify elasticities of all three factors in relation to each 
-% other. Furthermore, you can determine which two factors are driving overall behavior in the aggregate function.}
-% \item{necessary of different factors in PF to explain growth for countries in diff. development status}
-% \end{itemize}
-% 
-% What do we add to the conversation?
-% 
-% \begin{itemize}
-% 
-% \item{We are able to gain rich insights 
-% on what really drives growth from detailed analysis (including uncertainties) 
-% by testing all functional forms across many different 
-% economy types.}
-% 
-% \item{We were unable to gain new insights from the various energy quantifications that we tried.}
-% 
-% \item{We find, surprisingly, that energy is not necessary 
-% to be included alongside $k$ and $l$ in all PF. Models with energy and models without energy
-% all perform well on an R$^2$ basis.}
-% 
-% \item{We also find that 
-% 
-% (1) covariance of energy($e$) with both $k$ and $l$ is very high, with few exceptions (UK?).
-% 
-% (2) with few exceptions, $\sigma_{(kl)e}$, $\sigma_{ke}$, and $\sigma_{le}$ 
-% are all very low (indicating complementarity) (verify!!!!), and 
-% 
-% (3) energy-only models (SF$e$ and LINEX) achieve very good fits, just like CD$e$ and CES$e$.
-% (should we make this point or not?)}
-% 
-% \item{What does that mean? 
-% It is a fallacy to think that saying energy is unnecessary 
-% to include in an equation means energy is unimportant for economic growth. How to support this argument?
-% 
-% If you find that energy is unnecessary to include alongside capital and labor 
-% to explain growth in one economy at the macro, aggregated level, 
-% you should not assume that energy is unimportant as a driver for economic growth for all economies.
-% For developed economies, energy is captial intensive: you need to have large capital to make use 
-% of energy. In developing economies, you don't need capital to make use of energy. 
-% Rather, you need labor.
-% 
-% We need to verify the above by comparison with our results.}
-% 
-% \item{Also signals that different types of countries likely 
-% to react differently to energy constraints. 
-% Interpret $\sigma$ here, substitution possibilities.}
-% 
-% \end{itemize}
-% 
-% More work?
-% 
-% 
-% 
-% 
-% Big picture
-% [insert test test]
-% 
-% Why do we do this? Want to link energy and economics on national level 
-% and in a modeled approach,informing energy policy during energy transitions.
-% Usually macro energy economic models rely on PF with energy included. 
-% Key papers using CES in energy economics incl high impact such as 
-% Stern, Gerlagh, Tol etc. 
-% Cite in introduction met energy economists using PF approaches, specially CES.
-% But, which form to choose and using which parameters? 
-% Literature is inconclusive, very little actual empirical testing of such functions. 
-% Mostly CES in CGE models used by Wbank and others. 
-% CD adviced to be used by CBO. 
-% How do we select a functional form and what are the parameters to be used? On what basis do we select?
-% 
-% We aim. to search for empirically robust solution, one that stands up to statistical testing.
-% 
-% What we find is counterintuitive for many cases: dropping energy from the PF has little impact, 
-% but some notable exceptions. 
-% On other hand, only including energy in a PF of LINEX form also yields good results and stats tests. 
-% Is not a simple case for dropping energy, but acknowledging its key role. 
-% Do we support the call for better bottom-up understanding? 
-% What do we say on the limitations of macroeconomic modelling approaches altogether? 
-% (Note such limitations are well known in ME literature, for example capital controversy Robinson).
-% We speculate on implications for choosing PF in energy economic models that inform growth policy.
-% 
-% Points on paper so far
-% 1. Does the relative small differences in fit between different production functions warrant 
-% such a large debate on validity of one vs other? Clearly not. 
-% CD been used by economists for ease of use and extreme flexibility (Miller).  
-% PF generally used on instrumentalist grounds if give reasonable good description of data. 
-% NK econ theory provide poor causal explanation of observed data, 
-% but yet CD shows very good fit (miller, p17). 
-% CES is  more general, but is a liability in forecasting because difficult 
-% to get estimate of EoS that is consistent across studies (Miller, p26). 
-% Aggregation is problem of both CD and CES functional forms, 
-% so being careful when making strong inferences that cannot be justified.
-% 
-% 2. We think we can contribute by emphasising the need 
-% for proper stats testing or inconsistent reporting on use of preferred functions. 
-% Problems with empirical testing presented by Shen, Serrenho.
-% What are our issues with multivariate OLS (Serrenho)?
-% 
-% 3. Are we joining the forced choice between production functions or 
-% acknowledge the similar problems with aggregate prod functions in general? 
-% Do we see this as sufficient evidence to doubt the top-down approach to econ growth altogether?
-% 
-% 4. R2 is a very crude measure and only very minor improvements 
-% are achieved when others factors such as energy is added in a CD. 
-% We concur. Puzzling is conclusion that such minor improvements 
-% does prove the need to include energy in PF (Serrenho).
-% 
-% 5. We do think it is a choice between CD and CES (Miller) as 
-% both have serious deficiencies after stats tests.
-% 
-% 6. One central issue within PF is elasticity of subs (EoS). 
-% That is the \%ch in factor proportions ( k,l, etc) 
-% because of one unit ch in MRTS. 
-% MRTS is rate at which one factor can be substituted for another holding output constant. 
-% EoS is low in Leontief cases, L shaped isoquants.
-% 
-% 7. Miller makes the point that even if parameters in model are stats artifacts, 
-% they are still useful for forecasting. Do we agree?
-% 
-% 8. Is Ockham's razor relevant to what we are doing?
-% 
-% 9. Assumptions of CD are strongly rejected by empirical work, Miller still makes case for using CD.
-% 
-% 11. What about energy augmented 
-% 
-% 10. TZ case
-% CDno e: almost 80\% l
-% CD with e: 25\% energy, rest c,importance of l drops to 0
-% CES no e: 20\% c ($\sigma$), 80\% l, but large range
-% CES with e: fig 35 e may be NB
-% LINEX: one of lowest ct parameters (low relative importance of labour eff compared to cap eff)
-% Does this mean that relative small increases in cap eff can really lift the economy?
-% 
-% 11. ZA case
-% CD no e: roughly half c, l
-% CD with e: roughly half, c, e, importance of l drops to 0
-% CES no e: 10\% c, 25\% l ??
-% CES with e: fig 35 e may be NB
-% LINEX: one of highest ct parameters (high relative importance of labour eff compared to cap eff)
-% Does this mean that relative small increases in labour eff can really lift the economy?
-% 
-% 12. Capital starved Zambia. Very high importance. Understand CES param better.
-% 
-% Discussion: What is Next?
-% 
-% a. A comparative analysis between diff PF reveal interesting 
-% enough information to warrant a more diffused approach to countries. 
-% Thus, we have a case for doing this for  all countries in the world 
-% (or at least those representative of countries in different groups 80/20)
-% 
-% b. If c is relatively more important than labour or energy 
-% for growth and if capital stock is low, a situation one would expect in LDCs, 
-% a relative small addition of capital stock can give relatively large returns in terms of growth.
-% 
-% c. Now it becomes interesting, in a 'stages of growth' approach, 
-% using LT econ data it may be the case that the importance 
-% of factors are different across growth stages. 
-% It would need a composite type of analysis - both stock and importance.
-% 
-% d. Is it possible to have evidence of diff stocks and diff importances across phases of growth? 
-% Maybe test this for a data rich nation that has worked through these stages, 
-% we try to identify them and do partial analysis on time periods coinciding with these stages.
-% 
-% Should we eliminate $u$ data? Only 3 countries. Only 20 years. Doesn't add much insight. 
-% Too bad, but perhaps necessary to simplify paper.
-% 
-% Discussions:
-% 
-% Counterfactuals: energy, cap, labour what ifs for future.
-% 
-% interpretation of type of economies, what does the data presentation say 
-% on relative change in each input and change in GDP?
-% 
-% Forcing const elast of subs in CES thru nested structures violates 
-% observation that more than two factor will not be const. elasticities Uzawa 1962.
-% 
-% R programming dealt with nested CES see paper discussion on Kemfert.
-% 
-% Next steps:
-% 
-% Stages of growth crowd implicitly assumes countries at similar stage of growth will
-% have similar values for $\alpha$, $\beta$, $\gamma$. However, our results show
-% that not to be true. Needs further exploration to cover more (all?) countries.
-% 
-% 
-% 
-% 
-% **** Notes on the introduction from Martin ****
-% 
-% 1. Set scene through energy economic modelling papers. 
-% Point out that PF approaches are alive and well (Stern, Tol, Gerlagh, World Bank, IMF), 
-% short lit review as part of a longer introduction.  
-% Mention competing PF approaches and parameter choice. 
-% On what basis selection and how estimate parameters? 
-% 
-% 2. Point out the need for adequate statistical testing and economic interpretation, 
-% citing some earlier critical papers on PF limitations. Take issue with 
-% 
-% 3. Spell out the contribution we will be making in this paper, 
-% we are taking the approach that all models are wrong but some are useful. 
-% We are after generating insights even after deeper assumptions of econ growth theory are very limiting.
-% 
-% 4. Introduce coordinates of analysis.
-% 
-% 
-% 
-% 
-% 
-% **** Original introduction that MKH wrote ****
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 of production: $\alpha + \beta + \gamma = 1$.
-
-% \citet{Ayres:2008cl} uses Equation~\ref{eq:CDe} with exergy ($x$) and 
-% useful work ($u$) quantifications for $e$ to describe historic Japanese 
-% and American economies from 1900-2000. \citet{Froling:2009vo} uses an 
-% energy-augmented Cobb-Douglas production function with thermal energy 
-% quantification ($q$) to describe output for the global economy from 1800--1970. 
-% Fr\"{o}ling's model endogenizes labor with respect to fertility 
-% and mortality rates and separates thermal energy into two types: biomass 
-% energy and coal energy. 
-% \citet{Serrenho:2010vq} use the log transform of 
-% the energy-augmented Cobb-Douglas function with thermal energy 
-% quantification ($q$) to describe output for the EU-15 countries. 
-% Serrenho divides thermal energy into renewables, non-renewables, 
-% wastes, and imports. 
-% The main argument of these papers is that 
-% energy is an important driver of growth and needs to be included
-% as an essential factor of production.
-% 
-% **** Martin: add more here about the conclusions of each paper regarding 
-% the role of energy in economic growth? Add additional literature? 
-% Or, adjust as you see fit. Especially, are there any confidence intervals 
-% or statistical evaluation in each of these studies? ****
 
@@
 
-% \citet{VanderWerf:2008tc} evalutes various nested CES production 
-% functions for 12 OECD countries with respect to climate change policy. 
-% \citeauthor{VanderWerf:2008tc} concludes that ($kl$)($e$) nesting structure 
-% best fits historical data. \citet{Lecca:2011kr} also evaluate a variety of 
-% CES production functions using a KLEM structure to determine how the various 
-% options for nesting the energy factor of production affect predictive ability. 
-% \citet{Stern:2012ey} also use a CES production function of the form ($kl$)($e$). 
-% \citeauthor{Stern:2012ey} apply their CES function to the Swedish economy 
-% from 1800-2000 and demonstrate the importance of the transition from wood to 
-% fossil fuels for economic growth. \citet{Shen:2013vp} included energy 
-% in nested aggregated CES production functions 
-% for China and found that the best nesting structure is ($le$)($k$).
-% 
-% 
-% **** Martin: add more here about the conclusions of each paper regarding 
-% the role of energy in economic growth? Add additional literature? 
-% Or, adjust as you see fit. Especially, are there any confidence 
-% intervals or statistical evaluation in each of these studies? ****
-
 %------------------------------
@@
 Both $a_0$ and $c_t$ are assumed constant with respect to time.
-
-% \citet{Kummel:2002tx} use the 
-% LINEX production function to describe economic output 
-% for the economies of the U.S., Japan, and Germany. 
-% \citet{Warr:2010ga} compare the LINEX production function with 
-% the Cobb-Douglas production function to assess economic growth 
-% for Austria, the United Kingdom, the United States, and Japan. 
-% \citet{Ayres:2005kn} argued that introducing energy inputs 
-% in traditional production functions does not improve its explanatory power, 
-% but including useful work in a LINEX function does. 
-% 
-% \authNote{Martin: add more here about the conclusions of each paper 
-% regarding the role of energy in economic growth? Add additional literature? 
-% Or, adjust as you see fit. Especially, are there any confidence intervals 
-% or statistical evaluation in each of these studies?}
-% 
-% \authNote{If we want to keep this quote, it should be clearer what point we are trying to
-% make with it. ---rjp}
-% \citet{Abramovitz:1956aa} wrote:
-% 
-% \begin{quote}
-%   This result [that ``technological progress'' explained
-%   175\% of the growth of the US economy since 1870] is surprising in the lopsided
-%   importance which it appears to give to productivity increase,
-%   and it should be, in a sense, sobering, if not discouraging,
-%   to students of economic growth.
-%   Since we know little about the causes of productivity increase,
-%   the indicated importance of this element may be taken to be some sort of measure
-%   of our ignorance about the causes of economic growth in the United States
-%   and some sort of indication of where
-%   we need to concentrate our attention.
-% \end{quote}
 
@@
 The fit to historical data is shown as a white line.
-The gray band encompasses 95\% of the fits to resampled data.
+The gray band encompasses \Sexpr{spaghettiGraphLevel * 100.0}\% of the fits to resampled data.
 
@@
 the fit to historical data is shown as a white line, and 
-the gray band encompasses 95\% of the fits to resampled data.
+the gray band encompasses \Sexpr{spaghettiGraphLevel * 100.0}\% of the fits to resampled data.
 
@@
 
-% Figure~\ref{fig:CES_Spaghetti_Graph_CN} shows details of the resample fits for China with the (kl)e nesting.
-% Again, historical data are shown as a black line. 
-% The fit to historical data is shown as a white line.
-% The gray band encompasses 95\% of the fits to resampled data.
-% 
-% <<CES_Spaghetti_Graph_CN, fig.pos="H", fig.align='center', fig.width=maxWidth, fig.height=maxHeight, fig.cap="CES fitted models for China with the (kl)e nesting.">>=
-% spaghettiPlot(data=subset(cesFittedData, Country=="CN" & nestStrParen=="(iK + iL) + (iQp)"), level=spaghettiGraphLevel) +
-%     labs(y="Indexed GDP (1980 = 1 or 1991 = 1")
-% @
-
 %++++++++++++++++++++++++++++++
@@
 the fit to historical data is shown as a white linem and 
-the gray band encompasses 95\% of the fits to resampled data.
+the gray band encompasses \Sexpr{spaghettiGraphLevel * 100.0}\% of the fits to resampled data.
 

### 2014-08-11 Articles/Article_EcolEcon_2014/Paper2.Rnw
Articles now use setwd("../..").

@@
 historicalData <- rbind.fill(REXS1960, IST, Leeds) # From the EconData package
+
+# Set working directory to the top level of the repository: Econ-Growt-R-Analysis
+# This is the same directory from which the RStudio project runs.
+# Setting this working directory eliminates the need to use dir="../.." in the 
+# loadPostPorcessedData function calls below.
+setwd(file.path("..", ".."))
+
 # Load coefficients from all models in one large data frame

### 2014-08-11 Articles/Article_EnerEcon_2014/EconGrowth3.Rnw
Articles now use setwd("../..").

@@
 historicalData <- Calvin # From the EconData package
+
+# Set working directory to the top level of the repository: Econ-Growt-R-Analysis
+# This is the same directory from which the RStudio project runs.
+# Setting this working directory eliminates the need to use dir="../.." in the 
+# loadPostPorcessedData function calls below.
+setwd(file.path("..", ".."))
+
 # Load coefficients from all models in one large data frame
-coeffs_df <- loadPostProcessedData(Source = "Calvin", kind = "coeffs", dir = "../../data_postprocessed")
+coeffs_df <- loadPostProcessedData(Source = "Calvin", kind = "coeffs")
 # Load fitted data from all models in one large data frame
-fitted_df <- loadPostProcessedData(Source = "Calvin", kind = "fitted", dir = "../../data_postprocessed")
+fitted_df <- loadPostProcessedData(Source = "Calvin", kind = "fitted")
 # Load the original models.
-oModels <- loadPostProcessedData(Source = "Calvin", kind = "models", dir = "../../data_postprocessed")
+oModels <- loadPostProcessedData(Source = "Calvin", kind = "models")
 @

### 2014-08-11 Articles/Article_Heun_Warr_2014/EcolEcon_HeunWarr.Rnw
Articles now use setwd("../..").

@@
 historicalData <- REXS # From the EconData package
+
+# Set working directory to the top level of the repository: Econ-Growt-R-Analysis
+# This is the same directory from which the RStudio project runs.
+# Setting this working directory eliminates the need to use dir="../.." in the 
+# loadPostPorcessedData function calls below.
+setwd(file.path("..", ".."))
+
 # Load coefficients from all models in one large data frame

### 2014-08-11 Articles/Article_JAE_2014/ZAGrowth_JAE.Rnw
Articles now use setwd("../..").

@@
 
+# Set working directory to the top level of the repository: Econ-Growt-R-Analysis
+# This is the same directory from which the RStudio project runs.
+# Setting this working directory eliminates the need to use dir="../.." in the 
+# loadPostPorcessedData function calls below.
+setwd(file.path("..", ".."))
+
 # Load coefficients from all models in one large data frame
-coeffs_df <- loadPostProcessedData(Source = "Calvin", kind = "coeffs", dir = "../../data_postprocessed")
+coeffs_df <- loadPostProcessedData(Source = "Calvin", kind = "coeffs")
 coeffs_df_ZA <- subset(coeffs_df, subset=country=="ZA")
 # Load fitted data from all models in one large data frame
-fitted_df <- loadPostProcessedData(Source = "Calvin", kind = "fitted", dir = "../../data_postprocessed")
+fitted_df <- loadPostProcessedData(Source = "Calvin", kind = "fitted")
 fitted_df_ZA <- subset(fitted_df, subset=Country=="ZA")
 # Load the original models.
-oModels <- loadPostProcessedData(Source = "Calvin", kind = "models", dir = "../../data_postprocessed")
+oModels <- loadPostProcessedData(Source = "Calvin", kind = "models")
 oModels_ZA <- oModels$Calvin$ZA

### 2014-08-12 Articles/Article_EnerEcon_2014/EconGrowth3.Rnw

@@
 Parameter estimates are chosen to minimize
+\authNote{Randy edit the following equation to reflect the fact that we're fitting in log space.}
 %
@@
 Again, historical data are shown as a black line, 
-the fit to historical data is shown as a white linem and 
+the fit to historical data is shown as a white line and 
 the gray band encompasses \Sexpr{spaghettiGraphLevel * 100.0}\% of the fits to resampled data.

### 2014-08-14 Articles/Article_EcolEcon_2014/Paper2.Rnw
standardTriPlot & standardScatterPlot now give colors.

--- 2014-08-05 Articles/Article_EcolEcon_2014/Paper2.Rnw
@@
 historicalData <- rbind.fill(REXS1960, IST, Leeds) # From the EconData package
+
+# The working directory is set to the directory that contains this file.
+# To reach the post-processed data, we need to move 
+# up two levels and into the data_postprocessed directory.
+# So, in each of the loadPostProcessedData calls below, we use
+# dir = "../../data_postprocessed".
+pp_path <- file.path("..", "..", "data_postprocessed")
+
 # Load coefficients from all models in one large data frame
-REXS1960_Coeffs <- loadPostProcessedData(Source = "REXS1960", kind = "coeffs")
-IST_Coeffs <- loadPostProcessedData(Source = "IST", kind = "coeffs")
-Leeds_Coeffs <- loadPostProcessedData(Source = "Leeds", kind = "coeffs")
+REXS1960_Coeffs <- loadPostProcessedData(Source = "REXS1960", kind = "coeffs",dir = pp_path)
+IST_Coeffs <- loadPostProcessedData(Source = "IST", kind = "coeffs",dir = pp_path)
+Leeds_Coeffs <- loadPostProcessedData(Source = "Leeds", kind = "coeffs", dir = pp_path)
 AllCoeffs <- rbind(REXS1960_Coeffs, IST_Coeffs, Leeds_Coeffs)
@@
 # Load fitted data from all models in one large data frame
-REXS1960_Fitted <- loadPostProcessedData(Source = "REXS1960", kind = "fitted")
-IST_Fitted <- loadPostProcessedData(Source = "IST", kind = "fitted")
-Leeds_Fitted <- loadPostProcessedData(Source = "Leeds", kind = "fitted")
+REXS1960_Fitted <- loadPostProcessedData(Source = "REXS1960", kind = "fitted", dir = pp_path)
+IST_Fitted <- loadPostProcessedData(Source = "IST", kind = "fitted", dir = pp_path)
+Leeds_Fitted <- loadPostProcessedData(Source = "Leeds", kind = "fitted", dir = pp_path)
 AllFitted <- rbind(REXS1960_Fitted, IST_Fitted, Leeds_Fitted)
@@
 
-<<Historical_Data_1, fig.pos="H", fig.align='center', fig.width=6.6, fig.height=3, fig.cap="Historical data.", eval=TRUE>>=
+<<Historical_Data_1, fig.pos="H", fig.align='center', fig.width=6.6, fig.height=6, fig.cap="Historical data.", eval=TRUE>>=
 mdata <- melt(historicalData, 
@@
 historicalPlot(mdata, 
+               mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
                facet_formula = Country ~ Source, 
-               lines_formula = variable + value ~ Year, 
-               line_types = c(1,2,3,4,5,6)) + 
+               line_types = c(1,5,2,6,4,3)) + 
   xlab("") + 
@@
 
-<<Historical_Data_2, fig.pos="H", fig.align='center', fig.width=8, fig.height=3, fig.cap="Historical data.", eval=TRUE>>=
+<<Historical_Data_2, fig.pos="H", fig.align='center', fig.width=8, fig.height=6, fig.cap="Historical data.", eval=TRUE>>=
 historicalPlot(mdata, 
-               facet_formula=Country~variable, 
-               lines_formula=Source+value~Year, 
-               line_types=c(1,2,3)) +  
+               mapping=aes(x=Year, y=value, group=Source, linetype=Source), 
+               facet_formula = Country ~ variable, 
+               line_types = c(1,5,3)) + 
   xlab("") + 
@@
 
-<<CD_lambda_theta_graph, fig.pos="H", fig.align='center', fig.width=4, fig.height=4.5, fig.cap="$\\lambda$ and $\\theta$ values for UK Cobb-Douglas resample models.">>=
+<<CD_lambda_theta_graph, fig.pos="H", fig.align='center', fig.width=6, fig.height=4.5, fig.cap="$\\lambda$ and $\\theta$ values for Cobb-Douglas resample models.">>=
 cdCoeffsData <- subset(AllCoeffs, subset = model=="cd")
-standardScatterPlot(data=cdCoeffsData, mapping=aes(scale, lambda), facet_formula=energy~Source, alpha=0.05) +
-    scale_x_continuous(limits=c(0.95, 1.05), breaks=c(0.95, 1.0)) +
-    scale_y_continuous(breaks=c(0.01, 0.015, 0.02)) +    
-    labs(x=expression(theta), y=expression(lambda))
-@
-
-<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=3.9, fig.height=4, fig.cap="UK Cobb-Douglas resample model parameters.">>=
-standardTriPlot(data=cdCoeffsData, facet_formula=energy~Source)
-@
-
-<<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=4, fig.height=4.5, fig.cap="UK Cobb-Douglas fitted models.">>=
-cdFittedData <- subset(AllFitted, subset = model=="cd")
-spaghettiPlot(data=cdFittedData, facet_formula=energy~Source, level=spaghettiGraphLevel) +
+standardScatterPlot(data=cdCoeffsData, mapping=aes(x=scale, y=lambda, color=Source), 
+                    facet_formula=country~energy, alpha=0.05) +
+    scale_x_continuous(limits=c(0.8, 1.2), breaks=c(0.9, 1.0, 1.1)) +
+    scale_y_continuous(limits=c(-0.1, 0.2), breaks=c(0.0, 0.1, 0.2)) +    
+    labs(x=expression(theta), y=expression(lambda)) +
+    guides(colour=guide_legend(override.aes = aes(alpha=1))) #+
+#     geom_density2d()
+@
+
+<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=6, fig.height=4, fig.cap="Cobb-Douglas resample model parameters.">>=
+standardTriPlot2(data=cdCoeffsData, 
+                mapping=aes(color=Source),
+                facet_formula=country~energy) +
+    guides(colour=guide_legend(override.aes = aes(alpha=1)))
+@
+
+<<CD_GDP_Spaghetti_Graphs_US, fig.pos="H", fig.align='center', fig.width=4, fig.height=2.5, fig.cap="US Cobb-Douglas fitted models.">>=
+cdFittedDataUS <- subset(AllFitted, subset = model=="cd" & Country=="US")
+spaghettiPlot(data=cdFittedDataUS, facet_formula=Source~energy, level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1960=1)") +
+  scale_x_continuous(breaks=c(1960, 1980, 2000))
+@
+
+<<CD_GDP_Spaghetti_Graphs_UK, fig.pos="H", fig.align='center', fig.width=4, fig.height=4.5, fig.cap="UK Cobb-Douglas fitted models.">>=
+cdFittedDataUK <- subset(AllFitted, subset = model=="cd" & Country=="UK")
+spaghettiPlot(data=cdFittedDataUK, facet_formula=Source~energy, level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1960=1)") +
+  scale_x_continuous(breaks=c(1960, 1980, 2000))
+@
+
+<<CD_GDP_Spaghetti_Graphs_JP, fig.pos="H", fig.align='center', fig.width=4, fig.height=2.5, fig.cap="JP Cobb-Douglas fitted models.">>=
+cdFittedDataJP <- subset(AllFitted, subset = model=="cd" & Country=="JP")
+spaghettiPlot(data=cdFittedDataJP, facet_formula=Source~energy, level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1960=1)") +
+  scale_x_continuous(breaks=c(1960, 1980, 2000))
+@
+
+<<CD_GDP_Spaghetti_Graphs_AT, fig.pos="H", fig.align='center', fig.width=5, fig.height=3.5, fig.cap="AT Cobb-Douglas fitted models.">>=
+cdFittedDataAT <- subset(AllFitted, subset = model=="cd" & Country=="AT")
+spaghettiPlot(data=cdFittedDataAT, facet_formula=Source~energy, level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1960=1)") +
+  scale_x_continuous(breaks=c(1960, 1980, 2000))
+@
+
+<<CD_GDP_Spaghetti_Graphs_CN, fig.pos="H", fig.align='center', fig.width=4, fig.height=2.5, fig.cap="CN Cobb-Douglas fitted models.">>=
+cdFittedDataCN <- subset(AllFitted, subset = model=="cd" & Country=="CN")
+spaghettiPlot(data=cdFittedDataCN, facet_formula=Source~energy, level=spaghettiGraphLevel) +
     labs(y="Indexed GDP (1960=1)") +
@@
 <<LINEX_abg_traj_graph_REXS_UK_U, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="UK LINEX trajectory for REXS with $u$.">>=
+REXS1960_Models <- loadPostProcessedData(Source = "REXS1960", kind = "models", dir=pp_path)
 triPlot(data=fortify(REXS1960_Models$REXS1960$UK$linex$`iK+iL+iU`), grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1960")
@@
 <<LINEX_abg_traj_graph_IST_UK_U, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="UK LINEX trajectory for IST with $u$.">>=
+IST_Models <- loadPostProcessedData(Source = "IST", kind = "models", dir=pp_path)
 triPlot(data=fortify(IST_Models$IST$UK$linex$`iK+iL+iU`), grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1960")
@@
 <<LINEX_abg_traj_graph_Leeds_UK_U, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="UK LINEX trajectory for Leeds with $u$.">>=
+Leeds_Models <- loadPostProcessedData(Source = "Leeds", kind = "models", dir=pp_path)
 triPlot(data=fortify(Leeds_Models$Leeds$UK$linex$`iK+iL+iU`), grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1960")

### 2014-08-14 Articles/Article_EnerEcon_2014/EconGrowth3.Rnw
standardTriPlot & standardScatterPlot now give colors.

@@
 
-# Set working directory to the top level of the repository: Econ-Growt-R-Analysis
-# This is the same directory from which the RStudio project runs.
-# Setting this working directory eliminates the need to use dir="../.." in the 
-# loadPostPorcessedData function calls below.
-setwd(file.path("..", ".."))
+# The working directory is set to the directory that contains this file.
+# To reach the post-processed data, we need to move 
+# up two levels and into the data_postprocessed directory.
+# So, in each of the loadPostProcessedData calls below, we use
+# dir = "../../data_postprocessed".
+pp_path <- file.path("..", "..", "data_postprocessed")
 
 # Load coefficients from all models in one large data frame
-coeffs_df <- loadPostProcessedData(Source = "Calvin", kind = "coeffs")
+coeffs_df <- loadPostProcessedData(Source = "Calvin", kind = "coeffs", dir = pp_path)
 # Load fitted data from all models in one large data frame
-fitted_df <- loadPostProcessedData(Source = "Calvin", kind = "fitted")
+fitted_df <- loadPostProcessedData(Source = "Calvin", kind = "fitted", dir = pp_path)
 # Load the original models.
-oModels <- loadPostProcessedData(Source = "Calvin", kind = "models")
+oModels <- loadPostProcessedData(Source = "Calvin", kind = "models", dir = pp_path)
 @
@@
 \citet{Nel:2010fv} argue for the 
-``\dots vital importance of energy security \dots'' 
-on the basis of a model based on an explicit 
-energy-based formulation of economic growth.  
+``\dots{}vital importance of energy security\dots'' 
+on the basis of an economic growth model with explicit 
+energy-based formulation.  
 \citet{Hamilton:2013vc} argues that 
-``[c]oping with a final peak in world oil production \dots 
+``[c]oping with a final peak in world oil production\dots%
 [will] have much in common with previous historical episodes that resulted from 
@@
 term.%
-  \footnote{The time-dependent term in production functions is often linked
-  to ``technological progress,'' but that is a very narrow reading of Solow's original intent:
+  \footnote{The time-dependent term in production functions is often associated with
+  ``technological progress,'' but that is a very narrow reading of Solow's original intent:
   \begin{quote}
@@
 $L$ is expressed in workers or work-hours/year, and
-0 subscripts indicate values at an initial year.%
+0 subscripts indicate values at an initial year.
+The parameters $\alpha$ and $\beta$ indicate the relative roles 
+of capital and labor in the economy.
+Typically, the constraint $\alpha + \beta = 1$ is assumed, 
+indicating constant returns to scale.%
   \footnote{Dimensionless, indexed quantities are represented by 
   lower-case symbols 
-($y$, $k$, $l$, $e$, $q$, $x$, and $u$), and dimensional 
+  ($y$, $k$, $l$, and $q$), and dimensional 
   quantities are represented by upper-case symbols 
-($Y$, $K$, $L$, $E$, $Q$, $X$, and $U$). 
+  ($Y$, $K$, $L$, and $Q$). 
   Model parameters are represented by Greek letters
@@
 might vary from one economy to the next.
-The parameters $\alpha$ and $\beta$ indicate the relative roles 
-of capital and labor in the economy.
-Typically, the constraint $\alpha + \beta = 1$ is assumed, 
-indicating constant returns to scale.
 
@@
 Section~\ref{sec:Sources_of_Data} details sources of data and calculations to 
-generate time series for economic output and factors of production. 
+generate time series for economic output ($y$) and factors of production ($k$, $l$, and $q$). 
 The procedures for and results from parameter estimation for the various production functions 
@@
 results, and Section~\ref{sec:Conclusion} concludes.
-An appendix provides details of all statistical results.
 
@@
 in ecological economic (including biophysical economic) models
-and that energy \emph{is included} in resource economic models, 
+and that energy \emph{is included in} resource economic models, 
 but \emph{remains isolated} within the sub-discipline.  
@@
 energy availability plays
-``\dots a key role in enabling growth,''
-despite the evidence of decreasing energy consumed per unit of output.  
+``\dots{}a key role in enabling growth,''
+despite evidence of decreasing energy consumed per unit of output.  
 He concludes, based on theory and time-series results, 
@@
 wherein energy is the only factor of production,
-and capital~($k$), labor~($l$), and energy~($e$)
+and capital~($k$), labor~($l$), and energy~($q$)
 combine to provide efficiencies that augment energy.
-Technological change is manifest in these efficiencies,
-as more useful work is done per joule of exergy \citep{Ayres:2005kn}.
+Technological change is manifest as increased efficiency:
+more useful work done per joule of exergy \citep{Ayres:2005kn}.
+There is no Solow-style term ($\mathrm{e}^{\lambda t}$) for technological change.
 
@@
 we present a comparative analysis among representatives of
-the World Bank’s main categories of countries, 
+the World Bank's main categories of countries, 
 namely Developed Countries (DCs), 
@@
               variable.name = "variable") 
-historicalPlot(mdata, 
+historicalPlot(data=mdata, 
+               mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
                facet_formula = Country ~ Source, 
-               lines_formula = variable + value ~ Year, 
-               line_types = c(1,2,3,4)) +
+               line_types = c(1,5,2,3)) +
   xlab("") +
-  ylab("Indexed (1980-1 or 1991=1")
+  ylab("Indexed (1980=1 or 1991=1)")
 @
@@
 
+Figure~\ref{fig:CD_lambda_theta_graph} shows $\lambda$ and $\theta$ values
+for Cobb-Douglas resample models with and without energy.
+Each reample is shown as a gray dot on the graph. 
+The fit to historical data is shown as a gray crosshairs.
+
 Figure~\ref{fig:CD_Ternary_Scatter_Graph} shows ternary plots 
@@
 for Cobb-Douglas (without and with energy) resample models.
-Each reample is shown as a gray dot on the graph. 
-The fit to historical data is shown as a gray crosshairs.
 
@@
 
+<<CD_lambda_theta_graph, fig.pos="H", fig.align='center', fig.width=2.8, fig.height=7.0, fig.cap="$\\lambda$ and $\\theta$ values for CD resample models.">>=
+cdCoeffsData <- filter(coeffs_df, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iQp"))
+standardScatterPlot(data=cdCoeffsData, mapping=aes(x=scale, y=lambda), facet_formula=country~energy, alpha=0.05) +
+    scale_x_continuous(limits=c(0.8, 1.2), breaks=c(0.8, 1.0, 1.2)) +
+    scale_y_continuous(limits=c(-0.05, 0.15), breaks=c(0, 0.05, 0.1)) +    
+    labs(x=expression(theta), y=expression(lambda))
+@
+
 \twocolumn{}
 <<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=2.9, fig.height=7.7, fig.cap="Cobb-Douglas resample model parameters.">>=
-cdCoeffsData <- filter(coeffs_df, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iQp"))
 standardTriPlot(data=cdCoeffsData, facet_formula=country~energy)

### 2014-08-14 Articles/Article_Heun_Warr_2014/EcolEcon_HeunWarr.Rnw
standardTriPlot & standardScatterPlot now give colors.

--- 2014-07-30 Articles/Article_Heun_Warr_2014/EcolEcon_HeunWarr.Rnw
@@
 historicalData <- REXS # From the EconData package
+
+# The working directory is set to the directory that contains this file.
+# To reach the post-processed data, we need to move 
+# up two levels and into the data_postprocessed directory.
+# So, in each of the loadPostProcessedData calls below, we use
+# dir = "../../data_postprocessed".
+pp_path <- file.path("..", "..", "data_postprocessed")
+
 # Load coefficients from all models in one large data frame
-coeffs_df <- tbl_df(REXS_Coeffs)
+coeffs_df <- loadPostProcessedData(Source = "REXS", kind = "coeffs", dir=pp_path)
 # Load fitted data from all models in one large data frame
-fitted_df <- tbl_df(REXS_Fitted)
-
+fitted_df <- loadPostProcessedData(Source = "REXS", kind = "fitted", dir=pp_path)
 # Load the original models.
-oModels <- REXS_Models
+oModels <- loadPostProcessedData(Source = "REXS", kind = "models", dir=pp_path)
 @

### 2014-08-14 Articles/Article_JAE_2014/ZAGrowth_JAE.Rnw
standardTriPlot & standardScatterPlot now give colors.

--- 2014-08-06 Articles/Article_JAE_2014/ZAGrowth_JAE.Rnw
@@
 
+# The working directory is set to the directory that contains this file.
+# To reach the post-processed data, we need to move 
+# up two levels and into the data_postprocessed directory.
+# So, in each of the loadPostProcessedData calls below, we use
+# dir = "../../data_postprocessed".
+pp_path <- file.path("..", "..", "data_postprocessed")
+
 # Load coefficients from all models in one large data frame
-coeffs_df <- loadPostProcessedData(Source = "Calvin", kind = "coeffs", dir = "../../data_postprocessed")
+coeffs_df <- loadPostProcessedData(Source = "Calvin", kind = "coeffs", dir=pp_path)
 coeffs_df_ZA <- subset(coeffs_df, subset=country=="ZA")
 # Load fitted data from all models in one large data frame
-fitted_df <- loadPostProcessedData(Source = "Calvin", kind = "fitted", dir = "../../data_postprocessed")
+fitted_df <- loadPostProcessedData(Source = "Calvin", kind = "fitted", dir=pp_path)
 fitted_df_ZA <- subset(fitted_df, subset=Country=="ZA")
 # Load the original models.
-oModels <- loadPostProcessedData(Source = "Calvin", kind = "models", dir = "../../data_postprocessed")
+oModels <- loadPostProcessedData(Source = "Calvin", kind = "models", dir=pp_path)
 oModels_ZA <- oModels$Calvin$ZA

### 2014-08-14 Packages/EconModels/R/Graphics.R

@@ -117,7 +117,7 @@ sigma_trans <- function(base = exp(1)) {
 }
 
 #' @export
-standardTriPlot2 <- function(data, 
+standardTriPlot <- function(data, 
                             grid_lines=5, 
                             aes_string="", #"color=lambda", 
                             orig_color = "gray70",
@@ -145,33 +145,33 @@ standardTriPlot2 <- function(data,
 
 # standardTriPlot2(ddd, facet_formula = Country ~ Source, mapping=aes(color=fred), size=3)
 
+# standardTriPlot <- function(data, 
+#                             grid_lines=5, 
+#                             aes_string="", #"color=lambda", 
+#                             orig_color = "gray70",
+#                             size=1.0, 
+#                             alpha=0.2,
+#                             facet_formula = country ~ nest ){
+#   p <- triPlot(subset(data, method!="orig"), 
+#                gamma, alpha, beta,
+#                labels=c("gamma", "alpha", "beta"),
+#                grid_lines=grid_lines,  aes_string=aes_string, 
+#                size=size, alpha=alpha ) + 
+#     geom_point(data=subset(data, method=="orig"), 
+#                color=orig_color, alpha=1, size=3, shape=10) 
+#   if ( !is.null(facet_formula) ) {
+#     if ( length(facet_formula)==2 ) {
+#       p <- p + facet_wrap( facet_formula )
+#     } else { 
+#       p <- p + facet_grid( facet_formula )
+#     }
+#   }  
+#   return(p)
+#   # scale_colour_gradient(expression(lambda), high="navy", low="skyblue") 
+# }
+
 #' @export
-standardTriPlot <- function(data, 
-                            grid_lines=5, 
-                            aes_string="", #"color=lambda", 
-                            orig_color = "gray70",
-                            size=1.0, 
-                            alpha=0.2,
-                            facet_formula = country ~ nest ){
-  p <- triPlot(subset(data, method!="orig"), 
-               gamma, alpha, beta,
-               labels=c("gamma", "alpha", "beta"),
-               grid_lines=grid_lines,  aes_string=aes_string, 
-               size=size, alpha=alpha ) + 
-    geom_point(data=subset(data, method=="orig"), 
-               color=orig_color, alpha=1, size=3, shape=10) 
-  if ( !is.null(facet_formula) ) {
-    if ( length(facet_formula)==2 ) {
-      p <- p + facet_wrap( facet_formula )
[…]

### 2014-08-14 Articles/Article_Heun_Warr_2014/EcolEcon_HeunWarr.Rnw
Articles now working with new code.

@@
 <<Historical_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=7.5, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), and thermal energy ($q$).">>=
-historicalPlot(historicalData)
+mdata <- melt(historicalData, 
+              measure.vars = c("iGDP", "iK", "iL", "iXp", "iU"), 
+              variable.name = "variable",
+              value.name = "value")
+historicalPlot(mdata, 
+               mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
+               facet_formula = Country ~ Source, 
+               line_types = c(1,5,2,6,4)) + 
+  xlab("") + 
+  ylab("Indexed (1900=1 or 1950=1)")
 @
@@
 <<CD_lambda_theta_graph, fig.pos="H", fig.align='center', fig.width=4, fig.height=4.5, fig.cap="$\\lambda$ and $\\theta$ values for Cobb-Douglas resample models.">>=
-cdCoeffsData <- filter(coeffs_df, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iX", "iK+iL+iU"))
+cdCoeffsData <- filter(coeffs_df, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iXp", "iK+iL+iU"))
 standardScatterPlot(data=cdCoeffsData, mapping=aes(scale, lambda), facet_formula=country~energy, alpha=0.05) +
@@
 <<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=3.9, fig.height=4, fig.cap="Cobb-Douglas resample model parameters.">>=
-cdCoeffsData <- filter(coeffs_df, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iX", "iK+iL+iU"))
+cdCoeffsData <- filter(coeffs_df, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iXp", "iK+iL+iU"))
 standardTriPlot(data=cdCoeffsData, facet_formula=country~energy)
@@
 <<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=4, fig.height=4.5, fig.cap="Cobb-Douglas fitted models.">>=
-cdFittedData <- filter(fitted_df, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iX", "iK+iL+iU"))
+cdFittedData <- filter(fitted_df, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iXp", "iK+iL+iU"))
 spaghettiPlot(data=cdFittedData, facet_formula=Country~energy, level=spaghettiGraphLevel) +
@@
 cesCoeffsDataX <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
-                                                                      "(iK + iL) + (iX)", 
-                                                                      "(iL + iX) + (iK)", 
-                                                                      "(iX + iK) + (iL)"))
+                                                                      "(iK + iL) + (iXp)", 
+                                                                      "(iL + iXp) + (iK)", 
+                                                                      "(iXp + iK) + (iL)"))
 standardScatterPlot(data=cesCoeffsDataX, mapping=aes(gamma_coef, lambda), facet_formula=country~nestStrParen, alpha=0.05) +
@@
 cesFittedDataX <- filter(fitted_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
-                                                                      "(iK + iL) + (iX)", 
-                                                                      "(iL + iX) + (iK)", 
-                                                                      "(iX + iK) + (iL)"))
+                                                                      "(iK + iL) + (iXp)", 
+                                                                      "(iL + iXp) + (iK)", 
+                                                                      "(iXp + iK) + (iL)"))
 spaghettiPlot(data=cesFittedDataX, facet_formula=Country~nestStrParen, level=spaghettiGraphLevel) +
@@
 <<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7, fig.cap="LINEX model (with energy) resampling results.">>=
-linexCoeffsData <- filter(coeffs_df, model=="linex", energy %in% c("iX", "iU"))
+linexCoeffsData <- filter(coeffs_df, model=="linex", energy %in% c("iXp", "iU"))
 standardScatterPlot(data=linexCoeffsData, aes(a_0, c_t), facet_formula=country~energy, alpha=0.05) +
@@
 <<LINEX_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7.1, fig.cap="LINEX fitted models.">>=
-linexFittedData <- filter(fitted_df, model=="linex", energy %in% c("iX", "iU"))
+linexFittedData <- filter(fitted_df, model=="linex", energy %in% c("iXp", "iU"))
 spaghettiPlot(data=linexFittedData, facet_formula=Country~energy, level=spaghettiGraphLevel) +
@@
 
-Figures~\ref{fig:LINEX_abg_traj_graph_CN} and~\ref{fig:LINEX_abg_traj_graph_IR} 
-show trajectories for China and Iran, respectively.
-**** Can we make a figure that has all 9 graphs in it? --MKH ****
-
-<<LINEX_abg_traj_graph_CN, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="LINEX trajectory for China.">>=
-dataCN <- fortify(oModels$Calvin$CN$linex$`iK+iL+iQ`)
-triPlot(data=dataCN, grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1990")
-@
-
-<<LINEX_abg_traj_graph_IR, fig.pos="H", fig.align='center', fig.width=3, fig.height=1.5, fig.cap="LINEX trajectory for Iran.">>=
-dataIR <- fortify(oModels$Calvin$IR$linex$`iK+iL+iQ`)
-triPlot(data=dataIR, grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1990")
+Figures~\ref{fig:LINEX_abg_traj_graph_US} and~\ref{fig:LINEX_abg_traj_graph_UK} 
+show trajectories for US and UK, respectively with $u$.
+
+<<LINEX_abg_traj_graph_US, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="LINEX trajectory for US.">>=
+dataUS <- fortify(oModels$REXS$US$linex$`iK+iL+iU`)
+triPlot(data=dataUS, grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1990")
+@
+
+<<LINEX_abg_traj_graph_UK, fig.pos="H", fig.align='center', fig.width=3, fig.height=1.5, fig.cap="LINEX trajectory for UK.">>=
+dataUK <- fortify(oModels$REXS$UK$linex$`iK+iL+iU`)
+triPlot(data=dataUK, grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1990")
 @

### 2014-08-14 Articles/Article_JAE_2014/ZAGrowth_JAE.Rnw
Articles now working with new code.

@@
 <<Historical_Graph, fig.pos="H", fig.align='center', fig.width=5, fig.height=3, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), and thermal energy ($q$).">>=
-mdata <- melt(historicalData, 
+mdata <- melt(data=subset(historicalData, subset = Country=="ZA"), 
               measure.vars = c("iGDP", "iK", "iL", "iQp"), 
@@
               variable.name = "variable") 
-historicalPlot(mdata, 
+historicalPlot(data=mdata, 
+               mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
                facet_formula = Country ~ Source, 
-               lines_formula = variable + value ~ Year, 
-               line_types = c(1,2,3,4)) +
+               line_types = c(1,5,2,3)) +
   xlab("") +
-  ylab("Indexed (1980-1 or 1991=1")
+  ylab("Indexed (1991=1)")
 @

### 2014-08-14 Articles/Article_EcolEcon_2014/Paper2.Rnw
Deleted standardTriPlot2. Fixed bug with crosshairs color.

@@
 
-Figure~\ref{fig:CD_GDP_Spaghetti_Graph} compares predictions 
+Figures~\ref{fig:CD_GDP_Spaghetti_Graph_US}--\ref{fig:CD_GDP_Spaghetti_Graph_CN} 
+compare predictions 
 from the Cobb-Douglas models 
@@
 <<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=6, fig.height=4, fig.cap="Cobb-Douglas resample model parameters.">>=
-standardTriPlot2(data=cdCoeffsData, 
+standardTriPlot(data=cdCoeffsData, 
                 mapping=aes(color=Source),
@@
 linexCoeffsData <- subset(AllCoeffs, subset = model=="linex")
-standardScatterPlot(data=linexCoeffsData, aes(a_0, c_t), facet_formula=energy~Source, alpha=0.05) +
-    scale_x_continuous(breaks=c(0.6, 0.8, 1.0)) +
-    labs(x=expression(a[0]), y=expression(c[t]))
-@
-
-<<LINEX_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=4, fig.height=4, fig.cap="UK LINEX fitted models.">>=
-linexFittedData <- subset(AllFitted, subset = model=="linex")
-spaghettiPlot(data=linexFittedData, facet_formula=energy~Source, level=spaghettiGraphLevel) +
-    scale_x_continuous(breaks=c(1960, 1980, 2000)) + 
-    labs(y="Indexed GDP (1960=1)")
+standardScatterPlot(data=linexCoeffsData,
+                    mapping=aes(x=a_0, y=c_t, color=Source),
+                    facet_formula=country~energy, alpha=0.05) +
+    scale_x_continuous(limits=c(0.0, 1.0), breaks=c(0.0, 0.5, 1.0)) +
+    scale_y_continuous(limits=c(-10.0, 10.0), breaks=c(10.0, -5.0, 0.0, 5.0, 10.0)) +
+    labs(x=expression(a[0]), y=expression(c[t])) +
+    guides(colour=guide_legend(override.aes = aes(alpha=1)))
+@
+
+<<LINEX_GDP_Spaghetti_Graphs_US, fig.pos="H", fig.align='center', fig.width=3, fig.height=2.5, fig.cap="US LINEX fitted models.">>=
+linexFittedDataUS <- subset(AllFitted, subset = model=="linex" & Country=="US")
+spaghettiPlot(data=linexFittedDataUS, facet_formula=Source~energy, level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1960=1)") +
+  scale_x_continuous(breaks=c(1960, 1980, 2000))
+@
+
+<<LINEX_GDP_Spaghetti_Graphs_UK, fig.pos="H", fig.align='center', fig.width=3, fig.height=4.5, fig.cap="UK LINEX fitted models.">>=
+linexFittedDataUK <- subset(AllFitted, subset = model=="linex" & Country=="UK")
+spaghettiPlot(data=linexFittedDataUK, facet_formula=Source~energy, level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1960=1)") +
+  scale_x_continuous(breaks=c(1960, 1980, 2000))
+@
+
+<<LINEX_GDP_Spaghetti_Graphs_JP, fig.pos="H", fig.align='center', fig.width=3, fig.height=2.5, fig.cap="JP LINEX fitted models.">>=
+linexFittedDataJP <- subset(AllFitted, subset = model=="linex" & Country=="JP")
+spaghettiPlot(data=linexFittedDataJP, facet_formula=Source~energy, level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1960=1)") +
+  scale_x_continuous(breaks=c(1960, 1980, 2000))
+@
+
+<<LINEX_GDP_Spaghetti_Graphs_AT, fig.pos="H", fig.align='center', fig.width=4, fig.height=3.5, fig.cap="AT LINEX fitted models.">>=
+linexFittedDataAT <- subset(AllFitted, subset = model=="linex" & Country=="AT")
+spaghettiPlot(data=linexFittedDataAT, facet_formula=Source~energy, level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1960=1)") +
+  scale_x_continuous(breaks=c(1960, 1980, 2000))
+@
+
+<<LINEX_GDP_Spaghetti_Graphs_CN, fig.pos="H", fig.align='center', fig.width=4, fig.height=2.5, fig.cap="CN LINEX fitted models.">>=
+linexFittedDataCN <- subset(AllFitted, subset = model=="linex" & Country=="CN")
+spaghettiPlot(data=linexFittedDataCN, facet_formula=Source~energy, level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1960=1)") +
+  scale_x_continuous(breaks=c(1960, 1980, 2000))
 @

### 2014-09-21 Articles/Article_EcolEcon_2014/Paper2.Rnw
New code to make pre-econometric graphs.

@@
 
+# Add some pre-econometric data
+historicalData <- transform(historicalData, KPerGDP = iK/iGDP)
+historicalData <- transform(historicalData, LPerGDP = iL/iGDP)
+historicalData <- transform(historicalData, XpPerGDP = iXp/iGDP)
+historicalData <- transform(historicalData, XfPerGDP = iXf/iGDP)
+historicalData <- transform(historicalData, UPerGDP = iU/iGDP)
+
 # The working directory is set to the directory that contains this file.
@@
 # Load coefficients from all models in one large data frame
-REXS1960_Coeffs <- loadPostProcessedData(Source = "REXS1960", kind = "coeffs",dir = pp_path)
+REXS1960_Coeffs <- loadPostProcessedData(Source = "REXS1960", kind = "coeffs", dir = pp_path)
 IST_Coeffs <- loadPostProcessedData(Source = "IST", kind = "coeffs",dir = pp_path)
@@
 
-<<Historical_Data_1, fig.pos="H", fig.align='center', fig.width=6.6, fig.height=6, fig.cap="Historical data.", eval=TRUE>>=
+<<Historical_Data_1, fig.pos="H", fig.align='center', fig.width=6.6, fig.height=7, fig.cap="Historical data.">>=
 mdata <- melt(historicalData, 
@@
 
-Figure~\ref{fig:Historical_Data_2} shows the same data in a different form.
-
-<<Historical_Data_2, fig.pos="H", fig.align='center', fig.width=8, fig.height=6, fig.cap="Historical data.", eval=TRUE>>=
+Figure~\ref{fig:Historical_Data_2} shows the same data as Figure~\ref{fit:Historical_Data_1} 
+in a different form.
+
+<<Historical_Data_2, fig.pos="H", fig.align='center', fig.width=8, fig.height=7, fig.cap="Historical data.">>=
 historicalPlot(mdata, 
@@
   ylab("Indexed (1960=1 or 1978=1)")
+@
+
+Figure~\ref{fig:Preeconometric_1} shows a graph of factors of production relative to GDP.
+
+<<Preeconometric_1, fig.pos="H", fig.align='center', fig.width=8, fig.height=7, fig.cap="Pre-econometric data.">>=
+mdata2 <- melt(historicalData, 
+               measure.vars = c("KPerGDP", "LPerGDP", "XpPerGDP", "XfPerGDP", "UPerGDP"), 
+               variable.name = "variable",
+               value.name = "value")
+
+historicalPlot(mdata2, 
+               mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
+               facet_formula = Country ~ Source, 
+               line_types = c(1,5,2,6,4)) + 
+  xlab("") + 
+  ylab("Indexed Econometric Ratios (1960=1 or 1978=1)")
+@
+
+Figure~\ref{fig:Preeconometric_2} shows the same data as Figure~\ref{fig:Preeconometric_1} 
+in a different form.
+
+<<Preeconometric_2, fig.pos="H", fig.align='center', fig.width=8, fig.height=7, fig.cap="Pre-econometric data.">>=
+historicalPlot(mdata2, 
+               mapping=aes(x=Year, y=value, group=Source, linetype=Source), 
+               facet_formula = Country ~ variable, 
+               line_types = c(1,3,5)) + 
+  xlab("") + 
+  ylab("Indexed Econometric Ratios (1960=1 or 1978=1)")
 @
@@
 
-<<CD_lambda_theta_graph, fig.pos="H", fig.align='center', fig.width=6, fig.height=4.5, fig.cap="$\\lambda$ and $\\theta$ values for Cobb-Douglas resample models.">>=
+<<CD_lambda_theta_graph, fig.pos="H", fig.align='center', fig.width=6, fig.height=5.5, fig.cap="$\\lambda$ and $\\theta$ values for Cobb-Douglas resample models.">>=
 cdCoeffsData <- subset(AllCoeffs, subset = model=="cd")
@@
                     facet_formula=country~energy, alpha=0.05) +
-    scale_x_continuous(limits=c(0.8, 1.2), breaks=c(0.9, 1.0, 1.1)) +
-    scale_y_continuous(limits=c(-0.1, 0.2), breaks=c(0.0, 0.1, 0.2)) +    
+    scale_x_continuous(limits=c(0.9, 1.5), breaks=c(1.0, 1.2, 1.4)) +
+    scale_y_continuous(limits=c(-0.02, 0.05), breaks=c(0.0, 0.025, 0.05)) +    
     labs(x=expression(theta), y=expression(lambda)) +
@@
 
-<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=6, fig.height=4, fig.cap="Cobb-Douglas resample model parameters.">>=
+<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=6, fig.height=5, fig.cap="Cobb-Douglas resample model parameters.">>=
 standardTriPlot(data=cdCoeffsData, 
@@
 
-<<CD_GDP_Spaghetti_Graphs_US, fig.pos="H", fig.align='center', fig.width=4, fig.height=2.5, fig.cap="US Cobb-Douglas fitted models.">>=
+<<CD_GDP_Spaghetti_Graphs_US, fig.pos="H", fig.align='center', fig.width=4, fig.height=3.5, fig.cap="US Cobb-Douglas fitted models.">>=
 cdFittedDataUS <- subset(AllFitted, subset = model=="cd" & Country=="US")
@@
 spaghettiPlot(data=cdFittedDataAT, facet_formula=Source~energy, level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1960=1)") +
+  scale_x_continuous(breaks=c(1960, 1980, 2000))
+@
+
+<<CD_GDP_Spaghetti_Graphs_PT, fig.pos="H", fig.align='center', fig.width=5, fig.height=2.5, fig.cap="PT Cobb-Douglas fitted models.">>=
+cdFittedDataPT <- subset(AllFitted, subset = model=="cd" & Country=="PT")
+spaghettiPlot(data=cdFittedDataPT, facet_formula=Source~energy, level=spaghettiGraphLevel) +
     labs(y="Indexed GDP (1960=1)") +
@@
 
-<<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=4, fig.height=4, fig.cap="UK LINEX model (with energy) resampling results.">>=
+<<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=6, fig.height=6, fig.cap="LINEX model resampling results.">>=
 linexCoeffsData <- subset(AllCoeffs, subset = model=="linex")
@@
 
+<<LINEXq_Resample_Graph_PT, fig.pos="H", fig.align='center', fig.width=6, fig.height=2.5, fig.cap="LINEX model resampling results for PT.">>=
+linexCoeffsData <- subset(AllCoeffs, subset = model=="linex" & country=="PT")
+standardScatterPlot(data=linexCoeffsData,
+                    mapping=aes(x=a_0, y=c_t, color=Source),
+                    facet_formula=country~energy, alpha=0.05) +
+#     scale_x_continuous(limits=c(0.0, 1.0), breaks=c(0.0, 0.5, 1.0)) +
+#     scale_y_continuous(limits=c(-10.0, 10.0), breaks=c(10.0, -5.0, 0.0, 5.0, 10.0)) +
+    labs(x=expression(a[0]), y=expression(c[t])) +
+    guides(colour=guide_legend(override.aes = aes(alpha=1)))
+@
+
 <<LINEX_GDP_Spaghetti_Graphs_US, fig.pos="H", fig.align='center', fig.width=3, fig.height=2.5, fig.cap="US LINEX fitted models.">>=
@@
 spaghettiPlot(data=linexFittedDataAT, facet_formula=Source~energy, level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1960=1)") +
+  scale_x_continuous(breaks=c(1960, 1980, 2000))
+@
+
+<<LINEX_GDP_Spaghetti_Graphs_PT, fig.pos="H", fig.align='center', fig.width=4, fig.height=2.5, fig.cap="PT LINEX fitted models.">>=
+linexFittedDataPT <- subset(AllFitted, subset = model=="linex" & Country=="PT")
+spaghettiPlot(data=linexFittedDataPT, facet_formula=Source~energy, level=spaghettiGraphLevel) +
     labs(y="Indexed GDP (1960=1)") +

### 2014-09-21 Articles/Article_EcolEcon_2014/Paper2.Rnw
1978=1 --> 1970=1

@@
   xlab("") + 
-  ylab("Indexed (1960=1 or 1978=1)")
+  ylab("Indexed (1960=1 or 1970=1)")
 @
@@
   xlab("") + 
-  ylab("Indexed Econometric Ratios (1960=1 or 1978=1)")
+  ylab("Indexed Econometric Ratios (1960=1 or 1970=1)")
 @

### 2014-10-08 Articles/Article_JAE_2014/ZAGrowth_JAE.Rnw
Now using SUN data instead of Calvin data.

--- 2014-08-14 Articles/Article_JAE_2014/ZAGrowth_JAE.Rnw
@@
 )
-spaghettiGraphLevel <- 0.95 # Spaghetti graph bands will encompass 95% of the data.
+spaghettiGraphLevel <- 1.0 # Spaghetti graph bands will encompass 95% of the data.
 @
@@
 # Load historical data
-historicalData <- Calvin # From the EconData package
+historicalData <- SUN # From the EconData package
 
@@
 # Load coefficients from all models in one large data frame
-coeffs_df <- loadPostProcessedData(Source = "Calvin", kind = "coeffs", dir=pp_path)
+coeffs_df <- loadPostProcessedData(Source = "SUN", kind = "coeffs", dir=pp_path)
 coeffs_df_ZA <- subset(coeffs_df, subset=country=="ZA")
 # Load fitted data from all models in one large data frame
-fitted_df <- loadPostProcessedData(Source = "Calvin", kind = "fitted", dir=pp_path)
+fitted_df <- loadPostProcessedData(Source = "SUN", kind = "fitted", dir=pp_path)
 fitted_df_ZA <- subset(fitted_df, subset=Country=="ZA")
 # Load the original models.
-oModels <- loadPostProcessedData(Source = "Calvin", kind = "models", dir=pp_path)
-oModels_ZA <- oModels$Calvin$ZA
+oModels <- loadPostProcessedData(Source = "SUN", kind = "models", dir=pp_path)
+oModels_ZA <- oModels$SUN$ZA
 @
@@
               variable.name = "variable") 
-historicalPlot(mdata, 
+historicalPlot(data=mdata, 
+               mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
                facet_formula = Country ~ Source, 
-               lines_formula = variable + value ~ Year, 
-               line_types = c(1,2,3,4)) +
+               line_types = c(1,5,2,3)) +
   xlab("") +
-  ylab("Indexed (1980-1 or 1991=1")
+  ylab("Indexed (1973=1)")
 @
@@
 spaghettiPlot(data=cdFittedData_ZA, facet_formula=Country~energy, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1991=1)")
+    labs(y="Indexed GDP (1973=1)")
 @
@@
 spaghettiPlot(data=cesFittedData_ZA, facet_formula=Country~nestStrParen, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1991=1)")
+    labs(y="Indexed GDP (1973=1)")
 @
@@
 spaghettiPlot(data=linexFittedData_ZA, facet_formula=Country~energy, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1991=1)")
+    labs(y="Indexed GDP (1973=1)")
 @

### 2014-10-08 Articles/Article_JAE_2014/ZAGrowth_JAE.Rnw
Better definition of data source.

@@
 historicalData <- SUN # From the EconData package
+sourceOfData <- "SUN"
 
@@
 # Load coefficients from all models in one large data frame
-coeffs_df <- loadPostProcessedData(Source = "SUN", kind = "coeffs", dir=pp_path)
+coeffs_df <- loadPostProcessedData(Source = sourceOfData, kind = "coeffs", dir=pp_path)
 coeffs_df_ZA <- subset(coeffs_df, subset=country=="ZA")
 # Load fitted data from all models in one large data frame
-fitted_df <- loadPostProcessedData(Source = "SUN", kind = "fitted", dir=pp_path)
+fitted_df <- loadPostProcessedData(Source = sourceOfData, kind = "fitted", dir=pp_path)
 fitted_df_ZA <- subset(fitted_df, subset=Country=="ZA")
 # Load the original models.
-oModels <- loadPostProcessedData(Source = "SUN", kind = "models", dir=pp_path)
+oModels <- loadPostProcessedData(Source = sourceOfData, kind = "models", dir=pp_path)
 oModels_ZA <- oModels$SUN$ZA

### 2014-10-14 Articles/Article_EcolEcon_2014/Paper2.Rnw
Minor changes before sending to Julia.

@@
 
-Discuss economies here. EU15 and MX?
+Discuss economies here.
 
@@
 
-Figure~\ref{fig:Historical_Data_2} shows the same data as Figure~\ref{fit:Historical_Data_1} 
+Figure~\ref{fig:Historical_Data_2} shows the same data as Figure~\ref{fig:Historical_Data_1} 
 in a different form.
@@
 Section~\ref{sec:Prod_Func_Forms} has parameters which must be estimated (fitted)
-using data for each economy (see Sections~\ref{sec:Economy_Types} and~\ref{sec:Sources_of_Data}).
+using data for each economy (see Sections~\ref{sec:Economies} and~\ref{sec:Sources_of_Data}).
 We obtained parameter estimates by applying the method of least-squares to 
@@
 
-Figures~\ref{fig:CD_GDP_Spaghetti_Graph_US}--\ref{fig:CD_GDP_Spaghetti_Graph_CN} 
+Figures~\ref{fig:CD_GDP_Spaghetti_Graphs_US}--\ref{fig:CD_GDP_Spaghetti_Graphs_CN} 
 compare predictions 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Reproducible Research}
+% \section*{Reproducible Research}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 % \protect\url{https://github.com/MatthewHeun/Econ-Growth-R-Analysis}.
-
-%% The Appendices part is started with the command \appendix;
-%% appendix sections are then done as normal sections
-%% \appendix
-%% \section{}
-%% \label{}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\appendix
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Appendix}
-
-Include data tables here?
 
@@
 %% References with bibTeX database:
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{References}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%% The Appendices part is started with the command \appendix;
+%% appendix sections are then done as normal sections
+%% \appendix
+%% \section{}
+%% \label{}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\appendix
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Appendix}
+
+Include data tables here?
+
 \end{document}

### 2014-10-28 Articles/Article_EcolEcon_2014/Paper2.Rnw
Created residuals_df for residual plots.

@@
 AllFitted$energy <- relevelFactor(AllFitted$energy, levs=energyLevels)
+
+# Load models
+REXS1960_Models <- loadPostProcessedData(Source = "REXS1960", kind = "models", dir=pp_path)
+IST_Models <- loadPostProcessedData(Source = "IST", kind = "models", dir=pp_path)
+Leeds_Models <- loadPostProcessedData(Source = "Leeds", kind = "models", dir=pp_path)
+All_Models <- unlist(list(REXS1960_Models, IST_Models, Leeds_Models), recursive=FALSE)
+
+# The function to extract data from the models
+extract_data <- function(x, name) {
+  # Names are in the form Source.Country.modelType.factor_string
+  # Parse various pieces of name
+  name_pieces <- strsplit(name, split=".", fixed=TRUE)[[1]]
+  Source <- name_pieces[[1]]
+  Country <- name_pieces[[2]]
+  modelType <- name_pieces[[3]]
+  factorString <- name_pieces[[4]]
+  # Parse the factorString to get the energyType
+  energyType <- parseFactorString(factorString)$energyType
+  data.frame(year = (attr(x, which="data"))$Year, resid = resid(x), name=name, Source=Source, Country=Country,
+             modelType=modelType, energyType=energyType)
+}
+residual_data <- leaf_apply(All_Models, extract_data, class=c("CDEmodel", "cesEst", "LINEXModel"))
+# Bind these all in a data frame. 
+residuals_df <- do.call(rbind, residual_data)
 @
@@
 
+<<CD_Residual_Plot, fig.pos="H", fig.align='center', fig.width=4, fig.height=2.5, fig.cap="Cobb-Douglas Residual Plots.">>=
+# Use residuals_df to make a graph.
+
+@
+
 %++++++++++++++++++++++++++++++
@@
 
-Figure~\ref{fig:LINEX_Spaghetti_Graph} compares LINEX model predictions to historical data.
+Figures~\ref{fig:LINEX_GDP_Spaghetti_Graphs_US}--\ref{fig:LINEX_GDP_Spaghetti_Graphs_CN} 
+compare LINEX model predictions to historical data.
 Again, historical data are shown as a black line, 
@@
 <<LINEX_abg_traj_graph_REXS_UK_U, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="UK LINEX trajectory for REXS with $u$.">>=
-REXS1960_Models <- loadPostProcessedData(Source = "REXS1960", kind = "models", dir=pp_path)
 triPlot(data=fortify(REXS1960_Models$REXS1960$UK$linex$`iK+iL+iU`), grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1960")
@@
 <<LINEX_abg_traj_graph_IST_UK_U, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="UK LINEX trajectory for IST with $u$.">>=
-IST_Models <- loadPostProcessedData(Source = "IST", kind = "models", dir=pp_path)
 triPlot(data=fortify(IST_Models$IST$UK$linex$`iK+iL+iU`), grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1960")
@@
 <<LINEX_abg_traj_graph_Leeds_UK_U, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="UK LINEX trajectory for Leeds with $u$.">>=
-Leeds_Models <- loadPostProcessedData(Source = "Leeds", kind = "models", dir=pp_path)
 triPlot(data=fortify(Leeds_Models$Leeds$UK$linex$`iK+iL+iU`), grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1960")

### 2014-10-28 Articles/Article_EcolEcon_2014/Paper2.Rnw
Now including a residual plot for CD models.

@@
 REXS1960_Coeffs <- loadPostProcessedData(Source = "REXS1960", kind = "coeffs", dir = pp_path)
-IST_Coeffs <- loadPostProcessedData(Source = "IST", kind = "coeffs",dir = pp_path)
+IST_Coeffs <- loadPostProcessedData(Source = "IST", kind = "coeffs", dir = pp_path)
 Leeds_Coeffs <- loadPostProcessedData(Source = "Leeds", kind = "coeffs", dir = pp_path)
@@
 Leeds_Models <- loadPostProcessedData(Source = "Leeds", kind = "models", dir=pp_path)
-All_Models <- unlist(list(REXS1960_Models, IST_Models, Leeds_Models), recursive=FALSE)
-
+AllModels <- unlist(list(REXS1960_Models, IST_Models, Leeds_Models), recursive=FALSE)
 # The function to extract data from the models
@@
 }
-residual_data <- leaf_apply(All_Models, extract_data, class=c("CDEmodel", "cesEst", "LINEXModel"))
+residual_data <- leaf_apply(AllModels, extract_data, class=c("CDEmodel", "cesEst", "LINEXModel"))
 # Bind these all in a data frame. 
 residuals_df <- do.call(rbind, residual_data)
+# Re-order the factors as desired for our graphs.
+residuals_df$Source <- as.factor(
+  replace(as.character(residuals_df$Source), which(residuals_df$Source=="REXS1960"), "REXS"))
+residuals_df$Source <- relevelFactor(residuals_df$Source, levs = c("REXS", "IST", "Leeds"))
+residuals_df$energyType <- as.factor(
+  replace(as.character(residuals_df$energyType), which(is.na(residuals_df$energyType)), "none"))
+residuals_df$energyType <- relevelFactor(as.factor(residuals_df$energyType), levs = energyLevels)
 @
@@
 
-<<CD_Residual_Plot, fig.pos="H", fig.align='center', fig.width=4, fig.height=2.5, fig.cap="Cobb-Douglas Residual Plots.">>=
+<<CD_Residual_Plot, fig.pos="H", fig.align='center', fig.width=6, fig.height=6, fig.cap="Cobb-Douglas Residual Plots.">>=
 # Use residuals_df to make a graph.
-
+cd_residuals_df <- subset(residuals_df, subset = modelType=="cd")
+ggplot(data=cd_residuals_df, aes(x=year, y=resid, color=Source)) + 
+  geom_point(size = 1.0) +
+  facet_grid(Country ~ energyType) +
+  labs(x = "", y = "Residuals") + 
+  xy_theme()
 @

### 2014-10-31 Articles/Article_EcolEcon_2014/Paper2.Rnw
Now includes LINEX residual plot.

@@
 }
-residual_data <- leaf_apply(AllModels, extract_data, class=c("CDEmodel", "cesEst", "LINEXModel"))
+residual_data <- leaf_apply(AllModels, extract_data, class=c("CDEmodel", "cesEst", "LINEXmodel"))
 # Bind these all in a data frame. 
@@
 
+<<LINEX_Residual_Plot, fig.pos="H", fig.align='center', fig.width=5, fig.height=6, fig.cap="LINEX Residual Plots.">>=
+# Use residuals_df to make a graph.
+linex_residuals_df <- subset(residuals_df, subset = modelType=="linex")
+ggplot(data=linex_residuals_df, aes(x=year, y=resid, color=Source)) + 
+  geom_point(size = 1.0) +
+  facet_grid(Country ~ energyType) +
+  labs(x = "", y = "Residuals") + 
+  scale_x_continuous(breaks=c(1960, 1980, 2000)) + 
+  scale_y_continuous(limits=c(-0.3, 0.2)) +
+  xy_theme()
+@
+
 The LINEX model coefficients $a_0$ and $c_t$ imply time-dependent

### 2014-11-02 Articles/Article_JAE_2014/Education Investigation.Rmd
Beginning Education Investigation.Rmd.

---
title: "Education Investigation"
author: "MK Heun"
date: "November 2, 2014"
output: pdf_document
---

```{r Setup, echo=FALSE, message=FALSE, warning=FALSE}
require(EconData)
require(EconModels)
require(ggplot2)
```

This is a study of the effects of education on the estimation of parameters for South African growth.

Data
----------------------------------------------------------------
The following graph shows historical data, indexed to 1973.

```{r HistoricalData}
historicalData <- SUN
```

Formal Education Only
----------------------------------------------------------------
We begin by fitting GDP to the historical capital (K) and labor (L) data, using formal labor data only.

```{r}
summary(cars)
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2014-11-03 Articles/Article_JAE_2014/Education Investigation.Rmd
Additional results on the education study.

@@
 ---
-title: "Education Investigation"
-author: "MK Heun"
+title: "The Effect of Education Adjustment on Parameter Estimates 
+for Cobb-Douglas Economic Growth in South Africa"
+author: "Matthew Kuperus Heun"
 date: "November 2, 2014"
@@
 require(ggplot2)
-```
-
-This is a study of the effects of education on the estimation of parameters for South African growth.
-
-Data
-----------------------------------------------------------------
-The following graph shows historical data, indexed to 1973.
-
-```{r HistoricalData}
+require(reshape2)
 historicalData <- SUN
@@
 
-Formal Education Only
+This is a study of the effects of education on the estimation of parameters for South African economic growth.
+
+Historical Data
 ----------------------------------------------------------------
-We begin by fitting GDP to the historical capital (K) and labor (L) data, using formal labor data only.
+The following figure shows historical data for GDP, capital stock, and thermal energy data, indexed to 1973.
 
-```{r}
-summary(cars)
+```{r HistoricalData, warning=FALSE, fig.cap="Historical GDP, capital stock, and thermal energy data."}
+mdata <- melt(historicalData, 
+              measure.vars = c("iGDP", "iK", "iQp"), 
+              variable.name = "variable",
+              value.name = "value")
+mapping <- aes(x=Year, y=value, group=variable, linetype=variable)
+ggplot(mdata, mapping=mapping) + 
+  geom_line(mapping) +
+  xy_theme() +
+  xlab("") + 
+  ylab("Indexed (1973=1)")
 ```
 
-You can also embed plots, for example:
+The following figure shows four different time series for labor.
+$iLf$ is indexed formal labor.
+$iLfe$ is indexed formal labor adjusted for education.
+$iLfi$ is indexed formal plus informal labor.
+$ilfie$ is indexed formal plus informal labor adjusted for education.
+Adjustment for education is performed as described in du Plessis and Smit. (2007)
 
-```{r, echo=FALSE}
-plot(cars)
+```{r HistoricalDataLabor, warning=FALSE, fig.cap="Historical labor time series."}
+mdata_labor <- melt(historicalData, 
+                    measure.vars = c("iLf", "iLfe", "iLfi", "iLfie"), 
+                    variable.name = "variable",
+                    value.name = "value")
+mapping <- aes(x=Year, y=value, group=variable, linetype=variable)
+ggplot(mdata_labor, mapping=mapping) + 
+  geom_line(mapping) +
+  xy_theme() +
+  xlab("") + 
+  ylab("Indexed (1973=1)") +
+  scale_y_continuous(breaks=c(1, 1.5, 2.0))
 ```
 
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+Note that the effect of education is not observed until 1986, 
+because the average education level is given as 4.8 years
+from 1970--1985.
+
+du Plessis and Smit (2007, p. 681) report that 
+capital income share is 0.43
+and wage income share is 0.57
+for the time period 1985--1994.
+For 1995--2004, 
+capital income share is 0.46
+and wage income share is 0.54
+
+Cobb-Douglas Equation
+----------------------------------------------------------------
+We fit a Cobb-Douglas equation of the form
+
+\begin{equation}
+  GDP = \mathrm{e}^{\lambda t} k^\alpha l^\beta
+\end{equation}
+
+under the constraint $\alpha + \beta = 1$ to ensure constant returns to scale.
+The GDP and capital stock time series are fixed.
+However, we will try four different labor time series.
+
+Without Education Adjustment
+----------------------------------------------------------------
+We begin by fitting GDP to the historical capital ($iK$) and formal sector labor ($iLf$) data.
+
+```{r Formal}
+naturalCoef(cdModel(formula = iGDP ~ iK + iLf + iYear, 
+                    data = historicalData, constrained = TRUE))
+```
+
+Next, fit using formal and informal labor data ($iLfi$)
+```{r FormalPlusInformal}
+naturalCoef(cdModel(formula = iGDP ~ iK + iLfi + iYear, 
+                    data = historicalData, constrained = TRUE))
+```
+
+Without adjusting for education, 
+both formal and formal+informal labor time series produce 
+$\alpha = 0$
+and $\beta = 1$.
+The Solow residual ($\lambda$) is on the order of 1.5 \%/year.
+
+With Education Adjustment
+----------------------------------------------------------------
+Now we fit using education-adjusted formal sector labor data ($iLfe$).
+```{r FormalPlusEducation}
+naturalCoef(cdModel(formula = iGDP ~ iK + iLfe + iYear, 
+                    data = historicalData, constrained = TRUE))
+```
+
+Finally, fit using education-adjusted formal and informal labor data ($iLfie$)
+```{r FormalPlusInformalPlueEducation}
+naturalCoef(cdModel(formula = iGDP ~ iK + iLfie + iYear, 
+                    data = historicalData, constrained = TRUE))
+```
+
+When adjustment is made for education, we obtain significantly different 
+coefficients for capital ($\alpha$) and labor ($\beta$), namely
+$\alpha \approx 0.44$
+and $\beta \approx 0.56$.
+The Solow residual is $\lambda \approx 0.5$ \%/year.
+
+Analysis
+----------------------------------------------------------------
+The education-adjusted coefficient estimates above 
+($\alpha \approx 0.44$
+and $\beta \approx 0.56$) 
+align closely with income shares as reported in du Plessis and Smit. (2007, p. 681)
+
+The fit to historical data is slightly better without education adjustment
+than with education adjustment
+($sse = 0.18$ without adjusting for education 
+vs. $sse = 0.27$ with education adjustment).
+However, the Solow residual is smaller when adjusting for education
+($\lambda \approx 1.5$ \%/year without adjusting for education
+vs. $\lambda \approx 0.5$ \%/year after adjusting for education).
+
+Furthermore $sse$ improves when the informal labor sector is included,
+regardless of whether labor is adjusted for education.
+
+The improvement in Solow residual 
+argues strongly in favor of including both education and the informal labor sector.
+
+It appears that adjusting for education 
+will be an important feature of these analyses moving forward.

### 2014-11-04 Articles/Article_JAE_2014/Education Investigation.Rmd
Added energy calcs.

@@
 mdata <- melt(historicalData, 
-              measure.vars = c("iGDP", "iK", "iQp"), 
+              measure.vars = c("iGDP", "iK", "iQp", "iQf"), 
               variable.name = "variable",
@@
 Finally, fit using education-adjusted formal and informal labor data ($iLfie$)
-```{r FormalPlusInformalPlueEducation}
+```{r FormalPlusInformalPlusEducation}
 naturalCoef(cdModel(formula = iGDP ~ iK + iLfie + iYear, 
@@
 will be an important feature of these analyses moving forward.
+
+Effect of Energy
+----------------------------------------------------------------
+
+Now, we use the Cobb-Douglas equation with an energy term.
+
+\begin{equation}
+  GDP = \mathrm{e}^{\lambda t} k^\alpha l^\beta e^\gamma
+\end{equation}
+
+under the constraint $\alpha + \beta + \gamma = 1$ to ensure constant returns to scale.
+
+First, we fit using education-adjusted formal and informal labor data ($iLfie$)
+and primary thermal energy ($iQp$).
+```{r FormalPlusInformalPlusEducationWithPrimaryEnergy}
+res <- naturalCoef(cdModel(formula = iGDP ~ iK + iLfie + iQp + iYear, 
+                           data = historicalData, constrained = TRUE))
+row.names(res)<-NULL
+res
+```
+
+Next, we fit using education-adjusted formal and informal labor data ($iLfie$)
+and final thermal energy ($iQf$).
+```{r FormalPlusInformalPlusEducationWithFinalEnergy}
+res <- naturalCoef(cdModel(formula = iGDP ~ iK + iLfie + iQf + iYear, 
+                           data = historicalData, constrained = TRUE))
+row.names(res)<-NULL
+res
+```

### 2014-11-07 Articles/Article_EcolEcon_2014/Paper2.Rnw
Now making lambda time series graphs.

@@
 require(plyr)
+require(dplyr) # Load in this order or the mutate and arrange functions will not work as desired.
 # Provides access to data melting. 
@@
 require(knitr)
+require(mosaic)
 
@@
 
-<<data, include=FALSE, eval=TRUE>>=
+<<data, include=FALSE>>=
 # Load historical data
@@
 
+The term $\mathrm{e}^{\lambda (t-t_0)}$ is known as the Solow Residual ($A$). 
+Assuming that parameters $\theta$, $\alpha$, and $\beta$ are known,
+we can estimate the value of $\lambda$ as follows.
+First, assume constant returns to scale such that $\gamma = 1 - \alpha - \beta$.
+Then, take the natural logarithm ($\ln$) of Equation~\ref{eq:CD} to obtain
+%
+\begin{equation} \label{eq:lnCD}
+  \ln y = \ln \theta + \ln A + \alpha \ln k + \beta \ln l + (1 - \alpha - \beta) \ln e \;.
+\end{equation}
+%
+By taking the derivative of Equation~\ref{eq:lnCD} with respect to time ($t$) 
+and noting that model parameters $\theta$ and $\alpha$ are 
+constant with respect to time, we obtain
+%
+\begin{equation} \label{eq:ddtlnCD}
+  \frac{1}{y}\frac{\mathrm{d}y}{\mathrm{d}t} 
+      = \frac{1}{A}\frac{\mathrm{d}A}{\mathrm{d}t} 
+      + \alpha \frac{1}{k}\frac{\mathrm{d}k}{\mathrm{d}t} 
+      + \beta \frac{1}{l}\frac{\mathrm{d}l}{\mathrm{d}t} 
+      + (1 - \alpha - \beta) \frac{1}{e}\frac{\mathrm{d}e}{\mathrm{d}t} \;.
+\end{equation}
+%
+Solving for the Solow Residual term gives
+%
+\begin{equation} \label{eq:solow_resid}
+  \frac{1}{A}\frac{\mathrm{d}A}{\mathrm{d}t} 
+      = \frac{1}{y}\frac{\mathrm{d}y}{\mathrm{d}t} 
+      - \left[
+              \alpha \frac{1}{k}\frac{\mathrm{d}k}{\mathrm{d}t} 
+              + \beta \frac{1}{l}\frac{\mathrm{d}l}{\mathrm{d}t} 
+              + (1 - \alpha - \beta) \frac{1}{e}\frac{\mathrm{d}e}{\mathrm{d}t} 
+        \right] \;.
+\end{equation}
+%
+Recognizing that $A \equiv \mathrm{e}^{\lambda (t-t_0)}$ gives
+%
+\begin{equation}
+  \frac{1}{A}\frac{\mathrm{d}A}{\mathrm{d}t} 
+    = \frac{1}{\mathrm{e}^{\lambda (t-t_0)}} \; \lambda \mathrm{e}^{\lambda (t-t_0)}
+    = \lambda \; ,
+\end{equation}
+%
+which can be substituted into Equation~\ref{eq:solow_resid} to find
+%
+\begin{equation} \label{eq:lambda}
+  \lambda 
+    = \frac{1}{y}\frac{\mathrm{d}y}{\mathrm{d}t} 
+    - \left[
+              \alpha \frac{1}{k}\frac{\mathrm{d}k}{\mathrm{d}t} 
+              + \beta \frac{1}{l}\frac{\mathrm{d}l}{\mathrm{d}t} 
+              + (1 - \alpha - \beta) \frac{1}{e}\frac{\mathrm{d}e}{\mathrm{d}t} 
+      \right] \;.
+\end{equation}
+%
+Equation~\ref{eq:lambda} applies for any instant in time.
+
+If we approximate derivatives in Equation~\ref{eq:lambda} with forward differences
+between times $i$ and $j$, we find
+%
+\begin{equation} \label{eq:lambdaij}
+  \lambda_{i,j}
+    \approx \frac{1}{y_i}\frac{y_j - y_i}{t_j - t_i} 
+    - \left[
+            \alpha \frac{1}{k_i}\frac{k_j - k_i}{t_j - t_i} 
+            + \beta \frac{1}{l_i}\frac{l_j - l_i}{t_j - t_i} 
+            + (1 - \alpha - \beta) \frac{1}{e_i}\frac{e_j - e_i}{t_j - t_i} 
+      \right] \;,
+\end{equation}
+% 
+where $\lambda_{i,j}$ approximates the true, instantaneous value of $\lambda$
+between times $i$ and $j$.
+
+Interestingly, 
+%
+\begin{equation}
+  \lambda_{1,n}
+    \neq \sum_{i=2}^{n} \lambda_{i,i-1}  \;.
+\end{equation}
+% 
+Rather,
+%
+\begin{equation} \label{eq:lambda1n}
+  \lambda_{1,n}
+    \approx \frac{1}{y_1}\frac{y_n - y_1}{t_n - t_1} 
+      - \left[ 
+            \alpha \frac{1}{k_1}\frac{k_n - k_1}{t_n - t_1} 
+            + \beta \frac{1}{l_1}\frac{l_n - l_1}{t_n - t_1} 
+            + (1 - \alpha - \beta) \frac{1}{e_1}\frac{e_n - e_1}{t_n - t_1} 
+      \right] \; ,
+\end{equation}
+% 
+which will become increasingly inaccurate over large time spans,
+because $y_1$, $k_1$, $l_1$, and $e_1$ will be less representative
+of the average value of $y$, $k$, $l$, and $e$ in the time span, respectively.
+This suggests that an averaging approach such as
+%
+\begin{equation}
+  \lambda_{1,n}
+    \approx \frac{\sum_{i=2}^{n} \lambda_{i,i-1}}{n-1}
+\end{equation}
+%
+is a better approximation of Equation~\ref{eq:lambda1n},
+which is, itself, an approximation of the true value of $\lambda$ 
+given by Equation~\ref{eq:lambda}.
+
 %------------------------------
@@
 
+Given the estimates for $\alpha$, $\beta$, and $\gamma$ for the Cobb-Douglas model,
+we can estimate values for $\lambda$ on a year-by-year basis using Equation~\ref{eq:lambdaij}.
+The results are shown in the Figure~\ref{fig:CD_lambda_time_series}.
+
+<<CD_lambda_time_series, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap='Solow residual time series.'>>=
+# Add a bogus "none" column that we can use for the no-energy case
+m_histData <- historicalData
+m_histData$none <- 1.0
+# Melt the the historical data to put energy in one column
+m_histData <- melt(select(m_histData, Year, iGDP, iK, iL, iXp, iXf, iU, none, Country, Source), 
+                   measure.vars = c("none", "iXp", "iXf", "iU"),
+                   variable.name = "energyType",
+                   value.name = "iE")
+# Calculate finite difference approximations of time derivatives for output and all factors of production
+fd <- m_histData %>% group_by(Source, Country, energyType) %>% arrange(Year) %>% 
+  mutate(dydt = ediff(iGDP, pad="tail") / ediff(Year, pad="tail")) %>%
+  mutate(dkdt = ediff(iK, pad="tail") / ediff(Year, pad="tail")) %>%
+  mutate(dldt = ediff(iL, pad="tail") / ediff(Year, pad="tail")) %>%
+  mutate(dedt = ediff(iE, pad="tail") / ediff(Year, pad="tail"))
+
+origCDKLCoeffs <- subset(AllCoeffs, method=="orig" & model=="cd")
+origCDKLCoeffs <- origCDKLCoeffs %>% select(method, country, Source, nestStr, energy, lambda, alpha, beta, gamma)
+# Change name of Source REXS to REXS1960 and relevel to conform to information in fdlambda.
+origCDKLCoeffs$Source <- as.character(origCDKLCoeffs$Source)
+origCDKLCoeffs$Source <- replace(origCDKLCoeffs$Source, which(origCDKLCoeffs$Source=="REXS"), "REXS1960")
+origCDKLCoeffs$Source <- as.factor(origCDKLCoeffs$Source)
+origCDKLCoeffs$Source <- relevelFactor(origCDKLCoeffs$Source, levs = c("REXS1960", "IST", "Leeds"))
+
+# Fill new columns in the fd data frame with 
+# lambda, alpha, beta, and gamma values from the parameter estimation process.
+# lambda, alpha, beta, and gamma values for the orig fits are in the origCDKLCoeffs data frame.
+# Using the hint at 
+# http://stackoverflow.com/questions/15059076/
+# r-how-to-call-apply-like-function-on-each-row-of-dataframe-with-multiple-argum
+labg <- apply(fd[ , c('Country', 'Source', 'energyType')], 1, function(x){
+    row <- as.data.frame(subset(origCDKLCoeffs, 
+                                country==x["Country"] & Source==x["Source"] & energy==x["energyType"]))
+    abg <- subset(row, select=c(lambda, alpha, beta, gamma))
+    if (nrow(abg) < 1){ abg[1, ] <- NA }
+    return(abg)
+  })
+cols <- do.call(rbind, labg)
+fd <- cbind(fd, cols)
+
+# Now calculate lambda by finite difference for every year to make a time series
+fdlambda <- mutate(fd, lambda_diff = 1/iGDP*dydt - (alpha/iK*dkdt + beta/iL*dldt + gamma/iE*dedt))
+
+# Create a time series graph of the lambda_diff values
+ggplot(data=fdlambda, aes(x=Year, y=lambda_diff, color=Source)) + 
+  geom_point(size = 1.0) +
+  facet_grid(Country ~ energyType) +
+  labs(x = "", y = expression(lambda)) + 
+#   scale_y_continuous(limits=c(-0.1, 0.1)) +
+  xy_theme()
+@
+
 <<CD_GDP_Spaghetti_Graphs_US, fig.pos="H", fig.align='center', fig.width=4, fig.height=3.5, fig.cap="US Cobb-Douglas fitted models.">>=

### 2014-11-10 Articles/Article_EnerEcon_2014/EconGrowth3.Rnw
Text of Energy Econ paper now reflects PWT source.

@@
 We measure economic output ($Y$) by gross domestic product (GDP). 
-GDP data in real 2005 U.S. dollars for developed countries (1980--2011) 
-and all other countries (1991--2011) was obtained from 
-the World Bank's Global Economic Prospects (GEP) database 
-\citep{WorldBankGEP:2013a}.
+GDP data in real 2005 U.S. dollars for all countries was obtained from the
+RGDP$^{\mathrm{NA}}$ time series of the Penn World Table.~\citep{Feenstra:2013aa}
 
@@
 Gross capital stock in real 2005 U.S. dollars 
-for developed countries (1980--2011) and 
-all other countries (1991--2011) was obtained from 
-the World Bank's Global Economic Prospects (GEP) database 
-\citep{WorldBankGEP:2013a}.
+for all countries was obtained from the
+RK$^{\mathrm{NA}}$ time series of the Penn World Table.~\citep{Feenstra:2013aa}
 
@@
 
-Total employment and average hours worked per worker per year 
-for the developed nations (United States, United Kingdom, and Japan) 
-for 1980--2011 were obtained from the United States 
-\citet[Tables 6 and 7]{BLS:2013a}. Total hours worked per year was 
-calculated by multiplying total employment by average hours worked 
-per worker per year.
-
-The World Bank's World Development Indicators database 
-\citep{WorldBankWDI:2013a} provides the employment to population 
-ratio for people fifteen and older, total population, and a percentage 
-of people under fifteen for other economies 
-(China, South Africa, 
-Saudi Arabia, Iran, 
-Tanzania, and Zambia) 
-for 1991--2011. 
-The population 
-of people under fifteen years of age was subtracted from total population 
-to calculate the population of people fifteen and older. 
-Total employment was calculated by multiplying the employment to 
-population ratio of people fifteen and older by the population 
-of people fifteen and older.
+Total employment (persons engaged) for all countries
+was obtained from the 
+EMP time series of the Penn World Table.~\citep{Feenstra:2013aa}
+The EMP time series was used as the labor factor of production 
+for CN, ZA, SA, IR, TZ, and ZM.
+For the developed nations (US, UK, and JP), 
+average hours worked per worker per year 
+was obtained from the AVH time series of the Penn World Table.~\citep{Feenstra:2013aa}
+The product of EMP and AVH was used as the labor factor of production 
+for the developed nations.
 

### 2014-11-12 Articles/Article_EcolEcon_2014/Paper2.Rnw
Now including graphs of %y explained by lambda.

@@
 
-The term $\mathrm{e}^{\lambda (t-t_0)}$ is known as the Solow Residual ($A$). 
-Assuming that parameters $\theta$, $\alpha$, and $\beta$ are known,
+The term $\mathrm{e}^{\lambda (t-t_0)}$ is known as total factor productivity~($A$),
+and $\lambda$ is the Solow residual. 
+Assuming that parameters $\theta$, $\alpha$, and $\beta$ are known from parameter estimation,
 we can estimate the value of $\lambda$ as follows.
@@
 By taking the derivative of Equation~\ref{eq:lnCD} with respect to time ($t$) 
-and noting that model parameters $\theta$ and $\alpha$ are 
+and noting that model parameters $\theta$, $\alpha$, and $\beta$ are 
 constant with respect to time, we obtain
@@
 
-<<CD_lambda_time_series, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap='Solow residual time series.'>>=
+<<CD_finite_diff_calcs, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap='Solow residual time series.'>>=
 # Add a bogus "none" column that we can use for the no-energy case
@@
 # Now calculate lambda by finite difference for every year to make a time series
-fdlambda <- mutate(fd, lambda_diff = 1/iGDP*dydt - (alpha/iK*dkdt + beta/iL*dldt + gamma/iE*dedt))
-
+fdlambda <- mutate(fd, lambda_diff = dydt/iGDP - (alpha/iK*dkdt + beta/iL*dldt + gamma/iE*dedt))
+
+# Calculate the fraction of GDP growth in each year that is explained by the solow residual
+fdlambda <- mutate(fdlambda, solowFrac = lambda_diff / (dydt/iGDP))
+
+# Calculate average values for lambda and solowFrac
+avgs <- fdlambda %>% 
+  group_by(Source, Country, energyType) %>% 
+  summarise(
+    avg.lambda_diff = mean(lambda_diff, na.rm=TRUE),
+    avg.solowFrac = mean(solowFrac, na.rm=TRUE)
+    )
+
+@
+
+<<CD_lambda_time_series, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap='Solow residual time series.'>>=
 # Create a time series graph of the lambda_diff values
@@
 #   scale_y_continuous(limits=c(-0.1, 0.1)) +
+  xy_theme()
+@
+
+<<CD_solowPerc_time_series, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap='Solow residual time series.'>>=
+# Create a time series graph of the solowPerc values
+ggplot(data=fdlambda, aes(x=Year, y=solowFrac, color=Source)) + 
+  geom_point(size = 1.0) +
+  facet_grid(Country ~ energyType) +
+  labs(x = "", y = "Fraction of GDP growth explained by Solow residual") + 
+  scale_y_continuous(limits=c(-0.5, 2)) +
   xy_theme()

### 2014-11-18 Workflow/Workflow.Rmd
Noted that the script now connects to dahl. Used to connect to fs1, but there were times when new files would not propagate across the cluster before the download request was made. This caused some confusion.
Added notes about the r-versions script.

@@
 ### Create the batch script
+* Run the script `r-versions` on `dahl` to see which nodes are operational and which nodes have a working version of `R`.
 * Create the file `Scripts/<Source>_batch.bash` file.
@@
     + Distribute the work over the nodes in a way that makes sense.
+    + Avoid non-working nodes or nodes that have an out-of-date version of `R` as revealed by `r-versions`.
 * Push the `<Source>_batch.bash` file to GitHub.
@@
 the environment. 
+* The `DownloadPostProcessed.bash` script connects to `dahl.calvin.edu` (`node-00`). 
+That choice was made to minimize the risk that a file won't prpogate across the cluster 
+file system prior to the download request.
 

### 2014-11-18 Articles/Article_JAE_2014/ZAGrowth_JAE.Rnw
Added require(plyr).

@@
 require(knitr)
+require(plyr)
 require(dplyr)
@@
 standardScatterPlot(data=cdCoeffsData_ZA, mapping=aes(scale, lambda), facet_formula=country~energy, alpha=0.05) +
-    scale_x_continuous(breaks=c(0.95, 1.0, 1.05)) +
-    scale_y_continuous(breaks=c(0, 0.002, 0.004, 0.006, 0.008)) +    
+#     scale_x_continuous(breaks=c(0.95, 1.0, 1.05)) +
+#     scale_y_continuous(breaks=c(0, 0.002, 0.004, 0.006, 0.008)) +    
     labs(x=expression(theta), y=expression(lambda))

### 2014-11-20 Articles/Article_EcolEcon_2014/Paper2.Rnw
Removed all require(plyr). Want to avoid conflicts with dplyr.

@@
 require(ggplot2)
-require(plyr)
 require(dplyr) # Load in this order or the mutate and arrange functions will not work as desired.
@@
 # Load historical data
-historicalData <- rbind.fill(REXS1960, IST, Leeds) # From the EconData package
+historicalData <- plyr::rbind.fill(REXS1960, IST, Leeds) # From the EconData package
 

### 2014-11-20 Articles/Article_EnerEcon_2014/EconGrowth3.Rnw
Removed all require(plyr). Want to avoid conflicts with dplyr.

@@
 require(nlmrt)
-# require(micEconCES)
-require(plyr)
 require(dplyr)

### 2014-11-20 Articles/Article_JAE_2014/ZAGrowth_JAE.Rnw
Removed all require(plyr). Want to avoid conflicts with dplyr.

@@
 require(knitr)
-require(plyr)
 require(dplyr)

### 2014-11-20 Scripts/OrigModels.R

@@ -17,7 +17,6 @@
 # 
 # Note, too, that <Source>_Models is an object in the EconData package.
 
-require(plyr)  # for rbind.fill()
 require(EconModels)
 require(EconData)
 require(optparse)

### 2014-11-20 Testing/FunkySpaghetti/FunkySpaghetti.R

@@ -1,6 +1,5 @@
 require(EconData)
 require(EconModels)
-require(plyr)
 require(ggplot2)
 
 # setwd() to the location of this file.

### 2014-11-20 Testing/ResamplingTesting.R

@@ -1,6 +1,5 @@
 
 require(EconModels2)
-require(plyr)  # for rbind.fill()
 
 All <- read.table("data/AllData.txt", header=TRUE)
 Countries <- unique(All$Country)
@@ -89,6 +88,6 @@ for (country in Countries) {
   }
 }
 
-coefs2 <- do.call(rbind.fill, coefs)
+coefs2 <- do.call(plyr::rbind.fill, coefs)
 
 

### 2014-11-28 Articles/Prod Func Primer/ProdFuncPrimer.tex
New ProdFuncPrimer files.

--- 2014-11-07 Articles/Article_EcolEcon_2014/Paper2.Rnw
@@
-% This article has been prepared for publication in Ecological Economics in RStudio with knitr.
-% According to http://www.elsevier.com/author-schemas/the-elsarticle-latex-document-class, we should be using the
-% elsarticle.cls file.
-% According to http://cdn.elsevier.com/assets/pdf_file/0006/109392/journal_refstyles.pdf, we should be using
-% elsarticle-template-2-harv.tex as the template for the text.
-% Furthermore, we should be using model2-names.bst for the bibliographic references.
-% The approach here is to load the frontmatter and backmatter from elsarticle-template-2-harv.tex
-% both ahead of and behind the text for our paper.
-% -- Matthew Kuperus Heun, 2014-08-01
-
 %% This is file `elsarticle-template-2-harv.tex',
@@
 \usepackage{wrapfig}    % Allows wrapping of text around figures
-\usepackage{soul}       % Provides strikethrough text
 \usepackage{float}      % Allows precise positioning of tables and figures within the text
@@
 \usepackage{hyperref}   % To create hyperlinks in the paper
-\usepackage{microtype}  % produces hanging punctuation and beautiful type
+\usepackage{microtype}  % Produces hanging punctuation and beautiful type
+\usepackage{booktabs}   % For nice tables
 
@@
 
-\journal{Ecological Economics}
+\journal{}
 
 \begin{document}
-
-<<setup, echo=FALSE, message=FALSE, eval=TRUE>>=
-require(EconModels)
-require(EconData)
-require(ggplot2)
-require(plyr)
-require(dplyr) # Load in this order or the mutate and arrange functions will not work as desired.
-# Provides access to data melting. 
-# See http://cran.r-project.org/web/packages/reshape2/reshape2.pdf
-require(reshape2) 
-require(knitr)
-require(mosaic)
-
-opts_chunk$set(
-  # ********************************************************
-  eval=TRUE,
-  # ********************************************************
-  # tikz allows LaTeX code in graphical output. 
-  # E.g., "$y$" for a variable name in the legend for a graph.  
-  # dev='tikz',
-  tidy=FALSE,
-  comment=NA,
-  # Tells whether to cache output from chunks are saved. Cacheing saves time. 
-  # However, references to LaTeX tables DO NOT WORK if cacheing is turned on.
-  cache=FALSE,
-  warning=FALSE,  #Tells whether to show warnings in the output.
-  # Turns off messages for all chunks. 
-  # Set TRUE on an individual chunk to see it.
-  message=FALSE, 
-  # Tells whether to echo code for all chunks. 
-  # Set TRUE on an individual chunk to see its code.
-  echo=FALSE     
-)
-@
-
-<<constants, include=FALSE, eval=TRUE>>=
-spaghettiGraphLevel <- 1.0 # Spaghetti graph bands will encompass 95% of the data.
-@
-
-<<data, include=FALSE>>=
-# Load historical data
-historicalData <- rbind.fill(REXS1960, IST, Leeds) # From the EconData package
-
-# Add some pre-econometric data
-historicalData <- transform(historicalData, KPerGDP = iK/iGDP)
-historicalData <- transform(historicalData, LPerGDP = iL/iGDP)
-historicalData <- transform(historicalData, XpPerGDP = iXp/iGDP)
-historicalData <- transform(historicalData, XfPerGDP = iXf/iGDP)
-historicalData <- transform(historicalData, UPerGDP = iU/iGDP)
-
-# The working directory is set to the directory that contains this file.
-# To reach the post-processed data, we need to move 
-# up two levels and into the data_postprocessed directory.
-# So, in each of the loadPostProcessedData calls below, we use
-# dir = "../../data_postprocessed".
-pp_path <- file.path("..", "..", "data_postprocessed")
-
-# Load coefficients from all models in one large data frame
-REXS1960_Coeffs <- loadPostProcessedData(Source = "REXS1960", kind = "coeffs", dir = pp_path)
-IST_Coeffs <- loadPostProcessedData(Source = "IST", kind = "coeffs", dir = pp_path)
-Leeds_Coeffs <- loadPostProcessedData(Source = "Leeds", kind = "coeffs", dir = pp_path)
-AllCoeffs <- rbind(REXS1960_Coeffs, IST_Coeffs, Leeds_Coeffs)
-AllCoeffs$Source <- as.factor(replace(AllCoeffs$Source, which(AllCoeffs$Source=="REXS1960"), "REXS"))
-AllCoeffs$Source <- relevelFactor(AllCoeffs$Source, levs = c("REXS", "IST", "Leeds"))
-AllCoeffs$energy <- relevelFactor(AllCoeffs$energy, levs = energyLevels)
-# Load fitted data from all models in one large data frame
-REXS1960_Fitted <- loadPostProcessedData(Source = "REXS1960", kind = "fitted", dir = pp_path)
-IST_Fitted <- loadPostProcessedData(Source = "IST", kind = "fitted", dir = pp_path)
-Leeds_Fitted <- loadPostProcessedData(Source = "Leeds", kind = "fitted", dir = pp_path)
-AllFitted <- rbind(REXS1960_Fitted, IST_Fitted, Leeds_Fitted)
-AllFitted$Source <- replace(AllFitted$Source, which(AllFitted$Source=="REXS1960"), "REXS")
-AllFitted$Source <- relevelFactor(as.factor(AllFitted$Source), levs = c("REXS", "IST", "Leeds"))
-AllFitted$energy <- relevelFactor(AllFitted$energy, levs=energyLevels)
-
-# Load models
-REXS1960_Models <- loadPostProcessedData(Source = "REXS1960", kind = "models", dir=pp_path)
-IST_Models <- loadPostProcessedData(Source = "IST", kind = "models", dir=pp_path)
-Leeds_Models <- loadPostProcessedData(Source = "Leeds", kind = "models", dir=pp_path)
-AllModels <- unlist(list(REXS1960_Models, IST_Models, Leeds_Models), recursive=FALSE)
-# The function to extract data from the models
-extract_data <- function(x, name) {
-  # Names are in the form Source.Country.modelType.factor_string
-  # Parse various pieces of name
-  name_pieces <- strsplit(name, split=".", fixed=TRUE)[[1]]
-  Source <- name_pieces[[1]]
-  Country <- name_pieces[[2]]
-  modelType <- name_pieces[[3]]
-  factorString <- name_pieces[[4]]
-  # Parse the factorString to get the energyType
-  energyType <- parseFactorString(factorString)$energyType
-  data.frame(year = (attr(x, which="data"))$Year, resid = resid(x), name=name, Source=Source, Country=Country,
-             modelType=modelType, energyType=energyType)
-}
-residual_data <- leaf_apply(AllModels, extract_data, class=c("CDEmodel", "cesEst", "LINEXmodel"))
-# Bind these all in a data frame. 
-residuals_df <- do.call(rbind, residual_data)
-# Re-order the factors as desired for our graphs.
-residuals_df$Source <- as.factor(
-  replace(as.character(residuals_df$Source), which(residuals_df$Source=="REXS1960"), "REXS"))
-residuals_df$Source <- relevelFactor(residuals_df$Source, levs = c("REXS", "IST", "Leeds"))
-residuals_df$energyType <- as.factor(
-  replace(as.character(residuals_df$energyType), which(is.na(residuals_df$energyType)), "none"))
-residuals_df$energyType <- relevelFactor(as.factor(residuals_df$energyType), levs = energyLevels)
-@
-
-% These equations are used in several locations in the paper.
-% By defining commands for them, we ensure consistent appearance
-% of the equations when they are used.
-
-% Add an argument if you want a label. Example: "\label{eq:CES}"
-\newcommand{\ceskl}[1]{\begin{equation} #1
-  y = \gamma \: A \: \left[\delta_1 k^{-\rho_1} 
-      + (1-\delta_1)l^{-\rho_1} \right]^{-1/\rho_1}; 
-      A = \mathrm{e}^{\lambda (t-t_0)}
-\end{equation}}
-
-\newcommand{\ceskle}[1]{\begin{equation} #1
-  y = \gamma \: A \: \left\{\delta \left[\delta_1 k^{-\rho_1} 
-      + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1} 
-      + (1-\delta) e^{-\rho} \right\}^{-1/\rho}; 
-      A = \mathrm{e}^{\lambda (t-t_0)}
-\end{equation}
-}
-
-\newcommand{\ceslek}[1]{\begin{equation} #1
-  y = \gamma \: A \: \left\{\delta \left[\delta_1 l^{-\rho_1} 
-      + (1-\delta_1) e^{-\rho_1} \right]^{\rho/\rho_1} 
-      + (1-\delta) k^{-\rho} \right\}^{-1/\rho}; 
-      A = \mathrm{e}^{\lambda (t-t_0)}
-\end{equation}
-}
-
-\newcommand{\cesekl}[1]{\begin{equation} #1
-  y = \gamma \: A \: \left\{\delta \left[\delta_1 e^{-\rho_1} 
-      + (1-\delta_1) k^{-\rho_1} \right]^{\rho/\rho_1} 
-      + (1-\delta) l^{-\rho} \right\}^{-1/\rho}; 
-      A = \mathrm{e}^{\lambda (t-t_0)}
-\end{equation}
-}
 
@@
 
-\title{Paper 2 !DRAFT! Do not circulate!}
+\title{Primer on Production Functions and Economic Growth}
 
@@
 % \author[Leeds]{Julia Steinberger}
-% \author[CalvinEngr]{Matthew Kuperus Heun\corref{cor1}}
-% \ead{mkh2@calvin.edu}
+\author[CalvinEngr]{Matthew Kuperus Heun\corref{cor1}}
+\ead{mkh2@calvin.edu}
 
@@
 % \address[Leeds]{Leeds University, Leeds, UK}
-% \cortext[cor1]{Corresponding author}
-% \address[CalvinEngr]{Engineering Department, Calvin College, Grand Rapids, MI 49546, USA}
+\cortext[cor1]{Corresponding author}
+\address[CalvinEngr]{Engineering Department, Calvin College, Grand Rapids, MI 49546, USA}
 
@@
 %% keywords here, in the form: keyword \sep keyword
-economic growth \sep exergy \sep energy \sep Cobb-Douglas \sep CES \sep LINEX
+production function \sep economic growth \sep energy \sep Cobb-Douglas \sep CES \sep LinEx
 %% MSC codes here, in the form: \MSC code \sep code
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Coordinates of Analysis} 
-\label{sec:Coordinates}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-This section describes the coordinates of analysis and briefly reviews 
-literature related to each.
-
-%++++++++++++++++++++++++++++++
-\subsection{Mathematical Forms of the Energy-augmented Production Function} 
-\label{sec:Prod_Func_Forms}
-%++++++++++++++++++++++++++++++
-
-In this paper, we assess three prominent energy-augmented production functions 
-that appear in the literature: 
-Cobb-Douglas (CD), 
-Constant Elasticity of Substitution (CES), and 
-LINear EXponential (LINEX). 
-The following subsections describe each.
-
-%------------------------------
-\subsubsection{Cobb-Douglas Production Function} 
-\label{sec:CDe}
-%------------------------------
-
-The Cobb-Douglas production function can be expressed as
-%
-\begin{equation} \label{eq:CD}
-  y = \theta \mathrm{e}^{\lambda(t-t_0)} k^\alpha l^\beta \;,
-\end{equation}
-%
-\noindent where 
+This primer on production functions 
+provides background on several production functions
+for the purpose of accounting for the role of energy
+in economic growth.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Differential Economic Growth} 
+\label{sec:diff_growth}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The differential equation for economic growth~($y$) with 
+capital~($k$), labor~($l$), and energy~($e$) factors of production, 
+i.e., $y = y(k, l, e; t)$ is
+
+\begin{equation} \label{eq:diff_growth}
+  \frac{1}{y}\frac{\mathrm{d}y}{\mathrm{d}t} 
+      = \lambda \frac{1}{t - t_0}
+      + \alpha \frac{1}{k}\frac{\mathrm{d}k}{\mathrm{d}t} 
+      + \beta \frac{1}{l}\frac{\mathrm{d}l}{\mathrm{d}t} 
+      + \gamma \frac{1}{e}\frac{\mathrm{d}e}{\mathrm{d}t} \; ,
+\end{equation}
+%
+where 
 $y \equiv Y/Y_{0}$,
-$\theta$ is a scale parameter,
-e is the base of the natural logarithm, 
-$\lambda$ is represents the pace of technological progress,
-$t$ (time) is measured in years,
-$k \equiv K/K_{0}$, 
-$l \equiv L/L_{0}$, 
-$Y$ (economic output) is represented by GDP, 
+$t$ (time) is often measured in years,
+$\lambda$ represents the time dependence of the change of $y$,
+$k \equiv K/K_0$, 
+$l \equiv L/L_0$, 
+$e \equiv E/E_0$.
+$Y$ (economic output) is measured by GDP in currency units, 
 $K$ (capital) is expressed in currency units, 
 $L$ (labor) is expressed in workers or work-hours/year, and
-the 0 subscript indicates values at an initial year.%
-  \footnote{Dimensionless, indexed quantities are represented by 
-  lower-case symbols 
-  ($y$, $k$, $l$, $e$, $q$, $x$, and $u$), and dimensional 
-  quantities are represented by upper-case symbols 
-  ($Y$, $K$, $L$, $E$, $Q$, $X$, and $U$). 
-  Model parameters are represented by Greek letters
-  ($\alpha$, $\beta$, $\lambda$, $\theta$).
+the subscript 0 indicates values at an initial year.
+Constant returns to scale are represented by the constraint
+$\alpha + \beta + \gamma = 1$.
+
+The output elasticities $\alpha$, $\beta$, and $\gamma$ are defined as
+
+\begin{equation} \label{eq:alaph_def}
+  \alpha \equiv \frac{k}{y} \frac{\partial k / \partial t}{\partial y / \partial t} \; , \;
+  \beta  \equiv \frac{l}{y} \frac{\partial k / \partial t}{\partial y / \partial t} \; , \;
+  \gamma \equiv \frac{e}{y} \frac{\partial e / \partial t}{\partial y / \partial t} \; .
+\end{equation}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Leontief Production Function} 
+\label{sec:Leontief}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The Leontief production function is given by 
+%
+\begin{equation} \label{eq:Leontief}
+  y = \min \left[ a k, b l, c e\right]
+\end{equation}
+%
+where $a$, $b$, and $c$ are technologically-determined constants. 
+The Leontief function is a recipe for production.
+
+An example of a Leontief system is the production of automobiles.
+If $Y$ is the production rate of cars (cars/year),
+$W$ is wheels (wheels/year), 
+$S$ is steering wheels (steering wheels/year), and
+$R$ is rear-view mirrors (rear-view mirrors/year), 
+a Leontief production function is
+%
+\begin{equation} \label{eq:cars}
+  Y = \min \left[ a W, \; b S, \; c R\right] \; ,
+\end{equation}
+%
+where $a$ = 1 car/4 wheels, $b$ = 1 car/steering wheel, and $c$ = 1 car/rear-view mirror.
+
+The Leontief production function indicates that 
+oversupplying a factor of production~($W$, $S$, or $R$) will not increase output~($Y$).
+Put another way, wheels~($W$), steering wheels~($S$), and rear-view mirrors~($R$)
+are not substitutable.
+
+In the Leontief world, there is always at least one limiting factor of production.
+With 8 wheels, 10 steering wheels, and 10 rear-view mirrors,
+an automaker can produce only 2 cars.
+Under these conditions, wheels are the limiting factor of production, 
+and there will be 8 unused steering wheels and 8 unused rear-view mirrors, 
+a non-optimal production system indeed.
+The optimal (profit-maximizing) production strategy to make 2 cars would be to supply
+8 wheels, 2 steering wheels, and 2 rear-view mirrors.
+
+In modern economies, 
+constraints exist in terms of capital~($k$), labor~($l$), and energy~($e$).~\citep{Kummel:2010vz}
+%
+\begin{itemize}
+
+  \item Given a fully-utilized machine, throwing more energy at it will \emph{not} increase output~($y$).%
+  \footnote{
+  In fact, adding additional energy to the machine may cause damage.
   }
-Constant returns to scale are represented by the constraint
-$\alpha + \beta = 1$.
-
-The capital-labor Cobb-Douglas production function shown in Equation~\ref{eq:CD}
-can be augmented to include an energy term:
-%
-\begin{equation} \label{eq:CDe}
-  y = \theta \mathrm{e}^{\lambda(t-t_0)}  k^\alpha l^\beta e^\gamma \;,
-\end{equation}
-%
-where $e \equiv E/E_0$, and $E$ is in units of energy per time, typically TJ/year. 
-The energy-augmented Cobb-Douglas production function 
-is often assumed to have constant returns to scale for the three factors 
-of production: $\alpha + \beta + \gamma = 1$.
-
-The term $\mathrm{e}^{\lambda (t-t_0)}$ is known as the Solow Residual ($A$). 
-Assuming that parameters $\theta$, $\alpha$, and $\beta$ are known,
-we can estimate the value of $\lambda$ as follows.
-First, assume constant returns to scale such that $\gamma = 1 - \alpha - \beta$.
-Then, take the natural logarithm ($\ln$) of Equation~\ref{eq:CD} to obtain
-%
-\begin{equation} \label{eq:lnCD}
-  \ln y = \ln \theta + \ln A + \alpha \ln k + \beta \ln l + (1 - \alpha - \beta) \ln e \;.
-\end{equation}
-%
-By taking the derivative of Equation~\ref{eq:lnCD} with respect to time ($t$) 
-and noting that model parameters $\theta$ and $\alpha$ are 
-constant with respect to time, we obtain
-%
-\begin{equation} \label{eq:ddtlnCD}
-  \frac{1}{y}\frac{\mathrm{d}y}{\mathrm{d}t} 
-      = \frac{1}{A}\frac{\mathrm{d}A}{\mathrm{d}t} 
-      + \alpha \frac{1}{k}\frac{\mathrm{d}k}{\mathrm{d}t} 
-      + \beta \frac{1}{l}\frac{\mathrm{d}l}{\mathrm{d}t} 
-      + (1 - \alpha - \beta) \frac{1}{e}\frac{\mathrm{d}e}{\mathrm{d}t} \;.
-\end{equation}
-%
-Solving for the Solow Residual term gives
-%
-\begin{equation} \label{eq:solow_resid}
-  \frac{1}{A}\frac{\mathrm{d}A}{\mathrm{d}t} 
-      = \frac{1}{y}\frac{\mathrm{d}y}{\mathrm{d}t} 
-      - \left[
-              \alpha \frac{1}{k}\frac{\mathrm{d}k}{\mathrm{d}t} 
-              + \beta \frac{1}{l}\frac{\mathrm{d}l}{\mathrm{d}t} 
-              + (1 - \alpha - \beta) \frac{1}{e}\frac{\mathrm{d}e}{\mathrm{d}t} 
-        \right] \;.
-\end{equation}
-%
-Recognizing that $A \equiv \mathrm{e}^{\lambda (t-t_0)}$ gives
-%
-\begin{equation}
-  \frac{1}{A}\frac{\mathrm{d}A}{\mathrm{d}t} 
-    = \frac{1}{\mathrm{e}^{\lambda (t-t_0)}} \; \lambda \mathrm{e}^{\lambda (t-t_0)}
-    = \lambda \; ,
-\end{equation}
-%
-which can be substituted into Equation~\ref{eq:solow_resid} to find
-%
-\begin{equation} \label{eq:lambda}
-  \lambda 
-    = \frac{1}{y}\frac{\mathrm{d}y}{\mathrm{d}t} 
-    - \left[
-              \alpha \frac{1}{k}\frac{\mathrm{d}k}{\mathrm{d}t} 
-              + \beta \frac{1}{l}\frac{\mathrm{d}l}{\mathrm{d}t} 
-              + (1 - \alpha - \beta) \frac{1}{e}\frac{\mathrm{d}e}{\mathrm{d}t} 
-      \right] \;.
-\end{equation}
-%
-Equation~\ref{eq:lambda} applies for any instant in time.
-
-If we approximate derivatives in Equation~\ref{eq:lambda} with forward differences
-between times $i$ and $j$, we find
-%
-\begin{equation} \label{eq:lambdaij}
-  \lambda_{i,j}
-    \approx \frac{1}{y_i}\frac{y_j - y_i}{t_j - t_i} 
-    - \left[
-            \alpha \frac{1}{k_i}\frac{k_j - k_i}{t_j - t_i} 
-            + \beta \frac{1}{l_i}\frac{l_j - l_i}{t_j - t_i} 
-            + (1 - \alpha - \beta) \frac{1}{e_i}\frac{e_j - e_i}{t_j - t_i} 
-      \right] \;,
-\end{equation}
-% 
-where $\lambda_{i,j}$ approximates the true, instantaneous value of $\lambda$
-between times $i$ and $j$.
-
-Interestingly, 
-%
-\begin{equation}
-  \lambda_{1,n}
-    \neq \sum_{i=2}^{n} \lambda_{i,i-1}  \;.
-\end{equation}
-% 
-Rather,
-%
-\begin{equation} \label{eq:lambda1n}
-  \lambda_{1,n}
-    \approx \frac{1}{y_1}\frac{y_n - y_1}{t_n - t_1} 
-      - \left[ 
-            \alpha \frac{1}{k_1}\frac{k_n - k_1}{t_n - t_1} 
-            + \beta \frac{1}{l_1}\frac{l_n - l_1}{t_n - t_1} 
-            + (1 - \alpha - \beta) \frac{1}{e_1}\frac{e_n - e_1}{t_n - t_1} 
-      \right] \; ,
-\end{equation}
-% 
-which will become increasingly inaccurate over large time spans,
-because $y_1$, $k_1$, $l_1$, and $e_1$ will be less representative
-of the average value of $y$, $k$, $l$, and $e$ in the time span, respectively.
-This suggests that an averaging approach such as
-%
-\begin{equation}
-  \lambda_{1,n}
-    \approx \frac{\sum_{i=2}^{n} \lambda_{i,i-1}}{n-1}
-\end{equation}
-%
-is a better approximation of Equation~\ref{eq:lambda1n},
-which is, itself, an approximation of the true value of $\lambda$ 
-given by Equation~\ref{eq:lambda}.
-
-%------------------------------
-\subsubsection{Constant Elasticity of Substitution Production Function (CES)} 
+  Capital~($k$) constrains energy~($e$).
+
+  \item Given a state of automation of the economy at an instant in time, 
+  and assuming full utilization of the capital~($k$)
+  in terms of both labor~($l$) and energy~($e$) for operation,
+  adding labor to the economy doesn't increase output~($y$). 
+  Capital~($k$) and energy~($e$) constrain labor~($l$).
+
+\end{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Linear Production Function} 
+\label{sec:linear}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The linear production function is given by
+%
+\begin{equation} \label{eq:linear}
+  y = a k + b l + c e \; .
+\end{equation}
+%
+In Equation~\ref{eq:linear}, $a$, $b$, and $c$ are positive constants.
+In the linear world, factors of production are perfect substitutes.
+
+Continuing the cooking analogy, consider producing toast ($Y$) 
+with a fatty substance~(butter or margarine).
+%
+\begin{equation} \label{eq:toast}
+  Y = a B + b M
+\end{equation}
+%
+The linear model (Equation~\ref{eq:toast}) indicates that butter~($B$) and margarine~($M$) 
+can be used interchangably as the fatty substance.
+Butter~($B$) and margarine~($M$) are perfect substitutes.%
+  \footnote{
+  Butter and margarine may be perfect substitutes for all but the most discerning toast consumers.
+  }%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Cobb-Douglas Production Function} 
+\label{sec:CD}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The Cobb-Douglas production function is given by
+%
+\begin{equation} \label{eq:CD}
+  y = A k^\alpha l^\beta e^\gamma \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)} \; .
+\end{equation}
+%
+$A$ is known as total factor productivity,
+and $\lambda$ is the Solow residual.
+
+In the Cobb-Douglas world, factors of production are substitutable, 
+eg., a reduction of labor~($l$) can be compensated by an increase of capital~($k$)
+without affecting output~($y$).%
+  \footnote{
+  In fact, the capital-for-labor substitution has a name: automation.
+  }
+Furthermore, an increase in one factor of production (say, $k$)
+without a concomitant increase in the others ($l$ or $e$) 
+will result in an increase of output ($y$), provided that the output elasticity 
+($\alpha$) is non-zero.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Constant Elasticity of Substitution Production Function (CES)} 
 \label{sec:CES}
-%------------------------------
-
-Other energy economists use an energy-augmented 
-Constant Elasticity of Substitution (CES) production function to 
-describe economic growth. The \texttt{R} \citep{R} package 
-\texttt{micEconCES} \citep{Henningsen:2011td} estimates CES production 
-functions of the following forms (among others):
-%
-\ceskl{\label{eq:CES}}
-%
-\ceskle{\label{eq:CESkle}}
-%
-\noindent Equation~\ref{eq:CES} is a CES production function with 
-capital stock ($k$) and labor ($l$) factors of production. 
-Equation~\ref{eq:CESkle} augments Equation~\ref{eq:CES} with energy 
-using a ($kl$)($e$) nesting structure, as is typical in the literature. 
-Equation~\ref{eq:CES} is a degenerate form of Equation~\ref{eq:CESkle} 
-where $\delta \rightarrow 1$.
-
-$\gamma$ is a fitting parameter that represents productivity. 
-The fitting parameters $\rho_1$ and $\rho$ indicate elasticities 
-of substitution ($\sigma_1$ and $\sigma$).
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The Constant Elasticity of Substitution production function
+provides smooth transition between perfectly complementary (Leontief) 
+and perfectly substitutable (linear) factors of production.
+
+%++++++++++++++++++++++++++++++
+\subsection{CES with Two Factors of Production} 
+\label{sec:CES-2}
+%++++++++++++++++++++++++++++++
+
+With two factors of production (capital, $k$ and labor, $l$), 
+the CES production function is given by
+%
+\begin{equation} \label{eq:CES}
+  y = A \: \left[\delta_1 k^{-\rho_1} 
+      + (1-\delta_1)l^{-\rho_1} \right]^{-1/\rho_1} \; ; \;
+      A = \mathrm{e}^{\lambda (t-t_0)}   \; .
+\end{equation}
+%
+In Equation~\ref{eq:CES}, capital~($k$) and labor~($l$) are said to be ``nested''
+together in the production function.
+
+$\delta_1$ describes the importance of capital ($k$)
+relative to labor ($l$).
+As $\delta_1 \rightarrow 1$, only capital~($k$) is necessary for production.
+As $\delta_1 \rightarrow 0$, only labor~($l$) is necessary for production.
+
+$\rho_1$ indicates the elasticity 
+of substitution~($\sigma_1$) between capital~($k$) and labor~($l$).
 The elasticity of substitution 
-between capital ($k$) and labor ($l$) is given by 
-$\sigma_1 = \frac{1}{1+\rho_1}$, and
-the elasticity of substitution between ($kl$) and ($e$) is given by 
-$\sigma = \frac{1}{1+\rho}$. 
-As $\rho_1 \rightarrow 0$, $\sigma_1 \rightarrow 1$,
-and the embedded CES production function for $k$ and $l$ degenerates 
-to the Cobb-Douglas production function.
-Similarly, as $\rho \rightarrow 0$, $\sigma \rightarrow 1$,
-and the CES production function for $(kl)$ and $(e)$ degenerates 
-to the Cobb-Douglas production function.
-As $\sigma \rightarrow \infty$ ($\rho \rightarrow -1$), 
-($kl$) and ($e$) are perfect substitutes. 
-As $\sigma \rightarrow 0$ ($\rho \rightarrow \infty$), 
-($kl$) and ($e$) are perfect complements: 
-no substitution is possible. Similarly, 
-as $\sigma_1 \rightarrow 0$ ($\rho_1 \rightarrow \infty$),
-$k$ and $l$ are perfect complements.
-$\delta_1$ describes the relative importance of capital ($k$)
-and labor ($l$), and
-$\delta$ describes the importance of ($kl$) relative to ($e$).
-
-Constraints on the fitting parameters include 
-$\delta_1 \in [0,1]$,
-$\delta \in [0,1]$,
-$\rho_1 \in [-1,0) \cup (0,\infty)$, and
-$\rho \in [-1,0) \cup (0,\infty)$.
-
-Two other nestings of the factors of production ($k$, $l$, and $e$)
-are possible with the CES model.
-%
-\ceslek{\label{eq:CESlek}}
-%
-\cesekl{\label{eq:CESekl}}
-%
-\noindent Note that the $\rho$ ($\sigma$) and $\delta$ parameters have different
-meanings that depend upon the nesting of the factors of production.
-
-%------------------------------
-\subsubsection{LINEX Production Function} 
-\label{sec:LINEX}
-%------------------------------
-
-A third production function, the LINear EXponential (LINEX) function
-%
-\begin{equation} \label{eq:LINEX}
-  y = \theta \; \mathrm{e}^{a_0\left[2 \left(1 - \frac{1}{\rho_k} \right) 
-    + c_t \left(\vphantom{\frac{1}{\rho_k}}\rho_l - 1 \right)\right]} \; e \;,
-\end{equation}
-%
-was derived from thermodynamic considerations
+between capital~($k$) and labor~($l$) is related to $\rho_1$ and given by 
+%
+\begin{equation} \label{eq:sigma_1}
+ \sigma_1 = \frac{1}{1+\rho_1} \; .
+\end{equation}
+%
+Solving for $\rho_1$ gives
+%
+\begin{equation} \label{eq:rho_1}
+  \rho_1 = \frac{1 - \sigma_1}{\sigma_1} \; .
+\end{equation}
+
+Constraints on the parameters include 
+$\delta_1 \in [0,1]$ and
+$\rho_1 \in (-1,0) \cup (0,\infty)$.
+
+%++++++++++++++++++++++++++++++
+\subsection{CES with Three Factors of Production} 
+\label{sec:CES-3}
+%++++++++++++++++++++++++++++++
+
+A doubly-nested form of the CES production function is required
+if a third factor of production~($e$) is to be included.
+%
+\begin{equation} \label{eq:CES-kle}
+  y = A \: \left\{\delta \left[\delta_1 k^{-\rho_1} 
+      + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1} 
+      + (1-\delta) e^{-\rho} \right\}^{-1/\rho} \; ; \; 
+      A = \mathrm{e}^{\lambda (t-t_0)}
+\end{equation}
+%
+In Equation~\ref{eq:CES-kle}, $\delta$ 
+describes the importance of the capital-labor ($kl$) nesting 
+relative to energy~($e$).
+
+Important questions arise: why nest capital~($k$) and labor~($l$) together 
+and separate energy~($e$)
+in the~($kl$)($e$) nest structure?
+Why not nest, e.g., labor~($l$) and energy~($e$) in a~($le$)($k$) structure?%
+  \footnote{
+  Note that the $\rho$ (and, therefore, $\sigma$) and $\delta$ parameters have different
+  meanings depending upon how the factors of production are nested.
+  }%
+%
+\begin{equation} \label{eq:CES-lek}
+  y = A \: \left\{\delta \left[\delta_1 l^{-\rho_1} 
+      + (1-\delta_1) e^{-\rho_1} \right]^{\rho/\rho_1} 
+      + (1-\delta) k^{-\rho} \right\}^{-1/\rho} \; ; \; 
+      A = \mathrm{e}^{\lambda (t-t_0)}
+\end{equation}
+%
+Or nest energy and capital in a~($ek$)($l$) structure?
+%
+\begin{equation} \label{eq:CES-ekl}
+  y = A \: \left\{\delta \left[\delta_1 e^{-\rho_1} 
+      + (1-\delta_1) k^{-\rho_1} \right]^{\rho/\rho_1} 
+      + (1-\delta) l^{-\rho} \right\}^{-1/\rho} \; ; \; 
+      A = \mathrm{e}^{\lambda (t-t_0)}
+\end{equation}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Relating CES to Other Production Functions} 
+\label{sec:CES-others}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Equation~\ref{eq:CES} simplifies to the other production functions 
+with different values of $\sigma$.
+For the two-factor CES production function, 
+Table~\ref{tab:ces_simplifications} describes the options.
+
+\begin{table}
+\caption[CES Simplifications]{CES Simplifications.}
+\begin{center}
+ \begin{tabular}{ c c c c }
+\toprule 
+$\sigma$ & $\rho$ & CES simplifies to \dots & Factors of production are \dots \\
+\midrule
+0        & $\infty$ & Leontief              & perfect complements             \\
+% \midrule
+1        & 0        & Cobb-Douglas          & substitutable                   \\
+% \midrule
+$\infty$ & $-1$     & linear                & perfect substitutes             \\
+\bottomrule
+\end{tabular}
+\end{center}
+\label{tab:ces_simplifications}
+\end{table}
+
+Figure~\ref{fig:CES_isoquants} shows the simplifications from Table~\ref{tab:ces_simplifications}
+graphically.
+%
+\begin{figure}[!ht]
+\centering\
+\includegraphics[width=0.8\linewidth]{figure/CESIsoquants.png}
+\caption[CES isoquants]{CES isoquants (lines of constant output). 
+$K$ is capital and $N$ is labor.~\citep{Klump:2011aa}}
+\label{fig:CES_isoquants}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{LinEx Production Function} 
+\label{sec:linex}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+An additional production function, the Linear Exponential (LinEx%
+    \footnote{
+    The name ``LinEx'' comes from the form of the equation:
+    production is \emph{linear} in energy~($e$) and \emph{exponential}
+    in ratios of the factors of production~($k$, $l$, and $e$).
+    }%
+) function is given by K\"{u}mmel in several places as
+%
+\begin{equation} \label{eq:LinEx-kummel}
+  y = e \exp{\left[ a \left( 2 - \frac{l + e}{k} \right)  + a c \left( \frac{l}{e} - 1 \right)\right]}
+\end{equation}
+%
+An alternative presentation that affords easier interpretation is
+%
+\begin{equation} \label{eq:LinEx}
+  y = A e \; ; \; A \equiv \mathrm{e}^{a\left[2 \left(1 - \frac{1}{\rho_k} \right) 
+    + c \left(\vphantom{\frac{1}{\rho_k}}\rho_l - 1 \right)\right]} \; .
+\end{equation}
+%
+The LinEx function was derived from thermodynamic considerations
 \citep{Kummel:1980wx,Kummel:1982vy,Kummel:1985vz,Kummel:1989tf,Kummel:2002tx,Kummel:2010vz}. 
-In contrast to both the Cobb-Douglas model (Equations~\ref{eq:CD} and 
-\ref{eq:CDe}) and the CES model (Equations~\ref{eq:CES}--\ref{eq:CESekl}), 
-the LINEX model (Equation~\ref{eq:LINEX}) does not include a generic, 
-time-dependent augmentation term ($A$).
-The LINEX model assumes energy ($e$) is the only factor of production.
-
-The LINEX model does, however, include terms that represent
+A key feature of the derivation involves
+constraints among capital~($k$), labor~($l$), and energy~($e$).
+These constraints were discussed in Section~\ref{sec:Leontief} above.%
+  \footnote{
+  As an aside, I'm not sure the constraints 
+  described in Section~\ref{sec:Leontief} are the right ones.
+  }%
+
+In contrast to both the Cobb-Douglas model (Equation~\ref{eq:CD}) 
+and the CES model~(Section~\ref{sec:CES}), 
+the LiNex model (Equation~\ref{eq:LinEx}) does not include a generic, 
+time-dependent augmentation term~($A$).
+The LinEx model assumes energy~($e$) is the only factor of production.
+
+The LinEx model does, however, include terms that represent
 efficiencies among capital, labor, and energy, in the form of 
-the ratios $\rho_k$ and $\rho_l$ which are defined by\footnote{The notation
-for the LINEX model breaks from the conventions used in the Cobb-Douglas and CES
-models:  $a_0$ and $c_t$ are parameters and $\rho_k$ and $\rho_l$ are not.}
+the ratios $\rho_k$ and $\rho_l$ which are defined by
 %
@@
 In that case, economic output ($y$) increases at the same rate as energy consumption ($e$).
-According to the LINEX model, an economy that increases 
+According to the LiNex model, an economy that increases 
 capital stock ($k$) without a commensurate increase in labor ($l$) 
@@
 of its increase of energy consumption ($e$), because
-\(
-\mathrm{e}^{a_0\left[2 \left(1 - \frac{1}{\rho_k} \right) 
-    + c_t \left(\vphantom{\frac{1}{\rho_k}}\rho_l - 1 \right)\right]}
-	> 1.
-\) 
+%
+\begin{equation}
+    \mathrm{e}^{a \left[2 \left(1 - \frac{1}{\rho_k} \right) 
+    + c \left(\vphantom{\frac{1}{\rho_k}}\rho_l - 1 \right)\right]}
+	> 1 \; .
+\end{equation}
+%
 Similarly, an economy benefits by increasing labor ($l$) 
@@
 
-The parameter $a_0$ represents the overall importance of efficiencies $\rho_k$ and $\rho_l$, 
-and the parameter $c_t$ represents the relative importance 
+The parameter $a$ represents the overall importance of efficiencies $\rho_k$ and $\rho_l$, 
+and the parameter $c$ represents the relative importance 
 of the labor efficiency term ($\rho_l$) compared to the capital stock efficiency term ($\rho_k$).
-Both $a_0$ and $c_t$ are assumed constant with respect to time.
-
-%++++++++++++++++++++++++++++++
-\subsection{Economies} 
-\label{sec:Economies}
-%++++++++++++++++++++++++++++++
-
-Discuss economies here.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Sources of Data}
-\label{sec:Sources_of_Data}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Discuss data sources here.
-
-%++++++++++++++++++++++++++++++
-\subsection{Historical Data} 
-\label{sec:Historical_Data}
-%++++++++++++++++++++++++++++++
-
-Figure~\ref{fig:Historical_Data_1} shows a graph of historical data.
-
-<<Historical_Data_1, fig.pos="H", fig.align='center', fig.width=6.6, fig.height=7, fig.cap="Historical data.">>=
-mdata <- melt(historicalData, 
-              measure.vars = c("iGDP", "iK", "iL", "iXp", "iXf", "iU"), 
-              variable.name = "variable",
-              value.name = "value")
-historicalPlot(mdata, 
-               mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
-               facet_formula = Country ~ Source, 
-               line_types = c(1,5,2,6,4,3)) + 
-  xlab("") + 
-  ylab("Indexed (1960=1 or 1970=1)")
-@
-
-Figure~\ref{fig:Historical_Data_2} shows the same data as Figure~\ref{fig:Historical_Data_1} 
-in a different form.
-
-<<Historical_Data_2, fig.pos="H", fig.align='center', fig.width=8, fig.height=7, fig.cap="Historical data.">>=
-historicalPlot(mdata, 
-               mapping=aes(x=Year, y=value, group=Source, linetype=Source), 
-               facet_formula = Country ~ variable, 
-               line_types = c(1,5,3)) + 
-  xlab("") + 
-  ylab("Indexed (1960=1 or 1970=1)")
-@
-
-Figure~\ref{fig:Preeconometric_1} shows a graph of factors of production relative to GDP.
-
-<<Preeconometric_1, fig.pos="H", fig.align='center', fig.width=8, fig.height=7, fig.cap="Pre-econometric data.">>=
-mdata2 <- melt(historicalData, 
-               measure.vars = c("KPerGDP", "LPerGDP", "XpPerGDP", "XfPerGDP", "UPerGDP"), 
-               variable.name = "variable",
-               value.name = "value")
-
-historicalPlot(mdata2, 
-               mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
-               facet_formula = Country ~ Source, 
-               line_types = c(1,5,2,6,4)) + 
-  xlab("") + 
-  ylab("Indexed Econometric Ratios (1960=1 or 1970=1)")
-@
-
-Figure~\ref{fig:Preeconometric_2} shows the same data as Figure~\ref{fig:Preeconometric_1} 
-in a different form.
-
-<<Preeconometric_2, fig.pos="H", fig.align='center', fig.width=8, fig.height=7, fig.cap="Pre-econometric data.">>=
-historicalPlot(mdata2, 
-               mapping=aes(x=Year, y=value, group=Source, linetype=Source), 
-               facet_formula = Country ~ variable, 
-               line_types = c(1,3,5)) + 
-  xlab("") + 
-  ylab("Indexed Econometric Ratios (1960=1 or 1970=1)")
-@
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Parameter Estimation}
-\label{sec:Parameter_Estimation}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%++++++++++++++++++++++++++++++
-\subsection{Point Estimates}
-%++++++++++++++++++++++++++++++
-
-Each of the economic growth models discussed in 
-Section~\ref{sec:Prod_Func_Forms} has parameters which must be estimated (fitted)
-using data for each economy (see Sections~\ref{sec:Economies} and~\ref{sec:Sources_of_Data}).
-We obtained parameter estimates by applying the method of least-squares to 
-log-transformed data using the \texttt{R} \citep{R} functions
-\texttt{lm} (for Cobb-Douglas and LINEX models) 
-and \texttt{cesEst} \citep{Henningsen:2011td} (for CES models).
-
-Although the details vary from model to model, each of our three models has the general form
-%
-\begin{equation}
-  y = f(t,k,l,e; \theta) + \mathrm{error} \;,
-\end{equation}
-%
-where $\theta$ is a vector of parameters for the function $f$.
-Parameter estimates are chosen to minimize
-%
-\begin{equation} \label{eq:sse}
-  sse = \sum_{i} (y_i - f(t,k,l,e; \theta) )^2
-\end{equation}
-%
-within constraints.
-For the optimal parameter values $\hat \theta$, we define the 
-fitted response by
-\[
-\hat y_i = f(t_i, k_i, l_i, e_i; \hat \theta)
-\]
-and the residuals ($r_i$)
-as the difference between the observed response and the fitted response
-%
-\begin{equation} \label{eq:residual}
-  r_i 
-  = y_i - \hat y_i
-  = y_i - f(t,k,l,e; \hat\theta)
-\end{equation}
-%
-The details for each of the models are discussed in 
-Sections~\ref{sec:CD_Parameter_Estimation}--\ref{sec:LINEX_Parameter_Estimation} below.
-
-%++++++++++++++++++++++++++++++
-\subsection{Resampling Methods}
-\label{sec:Resampling}
-%++++++++++++++++++++++++++++++
-
-Bootstrapping is a statistical resampling technique for assigning
-measures of accuracy and precision to sample estimates by measuring
-properties of an estimator when sampling from a resampling
-distribution.  
-Resampling distributions can be formed in a number of 
-ways in accordance with the type of data, experimental design,
-and modeling assumptions involved.  
-In each case, many new resamples 
-are created, each of which is a randomized version of the original sample data to 
-which the desired analysis method can be applied.  
-By investigating, for example,
-the variability of a parameter estimate from one resample to another,
-one can learn about the precision of the estimation method.
-
-In the context of linear models (regression), resamples are generally created
-by residual resampling.  
-In our case, we formed resamples by adding to the fitted 
-response ($\hat{y}$) the product of a residual from the original model fit and 
-random sign ($-1$ or $1$, each with probability $0.5$).  
-For the case of Cobb-Douglas and LINEX models, 
-this residual resampling occurs on the 
-log-transformed data.
-
-Intuitively, this method assumes that the residuals are indicative of 
-the variability (from many potential sources) inherent in the data such that
-it would be unsurprising if the residual from 
-any particular year had been observed in a different year. 
-Thus, a resampled response $\tilde Y'$ can be computed as 
-%
-\begin{equation} \label{eq:Y_tilde}
-  \tilde Y_i' = \hat y_i \pm r_j \; ,
-\end{equation}
-%
-where 
-%
-\begin{equation}
-  r_i = y_i - \hat y_i \; .
-\end{equation}
-%
-In Equation~\ref{eq:Y_tilde}, both the sign ($\pm$) 
-and the index ($j$,~typically different from $i$) 
-of the residual ($r$) 
-are chosen at random (with replacement). 
-We repeated the resampling process 1000 times for each
-combination of growth model, country, and data source, 
-both with and without energy as appropriate.
-
-The coefficients from the fit to a resampled time series
-(the ``resample coefficients'') will be different from the coefficients 
-obtained from the fit to historical data (the ``base coefficients'').
-When these resample coefficients are highly variable, 
-it is an indication
-that the data do not determine the parameter estimates very precisely.
-Lack of precision can stem from a number of factors, most obviously
-a poor model fit, low model sensitivity to one or more parameters, 
-or correlations between parameter estimates.
-
-It is important to note that large residuals can arise from either
-(a) poor quality historical time series data, or 
-(b) a mathematical model that does not describe the underlying phenomena well.
-It is also important to note that (c) even when the residuals are small and the 
-model produces fitted values that track the observed data closely, it may
-yet be difficult to estimate some or all of the model parameters precisely.
-The resampling method employed herein reflects all three of these potential 
-sources of uncertainty in parameter estimates.
-
-%++++++++++++++++++++++++++++++
-\subsection{Cobb-Douglas Models}
-\label{sec:CD_Parameter_Estimation}
-%++++++++++++++++++++++++++++++
-
-The Cobb-Douglas model without energy is given by 
-Equation~\ref{eq:CD}. Equation~\ref{eq:CD} was
-reparameterized as
-%
-\begin{equation} \label{eq:CD_reparam}
-  y = \theta \mathrm{e}^{\lambda (t-t_0)} k^{\alpha} l^{1-\alpha}
-\end{equation}
-%
-\noindent to ensure $\alpha + \beta = 1$ for constant returns to scale. 
-$\theta$, $\lambda$, and $\alpha$ were estimated by the 
-\texttt{R} \citep{R} function \texttt{lm} in log-transform space. 
-If the estimated value for $\alpha$ was found outside the interval $[0,1]$, 
-we set $\alpha$ to its boundary value and re-estimated $\lambda$. 
-The value of $\beta$ was found with $\beta = 1 - \alpha$.
-
-To estimate the parameters $\theta$, $\lambda$, $\alpha$, $\beta$, and $\gamma$ 
-in the energy-augmented Cobb-Douglas model, Equation~\ref{eq:CDe} 
-was reparameterized as
-%
-\begin{equation} \label{eq:CDe_AB_reparam}
-  y = \theta \mathrm{e}^{\lambda (t-t_0)} k^{\alpha} l^{\beta} e^{1 - \alpha - \beta}
-\end{equation}
-%
-\noindent ensuring that $\alpha + \beta + \gamma = 1$,
-thereby providing constant returns to scale.
-The \texttt{R} \citep{R} function \texttt{lm} was used to estimate 
-values of $\lambda$, $\theta$, $\alpha$, and $\beta$ in log-transform space.
-If the fitted value for $\alpha$ or $\beta$ fell outside the interval $[0,1]$,
-we fit along all boundaries 
-($\alpha = 1$,
-$\beta = 1$,
-$\gamma = 1$,
-$\alpha = 0$,
-$\beta = 0$, and
-$\gamma = 0$)
-and chose the boundary fit with
-minimum $sse$ (Equation~\ref{eq:sse}) as the winner.
-$\gamma$ was recovered with $\gamma = 1 - \alpha - \beta$.
-
-Figure~\ref{fig:CD_Ternary_Scatter_Graph} shows ternary plots 
-for $\alpha$, $\beta$, and $\gamma$ parameter values 
-for Cobb-Douglas (without and with energy) resample models.
-Each reample is shown as a gray dot on the graph. 
-The fit to historical data is shown as a gray crosshairs.
-
-Figures~\ref{fig:CD_GDP_Spaghetti_Graphs_US}--\ref{fig:CD_GDP_Spaghetti_Graphs_CN} 
-compare predictions 
-from the Cobb-Douglas models 
-(without and with energy) to historical data.
-Historical data are shown as a black line. 
-The fit to historical data is shown as a white line.
-The gray band encompasses \Sexpr{spaghettiGraphLevel*100}\% of the fits to resampled data.
-
-<<CD_lambda_theta_graph, fig.pos="H", fig.align='center', fig.width=6, fig.height=5.5, fig.cap="$\\lambda$ and $\\theta$ values for Cobb-Douglas resample models.">>=
-cdCoeffsData <- subset(AllCoeffs, subset = model=="cd")
-standardScatterPlot(data=cdCoeffsData, mapping=aes(x=scale, y=lambda, color=Source), 
-                    facet_formula=country~energy, alpha=0.05) +
-    scale_x_continuous(limits=c(0.9, 1.5), breaks=c(1.0, 1.2, 1.4)) +
-    scale_y_continuous(limits=c(-0.02, 0.05), breaks=c(0.0, 0.025, 0.05)) +    
-    labs(x=expression(theta), y=expression(lambda)) +
-    guides(colour=guide_legend(override.aes = aes(alpha=1))) #+
-#     geom_density2d()
-@
-
-<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=6, fig.height=5, fig.cap="Cobb-Douglas resample model parameters.">>=
-standardTriPlot(data=cdCoeffsData, 
-                mapping=aes(color=Source),
-                facet_formula=country~energy) +
-    guides(colour=guide_legend(override.aes = aes(alpha=1)))
-@
-
-Given the estimates for $\alpha$, $\beta$, and $\gamma$ for the Cobb-Douglas model,
-we can estimate values for $\lambda$ on a year-by-year basis using Equation~\ref{eq:lambdaij}.
-The results are shown in the Figure~\ref{fig:CD_lambda_time_series}.
-
-<<CD_lambda_time_series, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap='Solow residual time series.'>>=
-# Add a bogus "none" column that we can use for the no-energy case
-m_histData <- historicalData
-m_histData$none <- 1.0
-# Melt the the historical data to put energy in one column
-m_histData <- melt(select(m_histData, Year, iGDP, iK, iL, iXp, iXf, iU, none, Country, Source), 
-                   measure.vars = c("none", "iXp", "iXf", "iU"),
-                   variable.name = "energyType",
-                   value.name = "iE")
-# Calculate finite difference approximations of time derivatives for output and all factors of production
-fd <- m_histData %>% group_by(Source, Country, energyType) %>% arrange(Year) %>% 
-  mutate(dydt = ediff(iGDP, pad="tail") / ediff(Year, pad="tail")) %>%
-  mutate(dkdt = ediff(iK, pad="tail") / ediff(Year, pad="tail")) %>%
-  mutate(dldt = ediff(iL, pad="tail") / ediff(Year, pad="tail")) %>%
-  mutate(dedt = ediff(iE, pad="tail") / ediff(Year, pad="tail"))
-
-origCDKLCoeffs <- subset(AllCoeffs, method=="orig" & model=="cd")
-origCDKLCoeffs <- origCDKLCoeffs %>% select(method, country, Source, nestStr, energy, lambda, alpha, beta, gamma)
-# Change name of Source REXS to REXS1960 and relevel to conform to information in fdlambda.
-origCDKLCoeffs$Source <- as.character(origCDKLCoeffs$Source)
-origCDKLCoeffs$Source <- replace(origCDKLCoeffs$Source, which(origCDKLCoeffs$Source=="REXS"), "REXS1960")
-origCDKLCoeffs$Source <- as.factor(origCDKLCoeffs$Source)
-origCDKLCoeffs$Source <- relevelFactor(origCDKLCoeffs$Source, levs = c("REXS1960", "IST", "Leeds"))
-
-# Fill new columns in the fd data frame with 
-# lambda, alpha, beta, and gamma values from the parameter estimation process.
-# lambda, alpha, beta, and gamma values for the orig fits are in the origCDKLCoeffs data frame.
-# Using the hint at 
-# http://stackoverflow.com/questions/15059076/
-# r-how-to-call-apply-like-function-on-each-row-of-dataframe-with-multiple-argum
-labg <- apply(fd[ , c('Country', 'Source', 'energyType')], 1, function(x){
-    row <- as.data.frame(subset(origCDKLCoeffs, 
-                                country==x["Country"] & Source==x["Source"] & energy==x["energyType"]))
-    abg <- subset(row, select=c(lambda, alpha, beta, gamma))
-    if (nrow(abg) < 1){ abg[1, ] <- NA }
-    return(abg)
-  })
-cols <- do.call(rbind, labg)
-fd <- cbind(fd, cols)
-
-# Now calculate lambda by finite difference for every year to make a time series
-fdlambda <- mutate(fd, lambda_diff = 1/iGDP*dydt - (alpha/iK*dkdt + beta/iL*dldt + gamma/iE*dedt))
-
-# Create a time series graph of the lambda_diff values
-ggplot(data=fdlambda, aes(x=Year, y=lambda_diff, color=Source)) + 
-  geom_point(size = 1.0) +
-  facet_grid(Country ~ energyType) +
-  labs(x = "", y = expression(lambda)) + 
-#   scale_y_continuous(limits=c(-0.1, 0.1)) +
-  xy_theme()
-@
-
-<<CD_GDP_Spaghetti_Graphs_US, fig.pos="H", fig.align='center', fig.width=4, fig.height=3.5, fig.cap="US Cobb-Douglas fitted models.">>=
-cdFittedDataUS <- subset(AllFitted, subset = model=="cd" & Country=="US")
-spaghettiPlot(data=cdFittedDataUS, facet_formula=Source~energy, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<CD_GDP_Spaghetti_Graphs_UK, fig.pos="H", fig.align='center', fig.width=4, fig.height=4.5, fig.cap="UK Cobb-Douglas fitted models.">>=
-cdFittedDataUK <- subset(AllFitted, subset = model=="cd" & Country=="UK")
-spaghettiPlot(data=cdFittedDataUK, facet_formula=Source~energy, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<CD_GDP_Spaghetti_Graphs_JP, fig.pos="H", fig.align='center', fig.width=4, fig.height=2.5, fig.cap="JP Cobb-Douglas fitted models.">>=
-cdFittedDataJP <- subset(AllFitted, subset = model=="cd" & Country=="JP")
-spaghettiPlot(data=cdFittedDataJP, facet_formula=Source~energy, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<CD_GDP_Spaghetti_Graphs_AT, fig.pos="H", fig.align='center', fig.width=5, fig.height=3.5, fig.cap="AT Cobb-Douglas fitted models.">>=
-cdFittedDataAT <- subset(AllFitted, subset = model=="cd" & Country=="AT")
-spaghettiPlot(data=cdFittedDataAT, facet_formula=Source~energy, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<CD_GDP_Spaghetti_Graphs_PT, fig.pos="H", fig.align='center', fig.width=5, fig.height=2.5, fig.cap="PT Cobb-Douglas fitted models.">>=
-cdFittedDataPT <- subset(AllFitted, subset = model=="cd" & Country=="PT")
-spaghettiPlot(data=cdFittedDataPT, facet_formula=Source~energy, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<CD_GDP_Spaghetti_Graphs_CN, fig.pos="H", fig.align='center', fig.width=4, fig.height=2.5, fig.cap="CN Cobb-Douglas fitted models.">>=
-cdFittedDataCN <- subset(AllFitted, subset = model=="cd" & Country=="CN")
-spaghettiPlot(data=cdFittedDataCN, facet_formula=Source~energy, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<CD_Residual_Plot, fig.pos="H", fig.align='center', fig.width=6, fig.height=6, fig.cap="Cobb-Douglas Residual Plots.">>=
-# Use residuals_df to make a graph.
-cd_residuals_df <- subset(residuals_df, subset = modelType=="cd")
-ggplot(data=cd_residuals_df, aes(x=year, y=resid, color=Source)) + 
-  geom_point(size = 1.0) +
-  facet_grid(Country ~ energyType) +
-  labs(x = "", y = "Residuals") + 
-  xy_theme()
-@
-
-%++++++++++++++++++++++++++++++
-\subsection{CES Models}
-\label{sec:CES_Parameter_Estimation}
-%++++++++++++++++++++++++++++++
-
-Information on CES models goes here.
-
-% The CES model without and with energy is given by 
-% Equations~\ref{eq:CES}--\ref{eq:CESekl}. 
-% The \texttt{R} \citep{R} package \texttt{micEconCES} 
-% \citep{Henningsen:2011td} was used to estimate parameters 
-% $\lambda$, $\gamma$, $\delta$, $\delta_1$, $\rho$, and $\rho_1$. 
-% The \texttt{cesEst} function of \texttt{micEconCES} provides 
-% several algorithm options for parameter estimation.
-% The default algorithm (Levenberg-Marquardt) does not respect
-% parameter constraints (see Section~\ref{sec:CES}) and, 
-% in our testing, nearly always violated them, often returning
-% negative values for elasticity of substitution~($\sigma$) parameters.
-% Thus, we used the two fitting algorithms available in \texttt{cesEst} that
-% respect coefficient constraints: \texttt{PORT} and \texttt{L-BFGS-B}. 
-% 
-% Our CES parameter estimation algorithm starts with an eleven-value grid search
-% in $\rho$ and $\rho_1$ (9, 2, 1, 0.43, 0.25, 0.1, -0.1, -0.5, -0.75, -0.9, -0.99),
-% which corresponds to $\sigma$ and $\sigma_1$ values of
-% 0.1, 0.33, 0.5, 0.7, 0.8, 0.9, 1.11, 2, 4, 10, and 100, respectively.
-% During the grid search, values of $\rho$ and $\rho_1$ are fixed,
-% and values of $\lambda$, $\gamma$, $\delta$, and $\delta_1$ are estimated 
-% by gradient search with the \texttt{PORT} and \texttt{L-BFGS-B} algorithms.
-% In all, 121 gradient searches in $\lambda$, $\gamma$, $\delta$, and $\delta_1$
-% at grid points representing all combinations of $\rho$ and $\rho_1$ are attempted.
-% During the grid search portion of our algorithm, starting values for the free parameters
-% are $\lambda$ = 0.015/year, $\delta$ = 0.5, $\delta_1$ = 0.5, 
-% and $\gamma$ is set to a value such that the mean of the residuals is zero
-% by the \texttt{cesEst} function.
-% 
-% Next, a gradient search (using both \texttt{PORT} and \texttt{L-BFGS-B}) 
-% is attempted wherein all fitting parameters 
-% ($\lambda$, $\gamma$, $\delta$, $\delta_1$, $\rho$, and $\rho_1$)
-% are allowed to float. 
-% The start values for fitting parameters are taken from 
-% the grid search fit that provided the lowest $sse$ (Equation~\ref{eq:sse}).
-% 
-% If resampled data are being fitted, a prior fit to historical data is available.
-% In the final step of our algorithm, 
-% a gradient search (using both \texttt{PORT} and \texttt{L-BFGS-B})
-% uses coefficients from the best 
-% fit to historical data as its starting point. 
-% In this final gradient search, all model parameters 
-% ($\lambda$, $\gamma$, $\delta$, $\delta_1$, $\rho$, and $\rho_1$)
-% are considered free parameters.
-% 
-% The fit with lowest $sse$ of all above trials is deemed the winner,
-% and its fitting parameters are used as the model.
-% 
-% \citet{Henningsen:2011td}, 
-% in their detailed analysis of \citet{Kemfert:1998vd}, found that 
-% 
-% \begin{quote}
-% \ldots the Levenberg-Marquardt and the \texttt{PORT} algorithms 
-% are---at least in this study---most likely to find the 
-% coefficients that give the best fit to the model, 
-% where the \texttt{PORT} algorithm can be used to restrict the estimates 
-% to the economically meaningful region.
-% \end{quote}
-% 
-% In our testing, we found that to be mostly true. 
-% \texttt{PORT} nearly always provided lower
-% $sse$ than \texttt{L-BFGS-B}, despite the fact that 
-% \texttt{L-BFGS-B} often reports convergence
-% and \texttt{PORT} does not for the same data
-% (i.e., for the same $y$, $k$, $l$, and $e$ data).
-% 
-% Coefficients for each resampled CES model for all countries and all nests
-% are shown in 
-% Figures~\ref{fig:CES_lambda_gamma_graph_X}--\ref{fig:CES_sigma_delta_graph_X}. 
-% The white crosshair on each graph shows the location 
-% of the fit to historical data. 
-% In Figures~\ref{fig:CES_sigma1_delta1_graph_X} and~\ref{fig:CES_sigma_delta_graph_X},
-% the bottom of the vertical axis represents $\sigma = 0$.
-% The top of the vertical axis represents $\sigma = \infty$.
-% 
-% Note that as $\delta$ or $\delta_1$ approaches 0 (1) 
-% in Equations~\ref{eq:CES}--\ref{eq:CESekl},
-% the corresponding value of $\sigma$ or $\sigma_1$ becomes irrelevant, and
-% resample points along the left (right) edge of
-% Figures \ref{fig:CES_sigma1_delta1_graph_X} and \ref{fig:CES_sigma_delta_graph_X}
-% are equivalent.
-% That is, all points along the left (right) edge of
-% Figures \ref{fig:CES_sigma1_delta1_graph_X} and \ref{fig:CES_sigma_delta_graph_X}
-% have the same $sse$. 
-% As a consequence, 
-% the \texttt{cesEst} fitting algorithm has no way 
-% to discriminate among points along the left (right) edge of
-% Figures \ref{fig:CES_sigma1_delta1_graph_X} and \ref{fig:CES_sigma_delta_graph_X}. 
-% Thus, resample point estimates where $\delta$ or $\delta_1$ approaches 0 (1)
-% tend to cluster at the locations of the initial grid search in 
-% $\sigma$ or $\sigma_1$
-% (0.1, 0.33, 0.5, 0.7, 0.8, 0.9, 1.11, 2, 4, 10, and 100).
-% 
-% <<CES_lambda_gamma_graph_X, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with exergy ($x$).", eval=FALSE>>=
-% cesCoeffsDataX <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
-%                                                                       "(iK + iL) + (iX)", 
-%                                                                       "(iL + iX) + (iK)", 
-%                                                                       "(iX + iK) + (iL)"))
-% standardScatterPlot(data=cesCoeffsDataX, mapping=aes(gamma_coef, lambda), 
-%                     facet_formula=country~nestStrParen, alpha=0.05) +
-%     scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
-%     labs(x=expression(gamma), y=expression(lambda))
-% 
-% @
-% 
-% <<CES_sigma1_delta1_graph_X, fig.pos="H", fig.align='center', fig.width=5, fig.height=5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with exergy ($x$).", eval=FALSE>>=
-% standardScatterPlot(data=cesCoeffsDataX, mapping=aes(delta_1, sigma_1), facet_formula=country~nestStrParen, alpha=0.05) +
-%     coord_trans(y="sigma") +
-%     scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-%     scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-%     labs(x=expression(delta[1]), y=expression(sigma[1]))
-% @
-% 
-% <<CES_sigma_delta_graph_X, fig.pos="H", fig.align='center', fig.width=4.4, fig.height=5, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models using exergy ($x$).", eval=FALSE>>=
-% standardScatterPlot(data=subset(cesCoeffsDataX, nestStrParen != "(iK + iL) + ()"),
-%                     mapping=aes(delta, sigma), facet_formula=country~nestStrParen, alpha=0.05) +
-%     coord_trans(y="sigma") +
-%     scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-%     scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-%     labs(x=expression(delta), y=expression(sigma))
-% @
-% 
-% We can develop pseudo $\alpha$, $\beta$, and $\gamma$ parameters 
-% for the CES model, based on values of $\delta$ and $\delta_1$.
-% Table~\ref{tab:CES_abg_equations} shows the permuted equations for each CES nesting.
-% 
-% \begin{table} \caption{Equations for $\alpha$, $\beta$, and $\gamma$ for the various CES nestings.} 
-% \label{tab:CES_abg_equations} 
-%   \begin{center}
-%     \begin{tabular}{c c c c c} 
-%       Nesting    & Equation        & $\alpha$                & $\beta$                 & $\gamma$                \\
-%       \hline
-%       ($kl$)     & \ref{eq:CES}    & $\delta_1$              & $1 - \delta_1$          & 0                       \\
-%       ($kl$)$e$  & \ref{eq:CESkle} & $\delta \delta_1$       & $\delta (1 - \delta_1)$ & $1 - \delta$            \\   
-%       ($le$)$k$  & \ref{eq:CESlek} & $1 - \delta$            & $\delta \delta_1$       & $\delta (1 - \delta_1)$ \\
-%       ($ek$)$l$  & \ref{eq:CESekl} & $\delta (1 - \delta_1)$ & $1 - \delta$            & $\delta \delta_1$       \\
-%     \end{tabular}
-%   \end{center}
-% \end{table}
-% 
-% Figure~\ref{fig:CES_ternary_graph} shows 
-% $\alpha$, $\beta$, and $\gamma$ parameters for the CES model for all nests and countries.
-% Figure~\ref{fig:CES_ternary_graph} is comparable to
-% the ternary graph for the Cobb-Douglas models, 
-% Figure~\ref{fig:CD_Ternary_Scatter_Graph}.
-% 
-% <<CES_ternary_graphX, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models with exergy ($x$).", eval=FALSE>>=
-% standardTriPlot(data=cesCoeffsDataX, facet_formula=country~nestStrParen)
-% @
-% 
-% Figure~\ref{fig:CES_Spaghetti_Graph} compares CES model predictions 
-% to historical data for all nestings. 
-% As with the Cobb-Douglas results, 
-% historical data are shown as a black line, 
-% the fit to historical data is shown as a white line, and 
-% the gray band encompasses \Sexpr{spaghettiGraphLevel*100}\% of the fits to resampled data.
-% 
-% <<CES_Spaghetti_Graph_X, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models with exergy ($x$).", eval=FALSE>>=
-% cesFittedDataX <- filter(fitted_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
-%                                                                       "(iK + iL) + (iX)", 
-%                                                                       "(iL + iX) + (iK)", 
-%                                                                       "(iX + iK) + (iL)"))
-% spaghettiPlot(data=cesFittedDataX, facet_formula=Country~nestStrParen, level=spaghettiGraphLevel) +
-%     labs(y="Indexed GDP (1900=1 or 1950=1)")
-% @
-% 
-% <<CES_lambda_gamma_graph_U, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with useful work ($u$).", eval=FALSE>>=
-% cesCoeffsDataU <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
-%                                                                       "(iK + iL) + (iU)", 
-%                                                                       "(iL + iU) + (iK)", 
-%                                                                       "(iU + iK) + (iL)"))
-% standardScatterPlot(data=cesCoeffsDataU, mapping=aes(gamma_coef, lambda), facet_formula=country~nestStrParen, alpha=0.05) +
-%     scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
-%     labs(x=expression(gamma), y=expression(lambda))
-% @
-% 
-% <<CES_sigma1_delta1_graph_U, fig.pos="H", fig.align='center', fig.width=5, fig.height=5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with useful work ($u$).", eval=FALSE>>=
-% standardScatterPlot(data=cesCoeffsDataU, mapping=aes(delta_1, sigma_1), facet_formula=country~nestStrParen, alpha=0.05) +
-%     coord_trans(y="sigma") +
-%     scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-%     scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-%     labs(x=expression(delta[1]), y=expression(sigma[1]))
-% @
-% 
-% <<CES_sigma_delta_graph_U, fig.pos="H", fig.align='center', fig.width=4.4, fig.height=5, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models with useful work ($u$).", eval=FALSE>>=
-% standardScatterPlot(data=subset(cesCoeffsDataU, nestStrParen != "(iK + iL) + ()"),
-%                     mapping=aes(delta, sigma), facet_formula=country~nestStrParen, alpha=0.05) +
-%     coord_trans(y="sigma") +
-%     scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-%     scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-%     labs(x=expression(delta), y=expression(sigma))
-% @
-% 
-% <<CES_Spaghetti_Graph_U, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models with useful work ($u$).", eval=FALSE>>=
-% cesFittedDataU <- filter(fitted_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
-%                                                                       "(iK + iL) + (iU)", 
-%                                                                       "(iL + iU) + (iK)", 
-%                                                                       "(iU + iK) + (iL)"))
-% spaghettiPlot(data=cesFittedDataU, facet_formula=Country~nestStrParen, level=spaghettiGraphLevel) +
-%     labs(y="Indexed GDP (1900=1 or 1950=1)")
-% @
-
-%++++++++++++++++++++++++++++++
-\subsection{LINEX Models}
-\label{sec:LINEX_Parameter_Estimation}
-%++++++++++++++++++++++++++++++
-
-The LINEX model is given in Equation~\ref{eq:LINEX}. 
-If the fitting algorithm drives $a_0 \rightarrow 0$, 
-any changes to $c_t$ have no effect on $sse$. 
-Therefore, we transformed the LINEX model into
-%
-\begin{equation} \label{eq:LINEX_transformed}
-  y = \theta A e; 
-  A = \mathrm{e}^{\left[2 a_0 \left(1 - \frac{1}{\rho_k} \right) 
-    + a_1 \left(\vphantom{\frac{1}{\rho_k}}\rho_l - 1 \right)\right]},
-\end{equation}
-%
-\noindent where $a_1 \equiv a_0 c_t$. 
-We used the \texttt{lm} function in \texttt{R}
-\citep{R} to estimate least-squares values for $a_0$ and $a_1$ in 
-Equation~\ref{eq:LINEX_transformed} in log-transformed space. 
-We recovered a value for $c_t$ with $c_t = a_1 / a_0$. 
-Figure~\ref{fig:LINEXq_Resample_Graph}
-shows the coefficients estimated from resampled data.
-
-Figures~\ref{fig:LINEX_GDP_Spaghetti_Graphs_US}--\ref{fig:LINEX_GDP_Spaghetti_Graphs_CN} 
-compare LINEX model predictions to historical data.
-Again, historical data are shown as a black line, 
-the fit to historical data is shown as a white line and 
-the gray band encompasses \Sexpr{spaghettiGraphLevel*100}\% of the fits to resampled data.
-
-<<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=6, fig.height=6, fig.cap="LINEX model resampling results.">>=
-linexCoeffsData <- subset(AllCoeffs, subset = model=="linex")
-standardScatterPlot(data=linexCoeffsData,
-                    mapping=aes(x=a_0, y=c_t, color=Source),
-                    facet_formula=country~energy, alpha=0.05) +
-    scale_x_continuous(limits=c(0.0, 1.0), breaks=c(0.0, 0.5, 1.0)) +
-    scale_y_continuous(limits=c(-10.0, 10.0), breaks=c(10.0, -5.0, 0.0, 5.0, 10.0)) +
-    labs(x=expression(a[0]), y=expression(c[t])) +
-    guides(colour=guide_legend(override.aes = aes(alpha=1)))
-@
-
-<<LINEXq_Resample_Graph_PT, fig.pos="H", fig.align='center', fig.width=6, fig.height=2.5, fig.cap="LINEX model resampling results for PT.">>=
-linexCoeffsData <- subset(AllCoeffs, subset = model=="linex" & country=="PT")
-standardScatterPlot(data=linexCoeffsData,
-                    mapping=aes(x=a_0, y=c_t, color=Source),
-                    facet_formula=country~energy, alpha=0.05) +
-#     scale_x_continuous(limits=c(0.0, 1.0), breaks=c(0.0, 0.5, 1.0)) +
-#     scale_y_continuous(limits=c(-10.0, 10.0), breaks=c(10.0, -5.0, 0.0, 5.0, 10.0)) +
-    labs(x=expression(a[0]), y=expression(c[t])) +
-    guides(colour=guide_legend(override.aes = aes(alpha=1)))
-@
-
-<<LINEX_GDP_Spaghetti_Graphs_US, fig.pos="H", fig.align='center', fig.width=3, fig.height=2.5, fig.cap="US LINEX fitted models.">>=
-linexFittedDataUS <- subset(AllFitted, subset = model=="linex" & Country=="US")
-spaghettiPlot(data=linexFittedDataUS, facet_formula=Source~energy, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<LINEX_GDP_Spaghetti_Graphs_UK, fig.pos="H", fig.align='center', fig.width=3, fig.height=4.5, fig.cap="UK LINEX fitted models.">>=
-linexFittedDataUK <- subset(AllFitted, subset = model=="linex" & Country=="UK")
-spaghettiPlot(data=linexFittedDataUK, facet_formula=Source~energy, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<LINEX_GDP_Spaghetti_Graphs_JP, fig.pos="H", fig.align='center', fig.width=3, fig.height=2.5, fig.cap="JP LINEX fitted models.">>=
-linexFittedDataJP <- subset(AllFitted, subset = model=="linex" & Country=="JP")
-spaghettiPlot(data=linexFittedDataJP, facet_formula=Source~energy, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<LINEX_GDP_Spaghetti_Graphs_AT, fig.pos="H", fig.align='center', fig.width=4, fig.height=3.5, fig.cap="AT LINEX fitted models.">>=
-linexFittedDataAT <- subset(AllFitted, subset = model=="linex" & Country=="AT")
-spaghettiPlot(data=linexFittedDataAT, facet_formula=Source~energy, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<LINEX_GDP_Spaghetti_Graphs_PT, fig.pos="H", fig.align='center', fig.width=4, fig.height=2.5, fig.cap="PT LINEX fitted models.">>=
-linexFittedDataPT <- subset(AllFitted, subset = model=="linex" & Country=="PT")
-spaghettiPlot(data=linexFittedDataPT, facet_formula=Source~energy, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<LINEX_GDP_Spaghetti_Graphs_CN, fig.pos="H", fig.align='center', fig.width=4, fig.height=2.5, fig.cap="CN LINEX fitted models.">>=
-linexFittedDataCN <- subset(AllFitted, subset = model=="linex" & Country=="CN")
-spaghettiPlot(data=linexFittedDataCN, facet_formula=Source~energy, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<LINEX_Residual_Plot, fig.pos="H", fig.align='center', fig.width=5, fig.height=6, fig.cap="LINEX Residual Plots.">>=
-# Use residuals_df to make a graph.
-linex_residuals_df <- subset(residuals_df, subset = modelType=="linex")
-ggplot(data=linex_residuals_df, aes(x=year, y=resid, color=Source)) + 
-  geom_point(size = 1.0) +
-  facet_grid(Country ~ energyType) +
-  labs(x = "", y = "Residuals") + 
-  scale_x_continuous(breaks=c(1960, 1980, 2000)) + 
-  scale_y_continuous(limits=c(-0.3, 0.2)) +
-  xy_theme()
-@
-
-The LINEX model coefficients $a_0$ and $c_t$ imply time-dependent
+
+\citet{Kummel:2010vz} use primary exergy for $e$ and find that 
+both $a$ and $c$ vary with time.
+\citet{Warr:2012cg} use useful work for $u$ and find that 
+constant values of $a$ and $c$ are sufficient to describe economic growth 
+over the long run.
+
+For the Leontief, linear, Cobb-Douglas, and CES production functions, 
+output elasticities are constant with respect to time.
+However, for the LinEx function, 
+the values of coefficients $a$ and $c$ imply time-dependent
 values of $\alpha$, $\beta$, and $\gamma$ as given by the following equations~\citep{Warr:2012cg}:
@@
 \begin{equation} \label{eq:LINEX_alpha}
-  \alpha \equiv \frac{k}{y}\frac{\partial y}{\partial k} = a_0 \left( \frac{l + e}{k} \right) \;,
+  \alpha \equiv \frac{k}{y}\frac{\partial y}{\partial k} = a \left( \frac{l + e}{k} \right) \;,
 \end{equation}
@@
 \begin{equation} \label{eq:LINEX_beta}
-  \beta \equiv \frac{l}{y} \frac{\partial y}{\partial l} = a_0 \left[ c_t \left( \frac{l}{e}\right) - \frac{l}{k} \right] \;,
+  \beta \equiv \frac{l}{y} \frac{\partial y}{\partial l} = a \left[ c \left( \frac{l}{e}\right) - \frac{l}{k} \right] \;,
 \end{equation}
@@
   \gamma \equiv \frac{e}{y} \frac{\partial y}{\partial e} 
-         = 1 - a_0 \left[ \frac{e}{k} + c_t \frac{l}{e} \right] 
+         = 1 - a \left[ \frac{e}{k} + c \frac{l}{e} \right] 
          = 1 - \alpha - \beta \;.
 \end{equation}
-
-\noindent Thus, each fitted model implies a trajectory of $\alpha$, $\beta$, and $\gamma$ values as time proceeds.
-If the trajectory stays within the triangle, 
-the constraints on $\alpha$, $\beta$, and $\gamma$ are respected.
-Conversely, if the trajectory goes outside the triangle, the constraints have been violated.
-
-Figure~\ref{fig:LINEX_abg_traj_graph_REXS_UK_U}
-shows trajectories for the UK and useful work ($u$) from the REXS data set.
-
-<<LINEX_abg_traj_graph_REXS_UK_U, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="UK LINEX trajectory for REXS with $u$.">>=
-triPlot(data=fortify(REXS1960_Models$REXS1960$UK$linex$`iK+iL+iU`), grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1960")
-@
-
-Figure~\ref{fig:LINEX_abg_traj_graph_IST_UK_U}
-shows trajectories for the UK and useful work ($u$) from the IST data set.
-
-<<LINEX_abg_traj_graph_IST_UK_U, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="UK LINEX trajectory for IST with $u$.">>=
-triPlot(data=fortify(IST_Models$IST$UK$linex$`iK+iL+iU`), grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1960")
-@
-
-Figure~\ref{fig:LINEX_abg_traj_graph_Leeds_UK_U}
-shows trajectories for the UK and useful work ($u$) from the Leeds data set.
-
-<<LINEX_abg_traj_graph_Leeds_UK_U, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="UK LINEX trajectory for Leeds with $u$.">>=
-triPlot(data=fortify(Leeds_Models$Leeds$UK$linex$`iK+iL+iU`), grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1960")
-@
-
-% In our testing, Iran is the only country for which the trajectory stays within 
-% the constraint triangle for the entire time period.
-% Thus, in our fitted models, the LINEX model is nearly always
-% violating constraints on $\alpha$, $\beta$, and $\gamma$.
-% If the LINEX model were made to respect the constraints,
-% it would fit worse than it already does for those countries where
-% the constraints are violated (that is, for every country except Iran).
-% We did nothing to correct this situation, because it is not clear what should be done.
-% \citet{Warr:2012cg} constrained the values of $a_0$ and $c_t$, while still holding them constant
-% for the entire time series, such that the constraints on $\alpha$, $\beta$, and $\gamma$
-% were respected.
-% But, Warr's approach necessarily leads to larger $sse$ values than unconstrained fitting.
-% Because unconstrained LINEX models already fit worse than 
-% constrained Cobb-Douglas and CES models,
-% we chose to report the unconstrained LINEX model fits in this paper.
-% Constraining $\alpha = 0$ in the case of China would imply that either
-% $a_0$ or $c_t$ or both varied with time.
-% At that point, $a_0$ and $c_t$ are no longer fitted parameters of the model, 
-% and we have a different model: it is no longer LINEX.
-
-%++++++++++++++++++++++++++++++
-\subsection{Parameter Estimation Summary}
-\label{sec:Parameter_Estimation_Summary}
-%++++++++++++++++++++++++++++++
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion of Results}
-\label{sec:Discussion_of_Results}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \section*{Reproducible Research}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% In the spirit of Reproducible Research \citep{Gandrud:2013vx}, 
-% all data, spreadsheets, \texttt{R} code \citep{R}, and other materials 
-% associated with this paper can be found at\\*
-% \protect\url{https://github.com/MatthewHeun/Econ-Growth-R-Analysis}.
 
@@
 %%\bibliography{<your-bib-database>}
-\bibliography{Paper2.bib}
+\bibliography{ProdFuncPrimer.bib}
 

### 2014-11-28 Articles/Article_EcolEcon_2014/Paper2.Rnw
Uncommented many lines for CES model.

@@
 
-% The CES model without and with energy is given by 
-% Equations~\ref{eq:CES}--\ref{eq:CESekl}. 
-% The \texttt{R} \citep{R} package \texttt{micEconCES} 
-% \citep{Henningsen:2011td} was used to estimate parameters 
-% $\lambda$, $\gamma$, $\delta$, $\delta_1$, $\rho$, and $\rho_1$. 
-% The \texttt{cesEst} function of \texttt{micEconCES} provides 
-% several algorithm options for parameter estimation.
-% The default algorithm (Levenberg-Marquardt) does not respect
-% parameter constraints (see Section~\ref{sec:CES}) and, 
-% in our testing, nearly always violated them, often returning
-% negative values for elasticity of substitution~($\sigma$) parameters.
-% Thus, we used the two fitting algorithms available in \texttt{cesEst} that
-% respect coefficient constraints: \texttt{PORT} and \texttt{L-BFGS-B}. 
-% 
-% Our CES parameter estimation algorithm starts with an eleven-value grid search
-% in $\rho$ and $\rho_1$ (9, 2, 1, 0.43, 0.25, 0.1, -0.1, -0.5, -0.75, -0.9, -0.99),
-% which corresponds to $\sigma$ and $\sigma_1$ values of
-% 0.1, 0.33, 0.5, 0.7, 0.8, 0.9, 1.11, 2, 4, 10, and 100, respectively.
-% During the grid search, values of $\rho$ and $\rho_1$ are fixed,
-% and values of $\lambda$, $\gamma$, $\delta$, and $\delta_1$ are estimated 
-% by gradient search with the \texttt{PORT} and \texttt{L-BFGS-B} algorithms.
-% In all, 121 gradient searches in $\lambda$, $\gamma$, $\delta$, and $\delta_1$
-% at grid points representing all combinations of $\rho$ and $\rho_1$ are attempted.
-% During the grid search portion of our algorithm, starting values for the free parameters
-% are $\lambda$ = 0.015/year, $\delta$ = 0.5, $\delta_1$ = 0.5, 
-% and $\gamma$ is set to a value such that the mean of the residuals is zero
-% by the \texttt{cesEst} function.
-% 
-% Next, a gradient search (using both \texttt{PORT} and \texttt{L-BFGS-B}) 
-% is attempted wherein all fitting parameters 
-% ($\lambda$, $\gamma$, $\delta$, $\delta_1$, $\rho$, and $\rho_1$)
-% are allowed to float. 
-% The start values for fitting parameters are taken from 
-% the grid search fit that provided the lowest $sse$ (Equation~\ref{eq:sse}).
-% 
-% If resampled data are being fitted, a prior fit to historical data is available.
-% In the final step of our algorithm, 
-% a gradient search (using both \texttt{PORT} and \texttt{L-BFGS-B})
-% uses coefficients from the best 
-% fit to historical data as its starting point. 
-% In this final gradient search, all model parameters 
-% ($\lambda$, $\gamma$, $\delta$, $\delta_1$, $\rho$, and $\rho_1$)
-% are considered free parameters.
-% 
-% The fit with lowest $sse$ of all above trials is deemed the winner,
-% and its fitting parameters are used as the model.
-% 
-% \citet{Henningsen:2011td}, 
-% in their detailed analysis of \citet{Kemfert:1998vd}, found that 
-% 
-% \begin{quote}
-% \ldots the Levenberg-Marquardt and the \texttt{PORT} algorithms 
-% are---at least in this study---most likely to find the 
-% coefficients that give the best fit to the model, 
-% where the \texttt{PORT} algorithm can be used to restrict the estimates 
-% to the economically meaningful region.
-% \end{quote}
-% 
-% In our testing, we found that to be mostly true. 
-% \texttt{PORT} nearly always provided lower
-% $sse$ than \texttt{L-BFGS-B}, despite the fact that 
-% \texttt{L-BFGS-B} often reports convergence
-% and \texttt{PORT} does not for the same data
-% (i.e., for the same $y$, $k$, $l$, and $e$ data).
-% 
-% Coefficients for each resampled CES model for all countries and all nests
-% are shown in 
-% Figures~\ref{fig:CES_lambda_gamma_graph_X}--\ref{fig:CES_sigma_delta_graph_X}. 
-% The white crosshair on each graph shows the location 
-% of the fit to historical data. 
-% In Figures~\ref{fig:CES_sigma1_delta1_graph_X} and~\ref{fig:CES_sigma_delta_graph_X},
-% the bottom of the vertical axis represents $\sigma = 0$.
-% The top of the vertical axis represents $\sigma = \infty$.
-% 
-% Note that as $\delta$ or $\delta_1$ approaches 0 (1) 
-% in Equations~\ref{eq:CES}--\ref{eq:CESekl},
-% the corresponding value of $\sigma$ or $\sigma_1$ becomes irrelevant, and
-% resample points along the left (right) edge of
-% Figures \ref{fig:CES_sigma1_delta1_graph_X} and \ref{fig:CES_sigma_delta_graph_X}
-% are equivalent.
-% That is, all points along the left (right) edge of
-% Figures \ref{fig:CES_sigma1_delta1_graph_X} and \ref{fig:CES_sigma_delta_graph_X}
-% have the same $sse$. 
-% As a consequence, 
-% the \texttt{cesEst} fitting algorithm has no way 
-% to discriminate among points along the left (right) edge of
-% Figures \ref{fig:CES_sigma1_delta1_graph_X} and \ref{fig:CES_sigma_delta_graph_X}. 
-% Thus, resample point estimates where $\delta$ or $\delta_1$ approaches 0 (1)
-% tend to cluster at the locations of the initial grid search in 
-% $\sigma$ or $\sigma_1$
-% (0.1, 0.33, 0.5, 0.7, 0.8, 0.9, 1.11, 2, 4, 10, and 100).
-% 
-% <<CES_lambda_gamma_graph_X, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with exergy ($x$).", eval=FALSE>>=
-% cesCoeffsDataX <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
-%                                                                       "(iK + iL) + (iX)", 
-%                                                                       "(iL + iX) + (iK)", 
-%                                                                       "(iX + iK) + (iL)"))
-% standardScatterPlot(data=cesCoeffsDataX, mapping=aes(gamma_coef, lambda), 
-%                     facet_formula=country~nestStrParen, alpha=0.05) +
-%     scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
-%     labs(x=expression(gamma), y=expression(lambda))
-% 
-% @
-% 
-% <<CES_sigma1_delta1_graph_X, fig.pos="H", fig.align='center', fig.width=5, fig.height=5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with exergy ($x$).", eval=FALSE>>=
-% standardScatterPlot(data=cesCoeffsDataX, mapping=aes(delta_1, sigma_1), facet_formula=country~nestStrParen, alpha=0.05) +
-%     coord_trans(y="sigma") +
-%     scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-%     scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-%     labs(x=expression(delta[1]), y=expression(sigma[1]))
-% @
-% 
-% <<CES_sigma_delta_graph_X, fig.pos="H", fig.align='center', fig.width=4.4, fig.height=5, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models using exergy ($x$).", eval=FALSE>>=
-% standardScatterPlot(data=subset(cesCoeffsDataX, nestStrParen != "(iK + iL) + ()"),
-%                     mapping=aes(delta, sigma), facet_formula=country~nestStrParen, alpha=0.05) +
-%     coord_trans(y="sigma") +
-%     scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-%     scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-%     labs(x=expression(delta), y=expression(sigma))
-% @
-% 
+The CES model without and with energy is given by 
+Equations~\ref{eq:CES}--\ref{eq:CESekl}. 
+The \texttt{R} \citep{R} package \texttt{micEconCES} 
+\citep{Henningsen:2011td} was used to estimate parameters 
+$\lambda$, $\gamma$, $\delta$, $\delta_1$, $\rho$, and $\rho_1$. 
+The \texttt{cesEst} function of \texttt{micEconCES} provides 
+several algorithm options for parameter estimation.
+The default algorithm (Levenberg-Marquardt) does not respect
+parameter constraints (see Section~\ref{sec:CES}) and, 
+in our testing, nearly always violated them, often returning
+negative values for elasticity of substitution~($\sigma$) parameters.
+Thus, we used the two fitting algorithms available in \texttt{cesEst} that
+respect coefficient constraints: \texttt{PORT} and \texttt{L-BFGS-B}.
+
+Our CES parameter estimation algorithm starts with an eleven-value grid search
+in $\rho$ and $\rho_1$ (9, 2, 1, 0.43, 0.25, 0.1, -0.1, -0.5, -0.75, -0.9, -0.99),
+which corresponds to $\sigma$ and $\sigma_1$ values of
+0.1, 0.33, 0.5, 0.7, 0.8, 0.9, 1.11, 2, 4, 10, and 100, respectively.
+During the grid search, values of $\rho$ and $\rho_1$ are fixed,
+and values of $\lambda$, $\gamma$, $\delta$, and $\delta_1$ are estimated 
+by gradient search with the \texttt{PORT} and \texttt{L-BFGS-B} algorithms.
+In all, 121 gradient searches in $\lambda$, $\gamma$, $\delta$, and $\delta_1$
+at grid points representing all combinations of $\rho$ and $\rho_1$ are attempted.
+During the grid search portion of our algorithm, starting values for the free parameters
+are $\lambda$ = 0.015/year, $\delta$ = 0.5, $\delta_1$ = 0.5, 
+and $\gamma$ is set to a value such that the mean of the residuals is zero
+by the \texttt{cesEst} function.
+
+Next, a gradient search (using both \texttt{PORT} and \texttt{L-BFGS-B}) 
+is attempted wherein all fitting parameters 
+($\lambda$, $\gamma$, $\delta$, $\delta_1$, $\rho$, and $\rho_1$)
+are allowed to float. 
+The start values for fitting parameters are taken from 
+the grid search fit that provided the lowest $sse$ (Equation~\ref{eq:sse}).
+
+If resampled data are being fitted, a prior fit to historical data is available.
+In the final step of our algorithm, 
+a gradient search (using both \texttt{PORT} and \texttt{L-BFGS-B})
+uses coefficients from the best 
+fit to historical data as its starting point. 
+In this final gradient search, all model parameters 
+($\lambda$, $\gamma$, $\delta$, $\delta_1$, $\rho$, and $\rho_1$)
+are considered free parameters.
+
+The fit with lowest $sse$ of all above trials is deemed the winner,
+and its fitting parameters are used as the model.
+
+\citet{Henningsen:2011td}, 
+in their detailed analysis of \citet{Kemfert:1998vd}, found that
+
+\begin{quote}
+\ldots the Levenberg-Marquardt and the \texttt{PORT} algorithms 
+are---at least in this study---most likely to find the 
+coefficients that give the best fit to the model, 
+where the \texttt{PORT} algorithm can be used to restrict the estimates 
+to the economically meaningful region.
+\end{quote}
+
+In our testing, we found that to be mostly true. 
+\texttt{PORT} nearly always provided lower
+$sse$ than \texttt{L-BFGS-B}, despite the fact that 
+\texttt{L-BFGS-B} often reports convergence
+and \texttt{PORT} does not for the same data
+(i.e., for the same $y$, $k$, $l$, and $e$ data).
+
+Coefficients for each resampled CES model for all countries and all nests
+are shown in 
+Figures~\ref{fig:CES_lambda_gamma_graph_X}--\ref{fig:CES_sigma_delta_graph_X}. 
+The white crosshair on each graph shows the location 
+of the fit to historical data. 
+In Figures~\ref{fig:CES_sigma1_delta1_graph_X} and~\ref{fig:CES_sigma_delta_graph_X},
+the bottom of the vertical axis represents $\sigma = 0$.
+The top of the vertical axis represents $\sigma = \infty$.
+
+Note that as $\delta$ or $\delta_1$ approaches 0 (1) 
+in Equations~\ref{eq:CES}--\ref{eq:CESekl},
+the corresponding value of $\sigma$ or $\sigma_1$ becomes irrelevant, and
+resample points along the left (right) edge of
+Figures \ref{fig:CES_sigma1_delta1_graph_X} and \ref{fig:CES_sigma_delta_graph_X}
+are equivalent.
+That is, all points along the left (right) edge of
+Figures \ref{fig:CES_sigma1_delta1_graph_X} and \ref{fig:CES_sigma_delta_graph_X}
+have the same $sse$. 
+As a consequence, 
+the \texttt{cesEst} fitting algorithm has no way 
+to discriminate among points along the left (right) edge of
+Figures \ref{fig:CES_sigma1_delta1_graph_X} and \ref{fig:CES_sigma_delta_graph_X}. 
+Thus, resample point estimates where $\delta$ or $\delta_1$ approaches 0 (1)
+tend to cluster at the locations of the initial grid search in 
+$\sigma$ or $\sigma_1$
+(0.1, 0.33, 0.5, 0.7, 0.8, 0.9, 1.11, 2, 4, 10, and 100).
+
+<<CES_lambda_gamma_graph_X, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with primary exergy ($x_p$).", eval=FALSE>>=
+cesCoeffsDataX <- filter(AllCoeffs, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
+                                                                      "(iK + iL) + (iXp)", 
+                                                                      "(iL + iXp) + (iK)", 
+                                                                      "(iXp + iK) + (iL)"))
+standardScatterPlot(data=cesCoeffsDataX, mapping=aes(x=gamma_coef, y=lambda, color=Source), 
+                    facet_formula=country~nestStrParen, alpha=0.05) +
+    scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
+    labs(x=expression(gamma), y=expression(lambda)) + 
+    guides(colour=guide_legend(override.aes = aes(alpha=1)))
+@
+
+<<CES_sigma1_delta1_graph_X, fig.pos="H", fig.align='center', fig.width=5, fig.height=5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with primary exergy ($x_p$).", eval=FALSE>>=
+standardScatterPlot(data=cesCoeffsDataX, mapping=aes(x=delta_1, y=sigma_1, color=Source), 
+                    facet_formula=country~nestStrParen, alpha=0.05) +
+    coord_trans(y="sigma") +
+    scale_x_continuous(breaks=c(0, 0.5, 1.0)) +
+    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
+    labs(x=expression(delta[1]), y=expression(sigma[1])) + 
+    guides(colour=guide_legend(override.aes = aes(alpha=1)))
+@
+
+<<CES_sigma_delta_graph_X, fig.pos="H", fig.align='center', fig.width=4.4, fig.height=5, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models using exergy ($x_p$).", eval=FALSE>>=
+standardScatterPlot(data=subset(cesCoeffsDataX, nestStrParen != "(iK + iL) + ()"),
+                    mapping=aes(x=delta, y=sigma, color=Source), 
+                    facet_formula=country~nestStrParen, alpha=0.05) +
+    coord_trans(y="sigma") +
+    scale_x_continuous(breaks=c(0, 0.5, 1.0)) +
+    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
+    labs(x=expression(delta), y=expression(sigma)) +
+    guides(colour=guide_legend(override.aes = aes(alpha=1)))
+@
+
 % We can develop pseudo $\alpha$, $\beta$, and $\gamma$ parameters 

### 2014-11-28 Articles/Prod Func Primer/ProdFuncPrimer.tex
Minor edits to Primer.

@@
 \usepackage{booktabs}   % For nice tables
+\usepackage{nicefrac}   % For beautiful fractions
 
@@
 \begin{equation} \label{eq:rho_k}
-  \rho_k \equiv \frac{k}{(1/2)(l+e)}
+  \rho_k \equiv \frac{k}{(\nicefrac{1}{2})(l+e)}
 \end{equation}
@@
 An economy that increases 
-capital stock ($k$) and labor ($l$) at the same rate as energy will have
+capital stock ($k$) and labor ($l$) at the same rate as energy ($e$) will have
 capital and labor efficiency ratios ($\rho_k$ and $\rho_l$, respectively) of unity.
@@
 According to the LiNex model, an economy that increases 
-capital stock ($k$) without a commensurate increase in labor ($l$) 
-and energy ($e$) will experience an increase in output ($y$) in excess 
-of its increase of energy consumption ($e$), because
+capital stock ($k$) without a commensurate increase in the average of labor
+and energy [$(\nicefrac{1}{2})(l+e)$] will experience an increase in output ($y$) in excess 
+of its increase of energy consumption ($e$), because $\rho_k > 1$ and
 %
@@
 Similarly, an economy benefits by increasing labor ($l$) 
-without a commensurate increase in energy ($e$). 
+without a commensurate increase in energy ($e$), because $\rho_l > 0$. 
 Thus, $\rho_k$ is an 
-efficiency of using additional labor and energy to make 
-additional capital stock available to the economy, 
-and $\rho_l$ is an efficiency of using additional energy to make 
-additional labor available to the economy. 
-Increases in $\rho_k$ and $\rho_l$ provide upward pressure on economic output ($y$),
-as the only factor of production ($e$) is used more efficiently.
+efficiency of using additional labor~($l$) and energy~($e$) to make 
+additional capital stock~($k$) available to the economy, 
+and $\rho_l$ is an efficiency of using additional energy~($e$) to make 
+additional labor~($l$) available to the economy. 
+Increases in $\rho_k$ and $\rho_l$ provide upward pressure on economic output~($y$),
+as the only factor of production~($e$) is used more efficiently.
 
@@
 and the parameter $c$ represents the relative importance 
-of the labor efficiency term ($\rho_l$) compared to the capital stock efficiency term ($\rho_k$).
+of the labor efficiency term~($\rho_l$) compared to the capital stock efficiency term~($\rho_k$).
 
@@
 both $a$ and $c$ vary with time.
-\citet{Warr:2012cg} use useful work for $u$ and find that 
+\citet{Warr:2012cg} use useful work for $e$ and find that 
 constant values of $a$ and $c$ are sufficient to describe economic growth 

### 2014-11-29 Articles/Prod Func Primer/ProdFuncPrimer.tex
Updates to primer.

@@
 Continuing the cooking analogy, consider producing toast ($Y$) 
-with a fatty substance~(butter or margarine).
+with a fatty substance~(butter, $B$, or margarine, $M$).
 %
@@
   \footnote{
-  Butter and margarine may be perfect substitutes for all but the most discerning toast consumers.
+  Butter and margarine are perfect substitutes for all but the most discerning toast consumers.
   }%
@@
 of substitution~($\sigma_1$) between capital~($k$) and labor~($l$).
-The elasticity of substitution 
+The elasticity of substitution~($\sigma_1$)
 between capital~($k$) and labor~($l$) is related to $\rho_1$ and given by 
@@
 \includegraphics[width=0.8\linewidth]{figure/CESIsoquants.png}
-\caption[CES isoquants]{CES isoquants (lines of constant output). 
-$K$ is capital and $N$ is labor.~\citep{Klump:2011aa}}
+\caption[CES isoquants]{CES isoquants (lines of constant output, $Y$). 
+$K$ is capital and $N$ is labor. From \citet{Klump:2011aa}.}
 \label{fig:CES_isoquants}
@@
     }%
-) function is given by K\"{u}mmel in several places as
+) function is given by K\"{u}mmel in several places~\citep{Kummel:1980wx,Kummel:1982vy,
+Kummel:1985vz,Kummel:1989tf,Kummel:2002tx,Kummel:2010vz} as
 %
 \begin{equation} \label{eq:LinEx-kummel}
-  y = e \exp{\left[ a \left( 2 - \frac{l + e}{k} \right)  + a c \left( \frac{l}{e} - 1 \right)\right]}
+  y = e \exp{\left[ a \left( 2 - \frac{l + e}{k} \right)  + a c \left( \frac{l}{e} - 1 \right)\right]} \; .
 \end{equation}
@@
 %
-The LinEx function was derived from thermodynamic considerations
-\citep{Kummel:1980wx,Kummel:1982vy,Kummel:1985vz,Kummel:1989tf,Kummel:2002tx,Kummel:2010vz}. 
+The LinEx function was derived from thermodynamic considerations. 
 A key feature of the derivation involves
@@
   \footnote{
-  As an aside, I'm not sure the constraints 
+  As an aside, I question whether the constraints 
   described in Section~\ref{sec:Leontief} are the right ones.
@@
 (\ref{eq:rho_l}) labor increase relative to energy.
-The effect of energy ($e$) on output ($y$) is enhanced if either
+The effect of energy ($e$) on output ($y$) is enhanced when $A > 1$,
+which occurs if either
 %
@@
 \item{capital stock ($k$) has increased more than the average 
-      of labor ($l$) and energy ($e$), i.e. if $\rho_k >$ 1, or}
+      of labor ($l$) and energy ($e$), i.e. if $\rho_k >$ 1 or}
 \item{labor ($l$) has increased more than energy ($e$), i.e. if $\rho_l >$ 1.}
@@
 Similarly, an economy benefits by increasing labor ($l$) 
-without a commensurate increase in energy ($e$), because $\rho_l > 0$. 
+without a commensurate increase in energy ($e$), because $\rho_l > 1$. 
 Thus, $\rho_k$ is an 
@@
 and the parameter $c$ represents the relative importance 
-of the labor efficiency term~($\rho_l$) compared to the capital stock efficiency term~($\rho_k$).
+of labor efficiency~($\rho_l$) compared to capital stock efficiency~($\rho_k$).
 
@@
 values of $\alpha$, $\beta$, and $\gamma$ as given by the following equations~\citep{Warr:2012cg}:
-
+%
 \begin{equation} \label{eq:LINEX_alpha}
@@
 \end{equation}
-
+%
 \noindent{}and
-
+%
 \begin{equation} \label{eq:LINEX_beta_2}
@@
 \end{equation}
+%
+The LinEx model assumes constant returns to scale.
 

### 2014-11-30 Workflow/Workflow.Rmd
Updated location of r-versions script.
Updated Workflow.R about Sources. PostProcess.R now accepts multiple Sources.

@@
 ### Create the batch script
-* Run the script `r-versions` on `dahl` to see which nodes are operational and which nodes have a working version of `R`.
+* Run the script `r-versions` on `dahl` to see which nodes are operational and which nodes have a working version of `R`. (This script is located at `/usr/local/bin/r-versions`.)
 * Create the file `Scripts/<Source>_batch.bash` file.
@@
     + `data_postprocessed/<Source>_Fitted.rda`.  
+* `PostProcess.R` will accept multiple `<Source>`s. E.g., `Scripts/PostProcess.R -S IST,Leeds,SUN,REXS1960`
 * Note that this command must be issued from a node of the cluster (e.g., `node-00`), not from `fs1.calvin.edu`.

### 2014-11-30 Articles/Article_EcolEcon_2014/Paper2.Rnw
Cleaned up a bunch of \noindents.

@@
 %
-\noindent where 
+where 
 $y \equiv Y/Y_{0}$,
@@
 %
-\noindent Equation~\ref{eq:CES} is a CES production function with 
+Equation~\ref{eq:CES} is a CES production function with 
 capital stock ($k$) and labor ($l$) factors of production. 
@@
 %
-\noindent Note that the $\rho$ ($\sigma$) and $\delta$ parameters have different
+Note that the $\rho$ ($\sigma$) and $\delta$ parameters have different
 meanings that depend upon the nesting of the factors of production.
@@
 %
-\noindent to ensure $\alpha + \beta = 1$ for constant returns to scale. 
+to ensure $\alpha + \beta = 1$ for constant returns to scale. 
 $\theta$, $\lambda$, and $\alpha$ were estimated by the 
@@
 %
-\noindent where $a_1 \equiv a_0 c_t$. 
+where $a_1 \equiv a_0 c_t$. 
 We used the \texttt{lm} function in \texttt{R}
@@
 values of $\alpha$, $\beta$, and $\gamma$ as given by the following equations~\citep{Warr:2012cg}:
-
+%
 \begin{equation} \label{eq:LINEX_alpha}
-  \alpha \equiv \frac{k}{y}\frac{\partial y}{\partial k} = a_0 \left( \frac{l + e}{k} \right) \;,
-\end{equation}
-
+  \alpha \equiv \frac{k}{y}\frac{\partial y}{\partial k} = a_0 \left( \frac{l + e}{k} \right) \; ,
+\end{equation}
+%
 \begin{equation} \label{eq:LINEX_beta}
@@
 \end{equation}
-
-\noindent{}and
-
+%
+and
+%
 \begin{equation} \label{eq:LINEX_beta_2}
@@
 \end{equation}
-
-\noindent Thus, each fitted model implies a trajectory of $\alpha$, $\beta$, and $\gamma$ values as time proceeds.
+%
+Thus, each fitted model implies a trajectory of $\alpha$, $\beta$, and $\gamma$ values as time proceeds.
 If the trajectory stays within the triangle, 

### 2014-11-30 Articles/Article_EcolEcon_2014/Paper2.Rnw
Uncommented and fixed a few things. Adding new CES graphs.

@@
 require(ggplot2)
-require(dplyr) # Load in this order or the mutate and arrange functions will not work as desired.
+require(dplyr)
 # Provides access to data melting. 
@@
 
-Information on CES models goes here.
-
 The CES model without and with energy is given by 
@@
 
-<<CES_lambda_gamma_graph_X, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with primary exergy ($x_p$).", eval=FALSE>>=
+<<CES_lambda_gamma_graph_X, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6.0, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with primary exergy ($x_p$).">>=
 cesCoeffsDataX <- filter(AllCoeffs, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
@@
 
-<<CES_sigma1_delta1_graph_X, fig.pos="H", fig.align='center', fig.width=5, fig.height=5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with primary exergy ($x_p$).", eval=FALSE>>=
+<<CES_sigma1_delta1_graph_X, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6.5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with primary exergy ($x_p$).">>=
 standardScatterPlot(data=cesCoeffsDataX, mapping=aes(x=delta_1, y=sigma_1, color=Source), 
@@
 
-<<CES_sigma_delta_graph_X, fig.pos="H", fig.align='center', fig.width=4.4, fig.height=5, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models using exergy ($x_p$).", eval=FALSE>>=
+<<CES_sigma_delta_graph_X, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=6, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models using primary exergy ($x_p$).">>=
 standardScatterPlot(data=subset(cesCoeffsDataX, nestStrParen != "(iK + iL) + ()"),
@@
 
-% We can develop pseudo $\alpha$, $\beta$, and $\gamma$ parameters 
-% for the CES model, based on values of $\delta$ and $\delta_1$.
-% Table~\ref{tab:CES_abg_equations} shows the permuted equations for each CES nesting.
-% 
-% \begin{table} \caption{Equations for $\alpha$, $\beta$, and $\gamma$ for the various CES nestings.} 
-% \label{tab:CES_abg_equations} 
-%   \begin{center}
-%     \begin{tabular}{c c c c c} 
-%       Nesting    & Equation        & $\alpha$                & $\beta$                 & $\gamma$                \\
-%       \hline
-%       ($kl$)     & \ref{eq:CES}    & $\delta_1$              & $1 - \delta_1$          & 0                       \\
-%       ($kl$)$e$  & \ref{eq:CESkle} & $\delta \delta_1$       & $\delta (1 - \delta_1)$ & $1 - \delta$            \\   
-%       ($le$)$k$  & \ref{eq:CESlek} & $1 - \delta$            & $\delta \delta_1$       & $\delta (1 - \delta_1)$ \\
-%       ($ek$)$l$  & \ref{eq:CESekl} & $\delta (1 - \delta_1)$ & $1 - \delta$            & $\delta \delta_1$       \\
-%     \end{tabular}
-%   \end{center}
-% \end{table}
-% 
-% Figure~\ref{fig:CES_ternary_graph} shows 
-% $\alpha$, $\beta$, and $\gamma$ parameters for the CES model for all nests and countries.
-% Figure~\ref{fig:CES_ternary_graph} is comparable to
-% the ternary graph for the Cobb-Douglas models, 
-% Figure~\ref{fig:CD_Ternary_Scatter_Graph}.
-% 
-% <<CES_ternary_graphX, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models with exergy ($x$).", eval=FALSE>>=
-% standardTriPlot(data=cesCoeffsDataX, facet_formula=country~nestStrParen)
-% @
-% 
+We can develop pseudo $\alpha$, $\beta$, and $\gamma$ parameters 
+for the CES model, based on values of $\delta$ and $\delta_1$.
+Table~\ref{tab:CES_abg_equations} shows the permuted equations for each CES nesting.
+
+\begin{table} \caption{Equations for $\alpha$, $\beta$, and $\gamma$ for the various CES nestings.} 
+\label{tab:CES_abg_equations} 
+  \begin{center}
+    \begin{tabular}{c c c c c} 
+      Nesting    & Equation        & $\alpha$                & $\beta$                 & $\gamma$                \\
+      \hline
+      ($kl$)     & \ref{eq:CES}    & $\delta_1$              & $1 - \delta_1$          & 0                       \\
+      ($kl$)$e$  & \ref{eq:CESkle} & $\delta \delta_1$       & $\delta (1 - \delta_1)$ & $1 - \delta$            \\   
+      ($le$)$k$  & \ref{eq:CESlek} & $1 - \delta$            & $\delta \delta_1$       & $\delta (1 - \delta_1)$ \\
+      ($ek$)$l$  & \ref{eq:CESekl} & $\delta (1 - \delta_1)$ & $1 - \delta$            & $\delta \delta_1$       \\
+    \end{tabular}
+  \end{center}
+\end{table}
+
+Figure~\ref{fig:CES_ternary_graph} shows 
+$\alpha$, $\beta$, and $\gamma$ parameters for the CES model for all nests and countries.
+Figure~\ref{fig:CES_ternary_graph} is comparable to
+the ternary graph for the Cobb-Douglas models, 
+Figure~\ref{fig:CD_Ternary_Scatter_Graph}.
+
+<<CES_ternary_graphX, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models with exergy ($x$).", eval=FALSE>>=
+standardTriPlot(data=cesCoeffsDataX, 
+                mapping=aes(color=Source), 
+                facet_formula=country~nestStrParen) +
+  guides(colour=guide_legend(override.aes = aes(alpha=1)))
+@
+
 % Figure~\ref{fig:CES_Spaghetti_Graph} compares CES model predictions 

### 2014-11-30 Articles/Prod Func Primer/ProdFuncPrimer.tex
Edited the Primer.

@@
 and $\lambda$ is the Solow residual.
+Constant returns to scale is represented by $\alpha + \beta + \gamma = 1$.
+
+%++++++++++++++++++++++++++++++
+\subsection{Cobb-Douglas and substutitability} 
+\label{sec:CD-substitution}
+%++++++++++++++++++++++++++++++
 
@@
 without a concomitant increase in the others ($l$ or $e$) 
-will result in an increase of output ($y$), provided that the output elasticity 
+will always result in an increase of output ($y$), provided that the output elasticity 
 ($\alpha$) is non-zero.
+
+%++++++++++++++++++++++++++++++
+\subsection{The cost share theorem} 
+\label{sec:CD-cost-share}
+%++++++++++++++++++++++++++++++
+
+The so-called ``cost share theorem'' says that coefficients ($\alpha$, $\beta$, and $\gamma$) 
+in the Cobb-Douglas model are equal to cost shares in the economy.~\citep[p.~150]{Kummel:2010vz}
+\citet[Eqn.~12]{Kummel:2010vz} shows (through the use of Lagrange multipliers) 
+that the ``cost share theorem'' is strictly true for a profit maximizing economy
+if and only if there are \emph{no technological constraints} on economic production.
+
+There are many technological constraints that affect economic production, such as
+the Second Law of Thermodynamics and
+the productive capability and energy efficiency 
+of capital~($k$) at any instant in time.
 
@@
 %++++++++++++++++++++++++++++++
-\subsection{CES with Two Factors of Production} 
+\subsection{CES with two factors of production} 
 \label{sec:CES-2}
@@
 %++++++++++++++++++++++++++++++
-\subsection{CES with Three Factors of Production} 
+\subsection{CES with three factors of production} 
 \label{sec:CES-3}
@@
 \end{equation}
+
+%++++++++++++++++++++++++++++++
+\subsection{CES assumptions} 
+\label{sec:CES_assumptions}
+%++++++++++++++++++++++++++++++
+
+The CES production function was derived by assuming profit maximization
+and perfect competition in the markets for both output and 
+factors of production.~\citep[p.~228]{Arrow:1961aa}
+In particular the assumption that 
+``the real wage equals the marginal product of labor''~\citep[p.~6]{Klump:2011aa}
+is made.
+
+As I have written before, these assumptions become problematic
+when considering energy.
+Many countries have parastatal or full government control 
+over electricity generation and/or fuel markets.  
+Many countries subsidize energy markets.  
+And, there are always health and environmental externalities 
+that are not priced into fossil fuel energy markets.  
+So, the conditions for perfect competition are not present for energy markets.
 
@@
 \begin{equation} \label{eq:LINEX_beta}
-  \beta \equiv \frac{l}{y} \frac{\partial y}{\partial l} = a \left[ c \left( \frac{l}{e}\right) - \frac{l}{k} \right] \;,
+  \beta \equiv \frac{l}{y} \frac{\partial y}{\partial l} 
+  = a \left[ c \left( \frac{l}{e}\right) - \frac{l}{k} \right] \;,
 \end{equation}
 %
-\noindent{}and
+and
 %
@@
 
+Common forms of macroeconomic production functions have been reviewed.
+Relationships among production functions have been examined.
+Key assumptions for each have been discussed.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+After reviewing this literature, I think there is a need
+for a book entitled \emph{Energy in the Production Function}
+which would start with Equation~\ref{eq:diff_growth}
+and carefully derive each of the production functions.
+In each derivation, assumptions should be clearly exposed.
+The constraints associated with the LiNex equation should be critically
+examined.
+New constraints should be introduced to round out the picture of 
+economic growth in an energy- and materials-constrained world.
+If possible, the price elasticity of supply, especially for energy, should be 
+included in the production function.
+I'm unsure how this should be done, 
+although a profitable route might be found by
+re-thinking the marginal product of energy.
+Finally, a new form of the production function should be derived
+and applied.
+
+This new piece should be an entry point for people interested 
+in the role of energy in macroeconomic growth
+who have a differential equations background.
+\emph{Lecture Notes in Energy} might be a good home for it.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Acknowledgements}
-\label{sec:Acknowledgements}
+% \section*{Acknowledgements}
+% \label{sec:Acknowledgements}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\appendix
+% \appendix
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\section{Appendix}
-
-Include data tables here?
+% \section{Appendix}
+%
+% Include data tables here?
 

### 2014-11-30 Articles/Article_EcolEcon_2014/Paper2.Rnw
Rearranging jobs on nodes. Made possible by fixes to dahl.

@@
 <<CES_lambda_gamma_graph_X, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6.0, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with primary exergy ($x_p$).">>=
-cesCoeffsDataX <- filter(AllCoeffs, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
+cesCoeffsDataXp <- filter(AllCoeffs, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
                                                                       "(iK + iL) + (iXp)", 
@@
                                                                       "(iXp + iK) + (iL)"))
-standardScatterPlot(data=cesCoeffsDataX, mapping=aes(x=gamma_coef, y=lambda, color=Source), 
+standardScatterPlot(data=cesCoeffsDataXp, mapping=aes(x=gamma_coef, y=lambda, color=Source), 
                     facet_formula=country~nestStrParen, alpha=0.05) +

### 2014-12-01 Articles/Article_EcolEcon_2014/Paper2.Rnw
Fixed a naming bug.

@@
 <<CES_sigma1_delta1_graph_X, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6.5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with primary exergy ($x_p$).">>=
-standardScatterPlot(data=cesCoeffsDataX, mapping=aes(x=delta_1, y=sigma_1, color=Source), 
+standardScatterPlot(data=cesCoeffsDataXp, mapping=aes(x=delta_1, y=sigma_1, color=Source), 
                     facet_formula=country~nestStrParen, alpha=0.05) +
@@
 <<CES_sigma_delta_graph_X, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=6, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models using primary exergy ($x_p$).">>=
-standardScatterPlot(data=subset(cesCoeffsDataX, nestStrParen != "(iK + iL) + ()"),
+standardScatterPlot(data=subset(cesCoeffsDataXp, nestStrParen != "(iK + iL) + ()"),
                     mapping=aes(x=delta, y=sigma, color=Source), 
@@
 <<CES_ternary_graphX, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models with exergy ($x$).", eval=FALSE>>=
-standardTriPlot(data=cesCoeffsDataX, 
+standardTriPlot(data=cesCoeffsDataXp, 
                 mapping=aes(color=Source), 

### 2014-12-01 Workflow/Workflow.Rmd
DownloadPostProcessed.R now exists. It accepts a comma-separated list of <Source>s.

@@
 ### Download post-processed results to local machine
-* From a local machine, say `Scripts/DownloadPostProcessed.bash -u <user> -S <Source> -d`, where `<user>` is 
-a username on `dahl`, `<Source>` is the data source of interest, and `-d` (debug) will 
+* From the `Econ-Growth-R-Analysis` directory of a local machine, 
+say `Scripts/DownloadPostProcessed.R -u <user> -S <Source> -d`, where `<user>` is 
+a username on `dahl`, `<Source>` is a comma-separated list of data sources of interest, and `-d` (debug) will 
 show the files to be transferred to the local machine, without actually transferring them.
 * Verify that the list of files to be transferred looks right.
-* From a local computer, say `Scripts/DownloadPostProcessed.bash -u <user> -S <Source>` to download the files.
+* From a local computer, say `Scripts/DownloadPostProcessed.R -u <user> -S <Source>` to download the files.
 * The files are downloaded to the `data_postprocessed` directory on the local machine.
@@
 the environment. 
-* The `DownloadPostProcessed.bash` script connects to `dahl.calvin.edu` (`node-00`). 
-That choice was made to minimize the risk that a file won't prpogate across the cluster 
+* The `DownloadPostProcessed.R` script connects to `dahl.calvin.edu` (`node-00`). 
+The choice to connect to `node-00` was made to minimize the risk that a file won't propagate across the cluster's 
 file system prior to the download request.

### 2014-12-10 Articles/Article_EcolEcon_2014/Paper2.Rnw
Editing graph sizes.

--- 2014-11-30 Articles/Article_EcolEcon_2014/Paper2.Rnw
@@
   energyType <- parseFactorString(factorString)$energyType
+
   data.frame(year = (attr(x, which="data"))$Year, resid = resid(x), name=name, Source=Source, Country=Country,
-             modelType=modelType, energyType=energyType)
+             modelType=modelType, factorString=factorString, 
+             nestStrParen=parseFactorString(factorString)$nestStrParen, energyType=energyType)
 }
@@
 
-<<CD_GDP_Spaghetti_Graphs_UK, fig.pos="H", fig.align='center', fig.width=4, fig.height=4.5, fig.cap="UK Cobb-Douglas fitted models.">>=
+<<CD_GDP_Spaghetti_Graphs_UK, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="UK Cobb-Douglas fitted models.">>=
 cdFittedDataUK <- subset(AllFitted, subset = model=="cd" & Country=="UK")
@@
 
-<<CD_GDP_Spaghetti_Graphs_JP, fig.pos="H", fig.align='center', fig.width=4, fig.height=2.5, fig.cap="JP Cobb-Douglas fitted models.">>=
+<<CD_GDP_Spaghetti_Graphs_JP, fig.pos="H", fig.align='center', fig.width=4, fig.height=2, fig.cap="JP Cobb-Douglas fitted models.">>=
 cdFittedDataJP <- subset(AllFitted, subset = model=="cd" & Country=="JP")
@@
 
-<<CD_GDP_Spaghetti_Graphs_PT, fig.pos="H", fig.align='center', fig.width=5, fig.height=2.5, fig.cap="PT Cobb-Douglas fitted models.">>=
+<<CD_GDP_Spaghetti_Graphs_PT, fig.pos="H", fig.align='center', fig.width=5, fig.height=2, fig.cap="PT Cobb-Douglas fitted models.">>=
 cdFittedDataPT <- subset(AllFitted, subset = model=="cd" & Country=="PT")
@@
 
-<<CD_GDP_Spaghetti_Graphs_CN, fig.pos="H", fig.align='center', fig.width=4, fig.height=2.5, fig.cap="CN Cobb-Douglas fitted models.">>=
+<<CD_GDP_Spaghetti_Graphs_CN, fig.pos="H", fig.align='center', fig.width=4, fig.height=2, fig.cap="CN Cobb-Douglas fitted models.">>=
 cdFittedDataCN <- subset(AllFitted, subset = model=="cd" & Country=="CN")
@@
   labs(x = "", y = "Residuals") +
+  scale_x_continuous(breaks=c(1960, 1980, 2000)) + 
   xy_theme()
@@
 are shown in 
-Figures~\ref{fig:CES_lambda_gamma_graph_X}--\ref{fig:CES_sigma_delta_graph_X}. 
+Figures~\ref{fig:CES_lambda_gamma_graph_Xp}--\ref{fig:CES_sigma_delta_graph_Xp}. 
 The white crosshair on each graph shows the location 
 of the fit to historical data. 
-In Figures~\ref{fig:CES_sigma1_delta1_graph_X} and~\ref{fig:CES_sigma_delta_graph_X},
+In Figures~\ref{fig:CES_sigma1_delta1_graph_Xp} and~\ref{fig:CES_sigma_delta_graph_Xp},
 the bottom of the vertical axis represents $\sigma = 0$.
@@
 resample points along the left (right) edge of
-Figures \ref{fig:CES_sigma1_delta1_graph_X} and \ref{fig:CES_sigma_delta_graph_X}
+Figures \ref{fig:CES_sigma1_delta1_graph_Xp} and \ref{fig:CES_sigma_delta_graph_Xp}
 are equivalent.
 That is, all points along the left (right) edge of
-Figures \ref{fig:CES_sigma1_delta1_graph_X} and \ref{fig:CES_sigma_delta_graph_X}
+Figures \ref{fig:CES_sigma1_delta1_graph_Xp} and \ref{fig:CES_sigma_delta_graph_Xp}
 have the same $sse$. 
@@
 to discriminate among points along the left (right) edge of
-Figures \ref{fig:CES_sigma1_delta1_graph_X} and \ref{fig:CES_sigma_delta_graph_X}. 
+Figures \ref{fig:CES_sigma1_delta1_graph_Xp} and \ref{fig:CES_sigma_delta_graph_Xp}. 
 Thus, resample point estimates where $\delta$ or $\delta_1$ approaches 0 (1)
@@
 
-<<CES_lambda_gamma_graph_X, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6.0, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with primary exergy ($x_p$).">>=
-cesCoeffsDataX <- filter(AllCoeffs, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
+%------------------------------
+\subsubsection{CES with primary exergy ($x_p$)} 
+\label{sec:ces_xp}
+%------------------------------
+
+The following graphs show results for the CES model using primary exergy ($x_p$).
+
+<<CES_lambda_gamma_graph_Xp, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6.0, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with primary exergy ($x_p$).">>=
+cesCoeffsDataXp <- filter(AllCoeffs, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
                                                                       "(iK + iL) + (iXp)", 
@@
 
-<<CES_sigma1_delta1_graph_X, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6.5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with primary exergy ($x_p$).">>=
-standardScatterPlot(data=cesCoeffsDataX, mapping=aes(x=delta_1, y=sigma_1, color=Source), 
+<<CES_sigma1_delta1_graph_Xp, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6.5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with primary exergy ($x_p$).">>=
+standardScatterPlot(data=cesCoeffsDataXp, mapping=aes(x=delta_1, y=sigma_1, color=Source), 
                     facet_formula=country~nestStrParen, alpha=0.05) +
@@
 
-<<CES_sigma_delta_graph_X, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=6, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models using primary exergy ($x_p$).">>=
-standardScatterPlot(data=subset(cesCoeffsDataX, nestStrParen != "(iK + iL) + ()"),
+<<CES_sigma_delta_graph_Xp, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=6, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models using primary exergy ($x_p$).">>=
+standardScatterPlot(data=subset(cesCoeffsDataXp, nestStrParen != "(iK + iL) + ()"),
                     mapping=aes(x=delta, y=sigma, color=Source), 
@@
 
-Figure~\ref{fig:CES_ternary_graph} shows 
+Figure~\ref{fig:CES_ternary_graphXp} shows 
 $\alpha$, $\beta$, and $\gamma$ parameters for the CES model for all nests and countries.
-Figure~\ref{fig:CES_ternary_graph} is comparable to
+Figure~\ref{fig:CES_ternary_graphXp} is comparable to
 the ternary graph for the Cobb-Douglas models, 
@@
 
-<<CES_ternary_graphX, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models with exergy ($x$).", eval=FALSE>>=
-standardTriPlot(data=cesCoeffsDataX, 
+<<CES_ternary_graphXp, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models with primary exergy ($x_p$).", eval=TRUE>>=
+standardTriPlot(data=cesCoeffsDataXp, 
                 mapping=aes(color=Source), 
@@
 
-% Figure~\ref{fig:CES_Spaghetti_Graph} compares CES model predictions 
-% to historical data for all nestings. 
-% As with the Cobb-Douglas results, 
-% historical data are shown as a black line, 
-% the fit to historical data is shown as a white line, and 
-% the gray band encompasses \Sexpr{spaghettiGraphLevel*100}\% of the fits to resampled data.
+Figures~\ref{fig:CES_GDP_Spaghetti_Graph_US_xp}--\ref{fig:CES_GDP_Spaghetti_Graph_CN_xp} 
+compare CES model predictions 
+to historical data for all nestings, countries, and data sources. 
+As with the Cobb-Douglas results, 
+historical data are shown as a black line, 
+the fit to historical data is shown as a white line, and 
+the gray band encompasses \Sexpr{spaghettiGraphLevel*100}\% of the fits to resampled data.
+
+<<CES_GDP_Spaghetti_Graph_US_xp, fig.pos="H", fig.align='center', fig.width=5, fig.height=3.5, fig.cap="US CES with $x_p$ fitted models.">>=
+cesFittedDataUS_xp <- subset(AllFitted, subset = model=="ces" & Country=="US" & (energy=="iXp" | energy=="none"))
+spaghettiPlot(data=cesFittedDataUS_xp, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1960=1)") +
+  scale_x_continuous(breaks=c(1960, 1980, 2000))
+@
+
+<<CES_GDP_Spaghetti_Graph_UK_xp, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="UK CES with $x_p$ fitted models.">>=
+cesFittedDataUK_xp <- subset(AllFitted, subset = model=="ces" & Country=="UK" & (energy=="iXp" | energy=="none"))
+spaghettiPlot(data=cesFittedDataUK_xp, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1960=1)") +
+  scale_x_continuous(breaks=c(1960, 1980, 2000))
+@
+
+<<CES_GDP_Spaghetti_Graph_JP_xp, fig.pos="H", fig.align='center', fig.width=5, fig.height=2.5, fig.cap="JP CES with $x_p$ fitted models.">>=
+cdFittedDataJP_xp <- subset(AllFitted, subset = model=="ces" & Country=="JP" & (energy=="iXp" | energy=="none"))
+spaghettiPlot(data=cdFittedDataJP_xp, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1960=1)") +
+  scale_x_continuous(breaks=c(1960, 1980, 2000))
+@
+
+<<CES_GDP_Spaghetti_Graph_AT_xp, fig.pos="H", fig.align='center', fig.width=5, fig.height=3.5, fig.cap="AT CES with $x_p$ fitted models.">>=
+cdFittedDataAT_xp <- subset(AllFitted, subset = model=="ces" & Country=="AT" & (energy=="iXp" | energy=="none"))
+spaghettiPlot(data=cdFittedDataAT_xp, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1960=1)") +
+  scale_x_continuous(breaks=c(1960, 1980, 2000))
+@
+
+<<CES_GDP_Spaghetti_Graph_PT_xp, fig.pos="H", fig.align='center', fig.width=5, fig.height=2.5, fig.cap="PT CES with $x_p$ fitted models.">>=
+cdFittedDataPT_xp <- subset(AllFitted, subset = model=="ces" & Country=="PT" & (energy=="iXp" | energy=="none"))
+spaghettiPlot(data=cdFittedDataPT_xp, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1960=1)") +
+  scale_x_continuous(breaks=c(1960, 1980, 2000))
+@
+
+<<CES_GDP_Spaghetti_Graph_CN_xp, fig.pos="H", fig.align='center', fig.width=5, fig.height=2.5, fig.cap="CN CES with $x_p$ fitted models.">>=
+cdFittedDataCN_xp <- subset(AllFitted, subset = model=="ces" & Country=="CN" & (energy=="iXp" | energy=="none"))
+spaghettiPlot(data=cdFittedDataCN_xp, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1960=1)") +
+  scale_x_continuous(breaks=c(1960, 1980, 2000))
+@
+
+<<CES_Residual_Plot, fig.pos="H", fig.align='center', fig.width=6, fig.height=6, fig.cap="CES with $x_p$ Residual Plots.">>=
+# Use residuals_df to make a graph.
+ces_xp_residuals_df <- subset(residuals_df, subset = modelType=="ces" & (energyType=="iXp" | energyType=="none"))
+ggplot(data=ces_xp_residuals_df, aes(x=year, y=resid, color=Source)) + 
+  geom_point(size = 1.0) +
+  facet_grid(Country ~ nestStrParen) +
+  labs(x = "", y = "Residuals") +
+  scale_x_continuous(breaks=c(1960, 1980, 2000)) + 
+  xy_theme()
+@
+
+%------------------------------
+\subsubsection{CES with final exergy ($x_f$)} 
+\label{sec:ces_xf}
+%------------------------------
+
+%------------------------------
+\subsubsection{CES with useful work ($u$)} 
+\label{sec:ces_u}
+%------------------------------
+
 % 

### 2014-12-24 Articles/Article_EnerEcon_2014/EconGrowth3.Rnw
Adding Martin and Matt's edits to interp.

@@
 \usepackage{microtype}  % produces hanging punctuation and beautiful type
+\usepackage{booktabs}   % produces beautiful tables
 
@@
 labor~($l$), indexed capital stock~($k$), and an additional exogenous, time-dependent 
-term.%
-  \footnote{The time-dependent term in production functions is often associated with
-  ``technological progress,'' but that is a very narrow reading of Solow's original intent:
-  \begin{quote}
-    It will be seen that I am using the phrase ``technical change''
-    as a short-hand expression for any kind of shift 
-    in the production function. 
-    Thus slowdowns, speed-ups, improvements in the education of the labor force, 
-    and all sorts of things will appear as ``technical change.''~\citep{solow1957technical}
-  \end{quote}
-  }
+term.
 This production function can be expressed as
@@
 %
-\noindent Note that the $\rho$ ($\sigma$) and $\delta$ parameters have different
-meanings that depend upon the nesting of the factors of production.
+\noindent Note that the parameters $\rho$ ($\sigma$) and $\delta$ have different
+meanings depending upon the nesting of the factors of production.
 
@@
     scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
-    scale_y_continuous(breaks=c(0, 0.025, 0.05, 0.075)) +    
+    scale_y_continuous(limits=c(-0.05, 0.15), breaks=c(0, 0.05, 0.1)) +    
     labs(x=expression(gamma), y=expression(lambda))
@@
 
-Interpretation goes here.
-
-*** One item from previous version of paper led me to a question that could be answered by our approach:
-Is it true that economies at similar stages of development will have similar
-$\alpha$, $\beta$, and $\gamma$ values? ****
-
-**** Another question to address: Would better data reduce the uncertainty in parameter estimates?
-Probably not. The US, presumably the best data in the world, still shows very high uncertainty. ****
+We find it beneficial to discuss results through a series of questions 
+about the techniques presented above.
+
+%++++++++++++++++++++++++++++++
+\subsection{Is it important to include energy in the production function?} 
+\label{sec:important_to_include_energy}
+%++++++++++++++++++++++++++++++
+
+For the Cobb-Douglas and CES production functions, 
+augmentation with energy improves goodness of fit when $\gamma > 0$.%
+  \footnote{
+  The LINEX function is unhelpful in answering the question 
+  ``Is it important to include energy in production functions?'' 
+  because LINEX presupposes that energy is the only factor of production.
+  }
+
+First, we look at the results of the Cobb-Douglas functions 
+in Figures~\ref{fig:CD_lambda_theta_graph} and~\ref{fig:CD_Ternary_Scatter_Graph}. 
+Visually, $\gamma > 0$ is shown in the right column 
+of Figure~\ref{fig:CD_Ternary_Scatter_Graph} 
+as data points that are above the horizontal base of the ternary plots. 
+We note that the list of countries for which $\gamma \gg 0$ includes 
+Tanzania, South Africa, Saudi Arabia, and the United Kingdom. 
+Especially for Tanzania, but also for Saudi Arabia and the United Kingdom, 
+it appears certain that including energy improves goodness of fit: 
+both the fit to historical data (crosshairs) 
+and all resample data points (black dots) 
+are above the base of the triangle in the energy columns of Figure~\ref{fig:CD_Ternary_Scatter_Graph}. 
+However, for South Africa, significant uncertainty in $\gamma$, 
+as shown by the large vertical spread of resample data points, 
+leads us to exercise caution in concluding that adding energy to the production function is helpful
+for improving fit to historical data. 
+A robust result 
+($\gamma$ equal or close to zero and very little vertical spread of the resample points) 
+indicates that including energy does not help to explain economic growth in Zambia,
+while for United States, Japan, China, and especially Iran, 
+it is less certain that augmenting with energy is unhelpful 
+(larger vertical spread of resample points).
+
+The results for the CES analysis (Figure~\ref{fig:CES_ternary_graph}) 
+indicate that including energy is clearly helpful 
+in explaining economic growth in Saudi Arabia, 
+because all resample data points are consistently far above the base of the ternary plots 
+($\gamma \gg 0$) for all possible ways of nesting of energy with capital and labor. 
+Two out of the three possible nestings suggest the importance of including energy for Japan and Tanzania.
+For Iran, the crosshairs indicate that energy may explain some growth, 
+but this is highly uncertain as the resample data points have a very large vertical spread.  
+Explaining economic growth in the United States, China, and Zambia will benefit 
+relatively less by including energy, 
+but the vertical spreads indicate some uncertainty 
+in the cases of the United States and Zambia.  
+The results for both the United Kingdom and South Africa 
+exhibit significant uncertainty and are contradictory for the various nests.
+
+Based on this analysis of the empirical data, 
+we find no grounds to argue for augmenting the production function 
+with energy for all economies. 
+Our results support \citeapos{Stern:2011bq} conclusion that energy 
+may or may not be required in production functions,
+depending on its abundance or scarcity. 
+But, one cannot know \emph{a-priori} the economies 
+for which augmenting by energy will improve goodness of fit. 
+Statistical testing is clearly warranted.
+
+%++++++++++++++++++++++++++++++
+\subsection{Are the World Bank country categories
+helpful for conceptualizing the role of energy in economic growth?} 
+\label{sec:wb_categories_helpful}
+%++++++++++++++++++++++++++++++
+
+Some developed economies (US) benefit little from including energy as a factor of production, 
+while some others (UK) benefit in a minor way. 
+For other developed economies (JP), the results of CD and CES models point in opposite directions.  
+For NICs the results are mixed; 
+China does not convincingly benefit from energy-augmented production functions, 
+and results are uncertain for South Africa (ZA) due to lack of precision in determining $\gamma$.  
+In one OPEC country (SA), adding energy clearly helps to explain economic growth, 
+while in another (IR), the benefit of energy augmentation is small and uncertain. 
+For LDCs there is a either a strong indication that energy-augmented production functions 
+are beneficial as an explanation for growth (TZ) or string indication otherwise (ZM).
+
+In summary, we observe that World Bank country categories (Table~\ref{tab:Economy_Examples}) 
+do not predict whether energy augmentation will be beneficial. 
+In fact, 
+there is as much variation of the role of energy in economic growth 
+within World Bank country categories
+as between World Bank country categories. 
+Thus, we conclude that the World Bank’s country categories are not helpful 
+in explaining the role of energy in economic growth. 
+Rather, a nuanced approach is necessary wherein the energy situation 
+in each economy is assessed independently.
+
+%++++++++++++++++++++++++++++++
+\subsection{Does augmentation by energy reduce the Solow residual?} 
+\label{sec:energy_reduce_solow}
+%++++++++++++++++++++++++++++++
+
+The so-called Solow residual ($\lambda$ in Equations~\ref{eq:CD}--\ref{eq:CESekl}) 
+accounts for “slowdowns, speed-ups, improvements in the education of the labor force, 
+and all sorts of things [that] appear as ``technical change.''~\citep{solow1957technical} 
+The time-dependent term is often associated with
+``technological progress,'' but that is a very narrow reading of Solow's original intent:
+  \begin{quote}
+    It will be seen that I am using the phrase ``technical change''
+    as a short-hand expression for any kind of shift 
+    in the production function. 
+    Thus slowdowns, speed-ups, improvements in the education of the labor force, 
+    and all sorts of things will appear as ``technical change.''~\citep{solow1957technical}
+  \end{quote}
+
+It has been shown elsewhere~\citep{Ayres:2010ug}
+that consideration of energy (specifically, useful work) 
+in the production function eliminates the need for the Solow residual~($\lambda$) 
+over the very long run (e.g.,~1900--2000). 
+The purpose of this paper, however, is to assess common production functions \emph{as used in practice}, 
+so we include $\lambda$ terms in all fitted production functions. 
+The present approach allows us to answer the question of whether augmentation by 
+primary energy in the production function reduces the \emph{value of} the Solow residual,
+as opposed to eliminating the \emph{need for} the Solow residual altogether (Ayres and Warr's question).
+After augmenting by energy, the Solow-residual ($\lambda$) 
+in the Cobb-Douglas~(Figure~\ref{fig:CD_lambda_theta_graph}) 
+and CES models~(\ref{fig:CES_lambda_gamma_graph}) 
+still explains a part of economic growth in several economies, 
+especially China, but also in the United Kingdom, Japan, and Tanzania,  
+and to a lesser extent in the United States and Iran. 
+In South Africa and Zambia, the Solow-residual is zero, while in Saudi Arabia it is negative.%
+  \footnote{
+  The negative Solow residual ($\lambda$) for Saudi Arabia is a consequence
+  of the fact that all indexed factors of production ($k$, $l$, and $e$) are greater than 
+  economic output ($y$) for most of the period under study (1991--2011).
+  }
+For the Chinese economy, energy augmentation significantly reduces 
+the uncertainty of the value of the Solow residual~(Figure~\ref{fig:CES_lambda_gamma_graph}). 
+Furthermore, no economies show reduced magnitude of the Solow residual from left to right
+in Figures~\ref{fig:CD_lambda_theta_graph} and~\ref{fig:CES_lambda_gamma_graph}.
+
+Thus, we conclude that energy augmentation of the production function 
+by primary thermal energy does not decrease the value of the Solow residual~($\lambda$) 
+over the years studied (1980--2011 and 1991--2011). 
+Longer-term analyses involving other energy quantifications (exergy or useful work) 
+are warranted.
+
+%++++++++++++++++++++++++++++++
+\subsection{Does the CES model structure (nesting) matter?} 
+\label{sec:nest_matter}
+%++++++++++++++++++++++++++++++
+
+The choice of CES nesting structure has significant influence 
+on model results for both 
+relative importance of factors of production ($\delta$ and $\delta_1$ values) and 
+substitutability among factors of production ($\sigma$ and $\sigma_1$ values).
+
+%------------------------------
+\subsubsection{Relative importance of factors of production ($\delta$ and $\delta_1$ values)} 
+\label{sec:importance_of_factors}
+%------------------------------
+
+For most economies (UK, JP, CN, ZA, SA, IR, and TZ), 
+Figure~\ref{fig:CES_ternary_graph} shows that the relative importance of 
+production factors capital~($k$), labour~($l$), and energy~($e$) 
+is different for the three different CES nestings (Equations~\ref{eq:CESkle}--\ref{eq:CESekl}). 
+In other words, you cannot view two of the ternary plots 
+in the rightmost three columns of Figure~\ref{fig:CES_ternary_graph} and predict the third. 
+Nesting structure matters little for the economies of the United States and Zambia.
+
+Certain combinations of economy, parameter values, and CES nesting structure 
+come with very large resampling spreads, 
+indicating large fitted parameter uncertainties. 
+For example, 
+for Iran's ($kl$)$e$ nesting in Figures~\ref{fig:CES_sigma1_delta1_graph}--\ref{fig:CES_ternary_graph} 
+there is virtually no useful information 
+in $\delta$, $\delta_1$, $\alpha$, $\beta$, and $\gamma$.
+
+%------------------------------
+\subsubsection{Elasticity of substitution among factors of production ($\sigma$ and $\sigma_1$ values)} 
+\label{sec:elasticity_of_substitution}
+%------------------------------
+
+The interpretation of elasticities of substitution 
+among factors of production ($k$, $l$, and $e$) is challenging,
+because a version of each elasticity of substitution appears three or four times 
+among the various nests. 
+For example, an elasticity of substitution between capital~($k$) and labor~($l$) 
+appears in the following nests: 
+($\underline{kl}$), 
+($\underline{kl}$)$e$, 
+($\underline{l}e$)$\underline{k}$, and 
+($e\underline{k}$)$\underline{l}$. 
+The following tables assist interpretation: 
+C (c) indicates strong (weak) complementarity, 
+S (s) indicates strong (weak) substitutability, 
+$\sim\sim\sim$ indicates large uncertainty, 
+and $\sim$ indicates small uncertainty.
+
+\begin{table} \caption{Elasticities of substitution (US).} \label{tab:sigma_US} 
+  \begin{center}
+    \begin{tabular}{r l l l} 
+      \toprule
+      & $k$ \& $l$ & $k$ \& $e$ & $l$ \& $e$ \\
+      \midrule
+      \multirow{2}{*}{$\sigma_1$} & ($\underline{kl}$): C 
+                                        & 
+                                              &  \\
+                                  & ($\underline{kl}$)$e$: C 
+                                        & ($\underline{ek}$)$l$: $\sim\sim\sim$ 
+                                              & ($\underline{le}$)$k$: $\sim\sim\sim$ \\
+      \midrule
+      \multirow{3}{*}{$\sigma$} & 
+                                      & ($\underline{k}l$)$\underline{e}$: $\sim\sim\sim$
+                                            & ($k\underline{l}$)$\underline{e}$: $\sim\sim\sim$ \\
+                                & ($\underline{l}e$)$\underline{k}$: C
+                                      & ($l\underline{e}$)$\underline{k}$: C
+                                            &  \\
+                                & ($e\underline{k}$)$\underline{l}$: C
+                                      & 
+                                            & ($\underline{e}k$)$\underline{l}$: C \\
+      \bottomrule
+%       \multirow{2}{*}{$sigma_1$}  & ($kl$): C        &                           &                           \\
+%                                   & ($kl$)$e$: C     & ($ek$)$l$: $\var\var\var$ & ($le$)$k$: $\var\var\var$ \\
+% 
+% 
+%       \multirow{3}{*}{Developed} & \includegraphics[height=0.11in]{flag/flag_US.png} & US & USA & \multirow{3}{*}{1980--2011}\\
+%                                  & \includegraphics[height=0.11in]{flag/flag_UK.png} & UK & United Kingdom & \\
+%                                  & \includegraphics[height=0.11in]{flag/flag_JP.png} & JP & Japan          & \\
+%       \hline
+%       \multirow{2}{*}{NICs}      & \includegraphics[height=0.11in]{flag/flag_CN.png} & CN & China & \multirow{2}{*}{1991--2011}        \\
+%                                  & \includegraphics[height=0.11in]{flag/flag_ZA.png} & ZA & South Africa & \\
+%       \hline
+%       \multirow{2}{*}{OPEC}      & \includegraphics[height=0.11in]{flag/flag_SA.png} & SA & Saudi Arabia & \multirow{2}{*}{1991--2011} \\
+%                                  & \includegraphics[height=0.11in]{flag/flag_IR.png} & IR & Iran         &  \\
+%       \hline
+%       \multirow{2}{*}{LDCs}      & \includegraphics[height=0.11in]{flag/flag_TZ.png} & TZ & Tanzania & \multirow{2}{*}{1991--2011}     \\
+%                                  & \includegraphics[height=0.11in]{flag/flag_ZM.png} & ZM & Zambia      & \\
+    \end{tabular}
+  \end{center}
+\end{table}
 

### 2014-12-24 Articles/Article_EnerEcon_2014/EconGrowth3.Rnw
US Elasticities of substitution table complete.

@@
     \begin{tabular}{r c c l l} 
+      \toprule
       \multirow{3}{*}{Developed} & \includegraphics[height=0.11in]{flag/flag_US.png} & US & USA & \multirow{3}{*}{1980--2011}\\
@@
                                  & \includegraphics[height=0.11in]{flag/flag_JP.png} & JP & Japan          & \\
-      \hline
+      \midrule
       \multirow{2}{*}{NICs}      & \includegraphics[height=0.11in]{flag/flag_CN.png} & CN & China & \multirow{2}{*}{1991--2011}        \\
                                  & \includegraphics[height=0.11in]{flag/flag_ZA.png} & ZA & South Africa & \\
-      \hline
+      \midrule
       \multirow{2}{*}{OPEC}      & \includegraphics[height=0.11in]{flag/flag_SA.png} & SA & Saudi Arabia & \multirow{2}{*}{1991--2011} \\
                                  & \includegraphics[height=0.11in]{flag/flag_IR.png} & IR & Iran         &  \\
-      \hline
+      \midrule
       \multirow{2}{*}{LDCs}      & \includegraphics[height=0.11in]{flag/flag_TZ.png} & TZ & Tanzania & \multirow{2}{*}{1991--2011}     \\
                                  & \includegraphics[height=0.11in]{flag/flag_ZM.png} & ZM & Zambia      & \\
+      \bottomrule
     \end{tabular}
@@
     \begin{tabular}{c c c c c} 
+      \toprule
       Nesting    & Equation        & $\alpha$                & $\beta$                 & $\gamma$       \\
-      \hline
+      \midrule
       ($kl$) + ()     & \ref{eq:CES}    & $\delta_1$              & $1 - \delta_1$          & 0          \\
@@
       ($ek$) + ($l$)  & \ref{eq:CESekl} & $\delta (1 - \delta_1)$ & $1 - \delta$            & $\delta \delta_1$ \\
+      \bottomrule
     \end{tabular}
@@
   \begin{center}
-    \begin{tabular}{r l l l} 
+    \begin{tabular}{r l c l c l c} 
       \toprule
-      & $k$ \& $l$ & $k$ \& $e$ & $l$ \& $e$ \\
+         & \multicolumn{2}{c}{$k$ \& $l$} & \multicolumn{2}{c}{$k$ \& $e$} & \multicolumn{2}{c}{$l$ \& $e$} \\
       \midrule
-      \multirow{2}{*}{$\sigma_1$} & ($\underline{kl}$): C 
-                                        & 
-                                              &  \\
-                                  & ($\underline{kl}$)$e$: C 
-                                        & ($\underline{ek}$)$l$: $\sim\sim\sim$ 
-                                              & ($\underline{le}$)$k$: $\sim\sim\sim$ \\
+      \multirow{2}{*}{$\sigma_1$} & ($\underline{kl}$) & C 
+                                        &  & 
+                                              & &  \\
+                                  & ($\underline{kl}$)$e$ & C 
+                                        & ($\underline{ek}$)$l$ & $\sim\sim\sim$ 
+                                              & ($\underline{le}$)$k$ & $\sim\sim\sim$ \\
       \midrule
-      \multirow{3}{*}{$\sigma$} & 
-                                      & ($\underline{k}l$)$\underline{e}$: $\sim\sim\sim$
-                                            & ($k\underline{l}$)$\underline{e}$: $\sim\sim\sim$ \\
-                                & ($\underline{l}e$)$\underline{k}$: C
-                                      & ($l\underline{e}$)$\underline{k}$: C
-                                            &  \\
-                                & ($e\underline{k}$)$\underline{l}$: C
-                                      & 
-                                            & ($\underline{e}k$)$\underline{l}$: C \\
+      \multirow{3}{*}{$\sigma$} & &
+                                      & ($\underline{k}l$)$\underline{e}$ & $\sim\sim\sim$
+                                            & ($k\underline{l}$)$\underline{e}$ & $\sim\sim\sim$ \\
+                                & ($\underline{l}e$)$\underline{k}$ & C
+                                      & ($l\underline{e}$)$\underline{k}$ & C
+                                            &  & \\
+                                & ($e\underline{k}$)$\underline{l}$ & C
+                                      & &
+                                            & ($\underline{e}k$)$\underline{l}$ & C \\
+      \midrule
+                                & \multicolumn{2}{c}{C} & \multicolumn{2}{c}{C} & \multicolumn{2}{c}{C} \\
       \bottomrule
-%       \multirow{2}{*}{$sigma_1$}  & ($kl$): C        &                           &                           \\
-%                                   & ($kl$)$e$: C     & ($ek$)$l$: $\var\var\var$ & ($le$)$k$: $\var\var\var$ \\
-% 
-% 
-%       \multirow{3}{*}{Developed} & \includegraphics[height=0.11in]{flag/flag_US.png} & US & USA & \multirow{3}{*}{1980--2011}\\
-%                                  & \includegraphics[height=0.11in]{flag/flag_UK.png} & UK & United Kingdom & \\
-%                                  & \includegraphics[height=0.11in]{flag/flag_JP.png} & JP & Japan          & \\
-%       \hline
-%       \multirow{2}{*}{NICs}      & \includegraphics[height=0.11in]{flag/flag_CN.png} & CN & China & \multirow{2}{*}{1991--2011}        \\
-%                                  & \includegraphics[height=0.11in]{flag/flag_ZA.png} & ZA & South Africa & \\
-%       \hline
-%       \multirow{2}{*}{OPEC}      & \includegraphics[height=0.11in]{flag/flag_SA.png} & SA & Saudi Arabia & \multirow{2}{*}{1991--2011} \\
-%                                  & \includegraphics[height=0.11in]{flag/flag_IR.png} & IR & Iran         &  \\
-%       \hline
-%       \multirow{2}{*}{LDCs}      & \includegraphics[height=0.11in]{flag/flag_TZ.png} & TZ & Tanzania & \multirow{2}{*}{1991--2011}     \\
-%                                  & \includegraphics[height=0.11in]{flag/flag_ZM.png} & ZM & Zambia      & \\
     \end{tabular}

### 2014-12-25 Articles/Article_EnerEcon_2014/EconGrowth3.Rnw
Final edits to include Martin and my interpretation.

@@
 
-We find it beneficial to discuss results through a series of questions 
-about the techniques presented above.
+We find it beneficial to discuss results through a series of questions, 
+answers to which are illuminated by the techniques and results presented above.
 
@@
 \end{table}
+
+\begin{table} \caption{Elasticities of substitution (UK).} \label{tab:sigma_UK} 
+  \begin{center}
+    \begin{tabular}{r l c l c l c} 
+      \toprule
+         & \multicolumn{2}{c}{$k$ \& $l$} & \multicolumn{2}{c}{$k$ \& $e$} & \multicolumn{2}{c}{$l$ \& $e$} \\
+      \midrule
+      \multirow{2}{*}{$\sigma_1$} & ($\underline{kl}$) & C 
+                                        &  & 
+                                              & &  \\
+                                  & ($\underline{kl}$)$e$ & $\sim\sim\sim$ 
+                                        & ($\underline{ek}$)$l$ & C
+                                              & ($\underline{le}$)$k$ & C \\
+      \midrule
+      \multirow{3}{*}{$\sigma$} & &
+                                      & ($\underline{k}l$)$\underline{e}$ & C
+                                            & ($k\underline{l}$)$\underline{e}$ & C \\
+                                & ($\underline{l}e$)$\underline{k}$ & C
+                                      & ($l\underline{e}$)$\underline{k}$ & C
+                                            &  & \\
+                                & ($e\underline{k}$)$\underline{l}$ & $\sim\sim\sim$
+                                      & &
+                                            & ($\underline{e}k$)$\underline{l}$ & $\sim\sim\sim$ \\
+      \midrule
+                                & \multicolumn{2}{c}{C} & \multicolumn{2}{c}{C} & \multicolumn{2}{c}{C} \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+\end{table}
+
+**** For the time being, I've added two of these tables.
+We can add the remaining seven tables easily, either here or in an appendix. --MKH ****
+
+For many estimates of elasticity of substitution, the resampling technique indicates high uncertainty. 
+Where results are not uncertain, 
+we find complementarity among factors of production 
+for most economies with the exception of China 
+where an indication of substitutability between labor and energy is observed.
+
+That so many estimates of elasticity of substitution exhibit large uncertainty, 
+often spanning the range from perfect complements ($\sigma, \sigma_1 = 0$) 
+to perfect substitutes ($\sigma, \sigma_1 = 1$), 
+is a troubling characteristic of the estimated CES models. 
+For some countries (IR, ZM), 
+estimating any elasticity of substitution at all is problematic and fraught with peril. 
+Note that this result is unlikely to be caused by poor-quality data alone. 
+Presumably the best data in the world (US, UK, JP) exhibits large uncertainty. 
+(See US and UK rows in Figures~\ref{fig:CD_Ternary_Scatter_Graph}  
+and~\ref{fig:CES_sigma1_delta1_graph}--\ref{fig:CES_ternary_graph}.)
+
+Some of the uncertainty is explained by the structure of the CES model. 
+If $\delta$ or $\delta_1$ achieves an extreme value (0 or 1), 
+the corresponding elasticity of substitution ($\sigma$ and $\sigma_1$) becomes meaningless. 
+(See Equations~\ref{eq:CES}--\ref{eq:CESekl}.) 
+Thus, large uncertainty in $\sigma$ and $\sigma_1$ is expected for any resampled model 
+in which parameter estimates are positioned on the left or right boundaries 
+of Figures~\ref{fig:CES_sigma1_delta1_graph} or~\ref{fig:CES_sigma_delta_graph}.
+
+Some of the uncertainty in parameter estimates may be explained by structural change in the economies. 
+For example, 
+**** Martin: can you select one of the highly uncertain economies and discuss it? 
+Perhaps Iran or Zambia? ****. 
+To account for the large uncertainty, 
+it may be useful to perform piecewise analyses of smaller time periods. 
+For the present study, doing piecewise analysis of, say, 
+Iran **** Use the economy that Martin discusses above **** 
+would mean that the CES model is estimated on a 10-year period. 
+Considering that there are six fitted parameters in the CES model 
+($\gamma$, $\lambda$, $\delta$, $\delta_1$, $\rho$, and $\rho_1$), 
+ten years of historical data leaves precious few (only 4) degrees of freedom for the fitting process.
+
+Based on the results and discussions above 
+regarding the relative importance of and 
+the elasticity of substitution among factors of production, 
+we conclude that use of the CES model for energy analysis 
+should be undertaken with utmost caution. 
+Indeed, empirical testing on the relative importance 
+of production factors and elasticities of substitution is highly recommended. 
+Sensitivity analysis is essential. 
+Our results support \citeapos{Lecca:2011kr} conclusion 
+for the need to econometrically specify production function relationships and 
+to perform sensitivity analysis on nesting choices in economies to enhance the reliability of results.
+
+%++++++++++++++++++++++++++++++
+\subsection{Implications of resampling results } 
+\label{sec:implications}
+%++++++++++++++++++++++++++++++
+
+In addition to the usual parameter estimation process 
+by linear coefficient determination (Cobb-Douglas and LinEx) 
+and non-linear optimization algorithms (CES), 
+the resampling/bootstrapping analysis performed herein 
+provides insight into the question of how accurately parameters are known. 
+We chose the resampling approach instead of the more-common technique 
+of estimating confidence intervals from standard errors for two reasons. 
+(1)~Model parameters are highly constrained, and confidence intervals often violate the constraints. 
+For example a result of $\alpha = 0.25 \pm 0.3$ is nonsensical, 
+because $ \alpha \in [0, 1]$. 
+(2)~True confidence intervals for constrained parameters are often asymmetric
+(e.g., $\alpha = 0.2 + 0.1, -0.05$), 
+but the standard error approach yields symmetric confidence intervals. 
+The resampling approach that we employed both respects constraints 
+and allows for asymmetric confidence intervals.%
+  \footnote{
+    We have chosen to present parameter uncertainty results visually, 
+    both because the resampling technique lends itself to visual presentation and 
+    because we believe visual comparison is more effective than tablefuls of numbers.
+  }
+A significant result to emerge from this work is that large parameter uncertainty 
+does not necessarily lead to poor model fit to economic output. 
+To choose one example of many, 
+the value of $\gamma$ for the Cobb-Douglas model for Tanzania (0.59) 
+shows a resampling range of 0.2–0.9. 
+(See Figure~\ref{fig:CD_Ternary_Scatter_Graph}.) 
+Yet, Cobb-Douglas models for Tanzania, with and without energy, both 
+(a)~fit historical data very well 
+(white line compared to black line in Tanzania row of Figure~\ref{fig:CD_GDP_Spaghetti_Graph}) 
+and 
+(b)~exhibit a very narrow range of resampled fits 
+(thin gray band in Tanzania row of Figure~\ref{fig:CD_GDP_Spaghetti_Graph}). 
+This means that a good fit to historical data does not indicate 
+that model parameters have small uncertainty. 
+In fact, similar to Tanzania, 
+many economies exhibit both large uncertainty in model parameters and
+very good fit to historical data. 
+(See Figures~\ref{fig:CD_lambda_theta_graph} ~\ref{fig:CD_Ternary_Scatter_Graph} 
+compared to Figure~\ref{fig:CD_GDP_Spaghetti_Graph}
+for the Cobb-Douglas models and 
+Figure~\ref{fig:CES_lambda_gamma_graph}--\ref{fig:CES_sigma_delta_graph}
+compared to Figure~\ref{fig:CES_Spaghetti_Graph} for CES models.) 
+This result is consistent across almost all economies and models. 
+Thus, we conclude that great care must be taken when interpreting estimated parameters: 
+it is very easy to claim more certainty than is warranted. 
+Where large uncertainty is observed, 
+additional work is needed to contextualize the results, 
+for example, 
+sector-based analysis or ****. **** Martin, add more here? ****
+
+We further caution against using $R^2$ only as the criteria for choosing a model, 
+because, in our experience, 
+both Cobb-Douglas and CES models yield high $R^2$ values for all countries. 
+(See Figures~\ref{fig:CD_Spaghetti_Graph} and~\ref{fig:CES_Spaghetti_Graph}.) 
+LinEx models fare poorly in some cases and might be excluded on that basis. 
+(See SA and TZ in Figure~\ref{fig:LINEX_Spaghetti_Graph}.) 
+It is more important to know the uncertainty of estimated parameters than to assess $R^2$. 
+With rigorous uncertainty testing as we have done here, 
+the quality of parameter estimates is exposed: 
+at a glance, the tightness of resampled results indicates 
+whether or not confidence in the model and data is warranted. 
+We conclude that it is insufficient to argue 
+in favor of a particular production function 
+on the grounds of its ability to fit historical data.
+
+The implications of parameter uncertainties should be obvious, 
+but we will state them here. 
+Basing policy upon parameters with high uncertainty can lead to bad, or completely wrong, policy. 
+**** Martin: can you find an example in our results that drives this point home? --MKH  
+May be barking up wrong production factor, may assume subs when complementarity: ****
+
+We conclude that the best policy will be made 
+with a macroeconomic modeling approach that is highly interpretative, 
+uses several production functions, and 
+estimates asymmetric uncertainties of fitted parameters.
 

### 2014-12-25 Articles/Article_EnerEcon_2014/EconGrowth3.Rnw
Edits to Energy Econ paper.

@@
 and \texttt{PORT} does not for the same data
-(i.e., for the same $y$, $k$, $l$, and $e$ data).
+(i.e., for the same $y$, $k$, $l$, and $e$ time series).
 
@@
 In Figures~\ref{fig:CES_sigma1_delta1_graph} and~\ref{fig:CES_sigma_delta_graph},
-the bottom of the vertical axis represents $\sigma = 0$.
-The top of the vertical axis represents $\sigma = \infty$.
+the bottom of the vertical axis represents $\sigma = 0$ (perfect complements).
+The top of the vertical axis represents $\sigma = \infty$ (perfect substitutes).
 
@@
     labs(x=expression(a[0]), y=expression(c[t])) +
-     scale_x_continuous(limits=c(-1, 2), breaks=c(-1, 0, 1.0, 2.0)) +
+     scale_x_continuous(limits=c(0, 2), breaks=c(0, 1.0, 2.0)) +
      scale_y_continuous(limits=c(0, 10), breaks=c(0, 5, 10))
@@
 and $\sim$ indicates small uncertainty.
+
+**** Need to think this presentation through, 
+want to see how balances with the rest of the paper; 
+do we have the space seems to be the limiting factor? --MdW ****
+
+**** I'm fine if we want to change to another form of these tables.
+But, I found the presentation below to be a good way to think about the results.
+My idea was to say ``hang on! We have several ways to get at some of these elasticities.
+Let's compare all the different ways to look at the elasticity between any two factors of production.
+Do they agree?  
+Are they in conflict?''  
+Another point to make is that these comparisons need to be done honestly. 
+We should not claim anything when the data are uncertain.
+
+Regarding Martin's question about length, 
+I've seen other papers in \emph{Energy Economics} that are 51 printed journal pages. (Saunders, 2008)
+I expect we are fine on length. --MKH ****
 
@@
 to perform sensitivity analysis on nesting choices in economies to enhance the reliability of results.
+
+%++++++++++++++++++++++++++++++
+\subsection{Which production function is best for energy augmentation?} 
+\label{sec:which_best}
+%++++++++++++++++++++++++++++++
+
+**** Shall we have a section here discussing which function is ``best''? --MKH ****
+What are the criteria?
+
+Allows assymetric uncertainty estimation via resampling: all work fine.
+
+Best match to historical data: CES.
+
+No ambiguity from model structure: CD and LinEx OK here. 
+CES has the undesireable characteristic that form (nesting) affects outcome.
+
+Easy to estimate: CD and LinEx can be fitted with linear function. 
+CES requires complex and time-consuming optimzation techniques.
+
+Small uncertainties in fitted parameters: CD and LinEx better than CES.
+
+Our assessment: None of the production functions is perfect. 
+Probably CD is best compromise among ease of estimating, good (but not best) fit to historical data, and
+small uncertainties in fitted parameters.
+
+Caution: none of the production functions analyzed herein allows for complex energy-economy phenomena
+like rebound effect, backfire, and super-conservation.
 
@@
 
+**** Not sure whether contextualization will work. 
+Could be read that macroeconomic growth modeling in such cases is not really useful at all? 
+--MdW ****
+
 We further caution against using $R^2$ only as the criteria for choosing a model, 
@@
 both Cobb-Douglas and CES models yield high $R^2$ values for all countries. 
-(See Figures~\ref{fig:CD_Spaghetti_Graph} and~\ref{fig:CES_Spaghetti_Graph}.) 
+(See Figures~\ref{fig:CD_GDP_Spaghetti_Graph} and~\ref{fig:CES_Spaghetti_Graph}.) 
 LinEx models fare poorly in some cases and might be excluded on that basis. 
@@
 estimates asymmetric uncertainties of fitted parameters.
+
+**** Other notes from our word document ****
+
+Lastly, what do aggregate models say?
+
+What direction can take from this work?
+
+What is the status of ME growth modeling after this?
 

### 2014-12-25 Articles/Article_EnerEcon_2014/EconGrowth3.Rnw
Article updates.

@@
 Thus, each fitted model implies a trajectory of $\alpha$, $\beta$, and $\gamma$ values as time proceeds.
-We found unconstrained fitting produced $\alpha$,$\beta$,$\gamma$ trajectories
+We found unconstrained fitting produced $\alpha$, $\beta$, $\gamma$ trajectories
 that violated parameter constraints ($[0,1]$) for all countries, with the exception of Iran.
@@
 **** Shall we have a section here discussing which function is ``best''? --MKH ****
-What are the criteria?
+Here is a first cut at some criteria and a recommendation.
 
@@
 
-Best match to historical data: CES.
+Best match to historical data: CES. But CD is close. LinEx struggles.
 
@@
 Small uncertainties in fitted parameters: CD and LinEx better than CES.
+
+Easy to respect constraints during fitting process: CD and CES easy. LinEx difficult.
 
@@
 small uncertainties in fitted parameters. 
+If precise fitting to historical data is paramount (and you're unconcerned about uncertainties
+in fitted coefficients), CES is the best.
 
@@
 
+Maybe put the discussion of ``Which production function is best'' here?
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2014-12-27 Articles/Article_EnerEcon_2014/EconGrowth3.Rnw
Added references to Saunders. Lots of editing on the article.

@@
 in economic growth modeling.  
-Neoclassical economic growth theory attributes output~($Y$) to factors of production:
+Mainstream economic growth theory attributes output~($Y$) to factors of production:
 capital stock~($K$) and labor~($L$). 
@@
 0 subscripts indicate values at an initial year.
-The parameters $\alpha$ and $\beta$ indicate the relative roles 
+The parameters $\alpha$ and $\beta$ are output elasticities
+that indicate the relative roles 
 of capital and labor in the economy.
@@
 
-Neoclassical economic growth theory as expressed in the Cobb-Douglas production 
+Mainstream economic growth theory as expressed in the Cobb-Douglas production 
 function makes no attempt, beyond growth in capital~($k$) and labor~($l$), 
 to describe the mechanisms that affect economic growth, 
-nor does it attempt, beyond different fitting parameters,
+nor does it attempt, beyond different values for the fitting parameters,
 to describe how such phenomena as
@@
 
-As shown in Equation~\ref{eq:CD} above, neoclassical economic theory does not 
+As shown in Equation~\ref{eq:CD} above, mainstream economic theory does not 
 include an explicit term for the role of energy in economic growth. 
 However, \citet{Bashmakov:2007ek}, \citet{Hamilton:2009ui}, \citet{Murphy:2011jh}, 
-\citet{Benes:2012tm}, \citet{Kumhof:2012ua}, \citet{Ayres:2013aa} and others indicate that the 
+\citet{Benes:2012tm}, \citet{Kumhof:2012ua}, \citet{Ayres:2013aa}, and others indicate that the 
 importance of energy for economic growth may far outweigh its cost share in the 
 economy. 
-That neoclassical economic growth theory ignores energy is, therefore, 
+That mainstream economic growth theory ignores energy is, therefore, 
 cause for concern, and inquiry into the proper approach for including energy 
 as a factor of production in economic growth modeling is both relevant and important.
+
+Furthermore, the \emph{cost share theorem} from mainstream economics states that 
+output elasticities 
+$\alpha$, $\beta$, and $\gamma$ 
+(if augmenting the production function by energy)
+can be calibrated from national accounts data as the 
+cost shares of capital, labor, and energy, respectively.
+However, the cost share theorem applies only under conditions of perfect competition
+in the markets for the factors of production.
+Although no market ever exhibits perfect competition, 
+in our opinion, energy markets are \emph{least} likely to be ``perfect.''
+Many governments have parastatal or full control 
+of electricity generation and/or fuel markets.  
+Other governments subsidize or incentivize energy markets.  
+And, there are always health and environmental externalities 
+that are not priced into fossil fuel energy markets.  
+If energy markets are farther from ``perfect'' 
+than capital~($K$) and/or labor~($L$) markets, 
+then energy is the factor of production least likely to have its
+output elasticity~($\gamma$) be well-represented 
+by cost share as reported in national accounts.
+Thus, when augmenting production functions by energy, 
+much care should be taken in estimating 
+the relative importance of the factors of production 
+($\alpha$, $\beta$, and $\gamma$).
+
+\citet{Kummel:2010vz} showed that the cost share theorem applies 
+only when economic growth is unconstrained.
+Real-world constraints such as the degree of automation and
+the degree of utilization of capital stock 
+result in shadow prices that move the values 
+of $\alpha$, $\beta$, and $\\gamma$ away from 
+their cost shares in the economy.\citep[Equations~12 and~13]{Kummel:2010vz}
+Thus, for this study, 
+we reject the cost share theorem and
+we have no \emph{a-priori} expectation that output elasticities 
+estimated from historical output data
+will match cost shares.
 
@@
 Neither the mathematical form of the energy-augmented 
-production function nor the quantification%
+production function nor the quantification of energy%
   \footnote{
@@
   }
-of energy is consistent in the 
-literature. 
+is consistent in the literature.
+
+**** Suggest moving content of the literature review section up to this point. --MKH ****
+
+**** Suggest deleting the next sentences:
 Furthermore, there has been little empirical work assessing the predictive ability 
@@
 rigorous statistical assessments of energy-related fitting parameters. 
+End of deleted section --MKH ****
+
 This paper contributes to the literature on the role of energy in economic growth
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+**** Merge the literature review into the Introduction? 
+We're already doing some literature review in the Introduction. --MKH ****
 
@@
 for misuse of model specifications 
-and selection of parameters 
+and selection of model parameters 
 to support certain theories (rather than empirically testing the theories
@@
 nested CES production function structure. 
-As a result, \citeauthor{Shen:2013vp} propose an atypical structure 
-for the Chinese economy. **** More detail here about nesting? ****  
+As a result, \citeauthor{Shen:2013vp} propose an atypical CES nesting structure 
+for the Chinese economy. **** More detail here about nesting? --MKH ****  
+\citet{Saunders:2008aa} evaluated several production and cost functions
+(including the Cobb-Douglas, CES, and LINEX functions studied herein)
+to assess whether they are capable of reproducing 
+rebound, backfire, and super-conservation effects.~\citep{Sorrell:2007um}
+\citeauthor{Saunders:2008aa} concludes that only the CES function is a candidate for 
+rebound analysis.
+The Cobb-Douglas function was found to exhibit only backfire.
+The LINEX function was found to 
+``not satisfy the standard concavity (diminishing marginal productivity) 
+conditions.''~\citet[p.~2195]{Saunders:2008aa}
 Both the choice of production function structure 
@@
 in a world where energy constraints are possible 
-\citep{Beckman:2011gb, Benes:2012tm, Nel:2010fv}.  
+\citep{Beckman:2011gb, Benes:2012tm, Nel:2010fv, Kummel:2010vz}.  
 We support the call from \citet{Shen:2013vp} that both
 the structure of the production function 
-and the parameters used to populate this function
+and the parameters that populate it 
 need empirical testing. 
@@
 \citep{Froling:2009vo, Jones:2001wn, Galor:2000up}. 
+**** The previous sentences sound a lot like we'll show that some groups of countries
+have similar charactersitics. 
+That's what we thought we might find, 
+but our new conclusion is that one must treat each country 
+individually. 
+We should consider revising the few sentences. --MKH ****
 
@@
 \texttt{micEconCES} \citep{Henningsen:2011td} estimates CES production 
-functions of the following forms (among others):
+functions of the following forms (among others).
 %
@@
 efficiencies among capital, labor, and energy, in the form of 
-the ratios $\rho_k$ and $\rho_l$ which are defined by\footnote{The notation
+the ratios $\rho_k$ and $\rho_l$ which are defined by%
+  \footnote{
+  The notation
   for the LINEX model breaks from the conventions used in the Cobb-Douglas and CES
-models:  $a_0$ and $c_t$ are parameters and $\rho_k$ and $\rho_l$ are not.}
-%
+  models:  $a_0$ and $c_t$ are parameters and $\rho_k$ and $\rho_l$ are not.
+  }
 \begin{equation} \label{eq:rho_k}
@@
 We measure economic output ($Y$) by gross domestic product (GDP). 
-GDP data in real 2005 U.S. dollars for all countries was obtained from the
+GDP data in real 2005 US dollars for all countries was obtained from the
 RGDP$^{\mathrm{NA}}$ time series of the Penn World Table.~\citep{Feenstra:2013aa}
@@
 for 1980--2011 (developed economies) and 1991--2011 (other economies). 
-% Factors of production track each other closely, 
-% and high covariances among these variables can be seen in 
-% Tables~\ref{tab:Covariance_US}--\ref{tab:Covariance_ZM}. 
-% \authNote{Do we want to discuss the covariances?}
 %
@@
 where $\theta$ is a vector of parameters for the function $f$.
-\authNote{if we use $\theta$ this way, we need a new scaling parameter. --rjp}%
+**** if we use $\theta$ this way, we need a new scaling parameter. --rjp ****
 Parameter estimates are chosen to minimize
-\authNote{Randy edit the following equation to reflect the fact that we're fitting in log space.}
+**** Randy edit the following equation to reflect the fact that we're fitting in log space. --MKH ****
 %
@@
 one can learn about the precision of the estimation method.
-\authNote{Add some references here. --rjp}
+**** Add some references here. --rjp ****
 
@@
 For the Cobb-Douglas and CES production functions, 
-augmentation with energy improves goodness of fit when $\gamma > 0$.%
+augmentation by energy improves goodness of fit when $\gamma > 0$.%
   \footnote{
@@
 Partial funding for Martin de Wit was provided 
-by the South African National Research Foundation (NRF).\footnote{Any opinion, 
+by the South African National Research Foundation (NRF).%
+  \footnote{
+  Any opinion, 
   findings, and conclusions or recommendations expressed herein are those 
-of the authors, and, therefore, NRF does not accept any liability in regard thereto.} 
+  of the authors, and, therefore, NRF does not accept any liability in regard thereto.
+  }
 The authors are grateful to Benjamin S. Warr (INSEAD) for providing 

### 2014-12-27 Articles/Article_EnerEcon_2014/EconGrowth3.Rnw
Moved lit review to Introduction.

@@
 suggest a near doubling of the real price of over the next decade.  
+**** Should we re-think this discussion in the light of the shale oil boom and the 
+recent drop in oil prices? --MKH ****
 \citet{Kumhof:2012ua} point out that 
@@
 However, \citet{Bashmakov:2007ek}, \citet{Hamilton:2009ui}, \citet{Murphy:2011jh}, 
-\citet{Benes:2012tm}, \citet{Kumhof:2012ua}, \citet{Ayres:2013aa}, and others indicate that the 
+\citet{Benes:2012tm}, \citet{Kumhof:2012ua}, \cite{Ayres:2010ug}, 
+\citet{Ayres:2013aa}, and others indicate that the 
 importance of energy for economic growth may far outweigh its cost share in the 
@@
 as a factor of production in economic growth modeling is both relevant and important.
-
-Furthermore, the \emph{cost share theorem} from mainstream economics states that 
-output elasticities 
-$\alpha$, $\beta$, and $\gamma$ 
-(if augmenting the production function by energy)
-can be calibrated from national accounts data as the 
-cost shares of capital, labor, and energy, respectively.
-However, the cost share theorem applies only under conditions of perfect competition
-in the markets for the factors of production.
-Although no market ever exhibits perfect competition, 
-in our opinion, energy markets are \emph{least} likely to be ``perfect.''
-Many governments have parastatal or full control 
-of electricity generation and/or fuel markets.  
-Other governments subsidize or incentivize energy markets.  
-And, there are always health and environmental externalities 
-that are not priced into fossil fuel energy markets.  
-If energy markets are farther from ``perfect'' 
-than capital~($K$) and/or labor~($L$) markets, 
-then energy is the factor of production least likely to have its
-output elasticity~($\gamma$) be well-represented 
-by cost share as reported in national accounts.
-Thus, when augmenting production functions by energy, 
-much care should be taken in estimating 
-the relative importance of the factors of production 
-($\alpha$, $\beta$, and $\gamma$).
-
-\citet{Kummel:2010vz} showed that the cost share theorem applies 
-only when economic growth is unconstrained.
-Real-world constraints such as the degree of automation and
-the degree of utilization of capital stock 
-result in shadow prices that move the values 
-of $\alpha$, $\beta$, and $\\gamma$ away from 
-their cost shares in the economy.\citep[Equations~12 and~13]{Kummel:2010vz}
-Thus, for this study, 
-we reject the cost share theorem and
-we have no \emph{a-priori} expectation that output elasticities 
-estimated from historical output data
-will match cost shares.
 
@@
 is consistent in the literature. 
-
-**** Suggest moving content of the literature review section up to this point. --MKH ****
-
-**** Suggest deleting the next sentences:
-Furthermore, there has been little empirical work assessing the predictive ability 
-of various energy-augmented production functions for different types of economies. 
-And, very few studies of the importance of energy in economic growth include 
-rigorous statistical assessments of energy-related fitting parameters. 
-End of deleted section --MKH ****
-
-This paper contributes to the literature on the role of energy in economic growth
-by applying statistically rigorous 
-methods along two coordinates of analysis: 
-form of the energy augmented production function 
-and type of economy.
-
-The remainder of this paper is organized as follows. 
-Section~\ref{sec:lit_review} provides a necessarily brief overview of relevant literature.
-Section~\ref{sec:Coordinates} discusses the coordinates of analysis for the present study. 
-Section~\ref{sec:Sources_of_Data} details sources of data and calculations to 
-generate time series for economic output ($y$) and factors of production ($k$, $l$, and $q$). 
-The procedures for and results from parameter estimation for the various production functions 
-are discussed in Section~\ref{sec:Parameter_Estimation}. 
-Section~\ref{sec:Discussion_of_Results} discusses implications of the parameter estimation 
-results, and Section~\ref{sec:Conclusion} concludes.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Literature Review} 
-\label{sec:lit_review}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-**** Merge the literature review into the Introduction? 
-We're already doing some literature review in the Introduction. --MKH ****
-
 \citet[p.~26]{Stern:2011bq} provides an overview of approaches to including energy 
@@
 
-Unsatisfactorily, the choice of a production function 
+Unsatisfactorily, both the choice of a production function 
 and the parameters used to populate these functions 
-affects results significantly.
+affect results significantly.
 This situation leaves far too much latitude 
@@
 to assess whether they are capable of reproducing 
-rebound, backfire, and super-conservation effects.~\citep{Sorrell:2007um}
-\citeauthor{Saunders:2008aa} concludes that only the CES function is a candidate for 
+rebound and backfire effects.~\citep{Sorrell:2007um}
+\citeauthor{Saunders:2008aa} concludes that,
+of the production functions evaluated in the present study,
+only the CES function is a candidate for 
 rebound analysis.
@@
 conditions.''~\citet[p.~2195]{Saunders:2008aa}
+
+In addition to model structure, 
+the way in which model parameters are determined is also subject to debate.
+The \emph{cost share theorem} from mainstream economics states that 
+output elasticities 
+$\alpha$, $\beta$, and $\gamma$ 
+(if augmenting the production function by energy)
+can be calibrated from national accounts data as the 
+cost shares of capital, labor, and energy, respectively.
+However, the cost share theorem applies only under conditions of perfect competition
+in the markets for the factors of production.
+Although no market ever exhibits perfect competition, 
+in our opinion, energy markets are \emph{least} likely to be ``perfect.''
+Many governments have parastatal or full control 
+of electricity generation and/or fuel markets.  
+Other governments subsidize or incentivize energy markets.  
+And, there are always health and environmental externalities 
+that are not priced into fossil fuel energy markets.  
+If energy markets are farther from ``perfect'' 
+than capital and/or labor markets, 
+then energy is the factor of production least likely to have its
+output elasticity~($\gamma$) be well-represented 
+by cost share as reported in national accounts.
+Thus, when augmenting production functions by energy, 
+much care should be taken in estimating 
+the relative importance of the factors of production 
+($\alpha$, $\beta$, and $\gamma$). 
+\citet{Kummel:2010vz} showed that the cost share theorem applies 
+only when economic growth is unconstrained.
+Real-world constraints such as the degree of automation and
+the degree of utilization of capital stock 
+result in shadow prices that move the values 
+of $\alpha$, $\beta$, and $\gamma$ away from 
+their cost shares in the economy.~\citep[Equations~12 and~13]{Kummel:2010vz}
+Thus, for this study, 
+we reject the cost share theorem and
+we have no \emph{a-priori} expectation that output elasticities 
+estimated from historical output data
+will match cost shares.
 Both the choice of production function structure 
-and the value of the model parameters 
+and the values of the model parameters 
 drive model results, and empirical and statistical testing 
@@
 such policy choices. 
-Therefore, we agree with those who have serious concerns 
-about the reliability of the results from economic growth models \citep{Lecca:2011kr}. 
+Therefore, we agree with those who express serious concerns 
+about the reliability of the results from economic growth models.~\citep{Lecca:2011kr} 
 We understand, however, 
@@
 and is increasingly informed by integrated energy-economic models, 
-in a world where energy constraints are possible 
-\citep{Beckman:2011gb, Benes:2012tm, Nel:2010fv, Kummel:2010vz}.  
+in a world where energy constraints are possible.~\citep{Beckman:2011gb, 
+Benes:2012tm, Nel:2010fv, Kummel:2010vz}
 We support the call from \citet{Shen:2013vp} that both
@@
 depending on its abundance or scarcity, 
-we will further argue in this paper that different types of countries 
+we will further test whether different types of countries 
 may need different factors of production to explain their respective growth paths.  
@@
 at different stages of their development, 
-a central point of long-wave economic growth modeling 
-\citep{Froling:2009vo, Jones:2001wn, Galor:2000up}. 
-**** The previous sentences sound a lot like we'll show that some groups of countries
+a central point of long-wave economic growth modeling.~\citep{Froling:2009vo, Jones:2001wn, Galor:2000up} 
+**** The previous sentences sound like we'll show that some groups of countries
 have similar charactersitics. 
-That's what we thought we might find, 
+That's what we thought we would find, 
 but our new conclusion is that one must treat each country 
 individually. 
-We should consider revising the few sentences. --MKH ****
+We should consider revising the previous few sentences. --MKH ****
+
+**** Suggest deleting the next two sentences:
+Furthermore, there has been little empirical work assessing the predictive ability 
+of various energy-augmented production functions for different types of economies. 
+And, very few studies of the importance of energy in economic growth include 
+rigorous statistical assessments of energy-related fitting parameters. 
+End of deleted section --MKH ****
+
+This paper contributes to the literature on the role of energy in economic growth
+by applying statistically rigorous 
+methods along two coordinates of analysis: 
+form of the energy augmented production function 
+and type of economy.
+
+The remainder of this paper is organized as follows. 
+% Section~\ref{sec:lit_review} provides a necessarily brief overview of relevant literature.
+Section~\ref{sec:Coordinates} discusses the coordinates of analysis for the present study. 
+Section~\ref{sec:Sources_of_Data} details sources of data and calculations to 
+generate time series for economic output ($y$) and factors of production ($k$, $l$, and $q$). 
+The procedures for and results from parameter estimation for the various production functions 
+are discussed in Section~\ref{sec:Parameter_Estimation}. 
+Section~\ref{sec:Discussion} discusses implications of the parameter estimation 
+results, and Section~\ref{sec:Conclusion} concludes.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion of Results}
-\label{sec:Discussion_of_Results}
+\section{Discussion}
+\label{sec:Discussion}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-We find it beneficial to discuss results through a series of questions, 
-answers to which are illuminated by the techniques and results presented above.
+We find it beneficial to discuss the results through a series of questions, 
+answers to which are illuminated by the techniques and data presented
+in Section~\ref{sec:Parameter_Estimation} above.
+
+**** We need to think about the order of the subsections below. --MKH ****
 
@@
   }
-
 First, we look at the results of the Cobb-Douglas functions 
@@
 as shown by the large vertical spread of resample data points, 
-leads us to exercise caution in concluding that adding energy to the production function is helpful
-for improving fit to historical data. 
+leads us to exercise caution in concluding that 
+augmenting the Cobb-Douglas production function by energy 
+is helpful for improving the goodness of fit to historical data. 
 A robust result 
@@
 depending on its abundance or scarcity. 
-But, one cannot know \emph{a-priori} the economies 
+One cannot know \emph{a-priori} the economies 
 for which augmenting by energy will improve goodness of fit. 
@@
 For other developed economies (JP), the results of CD and CES models point in opposite directions.  
-For NICs the results are mixed; 
+For NICs, the results are mixed; 
 China does not convincingly benefit from energy-augmented production functions, 
@@
 For LDCs there is a either a strong indication that energy-augmented production functions 
-are beneficial as an explanation for growth (TZ) or string indication otherwise (ZM).
+are beneficial as an explanation for growth (TZ) or strong indication otherwise (ZM).
 
@@
 Rather, a nuanced approach is necessary wherein the energy situation 
-in each economy is assessed independently.
+in each economy is assessed individually.
 
@@
 C (c) indicates strong (weak) complementarity, 
-S (s) indicates strong (weak) substitutability, 
-$\sim\sim\sim$ indicates large uncertainty, 
-and $\sim$ indicates small uncertainty.
+S (s) indicates strong (weak) substitutability, and
+$\sim\sim\sim$ ($\sim$) indicates large (small) uncertainty.
 
@@
 
-Regarding Martin's question about length, 
-I've seen other papers in \emph{Energy Economics} that are 51 printed journal pages. (Saunders, 2008)
+Regarding Martin's question about space, 
+I've seen other papers in \emph{Energy Economics} that are 51 printed journal pages. \citep{Saunders:2008aa}
 I expect we are fine on length. --MKH ****
@@
 
-**** For the time being, I've added two of these tables.
-We can add the remaining seven tables easily, either here or in an appendix. --MKH ****
+**** For the time being, I've added two of these tables, US and UK.
+We can add the remaining seven tables easily, either here or in an appendix. 
+Data to fill the appendices is in the Word document on Dropbox. --MKH ****
 
@@
 That so many estimates of elasticity of substitution exhibit large uncertainty, 
-often spanning the range from perfect complements ($\sigma, \sigma_1 = 0$) 
-to perfect substitutes ($\sigma, \sigma_1 = 1$), 
-is a troubling characteristic of the estimated CES models. 
+often spanning the range from perfect complements ($\sigma, \, \sigma_1 = 0$) 
+to perfect substitutes ($\sigma, \, \sigma_1 = \infty$), 
+is a troubling characteristic of the estimated CES coefficients 
+that is rarely reported in the literature.
 For some countries (IR, ZM), 
@@
 For the present study, doing piecewise analysis of, say, 
-Iran **** Use the economy that Martin discusses above **** 
-would mean that the CES model is estimated on a 10-year period. 
+Iran **** use the economy that Martin discusses above **** 
+would mean that the CES model is estimated on two 10-year periods. 
 Considering that there are six fitted parameters in the CES model 
 ($\gamma$, $\lambda$, $\delta$, $\delta_1$, $\rho$, and $\rho_1$), 
-ten years of historical data leaves precious few (only 4) degrees of freedom for the fitting process.
+ten years of historical data leaves precious few 
+(only 4) degrees of freedom for the fitting process.
 
@@
 should be undertaken with utmost caution. 
-Indeed, empirical testing on the relative importance 
+Indeed, rigorous statistical testing on the relative importance 
 of production factors and elasticities of substitution is highly recommended. 
-Sensitivity analysis is essential. 
 Our results support \citeapos{Lecca:2011kr} conclusion 
 for the need to econometrically specify production function relationships and 
-to perform sensitivity analysis on nesting choices in economies to enhance the reliability of results.
+to perform sensitivity analysis on nesting choices in economies 
+to enhance the reliability of results.
 
@@
 small uncertainties in fitted parameters.
+
 If precise fitting to historical data is paramount (and you're unconcerned about uncertainties
@@
 
-Caution: none of the production functions analyzed herein allows for complex energy-economy phenomena
-like rebound effect, backfire, and super-conservation.
-
-%++++++++++++++++++++++++++++++
-\subsection{Implications of resampling results } 
+If you need to represent rebound effects (not just backfire), 
+CES must be employed, 
+because the CES function was found by \citet{Saunders:2008aa} to be the only one of the production
+functions studied here that is capable of representing rebound rebound in addition to backfire.
+However, its ability to do so is tied to the values of the elasticity of substitution.
+Unfortunately, we find that value of the elasticity of substitution is often highly uncertain.
+Thus, whether the CES function is helpful for estimating both rebound and backfire effects
+is questionable.
+
+%++++++++++++++++++++++++++++++
+\subsection{Implications of parameter uncertainty} 
 \label{sec:implications}
@@
 provides insight into the question of how accurately parameters are known.
+
+**** Move this paragraph elsewhere? --MKH ****
 We chose the resampling approach instead of the more-common technique 
@@
   }
+
 A significant result to emerge from this work is that large parameter uncertainty 
@@
 the value of $\gamma$ for the Cobb-Douglas model for Tanzania (0.59) 
-shows a resampling range of 0.2–0.9. 
+shows a resampling range of 0.2--0.9. 
 (See Figure~\ref{fig:CD_Ternary_Scatter_Graph}.) 
@@
 
-We further caution against using $R^2$ only as the criteria for choosing a model, 
+The implications of parameter uncertainties should be obvious, 
+but we will state them here. 
+Basing policy upon parameters with high uncertainty can lead to bad, or completely wrong, policy. 
+**** Martin: can you find an example in our results that drives this point home? --MKH  
+May be barking up wrong production factor, may assume subs when complementarity: ****
+
+%++++++++++++++++++++++++++++++
+\subsection{Is $R^2$ a good criterion for choosing a model?} 
+\label{sec:is_r2_good}
+%++++++++++++++++++++++++++++++
+
+We caution against using $R^2$ as the only criterion for choosing a model, 
 because, in our experience, 
-both Cobb-Douglas and CES models yield high $R^2$ values for all countries. 
-(See Figures~\ref{fig:CD_GDP_Spaghetti_Graph} and~\ref{fig:CES_Spaghetti_Graph}.) 
-LinEx models fare poorly in some cases and might be excluded on that basis. 
+both Cobb-Douglas and CES models yield high $R^2$ values for all countries 
+(see Figures~\ref{fig:CD_GDP_Spaghetti_Graph} and~\ref{fig:CES_Spaghetti_Graph}), yet
+very different uncertainties for fitted parameters.
+In some cases, LINEX models fare poorly regarding $R^2$ and might be excluded on that basis. 
 (See SA and TZ in Figure~\ref{fig:LINEX_Spaghetti_Graph}.) 
-It is more important to know the uncertainty of estimated parameters than to assess $R^2$. 
+In our opinion, 
+it is equally, if not more, important to know the uncertainty 
+of estimated parameters than to assess $R^2$.
 With rigorous uncertainty testing as we have done here, 
@@
 in favor of a particular production function 
-on the grounds of its ability to fit historical data.
-
-The implications of parameter uncertainties should be obvious, 
-but we will state them here. 
-Basing policy upon parameters with high uncertainty can lead to bad, or completely wrong, policy. 
-**** Martin: can you find an example in our results that drives this point home? --MKH  
-May be barking up wrong production factor, may assume subs when complementarity: ****
+on the grounds $R^2$.
+
+**** Other notes from our Word document that didn't fit anywhere above. ****
+
+Lastly, what do aggregate models say?
+
+What direction can take from this work?
+
+What is the status of ME growth modeling after this?
+
+%++++++++++++++++++++++++++++++
+\subsection{Summary of discussion} 
+\label{sec:summary_of_discussion}
+%++++++++++++++++++++++++++++++
+
+**** Do we want to summarize the discussion here? --MKH ****
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Conclusion}
+\label{sec:Conclusion}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+**** Conclusion goes here.  ****
+
+Review the issues.
+
+Review our methods.
+
+Review our significant results.
+
+**** Maybe put the discussion of ``Which production function is best'' here? ****
 
@@
 estimates asymmetric uncertainties of fitted parameters.
-
-**** Other notes from our word document ****
-
-Lastly, what do aggregate models say?
-
-What direction can take from this work?
-
-What is the status of ME growth modeling after this?
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusion}
-\label{sec:Conclusion}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Conclusion goes here.
-
-Maybe put the discussion of ``Which production function is best'' here?
 

### 2014-12-29 Articles/Article_EnerEcon_2014/EconGrowth3.Rnw
Adding sigma tables created by macros.

@@
 \usepackage{booktabs}   % produces beautiful tables
+\usepackage{tablefootnote}  % allows footnotes in tables
 
@@
 \end{equation}
+}
+
+% The following commands assist making tables for elasticity of substitution (sigma and sigma_1).
+% The \firstrow macro creates the sigma_1 row.  The following arguments apply:
+% #1 sigma_1 for (kl) nest
+% #2 sigma_1 for (kl)e nest
+% #3 sigma_1 for (ek)l nest
+% #4 sigma_1 for (le)k nest
+\newcommand{\firstrow}[4]{\multirow{2}{*}{$\sigma_1$} & ($\underline{kl}$) & #1 
+                                  &  & 
+                                        & &  \\
+                            & ($\underline{kl}$)$e$ & #2
+                                  & ($\underline{ek}$)$l$ & #3
+                                        & ($\underline{le}$)$k$ & #4 \\
+}
+
+% The \secondrow macro creates the sigma row.  The following arguments apply:
+% #1 sigma for (kl)e nest
+% #2 sigma for (kl)e nest
+% #3 sigma for (le)k nest
+% #4 sigma for (le)k nest
+% #5 sigma for (ek)l nest
+% #6 sigma for (ek)l nest
+\newcommand{\secondrow}[6]{      \multirow{3}{*}{$\sigma$} & &
+                                      & ($\underline{k}l$)$\underline{e}$ & #1
+                                            & ($k\underline{l}$)$\underline{e}$ & #2 \\
+                                & ($\underline{l}e$)$\underline{k}$ & #3
+                                      & ($l\underline{e}$)$\underline{k}$ & #4
+                                            &  & \\
+                                & ($e\underline{k}$)$\underline{l}$ & #5
+                                      & &
+                                            & ($\underline{e}k$)$\underline{l}$ & #6 \\
+}
+
+% The \thirdrow macro creates the summary row at the bottom.  The following arguments apply:
+% #1 summary for elasticity of substitution between k and l
+% #2 summary for elasticity of substitution between k and e
+% #3 summary for elasticity of substitution between l and e
+\newcommand{\thirdrow}[3]{    & \multicolumn{2}{c}{#1} & \multicolumn{2}{c}{#2} & \multicolumn{2}{c}{#3} \\ }
+
+% The \eostable macro creates the overall table.  
+% The label for the table is tab:sigma_#1, i.e., tab:sigma_<2-letter country code>.  
+% The following arguments apply:
+% #1 2-letter country abbreviation
+% #2 sigma_1 row.  Use \firstrow macro here.
+% #3 sigma row.  Use \secondrow macro here.
+% #4 summary row.  Use \thirdrow macro here.
+\newcommand{\eostable}[4] {\begin{table} \caption{Elasticities of substitution (#1).} \label{tab:sigma_#1} 
+  \begin{center}
+    \begin{tabular}{r l c l c l c} 
+      \toprule
+         & \multicolumn{2}{c}{$k$ \& $l$} & \multicolumn{2}{c}{$k$ \& $e$} & \multicolumn{2}{c}{$l$ \& $e$} \\
+      \midrule
+      #2
+      \midrule
+      #3
+      \midrule
+      #4
+      \bottomrule
+    \end{tabular}
+  \end{center}
+\end{table}
 }
@@
 \subsection{Are the World Bank country categories
-helpful for conceptualizing the role of energy in economic growth?} 
+helpful for understanding the role of energy in economic growth?} 
 \label{sec:wb_categories_helpful}
@@
 
-\begin{table} \caption{Elasticities of substitution (US).} \label{tab:sigma_US} 
-  \begin{center}
-    \begin{tabular}{r l c l c l c} 
-      \toprule
-         & \multicolumn{2}{c}{$k$ \& $l$} & \multicolumn{2}{c}{$k$ \& $e$} & \multicolumn{2}{c}{$l$ \& $e$} \\
-      \midrule
-      \multirow{2}{*}{$\sigma_1$} & ($\underline{kl}$) & C 
-                                        &  & 
-                                              & &  \\
-                                  & ($\underline{kl}$)$e$ & C 
-                                        & ($\underline{ek}$)$l$ & $\sim\sim\sim$ 
-                                              & ($\underline{le}$)$k$ & $\sim\sim\sim$ \\
-      \midrule
-      \multirow{3}{*}{$\sigma$} & &
-                                      & ($\underline{k}l$)$\underline{e}$ & $\sim\sim\sim$
-                                            & ($k\underline{l}$)$\underline{e}$ & $\sim\sim\sim$ \\
-                                & ($\underline{l}e$)$\underline{k}$ & C
-                                      & ($l\underline{e}$)$\underline{k}$ & C
-                                            &  & \\
-                                & ($e\underline{k}$)$\underline{l}$ & C
-                                      & &
-                                            & ($\underline{e}k$)$\underline{l}$ & C \\
-      \midrule
-                                & \multicolumn{2}{c}{C} & \multicolumn{2}{c}{C} & \multicolumn{2}{c}{C} \\
-      \bottomrule
-    \end{tabular}
-  \end{center}
-\end{table}
-
-\begin{table} \caption{Elasticities of substitution (UK).} \label{tab:sigma_UK} 
-  \begin{center}
-    \begin{tabular}{r l c l c l c} 
-      \toprule
-         & \multicolumn{2}{c}{$k$ \& $l$} & \multicolumn{2}{c}{$k$ \& $e$} & \multicolumn{2}{c}{$l$ \& $e$} \\
-      \midrule
-      \multirow{2}{*}{$\sigma_1$} & ($\underline{kl}$) & C 
-                                        &  & 
-                                              & &  \\
-                                  & ($\underline{kl}$)$e$ & $\sim\sim\sim$ 
-                                        & ($\underline{ek}$)$l$ & C
-                                              & ($\underline{le}$)$k$ & C \\
-      \midrule
-      \multirow{3}{*}{$\sigma$} & &
-                                      & ($\underline{k}l$)$\underline{e}$ & C
-                                            & ($k\underline{l}$)$\underline{e}$ & C \\
-                                & ($\underline{l}e$)$\underline{k}$ & C
-                                      & ($l\underline{e}$)$\underline{k}$ & C
-                                            &  & \\
-                                & ($e\underline{k}$)$\underline{l}$ & $\sim\sim\sim$
-                                      & &
-                                            & ($\underline{e}k$)$\underline{l}$ & $\sim\sim\sim$ \\
-      \midrule
-                                & \multicolumn{2}{c}{C} & \multicolumn{2}{c}{C} & \multicolumn{2}{c}{C} \\
-      \bottomrule
-    \end{tabular}
-  \end{center}
-\end{table}
+% \begin{table} \caption{Elasticities of substitution (US).} \label{tab:sigma_US} 
+%   \begin{center}
+%     \begin{tabular}{r l c l c l c} 
+%       \toprule
+%          & \multicolumn{2}{c}{$k$ \& $l$} & \multicolumn{2}{c}{$k$ \& $e$} & \multicolumn{2}{c}{$l$ \& $e$} \\
+%       \midrule
+%       \multirow{2}{*}{$\sigma_1$} & ($\underline{kl}$) & C 
+%                                         &  & 
+%                                               & &  \\
+%                                   & ($\underline{kl}$)$e$ & C 
+%                                         & ($\underline{ek}$)$l$ & $\sim\sim\sim$ 
+%                                               & ($\underline{le}$)$k$ & $\sim\sim\sim$ \\
+%       \midrule
+%       \multirow{3}{*}{$\sigma$} & &
+%                                       & ($\underline{k}l$)$\underline{e}$ & $\sim\sim\sim$
+%                                             & ($k\underline{l}$)$\underline{e}$ & $\sim\sim\sim$ \\
+%                                 & ($\underline{l}e$)$\underline{k}$ & C
+%                                       & ($l\underline{e}$)$\underline{k}$ & C
+%                                             &  & \\
+%                                 & ($e\underline{k}$)$\underline{l}$ & C
+%                                       & &
+%                                             & ($\underline{e}k$)$\underline{l}$ & C \\
+%       \midrule
+%                                 & \multicolumn{2}{c}{C} & \multicolumn{2}{c}{C} & \multicolumn{2}{c}{C} \\
+%       \bottomrule
+%     \end{tabular}
+%   \end{center}
+% \end{table}
+
+% label is tab:sigma_US
+\eostable{US}
+          {\firstrow{C}{C}{$\sim\sim\sim$}{$\sim\sim\sim$}}
+          {\secondrow{$\sim\sim\sim$}{$\sim\sim\sim$}{C}{C}{C}{C}}
+          {\thirdrow{C}{C}{C}}
+
+% label is tab:sigma_UK
+\eostable{UK}
+          {\firstrow{C}{$\sim\sim\sim$}{C}{C}}
+          {\secondrow{C}{C}{C}{C}{$\sim\sim\sim$}{$\sim\sim\sim$}}
+          {\thirdrow{C}{C}{C}}
+
+% label is tab:sigma_JP
+\eostable{JP}
+          {\firstrow{c}{C}{$\sim\sim\sim$}{C}}
+          {\secondrow{C}{C}{C}{C}{C}{C}}
+          {\thirdrow{C}{C}{C}}
+
+% label is tab:sigma_CN
+\eostable{CN}
+          {\firstrow{$\sim\sim\sim$}{C}{C}{S}}
+%           {\secondrow{S {\scriptsize (driven by $le$?)}}{S}{C}{C}{c}{c {\scriptsize (driven by $kl$?)}}}
+          {\secondrow{S\tablefootnote{Driven by $le$?}}{S}{C}{C}{c}{c\tablefootnote{Driven by $kl$?}}}
+          {\thirdrow{C}{C}{S}}
+
+% label is tab:sigma_ZA
+\eostable{ZA}
+          {\firstrow{c$\sim$}{$\sim\sim\sim$}{C}{$\sim\sim\sim$}}
+          {\secondrow{C}{C}{C}{C}{$\sim\sim\sim$}{C\tablefootnote{Points on right are all same.}}}
+          {\thirdrow{c}{C}{C}}
+
+% label is tab:sigma_SA
+\eostable{SA}
+          {\firstrow{c$\sim$}{$\sim\sim\sim$}{C}{$\sim\sim\sim$}}
+          {\secondrow{C}{C}{C}{C}{$\sim\sim\sim$}{C\tablefootnote{Points on right are all same.}}}
+          {\thirdrow{c}{C}{C}}
 

### 2014-12-29 Articles/Article_EnerEcon_2014/EconGrowth3.Rnw
Now all sigma tables are included.
Edits to sigma table interpretations.

@@
 ($e\underline{k}$)$\underline{l}$. 
-The following tables assist interpretation: 
+Tables~\ref{tab:sigma_US}--\ref{tab:sigma_ZM} 
+provide interpretation of Figures~\ref{fig:CES_sigma1_delta1_graph}
+and~\ref{fig:CES_sigma1_delta1_graph}. 
+In the tables,
 C (c) indicates strong (weak) complementarity, 
@@
 $\sim\sim\sim$ ($\sim$) indicates large (small) uncertainty.
+
+**** If we stick with these tables, do we want to use $\sim\sim\sim$ to indicate uncertainty? ****
 
@@
 
+% This is the original sigma table. 
+% It has been replaced by macros that make for more-efficient LaTeX code.
 % \begin{table} \caption{Elasticities of substitution (US).} \label{tab:sigma_US} 
@@
 \eostable{SA}
-          {\firstrow{c$\sim$}{$\sim\sim\sim$}{C}{$\sim\sim\sim$}}
-          {\secondrow{C}{C}{C}{C}{$\sim\sim\sim$}{C\tablefootnote{Points on right are all same.}}}
-          {\thirdrow{c}{C}{C}}
-
-**** For the time being, I've added two of these tables, US and UK.
-We can add the remaining seven tables easily, either here or in an appendix. 
-Data to fill the appendices is in the Word document on Dropbox. --MKH ****
-
-For many estimates of elasticity of substitution, the resampling technique indicates high uncertainty. 
+          {\firstrow{$\sim\sim\sim$}{$\sim\sim\sim$}{C}{C}}
+          {\secondrow{C}{C}{$\sim\sim\sim$}{$\sim\sim\sim$}{$\sim\sim\sim$}{$\sim\sim\sim$}}
+          {\thirdrow{$\sim\sim\sim$}{C}{C}}
+
+% label is tab:sigma_IR
+\eostable{IR}
+          {\firstrow{$\sim\sim\sim$}{$\sim\sim\sim$}{$\sim\sim\sim$}{$\sim\sim\sim$}}
+          {\secondrow{$\sim\sim\sim$}{$\sim\sim\sim$}{$\sim\sim\sim$}{$\sim\sim\sim$}{C}{C}}
+          {\thirdrow{$\sim\sim\sim$}{$\sim\sim\sim$}{$\sim\sim\sim$}}
+
+% label is tab:sigma_TZ
+\eostable{TZ}
+          {\firstrow{C}{C}{$\sim\sim\sim$}{C}}
+          {\secondrow{$\sim\sim\sim$}{$\sim\sim\sim$}{C}{C}{C}{C}}
+          {\thirdrow{C}{$\sim\sim\sim$}{C}}
+
+% label is tab:sigma_ZM
+\eostable{ZM}
+          {\firstrow{$\sim\sim\sim$}{$\sim\sim\sim$}{$\sim\sim\sim$}{$\sim\sim\sim$}}
+          {\secondrow{$\sim\sim\sim$}{$\sim\sim\sim$}{$\sim\sim\sim$}
+                     {$\sim\sim\sim$}{$\sim\sim\sim$}{$\sim\sim\sim$}}
+          {\thirdrow{$\sim\sim\sim$}{$\sim\sim\sim$}{$\sim\sim\sim$}}
+
+For many estimates of elasticity of substitution~($\sigma$ and $\sigma_1$), 
+the resampling technique indicates high uncertainty~($\sim\sim\sim$). 
 Where results are not uncertain, 
-we find complementarity among factors of production 
+we find complementarity~(C and c) among factors of production 
 for most economies with the exception of China 
-where an indication of substitutability between labor and energy is observed.
+where an indication of substitutability between labor and energy is observed~(S and s).
 
@@
 that is rarely reported in the literature.
-For some countries (IR, ZM), 
+For some economies (Iran and Zambia), 
 estimating any elasticity of substitution at all is problematic and fraught with peril. 
 Note that this result is unlikely to be caused by poor-quality data alone. 
-Presumably the best data in the world (US, UK, JP) exhibits large uncertainty. 
-(See US and UK rows in Figures~\ref{fig:CD_Ternary_Scatter_Graph}  
+Presumably the best data in the world 
+(United States, United Kingdom, and Japan) exhibits large uncertainty. 
+(See United States and United Kingdom rows in Figures~\ref{fig:CD_Ternary_Scatter_Graph}  
 and~\ref{fig:CES_sigma1_delta1_graph}--\ref{fig:CES_ternary_graph}.)

### 2014-12-30 Articles/Article_EnerEcon_2014/EconGrowth3.Rnw
Edited the implications section (thoroughly).

@@
 
-Some developed economies (US) benefit little from including energy as a factor of production, 
-while some others (UK) benefit in a minor way. 
-For other developed economies (JP), the results of CD and CES models point in opposite directions.  
+Some developed economies (United States) benefit little from including energy as a factor of production, 
+while some others (United Kingdom) benefit in a minor way. 
+For other developed economies (Japan), the results of CD and CES models point in opposite directions.  
 For NICs, the results are mixed; 
 China does not convincingly benefit from energy-augmented production functions, 
-and results are uncertain for South Africa (ZA) due to lack of precision in determining $\gamma$.  
-In one OPEC country (SA), adding energy clearly helps to explain economic growth, 
-while in another (IR), the benefit of energy augmentation is small and uncertain. 
+and results are uncertain for South Africa due to lack of precision in determining $\gamma$.  
+In one OPEC country, Saudi Arabia, adding energy clearly helps to explain economic growth, 
+while in another, Iran, the benefit of energy augmentation is small and uncertain. 
 For LDCs there is a either a strong indication that energy-augmented production functions 
-are beneficial as an explanation for growth (TZ) or strong indication otherwise (ZM).
+are beneficial as an explanation for growth (Tanzania) or strong indication otherwise (Zambia).
 
@@
 
-For most economies (UK, JP, CN, ZA, SA, IR, and TZ), 
+For most economies (United Kingdom, Japan, China, South Africa, Saudi Arabia, Iran, and Tanzania), 
 Figure~\ref{fig:CES_ternary_graph} shows that the relative importance of 
@@
 
-**** If we stick with these tables, do we want to use $\sim\sim\sim$ to indicate uncertainty? ****
+**** If we stick with these tables, do we want to use $\sim\sim\sim$ to indicate uncertainty? --MKH ****
 
@@
 Another point to make is that these comparisons need to be done honestly. 
-We should not claim anything when the data are uncertain.
-
-Regarding Martin's question about space, 
+We should not claim anything when the data are uncertain. --MKH ****
+
+**** Regarding Martin's question about space, 
 I've seen other papers in \emph{Energy Economics} that are 51 printed journal pages. \citep{Saunders:2008aa}
@@
 %++++++++++++++++++++++++++++++
-\subsection{Which production function is best for energy augmentation?} 
-\label{sec:which_best}
-%++++++++++++++++++++++++++++++
-
-**** Shall we have a section here discussing which function is ``best''? --MKH ****
-Here is a first cut at some criteria and a recommendation.
-
-Allows assymetric uncertainty estimation via resampling: all work fine.
-
-Best match to historical data: CES. But CD is close. LinEx struggles.
-
-No ambiguity from model structure: CD and LinEx OK here. 
-CES has the undesireable characteristic that form (nesting) affects outcome.
-
-Easy to estimate: CD and LinEx can be fitted with linear function. 
-CES requires complex and time-consuming optimzation techniques.
-
-Small uncertainties in fitted parameters: CD and LinEx better than CES.
-
-Easy to respect constraints during fitting process: CD and CES easy. LinEx difficult.
-
-Our assessment: None of the production functions is perfect. 
-Probably CD is best compromise among ease of estimating, good (but not best) fit to historical data, and
-small uncertainties in fitted parameters.
-
-If precise fitting to historical data is paramount (and you're unconcerned about uncertainties
-in fitted coefficients), CES is the best.
-
-If you need to represent rebound effects (not just backfire), 
-CES must be employed, 
-because the CES function was found by \citet{Saunders:2008aa} to be the only one of the production
-functions studied here that is capable of representing rebound rebound in addition to backfire.
-However, its ability to do so is tied to the values of the elasticity of substitution.
-Unfortunately, we find that value of the elasticity of substitution is often highly uncertain.
-Thus, whether the CES function is helpful for estimating both rebound and backfire effects
-is questionable.
-
-%++++++++++++++++++++++++++++++
 \subsection{Implications of parameter uncertainty} 
@@
 and non-linear optimization algorithms (CES), 
-the resampling/bootstrapping analysis performed herein 
-provides insight into the question of how accurately parameters are known.
+the resampling analysis performed herein 
+provides insight into the questions of 
+(a)~how accurately parameters are known and 
+(b)~the implications of parameter imprecision.
 
@@
 A significant result to emerge from this work is that large parameter uncertainty 
-does not necessarily lead to poor model fit to economic output. 
+does not necessarily lead to poor model fit to historical economic output. 
 To choose one example of many, 
@@
 %++++++++++++++++++++++++++++++
+\subsection{Which production function is best for energy augmentation?} 
+\label{sec:which_best}
+%++++++++++++++++++++++++++++++
+
+Several criteria could be applied 
+to the question of which production function is best
+for describing the role of energy in economic growth:
+best match to historical data, 
+minimum ambiguity in model structure,
+minimum uncertainty in model parameters, and
+easy parameter estimation process.
+In the sections below, we evaluate the Cobb-Douglas, CES, and LINEX
+models using these criteria.
+
+%------------------------------
+\subsubsection{Best match to historical data} 
+\label{sec:match_history}
+%------------------------------
+
+Figures~\ref{fig:CD_GDP_Spaghetti_Graph}, \ref{fig:CES_Spaghetti_Graph}, and
+\ref{fig:LINEX_Spaghetti_Graph} indicate that the CES production function
+is consistently better than Cobb-Douglas or LINEX in terms of matching historical data.
+Cobb-Douglas is a close second, but
+LINEX struggles, especially with the Saudi Arabian and Tanzanian economies.%
+  \footnote{
+  The order of these results is unsurprising: 
+  CES contains 6 fitted parameters; Cobb-Douglas, 4; and LINEX, 3.
+  We expect models with more parameters to provide a better fit to historical data.
+  }$^,$%
+  \footnote{
+  We also note that in contrast to our approach, shared by \citet{Warr:2012cg},
+  of fitting constant $a_0$ and $c_t$ values, 
+  \citet{Kummel:2011aa} used logistic functions to generate time-varying
+  $a_0$ and $c_t$ values.
+  \citeauthor{Kummel:2011aa}'s approach will necessarily produce a better match to historical data,
+  because the logistic curves involve several additional fitting parameters.
+  }
+
+Thus, CES is preferred on this criterion.
+
+%------------------------------
+\subsubsection{Minimum ambiguity in model structure and interpretation} 
+\label{sec:min_ambiguity}
+%------------------------------
+
+For each production function, 
+values of fitted parameters give rise to interpretations of macroeconomic dynamics
+that, in turn, have significant implications for macroeconomic policy
+and human well-being.
+Thus, it is desirable that such interpretations have little ambiguity.
+
+The energy-augmented CES production function presents ambiguity to the energy analyst
+in the form of the choice of factor nesting.
+We showed above that nesting can significantly affect 
+the interpretation of macroecnomic dynamics, especially 
+the relative importance of factors of production~(\ref{fig:CES_ternary_graph}) and 
+the understanding of substitutibility 
+among factors of production. (See Section~\ref{sec:elasticity_of_substitution}).
+Thus, the CES production function has the undesireable characteristic 
+that model structure (i.e., nesting) affects both parameter values 
+and macroeconomic interpretation.
+Neither the Cobb-Douglas nor the LINEX production function 
+exhibits similar structural ambiguity.
+
+Thus, Cobb-Douglas or LINEX are preferred on this criterion.
+
+%------------------------------
+\subsubsection{Minimum uncertainty in model parameters} 
+\label{sec:min_uncertainty}
+%------------------------------
+
+Uncertainties in fitted parameters give rise to uncertainty 
+in macroeconomic dynamics inferred from fitted parameters.
+Thus, small uncertainty in fitted parameters is desirable. 
+Figures~\ref{fig:CD_lambda_theta_graph}, \ref{fig:CD_Ternary_Scatter_Graph},
+\ref{fig:CES_lambda_gamma_graph}--\ref{fig:CES_ternary_graph}, and
+\ref{fig:LINEXq_Resample_Graph} show that 
+Cobb-Douglas and LINEX have, by and large, 
+smaller uncertainties in fitted parameters than the CES production function.
+Thus, Cobb-Douglas and LINEX are preferred on this criterion.
+
+%------------------------------
+\subsubsection{Robust parameter estimation process} 
+\label{sec:robust_estimation}
+%------------------------------
+
+It is desirable that the combination of production function and parameter estimation process
+has the following characteristics:
+affords easy mathematical and numerical implementation, 
+provides an easy way to respect fitted parameter constraints, and
+allows asymmetric estimates of fitted parameter uncertainty.
+
+%..............................
+\paragraph{Easy mathematical and numerical implementation} 
+\label{sec:easy_implementation}
+%..............................
+
+For the Cobb-Douglas and LINEX models, 
+logarithmic transformation of the production functions 
+allows simple linear estimation of model parameters.
+In contrast, it is impossible to fit the CES model linearly,
+so parameters must be estimated by a more-complicated and time-consuming optimization process.
+(See Section~\ref{sec:CES_Parameter_Estimation}.)
+On the 40-node \texttt{dahl} supercomputer at Calvin College~\citep{Adams:2008aa},
+complete analysis of all data shown in this paper
+(including 1000 resamples for every model, every economy, and every CES nesting)
+takes about 15 hours.
+Approximately 98\% of the processing effort is spent on the CES models.%
+  \footnote{
+  All Cobb-Douglas and LINEX models run on a single node (using 4 processors per node) 
+  in about 1.5 hours (6 processor-hours).
+  All CES models run on 9 nodes (using 3 processors per node for a total of 27 processors) 
+  in about 15 hours (405 processor-hours).
+  }
+Thus, Cobb-Douglas and LINEX are preferred on this criterion.
+
+%..............................
+\paragraph{Easy to respect parameter constraints} 
+\label{sec:easy_constraints}
+%..............................
+
+It is relatively easy to implement constraints on fitting parameter 
+for the Cobb-Douglas production function. (See Section~\ref{sec:CD_Parameter_Estimation}.)
+For the CES prodcution function, 
+the capability to respect parameter constraints is a feature of the 
+\texttt{cesEst} function~\citep{Henningsen:2011td} and is, therefore,
+relatively easy to implement.
+In contrast, because output elasticities $\alpha$, $\beta$, and $\gamma$ 
+are not directly available as parameters in the LINEX model
+(see Equations~\ref{eq:LINEX} and~\ref{eq:LINEX_transformed}),
+it is very difficult to enforce constraints during the fitting process.%
+  \footnote{
+  See \citet{Kummel:2011aa} for one approach to respecting parameter constraints 
+  for the LINEX function. 
+  }
+Indeed, we found in Section~\ref{sec:LINEX_Parameter_Estimation}
+that the LINEX model regularly violates parameter constraints.
+
+Thus, Cobb-Douglas and CES are preferred on this criterion.
+
+%..............................
+\paragraph{Easy asymmetric uncertainties} 
+\label{sec:asymmetric_uncertainty}
+%..............................
+
+As discussed in Section~\ref{sec:implications},
+constraints on fitting parameters make it 
+desirable that the combination of production function
+and the parameter estimation process
+allows estimation of asymmetric parameter uncertainties.
+In the present work, we found that the resampling techniques described 
+in Section~\ref{sec:Resampling} afford estimates 
+of asymmetric parameter uncertainties. 
+Thus, none of the prodcution functions are preferred over the others on this criterion.
+
+%++++++++++++++++++++++++++++++
 \subsection{Summary of discussion} 
@@
 
-**** Do we want to summarize the discussion here? --MKH ****
+The evidence above indicates that 
+there is no quick or easy answer to the question
+``which production function is best for augmentation by energy?''
+We find that the answer depends upon the objective of the analysis.
+In our opinion, 
+the Cobb-Douglas models provides a good compromise among the competing criteria of
+ease of parameter estimation, good fit to historical data, and
+small uncertainties in fitted parameters.
+
+If precise fitting to historical data is paramount and uncertainty
+in fitted coefficients, especially elasticities of substitution, is not an issue, 
+the CES model is the best.
+
+If you need to represent rebound effects (not just backfire), 
+CES \emph{must} be employed, 
+because the CES function was found by \citet{Saunders:2008aa} to be the only production
+function studied here that is capable of representing rebound in addition to backfire.
+However, the ability of CES to represent rebound effects 
+is tied to the presence of elasticities of substitution ($\sigma$ and $\sigma_1$) in the CES model.
+Unfortunately, we resampling analyses show that estimated values 
+of elasticity of substitution are often highly uncertain.
+Thus, whether the CES function is helpful for estimating rebound in addition to backfire effects
+remains an open question.
+
+The LINEX model is intriguing, because of its thermodynamic roots, 
+but our implementation suffers from 
+poor reproduction of historical data and
+difficulty in respecting parameter constraints.
+If the LINEX function is to be used, we recommend that 
+\citeapos{Kummel:2011aa} fitting approach (logistic curves for $a_0$ and $c_t$) be employed
+and that the results be thoroughly tested and compared against other production functions.
 

### 2014-12-30 Articles/Article_EnerEcon_2014/EconGrowth3.Rnw
Edits to text.

@@
 whether and how to include appropriate energy indicators 
-in economic growth modeling.  
+in macroeconomic growth modeling.  
 Mainstream economic growth theory attributes output~($Y$) to factors of production:
@@
 \begin{equation} \label{eq:CD}
-  y = \theta \mathrm{e}^{\lambda(t-t_0)} k^\alpha l^\beta \;,
+  y = \theta A k^\alpha l^\beta \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)},
 \end{equation}
@@
 production function 
-where the constraints or abundance of energy 
+where the constraints on or abundance of energy 
 determines whether to include energy explicitly 
@@
 wherein energy is the only factor of production,
-and capital~($k$), labor~($l$), and energy~($q$)
+and capital~($k$), labor~($l$), and energy~($e$)
 combine to provide efficiencies that augment energy.
@@
 \citet{Saunders:2008aa} evaluated several production and cost functions
-(including the Cobb-Douglas, CES, and LINEX functions studied herein)
+(including the Cobb-Douglas, CES, and LINEX functions studied herein, 
+see Section~\ref{sec:Prod_Func_Forms})
 to assess whether they are capable of reproducing 
-rebound and backfire effects.~\citep{Sorrell:2007um}
+rebound and backfire effects.%
+  \footnote{
+  See \citet{Sorrell:2007um} for details about rebound and backfire effects.
+  }
 \citeauthor{Saunders:2008aa} concludes that,
@@
 will match cost shares.
-Both the choice of production function structure 
+
+Thus, both the choice of production function structure 
 and the values of the model parameters 
@@
 that macroeconomic policymaking is needed 
-and is increasingly informed by integrated energy-economic models, 
+and is increasingly informed by integrated energy-economy models, 
 in a world where energy constraints are possible.~\citep{Beckman:2011gb, 
 Benes:2012tm, Nel:2010fv, Kummel:2010vz}
-We support the call from \citet{Shen:2013vp} that both
+Unfortunately, there has been little empirical work assessing the predictive ability 
+of various energy-augmented production functions for different types of economies. 
+And, very few studies of the importance of energy in economic growth include 
+rigorous statistical assessments of energy-related fitting parameters. 
+Thus, we support the call from \citet{Shen:2013vp} that both
 the structure of the production function 
@@
 depending on its abundance or scarcity, 
-we will further test whether different types of countries 
-may need different factors of production to explain their respective growth paths.  
-This further leaves open the possibility for 
+we will test whether different types of countries 
+may need different factors of production to explain their respective growth paths, 
+leaving open the possibility for 
 different explanations of growth in various countries
@@
 a central point of long-wave economic growth modeling.~\citep{Froling:2009vo, Jones:2001wn, Galor:2000up}
-**** The previous sentences sound like we'll show that some groups of countries
-have similar charactersitics. 
-That's what we thought we would find, 
-but our new conclusion is that one must treat each country 
-individually. 
-We should consider revising the previous few sentences. --MKH ****
-
-**** Suggest deleting the next two sentences:
-Furthermore, there has been little empirical work assessing the predictive ability 
-of various energy-augmented production functions for different types of economies. 
-And, very few studies of the importance of energy in economic growth include 
-rigorous statistical assessments of energy-related fitting parameters. 
-End of deleted section --MKH ****
 
@@
 The capital-labor Cobb-Douglas production function shown in Equation~\ref{eq:CD}
-can be augmented to include an energy term:
+can be augmented by energy:
 %
 \begin{equation} \label{eq:CDe}
-  y = \theta \mathrm{e}^{\lambda(t-t_0)}  k^\alpha l^\beta e^\gamma \;,
+  y = \theta A k^\alpha l^\beta e^\gamma \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)},
 \end{equation}
@@
 time-dependent augmentation term ($A$).
-The LINEX models assumes energy ($e$) is the only factor of production.
-
-The LINEX model does, however, include terms that represent
+
+The LINEX model assumes energy ($e$) is the only factor of production.
+However, the LINEX model also includes terms that represent
 efficiencies among capital, labor, and energy, in the form of 
@@
   for the LINEX model breaks from the conventions used in the Cobb-Douglas and CES
-  models:  $a_0$ and $c_t$ are parameters and $\rho_k$ and $\rho_l$ are not.
+  models:  $a_0$ and $c_t$ are parameters, and $\rho_k$ and $\rho_l$ are not.
   }
@@
 (\ref{eq:rho_l}) labor increase relative to energy.
-The effect of energy ($e$) on production is enhanced if either
+The effect of the only factor of production, energy ($e$), on production is enhanced if either
 %
@@
 of the labor efficiency term ($\rho_l$) compared to the capital stock efficiency term ($\rho_k$). 
-Both $a_0$ and $c_t$ are assumed constant with respect to time.
+For this study, 
+we assume both $a_0$ and $c_t$ are constant 
+with respect to time.
 
@@
 LINEX to describe the West German economy, 
-\citet{Serrenho:2010vq} applying Cobb-Douglas variants to EU-15 countries, 
+\citet{Serrenho:2010vq} applying Cobb-Douglas variants to EU-15 economies, 
 \citet{VanderWerf:2008tc} applying CES nesting variants 
-to the 12 OECD countries, 
+to the 12 OECD economies, 
 \citet{Lecca:2011kr} applying CES nesting variants to the Scottish economy, 
@@
 we present a comparative analysis among representatives of
-the World Bank's main categories of countries, 
+the World Bank's country categories, 
 namely Developed Countries (DCs), 
@@
 labor~($L$), and 
-thermal energy~($Q$)
+primary thermal energy~($Q_p$)
 are required. 
@@
 We also added animal muscle work. 
-Following \citet{Ayres:2010ug}, 
-human muscle work is excluded from the energy time series,
-because it is counted as labor.
 Similar to the economic data discussed in 
@@
 Animal muscle work was estimated using an approach 
-similar to \citet{Ayres:2010ug}, using data from Warr's 
+similar to \citet{Ayres:2010ug}, using data from \citeauthor{Warr:2012a}'s
 REXS database \citep{Warr:2012a} and results from 
-\citet{Wirsenius:2000vi}. 
-Similar to Warr, we excluded human muscle work from the energy term
+\citet{Wirsenius:2000vi}.%
+  \footnote{
+  Following \citet{Ayres:2010ug}, 
+  human muscle work is excluded from the energy time series,
   on the grounds that labor terms are
   already present in all production functions.
+  }
 For animal work, our analysis was 
@@
 as the difference between the observed response and the fitted response
+**** Randy edit the following equation to reflect the fact that we're fitting in log space. --MKH ****
 %
@@
 %
-The details for each of the models are discussed in 
+Details for each of the models are discussed in 
 Sections~\ref{sec:CD_Parameter_Estimation}--\ref{sec:LINEX_Parameter_Estimation} below.
@@
 Thus, a resampled response $\tilde Y'$ can be computed as 
+**** Randy edit the following equations to reflect the fact that we're fitting in log space? --MKH ****
 %
@@
 in our testing, nearly always violated them, often returning
-negative values for elasticity of substitution~($\sigma$) parameters.
+negative values for elasticity of substitution parameters $\sigma$ and $\sigma_1$.
 Thus, we used the two fitting algorithms available in \texttt{cesEst} that
@@
 The start values for fitting parameters are taken from 
-the grid search fit that provided the lowest $sse$ (Equation~\ref{eq:sse}).
+the grid search point that provided the lowest $sse$ (Equation~\ref{eq:sse}).
 
@@
 In Figures~\ref{fig:CES_sigma1_delta1_graph} and~\ref{fig:CES_sigma_delta_graph},
-the bottom of the vertical axis represents $\sigma = 0$ (perfect complements).
-The top of the vertical axis represents $\sigma = \infty$ (perfect substitutes).
+the bottom of the vertical axes represents $\sigma = 0$ (perfect complements).
+The top of the vertical axes represents $\sigma = \infty$ (perfect substitutes).
 
@@
 Equation~\ref{eq:LINEX_transformed} in log-transformed space. 
-We recovered a value for $c_t$ with $c_t = a_1 / a_0$. 
+We recovered the value of $c_t$ with $c_t = a_1 / a_0$. 
 Figure~\ref{fig:LINEXq_Resample_Graph}
 shows the coefficients estimated from resampled data.
-We fit $a_0$ and $c_t$ unconstrained.
+We fit $a_0$ and $c_t$ as unconstrained constants.
 

### 2014-12-30 Articles/Article_EnerEcon_2014/EconGrowth3.Rnw
Many additional edits.

@@
 % #4 sigma_1 for (le)k nest
-\newcommand{\firstrow}[4]{\multirow{2}{*}{$\sigma_1$} & ($\underline{kl}$) & #1 
+\newcommand{\firstrow}[4]{\multirow{2}{*}{$\sigma_1$} & ($\underline{k}$+$\underline{l}$)+() & #1 
                                   &  & 
                                         & &  \\
-                            & ($\underline{kl}$)$e$ & #2
-                                  & ($\underline{ek}$)$l$ & #3
-                                        & ($\underline{le}$)$k$ & #4 \\
+                            & ($\underline{k}$+$\underline{l}$)+($e$) & #2
+                                  & ($\underline{e}$+$\underline{k}$)+($l$) & #3
+                                        & ($\underline{l}$+$\underline{e}$)+($k$) & #4 \\
 }
@@
 \newcommand{\secondrow}[6]{      \multirow{3}{*}{$\sigma$} & &
-                                      & ($\underline{k}l$)$\underline{e}$ & #1
-                                            & ($k\underline{l}$)$\underline{e}$ & #2 \\
-                                & ($\underline{l}e$)$\underline{k}$ & #3
-                                      & ($l\underline{e}$)$\underline{k}$ & #4
+                                      & ($\underline{k}$+$l$)+($\underline{e}$) & #1
+                                            & ($k$+$\underline{l}$)+($\underline{e}$) & #2 \\
+                                & ($\underline{l}$+$e$)+($\underline{k}$) & #3
+                                      & ($l$+$\underline{e}$)+($\underline{k}$) & #4
                                             &  & \\
-                                & ($e\underline{k}$)$\underline{l}$ & #5
+                                & ($e$+$\underline{k}$)+($\underline{l}$) & #5
                                       & &
-                                            & ($\underline{e}k$)$\underline{l}$ & #6 \\
+                                            & ($\underline{e}$+$k$)+($\underline{l}$) & #6 \\
 }
@@
 
+We choose the resampling approach instead of the more-common technique 
+of estimating confidence intervals from standard errors for two reasons. 
+First, model parameters are highly constrained, and confidence intervals often violate the constraints. 
+For example a result of $\alpha = 0.25 \pm 0.3$ is nonsensical, 
+because $ \alpha \in [0, 1]$. 
+Second, true confidence intervals for constrained parameters are often asymmetric
+(e.g., $\alpha = 0.2 + 0.1, -0.05$), 
+but the standard error approach yields symmetric confidence intervals. 
+The resampling approach that we employed both respects constraints 
+and allows for asymmetric confidence intervals.%
+  \footnote{
+  In addition, we choose to present parameter uncertainty results visually 
+  (see Figures~\ref{fig:CD_lambda_theta_graph}, \ref{fig:CD_Ternary_Scatter_Graph},
+  \ref{fig:CES_lambda_gamma_graph}--\ref{fig:CES_ternary_graph}, and
+  \ref{fig:LINEXq_Resample_Graph}),
+  both because the resampling technique lends itself to visual presentation and 
+  because we believe visual comparison is more effective than tables of numbers.
+  }
+
 %++++++++++++++++++++++++++++++
@@
 
+<<abg_trajectories, eval=FALSE>>=
+# This code can be run to test the conclusion about the LINEX model meeting constraints.
+# This chunk of R code has eval=FALSE, because it is not a part of the paper.
+Calvin_Models <- loadPostProcessedData(Source = "Calvin", kind = "models", dir=pp_path)
+abgplotdata <- fortify(Calvin_Models$Calvin$IR$linex$`iK+iL+iQp`)
+triPlot(data=abgplotdata, grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear")
+@
+
 The LINEX model coefficients $a_0$ and $c_t$ imply time-varying
@@
 
+**** Other notes from our Word document that didn't fit anywhere above. ****
+
+Lastly, what do aggregate models say?
+
+What direction can take from this work?
+
+What is the status of ME growth modeling after this?
+
+**** End other notes ****
+
 We find it beneficial to discuss the results through a series of questions, 
@@
 
-**** We need to think about the order of the subsections below. --MKH ****
+**** Martin: Do you think it would be helpful to tie the conclusions 
+of each section to the literature? 
+If so, give it a shot. --MKH ****
 
@@
   }
-First, we look at the results of the Cobb-Douglas functions 
+First, we evaluate the results of the Cobb-Douglas functions 
 in Figures~\ref{fig:CD_lambda_theta_graph} and~\ref{fig:CD_Ternary_Scatter_Graph}. 
@@
 because all resample data points are consistently far above the base of the ternary plots 
-($\gamma \gg 0$) for all possible ways of nesting of energy with capital and labor. 
+($\gamma \gg 0$) for all possible ways of nesting energy with capital and labor. 
 Two out of the three possible nestings suggest the importance of including energy for Japan and Tanzania.
@@
 while some others (United Kingdom) benefit in a minor way. 
-For other developed economies (Japan), the results of CD and CES models point in opposite directions.  
-For NICs, the results are mixed; 
+For other developed economies (Japan), 
+the results of Cobb-Douglas and CES models point in opposite directions.  
+For NICs, the results are mixed:
 China does not convincingly benefit from energy-augmented production functions, 
 and results are uncertain for South Africa due to lack of precision in determining $\gamma$.  
-In one OPEC country, Saudi Arabia, adding energy clearly helps to explain economic growth, 
-while in another, Iran, the benefit of energy augmentation is small and uncertain. 
+In one OPEC country (Saudi Arabia) adding energy clearly helps to explain economic growth, 
+while in another (Iran), the benefit of energy augmentation is small and uncertain. 
 For LDCs there is a either a strong indication that energy-augmented production functions 
@@
 primary energy in the production function reduces the \emph{value of} the Solow residual,
-as opposed to eliminating the \emph{need for} the Solow residual altogether (Ayres and Warr's question).
-After augmenting by energy, the Solow-residual ($\lambda$) 
+as opposed to eliminating the \emph{need for} the Solow residual altogether 
+(\citeauthor{Ayres:2010ug}'s question).
+After augmenting by energy, the Solow-residual~($\lambda$) 
 in the Cobb-Douglas~(Figure~\ref{fig:CD_lambda_theta_graph}) 
-and CES models~(\ref{fig:CES_lambda_gamma_graph}) 
-still explains a part of economic growth in several economies, 
-especially China, but also in the United Kingdom, Japan, and Tanzania,  
-and to a lesser extent in the United States and Iran. 
-In South Africa and Zambia, the Solow-residual is zero, while in Saudi Arabia it is negative.%
+and CES models~(Figure~\ref{fig:CES_lambda_gamma_graph}) 
+still explains a part of economic growth for several economies, 
+especially China, but also for the United Kingdom, Japan, and Tanzania,  
+and to a lesser extent for the United States and Iran. 
+In South Africa and Zambia, the Solow-residual is zero, while for Saudi Arabia it is negative.%
   \footnote{
   The negative Solow residual ($\lambda$) for Saudi Arabia is a consequence
-  of the fact that all indexed factors of production ($k$, $l$, and $e$) are greater than 
-  economic output ($y$) for most of the period under study (1991--2011).
+  of the fact that all indexed factors of production~($k$, $l$, and $e$) are greater than 
+  economic output~($y$) for most of the period under study (1991--2011).
+  See Figure~\ref{fig:Historical_Graph}.
   }
@@
 %++++++++++++++++++++++++++++++
+\subsection{Implications of parameter uncertainty} 
+\label{sec:implications}
+%++++++++++++++++++++++++++++++
+
+In addition to the usual parameter estimation process 
+by linear coefficient determination (Cobb-Douglas and LINEX) 
+and non-linear optimization algorithms (CES), 
+the resampling analysis performed herein 
+provides insight into the questions of 
+(a)~how accurately parameters are known and 
+(b)~the implications of parameter imprecision.
+
+A significant result to emerge from this work is that large parameter uncertainty 
+does not necessarily lead to poor model fit to historical economic output. 
+To choose one example of many, 
+the value of $\gamma$ for the Cobb-Douglas model for Tanzania (0.59) 
+shows a resampling range of 0.2--0.9. 
+(See Figure~\ref{fig:CD_Ternary_Scatter_Graph}.) 
+Yet, Cobb-Douglas models for Tanzania, with and without energy, both 
+(a)~fit historical data very well 
+(white line compared to black line in Tanzania row of Figure~\ref{fig:CD_GDP_Spaghetti_Graph}) 
+and 
+(b)~exhibit a very narrow range of resampled fits 
+(thin gray band in Tanzania row of Figure~\ref{fig:CD_GDP_Spaghetti_Graph}). 
+This means that a good fit to historical data does not indicate 
+that model parameters have small uncertainty. 
+In fact, similar to Tanzania, 
+many economies exhibit both large uncertainty in model parameters and
+very good fit to historical data. 
+(See Figures~\ref{fig:CD_lambda_theta_graph} and~\ref{fig:CD_Ternary_Scatter_Graph} 
+compared to Figure~\ref{fig:CD_GDP_Spaghetti_Graph}
+for the Cobb-Douglas models and 
+Figure~\ref{fig:CES_lambda_gamma_graph}--\ref{fig:CES_sigma_delta_graph}
+compared to Figure~\ref{fig:CES_Spaghetti_Graph} for CES models.) 
+This result is consistent across almost all economies and models. 
+Thus, we conclude that great care must be taken when interpreting estimated parameters: 
+it is very easy to claim more certainty than is warranted. 
+Where large uncertainty is observed, 
+additional work is needed to contextualize the results, 
+for example, 
+sector-based analysis or ****. **** Martin, add more here? ****
+
+**** Not sure whether contextualization will work. 
+Could be read that macroeconomic growth modeling in such cases is not really useful at all? 
+--MdW ****
+
+The implications of parameter uncertainties should be obvious, 
+but we will state them here. 
+Policy based upon parameters with high uncertainty can lead to bad, or completely wrong, policy. 
+**** Martin: can you find an example in our results that drives this point home? --MKH  
+May be barking up wrong production factor, may assume subs when complementarity: ****
+
+%++++++++++++++++++++++++++++++
+\subsection{Is $R^2$ a good criterion for choosing a model?} 
+\label{sec:is_r2_good}
+%++++++++++++++++++++++++++++++
+
+We caution against using $R^2$ as the only criterion for choosing a model, 
+because, in our experience, 
+both Cobb-Douglas and CES models yield high $R^2$ values for all countries 
+(see Figures~\ref{fig:CD_GDP_Spaghetti_Graph} and~\ref{fig:CES_Spaghetti_Graph}), yet
+very different uncertainties for fitted parameters.
+In some cases, LINEX models fare poorly regarding $R^2$ and might be excluded on that basis. 
+(See South Africa and Tanzania in Figure~\ref{fig:LINEX_Spaghetti_Graph}.) 
+In our opinion, 
+it is equally, if not more, important to know the uncertainty 
+of estimated parameters than to assess $R^2$.
+With rigorous uncertainty testing as we have done here, 
+the quality of parameter estimates is exposed: 
+at a glance, the tightness of resampled results indicates 
+whether or not confidence in the parameters or model is warranted. 
+We conclude that it is insufficient to argue 
+in favor of a particular production function 
+on the grounds of $R^2$ alone.
+
+%++++++++++++++++++++++++++++++
 \subsection{Does the CES model structure (nesting) matter?} 
@@
 
-The choice of CES nesting structure has significant influence 
-on model results for both 
+The subsections below assess whether the choice of CES nesting structure 
+influences model results for both 
 relative importance of factors of production ($\delta$ and $\delta_1$ values) and 
@@
 Figure~\ref{fig:CES_ternary_graph} shows that the relative importance of 
-production factors capital~($k$), labour~($l$), and energy~($e$) 
+production factors capital~($k$), labor~($l$), and energy~($e$) 
 is different for the three different CES nestings (Equations~\ref{eq:CESkle}--\ref{eq:CESekl}). 
@@
 For example, 
-for Iran's ($kl$)$e$ nesting in Figures~\ref{fig:CES_sigma1_delta1_graph}--\ref{fig:CES_ternary_graph} 
+for Iran's ($k$+$l$)+($e$) nesting in Figures~\ref{fig:CES_sigma1_delta1_graph}--\ref{fig:CES_ternary_graph}, 
 there is virtually no useful information 
 in $\delta$, $\delta_1$, $\alpha$, $\beta$, and $\gamma$.
+
+Thus, we find that nesting has significant influence on model results.
 
@@
 appears in the following nests: 
-($\underline{kl}$), 
-($\underline{kl}$)$e$, 
-($\underline{l}e$)$\underline{k}$, and 
-($e\underline{k}$)$\underline{l}$. 
+($\underline{k}$+$\underline{l}$), 
+($\underline{k}$+$\underline{l}$)+($e$), 
+($\underline{l}$+$e$)+$\underline{k}$, and 
+($e$+$\underline{k}$)+$\underline{l}$. 
 Tables~\ref{tab:sigma_US}--\ref{tab:sigma_ZM} 
 provide interpretation of Figures~\ref{fig:CES_sigma1_delta1_graph}
-and~\ref{fig:CES_sigma1_delta1_graph}. 
+and~\ref{fig:CES_sigma_delta_graph}. 
 In the tables,
@@
 we find complementarity~(C and c) among factors of production 
-for most economies with the exception of China 
-where an indication of substitutability between labor and energy is observed~(S and s).
+for most economies with the exception of China, 
+where an indication of substitutability between labor and energy is observed.
 
@@
 is a troubling characteristic of the estimated CES coefficients 
-that is rarely reported in the literature.
-For some economies (Iran and Zambia), 
+that is rarely investigated in the literature.
+Indeed, for some economies (Iran and Zambia), 
 estimating any elasticity of substitution at all is problematic and fraught with peril. 
@@
 (United States, United Kingdom, and Japan) exhibits large uncertainty.
-(See United States and United Kingdom rows in Figures~\ref{fig:CD_Ternary_Scatter_Graph}  
-and~\ref{fig:CES_sigma1_delta1_graph}--\ref{fig:CES_ternary_graph}.)
-
-Some of the uncertainty is explained by the structure of the CES model. 
+
+Some of the uncertainty is explained by the structure of the CES model itself. 
 If $\delta$ or $\delta_1$ achieves an extreme value (0 or 1), 
@@
 
+\vspace{5 mm}
+
 Based on the results and discussions above 
@@
 to enhance the reliability of results. 
-
-%++++++++++++++++++++++++++++++
-\subsection{Implications of parameter uncertainty} 
-\label{sec:implications}
-%++++++++++++++++++++++++++++++
-
-In addition to the usual parameter estimation process 
-by linear coefficient determination (Cobb-Douglas and LinEx) 
-and non-linear optimization algorithms (CES), 
-the resampling analysis performed herein 
-provides insight into the questions of 
-(a)~how accurately parameters are known and 
-(b)~the implications of parameter imprecision.
-
-**** Move this paragraph elsewhere? --MKH ****
-We chose the resampling approach instead of the more-common technique 
-of estimating confidence intervals from standard errors for two reasons. 
-(1)~Model parameters are highly constrained, and confidence intervals often violate the constraints. 
-For example a result of $\alpha = 0.25 \pm 0.3$ is nonsensical, 
-because $ \alpha \in [0, 1]$. 
-(2)~True confidence intervals for constrained parameters are often asymmetric
-(e.g., $\alpha = 0.2 + 0.1, -0.05$), 
-but the standard error approach yields symmetric confidence intervals. 
-The resampling approach that we employed both respects constraints 
-and allows for asymmetric confidence intervals.%
-  \footnote{
-  We have chosen to present parameter uncertainty results visually, 
-  both because the resampling technique lends itself to visual presentation and 
-  because we believe visual comparison is more effective than tablefuls of numbers.
-  }
-
-A significant result to emerge from this work is that large parameter uncertainty 
-does not necessarily lead to poor model fit to historical economic output. 
-To choose one example of many, 
-the value of $\gamma$ for the Cobb-Douglas model for Tanzania (0.59) 
-shows a resampling range of 0.2--0.9. 
-(See Figure~\ref{fig:CD_Ternary_Scatter_Graph}.) 
-Yet, Cobb-Douglas models for Tanzania, with and without energy, both 
-(a)~fit historical data very well 
-(white line compared to black line in Tanzania row of Figure~\ref{fig:CD_GDP_Spaghetti_Graph}) 
-and 
-(b)~exhibit a very narrow range of resampled fits 
-(thin gray band in Tanzania row of Figure~\ref{fig:CD_GDP_Spaghetti_Graph}). 
-This means that a good fit to historical data does not indicate 
-that model parameters have small uncertainty. 
-In fact, similar to Tanzania, 
-many economies exhibit both large uncertainty in model parameters and
-very good fit to historical data. 
-(See Figures~\ref{fig:CD_lambda_theta_graph} ~\ref{fig:CD_Ternary_Scatter_Graph} 
-compared to Figure~\ref{fig:CD_GDP_Spaghetti_Graph}
-for the Cobb-Douglas models and 
-Figure~\ref{fig:CES_lambda_gamma_graph}--\ref{fig:CES_sigma_delta_graph}
-compared to Figure~\ref{fig:CES_Spaghetti_Graph} for CES models.) 
-This result is consistent across almost all economies and models. 
-Thus, we conclude that great care must be taken when interpreting estimated parameters: 
-it is very easy to claim more certainty than is warranted. 
-Where large uncertainty is observed, 
-additional work is needed to contextualize the results, 
-for example, 
-sector-based analysis or ****. **** Martin, add more here? ****
-
-**** Not sure whether contextualization will work. 
-Could be read that macroeconomic growth modeling in such cases is not really useful at all? 
---MdW ****
-
-The implications of parameter uncertainties should be obvious, 
-but we will state them here. 
-Basing policy upon parameters with high uncertainty can lead to bad, or completely wrong, policy. 
-**** Martin: can you find an example in our results that drives this point home? --MKH  
-May be barking up wrong production factor, may assume subs when complementarity: ****
-
-%++++++++++++++++++++++++++++++
-\subsection{Is $R^2$ a good criterion for choosing a model?} 
-\label{sec:is_r2_good}
-%++++++++++++++++++++++++++++++
-
-We caution against using $R^2$ as the only criterion for choosing a model, 
-because, in our experience, 
-both Cobb-Douglas and CES models yield high $R^2$ values for all countries 
-(see Figures~\ref{fig:CD_GDP_Spaghetti_Graph} and~\ref{fig:CES_Spaghetti_Graph}), yet
-very different uncertainties for fitted parameters.
-In some cases, LINEX models fare poorly regarding $R^2$ and might be excluded on that basis. 
-(See SA and TZ in Figure~\ref{fig:LINEX_Spaghetti_Graph}.) 
-In our opinion, 
-it is equally, if not more, important to know the uncertainty 
-of estimated parameters than to assess $R^2$.
-With rigorous uncertainty testing as we have done here, 
-the quality of parameter estimates is exposed: 
-at a glance, the tightness of resampled results indicates 
-whether or not confidence in the model and data is warranted. 
-We conclude that it is insufficient to argue 
-in favor of a particular production function 
-on the grounds $R^2$.
-
-**** Other notes from our Word document that didn't fit anywhere above. ****
-
-Lastly, what do aggregate models say?
-
-What direction can take from this work?
-
-What is the status of ME growth modeling after this?
+**** Would econometrically specifying production function relationships and
+performing sensitivity analysis really ``enhance the reliability'' of results? 
+Or, would doing so improve transparency? --MKH ****
 
@@
 to the question of which production function is best
-for describing the role of energy in economic growth:
+for describing the role of energy in economic growth. 
+We consider four criteria here:
 best match to historical data, 
@@
 minimum uncertainty in model parameters, and
-easy parameter estimation process.
+robust parameter estimation process.
 In the sections below, we evaluate the Cobb-Douglas, CES, and LINEX
-models using these criteria.
+models on these criteria.
 
@@
   The order of these results is unsurprising: 
-  CES contains 6 fitted parameters; Cobb-Douglas, 4; and LINEX, 3.
+  energy-augmented CES contains 6 fitted parameters; 
+  Cobb-Douglas, 4; 
+  and LINEX, 3.
   We expect models with more parameters to provide a better fit to historical data.
@@
   \footnote{
-  We also note that in contrast to our approach, shared by \citet{Warr:2012cg},
-  of fitting constant $a_0$ and $c_t$ values, 
+  We also note that in contrast to our approach of fitting constant $a_0$ and $c_t$ values, 
+  which is shared by \citet{Warr:2012cg},
   \citet{Kummel:2011aa} used logistic functions to generate time-varying
@@
 
-The energy-augmented CES production function presents ambiguity to the energy analyst
+The energy-augmented CES production function presents 
+significant ambiguity to the energy analyst
 in the form of the choice of factor nesting.
-We showed above that nesting can significantly affect 
-the interpretation of macroecnomic dynamics, especially 
-the relative importance of factors of production~(\ref{fig:CES_ternary_graph}) and 
+We showed above that choice of nesting 
+can significantly affect 
+the interpretation of macroecnomic dynamics, 
+especially the relative importance of 
+factors of production (see Section~\ref{sec:importance_of_factors}
+and Figure~\ref{fig:CES_ternary_graph}) and 
 the understanding of substitutibility 
-among factors of production. (See Section~\ref{sec:elasticity_of_substitution}).
+among factors of production (see Section~\ref{sec:elasticity_of_substitution}).
 Thus, the CES production function has the undesireable characteristic 
@@
 Neither the Cobb-Douglas nor the LINEX production function 
-exhibits similar structural ambiguity.
-
-Thus, Cobb-Douglas or LINEX are preferred on this criterion.
+presents similar structural ambiguity.
+
+Thus, Cobb-Douglas and LINEX are preferred on this criterion.
 
@@
 Cobb-Douglas and LINEX have, by and large, 
-smaller uncertainties in fitted parameters than the CES production function.
+smaller uncertainties in fitted parameters than CES.
 Thus, Cobb-Douglas and LINEX are preferred on this criterion.
@@
 affords easy mathematical and numerical implementation, 
-provides an easy way to respect fitted parameter constraints, and
+provides an easy way to respect constraints on fitted parameters, and
 allows asymmetric estimates of fitted parameter uncertainty.
@@
 (See Section~\ref{sec:CES_Parameter_Estimation}.)
-On the 40-node \texttt{dahl} supercomputer at Calvin College~\citep{Adams:2008aa},
+On the \texttt{dahl} supercomputer at Calvin College~\citep{Adams:2008aa},
 complete analysis of all data shown in this paper
@@
 \texttt{cesEst} function~\citep{Henningsen:2011td} and is, therefore,
-relatively easy to implement.
+also relatively easy to implement.
 In contrast, because output elasticities $\alpha$, $\beta$, and $\gamma$ 
@@
   \footnote{
-  See \citet{Kummel:2011aa} for one approach to respecting parameter constraints 
+  See \citet{Kummel:2011aa} for an approach to respecting parameter constraints 
   for the LINEX function. 
   }
-Indeed, we found in Section~\ref{sec:LINEX_Parameter_Estimation}
+Indeed, we found (Section~\ref{sec:LINEX_Parameter_Estimation})
 that the LINEX model regularly violates parameter constraints.
@@
 of asymmetric parameter uncertainties. 
-Thus, none of the prodcution functions are preferred over the others on this criterion.
+Thus, none of the prodcution functions are preferred over any other on this criterion.
 
@@
 
-If you need to represent rebound effects (not just backfire), 
+If one needs to represent rebound effects (not just backfire), 
 CES \emph{must} be employed, 
@@
 is tied to the presence of elasticities of substitution ($\sigma$ and $\sigma_1$) in the CES model.
-Unfortunately, we resampling analyses show that estimated values 
+Unfortunately, the resampling analyses show that estimated values 
 of elasticity of substitution are often highly uncertain.
@@
 
-The LINEX model is intriguing, because of its thermodynamic roots, 
+The LINEX model is intriguing because of its thermodynamic roots, 
 but our implementation suffers from 

### 2014-12-31 Articles/Article_EnerEcon_2014/EconGrowth3.Rnw
Changed to using oModels in the code we don't use.

@@
 # This code can be run to test the conclusion about the LINEX model meeting constraints.
+# Need to put oModels in the environment much earlier in this file.
 # This chunk of R code has eval=FALSE, because it is not a part of the paper.
-Calvin_Models <- loadPostProcessedData(Source = "Calvin", kind = "models", dir=pp_path)
-abgplotdata <- fortify(Calvin_Models$Calvin$IR$linex$`iK+iL+iQp`)
+abgplotdata <- fortify(oModels$Calvin$IR$linex$`iK+iL+iQp`)
 triPlot(data=abgplotdata, grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear")

### 2015-01-01 Articles/Article_EcolEcon_2014/Paper2.Rnw
Clarified how fraction of GDP is calculated.

@@
 First, assume constant returns to scale such that $\gamma = 1 - \alpha - \beta$.
-Then, take the natural logarithm ($\ln$) of Equation~\ref{eq:CD} to obtain
+Then, take the natural logarithm ($\ln$) of Equation~\ref{eq:CDe} to obtain
 %
@@
 
+The fraction of GDP growth explained by the Solow residual~($f$)
+can be given as
+%
+\begin{equation} \label{eq:frac_growth_explained_by_solow}
+  f \equiv \frac{\lambda}{\frac{1}{y}\frac{\mathrm{d}y}{\mathrm{d}t}} 
+            = 1 - \frac{\alpha \frac{1}{k}\frac{\mathrm{d}k}{\mathrm{d}t} 
+                      + \beta \frac{1}{l}\frac{\mathrm{d}l}{\mathrm{d}t} 
+                      + (1 - \alpha - \beta) \frac{1}{e}\frac{\mathrm{d}e}{\mathrm{d}t}}
+                  {\frac{\lambda}{\frac{1}{y}\frac{\mathrm{d}y}{\mathrm{d}t}}}
+\end{equation}
+%
 If we approximate derivatives in Equation~\ref{eq:lambda} with forward differences
@@
   \lambda_{i,j}
-    \approx \frac{1}{y_i}\frac{y_j - y_i}{t_j - t_i} 
+    = \frac{1}{y_i}\frac{y_j - y_i}{t_j - t_i} 
     - \left[
@@
   \lambda_{1,n}
-    \approx \frac{1}{y_1}\frac{y_n - y_1}{t_n - t_1} 
+    = \frac{1}{y_1}\frac{y_n - y_1}{t_n - t_1} 
       - \left[ 
@@
   \lambda_{1,n}
-    \approx \frac{\sum_{i=2}^{n} \lambda_{i,i-1}}{n-1}
+    = \frac{\sum_{i=2}^{n} \lambda_{i,i-1}}{n-1}
 \end{equation}
@@
 given by Equation~\ref{eq:lambda}.
+
+Using forward differences to estimate $f$ yields
+%
+\begin{equation} \label{eq:f_finite_diff}
+  f_{i,j} = \frac{\lambda_{i,j}}{\frac{1}{y_i}\frac{y_j - y_i}{t_j - t_i}}
+       = 1 - \frac{\alpha \frac{1}{k_i}\frac{k_j - k_i}{t_j - t_i} 
+            + \beta \frac{1}{l_i}\frac{l_j - l_i}{t_j - t_i} 
+            + (1 - \alpha - \beta) \frac{1}{e_i}\frac{e_j - e_i}{t_j - t_i} }
+            {\frac{1}{y_i}\frac{y_j - y_i}{t_j - t_i}}
+\end{equation}
+%
+which is an estimate to the true value of $f$ given by Equation~\ref{eq:frac_growth_explained_by_solow}.
 
@@
 
-<<CD_solowPerc_time_series, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap='Solow residual time series.'>>=
+<<CD_solowPerc_time_series, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap='Fraction of GDP growth explained by Solow residual~($\\lambda$).'>>=
 # Create a time series graph of the solowPerc values

### 2015-01-01 Articles/Article_EcolEcon_2014/Paper2.Rnw
Rewritten section on lambda and f.

--- 2014-12-10 Articles/Article_EcolEcon_2014/Paper2.Rnw
@@
 of production: $\alpha + \beta + \gamma = 1$.
-
 The term $\mathrm{e}^{\lambda (t-t_0)}$ is known as total factor productivity~($A$),
 and $\lambda$ is the Solow residual.
+
+%..............................
+\paragraph{Estimating the Solow residual} 
+\label{sec:estimating_the_solow_residual}
+%..............................
+
 Assuming that parameters $\theta$, $\alpha$, and $\beta$ are known from parameter estimation,
@@
 %
-Solving for the Solow Residual term gives
+Solving for the total factor productivity term gives
 %
@@
 given by Equation~\ref{eq:lambda}.
+
+%..............................
+\paragraph{Fraction of growth explained by the Solow residual} 
+\label{sec:fraction_of_growth_solow}
+%..............................
+
+The fraction of GDP growth explained by the Solow residual~($f$)
+can be given as
+%
+\begin{equation} \label{eq:frac_growth_explained_by_solow}
+  f \equiv \frac{\lambda}{\frac{1}{y}\frac{\mathrm{d}y}{\mathrm{d}t}} 
+            = 1 - \frac{\alpha \frac{1}{k}\frac{\mathrm{d}k}{\mathrm{d}t} 
+                      + \beta \frac{1}{l}\frac{\mathrm{d}l}{\mathrm{d}t} 
+                      + (1 - \alpha - \beta) \frac{1}{e}\frac{\mathrm{d}e}{\mathrm{d}t}}
+                  {\frac{1}{y}\frac{\mathrm{d}y}{\mathrm{d}t}} \; .
+\end{equation}
+%
+Using forward differences to estimate $f$ yields
+%
+\begin{equation} \label{eq:f_finite_diff}
+  f_{i,j} = \frac{\lambda_{i,j}}{\frac{1}{y_i}\frac{y_j - y_i}{t_j - t_i}}
+       = 1 - \frac{\alpha \frac{1}{k_i}\frac{k_j - k_i}{t_j - t_i} 
+            + \beta \frac{1}{l_i}\frac{l_j - l_i}{t_j - t_i} 
+            + (1 - \alpha - \beta) \frac{1}{e_i}\frac{e_j - e_i}{t_j - t_i} }
+            {\frac{1}{y_i}\frac{y_j - y_i}{t_j - t_i}} \; ,
+\end{equation}
+%
+which is an estimate to the true value of $f$ given by Equation~\ref{eq:frac_growth_explained_by_solow}.
 
@@
 
-Given the estimates for $\alpha$, $\beta$, and $\gamma$ for the Cobb-Douglas model,
-we can estimate values for $\lambda$ on a year-by-year basis using Equation~\ref{eq:lambdaij}.
-The results are shown in the Figure~\ref{fig:CD_lambda_time_series}.
-
 <<CD_finite_diff_calcs, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap='Solow residual time series.'>>=
@@
 # Calculate finite difference approximations of time derivatives for output and all factors of production
+lag <- 5       # Desired lag for calculations. Set to n for differences across n years.
+pad <- "tail"  # Desired padding for NA valuse
 fd <- m_histData %>% group_by(Source, Country, energyType) %>% arrange(Year) %>% 
-  mutate(dydt = ediff(iGDP, pad="tail") / ediff(Year, pad="tail")) %>%
-  mutate(dkdt = ediff(iK, pad="tail") / ediff(Year, pad="tail")) %>%
-  mutate(dldt = ediff(iL, pad="tail") / ediff(Year, pad="tail")) %>%
-  mutate(dedt = ediff(iE, pad="tail") / ediff(Year, pad="tail"))
+  mutate(dydt = ediff(iGDP, pad=pad, lag=lag) / ediff(Year, pad=pad, lag=lag)) %>%
+  mutate(dkdt = ediff(iK, pad=pad,   lag=lag) / ediff(Year, pad=pad, lag=lag)) %>%
+  mutate(dldt = ediff(iL, pad=pad,   lag=lag) / ediff(Year, pad=pad, lag=lag)) %>%
+  mutate(dedt = ediff(iE, pad=pad,   lag=lag) / ediff(Year, pad=pad, lag=lag))
 
@@
 
+Given the estimates for $\alpha$, $\beta$, and $\gamma$ for the Cobb-Douglas model,
+we can estimate values for $\lambda$ by $\lambda_{i,j}$,
+with $i$ and $j$ in Equation~\ref{eq:lambdaij} separated by \Sexpr{lag} years.
+The results are shown in Figure~\ref{fig:CD_lambda_time_series}.
+
+We can also estimate values for 
+the fraction of economic growth explained by the Solow residual ($f$)
+by $f_{ij}$
+with $i$ and $j$ in Equation~\ref{eq:f_finite_diff} separated by \Sexpr{lag} years.
+The results are shown in Figure~\ref{fig:CD_solowPerc_time_series}.
+
 <<CD_lambda_time_series, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap='Solow residual time series.'>>=
@@
 
-<<CD_solowPerc_time_series, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap='Solow residual time series.'>>=
+<<CD_solowPerc_time_series, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap='Fraction of GDP growth explained by Solow residual.'>>=
 # Create a time series graph of the solowPerc values
@@
   facet_grid(Country ~ energyType) +
-  labs(x = "", y = "Fraction of GDP growth explained by Solow residual") + 
+  labs(x = "", y = "f") + 
   scale_y_continuous(limits=c(-0.5, 2)) +

### 2015-01-01 Articles/Article_EcolEcon_2014/Paper2.Rnw
Small edits.

@@
 \begin{equation} \label{eq:CD}
-  y = \theta \mathrm{e}^{\lambda(t-t_0)} k^\alpha l^\beta \;,
+  y = \theta A k^\alpha l^\beta \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)} \; ,
 \end{equation}
@@
 \begin{equation} \label{eq:CDe}
-  y = \theta \mathrm{e}^{\lambda(t-t_0)}  k^\alpha l^\beta e^\gamma \;,
+  y = \theta A k^\alpha l^\beta e^\gamma \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)} \; ,
 \end{equation}
@@
 of production: $\alpha + \beta + \gamma = 1$.
-The term $\mathrm{e}^{\lambda (t-t_0)}$ is known as total factor productivity~($A$),
+The term $A$ is known as total factor productivity,
 and $\lambda$ is the Solow residual.
@@
 
-Assuming that parameters $\theta$, $\alpha$, and $\beta$ are known from parameter estimation,
+Assuming that parameters $\theta$, $\alpha$, and $\beta$
+in Equation~\ref{eq:CDe} are known from parameter estimation,
 we can estimate the value of $\lambda$ as follows.
-First, assume constant returns to scale such that $\gamma = 1 - \alpha - \beta$.
+First, assume constant returns to scale such that 
+$\alpha + \beta + \gamma = 1$, 
+and calculate $\gamma = 1 - \alpha - \beta$.
 Then, take the natural logarithm ($\ln$) of Equation~\ref{eq:CDe} to obtain
@@
 where $\lambda_{i,j}$ approximates the true, instantaneous value of $\lambda$
-between times $i$ and $j$.
+from Equation~\ref{eq:lambda} between times $i$ and $j$.
 
@@
 %
-\begin{equation} \label{eq:f_finite_diff}
+\begin{equation} \label{eq:f_finite_diff_1}
   f_{i,j} = \frac{\lambda_{i,j}}{\frac{1}{y_i}\frac{y_j - y_i}{t_j - t_i}}
@@
             + (1 - \alpha - \beta) \frac{1}{e_i}\frac{e_j - e_i}{t_j - t_i} }
-            {\frac{1}{y_i}\frac{y_j - y_i}{t_j - t_i}} \; ,
-\end{equation}
-%
-which is an estimate to the true value of $f$ given by Equation~\ref{eq:frac_growth_explained_by_solow}.
+            {\frac{1}{y_i}\frac{y_j - y_i}{t_j - t_i}} \; .
+\end{equation}
+%
+Simplifying slightly gives
+%
+\begin{equation} \label{eq:f_finite_diff_2}
+  f_{i,j} = 1 - \frac{\alpha \left( \frac{k_j}{k_i} - 1 \right) 
+                      + \beta \left( \frac{l_j}{l_i} - 1 \right)
+                      + (1 - \alpha - \beta) \left( \frac{e_j}{e_i} - 1 \right)}
+            {\left( \frac{y_j}{y_i} - 1 \right)} \; ,
+\end{equation}
+%
+which is an estimate to the instantaneous value of $f$ 
+given by Equation~\ref{eq:frac_growth_explained_by_solow}.
 
@@
 by $f_{ij}$
-with $i$ and $j$ in Equation~\ref{eq:f_finite_diff} separated by \Sexpr{lag} years.
+with $i$ and $j$ in Equation~\ref{eq:f_finite_diff_2} separated by \Sexpr{lag} years.
 The results are shown in Figure~\ref{fig:CD_solowPerc_time_series}.

### 2015-01-01 Articles/Article_EcolEcon_2014/Paper2.Rnw
Explanatory note.
Moved text for spaghetti graphs.
Minor edits.

@@
 
-The fraction of GDP growth explained by the Solow residual~($f$)
+The fraction~($f$) of GDP growth explained by the Solow residual
 can be given as
@@
 %
-Simplifying slightly gives
+Simplifying by cancelling $t_j - t_i$ terms and simplifying gives
 %
@@
 %
-which is an estimate to the instantaneous value of $f$ 
+which is an estimate of the instantaneous value of $f$ 
 given by Equation~\ref{eq:frac_growth_explained_by_solow}.
@@
 
-Figures~\ref{fig:CD_GDP_Spaghetti_Graphs_US}--\ref{fig:CD_GDP_Spaghetti_Graphs_CN} 
-compare predictions 
-from the Cobb-Douglas models 
-(without and with energy) to historical data.
-Historical data are shown as a black line. 
-The fit to historical data is shown as a white line.
-The gray band encompasses \Sexpr{spaghettiGraphLevel*100}\% of the fits to resampled data.
-
 <<CD_lambda_theta_graph, fig.pos="H", fig.align='center', fig.width=6, fig.height=5.5, fig.cap="$\\lambda$ and $\\theta$ values for Cobb-Douglas resample models.">>=
@@
 We can also estimate values for 
-the fraction of economic growth explained by the Solow residual ($f$)
+the fraction~($f$) of economic growth explained by the Solow residual
 by $f_{ij}$
@@
 The results are shown in Figure~\ref{fig:CD_solowPerc_time_series}. 
+Note that data spanning year~$i$--year~$j$ is plotted at year~$i$ in 
+Figures~\ref{fig:CD_lambda_time_series} and~\ref{fig:CD_solow_Perc_time_series}.
 
@@
 @
+
+Figures~\ref{fig:CD_GDP_Spaghetti_Graphs_US}--\ref{fig:CD_GDP_Spaghetti_Graphs_CN} 
+compare predictions 
+from the Cobb-Douglas models 
+(without and with energy) to historical data.
+Historical data are shown as a black line. 
+The fit to historical data is shown as a white line.
+The gray band encompasses \Sexpr{spaghettiGraphLevel*100}\% of the fits to resampled data.
 

### 2015-01-01 Articles/Article_EnerEcon_2014/EconGrowth3.Rnw
Changed title of one subsection. Now a question.
Deleted many lines of unused constants.

@@
 <<constants, include=FALSE, eval=TRUE>>=
-# Graph Heights
-maxHeight <- 8.5 # Inches
-ninePanelScatterGraphHeight <- maxHeight # Inches
-
-# Graph Widths
-maxWidth <- 6.5 # Inches
-fourPanelScatterGraphWidth <- maxWidth # Inches
-
-presentationGraph1RowHeight <- 2.8 # Inches
-presentationGraph2ColWidth <- 2 # Inches
-presentationGraph1ColWidth <- 2*presentationGraph2ColWidth
-h_param_graph <- 2.07 # Inches for a single panel
-h_param_axis <- 0.86 # Inches (also includes whatever margin is applied)
-# sfParameterGraphHeight <- h_param_graph + h_param_axis
-cdParameterGraphHeight <- 2*h_param_graph + h_param_axis
-cesParameterGraphHeight <- 3*h_param_graph + h_param_axis
-linexParameterGraphHeight <- h_param_graph + h_param_axis
-sfParameterGraphWidth <- maxWidth
-cdParameterGraphWidth <- maxWidth
-cesParameterGraphWidth <- maxWidth
-linexParameterGraphWidth <- maxWidth
-# Other graph parameters that apply to all graphs
-scaleTextSize <- 0.8  # Multiple of normal size
-scaleTickSize <- -0.5 # 50% of normal size and pointing INWARD!
-
-spaghettiGraphLevel <- 1.0 # Spaghetti graph bands will encompass 95% of the data.
+spaghettiGraphLevel <- 1.0 # Spaghetti graph bands will encompass a certain percentage of the data.
 @
@@
 
-<<CES_lambda_gamma_graph, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models.">>=
+<<CES_lambda_gamma_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models.">>=
 cesCoeffsData <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
@@
 
-<<CES_sigma1_delta1_graph, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models.">>=
+<<CES_sigma1_delta1_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models.">>=
 standardScatterPlot(data=cesCoeffsData, mapping=aes(delta_1, sigma_1), facet_formula=country~nestStrParen, alpha=0.05) +
@@
 %++++++++++++++++++++++++++++++
-\subsection{Implications of parameter uncertainty} 
+\subsection{What are the implications of parameter uncertainty?}
 \label{sec:implications}

### 2015-01-02 Workflow/Workflow.Rmd
Updated documenation for PreProcess in Workflow.Rmd

@@
 ### Create historical data frame
-* Run `Scripts/PreProcess.R -S <Source>` to create the historical data frame for `<Source>`.
-The file will be stored at `Packages/EconData/data/<Source>.rda`.
+* Run `Scripts/PreProcess.R -S <Sources>` to create the historical data frame for `<Sources>`.
+Note that` <Sources>` can be a comma-separated list of sources.
+The files will be stored at `Packages/EconData/data/<Source>.rda`.
 This command is fast; it can be run on a local machine.    

### 2015-01-03 Articles/Article_EnerEcon_2014/EconGrowth3.Rnw
Edits to discussion of useful work.

@@
 is generally accepted by most 
-resource and energy economists
-\citep{Smulders:2003wc, vanderZwaan:2002wn, Kemfert:1998vd}.
+resource and energy economists \citep{Smulders:2003wc, vanderZwaan:2002wn, Kemfert:1998vd}.
 Researchers interested in explaining long-term economic growth 
 and possible constraints on growth 
-have started to include energy as an explicit factor of production
-\citep{Froling:2009vo, Tahvonen:2001tz}.  
+have begun to include energy 
+as an explicit factor of production, too \citep{Froling:2009vo, Tahvonen:2001tz}.
+
 An alternative approach, attempting to be 
@@
 combine to provide efficiencies that augment energy.
-Technological change is manifest as increased efficiency:
-more useful work done per joule of exergy \citep{Ayres:2005kn}.
 There is no Solow-style term ($\mathrm{e}^{\lambda t}$) for technological change.
+Rather, technological change is manifest as increased efficiency:
+more useful work done per joule of exergy input to the economy \citep{Ayres:2005kn}.
+\citet{Kummel:1980wx} developed the LINEX function
+using energy quantified as primary thermal energy input to the economy.
+\citeauthor{Kummel:1980wx} represented 
+energy efficiency coefficients in the LINEX function by logistic functions,
+effectively converting from primary thermal energy to energy at the point of use
+within the LINEX function itself.
+
+In a series of papers culminating in a book~\citep{Ayres:2010ug},
+\citeauthor{Ayres:2010ug} used the LINEX function with energy quantified as ``useful work,''
+which is much closer to the point of use than 
+the primary thermal energy quantification favored by \citeauthor{Kummel:1980wx}.
+\citeauthor{Ayres:2010ug} do not find the need to use logistic functions representing energy efficiency,
+presumably because useful work ``already incorporate[s] the energy-related efficiency changes 
+in the economic system''~\citep[p.~35]{Kummel:2013aa}.
+Both \citeauthor{Kummel:1980wx} and \citeauthor{Ayres:2010ug}
+report satisfactory agreement between the LINEX function and historical economic output.
 
@@
 and selection of model parameters 
-to support certain theories (rather than empirically testing the theories
-and parameters \emph{before} they are employed).  
+to support certain theories, rather than empirically testing the theories
+and parameters \emph{before} they are employed.  
 For example, \citet{Lecca:2011kr} pointed out that 
@@
 As a result, \citeauthor{Shen:2013vp} propose an atypical CES nesting structure 
-for the Chinese economy. **** More detail here about nesting? --MKH ****  
+for the Chinese economy. **** Martin: More detail here about nesting? --MKH ****  
 \citet{Saunders:2008aa} evaluated several production and cost functions
@@
   \footnote{
-  See \citet{Sorrell:2007um} for details about rebound and backfire effects.
+  See \citet{Sorrell:2007um} for background on rebound and backfire.
   }
@@
 output elasticities 
-$\alpha$, $\beta$, and $\gamma$ 
-(if augmenting the production function by energy)
 can be calibrated from national accounts data as the 
-cost shares of capital, labor, and energy, respectively.
+cost shares of factors of production: capital, labor, 
+and energy (if augmenting the production function by energy).
 However, the cost share theorem applies only under conditions of perfect competition
@@
 Although no market ever exhibits perfect competition, 
-in our opinion, energy markets are \emph{least} likely to be ``perfect.''
+in our opinion energy markets are \emph{least} likely to be ``perfect.''
 Many governments have parastatal or full control 
-of electricity generation and/or fuel markets.  
+of electricity generation and fuel markets.  
 Other governments subsidize or incentivize energy markets.  
@@
 If energy markets are farther from ``perfect'' 
-than capital and/or labor markets, 
+than capital and labor markets, 
 then energy is the factor of production least likely to have its
-output elasticity~($\gamma$) be well-represented 
-by cost share as reported in national accounts.
+output elasticity be well-represented 
+by cost share as reported in national accounts~\citep{Ayres:2013aa, Kummel:2013aa}.
 Thus, when augmenting production functions by energy, 
 much care should be taken in estimating 
-the relative importance of the factors of production 
-($\alpha$, $\beta$, and $\gamma$). 
+the relative importance of the factors of production. 
 \citet{Kummel:2010vz} showed that the cost share theorem applies 
@@
 the degree of utilization of capital stock 
-result in shadow prices that move the values 
-of $\alpha$, $\beta$, and $\gamma$ away from 
-their cost shares in the economy.~\citep[Equations~12 and~13]{Kummel:2010vz}
+result in shadow prices that move 
+output elasticities away from 
+their cost shares in the economy \citep[Equations~12 and~13]{Kummel:2010vz}.
 Thus, for this study, 
-we reject the cost share theorem and
+we reject the cost share theorem, and
 we have no \emph{a-priori} expectation that output elasticities 
@@
 
-Thus, both the choice of production function structure 
+Thus, there are stong indications in the literature that
+both the choice of production function structure 
 and the values of the model parameters 
@@
 Therefore, we agree with those who express serious concerns 
-about the reliability of the results from economic growth models.~\citep{Lecca:2011kr} 
+about the reliability of the results from economic growth models \citep{Lecca:2011kr}.
 We understand, however, 
@@
 and is increasingly informed by integrated energy-economy models, 
-in a world where energy constraints are possible.~\citep{Beckman:2011gb, 
-Benes:2012tm, Nel:2010fv, Kummel:2010vz}
+in a world where energy constraints are possible \citep{Beckman:2011gb, 
+Benes:2012tm, Nel:2010fv, Kummel:2010vz}.
 Unfortunately, there has been little empirical work assessing the predictive ability 
@@
 And, very few studies of the importance of energy in economic growth include 
-rigorous statistical assessments of energy-related fitting parameters. 
-Thus, we support the call from \citet{Shen:2013vp} that both
+rigorous statistical assessment of energy-related fitting parameters.
+
+This paper contributes to the literature on the role of energy in economic growth
+by applying statistically rigorous 
+methods along two coordinates of analysis: 
+form of the energy augmented production function 
+and type of economy.
+We support the call from \citet{Shen:2013vp} that both
 the structure of the production function 
@@
 at different stages of their development, 
-a central point of long-wave economic growth modeling.~\citep{Froling:2009vo, Jones:2001wn, Galor:2000up}
-
-This paper contributes to the literature on the role of energy in economic growth
-by applying statistically rigorous 
-methods along two coordinates of analysis: 
-form of the energy augmented production function 
-and type of economy.
+a central point of long-wave economic growth modeling \citep{Froling:2009vo, Jones:2001wn, Galor:2000up}.
 
 The remainder of this paper is organized as follows. 
-% Section~\ref{sec:lit_review} provides a necessarily brief overview of relevant literature.
 Section~\ref{sec:Coordinates} discusses the coordinates of analysis for the present study. 
@@
 difficulty in respecting parameter constraints.
-If the LINEX function is to be used, we recommend that 
-\citeapos{Kummel:2011aa} fitting approach (logistic curves for $a_0$ and $c_t$) be employed
-and that the results be thoroughly tested and compared against other production functions.
+If the LINEX function is to be used, 
+we recommend that \citeapos{Kummel:2011aa} fitting approach 
+(energy quantified by primary thermal energy and logistic curves for $a_0$ and $c_t$) 
+or \citeapos{Ayres:2010ug} approach (energy quantified by useful work and constant values for $a_0$ and $c_t$) 
+be employed 
+and that the results be 
+thoroughly tested and compared 
+against other production functions.
 

### 2015-01-03 Articles/Article_EnerEcon_2014/EconGrowth3.Rnw
Added a note about data not determining coeffs precisely.

@@
 estimating any elasticity of substitution at all is problematic and fraught with peril. 
+Earlier, we noted that 
+even when residuals for the fit to historical data are small 
+and the model produces fitted values that track the historical data closely, 
+it may yet be difficult to estimate some or all of the model parameters precisely.
+That appears to be the case for 
+values of $\rho$ and $\rho_1$ and associated
+elasticities of substitution~($\sigma$ and $\sigma_1$)
+in the CES production function.
 Note that this result is unlikely to be caused by poor-quality data alone. 
-Presumably the best data in the world 
-(United States, United Kingdom, and Japan) exhibits large uncertainty.
-
-Some of the uncertainty is explained by the structure of the CES model itself. 
-If $\delta$ or $\delta_1$ achieves an extreme value (0 or 1), 
-the corresponding elasticity of substitution ($\sigma$ and $\sigma_1$) becomes meaningless. 
-(See Equations~\ref{eq:CES}--\ref{eq:CESekl}.) 
-Thus, large uncertainty in $\sigma$ and $\sigma_1$ is expected for any resampled model 
+Elasticities of substitution for the economies with presumably the best data in the world 
+(United States, United Kingdom, and Japan) exhibit large uncertainty.
+
+Some of the uncertainty in parameter estimates is explained by 
+the mathematical structure of the CES model itself. 
+Equations~\ref{eq:CES}--\ref{eq:CESekl} indicate that 
+if $\delta$ or $\delta_1$ achieves an extreme value (0 or 1), 
+the corresponding elasticity of substitution ($\sigma$ or $\sigma_1$) becomes meaningless. 
+If $\delta$ approaches unity, values of $\delta_1$ and $\sigma_1$ become meaningless.
+Thus, large uncertainty in $\sigma$, $\sigma_1$, and $\delta_1$ can be expected for any CES model 
 in which parameter estimates are positioned on the left or right boundaries
@@
 would mean that the CES model is estimated on two 10-year periods. 
-Considering that there are six fitted parameters in the CES model 
-($\gamma$, $\lambda$, $\delta$, $\delta_1$, $\rho$, and $\rho_1$), 
+Considering that there are six fitted parameters in the energy-augmented CES model 
+($\gamma$, $\lambda$, $\delta$, $\delta_1$, $\rho$, and $\rho_1$
+in Equations~\ref{eq:CESkle}--\ref{eq:CESekl}), 
 ten years of historical data leaves precious few 
@@
 Based on the results and discussions above 
-regarding the relative importance of and 
-the elasticity of substitution among factors of production, 
+regarding (a)~the relative importance of factors of production and 
+(b)~the elasticity of substitution among factors of production, 
 we conclude that use of the CES model for energy analysis 
+(Equations \ref{eq:CESkle}--\ref{eq:CESekl})
 should be undertaken with utmost caution. 
-Indeed, rigorous statistical testing on the relative importance 
-of production factors and elasticities of substitution is highly recommended. 
 Our results support \citeapos{Lecca:2011kr} conclusion 
@@
 Or, would doing so improve transparency? --MKH ****
+Indeed, rigorous statistical testing on the relative importance 
+of production factors and elasticities of substitution is strongly recommended.
 
@@
 difficulty in respecting parameter constraints.
-If the LINEX function is to be used, 
-we recommend that \citeapos{Kummel:2011aa} fitting approach 
+If the LINEX function is to be used for energy analysis, 
+we recommend that either \citeapos{Kummel:2011aa} fitting approach 
 (energy quantified by primary thermal energy and logistic curves for $a_0$ and $c_t$) 
-or \citeapos{Ayres:2010ug} approach (energy quantified by useful work and constant values for $a_0$ and $c_t$) 
+or \citeapos{Ayres:2010ug} fitting approach 
+(energy quantified by useful work and constant values for $a_0$ and $c_t$) 
 be employed 
@@
 against other production functions.
+Doing so is left as future work.
 

### 2015-01-03 Articles/Article_EcolEcon_2014/Paper2.Rnw
Minor edits.

@@
 %
-Simplifying by cancelling $t_j - t_i$ terms and simplifying gives
+Cancelling $t_j - t_i$ terms and simplifying gives
 %
@@
 The results are shown in Figure~\ref{fig:CD_solowPerc_time_series}. 
-Note that data spanning year~$i$--year~$j$ is plotted at year~$i$ in 
-Figures~\ref{fig:CD_lambda_time_series} and~\ref{fig:CD_solow_Perc_time_series}.
+Note that data spanning years~$i \rightarrow j$ is plotted at year~$i$ in 
+Figures~\ref{fig:CD_lambda_time_series} and~\ref{fig:CD_solowPerc_time_series}.
 

### 2015-01-04 Articles/Article_EcolEcon_2014/Paper2.Rnw
Minor re-arrangement.
Added all CES graphs.

@@
 The results are shown in Figure~\ref{fig:CD_lambda_time_series}.
-
-We can also estimate values for 
-the fraction~($f$) of economic growth explained by the Solow residual
-by $f_{ij}$
-with $i$ and $j$ in Equation~\ref{eq:f_finite_diff_2} separated by \Sexpr{lag} years.
-The results are shown in Figure~\ref{fig:CD_solowPerc_time_series}. 
-Note that data spanning years~$i \rightarrow j$ is plotted at year~$i$ in 
-Figures~\ref{fig:CD_lambda_time_series} and~\ref{fig:CD_solowPerc_time_series}.
+Note that data spanning years~$i \rightarrow j$ is plotted at year~$i$.
 
@@
 
+We can also estimate values for 
+the fraction~($f$) of economic growth explained by the Solow residual
+by $f_{ij}$
+with $i$ and $j$ in Equation~\ref{eq:f_finite_diff_2} separated by \Sexpr{lag} years.
+The results are shown in Figure~\ref{fig:CD_solowPerc_time_series}. 
+Note that data spanning years~$i \rightarrow j$ is plotted at year~$i$.
+
 <<CD_solowPerc_time_series, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap='Fraction of GDP growth explained by Solow residual.'>>=
@@
 <<CD_GDP_Spaghetti_Graphs_US, fig.pos="H", fig.align='center', fig.width=4, fig.height=3.5, fig.cap="US Cobb-Douglas fitted models.">>=
-cdFittedDataUS <- subset(AllFitted, subset = model=="cd" & Country=="US")
+# Use this result several times later. Saves lots of time doing it this way.
+cdFittedData <- filter(AllFitted, model=="cd")
+
+cdFittedDataUS <- filter(cdFittedData, Country=="US")
 spaghettiPlot(data=cdFittedDataUS, facet_formula=Source~energy, level=spaghettiGraphLevel) +
@@
 <<CD_GDP_Spaghetti_Graphs_UK, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="UK Cobb-Douglas fitted models.">>=
-cdFittedDataUK <- subset(AllFitted, subset = model=="cd" & Country=="UK")
+cdFittedDataUK <- filter(cdFittedData, Country=="UK")
 spaghettiPlot(data=cdFittedDataUK, facet_formula=Source~energy, level=spaghettiGraphLevel) +
@@
 <<CD_GDP_Spaghetti_Graphs_JP, fig.pos="H", fig.align='center', fig.width=4, fig.height=2, fig.cap="JP Cobb-Douglas fitted models.">>=
-cdFittedDataJP <- subset(AllFitted, subset = model=="cd" & Country=="JP")
+cdFittedDataJP <- filter(cdFittedData, Country=="JP")
 spaghettiPlot(data=cdFittedDataJP, facet_formula=Source~energy, level=spaghettiGraphLevel) +
@@
 <<CD_GDP_Spaghetti_Graphs_AT, fig.pos="H", fig.align='center', fig.width=5, fig.height=3.5, fig.cap="AT Cobb-Douglas fitted models.">>=
-cdFittedDataAT <- subset(AllFitted, subset = model=="cd" & Country=="AT")
+cdFittedDataAT <- filter(cdFittedData, Country=="AT")
 spaghettiPlot(data=cdFittedDataAT, facet_formula=Source~energy, level=spaghettiGraphLevel) +
@@
 <<CD_GDP_Spaghetti_Graphs_PT, fig.pos="H", fig.align='center', fig.width=5, fig.height=2, fig.cap="PT Cobb-Douglas fitted models.">>=
-cdFittedDataPT <- subset(AllFitted, subset = model=="cd" & Country=="PT")
+cdFittedDataPT <- filter(cdFittedData, Country=="PT")
 spaghettiPlot(data=cdFittedDataPT, facet_formula=Source~energy, level=spaghettiGraphLevel) +
@@
 <<CD_GDP_Spaghetti_Graphs_CN, fig.pos="H", fig.align='center', fig.width=4, fig.height=2, fig.cap="CN Cobb-Douglas fitted models.">>=
-cdFittedDataCN <- subset(AllFitted, subset = model=="cd" & Country=="CN")
+cdFittedDataCN <- filter(cdFittedData, Country=="CN")
 spaghettiPlot(data=cdFittedDataCN, facet_formula=Source~energy, level=spaghettiGraphLevel) +
@@
 <<CES_sigma_delta_graph_Xp, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=6, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models using primary exergy ($x_p$).">>=
-standardScatterPlot(data=subset(cesCoeffsDataXp, nestStrParen != "(iK + iL) + ()"),
+standardScatterPlot(data=filter(cesCoeffsDataXp, nestStrParen != "(iK + iL) + ()"),
                     mapping=aes(x=delta, y=sigma, color=Source), 
@@
 <<CES_GDP_Spaghetti_Graph_US_xp, fig.pos="H", fig.align='center', fig.width=5, fig.height=3.5, fig.cap="US CES with $x_p$ fitted models.">>=
-cesFittedDataUS_xp <- subset(AllFitted, subset = model=="ces" & Country=="US" & (energy=="iXp" | energy=="none"))
+# Use this result later. Do it once to speed things up.
+cesFittedData_xp <- filter(AllFitted, model=="ces", energy %in% c("iXp", "none"))
+
+cesFittedDataUS_xp <- filter(cesFittedData_xp, Country=="US")
 spaghettiPlot(data=cesFittedDataUS_xp, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
@@
 <<CES_GDP_Spaghetti_Graph_UK_xp, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="UK CES with $x_p$ fitted models.">>=
-cesFittedDataUK_xp <- subset(AllFitted, subset = model=="ces" & Country=="UK" & (energy=="iXp" | energy=="none"))
+cesFittedDataUK_xp <- filter(cesFittedData_xp, Country=="UK")
 spaghettiPlot(data=cesFittedDataUK_xp, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
@@
 <<CES_GDP_Spaghetti_Graph_JP_xp, fig.pos="H", fig.align='center', fig.width=5, fig.height=2.5, fig.cap="JP CES with $x_p$ fitted models.">>=
-cdFittedDataJP_xp <- subset(AllFitted, subset = model=="ces" & Country=="JP" & (energy=="iXp" | energy=="none"))
+cdFittedDataJP_xp <- filter(cesFittedData_xp, Country=="JP")
 spaghettiPlot(data=cdFittedDataJP_xp, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
@@
 <<CES_GDP_Spaghetti_Graph_AT_xp, fig.pos="H", fig.align='center', fig.width=5, fig.height=3.5, fig.cap="AT CES with $x_p$ fitted models.">>=
-cdFittedDataAT_xp <- subset(AllFitted, subset = model=="ces" & Country=="AT" & (energy=="iXp" | energy=="none"))
+cdFittedDataAT_xp <- filter(cesFittedData_xp, Country=="AT")
 spaghettiPlot(data=cdFittedDataAT_xp, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
@@
 <<CES_GDP_Spaghetti_Graph_PT_xp, fig.pos="H", fig.align='center', fig.width=5, fig.height=2.5, fig.cap="PT CES with $x_p$ fitted models.">>=
-cdFittedDataPT_xp <- subset(AllFitted, subset = model=="ces" & Country=="PT" & (energy=="iXp" | energy=="none"))
+cdFittedDataPT_xp <- filter(cesFittedData_xp, Country=="PT")
 spaghettiPlot(data=cdFittedDataPT_xp, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
@@
 <<CES_GDP_Spaghetti_Graph_CN_xp, fig.pos="H", fig.align='center', fig.width=5, fig.height=2.5, fig.cap="CN CES with $x_p$ fitted models.">>=
-cdFittedDataCN_xp <- subset(AllFitted, subset = model=="ces" & Country=="CN" & (energy=="iXp" | energy=="none"))
+cdFittedDataCN_xp <- filter(cesFittedData_xp, Country=="CN")
 spaghettiPlot(data=cdFittedDataCN_xp, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
@@
 
-<<CES_Residual_Plot, fig.pos="H", fig.align='center', fig.width=6, fig.height=6, fig.cap="CES with $x_p$ Residual Plots.">>=
+<<CES_Residual_Plot_xp, fig.pos="H", fig.align='center', fig.width=6, fig.height=6, fig.cap="CES with $x_p$ Residual Plots.">>=
 # Use residuals_df to make a graph.
-ces_xp_residuals_df <- subset(residuals_df, subset = modelType=="ces" & (energyType=="iXp" | energyType=="none"))
+ces_xp_residuals_df <- filter(residuals_df, modelType=="ces", energyType %in% c("iXp", "none"))
 ggplot(data=ces_xp_residuals_df, aes(x=year, y=resid, color=Source)) + 
@@
 
+The following graphs show results for the CES model using final exergy ($x_f$).
+
+<<CES_lambda_gamma_graph_Xf, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6.0, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with final exergy ($x_f$).">>=
+# We need to keep only those combinations of country and Source that have final exergy.
+temp <- filter(AllCoeffs, model=="ces", nestStrParen %in% c("(iK + iL) + (iXf)", 
+                                                            "(iL + iXf) + (iK)", 
+                                                            "(iXf + iK) + (iL)"))
+countrySource <- paste0(temp$country, "+", temp$Source)
+rm(temp) # No need to keep this data frame around
+# Keep only unique combinations of country and Source in the temp data frame.
+keep <- unique(countrySource)
+cesCoeffsDataXf <- filter(AllCoeffs, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
+                                                                      "(iK + iL) + (iXf)", 
+                                                                      "(iL + iXf) + (iK)", 
+                                                                      "(iXf + iK) + (iL)"))
+cesCoeffsDataXf$countrySource <- paste0(cesCoeffsDataXf$country, "+", cesCoeffsDataXf$Source)
+cesCoeffsDataXf <- filter(cesCoeffsDataXf, countrySource %in% keep)
+
+standardScatterPlot(data=cesCoeffsDataXf, mapping=aes(x=gamma_coef, y=lambda, color=Source), 
+                    facet_formula=country~nestStrParen, alpha=0.05) +
+    scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
+    labs(x=expression(gamma), y=expression(lambda)) + 
+    guides(colour=guide_legend(override.aes = aes(alpha=1)))
+@
+
+<<CES_sigma1_delta1_graph_Xf, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6.5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with final exergy ($x_f$).">>=
+standardScatterPlot(data=cesCoeffsDataXf, mapping=aes(x=delta_1, y=sigma_1, color=Source), 
+                    facet_formula=country~nestStrParen, alpha=0.05) +
+    coord_trans(y="sigma") +
+    scale_x_continuous(breaks=c(0, 0.5, 1.0)) +
+    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
+    labs(x=expression(delta[1]), y=expression(sigma[1])) + 
+    guides(colour=guide_legend(override.aes = aes(alpha=1)))
+@
+
+<<CES_sigma_delta_graph_Xf, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=6, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models using final exergy ($x_f$).">>=
+standardScatterPlot(data=subset(cesCoeffsDataXf, nestStrParen != "(iK + iL) + ()"),
+                    mapping=aes(x=delta, y=sigma, color=Source), 
+                    facet_formula=country~nestStrParen, alpha=0.05) +
+    coord_trans(y="sigma") +
+    scale_x_continuous(breaks=c(0, 0.5, 1.0)) +
+    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
+    labs(x=expression(delta), y=expression(sigma)) +
+    guides(colour=guide_legend(override.aes = aes(alpha=1)))
+@
+
+Figure~\ref{fig:CES_ternary_graphXf} shows 
+$\alpha$, $\beta$, and $\gamma$ parameters for the CES model for all nests and countries.
+Figure~\ref{fig:CES_ternary_graphXf} is comparable to
+earlier ternary graphs, 
+Figures~\ref{fig:CD_Ternary_Scatter_Graph} and~\ref{fig:CES_ternary_graphXp}.
+
+<<CES_ternary_graphXf, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models with final exergy ($x_f$).", eval=TRUE>>=
+standardTriPlot(data=cesCoeffsDataXf, 
+                mapping=aes(color=Source), 
+                facet_formula=country~nestStrParen) +
+  guides(colour=guide_legend(override.aes = aes(alpha=1)))
+@
+
+Figures~\ref{fig:CES_GDP_Spaghetti_Graph_UK_xf}--\ref{fig:CES_GDP_Spaghetti_Graph_PT_xf} 
+compare CES model predictions with final exergy ($x_f$)
+to historical data for all nestings, countries, and data sources. 
+As with the previous results, 
+historical data are shown as a black line, 
+the fit to historical data is shown as a white line, and 
+the gray band encompasses \Sexpr{spaghettiGraphLevel*100}\% of the fits to resampled data.
+
+<<CES_GDP_Spaghetti_Graph_UK_xf, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="UK CES with $x_f$ fitted models.">>=
+cesFittedData_xf <- filter(AllFitted, model=="ces", energy %in% c("iXf", "none"))
+cesFittedData_xf$CountrySource <- paste0(cesFittedData_xf$Country, "+", cesFittedData_xf$Source)
+cesFittedData_xf <- filter(cesFittedData_xf, CountrySource %in% keep)
+
+cesFittedDataUK_xf <- filter(cesFittedData_xf, Country=="UK")
+spaghettiPlot(data=cesFittedDataUK_xf, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1960=1)") +
+  scale_x_continuous(breaks=c(1960, 1980, 2000))
+@
+
+<<CES_GDP_Spaghetti_Graph_AT_xf, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="AT CES with $x_f$ fitted models.">>=
+cesFittedDataAT_xf <- filter(cesFittedData_xf, Country=="AT")
+spaghettiPlot(data=cesFittedDataAT_xf, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1960=1)") +
+  scale_x_continuous(breaks=c(1960, 1980, 2000))
+@
+
+<<CES_GDP_Spaghetti_Graph_PT_xf, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="PT CES with $x_f$ fitted models.">>=
+cesFittedDataPT_xf <- filter(cesFittedData_xf, Country=="PT")
+spaghettiPlot(data=cesFittedDataPT_xf, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1960=1)") +
+  scale_x_continuous(breaks=c(1960, 1980, 2000))
+@
+
+<<CES_Residual_Plot_xf, fig.pos="H", fig.align='center', fig.width=6, fig.height=6, fig.cap="CES with $x_f$ Residual Plots.">>=
+# Use residuals_df to make a graph.
+ces_xf_residuals_df <- filter(residuals_df, modelType=="ces", energyType %in% c("iXf", "none"))
+ces_xf_residuals_df$CountrySource <- paste0(ces_xf_residuals_df$Country, "+", ces_xf_residuals_df$Source)
+ces_xf_residuals_df <- filter(ces_xf_residuals_df, CountrySource %in% keep)
+
+ggplot(data=ces_xf_residuals_df, aes(x=year, y=resid, color=Source)) + 
+  geom_point(size = 1.0) +
+  facet_grid(Country ~ nestStrParen) +
+  labs(x = "", y = "Residuals") +
+  scale_x_continuous(breaks=c(1960, 1980, 2000)) + 
+  xy_theme()
+@
+
 %------------------------------
@@
 
-% 
-% <<CES_Spaghetti_Graph_X, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models with exergy ($x$).", eval=FALSE>>=
-% cesFittedDataX <- filter(fitted_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
-%                                                                       "(iK + iL) + (iX)", 
-%                                                                       "(iL + iX) + (iK)", 
-%                                                                       "(iX + iK) + (iL)"))
-% spaghettiPlot(data=cesFittedDataX, facet_formula=Country~nestStrParen, level=spaghettiGraphLevel) +
-%     labs(y="Indexed GDP (1900=1 or 1950=1)")
-% @
-% 
-% <<CES_lambda_gamma_graph_U, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with useful work ($u$).", eval=FALSE>>=
-% cesCoeffsDataU <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
-%                                                                       "(iK + iL) + (iU)", 
-%                                                                       "(iL + iU) + (iK)", 
-%                                                                       "(iU + iK) + (iL)"))
-% standardScatterPlot(data=cesCoeffsDataU, mapping=aes(gamma_coef, lambda), facet_formula=country~nestStrParen, alpha=0.05) +
-%     scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
-%     labs(x=expression(gamma), y=expression(lambda))
-% @
-% 
-% <<CES_sigma1_delta1_graph_U, fig.pos="H", fig.align='center', fig.width=5, fig.height=5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with useful work ($u$).", eval=FALSE>>=
-% standardScatterPlot(data=cesCoeffsDataU, mapping=aes(delta_1, sigma_1), facet_formula=country~nestStrParen, alpha=0.05) +
-%     coord_trans(y="sigma") +
-%     scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-%     scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-%     labs(x=expression(delta[1]), y=expression(sigma[1]))
-% @
-% 
-% <<CES_sigma_delta_graph_U, fig.pos="H", fig.align='center', fig.width=4.4, fig.height=5, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models with useful work ($u$).", eval=FALSE>>=
-% standardScatterPlot(data=subset(cesCoeffsDataU, nestStrParen != "(iK + iL) + ()"),
-%                     mapping=aes(delta, sigma), facet_formula=country~nestStrParen, alpha=0.05) +
-%     coord_trans(y="sigma") +
-%     scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-%     scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-%     labs(x=expression(delta), y=expression(sigma))
-% @
-% 
-% <<CES_Spaghetti_Graph_U, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models with useful work ($u$).", eval=FALSE>>=
-% cesFittedDataU <- filter(fitted_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
-%                                                                       "(iK + iL) + (iU)", 
-%                                                                       "(iL + iU) + (iK)", 
-%                                                                       "(iU + iK) + (iL)"))
-% spaghettiPlot(data=cesFittedDataU, facet_formula=Country~nestStrParen, level=spaghettiGraphLevel) +
-%     labs(y="Indexed GDP (1900=1 or 1950=1)")
-% @
+The following graphs show results for the CES model using useful work ($u$).
+
+<<CES_lambda_gamma_graph_U, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6.0, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with useful work ($u$).">>=
+cesCoeffsDataU <- filter(AllCoeffs, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
+                                                                      "(iK + iL) + (iU)", 
+                                                                      "(iL + iU) + (iK)", 
+                                                                      "(iU + iK) + (iL)"))
+standardScatterPlot(data=cesCoeffsDataU, mapping=aes(x=gamma_coef, y=lambda, color=Source), 
+                    facet_formula=country~nestStrParen, alpha=0.05) +
+    scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
+    labs(x=expression(gamma), y=expression(lambda)) + 
+    guides(colour=guide_legend(override.aes = aes(alpha=1)))
+@
+
+<<CES_sigma1_delta1_graph_U, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6.5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with useful work ($u$).">>=
+standardScatterPlot(data=cesCoeffsDataU, mapping=aes(x=delta_1, y=sigma_1, color=Source), 
+                    facet_formula=country~nestStrParen, alpha=0.05) +
+    coord_trans(y="sigma") +
+    scale_x_continuous(breaks=c(0, 0.5, 1.0)) +
+    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
+    labs(x=expression(delta[1]), y=expression(sigma[1])) + 
+    guides(colour=guide_legend(override.aes = aes(alpha=1)))
+@
+
+<<CES_sigma_delta_graph_U, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=6, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models using useful work ($u$).">>=
+standardScatterPlot(data=subset(cesCoeffsDataU, nestStrParen != "(iK + iL) + ()"),
+                    mapping=aes(x=delta, y=sigma, color=Source), 
+                    facet_formula=country~nestStrParen, alpha=0.05) +
+    coord_trans(y="sigma") +
+    scale_x_continuous(breaks=c(0, 0.5, 1.0)) +
+    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
+    labs(x=expression(delta), y=expression(sigma)) +
+    guides(colour=guide_legend(override.aes = aes(alpha=1)))
+@
+
+Figure~\ref{fig:CES_ternary_graphU} shows 
+$\alpha$, $\beta$, and $\gamma$ parameters for the CES model with $u$ for all nests and countries.
+Figure~\ref{fig:CES_ternary_graphU} is comparable to
+earlier ternary graphs, 
+Figures~\ref{fig:CD_Ternary_Scatter_Graph}, \ref{fig:CES_ternary_graphXp}, and~\ref{fig:CES_ternary_graphXf}.
+
+<<CES_ternary_graphU, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models with final exergy ($u$).", eval=TRUE>>=
+standardTriPlot(data=cesCoeffsDataU, 
+                mapping=aes(color=Source), 
+                facet_formula=country~nestStrParen) +
+  guides(colour=guide_legend(override.aes = aes(alpha=1)))
+@
+
+Figures~\ref{fig:CES_GDP_Spaghetti_Graph_US_u}--\ref{fig:CES_GDP_Spaghetti_Graph_CN_u} 
+compare CES with $u$ model predictions 
+to historical data for all nestings, countries, and data sources. 
+As with previous graphs, 
+historical data are shown as a black line, 
+the fit to historical data is shown as a white line, and 
+the gray band encompasses \Sexpr{spaghettiGraphLevel*100}\% of the fits to resampled data.
+
+<<CES_GDP_Spaghetti_Graph_US_u, fig.pos="H", fig.align='center', fig.width=5, fig.height=3.5, fig.cap="US CES with $u$ fitted models.">>=
+# Use this result several times later.
+cesFittedData_u <- filter(AllFitted, model=="ces", energy %in% c("iU", "none"))
+
+cesFittedDataUS_u <- filter(cesFittedData_u, Country=="US")
+spaghettiPlot(data=cesFittedDataUS_u, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1960=1)") +
+  scale_x_continuous(breaks=c(1960, 1980, 2000))
+@
+
+<<CES_GDP_Spaghetti_Graph_UK_u, fig.pos="H", fig.align='center', fig.width=5, fig.height=3.5, fig.cap="UK CES with $u$ fitted models.">>=
+# Use this result several times later.
+cesFittedDataUK_u <- filter(cesFittedData_u, Country=="UK")
+spaghettiPlot(data=cesFittedDataUK_u, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1960=1)") +
+  scale_x_continuous(breaks=c(1960, 1980, 2000))
+@
+
+<<CES_GDP_Spaghetti_Graph_JP_u, fig.pos="H", fig.align='center', fig.width=5, fig.height=3.5, fig.cap="JP CES with $u$ fitted models.">>=
+# Use this result several times later.
+cesFittedDataJP_u <- filter(cesFittedData_u, Country=="JP")
+spaghettiPlot(data=cesFittedDataJP_u, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1960=1)") +
+  scale_x_continuous(breaks=c(1960, 1980, 2000))
+@
+
+<<CES_GDP_Spaghetti_Graph_AT_u, fig.pos="H", fig.align='center', fig.width=5, fig.height=3.5, fig.cap="AT CES with $u$ fitted models.">>=
+# Use this result several times later.
+cesFittedDataAT_u <- filter(cesFittedData_u, Country=="AT")
+spaghettiPlot(data=cesFittedDataAT_u, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1960=1)") +
+  scale_x_continuous(breaks=c(1960, 1980, 2000))
+@
+
+<<CES_GDP_Spaghetti_Graph_PT_u, fig.pos="H", fig.align='center', fig.width=5, fig.height=3.5, fig.cap="PT CES with $u$ fitted models.">>=
+# Use this result several times later.
+cesFittedDataPT_u <- filter(cesFittedData_u, Country=="PT")
+spaghettiPlot(data=cesFittedDataPT_u, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1960=1)") +
+  scale_x_continuous(breaks=c(1960, 1980, 2000))
+@
+
+<<CES_GDP_Spaghetti_Graph_CN_u, fig.pos="H", fig.align='center', fig.width=5, fig.height=3.5, fig.cap="CN CES with $u$ fitted models.">>=
+# Use this result several times later.
+cesFittedDataCN_u <- filter(cesFittedData_u, Country=="CN")
+spaghettiPlot(data=cesFittedDataCN_u, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
+    labs(y="Indexed GDP (1960=1)") +
+  scale_x_continuous(breaks=c(1960, 1980, 2000))
+@
+
+<<CES_Residual_Plot_u, fig.pos="H", fig.align='center', fig.width=6, fig.height=6, fig.cap="CES with $i$ Residual Plots.">>=
+# Use residuals_df to make a graph.
+ces_u_residuals_df <- subset(residuals_df, subset = modelType=="ces" & (energyType=="iU" | energyType=="none"))
+ggplot(data=ces_u_residuals_df, aes(x=year, y=resid, color=Source)) + 
+  geom_point(size = 1.0) +
+  facet_grid(Country ~ nestStrParen) +
+  labs(x = "", y = "Residuals") +
+  scale_x_continuous(breaks=c(1960, 1980, 2000)) + 
+  xy_theme()
+@
 

### 2015-01-04 Articles/Article_EcolEcon_2014/Paper2.Rnw
Converting everything to use filter instead of subset. Filter is FASTER!

@@
 <<CD_lambda_theta_graph, fig.pos="H", fig.align='center', fig.width=6, fig.height=5.5, fig.cap="$\\lambda$ and $\\theta$ values for Cobb-Douglas resample models.">>=
-cdCoeffsData <- subset(AllCoeffs, subset = model=="cd")
+cdCoeffsData <- filter(AllCoeffs, model=="cd")
 standardScatterPlot(data=cdCoeffsData, mapping=aes(x=scale, y=lambda, color=Source), 
@@
 
-origCDKLCoeffs <- subset(AllCoeffs, method=="orig" & model=="cd")
+origCDKLCoeffs <- filter(AllCoeffs, method=="orig", model=="cd")
 origCDKLCoeffs <- origCDKLCoeffs %>% select(method, country, Source, nestStr, energy, lambda, alpha, beta, gamma)
@@
 labg <- apply(fd[ , c('Country', 'Source', 'energyType')], 1, function(x){
-    row <- as.data.frame(subset(origCDKLCoeffs, 
-                                country==x["Country"] & Source==x["Source"] & energy==x["energyType"]))
+    row <- as.data.frame(filter(origCDKLCoeffs, 
+                                country==x["Country"], Source==x["Source"], energy==x["energyType"]))
     abg <- subset(row, select=c(lambda, alpha, beta, gamma))
@@
 # Use residuals_df to make a graph.
-cd_residuals_df <- subset(residuals_df, subset = modelType=="cd")
+cd_residuals_df <- filter(residuals_df, modelType=="cd")
 ggplot(data=cd_residuals_df, aes(x=year, y=resid, color=Source)) + 
@@
 <<CES_sigma_delta_graph_Xf, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=6, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models using final exergy ($x_f$).">>=
-standardScatterPlot(data=subset(cesCoeffsDataXf, nestStrParen != "(iK + iL) + ()"),
+standardScatterPlot(data=filter(cesCoeffsDataXf, nestStrParen != "(iK + iL) + ()"),
                     mapping=aes(x=delta, y=sigma, color=Source), 
@@
 <<CES_sigma_delta_graph_U, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=6, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models using useful work ($u$).">>=
-standardScatterPlot(data=subset(cesCoeffsDataU, nestStrParen != "(iK + iL) + ()"),
+standardScatterPlot(data=filter(cesCoeffsDataU, nestStrParen != "(iK + iL) + ()"),
                     mapping=aes(x=delta, y=sigma, color=Source), 
@@
 # Use residuals_df to make a graph.
-ces_u_residuals_df <- subset(residuals_df, subset = modelType=="ces" & (energyType=="iU" | energyType=="none"))
+ces_u_residuals_df <- filter(residuals_df, modelType=="ces", energyType %in% c("iU", "none"))
 ggplot(data=ces_u_residuals_df, aes(x=year, y=resid, color=Source)) + 
@@
 <<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=6, fig.height=6, fig.cap="LINEX model resampling results.">>=
-linexCoeffsData <- subset(AllCoeffs, subset = model=="linex")
+linexCoeffsData <- filter(AllCoeffs, model=="linex")
 standardScatterPlot(data=linexCoeffsData,
@@
 <<LINEXq_Resample_Graph_PT, fig.pos="H", fig.align='center', fig.width=6, fig.height=2.5, fig.cap="LINEX model resampling results for PT.">>=
-linexCoeffsData <- subset(AllCoeffs, subset = model=="linex" & country=="PT")
+linexCoeffsData <- filter(AllCoeffs, model=="linex", country=="PT")
 standardScatterPlot(data=linexCoeffsData,
@@
                     facet_formula=country~energy, alpha=0.05) +
-#     scale_x_continuous(limits=c(0.0, 1.0), breaks=c(0.0, 0.5, 1.0)) +
-#     scale_y_continuous(limits=c(-10.0, 10.0), breaks=c(10.0, -5.0, 0.0, 5.0, 10.0)) +
+    scale_y_continuous(limits=c(-10.0, 10.0), breaks=c(10.0, -5.0, 0.0, 5.0, 10.0)) +
     labs(x=expression(a[0]), y=expression(c[t])) +
@@
 <<LINEX_GDP_Spaghetti_Graphs_US, fig.pos="H", fig.align='center', fig.width=3, fig.height=2.5, fig.cap="US LINEX fitted models.">>=
-linexFittedDataUS <- subset(AllFitted, subset = model=="linex" & Country=="US")
+linexFittedData <- filter(AllFitted, model=="linex")
+
+linexFittedDataUS <- filter(linexFittedData, Country=="US")
 spaghettiPlot(data=linexFittedDataUS, facet_formula=Source~energy, level=spaghettiGraphLevel) +
@@
 <<LINEX_GDP_Spaghetti_Graphs_UK, fig.pos="H", fig.align='center', fig.width=3, fig.height=4.5, fig.cap="UK LINEX fitted models.">>=
-linexFittedDataUK <- subset(AllFitted, subset = model=="linex" & Country=="UK")
+linexFittedDataUK <- filter(linexFittedData, Country=="UK")
 spaghettiPlot(data=linexFittedDataUK, facet_formula=Source~energy, level=spaghettiGraphLevel) +
@@
 <<LINEX_GDP_Spaghetti_Graphs_JP, fig.pos="H", fig.align='center', fig.width=3, fig.height=2.5, fig.cap="JP LINEX fitted models.">>=
-linexFittedDataJP <- subset(AllFitted, subset = model=="linex" & Country=="JP")
+linexFittedDataJP <- filter(linexFittedData, Country=="JP")
 spaghettiPlot(data=linexFittedDataJP, facet_formula=Source~energy, level=spaghettiGraphLevel) +
@@
 <<LINEX_GDP_Spaghetti_Graphs_AT, fig.pos="H", fig.align='center', fig.width=4, fig.height=3.5, fig.cap="AT LINEX fitted models.">>=
-linexFittedDataAT <- subset(AllFitted, subset = model=="linex" & Country=="AT")
+linexFittedDataAT <- filter(linexFittedData, Country=="AT")
 spaghettiPlot(data=linexFittedDataAT, facet_formula=Source~energy, level=spaghettiGraphLevel) +
@@
 <<LINEX_GDP_Spaghetti_Graphs_PT, fig.pos="H", fig.align='center', fig.width=4, fig.height=2.5, fig.cap="PT LINEX fitted models.">>=
-linexFittedDataPT <- subset(AllFitted, subset = model=="linex" & Country=="PT")
+linexFittedDataPT <- filter(linexFittedData, Country=="PT")
 spaghettiPlot(data=linexFittedDataPT, facet_formula=Source~energy, level=spaghettiGraphLevel) +
@@
 <<LINEX_GDP_Spaghetti_Graphs_CN, fig.pos="H", fig.align='center', fig.width=4, fig.height=2.5, fig.cap="CN LINEX fitted models.">>=
-linexFittedDataCN <- subset(AllFitted, subset = model=="linex" & Country=="CN")
+linexFittedDataCN <- filter(linexFittedData, Country=="CN")
 spaghettiPlot(data=linexFittedDataCN, facet_formula=Source~energy, level=spaghettiGraphLevel) +
@@
 # Use residuals_df to make a graph.
-linex_residuals_df <- subset(residuals_df, subset = modelType=="linex")
+linex_residuals_df <- filter(residuals_df, modelType=="linex")
 ggplot(data=linex_residuals_df, aes(x=year, y=resid, color=Source)) + 

### 2015-01-05 Articles/Article_EcolEcon_2014/Paper2.Rnw
Added text about uncertainty of CES parameters.

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Certain combinations of economy, parameter values, CES nesting structure, and data source
+come with very large resampling spreads, 
+indicating large fitted parameter uncertainties. 
+Often, there is virtually no useful information 
+in $\delta$, $\delta_1$, $\alpha$, $\beta$, and $\gamma$.
+
+Thus, we find that nesting has significant influence on model results.
+
+That so many estimates of elasticity of substitution exhibit large uncertainty, 
+often spanning the range from perfect complements ($\sigma, \, \sigma_1 = 0$) 
+to perfect substitutes ($\sigma, \, \sigma_1 = \infty$), 
+is a troubling characteristic of the estimated CES coefficients 
+that is rarely investigated in the literature.
+Indeed, for some economies, 
+estimating any elasticity of substitution at all is problematic and fraught with peril. 
+Earlier, we noted that 
+even when residuals for the fit to historical data are small 
+and the model produces fitted values that track the historical data closely, 
+it may yet be difficult to estimate some or all of the model parameters precisely.
+That appears to be the case for 
+values of $\rho$ and $\rho_1$ and associated
+elasticities of substitution~($\sigma$ and $\sigma_1$)
+in the CES production function.
+Note that this result is unlikely to be caused by poor-quality data alone. 
+Elasticities of substitution for the economies with presumably the best data in the world 
+(United States, United Kingdom, Japan, and Austria) exhibit large uncertainty.
+
+Some of the uncertainty in parameter estimates is explained by 
+the mathematical structure of the CES model itself. 
+Equations~\ref{eq:CES}--\ref{eq:CESekl} indicate that 
+if $\delta$ or $\delta_1$ achieves an extreme value (0 or 1), 
+the corresponding elasticity of substitution ($\sigma$ or $\sigma_1$) becomes meaningless. 
+If $\delta$ approaches unity, values of $\delta_1$ and $\sigma_1$ become meaningless.
+Thus, large uncertainty in $\sigma$, $\sigma_1$, and $\delta_1$ can be expected for any CES model 
+in which parameter estimates are positioned on the left or right boundaries
+of Figures~\ref{fig:CES_sigma1_delta1_graph} or~\ref{fig:CES_sigma_delta_graph}.
+
+Some of the uncertainty in parameter estimates may be explained by structural change 
+in the economies over the time period under study (1960--2011). 
+To account for the large uncertainty, 
+it may be useful to perform piecewise analyses of smaller time periods.
 

### 2015-01-06 Articles/Article_EnerEcon_2014/EconGrowth3.Rnw
Added new table about imprecision.

--- 2015-01-03 Articles/Article_EnerEcon_2014/EconGrowth3.Rnw
@@
       \midrule
-      #2
-      \midrule
+      #2 [3 mm]
+%       \midrule
       #3
@@
 Some of the uncertainty in parameter estimates is explained by 
-the mathematical structure of the CES model itself. 
-Equations~\ref{eq:CES}--\ref{eq:CESekl} indicate that 
-if $\delta$ or $\delta_1$ achieves an extreme value (0 or 1), 
-the corresponding elasticity of substitution ($\sigma$ or $\sigma_1$) becomes meaningless. 
-If $\delta$ approaches unity, values of $\delta_1$ and $\sigma_1$ become meaningless.
-Thus, large uncertainty in $\sigma$, $\sigma_1$, and $\delta_1$ can be expected for any CES model 
-in which parameter estimates are positioned on the left or right boundaries
-of Figures~\ref{fig:CES_sigma1_delta1_graph} or~\ref{fig:CES_sigma_delta_graph}.
+the mathematical structure of the CES model itself.%
+  \footnote{
+  Numbers in parentheses indicate rows in Table~\ref{tab:ces_sensitivity_table}.
+  }
+(1, 2)~Equations~\ref{eq:CES}--\ref{eq:CESekl} indicate that 
+if $\delta_1 = 0$
+or $\delta_1 = 1$,
+$\rho_1$ cancels.
+As a result, 
+$sse$ becomes increasingly insensitive to $\rho_1$ (and, therefore, $\sigma_1$)
+as $\delta_1 \rightarrow 0$ or $\delta_1 \rightarrow 1$.
+Decreasing sensitivity leads to reduced precision in estimating $\sigma_1$.
+%
+(3)~If $\delta = 0$, $\delta_1$ and $\rho_1$ are eliminated.
+Furthermore, with $\delta = 0$, $\rho$ cancels, 
+and $sse$ becomes insensitive to $\rho$ and, therefore, $\sigma$.
+Thus, as $\delta \rightarrow 0$, the precision with which 
+$\delta_1$, $\sigma_1$, and $\sigma$ are estimated declines.
+%
+(4)~If $\delta = 1$, $\rho$ cancels, 
+and $sse$ becomes insensitive to values of $\sigma$.
+Given that both (a)~ the \texttt{cesEst} fitting algorithm
+still uses a meaningless value for $\rho$ when $\delta \rightarrow 1$
+and (b)~the ratio $\rho/\rho_1$ appears in the CES equation,
+the value of $\rho_1$ will also become highly uncertain 
+as $\delta \rightarrow 1$
+due to the large uncertainty of $\rho$.
+Essentially, $\rho_1$ compensates for imprecise values of $\rho$
+on each successive resample,
+taking on $\rho$'s uncertainty.
+Thus, as $\delta \rightarrow 1$, 
+the precision with which both $\sigma$ and $\sigma_1$ can be estimated declines.
+%
+(5)~If $\rho_1 = \infty$, $\sigma_1 = 0$, 
+and the CES function (Equation~\ref{eq:CES}) simplifies to the Leontief function:
+%
+\begin{equation} \label{eq:ces_simplified_2_terms}
+  y = \gamma A \min \left[ k, \, l \right] \; ,
+\end{equation}
+%
+and $\delta_1$ is eliminated.
+Thus, as $\sigma_1 \rightarrow 0$, estimation of $\delta_1$ becomes increasingly imprecise.
+(6)~If $\rho = \infty$, $\sigma = 0$.
+Using Equation~\ref{eq:CESkle} as an example, we find that 
+%
+\begin{equation} \label{eq:ces_simplifies_3_terms}
+  y = \gamma A \min \left[ \delta_1 k^{-\rho_1} + (1-\delta_1) l^{-\rho_1}, \; e \right] \; ,
+\end{equation}
+%
+and $\delta$ is eliminated.
+Thus, as $\sigma \rightarrow 0$, estimation of $\delta$ becomes increasingly imprecise.
+
+\begin{table} \caption{Implications of CES model structure 
+                        on parameter precision.} \label{tab:ces_sensitivity_table} 
+  \begin{center}
+    \begin{tabular}{c c l c l} 
+      \toprule
+       & \multicolumn{2}{c}{Mathematical effect} & \multicolumn{2}{c}{Affect on precision} \\
+      \midrule
+% Row 1
+      1 & $\delta_1 = 0$ & $\rho_1$ cancels & $\delta_1 \rightarrow 0$ & $\sigma_1$ imprecise \\ [2 mm]
+% Row 2
+      2 & $\delta_1 = 1$ & $\rho_1$ cancels & $\delta_1 \rightarrow 1$ & $\sigma_1$ imprecise \\ [2 mm]
+% Row 3
+      \multirow{3}{*}{3} 
+        & \multirow{3}{*}{$\delta = 0$}   
+                         & $\delta_1$ eliminated
+                                            & \multirow{3}{*}{$\delta \rightarrow 0$}
+                                                                       & $\delta_1$ imprecise \\ [-1 mm]
+%
+        &                & $\rho_1$ eliminated &                       & $\sigma_1$ imprecise \\ [-1 mm]
+%
+        &                & $\rho$\; cancels   
+                                            &                          & $\sigma$\; imprecise \\ [2 mm]
+% Row 4
+      \multirow{2}{*}{4}
+        & \multirow{2}{*}{$\delta = 1$}
+                         & \multirow{2}{*}{$\rho$\; cancels}
+                                            & \multirow{2}{*}{$\delta \rightarrow 1$}
+                                                                       & $\sigma$\; imprecise   \\ [-1 mm] 
+%
+        &                &                  &                          & $\sigma_1$ imprecise    \\ [2 mm]
+% Row 5
+      \multirow{2}{*}{5}
+        & \multirow{2}{*}{$\rho_1 = \infty$}
+                         & $\sigma_1 = 0$   & \multirow{2}{*}{$\sigma_1 \rightarrow 0$}
+                                                                       & \multirow{2}{*}{$\delta_1$ imprecise} 
+                                                                                    \\ [-1 mm]
+%
+        &                & $\delta_1$ eliminated
+                                            &                          &                      \\ [2 mm]
+% Row 6
+      \multirow{2}{*}{6}
+        & \multirow{2}{*}{$\rho = \infty$}
+                         & $\sigma = 0$     & \multirow{2}{*}{$\sigma \rightarrow 0$}
+                                                                       & \multirow{2}{*}{$\delta$ imprecise} 
+                                                                                    \\ [-1 mm]
+%
+        &                & $\delta$\; eliminated
+                                            &                          &                      \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+\end{table}
 

### 2015-01-06 Articles/Article_EnerEcon_2014/EconGrowth3.Rnw
Added Csontos reference.

@@
 Some of the uncertainty in parameter estimates is explained by 
-the mathematical structure of the CES model itself.%
-  \footnote{
-  Numbers in parentheses indicate rows in Table~\ref{tab:ces_sensitivity_table}.
-  }
-(1, 2)~Equations~\ref{eq:CES}--\ref{eq:CESekl} indicate that 
+the mathematical structure of the CES equations.
+Table~\ref{tab:ces_sensitivity_table} summarizes these observations.
+Numbers in parentheses below correspond to row numbers in the table.
+(1,~2)~Equations~\ref{eq:CES}--\ref{eq:CESekl} indicate that 
 if $\delta_1 = 0$
@@
 $\rho_1$ cancels.
-As a result, 
-$sse$ becomes increasingly insensitive to $\rho_1$ (and, therefore, $\sigma_1$)
-as $\delta_1 \rightarrow 0$ or $\delta_1 \rightarrow 1$.
-Decreasing sensitivity leads to reduced precision in estimating $\sigma_1$.
+Consequently, 
+$sse$ (Equation~\ref{eq:sse}) is insensitive to $\rho_1$ (and, therefore, $\sigma_1$).
+As $\delta_1 \rightarrow 0$ or $\delta_1 \rightarrow 1$,
+the precision with which $\sigma_1$ can be estimated declines.
 %
 (3)~If $\delta = 0$, $\delta_1$ and $\rho_1$ are eliminated.
-Furthermore, with $\delta = 0$, $\rho$ cancels, 
-and $sse$ becomes insensitive to $\rho$ and, therefore, $\sigma$.
+Furthermore, with $\delta = 0$, $\rho$ cancels
+and $sse$ becomes insensitive to $\rho$~($\sigma$).
 Thus, as $\delta \rightarrow 0$, the precision with which 
-$\delta_1$, $\sigma_1$, and $\sigma$ are estimated declines.
-%
-(4)~If $\delta = 1$, $\rho$ cancels, 
+$\delta_1$, $\sigma_1$, and $\sigma$ can be estimated declines.
+%
+(4)~If $\delta = 1$, $\rho$ cancels
 and $sse$ becomes insensitive to values of $\sigma$.
-Given that both (a)~ the \texttt{cesEst} fitting algorithm
-still uses a meaningless value for $\rho$ when $\delta \rightarrow 1$
-and (b)~the ratio $\rho/\rho_1$ appears in the CES equation,
-the value of $\rho_1$ will also become highly uncertain 
+Given that both 
+(a)~ the \texttt{cesEst} fitting algorithm
+still uses a meaningless value for $\rho$ when $\delta \rightarrow 1$ and 
+(b)~the ratio $\rho/\rho_1$ appears in the CES equation,
+the value of $\rho_1$ will also become imprecise
 as $\delta \rightarrow 1$
@@
 on each successive resample,
-taking on $\rho$'s uncertainty.
+thereby taking on $\rho$'s uncertainty.
 Thus, as $\delta \rightarrow 1$, 
@@
 %
-(5)~If $\rho_1 = \infty$, $\sigma_1 = 0$, 
-and the CES function (Equation~\ref{eq:CES}) simplifies to the Leontief function:
+(5)~If $\rho_1 = \infty$, $\sigma_1 = 0$
+and the CES function (Equation~\ref{eq:CES}) simplifies to the Leontief function
+\citep{Csontos:1992aa}:
 %
@@
 and $\delta_1$ is eliminated.
-Thus, as $\sigma_1 \rightarrow 0$, estimation of $\delta_1$ becomes increasingly imprecise.
+Thus, as $\sigma_1 \rightarrow 0$, 
+the precision with which we can estimate $\delta_1$ declines.
+%
 (6)~If $\rho = \infty$, $\sigma = 0$.
@@
 %
-and $\delta$ is eliminated.
-Thus, as $\sigma \rightarrow 0$, estimation of $\delta$ becomes increasingly imprecise.
+and $\delta$ is eliminated \citep{Csontos:1992aa}.
+Thus, as $\sigma \rightarrow 0$, the precision with which $\delta$ can be estimated declines.
 
@@
                          & $\sigma = 0$     & \multirow{2}{*}{$\sigma \rightarrow 0$}
-                                                                       & \multirow{2}{*}{$\delta$ imprecise} 
+                                                                       & \multirow{2}{*}{$\delta$\; imprecise} 
                                                                                     \\ [-1 mm]

### 2015-01-07 Articles/Article_EnerEcon_2014/EconGrowth3.Rnw
Added notes about precision.

@@
 <<CES_sigma_delta_graph, fig.pos="H", fig.align='center', fig.width=4.5, fig.height=7, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models.">>=
-standardScatterPlot(data=subset(cesCoeffsData, nestStrParen != "(iK + iL) + ()"),
+standardScatterPlot(data=filter(cesCoeffsData, nestStrParen != "(iK + iL) + ()"),
                     mapping=aes(delta, sigma), facet_formula=country~nestStrParen, alpha=0.05) +
@@
 Thus, as $\sigma \rightarrow 0$, the precision with which $\delta$ can be estimated declines.
+
+**** From the above discussion, 
+it is clear that when $\min{sse}$ occurs at any boundary 
+(with the exception of $\sigma, \, \sigma_1 = 0$, $\rho, \, \rho_1 = -1$), 
+it will be difficult to estimate many CES parameters with precision.
+It is concerning that so many of our CES results end up on boundaries. 
+I don't think we know why we hit the boundaries so frequently. 
+I think it's real, i.e., lowest $sse$ occurs at the boundary. 
+But, I can't know for sure, because the \texttt{cesEst} function
+is a black box to us.
+One thing in our favor is that we do a thorough grid search in $\rho$ and $\rho_1$ first.
+Presumably, the grid search finds any potential 
+$sse$ valleys before starting the full gradient search. 
+This is probably an issue to be discussed with Randy. --MKH ****
+
+**** We do a thorough job of fitting along the boundaries for the Cobb-Douglas function.
+Perhaps we should do something similar for the CES model? 
+I.e., we could fit the CES model unconstrained.
+We could set up a list of models to try along each boundary. 
+Similar to Cobb-Douglas, if an unconstrained CES point estimate lands beyond the boundary,
+we could simply choose the lowest $sse$ anywhere on the boundary as the winner. --MKH ****
+
+**** This raises another question,
+namely whether we should be reporting coefficients that are, by definition unknowable.
+In the worst case, when $\delta = 0$ 
+(as it is for the fit to historical data for 
+US;
+(le)k nesting, Equation~\ref{eq:CESlek}; in Figure~\ref{fig:CES_sigma_delta_graph}), 
+CES simplifies to $y = \gamma A l$.
+All of $\sigma$, $\delta$, $\sigma_1$, and $\delta_1$
+are eliminated from the model
+and are, therefore, unknowable.  
+At present, we report the values of uknowable coefficients on the resample graphs.
+One approach would be to decide \emph{not} to report unknowable values.
+But, there are a few resample models that are rather close to but not exactly at $\delta = 1$
+in Figure~\ref{fig:CES_sigma_delta_graph}.
+Should we report parameters for the resample models where $\delta \ne 1$? --MKH ****
 

### 2015-01-08 Articles/Article_EnerEcon_2014/EconGrowth4.Rnw
Created EconGrowth4 and began making Martin's edits.

--- 2015-01-07 Articles/Article_EnerEcon_2014/EconGrowth3.Rnw
@@
 technological solutions to oil production, 
-suggest a near doubling of the real price of over the next decade.  
+suggest a near doubling of the real price of oil over the next decade.  
 **** Should we re-think this discussion in the light of the shale oil boom and the 
 recent drop in oil prices? --MKH ****
+**** Yes, we need to explain in a sentence or two what we think is going on. 
+Saudi's playing for market share and increased supply 
+from the US. 
+Potential crippling impacts on green energy upstarts. 
+Possible rebound of oil price soon? --MdW ****
 \citet{Kumhof:2012ua} point out that 
@@
 If the future decades look like the last 5 years, we are in for a rough time.'' 
+**** Possibly insert here what we make of the last few months' 
+developments in oil prices. 
+But, as it will be speculative, it needs to be very short and focused. --MdW ****
 
 The current trends in energy production and consumption and 
-the possible dire impacts on the world economy 
+the possible significant impacts on the world economy 
 as argued by the above-mentioned scholars 
@@
 
-Mainstream economic growth theory as expressed in the Cobb-Douglas production 
-function makes no attempt, beyond growth in capital~($k$) and labor~($l$), 
-to describe the mechanisms that affect economic growth, 
-nor does it attempt, beyond different values for the fitting parameters,
-to describe how such phenomena as
-slowdowns, speedups, and improvements of the education of the labor force
-might vary from one economy to the next.
+% Mainstream economic growth theory as expressed in the Cobb-Douglas production 
+% function makes no attempt, beyond growth in capital~($k$) and labor~($l$), 
+% to describe the mechanisms that affect economic growth, 
+% nor does it attempt, beyond different values for the fitting parameters,
+% to describe how such phenomena as
+% slowdowns, speedups, and improvements of the education of the labor force
+% might vary from one economy to the next.
 
@@
 economy. 
-That mainstream economic growth theory ignores energy is, therefore, 
-cause for concern, and inquiry into the proper approach for including energy 
+That mainstream economic growth theory excludes energy warrants
+an inquiry into the proper approach for including energy 
 as a factor of production in economic growth modeling is both relevant and important.
@@
 As a result, \citeauthor{Shen:2013vp} propose an atypical CES nesting structure 
-for the Chinese economy. **** Martin: More detail here about nesting? --MKH ****  
+for the Chinese economy.
 \citet{Saunders:2008aa} evaluated several production and cost functions
@@
 the way in which model parameters are determined is also subject to debate.
-The \emph{cost share theorem} from mainstream economics states that 
+The \emph{cost share theorem}%
+  \footnote{
+  See \citet[p.~150]{Kummel:2010vz} for a description of the cost share theorem.
+  }
+from mainstream economics states that 
 output elasticities 
@@
 in the markets for the factors of production.
-Although no market ever exhibits perfect competition, 
-in our opinion energy markets are \emph{least} likely to be ``perfect.''
+Energy markets are not ``perfect.''
 Many governments have parastatal or full control 
@@
 that are not priced into fossil fuel energy markets.  
-If energy markets are farther from ``perfect'' 
+If energy markets are further from ``perfect'' 
 than capital and labor markets, 
@@
 Thus, for this study, 
-we reject the cost share theorem, and
 we have no \emph{a-priori} expectation that output elasticities 
 estimated from historical output data
-will match cost shares.
+will match cost shares in national accounts.
 
@@
 
-In this paper, we assess three prominent energy-augmented production functions 
+We assess three prominent energy-augmented production functions 
 that appear in the literature: 
@@
 
-$\gamma$ is a scale factor.
+$\gamma$ is a scale factor that adjusts for atypicality 
+of the initial year of the time series.
 The fitting parameters $\rho_1$ and $\rho$ indicate elasticities 
@@
 GDP data in real 2005 US dollars for all countries was obtained from the
-RGDP$^{\mathrm{NA}}$ time series of the Penn World Table.~\citep{Feenstra:2013aa}
+RGDP$^{\mathrm{NA}}$~(Real GDP at constant 2005 national prices)
+time series of the Penn World Table~\citep{Feenstra:2013aa}.
 
@@
 for all countries was obtained from the
-RK$^{\mathrm{NA}}$ time series of the Penn World Table.~\citep{Feenstra:2013aa}
+RK$^{\mathrm{NA}}$~(Capital stock at constant 2005 national prices)
+time series of the Penn World Table~\citep{Feenstra:2013aa}.
 
@@
 
-Total employment (persons engaged) for all countries
+Total employment for all countries
 was obtained from the 
-EMP time series of the Penn World Table.~\citep{Feenstra:2013aa}
+EMP (Number of persons engaged)
+time series of the Penn World Table~\citep{Feenstra:2013aa}.
 The EMP time series was used as the labor factor of production 
@@
 average hours worked per worker per year 
-was obtained from the AVH time series of the Penn World Table.~\citep{Feenstra:2013aa}
+was obtained from the AVH (Average annual hours worked by persons engaged)
+time series of the Penn World Table~\citep{Feenstra:2013aa}.
 The product of EMP and AVH was used as the labor factor of production 
@@
 for 1980--2011 (developed economies) and 1991--2011 (other economies). 
+**** Remove word ``Calvin'' from top. --MKH ****
 %
@@
 We obtained parameter estimates by applying the method of least-squares to 
-log-transformed data using the \texttt{R} \citep{R} functions
+log-transformed data%
+  \footnote{
+  As is typical in the literature, we employ the natural logarithm transform
+  to allow linear fitting of exponential coefficients.
+  }
+using the \texttt{R} \citep{R} functions
 \texttt{lm} (for Cobb-Douglas and LINEX models) 
@@
 I think it's real, i.e., lowest $sse$ occurs at the boundary. 
-But, I can't know for sure, because the \texttt{cesEst} function
+But, we can't know for sure, because the \texttt{cesEst} function
 is a black box to us.

### 2015-01-08 Articles/Article_EnerEcon_2014/EconGrowth4.tex
Created EconGrowth4 and began making Martin's edits.

--- 2015-01-08 Articles/Article_EnerEcon_2014/EconGrowth4.Rnw
@@
 %%
-\documentclass[preprint,authoryear,12pt]{elsarticle}
+\documentclass[preprint,authoryear,12pt]{elsarticle}\usepackage[]{graphicx}\usepackage[]{color}
+%% maxwidth is the original width if it is less than linewidth
+%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
+\makeatletter
+\def\maxwidth{ %
+  \ifdim\Gin@nat@width>\linewidth
+    \linewidth
+  \else
+    \Gin@nat@width
+  \fi
+}
+\makeatother
+
+\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
+\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
+\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
+\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
+\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
+\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
+\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
+\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
+\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
+\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
+
+\usepackage{framed}
+\makeatletter
+\newenvironment{kframe}{%
+ \def\at@end@of@kframe{}%
+ \ifinner\ifhmode%
+  \def\at@end@of@kframe{\end{minipage}}%
+  \begin{minipage}{\columnwidth}%
+ \fi\fi%
+ \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
+ \colorbox{shadecolor}{##1}\hskip-\fboxsep
+     % There is no \\@totalrightmargin, so:
+     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
+ \MakeFramed {\advance\hsize-\width
+   \@totalleftmargin\z@ \linewidth\hsize
+   \@setminipage}}%
+ {\par\unskip\endMakeFramed%
+ \at@end@of@kframe}
+\makeatother
+
+\definecolor{shadecolor}{rgb}{.97, .97, .97}
+\definecolor{messagecolor}{rgb}{0, 0, 0}
+\definecolor{warningcolor}{rgb}{1, 0, 1}
+\definecolor{errorcolor}{rgb}{1, 0, 0}
+\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
+
+\usepackage{alltt}
 
@@
 \journal{Energy Economics}
-
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
 \begin{document}
 
-<<setup, echo=FALSE, message=FALSE, eval=TRUE>>=
-require(EconModels)
-require(EconData)
-require(lattice)
-require(latticeExtra)
-require(ggplot2)
-require(car)
-require(mosaic)
-require(xtable)
-require(nlmrt)
-require(dplyr)
-# Provides access to data melting. 
-# See http://cran.r-project.org/web/packages/reshape2/reshape2.pdf
-require(reshape2) 
-# tikz allows use of LaTeX formatting and font in graphs. 
-# Allows for a consistent look across the paper.
-# See http://r-forge.r-project.org/R/?group_id=440 for instructions 
-# on installing tikzDevice.
-# require(tikzDevice) 
-trellis.par.set(theme=theme.mosaic())
-options(width=75)
-options(show.signif.stars=TRUE)
-require(knitr)
-
-opts_chunk$set(
-  # ********************************************************
-  eval=TRUE,
-  # ********************************************************
-  # tikz allows LaTeX code in graphical output. 
-  # E.g., "$y$" for a variable name in the legend for a graph.  
-  # dev='tikz',
-  tidy=FALSE,
-  comment=NA,
-  # Tells whether to cache output from chunks are saved. Cacheing saves time. 
-  # However, references to LaTeX tables DO NOT WORK if cacheing is turned on.
-  cache=FALSE,
-  warning=FALSE,  #Tells whether to show warnings in the output.
-  # Turns off messages for all chunks. 
-  # Set TRUE on an individual chunk to see it.
-  message=FALSE, 
-  # Tells whether to echo code for all chunks. 
-  # Set TRUE on an individual chunk to see its code.
-  echo=FALSE     
-)
-@
-
-<<constants, include=FALSE, eval=TRUE>>=
-spaghettiGraphLevel <- 1.0 # Spaghetti graph bands will encompass a certain percentage of the data.
-@
-
-<<data>>=
-# Load historical data
-historicalData <- Calvin # From the EconData package
-
-# The working directory is set to the directory that contains this file.
-# To reach the post-processed data, we need to move 
-# up two levels and into the data_postprocessed directory.
-# So, in each of the loadPostProcessedData calls below, we use
-# dir = "../../data_postprocessed".
-pp_path <- file.path("..", "..", "data_postprocessed")
-
-# Load coefficients from all models in one large data frame
-coeffs_df <- loadPostProcessedData(Source = "Calvin", kind = "coeffs", dir = pp_path)
-# Load fitted data from all models in one large data frame
-fitted_df <- loadPostProcessedData(Source = "Calvin", kind = "fitted", dir = pp_path)
-# Load the original models.
-oModels <- loadPostProcessedData(Source = "Calvin", kind = "models", dir = pp_path)
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning: replacing previous import by 'scales::rescale' when loading 'EconModels'}}\end{kframe}
+\end{knitrout}
 
@@
 %
-<<Historical_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=7.5, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), and thermal energy ($q$).">>=
-mdata <- melt(historicalData, 
-              measure.vars = c("iGDP", "iK", "iL", "iQp"), 
-              value.name = "value", 
-              variable.name = "variable") 
-historicalPlot(data=mdata, 
-               mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
-               facet_formula = Country ~ Source, 
-               line_types = c(1,5,2,3)) +
-  xlab("") +
-  ylab("Indexed (1980=1 or 1991=1)")
-@
 
@@
 We obtained parameter estimates by applying the method of least-squares to 
-log-transformed data%
+log-transformed data using the \texttt{R} \citep{R} functions
+\texttt{lm} (for Cobb-Douglas and LINEX models) 
+and \texttt{cesEst} \citep{Henningsen:2011td} (for CES models).%
   \footnote{
@@
   }
-using the \texttt{R} \citep{R} functions
-\texttt{lm} (for Cobb-Douglas and LINEX models) 
-and \texttt{cesEst} \citep{Henningsen:2011td} (for CES models).
 
@@
 The fit to historical data is shown as a white line.
-The gray band encompasses \Sexpr{spaghettiGraphLevel * 100.0}\% of the fits to resampled data.
-
-<<CD_lambda_theta_graph, fig.pos="H", fig.align='center', fig.width=2.8, fig.height=7.0, fig.cap="$\\lambda$ and $\\theta$ values for CD resample models.">>=
-cdCoeffsData <- filter(coeffs_df, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iQp"))
-standardScatterPlot(data=cdCoeffsData, mapping=aes(x=scale, y=lambda), facet_formula=country~energy, alpha=0.05) +
-    scale_x_continuous(limits=c(0.8, 1.2), breaks=c(0.8, 1.0, 1.2)) +
-    scale_y_continuous(limits=c(-0.05, 0.15), breaks=c(0, 0.05, 0.1)) +    
-    labs(x=expression(theta), y=expression(lambda))
-@
+The gray band encompasses ??\% of the fits to resampled data.
 
 \twocolumn{}
-<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=2.9, fig.height=7.7, fig.cap="Cobb-Douglas resample model parameters.">>=
-standardTriPlot(data=cdCoeffsData, facet_formula=country~energy)
-@
-
-<<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=8.2, fig.cap="Cobb-Douglas fitted models.">>=
-cdFittedData <- filter(fitted_df, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iQp"))
-spaghettiPlot(data=cdFittedData, facet_formula=Country~energy, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1980=1 or 1991=1)")
-@
+
 \onecolumn{}
@@
 
-<<CES_lambda_gamma_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models.">>=
-cesCoeffsData <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
-                                                                     "(iK + iL) + (iQp)", 
-                                                                     "(iL + iQp) + (iK)", 
-                                                                     "(iQp + iK) + (iL)"))
-standardScatterPlot(data=cesCoeffsData, mapping=aes(gamma_coef, lambda), facet_formula=country~nestStrParen, alpha=0.05) +
-    scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
-    scale_y_continuous(limits=c(-0.05, 0.15), breaks=c(0, 0.05, 0.1)) +    
-    labs(x=expression(gamma), y=expression(lambda))
-@
-
-<<CES_sigma1_delta1_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models.">>=
-standardScatterPlot(data=cesCoeffsData, mapping=aes(delta_1, sigma_1), facet_formula=country~nestStrParen, alpha=0.05) +
-    coord_trans(y="sigma") +
-    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-    labs(x=expression(delta[1]), y=expression(sigma[1]))
-@
-
-<<CES_sigma_delta_graph, fig.pos="H", fig.align='center', fig.width=4.5, fig.height=7, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models.">>=
-standardScatterPlot(data=filter(cesCoeffsData, nestStrParen != "(iK + iL) + ()"),
-                    mapping=aes(delta, sigma), facet_formula=country~nestStrParen, alpha=0.05) +
-    coord_trans(y="sigma") +
-    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-    labs(x=expression(delta), y=expression(sigma))
-@
-
 We can develop pseudo $\alpha$, $\beta$, and $\gamma$ parameters 
@@
 
-<<CES_ternary_graph, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models.">>=
-standardTriPlot(data=cesCoeffsData, facet_formula=country~nestStrParen)
-@
-
 Figure~\ref{fig:CES_Spaghetti_Graph} compares CES model predictions 
@@
 the fit to historical data is shown as a white line, and 
-the gray band encompasses \Sexpr{spaghettiGraphLevel * 100.0}\% of the fits to resampled data.
-
-<<CES_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models.">>=
-cesFittedData <- filter(fitted_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
-                                                                     "(iK + iL) + (iQp)", 
-                                                                     "(iL + iQp) + (iK)", 
-                                                                     "(iQp + iK) + (iL)"))
-spaghettiPlot(data=cesFittedData, facet_formula=Country~nestStrParen, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1980=1 or 1991=1)")
-@
+the gray band encompasses ??\% of the fits to resampled data.
 
@@
 the fit to historical data is shown as a white line and 
-the gray band encompasses \Sexpr{spaghettiGraphLevel * 100.0}\% of the fits to resampled data.
+the gray band encompasses ??\% of the fits to resampled data.
 
 \twocolumn{}
-<<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7, fig.cap="LINEX model (with energy) resampling results.">>=
-linexCoeffsData <- filter(coeffs_df, model=="linex", energy=="iQp")
-standardScatterPlot(data=linexCoeffsData, aes(a_0, c_t), facet_formula=country~energy, alpha=0.05) +
-    labs(x=expression(a[0]), y=expression(c[t])) +
-     scale_x_continuous(limits=c(0, 2), breaks=c(0, 1.0, 2.0)) +
-     scale_y_continuous(limits=c(0, 10), breaks=c(0, 5, 10))
-@
-
-<<LINEX_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7.1, fig.cap="LINEX fitted models.">>=
-linexFittedData <- filter(fitted_df, model=="linex", energy=="iQp")
-spaghettiPlot(data=linexFittedData, facet_formula=Country~energy, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1980=1 or 1991=1)")
-@
+
 \onecolumn{}
-
-<<abg_trajectories, eval=FALSE>>=
-# This code can be run to test the conclusion about the LINEX model meeting constraints.
-# Need to put oModels in the environment much earlier in this file.
-# This chunk of R code has eval=FALSE, because it is not a part of the paper.
-abgplotdata <- fortify(oModels$Calvin$IR$linex$`iK+iL+iQp`)
-triPlot(data=abgplotdata, grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear")
-@
 

### 2015-01-08 Articles/Article_EnerEcon_2014/EconGrowth4.Rnw
Added more of Martin's comments.

@@
 random sign ($-1$ or $1$, each with probability $0.5$).  
+**** I have little idea what this means, 
+and more importantly why we follow this particular approach :) 
+(another way of saying as we are publishing 
+in an economics journal with an audience limited in statistics, 
+we must be very clear) --MdW ****
+**** Randy: can you do a little more explaining here? 
+Perhaps we should say that this is a standard way of forming the resample time series? --MKH ****
 For the case of Cobb-Douglas and LINEX models, 
@@
 log-transformed data.
-
 Intuitively, this method assumes that the residuals are indicative of 
@@
 both with and without energy as appropriate.
+**** do we follow precedent here? or just a number we fell comfortable with? 
+may warrant a reference and/or short explanation why we choose 1000 times. --MdW ****
+**** Randy: Can you provide some additional explanation here? --MKH ****
 

### 2015-01-08 Articles/Article_EnerEcon_2014/EconGrowth4.Rnw
Deleting .pdf and .tex files for EconGrowth4.

@@
 \usepackage{tablefootnote}  % allows footnotes in tables
+\usepackage{nicefrac}   % Gives nice fractions
 
@@
 It is important to note that large residuals can arise from either
-(a) poor quality historical time series data, or 
-(b) a mathematical model that does not describe the underlying phenomena well.
-It is also important to note that (c) even when the residuals are small and the 
+poor quality historical time series data or 
+a mathematical model that does not describe the underlying phenomena well.
+It is also important to note that even when the residuals are small and the 
 model produces fitted values that track the observed data closely, it may
@@
   both because the resampling technique lends itself to visual presentation and 
-  because we believe visual comparison is more effective than tables of numbers.
+  because we believe visual comparison is more effective 
+  in communicating results than endless tables of numbers.
   }
@@
 for Cobb-Douglas resample models with and without energy.
-Each reample is shown as a gray dot on the graph. 
+Each resample is shown as a gray dot on the graph. 
 The fit to historical data is shown as a gray crosshairs.
 
-Figure~\ref{fig:CD_Ternary_Scatter_Graph} shows ternary plots 
+Figure~\ref{fig:CD_Ternary_Scatter_Graph} shows ternary plots%
+  \footnote{
+  Ternary plots are effective for communicating relationships among three variables
+  that sum to a constant value.
+  Each vertex is labeled with a variable ($\alpha$, $\beta$, or $\gamma$)
+  whose value is unity at that location.
+  For example, a data point at the top of the ternary plots in Figure~\ref{fig:CD_Ternary_Scatter_Graph}
+  has $\gamma = 1$ and both $\alpha = 0$ and $\beta = 0$, 
+  by the constant returns to scale assumption.
+  Along each edge, the variable labeled at the opposite vertex is equal to zero.
+  For example, a data point along the bottom edge 
+  of the ternary plots in Figure~\ref{fig:CD_Ternary_Scatter_Graph}
+  has $\gamma = 0$.
+  A data point along the bottom edge and two-thirds of the way toward the $\beta$ vertex
+  has $\alpha = \nicefrac{1}{3}$, $\beta = \nicefrac{2}{3}$, and $\gamma = 0$.
+  }
 for $\alpha$, $\beta$, and $\gamma$ parameter values 

### 2015-01-08 Articles/Article_EnerEcon_2014/EconGrowth4.Rnw
Incorporated last of Martin's suggestions.

@@
 7,215 kcal/day-mule) were taken from \citet{Warr:2012a}.
+
+\twocolumn{}
+
 $Q_m$ represents the amount of energy in the feed consumed by 
@@
 **** Remove word ``Calvin'' from top. --MKH ****
-%
+
 <<Historical_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=7.5, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), and thermal energy ($q$).">>=
@@
 @
+
+\onecolumn{}
 
@@
 and chose the boundary fit with
-minimum $sse$ (Equation~\ref{eq:sse}) as the winner.
+minimum $sse$ (Equation~\ref{eq:sse}) as the winning model
+to be presented in graphs.
 $\gamma$ was recovered with $\gamma = 1 - \alpha - \beta$.
 
+\twocolumn{}
 Figure~\ref{fig:CD_lambda_theta_graph} shows $\lambda$ and $\theta$ values
-for Cobb-Douglas resample models with and without energy.
-Each resample is shown as a gray dot on the graph. 
-The fit to historical data is shown as a gray crosshairs.
+for Cobb-Douglas resample models with and without energy.%
+  \footnote{
+  In all resample graphs, 
+  resample points are shown as 95\% transparent black dots
+  (alpha channel set at 0.05).
+  The overlapping portion of twenty resample points 
+  appears as dark as the type of this article.
+  }
+The fit to historical data is shown as gray crosshairs.
 
@@
 
-<<CD_lambda_theta_graph, fig.pos="H", fig.align='center', fig.width=2.8, fig.height=7.0, fig.cap="$\\lambda$ and $\\theta$ values for CD resample models.">>=
+**** Fix colliding x axis labels in all Figures --MKH ****
+
+<<CD_lambda_theta_graph, fig.pos="H", fig.align='center', fig.width=2.8, fig.height=7.0, fig.cap="$\\lambda$ and $\\theta$ values for Cobb-Douglas resample models.">>=
 cdCoeffsData <- filter(coeffs_df, model=="cd", nestStr %in% c("iK+iL", "iK+iL+iQp"))
@@
 
+\onecolumn{}
+
 \twocolumn{}
 <<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=2.9, fig.height=7.7, fig.cap="Cobb-Douglas resample model parameters.">>=
-standardTriPlot(data=cdCoeffsData, facet_formula=country~energy)
+standardTriPlot(data=cdCoeffsData, facet_formula=country~energy, alpha=0.05)
 @
@@
 
-The fit with lowest $sse$ of all above trials is deemed the winner,
-and its fitting parameters are used as the model.
+The fit with lowest $sse$ of all above trials 
+is deemed the winning model to be presented in graphs.
 
@@
 Figures~\ref{fig:CES_lambda_gamma_graph}--\ref{fig:CES_sigma_delta_graph}. 
-The white crosshair on each graph shows the location 
+The gray crosshairs on each graph shows the location 
 of the fit to historical data. 
@@
 <<CES_sigma1_delta1_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models.">>=
-standardScatterPlot(data=cesCoeffsData, mapping=aes(delta_1, sigma_1), facet_formula=country~nestStrParen, alpha=0.05) +
+standardScatterPlot(data=cesCoeffsData, mapping=aes(delta_1, sigma_1), 
+                    facet_formula=country~nestStrParen, alpha=0.05) +
     coord_trans(y="sigma") +
@@
 <<CES_ternary_graph, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models.">>=
-standardTriPlot(data=cesCoeffsData, facet_formula=country~nestStrParen)
+standardTriPlot(data=cesCoeffsData, facet_formula=country~nestStrParen, alpha=0.05)
 @

### 2015-01-08 Articles/Article_EnerEcon_2014/EconGrowth4.Rnw
Added discussion of oil prices.

@@
 
-Many who accept that energy use is closely correlated with
-economic performance, regardless of the direction of causality,
-express concern regarding the negative effects of 
-rising energy prices and fossil fuel depletion 
-on current and future economic growth.
-\citet{Benes:2012tm}, incorporating views on both
-geological physical constraints and 
-technological solutions to oil production, 
-suggest a near doubling of the real price of oil over the next decade.  
+**** Possibly insert here what we make of the last few months' 
+developments in oil prices. 
+But, as it will be speculative, it needs to be very short and focused. --MdW ****
 **** Should we re-think this discussion in the light of the shale oil boom and the 
@@
 Possible rebound of oil price soon? --MdW ****
+
+**** How does this discussion sound now? --MKH ****
+Many who accept that energy use is closely correlated with
+economic performance, regardless of the direction of causality,
+express concern regarding the negative effects of 
+energy market volatility, 
+rising energy prices,
+and fossil fuel depletion 
+on current and future economic performance.
+\citet{Benes:2012tm}, incorporating views on both
+geological physical constraints and 
+technological solutions to oil production, 
+suggest a near doubling of the real price of oil over the next decade.  
+The recent 50\% drop in oil prices, 
+brought about by the US shale boom,
+has led to costs exceeding revenue for many producers
+and put future viability of many firms in question~\citep{Krauss:2015aa}.
+For many OPEC countries, 
+the price of oil is below the break-even point for national budgets,
+but they may be willing to wait for a shakeout of marginal shale producers
+before providing oil price support~\citep{Krauss:2014ab}.
 \citet{Kumhof:2012ua} point out that 
@@
 \citet{Hamilton:2013vc} argues that 
-``[c]oping with a final peak in world oil production\dots%
+``[c]oping with a final peak in world oil production\dots{}
 [will] have much in common with previous historical episodes that resulted from 
@@
 If the future decades look like the last 5 years, we are in for a rough time.'' 
-**** Possibly insert here what we make of the last few months' 
-developments in oil prices. 
-But, as it will be speculative, it needs to be very short and focused. --MdW ****
+Lower oil prices may be good for many world economies in the short term, 
+but the long-term viablity of today's \$50/barrel oil is questionable
+as the shale industry shakes out and as demand creeps upward.
 

### 2015-01-15 Articles/Article_EnerEcon_2014/EconGrowth4.Rnw
Adding boundary models to paper.
Working on CES boundary models.

@@
 
+****
+
+In addition to the above trials, we fit along all boundaries.
+Table~\ref{tab:CES_boundary_models} shows the degenerate forms of CES on each boundary.
+Equation~\ref{eq:ces_generic} accompanies Table~\ref{tab:CES_boundary_models}
+and provides the generic CES equation
+in which factors of production ($x_1$, $x_2$, $x_3$) 
+are permutations of ($k$, $l$, $e$).
+%
+\begin{equation} \label{eq:ces_generic}
+  y = \gamma A \left\{ \delta \left[ \delta_1 x_1^{-\rho_1} 
+      + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{\rho/\rho_1}  
+          + \left( 1 - \delta \right) x_3^{-\rho}  \right\} ^ {-1/\rho} \; ,
+\end{equation}
+%
+In the parameter columns of Table~\ref{tab:CES_boundary_models}, 
+``---'' indicates that a parameter is unknowable on that boundary
+(because it has been eliminated from the model), and
+an empty space indicates that the parameter is to be estimated on that boundary.
+
+\begin{table} \caption{Boundary models for the CES equation.} 
+\label{tab:CES_boundary_models} 
+  \begin{center}
+    \begin{tabular}{c c c c l} 
+      \toprule
+      $\delta_1$  & $\delta$   & $\sigma_1$ & $\sigma$ & Boundary model \\
+      \midrule
+      1           & 1          & ---        & ---      & $y = \gamma A x_1$ \\
+      0           & 1          & ---        & ---      & $y = \gamma A x_2$ \\
+      ---         & 0          & ---        & ---      & $y = \gamma A x_3$ \\
+      ---         & 1          & 0          & ---      & $y = \gamma A \min (x_1, \, x_2)$ \\
+      0           & ---        & ---        & 0        & $y = \gamma A \min (x_2, \, x_3)$ \\
+      1           & ---        & ---        & 0        & $y = \gamma A \min (x_1, \, x_3)$ \\
+      ---         & ---        & 0          & 0        & $y = \gamma A \min (x_1, \, x_2, \, x_3)$ \\
+%
+                  & 1          & $\infty$   & ---        
+            & $y = \gamma A \left[ \delta_1 x_1 + (1 - \delta_1) x_2 \right]$ \\
+%
+      0           &            & ---        & $\infty$        
+            & $y = \gamma A \left[ \delta x_2 + (1 - \delta) x_3 \right]$ \\
+%
+      1           &            & ---        & $\infty$        
+            & $y = \gamma A \left[ \delta x_1 + (1 - \delta) x_3 \right]$ \\
+%
+                  &            & $\infty$   & $\infty$        
+            & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1 + \left( 1 - \delta_1 \right) x_2 \right] 
+                    + \left( 1 - \delta \right) x_3  \right\}$ \\
+%
+      ---         &            & 0          & $\infty$        
+            & $y = \gamma A \left[ \delta \min (x_1, \, x_2) + \left( 1 - \delta \right) x_3  \right]$ \\
+%
+                  & ---        & $\infty$   & 0
+            & $y = \gamma A \min \left[ \delta_1 x_1 + \left(1 - \delta_1 \right) x_2, \, x_3  \right]$ \\
+%
+      \bottomrule
+    \end{tabular}
+  \end{center}
+\end{table}
+
+****
+
 The fit with lowest $sse$ of all above trials 
-is deemed the winning model to be presented in graphs.
+is deemed the winning model and presented in graphs.
 

### 2015-01-16 Articles/Article_EnerEcon_2014/EconGrowth4.Rnw
Finished boundary models.
Added text about CES boundary models.

--- 2015-01-08 Articles/Article_EnerEcon_2014/EconGrowth4.Rnw
@@
 
+****
+
+In addition to the above trials, 
+and in a manner similar to our approach to the Cobb-Douglas model,
+we fit along all possible CES boundaries.
+Boundaries are given by all combinations of the following:
+$\delta_1$~=~0~or~1, 
+$\sigma_1$~=~0~or~$\infty$,
+$\delta$~=~0~or~1, and
+$\sigma$~=~0~or~$\infty$.
+Equation~\ref{eq:ces_generic} shows the generic three-factor CES equation,
+wherein factors of production ($x_1$,~$x_2$,~$x_3$) 
+are permutations of ($k$,~$l$,~$e$).
+%
+\begin{equation} \label{eq:ces_generic}
+  y = \gamma A \left\{ \delta \left[ \delta_1 x_1^{-\rho_1} 
+      + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{\rho/\rho_1}  
+          + \left( 1 - \delta \right) x_3^{-\rho}  \right\} ^ {-1/\rho}
+\end{equation}
+%
+Table~\ref{tab:CES_boundary_models} shows the set 
+of degenerate equations found along parameter boundaries.
+Each degenerate equation provides a boundary model.
+Note that many boundary parameter combinations 
+yield equivalent CES degenerate equations,%
+  \footnote{
+  For example, all possible boundary parameter combinations 
+  that include $\delta = 0$ yield the same boundary model, $y = \gamma A x_3$.
+  }
+so there are far fewer than the maximum possible number of boundary models, 81.%
+  \footnote{
+  There are three possible states (unspecified, lower boundary, upper boundary)
+  for four parameters ($\delta_1$, $\sigma_1$, $\delta$, $\sigma$),
+  which gives $3^4 = 81$ possible boundary models.
+  }
+In the parameter columns of Table~\ref{tab:CES_boundary_models}, 
+``---'' indicates that a parameter is unknowable on that boundary
+(because it does not appear in the boundary model), and
+an empty space indicates that the parameter 
+can be estimated on that boundary using the degenerate equation.
+The top portion of Table~\ref{tab:CES_boundary_models} shows 
+two-parameter CES boundary models
+(similar to the CES model without energy in Equation~\ref{eq:CES})
+with $\delta = 1$, $\sigma$ unknowable, and $x_3$ absent.
+If the fitted parameters in a boundary model violate constraints, 
+the boundary model is rejected.
+
+\begin{table} \caption{Boundary models for the CES equation.} 
+\label{tab:CES_boundary_models} 
+  \begin{center}
+    \begin{tabular}{c c c c l} 
+      \toprule
+      $\delta_1$  & $\sigma_1$ & $\delta$   & $\sigma$ & Boundary model \\
+      \midrule
+      1           & ---        & 1          & ---      & $y = \gamma A x_1$ \\
+      0           & ---        & 1          & ---      & $y = \gamma A x_2$ \\
+      ---         & 0          & 1          & ---      & $y = \gamma A \min (x_1, \, x_2)$ \\
+%
+                  & $\infty$   & 1          & ---        
+            & $y = \gamma A \left[ \delta_1 x_1 + (1 - \delta_1) x_2 \right]$ \\
+%
+                  &            & 1          & ---
+            & $y = \gamma A \left[ \delta_1 x_1^{-\rho_1} 
+                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{-1/\rho_1}$ \\
+\midrule
+      ---         & ---        & 0          & ---      & $y = \gamma A x_3$ \\
+      1           & ---        & ---        & 0        & $y = \gamma A \min (x_1, \, x_3)$ \\
+      0           & ---        & ---        & 0        & $y = \gamma A \min (x_2, \, x_3)$ \\
+      ---         & 0          & ---        & 0        & $y = \gamma A \min (x_1, \, x_2, \, x_3)$ \\
+%
+      1           & ---        &            & $\infty$        
+            & $y = \gamma A \left[ \delta x_1 + (1 - \delta) x_3 \right]$ \\
+%
+      0           & ---        &            & $\infty$        
+            & $y = \gamma A \left[ \delta x_2 + (1 - \delta) x_3 \right]$ \\
+%
+                  & $\infty$   &            & $\infty$        
+            & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1 + \left( 1 - \delta_1 \right) x_2 \right] 
+                    + \left( 1 - \delta \right) x_3  \right\}$ \\
+%
+      ---         & 0          &            & $\infty$        
+            & $y = \gamma A \left[ \delta \min (x_1, \, x_2) + \left( 1 - \delta \right) x_3  \right]$ \\
+%
+                  & $\infty$   & ---        & 0
+            & $y = \gamma A \min \left[ \delta_1 x_1 + \left(1 - \delta_1 \right) x_2, \, x_3  \right]$ \\
+%
+      1           & ---        &         & 
+            & $y = \gamma A \left[ \delta x_1^{-\rho} 
+                    + \left(1 - \delta \right) x_3^{-\rho} \right] ^ {-1/\rho}$ \\ 
+%
+      0           & ---        &            & 
+            & $y = \gamma A \left[ \delta x_2^{-\rho} + \left(1 - \delta \right) x_3^{-\rho} \right]^{-1/\rho}$ \\
+%
+                  &            & ---     & 0
+            & $y = \gamma A \min \left\{ \left[ \delta_1 x_1^{-\rho_1} 
+                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{-1/\rho_1}, \, x_3 \right\}$ \\ 
+%
+      ---         & 0          &            & 
+            & $y = \gamma A \left\{ \delta \left[ \min \left( x_1, \, x_2 \right) \right]^{-\rho}  
+                    + \left( 1 - \delta \right) x_3^{-\rho}  \right\} ^ {-1/\rho}$ \\ 
+%
+                  &            &            & $\infty$
+            & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1^{-\rho_1} 
+                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{-1/\rho_1}  
+                    + \left( 1 - \delta \right) x_3  \right\}$ \\ 
+%
+                  & $\infty$   &            &
+            & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1 
+                    + \left( 1 - \delta_1 \right) x_2 \right]^{-\rho}  
+                    + \left( 1 - \delta \right) x_3^{-\rho}  \right\} ^ {-1/\rho}$ \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+\end{table}
+
+****
+
 The fit with lowest $sse$ of all above trials 
-is deemed the winning model to be presented in graphs.
+is deemed the winning model and presented in graphs.
 

### 2015-01-16 Articles/Article_EnerEcon_2014/EconGrowth4.Rnw
Editing text for CES boundary models.

@@
 Table~\ref{tab:CES_boundary_models} shows the set 
-of degenerate equations found along parameter boundaries.
+of 20 degenerate equations found along parameter boundaries.
 Each degenerate equation provides a boundary model.
 Note that many boundary parameter combinations 
-yield equivalent CES degenerate equations,%
+yield equivalent CES boundary models,%
   \footnote{
@@
   }
-so there are far fewer than the maximum possible number of boundary models, 81.%
+so there are far fewer than the maximum possible number of degenerate equations~(81).%
   \footnote{
@@
   which gives $3^4 = 81$ possible boundary models.
+  }
+Boundary models obtained when $\delta_1$ or $\delta$ is at an extreme value
+are straightforward to derive from Equation~\ref{eq:ces_generic}.
+When $\sigma_1$ or $\sigma$ is 0, 
+factors of production are complimentary,
+and the Leontief model applies.%
+  \footnote{
+  For the case of $\sigma_1 = 0$ and $\delta~=~1$, the Leontief model is
+  $y = \gamma A \min (x_1, x_2)$.
+  }
+When $\sigma_1$ or $\sigma$ is $\infty$, 
+factors of production are subsitutible,
+and the linear model applies.%
+  \footnote{
+  For the case of $\sigma_1 = \infty$ and $\delta~=~1$, the linear model is
+  $y = \gamma A \left[ \delta_1 x_1 + (1 - \delta_1) x_2 \right]$.
   }
@@
 (similar to the CES model without energy in Equation~\ref{eq:CES})
-with $\delta = 1$, $\sigma$ unknowable, and $x_3$ absent.
+with $\delta~=~1$, $\sigma$~unknowable, and $x_3$~absent.
 If the fitted parameters in a boundary model violate constraints, 

### 2015-02-01 Articles/Article_EnerEcon_2014/EconGrowth4.Rnw
Added identifying number to the boundary mod tbl.
Changed order of rows in the boundary mod table.

@@
   \footnote{
-  For the case of $\sigma_1 = 0$ and $\delta~=~1$, the Leontief model is
+  E.g., when $\sigma_1 = 0$ and $\delta~=~1$, the Leontief model is
   $y = \gamma A \min (x_1, x_2)$.
@@
   \footnote{
-  For the case of $\sigma_1 = \infty$ and $\delta~=~1$, the linear model is
+  E.g., when $\sigma_1 = \infty$ and $\delta~=~1$, the linear model is
   $y = \gamma A \left[ \delta_1 x_1 + (1 - \delta_1) x_2 \right]$.
@@
   \begin{center}
-    \begin{tabular}{c c c c l} 
+    \begin{tabular}{r c c c c l} 
       \toprule
-      $\delta_1$  & $\sigma_1$ & $\delta$   & $\sigma$ & Boundary model \\
+      & $\delta_1$  & $\sigma_1$ & $\delta$   & $\sigma$ & Boundary model \\
       \midrule
-      1           & ---        & 1          & ---      & $y = \gamma A x_1$ \\
-      0           & ---        & 1          & ---      & $y = \gamma A x_2$ \\
-      ---         & 0          & 1          & ---      & $y = \gamma A \min (x_1, \, x_2)$ \\
-%
-                  & $\infty$   & 1          & ---        
+      1. & 1           & ---        & 1          & ---      & $y = \gamma A x_1$ \\
+      2. & 0           & ---        & 1          & ---      & $y = \gamma A x_2$ \\
+      3. & ---         & 0          & 1          & ---      & $y = \gamma A \min (x_1, \, x_2)$ \\
+%
+      4. &             & $\infty$   & 1          & ---        
             & $y = \gamma A \left[ \delta_1 x_1 + (1 - \delta_1) x_2 \right]$ \\
 %
-                  &            & 1          & ---
+      5. &             &            & 1          & ---
             & $y = \gamma A \left[ \delta_1 x_1^{-\rho_1} 
@@
 \midrule
-      ---         & ---        & 0          & ---      & $y = \gamma A x_3$ \\
-      1           & ---        & ---        & 0        & $y = \gamma A \min (x_1, \, x_3)$ \\
-      0           & ---        & ---        & 0        & $y = \gamma A \min (x_2, \, x_3)$ \\
-      ---         & 0          & ---        & 0        & $y = \gamma A \min (x_1, \, x_2, \, x_3)$ \\
-%
-      1           & ---        &            & $\infty$        
+      6. & ---         & ---        & 0          & ---      & $y = \gamma A x_3$ \\
+      7. & 1           & ---        & ---        & 0        & $y = \gamma A \min (x_1, \, x_3)$ \\
+      8. & 0           & ---        & ---        & 0        & $y = \gamma A \min (x_2, \, x_3)$ \\
+      9. & ---         & 0          & ---        & 0        & $y = \gamma A \min (x_1, \, x_2, \, x_3)$ \\
+%
+     10. & 1           & ---        &            & $\infty$        
             & $y = \gamma A \left[ \delta x_1 + (1 - \delta) x_3 \right]$ \\
 %
-      0           & ---        &            & $\infty$        
+     11. & 0           & ---        &            & $\infty$        
             & $y = \gamma A \left[ \delta x_2 + (1 - \delta) x_3 \right]$ \\
 %
-                  & $\infty$   &            & $\infty$        
+     12. &             & $\infty$   &            & $\infty$        
             & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1 + \left( 1 - \delta_1 \right) x_2 \right] 
@@
 %
-      ---         & 0          &            & $\infty$        
+     13. & ---         & 0          &            & $\infty$        
             & $y = \gamma A \left[ \delta \min (x_1, \, x_2) + \left( 1 - \delta \right) x_3  \right]$ \\
 %
-                  & $\infty$   & ---        & 0
+     14. &             & $\infty$   & ---        & 0
             & $y = \gamma A \min \left[ \delta_1 x_1 + \left(1 - \delta_1 \right) x_2, \, x_3  \right]$ \\
 %
-      1           & ---        &         & 
+     15. & 1           & ---        &         & 
             & $y = \gamma A \left[ \delta x_1^{-\rho} 
@@
 %
-      0           & ---        &            & 
+     16. & 0           & ---        &            & 
             & $y = \gamma A \left[ \delta x_2^{-\rho} + \left(1 - \delta \right) x_3^{-\rho} \right]^{-1/\rho}$ \\
 %
-                  &            & ---     & 0
-            & $y = \gamma A \min \left\{ \left[ \delta_1 x_1^{-\rho_1} 
-                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{-1/\rho_1}, \, x_3 \right\}$ \\ 
-%
-      ---         & 0          &            & 
+     17. &             & $\infty$   &            &
+            & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1 
+                    + \left( 1 - \delta_1 \right) x_2 \right]^{-\rho}  
+                    + \left( 1 - \delta \right) x_3^{-\rho}  \right\} ^ {-1/\rho}$ \\
+%
+     18. & ---         & 0          &            & 
             & $y = \gamma A \left\{ \delta \left[ \min \left( x_1, \, x_2 \right) \right]^{-\rho}  
@@
 %
-                  &            &            & $\infty$
+     19. &             &            &            & $\infty$
             & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1^{-\rho_1} 
@@
 %
-                  & $\infty$   &            &
-            & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1 
-                    + \left( 1 - \delta_1 \right) x_2 \right]^{-\rho}  
-                    + \left( 1 - \delta \right) x_3^{-\rho}  \right\} ^ {-1/\rho}$ \\
+     20. &            &            & ---     & 0
+            & $y = \gamma A \min \left\{ \left[ \delta_1 x_1^{-\rho_1} 
+                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{-1/\rho_1}, \, x_3 \right\}$ \\ 
       \bottomrule

### 2015-02-06 Articles/Article_EnerEcon_2014/EconGrowth4.Rnw
Adjusted the discussion of the CES boundary models.

@@
 
-****
+\citet{Henningsen:2011td}, 
+in their detailed analysis of \citet{Kemfert:1998vd}, found that 
+%
+\begin{quote}
+\ldots the Levenberg-Marquardt and the \texttt{PORT} algorithms 
+are---at least in this study---most likely to find the 
+coefficients that give the best fit to the model, 
+where the \texttt{PORT} algorithm can be used to restrict the estimates 
+to the economically meaningful region.
+\end{quote}
+%
+In our testing, we found that to be mostly true. 
+\texttt{PORT} nearly always provided lower
+$sse$ than \texttt{L-BFGS-B}, despite the fact that 
+\texttt{L-BFGS-B} often reports convergence
+and \texttt{PORT} does not for the same data
+(i.e., for the same $y$, $k$, $l$, and $e$ time series).
 
@@
 $\delta_1$~=~0~or~1, 
-$\sigma_1$~=~0~or~$\infty$,
-$\delta$~=~0~or~1, and
+$\delta$~=~0~or~1,
+$\sigma_1$~=~0~or~$\infty$, and
 $\sigma$~=~0~or~$\infty$.
-Equation~\ref{eq:ces_generic} shows the generic three-factor CES equation,
+Table~\ref{tab:CES_boundary_models} shows the set 
+of 20 degenerate equations found along parameter boundaries~(rows~1--20).
+Row~21 of Table~\ref{tab:CES_boundary_models} shows the generic three-factor CES equation,
 wherein factors of production ($x_1$,~$x_2$,~$x_3$) 
 are permutations of ($k$,~$l$,~$e$).
-%
-\begin{equation} \label{eq:ces_generic}
-  y = \gamma A \left\{ \delta \left[ \delta_1 x_1^{-\rho_1} 
-      + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{\rho/\rho_1}  
-          + \left( 1 - \delta \right) x_3^{-\rho}  \right\} ^ {-1/\rho}
-\end{equation}
-%
-Table~\ref{tab:CES_boundary_models} shows the set 
-of 20 degenerate equations found along parameter boundaries.
 Each degenerate equation provides a boundary model.
@@
 Boundary models obtained when $\delta_1$ or $\delta$ is at an extreme value
-are straightforward to derive from Equation~\ref{eq:ces_generic}.
+are straightforward to derive from row~21 of Table~\ref{tab:CES_boundary_models}.
 When $\sigma_1$ or $\sigma$ is 0, 
-factors of production are complimentary,
+factors of production are perfect complements,
 and the Leontief model applies.%
@@
 When $\sigma_1$ or $\sigma$ is $\infty$, 
-factors of production are subsitutible,
+factors of production are perfect substitutes,
 and the linear model applies.%
@@
 
-\begin{table} \caption{Boundary models for the CES equation.} 
+\begin{table} \caption{Boundary (rows~1--20) and generic (row~21) models for the CES equation.} 
 \label{tab:CES_boundary_models} 
@@
                     + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{-1/\rho_1}, \, x_3 \right\}$ \\ 
+\midrule
+     21. &            &            &         & 
+            & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1^{-\rho_1} 
+                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{\rho/\rho_1}  
+                    + \left( 1 - \delta \right) x_3^{-\rho}  \right\} ^ {-1/\rho}$ \\ 
       \bottomrule
@@
 
-****
-
-The fit with lowest $sse$ of all above trials 
-is deemed the winning model and presented in graphs.
-
-\citet{Henningsen:2011td}, 
-in their detailed analysis of \citet{Kemfert:1998vd}, found that
-
-\begin{quote}
-\ldots the Levenberg-Marquardt and the \texttt{PORT} algorithms 
-are---at least in this study---most likely to find the 
-coefficients that give the best fit to the model, 
-where the \texttt{PORT} algorithm can be used to restrict the estimates 
-to the economically meaningful region.
-\end{quote}
-
-In our testing, we found that to be mostly true. 
-\texttt{PORT} nearly always provided lower
-$sse$ than \texttt{L-BFGS-B}, despite the fact that 
-\texttt{L-BFGS-B} often reports convergence
-and \texttt{PORT} does not for the same data
-(i.e., for the same $y$, $k$, $l$, and $e$ time series).
+The model with lowest $sse$ of all above trials 
+is deemed the winning (i.e.,~best) model,
+and its parameters are presented in graphs herein.
+In special cases, two boundary models will be equivalent.
+For example, boundary model~3 is identical to boundary model~1~(2)
+if $x_1$ is always less than (greater than) $x_2$ for all years.
+If two or more models have the same $sse$ (to six digits), 
+the model with the lowest row number in Table~\ref{tab:CES_boundary_models} is deemed the winner,
+thereby ensuring that the simplest model is selected.
+
+**** Edit the next paragraphs after we finalize the appearance
+of the distribution graphs. 
+Also, add a discussion of the boundary models and how the reduce 
+the amount of data available in the bar graphs. ****
 

### 2015-02-07 Articles/Article_EnerEcon_2014/EconGrowth4.Rnw
Edits to the text surrounding CES boundary mods.

@@
 \citep{Henningsen:2011td} was used to estimate parameters 
-$\lambda$, $\gamma$, $\delta$, $\delta_1$, $\rho$, and $\rho_1$. 
+$\gamma$, $\lambda$, $\delta_1$, $\delta$, $\rho_1$, and $\rho$. 
 The \texttt{cesEst} function of \texttt{micEconCES} provides 
@@
 in our testing, nearly always violated them, often returning
-negative values for elasticity of substitution parameters $\sigma$ and $\sigma_1$.
+negative values for elasticity of substitution parameters $\sigma_1$ and $\sigma$.
 Thus, we used the two fitting algorithms available in \texttt{cesEst} that
@@
 Our CES parameter estimation algorithm starts with an eleven-value grid search
-in $\rho$ and $\rho_1$ (9, 2, 1, 0.43, 0.25, 0.1, -0.1, -0.5, -0.75, -0.9, -0.99),
-which corresponds to $\sigma$ and $\sigma_1$ values of
+in $\rho_1$ and $\rho$ (9, 2, 1, 0.43, 0.25, 0.1, -0.1, -0.5, -0.75, -0.9, -0.99),
+corresponding to $\sigma_1$ and $\sigma$ values of
 0.1, 0.33, 0.5, 0.7, 0.8, 0.9, 1.11, 2, 4, 10, and 100, respectively.
-During the grid search, values of $\rho$ and $\rho_1$ are fixed,
-and values of $\lambda$, $\gamma$, $\delta$, and $\delta_1$ are estimated 
+During the grid search, values of $\rho_1$ and $\rho$ are fixed,
+and values of $\gamma$, $\lambda$, $\delta_1$, and $\delta$ are estimated 
 by gradient search with the \texttt{PORT} and \texttt{L-BFGS-B} algorithms.
-In all, 121 gradient searches in $\lambda$, $\gamma$, $\delta$, and $\delta_1$
-at grid points representing all combinations of $\rho$ and $\rho_1$ are attempted.
+In all, 121 gradient searches in $\gamma$, $\lambda$, $\delta_1$, and $\delta$
+at grid points representing all combinations of $\rho_1$ and $\rho$ are attempted.
 During the grid search portion of our algorithm, starting values for the free parameters
-are $\lambda$ = 0.015/year, $\delta$ = 0.5, $\delta_1$ = 0.5, 
-and $\gamma$ is set to a value such that the mean of the residuals is zero
-by the \texttt{cesEst} function.
+are $\lambda$ = 0.015/year, $\delta_1$ = 0.5, $\delta$ = 0.5, 
+and $\gamma$ is set by the \texttt{cesEst} function
+to a value such that the mean of the residuals is zero.
 
@@
 is attempted wherein all fitting parameters 
-($\lambda$, $\gamma$, $\delta$, $\delta_1$, $\rho$, and $\rho_1$)
+($\gamma$, $\lambda$, $\delta_1$, $\delta$, $\rho_1$, and $\rho$)
 are allowed to float.
-The start values for fitting parameters are taken from 
+The starting values for fitting parameters are taken from 
 the grid search point that provided the lowest $sse$ (Equation~\ref{eq:sse}).
@@
 In this final gradient search, all model parameters 
-($\lambda$, $\gamma$, $\delta$, $\delta_1$, $\rho$, and $\rho_1$)
+($\gamma$, $\lambda$, $\delta_1$, $\delta$, $\rho_1$, and $\rho$)
 are considered free parameters.
@@
 In addition to the above trials, 
-and in a manner similar to our approach to the Cobb-Douglas model,
-we fit along all possible CES boundaries.
+and in a manner similar to our approach 
+to the Cobb-Douglas model~(see section \ref{sec:CD_Parameter_Estimation}),
+we also fit along all possible CES boundaries.
 Boundaries are given by all combinations of the following:
@@
   E.g., when $\sigma_1 = 0$ and $\delta~=~1$, the Leontief model is
-  $y = \gamma A \min (x_1, x_2)$.
+  $y = \gamma A \min (x_1, x_2)$, row 3 in Table~\ref{tab:CES_boundary_models}.
   }
@@
   E.g., when $\sigma_1 = \infty$ and $\delta~=~1$, the linear model is
-  $y = \gamma A \left[ \delta_1 x_1 + (1 - \delta_1) x_2 \right]$.
+  $y = \gamma A \left[ \delta_1 x_1 + (1 - \delta_1) x_2 \right]$,
+  row 4 in Table~\ref{tab:CES_boundary_models}.
   }
@@
 If two or more models have the same $sse$ (to six digits), 
-the model with the lowest row number in Table~\ref{tab:CES_boundary_models} is deemed the winner,
-thereby ensuring that the simplest model is selected.
+the model with the lowest row number in Table~\ref{tab:CES_boundary_models} 
+is deemed the winning model,
+thereby ensuring that the simpler model is selected.
 

### 2015-03-18 Articles/Article_EnerEcon_2014/EconGrowth4.Rnw
Removed row number for full CES model.
Changed Table 2 caption.
Added a new version of the models table.
New order for CES boundary models.

@@
 
-\begin{table} \caption{Boundary (rows~1--20) and generic (row~21) models for the CES equation.} 
+\begin{table} \caption{CES boundary models (rows~1--20) and full model (bottom row). ORIGINAL.  **** DELETE EVENTUALLY ****} 
+  \begin{center}
+    \begin{tabular}{r c c c c l} 
+      \toprule
+      & $\delta_1$  & $\sigma_1$ & $\delta$   & $\sigma$ & Boundary model \\
+      \midrule
+      1. & 1           & ---        & 1          & ---      & $y = \gamma A x_1$ \\
+      2. & 0           & ---        & 1          & ---      & $y = \gamma A x_2$ \\
+      3. & ---         & 0          & 1          & ---      & $y = \gamma A \min (x_1, \, x_2)$ \\
+%
+      4. &             & $\infty$   & 1          & ---        
+            & $y = \gamma A \left[ \delta_1 x_1 + (1 - \delta_1) x_2 \right]$ \\
+%
+      5. &             &            & 1          & ---
+            & $y = \gamma A \left[ \delta_1 x_1^{-\rho_1} 
+                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{-1/\rho_1}$ \\
+\midrule
+      6. & ---         & ---        & 0          & ---      & $y = \gamma A x_3$ \\
+      7. & 1           & ---        & ---        & 0        & $y = \gamma A \min (x_1, \, x_3)$ \\
+      8. & 0           & ---        & ---        & 0        & $y = \gamma A \min (x_2, \, x_3)$ \\
+      9. & ---         & 0          & ---        & 0        & $y = \gamma A \min (x_1, \, x_2, \, x_3)$ \\
+%
+     10. & 1           & ---        &            & $\infty$        
+            & $y = \gamma A \left[ \delta x_1 + (1 - \delta) x_3 \right]$ \\
+%
+     11. & 0           & ---        &            & $\infty$        
+            & $y = \gamma A \left[ \delta x_2 + (1 - \delta) x_3 \right]$ \\
+%
+     12. &             & $\infty$   &            & $\infty$        
+            & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1 + \left( 1 - \delta_1 \right) x_2 \right] 
+                    + \left( 1 - \delta \right) x_3  \right\}$ \\
+%
+     13. & ---         & 0          &            & $\infty$        
+            & $y = \gamma A \left[ \delta \min (x_1, \, x_2) + \left( 1 - \delta \right) x_3  \right]$ \\
+%
+     14. &             & $\infty$   & ---        & 0
+            & $y = \gamma A \min \left[ \delta_1 x_1 + \left(1 - \delta_1 \right) x_2, \, x_3  \right]$ \\
+%
+     15. & 1           & ---        &         & 
+            & $y = \gamma A \left[ \delta x_1^{-\rho} 
+                    + \left(1 - \delta \right) x_3^{-\rho} \right] ^ {-1/\rho}$ \\ 
+%
+     16. & 0           & ---        &            & 
+            & $y = \gamma A \left[ \delta x_2^{-\rho} + \left(1 - \delta \right) x_3^{-\rho} \right]^{-1/\rho}$ \\
+%
+     17. &             & $\infty$   &            &
+            & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1 
+                    + \left( 1 - \delta_1 \right) x_2 \right]^{-\rho}  
+                    + \left( 1 - \delta \right) x_3^{-\rho}  \right\} ^ {-1/\rho}$ \\
+%
+     18. & ---         & 0          &            & 
+            & $y = \gamma A \left\{ \delta \left[ \min \left( x_1, \, x_2 \right) \right]^{-\rho}  
+                    + \left( 1 - \delta \right) x_3^{-\rho}  \right\} ^ {-1/\rho}$ \\ 
+%
+     19. &             &            &            & $\infty$
+            & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1^{-\rho_1} 
+                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{-1/\rho_1}  
+                    + \left( 1 - \delta \right) x_3  \right\}$ \\ 
+%
+     20. &            &            & ---     & 0
+            & $y = \gamma A \min \left\{ \left[ \delta_1 x_1^{-\rho_1} 
+                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{-1/\rho_1}, \, x_3 \right\}$ \\ 
+\midrule
+         &            &            &         & 
+            & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1^{-\rho_1} 
+                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{\rho/\rho_1}  
+                    + \left( 1 - \delta \right) x_3^{-\rho}  \right\} ^ {-1/\rho}$ \\ 
+      \bottomrule
+    \end{tabular}
+  \end{center}
+\end{table}
+
+\begin{table} \caption{CES boundary models (rows~1--20) and full model (bottom row). 
+                       Re-ordered, but with original model numbers. **** DELETE EVENTUALLY ****}
+  \begin{center}
+    \begin{tabular}{r c c c c l} 
+      \toprule
+      & $\delta_1$  & $\sigma_1$ & $\delta$   & $\sigma$ & Boundary model \\
+      \midrule
+      1. & 1           & ---        & 1          & ---      & $y = \gamma A x_1$ \\
+      2. & 0           & ---        & 1          & ---      & $y = \gamma A x_2$ \\
+      6. & ---         & ---        & 0          & ---      & $y = \gamma A x_3$ \\
+      \midrule
+      3. & ---         & 0          & 1          & ---      & $y = \gamma A \min (x_1, \, x_2)$ \\
+      7. & 1           & ---        & ---        & 0        & $y = \gamma A \min (x_1, \, x_3)$ \\
+      8. & 0           & ---        & ---        & 0        & $y = \gamma A \min (x_2, \, x_3)$ \\
+%
+      4. &             & $\infty$   & 1          & ---        
+            & $y = \gamma A \left[ \delta_1 x_1 + (1 - \delta_1) x_2 \right]$ \\
+%
+     10. & 1           & ---        &            & $\infty$        
+            & $y = \gamma A \left[ \delta x_1 + (1 - \delta) x_3 \right]$ \\
+%
+     11. & 0           & ---        &            & $\infty$        
+            & $y = \gamma A \left[ \delta x_2 + (1 - \delta) x_3 \right]$ \\
+%
+      5. &             &            & 1          & ---
+            & $y = \gamma A \left[ \delta_1 x_1^{-\rho_1} 
+                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{-1/\rho_1}$ \\
+%
+     15. & 1           & ---        &         & 
+            & $y = \gamma A \left[ \delta x_1^{-\rho} 
+                    + \left(1 - \delta \right) x_3^{-\rho} \right] ^ {-1/\rho}$ \\ 
+%
+     16. & 0           & ---        &            & 
+            & $y = \gamma A \left[ \delta x_2^{-\rho} + \left(1 - \delta \right) x_3^{-\rho} \right]^{-1/\rho}$ \\
+      \midrule
+      9. & ---         & 0          & ---        & 0        & $y = \gamma A \min (x_1, \, x_2, \, x_3)$ \\
+%
+     13. & ---         & 0          &            & $\infty$        
+            & $y = \gamma A \left[ \delta \min (x_1, \, x_2) + \left( 1 - \delta \right) x_3  \right]$ \\
+%
+     14. &             & $\infty$   & ---        & 0
+            & $y = \gamma A \min \left[ \delta_1 x_1 + \left(1 - \delta_1 \right) x_2, \, x_3  \right]$ \\
+%
+     12. &             & $\infty$   &            & $\infty$        
+            & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1 + \left( 1 - \delta_1 \right) x_2 \right] 
+                    + \left( 1 - \delta \right) x_3  \right\}$ \\
+%
+     18. & ---         & 0          &            & 
+            & $y = \gamma A \left\{ \delta \left[ \min \left( x_1, \, x_2 \right) \right]^{-\rho}  
+                    + \left( 1 - \delta \right) x_3^{-\rho}  \right\} ^ {-1/\rho}$ \\ 
+%
+     20. &            &            & ---     & 0
+            & $y = \gamma A \min \left\{ \left[ \delta_1 x_1^{-\rho_1} 
+                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{-1/\rho_1}, \, x_3 \right\}$ \\ 
+%
+     19. &             &            &            & $\infty$
+            & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1^{-\rho_1} 
+                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{-1/\rho_1}  
+                    + \left( 1 - \delta \right) x_3  \right\}$ \\ 
+%
+     17. &             & $\infty$   &            &
+            & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1 
+                    + \left( 1 - \delta_1 \right) x_2 \right]^{-\rho}  
+                    + \left( 1 - \delta \right) x_3^{-\rho}  \right\} ^ {-1/\rho}$ \\
+\midrule
+         &            &            &         & 
+            & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1^{-\rho_1} 
+                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{\rho/\rho_1}  
+                    + \left( 1 - \delta \right) x_3^{-\rho}  \right\} ^ {-1/\rho}$ \\ 
+      \bottomrule
+    \end{tabular}
+  \end{center}
+\end{table}
+
+\begin{table} \caption{CES boundary models (rows~1--20) and full model (bottom row).} 
 \label{tab:CES_boundary_models} 
@@
       2. & 0           & ---        & 1          & ---      & $y = \gamma A x_2$ \\
-      3. & ---         & 0          & 1          & ---      & $y = \gamma A \min (x_1, \, x_2)$ \\
-%
-      4. &             & $\infty$   & 1          & ---        
+      3. & ---         & ---        & 0          & ---      & $y = \gamma A x_3$ \\
+      \midrule
+      4. & ---         & 0          & 1          & ---      & $y = \gamma A \min (x_1, \, x_2)$ \\
+      5. & 1           & ---        & ---        & 0        & $y = \gamma A \min (x_1, \, x_3)$ \\
+      6. & 0           & ---        & ---        & 0        & $y = \gamma A \min (x_2, \, x_3)$ \\
+%
+      7. &             & $\infty$   & 1          & ---        
             & $y = \gamma A \left[ \delta_1 x_1 + (1 - \delta_1) x_2 \right]$ \\
 %
-      5. &             &            & 1          & ---
+      8. & 1           & ---        &            & $\infty$        
+            & $y = \gamma A \left[ \delta x_1 + (1 - \delta) x_3 \right]$ \\
+%
+      9. & 0           & ---        &            & $\infty$        
+            & $y = \gamma A \left[ \delta x_2 + (1 - \delta) x_3 \right]$ \\
+%
+     10. &             &            & 1          & ---
             & $y = \gamma A \left[ \delta_1 x_1^{-\rho_1} 
                     + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{-1/\rho_1}$ \\
+%
+     11. & 1           & ---        &         & 
+            & $y = \gamma A \left[ \delta x_1^{-\rho} 
+                    + \left(1 - \delta \right) x_3^{-\rho} \right] ^ {-1/\rho}$ \\ 
+%
+     12. & 0           & ---        &            & 
+            & $y = \gamma A \left[ \delta x_2^{-\rho} + \left(1 - \delta \right) x_3^{-\rho} \right]^{-1/\rho}$ \\
       \midrule
-      6. & ---         & ---        & 0          & ---      & $y = \gamma A x_3$ \\
-      7. & 1           & ---        & ---        & 0        & $y = \gamma A \min (x_1, \, x_3)$ \\
-      8. & 0           & ---        & ---        & 0        & $y = \gamma A \min (x_2, \, x_3)$ \\
-      9. & ---         & 0          & ---        & 0        & $y = \gamma A \min (x_1, \, x_2, \, x_3)$ \\
-%
-     10. & 1           & ---        &            & $\infty$        
-            & $y = \gamma A \left[ \delta x_1 + (1 - \delta) x_3 \right]$ \\
-%
-     11. & 0           & ---        &            & $\infty$        
-            & $y = \gamma A \left[ \delta x_2 + (1 - \delta) x_3 \right]$ \\
-%
-     12. &             & $\infty$   &            & $\infty$        
+     13. & ---         & 0          & ---        & 0        & $y = \gamma A \min (x_1, \, x_2, \, x_3)$ \\
+%
+     14. & ---         & 0          &            & $\infty$        
+            & $y = \gamma A \left[ \delta \min (x_1, \, x_2) + \left( 1 - \delta \right) x_3  \right]$ \\
+%
+     15. &             & $\infty$   & ---        & 0
+            & $y = \gamma A \min \left[ \delta_1 x_1 + \left(1 - \delta_1 \right) x_2, \, x_3  \right]$ \\
+%
+     16. &             & $\infty$   &            & $\infty$        
             & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1 + \left( 1 - \delta_1 \right) x_2 \right] 
@@
 %
-     13. & ---         & 0          &            & $\infty$        
-            & $y = \gamma A \left[ \delta \min (x_1, \, x_2) + \left( 1 - \delta \right) x_3  \right]$ \\
-%
-     14. &             & $\infty$   & ---        & 0
-            & $y = \gamma A \min \left[ \delta_1 x_1 + \left(1 - \delta_1 \right) x_2, \, x_3  \right]$ \\
-%
-     15. & 1           & ---        &         & 
-            & $y = \gamma A \left[ \delta x_1^{-\rho} 
-                    + \left(1 - \delta \right) x_3^{-\rho} \right] ^ {-1/\rho}$ \\ 
-%
-     16. & 0           & ---        &            & 
-            & $y = \gamma A \left[ \delta x_2^{-\rho} + \left(1 - \delta \right) x_3^{-\rho} \right]^{-1/\rho}$ \\
-%
-     17. &             & $\infty$   &            &
-            & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1 
-                    + \left( 1 - \delta_1 \right) x_2 \right]^{-\rho}  
-                    + \left( 1 - \delta \right) x_3^{-\rho}  \right\} ^ {-1/\rho}$ \\
-%
-     18. & ---         & 0          &            & 
+     17. & ---         & 0          &            & 
             & $y = \gamma A \left\{ \delta \left[ \min \left( x_1, \, x_2 \right) \right]^{-\rho}  
                     + \left( 1 - \delta \right) x_3^{-\rho}  \right\} ^ {-1/\rho}$ \\ 
+%
+     18. &            &            & ---     & 0
+            & $y = \gamma A \min \left\{ \left[ \delta_1 x_1^{-\rho_1} 
+                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{-1/\rho_1}, \, x_3 \right\}$ \\ 
 %
@@
 %
-     20. &            &            & ---     & 0
-            & $y = \gamma A \min \left\{ \left[ \delta_1 x_1^{-\rho_1} 
-                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{-1/\rho_1}, \, x_3 \right\}$ \\ 
+     20. &             & $\infty$   &            &
+            & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1 
+                    + \left( 1 - \delta_1 \right) x_2 \right]^{-\rho}  
+                    + \left( 1 - \delta \right) x_3^{-\rho}  \right\} ^ {-1/\rho}$ \\
 \midrule
-     21. &            &            &         & 
+         &            &            &         & 
             & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1^{-\rho_1} 

### 2015-03-18 Articles/Article_EnerEcon_2014/EconGrowth4.Rnw
Discussion of boundary models reflects new order.

@@
 Table~\ref{tab:CES_boundary_models} shows the set 
-of 20 degenerate equations found along parameter boundaries~(rows~1--20).
-Row~21 of Table~\ref{tab:CES_boundary_models} shows the generic three-factor CES equation,
+of 20 degenerate equations found along parameter boundaries~(rows~1--20),
 wherein factors of production ($x_1$,~$x_2$,~$x_3$) 
 are permutations of ($k$,~$l$,~$e$).
+The bottom (unnumbered) row of Table~\ref{tab:CES_boundary_models} 
+shows the generic three-factor CES equation.
 Each degenerate equation provides a boundary model.
@@
 Boundary models obtained when $\delta_1$ or $\delta$ is at an extreme value
-are straightforward to derive from row~21 of Table~\ref{tab:CES_boundary_models}.
+are straightforward to derive from the bottom row of Table~\ref{tab:CES_boundary_models}.
 When $\sigma_1$ or $\sigma$ is 0, 
@@
   E.g., when $\sigma_1 = 0$ and $\delta~=~1$, the Leontief model is
-  $y = \gamma A \min (x_1, x_2)$, row 3 in Table~\ref{tab:CES_boundary_models}.
+  $y = \gamma A \min (x_1, x_2)$, row 4 in Table~\ref{tab:CES_boundary_models}.
   }
@@
   $y = \gamma A \left[ \delta_1 x_1 + (1 - \delta_1) x_2 \right]$,
-  row 4 in Table~\ref{tab:CES_boundary_models}.
+  row 7 in Table~\ref{tab:CES_boundary_models}.
   }
@@
 can be estimated on that boundary using the degenerate equation.
-The top portion of Table~\ref{tab:CES_boundary_models} shows 
-two-parameter CES boundary models
-(similar to the CES model without energy in Equation~\ref{eq:CES})
-with $\delta~=~1$, $\sigma$~unknowable, and $x_3$~absent.
 If the fitted parameters in a boundary model violate constraints, 
@@
 In special cases, two boundary models will be equivalent.
-For example, boundary model~3 is identical to boundary model~1~(2)
+For example, boundary model~4 is identical to boundary model~1~(2)
 if $x_1$ is always less than (greater than) $x_2$ for all years.
@@
 the model with the lowest row number in Table~\ref{tab:CES_boundary_models} 
-is deemed the winning model,
-thereby ensuring that the simpler model is selected.
+is deemed the winning model.
 

### 2015-04-11 Articles/Presentation_ESEE_2015/ESEE 2015.Rmd
Added new file for the ESEE meeting.

---
title: "Effect of quality-adjusted production function inputs"
author: "Paul Brockway, João dos Santos, Matthew Kuperus Heun"
date: "10 April 2015"
output: pdf_document
---

```{r Setup, message=FALSE, warning=FALSE}
require(EconData)
require(EconModels)
require(dplyr)
historicalData <- filter(rbind(IST, Leeds, REXS1960), Country %in% c("UK", "PT"))
dataPT <- filter(historicalData, Country == "PT")
dataPTIST <- filter(dataPT, Source == "IST")
```

This is a study of the effects of quality-adjusted production function inputs
on the importance of energy in the production function.

# Historical Data

We use the following time series for the production functions:

## Unadjusted variables

Variable | PT       | UK    
-------- | -------- | -----------
Output   | iGDP     | iGDP
Capital  | iKstkS.L | iKstkO.WwithRD
Labor    | iL       | iL
Energy   | iXpMP    | iXp

## Quality-adjusted variables

Variable | PT         | UK    
-------- | ---------- | ---------------
Output   | iGDP       | iGDP
Capital  | iKservS.L  | iKservO.WwithRD
Labor    | ihLest     | ihLest
Energy   | iUMP       | iU

# Portugal (PT) results

## Cobb-Douglas, unadjusted inputs

```{r PT-unadj}
naturalCoef(cdModel(formula = iGDP ~ iKstkS.L + iL + iYear, 
                    data = dataPTIST, constrained = TRUE))

naturalCoef(cdModel(formula = iGDP ~ iKstkS.L + iL + iXpMP + iYear, 
                    data = dataPTIST, constrained = TRUE))
```

## Cobb-Douglas, quality-adjusted inputs

```{r PT-qadj}
naturalCoef(cdModel(formula = iGDP ~ iKservS.L + ihLest + iYear, 
                    data = dataPTIST, constrained = TRUE))

naturalCoef(cdModel(formula = iGDP ~ iKservS.L + ihLest + iUMP + iYear, 
                    data = dataPTIST, constrained = TRUE))
```

### 2015-04-12 Articles/Presentation_ESEE_2015/ESEE 2015.Rmd
Updated ESEE paper.

@@
 
-```{r Setup, message=FALSE, warning=FALSE}
+```{r Setup, message=FALSE, warning=FALSE, echo=FALSE}
 require(EconData)
@@
 require(dplyr)
-historicalData <- filter(rbind(IST, Leeds, REXS1960), Country %in% c("UK", "PT"))
-dataPT <- filter(historicalData, Country == "PT")
-dataPTIST <- filter(dataPT, Source == "IST")
+
+#####################################################
+evalCES=FALSE
+#####################################################
 ```
@@
 
-We use the following time series for the production functions:
+Historical data are stored in the `IST` and `Leeds` data sets.
+
+```{r Data}
+dataPT <- filter(IST, Country == "PT")
+dataUK <- filter(Leeds, Country == "UK")
+```
 
 ## Unadjusted variables
+
+For unadjusted variables, we use the following time series:
 
@@
 
+For quality-adjusted variables, we use the following time series:
+
 Variable | PT         | UK    
@@
 
-# Portugal (PT) results
+# Fitting
 
-## Cobb-Douglas, unadjusted inputs
+Fitting is accomplished with \emph{formulas} of the form
 
-```{r PT-unadj}
-naturalCoef(cdModel(formula = iGDP ~ iKstkS.L + iL + iYear, 
-                    data = dataPTIST, constrained = TRUE))
+$$
+y \sim x_1 + x_2 + x_3 + time,
+$$
 
+where $y$ is economic output (measured by GDP) and 
+$x_1$, $x_2$, and $x_3$ are factors of production
+and permutations of
+capital ($k$), labor ($l$), and energy ($e$).
+(The factors of production may be quality-adjusted.)
+$time$ is the time variable, usually \texttt{iYear}.
+
+# Models
+
+The Cobb-Douglas model is given as
+
+$$
+  y = \theta \: A \: x_1^{\alpha_1} \: x_2^{\alpha_2} \: x_3^{\alpha_3}; 
+      A = \mathrm{e}^{\lambda (t-t_0)}.
+$$
+
+Note that 
+`scale`   $= \theta$, 
+$\alpha_1 = \alpha$,
+$\alpha_2 = \beta$, and
+$\alpha_3 = \gamma$,
+when the `formula` is specified as \texttt{y~$\sim$~k~+~l~+~e~+~time}.
+
+The CES model is given as
+
+$$
+  y = \gamma \: A \: \left\{\delta \left[\delta_1 x_1^{-\rho_1} 
+      + (1-\delta_1)x_2^{-\rho_1} \right]^{\rho/\rho_1} 
+      + (1-\delta) x_3^{-\rho} \right\}^{-1/\rho}; 
+      A = \mathrm{e}^{\lambda (t-t_0)}.
+$$
+
+Note that `scale` $= \gamma$. 
+Equations for $\alpha_1$, $\alpha_2$, and $\alpha_3$ are given in Table \ref{tab:CES_abg_equations}.
+
+\begin{table} \caption{Equations for $\alpha$, $\beta$, and $\gamma$ for the various CES nestings, 
+                        provided that the \texttt{formula} is specified as \texttt{y~$\sim$~k~+~l~+~e~+~time}.} 
+\label{tab:CES_abg_equations} 
+  \begin{center}
+    \begin{tabular}{c c c c c} 
+      \toprule
+      Nesting    & Nest        & $\alpha_1$ ($\alpha$)                & $\alpha_2$ ($\beta$)     & $\alpha_3$ ($\gamma$)       \\
+      \midrule
+      ($kl$) + ()     & \texttt{c(1,2)}   & $\delta_1$              & $1 - \delta_1$          & 0          \\
+      ($kl$) + ($e$)  & \texttt{c(1,2,3)} & $\delta \delta_1$       & $\delta (1 - \delta_1)$ & $1 - \delta$ \\   
+      ($le$) + ($k$)  & \texttt{c(2,3,1)} & $1 - \delta$            & $\delta \delta_1$       & $\delta (1 - \delta_1)$ \\
+      ($ek$) + ($l$)  & \texttt{c(3,1,2)} & $\delta (1 - \delta_1)$ & $1 - \delta$            & $\delta \delta_1$ \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+\end{table}
+
+# Cobb-Douglas results
+
+## Unadjusted inputs
+
+```{r CD unadjusted}
 naturalCoef(cdModel(formula = iGDP ~ iKstkS.L + iL + iXpMP + iYear, 
-                    data = dataPTIST, constrained = TRUE))
+                    data = dataPT, constrained = TRUE))
+naturalCoef(cdModel(formula = iGDP ~ iKstkO.WwithRD + iL + iXp + iYear, 
+                    data = dataUK, constrained = TRUE))
 ```
 
-## Cobb-Douglas, quality-adjusted inputs
+## Quality-adjusted inputs
 
-```{r PT-qadj}
-naturalCoef(cdModel(formula = iGDP ~ iKservS.L + ihLest + iYear, 
-                    data = dataPTIST, constrained = TRUE))
+```{r CD quality adjusted}
+naturalCoef(cdModel(formula = iGDP ~ iKservS.L + ihLest + iUMP + iYear, 
+                    data = dataPT, constrained = TRUE))
+naturalCoef(cdModel(formula = iGDP ~ iKservO.WwithRD + ihLest + iU + iYear, 
+                    data = dataUK, constrained = TRUE))
+```
 
-naturalCoef(cdModel(formula = iGDP ~ iKservS.L + ihLest + iUMP + iYear, 
-                    data = dataPTIST, constrained = TRUE))
+# CES results
+
+## Unadjusted inputs
+
+```{r CES unadjusted, warning=FALSE, eval=evalCES}
+naturalCoef(cesModel(formula = iGDP ~ iKstkS.L + iL + iXpMP + iYear, 
+                     nest = c(1,2,3), data = dataPT, constrained = TRUE))
+naturalCoef(cesModel(formula = iGDP ~ iKstkO.WwithRD + iL + iXp + iYear, 
+                     nest = c(1,2,3), data = dataUK, constrained = TRUE))
 ```
+
+## Quality-adjusted inputs
+
+```{r CES quality adjusted, warning=FALSE, eval=evalCES}
+naturalCoef(cesModel(formula = iGDP ~ iKservS.L + ihLest + iUMP + iYear, 
+                    nest = c(1,2,3), data = dataPT, constrained = TRUE))
+naturalCoef(cesModel(formula = iGDP ~ iKservO.WwithRD + ihLest + iU + iYear, 
+                    nest = c(1,2,3), data = dataUK, constrained = TRUE))
+```

### 2015-04-14 Articles/Presentation_ESEE_2015/ESEE 2015.Rmd
Changes to ESEE playground.
Restructured the ESEE work around questions.

@@
 
-Fitting is accomplished with \emph{formulas} of the form
+Fitting is accomplished with `formula`s of the form
 
@@
 when the `formula` is specified as \texttt{y~$\sim$~k~+~l~+~e~+~time}.
+$\theta$ is expected to be near unity.
 
@@
 
-Note that `scale` $= \gamma$. 
+Note that `scale` $= \gamma$ and is expected to be close to unity. 
 Equations for $\alpha_1$, $\alpha_2$, and $\alpha_3$ are given in Table \ref{tab:CES_abg_equations}.
@@
 
-# Cobb-Douglas results
+# Questions
 
-## Unadjusted inputs
+## What effect does including energy and quality-adjustment have on the Solow residual in the Cobb-Douglas model?
 
-```{r CD unadjusted}
-naturalCoef(cdModel(formula = iGDP ~ iKstkS.L + iL + iXpMP + iYear, 
-                    data = dataPT, constrained = TRUE))
-naturalCoef(cdModel(formula = iGDP ~ iKstkO.WwithRD + iL + iXp + iYear, 
-                    data = dataUK, constrained = TRUE))
+First, use non-quality-adjusted data for Portugal and the Cobb-Douglas model.
+
+```{r reduce Solow residual PT unadjusted}
+ptCDunadjNoE <- cdModel(formula = iGDP ~ iKstkS.L + iL + iYear, 
+                        data = dataPT, constrained = TRUE)
+ptCDunadjWithE <- cdModel(formula = iGDP ~ iKstkS.L + iL + iXpMP + iYear, 
+                          data = dataPT, constrained = TRUE)
+naturalCoef(ptCDunadjNoE)
+naturalCoef(ptCDunadjWithE)
 ```
 
-## Quality-adjusted inputs
+The Solow residual (`lambda`) decreased from 
+`r naturalCoef(ptCDunadjNoE)$lambda` to 
+`r naturalCoef(ptCDunadjWithE)$lambda`,
+so it appears that for Portugal, 
+using unadjusted inputs and including energy as a factor of production
+reduces the Solow residual significantly.
 
-```{r CD quality adjusted}
-naturalCoef(cdModel(formula = iGDP ~ iKservS.L + ihLest + iUMP + iYear, 
-                    data = dataPT, constrained = TRUE))
-naturalCoef(cdModel(formula = iGDP ~ iKservO.WwithRD + ihLest + iU + iYear, 
-                    data = dataUK, constrained = TRUE))
+What about for quality-adjusted data and Portugal?
+
+``` {r reduce Solow residual PT adjusted}
+ptCDadjNoE <- cdModel(formula = iGDP ~ iKservS.L + ihLest + iYear, 
+                        data = dataPT, constrained = TRUE)
+ptCDadjWithE <- cdModel(formula = iGDP ~ iKservS.L + ihLest + iUMP + iYear, 
+                          data = dataPT, constrained = TRUE)
+naturalCoef(ptCDadjNoE)
+naturalCoef(ptCDadjWithE)
 ```
+
+Using quality-adjusted inputs, the Solow residual (`lambda`) moves from 
+`r naturalCoef(ptCDadjNoE)$lambda` to
+`r naturalCoef(ptCDadjWithE)$lambda`.
+
+When we look at the effect of both quality-corrected factors of production and energy,
+we see that both including energy and quality-adjusting the factors of production 
+reduce the Solow residual (`lambda`). 
+Quality-adjustment gets part of the way toward eliminating the Solow residual.
+Including energy (whether or not the factors of production are quality-adjusted)
+reduces the Solow residual significantly.
+
+Energy/Adjusted | Unadjusted                             | Quality-adjusted
+--------------- | -------------------------------------- | -----------------------------------
+Without energy  | `r naturalCoef(ptCDunadjNoE)$lambda`   | `r naturalCoef(ptCDadjNoE)$lambda`
+With energy     | `r naturalCoef(ptCDunadjWithE)$lambda` | `r naturalCoef(ptCDadjWithE)$lambda`
+
+Note that the contribution of capital (`alpha_1`)
+always decreases as energy (`alpha_3`) is allowed to play a role.
+
+What about for the UK?
+
+```{r reduce Solow residual UK}
+ukCDunadjNoE <- cdModel(formula = iGDP ~ iKstkO.WwithRD + iL + iYear, 
+                        data = dataUK, constrained = TRUE)
+ukCDunadjWithE <- cdModel(formula = iGDP ~ iKstkO.WwithRD + iL + iXp + iYear, 
+                          data = dataUK, constrained = TRUE)
+ukCDadjNoE <- cdModel(formula = iGDP ~ iKservO.WwithRD + ihLest + iYear, 
+                        data = dataUK, constrained = TRUE)
+ukCDadjWithE <- cdModel(formula = iGDP ~ iKservO.WwithRD + ihLest + iU + iYear, 
+                          data = dataUK, constrained = TRUE)
+```
+
+Energy/Adjusted | Unadjusted                             | Quality-adjusted
+--------------- | -------------------------------------- | -----------------------------------
+Without energy  | `r naturalCoef(ukCDunadjNoE)$lambda`   | `r naturalCoef(ukCDadjNoE)$lambda`
+With energy     | `r naturalCoef(ukCDunadjWithE)$lambda` | `r naturalCoef(ukCDadjWithE)$lambda`
+
+For the UK, the quality-adjusted, with energy Solow residual is 
+`r naturalCoef(ukCDadjWithE)$lambda * 100`%,
+a very small number indeed.
+For the UK, it appears that both quality-adjustment and addition of energy as a factor of production
+can effectively eliminate the Solow residual,
+reducing it to `r naturalCoef(ukCDadjWithE)$lambda`.
+
+Interestingly, the Solow residual acutally increases from 
+`r naturalCoef(ukCDunadjNoE)$lambda` to
+`r naturalCoef(ukCDunadjWithE)$lambda`
+for unadjusted factors of production when energy is added.
+To find out why, let's look at all the coefficients.
+
+``` {r}
+naturalCoef(ukCDunadjNoE)
+naturalCoef(ukCDunadjWithE)
+```
+
+When energy is included, much of the effect of capital (`alpha_1`) is 
+attributed to energy (`alpha_3`), 
+as `alpha_1` moves from 
+`r naturalCoef(ukCDunadjNoE)$alpha_1` to
+`r naturalCoef(ukCDunadjWithE)$alpha_1`.
+
+When we look at quality-adjusted inputs, we find similar results.
+
+``` {r}
+naturalCoef(ukCDadjNoE)
+naturalCoef(ukCDadjWithE)
+```
+
+`alpha_1` moves from 
+`r naturalCoef(ukCDadjNoE)$alpha_1` to
+`r naturalCoef(ukCDadjWithE)$alpha_1`.
 

### 2015-04-19 Articles/Presentation_ESEE_2015/ESEE 2015.Rmd
Minor changes.

@@
 
+For now, I've organized the analysis by questions that we would like to answer.
+
 ## What effect does including energy and quality-adjustment have on the Solow residual in the Cobb-Douglas model?
+
+We'll first look at Portugal.
+
+### Portugal
 
@@
 Note that the contribution of capital (`alpha_1`)
-always decreases as energy (`alpha_3`) is allowed to play a role.
+always decreases when energy (`alpha_3`) is included as a factor of production.
 
 What about for the UK?
+
+### United Kingdom
 

### 2015-04-22 Articles/Article_EcolEcon_2014/Paper2.Rnw
One spelling change in a comment.

@@
 lag <- 5       # Desired lag for calculations. Set to n for differences across n years.
-pad <- "tail"  # Desired padding for NA valuse
+pad <- "tail"  # Desired padding for NA values
 fd <- m_histData %>% group_by(Source, Country, energyType) %>% arrange(Year) %>% 

### 2015-04-22 Articles/Presentation_ESEE_2015/ESEE 2015.Rmd
Rearranged some of the analysis.

--- 2015-04-14 Articles/Presentation_ESEE_2015/ESEE 2015.Rmd
@@
 #####################################################
-evalCES=FALSE
+evalCES=TRUE
 #####################################################
@@
 $time$ is the time variable, usually \texttt{iYear}. 
+The \texttt{formula}s are used in a fitting function such as 
+\texttt{cdModel} to create a \texttt{model} object.
+The function \texttt{naturalCoef} extracts reasonable
+coefficients from \texttt{model} objects.
 
@@
 
+For now, I've organized the analysis around questions that we would like to answer.
+
 ## What effect does including energy and quality-adjustment have on the Solow residual in the Cobb-Douglas model?
+
+We'll first look at Portugal.
+
+### Portugal
 
@@
 
-```{r reduce Solow residual PT unadjusted}
+```{r}
 ptCDunadjNoE <- cdModel(formula = iGDP ~ iKstkS.L + iL + iYear, 
                         data = dataPT, constrained = TRUE)
+naturalCoef(ptCDunadjNoE)
+```
+
+```{r}
 ptCDunadjWithE <- cdModel(formula = iGDP ~ iKstkS.L + iL + iXpMP + iYear, 
                           data = dataPT, constrained = TRUE)
-naturalCoef(ptCDunadjNoE)
 naturalCoef(ptCDunadjWithE)
@@
 
-The Solow residual (`lambda`) decreased from 
+The Solow residual (\texttt{lambda}) is always negative. 
+However, the absolute value of \texttt{lambda} decreases from 
 `r naturalCoef(ptCDunadjNoE)$lambda` to 
-`r naturalCoef(ptCDunadjWithE)$lambda`,
-so it appears that for Portugal, 
+`r naturalCoef(ptCDunadjWithE)$lambda`
+when adding energy.
+So it appears that for Portugal, 
 using unadjusted inputs and including energy as a factor of production
-reduces the Solow residual significantly.
+reduces the absolute value of the Solow residual somewhat.
 
@@
                         data = dataPT, constrained = TRUE)
+naturalCoef(ptCDadjNoE)
+```
+
+```{r}
 ptCDadjWithE <- cdModel(formula = iGDP ~ iKservS.L + ihLest + iUMP + iYear, 
                           data = dataPT, constrained = TRUE)
-naturalCoef(ptCDadjNoE)
+
 naturalCoef(ptCDadjWithE)
@@
 `r naturalCoef(ptCDadjNoE)$lambda` to
-`r naturalCoef(ptCDadjWithE)$lambda`.
+`r naturalCoef(ptCDadjWithE)$lambda` when including energy.
+The absolute value of the Solow residual again decreases when adding energy.
+But, with quality-adjusted inputs, the effect is much stronger.
 
@@
 Note that the contribution of capital (`alpha_1`)
-always decreases as energy (`alpha_3`) is allowed to play a role.
+always shifts to energy (`alpha_3`) when energy is included 
+as a factor of production.
 
 What about for the UK?
+
+### United Kingdom
 

### 2015-04-23 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Moved LaTeX/knitr for ESEE paper.

--- 2015-01-04 Articles/Article_EcolEcon_2014/Paper2.Rnw
@@
-% This article has been prepared for publication in Ecological Economics in RStudio with knitr.
+% This article has been prepared for publication in RStudio with knitr.
 % According to http://www.elsevier.com/author-schemas/the-elsarticle-latex-document-class, we should be using the
@@
 \usepackage{microtype}  % produces hanging punctuation and beautiful type
+\usepackage{booktabs}   % for beautiful tables
 
@@
 <<setup, echo=FALSE, message=FALSE, eval=TRUE>>=
+require(EconData)
 require(EconModels)
-require(EconData)
-require(ggplot2)
 require(dplyr)
-# Provides access to data melting. 
-# See http://cran.r-project.org/web/packages/reshape2/reshape2.pdf
-require(reshape2) 
-require(knitr)
-require(mosaic)
-
-opts_chunk$set(
-  # ********************************************************
-  eval=TRUE,
-  # ********************************************************
-  # tikz allows LaTeX code in graphical output. 
-  # E.g., "$y$" for a variable name in the legend for a graph.  
-  # dev='tikz',
-  tidy=FALSE,
-  comment=NA,
-  # Tells whether to cache output from chunks are saved. Cacheing saves time. 
-  # However, references to LaTeX tables DO NOT WORK if cacheing is turned on.
-  cache=FALSE,
-  warning=FALSE,  #Tells whether to show warnings in the output.
-  # Turns off messages for all chunks. 
-  # Set TRUE on an individual chunk to see it.
-  message=FALSE, 
-  # Tells whether to echo code for all chunks. 
-  # Set TRUE on an individual chunk to see its code.
-  echo=FALSE     
-)
-@
-
-<<constants, include=FALSE, eval=TRUE>>=
-spaghettiGraphLevel <- 1.0 # Spaghetti graph bands will encompass 95% of the data.
-@
-
-<<data, include=FALSE>>=
-# Load historical data
-historicalData <- plyr::rbind.fill(REXS1960, IST, Leeds) # From the EconData package
-
-# Add some pre-econometric data
-historicalData <- transform(historicalData, KPerGDP = iK/iGDP)
-historicalData <- transform(historicalData, LPerGDP = iL/iGDP)
-historicalData <- transform(historicalData, XpPerGDP = iXp/iGDP)
-historicalData <- transform(historicalData, XfPerGDP = iXf/iGDP)
-historicalData <- transform(historicalData, UPerGDP = iU/iGDP)
-
-# The working directory is set to the directory that contains this file.
-# To reach the post-processed data, we need to move 
-# up two levels and into the data_postprocessed directory.
-# So, in each of the loadPostProcessedData calls below, we use
-# dir = "../../data_postprocessed".
-pp_path <- file.path("..", "..", "data_postprocessed")
-
-# Load coefficients from all models in one large data frame
-REXS1960_Coeffs <- loadPostProcessedData(Source = "REXS1960", kind = "coeffs", dir = pp_path)
-IST_Coeffs <- loadPostProcessedData(Source = "IST", kind = "coeffs", dir = pp_path)
-Leeds_Coeffs <- loadPostProcessedData(Source = "Leeds", kind = "coeffs", dir = pp_path)
-AllCoeffs <- rbind(REXS1960_Coeffs, IST_Coeffs, Leeds_Coeffs)
-AllCoeffs$Source <- as.factor(replace(AllCoeffs$Source, which(AllCoeffs$Source=="REXS1960"), "REXS"))
-AllCoeffs$Source <- relevelFactor(AllCoeffs$Source, levs = c("REXS", "IST", "Leeds"))
-AllCoeffs$energy <- relevelFactor(AllCoeffs$energy, levs = energyLevels)
-# Load fitted data from all models in one large data frame
-REXS1960_Fitted <- loadPostProcessedData(Source = "REXS1960", kind = "fitted", dir = pp_path)
-IST_Fitted <- loadPostProcessedData(Source = "IST", kind = "fitted", dir = pp_path)
-Leeds_Fitted <- loadPostProcessedData(Source = "Leeds", kind = "fitted", dir = pp_path)
-AllFitted <- rbind(REXS1960_Fitted, IST_Fitted, Leeds_Fitted)
-AllFitted$Source <- replace(AllFitted$Source, which(AllFitted$Source=="REXS1960"), "REXS")
-AllFitted$Source <- relevelFactor(as.factor(AllFitted$Source), levs = c("REXS", "IST", "Leeds"))
-AllFitted$energy <- relevelFactor(AllFitted$energy, levs=energyLevels)
-
-# Load models
-REXS1960_Models <- loadPostProcessedData(Source = "REXS1960", kind = "models", dir=pp_path)
-IST_Models <- loadPostProcessedData(Source = "IST", kind = "models", dir=pp_path)
-Leeds_Models <- loadPostProcessedData(Source = "Leeds", kind = "models", dir=pp_path)
-AllModels <- unlist(list(REXS1960_Models, IST_Models, Leeds_Models), recursive=FALSE)
-# The function to extract data from the models
-extract_data <- function(x, name) {
-  # Names are in the form Source.Country.modelType.factor_string
-  # Parse various pieces of name
-  name_pieces <- strsplit(name, split=".", fixed=TRUE)[[1]]
-  Source <- name_pieces[[1]]
-  Country <- name_pieces[[2]]
-  modelType <- name_pieces[[3]]
-  factorString <- name_pieces[[4]]
-  # Parse the factorString to get the energyType
-  energyType <- parseFactorString(factorString)$energyType
-
-  data.frame(year = (attr(x, which="data"))$Year, resid = resid(x), name=name, Source=Source, Country=Country,
-             modelType=modelType, factorString=factorString, 
-             nestStrParen=parseFactorString(factorString)$nestStrParen, energyType=energyType)
-}
-residual_data <- leaf_apply(AllModels, extract_data, class=c("CDEmodel", "cesEst", "LINEXmodel"))
-# Bind these all in a data frame. 
-residuals_df <- do.call(rbind, residual_data)
-# Re-order the factors as desired for our graphs.
-residuals_df$Source <- as.factor(
-  replace(as.character(residuals_df$Source), which(residuals_df$Source=="REXS1960"), "REXS"))
-residuals_df$Source <- relevelFactor(residuals_df$Source, levs = c("REXS", "IST", "Leeds"))
-residuals_df$energyType <- as.factor(
-  replace(as.character(residuals_df$energyType), which(is.na(residuals_df$energyType)), "none"))
-residuals_df$energyType <- relevelFactor(as.factor(residuals_df$energyType), levs = energyLevels)
-@
-
-% These equations are used in several locations in the paper.
-% By defining commands for them, we ensure consistent appearance
-% of the equations when they are used.
-
-% Add an argument if you want a label. Example: "\label{eq:CES}"
-\newcommand{\ceskl}[1]{\begin{equation} #1
-  y = \gamma \: A \: \left[\delta_1 k^{-\rho_1} 
-      + (1-\delta_1)l^{-\rho_1} \right]^{-1/\rho_1}; 
-      A = \mathrm{e}^{\lambda (t-t_0)}
-\end{equation}}
-
-\newcommand{\ceskle}[1]{\begin{equation} #1
-  y = \gamma \: A \: \left\{\delta \left[\delta_1 k^{-\rho_1} 
-      + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1} 
-      + (1-\delta) e^{-\rho} \right\}^{-1/\rho}; 
-      A = \mathrm{e}^{\lambda (t-t_0)}
-\end{equation}
-}
-
-\newcommand{\ceslek}[1]{\begin{equation} #1
-  y = \gamma \: A \: \left\{\delta \left[\delta_1 l^{-\rho_1} 
-      + (1-\delta_1) e^{-\rho_1} \right]^{\rho/\rho_1} 
-      + (1-\delta) k^{-\rho} \right\}^{-1/\rho}; 
-      A = \mathrm{e}^{\lambda (t-t_0)}
-\end{equation}
-}
-
-\newcommand{\cesekl}[1]{\begin{equation} #1
-  y = \gamma \: A \: \left\{\delta \left[\delta_1 e^{-\rho_1} 
-      + (1-\delta_1) k^{-\rho_1} \right]^{\rho/\rho_1} 
-      + (1-\delta) l^{-\rho} \right\}^{-1/\rho}; 
-      A = \mathrm{e}^{\lambda (t-t_0)}
-\end{equation}
-}
+
+#####################################################
+evalCES=TRUE
+#####################################################
+@
 
@@
 
-\title{Paper 2 !DRAFT! Do not circulate!}
+\title{Effect of quality-adjusted production function inputs}
 
@@
 
-% \author[BenWarr]{Benjamin Warr}
-% \author[IST]{Tiago Domingos}
-% \author[Leeds]{Paul Brockway}
-% \author[Leeds]{Julia Steinberger}
-% \author[CalvinEngr]{Matthew Kuperus Heun\corref{cor1}}
-% \ead{mkh2@calvin.edu}
-
-% \address[BenWarr]{Ben Warr's address, Zambia}
+\author[Leeds]{Paul Brockway}
+\author[IST]{Tiago Domingos}
+\author[CalvinEngr]{Matthew Kuperus Heun\corref{cor1}}
+\ead{mkh2@calvin.edu}
+
 % \address[IST]{IST, Lisbon, Portugal}
@@
 %% keywords here, in the form: keyword \sep keyword
-economic growth \sep exergy \sep energy \sep Cobb-Douglas \sep CES \sep LINEX
+economic growth \sep exergy \sep energy \sep Cobb-Douglas \sep CES
 %% MSC codes here, in the form: \MSC code \sep code
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+This is a study of the effects of quality-adjusted production function inputs
+on the importance of energy in the production function.
 
@@
 
-In this paper, we assess three prominent energy-augmented production functions 
+In this paper, we assess two prominent energy-augmented production functions 
 that appear in the literature: 
-Cobb-Douglas (CD), 
-Constant Elasticity of Substitution (CES), and 
-LINear EXponential (LINEX). 
+Cobb-Douglas (CD) and
+Constant Elasticity of Substitution (CES).
 The following subsections describe each.
@@
 Constant Elasticity of Substitution (CES) production function to 
-describe economic growth. The \texttt{R} \citep{R} package 
-\texttt{micEconCES} \citep{Henningsen:2011td} estimates CES production 
+describe economic growth. The \texttt{R} 
+% \citep{R} 
+package \texttt{micEconCES} 
+% \citep{Henningsen:2011td} 
+estimates CES production 
 functions of the following forms (among others):
 %
-\ceskl{\label{eq:CES}}
-%
-\ceskle{\label{eq:CESkle}}
-%
-Equation~\ref{eq:CES} is a CES production function with 
+\begin{equation} \label{eq:CESkl}
+  y = \gamma \: A \: \left[\delta_1 k^{-\rho_1} 
+      + (1-\delta_1)l^{-\rho_1} \right]^{-1/\rho_1}; 
+      A \equiv \mathrm{e}^{\lambda (t-t_0)}  
+\end{equation}
+%
+\begin{equation} \label{eq:CESkle}
+  y = \gamma \: A \: \left\{\delta \left[\delta_1 k^{-\rho_1} 
+      + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1} 
+      + (1-\delta) e^{-\rho} \right\}^{-1/\rho}; 
+      A \equiv \mathrm{e}^{\lambda (t-t_0)}
+\end{equation}
+%
+Equation~\ref{eq:CESkl} is a CES production function with 
 capital stock ($k$) and labor ($l$) factors of production. 
-Equation~\ref{eq:CESkle} augments Equation~\ref{eq:CES} with energy 
+Equation~\ref{eq:CESkle} augments Equation~\ref{eq:CESkl} with energy 
 using a ($kl$)($e$) nesting structure, as is typical in the literature. 
-Equation~\ref{eq:CES} is a degenerate form of Equation~\ref{eq:CESkle} 
+Equation~\ref{eq:CESkl} is a degenerate form of Equation~\ref{eq:CESkle} 
 where $\delta \rightarrow 1$.
@@
 %
-\ceslek{\label{eq:CESlek}}
-%
-\cesekl{\label{eq:CESekl}}
+\begin{equation} \label{eq:CESlek}
+  y = \gamma \: A \: \left\{\delta \left[\delta_1 l^{-\rho_1} 
+      + (1-\delta_1) e^{-\rho_1} \right]^{\rho/\rho_1} 
+      + (1-\delta) k^{-\rho} \right\}^{-1/\rho}; 
+      A \equiv \mathrm{e}^{\lambda (t-t_0)}
+\end{equation}
+%
+\begin{equation} \label{eq:CESekl}
+  y = \gamma \: A \: \left\{\delta \left[\delta_1 e^{-\rho_1} 
+      + (1-\delta_1) k^{-\rho_1} \right]^{\rho/\rho_1} 
+      + (1-\delta) l^{-\rho} \right\}^{-1/\rho}; 
+      A \equiv \mathrm{e}^{\lambda (t-t_0)}
+\end{equation}
 % 
@@
 meanings that depend upon the nesting of the factors of production.
-
-%------------------------------
-\subsubsection{LINEX Production Function} 
-\label{sec:LINEX}
-%------------------------------
-
-A third production function, the LINear EXponential (LINEX) function
-%
-\begin{equation} \label{eq:LINEX}
-  y = \theta \; \mathrm{e}^{a_0\left[2 \left(1 - \frac{1}{\rho_k} \right) 
-    + c_t \left(\vphantom{\frac{1}{\rho_k}}\rho_l - 1 \right)\right]} \; e \;,
-\end{equation}
-%
-was derived from thermodynamic considerations
-\citep{Kummel:1980wx,Kummel:1982vy,Kummel:1985vz,Kummel:1989tf,Kummel:2002tx,Kummel:2010vz}. 
-In contrast to both the Cobb-Douglas model (Equations~\ref{eq:CD} and 
-\ref{eq:CDe}) and the CES model (Equations~\ref{eq:CES}--\ref{eq:CESekl}), 
-the LINEX model (Equation~\ref{eq:LINEX}) does not include a generic, 
-time-dependent augmentation term ($A$).
-The LINEX model assumes energy ($e$) is the only factor of production.
-
-The LINEX model does, however, include terms that represent
-efficiencies among capital, labor, and energy, in the form of 
-the ratios $\rho_k$ and $\rho_l$ which are defined by\footnote{The notation
-for the LINEX model breaks from the conventions used in the Cobb-Douglas and CES
-models:  $a_0$ and $c_t$ are parameters and $\rho_k$ and $\rho_l$ are not.}
-%
-\begin{equation} \label{eq:rho_k}
-  \rho_k \equiv \frac{k}{(1/2)(l+e)}
-\end{equation}
-%
-and
-%
-\begin{equation} \label{eq:rho_l}
-  \rho_l \equiv \frac{l}{e}
-\end{equation}
-%
-and represent 
-%
-(\ref{eq:rho_k}) capital stock increase relative to the average of labor and energy (capital deepening) and 
-(\ref{eq:rho_l}) labor increase relative to energy.
-The effect of energy ($e$) on output ($y$) is enhanced if either
-%
-\begin{itemize}
-\item{capital stock ($k$) has increased more than the average 
-      of labor ($l$) and energy ($e$), i.e. if $\rho_k >$ 1, or}
-\item{labor ($l$) has increased more than energy ($e$), i.e. if $\rho_l >$ 1.}
-\end{itemize}
-%
-An economy that increases 
-capital stock ($k$) and labor ($l$) at the same rate as energy will have
-capital and labor efficiency ratios ($\rho_k$ and $\rho_l$, respectively) of unity.
-In that case, economic output ($y$) increases at the same rate as energy consumption ($e$).
-According to the LINEX model, an economy that increases 
-capital stock ($k$) without a commensurate increase in labor ($l$) 
-and energy ($e$) will experience an increase in output ($y$) in excess 
-of its increase of energy consumption ($e$), because
-\(
-\mathrm{e}^{a_0\left[2 \left(1 - \frac{1}{\rho_k} \right) 
-    + c_t \left(\vphantom{\frac{1}{\rho_k}}\rho_l - 1 \right)\right]}
-	> 1.
-\) 
-Similarly, an economy benefits by increasing labor ($l$) 
-without a commensurate increase in energy ($e$). 
-Thus, $\rho_k$ is an 
-efficiency of using additional labor and energy to make 
-additional capital stock available to the economy, 
-and $\rho_l$ is an efficiency of using additional energy to make 
-additional labor available to the economy. 
-Increases in $\rho_k$ and $\rho_l$ provide upward pressure on economic output ($y$),
-as the only factor of production ($e$) is used more efficiently.
-
-The parameter $a_0$ represents the overall importance of efficiencies $\rho_k$ and $\rho_l$, 
-and the parameter $c_t$ represents the relative importance 
-of the labor efficiency term ($\rho_l$) compared to the capital stock efficiency term ($\rho_k$). 
-Both $a_0$ and $c_t$ are assumed constant with respect to time.
 
@@
 
+UK and Portugal.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Figure~\ref{fig:Historical_Data_1} shows a graph of historical data.
-
-<<Historical_Data_1, fig.pos="H", fig.align='center', fig.width=6.6, fig.height=7, fig.cap="Historical data.">>=
-mdata <- melt(historicalData, 
-              measure.vars = c("iGDP", "iK", "iL", "iXp", "iXf", "iU"), 
-              variable.name = "variable",
-              value.name = "value")
-historicalPlot(mdata, 
-               mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
-               facet_formula = Country ~ Source, 
-               line_types = c(1,5,2,6,4,3)) + 
-  xlab("") + 
-  ylab("Indexed (1960=1 or 1970=1)")
-@
-
-Figure~\ref{fig:Historical_Data_2} shows the same data as Figure~\ref{fig:Historical_Data_1} 
-in a different form.
-
-<<Historical_Data_2, fig.pos="H", fig.align='center', fig.width=8, fig.height=7, fig.cap="Historical data.">>=
-historicalPlot(mdata, 
-               mapping=aes(x=Year, y=value, group=Source, linetype=Source), 
-               facet_formula = Country ~ variable, 
-               line_types = c(1,5,3)) + 
-  xlab("") + 
-  ylab("Indexed (1960=1 or 1970=1)")
-@
-
-Figure~\ref{fig:Preeconometric_1} shows a graph of factors of production relative to GDP.
-
-<<Preeconometric_1, fig.pos="H", fig.align='center', fig.width=8, fig.height=7, fig.cap="Pre-econometric data.">>=
-mdata2 <- melt(historicalData, 
-               measure.vars = c("KPerGDP", "LPerGDP", "XpPerGDP", "XfPerGDP", "UPerGDP"), 
-               variable.name = "variable",
-               value.name = "value")
-
-historicalPlot(mdata2, 
-               mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
-               facet_formula = Country ~ Source, 
-               line_types = c(1,5,2,6,4)) + 
-  xlab("") + 
-  ylab("Indexed Econometric Ratios (1960=1 or 1970=1)")
-@
-
-Figure~\ref{fig:Preeconometric_2} shows the same data as Figure~\ref{fig:Preeconometric_1} 
-in a different form.
-
-<<Preeconometric_2, fig.pos="H", fig.align='center', fig.width=8, fig.height=7, fig.cap="Pre-econometric data.">>=
-historicalPlot(mdata2, 
-               mapping=aes(x=Year, y=value, group=Source, linetype=Source), 
-               facet_formula = Country ~ variable, 
-               line_types = c(1,3,5)) + 
-  xlab("") + 
-  ylab("Indexed Econometric Ratios (1960=1 or 1970=1)")
-@
+Historical data are stored in the \texttt{IST} and \texttt{Leeds} data sets.
+
+<<Data, eval=TRUE>>=
+dataPT <- filter(IST, Country == "PT")
+dataUK <- filter(Leeds, Country == "UK")
+historicalData <- plyr::rbind.fill(dataPT, dataUK)
+@
+
+<<Time Series Variables>>=
+# This block of code sets up the time-series variables 
+# to be used for each country.
+# Adding this level of abstraction makes it easier 
+# for us to change variables later.
+# It also makes it easier to see what is going on 
+# in each formula throughout the document.
+# Economic output
+y_PT <- "iGDP"
+y_UK <- "iGDP"
+# Portugal undajusted inputs
+y_PT <- "iGDP"
+K_PT_unadj <- "iKstkS.L"
+L_PT_unadj <- "iL"
+E_PT_unadj <- "iXpMP"
+# Partugal quality-adjusted inputs
+K_PT_adj <- "iKservS.L"
+L_PT_adj <- "ihLest"
+E_PT_adj <- "iUMP"
+# UK unadjusted inputs
+K_UK_unadj <- "iKstkO.WwithRD"
+L_UK_unadj <- "iL"
+E_UK_unadj <- "iXp"
+# UK quality-adjusted inputs
+K_UK_adj <- "iKservO.WwithRD"
+L_UK_adj <- "ihLest"
+E_UK_adj <- "iU"
+# Time variables
+time_PT <- "iYear"
+time_UK <- "iYear"
+@
+
+<<Formulas, echo=FALSE>>=
+# Set up the formulas for each type of analysis.
+# To do this, use the substitute function.
+
+# response <- "iGDP"
+# # Portugal undajusted inputs
+# capital <- "iKstkS.L"
+# labor <- "iL"
+# time <- "iYear"
+# 
+# formula <- substitute( response ~ capital + labor + time,
+#                        list( response = substitute(response),
+#                              capital = substitute(capital),
+#                              labor = substitute(labor),
+#                              time = substitute(time)
+#                        )
+# )
+# formula
+# 
+# 
+# 
+# f_PT_unadj_woe <- substitute(y ~ k + l + t, list(y = y_PT,
+#                                                  k = K_PT_unadj,
+#                                                  l = L_PT_unadj,
+#                                                  t = time_PT))
+# y_PT
+# substitute(y_PT)
+# eval(y_PT)
+# f_PT_unadj_woe
+@
+
+For unadjusted variables, we use the time series shown in Table~\ref{tab:unadjusted_variables}.
+
+\begin{table} \caption{Unadjusted variables.} 
+\label{tab:unadjusted_variables} 
+  \begin{center}
+    \begin{tabular}{r l l} 
+      \toprule
+      Variable    & Portugal           & UK                 \\
+      \midrule
+      Output      & \Sexpr{y_PT}       & \Sexpr{y_UK}       \\
+      Capital     & \Sexpr{K_PT_unadj} & \Sexpr{K_UK_unadj} \\
+      Labor       & \Sexpr{L_PT_unadj} & \Sexpr{L_UK_unadj} \\
+      Energy      & \Sexpr{E_PT_unadj} & \Sexpr{E_UK_unadj} \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+\end{table}
+
+For quality-adjusted variables, we use the time series shown in Table~\ref{tab:quality_adjusted_variables}.
+
+\begin{table} \caption{Unadjusted variables.} 
+\label{tab:quality_adjusted_variables} 
+  \begin{center}
+    \begin{tabular}{r l l} 
+      \toprule
+      Variable    & Portugal         & UK               \\
+      \midrule
+      Output      & \Sexpr{y_PT}     & \Sexpr{y_UK}     \\
+      Capital     & \Sexpr{K_PT_adj} & \Sexpr{K_UK_adj} \\
+      Labor       & \Sexpr{L_PT_adj} & \Sexpr{L_UK_adj} \\
+      Energy      & \Sexpr{E_PT_adj} & \Sexpr{E_UK_adj} \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+\end{table}
 
@@
 \section{Parameter Estimation}
-\label{sec:Parameter_Estimation}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%++++++++++++++++++++++++++++++
-\subsection{Point Estimates}
-%++++++++++++++++++++++++++++++
-
-Each of the economic growth models discussed in 
-Section~\ref{sec:Prod_Func_Forms} has parameters which must be estimated (fitted)
-using data for each economy (see Sections~\ref{sec:Economies} and~\ref{sec:Sources_of_Data}).
-We obtained parameter estimates by applying the method of least-squares to 
-log-transformed data using the \texttt{R} \citep{R} functions
-\texttt{lm} (for Cobb-Douglas and LINEX models) 
-and \texttt{cesEst} \citep{Henningsen:2011td} (for CES models).
-
-Although the details vary from model to model, each of our three models has the general form
-%
-\begin{equation}
-  y = f(t,k,l,e; \theta) + \mathrm{error} \;,
-\end{equation}
-%
-where $\theta$ is a vector of parameters for the function $f$.
-Parameter estimates are chosen to minimize
-%
-\begin{equation} \label{eq:sse}
-  sse = \sum_{i} (y_i - f(t,k,l,e; \theta) )^2
-\end{equation}
-%
-within constraints.
-For the optimal parameter values $\hat \theta$, we define the 
-fitted response by
-\[
-\hat y_i = f(t_i, k_i, l_i, e_i; \hat \theta)
-\]
-and the residuals ($r_i$)
-as the difference between the observed response and the fitted response
-%
-\begin{equation} \label{eq:residual}
-  r_i 
-  = y_i - \hat y_i
-  = y_i - f(t,k,l,e; \hat\theta)
-\end{equation}
-%
-The details for each of the models are discussed in 
-Sections~\ref{sec:CD_Parameter_Estimation}--\ref{sec:LINEX_Parameter_Estimation} below.
-
-%++++++++++++++++++++++++++++++
-\subsection{Resampling Methods}
-\label{sec:Resampling}
-%++++++++++++++++++++++++++++++
-
-Bootstrapping is a statistical resampling technique for assigning
-measures of accuracy and precision to sample estimates by measuring
-properties of an estimator when sampling from a resampling
-distribution.  
-Resampling distributions can be formed in a number of 
-ways in accordance with the type of data, experimental design,
-and modeling assumptions involved.  
-In each case, many new resamples 
-are created, each of which is a randomized version of the original sample data to 
-which the desired analysis method can be applied.  
-By investigating, for example,
-the variability of a parameter estimate from one resample to another,
-one can learn about the precision of the estimation method.
-
-In the context of linear models (regression), resamples are generally created
-by residual resampling.  
-In our case, we formed resamples by adding to the fitted 
-response ($\hat{y}$) the product of a residual from the original model fit and 
-random sign ($-1$ or $1$, each with probability $0.5$).  
-For the case of Cobb-Douglas and LINEX models, 
-this residual resampling occurs on the 
-log-transformed data.
-
-Intuitively, this method assumes that the residuals are indicative of 
-the variability (from many potential sources) inherent in the data such that
-it would be unsurprising if the residual from 
-any particular year had been observed in a different year. 
-Thus, a resampled response $\tilde Y'$ can be computed as 
-%
-\begin{equation} \label{eq:Y_tilde}
-  \tilde Y_i' = \hat y_i \pm r_j \; ,
-\end{equation}
-%
-where 
-%
-\begin{equation}
-  r_i = y_i - \hat y_i \; .
-\end{equation}
-%
-In Equation~\ref{eq:Y_tilde}, both the sign ($\pm$) 
-and the index ($j$,~typically different from $i$) 
-of the residual ($r$) 
-are chosen at random (with replacement). 
-We repeated the resampling process 1000 times for each
-combination of growth model, country, and data source, 
-both with and without energy as appropriate.
-
-The coefficients from the fit to a resampled time series
-(the ``resample coefficients'') will be different from the coefficients 
-obtained from the fit to historical data (the ``base coefficients'').
-When these resample coefficients are highly variable, 
-it is an indication
-that the data do not determine the parameter estimates very precisely.
-Lack of precision can stem from a number of factors, most obviously
-a poor model fit, low model sensitivity to one or more parameters, 
-or correlations between parameter estimates.
-
-It is important to note that large residuals can arise from either
-(a) poor quality historical time series data, or 
-(b) a mathematical model that does not describe the underlying phenomena well.
-It is also important to note that (c) even when the residuals are small and the 
-model produces fitted values that track the observed data closely, it may
-yet be difficult to estimate some or all of the model parameters precisely.
-The resampling method employed herein reflects all three of these potential 
-sources of uncertainty in parameter estimates.
-
-%++++++++++++++++++++++++++++++
-\subsection{Cobb-Douglas Models}
-\label{sec:CD_Parameter_Estimation}
-%++++++++++++++++++++++++++++++
-
-The Cobb-Douglas model without energy is given by 
-Equation~\ref{eq:CD}. Equation~\ref{eq:CD} was
-reparameterized as
-%
-\begin{equation} \label{eq:CD_reparam}
-  y = \theta \mathrm{e}^{\lambda (t-t_0)} k^{\alpha} l^{1-\alpha}
-\end{equation}
-%
-to ensure $\alpha + \beta = 1$ for constant returns to scale. 
-$\theta$, $\lambda$, and $\alpha$ were estimated by the 
-\texttt{R} \citep{R} function \texttt{lm} in log-transform space. 
-If the estimated value for $\alpha$ was found outside the interval $[0,1]$, 
-we set $\alpha$ to its boundary value and re-estimated $\lambda$. 
-The value of $\beta$ was found with $\beta = 1 - \alpha$.
-
-To estimate the parameters $\theta$, $\lambda$, $\alpha$, $\beta$, and $\gamma$ 
-in the energy-augmented Cobb-Douglas model, Equation~\ref{eq:CDe} 
-was reparameterized as
-%
-\begin{equation} \label{eq:CDe_AB_reparam}
-  y = \theta \mathrm{e}^{\lambda (t-t_0)} k^{\alpha} l^{\beta} e^{1 - \alpha - \beta}
-\end{equation}
-%
-ensuring that $\alpha + \beta + \gamma = 1$,
-thereby providing constant returns to scale.
-The \texttt{R} \citep{R} function \texttt{lm} was used to estimate 
-values of $\lambda$, $\theta$, $\alpha$, and $\beta$ in log-transform space.
-If the fitted value for $\alpha$ or $\beta$ fell outside the interval $[0,1]$,
-we fit along all boundaries 
-($\alpha = 1$,
-$\beta = 1$,
-$\gamma = 1$,
-$\alpha = 0$,
-$\beta = 0$, and
-$\gamma = 0$)
-and chose the boundary fit with
-minimum $sse$ (Equation~\ref{eq:sse}) as the winner.
-$\gamma$ was recovered with $\gamma = 1 - \alpha - \beta$.
-
-Figure~\ref{fig:CD_Ternary_Scatter_Graph} shows ternary plots 
-for $\alpha$, $\beta$, and $\gamma$ parameter values 
-for Cobb-Douglas (without and with energy) resample models.
-Each reample is shown as a gray dot on the graph. 
-The fit to historical data is shown as a gray crosshairs.
-
-<<CD_lambda_theta_graph, fig.pos="H", fig.align='center', fig.width=6, fig.height=5.5, fig.cap="$\\lambda$ and $\\theta$ values for Cobb-Douglas resample models.">>=
-cdCoeffsData <- filter(AllCoeffs, model=="cd")
-standardScatterPlot(data=cdCoeffsData, mapping=aes(x=scale, y=lambda, color=Source), 
-                    facet_formula=country~energy, alpha=0.05) +
-    scale_x_continuous(limits=c(0.9, 1.5), breaks=c(1.0, 1.2, 1.4)) +
-    scale_y_continuous(limits=c(-0.02, 0.05), breaks=c(0.0, 0.025, 0.05)) +    
-    labs(x=expression(theta), y=expression(lambda)) +
-    guides(colour=guide_legend(override.aes = aes(alpha=1))) #+
-#     geom_density2d()
-@
-
-<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=6, fig.height=5, fig.cap="Cobb-Douglas resample model parameters.">>=
-standardTriPlot(data=cdCoeffsData, 
-                mapping=aes(color=Source),
-                facet_formula=country~energy) +
-    guides(colour=guide_legend(override.aes = aes(alpha=1)))
-@
-
-<<CD_finite_diff_calcs, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap='Solow residual time series.'>>=
-# Add a bogus "none" column that we can use for the no-energy case
-m_histData <- historicalData
-m_histData$none <- 1.0
-# Melt the the historical data to put energy in one column
-m_histData <- melt(select(m_histData, Year, iGDP, iK, iL, iXp, iXf, iU, none, Country, Source), 
-                   measure.vars = c("none", "iXp", "iXf", "iU"),
-                   variable.name = "energyType",
-                   value.name = "iE")
-# Calculate finite difference approximations of time derivatives for output and all factors of production
-lag <- 5       # Desired lag for calculations. Set to n for differences across n years.
-pad <- "tail"  # Desired padding for NA valuse
-fd <- m_histData %>% group_by(Source, Country, energyType) %>% arrange(Year) %>% 
-  mutate(dydt = ediff(iGDP, pad=pad, lag=lag) / ediff(Year, pad=pad, lag=lag)) %>%
-  mutate(dkdt = ediff(iK, pad=pad,   lag=lag) / ediff(Year, pad=pad, lag=lag)) %>%
-  mutate(dldt = ediff(iL, pad=pad,   lag=lag) / ediff(Year, pad=pad, lag=lag)) %>%
-  mutate(dedt = ediff(iE, pad=pad,   lag=lag) / ediff(Year, pad=pad, lag=lag))
-
-origCDKLCoeffs <- filter(AllCoeffs, method=="orig", model=="cd")
-origCDKLCoeffs <- origCDKLCoeffs %>% select(method, country, Source, nestStr, energy, lambda, alpha, beta, gamma)
-# Change name of Source REXS to REXS1960 and relevel to conform to information in fdlambda.
-origCDKLCoeffs$Source <- as.character(origCDKLCoeffs$Source)
-origCDKLCoeffs$Source <- replace(origCDKLCoeffs$Source, which(origCDKLCoeffs$Source=="REXS"), "REXS1960")
-origCDKLCoeffs$Source <- as.factor(origCDKLCoeffs$Source)
-origCDKLCoeffs$Source <- relevelFactor(origCDKLCoeffs$Source, levs = c("REXS1960", "IST", "Leeds"))
-
-# Fill new columns in the fd data frame with 
-# lambda, alpha, beta, and gamma values from the parameter estimation process.
-# lambda, alpha, beta, and gamma values for the orig fits are in the origCDKLCoeffs data frame.
-# Using the hint at 
-# http://stackoverflow.com/questions/15059076/
-# r-how-to-call-apply-like-function-on-each-row-of-dataframe-with-multiple-argum
-labg <- apply(fd[ , c('Country', 'Source', 'energyType')], 1, function(x){
-    row <- as.data.frame(filter(origCDKLCoeffs, 
-                                country==x["Country"], Source==x["Source"], energy==x["energyType"]))
-    abg <- subset(row, select=c(lambda, alpha, beta, gamma))
-    if (nrow(abg) < 1){ abg[1, ] <- NA }
-    return(abg)
-  })
-cols <- do.call(rbind, labg)
-fd <- cbind(fd, cols)
-
-# Now calculate lambda by finite difference for every year to make a time series
-fdlambda <- mutate(fd, lambda_diff = dydt/iGDP - (alpha/iK*dkdt + beta/iL*dldt + gamma/iE*dedt))
-
-# Calculate the fraction of GDP growth in each year that is explained by the solow residual
-fdlambda <- mutate(fdlambda, solowFrac = lambda_diff / (dydt/iGDP))
-
-# Calculate average values for lambda and solowFrac
-avgs <- fdlambda %>% 
-  group_by(Source, Country, energyType) %>% 
-  summarise(
-    avg.lambda_diff = mean(lambda_diff, na.rm=TRUE),
-    avg.solowFrac = mean(solowFrac, na.rm=TRUE)
-    )
-
-@
-
-Given the estimates for $\alpha$, $\beta$, and $\gamma$ for the Cobb-Douglas model,
-we can estimate values for $\lambda$ by $\lambda_{i,j}$,
-with $i$ and $j$ in Equation~\ref{eq:lambdaij} separated by \Sexpr{lag} years.
-The results are shown in Figure~\ref{fig:CD_lambda_time_series}.
-Note that data spanning years~$i \rightarrow j$ is plotted at year~$i$.
-
-<<CD_lambda_time_series, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap='Solow residual time series.'>>=
-# Create a time series graph of the lambda_diff values
-ggplot(data=fdlambda, aes(x=Year, y=lambda_diff, color=Source)) + 
-  geom_point(size = 1.0) +
-  facet_grid(Country ~ energyType) +
-  labs(x = "", y = expression(lambda)) + 
-#   scale_y_continuous(limits=c(-0.1, 0.1)) +
-  xy_theme()
-@
-
-We can also estimate values for 
-the fraction~($f$) of economic growth explained by the Solow residual
-by $f_{ij}$
-with $i$ and $j$ in Equation~\ref{eq:f_finite_diff_2} separated by \Sexpr{lag} years.
-The results are shown in Figure~\ref{fig:CD_solowPerc_time_series}. 
-Note that data spanning years~$i \rightarrow j$ is plotted at year~$i$.
-
-<<CD_solowPerc_time_series, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap='Fraction of GDP growth explained by Solow residual.'>>=
-# Create a time series graph of the solowPerc values
-ggplot(data=fdlambda, aes(x=Year, y=solowFrac, color=Source)) + 
-  geom_point(size = 1.0) +
-  facet_grid(Country ~ energyType) +
-  labs(x = "", y = "f") + 
-  scale_y_continuous(limits=c(-0.5, 2)) +
-  xy_theme()
-@
-
-Figures~\ref{fig:CD_GDP_Spaghetti_Graphs_US}--\ref{fig:CD_GDP_Spaghetti_Graphs_CN} 
-compare predictions 
-from the Cobb-Douglas models 
-(without and with energy) to historical data.
-Historical data are shown as a black line. 
-The fit to historical data is shown as a white line.
-The gray band encompasses \Sexpr{spaghettiGraphLevel*100}\% of the fits to resampled data.
-
-<<CD_GDP_Spaghetti_Graphs_US, fig.pos="H", fig.align='center', fig.width=4, fig.height=3.5, fig.cap="US Cobb-Douglas fitted models.">>=
-# Use this result several times later. Saves lots of time doing it this way.
-cdFittedData <- filter(AllFitted, model=="cd")
-
-cdFittedDataUS <- filter(cdFittedData, Country=="US")
-spaghettiPlot(data=cdFittedDataUS, facet_formula=Source~energy, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<CD_GDP_Spaghetti_Graphs_UK, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="UK Cobb-Douglas fitted models.">>=
-cdFittedDataUK <- filter(cdFittedData, Country=="UK")
-spaghettiPlot(data=cdFittedDataUK, facet_formula=Source~energy, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<CD_GDP_Spaghetti_Graphs_JP, fig.pos="H", fig.align='center', fig.width=4, fig.height=2, fig.cap="JP Cobb-Douglas fitted models.">>=
-cdFittedDataJP <- filter(cdFittedData, Country=="JP")
-spaghettiPlot(data=cdFittedDataJP, facet_formula=Source~energy, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<CD_GDP_Spaghetti_Graphs_AT, fig.pos="H", fig.align='center', fig.width=5, fig.height=3.5, fig.cap="AT Cobb-Douglas fitted models.">>=
-cdFittedDataAT <- filter(cdFittedData, Country=="AT")
-spaghettiPlot(data=cdFittedDataAT, facet_formula=Source~energy, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<CD_GDP_Spaghetti_Graphs_PT, fig.pos="H", fig.align='center', fig.width=5, fig.height=2, fig.cap="PT Cobb-Douglas fitted models.">>=
-cdFittedDataPT <- filter(cdFittedData, Country=="PT")
-spaghettiPlot(data=cdFittedDataPT, facet_formula=Source~energy, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<CD_GDP_Spaghetti_Graphs_CN, fig.pos="H", fig.align='center', fig.width=4, fig.height=2, fig.cap="CN Cobb-Douglas fitted models.">>=
-cdFittedDataCN <- filter(cdFittedData, Country=="CN")
-spaghettiPlot(data=cdFittedDataCN, facet_formula=Source~energy, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<CD_Residual_Plot, fig.pos="H", fig.align='center', fig.width=6, fig.height=6, fig.cap="Cobb-Douglas Residual Plots.">>=
-# Use residuals_df to make a graph.
-cd_residuals_df <- filter(residuals_df, modelType=="cd")
-ggplot(data=cd_residuals_df, aes(x=year, y=resid, color=Source)) + 
-  geom_point(size = 1.0) +
-  facet_grid(Country ~ energyType) +
-  labs(x = "", y = "Residuals") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000)) + 
-  xy_theme()
-@
-
-%++++++++++++++++++++++++++++++
-\subsection{CES Models}
-\label{sec:CES_Parameter_Estimation}
-%++++++++++++++++++++++++++++++
-
-The CES model without and with energy is given by 
-Equations~\ref{eq:CES}--\ref{eq:CESekl}. 
-The \texttt{R} \citep{R} package \texttt{micEconCES} 
-\citep{Henningsen:2011td} was used to estimate parameters 
-$\lambda$, $\gamma$, $\delta$, $\delta_1$, $\rho$, and $\rho_1$. 
-The \texttt{cesEst} function of \texttt{micEconCES} provides 
-several algorithm options for parameter estimation.
-The default algorithm (Levenberg-Marquardt) does not respect
-parameter constraints (see Section~\ref{sec:CES}) and, 
-in our testing, nearly always violated them, often returning
-negative values for elasticity of substitution~($\sigma$) parameters.
-Thus, we used the two fitting algorithms available in \texttt{cesEst} that
-respect coefficient constraints: \texttt{PORT} and \texttt{L-BFGS-B}.
-
-Our CES parameter estimation algorithm starts with an eleven-value grid search
-in $\rho$ and $\rho_1$ (9, 2, 1, 0.43, 0.25, 0.1, -0.1, -0.5, -0.75, -0.9, -0.99),
-which corresponds to $\sigma$ and $\sigma_1$ values of
-0.1, 0.33, 0.5, 0.7, 0.8, 0.9, 1.11, 2, 4, 10, and 100, respectively.
-During the grid search, values of $\rho$ and $\rho_1$ are fixed,
-and values of $\lambda$, $\gamma$, $\delta$, and $\delta_1$ are estimated 
-by gradient search with the \texttt{PORT} and \texttt{L-BFGS-B} algorithms.
-In all, 121 gradient searches in $\lambda$, $\gamma$, $\delta$, and $\delta_1$
-at grid points representing all combinations of $\rho$ and $\rho_1$ are attempted.
-During the grid search portion of our algorithm, starting values for the free parameters
-are $\lambda$ = 0.015/year, $\delta$ = 0.5, $\delta_1$ = 0.5, 
-and $\gamma$ is set to a value such that the mean of the residuals is zero
-by the \texttt{cesEst} function.
-
-Next, a gradient search (using both \texttt{PORT} and \texttt{L-BFGS-B}) 
-is attempted wherein all fitting parameters 
-($\lambda$, $\gamma$, $\delta$, $\delta_1$, $\rho$, and $\rho_1$)
-are allowed to float. 
-The start values for fitting parameters are taken from 
-the grid search fit that provided the lowest $sse$ (Equation~\ref{eq:sse}).
-
-If resampled data are being fitted, a prior fit to historical data is available.
-In the final step of our algorithm, 
-a gradient search (using both \texttt{PORT} and \texttt{L-BFGS-B})
-uses coefficients from the best 
-fit to historical data as its starting point. 
-In this final gradient search, all model parameters 
-($\lambda$, $\gamma$, $\delta$, $\delta_1$, $\rho$, and $\rho_1$)
-are considered free parameters.
-
-The fit with lowest $sse$ of all above trials is deemed the winner,
-and its fitting parameters are used as the model.
-
-\citet{Henningsen:2011td}, 
-in their detailed analysis of \citet{Kemfert:1998vd}, found that
-
-\begin{quote}
-\ldots the Levenberg-Marquardt and the \texttt{PORT} algorithms 
-are---at least in this study---most likely to find the 
-coefficients that give the best fit to the model, 
-where the \texttt{PORT} algorithm can be used to restrict the estimates 
-to the economically meaningful region.
-\end{quote}
-
-In our testing, we found that to be mostly true. 
-\texttt{PORT} nearly always provided lower
-$sse$ than \texttt{L-BFGS-B}, despite the fact that 
-\texttt{L-BFGS-B} often reports convergence
-and \texttt{PORT} does not for the same data
-(i.e., for the same $y$, $k$, $l$, and $e$ data).
-
-Coefficients for each resampled CES model for all countries and all nests
-are shown in 
-Figures~\ref{fig:CES_lambda_gamma_graph_Xp}--\ref{fig:CES_sigma_delta_graph_Xp}. 
-The white crosshair on each graph shows the location 
-of the fit to historical data. 
-In Figures~\ref{fig:CES_sigma1_delta1_graph_Xp} and~\ref{fig:CES_sigma_delta_graph_Xp},
-the bottom of the vertical axis represents $\sigma = 0$.
-The top of the vertical axis represents $\sigma = \infty$.
-
-Note that as $\delta$ or $\delta_1$ approaches 0 (1) 
-in Equations~\ref{eq:CES}--\ref{eq:CESekl},
-the corresponding value of $\sigma$ or $\sigma_1$ becomes irrelevant, and
-resample points along the left (right) edge of
-Figures \ref{fig:CES_sigma1_delta1_graph_Xp} and \ref{fig:CES_sigma_delta_graph_Xp}
-are equivalent.
-That is, all points along the left (right) edge of
-Figures \ref{fig:CES_sigma1_delta1_graph_Xp} and \ref{fig:CES_sigma_delta_graph_Xp}
-have the same $sse$. 
-As a consequence, 
-the \texttt{cesEst} fitting algorithm has no way 
-to discriminate among points along the left (right) edge of
-Figures \ref{fig:CES_sigma1_delta1_graph_Xp} and \ref{fig:CES_sigma_delta_graph_Xp}. 
-Thus, resample point estimates where $\delta$ or $\delta_1$ approaches 0 (1)
-tend to cluster at the locations of the initial grid search in 
-$\sigma$ or $\sigma_1$
-(0.1, 0.33, 0.5, 0.7, 0.8, 0.9, 1.11, 2, 4, 10, and 100).
-
-%------------------------------
-\subsubsection{CES with primary exergy ($x_p$)} 
-\label{sec:ces_xp}
-%------------------------------
-
-The following graphs show results for the CES model using primary exergy ($x_p$).
-
-<<CES_lambda_gamma_graph_Xp, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6.0, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with primary exergy ($x_p$).">>=
-cesCoeffsDataXp <- filter(AllCoeffs, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
-                                                                      "(iK + iL) + (iXp)", 
-                                                                      "(iL + iXp) + (iK)", 
-                                                                      "(iXp + iK) + (iL)"))
-standardScatterPlot(data=cesCoeffsDataXp, mapping=aes(x=gamma_coef, y=lambda, color=Source), 
-                    facet_formula=country~nestStrParen, alpha=0.05) +
-    scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
-    labs(x=expression(gamma), y=expression(lambda)) + 
-    guides(colour=guide_legend(override.aes = aes(alpha=1)))
-@
-
-<<CES_sigma1_delta1_graph_Xp, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6.5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with primary exergy ($x_p$).">>=
-standardScatterPlot(data=cesCoeffsDataXp, mapping=aes(x=delta_1, y=sigma_1, color=Source), 
-                    facet_formula=country~nestStrParen, alpha=0.05) +
-    coord_trans(y="sigma") +
-    scale_x_continuous(breaks=c(0, 0.5, 1.0)) +
-    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-    labs(x=expression(delta[1]), y=expression(sigma[1])) + 
-    guides(colour=guide_legend(override.aes = aes(alpha=1)))
-@
-
-<<CES_sigma_delta_graph_Xp, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=6, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models using primary exergy ($x_p$).">>=
-standardScatterPlot(data=filter(cesCoeffsDataXp, nestStrParen != "(iK + iL) + ()"),
-                    mapping=aes(x=delta, y=sigma, color=Source), 
-                    facet_formula=country~nestStrParen, alpha=0.05) +
-    coord_trans(y="sigma") +
-    scale_x_continuous(breaks=c(0, 0.5, 1.0)) +
-    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-    labs(x=expression(delta), y=expression(sigma)) +
-    guides(colour=guide_legend(override.aes = aes(alpha=1)))
-@
-
-We can develop pseudo $\alpha$, $\beta$, and $\gamma$ parameters 
-for the CES model, based on values of $\delta$ and $\delta_1$.
-Table~\ref{tab:CES_abg_equations} shows the permuted equations for each CES nesting.
-
-\begin{table} \caption{Equations for $\alpha$, $\beta$, and $\gamma$ for the various CES nestings.} 
+\label{sec:parameter_estimation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Parameter estimation is accomplished with \texttt{formula}s of the form
+%
+\begin{equation} \label{eq:formulas}
+  y \sim x_1 + x_2 + x_3 + time,
+\end{equation}
+%
+where $y$ is economic output and 
+$x_1$, $x_2$, and $x_3$ are factors of production
+and permutations of
+capital ($k$), labor ($l$), and energy ($e$).
+(The factors of production may be quality-adjusted.)
+$time$ is the time variable, usually \texttt{iYear}. 
+The \texttt{formula}s are used in a fitting function such as 
+\texttt{cdModel} to create a \texttt{model} object.
+The function \texttt{naturalCoef} extracts reasonable
+coefficients from \texttt{model} objects.
+
+Note that in the fitting process for the Cobb-Douglas equation,
+$\texttt{scale} = \theta$, 
+$\alpha_1 = \alpha$,
+$\alpha_2 = \beta$, and
+$\alpha_3 = \gamma$,
+when the \texttt{formula} is specified as 
+%
+\begin{equation} \label{eq:formula_kle}
+  \texttt{y} \sim \texttt{k + l + e + time}.
+\end{equation}
+%
+$\theta$ is expected to be near unity.
+
+Note that for the CES model, $\texttt{scale} = \gamma$ and is expected to be close to unity. 
+Equations for $\alpha_1$, $\alpha_2$, and $\alpha_3$ are given in Table \ref{tab:CES_abg_equations}.
+
+\begin{table} \caption{Equations for $\alpha$, $\beta$, and $\gamma$ for the various CES nestings, 
+                        provided that the \texttt{formula} is specified as \texttt{y~$\sim$~k~+~l~+~e~+~time}.} 
 \label{tab:CES_abg_equations} 
@@
     \begin{tabular}{c c c c c} 
-      Nesting    & Equation        & $\alpha$                & $\beta$                 & $\gamma$                \\
-      \hline
-      ($kl$)     & \ref{eq:CES}    & $\delta_1$              & $1 - \delta_1$          & 0                       \\
-      ($kl$)$e$  & \ref{eq:CESkle} & $\delta \delta_1$       & $\delta (1 - \delta_1)$ & $1 - \delta$            \\   
-      ($le$)$k$  & \ref{eq:CESlek} & $1 - \delta$            & $\delta \delta_1$       & $\delta (1 - \delta_1)$ \\
-      ($ek$)$l$  & \ref{eq:CESekl} & $\delta (1 - \delta_1)$ & $1 - \delta$            & $\delta \delta_1$       \\
+      \toprule
+      Nesting         & \texttt{nest}     & $\alpha_1$ ($\alpha$)   & $\alpha_2$ ($\beta$)    & $\alpha_3$ ($\gamma$)       \\
+      \midrule
+      ($kl$) + ()     & \texttt{c(1,2)}   & $\delta_1$              & $1 - \delta_1$          & 0          \\
+      ($kl$) + ($e$)  & \texttt{c(1,2,3)} & $\delta \delta_1$       & $\delta (1 - \delta_1)$ & $1 - \delta$ \\   
+      ($le$) + ($k$)  & \texttt{c(2,3,1)} & $1 - \delta$            & $\delta \delta_1$       & $\delta (1 - \delta_1)$ \\
+      ($ek$) + ($l$)  & \texttt{c(3,1,2)} & $\delta (1 - \delta_1)$ & $1 - \delta$            & $\delta \delta_1$ \\
+      \bottomrule
     \end{tabular}
@@
 
-Figure~\ref{fig:CES_ternary_graphXp} shows 
-$\alpha$, $\beta$, and $\gamma$ parameters for the CES model for all nests and countries.
-Figure~\ref{fig:CES_ternary_graphXp} is comparable to
-the ternary graph for the Cobb-Douglas models, 
-Figure~\ref{fig:CD_Ternary_Scatter_Graph}.
-
-<<CES_ternary_graphXp, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models with primary exergy ($x_p$).", eval=TRUE>>=
-standardTriPlot(data=cesCoeffsDataXp, 
-                mapping=aes(color=Source), 
-                facet_formula=country~nestStrParen) +
-  guides(colour=guide_legend(override.aes = aes(alpha=1)))
-@
-
-Figures~\ref{fig:CES_GDP_Spaghetti_Graph_US_xp}--\ref{fig:CES_GDP_Spaghetti_Graph_CN_xp} 
-compare CES model predictions 
-to historical data for all nestings, countries, and data sources. 
-As with the Cobb-Douglas results, 
-historical data are shown as a black line, 
-the fit to historical data is shown as a white line, and 
-the gray band encompasses \Sexpr{spaghettiGraphLevel*100}\% of the fits to resampled data.
-
-<<CES_GDP_Spaghetti_Graph_US_xp, fig.pos="H", fig.align='center', fig.width=5, fig.height=3.5, fig.cap="US CES with $x_p$ fitted models.">>=
-# Use this result later. Do it once to speed things up.
-cesFittedData_xp <- filter(AllFitted, model=="ces", energy %in% c("iXp", "none"))
-
-cesFittedDataUS_xp <- filter(cesFittedData_xp, Country=="US")
-spaghettiPlot(data=cesFittedDataUS_xp, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<CES_GDP_Spaghetti_Graph_UK_xp, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="UK CES with $x_p$ fitted models.">>=
-cesFittedDataUK_xp <- filter(cesFittedData_xp, Country=="UK")
-spaghettiPlot(data=cesFittedDataUK_xp, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<CES_GDP_Spaghetti_Graph_JP_xp, fig.pos="H", fig.align='center', fig.width=5, fig.height=2.5, fig.cap="JP CES with $x_p$ fitted models.">>=
-cdFittedDataJP_xp <- filter(cesFittedData_xp, Country=="JP")
-spaghettiPlot(data=cdFittedDataJP_xp, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<CES_GDP_Spaghetti_Graph_AT_xp, fig.pos="H", fig.align='center', fig.width=5, fig.height=3.5, fig.cap="AT CES with $x_p$ fitted models.">>=
-cdFittedDataAT_xp <- filter(cesFittedData_xp, Country=="AT")
-spaghettiPlot(data=cdFittedDataAT_xp, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<CES_GDP_Spaghetti_Graph_PT_xp, fig.pos="H", fig.align='center', fig.width=5, fig.height=2.5, fig.cap="PT CES with $x_p$ fitted models.">>=
-cdFittedDataPT_xp <- filter(cesFittedData_xp, Country=="PT")
-spaghettiPlot(data=cdFittedDataPT_xp, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<CES_GDP_Spaghetti_Graph_CN_xp, fig.pos="H", fig.align='center', fig.width=5, fig.height=2.5, fig.cap="CN CES with $x_p$ fitted models.">>=
-cdFittedDataCN_xp <- filter(cesFittedData_xp, Country=="CN")
-spaghettiPlot(data=cdFittedDataCN_xp, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<CES_Residual_Plot_xp, fig.pos="H", fig.align='center', fig.width=6, fig.height=6, fig.cap="CES with $x_p$ Residual Plots.">>=
-# Use residuals_df to make a graph.
-ces_xp_residuals_df <- filter(residuals_df, modelType=="ces", energyType %in% c("iXp", "none"))
-ggplot(data=ces_xp_residuals_df, aes(x=year, y=resid, color=Source)) + 
-  geom_point(size = 1.0) +
-  facet_grid(Country ~ nestStrParen) +
-  labs(x = "", y = "Residuals") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000)) + 
-  xy_theme()
-@
-
-%------------------------------
-\subsubsection{CES with final exergy ($x_f$)} 
-\label{sec:ces_xf}
-%------------------------------
-
-The following graphs show results for the CES model using final exergy ($x_f$).
-
-<<CES_lambda_gamma_graph_Xf, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6.0, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with final exergy ($x_f$).">>=
-# We need to keep only those combinations of country and Source that have final exergy.
-temp <- filter(AllCoeffs, model=="ces", nestStrParen %in% c("(iK + iL) + (iXf)", 
-                                                            "(iL + iXf) + (iK)", 
-                                                            "(iXf + iK) + (iL)"))
-countrySource <- paste0(temp$country, "+", temp$Source)
-rm(temp) # No need to keep this data frame around
-# Keep only unique combinations of country and Source in the temp data frame.
-keep <- unique(countrySource)
-cesCoeffsDataXf <- filter(AllCoeffs, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
-                                                                      "(iK + iL) + (iXf)", 
-                                                                      "(iL + iXf) + (iK)", 
-                                                                      "(iXf + iK) + (iL)"))
-cesCoeffsDataXf$countrySource <- paste0(cesCoeffsDataXf$country, "+", cesCoeffsDataXf$Source)
-cesCoeffsDataXf <- filter(cesCoeffsDataXf, countrySource %in% keep)
-
-standardScatterPlot(data=cesCoeffsDataXf, mapping=aes(x=gamma_coef, y=lambda, color=Source), 
-                    facet_formula=country~nestStrParen, alpha=0.05) +
-    scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
-    labs(x=expression(gamma), y=expression(lambda)) + 
-    guides(colour=guide_legend(override.aes = aes(alpha=1)))
-@
-
-<<CES_sigma1_delta1_graph_Xf, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6.5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with final exergy ($x_f$).">>=
-standardScatterPlot(data=cesCoeffsDataXf, mapping=aes(x=delta_1, y=sigma_1, color=Source), 
-                    facet_formula=country~nestStrParen, alpha=0.05) +
-    coord_trans(y="sigma") +
-    scale_x_continuous(breaks=c(0, 0.5, 1.0)) +
-    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-    labs(x=expression(delta[1]), y=expression(sigma[1])) + 
-    guides(colour=guide_legend(override.aes = aes(alpha=1)))
-@
-
-<<CES_sigma_delta_graph_Xf, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=6, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models using final exergy ($x_f$).">>=
-standardScatterPlot(data=filter(cesCoeffsDataXf, nestStrParen != "(iK + iL) + ()"),
-                    mapping=aes(x=delta, y=sigma, color=Source), 
-                    facet_formula=country~nestStrParen, alpha=0.05) +
-    coord_trans(y="sigma") +
-    scale_x_continuous(breaks=c(0, 0.5, 1.0)) +
-    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-    labs(x=expression(delta), y=expression(sigma)) +
-    guides(colour=guide_legend(override.aes = aes(alpha=1)))
-@
-
-Figure~\ref{fig:CES_ternary_graphXf} shows 
-$\alpha$, $\beta$, and $\gamma$ parameters for the CES model for all nests and countries.
-Figure~\ref{fig:CES_ternary_graphXf} is comparable to
-earlier ternary graphs, 
-Figures~\ref{fig:CD_Ternary_Scatter_Graph} and~\ref{fig:CES_ternary_graphXp}.
-
-<<CES_ternary_graphXf, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models with final exergy ($x_f$).", eval=TRUE>>=
-standardTriPlot(data=cesCoeffsDataXf, 
-                mapping=aes(color=Source), 
-                facet_formula=country~nestStrParen) +
-  guides(colour=guide_legend(override.aes = aes(alpha=1)))
-@
-
-Figures~\ref{fig:CES_GDP_Spaghetti_Graph_UK_xf}--\ref{fig:CES_GDP_Spaghetti_Graph_PT_xf} 
-compare CES model predictions with final exergy ($x_f$)
-to historical data for all nestings, countries, and data sources. 
-As with the previous results, 
-historical data are shown as a black line, 
-the fit to historical data is shown as a white line, and 
-the gray band encompasses \Sexpr{spaghettiGraphLevel*100}\% of the fits to resampled data.
-
-<<CES_GDP_Spaghetti_Graph_UK_xf, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="UK CES with $x_f$ fitted models.">>=
-cesFittedData_xf <- filter(AllFitted, model=="ces", energy %in% c("iXf", "none"))
-cesFittedData_xf$CountrySource <- paste0(cesFittedData_xf$Country, "+", cesFittedData_xf$Source)
-cesFittedData_xf <- filter(cesFittedData_xf, CountrySource %in% keep)
-
-cesFittedDataUK_xf <- filter(cesFittedData_xf, Country=="UK")
-spaghettiPlot(data=cesFittedDataUK_xf, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<CES_GDP_Spaghetti_Graph_AT_xf, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="AT CES with $x_f$ fitted models.">>=
-cesFittedDataAT_xf <- filter(cesFittedData_xf, Country=="AT")
-spaghettiPlot(data=cesFittedDataAT_xf, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<CES_GDP_Spaghetti_Graph_PT_xf, fig.pos="H", fig.align='center', fig.width=5, fig.height=4.5, fig.cap="PT CES with $x_f$ fitted models.">>=
-cesFittedDataPT_xf <- filter(cesFittedData_xf, Country=="PT")
-spaghettiPlot(data=cesFittedDataPT_xf, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<CES_Residual_Plot_xf, fig.pos="H", fig.align='center', fig.width=6, fig.height=6, fig.cap="CES with $x_f$ Residual Plots.">>=
-# Use residuals_df to make a graph.
-ces_xf_residuals_df <- filter(residuals_df, modelType=="ces", energyType %in% c("iXf", "none"))
-ces_xf_residuals_df$CountrySource <- paste0(ces_xf_residuals_df$Country, "+", ces_xf_residuals_df$Source)
-ces_xf_residuals_df <- filter(ces_xf_residuals_df, CountrySource %in% keep)
-
-ggplot(data=ces_xf_residuals_df, aes(x=year, y=resid, color=Source)) + 
-  geom_point(size = 1.0) +
-  facet_grid(Country ~ nestStrParen) +
-  labs(x = "", y = "Residuals") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000)) + 
-  xy_theme()
-@
-
-%------------------------------
-\subsubsection{CES with useful work ($u$)} 
-\label{sec:ces_u}
-%------------------------------
-
-The following graphs show results for the CES model using useful work ($u$).
-
-<<CES_lambda_gamma_graph_U, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6.0, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with useful work ($u$).">>=
-cesCoeffsDataU <- filter(AllCoeffs, model=="ces", nestStrParen %in% c("(iK + iL) + ()", 
-                                                                      "(iK + iL) + (iU)", 
-                                                                      "(iL + iU) + (iK)", 
-                                                                      "(iU + iK) + (iL)"))
-standardScatterPlot(data=cesCoeffsDataU, mapping=aes(x=gamma_coef, y=lambda, color=Source), 
-                    facet_formula=country~nestStrParen, alpha=0.05) +
-    scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
-    labs(x=expression(gamma), y=expression(lambda)) + 
-    guides(colour=guide_legend(override.aes = aes(alpha=1)))
-@
-
-<<CES_sigma1_delta1_graph_U, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6.5, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with useful work ($u$).">>=
-standardScatterPlot(data=cesCoeffsDataU, mapping=aes(x=delta_1, y=sigma_1, color=Source), 
-                    facet_formula=country~nestStrParen, alpha=0.05) +
-    coord_trans(y="sigma") +
-    scale_x_continuous(breaks=c(0, 0.5, 1.0)) +
-    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-    labs(x=expression(delta[1]), y=expression(sigma[1])) + 
-    guides(colour=guide_legend(override.aes = aes(alpha=1)))
-@
-
-<<CES_sigma_delta_graph_U, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=6, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models using useful work ($u$).">>=
-standardScatterPlot(data=filter(cesCoeffsDataU, nestStrParen != "(iK + iL) + ()"),
-                    mapping=aes(x=delta, y=sigma, color=Source), 
-                    facet_formula=country~nestStrParen, alpha=0.05) +
-    coord_trans(y="sigma") +
-    scale_x_continuous(breaks=c(0, 0.5, 1.0)) +
-    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
-    labs(x=expression(delta), y=expression(sigma)) +
-    guides(colour=guide_legend(override.aes = aes(alpha=1)))
-@
-
-Figure~\ref{fig:CES_ternary_graphU} shows 
-$\alpha$, $\beta$, and $\gamma$ parameters for the CES model with $u$ for all nests and countries.
-Figure~\ref{fig:CES_ternary_graphU} is comparable to
-earlier ternary graphs, 
-Figures~\ref{fig:CD_Ternary_Scatter_Graph}, \ref{fig:CES_ternary_graphXp}, and~\ref{fig:CES_ternary_graphXf}.
-
-<<CES_ternary_graphU, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models with final exergy ($u$).", eval=TRUE>>=
-standardTriPlot(data=cesCoeffsDataU, 
-                mapping=aes(color=Source), 
-                facet_formula=country~nestStrParen) +
-  guides(colour=guide_legend(override.aes = aes(alpha=1)))
-@
-
-Figures~\ref{fig:CES_GDP_Spaghetti_Graph_US_u}--\ref{fig:CES_GDP_Spaghetti_Graph_CN_u} 
-compare CES with $u$ model predictions 
-to historical data for all nestings, countries, and data sources. 
-As with previous graphs, 
-historical data are shown as a black line, 
-the fit to historical data is shown as a white line, and 
-the gray band encompasses \Sexpr{spaghettiGraphLevel*100}\% of the fits to resampled data.
-
-<<CES_GDP_Spaghetti_Graph_US_u, fig.pos="H", fig.align='center', fig.width=5, fig.height=3.5, fig.cap="US CES with $u$ fitted models.">>=
-# Use this result several times later.
-cesFittedData_u <- filter(AllFitted, model=="ces", energy %in% c("iU", "none"))
-
-cesFittedDataUS_u <- filter(cesFittedData_u, Country=="US")
-spaghettiPlot(data=cesFittedDataUS_u, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<CES_GDP_Spaghetti_Graph_UK_u, fig.pos="H", fig.align='center', fig.width=5, fig.height=3.5, fig.cap="UK CES with $u$ fitted models.">>=
-# Use this result several times later.
-cesFittedDataUK_u <- filter(cesFittedData_u, Country=="UK")
-spaghettiPlot(data=cesFittedDataUK_u, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<CES_GDP_Spaghetti_Graph_JP_u, fig.pos="H", fig.align='center', fig.width=5, fig.height=3.5, fig.cap="JP CES with $u$ fitted models.">>=
-# Use this result several times later.
-cesFittedDataJP_u <- filter(cesFittedData_u, Country=="JP")
-spaghettiPlot(data=cesFittedDataJP_u, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<CES_GDP_Spaghetti_Graph_AT_u, fig.pos="H", fig.align='center', fig.width=5, fig.height=3.5, fig.cap="AT CES with $u$ fitted models.">>=
-# Use this result several times later.
-cesFittedDataAT_u <- filter(cesFittedData_u, Country=="AT")
-spaghettiPlot(data=cesFittedDataAT_u, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<CES_GDP_Spaghetti_Graph_PT_u, fig.pos="H", fig.align='center', fig.width=5, fig.height=3.5, fig.cap="PT CES with $u$ fitted models.">>=
-# Use this result several times later.
-cesFittedDataPT_u <- filter(cesFittedData_u, Country=="PT")
-spaghettiPlot(data=cesFittedDataPT_u, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<CES_GDP_Spaghetti_Graph_CN_u, fig.pos="H", fig.align='center', fig.width=5, fig.height=3.5, fig.cap="CN CES with $u$ fitted models.">>=
-# Use this result several times later.
-cesFittedDataCN_u <- filter(cesFittedData_u, Country=="CN")
-spaghettiPlot(data=cesFittedDataCN_u, facet_formula=Source~nestStrParen, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<CES_Residual_Plot_u, fig.pos="H", fig.align='center', fig.width=6, fig.height=6, fig.cap="CES with $i$ Residual Plots.">>=
-# Use residuals_df to make a graph.
-ces_u_residuals_df <- filter(residuals_df, modelType=="ces", energyType %in% c("iU", "none"))
-ggplot(data=ces_u_residuals_df, aes(x=year, y=resid, color=Source)) + 
-  geom_point(size = 1.0) +
-  facet_grid(Country ~ nestStrParen) +
-  labs(x = "", y = "Residuals") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000)) + 
-  xy_theme()
-@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results}
+\label{sec:results}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+For now, I've organized the analysis around questions that we would like to answer.
 
 %++++++++++++++++++++++++++++++
-\subsection{LINEX Models}
-\label{sec:LINEX_Parameter_Estimation}
+\subsection{What effect does including energy and quality-adjustment have 
+            on the Solow residual in the Cobb-Douglas model?} 
+\label{sec:quality_adj_energy_and_solow_residual}
 %++++++++++++++++++++++++++++++
 
-The LINEX model is given in Equation~\ref{eq:LINEX}. 
-If the fitting algorithm drives $a_0 \rightarrow 0$, 
-any changes to $c_t$ have no effect on $sse$. 
-Therefore, we transformed the LINEX model into
-%
-\begin{equation} \label{eq:LINEX_transformed}
-  y = \theta A e; 
-  A = \mathrm{e}^{\left[2 a_0 \left(1 - \frac{1}{\rho_k} \right) 
-    + a_1 \left(\vphantom{\frac{1}{\rho_k}}\rho_l - 1 \right)\right]},
-\end{equation}
-%
-where $a_1 \equiv a_0 c_t$. 
-We used the \texttt{lm} function in \texttt{R}
-\citep{R} to estimate least-squares values for $a_0$ and $a_1$ in 
-Equation~\ref{eq:LINEX_transformed} in log-transformed space. 
-We recovered a value for $c_t$ with $c_t = a_1 / a_0$. 
-Figure~\ref{fig:LINEXq_Resample_Graph}
-shows the coefficients estimated from resampled data.
-
-Figures~\ref{fig:LINEX_GDP_Spaghetti_Graphs_US}--\ref{fig:LINEX_GDP_Spaghetti_Graphs_CN} 
-compare LINEX model predictions to historical data.
-Again, historical data are shown as a black line, 
-the fit to historical data is shown as a white line and 
-the gray band encompasses \Sexpr{spaghettiGraphLevel*100}\% of the fits to resampled data.
-
-<<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=6, fig.height=6, fig.cap="LINEX model resampling results.">>=
-linexCoeffsData <- filter(AllCoeffs, model=="linex")
-standardScatterPlot(data=linexCoeffsData,
-                    mapping=aes(x=a_0, y=c_t, color=Source),
-                    facet_formula=country~energy, alpha=0.05) +
-    scale_x_continuous(limits=c(0.0, 1.0), breaks=c(0.0, 0.5, 1.0)) +
-    scale_y_continuous(limits=c(-10.0, 10.0), breaks=c(10.0, -5.0, 0.0, 5.0, 10.0)) +
-    labs(x=expression(a[0]), y=expression(c[t])) +
-    guides(colour=guide_legend(override.aes = aes(alpha=1)))
-@
-
-<<LINEXq_Resample_Graph_PT, fig.pos="H", fig.align='center', fig.width=6, fig.height=2.5, fig.cap="LINEX model resampling results for PT.">>=
-linexCoeffsData <- filter(AllCoeffs, model=="linex", country=="PT")
-standardScatterPlot(data=linexCoeffsData,
-                    mapping=aes(x=a_0, y=c_t, color=Source),
-                    facet_formula=country~energy, alpha=0.05) +
-    scale_y_continuous(limits=c(-10.0, 10.0), breaks=c(10.0, -5.0, 0.0, 5.0, 10.0)) +
-    labs(x=expression(a[0]), y=expression(c[t])) +
-    guides(colour=guide_legend(override.aes = aes(alpha=1)))
-@
-
-<<LINEX_GDP_Spaghetti_Graphs_US, fig.pos="H", fig.align='center', fig.width=3, fig.height=2.5, fig.cap="US LINEX fitted models.">>=
-linexFittedData <- filter(AllFitted, model=="linex")
-
-linexFittedDataUS <- filter(linexFittedData, Country=="US")
-spaghettiPlot(data=linexFittedDataUS, facet_formula=Source~energy, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<LINEX_GDP_Spaghetti_Graphs_UK, fig.pos="H", fig.align='center', fig.width=3, fig.height=4.5, fig.cap="UK LINEX fitted models.">>=
-linexFittedDataUK <- filter(linexFittedData, Country=="UK")
-spaghettiPlot(data=linexFittedDataUK, facet_formula=Source~energy, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<LINEX_GDP_Spaghetti_Graphs_JP, fig.pos="H", fig.align='center', fig.width=3, fig.height=2.5, fig.cap="JP LINEX fitted models.">>=
-linexFittedDataJP <- filter(linexFittedData, Country=="JP")
-spaghettiPlot(data=linexFittedDataJP, facet_formula=Source~energy, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<LINEX_GDP_Spaghetti_Graphs_AT, fig.pos="H", fig.align='center', fig.width=4, fig.height=3.5, fig.cap="AT LINEX fitted models.">>=
-linexFittedDataAT <- filter(linexFittedData, Country=="AT")
-spaghettiPlot(data=linexFittedDataAT, facet_formula=Source~energy, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<LINEX_GDP_Spaghetti_Graphs_PT, fig.pos="H", fig.align='center', fig.width=4, fig.height=2.5, fig.cap="PT LINEX fitted models.">>=
-linexFittedDataPT <- filter(linexFittedData, Country=="PT")
-spaghettiPlot(data=linexFittedDataPT, facet_formula=Source~energy, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<LINEX_GDP_Spaghetti_Graphs_CN, fig.pos="H", fig.align='center', fig.width=4, fig.height=2.5, fig.cap="CN LINEX fitted models.">>=
-linexFittedDataCN <- filter(linexFittedData, Country=="CN")
-spaghettiPlot(data=linexFittedDataCN, facet_formula=Source~energy, level=spaghettiGraphLevel) +
-    labs(y="Indexed GDP (1960=1)") +
-  scale_x_continuous(breaks=c(1960, 1980, 2000))
-@
-
-<<LINEX_Residual_Plot, fig.pos="H", fig.align='center', fig.width=5, fig.height=6, fig.cap="LINEX Residual Plots.">>=
-# Use residuals_df to make a graph.
-linex_residuals_df <- filter(residuals_df, modelType=="linex")
-ggplot(data=linex_residuals_df, aes(x=year, y=resid, color=Source)) + 
-  geom_point(size = 1.0) +
-  facet_grid(Country ~ energyType) +
-  labs(x = "", y = "Residuals") + 
-  scale_x_continuous(breaks=c(1960, 1980, 2000)) + 
-  scale_y_continuous(limits=c(-0.3, 0.2)) +
-  xy_theme()
-@
-
-The LINEX model coefficients $a_0$ and $c_t$ imply time-dependent
-values of $\alpha$, $\beta$, and $\gamma$ as given by the following equations~\citep{Warr:2012cg}:
-%
-\begin{equation} \label{eq:LINEX_alpha}
-  \alpha \equiv \frac{k}{y}\frac{\partial y}{\partial k} = a_0 \left( \frac{l + e}{k} \right) \; ,
-\end{equation}
-%
-\begin{equation} \label{eq:LINEX_beta}
-  \beta \equiv \frac{l}{y} \frac{\partial y}{\partial l} = a_0 \left[ c_t \left( \frac{l}{e}\right) - \frac{l}{k} \right] \;,
-\end{equation}
-%
-and
-%
-\begin{equation} \label{eq:LINEX_beta_2}
-  \gamma \equiv \frac{e}{y} \frac{\partial y}{\partial e} 
-         = 1 - a_0 \left[ \frac{e}{k} + c_t \frac{l}{e} \right] 
-         = 1 - \alpha - \beta \;.
-\end{equation}
-%
-Thus, each fitted model implies a trajectory of $\alpha$, $\beta$, and $\gamma$ values as time proceeds.
-If the trajectory stays within the triangle, 
-the constraints on $\alpha$, $\beta$, and $\gamma$ are respected.
-Conversely, if the trajectory goes outside the triangle, the constraints have been violated.
-
-Figure~\ref{fig:LINEX_abg_traj_graph_REXS_UK_U}
-shows trajectories for the UK and useful work ($u$) from the REXS data set.
-
-<<LINEX_abg_traj_graph_REXS_UK_U, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="UK LINEX trajectory for REXS with $u$.">>=
-triPlot(data=fortify(REXS1960_Models$REXS1960$UK$linex$`iK+iL+iU`), grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1960")
-@
-
-Figure~\ref{fig:LINEX_abg_traj_graph_IST_UK_U}
-shows trajectories for the UK and useful work ($u$) from the IST data set.
-
-<<LINEX_abg_traj_graph_IST_UK_U, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="UK LINEX trajectory for IST with $u$.">>=
-triPlot(data=fortify(IST_Models$IST$UK$linex$`iK+iL+iU`), grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1960")
-@
-
-Figure~\ref{fig:LINEX_abg_traj_graph_Leeds_UK_U}
-shows trajectories for the UK and useful work ($u$) from the Leeds data set.
-
-<<LINEX_abg_traj_graph_Leeds_UK_U, fig.pos="H", fig.align='center', fig.width=3, fig.height=3.5, fig.cap="UK LINEX trajectory for Leeds with $u$.">>=
-triPlot(data=fortify(Leeds_Models$Leeds$UK$linex$`iK+iL+iU`), grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1960")
-@
-
-% In our testing, Iran is the only country for which the trajectory stays within 
-% the constraint triangle for the entire time period.
-% Thus, in our fitted models, the LINEX model is nearly always
-% violating constraints on $\alpha$, $\beta$, and $\gamma$.
-% If the LINEX model were made to respect the constraints,
-% it would fit worse than it already does for those countries where
-% the constraints are violated (that is, for every country except Iran).
-% We did nothing to correct this situation, because it is not clear what should be done.
-% \citet{Warr:2012cg} constrained the values of $a_0$ and $c_t$, while still holding them constant
-% for the entire time series, such that the constraints on $\alpha$, $\beta$, and $\gamma$
-% were respected.
-% But, Warr's approach necessarily leads to larger $sse$ values than unconstrained fitting.
-% Because unconstrained LINEX models already fit worse than 
-% constrained Cobb-Douglas and CES models,
-% we chose to report the unconstrained LINEX model fits in this paper.
-% Constraining $\alpha = 0$ in the case of China would imply that either
-% $a_0$ or $c_t$ or both varied with time.
-% At that point, $a_0$ and $c_t$ are no longer fitted parameters of the model, 
-% and we have a different model: it is no longer LINEX.
+We'll first look at Portugal.
+
+%------------------------------
+\subsubsection{Portugal} 
+%------------------------------
+
+First, use non-quality-adjusted data for Portugal and the Cobb-Douglas model.
+
+<<Portugal C-D undadjusted without energy>>=
+ptCDunadjNoE <- cdModel(formula = iGDP ~ iKstkS.L + iL + iYear, 
+                        data = dataPT, constrained = TRUE)
+naturalCoef(ptCDunadjNoE)
+@
+
+<<Portugal C-D undadjusted with energy>>=
+ptCDunadjWithE <- cdModel(formula = iGDP ~ iKstkS.L + iL + iXpMP + iYear, 
+                          data = dataPT, constrained = TRUE)
+naturalCoef(ptCDunadjWithE)
+@
+
+The Solow residual (\texttt{lambda}) is always negative. 
+However, the absolute value of \texttt{lambda} decreases from 
+\Sexpr{naturalCoef(ptCDunadjNoE)$lambda} to 
+\Sexpr{naturalCoef(ptCDunadjWithE)$lambda}
+when adding energy.
+So it appears that for Portugal, 
+using unadjusted inputs and including energy as a factor of production
+reduces the absolute value of the Solow residual somewhat.
+
+What about for quality-adjusted data and Portugal?
+
+<<Portugal C-D adjusted without energy>>=
+ptCDadjNoE <- cdModel(formula = iGDP ~ iKservS.L + ihLest + iYear, 
+                      data = dataPT, constrained = TRUE)
+naturalCoef(ptCDadjNoE)
+@
+
+<<Portugal C-D adjusted with energy>>=
+ptCDadjWithE <- cdModel(formula = iGDP ~ iKservS.L + ihLest + iUMP + iYear, 
+                          data = dataPT, constrained = TRUE)
+naturalCoef(ptCDadjWithE)
+@
+
+Using quality-adjusted inputs, the Solow residual (\texttt{lambda}) moves from 
+\Sexpr{naturalCoef(ptCDadjNoE)$lambda} to
+\Sexpr{naturalCoef(ptCDadjWithE)$lambda} when including energy.
+The absolute value of the Solow residual again decreases when adding energy.
+But, with quality-adjusted inputs, the effect is much stronger.
+
+Table~\ref{tab:lambda_CD_PT} shows
+the effect of both quality-corrected factors of production and energy.
+We find that both including energy and quality-adjusting the factors of production 
+reduce the Solow residual (\texttt{lambda}). 
+Quality-adjustment gets part of the way toward eliminating the Solow residual.
+Including energy (whether or not the factors of production are quality-adjusted)
+reduces the Solow residual significantly.
+
+\begin{table} \caption{Portugal Solow residual results with Cobb-Douglas.} 
+\label{tab:lambda_CD_PT} 
+  \begin{center}
+    \begin{tabular}{r c c} 
+      \toprule
+                      & Unadjusted     & Quality-adjusted   \\
+      \midrule
+      Without energy  & \Sexpr{naturalCoef(ptCDunadjNoE)$lambda}      & \Sexpr{naturalCoef(ptCDadjNoE)$lambda} \\
+      With energy     & \Sexpr{naturalCoef(ptCDunadjWithE)$lambda}    & \Sexpr{naturalCoef(ptCDadjWithE)$lambda} \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+\end{table}
+
+Note that the contribution of capital (\texttt{alpha\_1})
+always shifts to energy (\texttt{alpha\_3}) when energy is included 
+as a factor of production.
+
+What about for the UK?
+
+%------------------------------
+\subsubsection{United Kingdom} 
+%------------------------------
+
+<<UK C-D>>=
+ukCDunadjNoE <- cdModel(formula = iGDP ~ iKstkO.WwithRD + iL + iYear, 
+                        data = dataUK, constrained = TRUE)
+ukCDunadjWithE <- cdModel(formula = iGDP ~ iKstkO.WwithRD + iL + iXp + iYear, 
+                          data = dataUK, constrained = TRUE)
+ukCDadjNoE <- cdModel(formula = iGDP ~ iKservO.WwithRD + ihLest + iYear, 
+                        data = dataUK, constrained = TRUE)
+ukCDadjWithE <- cdModel(formula = iGDP ~ iKservO.WwithRD + ihLest + iU + iYear, 
+                          data = dataUK, constrained = TRUE)
+@
+
+\begin{table} \caption{UK Solow residual results with Cobb-Douglas.} 
+\label{tab:lambda_CD_UK} 
+  \begin{center}
+    \begin{tabular}{r c c} 
+      \toprule
+                      & Unadjusted     & Quality-adjusted   \\
+      \midrule
+      Without energy  & \Sexpr{naturalCoef(ukCDunadjNoE)$lambda}      & \Sexpr{naturalCoef(ukCDadjNoE)$lambda} \\
+      With energy     & \Sexpr{naturalCoef(ukCDunadjWithE)$lambda}    & \Sexpr{naturalCoef(ukCDadjWithE)$lambda} \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+\end{table}
+
+For the UK, the quality-adjusted, with energy Solow residual is 
+\Sexpr{naturalCoef(ukCDadjWithE)$lambda * 100}%,
+a very small number indeed.
+For the UK, it appears that both quality-adjustment and addition of energy as a factor of production
+can effectively eliminate the Solow residual,
+reducing it to \Sexpr{naturalCoef(ukCDadjWithE)$lambda}.
+
+Interestingly, the Solow residual acutally increases from 
+\Sexpr{naturalCoef(ukCDunadjNoE)$lambda} to
+\Sexpr{naturalCoef(ukCDunadjWithE)$lambda}
+for unadjusted factors of production when energy is added.
+To find out why, let's look at all the coefficients.
+
+<<UK CD Unadjusted Coefficients>>=
+naturalCoef(ukCDunadjNoE)
+naturalCoef(ukCDunadjWithE)
+@
+
+When energy is included, much of the effect of capital (\texttt{alpha\_1}) is 
+attributed to energy (\texttt{alpha\_3}), 
+as \texttt{alpha\_1} moves from 
+\Sexpr{naturalCoef(ukCDunadjNoE)$alpha_1} to
+\Sexpr{naturalCoef(ukCDunadjWithE)$alpha_1}.
+
+When we look at quality-adjusted inputs, we find similar results.
+
+<<UK CD Quality-adjusted Coefficients>>=
+naturalCoef(ukCDadjNoE)
+naturalCoef(ukCDadjWithE)
+@
+
+\texttt{alpha\_1} moves from 
+\Sexpr{naturalCoef(ukCDadjNoE)$alpha_1} to
+\Sexpr{naturalCoef(ukCDadjWithE)$alpha_1}.
 
 %++++++++++++++++++++++++++++++
-\subsection{Parameter Estimation Summary}
-\label{sec:Parameter_Estimation_Summary}
+\subsection{Do we obtain a negative Solow residual for Portugal with the CES model?} 
+\label{sec:Solow_negative_for_PT_in_CES?}
 %++++++++++++++++++++++++++++++
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion of Results}
-\label{sec:Discussion_of_Results}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%------------------------------
+\subsubsection{($kl$)$e$ nesting} 
+%------------------------------
+
+First, look at unadjusted inputs using the ($kl$)$e$ nesting.
+
+<<PT CES-kle unadjusted, warning=FALSE, eval=evalCES>>=
+# Not working at this time.
+# ptCESkleunadjNoE <- cesModel(formula = iGDP ~ iKstkS.L + iL + iYear, 
+#                nest = c(1,2,3), data = dataPT, constrained = TRUE)
+# naturalCoef(ptCESkleunadjNoE)
+ptCESkleunadjWithE <- cesModel(formula = iGDP ~ iKstkS.L + iL + iXpMP + iYear, 
+                            nest = c(1,2,3), data = dataPT, constrained = TRUE)
+naturalCoef(ptCESkleunadjWithE)
+@
+
+Now look at quality-adjusted inputs using the ($kl$)$e$ nesting.
+
+<<PT CES-kle quality-adjusted, warning=FALSE, eval=evalCES>>=
+# Not working at this time.
+# ptCESkleadjNoE <- cesModel(formula = iGDP ~ iKservS.L + ihLest + iYear, 
+#                         nest = c(1,2,3), data = dataPT, constrained = TRUE)
+# naturalCoef(ptCESkleadjNoE)
+ptCESkleadjWithE <- cesModel(formula = iGDP ~ iKservS.L + ihLest + iUMP + iYear, 
+                          nest = c(1,2,3), data = dataPT, constrained = TRUE)
+naturalCoef(ptCESkleadjWithE)
+@
+
+Table~\ref{tab:lambda_CES-kle_PT} summarizes the Portugal Solow residual results with CES and the ($kl$)$e$ nesting.
+
+\begin{table} \caption{Portugal Solow residual results with CES and ($kl$)$e$ nesting.} 
+\label{tab:lambda_CES-kle_PT} 
+  \begin{center}
+    \begin{tabular}{r c c} 
+      \toprule
+                      & Unadjusted     & Quality-adjusted   \\
+      \midrule
+%      Without energy  & \Sexpr{naturalCoef(ptCESkleunadjNoE)$lambda}      & \Sexpr{naturalCoef(ptCESkleadjNoE)$lambda} \\
+      With energy     & \Sexpr{naturalCoef(ptCESkleunadjWithE)$lambda}    & \Sexpr{naturalCoef(ptCESkleadjWithE)$lambda} \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+\end{table}
+
+The Solow residual is positive, and 
+quality-adjusting the inputs 
+reduces the Solow residual (\texttt{lambda}).
+
+%------------------------------
+\subsubsection{($le$)$k$ nesting} 
+%------------------------------
+
+Next, look at unadjusted inputs using the ($le$)$k$ nesting.
+
+<<PT CES-lek unadjusted, warning=FALSE, eval=evalCES>>=
+# Not working at this time.
+# ptCESlekunadjNoE <- cesModel(formula = iGDP ~ iKstkS.L + iL + iYear, 
+#                nest = c(2,3,1), data = dataPT, constrained = TRUE)
+# naturalCoef(ptCESlekunadjNoE)
+ptCESlekunadjWithE <- cesModel(formula = iGDP ~ iKstkS.L + iL + iXpMP + iYear, 
+                            nest = c(2,3,1), data = dataPT, constrained = TRUE)
+naturalCoef(ptCESlekunadjWithE)
+@
+
+Now look at quality-adjusted inputs using the ($le$)$k$ nesting.
+
+<<PT CES-lek quality-adjusted, warning=FALSE, eval=evalCES>>=
+# Not working at this time.
+# ptCESlekadjNoE <- cesModel(formula = iGDP ~ iKservS.L + ihLest + iYear, 
+#                         nest = c(2,3,1), data = dataPT, constrained = TRUE)
+# naturalCoef(ptCESlekadjNoE)
+ptCESlekadjWithE <- cesModel(formula = iGDP ~ iKservS.L + ihLest + iUMP + iYear, 
+                          nest = c(2,3,1), data = dataPT, constrained = TRUE)
+naturalCoef(ptCESlekadjWithE)
+@
+
+Table~\ref{tab:lambda_CES-lek_PT} summarizes the Portugal Solow residual results with CES and the ($le$)$k$ nesting.
+
+\begin{table} \caption{Portugal Solow residual results with CES and ($le$)$k$ nesting.} 
+\label{tab:lambda_CES-lek_PT} 
+  \begin{center}
+    \begin{tabular}{r c c} 
+      \toprule
+                      & Unadjusted     & Quality-adjusted   \\
+      \midrule
+%      Without energy  & \Sexpr{naturalCoef(ptCESlekunadjNoE)$lambda}      & \Sexpr{naturalCoef(ptCESlekadjNoE)$lambda} \\
+      With energy     & \Sexpr{naturalCoef(ptCESlekunadjWithE)$lambda}    & \Sexpr{naturalCoef(ptCESlekadjWithE)$lambda} \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+\end{table}
+
+The Solow residual is positive, and 
+quality-adjusting the inputs 
+reduces the Solow residual (\texttt{lambda}).
+
+%------------------------------
+\subsubsection{($ek$)$k$ nesting} 
+%------------------------------
+
+Next, look at unadjusted inputs using the ($ek$)$l$ nesting.
+
+<<PT CES-ekl unadjusted, warning=FALSE, eval=evalCES>>=
+# Not working at this time.
+# ptCESeklunadjNoE <- cesModel(formula = iGDP ~ iKstkS.L + iL + iYear, 
+#                nest = c(3,1,2), data = dataPT, constrained = TRUE)
+# naturalCoef(ptCESeklunadjNoE)
+ptCESeklunadjWithE <- cesModel(formula = iGDP ~ iKstkS.L + iL + iXpMP + iYear, 
+                            nest = c(3,1,2), data = dataPT, constrained = TRUE)
+naturalCoef(ptCESeklunadjWithE)
+@
+
+Now look at quality-adjusted inputs using the ($ek$)$l$ nesting.
+
+<<PT CES-ekl quality-adjusted, warning=FALSE, eval=evalCES>>=
+# Not working at this time.
+# ptCESekladjNoE <- cesModel(formula = iGDP ~ iKservS.L + ihLest + iYear, 
+#                         nest = c(3,1,2), data = dataPT, constrained = TRUE)
+# naturalCoef(ptCESekladjNoE)
+ptCESekladjWithE <- cesModel(formula = iGDP ~ iKservS.L + ihLest + iUMP + iYear, 
+                          nest = c(3,1,2), data = dataPT, constrained = TRUE)
+naturalCoef(ptCESekladjWithE)
+@
+
+Table~\ref{tab:lambda_CES-ekl_PT} summarizes the Portugal Solow residual results with CES and the ($ek$)$l$ nesting.
+
+\begin{table} \caption{Portugal Solow residual results with CES and ($ek$)$l$ nesting.} 
+\label{tab:lambda_CES-ekl_PT} 
+  \begin{center}
+    \begin{tabular}{r c c} 
+      \toprule
+                      & Unadjusted     & Quality-adjusted   \\
+      \midrule
+%      Without energy  & \Sexpr{naturalCoef(ptCESeklunadjNoE)$lambda}      & \Sexpr{naturalCoef(ptCESekladjNoE)$lambda} \\
+      With energy     & \Sexpr{naturalCoef(ptCESeklunadjWithE)$lambda}    & \Sexpr{naturalCoef(ptCESekladjWithE)$lambda} \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+\end{table}
+
+The Solow residual is positive, and 
+quality-adjusting the inputs 
+reduces the Solow residual (\texttt{lambda}).
 
@@
 
-\bibliographystyle{model2-names}
+% \bibliographystyle{model2-names}
 %%\bibliography{<your-bib-database>}
-\bibliography{Paper2.bib}
+% \bibliography{Paper2.bib}
 

### 2015-04-24 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Abstraction for formulas.

@@
 # in each formula throughout the document.
+# Use of substitute establishes an R "name"
+# that can be a component of a formula.
 # Economic output
-y_PT <- "iGDP"
-y_UK <- "iGDP"
+y_PT <- substitute(iGDP)
+y_UK <- substitute(iGDP)
 # Portugal undajusted inputs
-y_PT <- "iGDP"
-K_PT_unadj <- "iKstkS.L"
-L_PT_unadj <- "iL"
-E_PT_unadj <- "iXpMP"
-# Partugal quality-adjusted inputs
-K_PT_adj <- "iKservS.L"
-L_PT_adj <- "ihLest"
-E_PT_adj <- "iUMP"
+k_PT_unadj <- substitute(iKstkS.L)
+l_PT_unadj <- substitute(iL)
+e_PT_unadj <- substitute(iXpMP)
+# Portugal quality-adjusted inputs
+k_PT_adj <- substitute(iKservS.L)
+l_PT_adj <- substitute(ihLest)
+e_PT_adj <- substitute(iUMP)
 # UK unadjusted inputs
-K_UK_unadj <- "iKstkO.WwithRD"
-L_UK_unadj <- "iL"
-E_UK_unadj <- "iXp"
+k_UK_unadj <- substitute(iKstkO.WwithRD)
+l_UK_unadj <- substitute(iL)
+e_UK_unadj <- substitute(iXp)
 # UK quality-adjusted inputs
-K_UK_adj <- "iKservO.WwithRD"
-L_UK_adj <- "ihLest"
-E_UK_adj <- "iU"
+k_UK_adj <- substitute(iKservO.WwithRD)
+l_UK_adj <- substitute(ihLest)
+e_UK_adj <- substitute(iU)
 # Time variables
-time_PT <- "iYear"
-time_UK <- "iYear"
-@
-
-<<Formulas, echo=FALSE>>=
+t_PT <- substitute(iYear)
+t_UK <- substitute(iYear)
+@
+
+<<Formulas>>=
 # Set up the formulas for each type of analysis.
-# To do this, use the substitute function.
-
-# response <- "iGDP"
-# # Portugal undajusted inputs
-# capital <- "iKstkS.L"
-# labor <- "iL"
-# time <- "iYear"
-# 
-# formula <- substitute( response ~ capital + labor + time,
-#                        list( response = substitute(response),
-#                              capital = substitute(capital),
-#                              labor = substitute(labor),
-#                              time = substitute(time)
-#                        )
-# )
-# formula
-# 
-# 
-# 
-# f_PT_unadj_woe <- substitute(y ~ k + l + t, list(y = y_PT,
-#                                                  k = K_PT_unadj,
-#                                                  l = L_PT_unadj,
-#                                                  t = time_PT))
-# y_PT
-# substitute(y_PT)
-# eval(y_PT)
-# f_PT_unadj_woe
+f_PT_unadj_noE <- as.formula(
+  substitute( y ~ k + l + t,
+              list( y = y_PT, k = k_PT_unadj, 
+                    l = l_PT_unadj, t = t_PT)))
+f_PT_unadj_withE <- as.formula(
+  substitute( y ~ k + l + e + t,
+              list( y = y_PT, k = k_PT_unadj,
+                    l = l_PT_unadj, e = e_PT_unadj, t = t_PT)))
+f_PT_adj_noE <- as.formula(
+  substitute( y ~ k + l + t,
+              list( y = y_PT, k = k_PT_adj,
+                    l = l_PT_adj, t = t_PT)))
+f_PT_adj_withE <- as.formula(
+  substitute( y ~ k + l + e + t,
+              list( y = y_PT, k = k_PT_adj,
+                    l = l_PT_adj, e = e_PT_adj, t = t_PT)))
+f_UK_unadj_noE <- as.formula(
+  substitute( y ~ k + l + t,
+              list( y = y_UK, k = k_UK_unadj,
+                    l = l_UK_unadj, t = t_UK)))
+f_UK_unadj_withE <- as.formula(
+  substitute( y ~ k + l + e + t,
+              list( y = y_UK, k = k_UK_unadj,
+                    l = l_UK_unadj, e = e_UK_unadj, t = t_UK)))
+f_UK_adj_noE <- as.formula(
+  substitute( y ~ k + l + t,
+              list( y = y_UK, k = k_UK_adj,
+                    l = l_UK_adj, t = t_UK)))
+f_UK_adj_withE <- as.formula(
+  substitute( y ~ k + l + e + t,
+              list( y = y_UK, k = k_UK_adj,
+                    l = l_UK_adj, e = e_UK_adj, t = t_UK)))
 @
@@
       Output      & \Sexpr{y_PT}       & \Sexpr{y_UK}       \\
-      Capital     & \Sexpr{K_PT_unadj} & \Sexpr{K_UK_unadj} \\
-      Labor       & \Sexpr{L_PT_unadj} & \Sexpr{L_UK_unadj} \\
-      Energy      & \Sexpr{E_PT_unadj} & \Sexpr{E_UK_unadj} \\
+      Capital     & \Sexpr{k_PT_unadj} & \Sexpr{k_UK_unadj} \\
+      Labor       & \Sexpr{l_PT_unadj} & \Sexpr{l_UK_unadj} \\
+      Energy      & \Sexpr{e_PT_unadj} & \Sexpr{e_UK_unadj} \\
       \bottomrule
@@
       Output      & \Sexpr{y_PT}     & \Sexpr{y_UK}     \\
-      Capital     & \Sexpr{K_PT_adj} & \Sexpr{K_UK_adj} \\
-      Labor       & \Sexpr{L_PT_adj} & \Sexpr{L_UK_adj} \\
-      Energy      & \Sexpr{E_PT_adj} & \Sexpr{E_UK_adj} \\
+      Capital     & \Sexpr{k_PT_adj} & \Sexpr{k_UK_adj} \\
+      Labor       & \Sexpr{l_PT_adj} & \Sexpr{l_UK_adj} \\
+      Energy      & \Sexpr{e_PT_adj} & \Sexpr{e_UK_adj} \\
       \bottomrule
@@
 <<Portugal C-D undadjusted without energy>>=
-ptCDunadjNoE <- cdModel(formula = iGDP ~ iKstkS.L + iL + iYear, 
+ptCDunadjNoE <- cdModel(formula = f_PT_unadj_noE, 
                         data = dataPT, constrained = TRUE)
@@
 <<Portugal C-D undadjusted with energy>>=
-ptCDunadjWithE <- cdModel(formula = iGDP ~ iKstkS.L + iL + iXpMP + iYear, 
+ptCDunadjWithE <- cdModel(formula = f_PT_unadj_withE, 
                           data = dataPT, constrained = TRUE)
@@
 <<Portugal C-D adjusted without energy>>=
-ptCDadjNoE <- cdModel(formula = iGDP ~ iKservS.L + ihLest + iYear, 
+ptCDadjNoE <- cdModel(formula = f_PT_adj_noE, 
                       data = dataPT, constrained = TRUE)
@@
 <<Portugal C-D adjusted with energy>>=
-ptCDadjWithE <- cdModel(formula = iGDP ~ iKservS.L + ihLest + iUMP + iYear, 
+ptCDadjWithE <- cdModel(formula = f_PT_adj_withE, 
                           data = dataPT, constrained = TRUE)
@@
 <<UK C-D>>=
-ukCDunadjNoE <- cdModel(formula = iGDP ~ iKstkO.WwithRD + iL + iYear, 
+ukCDunadjNoE <- cdModel(formula = f_UK_unadj_noE, 
                         data = dataUK, constrained = TRUE)
-ukCDunadjWithE <- cdModel(formula = iGDP ~ iKstkO.WwithRD + iL + iXp + iYear, 
+ukCDunadjWithE <- cdModel(formula = f_UK_unadj_withE, 
                           data = dataUK, constrained = TRUE)
-ukCDadjNoE <- cdModel(formula = iGDP ~ iKservO.WwithRD + ihLest + iYear, 
+ukCDadjNoE <- cdModel(formula = f_UK_adj_noE, 
                         data = dataUK, constrained = TRUE)
-ukCDadjWithE <- cdModel(formula = iGDP ~ iKservO.WwithRD + ihLest + iU + iYear, 
+ukCDadjWithE <- cdModel(formula = f_UK_adj_withE, 
                           data = dataUK, constrained = TRUE)
@@
 
+First, look at the CES model without energy.
+Nesting is unabmiguous, so this fit does not need to be repeated
+for each nesting option.
+
+<<PT CES-kl, warning=FALSE, eval=evalCES>>=
+ptCESklunadjNoE <- cesModel(formula = f_PT_unadj_noE, 
+                            nest = c(1,2), data = dataPT, constrained = TRUE)
+naturalCoef(ptCESklunadjNoE)
+ptCESkladjNoE <- cesModel(formula = f_PT_adj_noE, 
+                          nest = c(1,2), data = dataPT, constrained = TRUE)
+naturalCoef(ptCESkladjNoE)
+@
+
 %------------------------------
@@
 <<PT CES-kle unadjusted, warning=FALSE, eval=evalCES>>=
-# Not working at this time.
-# ptCESkleunadjNoE <- cesModel(formula = iGDP ~ iKstkS.L + iL + iYear, 
-#                nest = c(1,2,3), data = dataPT, constrained = TRUE)
-# naturalCoef(ptCESkleunadjNoE)
-ptCESkleunadjWithE <- cesModel(formula = iGDP ~ iKstkS.L + iL + iXpMP + iYear, 
+ptCESkleunadjWithE <- cesModel(formula = f_PT_unadj_withE, 
                             nest = c(1,2,3), data = dataPT, constrained = TRUE)
@@
 <<PT CES-kle quality-adjusted, warning=FALSE, eval=evalCES>>=
-# Not working at this time.
-# ptCESkleadjNoE <- cesModel(formula = iGDP ~ iKservS.L + ihLest + iYear, 
-#                         nest = c(1,2,3), data = dataPT, constrained = TRUE)
-# naturalCoef(ptCESkleadjNoE)
-ptCESkleadjWithE <- cesModel(formula = iGDP ~ iKservS.L + ihLest + iUMP + iYear, 
+ptCESkleadjWithE <- cesModel(formula = f_PT_adj_withE, 
                           nest = c(1,2,3), data = dataPT, constrained = TRUE)
@@
       \midrule
-%      Without energy  & \Sexpr{naturalCoef(ptCESkleunadjNoE)$lambda}      & \Sexpr{naturalCoef(ptCESkleadjNoE)$lambda} \\
+      Without energy  & \Sexpr{naturalCoef(ptCESklunadjNoE)$lambda}       & \Sexpr{naturalCoef(ptCESkladjNoE)$lambda} \\
       With energy     & \Sexpr{naturalCoef(ptCESkleunadjWithE)$lambda}    & \Sexpr{naturalCoef(ptCESkleadjWithE)$lambda} \\
@@
 <<PT CES-lek unadjusted, warning=FALSE, eval=evalCES>>=
-# Not working at this time.
-# ptCESlekunadjNoE <- cesModel(formula = iGDP ~ iKstkS.L + iL + iYear, 
-#                nest = c(2,3,1), data = dataPT, constrained = TRUE)
-# naturalCoef(ptCESlekunadjNoE)
-ptCESlekunadjWithE <- cesModel(formula = iGDP ~ iKstkS.L + iL + iXpMP + iYear, 
+ptCESlekunadjWithE <- cesModel(formula = f_PT_unadj_withE, 
                             nest = c(2,3,1), data = dataPT, constrained = TRUE)
@@
 <<PT CES-lek quality-adjusted, warning=FALSE, eval=evalCES>>=
-# Not working at this time.
-# ptCESlekadjNoE <- cesModel(formula = iGDP ~ iKservS.L + ihLest + iYear, 
-#                         nest = c(2,3,1), data = dataPT, constrained = TRUE)
-# naturalCoef(ptCESlekadjNoE)
-ptCESlekadjWithE <- cesModel(formula = iGDP ~ iKservS.L + ihLest + iUMP + iYear, 
+ptCESlekadjWithE <- cesModel(formula = f_PT_adj_withE, 
                           nest = c(2,3,1), data = dataPT, constrained = TRUE)
@@
       \midrule
-%      Without energy  & \Sexpr{naturalCoef(ptCESlekunadjNoE)$lambda}      & \Sexpr{naturalCoef(ptCESlekadjNoE)$lambda} \\
+      Without energy  & \Sexpr{naturalCoef(ptCESklunadjNoE)$lambda}       & \Sexpr{naturalCoef(ptCESkladjNoE)$lambda} \\
       With energy     & \Sexpr{naturalCoef(ptCESlekunadjWithE)$lambda}    & \Sexpr{naturalCoef(ptCESlekadjWithE)$lambda} \\
@@
 <<PT CES-ekl unadjusted, warning=FALSE, eval=evalCES>>=
-# Not working at this time.
-# ptCESeklunadjNoE <- cesModel(formula = iGDP ~ iKstkS.L + iL + iYear, 
-#                nest = c(3,1,2), data = dataPT, constrained = TRUE)
-# naturalCoef(ptCESeklunadjNoE)
-ptCESeklunadjWithE <- cesModel(formula = iGDP ~ iKstkS.L + iL + iXpMP + iYear, 
+ptCESeklunadjWithE <- cesModel(formula = f_PT_unadj_withE, 
                             nest = c(3,1,2), data = dataPT, constrained = TRUE)
@@
 <<PT CES-ekl quality-adjusted, warning=FALSE, eval=evalCES>>=
-# Not working at this time.
-# ptCESekladjNoE <- cesModel(formula = iGDP ~ iKservS.L + ihLest + iYear, 
-#                         nest = c(3,1,2), data = dataPT, constrained = TRUE)
-# naturalCoef(ptCESekladjNoE)
-ptCESekladjWithE <- cesModel(formula = iGDP ~ iKservS.L + ihLest + iUMP + iYear, 
+ptCESekladjWithE <- cesModel(formula = f_PT_adj_withE, 
                           nest = c(3,1,2), data = dataPT, constrained = TRUE)
@@
       \midrule
-%      Without energy  & \Sexpr{naturalCoef(ptCESeklunadjNoE)$lambda}      & \Sexpr{naturalCoef(ptCESekladjNoE)$lambda} \\
+      Without energy  & \Sexpr{naturalCoef(ptCESklunadjNoE)$lambda}       & \Sexpr{naturalCoef(ptCESkladjNoE)$lambda} \\
       With energy     & \Sexpr{naturalCoef(ptCESeklunadjWithE)$lambda}    & \Sexpr{naturalCoef(ptCESekladjWithE)$lambda} \\

### 2015-04-24 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Can now use saved model data.

@@
 #####################################################
-evalCES=TRUE
+rerunModels=FALSE
 #####################################################
@@
 # Set up the formulas for each type of analysis.
-f_PT_unadj_noE <- as.formula(
+f <- NULL
+f$PT$unadj$noE <- as.formula(
   substitute( y ~ k + l + t,
@@
                     l = l_PT_unadj, t = t_PT)))
-f_PT_unadj_withE <- as.formula(
+f$PT$unadj$withE <- as.formula(
   substitute( y ~ k + l + e + t,
@@
                     l = l_PT_unadj, e = e_PT_unadj, t = t_PT)))
-f_PT_adj_noE <- as.formula(
+f$PT$adj$noE <- as.formula(
   substitute( y ~ k + l + t,
@@
                     l = l_PT_adj, t = t_PT)))
-f_PT_adj_withE <- as.formula(
+f$PT$adj$withE <- as.formula(
   substitute( y ~ k + l + e + t,
@@
                     l = l_PT_adj, e = e_PT_adj, t = t_PT)))
-f_UK_unadj_noE <- as.formula(
+f$UK$unadj$noE <- as.formula(
   substitute( y ~ k + l + t,
@@
                     l = l_UK_unadj, t = t_UK)))
-f_UK_unadj_withE <- as.formula(
+f$UK$unadj$withE <- as.formula(
   substitute( y ~ k + l + e + t,
@@
                     l = l_UK_unadj, e = e_UK_unadj, t = t_UK)))
-f_UK_adj_noE <- as.formula(
+f$UK$adj$noE <- as.formula(
   substitute( y ~ k + l + t,
@@
                     l = l_UK_adj, t = t_UK)))
-f_UK_adj_withE <- as.formula(
+f$UK$adj$withE <- as.formula(
   substitute( y ~ k + l + e + t,
@@
                     l = l_UK_adj, e = e_UK_adj, t = t_UK)))
+@
+
+<<Models>>=
+fileName <- "ESEE2015Models.Rdata"
+if (!rerunModels){
+  # load from the file on disk
+  load(fileName)
+} else {
+  # re-run the models and save to disk.
+  # In RStudio, be sure to set the working directory to the source file directory.
+  nest <- NULL
+  nest$kl <- c(1,2)
+  nest$kle <- c(1,2,3)
+  nest$lek <- c(2,3,1)
+  nest$ekl <- c(3,1,2)
+  models <- NULL
+  # Portugal, CD
+  models$PT$unadj$noE$CD <- cdModel(formula = f$PT$unadj$noE, 
+                                    data = dataPT, constrained = TRUE)
+  models$PT$unadj$withE$CD <- cdModel(formula = f$PT$unadj$withE, 
+                                      data = dataPT, constrained = TRUE)
+  models$PT$adj$noE$CD <- cdModel(formula = f$PT$adj$noE, 
+                        data = dataPT, constrained = TRUE)
+  models$PT$adj$withE$CD <- cdModel(formula = f$PT$adj$withE, 
+                          data = dataPT, constrained = TRUE)
+  # UK, CD
+  models$UK$unadj$noE$CD <- cdModel(formula = f$UK$unadj$noE, 
+                          data = dataUK, constrained = TRUE)
+  models$UK$unadj$withE$CD <- cdModel(formula = f$UK$unadj$withE, 
+                            data = dataUK, constrained = TRUE)
+  models$UK$adj$noE$CD <- cdModel(formula = f$UK$adj$noE, 
+                        data = dataUK, constrained = TRUE)
+  models$UK$adj$withE$CD <- cdModel(formula = f$UK$adj$withE, 
+                          data = dataUK, constrained = TRUE)
+  # PT, CESkl
+  models$PT$unadj$noE$CESkl <- cesModel(formula = f$PT$unadj$noE, 
+                              nest = nest$kl, data = dataPT, constrained = TRUE)
+  models$PT$adj$noE$CESkl <- cesModel(formula = f$PT$adj$noE, 
+                            nest = nest$kl, data = dataPT, constrained = TRUE)
+  # PT, CESkle
+  models$PT$unadj$withE$CESkle <- cesModel(formula = f$PT$unadj$withE, 
+                                 nest = nest$kle, data = dataPT, constrained = TRUE)
+  models$PT$adj$withE$CESkle <- cesModel(formula = f$PT$adj$withE, 
+                               nest = nest$kle, data = dataPT, constrained = TRUE)
+  # PT, CESlek
+  models$PT$unadj$withE$CESlek <- cesModel(formula = f$PT$unadj$withE, 
+                                 nest = nest$lek, data = dataPT, constrained = TRUE)
+  models$PT$adj$withE$CESlek <- cesModel(formula = f$PT$adj$withE, 
+                               nest = nest$lek, data = dataPT, constrained = TRUE)
+  # PT, CESekl
+  models$PT$unadj$withE$CESekl <- cesModel(formula = f$PT$unadj$withE, 
+                                 nest = nest$ekl, data = dataPT, constrained = TRUE)
+  models$PT$adj$withE$CESekl <- cesModel(formula = f$PT$adj$withE, 
+                               nest = nest$ekl, data = dataPT, constrained = TRUE)
+  # UK, CESkl
+  models$UK$unadj$noE$CESkl <- cesModel(formula = f$UK$unadj$noE, 
+                              nest = nest$kl, data = dataUK, constrained = TRUE)
+  models$UK$adj$noE$CESkl <- cesModel(formula = f$UK$adj$noE, 
+                            nest = nest$kl, data = dataUK, constrained = TRUE)
+  # UK, CESkle
+  models$UK$unadj$withE$CESkle <- cesModel(formula = f$UK$unadj$withE, 
+                                 nest = nest$kle, data = dataUK, constrained = TRUE)
+  models$UK$adj$withE$CESkle <- cesModel(formula = f$UK$adj$withE, 
+                               nest = nest$kle, data = dataUK, constrained = TRUE)
+  # UK, CESlek
+  models$UK$unadj$withE$CESlek <- cesModel(formula = f$UK$unadj$withE, 
+                                 nest = nest$lek, data = dataUK, constrained = TRUE)
+  models$UK$adj$withE$CESlek <- cesModel(formula = f$UK$adj$withE, 
+                               nest = nest$lek, data = dataUK, constrained = TRUE)
+  # UK, CESekl
+  models$UK$unadj$withE$CESekl <- cesModel(formula = f$UK$unadj$withE, 
+                                 nest = nest$ekl, data = dataUK, constrained = TRUE)
+  models$UK$adj$withE$CESekl <- cesModel(formula = f$UK$adj$withE, 
+                               nest = nest$ekl, data = dataUK, constrained = TRUE)
+  # Save models to disk.
+  save(models, file=fileName)
+}
+
 @
@@
 <<Portugal C-D undadjusted without energy>>=
-ptCDunadjNoE <- cdModel(formula = f_PT_unadj_noE, 
-                        data = dataPT, constrained = TRUE)
-naturalCoef(ptCDunadjNoE)
+naturalCoef(models$PT$unadj$noE$CD)
 @
@@
 <<Portugal C-D undadjusted with energy>>=
-ptCDunadjWithE <- cdModel(formula = f_PT_unadj_withE, 
-                          data = dataPT, constrained = TRUE)
-naturalCoef(ptCDunadjWithE)
+naturalCoef(models$PT$unadj$withE$CD)
 @
@@
 However, the absolute value of \texttt{lambda} decreases from 
-\Sexpr{naturalCoef(ptCDunadjNoE)$lambda} to 
-\Sexpr{naturalCoef(ptCDunadjWithE)$lambda}
+\Sexpr{naturalCoef(models$PT$unadj$noE$CD)$lambda} to 
+\Sexpr{naturalCoef(models$PT$unadj$withE$CD)$lambda}
 when adding energy.
@@
 <<Portugal C-D adjusted without energy>>=
-ptCDadjNoE <- cdModel(formula = f_PT_adj_noE, 
-                      data = dataPT, constrained = TRUE)
-naturalCoef(ptCDadjNoE)
+naturalCoef(models$PT$adj$noE$CD)
 @
@@
 <<Portugal C-D adjusted with energy>>=
-ptCDadjWithE <- cdModel(formula = f_PT_adj_withE, 
-                          data = dataPT, constrained = TRUE)
-naturalCoef(ptCDadjWithE)
+naturalCoef(models$PT$adj$withE$CD)
 @
@@
 Using quality-adjusted inputs, the Solow residual (\texttt{lambda}) moves from 
-\Sexpr{naturalCoef(ptCDadjNoE)$lambda} to
-\Sexpr{naturalCoef(ptCDadjWithE)$lambda} when including energy.
+\Sexpr{naturalCoef(models$PT$adj$noE$CD)$lambda} to
+\Sexpr{naturalCoef(models$PT$adj$withE$CD)$lambda} when including energy.
 The absolute value of the Solow residual again decreases when adding energy.
@@
       \midrule
-      Without energy  & \Sexpr{naturalCoef(ptCDunadjNoE)$lambda}      & \Sexpr{naturalCoef(ptCDadjNoE)$lambda} \\
-      With energy     & \Sexpr{naturalCoef(ptCDunadjWithE)$lambda}    & \Sexpr{naturalCoef(ptCDadjWithE)$lambda} \\
+      Without energy  & \Sexpr{naturalCoef(models$PT$unadj$noE$CD)$lambda}    & \Sexpr{naturalCoef(models$PT$adj$noE$CD)$lambda} \\
+      With energy     & \Sexpr{naturalCoef(models$PT$unadj$withE$CD)$lambda}  & \Sexpr{naturalCoef(models$PT$adj$withE$CD)$lambda} \\
       \bottomrule
@@
 <<UK C-D>>=
-ukCDunadjNoE <- cdModel(formula = f_UK_unadj_noE, 
-                        data = dataUK, constrained = TRUE)
-ukCDunadjWithE <- cdModel(formula = f_UK_unadj_withE, 
-                          data = dataUK, constrained = TRUE)
-ukCDadjNoE <- cdModel(formula = f_UK_adj_noE, 
-                        data = dataUK, constrained = TRUE)
-ukCDadjWithE <- cdModel(formula = f_UK_adj_withE, 
-                          data = dataUK, constrained = TRUE)
 @
@@
       \midrule
-      Without energy  & \Sexpr{naturalCoef(ukCDunadjNoE)$lambda}      & \Sexpr{naturalCoef(ukCDadjNoE)$lambda} \\
-      With energy     & \Sexpr{naturalCoef(ukCDunadjWithE)$lambda}    & \Sexpr{naturalCoef(ukCDadjWithE)$lambda} \\
+      Without energy  & \Sexpr{naturalCoef(models$UK$unadj$noE$CD)$lambda}   & \Sexpr{naturalCoef(models$UK$adj$noE$CD)$lambda} \\
+      With energy     & \Sexpr{naturalCoef(models$UK$unadj$withE$CD)$lambda} & \Sexpr{naturalCoef(models$UK$adj$withE$CD)$lambda} \\
       \bottomrule
@@
 For the UK, the quality-adjusted, with energy Solow residual is 
-\Sexpr{naturalCoef(ukCDadjWithE)$lambda * 100}%,
+\Sexpr{naturalCoef(models$UK$adj$withE$CD)$lambda * 100}%,
 a very small number indeed.
@@
 can effectively eliminate the Solow residual,
-reducing it to \Sexpr{naturalCoef(ukCDadjWithE)$lambda}.
+reducing it to \Sexpr{naturalCoef(models$UK$adj$withE$CD)$lambda}.
 
 Interestingly, the Solow residual acutally increases from 
-\Sexpr{naturalCoef(ukCDunadjNoE)$lambda} to
-\Sexpr{naturalCoef(ukCDunadjWithE)$lambda}
+\Sexpr{naturalCoef(models$UK$unadj$noE$CD)$lambda} to
+\Sexpr{naturalCoef(models$UK$unadj$withE$CD)$lambda}
 for unadjusted factors of production when energy is added.
@@
 <<UK CD Unadjusted Coefficients>>=
-naturalCoef(ukCDunadjNoE)
-naturalCoef(ukCDunadjWithE)
+naturalCoef(models$UK$unadj$noE$CD)
+naturalCoef(models$UK$unadj$withE$CD)
 @
@@
 as \texttt{alpha\_1} moves from 
-\Sexpr{naturalCoef(ukCDunadjNoE)$alpha_1} to
-\Sexpr{naturalCoef(ukCDunadjWithE)$alpha_1}.
+\Sexpr{naturalCoef(models$UK$unadj$noE$CD)$alpha_1} to
+\Sexpr{naturalCoef(models$UK$unadj$withE$CD)$alpha_1}.
 
@@
 <<UK CD Quality-adjusted Coefficients>>=
-naturalCoef(ukCDadjNoE)
-naturalCoef(ukCDadjWithE)
+naturalCoef(models$UK$adj$noE$CD)
+naturalCoef(models$UK$adj$withE$CD)
 @
@@
 \texttt{alpha\_1} moves from 
-\Sexpr{naturalCoef(ukCDadjNoE)$alpha_1} to
-\Sexpr{naturalCoef(ukCDadjWithE)$alpha_1}.
+\Sexpr{naturalCoef(models$UK$adj$noE$CD)$alpha_1} to
+\Sexpr{naturalCoef(models$UK$adj$withE$CD)$alpha_1}.
 
@@
 
-<<PT CES-kl, warning=FALSE, eval=evalCES>>=
-ptCESklunadjNoE <- cesModel(formula = f_PT_unadj_noE, 
-                            nest = c(1,2), data = dataPT, constrained = TRUE)
-naturalCoef(ptCESklunadjNoE)
-ptCESkladjNoE <- cesModel(formula = f_PT_adj_noE, 
-                          nest = c(1,2), data = dataPT, constrained = TRUE)
-naturalCoef(ptCESkladjNoE)
-@
+<<PT CES-kl, warning=FALSE>>=
+naturalCoef(models$PT$unadj$noE$CESkl)
+naturalCoef(models$PT$adj$noE$CESkl)
+@
+
+Both unadjusted and quality-adjusted variables give positive Solow residuals,
+\Sexpr{naturalCoef(models$PT$unadj$noE$CESkl)$lambda} for unadjusted inputs and
+\Sexpr{naturalCoef(models$PT$adj$noE$CESkl)$lambda} for quality-adjusted inputs.
+Furthermore, quality-adjustment reduces the magnitude of the Solow residual.
 
@@
 
-First, look at unadjusted inputs using the ($kl$)$e$ nesting.
-
-<<PT CES-kle unadjusted, warning=FALSE, eval=evalCES>>=
-ptCESkleunadjWithE <- cesModel(formula = f_PT_unadj_withE, 
-                            nest = c(1,2,3), data = dataPT, constrained = TRUE)
-naturalCoef(ptCESkleunadjWithE)
+Now, look at unadjusted inputs using the ($kl$)$e$ nesting.
+
+<<PT CES-kle unadjusted, warning=FALSE>>=
+naturalCoef(models$PT$unadj$withE$CESkle)
 @
@@
 
-<<PT CES-kle quality-adjusted, warning=FALSE, eval=evalCES>>=
-ptCESkleadjWithE <- cesModel(formula = f_PT_adj_withE, 
-                          nest = c(1,2,3), data = dataPT, constrained = TRUE)
-naturalCoef(ptCESkleadjWithE)
+<<PT CES-kle quality-adjusted, warning=FALSE>>=
+naturalCoef(models$PT$adj$withE$CESkle)
 @
@@
       \midrule
-      Without energy  & \Sexpr{naturalCoef(ptCESklunadjNoE)$lambda}       & \Sexpr{naturalCoef(ptCESkladjNoE)$lambda} \\
-      With energy     & \Sexpr{naturalCoef(ptCESkleunadjWithE)$lambda}    & \Sexpr{naturalCoef(ptCESkleadjWithE)$lambda} \\
+      Without energy  & \Sexpr{naturalCoef(models$PT$unadj$noE$CESkl)$lambda} & \Sexpr{naturalCoef(models$PT$adj$noE$CESkl)$lambda} \\
+      With energy     & \Sexpr{naturalCoef(models$PT$unadj$withE$CESkle)$lambda} 
+                                                                    & \Sexpr{naturalCoef(models$PT$adj$withE$CESkle)$lambda} \\
       \bottomrule
@@
 
-The Solow residual is positive, and 
-quality-adjusting the inputs 
-reduces the Solow residual (\texttt{lambda}).
+In contrast to the Cobb-Douglas model,
+the CES model with ($kl$)$e$ nesting
+produces positive Solow residuals in all cases. 
+We also see that both 
+quality-adjusting the inputs and
+including energy
+reduce the Solow residual (\texttt{lambda}).
 
@@
 
-<<PT CES-lek unadjusted, warning=FALSE, eval=evalCES>>=
-ptCESlekunadjWithE <- cesModel(formula = f_PT_unadj_withE, 
-                            nest = c(2,3,1), data = dataPT, constrained = TRUE)
-naturalCoef(ptCESlekunadjWithE)
+<<PT CES-lek unadjusted, warning=FALSE>>=
+naturalCoef(models$PT$unadj$withE$CESlek)
 @
@@
 
-<<PT CES-lek quality-adjusted, warning=FALSE, eval=evalCES>>=
-ptCESlekadjWithE <- cesModel(formula = f_PT_adj_withE, 
-                          nest = c(2,3,1), data = dataPT, constrained = TRUE)
-naturalCoef(ptCESlekadjWithE)
+<<PT CES-lek quality-adjusted, warning=FALSE>>=
+naturalCoef(models$PT$adj$withE$CESlek)
 @
@@
       \midrule
-      Without energy  & \Sexpr{naturalCoef(ptCESklunadjNoE)$lambda}       & \Sexpr{naturalCoef(ptCESkladjNoE)$lambda} \\
-      With energy     & \Sexpr{naturalCoef(ptCESlekunadjWithE)$lambda}    & \Sexpr{naturalCoef(ptCESlekadjWithE)$lambda} \\
+      Without energy  & \Sexpr{naturalCoef(models$PT$unadj$noE$CESkl)$lambda} & \Sexpr{naturalCoef(models$PT$adj$noE$CESkl)$lambda} \\
+      With energy     & \Sexpr{naturalCoef(models$PT$unadj$withE$CESlek)$lambda} & \Sexpr{naturalCoef(models$PT$adj$withE$CESle)$lambda} \\
       \bottomrule
@@
 
-The Solow residual is positive, and 
-quality-adjusting the inputs 
-reduces the Solow residual (\texttt{lambda}).
-
-%------------------------------
-\subsubsection{($ek$)$k$ nesting} 
+Similar to the CES model with ($kl$)$e$ nesting,
+the CES model with ($le$)$k$ nesting
+produces positive Solow residuals in all cases. 
+After energy has been added, quality-adjustment 
+has very little effect on the Solow residual,
+creating a slight increase from 
+\Sexpr{naturalCoef(models$PT$unadj$withE$CESlek)$lambda} to
+\Sexpr{naturalCoef(models$PT$adj$withE$CESlek)$lambda}.
+
+%------------------------------
+\subsubsection{($ek$)$l$ nesting} 
 %------------------------------
@@
 
-<<PT CES-ekl unadjusted, warning=FALSE, eval=evalCES>>=
-ptCESeklunadjWithE <- cesModel(formula = f_PT_unadj_withE, 
-                            nest = c(3,1,2), data = dataPT, constrained = TRUE)
-naturalCoef(ptCESeklunadjWithE)
+<<PT CES-ekl unadjusted, warning=FALSE>>=
+naturalCoef(models$PT$unadj$withE$CESekl)
 @
@@
 
-<<PT CES-ekl quality-adjusted, warning=FALSE, eval=evalCES>>=
-ptCESekladjWithE <- cesModel(formula = f_PT_adj_withE, 
-                          nest = c(3,1,2), data = dataPT, constrained = TRUE)
-naturalCoef(ptCESekladjWithE)
+<<PT CES-ekl quality-adjusted, warning=FALSE>>=
+naturalCoef(models$PT$adj$withE$CESekl)
 @
@@
       \midrule
-      Without energy  & \Sexpr{naturalCoef(ptCESklunadjNoE)$lambda}       & \Sexpr{naturalCoef(ptCESkladjNoE)$lambda} \\
-      With energy     & \Sexpr{naturalCoef(ptCESeklunadjWithE)$lambda}    & \Sexpr{naturalCoef(ptCESekladjWithE)$lambda} \\
+      Without energy  & \Sexpr{naturalCoef(models$PT$unadj$noE$CESkl)$lambda} & \Sexpr{naturalCoef(models$PT$adj$noE$CESkl)$lambda} \\
+      With energy     & \Sexpr{naturalCoef(models$PT$unadj$withE$CESekl)$lambda} 
+                                                                          & \Sexpr{naturalCoef(models$PT$adj$withE$CESekl)$lambda} \\
       \bottomrule
@@
 
-The Solow residual is positive, and 
+For the ($ek$)$l$ nesting, 
+the Solow residual is positive, and 
 quality-adjusting the inputs 
 reduces the Solow residual (\texttt{lambda}).
+Adding energy decreases the Solow residual 
+(from \Sexpr{naturalCoef(models$PT$unadj$withE$CESekl)$lambda} to 
+\Sexpr{naturalCoef(models$PT$adj$withE$CESekl)$lambda})
+when enegy is included in the model.
+But, adding energy slightly increases the Solow residual
+(from \Sexpr{naturalCoef(models$PT$adj$noE$CESkl)$lambda} to \Sexpr{naturalCoef(models$PT$adj$withE$CESekl)$lambda})
+when quality-adjusted inputs are used.
+
+%++++++++++++++++++++++++++++++
+\subsection{Do we obtain a positive Solow residual for the UK with the CES model?} 
+\label{sec:Solow_positive_for_UK_in_CES?}
+%++++++++++++++++++++++++++++++
+
+First, look at the CES model without energy.
+Nesting is unabmiguous, so this fit does not need to be repeated
+for each nesting option.
+
+<<UK CES-kl, warning=FALSE>>=
+naturalCoef(models$UK$unadj$noE$CESkl)
+naturalCoef(models$UK$adj$noE$CESkl)
+@
+
+Both unadjusted and quality-adjusted variables give positive Solow residuals for the UK,
+\Sexpr{naturalCoef(models$UK$unadj$noE$CESkl)$lambda} for unadjusted inputs and
+\Sexpr{naturalCoef(models$UK$adj$noE$CESkl)$lambda} for quality-adjusted inputs.
+Furthermore, quality-adjustment reduces the magnitude of the UK Solow residual.
+
+%------------------------------
+\subsubsection{($kl$)$e$ nesting} 
+%------------------------------
+
+Now, look at unadjusted inputs using the ($kl$)$e$ nesting.
+
+<<UK CES-kle unadjusted>>=
+naturalCoef(models$UK$unadj$withE$CESkle)
+@
+
+Now look at quality-adjusted inputs using the ($kl$)$e$ nesting.
+
+<<UK CES-kle quality-adjusted>>=
+naturalCoef(models$UK$adj$withE$CESkle)
+@
+
+Table~\ref{tab:lambda_CES-kle_UK} summarizes the UK Solow residual results with CES and the ($kl$)$e$ nesting.
+
+\begin{table} \caption{UK Solow residual results with CES and ($kl$)$e$ nesting.} 
+\label{tab:lambda_CES-kle_UK} 
+  \begin{center}
+    \begin{tabular}{r c c} 
+      \toprule
+                      & Unadjusted     & Quality-adjusted   \\
+      \midrule
+      Without energy  & \Sexpr{naturalCoef(models$UK$unadj$noE$CESkl)$lambda} & \Sexpr{naturalCoef(models$UK$adj$noE$CESkl)$lambda} \\
+      With energy     & \Sexpr{naturalCoef(models$UK$unadj$withE$CESkle)$lambda} 
+                                                                & \Sexpr{naturalCoef(models$UK$adj$withE$CESkle)$lambda} \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+\end{table}
+
+Like the Cobb-Douglas model, the CES model produces positive Solow residuals
+with the ($kl$)$e$ nesting.
+We also see that both 
+quality-adjusting the inputs and
+including energy
+reduce the Solow residual (\texttt{lambda}).
+
+%------------------------------
+\subsubsection{($le$)$k$ nesting}
+%------------------------------
+
+Next, look at unadjusted inputs using the ($le$)$k$ nesting.
+
+<<UK CES-lek unadjusted>>=
+naturalCoef(models$UK$unadj$withE$CESlek)
+@
+
+Now look at quality-adjusted inputs using the ($le$)$k$ nesting.
+
+<<UK CES-lek quality-adjusted>>=
+naturalCoef(models$UK$adj$withE$CESlek)
+@
+
+Table~\ref{tab:lambda_CES-lek_UK} summarizes the UK Solow residual results with CES and the ($le$)$k$ nesting.
+
+\begin{table} \caption{UK Solow residual results with CES and ($le$)$k$ nesting.} 
+\label{tab:lambda_CES-lek_UK} 
+  \begin{center}
+    \begin{tabular}{r c c} 
+      \toprule
+                      & Unadjusted     & Quality-adjusted   \\
+      \midrule
+      Without energy  & \Sexpr{naturalCoef(models$UK$unadj$noE$CESkl)$lambda} & \Sexpr{naturalCoef(models$UK$adj$noE$CESkl)$lambda} \\
+      With energy     & \Sexpr{naturalCoef(models$UK$unadj$withE$CESlek)$lambda} 
+                                                            & \Sexpr{naturalCoef(models$UK$adj$withE$CESlek)$lambda} \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+\end{table}
+
+Similar to the CES model with ($kl$)$e$ nesting,
+the CES model with ($le$)$k$ nesting
+produces positive Solow residuals in all cases. 
+Both quality-adjustment and inclusion of energy 
+decrease the magnitude of the Solow residual.
+
+%------------------------------
+\subsubsection{($ek$)$l$ nesting}
+%------------------------------
+
+Next, look at unadjusted inputs using the ($el$)$l$ nesting.
+
+<<UK CES-ekl unadjusted>>=
+naturalCoef(models$UK$unadj$withE$CESekl)
+@
+
+Now look at quality-adjusted inputs using the ($ek$)$l$ nesting.
+
+<<UK CES-ekl quality-adjusted>>=
+naturalCoef(models$UK$adj$withE$CESekl)
+@
+
+Table~\ref{tab:lambda_CES-ekl_UK} summarizes the UK Solow residual results with CES and the ($ek$)$l$ nesting.
+
+\begin{table} \caption{UK Solow residual results with CES and ($ek$)$l$ nesting.} 
+\label{tab:lambda_CES-ekl_UK} 
+  \begin{center}
+    \begin{tabular}{r c c} 
+      \toprule
+                      & Unadjusted     & Quality-adjusted   \\
+      \midrule
+      Without energy  & \Sexpr{naturalCoef(models$UK$unadj$noE$CESkl)$lambda} & \Sexpr{naturalCoef(models$UK$adj$noE$CESkl)$lambda} \\
+      With energy     & \Sexpr{naturalCoef(models$UK$unadj$withE$CESekl)$lambda} 
+                                                            & \Sexpr{naturalCoef(models$UK$adj$withE$CESekl)$lambda} \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+\end{table}
+
+Similar to the CES model with ($ek$)$l$ nesting,
+the CES model with ($ek$)$l$ nesting
+produces positive Solow residuals in all cases. 
+Both quality-adjustment and inclusion of energy 
+decrease the magnitude of the Solow residual.
 

### 2015-04-27 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Added comments about rerunning models.

@@
 
+# Tell whether to re-run the analysis to create the models.
+# This file will use previously-saved models to generate
+# the paper if set to FALSE, greatly reducing time.
+# If something changes in the data or in the code that
+# performs the analysis, set 
+# rerunModels = TRUE
+# once to re-generate the information needed to 
+# create the paper.
 #####################################################

### 2015-04-29 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Improved authors. Improved text.

@@
 
+\author[IST]{João dos Santos}
 \author[Leeds]{Paul Brockway}
-\author[IST]{Tiago Domingos}
 \author[CalvinEngr]{Matthew Kuperus Heun\corref{cor1}}
 \ead{mkh2@calvin.edu}
-
-% \address[IST]{IST, Lisbon, Portugal}
-% \address[Leeds]{Leeds University, Leeds, UK}
-% \cortext[cor1]{Corresponding author}
-% \address[CalvinEngr]{Engineering Department, Calvin College, Grand Rapids, MI 49546, USA}
+\author[Leeds]{Marco Sekai}
+\author[IST]{Tiago Domingos}
+\author[Leeds]{Julia Steinberger}
+
+\address[IST]{IST, Lisbon, Portugal}
+\address[Leeds]{Leeds University, Leeds, UK}
+\address[CalvinEngr]{Engineering Department, Calvin College, Grand Rapids, MI 49546, USA}
+\cortext[cor1]{Corresponding author}
 
@@
 %
-$\theta$ is expected to be near unity.
-
 Note that for the CES model, $\texttt{scale} = \gamma$ and is expected to be close to unity.
-Equations for $\alpha_1$, $\alpha_2$, and $\alpha_3$ are given in Table \ref{tab:CES_abg_equations}.
-
-\begin{table} \caption{Equations for $\alpha$, $\beta$, and $\gamma$ for the various CES nestings, 
+
+For the CES model, values of $\alpha_1$, $\alpha_2$, and $\alpha_3$ are calculated by
+$\alpha_1 = \delta_1$, $\alpha_2 = 1 - \delta_1$, and $\alpha_3 = 0$ 
+for the CES model with two factors of production
+and by 
+$\alpha_1 = \delta \delta_1$, $\alpha_2 = \delta(1 - \delta_1)$, and $\alpha_3 = 1 - \delta$
+for the CES model with three factors of production.
+The values of $\alpha_1$, $\alpha_2$, and $\alpha_3$ are interpreted as
+$\alpha$, $\beta$, and $\gamma$ (coefficients for capital, labor, and energy, respectively)
+as shown in Table \ref{tab:CES_abg_equations}, 
+assuming factors of production are specified in the fitting \texttt{formula} as
+\texttt{y~$\sim$~k~+~l~+~e~+~time}.
+
+\begin{table} \caption{Equations for $\alpha$, $\beta$, and $\gamma$ 
+                        (importance of capital, labor, and energy, respectively)
+                        for the various CES nestings, 
                         provided that the \texttt{formula} is specified as \texttt{y~$\sim$~k~+~l~+~e~+~time}.} 
@@
       \toprule
-      Nesting         & \texttt{nest}     & $\alpha_1$ ($\alpha$)   & $\alpha_2$ ($\beta$)    & $\alpha_3$ ($\gamma$)       \\
+      Nesting         & \texttt{nest}     & $\alpha$                & $\beta$                 & $\gamma$       \\
       \midrule
@@
 the effect of both quality-corrected factors of production and energy.
-We find that both including energy and quality-adjusting the factors of production 
-reduce the Solow residual (\texttt{lambda}). 
+We find that including energy as a factor of production 
+reduces the absolute value of the Solow residual (\texttt{lambda})
+whether or not the factors of production are quality-adjusted. 
 Quality-adjustment gets part of the way toward eliminating the Solow residual.
-Including energy (whether or not the factors of production are quality-adjusted)
-reduces the Solow residual significantly.
 
@@
 
-Note that the contribution of capital (\texttt{alpha\_1})
+Note that for Portugal the contribution of capital (\texttt{alpha\_1})
 always shifts to energy (\texttt{alpha\_3}) when energy is included 
@@
 
-<<UK C-D>>=
-@
+Table~\ref{tab:lambda_CD_UK} shows fitted Cobb-Douglas coefficients for the UK.
 
@@
       \midrule
-      Without energy  & \Sexpr{naturalCoef(models$UK$unadj$noE$CD)$lambda}   & \Sexpr{naturalCoef(models$UK$adj$noE$CD)$lambda} \\
-      With energy     & \Sexpr{naturalCoef(models$UK$unadj$withE$CD)$lambda} & \Sexpr{naturalCoef(models$UK$adj$withE$CD)$lambda} \\
+      Without energy  & \Sexpr{naturalCoef(models$UK$unadj$noE$CD)$lambda}   
+                                                & \Sexpr{naturalCoef(models$UK$adj$noE$CD)$lambda} \\
+      With energy     & \Sexpr{naturalCoef(models$UK$unadj$withE$CD)$lambda} 
+                                                & \Sexpr{naturalCoef(models$UK$adj$withE$CD)$lambda} \\
       \bottomrule
@@
 For the UK, the quality-adjusted, with energy Solow residual is 
-\Sexpr{naturalCoef(models$UK$adj$withE$CD)$lambda * 100}%,
+\Sexpr{naturalCoef(models$UK$adj$withE$CD)$lambda * 100}\%,
 a very small number indeed.
-For the UK, it appears that both quality-adjustment and addition of energy as a factor of production
-can effectively eliminate the Solow residual,
+For the UK, it appears that \emph{both} quality-adjustment and addition of energy as a factor of production
+are required to effectively eliminate the Solow residual,
 reducing it to \Sexpr{naturalCoef(models$UK$adj$withE$CD)$lambda}.
 
-Interestingly, the Solow residual acutally increases from 
+Adding energy alone actually \emph{in}creases the Solow residual from 
 \Sexpr{naturalCoef(models$UK$unadj$noE$CD)$lambda} to
-\Sexpr{naturalCoef(models$UK$unadj$withE$CD)$lambda}
-for unadjusted factors of production when energy is added.
-To find out why, let's look at all the coefficients.
+\Sexpr{naturalCoef(models$UK$unadj$withE$CD)$lambda}.
+The details for each model with unadjusted factors of production are shown below.
 
@@
 for each nesting option. 
+(This means that the top rows of Tables~\ref{tab:lambda_CES-kle_PT}--\ref{tab:lambda_CES-ekl_PT}
+are identical.)
 
@@
 for each nesting option. 
+(This means that the top rows of Tables~\ref{tab:lambda_CES-kle_UK}--\ref{tab:lambda_CES-ekl_UK}
+are identical.)
 

### 2015-04-29 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Editing the text.

@@
 estimates CES production 
-functions of the following forms (among others):
+functions of the following form
+%
+\begin{equation} \label{eq:CESgeneric}
+  y = \gamma \: A \: \left\{\delta \left[\delta_1 x_1^{-\rho_1} 
+      + (1-\delta_1)x_2^{-\rho_1} \right]^{\rho/\rho_1} 
+      + (1-\delta) x_3^{-\rho} \right\}^{-1/\rho}; 
+      A \equiv \mathrm{e}^{\lambda (t-t_0)},
+\end{equation}
+%
+where $x_1$, $x_2$, and $x_3$ are factors of production
+and permutations of capital~($k$), labor~($l$), and energy~($e$).
+
+The CES model without energy is given in Equation~\ref{eq:CESkl}.
 %
@@
       + (1-\delta_1)l^{-\rho_1} \right]^{-1/\rho_1}; 
-      A \equiv \mathrm{e}^{\lambda (t-t_0)}  
-\end{equation}
+      A \equiv \mathrm{e}^{\lambda (t-t_0)} . 
+\end{equation}
+%
+Equation~\ref{eq:CESkle} augments Equation~\ref{eq:CESkl} with energy 
+using a ($kl$)($e$) nesting structure, as is typical in the literature. 
+Equation~\ref{eq:CESkl} is a degenerate form of Equation~\ref{eq:CESkle} 
+where $\delta \rightarrow 1$. 
 %
@@
       + (1-\delta) e^{-\rho} \right\}^{-1/\rho}; 
-      A \equiv \mathrm{e}^{\lambda (t-t_0)}
-\end{equation}
-%
-Equation~\ref{eq:CESkl} is a CES production function with 
-capital stock ($k$) and labor ($l$) factors of production. 
-Equation~\ref{eq:CESkle} augments Equation~\ref{eq:CESkl} with energy 
-using a ($kl$)($e$) nesting structure, as is typical in the literature. 
-Equation~\ref{eq:CESkl} is a degenerate form of Equation~\ref{eq:CESkle} 
-where $\delta \rightarrow 1$.
-
-$\gamma$ is a fitting parameter that represents productivity. 
+      A \equiv \mathrm{e}^{\lambda (t-t_0)}.
+\end{equation}
+%
+
+In the CES production function, 
+$\gamma$ is a fitting parameter that accounts for an atypical first year. 
 The fitting parameters $\rho_1$ and $\rho$ indicate elasticities 
@@
 % 
-Note that the $\rho$ ($\sigma$) and $\delta$ parameters have different
+Note that $\rho$ ($\sigma$), $\delta$, and $\delta_1$ have different
 meanings that depend upon the nesting of the factors of production.

### 2015-05-01 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Added rho_1.
Word changes.
Working toward making graphs.

@@
 require(dplyr)
+require(reshape2)
+require(ggplot2)
 
@@
 % 
-Note that $\rho$ ($\sigma$), $\delta$, and $\delta_1$ have different
-meanings that depend upon the nesting of the factors of production.
+Note that $\rho$ ($\sigma$), $\rho_1$ ($\sigma_1$), $\delta$, and $\delta_1$ have different
+meanings depending upon the nesting of the factors of production.
 
@@
 @
+
+For unadjusted variables, we use the time series shown in Table~\ref{tab:unadjusted_variables}.
+
+\begin{table} \caption{Unadjusted time-series variables.} 
+\label{tab:unadjusted_variables} 
+  \begin{center}
+    \begin{tabular}{r l l} 
+      \toprule
+      Variable    & Portugal           & UK                 \\
+      \midrule
+      Output      & \Sexpr{y_PT}       & \Sexpr{y_UK}       \\
+      Capital     & \Sexpr{k_PT_unadj} & \Sexpr{k_UK_unadj} \\
+      Labor       & \Sexpr{l_PT_unadj} & \Sexpr{l_UK_unadj} \\
+      Energy      & \Sexpr{e_PT_unadj} & \Sexpr{e_UK_unadj} \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+\end{table}
+
+For quality-adjusted variables, we use the time series shown in Table~\ref{tab:quality_adjusted_variables}.
+
+\begin{table} \caption{Quality-adjusted time series variables.} 
+\label{tab:quality_adjusted_variables} 
+  \begin{center}
+    \begin{tabular}{r l l} 
+      \toprule
+      Variable    & Portugal         & UK               \\
+      \midrule
+      Output      & \Sexpr{y_PT}     & \Sexpr{y_UK}     \\
+      Capital     & \Sexpr{k_PT_adj} & \Sexpr{k_UK_adj} \\
+      Labor       & \Sexpr{l_PT_adj} & \Sexpr{l_UK_adj} \\
+      Energy      & \Sexpr{e_PT_adj} & \Sexpr{e_UK_adj} \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+\end{table}
+
+<<Historical Data, fig.pos="H", fig.align='center', fig.width=6.6, fig.height=7, fig.cap="Historical data.">>=
+mdata <- melt(historicalData, 
+              measure.vars = c(as.character(y_PT), 
+                               as.character(k_PT_unadj), as.character(l_PT_unadj), as.character(e_PT_unadj),
+                               as.character(k_PT_adj), as.character(l_PT_adj), as.character(e_PT_adj),
+                               as.character(y_UK), 
+                               as.character(k_UK_unadj), as.character(l_UK_unadj), as.character(e_UK_unadj),
+                               as.character(k_UK_adj), as.character(l_UK_adj), as.character(e_UK_adj)), 
+              variable.name = "variable",
+              value.name = "value")
+historicalPlot(mdata, 
+               mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
+               facet_formula = Country ~ Source, 
+               line_types = c(1,5,2,6,4,3)) + 
+  xlab("") + 
+  ylab("Indexed (1960=1 or 1970=1)")
+
+ggplot(mdata, mapping=aes(x=Year, y=value, group=variable) + 
+  geom_line(mapping) +
+  facet_grid( facet_formula, scales="free_y" ) + 
+  scale_linetype_manual(name="", values=line_types) + 
+  xy_theme()
+
+@
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Parameter Estimation}
+\label{sec:parameter_estimation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Parameter estimation is accomplished with \texttt{formula}s of the form
+%
+\begin{equation} \label{eq:formulas}
+  y \sim x_1 + x_2 + x_3 + time,
+\end{equation}
+%
+where $y$ is economic output and 
+$x_1$, $x_2$, and $x_3$ are factors of production
+and permutations of
+capital ($k$), labor ($l$), and energy ($e$).
+(The factors of production may be quality-adjusted.)
+$time$ is the time variable, usually \texttt{iYear}. 
+The \texttt{formula}s are used in a fitting function such as 
+\texttt{cdModel} to create a \texttt{model} object.
+The function \texttt{naturalCoef} extracts reasonable
+coefficients from \texttt{model} objects.
+
+Note that in the fitting process for the Cobb-Douglas equation,
+$\texttt{scale} = \theta$, 
+$\alpha_1 = \alpha$,
+$\alpha_2 = \beta$, and
+$\alpha_3 = \gamma$,
+when the \texttt{formula} is specified as 
+%
+\begin{equation} \label{eq:formula_kle}
+  \texttt{y} \sim \texttt{k + l + e + time}.
+\end{equation}
+%
+Note that for the CES model, $\texttt{scale} = \gamma$ and is expected to be close to unity.
+
+For the CES model, values of $\alpha_1$, $\alpha_2$, and $\alpha_3$ are calculated by
+$\alpha_1 = \delta_1$, $\alpha_2 = 1 - \delta_1$, and $\alpha_3 = 0$ 
+for the CES model with two factors of production
+and by 
+$\alpha_1 = \delta \delta_1$, $\alpha_2 = \delta(1 - \delta_1)$, and $\alpha_3 = 1 - \delta$
+for the CES model with three factors of production.
+The values of $\alpha_1$, $\alpha_2$, and $\alpha_3$ are interpreted as
+$\alpha$, $\beta$, and $\gamma$ (coefficients for capital, labor, and energy, respectively)
+as shown in Table \ref{tab:CES_abg_equations}, 
+assuming factors of production are specified in the fitting \texttt{formula} as
+\texttt{y~$\sim$~k~+~l~+~e~+~time}.
+
+\begin{table} \caption{Equations for $\alpha$, $\beta$, and $\gamma$ 
+                        (importance of capital, labor, and energy, respectively)
+                        for the various CES nestings, 
+                        provided that the \texttt{formula} is specified as \texttt{y~$\sim$~k~+~l~+~e~+~time}.} 
+\label{tab:CES_abg_equations} 
+  \begin{center}
+    \begin{tabular}{c c c c c} 
+      \toprule
+      Nesting         & \texttt{nest}     & $\alpha$                & $\beta$                 & $\gamma$       \\
+      \midrule
+      ($kl$) + ()     & \texttt{c(1,2)}   & $\delta_1$              & $1 - \delta_1$          & 0          \\
+      ($kl$) + ($e$)  & \texttt{c(1,2,3)} & $\delta \delta_1$       & $\delta (1 - \delta_1)$ & $1 - \delta$ \\   
+      ($le$) + ($k$)  & \texttt{c(2,3,1)} & $1 - \delta$            & $\delta \delta_1$       & $\delta (1 - \delta_1)$ \\
+      ($ek$) + ($l$)  & \texttt{c(3,1,2)} & $\delta (1 - \delta_1)$ & $1 - \delta$            & $\delta \delta_1$ \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+\end{table}
 
@@
 
-For unadjusted variables, we use the time series shown in Table~\ref{tab:unadjusted_variables}.
-
-\begin{table} \caption{Unadjusted variables.} 
-\label{tab:unadjusted_variables} 
-  \begin{center}
-    \begin{tabular}{r l l} 
-      \toprule
-      Variable    & Portugal           & UK                 \\
-      \midrule
-      Output      & \Sexpr{y_PT}       & \Sexpr{y_UK}       \\
-      Capital     & \Sexpr{k_PT_unadj} & \Sexpr{k_UK_unadj} \\
-      Labor       & \Sexpr{l_PT_unadj} & \Sexpr{l_UK_unadj} \\
-      Energy      & \Sexpr{e_PT_unadj} & \Sexpr{e_UK_unadj} \\
-      \bottomrule
-    \end{tabular}
-  \end{center}
-\end{table}
-
-For quality-adjusted variables, we use the time series shown in Table~\ref{tab:quality_adjusted_variables}.
-
-\begin{table} \caption{Unadjusted variables.} 
-\label{tab:quality_adjusted_variables} 
-  \begin{center}
-    \begin{tabular}{r l l} 
-      \toprule
-      Variable    & Portugal         & UK               \\
-      \midrule
-      Output      & \Sexpr{y_PT}     & \Sexpr{y_UK}     \\
-      Capital     & \Sexpr{k_PT_adj} & \Sexpr{k_UK_adj} \\
-      Labor       & \Sexpr{l_PT_adj} & \Sexpr{l_UK_adj} \\
-      Energy      & \Sexpr{e_PT_adj} & \Sexpr{e_UK_adj} \\
-      \bottomrule
-    \end{tabular}
-  \end{center}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Parameter Estimation}
-\label{sec:parameter_estimation}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Parameter estimation is accomplished with \texttt{formula}s of the form
-%
-\begin{equation} \label{eq:formulas}
-  y \sim x_1 + x_2 + x_3 + time,
-\end{equation}
-%
-where $y$ is economic output and 
-$x_1$, $x_2$, and $x_3$ are factors of production
-and permutations of
-capital ($k$), labor ($l$), and energy ($e$).
-(The factors of production may be quality-adjusted.)
-$time$ is the time variable, usually \texttt{iYear}. 
-The \texttt{formula}s are used in a fitting function such as 
-\texttt{cdModel} to create a \texttt{model} object.
-The function \texttt{naturalCoef} extracts reasonable
-coefficients from \texttt{model} objects.
-
-Note that in the fitting process for the Cobb-Douglas equation,
-$\texttt{scale} = \theta$, 
-$\alpha_1 = \alpha$,
-$\alpha_2 = \beta$, and
-$\alpha_3 = \gamma$,
-when the \texttt{formula} is specified as 
-%
-\begin{equation} \label{eq:formula_kle}
-  \texttt{y} \sim \texttt{k + l + e + time}.
-\end{equation}
-%
-Note that for the CES model, $\texttt{scale} = \gamma$ and is expected to be close to unity.
-
-For the CES model, values of $\alpha_1$, $\alpha_2$, and $\alpha_3$ are calculated by
-$\alpha_1 = \delta_1$, $\alpha_2 = 1 - \delta_1$, and $\alpha_3 = 0$ 
-for the CES model with two factors of production
-and by 
-$\alpha_1 = \delta \delta_1$, $\alpha_2 = \delta(1 - \delta_1)$, and $\alpha_3 = 1 - \delta$
-for the CES model with three factors of production.
-The values of $\alpha_1$, $\alpha_2$, and $\alpha_3$ are interpreted as
-$\alpha$, $\beta$, and $\gamma$ (coefficients for capital, labor, and energy, respectively)
-as shown in Table \ref{tab:CES_abg_equations}, 
-assuming factors of production are specified in the fitting \texttt{formula} as
-\texttt{y~$\sim$~k~+~l~+~e~+~time}.
-
-\begin{table} \caption{Equations for $\alpha$, $\beta$, and $\gamma$ 
-                        (importance of capital, labor, and energy, respectively)
-                        for the various CES nestings, 
-                        provided that the \texttt{formula} is specified as \texttt{y~$\sim$~k~+~l~+~e~+~time}.} 
-\label{tab:CES_abg_equations} 
-  \begin{center}
-    \begin{tabular}{c c c c c} 
-      \toprule
-      Nesting         & \texttt{nest}     & $\alpha$                & $\beta$                 & $\gamma$       \\
-      \midrule
-      ($kl$) + ()     & \texttt{c(1,2)}   & $\delta_1$              & $1 - \delta_1$          & 0          \\
-      ($kl$) + ($e$)  & \texttt{c(1,2,3)} & $\delta \delta_1$       & $\delta (1 - \delta_1)$ & $1 - \delta$ \\   
-      ($le$) + ($k$)  & \texttt{c(2,3,1)} & $1 - \delta$            & $\delta \delta_1$       & $\delta (1 - \delta_1)$ \\
-      ($ek$) + ($l$)  & \texttt{c(3,1,2)} & $\delta (1 - \delta_1)$ & $1 - \delta$            & $\delta \delta_1$ \\
-      \bottomrule
-    \end{tabular}
-  \end{center}
-\end{table}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-05-04 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Creating graphs.

--- 2015-04-29 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
@@
 @
+
+For unadjusted variables, we use the time series shown in Table~\ref{tab:unadjusted_variables}.
+
+\begin{table} \caption{Unadjusted time-series variables.} 
+\label{tab:unadjusted_variables} 
+  \begin{center}
+    \begin{tabular}{r l l} 
+      \toprule
+      Variable    & Portugal           & UK                 \\
+      \midrule
+      Output      & \Sexpr{y_PT}       & \Sexpr{y_UK}       \\
+      Capital     & \Sexpr{k_PT_unadj} & \Sexpr{k_UK_unadj} \\
+      Labor       & \Sexpr{l_PT_unadj} & \Sexpr{l_UK_unadj} \\
+      Energy      & \Sexpr{e_PT_unadj} & \Sexpr{e_UK_unadj} \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+\end{table}
+
+For quality-adjusted variables, we use the time series shown in Table~\ref{tab:quality_adjusted_variables}.
+
+\begin{table} \caption{Quality-adjusted time series variables.} 
+\label{tab:quality_adjusted_variables} 
+  \begin{center}
+    \begin{tabular}{r l l} 
+      \toprule
+      Variable    & Portugal         & UK               \\
+      \midrule
+      Output      & \Sexpr{y_PT}     & \Sexpr{y_UK}     \\
+      Capital     & \Sexpr{k_PT_adj} & \Sexpr{k_UK_adj} \\
+      Labor       & \Sexpr{l_PT_adj} & \Sexpr{l_UK_adj} \\
+      Energy      & \Sexpr{e_PT_adj} & \Sexpr{e_UK_adj} \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+\end{table}
+
+<<Historical Data, fig.pos="H", fig.align='center', fig.width=6.6, fig.height=7, fig.cap="Historical data.">>=
+mdata <- melt(historicalData, 
+              measure.vars = c(as.character(y_PT), 
+                               as.character(k_PT_unadj), as.character(l_PT_unadj), as.character(e_PT_unadj),
+                               as.character(k_PT_adj), as.character(l_PT_adj), as.character(e_PT_adj),
+                               as.character(y_UK), 
+                               as.character(k_UK_unadj), as.character(l_UK_unadj), as.character(e_UK_unadj),
+                               as.character(k_UK_adj), as.character(l_UK_adj), as.character(e_UK_adj)), 
+              variable.name = "variable",
+              value.name = "value")
+historicalPlot(mdata, 
+               mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
+               facet_formula = Country ~ Source, 
+               line_types = c(1:11)) + 
+  xlab("") + 
+  ylab("Indexed (1960=1)")
+@
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Parameter Estimation}
+\label{sec:parameter_estimation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Parameter estimation is accomplished with \texttt{formula}s of the form
+%
+\begin{equation} \label{eq:formulas}
+  y \sim x_1 + x_2 + x_3 + time,
+\end{equation}
+%
+where $y$ is economic output and 
+$x_1$, $x_2$, and $x_3$ are factors of production
+and permutations of
+capital ($k$), labor ($l$), and energy ($e$).
+(The factors of production may be quality-adjusted.)
+$time$ is the time variable, usually \texttt{iYear}. 
+The \texttt{formula}s are used in a fitting function such as 
+\texttt{cdModel} to create a \texttt{model} object.
+The function \texttt{naturalCoef} extracts reasonable
+coefficients from \texttt{model} objects.
+
+Note that in the fitting process for the Cobb-Douglas equation,
+$\texttt{scale} = \theta$, 
+$\alpha_1 = \alpha$,
+$\alpha_2 = \beta$, and
+$\alpha_3 = \gamma$,
+when the \texttt{formula} is specified as 
+%
+\begin{equation} \label{eq:formula_kle}
+  \texttt{y} \sim \texttt{k + l + e + time}.
+\end{equation}
+%
+Note that for the CES model, $\texttt{scale} = \gamma$ and is expected to be close to unity.
+
+For the CES model, values of $\alpha_1$, $\alpha_2$, and $\alpha_3$ are calculated by
+$\alpha_1 = \delta_1$, $\alpha_2 = 1 - \delta_1$, and $\alpha_3 = 0$ 
+for the CES model with two factors of production
+and by 
+$\alpha_1 = \delta \delta_1$, $\alpha_2 = \delta(1 - \delta_1)$, and $\alpha_3 = 1 - \delta$
+for the CES model with three factors of production.
+The values of $\alpha_1$, $\alpha_2$, and $\alpha_3$ are interpreted as
+$\alpha$, $\beta$, and $\gamma$ (coefficients for capital, labor, and energy, respectively)
+as shown in Table \ref{tab:CES_abg_equations}, 
+assuming factors of production are specified in the fitting \texttt{formula} as
+\texttt{y~$\sim$~k~+~l~+~e~+~time}.
+
+\begin{table} \caption{Equations for $\alpha$, $\beta$, and $\gamma$ 
+                        (importance of capital, labor, and energy, respectively)
+                        for the various CES nestings, 
+                        provided that the \texttt{formula} is specified as \texttt{y~$\sim$~k~+~l~+~e~+~time}.} 
+\label{tab:CES_abg_equations} 
+  \begin{center}
+    \begin{tabular}{c c c c c} 
+      \toprule
+      Nesting         & \texttt{nest}     & $\alpha$                & $\beta$                 & $\gamma$       \\
+      \midrule
+      ($kl$) + ()     & \texttt{c(1,2)}   & $\delta_1$              & $1 - \delta_1$          & 0          \\
+      ($kl$) + ($e$)  & \texttt{c(1,2,3)} & $\delta \delta_1$       & $\delta (1 - \delta_1)$ & $1 - \delta$ \\   
+      ($le$) + ($k$)  & \texttt{c(2,3,1)} & $1 - \delta$            & $\delta \delta_1$       & $\delta (1 - \delta_1)$ \\
+      ($ek$) + ($l$)  & \texttt{c(3,1,2)} & $\delta (1 - \delta_1)$ & $1 - \delta$            & $\delta \delta_1$ \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+\end{table}
 

### 2015-05-04 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Now contains graphs.

--- 2015-04-29 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
@@
 @
+
+For unadjusted variables, we use the time series shown in Table~\ref{tab:unadjusted_variables}.
+
+\begin{table} \caption{Unadjusted time-series variables.} 
+\label{tab:unadjusted_variables} 
+  \begin{center}
+    \begin{tabular}{r l l} 
+      \toprule
+      Variable    & Portugal           & UK                 \\
+      \midrule
+      Output      & \Sexpr{y_PT}       & \Sexpr{y_UK}       \\
+      Capital     & \Sexpr{k_PT_unadj} & \Sexpr{k_UK_unadj} \\
+      Labor       & \Sexpr{l_PT_unadj} & \Sexpr{l_UK_unadj} \\
+      Energy      & \Sexpr{e_PT_unadj} & \Sexpr{e_UK_unadj} \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+\end{table}
+
+For quality-adjusted variables, we use the time series shown in Table~\ref{tab:quality_adjusted_variables}.
+
+\begin{table} \caption{Quality-adjusted time series variables.} 
+\label{tab:quality_adjusted_variables} 
+  \begin{center}
+    \begin{tabular}{r l l} 
+      \toprule
+      Variable    & Portugal         & UK               \\
+      \midrule
+      Output      & \Sexpr{y_PT}     & \Sexpr{y_UK}     \\
+      Capital     & \Sexpr{k_PT_adj} & \Sexpr{k_UK_adj} \\
+      Labor       & \Sexpr{l_PT_adj} & \Sexpr{l_UK_adj} \\
+      Energy      & \Sexpr{e_PT_adj} & \Sexpr{e_UK_adj} \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+\end{table}
+
+Unadjusted and quality-adjusted data for both Portugal and the United Kingdom 
+are shown in Figure~\ref{fig:Historical Data}.
+
+<<Historical Data, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Historical data.", warning=FALSE>>=
+unadjVars_PT <- c(y_PT, k_PT_unadj, l_PT_unadj, e_PT_unadj)
+unadjVars_UK <- c(y_UK, k_UK_unadj, l_UK_unadj, e_UK_unadj)
+commonVars <- c("Year", "iYear", "Country")
+unadjData_PT <- historicalData[ , as.character(unique(c(unadjVars_PT, commonVars)))] %>% filter(Country=="PT")
+unadjData_UK <- historicalData[ , as.character(unique(c(unadjVars_UK, commonVars)))] %>% filter(Country=="UK")
+unadjData <- plyr::rbind.fill(unadjData_PT, unadjData_UK)
+unadjData$adjusted <- "Unadjusted"
+
+adjVars_PT <- c(y_PT, k_PT_adj, l_PT_adj, e_PT_adj)
+adjVars_UK <- c(y_UK, k_UK_adj, l_UK_adj, e_UK_adj)
+adjData_PT <- historicalData[ , as.character(unique(c(adjVars_PT, commonVars)))] %>% filter(Country=="PT")
+adjData_UK <- historicalData[ , as.character(unique(c(adjVars_UK, commonVars)))] %>% filter(Country=="UK")
+adjData <- plyr::rbind.fill(adjData_PT, adjData_UK)
+adjData$adjusted <- "Quality-adjusted"
+
+trimmedData <- plyr::rbind.fill(unadjData, adjData)
+
+mdata <- melt(trimmedData, 
+              measure.vars = unique(as.character(c(unadjVars_PT, unadjVars_UK, adjVars_PT, adjVars_UK))), 
+              variable.name = "variable",
+              value.name = "value")
+
+# Relevel factors before plotting
+mdata$Country <- relevelFactor(as.factor(mdata$Country), c("PT", "UK"))
+mdata$adjusted <- relevelFactor(as.factor(mdata$adjusted), c("Unadjusted", "Quality-adjusted"))
+mdata$variable <- relevelFactor(as.factor(mdata$variable), unique(as.character(
+  c(y_PT, k_PT_unadj, l_PT_unadj, e_PT_unadj, k_PT_adj, l_PT_adj, e_PT_adj,
+    y_UK, k_UK_unadj, l_UK_unadj, e_UK_unadj, k_UK_adj, l_UK_adj, e_UK_adj))))
+
+historicalPlot(mdata, 
+               mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
+               facet_formula = Country ~ adjusted, 
+               line_types = c(1,2,4,3,2,4,3,2,3,2,3)) + 
+  scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12)) +
+  coord_cartesian(ylim=c(0.5, 13)) +
+  xlab("") + 
+  ylab("Indexed (1960=1)")
+@
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Parameter Estimation}
+\label{sec:parameter_estimation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Parameter estimation is accomplished with \texttt{formula}s of the form
+%
+\begin{equation} \label{eq:formulas}
+  y \sim x_1 + x_2 + x_3 + time,
+\end{equation}
+%
+where $y$ is economic output and 
+$x_1$, $x_2$, and $x_3$ are factors of production
+and permutations of
+capital ($k$), labor ($l$), and energy ($e$).
+(The factors of production may be quality-adjusted.)
+$time$ is the time variable, usually \texttt{iYear}. 
+The \texttt{formula}s are used in a fitting function such as 
+\texttt{cdModel} to create a \texttt{model} object.
+The function \texttt{naturalCoef} extracts reasonable
+coefficients from \texttt{model} objects.
+
+Note that in the fitting process for the Cobb-Douglas equation,
+$\texttt{scale} = \theta$, 
+$\alpha_1 = \alpha$,
+$\alpha_2 = \beta$, and
+$\alpha_3 = \gamma$,
+when the \texttt{formula} is specified as 
+%
+\begin{equation} \label{eq:formula_kle}
+  \texttt{y} \sim \texttt{k + l + e + time}.
+\end{equation}
+%
+Note that for the CES model, $\texttt{scale} = \gamma$ and is expected to be close to unity.
+
+For the CES model, values of $\alpha_1$, $\alpha_2$, and $\alpha_3$ are calculated by
+$\alpha_1 = \delta_1$, $\alpha_2 = 1 - \delta_1$, and $\alpha_3 = 0$ 
+for the CES model with two factors of production
+and by 
+$\alpha_1 = \delta \delta_1$, $\alpha_2 = \delta(1 - \delta_1)$, and $\alpha_3 = 1 - \delta$
+for the CES model with three factors of production.
+The values of $\alpha_1$, $\alpha_2$, and $\alpha_3$ are interpreted as
+$\alpha$, $\beta$, and $\gamma$ (coefficients for capital, labor, and energy, respectively)
+as shown in Table \ref{tab:CES_abg_equations}, 
+assuming factors of production are specified in the fitting \texttt{formula} as
+\texttt{y~$\sim$~k~+~l~+~e~+~time}.
+
+\begin{table} \caption{Equations for $\alpha$, $\beta$, and $\gamma$ 
+                        (importance of capital, labor, and energy, respectively)
+                        for the various CES nestings, 
+                        provided that the \texttt{formula} is specified as \texttt{y~$\sim$~k~+~l~+~e~+~time}.} 
+\label{tab:CES_abg_equations} 
+  \begin{center}
+    \begin{tabular}{c c c c c} 
+      \toprule
+      Nesting         & \texttt{nest}     & $\alpha$                & $\beta$                 & $\gamma$       \\
+      \midrule
+      ($kl$) + ()     & \texttt{c(1,2)}   & $\delta_1$              & $1 - \delta_1$          & 0          \\
+      ($kl$) + ($e$)  & \texttt{c(1,2,3)} & $\delta \delta_1$       & $\delta (1 - \delta_1)$ & $1 - \delta$ \\   
+      ($le$) + ($k$)  & \texttt{c(2,3,1)} & $1 - \delta$            & $\delta \delta_1$       & $\delta (1 - \delta_1)$ \\
+      ($ek$) + ($l$)  & \texttt{c(3,1,2)} & $\delta (1 - \delta_1)$ & $1 - \delta$            & $\delta \delta_1$ \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+\end{table}
 

### 2015-05-05 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Now using leaf_apply for fitted data.

@@
 }
-
+@
+
+<<Fitted_Data>>=
+  extract_fitted_comparison <- function(mod, id){
+    df <- mod$data[ , c("Year", "iGDP", "Country")]
+    # Trim fitted to be same length as df to eliminate problems with possible NAs at end of fitted
+    df$fitted <- yhat(mod)[c(1:length(df$Year))]
+    # Parse the id to find out whether this is quality-adjusted data
+    id_list <- strsplit(id, split = "[.]")[[1]]
+    if (id_list[[2]] == "unadj"){
+      df$adjusted <- "Unadjusted"
+    } else if (id_list[[2]] == "adj"){
+      df$adjusted <- "Quality-adjusted"
+    } else {
+      stop("Unknown adjustment.")
+    }
+    if (id_list[[3]] == "noE"){
+      df$energy <- "Without energy"
+    } else if (id_list[[3]] == "withE"){
+      df$energy <- "With energy"
+    } else {
+      stop("Unknown energy.")
+    }
+    df$model <- id_list[[4]]    
+    return(df)
+  }
+  fitted_data <- leaf_apply(models, extract_fitted_comparison, class=c("CDEmodel", "cesEst", "LINEXmodel"))
+  fitted_data <- do.call(rbind, fitted_data)
 @
@@
 
+Now, let's compare the fits to historical data.
+
 %++++++++++++++++++++++++++++++

### 2015-05-06 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Now includes graphs of fits to historical data.

--- 2015-05-04 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
@@
 }
-
+@
+
+<<Fitted_Data>>=
+extract_fitted_comparison <- function(mod, id){
+  df <- mod$data[ , c("Year", "iGDP", "Country")]
+  # Trim fitted to be same length as df to eliminate problems with possible NAs at end of fitted
+  df$fitted <- yhat(mod)[c(1:length(df$Year))]
+  # Parse the id to find out whether this is quality-adjusted data
+  id_list <- strsplit(id, split = "[.]")[[1]]
+  if (id_list[[2]] == "unadj"){
+    df$adjusted <- "Unadjusted"
+  } else if (id_list[[2]] == "adj"){
+    df$adjusted <- "Quality-adjusted"
+  } else {
+    stop("Unknown adjustment.")
+  }
+  if (id_list[[3]] == "noE"){
+    df$energy <- "Without energy"
+  } else if (id_list[[3]] == "withE"){
+    df$energy <- "With energy"
+  } else {
+    stop("Unknown energy.")
+  }
+  df$model <- id_list[[4]]    
+  return(df)
+}
+fitted_data <- leaf_apply(models, extract_fitted_comparison, class=c("CDEmodel", "cesEst", "LINEXmodel"))
+fitted_data <- do.call(rbind, fitted_data)
+# Melt fitted_data so it can be used for plotting
+# Relevel factors before plotting
+fitted_data$Country <- relevelFactor(as.factor(fitted_data$Country), c("PT", "UK"))
+fitted_data$adjusted <- relevelFactor(as.factor(fitted_data$adjusted), c("Unadjusted", "Quality-adjusted"))
+fitted_data$energy <- relevelFactor(as.factor(fitted_data$energy), c("Without energy", "With Energy"))
 @
@@
 \label{sec:results}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%++++++++++++++++++++++++++++++
+\subsection{Fits to historical data} 
+\label{sec:fits_to_historical_data}
+%++++++++++++++++++++++++++++++
+
+This section shows graphs of fits to historical data.
+
+<<Fitted Graph>>=
+fittedGraph <- function(data){
+  ggplot() +
+    geom_line(data=filter(data, energy=="Without energy"), mapping=aes(x=Year, y=iGDP)) +
+    geom_line(data=data, mapping=aes(x=Year, y=fitted, linetype=energy)) +
+    scale_linetype_manual(values=c(2,3), name="") +
+    facet_grid(Country ~ adjusted) +
+    xy_theme()
+}
+@
+
+<<Graphs CD, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Cobb-Douglas models. Solid line is historical GDP.">>=
+fittedGraph(filter(fitted_data, model=="CD"))
+@
+
+<<Graphs CESkle, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($kl$)$e$ nesting. Solid line is historical GDP.">>=
+fittedGraph(filter(fitted_data, model=="CESkle" | model=="CESkl"))
+@
+
+<<Graphs CESlek, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($le$)$k$ nesting. Solid line is historical GDP.">>=
+fittedGraph(filter(fitted_data, model=="CESlek" | model=="CESkl"))
+@
+
+<<Graphs CESekl, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($ek$)$l$ nesting. Solid line is historical GDP.">>=
+fittedGraph(filter(fitted_data, model=="CESekl" | model=="CESkl"))
+@
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Analysis}
+\label{sec:analysis}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-05-08 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Now calculating pre-econometric data.

@@
 dataUK <- filter(Leeds, Country == "UK")
-historicalData <- plyr::rbind.fill(dataPT, dataUK)
 @
@@
 t_UK <- substitute(iYear)
+
+# Create some pre-econometric ratios
+# Unadjusted variables
+dataPT <- transform(dataPT, kPerGDP_unadj = eval(k_PT_unadj)/iGDP)
+dataPT <- transform(dataPT, lPerGDP_unadj = eval(k_PT_unadj)/iGDP)
+dataPT <- transform(dataPT, ePerGDP_unadj = eval(e_PT_unadj)/iGDP)
+dataUK <- transform(dataUK, kPerGDP_unadj = eval(k_UK_unadj)/iGDP)
+dataUK <- transform(dataUK, lPerGDP_unadj = eval(k_UK_unadj)/iGDP)
+dataUK <- transform(dataUK, ePerGDP_unadj = eval(e_UK_unadj)/iGDP)
+# Quality-adjusted variables
+dataPT <- transform(dataPT, kPerGDP_adj = eval(k_PT_adj)/iGDP)
+dataPT <- transform(dataPT, lPerGDP_adj = eval(k_PT_adj)/iGDP)
+dataPT <- transform(dataPT, ePerGDP_adj = eval(e_PT_adj)/iGDP)
+dataUK <- transform(dataUK, kPerGDP_adj = eval(k_UK_adj)/iGDP)
+dataUK <- transform(dataUK, lPerGDP_adj = eval(k_UK_adj)/iGDP)
+dataUK <- transform(dataUK, ePerGDP_adj = eval(e_UK_adj)/iGDP)
+
+# Now create the historicalData data frame
+historicalData <- plyr::rbind.fill(dataPT, dataUK)
 @
@@
   ylab("Indexed (1960=1)")
+@
+
+<<Pre-econometric graph>>=
+
 @
@@
 fitted_data <- leaf_apply(models, extract_fitted_comparison, class=c("CDEmodel", "cesEst", "LINEXmodel"))
+# Create a data frame.
 fitted_data <- do.call(rbind, fitted_data)

### 2015-05-08 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Added residual plots for all models.

--- 2015-05-05 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
@@
 t_UK <- substitute(iYear)
+
+# Create some pre-econometric ratios
+# Unadjusted variables
+dataPT <- transform(dataPT, kPerGDP_unadj = eval(k_PT_unadj)/iGDP)
+dataPT <- transform(dataPT, lPerGDP_unadj = eval(l_PT_unadj)/iGDP)
+dataPT <- transform(dataPT, ePerGDP_unadj = eval(e_PT_unadj)/iGDP)
+dataUK <- transform(dataUK, kPerGDP_unadj = eval(k_UK_unadj)/iGDP)
+dataUK <- transform(dataUK, lPerGDP_unadj = eval(l_UK_unadj)/iGDP)
+dataUK <- transform(dataUK, ePerGDP_unadj = eval(e_UK_unadj)/iGDP)
+# Quality-adjusted variables
+dataPT <- transform(dataPT, kPerGDP_adj = eval(k_PT_adj)/iGDP)
+dataPT <- transform(dataPT, lPerGDP_adj = eval(l_PT_adj)/iGDP)
+dataPT <- transform(dataPT, ePerGDP_adj = eval(e_PT_adj)/iGDP)
+dataUK <- transform(dataUK, kPerGDP_adj = eval(k_UK_adj)/iGDP)
+dataUK <- transform(dataUK, lPerGDP_adj = eval(l_UK_adj)/iGDP)
+dataUK <- transform(dataUK, ePerGDP_adj = eval(e_UK_adj)/iGDP)
+
+# Now create the historicalData data frame
+historicalData <- plyr::rbind.fill(dataPT, dataUK)
 @
@@
   coord_cartesian(ylim=c(0.5, 13)) +
+  xlab("") + 
+  ylab("Indexed (1960=1)")
+@
+
+<<Pre-econometric graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Pre-econometric data.", warning=FALSE>>=
+# Melt the data
+mdata_preeconometric <- melt(historicalData, 
+                             measure.vars = c("kPerGDP_unadj", "lPerGDP_unadj", "ePerGDP_unadj",
+                                              "kPerGDP_adj", "lPerGDP_adj", "ePerGDP_adj"),
+                             variable.name = "variable",
+                             value.name = "value")
+# Add a column to say whether the variable is Unadjusted or Quality-adjusted based on variable name
+mdata_preeconometric$adjusted <- lapply(mdata_preeconometric$variable, function(x) {
+  suffix <- unlist(strsplit(as.character(x), split="[_]")) [2]
+  if (suffix == "unadj"){
+    return("Unadjusted")
+  } else if (suffix == "adj"){
+    return("Quality-adjusted")
+  } else {
+    stop(paste("Unknown suffix:", suffix))
+  }
+})
+# Fix levels
+mdata_preeconometric$adjusted <- relevelFactor(as.factor(as.character(mdata_preeconometric$adjusted)), 
+                                               c("Unadjusted", "Quality-adjusted"))
+mdata_preeconometric$Country <- relevelFactor(as.factor(mdata_preeconometric$Country), 
+                                              c("PT", "UK"))
+# Now make the plot
+historicalPlot(mdata_preeconometric, 
+               mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
+               facet_formula = Country ~ adjusted, 
+               line_types = c(2,4,3, 2,4,3)) + 
   xlab("") + 
@@
 
-<<Fitted_Data>>=
-  extract_fitted_comparison <- function(mod, id){
+<<Fitted_and_Residuals>>=
+extract_fitted_and_resid <- function(mod, id){
   df <- mod$data[ , c("Year", "iGDP", "Country")]
@@
   df$fitted <- yhat(mod)[c(1:length(df$Year))]
+  df$Residuals <- resid(mod)[c(1:length(df$Year))]
   # Parse the id to find out whether this is quality-adjusted data
@@
 }
-  fitted_data <- leaf_apply(models, extract_fitted_comparison, class=c("CDEmodel", "cesEst", "LINEXmodel"))
-  fitted_data <- do.call(rbind, fitted_data)
+fitted_and_resid_data <- leaf_apply(models, extract_fitted_and_resid, class=c("CDEmodel", "cesEst", "LINEXmodel"))
+# Create a data frame.
+fitted_and_resid_data <- do.call(rbind, fitted_and_resid_data)
+
+# Relevel factors before plotting
+fitted_and_resid_data$Country <- relevelFactor(as.factor(fitted_and_resid_data$Country), c("PT", "UK"))
+fitted_and_resid_data$adjusted <- relevelFactor(as.factor(fitted_and_resid_data$adjusted), c("Unadjusted", "Quality-adjusted"))
+fitted_and_resid_data$energy <- relevelFactor(as.factor(fitted_and_resid_data$energy), c("Without energy", "With Energy"))
 @
@@
 \label{sec:results}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%++++++++++++++++++++++++++++++
+\subsection{Fits to historical data} 
+\label{sec:fits_to_historical_data}
+%++++++++++++++++++++++++++++++
+
+This section shows graphs of fits to historical data and residuals.
+
+<<Fitted and Residual Graphs>>=
+fittedGraph <- function(data){
+  ggplot() +
+    geom_line(data=filter(data, energy=="Without energy"), mapping=aes(x=Year, y=iGDP)) +
+    geom_line(data=data, mapping=aes(x=Year, y=fitted, linetype=energy)) +
+    scale_linetype_manual(values=c(2,3), name="") +
+    facet_grid(Country ~ adjusted) +
+    xy_theme()
+}
+
+residualPlot <- function(data){
+  ggplot() +
+    geom_line(data=data, mapping=aes(x=Year, y=Residuals, linetype=energy)) +
+    scale_linetype_manual(values=c(2,3), name="") +
+    facet_grid(Country ~ adjusted) +
+    xy_theme()
+}
+@
+
+<<Graphs CD-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Cobb-Douglas models. Solid line is historical GDP.">>=
+fittedGraph(filter(fitted_and_resid_data, model=="CD"))
+@
+
+<<Graphs CD-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Residuals for Cobb-Douglas models.">>=
+residualPlot(filter(fitted_and_resid_data, model=="CD"))
+@
+
+<<Graphs CESkle-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($kl$)$e$ nesting. Solid line is historical GDP.">>=
+fittedGraph(filter(fitted_and_resid_data, model=="CESkle" | model=="CESkl"))
+@
+
+<<Graphs CESkle-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Residuals for CES models with $(kl$)$e$ nesting.">>=
+residualPlot(filter(fitted_and_resid_data, model=="CESkle" | model=="CESkl"))
+@
+
+<<Graphs CESlek-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($le$)$k$ nesting. Solid line is historical GDP.">>=
+fittedGraph(filter(fitted_and_resid_data, model=="CESlek" | model=="CESkl"))
+@
+
+<<Graphs CESlek-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Residuals for CES models with $(le$)$k$ nesting.">>=
+residualPlot(filter(fitted_and_resid_data, model=="CESlek" | model=="CESkl"))
+@
+
+<<Graphs CESekl-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($ek$)$l$ nesting. Solid line is historical GDP.">>=
+fittedGraph(filter(fitted_and_resid_data, model=="CESekl" | model=="CESkl"))
+@
+
+<<Graphs CESekl-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Residuals for CES models with $(ek$)$l$ nesting.">>=
+residualPlot(filter(fitted_and_resid_data, model=="CESekl" | model=="CESkl"))
+@
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Analysis}
+\label{sec:analysis}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+Table~\ref{tab:sse_CES-kle_PT} shows the $sse$ values for each of these models.
+
+\begin{table} \caption{PT $sse$ with CES and ($kl$)$e$ nesting.} 
+\label{tab:sse_CES-kle_PT} 
+  \begin{center}
+    \begin{tabular}{r c c} 
+      \toprule
+                      & Unadjusted     & Quality-adjusted   \\
+      \midrule
+      Without energy  & \Sexpr{EconModels:::sse(models$PT$unadj$noE$CESkl)$sse} & \Sexpr{EconModels:::sse(models$PT$adj$noE$CESkl)$sse} \\
+      With energy     & \Sexpr{EconModels:::sse(models$PT$unadj$withE$CESkle)$sse} 
+                                                            & \Sexpr{EconModels:::sse(models$PT$adj$withE$CESkle)$sse} \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+\end{table}
+
 In contrast to the Cobb-Douglas model,
@@
       With energy     & \Sexpr{naturalCoef(models$PT$unadj$withE$CESlek)$lambda} & \Sexpr{naturalCoef(models$PT$adj$withE$CESle)$lambda} \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+\end{table}
+
+Table~\ref{tab:sse_CES-lek_PT} shows the $sse$ values for each of these models.
+
+\begin{table} \caption{PT $sse$ with CES and ($le$)$k$ nesting.} 
+\label{tab:sse_CES-lek_PT} 
+  \begin{center}
+    \begin{tabular}{r c c} 
+      \toprule
+                      & Unadjusted     & Quality-adjusted   \\
+      \midrule
+      Without energy  & \Sexpr{EconModels:::sse(models$PT$unadj$noE$CESkl)$sse} & \Sexpr{EconModels:::sse(models$PT$adj$noE$CESkl)$sse} \\
+      With energy     & \Sexpr{EconModels:::sse(models$PT$unadj$withE$CESlek)$sse} 
+                                                            & \Sexpr{EconModels:::sse(models$PT$adj$withE$CESlek)$sse} \\
       \bottomrule
@@
 
+Table~\ref{tab:sse_CES-ekl_PT} shows the $sse$ values for each of these models.
+
+\begin{table} \caption{PT $sse$ with CES and ($ek$)$l$ nesting.} 
+\label{tab:sse_CES-ekl_PT} 
+  \begin{center}
+    \begin{tabular}{r c c} 
+      \toprule
+                      & Unadjusted     & Quality-adjusted   \\
+      \midrule
+      Without energy  & \Sexpr{EconModels:::sse(models$PT$unadj$noE$CESkl)$sse} & \Sexpr{EconModels:::sse(models$PT$adj$noE$CESkl)$sse} \\
+      With energy     & \Sexpr{EconModels:::sse(models$PT$unadj$withE$CESekl)$sse} 
+                                                            & \Sexpr{EconModels:::sse(models$PT$adj$withE$CESekl)$sse} \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+\end{table}
+
 For the ($ek$)$l$ nesting, 
@@
 
+Table~\ref{tab:sse_CES-kle_UK} shows the $sse$ values for each of these models.
+
+\begin{table} \caption{UK $sse$ with CES and ($kl$)$e$ nesting.} 
+\label{tab:sse_CES-kle_UK} 
+  \begin{center}
+    \begin{tabular}{r c c} 
+      \toprule
+                      & Unadjusted     & Quality-adjusted   \\
+      \midrule
+      Without energy  & \Sexpr{EconModels:::sse(models$UK$unadj$noE$CESkl)$sse} & \Sexpr{EconModels:::sse(models$UK$adj$noE$CESkl)$sse} \\
+      With energy     & \Sexpr{EconModels:::sse(models$UK$unadj$withE$CESkle)$sse} 
+                                                            & \Sexpr{EconModels:::sse(models$UK$adj$withE$CESkle)$sse} \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+\end{table}
+
 Like the Cobb-Douglas model, the CES model produces positive Solow residuals
@@
 
+Table~\ref{tab:sse_CES-ekl_UK} shows the $sse$ values for each of these models.
+
+\begin{table} \caption{UK $sse$ with CES and ($le$)$k$ nesting.} 
+\label{tab:sse_CES-lek_UK} 
+  \begin{center}
+    \begin{tabular}{r c c} 
+      \toprule
+                      & Unadjusted     & Quality-adjusted   \\
+      \midrule
+      Without energy  & \Sexpr{EconModels:::sse(models$UK$unadj$noE$CESkl)$sse} & \Sexpr{EconModels:::sse(models$UK$adj$noE$CESkl)$sse} \\
+      With energy     & \Sexpr{EconModels:::sse(models$UK$unadj$withE$CESlek)$sse} 
+                                                            & \Sexpr{EconModels:::sse(models$UK$adj$withE$CESlek)$sse} \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+\end{table}
+
 Similar to the CES model with ($kl$)$e$ nesting,
@@
 
+Table~\ref{tab:sse_CES-ekl_UK} shows the $sse$ values for each of these models.
+
+\begin{table} \caption{UK $sse$ with CES and ($ek$)$l$ nesting.} 
+\label{tab:sse_CES-ekl_UK} 
+  \begin{center}
+    \begin{tabular}{r c c} 
+      \toprule
+                      & Unadjusted     & Quality-adjusted   \\
+      \midrule
+      Without energy  & \Sexpr{EconModels:::sse(models$UK$unadj$noE$CESkl)$sse} & \Sexpr{EconModels:::sse(models$UK$adj$noE$CESkl)$sse} \\
+      With energy     & \Sexpr{EconModels:::sse(models$UK$unadj$withE$CESekl)$sse} 
+                                                            & \Sexpr{EconModels:::sse(models$UK$adj$withE$CESekl)$sse} \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+\end{table}
+
 Similar to the CES model with ($ek$)$l$ nesting,

### 2015-05-10 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Now including tilde on João's name.

@@
 
-\author[IST]{João dos Santos}
+\author[IST]{Jo\~{a}o dos Santos}
 \author[Leeds]{Paul Brockway}
@@
 t_UK <- substitute(iYear)
+
+# Lists
+y <- NULL
+k <- NULL
+l <- NULL
+e <- NULL
+t <- NULL
+f <- NULL
+# Economic output
+y$PT <- substitute(iGDP)
+y$UK <- substitute(iGDP)
+# Portugal undajusted inputs
+k$PT$unadj <- substitute(iKstkS.L)
+l$PT$unadj <- substitute(iL)
+e$PT$unadj <- substitute(iXpMP)
+# Portugal quality-adjusted inputs
+k$PT$adj <- substitute(iKservS.L)
+l$PT$adj <- substitute(ihLest)
+e$PT$adj <- substitute(iUMP)
+# UK unadjusted inputs
+k$UK$unadj <- substitute(iKstkO.WwithRD)
+l$UK$unadj <- substitute(iL)
+e$UK$unadj <- substitute(iXp)
+# UK quality-adjusted inputs
+k$UK$adj <- substitute(iKservO.WwithRD)
+l$UK$adj <- substitute(ihLest)
+e$UK$adj <- substitute(iU)
+# Time variables
+t$PT <- substitute(iYear)
+t$UK <- substitute(iYear)
+
+# countries <- c(substitute(PT), substitute(UK))
+# adjusteds <- c(substitute(unadj), substitute(adj))
+# energies <- c(substitute(noE), substitute(withE))
+# 
+# for (country in countries){
+#   for (adjusted in adjusteds){
+#     for (energy in energies){
+#       substitute(f$country$adjusted$energy, 
+#                  list(country=country, adjusted=adjusted, energy=energy)) <- "a"
+#     }
+#   }
+# }
 

### 2015-05-12 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Trying to create formulas in a loop.

--- 2015-05-08 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
@@
 # that can be a component of a formula.
+# # Economic output
+# y_PT <- substitute(iGDP)
+# y_UK <- substitute(iGDP)
+# # Portugal undajusted inputs
+# k_PT_unadj <- substitute(iKstkS.L)
+# l_PT_unadj <- substitute(iL)
+# e_PT_unadj <- substitute(iXpMP)
+# # Portugal quality-adjusted inputs
+# k_PT_adj <- substitute(iKservS.L)
+# l_PT_adj <- substitute(ihLest)
+# e_PT_adj <- substitute(iUMP)
+# # UK unadjusted inputs
+# k_UK_unadj <- substitute(iKstkO.WwithRD)
+# l_UK_unadj <- substitute(iL)
+# e_UK_unadj <- substitute(iXp)
+# # UK quality-adjusted inputs
+# k_UK_adj <- substitute(iKservO.WwithRD)
+# l_UK_adj <- substitute(ihLest)
+# e_UK_adj <- substitute(iU)
+# # Time variables
+# t_PT <- substitute(iYear)
+# t_UK <- substitute(iYear)
+
+# vars <- list()
+# # Economic output
+# vars$y.PT <- substitute(iGDP)
+# vars$y.UK <- substitute(iGDP)
+# # Portugal undajusted inputs
+# vars$k.PT.unadj <- substitute(iKstkS.L)
+# vars$l.PT.unadj <- substitute(iL)
+# vars$e.PT.unadj <- substitute(iXpMP)
+# # Portugal quality-adjusted inputs
+# vars$k.PT.adj <- substitute(iKservS.L)
+# vars$l.PT.adj <- substitute(ihLest)
+# vars$e.PT.adj <- substitute(iUMP)
+# # UK unadjusted inputs
+# vars$k.UK.unadj <- substitute(iKstkO.WwithRD)
+# vars$l.UK.unadj <- substitute(iL)
+# vars$e.UK.unadj <- substitute(iXp)
+# # UK quality-adjusted inputs
+# vars$k.UK.adj <- substitute(iKservO.WwithRD)
+# vars$l.UK.adj <- substitute(ihLest)
+# vars$e.UK.adj <- substitute(iU)
+# # Time variables
+# vars$t.PT <- substitute(iYear)
+# vars$t.UK <- substitute(iYear)
+
+y <- list()
+k <- list()
+l <- list()
+e <- list()
+t <- list()
 # Economic output
-y_PT <- substitute(iGDP)
-y_UK <- substitute(iGDP)
+y$PT <- substitute(iGDP)
+y$UK <- substitute(iGDP)
 # Portugal undajusted inputs
-k_PT_unadj <- substitute(iKstkS.L)
-l_PT_unadj <- substitute(iL)
-e_PT_unadj <- substitute(iXpMP)
+k$PT$unadj <- substitute(iKstkS.L)
+l$PT$unadj <- substitute(iL)
+e$PT$unadj <- substitute(iXpMP)
 # Portugal quality-adjusted inputs
-k_PT_adj <- substitute(iKservS.L)
-l_PT_adj <- substitute(ihLest)
-e_PT_adj <- substitute(iUMP)
+k$PT$adj <- substitute(iKservS.L)
+l$PT$adj <- substitute(ihLest)
+e$PT$adj <- substitute(iUMP)
 # UK unadjusted inputs
-k_UK_unadj <- substitute(iKstkO.WwithRD)
-l_UK_unadj <- substitute(iL)
-e_UK_unadj <- substitute(iXp)
+k$UK$unadj <- substitute(iKstkO.WwithRD)
+l$UK$unadj <- substitute(iL)
+e$UK$unadj <- substitute(iXp)
 # UK quality-adjusted inputs
-k_UK_adj <- substitute(iKservO.WwithRD)
-l_UK_adj <- substitute(ihLest)
-e_UK_adj <- substitute(iU)
+k$UK$adj <- substitute(iKservO.WwithRD)
+l$UK$adj <- substitute(ihLest)
+e$UK$adj <- substitute(iU)
 # Time variables
-t_PT <- substitute(iYear)
-t_UK <- substitute(iYear)
+t$PT <- substitute(iYear)
+t$UK <- substitute(iYear)
+
+countries <- c(substitute(PT), substitute(UK))
+adjusteds <- c(substitute(unadj), substitute(adj))
+energies <- c(substitute(noE), substitute(withE))
+f <- list()
+for (country in c(substitute(PT), substitute(UK))){
+  for (adjusted in adjusteds){
+    for (energy in energies){
+      if (energy == substitute(noE)){
+        eval(substitute(f$ctry$adjst$ener <- y$ctry ~ k$ctry$adjst + l$ctry$adjst + t$ctry, 
+                        list(ctry=country, adjst=adjusted, ener=energy)))
+      } else if (energy == substitute(withE)){
+        eval(substitute(f$ctry$adjst$ener <- y$ctry ~ k$ctry$adjst + l$ctry$adjst + e$ctry$adjst + t$ctry, 
+                        list(ctry=country, adjst=adjusted, ener=energy)))
+      } else {
+        stop(paste("Unknown energy", energy, "in loop for f"))
+      }
+    }
+  }
+}
 

### 2015-05-13 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Improved code for ESEE analysis.

@@
 <<Data, eval=TRUE>>=
+countries <- c("PT", "UK")
 dataPT <- filter(IST, Country == "PT")
@@
 # that can be a component of a formula.
+
+vars <-   
+  list( 
+    PT = list(
+      response = list(unadjusted = "iGDP", adjusted = "iGDP"),
+      capital = list(unadjusted ="iKstkS.L", adjusted = "iKservS.L"),
+      labor = list(unadjusted = "iL", adjusted = "ihLest"),
+      energy = list(unadjusted = "iXpMP", adjusted = "iUMP"),
+      time = list(unadjusted = "iYear", adjusted = "iYear")
+    ), 
+    UK = list(
+      response = list(unadjusted = "iGDP", adjusted = "iGDP"),
+      capital = list(unadjusted = "iKstkO.WwithRD", adjusted = "iKservO.WwithRD"), 
+      labor = list(unadjusted = "iL", adjusted = "ihLest"),
+      energy = list(unadjusted = "iXp", adjusted = "iU"),
+      time = list(unadjusted = "iYear", adjusted = "iYear")
+    )
+  )
+
 # # Economic output
@@
 
-y <- list()
-k <- list()
-l <- list()
-e <- list()
-t <- list()
-# Economic output
-y$PT <- substitute(iGDP)
-y$UK <- substitute(iGDP)
-# Portugal undajusted inputs
-k$PT$unadj <- substitute(iKstkS.L)
-l$PT$unadj <- substitute(iL)
-e$PT$unadj <- substitute(iXpMP)
-# Portugal quality-adjusted inputs
-k$PT$adj <- substitute(iKservS.L)
-l$PT$adj <- substitute(ihLest)
-e$PT$adj <- substitute(iUMP)
-# UK unadjusted inputs
-k$UK$unadj <- substitute(iKstkO.WwithRD)
-l$UK$unadj <- substitute(iL)
-e$UK$unadj <- substitute(iXp)
-# UK quality-adjusted inputs
-k$UK$adj <- substitute(iKservO.WwithRD)
-l$UK$adj <- substitute(ihLest)
-e$UK$adj <- substitute(iU)
-# Time variables
-t$PT <- substitute(iYear)
-t$UK <- substitute(iYear)
-
-countries <- c(substitute(PT), substitute(UK))
-adjusteds <- c(substitute(unadj), substitute(adj))
-energies <- c(substitute(noE), substitute(withE))
+# y <- list()
+# k <- list()
+# l <- list()
+# e <- list()
+# t <- list()
+# # Economic output
+# y$PT <- substitute(iGDP)
+# y$UK <- substitute(iGDP)
+# # Portugal undajusted inputs
+# k$PT$unadj <- substitute(iKstkS.L)
+# l$PT$unadj <- substitute(iL)
+# e$PT$unadj <- substitute(iXpMP)
+# # Portugal quality-adjusted inputs
+# k$PT$adj <- substitute(iKservS.L)
+# l$PT$adj <- substitute(ihLest)
+# e$PT$adj <- substitute(iUMP)
+# # UK unadjusted inputs
+# k$UK$unadj <- substitute(iKstkO.WwithRD)
+# l$UK$unadj <- substitute(iL)
+# e$UK$unadj <- substitute(iXp)
+# # UK quality-adjusted inputs
+# k$UK$adj <- substitute(iKservO.WwithRD)
+# l$UK$adj <- substitute(ihLest)
+# e$UK$adj <- substitute(iU)
+# # Time variables
+# t$PT <- substitute(iYear)
+# t$UK <- substitute(iYear)
+# 
+# foo <- function(country = c("UK", "PT"), adjusted=TRUE, energy=TRUE, envir=parent.frame()) {
+#   country <- match.arg(country)
+#   type <- if (adjusted) "adj" else "unadj"
+#   res <- as.formula(
+#       paste(y[[country]], 
+#             paste(k[[country]][[type]], l[[country]][[type]], if (energy) e[[country]][[type]] else NULL, t[[country]], sep="+"), 
+#             sep="~")
+#     )
+#   environment(res) <- envir
+#   res
+# }
+# 
+# 
+# for (country in c("PT", "UK")) {
+#   for (adjusted in c(TRUE, FALSE)) {
+#     for (energy in c(TRUE, FALSE)) {
+#       print(foo(country = country, adjusted = adjusted, energy=energy))
+#     }
+#   }
+# }
+#
+
+# 
+# countries <- c(substitute(PT), substitute(UK))
+# adjusteds <- c(substitute(unadj), substitute(adj))
+# energies <- c(substitute(noE), substitute(withE))
+# f <- list()
+# for (country in c(substitute(PT), substitute(UK))){
+#   for (adjusted in adjusteds){
+#     for (energy in energies){
+#       if (energy == substitute(noE)){
+#         eval(substitute(f$ctry$adjst$ener <- y$ctry ~ k$ctry$adjst + l$ctry$adjst + t$ctry, 
+#                         list(ctry=country, adjst=adjusted, ener=energy)))
+#       } else if (energy == substitute(withE)){
+#         eval(substitute(f$ctry$adjst$ener <- y$ctry ~ k$ctry$adjst + l$ctry$adjst + e$ctry$adjst + t$ctry, 
+#                         list(ctry=country, adjst=adjusted, ener=energy)))
+#       } else {
+#         stop(paste("Unknown energy", energy, "in loop for f"))
+#       }
+#     }
+#   }
+# }
+
+# Create some pre-econometric ratios
+# Unadjusted variables
+dataPT <- transform(dataPT, kPerGDP.unadj = dataPT[[vars$PT$capital$unadjusted]]/dataPT[[vars$PT$response$unadjusted]])
+dataPT <- transform(dataPT, kPerGDP.unadj = iKstkS.L/iGDP)
+dataPT <- transform(dataPT, kPerGDP.unadj = as.name(vars$PT$capital$unadjusted)/iGDP)
+dataPT <- transform(dataPT, kPerGDP.unadj = eval(substitute(as.name(vars$PT$capital$unadjusted)))/iGDP)
+dataPT <- transform(dataPT, kPerGDP.unadj = eval(quote(as.name(vars$PT$capital$unadjusted)))/iGDP)
+
+dataPT <- transform(dataPT, lPerGDP.unadj = eval(k_PT_unadj)/iGDP)
+dataPT <- transform(dataPT, lPerGDP.unadj = eval(l_PT_unadj)/iGDP)
+dataPT <- transform(dataPT, ePerGDP.unadj = eval(e_PT_unadj)/iGDP)
+dataUK <- transform(dataUK, kPerGDP.unadj = eval(k_UK_unadj)/iGDP)
+dataUK <- transform(dataUK, lPerGDP.unadj = eval(l_UK_unadj)/iGDP)
+dataUK <- transform(dataUK, ePerGDP.unadj = eval(e_UK_unadj)/iGDP)
+# Quality-adjusted variables
+dataPT <- transform(dataPT, kPerGDP.adj = eval(k_PT_adj)/iGDP)
+dataPT <- transform(dataPT, lPerGDP.adj = eval(l_PT_adj)/iGDP)
+dataPT <- transform(dataPT, ePerGDP.adj = eval(e_PT_adj)/iGDP)
+dataUK <- transform(dataUK, kPerGDP.adj = eval(k_UK_adj)/iGDP)
+dataUK <- transform(dataUK, lPerGDP.adj = eval(l_UK_adj)/iGDP)
+dataUK <- transform(dataUK, ePerGDP.adj = eval(e_UK_adj)/iGDP)
+
+# Now create the historicalData data frame
+historicalData <- plyr::rbind.fill(dataPT, dataUK)
+@
+
+<<Formulas>>=
+# Set up the formulas for each type of analysis.
+# f <- NULL
+# f$PT$unadj$noE <- as.formula(
+#   substitute( y ~ k + l + t,
+#               list( y = y_PT, k = k_PT_unadj, 
+#                     l = l_PT_unadj, t = t_PT)))
+# f$PT$unadj$withE <- as.formula(
+#   substitute( y ~ k + l + e + t,
+#               list( y = y_PT, k = k_PT_unadj,
+#                     l = l_PT_unadj, e = e_PT_unadj, t = t_PT)))
+# f$PT$adj$noE <- as.formula(
+#   substitute( y ~ k + l + t,
+#               list( y = y_PT, k = k_PT_adj,
+#                     l = l_PT_adj, t = t_PT)))
+# f$PT$adj$withE <- as.formula(
+#   substitute( y ~ k + l + e + t,
+#               list( y = y_PT, k = k_PT_adj,
+#                     l = l_PT_adj, e = e_PT_adj, t = t_PT)))
+# f$UK$unadj$noE <- as.formula(
+#   substitute( y ~ k + l + t,
+#               list( y = y_UK, k = k_UK_unadj,
+#                     l = l_UK_unadj, t = t_UK)))
+# f$UK$unadj$withE <- as.formula(
+#   substitute( y ~ k + l + e + t,
+#               list( y = y_UK, k = k_UK_unadj,
+#                     l = l_UK_unadj, e = e_UK_unadj, t = t_UK)))
+# f$UK$adj$noE <- as.formula(
+#   substitute( y ~ k + l + t,
+#               list( y = y_UK, k = k_UK_adj,
+#                     l = l_UK_adj, t = t_UK)))
+# f$UK$adj$withE <- as.formula(
+#   substitute( y ~ k + l + e + t,
+#               list( y = y_UK, k = k_UK_adj,
+#                     l = l_UK_adj, e = e_UK_adj, t = t_UK)))
+
+makeFormula <- function(time.series, country, adjusted, energy, envir=parent.frame()) {
+  country <- match.arg(country, names(time.series))
+  if (! adjusted %in% c(FALSE, TRUE)){
+    stop("adjusted must be a boolean")
+  }
+  if (! energy %in% c(FALSE, TRUE)){
+    stop("energy must be a boolean")
+  }
+  type <- if (adjusted) "adjusted" else "unadjusted"
+  res <- as.formula( 
+    gsub( "\\+ *\\+", "+ ", 
+          paste(time.series[[country]][["response"]][[type]], 
+                paste(time.series[[country]][["capital"]][[type]], 
+                      time.series[[country]][["labor"]][[type]], 
+                      if (energy) {
+                        time.series[[country]][["energy"]][[type]]
+                      } else {
+                        NULL
+                      }, 
+                      time.series[[country]][["time"]][[type]], sep="+"), 
+                sep="~")
+    )
+  )
+  environment(res) <- envir
+  return(res)
+}
+
 f <- list()
-for (country in c(substitute(PT), substitute(UK))){
-  for (adjusted in adjusteds){
-    for (energy in energies){
-      if (energy == substitute(noE)){
-        eval(substitute(f$ctry$adjst$ener <- y$ctry ~ k$ctry$adjst + l$ctry$adjst + t$ctry, 
-                        list(ctry=country, adjst=adjusted, ener=energy)))
-      } else if (energy == substitute(withE)){
-        eval(substitute(f$ctry$adjst$ener <- y$ctry ~ k$ctry$adjst + l$ctry$adjst + e$ctry$adjst + t$ctry, 
-                        list(ctry=country, adjst=adjusted, ener=energy)))
-      } else {
-        stop(paste("Unknown energy", energy, "in loop for f"))
+for (country in countries) {
+  for (adjusted in c(FALSE, TRUE)) {
+    for (energy in c(FALSE, TRUE)) {
+      newf <- makeFormula(vars, country = country, adjusted = adjusted, energy=energy)
+      namef <- paste(country, if(adjusted) "adj" else "unadj", if(energy) "withE" else "noE", sep=".")
+      newnames <- c(names(f), namef)
+      f <- c(f, newf)
+      names(f) <- newnames
     }
@@
 }
-}
-
-# Create some pre-econometric ratios
-# Unadjusted variables
-dataPT <- transform(dataPT, kPerGDP_unadj = eval(k_PT_unadj)/iGDP)
-dataPT <- transform(dataPT, lPerGDP_unadj = eval(l_PT_unadj)/iGDP)
-dataPT <- transform(dataPT, ePerGDP_unadj = eval(e_PT_unadj)/iGDP)
-dataUK <- transform(dataUK, kPerGDP_unadj = eval(k_UK_unadj)/iGDP)
-dataUK <- transform(dataUK, lPerGDP_unadj = eval(l_UK_unadj)/iGDP)
-dataUK <- transform(dataUK, ePerGDP_unadj = eval(e_UK_unadj)/iGDP)
-# Quality-adjusted variables
-dataPT <- transform(dataPT, kPerGDP_adj = eval(k_PT_adj)/iGDP)
-dataPT <- transform(dataPT, lPerGDP_adj = eval(l_PT_adj)/iGDP)
-dataPT <- transform(dataPT, ePerGDP_adj = eval(e_PT_adj)/iGDP)
-dataUK <- transform(dataUK, kPerGDP_adj = eval(k_UK_adj)/iGDP)
-dataUK <- transform(dataUK, lPerGDP_adj = eval(l_UK_adj)/iGDP)
-dataUK <- transform(dataUK, ePerGDP_adj = eval(e_UK_adj)/iGDP)
-
-# Now create the historicalData data frame
-historicalData <- plyr::rbind.fill(dataPT, dataUK)
-@
-
-<<Formulas>>=
-# Set up the formulas for each type of analysis.
-f <- NULL
-f$PT$unadj$noE <- as.formula(
-  substitute( y ~ k + l + t,
-              list( y = y_PT, k = k_PT_unadj, 
-                    l = l_PT_unadj, t = t_PT)))
-f$PT$unadj$withE <- as.formula(
-  substitute( y ~ k + l + e + t,
-              list( y = y_PT, k = k_PT_unadj,
-                    l = l_PT_unadj, e = e_PT_unadj, t = t_PT)))
-f$PT$adj$noE <- as.formula(
-  substitute( y ~ k + l + t,
-              list( y = y_PT, k = k_PT_adj,
-                    l = l_PT_adj, t = t_PT)))
-f$PT$adj$withE <- as.formula(
-  substitute( y ~ k + l + e + t,
-              list( y = y_PT, k = k_PT_adj,
-                    l = l_PT_adj, e = e_PT_adj, t = t_PT)))
-f$UK$unadj$noE <- as.formula(
-  substitute( y ~ k + l + t,
-              list( y = y_UK, k = k_UK_unadj,
-                    l = l_UK_unadj, t = t_UK)))
-f$UK$unadj$withE <- as.formula(
-  substitute( y ~ k + l + e + t,
-              list( y = y_UK, k = k_UK_unadj,
-                    l = l_UK_unadj, e = e_UK_unadj, t = t_UK)))
-f$UK$adj$noE <- as.formula(
-  substitute( y ~ k + l + t,
-              list( y = y_UK, k = k_UK_adj,
-                    l = l_UK_adj, t = t_UK)))
-f$UK$adj$withE <- as.formula(
-  substitute( y ~ k + l + e + t,
-              list( y = y_UK, k = k_UK_adj,
-                    l = l_UK_adj, e = e_UK_adj, t = t_UK)))
 @
@@
       \midrule
-      Output      & \Sexpr{y_PT}       & \Sexpr{y_UK}       \\
-      Capital     & \Sexpr{k_PT_unadj} & \Sexpr{k_UK_unadj} \\
-      Labor       & \Sexpr{l_PT_unadj} & \Sexpr{l_UK_unadj} \\
-      Energy      & \Sexpr{e_PT_unadj} & \Sexpr{e_UK_unadj} \\
+      Output      & \Sexpr{vars$PT$response$unadjusted}       & \Sexpr{vars$UK$response$unadjusted}       \\
+      Capital     & \Sexpr{vars$PT$capital$unadjusted} & \Sexpr{vars$UK$capital$unadjusted} \\
+      Labor       & \Sexpr{vars$PT$labor$unadjusted} & \Sexpr{vars$UK$labor$unadjusted} \\
+      Energy      & \Sexpr{vars$PT$energy$unadjusted} & \Sexpr{vars$UK$energy$unadjusted} \\
       \bottomrule
@@
       \midrule
-      Output      & \Sexpr{y_PT}     & \Sexpr{y_UK}     \\
-      Capital     & \Sexpr{k_PT_adj} & \Sexpr{k_UK_adj} \\
-      Labor       & \Sexpr{l_PT_adj} & \Sexpr{l_UK_adj} \\
-      Energy      & \Sexpr{e_PT_adj} & \Sexpr{e_UK_adj} \\
+      Output      & \Sexpr{vars$PT$response$adjusted}       & \Sexpr{vars$UK$response$adjusted}       \\
+      Capital     & \Sexpr{vars$PT$capital$adjusted} & \Sexpr{vars$UK$capital$adjusted} \\
+      Labor       & \Sexpr{vars$PT$labor$adjusted} & \Sexpr{vars$UK$labor$adjusted} \\
+      Energy      & \Sexpr{vars$PT$energy$adjusted} & \Sexpr{vars$UK$energy$adjusted} \\
       \bottomrule
@@
 <<Historical Data, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Historical data.", warning=FALSE>>=
-unadjVars_PT <- c(y_PT, k_PT_unadj, l_PT_unadj, e_PT_unadj)
-unadjVars_UK <- c(y_UK, k_UK_unadj, l_UK_unadj, e_UK_unadj)
+unadjVars_PT <- c(vars$PT$response$unadjusted, 
+                  vars$PT$capital$unadjusted, 
+                  vars$PT$labor$unadjusted, 
+                  vars$PT$energy$unadjusted)
+unadjVars_UK <- c(vars$UK$response$unadjusted, 
+                  vars$UK$capital$unadjusted, 
+                  vars$UK$labor$unadjusted, 
+                  vars$UK$energy$unadjusted)
 commonVars <- c("Year", "iYear", "Country")
-unadjData_PT <- historicalData[ , as.character(unique(c(unadjVars_PT, commonVars)))] %>% filter(Country=="PT")
-unadjData_UK <- historicalData[ , as.character(unique(c(unadjVars_UK, commonVars)))] %>% filter(Country=="UK")
+unadjData_PT <- historicalData[ , unique(c(unadjVars_PT, commonVars))] %>% filter(Country=="PT")
+unadjData_UK <- historicalData[ , unique(c(unadjVars_UK, commonVars))] %>% filter(Country=="UK")
 unadjData <- plyr::rbind.fill(unadjData_PT, unadjData_UK)
-unadjData$adjusted <- "Unadjusted"
-
-adjVars_PT <- c(y_PT, k_PT_adj, l_PT_adj, e_PT_adj)
-adjVars_UK <- c(y_UK, k_UK_adj, l_UK_adj, e_UK_adj)
-adjData_PT <- historicalData[ , as.character(unique(c(adjVars_PT, commonVars)))] %>% filter(Country=="PT")
-adjData_UK <- historicalData[ , as.character(unique(c(adjVars_UK, commonVars)))] %>% filter(Country=="UK")
+unadjData$type <- "Unadjusted"
+adjVars_PT <- c(vars$PT$response$adjusted, 
+                vars$PT$capital$adjusted, 
+                vars$PT$labor$adjusted, 
+                vars$PT$energy$adjusted)
+adjVars_UK <- c(vars$UK$response$adjusted, 
+                vars$UK$capital$adjusted, 
+                vars$UK$labor$adjusted, 
+                vars$UK$energy$adjusted)
+adjData_PT <- historicalData[ , unique(c(adjVars_PT, commonVars))] %>% filter(Country=="PT")
+adjData_UK <- historicalData[ , unique(c(adjVars_UK, commonVars))] %>% filter(Country=="UK")
 adjData <- plyr::rbind.fill(adjData_PT, adjData_UK)
-adjData$adjusted <- "Quality-adjusted"
+adjData$type <- "Quality-adjusted"
 
@@
 mdata <- melt(trimmedData, 
-              measure.vars = unique(as.character(c(unadjVars_PT, unadjVars_UK, adjVars_PT, adjVars_UK))), 
+              measure.vars = unique(c(unadjVars_PT, unadjVars_UK, adjVars_PT, adjVars_UK)), 
               variable.name = "variable",
@@
 mdata$Country <- relevelFactor(as.factor(mdata$Country), c("PT", "UK"))
-mdata$adjusted <- relevelFactor(as.factor(mdata$adjusted), c("Unadjusted", "Quality-adjusted"))
-mdata$variable <- relevelFactor(as.factor(mdata$variable), unique(as.character(
-  c(y_PT, k_PT_unadj, l_PT_unadj, e_PT_unadj, k_PT_adj, l_PT_adj, e_PT_adj,
-    y_UK, k_UK_unadj, l_UK_unadj, e_UK_unadj, k_UK_adj, l_UK_adj, e_UK_adj))))
-
+mdata$type <- relevelFactor(as.factor(mdata$type), c("Unadjusted", "Quality-adjusted"))
+mdata$variable <- relevelFactor(as.factor(mdata$variable), unique(
+  c(vars$PT$response$unadjusted, vars$PT$capital$unadjusted, vars$PT$labor$unadjusted, vars$PT$energy$unadjusted, 
+    vars$PT$response$adjusted,   vars$PT$capital$adjusted,   vars$PT$labor$adjusted,   vars$PT$energy$adjusted, 
+    vars$UK$response$unadjusted, vars$UK$capital$unadjusted, vars$UK$labor$unadjusted, vars$UK$energy$unadjusted, 
+    vars$UK$response$adjusted,   vars$UK$capital$adjusted,   vars$UK$labor$adjusted,   vars$UK$energy$adjusted)))
 historicalPlot(mdata, 
                mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
-               facet_formula = Country ~ adjusted, 
+               facet_formula = Country ~ type, 
                line_types = c(1,2,4,3,2,4,3,2,3,2,3)) + 
@@
   nest$ekl <- c(3,1,2)
-  models <- NULL
-  # Portugal, CD
-  models$PT$unadj$noE$CD <- cdModel(formula = f$PT$unadj$noE, 
-                                    data = dataPT, constrained = TRUE)
-  models$PT$unadj$withE$CD <- cdModel(formula = f$PT$unadj$withE, 
-                                      data = dataPT, constrained = TRUE)
-  models$PT$adj$noE$CD <- cdModel(formula = f$PT$adj$noE, 
-                                  data = dataPT, constrained = TRUE)
-  models$PT$adj$withE$CD <- cdModel(formula = f$PT$adj$withE, 
-                                    data = dataPT, constrained = TRUE)
-  # UK, CD
-  models$UK$unadj$noE$CD <- cdModel(formula = f$UK$unadj$noE, 
-                                    data = dataUK, constrained = TRUE)
-  models$UK$unadj$withE$CD <- cdModel(formula = f$UK$unadj$withE, 
-                                      data = dataUK, constrained = TRUE)
-  models$UK$adj$noE$CD <- cdModel(formula = f$UK$adj$noE, 
-                                  data = dataUK, constrained = TRUE)
-  models$UK$adj$withE$CD <- cdModel(formula = f$UK$adj$withE, 
-                                    data = dataUK, constrained = TRUE)
-  # PT, CESkl
-  models$PT$unadj$noE$CESkl <- cesModel(formula = f$PT$unadj$noE, 
-                                        nest = nest$kl, data = dataPT, constrained = TRUE)
-  models$PT$adj$noE$CESkl <- cesModel(formula = f$PT$adj$noE, 
-                                      nest = nest$kl, data = dataPT, constrained = TRUE)
-  # PT, CESkle
-  models$PT$unadj$withE$CESkle <- cesModel(formula = f$PT$unadj$withE, 
-                                           nest = nest$kle, data = dataPT, constrained = TRUE)
-  models$PT$adj$withE$CESkle <- cesModel(formula = f$PT$adj$withE, 
-                                         nest = nest$kle, data = dataPT, constrained = TRUE)
-  # PT, CESlek
-  models$PT$unadj$withE$CESlek <- cesModel(formula = f$PT$unadj$withE, 
-                                           nest = nest$lek, data = dataPT, constrained = TRUE)
-  models$PT$adj$withE$CESlek <- cesModel(formula = f$PT$adj$withE, 
-                                         nest = nest$lek, data = dataPT, constrained = TRUE)
-  # PT, CESekl
-  models$PT$unadj$withE$CESekl <- cesModel(formula = f$PT$unadj$withE, 
-                                           nest = nest$ekl, data = dataPT, constrained = TRUE)
-  models$PT$adj$withE$CESekl <- cesModel(formula = f$PT$adj$withE, 
-                                         nest = nest$ekl, data = dataPT, constrained = TRUE)
-  # UK, CESkl
-  models$UK$unadj$noE$CESkl <- cesModel(formula = f$UK$unadj$noE, 
-                                        nest = nest$kl, data = dataUK, constrained = TRUE)
-  models$UK$adj$noE$CESkl <- cesModel(formula = f$UK$adj$noE, 
-                                      nest = nest$kl, data = dataUK, constrained = TRUE)
-  # UK, CESkle
-  models$UK$unadj$withE$CESkle <- cesModel(formula = f$UK$unadj$withE, 
-                                           nest = nest$kle, data = dataUK, constrained = TRUE)
-  models$UK$adj$withE$CESkle <- cesModel(formula = f$UK$adj$withE, 
-                                         nest = nest$kle, data = dataUK, constrained = TRUE)
-  # UK, CESlek
-  models$UK$unadj$withE$CESlek <- cesModel(formula = f$UK$unadj$withE, 
-                                           nest = nest$lek, data = dataUK, constrained = TRUE)
-  models$UK$adj$withE$CESlek <- cesModel(formula = f$UK$adj$withE, 
-                                         nest = nest$lek, data = dataUK, constrained = TRUE)
-  # UK, CESekl
-  models$UK$unadj$withE$CESekl <- cesModel(formula = f$UK$unadj$withE, 
-                                           nest = nest$ekl, data = dataUK, constrained = TRUE)
-  models$UK$adj$withE$CESekl <- cesModel(formula = f$UK$adj$withE, 
-                                         nest = nest$ekl, data = dataUK, constrained = TRUE)
+
+  models <- list()
+  for ()
+
+#   models <- NULL
+#   # Portugal, CD
+#   models$PT$unadj$noE$CD <- cdModel(formula = f$PT$unadj$noE, 
+#                                     data = dataPT, constrained = TRUE)
+#   models$PT$unadj$withE$CD <- cdModel(formula = f$PT$unadj$withE, 
+#                                       data = dataPT, constrained = TRUE)
+#   models$PT$adj$noE$CD <- cdModel(formula = f$PT$adj$noE, 
+#                                   data = dataPT, constrained = TRUE)
+#   models$PT$adj$withE$CD <- cdModel(formula = f$PT$adj$withE, 
+#                                     data = dataPT, constrained = TRUE)
+#   # UK, CD
+#   models$UK$unadj$noE$CD <- cdModel(formula = f$UK$unadj$noE, 
+#                                     data = dataUK, constrained = TRUE)
+#   models$UK$unadj$withE$CD <- cdModel(formula = f$UK$unadj$withE, 
+#                                       data = dataUK, constrained = TRUE)
+#   models$UK$adj$noE$CD <- cdModel(formula = f$UK$adj$noE, 
+#                                   data = dataUK, constrained = TRUE)
+#   models$UK$adj$withE$CD <- cdModel(formula = f$UK$adj$withE, 
+#                                     data = dataUK, constrained = TRUE)
+#   # PT, CESkl
+#   models$PT$unadj$noE$CESkl <- cesModel(formula = f$PT$unadj$noE, 
+#                                         nest = nest$kl, data = dataPT, constrained = TRUE)
+#   models$PT$adj$noE$CESkl <- cesModel(formula = f$PT$adj$noE, 
+#                                       nest = nest$kl, data = dataPT, constrained = TRUE)
+#   # PT, CESkle
+#   models$PT$unadj$withE$CESkle <- cesModel(formula = f$PT$unadj$withE, 
+#                                            nest = nest$kle, data = dataPT, constrained = TRUE)
+#   models$PT$adj$withE$CESkle <- cesModel(formula = f$PT$adj$withE, 
+#                                          nest = nest$kle, data = dataPT, constrained = TRUE)
+#   # PT, CESlek
+#   models$PT$unadj$withE$CESlek <- cesModel(formula = f$PT$unadj$withE, 
+#                                            nest = nest$lek, data = dataPT, constrained = TRUE)
+#   models$PT$adj$withE$CESlek <- cesModel(formula = f$PT$adj$withE, 
+#                                          nest = nest$lek, data = dataPT, constrained = TRUE)
+#   # PT, CESekl
+#   models$PT$unadj$withE$CESekl <- cesModel(formula = f$PT$unadj$withE, 
+#                                            nest = nest$ekl, data = dataPT, constrained = TRUE)
+#   models$PT$adj$withE$CESekl <- cesModel(formula = f$PT$adj$withE, 
+#                                          nest = nest$ekl, data = dataPT, constrained = TRUE)
+#   # UK, CESkl
+#   models$UK$unadj$noE$CESkl <- cesModel(formula = f$UK$unadj$noE, 
+#                                         nest = nest$kl, data = dataUK, constrained = TRUE)
+#   models$UK$adj$noE$CESkl <- cesModel(formula = f$UK$adj$noE, 
+#                                       nest = nest$kl, data = dataUK, constrained = TRUE)
+#   # UK, CESkle
+#   models$UK$unadj$withE$CESkle <- cesModel(formula = f$UK$unadj$withE, 
+#                                            nest = nest$kle, data = dataUK, constrained = TRUE)
+#   models$UK$adj$withE$CESkle <- cesModel(formula = f$UK$adj$withE, 
+#                                          nest = nest$kle, data = dataUK, constrained = TRUE)
+#   # UK, CESlek
+#   models$UK$unadj$withE$CESlek <- cesModel(formula = f$UK$unadj$withE, 
+#                                            nest = nest$lek, data = dataUK, constrained = TRUE)
+#   models$UK$adj$withE$CESlek <- cesModel(formula = f$UK$adj$withE, 
+#                                          nest = nest$lek, data = dataUK, constrained = TRUE)
+#   # UK, CESekl
+#   models$UK$unadj$withE$CESekl <- cesModel(formula = f$UK$unadj$withE, 
+#                                            nest = nest$ekl, data = dataUK, constrained = TRUE)
+#   models$UK$adj$withE$CESekl <- cesModel(formula = f$UK$adj$withE, 
+#                                          nest = nest$ekl, data = dataUK, constrained = TRUE)
   # Save models to disk.

### 2015-05-13 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
var names now use . instead of _

@@
 mdata_preeconometric <- melt(historicalData, 
-                             measure.vars = c("kPerGDP_unadj", "lPerGDP_unadj", "ePerGDP_unadj",
-                                              "kPerGDP_adj", "lPerGDP_adj", "ePerGDP_adj"),
+                             measure.vars = c("kPerGDP.unadj", "lPerGDP.unadj", "ePerGDP.unadj",
+                                              "kPerGDP.adj", "lPerGDP.adj", "ePerGDP.adj"),
                              variable.name = "variable",
@@
 mdata_preeconometric$adjusted <- lapply(mdata_preeconometric$variable, function(x) {
-  suffix <- unlist(strsplit(as.character(x), split="[_]")) [2]
+  suffix <- unlist(strsplit(as.character(x), split="[.]")) [2]
   if (suffix == "unadj"){

### 2015-05-14 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Cleaning up ESEE analysis using formulaUtils.

@@
 
-<<Data, eval=TRUE>>=
+<<Data>>=
 countries <- c("PT", "UK")
@@
 dataUK <- filter(Leeds, Country == "UK")
-@
-
-<<Time Series Variables>>=
-# This block of code sets up the time-series variables 
-# to be used for each country.
-# Adding this level of abstraction makes it easier 
-# for us to change variables later.
-# It also makes it easier to see what is going on 
-# in each formula throughout the document.
-# Use of substitute establishes an R "name"
-# that can be a component of a formula.
-
-vars <-   
-  list( 
-    PT = list(
-      response = list(unadjusted = "iGDP", adjusted = "iGDP"),
-      capital = list(unadjusted ="iKstkS.L", adjusted = "iKservS.L"),
-      labor = list(unadjusted = "iL", adjusted = "ihLest"),
-      energy = list(unadjusted = "iXpMP", adjusted = "iUMP"),
-      time = list(unadjusted = "iYear", adjusted = "iYear")
-    ), 
-    UK = list(
-      response = list(unadjusted = "iGDP", adjusted = "iGDP"),
-      capital = list(unadjusted = "iKstkO.WwithRD", adjusted = "iKservO.WwithRD"), 
-      labor = list(unadjusted = "iL", adjusted = "ihLest"),
-      energy = list(unadjusted = "iXp", adjusted = "iU"),
-      time = list(unadjusted = "iYear", adjusted = "iYear")
-    )
-  )
-
-# # Economic output
-# y_PT <- substitute(iGDP)
-# y_UK <- substitute(iGDP)
-# # Portugal undajusted inputs
-# k_PT_unadj <- substitute(iKstkS.L)
-# l_PT_unadj <- substitute(iL)
-# e_PT_unadj <- substitute(iXpMP)
-# # Portugal quality-adjusted inputs
-# k_PT_adj <- substitute(iKservS.L)
-# l_PT_adj <- substitute(ihLest)
-# e_PT_adj <- substitute(iUMP)
-# # UK unadjusted inputs
-# k_UK_unadj <- substitute(iKstkO.WwithRD)
-# l_UK_unadj <- substitute(iL)
-# e_UK_unadj <- substitute(iXp)
-# # UK quality-adjusted inputs
-# k_UK_adj <- substitute(iKservO.WwithRD)
-# l_UK_adj <- substitute(ihLest)
-# e_UK_adj <- substitute(iU)
-# # Time variables
-# t_PT <- substitute(iYear)
-# t_UK <- substitute(iYear)
-
-# vars <- list()
-# # Economic output
-# vars$y.PT <- substitute(iGDP)
-# vars$y.UK <- substitute(iGDP)
-# # Portugal undajusted inputs
-# vars$k.PT.unadj <- substitute(iKstkS.L)
-# vars$l.PT.unadj <- substitute(iL)
-# vars$e.PT.unadj <- substitute(iXpMP)
-# # Portugal quality-adjusted inputs
-# vars$k.PT.adj <- substitute(iKservS.L)
-# vars$l.PT.adj <- substitute(ihLest)
-# vars$e.PT.adj <- substitute(iUMP)
-# # UK unadjusted inputs
-# vars$k.UK.unadj <- substitute(iKstkO.WwithRD)
-# vars$l.UK.unadj <- substitute(iL)
-# vars$e.UK.unadj <- substitute(iXp)
-# # UK quality-adjusted inputs
-# vars$k.UK.adj <- substitute(iKservO.WwithRD)
-# vars$l.UK.adj <- substitute(ihLest)
-# vars$e.UK.adj <- substitute(iU)
-# # Time variables
-# vars$t.PT <- substitute(iYear)
-# vars$t.UK <- substitute(iYear)
-
-# y <- list()
-# k <- list()
-# l <- list()
-# e <- list()
-# t <- list()
-# # Economic output
-# y$PT <- substitute(iGDP)
-# y$UK <- substitute(iGDP)
-# # Portugal undajusted inputs
-# k$PT$unadj <- substitute(iKstkS.L)
-# l$PT$unadj <- substitute(iL)
-# e$PT$unadj <- substitute(iXpMP)
-# # Portugal quality-adjusted inputs
-# k$PT$adj <- substitute(iKservS.L)
-# l$PT$adj <- substitute(ihLest)
-# e$PT$adj <- substitute(iUMP)
-# # UK unadjusted inputs
-# k$UK$unadj <- substitute(iKstkO.WwithRD)
-# l$UK$unadj <- substitute(iL)
-# e$UK$unadj <- substitute(iXp)
-# # UK quality-adjusted inputs
-# k$UK$adj <- substitute(iKservO.WwithRD)
-# l$UK$adj <- substitute(ihLest)
-# e$UK$adj <- substitute(iU)
-# # Time variables
-# t$PT <- substitute(iYear)
-# t$UK <- substitute(iYear)
-# 
-# foo <- function(country = c("UK", "PT"), adjusted=TRUE, energy=TRUE, envir=parent.frame()) {
-#   country <- match.arg(country)
-#   type <- if (adjusted) "adj" else "unadj"
-#   res <- as.formula(
-#       paste(y[[country]], 
-#             paste(k[[country]][[type]], l[[country]][[type]], if (energy) e[[country]][[type]] else NULL, t[[country]], sep="+"), 
-#             sep="~")
-#     )
-#   environment(res) <- envir
-#   res
-# }
-# 
-# 
-# for (country in c("PT", "UK")) {
-#   for (adjusted in c(TRUE, FALSE)) {
-#     for (energy in c(TRUE, FALSE)) {
-#       print(foo(country = country, adjusted = adjusted, energy=energy))
-#     }
-#   }
-# }
-#
-
-# 
-# countries <- c(substitute(PT), substitute(UK))
-# adjusteds <- c(substitute(unadj), substitute(adj))
-# energies <- c(substitute(noE), substitute(withE))
-# f <- list()
-# for (country in c(substitute(PT), substitute(UK))){
-#   for (adjusted in adjusteds){
-#     for (energy in energies){
-#       if (energy == substitute(noE)){
-#         eval(substitute(f$ctry$adjst$ener <- y$ctry ~ k$ctry$adjst + l$ctry$adjst + t$ctry, 
-#                         list(ctry=country, adjst=adjusted, ener=energy)))
-#       } else if (energy == substitute(withE)){
-#         eval(substitute(f$ctry$adjst$ener <- y$ctry ~ k$ctry$adjst + l$ctry$adjst + e$ctry$adjst + t$ctry, 
-#                         list(ctry=country, adjst=adjusted, ener=energy)))
-#       } else {
-#         stop(paste("Unknown energy", energy, "in loop for f"))
-#       }
-#     }
-#   }
-# }
 
@@
 
-dataPT <- transform(dataPT, lPerGDP.unadj = eval(k_PT_unadj)/iGDP)
+dataPT <- within(filter(IST, Country == "PT"), {
+  kPerGDP.unadj <- iKstkS.L / iGDP # Works
+#   kPerGDP.unadj <- as.name(extract_rhs(forms$PT$unadjusted, 1)) / as.name(extract_lhs(forms$PT$unadjusted, 1)) # Fails
+})
+
+dataPT <- transform(dataPT, kPerGDP.unadj = eval(k_PT_unadj)/iGDP)
 dataPT <- transform(dataPT, lPerGDP.unadj = eval(l_PT_unadj)/iGDP)
@@
 # Set up the formulas for each type of analysis.
-# f <- NULL
-# f$PT$unadj$noE <- as.formula(
-#   substitute( y ~ k + l + t,
-#               list( y = y_PT, k = k_PT_unadj, 
-#                     l = l_PT_unadj, t = t_PT)))
-# f$PT$unadj$withE <- as.formula(
-#   substitute( y ~ k + l + e + t,
-#               list( y = y_PT, k = k_PT_unadj,
-#                     l = l_PT_unadj, e = e_PT_unadj, t = t_PT)))
-# f$PT$adj$noE <- as.formula(
-#   substitute( y ~ k + l + t,
-#               list( y = y_PT, k = k_PT_adj,
-#                     l = l_PT_adj, t = t_PT)))
-# f$PT$adj$withE <- as.formula(
-#   substitute( y ~ k + l + e + t,
-#               list( y = y_PT, k = k_PT_adj,
-#                     l = l_PT_adj, e = e_PT_adj, t = t_PT)))
-# f$UK$unadj$noE <- as.formula(
-#   substitute( y ~ k + l + t,
-#               list( y = y_UK, k = k_UK_unadj,
-#                     l = l_UK_unadj, t = t_UK)))
-# f$UK$unadj$withE <- as.formula(
-#   substitute( y ~ k + l + e + t,
-#               list( y = y_UK, k = k_UK_unadj,
-#                     l = l_UK_unadj, e = e_UK_unadj, t = t_UK)))
-# f$UK$adj$noE <- as.formula(
-#   substitute( y ~ k + l + t,
-#               list( y = y_UK, k = k_UK_adj,
-#                     l = l_UK_adj, t = t_UK)))
-# f$UK$adj$withE <- as.formula(
-#   substitute( y ~ k + l + e + t,
-#               list( y = y_UK, k = k_UK_adj,
-#                     l = l_UK_adj, e = e_UK_adj, t = t_UK)))
-
-makeFormula <- function(time.series, country, adjusted, energy, envir=parent.frame()) {
-  country <- match.arg(country, names(time.series))
-  if (! adjusted %in% c(FALSE, TRUE)){
-    stop("adjusted must be a boolean")
-  }
-  if (! energy %in% c(FALSE, TRUE)){
-    stop("energy must be a boolean")
-  }
-  type <- if (adjusted) "adjusted" else "unadjusted"
-  res <- as.formula( 
-    gsub( "\\+ *\\+", "+ ", 
-          paste(time.series[[country]][["response"]][[type]], 
-                paste(time.series[[country]][["capital"]][[type]], 
-                      time.series[[country]][["labor"]][[type]], 
-                      if (energy) {
-                        time.series[[country]][["energy"]][[type]]
-                      } else {
-                        NULL
-                      }, 
-                      time.series[[country]][["time"]][[type]], sep="+"), 
-                sep="~")
+forms <- 
+  list( 
+    PT = c(unadjusted = build_formula("iGDP", list("iKstkS.L", "iL", "iXpMP", "iYear")),
+             adjusted = build_formula("iGDP", list("iKservS.L", "ihLest", "iUMP", "iYear"))),
+    UK = c(unadjusted = build_formula("iGDP", list("iKservO.WwithRD", "iL", "iXp", "iYear")),
+             adjusted = build_formula("iGDP", list("iKservO.WwithRD", "ihLest", "iU", "iYear")))
   )
-  )
-  environment(res) <- envir
-  return(res)
-}
-
-f <- list()
-for (country in countries) {
-  for (adjusted in c(FALSE, TRUE)) {
-    for (energy in c(FALSE, TRUE)) {
-      newf <- makeFormula(vars, country = country, adjusted = adjusted, energy=energy)
-      namef <- paste(country, if(adjusted) "adj" else "unadj", if(energy) "withE" else "noE", sep=".")
-      newnames <- c(names(f), namef)
-      f <- c(f, newf)
-      names(f) <- newnames
-    }
-  }
-}
+
 @
@@
       \midrule
-      Output      & \Sexpr{vars$PT$response$unadjusted}       & \Sexpr{vars$UK$response$unadjusted}       \\
-      Capital     & \Sexpr{vars$PT$capital$unadjusted} & \Sexpr{vars$UK$capital$unadjusted} \\
-      Labor       & \Sexpr{vars$PT$labor$unadjusted} & \Sexpr{vars$UK$labor$unadjusted} \\
-      Energy      & \Sexpr{vars$PT$energy$unadjusted} & \Sexpr{vars$UK$energy$unadjusted} \\
+      Output      & \Sexpr{deparse(lhs(forms$PT$unadjusted))}   & \Sexpr{deparse(lhs(forms$UK$unadjusted))}   \\
+      Capital     & \Sexpr{extract_rhs(forms$PT$unadjusted, 1)} & \Sexpr{extract_rhs(forms$UK$unadjusted, 1)} \\
+      Labor       & \Sexpr{extract_rhs(forms$PT$unadjusted, 2)} & \Sexpr{extract_rhs(forms$UK$unadjusted, 2)} \\
+      Energy      & \Sexpr{extract_rhs(forms$PT$unadjusted, 3)} & \Sexpr{extract_rhs(forms$UK$unadjusted, 3)} \\
       \bottomrule
@@
       \midrule
-      Output      & \Sexpr{vars$PT$response$adjusted}       & \Sexpr{vars$UK$response$adjusted}       \\
-      Capital     & \Sexpr{vars$PT$capital$adjusted} & \Sexpr{vars$UK$capital$adjusted} \\
-      Labor       & \Sexpr{vars$PT$labor$adjusted} & \Sexpr{vars$UK$labor$adjusted} \\
-      Energy      & \Sexpr{vars$PT$energy$adjusted} & \Sexpr{vars$UK$energy$adjusted} \\
+      Output      & \Sexpr{deparse(lhs(forms$PT$adjusted))}   & \Sexpr{deparse(lhs(forms$UK$adjusted))}   \\
+      Capital     & \Sexpr{extract_rhs(forms$PT$adjusted, 1)} & \Sexpr{extract_rhs(forms$UK$adjusted, 1)} \\
+      Labor       & \Sexpr{extract_rhs(forms$PT$adjusted, 2)} & \Sexpr{extract_rhs(forms$UK$adjusted, 2)} \\
+      Energy      & \Sexpr{extract_rhs(forms$PT$adjusted, 3)} & \Sexpr{extract_rhs(forms$UK$adjusted, 3)} \\
       \bottomrule
@@
 <<Historical Data, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Historical data.", warning=FALSE>>=
-unadjVars_PT <- c(vars$PT$response$unadjusted, 
-                  vars$PT$capital$unadjusted, 
-                  vars$PT$labor$unadjusted, 
-                  vars$PT$energy$unadjusted)
-unadjVars_UK <- c(vars$UK$response$unadjusted, 
-                  vars$UK$capital$unadjusted, 
-                  vars$UK$labor$unadjusted, 
-                  vars$UK$energy$unadjusted)
+unadjVars_PT <- all.vars(forms$PT$unadjusted)[1:4]
+unadjVars_UK <- all.vars(forms$UK$unadjusted)[1:4]
 commonVars <- c("Year", "iYear", "Country")
@@
 unadjData$type <- "Unadjusted"
-adjVars_PT <- c(vars$PT$response$adjusted, 
-                vars$PT$capital$adjusted, 
-                vars$PT$labor$adjusted, 
-                vars$PT$energy$adjusted)
-adjVars_UK <- c(vars$UK$response$adjusted, 
-                vars$UK$capital$adjusted, 
-                vars$UK$labor$adjusted, 
-                vars$UK$energy$adjusted)
+adjVars_PT <- all.vars(forms$PT$adjusted)[1:4]
+adjVars_UK <- all.vars(forms$UK$adjusted)[1:4]
 adjData_PT <- historicalData[ , unique(c(adjVars_PT, commonVars))] %>% filter(Country=="PT")
@@
 adjData$type <- "Quality-adjusted"
-
 trimmedData <- plyr::rbind.fill(unadjData, adjData)
@@
 mdata$type <- relevelFactor(as.factor(mdata$type), c("Unadjusted", "Quality-adjusted"))
-mdata$variable <- relevelFactor(as.factor(mdata$variable), unique(
-  c(vars$PT$response$unadjusted, vars$PT$capital$unadjusted, vars$PT$labor$unadjusted, vars$PT$energy$unadjusted, 
-    vars$PT$response$adjusted,   vars$PT$capital$adjusted,   vars$PT$labor$adjusted,   vars$PT$energy$adjusted, 
-    vars$UK$response$unadjusted, vars$UK$capital$unadjusted, vars$UK$labor$unadjusted, vars$UK$energy$unadjusted, 
-    vars$UK$response$adjusted,   vars$UK$capital$adjusted,   vars$UK$labor$adjusted,   vars$UK$energy$adjusted)))
+mdata$variable <- relevelFactor(as.factor(mdata$variable), unique(c(unadjVars_PT, adjVars_PT, unadjVars_UK, adjVars_UK)))
+
 historicalPlot(mdata, 

### 2015-05-14 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Lots of progress using formulas.

@@
 require(ggplot2)
+require(mosaic)
 
@@
 
-<<Data>>=
-countries <- c("PT", "UK")
-dataPT <- filter(IST, Country == "PT")
-dataUK <- filter(Leeds, Country == "UK")
-
-# Create some pre-econometric ratios
-# Unadjusted variables
-dataPT <- transform(dataPT, kPerGDP.unadj = dataPT[[vars$PT$capital$unadjusted]]/dataPT[[vars$PT$response$unadjusted]])
-dataPT <- transform(dataPT, kPerGDP.unadj = iKstkS.L/iGDP)
-dataPT <- transform(dataPT, kPerGDP.unadj = as.name(vars$PT$capital$unadjusted)/iGDP)
-dataPT <- transform(dataPT, kPerGDP.unadj = eval(substitute(as.name(vars$PT$capital$unadjusted)))/iGDP)
-dataPT <- transform(dataPT, kPerGDP.unadj = eval(quote(as.name(vars$PT$capital$unadjusted)))/iGDP)
-
-dataPT <- within(filter(IST, Country == "PT"), {
-  kPerGDP.unadj <- iKstkS.L / iGDP # Works
-#   kPerGDP.unadj <- as.name(extract_rhs(forms$PT$unadjusted, 1)) / as.name(extract_lhs(forms$PT$unadjusted, 1)) # Fails
-})
-
-dataPT <- transform(dataPT, kPerGDP.unadj = eval(k_PT_unadj)/iGDP)
-dataPT <- transform(dataPT, lPerGDP.unadj = eval(l_PT_unadj)/iGDP)
-dataPT <- transform(dataPT, ePerGDP.unadj = eval(e_PT_unadj)/iGDP)
-dataUK <- transform(dataUK, kPerGDP.unadj = eval(k_UK_unadj)/iGDP)
-dataUK <- transform(dataUK, lPerGDP.unadj = eval(l_UK_unadj)/iGDP)
-dataUK <- transform(dataUK, ePerGDP.unadj = eval(e_UK_unadj)/iGDP)
-# Quality-adjusted variables
-dataPT <- transform(dataPT, kPerGDP.adj = eval(k_PT_adj)/iGDP)
-dataPT <- transform(dataPT, lPerGDP.adj = eval(l_PT_adj)/iGDP)
-dataPT <- transform(dataPT, ePerGDP.adj = eval(e_PT_adj)/iGDP)
-dataUK <- transform(dataUK, kPerGDP.adj = eval(k_UK_adj)/iGDP)
-dataUK <- transform(dataUK, lPerGDP.adj = eval(l_UK_adj)/iGDP)
-dataUK <- transform(dataUK, ePerGDP.adj = eval(e_UK_adj)/iGDP)
-
-# Now create the historicalData data frame
-historicalData <- plyr::rbind.fill(dataPT, dataUK)
-@
-
 <<Formulas>>=
 # Set up the formulas for each type of analysis.
-forms <- 
+# These formulas contain energy. 
+# We can use keep_summands to drop the energy term (3rd summand on the rhs)
+# later if needed.
+formulas <- 
   list( 
@@
   )
-
+@
+
+<<Data>>=
+# Create the historicalData data frames
+historicalData <- list()
+historicalData$PT <- filter(IST, Country == "PT")
+historicalData$UK <- filter(Leeds, Country == "UK")
+allHistoricalData <- do.call(plyr::rbind.fill, historicalData)
 @
@@
       \midrule
-      Output      & \Sexpr{deparse(lhs(forms$PT$unadjusted))}   & \Sexpr{deparse(lhs(forms$UK$unadjusted))}   \\
-      Capital     & \Sexpr{extract_rhs(forms$PT$unadjusted, 1)} & \Sexpr{extract_rhs(forms$UK$unadjusted, 1)} \\
-      Labor       & \Sexpr{extract_rhs(forms$PT$unadjusted, 2)} & \Sexpr{extract_rhs(forms$UK$unadjusted, 2)} \\
-      Energy      & \Sexpr{extract_rhs(forms$PT$unadjusted, 3)} & \Sexpr{extract_rhs(forms$UK$unadjusted, 3)} \\
+      Output      & \Sexpr{summands(formulas$PT$unadjusted, n=1, right=FALSE)}   
+                                                             & \Sexpr{summands(formulas$UK$unadjusted, n=1, right=FALSE)}\\
+      Capital     & \Sexpr{summands(formulas$PT$unadjusted, 1)} & \Sexpr{summands(formulas$UK$unadjusted, 1)} \\
+      Labor       & \Sexpr{summands(formulas$PT$unadjusted, 2)} & \Sexpr{summands(formulas$UK$unadjusted, 2)} \\
+      Energy      & \Sexpr{summands(formulas$PT$unadjusted, 3)} & \Sexpr{summands(formulas$UK$unadjusted, 3)} \\
       \bottomrule
@@
       \midrule
-      Output      & \Sexpr{deparse(lhs(forms$PT$adjusted))}   & \Sexpr{deparse(lhs(forms$UK$adjusted))}   \\
-      Capital     & \Sexpr{extract_rhs(forms$PT$adjusted, 1)} & \Sexpr{extract_rhs(forms$UK$adjusted, 1)} \\
-      Labor       & \Sexpr{extract_rhs(forms$PT$adjusted, 2)} & \Sexpr{extract_rhs(forms$UK$adjusted, 2)} \\
-      Energy      & \Sexpr{extract_rhs(forms$PT$adjusted, 3)} & \Sexpr{extract_rhs(forms$UK$adjusted, 3)} \\
+      Output      & \Sexpr{summands(formulas$PT$adjusted, n=1, right=FALSE)}   
+                                                           & \Sexpr{summands(formulas$UK$adjusted, n=1, right=FALSE)} \\
+      Capital     & \Sexpr{summands(formulas$PT$adjusted, 1)} & \Sexpr{summands(formulas$UK$adjusted, 1)} \\
+      Labor       & \Sexpr{summands(formulas$PT$adjusted, 2)} & \Sexpr{summands(formulas$UK$adjusted, 2)} \\
+      Energy      & \Sexpr{summands(formulas$PT$adjusted, 3)} & \Sexpr{summands(formulas$UK$adjusted, 3)} \\
       \bottomrule
@@
 <<Historical Data, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Historical data.", warning=FALSE>>=
-unadjVars_PT <- all.vars(forms$PT$unadjusted)[1:4]
-unadjVars_UK <- all.vars(forms$UK$unadjusted)[1:4]
-commonVars <- c("Year", "iYear", "Country")
-unadjData_PT <- historicalData[ , unique(c(unadjVars_PT, commonVars))] %>% filter(Country=="PT")
-unadjData_UK <- historicalData[ , unique(c(unadjVars_UK, commonVars))] %>% filter(Country=="UK")
-unadjData <- plyr::rbind.fill(unadjData_PT, unadjData_UK)
-unadjData$type <- "Unadjusted"
-adjVars_PT <- all.vars(forms$PT$adjusted)[1:4]
-adjVars_UK <- all.vars(forms$UK$adjusted)[1:4]
-adjData_PT <- historicalData[ , unique(c(adjVars_PT, commonVars))] %>% filter(Country=="PT")
-adjData_UK <- historicalData[ , unique(c(adjVars_UK, commonVars))] %>% filter(Country=="UK")
-adjData <- plyr::rbind.fill(adjData_PT, adjData_UK)
-adjData$type <- "Quality-adjusted"
-trimmedData <- plyr::rbind.fill(unadjData, adjData)
-
-mdata <- melt(trimmedData, 
-              measure.vars = unique(c(unadjVars_PT, unadjVars_UK, adjVars_PT, adjVars_UK)), 
-              variable.name = "variable",
-              value.name = "value")
+histDataForGraph <- leaf_apply(formulas, class = "formula", f=function(form, name){
+  meta <- strsplit(name, split="[.]") %>% unlist
+  Country <- meta[1]
+  flavor <- meta[2]
+  measure.vars <- c(summands(form, right=FALSE), summands(form, 1:3))
+  trimmed_historical_data <- historicalData[[Country]][c("Year", measure.vars)]
+  mtrimmed_historical_data <- melt(trimmed_historical_data, measure.vars = measure.vars, 
+                                   value.name = "value", variable.name = "variable")
+  mtrimmed_historical_data$Country <- Country
+  if (flavor == "unadjusted"){
+    mtrimmed_historical_data$flavor <- "Unadjusted"
+  } else if (flavor == "adjusted") {
+    mtrimmed_historical_data$flavor <- "Quality-adjusted"
+  } else {
+    stop(paste("Unknown flavor", flavor, "in histDataForGraph."))
+  }
+  return(mtrimmed_historical_data)
+}) %>% do.call(rbind, .)
 
 # Relevel factors before plotting
-mdata$Country <- relevelFactor(as.factor(mdata$Country), c("PT", "UK"))
-mdata$type <- relevelFactor(as.factor(mdata$type), c("Unadjusted", "Quality-adjusted"))
-mdata$variable <- relevelFactor(as.factor(mdata$variable), unique(c(unadjVars_PT, adjVars_PT, unadjVars_UK, adjVars_UK)))
-
-historicalPlot(mdata, 
+histDataForGraph$Country <- relevelFactor(as.factor(histDataForGraph$Country), c("PT", "UK"))
+histDataForGraph$flavor <- relevelFactor(as.factor(histDataForGraph$flavor), c("Unadjusted", "Quality-adjusted"))
+histDataForGraph$variable <- relevelFactor(as.factor(histDataForGraph$variable), unique(histDataForGraph$variable))
+
+historicalPlot(histDataForGraph, 
                mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
-               facet_formula = Country ~ type, 
-               line_types = c(1,2,4,3,2,4,3,2,3,2,3)) + 
+               facet_formula = Country ~ flavor, 
+               line_types = c(1,2,4,3,2,4,3,2,3,3)) + 
   scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12)) +
@@
 <<Pre-econometric graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Pre-econometric data.", warning=FALSE>>=
-# Melt the data
-mdata_preeconometric <- melt(historicalData, 
-                             measure.vars = c("kPerGDP.unadj", "lPerGDP.unadj", "ePerGDP.unadj",
-                                              "kPerGDP.adj", "lPerGDP.adj", "ePerGDP.adj"),
-                             variable.name = "variable",
-                             value.name = "value")
-# Add a column to say whether the variable is Unadjusted or Quality-adjusted based on variable name
-mdata_preeconometric$adjusted <- lapply(mdata_preeconometric$variable, function(x) {
-  suffix <- unlist(strsplit(as.character(x), split="[.]")) [2]
-  if (suffix == "unadj"){
-    return("Unadjusted")
-  } else if (suffix == "adj"){
-    return("Quality-adjusted")
-  } else {
-    stop(paste("Unknown suffix:", suffix))
-  }
-})
+
+# Create some pre-econometric ratios
+
+# # Melt the data
+# mdata_preeconometric <- melt(historicalData, 
+#                              measure.vars = c("kPerGDP.unadj", "lPerGDP.unadj", "ePerGDP.unadj",
+#                                               "kPerGDP.adj", "lPerGDP.adj", "ePerGDP.adj"),
+#                              variable.name = "variable",
+#                              value.name = "value")
+# # Add a column to say whether the variable is Unadjusted or Quality-adjusted based on variable name
+# mdata_preeconometric$adjusted <- lapply(mdata_preeconometric$variable, function(x) {
+#   suffix <- unlist(strsplit(as.character(x), split="[.]")) [2]
+#   if (suffix == "unadj"){
+#     return("Unadjusted")
+#   } else if (suffix == "adj"){
+#     return("Quality-adjusted")
+#   } else {
+#     stop(paste("Unknown suffix:", suffix))
+#   }
+# })
+
+pre_econometric_data <- leaf_apply(formulas, class = "formula", f=function(form, name){
+  meta <- strsplit(name, split="[.]") %>% unlist
+  Country <- meta[1]
+  flavor <- meta[2]
+  nums <- summands(form, n=1:3)
+  denom <- summands(form, n=1, right=FALSE)
+  ratios <- lapply(nums, function(num) {paste(num, denom, sep="/")}) %>% unlist
+  coltemplate <- build_formula(NULL, c("Year", ratios))
+  trimmed_historical_data <- historicalData[[Country]][all.vars(coltemplate)]
+  ratio_data <- evalFormula(coltemplate, data=trimmed_historical_data)$right
+  mratio_data <- melt(ratio_data, measure.vars = ratios, value.name = "ratio", variable.name = "variable")
+  mratio_data$Country <- Country
+  mratio_data$flavor <- flavor
+  return(mratio_data)
+}) %>% do.call(rbind, .)
+
 # Fix levels
-mdata_preeconometric$adjusted <- relevelFactor(as.factor(as.character(mdata_preeconometric$adjusted)), 
+pre_econometric_data$flavor <- relevelFactor(as.factor(as.character(pre_econometric_data$flavor)), 
                                                c("Unadjusted", "Quality-adjusted"))
-mdata_preeconometric$Country <- relevelFactor(as.factor(mdata_preeconometric$Country), 
+pre_econometric_data$Country <- relevelFactor(as.factor(pre_econometric_data$Country), 
                                               c("PT", "UK"))
+pre_econometric_data$variable <- relevelFactor(as.factor(pre_econometric_data$variable),
+                                               unique(pre_econometric_data$variable))
 # Now make the plot
-historicalPlot(mdata_preeconometric, 
-               mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
-               facet_formula = Country ~ adjusted, 
-               line_types = c(2,4,3, 2,4,3)) + 
+historicalPlot(pre_econometric_data, 
+               mapping=aes(x=Year, y=ratio, group=variable, linetype=variable), 
+               facet_formula = Country ~ flavor, 
+               line_types = c(2,4,3, 2,4,3, 2,3,3)) + 
   xlab("") + 
@@
 
-  models <- list()
-  for ()
+#   models <- list()
+#   for ()
 

### 2015-05-15 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Now using cleaner code to make all models.

@@
   )
+countries <- names(formulas)
 @
@@
   mtrimmed_historical_data$Country <- Country
-  if (flavor == "unadjusted"){
-    mtrimmed_historical_data$flavor <- "Unadjusted"
-  } else if (flavor == "adjusted") {
-    mtrimmed_historical_data$flavor <- "Quality-adjusted"
-  } else {
-    stop(paste("Unknown flavor", flavor, "in histDataForGraph."))
-  }
+  mtrimmed_historical_data$flavor <- if (flavor == "adjusted") "Quality-adjusted" else "Unadjusted"
   return(mtrimmed_historical_data)
@@
 <<Pre-econometric graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Pre-econometric data.", warning=FALSE>>=
-
-# Create some pre-econometric ratios
-
-# # Melt the data
-# mdata_preeconometric <- melt(historicalData, 
-#                              measure.vars = c("kPerGDP.unadj", "lPerGDP.unadj", "ePerGDP.unadj",
-#                                               "kPerGDP.adj", "lPerGDP.adj", "ePerGDP.adj"),
-#                              variable.name = "variable",
-#                              value.name = "value")
-# # Add a column to say whether the variable is Unadjusted or Quality-adjusted based on variable name
-# mdata_preeconometric$adjusted <- lapply(mdata_preeconometric$variable, function(x) {
-#   suffix <- unlist(strsplit(as.character(x), split="[.]")) [2]
-#   if (suffix == "unadj"){
-#     return("Unadjusted")
-#   } else if (suffix == "adj"){
-#     return("Quality-adjusted")
-#   } else {
-#     stop(paste("Unknown suffix:", suffix))
-#   }
-# })
-
 pre_econometric_data <- leaf_apply(formulas, class = "formula", f=function(form, name){
@@
   mratio_data$Country <- Country
-  mratio_data$flavor <- flavor
+  mratio_data$flavor <- if (flavor == "adjusted") "Quality-adjusted" else "Unadjusted"
   return(mratio_data)
@@
   # In RStudio, be sure to set the working directory to the source file directory.
-  nest <- NULL
-  nest$kl <- c(1,2)
-  nest$kle <- c(1,2,3)
-  nest$lek <- c(2,3,1)
-  nest$ekl <- c(3,1,2)
-
-#   models <- list()
-#   for ()
-
-#   models <- NULL
-#   # Portugal, CD
-#   models$PT$unadj$noE$CD <- cdModel(formula = f$PT$unadj$noE, 
-#                                     data = dataPT, constrained = TRUE)
-#   models$PT$unadj$withE$CD <- cdModel(formula = f$PT$unadj$withE, 
-#                                       data = dataPT, constrained = TRUE)
-#   models$PT$adj$noE$CD <- cdModel(formula = f$PT$adj$noE, 
-#                                   data = dataPT, constrained = TRUE)
-#   models$PT$adj$withE$CD <- cdModel(formula = f$PT$adj$withE, 
-#                                     data = dataPT, constrained = TRUE)
-#   # UK, CD
-#   models$UK$unadj$noE$CD <- cdModel(formula = f$UK$unadj$noE, 
-#                                     data = dataUK, constrained = TRUE)
-#   models$UK$unadj$withE$CD <- cdModel(formula = f$UK$unadj$withE, 
-#                                       data = dataUK, constrained = TRUE)
-#   models$UK$adj$noE$CD <- cdModel(formula = f$UK$adj$noE, 
-#                                   data = dataUK, constrained = TRUE)
-#   models$UK$adj$withE$CD <- cdModel(formula = f$UK$adj$withE, 
-#                                     data = dataUK, constrained = TRUE)
-#   # PT, CESkl
-#   models$PT$unadj$noE$CESkl <- cesModel(formula = f$PT$unadj$noE, 
-#                                         nest = nest$kl, data = dataPT, constrained = TRUE)
-#   models$PT$adj$noE$CESkl <- cesModel(formula = f$PT$adj$noE, 
-#                                       nest = nest$kl, data = dataPT, constrained = TRUE)
-#   # PT, CESkle
-#   models$PT$unadj$withE$CESkle <- cesModel(formula = f$PT$unadj$withE, 
-#                                            nest = nest$kle, data = dataPT, constrained = TRUE)
-#   models$PT$adj$withE$CESkle <- cesModel(formula = f$PT$adj$withE, 
-#                                          nest = nest$kle, data = dataPT, constrained = TRUE)
-#   # PT, CESlek
-#   models$PT$unadj$withE$CESlek <- cesModel(formula = f$PT$unadj$withE, 
-#                                            nest = nest$lek, data = dataPT, constrained = TRUE)
-#   models$PT$adj$withE$CESlek <- cesModel(formula = f$PT$adj$withE, 
-#                                          nest = nest$lek, data = dataPT, constrained = TRUE)
-#   # PT, CESekl
-#   models$PT$unadj$withE$CESekl <- cesModel(formula = f$PT$unadj$withE, 
-#                                            nest = nest$ekl, data = dataPT, constrained = TRUE)
-#   models$PT$adj$withE$CESekl <- cesModel(formula = f$PT$adj$withE, 
-#                                          nest = nest$ekl, data = dataPT, constrained = TRUE)
-#   # UK, CESkl
-#   models$UK$unadj$noE$CESkl <- cesModel(formula = f$UK$unadj$noE, 
-#                                         nest = nest$kl, data = dataUK, constrained = TRUE)
-#   models$UK$adj$noE$CESkl <- cesModel(formula = f$UK$adj$noE, 
-#                                       nest = nest$kl, data = dataUK, constrained = TRUE)
-#   # UK, CESkle
-#   models$UK$unadj$withE$CESkle <- cesModel(formula = f$UK$unadj$withE, 
-#                                            nest = nest$kle, data = dataUK, constrained = TRUE)
-#   models$UK$adj$withE$CESkle <- cesModel(formula = f$UK$adj$withE, 
-#                                          nest = nest$kle, data = dataUK, constrained = TRUE)
-#   # UK, CESlek
-#   models$UK$unadj$withE$CESlek <- cesModel(formula = f$UK$unadj$withE, 
-#                                            nest = nest$lek, data = dataUK, constrained = TRUE)
-#   models$UK$adj$withE$CESlek <- cesModel(formula = f$UK$adj$withE, 
-#                                          nest = nest$lek, data = dataUK, constrained = TRUE)
-#   # UK, CESekl
-#   models$UK$unadj$withE$CESekl <- cesModel(formula = f$UK$unadj$withE, 
-#                                            nest = nest$ekl, data = dataUK, constrained = TRUE)
-#   models$UK$adj$withE$CESekl <- cesModel(formula = f$UK$adj$withE, 
-#                                          nest = nest$ekl, data = dataUK, constrained = TRUE)
+  flavors <- c("unadjusted", "adjusted")
+  nests <- NULL
+  nests$kle <- c(1,2,3); nests$lek <- c(2,3,1); nests$ekl <- c(3,1,2)
+  energies <- c(FALSE, TRUE)
+
+  models <- list()
+  for(country in countries){
+    for (flavor in flavors){
+      fnoE <- keep_summands(formulas[[country]][[flavor]], -3) # Drop the energy term
+      fwithE <- formulas[[country]][[flavor]]
+      # CD models
+      models[[country]][[flavor]][["noE"]][["CD"]]   <- cdModel(fnoE, data = historicalData[[country]])
+      models[[country]][[flavor]][["withE"]][["CD"]] <- cdModel(fwithE, data = historicalData[[country]])
+      # CES models
+      models[[country]][[flavor]][["noE"]][["CES"]][["kl"]] <- cesModel(fnoE, data = historicalData[[country]], nest=c(1,2))
+      models[[country]][[flavor]][["withE"]][["CES"]] <- 
+        lapply(nests, function(nest){
+          cesModel(formula=fwithE, data=historicalData[[country]], nest=nest)
+        })
+    }      
+  }
+}
   # Save models to disk.

### 2015-05-15 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Entire analysis is working again with efficient code.

@@
   }
-}
   # Save models to disk.
@@
 <<Fitted_and_Residuals>>=
-extract_fitted_and_resid <- function(mod, id){
+fitted_and_resid_data <- leaf_apply(models, class=c("CDEmodel", "cesEst", "LINEXmodel"), function(mod, id){
   df <- mod$data[ , c("Year", "iGDP", "Country")]
@@
   id_list <- strsplit(id, split = "[.]")[[1]]
-  if (id_list[[2]] == "unadj"){
-    df$adjusted <- "Unadjusted"
-  } else if (id_list[[2]] == "adj"){
-    df$adjusted <- "Quality-adjusted"
+  if (id_list[[2]] == "unadjusted"){
+    df$flavor <- "Unadjusted"
+  } else if (id_list[[2]] == "adjusted"){
+    df$flavor <- "Quality-adjusted"
   } else {
@@
   df$model <- id_list[[4]]
+  df$nest <- if (length(id_list) > 4) id_list[[5]] else NA
   return(df)  
-}
-fitted_and_resid_data <- leaf_apply(models, extract_fitted_and_resid, class=c("CDEmodel", "cesEst", "LINEXmodel"))
-# Create a data frame.
-fitted_and_resid_data <- do.call(rbind, fitted_and_resid_data)
+}) %>% do.call(rbind, .)
 
@@
 fitted_and_resid_data$Country <- relevelFactor(as.factor(fitted_and_resid_data$Country), c("PT", "UK"))
-fitted_and_resid_data$adjusted <- relevelFactor(as.factor(fitted_and_resid_data$adjusted), c("Unadjusted", "Quality-adjusted"))
+fitted_and_resid_data$adjusted <- relevelFactor(as.factor(fitted_and_resid_data$flavor), c("Unadjusted", "Quality-adjusted"))
 fitted_and_resid_data$energy <- relevelFactor(as.factor(fitted_and_resid_data$energy), c("Without energy", "With Energy"))
@@
     scale_linetype_manual(values=c(2,3), name="") +
-    facet_grid(Country ~ adjusted) +
+    facet_grid(Country ~ flavor) +
     xy_theme()
@@
 <<Graphs CESkle-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($kl$)$e$ nesting. Solid line is historical GDP.">>=
-fittedGraph(filter(fitted_and_resid_data, model=="CESkle" | model=="CESkl"))
+fittedGraph(filter(fitted_and_resid_data, model=="CES" & (nest=="kle" | nest=="kl")))
 @
@@
 <<Graphs CESkle-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Residuals for CES models with $(kl$)$e$ nesting.">>=
-residualPlot(filter(fitted_and_resid_data, model=="CESkle" | model=="CESkl"))
+residualPlot(filter(fitted_and_resid_data, model=="CES" & (nest=="kle" | nest=="kl")))
 @
@@
 <<Graphs CESlek-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($le$)$k$ nesting. Solid line is historical GDP.">>=
-fittedGraph(filter(fitted_and_resid_data, model=="CESlek" | model=="CESkl"))
+fittedGraph(filter(fitted_and_resid_data, model=="CES" & (nest=="lek" | nest=="kl")))
 @
@@
 <<Graphs CESlek-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Residuals for CES models with $(le$)$k$ nesting.">>=
-residualPlot(filter(fitted_and_resid_data, model=="CESlek" | model=="CESkl"))
+residualPlot(filter(fitted_and_resid_data, model=="CES" & (nest == "lek" | nest=="kl")))
 @
@@
 <<Graphs CESekl-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($ek$)$l$ nesting. Solid line is historical GDP.">>=
-fittedGraph(filter(fitted_and_resid_data, model=="CESekl" | model=="CESkl"))
+fittedGraph(filter(fitted_and_resid_data, model=="CES" & (nest=="ekl" | nest=="kl")))
 @
@@
 <<Graphs CESekl-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Residuals for CES models with $(ek$)$l$ nesting.">>=
-residualPlot(filter(fitted_and_resid_data, model=="CESekl" | model=="CESkl"))
+residualPlot(filter(fitted_and_resid_data, model=="CES" & (nest=="ekl" | nest=="kl")))
 @
@@
 <<PT CES-kl, warning=FALSE>>=
-naturalCoef(models$PT$unadj$noE$CESkl)
-naturalCoef(models$PT$adj$noE$CESkl)
+naturalCoef(models$PT$unadj$noE$CES$kl)
+naturalCoef(models$PT$adj$noE$CES$kl)
 @
@@
 Both unadjusted and quality-adjusted variables give positive Solow residuals,
-\Sexpr{naturalCoef(models$PT$unadj$noE$CESkl)$lambda} for unadjusted inputs and
-\Sexpr{naturalCoef(models$PT$adj$noE$CESkl)$lambda} for quality-adjusted inputs.
+\Sexpr{naturalCoef(models$PT$unadj$noE$CES$kl)$lambda} for unadjusted inputs and
+\Sexpr{naturalCoef(models$PT$adj$noE$CES$kl)$lambda} for quality-adjusted inputs.
 Furthermore, quality-adjustment reduces the magnitude of the Solow residual.
@@
 <<PT CES-kle unadjusted, warning=FALSE>>=
-naturalCoef(models$PT$unadj$withE$CESkle)
+naturalCoef(models$PT$unadj$withE$CES$kle)
 @
@@
 <<PT CES-kle quality-adjusted, warning=FALSE>>=
-naturalCoef(models$PT$adj$withE$CESkle)
+naturalCoef(models$PT$adj$withE$CES$kle)
 @
@@
       \midrule
-      Without energy  & \Sexpr{naturalCoef(models$PT$unadj$noE$CESkl)$lambda} & \Sexpr{naturalCoef(models$PT$adj$noE$CESkl)$lambda} \\
-      With energy     & \Sexpr{naturalCoef(models$PT$unadj$withE$CESkle)$lambda} 
-                                                                    & \Sexpr{naturalCoef(models$PT$adj$withE$CESkle)$lambda} \\
+      Without energy  & \Sexpr{naturalCoef(models$PT$unadj$noE$CES$kl)$lambda} 
+                                                            & \Sexpr{naturalCoef(models$PT$adj$noE$CES$kl)$lambda} \\
+      With energy     & \Sexpr{naturalCoef(models$PT$unadj$withE$CES$kle)$lambda} 
+                                                            & \Sexpr{naturalCoef(models$PT$adj$withE$CES$kle)$lambda} \\
       \bottomrule
@@
       \midrule
-      Without energy  & \Sexpr{EconModels:::sse(models$PT$unadj$noE$CESkl)$sse} & \Sexpr{EconModels:::sse(models$PT$adj$noE$CESkl)$sse} \\
-      With energy     & \Sexpr{EconModels:::sse(models$PT$unadj$withE$CESkle)$sse} 
-                                                            & \Sexpr{EconModels:::sse(models$PT$adj$withE$CESkle)$sse} \\
+      Without energy  & \Sexpr{EconModels:::sse(models$PT$unadj$noE$CES$kl)$sse} 
+                                                            & \Sexpr{EconModels:::sse(models$PT$adj$noE$CES$kl)$sse} \\
+      With energy     & \Sexpr{EconModels:::sse(models$PT$unadj$withE$CES$kle)$sse} 
+                                                            & \Sexpr{EconModels:::sse(models$PT$adj$withE$CES$kle)$sse} \\
       \bottomrule
@@
 <<PT CES-lek unadjusted, warning=FALSE>>=
-naturalCoef(models$PT$unadj$withE$CESlek)
+naturalCoef(models$PT$unadj$withE$CES$lek)
 @
@@
 <<PT CES-lek quality-adjusted, warning=FALSE>>=
-naturalCoef(models$PT$adj$withE$CESlek)
+naturalCoef(models$PT$adj$withE$CES$lek)
 @
@@
       \midrule
-      Without energy  & \Sexpr{naturalCoef(models$PT$unadj$noE$CESkl)$lambda} & \Sexpr{naturalCoef(models$PT$adj$noE$CESkl)$lambda} \\
-      With energy     & \Sexpr{naturalCoef(models$PT$unadj$withE$CESlek)$lambda} & \Sexpr{naturalCoef(models$PT$adj$withE$CESle)$lambda} \\
+      Without energy  & \Sexpr{naturalCoef(models$PT$unadj$noE$CES$kl)$lambda} 
+                                        & \Sexpr{naturalCoef(models$PT$adj$noE$CES$kl)$lambda} \\
+      With energy     & \Sexpr{naturalCoef(models$PT$unadj$withE$CES$lek)$lambda} 
+                                        & \Sexpr{naturalCoef(models$PT$adj$withE$CESle)$lambda} \\
       \bottomrule
@@
       \midrule
-      Without energy  & \Sexpr{EconModels:::sse(models$PT$unadj$noE$CESkl)$sse} & \Sexpr{EconModels:::sse(models$PT$adj$noE$CESkl)$sse} \\
-      With energy     & \Sexpr{EconModels:::sse(models$PT$unadj$withE$CESlek)$sse} 
-                                                            & \Sexpr{EconModels:::sse(models$PT$adj$withE$CESlek)$sse} \\
+      Without energy  & \Sexpr{EconModels:::sse(models$PT$unadj$noE$CES$kl)$sse} 
+                                        & \Sexpr{EconModels:::sse(models$PT$adj$noE$CES$kl)$sse} \\
+      With energy     & \Sexpr{EconModels:::sse(models$PT$unadj$withE$CES$lek)$sse} 
+                                        & \Sexpr{EconModels:::sse(models$PT$adj$withE$CES$lek)$sse} \\
       \bottomrule
@@
 creating a slight increase from 
-\Sexpr{naturalCoef(models$PT$unadj$withE$CESlek)$lambda} to
-\Sexpr{naturalCoef(models$PT$adj$withE$CESlek)$lambda}.
+\Sexpr{naturalCoef(models$PT$unadj$withE$CES$lek)$lambda} to
+\Sexpr{naturalCoef(models$PT$adj$withE$CES$lek)$lambda}.
 
@@
 <<PT CES-ekl unadjusted, warning=FALSE>>=
-naturalCoef(models$PT$unadj$withE$CESekl)
+naturalCoef(models$PT$unadj$withE$CES$ekl)
 @
@@
 <<PT CES-ekl quality-adjusted, warning=FALSE>>=
-naturalCoef(models$PT$adj$withE$CESekl)
+naturalCoef(models$PT$adj$withE$CES$ekl)
 @
@@
       \midrule
-      Without energy  & \Sexpr{naturalCoef(models$PT$unadj$noE$CESkl)$lambda} & \Sexpr{naturalCoef(models$PT$adj$noE$CESkl)$lambda} \\
-      With energy     & \Sexpr{naturalCoef(models$PT$unadj$withE$CESekl)$lambda} 
-                                                                          & \Sexpr{naturalCoef(models$PT$adj$withE$CESekl)$lambda} \\
+      Without energy  & \Sexpr{naturalCoef(models$PT$unadj$noE$CES$kl)$lambda} 
+                                        & \Sexpr{naturalCoef(models$PT$adj$noE$CES$kl)$lambda} \\
+      With energy     & \Sexpr{naturalCoef(models$PT$unadj$withE$CES$ekl)$lambda} 
+                                        & \Sexpr{naturalCoef(models$PT$adj$withE$CES$ekl)$lambda} \\
       \bottomrule
@@
       \midrule
-      Without energy  & \Sexpr{EconModels:::sse(models$PT$unadj$noE$CESkl)$sse} & \Sexpr{EconModels:::sse(models$PT$adj$noE$CESkl)$sse} \\
-      With energy     & \Sexpr{EconModels:::sse(models$PT$unadj$withE$CESekl)$sse} 
-                                                            & \Sexpr{EconModels:::sse(models$PT$adj$withE$CESekl)$sse} \\
+      Without energy  & \Sexpr{EconModels:::sse(models$PT$unadj$noE$CES$kl)$sse} 
+                                        & \Sexpr{EconModels:::sse(models$PT$adj$noE$CES$kl)$sse} \\
+      With energy     & \Sexpr{EconModels:::sse(models$PT$unadj$withE$CES$ekl)$sse} 
+                                        & \Sexpr{EconModels:::sse(models$PT$adj$withE$CES$ekl)$sse} \\
       \bottomrule
@@
 Adding energy decreases the Solow residual 
-(from \Sexpr{naturalCoef(models$PT$unadj$withE$CESekl)$lambda} to 
-\Sexpr{naturalCoef(models$PT$adj$withE$CESekl)$lambda})
+(from \Sexpr{naturalCoef(models$PT$unadj$withE$CES$ekl)$lambda} to 
+\Sexpr{naturalCoef(models$PT$adj$withE$CES$ekl)$lambda})
 when enegy is included in the model.
 But, adding energy slightly increases the Solow residual
-(from \Sexpr{naturalCoef(models$PT$adj$noE$CESkl)$lambda} to \Sexpr{naturalCoef(models$PT$adj$withE$CESekl)$lambda})
+(from \Sexpr{naturalCoef(models$PT$adj$noE$CES$kl)$lambda} to \Sexpr{naturalCoef(models$PT$adj$withE$CES$ekl)$lambda})
 when quality-adjusted inputs are used.
@@
 <<UK CES-kl, warning=FALSE>>=
-naturalCoef(models$UK$unadj$noE$CESkl)
-naturalCoef(models$UK$adj$noE$CESkl)
+naturalCoef(models$UK$unadj$noE$CES$kl)
+naturalCoef(models$UK$adj$noE$CES$kl)
 @
@@
 Both unadjusted and quality-adjusted variables give positive Solow residuals for the UK,
-\Sexpr{naturalCoef(models$UK$unadj$noE$CESkl)$lambda} for unadjusted inputs and
-\Sexpr{naturalCoef(models$UK$adj$noE$CESkl)$lambda} for quality-adjusted inputs.
+\Sexpr{naturalCoef(models$UK$unadj$noE$CES$kl)$lambda} for unadjusted inputs and
+\Sexpr{naturalCoef(models$UK$adj$noE$CES$kl)$lambda} for quality-adjusted inputs.
 Furthermore, quality-adjustment reduces the magnitude of the UK Solow residual.
@@
 <<UK CES-kle unadjusted>>=
-naturalCoef(models$UK$unadj$withE$CESkle)
+naturalCoef(models$UK$unadj$withE$CES$kle)
 @
@@
 <<UK CES-kle quality-adjusted>>=
-naturalCoef(models$UK$adj$withE$CESkle)
+naturalCoef(models$UK$adj$withE$CES$kle)
 @
@@
       \midrule
-      Without energy  & \Sexpr{naturalCoef(models$UK$unadj$noE$CESkl)$lambda} & \Sexpr{naturalCoef(models$UK$adj$noE$CESkl)$lambda} \\
-      With energy     & \Sexpr{naturalCoef(models$UK$unadj$withE$CESkle)$lambda} 
-                                                                & \Sexpr{naturalCoef(models$UK$adj$withE$CESkle)$lambda} \\
+      Without energy  & \Sexpr{naturalCoef(models$UK$unadj$noE$CES$kl)$lambda} & \Sexpr{naturalCoef(models$UK$adj$noE$CES$kl)$lambda} \\
+      With energy     & \Sexpr{naturalCoef(models$UK$unadj$withE$CES$kle)$lambda} 
+                                                                & \Sexpr{naturalCoef(models$UK$adj$withE$CES$kle)$lambda} \\
       \bottomrule
@@
       \midrule
-      Without energy  & \Sexpr{EconModels:::sse(models$UK$unadj$noE$CESkl)$sse} & \Sexpr{EconModels:::sse(models$UK$adj$noE$CESkl)$sse} \\
-      With energy     & \Sexpr{EconModels:::sse(models$UK$unadj$withE$CESkle)$sse} 
-                                                            & \Sexpr{EconModels:::sse(models$UK$adj$withE$CESkle)$sse} \\
+      Without energy  & \Sexpr{EconModels:::sse(models$UK$unadj$noE$CES$kl)$sse} & \Sexpr{EconModels:::sse(models$UK$adj$noE$CES$kl)$sse} \\
+      With energy     & \Sexpr{EconModels:::sse(models$UK$unadj$withE$CES$kle)$sse} 
+                                                            & \Sexpr{EconModels:::sse(models$UK$adj$withE$CES$kle)$sse} \\
       \bottomrule
@@
 <<UK CES-lek unadjusted>>=
-naturalCoef(models$UK$unadj$withE$CESlek)
+naturalCoef(models$UK$unadj$withE$CES$lek)
 @
@@
 <<UK CES-lek quality-adjusted>>=
-naturalCoef(models$UK$adj$withE$CESlek)
+naturalCoef(models$UK$adj$withE$CES$lek)
 @
@@
       \midrule
-      Without energy  & \Sexpr{naturalCoef(models$UK$unadj$noE$CESkl)$lambda} & \Sexpr{naturalCoef(models$UK$adj$noE$CESkl)$lambda} \\
-      With energy     & \Sexpr{naturalCoef(models$UK$unadj$withE$CESlek)$lambda} 
-                                                            & \Sexpr{naturalCoef(models$UK$adj$withE$CESlek)$lambda} \\
+      Without energy  & \Sexpr{naturalCoef(models$UK$unadj$noE$CES$kl)$lambda} & \Sexpr{naturalCoef(models$UK$adj$noE$CES$kl)$lambda} \\
+      With energy     & \Sexpr{naturalCoef(models$UK$unadj$withE$CES$lek)$lambda} 
+                                                            & \Sexpr{naturalCoef(models$UK$adj$withE$CES$lek)$lambda} \\
       \bottomrule
@@
       \midrule
-      Without energy  & \Sexpr{EconModels:::sse(models$UK$unadj$noE$CESkl)$sse} & \Sexpr{EconModels:::sse(models$UK$adj$noE$CESkl)$sse} \\
-      With energy     & \Sexpr{EconModels:::sse(models$UK$unadj$withE$CESlek)$sse} 
-                                                            & \Sexpr{EconModels:::sse(models$UK$adj$withE$CESlek)$sse} \\
+      Without energy  & \Sexpr{EconModels:::sse(models$UK$unadj$noE$CES$kl)$sse} & \Sexpr{EconModels:::sse(models$UK$adj$noE$CES$kl)$sse} \\
+      With energy     & \Sexpr{EconModels:::sse(models$UK$unadj$withE$CES$lek)$sse} 
+                                                            & \Sexpr{EconModels:::sse(models$UK$adj$withE$CES$lek)$sse} \\
       \bottomrule
@@
 <<UK CES-ekl unadjusted>>=
-naturalCoef(models$UK$unadj$withE$CESekl)
+naturalCoef(models$UK$unadj$withE$CES$ekl)
 @
@@
 <<UK CES-ekl quality-adjusted>>=
-naturalCoef(models$UK$adj$withE$CESekl)
+naturalCoef(models$UK$adj$withE$CES$ekl)
 @
@@
       \midrule
-      Without energy  & \Sexpr{naturalCoef(models$UK$unadj$noE$CESkl)$lambda} & \Sexpr{naturalCoef(models$UK$adj$noE$CESkl)$lambda} \\
-      With energy     & \Sexpr{naturalCoef(models$UK$unadj$withE$CESekl)$lambda} 
-                                                            & \Sexpr{naturalCoef(models$UK$adj$withE$CESekl)$lambda} \\
+      Without energy  & \Sexpr{naturalCoef(models$UK$unadj$noE$CES$kl)$lambda} & \Sexpr{naturalCoef(models$UK$adj$noE$CES$kl)$lambda} \\
+      With energy     & \Sexpr{naturalCoef(models$UK$unadj$withE$CES$ekl)$lambda} 
+                                                            & \Sexpr{naturalCoef(models$UK$adj$withE$CES$ekl)$lambda} \\
       \bottomrule
@@
       \midrule
-      Without energy  & \Sexpr{EconModels:::sse(models$UK$unadj$noE$CESkl)$sse} & \Sexpr{EconModels:::sse(models$UK$adj$noE$CESkl)$sse} \\
-      With energy     & \Sexpr{EconModels:::sse(models$UK$unadj$withE$CESekl)$sse} 
-                                                            & \Sexpr{EconModels:::sse(models$UK$adj$withE$CESekl)$sse} \\
+      Without energy  & \Sexpr{EconModels:::sse(models$UK$unadj$noE$CES$kl)$sse} & \Sexpr{EconModels:::sse(models$UK$adj$noE$CES$kl)$sse} \\
+      With energy     & \Sexpr{EconModels:::sse(models$UK$unadj$withE$CES$ekl)$sse} 
+                                                            & \Sexpr{EconModels:::sse(models$UK$adj$withE$CES$ekl)$sse} \\
       \bottomrule

### 2015-05-15 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Fixed capital services vs. stock bug.

@@
              adjusted = build_formula("iGDP", list("iKservS.L", "ihLest", "iUMP", "iYear"))),
-    UK = c(unadjusted = build_formula("iGDP", list("iKservO.WwithRD", "iL", "iXp", "iYear")),
+    UK = c(unadjusted = build_formula("iGDP", list("iKstkO.WwithRD", "iL", "iXp", "iYear")),
              adjusted = build_formula("iGDP", list("iKservO.WwithRD", "ihLest", "iU", "iYear")))
@@
 fitted_and_resid_data$Country <- relevelFactor(as.factor(fitted_and_resid_data$Country), c("PT", "UK"))
-fitted_and_resid_data$adjusted <- relevelFactor(as.factor(fitted_and_resid_data$flavor), c("Unadjusted", "Quality-adjusted"))
+fitted_and_resid_data$flavor <- relevelFactor(as.factor(fitted_and_resid_data$flavor), c("Unadjusted", "Quality-adjusted"))
 fitted_and_resid_data$energy <- relevelFactor(as.factor(fitted_and_resid_data$energy), c("Without energy", "With Energy"))
@@
     facet_grid(Country ~ flavor) +
+    scale_x_continuous(breaks=c(1960, 1980, 2000)) +
     xy_theme()
@@
       With energy     & \Sexpr{naturalCoef(models$PT$unadj$withE$CES$lek)$lambda} 
-                                        & \Sexpr{naturalCoef(models$PT$adj$withE$CESle)$lambda} \\
+                                        & \Sexpr{naturalCoef(models$PT$adj$withE$CES$lek)$lambda} \\
       \bottomrule

### 2015-05-15 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
adj-->adjusted, unadj-->unadjusted

@@
 
-<<setup, echo=FALSE, message=FALSE, eval=TRUE>>=
+<<setup, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE>>=
 require(EconData)
@@
 # create the paper.
-#####################################################
+# ********************************************************
 rerunModels=FALSE
-#####################################################
+# ********************************************************
+
+opts_chunk$set(
+  # ********************************************************
+  eval=TRUE,
+  # ********************************************************
+  # tikz allows LaTeX code in graphical output. 
+  # E.g., "$y$" for a variable name in the legend for a graph.  
+  # dev='tikz',
+  tidy=FALSE,
+  comment=NA,
+  # Tells whether to cache output from chunks are saved. Cacheing saves time. 
+  # However, references to LaTeX tables DO NOT WORK if cacheing is turned on.
+  cache=FALSE,
+  warning=FALSE,  #Tells whether to show warnings in the output.
+  # Turns off messages for all chunks. 
+  # Set TRUE on an individual chunk to see it.
+  message=FALSE, 
+  # Tells whether to echo code for all chunks. 
+  # Set TRUE on an individual chunk to see its code.
+  echo=FALSE     
+)
 @
@@
                facet_formula = Country ~ flavor, 
-               line_types = c(1,2,4,3,2,4,3,2,3,3)) + 
+               line_types = c(1,2,4,3,2,4,3,2,3,2,3)) + 
   scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12)) +
@@
                facet_formula = Country ~ flavor, 
-               line_types = c(2,4,3, 2,4,3, 2,3,3)) + 
+               line_types = c(2,4,3, 2,4,3, 2,3,2, 3)) + 
   xlab("") + 
@@
 
-<<Graphs CESlek-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Residuals for CES models with $(le$)$k$ nesting.">>=
+<<Graphs CESlek-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Residuals for CES models with ($le$)$k$ nesting.">>=
 residualPlot(filter(fitted_and_resid_data, model=="CES" & (nest == "lek" | nest=="kl")))
@@
 <<Portugal C-D undadjusted without energy>>=
-naturalCoef(models$PT$unadj$noE$CD)
+naturalCoef(models$PT$unadjusted$noE$CD)
 @
@@
 <<Portugal C-D undadjusted with energy>>=
-naturalCoef(models$PT$unadj$withE$CD)
+naturalCoef(models$PT$unadjusted$withE$CD)
 @
@@
 However, the absolute value of \texttt{lambda} decreases from 
-\Sexpr{naturalCoef(models$PT$unadj$noE$CD)$lambda} to 
-\Sexpr{naturalCoef(models$PT$unadj$withE$CD)$lambda}
+\Sexpr{naturalCoef(models$PT$unadjusted$noE$CD)$lambda} to 
+\Sexpr{naturalCoef(models$PT$unadjusted$withE$CD)$lambda}
 when adding energy.
@@
 <<Portugal C-D adjusted without energy>>=
-naturalCoef(models$PT$adj$noE$CD)
+naturalCoef(models$PT$adjusted$noE$CD)
 @
@@
 <<Portugal C-D adjusted with energy>>=
-naturalCoef(models$PT$adj$withE$CD)
+naturalCoef(models$PT$adjusted$withE$CD)
 @
@@
 Using quality-adjusted inputs, the Solow residual (\texttt{lambda}) moves from 
-\Sexpr{naturalCoef(models$PT$adj$noE$CD)$lambda} to
-\Sexpr{naturalCoef(models$PT$adj$withE$CD)$lambda} when including energy.
+\Sexpr{naturalCoef(models$PT$adjusted$noE$CD)$lambda} to
+\Sexpr{naturalCoef(models$PT$adjusted$withE$CD)$lambda} when including energy.
 The absolute value of the Solow residual again decreases when adding energy.
@@
       \midrule
-      Without energy  & \Sexpr{naturalCoef(models$PT$unadj$noE$CD)$lambda}    & \Sexpr{naturalCoef(models$PT$adj$noE$CD)$lambda} \\
-      With energy     & \Sexpr{naturalCoef(models$PT$unadj$withE$CD)$lambda}  & \Sexpr{naturalCoef(models$PT$adj$withE$CD)$lambda} \\
+      Without energy  & \Sexpr{naturalCoef(models$PT$unadjusted$noE$CD)$lambda}    & \Sexpr{naturalCoef(models$PT$adjusted$noE$CD)$lambda} \\
+      With energy     & \Sexpr{naturalCoef(models$PT$unadjusted$withE$CD)$lambda}  & \Sexpr{naturalCoef(models$PT$adjusted$withE$CD)$lambda} \\
       \bottomrule
@@
       \midrule
-      Without energy  & \Sexpr{naturalCoef(models$UK$unadj$noE$CD)$lambda}   
-                                                & \Sexpr{naturalCoef(models$UK$adj$noE$CD)$lambda} \\
-      With energy     & \Sexpr{naturalCoef(models$UK$unadj$withE$CD)$lambda} 
-                                                & \Sexpr{naturalCoef(models$UK$adj$withE$CD)$lambda} \\
+      Without energy  & \Sexpr{naturalCoef(models$UK$unadjusted$noE$CD)$lambda}   
+                                                & \Sexpr{naturalCoef(models$UK$adjusted$noE$CD)$lambda} \\
+      With energy     & \Sexpr{naturalCoef(models$UK$unadjusted$withE$CD)$lambda} 
+                                                & \Sexpr{naturalCoef(models$UK$adjusted$withE$CD)$lambda} \\
       \bottomrule
@@
 For the UK, the quality-adjusted, with energy Solow residual is 
-\Sexpr{naturalCoef(models$UK$adj$withE$CD)$lambda * 100}\%,
+\Sexpr{naturalCoef(models$UK$adjusted$withE$CD)$lambda * 100}\%,
 a very small number indeed.
@@
 are required to effectively eliminate the Solow residual,
-reducing it to \Sexpr{naturalCoef(models$UK$adj$withE$CD)$lambda}.
+reducing it to \Sexpr{naturalCoef(models$UK$adjusted$withE$CD)$lambda}.
 
 Adding energy alone actually \emph{in}creases the Solow residual from 
-\Sexpr{naturalCoef(models$UK$unadj$noE$CD)$lambda} to
-\Sexpr{naturalCoef(models$UK$unadj$withE$CD)$lambda}.
+\Sexpr{naturalCoef(models$UK$unadjusted$noE$CD)$lambda} to
+\Sexpr{naturalCoef(models$UK$unadjusted$withE$CD)$lambda}.
 The details for each model with unadjusted factors of production are shown below.
@@
 <<UK CD Unadjusted Coefficients>>=
-naturalCoef(models$UK$unadj$noE$CD)
-naturalCoef(models$UK$unadj$withE$CD)
+naturalCoef(models$UK$unadjusted$noE$CD)
+naturalCoef(models$UK$unadjusted$withE$CD)
 @
@@
 as \texttt{alpha\_1} moves from 
-\Sexpr{naturalCoef(models$UK$unadj$noE$CD)$alpha_1} to
-\Sexpr{naturalCoef(models$UK$unadj$withE$CD)$alpha_1}.
+\Sexpr{naturalCoef(models$UK$unadjusted$noE$CD)$alpha_1} to
+\Sexpr{naturalCoef(models$UK$unadjusted$withE$CD)$alpha_1}.
 
@@
 <<UK CD Quality-adjusted Coefficients>>=
-naturalCoef(models$UK$adj$noE$CD)
-naturalCoef(models$UK$adj$withE$CD)
+naturalCoef(models$UK$adjusted$noE$CD)
+naturalCoef(models$UK$adjusted$withE$CD)
 @
@@
 \texttt{alpha\_1} moves from 
-\Sexpr{naturalCoef(models$UK$adj$noE$CD)$alpha_1} to
-\Sexpr{naturalCoef(models$UK$adj$withE$CD)$alpha_1}.
+\Sexpr{naturalCoef(models$UK$adjusted$noE$CD)$alpha_1} to
+\Sexpr{naturalCoef(models$UK$adjusted$withE$CD)$alpha_1}.
 
@@
 <<PT CES-kl, warning=FALSE>>=
-naturalCoef(models$PT$unadj$noE$CES$kl)
-naturalCoef(models$PT$adj$noE$CES$kl)
+naturalCoef(models$PT$unadjusted$noE$CES$kl)
+naturalCoef(models$PT$adjusted$noE$CES$kl)
 @
@@
 Both unadjusted and quality-adjusted variables give positive Solow residuals,
-\Sexpr{naturalCoef(models$PT$unadj$noE$CES$kl)$lambda} for unadjusted inputs and
-\Sexpr{naturalCoef(models$PT$adj$noE$CES$kl)$lambda} for quality-adjusted inputs.
+\Sexpr{naturalCoef(models$PT$unadjusted$noE$CES$kl)$lambda} for unadjusted inputs and
+\Sexpr{naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda} for quality-adjusted inputs.
 Furthermore, quality-adjustment reduces the magnitude of the Solow residual.
@@
 <<PT CES-kle unadjusted, warning=FALSE>>=
-naturalCoef(models$PT$unadj$withE$CES$kle)
+naturalCoef(models$PT$unadjusted$withE$CES$kle)
 @
@@
 <<PT CES-kle quality-adjusted, warning=FALSE>>=
-naturalCoef(models$PT$adj$withE$CES$kle)
+naturalCoef(models$PT$adjusted$withE$CES$kle)
 @
@@
       \midrule
-      Without energy  & \Sexpr{naturalCoef(models$PT$unadj$noE$CES$kl)$lambda} 
-                                                            & \Sexpr{naturalCoef(models$PT$adj$noE$CES$kl)$lambda} \\
-      With energy     & \Sexpr{naturalCoef(models$PT$unadj$withE$CES$kle)$lambda} 
-                                                            & \Sexpr{naturalCoef(models$PT$adj$withE$CES$kle)$lambda} \\
+      Without energy  & \Sexpr{naturalCoef(models$PT$unadjusted$noE$CES$kl)$lambda} 
+                                                            & \Sexpr{naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda} \\
+      With energy     & \Sexpr{naturalCoef(models$PT$unadjusted$withE$CES$kle)$lambda} 
+                                                            & \Sexpr{naturalCoef(models$PT$adjusted$withE$CES$kle)$lambda} \\
       \bottomrule
@@
       \midrule
-      Without energy  & \Sexpr{EconModels:::sse(models$PT$unadj$noE$CES$kl)$sse} 
-                                                            & \Sexpr{EconModels:::sse(models$PT$adj$noE$CES$kl)$sse} \\
-      With energy     & \Sexpr{EconModels:::sse(models$PT$unadj$withE$CES$kle)$sse} 
-                                                            & \Sexpr{EconModels:::sse(models$PT$adj$withE$CES$kle)$sse} \\
+      Without energy  & \Sexpr{EconModels:::sse(models$PT$unadjusted$noE$CES$kl)$sse} 
+                                                            & \Sexpr{EconModels:::sse(models$PT$adjusted$noE$CES$kl)$sse} \\
+      With energy     & \Sexpr{EconModels:::sse(models$PT$unadjusted$withE$CES$kle)$sse} 
+                                                            & \Sexpr{EconModels:::sse(models$PT$adjusted$withE$CES$kle)$sse} \\
       \bottomrule
@@
 <<PT CES-lek unadjusted, warning=FALSE>>=
-naturalCoef(models$PT$unadj$withE$CES$lek)
+naturalCoef(models$PT$unadjusted$withE$CES$lek)
 @
@@
 <<PT CES-lek quality-adjusted, warning=FALSE>>=
-naturalCoef(models$PT$adj$withE$CES$lek)
+naturalCoef(models$PT$adjusted$withE$CES$lek)
 @
@@
       \midrule
-      Without energy  & \Sexpr{naturalCoef(models$PT$unadj$noE$CES$kl)$lambda} 
-                                        & \Sexpr{naturalCoef(models$PT$adj$noE$CES$kl)$lambda} \\
-      With energy     & \Sexpr{naturalCoef(models$PT$unadj$withE$CES$lek)$lambda} 
-                                        & \Sexpr{naturalCoef(models$PT$adj$withE$CES$lek)$lambda} \\
+      Without energy  & \Sexpr{naturalCoef(models$PT$unadjusted$noE$CES$kl)$lambda} 
+                                        & \Sexpr{naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda} \\
+      With energy     & \Sexpr{naturalCoef(models$PT$unadjusted$withE$CES$lek)$lambda} 
+                                        & \Sexpr{naturalCoef(models$PT$adjusted$withE$CES$lek)$lambda} \\
       \bottomrule
@@
       \midrule
-      Without energy  & \Sexpr{EconModels:::sse(models$PT$unadj$noE$CES$kl)$sse} 
-                                        & \Sexpr{EconModels:::sse(models$PT$adj$noE$CES$kl)$sse} \\
-      With energy     & \Sexpr{EconModels:::sse(models$PT$unadj$withE$CES$lek)$sse} 
-                                        & \Sexpr{EconModels:::sse(models$PT$adj$withE$CES$lek)$sse} \\
+      Without energy  & \Sexpr{EconModels:::sse(models$PT$unadjusted$noE$CES$kl)$sse} 
+                                        & \Sexpr{EconModels:::sse(models$PT$adjusted$noE$CES$kl)$sse} \\
+      With energy     & \Sexpr{EconModels:::sse(models$PT$unadjusted$withE$CES$lek)$sse} 
+                                        & \Sexpr{EconModels:::sse(models$PT$adjusted$withE$CES$lek)$sse} \\
       \bottomrule
@@
 creating a slight increase from 
-\Sexpr{naturalCoef(models$PT$unadj$withE$CES$lek)$lambda} to
-\Sexpr{naturalCoef(models$PT$adj$withE$CES$lek)$lambda}.
+\Sexpr{naturalCoef(models$PT$unadjusted$withE$CES$lek)$lambda} to
+\Sexpr{naturalCoef(models$PT$adjusted$withE$CES$lek)$lambda}.
 
@@
 <<PT CES-ekl unadjusted, warning=FALSE>>=
-naturalCoef(models$PT$unadj$withE$CES$ekl)
+naturalCoef(models$PT$unadjusted$withE$CES$ekl)
 @
@@
 <<PT CES-ekl quality-adjusted, warning=FALSE>>=
-naturalCoef(models$PT$adj$withE$CES$ekl)
+naturalCoef(models$PT$adjusted$withE$CES$ekl)
 @
@@
       \midrule
-      Without energy  & \Sexpr{naturalCoef(models$PT$unadj$noE$CES$kl)$lambda} 
-                                        & \Sexpr{naturalCoef(models$PT$adj$noE$CES$kl)$lambda} \\
-      With energy     & \Sexpr{naturalCoef(models$PT$unadj$withE$CES$ekl)$lambda} 
-                                        & \Sexpr{naturalCoef(models$PT$adj$withE$CES$ekl)$lambda} \\
+      Without energy  & \Sexpr{naturalCoef(models$PT$unadjusted$noE$CES$kl)$lambda} 
+                                        & \Sexpr{naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda} \\
+      With energy     & \Sexpr{naturalCoef(models$PT$unadjusted$withE$CES$ekl)$lambda} 
+                                        & \Sexpr{naturalCoef(models$PT$adjusted$withE$CES$ekl)$lambda} \\
       \bottomrule
@@
       \midrule
-      Without energy  & \Sexpr{EconModels:::sse(models$PT$unadj$noE$CES$kl)$sse} 
-                                        & \Sexpr{EconModels:::sse(models$PT$adj$noE$CES$kl)$sse} \\
-      With energy     & \Sexpr{EconModels:::sse(models$PT$unadj$withE$CES$ekl)$sse} 
-                                        & \Sexpr{EconModels:::sse(models$PT$adj$withE$CES$ekl)$sse} \\
+      Without energy  & \Sexpr{EconModels:::sse(models$PT$unadjusted$noE$CES$kl)$sse} 
+                                        & \Sexpr{EconModels:::sse(models$PT$adjusted$noE$CES$kl)$sse} \\
+      With energy     & \Sexpr{EconModels:::sse(models$PT$unadjusted$withE$CES$ekl)$sse} 
+                                        & \Sexpr{EconModels:::sse(models$PT$adjusted$withE$CES$ekl)$sse} \\
       \bottomrule
@@
 Adding energy decreases the Solow residual 
-(from \Sexpr{naturalCoef(models$PT$unadj$withE$CES$ekl)$lambda} to 
-\Sexpr{naturalCoef(models$PT$adj$withE$CES$ekl)$lambda})
+(from \Sexpr{naturalCoef(models$PT$unadjusted$withE$CES$ekl)$lambda} to 
+\Sexpr{naturalCoef(models$PT$adjusted$withE$CES$ekl)$lambda})
 when enegy is included in the model.
 But, adding energy slightly increases the Solow residual
-(from \Sexpr{naturalCoef(models$PT$adj$noE$CES$kl)$lambda} to \Sexpr{naturalCoef(models$PT$adj$withE$CES$ekl)$lambda})
+(from \Sexpr{naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda} to \Sexpr{naturalCoef(models$PT$adjusted$withE$CES$ekl)$lambda})
 when quality-adjusted inputs are used.
@@
 <<UK CES-kl, warning=FALSE>>=
-naturalCoef(models$UK$unadj$noE$CES$kl)
-naturalCoef(models$UK$adj$noE$CES$kl)
+naturalCoef(models$UK$unadjusted$noE$CES$kl)
+naturalCoef(models$UK$adjusted$noE$CES$kl)
 @
@@
 Both unadjusted and quality-adjusted variables give positive Solow residuals for the UK,
-\Sexpr{naturalCoef(models$UK$unadj$noE$CES$kl)$lambda} for unadjusted inputs and
-\Sexpr{naturalCoef(models$UK$adj$noE$CES$kl)$lambda} for quality-adjusted inputs.
+\Sexpr{naturalCoef(models$UK$unadjusted$noE$CES$kl)$lambda} for unadjusted inputs and
+\Sexpr{naturalCoef(models$UK$adjusted$noE$CES$kl)$lambda} for quality-adjusted inputs.
 Furthermore, quality-adjustment reduces the magnitude of the UK Solow residual.
@@
 <<UK CES-kle unadjusted>>=
-naturalCoef(models$UK$unadj$withE$CES$kle)
+naturalCoef(models$UK$unadjusted$withE$CES$kle)
 @
@@
 <<UK CES-kle quality-adjusted>>=
-naturalCoef(models$UK$adj$withE$CES$kle)
+naturalCoef(models$UK$adjusted$withE$CES$kle)
 @
@@
       \midrule
-      Without energy  & \Sexpr{naturalCoef(models$UK$unadj$noE$CES$kl)$lambda} & \Sexpr{naturalCoef(models$UK$adj$noE$CES$kl)$lambda} \\
-      With energy     & \Sexpr{naturalCoef(models$UK$unadj$withE$CES$kle)$lambda} 
-                                                                & \Sexpr{naturalCoef(models$UK$adj$withE$CES$kle)$lambda} \\
+      Without energy  & \Sexpr{naturalCoef(models$UK$unadjusted$noE$CES$kl)$lambda} & \Sexpr{naturalCoef(models$UK$adjusted$noE$CES$kl)$lambda} \\
+      With energy     & \Sexpr{naturalCoef(models$UK$unadjusted$withE$CES$kle)$lambda} 
+                                                                & \Sexpr{naturalCoef(models$UK$adjusted$withE$CES$kle)$lambda} \\
       \bottomrule
@@
       \midrule
-      Without energy  & \Sexpr{EconModels:::sse(models$UK$unadj$noE$CES$kl)$sse} & \Sexpr{EconModels:::sse(models$UK$adj$noE$CES$kl)$sse} \\
-      With energy     & \Sexpr{EconModels:::sse(models$UK$unadj$withE$CES$kle)$sse} 
-                                                            & \Sexpr{EconModels:::sse(models$UK$adj$withE$CES$kle)$sse} \\
+      Without energy  & \Sexpr{EconModels:::sse(models$UK$unadjusted$noE$CES$kl)$sse} & \Sexpr{EconModels:::sse(models$UK$adjusted$noE$CES$kl)$sse} \\
+      With energy     & \Sexpr{EconModels:::sse(models$UK$unadjusted$withE$CES$kle)$sse} 
+                                                            & \Sexpr{EconModels:::sse(models$UK$adjusted$withE$CES$kle)$sse} \\
       \bottomrule
@@
 <<UK CES-lek unadjusted>>=
-naturalCoef(models$UK$unadj$withE$CES$lek)
+naturalCoef(models$UK$unadjusted$withE$CES$lek)
 @
@@
 <<UK CES-lek quality-adjusted>>=
-naturalCoef(models$UK$adj$withE$CES$lek)
+naturalCoef(models$UK$adjusted$withE$CES$lek)
 @
@@
       \midrule
-      Without energy  & \Sexpr{naturalCoef(models$UK$unadj$noE$CES$kl)$lambda} & \Sexpr{naturalCoef(models$UK$adj$noE$CES$kl)$lambda} \\
-      With energy     & \Sexpr{naturalCoef(models$UK$unadj$withE$CES$lek)$lambda} 
-                                                            & \Sexpr{naturalCoef(models$UK$adj$withE$CES$lek)$lambda} \\
-      \bottomrule
-    \end{tabular}
-  \end{center}
-\end{table}
-
-Table~\ref{tab:sse_CES-ekl_UK} shows the $sse$ values for each of these models.
+      Without energy  & \Sexpr{naturalCoef(models$UK$unadjusted$noE$CES$kl)$lambda} & \Sexpr{naturalCoef(models$UK$adjusted$noE$CES$kl)$lambda} \\
+      With energy     & \Sexpr{naturalCoef(models$UK$unadjusted$withE$CES$lek)$lambda} 
+                                                            & \Sexpr{naturalCoef(models$UK$adjusted$withE$CES$lek)$lambda} \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+\end{table}
+
+Table~\ref{tab:sse_CES-lek_UK} shows the $sse$ values for each of these models.
 
@@
       \midrule
-      Without energy  & \Sexpr{EconModels:::sse(models$UK$unadj$noE$CES$kl)$sse} & \Sexpr{EconModels:::sse(models$UK$adj$noE$CES$kl)$sse} \\
-      With energy     & \Sexpr{EconModels:::sse(models$UK$unadj$withE$CES$lek)$sse} 
-                                                            & \Sexpr{EconModels:::sse(models$UK$adj$withE$CES$lek)$sse} \\
+      Without energy  & \Sexpr{EconModels:::sse(models$UK$unadjusted$noE$CES$kl)$sse} & \Sexpr{EconModels:::sse(models$UK$adjusted$noE$CES$kl)$sse} \\
+      With energy     & \Sexpr{EconModels:::sse(models$UK$unadjusted$withE$CES$lek)$sse} 
+                                                            & \Sexpr{EconModels:::sse(models$UK$adjusted$withE$CES$lek)$sse} \\
       \bottomrule
@@
 <<UK CES-ekl unadjusted>>=
-naturalCoef(models$UK$unadj$withE$CES$ekl)
+naturalCoef(models$UK$unadjusted$withE$CES$ekl)
 @
@@
 <<UK CES-ekl quality-adjusted>>=
-naturalCoef(models$UK$adj$withE$CES$ekl)
+naturalCoef(models$UK$adjusted$withE$CES$ekl)
 @
@@
       \midrule
-      Without energy  & \Sexpr{naturalCoef(models$UK$unadj$noE$CES$kl)$lambda} & \Sexpr{naturalCoef(models$UK$adj$noE$CES$kl)$lambda} \\
-      With energy     & \Sexpr{naturalCoef(models$UK$unadj$withE$CES$ekl)$lambda} 
-                                                            & \Sexpr{naturalCoef(models$UK$adj$withE$CES$ekl)$lambda} \\
+      Without energy  & \Sexpr{naturalCoef(models$UK$unadjusted$noE$CES$kl)$lambda} & \Sexpr{naturalCoef(models$UK$adjusted$noE$CES$kl)$lambda} \\
+      With energy     & \Sexpr{naturalCoef(models$UK$unadjusted$withE$CES$ekl)$lambda} 
+                                                            & \Sexpr{naturalCoef(models$UK$adjusted$withE$CES$ekl)$lambda} \\
       \bottomrule
@@
       \midrule
-      Without energy  & \Sexpr{EconModels:::sse(models$UK$unadj$noE$CES$kl)$sse} & \Sexpr{EconModels:::sse(models$UK$adj$noE$CES$kl)$sse} \\
-      With energy     & \Sexpr{EconModels:::sse(models$UK$unadj$withE$CES$ekl)$sse} 
-                                                            & \Sexpr{EconModels:::sse(models$UK$adj$withE$CES$ekl)$sse} \\
+      Without energy  & \Sexpr{EconModels:::sse(models$UK$unadjusted$noE$CES$kl)$sse} & \Sexpr{EconModels:::sse(models$UK$adjusted$noE$CES$kl)$sse} \\
+      With energy     & \Sexpr{EconModels:::sse(models$UK$unadjusted$withE$CES$ekl)$sse} 
+                                                            & \Sexpr{EconModels:::sse(models$UK$adjusted$withE$CES$ekl)$sse} \\
       \bottomrule

### 2015-05-15 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Now includes boundary models in some graphs.

@@
 <<Fitted_and_Residuals>>=
-fitted_and_resid_data <- leaf_apply(models, class=c("CDEmodel", "cesEst", "LINEXmodel"), function(mod, id){
+fitted_and_resid_data <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), function(mod, id){
   df <- mod$data[ , c("Year", "iGDP", "Country")]

### 2015-05-17 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Added sentence and eqn about residuals.
Now using select.

--- 2015-05-15 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
@@
 <<Fitted_and_Residuals>>=
-fitted_and_resid_data <- leaf_apply(models, class=c("CDEmodel", "cesEst", "LINEXmodel"), function(mod, id){
-  df <- mod$data[ , c("Year", "iGDP", "Country")]
+fitted_and_resid_data <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), function(mod, id){
+  df <- select(mod$data, Year, iGDP, Country)
   # Trim fitted to be same length as df to eliminate problems with possible NAs at end of fitted
@@
 This section shows graphs of fits to historical data and residuals.
+Because we fit in log-space, the residuals ($r_i$) are defined as
+%
+\begin{equation} \label{eq:log-residuals}
+  r_i \equiv \ln(y_i) - \ln(\hat{y}_i) =\ln\left( \frac{y_i}{\hat{y}_i} \right), 
+\end{equation}
+%
+where $r_i$ will be zero when there is agreement between 
+historical~($y_i$) and fitted~($\hat{y}_i$) economic output.
 

### 2015-05-17 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Better y axes.

@@
     scale_x_continuous(breaks=c(1960, 1980, 2000)) +
+    scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12)) +
+    ylab("Indexed GDP (1960=1)") +
     xy_theme()

### 2015-05-17 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Working on dynamic solow residual.

@@
 historicalData <- list()
+commonVars <- c("Year", "Country", "Source")
 historicalData$PT <- filter(IST, Country == "PT") 
+historicalData$PT <- historicalData$PT[ , unique(c(commonVars,
+                                                   all.vars(formulas$PT$unadjusted), 
+                                                   all.vars(formulas$PT$adjusted)))]
 historicalData$UK <- filter(Leeds, Country == "UK")
-allHistoricalData <- do.call(plyr::rbind.fill, historicalData)
+historicalData$UK <- historicalData$UK[ , unique(c(commonVars,
+                                                   all.vars(formulas$UK$unadjusted), 
+                                                   all.vars(formulas$UK$adjusted)))]
+# allHistoricalData <- do.call(plyr::rbind.fill, historicalData)
 @
@@
 Unadjusted and quality-adjusted data for both Portugal and the United Kingdom 
-are shown in Figure~\ref{fig:Historical Data}.
-
-<<Historical Data, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Historical data.", warning=FALSE>>=
+are shown in Figure~\ref{fig:Historical Data Graph}.
+
+<<Historical Data Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Historical data.", warning=FALSE>>=
+# Melt the data into a form that is useful in a couple places
 histDataForGraph <- leaf_apply(formulas, class = "formula", f=function(form, name){
@@
 
+%++++++++++++++++++++++++++++++
+\subsection{Dynamic Solow Residual} 
+\label{sec:dynamic_solow_residual}
+%++++++++++++++++++++++++++++++
+
+This section presents results of dynamic Solow Residual analyses.
+
+<<Dynamic Solow Residual>>=
+# Calculate finite difference approximations of time derivatives for output and all factors of production
+lag <- 1       # Desired lag for calculations. Set to n for differences across n years.
+pad <- "tail"  # Desired padding for NA values
+
+fd <- leaf_apply(formulas, class = "formula", f = function(form, name){
+  meta <- strsplit(name, split="[.]") %>% unlist
+  Country <- meta[1]
+  flavor <- meta[2]
+
+  denom <- summands(form, n=length(summands(form))) # time variable
+  nums <- c(summands(form, n=1, right = FALSE), summands(form, n=1:3)) # y, k, l, and e
+  trimmedData <- historicalData[[Country]][c(denom, nums)] # columns are: iYear, y, k, l, and e
+  df <- list()
+  df <- historicalData[[Country]][ , c("Year", "Country")]
+  df$dydt <- ediff(trimmedData[[2]], pad=pad, lag=lag) / ediff(trimmedData[[1]], pad=pad, lag=lag)
+  df$dkdt <- ediff(trimmedData[[3]], pad=pad, lag=lag) / ediff(trimmedData[[1]], pad=pad, lag=lag)
+  df$dldt <- ediff(trimmedData[[4]], pad=pad, lag=lag) / ediff(trimmedData[[1]], pad=pad, lag=lag)
+  df$dedt <- ediff(trimmedData[[5]], pad=pad, lag=lag) / ediff(trimmedData[[1]], pad=pad, lag=lag)
+
+  df$flavor <- flavor
+  return(df)
+}) %>% do.call(rbind, .)
+
+# origCDKLCoeffs <- filter(AllCoeffs, method=="orig", model=="cd")
+# origCDKLCoeffs <- origCDKLCoeffs %>% select(method, country, Source, nestStr, energy, lambda, alpha, beta, gamma)
+# # Change name of Source REXS to REXS1960 and relevel to conform to information in fdlambda.
+# origCDKLCoeffs$Source <- as.character(origCDKLCoeffs$Source)
+# origCDKLCoeffs$Source <- replace(origCDKLCoeffs$Source, which(origCDKLCoeffs$Source=="REXS"), "REXS1960")
+# origCDKLCoeffs$Source <- as.factor(origCDKLCoeffs$Source)
+# origCDKLCoeffs$Source <- relevelFactor(origCDKLCoeffs$Source, levs = c("REXS1960", "IST", "Leeds"))
+# 
+# # Fill new columns in the fd data frame with 
+# # lambda, alpha, beta, and gamma values from the parameter estimation process.
+# # lambda, alpha, beta, and gamma values for the orig fits are in the origCDKLCoeffs data frame.
+# # Using the hint at 
+# # http://stackoverflow.com/questions/15059076/
+# # r-how-to-call-apply-like-function-on-each-row-of-dataframe-with-multiple-argum
+# labg <- apply(fd[ , c('Country', 'Source', 'energyType')], 1, function(x){
+#     row <- as.data.frame(filter(origCDKLCoeffs, 
+#                                 country==x["Country"], Source==x["Source"], energy==x["energyType"]))
+#     abg <- subset(row, select=c(lambda, alpha, beta, gamma))
+#     if (nrow(abg) < 1){ abg[1, ] <- NA }
+#     return(abg)
+#   })
+# cols <- do.call(rbind, labg)
+# fd <- cbind(fd, cols)
+# 
+# # Now calculate lambda by finite difference for every year to make a time series
+# fdlambda <- mutate(fd, lambda_diff = dydt/iGDP - (alpha/iK*dkdt + beta/iL*dldt + gamma/iE*dedt))
+# 
+# # Calculate the fraction of GDP growth in each year that is explained by the solow residual
+# fdlambda <- mutate(fdlambda, solowFrac = lambda_diff / (dydt/iGDP))
+# 
+# # Calculate average values for lambda and solowFrac
+# avgs <- fdlambda %>% 
+#   group_by(Source, Country, energyType) %>% 
+#   summarise(
+#     avg.lambda_diff = mean(lambda_diff, na.rm=TRUE),
+#     avg.solowFrac = mean(solowFrac, na.rm=TRUE)
+#     )
+
+@
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-05-18 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Now creating an AllCoeffs data frame.

@@
 }
+# Put all the coefficients into a data frame
+AllCoeffs <- leaf_apply(models, class = c("CDEmodel", "cesModel", "LINEXmodel"), f = function(mod, id){
+  # Parse the id to find out whether this is quality-adjusted data, etc.
+  id_list <- strsplit(id, split = "[.]")[[1]]
+  Country <- id_list[[1]]
+  flavor <- id_list[[2]]
+  energy <- id_list[[3]]
+  model <- id_list[[4]]
+  nest <- if(length(id_list) > 4) id_list[[5]] else NA
+  coeffs <- naturalCoef(mod)
+  res <- rbind(list(Country=Country, flavor=flavor, energy=energy, model=model, nest=nest))
+  res <- cbind(res, coeffs)
+  return(res)
+}) %>% do.call(plyr::rbind.fill, .)
 @
@@
 <<Fitted_and_Residuals>>=
-fitted_and_resid_data <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), function(mod, id){
+fitted_and_resid_data <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), f = function(mod, id){
   df <- select(mod$data, Year, iGDP, Country)

### 2015-05-20 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Now including dynamic SR graph.

@@
                                                    all.vars(formulas$UK$adjusted)))]
-# allHistoricalData <- do.call(plyr::rbind.fill, historicalData)
 @
@@
                                                unique(pre_econometric_data$variable))
-# Now make the plot
+# Now make the plot of pre-econometric data
 historicalPlot(pre_econometric_data, 
@@
   nests$kle <- c(1,2,3); nests$lek <- c(2,3,1); nests$ekl <- c(3,1,2)
-  energies <- c(FALSE, TRUE)
 
@@
       # CES models
-      models[[country]][[flavor]][["noE"]][["CES"]][["kl"]] <- cesModel(fnoE, data = historicalData[[country]], nest=c(1,2))
+      models[[country]][[flavor]][["noE"]][["CES"]][["kl"]] <- cesModel(fnoE, 
+                                                                        data = historicalData[[country]], 
+                                                                        nest=c(1,2))
       models[[country]][[flavor]][["withE"]][["CES"]] <- 
@@
 }) %>% do.call(plyr::rbind.fill, .)
+# Relevel factors
+AllCoeffs$Country <- relevelFactor(as.factor(unlist(AllCoeffs$Country)), c("PT", "UK"))
+AllCoeffs$flavor <- relevelFactor(as.factor(unlist(AllCoeffs$flavor)), c("unadjusted", "adjusted"))
+AllCoeffs$energy <- relevelFactor(as.factor(unlist(AllCoeffs$energy)), c("noE", "withE"))
+AllCoeffs$model <- relevelFactor(as.factor(unlist(AllCoeffs$model)), c("CD", "CES"))
+AllCoeffs$nest <- relevelFactor(as.factor(unlist(AllCoeffs$nest)), c("kl", "kle", "lek", "ekl"))
 @
@@
 
-<<Dynamic Solow Residual>>=
+<<Dynamic Solow Residuals>>=
 # Calculate finite difference approximations of time derivatives for output and all factors of production
-lag <- 1       # Desired lag for calculations. Set to n for differences across n years.
+lag <- 2       # Desired lag for calculations. Set to n for differences across n years.
 pad <- "tail"  # Desired padding for NA values
 
-fd <- leaf_apply(formulas, class = "formula", f = function(form, name){
-  meta <- strsplit(name, split="[.]") %>% unlist
-  Country <- meta[1]
-  flavor <- meta[2]
-
+flavors <- c("unadjusted", "adjusted")
+# model.types <- c("CD", "CES")
+model.types <- c("CD")
+nests <- list(kle=c(1,2,3), lek=c(2,3,1), ekl=c(3,1,2))
+
+dframes <- list()
+for (Coun in countries){
+  for (flav in flavors){
+    forms <- list(noE = keep_summands(formulas[[Coun]][[flav]], -3), withE = formulas[[Coun]][[flav]])
+    for (form in forms){
       denom <- summands(form, n=length(summands(form))) # time variable
-  nums <- c(summands(form, n=1, right = FALSE), summands(form, n=1:3)) # y, k, l, and e
-  trimmedData <- historicalData[[Country]][c(denom, nums)] # columns are: iYear, y, k, l, and e
-  df <- list()
-  df <- historicalData[[Country]][ , c("Year", "Country")]
-  df$dydt <- ediff(trimmedData[[2]], pad=pad, lag=lag) / ediff(trimmedData[[1]], pad=pad, lag=lag)
-  df$dkdt <- ediff(trimmedData[[3]], pad=pad, lag=lag) / ediff(trimmedData[[1]], pad=pad, lag=lag)
-  df$dldt <- ediff(trimmedData[[4]], pad=pad, lag=lag) / ediff(trimmedData[[1]], pad=pad, lag=lag)
-  df$dedt <- ediff(trimmedData[[5]], pad=pad, lag=lag) / ediff(trimmedData[[1]], pad=pad, lag=lag)
-
-  df$flavor <- flavor
-  return(df)
-}) %>% do.call(rbind, .)
-
-# origCDKLCoeffs <- filter(AllCoeffs, method=="orig", model=="cd")
-# origCDKLCoeffs <- origCDKLCoeffs %>% select(method, country, Source, nestStr, energy, lambda, alpha, beta, gamma)
-# # Change name of Source REXS to REXS1960 and relevel to conform to information in fdlambda.
-# origCDKLCoeffs$Source <- as.character(origCDKLCoeffs$Source)
-# origCDKLCoeffs$Source <- replace(origCDKLCoeffs$Source, which(origCDKLCoeffs$Source=="REXS"), "REXS1960")
-# origCDKLCoeffs$Source <- as.factor(origCDKLCoeffs$Source)
-# origCDKLCoeffs$Source <- relevelFactor(origCDKLCoeffs$Source, levs = c("REXS1960", "IST", "Leeds"))
-# 
-# # Fill new columns in the fd data frame with 
-# # lambda, alpha, beta, and gamma values from the parameter estimation process.
-# # lambda, alpha, beta, and gamma values for the orig fits are in the origCDKLCoeffs data frame.
-# # Using the hint at 
-# # http://stackoverflow.com/questions/15059076/
-# # r-how-to-call-apply-like-function-on-each-row-of-dataframe-with-multiple-argum
-# labg <- apply(fd[ , c('Country', 'Source', 'energyType')], 1, function(x){
-#     row <- as.data.frame(filter(origCDKLCoeffs, 
-#                                 country==x["Country"], Source==x["Source"], energy==x["energyType"]))
-#     abg <- subset(row, select=c(lambda, alpha, beta, gamma))
-#     if (nrow(abg) < 1){ abg[1, ] <- NA }
-#     return(abg)
-#   })
-# cols <- do.call(rbind, labg)
-# fd <- cbind(fd, cols)
-# 
-# # Now calculate lambda by finite difference for every year to make a time series
-# fdlambda <- mutate(fd, lambda_diff = dydt/iGDP - (alpha/iK*dkdt + beta/iL*dldt + gamma/iE*dedt))
-# 
-# # Calculate the fraction of GDP growth in each year that is explained by the solow residual
-# fdlambda <- mutate(fdlambda, solowFrac = lambda_diff / (dydt/iGDP))
-# 
-# # Calculate average values for lambda and solowFrac
-# avgs <- fdlambda %>% 
-#   group_by(Source, Country, energyType) %>% 
-#   summarise(
-#     avg.lambda_diff = mean(lambda_diff, na.rm=TRUE),
-#     avg.solowFrac = mean(solowFrac, na.rm=TRUE)
-#     )
-
+      nums <- all.vars(form) [1:(length(all.vars(form))-1)] # y, k, l, and e (if present)
+      trimmedData <- historicalData[[Coun]][c(denom, nums)] # columns are: iYear, y, k, l, and e (if present)
+      df <- historicalData[[Coun]][ , c(nums, "Year")]
+      # Calculate names for the columns of finite difference derivatives
+      derivNames <- lapply(1:length(nums), function(i){paste0("d", nums[[i]], "/", "dt")}) %>% unlist
+      derivCols <- lapply(1:length(nums), function(i){
+        # Calculate finite difference derivative columns
+        ediff(trimmedData[[i+1]], pad=pad, lag=lag) / ediff(trimmedData[[1]], pad=pad, lag=lag)
+      }) %>% do.call(cbind, .) %>% as.data.frame
+      names(derivCols) <- derivNames
+      df <- cbind(derivCols, df)
+      e <- if (length(summands(form))==4) "withE" else "noE"
+      for (m in model.types){
+        origCoeffs <- filter(AllCoeffs, model==m & energy==e & Country==Coun & flavor==flav)
+        df <- cbind(df, origCoeffs)
+        if (m == "CD"){
+          lambda <- lapply(1:length(derivNames), function(i){
+            # derivative term divided by its numerator.
+            # derivative term is in the ith column of df
+            # numerator is in i + length(derivNames) th column of df
+            out <- df[[i]] / df[[i+length(derivNames)]]
+            if (i > 1){
+              # Need to make it negative and multiply by the corresponding alpha term.
+              # Typical setup is that columns 2 is capital, and we need alpha_1 for capital.
+              # So, subtract 1 from i.
+              out <- - out * df[[paste0("alpha_", i-1)]]
+            }
+            return(out)
+          }) %>% as.data.frame %>% rowSums
+          df$lambda_fd <- lambda
+          avg.lambda_fd <- mean(df$lambda_fd, na.rm = TRUE)
+          # Fraction of growth explained by Solow Residual
+          df$solowFrac <- df$lambda_fd / (df[[1]] / df[[length(derivNames) + 1]])
+          avg.solowFrac <- mean(df$solowFrac, na.rm = TRUE)
+        } else if (m == "CES"){
+
+        } else {
+          stop(paste("Unknown model", model))
+        }
+        df$flavor <- if (flav == "adjusted") "Quality-adjusted" else "Unadjusted"
+        df$flavor <- relevelFactor(as.factor(df$flavor), c("Unadjusted", "Quality-adjusted"))
+        df$energy <- if (e == "noE") "Without energy" else "With energy"
+        df$energy <- relevelFactor(as.factor(df$energy), c("Without energy", "With energy"))
+        dframes[[length(dframes)+1]] <- df
+      }
+    }
+  }      
+}
+solowResiduals <- do.call(plyr::rbind.fill, dframes)
+@
+
+Figure~\ref{fig:DynamicSR_CD_Graph} shows the evolution 
+of the Solow Residual~($\lambda$) over time
+as calculated by Equation~\ref{eq:lambdaij} 
+with timespan for finite differences set to 
+\Sexpr{lag}~\Sexpr{if (lag == 1) "year" else "years"}.
+
+<<DynamicSR_CD_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residuals for the Cobb-Douglas model.">>=
+data <- filter(solowResiduals, model=="CD")
+ggplot(data=data) +
+  geom_line(mapping=aes(x=Year, y=lambda_fd, linetype=energy)) +
+  scale_linetype_manual(values=c(2,3), name="") +
+  facet_grid(Country ~ flavor) +
+  scale_x_continuous(breaks=c(1960, 1980, 2000)) +
+  xlab("") + 
+  ylab(expression(lambda)) +
+  xy_theme()
 @

### 2015-05-20 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Rearranged sections.

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Analysis}
+\label{sec:analysis}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+For now, I've organized the analysis around questions that we would like to answer.
+
 %++++++++++++++++++++++++++++++
-\subsection{Dynamic Solow Residual} 
-\label{sec:dynamic_solow_residual}
+\subsection{Does quality-adjusting the factors of production 
+            decrease the dynamic Solow residual?} 
+\label{sec:quality_adj_energy_and_dynamic_solow_residual}
 %++++++++++++++++++++++++++++++
-
-This section presents results of dynamic Solow Residual analyses.
 
@@
 # Calculate finite difference approximations of time derivatives for output and all factors of production
-lag <- 2       # Desired lag for calculations. Set to n for differences across n years.
+lag <- 3       # Desired lag for calculations. Set to n for differences across n years.
 pad <- "tail"  # Desired padding for NA values
@@
 Figure~\ref{fig:DynamicSR_CD_Graph} shows the evolution 
-of the Solow Residual~($\lambda$) over time
+of the Solow residual~($\lambda$) over time
 as calculated by Equation~\ref{eq:lambdaij} 
-with timespan for finite differences set to 
+with the timespan for finite differences ($t_j - t_i$) set to 
 \Sexpr{lag}~\Sexpr{if (lag == 1) "year" else "years"}.
+It appears that quality-adjusting the factors of production
+decreases the Solow residual~($\lambda$).
 
@@
   xlab("") + 
-  ylab(expression(lambda)) +
+  ylab(expression(lambda[ij])) +
   xy_theme()
 @
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Analysis}
-\label{sec:analysis}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-For now, I've organized the analysis around questions that we would like to answer.
 

### 2015-05-22 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
All Solow residual derivations in appendix

@@
 and $\lambda$ is the Solow residual.
-
-%..............................
-\paragraph{Estimating the Solow residual} 
-\label{sec:estimating_the_solow_residual}
-%..............................
-
-Assuming that parameters $\theta$, $\alpha$, and $\beta$
-in Equation~\ref{eq:CDe} are known from parameter estimation,
-we can estimate the value of $\lambda$ as follows.
-First, assume constant returns to scale such that 
-$\alpha + \beta + \gamma = 1$, 
-and calculate $\gamma = 1 - \alpha - \beta$.
-Then, take the natural logarithm ($\ln$) of Equation~\ref{eq:CDe} to obtain
-%
-\begin{equation} \label{eq:lnCD}
-  \ln y = \ln \theta + \ln A + \alpha \ln k + \beta \ln l + (1 - \alpha - \beta) \ln e \;.
-\end{equation}
-%
-By taking the derivative of Equation~\ref{eq:lnCD} with respect to time ($t$) 
-and noting that model parameters $\theta$, $\alpha$, and $\beta$ are 
-constant with respect to time, we obtain
-%
-\begin{equation} \label{eq:ddtlnCD}
-  \frac{1}{y}\frac{\mathrm{d}y}{\mathrm{d}t} 
-      = \frac{1}{A}\frac{\mathrm{d}A}{\mathrm{d}t} 
-      + \alpha \frac{1}{k}\frac{\mathrm{d}k}{\mathrm{d}t} 
-      + \beta \frac{1}{l}\frac{\mathrm{d}l}{\mathrm{d}t} 
-      + (1 - \alpha - \beta) \frac{1}{e}\frac{\mathrm{d}e}{\mathrm{d}t} \;.
-\end{equation}
-%
-Solving for the total factor productivity term gives
-%
-\begin{equation} \label{eq:solow_resid}
-  \frac{1}{A}\frac{\mathrm{d}A}{\mathrm{d}t} 
-      = \frac{1}{y}\frac{\mathrm{d}y}{\mathrm{d}t} 
-      - \left[
-              \alpha \frac{1}{k}\frac{\mathrm{d}k}{\mathrm{d}t} 
-              + \beta \frac{1}{l}\frac{\mathrm{d}l}{\mathrm{d}t} 
-              + (1 - \alpha - \beta) \frac{1}{e}\frac{\mathrm{d}e}{\mathrm{d}t} 
-        \right] \;.
-\end{equation}
-%
-Recognizing that $A \equiv \mathrm{e}^{\lambda (t-t_0)}$ gives
-%
-\begin{equation}
-  \frac{1}{A}\frac{\mathrm{d}A}{\mathrm{d}t} 
-    = \frac{1}{\mathrm{e}^{\lambda (t-t_0)}} \; \lambda \mathrm{e}^{\lambda (t-t_0)}
-    = \lambda \; ,
-\end{equation}
-%
-which can be substituted into Equation~\ref{eq:solow_resid} to find
-%
-\begin{equation} \label{eq:lambda}
-  \lambda 
-    = \frac{1}{y}\frac{\mathrm{d}y}{\mathrm{d}t} 
-    - \left[
-              \alpha \frac{1}{k}\frac{\mathrm{d}k}{\mathrm{d}t} 
-              + \beta \frac{1}{l}\frac{\mathrm{d}l}{\mathrm{d}t} 
-              + (1 - \alpha - \beta) \frac{1}{e}\frac{\mathrm{d}e}{\mathrm{d}t} 
-      \right] \;.
-\end{equation}
-%
-Equation~\ref{eq:lambda} applies for any instant in time.
-
-If we approximate derivatives in Equation~\ref{eq:lambda} with forward differences
-between times $i$ and $j$, we find
-%
-\begin{equation} \label{eq:lambdaij}
-  \lambda_{i,j}
-    = \frac{1}{y_i}\frac{y_j - y_i}{t_j - t_i} 
-    - \left[
-            \alpha \frac{1}{k_i}\frac{k_j - k_i}{t_j - t_i} 
-            + \beta \frac{1}{l_i}\frac{l_j - l_i}{t_j - t_i} 
-            + (1 - \alpha - \beta) \frac{1}{e_i}\frac{e_j - e_i}{t_j - t_i} 
-      \right] \;,
-\end{equation}
-% 
-where $\lambda_{i,j}$ approximates the true, instantaneous value of $\lambda$
-from Equation~\ref{eq:lambda} between times $i$ and $j$.
-
-Interestingly, 
-%
-\begin{equation}
-  \lambda_{1,n}
-    \neq \sum_{i=2}^{n} \lambda_{i,i-1}  \;.
-\end{equation}
-% 
-Rather,
-%
-\begin{equation} \label{eq:lambda1n}
-  \lambda_{1,n}
-    = \frac{1}{y_1}\frac{y_n - y_1}{t_n - t_1} 
-      - \left[ 
-            \alpha \frac{1}{k_1}\frac{k_n - k_1}{t_n - t_1} 
-            + \beta \frac{1}{l_1}\frac{l_n - l_1}{t_n - t_1} 
-            + (1 - \alpha - \beta) \frac{1}{e_1}\frac{e_n - e_1}{t_n - t_1} 
-      \right] \; ,
-\end{equation}
-% 
-which will become increasingly inaccurate over large time spans,
-because $y_1$, $k_1$, $l_1$, and $e_1$ will be less representative
-of the average value of $y$, $k$, $l$, and $e$ in the time span, respectively.
-This suggests that an averaging approach such as
-%
-\begin{equation}
-  \lambda_{1,n}
-    = \frac{\sum_{i=2}^{n} \lambda_{i,i-1}}{n-1}
-\end{equation}
-%
-is a better approximation of Equation~\ref{eq:lambda1n},
-which is, itself, an approximation of the true value of $\lambda$ 
-given by Equation~\ref{eq:lambda}.
-
-%..............................
-\paragraph{Fraction of growth explained by the Solow residual} 
-\label{sec:fraction_of_growth_solow}
-%..............................
-
-The fraction~($f$) of GDP growth explained by the Solow residual
-can be given as
-%
-\begin{equation} \label{eq:frac_growth_explained_by_solow}
-  f \equiv \frac{\lambda}{\frac{1}{y}\frac{\mathrm{d}y}{\mathrm{d}t}} 
-            = 1 - \frac{\alpha \frac{1}{k}\frac{\mathrm{d}k}{\mathrm{d}t} 
-                      + \beta \frac{1}{l}\frac{\mathrm{d}l}{\mathrm{d}t} 
-                      + (1 - \alpha - \beta) \frac{1}{e}\frac{\mathrm{d}e}{\mathrm{d}t}}
-                  {\frac{1}{y}\frac{\mathrm{d}y}{\mathrm{d}t}} \; .
-\end{equation}
-%
-Using forward differences to estimate $f$ yields
-%
-\begin{equation} \label{eq:f_finite_diff_1}
-  f_{i,j} = \frac{\lambda_{i,j}}{\frac{1}{y_i}\frac{y_j - y_i}{t_j - t_i}}
-       = 1 - \frac{\alpha \frac{1}{k_i}\frac{k_j - k_i}{t_j - t_i} 
-            + \beta \frac{1}{l_i}\frac{l_j - l_i}{t_j - t_i} 
-            + (1 - \alpha - \beta) \frac{1}{e_i}\frac{e_j - e_i}{t_j - t_i} }
-            {\frac{1}{y_i}\frac{y_j - y_i}{t_j - t_i}} \; .
-\end{equation}
-%
-Cancelling $t_j - t_i$ terms and simplifying gives
-%
-\begin{equation} \label{eq:f_finite_diff_2}
-  f_{i,j} = 1 - \frac{\alpha \left( \frac{k_j}{k_i} - 1 \right) 
-                      + \beta \left( \frac{l_j}{l_i} - 1 \right)
-                      + (1 - \alpha - \beta) \left( \frac{e_j}{e_i} - 1 \right)}
-            {\left( \frac{y_j}{y_i} - 1 \right)} \; ,
-\end{equation}
-%
-which is an estimate of the instantaneous value of $f$ 
-given by Equation~\ref{eq:frac_growth_explained_by_solow}.
 
@@
 <<Models>>=
+flavors <- c("unadjusted", "adjusted")
+nests <- list(kle=c(1,2,3), lek=c(2,3,1), ekl=c(3,1,2))
+model.types <- c("CD", "CES")
+
 fileName <- "ESEE2015Models.Rdata"
@@
   # In RStudio, be sure to set the working directory to the source file directory.
-  flavors <- c("unadjusted", "adjusted")
-  nests <- NULL
-  nests$kle <- c(1,2,3); nests$lek <- c(2,3,1); nests$ekl <- c(3,1,2)
 
@@
 
-flavors <- c("unadjusted", "adjusted")
-# model.types <- c("CD", "CES")
-model.types <- c("CD")
-nests <- list(kle=c(1,2,3), lek=c(2,3,1), ekl=c(3,1,2))
-
 dframes <- list()
@@
       nums <- all.vars(form) [1:(length(all.vars(form))-1)] # y, k, l, and e (if present)
-      trimmedData <- historicalData[[Coun]][c(denom, nums)] # columns are: iYear, y, k, l, and e (if present)
-      df <- historicalData[[Coun]][ , c(nums, "Year")]
+      df <- historicalData[[Coun]][c(denom, nums)] # columns are: iYear, y, k, l, and e (if present)
       # Calculate names for the columns of finite difference derivatives
@@
         # Calculate finite difference derivative columns
-        ediff(trimmedData[[i+1]], pad=pad, lag=lag) / ediff(trimmedData[[1]], pad=pad, lag=lag)
+        ediff(df[[i+1]], pad=pad, lag=lag) / ediff(df[[1]], pad=pad, lag=lag)
       }) %>% do.call(cbind, .) %>% as.data.frame
       names(derivCols) <- derivNames
-      df <- cbind(derivCols, df)
+      df <- cbind(derivCols, historicalData[[Coun]][ , c(nums, "Year")])
       e <- if (length(summands(form))==4) "withE" else "noE"
@@
         } else if (m == "CES"){
+          if (e == "noE"){
+            # kl nesting
+#             df$lambda_fd <- df[[1]] / 
+          } else if (e == "withE"){
+
+          } else {
+            stop (paste("Unknown e:", e))
+          }
 
@@
 It appears that quality-adjusting the factors of production
-decreases the Solow residual~($\lambda$).
+\emph{and} adding augmenting the production function with energy
+decreases the Solow residual~($\lambda$),
+i.e., brings the Solow residual closer to zero.
 
@@
 
-\section{Appendix}
-
-Include data tables here?
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Derivation of dynamic Solow residual for the CD equation}
+\label{sec:dynamic_sr_CD}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Assuming that parameters $\theta$, $\alpha$, and $\beta$
+in Equation~\ref{eq:CDe} are known from parameter estimation,
+we can estimate the value of $\lambda$ as follows.
+First, assume constant returns to scale such that 
+$\alpha + \beta + \gamma = 1$, 
+and calculate $\gamma = 1 - \alpha - \beta$.
+Then, take the natural logarithm ($\ln$) of Equation~\ref{eq:CDe} to obtain
+%
+\begin{equation} \label{eq:lnCD}
+  \ln y = \ln \theta + \ln A + \alpha \ln k + \beta \ln l + (1 - \alpha - \beta) \ln e \;.
+\end{equation}
+%
+By taking the derivative of Equation~\ref{eq:lnCD} with respect to time ($t$) 
+and noting that model parameters $\theta$, $\alpha$, and $\beta$ are 
+constant with respect to time, we obtain
+%
+\begin{equation} \label{eq:ddtlnCD}
+  \frac{1}{y}\frac{\mathrm{d}y}{\mathrm{d}t} 
+      = \frac{1}{A}\frac{\mathrm{d}A}{\mathrm{d}t} 
+      + \alpha \frac{1}{k}\frac{\mathrm{d}k}{\mathrm{d}t} 
+      + \beta \frac{1}{l}\frac{\mathrm{d}l}{\mathrm{d}t} 
+      + (1 - \alpha - \beta) \frac{1}{e}\frac{\mathrm{d}e}{\mathrm{d}t} \;.
+\end{equation}
+%
+Solving for the total factor productivity term gives
+%
+\begin{equation} \label{eq:solow_resid}
+  \frac{1}{A}\frac{\mathrm{d}A}{\mathrm{d}t} 
+      = \frac{1}{y}\frac{\mathrm{d}y}{\mathrm{d}t} 
+      - \left[
+              \alpha \frac{1}{k}\frac{\mathrm{d}k}{\mathrm{d}t} 
+              + \beta \frac{1}{l}\frac{\mathrm{d}l}{\mathrm{d}t} 
+              + (1 - \alpha - \beta) \frac{1}{e}\frac{\mathrm{d}e}{\mathrm{d}t} 
+        \right] \;.
+\end{equation}
+%
+Recognizing that $A \equiv \mathrm{e}^{\lambda (t-t_0)}$ gives
+%
+\begin{equation} \label{eq:lambda_calc}
+  \frac{1}{A}\frac{\mathrm{d}A}{\mathrm{d}t} 
+    = \frac{1}{\mathrm{e}^{\lambda (t-t_0)}} \; \lambda \mathrm{e}^{\lambda (t-t_0)}
+    = \lambda \; ,
+\end{equation}
+%
+which can be substituted into Equation~\ref{eq:solow_resid} to find
+%
+\begin{equation} \label{eq:lambda}
+  \lambda 
+    = \frac{1}{y}\frac{\mathrm{d}y}{\mathrm{d}t} 
+    - \left[
+              \alpha \frac{1}{k}\frac{\mathrm{d}k}{\mathrm{d}t} 
+              + \beta \frac{1}{l}\frac{\mathrm{d}l}{\mathrm{d}t} 
+              + (1 - \alpha - \beta) \frac{1}{e}\frac{\mathrm{d}e}{\mathrm{d}t} 
+      \right] \;.
+\end{equation}
+%
+Equation~\ref{eq:lambda} applies for any instant in time.
+
+If we approximate derivatives in Equation~\ref{eq:lambda} with forward differences
+between times $i$ and $j$, we find
+%
+\begin{equation} \label{eq:lambdaij}
+  \lambda_{i,j}
+    = \frac{1}{y_i}\frac{y_j - y_i}{t_j - t_i} 
+    - \left[
+            \alpha \frac{1}{k_i}\frac{k_j - k_i}{t_j - t_i} 
+            + \beta \frac{1}{l_i}\frac{l_j - l_i}{t_j - t_i} 
+            + (1 - \alpha - \beta) \frac{1}{e_i}\frac{e_j - e_i}{t_j - t_i} 
+      \right] \;,
+\end{equation}
+% 
+where $\lambda_{i,j}$ approximates the true, instantaneous value of $\lambda$
+from Equation~\ref{eq:lambda} between times $i$ and $j$.
+
+Interestingly, 
+%
+\begin{equation}
+  \lambda_{1,n}
+    \neq \sum_{i=2}^{n} \lambda_{i,i-1}  \;.
+\end{equation}
+% 
+Rather,
+%
+\begin{equation} \label{eq:lambda1n}
+  \lambda_{1,n}
+    = \frac{1}{y_1}\frac{y_n - y_1}{t_n - t_1} 
+      - \left[ 
+            \alpha \frac{1}{k_1}\frac{k_n - k_1}{t_n - t_1} 
+            + \beta \frac{1}{l_1}\frac{l_n - l_1}{t_n - t_1} 
+            + (1 - \alpha - \beta) \frac{1}{e_1}\frac{e_n - e_1}{t_n - t_1} 
+      \right] \; ,
+\end{equation}
+% 
+which will become increasingly inaccurate over large time spans,
+because $y_1$, $k_1$, $l_1$, and $e_1$ will be less representative
+of the average value of $y$, $k$, $l$, and $e$ in the time span, respectively.
+This suggests that an averaging approach such as
+%
+\begin{equation}
+  \lambda_{1,n}
+    = \frac{\sum_{i=2}^{n} \lambda_{i,i-1}}{n-1}
+\end{equation}
+%
+is a better approximation of Equation~\ref{eq:lambda1n},
+which is, itself, an approximation of the true value of $\lambda$ 
+given by Equation~\ref{eq:lambda}.
+
+The fraction~($f$) of GDP growth explained by the Solow residual
+for the CD model
+can be given as
+%
+\begin{equation} \label{eq:frac_growth_explained_by_solow}
+  f \equiv \frac{\lambda}{\frac{1}{y}\frac{\mathrm{d}y}{\mathrm{d}t}} 
+            = 1 - \frac{\alpha \frac{1}{k}\frac{\mathrm{d}k}{\mathrm{d}t} 
+                      + \beta \frac{1}{l}\frac{\mathrm{d}l}{\mathrm{d}t} 
+                      + (1 - \alpha - \beta) \frac{1}{e}\frac{\mathrm{d}e}{\mathrm{d}t}}
+                  {\frac{1}{y}\frac{\mathrm{d}y}{\mathrm{d}t}} \; .
+\end{equation}
+%
+Using forward differences to estimate $f$ yields
+%
+\begin{equation} \label{eq:f_finite_diff_1}
+  f_{i,j} = \frac{\lambda_{i,j}}{\frac{1}{y_i}\frac{y_j - y_i}{t_j - t_i}}
+       = 1 - \frac{\alpha \frac{1}{k_i}\frac{k_j - k_i}{t_j - t_i} 
+            + \beta \frac{1}{l_i}\frac{l_j - l_i}{t_j - t_i} 
+            + (1 - \alpha - \beta) \frac{1}{e_i}\frac{e_j - e_i}{t_j - t_i} }
+            {\frac{1}{y_i}\frac{y_j - y_i}{t_j - t_i}} \; .
+\end{equation}
+%
+Cancelling $t_j - t_i$ terms and simplifying gives
+%
+\begin{equation} \label{eq:f_finite_diff_2}
+  f_{i,j} = 1 - \frac{\alpha \left( \frac{k_j}{k_i} - 1 \right) 
+                      + \beta \left( \frac{l_j}{l_i} - 1 \right)
+                      + (1 - \alpha - \beta) \left( \frac{e_j}{e_i} - 1 \right)}
+            {\left( \frac{y_j}{y_i} - 1 \right)} \; ,
+\end{equation}
+%
+which is an estimate of the instantaneous value of $f$ 
+given by Equation~\ref{eq:frac_growth_explained_by_solow}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Derivation of dynamic Solow residual for the CES equation}
+\label{sec:dynamic_sr_CES}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In this section, we derive the dynamic Solow residual ($\lambda$) 
+for the CES equation with three generic factors of production, namely
+$x_1$, $x_2$, and $x_3$.
+
+We can define
+%
+\begin{equation} \label{eq:a_def}
+  a \equiv \delta b^{\rho/\rho_1} + (1-\delta) x_3^{-\rho}
+\end{equation}
+%
+and
+%
+\begin{equation} \label{eq:b_def}
+  b \equiv \delta_1 x_1^{-\rho_1} + (1 - \delta_1) x_2^{-\rho_1} \; ,
+\end{equation}
+%
+such that Equation~\ref{eq:CESgeneric} can be restated as
+%
+\begin{equation} \label{eq:simple_y} 
+  y = \gamma A a^{-1/\rho} \; .
+\end{equation}
+%
+Taking the natural logarithm of Equation~\ref{eq:simple_y}
+and realizing that $\gamma$ is not a function of time, we find
+%
+\begin{equation}
+  \frac{1}{y} \frac{\mathrm{d} y}{\mathrm{d} t} = \frac{1}{A} \frac{\mathrm{d} A}{\mathrm{d} t} 
+                      + \left( - \frac{1}{\rho} \right) \frac{1}{a} \frac{\mathrm{d} a}{\mathrm{d} t} \; .
+\end{equation}
+%
+By Equation~\ref{eq:lambda_calc}, and after rearranging, 
+the dynamic Solow residual for the CES equation can be stated as
+%
+\begin{equation} \label{eq:lambda_for_CES}
+  \lambda = \frac{1}{y} \frac{\mathrm{d} y}{\mathrm{d} t} + \frac{1}{a} \frac{1}{\rho} \frac{\mathrm{d} a}{\mathrm{d} t} \; .
+\end{equation}
+%
+To find $\frac{\mathrm{d} a}{\mathrm{d} t}$ and $\frac{\mathrm{d} b}{\mathrm{d} t}$, 
+we take the time derivatives 
+of Equations~\ref{eq:a_def} and~\ref{eq:b_def}
+and rearrange slightly to obtain
+%
+\begin{equation} \label{eq:da_dt}
+  \frac{1}{\rho} \frac{\mathrm{d} a}{\mathrm{d} t} = \delta b^{(\rho/\rho_1 - 1)} \frac{1}{\rho_1} \frac{\mathrm{d} b}{\mathrm{d} t}
+                                      - (1-\delta) x_3^{-(\rho + 1)} \frac{\mathrm{d} x_3}{\mathrm{d} t}
+\end{equation}
+%
+and
+%
+\begin{equation} \label{eq:db_dt}
+  \frac{1}{\rho_1} \frac{\mathrm{d} b}{\mathrm{d} t} = - \delta_1 x_1^{-(\rho_1 + 1)} \frac{\mathrm{d} x_1}{\mathrm{d} t}
+                                      - (1 - \delta_1) x_2^{-(\rho_1 + 1)} \frac{\mathrm{d} x_2}{\mathrm{d} t} \; .
+\end{equation}
+%
+Equations~\ref{eq:lambda_for_CES}--\ref{eq:db_dt} can be used to 
+calculate a dynamic time series for $\lambda$ given 
+fitted parameters from the CES model
+($\rho, \rho_1, \delta, \, \mathrm{and} \; \delta_1$)
+and time series for economic output~($y$) and
+factors of production 
+($x_1, x_2, \, \mathrm{and} \; x_3$).
+The time derivatives $\left( 
+\frac{\mathrm{d} y}{\mathrm{d} t}, 
+\frac{\mathrm{d} x_1}{\mathrm{d} t},
+\frac{\mathrm{d} x_2}{\mathrm{d} t}, \, \mathrm{and} \;
+\frac{\mathrm{d} x_3}{\mathrm{d} t} \right)$
+can be approximated from historical data
+by forward finite differences in a manner similar to Equation~\ref{eq:lambdaij}.
 

### 2015-05-27 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw

@@
 nests <- list(kle=c(1,2,3), lek=c(2,3,1), ekl=c(3,1,2))
-model.types <- c("CD", "CES")
+model.types <- c("CD")
+# model.types <- c("CD", "CES")
 
@@
   id_list <- strsplit(id, split = "[.]")[[1]]
-  if (id_list[[2]] == "unadjusted"){
-    df$flavor <- "Unadjusted"
-  } else if (id_list[[2]] == "adjusted"){
-    df$flavor <- "Quality-adjusted"
-  } else {
-    stop("Unknown adjustment.")
-  }
-  if (id_list[[3]] == "noE"){
-    df$energy <- "Without energy"
-  } else if (id_list[[3]] == "withE"){
-    df$energy <- "With energy"
-  } else {
-    stop("Unknown energy.")
-  }
+  df$flavor <- if (id_list[[2]] == "unadjusted") "Unadjusted" else "Quality-adjusted"
+  df$energy <- if (id_list[[3]] == "noE") "Without energy" else "With energy"
   df$model <- id_list[[4]]
@@
 
+# Get the unadjusted, without-energy residuals and store them in a data frame
+r_unadj_noE <- filter(fitted_and_resid_data, flavor=="Unadjusted" & energy=="Without energy") %>% 
+               select(Year, Country, Residuals, model)
+colnames(r_unadj_noE)[colnames(r_unadj_noE)=="Residuals"] <- "r_unadj_noE"
+# Merge to get the unadjusted, without-energy values next to each country, year, and model
+fitted_and_resid_data <- merge(fitted_and_resid_data, r_unadj_noE)
+# Create a column containing ∆r, the difference between a residual value
+# and the residual value in the same year for the unadjusted, no-energy case
+fitted_and_resid_data[["Dr"]] <- abs(fitted_and_resid_data[["Residuals"]]) - abs(fitted_and_resid_data[["r_unadj_noE"]])
+
 # Relevel factors before plotting
@@
 fitted_and_resid_data$flavor <- relevelFactor(as.factor(fitted_and_resid_data$flavor), c("Unadjusted", "Quality-adjusted"))
-fitted_and_resid_data$energy <- relevelFactor(as.factor(fitted_and_resid_data$energy), c("Without energy", "With Energy"))
+fitted_and_resid_data$energy <- relevelFactor(as.factor(fitted_and_resid_data$energy), c("Without energy", "With energy"))
 @
@@
 
-<<Fitted and Residual Graphs>>=
+<<Fitted and Residual Graph Functions>>=
 fittedGraph <- function(data){
@@
 # Calculate finite difference approximations of time derivatives for output and all factors of production
-lag <- 3       # Desired lag for calculations. Set to n for differences across n years.
+lag <- 1       # Desired lag for calculations. Set to n for differences across n years.
 pad <- "tail"  # Desired padding for NA values
@@
       e <- if (length(summands(form))==4) "withE" else "noE"
+      df$flavor <- if (flav == "unadjusted") "Unadjusted" else "Quality-adjusted"
+      df$energy <- if (e == "noE") "Without energy" else "With energy"
+      # Add a column for 1/y * dy/dt
+#       growth.col.name <- paste0("1/", nums[[1]], "*", derivNames[[1]])
+      df[["dydtOvery"]] <- 1 / df[[nums[[1]]]] * df[[derivNames[[1]]]]
       for (m in model.types){
@@
         if (m == "CD"){
-          lambda <- lapply(1:length(derivNames), function(i){
+          lambda_fd <- lapply(1:length(derivNames), function(i){
             # derivative term divided by its numerator.
@@
           }) %>% as.data.frame %>% rowSums
-          df$lambda_fd <- lambda
+          df$lambda_fd <- lambda_fd
           avg.lambda_fd <- mean(df$lambda_fd, na.rm = TRUE)
@@
         } else if (m == "CES"){
+          df <- data.frame()
           if (e == "noE"){
@@
         }
-        df$flavor <- if (flav == "adjusted") "Quality-adjusted" else "Unadjusted"
-        df$flavor <- relevelFactor(as.factor(df$flavor), c("Unadjusted", "Quality-adjusted"))
-        df$energy <- if (e == "noE") "Without energy" else "With energy"
-        df$energy <- relevelFactor(as.factor(df$energy), c("Without energy", "With energy"))
+        # Add to the list of data frames
         dframes[[length(dframes)+1]] <- df
@@
 solowResiduals <- do.call(plyr::rbind.fill, dframes)
+
+# Grab the unadjusted, no-energy Solow residuals and create a column in solowResiduals with them. 
+# Using the hint at 
+# http://stackoverflow.com/questions/15059076/
+# r-how-to-call-apply-like-function-on-each-row-of-dataframe-with-multiple-argum
+sr_unadj_noE_col <- apply(solowResiduals[ , c("Country", "model", "energy", "Year", "flavor")], 1, function(x){
+    row <- as.data.frame(filter(solowResiduals, 
+                                Country==x["Country"], model==x["model"], energy=="Without energy",
+                                Year==x["Year"], flavor=="Unadjusted"))
+    return(row[["lambda_fd"]])
+  })
+solowResiduals[["sr_unadj_noE"]] <- do.call(rbind, as.list(sr_unadj_noE_col))
+# Create a column containing ∆lambda_df, the difference between a lambda_df value
+# and the lambda_df value in the same year for the unadjusted, no-energy case
+solowResiduals[["Dlambda_fd"]] <- abs(solowResiduals[["lambda_fd"]]) - abs(solowResiduals[["sr_unadj_noE"]])
+
+# Adjust levels before creating graphs.
+solowResiduals$flavor <- relevelFactor(as.factor(solowResiduals$flavor), c("Unadjusted", "Quality-adjusted"))
+solowResiduals$energy <- relevelFactor(as.factor(solowResiduals$energy), c("Without energy", "With energy"))
 @
@@
 
-<<DynamicSR_CD_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residuals for the Cobb-Douglas model.">>=
+<<DynamicSR_CD_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residuals for the Cobb-Douglas model.
+Dashed lines are $\\lambda$ values.
+Solid lines are $\\frac{1}{y}\\frac{\\mathrm{d} y}{\\mathrm{d} t}$.">>=
 data <- filter(solowResiduals, model=="CD")
 ggplot(data=data) +
+  geom_line(data=filter(data, energy=="Without energy"), mapping=aes(x=Year, y=dydtOvery)) +
   geom_line(mapping=aes(x=Year, y=lambda_fd, linetype=energy)) +
@@
   xy_theme()
+@
+
+%++++++++++++++++++++++++++++++
+\subsection{How does quality-adjusting and including energy affect the dynamic Solow residual?} 
+\label{sec:trajectory_graphs}
+%++++++++++++++++++++++++++++++
+
+<<SR and R trajectory graph functions>>=
+residualsGraph <- function(data){
+  plot <- ggplot(data=data) + 
+    geom_point(mapping=aes(x=Dr, y=Dlambda_fd)) + 
+    xlab(expression(Delta*r)) +
+    ylab(expression(Delta*lambda)) +
+    xy_theme()
+  return(plot)
+}
+traj.data <- merge(solowResiduals[c("Country", "Year", "model", "flavor", "energy", "nest", "Dlambda_fd")], 
+                   fitted_and_resid_data[c("Country", "Year", "model", "flavor", "energy", "nest", "Dr")])
+traj.data.means <- traj.data %>% 
+  group_by(model, Country, flavor, energy, nest) %>%
+  summarise(Dlambda_fd.mean = mean(Dlambda_fd, na.rm=TRUE), Dr.mean = mean(Dr))
+@
+
+We can test our hypothesis that quality-adjusting the factors of production
+and including energy will reduce the Solow residual ($\lambda$)
+and the fitting residuals ($r$) by plotting
+$\Delta\lambda$ vs. $\Delta r$, where
+%
+\begin{equation} \label{eq:delta_lambda}
+  \Delta \lambda \equiv \lambda - \lambda_{Unadjusted, \, Without \, energy}
+\end{equation}
+%
+and
+%
+\begin{equation} \label{eq:delta_r}
+  \Delta r \equiv r - r_{Unadjusted, \, Without \, energy}.
+\end{equation}
+%
+
+<<Solow_residual_trajectories, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residual trajectories for the Cobb-Douglas model.">>=
+residualsGraph(subset(traj.data, model=="CD" & Country=="UK" & energy=="With energy" & flavor=="Unadjusted"))
 @

### 2015-05-27 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Now putting all CD data on one graph for resids.

@@
 <<Fitted_and_Residuals>>=
-fitted_and_resid_data <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), f = function(mod, id){
+temp_data <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), f = function(mod, id){
   df <- select(mod$data, Year, iGDP, Country)
@@
 # Get the unadjusted, without-energy residuals and store them in a data frame
-r_unadj_noE <- filter(fitted_and_resid_data, flavor=="Unadjusted" & energy=="Without energy") %>% 
+r_unadj_noE <- filter(temp_data, flavor=="Unadjusted" & energy=="Without energy") %>% 
                select(Year, Country, Residuals, model)
@@
 # Merge to get the unadjusted, without-energy values next to each country, year, and model
-fitted_and_resid_data <- merge(fitted_and_resid_data, r_unadj_noE)
+fitted_and_resid_data <- merge(temp_data, r_unadj_noE)
 # Create a column containing ∆r, the difference between a residual value
@@
 fitted_and_resid_data$energy <- relevelFactor(as.factor(fitted_and_resid_data$energy), c("Without energy", "With energy"))
+fitted_and_resid_data$nest <- relevelFactor(as.factor(fitted_and_resid_data$nest), c("kl", "kle", "lek", "ekl"))
+
+# Make data viewing easier
+fitted_and_resid_data <- arrange(fitted_and_resid_data, Country, model, flavor, energy, nest)
 @
@@
 }
-solowResiduals <- do.call(plyr::rbind.fill, dframes)
-
-# Grab the unadjusted, no-energy Solow residuals and create a column in solowResiduals with them. 
-# Using the hint at 
-# http://stackoverflow.com/questions/15059076/
-# r-how-to-call-apply-like-function-on-each-row-of-dataframe-with-multiple-argum
-sr_unadj_noE_col <- apply(solowResiduals[ , c("Country", "model", "energy", "Year", "flavor")], 1, function(x){
-    row <- as.data.frame(filter(solowResiduals, 
-                                Country==x["Country"], model==x["model"], energy=="Without energy",
-                                Year==x["Year"], flavor=="Unadjusted"))
-    return(row[["lambda_fd"]])
-  })
-solowResiduals[["sr_unadj_noE"]] <- do.call(rbind, as.list(sr_unadj_noE_col))
+temp_data <- do.call(plyr::rbind.fill, dframes)
+
+# Get the unadjusted, without-energy Solow residuals and store them in a data frame
+sr_unadj_noE <- filter(temp_data, flavor=="Unadjusted" & energy=="Without energy") %>% 
+                select(Year, Country, lambda_fd, model)
+colnames(sr_unadj_noE)[colnames(sr_unadj_noE)=="lambda_fd"] <- "sr_unadj_noE"
+# Merge to get the unadjusted, without-energy values next to each country, year, and model
+solowResiduals <- merge(temp_data, sr_unadj_noE)
+
 # Create a column containing ∆lambda_df, the difference between a lambda_df value
@@
 
-# Adjust levels before creating graphs.
+# Relevel factors before plotting
+solowResiduals$Country <- relevelFactor(as.factor(solowResiduals$Country), c("PT", "UK"))
 solowResiduals$flavor <- relevelFactor(as.factor(solowResiduals$flavor), c("Unadjusted", "Quality-adjusted"))
 solowResiduals$energy <- relevelFactor(as.factor(solowResiduals$energy), c("Without energy", "With energy"))
+solowResiduals$nest <- relevelFactor(as.factor(solowResiduals$nest), c("kl", "kle", "lek", "ekl"))
+
+# Make data viewing easier
+solowResiduals <- arrange(solowResiduals, Country, model, flavor, energy, nest)
 @
@@
 
-<<SR and R trajectory graph functions>>=
-residualsGraph <- function(data){
+<<SR and R trajectory data>>=
+traj.data <- merge(solowResiduals[c("Country", "Year", "model", "flavor", "energy", "nest", "Dlambda_fd")], 
+                   fitted_and_resid_data[c("Country", "Year", "model", "flavor", "energy", "nest", "Dr")]) %>%
+                   arrange(Country, model, flavor, energy, nest)
+traj.data.means <- traj.data %>% 
+  group_by(model, Country, flavor, energy, nest) %>%
+  summarise(Dlambda_fd.mean = mean(Dlambda_fd, na.rm=TRUE), Dr.mean = mean(Dr))
+@
+
+<<SR and R trajectory plot function>>=
+residualsTrajGraph <- function(data){
   plot <- ggplot(data=data) + 
-    geom_point(mapping=aes(x=Dr, y=Dlambda_fd)) + 
+    geom_point(mapping=aes(x=Dr, y=Dlambda_fd, color=energy)) + 
+    facet_grid(Country ~ flavor) +
     xlab(expression(Delta*r)) +
@@
 }
-traj.data <- merge(solowResiduals[c("Country", "Year", "model", "flavor", "energy", "nest", "Dlambda_fd")], 
-                   fitted_and_resid_data[c("Country", "Year", "model", "flavor", "energy", "nest", "Dr")])
-traj.data.means <- traj.data %>% 
-  group_by(model, Country, flavor, energy, nest) %>%
-  summarise(Dlambda_fd.mean = mean(Dlambda_fd, na.rm=TRUE), Dr.mean = mean(Dr))
 @
@@
 <<Solow_residual_trajectories, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residual trajectories for the Cobb-Douglas model.">>=
-residualsGraph(subset(traj.data, model=="CD" & Country=="UK" & energy=="With energy" & flavor=="Unadjusted"))
+residualsTrajGraph(filter(traj.data, model=="CD"))
 @

### 2015-05-27 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw

@@
     geom_point(mapping=aes(x=Dr, y=Dlambda_fd, color=energy)) + 
+#     geom_path(mapping=aes(x=Dr, y=Dlambda_fd, color=energy)) + 
     facet_grid(Country ~ flavor) +
@@
     ylab(expression(Delta*lambda)) +
-    xy_theme()
+    xy_theme() + 
+    theme(legend.title=element_blank())
   return(plot)
@@
 We can test our hypothesis that quality-adjusting the factors of production
-and including energy will reduce the Solow residual ($\lambda$)
-and the fitting residuals ($r$) by plotting
-$\Delta\lambda$ vs. $\Delta r$, where
+and including energy will reduce the Solow residuals~($\lambda$)
+and the fitting residuals~($r$) by plotting
+$\Delta \lambda_i$ vs. $\Delta r_i$, where
 %
 \begin{equation} \label{eq:delta_lambda}
-  \Delta \lambda \equiv \lambda - \lambda_{Unadjusted, \, Without \, energy}
+  \Delta \lambda_i \equiv \left| \lambda_i \right| - \left| \lambda_{i, \, Unadjusted, \, Without \, energy} \right|
 \end{equation}
@@
 \begin{equation} \label{eq:delta_r}
-  \Delta r \equiv r - r_{Unadjusted, \, Without \, energy}.
-\end{equation}
-%
-
-<<Solow_residual_trajectories, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residual trajectories for the Cobb-Douglas model.">>=
+  \Delta r_i \equiv \left| r_i \right| - \left| r_{i, \,Unadjusted, \, Without \, energy} \right|.
+\end{equation}
+%
+If most of the points fall in the lower-left quadrant of a graph, 
+we can conclude that both Solow residual~($\lambda$) and
+fitting residual~($r$) have decreased due to either 
+quality-adjustment of the factors of production or 
+including energy.
+
+Figure~\ref{fig:Solow_residual_trajectories_CD} indicates that
+for the Cobb-Douglas model, 
+neither 
+quality-adjusting the factors of production
+nor including energy 
+consistently reduces
+the Solow residual or the fitting residual.
+
+<<Solow_residual_trajectories_CD, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residual and fitting residual trajectories relative to the Unadjusted, Without-energy condition for the Cobb-Douglas model.">>=
 residualsTrajGraph(filter(traj.data, model=="CD"))
 @
+
+We can also calculate the average values for $\Delta \lambda$ and $\Delta r$ 
+as shown in Table~\ref{tab:traj.means.CD}.
+%
+<<Trajectory_Means_CD, results="asis">>=
+xtable::xtable(filter(traj.data.means, model=="CD") %>% select(-nest),
+               caption="Average $\\Delta\\lambda$ and $\\lambda r$ for Cobb-Douglas models.",
+               label="tab:traj.means.CD", 
+               digits=6) %>% 
+  print(., 
+        caption.placement="top", 
+        size="\\tiny", 
+        include.rownames=FALSE, 
+        math.style.negative=TRUE)
+@
+%
+These results for the Cobb-Douglas model indicate that 
+we should perform the same analysis for the CES model.
 

### 2015-05-29 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Calculating dyn lambda for CES.

@@
 countries <- names(formulas)
+flavors <- names(formulas$PT)
 @
@@
 <<Models>>=
-flavors <- c("unadjusted", "adjusted")
-nests <- list(kle=c(1,2,3), lek=c(2,3,1), ekl=c(3,1,2))
-model.types <- c("CD")
-# model.types <- c("CD", "CES")
-
 fileName <- "ESEE2015Models.Rdata"
@@
 
-dframes <- list()
+dframes <- list() # Fill with data frames for each combination of country, flavor, energy, model, and nest
 for (Coun in countries){
   for (flav in flavors){
+
     forms <- list(noE = keep_summands(formulas[[Coun]][[flav]], -3), withE = formulas[[Coun]][[flav]])
@@
       # Add a column for 1/y * dy/dt
-#       growth.col.name <- paste0("1/", nums[[1]], "*", derivNames[[1]])
       df[["dydtOvery"]] <- 1 / df[[nums[[1]]]] * df[[derivNames[[1]]]]
+
+#       model.types <- c(CD="CD")
+      model.types <- c(CD="CD", CES="CES")
       for (m in model.types){
+        if (m == "CD"){
           origCoeffs <- filter(AllCoeffs, model==m & energy==e & Country==Coun & flavor==flav)
-        df <- cbind(df, origCoeffs)
-        if (m == "CD"){
-          lambda_fd <- lapply(1:length(derivNames), function(i){
-            # derivative term divided by its numerator.
-            # derivative term is in the ith column of df
-            # numerator is in i + length(derivNames) th column of df
-            out <- df[[i]] / df[[i+length(derivNames)]]
-            if (i > 1){
-              # Need to make it negative and multiply by the corresponding alpha term.
-              # Typical setup is that columns 2 is capital, and we need alpha_1 for capital.
-              # So, subtract 1 from i.
-              out <- - out * df[[paste0("alpha_", i-1)]]
+          df.CD <- cbind(df, origCoeffs)
+          df.CD$nest <- NA
+          lambda_fd <- 
+            df.CD[["dydtOvery"]] - 
+            df.CD[["alpha_1"]] / df.CD[[nums[[2]]]] * df.CD[[derivNames[[2]]]] - 
+            df.CD[["alpha_2"]] / df.CD[[nums[[3]]]] * df.CD[[derivNames[[3]]]]
+          if (e == "withE"){
+            # Subtract the energy term also
+            lambda_fd <- lambda_fd - 
+              df.CD[["alpha_3"]] / df.CD[[nums[[4]]]] * df.CD[[derivNames[[4]]]]
           }
-            return(out)
-          }) %>% as.data.frame %>% rowSums
-          df$lambda_fd <- lambda_fd
-          avg.lambda_fd <- mean(df$lambda_fd, na.rm = TRUE)
           # Fraction of growth explained by Solow Residual
-          df$solowFrac <- df$lambda_fd / (df[[1]] / df[[length(derivNames) + 1]])
-          avg.solowFrac <- mean(df$solowFrac, na.rm = TRUE)
+          solowFrac <- lambda_fd / df.CD[["dydtOvery"]]
+          # Add to data frame
+          df.CD$lambda_fd <- lambda_fd
+          df.CD$solowFrac <- solowFrac
+          # Add to the list of data frames
+          dframes[[length(dframes)+1]] <- df.CD
         } else if (m == "CES"){
-          df <- data.frame()
           if (e == "noE"){
-            # kl nesting
-#             df$lambda_fd <- df[[1]] / 
+            origCoeffs <- filter(AllCoeffs, model==m & energy==e & Country==Coun & flavor==flav)
+            df.kl <- cbind(df, select(origCoeffs, -nest, -flavor, -energy))
+            df.kl$nest <- "kl"
+            n <- c(1,2)
+            # Get the values for x1 and x2
+            df.kl$x1 <- df.kl[[ nums[ unlist(n)[1]+1 ] ]] # GDP is first column, add 1 to get to the factors of production
+            df.kl$x2 <- df.kl[[ nums[ unlist(n)[2]+1 ] ]]
+            df.kl$dx1dt <- df.kl[[ derivNames[ unlist(n)[1]+1 ] ]]
+            df.kl$dx2dt <- df.kl[[ derivNames[ unlist(n)[2]+1 ] ]]
+            # Calculate derivative terms
+            df.kl <- df.kl %>% 
+              transform(b = delta_1 * x1^(-rho_1) + (1 - delta_1) * x2^(-rho_1)) %>%
+              transform(dbdtOverrho1 = -delta_1 * x1^(-(rho_1+1))*dx1dt - (1 - delta_1) * x2^(-(rho_1+1))*dx2dt) %>%
+              transform(lambda_fd = dydtOvery + 1/b * dbdtOverrho1) %>%
+              transform(solowFrac = lambda_fd / dydtOvery)
+            # Add to the list of data frames
+            dframes[[length(dframes)+1]] <- df.kl
           } else if (e == "withE"){
-
+            nests <- list(kle=c(1,2,3), lek=c(2,3,1), ekl=c(3,1,2))
+            for (i in 1:3){
+              n <- nests[i] # preserves name
+              origCoeffs <- filter(AllCoeffs, model==m & energy==e & Country==Coun & flavor==flav & nest==names(n)[[1]])
+              df.CESe <- cbind(df, select(origCoeffs, -nest, -flavor, -energy))
+              df.CESe$nest <- names(n)[[1]]
+              # Unpack names so that the formulae below are readable.
+              df.CESe$x1 <- df.CESe[[ nums[ unlist(n)[1]+1 ] ]] # GDP is 1st column, add 1 to get factors of production
+              df.CESe$x2 <- df.CESe[[ nums[ unlist(n)[2]+1 ] ]]
+              df.CESe$x3 <- df.CESe[[ nums[ unlist(n)[3]+1 ] ]]
+              df.CESe$dx1dt <- df.CESe[[ derivNames[ unlist(n)[1]+1 ] ]]
+              df.CESe$dx2dt <- df.CESe[[ derivNames[ unlist(n)[2]+1 ] ]]
+              df.CESe$dx3dt <- df.CESe[[ derivNames[ unlist(n)[3]+1 ] ]]
+              # Calculate derivative terms
+              df.CESe <- df.CESe %>% 
+                transform(b = delta_1 * x1^(-rho_1) + (1 - delta_1) * x2^(-rho_1)) %>%
+                transform(a = delta * b^(rho/rho_1) + (1 - delta) * x3^(-rho)) %>%
+                transform(dbdtOverrho1 = -delta_1 * x1^(-(rho_1+1))*dx1dt - (1 - delta_1) * x2^(-(rho_1+1))*dx2dt) %>%
+                transform(dadtOverrho = delta * b^(rho/rho_1 - 1) * dbdtOverrho1 - (1 - delta) * x3^(-(rho+1))*dx3dt) %>%
+                transform(lambda_fd = dydtOvery + 1/a * dadtOverrho) %>%
+                transform(solowFrac = lambda_fd / dydtOvery)
+              # Add to the list of data frames
+              dframes[[length(dframes)+1]] <- df.CESe
+            }
           } else {
@@
           }
-
         } else {
@@
         }
-        # Add to the list of data frames
-        dframes[[length(dframes)+1]] <- df
       }

### 2015-05-29 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Creating graphs for delta lambda vs. delta r.

@@
 
-<<DynamicSR_CD_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residuals for the Cobb-Douglas model.
-Dashed lines are $\\lambda$ values.
-Solid lines are $\\frac{1}{y}\\frac{\\mathrm{d} y}{\\mathrm{d} t}$.">>=
-data <- filter(solowResiduals, model=="CD")
+<<DynamicSR_Graph>>=
+dynamicSRGraph <- function(data){
 ggplot(data=data) +
@@
   xy_theme()  
+}
+@
+
+<<DynamicSR_CD_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residuals for the Cobb-Douglas model.
+Dashed lines are $\\lambda$ values.
+Solid lines are $\\frac{1}{y}\\frac{\\mathrm{d} y}{\\mathrm{d} t}$.">>=
+dynamicSRGraph(filter(solowResiduals, model=="CD"))
+@
+
+<<DynamicSR_CESkle_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residuals for the CES model with ($kl$)$e$ nesting.
+Dashed lines are $\\lambda$ values.
+Solid lines are $\\frac{1}{y}\\frac{\\mathrm{d} y}{\\mathrm{d} t}$.">>=
+dynamicSRGraph(filter(solowResiduals, model=="CES" & (nest=="kle" | nest=="kl")))
+@
+
+<<DynamicSR_CESlek_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residuals for the CES model with ($le$)$k$ nesting.
+Dashed lines are $\\lambda$ values.
+Solid lines are $\\frac{1}{y}\\frac{\\mathrm{d} y}{\\mathrm{d} t}$.">>=
+dynamicSRGraph(filter(solowResiduals, model=="CES" & (nest=="lek" | nest=="kl")))
+@
+
+<<DynamicSR_CESekl_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residuals for the CES model with ($ek$)$l$ nesting.
+Dashed lines are $\\lambda$ values.
+Solid lines are $\\frac{1}{y}\\frac{\\mathrm{d} y}{\\mathrm{d} t}$.">>=
+dynamicSRGraph(filter(solowResiduals, model=="CES" & (nest=="ekl" | nest=="kl")))
 @
@@
 we should perform the same analysis for the CES model.
+
+<<Solow_residual_trajectories_CESkle, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residual and fitting residual trajectories relative to the Unadjusted, Without-energy condition for the CES model with ($kl$)$e$ nesting.">>=
+residualsTrajGraph(filter(traj.data, model=="CES" & (nest=="kl" | nest=="kle")))
+@
+
+<<Solow_residual_trajectories_CESlek, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residual and fitting residual trajectories relative to the Unadjusted, Without-energy condition for the CES model with ($le$)$k$ nesting.">>=
+residualsTrajGraph(filter(traj.data, model=="CES" & (nest=="kl" | nest=="lek")))
+@
+
+<<Solow_residual_trajectories_CESekl, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residual and fitting residual trajectories relative to the Unadjusted, Without-energy condition for the CES model with ($ek$)$l$ nesting.">>=
+residualsTrajGraph(filter(traj.data, model=="CES" & (nest=="kl" | nest=="ekl")))
+@
 

### 2015-06-01 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Now using the model to extract fitted_and_resid_data. This streamlines the code quite a bit.

@@
 <<Fitted_and_Residuals>>=
-temp_data <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), f = function(mod, id){
-  df <- select(mod$data, Year, iGDP, Country)
+fittedAndResidData <- function(model){
+  df <- data.frame(select(model$data, Year))
   # Trim fitted to be same length as df to eliminate problems with possible NAs at end of fitted
-  df$fitted <- yhat(mod)[c(1:length(df$Year))]
-  df$Residuals <- resid(mod)[c(1:length(df$Year))]
-  # Parse the id to find out whether this is quality-adjusted data
+  df$fitted <- yhat(model)[c(1:length(df$Year))]
+  df$Residuals <- resid(model)[c(1:length(df$Year))]
+  return(df)  
+}
+
+temp_data <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, id){
+  df <- fittedAndResidData(model)
+  f <- model$formula
+  response <- summands(f, right = FALSE)
+  df[[response]] <- model$data[[response]] # Add iGDP to the data frame
   id_list <- strsplit(id, split = "[.]")[[1]]
+  df$Country <- id_list[[1]]
   df$flavor <- if (id_list[[2]] == "unadjusted") "Unadjusted" else "Quality-adjusted"
@@
 %
-<<Trajectory_Means_CD, results="asis">>=
-xtable::xtable(filter(traj.data.means, model=="CD") %>% select(-nest),
-               caption="Average $\\Delta\\lambda$ and $\\lambda r$ for Cobb-Douglas models.",
-               label="tab:traj.means.CD", 
-               digits=6) %>% 
-  print(., 
+<<TrajMeansTableFunction>>=
+trajMeansTable <- function(data, caption, label){
+  table <- xtable::xtable(data, caption=caption, label=label, digits=6)
+  print(table, 
         caption.placement="top", 
@@
         math.style.negative=TRUE)
+}
+@
+
+<<Trajectory_Means_CD, results="asis">>=
+trajMeansTable(data = filter(traj.data.means, model=="CD") %>% select(-nest), 
+               caption = "Average $\\Delta\\lambda$ and $\\Delta r$ for Cobb-Douglas models.",
+               label="tab:traj.means.CD")
+# xtable::xtable(filter(traj.data.means, model=="CD") %>% select(-nest),
+#                caption="Average $\\Delta\\lambda$ and $\\Delta r$ for Cobb-Douglas models.",
+#                label="tab:traj.means.CD", 
+#                digits=6) %>% 
+#   print(., 
+#         caption.placement="top", 
+#         size="\\tiny", 
+#         include.rownames=FALSE, 
+#         math.style.negative=TRUE)
 @

### 2015-06-01 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Refactored dynamic solow residual code. Now using models more effectively.

@@
 # Calculate finite difference approximations of time derivatives for output and all factors of production
-lag <- 1       # Desired lag for calculations. Set to n for differences across n years.
-pad <- "tail"  # Desired padding for NA values
-
-dframes <- list() # Fill with data frames for each combination of country, flavor, energy, model, and nest
-for (Coun in countries){
-  for (flav in flavors){
-
-    forms <- list(noE = keep_summands(formulas[[Coun]][[flav]], -3), withE = formulas[[Coun]][[flav]])
-    for (form in forms){
-      denom <- summands(form, n=length(summands(form))) # time variable
-      nums <- all.vars(form) [1:(length(all.vars(form))-1)] # y, k, l, and e (if present)
-      df <- historicalData[[Coun]][c(denom, nums)] # columns are: iYear, y, k, l, and e (if present)
+dynamicSR <- function(model, id, lag=1, pad="tail"){
+  id_list <- strsplit(id, split = "[.]")[[1]]
+  energy <- id_list[[3]]
+  modelStr <- id_list[[4]]
+
+  f <- model$formula
+  denom <- summands(f, n=length(summands(f))) # time variable
+  nums <- all.vars(f) [1:(length(all.vars(f))-1)] # y, k, l, and e (if present)
+  df <- model$data[c(denom, nums)] # columns are: iYear, y, k, l, and e (if present)
+
   # Calculate names for the columns of finite difference derivatives
-      derivNames <- lapply(1:length(nums), function(i){paste0("d", nums[[i]], "/", "dt")}) %>% unlist
+  derivNames <- lapply(1:length(nums), function(i){paste0("d", nums[[i]], ".d", denom)}) %>% unlist
   derivCols <- lapply(1:length(nums), function(i){
@@
   names(derivCols) <- derivNames  
-      df <- cbind(derivCols, historicalData[[Coun]][ , c(nums, "Year")])
-      e <- if (length(summands(form))==4) "withE" else "noE"
-      df$flavor <- if (flav == "unadjusted") "Unadjusted" else "Quality-adjusted"
-      df$energy <- if (e == "noE") "Without energy" else "With energy"
-      # Add a column for 1/y * dy/dt
-      df[["dydtOvery"]] <- 1 / df[[nums[[1]]]] * df[[derivNames[[1]]]]
-
-#       model.types <- c(CD="CD")
-      model.types <- c(CD="CD", CES="CES")
-      for (m in model.types){
-        if (m == "CD"){
-          origCoeffs <- filter(AllCoeffs, model==m & energy==e & Country==Coun & flavor==flav)
-          df.CD <- cbind(df, origCoeffs)
-          df.CD$nest <- NA
+  df <- cbind(derivCols, df[ , c(nums, denom)]) # puts derivatives first, then raw numbers, then time
+  df[["dydtOvery"]] <- 1 / df[[ nums[[1]] ]] * df[[ derivNames[[1]] ]]
+  coeffs <- naturalCoef(model)
+  df <- cbind(df, coeffs)
+
+  if (modelStr == "CD"){
     lambda_fd <- 
-            df.CD[["dydtOvery"]] - 
-            df.CD[["alpha_1"]] / df.CD[[nums[[2]]]] * df.CD[[derivNames[[2]]]] - 
-            df.CD[["alpha_2"]] / df.CD[[nums[[3]]]] * df.CD[[derivNames[[3]]]]
-          if (e == "withE"){
+      df[["dydtOvery"]] - 
+      df[["alpha_1"]] / df[[nums[[2]]]] * df[[derivNames[[2]]]] - 
+      df[["alpha_2"]] / df[[nums[[3]]]] * df[[derivNames[[3]]]]
+    if (energy == "withE"){
       # Subtract the energy term also
       lambda_fd <- lambda_fd - 
-              df.CD[["alpha_3"]] / df.CD[[nums[[4]]]] * df.CD[[derivNames[[4]]]]
+        df[["alpha_3"]] / df[[nums[[4]]]] * df[[derivNames[[4]]]]
     }
     # Fraction of growth explained by Solow Residual
-          solowFrac <- lambda_fd / df.CD[["dydtOvery"]]
+    solowFrac <- lambda_fd / df[["dydtOvery"]]
     # Add to data frame
-          df.CD$lambda_fd <- lambda_fd
-          df.CD$solowFrac <- solowFrac
-          # Add to the list of data frames
-          dframes[[length(dframes)+1]] <- df.CD
-        } else if (m == "CES"){
-          if (e == "noE"){
-            origCoeffs <- filter(AllCoeffs, model==m & energy==e & Country==Coun & flavor==flav)
-            df.kl <- cbind(df, select(origCoeffs, -nest, -flavor, -energy))
-            df.kl$nest <- "kl"
-            n <- c(1,2)
-            # Get the values for x1 and x2
-            df.kl$x1 <- df.kl[[ nums[ unlist(n)[1]+1 ] ]] # GDP is first column, add 1 to get to the factors of production
-            df.kl$x2 <- df.kl[[ nums[ unlist(n)[2]+1 ] ]]
-            df.kl$dx1dt <- df.kl[[ derivNames[ unlist(n)[1]+1 ] ]]
-            df.kl$dx2dt <- df.kl[[ derivNames[ unlist(n)[2]+1 ] ]]
-            # Calculate derivative terms
-            df.kl <- df.kl %>% 
+    df$lambda_fd <- lambda_fd
+    df$solowFrac <- solowFrac
+    return(df)
+  } else if (modelStr == "CES"){
+    # Assign nice variable names so that the equations below are easier to read (and debug, and maintain)
+    # This code is nest-aware.
+    n <- model$nest
+    for (i in 1:length(model$nest)){
+      df[[paste0("x", i)]] <- df[[ nums[ model$nest[i]+1 ] ]] # GDP is 1st col, add 1 to get to the factors of production
+      df[[paste0("dx", i, "dt")]] <- df[[ derivNames[ model$nest[i]+1 ] ]]
+    }
+    if (energy == "noE"){
+      # Calculate terms for the finite-difference Solow residual (lambda_fd)
+      df <- df %>% 
         transform(b = delta_1 * x1^(-rho_1) + (1 - delta_1) * x2^(-rho_1)) %>%
@@
         transform(solowFrac = lambda_fd / dydtOvery)
-            # Add to the list of data frames
-            dframes[[length(dframes)+1]] <- df.kl
-          } else if (e == "withE"){
-            nests <- list(kle=c(1,2,3), lek=c(2,3,1), ekl=c(3,1,2))
-            for (i in 1:3){
-              n <- nests[i] # preserves name
-              origCoeffs <- filter(AllCoeffs, model==m & energy==e & Country==Coun & flavor==flav & nest==names(n)[[1]])
-              df.CESe <- cbind(df, select(origCoeffs, -nest, -flavor, -energy))
-              df.CESe$nest <- names(n)[[1]]
-              # Unpack names so that the formulae below are readable.
-              df.CESe$x1 <- df.CESe[[ nums[ unlist(n)[1]+1 ] ]] # GDP is 1st column, add 1 to get factors of production
-              df.CESe$x2 <- df.CESe[[ nums[ unlist(n)[2]+1 ] ]]
-              df.CESe$x3 <- df.CESe[[ nums[ unlist(n)[3]+1 ] ]]
-              df.CESe$dx1dt <- df.CESe[[ derivNames[ unlist(n)[1]+1 ] ]]
-              df.CESe$dx2dt <- df.CESe[[ derivNames[ unlist(n)[2]+1 ] ]]
-              df.CESe$dx3dt <- df.CESe[[ derivNames[ unlist(n)[3]+1 ] ]]
-              # Calculate derivative terms
-              df.CESe <- df.CESe %>% 
+      return(df)
+    } else if (energy == "withE"){
+      df <- df %>% 
         transform(b = delta_1 * x1^(-rho_1) + (1 - delta_1) * x2^(-rho_1)) %>%
@@
         transform(solowFrac = lambda_fd / dydtOvery)
-              # Add to the list of data frames
-              dframes[[length(dframes)+1]] <- df.CESe
+      return(df)
+    } else {
+      stop (paste("Unknown energy:", energy))
     }
   } else {
-            stop (paste("Unknown e:", e))
-          }
-        } else {
-          stop(paste("Unknown model", model))
+    stop(paste("Unknown modelStr", modelStr))
   }
 }
-    }
-  }      
-}
-temp_data <- do.call(plyr::rbind.fill, dframes)
+
+lag <- 1 # year
+temp_data <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, id, lag=1, pad="tail"){
+  df <- dynamicSR(model, id=id, lag=lag, pad=pad)
+  id_list <- strsplit(id, split = "[.]")[[1]]
+  df$Country <- id_list[[1]]
+  df$flavor <- if (id_list[[2]] == "unadjusted") "Unadjusted" else "Quality-adjusted"
+  df$energy <- if (id_list[[3]] == "noE") "Without energy" else "With energy"
+  df$model <- id_list[[4]]
+  df$nest <- if (length(id_list) > 4) id_list[[5]] else NA
+  df$Year <- model$data[["Year"]]
+  return(df)  
+}) %>% do.call(plyr::rbind.fill, .)
 
@@
                label="tab:traj.means.CD")
-# xtable::xtable(filter(traj.data.means, model=="CD") %>% select(-nest),
-#                caption="Average $\\Delta\\lambda$ and $\\Delta r$ for Cobb-Douglas models.",
-#                label="tab:traj.means.CD", 
-#                digits=6) %>% 
-#   print(., 
-#         caption.placement="top", 
-#         size="\\tiny", 
-#         include.rownames=FALSE, 
-#         math.style.negative=TRUE)
 @
@@
 
+<<Trajectory_Means_CESkle, results="asis">>=
+trajMeansTable(data = filter(traj.data.means, model=="CES" & (nest=="kl" | nest=="kle")), 
+               caption = "Average $\\Delta\\lambda$ and $\\Delta r$ for CES models with ($kl$)$e$ nesting.",
+               label="tab:traj.means.CESkle")
+@
+
 <<Solow_residual_trajectories_CESlek, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residual and fitting residual trajectories relative to the Unadjusted, Without-energy condition for the CES model with ($le$)$k$ nesting.">>=
@@
 
+<<Trajectory_Means_CESlek, results="asis">>=
+trajMeansTable(data = filter(traj.data.means, model=="CES" & (nest=="kl" | nest=="lek")), 
+               caption = "Average $\\Delta\\lambda$ and $\\Delta r$ for CES models with ($le$)$k$ nesting.",
+               label="tab:traj.means.CESlek")
+@
+
 <<Solow_residual_trajectories_CESekl, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residual and fitting residual trajectories relative to the Unadjusted, Without-energy condition for the CES model with ($ek$)$l$ nesting.">>=
 residualsTrajGraph(filter(traj.data, model=="CES" & (nest=="kl" | nest=="ekl")))
+@
+
+<<Trajectory_Means_CESekl, results="asis">>=
+trajMeansTable(data = filter(traj.data.means, model=="CES" & (nest=="kl" | nest=="ekl")), 
+               caption = "Average $\\Delta\\lambda$ and $\\Delta r$ for CES models with ($ek$)$l$ nesting.",
+               label="tab:traj.means.CESekl")
 @

### 2015-06-02 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Now calculate deltas on mse and lambda. This is for non-dynamic SR.

@@
   nest <- if(length(id_list) > 4) id_list[[5]] else NA
+  res <- rbind(list(Country=Country, flavor=flavor, energy=energy, model=model, nest=nest))
   coeffs <- naturalCoef(mod)
-  res <- rbind(list(Country=Country, flavor=flavor, energy=energy, model=model, nest=nest))
   res <- cbind(res, coeffs)
+  # Now calculate the mean squared error (mse) for each model.
+  sqResids <- resid(mod)^2
+  mse <- sum(sqResids)/(length(sqResids))
+  res <- cbind(res, list(mse=mse))
   return(res)
 }) %>% do.call(plyr::rbind.fill, .)
+# Get the unadjusted, no-energy values for mse and lambda and place them on each appropriate row
+AllCoeffs_unadj_noE <- filter(AllCoeffs, flavor=="unadjusted", energy=="noE") %>% 
+                              select(Country, flavor, energy, model, nest, mse, lambda)
+colnames(AllCoeffs_unadj_noE)[colnames(AllCoeffs_unadj_noE)=="mse"] <- "mse_unadj_noE"
+colnames(AllCoeffs_unadj_noE)[colnames(AllCoeffs_unadj_noE)=="lambda"] <- "lambda_unadj_noE"
+AllCoeffs <- merge(AllCoeffs, AllCoeffs_unadj_noE[c("Country", "model", "mse_unadj_noE", "lambda_unadj_noE")])
+# Calculate differences relative to the unadjusted, no-energy condition
+AllCoeffs <- mutate(AllCoeffs, Dlambda = abs(lambda) - abs(lambda_unadj_noE), Dmse = mse - mse_unadj_noE)
+
 # Relevel factors
@@
 AllCoeffs$nest <- relevelFactor(as.factor(unlist(AllCoeffs$nest)), c("kl", "kle", "lek", "ekl"))
+# Rearrange for easier viewing
+AllCoeffs <- arrange(AllCoeffs, Country, model, flavor, energy, nest)
 @
@@
 
-lag <- 1 # year
-temp_data <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, id, lag=1, pad="tail"){
+lag.to.use <- 1 # years
+temp_data <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), 
+                        f = function(model, id, lag=lag.to.use, pad="tail"){
+print(lag)
   df <- dynamicSR(model, id=id, lag=lag, pad=pad)
@@
 with the timespan for finite differences ($t_j - t_i$) set to 
-\Sexpr{lag}~\Sexpr{if (lag == 1) "year" else "years"}.
+\Sexpr{lag.to.use}~\Sexpr{if (lag.to.use == 1) "year" else "years"}.
 It appears that quality-adjusting the factors of production

### 2015-06-02 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
New tables of Dmse and Dlambda.

@@
 require(mosaic)
+require(xtable)
 
@@
   # Set TRUE on an individual chunk to see its code.
-  echo=FALSE     
+  echo=FALSE,
+  # Sets all table captions to the top.
+  xtable.caption.placement="top"
 )
@@
 For now, I've organized the analysis around questions that we would like to answer.
+
+%++++++++++++++++++++++++++++++
+\subsection{Does quality-adjusting the factors of production 
+            decrease the fitting residual and dynamic Solow residual?} 
+\label{sec:quality_adj_energy_and_dynamic_solow_residual}
+%++++++++++++++++++++++++++++++
+
+We can test our hypothesis that quality-adjusting the factors of production
+and including energy will both reduce the Solow residuals~($\lambda$)
+and improve the fit to historical data
+(thereby, reducing the fitting residuals, $r$)
+by calculating 
+$\Delta \lambda$ and $\Delta mse$, where
+%
+\begin{equation} \label{eq:delta_lambda}
+  \Delta \lambda \equiv \left| \lambda \right| - \left| \lambda_{Unadjusted, \, Without \, energy} \right|
+\end{equation}
+%
+and
+%
+\begin{equation} \label{eq:delta_mse}
+  \Delta mse \equiv \frac{1}{N} \sum_i{r_i^2} - mse_{Unadjusted, \, Without \, energy}.
+\end{equation}
+%
+where~$N$ is the number of years of data.
+When $\Delta \lambda$ and $\Delta mse$ are negative, 
+we observe reduction in the Solow residual ($\lambda$) and
+the fitting residuals ($r$).
+
+Table~\ref{tab:DSRmse_CD} shows the results for the Cobb-Douglas models.
+%
+<<MyXTableFunction>>=
+myXTable <- function(data, caption, label, digits=2){
+  table <- xtable(data, caption=caption, label=label, digits=digits)
+  print(table, 
+        caption.placement="top", 
+        size="\\tiny", 
+        include.rownames=FALSE, 
+        math.style.negative=TRUE)
+}
+@
+%
+<<DSRmse_CD, results="asis">>=
+myXTable(filter(AllCoeffs, model=="CD") %>% select(Country, model, flavor, energy, Dlambda, Dmse),
+         caption="$\\Delta \\lambda$ and $\\Delta mse$ for Cobb-Douglas models.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
+%
+Tables~\ref{tab:DSRmse_CESkle}--\ref{tab:CSRmse_CESekl} show results for the various CES nestings.
+%
+<<DSRmse_CESkle, results="asis">>=
+myXTable(filter(AllCoeffs, model=="CES" & (nest=="kl" | nest=="kle")) %>% 
+           select(Country, model, flavor, energy, nest, Dlambda, Dmse),
+         caption="$\\Delta \\lambda$ and $\\Delta mse$ for CES models with ($kl$)$e$ nesting.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
+%
+<<DSRmse_CESlek, results="asis">>=
+myXTable(filter(AllCoeffs, model=="CES" & (nest=="kl" | nest=="lek")) %>% 
+           select(Country, model, flavor, energy, nest, Dlambda, Dmse),
+         caption="$\\Delta \\lambda$ and $\\Delta mse$ for CES models with ($le$)$k$ nesting.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
+%
+<<DSRmse_CESekk, results="asis">>=
+myXTable(filter(AllCoeffs, model=="CES" & (nest=="kl" | nest=="ekl")) %>% 
+           select(Country, model, flavor, energy, nest, Dlambda, Dmse),
+         caption="$\\Delta \\lambda$ and $\\Delta mse$ for CES models with ($ek$)$l$ nesting.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
 
@@
                         f = function(model, id, lag=lag.to.use, pad="tail"){
-print(lag)
   df <- dynamicSR(model, id=id, lag=lag, pad=pad)
@@
 %
-\begin{equation} \label{eq:delta_lambda}
+\begin{equation} \label{eq:delta_lambda_i}
   \Delta \lambda_i \equiv \left| \lambda_i \right| - \left| \lambda_{i, \, Unadjusted, \, Without \, energy} \right|
@@
 %
-<<TrajMeansTableFunction>>=
-trajMeansTable <- function(data, caption, label){
-  table <- xtable::xtable(data, caption=caption, label=label, digits=6)
-  print(table, 
-        caption.placement="top", 
-        size="\\tiny", 
-        include.rownames=FALSE, 
-        math.style.negative=TRUE)
-}
-@
-
 <<Trajectory_Means_CD, results="asis">>=
-trajMeansTable(data = filter(traj.data.means, model=="CD") %>% select(-nest), 
+myXTable(data = filter(traj.data.means, model=="CD") %>% select(-nest), 
          caption = "Average $\\Delta\\lambda$ and $\\Delta r$ for Cobb-Douglas models.",
-               label="tab:traj.means.CD")
+         label="tab:traj.means.CD",
+         digits=6)
 @
@@
 we should perform the same analysis for the CES model.
-
+%
 <<Solow_residual_trajectories_CESkle, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residual and fitting residual trajectories relative to the Unadjusted, Without-energy condition for the CES model with ($kl$)$e$ nesting.">>=
@@
 @
-
+%
 <<Trajectory_Means_CESkle, results="asis">>=
-trajMeansTable(data = filter(traj.data.means, model=="CES" & (nest=="kl" | nest=="kle")), 
+myXTable(data = filter(traj.data.means, model=="CES" & (nest=="kl" | nest=="kle")), 
          caption = "Average $\\Delta\\lambda$ and $\\Delta r$ for CES models with ($kl$)$e$ nesting.",
-               label="tab:traj.means.CESkle")
+         label="tab:traj.means.CESkle",
+         digits=6)
 @
@@
                caption = "Average $\\Delta\\lambda$ and $\\Delta r$ for CES models with ($le$)$k$ nesting.",
-               label="tab:traj.means.CESlek")
+               label="tab:traj.means.CESlek",
+               digits=6)
 @
@@
 <<Trajectory_Means_CESekl, results="asis">>=
-trajMeansTable(data = filter(traj.data.means, model=="CES" & (nest=="kl" | nest=="ekl")), 
+myXTable(data = filter(traj.data.means, model=="CES" & (nest=="kl" | nest=="ekl")), 
          caption = "Average $\\Delta\\lambda$ and $\\Delta r$ for CES models with ($ek$)$l$ nesting.",
-               label="tab:traj.means.CESekl")
+         label="tab:traj.means.CESekl",
+         digits=6)
 @

### 2015-06-03 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Rearranged much of the analysis.

@@
   nest <- if(length(id_list) > 4) id_list[[5]] else NA
-  res <- rbind(list(Country=Country, flavor=flavor, energy=energy, model=model, nest=nest))
+  res <- rbind(list(Country = Country, 
+                    flavor = if (flavor=="unadjusted") "Unadjusted" else "Quality-adjusted",
+                    energy = if (energy=="noE") "Without energy" else "With energy",
+                    model=model, 
+                    nest=nest))
   coeffs <- naturalCoef(mod)
@@
 # Get the unadjusted, no-energy values for mse and lambda and place them on each appropriate row
-AllCoeffs_unadj_noE <- filter(AllCoeffs, flavor=="unadjusted", energy=="noE") %>% 
+AllCoeffs_unadj_noE <- filter(AllCoeffs, flavor=="Unadjusted", energy=="Without energy") %>% 
                               select(Country, flavor, energy, model, nest, mse, lambda)
@@
 AllCoeffs$Country <- relevelFactor(as.factor(unlist(AllCoeffs$Country)), c("PT", "UK"))
-AllCoeffs$flavor <- relevelFactor(as.factor(unlist(AllCoeffs$flavor)), c("unadjusted", "adjusted"))
-AllCoeffs$energy <- relevelFactor(as.factor(unlist(AllCoeffs$energy)), c("noE", "withE"))
+AllCoeffs$flavor <- relevelFactor(as.factor(unlist(AllCoeffs$flavor)), c("Unadjusted", "Quality-adjusted"))
+AllCoeffs$energy <- relevelFactor(as.factor(unlist(AllCoeffs$energy)), c("Without energy", "With energy"))
 AllCoeffs$model <- relevelFactor(as.factor(unlist(AllCoeffs$model)), c("CD", "CES"))
@@
 
-This section shows graphs of fits to historical data and residuals.
-Because we fit in log-space, the residuals ($r_i$) are defined as
-%
-\begin{equation} \label{eq:log-residuals}
-  r_i \equiv \ln(y_i) - \ln(\hat{y}_i) =\ln\left( \frac{y_i}{\hat{y}_i} \right), 
-\end{equation}
-%
-where $r_i$ will be zero when there is agreement between 
-historical~($y_i$) and fitted~($\hat{y}_i$) economic output.
-
 <<Fitted and Residual Graph Functions>>=
@@
     scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12)) +
+    xlab("") +
     ylab("Indexed GDP (1960=1)") +
@@
 }
-
+@
+
+Both historical GDP and fitted GDP are shown in 
+Figures~\ref{fig:Graphs CD-fitted}--\ref{fig:Graphs CESekl-fitted}.
+%
+<<Graphs CD-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Cobb-Douglas models. Solid line is historical GDP.">>=
+fittedGraph(filter(fitted_and_resid_data, model=="CD"))
+@
+%
+<<Graphs CESkle-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($kl$)$e$ nesting. Solid line is historical GDP.">>=
+fittedGraph(filter(fitted_and_resid_data, model=="CES" & (nest=="kle" | nest=="kl")))
+@
+%
+<<Graphs CESlek-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($le$)$k$ nesting. Solid line is historical GDP.">>=
+fittedGraph(filter(fitted_and_resid_data, model=="CES" & (nest=="lek" | nest=="kl")))
+@
+%
+<<Graphs CESekl-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($ek$)$l$ nesting. Solid line is historical GDP.">>=
+fittedGraph(filter(fitted_and_resid_data, model=="CES" & (nest=="ekl" | nest=="kl")))
+@
+
+%++++++++++++++++++++++++++++++
+\subsection{Fitting residuals} 
+\label{sec:fitting_residuals}
+%++++++++++++++++++++++++++++++
+
+<<ResidualPlotFunction>>=
 residualPlot <- function(data){
@@
     scale_x_continuous(breaks=c(1960, 1980, 2000)) +
+    xlab("") +
+    ylab("r") + 
     xy_theme()
@@
 
-<<Graphs CD-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Cobb-Douglas models. Solid line is historical GDP.">>=
-fittedGraph(filter(fitted_and_resid_data, model=="CD"))
-@
-
-<<Graphs CD-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Residuals for Cobb-Douglas models.">>=
+Because we fit in log-space, fitting residuals ($r_i$) are defined as
+%
+\begin{equation} \label{eq:log-residuals}
+  r_i \equiv \ln(y_i) - \ln(\hat{y}_i) =\ln\left( \frac{y_i}{\hat{y}_i} \right), 
+\end{equation}
+%
+where $r_i$ will be zero when there is agreement between 
+historical~($y_i$) and fitted~($\hat{y}_i$) economic output.
+
+The mean squared error~($mse$) for any fitted model can be calculated by
+%
+\begin{equation} \label{eq:mse}
+  mse \equiv \frac{1}{N} \sum_{i=1}^N{r_i^2} .
+\end{equation}
+
+Figures~\ref{fig:Graphs CD-resid}--\ref{fig:Graphs CESekl-resid}
+show fitting residuals for all models.
+%
+<<Graphs CD-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for Cobb-Douglas models.">>=
 residualPlot(filter(fitted_and_resid_data, model=="CD"))
 @
-
-<<Graphs CESkle-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($kl$)$e$ nesting. Solid line is historical GDP.">>=
-fittedGraph(filter(fitted_and_resid_data, model=="CES" & (nest=="kle" | nest=="kl")))
-@
-
-<<Graphs CESkle-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Residuals for CES models with $(kl$)$e$ nesting.">>=
+%
+<<Graphs CESkle-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(kl$)$e$ nesting.">>=
 residualPlot(filter(fitted_and_resid_data, model=="CES" & (nest=="kle" | nest=="kl")))
 @
-
-<<Graphs CESlek-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($le$)$k$ nesting. Solid line is historical GDP.">>=
-fittedGraph(filter(fitted_and_resid_data, model=="CES" & (nest=="lek" | nest=="kl")))
-@
-
-<<Graphs CESlek-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Residuals for CES models with ($le$)$k$ nesting.">>=
+%
+<<Graphs CESlek-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with ($le$)$k$ nesting.">>=
 residualPlot(filter(fitted_and_resid_data, model=="CES" & (nest == "lek" | nest=="kl")))
 @
-
-<<Graphs CESekl-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($ek$)$l$ nesting. Solid line is historical GDP.">>=
-fittedGraph(filter(fitted_and_resid_data, model=="CES" & (nest=="ekl" | nest=="kl")))
-@
-
-<<Graphs CESekl-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Residuals for CES models with $(ek$)$l$ nesting.">>=
+%
+<<Graphs CESekl-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(ek$)$l$ nesting.">>=
 residualPlot(filter(fitted_and_resid_data, model=="CES" & (nest=="ekl" | nest=="kl")))
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Analysis}
-\label{sec:analysis}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-For now, I've organized the analysis around questions that we would like to answer.
-
 %++++++++++++++++++++++++++++++
-\subsection{Does quality-adjusting the factors of production 
-            decrease the fitting residual and dynamic Solow residual?} 
-\label{sec:quality_adj_energy_and_dynamic_solow_residual}
-%++++++++++++++++++++++++++++++
-
-We can test our hypothesis that quality-adjusting the factors of production
-and including energy will both reduce the Solow residuals~($\lambda$)
-and improve the fit to historical data
-(thereby, reducing the fitting residuals, $r$)
-by calculating 
-$\Delta \lambda$ and $\Delta mse$, where
-%
-\begin{equation} \label{eq:delta_lambda}
-  \Delta \lambda \equiv \left| \lambda \right| - \left| \lambda_{Unadjusted, \, Without \, energy} \right|
-\end{equation}
-%
-and
-%
-\begin{equation} \label{eq:delta_mse}
-  \Delta mse \equiv \frac{1}{N} \sum_i{r_i^2} - mse_{Unadjusted, \, Without \, energy}.
-\end{equation}
-%
-where~$N$ is the number of years of data.
-When $\Delta \lambda$ and $\Delta mse$ are negative, 
-we observe reduction in the Solow residual ($\lambda$) and
-the fitting residuals ($r$).
-
-Table~\ref{tab:DSRmse_CD} shows the results for the Cobb-Douglas models.
-%
-<<MyXTableFunction>>=
-myXTable <- function(data, caption, label, digits=2){
-  table <- xtable(data, caption=caption, label=label, digits=digits)
-  print(table, 
-        caption.placement="top", 
-        size="\\tiny", 
-        include.rownames=FALSE, 
-        math.style.negative=TRUE)
-}
-@
-%
-<<DSRmse_CD, results="asis">>=
-myXTable(filter(AllCoeffs, model=="CD") %>% select(Country, model, flavor, energy, Dlambda, Dmse),
-         caption="$\\Delta \\lambda$ and $\\Delta mse$ for Cobb-Douglas models.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-%
-Tables~\ref{tab:DSRmse_CESkle}--\ref{tab:CSRmse_CESekl} show results for the various CES nestings.
-%
-<<DSRmse_CESkle, results="asis">>=
-myXTable(filter(AllCoeffs, model=="CES" & (nest=="kl" | nest=="kle")) %>% 
-           select(Country, model, flavor, energy, nest, Dlambda, Dmse),
-         caption="$\\Delta \\lambda$ and $\\Delta mse$ for CES models with ($kl$)$e$ nesting.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-%
-<<DSRmse_CESlek, results="asis">>=
-myXTable(filter(AllCoeffs, model=="CES" & (nest=="kl" | nest=="lek")) %>% 
-           select(Country, model, flavor, energy, nest, Dlambda, Dmse),
-         caption="$\\Delta \\lambda$ and $\\Delta mse$ for CES models with ($le$)$k$ nesting.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-%
-<<DSRmse_CESekk, results="asis">>=
-myXTable(filter(AllCoeffs, model=="CES" & (nest=="kl" | nest=="ekl")) %>% 
-           select(Country, model, flavor, energy, nest, Dlambda, Dmse),
-         caption="$\\Delta \\lambda$ and $\\Delta mse$ for CES models with ($ek$)$l$ nesting.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-
-%++++++++++++++++++++++++++++++
-\subsection{Does quality-adjusting the factors of production 
-            decrease the dynamic Solow residual?} 
-\label{sec:quality_adj_energy_and_dynamic_solow_residual}
+\subsection{Dynamic Solow residuals} 
+\label{sec:dynamic_solow_residuals}
 %++++++++++++++++++++++++++++++
@@
 
-Figure~\ref{fig:DynamicSR_CD_Graph} shows the evolution 
-of the Solow residual~($\lambda$) over time
-as calculated by Equation~\ref{eq:lambdaij} 
-with the timespan for finite differences ($t_j - t_i$) set to 
-\Sexpr{lag.to.use}~\Sexpr{if (lag.to.use == 1) "year" else "years"}.
-It appears that quality-adjusting the factors of production
-\emph{and} adding augmenting the production function with energy
-decreases the Solow residual~($\lambda$),
-i.e., brings the Solow residual closer to zero.
-
 <<DynamicSR_Graph>>=
@@
 
+``Dynamic'' Solow residuals~($\lambda_{i,j}$) can be calculated 
+for the Cobb-Douglas and CES models
+as shown in Appendices~\ref{sec:dynamic_sr_CD} and~\ref{sec:dynamic_sr_CES},
+respectively.
+
+Figure~\ref{fig:DynamicSR_CD_Graph} shows the evolution 
+of the Solow residual~($\lambda_{i,j}$) over time
+as calculated by Equation~\ref{eq:lambdaij} 
+with the timespan for finite differences ($t_j - t_i$) set to 
+\Sexpr{lag.to.use}~\Sexpr{if (lag.to.use == 1) "year" else "years"}.
+%
 <<DynamicSR_CD_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residuals for the Cobb-Douglas model.
@@
 @
-
+%
 <<DynamicSR_CESkle_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residuals for the CES model with ($kl$)$e$ nesting.
@@
 @
-
+%
 <<DynamicSR_CESlek_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residuals for the CES model with ($le$)$k$ nesting.
@@
 @
-
+%
 <<DynamicSR_CESekl_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residuals for the CES model with ($ek$)$l$ nesting.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Analysis}
+\label{sec:analysis}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+For now, I've organized the analysis around questions that we would like to answer.
+
 %++++++++++++++++++++++++++++++
-\subsection{How does quality-adjusting and including energy affect the dynamic Solow residual?} 
-\label{sec:trajectory_graphs}
+\subsection{Does quality-adjusting the factors of production 
+            decrease the mean squared error and/or the Solow residual?} 
+\label{sec:quality_adj_energy_and_solow_residual}
+%++++++++++++++++++++++++++++++
+
+We can test our hypothesis that quality-adjusting the factors of production
+and including energy will both reduce the Solow residuals~($\lambda$)
+and improve the fit to historical data
+(thereby, reducing the fitting residuals, $r_i$)
+by calculating 
+$\Delta \lambda$ and $\Delta mse$, where
+%
+\begin{equation} \label{eq:delta_lambda}
+  \Delta \lambda \equiv \left| \lambda \right| - \left| \lambda_{Unadjusted, \, Without \, energy} \right|
+\end{equation}
+%
+and
+%
+\begin{equation} \label{eq:delta_mse}
+  \Delta mse \equiv mse - mse_{Unadjusted, \, Without \, energy}.
+\end{equation}
+%
+where~$N$ is the number of years of data.
+When $\Delta \lambda$ and $\Delta mse$ are negative, 
+we observe reduction in the Solow residual ($\lambda$) and
+the fitting residuals ($mse$)
+relative to the unadjusted, no-energy condition.
+
+Table~\ref{tab:DSRmse_CD} shows the results for the Cobb-Douglas models.
+%
+<<MyXTableFunction>>=
+myXTable <- function(data, caption, label, digits=2){
+  table <- xtable(data, caption=caption, label=label, digits=digits)
+  print(table, 
+        caption.placement="top", 
+        size="\\tiny", 
+        include.rownames=FALSE, 
+        math.style.negative=TRUE)
+}
+@
+%
+<<DSRmse_CD, results="asis">>=
+myXTable(filter(AllCoeffs, model=="CD") %>% select(Country, model, flavor, energy, Dlambda, Dmse),
+         caption="$\\Delta \\lambda$ and $\\Delta mse$ for Cobb-Douglas models.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
+% 
+Tables~\ref{tab:DSRmse_CESkle}--\ref{tab:DSRmse_CESekl} show results 
+for CES models with various nestings.
+%
+<<DSRmse_CESkle, results="asis">>=
+myXTable(filter(AllCoeffs, model=="CES" & (nest=="kl" | nest=="kle")) %>% 
+           select(Country, model, flavor, energy, nest, Dlambda, Dmse),
+         caption="$\\Delta \\lambda$ and $\\Delta mse$ for CES models with ($kl$)$e$ nesting.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
+%
+<<DSRmse_CESlek, results="asis">>=
+myXTable(filter(AllCoeffs, model=="CES" & (nest=="kl" | nest=="lek")) %>% 
+           select(Country, model, flavor, energy, nest, Dlambda, Dmse),
+         caption="$\\Delta \\lambda$ and $\\Delta mse$ for CES models with ($le$)$k$ nesting.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
+%
+<<DSRmse_CESekl, results="asis">>=
+myXTable(filter(AllCoeffs, model=="CES" & (nest=="kl" | nest=="ekl")) %>% 
+           select(Country, model, flavor, energy, nest, Dlambda, Dmse),
+         caption="$\\Delta \\lambda$ and $\\Delta mse$ for CES models with ($ek$)$l$ nesting.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
+%
+Figure~\ref{fig:DSRmse_CD_graph} summarizes the data for the Cobb-Douglas model.
+%
+<<DSRmse_CD_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta mse$) for the Cobb-Douglas model relative to the unadjusted, no-energy condition.">>=
+ggplot(data=filter(AllCoeffs, model=="CD")) +
+  geom_point(mapping=aes(x=Dmse, y=Dlambda, color = energy)) +
+  facet_grid(Country ~ flavor) +
+  xlab(expression(Delta * mse)) + 
+  ylab(expression(Delta * lambda)) +
+  xy_theme() + 
+  theme(legend.title=element_blank())
+@
+%
+Figure~\ref{fig:DSRmse_CES_graph} summarizes the data for the CES models.
+%
+<<DSRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta mse$) for the Cobb-Douglas model relative to the unadjusted, no-energy condition.">>=
+ggplot(data=filter(AllCoeffs, model=="CES")) +
+  geom_point(mapping=aes(x=Dmse, y=Dlambda, color = energy, shape=nest)) +
+  facet_grid(Country ~ flavor) +
+  xlab(expression(Delta * mse)) + 
+  ylab(expression(Delta * lambda)) +
+  xy_theme() +
+  theme(legend.title=element_blank())
+@
+
+%++++++++++++++++++++++++++++++
+\subsection{Does quality-adjusting the factors of production 
+            decrease fitting residuals and/or the dynamic Solow residual?} 
+\label{sec:quality_adj_energy_and_dynamic_solow_residual}
 %++++++++++++++++++++++++++++++
@@
                    arrange(Country, model, flavor, energy, nest)
-traj.data.means <- traj.data %>% 
+traj.data.stats <- traj.data %>% 
   group_by(model, Country, flavor, energy, nest) %>%
   summarise(Dlambda_fd.mean = mean(Dlambda_fd, na.rm=TRUE), Dr.mean = mean(Dr))
+
+############################################
+# Dlambda_fd.p <- traj.data %>% 
+#   group_by(model, Country, flavor, energy, nest) %>% 
+#   select(Dlambda_fd) %>%
+#   t.test(., alternative="less")[["p.value"]]
+############################################  
 @
@@
     geom_point(mapping=aes(x=Dr, y=Dlambda_fd, color=energy)) + 
-#     geom_path(mapping=aes(x=Dr, y=Dlambda_fd, color=energy)) + 
     facet_grid(Country ~ flavor) +
-    xlab(expression(Delta*r)) +
-    ylab(expression(Delta*lambda)) +
+    xlab(expression(Delta*r[i])) +
+    ylab(expression(Delta*lambda[ij])) +
     xy_theme() + 
@@
 
-We can also calculate the average values for $\Delta \lambda$ and $\Delta r$ 
-as shown in Table~\ref{tab:traj.means.CD}.
+We can also calculate the average values for $\Delta \lambda_{i,j}$ and $\Delta r_{i}$ 
+as shown in Table~\ref{tab:Trajectory_Means_CD}.
 %
 <<Trajectory_Means_CD, results="asis">>=
-myXTable(data = filter(traj.data.means, model=="CD") %>% select(-nest), 
+myXTable(data = filter(traj.data.stats, model=="CD") %>% select(-nest), 
          caption = "Average $\\Delta\\lambda$ and $\\Delta r$ for Cobb-Douglas models.",
-         label="tab:traj.means.CD",
+         label=paste0("tab:", opts_current$get("label")),
          digits=6)
@@
 %
-These results for the Cobb-Douglas model indicate that 
-we should perform the same analysis for the CES model.
+The following tables and figures show the same analysis for the CES model.
 %
@@
 <<Trajectory_Means_CESkle, results="asis">>=
-myXTable(data = filter(traj.data.means, model=="CES" & (nest=="kl" | nest=="kle")), 
+myXTable(data = filter(traj.data.stats, model=="CES" & (nest=="kl" | nest=="kle")), 
          caption = "Average $\\Delta\\lambda$ and $\\Delta r$ for CES models with ($kl$)$e$ nesting.",
-         label="tab:traj.means.CESkle",
+         label=paste0("tab:", opts_current$get("label")),
          digits=6)
@@
 <<Trajectory_Means_CESlek, results="asis">>=
-trajMeansTable(data = filter(traj.data.means, model=="CES" & (nest=="kl" | nest=="lek")), 
+myXTable(data = filter(traj.data.stats, model=="CES" & (nest=="kl" | nest=="lek")), 
          caption = "Average $\\Delta\\lambda$ and $\\Delta r$ for CES models with ($le$)$k$ nesting.",
-               label="tab:traj.means.CESlek",
+         label=paste0("tab:", opts_current$get("label")),
          digits=6)
@@
 <<Trajectory_Means_CESekl, results="asis">>=
-myXTable(data = filter(traj.data.means, model=="CES" & (nest=="kl" | nest=="ekl")), 
+myXTable(data = filter(traj.data.stats, model=="CES" & (nest=="kl" | nest=="ekl")), 
          caption = "Average $\\Delta\\lambda$ and $\\Delta r$ for CES models with ($ek$)$l$ nesting.",
-         label="tab:traj.means.CESekl",
+         label=paste0("tab:", opts_current$get("label")),
          digits=6)
@@
 
-%++++++++++++++++++++++++++++++
-\subsection{What effect does including energy and quality-adjustment have 
-            on the Solow residual in the Cobb-Douglas model?} 
-\label{sec:quality_adj_energy_and_solow_residual}
-%++++++++++++++++++++++++++++++
-
-We'll first look at Portugal.
-
-%------------------------------
-\subsubsection{Portugal} 
-%------------------------------
-
-First, use non-quality-adjusted data for Portugal and the Cobb-Douglas model.
-
-<<Portugal C-D undadjusted without energy>>=
-naturalCoef(models$PT$unadjusted$noE$CD)
-@
-
-<<Portugal C-D undadjusted with energy>>=
-naturalCoef(models$PT$unadjusted$withE$CD)
-@
-
-The Solow residual (\texttt{lambda}) is always negative. 
-However, the absolute value of \texttt{lambda} decreases from 
-\Sexpr{naturalCoef(models$PT$unadjusted$noE$CD)$lambda} to 
-\Sexpr{naturalCoef(models$PT$unadjusted$withE$CD)$lambda}
-when adding energy.
-So it appears that for Portugal, 
-using unadjusted inputs and including energy as a factor of production
-reduces the absolute value of the Solow residual somewhat.
-
-What about for quality-adjusted data and Portugal?
-
-<<Portugal C-D adjusted without energy>>=
-naturalCoef(models$PT$adjusted$noE$CD)
-@
-
-<<Portugal C-D adjusted with energy>>=
-naturalCoef(models$PT$adjusted$withE$CD)
-@
-
-Using quality-adjusted inputs, the Solow residual (\texttt{lambda}) moves from 
-\Sexpr{naturalCoef(models$PT$adjusted$noE$CD)$lambda} to
-\Sexpr{naturalCoef(models$PT$adjusted$withE$CD)$lambda} when including energy.
-The absolute value of the Solow residual again decreases when adding energy.
-But, with quality-adjusted inputs, the effect is much stronger.
-
-Table~\ref{tab:lambda_CD_PT} shows
-the effect of both quality-corrected factors of production and energy.
-We find that including energy as a factor of production 
-reduces the absolute value of the Solow residual (\texttt{lambda})
-whether or not the factors of production are quality-adjusted. 
-Quality-adjustment gets part of the way toward eliminating the Solow residual.
-
-\begin{table} \caption{Portugal Solow residual results with Cobb-Douglas.} 
-\label{tab:lambda_CD_PT} 
-  \begin{center}
-    \begin{tabular}{r c c} 
-      \toprule
-                      & Unadjusted     & Quality-adjusted   \\
-      \midrule
-      Without energy  & \Sexpr{naturalCoef(models$PT$unadjusted$noE$CD)$lambda}    & \Sexpr{naturalCoef(models$PT$adjusted$noE$CD)$lambda} \\
-      With energy     & \Sexpr{naturalCoef(models$PT$unadjusted$withE$CD)$lambda}  & \Sexpr{naturalCoef(models$PT$adjusted$withE$CD)$lambda} \\
-      \bottomrule
-    \end{tabular}
-  \end{center}
-\end{table}
-
-Note that for Portugal the contribution of capital (\texttt{alpha\_1})
-always shifts to energy (\texttt{alpha\_3}) when energy is included 
-as a factor of production.
-
-What about for the UK?
-
-%------------------------------
-\subsubsection{United Kingdom} 
-%------------------------------
-
-Table~\ref{tab:lambda_CD_UK} shows fitted Cobb-Douglas coefficients for the UK.
-
-\begin{table} \caption{UK Solow residual results with Cobb-Douglas.} 
-\label{tab:lambda_CD_UK} 
-  \begin{center}
-    \begin{tabular}{r c c} 
-      \toprule
-                      & Unadjusted     & Quality-adjusted   \\
-      \midrule
-      Without energy  & \Sexpr{naturalCoef(models$UK$unadjusted$noE$CD)$lambda}   
-                                                & \Sexpr{naturalCoef(models$UK$adjusted$noE$CD)$lambda} \\
-      With energy     & \Sexpr{naturalCoef(models$UK$unadjusted$withE$CD)$lambda} 
-                                                & \Sexpr{naturalCoef(models$UK$adjusted$withE$CD)$lambda} \\
-      \bottomrule
-    \end{tabular}
-  \end{center}
-\end{table}
-
-For the UK, the quality-adjusted, with energy Solow residual is 
-\Sexpr{naturalCoef(models$UK$adjusted$withE$CD)$lambda * 100}\%,
-a very small number indeed.
-For the UK, it appears that \emph{both} quality-adjustment and addition of energy as a factor of production
-are required to effectively eliminate the Solow residual,
-reducing it to \Sexpr{naturalCoef(models$UK$adjusted$withE$CD)$lambda}.
-
-Adding energy alone actually \emph{in}creases the Solow residual from 
-\Sexpr{naturalCoef(models$UK$unadjusted$noE$CD)$lambda} to
-\Sexpr{naturalCoef(models$UK$unadjusted$withE$CD)$lambda}.
-The details for each model with unadjusted factors of production are shown below.
-
-<<UK CD Unadjusted Coefficients>>=
-naturalCoef(models$UK$unadjusted$noE$CD)
-naturalCoef(models$UK$unadjusted$withE$CD)
-@
-
-When energy is included, much of the effect of capital (\texttt{alpha\_1}) is 
-attributed to energy (\texttt{alpha\_3}), 
-as \texttt{alpha\_1} moves from 
-\Sexpr{naturalCoef(models$UK$unadjusted$noE$CD)$alpha_1} to
-\Sexpr{naturalCoef(models$UK$unadjusted$withE$CD)$alpha_1}.
-
-When we look at quality-adjusted inputs, we find similar results.
-
-<<UK CD Quality-adjusted Coefficients>>=
-naturalCoef(models$UK$adjusted$noE$CD)
-naturalCoef(models$UK$adjusted$withE$CD)
-@
-
-\texttt{alpha\_1} moves from 
-\Sexpr{naturalCoef(models$UK$adjusted$noE$CD)$alpha_1} to
-\Sexpr{naturalCoef(models$UK$adjusted$withE$CD)$alpha_1}.
-
-Now, let's compare the fits to historical data.
-
-%++++++++++++++++++++++++++++++
-\subsection{Do we obtain a negative Solow residual for Portugal with the CES model?} 
-\label{sec:Solow_negative_for_PT_in_CES?}
-%++++++++++++++++++++++++++++++
-
-First, look at the CES model without energy.
-Nesting is unabmiguous, so this fit does not need to be repeated
-for each nesting option. 
-(This means that the top rows of Tables~\ref{tab:lambda_CES-kle_PT}--\ref{tab:lambda_CES-ekl_PT}
-are identical.)
-
-<<PT CES-kl, warning=FALSE>>=
-naturalCoef(models$PT$unadjusted$noE$CES$kl)
-naturalCoef(models$PT$adjusted$noE$CES$kl)
-@
-
-Both unadjusted and quality-adjusted variables give positive Solow residuals,
-\Sexpr{naturalCoef(models$PT$unadjusted$noE$CES$kl)$lambda} for unadjusted inputs and
-\Sexpr{naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda} for quality-adjusted inputs.
-Furthermore, quality-adjustment reduces the magnitude of the Solow residual.
-
-%------------------------------
-\subsubsection{($kl$)$e$ nesting} 
-%------------------------------
-
-Now, look at unadjusted inputs using the ($kl$)$e$ nesting.
-
-<<PT CES-kle unadjusted, warning=FALSE>>=
-naturalCoef(models$PT$unadjusted$withE$CES$kle)
-@
-
-Now look at quality-adjusted inputs using the ($kl$)$e$ nesting.
-
-<<PT CES-kle quality-adjusted, warning=FALSE>>=
-naturalCoef(models$PT$adjusted$withE$CES$kle)
-@
-
-Table~\ref{tab:lambda_CES-kle_PT} summarizes the Portugal Solow residual results with CES and the ($kl$)$e$ nesting.
-
-\begin{table} \caption{Portugal Solow residual results with CES and ($kl$)$e$ nesting.} 
-\label{tab:lambda_CES-kle_PT} 
-  \begin{center}
-    \begin{tabular}{r c c} 
-      \toprule
-                      & Unadjusted     & Quality-adjusted   \\
-      \midrule
-      Without energy  & \Sexpr{naturalCoef(models$PT$unadjusted$noE$CES$kl)$lambda} 
-                                                            & \Sexpr{naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda} \\
-      With energy     & \Sexpr{naturalCoef(models$PT$unadjusted$withE$CES$kle)$lambda} 
-                                                            & \Sexpr{naturalCoef(models$PT$adjusted$withE$CES$kle)$lambda} \\
-      \bottomrule
-    \end{tabular}
-  \end{center}
-\end{table}
-
-Table~\ref{tab:sse_CES-kle_PT} shows the $sse$ values for each of these models.
-
-\begin{table} \caption{PT $sse$ with CES and ($kl$)$e$ nesting.} 
-\label{tab:sse_CES-kle_PT} 
-  \begin{center}
-    \begin{tabular}{r c c} 
-      \toprule
-                      & Unadjusted     & Quality-adjusted   \\
-      \midrule
-      Without energy  & \Sexpr{EconModels:::sse(models$PT$unadjusted$noE$CES$kl)$sse} 
-                                                            & \Sexpr{EconModels:::sse(models$PT$adjusted$noE$CES$kl)$sse} \\
-      With energy     & \Sexpr{EconModels:::sse(models$PT$unadjusted$withE$CES$kle)$sse} 
-                                                            & \Sexpr{EconModels:::sse(models$PT$adjusted$withE$CES$kle)$sse} \\
-      \bottomrule
-    \end{tabular}
-  \end{center}
-\end{table}
-
-In contrast to the Cobb-Douglas model,
-the CES model with ($kl$)$e$ nesting
-produces positive Solow residuals in all cases. 
-We also see that both 
-quality-adjusting the inputs and
-including energy
-reduce the Solow residual (\texttt{lambda}).
-
-%------------------------------
-\subsubsection{($le$)$k$ nesting} 
-%------------------------------
-
-Next, look at unadjusted inputs using the ($le$)$k$ nesting.
-
-<<PT CES-lek unadjusted, warning=FALSE>>=
-naturalCoef(models$PT$unadjusted$withE$CES$lek)
-@
-
-Now look at quality-adjusted inputs using the ($le$)$k$ nesting.
-
-<<PT CES-lek quality-adjusted, warning=FALSE>>=
-naturalCoef(models$PT$adjusted$withE$CES$lek)
-@
-
-Table~\ref{tab:lambda_CES-lek_PT} summarizes the Portugal Solow residual results with CES and the ($le$)$k$ nesting.
-
-\begin{table} \caption{Portugal Solow residual results with CES and ($le$)$k$ nesting.} 
-\label{tab:lambda_CES-lek_PT} 
-  \begin{center}
-    \begin{tabular}{r c c} 
-      \toprule
-                      & Unadjusted     & Quality-adjusted   \\
-      \midrule
-      Without energy  & \Sexpr{naturalCoef(models$PT$unadjusted$noE$CES$kl)$lambda} 
-                                        & \Sexpr{naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda} \\
-      With energy     & \Sexpr{naturalCoef(models$PT$unadjusted$withE$CES$lek)$lambda} 
-                                        & \Sexpr{naturalCoef(models$PT$adjusted$withE$CES$lek)$lambda} \\
-      \bottomrule
-    \end{tabular}
-  \end{center}
-\end{table}
-
-Table~\ref{tab:sse_CES-lek_PT} shows the $sse$ values for each of these models.
-
-\begin{table} \caption{PT $sse$ with CES and ($le$)$k$ nesting.} 
-\label{tab:sse_CES-lek_PT} 
-  \begin{center}
-    \begin{tabular}{r c c} 
-      \toprule
-                      & Unadjusted     & Quality-adjusted   \\
-      \midrule
-      Without energy  & \Sexpr{EconModels:::sse(models$PT$unadjusted$noE$CES$kl)$sse} 
-                                        & \Sexpr{EconModels:::sse(models$PT$adjusted$noE$CES$kl)$sse} \\
-      With energy     & \Sexpr{EconModels:::sse(models$PT$unadjusted$withE$CES$lek)$sse} 
-                                        & \Sexpr{EconModels:::sse(models$PT$adjusted$withE$CES$lek)$sse} \\
-      \bottomrule
-    \end{tabular}
-  \end{center}
-\end{table}
-
-Similar to the CES model with ($kl$)$e$ nesting,
-the CES model with ($le$)$k$ nesting
-produces positive Solow residuals in all cases. 
-After energy has been added, quality-adjustment 
-has very little effect on the Solow residual,
-creating a slight increase from 
-\Sexpr{naturalCoef(models$PT$unadjusted$withE$CES$lek)$lambda} to
-\Sexpr{naturalCoef(models$PT$adjusted$withE$CES$lek)$lambda}.
-
-%------------------------------
-\subsubsection{($ek$)$l$ nesting} 
-%------------------------------
-
-Next, look at unadjusted inputs using the ($ek$)$l$ nesting.
-
-<<PT CES-ekl unadjusted, warning=FALSE>>=
-naturalCoef(models$PT$unadjusted$withE$CES$ekl)
-@
-
-Now look at quality-adjusted inputs using the ($ek$)$l$ nesting.
-
-<<PT CES-ekl quality-adjusted, warning=FALSE>>=
-naturalCoef(models$PT$adjusted$withE$CES$ekl)
-@
-
-Table~\ref{tab:lambda_CES-ekl_PT} summarizes the Portugal Solow residual results with CES and the ($ek$)$l$ nesting.
-
-\begin{table} \caption{Portugal Solow residual results with CES and ($ek$)$l$ nesting.} 
-\label{tab:lambda_CES-ekl_PT} 
-  \begin{center}
-    \begin{tabular}{r c c} 
-      \toprule
-                      & Unadjusted     & Quality-adjusted   \\
-      \midrule
-      Without energy  & \Sexpr{naturalCoef(models$PT$unadjusted$noE$CES$kl)$lambda} 
-                                        & \Sexpr{naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda} \\
-      With energy     & \Sexpr{naturalCoef(models$PT$unadjusted$withE$CES$ekl)$lambda} 
-                                        & \Sexpr{naturalCoef(models$PT$adjusted$withE$CES$ekl)$lambda} \\
-      \bottomrule
-    \end{tabular}
-  \end{center}
-\end{table}
-
-Table~\ref{tab:sse_CES-ekl_PT} shows the $sse$ values for each of these models.
-
-\begin{table} \caption{PT $sse$ with CES and ($ek$)$l$ nesting.} 
-\label{tab:sse_CES-ekl_PT} 
-  \begin{center}
-    \begin{tabular}{r c c} 
-      \toprule
-                      & Unadjusted     & Quality-adjusted   \\
-      \midrule
-      Without energy  & \Sexpr{EconModels:::sse(models$PT$unadjusted$noE$CES$kl)$sse} 
-                                        & \Sexpr{EconModels:::sse(models$PT$adjusted$noE$CES$kl)$sse} \\
-      With energy     & \Sexpr{EconModels:::sse(models$PT$unadjusted$withE$CES$ekl)$sse} 
-                                        & \Sexpr{EconModels:::sse(models$PT$adjusted$withE$CES$ekl)$sse} \\
-      \bottomrule
-    \end{tabular}
-  \end{center}
-\end{table}
-
-For the ($ek$)$l$ nesting, 
-the Solow residual is positive, and 
-quality-adjusting the inputs 
-reduces the Solow residual (\texttt{lambda}).
-Adding energy decreases the Solow residual 
-(from \Sexpr{naturalCoef(models$PT$unadjusted$withE$CES$ekl)$lambda} to 
-\Sexpr{naturalCoef(models$PT$adjusted$withE$CES$ekl)$lambda})
-when enegy is included in the model.
-But, adding energy slightly increases the Solow residual
-(from \Sexpr{naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda} to \Sexpr{naturalCoef(models$PT$adjusted$withE$CES$ekl)$lambda})
-when quality-adjusted inputs are used.
-
-%++++++++++++++++++++++++++++++
-\subsection{Do we obtain a positive Solow residual for the UK with the CES model?} 
-\label{sec:Solow_positive_for_UK_in_CES?}
-%++++++++++++++++++++++++++++++
-
-First, look at the CES model without energy.
-Nesting is unabmiguous, so this fit does not need to be repeated
-for each nesting option. 
-(This means that the top rows of Tables~\ref{tab:lambda_CES-kle_UK}--\ref{tab:lambda_CES-ekl_UK}
-are identical.)
-
-<<UK CES-kl, warning=FALSE>>=
-naturalCoef(models$UK$unadjusted$noE$CES$kl)
-naturalCoef(models$UK$adjusted$noE$CES$kl)
-@
-
-Both unadjusted and quality-adjusted variables give positive Solow residuals for the UK,
-\Sexpr{naturalCoef(models$UK$unadjusted$noE$CES$kl)$lambda} for unadjusted inputs and
-\Sexpr{naturalCoef(models$UK$adjusted$noE$CES$kl)$lambda} for quality-adjusted inputs.
-Furthermore, quality-adjustment reduces the magnitude of the UK Solow residual.
-
-%------------------------------
-\subsubsection{($kl$)$e$ nesting} 
-%------------------------------
-
-Now, look at unadjusted inputs using the ($kl$)$e$ nesting.
-
-<<UK CES-kle unadjusted>>=
-naturalCoef(models$UK$unadjusted$withE$CES$kle)
-@
-
-Now look at quality-adjusted inputs using the ($kl$)$e$ nesting.
-
-<<UK CES-kle quality-adjusted>>=
-naturalCoef(models$UK$adjusted$withE$CES$kle)
-@
-
-Table~\ref{tab:lambda_CES-kle_UK} summarizes the UK Solow residual results with CES and the ($kl$)$e$ nesting.
-
-\begin{table} \caption{UK Solow residual results with CES and ($kl$)$e$ nesting.} 
-\label{tab:lambda_CES-kle_UK} 
-  \begin{center}
-    \begin{tabular}{r c c} 
-      \toprule
-                      & Unadjusted     & Quality-adjusted   \\
-      \midrule
-      Without energy  & \Sexpr{naturalCoef(models$UK$unadjusted$noE$CES$kl)$lambda} & \Sexpr{naturalCoef(models$UK$adjusted$noE$CES$kl)$lambda} \\
-      With energy     & \Sexpr{naturalCoef(models$UK$unadjusted$withE$CES$kle)$lambda} 
-                                                                & \Sexpr{naturalCoef(models$UK$adjusted$withE$CES$kle)$lambda} \\
-      \bottomrule
-    \end{tabular}
-  \end{center}
-\end{table}
-
-Table~\ref{tab:sse_CES-kle_UK} shows the $sse$ values for each of these models.
-
-\begin{table} \caption{UK $sse$ with CES and ($kl$)$e$ nesting.} 
-\label{tab:sse_CES-kle_UK} 
-  \begin{center}
-    \begin{tabular}{r c c} 
-      \toprule
-                      & Unadjusted     & Quality-adjusted   \\
-      \midrule
-      Without energy  & \Sexpr{EconModels:::sse(models$UK$unadjusted$noE$CES$kl)$sse} & \Sexpr{EconModels:::sse(models$UK$adjusted$noE$CES$kl)$sse} \\
-      With energy     & \Sexpr{EconModels:::sse(models$UK$unadjusted$withE$CES$kle)$sse} 
-                                                            & \Sexpr{EconModels:::sse(models$UK$adjusted$withE$CES$kle)$sse} \\
-      \bottomrule
-    \end{tabular}
-  \end{center}
-\end{table}
-
-Like the Cobb-Douglas model, the CES model produces positive Solow residuals
-with the ($kl$)$e$ nesting.
-We also see that both 
-quality-adjusting the inputs and
-including energy
-reduce the Solow residual (\texttt{lambda}).
-
-%------------------------------
-\subsubsection{($le$)$k$ nesting}
-%------------------------------
-
-Next, look at unadjusted inputs using the ($le$)$k$ nesting.
-
-<<UK CES-lek unadjusted>>=
-naturalCoef(models$UK$unadjusted$withE$CES$lek)
-@
-
-Now look at quality-adjusted inputs using the ($le$)$k$ nesting.
-
-<<UK CES-lek quality-adjusted>>=
-naturalCoef(models$UK$adjusted$withE$CES$lek)
-@
-
-Table~\ref{tab:lambda_CES-lek_UK} summarizes the UK Solow residual results with CES and the ($le$)$k$ nesting.
-
-\begin{table} \caption{UK Solow residual results with CES and ($le$)$k$ nesting.} 
-\label{tab:lambda_CES-lek_UK} 
-  \begin{center}
-    \begin{tabular}{r c c} 
-      \toprule
-                      & Unadjusted     & Quality-adjusted   \\
-      \midrule
-      Without energy  & \Sexpr{naturalCoef(models$UK$unadjusted$noE$CES$kl)$lambda} & \Sexpr{naturalCoef(models$UK$adjusted$noE$CES$kl)$lambda} \\
-      With energy     & \Sexpr{naturalCoef(models$UK$unadjusted$withE$CES$lek)$lambda} 
-                                                            & \Sexpr{naturalCoef(models$UK$adjusted$withE$CES$lek)$lambda} \\
-      \bottomrule
-    \end{tabular}
-  \end{center}
-\end{table}
-
-Table~\ref{tab:sse_CES-lek_UK} shows the $sse$ values for each of these models.
-
-\begin{table} \caption{UK $sse$ with CES and ($le$)$k$ nesting.} 
-\label{tab:sse_CES-lek_UK} 
-  \begin{center}
-    \begin{tabular}{r c c} 
-      \toprule
-                      & Unadjusted     & Quality-adjusted   \\
-      \midrule
-      Without energy  & \Sexpr{EconModels:::sse(models$UK$unadjusted$noE$CES$kl)$sse} & \Sexpr{EconModels:::sse(models$UK$adjusted$noE$CES$kl)$sse} \\
-      With energy     & \Sexpr{EconModels:::sse(models$UK$unadjusted$withE$CES$lek)$sse} 
-                                                            & \Sexpr{EconModels:::sse(models$UK$adjusted$withE$CES$lek)$sse} \\
-      \bottomrule
-    \end{tabular}
-  \end{center}
-\end{table}
-
-Similar to the CES model with ($kl$)$e$ nesting,
-the CES model with ($le$)$k$ nesting
-produces positive Solow residuals in all cases. 
-Both quality-adjustment and inclusion of energy 
-decrease the magnitude of the Solow residual.
-
-%------------------------------
-\subsubsection{($ek$)$l$ nesting}
-%------------------------------
-
-Next, look at unadjusted inputs using the ($el$)$l$ nesting.
-
-<<UK CES-ekl unadjusted>>=
-naturalCoef(models$UK$unadjusted$withE$CES$ekl)
-@
-
-Now look at quality-adjusted inputs using the ($ek$)$l$ nesting.
-
-<<UK CES-ekl quality-adjusted>>=
-naturalCoef(models$UK$adjusted$withE$CES$ekl)
-@
-
-Table~\ref{tab:lambda_CES-ekl_UK} summarizes the UK Solow residual results with CES and the ($ek$)$l$ nesting.
-
-\begin{table} \caption{UK Solow residual results with CES and ($ek$)$l$ nesting.} 
-\label{tab:lambda_CES-ekl_UK} 
-  \begin{center}
-    \begin{tabular}{r c c} 
-      \toprule
-                      & Unadjusted     & Quality-adjusted   \\
-      \midrule
-      Without energy  & \Sexpr{naturalCoef(models$UK$unadjusted$noE$CES$kl)$lambda} & \Sexpr{naturalCoef(models$UK$adjusted$noE$CES$kl)$lambda} \\
-      With energy     & \Sexpr{naturalCoef(models$UK$unadjusted$withE$CES$ekl)$lambda} 
-                                                            & \Sexpr{naturalCoef(models$UK$adjusted$withE$CES$ekl)$lambda} \\
-      \bottomrule
-    \end{tabular}
-  \end{center}
-\end{table}
-
-Table~\ref{tab:sse_CES-ekl_UK} shows the $sse$ values for each of these models.
-
-\begin{table} \caption{UK $sse$ with CES and ($ek$)$l$ nesting.} 
-\label{tab:sse_CES-ekl_UK} 
-  \begin{center}
-    \begin{tabular}{r c c} 
-      \toprule
-                      & Unadjusted     & Quality-adjusted   \\
-      \midrule
-      Without energy  & \Sexpr{EconModels:::sse(models$UK$unadjusted$noE$CES$kl)$sse} & \Sexpr{EconModels:::sse(models$UK$adjusted$noE$CES$kl)$sse} \\
-      With energy     & \Sexpr{EconModels:::sse(models$UK$unadjusted$withE$CES$ekl)$sse} 
-                                                            & \Sexpr{EconModels:::sse(models$UK$adjusted$withE$CES$ekl)$sse} \\
-      \bottomrule
-    \end{tabular}
-  \end{center}
-\end{table}
-
-Similar to the CES model with ($ek$)$l$ nesting,
-the CES model with ($ek$)$l$ nesting
-produces positive Solow residuals in all cases. 
-Both quality-adjustment and inclusion of energy 
-decrease the magnitude of the Solow residual.
+% %++++++++++++++++++++++++++++++
+% \subsection{What effect does including energy and quality-adjustment have 
+%             on the Solow residual in the Cobb-Douglas model?} 
+% \label{sec:quality_adj_energy_and_solow_residual}
+% %++++++++++++++++++++++++++++++
+% 
+% We'll first look at Portugal.
+% 
+% %------------------------------
+% \subsubsection{Portugal} 
+% %------------------------------
+% 
+% First, use non-quality-adjusted data for Portugal and the Cobb-Douglas model.
+% 
+% <<Portugal C-D undadjusted without energy>>=
+% naturalCoef(models$PT$unadjusted$noE$CD)
+% @
+% 
+% <<Portugal C-D undadjusted with energy>>=
+% naturalCoef(models$PT$unadjusted$withE$CD)
+% @
+% 
+% The Solow residual (\texttt{lambda}) is always negative. 
+% However, the absolute value of \texttt{lambda} decreases from 
+% \Sexpr{naturalCoef(models$PT$unadjusted$noE$CD)$lambda} to 
+% \Sexpr{naturalCoef(models$PT$unadjusted$withE$CD)$lambda}
+% when adding energy.
+% So it appears that for Portugal, 
+% using unadjusted inputs and including energy as a factor of production
+% reduces the absolute value of the Solow residual somewhat.
+% 
+% What about for quality-adjusted data and Portugal?
+% 
+% <<Portugal C-D adjusted without energy>>=
+% naturalCoef(models$PT$adjusted$noE$CD)
+% @
+% 
+% <<Portugal C-D adjusted with energy>>=
+% naturalCoef(models$PT$adjusted$withE$CD)
+% @
+% 
+% Using quality-adjusted inputs, the Solow residual (\texttt{lambda}) moves from 
+% \Sexpr{naturalCoef(models$PT$adjusted$noE$CD)$lambda} to
+% \Sexpr{naturalCoef(models$PT$adjusted$withE$CD)$lambda} when including energy.
+% The absolute value of the Solow residual again decreases when adding energy.
+% But, with quality-adjusted inputs, the effect is much stronger.
+% 
+% Table~\ref{tab:lambda_CD_PT} shows
+% the effect of both quality-corrected factors of production and energy.
+% We find that including energy as a factor of production 
+% reduces the absolute value of the Solow residual (\texttt{lambda})
+% whether or not the factors of production are quality-adjusted. 
+% Quality-adjustment gets part of the way toward eliminating the Solow residual.
+% 
+% \begin{table} \caption{Portugal Solow residual results with Cobb-Douglas.} 
+% \label{tab:lambda_CD_PT} 
+%   \begin{center}
+%     \begin{tabular}{r c c} 
+%       \toprule
+%                       & Unadjusted     & Quality-adjusted   \\
+%       \midrule
+%       Without energy  & \Sexpr{naturalCoef(models$PT$unadjusted$noE$CD)$lambda}    & \Sexpr{naturalCoef(models$PT$adjusted$noE$CD)$lambda} \\
+%       With energy     & \Sexpr{naturalCoef(models$PT$unadjusted$withE$CD)$lambda}  & \Sexpr{naturalCoef(models$PT$adjusted$withE$CD)$lambda} \\
+%       \bottomrule
+%     \end{tabular}
+%   \end{center}
+% \end{table}
+% 
+% Note that for Portugal the contribution of capital (\texttt{alpha\_1})
+% always shifts to energy (\texttt{alpha\_3}) when energy is included 
+% as a factor of production.
+% 
+% What about for the UK?
+% 
+% %------------------------------
+% \subsubsection{United Kingdom} 
+% %------------------------------
+% 
+% Table~\ref{tab:lambda_CD_UK} shows fitted Cobb-Douglas coefficients for the UK. 
+% 
+% \begin{table} \caption{UK Solow residual results with Cobb-Douglas.} 
+% \label{tab:lambda_CD_UK} 
+%   \begin{center}
+%     \begin{tabular}{r c c} 
+%       \toprule
+%                       & Unadjusted     & Quality-adjusted   \\
+%       \midrule
+%       Without energy  & \Sexpr{naturalCoef(models$UK$unadjusted$noE$CD)$lambda}   
+%                                                 & \Sexpr{naturalCoef(models$UK$adjusted$noE$CD)$lambda} \\
+%       With energy     & \Sexpr{naturalCoef(models$UK$unadjusted$withE$CD)$lambda} 
+%                                                 & \Sexpr{naturalCoef(models$UK$adjusted$withE$CD)$lambda} \\
+%       \bottomrule
+%     \end{tabular}
+%   \end{center}
+% \end{table}
+% 
+% For the UK, the quality-adjusted, with energy Solow residual is 
+% \Sexpr{naturalCoef(models$UK$adjusted$withE$CD)$lambda * 100}\%,
+% a very small number indeed.
+% For the UK, it appears that \emph{both} quality-adjustment and addition of energy as a factor of production
+% are required to effectively eliminate the Solow residual,
+% reducing it to \Sexpr{naturalCoef(models$UK$adjusted$withE$CD)$lambda}.
+% 
+% Adding energy alone actually \emph{in}creases the Solow residual from 
+% \Sexpr{naturalCoef(models$UK$unadjusted$noE$CD)$lambda} to
+% \Sexpr{naturalCoef(models$UK$unadjusted$withE$CD)$lambda}.
+% The details for each model with unadjusted factors of production are shown below.
+% 
+% <<UK CD Unadjusted Coefficients>>=
+% naturalCoef(models$UK$unadjusted$noE$CD)
+% naturalCoef(models$UK$unadjusted$withE$CD)
+% @
+% 
+% When energy is included, much of the effect of capital (\texttt{alpha\_1}) is 
+% attributed to energy (\texttt{alpha\_3}), 
+% as \texttt{alpha\_1} moves from 
+% \Sexpr{naturalCoef(models$UK$unadjusted$noE$CD)$alpha_1} to
+% \Sexpr{naturalCoef(models$UK$unadjusted$withE$CD)$alpha_1}.
+% 
+% When we look at quality-adjusted inputs, we find similar results.
+% 
+% <<UK CD Quality-adjusted Coefficients>>=
+% naturalCoef(models$UK$adjusted$noE$CD)
+% naturalCoef(models$UK$adjusted$withE$CD)
+% @
+% 
+% \texttt{alpha\_1} moves from 
+% \Sexpr{naturalCoef(models$UK$adjusted$noE$CD)$alpha_1} to
+% \Sexpr{naturalCoef(models$UK$adjusted$withE$CD)$alpha_1}.
+% 
+% Now, let's compare the fits to historical data.
+% 
+% 
+% 
+% %++++++++++++++++++++++++++++++
+% \subsection{Do we obtain a negative Solow residual for Portugal with the CES model?} 
+% \label{sec:Solow_negative_for_PT_in_CES?}
+% %++++++++++++++++++++++++++++++
+% 
+% First, look at the CES model without energy.
+% Nesting is unabmiguous, so this fit does not need to be repeated
+% for each nesting option. 
+% (This means that the top rows of Tables~\ref{tab:lambda_CES-kle_PT}--\ref{tab:lambda_CES-ekl_PT}
+% are identical.)
+% 
+% <<PT CES-kl, warning=FALSE>>=
+% naturalCoef(models$PT$unadjusted$noE$CES$kl)
+% naturalCoef(models$PT$adjusted$noE$CES$kl)
+% @
+% 
+% Both unadjusted and quality-adjusted variables give positive Solow residuals,
+% \Sexpr{naturalCoef(models$PT$unadjusted$noE$CES$kl)$lambda} for unadjusted inputs and
+% \Sexpr{naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda} for quality-adjusted inputs.
+% Furthermore, quality-adjustment reduces the magnitude of the Solow residual.
+% 
+% %------------------------------
+% \subsubsection{($kl$)$e$ nesting} 
+% %------------------------------
+% 
+% Now, look at unadjusted inputs using the ($kl$)$e$ nesting.
+% 
+% <<PT CES-kle unadjusted, warning=FALSE>>=
+% naturalCoef(models$PT$unadjusted$withE$CES$kle)
+% @
+% 
+% Now look at quality-adjusted inputs using the ($kl$)$e$ nesting.
+% 
+% <<PT CES-kle quality-adjusted, warning=FALSE>>=
+% naturalCoef(models$PT$adjusted$withE$CES$kle)
+% @
+% 
+% Table~\ref{tab:lambda_CES-kle_PT} summarizes the Portugal Solow residual results with CES and the ($kl$)$e$ nesting.
+% 
+% \begin{table} \caption{Portugal Solow residual results with CES and ($kl$)$e$ nesting.} 
+% \label{tab:lambda_CES-kle_PT} 
+%   \begin{center}
+%     \begin{tabular}{r c c} 
+%       \toprule
+%                       & Unadjusted     & Quality-adjusted   \\
+%       \midrule
+%       Without energy  & \Sexpr{naturalCoef(models$PT$unadjusted$noE$CES$kl)$lambda} 
+%                                                             & \Sexpr{naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda} \\
+%       With energy     & \Sexpr{naturalCoef(models$PT$unadjusted$withE$CES$kle)$lambda} 
+%                                                             & \Sexpr{naturalCoef(models$PT$adjusted$withE$CES$kle)$lambda} \\
+%       \bottomrule
+%     \end{tabular}
+%   \end{center}
+% \end{table}
+% 
+% Table~\ref{tab:sse_CES-kle_PT} shows the $sse$ values for each of these models.
+% 
+% \begin{table} \caption{PT $sse$ with CES and ($kl$)$e$ nesting.} 
+% \label{tab:sse_CES-kle_PT} 
+%   \begin{center}
+%     \begin{tabular}{r c c} 
+%       \toprule
+%                       & Unadjusted     & Quality-adjusted   \\
+%       \midrule
+%       Without energy  & \Sexpr{EconModels:::sse(models$PT$unadjusted$noE$CES$kl)$sse} 
+%                                                             & \Sexpr{EconModels:::sse(models$PT$adjusted$noE$CES$kl)$sse} \\
+%       With energy     & \Sexpr{EconModels:::sse(models$PT$unadjusted$withE$CES$kle)$sse} 
+%                                                             & \Sexpr{EconModels:::sse(models$PT$adjusted$withE$CES$kle)$sse} \\
+%       \bottomrule
+%     \end{tabular}
+%   \end{center}
+% \end{table}
+% 
+% In contrast to the Cobb-Douglas model,
+% the CES model with ($kl$)$e$ nesting
+% produces positive Solow residuals in all cases. 
+% We also see that both 
+% quality-adjusting the inputs and
+% including energy
+% reduce the Solow residual (\texttt{lambda}).
+% 
+% %------------------------------
+% \subsubsection{($le$)$k$ nesting} 
+% %------------------------------
+% 
+% Next, look at unadjusted inputs using the ($le$)$k$ nesting.
+% 
+% <<PT CES-lek unadjusted, warning=FALSE>>=
+% naturalCoef(models$PT$unadjusted$withE$CES$lek)
+% @
+% 
+% Now look at quality-adjusted inputs using the ($le$)$k$ nesting.
+% 
+% <<PT CES-lek quality-adjusted, warning=FALSE>>=
+% naturalCoef(models$PT$adjusted$withE$CES$lek)
+% @
+% 
+% Table~\ref{tab:lambda_CES-lek_PT} summarizes the Portugal Solow residual results with CES and the ($le$)$k$ nesting.
+% 
+% \begin{table} \caption{Portugal Solow residual results with CES and ($le$)$k$ nesting.} 
+% \label{tab:lambda_CES-lek_PT} 
+%   \begin{center}
+%     \begin{tabular}{r c c} 
+%       \toprule
+%                       & Unadjusted     & Quality-adjusted   \\
+%       \midrule
+%       Without energy  & \Sexpr{naturalCoef(models$PT$unadjusted$noE$CES$kl)$lambda} 
+%                                         & \Sexpr{naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda} \\
+%       With energy     & \Sexpr{naturalCoef(models$PT$unadjusted$withE$CES$lek)$lambda} 
+%                                         & \Sexpr{naturalCoef(models$PT$adjusted$withE$CES$lek)$lambda} \\
+%       \bottomrule
+%     \end{tabular}
+%   \end{center}
+% \end{table}
+% 
+% Table~\ref{tab:sse_CES-lek_PT} shows the $sse$ values for each of these models.
+% 
+% \begin{table} \caption{PT $sse$ with CES and ($le$)$k$ nesting.} 
+% \label{tab:sse_CES-lek_PT} 
+%   \begin{center}
+%     \begin{tabular}{r c c} 
+%       \toprule
+%                       & Unadjusted     & Quality-adjusted   \\
+%       \midrule
+%       Without energy  & \Sexpr{EconModels:::sse(models$PT$unadjusted$noE$CES$kl)$sse} 
+%                                         & \Sexpr{EconModels:::sse(models$PT$adjusted$noE$CES$kl)$sse} \\
+%       With energy     & \Sexpr{EconModels:::sse(models$PT$unadjusted$withE$CES$lek)$sse} 
+%                                         & \Sexpr{EconModels:::sse(models$PT$adjusted$withE$CES$lek)$sse} \\
+%       \bottomrule
+%     \end{tabular}
+%   \end{center}
+% \end{table}
+% 
+% Similar to the CES model with ($kl$)$e$ nesting,
+% the CES model with ($le$)$k$ nesting
+% produces positive Solow residuals in all cases. 
+% After energy has been added, quality-adjustment 
+% has very little effect on the Solow residual,
+% creating a slight increase from 
+% \Sexpr{naturalCoef(models$PT$unadjusted$withE$CES$lek)$lambda} to
+% \Sexpr{naturalCoef(models$PT$adjusted$withE$CES$lek)$lambda}.
+% 
+% 
+% %------------------------------
+% \subsubsection{($ek$)$l$ nesting} 
+% %------------------------------
+% 
+% Next, look at unadjusted inputs using the ($ek$)$l$ nesting.
+% 
+% <<PT CES-ekl unadjusted, warning=FALSE>>=
+% naturalCoef(models$PT$unadjusted$withE$CES$ekl)
+% @
+% 
+% Now look at quality-adjusted inputs using the ($ek$)$l$ nesting.
+% 
+% <<PT CES-ekl quality-adjusted, warning=FALSE>>=
+% naturalCoef(models$PT$adjusted$withE$CES$ekl)
+% @
+% 
+% Table~\ref{tab:lambda_CES-ekl_PT} summarizes the Portugal Solow residual results with CES and the ($ek$)$l$ nesting.
+% 
+% \begin{table} \caption{Portugal Solow residual results with CES and ($ek$)$l$ nesting.} 
+% \label{tab:lambda_CES-ekl_PT} 
+%   \begin{center}
+%     \begin{tabular}{r c c} 
+%       \toprule
+%                       & Unadjusted     & Quality-adjusted   \\
+%       \midrule
+%       Without energy  & \Sexpr{naturalCoef(models$PT$unadjusted$noE$CES$kl)$lambda} 
+%                                         & \Sexpr{naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda} \\
+%       With energy     & \Sexpr{naturalCoef(models$PT$unadjusted$withE$CES$ekl)$lambda} 
+%                                         & \Sexpr{naturalCoef(models$PT$adjusted$withE$CES$ekl)$lambda} \\
+%       \bottomrule
+%     \end{tabular}
+%   \end{center}
+% \end{table}
+% 
+% Table~\ref{tab:sse_CES-ekl_PT} shows the $sse$ values for each of these models.
+% 
+% \begin{table} \caption{PT $sse$ with CES and ($ek$)$l$ nesting.} 
+% \label{tab:sse_CES-ekl_PT} 
+%   \begin{center}
+%     \begin{tabular}{r c c} 
+%       \toprule
+%                       & Unadjusted     & Quality-adjusted   \\
+%       \midrule
+%       Without energy  & \Sexpr{EconModels:::sse(models$PT$unadjusted$noE$CES$kl)$sse} 
+%                                         & \Sexpr{EconModels:::sse(models$PT$adjusted$noE$CES$kl)$sse} \\
+%       With energy     & \Sexpr{EconModels:::sse(models$PT$unadjusted$withE$CES$ekl)$sse} 
+%                                         & \Sexpr{EconModels:::sse(models$PT$adjusted$withE$CES$ekl)$sse} \\
+%       \bottomrule
+%     \end{tabular}
+%   \end{center}
+% \end{table}
+% 
+% For the ($ek$)$l$ nesting, 
+% the Solow residual is positive, and 
+% quality-adjusting the inputs 
+% reduces the Solow residual (\texttt{lambda}).
+% Adding energy decreases the Solow residual 
+% (from \Sexpr{naturalCoef(models$PT$unadjusted$withE$CES$ekl)$lambda} to 
+% \Sexpr{naturalCoef(models$PT$adjusted$withE$CES$ekl)$lambda})
+% when enegy is included in the model.
+% But, adding energy slightly increases the Solow residual
+% (from \Sexpr{naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda} to \Sexpr{naturalCoef(models$PT$adjusted$withE$CES$ekl)$lambda})
+% when quality-adjusted inputs are used.
+% 
+% 
+% %++++++++++++++++++++++++++++++
+% \subsection{Do we obtain a positive Solow residual for the UK with the CES model?} 
+% \label{sec:Solow_positive_for_UK_in_CES?}
+% %++++++++++++++++++++++++++++++
+% 
+% First, look at the CES model without energy.
+% Nesting is unabmiguous, so this fit does not need to be repeated
+% for each nesting option. 
+% (This means that the top rows of Tables~\ref{tab:lambda_CES-kle_UK}--\ref{tab:lambda_CES-ekl_UK}
+% are identical.)
+% 
+% <<UK CES-kl, warning=FALSE>>=
+% naturalCoef(models$UK$unadjusted$noE$CES$kl)
+% naturalCoef(models$UK$adjusted$noE$CES$kl)
+% @
+% 
+% Both unadjusted and quality-adjusted variables give positive Solow residuals for the UK,
+% \Sexpr{naturalCoef(models$UK$unadjusted$noE$CES$kl)$lambda} for unadjusted inputs and
+% \Sexpr{naturalCoef(models$UK$adjusted$noE$CES$kl)$lambda} for quality-adjusted inputs.
+% Furthermore, quality-adjustment reduces the magnitude of the UK Solow residual.
+% 
+% %------------------------------
+% \subsubsection{($kl$)$e$ nesting} 
+% %------------------------------
+% 
+% Now, look at unadjusted inputs using the ($kl$)$e$ nesting.
+% 
+% <<UK CES-kle unadjusted>>=
+% naturalCoef(models$UK$unadjusted$withE$CES$kle)
+% @
+% 
+% Now look at quality-adjusted inputs using the ($kl$)$e$ nesting.
+% 
+% <<UK CES-kle quality-adjusted>>=
+% naturalCoef(models$UK$adjusted$withE$CES$kle)
+% @
+% 
+% Table~\ref{tab:lambda_CES-kle_UK} summarizes the UK Solow residual results with CES and the ($kl$)$e$ nesting.
+% 
+% \begin{table} \caption{UK Solow residual results with CES and ($kl$)$e$ nesting.} 
+% \label{tab:lambda_CES-kle_UK} 
+%   \begin{center}
+%     \begin{tabular}{r c c} 
+%       \toprule
+%                       & Unadjusted     & Quality-adjusted   \\
+%       \midrule
+%       Without energy  & \Sexpr{naturalCoef(models$UK$unadjusted$noE$CES$kl)$lambda} & \Sexpr{naturalCoef(models$UK$adjusted$noE$CES$kl)$lambda} \\
+%       With energy     & \Sexpr{naturalCoef(models$UK$unadjusted$withE$CES$kle)$lambda} 
+%                                                                 & \Sexpr{naturalCoef(models$UK$adjusted$withE$CES$kle)$lambda} \\
+%       \bottomrule
+%     \end{tabular}
+%   \end{center}
+% \end{table}
+% 
+% Table~\ref{tab:sse_CES-kle_UK} shows the $sse$ values for each of these models.
+% 
+% \begin{table} \caption{UK $sse$ with CES and ($kl$)$e$ nesting.} 
+% \label{tab:sse_CES-kle_UK} 
+%   \begin{center}
+%     \begin{tabular}{r c c} 
+%       \toprule
+%                       & Unadjusted     & Quality-adjusted   \\
+%       \midrule
+%       Without energy  & \Sexpr{EconModels:::sse(models$UK$unadjusted$noE$CES$kl)$sse} & \Sexpr{EconModels:::sse(models$UK$adjusted$noE$CES$kl)$sse} \\
+%       With energy     & \Sexpr{EconModels:::sse(models$UK$unadjusted$withE$CES$kle)$sse} 
+%                                                             & \Sexpr{EconModels:::sse(models$UK$adjusted$withE$CES$kle)$sse} \\
+%       \bottomrule
+%     \end{tabular}
+%   \end{center}
+% \end{table}
+% 
+% Like the Cobb-Douglas model, the CES model produces positive Solow residuals
+% with the ($kl$)$e$ nesting.
+% We also see that both 
+% quality-adjusting the inputs and
+% including energy
+% reduce the Solow residual (\texttt{lambda}).
+% 
+% %------------------------------
+% \subsubsection{($le$)$k$ nesting}
+% %------------------------------
+% 
+% Next, look at unadjusted inputs using the ($le$)$k$ nesting.
+% 
+% <<UK CES-lek unadjusted>>=
+% naturalCoef(models$UK$unadjusted$withE$CES$lek)
+% @
+% 
+% Now look at quality-adjusted inputs using the ($le$)$k$ nesting.
+% 
+% <<UK CES-lek quality-adjusted>>=
+% naturalCoef(models$UK$adjusted$withE$CES$lek)
+% @
+% 
+% Table~\ref{tab:lambda_CES-lek_UK} summarizes the UK Solow residual results with CES and the ($le$)$k$ nesting.
+% 
+% \begin{table} \caption{UK Solow residual results with CES and ($le$)$k$ nesting.} 
+% \label{tab:lambda_CES-lek_UK} 
+%   \begin{center}
+%     \begin{tabular}{r c c} 
+%       \toprule
+%                       & Unadjusted     & Quality-adjusted   \\
+%       \midrule
+%       Without energy  & \Sexpr{naturalCoef(models$UK$unadjusted$noE$CES$kl)$lambda} & \Sexpr{naturalCoef(models$UK$adjusted$noE$CES$kl)$lambda} \\
+%       With energy     & \Sexpr{naturalCoef(models$UK$unadjusted$withE$CES$lek)$lambda} 
+%                                                             & \Sexpr{naturalCoef(models$UK$adjusted$withE$CES$lek)$lambda} \\
+%       \bottomrule
+%     \end{tabular}
+%   \end{center}
+% \end{table}
+% 
+% Table~\ref{tab:sse_CES-lek_UK} shows the $sse$ values for each of these models.
+% 
+% \begin{table} \caption{UK $sse$ with CES and ($le$)$k$ nesting.} 
+% \label{tab:sse_CES-lek_UK} 
+%   \begin{center}
+%     \begin{tabular}{r c c} 
+%       \toprule
+%                       & Unadjusted     & Quality-adjusted   \\
+%       \midrule
+%       Without energy  & \Sexpr{EconModels:::sse(models$UK$unadjusted$noE$CES$kl)$sse} & \Sexpr{EconModels:::sse(models$UK$adjusted$noE$CES$kl)$sse} \\
+%       With energy     & \Sexpr{EconModels:::sse(models$UK$unadjusted$withE$CES$lek)$sse} 
+%                                                             & \Sexpr{EconModels:::sse(models$UK$adjusted$withE$CES$lek)$sse} \\
+%       \bottomrule
+%     \end{tabular}
+%   \end{center}
+% \end{table}
+% 
+% 
+% Similar to the CES model with ($kl$)$e$ nesting,
+% the CES model with ($le$)$k$ nesting
+% produces positive Solow residuals in all cases. 
+% Both quality-adjustment and inclusion of energy 
+% decrease the magnitude of the Solow residual.
+% 
+% %------------------------------
+% \subsubsection{($ek$)$l$ nesting}
+% %------------------------------
+% 
+% Next, look at unadjusted inputs using the ($el$)$l$ nesting.
+% 
+% <<UK CES-ekl unadjusted>>=
+% naturalCoef(models$UK$unadjusted$withE$CES$ekl)
+% @
+% 
+% Now look at quality-adjusted inputs using the ($ek$)$l$ nesting.
+% 
+% <<UK CES-ekl quality-adjusted>>=
+% naturalCoef(models$UK$adjusted$withE$CES$ekl)
+% @
+% 
+% Table~\ref{tab:lambda_CES-ekl_UK} summarizes the UK Solow residual results with CES and the ($ek$)$l$ nesting.
+% 
+% \begin{table} \caption{UK Solow residual results with CES and ($ek$)$l$ nesting.} 
+% \label{tab:lambda_CES-ekl_UK} 
+%   \begin{center}
+%     \begin{tabular}{r c c} 
+%       \toprule
+%                       & Unadjusted     & Quality-adjusted   \\
+%       \midrule
+%       Without energy  & \Sexpr{naturalCoef(models$UK$unadjusted$noE$CES$kl)$lambda} & \Sexpr{naturalCoef(models$UK$adjusted$noE$CES$kl)$lambda} \\
+%       With energy     & \Sexpr{naturalCoef(models$UK$unadjusted$withE$CES$ekl)$lambda} 
+%                                                             & \Sexpr{naturalCoef(models$UK$adjusted$withE$CES$ekl)$lambda} \\
+%       \bottomrule
+%     \end{tabular}
+%   \end{center}
+% \end{table}
+% 
+% Table~\ref{tab:sse_CES-ekl_UK} shows the $sse$ values for each of these models.
+% 
+% \begin{table} \caption{UK $sse$ with CES and ($ek$)$l$ nesting.} 
+% \label{tab:sse_CES-ekl_UK} 
+%   \begin{center}
+%     \begin{tabular}{r c c} 
+%       \toprule
+%                       & Unadjusted     & Quality-adjusted   \\
+%       \midrule
+%       Without energy  & \Sexpr{EconModels:::sse(models$UK$unadjusted$noE$CES$kl)$sse} & \Sexpr{EconModels:::sse(models$UK$adjusted$noE$CES$kl)$sse} \\
+%       With energy     & \Sexpr{EconModels:::sse(models$UK$unadjusted$withE$CES$ekl)$sse} 
+%                                                             & \Sexpr{EconModels:::sse(models$UK$adjusted$withE$CES$ekl)$sse} \\
+%       \bottomrule
+%     \end{tabular}
+%   \end{center}
+% \end{table}
+% 
+% 
+% Similar to the CES model with ($ek$)$l$ nesting,
+% the CES model with ($ek$)$l$ nesting
+% produces positive Solow residuals in all cases. 
+% Both quality-adjustment and inclusion of energy 
+% decrease the magnitude of the Solow residual.
 

### 2015-06-04 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
require(knitr)

@@
 # ********************************************************
-
+require(knitr)
 opts_chunk$set(

### 2015-06-05 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Incorporating suggestions from Randy.

@@
 
-Parameter estimation is accomplished with \texttt{formula}s of the form
-%
-\begin{equation} \label{eq:formulas}
-  y \sim x_1 + x_2 + x_3 + time,
-\end{equation}
-%
-where $y$ is economic output and 
-$x_1$, $x_2$, and $x_3$ are factors of production
-and permutations of
-capital ($k$), labor ($l$), and energy ($e$).
-(The factors of production may be quality-adjusted.)
-$time$ is the time variable, usually \texttt{iYear}. 
-The \texttt{formula}s are used in a fitting function such as 
-\texttt{cdModel} to create a \texttt{model} object.
-The function \texttt{naturalCoef} extracts reasonable
-coefficients from \texttt{model} objects.
-
-Note that in the fitting process for the Cobb-Douglas equation,
-$\texttt{scale} = \theta$, 
-$\alpha_1 = \alpha$,
-$\alpha_2 = \beta$, and
-$\alpha_3 = \gamma$,
-when the \texttt{formula} is specified as 
-%
-\begin{equation} \label{eq:formula_kle}
-  \texttt{y} \sim \texttt{k + l + e + time}.
-\end{equation}
-%
-Note that for the CES model, $\texttt{scale} = \gamma$ and is expected to be close to unity.
+% Parameter estimation is accomplished with \texttt{formula}s of the form
+% %
+% \begin{equation} \label{eq:formulas}
+%   y \sim x_1 + x_2 + x_3 + time,
+% \end{equation}
+% %
+% where $y$ is economic output and 
+% $x_1$, $x_2$, and $x_3$ are factors of production
+% and permutations of
+% capital ($k$), labor ($l$), and energy ($e$).
+% (The factors of production may be quality-adjusted.)
+% $time$ is the time variable, usually \texttt{iYear}. 
+% The \texttt{formula}s are used in a fitting function such as 
+% \texttt{cdModel} to create a \texttt{model} object.
+% The function \texttt{naturalCoef} extracts reasonable
+% coefficients from \texttt{model} objects.
+% 
+% Note that in the fitting process for the Cobb-Douglas equation,
+% $\texttt{scale} = \theta$, 
+% $\alpha_1 = \alpha$,
+% $\alpha_2 = \beta$, and
+% $\alpha_3 = \gamma$,
+% when the \texttt{formula} is specified as 
+% %
+% \begin{equation} \label{eq:formula_kle}
+%   \texttt{y} \sim \texttt{k + l + e + time}.
+% \end{equation}
+% %
+% Note that for the CES model, $\texttt{scale} = \gamma$ and is expected to be close to unity.
+
+The models being fit can be described by the algebraic form of the model 
+(Cobb-Douglas, CES, etc.) and a formula that enumerates 
+which data variables are being used in which roles to fit the model.  
+A formula of the form
+%
+\begin{equation} \label{eq:formulas-3-factor}
+y \sim x_1 + x_2 + x_3 + t,
+\end{equation}
+%
+or 
+%
+\begin{equation} \label{eq:formulas-2-factor}
+y \sim x_1 + x_2 + t,
+\end{equation}
+%
+describes the economic output variable ($y$, usually \texttt{iGDP},
+                                        indexed GDP) 
+and the factors of production ($x_1$, $x_2$, and $x_3$,
+                               which will be some measure of capital, labor, and energy, 
+                               but perhaps not in that order), 
+and a time variable ($t$, usually \texttt{iYear}, 
+                     the number of years since the beginning of data collection).  
+All of the models assume an error term that is additive on the 
+logarithmic scale and are fit by the method of least squares.  
+Model fitting provides estimates for all parameters in the model.
 

### 2015-06-08 Articles/Article_EnerEcon_2014/EconGrowth4.Rnw
Added old-new numbering to bmod table.
Only setting eval=TRUE.

@@
 \begin{table} \caption{CES boundary models (rows~1--20) and full model (bottom row). 
-                       Re-ordered, but with original model numbers. **** DELETE EVENTUALLY ****}
+                       Re-ordered, but with original model numbers. old-new numbering **** DELETE EVENTUALLY ****}
   \begin{center}
@@
       \midrule
-      1. & 1           & ---        & 1          & ---      & $y = \gamma A x_1$ \\
-      2. & 0           & ---        & 1          & ---      & $y = \gamma A x_2$ \\
-      6. & ---         & ---        & 0          & ---      & $y = \gamma A x_3$ \\
+      01-01 & 1           & ---        & 1          & ---      & $y = \gamma A x_1$ \\
+      02-02 & 0           & ---        & 1          & ---      & $y = \gamma A x_2$ \\
+      06-03 & ---         & ---        & 0          & ---      & $y = \gamma A x_3$ \\
       \midrule
-      3. & ---         & 0          & 1          & ---      & $y = \gamma A \min (x_1, \, x_2)$ \\
-      7. & 1           & ---        & ---        & 0        & $y = \gamma A \min (x_1, \, x_3)$ \\
-      8. & 0           & ---        & ---        & 0        & $y = \gamma A \min (x_2, \, x_3)$ \\
-%
-      4. &             & $\infty$   & 1          & ---        
+      03-04 & ---         & 0          & 1          & ---      & $y = \gamma A \min (x_1, \, x_2)$ \\
+      07-05 & 1           & ---        & ---        & 0        & $y = \gamma A \min (x_1, \, x_3)$ \\
+      08-06 & 0           & ---        & ---        & 0        & $y = \gamma A \min (x_2, \, x_3)$ \\
+%
+     04-07 &             & $\infty$   & 1          & ---        
             & $y = \gamma A \left[ \delta_1 x_1 + (1 - \delta_1) x_2 \right]$ \\
 %
-     10. & 1           & ---        &            & $\infty$        
+     10-08 & 1           & ---        &            & $\infty$        
             & $y = \gamma A \left[ \delta x_1 + (1 - \delta) x_3 \right]$ \\
 %
-     11. & 0           & ---        &            & $\infty$        
+     11-09 & 0           & ---        &            & $\infty$        
             & $y = \gamma A \left[ \delta x_2 + (1 - \delta) x_3 \right]$ \\
 %
-      5. &             &            & 1          & ---
+     05-10 &             &            & 1          & ---
             & $y = \gamma A \left[ \delta_1 x_1^{-\rho_1} 
@@
 %
-     15. & 1           & ---        &         & 
+     15-11 & 1           & ---        &         & 
             & $y = \gamma A \left[ \delta x_1^{-\rho} 
@@
 %
-     16. & 0           & ---        &            & 
+     16-12 & 0           & ---        &            & 
             & $y = \gamma A \left[ \delta x_2^{-\rho} + \left(1 - \delta \right) x_3^{-\rho} \right]^{-1/\rho}$ \\
       \midrule
-      9. & ---         & 0          & ---        & 0        & $y = \gamma A \min (x_1, \, x_2, \, x_3)$ \\
-%
-     13. & ---         & 0          &            & $\infty$        
+     09-13 & ---         & 0          & ---        & 0        & $y = \gamma A \min (x_1, \, x_2, \, x_3)$ \\
+%
+     13-14 & ---         & 0          &            & $\infty$        
             & $y = \gamma A \left[ \delta \min (x_1, \, x_2) + \left( 1 - \delta \right) x_3  \right]$ \\
 %
-     14. &             & $\infty$   & ---        & 0
+     14-15 &             & $\infty$   & ---        & 0
             & $y = \gamma A \min \left[ \delta_1 x_1 + \left(1 - \delta_1 \right) x_2, \, x_3  \right]$ \\
 %
-     12. &             & $\infty$   &            & $\infty$        
+     12-16 &             & $\infty$   &            & $\infty$        
             & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1 + \left( 1 - \delta_1 \right) x_2 \right] 
@@
 %
-     18. & ---         & 0          &            & 
+     18-17 & ---         & 0          &            & 
             & $y = \gamma A \left\{ \delta \left[ \min \left( x_1, \, x_2 \right) \right]^{-\rho}  
@@
 %
-     20. &            &            & ---     & 0
+     20-18 &            &            & ---     & 0
             & $y = \gamma A \min \left\{ \left[ \delta_1 x_1^{-\rho_1} 
@@
 %
-     19. &             &            &            & $\infty$
+     19-19 &             &            &            & $\infty$
             & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1^{-\rho_1} 
@@
 %
-     17. &             & $\infty$   &            &
+     17-20 &             & $\infty$   &            &
             & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1 

### 2015-06-08 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Now using getData instead of model$data.

@@
 fittedAndResidData <- function(model){
-  df <- data.frame(select(model$data, Year))
+  df <- data.frame(select(getData(model), Year))
   # Trim fitted to be same length as df to eliminate problems with possible NAs at end of fitted
@@
   response <- summands(f, right = FALSE)
-  df[[response]] <- model$data[[response]] # Add iGDP to the data frame
+  df[[response]] <- getData(model)[[response]] # Add iGDP to the data frame
   id_list <- strsplit(id, split = "[.]")[[1]]
@@
   nums <- all.vars(f) [1:(length(all.vars(f))-1)] # y, k, l, and e (if present)
-  df <- model$data[c(denom, nums)] # columns are: iYear, y, k, l, and e (if present)
+  df <- getData(model)[c(denom, nums)] # columns are: iYear, y, k, l, and e (if present)
 
@@
   df$nest <- if (length(id_list) > 4) id_list[[5]] else NA
-  df$Year <- model$data[["Year"]]
+  df$Year <- getData(model)[["Year"]]
   return(df)  

### 2015-06-08 Packages/EconModels/R/fortify.R

@@ -8,7 +8,7 @@
 #' @export
 #' 
 fortify.LINEXmodel <- function(model, data, ...) {
-  if(missing(data)) { data <- model$data }
+  if(missing(data)) { data <- getData(model) }
   formula <- model$formula
   data <- model.frame(formula, data)
   if (ncol(data) != 5) {

### 2015-06-10 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Now calculating p values for ∆r.

@@
 fitted_and_resid_data <- arrange(fitted_and_resid_data, Country, model, flavor, energy, nest)
+
+# Calculate p values for groups of Dr values.
+Dr.t.values <- fitted_and_resid_data %>% 
+  group_by(Country, model, flavor, energy, nest) %>% 
+  summarize(Dr.mean = mean(Dr), Dr.p.value = stats::t.test(Dr, alternative = "less")[["p.value"]])
+Dr.t.values <- arrange(ungroup(Dr.t.values), Country, model, flavor, energy, nest)
 @
@@
 residualPlot(filter(fitted_and_resid_data, model=="CES" & (nest=="ekl" | nest=="kl")))
+@
+
+The set of $\Delta r$ values for each combination of 
+country~(PT or UK), 
+model~(Cobb-Douglas or CES),
+flavor~(Unadjusted or Quality-adjusted), and
+nest~[($kl$)$e$, ($le$)$k$, or ($ek$)$l$, for the CES models]
+forms a set of numbers (one for each year) 
+that can be assessed for statistical significance
+compared to zero by a t-test.
+The null hypothesis of the t-test is that the mean of each group is
+equal to zero. 
+The alternative hypothesis is that the mean is less than zero.
+Smaller p-values indicate increasing confidence that the 
+mean is actually less than zero.
+Table~\ref{tab:Dr_p_values} summarizes the mean values for $\Delta r$
+and the associated p-values.
+%
+<<MyXTableFunction>>=
+myXTable <- function(data, caption, label, digits=2){
+  table <- xtable(data, caption=caption, label=label, digits=digits)
+  print(table, 
+        caption.placement="top", 
+        size="\\tiny", 
+        include.rownames=FALSE, 
+        math.style.negative=TRUE)
+}
+@
+%
+<<Dr_p_values, results="asis">>=
+myXTable(Dr.t.values,
+         caption="Means and p values for $\\Delta r$.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
 @
@@
 %
-<<MyXTableFunction>>=
-myXTable <- function(data, caption, label, digits=2){
-  table <- xtable(data, caption=caption, label=label, digits=digits)
-  print(table, 
-        caption.placement="top", 
-        size="\\tiny", 
-        include.rownames=FALSE, 
-        math.style.negative=TRUE)
-}
-@
-%
 <<DSRmse_CD, results="asis">>=

### 2015-06-10 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
More analysis of residuals.

--- 2015-06-08 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
@@
 require(xtable)
+require(knitr)
 
@@
 # ********************************************************
-require(knitr)
 opts_chunk$set(
@@
 %++++++++++++++++++++++++++++++
+\subsection{Are the means of the fitting residuals 
+            significantly different from zero?} 
+\label{sec:fitting_residuals_different_from_zero}
+%++++++++++++++++++++++++++++++
+
+The set of fitting residual values~($r_i$)
+for each combination of 
+country~(PT or UK), 
+model~(Cobb-Douglas or CES),
+flavor~(Unadjusted or Quality-adjusted), 
+energy~(with or without), and
+nest~[($kl$), ($kl$)$e$, ($le$)$k$, or ($ek$)$l$, for the CES models]
+can be assessed for statistical significance
+compared to zero by a t-test.
+The null hypothesis for the t-test is that the mean of each group is
+equal to zero, and 
+the alternative hypothesis is that the mean is not equal to zero.
+Smaller p-values indicate increasing confidence that the 
+mean is different from zero. 
+We expect that p-values will be large (close to unity), 
+because residuals are expected to be small (close to zero).
+Indeed, that is the case.
+Table~\ref{tab:r_p_values} summarizes the mean 
+and associated p-values values for the fitting residuals~($r_i$).
+%
+<<r_p_values, results="asis">>=
+# Calculate p values for groups of fitting residuals.
+r.t.values <- fitted_and_resid_data %>% 
+  group_by(Country, model, flavor, energy, nest) %>% 
+  summarize(Residuals.mean = mean(Residuals), Residuals.p.value = stats::t.test(Residuals)[["p.value"]])
+r.t.values <- arrange(ungroup(r.t.values), Country, model, flavor, energy, nest)
+# Display the values in a table
+myXTable(r.t.values,
+         caption="Means and p-values for fitting residuals~($r_i$).",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
+
+%++++++++++++++++++++++++++++++
+\subsection{Does quality-adjusting the factors of production or including energy
+            decrease the fitting residuals in a statistically-significant manner?} 
+\label{sec:quality_adj_energy_and_fitting_residual}
+%++++++++++++++++++++++++++++++
+
+The set of annual $\Delta r$ values for each combination of 
+country~(PT or UK), 
+model~(Cobb-Douglas or CES),
+flavor~(Unadjusted or Quality-adjusted), 
+energy~(with or without), and
+nest~[($kl$), ($kl$)$e$, ($le$)$k$, or ($ek$)$l$, for the CES models]
+can be assessed for statistical significance
+compared to zero by a t-test.
+The null hypothesis for the t-test is that the mean of each group is
+equal to zero, and 
+the alternative hypothesis is that the mean is less than zero.
+Smaller p-values indicate increasing confidence that the 
+mean is actually less than zero.
+Table~\ref{tab:Dr_p_values} summarizes the mean 
+and associated p-values values for $\Delta r$.
+%
+<<Dr_p_values, results="asis">>=
+# Calculate p values for groups of Dr values.
+Dr.t.values <- fitted_and_resid_data %>% 
+  group_by(Country, model, flavor, energy, nest) %>% 
+  summarize(Dr.mean = mean(Dr), Dr.p.value = stats::t.test(Dr, alternative = "less")[["p.value"]])
+Dr.t.values <- arrange(ungroup(Dr.t.values), Country, model, flavor, energy, nest)
+# Display the values in a table
+myXTable(Dr.t.values,
+         caption="Means and p-values for $\\Delta r$.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
+
+%++++++++++++++++++++++++++++++
 \subsection{Does quality-adjusting the factors of production 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Thoughts on the ``dynamic'' Solow residual}
+\label{sec:thoughts_dynamic_sr}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\ref{sec:dynamic_sr_CD} and \ref{sec:dynamic_sr_CES} derived expressions
+for a ``dynamic'' Solow residual 
+for Cobb-Douglas and CES production functions.
+However, these approaches conflate 
+stochastic error terms and the time-dependent contribution of ``technology'' 
+to economic growth
+in one variable~($\lambda_{i,j}$).
+In this appendix, we let the Solow residual 
+(expressed as time-independent $\lambda$)
+stand on its own and try to separate the stochastic and time-dependent
+aspects of the fitting residuals~($r_i$).
+Note: this section is speculative, and we need feedback from Marco and Randy 
+before moving ahead with a presentation or publication based on this work.
+
+We can re-state the models (in general) as
+%
+\begin{equation} \label{eq:general_y}
+  y_i = \hat{y}_i \epsilon_i
+\end{equation}
+%
+where $\epsilon_i$ is a multiplicative error term, 
+$\hat{y}_i$ is the predicted economic output, and
+$\hat{y}_i \equiv f(\theta, \lambda, \alpha, \beta, \gamma; \; t_i)$.
+(For the Cobb-Douglas model, $f = \theta A k^\alpha l^\beta e^\gamma$.)
+
+Taking the natural logarithm~($\ln$) of Equation~\ref{eq:general_y} yields
+%
+\begin{equation} \label{eq:ln_y}
+  \ln y_i = \ln \hat{y}_i + \ln \epsilon_i
+\end{equation}
+%
+which can be rearranged to show
+%
+\begin{equation} \label{eq:lny_prep_for_r}
+  \ln y_i - \ln \hat{y}_i = \ln \epsilon_i \; .
+\end{equation}
+%
+Using Equation~\ref{eq:log-residuals}, we can write
+%
+\begin{equation} \label{eq:r_epsilon}
+  r_i = \ln \epsilon_i \; .
+\end{equation}
+%
+Our concern is that the residuals may have a time-dependent component 
+and a stochastic component.
+To decompose, we can define
+%
+\begin{equation} \label{eq:epsilon_definition}
+  \epsilon_i = \mathrm{e}^{m(t_i - t_0)} \mathrm{e}^{\varepsilon_i^*} \; .
+\end{equation}
+%
+Substituting Equation~\ref{eq:epsilon_definition} into \ref{eq:r_epsilon} yields
+%
+\begin{equation} \label{eq:r_for_correlation}
+  r_i = m (t_i - t_0) + \varepsilon_i^* \; .
+\end{equation}
+%
+where
+$m$ is a slope and captures the linear (in natural logarithmic space), 
+time-dependent component of $r_i$. 
+$\varepsilon_i^*$ is a variable that captures a stochastic component of $\epsilon_i$.
+Equation~\ref{eq:r_for_correlation} can be fitted via linear regression in time~($t_i$).
+%
+\begin{equation} \label{eq:r_regression_eqn}
+  r_i = m (t_i - t_0) + b + \varepsilon_i^* \; .
+\end{equation}
+%
+In Equation~\ref{eq:r_regression_eqn},
+$b$ is the $y$-intercept of the regression and captures a time-independent offset of $r_i$,
+(Recall that $\epsilon_i$ is related to the fitting residuals~($r_i$)
+by Equation~\ref{eq:r_epsilon}.
+Thus, obtaining estimates of $m$ and $b$ and values for $\varepsilon_i^*$
+is equivalent to estimating the time-dependent, time-independent, and stochastic
+components, respectively, of the multiplicative errors~($\epsilon_i$).)
+This regression is equivalent to performing a linear fit to data in 
+Figures~\ref{fig:Graphs CD-resid}--\ref{fig:Graphs CESekl-resid}.
+
+For PT, Cobb-Douglas, unadjusted, without energy, we obtain the following:
+%
+<<residual_correlation, echo=TRUE>>=
+mod <- models$PT$unadjusted$noE$CD
+r_regression <- lm(formula = resid(mod) ~ mod$data$iYear)
+print(summary(r_regression))
+@
+%
+Note that the estimate for the coefficient in front of \texttt{mod\$data\$iYear}
+($m$ in Equation~\ref{eq:r_for_correlation})
+is incredibly small relative to the scale of the residuals~($r_i$),
+\Sexpr{coef(r_regression)[[2]]}, 
+indicating that there is little 
+linear time-dependent information in the residuals~($r_i$).
+This result is the same as saying that 
+the slope of a line fitted through the 
+PT, Unadjusted, Without energy data 
+in Figure~\ref{fig:Graphs CD-resid}
+is (effectively) zero.
+There is (effectively) no linear time trend in the residuals.
+
+Furthermore, the intercept ($b$ in Equation~\ref{eq:r_for_correlation})
+is very small relative to the scale of the residuals~($r_i$),
+\Sexpr{coef(r_regression)[[1]]}, 
+indicating that there is little time-independent information in the residuals~($r_i$).
+This result is the same as saying that the line fitted to the
+PT, Unadjusted, Without energy 
+data in Figure~\ref{fig:Graphs CD-resid}
+is nearly coincident with the $x$-axis.
+
+Almost all of the information in the residuals~($r_i$)
+is stochastic and captured by the $\varepsilon_i^*$ term.
+
+Perhaps Marco can help us interpret the rest of the
+output here (\texttt{F-statistic}, \texttt{p-value}, etc.).
+(An aside: what about fitting a quadratic curve,
+instead of a line, 
+through the $r_i$ values in Figure~\ref{fig:Graphs CD-resid}?)
+
+We can compare $r_i$ and $\varepsilon_i^*$, graphically,
+but the result is uninteresting. 
+We would expect $r_i$ and $\varepsilon_i^*$
+to be equal to each other, because
+(a) $m (t_i - t_0) \ll \max(r_i)$
+for any value of $t_i$
+and
+(b) $b \ll \max(r_i)$.
+Indeed, Figure~\ref{fig:Residuals_comparison}
+shows this is the case.
+%
+<<Residuals_comparison, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Comparison between $\\varepsilon_i^*$ and $r_i$">>=
+resids_comparison_df <- data.frame(list(iYear=mod$data$iYear, r=resid(mod), epsistar = resid(r_regression)))
+# resids_comparison_df <- melt(resids_comparison_df, measure.vars=c(r, epsistar), value.name="value", 
+#                              variable.name="name")
+ggplot(resids_comparison_df) + 
+  geom_point(mapping=aes(x=r, y=epsistar)) + 
+  xlab(expression(r[i])) +
+  ylab(expression(epsilon[i]^"*")) +
+  xy_theme()
+@
+%
+I'm not sure where this leaves us.
+Marco and I agreed that I would re-derive the ``dynamic'' Solow residual
+equation while properly including the multiplicative error term~($\epsilon_i$).
+I think I have done that, but the results aren't terribly interesting.
+There is little (linear) time-dependent~($m$) or 
+time-independent~($b$) 
+information in the residuals~($r_i$),
+as evidenced by Figures~\ref{fig:Graphs CD-resid}--\ref{fig:Graphs CESekl-resid}.
+
+Perhaps there is another direction in which I should go with this analysis?
+
 \end{document}

### 2015-06-11 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Updated narrative.

@@
 We expect that p-values will be large (close to unity), 
-because residuals are expected to be small (close to zero).
+because the mean of the residuals is expected to be small (close to zero).
 Indeed, that is the case.
@@
 for a ``dynamic'' Solow residual 
-for Cobb-Douglas and CES production functions.
+for Cobb-Douglas and CES production functions, respectively.
 However, these approaches conflate 
@@
 \begin{equation} \label{eq:ln_y}
-  \ln y_i = \ln \hat{y}_i + \ln \epsilon_i
+  \ln y_i = \ln \hat{y}_i + \ln \epsilon_i \; ,
 \end{equation}
@@
 %
-Our concern is that the residuals may have a time-dependent component 
-and a stochastic component.
+Our concern is that the residuals~($r_i$) may have a time-dependent component 
+in addition to a stochastic component.
 To decompose, we can define
@@
 $\varepsilon_i^*$ is a variable that captures a stochastic component of $\epsilon_i$.
-Equation~\ref{eq:r_for_correlation} can be fitted via linear regression in time~($t_i$).
+Equation~\ref{eq:r_for_correlation} can be fitted via linear regression in time~($t_i$) as
 %
@@
 In Equation~\ref{eq:r_regression_eqn},
-$b$ is the $y$-intercept of the regression and captures a time-independent offset of $r_i$,
-(Recall that $\epsilon_i$ is related to the fitting residuals~($r_i$)
+$b$ is the $y$-intercept of the regression and captures a time-independent offset of $r_i$.
+Recall that $\epsilon_i$ is related to the fitting residuals~($r_i$)
 by Equation~\ref{eq:r_epsilon}.
@@
 is equivalent to estimating the time-dependent, time-independent, and stochastic
-components, respectively, of the multiplicative errors~($\epsilon_i$).)
+components, respectively, of the multiplicative errors~($\epsilon_i$).
 This regression is equivalent to performing a linear fit to data in 
@@
 We would expect $r_i$ and $\varepsilon_i^*$
-to be equal to each other, because
+to be equal to each other by Equation~\ref{eq:r_regression_eqn}, 
+because
 (a) $m (t_i - t_0) \ll \max(r_i)$

### 2015-06-12 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Now including percentages for delta lambda.

@@
 # Calculate differences relative to the unadjusted, no-energy condition
-AllCoeffs <- mutate(AllCoeffs, Dlambda = abs(lambda) - abs(lambda_unadj_noE), Dmse = mse - mse_unadj_noE)
+AllCoeffs <- mutate(AllCoeffs, Dlambda = abs(lambda) - abs(lambda_unadj_noE), 
+                    Dmse = mse - mse_unadj_noE,
+                    percDlambda = Dlambda / abs(lambda_unadj_noE) * 100)
 
@@
 where~$N$ is the number of years of data.
-When $\Delta \lambda$ and $\Delta mse$ are negative, 
-we observe reduction in the Solow residual ($\lambda$) and
+On a percentage basis,
+%
+\begin{equation} \label{eq:delta_lambda_perc}
+  \Delta \lambda \, [\%] = \frac{100 \, \Delta \lambda}{\left| \lambda_{Unadjusted, \, Without \, energy} \right|} 
+            = \frac{100 \, \left| \lambda \right|}{\left| \lambda_{Unadjusted, \, Without \, energy} \right|} - 1
+\end{equation}
+%
+When $\Delta \lambda$, $\Delta \lambda \, [\%]$, or $\Delta mse$ are negative, 
+we observe reduction in the Solow residual ($\lambda$) or
 the fitting residuals ($mse$)
@@
 %
-<<DSRmse_CD_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta mse$) for the Cobb-Douglas model relative to the unadjusted, no-energy condition.">>=
+<<DSRmse_CD_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta mse$) for the Cobb-Douglas model relative to the Unadjusted, Without energy condition.">>=
 ggplot(data=filter(AllCoeffs, model=="CD")) +
@@
 %
+<<percDSRmse_CD_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Percentage change in Solow Residuals~($\\Delta\\lambda \\, [\\%]$) and mean squared error~($\\Delta mse$) for the Cobb-Douglas model relative to the Unadjusted, Without energy condition.">>=
+ggplot(data=filter(AllCoeffs, model=="CD")) +
+  geom_point(mapping=aes(x=Dmse, y=percDlambda, color = energy)) +
+  facet_grid(Country ~ flavor) +
+  xlab(expression(Delta * mse)) + 
+  ylab(expression(paste(Delta * lambda, " [%]"))) +
+  scale_y_continuous(breaks=c(-50, 0, 50, 100)) +
+  xy_theme() + 
+  theme(legend.title=element_blank())
+@
+%
 Figure~\ref{fig:DSRmse_CES_graph} summarizes the data for the CES models.
 %
-<<DSRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta mse$) for the Cobb-Douglas model relative to the unadjusted, no-energy condition.">>=
+<<DSRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta mse$) for the CES modles relative to the Unadjusted, Without energy condition.">>=
 ggplot(data=filter(AllCoeffs, model=="CES")) +
@@
   ylab(expression(Delta * lambda)) +
+  xy_theme() +
+  theme(legend.title=element_blank())
+@
+%
+<<percDSRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Percentage change in Solow Residuals~($\\Delta\\lambda \\, [\\%]$) and mean squared error~($\\Delta mse$) for the CES modles relative to the Unadjusted, Without energy condition.">>=
+ggplot(data=filter(AllCoeffs, model=="CES")) +
+  geom_point(mapping=aes(x=Dmse, y=percDlambda, color = energy, shape=nest)) +
+  facet_grid(Country ~ flavor) +
+  xlab(expression(Delta * mse)) + 
+  ylab(expression(paste(Delta * lambda, " [%]"))) +
+  scale_y_continuous(breaks=c(-50, -25, 0, 25)) +  
   xy_theme() +

### 2015-06-15 Workflow/Workflow.Rmd
Added a section on dowloading to Matt's laptop.
Additional text on resampline results.

@@
 As a consequence, `loadPostProcessedData` returns an object which must be assigned to a variable in `R`.
+
+### 
+* If Randy has run the analysis, resampling results can be placed in `/home/rpruim/Share`. 
+* To download resampling results to his laptop, Matt can say, for example, `scp -P 22122 mkh2@dahl.calvin.edu:/home/rpruim/Share/2015-06-11-run/data_resample/Calvin/* ~/github/Econ-Growth-R-Analysis/data_resample/Calvin`

### 2015-06-16 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
New section comparing Marco and Calvin CES models.

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Marco/Matt coefficient comparison}
+\label{sec:marco_matt_coeff_comp}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+<<Comparison, echo=TRUE>>=
+# Marco's coefficients for PT, CES, unadjusted, without energy
+gamma_marco <- 1.0306
+lambda_marco <- 0.0055
+delta_1_marco <- 0.9844
+rho_1_marco <- 3.4647
+
+# Generate a predicted GDP from a CES model with the above parameters
+form <- formulas$PT$unadjusted
+form <- keep_summands(form, n = -3) # Remove energy
+form
+y_hat_marco <- cesCalc(xNames = c(summands(form, n=1), summands(form, n=2)), 
+                       data = historicalData$PT, 
+                       coef = c(gamma=gamma_marco,
+                                lambda=lambda_marco,
+                                delta=delta_1_marco,
+                                rho=rho_1_marco),
+                       tName = summands(form, n=3))
+sse_marco <- sum((historicalData$PT$iGDP - y_hat_marco)^2, na.rm=TRUE)
+sse_marco # Marco reported 0.6625
+
+# Now do the same thing with Matt's parameters
+y <- historicalData$PT$iGDP
+coeffs_matt <- naturalCoef(models$PT$unadjusted$noE$CES$kl) 
+coeffs_matt
+y_hat_matt <- cesCalc(xNames = c(summands(form, n=1), summands(form, n=2)), 
+                      data = historicalData$PT, 
+                      coef = c(gamma=coeffs_matt$gamma,
+                               lambda=coeffs_matt$lambda,
+                               delta=coeffs_matt$delta_1,
+                               rho=coeffs_matt$rho_1),
+                      tName = summands(form, n=3))
+sse_matt <- sum((y - y_hat_matt)^2, na.rm=TRUE)
+sse_matt
+
+# Get the SSE from the model itself. This is in log space.
+r <- resid(models$PT$unadjusted$noE$CES$kl)
+sse_matt_log <- sum(r^2)
+sse_matt_log # Isn't what we want.
+
+# Convert to linear space
+y <- y[!is.na(y)] # removes NA values at end of time series
+y_hat <- y / exp(resid(models$PT$unadjusted$noE$CES$kl))
+sse_matt_lin <- sum((y - y_hat)^2)
+sse_matt_lin
+@
+
 \end{document}

### 2015-06-17 Articles/Presentation_ESEE_2015/Other results/Marco CES results/Comparison--Matt-and-Marco.Rmd
New file for comparing Matt and Marco's fitters.

---
title: "Comparison of Fitting Algorithms"
author: "MK Heun"
date: "17 June 2015"
output: pdf_document
---

```{r, echo=FALSE, include=FALSE}
require(EconData)
require(EconModels)
require(dplyr)
```

This document compares Marco's results to Matt's results
for fitting the CES model for Portugal, Without energy, and
with Unadjusted factors of production.

First, some setup code.

```{r setup}
formulas <- 
  list( 
    PT = c(unadjusted = build_formula("iGDP", list("iKstkS.L", "iL", "iXpMP", "iYear")),
             adjusted = build_formula("iGDP", list("iKservS.L", "ihLest", "iUMP", "iYear"))),
    UK = c(unadjusted = build_formula("iGDP", list("iKstkO.WwithRD", "iL", "iXp", "iYear")),
             adjusted = build_formula("iGDP", list("iKservO.WwithRD", "ihLest", "iU", "iYear")))
  )
historicalData <- list()
commonVars <- c("Year", "Country", "Source")
historicalData$PT <- filter(IST, Country == "PT") 
historicalData$PT <- historicalData$PT[ , unique(c(commonVars,
                                                   all.vars(formulas$PT$unadjusted), 
                                                   all.vars(formulas$PT$adjusted)))]
historicalData$UK <- filter(Leeds, Country == "UK")
historicalData$UK <- historicalData$UK[ , unique(c(commonVars,
                                                   all.vars(formulas$UK$unadjusted), 
                                                   all.vars(formulas$UK$adjusted)))]
# Remove energy to create the formula we'll use for fitting below
form <- keep_summands(formulas$PT$unadjusted, n = -3) 
form
```

# Additive Errors

Marco reports the following results from his CES fitter:

```{r Marcos results}
# Marco's coefficients for PT, CES, unadjusted, without energy
gamma_marco <- 1.0306
lambda_marco <- 0.0055
delta_1_marco <- 0.9844
rho_1_marco <- 3.4647
sse_marco <- 0.6625
```

I'll first try to reproduce Marco's results 
using additive errors, as opposed to multiplicative errors (`multErr = FALSE`),
with unconstrained fitting (`constrained = FALSE`) and
no boundary models (`fitBoundaries = FALSE`).
Setting `fitBoundaries = FALSE`
turns off boundary model fitting.
Setting `constrained = FALSE` turns off the typical constraints on parameters,
which are
$0 \le \gamma < \infty$, $0 \le \delta,\delta_1 \le 1$, and $-1 \le \rho,\rho_1 < \infty$.
Note that $\gamma$ is the pre-multiplier in the CES equation,
not the coefficient for energy.

```{r Reproduce Marcos results}
mod_unconstrained <- cesModel(form, data = historicalData$PT, multErr = FALSE,
                              constrained = FALSE, fitBoundaries = FALSE,
                              algorithms = "PORT")
naturalCoef(mod_unconstrained)
sum(resid(mod_unconstrained)^2)
```

Although these results are not *exactly* identical to Marco's,
they are very close.
Thus, I think we have found the assumptions that Marco's fitter used.
Furthermore, we have confirmed that our fitters produce (nearly) identical
results for models that assume additive errors and unconstrained fitting.

[//]: (Next, let's try a fit using additive errors using our algorithms
with our constrained fitting approach.)

```{r, eval=FALSE, include=FALSE}
mod_additive <- cesModel(form, data=historicalData$PT, multErr = FALSE,
                         constrained = TRUE, fitBoundaries = TRUE,
                         algorithms = "PORT")
naturalCoef(mod_additive)
sum(resid(mod_additive)^2)
```

[//]: (We are able to find a better fit, i.e., one with smaller *sse*.
Note that this "better" solution is on a boundary,
namely where `delta_1 = 1`.
Marco's fit is at `delta_1 = 0.9844`, close but not exactly on the boundary.)

# Multiplicative Errors

We (at Calvin) usually fit using multiplicative errors as follows:

```{r}
# Fit using cesModel with multiplicative errors by setting multErr=TRUE (the default)
mod_mult <- cesModel(form, data=historicalData$PT, multErr = TRUE,
                     constrained = TRUE, fitBoundaries = TRUE)
naturalCoef(mod_mult)
sum(resid(mod_mult)^2)
```

Because the errors (and their assumed form) are an integral part of the model,
the fitted coefficients are a function of the type of errors assumed
(multiplicative or additive).
At this time, I don't have results from Marco's software
when fitting with multiplicative errors.
Thus, it is not possible to compare results 
when fitting assuming multiplicative.

Furthermore, it is inappropriate to try to calculate an `additive error sse` from the
multiplicative error model to compare against the `sse` from an additive error model.
When you switch from additive to multiplicative errors, 
the values of your fitted coefficients will necessarily change.
Calculating an additive `sse` from multiplicative coefficients is like comparing
apples to oranges.

The next step on this comparison process will be for Marco to run his fitter
using multiplicative errors, if that is possible.
After doing so, we can compare `sse` values and coefficients.
If things work as well for the multiplicative error models as for
the additive error models, we'll find the exact same results for both
Marco's and my multiplicative models.

### 2015-06-18 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Moved fitter comparison to its own file.
Parameter estimating for CST models.

--- 2015-06-12 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Parameter Estimation}
-\label{sec:parameter_estimation}
+\section{Parameter Estimation (Without Cost-share Theorem)}
+\label{sec:parameter_estimation_noCST}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 <<Models>>=
-fileName <- "ESEE2015Models.Rdata"
+fileName <- "ESEE2015Models.rds"
+fileNameCST <- "EESE2015ModelsCST.rds"
 if (!rerunModels){
   # load from the file on disk
-  load(fileName)
+  models <- readRDS(fileName)
+  modelsCST <- readRDS(fileNameCST)
 } else {
@@
   # In RStudio, be sure to set the working directory to the source file directory.
+
+  #
+  # Models that adhere to the cost-share theorem
+  #
+
+  modelsCST <- list()
+  # Output elasticities based on cost share theorem
+  alphaCST <- 0.3 # Fraction of national accounts spent on capital
+  betaCST <- 0.7 # Fraction of national accounts spent on labor
+  for (country in countries){
+    form <- formulas[[country]][["unadjusted"]]
+    form <- keep_summands(form, n=-3) # Remove energy
+    yVar <- as.name(summands(form, n=1, right=FALSE))
+    kVar <- as.name(summands(form, n=1))
+    lVar <- as.name(summands(form, n=2))
+    tVar <- as.name(summands(form, n=3))
+    mod <- lm(log(eval(yVar)) - alpha_CST*log(eval(kVar)) - beta_CST*log(eval(lVar)) ~ eval(tVar), 
+              data = historicalData[[country]])
+    attr(mod, "naturalCoeffs") <- c(lambda=coef(mod)[[2]],
+                                    logscale=coef(mod)[[1]], 
+                                    scale=exp(coef(mod)[[1]]),
+                                    alpha_1=alphaCST,
+                                    alpha_2=betaCST, 
+                                    alpha_3=0)
+    modelsCST[[country]][["unadjusted"]][["noE"]][["CD"]] <- mod
+  }
+
+  # Save cost-share theorem models to disk.
+  saveRDS(modelsCST, file=fileNameCST)
+
+  #
+  # Models where all parameters are estimated
+  #
 
@@
                                                                         nest=c(1,2))
+      nestsWithE <- list(kle=c(1,2,3), lek=c(2,3,1), ekl=c(3,1,2))
       models[[country]][[flavor]][["withE"]][["CES"]] <- 
-        lapply(nests, function(nest){
+        lapply(nestsWithE, function(nest){
           cesModel(formula=fwithE, data=historicalData[[country]], nest=nest)
@@
   # Save models to disk.
-  save(models, file=fileName)
+  saveRDS(models, file=fileName)
 }

### 2015-06-18 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Now including CST models.

@@
   for (country in countries){
-    form <- formulas[[country]][["unadjusted"]]
-    form <- keep_summands(form, n=-3) # Remove energy
+    form <- keep_summands(formulas[[country]][["unadjusted"]], n=-3) # Remove energy
     yVar <- as.name(summands(form, n=1, right=FALSE))
@@
     tVar <- as.name(summands(form, n=3))
-    mod <- lm(log(eval(yVar)) - alpha_CST*log(eval(kVar)) - beta_CST*log(eval(lVar)) ~ eval(tVar), 
+    # Cobb-Douglas
+    cdModCST <- lm(log(eval(yVar)) - alphaCST*log(eval(kVar)) - betaCST*log(eval(lVar)) ~ eval(tVar), 
                    data = historicalData[[country]])
-    attr(mod, "naturalCoeffs") <- c(lambda=coef(mod)[[2]],
-                                    logscale=coef(mod)[[1]], 
-                                    scale=exp(coef(mod)[[1]]),
+    attr(cdModCST, "naturalCoeffs") <- data.frame(lambda=coef(cdModCST)[[2]],
+                                                  logscale=coef(cdModCST)[[1]], 
+                                                  scale=exp(coef(cdModCST)[[1]]),
                                                   alpha_1=alphaCST,
@@
                                                   alpha_3=0)
-    modelsCST[[country]][["unadjusted"]][["noE"]][["CD"]] <- mod
+    modelsCST[[country]][["unadjusted"]][["noE"]][["CD"]] <- cdModCST
+    # CES
+    cesModCST <- plm(log(eval(yVar) / (alphaCST*eval(kVar)^(-rho_1) + betaCST*eval(lVar)^(-rho_1))^(-1/rho_1)) ~ eval(tVar),
+                     data = historicalData[[country]],
+                     params=c(rho_1=0.8))
+    names(cesModCST$coefficients) <- c("logscale", "lambda", "rho_1")
+    cesModCST$coefficients <- c(coef(cesModCST), c(delta_1=alphaCST, delta=1))
+    attr(cesModCST, "naturalCoeffs") <- EconModels:::makeNatCoef(cesModCST)
+    modelsCST[[country]][["unadjusted"]][["noE"]][["CES"]][["kl"]] <- cesModCST
   }
@@
   #
-  # Models where all parameters are estimated
+  # Models where all parameters are estimated (models don't adhere to the cost share theorem)
   #
@@
 }
-# Put all the coefficients into a data frame
-AllCoeffs <- leaf_apply(models, class = c("CDEmodel", "cesModel", "LINEXmodel"), f = function(mod, id){
+# Put all the cost-share theorem (CST) coefficients into a data frame
+AllCoeffsCST <- leaf_apply(modelsCST, class = c("lm"), f = function(modCST, id){
   # Parse the id to find out whether this is quality-adjusted data, etc.
   id_list <- strsplit(id, split = "[.]")[[1]]
-  Country <- id_list[[1]]
-  flavor <- id_list[[2]]
-  energy <- id_list[[3]]
-  model <- id_list[[4]]
-  nest <- if(length(id_list) > 4) id_list[[5]] else NA
-  res <- rbind(list(Country = Country, 
-                    flavor = if (flavor=="unadjusted") "Unadjusted" else "Quality-adjusted",
-                    energy = if (energy=="noE") "Without energy" else "With energy",
-                    model=model, 
-                    nest=nest))
-  coeffs <- naturalCoef(mod)
-  res <- cbind(res, coeffs)
+  res <- rbind(list(Country = id_list[[1]], 
+                    flavor = if (id_list[[2]]=="unadjusted") "Unadjusted" else "Quality-adjusted",
+                    energy = if (id_list[[3]]=="noE") "Without energy" else "With energy",
+                    model=id_list[[4]], 
+                    nest=if(length(id_list) > 4) id_list[[5]] else NA,
+                    cst=TRUE))
+  res <- cbind(res, naturalCoef(modCST))
+  # Now calculate the mean squared error (mse) for each model.
+  sqResids <- resid(modCST)^2
+  mse <- sum(sqResids)/(length(sqResids))
+  res <- cbind(res, list(mse=mse))
+  return(res)
+}) %>% do.call(plyr::rbind.fill, .)
+
+AllCoeffsNoCST <- leaf_apply(models, class = c("CDEmodel", "cesModel", "LINEXmodel"), f = function(mod, id){
+  # Parse the id to find out whether this is quality-adjusted data, etc.
+  id_list <- strsplit(id, split = "[.]")[[1]]
+  res <- rbind(list(Country = id_list[[1]], 
+                    flavor = if (id_list[[2]]=="unadjusted") "Unadjusted" else "Quality-adjusted",
+                    energy = if (id_list[[3]]=="noE") "Without energy" else "With energy",
+                    model=id_list[[4]], 
+                    nest=if(length(id_list) > 4) id_list[[5]] else NA,
+                    cst=FALSE))
+  res <- cbind(res, naturalCoef(mod))
   # Now calculate the mean squared error (mse) for each model.
@@
 }) %>% do.call(plyr::rbind.fill, .)
-# Get the unadjusted, no-energy values for mse and lambda and place them on each appropriate row
-AllCoeffs_unadj_noE <- filter(AllCoeffs, flavor=="Unadjusted", energy=="Without energy") %>% 
+AllCoeffs <- plyr::rbind.fill(AllCoeffsCST, AllCoeffsNoCST)
+# Get reference values for lambda and sse.
+ref <- filter(AllCoeffs, cst==TRUE & flavor=="Unadjusted" & energy=="Without energy") %>% 
               select(Country, flavor, energy, model, nest, mse, lambda)
-colnames(AllCoeffs_unadj_noE)[colnames(AllCoeffs_unadj_noE)=="mse"] <- "mse_unadj_noE"
-colnames(AllCoeffs_unadj_noE)[colnames(AllCoeffs_unadj_noE)=="lambda"] <- "lambda_unadj_noE"
-AllCoeffs <- merge(AllCoeffs, AllCoeffs_unadj_noE[c("Country", "model", "mse_unadj_noE", "lambda_unadj_noE")])
+
+colnames(ref)[colnames(ref)=="mse"] <- "mse_ref"
+colnames(ref)[colnames(ref)=="lambda"] <- "lambda_ref"
+AllCoeffs <- merge(AllCoeffs, ref[c("Country", "model", "mse_ref", "lambda_ref")])
 # Calculate differences relative to the unadjusted, no-energy condition
-AllCoeffs <- mutate(AllCoeffs, Dlambda = abs(lambda) - abs(lambda_unadj_noE), 
-                    Dmse = mse - mse_unadj_noE,
-                    percDlambda = Dlambda / abs(lambda_unadj_noE) * 100)
+AllCoeffs <- mutate(AllCoeffs, Dlambda = abs(lambda) - abs(lambda_ref), 
+                    Dmse = mse - mse_ref,
+                    percDlambda = Dlambda / abs(lambda_ref) * 100)
 
@@
 AllCoeffs$nest <- relevelFactor(as.factor(unlist(AllCoeffs$nest)), c("kl", "kle", "lek", "ekl"))
+AllCoeffs$cst <- relevelFactor(as.factor(unlist(AllCoeffs$cst)), c("TRUE", "FALSE"))
 # Rearrange for easier viewing
-AllCoeffs <- arrange(AllCoeffs, Country, model, flavor, energy, nest)
+AllCoeffs <- arrange(AllCoeffs, Country, model, flavor, energy, nest, cst)
 @

### 2015-06-19 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Now using CST models as the basis of comparison

@@
 )
+
+# This function is used in many places below.
+myXTable <- function(data, caption, label, digits=2){
+  table <- xtable(data, caption=caption, label=label, digits=digits)
+  print(table, 
+        caption.placement="top", 
+        size="\\tiny", 
+        include.rownames=FALSE, 
+        math.style.negative=TRUE)
+}
 @
@@
 %++++++++++++++++++++++++++++++
+\subsection{Does rejecting the cost-share theorem 
+            decrease the mean squared error and/or the Solow residual?} 
+\label{sec:cst_and_solow_residual}
+%++++++++++++++++++++++++++++++
+
+Our hypothesis is that rejecting the cost-share theorem~(CST) will decrease
+both mean squared error~($mse$) and
+the Solow residual~($\lambda$).
+The mean squared error~($mse$) is expected to decrease 
+because rejecting the CST adds one or more fitting parameters
+to the model.
+The Solow residual~($\lambda$) is expected to decrease 
+because the factor shares for capital~($\alpha_1$) and labor~($\alpha_2 = 1 - \alpha_1$)
+are free to float, 
+allowing each factor of production 
+to contribute optimally toward production and
+bringing the model's prediction for economic output closer to 
+historical output. 
+In so doing, we expect less ``unexplained'' economic growth 
+and a decreased Solow residual~($\lambda$).
+
+Table~\ref{tab:Effect_of_CST_CD} shows the effect of the CST 
+on fitted parameters for the Cobb-Douglas model.
+%
+<<Effect_of_CST_CD, results="asis">>=
+myXTable(filter(AllCoeffs, model=="CD" & flavor=="Unadjusted" & energy=="Without energy") %>% 
+           select(Country, cst, scale, lambda, alpha_1, alpha_2, mse),
+         caption="Model parameters for Cobb-Douglas models with unadjusted factors of production, without energy.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
+%
+Table~\ref{tab:Effect_of_CST_CES} shows the effect of the CST 
+on fitted parameters for the CES model.
+%
+<<Effect_of_CST_CES, results="asis">>=
+myXTable(filter(AllCoeffs, model=="CES" & flavor=="Unadjusted" & energy=="Without energy") %>% 
+           select(Country, cst, gamma, lambda, alpha_1, alpha_2, sigma_1, mse),
+         caption="Model parameters for CES models with unadjusted factors of production, without energy.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
+%
+For both Cobb-Douglas and CES, rejecting the Cost Share Theorem yields
+decreased mean squared error~($mse$) and
+smaller Solow residual ($\lambda$, on an absolute-value basis),
+as expected.
+
+***************
+
+Note that in Table~\ref{tab:Effect_of_CST_CES}, we see $\sigma_1 = 0.5$ 
+for UK when the cost share theorem is rejected. 
+This even-numbered result is coming from the grid search in $\rho_1$. 
+For an unknown reason, the gradient search from the best grid search point
+fails.
+I will investigate.
+
+This result means that we have found a set of fitting coefficients
+for this situation 
+that is \emph{close} to providing the minimum possible $mse$,
+but it may not be the \emph{exact} minimum.
+Regardless, the point above (that $mse$ and $\lambda$ always decrease 
+when rejecting the cost share theorem) remains valid.
+Investigating and fixing this problem
+will only serve to \emph{further} reduce $mse$ and $\lambda$ 
+from the values reported in Table~\ref{tab:Effect_of_CST_CES}.
+
+************
+
+%++++++++++++++++++++++++++++++
 \subsection{Does quality-adjusting the factors of production 
@@
 
-We can test our hypothesis that quality-adjusting the factors of production
+We can test our hypothesis that 
+quality-adjusting the factors of production
 and including energy will both reduce the Solow residuals~($\lambda$)
 and improve the fit to historical data
-(thereby, reducing the fitting residuals, $r_i$)
+(thereby reducing the fitting residuals, $r_i$, and mean squared error, $mse$)
 by calculating 
@@
 \begin{equation} \label{eq:delta_lambda}
-  \Delta \lambda \equiv \left| \lambda \right| - \left| \lambda_{Unadjusted, \, Without \, energy} \right|
+  \Delta \lambda \equiv \left| \lambda \right| - \left| \lambda_{Unadjusted, \, Without \, energy, \, CST} \right|
 \end{equation}
@@
 \begin{equation} \label{eq:delta_mse}
-  \Delta mse \equiv mse - mse_{Unadjusted, \, Without \, energy}.
+  \Delta mse \equiv mse - mse_{Unadjusted, \, Without \, energy, \, CST}.
 \end{equation}
@@
 \begin{equation} \label{eq:delta_lambda_perc}
-  \Delta \lambda \, [\%] = \frac{100 \, \Delta \lambda}{\left| \lambda_{Unadjusted, \, Without \, energy} \right|} 
-            = \frac{100 \, \left| \lambda \right|}{\left| \lambda_{Unadjusted, \, Without \, energy} \right|} - 1
+  \Delta \lambda \, [\%] = \frac{100 \, \Delta \lambda}{\left| \lambda_{Unadjusted, \, Without \, energy, \, CST} \right|} 
+            = \frac{100 \, \left| \lambda \right|}{\left| \lambda_{Unadjusted, \, Without \, energy, \, CST} \right|} - 1
 \end{equation}
@@
 %
-<<MyXTableFunction>>=
-myXTable <- function(data, caption, label, digits=2){
-  table <- xtable(data, caption=caption, label=label, digits=digits)
-  print(table, 
-        caption.placement="top", 
-        size="\\tiny", 
-        include.rownames=FALSE, 
-        math.style.negative=TRUE)
-}
-@
-%
 <<DSRmse_CD, results="asis">>=
-myXTable(filter(AllCoeffs, model=="CD") %>% select(Country, model, flavor, energy, Dlambda, Dmse),
+myXTable(filter(AllCoeffs, model=="CD") %>% select(Country, model, flavor, energy, cst, Dlambda, Dmse),
          caption="$\\Delta \\lambda$ and $\\Delta mse$ for Cobb-Douglas models.",
@@
 myXTable(filter(AllCoeffs, model=="CES" & (nest=="kl" | nest=="kle")) %>% 
-           select(Country, model, flavor, energy, nest, Dlambda, Dmse),
+           select(Country, model, flavor, energy, nest, cst, Dlambda, Dmse),
          caption="$\\Delta \\lambda$ and $\\Delta mse$ for CES models with ($kl$)$e$ nesting.",
@@
 myXTable(filter(AllCoeffs, model=="CES" & (nest=="kl" | nest=="lek")) %>% 
-           select(Country, model, flavor, energy, nest, Dlambda, Dmse),
+           select(Country, model, flavor, energy, nest, cst, Dlambda, Dmse),
          caption="$\\Delta \\lambda$ and $\\Delta mse$ for CES models with ($le$)$k$ nesting.",
@@
 myXTable(filter(AllCoeffs, model=="CES" & (nest=="kl" | nest=="ekl")) %>% 
-           select(Country, model, flavor, energy, nest, Dlambda, Dmse),
+           select(Country, model, flavor, energy, nest, cst, Dlambda, Dmse),
          caption="$\\Delta \\lambda$ and $\\Delta mse$ for CES models with ($ek$)$l$ nesting.",
@@
 %
-<<DSRmse_CD_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta mse$) for the Cobb-Douglas model relative to the Unadjusted, Without energy condition.">>=
-ggplot(data=filter(AllCoeffs, model=="CD")) +
-  geom_point(mapping=aes(x=Dmse, y=Dlambda, color = energy)) +
+<<DSRmse_CD_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta mse$) for the Cobb-Douglas model relative to the Unadjusted, Without energy, CST case.">>=
+ggplot() +
+  geom_point(data=filter(AllCoeffs, cst==FALSE & model=="CD"), mapping=aes(x=Dmse, y=Dlambda, color=energy)) +
+  scale_shape(solid=FALSE) +
+  guides(shape=FALSE) +
+  geom_point(data=filter(AllCoeffs, cst==TRUE & model=="CD"), mapping=aes(x=Dmse, y=Dlambda, color=energy, shape=cst)) +
   facet_grid(Country ~ flavor) +
   xlab(expression(Delta * mse)) + 
+  scale_x_continuous(breaks=seq(-0.005, 0, 0.005)) +  
   ylab(expression(Delta * lambda)) +
@@
 %
-<<percDSRmse_CD_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Percentage change in Solow Residuals~($\\Delta\\lambda \\, [\\%]$) and mean squared error~($\\Delta mse$) for the Cobb-Douglas model relative to the Unadjusted, Without energy condition.">>=
-ggplot(data=filter(AllCoeffs, model=="CD")) +
-  geom_point(mapping=aes(x=Dmse, y=percDlambda, color = energy)) +
+<<percDSRmse_CD_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Percentage change in Solow Residuals~($\\Delta\\lambda \\, [\\%]$) and mean squared error~($\\Delta mse$) for the Cobb-Douglas model relative to the Unadjusted, Without energy, CST case.">>=
+ggplot() +
+  geom_point(data=filter(AllCoeffs, cst==FALSE & model=="CD"), mapping=aes(x=Dmse, y=percDlambda, color=energy)) +
+  scale_shape(solid=FALSE) +
+  guides(shape=FALSE) +
+  geom_point(data=filter(AllCoeffs, cst==TRUE & model=="CD"), mapping=aes(x=Dmse, y=percDlambda, color=energy, shape=cst)) +
   facet_grid(Country ~ flavor) +
   xlab(expression(Delta * mse)) + 
+  scale_x_continuous(breaks=seq(-0.005, 0, 0.005)) +  
   ylab(expression(paste(Delta * lambda, " [%]"))) +
-  scale_y_continuous(breaks=c(-50, 0, 50, 100)) +
+  scale_y_continuous(breaks=seq(-75, 25, 25)) +  
   xy_theme() + 
@@
 %
-<<DSRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta mse$) for the CES modles relative to the Unadjusted, Without energy condition.">>=
+<<DSRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta mse$) for the CES modles relative to the Unadjusted, Without energy, CST case.">>=
 ggplot(data=filter(AllCoeffs, model=="CES")) +
-  geom_point(mapping=aes(x=Dmse, y=Dlambda, color = energy, shape=nest)) +
+  geom_point(mapping=aes(x=Dmse, y=Dlambda, color=energy, shape=nest)) +
   facet_grid(Country ~ flavor) +
   xlab(expression(Delta * mse)) + 
+  scale_x_continuous(breaks=seq(-0.005, 0, 0.005)) +  
   ylab(expression(Delta * lambda)) +
@@
 %
-<<percDSRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Percentage change in Solow Residuals~($\\Delta\\lambda \\, [\\%]$) and mean squared error~($\\Delta mse$) for the CES modles relative to the Unadjusted, Without energy condition.">>=
+<<percDSRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Percentage change in Solow Residuals~($\\Delta\\lambda \\, [\\%]$) and mean squared error~($\\Delta mse$) for the CES modles relative to the Unadjusted, Without energy, CST case.">>=
 ggplot(data=filter(AllCoeffs, model=="CES")) +
-  geom_point(mapping=aes(x=Dmse, y=percDlambda, color = energy, shape=nest)) +
+  geom_point(mapping=aes(x=Dmse, y=percDlambda, color=energy, shape=nest)) +
   facet_grid(Country ~ flavor) +
   xlab(expression(Delta * mse)) + 
+  scale_x_continuous(breaks=seq(-0.005, 0, 0.005)) +  
   ylab(expression(paste(Delta * lambda, " [%]"))) +
-  scale_y_continuous(breaks=c(-50, -25, 0, 25)) +  
+  scale_y_continuous(breaks=seq(-75, 25, 25)) +  
   xy_theme() +

### 2015-06-19 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Now adding additional tables of results.

@@
 the fitting residuals ($mse$)
-relative to the unadjusted, no-energy condition.
-
-Table~\ref{tab:DSRmse_CD} shows the results for the Cobb-Douglas models.
+relative to the unadjusted, no-energy, CST case.
+
+To calculate $\Delta \lambda$ and $\Delta mse$, we need to fit all combinations of 
+country, model, flavor, energy, nest, and CST.
+Table~\ref{tab:CD_coeffs} shows coefficients for all fitted Cobb-Douglas models.
+%
+<<CD_coeffs, results="asis">>=
+myXTable(filter(AllCoeffs, model=="CD") %>% 
+           select(Country, flavor, energy, cst, scale, lambda, alpha_1, alpha_2, alpha_3, mse),
+         caption="Model parameters for all Cobb-Douglas models.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
+%
+Tables~\ref{tab:CES_coeffs} and~\ref{tab:CES_coeffs_sigmas} show 
+coefficients for all fitted CES models.
+%
+<<CES_coeffs, results="asis">>=
+myXTable(filter(AllCoeffs, model=="CES") %>% 
+           select(Country, flavor, energy, nest, cst, gamma, lambda, alpha_1, alpha_2, alpha_3),
+         caption="Model parameters for all CES models.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
+%
+<<CES_coeffs_sigmas, results="asis">>=
+myXTable(filter(AllCoeffs, model=="CES") %>% 
+           select(Country, flavor, energy, nest, cst, sigma_1, sigma, mse),
+         caption="Model parameters for all CES models.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
+%
+Table~\ref{tab:DSRmse_CD} shows $\Delta \lambda$ and $\Delta mse$ results for the Cobb-Douglas models.
 %
@@
 % 
-Tables~\ref{tab:DSRmse_CESkle}--\ref{tab:DSRmse_CESekl} show results 
-for CES models with various nestings.
+Tables~\ref{tab:DSRmse_CESkle}--\ref{tab:DSRmse_CESekl} show $\Delta \lambda$ and $\Delta mse$ 
+results for CES models with various nestings.
 %
@@
 %
-Figure~\ref{fig:DSRmse_CD_graph} summarizes the data for the Cobb-Douglas model.
+Figures~\ref{fig:DSRmse_CD_graph} and~\ref{fig:percDSRmse_CD_graph} summarize 
+$\Delta \lambda$ and $\Delta mse$ 
+results for the Cobb-Douglas model.
 %
@@
 %
-Figure~\ref{fig:DSRmse_CES_graph} summarizes the data for the CES models.
+Figures~\ref{fig:DSRmse_CES_graph} and~\ref{fig:percDSRmse_CES_graph} summarize 
+$\Delta \lambda$ and $\Delta mse$ 
+results for CES models.
 %

### 2015-06-22 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Streamlined code for fittedAndResidData.

@@
 <<Fitted_and_Residuals>>=
-fittedAndResidData <- function(model){
+fittedAndResidData <- function(model, id){
   df <- data.frame(select(getData(model), Year))
@@
   df$Residuals <- resid(model)[c(1:length(df$Year))]
-  return(df)  
-}
-
-temp_data <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, id){
-  df <- fittedAndResidData(model)
-  f <- model$formula
-  response <- summands(f, right = FALSE)
-  df[[response]] <- getData(model)[[response]] # Add iGDP to the data frame
+  df <- na.omit(df)
+  # Now add the response, using the original variable name.
+  df[[summands(model$formula, right = FALSE)]] <- response(model)
+  # Now add meta information
   id_list <- strsplit(id, split = "[.]")[[1]]
@@
   return(df)  
+}
+
+temp_data <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, id){
+  return(fittedAndResidData(model, id))  
 }) %>% do.call(rbind, .)
+temp_data$cst <- FALSE
+
+# temp_data_CST <- leaf_apply(modelsCST,class=c("plm", "lm"), f = function(model, id){
+#   return(fittedAndResidData(model, id))
+# }) %>% do.call(rbind, .)
+# temp_data_CST$cst <- TRUE
 

### 2015-06-24 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Adding data to models.

@@
     tVar <- as.name(summands(form, n=3))
+    data <- historicalData[[country]]
     # Cobb-Douglas
-    cdModCST <- lm(log(eval(yVar)) - alphaCST*log(eval(kVar)) - betaCST*log(eval(lVar)) ~ eval(tVar), 
-                   data = historicalData[[country]])
+    cdModCST <- lm(log(eval(yVar)) - alphaCST*log(eval(kVar)) - betaCST*log(eval(lVar)) ~ eval(tVar), data = data)
     attr(cdModCST, "naturalCoeffs") <- data.frame(lambda=coef(cdModCST)[[2]],
@@
                                                   alpha_3=0)
+    cdModCST$formula <- form
+    sdata <- subset(data, select=all.vars(form))
+    sdata <- data[complete.cases(sdata), unique(c(all.vars(form), names(data)))]
+    cdModCST$data <- sdata
     modelsCST[[country]][["unadjusted"]][["noE"]][["CD"]] <- cdModCST
@@
     attr(cesModCST, "naturalCoeffs") <- EconModels:::makeNatCoef(cesModCST)
+    cesModCST$formula <- form
+    cesModCST$data <- sdata
     modelsCST[[country]][["unadjusted"]][["noE"]][["CES"]][["kl"]] <- cesModCST

### 2015-06-24 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Adding data to CST models.

@@
 fittedAndResidData <- function(model, id){
-  df <- data.frame(select(getData(model), Year))
-  # Trim fitted to be same length as df to eliminate problems with possible NAs at end of fitted
+  df <- data.frame(select(model$data, Year)) # getData doesn't work for lm models that are created for CST=TRUE.
+  # By including [c(1:length(df$Year))] on the end, we 
+  # add NAs (as appropriate) to the end of these columns
+  # if data do not exist.
   df$fitted <- yhat(model)[c(1:length(df$Year))]
   df$Residuals <- resid(model)[c(1:length(df$Year))]
-  df <- na.omit(df)
   # Now add the response, using the original variable name.
-  df[[summands(model$formula, right = FALSE)]] <- response(model)
+  df[[summands(model$formula, right = FALSE)]] <- response(model)[c(1:length(df$Year))]
   # Now add meta information
@@
 
-temp_data <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, id){
+temp_data_CST <- leaf_apply(modelsCST, class=c("plm", "lm"), f = function(model, id){
   return(fittedAndResidData(model, id))
 }) %>% do.call(rbind, .)
-temp_data$cst <- FALSE
-
-# temp_data_CST <- leaf_apply(modelsCST,class=c("plm", "lm"), f = function(model, id){
-#   return(fittedAndResidData(model, id))
-# }) %>% do.call(rbind, .)
-# temp_data_CST$cst <- TRUE
-
-# Get the unadjusted, without-energy residuals and store them in a data frame
-r_unadj_noE <- filter(temp_data, flavor=="Unadjusted" & energy=="Without energy") %>% 
+temp_data_CST$cst <- TRUE
+
+temp_data_noCST <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, id){
+  return(fittedAndResidData(model, id))  
+}) %>% do.call(rbind, .)
+temp_data_noCST$cst <- FALSE
+
+temp_data <- plyr::rbind.fill( temp_data_CST, temp_data_noCST )
+
+# Get the unadjusted, without-energy residuals from models that obey the CST
+# and store them in a data frame
+r_unadj_noE_CST <- filter(temp_data, flavor=="Unadjusted" & energy=="Without energy" & cst==TRUE) %>% 
   select(Year, Country, Residuals, model)
-colnames(r_unadj_noE)[colnames(r_unadj_noE)=="Residuals"] <- "r_unadj_noE"
+colnames(r_unadj_noE_CST)[colnames(r_unadj_noE_CST)=="Residuals"] <- "r_unadj_noE"
 # Merge to get the unadjusted, without-energy values next to each country, year, and model
-fitted_and_resid_data <- merge(temp_data, r_unadj_noE)
+fitted_and_resid_data <- merge(temp_data, r_unadj_noE_CST)
 # Create a column containing ∆r, the difference between a residual value
@@
 <<Graphs CD-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Cobb-Douglas models. Solid line is historical GDP.">>=
-fittedGraph(filter(fitted_and_resid_data, model=="CD"))
+fittedGraph(filter(fitted_and_resid_data, model=="CD" & cst==FALSE))
 @
@@
 <<Graphs CESkle-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($kl$)$e$ nesting. Solid line is historical GDP.">>=
-fittedGraph(filter(fitted_and_resid_data, model=="CES" & (nest=="kle" | nest=="kl")))
+fittedGraph(filter(fitted_and_resid_data, model=="CES" & cst==FALSE & (nest=="kle" | nest=="kl")))
 @
@@
 <<Graphs CESlek-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($le$)$k$ nesting. Solid line is historical GDP.">>=
-fittedGraph(filter(fitted_and_resid_data, model=="CES" & (nest=="lek" | nest=="kl")))
+fittedGraph(filter(fitted_and_resid_data, model=="CES" & cst==FALSE & (nest=="lek" | nest=="kl")))
 @
@@
 <<Graphs CESekl-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($ek$)$l$ nesting. Solid line is historical GDP.">>=
-fittedGraph(filter(fitted_and_resid_data, model=="CES" & (nest=="ekl" | nest=="kl")))
+fittedGraph(filter(fitted_and_resid_data, model=="CES" & cst==FALSE & (nest=="ekl" | nest=="kl")))
 @
@@
 <<Graphs CD-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for Cobb-Douglas models.">>=
-residualPlot(filter(fitted_and_resid_data, model=="CD"))
+residualPlot(filter(fitted_and_resid_data, model=="CD" & cst==FALSE))
 @
@@
 <<Graphs CESkle-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(kl$)$e$ nesting.">>=
-residualPlot(filter(fitted_and_resid_data, model=="CES" & (nest=="kle" | nest=="kl")))
+residualPlot(filter(fitted_and_resid_data, model=="CES" & cst==FALSE & (nest=="kle" | nest=="kl")))
 @
@@
 <<Graphs CESlek-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with ($le$)$k$ nesting.">>=
-residualPlot(filter(fitted_and_resid_data, model=="CES" & (nest == "lek" | nest=="kl")))
+residualPlot(filter(fitted_and_resid_data, model=="CES" & cst==FALSE & (nest == "lek" | nest=="kl")))
 @
@@
 <<Graphs CESekl-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(ek$)$l$ nesting.">>=
-residualPlot(filter(fitted_and_resid_data, model=="CES" & (nest=="ekl" | nest=="kl")))
-@
-
-%++++++++++++++++++++++++++++++
-\subsection{Dynamic Solow residuals} 
-\label{sec:dynamic_solow_residuals}
-%++++++++++++++++++++++++++++++
-
-<<Dynamic Solow Residuals>>=
-# Calculate finite difference approximations of time derivatives for output and all factors of production
-dynamicSR <- function(model, id, lag=1, pad="tail"){
-  id_list <- strsplit(id, split = "[.]")[[1]]
-  energy <- id_list[[3]]
-  modelStr <- id_list[[4]]
-
-  f <- model$formula
-  denom <- summands(f, n=length(summands(f))) # time variable
-  nums <- all.vars(f) [1:(length(all.vars(f))-1)] # y, k, l, and e (if present)
-  df <- getData(model)[c(denom, nums)] # columns are: iYear, y, k, l, and e (if present)
-
-  # Calculate names for the columns of finite difference derivatives
-  derivNames <- lapply(1:length(nums), function(i){paste0("d", nums[[i]], ".d", denom)}) %>% unlist
-  derivCols <- lapply(1:length(nums), function(i){
-    # Calculate finite difference derivative columns
-    ediff(df[[i+1]], pad=pad, lag=lag) / ediff(df[[1]], pad=pad, lag=lag)
-  }) %>% do.call(cbind, .) %>% as.data.frame
-  names(derivCols) <- derivNames  
-  df <- cbind(derivCols, df[ , c(nums, denom)]) # puts derivatives first, then raw numbers, then time
-  df[["dydtOvery"]] <- 1 / df[[ nums[[1]] ]] * df[[ derivNames[[1]] ]]
-  coeffs <- naturalCoef(model)
-  df <- cbind(df, coeffs)
-
-  if (modelStr == "CD"){
-    lambda_fd <- 
-      df[["dydtOvery"]] - 
-      df[["alpha_1"]] / df[[nums[[2]]]] * df[[derivNames[[2]]]] - 
-      df[["alpha_2"]] / df[[nums[[3]]]] * df[[derivNames[[3]]]]
-    if (energy == "withE"){
-      # Subtract the energy term also
-      lambda_fd <- lambda_fd - 
-        df[["alpha_3"]] / df[[nums[[4]]]] * df[[derivNames[[4]]]]
-    }
-    # Fraction of growth explained by Solow Residual
-    solowFrac <- lambda_fd / df[["dydtOvery"]]
-    # Add to data frame
-    df$lambda_fd <- lambda_fd
-    df$solowFrac <- solowFrac
-    return(df)
-  } else if (modelStr == "CES"){
-    # Assign nice variable names so that the equations below are easier to read (and debug, and maintain)
-    # This code is nest-aware.
-    n <- model$nest
-    for (i in 1:length(model$nest)){
-      df[[paste0("x", i)]] <- df[[ nums[ model$nest[i]+1 ] ]] # GDP is 1st col, add 1 to get to the factors of production
-      df[[paste0("dx", i, "dt")]] <- df[[ derivNames[ model$nest[i]+1 ] ]]
-    }
-    if (energy == "noE"){
-      # Calculate terms for the finite-difference Solow residual (lambda_fd)
-      df <- df %>% 
-        transform(b = delta_1 * x1^(-rho_1) + (1 - delta_1) * x2^(-rho_1)) %>%
-        transform(dbdtOverrho1 = -delta_1 * x1^(-(rho_1+1))*dx1dt - (1 - delta_1) * x2^(-(rho_1+1))*dx2dt) %>%
-        transform(lambda_fd = dydtOvery + 1/b * dbdtOverrho1) %>%
-        transform(solowFrac = lambda_fd / dydtOvery)
-      return(df)
-    } else if (energy == "withE"){
-      df <- df %>% 
-        transform(b = delta_1 * x1^(-rho_1) + (1 - delta_1) * x2^(-rho_1)) %>%
-        transform(a = delta * b^(rho/rho_1) + (1 - delta) * x3^(-rho)) %>%
-        transform(dbdtOverrho1 = -delta_1 * x1^(-(rho_1+1))*dx1dt - (1 - delta_1) * x2^(-(rho_1+1))*dx2dt) %>%
-        transform(dadtOverrho = delta * b^(rho/rho_1 - 1) * dbdtOverrho1 - (1 - delta) * x3^(-(rho+1))*dx3dt) %>%
-        transform(lambda_fd = dydtOvery + 1/a * dadtOverrho) %>%
-        transform(solowFrac = lambda_fd / dydtOvery)
-      return(df)
-    } else {
-      stop (paste("Unknown energy:", energy))
-    }
-  } else {
-    stop(paste("Unknown modelStr", modelStr))
-  }
-}
-
-lag.to.use <- 1 # years
-temp_data <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), 
-                        f = function(model, id, lag=lag.to.use, pad="tail"){
-  df <- dynamicSR(model, id=id, lag=lag, pad=pad)
-  id_list <- strsplit(id, split = "[.]")[[1]]
-  df$Country <- id_list[[1]]
-  df$flavor <- if (id_list[[2]] == "unadjusted") "Unadjusted" else "Quality-adjusted"
-  df$energy <- if (id_list[[3]] == "noE") "Without energy" else "With energy"
-  df$model <- id_list[[4]]
-  df$nest <- if (length(id_list) > 4) id_list[[5]] else NA
-  df$Year <- getData(model)[["Year"]]
-  return(df)  
-}) %>% do.call(plyr::rbind.fill, .)
-
-# Get the unadjusted, without-energy Solow residuals and store them in a data frame
-sr_unadj_noE <- filter(temp_data, flavor=="Unadjusted" & energy=="Without energy") %>% 
-                select(Year, Country, lambda_fd, model)
-colnames(sr_unadj_noE)[colnames(sr_unadj_noE)=="lambda_fd"] <- "sr_unadj_noE"
-# Merge to get the unadjusted, without-energy values next to each country, year, and model
-solowResiduals <- merge(temp_data, sr_unadj_noE)
-
-# Create a column containing ∆lambda_df, the difference between a lambda_df value
-# and the lambda_df value in the same year for the unadjusted, no-energy case
-solowResiduals[["Dlambda_fd"]] <- abs(solowResiduals[["lambda_fd"]]) - abs(solowResiduals[["sr_unadj_noE"]])
-
-# Relevel factors before plotting
-solowResiduals$Country <- relevelFactor(as.factor(solowResiduals$Country), c("PT", "UK"))
-solowResiduals$flavor <- relevelFactor(as.factor(solowResiduals$flavor), c("Unadjusted", "Quality-adjusted"))
-solowResiduals$energy <- relevelFactor(as.factor(solowResiduals$energy), c("Without energy", "With energy"))
-solowResiduals$nest <- relevelFactor(as.factor(solowResiduals$nest), c("kl", "kle", "lek", "ekl"))
-
-# Make data viewing easier
-solowResiduals <- arrange(solowResiduals, Country, model, flavor, energy, nest)
-@
-
-<<DynamicSR_Graph>>=
-dynamicSRGraph <- function(data){
-ggplot(data=data) +
-  geom_line(data=filter(data, energy=="Without energy"), mapping=aes(x=Year, y=dydtOvery)) +
-  geom_line(mapping=aes(x=Year, y=lambda_fd, linetype=energy)) +
-  scale_linetype_manual(values=c(2,3), name="") +
-  facet_grid(Country ~ flavor) +
-  scale_x_continuous(breaks=c(1960, 1980, 2000)) +
-  xlab("") + 
-  ylab(expression(lambda[ij])) +
-  xy_theme()  
-}
-@
-
-``Dynamic'' Solow residuals~($\lambda_{i,j}$) can be calculated 
-for the Cobb-Douglas and CES models
-as shown in Appendices~\ref{sec:dynamic_sr_CD} and~\ref{sec:dynamic_sr_CES},
-respectively.
-
-Figure~\ref{fig:DynamicSR_CD_Graph} shows the evolution 
-of the Solow residual~($\lambda_{i,j}$) over time
-as calculated by Equation~\ref{eq:lambdaij} 
-with the timespan for finite differences ($t_j - t_i$) set to 
-\Sexpr{lag.to.use}~\Sexpr{if (lag.to.use == 1) "year" else "years"}.
-%
-<<DynamicSR_CD_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residuals for the Cobb-Douglas model.
-Dashed lines are $\\lambda$ values.
-Solid lines are $\\frac{1}{y}\\frac{\\mathrm{d} y}{\\mathrm{d} t}$.">>=
-dynamicSRGraph(filter(solowResiduals, model=="CD"))
-@
-%
-<<DynamicSR_CESkle_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residuals for the CES model with ($kl$)$e$ nesting.
-Dashed lines are $\\lambda$ values.
-Solid lines are $\\frac{1}{y}\\frac{\\mathrm{d} y}{\\mathrm{d} t}$.">>=
-dynamicSRGraph(filter(solowResiduals, model=="CES" & (nest=="kle" | nest=="kl")))
-@
-%
-<<DynamicSR_CESlek_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residuals for the CES model with ($le$)$k$ nesting.
-Dashed lines are $\\lambda$ values.
-Solid lines are $\\frac{1}{y}\\frac{\\mathrm{d} y}{\\mathrm{d} t}$.">>=
-dynamicSRGraph(filter(solowResiduals, model=="CES" & (nest=="lek" | nest=="kl")))
-@
-%
-<<DynamicSR_CESekl_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residuals for the CES model with ($ek$)$l$ nesting.
-Dashed lines are $\\lambda$ values.
-Solid lines are $\\frac{1}{y}\\frac{\\mathrm{d} y}{\\mathrm{d} t}$.">>=
-dynamicSRGraph(filter(solowResiduals, model=="CES" & (nest=="ekl" | nest=="kl")))
+residualPlot(filter(fitted_and_resid_data, model=="CES" & cst==FALSE & (nest=="ekl" | nest=="kl")))
 @
@@
   geom_point(data=filter(AllCoeffs, cst==FALSE & model=="CD"), mapping=aes(x=Dmse, y=Dlambda, color=energy)) +
-  scale_shape(solid=FALSE) +
-  guides(shape=FALSE) +
-  geom_point(data=filter(AllCoeffs, cst==TRUE & model=="CD"), mapping=aes(x=Dmse, y=Dlambda, color=energy, shape=cst)) +
+  geom_point(data=filter(AllCoeffs, cst==TRUE & model=="CD"), mapping=aes(x=Dmse, y=Dlambda, color=energy), shape=1) +
   facet_grid(Country ~ flavor) +
@@
   geom_point(data=filter(AllCoeffs, cst==FALSE & model=="CD"), mapping=aes(x=Dmse, y=percDlambda, color=energy)) +
-  scale_shape(solid=FALSE) +
-  guides(shape=FALSE) +
-  geom_point(data=filter(AllCoeffs, cst==TRUE & model=="CD"), mapping=aes(x=Dmse, y=percDlambda, color=energy, shape=cst)) +
+  geom_point(data=filter(AllCoeffs, cst==TRUE & model=="CD"), mapping=aes(x=Dmse, y=percDlambda, color=energy), shape=1) +
   facet_grid(Country ~ flavor) +
@@
 <<DSRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta mse$) for the CES modles relative to the Unadjusted, Without energy, CST case.">>=
-ggplot(data=filter(AllCoeffs, model=="CES")) +
-  geom_point(mapping=aes(x=Dmse, y=Dlambda, color=energy, shape=nest)) +
+ggplot() +
+  geom_point(data=filter(AllCoeffs, model=="CES" & cst==FALSE), mapping=aes(x=Dmse, y=Dlambda, color=energy, shape=nest)) +
+  geom_point(data=filter(AllCoeffs, model=="CES" & cst==TRUE), mapping=aes(x=Dmse, y=Dlambda, color=energy), shape=1) +
   facet_grid(Country ~ flavor) +
@@
 <<percDSRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Percentage change in Solow Residuals~($\\Delta\\lambda \\, [\\%]$) and mean squared error~($\\Delta mse$) for the CES modles relative to the Unadjusted, Without energy, CST case.">>=
-ggplot(data=filter(AllCoeffs, model=="CES")) +
-  geom_point(mapping=aes(x=Dmse, y=percDlambda, color=energy, shape=nest)) +
+ggplot() +
+  geom_point(data=filter(AllCoeffs, model=="CES" & cst==FALSE), mapping=aes(x=Dmse, y=percDlambda, color=energy, shape=nest)) +
+  geom_point(data=filter(AllCoeffs, model=="CES" & cst==TRUE), mapping=aes(x=Dmse, y=percDlambda, color=energy), shape=1) + 
   facet_grid(Country ~ flavor) +
@@
 @
-
-%++++++++++++++++++++++++++++++
-\subsection{Does quality-adjusting the factors of production 
-            decrease fitting residuals and/or the dynamic Solow residual?} 
-\label{sec:quality_adj_energy_and_dynamic_solow_residual}
-%++++++++++++++++++++++++++++++
-
-<<SR and R trajectory data>>=
-traj.data <- merge(solowResiduals[c("Country", "Year", "model", "flavor", "energy", "nest", "Dlambda_fd")], 
-                   fitted_and_resid_data[c("Country", "Year", "model", "flavor", "energy", "nest", "Dr")]) %>%
-                   arrange(Country, model, flavor, energy, nest)
-traj.data.stats <- traj.data %>% 
-  group_by(model, Country, flavor, energy, nest) %>%
-  summarise(Dlambda_fd.mean = mean(Dlambda_fd, na.rm=TRUE), Dr.mean = mean(Dr))
-
-############################################
-# Dlambda_fd.p <- traj.data %>% 
-#   group_by(model, Country, flavor, energy, nest) %>% 
-#   select(Dlambda_fd) %>%
-#   t.test(., alternative="less")[["p.value"]]
-############################################  
-@
-
-<<SR and R trajectory plot function>>=
-residualsTrajGraph <- function(data){
-  plot <- ggplot(data=data) + 
-    geom_point(mapping=aes(x=Dr, y=Dlambda_fd, color=energy)) + 
-    facet_grid(Country ~ flavor) +
-    xlab(expression(Delta*r[i])) +
-    ylab(expression(Delta*lambda[ij])) +
-    xy_theme() + 
-    theme(legend.title=element_blank())
-  return(plot)
-}
-@
-
-We can test our hypothesis that quality-adjusting the factors of production
-and including energy will reduce the Solow residuals~($\lambda$)
-and the fitting residuals~($r$) by plotting
-$\Delta \lambda_i$ vs. $\Delta r_i$, where
-%
-\begin{equation} \label{eq:delta_lambda_i}
-  \Delta \lambda_i \equiv \left| \lambda_i \right| - \left| \lambda_{i, \, Unadjusted, \, Without \, energy} \right|
-\end{equation}
-%
-and
-%
-\begin{equation} \label{eq:delta_r}
-  \Delta r_i \equiv \left| r_i \right| - \left| r_{i, \,Unadjusted, \, Without \, energy} \right|.
-\end{equation}
-%
-If most of the points fall in the lower-left quadrant of a graph, 
-we can conclude that both Solow residual~($\lambda$) and
-fitting residual~($r$) have decreased due to either 
-quality-adjustment of the factors of production or 
-including energy.
-
-Figure~\ref{fig:Solow_residual_trajectories_CD} indicates that
-for the Cobb-Douglas model, 
-neither 
-quality-adjusting the factors of production
-nor including energy 
-consistently reduces
-the Solow residual or the fitting residual.
-
-<<Solow_residual_trajectories_CD, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residual and fitting residual trajectories relative to the Unadjusted, Without-energy condition for the Cobb-Douglas model.">>=
-residualsTrajGraph(filter(traj.data, model=="CD"))
-@
-
-We can also calculate the average values for $\Delta \lambda_{i,j}$ and $\Delta r_{i}$ 
-as shown in Table~\ref{tab:Trajectory_Means_CD}.
-%
-<<Trajectory_Means_CD, results="asis">>=
-myXTable(data = filter(traj.data.stats, model=="CD") %>% select(-nest), 
-         caption = "Average $\\Delta\\lambda$ and $\\Delta r$ for Cobb-Douglas models.",
-         label=paste0("tab:", opts_current$get("label")),
-         digits=6)
-@
-%
-The following tables and figures show the same analysis for the CES model.
-%
-<<Solow_residual_trajectories_CESkle, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residual and fitting residual trajectories relative to the Unadjusted, Without-energy condition for the CES model with ($kl$)$e$ nesting.">>=
-residualsTrajGraph(filter(traj.data, model=="CES" & (nest=="kl" | nest=="kle")))
-@
-%
-<<Trajectory_Means_CESkle, results="asis">>=
-myXTable(data = filter(traj.data.stats, model=="CES" & (nest=="kl" | nest=="kle")), 
-         caption = "Average $\\Delta\\lambda$ and $\\Delta r$ for CES models with ($kl$)$e$ nesting.",
-         label=paste0("tab:", opts_current$get("label")),
-         digits=6)
-@
-
-<<Solow_residual_trajectories_CESlek, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residual and fitting residual trajectories relative to the Unadjusted, Without-energy condition for the CES model with ($le$)$k$ nesting.">>=
-residualsTrajGraph(filter(traj.data, model=="CES" & (nest=="kl" | nest=="lek")))
-@
-
-<<Trajectory_Means_CESlek, results="asis">>=
-myXTable(data = filter(traj.data.stats, model=="CES" & (nest=="kl" | nest=="lek")), 
-         caption = "Average $\\Delta\\lambda$ and $\\Delta r$ for CES models with ($le$)$k$ nesting.",
-         label=paste0("tab:", opts_current$get("label")),
-         digits=6)
-@
-
-<<Solow_residual_trajectories_CESekl, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residual and fitting residual trajectories relative to the Unadjusted, Without-energy condition for the CES model with ($ek$)$l$ nesting.">>=
-residualsTrajGraph(filter(traj.data, model=="CES" & (nest=="kl" | nest=="ekl")))
-@
-
-<<Trajectory_Means_CESekl, results="asis">>=
-myXTable(data = filter(traj.data.stats, model=="CES" & (nest=="kl" | nest=="ekl")), 
-         caption = "Average $\\Delta\\lambda$ and $\\Delta r$ for CES models with ($ek$)$l$ nesting.",
-         label=paste0("tab:", opts_current$get("label")),
-         digits=6)
-@
-
-% %++++++++++++++++++++++++++++++
-% \subsection{What effect does including energy and quality-adjustment have 
-%             on the Solow residual in the Cobb-Douglas model?} 
-% \label{sec:quality_adj_energy_and_solow_residual}
-% %++++++++++++++++++++++++++++++
-% 
-% We'll first look at Portugal.
-% 
-% %------------------------------
-% \subsubsection{Portugal} 
-% %------------------------------
-% 
-% First, use non-quality-adjusted data for Portugal and the Cobb-Douglas model.
-% 
-% <<Portugal C-D undadjusted without energy>>=
-% naturalCoef(models$PT$unadjusted$noE$CD)
-% @
-% 
-% <<Portugal C-D undadjusted with energy>>=
-% naturalCoef(models$PT$unadjusted$withE$CD)
-% @
-% 
-% The Solow residual (\texttt{lambda}) is always negative. 
-% However, the absolute value of \texttt{lambda} decreases from 
-% \Sexpr{naturalCoef(models$PT$unadjusted$noE$CD)$lambda} to 
-% \Sexpr{naturalCoef(models$PT$unadjusted$withE$CD)$lambda}
-% when adding energy.
-% So it appears that for Portugal, 
-% using unadjusted inputs and including energy as a factor of production
-% reduces the absolute value of the Solow residual somewhat.
-% 
-% What about for quality-adjusted data and Portugal?
-% 
-% <<Portugal C-D adjusted without energy>>=
-% naturalCoef(models$PT$adjusted$noE$CD)
-% @
-% 
-% <<Portugal C-D adjusted with energy>>=
-% naturalCoef(models$PT$adjusted$withE$CD)
-% @
-% 
-% Using quality-adjusted inputs, the Solow residual (\texttt{lambda}) moves from 
-% \Sexpr{naturalCoef(models$PT$adjusted$noE$CD)$lambda} to
-% \Sexpr{naturalCoef(models$PT$adjusted$withE$CD)$lambda} when including energy.
-% The absolute value of the Solow residual again decreases when adding energy.
-% But, with quality-adjusted inputs, the effect is much stronger.
-% 
-% Table~\ref{tab:lambda_CD_PT} shows
-% the effect of both quality-corrected factors of production and energy.
-% We find that including energy as a factor of production 
-% reduces the absolute value of the Solow residual (\texttt{lambda})
-% whether or not the factors of production are quality-adjusted. 
-% Quality-adjustment gets part of the way toward eliminating the Solow residual.
-% 
-% \begin{table} \caption{Portugal Solow residual results with Cobb-Douglas.} 
-% \label{tab:lambda_CD_PT} 
-%   \begin{center}
-%     \begin{tabular}{r c c} 
-%       \toprule
-%                       & Unadjusted     & Quality-adjusted   \\
-%       \midrule
-%       Without energy  & \Sexpr{naturalCoef(models$PT$unadjusted$noE$CD)$lambda}    & \Sexpr{naturalCoef(models$PT$adjusted$noE$CD)$lambda} \\
-%       With energy     & \Sexpr{naturalCoef(models$PT$unadjusted$withE$CD)$lambda}  & \Sexpr{naturalCoef(models$PT$adjusted$withE$CD)$lambda} \\
-%       \bottomrule
-%     \end{tabular}
-%   \end{center}
-% \end{table}
-% 
-% Note that for Portugal the contribution of capital (\texttt{alpha\_1})
-% always shifts to energy (\texttt{alpha\_3}) when energy is included 
-% as a factor of production.
-% 
-% What about for the UK?
-% 
-% %------------------------------
-% \subsubsection{United Kingdom} 
-% %------------------------------
-% 
-% Table~\ref{tab:lambda_CD_UK} shows fitted Cobb-Douglas coefficients for the UK. 
-% 
-% \begin{table} \caption{UK Solow residual results with Cobb-Douglas.} 
-% \label{tab:lambda_CD_UK} 
-%   \begin{center}
-%     \begin{tabular}{r c c} 
-%       \toprule
-%                       & Unadjusted     & Quality-adjusted   \\
-%       \midrule
-%       Without energy  & \Sexpr{naturalCoef(models$UK$unadjusted$noE$CD)$lambda}   
-%                                                 & \Sexpr{naturalCoef(models$UK$adjusted$noE$CD)$lambda} \\
-%       With energy     & \Sexpr{naturalCoef(models$UK$unadjusted$withE$CD)$lambda} 
-%                                                 & \Sexpr{naturalCoef(models$UK$adjusted$withE$CD)$lambda} \\
-%       \bottomrule
-%     \end{tabular}
-%   \end{center}
-% \end{table}
-% 
-% For the UK, the quality-adjusted, with energy Solow residual is 
-% \Sexpr{naturalCoef(models$UK$adjusted$withE$CD)$lambda * 100}\%,
-% a very small number indeed.
-% For the UK, it appears that \emph{both} quality-adjustment and addition of energy as a factor of production
-% are required to effectively eliminate the Solow residual,
-% reducing it to \Sexpr{naturalCoef(models$UK$adjusted$withE$CD)$lambda}.
-% 
-% Adding energy alone actually \emph{in}creases the Solow residual from 
-% \Sexpr{naturalCoef(models$UK$unadjusted$noE$CD)$lambda} to
-% \Sexpr{naturalCoef(models$UK$unadjusted$withE$CD)$lambda}.
-% The details for each model with unadjusted factors of production are shown below.
-% 
-% <<UK CD Unadjusted Coefficients>>=
-% naturalCoef(models$UK$unadjusted$noE$CD)
-% naturalCoef(models$UK$unadjusted$withE$CD)
-% @
-% 
-% When energy is included, much of the effect of capital (\texttt{alpha\_1}) is 
-% attributed to energy (\texttt{alpha\_3}), 
-% as \texttt{alpha\_1} moves from 
-% \Sexpr{naturalCoef(models$UK$unadjusted$noE$CD)$alpha_1} to
-% \Sexpr{naturalCoef(models$UK$unadjusted$withE$CD)$alpha_1}.
-% 
-% When we look at quality-adjusted inputs, we find similar results.
-% 
-% <<UK CD Quality-adjusted Coefficients>>=
-% naturalCoef(models$UK$adjusted$noE$CD)
-% naturalCoef(models$UK$adjusted$withE$CD)
-% @
-% 
-% \texttt{alpha\_1} moves from 
-% \Sexpr{naturalCoef(models$UK$adjusted$noE$CD)$alpha_1} to
-% \Sexpr{naturalCoef(models$UK$adjusted$withE$CD)$alpha_1}.
-% 
-% Now, let's compare the fits to historical data.
-% 
-% 
-% 
-% %++++++++++++++++++++++++++++++
-% \subsection{Do we obtain a negative Solow residual for Portugal with the CES model?} 
-% \label{sec:Solow_negative_for_PT_in_CES?}
-% %++++++++++++++++++++++++++++++
-% 
-% First, look at the CES model without energy.
-% Nesting is unabmiguous, so this fit does not need to be repeated
-% for each nesting option. 
-% (This means that the top rows of Tables~\ref{tab:lambda_CES-kle_PT}--\ref{tab:lambda_CES-ekl_PT}
-% are identical.)
-% 
-% <<PT CES-kl, warning=FALSE>>=
-% naturalCoef(models$PT$unadjusted$noE$CES$kl)
-% naturalCoef(models$PT$adjusted$noE$CES$kl)
-% @
-% 
-% Both unadjusted and quality-adjusted variables give positive Solow residuals,
-% \Sexpr{naturalCoef(models$PT$unadjusted$noE$CES$kl)$lambda} for unadjusted inputs and
-% \Sexpr{naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda} for quality-adjusted inputs.
-% Furthermore, quality-adjustment reduces the magnitude of the Solow residual.
-% 
-% %------------------------------
-% \subsubsection{($kl$)$e$ nesting} 
-% %------------------------------
-% 
-% Now, look at unadjusted inputs using the ($kl$)$e$ nesting.
-% 
-% <<PT CES-kle unadjusted, warning=FALSE>>=
-% naturalCoef(models$PT$unadjusted$withE$CES$kle)
-% @
-% 
-% Now look at quality-adjusted inputs using the ($kl$)$e$ nesting.
-% 
-% <<PT CES-kle quality-adjusted, warning=FALSE>>=
-% naturalCoef(models$PT$adjusted$withE$CES$kle)
-% @
-% 
-% Table~\ref{tab:lambda_CES-kle_PT} summarizes the Portugal Solow residual results with CES and the ($kl$)$e$ nesting.
-% 
-% \begin{table} \caption{Portugal Solow residual results with CES and ($kl$)$e$ nesting.} 
-% \label{tab:lambda_CES-kle_PT} 
-%   \begin{center}
-%     \begin{tabular}{r c c} 
-%       \toprule
-%                       & Unadjusted     & Quality-adjusted   \\
-%       \midrule
-%       Without energy  & \Sexpr{naturalCoef(models$PT$unadjusted$noE$CES$kl)$lambda} 
-%                                                             & \Sexpr{naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda} \\
-%       With energy     & \Sexpr{naturalCoef(models$PT$unadjusted$withE$CES$kle)$lambda} 
-%                                                             & \Sexpr{naturalCoef(models$PT$adjusted$withE$CES$kle)$lambda} \\
-%       \bottomrule
-%     \end{tabular}
-%   \end{center}
-% \end{table}
-% 
-% Table~\ref{tab:sse_CES-kle_PT} shows the $sse$ values for each of these models.
-% 
-% \begin{table} \caption{PT $sse$ with CES and ($kl$)$e$ nesting.} 
-% \label{tab:sse_CES-kle_PT} 
-%   \begin{center}
-%     \begin{tabular}{r c c} 
-%       \toprule
-%                       & Unadjusted     & Quality-adjusted   \\
-%       \midrule
-%       Without energy  & \Sexpr{EconModels:::sse(models$PT$unadjusted$noE$CES$kl)$sse} 
-%                                                             & \Sexpr{EconModels:::sse(models$PT$adjusted$noE$CES$kl)$sse} \\
-%       With energy     & \Sexpr{EconModels:::sse(models$PT$unadjusted$withE$CES$kle)$sse} 
-%                                                             & \Sexpr{EconModels:::sse(models$PT$adjusted$withE$CES$kle)$sse} \\
-%       \bottomrule
-%     \end{tabular}
-%   \end{center}
-% \end{table}
-% 
-% In contrast to the Cobb-Douglas model,
-% the CES model with ($kl$)$e$ nesting
-% produces positive Solow residuals in all cases. 
-% We also see that both 
-% quality-adjusting the inputs and
-% including energy
-% reduce the Solow residual (\texttt{lambda}).
-% 
-% %------------------------------
-% \subsubsection{($le$)$k$ nesting} 
-% %------------------------------
-% 
-% Next, look at unadjusted inputs using the ($le$)$k$ nesting.
-% 
-% <<PT CES-lek unadjusted, warning=FALSE>>=
-% naturalCoef(models$PT$unadjusted$withE$CES$lek)
-% @
-% 
-% Now look at quality-adjusted inputs using the ($le$)$k$ nesting.
-% 
-% <<PT CES-lek quality-adjusted, warning=FALSE>>=
-% naturalCoef(models$PT$adjusted$withE$CES$lek)
-% @
-% 
-% Table~\ref{tab:lambda_CES-lek_PT} summarizes the Portugal Solow residual results with CES and the ($le$)$k$ nesting.
-% 
-% \begin{table} \caption{Portugal Solow residual results with CES and ($le$)$k$ nesting.} 
-% \label{tab:lambda_CES-lek_PT} 
-%   \begin{center}
-%     \begin{tabular}{r c c} 
-%       \toprule
-%                       & Unadjusted     & Quality-adjusted   \\
-%       \midrule
-%       Without energy  & \Sexpr{naturalCoef(models$PT$unadjusted$noE$CES$kl)$lambda} 
-%                                         & \Sexpr{naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda} \\
-%       With energy     & \Sexpr{naturalCoef(models$PT$unadjusted$withE$CES$lek)$lambda} 
-%                                         & \Sexpr{naturalCoef(models$PT$adjusted$withE$CES$lek)$lambda} \\
-%       \bottomrule
-%     \end{tabular}
-%   \end{center}
-% \end{table}
-% 
-% Table~\ref{tab:sse_CES-lek_PT} shows the $sse$ values for each of these models.
-% 
-% \begin{table} \caption{PT $sse$ with CES and ($le$)$k$ nesting.} 
-% \label{tab:sse_CES-lek_PT} 
-%   \begin{center}
-%     \begin{tabular}{r c c} 
-%       \toprule
-%                       & Unadjusted     & Quality-adjusted   \\
-%       \midrule
-%       Without energy  & \Sexpr{EconModels:::sse(models$PT$unadjusted$noE$CES$kl)$sse} 
-%                                         & \Sexpr{EconModels:::sse(models$PT$adjusted$noE$CES$kl)$sse} \\
-%       With energy     & \Sexpr{EconModels:::sse(models$PT$unadjusted$withE$CES$lek)$sse} 
-%                                         & \Sexpr{EconModels:::sse(models$PT$adjusted$withE$CES$lek)$sse} \\
-%       \bottomrule
-%     \end{tabular}
-%   \end{center}
-% \end{table}
-% 
-% Similar to the CES model with ($kl$)$e$ nesting,
-% the CES model with ($le$)$k$ nesting
-% produces positive Solow residuals in all cases. 
-% After energy has been added, quality-adjustment 
-% has very little effect on the Solow residual,
-% creating a slight increase from 
-% \Sexpr{naturalCoef(models$PT$unadjusted$withE$CES$lek)$lambda} to
-% \Sexpr{naturalCoef(models$PT$adjusted$withE$CES$lek)$lambda}.
-% 
-% 
-% %------------------------------
-% \subsubsection{($ek$)$l$ nesting} 
-% %------------------------------
-% 
-% Next, look at unadjusted inputs using the ($ek$)$l$ nesting.
-% 
-% <<PT CES-ekl unadjusted, warning=FALSE>>=
-% naturalCoef(models$PT$unadjusted$withE$CES$ekl)
-% @
-% 
-% Now look at quality-adjusted inputs using the ($ek$)$l$ nesting.
-% 
-% <<PT CES-ekl quality-adjusted, warning=FALSE>>=
-% naturalCoef(models$PT$adjusted$withE$CES$ekl)
-% @
-% 
-% Table~\ref{tab:lambda_CES-ekl_PT} summarizes the Portugal Solow residual results with CES and the ($ek$)$l$ nesting.
-% 
-% \begin{table} \caption{Portugal Solow residual results with CES and ($ek$)$l$ nesting.} 
-% \label{tab:lambda_CES-ekl_PT} 
-%   \begin{center}
-%     \begin{tabular}{r c c} 
-%       \toprule
-%                       & Unadjusted     & Quality-adjusted   \\
-%       \midrule
-%       Without energy  & \Sexpr{naturalCoef(models$PT$unadjusted$noE$CES$kl)$lambda} 
-%                                         & \Sexpr{naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda} \\
-%       With energy     & \Sexpr{naturalCoef(models$PT$unadjusted$withE$CES$ekl)$lambda} 
-%                                         & \Sexpr{naturalCoef(models$PT$adjusted$withE$CES$ekl)$lambda} \\
-%       \bottomrule
-%     \end{tabular}
-%   \end{center}
-% \end{table}
-% 
-% Table~\ref{tab:sse_CES-ekl_PT} shows the $sse$ values for each of these models.
-% 
-% \begin{table} \caption{PT $sse$ with CES and ($ek$)$l$ nesting.} 
-% \label{tab:sse_CES-ekl_PT} 
-%   \begin{center}
-%     \begin{tabular}{r c c} 
-%       \toprule
-%                       & Unadjusted     & Quality-adjusted   \\
-%       \midrule
-%       Without energy  & \Sexpr{EconModels:::sse(models$PT$unadjusted$noE$CES$kl)$sse} 
-%                                         & \Sexpr{EconModels:::sse(models$PT$adjusted$noE$CES$kl)$sse} \\
-%       With energy     & \Sexpr{EconModels:::sse(models$PT$unadjusted$withE$CES$ekl)$sse} 
-%                                         & \Sexpr{EconModels:::sse(models$PT$adjusted$withE$CES$ekl)$sse} \\
-%       \bottomrule
-%     \end{tabular}
-%   \end{center}
-% \end{table}
-% 
-% For the ($ek$)$l$ nesting, 
-% the Solow residual is positive, and 
-% quality-adjusting the inputs 
-% reduces the Solow residual (\texttt{lambda}).
-% Adding energy decreases the Solow residual 
-% (from \Sexpr{naturalCoef(models$PT$unadjusted$withE$CES$ekl)$lambda} to 
-% \Sexpr{naturalCoef(models$PT$adjusted$withE$CES$ekl)$lambda})
-% when enegy is included in the model.
-% But, adding energy slightly increases the Solow residual
-% (from \Sexpr{naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda} to \Sexpr{naturalCoef(models$PT$adjusted$withE$CES$ekl)$lambda})
-% when quality-adjusted inputs are used.
-% 
-% 
-% %++++++++++++++++++++++++++++++
-% \subsection{Do we obtain a positive Solow residual for the UK with the CES model?} 
-% \label{sec:Solow_positive_for_UK_in_CES?}
-% %++++++++++++++++++++++++++++++
-% 
-% First, look at the CES model without energy.
-% Nesting is unabmiguous, so this fit does not need to be repeated
-% for each nesting option. 
-% (This means that the top rows of Tables~\ref{tab:lambda_CES-kle_UK}--\ref{tab:lambda_CES-ekl_UK}
-% are identical.)
-% 
-% <<UK CES-kl, warning=FALSE>>=
-% naturalCoef(models$UK$unadjusted$noE$CES$kl)
-% naturalCoef(models$UK$adjusted$noE$CES$kl)
-% @
-% 
-% Both unadjusted and quality-adjusted variables give positive Solow residuals for the UK,
-% \Sexpr{naturalCoef(models$UK$unadjusted$noE$CES$kl)$lambda} for unadjusted inputs and
-% \Sexpr{naturalCoef(models$UK$adjusted$noE$CES$kl)$lambda} for quality-adjusted inputs.
-% Furthermore, quality-adjustment reduces the magnitude of the UK Solow residual.
-% 
-% %------------------------------
-% \subsubsection{($kl$)$e$ nesting} 
-% %------------------------------
-% 
-% Now, look at unadjusted inputs using the ($kl$)$e$ nesting.
-% 
-% <<UK CES-kle unadjusted>>=
-% naturalCoef(models$UK$unadjusted$withE$CES$kle)
-% @
-% 
-% Now look at quality-adjusted inputs using the ($kl$)$e$ nesting.
-% 
-% <<UK CES-kle quality-adjusted>>=
-% naturalCoef(models$UK$adjusted$withE$CES$kle)
-% @
-% 
-% Table~\ref{tab:lambda_CES-kle_UK} summarizes the UK Solow residual results with CES and the ($kl$)$e$ nesting.
-% 
-% \begin{table} \caption{UK Solow residual results with CES and ($kl$)$e$ nesting.} 
-% \label{tab:lambda_CES-kle_UK} 
-%   \begin{center}
-%     \begin{tabular}{r c c} 
-%       \toprule
-%                       & Unadjusted     & Quality-adjusted   \\
-%       \midrule
-%       Without energy  & \Sexpr{naturalCoef(models$UK$unadjusted$noE$CES$kl)$lambda} & \Sexpr{naturalCoef(models$UK$adjusted$noE$CES$kl)$lambda} \\
-%       With energy     & \Sexpr{naturalCoef(models$UK$unadjusted$withE$CES$kle)$lambda} 
-%                                                                 & \Sexpr{naturalCoef(models$UK$adjusted$withE$CES$kle)$lambda} \\
-%       \bottomrule
-%     \end{tabular}
-%   \end{center}
-% \end{table}
-% 
-% Table~\ref{tab:sse_CES-kle_UK} shows the $sse$ values for each of these models.
-% 
-% \begin{table} \caption{UK $sse$ with CES and ($kl$)$e$ nesting.} 
-% \label{tab:sse_CES-kle_UK} 
-%   \begin{center}
-%     \begin{tabular}{r c c} 
-%       \toprule
-%                       & Unadjusted     & Quality-adjusted   \\
-%       \midrule
-%       Without energy  & \Sexpr{EconModels:::sse(models$UK$unadjusted$noE$CES$kl)$sse} & \Sexpr{EconModels:::sse(models$UK$adjusted$noE$CES$kl)$sse} \\
-%       With energy     & \Sexpr{EconModels:::sse(models$UK$unadjusted$withE$CES$kle)$sse} 
-%                                                             & \Sexpr{EconModels:::sse(models$UK$adjusted$withE$CES$kle)$sse} \\
-%       \bottomrule
-%     \end{tabular}
-%   \end{center}
-% \end{table}
-% 
-% Like the Cobb-Douglas model, the CES model produces positive Solow residuals
-% with the ($kl$)$e$ nesting.
-% We also see that both 
-% quality-adjusting the inputs and
-% including energy
-% reduce the Solow residual (\texttt{lambda}).
-% 
-% %------------------------------
-% \subsubsection{($le$)$k$ nesting}
-% %------------------------------
-% 
-% Next, look at unadjusted inputs using the ($le$)$k$ nesting.
-% 
-% <<UK CES-lek unadjusted>>=
-% naturalCoef(models$UK$unadjusted$withE$CES$lek)
-% @
-% 
-% Now look at quality-adjusted inputs using the ($le$)$k$ nesting.
-% 
-% <<UK CES-lek quality-adjusted>>=
-% naturalCoef(models$UK$adjusted$withE$CES$lek)
-% @
-% 
-% Table~\ref{tab:lambda_CES-lek_UK} summarizes the UK Solow residual results with CES and the ($le$)$k$ nesting.
-% 
-% \begin{table} \caption{UK Solow residual results with CES and ($le$)$k$ nesting.} 
-% \label{tab:lambda_CES-lek_UK} 
-%   \begin{center}
-%     \begin{tabular}{r c c} 
-%       \toprule
-%                       & Unadjusted     & Quality-adjusted   \\
-%       \midrule
-%       Without energy  & \Sexpr{naturalCoef(models$UK$unadjusted$noE$CES$kl)$lambda} & \Sexpr{naturalCoef(models$UK$adjusted$noE$CES$kl)$lambda} \\
-%       With energy     & \Sexpr{naturalCoef(models$UK$unadjusted$withE$CES$lek)$lambda} 
-%                                                             & \Sexpr{naturalCoef(models$UK$adjusted$withE$CES$lek)$lambda} \\
-%       \bottomrule
-%     \end{tabular}
-%   \end{center}
-% \end{table}
-% 
-% Table~\ref{tab:sse_CES-lek_UK} shows the $sse$ values for each of these models.
-% 
-% \begin{table} \caption{UK $sse$ with CES and ($le$)$k$ nesting.} 
-% \label{tab:sse_CES-lek_UK} 
-%   \begin{center}
-%     \begin{tabular}{r c c} 
-%       \toprule
-%                       & Unadjusted     & Quality-adjusted   \\
-%       \midrule
-%       Without energy  & \Sexpr{EconModels:::sse(models$UK$unadjusted$noE$CES$kl)$sse} & \Sexpr{EconModels:::sse(models$UK$adjusted$noE$CES$kl)$sse} \\
-%       With energy     & \Sexpr{EconModels:::sse(models$UK$unadjusted$withE$CES$lek)$sse} 
-%                                                             & \Sexpr{EconModels:::sse(models$UK$adjusted$withE$CES$lek)$sse} \\
-%       \bottomrule
-%     \end{tabular}
-%   \end{center}
-% \end{table}
-% 
-% 
-% Similar to the CES model with ($kl$)$e$ nesting,
-% the CES model with ($le$)$k$ nesting
-% produces positive Solow residuals in all cases. 
-% Both quality-adjustment and inclusion of energy 
-% decrease the magnitude of the Solow residual.
-% 
-% %------------------------------
-% \subsubsection{($ek$)$l$ nesting}
-% %------------------------------
-% 
-% Next, look at unadjusted inputs using the ($el$)$l$ nesting.
-% 
-% <<UK CES-ekl unadjusted>>=
-% naturalCoef(models$UK$unadjusted$withE$CES$ekl)
-% @
-% 
-% Now look at quality-adjusted inputs using the ($ek$)$l$ nesting.
-% 
-% <<UK CES-ekl quality-adjusted>>=
-% naturalCoef(models$UK$adjusted$withE$CES$ekl)
-% @
-% 
-% Table~\ref{tab:lambda_CES-ekl_UK} summarizes the UK Solow residual results with CES and the ($ek$)$l$ nesting.
-% 
-% \begin{table} \caption{UK Solow residual results with CES and ($ek$)$l$ nesting.} 
-% \label{tab:lambda_CES-ekl_UK} 
-%   \begin{center}
-%     \begin{tabular}{r c c} 
-%       \toprule
-%                       & Unadjusted     & Quality-adjusted   \\
-%       \midrule
-%       Without energy  & \Sexpr{naturalCoef(models$UK$unadjusted$noE$CES$kl)$lambda} & \Sexpr{naturalCoef(models$UK$adjusted$noE$CES$kl)$lambda} \\
-%       With energy     & \Sexpr{naturalCoef(models$UK$unadjusted$withE$CES$ekl)$lambda} 
-%                                                             & \Sexpr{naturalCoef(models$UK$adjusted$withE$CES$ekl)$lambda} \\
-%       \bottomrule
-%     \end{tabular}
-%   \end{center}
-% \end{table}
-% 
-% Table~\ref{tab:sse_CES-ekl_UK} shows the $sse$ values for each of these models.
-% 
-% \begin{table} \caption{UK $sse$ with CES and ($ek$)$l$ nesting.} 
-% \label{tab:sse_CES-ekl_UK} 
-%   \begin{center}
-%     \begin{tabular}{r c c} 
-%       \toprule
-%                       & Unadjusted     & Quality-adjusted   \\
-%       \midrule
-%       Without energy  & \Sexpr{EconModels:::sse(models$UK$unadjusted$noE$CES$kl)$sse} & \Sexpr{EconModels:::sse(models$UK$adjusted$noE$CES$kl)$sse} \\
-%       With energy     & \Sexpr{EconModels:::sse(models$UK$unadjusted$withE$CES$ekl)$sse} 
-%                                                             & \Sexpr{EconModels:::sse(models$UK$adjusted$withE$CES$ekl)$sse} \\
-%       \bottomrule
-%     \end{tabular}
-%   \end{center}
-% \end{table}
-% 
-% 
-% Similar to the CES model with ($ek$)$l$ nesting,
-% the CES model with ($ek$)$l$ nesting
-% produces positive Solow residuals in all cases. 
-% Both quality-adjustment and inclusion of energy 
-% decrease the magnitude of the Solow residual.
 
@@
 
+% %++++++++++++++++++++++++++++++
+% \subsection{What effect does including energy and quality-adjustment have 
+%             on the Solow residual in the Cobb-Douglas model?} 
+% \label{sec:quality_adj_energy_and_solow_residual}
+% %++++++++++++++++++++++++++++++
+% 
+% We'll first look at Portugal.
+% 
+% %------------------------------
+% \subsubsection{Portugal} 
+% %------------------------------
+% 
+% First, use non-quality-adjusted data for Portugal and the Cobb-Douglas model.
+% 
+% <<Portugal C-D undadjusted without energy>>=
+% naturalCoef(models$PT$unadjusted$noE$CD)
+% @
+% 
+% <<Portugal C-D undadjusted with energy>>=
+% naturalCoef(models$PT$unadjusted$withE$CD)
+% @
+% 
+% The Solow residual (\texttt{lambda}) is always negative. 
+% However, the absolute value of \texttt{lambda} decreases from 
+% \Sexpr{naturalCoef(models$PT$unadjusted$noE$CD)$lambda} to 
+% \Sexpr{naturalCoef(models$PT$unadjusted$withE$CD)$lambda}
+% when adding energy.
+% So it appears that for Portugal, 
+% using unadjusted inputs and including energy as a factor of production
+% reduces the absolute value of the Solow residual somewhat.
+% 
+% What about for quality-adjusted data and Portugal?
+% 
+% <<Portugal C-D adjusted without energy>>=
+% naturalCoef(models$PT$adjusted$noE$CD)
+% @
+% 
+% <<Portugal C-D adjusted with energy>>=
+% naturalCoef(models$PT$adjusted$withE$CD)
+% @
+% 
+% Using quality-adjusted inputs, the Solow residual (\texttt{lambda}) moves from 
+% \Sexpr{naturalCoef(models$PT$adjusted$noE$CD)$lambda} to
+% \Sexpr{naturalCoef(models$PT$adjusted$withE$CD)$lambda} when including energy.
+% The absolute value of the Solow residual again decreases when adding energy.
+% But, with quality-adjusted inputs, the effect is much stronger.
+% 
+% Table~\ref{tab:lambda_CD_PT} shows
+% the effect of both quality-corrected factors of production and energy.
+% We find that including energy as a factor of production 
+% reduces the absolute value of the Solow residual (\texttt{lambda})
+% whether or not the factors of production are quality-adjusted. 
+% Quality-adjustment gets part of the way toward eliminating the Solow residual.
+% 
+% \begin{table} \caption{Portugal Solow residual results with Cobb-Douglas.} 
+% \label{tab:lambda_CD_PT} 
+%   \begin{center}
+%     \begin{tabular}{r c c} 
+%       \toprule
+%                       & Unadjusted     & Quality-adjusted   \\
+%       \midrule
+%       Without energy  & \Sexpr{naturalCoef(models$PT$unadjusted$noE$CD)$lambda}    & \Sexpr{naturalCoef(models$PT$adjusted$noE$CD)$lambda} \\
+%       With energy     & \Sexpr{naturalCoef(models$PT$unadjusted$withE$CD)$lambda}  & \Sexpr{naturalCoef(models$PT$adjusted$withE$CD)$lambda} \\
+%       \bottomrule
+%     \end{tabular}
+%   \end{center}
+% \end{table}
+% 
+% Note that for Portugal the contribution of capital (\texttt{alpha\_1})
+% always shifts to energy (\texttt{alpha\_3}) when energy is included 
+% as a factor of production.
+% 
+% What about for the UK?
+% 
+% %------------------------------
+% \subsubsection{United Kingdom} 
+% %------------------------------
+% 
+% Table~\ref{tab:lambda_CD_UK} shows fitted Cobb-Douglas coefficients for the UK. 
+% 
+% \begin{table} \caption{UK Solow residual results with Cobb-Douglas.} 
+% \label{tab:lambda_CD_UK} 
+%   \begin{center}
+%     \begin{tabular}{r c c} 
+%       \toprule
+%                       & Unadjusted     & Quality-adjusted   \\
+%       \midrule
+%       Without energy  & \Sexpr{naturalCoef(models$UK$unadjusted$noE$CD)$lambda}   
+%                                                 & \Sexpr{naturalCoef(models$UK$adjusted$noE$CD)$lambda} \\
+%       With energy     & \Sexpr{naturalCoef(models$UK$unadjusted$withE$CD)$lambda} 
+%                                                 & \Sexpr{naturalCoef(models$UK$adjusted$withE$CD)$lambda} \\
+%       \bottomrule
+%     \end{tabular}
+%   \end{center}
+% \end{table}
+% 
+% For the UK, the quality-adjusted, with energy Solow residual is 
+% \Sexpr{naturalCoef(models$UK$adjusted$withE$CD)$lambda * 100}\%,
+% a very small number indeed.
+% For the UK, it appears that \emph{both} quality-adjustment and addition of energy as a factor of production
+% are required to effectively eliminate the Solow residual,
+% reducing it to \Sexpr{naturalCoef(models$UK$adjusted$withE$CD)$lambda}.
+% 
+% Adding energy alone actually \emph{in}creases the Solow residual from 
+% \Sexpr{naturalCoef(models$UK$unadjusted$noE$CD)$lambda} to
+% \Sexpr{naturalCoef(models$UK$unadjusted$withE$CD)$lambda}.
+% The details for each model with unadjusted factors of production are shown below.
+% 
+% <<UK CD Unadjusted Coefficients>>=
+% naturalCoef(models$UK$unadjusted$noE$CD)
+% naturalCoef(models$UK$unadjusted$withE$CD)
+% @
+% 
+% When energy is included, much of the effect of capital (\texttt{alpha\_1}) is 
+% attributed to energy (\texttt{alpha\_3}), 
+% as \texttt{alpha\_1} moves from 
+% \Sexpr{naturalCoef(models$UK$unadjusted$noE$CD)$alpha_1} to
+% \Sexpr{naturalCoef(models$UK$unadjusted$withE$CD)$alpha_1}.
+% 
+% When we look at quality-adjusted inputs, we find similar results.
+% 
+% <<UK CD Quality-adjusted Coefficients>>=
+% naturalCoef(models$UK$adjusted$noE$CD)
+% naturalCoef(models$UK$adjusted$withE$CD)
+% @
+% 
+% \texttt{alpha\_1} moves from 
+% \Sexpr{naturalCoef(models$UK$adjusted$noE$CD)$alpha_1} to
+% \Sexpr{naturalCoef(models$UK$adjusted$withE$CD)$alpha_1}.
+% 
+% Now, let's compare the fits to historical data.
+% 
+% 
+% 
+% %++++++++++++++++++++++++++++++
+% \subsection{Do we obtain a negative Solow residual for Portugal with the CES model?} 
+% \label{sec:Solow_negative_for_PT_in_CES?}
+% %++++++++++++++++++++++++++++++
+% 
+% First, look at the CES model without energy.
+% Nesting is unabmiguous, so this fit does not need to be repeated
+% for each nesting option. 
+% (This means that the top rows of Tables~\ref{tab:lambda_CES-kle_PT}--\ref{tab:lambda_CES-ekl_PT}
+% are identical.)
+% 
+% <<PT CES-kl, warning=FALSE>>=
+% naturalCoef(models$PT$unadjusted$noE$CES$kl)
+% naturalCoef(models$PT$adjusted$noE$CES$kl)
+% @
+% 
+% Both unadjusted and quality-adjusted variables give positive Solow residuals,
+% \Sexpr{naturalCoef(models$PT$unadjusted$noE$CES$kl)$lambda} for unadjusted inputs and
+% \Sexpr{naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda} for quality-adjusted inputs.
+% Furthermore, quality-adjustment reduces the magnitude of the Solow residual.
+% 
+% %------------------------------
+% \subsubsection{($kl$)$e$ nesting} 
+% %------------------------------
+% 
+% Now, look at unadjusted inputs using the ($kl$)$e$ nesting.
+% 
+% <<PT CES-kle unadjusted, warning=FALSE>>=
+% naturalCoef(models$PT$unadjusted$withE$CES$kle)
+% @
+% 
+% Now look at quality-adjusted inputs using the ($kl$)$e$ nesting.
+% 
+% <<PT CES-kle quality-adjusted, warning=FALSE>>=
+% naturalCoef(models$PT$adjusted$withE$CES$kle)
+% @
+% 
+% Table~\ref{tab:lambda_CES-kle_PT} summarizes the Portugal Solow residual results with CES and the ($kl$)$e$ nesting.
+% 
+% \begin{table} \caption{Portugal Solow residual results with CES and ($kl$)$e$ nesting.} 
+% \label{tab:lambda_CES-kle_PT} 
+%   \begin{center}
+%     \begin{tabular}{r c c} 
+%       \toprule
+%                       & Unadjusted     & Quality-adjusted   \\
+%       \midrule
+%       Without energy  & \Sexpr{naturalCoef(models$PT$unadjusted$noE$CES$kl)$lambda} 
+%                                                             & \Sexpr{naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda} \\
+%       With energy     & \Sexpr{naturalCoef(models$PT$unadjusted$withE$CES$kle)$lambda} 
+%                                                             & \Sexpr{naturalCoef(models$PT$adjusted$withE$CES$kle)$lambda} \\
+%       \bottomrule
+%     \end{tabular}
+%   \end{center}
+% \end{table}
+% 
+% Table~\ref{tab:sse_CES-kle_PT} shows the $sse$ values for each of these models.
+% 
+% \begin{table} \caption{PT $sse$ with CES and ($kl$)$e$ nesting.} 
+% \label{tab:sse_CES-kle_PT} 
+%   \begin{center}
+%     \begin{tabular}{r c c} 
+%       \toprule
+%                       & Unadjusted     & Quality-adjusted   \\
+%       \midrule
+%       Without energy  & \Sexpr{EconModels:::sse(models$PT$unadjusted$noE$CES$kl)$sse} 
+%                                                             & \Sexpr{EconModels:::sse(models$PT$adjusted$noE$CES$kl)$sse} \\
+%       With energy     & \Sexpr{EconModels:::sse(models$PT$unadjusted$withE$CES$kle)$sse} 
+%                                                             & \Sexpr{EconModels:::sse(models$PT$adjusted$withE$CES$kle)$sse} \\
+%       \bottomrule
+%     \end{tabular}
+%   \end{center}
+% \end{table}
+% 
+% In contrast to the Cobb-Douglas model,
+% the CES model with ($kl$)$e$ nesting
+% produces positive Solow residuals in all cases. 
+% We also see that both 
+% quality-adjusting the inputs and
+% including energy
+% reduce the Solow residual (\texttt{lambda}).
+% 
+% %------------------------------
+% \subsubsection{($le$)$k$ nesting} 
+% %------------------------------
+% 
+% Next, look at unadjusted inputs using the ($le$)$k$ nesting.
+% 
+% <<PT CES-lek unadjusted, warning=FALSE>>=
+% naturalCoef(models$PT$unadjusted$withE$CES$lek)
+% @
+% 
+% Now look at quality-adjusted inputs using the ($le$)$k$ nesting.
+% 
+% <<PT CES-lek quality-adjusted, warning=FALSE>>=
+% naturalCoef(models$PT$adjusted$withE$CES$lek)
+% @
+% 
+% Table~\ref{tab:lambda_CES-lek_PT} summarizes the Portugal Solow residual results with CES and the ($le$)$k$ nesting.
+% 
+% \begin{table} \caption{Portugal Solow residual results with CES and ($le$)$k$ nesting.} 
+% \label{tab:lambda_CES-lek_PT} 
+%   \begin{center}
+%     \begin{tabular}{r c c} 
+%       \toprule
+%                       & Unadjusted     & Quality-adjusted   \\
+%       \midrule
+%       Without energy  & \Sexpr{naturalCoef(models$PT$unadjusted$noE$CES$kl)$lambda} 
+%                                         & \Sexpr{naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda} \\
+%       With energy     & \Sexpr{naturalCoef(models$PT$unadjusted$withE$CES$lek)$lambda} 
+%                                         & \Sexpr{naturalCoef(models$PT$adjusted$withE$CES$lek)$lambda} \\
+%       \bottomrule
+%     \end{tabular}
+%   \end{center}
+% \end{table}
+% 
+% Table~\ref{tab:sse_CES-lek_PT} shows the $sse$ values for each of these models.
+% 
+% \begin{table} \caption{PT $sse$ with CES and ($le$)$k$ nesting.} 
+% \label{tab:sse_CES-lek_PT} 
+%   \begin{center}
+%     \begin{tabular}{r c c} 
+%       \toprule
+%                       & Unadjusted     & Quality-adjusted   \\
+%       \midrule
+%       Without energy  & \Sexpr{EconModels:::sse(models$PT$unadjusted$noE$CES$kl)$sse} 
+%                                         & \Sexpr{EconModels:::sse(models$PT$adjusted$noE$CES$kl)$sse} \\
+%       With energy     & \Sexpr{EconModels:::sse(models$PT$unadjusted$withE$CES$lek)$sse} 
+%                                         & \Sexpr{EconModels:::sse(models$PT$adjusted$withE$CES$lek)$sse} \\
+%       \bottomrule
+%     \end{tabular}
+%   \end{center}
+% \end{table}
+% 
+% Similar to the CES model with ($kl$)$e$ nesting,
+% the CES model with ($le$)$k$ nesting
+% produces positive Solow residuals in all cases. 
+% After energy has been added, quality-adjustment 
+% has very little effect on the Solow residual,
+% creating a slight increase from 
+% \Sexpr{naturalCoef(models$PT$unadjusted$withE$CES$lek)$lambda} to
+% \Sexpr{naturalCoef(models$PT$adjusted$withE$CES$lek)$lambda}.
+% 
+% 
+% %------------------------------
+% \subsubsection{($ek$)$l$ nesting} 
+% %------------------------------
+% 
+% Next, look at unadjusted inputs using the ($ek$)$l$ nesting.
+% 
+% <<PT CES-ekl unadjusted, warning=FALSE>>=
+% naturalCoef(models$PT$unadjusted$withE$CES$ekl)
+% @
+% 
+% Now look at quality-adjusted inputs using the ($ek$)$l$ nesting.
+% 
+% <<PT CES-ekl quality-adjusted, warning=FALSE>>=
+% naturalCoef(models$PT$adjusted$withE$CES$ekl)
+% @
+% 
+% Table~\ref{tab:lambda_CES-ekl_PT} summarizes the Portugal Solow residual results with CES and the ($ek$)$l$ nesting.
+% 
+% \begin{table} \caption{Portugal Solow residual results with CES and ($ek$)$l$ nesting.} 
+% \label{tab:lambda_CES-ekl_PT} 
+%   \begin{center}
+%     \begin{tabular}{r c c} 
+%       \toprule
+%                       & Unadjusted     & Quality-adjusted   \\
+%       \midrule
+%       Without energy  & \Sexpr{naturalCoef(models$PT$unadjusted$noE$CES$kl)$lambda} 
+%                                         & \Sexpr{naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda} \\
+%       With energy     & \Sexpr{naturalCoef(models$PT$unadjusted$withE$CES$ekl)$lambda} 
+%                                         & \Sexpr{naturalCoef(models$PT$adjusted$withE$CES$ekl)$lambda} \\
+%       \bottomrule
+%     \end{tabular}
+%   \end{center}
+% \end{table}
+% 
+% Table~\ref{tab:sse_CES-ekl_PT} shows the $sse$ values for each of these models.
+% 
+% \begin{table} \caption{PT $sse$ with CES and ($ek$)$l$ nesting.} 
+% \label{tab:sse_CES-ekl_PT} 
+%   \begin{center}
+%     \begin{tabular}{r c c} 
+%       \toprule
+%                       & Unadjusted     & Quality-adjusted   \\
+%       \midrule
+%       Without energy  & \Sexpr{EconModels:::sse(models$PT$unadjusted$noE$CES$kl)$sse} 
+%                                         & \Sexpr{EconModels:::sse(models$PT$adjusted$noE$CES$kl)$sse} \\
+%       With energy     & \Sexpr{EconModels:::sse(models$PT$unadjusted$withE$CES$ekl)$sse} 
+%                                         & \Sexpr{EconModels:::sse(models$PT$adjusted$withE$CES$ekl)$sse} \\
+%       \bottomrule
+%     \end{tabular}
+%   \end{center}
+% \end{table}
+% 
+% For the ($ek$)$l$ nesting, 
+% the Solow residual is positive, and 
+% quality-adjusting the inputs 
+% reduces the Solow residual (\texttt{lambda}).
+% Adding energy decreases the Solow residual 
+% (from \Sexpr{naturalCoef(models$PT$unadjusted$withE$CES$ekl)$lambda} to 
+% \Sexpr{naturalCoef(models$PT$adjusted$withE$CES$ekl)$lambda})
+% when enegy is included in the model.
+% But, adding energy slightly increases the Solow residual
+% (from \Sexpr{naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda} to \Sexpr{naturalCoef(models$PT$adjusted$withE$CES$ekl)$lambda})
+% when quality-adjusted inputs are used.
+% 
+% 
+% %++++++++++++++++++++++++++++++
+% \subsection{Do we obtain a positive Solow residual for the UK with the CES model?} 
+% \label{sec:Solow_positive_for_UK_in_CES?}
+% %++++++++++++++++++++++++++++++
+% 
+% First, look at the CES model without energy.
+% Nesting is unabmiguous, so this fit does not need to be repeated
+% for each nesting option. 
+% (This means that the top rows of Tables~\ref{tab:lambda_CES-kle_UK}--\ref{tab:lambda_CES-ekl_UK}
+% are identical.)
+% 
+% <<UK CES-kl, warning=FALSE>>=
+% naturalCoef(models$UK$unadjusted$noE$CES$kl)
+% naturalCoef(models$UK$adjusted$noE$CES$kl)
+% @
+% 
+% Both unadjusted and quality-adjusted variables give positive Solow residuals for the UK,
+% \Sexpr{naturalCoef(models$UK$unadjusted$noE$CES$kl)$lambda} for unadjusted inputs and
+% \Sexpr{naturalCoef(models$UK$adjusted$noE$CES$kl)$lambda} for quality-adjusted inputs.
+% Furthermore, quality-adjustment reduces the magnitude of the UK Solow residual.
+% 
+% %------------------------------
+% \subsubsection{($kl$)$e$ nesting} 
+% %------------------------------
+% 
+% Now, look at unadjusted inputs using the ($kl$)$e$ nesting.
+% 
+% <<UK CES-kle unadjusted>>=
+% naturalCoef(models$UK$unadjusted$withE$CES$kle)
+% @
+% 
+% Now look at quality-adjusted inputs using the ($kl$)$e$ nesting.
+% 
+% <<UK CES-kle quality-adjusted>>=
+% naturalCoef(models$UK$adjusted$withE$CES$kle)
+% @
+% 
+% Table~\ref{tab:lambda_CES-kle_UK} summarizes the UK Solow residual results with CES and the ($kl$)$e$ nesting.
+% 
+% \begin{table} \caption{UK Solow residual results with CES and ($kl$)$e$ nesting.} 
+% \label{tab:lambda_CES-kle_UK} 
+%   \begin{center}
+%     \begin{tabular}{r c c} 
+%       \toprule
+%                       & Unadjusted     & Quality-adjusted   \\
+%       \midrule
+%       Without energy  & \Sexpr{naturalCoef(models$UK$unadjusted$noE$CES$kl)$lambda} & \Sexpr{naturalCoef(models$UK$adjusted$noE$CES$kl)$lambda} \\
+%       With energy     & \Sexpr{naturalCoef(models$UK$unadjusted$withE$CES$kle)$lambda} 
+%                                                                 & \Sexpr{naturalCoef(models$UK$adjusted$withE$CES$kle)$lambda} \\
+%       \bottomrule
+%     \end{tabular}
+%   \end{center}
+% \end{table}
+% 
+% Table~\ref{tab:sse_CES-kle_UK} shows the $sse$ values for each of these models.
+% 
+% \begin{table} \caption{UK $sse$ with CES and ($kl$)$e$ nesting.} 
+% \label{tab:sse_CES-kle_UK} 
+%   \begin{center}
+%     \begin{tabular}{r c c} 
+%       \toprule
+%                       & Unadjusted     & Quality-adjusted   \\
+%       \midrule
+%       Without energy  & \Sexpr{EconModels:::sse(models$UK$unadjusted$noE$CES$kl)$sse} & \Sexpr{EconModels:::sse(models$UK$adjusted$noE$CES$kl)$sse} \\
+%       With energy     & \Sexpr{EconModels:::sse(models$UK$unadjusted$withE$CES$kle)$sse} 
+%                                                             & \Sexpr{EconModels:::sse(models$UK$adjusted$withE$CES$kle)$sse} \\
+%       \bottomrule
+%     \end{tabular}
+%   \end{center}
+% \end{table}
+% 
+% Like the Cobb-Douglas model, the CES model produces positive Solow residuals
+% with the ($kl$)$e$ nesting.
+% We also see that both 
+% quality-adjusting the inputs and
+% including energy
+% reduce the Solow residual (\texttt{lambda}).
+% 
+% %------------------------------
+% \subsubsection{($le$)$k$ nesting}
+% %------------------------------
+% 
+% Next, look at unadjusted inputs using the ($le$)$k$ nesting.
+% 
+% <<UK CES-lek unadjusted>>=
+% naturalCoef(models$UK$unadjusted$withE$CES$lek)
+% @
+% 
+% Now look at quality-adjusted inputs using the ($le$)$k$ nesting.
+% 
+% <<UK CES-lek quality-adjusted>>=
+% naturalCoef(models$UK$adjusted$withE$CES$lek)
+% @
+% 
+% Table~\ref{tab:lambda_CES-lek_UK} summarizes the UK Solow residual results with CES and the ($le$)$k$ nesting.
+% 
+% \begin{table} \caption{UK Solow residual results with CES and ($le$)$k$ nesting.} 
+% \label{tab:lambda_CES-lek_UK} 
+%   \begin{center}
+%     \begin{tabular}{r c c} 
+%       \toprule
+%                       & Unadjusted     & Quality-adjusted   \\
+%       \midrule
+%       Without energy  & \Sexpr{naturalCoef(models$UK$unadjusted$noE$CES$kl)$lambda} & \Sexpr{naturalCoef(models$UK$adjusted$noE$CES$kl)$lambda} \\
+%       With energy     & \Sexpr{naturalCoef(models$UK$unadjusted$withE$CES$lek)$lambda} 
+%                                                             & \Sexpr{naturalCoef(models$UK$adjusted$withE$CES$lek)$lambda} \\
+%       \bottomrule
+%     \end{tabular}
+%   \end{center}
+% \end{table}
+% 
+% Table~\ref{tab:sse_CES-lek_UK} shows the $sse$ values for each of these models.
+% 
+% \begin{table} \caption{UK $sse$ with CES and ($le$)$k$ nesting.} 
+% \label{tab:sse_CES-lek_UK} 
+%   \begin{center}
+%     \begin{tabular}{r c c} 
+%       \toprule
+%                       & Unadjusted     & Quality-adjusted   \\
+%       \midrule
+%       Without energy  & \Sexpr{EconModels:::sse(models$UK$unadjusted$noE$CES$kl)$sse} & \Sexpr{EconModels:::sse(models$UK$adjusted$noE$CES$kl)$sse} \\
+%       With energy     & \Sexpr{EconModels:::sse(models$UK$unadjusted$withE$CES$lek)$sse} 
+%                                                             & \Sexpr{EconModels:::sse(models$UK$adjusted$withE$CES$lek)$sse} \\
+%       \bottomrule
+%     \end{tabular}
+%   \end{center}
+% \end{table}
+% 
+% 
+% Similar to the CES model with ($kl$)$e$ nesting,
+% the CES model with ($le$)$k$ nesting
+% produces positive Solow residuals in all cases. 
+% Both quality-adjustment and inclusion of energy 
+% decrease the magnitude of the Solow residual.
+% 
+% %------------------------------
+% \subsubsection{($ek$)$l$ nesting}
+% %------------------------------
+% 
+% Next, look at unadjusted inputs using the ($el$)$l$ nesting.
+% 
+% <<UK CES-ekl unadjusted>>=
+% naturalCoef(models$UK$unadjusted$withE$CES$ekl)
+% @
+% 
+% Now look at quality-adjusted inputs using the ($ek$)$l$ nesting.
+% 
+% <<UK CES-ekl quality-adjusted>>=
+% naturalCoef(models$UK$adjusted$withE$CES$ekl)
+% @
+% 
+% Table~\ref{tab:lambda_CES-ekl_UK} summarizes the UK Solow residual results with CES and the ($ek$)$l$ nesting.
+% 
+% \begin{table} \caption{UK Solow residual results with CES and ($ek$)$l$ nesting.} 
+% \label{tab:lambda_CES-ekl_UK} 
+%   \begin{center}
+%     \begin{tabular}{r c c} 
+%       \toprule
+%                       & Unadjusted     & Quality-adjusted   \\
+%       \midrule
+%       Without energy  & \Sexpr{naturalCoef(models$UK$unadjusted$noE$CES$kl)$lambda} & \Sexpr{naturalCoef(models$UK$adjusted$noE$CES$kl)$lambda} \\
+%       With energy     & \Sexpr{naturalCoef(models$UK$unadjusted$withE$CES$ekl)$lambda} 
+%                                                             & \Sexpr{naturalCoef(models$UK$adjusted$withE$CES$ekl)$lambda} \\
+%       \bottomrule
+%     \end{tabular}
+%   \end{center}
+% \end{table}
+% 
+% Table~\ref{tab:sse_CES-ekl_UK} shows the $sse$ values for each of these models.
+% 
+% \begin{table} \caption{UK $sse$ with CES and ($ek$)$l$ nesting.} 
+% \label{tab:sse_CES-ekl_UK} 
+%   \begin{center}
+%     \begin{tabular}{r c c} 
+%       \toprule
+%                       & Unadjusted     & Quality-adjusted   \\
+%       \midrule
+%       Without energy  & \Sexpr{EconModels:::sse(models$UK$unadjusted$noE$CES$kl)$sse} & \Sexpr{EconModels:::sse(models$UK$adjusted$noE$CES$kl)$sse} \\
+%       With energy     & \Sexpr{EconModels:::sse(models$UK$unadjusted$withE$CES$ekl)$sse} 
+%                                                             & \Sexpr{EconModels:::sse(models$UK$adjusted$withE$CES$ekl)$sse} \\
+%       \bottomrule
+%     \end{tabular}
+%   \end{center}
+% \end{table}
+% 
+% 
+% Similar to the CES model with ($ek$)$l$ nesting,
+% the CES model with ($ek$)$l$ nesting
+% produces positive Solow residuals in all cases. 
+% Both quality-adjustment and inclusion of energy 
+% decrease the magnitude of the Solow residual.
+
+%' %++++++++++++++++++++++++++++++
+%' \subsection{Dynamic Solow residuals} 
+%' \label{sec:dynamic_solow_residuals}
+%' %++++++++++++++++++++++++++++++
+%' 
+%' <<Dynamic Solow Residuals>>=
+%' # Calculate finite difference approximations of time derivatives for output and all factors of production
+%' dynamicSR <- function(model, id, lag=1, pad="tail"){
+%'   id_list <- strsplit(id, split = "[.]")[[1]]
+%'   energy <- id_list[[3]]
+%'   modelStr <- id_list[[4]]
+%'   
+%'   f <- model$formula
+%'   denom <- summands(f, n=length(summands(f))) # time variable
+%'   nums <- all.vars(f) [1:(length(all.vars(f))-1)] # y, k, l, and e (if present)
+%'   df <- getData(model)[c(denom, nums)] # columns are: iYear, y, k, l, and e (if present)
+%'   
+%'   # Calculate names for the columns of finite difference derivatives
+%'   derivNames <- lapply(1:length(nums), function(i){paste0("d", nums[[i]], ".d", denom)}) %>% unlist
+%'   derivCols <- lapply(1:length(nums), function(i){
+%'     # Calculate finite difference derivative columns
+%'     ediff(df[[i+1]], pad=pad, lag=lag) / ediff(df[[1]], pad=pad, lag=lag)
+%'   }) %>% do.call(cbind, .) %>% as.data.frame
+%'   names(derivCols) <- derivNames  
+%'   df <- cbind(derivCols, df[ , c(nums, denom)]) # puts derivatives first, then raw numbers, then time
+%'   df[["dydtOvery"]] <- 1 / df[[ nums[[1]] ]] * df[[ derivNames[[1]] ]]
+%'   coeffs <- naturalCoef(model)
+%'   df <- cbind(df, coeffs)
+%'   
+%'   if (modelStr == "CD"){
+%'     lambda_fd <- 
+%'       df[["dydtOvery"]] - 
+%'       df[["alpha_1"]] / df[[nums[[2]]]] * df[[derivNames[[2]]]] - 
+%'       df[["alpha_2"]] / df[[nums[[3]]]] * df[[derivNames[[3]]]]
+%'     if (energy == "withE"){
+%'       # Subtract the energy term also
+%'       lambda_fd <- lambda_fd - 
+%'         df[["alpha_3"]] / df[[nums[[4]]]] * df[[derivNames[[4]]]]
+%'     }
+%'     # Fraction of growth explained by Solow Residual
+%'     solowFrac <- lambda_fd / df[["dydtOvery"]]
+%'     # Add to data frame
+%'     df$lambda_fd <- lambda_fd
+%'     df$solowFrac <- solowFrac
+%'     return(df)
+%'   } else if (modelStr == "CES"){
+%'     # Assign nice variable names so that the equations below are easier to read (and debug, and maintain)
+%'     # This code is nest-aware.
+%'     n <- model$nest
+%'     for (i in 1:length(model$nest)){
+%'       df[[paste0("x", i)]] <- df[[ nums[ model$nest[i]+1 ] ]] # GDP is 1st col, add 1 to get to the factors of production
+%'       df[[paste0("dx", i, "dt")]] <- df[[ derivNames[ model$nest[i]+1 ] ]]
+%'     }
+%'     if (energy == "noE"){
+%'       # Calculate terms for the finite-difference Solow residual (lambda_fd)
+%'       df <- df %>% 
+%'         transform(b = delta_1 * x1^(-rho_1) + (1 - delta_1) * x2^(-rho_1)) %>%
+%'         transform(dbdtOverrho1 = -delta_1 * x1^(-(rho_1+1))*dx1dt - (1 - delta_1) * x2^(-(rho_1+1))*dx2dt) %>%
+%'         transform(lambda_fd = dydtOvery + 1/b * dbdtOverrho1) %>%
+%'         transform(solowFrac = lambda_fd / dydtOvery)
+%'       return(df)
+%'     } else if (energy == "withE"){
+%'       df <- df %>% 
+%'         transform(b = delta_1 * x1^(-rho_1) + (1 - delta_1) * x2^(-rho_1)) %>%
+%'         transform(a = delta * b^(rho/rho_1) + (1 - delta) * x3^(-rho)) %>%
+%'         transform(dbdtOverrho1 = -delta_1 * x1^(-(rho_1+1))*dx1dt - (1 - delta_1) * x2^(-(rho_1+1))*dx2dt) %>%
+%'         transform(dadtOverrho = delta * b^(rho/rho_1 - 1) * dbdtOverrho1 - (1 - delta) * x3^(-(rho+1))*dx3dt) %>%
+%'         transform(lambda_fd = dydtOvery + 1/a * dadtOverrho) %>%
+%'         transform(solowFrac = lambda_fd / dydtOvery)
+%'       return(df)
+%'     } else {
+%'       stop (paste("Unknown energy:", energy))
+%'     }
+%'   } else {
+%'     stop(paste("Unknown modelStr", modelStr))
+%'   }
+%' }
+%' 
+%' lag.to.use <- 1 # years
+%' temp_data <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), 
+%'                         f = function(model, id, lag=lag.to.use, pad="tail"){
+%'   df <- dynamicSR(model, id=id, lag=lag, pad=pad)
+%'   id_list <- strsplit(id, split = "[.]")[[1]]
+%'   df$Country <- id_list[[1]]
+%'   df$flavor <- if (id_list[[2]] == "unadjusted") "Unadjusted" else "Quality-adjusted"
+%'   df$energy <- if (id_list[[3]] == "noE") "Without energy" else "With energy"
+%'   df$model <- id_list[[4]]
+%'   df$nest <- if (length(id_list) > 4) id_list[[5]] else NA
+%'   df$Year <- getData(model)[["Year"]]
+%'   return(df)  
+%' }) %>% do.call(plyr::rbind.fill, .)
+%' 
+%' # Get the unadjusted, without-energy Solow residuals and store them in a data frame
+%' sr_unadj_noE <- filter(temp_data, flavor=="Unadjusted" & energy=="Without energy") %>% 
+%'                 select(Year, Country, lambda_fd, model)
+%' colnames(sr_unadj_noE)[colnames(sr_unadj_noE)=="lambda_fd"] <- "sr_unadj_noE"
+%' # Merge to get the unadjusted, without-energy values next to each country, year, and model
+%' solowResiduals <- merge(temp_data, sr_unadj_noE)
+%' 
+%' # Create a column containing ∆lambda_df, the difference between a lambda_df value
+%' # and the lambda_df value in the same year for the unadjusted, no-energy case
+%' solowResiduals[["Dlambda_fd"]] <- abs(solowResiduals[["lambda_fd"]]) - abs(solowResiduals[["sr_unadj_noE"]])
+%' 
+%' # Relevel factors before plotting
+%' solowResiduals$Country <- relevelFactor(as.factor(solowResiduals$Country), c("PT", "UK"))
+%' solowResiduals$flavor <- relevelFactor(as.factor(solowResiduals$flavor), c("Unadjusted", "Quality-adjusted"))
+%' solowResiduals$energy <- relevelFactor(as.factor(solowResiduals$energy), c("Without energy", "With energy"))
+%' solowResiduals$nest <- relevelFactor(as.factor(solowResiduals$nest), c("kl", "kle", "lek", "ekl"))
+%' 
+%' # Make data viewing easier
+%' solowResiduals <- arrange(solowResiduals, Country, model, flavor, energy, nest)
+%' @
+%' 
+%' <<DynamicSR_Graph>>=
+%' dynamicSRGraph <- function(data){
+%' ggplot(data=data) +
+%'   geom_line(data=filter(data, energy=="Without energy"), mapping=aes(x=Year, y=dydtOvery)) +
+%'   geom_line(mapping=aes(x=Year, y=lambda_fd, linetype=energy)) +
+%'   scale_linetype_manual(values=c(2,3), name="") +
+%'   facet_grid(Country ~ flavor) +
+%'   scale_x_continuous(breaks=c(1960, 1980, 2000)) +
+%'   xlab("") + 
+%'   ylab(expression(lambda[ij])) +
+%'   xy_theme()  
+%' }
+%' @
+%' 
+%' ``Dynamic'' Solow residuals~($\lambda_{i,j}$) can be calculated 
+%' for the Cobb-Douglas and CES models
+%' as shown in Appendices~\ref{sec:dynamic_sr_CD} and~\ref{sec:dynamic_sr_CES},
+%' respectively.
+%' 
+%' Figure~\ref{fig:DynamicSR_CD_Graph} shows the evolution 
+%' of the Solow residual~($\lambda_{i,j}$) over time
+%' as calculated by Equation~\ref{eq:lambdaij} 
+%' with the timespan for finite differences ($t_j - t_i$) set to 
+%' \Sexpr{lag.to.use}~\Sexpr{if (lag.to.use == 1) "year" else "years"}.
+%' %
+%' <<DynamicSR_CD_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residuals for the Cobb-Douglas model.
+Dashed lines are $\\lambda$ values.
+Solid lines are $\\frac{1}{y}\\frac{\\mathrm{d} y}{\\mathrm{d} t}$.">>=
+%' dynamicSRGraph(filter(solowResiduals, model=="CD"))
+%' @
+%' %
+%' <<DynamicSR_CESkle_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residuals for the CES model with ($kl$)$e$ nesting.
+Dashed lines are $\\lambda$ values.
+Solid lines are $\\frac{1}{y}\\frac{\\mathrm{d} y}{\\mathrm{d} t}$.">>=
+%' dynamicSRGraph(filter(solowResiduals, model=="CES" & (nest=="kle" | nest=="kl")))
+%' @
+%' %
+%' <<DynamicSR_CESlek_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residuals for the CES model with ($le$)$k$ nesting.
+Dashed lines are $\\lambda$ values.
+Solid lines are $\\frac{1}{y}\\frac{\\mathrm{d} y}{\\mathrm{d} t}$.">>=
+%' dynamicSRGraph(filter(solowResiduals, model=="CES" & (nest=="lek" | nest=="kl")))
+%' @
+%' %
+%' <<DynamicSR_CESekl_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residuals for the CES model with ($ek$)$l$ nesting.
+Dashed lines are $\\lambda$ values.
+Solid lines are $\\frac{1}{y}\\frac{\\mathrm{d} y}{\\mathrm{d} t}$.">>=
+%' dynamicSRGraph(filter(solowResiduals, model=="CES" & (nest=="ekl" | nest=="kl")))
+%' @
+
+%' %++++++++++++++++++++++++++++++
+%' \subsection{Does quality-adjusting the factors of production 
+%'             decrease fitting residuals and/or the dynamic Solow residual?} 
+%' \label{sec:quality_adj_energy_and_dynamic_solow_residual}
+%' %++++++++++++++++++++++++++++++
+%' 
+%' <<SR and R trajectory data>>=
+%' traj.data <- merge(solowResiduals[c("Country", "Year", "model", "flavor", "energy", "nest", "Dlambda_fd")], 
+%'                    fitted_and_resid_data[c("Country", "Year", "model", "flavor", "energy", "nest", "Dr")]) %>%
+%'                    arrange(Country, model, flavor, energy, nest)
+%' traj.data.stats <- traj.data %>% 
+%'   group_by(model, Country, flavor, energy, nest) %>%
+%'   summarise(Dlambda_fd.mean = mean(Dlambda_fd, na.rm=TRUE), Dr.mean = mean(Dr))
+%' 
+%' ############################################
+%' # Dlambda_fd.p <- traj.data %>% 
+%' #   group_by(model, Country, flavor, energy, nest) %>% 
+%' #   select(Dlambda_fd) %>%
+%' #   t.test(., alternative="less")[["p.value"]]
+%' ############################################  
+%' @
+%' 
+%' <<SR and R trajectory plot function>>=
+%' residualsTrajGraph <- function(data){
+%'   plot <- ggplot(data=data) + 
+%'     geom_point(mapping=aes(x=Dr, y=Dlambda_fd, color=energy)) + 
+%'     facet_grid(Country ~ flavor) +
+%'     xlab(expression(Delta*r[i])) +
+%'     ylab(expression(Delta*lambda[ij])) +
+%'     xy_theme() + 
+%'     theme(legend.title=element_blank())
+%'   return(plot)
+%' }
+%' @
+%' 
+%' We can test our hypothesis that quality-adjusting the factors of production
+%' and including energy will reduce the Solow residuals~($\lambda$)
+%' and the fitting residuals~($r$) by plotting
+%' $\Delta \lambda_i$ vs. $\Delta r_i$, where
+%' %
+%' \begin{equation} \label{eq:delta_lambda_i}
+%'   \Delta \lambda_i \equiv \left| \lambda_i \right| - \left| \lambda_{i, \, Unadjusted, \, Without \, energy} \right|
+%' \end{equation}
+%' %
+%' and
+%' %
+%' \begin{equation} \label{eq:delta_r}
+%'   \Delta r_i \equiv \left| r_i \right| - \left| r_{i, \,Unadjusted, \, Without \, energy} \right|.
+%' \end{equation}
+%' %
+%' If most of the points fall in the lower-left quadrant of a graph, 
+%' we can conclude that both Solow residual~($\lambda$) and
+%' fitting residual~($r$) have decreased due to either 
+%' quality-adjustment of the factors of production or 
+%' including energy.
+%' 
+%' Figure~\ref{fig:Solow_residual_trajectories_CD} indicates that
+%' for the Cobb-Douglas model, 
+%' neither 
+%' quality-adjusting the factors of production
+%' nor including energy 
+%' consistently reduces
+%' the Solow residual or the fitting residual.
+%' 
+%' <<Solow_residual_trajectories_CD, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residual and fitting residual trajectories relative to the Unadjusted, Without-energy condition for the Cobb-Douglas model.">>=
+%' residualsTrajGraph(filter(traj.data, model=="CD"))
+%' @
+%' 
+%' We can also calculate the average values for $\Delta \lambda_{i,j}$ and $\Delta r_{i}$ 
+%' as shown in Table~\ref{tab:Trajectory_Means_CD}.
+%' %
+%' <<Trajectory_Means_CD, results="asis">>=
+%' myXTable(data = filter(traj.data.stats, model=="CD") %>% select(-nest), 
+%'          caption = "Average $\\Delta\\lambda$ and $\\Delta r$ for Cobb-Douglas models.",
+%'          label=paste0("tab:", opts_current$get("label")),
+%'          digits=6)
+%' @
+%' %
+%' The following tables and figures show the same analysis for the CES model.
+%' %
+%' <<Solow_residual_trajectories_CESkle, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residual and fitting residual trajectories relative to the Unadjusted, Without-energy condition for the CES model with ($kl$)$e$ nesting.">>=
+%' residualsTrajGraph(filter(traj.data, model=="CES" & (nest=="kl" | nest=="kle")))
+%' @
+%' %
+%' <<Trajectory_Means_CESkle, results="asis">>=
+%' myXTable(data = filter(traj.data.stats, model=="CES" & (nest=="kl" | nest=="kle")), 
+%'          caption = "Average $\\Delta\\lambda$ and $\\Delta r$ for CES models with ($kl$)$e$ nesting.",
+%'          label=paste0("tab:", opts_current$get("label")),
+%'          digits=6)
+%' @
+%' 
+%' <<Solow_residual_trajectories_CESlek, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residual and fitting residual trajectories relative to the Unadjusted, Without-energy condition for the CES model with ($le$)$k$ nesting.">>=
+%' residualsTrajGraph(filter(traj.data, model=="CES" & (nest=="kl" | nest=="lek")))
+%' @
+%' 
+%' <<Trajectory_Means_CESlek, results="asis">>=
+%' myXTable(data = filter(traj.data.stats, model=="CES" & (nest=="kl" | nest=="lek")), 
+%'          caption = "Average $\\Delta\\lambda$ and $\\Delta r$ for CES models with ($le$)$k$ nesting.",
+%'          label=paste0("tab:", opts_current$get("label")),
+%'          digits=6)
+%' @
+%' 
+%' <<Solow_residual_trajectories_CESekl, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residual and fitting residual trajectories relative to the Unadjusted, Without-energy condition for the CES model with ($ek$)$l$ nesting.">>=
+%' residualsTrajGraph(filter(traj.data, model=="CES" & (nest=="kl" | nest=="ekl")))
+%' @
+%' 
+%' <<Trajectory_Means_CESekl, results="asis">>=
+%' myXTable(data = filter(traj.data.stats, model=="CES" & (nest=="kl" | nest=="ekl")), 
+%'          caption = "Average $\\Delta\\lambda$ and $\\Delta r$ for CES models with ($ek$)$l$ nesting.",
+%'          label=paste0("tab:", opts_current$get("label")),
+%'          digits=6)
+%' @
+%'
+
 \end{document}

### 2015-06-24 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Added notes about response() not working. This is for CST models only.

@@
     cdModCST$data <- sdata
+    cdModCST$response <- sdata$iGDP 
     modelsCST[[country]][["unadjusted"]][["noE"]][["CD"]] <- cdModCST
@@
   }
-
   # Save cost-share theorem models to disk.
@@
 fittedAndResidData <- function(model, id){
-  df <- data.frame(select(model$data, Year)) # getData doesn't work for lm models that are created for CST=TRUE.
+  # ******************************************
+  # getData doesn't work for lm models that are created for CST=TRUE.
+  # After we implement fixed values for alpha_1 and alpha_2 in our fitting functions, 
+  # getData(model) will probably work.
+  # At that time, change model$data to getData(model)
+  df <- data.frame(select(model$data, Year)) 
   # By including [c(1:length(df$Year))] on the end, we 
@@
 }
-
-temp_data_CST <- leaf_apply(modelsCST, class=c("plm", "lm"), f = function(model, id){
-  return(fittedAndResidData(model, id))
-}) %>% do.call(rbind, .)
-temp_data_CST$cst <- TRUE
-
 temp_data_noCST <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, id){
@@
 temp_data_noCST$cst <- FALSE
+
+temp_data_CST <- leaf_apply(modelsCST, class=c("plm", "lm"), f = function(model, id){
+  # ****************************************************
+  # Not all of the results from this code are not correct at this time.
+  # The residuals are OK.
+  # But, the yhat() call in fittedAndResidData() will not return the correct information from the CST models.
+  # This is because modelsCST was not created with our typical functions.
+  # To correct this problem, we need to add arguments to cdModel and cesModel such that 
+  # the models produced by those functions will be in the correct form for yhat() function.
+  return(fittedAndResidData(model, id))
+}) %>% do.call(rbind, .)
+temp_data_CST$cst <- TRUE
 
@@
 <<Fitted and Residual Graph Functions>>=
-fittedGraph <- function(data){
+fittedGraphCST <- function(data){
+  ggplot() +
+    geom_line(data=filter(data, cst==TRUE), mapping=aes(x=Year, y=iGDP)) +
+    geom_line(data=data, mapping=aes(x=Year, y=fitted, linetype=cst)) +
+    scale_linetype_manual(values=c(2,3), name="") +
+    facet_grid(Country ~ flavor) + 
+    xlab("") +
+    ylab("Indexed GDP (1960=1)") +
+    xy_theme()
+}
+
+fittedGraphNoCST <- function(data){
   ggplot() +
@@
 %
-<<Graphs CD-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Cobb-Douglas models. Solid line is historical GDP.">>=
-fittedGraph(filter(fitted_and_resid_data, model=="CD" & cst==FALSE))
+<<Graphs CD-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Cobb-Douglas models that reject the cost-share theorem. Solid line is historical GDP.">>=
+fittedGraphNoCST(filter(fitted_and_resid_data, model=="CD" & cst==FALSE))
 @
@@
 <<Graphs CESkle-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($kl$)$e$ nesting. Solid line is historical GDP.">>=
-fittedGraph(filter(fitted_and_resid_data, model=="CES" & cst==FALSE & (nest=="kle" | nest=="kl")))
+fittedGraphNoCST(filter(fitted_and_resid_data, model=="CES" & cst==FALSE & (nest=="kle" | nest=="kl")))
 @
@@
 <<Graphs CESlek-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($le$)$k$ nesting. Solid line is historical GDP.">>=
-fittedGraph(filter(fitted_and_resid_data, model=="CES" & cst==FALSE & (nest=="lek" | nest=="kl")))
+fittedGraphNoCST(filter(fitted_and_resid_data, model=="CES" & cst==FALSE & (nest=="lek" | nest=="kl")))
 @
@@
 <<Graphs CESekl-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($ek$)$l$ nesting. Solid line is historical GDP.">>=
-fittedGraph(filter(fitted_and_resid_data, model=="CES" & cst==FALSE & (nest=="ekl" | nest=="kl")))
+fittedGraphNoCST(filter(fitted_and_resid_data, model=="CES" & cst==FALSE & (nest=="ekl" | nest=="kl")))
 @

### 2015-06-26 Articles/Article_JAE_2014/Results_Comparisons/Results_Comparison.Rmd
Comparison between Stan and Matt.

---
title: "Comparison of CD Fits"
author: "MK Heun"
date: "June 26, 2015"
output: pdf_document
---

This document compares fits performed by Matt and Stan using
ZA data with `iLfi` for labor.

```{r Setup, echo=FALSE, include=FALSE}
require(EconData)
require(EconModels)
require(dplyr)
```

First, set up the data and the formula.

```{r Data and formula}
form <- iGDP ~ iK + iLfi + iYear
zaData <- filter(SUN, Country=="ZA")
# Keeps only the variabls that are in the formula
zaData <- subset(zaData, select=c(all.vars(form), "Year"))
# Removes any years that do not have complete information 
zaData <- zaData[complete.cases(zaData), ]
# Tells how many rows are available.
nrow(zaData)
head(zaData)
tail(zaData)
```

Here are Stan's results as reported in his email to me on 26 June 2015:

```{r Stan\'s results}
alpha_1 <- 0.0533081
alpha_2 <- 0.9466919
alpha_3 <- 0
logscale <- -0.0753839
lambda <- 0.0137483
# Calculate sse in log space using all available data
zaData <- within(zaData, {
  residual <- log(iGDP) - (logscale + lambda*iYear + alpha_1*log(iK) + alpha_2*log(iLfi)) 
})
sse_stan <- sum(zaData$residual^2)
sse_stan
```

The above result does not match the number reported by Stan
during the telecon on 26 June 2015 (0.168).

One question arises immediately:
which years are being fitted?
There are `r nrow(zaData)` rows of data
where complete cases exist.
Yet, Stan's email indicated that he is fitting 41 observations, 1973--2013.
I suspect that Stan is trimming the rows
where `iYear < 0`.
So, let's make another data set where the
rows where `iYear < 0` are trimmed
and re-calculate `sse`.

```{r Stan\'s results, trimmed data}
zaData_trimmed <- zaData[zaData$iYear >= 0, ]
sse_stan_trimmed <- sum(zaData_trimmed$residual^2)
sse_stan_trimmed
```

For a correct comparison, I'll also fit using the 1973--2013 data only.

```{r Matt\'s results trimmed}
mod_trimmed <- cdModel(form, data = zaData_trimmed, constrained = TRUE)
summary(mod_trimmed)
naturalCoef(mod_trimmed)
sum(resid(mod_trimmed)^2)
```

If we use the \emph{exact same data}, specifically 1973--2013, we obtain exactly the same results.

For completeness, here are Matt's results when all available years are fitted:

```{r Matt\'s results}
mod <- cdModel(form, data = zaData, constrained = TRUE)
summary(mod)
sum(resid(mod)^2)
```

This number (`r sum(resid(mod)^2)`) is what Matt reported
during the telecon on 26 June 2015.

It is unsurprising that Stan (`r sse_stan_trimmed`)
reported a lower `sse` value than Matt (`r sum(resid(mod)^2)`)
during the telecon of 26 June 2015,
because Stan was using fewer observations!

### 2015-06-29 Articles/Presentation_ESEE_2015/Other results/Investigation/Investigation.Rmd
Investigation of model parameters.

---
title: "Investigation of results"
author: "MK Heun"
date: "June 29, 2015"
output: pdf_document
---

```{r setup, echo=FALSE, include=FALSE}
require(EconModels)
require(EconData)
require(dplyr)
require(ggplot2)
require(xtable)
```

```{r models}
# Set working directory to the location of these data files relative to the location of this file.
setwd("../..")
fileName <- "ESEE2015Models.rds"
fileNameCST <- "EESE2015ModelsCST.rds"
# load from the file on disk
models <- readRDS(fileName)
modelsCST <- readRDS(fileNameCST)
```

```{r investigation}
mod <- models$PT$adjusted$withE$CES$ekl
naturalCoef(mod)
summary(mod)

sum(resid(mod)^2)

attempts <- attr(mod, "model.attempts")

df <- lapply(attempts, function(attempt){
  coeffs <- naturalCoef(attempt)
  sse <- sum(resid(attempt)^2)
  coeffs$sse <- sse
  return(as.data.frame(coeffs))
}) %>% do.call(plyr::rbind.fill, .)
```

```{r all_model_attempts, tidy=FALSE, comment=NA, echo=FALSE, message=FALSE, warning=FALSE, results="asis"}
print(xtable(df), type = "latex", include.rownames = T, floating=FALSE)
```

```{r sse, tidy=FALSE, comment=NA, echo=FALSE, message=FALSE, warning=FALSE, results="asis"}
print(xtable(select(df, sse), digits = 6), type = "latex", include.rownames = T, floating=FALSE)
```

### 2015-06-29 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Edits for better documentation and formatting.

@@
   for (country in countries){
+    # Replace with better code later. 
+    # Would like to say cdMod(formula, data, fittingParams=c(alpha_1 = 0.3, alpha_2 = 0.7, alpha_3 = 0))
+    # or something like that.
     form <- keep_summands(formulas[[country]][["unadjusted"]], n=-3) # Remove energy
@@
     for (flavor in flavors){
-      fnoE <- keep_summands(formulas[[country]][[flavor]], -3) # Drop the energy term
+      fnoE <- keep_summands(formulas[[country]][[flavor]], -3) # Drop the energy term (3rd term on RHS)
       fwithE <- formulas[[country]][[flavor]]
@@
       nestsWithE <- list(kle=c(1,2,3), lek=c(2,3,1), ekl=c(3,1,2))
-      models[[country]][[flavor]][["withE"]][["CES"]] <- 
-        lapply(nestsWithE, function(nest){
+      models[[country]][[flavor]][["withE"]][["CES"]] <- lapply(nestsWithE, function(nest){
           cesModel(formula=fwithE, data=historicalData[[country]], nest=nest)

### 2015-06-29 Articles/Presentation_ESEE_2015/Other results/Paul and Joao summary/Investigation.Rmd
Deleted, because this problem was operator error.

--- 2015-06-29 Articles/Presentation_ESEE_2015/Other results/Investigation/Investigation.Rmd
@@
 
-sum(resid(mod)^2)
+EconModels:::sse(mod)
 
@@
 ```
+
+```{r make model}
+formulas <- 
+  list( 
+    PT = c(unadjusted = build_formula("iGDP", list("iKstkS.L", "iL", "iXpMP", "iYear")),
+             adjusted = build_formula("iGDP", list("iKservS.L", "ihLest", "iUMP", "iYear"))),
+    UK = c(unadjusted = build_formula("iGDP", list("iKstkO.WwithRD", "iL", "iXp", "iYear")),
+             adjusted = build_formula("iGDP", list("iKservO.WwithRD", "ihLest", "iU", "iYear")))
+  )
+countries <- names(formulas)
+flavors <- names(formulas$PT)
+
+# Create the historicalData data frames
+historicalData <- list()
+commonVars <- c("Year", "Country", "Source")
+historicalData$PT <- filter(IST, Country == "PT") 
+historicalData$PT <- historicalData$PT[ , unique(c(commonVars,
+                                                   all.vars(formulas$PT$unadjusted), 
+                                                   all.vars(formulas$PT$adjusted)))]
+historicalData$UK <- filter(Leeds, Country == "UK")
+historicalData$UK <- historicalData$UK[ , unique(c(commonVars,
+                                                   all.vars(formulas$UK$unadjusted), 
+                                                   all.vars(formulas$UK$adjusted)))]
+
+modMade <- cesModel(formulas$PT$adjusted, data=historicalData$PT, nest=c(3,1,2))
+# Compare with model from models
+rbind(naturalCoef(models$PT$adjusted$withE$CES$ekl), naturalCoef(modMade))
+```

### 2015-06-30 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Don't run models.

@@
 # ********************************************************
-rerunModels=FALSE
+rerunModels=TRUE
 # ********************************************************

### 2015-07-03 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Now including correlograms.

--- 2015-06-29 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
@@
 Perhaps there is another direction in which I should go with this analysis?
+
+%++++++++++++++++++++++++++++++
+\section{Correlograms} 
+\label{sec:correlograms}
+%++++++++++++++++++++++++++++++
+
+This appendix contains correlograms for all models.
+
+%++++++++++++++++++++++++++++++
+\subsection{Correlograms for models respecting the cost-share theorem} 
+\label{sec:correlograms_CST}
+%++++++++++++++++++++++++++++++
+
+In this section we present correlograms for all models that respect the cost-share theorem.
+
+<<Correlograms_CST, echo=FALSE, message=FALSE>>=
+leaf_apply(l = modelsCST, class = c("lm", "plm"), f = function(model, name){
+  acf(resid(model), main=name)
+})
+@
+
+%++++++++++++++++++++++++++++++
+\subsection{Correlograms for models reject the cost-share theorem} 
+\label{sec:correlograms_noCST}
+%++++++++++++++++++++++++++++++
+
+In this section we present correlograms for all models that do not adhere to the cost-share theorem.
+
+<<Correlograms_noCST, echo=FALSE, message=FALSE>>=
+leaf_apply(l = models, class = c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, name){
+  acf(resid(model), main=name)
+})
+
+@
 

### 2015-07-06 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Example of using the texreg package to create a table.

@@
 \usepackage{booktabs}   % for beautiful tables
+\usepackage{dcolumn}    % aligns table columns at decimal places
 
@@
 require(knitr)
+require(texreg)
 
@@
 })
-
+@
+
+%++++++++++++++++++++++++++++++
+\section{Statistical details on all models} 
+\label{sec:staistical_details}
+%++++++++++++++++++++++++++++++
+
+In this section, we present statistical details of all models.
+
+At the moment, this is a simple example of two models.
+I hope to develop a table later, after I figure out some things.
+Both models are CES models with energy fitted to Quality-adjusted data using the ($kl$)($e$) nesting.
+In Table~\ref{tab:stat_details_table}, Model 1 is for Portugal, and Model 2 is for the UK.
+
+<<stat_details_table, results="asis">>=
+mods <- list(models$PT$adjusted$withE$CES$kle, models$UK$adjusted$withE$CES$kle)
+texreg(mods, dcolumn = TRUE, booktabs = TRUE, use.packages = FALSE, 
+       label=paste0("tab:", opts_current$get("label")), 
+       caption = "Example output from \\texttt{texreg}.",
+       caption.above = TRUE, 
+       digits = 6,
+       fontsize = "tiny",
+       float.pos = "hb")
 @

### 2015-07-07 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Now including bar graphs.

@@
 \begin{equation} \label{eq:CD}
-  y = \theta A k^\alpha l^\beta \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)} \; ,
+  y = \theta A k^{\alpha_1} l^{\alpha_2} \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)} \; ,
 \end{equation}
@@
   Model parameters are represented by Greek letters
-  ($\alpha$, $\beta$, $\lambda$, $\theta$).
+  ($\alpha_1$, $\alpha_2$, $\lambda$, $\theta$).
   }
 Constant returns to scale are represented by the constraint
-$\alpha + \beta = 1$.
+$\alpha_1 + \alpha_2 = 1$.
 
@@
 \begin{equation} \label{eq:CDe}
-  y = \theta A k^\alpha l^\beta e^\gamma \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)} \; ,
+  y = \theta A k^{\alpha_1} l^{\alpha_2} e^{\alpha_3} \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)} \; ,
 \end{equation}
@@
 is often assumed to have constant returns to scale for the three factors 
-of production: $\alpha + \beta + \gamma = 1$.
+of production: $\alpha_1 + \alpha_2 + \alpha_3 = 1$.
 The term $A$ is known as total factor productivity,
@@
 $\alpha_1 = \delta \delta_1$, $\alpha_2 = \delta(1 - \delta_1)$, and $\alpha_3 = 1 - \delta$
-for the CES model with three factors of production.
+for the CES model with three factors of production and the ($kl$)$e$ nesting.
 The values of $\alpha_1$, $\alpha_2$, and $\alpha_3$ are interpreted as
-$\alpha$, $\beta$, and $\gamma$ (coefficients for capital, labor, and energy, respectively)
+factor shares for capital, labor, and energy, respectively,
 as shown in Table \ref{tab:CES_abg_equations}, 
@@
 
-\begin{table} \caption{Equations for $\alpha$, $\beta$, and $\gamma$ 
-                        (importance of capital, labor, and energy, respectively)
+\begin{table} \caption{Equations for $\alpha_1$, $\alpha_2$, and $\alpha_3$ 
+                        (factor shares for capital, labor, and energy, respectively)
                         for the various CES nestings, 
@@
       \toprule
-      Nesting         & \texttt{nest}     & $\alpha$                & $\beta$                 & $\gamma$       \\
+      Nesting         & \texttt{nest}     & $\alpha_1$              & $\alpha_2$              & $\alpha_3$       \\
       \midrule
@@
          digits=6)
+@
+
+%++++++++++++++++++++++++++++++
+\subsection{What trends exist in factors shares?} 
+\label{sec:factor_shares}
+%++++++++++++++++++++++++++++++
+
+Figures~\ref{fig:Factor_shares_graph_PT} and~\ref{fig:Factor_shares_graph_UK}
+show factor shares ($\alpha$ values) for CES models for
+Portugal and the UK, respectively.
+See Table~\ref{tab:CES_abg_equations} for details.
+
+<<Factor_shares_bar_graph_function>>=
+fsbg <- function(coun, mod){
+  bar_chart_data <- filter(AllCoeffs, Country==coun & model==mod) %>% 
+    select(Country, model, flavor, energy, nest, cst, alpha_1, alpha_2, alpha_3)
+  # Change boolean cst column to meaningful words
+  bar_chart_data$cst <- plyr::mapvalues(bar_chart_data$cst, from=c(TRUE, FALSE), to=c("Adhere to CST", "Reject CST"))
+  # Change nest to a nicer-looking nest string
+  bar_chart_data$nest <- plyr::mapvalues(bar_chart_data$nest, 
+                                         from=c("kl", "kle", "lek", "ekl"), 
+                                         to=c("(kl)", "(kl)e", "(le)k", "(ek)l"))
+  # Add a label column
+  bar_chart_data$label <- paste(bar_chart_data$cst, bar_chart_data$flavor, 
+                                bar_chart_data$energy, bar_chart_data$nest, sep=", ")
+  # Capture the order that we want for the models on the vertical axis.
+  order <- bar_chart_data$label
+  # Now melt the data
+  bar_chart_data <- melt(bar_chart_data, 
+                         measure.vars = c("alpha_1", "alpha_2", "alpha_3"), 
+                         value.name = "value", 
+                         variable.name = "variable")
+  # Define the color palette (see http://www.cookbook-r.com/Graphs/Colors_(ggplot2))
+  cbPalette <- c("#E69F00", "#999999", "#F0E442", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")
+  # Make the plot
+  plot <- ggplot(bar_chart_data, mapping=aes(x=label, y=value, fill=variable, width=0.4)) + 
+    geom_bar(stat="identity") + 
+    xlab("") +
+    scale_x_discrete(limits=rev(order)) +
+    ylab("") +
+    scale_y_continuous(breaks=c(0, 0.5, 1)) + 
+    guides(fill=guide_legend(title=NULL)) +
+    coord_flip() + 
+    scale_fill_brewer(palette="OrRd") +
+    xy_theme()
+  return(plot)
+}
+@
+
+<<Factor_shares_graph_PT, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=2.5, fig.cap="Factor shares ($\\alpha$ values) for CES models for Portugal.">>=
+fsbg(coun = "PT", mod = "CES")
+@
+
+<<Factor_shares_graph_UK, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=2.5, fig.cap="Factor shares ($\\alpha$ values) for CES models for the UK.">>=
+fsbg(coun = "UK", mod = "CES")
 @
@@
 <<stat_details_table, results="asis">>=
-mods <- list(models$PT$adjusted$withE$CES$kle, models$UK$adjusted$withE$CES$kle)
-texreg(mods, dcolumn = TRUE, booktabs = TRUE, use.packages = FALSE, 
+texreg(list(models$PT$adjusted$withE$CES$kle, models$UK$adjusted$withE$CES$kle), 
+       dcolumn = TRUE, 
+       booktabs = TRUE, 
+       use.packages = FALSE, 
        label=paste0("tab:", opts_current$get("label")), 

### 2015-07-07 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Removing y axis ticks.

@@
     scale_fill_brewer(palette="OrRd") +
-    xy_theme()
+    xy_theme() +
+    theme(axis.ticks.y = element_blank())
   return(plot)

### 2015-07-07 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
New code to calculate exponential-only models.

@@
 fileNameCST <- "EESE2015ModelsCST.rds"
+fileNameExp <- "EESE2015ModelsExp.rds"
 if (!rerunModels){
@@
   modelsCST <- readRDS(fileNameCST)
+  modelsExp <- readRDS(fileNameExp)
 } else {
@@
   # In RStudio, be sure to set the working directory to the source file directory.
+
+  #
+  # Models that are exponential only
+  #
+  modelsExp <- list()
+  alphaExp <- 0
+  betaExp <- 0
+  gammaExp <- 0
+  for (country in countries){
+    # Replace with better code later. 
+    # Would like to say cdModel(formula, data, factorShares=c(alpha_1 = 0, alpha_2 = 0, alpha_3 = 0))
+    # or something like that.
+    form <- keep_summands(formulas[[country]][["unadjusted"]], n = c(-1, -2, -3)) # Remove energy
+    yVar <- as.name(summands(form, n=1, right=FALSE))
+    tVar <- as.name(summands(form, n=1))
+    data <- historicalData[[country]]
+    expMod <- lm(log(eval(yVar)) ~ eval(tVar), data=data)
+    attr(expMod, "naturalCoeffs") <- data.frame(lambda=coef(expMod)[[2]],
+                                                  logscale=coef(expMod)[[1]], 
+                                                  scale=exp(coef(expMod)[[1]]),
+                                                  alpha_1=alphaExp,
+                                                  alpha_2=betaExp, 
+                                                  alpha_3=gammaExp)
+    expMod$formula <- form
+    sdata <- subset(data, select=all.vars(form))
+    sdata <- data[complete.cases(sdata), unique(c(all.vars(form), names(data)))]
+    expMod$data <- sdata
+    expMod$response <- sdata$iGDP 
+    modelsExp[[country]] <- expMod
+  }
+  # Save exponential theorem models to disk.
+  saveRDS(modelsExp, file=fileNameExp)
 
@@
     # Replace with better code later. 
-    # Would like to say cdMod(formula, data, fittingParams=c(alpha_1 = 0.3, alpha_2 = 0.7, alpha_3 = 0))
+    # Would like to say cdModel(formula, data, factorShares=c(alpha_1 = 0.3, alpha_2 = 0.7, alpha_3 = 0))
     # or something like that.
@@
 }
-# Put all the cost-share theorem (CST) coefficients into a data frame
+# Put all exponential model coefficients into a data frame
+AllCoeffsExp <- leaf_apply(modelsExp, class = c("lm"), f = function(modExp, id){
+  # Parse the id to find details of this model
+  id_list <- strsplit(id, split = "[.]")[[1]]
+  res <- rbind(list(Country = id_list[[1]], 
+                    flavor = NA,
+                    energy = NA, 
+                    model = "exp", 
+                    nest = NA,
+                    cst = FALSE))
+  res <- cbind(res, naturalCoef(modExp))
+  # Now caluculate mean squared error (mse) for each model.
+  sqResids <- resid(modExp)^2
+  mse <- sum(sqResids) / (length(sqResids))
+  res <- cbind(res, list(mse=mse))
+  return(res)
+}) %>% do.call(plyr::rbind.fill, .)
+
+# Put all the cost-share theorem (CST) model coefficients into a data frame
 AllCoeffsCST <- leaf_apply(modelsCST, class = c("lm"), f = function(modCST, id){

### 2015-07-07 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Updating for new ref case (exp only).

@@
                     flavor = NA,
-                    energy = NA, 
+                    energy = "Without energy", 
                     model = "exp", 
@@
 }) %>% do.call(plyr::rbind.fill, .)
-AllCoeffs <- plyr::rbind.fill(AllCoeffsCST, AllCoeffsNoCST)
+AllCoeffs <- plyr::rbind.fill(AllCoeffsExp, AllCoeffsCST, AllCoeffsNoCST)
+# See hint at http://stackoverflow.com/questions/22555249/how-to-merge-data-frame-with-same-column-names
+AllCoeffs <- as.data.frame(lapply(AllCoeffs, function(x) unname(unlist(x))))
 # Get reference values for lambda and sse.
-ref <- filter(AllCoeffs, cst==TRUE & flavor=="Unadjusted" & energy=="Without energy") %>% 
-              select(Country, flavor, energy, model, nest, mse, lambda)
-
+# ref <- filter(AllCoeffs, cst==TRUE & flavor=="Unadjusted" & energy=="Without energy") %>% 
+#               select(Country, model, mse, lambda)
+ref <- filter(AllCoeffs, model=="exp") %>% select(Country, mse, lambda)
 colnames(ref)[colnames(ref)=="mse"] <- "mse_ref"
 colnames(ref)[colnames(ref)=="lambda"] <- "lambda_ref"
-AllCoeffs <- merge(AllCoeffs, ref[c("Country", "model", "mse_ref", "lambda_ref")])
+AllCoeffs <- merge(AllCoeffs, ref)
 # Calculate differences relative to the unadjusted, no-energy condition
-AllCoeffs <- mutate(AllCoeffs, Dlambda = abs(lambda) - abs(lambda_ref), 
+AllCoeffs <- mutate(AllCoeffs, 
+                    Dlambda = abs(lambda) - abs(lambda_ref), 
                     Dmse = mse - mse_ref,
@@
 AllCoeffs$energy <- relevelFactor(as.factor(unlist(AllCoeffs$energy)), c("Without energy", "With energy"))
-AllCoeffs$model <- relevelFactor(as.factor(unlist(AllCoeffs$model)), c("CD", "CES"))
+AllCoeffs$model <- relevelFactor(as.factor(unlist(AllCoeffs$model)), c("exp", "CD", "CES"))
 AllCoeffs$nest <- relevelFactor(as.factor(unlist(AllCoeffs$nest)), c("kl", "kle", "lek", "ekl"))
@@
   # getData doesn't work for lm models that are created for CST=TRUE.
-  # After we implement fixed values for alpha_1 and alpha_2 in our fitting functions, 
+  # After we implement specified values for alpha_1, alpha_2, and alpha_3 in our fitting functions, 
   # getData(model) will probably work.
@@
   id_list <- strsplit(id, split = "[.]")[[1]]
+  len <- length(id_list)
   df$Country <- id_list[[1]]
-  df$flavor <- if (id_list[[2]] == "unadjusted") "Unadjusted" else "Quality-adjusted"
-  df$energy <- if (id_list[[3]] == "noE") "Without energy" else "With energy"
-  df$model <- id_list[[4]]
-  df$nest <- if (length(id_list) > 4) id_list[[5]] else NA
+  df$flavor <- if (len > 1) (if (id_list[[2]] ==  "unadjusted") "Unadjusted" else "Quality-adjusted") else NA
+  df$energy <- if (len > 2) (if (id_list[[3]] == "noE") "Without energy" else "With energy") else "Without energy"
+  df$model <- if (len > 3) id_list[[4]] else "exp"
+  df$nest <- if (len > 4) id_list[[5]] else NA
   return(df)  
 }
-temp_data_noCST <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, id){
+
+temp_data_exp <- leaf_apply(modelsExp, class=c("lm"), f = function(model, id){
+  # ****************************************************
+  # Not all of the results from this code are not correct at this time.
+  # The residuals are OK.
+  # But, the yhat() call in fittedAndResidData() will not return the correct information from the CST models.
+  # This is because modelsCST was not created with our typical functions.
+  # To correct this problem, we need to add arguments to cdModel and cesModel such that 
+  # the models produced by those functions will be in the correct form for yhat() function.
   return(fittedAndResidData(model, id))
 }) %>% do.call(rbind, .)
-temp_data_noCST$cst <- FALSE
+temp_data_exp$cst <- FALSE
 
@@
 
-temp_data <- plyr::rbind.fill( temp_data_CST, temp_data_noCST )
+temp_data_noCST <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, id){
+  return(fittedAndResidData(model, id))  
+}) %>% do.call(rbind, .)
+temp_data_noCST$cst <- FALSE
+
+temp_data <- plyr::rbind.fill( temp_data_exp, temp_data_CST, temp_data_noCST )
 
@@
 # and store them in a data frame
-r_unadj_noE_CST <- filter(temp_data, flavor=="Unadjusted" & energy=="Without energy" & cst==TRUE) %>% 
-  select(Year, Country, Residuals, model)
-colnames(r_unadj_noE_CST)[colnames(r_unadj_noE_CST)=="Residuals"] <- "r_unadj_noE"
+# r_unadj_noE_CST <- filter(temp_data, flavor=="Unadjusted" & energy=="Without energy" & cst==TRUE) %>% 
+#   select(Year, Country, Residuals, model)
+# colnames(r_unadj_noE_CST)[colnames(r_unadj_noE_CST)=="Residuals"] <- "r_unadj_noE"
 # Merge to get the unadjusted, without-energy values next to each country, year, and model
-fitted_and_resid_data <- merge(temp_data, r_unadj_noE_CST)
+# fitted_and_resid_data <- merge(temp_data, r_unadj_noE_CST)
 # Create a column containing ∆r, the difference between a residual value
 # and the residual value in the same year for the unadjusted, no-energy case
-fitted_and_resid_data[["Dr"]] <- abs(fitted_and_resid_data[["Residuals"]]) - abs(fitted_and_resid_data[["r_unadj_noE"]])
+# fitted_and_resid_data[["Dr"]] <- abs(fitted_and_resid_data[["Residuals"]]) - abs(fitted_and_resid_data[["r_unadj_noE"]])
+
+# Get the reference residuals (from the exponential-only models) and store them in a data frame
+r_ref <- filter(temp_data, model=="exp") %>% select(Year, Country, Residuals)
+colnames(r_ref)[colnames(r_ref)=="Residuals"] <- "r_ref"
+# Merge to get the reference values in each appropriate row
+fitted_and_resid_data <- merge(temp_data, r_ref)
+# Create a column containing ∆r, the difference between a residual value
+# and the residual value in the same year for the reference case
+fitted_and_resid_data[["Dr"]] <- abs(fitted_and_resid_data[["Residuals"]]) - abs(fitted_and_resid_data[["r_ref"]])
 
@@
 # Make data viewing easier
-fitted_and_resid_data <- arrange(fitted_and_resid_data, Country, model, flavor, energy, nest)
+fitted_and_resid_data <- arrange(fitted_and_resid_data, Country, cst, model, flavor, energy, nest)
 @
@@
 Table~\ref{tab:Effect_of_CST_CD} shows the effect of the CST 
-on fitted parameters for the Cobb-Douglas model.
+on fitted parameters for the Cobb-Douglas model and the exponential-only model.
+The Cobb-Douglas models show lower $mse$ than the exponential-only models.
+The Cobb-Douglas models also reduce solow residual ($\lambda$) relative
+to the exponential-only case.
 %
 <<Effect_of_CST_CD, results="asis">>=
-myXTable(filter(AllCoeffs, model=="CD" & flavor=="Unadjusted" & energy=="Without energy") %>% 
-           select(Country, cst, scale, lambda, alpha_1, alpha_2, mse),
+myXTable(filter(AllCoeffs, (model=="CD" & flavor=="Unadjusted" & energy=="Without energy") | model=="exp") %>% 
+           select(Country, model, cst, scale, lambda, alpha_1, alpha_2, mse),
          caption="Model parameters for Cobb-Douglas models with unadjusted factors of production, without energy.",
@@
 on fitted parameters for the CES model.
+The CES models show lower $mse$ than the exponential-only models.
+The CES models also reduce solow residual ($\lambda$) relative
+to the exponential-only case.
 %
 <<Effect_of_CST_CES, results="asis">>=
-myXTable(filter(AllCoeffs, model=="CES" & flavor=="Unadjusted" & energy=="Without energy") %>% 
-           select(Country, cst, gamma, lambda, alpha_1, alpha_2, sigma_1, mse),
+myXTable(filter(AllCoeffs, (model=="CES" & flavor=="Unadjusted" & energy=="Without energy") | model=="exp") %>% 
+           select(Country, model, cst, gamma, lambda, alpha_1, alpha_2, sigma_1, mse),
          caption="Model parameters for CES models with unadjusted factors of production, without energy.",
@@
 %
+Both Cobb-Douglas and CES models do a better job of fitting 
+historical data than an exponential-only model
+as evidenced by decreased $mse$ values.
+Both Cobb-Douglas and CES models exhibit reduced Solow residual~($\lambda$
+compared to the exponential-only model.
 For both Cobb-Douglas and CES, rejecting the Cost Share Theorem yields
@@
 country, model, flavor, energy, nest, and CST.
-Table~\ref{tab:CD_coeffs} shows coefficients for all fitted Cobb-Douglas models.
+Table~\ref{tab:CD_coeffs} shows coefficients for all fitted Cobb-Douglas models
+and the reference model (exponential-only).
 %
 <<CD_coeffs, results="asis">>=
-myXTable(filter(AllCoeffs, model=="CD") %>% 
-           select(Country, flavor, energy, cst, scale, lambda, alpha_1, alpha_2, alpha_3, mse),
+myXTable(filter(AllCoeffs, model=="CD" | model=="exp") %>% 
+           select(Country, model, flavor, energy, cst, scale, lambda, alpha_1, alpha_2, alpha_3, mse),
          caption="Model parameters for all Cobb-Douglas models.",
@@
 Tables~\ref{tab:CES_coeffs} and~\ref{tab:CES_coeffs_sigmas} show 
-coefficients for all fitted CES models.
+coefficients for all fitted CES models and the reference model (exponential-only).
 %
 <<CES_coeffs, results="asis">>=
-myXTable(filter(AllCoeffs, model=="CES") %>% 
-           select(Country, flavor, energy, nest, cst, gamma, lambda, alpha_1, alpha_2, alpha_3),
+myXTable(filter(AllCoeffs, model=="CES" | model=="exp") %>% 
+           select(Country, model, flavor, energy, nest, cst, gamma, lambda, alpha_1, alpha_2, alpha_3),
          caption="Model parameters for all CES models.",
@@
 <<CES_coeffs_sigmas, results="asis">>=
-myXTable(filter(AllCoeffs, model=="CES") %>% 
-           select(Country, flavor, energy, nest, cst, sigma_1, sigma, mse),
+myXTable(filter(AllCoeffs, model=="CES" | model=="exp") %>% 
+           select(Country, model, flavor, energy, nest, cst, sigma_1, sigma, mse),
          caption="Model parameters for all CES models.",
@@
 %
-<<DSRmse_CD_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta mse$) for the Cobb-Douglas model relative to the Unadjusted, Without energy, CST case.">>=
+<<DSRmse_CD_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta mse$) for the Cobb-Douglas model relative to the exponential-only model.">>=
 ggplot() +
@@
   xlab(expression(Delta * mse)) + 
-  scale_x_continuous(breaks=seq(-0.005, 0, 0.005)) +  
+  scale_x_continuous(breaks=seq(-0.01, 0, 0.005), limits=c(-0.012, 0.003)) +  
   ylab(expression(Delta * lambda)) +
+  scale_y_continuous(limits=c(-0.04, 0)) +
   xy_theme() + 

### 2015-07-07 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Additional work on graphs.

@@
   for (country in countries){
+    for (adj in c("unadjusted", "adjusted")){
       # Replace with better code later. 
@@
       # or something like that.
-    form <- keep_summands(formulas[[country]][["unadjusted"]], n=-3) # Remove energy
+      form <- keep_summands(formulas[[country]][[adj]], n=-3) # Remove energy
       yVar <- as.name(summands(form, n=1, right=FALSE))
@@
       cdModCST$response <- sdata$iGDP
-    modelsCST[[country]][["unadjusted"]][["noE"]][["CD"]] <- cdModCST
+      modelsCST[[country]][[adj]][["noE"]][["CD"]] <- cdModCST
       # CES
@@
       cesModCST$data <- sdata
-    modelsCST[[country]][["unadjusted"]][["noE"]][["CES"]][["kl"]] <- cesModCST
+      modelsCST[[country]][[adj]][["noE"]][["CES"]][["kl"]] <- cesModCST
+    }
   }
@@
                     nest = NA,
-                    cst = FALSE))
+                    cst = "Reject CST"))
   res <- cbind(res, naturalCoef(modExp))
@@
                     nest=if(length(id_list) > 4) id_list[[5]] else NA,
-                    cst=TRUE))
+                    cst="Adhere to CST"))
   res <- cbind(res, naturalCoef(modCST))
@@
                     nest=if(length(id_list) > 4) id_list[[5]] else NA,
-                    cst=FALSE))
+                    cst="Reject CST"))
   res <- cbind(res, naturalCoef(mod))
@@
 # Get reference values for lambda and sse.
-# ref <- filter(AllCoeffs, cst==TRUE & flavor=="Unadjusted" & energy=="Without energy") %>% 
+# ref <- filter(AllCoeffs, cst=="Adhere to CST" & flavor=="Unadjusted" & energy=="Without energy") %>% 
 #               select(Country, model, mse, lambda)
@@
 AllCoeffs <- merge(AllCoeffs, ref)
-# Calculate differences relative to the unadjusted, no-energy condition
+# Calculate differences relative to the reference model
 AllCoeffs <- mutate(AllCoeffs, 
@@
                     Dmse = mse - mse_ref,
-                    percDlambda = Dlambda / abs(lambda_ref) * 100)
+                    percDlambda = Dlambda / abs(lambda_ref) * 100, 
+                    percDmse = Dmse / mse_ref * 100)
 
@@
 AllCoeffs$nest <- relevelFactor(as.factor(unlist(AllCoeffs$nest)), c("kl", "kle", "lek", "ekl"))
-AllCoeffs$cst <- relevelFactor(as.factor(unlist(AllCoeffs$cst)), c("TRUE", "FALSE"))
+AllCoeffs$cst <- relevelFactor(as.factor(unlist(AllCoeffs$cst)), c("Adhere to CST", "Reject CST"))
 # Rearrange for easier viewing
@@
   # ******************************************
-  # getData doesn't work for lm models that are created for CST=TRUE.
+  # getData doesn't work for lm models that are created for CST="Adhere to CST".
   # After we implement specified values for alpha_1, alpha_2, and alpha_3 in our fitting functions, 
@@
   df$Country <- id_list[[1]]
+  # Exponential models have only 1 item in the id list, namely country. Accommodate that length with if statements.
   df$flavor <- if (len > 1) (if (id_list[[2]] ==  "unadjusted") "Unadjusted" else "Quality-adjusted") else NA
@@
 }) %>% do.call(rbind, .)
-temp_data_exp$cst <- FALSE
+temp_data_exp$cst <- "Reject CST"
 
@@
 }) %>% do.call(rbind, .)
-temp_data_CST$cst <- TRUE
+temp_data_CST$cst <- "Adhere to CST"
 
@@
 }) %>% do.call(rbind, .)
-temp_data_noCST$cst <- FALSE
+temp_data_noCST$cst <- "Reject CST"
 
@@
 # and store them in a data frame
-# r_unadj_noE_CST <- filter(temp_data, flavor=="Unadjusted" & energy=="Without energy" & cst==TRUE) %>% 
+# r_unadj_noE_CST <- filter(temp_data, flavor=="Unadjusted" & energy=="Without energy" & cst=="Adhere to CST") %>% 
 #   select(Year, Country, Residuals, model)
@@
   ggplot() +
-    geom_line(data=filter(data, cst==TRUE), mapping=aes(x=Year, y=iGDP)) +
+    geom_line(data=filter(data, cst=="Adhere to CST"), mapping=aes(x=Year, y=iGDP)) +
     geom_line(data=data, mapping=aes(x=Year, y=fitted, linetype=cst)) +
@@
 <<Graphs CD-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Cobb-Douglas models that reject the cost-share theorem. Solid line is historical GDP.">>=
-fittedGraphNoCST(filter(fitted_and_resid_data, model=="CD" & cst==FALSE))
+fittedGraphNoCST(filter(fitted_and_resid_data, model=="CD" & cst=="Reject CST"))
 @
@@
 <<Graphs CESkle-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($kl$)$e$ nesting. Solid line is historical GDP.">>=
-fittedGraphNoCST(filter(fitted_and_resid_data, model=="CES" & cst==FALSE & (nest=="kle" | nest=="kl")))
+fittedGraphNoCST(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest=="kle" | nest=="kl")))
 @
@@
 <<Graphs CESlek-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($le$)$k$ nesting. Solid line is historical GDP.">>=
-fittedGraphNoCST(filter(fitted_and_resid_data, model=="CES" & cst==FALSE & (nest=="lek" | nest=="kl")))
+fittedGraphNoCST(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest=="lek" | nest=="kl")))
 @
@@
 <<Graphs CESekl-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($ek$)$l$ nesting. Solid line is historical GDP.">>=
-fittedGraphNoCST(filter(fitted_and_resid_data, model=="CES" & cst==FALSE & (nest=="ekl" | nest=="kl")))
+fittedGraphNoCST(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest=="ekl" | nest=="kl")))
 @
@@
 <<Graphs CD-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for Cobb-Douglas models.">>=
-residualPlot(filter(fitted_and_resid_data, model=="CD" & cst==FALSE))
+residualPlot(filter(fitted_and_resid_data, model=="CD" & cst=="Reject CST"))
 @
@@
 <<Graphs CESkle-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(kl$)$e$ nesting.">>=
-residualPlot(filter(fitted_and_resid_data, model=="CES" & cst==FALSE & (nest=="kle" | nest=="kl")))
+residualPlot(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest=="kle" | nest=="kl")))
 @
@@
 <<Graphs CESlek-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with ($le$)$k$ nesting.">>=
-residualPlot(filter(fitted_and_resid_data, model=="CES" & cst==FALSE & (nest == "lek" | nest=="kl")))
+residualPlot(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest == "lek" | nest=="kl")))
 @
@@
 <<Graphs CESekl-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(ek$)$l$ nesting.">>=
-residualPlot(filter(fitted_and_resid_data, model=="CES" & cst==FALSE & (nest=="ekl" | nest=="kl")))
+residualPlot(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest=="ekl" | nest=="kl")))
 @
@@
 ggplot() +
-  geom_point(data=filter(AllCoeffs, cst==FALSE & model=="CD"), mapping=aes(x=Dmse, y=Dlambda, color=energy)) +
-  geom_point(data=filter(AllCoeffs, cst==TRUE & model=="CD"), mapping=aes(x=Dmse, y=Dlambda, color=energy), shape=1) +
+  geom_point(data=filter(AllCoeffs, model=="CD"), mapping=aes(x=Dmse, y=Dlambda, color=energy, shape=cst)) +
   facet_grid(Country ~ flavor) +
+  scale_shape_manual(values=c(1, 16)) + 
   xlab(expression(Delta * mse)) + 
@@
 %
-<<percDSRmse_CD_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Percentage change in Solow Residuals~($\\Delta\\lambda \\, [\\%]$) and mean squared error~($\\Delta mse$) for the Cobb-Douglas model relative to the Unadjusted, Without energy, CST case.">>=
+<<percDSRmse_CD_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Percentage change in Solow Residuals~($\\Delta\\lambda \\, [\\%]$) and mean squared error~($\\Delta mse \\, [\\%]$) for the Cobb-Douglas model relative to exponential-only models.">>=
 ggplot() +
-  geom_point(data=filter(AllCoeffs, cst==FALSE & model=="CD"), mapping=aes(x=Dmse, y=percDlambda, color=energy)) +
-  geom_point(data=filter(AllCoeffs, cst==TRUE & model=="CD"), mapping=aes(x=Dmse, y=percDlambda, color=energy), shape=1) +
+  geom_point(data=filter(AllCoeffs, model=="CD"), mapping=aes(x=percDmse, y=percDlambda, color=energy, shape=cst)) +
   facet_grid(Country ~ flavor) +
-  xlab(expression(Delta * mse)) + 
-  scale_x_continuous(breaks=seq(-0.005, 0, 0.005)) +  
+  scale_shape_manual(values=c(1, 16)) + 
+  xlab(expression(paste(Delta * mse, " [%]"))) + 
+#   scale_x_continuous(breaks=seq(-0.005, 0, 0.005)) +  
   ylab(expression(paste(Delta * lambda, " [%]"))) +
-  scale_y_continuous(breaks=seq(-75, 25, 25)) +  
+  scale_y_continuous(breaks=seq(-80, 0, 20), limits=c(-100, 10)) +  
   xy_theme() + 
@@
 ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CES" & cst==FALSE), mapping=aes(x=Dmse, y=Dlambda, color=energy, shape=nest)) +
-  geom_point(data=filter(AllCoeffs, model=="CES" & cst==TRUE), mapping=aes(x=Dmse, y=Dlambda, color=energy), shape=1) +
+  geom_point(data=filter(AllCoeffs, model=="CES" & cst=="Reject CST"), 
+             mapping=aes(x=Dmse, y=Dlambda, color=energy, shape=nest)) +
+  geom_point(data=filter(AllCoeffs, model=="CES" & cst=="Adhere to CST"), 
+             mapping=aes(x=Dmse, y=Dlambda, color=energy), shape=1) +
   facet_grid(Country ~ flavor) +
@@
 ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CES" & cst==FALSE), mapping=aes(x=Dmse, y=percDlambda, color=energy, shape=nest)) +
-  geom_point(data=filter(AllCoeffs, model=="CES" & cst==TRUE), mapping=aes(x=Dmse, y=percDlambda, color=energy), shape=1) + 
+  geom_point(data=filter(AllCoeffs, model=="CES" & cst=="Reject CST"), 
+             mapping=aes(x=Dmse, y=percDlambda, color=energy, shape=nest)) +
+  geom_point(data=filter(AllCoeffs, model=="CES" & cst=="Adhere to CST"), 
+             mapping=aes(x=Dmse, y=percDlambda, color=energy), shape=1) + 
   facet_grid(Country ~ flavor) +
@@
     select(Country, model, flavor, energy, nest, cst, alpha_1, alpha_2, alpha_3)
-  # Change boolean cst column to meaningful words
-  bar_chart_data$cst <- plyr::mapvalues(bar_chart_data$cst, from=c(TRUE, FALSE), to=c("Adhere to CST", "Reject CST"))
   # Change nest to a nicer-looking nest string

### 2015-07-08 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Rearranging the articles.

--- 2015-07-07 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
@@
 Constant Elasticity of Substitution (CES).
+These production functions are assessed relative to 
+a model of exponential growth only.
 The following subsections describe each.
@@
 meanings depending upon the nesting of the factors of production.
+
+%------------------------------
+\subsubsection{Exponential Production Function} 
+\label{sec:exp}
+%------------------------------
+
+We define an exponential-only reference model for economic growth
+in Equation~\ref{eq:exponential-only-model}.
+%
+\begin{equation} \label{eq:exponential-only-model}
+  y = \theta A \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)} \; .
+\end{equation}
+%
+The reference model is a degenerate case of the Cobb-Douglas production function
+wherein all factor shares are zero~($\alpha_1 = \alpha_2 = \alpha_3 = 0$)
+and the constant returns to scale constraint is not respected.
+
+We expect that the reference model will have a larger fitted Solow residual term than
+the Cobb-Douglas and CES models, because no factors of production are
+included in the reference model to drive growth.
+Indeed, in the reference model, 
+all growth is attributed to the Solow residual.
+
+In contrast, it is not necessarily true that 
+Cobb-Douglas and CES models 
+will exhibit lower $mse$ than the reference model
+shown in Equation~\ref{eq:exponential-only-model}.
+The Cobb-Douglas and CES models have more fitting parameters,
+but they incorporate the factors of production
+at constant returns to scale. 
+The reference model has $\alpha_1 + \alpha_2 + \alpha_3 = 0$,
+whereas our implementations of both the Cobb-Douglas and CES models
+requires constant returns to scale, $\alpha_1 + \alpha_2 + \alpha_3 = 1$.
+Thus, if the factors of production ($\alpha_1$, $\alpha_2$, and $\alpha_3$) 
+are poorly correlated to output ($y$),
+the constant returns to scale constraint may cause higher $mse$ for
+the Cobb-Douglas or CES models relative to the reference model.
+
+In the sections that follow, 
+we assess the Cobb-Douglas and CES models relative to the reference model
+in terms of goodness of both goodness of fit~($mse$) and Solow residual~($\lambda$).
 
@@
 <<DSRmse_CESkle, results="asis">>=
-myXTable(filter(AllCoeffs, model=="CES" & (nest=="kl" | nest=="kle")) %>% 
+myXTable(filter(AllCoeffs, (model=="CES" & (nest=="kl" | nest=="kle")) | model=="exp") %>% 
            select(Country, model, flavor, energy, nest, cst, Dlambda, Dmse),
@@
 <<DSRmse_CESlek, results="asis">>=
-myXTable(filter(AllCoeffs, model=="CES" & (nest=="kl" | nest=="lek")) %>% 
+myXTable(filter(AllCoeffs, (model=="CES" & (nest=="kl" | nest=="lek")) | model=="exp") %>% 
            select(Country, model, flavor, energy, nest, cst, Dlambda, Dmse),
@@
 <<DSRmse_CESekl, results="asis">>=
-myXTable(filter(AllCoeffs, model=="CES" & (nest=="kl" | nest=="ekl")) %>% 
+myXTable(filter(AllCoeffs, (model=="CES" & (nest=="kl" | nest=="ekl")) | model=="exp") %>% 
            select(Country, model, flavor, energy, nest, cst, Dlambda, Dmse),
@@
 ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CD"), mapping=aes(x=Dmse, y=Dlambda, color=energy, shape=cst)) +
+  geom_point(data=filter(AllCoeffs, model=="CD"), mapping=aes(x=Dmse, y=Dlambda, color=energy, size=cst)) +
   facet_grid(Country ~ flavor) +
-  scale_shape_manual(values=c(1, 16)) + 
+  scale_size_manual(values=c(2,3.5)) +
   xlab(expression(Delta * mse)) + 
@@
 ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CD"), mapping=aes(x=percDmse, y=percDlambda, color=energy, shape=cst)) +
+  geom_point(data=filter(AllCoeffs, model=="CD"), mapping=aes(x=percDmse, y=percDlambda, color=energy, size=cst)) +
   facet_grid(Country ~ flavor) +
-  scale_shape_manual(values=c(1, 16)) + 
+  scale_size_manual(values=c(2,3.5)) +
   xlab(expression(paste(Delta * mse, " [%]"))) + 
-#   scale_x_continuous(breaks=seq(-0.005, 0, 0.005)) +  
+  scale_x_continuous(breaks=seq(-50, 50, 50), limits=c(-90, 50)) +  
   ylab(expression(paste(Delta * lambda, " [%]"))) +
@@
 %
-<<DSRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta mse$) for the CES modles relative to the Unadjusted, Without energy, CST case.">>=
+<<DSRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta mse$) for the CES modles relative to the exponential-only model.">>=
 ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CES" & cst=="Reject CST"), 
-             mapping=aes(x=Dmse, y=Dlambda, color=energy, shape=nest)) +
-  geom_point(data=filter(AllCoeffs, model=="CES" & cst=="Adhere to CST"), 
-             mapping=aes(x=Dmse, y=Dlambda, color=energy), shape=1) +
+  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=Dmse, y=Dlambda, color=energy, size=cst, shape=nest)) +
+  scale_size_manual(values=c(2,3.5)) +
+  scale_shape_manual(values=c(16,17,18,15)) +
   facet_grid(Country ~ flavor) +
@@
 %
-<<percDSRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Percentage change in Solow Residuals~($\\Delta\\lambda \\, [\\%]$) and mean squared error~($\\Delta mse$) for the CES modles relative to the Unadjusted, Without energy, CST case.">>=
+<<percDSRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Percentage change in Solow Residuals~($\\Delta\\lambda \\, [\\%]$) and mean squared error~($\\Delta mse \\, [\\%]$) for the CES models relative to the exponential-only model.">>=
 ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CES" & cst=="Reject CST"), 
-             mapping=aes(x=Dmse, y=percDlambda, color=energy, shape=nest)) +
-  geom_point(data=filter(AllCoeffs, model=="CES" & cst=="Adhere to CST"), 
-             mapping=aes(x=Dmse, y=percDlambda, color=energy), shape=1) + 
+  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=percDmse, y=percDlambda, color=energy, size=cst, shape=nest)) +
+  scale_size_manual(values=c(2,3.5)) +
+  scale_shape_manual(values=c(16,17,18,15)) +
   facet_grid(Country ~ flavor) +
-  xlab(expression(Delta * mse)) + 
-  scale_x_continuous(breaks=seq(-0.005, 0, 0.005)) +  
+  xlab(expression(paste(Delta * mse, " [%]"))) + 
+  scale_x_continuous(breaks=seq(-80, 0, 20)) +  
   ylab(expression(paste(Delta * lambda, " [%]"))) +
-  scale_y_continuous(breaks=seq(-75, 25, 25)) +  
+  scale_y_continuous(breaks=seq(-80, 0, 20), limits=c(-100, 10)) +  
   xy_theme() +

### 2015-07-08 Articles/Article_EcolEcon_2015/EcolEcon_2015.tex
Rearranging the articles.

--- 2015-07-08 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
@@
 \journal{Ecological Economics}
-
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
 \begin{document}
-
-<<setup, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE>>=
-require(EconData)
-require(EconModels)
-require(dplyr)
-require(reshape2)
-require(ggplot2)
-require(mosaic)
-require(xtable)
-require(knitr)
-require(texreg)
-
-# Tell whether to re-run the analysis to create the models.
-# This file will use previously-saved models to generate
-# the paper if set to FALSE, greatly reducing time.
-# If something changes in the data or in the code that
-# performs the analysis, set 
-# rerunModels = TRUE
-# once to re-generate the information needed to 
-# create the paper.
-# ********************************************************
-rerunModels=FALSE
-# ********************************************************
-opts_chunk$set(
-  # ********************************************************
-  eval=TRUE,
-  # ********************************************************
-  # tikz allows LaTeX code in graphical output. 
-  # E.g., "$y$" for a variable name in the legend for a graph.  
-  # dev='tikz',
-  tidy=FALSE,
-  comment=NA,
-  # Tells whether to cache output from chunks are saved. Cacheing saves time. 
-  # However, references to LaTeX tables DO NOT WORK if cacheing is turned on.
-  cache=FALSE,
-  warning=FALSE,  #Tells whether to show warnings in the output.
-  # Turns off messages for all chunks. 
-  # Set TRUE on an individual chunk to see it.
-  message=FALSE, 
-  # Tells whether to echo code for all chunks. 
-  # Set TRUE on an individual chunk to see its code.
-  echo=FALSE,
-  # Sets all table captions to the top.
-  xtable.caption.placement="top"
-)
-
-# This function is used in many places below.
-myXTable <- function(data, caption, label, digits=2){
-  table <- xtable(data, caption=caption, label=label, digits=digits)
-  print(table, 
-        caption.placement="top", 
-        size="\\tiny", 
-        include.rownames=FALSE, 
-        math.style.negative=TRUE)
-}
-@
 
@@
 
-<<Formulas>>=
-# Set up the formulas for each type of analysis.
-# These formulas contain energy. 
-# We can use keep_summands to drop the energy term (3rd summand on the rhs)
-# later if needed.
-formulas <- 
-  list( 
-    PT = c(unadjusted = build_formula("iGDP", list("iKstkS.L", "iL", "iXpMP", "iYear")),
-             adjusted = build_formula("iGDP", list("iKservS.L", "ihLest", "iUMP", "iYear"))),
-    UK = c(unadjusted = build_formula("iGDP", list("iKstkO.WwithRD", "iL", "iXp", "iYear")),
-             adjusted = build_formula("iGDP", list("iKservO.WwithRD", "ihLest", "iU", "iYear")))
-  )
-countries <- names(formulas)
-flavors <- names(formulas$PT)
-@
-
-<<Data>>=
-# Create the historicalData data frames
-historicalData <- list()
-commonVars <- c("Year", "Country", "Source")
-historicalData$PT <- filter(IST, Country == "PT") 
-historicalData$PT <- historicalData$PT[ , unique(c(commonVars,
-                                                   all.vars(formulas$PT$unadjusted), 
-                                                   all.vars(formulas$PT$adjusted)))]
-historicalData$UK <- filter(Leeds, Country == "UK")
-historicalData$UK <- historicalData$UK[ , unique(c(commonVars,
-                                                   all.vars(formulas$UK$unadjusted), 
-                                                   all.vars(formulas$UK$adjusted)))]
-@
-
 For unadjusted variables, we use the time series shown in Table~\ref{tab:unadjusted_variables}.
@@
       \midrule
-      Output      & \Sexpr{summands(formulas$PT$unadjusted, n=1, right=FALSE)}   
-                                                             & \Sexpr{summands(formulas$UK$unadjusted, n=1, right=FALSE)}\\
-      Capital     & \Sexpr{summands(formulas$PT$unadjusted, 1)} & \Sexpr{summands(formulas$UK$unadjusted, 1)} \\
-      Labor       & \Sexpr{summands(formulas$PT$unadjusted, 2)} & \Sexpr{summands(formulas$UK$unadjusted, 2)} \\
-      Energy      & \Sexpr{summands(formulas$PT$unadjusted, 3)} & \Sexpr{summands(formulas$UK$unadjusted, 3)} \\
+      Output      & iGDP   
+                                                             & iGDP\\
+      Capital     & iKstkS.L & iKstkO.WwithRD \\
+      Labor       & iL & iL \\
+      Energy      & iXpMP & iXp \\
       \bottomrule
@@
       \midrule
-      Output      & \Sexpr{summands(formulas$PT$adjusted, n=1, right=FALSE)}   
-                                                           & \Sexpr{summands(formulas$UK$adjusted, n=1, right=FALSE)} \\
-      Capital     & \Sexpr{summands(formulas$PT$adjusted, 1)} & \Sexpr{summands(formulas$UK$adjusted, 1)} \\
-      Labor       & \Sexpr{summands(formulas$PT$adjusted, 2)} & \Sexpr{summands(formulas$UK$adjusted, 2)} \\
-      Energy      & \Sexpr{summands(formulas$PT$adjusted, 3)} & \Sexpr{summands(formulas$UK$adjusted, 3)} \\
+      Output      & iGDP   
+                                                           & iGDP \\
+      Capital     & iKservS.L & iKservO.WwithRD \\
+      Labor       & ihLest & ihLest \\
+      Energy      & iUMP & iU \\
       \bottomrule
@@
 
-<<Historical Data Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Historical data.", warning=FALSE>>=
-# Melt the data into a form that is useful in a couple places
-histDataForGraph <- leaf_apply(formulas, class = "formula", f=function(form, name){
-  meta <- strsplit(name, split="[.]") %>% unlist
-  Country <- meta[1]
-  flavor <- meta[2]
-  measure.vars <- c(summands(form, right=FALSE), summands(form, 1:3))
-  trimmed_historical_data <- historicalData[[Country]][c("Year", measure.vars)]
-  mtrimmed_historical_data <- melt(trimmed_historical_data, measure.vars = measure.vars, 
-                                   value.name = "value", variable.name = "variable")
-  mtrimmed_historical_data$Country <- Country
-  mtrimmed_historical_data$flavor <- if (flavor == "adjusted") "Quality-adjusted" else "Unadjusted"
-  return(mtrimmed_historical_data)
-}) %>% do.call(rbind, .)
-
-# Relevel factors before plotting
-histDataForGraph$Country <- relevelFactor(as.factor(histDataForGraph$Country), c("PT", "UK"))
-histDataForGraph$flavor <- relevelFactor(as.factor(histDataForGraph$flavor), c("Unadjusted", "Quality-adjusted"))
-histDataForGraph$variable <- relevelFactor(as.factor(histDataForGraph$variable), unique(histDataForGraph$variable))
-
-historicalPlot(histDataForGraph, 
-               mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
-               facet_formula = Country ~ flavor, 
-               line_types = c(1,2,4,3,2,4,3,2,3,2,3)) + 
-  scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12)) +
-  coord_cartesian(ylim=c(0.5, 13)) +
-  xlab("") + 
-  ylab("Indexed (1960=1)")
-@
-
-<<Pre-econometric graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Pre-econometric data.", warning=FALSE>>=
-pre_econometric_data <- leaf_apply(formulas, class = "formula", f=function(form, name){
-  meta <- strsplit(name, split="[.]") %>% unlist
-  Country <- meta[1]
-  flavor <- meta[2]
-  nums <- summands(form, n=1:3)
-  denom <- summands(form, n=1, right=FALSE)
-  ratios <- lapply(nums, function(num) {paste(num, denom, sep="/")}) %>% unlist
-  coltemplate <- build_formula(NULL, c("Year", ratios))
-  trimmed_historical_data <- historicalData[[Country]][all.vars(coltemplate)]
-  ratio_data <- evalFormula(coltemplate, data=trimmed_historical_data)$right
-  mratio_data <- melt(ratio_data, measure.vars = ratios, value.name = "ratio", variable.name = "variable")
-  mratio_data$Country <- Country
-  mratio_data$flavor <- if (flavor == "adjusted") "Quality-adjusted" else "Unadjusted"
-  return(mratio_data)
-}) %>% do.call(rbind, .)
-
-# Fix levels
-pre_econometric_data$flavor <- relevelFactor(as.factor(as.character(pre_econometric_data$flavor)), 
-                                               c("Unadjusted", "Quality-adjusted"))
-pre_econometric_data$Country <- relevelFactor(as.factor(pre_econometric_data$Country), 
-                                              c("PT", "UK"))
-pre_econometric_data$variable <- relevelFactor(as.factor(pre_econometric_data$variable),
-                                               unique(pre_econometric_data$variable))
-# Now make the plot of pre-econometric data
-historicalPlot(pre_econometric_data, 
-               mapping=aes(x=Year, y=ratio, group=variable, linetype=variable), 
-               facet_formula = Country ~ flavor, 
-               line_types = c(2,4,3, 2,4,3, 2,3,2, 3)) + 
-  xlab("") + 
-  ylab("Indexed (1960=1)")
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[H]
+
+{\centering \includegraphics[width=\maxwidth]{figure/Historical_Data_Graph-1}
+
+}
+
+\caption[Historical data]{Historical data.}\label{fig:Historical Data Graph}
+\end{figure}
+
+\end{knitrout}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[H]
+
+{\centering \includegraphics[width=\maxwidth]{figure/Pre-econometric_graph-1}
+
+}
+
+\caption[Pre-econometric data]{Pre-econometric data.}\label{fig:Pre-econometric graph}
+\end{figure}
+
+\end{knitrout}
 
@@
 
-<<Models>>=
-fileName <- "ESEE2015Models.rds"
-fileNameCST <- "EESE2015ModelsCST.rds"
-fileNameExp <- "EESE2015ModelsExp.rds"
-if (!rerunModels){
-  # load from the file on disk
-  models <- readRDS(fileName)
-  modelsCST <- readRDS(fileNameCST)
-  modelsExp <- readRDS(fileNameExp)
-} else {
-  # re-run the models and save to disk.
-  # In RStudio, be sure to set the working directory to the source file directory.
-
-  #
-  # Models that are exponential only
-  #
-  modelsExp <- list()
-  alphaExp <- 0
-  betaExp <- 0
-  gammaExp <- 0
-  for (country in countries){
-    # Replace with better code later. 
-    # Would like to say cdModel(formula, data, factorShares=c(alpha_1 = 0, alpha_2 = 0, alpha_3 = 0))
-    # or something like that.
-    form <- keep_summands(formulas[[country]][["unadjusted"]], n = c(-1, -2, -3)) # Remove energy
-    yVar <- as.name(summands(form, n=1, right=FALSE))
-    tVar <- as.name(summands(form, n=1))
-    data <- historicalData[[country]]
-    expMod <- lm(log(eval(yVar)) ~ eval(tVar), data=data)
-    attr(expMod, "naturalCoeffs") <- data.frame(lambda=coef(expMod)[[2]],
-                                                  logscale=coef(expMod)[[1]], 
-                                                  scale=exp(coef(expMod)[[1]]),
-                                                  alpha_1=alphaExp,
-                                                  alpha_2=betaExp, 
-                                                  alpha_3=gammaExp)
-    expMod$formula <- form
-    sdata <- subset(data, select=all.vars(form))
-    sdata <- data[complete.cases(sdata), unique(c(all.vars(form), names(data)))]
-    expMod$data <- sdata
-    expMod$response <- sdata$iGDP 
-    modelsExp[[country]] <- expMod
-  }
-  # Save exponential theorem models to disk.
-  saveRDS(modelsExp, file=fileNameExp)
-
-  #
-  # Models that adhere to the cost-share theorem
-  #
-
-  modelsCST <- list()
-  # Output elasticities based on cost share theorem
-  alphaCST <- 0.3 # Fraction of national accounts spent on capital
-  betaCST <- 0.7 # Fraction of national accounts spent on labor
-  for (country in countries){
-    for (adj in c("unadjusted", "adjusted")){
-      # Replace with better code later. 
-      # Would like to say cdModel(formula, data, factorShares=c(alpha_1 = 0.3, alpha_2 = 0.7, alpha_3 = 0))
-      # or something like that.
-      form <- keep_summands(formulas[[country]][[adj]], n=-3) # Remove energy
-      yVar <- as.name(summands(form, n=1, right=FALSE))
-      kVar <- as.name(summands(form, n=1))
-      lVar <- as.name(summands(form, n=2))
-      tVar <- as.name(summands(form, n=3))
-      data <- historicalData[[country]]
-      # Cobb-Douglas
-      cdModCST <- lm(log(eval(yVar)) - alphaCST*log(eval(kVar)) - betaCST*log(eval(lVar)) ~ eval(tVar), data = data)
-      attr(cdModCST, "naturalCoeffs") <- data.frame(lambda=coef(cdModCST)[[2]],
-                                                    logscale=coef(cdModCST)[[1]], 
-                                                    scale=exp(coef(cdModCST)[[1]]),
-                                                    alpha_1=alphaCST,
-                                                    alpha_2=betaCST, 
-                                                    alpha_3=0)
-      cdModCST$formula <- form
-      sdata <- subset(data, select=all.vars(form))
-      sdata <- data[complete.cases(sdata), unique(c(all.vars(form), names(data)))]
-      cdModCST$data <- sdata
-      cdModCST$response <- sdata$iGDP
-      modelsCST[[country]][[adj]][["noE"]][["CD"]] <- cdModCST
-      # CES
-      cesModCST <- plm(log(eval(yVar) / (alphaCST*eval(kVar)^(-rho_1) + betaCST*eval(lVar)^(-rho_1))^(-1/rho_1)) ~ eval(tVar),
-                       data = historicalData[[country]],
-                       params=c(rho_1=0.8))
-      names(cesModCST$coefficients) <- c("logscale", "lambda", "rho_1")
-      cesModCST$coefficients <- c(coef(cesModCST), c(delta_1=alphaCST, delta=1))
-      attr(cesModCST, "naturalCoeffs") <- EconModels:::makeNatCoef(cesModCST)
-      cesModCST$formula <- form
-      cesModCST$data <- sdata
-      modelsCST[[country]][[adj]][["noE"]][["CES"]][["kl"]] <- cesModCST
-    }
-  }
-  # Save cost-share theorem models to disk.
-  saveRDS(modelsCST, file=fileNameCST)
-
-  #
-  # Models where all parameters are estimated (models don't adhere to the cost share theorem)
-  #
-
-  models <- list()
-  for(country in countries){
-    for (flavor in flavors){
-      fnoE <- keep_summands(formulas[[country]][[flavor]], -3) # Drop the energy term (3rd term on RHS)
-      fwithE <- formulas[[country]][[flavor]]
-      # CD models
-      models[[country]][[flavor]][["noE"]][["CD"]]   <- cdModel(fnoE, data = historicalData[[country]])
-      models[[country]][[flavor]][["withE"]][["CD"]] <- cdModel(fwithE, data = historicalData[[country]])
-      # CES models
-      models[[country]][[flavor]][["noE"]][["CES"]][["kl"]] <- cesModel(fnoE, 
-                                                                        data = historicalData[[country]], 
-                                                                        nest=c(1,2))
-      nestsWithE <- list(kle=c(1,2,3), lek=c(2,3,1), ekl=c(3,1,2))
-      models[[country]][[flavor]][["withE"]][["CES"]] <- lapply(nestsWithE, function(nest){
-          cesModel(formula=fwithE, data=historicalData[[country]], nest=nest)
-        })
-    }      
-  }
-  # Save models to disk.
-  saveRDS(models, file=fileName)
-}
-# Put all exponential model coefficients into a data frame
-AllCoeffsExp <- leaf_apply(modelsExp, class = c("lm"), f = function(modExp, id){
-  # Parse the id to find details of this model
-  id_list <- strsplit(id, split = "[.]")[[1]]
-  res <- rbind(list(Country = id_list[[1]], 
-                    flavor = NA,
-                    energy = "Without energy", 
-                    model = "exp", 
-                    nest = NA,
-                    cst = "Reject CST"))
-  res <- cbind(res, naturalCoef(modExp))
-  # Now caluculate mean squared error (mse) for each model.
-  sqResids <- resid(modExp)^2
-  mse <- sum(sqResids) / (length(sqResids))
-  res <- cbind(res, list(mse=mse))
-  return(res)
-}) %>% do.call(plyr::rbind.fill, .)
-
-# Put all the cost-share theorem (CST) model coefficients into a data frame
-AllCoeffsCST <- leaf_apply(modelsCST, class = c("lm"), f = function(modCST, id){
-  # Parse the id to find out whether this is quality-adjusted data, etc.
-  id_list <- strsplit(id, split = "[.]")[[1]]
-  res <- rbind(list(Country = id_list[[1]], 
-                    flavor = if (id_list[[2]]=="unadjusted") "Unadjusted" else "Quality-adjusted",
-                    energy = if (id_list[[3]]=="noE") "Without energy" else "With energy",
-                    model=id_list[[4]], 
-                    nest=if(length(id_list) > 4) id_list[[5]] else NA,
-                    cst="Adhere to CST"))
-  res <- cbind(res, naturalCoef(modCST))
-  # Now calculate the mean squared error (mse) for each model.
-  sqResids <- resid(modCST)^2
-  mse <- sum(sqResids)/(length(sqResids))
-  res <- cbind(res, list(mse=mse))
-  return(res)
-}) %>% do.call(plyr::rbind.fill, .)
-
-AllCoeffsNoCST <- leaf_apply(models, class = c("CDEmodel", "cesModel", "LINEXmodel"), f = function(mod, id){
-  # Parse the id to find out whether this is quality-adjusted data, etc.
-  id_list <- strsplit(id, split = "[.]")[[1]]
-  res <- rbind(list(Country = id_list[[1]], 
-                    flavor = if (id_list[[2]]=="unadjusted") "Unadjusted" else "Quality-adjusted",
-                    energy = if (id_list[[3]]=="noE") "Without energy" else "With energy",
-                    model=id_list[[4]], 
-                    nest=if(length(id_list) > 4) id_list[[5]] else NA,
-                    cst="Reject CST"))
-  res <- cbind(res, naturalCoef(mod))
-  # Now calculate the mean squared error (mse) for each model.
-  sqResids <- resid(mod)^2
-  mse <- sum(sqResids)/(length(sqResids))
-  res <- cbind(res, list(mse=mse))
-  return(res)
-}) %>% do.call(plyr::rbind.fill, .)
-AllCoeffs <- plyr::rbind.fill(AllCoeffsExp, AllCoeffsCST, AllCoeffsNoCST)
-# See hint at http://stackoverflow.com/questions/22555249/how-to-merge-data-frame-with-same-column-names
-AllCoeffs <- as.data.frame(lapply(AllCoeffs, function(x) unname(unlist(x))))
-# Get reference values for lambda and sse.
-# ref <- filter(AllCoeffs, cst=="Adhere to CST" & flavor=="Unadjusted" & energy=="Without energy") %>% 
-#               select(Country, model, mse, lambda)
-ref <- filter(AllCoeffs, model=="exp") %>% select(Country, mse, lambda)
-colnames(ref)[colnames(ref)=="mse"] <- "mse_ref"
-colnames(ref)[colnames(ref)=="lambda"] <- "lambda_ref"
-AllCoeffs <- merge(AllCoeffs, ref)
-# Calculate differences relative to the reference model
-AllCoeffs <- mutate(AllCoeffs, 
-                    Dlambda = abs(lambda) - abs(lambda_ref), 
-                    Dmse = mse - mse_ref,
-                    percDlambda = Dlambda / abs(lambda_ref) * 100, 
-                    percDmse = Dmse / mse_ref * 100)
-
-# Relevel factors
-AllCoeffs$Country <- relevelFactor(as.factor(unlist(AllCoeffs$Country)), c("PT", "UK"))
-AllCoeffs$flavor <- relevelFactor(as.factor(unlist(AllCoeffs$flavor)), c("Unadjusted", "Quality-adjusted"))
-AllCoeffs$energy <- relevelFactor(as.factor(unlist(AllCoeffs$energy)), c("Without energy", "With energy"))
-AllCoeffs$model <- relevelFactor(as.factor(unlist(AllCoeffs$model)), c("exp", "CD", "CES"))
-AllCoeffs$nest <- relevelFactor(as.factor(unlist(AllCoeffs$nest)), c("kl", "kle", "lek", "ekl"))
-AllCoeffs$cst <- relevelFactor(as.factor(unlist(AllCoeffs$cst)), c("Adhere to CST", "Reject CST"))
-# Rearrange for easier viewing
-AllCoeffs <- arrange(AllCoeffs, Country, model, flavor, energy, nest, cst)
-@
-
-<<Fitted_and_Residuals>>=
-fittedAndResidData <- function(model, id){
-  # ******************************************
-  # getData doesn't work for lm models that are created for CST="Adhere to CST".
-  # After we implement specified values for alpha_1, alpha_2, and alpha_3 in our fitting functions, 
-  # getData(model) will probably work.
-  # At that time, change model$data to getData(model)
-  df <- data.frame(select(model$data, Year)) 
-  # By including [c(1:length(df$Year))] on the end, we 
-  # add NAs (as appropriate) to the end of these columns
-  # if data do not exist.
-  df$fitted <- yhat(model)[c(1:length(df$Year))]
-  df$Residuals <- resid(model)[c(1:length(df$Year))]
-  # Now add the response, using the original variable name.
-  df[[summands(model$formula, right = FALSE)]] <- response(model)[c(1:length(df$Year))]
-  # Now add meta information
-  id_list <- strsplit(id, split = "[.]")[[1]]
-  len <- length(id_list)
-  df$Country <- id_list[[1]]
-  # Exponential models have only 1 item in the id list, namely country. Accommodate that length with if statements.
-  df$flavor <- if (len > 1) (if (id_list[[2]] ==  "unadjusted") "Unadjusted" else "Quality-adjusted") else NA
-  df$energy <- if (len > 2) (if (id_list[[3]] == "noE") "Without energy" else "With energy") else "Without energy"
-  df$model <- if (len > 3) id_list[[4]] else "exp"
-  df$nest <- if (len > 4) id_list[[5]] else NA
-  return(df)  
-}
-
-temp_data_exp <- leaf_apply(modelsExp, class=c("lm"), f = function(model, id){
-  # ****************************************************
-  # Not all of the results from this code are not correct at this time.
-  # The residuals are OK.
-  # But, the yhat() call in fittedAndResidData() will not return the correct information from the CST models.
-  # This is because modelsCST was not created with our typical functions.
-  # To correct this problem, we need to add arguments to cdModel and cesModel such that 
-  # the models produced by those functions will be in the correct form for yhat() function.
-  return(fittedAndResidData(model, id))
-}) %>% do.call(rbind, .)
-temp_data_exp$cst <- "Reject CST"
-
-temp_data_CST <- leaf_apply(modelsCST, class=c("plm", "lm"), f = function(model, id){
-  # ****************************************************
-  # Not all of the results from this code are not correct at this time.
-  # The residuals are OK.
-  # But, the yhat() call in fittedAndResidData() will not return the correct information from the CST models.
-  # This is because modelsCST was not created with our typical functions.
-  # To correct this problem, we need to add arguments to cdModel and cesModel such that 
-  # the models produced by those functions will be in the correct form for yhat() function.
-  return(fittedAndResidData(model, id))
-}) %>% do.call(rbind, .)
-temp_data_CST$cst <- "Adhere to CST"
-
-temp_data_noCST <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, id){
-  return(fittedAndResidData(model, id))  
-}) %>% do.call(rbind, .)
-temp_data_noCST$cst <- "Reject CST"
-
-temp_data <- plyr::rbind.fill( temp_data_exp, temp_data_CST, temp_data_noCST )
-
-# Get the unadjusted, without-energy residuals from models that obey the CST
-# and store them in a data frame
-# r_unadj_noE_CST <- filter(temp_data, flavor=="Unadjusted" & energy=="Without energy" & cst=="Adhere to CST") %>% 
-#   select(Year, Country, Residuals, model)
-# colnames(r_unadj_noE_CST)[colnames(r_unadj_noE_CST)=="Residuals"] <- "r_unadj_noE"
-# Merge to get the unadjusted, without-energy values next to each country, year, and model
-# fitted_and_resid_data <- merge(temp_data, r_unadj_noE_CST)
-# Create a column containing ∆r, the difference between a residual value
-# and the residual value in the same year for the unadjusted, no-energy case
-# fitted_and_resid_data[["Dr"]] <- abs(fitted_and_resid_data[["Residuals"]]) - abs(fitted_and_resid_data[["r_unadj_noE"]])
-
-# Get the reference residuals (from the exponential-only models) and store them in a data frame
-r_ref <- filter(temp_data, model=="exp") %>% select(Year, Country, Residuals)
-colnames(r_ref)[colnames(r_ref)=="Residuals"] <- "r_ref"
-# Merge to get the reference values in each appropriate row
-fitted_and_resid_data <- merge(temp_data, r_ref)
-# Create a column containing ∆r, the difference between a residual value
-# and the residual value in the same year for the reference case
-fitted_and_resid_data[["Dr"]] <- abs(fitted_and_resid_data[["Residuals"]]) - abs(fitted_and_resid_data[["r_ref"]])
-
-# Relevel factors before plotting
-fitted_and_resid_data$Country <- relevelFactor(as.factor(fitted_and_resid_data$Country), c("PT", "UK"))
-fitted_and_resid_data$flavor <- relevelFactor(as.factor(fitted_and_resid_data$flavor), c("Unadjusted", "Quality-adjusted"))
-fitted_and_resid_data$energy <- relevelFactor(as.factor(fitted_and_resid_data$energy), c("Without energy", "With energy"))
-fitted_and_resid_data$nest <- relevelFactor(as.factor(fitted_and_resid_data$nest), c("kl", "kle", "lek", "ekl"))
-
-# Make data viewing easier
-fitted_and_resid_data <- arrange(fitted_and_resid_data, Country, cst, model, flavor, energy, nest)
-@
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-<<Fitted and Residual Graph Functions>>=
-fittedGraphCST <- function(data){
-  ggplot() +
-    geom_line(data=filter(data, cst=="Adhere to CST"), mapping=aes(x=Year, y=iGDP)) +
-    geom_line(data=data, mapping=aes(x=Year, y=fitted, linetype=cst)) +
-    scale_linetype_manual(values=c(2,3), name="") +
-    facet_grid(Country ~ flavor) + 
-    xlab("") +
-    ylab("Indexed GDP (1960=1)") +
-    xy_theme()
-}
-
-fittedGraphNoCST <- function(data){
-  ggplot() +
-    geom_line(data=filter(data, energy=="Without energy"), mapping=aes(x=Year, y=iGDP)) +
-    geom_line(data=data, mapping=aes(x=Year, y=fitted, linetype=energy)) +
-    scale_linetype_manual(values=c(2,3), name="") +
-    facet_grid(Country ~ flavor) +
-    scale_x_continuous(breaks=c(1960, 1980, 2000)) +
-    scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12)) +
-    xlab("") +
-    ylab("Indexed GDP (1960=1)") +
-    xy_theme()
-}
-@
-
 Both historical GDP and fitted GDP are shown in 
@@
 %
-<<Graphs CD-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Cobb-Douglas models that reject the cost-share theorem. Solid line is historical GDP.">>=
-fittedGraphNoCST(filter(fitted_and_resid_data, model=="CD" & cst=="Reject CST"))
-@
-%
-<<Graphs CESkle-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($kl$)$e$ nesting. Solid line is historical GDP.">>=
-fittedGraphNoCST(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest=="kle" | nest=="kl")))
-@
-%
-<<Graphs CESlek-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($le$)$k$ nesting. Solid line is historical GDP.">>=
-fittedGraphNoCST(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest=="lek" | nest=="kl")))
-@
-%
-<<Graphs CESekl-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($ek$)$l$ nesting. Solid line is historical GDP.">>=
-fittedGraphNoCST(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest=="ekl" | nest=="kl")))
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[H]
+
+{\centering \includegraphics[width=\maxwidth]{figure/Graphs_CD-fitted-1}
+
+}
+
+\caption[Cobb-Douglas models that reject the cost-share theorem]{Cobb-Douglas models that reject the cost-share theorem. Solid line is historical GDP.}\label{fig:Graphs CD-fitted}
+\end{figure}
+
+\end{knitrout}
+%
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[H]
+
+{\centering \includegraphics[width=\maxwidth]{figure/Graphs_CESkle-fitted-1}
+
+}
+
+\caption[CES models with (]{CES models with ($kl$)$e$ nesting. Solid line is historical GDP.}\label{fig:Graphs CESkle-fitted}
+\end{figure}
+
+\end{knitrout}
+%
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[H]
+
+{\centering \includegraphics[width=\maxwidth]{figure/Graphs_CESlek-fitted-1}
+
+}
+
+\caption[CES models with (]{CES models with ($le$)$k$ nesting. Solid line is historical GDP.}\label{fig:Graphs CESlek-fitted}
+\end{figure}
+
+\end{knitrout}
+%
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[H]
+
+{\centering \includegraphics[width=\maxwidth]{figure/Graphs_CESekl-fitted-1}
+
+}
+
+\caption[CES models with (]{CES models with ($ek$)$l$ nesting. Solid line is historical GDP.}\label{fig:Graphs CESekl-fitted}
+\end{figure}
+
+\end{knitrout}
 
@@
 
-<<ResidualPlotFunction>>=
-residualPlot <- function(data){
-  ggplot() +
-    geom_line(data=data, mapping=aes(x=Year, y=Residuals, linetype=energy)) +
-    scale_linetype_manual(values=c(2,3), name="") +
-    facet_grid(Country ~ flavor) +
-    scale_x_continuous(breaks=c(1960, 1980, 2000)) +
-    xlab("") +
-    ylab("r") + 
-    xy_theme()
-}
-@
-
 Because we fit in log-space, fitting residuals ($r_i$) are defined as
@@
 %
-<<Graphs CD-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for Cobb-Douglas models.">>=
-residualPlot(filter(fitted_and_resid_data, model=="CD" & cst=="Reject CST"))
-@
-%
-<<Graphs CESkle-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(kl$)$e$ nesting.">>=
-residualPlot(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest=="kle" | nest=="kl")))
-@
-%
-<<Graphs CESlek-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with ($le$)$k$ nesting.">>=
-residualPlot(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest == "lek" | nest=="kl")))
-@
-%
-<<Graphs CESekl-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(ek$)$l$ nesting.">>=
-residualPlot(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest=="ekl" | nest=="kl")))
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[H]
+
+{\centering \includegraphics[width=\maxwidth]{figure/Graphs_CD-resid-1}
+
+}
+
+\caption[Fitting residuals for Cobb-Douglas models]{Fitting residuals for Cobb-Douglas models.}\label{fig:Graphs CD-resid}
+\end{figure}
+
+\end{knitrout}
+%
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[H]
+
+{\centering \includegraphics[width=\maxwidth]{figure/Graphs_CESkle-resid-1}
+
+}
+
+\caption[Fitting residuals for CES models with ]{Fitting residuals for CES models with $(kl$)$e$ nesting.}\label{fig:Graphs CESkle-resid}
+\end{figure}
+
+\end{knitrout}
+%
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[H]
+
+{\centering \includegraphics[width=\maxwidth]{figure/Graphs_CESlek-resid-1}
+
+}
+
+\caption[Fitting residuals for CES models with (]{Fitting residuals for CES models with ($le$)$k$ nesting.}\label{fig:Graphs CESlek-resid}
+\end{figure}
+
+\end{knitrout}
+%
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[H]
+
+{\centering \includegraphics[width=\maxwidth]{figure/Graphs_CESekl-resid-1}
+
+}
+
+\caption[Fitting residuals for CES models with ]{Fitting residuals for CES models with $(ek$)$l$ nesting.}\label{fig:Graphs CESekl-resid}
+\end{figure}
+
+\end{knitrout}
 
@@
 %
-<<Effect_of_CST_CD, results="asis">>=
-myXTable(filter(AllCoeffs, (model=="CD" & flavor=="Unadjusted" & energy=="Without energy") | model=="exp") %>% 
-           select(Country, model, cst, scale, lambda, alpha_1, alpha_2, mse),
-         caption="Model parameters for Cobb-Douglas models with unadjusted factors of production, without energy.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
+% latex table generated in R 3.2.0 by xtable 1.7-4 package
+% Wed Jul  8 15:28:27 2015
+\begin{table}[ht]
+\centering
+\caption{Model parameters for Cobb-Douglas models with unadjusted factors of production, without energy.} 
+\label{tab:Effect_of_CST_CD}
+{\tiny
+\begin{tabular}{lllrrrrr}
+  \hline
+Country & model & cst & scale & lambda & alpha\_1 & alpha\_2 & mse \\ 
+  \hline
+PT & exp & Reject CST & 1.283537 & 0.034507 & 0.000000 & 0.000000 & 0.013359 \\ 
+  PT & CD & Adhere to CST & 1.328501 & 0.016080 & 0.300000 & 0.700000 & 0.011724 \\ 
+  PT & CD & Reject CST & 1.113489 & $-$0.005539 & 1.000000 & 0.000000 & 0.003190 \\ 
+  UK & exp & Reject CST & 1.021833 & 0.023565 & 0.000000 & 0.000000 & 0.001212 \\ 
+  UK & CD & Adhere to CST & 1.032978 & 0.015510 & 0.300000 & 0.700000 & 0.000775 \\ 
+  UK & CD & Reject CST & 1.000925 & 0.006654 & 0.544956 & 0.455044 & 0.000494 \\ 
+   \hline
+\end{tabular}
+}
+\end{table}
+
 %
@@
 %
-<<Effect_of_CST_CES, results="asis">>=
-myXTable(filter(AllCoeffs, (model=="CES" & flavor=="Unadjusted" & energy=="Without energy") | model=="exp") %>% 
-           select(Country, model, cst, gamma, lambda, alpha_1, alpha_2, sigma_1, mse),
-         caption="Model parameters for CES models with unadjusted factors of production, without energy.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
+% latex table generated in R 3.2.0 by xtable 1.7-4 package
+% Wed Jul  8 15:28:27 2015
+\begin{table}[ht]
+\centering
+\caption{Model parameters for CES models with unadjusted factors of production, without energy.} 
+\label{tab:Effect_of_CST_CES}
+{\tiny
+\begin{tabular}{lllrrrrrr}
+  \hline
+Country & model & cst & gamma & lambda & alpha\_1 & alpha\_2 & sigma\_1 & mse \\ 
+  \hline
+PT & exp & Reject CST &  & 0.034507 & 0.000000 & 0.000000 &  & 0.013359 \\ 
+  PT & CES & Adhere to CST & 1.318284 & 0.018825 & 0.300000 & 0.700000 & 0.665163 & 0.011450 \\ 
+  PT & CES & Reject CST & 0.998729 & 0.012404 & 0.983352 & 0.016648 & 0.173623 & 0.001113 \\ 
+  UK & exp & Reject CST &  & 0.023565 & 0.000000 & 0.000000 &  & 0.001212 \\ 
+  UK & CES & Adhere to CST & 1.006734 & 0.020914 & 0.300000 & 0.700000 & 0.509524 & 0.000491 \\ 
+  UK & CES & Reject CST & 0.977872 & 0.017904 & 0.436298 & 0.563702 & 0.500000 & 0.000326 \\ 
+   \hline
+\end{tabular}
+}
+\end{table}
+
 %
@@
 %
-<<CD_coeffs, results="asis">>=
-myXTable(filter(AllCoeffs, model=="CD" | model=="exp") %>% 
-           select(Country, model, flavor, energy, cst, scale, lambda, alpha_1, alpha_2, alpha_3, mse),
-         caption="Model parameters for all Cobb-Douglas models.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
+% latex table generated in R 3.2.0 by xtable 1.7-4 package
+% Wed Jul  8 15:28:28 2015
+\begin{table}[ht]
+\centering
+\caption{Model parameters for all Cobb-Douglas models.} 
+\label{tab:CD_coeffs}
+{\tiny
+\begin{tabular}{lllllrrrrrr}
+  \hline
+Country & model & flavor & energy & cst & scale & lambda & alpha\_1 & alpha\_2 & alpha\_3 & mse \\ 
+  \hline
+PT & exp &  & Without energy & Reject CST & 1.283537 & 0.034507 & 0.000000 & 0.000000 & 0.000000 & 0.013359 \\ 
+  PT & CD & Unadjusted & Without energy & Adhere to CST & 1.328501 & 0.016080 & 0.300000 & 0.700000 & 0.000000 & 0.011724 \\ 
+  PT & CD & Unadjusted & Without energy & Reject CST & 1.113489 & $-$0.005539 & 1.000000 & 0.000000 & 0.000000 & 0.003190 \\ 
+  PT & CD & Unadjusted & With energy & Reject CST & 1.130790 & $-$0.004439 & 0.755978 & 0.000000 & 0.244022 & 0.002628 \\ 
+  PT & CD & Quality-adjusted & Without energy & Adhere to CST & 1.364226 & 0.004183 & 0.300000 & 0.700000 & 0.000000 & 0.011340 \\ 
+  PT & CD & Quality-adjusted & Without energy & Reject CST & 1.231989 & $-$0.015079 & 1.000000 & 0.000000 & 0.000000 & 0.008937 \\ 
+  PT & CD & Quality-adjusted & With energy & Reject CST & 1.111839 & $-$0.004569 & 0.000000 & 0.000000 & 1.000000 & 0.002268 \\ 
+  UK & exp &  & Without energy & Reject CST & 1.021833 & 0.023565 & 0.000000 & 0.000000 & 0.000000 & 0.001212 \\ 
+  UK & CD & Unadjusted & Without energy & Adhere to CST & 1.032978 & 0.015510 & 0.300000 & 0.700000 & 0.000000 & 0.000775 \\ 
+  UK & CD & Unadjusted & Without energy & Reject CST & 1.000925 & 0.006654 & 0.544956 & 0.455044 & 0.000000 & 0.000494 \\ 
+  UK & CD & Unadjusted & With energy & Reject CST & 0.995030 & 0.018134 & 0.162500 & 0.460325 & 0.377175 & 0.000331 \\ 
+  UK & CD & Quality-adjusted & Without energy & Adhere to CST & 1.038384 & 0.008725 & 0.300000 & 0.700000 & 0.000000 & 0.001564 \\ 
+  UK & CD & Quality-adjusted & Without energy & Reject CST & 1.015146 & $-$0.008149 & 0.751058 & 0.248942 & 0.000000 & 0.000720 \\ 
+  UK & CD & Quality-adjusted & With energy & Reject CST & 0.970614 & 0.001981 & 0.403433 & 0.330248 & 0.266319 & 0.000453 \\ 
+   \hline
+\end{tabular}
+}
+\end{table}
+
 %
@@
 %
-<<CES_coeffs, results="asis">>=
-myXTable(filter(AllCoeffs, model=="CES" | model=="exp") %>% 
-           select(Country, model, flavor, energy, nest, cst, gamma, lambda, alpha_1, alpha_2, alpha_3),
-         caption="Model parameters for all CES models.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-%
-<<CES_coeffs_sigmas, results="asis">>=
-myXTable(filter(AllCoeffs, model=="CES" | model=="exp") %>% 
-           select(Country, model, flavor, energy, nest, cst, sigma_1, sigma, mse),
-         caption="Model parameters for all CES models.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
+% latex table generated in R 3.2.0 by xtable 1.7-4 package
+% Wed Jul  8 15:28:28 2015
+\begin{table}[ht]
+\centering
+\caption{Model parameters for all CES models.} 
+\label{tab:CES_coeffs}
+{\tiny
+\begin{tabular}{llllllrrrrr}
+  \hline
+Country & model & flavor & energy & nest & cst & gamma & lambda & alpha\_1 & alpha\_2 & alpha\_3 \\ 
+  \hline
+PT & exp &  & Without energy &  & Reject CST &  & 0.034507 & 0.000000 & 0.000000 & 0.000000 \\ 
+  PT & CES & Unadjusted & Without energy & kl & Adhere to CST & 1.318284 & 0.018825 & 0.300000 & 0.700000 & 0.000000 \\ 
+  PT & CES & Unadjusted & Without energy & kl & Reject CST & 0.998729 & 0.012404 & 0.983352 & 0.016648 & 0.000000 \\ 
+  PT & CES & Unadjusted & With energy & kle & Reject CST & 1.022631 & 0.009738 & 0.727922 & 0.000064 & 0.272014 \\ 
+  PT & CES & Unadjusted & With energy & lek & Reject CST & 1.005212 & 0.008318 & 1.000000 & 0.000000 & 0.000000 \\ 
+  PT & CES & Unadjusted & With energy & ekl & Reject CST & 1.009966 & 0.010742 & 0.983292 & 0.016708 & 0.000000 \\ 
+  PT & CES & Quality-adjusted & Without energy & kl & Adhere to CST & 1.335143 & 0.009131 & 0.300000 & 0.700000 & 0.000000 \\ 
+  PT & CES & Quality-adjusted & Without energy & kl & Reject CST & 1.017672 & 0.005739 & 1.000000 & 0.000000 & 0.000000 \\ 
+  PT & CES & Quality-adjusted & With energy & kle & Reject CST & 1.027582 & 0.004508 & 0.902835 & 0.000000 & 0.097165 \\ 
+  PT & CES & Quality-adjusted & With energy & lek & Reject CST & 1.016454 & 0.005790 & 1.000000 & 0.000000 & 0.000000 \\ 
+  PT & CES & Quality-adjusted & With energy & ekl & Reject CST & 1.017327 & 0.005789 & 1.000000 & 0.000000 & 0.000000 \\ 
+  UK & exp &  & Without energy &  & Reject CST &  & 0.023565 & 0.000000 & 0.000000 & 0.000000 \\ 
+  UK & CES & Unadjusted & Without energy & kl & Adhere to CST & 1.006734 & 0.020914 & 0.300000 & 0.700000 & 0.000000 \\ 
+  UK & CES & Unadjusted & Without energy & kl & Reject CST & 0.977872 & 0.017904 & 0.436298 & 0.563702 & 0.000000 \\ 
+  UK & CES & Unadjusted & With energy & kle & Reject CST & 0.989712 & 0.013857 & 0.445243 & 0.554757 & 0.000000 \\ 
+  UK & CES & Unadjusted & With energy & lek & Reject CST & 0.982919 & 0.020230 & 0.570049 & 0.134387 & 0.295564 \\ 
+  UK & CES & Unadjusted & With energy & ekl & Reject CST & 0.985088 & 0.022682 & 0.254298 & 0.738243 & 0.007460 \\ 
+  UK & CES & Quality-adjusted & Without energy & kl & Adhere to CST & 1.008638 & 0.013592 & 0.300000 & 0.700000 & 0.000000 \\ 
+  UK & CES & Quality-adjusted & Without energy & kl & Reject CST & 0.983725 & 0.001956 & 0.628728 & 0.371272 & 0.000000 \\ 
+  UK & CES & Quality-adjusted & With energy & kle & Reject CST & 0.980315 & 0.007103 & 0.426684 & 0.421804 & 0.151512 \\ 
+  UK & CES & Quality-adjusted & With energy & lek & Reject CST & 0.968799 & 0.007115 & 0.469167 & 0.144017 & 0.386817 \\ 
+  UK & CES & Quality-adjusted & With energy & ekl & Reject CST & 0.981695 & 0.011338 & 0.305749 & 0.642022 & 0.052229 \\ 
+   \hline
+\end{tabular}
+}
+\end{table}
+
+%
+% latex table generated in R 3.2.0 by xtable 1.7-4 package
+% Wed Jul  8 15:28:28 2015
+\begin{table}[ht]
+\centering
+\caption{Model parameters for all CES models.} 
+\label{tab:CES_coeffs_sigmas}
+{\tiny
+\begin{tabular}{llllllrrr}
+  \hline
+Country & model & flavor & energy & nest & cst & sigma\_1 & sigma & mse \\ 
+  \hline
+PT & exp &  & Without energy &  & Reject CST &  &  & 0.013359 \\ 
+  PT & CES & Unadjusted & Without energy & kl & Adhere to CST & 0.665163 &  & 0.011450 \\ 
+  PT & CES & Unadjusted & Without energy & kl & Reject CST & 0.173623 &  & 0.001113 \\ 
+  PT & CES & Unadjusted & With energy & kle & Reject CST & 0.078512 & 1.747120 & 0.000746 \\ 
+  PT & CES & Unadjusted & With energy & lek & Reject CST & 0.398887 & 0.013645 & 0.000588 \\ 
+  PT & CES & Unadjusted & With energy & ekl & Reject CST & 0.005193 & 0.186281 & 0.000985 \\ 
+  PT & CES & Quality-adjusted & Without energy & kl & Adhere to CST & 0.399944 &  & 0.009694 \\ 
+  PT & CES & Quality-adjusted & Without energy & kl & Reject CST & 0.017511 &  & 0.000804 \\ 
+  PT & CES & Quality-adjusted & With energy & kle & Reject CST & 0.017991 &     Inf & 0.000792 \\ 
+  PT & CES & Quality-adjusted & With energy & lek & Reject CST & 0.017595 & 0.005358 & 0.000812 \\ 
+  PT & CES & Quality-adjusted & With energy & ekl & Reject CST & 0.017013 &  & 0.000817 \\ 
+  UK & exp &  & Without energy &  & Reject CST &  &  & 0.001212 \\ 
+  UK & CES & Unadjusted & Without energy & kl & Adhere to CST & 0.509524 &  & 0.000491 \\ 
+  UK & CES & Unadjusted & Without energy & kl & Reject CST & 0.500000 &  & 0.000326 \\ 
+  UK & CES & Unadjusted & With energy & kle & Reject CST & 0.720815 & 0.009391 & 0.000223 \\ 
+  UK & CES & Unadjusted & With energy & lek & Reject CST &     Inf & 0.465188 & 0.000289 \\ 
+  UK & CES & Unadjusted & With energy & ekl & Reject CST & 0.103338 & 1.340508 & 0.000281 \\ 
+  UK & CES & Quality-adjusted & Without energy & kl & Adhere to CST & 0.545219 &  & 0.001207 \\ 
+  UK & CES & Quality-adjusted & Without energy & kl & Reject CST & 0.607601 &  & 0.000571 \\ 
+  UK & CES & Quality-adjusted & With energy & kle & Reject CST & 0.611818 & 0.014357 & 0.000267 \\ 
+  UK & CES & Quality-adjusted & With energy & lek & Reject CST &     Inf & 0.611994 & 0.000380 \\ 
+  UK & CES & Quality-adjusted & With energy & ekl & Reject CST & 0.190138 & 1.247783 & 0.000301 \\ 
+   \hline
+\end{tabular}
+}
+\end{table}
+
 %
@@
 %
-<<DSRmse_CD, results="asis">>=
-myXTable(filter(AllCoeffs, model=="CD") %>% select(Country, model, flavor, energy, cst, Dlambda, Dmse),
-         caption="$\\Delta \\lambda$ and $\\Delta mse$ for Cobb-Douglas models.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
+% latex table generated in R 3.2.0 by xtable 1.7-4 package
+% Wed Jul  8 15:28:28 2015
+\begin{table}[ht]
+\centering
+\caption{$\Delta \lambda$ and $\Delta mse$ for Cobb-Douglas models.} 
+\label{tab:DSRmse_CD}
+{\tiny
+\begin{tabular}{lllllrr}
+  \hline
+Country & model & flavor & energy & cst & Dlambda & Dmse \\ 
+  \hline
+PT & CD & Unadjusted & Without energy & Adhere to CST & $-$0.018427 & $-$0.001635 \\ 
+  PT & CD & Unadjusted & Without energy & Reject CST & $-$0.028968 & $-$0.010168 \\ 
+  PT & CD & Unadjusted & With energy & Reject CST & $-$0.030068 & $-$0.010730 \\ 
+  PT & CD & Quality-adjusted & Without energy & Adhere to CST & $-$0.030324 & $-$0.002019 \\ 
+  PT & CD & Quality-adjusted & Without energy & Reject CST & $-$0.019428 & $-$0.004422 \\ 
+  PT & CD & Quality-adjusted & With energy & Reject CST & $-$0.029938 & $-$0.011091 \\ 
+  UK & CD & Unadjusted & Without energy & Adhere to CST & $-$0.008055 & $-$0.000437 \\ 
+  UK & CD & Unadjusted & Without energy & Reject CST & $-$0.016911 & $-$0.000717 \\ 
+  UK & CD & Unadjusted & With energy & Reject CST & $-$0.005432 & $-$0.000880 \\ 
+  UK & CD & Quality-adjusted & Without energy & Adhere to CST & $-$0.014840 & 0.000352 \\ 
+  UK & CD & Quality-adjusted & Without energy & Reject CST & $-$0.015416 & $-$0.000492 \\ 
+  UK & CD & Quality-adjusted & With energy & Reject CST & $-$0.021584 & $-$0.000758 \\ 
+   \hline
+\end{tabular}
+}
+\end{table}
+
 % 
@@
 %
-<<DSRmse_CESkle, results="asis">>=
-myXTable(filter(AllCoeffs, (model=="CES" & (nest=="kl" | nest=="kle")) | model=="exp") %>% 
-           select(Country, model, flavor, energy, nest, cst, Dlambda, Dmse),
-         caption="$\\Delta \\lambda$ and $\\Delta mse$ for CES models with ($kl$)$e$ nesting.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-%
-<<DSRmse_CESlek, results="asis">>=
-myXTable(filter(AllCoeffs, (model=="CES" & (nest=="kl" | nest=="lek")) | model=="exp") %>% 
-           select(Country, model, flavor, energy, nest, cst, Dlambda, Dmse),
-         caption="$\\Delta \\lambda$ and $\\Delta mse$ for CES models with ($le$)$k$ nesting.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-%
-<<DSRmse_CESekl, results="asis">>=
-myXTable(filter(AllCoeffs, (model=="CES" & (nest=="kl" | nest=="ekl")) | model=="exp") %>% 
-           select(Country, model, flavor, energy, nest, cst, Dlambda, Dmse),
-         caption="$\\Delta \\lambda$ and $\\Delta mse$ for CES models with ($ek$)$l$ nesting.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
+% latex table generated in R 3.2.0 by xtable 1.7-4 package
+% Wed Jul  8 15:28:28 2015
+\begin{table}[ht]
+\centering
+\caption{$\Delta \lambda$ and $\Delta mse$ for CES models with ($kl$)$e$ nesting.} 
+\label{tab:DSRmse_CESkle}
+{\tiny
+\begin{tabular}{llllllrr}
+  \hline
+Country & model & flavor & energy & nest & cst & Dlambda & Dmse \\ 
+  \hline
+PT & exp &  & Without energy &  & Reject CST & 0.000000 & 0.000000 \\ 
+  PT & CES & Unadjusted & Without energy & kl & Adhere to CST & $-$0.015683 & $-$0.001908 \\ 
+  PT & CES & Unadjusted & Without energy & kl & Reject CST & $-$0.022103 & $-$0.012246 \\ 
+  PT & CES & Unadjusted & With energy & kle & Reject CST & $-$0.024769 & $-$0.012613 \\ 
+  PT & CES & Quality-adjusted & Without energy & kl & Adhere to CST & $-$0.025377 & $-$0.003665 \\ 
+  PT & CES & Quality-adjusted & Without energy & kl & Reject CST & $-$0.028768 & $-$0.012555 \\ 
+  PT & CES & Quality-adjusted & With energy & kle & Reject CST & $-$0.029999 & $-$0.012566 \\ 
+  UK & exp &  & Without energy &  & Reject CST & 0.000000 & 0.000000 \\ 
+  UK & CES & Unadjusted & Without energy & kl & Adhere to CST & $-$0.002651 & $-$0.000721 \\ 
+  UK & CES & Unadjusted & Without energy & kl & Reject CST & $-$0.005661 & $-$0.000886 \\ 
+  UK & CES & Unadjusted & With energy & kle & Reject CST & $-$0.009708 & $-$0.000989 \\ 
+  UK & CES & Quality-adjusted & Without energy & kl & Adhere to CST & $-$0.009973 & $-$0.000004 \\ 
+  UK & CES & Quality-adjusted & Without energy & kl & Reject CST & $-$0.021609 & $-$0.000641 \\ 
+  UK & CES & Quality-adjusted & With energy & kle & Reject CST & $-$0.016463 & $-$0.000944 \\ 
+   \hline
+\end{tabular}
+}
+\end{table}
+
+%
+% latex table generated in R 3.2.0 by xtable 1.7-4 package
+% Wed Jul  8 15:28:28 2015
+\begin{table}[ht]
+\centering
+\caption{$\Delta \lambda$ and $\Delta mse$ for CES models with ($le$)$k$ nesting.} 
+\label{tab:DSRmse_CESlek}
+{\tiny
+\begin{tabular}{llllllrr}
+  \hline
+Country & model & flavor & energy & nest & cst & Dlambda & Dmse \\ 
+  \hline
+PT & exp &  & Without energy &  & Reject CST & 0.000000 & 0.000000 \\ 
+  PT & CES & Unadjusted & Without energy & kl & Adhere to CST & $-$0.015683 & $-$0.001908 \\ 
+  PT & CES & Unadjusted & Without energy & kl & Reject CST & $-$0.022103 & $-$0.012246 \\ 
+  PT & CES & Unadjusted & With energy & lek & Reject CST & $-$0.026189 & $-$0.012771 \\ 
+  PT & CES & Quality-adjusted & Without energy & kl & Adhere to CST & $-$0.025377 & $-$0.003665 \\ 
+  PT & CES & Quality-adjusted & Without energy & kl & Reject CST & $-$0.028768 & $-$0.012555 \\ 
+  PT & CES & Quality-adjusted & With energy & lek & Reject CST & $-$0.028717 & $-$0.012546 \\ 
+  UK & exp &  & Without energy &  & Reject CST & 0.000000 & 0.000000 \\ 
+  UK & CES & Unadjusted & Without energy & kl & Adhere to CST & $-$0.002651 & $-$0.000721 \\ 
+  UK & CES & Unadjusted & Without energy & kl & Reject CST & $-$0.005661 & $-$0.000886 \\ 
+  UK & CES & Unadjusted & With energy & lek & Reject CST & $-$0.003335 & $-$0.000923 \\ 
+  UK & CES & Quality-adjusted & Without energy & kl & Adhere to CST & $-$0.009973 & $-$0.000004 \\ 
+  UK & CES & Quality-adjusted & Without energy & kl & Reject CST & $-$0.021609 & $-$0.000641 \\ 
+  UK & CES & Quality-adjusted & With energy & lek & Reject CST & $-$0.016450 & $-$0.000831 \\ 
+   \hline
+\end{tabular}
+}
+\end{table}
+
+%
+% latex table generated in R 3.2.0 by xtable 1.7-4 package
+% Wed Jul  8 15:28:28 2015
+\begin{table}[ht]
+\centering
+\caption{$\Delta \lambda$ and $\Delta mse$ for CES models with ($ek$)$l$ nesting.} 
+\label{tab:DSRmse_CESekl}
+{\tiny
+\begin{tabular}{llllllrr}
+  \hline
+Country & model & flavor & energy & nest & cst & Dlambda & Dmse \\ 
+  \hline
+PT & exp &  & Without energy &  & Reject CST & 0.000000 & 0.000000 \\ 
+  PT & CES & Unadjusted & Without energy & kl & Adhere to CST & $-$0.015683 & $-$0.001908 \\ 
+  PT & CES & Unadjusted & Without energy & kl & Reject CST & $-$0.022103 & $-$0.012246 \\ 
+  PT & CES & Unadjusted & With energy & ekl & Reject CST & $-$0.023766 & $-$0.012374 \\ 
+  PT & CES & Quality-adjusted & Without energy & kl & Adhere to CST & $-$0.025377 & $-$0.003665 \\ 
+  PT & CES & Quality-adjusted & Without energy & kl & Reject CST & $-$0.028768 & $-$0.012555 \\ 
+  PT & CES & Quality-adjusted & With energy & ekl & Reject CST & $-$0.028718 & $-$0.012542 \\ 
+  UK & exp &  & Without energy &  & Reject CST & 0.000000 & 0.000000 \\ 
+  UK & CES & Unadjusted & Without energy & kl & Adhere to CST & $-$0.002651 & $-$0.000721 \\ 
+  UK & CES & Unadjusted & Without energy & kl & Reject CST & $-$0.005661 & $-$0.000886 \\ 
+  UK & CES & Unadjusted & With energy & ekl & Reject CST & $-$0.000883 & $-$0.000930 \\ 
+  UK & CES & Quality-adjusted & Without energy & kl & Adhere to CST & $-$0.009973 & $-$0.000004 \\ 
+  UK & CES & Quality-adjusted & Without energy & kl & Reject CST & $-$0.021609 & $-$0.000641 \\ 
+  UK & CES & Quality-adjusted & With energy & ekl & Reject CST & $-$0.012227 & $-$0.000910 \\ 
+   \hline
+\end{tabular}
+}
+\end{table}
+
 %
@@
 %
-<<DSRmse_CD_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta mse$) for the Cobb-Douglas model relative to the exponential-only model.">>=
-ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CD"), mapping=aes(x=Dmse, y=Dlambda, color=energy, size=cst)) +
-  facet_grid(Country ~ flavor) +
-  scale_size_manual(values=c(2,3.5)) +
-  xlab(expression(Delta * mse)) + 
-  scale_x_continuous(breaks=seq(-0.01, 0, 0.005), limits=c(-0.012, 0.003)) +  
-  ylab(expression(Delta * lambda)) +
-  scale_y_continuous(limits=c(-0.04, 0)) +
-  xy_theme() + 
-  theme(legend.title=element_blank())
-@
-%
-<<percDSRmse_CD_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Percentage change in Solow Residuals~($\\Delta\\lambda \\, [\\%]$) and mean squared error~($\\Delta mse \\, [\\%]$) for the Cobb-Douglas model relative to exponential-only models.">>=
-ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CD"), mapping=aes(x=percDmse, y=percDlambda, color=energy, size=cst)) +
-  facet_grid(Country ~ flavor) +
-  scale_size_manual(values=c(2,3.5)) +
-  xlab(expression(paste(Delta * mse, " [%]"))) + 
-  scale_x_continuous(breaks=seq(-50, 50, 50), limits=c(-90, 50)) +  
-  ylab(expression(paste(Delta * lambda, " [%]"))) +
-  scale_y_continuous(breaks=seq(-80, 0, 20), limits=c(-100, 10)) +  
-  xy_theme() + 
-  theme(legend.title=element_blank())
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[H]
+
+{\centering \includegraphics[width=\maxwidth]{figure/DSRmse_CD_graph-1}
+
+}
+
+\caption[Change in Solow Residuals~(]{Change in Solow Residuals~($\Delta\lambda$) and mean squared error~($\Delta mse$) for the Cobb-Douglas model relative to the exponential-only model.}\label{fig:DSRmse_CD_graph}
+\end{figure}
+
+\end{knitrout}
+%
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[H]
+
+{\centering \includegraphics[width=\maxwidth]{figure/percDSRmse_CD_graph-1}
+
+}
+
+\caption[Percentage change in Solow Residuals~(]{Percentage change in Solow Residuals~($\Delta\lambda \, [\%]$) and mean squared error~($\Delta mse \, [\%]$) for the Cobb-Douglas model relative to exponential-only models.}\label{fig:percDSRmse_CD_graph}
+\end{figure}
+
+\end{knitrout}
 %
@@
 %
-<<DSRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta mse$) for the CES modles relative to the exponential-only model.">>=
-ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=Dmse, y=Dlambda, color=energy, size=cst, shape=nest)) +
-  scale_size_manual(values=c(2,3.5)) +
-  scale_shape_manual(values=c(16,17,18,15)) +
-  facet_grid(Country ~ flavor) +
-  xlab(expression(Delta * mse)) + 
-  scale_x_continuous(breaks=seq(-0.005, 0, 0.005)) +  
-  ylab(expression(Delta * lambda)) +
-  xy_theme() +
-  theme(legend.title=element_blank())
-@
-%
-<<percDSRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Percentage change in Solow Residuals~($\\Delta\\lambda \\, [\\%]$) and mean squared error~($\\Delta mse \\, [\\%]$) for the CES models relative to the exponential-only model.">>=
-ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=percDmse, y=percDlambda, color=energy, size=cst, shape=nest)) +
-  scale_size_manual(values=c(2,3.5)) +
-  scale_shape_manual(values=c(16,17,18,15)) +
-  facet_grid(Country ~ flavor) +
-  xlab(expression(paste(Delta * mse, " [%]"))) + 
-  scale_x_continuous(breaks=seq(-80, 0, 20)) +  
-  ylab(expression(paste(Delta * lambda, " [%]"))) +
-  scale_y_continuous(breaks=seq(-80, 0, 20), limits=c(-100, 10)) +  
-  xy_theme() +
-  theme(legend.title=element_blank())
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[H]
+
+{\centering \includegraphics[width=\maxwidth]{figure/DSRmse_CES_graph-1}
+
+}
+
+\caption[Change in Solow Residuals~(]{Change in Solow Residuals~($\Delta\lambda$) and mean squared error~($\Delta mse$) for the CES modles relative to the exponential-only model.}\label{fig:DSRmse_CES_graph}
+\end{figure}
+
+\end{knitrout}
+%
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[H]
+
+{\centering \includegraphics[width=\maxwidth]{figure/percDSRmse_CES_graph-1}
+
+}
+
+\caption[Percentage change in Solow Residuals~(]{Percentage change in Solow Residuals~($\Delta\lambda \, [\%]$) and mean squared error~($\Delta mse \, [\%]$) for the CES models relative to the exponential-only model.}\label{fig:percDSRmse_CES_graph}
+\end{figure}
+
+\end{knitrout}
 
@@
 %
-<<r_p_values, results="asis">>=
-# Calculate p values for groups of fitting residuals.
-r.t.values <- fitted_and_resid_data %>% 
-  group_by(Country, model, flavor, energy, nest) %>% 
-  summarize(Residuals.mean = mean(Residuals), Residuals.p.value = stats::t.test(Residuals)[["p.value"]])
-r.t.values <- arrange(ungroup(r.t.values), Country, model, flavor, energy, nest)
-# Display the values in a table
-myXTable(r.t.values,
-         caption="Means and p-values for fitting residuals~($r_i$).",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
+% latex table generated in R 3.2.0 by xtable 1.7-4 package
+% Wed Jul  8 15:28:29 2015
+\begin{table}[ht]
+\centering
+\caption{Means and p-values for fitting residuals~($r_i$).} 
+\label{tab:r_p_values}
+{\tiny
+\begin{tabular}{lllllrr}
+  \hline
+Country & model & flavor & energy & nest & Residuals.mean & Residuals.p.value \\ 
+  \hline
+PT & CD & Unadjusted & Without energy &  & $-$0.000000 & 1.000000 \\ 
+  PT & CD & Unadjusted & With energy &  & $-$0.000000 & 1.000000 \\ 
+  PT & CD & Quality-adjusted & Without energy &  & 0.000000 & 1.000000 \\ 
+  PT & CD & Quality-adjusted & With energy &  & 0.000000 & 1.000000 \\ 
+  PT & CES & Unadjusted & Without energy & kl & 0.000000 & 0.999999 \\ 
+  PT & CES & Unadjusted & With energy & kle & $-$0.000000 & 0.999999 \\ 
+  PT & CES & Unadjusted & With energy & lek & $-$0.000162 & 0.962887 \\ 
+  PT & CES & Unadjusted & With energy & ekl & $-$0.000080 & 0.985890 \\ 
+  PT & CES & Quality-adjusted & Without energy & kl & $-$0.000025 & 0.997238 \\ 
+  PT & CES & Quality-adjusted & With energy & kle & $-$0.000083 & 0.983608 \\ 
+  PT & CES & Quality-adjusted & With energy & lek & $-$0.000007 & 0.998657 \\ 
+  PT & CES & Quality-adjusted & With energy & ekl & 0.000001 & 0.999715 \\ 
+  PT & exp &  & Without energy &  & $-$0.000000 & 1.000000 \\ 
+  UK & CD & Unadjusted & Without energy &  & 0.000000 & 1.000000 \\ 
+  UK & CD & Unadjusted & With energy &  & $-$0.000000 & 1.000000 \\ 
+  UK & CD & Quality-adjusted & Without energy &  & 0.000000 & 1.000000 \\ 
+  UK & CD & Quality-adjusted & With energy &  & $-$0.000000 & 1.000000 \\ 
+  UK & CES & Unadjusted & Without energy & kl & $-$0.000000 & 1.000000 \\ 
+  UK & CES & Unadjusted & With energy & kle & $-$0.000037 & 0.986099 \\ 
+  UK & CES & Unadjusted & With energy & lek & $-$0.000000 & 1.000000 \\ 
+  UK & CES & Unadjusted & With energy & ekl & 0.000000 & 0.999997 \\ 
+  UK & CES & Quality-adjusted & Without energy & kl & 0.000000 & 0.999999 \\ 
+  UK & CES & Quality-adjusted & With energy & kle & $-$0.000000 & 0.999998 \\ 
+  UK & CES & Quality-adjusted & With energy & lek & 0.000000 & 1.000000 \\ 
+  UK & CES & Quality-adjusted & With energy & ekl & 0.000000 & 0.999998 \\ 
+  UK & exp &  & Without energy &  & $-$0.000000 & 1.000000 \\ 
+   \hline
+\end{tabular}
+}
+\end{table}
 
@@
 %
-<<Dr_p_values, results="asis">>=
-# Calculate p values for groups of Dr values.
-Dr.t.values <- fitted_and_resid_data %>% 
-  group_by(Country, model, flavor, energy, nest) %>% 
-  summarize(Dr.mean = mean(Dr), Dr.p.value = stats::t.test(Dr, alternative = "less")[["p.value"]])
-Dr.t.values <- arrange(ungroup(Dr.t.values), Country, model, flavor, energy, nest)
-# Display the values in a table
-myXTable(Dr.t.values,
-         caption="Means and p-values for $\\Delta r$.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
+% latex table generated in R 3.2.0 by xtable 1.7-4 package
+% Wed Jul  8 15:28:29 2015
+\begin{table}[ht]
+\centering
+\caption{Means and p-values for $\Delta r$.} 
+\label{tab:Dr_p_values}
+{\tiny
+\begin{tabular}{lllllrr}
+  \hline
+Country & model & flavor & energy & nest & Dr.mean & Dr.p.value \\ 
+  \hline
+PT & CD & Unadjusted & Without energy &  & $-$0.025733 & 0.000000 \\ 
+  PT & CD & Unadjusted & With energy &  & $-$0.048181 & 0.000000 \\ 
+  PT & CD & Quality-adjusted & Without energy &  & $-$0.009587 & 0.003533 \\ 
+  PT & CD & Quality-adjusted & With energy &  & $-$0.051804 & 0.000000 \\ 
+  PT & CES & Unadjusted & Without energy & kl & $-$0.038049 & 0.000000 \\ 
+  PT & CES & Unadjusted & With energy & kle & $-$0.069223 & 0.000000 \\ 
+  PT & CES & Unadjusted & With energy & lek & $-$0.071483 & 0.000000 \\ 
+  PT & CES & Unadjusted & With energy & ekl & $-$0.065928 & 0.000000 \\ 
+  PT & CES & Quality-adjusted & Without energy & kl & $-$0.042697 & 0.000000 \\ 
+  PT & CES & Quality-adjusted & With energy & kle & $-$0.067761 & 0.000000 \\ 
+  PT & CES & Quality-adjusted & With energy & lek & $-$0.067419 & 0.000000 \\ 
+  PT & CES & Quality-adjusted & With energy & ekl & $-$0.067335 & 0.000000 \\ 
+  PT & exp &  & Without energy &  & 0.000000 &  \\ 
+  UK & CD & Unadjusted & Without energy &  & $-$0.011254 & 0.000003 \\ 
+  UK & CD & Unadjusted & With energy &  & $-$0.014450 & 0.000000 \\ 
+  UK & CD & Quality-adjusted & Without energy &  & $-$0.004538 & 0.055557 \\ 
+  UK & CD & Quality-adjusted & With energy &  & $-$0.012454 & 0.000072 \\ 
+  UK & CES & Unadjusted & Without energy & kl & $-$0.013655 & 0.000000 \\ 
+  UK & CES & Unadjusted & With energy & kle & $-$0.017349 & 0.000000 \\ 
+  UK & CES & Unadjusted & With energy & lek & $-$0.015158 & 0.000000 \\ 
+  UK & CES & Unadjusted & With energy & ekl & $-$0.015557 & 0.000000 \\ 
+  UK & CES & Quality-adjusted & Without energy & kl & $-$0.007222 & 0.003270 \\ 
+  UK & CES & Quality-adjusted & With energy & kle & $-$0.016547 & 0.000000 \\ 
+  UK & CES & Quality-adjusted & With energy & lek & $-$0.013366 & 0.000007 \\ 
+  UK & CES & Quality-adjusted & With energy & ekl & $-$0.014973 & 0.000000 \\ 
+  UK & exp &  & Without energy &  & 0.000000 &  \\ 
+   \hline
+\end{tabular}
+}
+\end{table}
 
@@
 
-<<Factor_shares_bar_graph_function>>=
-fsbg <- function(coun, mod){
-  bar_chart_data <- filter(AllCoeffs, Country==coun & model==mod) %>% 
-    select(Country, model, flavor, energy, nest, cst, alpha_1, alpha_2, alpha_3)
-  # Change nest to a nicer-looking nest string
-  bar_chart_data$nest <- plyr::mapvalues(bar_chart_data$nest, 
-                                         from=c("kl", "kle", "lek", "ekl"), 
-                                         to=c("(kl)", "(kl)e", "(le)k", "(ek)l"))
-  # Add a label column
-  bar_chart_data$label <- paste(bar_chart_data$cst, bar_chart_data$flavor, 
-                                bar_chart_data$energy, bar_chart_data$nest, sep=", ")
-  # Capture the order that we want for the models on the vertical axis.
-  order <- bar_chart_data$label
-  # Now melt the data
-  bar_chart_data <- melt(bar_chart_data, 
-                         measure.vars = c("alpha_1", "alpha_2", "alpha_3"), 
-                         value.name = "value", 
-                         variable.name = "variable")
-  # Define the color palette (see http://www.cookbook-r.com/Graphs/Colors_(ggplot2))
-  cbPalette <- c("#E69F00", "#999999", "#F0E442", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")
-  # Make the plot
-  plot <- ggplot(bar_chart_data, mapping=aes(x=label, y=value, fill=variable, width=0.4)) + 
-    geom_bar(stat="identity") + 
-    xlab("") +
-    scale_x_discrete(limits=rev(order)) +
-    ylab("") +
-    scale_y_continuous(breaks=c(0, 0.5, 1)) + 
-    guides(fill=guide_legend(title=NULL)) +
-    coord_flip() + 
-    scale_fill_brewer(palette="OrRd") +
-    xy_theme() +
-    theme(axis.ticks.y = element_blank())
-  return(plot)
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[H]
+
+{\centering \includegraphics[width=\maxwidth]{figure/Factor_shares_graph_PT-1}
+
 }
-@
-
-<<Factor_shares_graph_PT, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=2.5, fig.cap="Factor shares ($\\alpha$ values) for CES models for Portugal.">>=
-fsbg(coun = "PT", mod = "CES")
-@
-
-<<Factor_shares_graph_UK, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=2.5, fig.cap="Factor shares ($\\alpha$ values) for CES models for the UK.">>=
-fsbg(coun = "UK", mod = "CES")
-@
+
+\caption[Factor shares (]{Factor shares ($\alpha$ values) for CES models for Portugal.}\label{fig:Factor_shares_graph_PT}
+\end{figure}
+
+\end{knitrout}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[H]
+
+{\centering \includegraphics[width=\maxwidth]{figure/Factor_shares_graph_UK-1}
+
+}
+
+\caption[Factor shares (]{Factor shares ($\alpha$ values) for CES models for the UK.}\label{fig:Factor_shares_graph_UK}
+\end{figure}
+
+\end{knitrout}
 
@@
 %
-<<residual_correlation, echo=TRUE>>=
-mod <- models$PT$unadjusted$noE$CD
-r_regression <- lm(formula = resid(mod) ~ mod$data$iYear)
-print(summary(r_regression))
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+\hlstd{mod} \hlkwb{<-} \hlstd{models}\hlopt{$}\hlstd{PT}\hlopt{$}\hlstd{unadjusted}\hlopt{$}\hlstd{noE}\hlopt{$}\hlstd{CD}
+\hlstd{r_regression} \hlkwb{<-} \hlkwd{lm}\hlstd{(}\hlkwc{formula} \hlstd{=} \hlkwd{resid}\hlstd{(mod)} \hlopt{~} \hlstd{mod}\hlopt{$}\hlstd{data}\hlopt{$}\hlstd{iYear)}
+\hlkwd{print}\hlstd{(}\hlkwd{summary}\hlstd{(r_regression))}
+\end{alltt}
+\begin{verbatim}
+
+Call:
+lm(formula = resid(mod) ~ mod$data$iYear)
+
+Residuals:
+      Min        1Q    Median        3Q       Max 
+-0.107498 -0.040098  0.009557  0.044471  0.109683
+
+Coefficients:
+                 Estimate Std. Error t value Pr(>|t|)
+(Intercept)    -1.366e-17  1.575e-02       0        1
+mod$data$iYear  3.847e-19  5.322e-04       0        1
+
+Residual standard error: 0.0576 on 50 degrees of freedom
+Multiple R-squared:  5.069e-32,	Adjusted R-squared:  -0.02 
+F-statistic: 2.535e-30 on 1 and 50 DF,  p-value: 1
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
 %
@@
 is incredibly small relative to the scale of the residuals~($r_i$),
-\Sexpr{coef(r_regression)[[2]]}, 
+\ensuremath{3.8468693\times 10^{-19}}, 
 indicating that there is little 
@@
 is very small relative to the scale of the residuals~($r_i$),
-\Sexpr{coef(r_regression)[[1]]}, 
+\ensuremath{-1.3658522\times 10^{-17}}, 
 indicating that there is little time-independent information in the residuals~($r_i$).
@@
 %
-<<Residuals_comparison, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Comparison between $\\varepsilon_i^*$ and $r_i$">>=
-resids_comparison_df <- data.frame(list(iYear=mod$data$iYear, r=resid(mod), epsistar = resid(r_regression)))
-# resids_comparison_df <- melt(resids_comparison_df, measure.vars=c(r, epsistar), value.name="value", 
-#                              variable.name="name")
-ggplot(resids_comparison_df) + 
-  geom_point(mapping=aes(x=r, y=epsistar)) + 
-  xlab(expression(r[i])) +
-  ylab(expression(epsilon[i]^"*")) +
-  xy_theme()
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[H]
+
+{\centering \includegraphics[width=\maxwidth]{figure/Residuals_comparison-1}
+
+}
+
+\caption[Comparison between ]{Comparison between $\varepsilon_i^*$ and $r_i$}\label{fig:Residuals_comparison}
+\end{figure}
+
+\end{knitrout}
 %
@@
 
-<<Correlograms_CST, echo=FALSE, message=FALSE>>=
-leaf_apply(l = modelsCST, class = c("lm", "plm"), f = function(model, name){
-  acf(resid(model), main=name)
-})
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/Correlograms_CST-1}
+
+\includegraphics[width=\maxwidth]{figure/Correlograms_CST-2}
+
+\includegraphics[width=\maxwidth]{figure/Correlograms_CST-3}
+
+\includegraphics[width=\maxwidth]{figure/Correlograms_CST-4}
+
+\includegraphics[width=\maxwidth]{figure/Correlograms_CST-5}
+
+\includegraphics[width=\maxwidth]{figure/Correlograms_CST-6}
+
+\includegraphics[width=\maxwidth]{figure/Correlograms_CST-7}
+
+\includegraphics[width=\maxwidth]{figure/Correlograms_CST-8} 
+\begin{kframe}\begin{verbatim}
+$PT.unadjusted.noE.CD
+
+Autocorrelations of series 'resid(model)', by lag
+
+     0      1      2      3      4      5      6      7      8      9 
+ 1.000  0.865  0.726  0.601  0.485  0.371  0.260  0.157  0.078  0.028 
+    10     11     12     13     14     15     16     17 
+-0.041 -0.110 -0.161 -0.174 -0.144 -0.150 -0.177 -0.190
+
+$PT.unadjusted.noE.CES.kl
+
+Autocorrelations of series 'resid(model)', by lag
+
+     0      1      2      3      4      5      6      7      8      9 
+ 1.000  0.865  0.727  0.605  0.492  0.379  0.267  0.164  0.086  0.036 
+    10     11     12     13     14     15     16     17 
+-0.034 -0.107 -0.162 -0.175 -0.144 -0.152 -0.179 -0.194
+
+$PT.adjusted.noE.CD
+
+Autocorrelations of series 'resid(model)', by lag
+
+     0      1      2      3      4      5      6      7      8      9 
+ 1.000  0.852  0.696  0.566  0.445  0.326  0.219  0.116  0.039 -0.003 
+    10     11     12     13     14     15     16     17 
+-0.069 -0.139 -0.176 -0.186 -0.148 -0.154 -0.186 -0.200
+
+$PT.adjusted.noE.CES.kl
+
+Autocorrelations of series 'resid(model)', by lag
+
+     0      1      2      3      4      5      6      7      8      9 
+ 1.000  0.842  0.676  0.543  0.422  0.299  0.186  0.083  0.008 -0.030 
+    10     11     12     13     14     15     16     17 
+-0.098 -0.174 -0.211 -0.213 -0.162 -0.163 -0.188 -0.198
+
+$UK.unadjusted.noE.CD
+
+Autocorrelations of series 'resid(model)', by lag
+
+     0      1      2      3      4      5      6      7      8      9 
+ 1.000  0.711  0.401  0.255  0.211  0.158  0.053 -0.011 -0.009  0.016 
+    10     11     12     13     14     15     16     17 
+ 0.018  0.017 -0.029 -0.014  0.029  0.047  0.002 -0.015
+
+$UK.unadjusted.noE.CES.kl
+
+Autocorrelations of series 'resid(model)', by lag
+
+     0      1      2      3      4      5      6      7      8      9 
+ 1.000  0.634  0.259  0.125  0.119  0.063 -0.072 -0.121 -0.067 -0.032 
+    10     11     12     13     14     15     16     17 
+ 0.000  0.024 -0.033 -0.006  0.029  0.049 -0.018 -0.030
+
+$UK.adjusted.noE.CD
+
+Autocorrelations of series 'resid(model)', by lag
+
+     0      1      2      3      4      5      6      7      8      9 
+ 1.000  0.784  0.548  0.427  0.373  0.304  0.203  0.123  0.086  0.068 
+    10     11     12     13     14     15     16     17 
+ 0.043  0.029 -0.011 -0.024 -0.024 -0.040 -0.092 -0.129
+
+$UK.adjusted.noE.CES.kl
+
+Autocorrelations of series 'resid(model)', by lag
+
+     0      1      2      3      4      5      6      7      8      9 
+ 1.000  0.740  0.470  0.344  0.298  0.226  0.120  0.054  0.041  0.021 
+    10     11     12     13     14     15     16     17 
+ 0.009  0.016 -0.018 -0.023 -0.031 -0.044 -0.093 -0.116 
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
 
@@
 
-<<Correlograms_noCST, echo=FALSE, message=FALSE>>=
-leaf_apply(l = models, class = c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, name){
-  acf(resid(model), main=name)
-})
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/Correlograms_noCST-1}
+
+\includegraphics[width=\maxwidth]{figure/Correlograms_noCST-2}
+
+\includegraphics[width=\maxwidth]{figure/Correlograms_noCST-3}
+
+\includegraphics[width=\maxwidth]{figure/Correlograms_noCST-4}
+
+\includegraphics[width=\maxwidth]{figure/Correlograms_noCST-5}
+
+\includegraphics[width=\maxwidth]{figure/Correlograms_noCST-6}
+
+\includegraphics[width=\maxwidth]{figure/Correlograms_noCST-7}
+
+\includegraphics[width=\maxwidth]{figure/Correlograms_noCST-8}
+
+\includegraphics[width=\maxwidth]{figure/Correlograms_noCST-9}
+
+\includegraphics[width=\maxwidth]{figure/Correlograms_noCST-10}
+
+\includegraphics[width=\maxwidth]{figure/Correlograms_noCST-11}
+
+\includegraphics[width=\maxwidth]{figure/Correlograms_noCST-12}
+
+\includegraphics[width=\maxwidth]{figure/Correlograms_noCST-13}
+
+\includegraphics[width=\maxwidth]{figure/Correlograms_noCST-14}
+
+\includegraphics[width=\maxwidth]{figure/Correlograms_noCST-15}
+
+\includegraphics[width=\maxwidth]{figure/Correlograms_noCST-16}
+
+\includegraphics[width=\maxwidth]{figure/Correlograms_noCST-17}
+
+\includegraphics[width=\maxwidth]{figure/Correlograms_noCST-18}
+
+\includegraphics[width=\maxwidth]{figure/Correlograms_noCST-19}
+
+\includegraphics[width=\maxwidth]{figure/Correlograms_noCST-20}
+
+\includegraphics[width=\maxwidth]{figure/Correlograms_noCST-21}
+
+\includegraphics[width=\maxwidth]{figure/Correlograms_noCST-22}
+
+\includegraphics[width=\maxwidth]{figure/Correlograms_noCST-23}
+
+\includegraphics[width=\maxwidth]{figure/Correlograms_noCST-24} 
+\begin{kframe}\begin{verbatim}
+$PT.unadjusted.noE.CD
+
+Autocorrelations of series 'resid(model)', by lag
+
+     0      1      2      3      4      5      6      7      8      9 
+ 1.000  0.813  0.597  0.388  0.185  0.045 -0.042 -0.125 -0.137 -0.133 
+    10     11     12     13     14     15     16     17 
+-0.210 -0.270 -0.304 -0.327 -0.270 -0.191 -0.155 -0.073
+
+$PT.unadjusted.noE.CES.kl
+
+Autocorrelations of series 'resid(model)', by lag
+
+     0      1      2      3      4      5      6      7      8      9 
+ 1.000  0.651  0.285  0.104 -0.064 -0.121 -0.178 -0.113  0.085  0.133 
+    10     11     12     13     14     15     16     17 
+-0.061 -0.278 -0.413 -0.472 -0.461 -0.324 -0.116  0.013
+
+$PT.unadjusted.withE.CD
+
+Autocorrelations of series 'resid(model)', by lag
+
+     0      1      2      3      4      5      6      7      8      9 
+ 1.000  0.780  0.551  0.386  0.215  0.058 -0.057 -0.161 -0.167 -0.119 
+    10     11     12     13     14     15     16 
+-0.184 -0.233 -0.276 -0.294 -0.213 -0.139 -0.151
+
+$PT.unadjusted.withE.CES.kle
+
+Autocorrelations of series 'resid(model)', by lag
+
+     0      1      2      3      4      5      6      7      8      9 
+ 1.000  0.514  0.042 -0.070 -0.098 -0.123 -0.275 -0.225  0.085  0.219 
+    10     11     12     13     14     15     16 
+ 0.005 -0.129 -0.217 -0.298 -0.213 -0.110 -0.043
+
+$PT.unadjusted.withE.CES.lek
+
+Autocorrelations of series 'resid(model)', by lag
+
+     0      1      2      3      4      5      6      7      8      9 
+ 1.000  0.404 -0.109 -0.163 -0.199 -0.253 -0.384 -0.175  0.255  0.386 
+    10     11     12     13     14     15     16 
+ 0.165  0.018 -0.107 -0.282 -0.286 -0.166 -0.028
+
+$PT.unadjusted.withE.CES.ekl
+
+Autocorrelations of series 'resid(model)', by lag
+
+     0      1      2      3      4      5      6      7      8      9 
+ 1.000  0.539  0.134  0.043 -0.038 -0.133 -0.285 -0.218  0.033  0.139 
+    10     11     12     13     14     15     16 
+-0.077 -0.203 -0.265 -0.336 -0.348 -0.259 -0.105
+
+$PT.adjusted.noE.CD
+
+Autocorrelations of series 'resid(model)', by lag
+
+     0      1      2      3      4      5      6      7      8      9 
+ 1.000  0.877  0.728  0.599  0.473  0.360  0.267  0.170  0.101  0.066 
+    10     11     12     13     14     15     16     17 
+-0.004 -0.064 -0.118 -0.162 -0.167 -0.175 -0.216 -0.232
+
+$PT.adjusted.noE.CES.kl
+
+Autocorrelations of series 'resid(model)', by lag
+
+     0      1      2      3      4      5      6      7      8      9 
+ 1.000  0.428 -0.104 -0.252 -0.335 -0.273 -0.252 -0.072  0.305  0.463 
+    10     11     12     13     14     15     16     17 
+ 0.184 -0.140 -0.289 -0.346 -0.284 -0.079  0.175  0.265
+
+$PT.adjusted.withE.CD
+
+Autocorrelations of series 'resid(model)', by lag
+
+     0      1      2      3      4      5      6      7      8      9 
+ 1.000  0.757  0.530  0.401  0.237  0.040 -0.133 -0.343 -0.420 -0.411 
+    10     11     12     13     14     15     16 
+-0.435 -0.397 -0.355 -0.274 -0.145 -0.004  0.065
+
+$PT.adjusted.withE.CES.kle
+
+Autocorrelations of series 'resid(model)', by lag
+
+     0      1      2      3      4      5      6      7      8      9 
+ 1.000  0.476 -0.023 -0.152 -0.239 -0.221 -0.255 -0.143  0.188  0.332 
+    10     11     12     13     14     15     16 
+ 0.077 -0.169 -0.286 -0.329 -0.245 -0.077  0.133
+
+$PT.adjusted.withE.CES.lek
+
+Autocorrelations of series 'resid(model)', by lag
+
+     0      1      2      3      4      5      6      7      8      9 
+ 1.000  0.410 -0.108 -0.246 -0.342 -0.275 -0.259 -0.080  0.305  0.465 
+    10     11     12     13     14     15     16 
+ 0.184 -0.113 -0.262 -0.332 -0.288 -0.094  0.165
+
+$PT.adjusted.withE.CES.ekl
+
+Autocorrelations of series 'resid(model)', by lag
+
+     0      1      2      3      4      5      6      7      8      9 
+ 1.000  0.422 -0.106 -0.249 -0.332 -0.268 -0.252 -0.075  0.302  0.457 
+    10     11     12     13     14     15     16 
+ 0.172 -0.130 -0.278 -0.338 -0.282 -0.084  0.173
+
+$UK.unadjusted.noE.CD
+
+Autocorrelations of series 'resid(model)', by lag
+
+     0      1      2      3      4      5      6      7      8      9 
+ 1.000  0.595  0.130 -0.075 -0.107 -0.130 -0.225 -0.260 -0.193 -0.121 
+    10     11     12     13     14     15     16     17 
+-0.048 -0.012 -0.045  0.001  0.084  0.177  0.199  0.222
+
+$UK.unadjusted.noE.CES.kl
+
+Autocorrelations of series 'resid(model)', by lag
+
+     0      1      2      3      4      5      6      7      8      9 
+ 1.000  0.509  0.021 -0.117 -0.085 -0.133 -0.294 -0.323 -0.198 -0.164 
+    10     11     12     13     14     15     16     17 
+-0.068 -0.001 -0.040  0.027  0.068  0.132  0.095  0.112
+
+$UK.unadjusted.withE.CD
+
+Autocorrelations of series 'resid(model)', by lag
+
+     0      1      2      3      4      5      6      7      8      9 
+ 1.000  0.527  0.105 -0.064  0.004 -0.051 -0.249 -0.339 -0.321 -0.272 
+    10     11     12     13     14     15     16     17 
+-0.172 -0.133 -0.109 -0.052  0.078  0.147  0.207  0.213
+
+$UK.unadjusted.withE.CES.kle
+
+Autocorrelations of series 'resid(model)', by lag
+
+     0      1      2      3      4      5      6      7      8      9 
+ 1.000  0.449  0.055 -0.100 -0.028 -0.044 -0.257 -0.376 -0.268 -0.179 
+    10     11     12     13     14     15     16     17 
+-0.099 -0.055 -0.128 -0.010  0.111  0.227  0.136  0.099
+
+$UK.unadjusted.withE.CES.lek
+
+Autocorrelations of series 'resid(model)', by lag
+
+     0      1      2      3      4      5      6      7      8      9 
+ 1.000  0.521  0.074 -0.053  0.014 -0.059 -0.291 -0.378 -0.309 -0.279 
+    10     11     12     13     14     15     16     17 
+-0.161 -0.091 -0.099 -0.027  0.058  0.136  0.156  0.157
+
+$UK.unadjusted.withE.CES.ekl
+
+Autocorrelations of series 'resid(model)', by lag
+
+     0      1      2      3      4      5      6      7      8      9 
+ 1.000  0.513  0.080 -0.037  0.017 -0.036 -0.304 -0.416 -0.346 -0.311 
+    10     11     12     13     14     15     16     17 
+-0.174 -0.085 -0.089  0.000  0.092  0.165  0.195  0.176
+
+$UK.adjusted.noE.CD
+
+Autocorrelations of series 'resid(model)', by lag
+
+     0      1      2      3      4      5      6      7      8      9 
+ 1.000  0.645  0.192 -0.020 -0.083 -0.109 -0.213 -0.302 -0.266 -0.140 
+    10     11     12     13     14     15     16     17 
+-0.063 -0.045 -0.072 -0.056  0.035  0.132  0.165  0.194
+
+$UK.adjusted.noE.CES.kl
+
+Autocorrelations of series 'resid(model)', by lag
+
+     0      1      2      3      4      5      6      7      8      9 
+ 1.000  0.615  0.186  0.039  0.032 -0.010 -0.146 -0.237 -0.207 -0.172 
+    10     11     12     13     14     15     16     17 
+-0.122 -0.085 -0.096 -0.048  0.003  0.067  0.067  0.085
+
+$UK.adjusted.withE.CD
+
+Autocorrelations of series 'resid(model)', by lag
+
+     0      1      2      3      4      5      6      7      8      9 
+ 1.000  0.604  0.196  0.023  0.025 -0.023 -0.162 -0.258 -0.222 -0.182 
+    10     11     12     13     14     15     16     17 
+-0.084 -0.063 -0.077 -0.056 -0.055 -0.031  0.011  0.023
+
+$UK.adjusted.withE.CES.kle
+
+Autocorrelations of series 'resid(model)', by lag
+
+     0      1      2      3      4      5      6      7      8      9 
+ 1.000  0.453  0.039 -0.098 -0.030 -0.034 -0.212 -0.332 -0.243 -0.142 
+    10     11     12     13     14     15     16     17 
+-0.053  0.008 -0.022  0.071  0.130  0.161  0.007 -0.086
+
+$UK.adjusted.withE.CES.lek
+
+Autocorrelations of series 'resid(model)', by lag
+
+     0      1      2      3      4      5      6      7      8      9 
+ 1.000  0.562  0.151  0.006  0.023 -0.021 -0.189 -0.288 -0.243 -0.236 
+    10     11     12     13     14     15     16     17 
+-0.138 -0.093 -0.094 -0.039 -0.025  0.007  0.052  0.068
+
+$UK.adjusted.withE.CES.ekl
+
+Autocorrelations of series 'resid(model)', by lag
+
+     0      1      2      3      4      5      6      7      8      9 
+ 1.000  0.500  0.067 -0.062 -0.024 -0.039 -0.255 -0.376 -0.316 -0.289 
+    10     11     12     13     14     15     16     17 
+-0.169 -0.080 -0.093 -0.006  0.061  0.136  0.182  0.188 
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
 
@@
 
-<<stat_details_table, results="asis">>=
-texreg(list(models$PT$adjusted$withE$CES$kle, models$UK$adjusted$withE$CES$kle), 
-       dcolumn = TRUE, 
-       booktabs = TRUE, 
-       use.packages = FALSE, 
-       label=paste0("tab:", opts_current$get("label")), 
-       caption = "Example output from \\texttt{texreg}.",
-       caption.above = TRUE, 
-       digits = 6,
-       fontsize = "tiny",
-       float.pos = "hb")
-@
+\begin{table}[hb]
+\caption{Example output from \texttt{texreg}.}
+\begin{center}
+\begin{tiny}
+\begin{tabular}{l D{.}{.}{4.9}@{} D{.}{.}{4.9}@{} }
+\toprule
+           & \multicolumn{1}{c}{Model 1} & \multicolumn{1}{c}{Model 2} \\
+\midrule
+gamma      & 1.027582^{***} & 0.980315^{***} \\
+           & (0.011759)     & (0.012946)     \\
+lambda     & 0.004508^{***} & 0.007103^{***} \\
+           & (0.001169)     & (0.001737)     \\
+delta\_1   & 1.000000^{***} & 0.502875^{***} \\
+           & (0.000000)     & (0.036155)     \\
+delta      & 0.902835^{***} & 0.848488       \\
+           & (0.161689)     & (0.661918)     \\
+rho\_1     & 54.581844      & 0.634472^{***} \\
+           & (119.786669)   & (0.138784)     \\
+rho        & -1.000000      & 68.650078      \\
+           & (6.852668)     & (115.484907)   \\
+\midrule
+R$^2$      & 0.997138       & 0.997823       \\
+Num.\ obs. & 50             & 51             \\
+\bottomrule
+\multicolumn{3}{l}{\tiny{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+\end{tabular}
+\end{tiny}
+\label{tab:stat_details_table}
+\end{center}
+\end{table}
 
@@
 % However, the absolute value of \texttt{lambda} decreases from 
-% \Sexpr{naturalCoef(models$PT$unadjusted$noE$CD)$lambda} to 
-% \Sexpr{naturalCoef(models$PT$unadjusted$withE$CD)$lambda}
+% naturalCoef(models$PT$unadjusted$noE$CD)$lambda to 
+% naturalCoef(models$PT$unadjusted$withE$CD)$lambda
 % when adding energy.
@@
 % Using quality-adjusted inputs, the Solow residual (\texttt{lambda}) moves from 
-% \Sexpr{naturalCoef(models$PT$adjusted$noE$CD)$lambda} to
-% \Sexpr{naturalCoef(models$PT$adjusted$withE$CD)$lambda} when including energy.
+% naturalCoef(models$PT$adjusted$noE$CD)$lambda to
+% naturalCoef(models$PT$adjusted$withE$CD)$lambda when including energy.
 % The absolute value of the Solow residual again decreases when adding energy.
@@
 %       \midrule
-%       Without energy  & \Sexpr{naturalCoef(models$PT$unadjusted$noE$CD)$lambda}    & \Sexpr{naturalCoef(models$PT$adjusted$noE$CD)$lambda} \\
-%       With energy     & \Sexpr{naturalCoef(models$PT$unadjusted$withE$CD)$lambda}  & \Sexpr{naturalCoef(models$PT$adjusted$withE$CD)$lambda} \\
+%       Without energy  & naturalCoef(models$PT$unadjusted$noE$CD)$lambda    & naturalCoef(models$PT$adjusted$noE$CD)$lambda \\
+%       With energy     & naturalCoef(models$PT$unadjusted$withE$CD)$lambda  & naturalCoef(models$PT$adjusted$withE$CD)$lambda \\
 %       \bottomrule
@@
 %       \midrule
-%       Without energy  & \Sexpr{naturalCoef(models$UK$unadjusted$noE$CD)$lambda}   
-%                                                 & \Sexpr{naturalCoef(models$UK$adjusted$noE$CD)$lambda} \\
-%       With energy     & \Sexpr{naturalCoef(models$UK$unadjusted$withE$CD)$lambda} 
-%                                                 & \Sexpr{naturalCoef(models$UK$adjusted$withE$CD)$lambda} \\
+%       Without energy  & naturalCoef(models$UK$unadjusted$noE$CD)$lambda   
+%                                                 & naturalCoef(models$UK$adjusted$noE$CD)$lambda \\
+%       With energy     & naturalCoef(models$UK$unadjusted$withE$CD)$lambda 
+%                                                 & naturalCoef(models$UK$adjusted$withE$CD)$lambda \\
 %       \bottomrule
@@
 % For the UK, the quality-adjusted, with energy Solow residual is 
-% \Sexpr{naturalCoef(models$UK$adjusted$withE$CD)$lambda * 100}\%,
+% naturalCoef(models$UK$adjusted$withE$CD)$lambda * 100\%,
 % a very small number indeed.
@@
 % are required to effectively eliminate the Solow residual,
-% reducing it to \Sexpr{naturalCoef(models$UK$adjusted$withE$CD)$lambda}.
+% reducing it to naturalCoef(models$UK$adjusted$withE$CD)$lambda.
 % 
 % Adding energy alone actually \emph{in}creases the Solow residual from 
-% \Sexpr{naturalCoef(models$UK$unadjusted$noE$CD)$lambda} to
-% \Sexpr{naturalCoef(models$UK$unadjusted$withE$CD)$lambda}.
+% naturalCoef(models$UK$unadjusted$noE$CD)$lambda to
+% naturalCoef(models$UK$unadjusted$withE$CD)$lambda.
 % The details for each model with unadjusted factors of production are shown below.
@@
 % as \texttt{alpha\_1} moves from 
-% \Sexpr{naturalCoef(models$UK$unadjusted$noE$CD)$alpha_1} to
-% \Sexpr{naturalCoef(models$UK$unadjusted$withE$CD)$alpha_1}.
+% naturalCoef(models$UK$unadjusted$noE$CD)$alpha_1 to
+% naturalCoef(models$UK$unadjusted$withE$CD)$alpha_1.
 % 
@@
 % \texttt{alpha\_1} moves from 
-% \Sexpr{naturalCoef(models$UK$adjusted$noE$CD)$alpha_1} to
-% \Sexpr{naturalCoef(models$UK$adjusted$withE$CD)$alpha_1}.
+% naturalCoef(models$UK$adjusted$noE$CD)$alpha_1 to
+% naturalCoef(models$UK$adjusted$withE$CD)$alpha_1.
 % 
@@
 % Both unadjusted and quality-adjusted variables give positive Solow residuals,
-% \Sexpr{naturalCoef(models$PT$unadjusted$noE$CES$kl)$lambda} for unadjusted inputs and
-% \Sexpr{naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda} for quality-adjusted inputs.
+% naturalCoef(models$PT$unadjusted$noE$CES$kl)$lambda for unadjusted inputs and
+% naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda for quality-adjusted inputs.
 % Furthermore, quality-adjustment reduces the magnitude of the Solow residual.
@@
 %       \midrule
-%       Without energy  & \Sexpr{naturalCoef(models$PT$unadjusted$noE$CES$kl)$lambda} 
-%                                                             & \Sexpr{naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda} \\
-%       With energy     & \Sexpr{naturalCoef(models$PT$unadjusted$withE$CES$kle)$lambda} 
-%                                                             & \Sexpr{naturalCoef(models$PT$adjusted$withE$CES$kle)$lambda} \\
+%       Without energy  & naturalCoef(models$PT$unadjusted$noE$CES$kl)$lambda 
+%                                                             & naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda \\
+%       With energy     & naturalCoef(models$PT$unadjusted$withE$CES$kle)$lambda 
+%                                                             & naturalCoef(models$PT$adjusted$withE$CES$kle)$lambda \\
 %       \bottomrule
@@
 %       \midrule
-%       Without energy  & \Sexpr{EconModels:::sse(models$PT$unadjusted$noE$CES$kl)$sse} 
-%                                                             & \Sexpr{EconModels:::sse(models$PT$adjusted$noE$CES$kl)$sse} \\
-%       With energy     & \Sexpr{EconModels:::sse(models$PT$unadjusted$withE$CES$kle)$sse} 
-%                                                             & \Sexpr{EconModels:::sse(models$PT$adjusted$withE$CES$kle)$sse} \\
+%       Without energy  & EconModels:::sse(models$PT$unadjusted$noE$CES$kl)$sse 
+%                                                             & EconModels:::sse(models$PT$adjusted$noE$CES$kl)$sse \\
+%       With energy     & EconModels:::sse(models$PT$unadjusted$withE$CES$kle)$sse 
+%                                                             & EconModels:::sse(models$PT$adjusted$withE$CES$kle)$sse \\
 %       \bottomrule
@@
 %       \midrule
-%       Without energy  & \Sexpr{naturalCoef(models$PT$unadjusted$noE$CES$kl)$lambda} 
-%                                         & \Sexpr{naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda} \\
-%       With energy     & \Sexpr{naturalCoef(models$PT$unadjusted$withE$CES$lek)$lambda} 
-%                                         & \Sexpr{naturalCoef(models$PT$adjusted$withE$CES$lek)$lambda} \\
+%       Without energy  & naturalCoef(models$PT$unadjusted$noE$CES$kl)$lambda 
+%                                         & naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda \\
+%       With energy     & naturalCoef(models$PT$unadjusted$withE$CES$lek)$lambda 
+%                                         & naturalCoef(models$PT$adjusted$withE$CES$lek)$lambda \\
 %       \bottomrule
@@
 %       \midrule
-%       Without energy  & \Sexpr{EconModels:::sse(models$PT$unadjusted$noE$CES$kl)$sse} 
-%                                         & \Sexpr{EconModels:::sse(models$PT$adjusted$noE$CES$kl)$sse} \\
-%       With energy     & \Sexpr{EconModels:::sse(models$PT$unadjusted$withE$CES$lek)$sse} 
-%                                         & \Sexpr{EconModels:::sse(models$PT$adjusted$withE$CES$lek)$sse} \\
+%       Without energy  & EconModels:::sse(models$PT$unadjusted$noE$CES$kl)$sse 
+%                                         & EconModels:::sse(models$PT$adjusted$noE$CES$kl)$sse \\
+%       With energy     & EconModels:::sse(models$PT$unadjusted$withE$CES$lek)$sse 
+%                                         & EconModels:::sse(models$PT$adjusted$withE$CES$lek)$sse \\
 %       \bottomrule
@@
 % creating a slight increase from 
-% \Sexpr{naturalCoef(models$PT$unadjusted$withE$CES$lek)$lambda} to
-% \Sexpr{naturalCoef(models$PT$adjusted$withE$CES$lek)$lambda}.
+% naturalCoef(models$PT$unadjusted$withE$CES$lek)$lambda to
+% naturalCoef(models$PT$adjusted$withE$CES$lek)$lambda.
 % 
@@
 %       \midrule
-%       Without energy  & \Sexpr{naturalCoef(models$PT$unadjusted$noE$CES$kl)$lambda} 
-%                                         & \Sexpr{naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda} \\
-%       With energy     & \Sexpr{naturalCoef(models$PT$unadjusted$withE$CES$ekl)$lambda} 
-%                                         & \Sexpr{naturalCoef(models$PT$adjusted$withE$CES$ekl)$lambda} \\
+%       Without energy  & naturalCoef(models$PT$unadjusted$noE$CES$kl)$lambda 
+%                                         & naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda \\
+%       With energy     & naturalCoef(models$PT$unadjusted$withE$CES$ekl)$lambda 
+%                                         & naturalCoef(models$PT$adjusted$withE$CES$ekl)$lambda \\
 %       \bottomrule
@@
 %       \midrule
-%       Without energy  & \Sexpr{EconModels:::sse(models$PT$unadjusted$noE$CES$kl)$sse} 
-%                                         & \Sexpr{EconModels:::sse(models$PT$adjusted$noE$CES$kl)$sse} \\
-%       With energy     & \Sexpr{EconModels:::sse(models$PT$unadjusted$withE$CES$ekl)$sse} 
-%                                         & \Sexpr{EconModels:::sse(models$PT$adjusted$withE$CES$ekl)$sse} \\
+%       Without energy  & EconModels:::sse(models$PT$unadjusted$noE$CES$kl)$sse 
+%                                         & EconModels:::sse(models$PT$adjusted$noE$CES$kl)$sse \\
+%       With energy     & EconModels:::sse(models$PT$unadjusted$withE$CES$ekl)$sse 
+%                                         & EconModels:::sse(models$PT$adjusted$withE$CES$ekl)$sse \\
 %       \bottomrule
@@
 % Adding energy decreases the Solow residual 
-% (from \Sexpr{naturalCoef(models$PT$unadjusted$withE$CES$ekl)$lambda} to 
-% \Sexpr{naturalCoef(models$PT$adjusted$withE$CES$ekl)$lambda})
+% (from naturalCoef(models$PT$unadjusted$withE$CES$ekl)$lambda to 
+% naturalCoef(models$PT$adjusted$withE$CES$ekl)$lambda)
 % when enegy is included in the model.
 % But, adding energy slightly increases the Solow residual
-% (from \Sexpr{naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda} to \Sexpr{naturalCoef(models$PT$adjusted$withE$CES$ekl)$lambda})
+% (from naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda to naturalCoef(models$PT$adjusted$withE$CES$ekl)$lambda)
 % when quality-adjusted inputs are used.
@@
 % Both unadjusted and quality-adjusted variables give positive Solow residuals for the UK,
-% \Sexpr{naturalCoef(models$UK$unadjusted$noE$CES$kl)$lambda} for unadjusted inputs and
-% \Sexpr{naturalCoef(models$UK$adjusted$noE$CES$kl)$lambda} for quality-adjusted inputs.
+% naturalCoef(models$UK$unadjusted$noE$CES$kl)$lambda for unadjusted inputs and
+% naturalCoef(models$UK$adjusted$noE$CES$kl)$lambda for quality-adjusted inputs.
 % Furthermore, quality-adjustment reduces the magnitude of the UK Solow residual.
@@
 %       \midrule
-%       Without energy  & \Sexpr{naturalCoef(models$UK$unadjusted$noE$CES$kl)$lambda} & \Sexpr{naturalCoef(models$UK$adjusted$noE$CES$kl)$lambda} \\
-%       With energy     & \Sexpr{naturalCoef(models$UK$unadjusted$withE$CES$kle)$lambda} 
-%                                                                 & \Sexpr{naturalCoef(models$UK$adjusted$withE$CES$kle)$lambda} \\
+%       Without energy  & naturalCoef(models$UK$unadjusted$noE$CES$kl)$lambda & naturalCoef(models$UK$adjusted$noE$CES$kl)$lambda \\
+%       With energy     & naturalCoef(models$UK$unadjusted$withE$CES$kle)$lambda 
+%                                                                 & naturalCoef(models$UK$adjusted$withE$CES$kle)$lambda \\
 %       \bottomrule
@@
 %       \midrule
-%       Without energy  & \Sexpr{EconModels:::sse(models$UK$unadjusted$noE$CES$kl)$sse} & \Sexpr{EconModels:::sse(models$UK$adjusted$noE$CES$kl)$sse} \\
-%       With energy     & \Sexpr{EconModels:::sse(models$UK$unadjusted$withE$CES$kle)$sse} 
-%                                                             & \Sexpr{EconModels:::sse(models$UK$adjusted$withE$CES$kle)$sse} \\
+%       Without energy  & EconModels:::sse(models$UK$unadjusted$noE$CES$kl)$sse & EconModels:::sse(models$UK$adjusted$noE$CES$kl)$sse \\
+%       With energy     & EconModels:::sse(models$UK$unadjusted$withE$CES$kle)$sse 
+%                                                             & EconModels:::sse(models$UK$adjusted$withE$CES$kle)$sse \\
 %       \bottomrule
@@
 %       \midrule
-%       Without energy  & \Sexpr{naturalCoef(models$UK$unadjusted$noE$CES$kl)$lambda} & \Sexpr{naturalCoef(models$UK$adjusted$noE$CES$kl)$lambda} \\
-%       With energy     & \Sexpr{naturalCoef(models$UK$unadjusted$withE$CES$lek)$lambda} 
-%                                                             & \Sexpr{naturalCoef(models$UK$adjusted$withE$CES$lek)$lambda} \\
+%       Without energy  & naturalCoef(models$UK$unadjusted$noE$CES$kl)$lambda & naturalCoef(models$UK$adjusted$noE$CES$kl)$lambda \\
+%       With energy     & naturalCoef(models$UK$unadjusted$withE$CES$lek)$lambda 
+%                                                             & naturalCoef(models$UK$adjusted$withE$CES$lek)$lambda \\
 %       \bottomrule
@@
 %       \midrule
-%       Without energy  & \Sexpr{EconModels:::sse(models$UK$unadjusted$noE$CES$kl)$sse} & \Sexpr{EconModels:::sse(models$UK$adjusted$noE$CES$kl)$sse} \\
-%       With energy     & \Sexpr{EconModels:::sse(models$UK$unadjusted$withE$CES$lek)$sse} 
-%                                                             & \Sexpr{EconModels:::sse(models$UK$adjusted$withE$CES$lek)$sse} \\
+%       Without energy  & EconModels:::sse(models$UK$unadjusted$noE$CES$kl)$sse & EconModels:::sse(models$UK$adjusted$noE$CES$kl)$sse \\
+%       With energy     & EconModels:::sse(models$UK$unadjusted$withE$CES$lek)$sse 
+%                                                             & EconModels:::sse(models$UK$adjusted$withE$CES$lek)$sse \\
 %       \bottomrule
@@
 %       \midrule
-%       Without energy  & \Sexpr{naturalCoef(models$UK$unadjusted$noE$CES$kl)$lambda} & \Sexpr{naturalCoef(models$UK$adjusted$noE$CES$kl)$lambda} \\
-%       With energy     & \Sexpr{naturalCoef(models$UK$unadjusted$withE$CES$ekl)$lambda} 
-%                                                             & \Sexpr{naturalCoef(models$UK$adjusted$withE$CES$ekl)$lambda} \\
+%       Without energy  & naturalCoef(models$UK$unadjusted$noE$CES$kl)$lambda & naturalCoef(models$UK$adjusted$noE$CES$kl)$lambda \\
+%       With energy     & naturalCoef(models$UK$unadjusted$withE$CES$ekl)$lambda 
+%                                                             & naturalCoef(models$UK$adjusted$withE$CES$ekl)$lambda \\
 %       \bottomrule
@@
 %       \midrule
-%       Without energy  & \Sexpr{EconModels:::sse(models$UK$unadjusted$noE$CES$kl)$sse} & \Sexpr{EconModels:::sse(models$UK$adjusted$noE$CES$kl)$sse} \\
-%       With energy     & \Sexpr{EconModels:::sse(models$UK$unadjusted$withE$CES$ekl)$sse} 
-%                                                             & \Sexpr{EconModels:::sse(models$UK$adjusted$withE$CES$ekl)$sse} \\
+%       Without energy  & EconModels:::sse(models$UK$unadjusted$noE$CES$kl)$sse & EconModels:::sse(models$UK$adjusted$noE$CES$kl)$sse \\
+%       With energy     & EconModels:::sse(models$UK$unadjusted$withE$CES$ekl)$sse 
+%                                                             & EconModels:::sse(models$UK$adjusted$withE$CES$ekl)$sse \\
 %       \bottomrule
@@
 %' with the timespan for finite differences ($t_j - t_i$) set to 
-%' \Sexpr{lag.to.use}~\Sexpr{if (lag.to.use == 1) "year" else "years"}.
+%' lag.to.use~if (lag.to.use == 1) "year" else "years".
 %' %

### 2015-07-08 Articles/Bonepile/Article_EcolEcon_2014/Paper2.Rnw
Rearranging the articles.

--- 2015-04-22 Articles/Article_EcolEcon_2014/Paper2.Rnw
@@
 
-<<CD_finite_diff_calcs, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap='Solow residual time series.'>>=
+<<CD_finite_diff_calcs>>=
 # Add a bogus "none" column that we can use for the no-energy case

### 2015-07-08 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Version of the file at ESEE2015 presentation.

--- 2015-07-07 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
@@
 \usepackage{booktabs}   % for beautiful tables
-\usepackage{dcolumn}    % aligns table columns at decimal places
 
@@
 require(knitr)
-require(texreg)
 
@@
 \begin{equation} \label{eq:CD}
-  y = \theta A k^{\alpha_1} l^{\alpha_2} \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)} \; ,
+  y = \theta A k^\alpha l^\beta \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)} \; ,
 \end{equation}
@@
   Model parameters are represented by Greek letters
-  ($\alpha_1$, $\alpha_2$, $\lambda$, $\theta$).
+  ($\alpha$, $\beta$, $\lambda$, $\theta$).
   }
 Constant returns to scale are represented by the constraint
-$\alpha_1 + \alpha_2 = 1$.
+$\alpha + \beta = 1$.
 
@@
 \begin{equation} \label{eq:CDe}
-  y = \theta A k^{\alpha_1} l^{\alpha_2} e^{\alpha_3} \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)} \; ,
+  y = \theta A k^\alpha l^\beta e^\gamma \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)} \; ,
 \end{equation}
@@
 is often assumed to have constant returns to scale for the three factors 
-of production: $\alpha_1 + \alpha_2 + \alpha_3 = 1$.
+of production: $\alpha + \beta + \gamma = 1$.
 The term $A$ is known as total factor productivity,
@@
 $\alpha_1 = \delta \delta_1$, $\alpha_2 = \delta(1 - \delta_1)$, and $\alpha_3 = 1 - \delta$
-for the CES model with three factors of production and the ($kl$)$e$ nesting.
+for the CES model with three factors of production.
 The values of $\alpha_1$, $\alpha_2$, and $\alpha_3$ are interpreted as
-factor shares for capital, labor, and energy, respectively,
+$\alpha$, $\beta$, and $\gamma$ (coefficients for capital, labor, and energy, respectively)
 as shown in Table \ref{tab:CES_abg_equations}, 
@@
 
-\begin{table} \caption{Equations for $\alpha_1$, $\alpha_2$, and $\alpha_3$ 
-                        (factor shares for capital, labor, and energy, respectively)
+\begin{table} \caption{Equations for $\alpha$, $\beta$, and $\gamma$ 
+                        (importance of capital, labor, and energy, respectively)
                         for the various CES nestings, 
@@
       \toprule
-      Nesting         & \texttt{nest}     & $\alpha_1$              & $\alpha_2$              & $\alpha_3$       \\
+      Nesting         & \texttt{nest}     & $\alpha$                & $\beta$                 & $\gamma$       \\
       \midrule
@@
 fileNameCST <- "EESE2015ModelsCST.rds"
-fileNameExp <- "EESE2015ModelsExp.rds"
 if (!rerunModels){
@@
   modelsCST <- readRDS(fileNameCST)
-  modelsExp <- readRDS(fileNameExp)
 } else {
@@
   # In RStudio, be sure to set the working directory to the source file directory.
-
-  #
-  # Models that are exponential only
-  #
-  modelsExp <- list()
-  alphaExp <- 0
-  betaExp <- 0
-  gammaExp <- 0
-  for (country in countries){
-    # Replace with better code later. 
-    # Would like to say cdModel(formula, data, factorShares=c(alpha_1 = 0, alpha_2 = 0, alpha_3 = 0))
-    # or something like that.
-    form <- keep_summands(formulas[[country]][["unadjusted"]], n = c(-1, -2, -3)) # Remove energy
-    yVar <- as.name(summands(form, n=1, right=FALSE))
-    tVar <- as.name(summands(form, n=1))
-    data <- historicalData[[country]]
-    expMod <- lm(log(eval(yVar)) ~ eval(tVar), data=data)
-    attr(expMod, "naturalCoeffs") <- data.frame(lambda=coef(expMod)[[2]],
-                                                  logscale=coef(expMod)[[1]], 
-                                                  scale=exp(coef(expMod)[[1]]),
-                                                  alpha_1=alphaExp,
-                                                  alpha_2=betaExp, 
-                                                  alpha_3=gammaExp)
-    expMod$formula <- form
-    sdata <- subset(data, select=all.vars(form))
-    sdata <- data[complete.cases(sdata), unique(c(all.vars(form), names(data)))]
-    expMod$data <- sdata
-    expMod$response <- sdata$iGDP 
-    modelsExp[[country]] <- expMod
-  }
-  # Save exponential theorem models to disk.
-  saveRDS(modelsExp, file=fileNameExp)
 
@@
     # Replace with better code later. 
-    # Would like to say cdModel(formula, data, factorShares=c(alpha_1 = 0.3, alpha_2 = 0.7, alpha_3 = 0))
+    # Would like to say cdMod(formula, data, fittingParams=c(alpha_1 = 0.3, alpha_2 = 0.7, alpha_3 = 0))
     # or something like that.
@@
 }
-# Put all exponential model coefficients into a data frame
-AllCoeffsExp <- leaf_apply(modelsExp, class = c("lm"), f = function(modExp, id){
-  # Parse the id to find details of this model
-  id_list <- strsplit(id, split = "[.]")[[1]]
-  res <- rbind(list(Country = id_list[[1]], 
-                    flavor = NA,
-                    energy = NA, 
-                    model = "exp", 
-                    nest = NA,
-                    cst = FALSE))
-  res <- cbind(res, naturalCoef(modExp))
-  # Now caluculate mean squared error (mse) for each model.
-  sqResids <- resid(modExp)^2
-  mse <- sum(sqResids) / (length(sqResids))
-  res <- cbind(res, list(mse=mse))
-  return(res)
-}) %>% do.call(plyr::rbind.fill, .)
-
-# Put all the cost-share theorem (CST) model coefficients into a data frame
+# Put all the cost-share theorem (CST) coefficients into a data frame
 AllCoeffsCST <- leaf_apply(modelsCST, class = c("lm"), f = function(modCST, id){
@@
          digits=6)
-@
-
-%++++++++++++++++++++++++++++++
-\subsection{What trends exist in factors shares?} 
-\label{sec:factor_shares}
-%++++++++++++++++++++++++++++++
-
-Figures~\ref{fig:Factor_shares_graph_PT} and~\ref{fig:Factor_shares_graph_UK}
-show factor shares ($\alpha$ values) for CES models for
-Portugal and the UK, respectively.
-See Table~\ref{tab:CES_abg_equations} for details.
-
-<<Factor_shares_bar_graph_function>>=
-fsbg <- function(coun, mod){
-  bar_chart_data <- filter(AllCoeffs, Country==coun & model==mod) %>% 
-    select(Country, model, flavor, energy, nest, cst, alpha_1, alpha_2, alpha_3)
-  # Change boolean cst column to meaningful words
-  bar_chart_data$cst <- plyr::mapvalues(bar_chart_data$cst, from=c(TRUE, FALSE), to=c("Adhere to CST", "Reject CST"))
-  # Change nest to a nicer-looking nest string
-  bar_chart_data$nest <- plyr::mapvalues(bar_chart_data$nest, 
-                                         from=c("kl", "kle", "lek", "ekl"), 
-                                         to=c("(kl)", "(kl)e", "(le)k", "(ek)l"))
-  # Add a label column
-  bar_chart_data$label <- paste(bar_chart_data$cst, bar_chart_data$flavor, 
-                                bar_chart_data$energy, bar_chart_data$nest, sep=", ")
-  # Capture the order that we want for the models on the vertical axis.
-  order <- bar_chart_data$label
-  # Now melt the data
-  bar_chart_data <- melt(bar_chart_data, 
-                         measure.vars = c("alpha_1", "alpha_2", "alpha_3"), 
-                         value.name = "value", 
-                         variable.name = "variable")
-  # Define the color palette (see http://www.cookbook-r.com/Graphs/Colors_(ggplot2))
-  cbPalette <- c("#E69F00", "#999999", "#F0E442", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")
-  # Make the plot
-  plot <- ggplot(bar_chart_data, mapping=aes(x=label, y=value, fill=variable, width=0.4)) + 
-    geom_bar(stat="identity") + 
-    xlab("") +
-    scale_x_discrete(limits=rev(order)) +
-    ylab("") +
-    scale_y_continuous(breaks=c(0, 0.5, 1)) + 
-    guides(fill=guide_legend(title=NULL)) +
-    coord_flip() + 
-    scale_fill_brewer(palette="OrRd") +
-    xy_theme() +
-    theme(axis.ticks.y = element_blank())
-  return(plot)
-}
-@
-
-<<Factor_shares_graph_PT, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=2.5, fig.cap="Factor shares ($\\alpha$ values) for CES models for Portugal.">>=
-fsbg(coun = "PT", mod = "CES")
-@
-
-<<Factor_shares_graph_UK, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=2.5, fig.cap="Factor shares ($\\alpha$ values) for CES models for the UK.">>=
-fsbg(coun = "UK", mod = "CES")
 @
@@
 Perhaps there is another direction in which I should go with this analysis?
-
-%++++++++++++++++++++++++++++++
-\section{Correlograms} 
-\label{sec:correlograms}
-%++++++++++++++++++++++++++++++
-
-This appendix contains correlograms for all models.
-
-%++++++++++++++++++++++++++++++
-\subsection{Correlograms for models respecting the cost-share theorem} 
-\label{sec:correlograms_CST}
-%++++++++++++++++++++++++++++++
-
-In this section we present correlograms for all models that respect the cost-share theorem.
-
-<<Correlograms_CST, echo=FALSE, message=FALSE>>=
-leaf_apply(l = modelsCST, class = c("lm", "plm"), f = function(model, name){
-  acf(resid(model), main=name)
-})
-@
-
-%++++++++++++++++++++++++++++++
-\subsection{Correlograms for models reject the cost-share theorem} 
-\label{sec:correlograms_noCST}
-%++++++++++++++++++++++++++++++
-
-In this section we present correlograms for all models that do not adhere to the cost-share theorem.
-
-<<Correlograms_noCST, echo=FALSE, message=FALSE>>=
-leaf_apply(l = models, class = c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, name){
-  acf(resid(model), main=name)
-})
-@
-
-%++++++++++++++++++++++++++++++
-\section{Statistical details on all models} 
-\label{sec:staistical_details}
-%++++++++++++++++++++++++++++++
-
-In this section, we present statistical details of all models.
-
-At the moment, this is a simple example of two models.
-I hope to develop a table later, after I figure out some things.
-Both models are CES models with energy fitted to Quality-adjusted data using the ($kl$)($e$) nesting.
-In Table~\ref{tab:stat_details_table}, Model 1 is for Portugal, and Model 2 is for the UK.
-
-<<stat_details_table, results="asis">>=
-texreg(list(models$PT$adjusted$withE$CES$kle, models$UK$adjusted$withE$CES$kle), 
-       dcolumn = TRUE, 
-       booktabs = TRUE, 
-       use.packages = FALSE, 
-       label=paste0("tab:", opts_current$get("label")), 
-       caption = "Example output from \\texttt{texreg}.",
-       caption.above = TRUE, 
-       digits = 6,
-       fontsize = "tiny",
-       float.pos = "hb")
-@
 

### 2015-07-08 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Redoing model names.

@@
 <<Models>>=
-fileName <- "ESEE2015Models.rds"
-fileNameCST <- "EESE2015ModelsCST.rds"
-fileNameExp <- "EESE2015ModelsExp.rds"
+fileNameCDCES <- "EcolEcon2015ModelsCDCES.rds"
+fileNameCST <- "EcolEcon2015ModelsCST.rds"
+fileNameExp <- "EcolEcon2015ModelsExp.rds"
 if (!rerunModels){
   # load from the file on disk
-  models <- readRDS(fileName)
+  models <- readRDS(fileNameCDCES)
   modelsCST <- readRDS(fileNameCST)

### 2015-07-08 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Rearranging text into paper order.

@@
 # ********************************************************
-rerunModels=TRUE
+rerunModels=FALSE
 # ********************************************************
@@
 %------------------------------
-\subsubsection{Exponential Production Function} 
+\subsubsection{Exponential Production Function (reference model)} 
 \label{sec:exp}
@@
 The reference model is a degenerate case of the Cobb-Douglas production function
-wherein all factor shares are zero~($\alpha_1 = \alpha_2 = \alpha_3 = 0$)
-and the constant returns to scale constraint is not respected.
+wherein the constant returns to scale constraint is not respected,
+because all factor shares are zero~($\alpha_1 = \alpha_2 = \alpha_3 = 0$).
 
@@
 the Cobb-Douglas and CES models, because no factors of production are
-included in the reference model to drive growth.
+included in the reference model to drive economic growth.
 Indeed, in the reference model, 
-all growth is attributed to the Solow residual.
+all economics growth is attributed to the Solow residual.
 
@@
   # Save models to disk.
-  saveRDS(models, file=fileName)
+  saveRDS(models, file=fileNameCDCES)
 }
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
-\label{sec:results}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 %++++++++++++++++++++++++++++++
@@
 Both historical GDP and fitted GDP are shown in 
-Figures~\ref{fig:Graphs CD-fitted}--\ref{fig:Graphs CESekl-fitted}.
-%
-<<Graphs CD-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Cobb-Douglas models that reject the cost-share theorem. Solid line is historical GDP.">>=
-fittedGraphNoCST(filter(fitted_and_resid_data, model=="CD" & cst=="Reject CST"))
-@
+Figures~\ref{fig:Graphs CESkle-fitted}--\ref{fig:Graphs CESekl-fitted}.
 %
@@
 
-Figures~\ref{fig:Graphs CD-resid}--\ref{fig:Graphs CESekl-resid}
-show fitting residuals for all models.
-%
-<<Graphs CD-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for Cobb-Douglas models.">>=
-residualPlot(filter(fitted_and_resid_data, model=="CD" & cst=="Reject CST"))
-@
+Figures~\ref{fig:Graphs CESkle-resid}--\ref{fig:Graphs CESekl-resid}
+show fitting residuals for all CES models.
 %
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Analysis}
-\label{sec:analysis}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-For now, I've organized the analysis around questions that we would like to answer.
-
-%++++++++++++++++++++++++++++++
-\subsection{Does rejecting the cost-share theorem 
-            decrease the mean squared error and/or the Solow residual?} 
-\label{sec:cst_and_solow_residual}
-%++++++++++++++++++++++++++++++
-
-Our hypothesis is that rejecting the cost-share theorem~(CST) will decrease
-both mean squared error~($mse$) and
-the Solow residual~($\lambda$).
-The mean squared error~($mse$) is expected to decrease 
-because rejecting the CST adds one or more fitting parameters
-to the model.
-The Solow residual~($\lambda$) is expected to decrease 
-because the factor shares for capital~($\alpha_1$) and labor~($\alpha_2 = 1 - \alpha_1$)
-are free to float, 
-allowing each factor of production 
-to contribute optimally toward production and
-bringing the model's prediction for economic output closer to 
-historical output. 
-In so doing, we expect less ``unexplained'' economic growth 
-and a decreased Solow residual~($\lambda$).
-
-Table~\ref{tab:Effect_of_CST_CD} shows the effect of the CST 
-on fitted parameters for the Cobb-Douglas model and the exponential-only model.
-The Cobb-Douglas models show lower $mse$ than the exponential-only models.
-The Cobb-Douglas models also reduce solow residual ($\lambda$) relative
-to the exponential-only case.
-%
-<<Effect_of_CST_CD, results="asis">>=
-myXTable(filter(AllCoeffs, (model=="CD" & flavor=="Unadjusted" & energy=="Without energy") | model=="exp") %>% 
-           select(Country, model, cst, scale, lambda, alpha_1, alpha_2, mse),
-         caption="Model parameters for Cobb-Douglas models with unadjusted factors of production, without energy.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-%
-Table~\ref{tab:Effect_of_CST_CES} shows the effect of the CST 
-on fitted parameters for the CES model.
-The CES models show lower $mse$ than the exponential-only models.
-The CES models also reduce solow residual ($\lambda$) relative
-to the exponential-only case.
-%
-<<Effect_of_CST_CES, results="asis">>=
-myXTable(filter(AllCoeffs, (model=="CES" & flavor=="Unadjusted" & energy=="Without energy") | model=="exp") %>% 
-           select(Country, model, cst, gamma, lambda, alpha_1, alpha_2, sigma_1, mse),
-         caption="Model parameters for CES models with unadjusted factors of production, without energy.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-%
-Both Cobb-Douglas and CES models do a better job of fitting 
-historical data than an exponential-only model
-as evidenced by decreased $mse$ values.
-Both Cobb-Douglas and CES models exhibit reduced Solow residual~($\lambda$
-compared to the exponential-only model.
-For both Cobb-Douglas and CES, rejecting the Cost Share Theorem yields
-decreased mean squared error~($mse$) and
-smaller Solow residual ($\lambda$, on an absolute-value basis),
-as expected.
-
-***************
-
-Note that in Table~\ref{tab:Effect_of_CST_CES}, we see $\sigma_1 = 0.5$ 
-for UK when the cost share theorem is rejected. 
-This even-numbered result is coming from the grid search in $\rho_1$. 
-For an unknown reason, the gradient search from the best grid search point
-fails.
-I will investigate.
-
-This result means that we have found a set of fitting coefficients
-for this situation 
-that is \emph{close} to providing the minimum possible $mse$,
-but it may not be the \emph{exact} minimum.
-Regardless, the point above (that $mse$ and $\lambda$ always decrease 
-when rejecting the cost share theorem) remains valid.
-Investigating and fixing this problem
-will only serve to \emph{further} reduce $mse$ and $\lambda$ 
-from the values reported in Table~\ref{tab:Effect_of_CST_CES}.
-
-************
-
-%++++++++++++++++++++++++++++++
-\subsection{Does quality-adjusting the factors of production 
-            decrease the mean squared error and/or the Solow residual?} 
-\label{sec:quality_adj_energy_and_solow_residual}
-%++++++++++++++++++++++++++++++
-
-We can test our hypothesis that 
-quality-adjusting the factors of production
-and including energy will both reduce the Solow residuals~($\lambda$)
-and improve the fit to historical data
-(thereby reducing the fitting residuals, $r_i$, and mean squared error, $mse$)
-by calculating 
-$\Delta \lambda$ and $\Delta mse$, where
-%
-\begin{equation} \label{eq:delta_lambda}
-  \Delta \lambda \equiv \left| \lambda \right| - \left| \lambda_{Unadjusted, \, Without \, energy, \, CST} \right|
-\end{equation}
-%
-and
-%
-\begin{equation} \label{eq:delta_mse}
-  \Delta mse \equiv mse - mse_{Unadjusted, \, Without \, energy, \, CST}.
-\end{equation}
-%
-where~$N$ is the number of years of data.
-On a percentage basis,
-%
-\begin{equation} \label{eq:delta_lambda_perc}
-  \Delta \lambda \, [\%] = \frac{100 \, \Delta \lambda}{\left| \lambda_{Unadjusted, \, Without \, energy, \, CST} \right|} 
-            = \frac{100 \, \left| \lambda \right|}{\left| \lambda_{Unadjusted, \, Without \, energy, \, CST} \right|} - 1
-\end{equation}
-%
-When $\Delta \lambda$, $\Delta \lambda \, [\%]$, or $\Delta mse$ are negative, 
-we observe reduction in the Solow residual ($\lambda$) or
-the fitting residuals ($mse$)
-relative to the unadjusted, no-energy, CST case.
-
-To calculate $\Delta \lambda$ and $\Delta mse$, we need to fit all combinations of 
-country, model, flavor, energy, nest, and CST.
-Table~\ref{tab:CD_coeffs} shows coefficients for all fitted Cobb-Douglas models
-and the reference model (exponential-only).
-%
-<<CD_coeffs, results="asis">>=
-myXTable(filter(AllCoeffs, model=="CD" | model=="exp") %>% 
-           select(Country, model, flavor, energy, cst, scale, lambda, alpha_1, alpha_2, alpha_3, mse),
-         caption="Model parameters for all Cobb-Douglas models.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-%
-Tables~\ref{tab:CES_coeffs} and~\ref{tab:CES_coeffs_sigmas} show 
-coefficients for all fitted CES models and the reference model (exponential-only).
-%
-<<CES_coeffs, results="asis">>=
-myXTable(filter(AllCoeffs, model=="CES" | model=="exp") %>% 
-           select(Country, model, flavor, energy, nest, cst, gamma, lambda, alpha_1, alpha_2, alpha_3),
-         caption="Model parameters for all CES models.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-%
-<<CES_coeffs_sigmas, results="asis">>=
-myXTable(filter(AllCoeffs, model=="CES" | model=="exp") %>% 
-           select(Country, model, flavor, energy, nest, cst, sigma_1, sigma, mse),
-         caption="Model parameters for all CES models.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-%
-Table~\ref{tab:DSRmse_CD} shows $\Delta \lambda$ and $\Delta mse$ results for the Cobb-Douglas models.
-%
-<<DSRmse_CD, results="asis">>=
-myXTable(filter(AllCoeffs, model=="CD") %>% select(Country, model, flavor, energy, cst, Dlambda, Dmse),
-         caption="$\\Delta \\lambda$ and $\\Delta mse$ for Cobb-Douglas models.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-% 
-Tables~\ref{tab:DSRmse_CESkle}--\ref{tab:DSRmse_CESekl} show $\Delta \lambda$ and $\Delta mse$ 
-results for CES models with various nestings.
-%
-<<DSRmse_CESkle, results="asis">>=
-myXTable(filter(AllCoeffs, (model=="CES" & (nest=="kl" | nest=="kle")) | model=="exp") %>% 
-           select(Country, model, flavor, energy, nest, cst, Dlambda, Dmse),
-         caption="$\\Delta \\lambda$ and $\\Delta mse$ for CES models with ($kl$)$e$ nesting.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-%
-<<DSRmse_CESlek, results="asis">>=
-myXTable(filter(AllCoeffs, (model=="CES" & (nest=="kl" | nest=="lek")) | model=="exp") %>% 
-           select(Country, model, flavor, energy, nest, cst, Dlambda, Dmse),
-         caption="$\\Delta \\lambda$ and $\\Delta mse$ for CES models with ($le$)$k$ nesting.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-%
-<<DSRmse_CESekl, results="asis">>=
-myXTable(filter(AllCoeffs, (model=="CES" & (nest=="kl" | nest=="ekl")) | model=="exp") %>% 
-           select(Country, model, flavor, energy, nest, cst, Dlambda, Dmse),
-         caption="$\\Delta \\lambda$ and $\\Delta mse$ for CES models with ($ek$)$l$ nesting.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-%
-Figures~\ref{fig:DSRmse_CD_graph} and~\ref{fig:percDSRmse_CD_graph} summarize 
-$\Delta \lambda$ and $\Delta mse$ 
-results for the Cobb-Douglas model.
-%
-<<DSRmse_CD_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta mse$) for the Cobb-Douglas model relative to the exponential-only model.">>=
-ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CD"), mapping=aes(x=Dmse, y=Dlambda, color=energy, size=cst)) +
-  facet_grid(Country ~ flavor) +
-  scale_size_manual(values=c(2,3.5)) +
-  xlab(expression(Delta * mse)) + 
-  scale_x_continuous(breaks=seq(-0.01, 0, 0.005), limits=c(-0.012, 0.003)) +  
-  ylab(expression(Delta * lambda)) +
-  scale_y_continuous(limits=c(-0.04, 0)) +
-  xy_theme() + 
-  theme(legend.title=element_blank())
-@
-%
-<<percDSRmse_CD_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Percentage change in Solow Residuals~($\\Delta\\lambda \\, [\\%]$) and mean squared error~($\\Delta mse \\, [\\%]$) for the Cobb-Douglas model relative to exponential-only models.">>=
-ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CD"), mapping=aes(x=percDmse, y=percDlambda, color=energy, size=cst)) +
-  facet_grid(Country ~ flavor) +
-  scale_size_manual(values=c(2,3.5)) +
-  xlab(expression(paste(Delta * mse, " [%]"))) + 
-  scale_x_continuous(breaks=seq(-50, 50, 50), limits=c(-90, 50)) +  
-  ylab(expression(paste(Delta * lambda, " [%]"))) +
-  scale_y_continuous(breaks=seq(-80, 0, 20), limits=c(-100, 10)) +  
-  xy_theme() + 
-  theme(legend.title=element_blank())
-@
-%
-Figures~\ref{fig:DSRmse_CES_graph} and~\ref{fig:percDSRmse_CES_graph} summarize 
-$\Delta \lambda$ and $\Delta mse$ 
-results for CES models.
-%
-<<DSRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta mse$) for the CES modles relative to the exponential-only model.">>=
-ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=Dmse, y=Dlambda, color=energy, size=cst, shape=nest)) +
-  scale_size_manual(values=c(2,3.5)) +
-  scale_shape_manual(values=c(16,17,18,15)) +
-  facet_grid(Country ~ flavor) +
-  xlab(expression(Delta * mse)) + 
-  scale_x_continuous(breaks=seq(-0.005, 0, 0.005)) +  
-  ylab(expression(Delta * lambda)) +
-  xy_theme() +
-  theme(legend.title=element_blank())
-@
-%
-<<percDSRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Percentage change in Solow Residuals~($\\Delta\\lambda \\, [\\%]$) and mean squared error~($\\Delta mse \\, [\\%]$) for the CES models relative to the exponential-only model.">>=
-ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=percDmse, y=percDlambda, color=energy, size=cst, shape=nest)) +
-  scale_size_manual(values=c(2,3.5)) +
-  scale_shape_manual(values=c(16,17,18,15)) +
-  facet_grid(Country ~ flavor) +
-  xlab(expression(paste(Delta * mse, " [%]"))) + 
-  scale_x_continuous(breaks=seq(-80, 0, 20)) +  
-  ylab(expression(paste(Delta * lambda, " [%]"))) +
-  scale_y_continuous(breaks=seq(-80, 0, 20), limits=c(-100, 10)) +  
-  xy_theme() +
-  theme(legend.title=element_blank())
-@
-
-%++++++++++++++++++++++++++++++
-\subsection{Are the means of the fitting residuals 
-            significantly different from zero?} 
-\label{sec:fitting_residuals_different_from_zero}
-%++++++++++++++++++++++++++++++
-
-The set of fitting residual values~($r_i$)
-for each combination of 
-country~(PT or UK), 
-model~(Cobb-Douglas or CES),
-flavor~(Unadjusted or Quality-adjusted), 
-energy~(with or without), and
-nest~[($kl$), ($kl$)$e$, ($le$)$k$, or ($ek$)$l$, for the CES models]
-can be assessed for statistical significance
-compared to zero by a t-test.
-The null hypothesis for the t-test is that the mean of each group is
-equal to zero, and 
-the alternative hypothesis is that the mean is not equal to zero.
-Smaller p-values indicate increasing confidence that the 
-mean is different from zero. 
-We expect that p-values will be large (close to unity), 
-because the mean of the residuals is expected to be small (close to zero).
-Indeed, that is the case.
-Table~\ref{tab:r_p_values} summarizes the mean 
-and associated p-values values for the fitting residuals~($r_i$).
-%
-<<r_p_values, results="asis">>=
-# Calculate p values for groups of fitting residuals.
-r.t.values <- fitted_and_resid_data %>% 
-  group_by(Country, model, flavor, energy, nest) %>% 
-  summarize(Residuals.mean = mean(Residuals), Residuals.p.value = stats::t.test(Residuals)[["p.value"]])
-r.t.values <- arrange(ungroup(r.t.values), Country, model, flavor, energy, nest)
-# Display the values in a table
-myXTable(r.t.values,
-         caption="Means and p-values for fitting residuals~($r_i$).",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-
-%++++++++++++++++++++++++++++++
-\subsection{Does quality-adjusting the factors of production or including energy
-            decrease the fitting residuals in a statistically-significant manner?} 
-\label{sec:quality_adj_energy_and_fitting_residual}
-%++++++++++++++++++++++++++++++
-
-The set of annual $\Delta r$ values for each combination of 
-country~(PT or UK), 
-model~(Cobb-Douglas or CES),
-flavor~(Unadjusted or Quality-adjusted), 
-energy~(with or without), and
-nest~[($kl$), ($kl$)$e$, ($le$)$k$, or ($ek$)$l$, for the CES models]
-can be assessed for statistical significance
-compared to zero by a t-test.
-The null hypothesis for the t-test is that the mean of each group is
-equal to zero, and 
-the alternative hypothesis is that the mean is less than zero.
-Smaller p-values indicate increasing confidence that the 
-mean is actually less than zero.
-Table~\ref{tab:Dr_p_values} summarizes the mean 
-and associated p-values values for $\Delta r$.
-%
-<<Dr_p_values, results="asis">>=
-# Calculate p values for groups of Dr values.
-Dr.t.values <- fitted_and_resid_data %>% 
-  group_by(Country, model, flavor, energy, nest) %>% 
-  summarize(Dr.mean = mean(Dr), Dr.p.value = stats::t.test(Dr, alternative = "less")[["p.value"]])
-Dr.t.values <- arrange(ungroup(Dr.t.values), Country, model, flavor, energy, nest)
-# Display the values in a table
-myXTable(Dr.t.values,
-         caption="Means and p-values for $\\Delta r$.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-
-%++++++++++++++++++++++++++++++
-\subsection{What trends exist in factors shares?} 
-\label{sec:factor_shares}
+\section{Results}
+\label{sec:results}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The primary results from this paper involve the effects of
+the following modeling decisions:
+rejecting (or adhering to) the cost share theorem,
+quality-adjusting (or not) the factors of production,
+including energy (or not) in the production function, and
+nesting (in the CES model).
+
+We evaluate the effects of these modeling decisions 
+first on goodness of fit and Solow residual,
+next on factor shares, and 
+finally on factor substitutability.
+
+%++++++++++++++++++++++++++++++
+\subsection{Goodness of fit and Solow residual} 
+\label{sec:fit_and_sr}
+%++++++++++++++++++++++++++++++
+
+%------------------------------
+\subsubsection{Rejecting (or adhering to) the cost share theorem} 
+\label{sec:gfsr_cst}
+%------------------------------
+
+%------------------------------
+\subsubsection{Quality-adjusting (or not) factors of production} 
+\label{sec:gfsr_fop}
+%------------------------------
+
+%------------------------------
+\subsubsection{Including energy (or not)} 
+\label{sec:gfsr_energy}
+%------------------------------
+
+%------------------------------
+\subsubsection{CES nesting} 
+\label{sec:gfsr_nesting}
+%------------------------------
+
+%++++++++++++++++++++++++++++++
+\subsection{Factor shares} 
+\label{sec:shares}
 %++++++++++++++++++++++++++++++
@@
 @
+
+%------------------------------
+\subsubsection{Rejecting (or adhering to) the cost share theorem} 
+\label{sec:fs_cst}
+%------------------------------
+
+%------------------------------
+\subsubsection{Quality-adjusting (or not) factors of production} 
+\label{sec:fs_fop}
+%------------------------------
+
+%------------------------------
+\subsubsection{Including energy (or not)} 
+\label{sec:fs_energy}
+%------------------------------
+
+%------------------------------
+\subsubsection{CES nesting} 
+\label{sec:fs_nesting}
+%------------------------------
+
+%++++++++++++++++++++++++++++++
+\subsection{Factor substitutability} 
+\label{sec:substitutability}
+%++++++++++++++++++++++++++++++
+
+%------------------------------
+\subsubsection{Rejecting (or adhering to) the cost share theorem} 
+\label{sec:sigma_cst}
+%------------------------------
+
+%------------------------------
+\subsubsection{Quality-adjusting (or not) factors of production} 
+\label{sec:sigma_fop}
+%------------------------------
+
+%------------------------------
+\subsubsection{Including energy (or not)} 
+\label{sec:sigma_energy}
+%------------------------------
+
+%------------------------------
+\subsubsection{CES nesting} 
+\label{sec:sigma_nesting}
+%------------------------------
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Analysis}
+\label{sec:analysis}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+For now, I've organized the analysis around questions that we would like to answer.
+
+%++++++++++++++++++++++++++++++
+\subsection{Does rejecting the cost-share theorem 
+            decrease the mean squared error and/or the Solow residual?} 
+\label{sec:cst_and_solow_residual}
+%++++++++++++++++++++++++++++++
+
+Our hypothesis is that rejecting the cost-share theorem~(CST) will decrease
+both mean squared error~($mse$) and
+the Solow residual~($\lambda$).
+The mean squared error~($mse$) is expected to decrease 
+because rejecting the CST adds one or more fitting parameters
+to the model.
+The Solow residual~($\lambda$) is expected to decrease 
+because the factor shares for capital~($\alpha_1$) and labor~($\alpha_2 = 1 - \alpha_1$)
+are free to float, 
+allowing each factor of production 
+to contribute optimally toward production and
+bringing the model's prediction for economic output closer to 
+historical output. 
+In so doing, we expect less ``unexplained'' economic growth 
+and a decreased Solow residual~($\lambda$).
+
+Table~\ref{tab:Effect_of_CST_CES} shows the effect of the CST 
+on fitted parameters for the CES model.
+The CES models show lower $mse$ than the exponential-only models.
+The CES models also reduce solow residual ($\lambda$) relative
+to the exponential-only case.
+%
+<<Effect_of_CST_CES, results="asis">>=
+myXTable(filter(AllCoeffs, (model=="CES" & flavor=="Unadjusted" & energy=="Without energy") | model=="exp") %>% 
+           select(Country, model, cst, gamma, lambda, alpha_1, alpha_2, sigma_1, mse),
+         caption="Model parameters for CES models with unadjusted factors of production, without energy.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
+%
+Both Cobb-Douglas and CES models do a better job of fitting 
+historical data than an exponential-only model
+as evidenced by decreased $mse$ values.
+Both Cobb-Douglas and CES models exhibit reduced Solow residual~($\lambda$
+compared to the exponential-only model.
+For both Cobb-Douglas and CES, rejecting the Cost Share Theorem yields
+decreased mean squared error~($mse$) and
+smaller Solow residual ($\lambda$, on an absolute-value basis),
+as expected.
+
+***************
+
+Note that in Table~\ref{tab:Effect_of_CST_CES}, we see $\sigma_1 = 0.5$ 
+for UK when the cost share theorem is rejected. 
+This even-numbered result is coming from the grid search in $\rho_1$. 
+For an unknown reason, the gradient search from the best grid search point
+fails.
+I will investigate.
+
+This result means that we have found a set of fitting coefficients
+for this situation 
+that is \emph{close} to providing the minimum possible $mse$,
+but it may not be the \emph{exact} minimum.
+Regardless, the point above (that $mse$ and $\lambda$ always decrease 
+when rejecting the cost share theorem) remains valid.
+Investigating and fixing this problem
+will only serve to \emph{further} reduce $mse$ and $\lambda$ 
+from the values reported in Table~\ref{tab:Effect_of_CST_CES}.
+
+************
+
+%++++++++++++++++++++++++++++++
+\subsection{Does quality-adjusting the factors of production 
+            decrease the mean squared error and/or the Solow residual?} 
+\label{sec:quality_adj_energy_and_solow_residual}
+%++++++++++++++++++++++++++++++
+
+We can test our hypothesis that 
+quality-adjusting the factors of production
+and including energy will both reduce the Solow residuals~($\lambda$)
+and improve the fit to historical data
+(thereby reducing the fitting residuals, $r_i$, and mean squared error, $mse$)
+by calculating 
+$\Delta \lambda$ and $\Delta mse$, where
+%
+\begin{equation} \label{eq:delta_lambda}
+  \Delta \lambda \equiv \left| \lambda \right| - \left| \lambda_{Unadjusted, \, Without \, energy, \, CST} \right|
+\end{equation}
+%
+and
+%
+\begin{equation} \label{eq:delta_mse}
+  \Delta mse \equiv mse - mse_{Unadjusted, \, Without \, energy, \, CST}.
+\end{equation}
+%
+where~$N$ is the number of years of data.
+On a percentage basis,
+%
+\begin{equation} \label{eq:delta_lambda_perc}
+  \Delta \lambda \, [\%] = \frac{100 \, \Delta \lambda}{\left| \lambda_{Unadjusted, \, Without \, energy, \, CST} \right|} 
+            = \frac{100 \, \left| \lambda \right|}{\left| \lambda_{Unadjusted, \, Without \, energy, \, CST} \right|} - 1
+\end{equation}
+%
+When $\Delta \lambda$, $\Delta \lambda \, [\%]$, or $\Delta mse$ are negative, 
+we observe reduction in the Solow residual ($\lambda$) or
+the fitting residuals ($mse$)
+relative to the unadjusted, no-energy, CST case.
+
+To calculate $\Delta \lambda$ and $\Delta mse$, we need to fit all combinations of 
+country, model, flavor, energy, nest, and CST.
+Tables~\ref{tab:CES_coeffs} and~\ref{tab:CES_coeffs_sigmas} show 
+coefficients for all fitted CES models and the reference model (exponential-only).
+%
+<<CES_coeffs, results="asis">>=
+myXTable(filter(AllCoeffs, model=="CES" | model=="exp") %>% 
+           select(Country, model, flavor, energy, nest, cst, gamma, lambda, alpha_1, alpha_2, alpha_3),
+         caption="Model parameters for all CES models.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
+%
+<<CES_coeffs_sigmas, results="asis">>=
+myXTable(filter(AllCoeffs, model=="CES" | model=="exp") %>% 
+           select(Country, model, flavor, energy, nest, cst, sigma_1, sigma, mse),
+         caption="Model parameters for all CES models.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
+%
+Tables~\ref{tab:DSRmse_CESkle}--\ref{tab:DSRmse_CESekl} show $\Delta \lambda$ and $\Delta mse$ 
+results for CES models with various nestings.
+%
+<<DSRmse_CESkle, results="asis">>=
+myXTable(filter(AllCoeffs, (model=="CES" & (nest=="kl" | nest=="kle")) | model=="exp") %>% 
+           select(Country, model, flavor, energy, nest, cst, Dlambda, Dmse),
+         caption="$\\Delta \\lambda$ and $\\Delta mse$ for CES models with ($kl$)$e$ nesting.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
+%
+<<DSRmse_CESlek, results="asis">>=
+myXTable(filter(AllCoeffs, (model=="CES" & (nest=="kl" | nest=="lek")) | model=="exp") %>% 
+           select(Country, model, flavor, energy, nest, cst, Dlambda, Dmse),
+         caption="$\\Delta \\lambda$ and $\\Delta mse$ for CES models with ($le$)$k$ nesting.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
+%
+<<DSRmse_CESekl, results="asis">>=
+myXTable(filter(AllCoeffs, (model=="CES" & (nest=="kl" | nest=="ekl")) | model=="exp") %>% 
+           select(Country, model, flavor, energy, nest, cst, Dlambda, Dmse),
+         caption="$\\Delta \\lambda$ and $\\Delta mse$ for CES models with ($ek$)$l$ nesting.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
+Figures~\ref{fig:DSRmse_CES_graph} and~\ref{fig:percDSRmse_CES_graph} summarize 
+$\Delta \lambda$ and $\Delta mse$ 
+results for CES models.
+%
+<<DSRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta mse$) for the CES modles relative to the exponential-only model.">>=
+ggplot() +
+  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=Dmse, y=Dlambda, color=energy, size=cst, shape=nest)) +
+  scale_size_manual(values=c(2,3.5)) +
+  scale_shape_manual(values=c(16,17,18,15)) +
+  facet_grid(Country ~ flavor) +
+  xlab(expression(Delta * mse)) + 
+  scale_x_continuous(breaks=seq(-0.005, 0, 0.005)) +  
+  ylab(expression(Delta * lambda)) +
+  xy_theme() +
+  theme(legend.title=element_blank())
+@
+%
+<<percDSRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Percentage change in Solow Residuals~($\\Delta\\lambda \\, [\\%]$) and mean squared error~($\\Delta mse \\, [\\%]$) for the CES models relative to the exponential-only model.">>=
+ggplot() +
+  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=percDmse, y=percDlambda, color=energy, size=cst, shape=nest)) +
+  scale_size_manual(values=c(2,3.5)) +
+  scale_shape_manual(values=c(16,17,18,15)) +
+  facet_grid(Country ~ flavor) +
+  xlab(expression(paste(Delta * mse, " [%]"))) + 
+  scale_x_continuous(breaks=seq(-80, 0, 20)) +  
+  ylab(expression(paste(Delta * lambda, " [%]"))) +
+  scale_y_continuous(breaks=seq(-80, 0, 20), limits=c(-100, 10)) +  
+  xy_theme() +
+  theme(legend.title=element_blank())
+@
+
+%++++++++++++++++++++++++++++++
+\subsection{Are the means of the fitting residuals 
+            significantly different from zero?} 
+\label{sec:fitting_residuals_different_from_zero}
+%++++++++++++++++++++++++++++++
+
+The set of fitting residual values~($r_i$)
+for each combination of 
+country~(PT or UK), 
+model~(Cobb-Douglas or CES),
+flavor~(Unadjusted or Quality-adjusted), 
+energy~(with or without), and
+nest~[($kl$), ($kl$)$e$, ($le$)$k$, or ($ek$)$l$, for the CES models]
+can be assessed for statistical significance
+compared to zero by a t-test.
+The null hypothesis for the t-test is that the mean of each group is
+equal to zero, and 
+the alternative hypothesis is that the mean is not equal to zero.
+Smaller p-values indicate increasing confidence that the 
+mean is different from zero. 
+We expect that p-values will be large (close to unity), 
+because the mean of the residuals is expected to be small (close to zero).
+Indeed, that is the case.
+Table~\ref{tab:r_p_values} summarizes the mean 
+and associated p-values values for the fitting residuals~($r_i$).
+%
+<<r_p_values, results="asis">>=
+# Calculate p values for groups of fitting residuals.
+r.t.values <- filter(fitted_and_resid_data, model != "CD") %>% 
+  group_by(Country, model, flavor, energy, nest) %>% 
+  summarize(Residuals.mean = mean(Residuals), Residuals.p.value = stats::t.test(Residuals)[["p.value"]])
+r.t.values <- arrange(ungroup(r.t.values), Country, model, flavor, energy, nest)
+# Display the values in a table
+myXTable(r.t.values,
+         caption="Means and p-values for fitting residuals~($r_i$).",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
+
+%++++++++++++++++++++++++++++++
+\subsection{Does quality-adjusting the factors of production or including energy
+            decrease the fitting residuals in a statistically-significant manner?} 
+\label{sec:quality_adj_energy_and_fitting_residual}
+%++++++++++++++++++++++++++++++
+
+The set of annual $\Delta r$ values for each combination of 
+country~(PT or UK), 
+model~(Cobb-Douglas or CES),
+flavor~(Unadjusted or Quality-adjusted), 
+energy~(with or without), and
+nest~[($kl$), ($kl$)$e$, ($le$)$k$, or ($ek$)$l$, for the CES models]
+can be assessed for statistical significance
+compared to zero by a t-test.
+The null hypothesis for the t-test is that the mean of each group is
+equal to zero, and 
+the alternative hypothesis is that the mean is less than zero.
+Smaller p-values indicate increasing confidence that the 
+mean is actually less than zero.
+Table~\ref{tab:Dr_p_values} summarizes the mean 
+and associated p-values values for $\Delta r$.
+%
+<<Dr_p_values, results="asis">>=
+# Calculate p values for groups of Dr values.
+Dr.t.values <- filter(fitted_and_resid_data, model != "CD") %>% 
+  group_by(Country, model, flavor, energy, nest) %>% 
+  summarize(Dr.mean = mean(Dr), Dr.p.value = stats::t.test(Dr, alternative = "less")[["p.value"]])
+Dr.t.values <- arrange(ungroup(Dr.t.values), Country, model, flavor, energy, nest)
+# Display the values in a table
+myXTable(Dr.t.values,
+         caption="Means and p-values for $\\Delta r$.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
+
+%++++++++++++++++++++++++++++++
+\subsection{What trends exist in factors shares?} 
+\label{sec:factor_shares}
+%++++++++++++++++++++++++++++++
 
@@
 
-%++++++++++++++++++++++++++++++
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Correlograms} 
 \label{sec:correlograms}
-%++++++++++++++++++++++++++++++
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 %++++++++++++++++++++++++++++++
-\subsection{Correlograms for models respecting the cost-share theorem} 
+\subsection{Correlograms for the reference models} 
+\label{sec:correlograms_ref}
+%++++++++++++++++++++++++++++++
+
+In this section we present correlograms for the reference (exponential-only) models.
+
+<<Correlograms_Exp, echo=FALSE, message=FALSE>>=
+leaf_apply(l = modelsExp, class = c("lm"), f = function(model, name){
+  acf(resid(model), main=name)
+})
+@
+
+%++++++++++++++++++++++++++++++
+\subsection{Correlograms for models that adhere to the cost-share theorem} 
 \label{sec:correlograms_CST}
@@
 
-In this section we present correlograms for all models that respect the cost-share theorem.
+In this section we present correlograms for all models that adhere to the cost-share theorem.
 
@@
 %++++++++++++++++++++++++++++++
-\subsection{Correlograms for models reject the cost-share theorem} 
+\subsection{Correlograms for models that reject the cost-share theorem} 
 \label{sec:correlograms_noCST}
@@
 
-In this section we present correlograms for all models that do not adhere to the cost-share theorem.
+In this section we present correlograms for all models that reject the cost-share theorem.
 
@@
 
-%++++++++++++++++++++++++++++++
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Statistical details on all models} 
 \label{sec:staistical_details}
-%++++++++++++++++++++++++++++++
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 @
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Cobb-Douglas results} 
+\label{sec:cd_results}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+This section is the graveyard for information pertaining to the Cobb-Douglas model.
+
+%
+<<Graphs CD-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Cobb-Douglas models that reject the cost-share theorem. Solid line is historical GDP.">>=
+fittedGraphNoCST(filter(fitted_and_resid_data, model=="CD" & cst=="Reject CST"))
+@
+
+%
+<<Graphs CD-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for Cobb-Douglas models.">>=
+residualPlot(filter(fitted_and_resid_data, model=="CD" & cst=="Reject CST"))
+@
+
+Table~\ref{tab:Effect_of_CST_CD} shows the effect of the CST 
+on fitted parameters for the Cobb-Douglas model and the exponential-only model.
+The Cobb-Douglas models show lower $mse$ than the exponential-only models.
+The Cobb-Douglas models also reduce solow residual ($\lambda$) relative
+to the exponential-only case.
+%
+<<Effect_of_CST_CD, results="asis">>=
+myXTable(filter(AllCoeffs, (model=="CD" & flavor=="Unadjusted" & energy=="Without energy") | model=="exp") %>% 
+           select(Country, model, cst, scale, lambda, alpha_1, alpha_2, mse),
+         caption="Model parameters for Cobb-Douglas models with unadjusted factors of production, without energy.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
+%
+
+Table~\ref{tab:CD_coeffs} shows coefficients for all fitted Cobb-Douglas models
+and the reference model (exponential-only).
+%
+<<CD_coeffs, results="asis">>=
+myXTable(filter(AllCoeffs, model=="CD" | model=="exp") %>% 
+           select(Country, model, flavor, energy, cst, scale, lambda, alpha_1, alpha_2, alpha_3, mse),
+         caption="Model parameters for all Cobb-Douglas models.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
+%
+
+Table~\ref{tab:DSRmse_CD} shows $\Delta \lambda$ and $\Delta mse$ results for the Cobb-Douglas models.
+%
+<<DSRmse_CD, results="asis">>=
+myXTable(filter(AllCoeffs, model=="CD") %>% select(Country, model, flavor, energy, cst, Dlambda, Dmse),
+         caption="$\\Delta \\lambda$ and $\\Delta mse$ for Cobb-Douglas models.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
+%
+
+%
+Figures~\ref{fig:DSRmse_CD_graph} and~\ref{fig:percDSRmse_CD_graph} summarize 
+$\Delta \lambda$ and $\Delta mse$ 
+results for the Cobb-Douglas model.
+%
+<<DSRmse_CD_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta mse$) for the Cobb-Douglas model relative to the exponential-only model.">>=
+ggplot() +
+  geom_point(data=filter(AllCoeffs, model=="CD"), mapping=aes(x=Dmse, y=Dlambda, color=energy, size=cst)) +
+  facet_grid(Country ~ flavor) +
+  scale_size_manual(values=c(2,3.5)) +
+  xlab(expression(Delta * mse)) + 
+  scale_x_continuous(breaks=seq(-0.01, 0, 0.005), limits=c(-0.012, 0.003)) +  
+  ylab(expression(Delta * lambda)) +
+  scale_y_continuous(limits=c(-0.04, 0)) +
+  xy_theme() + 
+  theme(legend.title=element_blank())
+@
+%
+<<percDSRmse_CD_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Percentage change in Solow Residuals~($\\Delta\\lambda \\, [\\%]$) and mean squared error~($\\Delta mse \\, [\\%]$) for the Cobb-Douglas model relative to exponential-only models.">>=
+ggplot() +
+  geom_point(data=filter(AllCoeffs, model=="CD"), mapping=aes(x=percDmse, y=percDlambda, color=energy, size=cst)) +
+  facet_grid(Country ~ flavor) +
+  scale_size_manual(values=c(2,3.5)) +
+  xlab(expression(paste(Delta * mse, " [%]"))) + 
+  scale_x_continuous(breaks=seq(-50, 50, 50), limits=c(-90, 50)) +  
+  ylab(expression(paste(Delta * lambda, " [%]"))) +
+  scale_y_continuous(breaks=seq(-80, 0, 20), limits=c(-100, 10)) +  
+  xy_theme() + 
+  theme(legend.title=element_blank())
+@
+%
 

### 2015-07-08 Articles/Article_EcolEcon_2015/EcolEcon_2015.tex
Redoing model names.
Rearranging text into paper order.

@@
 Both historical GDP and fitted GDP are shown in 
-Figures~\ref{fig:Graphs CD-fitted}--\ref{fig:Graphs CESekl-fitted}.
-%
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[H]
-
-{\centering \includegraphics[width=\maxwidth]{figure/Graphs_CD-fitted-1}
-
-}
-
-\caption[Cobb-Douglas models that reject the cost-share theorem]{Cobb-Douglas models that reject the cost-share theorem. Solid line is historical GDP.}\label{fig:Graphs CD-fitted}
-\end{figure}
-
-\end{knitrout}
+Figures~\ref{fig:Graphs CESkle-fitted}--\ref{fig:Graphs CESekl-fitted}.
 %
@@
 
-Figures~\ref{fig:Graphs CD-resid}--\ref{fig:Graphs CESekl-resid}
-show fitting residuals for all models.
+Figures~\ref{fig:Graphs CESkle-resid}--\ref{fig:Graphs CESekl-resid}
+show fitting residuals for all CES models.
 %
@@
 
-{\centering \includegraphics[width=\maxwidth]{figure/Graphs_CD-resid-1}
+{\centering \includegraphics[width=\maxwidth]{figure/Graphs_CESkle-resid-1}
 
@@
 
-\caption[Fitting residuals for Cobb-Douglas models]{Fitting residuals for Cobb-Douglas models.}\label{fig:Graphs CD-resid}
+\caption[Fitting residuals for CES models with ]{Fitting residuals for CES models with $(kl$)$e$ nesting.}\label{fig:Graphs CESkle-resid}
 \end{figure}
@@
 
-{\centering \includegraphics[width=\maxwidth]{figure/Graphs_CESkle-resid-1}
+{\centering \includegraphics[width=\maxwidth]{figure/Graphs_CESlek-resid-1}
 
@@
 
-\caption[Fitting residuals for CES models with ]{Fitting residuals for CES models with $(kl$)$e$ nesting.}\label{fig:Graphs CESkle-resid}
+\caption[Fitting residuals for CES models with (]{Fitting residuals for CES models with ($le$)$k$ nesting.}\label{fig:Graphs CESlek-resid}
 \end{figure}
@@
 
-{\centering \includegraphics[width=\maxwidth]{figure/Graphs_CESlek-resid-1}
+{\centering \includegraphics[width=\maxwidth]{figure/Graphs_CESekl-resid-1}
 
@@
 
-\caption[Fitting residuals for CES models with (]{Fitting residuals for CES models with ($le$)$k$ nesting.}\label{fig:Graphs CESlek-resid}
+\caption[Fitting residuals for CES models with ]{Fitting residuals for CES models with $(ek$)$l$ nesting.}\label{fig:Graphs CESekl-resid}
 \end{figure}
@@
 \end{knitrout}
-%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results}
+\label{sec:results}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The primary results from this paper involve the effects of
+the following modeling decisions:
+rejecting (or adhering to) the cost share theorem,
+quality-adjusting (or not) the factors of production,
+including energy (or not) in the production function, and
+nesting (in the CES model).
+
+We evaluate the effects of these modeling decisions 
+first on goodness of fit and Solow residual,
+next on factor shares, and 
+finally on factor substitutability.
+
+%++++++++++++++++++++++++++++++
+\subsection{Goodness of fit and Solow residual} 
+\label{sec:fit_and_sr}
+%++++++++++++++++++++++++++++++
+
+%------------------------------
+\subsubsection{Rejecting (or adhering to) the cost share theorem} 
+\label{sec:gfsr_cst}
+%------------------------------
+
+%------------------------------
+\subsubsection{Quality-adjusting (or not) factors of production} 
+\label{sec:gfsr_fop}
+%------------------------------
+
+%------------------------------
+\subsubsection{Including energy (or not)} 
+\label{sec:gfsr_energy}
+%------------------------------
+
+%------------------------------
+\subsubsection{CES nesting} 
+\label{sec:gfsr_nesting}
+%------------------------------
+
+%++++++++++++++++++++++++++++++
+\subsection{Factor shares} 
+\label{sec:shares}
+%++++++++++++++++++++++++++++++
+
+Figures~\ref{fig:Factor_shares_graph_PT} and~\ref{fig:Factor_shares_graph_UK}
+show factor shares ($\alpha$ values) for CES models for
+Portugal and the UK, respectively.
+See Table~\ref{tab:CES_abg_equations} for details.
+
 \begin{knitrout}
@@
 
-{\centering \includegraphics[width=\maxwidth]{figure/Graphs_CESekl-resid-1}
+{\centering \includegraphics[width=\maxwidth]{figure/Factor_shares_graph_PT-1}
 
@@
 
-\caption[Fitting residuals for CES models with ]{Fitting residuals for CES models with $(ek$)$l$ nesting.}\label{fig:Graphs CESekl-resid}
+\caption[Factor shares (]{Factor shares ($\alpha$ values) for CES models for Portugal.}\label{fig:Factor_shares_graph_PT}
 \end{figure}
@@
 \end{knitrout}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[H]
+
+{\centering \includegraphics[width=\maxwidth]{figure/Factor_shares_graph_UK-1}
+
+}
+
+\caption[Factor shares (]{Factor shares ($\alpha$ values) for CES models for the UK.}\label{fig:Factor_shares_graph_UK}
+\end{figure}
+
+\end{knitrout}
+
+%------------------------------
+\subsubsection{Rejecting (or adhering to) the cost share theorem} 
+\label{sec:fs_cst}
+%------------------------------
+
+%------------------------------
+\subsubsection{Quality-adjusting (or not) factors of production} 
+\label{sec:fs_fop}
+%------------------------------
+
+%------------------------------
+\subsubsection{Including energy (or not)} 
+\label{sec:fs_energy}
+%------------------------------
+
+%------------------------------
+\subsubsection{CES nesting} 
+\label{sec:fs_nesting}
+%------------------------------
+
+%++++++++++++++++++++++++++++++
+\subsection{Factor substitutability} 
+\label{sec:substitutability}
+%++++++++++++++++++++++++++++++
+
+%------------------------------
+\subsubsection{Rejecting (or adhering to) the cost share theorem} 
+\label{sec:sigma_cst}
+%------------------------------
+
+%------------------------------
+\subsubsection{Quality-adjusting (or not) factors of production} 
+\label{sec:sigma_fop}
+%------------------------------
+
+%------------------------------
+\subsubsection{Including energy (or not)} 
+\label{sec:sigma_energy}
+%------------------------------
+
+%------------------------------
+\subsubsection{CES nesting} 
+\label{sec:sigma_nesting}
+%------------------------------
 
@@
 
-Table~\ref{tab:Effect_of_CST_CD} shows the effect of the CST 
-on fitted parameters for the Cobb-Douglas model and the exponential-only model.
-The Cobb-Douglas models show lower $mse$ than the exponential-only models.
-The Cobb-Douglas models also reduce solow residual ($\lambda$) relative
-to the exponential-only case.
-%
-% latex table generated in R 3.2.0 by xtable 1.7-4 package
-% Wed Jul  8 15:28:27 2015
-\begin{table}[ht]
-\centering
-\caption{Model parameters for Cobb-Douglas models with unadjusted factors of production, without energy.} 
-\label{tab:Effect_of_CST_CD}
-{\tiny
-\begin{tabular}{lllrrrrr}
-  \hline
-Country & model & cst & scale & lambda & alpha\_1 & alpha\_2 & mse \\ 
-  \hline
-PT & exp & Reject CST & 1.283537 & 0.034507 & 0.000000 & 0.000000 & 0.013359 \\ 
-  PT & CD & Adhere to CST & 1.328501 & 0.016080 & 0.300000 & 0.700000 & 0.011724 \\ 
-  PT & CD & Reject CST & 1.113489 & $-$0.005539 & 1.000000 & 0.000000 & 0.003190 \\ 
-  UK & exp & Reject CST & 1.021833 & 0.023565 & 0.000000 & 0.000000 & 0.001212 \\ 
-  UK & CD & Adhere to CST & 1.032978 & 0.015510 & 0.300000 & 0.700000 & 0.000775 \\ 
-  UK & CD & Reject CST & 1.000925 & 0.006654 & 0.544956 & 0.455044 & 0.000494 \\ 
-   \hline
-\end{tabular}
-}
-\end{table}
-
-%
 Table~\ref{tab:Effect_of_CST_CES} shows the effect of the CST 
@@
 % latex table generated in R 3.2.0 by xtable 1.7-4 package
-% Wed Jul  8 15:28:27 2015
+% Wed Jul  8 16:46:02 2015
 \begin{table}[ht]
@@
 country, model, flavor, energy, nest, and CST.
-Table~\ref{tab:CD_coeffs} shows coefficients for all fitted Cobb-Douglas models
-and the reference model (exponential-only).
-%
-% latex table generated in R 3.2.0 by xtable 1.7-4 package
-% Wed Jul  8 15:28:28 2015
-\begin{table}[ht]
-\centering
-\caption{Model parameters for all Cobb-Douglas models.} 
-\label{tab:CD_coeffs}
-{\tiny
-\begin{tabular}{lllllrrrrrr}
-  \hline
-Country & model & flavor & energy & cst & scale & lambda & alpha\_1 & alpha\_2 & alpha\_3 & mse \\ 
-  \hline
-PT & exp &  & Without energy & Reject CST & 1.283537 & 0.034507 & 0.000000 & 0.000000 & 0.000000 & 0.013359 \\ 
-  PT & CD & Unadjusted & Without energy & Adhere to CST & 1.328501 & 0.016080 & 0.300000 & 0.700000 & 0.000000 & 0.011724 \\ 
-  PT & CD & Unadjusted & Without energy & Reject CST & 1.113489 & $-$0.005539 & 1.000000 & 0.000000 & 0.000000 & 0.003190 \\ 
-  PT & CD & Unadjusted & With energy & Reject CST & 1.130790 & $-$0.004439 & 0.755978 & 0.000000 & 0.244022 & 0.002628 \\ 
-  PT & CD & Quality-adjusted & Without energy & Adhere to CST & 1.364226 & 0.004183 & 0.300000 & 0.700000 & 0.000000 & 0.011340 \\ 
-  PT & CD & Quality-adjusted & Without energy & Reject CST & 1.231989 & $-$0.015079 & 1.000000 & 0.000000 & 0.000000 & 0.008937 \\ 
-  PT & CD & Quality-adjusted & With energy & Reject CST & 1.111839 & $-$0.004569 & 0.000000 & 0.000000 & 1.000000 & 0.002268 \\ 
-  UK & exp &  & Without energy & Reject CST & 1.021833 & 0.023565 & 0.000000 & 0.000000 & 0.000000 & 0.001212 \\ 
-  UK & CD & Unadjusted & Without energy & Adhere to CST & 1.032978 & 0.015510 & 0.300000 & 0.700000 & 0.000000 & 0.000775 \\ 
-  UK & CD & Unadjusted & Without energy & Reject CST & 1.000925 & 0.006654 & 0.544956 & 0.455044 & 0.000000 & 0.000494 \\ 
-  UK & CD & Unadjusted & With energy & Reject CST & 0.995030 & 0.018134 & 0.162500 & 0.460325 & 0.377175 & 0.000331 \\ 
-  UK & CD & Quality-adjusted & Without energy & Adhere to CST & 1.038384 & 0.008725 & 0.300000 & 0.700000 & 0.000000 & 0.001564 \\ 
-  UK & CD & Quality-adjusted & Without energy & Reject CST & 1.015146 & $-$0.008149 & 0.751058 & 0.248942 & 0.000000 & 0.000720 \\ 
-  UK & CD & Quality-adjusted & With energy & Reject CST & 0.970614 & 0.001981 & 0.403433 & 0.330248 & 0.266319 & 0.000453 \\ 
-   \hline
-\end{tabular}
-}
-\end{table}
-
-%
 Tables~\ref{tab:CES_coeffs} and~\ref{tab:CES_coeffs_sigmas} show 
@@
 % latex table generated in R 3.2.0 by xtable 1.7-4 package
-% Wed Jul  8 15:28:28 2015
+% Wed Jul  8 16:46:02 2015
 \begin{table}[ht]
@@
 %
-Table~\ref{tab:DSRmse_CD} shows $\Delta \lambda$ and $\Delta mse$ results for the Cobb-Douglas models.
-%
-% latex table generated in R 3.2.0 by xtable 1.7-4 package
-% Wed Jul  8 15:28:28 2015
-\begin{table}[ht]
-\centering
-\caption{$\Delta \lambda$ and $\Delta mse$ for Cobb-Douglas models.} 
-\label{tab:DSRmse_CD}
-{\tiny
-\begin{tabular}{lllllrr}
-  \hline
-Country & model & flavor & energy & cst & Dlambda & Dmse \\ 
-  \hline
-PT & CD & Unadjusted & Without energy & Adhere to CST & $-$0.018427 & $-$0.001635 \\ 
-  PT & CD & Unadjusted & Without energy & Reject CST & $-$0.028968 & $-$0.010168 \\ 
-  PT & CD & Unadjusted & With energy & Reject CST & $-$0.030068 & $-$0.010730 \\ 
-  PT & CD & Quality-adjusted & Without energy & Adhere to CST & $-$0.030324 & $-$0.002019 \\ 
-  PT & CD & Quality-adjusted & Without energy & Reject CST & $-$0.019428 & $-$0.004422 \\ 
-  PT & CD & Quality-adjusted & With energy & Reject CST & $-$0.029938 & $-$0.011091 \\ 
-  UK & CD & Unadjusted & Without energy & Adhere to CST & $-$0.008055 & $-$0.000437 \\ 
-  UK & CD & Unadjusted & Without energy & Reject CST & $-$0.016911 & $-$0.000717 \\ 
-  UK & CD & Unadjusted & With energy & Reject CST & $-$0.005432 & $-$0.000880 \\ 
-  UK & CD & Quality-adjusted & Without energy & Adhere to CST & $-$0.014840 & 0.000352 \\ 
-  UK & CD & Quality-adjusted & Without energy & Reject CST & $-$0.015416 & $-$0.000492 \\ 
-  UK & CD & Quality-adjusted & With energy & Reject CST & $-$0.021584 & $-$0.000758 \\ 
-   \hline
-\end{tabular}
-}
-\end{table}
-
-% 
 Tables~\ref{tab:DSRmse_CESkle}--\ref{tab:DSRmse_CESekl} show $\Delta \lambda$ and $\Delta mse$ 
@@
 
-%
-Figures~\ref{fig:DSRmse_CD_graph} and~\ref{fig:percDSRmse_CD_graph} summarize 
-$\Delta \lambda$ and $\Delta mse$ 
-results for the Cobb-Douglas model.
-%
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[H]
-
-{\centering \includegraphics[width=\maxwidth]{figure/DSRmse_CD_graph-1}
-
-}
-
-\caption[Change in Solow Residuals~(]{Change in Solow Residuals~($\Delta\lambda$) and mean squared error~($\Delta mse$) for the Cobb-Douglas model relative to the exponential-only model.}\label{fig:DSRmse_CD_graph}
-\end{figure}
-
-\end{knitrout}
-%
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[H]
-
-{\centering \includegraphics[width=\maxwidth]{figure/percDSRmse_CD_graph-1}
-
-}
-
-\caption[Percentage change in Solow Residuals~(]{Percentage change in Solow Residuals~($\Delta\lambda \, [\%]$) and mean squared error~($\Delta mse \, [\%]$) for the Cobb-Douglas model relative to exponential-only models.}\label{fig:percDSRmse_CD_graph}
-\end{figure}
-
-\end{knitrout}
-%
 Figures~\ref{fig:DSRmse_CES_graph} and~\ref{fig:percDSRmse_CES_graph} summarize 
@@
 % latex table generated in R 3.2.0 by xtable 1.7-4 package
-% Wed Jul  8 15:28:29 2015
+% Wed Jul  8 16:46:03 2015
 \begin{table}[ht]
@@
   \hline
-PT & CD & Unadjusted & Without energy &  & $-$0.000000 & 1.000000 \\ 
-  PT & CD & Unadjusted & With energy &  & $-$0.000000 & 1.000000 \\ 
-  PT & CD & Quality-adjusted & Without energy &  & 0.000000 & 1.000000 \\ 
-  PT & CD & Quality-adjusted & With energy &  & 0.000000 & 1.000000 \\ 
 PT & CES & Unadjusted & Without energy & kl & 0.000000 & 0.999999 \\ 
@@
   PT & exp &  & Without energy &  & $-$0.000000 & 1.000000 \\ 
-  UK & CD & Unadjusted & Without energy &  & 0.000000 & 1.000000 \\ 
-  UK & CD & Unadjusted & With energy &  & $-$0.000000 & 1.000000 \\ 
-  UK & CD & Quality-adjusted & Without energy &  & 0.000000 & 1.000000 \\ 
-  UK & CD & Quality-adjusted & With energy &  & $-$0.000000 & 1.000000 \\ 
   UK & CES & Unadjusted & Without energy & kl & $-$0.000000 & 1.000000 \\ 
@@
   \hline
-PT & CD & Unadjusted & Without energy &  & $-$0.025733 & 0.000000 \\ 
-  PT & CD & Unadjusted & With energy &  & $-$0.048181 & 0.000000 \\ 
-  PT & CD & Quality-adjusted & Without energy &  & $-$0.009587 & 0.003533 \\ 
-  PT & CD & Quality-adjusted & With energy &  & $-$0.051804 & 0.000000 \\ 
 PT & CES & Unadjusted & Without energy & kl & $-$0.038049 & 0.000000 \\ 
@@
   PT & exp &  & Without energy &  & 0.000000 &  \\ 
-  UK & CD & Unadjusted & Without energy &  & $-$0.011254 & 0.000003 \\ 
-  UK & CD & Unadjusted & With energy &  & $-$0.014450 & 0.000000 \\ 
-  UK & CD & Quality-adjusted & Without energy &  & $-$0.004538 & 0.055557 \\ 
-  UK & CD & Quality-adjusted & With energy &  & $-$0.012454 & 0.000072 \\ 
   UK & CES & Unadjusted & Without energy & kl & $-$0.013655 & 0.000000 \\ 
@@
 %++++++++++++++++++++++++++++++
-
-Figures~\ref{fig:Factor_shares_graph_PT} and~\ref{fig:Factor_shares_graph_UK}
-show factor shares ($\alpha$ values) for CES models for
-Portugal and the UK, respectively.
-See Table~\ref{tab:CES_abg_equations} for details.
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[H]
-
-{\centering \includegraphics[width=\maxwidth]{figure/Factor_shares_graph_PT-1}
-
-}
-
-\caption[Factor shares (]{Factor shares ($\alpha$ values) for CES models for Portugal.}\label{fig:Factor_shares_graph_PT}
-\end{figure}
-
-\end{knitrout}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[H]
-
-{\centering \includegraphics[width=\maxwidth]{figure/Factor_shares_graph_UK-1}
-
-}
-
-\caption[Factor shares (]{Factor shares ($\alpha$ values) for CES models for the UK.}\label{fig:Factor_shares_graph_UK}
-\end{figure}
-
-\end{knitrout}
 
@@
 
-%++++++++++++++++++++++++++++++
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Correlograms} 
 \label{sec:correlograms}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+This appendix contains correlograms for all models.
+
 %++++++++++++++++++++++++++++++
-
-This appendix contains correlograms for all models.
-
+\subsection{Correlograms for the reference models} 
+\label{sec:correlograms_ref}
 %++++++++++++++++++++++++++++++
-\subsection{Correlograms for models respecting the cost-share theorem} 
+
+In this section we present correlograms for the reference (exponential-only) models.
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\maxwidth]{figure/Correlograms_Exp-1}
+
+\includegraphics[width=\maxwidth]{figure/Correlograms_Exp-2} 
+\begin{kframe}\begin{verbatim}
+$PT
+
+Autocorrelations of series 'resid(model)', by lag
+
+     0      1      2      3      4      5      6      7      8      9 
+ 1.000  0.863  0.724  0.585  0.460  0.350  0.254  0.153  0.075  0.018 
+    10     11     12     13     14     15     16     17 
+-0.051 -0.108 -0.150 -0.178 -0.168 -0.157 -0.179 -0.187
+
+$UK
+
+Autocorrelations of series 'resid(model)', by lag
+
+     0      1      2      3      4      5      6      7      8      9 
+ 1.000  0.785  0.492  0.237  0.084  0.008 -0.110 -0.207 -0.234 -0.182 
+    10     11     12     13     14     15     16     17 
+-0.153 -0.155 -0.180 -0.192 -0.143 -0.086 -0.067 -0.060 
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
+
+%++++++++++++++++++++++++++++++
+\subsection{Correlograms for models that adhere to the cost-share theorem} 
 \label{sec:correlograms_CST}
@@
 \end{table}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Cobb-Douglas results} 
+\label{sec:cd_results}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+This section is the graveyard for information pertaining to the Cobb-Douglas model.
+
+%
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[H]
+
+{\centering \includegraphics[width=\maxwidth]{figure/Graphs_CD-fitted-1}
+
+}
+
+\caption[Cobb-Douglas models that reject the cost-share theorem]{Cobb-Douglas models that reject the cost-share theorem. Solid line is historical GDP.}\label{fig:Graphs CD-fitted}
+\end{figure}
+
+\end{knitrout}
+
+%
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[H]
+
+{\centering \includegraphics[width=\maxwidth]{figure/Graphs_CD-resid-1}
+
+}
+
+\caption[Fitting residuals for Cobb-Douglas models]{Fitting residuals for Cobb-Douglas models.}\label{fig:Graphs CD-resid}
+\end{figure}
+
+\end{knitrout}
+
+Table~\ref{tab:Effect_of_CST_CD} shows the effect of the CST 
+on fitted parameters for the Cobb-Douglas model and the exponential-only model.
+The Cobb-Douglas models show lower $mse$ than the exponential-only models.
+The Cobb-Douglas models also reduce solow residual ($\lambda$) relative
+to the exponential-only case.
+%
+% latex table generated in R 3.2.0 by xtable 1.7-4 package
+% Wed Jul  8 16:46:04 2015
+\begin{table}[ht]
+\centering
+\caption{Model parameters for Cobb-Douglas models with unadjusted factors of production, without energy.} 
+\label{tab:Effect_of_CST_CD}
+{\tiny
+\begin{tabular}{lllrrrrr}
+  \hline
+Country & model & cst & scale & lambda & alpha\_1 & alpha\_2 & mse \\ 
+  \hline
+PT & exp & Reject CST & 1.283537 & 0.034507 & 0.000000 & 0.000000 & 0.013359 \\ 
+  PT & CD & Adhere to CST & 1.328501 & 0.016080 & 0.300000 & 0.700000 & 0.011724 \\ 
+  PT & CD & Reject CST & 1.113489 & $-$0.005539 & 1.000000 & 0.000000 & 0.003190 \\ 
+  UK & exp & Reject CST & 1.021833 & 0.023565 & 0.000000 & 0.000000 & 0.001212 \\ 
+  UK & CD & Adhere to CST & 1.032978 & 0.015510 & 0.300000 & 0.700000 & 0.000775 \\ 
+  UK & CD & Reject CST & 1.000925 & 0.006654 & 0.544956 & 0.455044 & 0.000494 \\ 
+   \hline
+\end{tabular}
+}
+\end{table}
+
+%
+
+Table~\ref{tab:CD_coeffs} shows coefficients for all fitted Cobb-Douglas models
+and the reference model (exponential-only).
+%
+% latex table generated in R 3.2.0 by xtable 1.7-4 package
+% Wed Jul  8 16:46:04 2015
+\begin{table}[ht]
+\centering
+\caption{Model parameters for all Cobb-Douglas models.} 
+\label{tab:CD_coeffs}
+{\tiny
+\begin{tabular}{lllllrrrrrr}
+  \hline
+Country & model & flavor & energy & cst & scale & lambda & alpha\_1 & alpha\_2 & alpha\_3 & mse \\ 
+  \hline
+PT & exp &  & Without energy & Reject CST & 1.283537 & 0.034507 & 0.000000 & 0.000000 & 0.000000 & 0.013359 \\ 
+  PT & CD & Unadjusted & Without energy & Adhere to CST & 1.328501 & 0.016080 & 0.300000 & 0.700000 & 0.000000 & 0.011724 \\ 
+  PT & CD & Unadjusted & Without energy & Reject CST & 1.113489 & $-$0.005539 & 1.000000 & 0.000000 & 0.000000 & 0.003190 \\ 
+  PT & CD & Unadjusted & With energy & Reject CST & 1.130790 & $-$0.004439 & 0.755978 & 0.000000 & 0.244022 & 0.002628 \\ 
+  PT & CD & Quality-adjusted & Without energy & Adhere to CST & 1.364226 & 0.004183 & 0.300000 & 0.700000 & 0.000000 & 0.011340 \\ 
+  PT & CD & Quality-adjusted & Without energy & Reject CST & 1.231989 & $-$0.015079 & 1.000000 & 0.000000 & 0.000000 & 0.008937 \\ 
+  PT & CD & Quality-adjusted & With energy & Reject CST & 1.111839 & $-$0.004569 & 0.000000 & 0.000000 & 1.000000 & 0.002268 \\ 
+  UK & exp &  & Without energy & Reject CST & 1.021833 & 0.023565 & 0.000000 & 0.000000 & 0.000000 & 0.001212 \\ 
+  UK & CD & Unadjusted & Without energy & Adhere to CST & 1.032978 & 0.015510 & 0.300000 & 0.700000 & 0.000000 & 0.000775 \\ 
+  UK & CD & Unadjusted & Without energy & Reject CST & 1.000925 & 0.006654 & 0.544956 & 0.455044 & 0.000000 & 0.000494 \\ 
+  UK & CD & Unadjusted & With energy & Reject CST & 0.995030 & 0.018134 & 0.162500 & 0.460325 & 0.377175 & 0.000331 \\ 
+  UK & CD & Quality-adjusted & Without energy & Adhere to CST & 1.038384 & 0.008725 & 0.300000 & 0.700000 & 0.000000 & 0.001564 \\ 
+  UK & CD & Quality-adjusted & Without energy & Reject CST & 1.015146 & $-$0.008149 & 0.751058 & 0.248942 & 0.000000 & 0.000720 \\ 
+  UK & CD & Quality-adjusted & With energy & Reject CST & 0.970614 & 0.001981 & 0.403433 & 0.330248 & 0.266319 & 0.000453 \\ 
+   \hline
+\end{tabular}
+}
+\end{table}
+
+%
+
+Table~\ref{tab:DSRmse_CD} shows $\Delta \lambda$ and $\Delta mse$ results for the Cobb-Douglas models.
+%
+% latex table generated in R 3.2.0 by xtable 1.7-4 package
+% Wed Jul  8 16:46:04 2015
+\begin{table}[ht]
+\centering
+\caption{$\Delta \lambda$ and $\Delta mse$ for Cobb-Douglas models.} 
+\label{tab:DSRmse_CD}
+{\tiny
+\begin{tabular}{lllllrr}
+  \hline
+Country & model & flavor & energy & cst & Dlambda & Dmse \\ 
+  \hline
+PT & CD & Unadjusted & Without energy & Adhere to CST & $-$0.018427 & $-$0.001635 \\ 
+  PT & CD & Unadjusted & Without energy & Reject CST & $-$0.028968 & $-$0.010168 \\ 
+  PT & CD & Unadjusted & With energy & Reject CST & $-$0.030068 & $-$0.010730 \\ 
+  PT & CD & Quality-adjusted & Without energy & Adhere to CST & $-$0.030324 & $-$0.002019 \\ 
+  PT & CD & Quality-adjusted & Without energy & Reject CST & $-$0.019428 & $-$0.004422 \\ 
+  PT & CD & Quality-adjusted & With energy & Reject CST & $-$0.029938 & $-$0.011091 \\ 
+  UK & CD & Unadjusted & Without energy & Adhere to CST & $-$0.008055 & $-$0.000437 \\ 
+  UK & CD & Unadjusted & Without energy & Reject CST & $-$0.016911 & $-$0.000717 \\ 
+  UK & CD & Unadjusted & With energy & Reject CST & $-$0.005432 & $-$0.000880 \\ 
+  UK & CD & Quality-adjusted & Without energy & Adhere to CST & $-$0.014840 & 0.000352 \\ 
+  UK & CD & Quality-adjusted & Without energy & Reject CST & $-$0.015416 & $-$0.000492 \\ 
+  UK & CD & Quality-adjusted & With energy & Reject CST & $-$0.021584 & $-$0.000758 \\ 
+   \hline
+\end{tabular}
+}
+\end{table}
+
+%
+
+%
+Figures~\ref{fig:DSRmse_CD_graph} and~\ref{fig:percDSRmse_CD_graph} summarize 
+$\Delta \lambda$ and $\Delta mse$ 
+results for the Cobb-Douglas model.
+%
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[H]
+
+{\centering \includegraphics[width=\maxwidth]{figure/DSRmse_CD_graph-1}
+
+}
+
+\caption[Change in Solow Residuals~(]{Change in Solow Residuals~($\Delta\lambda$) and mean squared error~($\Delta mse$) for the Cobb-Douglas model relative to the exponential-only model.}\label{fig:DSRmse_CD_graph}
+\end{figure}
+
+\end{knitrout}
+%
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[H]
+
+{\centering \includegraphics[width=\maxwidth]{figure/percDSRmse_CD_graph-1}
+
+}
+
+\caption[Percentage change in Solow Residuals~(]{Percentage change in Solow Residuals~($\Delta\lambda \, [\%]$) and mean squared error~($\Delta mse \, [\%]$) for the Cobb-Douglas model relative to exponential-only models.}\label{fig:percDSRmse_CD_graph}
+\end{figure}
+
+\end{knitrout}
+%
 

### 2015-07-08 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Rearranging sections.

@@
 
+Table~\ref{tab:CES_sr_gof} shows 
+the Solow residual~($\lambda$) and
+goodness of fit~($mse$)
+for all modeling decisions.
+%
+<<CES_sr_gof, results="asis">>=
+myXTable(filter(AllCoeffs, model=="CES" | model=="exp") %>% 
+           select(Country, model, flavor, energy, nest, cst, gamma, lambda, mse),
+         caption="$\\theta$, Solow residual, and $mse$ for CES models.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
+%
+We can evaluate the effect of modeling decisions on 
+goodness of fit and Solow residual by
+calculating values relative to the reference model.
+To do so, we define 
+$\Delta \lambda$ and $\Delta mse$, where
+%
+\begin{equation} \label{eq:delta_lambda}
+  \Delta \lambda \equiv \left| \lambda \right| - \left| \lambda_{ref} \right|
+\end{equation}
+%
+and
+%
+\begin{equation} \label{eq:delta_mse}
+  \Delta mse \equiv mse - mse_{ref}.
+\end{equation}
+%
+where~$\lambda_{ref}$ and $mse_{ref}$ are the values 
+of the Solow residual and $mse$ for the reference model, respectively.
+On a percentage basis,
+%
+\begin{equation} \label{eq:delta_lambda_perc}
+  \Delta \lambda \, [\%] = \frac{100 \, \Delta \lambda}{\left| \lambda_{ref} \right|} 
+            = \frac{100 \, \left| \lambda \right|}{\left| \lambda_{ref} \right|} - 1
+\end{equation}
+%
+When $\Delta \lambda$, $\Delta \lambda \, [\%]$, or $\Delta mse$ are negative, 
+we observe reduction in the Solow residual ($\lambda$) or
+the fitting residuals ($mse$)
+relative to the reference model.
+
+Figures~\ref{fig:DSRmse_CES_graph} and~\ref{fig:percDSRmse_CES_graph} summarize 
+$\Delta \lambda$ and $\Delta mse$ 
+results for CES models.
+%
+<<DSRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta mse$) for the CES modles relative to the exponential-only model.">>=
+ggplot() +
+  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=Dmse, y=Dlambda, color=energy, size=cst, shape=nest)) +
+  scale_size_manual(values=c(2,3.5)) +
+  scale_shape_manual(values=c(16,17,18,15)) +
+  facet_grid(Country ~ flavor) +
+  xlab(expression(Delta * mse)) + 
+  scale_x_continuous(breaks=seq(-0.005, 0, 0.005)) +  
+  ylab(expression(Delta * lambda)) +
+  xy_theme() +
+  theme(legend.title=element_blank())
+@
+%
+<<percDSRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Percentage change in Solow Residuals~($\\Delta\\lambda \\, [\\%]$) and mean squared error~($\\Delta mse \\, [\\%]$) for the CES models relative to the exponential-only model.">>=
+ggplot() +
+  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=percDmse, y=percDlambda, color=energy, size=cst, shape=nest)) +
+  scale_size_manual(values=c(2,3.5)) +
+  scale_shape_manual(values=c(16,17,18,15)) +
+  facet_grid(Country ~ flavor) +
+  xlab(expression(paste(Delta * mse, " [%]"))) + 
+  scale_x_continuous(breaks=seq(-80, 0, 20)) +  
+  ylab(expression(paste(Delta * lambda, " [%]"))) +
+  scale_y_continuous(breaks=seq(-80, 0, 20), limits=c(-100, 10)) +  
+  xy_theme() +
+  theme(legend.title=element_blank())
+@
+
 %------------------------------
@@
 
+Table~\ref{tab:CES_alpha} shows 
+the factor shares for all CES modeling decisions.
+%
+<<CES_alpha, results="asis">>=
+myXTable(filter(AllCoeffs, model=="CES" | model=="exp") %>% 
+           select(Country, model, flavor, energy, nest, cst, alpha_1, alpha_2, alpha_3),
+         caption="Factor shares~($\\alpha$) for CES models.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
+%
 Figures~\ref{fig:Factor_shares_graph_PT} and~\ref{fig:Factor_shares_graph_UK}
@@
 
+<<CES_sigma, results="asis">>=
+myXTable(filter(AllCoeffs, model=="CES" | model=="exp") %>% 
+           select(Country, model, flavor, energy, nest, cst, sigma_1, sigma),
+         caption="Factor substitution~($\\sigma$) for CES models.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
+%
+
 %------------------------------
@@
 
-We can test our hypothesis that 
-quality-adjusting the factors of production
-and including energy will both reduce the Solow residuals~($\lambda$)
-and improve the fit to historical data
-(thereby reducing the fitting residuals, $r_i$, and mean squared error, $mse$)
-by calculating 
-$\Delta \lambda$ and $\Delta mse$, where
-%
-\begin{equation} \label{eq:delta_lambda}
-  \Delta \lambda \equiv \left| \lambda \right| - \left| \lambda_{Unadjusted, \, Without \, energy, \, CST} \right|
-\end{equation}
-%
-and
-%
-\begin{equation} \label{eq:delta_mse}
-  \Delta mse \equiv mse - mse_{Unadjusted, \, Without \, energy, \, CST}.
-\end{equation}
-%
-where~$N$ is the number of years of data.
-On a percentage basis,
-%
-\begin{equation} \label{eq:delta_lambda_perc}
-  \Delta \lambda \, [\%] = \frac{100 \, \Delta \lambda}{\left| \lambda_{Unadjusted, \, Without \, energy, \, CST} \right|} 
-            = \frac{100 \, \left| \lambda \right|}{\left| \lambda_{Unadjusted, \, Without \, energy, \, CST} \right|} - 1
-\end{equation}
-%
-When $\Delta \lambda$, $\Delta \lambda \, [\%]$, or $\Delta mse$ are negative, 
-we observe reduction in the Solow residual ($\lambda$) or
-the fitting residuals ($mse$)
-relative to the unadjusted, no-energy, CST case.
-
-To calculate $\Delta \lambda$ and $\Delta mse$, we need to fit all combinations of 
-country, model, flavor, energy, nest, and CST.
-Tables~\ref{tab:CES_coeffs} and~\ref{tab:CES_coeffs_sigmas} show 
-coefficients for all fitted CES models and the reference model (exponential-only).
 %
@@
          digits=6)
-@
-Figures~\ref{fig:DSRmse_CES_graph} and~\ref{fig:percDSRmse_CES_graph} summarize 
-$\Delta \lambda$ and $\Delta mse$ 
-results for CES models.
-%
-<<DSRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta mse$) for the CES modles relative to the exponential-only model.">>=
-ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=Dmse, y=Dlambda, color=energy, size=cst, shape=nest)) +
-  scale_size_manual(values=c(2,3.5)) +
-  scale_shape_manual(values=c(16,17,18,15)) +
-  facet_grid(Country ~ flavor) +
-  xlab(expression(Delta * mse)) + 
-  scale_x_continuous(breaks=seq(-0.005, 0, 0.005)) +  
-  ylab(expression(Delta * lambda)) +
-  xy_theme() +
-  theme(legend.title=element_blank())
-@
-%
-<<percDSRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Percentage change in Solow Residuals~($\\Delta\\lambda \\, [\\%]$) and mean squared error~($\\Delta mse \\, [\\%]$) for the CES models relative to the exponential-only model.">>=
-ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=percDmse, y=percDlambda, color=energy, size=cst, shape=nest)) +
-  scale_size_manual(values=c(2,3.5)) +
-  scale_shape_manual(values=c(16,17,18,15)) +
-  facet_grid(Country ~ flavor) +
-  xlab(expression(paste(Delta * mse, " [%]"))) + 
-  scale_x_continuous(breaks=seq(-80, 0, 20)) +  
-  ylab(expression(paste(Delta * lambda, " [%]"))) +
-  scale_y_continuous(breaks=seq(-80, 0, 20), limits=c(-100, 10)) +  
-  xy_theme() +
-  theme(legend.title=element_blank())
 @

### 2015-07-09 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Reorganized paper.

@@
 
-For the CES model, values of $\alpha_1$, $\alpha_2$, and $\alpha_3$ are calculated by
+For the CES model, factors shares~($\alpha_1$, $\alpha_2$, and $\alpha_3$) are calculated by
 $\alpha_1 = \delta_1$, $\alpha_2 = 1 - \delta_1$, and $\alpha_3 = 0$ 
@@
 \begin{equation} \label{eq:delta_lambda}
-  \Delta \lambda \equiv \left| \lambda \right| - \left| \lambda_{ref} \right|
+  \Delta \lambda \equiv \lambda - \lambda_{ref}
 \end{equation}
@@
 \begin{equation} \label{eq:delta_mse}
-  \Delta mse \equiv mse - mse_{ref}.
+  \Delta mse \equiv mse - mse_{ref},
 \end{equation}
 %
-where~$\lambda_{ref}$ and $mse_{ref}$ are the values 
+with~$\lambda_{ref}$ and $mse_{ref}$ being the values 
 of the Solow residual and $mse$ for the reference model, respectively.
@@
 \begin{equation} \label{eq:delta_lambda_perc}
-  \Delta \lambda \, [\%] = \frac{100 \, \Delta \lambda}{\left| \lambda_{ref} \right|} 
-            = \frac{100 \, \left| \lambda \right|}{\left| \lambda_{ref} \right|} - 1
+  \Delta \lambda \, [\%] = \frac{100 \, \Delta \lambda}{\lambda_{ref}} 
+            = \frac{100 \, \lambda}{\lambda_{ref}} - 1 \; ,
 \end{equation}
 %
+and
+%
+\begin{equation} \label{eq:delta_mse_perc}
+  \Delta mse \, [\%] = \frac{100 \, \Delta mse}{mse_{ref}} 
+            = \frac{100 \, mse}{mse_{ref}} - 1 \; .
+\end{equation}
+
 When $\Delta \lambda$, $\Delta \lambda \, [\%]$, or $\Delta mse$ are negative, 
@@
 Figures~\ref{fig:DSRmse_CES_graph} and~\ref{fig:percDSRmse_CES_graph} summarize 
-$\Delta \lambda$ and $\Delta mse$ 
+$\Delta \lambda \, [\%]$ and $\Delta mse \, [\%]$ 
 results for CES models.
-%
-<<DSRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta mse$) for the CES modles relative to the exponential-only model.">>=
-ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=Dmse, y=Dlambda, color=energy, size=cst, shape=nest)) +
-  scale_size_manual(values=c(2,3.5)) +
-  scale_shape_manual(values=c(16,17,18,15)) +
-  facet_grid(Country ~ flavor) +
-  xlab(expression(Delta * mse)) + 
-  scale_x_continuous(breaks=seq(-0.005, 0, 0.005)) +  
-  ylab(expression(Delta * lambda)) +
-  xy_theme() +
-  theme(legend.title=element_blank())
-@
 %
@@
 Table~\ref{tab:CES_alpha} shows 
-the factor shares for all CES modeling decisions.
+the factor shares~($\alpha_i$ values) for all CES modeling decisions.
 %
@@
 Portugal and the UK, respectively.
-See Table~\ref{tab:CES_abg_equations} for details.
-
+See Table~\ref{tab:CES_abg_equations} for details on the calculation
+of factor shares from fitted values of $\delta_1$ and $\delta$.
+%
 <<Factor_shares_bar_graph_function>>=
@@
 
+Table~\ref{tab:CES_sigma} shows 
+substitutability parameters~($\sigma_i$ values) 
+for all CES modeling decisions.
+
+**** Note: At the present time, Table~\ref{tab:CES_sigma}
+requires a LOT of effort to interpret, 
+because $\sigma_1$ and $\sigma$ have different meanings
+for each nesting.
+I'm planning to change the table to make interpretation easier. ---MKH ****
+
+**** Is there a graph we want to make here? ---MKH ****
+%
 <<CES_sigma, results="asis">>=
-myXTable(filter(AllCoeffs, model=="CES" | model=="exp") %>% 
+myXTable(filter(AllCoeffs, model=="CES") %>% 
            select(Country, model, flavor, energy, nest, cst, sigma_1, sigma),
@@
 %------------------------------
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Analysis}
-\label{sec:analysis}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-For now, I've organized the analysis around questions that we would like to answer.
-
-%++++++++++++++++++++++++++++++
-\subsection{Does rejecting the cost-share theorem 
-            decrease the mean squared error and/or the Solow residual?} 
-\label{sec:cst_and_solow_residual}
-%++++++++++++++++++++++++++++++
-
-Our hypothesis is that rejecting the cost-share theorem~(CST) will decrease
-both mean squared error~($mse$) and
-the Solow residual~($\lambda$).
-The mean squared error~($mse$) is expected to decrease 
-because rejecting the CST adds one or more fitting parameters
-to the model.
-The Solow residual~($\lambda$) is expected to decrease 
-because the factor shares for capital~($\alpha_1$) and labor~($\alpha_2 = 1 - \alpha_1$)
-are free to float, 
-allowing each factor of production 
-to contribute optimally toward production and
-bringing the model's prediction for economic output closer to 
-historical output. 
-In so doing, we expect less ``unexplained'' economic growth 
-and a decreased Solow residual~($\lambda$).
-
-Table~\ref{tab:Effect_of_CST_CES} shows the effect of the CST 
-on fitted parameters for the CES model.
-The CES models show lower $mse$ than the exponential-only models.
-The CES models also reduce solow residual ($\lambda$) relative
-to the exponential-only case.
-%
-<<Effect_of_CST_CES, results="asis">>=
-myXTable(filter(AllCoeffs, (model=="CES" & flavor=="Unadjusted" & energy=="Without energy") | model=="exp") %>% 
-           select(Country, model, cst, gamma, lambda, alpha_1, alpha_2, sigma_1, mse),
-         caption="Model parameters for CES models with unadjusted factors of production, without energy.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-%
-Both Cobb-Douglas and CES models do a better job of fitting 
-historical data than an exponential-only model
-as evidenced by decreased $mse$ values.
-Both Cobb-Douglas and CES models exhibit reduced Solow residual~($\lambda$
-compared to the exponential-only model.
-For both Cobb-Douglas and CES, rejecting the Cost Share Theorem yields
-decreased mean squared error~($mse$) and
-smaller Solow residual ($\lambda$, on an absolute-value basis),
-as expected.
-
-***************
-
-Note that in Table~\ref{tab:Effect_of_CST_CES}, we see $\sigma_1 = 0.5$ 
-for UK when the cost share theorem is rejected. 
-This even-numbered result is coming from the grid search in $\rho_1$. 
-For an unknown reason, the gradient search from the best grid search point
-fails.
-I will investigate.
-
-This result means that we have found a set of fitting coefficients
-for this situation 
-that is \emph{close} to providing the minimum possible $mse$,
-but it may not be the \emph{exact} minimum.
-Regardless, the point above (that $mse$ and $\lambda$ always decrease 
-when rejecting the cost share theorem) remains valid.
-Investigating and fixing this problem
-will only serve to \emph{further} reduce $mse$ and $\lambda$ 
-from the values reported in Table~\ref{tab:Effect_of_CST_CES}.
-
-************
-
-%++++++++++++++++++++++++++++++
-\subsection{Does quality-adjusting the factors of production 
-            decrease the mean squared error and/or the Solow residual?} 
-\label{sec:quality_adj_energy_and_solow_residual}
-%++++++++++++++++++++++++++++++
-
-%
-<<CES_coeffs, results="asis">>=
-myXTable(filter(AllCoeffs, model=="CES" | model=="exp") %>% 
-           select(Country, model, flavor, energy, nest, cst, gamma, lambda, alpha_1, alpha_2, alpha_3),
-         caption="Model parameters for all CES models.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-%
-<<CES_coeffs_sigmas, results="asis">>=
-myXTable(filter(AllCoeffs, model=="CES" | model=="exp") %>% 
-           select(Country, model, flavor, energy, nest, cst, sigma_1, sigma, mse),
-         caption="Model parameters for all CES models.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-%
-Tables~\ref{tab:DSRmse_CESkle}--\ref{tab:DSRmse_CESekl} show $\Delta \lambda$ and $\Delta mse$ 
-results for CES models with various nestings.
-%
-<<DSRmse_CESkle, results="asis">>=
-myXTable(filter(AllCoeffs, (model=="CES" & (nest=="kl" | nest=="kle")) | model=="exp") %>% 
-           select(Country, model, flavor, energy, nest, cst, Dlambda, Dmse),
-         caption="$\\Delta \\lambda$ and $\\Delta mse$ for CES models with ($kl$)$e$ nesting.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-%
-<<DSRmse_CESlek, results="asis">>=
-myXTable(filter(AllCoeffs, (model=="CES" & (nest=="kl" | nest=="lek")) | model=="exp") %>% 
-           select(Country, model, flavor, energy, nest, cst, Dlambda, Dmse),
-         caption="$\\Delta \\lambda$ and $\\Delta mse$ for CES models with ($le$)$k$ nesting.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-%
-<<DSRmse_CESekl, results="asis">>=
-myXTable(filter(AllCoeffs, (model=="CES" & (nest=="kl" | nest=="ekl")) | model=="exp") %>% 
-           select(Country, model, flavor, energy, nest, cst, Dlambda, Dmse),
-         caption="$\\Delta \\lambda$ and $\\Delta mse$ for CES models with ($ek$)$l$ nesting.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-
-%++++++++++++++++++++++++++++++
-\subsection{Are the means of the fitting residuals 
-            significantly different from zero?} 
-\label{sec:fitting_residuals_different_from_zero}
-%++++++++++++++++++++++++++++++
-
-The set of fitting residual values~($r_i$)
-for each combination of 
-country~(PT or UK), 
-model~(Cobb-Douglas or CES),
-flavor~(Unadjusted or Quality-adjusted), 
-energy~(with or without), and
-nest~[($kl$), ($kl$)$e$, ($le$)$k$, or ($ek$)$l$, for the CES models]
-can be assessed for statistical significance
-compared to zero by a t-test.
-The null hypothesis for the t-test is that the mean of each group is
-equal to zero, and 
-the alternative hypothesis is that the mean is not equal to zero.
-Smaller p-values indicate increasing confidence that the 
-mean is different from zero. 
-We expect that p-values will be large (close to unity), 
-because the mean of the residuals is expected to be small (close to zero).
-Indeed, that is the case.
-Table~\ref{tab:r_p_values} summarizes the mean 
-and associated p-values values for the fitting residuals~($r_i$).
-%
-<<r_p_values, results="asis">>=
-# Calculate p values for groups of fitting residuals.
-r.t.values <- filter(fitted_and_resid_data, model != "CD") %>% 
-  group_by(Country, model, flavor, energy, nest) %>% 
-  summarize(Residuals.mean = mean(Residuals), Residuals.p.value = stats::t.test(Residuals)[["p.value"]])
-r.t.values <- arrange(ungroup(r.t.values), Country, model, flavor, energy, nest)
-# Display the values in a table
-myXTable(r.t.values,
-         caption="Means and p-values for fitting residuals~($r_i$).",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-
-%++++++++++++++++++++++++++++++
-\subsection{Does quality-adjusting the factors of production or including energy
-            decrease the fitting residuals in a statistically-significant manner?} 
-\label{sec:quality_adj_energy_and_fitting_residual}
-%++++++++++++++++++++++++++++++
-
-The set of annual $\Delta r$ values for each combination of 
-country~(PT or UK), 
-model~(Cobb-Douglas or CES),
-flavor~(Unadjusted or Quality-adjusted), 
-energy~(with or without), and
-nest~[($kl$), ($kl$)$e$, ($le$)$k$, or ($ek$)$l$, for the CES models]
-can be assessed for statistical significance
-compared to zero by a t-test.
-The null hypothesis for the t-test is that the mean of each group is
-equal to zero, and 
-the alternative hypothesis is that the mean is less than zero.
-Smaller p-values indicate increasing confidence that the 
-mean is actually less than zero.
-Table~\ref{tab:Dr_p_values} summarizes the mean 
-and associated p-values values for $\Delta r$.
-%
-<<Dr_p_values, results="asis">>=
-# Calculate p values for groups of Dr values.
-Dr.t.values <- filter(fitted_and_resid_data, model != "CD") %>% 
-  group_by(Country, model, flavor, energy, nest) %>% 
-  summarize(Dr.mean = mean(Dr), Dr.p.value = stats::t.test(Dr, alternative = "less")[["p.value"]])
-Dr.t.values <- arrange(ungroup(Dr.t.values), Country, model, flavor, energy, nest)
-# Display the values in a table
-myXTable(Dr.t.values,
-         caption="Means and p-values for $\\Delta r$.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-
-%++++++++++++++++++++++++++++++
-\subsection{What trends exist in factors shares?} 
-\label{sec:factor_shares}
-%++++++++++++++++++++++++++++++
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Derivation of dynamic Solow residual for the CD equation}
-\label{sec:dynamic_sr_CD}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Assuming that parameters $\theta$, $\alpha$, and $\beta$
-in Equation~\ref{eq:CDe} are known from parameter estimation,
-we can estimate the value of $\lambda$ as follows.
-First, assume constant returns to scale such that 
-$\alpha + \beta + \gamma = 1$, 
-and calculate $\gamma = 1 - \alpha - \beta$.
-Then, take the natural logarithm ($\ln$) of Equation~\ref{eq:CDe} to obtain
-%
-\begin{equation} \label{eq:lnCD}
-  \ln y = \ln \theta + \ln A + \alpha \ln k + \beta \ln l + (1 - \alpha - \beta) \ln e \;.
-\end{equation}
-%
-By taking the derivative of Equation~\ref{eq:lnCD} with respect to time ($t$) 
-and noting that model parameters $\theta$, $\alpha$, and $\beta$ are 
-constant with respect to time, we obtain
-%
-\begin{equation} \label{eq:ddtlnCD}
-  \frac{1}{y}\frac{\mathrm{d}y}{\mathrm{d}t} 
-      = \frac{1}{A}\frac{\mathrm{d}A}{\mathrm{d}t} 
-      + \alpha \frac{1}{k}\frac{\mathrm{d}k}{\mathrm{d}t} 
-      + \beta \frac{1}{l}\frac{\mathrm{d}l}{\mathrm{d}t} 
-      + (1 - \alpha - \beta) \frac{1}{e}\frac{\mathrm{d}e}{\mathrm{d}t} \;.
-\end{equation}
-%
-Solving for the total factor productivity term gives
-%
-\begin{equation} \label{eq:solow_resid}
-  \frac{1}{A}\frac{\mathrm{d}A}{\mathrm{d}t} 
-      = \frac{1}{y}\frac{\mathrm{d}y}{\mathrm{d}t} 
-      - \left[
-              \alpha \frac{1}{k}\frac{\mathrm{d}k}{\mathrm{d}t} 
-              + \beta \frac{1}{l}\frac{\mathrm{d}l}{\mathrm{d}t} 
-              + (1 - \alpha - \beta) \frac{1}{e}\frac{\mathrm{d}e}{\mathrm{d}t} 
-        \right] \;.
-\end{equation}
-%
-Recognizing that $A \equiv \mathrm{e}^{\lambda (t-t_0)}$ gives
-%
-\begin{equation} \label{eq:lambda_calc}
-  \frac{1}{A}\frac{\mathrm{d}A}{\mathrm{d}t} 
-    = \frac{1}{\mathrm{e}^{\lambda (t-t_0)}} \; \lambda \mathrm{e}^{\lambda (t-t_0)}
-    = \lambda \; ,
-\end{equation}
-%
-which can be substituted into Equation~\ref{eq:solow_resid} to find
-%
-\begin{equation} \label{eq:lambda}
-  \lambda 
-    = \frac{1}{y}\frac{\mathrm{d}y}{\mathrm{d}t} 
-    - \left[
-              \alpha \frac{1}{k}\frac{\mathrm{d}k}{\mathrm{d}t} 
-              + \beta \frac{1}{l}\frac{\mathrm{d}l}{\mathrm{d}t} 
-              + (1 - \alpha - \beta) \frac{1}{e}\frac{\mathrm{d}e}{\mathrm{d}t} 
-      \right] \;.
-\end{equation}
-%
-Equation~\ref{eq:lambda} applies for any instant in time.
-
-If we approximate derivatives in Equation~\ref{eq:lambda} with forward differences
-between times $i$ and $j$, we find
-%
-\begin{equation} \label{eq:lambdaij}
-  \lambda_{i,j}
-    = \frac{1}{y_i}\frac{y_j - y_i}{t_j - t_i} 
-    - \left[
-            \alpha \frac{1}{k_i}\frac{k_j - k_i}{t_j - t_i} 
-            + \beta \frac{1}{l_i}\frac{l_j - l_i}{t_j - t_i} 
-            + (1 - \alpha - \beta) \frac{1}{e_i}\frac{e_j - e_i}{t_j - t_i} 
-      \right] \;,
-\end{equation}
-% 
-where $\lambda_{i,j}$ approximates the true, instantaneous value of $\lambda$
-from Equation~\ref{eq:lambda} between times $i$ and $j$.
-
-Interestingly, 
-%
-\begin{equation}
-  \lambda_{1,n}
-    \neq \sum_{i=2}^{n} \lambda_{i,i-1}  \;.
-\end{equation}
-% 
-Rather,
-%
-\begin{equation} \label{eq:lambda1n}
-  \lambda_{1,n}
-    = \frac{1}{y_1}\frac{y_n - y_1}{t_n - t_1} 
-      - \left[ 
-            \alpha \frac{1}{k_1}\frac{k_n - k_1}{t_n - t_1} 
-            + \beta \frac{1}{l_1}\frac{l_n - l_1}{t_n - t_1} 
-            + (1 - \alpha - \beta) \frac{1}{e_1}\frac{e_n - e_1}{t_n - t_1} 
-      \right] \; ,
-\end{equation}
-% 
-which will become increasingly inaccurate over large time spans,
-because $y_1$, $k_1$, $l_1$, and $e_1$ will be less representative
-of the average value of $y$, $k$, $l$, and $e$ in the time span, respectively.
-This suggests that an averaging approach such as
-%
-\begin{equation}
-  \lambda_{1,n}
-    = \frac{\sum_{i=2}^{n} \lambda_{i,i-1}}{n-1}
-\end{equation}
-%
-is a better approximation of Equation~\ref{eq:lambda1n},
-which is, itself, an approximation of the true value of $\lambda$ 
-given by Equation~\ref{eq:lambda}.
-
-The fraction~($f$) of GDP growth explained by the Solow residual
-for the CD model
-can be given as
-%
-\begin{equation} \label{eq:frac_growth_explained_by_solow}
-  f \equiv \frac{\lambda}{\frac{1}{y}\frac{\mathrm{d}y}{\mathrm{d}t}} 
-            = 1 - \frac{\alpha \frac{1}{k}\frac{\mathrm{d}k}{\mathrm{d}t} 
-                      + \beta \frac{1}{l}\frac{\mathrm{d}l}{\mathrm{d}t} 
-                      + (1 - \alpha - \beta) \frac{1}{e}\frac{\mathrm{d}e}{\mathrm{d}t}}
-                  {\frac{1}{y}\frac{\mathrm{d}y}{\mathrm{d}t}} \; .
-\end{equation}
-%
-Using forward differences to estimate $f$ yields
-%
-\begin{equation} \label{eq:f_finite_diff_1}
-  f_{i,j} = \frac{\lambda_{i,j}}{\frac{1}{y_i}\frac{y_j - y_i}{t_j - t_i}}
-       = 1 - \frac{\alpha \frac{1}{k_i}\frac{k_j - k_i}{t_j - t_i} 
-            + \beta \frac{1}{l_i}\frac{l_j - l_i}{t_j - t_i} 
-            + (1 - \alpha - \beta) \frac{1}{e_i}\frac{e_j - e_i}{t_j - t_i} }
-            {\frac{1}{y_i}\frac{y_j - y_i}{t_j - t_i}} \; .
-\end{equation}
-%
-Cancelling $t_j - t_i$ terms and simplifying gives
-%
-\begin{equation} \label{eq:f_finite_diff_2}
-  f_{i,j} = 1 - \frac{\alpha \left( \frac{k_j}{k_i} - 1 \right) 
-                      + \beta \left( \frac{l_j}{l_i} - 1 \right)
-                      + (1 - \alpha - \beta) \left( \frac{e_j}{e_i} - 1 \right)}
-            {\left( \frac{y_j}{y_i} - 1 \right)} \; ,
-\end{equation}
-%
-which is an estimate of the instantaneous value of $f$ 
-given by Equation~\ref{eq:frac_growth_explained_by_solow}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Derivation of dynamic Solow residual for the CES equation}
-\label{sec:dynamic_sr_CES}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-In this section, we derive the dynamic Solow residual ($\lambda$) 
-for the CES equation with three generic factors of production, namely
-$x_1$, $x_2$, and $x_3$.
-
-We can define
-%
-\begin{equation} \label{eq:a_def}
-  a \equiv \delta b^{\rho/\rho_1} + (1-\delta) x_3^{-\rho}
-\end{equation}
-%
-and
-%
-\begin{equation} \label{eq:b_def}
-  b \equiv \delta_1 x_1^{-\rho_1} + (1 - \delta_1) x_2^{-\rho_1} \; ,
-\end{equation}
-%
-such that Equation~\ref{eq:CESgeneric} can be restated as
-%
-\begin{equation} \label{eq:simple_y} 
-  y = \gamma A a^{-1/\rho} \; .
-\end{equation}
-%
-Taking the natural logarithm of Equation~\ref{eq:simple_y}
-and realizing that $\gamma$ is not a function of time, we find
-%
-\begin{equation}
-  \frac{1}{y} \frac{\mathrm{d} y}{\mathrm{d} t} = \frac{1}{A} \frac{\mathrm{d} A}{\mathrm{d} t} 
-                      + \left( - \frac{1}{\rho} \right) \frac{1}{a} \frac{\mathrm{d} a}{\mathrm{d} t} \; .
-\end{equation}
-%
-By Equation~\ref{eq:lambda_calc}, and after rearranging, 
-the dynamic Solow residual for the CES equation can be stated as
-%
-\begin{equation} \label{eq:lambda_for_CES}
-  \lambda = \frac{1}{y} \frac{\mathrm{d} y}{\mathrm{d} t} + \frac{1}{a} \frac{1}{\rho} \frac{\mathrm{d} a}{\mathrm{d} t} \; .
-\end{equation}
-%
-To find $\frac{\mathrm{d} a}{\mathrm{d} t}$ and $\frac{\mathrm{d} b}{\mathrm{d} t}$, 
-we take the time derivatives 
-of Equations~\ref{eq:a_def} and~\ref{eq:b_def}
-and rearrange slightly to obtain
-%
-\begin{equation} \label{eq:da_dt}
-  \frac{1}{\rho} \frac{\mathrm{d} a}{\mathrm{d} t} = \delta b^{(\rho/\rho_1 - 1)} \frac{1}{\rho_1} \frac{\mathrm{d} b}{\mathrm{d} t}
-                                      - (1-\delta) x_3^{-(\rho + 1)} \frac{\mathrm{d} x_3}{\mathrm{d} t}
-\end{equation}
-%
-and
-%
-\begin{equation} \label{eq:db_dt}
-  \frac{1}{\rho_1} \frac{\mathrm{d} b}{\mathrm{d} t} = - \delta_1 x_1^{-(\rho_1 + 1)} \frac{\mathrm{d} x_1}{\mathrm{d} t}
-                                      - (1 - \delta_1) x_2^{-(\rho_1 + 1)} \frac{\mathrm{d} x_2}{\mathrm{d} t} \; .
-\end{equation}
-%
-Equations~\ref{eq:lambda_for_CES}--\ref{eq:db_dt} can be used to 
-calculate a dynamic time series for $\lambda$ given 
-fitted parameters from the CES model
-($\rho, \rho_1, \delta, \, \mathrm{and} \; \delta_1$)
-and time series for economic output~($y$) and
-factors of production 
-($x_1, x_2, \, \mathrm{and} \; x_3$).
-The time derivatives $\left( 
-\frac{\mathrm{d} y}{\mathrm{d} t}, 
-\frac{\mathrm{d} x_1}{\mathrm{d} t},
-\frac{\mathrm{d} x_2}{\mathrm{d} t}, \, \mathrm{and} \;
-\frac{\mathrm{d} x_3}{\mathrm{d} t} \right)$
-can be approximated from historical data
-by forward finite differences in a manner similar to Equation~\ref{eq:lambdaij}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Thoughts on the ``dynamic'' Solow residual}
-\label{sec:thoughts_dynamic_sr}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\ref{sec:dynamic_sr_CD} and \ref{sec:dynamic_sr_CES} derived expressions
-for a ``dynamic'' Solow residual 
-for Cobb-Douglas and CES production functions, respectively.
-However, these approaches conflate 
-stochastic error terms and the time-dependent contribution of ``technology'' 
-to economic growth
-in one variable~($\lambda_{i,j}$).
-In this appendix, we let the Solow residual 
-(expressed as time-independent $\lambda$)
-stand on its own and try to separate the stochastic and time-dependent
-aspects of the fitting residuals~($r_i$).
-Note: this section is speculative, and we need feedback from Marco and Randy 
-before moving ahead with a presentation or publication based on this work.
-
-We can re-state the models (in general) as
-%
-\begin{equation} \label{eq:general_y}
-  y_i = \hat{y}_i \epsilon_i
-\end{equation}
-%
-where $\epsilon_i$ is a multiplicative error term, 
-$\hat{y}_i$ is the predicted economic output, and
-$\hat{y}_i \equiv f(\theta, \lambda, \alpha, \beta, \gamma; \; t_i)$.
-(For the Cobb-Douglas model, $f = \theta A k^\alpha l^\beta e^\gamma$.)
-
-Taking the natural logarithm~($\ln$) of Equation~\ref{eq:general_y} yields
-%
-\begin{equation} \label{eq:ln_y}
-  \ln y_i = \ln \hat{y}_i + \ln \epsilon_i \; ,
-\end{equation}
-%
-which can be rearranged to show
-%
-\begin{equation} \label{eq:lny_prep_for_r}
-  \ln y_i - \ln \hat{y}_i = \ln \epsilon_i \; .
-\end{equation}
-%
-Using Equation~\ref{eq:log-residuals}, we can write
-%
-\begin{equation} \label{eq:r_epsilon}
-  r_i = \ln \epsilon_i \; .
-\end{equation}
-%
-Our concern is that the residuals~($r_i$) may have a time-dependent component 
-in addition to a stochastic component.
-To decompose, we can define
-%
-\begin{equation} \label{eq:epsilon_definition}
-  \epsilon_i = \mathrm{e}^{m(t_i - t_0)} \mathrm{e}^{\varepsilon_i^*} \; .
-\end{equation}
-%
-Substituting Equation~\ref{eq:epsilon_definition} into \ref{eq:r_epsilon} yields
-%
-\begin{equation} \label{eq:r_for_correlation}
-  r_i = m (t_i - t_0) + \varepsilon_i^* \; .
-\end{equation}
-%
-where
-$m$ is a slope and captures the linear (in natural logarithmic space), 
-time-dependent component of $r_i$. 
-$\varepsilon_i^*$ is a variable that captures a stochastic component of $\epsilon_i$.
-Equation~\ref{eq:r_for_correlation} can be fitted via linear regression in time~($t_i$) as
-%
-\begin{equation} \label{eq:r_regression_eqn}
-  r_i = m (t_i - t_0) + b + \varepsilon_i^* \; .
-\end{equation}
-%
-In Equation~\ref{eq:r_regression_eqn},
-$b$ is the $y$-intercept of the regression and captures a time-independent offset of $r_i$.
-Recall that $\epsilon_i$ is related to the fitting residuals~($r_i$)
-by Equation~\ref{eq:r_epsilon}.
-Thus, obtaining estimates of $m$ and $b$ and values for $\varepsilon_i^*$
-is equivalent to estimating the time-dependent, time-independent, and stochastic
-components, respectively, of the multiplicative errors~($\epsilon_i$).
-This regression is equivalent to performing a linear fit to data in 
-Figures~\ref{fig:Graphs CD-resid}--\ref{fig:Graphs CESekl-resid}.
-
-For PT, Cobb-Douglas, unadjusted, without energy, we obtain the following:
-%
-<<residual_correlation, echo=TRUE>>=
-mod <- models$PT$unadjusted$noE$CD
-r_regression <- lm(formula = resid(mod) ~ mod$data$iYear)
-print(summary(r_regression))
-@
-%
-Note that the estimate for the coefficient in front of \texttt{mod\$data\$iYear}
-($m$ in Equation~\ref{eq:r_for_correlation})
-is incredibly small relative to the scale of the residuals~($r_i$),
-\Sexpr{coef(r_regression)[[2]]}, 
-indicating that there is little 
-linear time-dependent information in the residuals~($r_i$).
-This result is the same as saying that 
-the slope of a line fitted through the 
-PT, Unadjusted, Without energy data 
-in Figure~\ref{fig:Graphs CD-resid}
-is (effectively) zero.
-There is (effectively) no linear time trend in the residuals.
-
-Furthermore, the intercept ($b$ in Equation~\ref{eq:r_for_correlation})
-is very small relative to the scale of the residuals~($r_i$),
-\Sexpr{coef(r_regression)[[1]]}, 
-indicating that there is little time-independent information in the residuals~($r_i$).
-This result is the same as saying that the line fitted to the
-PT, Unadjusted, Without energy 
-data in Figure~\ref{fig:Graphs CD-resid}
-is nearly coincident with the $x$-axis.
-
-Almost all of the information in the residuals~($r_i$)
-is stochastic and captured by the $\varepsilon_i^*$ term.
-
-Perhaps Marco can help us interpret the rest of the
-output here (\texttt{F-statistic}, \texttt{p-value}, etc.).
-(An aside: what about fitting a quadratic curve,
-instead of a line, 
-through the $r_i$ values in Figure~\ref{fig:Graphs CD-resid}?)
-
-We can compare $r_i$ and $\varepsilon_i^*$, graphically,
-but the result is uninteresting. 
-We would expect $r_i$ and $\varepsilon_i^*$
-to be equal to each other by Equation~\ref{eq:r_regression_eqn}, 
-because
-(a) $m (t_i - t_0) \ll \max(r_i)$
-for any value of $t_i$
-and
-(b) $b \ll \max(r_i)$.
-Indeed, Figure~\ref{fig:Residuals_comparison}
-shows this is the case.
-%
-<<Residuals_comparison, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Comparison between $\\varepsilon_i^*$ and $r_i$">>=
-resids_comparison_df <- data.frame(list(iYear=mod$data$iYear, r=resid(mod), epsistar = resid(r_regression)))
-# resids_comparison_df <- melt(resids_comparison_df, measure.vars=c(r, epsistar), value.name="value", 
-#                              variable.name="name")
-ggplot(resids_comparison_df) + 
-  geom_point(mapping=aes(x=r, y=epsistar)) + 
-  xlab(expression(r[i])) +
-  ylab(expression(epsilon[i]^"*")) +
-  xy_theme()
-@
-%
-I'm not sure where this leaves us.
-Marco and I agreed that I would re-derive the ``dynamic'' Solow residual
-equation while properly including the multiplicative error term~($\epsilon_i$).
-I think I have done that, but the results aren't terribly interesting.
-There is little (linear) time-dependent~($m$) or 
-time-independent~($b$) 
-information in the residuals~($r_i$),
-as evidenced by Figures~\ref{fig:Graphs CD-resid}--\ref{fig:Graphs CESekl-resid}.
-
-Perhaps there is another direction in which I should go with this analysis?
 
@@
 %
-
-% %++++++++++++++++++++++++++++++
-% \subsection{What effect does including energy and quality-adjustment have 
-%             on the Solow residual in the Cobb-Douglas model?} 
-% \label{sec:quality_adj_energy_and_solow_residual}
-% %++++++++++++++++++++++++++++++
-% 
-% We'll first look at Portugal.
-% 
-% %------------------------------
-% \subsubsection{Portugal} 
-% %------------------------------
-% 
-% First, use non-quality-adjusted data for Portugal and the Cobb-Douglas model.
-% 
-% <<Portugal C-D undadjusted without energy>>=
-% naturalCoef(models$PT$unadjusted$noE$CD)
-% @
-% 
-% <<Portugal C-D undadjusted with energy>>=
-% naturalCoef(models$PT$unadjusted$withE$CD)
-% @
-% 
-% The Solow residual (\texttt{lambda}) is always negative. 
-% However, the absolute value of \texttt{lambda} decreases from 
-% \Sexpr{naturalCoef(models$PT$unadjusted$noE$CD)$lambda} to 
-% \Sexpr{naturalCoef(models$PT$unadjusted$withE$CD)$lambda}
-% when adding energy.
-% So it appears that for Portugal, 
-% using unadjusted inputs and including energy as a factor of production
-% reduces the absolute value of the Solow residual somewhat.
-% 
-% What about for quality-adjusted data and Portugal?
-% 
-% <<Portugal C-D adjusted without energy>>=
-% naturalCoef(models$PT$adjusted$noE$CD)
-% @
-% 
-% <<Portugal C-D adjusted with energy>>=
-% naturalCoef(models$PT$adjusted$withE$CD)
-% @
-% 
-% Using quality-adjusted inputs, the Solow residual (\texttt{lambda}) moves from 
-% \Sexpr{naturalCoef(models$PT$adjusted$noE$CD)$lambda} to
-% \Sexpr{naturalCoef(models$PT$adjusted$withE$CD)$lambda} when including energy.
-% The absolute value of the Solow residual again decreases when adding energy.
-% But, with quality-adjusted inputs, the effect is much stronger.
-% 
-% Table~\ref{tab:lambda_CD_PT} shows
-% the effect of both quality-corrected factors of production and energy.
-% We find that including energy as a factor of production 
-% reduces the absolute value of the Solow residual (\texttt{lambda})
-% whether or not the factors of production are quality-adjusted. 
-% Quality-adjustment gets part of the way toward eliminating the Solow residual.
-% 
-% \begin{table} \caption{Portugal Solow residual results with Cobb-Douglas.} 
-% \label{tab:lambda_CD_PT} 
-%   \begin{center}
-%     \begin{tabular}{r c c} 
-%       \toprule
-%                       & Unadjusted     & Quality-adjusted   \\
-%       \midrule
-%       Without energy  & \Sexpr{naturalCoef(models$PT$unadjusted$noE$CD)$lambda}    & \Sexpr{naturalCoef(models$PT$adjusted$noE$CD)$lambda} \\
-%       With energy     & \Sexpr{naturalCoef(models$PT$unadjusted$withE$CD)$lambda}  & \Sexpr{naturalCoef(models$PT$adjusted$withE$CD)$lambda} \\
-%       \bottomrule
-%     \end{tabular}
-%   \end{center}
-% \end{table}
-% 
-% Note that for Portugal the contribution of capital (\texttt{alpha\_1})
-% always shifts to energy (\texttt{alpha\_3}) when energy is included 
-% as a factor of production.
-% 
-% What about for the UK?
-% 
-% %------------------------------
-% \subsubsection{United Kingdom} 
-% %------------------------------
-% 
-% Table~\ref{tab:lambda_CD_UK} shows fitted Cobb-Douglas coefficients for the UK. 
-% 
-% \begin{table} \caption{UK Solow residual results with Cobb-Douglas.} 
-% \label{tab:lambda_CD_UK} 
-%   \begin{center}
-%     \begin{tabular}{r c c} 
-%       \toprule
-%                       & Unadjusted     & Quality-adjusted   \\
-%       \midrule
-%       Without energy  & \Sexpr{naturalCoef(models$UK$unadjusted$noE$CD)$lambda}   
-%                                                 & \Sexpr{naturalCoef(models$UK$adjusted$noE$CD)$lambda} \\
-%       With energy     & \Sexpr{naturalCoef(models$UK$unadjusted$withE$CD)$lambda} 
-%                                                 & \Sexpr{naturalCoef(models$UK$adjusted$withE$CD)$lambda} \\
-%       \bottomrule
-%     \end{tabular}
-%   \end{center}
-% \end{table}
-% 
-% For the UK, the quality-adjusted, with energy Solow residual is 
-% \Sexpr{naturalCoef(models$UK$adjusted$withE$CD)$lambda * 100}\%,
-% a very small number indeed.
-% For the UK, it appears that \emph{both} quality-adjustment and addition of energy as a factor of production
-% are required to effectively eliminate the Solow residual,
-% reducing it to \Sexpr{naturalCoef(models$UK$adjusted$withE$CD)$lambda}.
-% 
-% Adding energy alone actually \emph{in}creases the Solow residual from 
-% \Sexpr{naturalCoef(models$UK$unadjusted$noE$CD)$lambda} to
-% \Sexpr{naturalCoef(models$UK$unadjusted$withE$CD)$lambda}.
-% The details for each model with unadjusted factors of production are shown below.
-% 
-% <<UK CD Unadjusted Coefficients>>=
-% naturalCoef(models$UK$unadjusted$noE$CD)
-% naturalCoef(models$UK$unadjusted$withE$CD)
-% @
-% 
-% When energy is included, much of the effect of capital (\texttt{alpha\_1}) is 
-% attributed to energy (\texttt{alpha\_3}), 
-% as \texttt{alpha\_1} moves from 
-% \Sexpr{naturalCoef(models$UK$unadjusted$noE$CD)$alpha_1} to
-% \Sexpr{naturalCoef(models$UK$unadjusted$withE$CD)$alpha_1}.
-% 
-% When we look at quality-adjusted inputs, we find similar results.
-% 
-% <<UK CD Quality-adjusted Coefficients>>=
-% naturalCoef(models$UK$adjusted$noE$CD)
-% naturalCoef(models$UK$adjusted$withE$CD)
-% @
-% 
-% \texttt{alpha\_1} moves from 
-% \Sexpr{naturalCoef(models$UK$adjusted$noE$CD)$alpha_1} to
-% \Sexpr{naturalCoef(models$UK$adjusted$withE$CD)$alpha_1}.
-% 
-% Now, let's compare the fits to historical data.
-% 
-% 
-% 
-% %++++++++++++++++++++++++++++++
-% \subsection{Do we obtain a negative Solow residual for Portugal with the CES model?} 
-% \label{sec:Solow_negative_for_PT_in_CES?}
-% %++++++++++++++++++++++++++++++
-% 
-% First, look at the CES model without energy.
-% Nesting is unabmiguous, so this fit does not need to be repeated
-% for each nesting option. 
-% (This means that the top rows of Tables~\ref{tab:lambda_CES-kle_PT}--\ref{tab:lambda_CES-ekl_PT}
-% are identical.)
-% 
-% <<PT CES-kl, warning=FALSE>>=
-% naturalCoef(models$PT$unadjusted$noE$CES$kl)
-% naturalCoef(models$PT$adjusted$noE$CES$kl)
-% @
-% 
-% Both unadjusted and quality-adjusted variables give positive Solow residuals,
-% \Sexpr{naturalCoef(models$PT$unadjusted$noE$CES$kl)$lambda} for unadjusted inputs and
-% \Sexpr{naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda} for quality-adjusted inputs.
-% Furthermore, quality-adjustment reduces the magnitude of the Solow residual.
-% 
-% %------------------------------
-% \subsubsection{($kl$)$e$ nesting} 
-% %------------------------------
-% 
-% Now, look at unadjusted inputs using the ($kl$)$e$ nesting.
-% 
-% <<PT CES-kle unadjusted, warning=FALSE>>=
-% naturalCoef(models$PT$unadjusted$withE$CES$kle)
-% @
-% 
-% Now look at quality-adjusted inputs using the ($kl$)$e$ nesting.
-% 
-% <<PT CES-kle quality-adjusted, warning=FALSE>>=
-% naturalCoef(models$PT$adjusted$withE$CES$kle)
-% @
-% 
-% Table~\ref{tab:lambda_CES-kle_PT} summarizes the Portugal Solow residual results with CES and the ($kl$)$e$ nesting.
-% 
-% \begin{table} \caption{Portugal Solow residual results with CES and ($kl$)$e$ nesting.} 
-% \label{tab:lambda_CES-kle_PT} 
-%   \begin{center}
-%     \begin{tabular}{r c c} 
-%       \toprule
-%                       & Unadjusted     & Quality-adjusted   \\
-%       \midrule
-%       Without energy  & \Sexpr{naturalCoef(models$PT$unadjusted$noE$CES$kl)$lambda} 
-%                                                             & \Sexpr{naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda} \\
-%       With energy     & \Sexpr{naturalCoef(models$PT$unadjusted$withE$CES$kle)$lambda} 
-%                                                             & \Sexpr{naturalCoef(models$PT$adjusted$withE$CES$kle)$lambda} \\
-%       \bottomrule
-%     \end{tabular}
-%   \end{center}
-% \end{table}
-% 
-% Table~\ref{tab:sse_CES-kle_PT} shows the $sse$ values for each of these models.
-% 
-% \begin{table} \caption{PT $sse$ with CES and ($kl$)$e$ nesting.} 
-% \label{tab:sse_CES-kle_PT} 
-%   \begin{center}
-%     \begin{tabular}{r c c} 
-%       \toprule
-%                       & Unadjusted     & Quality-adjusted   \\
-%       \midrule
-%       Without energy  & \Sexpr{EconModels:::sse(models$PT$unadjusted$noE$CES$kl)$sse} 
-%                                                             & \Sexpr{EconModels:::sse(models$PT$adjusted$noE$CES$kl)$sse} \\
-%       With energy     & \Sexpr{EconModels:::sse(models$PT$unadjusted$withE$CES$kle)$sse} 
-%                                                             & \Sexpr{EconModels:::sse(models$PT$adjusted$withE$CES$kle)$sse} \\
-%       \bottomrule
-%     \end{tabular}
-%   \end{center}
-% \end{table}
-% 
-% In contrast to the Cobb-Douglas model,
-% the CES model with ($kl$)$e$ nesting
-% produces positive Solow residuals in all cases. 
-% We also see that both 
-% quality-adjusting the inputs and
-% including energy
-% reduce the Solow residual (\texttt{lambda}).
-% 
-% %------------------------------
-% \subsubsection{($le$)$k$ nesting} 
-% %------------------------------
-% 
-% Next, look at unadjusted inputs using the ($le$)$k$ nesting.
-% 
-% <<PT CES-lek unadjusted, warning=FALSE>>=
-% naturalCoef(models$PT$unadjusted$withE$CES$lek)
-% @
-% 
-% Now look at quality-adjusted inputs using the ($le$)$k$ nesting.
-% 
-% <<PT CES-lek quality-adjusted, warning=FALSE>>=
-% naturalCoef(models$PT$adjusted$withE$CES$lek)
-% @
-% 
-% Table~\ref{tab:lambda_CES-lek_PT} summarizes the Portugal Solow residual results with CES and the ($le$)$k$ nesting.
-% 
-% \begin{table} \caption{Portugal Solow residual results with CES and ($le$)$k$ nesting.} 
-% \label{tab:lambda_CES-lek_PT} 
-%   \begin{center}
-%     \begin{tabular}{r c c} 
-%       \toprule
-%                       & Unadjusted     & Quality-adjusted   \\
-%       \midrule
-%       Without energy  & \Sexpr{naturalCoef(models$PT$unadjusted$noE$CES$kl)$lambda} 
-%                                         & \Sexpr{naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda} \\
-%       With energy     & \Sexpr{naturalCoef(models$PT$unadjusted$withE$CES$lek)$lambda} 
-%                                         & \Sexpr{naturalCoef(models$PT$adjusted$withE$CES$lek)$lambda} \\
-%       \bottomrule
-%     \end{tabular}
-%   \end{center}
-% \end{table}
-% 
-% Table~\ref{tab:sse_CES-lek_PT} shows the $sse$ values for each of these models.
-% 
-% \begin{table} \caption{PT $sse$ with CES and ($le$)$k$ nesting.} 
-% \label{tab:sse_CES-lek_PT} 
-%   \begin{center}
-%     \begin{tabular}{r c c} 
-%       \toprule
-%                       & Unadjusted     & Quality-adjusted   \\
-%       \midrule
-%       Without energy  & \Sexpr{EconModels:::sse(models$PT$unadjusted$noE$CES$kl)$sse} 
-%                                         & \Sexpr{EconModels:::sse(models$PT$adjusted$noE$CES$kl)$sse} \\
-%       With energy     & \Sexpr{EconModels:::sse(models$PT$unadjusted$withE$CES$lek)$sse} 
-%                                         & \Sexpr{EconModels:::sse(models$PT$adjusted$withE$CES$lek)$sse} \\
-%       \bottomrule
-%     \end{tabular}
-%   \end{center}
-% \end{table}
-% 
-% Similar to the CES model with ($kl$)$e$ nesting,
-% the CES model with ($le$)$k$ nesting
-% produces positive Solow residuals in all cases. 
-% After energy has been added, quality-adjustment 
-% has very little effect on the Solow residual,
-% creating a slight increase from 
-% \Sexpr{naturalCoef(models$PT$unadjusted$withE$CES$lek)$lambda} to
-% \Sexpr{naturalCoef(models$PT$adjusted$withE$CES$lek)$lambda}.
-% 
-% 
-% %------------------------------
-% \subsubsection{($ek$)$l$ nesting} 
-% %------------------------------
-% 
-% Next, look at unadjusted inputs using the ($ek$)$l$ nesting.
-% 
-% <<PT CES-ekl unadjusted, warning=FALSE>>=
-% naturalCoef(models$PT$unadjusted$withE$CES$ekl)
-% @
-% 
-% Now look at quality-adjusted inputs using the ($ek$)$l$ nesting.
-% 
-% <<PT CES-ekl quality-adjusted, warning=FALSE>>=
-% naturalCoef(models$PT$adjusted$withE$CES$ekl)
-% @
-% 
-% Table~\ref{tab:lambda_CES-ekl_PT} summarizes the Portugal Solow residual results with CES and the ($ek$)$l$ nesting.
-% 
-% \begin{table} \caption{Portugal Solow residual results with CES and ($ek$)$l$ nesting.} 
-% \label{tab:lambda_CES-ekl_PT} 
-%   \begin{center}
-%     \begin{tabular}{r c c} 
-%       \toprule
-%                       & Unadjusted     & Quality-adjusted   \\
-%       \midrule
-%       Without energy  & \Sexpr{naturalCoef(models$PT$unadjusted$noE$CES$kl)$lambda} 
-%                                         & \Sexpr{naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda} \\
-%       With energy     & \Sexpr{naturalCoef(models$PT$unadjusted$withE$CES$ekl)$lambda} 
-%                                         & \Sexpr{naturalCoef(models$PT$adjusted$withE$CES$ekl)$lambda} \\
-%       \bottomrule
-%     \end{tabular}
-%   \end{center}
-% \end{table}
-% 
-% Table~\ref{tab:sse_CES-ekl_PT} shows the $sse$ values for each of these models.
-% 
-% \begin{table} \caption{PT $sse$ with CES and ($ek$)$l$ nesting.} 
-% \label{tab:sse_CES-ekl_PT} 
-%   \begin{center}
-%     \begin{tabular}{r c c} 
-%       \toprule
-%                       & Unadjusted     & Quality-adjusted   \\
-%       \midrule
-%       Without energy  & \Sexpr{EconModels:::sse(models$PT$unadjusted$noE$CES$kl)$sse} 
-%                                         & \Sexpr{EconModels:::sse(models$PT$adjusted$noE$CES$kl)$sse} \\
-%       With energy     & \Sexpr{EconModels:::sse(models$PT$unadjusted$withE$CES$ekl)$sse} 
-%                                         & \Sexpr{EconModels:::sse(models$PT$adjusted$withE$CES$ekl)$sse} \\
-%       \bottomrule
-%     \end{tabular}
-%   \end{center}
-% \end{table}
-% 
-% For the ($ek$)$l$ nesting, 
-% the Solow residual is positive, and 
-% quality-adjusting the inputs 
-% reduces the Solow residual (\texttt{lambda}).
-% Adding energy decreases the Solow residual 
-% (from \Sexpr{naturalCoef(models$PT$unadjusted$withE$CES$ekl)$lambda} to 
-% \Sexpr{naturalCoef(models$PT$adjusted$withE$CES$ekl)$lambda})
-% when enegy is included in the model.
-% But, adding energy slightly increases the Solow residual
-% (from \Sexpr{naturalCoef(models$PT$adjusted$noE$CES$kl)$lambda} to \Sexpr{naturalCoef(models$PT$adjusted$withE$CES$ekl)$lambda})
-% when quality-adjusted inputs are used.
-% 
-% 
-% %++++++++++++++++++++++++++++++
-% \subsection{Do we obtain a positive Solow residual for the UK with the CES model?} 
-% \label{sec:Solow_positive_for_UK_in_CES?}
-% %++++++++++++++++++++++++++++++
-% 
-% First, look at the CES model without energy.
-% Nesting is unabmiguous, so this fit does not need to be repeated
-% for each nesting option. 
-% (This means that the top rows of Tables~\ref{tab:lambda_CES-kle_UK}--\ref{tab:lambda_CES-ekl_UK}
-% are identical.)
-% 
-% <<UK CES-kl, warning=FALSE>>=
-% naturalCoef(models$UK$unadjusted$noE$CES$kl)
-% naturalCoef(models$UK$adjusted$noE$CES$kl)
-% @
-% 
-% Both unadjusted and quality-adjusted variables give positive Solow residuals for the UK,
-% \Sexpr{naturalCoef(models$UK$unadjusted$noE$CES$kl)$lambda} for unadjusted inputs and
-% \Sexpr{naturalCoef(models$UK$adjusted$noE$CES$kl)$lambda} for quality-adjusted inputs.
-% Furthermore, quality-adjustment reduces the magnitude of the UK Solow residual.
-% 
-% %------------------------------
-% \subsubsection{($kl$)$e$ nesting} 
-% %------------------------------
-% 
-% Now, look at unadjusted inputs using the ($kl$)$e$ nesting.
-% 
-% <<UK CES-kle unadjusted>>=
-% naturalCoef(models$UK$unadjusted$withE$CES$kle)
-% @
-% 
-% Now look at quality-adjusted inputs using the ($kl$)$e$ nesting.
-% 
-% <<UK CES-kle quality-adjusted>>=
-% naturalCoef(models$UK$adjusted$withE$CES$kle)
-% @
-% 
-% Table~\ref{tab:lambda_CES-kle_UK} summarizes the UK Solow residual results with CES and the ($kl$)$e$ nesting.
-% 
-% \begin{table} \caption{UK Solow residual results with CES and ($kl$)$e$ nesting.} 
-% \label{tab:lambda_CES-kle_UK} 
-%   \begin{center}
-%     \begin{tabular}{r c c} 
-%       \toprule
-%                       & Unadjusted     & Quality-adjusted   \\
-%       \midrule
-%       Without energy  & \Sexpr{naturalCoef(models$UK$unadjusted$noE$CES$kl)$lambda} & \Sexpr{naturalCoef(models$UK$adjusted$noE$CES$kl)$lambda} \\
-%       With energy     & \Sexpr{naturalCoef(models$UK$unadjusted$withE$CES$kle)$lambda} 
-%                                                                 & \Sexpr{naturalCoef(models$UK$adjusted$withE$CES$kle)$lambda} \\
-%       \bottomrule
-%     \end{tabular}
-%   \end{center}
-% \end{table}
-% 
-% Table~\ref{tab:sse_CES-kle_UK} shows the $sse$ values for each of these models.
-% 
-% \begin{table} \caption{UK $sse$ with CES and ($kl$)$e$ nesting.} 
-% \label{tab:sse_CES-kle_UK} 
-%   \begin{center}
-%     \begin{tabular}{r c c} 
-%       \toprule
-%                       & Unadjusted     & Quality-adjusted   \\
-%       \midrule
-%       Without energy  & \Sexpr{EconModels:::sse(models$UK$unadjusted$noE$CES$kl)$sse} & \Sexpr{EconModels:::sse(models$UK$adjusted$noE$CES$kl)$sse} \\
-%       With energy     & \Sexpr{EconModels:::sse(models$UK$unadjusted$withE$CES$kle)$sse} 
-%                                                             & \Sexpr{EconModels:::sse(models$UK$adjusted$withE$CES$kle)$sse} \\
-%       \bottomrule
-%     \end{tabular}
-%   \end{center}
-% \end{table}
-% 
-% Like the Cobb-Douglas model, the CES model produces positive Solow residuals
-% with the ($kl$)$e$ nesting.
-% We also see that both 
-% quality-adjusting the inputs and
-% including energy
-% reduce the Solow residual (\texttt{lambda}).
-% 
-% %------------------------------
-% \subsubsection{($le$)$k$ nesting}
-% %------------------------------
-% 
-% Next, look at unadjusted inputs using the ($le$)$k$ nesting.
-% 
-% <<UK CES-lek unadjusted>>=
-% naturalCoef(models$UK$unadjusted$withE$CES$lek)
-% @
-% 
-% Now look at quality-adjusted inputs using the ($le$)$k$ nesting.
-% 
-% <<UK CES-lek quality-adjusted>>=
-% naturalCoef(models$UK$adjusted$withE$CES$lek)
-% @
-% 
-% Table~\ref{tab:lambda_CES-lek_UK} summarizes the UK Solow residual results with CES and the ($le$)$k$ nesting.
-% 
-% \begin{table} \caption{UK Solow residual results with CES and ($le$)$k$ nesting.} 
-% \label{tab:lambda_CES-lek_UK} 
-%   \begin{center}
-%     \begin{tabular}{r c c} 
-%       \toprule
-%                       & Unadjusted     & Quality-adjusted   \\
-%       \midrule
-%       Without energy  & \Sexpr{naturalCoef(models$UK$unadjusted$noE$CES$kl)$lambda} & \Sexpr{naturalCoef(models$UK$adjusted$noE$CES$kl)$lambda} \\
-%       With energy     & \Sexpr{naturalCoef(models$UK$unadjusted$withE$CES$lek)$lambda} 
-%                                                             & \Sexpr{naturalCoef(models$UK$adjusted$withE$CES$lek)$lambda} \\
-%       \bottomrule
-%     \end{tabular}
-%   \end{center}
-% \end{table}
-% 
-% Table~\ref{tab:sse_CES-lek_UK} shows the $sse$ values for each of these models.
-% 
-% \begin{table} \caption{UK $sse$ with CES and ($le$)$k$ nesting.} 
-% \label{tab:sse_CES-lek_UK} 
-%   \begin{center}
-%     \begin{tabular}{r c c} 
-%       \toprule
-%                       & Unadjusted     & Quality-adjusted   \\
-%       \midrule
-%       Without energy  & \Sexpr{EconModels:::sse(models$UK$unadjusted$noE$CES$kl)$sse} & \Sexpr{EconModels:::sse(models$UK$adjusted$noE$CES$kl)$sse} \\
-%       With energy     & \Sexpr{EconModels:::sse(models$UK$unadjusted$withE$CES$lek)$sse} 
-%                                                             & \Sexpr{EconModels:::sse(models$UK$adjusted$withE$CES$lek)$sse} \\
-%       \bottomrule
-%     \end{tabular}
-%   \end{center}
-% \end{table}
-% 
-% 
-% Similar to the CES model with ($kl$)$e$ nesting,
-% the CES model with ($le$)$k$ nesting
-% produces positive Solow residuals in all cases. 
-% Both quality-adjustment and inclusion of energy 
-% decrease the magnitude of the Solow residual.
-% 
-% %------------------------------
-% \subsubsection{($ek$)$l$ nesting}
-% %------------------------------
-% 
-% Next, look at unadjusted inputs using the ($el$)$l$ nesting.
-% 
-% <<UK CES-ekl unadjusted>>=
-% naturalCoef(models$UK$unadjusted$withE$CES$ekl)
-% @
-% 
-% Now look at quality-adjusted inputs using the ($ek$)$l$ nesting.
-% 
-% <<UK CES-ekl quality-adjusted>>=
-% naturalCoef(models$UK$adjusted$withE$CES$ekl)
-% @
-% 
-% Table~\ref{tab:lambda_CES-ekl_UK} summarizes the UK Solow residual results with CES and the ($ek$)$l$ nesting.
-% 
-% \begin{table} \caption{UK Solow residual results with CES and ($ek$)$l$ nesting.} 
-% \label{tab:lambda_CES-ekl_UK} 
-%   \begin{center}
-%     \begin{tabular}{r c c} 
-%       \toprule
-%                       & Unadjusted     & Quality-adjusted   \\
-%       \midrule
-%       Without energy  & \Sexpr{naturalCoef(models$UK$unadjusted$noE$CES$kl)$lambda} & \Sexpr{naturalCoef(models$UK$adjusted$noE$CES$kl)$lambda} \\
-%       With energy     & \Sexpr{naturalCoef(models$UK$unadjusted$withE$CES$ekl)$lambda} 
-%                                                             & \Sexpr{naturalCoef(models$UK$adjusted$withE$CES$ekl)$lambda} \\
-%       \bottomrule
-%     \end{tabular}
-%   \end{center}
-% \end{table}
-% 
-% Table~\ref{tab:sse_CES-ekl_UK} shows the $sse$ values for each of these models.
-% 
-% \begin{table} \caption{UK $sse$ with CES and ($ek$)$l$ nesting.} 
-% \label{tab:sse_CES-ekl_UK} 
-%   \begin{center}
-%     \begin{tabular}{r c c} 
-%       \toprule
-%                       & Unadjusted     & Quality-adjusted   \\
-%       \midrule
-%       Without energy  & \Sexpr{EconModels:::sse(models$UK$unadjusted$noE$CES$kl)$sse} & \Sexpr{EconModels:::sse(models$UK$adjusted$noE$CES$kl)$sse} \\
-%       With energy     & \Sexpr{EconModels:::sse(models$UK$unadjusted$withE$CES$ekl)$sse} 
-%                                                             & \Sexpr{EconModels:::sse(models$UK$adjusted$withE$CES$ekl)$sse} \\
-%       \bottomrule
-%     \end{tabular}
-%   \end{center}
-% \end{table}
-% 
-% 
-% Similar to the CES model with ($ek$)$l$ nesting,
-% the CES model with ($ek$)$l$ nesting
-% produces positive Solow residuals in all cases. 
-% Both quality-adjustment and inclusion of energy 
-% decrease the magnitude of the Solow residual.
-
-%' %++++++++++++++++++++++++++++++
-%' \subsection{Dynamic Solow residuals} 
-%' \label{sec:dynamic_solow_residuals}
-%' %++++++++++++++++++++++++++++++
-%' 
-%' <<Dynamic Solow Residuals>>=
-%' # Calculate finite difference approximations of time derivatives for output and all factors of production
-%' dynamicSR <- function(model, id, lag=1, pad="tail"){
-%'   id_list <- strsplit(id, split = "[.]")[[1]]
-%'   energy <- id_list[[3]]
-%'   modelStr <- id_list[[4]]
-%'   
-%'   f <- model$formula
-%'   denom <- summands(f, n=length(summands(f))) # time variable
-%'   nums <- all.vars(f) [1:(length(all.vars(f))-1)] # y, k, l, and e (if present)
-%'   df <- getData(model)[c(denom, nums)] # columns are: iYear, y, k, l, and e (if present)
-%'   
-%'   # Calculate names for the columns of finite difference derivatives
-%'   derivNames <- lapply(1:length(nums), function(i){paste0("d", nums[[i]], ".d", denom)}) %>% unlist
-%'   derivCols <- lapply(1:length(nums), function(i){
-%'     # Calculate finite difference derivative columns
-%'     ediff(df[[i+1]], pad=pad, lag=lag) / ediff(df[[1]], pad=pad, lag=lag)
-%'   }) %>% do.call(cbind, .) %>% as.data.frame
-%'   names(derivCols) <- derivNames  
-%'   df <- cbind(derivCols, df[ , c(nums, denom)]) # puts derivatives first, then raw numbers, then time
-%'   df[["dydtOvery"]] <- 1 / df[[ nums[[1]] ]] * df[[ derivNames[[1]] ]]
-%'   coeffs <- naturalCoef(model)
-%'   df <- cbind(df, coeffs)
-%'   
-%'   if (modelStr == "CD"){
-%'     lambda_fd <- 
-%'       df[["dydtOvery"]] - 
-%'       df[["alpha_1"]] / df[[nums[[2]]]] * df[[derivNames[[2]]]] - 
-%'       df[["alpha_2"]] / df[[nums[[3]]]] * df[[derivNames[[3]]]]
-%'     if (energy == "withE"){
-%'       # Subtract the energy term also
-%'       lambda_fd <- lambda_fd - 
-%'         df[["alpha_3"]] / df[[nums[[4]]]] * df[[derivNames[[4]]]]
-%'     }
-%'     # Fraction of growth explained by Solow Residual
-%'     solowFrac <- lambda_fd / df[["dydtOvery"]]
-%'     # Add to data frame
-%'     df$lambda_fd <- lambda_fd
-%'     df$solowFrac <- solowFrac
-%'     return(df)
-%'   } else if (modelStr == "CES"){
-%'     # Assign nice variable names so that the equations below are easier to read (and debug, and maintain)
-%'     # This code is nest-aware.
-%'     n <- model$nest
-%'     for (i in 1:length(model$nest)){
-%'       df[[paste0("x", i)]] <- df[[ nums[ model$nest[i]+1 ] ]] # GDP is 1st col, add 1 to get to the factors of production
-%'       df[[paste0("dx", i, "dt")]] <- df[[ derivNames[ model$nest[i]+1 ] ]]
-%'     }
-%'     if (energy == "noE"){
-%'       # Calculate terms for the finite-difference Solow residual (lambda_fd)
-%'       df <- df %>% 
-%'         transform(b = delta_1 * x1^(-rho_1) + (1 - delta_1) * x2^(-rho_1)) %>%
-%'         transform(dbdtOverrho1 = -delta_1 * x1^(-(rho_1+1))*dx1dt - (1 - delta_1) * x2^(-(rho_1+1))*dx2dt) %>%
-%'         transform(lambda_fd = dydtOvery + 1/b * dbdtOverrho1) %>%
-%'         transform(solowFrac = lambda_fd / dydtOvery)
-%'       return(df)
-%'     } else if (energy == "withE"){
-%'       df <- df %>% 
-%'         transform(b = delta_1 * x1^(-rho_1) + (1 - delta_1) * x2^(-rho_1)) %>%
-%'         transform(a = delta * b^(rho/rho_1) + (1 - delta) * x3^(-rho)) %>%
-%'         transform(dbdtOverrho1 = -delta_1 * x1^(-(rho_1+1))*dx1dt - (1 - delta_1) * x2^(-(rho_1+1))*dx2dt) %>%
-%'         transform(dadtOverrho = delta * b^(rho/rho_1 - 1) * dbdtOverrho1 - (1 - delta) * x3^(-(rho+1))*dx3dt) %>%
-%'         transform(lambda_fd = dydtOvery + 1/a * dadtOverrho) %>%
-%'         transform(solowFrac = lambda_fd / dydtOvery)
-%'       return(df)
-%'     } else {
-%'       stop (paste("Unknown energy:", energy))
-%'     }
-%'   } else {
-%'     stop(paste("Unknown modelStr", modelStr))
-%'   }
-%' }
-%' 
-%' lag.to.use <- 1 # years
-%' temp_data <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), 
-%'                         f = function(model, id, lag=lag.to.use, pad="tail"){
-%'   df <- dynamicSR(model, id=id, lag=lag, pad=pad)
-%'   id_list <- strsplit(id, split = "[.]")[[1]]
-%'   df$Country <- id_list[[1]]
-%'   df$flavor <- if (id_list[[2]] == "unadjusted") "Unadjusted" else "Quality-adjusted"
-%'   df$energy <- if (id_list[[3]] == "noE") "Without energy" else "With energy"
-%'   df$model <- id_list[[4]]
-%'   df$nest <- if (length(id_list) > 4) id_list[[5]] else NA
-%'   df$Year <- getData(model)[["Year"]]
-%'   return(df)  
-%' }) %>% do.call(plyr::rbind.fill, .)
-%' 
-%' # Get the unadjusted, without-energy Solow residuals and store them in a data frame
-%' sr_unadj_noE <- filter(temp_data, flavor=="Unadjusted" & energy=="Without energy") %>% 
-%'                 select(Year, Country, lambda_fd, model)
-%' colnames(sr_unadj_noE)[colnames(sr_unadj_noE)=="lambda_fd"] <- "sr_unadj_noE"
-%' # Merge to get the unadjusted, without-energy values next to each country, year, and model
-%' solowResiduals <- merge(temp_data, sr_unadj_noE)
-%' 
-%' # Create a column containing ∆lambda_df, the difference between a lambda_df value
-%' # and the lambda_df value in the same year for the unadjusted, no-energy case
-%' solowResiduals[["Dlambda_fd"]] <- abs(solowResiduals[["lambda_fd"]]) - abs(solowResiduals[["sr_unadj_noE"]])
-%' 
-%' # Relevel factors before plotting
-%' solowResiduals$Country <- relevelFactor(as.factor(solowResiduals$Country), c("PT", "UK"))
-%' solowResiduals$flavor <- relevelFactor(as.factor(solowResiduals$flavor), c("Unadjusted", "Quality-adjusted"))
-%' solowResiduals$energy <- relevelFactor(as.factor(solowResiduals$energy), c("Without energy", "With energy"))
-%' solowResiduals$nest <- relevelFactor(as.factor(solowResiduals$nest), c("kl", "kle", "lek", "ekl"))
-%' 
-%' # Make data viewing easier
-%' solowResiduals <- arrange(solowResiduals, Country, model, flavor, energy, nest)
-%' @
-%' 
-%' <<DynamicSR_Graph>>=
-%' dynamicSRGraph <- function(data){
-%' ggplot(data=data) +
-%'   geom_line(data=filter(data, energy=="Without energy"), mapping=aes(x=Year, y=dydtOvery)) +
-%'   geom_line(mapping=aes(x=Year, y=lambda_fd, linetype=energy)) +
-%'   scale_linetype_manual(values=c(2,3), name="") +
-%'   facet_grid(Country ~ flavor) +
-%'   scale_x_continuous(breaks=c(1960, 1980, 2000)) +
-%'   xlab("") + 
-%'   ylab(expression(lambda[ij])) +
-%'   xy_theme()  
-%' }
-%' @
-%' 
-%' ``Dynamic'' Solow residuals~($\lambda_{i,j}$) can be calculated 
-%' for the Cobb-Douglas and CES models
-%' as shown in Appendices~\ref{sec:dynamic_sr_CD} and~\ref{sec:dynamic_sr_CES},
-%' respectively.
-%' 
-%' Figure~\ref{fig:DynamicSR_CD_Graph} shows the evolution 
-%' of the Solow residual~($\lambda_{i,j}$) over time
-%' as calculated by Equation~\ref{eq:lambdaij} 
-%' with the timespan for finite differences ($t_j - t_i$) set to 
-%' \Sexpr{lag.to.use}~\Sexpr{if (lag.to.use == 1) "year" else "years"}.
-%' %
-%' <<DynamicSR_CD_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residuals for the Cobb-Douglas model.
-Dashed lines are $\\lambda$ values.
-Solid lines are $\\frac{1}{y}\\frac{\\mathrm{d} y}{\\mathrm{d} t}$.">>=
-%' dynamicSRGraph(filter(solowResiduals, model=="CD"))
-%' @
-%' %
-%' <<DynamicSR_CESkle_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residuals for the CES model with ($kl$)$e$ nesting.
-Dashed lines are $\\lambda$ values.
-Solid lines are $\\frac{1}{y}\\frac{\\mathrm{d} y}{\\mathrm{d} t}$.">>=
-%' dynamicSRGraph(filter(solowResiduals, model=="CES" & (nest=="kle" | nest=="kl")))
-%' @
-%' %
-%' <<DynamicSR_CESlek_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residuals for the CES model with ($le$)$k$ nesting.
-Dashed lines are $\\lambda$ values.
-Solid lines are $\\frac{1}{y}\\frac{\\mathrm{d} y}{\\mathrm{d} t}$.">>=
-%' dynamicSRGraph(filter(solowResiduals, model=="CES" & (nest=="lek" | nest=="kl")))
-%' @
-%' %
-%' <<DynamicSR_CESekl_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residuals for the CES model with ($ek$)$l$ nesting.
-Dashed lines are $\\lambda$ values.
-Solid lines are $\\frac{1}{y}\\frac{\\mathrm{d} y}{\\mathrm{d} t}$.">>=
-%' dynamicSRGraph(filter(solowResiduals, model=="CES" & (nest=="ekl" | nest=="kl")))
-%' @
-
-%' %++++++++++++++++++++++++++++++
-%' \subsection{Does quality-adjusting the factors of production 
-%'             decrease fitting residuals and/or the dynamic Solow residual?} 
-%' \label{sec:quality_adj_energy_and_dynamic_solow_residual}
-%' %++++++++++++++++++++++++++++++
-%' 
-%' <<SR and R trajectory data>>=
-%' traj.data <- merge(solowResiduals[c("Country", "Year", "model", "flavor", "energy", "nest", "Dlambda_fd")], 
-%'                    fitted_and_resid_data[c("Country", "Year", "model", "flavor", "energy", "nest", "Dr")]) %>%
-%'                    arrange(Country, model, flavor, energy, nest)
-%' traj.data.stats <- traj.data %>% 
-%'   group_by(model, Country, flavor, energy, nest) %>%
-%'   summarise(Dlambda_fd.mean = mean(Dlambda_fd, na.rm=TRUE), Dr.mean = mean(Dr))
-%' 
-%' ############################################
-%' # Dlambda_fd.p <- traj.data %>% 
-%' #   group_by(model, Country, flavor, energy, nest) %>% 
-%' #   select(Dlambda_fd) %>%
-%' #   t.test(., alternative="less")[["p.value"]]
-%' ############################################  
-%' @
-%' 
-%' <<SR and R trajectory plot function>>=
-%' residualsTrajGraph <- function(data){
-%'   plot <- ggplot(data=data) + 
-%'     geom_point(mapping=aes(x=Dr, y=Dlambda_fd, color=energy)) + 
-%'     facet_grid(Country ~ flavor) +
-%'     xlab(expression(Delta*r[i])) +
-%'     ylab(expression(Delta*lambda[ij])) +
-%'     xy_theme() + 
-%'     theme(legend.title=element_blank())
-%'   return(plot)
-%' }
-%' @
-%' 
-%' We can test our hypothesis that quality-adjusting the factors of production
-%' and including energy will reduce the Solow residuals~($\lambda$)
-%' and the fitting residuals~($r$) by plotting
-%' $\Delta \lambda_i$ vs. $\Delta r_i$, where
-%' %
-%' \begin{equation} \label{eq:delta_lambda_i}
-%'   \Delta \lambda_i \equiv \left| \lambda_i \right| - \left| \lambda_{i, \, Unadjusted, \, Without \, energy} \right|
-%' \end{equation}
-%' %
-%' and
-%' %
-%' \begin{equation} \label{eq:delta_r}
-%'   \Delta r_i \equiv \left| r_i \right| - \left| r_{i, \,Unadjusted, \, Without \, energy} \right|.
-%' \end{equation}
-%' %
-%' If most of the points fall in the lower-left quadrant of a graph, 
-%' we can conclude that both Solow residual~($\lambda$) and
-%' fitting residual~($r$) have decreased due to either 
-%' quality-adjustment of the factors of production or 
-%' including energy.
-%' 
-%' Figure~\ref{fig:Solow_residual_trajectories_CD} indicates that
-%' for the Cobb-Douglas model, 
-%' neither 
-%' quality-adjusting the factors of production
-%' nor including energy 
-%' consistently reduces
-%' the Solow residual or the fitting residual.
-%' 
-%' <<Solow_residual_trajectories_CD, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residual and fitting residual trajectories relative to the Unadjusted, Without-energy condition for the Cobb-Douglas model.">>=
-%' residualsTrajGraph(filter(traj.data, model=="CD"))
-%' @
-%' 
-%' We can also calculate the average values for $\Delta \lambda_{i,j}$ and $\Delta r_{i}$ 
-%' as shown in Table~\ref{tab:Trajectory_Means_CD}.
-%' %
-%' <<Trajectory_Means_CD, results="asis">>=
-%' myXTable(data = filter(traj.data.stats, model=="CD") %>% select(-nest), 
-%'          caption = "Average $\\Delta\\lambda$ and $\\Delta r$ for Cobb-Douglas models.",
-%'          label=paste0("tab:", opts_current$get("label")),
-%'          digits=6)
-%' @
-%' %
-%' The following tables and figures show the same analysis for the CES model.
-%' %
-%' <<Solow_residual_trajectories_CESkle, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residual and fitting residual trajectories relative to the Unadjusted, Without-energy condition for the CES model with ($kl$)$e$ nesting.">>=
-%' residualsTrajGraph(filter(traj.data, model=="CES" & (nest=="kl" | nest=="kle")))
-%' @
-%' %
-%' <<Trajectory_Means_CESkle, results="asis">>=
-%' myXTable(data = filter(traj.data.stats, model=="CES" & (nest=="kl" | nest=="kle")), 
-%'          caption = "Average $\\Delta\\lambda$ and $\\Delta r$ for CES models with ($kl$)$e$ nesting.",
-%'          label=paste0("tab:", opts_current$get("label")),
-%'          digits=6)
-%' @
-%' 
-%' <<Solow_residual_trajectories_CESlek, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residual and fitting residual trajectories relative to the Unadjusted, Without-energy condition for the CES model with ($le$)$k$ nesting.">>=
-%' residualsTrajGraph(filter(traj.data, model=="CES" & (nest=="kl" | nest=="lek")))
-%' @
-%' 
-%' <<Trajectory_Means_CESlek, results="asis">>=
-%' myXTable(data = filter(traj.data.stats, model=="CES" & (nest=="kl" | nest=="lek")), 
-%'          caption = "Average $\\Delta\\lambda$ and $\\Delta r$ for CES models with ($le$)$k$ nesting.",
-%'          label=paste0("tab:", opts_current$get("label")),
-%'          digits=6)
-%' @
-%' 
-%' <<Solow_residual_trajectories_CESekl, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residual and fitting residual trajectories relative to the Unadjusted, Without-energy condition for the CES model with ($ek$)$l$ nesting.">>=
-%' residualsTrajGraph(filter(traj.data, model=="CES" & (nest=="kl" | nest=="ekl")))
-%' @
-%' 
-%' <<Trajectory_Means_CESekl, results="asis">>=
-%' myXTable(data = filter(traj.data.stats, model=="CES" & (nest=="kl" | nest=="ekl")), 
-%'          caption = "Average $\\Delta\\lambda$ and $\\Delta r$ for CES models with ($ek$)$l$ nesting.",
-%'          label=paste0("tab:", opts_current$get("label")),
-%'          digits=6)
-%' @
-%'
+<<DSRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta mse$) for the CES modles relative to the exponential-only model.">>=
+ggplot() +
+  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=Dmse, y=Dlambda, color=energy, size=cst, shape=nest)) +
+  scale_size_manual(values=c(2,3.5)) +
+  scale_shape_manual(values=c(16,17,18,15)) +
+  facet_grid(Country ~ flavor) +
+  xlab(expression(Delta * mse)) + 
+  scale_x_continuous(breaks=seq(-0.005, 0, 0.005)) +  
+  ylab(expression(Delta * lambda)) +
+  xy_theme() +
+  theme(legend.title=element_blank())
+@
+%
 

### 2015-07-09 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Editing the EcolEcon_2015 paper.

@@
 
-\title{Effect of quality-adjusted production function inputs}
+\title{Energy and the CES production function}
 
@@
 \author[IST]{Jo\~{a}o dos Santos}
+\author[CalvinEngr]{Matthew Kuperus Heun\corref{cor1}}
 \author[Leeds]{Paul Brockway}
-\author[CalvinEngr]{Matthew Kuperus Heun\corref{cor1}}
 \ead{mkh2@calvin.edu}
@@
 \author[IST]{Tiago Domingos}
-\author[Leeds]{Julia Steinberger}
+\author[CalvinMath]{Randall Pruim}
 
@@
 \address[CalvinEngr]{Engineering Department, Calvin College, Grand Rapids, MI 49546, USA}
+\address[CalvinMath]{Mathematics \& Statistics Department, Calvin College, Grand Rapids, MI 49546, USA}
 \cortext[cor1]{Corresponding author}
@@
 %% keywords here, in the form: keyword \sep keyword
-economic growth \sep exergy \sep energy \sep Cobb-Douglas \sep CES
+economic growth \sep exergy \sep energy \sep CES
 %% MSC codes here, in the form: \MSC code \sep code
@@
 
-In this paper, we assess two prominent energy-augmented production functions 
-that appear in the literature: 
-Cobb-Douglas (CD) and
+In this paper, we assess a prominent energy-augmented production function:
 Constant Elasticity of Substitution (CES).
-These production functions are assessed relative to 
+The CES model is assessed relative to 
 a model of exponential growth only.
@@
 
-%------------------------------
-\subsubsection{Cobb-Douglas Production Function} 
-\label{sec:CDe}
-%------------------------------
-
 The Cobb-Douglas production function can be expressed as
@@
 where
+
+Constant returns to scale are represented by the constraint
+$\alpha_1 + \alpha_2 = 1$.
+
+The capital-labor Cobb-Douglas production function shown in Equation~\ref{eq:CD}
+can be augmented to include an energy term:
+%
+\begin{equation} \label{eq:CDe}
+  y = \theta A k^{\alpha_1} l^{\alpha_2} e^{\alpha_3} \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)} \; ,
+\end{equation}
+%
+where $e \equiv E/E_0$, and $E$ is in units of energy per time, typically TJ/year.
+The energy-augmented Cobb-Douglas production function 
+is often assumed to have constant returns to scale for the three factors 
+of production: $\alpha_1 + \alpha_2 + \alpha_3 = 1$.
+The term $A$ is known as total factor productivity,
+and $\lambda$ is the Solow residual.
+
+%------------------------------
+\subsubsection{Constant Elasticity of Substitution Production Function (CES)} 
+\label{sec:CES}
+%------------------------------
+
+The energy-augmented 
+Constant Elasticity of Substitution (CES) production function%
+  \footnote{
+  We use the The \texttt{R} 
+  % \citep{R} 
+  package \texttt{micEconCES} 
+  % \citep{Henningsen:2011td} 
+  to estimate the CES production function.
+  }
+can be given as
+%
+\begin{equation} \label{eq:CESgeneric}
+  y = \gamma \: A \: \left\{\delta \left[\delta_1 x_1^{-\rho_1} 
+      + (1-\delta_1)x_2^{-\rho_1} \right]^{\rho/\rho_1} 
+      + (1-\delta) x_3^{-\rho} \right\}^{-1/\rho}; 
+      A \equiv \mathrm{e}^{\lambda (t-t_0)},
+\end{equation}
+%
+where
 $y \equiv Y/Y_{0}$,
-$\theta$ is a scale parameter,
+$\gamma$ is a scale parameter,
 e is the base of the natural logarithm, 
-$\lambda$ is represents the pace of technological progress,
+$\lambda$ is the Solow residual (often thougth to represent the pace of technological progress),
 $t$ (time) is measured in years,
+$x_1$, $x_2$, and $x_3$ are factors of production
+and permutations of capital~($k$), labor~($l$), and energy~($e$),
 $k \equiv K/K_{0}$, 
@@
   }
-Constant returns to scale are represented by the constraint
-$\alpha_1 + \alpha_2 = 1$.
-
-The capital-labor Cobb-Douglas production function shown in Equation~\ref{eq:CD}
-can be augmented to include an energy term:
-%
-\begin{equation} \label{eq:CDe}
-  y = \theta A k^{\alpha_1} l^{\alpha_2} e^{\alpha_3} \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)} \; ,
-\end{equation}
-%
-where $e \equiv E/E_0$, and $E$ is in units of energy per time, typically TJ/year.
-The energy-augmented Cobb-Douglas production function 
-is often assumed to have constant returns to scale for the three factors 
-of production: $\alpha_1 + \alpha_2 + \alpha_3 = 1$.
-The term $A$ is known as total factor productivity,
-and $\lambda$ is the Solow residual.
-
-%------------------------------
-\subsubsection{Constant Elasticity of Substitution Production Function (CES)} 
-\label{sec:CES}
-%------------------------------
-
-Other energy economists use an energy-augmented 
-Constant Elasticity of Substitution (CES) production function to 
-describe economic growth. The \texttt{R} 
-% \citep{R} 
-package \texttt{micEconCES} 
-% \citep{Henningsen:2011td} 
-estimates CES production 
-functions of the following form
-%
-\begin{equation} \label{eq:CESgeneric}
-  y = \gamma \: A \: \left\{\delta \left[\delta_1 x_1^{-\rho_1} 
-      + (1-\delta_1)x_2^{-\rho_1} \right]^{\rho/\rho_1} 
-      + (1-\delta) x_3^{-\rho} \right\}^{-1/\rho}; 
-      A \equiv \mathrm{e}^{\lambda (t-t_0)},
-\end{equation}
-%
-where $x_1$, $x_2$, and $x_3$ are factors of production
-and permutations of capital~($k$), labor~($l$), and energy~($e$).
-
 The CES model without energy is given in Equation~\ref{eq:CESkl}.
@@
 %
-
 In the CES production function, 
@@
 
+For the CES model, factors shares~($\alpha_1$, $\alpha_2$, and $\alpha_3$) are calculated by
+$\alpha_1 = \delta_1$, $\alpha_2 = 1 - \delta_1$, and $\alpha_3 = 0$ 
+for the CES model with two factors of production
+and by 
+$\alpha_1 = \delta \delta_1$, $\alpha_2 = \delta(1 - \delta_1)$, and $\alpha_3 = 1 - \delta$
+for the CES model with three factors of production and the ($kl$)$e$ nesting.
+The values of $\alpha_1$, $\alpha_2$, and $\alpha_3$ are interpreted as
+factor shares for capital, labor, and energy, respectively,
+as shown in Table \ref{tab:CES_abg_equations}.
+
+\begin{table} \caption{Equations for $\alpha_1$, $\alpha_2$, and $\alpha_3$ 
+                        (factor shares for capital, labor, and energy, respectively)
+                        for the various CES nestings.} 
+\label{tab:CES_abg_equations} 
+  \begin{center}
+    \begin{tabular}{c c c c c} 
+      \toprule
+      Nesting         & \texttt{nest}     & $\alpha_1$              & $\alpha_2$              & $\alpha_3$       \\
+      \midrule
+      ($kl$) + ()     & \texttt{c(1,2)}   & $\delta_1$              & $1 - \delta_1$          & 0          \\
+      ($kl$) + ($e$)  & \texttt{c(1,2,3)} & $\delta \delta_1$       & $\delta (1 - \delta_1)$ & $1 - \delta$ \\   
+      ($le$) + ($k$)  & \texttt{c(2,3,1)} & $1 - \delta$            & $\delta \delta_1$       & $\delta (1 - \delta_1)$ \\
+      ($ek$) + ($l$)  & \texttt{c(3,1,2)} & $\delta (1 - \delta_1)$ & $1 - \delta$            & $\delta \delta_1$ \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+\end{table}
+
 %------------------------------
@@
 %
-The reference model is a degenerate case of the Cobb-Douglas production function
-wherein the constant returns to scale constraint is not respected,
-because all factor shares are zero~($\alpha_1 = \alpha_2 = \alpha_3 = 0$).
-
-We expect that the reference model will have a larger fitted Solow residual term than
-the Cobb-Douglas and CES models, because no factors of production are
+We expect that the reference model
+will have a larger fitted Solow residual term than
+the CES model, because no factors of production are
 included in the reference model to drive economic growth.
 Indeed, in the reference model, 
-all economics growth is attributed to the Solow residual.
+all economic growth is attributed to the Solow residual~($\lambda$).
 
 In contrast, it is not necessarily true that 
-Cobb-Douglas and CES models 
-will exhibit lower $mse$ than the reference model
+CES models will exhibit lower $mse$ than the reference model
 shown in Equation~\ref{eq:exponential-only-model}.
-The Cobb-Douglas and CES models have more fitting parameters,
-but they incorporate the factors of production
+The CES model has more fitting parameters,
+but it incorporates the factors of production
 at constant returns to scale. 
 The reference model has $\alpha_1 + \alpha_2 + \alpha_3 = 0$,
-whereas our implementations of both the Cobb-Douglas and CES models
-requires constant returns to scale, $\alpha_1 + \alpha_2 + \alpha_3 = 1$.
+whereas our implementation of the CES model~(Equation~\ref{eq:CESgeneric})
+assumes constant returns to scale.
 Thus, if the factors of production ($\alpha_1$, $\alpha_2$, and $\alpha_3$) 
@@
 Model fitting provides estimates for all parameters in the model.
-
-For the CES model, factors shares~($\alpha_1$, $\alpha_2$, and $\alpha_3$) are calculated by
-$\alpha_1 = \delta_1$, $\alpha_2 = 1 - \delta_1$, and $\alpha_3 = 0$ 
-for the CES model with two factors of production
-and by 
-$\alpha_1 = \delta \delta_1$, $\alpha_2 = \delta(1 - \delta_1)$, and $\alpha_3 = 1 - \delta$
-for the CES model with three factors of production and the ($kl$)$e$ nesting.
-The values of $\alpha_1$, $\alpha_2$, and $\alpha_3$ are interpreted as
-factor shares for capital, labor, and energy, respectively,
-as shown in Table \ref{tab:CES_abg_equations}, 
-assuming factors of production are specified in the fitting \texttt{formula} as
-\texttt{y~$\sim$~k~+~l~+~e~+~time}.
-
-\begin{table} \caption{Equations for $\alpha_1$, $\alpha_2$, and $\alpha_3$ 
-                        (factor shares for capital, labor, and energy, respectively)
-                        for the various CES nestings, 
-                        provided that the \texttt{formula} is specified as \texttt{y~$\sim$~k~+~l~+~e~+~time}.} 
-\label{tab:CES_abg_equations} 
-  \begin{center}
-    \begin{tabular}{c c c c c} 
-      \toprule
-      Nesting         & \texttt{nest}     & $\alpha_1$              & $\alpha_2$              & $\alpha_3$       \\
-      \midrule
-      ($kl$) + ()     & \texttt{c(1,2)}   & $\delta_1$              & $1 - \delta_1$          & 0          \\
-      ($kl$) + ($e$)  & \texttt{c(1,2,3)} & $\delta \delta_1$       & $\delta (1 - \delta_1)$ & $1 - \delta$ \\   
-      ($le$) + ($k$)  & \texttt{c(2,3,1)} & $1 - \delta$            & $\delta \delta_1$       & $\delta (1 - \delta_1)$ \\
-      ($ek$) + ($l$)  & \texttt{c(3,1,2)} & $\delta (1 - \delta_1)$ & $1 - \delta$            & $\delta \delta_1$ \\
-      \bottomrule
-    \end{tabular}
-  \end{center}
-\end{table}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Cobb-Douglas results} 
+\section{Cobb-Douglas Graveyard} 
 \label{sec:cd_results}
@@
 
+%------------------------------
+\subsubsection{Cobb-Douglas Production Function} 
+\label{sec:CDe}
+%------------------------------
+
+The Cobb-Douglas production function can be expressed as
+%
+\begin{equation} \label{eq:CD}
+  y = \theta A k^{\alpha_1} l^{\alpha_2} \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)} \; ,
+\end{equation}
+%
+where 
+$y \equiv Y/Y_{0}$,
+$\theta$ is a scale parameter,
+e is the base of the natural logarithm, 
+$\lambda$ is represents the pace of technological progress,
+$t$ (time) is measured in years,
+$k \equiv K/K_{0}$, 
+$l \equiv L/L_{0}$, 
+$Y$ (economic output) is represented by GDP, 
+$K$ (capital) is expressed in currency units, 
+$L$ (labor) is expressed in workers or work-hours/year, and
+the 0 subscript indicates values at an initial year.%
+  \footnote{Dimensionless, indexed quantities are represented by 
+  lower-case symbols 
+  ($y$, $k$, $l$, $e$, $q$, $x$, and $u$), and dimensional 
+  quantities are represented by upper-case symbols 
+  ($Y$, $K$, $L$, $E$, $Q$, $X$, and $U$). 
+  Model parameters are represented by Greek letters
+  ($\alpha_1$, $\alpha_2$, $\lambda$, $\theta$).
+  }
+Constant returns to scale are represented by the constraint
+$\alpha_1 + \alpha_2 = 1$.
+
+The capital-labor Cobb-Douglas production function shown in Equation~\ref{eq:CD}
+can be augmented to include an energy term:
+%
+\begin{equation} \label{eq:CDe}
+  y = \theta A k^{\alpha_1} l^{\alpha_2} e^{\alpha_3} \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)} \; ,
+\end{equation}
+%
+where $e \equiv E/E_0$, and $E$ is in units of energy per time, typically TJ/year.
+The energy-augmented Cobb-Douglas production function 
+is often assumed to have constant returns to scale for the three factors 
+of production: $\alpha_1 + \alpha_2 + \alpha_3 = 1$.
+The term $A$ is known as total factor productivity,
+and $\lambda$ is the Solow residual. 
 %

### 2015-07-09 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Edited the alpha table.

@@
   \begin{center}
-    \begin{tabular}{c c c c c} 
+    \begin{tabular}{c c c c} 
       \toprule
-      Nesting         & \texttt{nest}     & $\alpha_1$              & $\alpha_2$              & $\alpha_3$       \\
+      Nesting    & $\alpha_1$              & $\alpha_2$              & $\alpha_3$       \\
       \midrule
-      ($kl$) + ()     & \texttt{c(1,2)}   & $\delta_1$              & $1 - \delta_1$          & 0          \\
-      ($kl$) + ($e$)  & \texttt{c(1,2,3)} & $\delta \delta_1$       & $\delta (1 - \delta_1)$ & $1 - \delta$ \\   
-      ($le$) + ($k$)  & \texttt{c(2,3,1)} & $1 - \delta$            & $\delta \delta_1$       & $\delta (1 - \delta_1)$ \\
-      ($ek$) + ($l$)  & \texttt{c(3,1,2)} & $\delta (1 - \delta_1)$ & $1 - \delta$            & $\delta \delta_1$ \\
+      ($kl$) \;  & $\delta_1$              & $1 - \delta_1$          & 0          \\
+      ($kl$)$e$  & $\delta \delta_1$       & $\delta (1 - \delta_1)$ & $1 - \delta$ \\   
+      ($le$)$k$  & $1 - \delta$            & $\delta \delta_1$       & $\delta (1 - \delta_1)$ \\
+      ($ek$)$l$  & $\delta (1 - \delta_1)$ & $1 - \delta$            & $\delta \delta_1$ \\
       \bottomrule
@@
 The reference model has $\alpha_1 + \alpha_2 + \alpha_3 = 0$,
-whereas our implementation of the CES model~(Equation~\ref{eq:CESgeneric})
-assumes constant returns to scale.
-Thus, if the factors of production ($\alpha_1$, $\alpha_2$, and $\alpha_3$) 
-are poorly correlated to output ($y$),
+whereas the CES model~(Equation~\ref{eq:CESgeneric})
+implicitly assumes constant returns to scale.
+Thus, if the factors of production~($\alpha_1$, $\alpha_2$, and $\alpha_3$) 
+are poorly correlated to output~($y$),
 the constant returns to scale constraint may cause higher $mse$ for
-the Cobb-Douglas or CES models relative to the reference model.
-
-In the sections that follow, 
-we assess the Cobb-Douglas and CES models relative to the reference model
-in terms of goodness of both goodness of fit~($mse$) and Solow residual~($\lambda$).
+the CES model relative to the reference model.
 

### 2015-07-10 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Improving lambda vs. mse graph.

@@
 
+<<percSRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Solow Residuals~($\\lambda$) and mean squared error~($mse$).
+$\\lambda$ and $mse$ values for the reference (exponential-only) model are shown as gridlines.">>=
+ggplot() +
+  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=mse, y=lambda, color=energy, size=cst, shape=nest)) +
+  scale_size_manual(values=c(2,3.5)) +
+  scale_shape_manual(values=c(16,17,18,15)) +
+  facet_grid(Country ~ flavor) +
+  scale_x_continuous(breaks=seq(0, 0.02, 0.01), limits=c(0, 0.02)) +  
+  ylab(expression(lambda)) +
+  scale_y_continuous(breaks=seq(0, 0.04, 0.01), limits=c(0, 0.04)) +  
+  xy_theme() +
+  theme(legend.title=element_blank())
+@
+
 %------------------------------

### 2015-07-10 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Add vertical and horizontal lines for exp model.

--- 2015-07-09 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
@@
 
+<<percSRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Solow Residuals~($\\lambda$) and mean squared error~($mse$).
+$\\lambda$ and $mse$ values for the reference (exponential-only) model are shown as gridlines.">>=
+ggplot() +
+  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=mse, y=lambda, color=energy, size=cst, shape=nest)) +
+  geom_vline(aes(xintercept = mse), filter(AllCoeffs, model=="exp") %>% select(Country, mse)) +
+  geom_hline(aes(yintercept = lambda), filter(AllCoeffs, model=="exp") %>% select(Country, lambda)) +
+  scale_size_manual(values=c(2,3.5)) +
+  scale_shape_manual(values=c(16,17,18,15)) +
+  facet_grid(Country ~ flavor) +
+  scale_x_continuous(breaks=seq(0, 0.02, 0.01), limits=c(0, 0.02)) +  
+  ylab(expression(lambda)) +
+  scale_y_continuous(breaks=seq(0, 0.04, 0.01), limits=c(0, 0.04)) +  
+  xy_theme() +
+  theme(legend.title=element_blank())
+@
+
 %------------------------------

### 2015-07-10 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Improving readability of lambda vs. mse graph.

--- 2015-07-09 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
@@
 
+<<SRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Solow Residuals~($\\lambda$) and mean squared error~($mse$).
+$\\lambda$ and $mse$ values for the reference (exponential-only) model are shown as gridlines.">>=
+ggplot() +
+  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=mse, y=lambda, color=energy, size=cst, shape=nest)) +
+  geom_vline(aes(xintercept = mse), filter(AllCoeffs, model=="exp") %>% select(Country, mse), colour="gray50", size=0.1) +
+  geom_hline(aes(yintercept = lambda), filter(AllCoeffs, model=="exp") %>% select(Country, lambda), colour="gray50", size=0.1) +
+  scale_size_manual(values=c(2,4)) +
+  scale_shape_manual(values=c(1,0,3,4)) + # 16,17,18,15
+  facet_grid(Country ~ flavor) +
+  # scale_x_continuous(breaks=seq(0, 0.02, 0.01), limits=c(0, 0.02)) +  
+  ylab(expression(lambda)) +
+  # scale_y_continuous(breaks=seq(0, 0.04, 0.01), limits=c(0, 0.04)) +  
+  xy_theme() +
+  theme(legend.title=element_blank())
+@
+
 %------------------------------

### 2015-07-13 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Change from require to library.

@@
 <<setup, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE>>=
-require(EconData)
-require(EconModels)
-require(dplyr)
-require(reshape2)
-require(ggplot2)
-require(mosaic)
-require(xtable)
-require(knitr)
-require(texreg)
+library(EconData)
+library(EconModels)
+library(dplyr)
+library(reshape2)
+library(ggplot2)
+library(mosaic)
+library(xtable)
+library(knitr)
+library(texreg)
 

### 2015-07-13 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Now using booktabs for xtable.

@@
         include.rownames=FALSE, 
-        math.style.negative=TRUE)
+        math.style.negative=TRUE, 
+        booktabs=TRUE)
 }

### 2015-07-30 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Minor edits.

@@
 The following subsections describe each.
-
-The Cobb-Douglas production function can be expressed as
-%
-\begin{equation} \label{eq:CD}
-  y = \theta A k^{\alpha_1} l^{\alpha_2} \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)} \; ,
-\end{equation}
-%
-where
-
-Constant returns to scale are represented by the constraint
-$\alpha_1 + \alpha_2 = 1$.
-
-The capital-labor Cobb-Douglas production function shown in Equation~\ref{eq:CD}
-can be augmented to include an energy term:
-%
-\begin{equation} \label{eq:CDe}
-  y = \theta A k^{\alpha_1} l^{\alpha_2} e^{\alpha_3} \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)} \; ,
-\end{equation}
-%
-where $e \equiv E/E_0$, and $E$ is in units of energy per time, typically TJ/year.
-The energy-augmented Cobb-Douglas production function 
-is often assumed to have constant returns to scale for the three factors 
-of production: $\alpha_1 + \alpha_2 + \alpha_3 = 1$.
-The term $A$ is known as total factor productivity,
-and $\lambda$ is the Solow residual.
 
@@
                          variable.name = "variable")
+  bar_chart_data$variable <- plyr::mapvalues(bar_chart_data$variable, 
+                                       from=c("alpha_1", "alpha_2", "alpha_3"), 
+                                       to=c("alpha_k", "alpha_l", "alpha_e"))
+
   # Define the color palette (see http://www.cookbook-r.com/Graphs/Colors_(ggplot2))
@@
 %------------------------------
+
+The Cobb-Douglas production function can be expressed as
+%
+\begin{equation} \label{eq:CD}
+  y = \theta A k^{\alpha_1} l^{\alpha_2} \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)} \; ,
+\end{equation}
+%
+where
+
+Constant returns to scale are represented by the constraint
+$\alpha_1 + \alpha_2 = 1$.
+
+The capital-labor Cobb-Douglas production function shown in Equation~\ref{eq:CD}
+can be augmented to include an energy term:
+%
+\begin{equation} \label{eq:CDe}
+  y = \theta A k^{\alpha_1} l^{\alpha_2} e^{\alpha_3} \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)} \; ,
+\end{equation}
+%
+where $e \equiv E/E_0$, and $E$ is in units of energy per time, typically TJ/year.
+The energy-augmented Cobb-Douglas production function 
+is often assumed to have constant returns to scale for the three factors 
+of production: $\alpha_1 + \alpha_2 + \alpha_3 = 1$.
+The term $A$ is known as total factor productivity,
+and $\lambda$ is the Solow residual.
 

### 2015-07-30 Articles/Brockway_Rebound_2015/Brockway_2015.Rnw
New files for Brockway analysis.

--- 2015-07-13 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
@@
 
-\journal{Ecological Economics}
+\journal{Unknown}
 
@@
 library(ggplot2)
-library(mosaic)
-library(xtable)
+# library(mosaic)
+# library(xtable)
 library(knitr)
-library(texreg)
+# library(texreg)
 
@@
 )
-
-# This function is used in many places below.
-myXTable <- function(data, caption, label, digits=2){
-  table <- xtable(data, caption=caption, label=label, digits=digits)
-  print(table, 
-        caption.placement="top", 
-        size="\\tiny", 
-        include.rownames=FALSE, 
-        math.style.negative=TRUE)
-}
 @
@@
 
-\title{Energy and the CES production function}
+\title{CES analysis for Paul Brockway rebound paper}
 
@@
 
-\author[IST]{Jo\~{a}o dos Santos}
 \author[CalvinEngr]{Matthew Kuperus Heun\corref{cor1}}
-\author[Leeds]{Paul Brockway}
 \ead{mkh2@calvin.edu}
-\author[Leeds]{Marco Sekai}
-\author[IST]{Tiago Domingos}
-\author[CalvinMath]{Randall Pruim}
 
-\address[IST]{IST, Lisbon, Portugal}
-\address[Leeds]{Leeds University, Leeds, UK}
 \address[CalvinEngr]{Engineering Department, Calvin College, Grand Rapids, MI 49546, USA}
-\address[CalvinMath]{Mathematics \& Statistics Department, Calvin College, Grand Rapids, MI 49546, USA}
 \cortext[cor1]{Corresponding author}
@@
 %% Text of abstract
-**** Add abstract ****
+This document provides an analysis of the CES production function
+for UK, US, and CN using quality-adjusted factors of production
+and the ($kl$)$e$ nesting.
 \end{abstract}
@@
 
-This is a study of the effects of quality-adjusted production function inputs
-on the importance of energy in the production function.
+This is a study of the effects of the CES production function 
+using quality-adjusted factors of production
+and the ($kl$)$e$ nesting.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Coordinates of Analysis} 
-\label{sec:Coordinates}
+\section{CES production function} 
+\label{sec:ces}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-This section describes the coordinates of analysis and briefly reviews 
-literature related to each.
-
-%++++++++++++++++++++++++++++++
-\subsection{Mathematical Forms of the Energy-augmented Production Function} 
-\label{sec:Prod_Func_Forms}
-%++++++++++++++++++++++++++++++
-
-In this paper, we assess a prominent energy-augmented production function:
-Constant Elasticity of Substitution (CES).
-The CES model is assessed relative to 
-a model of exponential growth only.
-The following subsections describe each.
-
-The Cobb-Douglas production function can be expressed as
-%
-\begin{equation} \label{eq:CD}
-  y = \theta A k^{\alpha_1} l^{\alpha_2} \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)} \; ,
-\end{equation}
-%
-where
-
-Constant returns to scale are represented by the constraint
-$\alpha_1 + \alpha_2 = 1$.
-
-The capital-labor Cobb-Douglas production function shown in Equation~\ref{eq:CD}
-can be augmented to include an energy term:
-%
-\begin{equation} \label{eq:CDe}
-  y = \theta A k^{\alpha_1} l^{\alpha_2} e^{\alpha_3} \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)} \; ,
-\end{equation}
-%
-where $e \equiv E/E_0$, and $E$ is in units of energy per time, typically TJ/year.
-The energy-augmented Cobb-Douglas production function 
-is often assumed to have constant returns to scale for the three factors 
-of production: $\alpha_1 + \alpha_2 + \alpha_3 = 1$.
-The term $A$ is known as total factor productivity,
-and $\lambda$ is the Solow residual.
-
-%------------------------------
-\subsubsection{Constant Elasticity of Substitution Production Function (CES)} 
-\label{sec:CES}
-%------------------------------
-
-The energy-augmented 
-Constant Elasticity of Substitution (CES) production function%
-  \footnote{
-  We use the The \texttt{R} 
-  % \citep{R} 
-  package \texttt{micEconCES} 
-  % \citep{Henningsen:2011td} 
-  to estimate the CES production function.
-  }
-can be given as
-%
-\begin{equation} \label{eq:CESgeneric}
-  y = \gamma \: A \: \left\{\delta \left[\delta_1 x_1^{-\rho_1} 
-      + (1-\delta_1)x_2^{-\rho_1} \right]^{\rho/\rho_1} 
-      + (1-\delta) x_3^{-\rho} \right\}^{-1/\rho}; 
-      A \equiv \mathrm{e}^{\lambda (t-t_0)},
-\end{equation}
-%
-where
-$y \equiv Y/Y_{0}$,
-$\gamma$ is a scale parameter,
-e is the base of the natural logarithm, 
-$\lambda$ is the Solow residual (often thougth to represent the pace of technological progress),
-$t$ (time) is measured in years,
-$x_1$, $x_2$, and $x_3$ are factors of production
-and permutations of capital~($k$), labor~($l$), and energy~($e$),
-$k \equiv K/K_{0}$, 
-$l \equiv L/L_{0}$, 
-$Y$ (economic output) is represented by GDP, 
-$K$ (capital) is expressed in currency units, 
-$L$ (labor) is expressed in workers or work-hours/year, and
-the 0 subscript indicates values at an initial year.%
-  \footnote{Dimensionless, indexed quantities are represented by 
-  lower-case symbols 
-  ($y$, $k$, $l$, $e$, $q$, $x$, and $u$), and dimensional 
-  quantities are represented by upper-case symbols 
-  ($Y$, $K$, $L$, $E$, $Q$, $X$, and $U$). 
-  Model parameters are represented by Greek letters
-  ($\alpha_1$, $\alpha_2$, $\lambda$, $\theta$).
-  }
-The CES model without energy is given in Equation~\ref{eq:CESkl}.
-%
-\begin{equation} \label{eq:CESkl}
-  y = \gamma \: A \: \left[\delta_1 k^{-\rho_1} 
-      + (1-\delta_1)l^{-\rho_1} \right]^{-1/\rho_1}; 
-      A \equiv \mathrm{e}^{\lambda (t-t_0)} . 
-\end{equation}
-%
-Equation~\ref{eq:CESkle} augments Equation~\ref{eq:CESkl} with energy 
-using a ($kl$)($e$) nesting structure, as is typical in the literature. 
-Equation~\ref{eq:CESkl} is a degenerate form of Equation~\ref{eq:CESkle} 
-where $\delta \rightarrow 1$. 
+The version of the CES production function being fitted is:
 %
 \begin{equation} \label{eq:CESkle}
-  y = \gamma \: A \: \left\{\delta \left[\delta_1 k^{-\rho_1} 
+  y = \theta \: A \: \left\{\delta \left[\delta_1 k^{-\rho_1} 
       + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1} 
-      + (1-\delta) e^{-\rho} \right\}^{-1/\rho}; 
-      A \equiv \mathrm{e}^{\lambda (t-t_0)}.
+      + (1-\delta) e^{-\rho} \right\}^{-1/\rho} \; ; \;
+      A \equiv \mathrm{e}^{\lambda (t-t_0)} \; .
 \end{equation}
-%
-In the CES production function, 
-$\gamma$ is a fitting parameter that accounts for an atypical first year. 
-The fitting parameters $\rho_1$ and $\rho$ indicate elasticities 
-of substitution ($\sigma_1$ and $\sigma$).
-The elasticity of substitution 
-between capital ($k$) and labor ($l$) is given by 
-$\sigma_1 = \frac{1}{1+\rho_1}$, and
-the elasticity of substitution between ($kl$) and ($e$) is given by 
-$\sigma = \frac{1}{1+\rho}$. 
-As $\rho_1 \rightarrow 0$, $\sigma_1 \rightarrow 1$,
-and the embedded CES production function for $k$ and $l$ degenerates 
-to the Cobb-Douglas production function.
-Similarly, as $\rho \rightarrow 0$, $\sigma \rightarrow 1$,
-and the CES production function for $(kl)$ and $(e)$ degenerates 
-to the Cobb-Douglas production function.
-As $\sigma \rightarrow \infty$ ($\rho \rightarrow -1$), 
-($kl$) and ($e$) are perfect substitutes. 
-As $\sigma \rightarrow 0$ ($\rho \rightarrow \infty$), 
-($kl$) and ($e$) are perfect complements: 
-no substitution is possible. Similarly, 
-as $\sigma_1 \rightarrow 0$ ($\rho_1 \rightarrow \infty$),
-$k$ and $l$ are perfect complements.
-$\delta_1$ describes the relative importance of capital ($k$)
-and labor ($l$), and
-$\delta$ describes the importance of ($kl$) relative to ($e$).
-
-Constraints on the fitting parameters include 
-$\delta_1 \in [0,1]$,
-$\delta \in [0,1]$,
-$\rho_1 \in [-1,0) \cup (0,\infty)$, and
-$\rho \in [-1,0) \cup (0,\infty)$.
-
-Two other nestings of the factors of production ($k$, $l$, and $e$)
-are possible with the CES model.
-%
-\begin{equation} \label{eq:CESlek}
-  y = \gamma \: A \: \left\{\delta \left[\delta_1 l^{-\rho_1} 
-      + (1-\delta_1) e^{-\rho_1} \right]^{\rho/\rho_1} 
-      + (1-\delta) k^{-\rho} \right\}^{-1/\rho}; 
-      A \equiv \mathrm{e}^{\lambda (t-t_0)}
-\end{equation}
-%
-\begin{equation} \label{eq:CESekl}
-  y = \gamma \: A \: \left\{\delta \left[\delta_1 e^{-\rho_1} 
-      + (1-\delta_1) k^{-\rho_1} \right]^{\rho/\rho_1} 
-      + (1-\delta) l^{-\rho} \right\}^{-1/\rho}; 
-      A \equiv \mathrm{e}^{\lambda (t-t_0)}
-\end{equation}
-% 
-Note that $\rho$ ($\sigma$), $\rho_1$ ($\sigma_1$), $\delta$, and $\delta_1$ have different
-meanings depending upon the nesting of the factors of production.
-
-For the CES model, factors shares~($\alpha_1$, $\alpha_2$, and $\alpha_3$) are calculated by
-$\alpha_1 = \delta_1$, $\alpha_2 = 1 - \delta_1$, and $\alpha_3 = 0$ 
-for the CES model with two factors of production
-and by 
-$\alpha_1 = \delta \delta_1$, $\alpha_2 = \delta(1 - \delta_1)$, and $\alpha_3 = 1 - \delta$
-for the CES model with three factors of production and the ($kl$)$e$ nesting.
-The values of $\alpha_1$, $\alpha_2$, and $\alpha_3$ are interpreted as
-factor shares for capital, labor, and energy, respectively,
-as shown in Table \ref{tab:CES_abg_equations}.
-
-\begin{table} \caption{Equations for $\alpha_1$, $\alpha_2$, and $\alpha_3$ 
-                        (factor shares for capital, labor, and energy, respectively)
-                        for the various CES nestings.} 
-\label{tab:CES_abg_equations} 
-  \begin{center}
-    \begin{tabular}{c c c c} 
-      \toprule
-      Nesting    & $\alpha_1$              & $\alpha_2$              & $\alpha_3$       \\
-      \midrule
-      ($kl$) \;  & $\delta_1$              & $1 - \delta_1$          & 0          \\
-      ($kl$)$e$  & $\delta \delta_1$       & $\delta (1 - \delta_1)$ & $1 - \delta$ \\   
-      ($le$)$k$  & $1 - \delta$            & $\delta \delta_1$       & $\delta (1 - \delta_1)$ \\
-      ($ek$)$l$  & $\delta (1 - \delta_1)$ & $1 - \delta$            & $\delta \delta_1$ \\
-      \bottomrule
-    \end{tabular}
-  \end{center}
-\end{table}
-
-%------------------------------
-\subsubsection{Exponential Production Function (reference model)} 
-\label{sec:exp}
-%------------------------------
-
-We define an exponential-only reference model for economic growth
-in Equation~\ref{eq:exponential-only-model}.
-%
-\begin{equation} \label{eq:exponential-only-model}
-  y = \theta A \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)} \; .
-\end{equation}
-%
-We expect that the reference model
-will have a larger fitted Solow residual term than
-the CES model, because no factors of production are
-included in the reference model to drive economic growth.
-Indeed, in the reference model, 
-all economic growth is attributed to the Solow residual~($\lambda$).
-
-In contrast, it is not necessarily true that 
-CES models will exhibit lower $mse$ than the reference model
-shown in Equation~\ref{eq:exponential-only-model}.
-The CES model has more fitting parameters,
-but it incorporates the factors of production
-at constant returns to scale. 
-The reference model has $\alpha_1 + \alpha_2 + \alpha_3 = 0$,
-whereas the CES model~(Equation~\ref{eq:CESgeneric})
-implicitly assumes constant returns to scale.
-Thus, if the factors of production~($\alpha_1$, $\alpha_2$, and $\alpha_3$) 
-are poorly correlated to output~($y$),
-the constant returns to scale constraint may cause higher $mse$ for
-the CES model relative to the reference model.
-
-%++++++++++++++++++++++++++++++
-\subsection{Economies} 
-\label{sec:Economies}
-%++++++++++++++++++++++++++++++
-
-Discuss economies here.
-
-UK and Portugal.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Sources of Data}
-\label{sec:Sources_of_Data}
+\section{Historical data} 
+\label{sec:historical_data}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-Discuss data sources here.
-
-%++++++++++++++++++++++++++++++
-\subsection{Historical Data} 
-\label{sec:Historical_Data}
-%++++++++++++++++++++++++++++++
-
-Historical data are stored in the \texttt{IST} and \texttt{Leeds} data sets.
-
-<<Formulas>>=
-# Set up the formulas for each type of analysis.
-# These formulas contain energy. 
-# We can use keep_summands to drop the energy term (3rd summand on the rhs)
-# later if needed.
-formulas <- 
-  list( 
-    PT = c(unadjusted = build_formula("iGDP", list("iKstkS.L", "iL", "iXpMP", "iYear")),
-             adjusted = build_formula("iGDP", list("iKservS.L", "ihLest", "iUMP", "iYear"))),
-    UK = c(unadjusted = build_formula("iGDP", list("iKstkO.WwithRD", "iL", "iXp", "iYear")),
-             adjusted = build_formula("iGDP", list("iKservO.WwithRD", "ihLest", "iU", "iYear")))
-  )
-countries <- names(formulas)
-flavors <- names(formulas$PT)
-@
+Historical data have been provided by Paul Brockway.
 
@@
 # Create the historicalData data frames
-historicalData <- list()
-commonVars <- c("Year", "Country", "Source")
-historicalData$PT <- filter(IST, Country == "PT") 
-historicalData$PT <- historicalData$PT[ , unique(c(commonVars,
-                                                   all.vars(formulas$PT$unadjusted), 
-                                                   all.vars(formulas$PT$adjusted)))]
-historicalData$UK <- filter(Leeds, Country == "UK")
-historicalData$UK <- historicalData$UK[ , unique(c(commonVars,
-                                                   all.vars(formulas$UK$unadjusted), 
-                                                   all.vars(formulas$UK$adjusted)))]
+# Set the working directory to the project directory.
+print(getwd())
+historicalData <- read.csv(file = "data/BrockwayData.csv")
 @
 
-For unadjusted variables, we use the time series shown in Table~\ref{tab:unadjusted_variables}.
-
-\begin{table} \caption{Unadjusted time-series variables.} 
-\label{tab:unadjusted_variables} 
-  \begin{center}
-    \begin{tabular}{r l l} 
-      \toprule
-      Variable    & Portugal           & UK                 \\
-      \midrule
-      Output      & \Sexpr{summands(formulas$PT$unadjusted, n=1, right=FALSE)}   
-                                                             & \Sexpr{summands(formulas$UK$unadjusted, n=1, right=FALSE)}\\
-      Capital     & \Sexpr{summands(formulas$PT$unadjusted, 1)} & \Sexpr{summands(formulas$UK$unadjusted, 1)} \\
-      Labor       & \Sexpr{summands(formulas$PT$unadjusted, 2)} & \Sexpr{summands(formulas$UK$unadjusted, 2)} \\
-      Energy      & \Sexpr{summands(formulas$PT$unadjusted, 3)} & \Sexpr{summands(formulas$UK$unadjusted, 3)} \\
-      \bottomrule
-    \end{tabular}
-  \end{center}
-\end{table}
-
-For quality-adjusted variables, we use the time series shown in Table~\ref{tab:quality_adjusted_variables}.
-
-\begin{table} \caption{Quality-adjusted time series variables.} 
-\label{tab:quality_adjusted_variables} 
-  \begin{center}
-    \begin{tabular}{r l l} 
-      \toprule
-      Variable    & Portugal         & UK               \\
-      \midrule
-      Output      & \Sexpr{summands(formulas$PT$adjusted, n=1, right=FALSE)}   
-                                                           & \Sexpr{summands(formulas$UK$adjusted, n=1, right=FALSE)} \\
-      Capital     & \Sexpr{summands(formulas$PT$adjusted, 1)} & \Sexpr{summands(formulas$UK$adjusted, 1)} \\
-      Labor       & \Sexpr{summands(formulas$PT$adjusted, 2)} & \Sexpr{summands(formulas$UK$adjusted, 2)} \\
-      Energy      & \Sexpr{summands(formulas$PT$adjusted, 3)} & \Sexpr{summands(formulas$UK$adjusted, 3)} \\
-      \bottomrule
-    \end{tabular}
-  \end{center}
-\end{table}
-
-Unadjusted and quality-adjusted data for both Portugal and the United Kingdom 
-are shown in Figure~\ref{fig:Historical Data Graph}.
-
 <<Historical Data Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Historical data.", warning=FALSE>>=
-# Melt the data into a form that is useful in a couple places
-histDataForGraph <- leaf_apply(formulas, class = "formula", f=function(form, name){
-  meta <- strsplit(name, split="[.]") %>% unlist
-  Country <- meta[1]
-  flavor <- meta[2]
-  measure.vars <- c(summands(form, right=FALSE), summands(form, 1:3))
-  trimmed_historical_data <- historicalData[[Country]][c("Year", measure.vars)]
-  mtrimmed_historical_data <- melt(trimmed_historical_data, measure.vars = measure.vars, 
+# Melt data for plotting
+historicalDataForGraph <- melt(data = historicalData, measure.vars = c("iY", "iK", "iL", "iU"), 
                                value.name = "value", variable.name = "variable")
-  mtrimmed_historical_data$Country <- Country
-  mtrimmed_historical_data$flavor <- if (flavor == "adjusted") "Quality-adjusted" else "Unadjusted"
-  return(mtrimmed_historical_data)
-}) %>% do.call(rbind, .)
 
 # Relevel factors before plotting
-histDataForGraph$Country <- relevelFactor(as.factor(histDataForGraph$Country), c("PT", "UK"))
-histDataForGraph$flavor <- relevelFactor(as.factor(histDataForGraph$flavor), c("Unadjusted", "Quality-adjusted"))
-histDataForGraph$variable <- relevelFactor(as.factor(histDataForGraph$variable), unique(histDataForGraph$variable))
+historicalDataForGraph$Country <- relevelFactor(as.factor(historicalDataForGraph$Country), c("UK", "US", "CN"))
 
-historicalPlot(histDataForGraph, 
+historicalPlot(historicalDataForGraph, 
                mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
-               facet_formula = Country ~ flavor, 
-               line_types = c(1,2,4,3,2,4,3,2,3,2,3)) + 
-  scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12)) +
-  coord_cartesian(ylim=c(0.5, 13)) +
+               facet_formula = ~ Country, 
+               line_types = c(1,2,4,3)) + 
+  scale_y_continuous(breaks=c(1, 10, 20)) +
   xlab("") + 
-  ylab("Indexed (1960=1)")
-@
-
-<<Pre-econometric graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Pre-econometric data.", warning=FALSE>>=
-pre_econometric_data <- leaf_apply(formulas, class = "formula", f=function(form, name){
-  meta <- strsplit(name, split="[.]") %>% unlist
-  Country <- meta[1]
-  flavor <- meta[2]
-  nums <- summands(form, n=1:3)
-  denom <- summands(form, n=1, right=FALSE)
-  ratios <- lapply(nums, function(num) {paste(num, denom, sep="/")}) %>% unlist
-  coltemplate <- build_formula(NULL, c("Year", ratios))
-  trimmed_historical_data <- historicalData[[Country]][all.vars(coltemplate)]
-  ratio_data <- evalFormula(coltemplate, data=trimmed_historical_data)$right
-  mratio_data <- melt(ratio_data, measure.vars = ratios, value.name = "ratio", variable.name = "variable")
-  mratio_data$Country <- Country
-  mratio_data$flavor <- if (flavor == "adjusted") "Quality-adjusted" else "Unadjusted"
-  return(mratio_data)
-}) %>% do.call(rbind, .)
-
-# Fix levels
-pre_econometric_data$flavor <- relevelFactor(as.factor(as.character(pre_econometric_data$flavor)), 
-                                               c("Unadjusted", "Quality-adjusted"))
-pre_econometric_data$Country <- relevelFactor(as.factor(pre_econometric_data$Country), 
-                                              c("PT", "UK"))
-pre_econometric_data$variable <- relevelFactor(as.factor(pre_econometric_data$variable),
-                                               unique(pre_econometric_data$variable))
-# Now make the plot of pre-econometric data
-historicalPlot(pre_econometric_data, 
-               mapping=aes(x=Year, y=ratio, group=variable, linetype=variable), 
-               facet_formula = Country ~ flavor, 
-               line_types = c(2,4,3, 2,4,3, 2,3,2, 3)) + 
-  xlab("") + 
-  ylab("Indexed (1960=1)")
+  ylab("Indexed Quantities")
 @
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Parameter Estimation (Without Cost-share Theorem)}
-\label{sec:parameter_estimation_noCST}
+\section{Parameter Estimation}
+\label{sec:parameter_estimation}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-% Parameter estimation is accomplished with \texttt{formula}s of the form
-% %
-% \begin{equation} \label{eq:formulas}
-%   y \sim x_1 + x_2 + x_3 + time,
-% \end{equation}
-% %
-% where $y$ is economic output and 
-% $x_1$, $x_2$, and $x_3$ are factors of production
-% and permutations of
-% capital ($k$), labor ($l$), and energy ($e$).
-% (The factors of production may be quality-adjusted.)
-% $time$ is the time variable, usually \texttt{iYear}. 
-% The \texttt{formula}s are used in a fitting function such as 
-% \texttt{cdModel} to create a \texttt{model} object.
-% The function \texttt{naturalCoef} extracts reasonable
-% coefficients from \texttt{model} objects.
-% 
-% Note that in the fitting process for the Cobb-Douglas equation,
-% $\texttt{scale} = \theta$, 
-% $\alpha_1 = \alpha$,
-% $\alpha_2 = \beta$, and
-% $\alpha_3 = \gamma$,
-% when the \texttt{formula} is specified as 
-% %
-% \begin{equation} \label{eq:formula_kle}
-%   \texttt{y} \sim \texttt{k + l + e + time}.
-% \end{equation}
-% %
-% Note that for the CES model, $\texttt{scale} = \gamma$ and is expected to be close to unity.
-
-The models being fit can be described by the algebraic form of the model 
-(Cobb-Douglas, CES, etc.) and a formula that enumerates 
-which data variables are being used in which roles to fit the model.  
-A formula of the form
-%
-\begin{equation} \label{eq:formulas-3-factor}
-y \sim x_1 + x_2 + x_3 + t,
-\end{equation}
-%
-or 
-%
-\begin{equation} \label{eq:formulas-2-factor}
-y \sim x_1 + x_2 + t,
-\end{equation}
-%
-describes the economic output variable ($y$, usually \texttt{iGDP},
-                                        indexed GDP) 
-and the factors of production ($x_1$, $x_2$, and $x_3$,
-                               which will be some measure of capital, labor, and energy, 
-                               but perhaps not in that order), 
-and a time variable ($t$, usually \texttt{iYear}, 
-                     the number of years since the beginning of data collection).  
-All of the models assume an error term that is additive on the 
-logarithmic scale and are fit by the method of least squares.  
-Model fitting provides estimates for all parameters in the model.
-
 <<Models>>=
-fileNameCDCES <- "EcolEcon2015ModelsCDCES.rds"
-fileNameCST <- "EcolEcon2015ModelsCST.rds"
-fileNameExp <- "EcolEcon2015ModelsExp.rds"
+fileName <- file.path("models", "Brockway2015Models.rds")
 if (!rerunModels){
   # load from the file on disk
-  models <- readRDS(fileNameCDCES)
-  modelsCST <- readRDS(fileNameCST)
-  modelsExp <- readRDS(fileNameExp)
+  models <- readRDS(fileName)
 } else {
@@
   # In RStudio, be sure to set the working directory to the source file directory.
-
-  #
-  # Models that are exponential only
-  #
-  modelsExp <- list()
-  alphaExp <- 0
-  betaExp <- 0
-  gammaExp <- 0
-  for (country in countries){
-    # Replace with better code later. 
-    # Would like to say cdModel(formula, data, factorShares=c(alpha_1 = 0, alpha_2 = 0, alpha_3 = 0))
-    # or something like that.
-    form <- keep_summands(formulas[[country]][["unadjusted"]], n = c(-1, -2, -3)) # Remove energy
-    yVar <- as.name(summands(form, n=1, right=FALSE))
-    tVar <- as.name(summands(form, n=1))
-    data <- historicalData[[country]]
-    expMod <- lm(log(eval(yVar)) ~ eval(tVar), data=data)
-    attr(expMod, "naturalCoeffs") <- data.frame(lambda=coef(expMod)[[2]],
-                                                  logscale=coef(expMod)[[1]], 
-                                                  scale=exp(coef(expMod)[[1]]),
-                                                  alpha_1=alphaExp,
-                                                  alpha_2=betaExp, 
-                                                  alpha_3=gammaExp)
-    expMod$formula <- form
-    sdata <- subset(data, select=all.vars(form))
-    sdata <- data[complete.cases(sdata), unique(c(all.vars(form), names(data)))]
-    expMod$data <- sdata
-    expMod$response <- sdata$iGDP 
-    modelsExp[[country]] <- expMod
+  models <- lapply(c("UK", "US", "CN"), function(coun){
+    return(cesModel(iY ~ iK + iL + iU + iYear, filter(historicalData, Country==coun, nest=1:3)))
+  })
+  # Save the models.
+  saveRDS(models, file = fileName)
 }
-  # Save exponential theorem models to disk.
-  saveRDS(modelsExp, file=fileNameExp)
-
-  #
-  # Models that adhere to the cost-share theorem
-  #
-
-  modelsCST <- list()
-  # Output elasticities based on cost share theorem
-  alphaCST <- 0.3 # Fraction of national accounts spent on capital
-  betaCST <- 0.7 # Fraction of national accounts spent on labor
-  for (country in countries){
-    for (adj in c("unadjusted", "adjusted")){
-      # Replace with better code later. 
-      # Would like to say cdModel(formula, data, factorShares=c(alpha_1 = 0.3, alpha_2 = 0.7, alpha_3 = 0))
-      # or something like that.
-      form <- keep_summands(formulas[[country]][[adj]], n=-3) # Remove energy
-      yVar <- as.name(summands(form, n=1, right=FALSE))
-      kVar <- as.name(summands(form, n=1))
-      lVar <- as.name(summands(form, n=2))
-      tVar <- as.name(summands(form, n=3))
-      data <- historicalData[[country]]
-      # Cobb-Douglas
-      cdModCST <- lm(log(eval(yVar)) - alphaCST*log(eval(kVar)) - betaCST*log(eval(lVar)) ~ eval(tVar), data = data)
-      attr(cdModCST, "naturalCoeffs") <- data.frame(lambda=coef(cdModCST)[[2]],
-                                                    logscale=coef(cdModCST)[[1]], 
-                                                    scale=exp(coef(cdModCST)[[1]]),
-                                                    alpha_1=alphaCST,
-                                                    alpha_2=betaCST, 
-                                                    alpha_3=0)
-      cdModCST$formula <- form
-      sdata <- subset(data, select=all.vars(form))
-      sdata <- data[complete.cases(sdata), unique(c(all.vars(form), names(data)))]
-      cdModCST$data <- sdata
-      cdModCST$response <- sdata$iGDP
-      modelsCST[[country]][[adj]][["noE"]][["CD"]] <- cdModCST
-      # CES
-      cesModCST <- plm(log(eval(yVar) / (alphaCST*eval(kVar)^(-rho_1) + betaCST*eval(lVar)^(-rho_1))^(-1/rho_1)) ~ eval(tVar),
-                       data = historicalData[[country]],
-                       params=c(rho_1=0.8))
-      names(cesModCST$coefficients) <- c("logscale", "lambda", "rho_1")
-      cesModCST$coefficients <- c(coef(cesModCST), c(delta_1=alphaCST, delta=1))
-      attr(cesModCST, "naturalCoeffs") <- EconModels:::makeNatCoef(cesModCST)
-      cesModCST$formula <- form
-      cesModCST$data <- sdata
-      modelsCST[[country]][[adj]][["noE"]][["CES"]][["kl"]] <- cesModCST
-    }
-  }
-  # Save cost-share theorem models to disk.
-  saveRDS(modelsCST, file=fileNameCST)
-
-  #
-  # Models where all parameters are estimated (models don't adhere to the cost share theorem)
-  #
-
-  models <- list()
-  for(country in countries){
-    for (flavor in flavors){
-      fnoE <- keep_summands(formulas[[country]][[flavor]], -3) # Drop the energy term (3rd term on RHS)
-      fwithE <- formulas[[country]][[flavor]]
-      # CD models
-      models[[country]][[flavor]][["noE"]][["CD"]]   <- cdModel(fnoE, data = historicalData[[country]])
-      models[[country]][[flavor]][["withE"]][["CD"]] <- cdModel(fwithE, data = historicalData[[country]])
-      # CES models
-      models[[country]][[flavor]][["noE"]][["CES"]][["kl"]] <- cesModel(fnoE, 
-                                                                        data = historicalData[[country]], 
-                                                                        nest=c(1,2))
-      nestsWithE <- list(kle=c(1,2,3), lek=c(2,3,1), ekl=c(3,1,2))
-      models[[country]][[flavor]][["withE"]][["CES"]] <- lapply(nestsWithE, function(nest){
-          cesModel(formula=fwithE, data=historicalData[[country]], nest=nest)
-        })
-    }      
-  }
-  # Save models to disk.
-  saveRDS(models, file=fileNameCDCES)
-}
-# Put all exponential model coefficients into a data frame
-AllCoeffsExp <- leaf_apply(modelsExp, class = c("lm"), f = function(modExp, id){
-  # Parse the id to find details of this model
-  id_list <- strsplit(id, split = "[.]")[[1]]
-  res <- rbind(list(Country = id_list[[1]], 
-                    flavor = NA,
-                    energy = "Without energy", 
-                    model = "exp", 
-                    nest = NA,
-                    cst = "Reject CST"))
-  res <- cbind(res, naturalCoef(modExp))
-  # Now caluculate mean squared error (mse) for each model.
-  sqResids <- resid(modExp)^2
-  mse <- sum(sqResids) / (length(sqResids))
-  res <- cbind(res, list(mse=mse))
-  return(res)
-}) %>% do.call(plyr::rbind.fill, .)
-
-# Put all the cost-share theorem (CST) model coefficients into a data frame
-AllCoeffsCST <- leaf_apply(modelsCST, class = c("lm"), f = function(modCST, id){
-  # Parse the id to find out whether this is quality-adjusted data, etc.
-  id_list <- strsplit(id, split = "[.]")[[1]]
-  res <- rbind(list(Country = id_list[[1]], 
-                    flavor = if (id_list[[2]]=="unadjusted") "Unadjusted" else "Quality-adjusted",
-                    energy = if (id_list[[3]]=="noE") "Without energy" else "With energy",
-                    model=id_list[[4]], 
-                    nest=if(length(id_list) > 4) id_list[[5]] else NA,
-                    cst="Adhere to CST"))
-  res <- cbind(res, naturalCoef(modCST))
-  # Now calculate the mean squared error (mse) for each model.
-  sqResids <- resid(modCST)^2
-  mse <- sum(sqResids)/(length(sqResids))
-  res <- cbind(res, list(mse=mse))
-  return(res)
-}) %>% do.call(plyr::rbind.fill, .)
-
-AllCoeffsNoCST <- leaf_apply(models, class = c("CDEmodel", "cesModel", "LINEXmodel"), f = function(mod, id){
-  # Parse the id to find out whether this is quality-adjusted data, etc.
-  id_list <- strsplit(id, split = "[.]")[[1]]
-  res <- rbind(list(Country = id_list[[1]], 
-                    flavor = if (id_list[[2]]=="unadjusted") "Unadjusted" else "Quality-adjusted",
-                    energy = if (id_list[[3]]=="noE") "Without energy" else "With energy",
-                    model=id_list[[4]], 
-                    nest=if(length(id_list) > 4) id_list[[5]] else NA,
-                    cst="Reject CST"))
-  res <- cbind(res, naturalCoef(mod))
-  # Now calculate the mean squared error (mse) for each model.
-  sqResids <- resid(mod)^2
-  mse <- sum(sqResids)/(length(sqResids))
-  res <- cbind(res, list(mse=mse))
-  return(res)
-}) %>% do.call(plyr::rbind.fill, .)
-AllCoeffs <- plyr::rbind.fill(AllCoeffsExp, AllCoeffsCST, AllCoeffsNoCST)
-# See hint at http://stackoverflow.com/questions/22555249/how-to-merge-data-frame-with-same-column-names
-AllCoeffs <- as.data.frame(lapply(AllCoeffs, function(x) unname(unlist(x))))
-# Get reference values for lambda and sse.
-# ref <- filter(AllCoeffs, cst=="Adhere to CST" & flavor=="Unadjusted" & energy=="Without energy") %>% 
-#               select(Country, model, mse, lambda)
-ref <- filter(AllCoeffs, model=="exp") %>% select(Country, mse, lambda)
-colnames(ref)[colnames(ref)=="mse"] <- "mse_ref"
-colnames(ref)[colnames(ref)=="lambda"] <- "lambda_ref"
-AllCoeffs <- merge(AllCoeffs, ref)
-# Calculate differences relative to the reference model
-AllCoeffs <- mutate(AllCoeffs, 
-                    Dlambda = abs(lambda) - abs(lambda_ref), 
-                    Dmse = mse - mse_ref,
-                    percDlambda = Dlambda / abs(lambda_ref) * 100, 
-                    percDmse = Dmse / mse_ref * 100)
-
-# Relevel factors
-AllCoeffs$Country <- relevelFactor(as.factor(unlist(AllCoeffs$Country)), c("PT", "UK"))
-AllCoeffs$flavor <- relevelFactor(as.factor(unlist(AllCoeffs$flavor)), c("Unadjusted", "Quality-adjusted"))
-AllCoeffs$energy <- relevelFactor(as.factor(unlist(AllCoeffs$energy)), c("Without energy", "With energy"))
-AllCoeffs$model <- relevelFactor(as.factor(unlist(AllCoeffs$model)), c("exp", "CD", "CES"))
-AllCoeffs$nest <- relevelFactor(as.factor(unlist(AllCoeffs$nest)), c("kl", "kle", "lek", "ekl"))
-AllCoeffs$cst <- relevelFactor(as.factor(unlist(AllCoeffs$cst)), c("Adhere to CST", "Reject CST"))
-# Rearrange for easier viewing
-AllCoeffs <- arrange(AllCoeffs, Country, model, flavor, energy, nest, cst)
-@
-
-<<Fitted_and_Residuals>>=
-fittedAndResidData <- function(model, id){
-  # ******************************************
-  # getData doesn't work for lm models that are created for CST="Adhere to CST".
-  # After we implement specified values for alpha_1, alpha_2, and alpha_3 in our fitting functions, 
-  # getData(model) will probably work.
-  # At that time, change model$data to getData(model)
-  df <- data.frame(select(model$data, Year)) 
-  # By including [c(1:length(df$Year))] on the end, we 
-  # add NAs (as appropriate) to the end of these columns
-  # if data do not exist.
-  df$fitted <- yhat(model)[c(1:length(df$Year))]
-  df$Residuals <- resid(model)[c(1:length(df$Year))]
-  # Now add the response, using the original variable name.
-  df[[summands(model$formula, right = FALSE)]] <- response(model)[c(1:length(df$Year))]
-  # Now add meta information
-  id_list <- strsplit(id, split = "[.]")[[1]]
-  len <- length(id_list)
-  df$Country <- id_list[[1]]
-  # Exponential models have only 1 item in the id list, namely country. Accommodate that length with if statements.
-  df$flavor <- if (len > 1) (if (id_list[[2]] ==  "unadjusted") "Unadjusted" else "Quality-adjusted") else NA
-  df$energy <- if (len > 2) (if (id_list[[3]] == "noE") "Without energy" else "With energy") else "Without energy"
-  df$model <- if (len > 3) id_list[[4]] else "exp"
-  df$nest <- if (len > 4) id_list[[5]] else NA
-  return(df)  
-}
-
-temp_data_exp <- leaf_apply(modelsExp, class=c("lm"), f = function(model, id){
-  # ****************************************************
-  # Not all of the results from this code are not correct at this time.
-  # The residuals are OK.
-  # But, the yhat() call in fittedAndResidData() will not return the correct information from the CST models.
-  # This is because modelsCST was not created with our typical functions.
-  # To correct this problem, we need to add arguments to cdModel and cesModel such that 
-  # the models produced by those functions will be in the correct form for yhat() function.
-  return(fittedAndResidData(model, id))
-}) %>% do.call(rbind, .)
-temp_data_exp$cst <- "Reject CST"
-
-temp_data_CST <- leaf_apply(modelsCST, class=c("plm", "lm"), f = function(model, id){
-  # ****************************************************
-  # Not all of the results from this code are not correct at this time.
-  # The residuals are OK.
-  # But, the yhat() call in fittedAndResidData() will not return the correct information from the CST models.
-  # This is because modelsCST was not created with our typical functions.
-  # To correct this problem, we need to add arguments to cdModel and cesModel such that 
-  # the models produced by those functions will be in the correct form for yhat() function.
-  return(fittedAndResidData(model, id))
-}) %>% do.call(rbind, .)
-temp_data_CST$cst <- "Adhere to CST"
-
-temp_data_noCST <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, id){
-  return(fittedAndResidData(model, id))  
-}) %>% do.call(rbind, .)
-temp_data_noCST$cst <- "Reject CST"
-
-temp_data <- plyr::rbind.fill( temp_data_exp, temp_data_CST, temp_data_noCST )
-
-# Get the unadjusted, without-energy residuals from models that obey the CST
-# and store them in a data frame
-# r_unadj_noE_CST <- filter(temp_data, flavor=="Unadjusted" & energy=="Without energy" & cst=="Adhere to CST") %>% 
-#   select(Year, Country, Residuals, model)
-# colnames(r_unadj_noE_CST)[colnames(r_unadj_noE_CST)=="Residuals"] <- "r_unadj_noE"
-# Merge to get the unadjusted, without-energy values next to each country, year, and model
-# fitted_and_resid_data <- merge(temp_data, r_unadj_noE_CST)
-# Create a column containing ∆r, the difference between a residual value
-# and the residual value in the same year for the unadjusted, no-energy case
-# fitted_and_resid_data[["Dr"]] <- abs(fitted_and_resid_data[["Residuals"]]) - abs(fitted_and_resid_data[["r_unadj_noE"]])
-
-# Get the reference residuals (from the exponential-only models) and store them in a data frame
-r_ref <- filter(temp_data, model=="exp") %>% select(Year, Country, Residuals)
-colnames(r_ref)[colnames(r_ref)=="Residuals"] <- "r_ref"
-# Merge to get the reference values in each appropriate row
-fitted_and_resid_data <- merge(temp_data, r_ref)
-# Create a column containing ∆r, the difference between a residual value
-# and the residual value in the same year for the reference case
-fitted_and_resid_data[["Dr"]] <- abs(fitted_and_resid_data[["Residuals"]]) - abs(fitted_and_resid_data[["r_ref"]])
-
-# Relevel factors before plotting
-fitted_and_resid_data$Country <- relevelFactor(as.factor(fitted_and_resid_data$Country), c("PT", "UK"))
-fitted_and_resid_data$flavor <- relevelFactor(as.factor(fitted_and_resid_data$flavor), c("Unadjusted", "Quality-adjusted"))
-fitted_and_resid_data$energy <- relevelFactor(as.factor(fitted_and_resid_data$energy), c("Without energy", "With energy"))
-fitted_and_resid_data$nest <- relevelFactor(as.factor(fitted_and_resid_data$nest), c("kl", "kle", "lek", "ekl"))
-
-# Make data viewing easier
-fitted_and_resid_data <- arrange(fitted_and_resid_data, Country, cst, model, flavor, energy, nest)
-@
-
-%++++++++++++++++++++++++++++++
-\subsection{Fits to historical data} 
-\label{sec:fits_to_historical_data}
-%++++++++++++++++++++++++++++++
-
-<<Fitted and Residual Graph Functions>>=
-fittedGraphCST <- function(data){
-  ggplot() +
-    geom_line(data=filter(data, cst=="Adhere to CST"), mapping=aes(x=Year, y=iGDP)) +
-    geom_line(data=data, mapping=aes(x=Year, y=fitted, linetype=cst)) +
-    scale_linetype_manual(values=c(2,3), name="") +
-    facet_grid(Country ~ flavor) + 
-    xlab("") +
-    ylab("Indexed GDP (1960=1)") +
-    xy_theme()
-}
-
-fittedGraphNoCST <- function(data){
-  ggplot() +
-    geom_line(data=filter(data, energy=="Without energy"), mapping=aes(x=Year, y=iGDP)) +
-    geom_line(data=data, mapping=aes(x=Year, y=fitted, linetype=energy)) +
-    scale_linetype_manual(values=c(2,3), name="") +
-    facet_grid(Country ~ flavor) +
-    scale_x_continuous(breaks=c(1960, 1980, 2000)) +
-    scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12)) +
-    xlab("") +
-    ylab("Indexed GDP (1960=1)") +
-    xy_theme()
-}
-@
-
-Both historical GDP and fitted GDP are shown in 
-Figures~\ref{fig:Graphs CESkle-fitted}--\ref{fig:Graphs CESekl-fitted}.
-%
-<<Graphs CESkle-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($kl$)$e$ nesting. Solid line is historical GDP.">>=
-fittedGraphNoCST(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest=="kle" | nest=="kl")))
-@
-%
-<<Graphs CESlek-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($le$)$k$ nesting. Solid line is historical GDP.">>=
-fittedGraphNoCST(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest=="lek" | nest=="kl")))
-@
-%
-<<Graphs CESekl-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($ek$)$l$ nesting. Solid line is historical GDP.">>=
-fittedGraphNoCST(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest=="ekl" | nest=="kl")))
-@
-
-%++++++++++++++++++++++++++++++
-\subsection{Fitting residuals} 
-\label{sec:fitting_residuals}
-%++++++++++++++++++++++++++++++
-
-<<ResidualPlotFunction>>=
-residualPlot <- function(data){
-  ggplot() +
-    geom_line(data=data, mapping=aes(x=Year, y=Residuals, linetype=energy)) +
-    scale_linetype_manual(values=c(2,3), name="") +
-    facet_grid(Country ~ flavor) +
-    scale_x_continuous(breaks=c(1960, 1980, 2000)) +
-    xlab("") +
-    ylab("r") + 
-    xy_theme()
-}
-@
-
-Because we fit in log-space, fitting residuals ($r_i$) are defined as
-%
-\begin{equation} \label{eq:log-residuals}
-  r_i \equiv \ln(y_i) - \ln(\hat{y}_i) =\ln\left( \frac{y_i}{\hat{y}_i} \right), 
-\end{equation}
-%
-where $r_i$ will be zero when there is agreement between 
-historical~($y_i$) and fitted~($\hat{y}_i$) economic output.
-
-The mean squared error~($mse$) for any fitted model can be calculated by
-%
-\begin{equation} \label{eq:mse}
-  mse \equiv \frac{1}{N} \sum_{i=1}^N{r_i^2} .
-\end{equation}
-
-Figures~\ref{fig:Graphs CESkle-resid}--\ref{fig:Graphs CESekl-resid}
-show fitting residuals for all CES models.
-%
-<<Graphs CESkle-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(kl$)$e$ nesting.">>=
-residualPlot(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest=="kle" | nest=="kl")))
-@
-%
-<<Graphs CESlek-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with ($le$)$k$ nesting.">>=
-residualPlot(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest == "lek" | nest=="kl")))
-@
-%
-<<Graphs CESekl-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(ek$)$l$ nesting.">>=
-residualPlot(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest=="ekl" | nest=="kl")))
 @
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The primary results from this paper involve the effects of
-the following modeling decisions:
-rejecting (or adhering to) the cost share theorem,
-quality-adjusting (or not) the factors of production,
-including energy (or not) in the production function, and
-nesting (in the CES model).
-
-We evaluate the effects of these modeling decisions 
-first on goodness of fit and Solow residual,
-next on factor shares, and 
-finally on factor substitutability.
-
-%++++++++++++++++++++++++++++++
-\subsection{Goodness of fit and Solow residual} 
-\label{sec:fit_and_sr}
-%++++++++++++++++++++++++++++++
-
-Table~\ref{tab:CES_sr_gof} shows 
-the Solow residual~($\lambda$) and
-goodness of fit~($mse$)
-for all modeling decisions.
-%
-<<CES_sr_gof, results="asis">>=
-myXTable(filter(AllCoeffs, model=="CES" | model=="exp") %>% 
-           select(Country, model, flavor, energy, nest, cst, gamma, lambda, mse),
-         caption="$\\theta$, Solow residual, and $mse$ for CES models.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-%
-We can evaluate the effect of modeling decisions on 
-goodness of fit and Solow residual by
-calculating values relative to the reference model.
-To do so, we define 
-$\Delta \lambda$ and $\Delta mse$, where
-%
-\begin{equation} \label{eq:delta_lambda}
-  \Delta \lambda \equiv \lambda - \lambda_{ref}
-\end{equation}
-%
-and
-%
-\begin{equation} \label{eq:delta_mse}
-  \Delta mse \equiv mse - mse_{ref},
-\end{equation}
-%
-with~$\lambda_{ref}$ and $mse_{ref}$ being the values 
-of the Solow residual and $mse$ for the reference model, respectively.
-On a percentage basis,
-%
-\begin{equation} \label{eq:delta_lambda_perc}
-  \Delta \lambda \, [\%] = \frac{100 \, \Delta \lambda}{\lambda_{ref}} 
-            = \frac{100 \, \lambda}{\lambda_{ref}} - 1 \; ,
-\end{equation}
-%
-and
-%
-\begin{equation} \label{eq:delta_mse_perc}
-  \Delta mse \, [\%] = \frac{100 \, \Delta mse}{mse_{ref}} 
-            = \frac{100 \, mse}{mse_{ref}} - 1 \; .
-\end{equation}
-
-When $\Delta \lambda$, $\Delta \lambda \, [\%]$, or $\Delta mse$ are negative, 
-we observe reduction in the Solow residual ($\lambda$) or
-the fitting residuals ($mse$)
-relative to the reference model.
-
-Figures~\ref{fig:DSRmse_CES_graph} and~\ref{fig:percDSRmse_CES_graph} summarize 
-$\Delta \lambda \, [\%]$ and $\Delta mse \, [\%]$ 
-results for CES models.
-%
-<<percDSRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Percentage change in Solow Residuals~($\\Delta\\lambda \\, [\\%]$) and mean squared error~($\\Delta mse \\, [\\%]$) for the CES models relative to the exponential-only model.">>=
-ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=percDmse, y=percDlambda, color=energy, size=cst, shape=nest)) +
-  scale_size_manual(values=c(2,3.5)) +
-  scale_shape_manual(values=c(16,17,18,15)) +
-  facet_grid(Country ~ flavor) +
-  xlab(expression(paste(Delta * mse, " [%]"))) + 
-  scale_x_continuous(breaks=seq(-80, 0, 20)) +  
-  ylab(expression(paste(Delta * lambda, " [%]"))) +
-  scale_y_continuous(breaks=seq(-80, 0, 20), limits=c(-100, 10)) +  
-  xy_theme() +
-  theme(legend.title=element_blank())
-@
-
-<<SRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Solow Residuals~($\\lambda$) and mean squared error~($mse$).
-$\\lambda$ and $mse$ values for the reference (exponential-only) model are shown as gridlines.">>=
-ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=mse, y=lambda, color=energy, size=cst, shape=nest)) +
-  geom_vline(aes(xintercept = mse), filter(AllCoeffs, model=="exp") %>% select(Country, mse), colour="gray50", size=0.1) +
-  geom_hline(aes(yintercept = lambda), filter(AllCoeffs, model=="exp") %>% select(Country, lambda), colour="gray50", size=0.1) +
-  scale_size_manual(values=c(2,4)) +
-  scale_shape_manual(values=c(1,0,3,4)) + # 16,17,18,15
-  facet_grid(Country ~ flavor) +
-  # scale_x_continuous(breaks=seq(0, 0.02, 0.01), limits=c(0, 0.02)) +  
-  ylab(expression(lambda)) +
-  # scale_y_continuous(breaks=seq(0, 0.04, 0.01), limits=c(0, 0.04)) +  
-  xy_theme() +
-  theme(legend.title=element_blank())
-@
-
-%------------------------------
-\subsubsection{Rejecting (or adhering to) the cost share theorem} 
-\label{sec:gfsr_cst}
-%------------------------------
-
-%------------------------------
-\subsubsection{Quality-adjusting (or not) factors of production} 
-\label{sec:gfsr_fop}
-%------------------------------
-
-%------------------------------
-\subsubsection{Including energy (or not)} 
-\label{sec:gfsr_energy}
-%------------------------------
-
-%------------------------------
-\subsubsection{CES nesting} 
-\label{sec:gfsr_nesting}
-%------------------------------
-
-%++++++++++++++++++++++++++++++
-\subsection{Factor shares} 
-\label{sec:shares}
-%++++++++++++++++++++++++++++++
-
-Table~\ref{tab:CES_alpha} shows 
-the factor shares~($\alpha_i$ values) for all CES modeling decisions.
-%
-<<CES_alpha, results="asis">>=
-myXTable(filter(AllCoeffs, model=="CES" | model=="exp") %>% 
-           select(Country, model, flavor, energy, nest, cst, alpha_1, alpha_2, alpha_3),
-         caption="Factor shares~($\\alpha$) for CES models.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-%
-Figures~\ref{fig:Factor_shares_graph_PT} and~\ref{fig:Factor_shares_graph_UK}
-show factor shares ($\alpha$ values) for CES models for
-Portugal and the UK, respectively.
-See Table~\ref{tab:CES_abg_equations} for details on the calculation
-of factor shares from fitted values of $\delta_1$ and $\delta$.
-%
-<<Factor_shares_bar_graph_function>>=
-fsbg <- function(coun, mod){
-  bar_chart_data <- filter(AllCoeffs, Country==coun & model==mod) %>% 
-    select(Country, model, flavor, energy, nest, cst, alpha_1, alpha_2, alpha_3)
-  # Change nest to a nicer-looking nest string
-  bar_chart_data$nest <- plyr::mapvalues(bar_chart_data$nest, 
-                                         from=c("kl", "kle", "lek", "ekl"), 
-                                         to=c("(kl)", "(kl)e", "(le)k", "(ek)l"))
-  # Add a label column
-  bar_chart_data$label <- paste(bar_chart_data$cst, bar_chart_data$flavor, 
-                                bar_chart_data$energy, bar_chart_data$nest, sep=", ")
-  # Capture the order that we want for the models on the vertical axis.
-  order <- bar_chart_data$label
-  # Now melt the data
-  bar_chart_data <- melt(bar_chart_data, 
-                         measure.vars = c("alpha_1", "alpha_2", "alpha_3"), 
-                         value.name = "value", 
-                         variable.name = "variable")
-  # Define the color palette (see http://www.cookbook-r.com/Graphs/Colors_(ggplot2))
-  cbPalette <- c("#E69F00", "#999999", "#F0E442", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")
-  # Make the plot
-  plot <- ggplot(bar_chart_data, mapping=aes(x=label, y=value, fill=variable, width=0.4)) + 
-    geom_bar(stat="identity") + 
-    xlab("") +
-    scale_x_discrete(limits=rev(order)) +
-    ylab("") +
-    scale_y_continuous(breaks=c(0, 0.5, 1)) + 
-    guides(fill=guide_legend(title=NULL)) +
-    coord_flip() + 
-    scale_fill_brewer(palette="OrRd") +
-    xy_theme() +
-    theme(axis.ticks.y = element_blank())
-  return(plot)
-}
-@
-
-<<Factor_shares_graph_PT, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=2.5, fig.cap="Factor shares ($\\alpha$ values) for CES models for Portugal.">>=
-fsbg(coun = "PT", mod = "CES")
-@
-
-<<Factor_shares_graph_UK, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=2.5, fig.cap="Factor shares ($\\alpha$ values) for CES models for the UK.">>=
-fsbg(coun = "UK", mod = "CES")
-@
-
-%------------------------------
-\subsubsection{Rejecting (or adhering to) the cost share theorem} 
-\label{sec:fs_cst}
-%------------------------------
-
-%------------------------------
-\subsubsection{Quality-adjusting (or not) factors of production} 
-\label{sec:fs_fop}
-%------------------------------
-
-%------------------------------
-\subsubsection{Including energy (or not)} 
-\label{sec:fs_energy}
-%------------------------------
-
-%------------------------------
-\subsubsection{CES nesting} 
-\label{sec:fs_nesting}
-%------------------------------
-
-%++++++++++++++++++++++++++++++
-\subsection{Factor substitutability} 
-\label{sec:substitutability}
-%++++++++++++++++++++++++++++++
-
-Table~\ref{tab:CES_sigma} shows 
-substitutability parameters~($\sigma_i$ values) 
-for all CES modeling decisions.
-
-**** Note: At the present time, Table~\ref{tab:CES_sigma}
-requires a LOT of effort to interpret, 
-because $\sigma_1$ and $\sigma$ have different meanings
-for each nesting.
-I'm planning to change the table to make interpretation easier. ---MKH ****
-
-**** Is there a graph we want to make here? ---MKH ****
-%
-<<CES_sigma, results="asis">>=
-myXTable(filter(AllCoeffs, model=="CES") %>% 
-           select(Country, model, flavor, energy, nest, cst, sigma_1, sigma),
-         caption="Factor substitution~($\\sigma$) for CES models.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-%
-
-%------------------------------
-\subsubsection{Rejecting (or adhering to) the cost share theorem} 
-\label{sec:sigma_cst}
-%------------------------------
-
-%------------------------------
-\subsubsection{Quality-adjusting (or not) factors of production} 
-\label{sec:sigma_fop}
-%------------------------------
-
-%------------------------------
-\subsubsection{Including energy (or not)} 
-\label{sec:sigma_energy}
-%------------------------------
-
-%------------------------------
-\subsubsection{CES nesting} 
-\label{sec:sigma_nesting}
-%------------------------------
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \section*{Reproducible Research}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% In the spirit of Reproducible Research \citep{Gandrud:2013vx}, 
-% all data, spreadsheets, \texttt{R} code \citep{R}, and other materials 
-% associated with this paper can be found at\\*
-% \protect\url{https://github.com/MatthewHeun/Econ-Growth-R-Analysis}.
-
-%% References
-%%
-%% Following citation commands can be used in the body text:
-%%
-%%  \citet{key}  ==>>  Jones et al. (1990)
-%%  \citep{key}  ==>>  (Jones et al., 1990)
-%%
-%% Multiple citations as normal:
-%% \citep{key1,key2}         ==>> (Jones et al., 1990; Smith, 1989)
-%%                            or  (Jones et al., 1990, 1991)
-%%                            or  (Jones et al., 1990a,b)
-%% \cite{key} is the equivalent of \citet{key} in author-year mode
-%%
-%% Full author lists may be forced with \citet* or \citep*, e.g.
-%%   \citep*{key}            ==>> (Jones, Baker, and Williams, 1990)
-%%
-%% Optional notes as:
-%%   \citep[chap. 2]{key}    ==>> (Jones et al., 1990, chap. 2)
-%%   \citep[e.g.,][]{key}    ==>> (e.g., Jones et al., 1990)
-%%   \citep[see][pg. 34]{key}==>> (see Jones et al., 1990, pg. 34)
-%%  (Note: in standard LaTeX, only one note is allowed, after the ref.
-%%   Here, one note is like the standard, two make pre- and post-notes.)
-%%
-%%   \citealt{key}          ==>> Jones et al. 1990
-%%   \citealt*{key}         ==>> Jones, Baker, and Williams 1990
-%%   \citealp{key}          ==>> Jones et al., 1990
-%%   \citealp*{key}         ==>> Jones, Baker, and Williams, 1990
-%%
-%% Additional citation possibilities
-%%   \citeauthor{key}       ==>> Jones et al.
-%%   \citeauthor*{key}      ==>> Jones, Baker, and Williams
-%%   \citeyear{key}         ==>> 1990
-%%   \citeyearpar{key}      ==>> (1990)
-%%   \citetext{priv. comm.} ==>> (priv. comm.)
-%%   \citenum{key}          ==>> 11 [non-superscripted]
-%% Note: full author lists depends on whether the bib style supports them;
-%%       if not, the abbreviated list is printed even when full requested.
-%%
-%% For names like della Robbia at the start of a sentence, use
-%%   \Citet{dRob98}         ==>> Della Robbia (1998)
-%%   \Citep{dRob98}         ==>> (Della Robbia, 1998)
-%%   \Citeauthor{dRob98}    ==>> Della Robbia
-
-%% References with bibTeX database:
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{References}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% \bibliographystyle{model2-names}
-%%\bibliography{<your-bib-database>}
-% \bibliography{Paper2.bib}
-
-%% Authors are advised to submit their bibtex database files. They are
-%% requested to list a bibtex style file in the manuscript if they do
-%% not want to use model2-names.bst.
-
-%% References without bibTeX database:
-
-% \begin{thebibliography}{00}
-
-%% \bibitem must have one of the following forms:
-%%   \bibitem[Jones et al.(1990)]{key}...
-%%   \bibitem[Jones et al.(1990)Jones, Baker, and Williams]{key}...
-%%   \bibitem[Jones et al., 1990]{key}...
-%%   \bibitem[\protect\citeauthoryear{Jones, Baker, and Williams}{Jones
-%%       et al.}{1990}]{key}...
-%%   \bibitem[\protect\citeauthoryear{Jones et al.}{1990}]{key}...
-%%   \bibitem[\protect\astroncite{Jones et al.}{1990}]{key}...
-%%   \bibitem[\protect\citename{Jones et al., }1990]{key}...
-%%   \harvarditem[Jones et al.]{Jones, Baker, and Williams}{1990}{key}...
-%%
-
-% \bibitem[ ()]{}
-
-% \end{thebibliography}
-
-%% The Appendices part is started with the command \appendix;
-%% appendix sections are then done as normal sections
-%% \appendix
-%% \section{}
-%% \label{}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \appendix
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Correlograms} 
-\label{sec:correlograms}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-This appendix contains correlograms for all models.
-
-%++++++++++++++++++++++++++++++
-\subsection{Correlograms for the reference models} 
-\label{sec:correlograms_ref}
-%++++++++++++++++++++++++++++++
-
-In this section we present correlograms for the reference (exponential-only) models.
-
-<<Correlograms_Exp, echo=FALSE, message=FALSE>>=
-leaf_apply(l = modelsExp, class = c("lm"), f = function(model, name){
-  acf(resid(model), main=name)
-})
-@
-
-%++++++++++++++++++++++++++++++
-\subsection{Correlograms for models that adhere to the cost-share theorem} 
-\label{sec:correlograms_CST}
-%++++++++++++++++++++++++++++++
-
-In this section we present correlograms for all models that adhere to the cost-share theorem.
-
-<<Correlograms_CST, echo=FALSE, message=FALSE>>=
-leaf_apply(l = modelsCST, class = c("lm", "plm"), f = function(model, name){
-  acf(resid(model), main=name)
-})
-@
-
-%++++++++++++++++++++++++++++++
-\subsection{Correlograms for models that reject the cost-share theorem} 
-\label{sec:correlograms_noCST}
-%++++++++++++++++++++++++++++++
-
-In this section we present correlograms for all models that reject the cost-share theorem.
-
-<<Correlograms_noCST, echo=FALSE, message=FALSE>>=
-leaf_apply(l = models, class = c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, name){
-  acf(resid(model), main=name)
-})
-@
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Statistical details on all models} 
-\label{sec:staistical_details}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-In this section, we present statistical details of all models.
-
-At the moment, this is a simple example of two models.
-I hope to develop a table later, after I figure out some things.
-Both models are CES models with energy fitted to Quality-adjusted data using the ($kl$)($e$) nesting.
-In Table~\ref{tab:stat_details_table}, Model 1 is for Portugal, and Model 2 is for the UK.
-
-<<stat_details_table, results="asis">>=
-texreg(list(models$PT$adjusted$withE$CES$kle, models$UK$adjusted$withE$CES$kle), 
-       dcolumn = TRUE, 
-       booktabs = TRUE, 
-       use.packages = FALSE, 
-       label=paste0("tab:", opts_current$get("label")), 
-       caption = "Example output from \\texttt{texreg}.",
-       caption.above = TRUE, 
-       digits = 6,
-       fontsize = "tiny",
-       float.pos = "hb")
-@
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Cobb-Douglas Graveyard} 
-\label{sec:cd_results}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-This section is the graveyard for information pertaining to the Cobb-Douglas model.
-
-%------------------------------
-\subsubsection{Cobb-Douglas Production Function} 
-\label{sec:CDe}
-%------------------------------
-
-The Cobb-Douglas production function can be expressed as
-%
-\begin{equation} \label{eq:CD}
-  y = \theta A k^{\alpha_1} l^{\alpha_2} \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)} \; ,
-\end{equation}
-%
-where 
-$y \equiv Y/Y_{0}$,
-$\theta$ is a scale parameter,
-e is the base of the natural logarithm, 
-$\lambda$ is represents the pace of technological progress,
-$t$ (time) is measured in years,
-$k \equiv K/K_{0}$, 
-$l \equiv L/L_{0}$, 
-$Y$ (economic output) is represented by GDP, 
-$K$ (capital) is expressed in currency units, 
-$L$ (labor) is expressed in workers or work-hours/year, and
-the 0 subscript indicates values at an initial year.%
-  \footnote{Dimensionless, indexed quantities are represented by 
-  lower-case symbols 
-  ($y$, $k$, $l$, $e$, $q$, $x$, and $u$), and dimensional 
-  quantities are represented by upper-case symbols 
-  ($Y$, $K$, $L$, $E$, $Q$, $X$, and $U$). 
-  Model parameters are represented by Greek letters
-  ($\alpha_1$, $\alpha_2$, $\lambda$, $\theta$).
-  }
-Constant returns to scale are represented by the constraint
-$\alpha_1 + \alpha_2 = 1$.
-
-The capital-labor Cobb-Douglas production function shown in Equation~\ref{eq:CD}
-can be augmented to include an energy term:
-%
-\begin{equation} \label{eq:CDe}
-  y = \theta A k^{\alpha_1} l^{\alpha_2} e^{\alpha_3} \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)} \; ,
-\end{equation}
-%
-where $e \equiv E/E_0$, and $E$ is in units of energy per time, typically TJ/year.
-The energy-augmented Cobb-Douglas production function 
-is often assumed to have constant returns to scale for the three factors 
-of production: $\alpha_1 + \alpha_2 + \alpha_3 = 1$.
-The term $A$ is known as total factor productivity,
-and $\lambda$ is the Solow residual. 
-%
-<<Graphs CD-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Cobb-Douglas models that reject the cost-share theorem. Solid line is historical GDP.">>=
-fittedGraphNoCST(filter(fitted_and_resid_data, model=="CD" & cst=="Reject CST"))
-@
-
-%
-<<Graphs CD-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for Cobb-Douglas models.">>=
-residualPlot(filter(fitted_and_resid_data, model=="CD" & cst=="Reject CST"))
-@
-
-Table~\ref{tab:Effect_of_CST_CD} shows the effect of the CST 
-on fitted parameters for the Cobb-Douglas model and the exponential-only model.
-The Cobb-Douglas models show lower $mse$ than the exponential-only models.
-The Cobb-Douglas models also reduce solow residual ($\lambda$) relative
-to the exponential-only case.
-%
-<<Effect_of_CST_CD, results="asis">>=
-myXTable(filter(AllCoeffs, (model=="CD" & flavor=="Unadjusted" & energy=="Without energy") | model=="exp") %>% 
-           select(Country, model, cst, scale, lambda, alpha_1, alpha_2, mse),
-         caption="Model parameters for Cobb-Douglas models with unadjusted factors of production, without energy.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-%
-
-Table~\ref{tab:CD_coeffs} shows coefficients for all fitted Cobb-Douglas models
-and the reference model (exponential-only).
-%
-<<CD_coeffs, results="asis">>=
-myXTable(filter(AllCoeffs, model=="CD" | model=="exp") %>% 
-           select(Country, model, flavor, energy, cst, scale, lambda, alpha_1, alpha_2, alpha_3, mse),
-         caption="Model parameters for all Cobb-Douglas models.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-%
-
-Table~\ref{tab:DSRmse_CD} shows $\Delta \lambda$ and $\Delta mse$ results for the Cobb-Douglas models.
-%
-<<DSRmse_CD, results="asis">>=
-myXTable(filter(AllCoeffs, model=="CD") %>% select(Country, model, flavor, energy, cst, Dlambda, Dmse),
-         caption="$\\Delta \\lambda$ and $\\Delta mse$ for Cobb-Douglas models.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-%
-
-%
-Figures~\ref{fig:DSRmse_CD_graph} and~\ref{fig:percDSRmse_CD_graph} summarize 
-$\Delta \lambda$ and $\Delta mse$ 
-results for the Cobb-Douglas model.
-%
-<<DSRmse_CD_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta mse$) for the Cobb-Douglas model relative to the exponential-only model.">>=
-ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CD"), mapping=aes(x=Dmse, y=Dlambda, color=energy, size=cst)) +
-  facet_grid(Country ~ flavor) +
-  scale_size_manual(values=c(2,3.5)) +
-  xlab(expression(Delta * mse)) + 
-  scale_x_continuous(breaks=seq(-0.01, 0, 0.005), limits=c(-0.012, 0.003)) +  
-  ylab(expression(Delta * lambda)) +
-  scale_y_continuous(limits=c(-0.04, 0)) +
-  xy_theme() + 
-  theme(legend.title=element_blank())
-@
-%
-<<percDSRmse_CD_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Percentage change in Solow Residuals~($\\Delta\\lambda \\, [\\%]$) and mean squared error~($\\Delta mse \\, [\\%]$) for the Cobb-Douglas model relative to exponential-only models.">>=
-ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CD"), mapping=aes(x=percDmse, y=percDlambda, color=energy, size=cst)) +
-  facet_grid(Country ~ flavor) +
-  scale_size_manual(values=c(2,3.5)) +
-  xlab(expression(paste(Delta * mse, " [%]"))) + 
-  scale_x_continuous(breaks=seq(-50, 50, 50), limits=c(-90, 50)) +  
-  ylab(expression(paste(Delta * lambda, " [%]"))) +
-  scale_y_continuous(breaks=seq(-80, 0, 20), limits=c(-100, 10)) +  
-  xy_theme() + 
-  theme(legend.title=element_blank())
-@
-%
-<<DSRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta mse$) for the CES modles relative to the exponential-only model.">>=
-ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=Dmse, y=Dlambda, color=energy, size=cst, shape=nest)) +
-  scale_size_manual(values=c(2,3.5)) +
-  scale_shape_manual(values=c(16,17,18,15)) +
-  facet_grid(Country ~ flavor) +
-  xlab(expression(Delta * mse)) + 
-  scale_x_continuous(breaks=seq(-0.005, 0, 0.005)) +  
-  ylab(expression(Delta * lambda)) +
-  xy_theme() +
-  theme(legend.title=element_blank())
-@
-%
 

### 2015-07-30 Articles/Brockway_Rebound_2015/Brockway_2015.Rnw
Updates to Brockway analysis.

@@
 # library(mosaic)
-# library(xtable)
+library(xtable)
 library(knitr)
@@
   # Set TRUE on an individual chunk to see its code.
-  echo=FALSE,
-  # Sets all table captions to the top.
-  xtable.caption.placement="top"
+  echo=FALSE
 )
@@
 # Set the working directory to the project directory.
-print(getwd())
-historicalData <- read.csv(file = "data/BrockwayData.csv")
+historicalData <- read.csv(file = file.path("data", "BrockwayData.csv"))
+countries <- c("UK", "US", "CN")
 @
@@
 # Relevel factors before plotting
-historicalDataForGraph$Country <- relevelFactor(as.factor(historicalDataForGraph$Country), c("UK", "US", "CN"))
+historicalDataForGraph$Country <- relevelFactor(as.factor(historicalDataForGraph$Country), countries)
 
@@
   # In RStudio, be sure to set the working directory to the source file directory.
-  models <- lapply(c("UK", "US", "CN"), function(coun){
+  models <- lapply(countries, function(coun){
     return(cesModel(iY ~ iK + iL + iU + iYear, filter(historicalData, Country==coun, nest=1:3)))
   })
+  names(models) <- countries
   # Save the models.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+<<resultsUK, echo=TRUE>>=
+summary(models[["UK"]])
+naturalCoef(models[["UK"]])
+@
+
+<<resultsUS, echo=TRUE>>=
+summary(models[["US"]])
+naturalCoef(models[["US"]])
+@
+
+<<resultsCN, echo=TRUE>>=
+summary(models[["CN"]])
+naturalCoef(models[["CN"]])
+@
+
+The following provides the results in tabular form.
+
+<<resultsTable>>=
+fittedParamsTable <- lapply(countries, function(coun){
+  cbind(coun, naturalCoef(models[[coun]]))
+}) %>% do.call(rbind, .)
+@
+
+<<print_resultsTable, results="asis">>=
+myXTable <- function(data, caption, label, digits=2){
+  table <- xtable(data, caption=caption, label=label, digits=digits)
+  print(table, 
+        caption.placement="top", 
+        size="\\tiny", 
+        include.rownames=FALSE, 
+        math.style.negative=TRUE, 
+        booktabs=TRUE)
+}
+myXTable(fittedParamsTable,
+         caption="Tabular results.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
 

### 2015-07-31 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Now including row numbers in bar charts.

@@
                                 bar_chart_data$energy, bar_chart_data$nest, sep=", ")
+  # Add row numbers to the label column
+  bar_chart_data$label <- paste(paste0(1:length(bar_chart_data$label), ". "), bar_chart_data$label)
   # Capture the order that we want for the models on the vertical axis.

### 2015-07-31 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Now including correct colors and shapes. This is for the residual plots.

@@
 <<ResidualPlotFunction>>=
-residualPlot <- function(data){
+residualPlot <- function(data, withEnergyShape = 0){
   ggplot() +
-    geom_line(data=data, mapping=aes(x=Year, y=Residuals, linetype=energy)) +
-    scale_linetype_manual(values=c(2,3), name="") +
+    geom_point(data=data, mapping=aes(x=Year, y=Residuals, shape=energy, color=energy)) +
+    scale_shape_manual(values=c(1, withEnergyShape)) +
     facet_grid(Country ~ flavor) +
@@
 <<Graphs CESkle-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(kl$)$e$ nesting.">>=
-residualPlot(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest=="kle" | nest=="kl")))
+residualPlot(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest=="kle" | nest=="kl")), 
+             withEnergyShape = 0) # square
 @
@@
 <<Graphs CESlek-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with ($le$)$k$ nesting.">>=
-residualPlot(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest == "lek" | nest=="kl")))
+residualPlot(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest == "lek" | nest=="kl")),
+             withEnergyShape = 3) # plus
 @
@@
 <<Graphs CESekl-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(ek$)$l$ nesting.">>=
-residualPlot(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest=="ekl" | nest=="kl")))
+residualPlot(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest=="ekl" | nest=="kl")),
+             withEnergyShape = 4) # times
 @

### 2015-07-31 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Now using correct sizes for residual graphs.

@@
   ggplot() +
-    geom_point(data=data, mapping=aes(x=Year, y=Residuals, shape=energy, color=energy)) +
+    geom_point(data=data, mapping=aes(x=Year, y=Residuals, shape=energy, color=energy, size=energy)) +
     scale_shape_manual(values=c(1, withEnergyShape)) +
+    scale_size_manual(values=c(4,4)) +
     facet_grid(Country ~ flavor) +
@@
     ylab("r") + 
-    xy_theme()
+    xy_theme() +
+    theme(legend.title=element_blank())
 }
@@
   scale_size_manual(values=c(2,4)) +
-  scale_shape_manual(values=c(1,0,3,4)) + # 16,17,18,15
+  scale_shape_manual(values=c(1,0,3,4)) + 
   facet_grid(Country ~ flavor) +
-  # scale_x_continuous(breaks=seq(0, 0.02, 0.01), limits=c(0, 0.02)) +  
   ylab(expression(lambda)) +
-  # scale_y_continuous(breaks=seq(0, 0.04, 0.01), limits=c(0, 0.04)) +  
   xy_theme() +

### 2015-07-31 Articles/Brockway_Rebound_2015/Brockway_2015.Rnw
Now uses better x-axis scale for hist data.

@@
 library(ggplot2)
-# library(mosaic)
 library(xtable)
 library(knitr)
-# library(texreg)
 
@@
                line_types = c(1,2,4,3)) + 
+  scale_x_continuous(breaks=c(1960, 1980, 2000)) +
   scale_y_continuous(breaks=c(1, 10, 20)) +

### 2015-07-31 Articles/Brockway_Rebound_2015/Brockway_2015.Rnw
Eliminated spaces in chunk name.

@@
 
-<<Historical Data Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Historical data.", warning=FALSE>>=
+<<Historical_Data_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Historical data.", warning=FALSE>>=
 # Melt data for plotting

### 2015-08-05 Articles/Brockway_Rebound_2015/Brockway_2015.Rnw
Looking at US and CN results in detail.

@@
 
+First, look a the UK results.
+
 <<resultsUK, echo=TRUE>>=
@@
 @
+
+The fitted model for the UK is not near any boundaries
+to the economically-meaningful solution space.
+
+Next, look at the US results.
 
@@
 
+These results for the US deserve additional scrutiny.
+The winning US model looks like a boundary model, 
+with $\delta = 1$ and $\rho_1 = -1$.
+Indeed, this appears to be Boundary Model~7 in \ref{sec:boundary_models}.
+Note that $\rho_1 = -1$ corresponds to $\sigma_1 = \infty$.
+However, the winning model results report a value for $\sigma$, 
+which would be unknowable in Boundary Model~7.
+
+Upon closer examination, we find the following.
+
+<<InvestigateUS, echo=TRUE>>=
+# Establish some variable names to make code readable
+usdata <- filter(historicalData, Country=="US")
+usmodel <- models[["US"]]
+# Get the boundary model that is near
+bmod7 <- (attr(usmodel, "model.attempts"))$`07:*N1-`
+# Did Boundary Model 7 converge?
+bmod7$converged
+# The fitted parameters in bmod7 are as expected,
+# i.e., we get NA for both rho and sigma, 
+# and we have delta = 1.
+naturalCoef(bmod7)
+# Calculate the sse for bmod7
+sum(resid(bmod7)^2)
+# Compare to sse for fitted model
+sum(resid(usmodel)^2)
+# So, the sse for the winning model is, indeed, 
+# less than the sse for the boundary model.
+# To investigate why that is happening,
+# let's first look at the coefficient for delta
+# in the fitted model.
+naturalCoef(usmodel)$delta
+# Comes back as 1.
+# But machine precision is an issue here. 
+# Try this:
+naturalCoef(usmodel)$delta - 1
+# to find that delta is not EXACTLY 1.00000.
+# And, this makes a big difference.
+# To investigate further, Randy made a function
+# that calculates the ln(y) given historical data and 
+# some model coefficients.
+logces <- function(coefs, data=usdata) {
+  coefs <- as.list(coefs)
+  with(coefs,
+       log(gamma) + 
+         lambda * data$iYear + 
+         (-1/rho) * (
+           log( 
+             delta * ( delta_1 * data$iK^(-rho_1) + (1-delta_1) * data$iL^(-rho_1))^(rho/rho_1) +
+               (1-delta) * data$iU^(-rho))
+         )
+  )
+}
+# Now, calculate sse in many different ways
+# First, the boundary model (repeated from above).
+sum(resid(bmod7)^2)
+# Next from the winning model (repeated from above).
+sum(resid(usmodel)^2)
+# Using the logces function
+sum((log(usdata$iY) - logces(coef(usmodel)))^2)
+# Also try with the boundary model.
+# First, need to make an array of coefficients that
+# matches the full model
+bmod7coeffs <- coef(bmod7)
+bmod7coeffs[["gamma"]] <- exp(coef(bmod7)[["logscale"]])
+bmod7coeffs[["rho"]] <- 2 # value doesn't matter, because delta = 1.
+sum((log(usdata$iY) - logces(bmod7coeffs))^2)
+# This result matches the sse value from Boundary Model 7.
+# The above tests demonstrate that the logces function is correct.
+# Let's understand the sensitivity of sse to 
+# the fitted coefficients.
+# To do so, we'll calculate sse using rounded values 
+# of the model coefficients.
+# Try rounding to the 16th decimal place
+sum((log(usdata$iY) - logces(round(coef(usmodel), 16)))^2)
+# The above works as expected. We
+# reproduce the sse value from the model itself.
+# Try rounding to the 15th decimal place
+sum((log(usdata$iY) - logces(round(coef(usmodel), 15)))^2)
+# Same sse value as 16th decimal place.
+# Again, works as expected.
+# Now, try rounding to the 14th decimal place
+sum((log(usdata$iY) - logces(round(coef(usmodel), 14)))^2)
+# The sse value is slightly different!
+# 13th decimal place
+sum((log(usdata$iY) - logces(round(coef(usmodel), 13)))^2)
+# 12th decimal place
+sum((log(usdata$iY) - logces(round(coef(usmodel), 12)))^2)
+# Suddenly, we get a big jump in sse value.
+# Note that the value of delta above
+coef(usmodel)[["delta"]] - 1
+# is on the order of 10^-13,
+# right at the point we begin to see 
+# significant differences in sse.
+@
+
+At this point, Randy and I think that 
+our code is correct and we are seeing reality.
+We showed that $sse$ is sensitive to very small variations
+(in the 13$^{\mathrm{th}}$ decimal place!)
+in the values of the fitted coefficients.
+Moving slightly away from the boundary
+appears to improve the $sse$ enough
+so that the full fitted model is superior to 
+Boundary Model~7.
+And, our software was correct to report
+a model that contained all the parameters.
+
+This hypersensitivity to fitted coefficient values
+may come about because the value for $\rho$ is so large.
+Regardless of the reason, the hypersensitivity
+is unnerving (to me). 
+And, it provides additional encouragement to
+determine the statistical precision of the fitted values.
+
+Finally, look at the CN results.
+
 <<resultsCN, echo=TRUE>>=
@@
 
-The following provides the results in tabular form.
+Similar to the US results above, we can
+investigate the CN results in more detail.
+It looks like we are on a boundary:
+$\delta_1 = 1$ is Boundary Model~11
+in \ref{sec:boundary_models}.
+But, in fact, we are not.
 
-<<resultsTable>>=
-fittedParamsTable <- lapply(countries, function(coun){
-  cbind(coun, naturalCoef(models[[coun]]))
-}) %>% do.call(rbind, .)
+<<InvestigateCN, echo=TRUE>>=
+cndata <- filter(historicalData, Country=="CN")
+cnmodel <- models[["CN"]]
+naturalCoef(cnmodel)$delta_1
+naturalCoef(cnmodel)$delta_1 - 1
+# Similar to the US situation, we are close to,
+# but not exactly on, the boundary.
+# Get the boundary model that is nearby.
+bmod11 <- (attr(cnmodel, "model.attempts"))$`11:1-**`
+# Calcualte sse for the fitted model.
+sum(resid(cnmodel)^2)
+# Calculate sse for the nearby boundary model.
+sum(resid(bmod11)^2)
 @
 
-<<print_resultsTable, results="asis">>=
+Again, I think we are looking at reality here.
+The full fitted model is better than the nearby boundary model.
+
+I think this all means that we can use the 
+UK, US, and CN
+results straight away
+for rebound calculations.
+
+Tables~\ref{tab:print_resultsTable1} and~\ref{tab:print_resultsTable2}
+present the results in readable format.
+
+<<resultsTables>>=
+fittedParamsTable1 <- lapply(countries, function(coun){
+  cbind(coun, select(naturalCoef(models[[coun]]), scale, lambda, delta, delta_1, rho, rho_1))
+}) %>% do.call(rbind, .)
+
+fittedParamsTable2 <- lapply(countries, function(coun){
+  cbind(coun, select(naturalCoef(models[[coun]]), alpha_1, alpha_2, alpha_3, sigma_1, sigma))
+}) %>% do.call(rbind, .)
+
 myXTable <- function(data, caption, label, digits=2){
@@
 }
-myXTable(fittedParamsTable,
-         caption="Tabular results.",
+@
+
+<<print_resultsTable1, results="asis">>=
+myXTable(fittedParamsTable1,
+         caption="Tabular results (1).",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
+
+<<print_resultsTable2, results="asis">>=
+myXTable(fittedParamsTable2,
+         caption="Tabular results (2).",
          label=paste0("tab:", opts_current$get("label")), 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Boundary models} 
+\label{sec:boundary_models}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{table} \caption{CES boundary models (rows~1--20) and full model 
+(bottom row).} 
+\label{tab:CES_boundary_models} 
+  \begin{center}
+    \begin{tabular}{r c c c c l} 
+      \toprule
+      & $\delta_1$  & $\sigma_1$ & $\delta$   & $\sigma$ & Boundary model \\
+      \midrule
+      1. & 1           & ---        & 1          & ---      & $y = \theta A x_1$ 
+      \\
+      2. & 0           & ---        & 1          & ---      & $y = \theta A x_2$ 
+      \\
+      3. & ---         & ---        & 0          & ---      & $y = \theta A x_3$ 
+      \\
+      \midrule
+      4. & ---         & 0          & 1          & ---      & $y = \theta A \min 
+      (x_1, \, x_2)$ \\
+      5. & 1           & ---        & ---        & 0        & $y = \theta A \min 
+      (x_1, \, x_3)$ \\
+      6. & 0           & ---        & ---        & 0        & $y = \theta A \min 
+      (x_2, \, x_3)$ \\
+%
+      7. &             & $\infty$   & 1          & ---        
+            & $y = \theta A \left[ \delta_1 x_1 + (1 - \delta_1) x_2 \right]$ \\
+%
+      8. & 1           & ---        &            & $\infty$        
+            & $y = \theta A \left[ \delta x_1 + (1 - \delta) x_3 \right]$ \\
+%
+      9. & 0           & ---        &            & $\infty$        
+            & $y = \theta A \left[ \delta x_2 + (1 - \delta) x_3 \right]$ \\
+%
+     10. &             &            & 1          & ---
+            & $y = \theta A \left[ \delta_1 x_1^{-\rho_1} 
+                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{-1/
+                    \rho_1}$ \\
+%
+     11. & 1           & ---        &         & 
+            & $y = \theta A \left[ \delta x_1^{-\rho} 
+                    + \left(1 - \delta \right) x_3^{-\rho} \right] ^ {-1/\rho}$ 
+                    \\ 
+%
+     12. & 0           & ---        &            & 
+            & $y = \theta A \left[ \delta x_2^{-\rho} + \left(1 - \delta \right) 
+            x_3^{-\rho} \right]^{-1/\rho}$ \\
+      \midrule
+     13. & ---         & 0          & ---        & 0        & $y = \theta A \min 
+     (x_1, \, x_2, \, x_3)$ \\
+%
+     14. & ---         & 0          &            & $\infty$        
+            & $y = \theta A \left[ \delta \min (x_1, \, x_2) + \left( 1 - \delta 
+            \right) x_3  \right]$ \\
+%
+     15. &             & $\infty$   & ---        & 0
+            & $y = \theta A \min \left[ \delta_1 x_1 + \left(1 - \delta_1 
+            \right) x_2, \, x_3  \right]$ \\
+%
+     16. &             & $\infty$   &            & $\infty$        
+            & $y = \theta A \left\{ \delta \left[ \delta_1 x_1 + \left( 1 - 
+            \delta_1 \right) x_2 \right] 
+                    + \left( 1 - \delta \right) x_3  \right\}$ \\
+%
+     17. & ---         & 0          &            & 
+            & $y = \theta A \left\{ \delta \left[ \min \left( x_1, \, x_2 
+            \right) \right]^{-\rho}  
+                    + \left( 1 - \delta \right) x_3^{-\rho}  \right\} ^ 
+                    {-1/\rho}$ \\ 
+%
+     18. &            &            & ---     & 0
+            & $y = \theta A \min \left\{ \left[ \delta_1 x_1^{-\rho_1} 
+                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{-1/
+                    \rho_1}, \, x_3 \right\}$ \\ 
+%
+     19. &             &            &            & $\infty$
+            & $y = \theta A \left\{ \delta \left[ \delta_1 x_1^{-\rho_1} 
+                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{-1/
+                    \rho_1}  
+                    + \left( 1 - \delta \right) x_3  \right\}$ \\ 
+%
+     20. &             & $\infty$   &            &
+            & $y = \theta A \left\{ \delta \left[ \delta_1 x_1 
+                    + \left( 1 - \delta_1 \right) x_2 \right]^{-\rho}  
+                    + \left( 1 - \delta \right) x_3^{-\rho}  \right\} ^ 
+                    {-1/\rho}$ \\
+\midrule
+         &            &            &         & 
+            & $y = \theta A \left\{ \delta \left[ \delta_1 x_1^{-\rho_1} 
+                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{\rho/
+                    \rho_1}  
+                    + \left( 1 - \delta \right) x_3^{-\rho}  \right\} ^ 
+                    {-1/\rho}$ \\ 
+      \bottomrule
+    \end{tabular}
+  \end{center}
+\end{table}
+
 \end{document}

### 2015-08-05 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
new code to do limited resampling.

@@
 rerunModels=FALSE
+rerunResampling=FALSE
+nResamples <- 4 # Number of resamples
 # ********************************************************
@@
 
+<<Resampling>>=
+resampleFilename <- "EcolEcon2015kleResamples.rds"
+if (rerunResampling){
+  # Run some resampling on the PT and UK models that adhere to the cost-share theorem,
+  # includes energy, uses quality-adjusted variables, and employs the (kl)e nesting.
+  # This is u-g-l-y code. Just getting something running for now.
+  modPT <- models$PT$adjusted$withE$CES$kle
+  modUK <- models$UK$adjusted$withE$CES$kle
+  resamplesPT <- resampledFits(modPT, method = "wild", n = nResamples)
+  resamplesUK <- resampledFits(modUK, method = "wild", n = nResamples)
+  resampleCoeffs <- rbind(cbind(resamplesPT$coeffs, Country="PT"), cbind(resamplesUK$coeffs, Country="UK"))
+  resampleCoeffs$energy <- TRUE
+  resampleCoeffs$nest <- "(kl)e"
+  saveRDS(resampleCoeffs, file = resampleFilename)
+} else {
+  resampleCoeffs <- readRDS(resampleFilename)
+}
+@
+
 <<Fitted_and_Residuals>>=
+filenameResampleCoeffs <- ""
 fittedAndResidData <- function(model, id){

### 2015-08-05 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
New resamples.

@@
 
+<<ResamplingGraph>>=
+
+@
+
 <<Fitted_and_Residuals>>=
@@
 myXTable(filter(AllCoeffs, model=="CES" | model=="exp") %>% 
-           select(Country, model, flavor, energy, nest, cst, gamma, lambda, mse),
+           select(Country, model, flavor, energy, nest, cst, scale, lambda, mse),
          caption="$\\theta$, Solow residual, and $mse$ for CES models.",

### 2015-08-06 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Now 100 resamples for each model.

@@
 rerunResampling=FALSE
-nResamples <- 4 # Number of resamples
+nResamples <- 100 # Number of resamples
 # ********************************************************

### 2015-08-06 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Now including resampling graphs.

@@
 
-<<ResamplingGraph>>=
-
-@
-
 <<Fitted_and_Residuals>>=
@@
 
+%++++++++++++++++++++++++++++++
+\subsection{Resampling} 
+\label{sec:resampling}
+%++++++++++++++++++++++++++++++
+
+<<lambda_theta_resampling_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.5, fig.cap="$\\lambda$ and $\\theta$ values for resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
+standardScatterPlot(data=resampleCoeffs, mapping=aes(scale, lambda), facet_formula=~Country, alpha=0.1) +
+    labs(x=expression(theta), y=expression(lambda))
+@
+
+<<alpha_resampling_graph, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha_k$, $\\alpha_l$, and $\\alpha_e$ values for CES resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
+standardTriPlot(data=resampleCoeffs, facet_formula=~Country, alpha=0.05)
+@
+
+<<sigma1_delta1_resampling_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.5, fig.cap="$\\sigma_{(kl)}$ and $\\delta_1$ values for resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
+standardScatterPlot(data=resampleCoeffs, mapping=aes(delta_1, sigma_1), 
+                    facet_formula=~Country, alpha=0.1) +
+    coord_trans(y="sigma") +
+    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0), limits=c(0,1)) +
+    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0), limits=c(0, 1e6)) +
+    labs(x=expression(delta[1]), y=expression(sigma[kl]))
+@
+
+<<sigma_delta_resampling_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.5, fig.cap="$\\sigma_{(kl)e}$ and $\\delta$ values for resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
+standardScatterPlot(data=resampleCoeffs, mapping=aes(delta, sigma), 
+                    facet_formula=~Country, alpha=0.1) +
+    coord_trans(y="sigma") +
+    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0), limits=c(0,1)) +
+    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0), limits=c(0, 1e6)) +
+    labs(x=expression(delta), y=expression(sigma[kle]))
+@
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-08-06 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Change mse to sse.

--- 2015-08-06 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
@@
 In contrast, it is not necessarily true that 
-CES models will exhibit lower $mse$ than the reference model
+CES models will exhibit lower $sse$ than the reference model
 shown in Equation~\ref{eq:exponential-only-model}.
@@
 are poorly correlated to output~($y$),
-the constant returns to scale constraint may cause higher $mse$ for
+the constant returns to scale constraint may cause higher $sse$ for
 the CES model relative to the reference model.
@@
   res <- cbind(res, naturalCoef(modExp))
-  # Now caluculate mean squared error (mse) for each model.
-  sqResids <- resid(modExp)^2
-  mse <- sum(sqResids) / (length(sqResids))
-  res <- cbind(res, list(mse=mse))
+  # Now caluculate mean squared error (sse) for each model.
+  sse <- sum(resid(modExp)^2)
+  res <- cbind(res, list(sse=sse))
   return(res)
@@
   res <- cbind(res, naturalCoef(modCST))
-  # Now calculate the mean squared error (mse) for each model.
-  sqResids <- resid(modCST)^2
-  mse <- sum(sqResids)/(length(sqResids))
-  res <- cbind(res, list(mse=mse))
+  # Now calculate the mean squared error (sse) for each model.
+  sse <- sum(resid(modCST)^2)
+  res <- cbind(res, list(sse=sse))
   return(res)
@@
   res <- cbind(res, naturalCoef(mod))
-  # Now calculate the mean squared error (mse) for each model.
-  sqResids <- resid(mod)^2
-  mse <- sum(sqResids)/(length(sqResids))
-  res <- cbind(res, list(mse=mse))
+  # Now calculate the sum of squared error (sse) for each model.
+  sse <- sum(resid(mod)^2)
+  res <- cbind(res, list(sse=sse))
   return(res)
@@
 # Get reference values for lambda and sse.
-# ref <- filter(AllCoeffs, cst=="Adhere to CST" & flavor=="Unadjusted" & energy=="Without energy") %>% 
-#               select(Country, model, mse, lambda)
-ref <- filter(AllCoeffs, model=="exp") %>% select(Country, mse, lambda)
-colnames(ref)[colnames(ref)=="mse"] <- "mse_ref"
+ref <- filter(AllCoeffs, model=="exp") %>% select(Country, sse, lambda)
+colnames(ref)[colnames(ref)=="sse"] <- "sse_ref"
 colnames(ref)[colnames(ref)=="lambda"] <- "lambda_ref"
@@
                     Dlambda = abs(lambda) - abs(lambda_ref), 
-                    Dmse = mse - mse_ref,
+                    Dsse = sse - sse_ref,
                     percDlambda = Dlambda / abs(lambda_ref) * 100, 
-                    percDmse = Dmse / mse_ref * 100)
+                    percDsse = Dsse / sse_ref * 100)
 
@@
 }
-@
-
-<<ResamplingGraph>>=
-
 @
@@
 
-The mean squared error~($mse$) for any fitted model can be calculated by
-%
-\begin{equation} \label{eq:mse}
-  mse \equiv \frac{1}{N} \sum_{i=1}^N{r_i^2} .
-\end{equation}
-
 Figures~\ref{fig:Graphs CESkle-resid}--\ref{fig:Graphs CESekl-resid}
@@
 the Solow residual~($\lambda$) and
-goodness of fit~($mse$)
+goodness of fit~($sse$)
 for all modeling decisions.
@@
 myXTable(filter(AllCoeffs, model=="CES" | model=="exp") %>% 
-           select(Country, model, flavor, energy, nest, cst, scale, lambda, mse),
-         caption="$\\theta$, Solow residual, and $mse$ for CES models.",
+           select(Country, model, flavor, energy, nest, cst, scale, lambda, sse),
+         caption="$\\theta$, Solow residual, and $sse$ for CES models.",
          label=paste0("tab:", opts_current$get("label")), 
@@
 To do so, we define 
-$\Delta \lambda$ and $\Delta mse$, where
+$\Delta \lambda$ and $\Delta sse$, where
 %
@@
 %
-\begin{equation} \label{eq:delta_mse}
-  \Delta mse \equiv mse - mse_{ref},
+\begin{equation} \label{eq:delta_sse}
+  \Delta sse \equiv sse - sse_{ref},
 \end{equation}
 %
-with~$\lambda_{ref}$ and $mse_{ref}$ being the values 
-of the Solow residual and $mse$ for the reference model, respectively.
+with~$\lambda_{ref}$ and $sse_{ref}$ being the values 
+of the Solow residual and $sse$ for the reference model, respectively.
 On a percentage basis,
@@
 %
-\begin{equation} \label{eq:delta_mse_perc}
-  \Delta mse \, [\%] = \frac{100 \, \Delta mse}{mse_{ref}} 
-            = \frac{100 \, mse}{mse_{ref}} - 1 \; .
+\begin{equation} \label{eq:delta_sse_perc}
+  \Delta sse \, [\%] = \frac{100 \, \Delta sse}{sse_{ref}} 
+            = \frac{100 \, sse}{sse_{ref}} - 1 \; .
 \end{equation}
 
-When $\Delta \lambda$, $\Delta \lambda \, [\%]$, or $\Delta mse$ are negative, 
+When $\Delta \lambda$, $\Delta \lambda \, [\%]$, or $\Delta sse$ are negative, 
 we observe reduction in the Solow residual ($\lambda$) or
-the fitting residuals ($mse$)
+the fitting residuals ($sse$)
 relative to the reference model.
 
-Figures~\ref{fig:DSRmse_CES_graph} and~\ref{fig:percDSRmse_CES_graph} summarize 
-$\Delta \lambda \, [\%]$ and $\Delta mse \, [\%]$ 
+Figure~\ref{fig:DSRsse_CES_graph} summarizes 
+$\lambda$ and $sse$ 
 results for CES models.
-%
-<<percDSRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Percentage change in Solow Residuals~($\\Delta\\lambda \\, [\\%]$) and mean squared error~($\\Delta mse \\, [\\%]$) for the CES models relative to the exponential-only model.">>=
+
+<<SRsse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Solow Residuals~($\\lambda$) and mean squared error~($sse$).
+$\\lambda$ and $sse$ values for the reference (exponential-only) model are shown as gridlines.">>=
 ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=percDmse, y=percDlambda, color=energy, size=cst, shape=nest)) +
-  scale_size_manual(values=c(2,3.5)) +
-  scale_shape_manual(values=c(16,17,18,15)) +
-  facet_grid(Country ~ flavor) +
-  xlab(expression(paste(Delta * mse, " [%]"))) + 
-  scale_x_continuous(breaks=seq(-80, 0, 20)) +  
-  ylab(expression(paste(Delta * lambda, " [%]"))) +
-  scale_y_continuous(breaks=seq(-80, 0, 20), limits=c(-100, 10)) +  
-  xy_theme() +
-  theme(legend.title=element_blank())
-@
-
-<<SRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Solow Residuals~($\\lambda$) and mean squared error~($mse$).
-$\\lambda$ and $mse$ values for the reference (exponential-only) model are shown as gridlines.">>=
-ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=mse, y=lambda, color=energy, size=cst, shape=nest)) +
-  geom_vline(aes(xintercept = mse), filter(AllCoeffs, model=="exp") %>% select(Country, mse), colour="gray50", size=0.1) +
+  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=sse, y=lambda, color=energy, size=cst, shape=nest)) +
+  geom_vline(aes(xintercept = sse), filter(AllCoeffs, model=="exp") %>% select(Country, sse), colour="gray50", size=0.1) +
   geom_hline(aes(yintercept = lambda), filter(AllCoeffs, model=="exp") %>% select(Country, lambda), colour="gray50", size=0.1) +
@@
   facet_grid(Country ~ flavor) +
+  scale_y_continuous(breaks=c(0, 0.01, 0.02), limits=c(0, 0.03)) +
+  xlab("SSE") + 
   ylab(expression(lambda)) +
@@
 
+%++++++++++++++++++++++++++++++
+\subsection{Resampling} 
+\label{sec:resampling}
+%++++++++++++++++++++++++++++++
+
+<<resample_graph_lambda_theta, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.5, fig.cap="$\\lambda$ and $\\theta$ values for resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
+standardScatterPlot(data=resampleCoeffs, mapping=aes(scale, lambda), facet_formula=~Country, alpha=0.1) +
+    scale_x_continuous(breaks=c(0.95, 1.0, 1.05)) + 
+    scale_y_continuous(breaks=c(0, 0.005, 0.01), limits=c(0, 0.01)) +
+    labs(x=expression(theta), y=expression(lambda))
+@
+
+<<resample_graph_alpha, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.0, fig.cap="$\\alpha_k$, $\\alpha_l$, and $\\alpha_e$ values for CES resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
+standardTriPlot(data=resampleCoeffs, facet_formula=~Country, alpha=0.1,
+                labels=c("alpha[e]", "alpha[k]", "alpha[l]"))
+@
+
+<<resample_graph_sigma1_delta1, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.5, fig.cap="$\\sigma_{(kl)}$ and $\\delta_1$ values for resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
+standardScatterPlot(data=resampleCoeffs, mapping=aes(delta_1, sigma_1), 
+                    facet_formula=~Country, alpha=0.1) +
+    coord_trans(y="sigma") +
+    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0), limits=c(0,1)) +
+    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0), limits=c(0, 1e6)) +
+    labs(x=expression(delta[1]), y=expression(sigma[kl]))
+@
+
+<<resample_graph_sigma_delta, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.5, fig.cap="$\\sigma_{(kl)e}$ and $\\delta$ values for resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
+standardScatterPlot(data=resampleCoeffs, mapping=aes(delta, sigma), 
+                    facet_formula=~Country, alpha=0.1) +
+    coord_trans(y="sigma") +
+    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0), limits=c(0,1)) +
+    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0), limits=c(0, 1e6)) +
+    labs(x=expression(delta), y=expression(sigma[kle]))
+@
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 on fitted parameters for the Cobb-Douglas model and the exponential-only model.
-The Cobb-Douglas models show lower $mse$ than the exponential-only models.
+The Cobb-Douglas models show lower $sse$ than the exponential-only models.
 The Cobb-Douglas models also reduce solow residual ($\lambda$) relative
@@
 myXTable(filter(AllCoeffs, (model=="CD" & flavor=="Unadjusted" & energy=="Without energy") | model=="exp") %>% 
-           select(Country, model, cst, scale, lambda, alpha_1, alpha_2, mse),
+           select(Country, model, cst, scale, lambda, alpha_1, alpha_2, sse),
          caption="Model parameters for Cobb-Douglas models with unadjusted factors of production, without energy.",
@@
 myXTable(filter(AllCoeffs, model=="CD" | model=="exp") %>% 
-           select(Country, model, flavor, energy, cst, scale, lambda, alpha_1, alpha_2, alpha_3, mse),
+           select(Country, model, flavor, energy, cst, scale, lambda, alpha_1, alpha_2, alpha_3, sse),
          caption="Model parameters for all Cobb-Douglas models.",
@@
 
-Table~\ref{tab:DSRmse_CD} shows $\Delta \lambda$ and $\Delta mse$ results for the Cobb-Douglas models.
-%
-<<DSRmse_CD, results="asis">>=
-myXTable(filter(AllCoeffs, model=="CD") %>% select(Country, model, flavor, energy, cst, Dlambda, Dmse),
-         caption="$\\Delta \\lambda$ and $\\Delta mse$ for Cobb-Douglas models.",
+Table~\ref{tab:DSRsse_CD} shows $\Delta \lambda$ and $\Delta sse$ results for the Cobb-Douglas models.
+%
+<<DSRsse_CD, results="asis">>=
+myXTable(filter(AllCoeffs, model=="CD") %>% select(Country, model, flavor, energy, cst, Dlambda, Dsse),
+         caption="$\\Delta \\lambda$ and $\\Delta sse$ for Cobb-Douglas models.",
          label=paste0("tab:", opts_current$get("label")), 
@@
 %
-Figures~\ref{fig:DSRmse_CD_graph} and~\ref{fig:percDSRmse_CD_graph} summarize 
-$\Delta \lambda$ and $\Delta mse$ 
+Figures~\ref{fig:DSRsse_CD_graph} and~\ref{fig:percDSRsse_CD_graph} summarize 
+$\Delta \lambda$ and $\Delta sse$ 
 results for the Cobb-Douglas model.
 %
-<<DSRmse_CD_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta mse$) for the Cobb-Douglas model relative to the exponential-only model.">>=
+<<DSRsse_CD_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta sse$) for the Cobb-Douglas model relative to the exponential-only model.">>=
 ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CD"), mapping=aes(x=Dmse, y=Dlambda, color=energy, size=cst)) +
+  geom_point(data=filter(AllCoeffs, model=="CD"), mapping=aes(x=Dsse, y=Dlambda, color=energy, size=cst)) +
   facet_grid(Country ~ flavor) +
   scale_size_manual(values=c(2,3.5)) +
-  xlab(expression(Delta * mse)) + 
+  xlab(expression(Delta * sse)) + 
   scale_x_continuous(breaks=seq(-0.01, 0, 0.005), limits=c(-0.012, 0.003)) +  
@@
 %
-<<percDSRmse_CD_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Percentage change in Solow Residuals~($\\Delta\\lambda \\, [\\%]$) and mean squared error~($\\Delta mse \\, [\\%]$) for the Cobb-Douglas model relative to exponential-only models.">>=
+<<percDSRsse_CD_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Percentage change in Solow Residuals~($\\Delta\\lambda \\, [\\%]$) and mean squared error~($\\Delta sse \\, [\\%]$) for the Cobb-Douglas model relative to exponential-only models.">>=
 ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CD"), mapping=aes(x=percDmse, y=percDlambda, color=energy, size=cst)) +
+  geom_point(data=filter(AllCoeffs, model=="CD"), mapping=aes(x=percDsse, y=percDlambda, color=energy, size=cst)) +
   facet_grid(Country ~ flavor) +
   scale_size_manual(values=c(2,3.5)) +
-  xlab(expression(paste(Delta * mse, " [%]"))) + 
+  xlab(expression(paste(Delta * sse, " [%]"))) + 
   scale_x_continuous(breaks=seq(-50, 50, 50), limits=c(-90, 50)) +  
@@
 %
-<<DSRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta mse$) for the CES modles relative to the exponential-only model.">>=
+<<DSRsse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta sse$) for the CES modles relative to the exponential-only model.">>=
 ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=Dmse, y=Dlambda, color=energy, size=cst, shape=nest)) +
+  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=Dsse, y=Dlambda, color=energy, size=cst, shape=nest)) +
   scale_size_manual(values=c(2,3.5)) +
@@
   facet_grid(Country ~ flavor) +
-  xlab(expression(Delta * mse)) + 
+  xlab(expression(Delta * sse)) + 
   scale_x_continuous(breaks=seq(-0.005, 0, 0.005)) +  
@@
 %
+<<percDSRsse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Percentage change in Solow Residuals~($\\Delta\\lambda \\, [\\%]$) and mean squared error~($\\Delta sse \\, [\\%]$) for the CES models relative to the exponential-only model.">>=
+ggplot() +
+  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=percDsse, y=percDlambda, color=energy, size=cst, shape=nest)) +
+  scale_size_manual(values=c(2,3.5)) +
+  scale_shape_manual(values=c(16,17,18,15)) +
+  facet_grid(Country ~ flavor) +
+  xlab(expression(paste(Delta * SSE, " [%]"))) + 
+  scale_x_continuous(breaks=seq(-80, 0, 20)) +  
+  ylab(expression(paste(Delta * lambda, " [%]"))) +
+  scale_y_continuous(breaks=seq(-80, 0, 20), limits=c(-100, 10)) +  
+  xy_theme() +
+  theme(legend.title=element_blank())
+@
 

### 2015-08-07 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Removing spaces from chunk labels.

@@
 
-<<Historical Data Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Historical data.", warning=FALSE>>=
+<<Historical_Data_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Historical data.", warning=FALSE>>=
 # Melt the data into a form that is useful in a couple places
@@
 
-<<Pre-econometric graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Pre-econometric data.", warning=FALSE>>=
+<<Pre-econometric_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Pre-econometric data.", warning=FALSE>>=
 pre_econometric_data <- leaf_apply(formulas, class = "formula", f=function(form, name){
@@
   #
-  # Models that are exponential only
+  # Models that are exponential only, y = A * exp(lambda*t)
   #
@@
     # or something like that.
-    form <- keep_summands(formulas[[country]][["unadjusted"]], n = c(-1, -2, -3)) # Remove energy
+    form <- keep_summands(formulas[[country]][["unadjusted"]], n = c(-1, -2, -3)) # Keep none of the factors of production
     yVar <- as.name(summands(form, n=1, right=FALSE))
@@
   }
-  # Save exponential theorem models to disk.
+  # Save exponential models to disk.
   saveRDS(modelsExp, file=fileNameExp)
@@
 
+# Put all CD and CES model coefficients into a data frame.  
 AllCoeffsNoCST <- leaf_apply(models, class = c("CDEmodel", "cesModel", "LINEXmodel"), f = function(mod, id){
@@
 }) %>% do.call(rbind, .)
-temp_data_exp$cst <- "Reject CST"
+temp_data_exp$cst <- NA
 
@@
 Both historical GDP and fitted GDP are shown in 
-Figures~\ref{fig:Graphs CESkle-fitted}--\ref{fig:Graphs CESekl-fitted}.
-%
-<<Graphs CESkle-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($kl$)$e$ nesting. Solid line is historical GDP.">>=
+Figures~\ref{fig:Graphs_CESkle-fitted}--\ref{fig:Graphs_CESekl-fitted}.
+%
+<<Graphs_CESkle-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($kl$)$e$ nesting. Solid line is historical GDP.">>=
 fittedGraphNoCST(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest=="kle" | nest=="kl")))
@@
 %
-<<Graphs CESlek-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($le$)$k$ nesting. Solid line is historical GDP.">>=
+<<Graphs_CESlek-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($le$)$k$ nesting. Solid line is historical GDP.">>=
 fittedGraphNoCST(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest=="lek" | nest=="kl")))
@@
 %
-<<Graphs CESekl-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($ek$)$l$ nesting. Solid line is historical GDP.">>=
+<<Graphs_CESekl-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($ek$)$l$ nesting. Solid line is historical GDP.">>=
 fittedGraphNoCST(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest=="ekl" | nest=="kl")))
@@
 standardTriPlot(data=resampleCoeffs, facet_formula=~Country, alpha=0.1,
-                labels=c("alpha[e]", "alpha[k]", "alpha[l]"))
+                labels=c("alpha[e]", "alpha[k]", "alpha[l]"), size=2.0)
 @

### 2015-08-14 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Now including horizontal line at 0.0.

@@
 }) %>% do.call(rbind, .)
+
+# Change variable names to make a nicer-looking graph
+histDataForGraph$variable <- plyr::mapvalues(histDataForGraph$variable,
+                                             from=c("iGDP", 
+                                                    "iKstkS.L", "iKservS.L", "iKstkO.WwithRD", "iKservO.WwithRD",
+                                                    "iL", "ihLest",
+                                                    "iXpMP", "iXp", "iUMP", "iU"),
+                                             to=c("y", 
+                                                  "k", "k", "k", "k",
+                                                  "l", "l",
+                                                  "e", "e", "e", "e"))
 
@@
     facet_grid(Country ~ flavor) +
+    # geom_hline(aes(yintercept = 0), colour="gray50", size=0.1) +
+    geom_hline(yintercept = 0, colour="gray50", size=0.1) +
     scale_x_continuous(breaks=c(1960, 1980, 2000)) +

### 2015-08-14 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
All grids now appear.

@@
   facet_grid(Country ~ flavor) +
-  scale_y_continuous(breaks=c(0, 0.01, 0.02), limits=c(0, 0.03)) +
+  scale_y_continuous(breaks=c(0, 0.01, 0.02, 0.03), limits=c(0, 0.035)) +
   xlab("SSE") + 

### 2015-08-14 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
No spaces in chunk names.

@@
 %
-<<Graphs CESkle-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(kl$)$e$ nesting.">>=
+<<Graphs_CESkle-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(kl$)$e$ nesting.">>=
 residualPlot(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest=="kle" | nest=="kl")), 
@@
 %
-<<Graphs CESlek-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with ($le$)$k$ nesting.">>=
+<<Graphs_CESlek-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with ($le$)$k$ nesting.">>=
 residualPlot(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest == "lek" | nest=="kl")),
@@
 %
-<<Graphs CESekl-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(ek$)$l$ nesting.">>=
+<<Graphs_CESekl-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(ek$)$l$ nesting.">>=
 residualPlot(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest=="ekl" | nest=="kl")),

### 2015-08-14 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Changed CST to CSP everywhere.

--- 2015-08-14 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
@@
 \section{Parameter Estimation (Without Cost-share Theorem)}
-\label{sec:parameter_estimation_noCST}
+\label{sec:parameter_estimation_noCSP}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 fileNameCDCES <- "EcolEcon2015ModelsCDCES.rds"
-fileNameCST <- "EcolEcon2015ModelsCST.rds"
+fileNameCSP <- "EcolEcon2015ModelsCSP.rds"
 fileNameExp <- "EcolEcon2015ModelsExp.rds"
@@
   models <- readRDS(fileNameCDCES)
-  modelsCST <- readRDS(fileNameCST)
+  modelsCSP <- readRDS(fileNameCSP)
   modelsExp <- readRDS(fileNameExp)
@@
 
-  modelsCST <- list()
+  modelsCSP <- list()
   # Output elasticities based on cost share theorem
-  alphaCST <- 0.3 # Fraction of national accounts spent on capital
-  betaCST <- 0.7 # Fraction of national accounts spent on labor
+  alphaCSP <- 0.3 # Fraction of national accounts spent on capital
+  betaCSP <- 0.7 # Fraction of national accounts spent on labor
   for (country in countries){
@@
       # Cobb-Douglas
-      cdModCST <- lm(log(eval(yVar)) - alphaCST*log(eval(kVar)) - betaCST*log(eval(lVar)) ~ eval(tVar), data = data)
-      attr(cdModCST, "naturalCoeffs") <- data.frame(lambda=coef(cdModCST)[[2]],
-                                                    logscale=coef(cdModCST)[[1]], 
-                                                    scale=exp(coef(cdModCST)[[1]]),
-                                                    alpha_1=alphaCST,
-                                                    alpha_2=betaCST, 
+      cdModCSP <- lm(log(eval(yVar)) - alphaCSP*log(eval(kVar)) - betaCSP*log(eval(lVar)) ~ eval(tVar), data = data)
+      attr(cdModCSP, "naturalCoeffs") <- data.frame(lambda=coef(cdModCSP)[[2]],
+                                                    logscale=coef(cdModCSP)[[1]], 
+                                                    scale=exp(coef(cdModCSP)[[1]]),
+                                                    alpha_1=alphaCSP,
+                                                    alpha_2=betaCSP, 
                                                     alpha_3=0)
-      cdModCST$formula <- form
+      cdModCSP$formula <- form
       sdata <- subset(data, select=all.vars(form))
       sdata <- data[complete.cases(sdata), unique(c(all.vars(form), names(data)))]
-      cdModCST$data <- sdata
-      cdModCST$response <- sdata$iGDP
-      modelsCST[[country]][[adj]][["noE"]][["CD"]] <- cdModCST
+      cdModCSP$data <- sdata
+      cdModCSP$response <- sdata$iGDP
+      modelsCSP[[country]][[adj]][["noE"]][["CD"]] <- cdModCSP
       # CES
-      cesModCST <- plm(log(eval(yVar) / (alphaCST*eval(kVar)^(-rho_1) + betaCST*eval(lVar)^(-rho_1))^(-1/rho_1)) ~ eval(tVar),
+      cesModCSP <- plm(log(eval(yVar) / (alphaCSP*eval(kVar)^(-rho_1) + betaCSP*eval(lVar)^(-rho_1))^(-1/rho_1)) ~ eval(tVar),
                        data = historicalData[[country]],
                        params=c(rho_1=0.8))
-      names(cesModCST$coefficients) <- c("logscale", "lambda", "rho_1")
-      cesModCST$coefficients <- c(coef(cesModCST), c(delta_1=alphaCST, delta=1))
-      attr(cesModCST, "naturalCoeffs") <- EconModels:::makeNatCoef(cesModCST)
-      cesModCST$formula <- form
-      cesModCST$data <- sdata
-      modelsCST[[country]][[adj]][["noE"]][["CES"]][["kl"]] <- cesModCST
+      names(cesModCSP$coefficients) <- c("logscale", "lambda", "rho_1")
+      cesModCSP$coefficients <- c(coef(cesModCSP), c(delta_1=alphaCSP, delta=1))
+      attr(cesModCSP, "naturalCoeffs") <- EconModels:::makeNatCoef(cesModCSP)
+      cesModCSP$formula <- form
+      cesModCSP$data <- sdata
+      modelsCSP[[country]][[adj]][["noE"]][["CES"]][["kl"]] <- cesModCSP
     }
@@
   # Save cost-share theorem models to disk.
-  saveRDS(modelsCST, file=fileNameCST)
+  saveRDS(modelsCSP, file=fileNameCSP)
 
@@
                     nest = NA,
-                    cst = "Reject CST"))
+                    CSP = "Reject CSP"))
   res <- cbind(res, naturalCoef(modExp))
@@
 
-# Put all the cost-share theorem (CST) model coefficients into a data frame
-AllCoeffsCST <- leaf_apply(modelsCST, class = c("lm"), f = function(modCST, id){
+# Put all the cost-share theorem (CSP) model coefficients into a data frame
+AllCoeffsCSP <- leaf_apply(modelsCSP, class = c("lm"), f = function(modCSP, id){
   # Parse the id to find out whether this is quality-adjusted data, etc.
@@
                     nest=if(length(id_list) > 4) id_list[[5]] else NA,
-                    cst="Adhere to CST"))
-  res <- cbind(res, naturalCoef(modCST))
+                    CSP="Adhere to CSP"))
+  res <- cbind(res, naturalCoef(modCSP))
   # Now calculate the mean squared error (sse) for each model.
-  sse <- sum(resid(modCST)^2)
+  sse <- sum(resid(modCSP)^2)
   res <- cbind(res, list(sse=sse))
@@
 # Put all CD and CES model coefficients into a data frame.  
-AllCoeffsNoCST <- leaf_apply(models, class = c("CDEmodel", "cesModel", "LINEXmodel"), f = function(mod, id){
+AllCoeffsNoCSP <- leaf_apply(models, class = c("CDEmodel", "cesModel", "LINEXmodel"), f = function(mod, id){
   # Parse the id to find out whether this is quality-adjusted data, etc.
@@
                     nest=if(length(id_list) > 4) id_list[[5]] else NA,
-                    cst="Reject CST"))
+                    CSP="Reject CSP"))
   res <- cbind(res, naturalCoef(mod))
@@
 }) %>% do.call(plyr::rbind.fill, .)
-AllCoeffs <- plyr::rbind.fill(AllCoeffsExp, AllCoeffsCST, AllCoeffsNoCST)
+AllCoeffs <- plyr::rbind.fill(AllCoeffsExp, AllCoeffsCSP, AllCoeffsNoCSP)
 # See hint at http://stackoverflow.com/questions/22555249/how-to-merge-data-frame-with-same-column-names
@@
 AllCoeffs$nest <- relevelFactor(as.factor(unlist(AllCoeffs$nest)), c("kl", "kle", "lek", "ekl"))
-AllCoeffs$cst <- relevelFactor(as.factor(unlist(AllCoeffs$cst)), c("Adhere to CST", "Reject CST"))
+AllCoeffs$CSP <- relevelFactor(as.factor(unlist(AllCoeffs$CSP)), c("Adhere to CSP", "Reject CSP"))
 # Rearrange for easier viewing
-AllCoeffs <- arrange(AllCoeffs, Country, model, flavor, energy, nest, cst)
+AllCoeffs <- arrange(AllCoeffs, Country, model, flavor, energy, nest, CSP)
 @
@@
   # ******************************************
-  # getData doesn't work for lm models that are created for CST="Adhere to CST".
+  # getData doesn't work for lm models that are created for CSP="Adhere to CSP".
   # After we implement specified values for alpha_1, alpha_2, and alpha_3 in our fitting functions, 
@@
   # The residuals are OK.
-  # But, the yhat() call in fittedAndResidData() will not return the correct information from the CST models.
-  # This is because modelsCST was not created with our typical functions.
+  # But, the yhat() call in fittedAndResidData() will not return the correct information from the CSP models.
+  # This is because modelsCSP was not created with our typical functions.
   # To correct this problem, we need to add arguments to cdModel and cesModel such that 
@@
 }) %>% do.call(rbind, .)
-temp_data_exp$cst <- NA
-
-temp_data_CST <- leaf_apply(modelsCST, class=c("plm", "lm"), f = function(model, id){
+temp_data_exp$CSP <- NA
+
+temp_data_CSP <- leaf_apply(modelsCSP, class=c("plm", "lm"), f = function(model, id){
   # ****************************************************
@@
 }) %>% do.call(rbind, .)
-temp_data_CST$cst <- "Adhere to CST"
-
-temp_data_noCST <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, id){
+temp_data_CSP$CSP <- "Adhere to CSP"
+
+temp_data_noCSP <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, id){
   return(fittedAndResidData(model, id))  
 }) %>% do.call(rbind, .)
-temp_data_noCST$cst <- "Reject CST"
-
-temp_data <- plyr::rbind.fill( temp_data_exp, temp_data_CST, temp_data_noCST )
-
-# Get the unadjusted, without-energy residuals from models that obey the CST
+temp_data_noCSP$CSP <- "Reject CSP"
+
+temp_data <- plyr::rbind.fill( temp_data_exp, temp_data_CSP, temp_data_noCSP )
+
+# Get the unadjusted, without-energy residuals from models that adhere to the CSP
 # and store them in a data frame
-# r_unadj_noE_CST <- filter(temp_data, flavor=="Unadjusted" & energy=="Without energy" & cst=="Adhere to CST") %>% 
+# r_unadj_noE_CSP <- filter(temp_data, flavor=="Unadjusted" & energy=="Without energy" & CSP=="Adhere to CSP") %>% 
 #   select(Year, Country, Residuals, model)
-# colnames(r_unadj_noE_CST)[colnames(r_unadj_noE_CST)=="Residuals"] <- "r_unadj_noE"
+# colnames(r_unadj_noE_CSP)[colnames(r_unadj_noE_CSP)=="Residuals"] <- "r_unadj_noE"
 # Merge to get the unadjusted, without-energy values next to each country, year, and model
-# fitted_and_resid_data <- merge(temp_data, r_unadj_noE_CST)
+# fitted_and_resid_data <- merge(temp_data, r_unadj_noE_CSP)
 # Create a column containing ∆r, the difference between a residual value
@@
 # Make data viewing easier
-fitted_and_resid_data <- arrange(fitted_and_resid_data, Country, cst, model, flavor, energy, nest)
+fitted_and_resid_data <- arrange(fitted_and_resid_data, Country, CSP, model, flavor, energy, nest)
 @
@@
 <<Fitted and Residual Graph Functions>>=
-fittedGraphCST <- function(data){
+fittedGraphCSP <- function(data){
   ggplot() +
-    geom_line(data=filter(data, cst=="Adhere to CST"), mapping=aes(x=Year, y=iGDP)) +
-    geom_line(data=data, mapping=aes(x=Year, y=fitted, linetype=cst)) +
+    geom_line(data=filter(data, CSP=="Adhere to CSP"), mapping=aes(x=Year, y=iGDP)) +
+    geom_line(data=data, mapping=aes(x=Year, y=fitted, linetype=CSP)) +
     scale_linetype_manual(values=c(2,3), name="") +
@@
 
-fittedGraphNoCST <- function(data){
+fittedGraphNoCSP <- function(data){
   ggplot() +
@@
 <<Graphs_CESkle-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($kl$)$e$ nesting. Solid line is historical GDP.">>=
-fittedGraphNoCST(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest=="kle" | nest=="kl")))
+fittedGraphNoCSP(filter(fitted_and_resid_data, model=="CES" & CSP=="Reject CSP" & (nest=="kle" | nest=="kl")))
 @
@@
 <<Graphs_CESlek-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($le$)$k$ nesting. Solid line is historical GDP.">>=
-fittedGraphNoCST(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest=="lek" | nest=="kl")))
+fittedGraphNoCSP(filter(fitted_and_resid_data, model=="CES" & CSP=="Reject CSP" & (nest=="lek" | nest=="kl")))
 @
@@
 <<Graphs_CESekl-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($ek$)$l$ nesting. Solid line is historical GDP.">>=
-fittedGraphNoCST(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest=="ekl" | nest=="kl")))
+fittedGraphNoCSP(filter(fitted_and_resid_data, model=="CES" & CSP=="Reject CSP" & (nest=="ekl" | nest=="kl")))
 @
@@
 %
-<<Graphs CESkle-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(kl$)$e$ nesting.">>=
-residualPlot(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest=="kle" | nest=="kl")), 
+<<Graphs_CESkle-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(kl$)$e$ nesting.">>=
+residualPlot(filter(fitted_and_resid_data, model=="CES" & CSP=="Reject CSP" & (nest=="kle" | nest=="kl")), 
              withEnergyShape = 0) # square
@@
 %
-<<Graphs CESlek-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with ($le$)$k$ nesting.">>=
-residualPlot(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest == "lek" | nest=="kl")),
+<<Graphs_CESlek-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with ($le$)$k$ nesting.">>=
+residualPlot(filter(fitted_and_resid_data, model=="CES" & CSP=="Reject CSP" & (nest == "lek" | nest=="kl")),
              withEnergyShape = 3) # plus
@@
 %
-<<Graphs CESekl-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(ek$)$l$ nesting.">>=
-residualPlot(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest=="ekl" | nest=="kl")),
+<<Graphs_CESekl-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(ek$)$l$ nesting.">>=
+residualPlot(filter(fitted_and_resid_data, model=="CES" & CSP=="Reject CSP" & (nest=="ekl" | nest=="kl")),
              withEnergyShape = 4) # times
@@
 myXTable(filter(AllCoeffs, model=="CES" | model=="exp") %>% 
-           select(Country, model, flavor, energy, nest, cst, scale, lambda, sse),
+           select(Country, model, flavor, energy, nest, CSP, scale, lambda, sse),
          caption="$\\theta$, Solow residual, and $sse$ for CES models.",
@@
 ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=sse, y=lambda, color=energy, size=cst, shape=nest)) +
+  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=sse, y=lambda, color=energy, size=CSP, shape=nest)) +
   geom_vline(aes(xintercept = sse), filter(AllCoeffs, model=="exp") %>% select(Country, sse), colour="gray50", size=0.1) +
@@
 \subsubsection{Rejecting (or adhering to) the cost share theorem} 
-\label{sec:gfsr_cst}
+\label{sec:gfsr_CSP}
 %------------------------------
@@
 myXTable(filter(AllCoeffs, model=="CES" | model=="exp") %>% 
-           select(Country, model, flavor, energy, nest, cst, alpha_1, alpha_2, alpha_3),
+           select(Country, model, flavor, energy, nest, CSP, alpha_1, alpha_2, alpha_3),
          caption="Factor shares~($\\alpha$) for CES models.",
@@
   bar_chart_data <- filter(AllCoeffs, Country==coun & model==mod) %>% 
-    select(Country, model, flavor, energy, nest, cst, alpha_1, alpha_2, alpha_3)
+    select(Country, model, flavor, energy, nest, CSP, alpha_1, alpha_2, alpha_3)
   # Change nest to a nicer-looking nest string
@@
   # Add a label column
-  bar_chart_data$label <- paste(bar_chart_data$cst, bar_chart_data$flavor, 
+  bar_chart_data$label <- paste(bar_chart_data$CSP, bar_chart_data$flavor, 
                                 bar_chart_data$energy, bar_chart_data$nest, sep=", ")
@@
 \subsubsection{Rejecting (or adhering to) the cost share theorem} 
-\label{sec:fs_cst}
+\label{sec:fs_CSP}
 %------------------------------
@@
 myXTable(filter(AllCoeffs, model=="CES") %>% 
-           select(Country, model, flavor, energy, nest, cst, sigma_1, sigma),
+           select(Country, model, flavor, energy, nest, CSP, sigma_1, sigma),
          caption="Factor substitution~($\\sigma$) for CES models.",
@@
 \subsubsection{Rejecting (or adhering to) the cost share theorem} 
-\label{sec:sigma_cst}
+\label{sec:sigma_CSP}
 %------------------------------
@@
 \subsection{Correlograms for models that adhere to the cost-share theorem} 
-\label{sec:correlograms_CST}
+\label{sec:correlograms_CSP}
 %++++++++++++++++++++++++++++++
@@
 
-<<Correlograms_CST, echo=FALSE, message=FALSE>>=
-leaf_apply(l = modelsCST, class = c("lm", "plm"), f = function(model, name){
+<<Correlograms_CSP, echo=FALSE, message=FALSE>>=
+leaf_apply(l = modelsCSP, class = c("lm", "plm"), f = function(model, name){
   acf(resid(model), main=name)
@@
 \subsection{Correlograms for models that reject the cost-share theorem} 
-\label{sec:correlograms_noCST}
+\label{sec:correlograms_noCSP}
 %++++++++++++++++++++++++++++++
@@
 
-<<Correlograms_noCST, echo=FALSE, message=FALSE>>=
+<<Correlograms_noCSP, echo=FALSE, message=FALSE>>=
 leaf_apply(l = models, class = c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, name){
@@
 <<Graphs CD-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Cobb-Douglas models that reject the cost-share theorem. Solid line is historical GDP.">>=
-fittedGraphNoCST(filter(fitted_and_resid_data, model=="CD" & cst=="Reject CST"))
+fittedGraphNoCSP(filter(fitted_and_resid_data, model=="CD" & CSP=="Reject CSP"))
 @
@@
 <<Graphs CD-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for Cobb-Douglas models.">>=
-residualPlot(filter(fitted_and_resid_data, model=="CD" & cst=="Reject CST"))
-@
-
-Table~\ref{tab:Effect_of_CST_CD} shows the effect of the CST 
+residualPlot(filter(fitted_and_resid_data, model=="CD" & CSP=="Reject CSP"))
+@
+
+Table~\ref{tab:Effect_of_CSP_CD} shows the effect of the CSP 
 on fitted parameters for the Cobb-Douglas model and the exponential-only model.
@@
 %
-<<Effect_of_CST_CD, results="asis">>=
+<<Effect_of_CSP_CD, results="asis">>=
 myXTable(filter(AllCoeffs, (model=="CD" & flavor=="Unadjusted" & energy=="Without energy") | model=="exp") %>% 
-           select(Country, model, cst, scale, lambda, alpha_1, alpha_2, sse),
+           select(Country, model, CSP, scale, lambda, alpha_1, alpha_2, sse),
          caption="Model parameters for Cobb-Douglas models with unadjusted factors of production, without energy.",
@@
 myXTable(filter(AllCoeffs, model=="CD" | model=="exp") %>% 
-           select(Country, model, flavor, energy, cst, scale, lambda, alpha_1, alpha_2, alpha_3, sse),
+           select(Country, model, flavor, energy, CSP, scale, lambda, alpha_1, alpha_2, alpha_3, sse),
          caption="Model parameters for all Cobb-Douglas models.",
@@
 <<DSRsse_CD, results="asis">>=
-myXTable(filter(AllCoeffs, model=="CD") %>% select(Country, model, flavor, energy, cst, Dlambda, Dsse),
+myXTable(filter(AllCoeffs, model=="CD") %>% select(Country, model, flavor, energy, CSP, Dlambda, Dsse),
          caption="$\\Delta \\lambda$ and $\\Delta sse$ for Cobb-Douglas models.",
@@
 ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CD"), mapping=aes(x=Dsse, y=Dlambda, color=energy, size=cst)) +
+  geom_point(data=filter(AllCoeffs, model=="CD"), mapping=aes(x=Dsse, y=Dlambda, color=energy, size=CSP)) +
   facet_grid(Country ~ flavor) +
@@
 ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CD"), mapping=aes(x=percDsse, y=percDlambda, color=energy, size=cst)) +
+  geom_point(data=filter(AllCoeffs, model=="CD"), mapping=aes(x=percDsse, y=percDlambda, color=energy, size=CSP)) +
   facet_grid(Country ~ flavor) +
@@
 ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=Dsse, y=Dlambda, color=energy, size=cst, shape=nest)) +
+  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=Dsse, y=Dlambda, color=energy, size=CSP, shape=nest)) +
   scale_size_manual(values=c(2,3.5)) +
@@
 ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=percDsse, y=percDlambda, color=energy, size=cst, shape=nest)) +
+  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=percDsse, y=percDlambda, color=energy, size=CSP, shape=nest)) +
   scale_size_manual(values=c(2,3.5)) +

### 2015-08-14 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Added helpful comment.
Now includes reference model in fitted graphs.

@@
 Unadjusted and quality-adjusted data for both Portugal and the United Kingdom 
-are shown in Figure~\ref{fig:Historical Data Graph}.
+are shown in Figure~\ref{fig:Historical_Data_Graph}.
 
@@
   # At that time, change model$data to getData(model)
+}
+
+temp_data_exp <- leaf_apply(modelsExp, class=c("lm"), f = function(model, id){
+  df <- data.frame(select(model$data, Year, Country))
+  df$fittedExp <- exp(fitted(model)) # exp accounts for the fact that the model was fitted in log space.
+  df$ResidualsExp <- resid(model)
+  # df$model <- "exp"
+  return(df)
+}) %>% do.call(rbind, .)
+
+temp_data_CSP <- leaf_apply(modelsCSP, class=c("plm", "lm"), f = function(model, id){
+  df <- data.frame(select(model$data, Year, Country, iGDP))
+  df$fitted <- exp(fitted(model)) # fitted is in log space. Return to regular space.
+  df$Residuals <- resid(model) # residuals are in log space, and that is what we want.
+  # Now add meta information
+  id_list <- strsplit(id, split = "[.]")[[1]]
+  df$flavor <- if (id_list[[2]] ==  "unadjusted") "Unadjusted" else "Quality-adjusted"
+  df$energy <- if (id_list[[3]] == "noE") "Without energy" else "With energy"
+  df$model <- id_list[[4]]
+  df$nest <- if (length(id_list) > 4) id_list[[5]] else NA
+  return(df)
+}) %>% do.call(rbind, .)
+temp_data_CSP$CSP <- "Adhere to CSP"
+
+temp_data_noCSP <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, id){
   df <- data.frame(select(model$data, Year)) 
@@
   df$Country <- id_list[[1]]
-  # Exponential models have only 1 item in the id list, namely country. Accommodate that length with if statements.
-  df$flavor <- if (len > 1) (if (id_list[[2]] ==  "unadjusted") "Unadjusted" else "Quality-adjusted") else NA
-  df$energy <- if (len > 2) (if (id_list[[3]] == "noE") "Without energy" else "With energy") else "Without energy"
-  df$model <- if (len > 3) id_list[[4]] else "exp"
-  df$nest <- if (len > 4) id_list[[5]] else NA
+  df$flavor <- if (id_list[[2]] ==  "unadjusted") "Unadjusted" else "Quality-adjusted"
+  df$energy <- if (id_list[[3]] == "noE") "Without energy" else "With energy"
+  df$model <- id_list[[4]]
+  df$nest <- if (length(id_list) > 4) id_list[[5]] else NA
   return(df)  
-}
-
-temp_data_exp <- leaf_apply(modelsExp, class=c("lm"), f = function(model, id){
-  # ****************************************************
-  # Not all of the results from this code are not correct at this time.
-  # The residuals are OK.
-  # But, the yhat() call in fittedAndResidData() will not return the correct information from the CSP models.
-  # This is because modelsCSP was not created with our typical functions.
-  # To correct this problem, we need to add arguments to cdModel and cesModel such that 
-  # the models produced by those functions will be in the correct form for yhat() function.
-  return(fittedAndResidData(model, id))
-}) %>% do.call(rbind, .)
-temp_data_exp$CSP <- NA
-
-temp_data_CSP <- leaf_apply(modelsCSP, class=c("plm", "lm"), f = function(model, id){
-  # ****************************************************
-  # Not all of the results from this code are not correct at this time.
-  # The residuals are OK.
-  # But, the yhat() call in fittedAndResidData() will not return the correct information from the CSP models.
-  # This is because modelsCSP was not created with our typical functions.
-  # To correct this problem, we need to add arguments to cdModel and cesModel such that 
-  # the models produced by those functions will be in the correct form for yhat() function.
-  return(fittedAndResidData(model, id))
-}) %>% do.call(rbind, .)
-temp_data_CSP$CSP <- "Adhere to CSP"
-
-temp_data_noCSP <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, id){
-  return(fittedAndResidData(model, id))  
 }) %>% do.call(rbind, .)
@@
 
-temp_data <- plyr::rbind.fill( temp_data_exp, temp_data_CSP, temp_data_noCSP )
-
+temp_data_noExp <- plyr::rbind.fill( temp_data_CSP, temp_data_noCSP )
+
+# Now merge the exponential-only model with the CSP and noCSP models. 
+# Doing this, because the exponential-only model is kind-of like iY:
+# it applies to all situations.
+# temp_data <- merge(temp_data_noExp, temp_data_exp)
+fitted_and_resid_data <- merge(temp_data_noExp, temp_data_exp)
+
+# No longer using this code, because we have a different "reference" model.
 # Get the unadjusted, without-energy residuals from models that adhere to the CSP
@@
 
+# # Get the reference residuals (from the exponential-only models) and store them in a data frame
+# r_ref <- filter(temp_data, model=="exp") %>% select(Year, Country, Residuals)
+# colnames(r_ref)[colnames(r_ref)=="Residuals"] <- "r_ref"
+# # Merge to get the reference values in each appropriate row
+# fitted_and_resid_data <- merge(temp_data, r_ref)
+# # Create a column containing ∆r, the difference between a residual value
+# # and the residual value in the same year for the reference case
+# fitted_and_resid_data[["Dr"]] <- abs(fitted_and_resid_data[["Residuals"]]) - abs(fitted_and_resid_data[["r_ref"]])
+
 # Get the reference residuals (from the exponential-only models) and store them in a data frame
-r_ref <- filter(temp_data, model=="exp") %>% select(Year, Country, Residuals)
-colnames(r_ref)[colnames(r_ref)=="Residuals"] <- "r_ref"
+# r_ref <- select(temp_data_exp, Year, Country, ResidualsExp)
+# colnames(r_ref)[colnames(r_ref)=="Residuals"] <- "r_ref"
 # Merge to get the reference values in each appropriate row
-fitted_and_resid_data <- merge(temp_data, r_ref)
+# fitted_and_resid_data <- merge(temp_data, r_ref)
 # Create a column containing ∆r, the difference between a residual value
 # and the residual value in the same year for the reference case
-fitted_and_resid_data[["Dr"]] <- abs(fitted_and_resid_data[["Residuals"]]) - abs(fitted_and_resid_data[["r_ref"]])
+fitted_and_resid_data[["Dr"]] <- abs(fitted_and_resid_data[["Residuals"]]) - abs(fitted_and_resid_data[["ResidualsExp"]])
 
@@
 <<Fitted and Residual Graph Functions>>=
-fittedGraphCSP <- function(data){
+fittedGraphNoCSP <- function(data){
+  fittedGraphData <- select(data, Year, Country, iGDP, fitted, fittedExp, flavor, energy, CSP, nest)
+  fittedGraphData <- melt(fittedGraphData, 
+                     measure.vars = c("iGDP", "fitted", "fittedExp"), 
+                     value.name = "value", 
+                     variable.name = "variable")
+  fittedGraphData$label <- with(fittedGraphData, paste(variable, energy))
+  # Now collapse some of the information. Don't need multiple versions of the exponential model, e.g.
+  fittedGraphData <- filter(fittedGraphData, label=="iGDP With energy" | label=="fittedExp With energy" |
+                       label == "fitted With energy" | label == "fitted Without energy")
+  fittedGraphData$label <- plyr::mapvalues(fittedGraphData$label, 
+                                      from = c("iGDP With energy", 
+                                               "fittedExp With energy",
+                                               "fitted With energy",
+                                               "fitted Without energy"), 
+                                      to = c("GDP", 
+                                             "Reference model",
+                                             "With energy",
+                                             "Without energy"))
+  # Relevel factors
+  fittedGraphData$label <- relevelFactor(as.factor(fittedGraphData$label), 
+                                         c("GDP", "Reference model", "Without energy", "With energy"))
+  # Make (and return) the graph
   ggplot() +
-    geom_line(data=filter(data, CSP=="Adhere to CSP"), mapping=aes(x=Year, y=iGDP)) +
-    geom_line(data=data, mapping=aes(x=Year, y=fitted, linetype=CSP)) +
-    scale_linetype_manual(values=c(2,3), name="") +
-    facet_grid(Country ~ flavor) + 
-    xlab("") +
-    ylab("Indexed GDP (1960=1)") +
-    xy_theme()
-}
-
-fittedGraphNoCSP <- function(data){
-  ggplot() +
-    geom_line(data=filter(data, energy=="Without energy"), mapping=aes(x=Year, y=iGDP)) +
-    geom_line(data=data, mapping=aes(x=Year, y=fitted, linetype=energy)) +
-    scale_linetype_manual(values=c(2,3), name="") +
+    geom_line(data=fittedGraphData, mapping=aes(x=Year, y=value, group=label, linetype=label)) +
+    scale_linetype_manual(values=c(1,4,2,3), name="") +
     facet_grid(Country ~ flavor) +
@@
 %
-<<Graphs_CESkle-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($kl$)$e$ nesting. Solid line is historical GDP.">>=
-fittedGraphNoCSP(filter(fitted_and_resid_data, model=="CES" & CSP=="Reject CSP" & (nest=="kle" | nest=="kl")))
-@
-%
-<<Graphs_CESlek-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($le$)$k$ nesting. Solid line is historical GDP.">>=
-fittedGraphNoCSP(filter(fitted_and_resid_data, model=="CES" & CSP=="Reject CSP" & (nest=="lek" | nest=="kl")))
-@
-%
-<<Graphs_CESekl-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($ek$)$l$ nesting. Solid line is historical GDP.">>=
-fittedGraphNoCSP(filter(fitted_and_resid_data, model=="CES" & CSP=="Reject CSP" & (nest=="ekl" | nest=="kl")))
+<<Graphs_CESkle-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with $kl$ and ($kl$)$e$ nesting that reject the CSP. Solid line is historical GDP.">>=
+fittedGraphData_kle <- fitted_and_resid_data %>% filter(model=="CES" & CSP=="Reject CSP" & (nest == "kl" | nest == "kle"))
+fittedGraphNoCSP(fittedGraphData_kle)
+@
+%
+<<Graphs_CESlek-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with $kl$ and ($le$)$k$ nesting that reject the CSP. Solid line is historical GDP.">>=
+fittedGraphData_lek <- fitted_and_resid_data %>% filter(model=="CES" & CSP=="Reject CSP" & (nest == "kl" | nest == "lek"))
+fittedGraphNoCSP(fittedGraphData_lek)
+@
+%
+<<Graphs_CESekl-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with $kl$ and ($ek$)$l$ nesting that reject the CSP. Solid line is historical GDP.">>=
+fittedGraphData_ekl <- fitted_and_resid_data %>% filter(model=="CES" & CSP=="Reject CSP" & (nest == "kl" | nest == "ekl"))
+fittedGraphNoCSP(fittedGraphData_ekl)
 @

### 2015-08-14 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Deleted unneeded, commented code.

@@
 <<Fitted_and_Residuals>>=
-filenameResampleCoeffs <- ""
-fittedAndResidData <- function(model, id){
-  # ******************************************
-  # getData doesn't work for lm models that are created for CSP="Adhere to CSP".
-  # After we implement specified values for alpha_1, alpha_2, and alpha_3 in our fitting functions, 
-  # getData(model) will probably work.
-  # At that time, change model$data to getData(model)
-}
-
 temp_data_exp <- leaf_apply(modelsExp, class=c("lm"), f = function(model, id){
@@
   df$ResidualsExp <- resid(model)
-  # df$model <- "exp"
   return(df)
@@
 
-# No longer using this code, because we have a different "reference" model.
-# Get the unadjusted, without-energy residuals from models that adhere to the CSP
-# and store them in a data frame
-# r_unadj_noE_CSP <- filter(temp_data, flavor=="Unadjusted" & energy=="Without energy" & CSP=="Adhere to CSP") %>% 
-#   select(Year, Country, Residuals, model)
-# colnames(r_unadj_noE_CSP)[colnames(r_unadj_noE_CSP)=="Residuals"] <- "r_unadj_noE"
-# Merge to get the unadjusted, without-energy values next to each country, year, and model
-# fitted_and_resid_data <- merge(temp_data, r_unadj_noE_CSP)
 # Create a column containing ∆r, the difference between a residual value
-# and the residual value in the same year for the unadjusted, no-energy case
-# fitted_and_resid_data[["Dr"]] <- abs(fitted_and_resid_data[["Residuals"]]) - abs(fitted_and_resid_data[["r_unadj_noE"]])
-
-# # Get the reference residuals (from the exponential-only models) and store them in a data frame
-# r_ref <- filter(temp_data, model=="exp") %>% select(Year, Country, Residuals)
-# colnames(r_ref)[colnames(r_ref)=="Residuals"] <- "r_ref"
-# # Merge to get the reference values in each appropriate row
-# fitted_and_resid_data <- merge(temp_data, r_ref)
-# # Create a column containing ∆r, the difference between a residual value
-# # and the residual value in the same year for the reference case
-# fitted_and_resid_data[["Dr"]] <- abs(fitted_and_resid_data[["Residuals"]]) - abs(fitted_and_resid_data[["r_ref"]])
-
-# Get the reference residuals (from the exponential-only models) and store them in a data frame
-# r_ref <- select(temp_data_exp, Year, Country, ResidualsExp)
-# colnames(r_ref)[colnames(r_ref)=="Residuals"] <- "r_ref"
-# Merge to get the reference values in each appropriate row
-# fitted_and_resid_data <- merge(temp_data, r_ref)
-# Create a column containing ∆r, the difference between a residual value
-# and the residual value in the same year for the reference case
+# and the residual value in the same year for the reference model
 fitted_and_resid_data[["Dr"]] <- abs(fitted_and_resid_data[["Residuals"]]) - abs(fitted_and_resid_data[["ResidualsExp"]])

### 2015-08-14 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
No spaces in chunk names.

@@
 
-<<Fitted and Residual Graph Functions>>=
+<<Fitted_and_Residual_Graph_Functions>>=
 fittedGraphNoCSP <- function(data){
@@
 %
-<<Graphs CD-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Cobb-Douglas models that reject the cost-share theorem. Solid line is historical GDP.">>=
+<<Graphs_CD-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Cobb-Douglas models that reject the cost-share theorem. Solid line is historical GDP.">>=
 fittedGraphNoCSP(filter(fitted_and_resid_data, model=="CD" & CSP=="Reject CSP"))
@@
 %
-<<Graphs CD-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for Cobb-Douglas models.">>=
+<<Graphs_CD-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for Cobb-Douglas models.">>=
 residualPlot(filter(fitted_and_resid_data, model=="CD" & CSP=="Reject CSP"))

### 2015-08-14 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Added a version of the residualPlot function. New version also plots residuals from reference model. Not using the new version at the moment.

@@
 <<ResidualPlotFunction>>=
+
 residualPlot <- function(data, withEnergyShape = 0){
@@
 }
+
+# This version also plots reference model residuals.
+# But the reference model dwarfs all other residuals and looks bad on the graph.
+# So, I decided not to use this. ---MKH, 14 Aug 2015
+
+# residualPlot <- function(data, withEnergyShape = 0){
+#   # Keep only the data we need
+#   residGraphData <- select(data, Year, Country, Residuals, flavor, energy, model, nest, CSP, ResidualsExp)
+#   # Melt the data so that we can include the reference model, too.
+#   residGraphData <- melt(residGraphData, 
+#                          measure.vars=c("Residuals", "ResidualsExp"),
+#                          value.name="value",
+#                          variable.name="variable")
+#   residGraphData$label <- with(residGraphData, paste(variable, energy))
+#   
+#   # Now collapse some of the information. Don't need multiple versions of the exponential model, e.g.
+#   residGraphData <- filter(residGraphData, label=="Residuals With energy" | label=="Residuals Without energy" |
+#                              label=="ResidualsExp Without energy")
+#   
+#   residGraphData$label <- plyr::mapvalues(residGraphData$label, 
+#                                           from = c("Residuals With energy", 
+#                                                    "Residuals Without energy",
+#                                                    "ResidualsExp Without energy"), 
+#                                           to = c("With energy", 
+#                                                  "Without energy",
+#                                                  "Reference model"))
+#   # Relevel factors
+#   residGraphData$label <- relevelFactor(as.factor(residGraphData$label), 
+#                                          c("Without energy", "With energy", "Reference model"))
+#   
+#   ggplot() +
+#     geom_point(data=residGraphData, mapping=aes(x=Year, y=value, shape=label, color=label, size=label)) +
+#     scale_shape_manual(values=c(1, withEnergyShape, 5)) +
+#     scale_size_manual(values=c(4, 4, 2)) +
+#     # scale_color_manual(values=c("gray50", "green", "red")) +
+#     facet_grid(Country ~ flavor) +
+#     geom_hline(yintercept = 0, colour="gray50", size=0.1) +
+#     scale_x_continuous(breaks=c(1960, 1980, 2000)) +
+#     xlab("") +
+#     ylab("r") + 
+#     xy_theme() +
+#     theme(legend.title=element_blank())
+# }
 @

### 2015-08-15 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Now doing 1000 resamples.

@@
 rerunResampling=FALSE
-nResamples <- 100 # Number of resamples
+nResamples <- 1000 # Number of resamples
 # ********************************************************

### 2015-08-15 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
\sigma_{(kl)e} in axis label.

@@
     scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0), limits=c(0, 1e6)) +
-    labs(x=expression(delta), y=expression(sigma[kle]))
+    labs(x=expression(delta), y=expression(sigma["(kl)"*e]))
 @

### 2015-08-16 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Crosshair how black.

@@
 <<resample_graph_lambda_theta, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.5, fig.cap="$\\lambda$ and $\\theta$ values for resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
-standardScatterPlot(data=resampleCoeffs, mapping=aes(scale, lambda), facet_formula=~Country, alpha=0.1) +
+standardScatterPlot(data=resampleCoeffs, mapping=aes(scale, lambda), facet_formula=~Country, alpha=0.05, orig_color = "black") +
     scale_x_continuous(breaks=c(0.95, 1.0, 1.05)) + 

### 2015-08-18 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
use trans_sigma2

--- 2015-08-15 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
@@
 rerunResampling=FALSE
-nResamples <- 1000 # Number of resamples
+nResamples <- 100 # Number of resamples
 # ********************************************************
@@
 Unadjusted and quality-adjusted data for both Portugal and the United Kingdom 
-are shown in Figure~\ref{fig:Historical_Data_Graph}.
-
-<<Historical_Data_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Historical data.", warning=FALSE>>=
+are shown in Figure~\ref{fig:Historical Data Graph}.
+
+<<Historical Data Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Historical data.", warning=FALSE>>=
 # Melt the data into a form that is useful in a couple places
@@
 
-# Change variable names to make a nicer-looking graph
-histDataForGraph$variable <- plyr::mapvalues(histDataForGraph$variable,
-                                             from=c("iGDP", 
-                                                    "iKstkS.L", "iKservS.L", "iKstkO.WwithRD", "iKservO.WwithRD",
-                                                    "iL", "ihLest",
-                                                    "iXpMP", "iXp", "iUMP", "iU"),
-                                             to=c("y", 
-                                                  "k", "k", "k", "k",
-                                                  "l", "l",
-                                                  "e", "e", "e", "e"))
-
 # Relevel factors before plotting
@@
 
-<<Pre-econometric_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Pre-econometric data.", warning=FALSE>>=
+<<Pre-econometric graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Pre-econometric data.", warning=FALSE>>=
 pre_econometric_data <- leaf_apply(formulas, class = "formula", f=function(form, name){
@@
 \section{Parameter Estimation (Without Cost-share Theorem)}
-\label{sec:parameter_estimation_noCSP}
+\label{sec:parameter_estimation_noCST}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 fileNameCDCES <- "EcolEcon2015ModelsCDCES.rds"
-fileNameCSP <- "EcolEcon2015ModelsCSP.rds"
+fileNameCST <- "EcolEcon2015ModelsCST.rds"
 fileNameExp <- "EcolEcon2015ModelsExp.rds"
@@
   models <- readRDS(fileNameCDCES)
-  modelsCSP <- readRDS(fileNameCSP)
+  modelsCST <- readRDS(fileNameCST)
   modelsExp <- readRDS(fileNameExp)
@@
   #
-  # Models that are exponential only, y = A * exp(lambda*t)
+  # Models that are exponential only
   #
@@
     # or something like that.
-    form <- keep_summands(formulas[[country]][["unadjusted"]], n = c(-1, -2, -3)) # Keep none of the factors of production
+    form <- keep_summands(formulas[[country]][["unadjusted"]], n = c(-1, -2, -3)) # Remove energy
     yVar <- as.name(summands(form, n=1, right=FALSE))
@@
   }
-  # Save exponential models to disk.
+  # Save exponential theorem models to disk.
   saveRDS(modelsExp, file=fileNameExp)
@@
 
-  modelsCSP <- list()
+  modelsCST <- list()
   # Output elasticities based on cost share theorem
-  alphaCSP <- 0.3 # Fraction of national accounts spent on capital
-  betaCSP <- 0.7 # Fraction of national accounts spent on labor
+  alphaCST <- 0.3 # Fraction of national accounts spent on capital
+  betaCST <- 0.7 # Fraction of national accounts spent on labor
   for (country in countries){
@@
       # Cobb-Douglas
-      cdModCSP <- lm(log(eval(yVar)) - alphaCSP*log(eval(kVar)) - betaCSP*log(eval(lVar)) ~ eval(tVar), data = data)
-      attr(cdModCSP, "naturalCoeffs") <- data.frame(lambda=coef(cdModCSP)[[2]],
-                                                    logscale=coef(cdModCSP)[[1]], 
-                                                    scale=exp(coef(cdModCSP)[[1]]),
-                                                    alpha_1=alphaCSP,
-                                                    alpha_2=betaCSP, 
+      cdModCST <- lm(log(eval(yVar)) - alphaCST*log(eval(kVar)) - betaCST*log(eval(lVar)) ~ eval(tVar), data = data)
+      attr(cdModCST, "naturalCoeffs") <- data.frame(lambda=coef(cdModCST)[[2]],
+                                                    logscale=coef(cdModCST)[[1]], 
+                                                    scale=exp(coef(cdModCST)[[1]]),
+                                                    alpha_1=alphaCST,
+                                                    alpha_2=betaCST, 
                                                     alpha_3=0)
-      cdModCSP$formula <- form
+      cdModCST$formula <- form
       sdata <- subset(data, select=all.vars(form))
       sdata <- data[complete.cases(sdata), unique(c(all.vars(form), names(data)))]
-      cdModCSP$data <- sdata
-      cdModCSP$response <- sdata$iGDP
-      modelsCSP[[country]][[adj]][["noE"]][["CD"]] <- cdModCSP
+      cdModCST$data <- sdata
+      cdModCST$response <- sdata$iGDP
+      modelsCST[[country]][[adj]][["noE"]][["CD"]] <- cdModCST
       # CES
-      cesModCSP <- plm(log(eval(yVar) / (alphaCSP*eval(kVar)^(-rho_1) + betaCSP*eval(lVar)^(-rho_1))^(-1/rho_1)) ~ eval(tVar),
+      cesModCST <- plm(log(eval(yVar) / (alphaCST*eval(kVar)^(-rho_1) + betaCST*eval(lVar)^(-rho_1))^(-1/rho_1)) ~ eval(tVar),
                        data = historicalData[[country]],
                        params=c(rho_1=0.8))
-      names(cesModCSP$coefficients) <- c("logscale", "lambda", "rho_1")
-      cesModCSP$coefficients <- c(coef(cesModCSP), c(delta_1=alphaCSP, delta=1))
-      attr(cesModCSP, "naturalCoeffs") <- EconModels:::makeNatCoef(cesModCSP)
-      cesModCSP$formula <- form
-      cesModCSP$data <- sdata
-      modelsCSP[[country]][[adj]][["noE"]][["CES"]][["kl"]] <- cesModCSP
+      names(cesModCST$coefficients) <- c("logscale", "lambda", "rho_1")
+      cesModCST$coefficients <- c(coef(cesModCST), c(delta_1=alphaCST, delta=1))
+      attr(cesModCST, "naturalCoeffs") <- EconModels:::makeNatCoef(cesModCST)
+      cesModCST$formula <- form
+      cesModCST$data <- sdata
+      modelsCST[[country]][[adj]][["noE"]][["CES"]][["kl"]] <- cesModCST
     }
@@
   # Save cost-share theorem models to disk.
-  saveRDS(modelsCSP, file=fileNameCSP)
+  saveRDS(modelsCST, file=fileNameCST)
 
@@
                     nest = NA,
-                    CSP = "Reject CSP"))
+                    cst = "Reject CST"))
   res <- cbind(res, naturalCoef(modExp))
@@
 
-# Put all the cost-share theorem (CSP) model coefficients into a data frame
-AllCoeffsCSP <- leaf_apply(modelsCSP, class = c("lm"), f = function(modCSP, id){
+# Put all the cost-share theorem (CST) model coefficients into a data frame
+AllCoeffsCST <- leaf_apply(modelsCST, class = c("lm"), f = function(modCST, id){
   # Parse the id to find out whether this is quality-adjusted data, etc.
@@
                     nest=if(length(id_list) > 4) id_list[[5]] else NA,
-                    CSP="Adhere to CSP"))
-  res <- cbind(res, naturalCoef(modCSP))
+                    cst="Adhere to CST"))
+  res <- cbind(res, naturalCoef(modCST))
   # Now calculate the mean squared error (sse) for each model.
-  sse <- sum(resid(modCSP)^2)
+  sse <- sum(resid(modCST)^2)
   res <- cbind(res, list(sse=sse))
@@
 
-# Put all CD and CES model coefficients into a data frame.  
-AllCoeffsNoCSP <- leaf_apply(models, class = c("CDEmodel", "cesModel", "LINEXmodel"), f = function(mod, id){
+AllCoeffsNoCST <- leaf_apply(models, class = c("CDEmodel", "cesModel", "LINEXmodel"), f = function(mod, id){
   # Parse the id to find out whether this is quality-adjusted data, etc.
@@
                     nest=if(length(id_list) > 4) id_list[[5]] else NA,
-                    CSP="Reject CSP"))
+                    cst="Reject CST"))
   res <- cbind(res, naturalCoef(mod))
@@
 }) %>% do.call(plyr::rbind.fill, .)
-AllCoeffs <- plyr::rbind.fill(AllCoeffsExp, AllCoeffsCSP, AllCoeffsNoCSP)
+AllCoeffs <- plyr::rbind.fill(AllCoeffsExp, AllCoeffsCST, AllCoeffsNoCST)
 # See hint at http://stackoverflow.com/questions/22555249/how-to-merge-data-frame-with-same-column-names
@@
 AllCoeffs$nest <- relevelFactor(as.factor(unlist(AllCoeffs$nest)), c("kl", "kle", "lek", "ekl"))
-AllCoeffs$CSP <- relevelFactor(as.factor(unlist(AllCoeffs$CSP)), c("Adhere to CSP", "Reject CSP"))
+AllCoeffs$cst <- relevelFactor(as.factor(unlist(AllCoeffs$cst)), c("Adhere to CST", "Reject CST"))
 # Rearrange for easier viewing
-AllCoeffs <- arrange(AllCoeffs, Country, model, flavor, energy, nest, CSP)
+AllCoeffs <- arrange(AllCoeffs, Country, model, flavor, energy, nest, cst)
 @
@@
 <<Fitted_and_Residuals>>=
-temp_data_exp <- leaf_apply(modelsExp, class=c("lm"), f = function(model, id){
-  df <- data.frame(select(model$data, Year, Country))
-  df$fittedExp <- exp(fitted(model)) # exp accounts for the fact that the model was fitted in log space.
-  df$ResidualsExp <- resid(model)
-  return(df)
-}) %>% do.call(rbind, .)
-
-temp_data_CSP <- leaf_apply(modelsCSP, class=c("plm", "lm"), f = function(model, id){
-  df <- data.frame(select(model$data, Year, Country, iGDP))
-  df$fitted <- exp(fitted(model)) # fitted is in log space. Return to regular space.
-  df$Residuals <- resid(model) # residuals are in log space, and that is what we want.
-  # Now add meta information
-  id_list <- strsplit(id, split = "[.]")[[1]]
-  df$flavor <- if (id_list[[2]] ==  "unadjusted") "Unadjusted" else "Quality-adjusted"
-  df$energy <- if (id_list[[3]] == "noE") "Without energy" else "With energy"
-  df$model <- id_list[[4]]
-  df$nest <- if (length(id_list) > 4) id_list[[5]] else NA
-  return(df)
-}) %>% do.call(rbind, .)
-temp_data_CSP$CSP <- "Adhere to CSP"
-
-temp_data_noCSP <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, id){
+filenameResampleCoeffs <- ""
+fittedAndResidData <- function(model, id){
+  # ******************************************
+  # getData doesn't work for lm models that are created for CST="Adhere to CST".
+  # After we implement specified values for alpha_1, alpha_2, and alpha_3 in our fitting functions, 
+  # getData(model) will probably work.
+  # At that time, change model$data to getData(model)
   df <- data.frame(select(model$data, Year)) 
@@
   df$Country <- id_list[[1]]
-  df$flavor <- if (id_list[[2]] ==  "unadjusted") "Unadjusted" else "Quality-adjusted"
-  df$energy <- if (id_list[[3]] == "noE") "Without energy" else "With energy"
-  df$model <- id_list[[4]]
-  df$nest <- if (length(id_list) > 4) id_list[[5]] else NA
+  # Exponential models have only 1 item in the id list, namely country. Accommodate that length with if statements.
+  df$flavor <- if (len > 1) (if (id_list[[2]] ==  "unadjusted") "Unadjusted" else "Quality-adjusted") else NA
+  df$energy <- if (len > 2) (if (id_list[[3]] == "noE") "Without energy" else "With energy") else "Without energy"
+  df$model <- if (len > 3) id_list[[4]] else "exp"
+  df$nest <- if (len > 4) id_list[[5]] else NA
   return(df)  
+}
+
+temp_data_exp <- leaf_apply(modelsExp, class=c("lm"), f = function(model, id){
+  # ****************************************************
+  # Not all of the results from this code are not correct at this time.
+  # The residuals are OK.
+  # But, the yhat() call in fittedAndResidData() will not return the correct information from the CST models.
+  # This is because modelsCST was not created with our typical functions.
+  # To correct this problem, we need to add arguments to cdModel and cesModel such that 
+  # the models produced by those functions will be in the correct form for yhat() function.
+  return(fittedAndResidData(model, id))
 }) %>% do.call(rbind, .)
-temp_data_noCSP$CSP <- "Reject CSP"
-
-temp_data_noExp <- plyr::rbind.fill( temp_data_CSP, temp_data_noCSP )
-
-# Now merge the exponential-only model with the CSP and noCSP models. 
-# Doing this, because the exponential-only model is kind-of like iY:
-# it applies to all situations.
-# temp_data <- merge(temp_data_noExp, temp_data_exp)
-fitted_and_resid_data <- merge(temp_data_noExp, temp_data_exp)
-
+temp_data_exp$cst <- "Reject CST"
+
+temp_data_CST <- leaf_apply(modelsCST, class=c("plm", "lm"), f = function(model, id){
+  # ****************************************************
+  # Not all of the results from this code are not correct at this time.
+  # The residuals are OK.
+  # But, the yhat() call in fittedAndResidData() will not return the correct information from the CST models.
+  # This is because modelsCST was not created with our typical functions.
+  # To correct this problem, we need to add arguments to cdModel and cesModel such that 
+  # the models produced by those functions will be in the correct form for yhat() function.
+  return(fittedAndResidData(model, id))
+}) %>% do.call(rbind, .)
+temp_data_CST$cst <- "Adhere to CST"
+
+temp_data_noCST <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, id){
+  return(fittedAndResidData(model, id))  
+}) %>% do.call(rbind, .)
+temp_data_noCST$cst <- "Reject CST"
+
+temp_data <- plyr::rbind.fill( temp_data_exp, temp_data_CST, temp_data_noCST )
+
+# Get the unadjusted, without-energy residuals from models that obey the CST
+# and store them in a data frame
+# r_unadj_noE_CST <- filter(temp_data, flavor=="Unadjusted" & energy=="Without energy" & cst=="Adhere to CST") %>% 
+#   select(Year, Country, Residuals, model)
+# colnames(r_unadj_noE_CST)[colnames(r_unadj_noE_CST)=="Residuals"] <- "r_unadj_noE"
+# Merge to get the unadjusted, without-energy values next to each country, year, and model
+# fitted_and_resid_data <- merge(temp_data, r_unadj_noE_CST)
 # Create a column containing ∆r, the difference between a residual value
-# and the residual value in the same year for the reference model
-fitted_and_resid_data[["Dr"]] <- abs(fitted_and_resid_data[["Residuals"]]) - abs(fitted_and_resid_data[["ResidualsExp"]])
+# and the residual value in the same year for the unadjusted, no-energy case
+# fitted_and_resid_data[["Dr"]] <- abs(fitted_and_resid_data[["Residuals"]]) - abs(fitted_and_resid_data[["r_unadj_noE"]])
+
+# Get the reference residuals (from the exponential-only models) and store them in a data frame
+r_ref <- filter(temp_data, model=="exp") %>% select(Year, Country, Residuals)
+colnames(r_ref)[colnames(r_ref)=="Residuals"] <- "r_ref"
+# Merge to get the reference values in each appropriate row
+fitted_and_resid_data <- merge(temp_data, r_ref)
+# Create a column containing ∆r, the difference between a residual value
+# and the residual value in the same year for the reference case
+fitted_and_resid_data[["Dr"]] <- abs(fitted_and_resid_data[["Residuals"]]) - abs(fitted_and_resid_data[["r_ref"]])
 
@@
 # Make data viewing easier
-fitted_and_resid_data <- arrange(fitted_and_resid_data, Country, CSP, model, flavor, energy, nest)
+fitted_and_resid_data <- arrange(fitted_and_resid_data, Country, cst, model, flavor, energy, nest)
 @
@@
 
-<<Fitted_and_Residual_Graph_Functions>>=
-fittedGraphNoCSP <- function(data){
-  fittedGraphData <- select(data, Year, Country, iGDP, fitted, fittedExp, flavor, energy, CSP, nest)
-  fittedGraphData <- melt(fittedGraphData, 
-                     measure.vars = c("iGDP", "fitted", "fittedExp"), 
-                     value.name = "value", 
-                     variable.name = "variable")
-  fittedGraphData$label <- with(fittedGraphData, paste(variable, energy))
-  # Now collapse some of the information. Don't need multiple versions of the exponential model, e.g.
-  fittedGraphData <- filter(fittedGraphData, label=="iGDP With energy" | label=="fittedExp With energy" |
-                       label == "fitted With energy" | label == "fitted Without energy")
-  fittedGraphData$label <- plyr::mapvalues(fittedGraphData$label, 
-                                      from = c("iGDP With energy", 
-                                               "fittedExp With energy",
-                                               "fitted With energy",
-                                               "fitted Without energy"), 
-                                      to = c("GDP", 
-                                             "Reference model",
-                                             "With energy",
-                                             "Without energy"))
-  # Relevel factors
-  fittedGraphData$label <- relevelFactor(as.factor(fittedGraphData$label), 
-                                         c("GDP", "Reference model", "Without energy", "With energy"))
-  # Make (and return) the graph
+<<Fitted and Residual Graph Functions>>=
+fittedGraphCST <- function(data){
   ggplot() +
-    geom_line(data=fittedGraphData, mapping=aes(x=Year, y=value, group=label, linetype=label)) +
-    scale_linetype_manual(values=c(1,4,2,3), name="") +
+    geom_line(data=filter(data, cst=="Adhere to CST"), mapping=aes(x=Year, y=iGDP)) +
+    geom_line(data=data, mapping=aes(x=Year, y=fitted, linetype=cst)) +
+    scale_linetype_manual(values=c(2,3), name="") +
+    facet_grid(Country ~ flavor) + 
+    xlab("") +
+    ylab("Indexed GDP (1960=1)") +
+    xy_theme()
+}
+
+fittedGraphNoCST <- function(data){
+  ggplot() +
+    geom_line(data=filter(data, energy=="Without energy"), mapping=aes(x=Year, y=iGDP)) +
+    geom_line(data=data, mapping=aes(x=Year, y=fitted, linetype=energy)) +
+    scale_linetype_manual(values=c(2,3), name="") +
     facet_grid(Country ~ flavor) +
@@
 Both historical GDP and fitted GDP are shown in 
-Figures~\ref{fig:Graphs_CESkle-fitted}--\ref{fig:Graphs_CESekl-fitted}.
-%
-<<Graphs_CESkle-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with $kl$ and ($kl$)$e$ nesting that reject the CSP. Solid line is historical GDP.">>=
-fittedGraphData_kle <- fitted_and_resid_data %>% filter(model=="CES" & CSP=="Reject CSP" & (nest == "kl" | nest == "kle"))
-fittedGraphNoCSP(fittedGraphData_kle)
-@
-%
-<<Graphs_CESlek-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with $kl$ and ($le$)$k$ nesting that reject the CSP. Solid line is historical GDP.">>=
-fittedGraphData_lek <- fitted_and_resid_data %>% filter(model=="CES" & CSP=="Reject CSP" & (nest == "kl" | nest == "lek"))
-fittedGraphNoCSP(fittedGraphData_lek)
-@
-%
-<<Graphs_CESekl-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with $kl$ and ($ek$)$l$ nesting that reject the CSP. Solid line is historical GDP.">>=
-fittedGraphData_ekl <- fitted_and_resid_data %>% filter(model=="CES" & CSP=="Reject CSP" & (nest == "kl" | nest == "ekl"))
-fittedGraphNoCSP(fittedGraphData_ekl)
+Figures~\ref{fig:Graphs CESkle-fitted}--\ref{fig:Graphs CESekl-fitted}.
+%
+<<Graphs CESkle-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($kl$)$e$ nesting. Solid line is historical GDP.">>=
+fittedGraphNoCST(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest=="kle" | nest=="kl")))
+@
+%
+<<Graphs CESlek-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($le$)$k$ nesting. Solid line is historical GDP.">>=
+fittedGraphNoCST(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest=="lek" | nest=="kl")))
+@
+%
+<<Graphs CESekl-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($ek$)$l$ nesting. Solid line is historical GDP.">>=
+fittedGraphNoCST(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest=="ekl" | nest=="kl")))
 @
@@
 <<ResidualPlotFunction>>=
-
 residualPlot <- function(data, withEnergyShape = 0){
@@
     facet_grid(Country ~ flavor) +
-    # geom_hline(aes(yintercept = 0), colour="gray50", size=0.1) +
-    geom_hline(yintercept = 0, colour="gray50", size=0.1) +
     scale_x_continuous(breaks=c(1960, 1980, 2000)) +
@@
 }
-
-# This version also plots reference model residuals.
-# But the reference model dwarfs all other residuals and looks bad on the graph.
-# So, I decided not to use this. ---MKH, 14 Aug 2015
-
-# residualPlot <- function(data, withEnergyShape = 0){
-#   # Keep only the data we need
-#   residGraphData <- select(data, Year, Country, Residuals, flavor, energy, model, nest, CSP, ResidualsExp)
-#   # Melt the data so that we can include the reference model, too.
-#   residGraphData <- melt(residGraphData, 
-#                          measure.vars=c("Residuals", "ResidualsExp"),
-#                          value.name="value",
-#                          variable.name="variable")
-#   residGraphData$label <- with(residGraphData, paste(variable, energy))
-#   
-#   # Now collapse some of the information. Don't need multiple versions of the exponential model, e.g.
-#   residGraphData <- filter(residGraphData, label=="Residuals With energy" | label=="Residuals Without energy" |
-#                              label=="ResidualsExp Without energy")
-#   
-#   residGraphData$label <- plyr::mapvalues(residGraphData$label, 
-#                                           from = c("Residuals With energy", 
-#                                                    "Residuals Without energy",
-#                                                    "ResidualsExp Without energy"), 
-#                                           to = c("With energy", 
-#                                                  "Without energy",
-#                                                  "Reference model"))
-#   # Relevel factors
-#   residGraphData$label <- relevelFactor(as.factor(residGraphData$label), 
-#                                          c("Without energy", "With energy", "Reference model"))
-#   
-#   ggplot() +
-#     geom_point(data=residGraphData, mapping=aes(x=Year, y=value, shape=label, color=label, size=label)) +
-#     scale_shape_manual(values=c(1, withEnergyShape, 5)) +
-#     scale_size_manual(values=c(4, 4, 2)) +
-#     # scale_color_manual(values=c("gray50", "green", "red")) +
-#     facet_grid(Country ~ flavor) +
-#     geom_hline(yintercept = 0, colour="gray50", size=0.1) +
-#     scale_x_continuous(breaks=c(1960, 1980, 2000)) +
-#     xlab("") +
-#     ylab("r") + 
-#     xy_theme() +
-#     theme(legend.title=element_blank())
-# }
 @
@@
 %
-<<Graphs_CESkle-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(kl$)$e$ nesting.">>=
-residualPlot(filter(fitted_and_resid_data, model=="CES" & CSP=="Reject CSP" & (nest=="kle" | nest=="kl")), 
+<<Graphs CESkle-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(kl$)$e$ nesting.">>=
+residualPlot(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest=="kle" | nest=="kl")), 
              withEnergyShape = 0) # square
@@
 %
-<<Graphs_CESlek-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with ($le$)$k$ nesting.">>=
-residualPlot(filter(fitted_and_resid_data, model=="CES" & CSP=="Reject CSP" & (nest == "lek" | nest=="kl")),
+<<Graphs CESlek-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with ($le$)$k$ nesting.">>=
+residualPlot(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest == "lek" | nest=="kl")),
              withEnergyShape = 3) # plus
@@
 %
-<<Graphs_CESekl-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(ek$)$l$ nesting.">>=
-residualPlot(filter(fitted_and_resid_data, model=="CES" & CSP=="Reject CSP" & (nest=="ekl" | nest=="kl")),
+<<Graphs CESekl-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(ek$)$l$ nesting.">>=
+residualPlot(filter(fitted_and_resid_data, model=="CES" & cst=="Reject CST" & (nest=="ekl" | nest=="kl")),
              withEnergyShape = 4) # times
@@
 myXTable(filter(AllCoeffs, model=="CES" | model=="exp") %>% 
-           select(Country, model, flavor, energy, nest, CSP, scale, lambda, sse),
+           select(Country, model, flavor, energy, nest, cst, scale, lambda, sse),
          caption="$\\theta$, Solow residual, and $sse$ for CES models.",
@@
 ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=sse, y=lambda, color=energy, size=CSP, shape=nest)) +
+  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=sse, y=lambda, color=energy, size=cst, shape=nest)) +
   geom_vline(aes(xintercept = sse), filter(AllCoeffs, model=="exp") %>% select(Country, sse), colour="gray50", size=0.1) +
@@
   facet_grid(Country ~ flavor) +
-  scale_y_continuous(breaks=c(0, 0.01, 0.02, 0.03), limits=c(0, 0.035)) +
+  scale_y_continuous(breaks=c(0, 0.01, 0.02), limits=c(0, 0.03)) +
   xlab("SSE") + 
@@
 \subsubsection{Rejecting (or adhering to) the cost share theorem} 
-\label{sec:gfsr_CSP}
+\label{sec:gfsr_cst}
 %------------------------------
@@
 myXTable(filter(AllCoeffs, model=="CES" | model=="exp") %>% 
-           select(Country, model, flavor, energy, nest, CSP, alpha_1, alpha_2, alpha_3),
+           select(Country, model, flavor, energy, nest, cst, alpha_1, alpha_2, alpha_3),
          caption="Factor shares~($\\alpha$) for CES models.",
@@
   bar_chart_data <- filter(AllCoeffs, Country==coun & model==mod) %>% 
-    select(Country, model, flavor, energy, nest, CSP, alpha_1, alpha_2, alpha_3)
+    select(Country, model, flavor, energy, nest, cst, alpha_1, alpha_2, alpha_3)
   # Change nest to a nicer-looking nest string
@@
   # Add a label column
-  bar_chart_data$label <- paste(bar_chart_data$CSP, bar_chart_data$flavor, 
+  bar_chart_data$label <- paste(bar_chart_data$cst, bar_chart_data$flavor, 
                                 bar_chart_data$energy, bar_chart_data$nest, sep=", ")
@@
 \subsubsection{Rejecting (or adhering to) the cost share theorem} 
-\label{sec:fs_CSP}
+\label{sec:fs_cst}
 %------------------------------
@@
 myXTable(filter(AllCoeffs, model=="CES") %>% 
-           select(Country, model, flavor, energy, nest, CSP, sigma_1, sigma),
+           select(Country, model, flavor, energy, nest, cst, sigma_1, sigma),
          caption="Factor substitution~($\\sigma$) for CES models.",
@@
 \subsubsection{Rejecting (or adhering to) the cost share theorem} 
-\label{sec:sigma_CSP}
+\label{sec:sigma_cst}
 %------------------------------
@@
 standardTriPlot(data=resampleCoeffs, facet_formula=~Country, alpha=0.1,
-                labels=c("alpha[e]", "alpha[k]", "alpha[l]"), size=2.0)
+                labels=c("alpha[e]", "alpha[k]", "alpha[l]"))
 @
@@
                     facet_formula=~Country, alpha=0.1) +
-    coord_trans(y="sigma") +
+    coord_trans(y="sigma2") +
     scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0), limits=c(0,1)) +
@@
 \subsection{Correlograms for models that adhere to the cost-share theorem} 
-\label{sec:correlograms_CSP}
+\label{sec:correlograms_CST}
 %++++++++++++++++++++++++++++++
@@
 
-<<Correlograms_CSP, echo=FALSE, message=FALSE>>=
-leaf_apply(l = modelsCSP, class = c("lm", "plm"), f = function(model, name){
+<<Correlograms_CST, echo=FALSE, message=FALSE>>=
+leaf_apply(l = modelsCST, class = c("lm", "plm"), f = function(model, name){
   acf(resid(model), main=name)
@@
 \subsection{Correlograms for models that reject the cost-share theorem} 
-\label{sec:correlograms_noCSP}
+\label{sec:correlograms_noCST}
 %++++++++++++++++++++++++++++++
@@
 
-<<Correlograms_noCSP, echo=FALSE, message=FALSE>>=
+<<Correlograms_noCST, echo=FALSE, message=FALSE>>=
 leaf_apply(l = models, class = c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, name){
@@
 %
-<<Graphs_CD-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Cobb-Douglas models that reject the cost-share theorem. Solid line is historical GDP.">>=
-fittedGraphNoCSP(filter(fitted_and_resid_data, model=="CD" & CSP=="Reject CSP"))
-@
-
-%
-<<Graphs_CD-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for Cobb-Douglas models.">>=
-residualPlot(filter(fitted_and_resid_data, model=="CD" & CSP=="Reject CSP"))
-@
-
-Table~\ref{tab:Effect_of_CSP_CD} shows the effect of the CSP 
+<<Graphs CD-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Cobb-Douglas models that reject the cost-share theorem. Solid line is historical GDP.">>=
+fittedGraphNoCST(filter(fitted_and_resid_data, model=="CD" & cst=="Reject CST"))
+@
+
+%
+<<Graphs CD-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for Cobb-Douglas models.">>=
+residualPlot(filter(fitted_and_resid_data, model=="CD" & cst=="Reject CST"))
+@
+
+Table~\ref{tab:Effect_of_CST_CD} shows the effect of the CST 
 on fitted parameters for the Cobb-Douglas model and the exponential-only model.
@@
 %
-<<Effect_of_CSP_CD, results="asis">>=
+<<Effect_of_CST_CD, results="asis">>=
 myXTable(filter(AllCoeffs, (model=="CD" & flavor=="Unadjusted" & energy=="Without energy") | model=="exp") %>% 
-           select(Country, model, CSP, scale, lambda, alpha_1, alpha_2, sse),
+           select(Country, model, cst, scale, lambda, alpha_1, alpha_2, sse),
          caption="Model parameters for Cobb-Douglas models with unadjusted factors of production, without energy.",
@@
 myXTable(filter(AllCoeffs, model=="CD" | model=="exp") %>% 
-           select(Country, model, flavor, energy, CSP, scale, lambda, alpha_1, alpha_2, alpha_3, sse),
+           select(Country, model, flavor, energy, cst, scale, lambda, alpha_1, alpha_2, alpha_3, sse),
          caption="Model parameters for all Cobb-Douglas models.",
@@
 <<DSRsse_CD, results="asis">>=
-myXTable(filter(AllCoeffs, model=="CD") %>% select(Country, model, flavor, energy, CSP, Dlambda, Dsse),
+myXTable(filter(AllCoeffs, model=="CD") %>% select(Country, model, flavor, energy, cst, Dlambda, Dsse),
          caption="$\\Delta \\lambda$ and $\\Delta sse$ for Cobb-Douglas models.",
@@
 ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CD"), mapping=aes(x=Dsse, y=Dlambda, color=energy, size=CSP)) +
+  geom_point(data=filter(AllCoeffs, model=="CD"), mapping=aes(x=Dsse, y=Dlambda, color=energy, size=cst)) +
   facet_grid(Country ~ flavor) +
@@
 ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CD"), mapping=aes(x=percDsse, y=percDlambda, color=energy, size=CSP)) +
+  geom_point(data=filter(AllCoeffs, model=="CD"), mapping=aes(x=percDsse, y=percDlambda, color=energy, size=cst)) +
   facet_grid(Country ~ flavor) +
@@
 ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=Dsse, y=Dlambda, color=energy, size=CSP, shape=nest)) +
+  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=Dsse, y=Dlambda, color=energy, size=cst, shape=nest)) +
   scale_size_manual(values=c(2,3.5)) +
@@
 ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=percDsse, y=percDlambda, color=energy, size=CSP, shape=nest)) +
+  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=percDsse, y=percDlambda, color=energy, size=cst, shape=nest)) +
   scale_size_manual(values=c(2,3.5)) +

### 2015-08-18 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Better comments.

@@
 
-# Tell whether to re-run the analysis to create the models.
-# This file will use previously-saved models to generate
+# Tell whether to re-run the analysis to create the models
+# or the resampling on the (kl)e models.
+# This file will use previously-saved models and resampling to generate
 # the paper if set to FALSE, greatly reducing time.
 # If something changes in the data or in the code that
-# performs the analysis, set 
+# performs the analysis or resampling, set 
 # rerunModels = TRUE
+# rerunResampling = TRUE
 # once to re-generate the information needed to 

### 2015-08-18 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Now including digits=10.

@@
                                                                         data = historicalData[[country]], 
-                                                                        nest=c(1,2))
+                                                                        nest=c(1,2), digits = 10)
       nestsWithE <- list(kle=c(1,2,3), lek=c(2,3,1), ekl=c(3,1,2))
       models[[country]][[flavor]][["withE"]][["CES"]] <- lapply(nestsWithE, function(nest){
-          cesModel(formula=fwithE, data=historicalData[[country]], nest=nest)
+          cesModel(formula=fwithE, data=historicalData[[country]], nest=nest, digits = 10)
         })

### 2015-08-18 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
No need to set limits.

@@
   xlab(expression(Delta * sse)) + 
-  scale_x_continuous(breaks=seq(-0.01, 0, 0.005), limits=c(-0.012, 0.003)) +  
+  # scale_x_continuous(breaks=seq(-0.01, 0, 0.005), limits=c(-0.012, 0.003)) +  
   ylab(expression(Delta * lambda)) +

### 2015-08-18 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Deleted unneeded comment.

--- 2015-08-18 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
@@
   xlab(expression(Delta * sse)) + 
-  scale_x_continuous(breaks=seq(-0.01, 0, 0.005), limits=c(-0.012, 0.003)) +  
   ylab(expression(Delta * lambda)) +

### 2015-08-18 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Now including two tables for nest-aware sigmas.

@@
 %
+<<CES_sigma_nest_aware_inner, results="asis">>=
+myXTable(filter(AllCoeffs, model=="CES") %>% 
+           select(Country, model, flavor, energy, nest, CSP, sigma_12, sigma_23, sigma_13),
+         caption="Factor substitution~($\\sigma$) for CES models. Inner nests.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
+%
+<<CES_sigma_nest_aware_outer, results="asis">>=
+myXTable(filter(AllCoeffs, model=="CES") %>% 
+           select(Country, model, flavor, energy, nest, CSP, sigma_12_3, sigma_23_1, sigma_13_2),
+         caption="Factor substitution~($\\sigma$) for CES models. Outer nests.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
 

### 2015-08-18 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Better formatting for column titles.

--- 2015-08-18 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
@@
         math.style.negative=TRUE, 
+        sanitize.text.function=function(x){x},
         booktabs=TRUE)
@@
 <<CES_alpha, results="asis">>=
-myXTable(filter(AllCoeffs, model=="CES" | model=="exp") %>% 
-           select(Country, model, flavor, energy, nest, CSP, alpha_1, alpha_2, alpha_3),
+data_CES_alpha <- filter(AllCoeffs, model=="CES" | model=="exp") %>% 
+  select(Country, model, flavor, energy, nest, CSP, alpha_1, alpha_2, alpha_3)
+data_CES_alpha <- plyr::rename(data_CES_alpha, c("alpha_1" = "$\\alpha_1$",
+                                                 "alpha_2" = "$\\alpha_2$",
+                                                 "alpha_3" = "$\\alpha_3$"))
+myXTable(data_CES_alpha,
          caption="Factor shares~($\\alpha$) for CES models.",
@@
 %
+<<CES_sigma_table_data>>=
+sigma_data <- filter(AllCoeffs, model=="CES") 
+sigma_data <- plyr::rename(sigma_data, c("model" = "Model", "flavor" = "Type", "energy" = "Energy", "nest" = "Nest"))
+@
+
 <<CES_sigma, results="asis">>=
-myXTable(filter(AllCoeffs, model=="CES") %>% 
-           select(Country, model, flavor, energy, nest, CSP, sigma_1, sigma),
+data_CES_sigma_raw <- sigma_data %>% select(Country, Model, Type, Energy, Nest, CSP, sigma_1, sigma)
+data_CES_sigma_raw <- plyr::rename(data_CES_sigma_raw, c("sigma" = "$\\sigma$",
+                                                         "sigma_1" = "$\\sigma_1$"))
+myXTable(data_CES_sigma_raw,
          caption="Factor substitution~($\\sigma$) for CES models.",
@@
 %
+<<CES_sigma_nest_aware_inner, results="asis">>=
+sigma_inner_data <- sigma_data %>% select(Country, Type, Energy, Nest, CSP, sigma_12, sigma_23, sigma_13)
+sigma_inner_data <- plyr::rename(sigma_inner_data, c("sigma_12" = "$\\sigma_{kl}$",
+                                                     "sigma_23" = "$\\sigma_{le}$",
+                                                     "sigma_13" = "$\\sigma_{ek}$"))
+#
+myXTable(sigma_inner_data,
+         caption="Factor substitution~($\\sigma$) for CES models. Inner nests.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
+%
+<<CES_sigma_nest_aware_outer, results="asis">>=
+sigma_outer_data <- sigma_data %>% select(Country, Type, Energy, Nest, CSP, sigma_12_3, sigma_23_1, sigma_13_2)
+sigma_outer_data <- plyr::rename(sigma_outer_data, c("sigma_12_3" = "$\\sigma_{(kl)e}$",
+                                                     "sigma_23_1" = "$\\sigma_{(le)k}$",
+                                                     "sigma_13_2" = "$\\sigma_{(ek)l}$"))
+myXTable(sigma_outer_data,
+         caption="Factor substitution~($\\sigma$) for CES models. Outer nests.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
 
@@
 <<Effect_of_CSP_CD, results="asis">>=
-myXTable(filter(AllCoeffs, (model=="CD" & flavor=="Unadjusted" & energy=="Without energy") | model=="exp") %>% 
-           select(Country, model, CSP, scale, lambda, alpha_1, alpha_2, sse),
+data_CSP_CD <- filter(AllCoeffs, (model=="CD" & flavor=="Unadjusted" & energy=="Without energy") | model=="exp") %>% 
+  select(Country, model, CSP, scale, lambda, alpha_1, alpha_2, sse)
+data_CSP_CD <- plyr::rename(data_CSP_CD, c("alpha_1" = "$\\alpha_1$", "alpha_2" = "$\\alpha_2$"))
+myXTable(data_CSP_CD,
          caption="Model parameters for Cobb-Douglas models with unadjusted factors of production, without energy.",
@@
 <<CD_coeffs, results="asis">>=
-myXTable(filter(AllCoeffs, model=="CD" | model=="exp") %>% 
-           select(Country, model, flavor, energy, CSP, scale, lambda, alpha_1, alpha_2, alpha_3, sse),
+data_CD_exp <- filter(AllCoeffs, model=="CD" | model=="exp") %>% 
+  select(Country, model, flavor, energy, CSP, scale, lambda, alpha_1, alpha_2, alpha_3, sse)
+data_CD_exp <- plyr::rename(data_CD_exp, c("alpha_1" = "$\\alpha_1$", 
+                                           "alpha_2" = "$\\alpha_2$", 
+                                           "alpha_3" = "$\\alpha_3$"))
+myXTable(data_CD_exp,
          caption="Model parameters for all Cobb-Douglas models.",

### 2015-08-19 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Better formatting for tables. Rearrange paper.

@@
 \end{table}
-
-Unadjusted and quality-adjusted data for both Portugal and the United Kingdom 
-are shown in Figure~\ref{fig:Historical_Data_Graph}.
-
-<<Historical_Data_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Historical data.", warning=FALSE>>=
-# Melt the data into a form that is useful in a couple places
-histDataForGraph <- leaf_apply(formulas, class = "formula", f=function(form, name){
-  meta <- strsplit(name, split="[.]") %>% unlist
-  Country <- meta[1]
-  flavor <- meta[2]
-  measure.vars <- c(summands(form, right=FALSE), summands(form, 1:3))
-  trimmed_historical_data <- historicalData[[Country]][c("Year", measure.vars)]
-  mtrimmed_historical_data <- melt(trimmed_historical_data, measure.vars = measure.vars, 
-                                   value.name = "value", variable.name = "variable")
-  mtrimmed_historical_data$Country <- Country
-  mtrimmed_historical_data$flavor <- if (flavor == "adjusted") "Quality-adjusted" else "Unadjusted"
-  return(mtrimmed_historical_data)
-}) %>% do.call(rbind, .)
-
-# Change variable names to make a nicer-looking graph
-histDataForGraph$variable <- plyr::mapvalues(histDataForGraph$variable,
-                                             from=c("iGDP", 
-                                                    "iKstkS.L", "iKservS.L", "iKstkO.WwithRD", "iKservO.WwithRD",
-                                                    "iL", "ihLest",
-                                                    "iXpMP", "iXp", "iUMP", "iU"),
-                                             to=c("y", 
-                                                  "k", "k", "k", "k",
-                                                  "l", "l",
-                                                  "e", "e", "e", "e"))
-
-# Relevel factors before plotting
-histDataForGraph$Country <- relevelFactor(as.factor(histDataForGraph$Country), c("PT", "UK"))
-histDataForGraph$flavor <- relevelFactor(as.factor(histDataForGraph$flavor), c("Unadjusted", "Quality-adjusted"))
-histDataForGraph$variable <- relevelFactor(as.factor(histDataForGraph$variable), unique(histDataForGraph$variable))
-
-historicalPlot(histDataForGraph, 
-               mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
-               facet_formula = Country ~ flavor, 
-               line_types = c(1,2,4,3,2,4,3,2,3,2,3)) + 
-  scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12)) +
-  coord_cartesian(ylim=c(0.5, 13)) +
-  xlab("") + 
-  ylab("Indexed (1960=1)")
-@
-
-<<Pre-econometric_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Pre-econometric data.", warning=FALSE>>=
-pre_econometric_data <- leaf_apply(formulas, class = "formula", f=function(form, name){
-  meta <- strsplit(name, split="[.]") %>% unlist
-  Country <- meta[1]
-  flavor <- meta[2]
-  nums <- summands(form, n=1:3)
-  denom <- summands(form, n=1, right=FALSE)
-  ratios <- lapply(nums, function(num) {paste(num, denom, sep="/")}) %>% unlist
-  coltemplate <- build_formula(NULL, c("Year", ratios))
-  trimmed_historical_data <- historicalData[[Country]][all.vars(coltemplate)]
-  ratio_data <- evalFormula(coltemplate, data=trimmed_historical_data)$right
-  mratio_data <- melt(ratio_data, measure.vars = ratios, value.name = "ratio", variable.name = "variable")
-  mratio_data$Country <- Country
-  mratio_data$flavor <- if (flavor == "adjusted") "Quality-adjusted" else "Unadjusted"
-  return(mratio_data)
-}) %>% do.call(rbind, .)
-
-# Fix levels
-pre_econometric_data$flavor <- relevelFactor(as.factor(as.character(pre_econometric_data$flavor)), 
-                                               c("Unadjusted", "Quality-adjusted"))
-pre_econometric_data$Country <- relevelFactor(as.factor(pre_econometric_data$Country), 
-                                              c("PT", "UK"))
-pre_econometric_data$variable <- relevelFactor(as.factor(pre_econometric_data$variable),
-                                               unique(pre_econometric_data$variable))
-# Now make the plot of pre-econometric data
-historicalPlot(pre_econometric_data, 
-               mapping=aes(x=Year, y=ratio, group=variable, linetype=variable), 
-               facet_formula = Country ~ flavor, 
-               line_types = c(2,4,3, 2,4,3, 2,3,2, 3)) + 
-  xlab("") + 
-  ylab("Indexed (1960=1)")
-@
 
@@
                     nest = NA,
-                    CSP = "Reject CSP"))
+                    CSP = NA))
   res <- cbind(res, naturalCoef(modExp))
@@
 fitted_and_resid_data <- arrange(fitted_and_resid_data, Country, CSP, model, flavor, energy, nest)
+@
+
+%++++++++++++++++++++++++++++++
+\subsection{Fitting residuals} 
+\label{sec:fitting_residuals}
+%++++++++++++++++++++++++++++++
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results}
+\label{sec:results}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The primary results from this paper involve the effects of
+the following modeling decisions:
+rejecting (or adhering to) the cost share theorem,
+quality-adjusting (or not) the factors of production,
+including energy (or not) in the production function, and
+nesting (in the CES model).
+
+We evaluate the effects of these modeling decisions 
+first on goodness of fit and Solow residual,
+next on factor shares, and 
+finally on factor substitutability.
+
+%++++++++++++++++++++++++++++++
+\subsection{Goodness of fit and Solow residual} 
+\label{sec:fit_and_sr}
+%++++++++++++++++++++++++++++++
+
+%
+We can evaluate the effect of modeling decisions on 
+goodness of fit and Solow residual by
+calculating values relative to the reference model.
+To do so, we define 
+$\Delta \lambda$ and $\Delta sse$, where
+%
+\begin{equation} \label{eq:delta_lambda}
+  \Delta \lambda \equiv \lambda - \lambda_{ref}
+\end{equation}
+%
+and
+%
+\begin{equation} \label{eq:delta_sse}
+  \Delta sse \equiv sse - sse_{ref},
+\end{equation}
+%
+with~$\lambda_{ref}$ and $sse_{ref}$ being the values 
+of the Solow residual and $sse$ for the reference model, respectively.
+On a percentage basis,
+%
+\begin{equation} \label{eq:delta_lambda_perc}
+  \Delta \lambda \, [\%] = \frac{100 \, \Delta \lambda}{\lambda_{ref}} 
+            = \frac{100 \, \lambda}{\lambda_{ref}} - 1 \; ,
+\end{equation}
+%
+and
+%
+\begin{equation} \label{eq:delta_sse_perc}
+  \Delta sse \, [\%] = \frac{100 \, \Delta sse}{sse_{ref}} 
+            = \frac{100 \, sse}{sse_{ref}} - 1 \; .
+\end{equation}
+
+When $\Delta \lambda$, $\Delta \lambda \, [\%]$, or $\Delta sse$ are negative, 
+we observe reduction in the Solow residual ($\lambda$) or
+the fitting residuals ($sse$)
+relative to the reference model.
+
+Figure~\ref{fig:DSRsse_CES_graph} summarizes 
+$\lambda$ and $sse$ 
+results for CES models.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Graphs for paper} 
+\label{sec:graphs_for_paper}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Unadjusted and quality-adjusted data for both Portugal and the United Kingdom 
+are shown in Figure~\ref{fig:Historical_Data_Graph}.
+
+<<Historical_Data_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Historical data.", warning=FALSE>>=
+# Melt the data into a form that is useful in a couple places
+histDataForGraph <- leaf_apply(formulas, class = "formula", f=function(form, name){
+  meta <- strsplit(name, split="[.]") %>% unlist
+  Country <- meta[1]
+  flavor <- meta[2]
+  measure.vars <- c(summands(form, right=FALSE), summands(form, 1:3))
+  trimmed_historical_data <- historicalData[[Country]][c("Year", measure.vars)]
+  mtrimmed_historical_data <- melt(trimmed_historical_data, measure.vars = measure.vars, 
+                                   value.name = "value", variable.name = "variable")
+  mtrimmed_historical_data$Country <- Country
+  mtrimmed_historical_data$flavor <- if (flavor == "adjusted") "Quality-adjusted" else "Unadjusted"
+  return(mtrimmed_historical_data)
+}) %>% do.call(rbind, .)
+
+# Change variable names to make a nicer-looking graph
+histDataForGraph$variable <- plyr::mapvalues(histDataForGraph$variable,
+                                             from=c("iGDP", 
+                                                    "iKstkS.L", "iKservS.L", "iKstkO.WwithRD", "iKservO.WwithRD",
+                                                    "iL", "ihLest",
+                                                    "iXpMP", "iXp", "iUMP", "iU"),
+                                             to=c("y", 
+                                                  "k", "k", "k", "k",
+                                                  "l", "l",
+                                                  "e", "e", "e", "e"))
+
+# Relevel factors before plotting
+histDataForGraph$Country <- relevelFactor(as.factor(histDataForGraph$Country), c("PT", "UK"))
+histDataForGraph$flavor <- relevelFactor(as.factor(histDataForGraph$flavor), c("Unadjusted", "Quality-adjusted"))
+histDataForGraph$variable <- relevelFactor(as.factor(histDataForGraph$variable), unique(histDataForGraph$variable))
+
+historicalPlot(histDataForGraph, 
+               mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
+               facet_formula = Country ~ flavor, 
+               line_types = c(1,2,4,3,2,4,3,2,3,2,3)) + 
+  scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12)) +
+  coord_cartesian(ylim=c(0.5, 13)) +
+  xlab("") + 
+  ylab("Indexed (1960=1)")
 @
@@
 @
-%
-<<Graphs_CESlek-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with $kl$ and ($le$)$k$ nesting that reject the CSP. Solid line is historical GDP.">>=
-fittedGraphData_lek <- fitted_and_resid_data %>% filter(model=="CES" & CSP=="Reject CSP" & (nest == "kl" | nest == "lek"))
-fittedGraphNoCSP(fittedGraphData_lek)
-@
-%
-<<Graphs_CESekl-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with $kl$ and ($ek$)$l$ nesting that reject the CSP. Solid line is historical GDP.">>=
-fittedGraphData_ekl <- fitted_and_resid_data %>% filter(model=="CES" & CSP=="Reject CSP" & (nest == "kl" | nest == "ekl"))
-fittedGraphNoCSP(fittedGraphData_ekl)
-@
-
-%++++++++++++++++++++++++++++++
-\subsection{Fitting residuals} 
-\label{sec:fitting_residuals}
-%++++++++++++++++++++++++++++++
 
 <<ResidualPlotFunction>>=
-
 residualPlot <- function(data, withEnergyShape = 0){
@@
 %
-<<Graphs_CESlek-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with ($le$)$k$ nesting.">>=
-residualPlot(filter(fitted_and_resid_data, model=="CES" & CSP=="Reject CSP" & (nest == "lek" | nest=="kl")),
-             withEnergyShape = 3) # plus
-@
-%
-<<Graphs_CESekl-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(ek$)$l$ nesting.">>=
-residualPlot(filter(fitted_and_resid_data, model=="CES" & CSP=="Reject CSP" & (nest=="ekl" | nest=="kl")),
-             withEnergyShape = 4) # times
-@
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
-\label{sec:results}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The primary results from this paper involve the effects of
-the following modeling decisions:
-rejecting (or adhering to) the cost share theorem,
-quality-adjusting (or not) the factors of production,
-including energy (or not) in the production function, and
-nesting (in the CES model).
-
-We evaluate the effects of these modeling decisions 
-first on goodness of fit and Solow residual,
-next on factor shares, and 
-finally on factor substitutability.
-
-%++++++++++++++++++++++++++++++
-\subsection{Goodness of fit and Solow residual} 
-\label{sec:fit_and_sr}
-%++++++++++++++++++++++++++++++
-
-Table~\ref{tab:CES_sr_gof} shows 
-the Solow residual~($\lambda$) and
-goodness of fit~($sse$)
-for all modeling decisions.
-%
-<<CES_sr_gof, results="asis">>=
-myXTable(filter(AllCoeffs, model=="CES" | model=="exp") %>% 
-           select(Country, model, flavor, energy, nest, CSP, scale, lambda, sse),
-         caption="$\\theta$, Solow residual, and $sse$ for CES models.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-%
-We can evaluate the effect of modeling decisions on 
-goodness of fit and Solow residual by
-calculating values relative to the reference model.
-To do so, we define 
-$\Delta \lambda$ and $\Delta sse$, where
-%
-\begin{equation} \label{eq:delta_lambda}
-  \Delta \lambda \equiv \lambda - \lambda_{ref}
-\end{equation}
-%
-and
-%
-\begin{equation} \label{eq:delta_sse}
-  \Delta sse \equiv sse - sse_{ref},
-\end{equation}
-%
-with~$\lambda_{ref}$ and $sse_{ref}$ being the values 
-of the Solow residual and $sse$ for the reference model, respectively.
-On a percentage basis,
-%
-\begin{equation} \label{eq:delta_lambda_perc}
-  \Delta \lambda \, [\%] = \frac{100 \, \Delta \lambda}{\lambda_{ref}} 
-            = \frac{100 \, \lambda}{\lambda_{ref}} - 1 \; ,
-\end{equation}
-%
-and
-%
-\begin{equation} \label{eq:delta_sse_perc}
-  \Delta sse \, [\%] = \frac{100 \, \Delta sse}{sse_{ref}} 
-            = \frac{100 \, sse}{sse_{ref}} - 1 \; .
-\end{equation}
-
-When $\Delta \lambda$, $\Delta \lambda \, [\%]$, or $\Delta sse$ are negative, 
-we observe reduction in the Solow residual ($\lambda$) or
-the fitting residuals ($sse$)
-relative to the reference model.
-
-Figure~\ref{fig:DSRsse_CES_graph} summarizes 
-$\lambda$ and $sse$ 
-results for CES models.
+
+%++++++++++++++++++++++++++++++
+\subsection{Factor shares} 
+\label{sec:shares}
+%++++++++++++++++++++++++++++++
 
@@
 
-%------------------------------
-\subsubsection{Rejecting (or adhering to) the cost share theorem} 
-\label{sec:gfsr_CSP}
-%------------------------------
-
-%------------------------------
-\subsubsection{Quality-adjusting (or not) factors of production} 
-\label{sec:gfsr_fop}
-%------------------------------
-
-%------------------------------
-\subsubsection{Including energy (or not)} 
-\label{sec:gfsr_energy}
-%------------------------------
-
-%------------------------------
-\subsubsection{CES nesting} 
-\label{sec:gfsr_nesting}
-%------------------------------
-
-%++++++++++++++++++++++++++++++
-\subsection{Factor shares} 
-\label{sec:shares}
-%++++++++++++++++++++++++++++++
-
-Table~\ref{tab:CES_alpha} shows 
-the factor shares~($\alpha_i$ values) for all CES modeling decisions.
-%
-<<CES_alpha, results="asis">>=
-data_CES_alpha <- filter(AllCoeffs, model=="CES" | model=="exp") %>% 
-  select(Country, model, flavor, energy, nest, CSP, alpha_1, alpha_2, alpha_3)
-data_CES_alpha <- plyr::rename(data_CES_alpha, c("alpha_1" = "$\\alpha_1$",
-                                                 "alpha_2" = "$\\alpha_2$",
-                                                 "alpha_3" = "$\\alpha_3$"))
-myXTable(data_CES_alpha,
-         caption="Factor shares~($\\alpha$) for CES models.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
 %
@@
 
-%------------------------------
-\subsubsection{Rejecting (or adhering to) the cost share theorem} 
-\label{sec:fs_CSP}
-%------------------------------
-
-%------------------------------
-\subsubsection{Quality-adjusting (or not) factors of production} 
-\label{sec:fs_fop}
-%------------------------------
-
-%------------------------------
-\subsubsection{Including energy (or not)} 
-\label{sec:fs_energy}
-%------------------------------
-
-%------------------------------
-\subsubsection{CES nesting} 
-\label{sec:fs_nesting}
-%------------------------------
-
-%++++++++++++++++++++++++++++++
-\subsection{Factor substitutability} 
-\label{sec:substitutability}
-%++++++++++++++++++++++++++++++
-
-Table~\ref{tab:CES_sigma} shows 
-substitutability parameters~($\sigma_i$ values) 
-for all CES modeling decisions.
-
-**** Note: At the present time, Table~\ref{tab:CES_sigma}
-requires a LOT of effort to interpret, 
-because $\sigma_1$ and $\sigma$ have different meanings
-for each nesting.
-I'm planning to change the table to make interpretation easier. ---MKH ****
-
-**** Is there a graph we want to make here? ---MKH ****
-%
-<<CES_sigma_table_data>>=
-sigma_data <- filter(AllCoeffs, model=="CES") 
-sigma_data <- plyr::rename(sigma_data, c("model" = "Model", "flavor" = "Type", "energy" = "Energy", "nest" = "Nest"))
-@
-
-<<CES_sigma, results="asis">>=
-data_CES_sigma_raw <- sigma_data %>% select(Country, Model, Type, Energy, Nest, CSP, sigma_1, sigma)
-data_CES_sigma_raw <- plyr::rename(data_CES_sigma_raw, c("sigma" = "$\\sigma$",
-                                                         "sigma_1" = "$\\sigma_1$"))
-myXTable(data_CES_sigma_raw,
-         caption="Factor substitution~($\\sigma$) for CES models.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-%
-<<CES_sigma_nest_aware_inner, results="asis">>=
-sigma_inner_data <- sigma_data %>% select(Country, Type, Energy, Nest, CSP, sigma_12, sigma_23, sigma_13)
-sigma_inner_data <- plyr::rename(sigma_inner_data, c("sigma_12" = "$\\sigma_{kl}$",
-                                                     "sigma_23" = "$\\sigma_{le}$",
-                                                     "sigma_13" = "$\\sigma_{ek}$"))
-#
-myXTable(sigma_inner_data,
-         caption="Factor substitution~($\\sigma$) for CES models. Inner nests.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-%
-<<CES_sigma_nest_aware_outer, results="asis">>=
-sigma_outer_data <- sigma_data %>% select(Country, Type, Energy, Nest, CSP, sigma_12_3, sigma_23_1, sigma_13_2)
-sigma_outer_data <- plyr::rename(sigma_outer_data, c("sigma_12_3" = "$\\sigma_{(kl)e}$",
-                                                     "sigma_23_1" = "$\\sigma_{(le)k}$",
-                                                     "sigma_13_2" = "$\\sigma_{(ek)l}$"))
-myXTable(sigma_outer_data,
-         caption="Factor substitution~($\\sigma$) for CES models. Outer nests.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-
-%------------------------------
-\subsubsection{Rejecting (or adhering to) the cost share theorem} 
-\label{sec:sigma_CSP}
-%------------------------------
-
-%------------------------------
-\subsubsection{Quality-adjusting (or not) factors of production} 
-\label{sec:sigma_fop}
-%------------------------------
-
-%------------------------------
-\subsubsection{Including energy (or not)} 
-\label{sec:sigma_energy}
-%------------------------------
-
-%------------------------------
-\subsubsection{CES nesting} 
-\label{sec:sigma_nesting}
-%------------------------------
-
 %++++++++++++++++++++++++++++++
@@
     labs(x=expression(delta), y=expression(sigma["(kl)"*e]))
+@
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Tables for paper} 
+\label{sec:tables_for_paper}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Table~\ref{tab:CES_sr_gof} shows estimated values of
+the scale parameter~($\theta$),
+the Solow residual~($\lambda$), and
+goodness of fit~($sse$)
+for all modeling choices.
+
+<<Table_data>>=
+table_data <- AllCoeffs 
+table_data <- plyr::rename(table_data, c("model" = "Model", 
+                                         "energy" = "Energy", 
+                                         "nest" = "Nest"))
+table_data$Nest <- plyr::mapvalues(table_data$Nest,
+                                   from=c("kl", "kle", "lek", "ekl"),
+                                   to=c("$kl$", "$(kl)e$", "$(le)k$", "$(ek)l$"))
+table_data$CSP <- plyr::mapvalues(table_data$CSP, 
+                                  from=c("Adhere to CSP", "Reject CSP"), 
+                                  to=c("Adhere", "Reject"))
+table_data$Energy <- plyr::mapvalues(table_data$Energy, 
+                                     from=c("Without energy", "With energy"), 
+                                     to=c("Without", "With"))
+table_data$model <- plyr::mapvalues(table_data$model, 
+                                    from=c("exp"), 
+                                    to=c("Ref."))
+@
+
+<<CES_sr_gof, results="asis">>=
+data_CES_SR_gof <- filter(table_data, Model=="CES" | Model=="Ref.") %>% 
+  select(Country, Model, flavor, Energy, Nest, CSP, scale, lambda, sse)
+data_CES_SR_gof <- plyr::rename(data_CES_SR_gof, c("flavor" = "Factors of prod.",
+                                                   "scale" = "$\\theta$",
+                                                   "lambda" = "$\\lambda$"))
+myXTable(data_CES_SR_gof,
+         caption="Scale parameter~($\\theta$), Solow residual~($\\lambda$), and sum of squared errors~($sse$) for all modeling choices.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
+
+Table~\ref{tab:CES_alpha} shows 
+output elasticities~($\alpha$) for all modeling choices.
+
+<<CES_alpha, results="asis">>=
+data_CES_alpha <- filter(table_data, Model=="CES" | Model=="Ref.") %>% 
+  select(Country, Model, flavor, Energy, Nest, CSP, alpha_1, alpha_2, alpha_3)
+data_CES_alpha <- plyr::rename(data_CES_alpha, c("flavor" = "Factors of prod.",
+                                                 "alpha_1" = "$\\alpha_k$",
+                                                 "alpha_2" = "$\\alpha_l$",
+                                                 "alpha_3" = "$\\alpha_e$"))
+myXTable(data_CES_alpha,
+         caption="Output elasticities~($\\alpha$) for all models.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
+
+<<CES_sigma_table_data>>=
+# This chunk does some preliminary processing
+@
+
+Table~\ref{tab:CES_sigma_nest_aware_inner} shows elasticity of substitution~($\sigma$)
+for inner nests.
+Note that the row with 
+``PT, Quality-adjusted, With energy, $(ek)l$ nesting, Rejecting the CSP''
+is, in fact, a boundary model that does not include energy.
+As such, the only knowable elasticity is $\sigma_{kl}$.
+
+<<CES_sigma_nest_aware_inner, results="asis">>=
+sigma_inner_data <- filter(table_data, Model=="CES") %>% 
+  select(Country, flavor, Energy, Nest, CSP, sigma_12, sigma_23, sigma_13)
+sigma_inner_data <- plyr::rename(sigma_inner_data, c("flavor" = "Factors of prod.",
+                                                     "sigma_12" = "$\\sigma_{kl}$",
+                                                     "sigma_23" = "$\\sigma_{le}$",
+                                                     "sigma_13" = "$\\sigma_{ek}$"))
+#
+myXTable(sigma_inner_data,
+         caption="Factor substitution~($\\sigma$) for inner nests of CES models.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
+
+Table~\ref{tab:CES_sigma_nest_aware_outer} shows elasticity of substitution~($\sigma$)
+for outer nests.
+Rows with the $kl$ nesting are blank, because they have no outer nest.
+The row with
+``PT, Quality-adjusted, With energy, $(ek)l$ nesting, Rejecting the CSP''
+has no values for $\sigma$, because it has no outer nest, being a boundary model
+that includes only~$k$ and~$l$.
+
+<<CES_sigma_nest_aware_outer, results="asis">>=
+sigma_outer_data <- filter(table_data, Model=="CES") %>% 
+  select(Country, flavor, Energy, Nest, CSP, sigma_12_3, sigma_23_1, sigma_13_2)
+sigma_outer_data <- plyr::rename(sigma_outer_data, c("flavor" = "Factors of prod.", 
+                                                     "sigma_12_3" = "$\\sigma_{(kl)e}$",
+                                                     "sigma_23_1" = "$\\sigma_{(le)k}$",
+                                                     "sigma_13_2" = "$\\sigma_{(ek)l}$"))
+myXTable(sigma_outer_data,
+         caption="Factor substitution~($\\sigma$) for outer nests of CES models.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
 @
@@
 This appendix contains correlograms for all models.
+But, they are not included for now.
 
@@
 
-<<Correlograms_Exp, echo=FALSE, message=FALSE>>=
+<<Correlograms_Exp, echo=FALSE, message=FALSE, include=FALSE>>=
 leaf_apply(l = modelsExp, class = c("lm"), f = function(model, name){
@@
 
-<<Correlograms_CSP, echo=FALSE, message=FALSE>>=
+<<Correlograms_CSP, echo=FALSE, message=FALSE, include=FALSE>>=
 leaf_apply(l = modelsCSP, class = c("lm", "plm"), f = function(model, name){
@@
 
-<<Correlograms_noCSP, echo=FALSE, message=FALSE>>=
+<<Correlograms_noCSP, echo=FALSE, message=FALSE, include=FALSE>>=
 leaf_apply(l = models, class = c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, name){
@@
 
-<<stat_details_table, results="asis">>=
+This information is not included at present.
+
+<<stat_details_table, results="asis", include=FALSE>>=
 texreg(list(models$PT$adjusted$withE$CES$kle, models$UK$adjusted$withE$CES$kle), 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Pre-econometrics graph} 
+\label{sec:pre-econometric_graph}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+<<Pre-econometric_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Pre-econometric data.", warning=FALSE>>=
+pre_econometric_data <- leaf_apply(formulas, class = "formula", f=function(form, name){
+  meta <- strsplit(name, split="[.]") %>% unlist
+  Country <- meta[1]
+  flavor <- meta[2]
+  nums <- summands(form, n=1:3)
+  denom <- summands(form, n=1, right=FALSE)
+  ratios <- lapply(nums, function(num) {paste(num, denom, sep="/")}) %>% unlist
+  coltemplate <- build_formula(NULL, c("Year", ratios))
+  trimmed_historical_data <- historicalData[[Country]][all.vars(coltemplate)]
+  ratio_data <- evalFormula(coltemplate, data=trimmed_historical_data)$right
+  mratio_data <- melt(ratio_data, measure.vars = ratios, value.name = "ratio", variable.name = "variable")
+  mratio_data$Country <- Country
+  mratio_data$flavor <- if (flavor == "adjusted") "Quality-adjusted" else "Unadjusted"
+  return(mratio_data)
+}) %>% do.call(rbind, .)
+
+# Fix levels
+pre_econometric_data$flavor <- relevelFactor(as.factor(as.character(pre_econometric_data$flavor)), 
+                                               c("Unadjusted", "Quality-adjusted"))
+pre_econometric_data$Country <- relevelFactor(as.factor(pre_econometric_data$Country), 
+                                              c("PT", "UK"))
+pre_econometric_data$variable <- relevelFactor(as.factor(pre_econometric_data$variable),
+                                               unique(pre_econometric_data$variable))
+# Now make the plot of pre-econometric data
+historicalPlot(pre_econometric_data, 
+               mapping=aes(x=Year, y=ratio, group=variable, linetype=variable), 
+               facet_formula = Country ~ flavor, 
+               line_types = c(2,4,3, 2,4,3, 2,3,2, 3)) + 
+  xlab("") + 
+  ylab("Indexed (1960=1)")
+@
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Cobb-Douglas Graveyard} 
-\label{sec:cd_results}
+\label{sec:cd_graveyard}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{CES Graveyard} 
+\label{sec:ces_graveyard}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Here is a table of the raw CES coefficient values. 
+This table is not used in the paper, so I'm putting it in 
+<<CES_sigma, results="asis">>=
+data_CES_sigma_raw <- sigma_data %>% select(Country, Model, flavor, Energy, Nest, CSP, sigma_1, sigma)
+data_CES_sigma_raw <- plyr::rename(data_CES_sigma_raw, c("sigma" = "$\\sigma$",
+                                                         "sigma_1" = "$\\sigma_1$"))
+data_CES_sigma_raw <- plyr::rename(data_CES_sigma_raw, c("flavor" = "Factors of prod."))
+data_CES_sigma_raw$CSP <- plyr::mapvalues(data_CES_sigma_raw$CSP, 
+                                         from=c("Adhere to CSP", "Reject CSP"), 
+                                         to=c("Adhere", "Reject"))
+data_CES_sigma_raw$Energy <- plyr::mapvalues(data_CES_sigma_raw$Energy, 
+                                         from=c("Without energy", "With energy"), 
+                                         to=c("Without", "With"))
+
+myXTable(data_CES_sigma_raw,
+         caption="Factor substitution~($\\sigma$) for CES models.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=6)
+@
+
+<<Graphs_CESlek-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with ($le$)$k$ nesting.">>=
+residualPlot(filter(fitted_and_resid_data, model=="CES" & CSP=="Reject CSP" & (nest == "lek" | nest=="kl")),
+             withEnergyShape = 3) # plus
+@
+%
+<<Graphs_CESekl-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(ek$)$l$ nesting.">>=
+residualPlot(filter(fitted_and_resid_data, model=="CES" & CSP=="Reject CSP" & (nest=="ekl" | nest=="kl")),
+             withEnergyShape = 4) # times
+@
+
+%
+<<Graphs_CESlek-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with $kl$ and ($le$)$k$ nesting that reject the CSP. Solid line is historical GDP.">>=
+fittedGraphData_lek <- fitted_and_resid_data %>% filter(model=="CES" & CSP=="Reject CSP" & (nest == "kl" | nest == "lek"))
+fittedGraphNoCSP(fittedGraphData_lek)
+@
+%
+<<Graphs_CESekl-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with $kl$ and ($ek$)$l$ nesting that reject the CSP. Solid line is historical GDP.">>=
+fittedGraphData_ekl <- fitted_and_resid_data %>% filter(model=="CES" & CSP=="Reject CSP" & (nest == "kl" | nest == "ekl"))
+fittedGraphNoCSP(fittedGraphData_ekl)
+@
+
 \end{document}

### 2015-08-19 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Slight cleanup.

@@
 
-<<CES_sigma_table_data>>=
-# This chunk does some preliminary processing
-@
-
 Table~\ref{tab:CES_sigma_nest_aware_inner} shows elasticity of substitution~($\sigma$)
@@
 myXTable(sigma_inner_data,
-         caption="Factor substitution~($\\sigma$) for inner nests of CES models.",
+         caption="Elasticities of substitution~($\\sigma$) for inner nests of CES models.",
          label=paste0("tab:", opts_current$get("label")), 
@@
 myXTable(sigma_outer_data,
-         caption="Factor substitution~($\\sigma$) for outer nests of CES models.",
+         caption="Elasticities of substitution~($\\sigma$) for outer nests of CES models.",
          label=paste0("tab:", opts_current$get("label")), 

### 2015-08-19 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Deleted unused lines.

@@
 
-  # Define the color palette (see http://www.cookbook-r.com/Graphs/Colors_(ggplot2))
-  cbPalette <- c("#E69F00", "#999999", "#F0E442", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")
   # Make the plot

### 2015-08-19 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
now greek letters in alpha graph scale.

@@
     coord_flip() + 
-    scale_fill_brewer(palette="OrRd") +
+    scale_fill_brewer(palette="OrRd", 
+                      labels=c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e]))) +
     xy_theme() +

### 2015-08-19 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Deleted unneeded lines.

@@
                          variable.name = "variable")
-  bar_chart_data$variable <- plyr::mapvalues(bar_chart_data$variable, 
-                                       from=c("alpha_1", "alpha_2", "alpha_3"), 
-                                       to=c("alpha_k", "alpha_l", "alpha_e"))
 

### 2015-08-19 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Better nest labels.

@@
 $\\lambda$ and $sse$ values for the reference (exponential-only) model are shown as gridlines.">>=
+data_sr_sse <- filter(AllCoeffs, model=="CES")
+data_sr_sse$nest <- plyr::mapvalues(data_sr_sse$nest, 
+                                    from=c("kl", "kle", "lek", "ekl"), 
+                                    to=c("kl", "(kl)e", "(le)k", "(ek)l"))
 ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=sse, y=lambda, color=energy, size=CSP, shape=nest)) +
+  geom_point(data=data_sr_sse, mapping=aes(x=sse, y=lambda, color=energy, size=CSP, shape=nest)) +
   geom_vline(aes(xintercept = sse), filter(AllCoeffs, model=="exp") %>% select(Country, sse), colour="gray50", size=0.1) +
@@
                                          from=c("kl", "kle", "lek", "ekl"), 
-                                         to=c("(kl)", "(kl)e", "(le)k", "(ek)l"))
+                                         to=c("kl", "(kl)e", "(le)k", "(ek)l"))
   # Add a label column

### 2015-08-19 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Beginnings of a sigma graph.

@@
 %++++++++++++++++++++++++++++++
+\subsection{$\sigma$ graph} 
+\label{sec:sigma_graph}
+%++++++++++++++++++++++++++++++
+
+<<sigma_graph>>=
+sigma_graph_data <- filter(AllCoeffs, model=="CES") %>% 
+  select(Country, CSP, flavor, energy, nest, sigma_12, sigma_23, sigma_13, sigma_12_3, sigma_23_1, sigma_13_2)
+# Change nest to a nicer-looking nest string
+sigma_graph_data$nest <- plyr::mapvalues(sigma_graph_data$nest, 
+                                         from=c("kl", "kle", "lek", "ekl"), 
+                                         to=c("kl", "(kl)e", "(le)k", "(ek)l"))
+# Now melt the data
+sigma_graph_data <- melt(sigma_graph_data, 
+                         measure.vars = c("sigma_12", "sigma_23", "sigma_13", "sigma_12_3", "sigma_23_1", "sigma_13_2"), 
+                         value.name = "value", 
+                         variable.name = "variable")
+# Create labels
+sigma_graph_data$label <- paste(sigma_graph_data$CSP, sigma_graph_data$flavor, 
+                                sigma_graph_data$energy, sigma_graph_data$nest, 
+                                sigma_graph_data$variable, sep=", ")
+sigma_graph_data <- na.omit(sigma_graph_data)
+
+# Make the plot
+plot <- ggplot(sigma_graph_data, mapping=aes(x=label, y=value, fill=variable, width=0.4)) + 
+  geom_bar(stat="identity") + 
+  xlab("") +
+  # scale_x_discrete(limits=rev(order)) +
+  ylab("") +
+#   scale_y_continuous(breaks=c(0, 0.5, 1)) + 
+  guides(fill=guide_legend(title=NULL)) +
+  scale_fill_brewer(palette="OrRd") +
+  coord_flip() + 
+  xy_theme() +
+  theme(axis.ticks.y = element_blank())
+plot # for debugging
+@
+
+%++++++++++++++++++++++++++++++
 \subsection{Resampling} 
@@
 the Solow residual~($\lambda$), and
-goodness of fit~($sse$)
+goodness of fit~(SSE)
 for all modeling choices.
@@
                                      to=c("Without", "With"))
-table_data$model <- plyr::mapvalues(table_data$model, 
+table_data$Model <- plyr::mapvalues(table_data$Model, 
                                     from=c("exp"), 
@@
 data_CES_SR_gof <- filter(table_data, Model=="CES" | Model=="Ref.") %>% 
-  select(Country, Model, flavor, Energy, Nest, CSP, scale, lambda, sse)
+  select(Country, Model, CSP, flavor, Energy, Nest, scale, lambda, sse)
 data_CES_SR_gof <- plyr::rename(data_CES_SR_gof, c("flavor" = "Factors of prod.",
@@
 data_CES_alpha <- filter(table_data, Model=="CES" | Model=="Ref.") %>% 
-  select(Country, Model, flavor, Energy, Nest, CSP, alpha_1, alpha_2, alpha_3)
+  select(Country, Model, CSP, flavor, Energy, Nest, alpha_1, alpha_2, alpha_3)
 data_CES_alpha <- plyr::rename(data_CES_alpha, c("flavor" = "Factors of prod.",
@@
 sigma_inner_data <- filter(table_data, Model=="CES") %>% 
-  select(Country, flavor, Energy, Nest, CSP, sigma_12, sigma_23, sigma_13)
+  select(Country, CSP, flavor, Energy, Nest, sigma_12, sigma_23, sigma_13)
 sigma_inner_data <- plyr::rename(sigma_inner_data, c("flavor" = "Factors of prod.",
@@
 sigma_outer_data <- filter(table_data, Model=="CES") %>% 
-  select(Country, flavor, Energy, Nest, CSP, sigma_12_3, sigma_23_1, sigma_13_2)
+  select(Country, CSP, flavor, Energy, Nest, sigma_12_3, sigma_23_1, sigma_13_2)
 sigma_outer_data <- plyr::rename(sigma_outer_data, c("flavor" = "Factors of prod.", 

### 2015-08-19 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Edits to sigma graph.

@@
 %++++++++++++++++++++++++++++++
-\subsection{$\sigma$ graph} 
-\label{sec:sigma_graph}
-%++++++++++++++++++++++++++++++
-
-<<sigma_graph>>=
-sigma_graph_data <- filter(AllCoeffs, model=="CES") %>% 
-  select(Country, CSP, flavor, energy, nest, sigma_12, sigma_23, sigma_13, sigma_12_3, sigma_23_1, sigma_13_2)
+\subsection{$\sigma$ graphs} 
+\label{sec:sigma_graphs}
+%++++++++++++++++++++++++++++++
+
+<<sigma_graph_function>>=
+
+sigma_graph_function <- function(data){
+  sigma_graph_data <- select(data, Country, CSP, flavor, energy, nest, 
+                             sigma_12, sigma_23, sigma_13, 
+                             sigma_12_3, sigma_23_1, sigma_13_2)
   # Change nest to a nicer-looking nest string
@@
                            variable.name = "variable")
+  # Create a nicer-looking sigma
+#   sigma_graph_data$variable <- plyr::mapvalues(sigma_graph_data$variable,
+#                                                from=c("sigma_12", 
+#                                                       "sigma_23",
+#                                                       "sigma_13",
+#                                                       "sigma_12_3",
+#                                                       "sigma_23_1",
+#                                                       "sigma_13_2"),
+#                                                to=c("expression(sigma[kl])", 
+#                                                     "expression(sigma[le])",
+#                                                     "expression(sigma[ek])",
+#                                                     'expression(sigma["(kl)"*e])',
+#                                                     'expression(sigma["(le)"*k])',
+#                                                     'expression(sigma["(ek)"*l])'))
   # Create labels
@@
     # scale_x_discrete(limits=rev(order)) +
+    scale_x_discrete(labels=sigma_graph_data$label) +
+    geom_hline(aes(yintercept = 1), colour="gray50", size=0.1) +
     ylab("") +
-#   scale_y_continuous(breaks=c(0, 0.5, 1)) + 
+    # coord_trans(y="sigma") +
+    scale_y_continuous(limits=c(0, 10), breaks=c(0, 1.0, 10)) +
     guides(fill=guide_legend(title=NULL)) +
     scale_fill_brewer(palette="OrRd") +
+#     scale_fill_brewer(palette="OrRd",
+#                       labels=c(expression(sigma[kl]), 
+#                                expression(sigma[le]), 
+#                                expression(sigma[ek]),
+#                                expression(sigma["(kl)e"]),
+#                                expression(sigma["(le)k"]),
+#                                expression(sigma["(ek)l"]))) +
     coord_flip() + 
@@
     theme(axis.ticks.y = element_blank())
-plot # for debugging
+  return(plot)
+}
+@
+
+<<sigma_graph_PT, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for Portugal.">>=
+sigma_graph_function(filter(AllCoeffs, model=="CES", Country=="PT"))
+@
+
+<<sigma_graph_UK, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for the UK.">>=
+sigma_graph_function(filter(AllCoeffs, model=="CES", Country=="UK"))
 @

### 2015-08-19 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Changing number of digits.

@@
          label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
+         digits=4)
 @
@@
          label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
+         digits=2)
 @

### 2015-08-20 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
refactoring some data frame constructions

@@
   return(res)
-}) %>% do.call(plyr::rbind.fill, .)
+}) %>% bind_rows() # do.call(plyr::rbind.fill, .)
 
@@
   return(res)
-}) %>% do.call(plyr::rbind.fill, .)
-AllCoeffs <- plyr::rbind.fill(AllCoeffsExp, AllCoeffsCSP, AllCoeffsNoCSP)
-# See hint at http://stackoverflow.com/questions/22555249/how-to-merge-data-frame-with-same-column-names
-AllCoeffs <- as.data.frame(lapply(AllCoeffs, function(x) unname(unlist(x))))
+}) %>% bind_rows()  # do.call(plyr::rbind.fill, .)
+AllCoeffs <- bind_rows(AllCoeffsExp, AllCoeffsCSP, AllCoeffsNoCSP)
+# # See hint at http://stackoverflow.com/questions/22555249/how-to-merge-data-frame-with-same-column-names
+# AllCoeffs <- as.data.frame(lapply(AllCoeffs, function(x) unname(unlist(x))))
 # Get reference values for lambda and sse.
@@
 # Calculate differences relative to the reference model
-AllCoeffs <- mutate(AllCoeffs, 
+AllCoeffs <- 
+  AllCoeffs %>%
+  mutate(
     Dlambda = abs(lambda) - abs(lambda_ref), 
@@
     percDlambda = Dlambda / abs(lambda_ref) * 100, 
-                    percDsse = Dsse / sse_ref * 100)
-
+    percDsse = Dsse / sse_ref * 100,
     # Relevel factors
-AllCoeffs$Country <- relevelFactor(as.factor(unlist(AllCoeffs$Country)), c("PT", "UK"))
-AllCoeffs$flavor <- relevelFactor(as.factor(unlist(AllCoeffs$flavor)), c("Unadjusted", "Quality-adjusted"))
-AllCoeffs$energy <- relevelFactor(as.factor(unlist(AllCoeffs$energy)), c("Without energy", "With energy"))
-AllCoeffs$model <- relevelFactor(as.factor(unlist(AllCoeffs$model)), c("exp", "CD", "CES"))
-AllCoeffs$nest <- relevelFactor(as.factor(unlist(AllCoeffs$nest)), c("kl", "kle", "lek", "ekl"))
-AllCoeffs$CSP <- relevelFactor(as.factor(unlist(AllCoeffs$CSP)), c("Adhere to CSP", "Reject CSP"))
-# Rearrange for easier viewing
-AllCoeffs <- arrange(AllCoeffs, Country, model, flavor, energy, nest, CSP)
+    Country = relevelFactor(Country, c("PT", "UK")),
+    flavor = relevelFactor(flavor, c("Unadjusted", "Quality-adjusted")),
+    energy = relevelFactor(energy, c("Without energy", "With energy")),
+    model = relevelFactor(model, c("exp", "CD", "CES")),
+    nest = relevelFactor(nest, c("kl", "kle", "lek", "ekl")),
+    CSP = relevelFactor(CSP, c("Adhere to CSP", "Reject CSP"))
+  ) %>% 
+  arrange(Country, model, flavor, energy, nest, CSP)
 @
@@
 
+<<>>=
+triPlot(
+  data=AllCoeffs, 
+  aes(x = alpha_3, y = alpha_1, z = alpha_2, 
+      fill  = nest, 
+      shape = nest,
+      size = CSP, alpha = CSP)) +
+  facet_grid(. ~ Country) +
+  scale_size_manual(values = c(5, 2)) +
+  scale_alpha_manual(values = c(.2, .6)) +
+  scale_shape_manual(values = 21:25)
+@
+
 Table~\ref{tab:CD_coeffs} shows coefficients for all fitted Cobb-Douglas models

### 2015-08-20 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
major refactoring of R code

@@
 library(texreg)
+library(tidyr)
 
@@
 # This function is used in many places below.
+### That's nice.  I assume that's why you wrote a function.  But what does it DO?
+
 myXTable <- function(data, caption, label, digits=2){
@@
 # Create the historicalData data frames
-historicalData <- list()
+### If we need to select variables, we can do that.  Unfortunately, select() and select_() don't do
+### what we would like here (they don't accept a vector of character strings), so we'd have to use
+### something else.  I've kept the fake select_() command here just to record what was done earlier.
+
 commonVars <- c("Year", "Country", "Source")
-historicalData$PT <- filter(IST, Country == "PT") 
-historicalData$PT <- historicalData$PT[ , unique(c(commonVars,
-                                                   all.vars(formulas$PT$unadjusted), 
-                                                   all.vars(formulas$PT$adjusted)))]
-historicalData$UK <- filter(Leeds, Country == "UK")
-historicalData$UK <- historicalData$UK[ , unique(c(commonVars,
-                                                   all.vars(formulas$UK$unadjusted), 
-                                                   all.vars(formulas$UK$adjusted)))]
+historicalData <- list(
+  PT =  IST %>% 
+    filter(Country == "PT"), 
+    #  %>% select_(unique(c(commonVars, all.vars(formulas$PT$unadjusted), all.vars(formulas$PT$adjusted)))),
+  UK = Leeds %>% 
+    filter(Country == "UK") 
+    # %>% select_(unique(c(commonVars, all.vars(formulas$UK$unadjusted), all.vars(formulas$UK$adjusted))))
+)
 @
@@
   modelsExp <- readRDS(fileNameExp)
-} else {
+} else {   ### PLEASE USE COMMENTS TO MARK WHERE LONG CHUNKS END; BETTER: AVOID LONG CHUNKS, WHERE POSSIBLE
+
+  ### This has not been inspected by rjp
+
   # re-run the models and save to disk.
@@
       # Cobb-Douglas
-      cdModCSP <- lm(log(eval(yVar)) - alphaCSP*log(eval(kVar)) - betaCSP*log(eval(lVar)) ~ eval(tVar), data = data)
+      ### breaking a formerly long line
+      cdModCSP <- 
+        lm(log(eval(yVar)) - alphaCSP*log(eval(kVar)) - betaCSP*log(eval(lVar)) ~ eval(tVar), 
+           data = data)
       attr(cdModCSP, "naturalCoeffs") <- data.frame(lambda=coef(cdModCSP)[[2]],
@@
   saveRDS(models, file=fileNameCDCES)
+}  ### END ELSE FROM WAY UP THERE???
+@
+
+<<Models2>>=
+### TIME FOR A NEW R CHUNK -- That helps detect the end of that long code chunk
+
+### This function is the same in each model group below.  DRY (Don't repeat yourself).
+### Using this makes it (a) easier to see what's going on, and (b) easier to make adjustments
+### that affect all of the situations simultaneously.
+
+### General hint:  If you find yourself wanting to copy and paste a chunk of code, there is usually
+### a better way to do what you are about to do.
+
+model2df <- function(mod, id){
+  # Parse the id to find out whether this is quality-adjusted data, etc.
+  ### Don't name non-lists with variables whose names sound like a list.
+  ### I'm guessing you just didn't know what kind of data you were working with here. 
+  ### Either way, it's a bad thing.
+  id_components <- strsplit(id, split = "[.]")[[1]]
+
+  # return this data frame 
+  ### NOTE: ifelse() and [ ] handle NAs the way we want here
+  ### The former use of [[ ]] was unnecessary and would break things in the new code
+  ### I'm guessing you had [[ ]] because you thought you had a list when you did not.
+
+  ### NOTE: data_frame does not auto-convert to factors.  It leaves things as strings.
+  data_frame(
+    Country = id_components[1], 
+    flavor  = ifelse(id_components[2]=="unadjusted", "Unadjusted", "Quality-adjusted"),
+    energy  = ifelse(id_components[3]=="noE", "Without energy", "With energy"),
+    model   = id_components[4], 
+    nest    = id_components[5]) %>%  
+  cbind(naturalCoef(mod)) %>% 
+  cbind(data.frame(sse = sum(resid(mod)^2)))
 }
+
+### AH: So much tidier here :-)
+### NOTE: dplyr::bind_rows() can replace plyr::rbind.fill() in most (all?) situations
+###       plyr should probably not be used for data frame level operations anymore.
+
 # Put all exponential model coefficients into a data frame
-AllCoeffsExp <- leaf_apply(modelsExp, class = c("lm"), f = function(modExp, id){
-  # Parse the id to find details of this model
-  id_list <- strsplit(id, split = "[.]")[[1]]
-  res <- rbind(list(Country = id_list[[1]], 
-                    flavor = NA,
-                    energy = "Without energy", 
-                    model = "exp", 
-                    nest = NA,
-                    CSP = NA))
-  res <- cbind(res, naturalCoef(modExp))
-  # Now caluculate mean squared error (sse) for each model.
-  sse <- sum(resid(modExp)^2)
-  res <- cbind(res, list(sse=sse))
-  return(res)
-}) %>% bind_rows() # do.call(plyr::rbind.fill, .)
+AllCoeffsExp <- 
+  leaf_apply(modelsExp, class = c("lm"), f = model2df) %>%
+  bind_rows() %>%
+  mutate(model = "exp", CSP = NA)
 
 # Put all the cost-share theorem (CSP) model coefficients into a data frame
-AllCoeffsCSP <- leaf_apply(modelsCSP, class = c("lm"), f = function(modCSP, id){
-  # Parse the id to find out whether this is quality-adjusted data, etc.
-  id_list <- strsplit(id, split = "[.]")[[1]]
-  res <- rbind(list(Country = id_list[[1]], 
-                    flavor = if (id_list[[2]]=="unadjusted") "Unadjusted" else "Quality-adjusted",
-                    energy = if (id_list[[3]]=="noE") "Without energy" else "With energy",
-                    model=id_list[[4]], 
-                    nest=if(length(id_list) > 4) id_list[[5]] else NA,
-                    CSP="Adhere to CSP"))
-  res <- cbind(res, naturalCoef(modCSP))
-  # Now calculate the mean squared error (sse) for each model.
-  sse <- sum(resid(modCSP)^2)
-  res <- cbind(res, list(sse=sse))
-  return(res)
-}) %>% bind_rows() # do.call(plyr::rbind.fill, .)
+AllCoeffsCSP <- 
+  leaf_apply(modelsCSP, class = c("lm"), f = model2df) %>% 
+  bind_rows() %>%
+  mutate(CSP = "Adhere to CSP")
 
 # Put all CD and CES model coefficients into a data frame.  
-AllCoeffsNoCSP <- leaf_apply(models, class = c("CDEmodel", "cesModel", "LINEXmodel"), f = function(mod, id){
-  # Parse the id to find out whether this is quality-adjusted data, etc.
-  id_list <- strsplit(id, split = "[.]")[[1]]
-  res <- rbind(list(Country = id_list[[1]], 
-                    flavor = if (id_list[[2]]=="unadjusted") "Unadjusted" else "Quality-adjusted",
-                    energy = if (id_list[[3]]=="noE") "Without energy" else "With energy",
-                    model=id_list[[4]], 
-                    nest=if(length(id_list) > 4) id_list[[5]] else NA,
-                    CSP="Reject CSP"))
-  res <- cbind(res, naturalCoef(mod))
-  # Now calculate the sum of squared error (sse) for each model.
-  sse <- sum(resid(mod)^2)
-  res <- cbind(res, list(sse=sse))
-  return(res)
-}) %>% bind_rows()  # do.call(plyr::rbind.fill, .)
+AllCoeffsNoCSP <- 
+  leaf_apply(models, class = c("CDEmodel", "cesModel", "LINEXmodel"), f = model2df) %>%
+  bind_rows() %>%
+  mutate(CSP="Reject CSP")
+
 AllCoeffs <- bind_rows(AllCoeffsExp, AllCoeffsCSP, AllCoeffsNoCSP)
-# # See hint at http://stackoverflow.com/questions/22555249/how-to-merge-data-frame-with-same-column-names
-# AllCoeffs <- as.data.frame(lapply(AllCoeffs, function(x) unname(unlist(x))))
+
+### It looks like this could also be done the otehr way arround:  We could scoop up all the models
+### into AllCoeffs and then filter to the subsets.
+
 # Get reference values for lambda and sse.
-ref <- filter(AllCoeffs, model=="exp") %>% select(Country, sse, lambda)
-colnames(ref)[colnames(ref)=="sse"] <- "sse_ref"
-colnames(ref)[colnames(ref)=="lambda"] <- "lambda_ref"
-AllCoeffs <- merge(AllCoeffs, ref)
+### This could be done without saving ref if we have no other need for it
+### I've renamed ref to Ref since it is a data frame.
+Ref <- 
+  AllCoeffs %>% 
+  filter(model=="exp") %>% 
+  select(Country, sse, lambda) %>%
+  rename(sse_ref = sse, lambda_ref = lambda)
+AllCoeffs <- merge(AllCoeffs, Ref)
+
 # Calculate differences relative to the reference model
+### If all we need are the differences, we could skip the part where we put the intermediate stuff 
+### into AllCoefs
+
 AllCoeffs <- 
@@
     percDlambda = Dlambda / abs(lambda_ref) * 100, 
-    percDsse = Dsse / sse_ref * 100,
-    # Relevel factors
-    Country = relevelFactor(Country, c("PT", "UK")),
-    flavor = relevelFactor(flavor, c("Unadjusted", "Quality-adjusted")),
-    energy = relevelFactor(energy, c("Without energy", "With energy")),
-    model = relevelFactor(model, c("exp", "CD", "CES")),
-    nest = relevelFactor(nest, c("kl", "kle", "lek", "ekl")),
-    CSP = relevelFactor(CSP, c("Adhere to CSP", "Reject CSP"))
+    percDsse = Dsse / sse_ref * 100
+  )
+
+# Relevel factors and re-order data
+### NOTE:  Need to convert from strings to factors to use relevelFactor()
+###        We could modify relevelFacotr() to accept character inputs
+AllCoeffs <- 
+  AllCoeffs %>%
+  mutate(
+    Country = relevelFactor(factor(Country), c("PT", "UK")),
+    flavor = relevelFactor(factor(flavor), c("Unadjusted", "Quality-adjusted")),
+    energy = relevelFactor(factor(energy), c("Without energy", "With energy")),
+    model = relevelFactor(factor(model), c("exp", "CD", "CES")),
+    nest = relevelFactor(factor(nest), c("kl", "kle", "lek", "ekl")),
+    CSP = relevelFactor(factor(CSP), c("Adhere to CSP", "Reject CSP"))
   ) %>% 
@@
 <<Fitted_and_Residuals>>=
-temp_data_exp <- leaf_apply(modelsExp, class=c("lm"), f = function(model, id){
-  df <- data.frame(select(model$data, Year, Country))
-  df$fittedExp <- exp(fitted(model)) # exp accounts for the fact that the model was fitted in log space.
-  df$ResidualsExp <- resid(model)
-  return(df)
-}) %>% do.call(rbind, .)
-
-temp_data_CSP <- leaf_apply(modelsCSP, class=c("plm", "lm"), f = function(model, id){
-  df <- data.frame(select(model$data, Year, Country, iGDP))
-  df$fitted <- exp(fitted(model)) # fitted is in log space. Return to regular space.
-  df$Residuals <- resid(model) # residuals are in log space, and that is what we want.
-  # Now add meta information
-  id_list <- strsplit(id, split = "[.]")[[1]]
-  df$flavor <- if (id_list[[2]] ==  "unadjusted") "Unadjusted" else "Quality-adjusted"
-  df$energy <- if (id_list[[3]] == "noE") "Without energy" else "With energy"
-  df$model <- id_list[[4]]
-  df$nest <- if (length(id_list) > 4) id_list[[5]] else NA
-  return(df)
-}) %>% do.call(rbind, .)
-temp_data_CSP$CSP <- "Adhere to CSP"
-
-temp_data_noCSP <- leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, id){
+temp_data_exp <- 
+  leaf_apply(
+    modelsExp, class=c("lm"), 
+    f = function(model, id){
+      ### Why wrap in data.frame() something that already is a tbl_df?  If this is necessary, say why.
+      #  df <- data.frame(select(model$data, Year, Country))
+      ### Also: let's use a consistent style for the dplyr commands, prefering to use %>% in most cases.
+      ### Also: The following use of white space makes it clearer what is going on (and how many steps 
+      ###       are involved.  I'm going to change A LOT of code to this format.
+      ### In this format, there is no name to create a temporary variable (or to use return())
+
+      model$dat %>% 
+        select(Year, Country) %>%
+        mutate(
+          Country = as.character(Country),  # to avoid warning about unmatched levels of factors
+          fittedExp = exp(fitted(model)), # exp accounts for the fact that the model was fitted in log space.
+          ResidualsExp = resid(model)     ### Why is this capitalized?
+        )
+    }
+  ) %>% 
+  bind_rows()
+
+### If the function is this long, it should be separated out and named rather than embedded in another
+### function call.  
+### But this looks like model2df from above.  Let's use that instead.
+
+### Probably just junk now.
+# function_that_was_here_before <- function(model, id){
+#   df <- data.frame(select(model$data, Year, Country, iGDP))
+#   df$fitted <- exp(fitted(model)) # fitted is in log space. Return to regular space.
+#   df$Residuals <- resid(model) # residuals are in log space, and that is what we want.
+#   # Now add meta information
+#   id_list <- strsplit(id, split = "[.]")[[1]]
+#   df$flavor <- if (id_list[[2]] ==  "unadjusted") "Unadjusted" else "Quality-adjusted"
+#   df$energy <- if (id_list[[3]] == "noE") "Without energy" else "With energy"
+#   df$model <- id_list[[4]]
+#   df$nest <- if (length(id_list) > 4) id_list[[5]] else NA
+#   return(df)
+# }
+
+### One line for each operation:  first leaf_apply, then rbind, then mutate -- Clarity by Code Convention
+temp_data_CSP <- 
+  leaf_apply(modelsCSP, class=c("plm", "lm"), model2df) %>% 
+  bind_rows() %>%
+  mutate(CSP = "Adhere to CSP")
+
+### This looks like a candidate for clean up a la model2df
+
+function_that_was_here_before <- function(model, id){
   df <- data.frame(select(model$data, Year)) 
@@
   return(df)  
-}) %>% do.call(rbind, .)
-temp_data_noCSP$CSP <- "Reject CSP"
-
-temp_data_noExp <- plyr::rbind.fill( temp_data_CSP, temp_data_noCSP )
+}
+
+temp_data_noCSP <- 
+  leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), function_that_was_here_before) %>% 
+  bind_rows() %>%
+  mutate(CSP = "Reject CSP")
+
+temp_data_noExp <- 
+  bind_rows( temp_data_CSP, temp_data_noCSP )
 
@@
 # it applies to all situations.
-# temp_data <- merge(temp_data_noExp, temp_data_exp)
-fitted_and_resid_data <- merge(temp_data_noExp, temp_data_exp)
+fitted_and_resid_data <- 
+  merge(temp_data_noExp, temp_data_exp) %>% 
+  mutate( Dr = abs(Residuals) - abs(ResidualsExp) )  
+### Caps in bad places?
 
@@
 # and the residual value in the same year for the reference model
-fitted_and_resid_data[["Dr"]] <- abs(fitted_and_resid_data[["Residuals"]]) - abs(fitted_and_resid_data[["ResidualsExp"]])
+### BREAK LONG LINES IN REASONABLE PLACES
+### BUT better to use mutate here.  See above.
+# fitted_and_resid_data[["Dr"]] <- 
+#   abs(fitted_and_resid_data[["Residuals"]]) - abs(fitted_and_resid_data[["ResidualsExp"]])
 
 # Relevel factors before plotting
-fitted_and_resid_data$Country <- relevelFactor(as.factor(fitted_and_resid_data$Country), c("PT", "UK"))
-fitted_and_resid_data$flavor <- relevelFactor(as.factor(fitted_and_resid_data$flavor), c("Unadjusted", "Quality-adjusted"))
-fitted_and_resid_data$energy <- relevelFactor(as.factor(fitted_and_resid_data$energy), c("Without energy", "With energy"))
-fitted_and_resid_data$nest <- relevelFactor(as.factor(fitted_and_resid_data$nest), c("kl", "kle", "lek", "ekl"))
-
-# Make data viewing easier
-fitted_and_resid_data <- arrange(fitted_and_resid_data, Country, CSP, model, flavor, energy, nest)
+### Use mutate for this stuff!
+### Align = to make similarities between successive lines stand out.
+
+fitted_and_resid_data <-
+  fitted_and_resid_data %>% 
+  mutate(
+    Country = relevelFactor(factor(Country), c("PT", "UK")),
+    flavor  = relevelFactor(factor(flavor), c("Unadjusted", "Quality-adjusted")),
+    energy  = relevelFactor(factor(energy), c("Without energy", "With energy")),
+    nest    = relevelFactor(factor(nest), c("kl", "kle", "lek", "ekl"))
+  ) %>%
+  arrange(Country, CSP, model, flavor, energy, nest)
 @
@@
 # Melt the data into a form that is useful in a couple places
-histDataForGraph <- leaf_apply(formulas, class = "formula", f=function(form, name){
-  meta <- strsplit(name, split="[.]") %>% unlist
+### Don't write comments like that.  Say what you are doing to reshape and why.  
+### I figured you were going to use it and don't need a comment for that.
+### But it not at all easy to glance at this and see what the point is.
+
+### Also, I find tidyr::gather() and tidyr::spread() easier to work with than melt() and cast()
+
+histDataForGraph <- 
+  leaf_apply(formulas, class = "formula", f=function(form, name){
+    meta <- strsplit(name, split="[.]")[[1]] # %>% unlist  ### Why use unlist() here?
     Country <- meta[1]
@@
     measure.vars <- c(summands(form, right=FALSE), summands(form, 1:3))
+    ### Is there any reason to select away some of the columns?
     trimmed_historical_data <- historicalData[[Country]][c("Year", measure.vars)]
-  mtrimmed_historical_data <- melt(trimmed_historical_data, measure.vars = measure.vars, 
-                                   value.name = "value", variable.name = "variable")
-  mtrimmed_historical_data$Country <- Country
-  mtrimmed_historical_data$flavor <- if (flavor == "adjusted") "Quality-adjusted" else "Unadjusted"
-  return(mtrimmed_historical_data)
-}) %>% do.call(rbind, .)
-
-# Change variable names to make a nicer-looking graph
-histDataForGraph$variable <- plyr::mapvalues(histDataForGraph$variable,
+
+    # return this.  ### No need to name and store it.
+    melt(trimmed_historical_data, measure.vars = measure.vars, 
+         value.name = "value", variable.name = "variable") %>%
+    mutate(
+        Country = Country,
+        flavor =  ifelse (flavor == "adjusted", "Quality-adjusted", "Unadjusted")
+      )
+  }
+  ) %>% bind_rows()
+
+# Change variable names to make a nicer-looking graph and relevel factors before plotting
+### Note: You an also change the order of things in the legend without changing the order in the data.
+
+histDataForGraph <- 
+  histDataForGraph %>% 
+  mutate( variable = plyr::mapvalues(
+    variable,
     from=c("iGDP", 
@@
          "l", "l",
-                                                  "e", "e", "e", "e"))
-
-# Relevel factors before plotting
-histDataForGraph$Country <- relevelFactor(as.factor(histDataForGraph$Country), c("PT", "UK"))
-histDataForGraph$flavor <- relevelFactor(as.factor(histDataForGraph$flavor), c("Unadjusted", "Quality-adjusted"))
-histDataForGraph$variable <- relevelFactor(as.factor(histDataForGraph$variable), unique(histDataForGraph$variable))
-
+         "e", "e", "e", "e")),
+    Country = relevelFactor(factor(Country), c("PT", "UK")),
+    flavor = relevelFactor(factor(flavor), c("Unadjusted", "Quality-adjusted")),
+    variable = relevelFactor(factor(variable), unique(variable)) 
+  )
+
+### I think this exhibits poor use of white space.  See alternative below. 
+if (FALSE)
 historicalPlot(histDataForGraph, 
@@
   ylab("Indexed (1960=1)")
+
+### Here each summand has the same indentation so you can see which things are being added together.
+historicalPlot(
+  histDataForGraph, 
+  mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
+  facet_formula = Country ~ flavor, 
+  line_types = c(1,2,4,3,2,4,3,2,3,2,3)) + 
+scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12)) +
+coord_cartesian(ylim=c(0.5, 13)) +
+xlab("") + 
+ylab("Indexed (1960=1)")
 @
@@
 fittedGraphNoCSP <- function(data){
-  fittedGraphData <- select(data, Year, Country, iGDP, fitted, fittedExp, flavor, energy, CSP, nest)
-  fittedGraphData <- melt(fittedGraphData, 
-                     measure.vars = c("iGDP", "fitted", "fittedExp"), 
-                     value.name = "value", 
-                     variable.name = "variable")
-  fittedGraphData$label <- with(fittedGraphData, paste(variable, energy))
+  fittedGraphData <- 
+    data %>% 
+    select(Year, Country, iGDP, fitted, fittedExp, flavor, energy, CSP, nest) %>%
+    melt(measure.vars = c("iGDP", "fitted", "fittedExp"), 
+         value.name = "value", variable.name = "variable") %>%
+    mutate(label = paste(variable, energy)) %>%
   # Now collapse some of the information. Don't need multiple versions of the exponential model, e.g.
-  fittedGraphData <- filter(fittedGraphData, label=="iGDP With energy" | label=="fittedExp With energy" |
-                       label == "fitted With energy" | label == "fitted Without energy")
-  fittedGraphData$label <- plyr::mapvalues(fittedGraphData$label, 
-                                      from = c("iGDP With energy", 
-                                               "fittedExp With energy",
-                                               "fitted With energy",
-                                               "fitted Without energy"), 
-                                      to = c("GDP", 
-                                             "Reference model",
-                                             "With energy",
-                                             "Without energy"))
-  # Relevel factors
-  fittedGraphData$label <- relevelFactor(as.factor(fittedGraphData$label), 
+    filter(label %in% c("iGDP With energy", "fittedExp With energy", 
+                        "fitted With energy", "fitted Without energy")
+    ) %>% 
+    mutate(
+      label = plyr::mapvalues(label, 
+        from = c("iGDP With energy",  "fittedExp With energy",
+                 "fitted With energy", "fitted Without energy"), 
+        to = c("GDP",  "Reference model",
+               "With energy", "Without energy")),
+      label = relevelFactor(factor(label), 
                             c("GDP", "Reference model", "Without energy", "With energy"))
+    )
+
   # Make (and return) the graph
@@
 <<Graphs_CESkle-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with $kl$ and ($kl$)$e$ nesting that reject the CSP. Solid line is historical GDP.">>=
-fittedGraphData_kle <- fitted_and_resid_data %>% filter(model=="CES" & CSP=="Reject CSP" & (nest == "kl" | nest == "kle"))
+fittedGraphData_kle <- 
+  fitted_and_resid_data %>% 
+  filter(model=="CES" & CSP=="Reject CSP" & (nest == "kl" | nest == "kle"))
+
 fittedGraphNoCSP(fittedGraphData_kle)
+
+### Note: I like a blank line have a chain of %>% operators to make it easy to spot where the chain ends.
 @
@@
 
+### Put in a separate R chunk and use eval=FALSE, include=FALSE 
 # This version also plots reference model residuals.
@@
 <<Graphs_CESkle-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(kl$)$e$ nesting.">>=
-residualPlot(filter(fitted_and_resid_data, model=="CES" & CSP=="Reject CSP" & (nest=="kle" | nest=="kl")), 
+residualPlot(
+  fitted_and_resid_data %>% 
+    filter(model=="CES" & CSP=="Reject CSP" & (nest=="kle" | nest=="kl")), 
   withEnergyShape = 0) # square
@@
 $\\lambda$ and $sse$ values for the reference (exponential-only) model are shown as gridlines.">>=
-data_sr_sse <- filter(AllCoeffs, model=="CES")
-data_sr_sse$nest <- plyr::mapvalues(data_sr_sse$nest, 
+data_sr_sse <- 
+  AllCoeffs %>% 
+  filter(model=="CES") %>% 
+  mutate(nest = 
+           plyr::mapvalues(
+             nest, 
              from=c("kl", "kle", "lek", "ekl"), 
-                                    to=c("kl", "(kl)e", "(le)k", "(ek)l"))
+             to=c("kl", "(kl)e", "(le)k", "(ek)l")
+             )
+  )
+
 ggplot() +
   geom_point(data=data_sr_sse, mapping=aes(x=sse, y=lambda, color=energy, size=CSP, shape=nest)) +
-  geom_vline(aes(xintercept = sse), filter(AllCoeffs, model=="exp") %>% select(Country, sse), colour="gray50", size=0.1) +
-  geom_hline(aes(yintercept = lambda), filter(AllCoeffs, model=="exp") %>% select(Country, lambda), colour="gray50", size=0.1) +
+  geom_vline(aes(xintercept = sse), 
+             AllCoeffs %>% filter(model=="exp") %>% select(Country, sse), 
+             colour="gray50", size=0.1) +
+  geom_hline(aes(yintercept = lambda), 
+             AllCoeffs %>% filter(model=="exp") %>% select(Country, lambda), 
+             colour="gray50", size=0.1) +
   scale_size_manual(values=c(2,4)) +
@@
 fsbg <- function(coun, mod){
-  bar_chart_data <- filter(AllCoeffs, Country==coun & model==mod) %>% 
-    select(Country, model, flavor, energy, nest, CSP, alpha_1, alpha_2, alpha_3)
-  # Change nest to a nicer-looking nest string
-  bar_chart_data$nest <- plyr::mapvalues(bar_chart_data$nest, 
+  bar_chart_data <- 
+    AllCoeffs %>% 
+    filter(Country==coun & model==mod) %>% 
+    select(Country, model, flavor, energy, nest, CSP, alpha_1, alpha_2, alpha_3) %>%
+    mutate(nest =   # Change nest to a nicer-looking nest string
+             plyr::mapvalues(nest, 
                              from=c("kl", "kle", "lek", "ekl"), 
-                                         to=c("kl", "(kl)e", "(le)k", "(ek)l"))
-  # Add a label column
-  bar_chart_data$label <- paste(bar_chart_data$CSP, bar_chart_data$flavor, 
-                                bar_chart_data$energy, bar_chart_data$nest, sep=", ")
-  # Add row numbers to the label column
-  bar_chart_data$label <- paste(paste0(1:length(bar_chart_data$label), ". "), bar_chart_data$label)
+                             to=c("kl", "(kl)e", "(le)k", "(ek)l")),
+           label = # Add a label column
+              paste(CSP, flavor, energy, nest, sep=", "),
+           label =  # Add row numbers to the label column
+              paste(paste0(1:length(label), ". "), label)
+    )
   # Capture the order that we want for the models on the vertical axis.
@@
   # Now melt the data
-  bar_chart_data <- melt(bar_chart_data, 
-                         measure.vars = c("alpha_1", "alpha_2", "alpha_3"), 
-                         value.name = "value", 
-                         variable.name = "variable")
+  ### tidyr::spread and tidyr::gather are preferred in most cases now
+#   bar_chart_data <- melt(bar_chart_data, 
+#                          measure.vars = c("alpha_1", "alpha_2", "alpha_3"), 
+#                          value.name = "value", 
+#                          variable.name = "variable")
+  bar_chart_data <-
+    bar_chart_data %>% gather( key=variable, value=value, alpha_1 : alpha_3 )
 
@@
 <<sigma_graph_function>>=
+### A function named blah_function should return a function, not a plot.  Don't use function in the name 
+### of a function unless it tells you something about the function.  All functions are functions, we don't
+### need to name them like that.
 
 sigma_graph_function <- function(data){
-  sigma_graph_data <- select(data, Country, CSP, flavor, energy, nest, 
+  sigma_graph_data <- 
+    data %>% 
+    select(Country, CSP, flavor, energy, nest, 
            sigma_12, sigma_23, sigma_13, 
-                             sigma_12_3, sigma_23_1, sigma_13_2)
-  # Change nest to a nicer-looking nest string
-  sigma_graph_data$nest <- plyr::mapvalues(sigma_graph_data$nest, 
+           sigma_12_3, sigma_23_1, sigma_13_2) %>%
+    mutate(nest = plyr::mapvalues( # Change nest to a nicer-looking nest string
+      nest, 
       from=c("kl", "kle", "lek", "ekl"), 
       to=c("kl", "(kl)e", "(le)k", "(ek)l"))
-  # Now melt the data
-  sigma_graph_data <- melt(sigma_graph_data, 
-                           measure.vars = c("sigma_12", "sigma_23", "sigma_13", "sigma_12_3", "sigma_23_1", "sigma_13_2"), 
-                           value.name = "value", 
-                           variable.name = "variable")
-  # Create a nicer-looking sigma
-#   sigma_graph_data$variable <- plyr::mapvalues(sigma_graph_data$variable,
-#                                                from=c("sigma_12", 
-#                                                       "sigma_23",
-#                                                       "sigma_13",
-#                                                       "sigma_12_3",
-#                                                       "sigma_23_1",
-#                                                       "sigma_13_2"),
-#                                                to=c("expression(sigma[kl])", 
-#                                                     "expression(sigma[le])",
-#                                                     "expression(sigma[ek])",
-#                                                     'expression(sigma["(kl)"*e])',
-#                                                     'expression(sigma["(le)"*k])',
-#                                                     'expression(sigma["(ek)"*l])'))
-  # Create labels
-  sigma_graph_data$label <- paste(sigma_graph_data$CSP, sigma_graph_data$flavor, 
-                                  sigma_graph_data$energy, sigma_graph_data$nest, 
-                                  sigma_graph_data$variable, sep=", ")
-  sigma_graph_data <- na.omit(sigma_graph_data)
+    ) %>%
+    gather(variable, value, sigma_12, sigma_23, sigma_13, sigma_12_3, sigma_23_1, sigma_13_2) %>%
+    mutate(label = paste(CSP, flavor, energy, nest, variable, sep=", ")) %>%
+    na.omit()
+
+  return(sigma_graph_data)
 
@@
 <<sigma_graph_PT, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for Portugal.">>=
-sigma_graph_function(filter(AllCoeffs, model=="CES", Country=="PT"))
+sigma_graph_function(AllCoeffs %>% filter(model=="CES", Country=="PT"))
 @
@@
 <<sigma_graph_UK, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for the UK.">>=
-sigma_graph_function(filter(AllCoeffs, model=="CES", Country=="UK"))
+sigma_graph_function(AllCoeffs %>% filter(model=="CES", Country=="UK"))
 @
@@
 <<Table_data>>=
-table_data <- AllCoeffs 
-table_data <- plyr::rename(table_data, c("model" = "Model", 
-                                         "energy" = "Energy", 
-                                         "nest" = "Nest"))
-table_data$Nest <- plyr::mapvalues(table_data$Nest,
+table_data <- 
+  AllCoeffs %>%
+  plyr::rename(c(model = "Model", energy = "Energy", nest = "Nest")) %>%
+  mutate(Nest = 
+           plyr::mapvalues(
+             Nest,
              from=c("kl", "kle", "lek", "ekl"),
-                                   to=c("$kl$", "$(kl)e$", "$(le)k$", "$(ek)l$"))
-table_data$CSP <- plyr::mapvalues(table_data$CSP, 
+             to=c("$kl$", "$(kl)e$", "$(le)k$", "$(ek)l$")),
+         CSP =  
+           plyr::mapvalues(
+             CSP, 
              from=c("Adhere to CSP", "Reject CSP"), 
-                                  to=c("Adhere", "Reject"))
-table_data$Energy <- plyr::mapvalues(table_data$Energy, 
+             to=c("Adhere", "Reject")),
+         Energy =
+           plyr::mapvalues(
+             Energy, 
              from=c("Without energy", "With energy"), 
-                                     to=c("Without", "With"))
-table_data$Model <- plyr::mapvalues(table_data$Model, 
+             to=c("Without", "With")),
+         Model = 
+           plyr::mapvalues(
+             Model, 
              from=c("exp"), 
              to=c("Ref."))
+  )
 @
@@
 <<CES_sr_gof, results="asis">>=
-data_CES_SR_gof <- filter(table_data, Model=="CES" | Model=="Ref.") %>% 
-  select(Country, Model, CSP, flavor, Energy, Nest, scale, lambda, sse)
-data_CES_SR_gof <- plyr::rename(data_CES_SR_gof, c("flavor" = "Factors of prod.",
+data_CES_SR_gof <- 
+  table_data %>% 
+  filter(Model=="CES" | Model=="Ref.") %>% 
+  select(Country, Model, CSP, flavor, Energy, Nest, scale, lambda, sse) %>%
+  plyr::rename(c("flavor" = "Factors of prod.",
                   "scale" = "$\\theta$",
                   "lambda" = "$\\lambda$"))
+
 myXTable(data_CES_SR_gof,
@@
 <<CES_alpha, results="asis">>=
-data_CES_alpha <- filter(table_data, Model=="CES" | Model=="Ref.") %>% 
-  select(Country, Model, CSP, flavor, Energy, Nest, alpha_1, alpha_2, alpha_3)
-data_CES_alpha <- plyr::rename(data_CES_alpha, c("flavor" = "Factors of prod.",
+data_CES_alpha <- 
+  table_data %>% 
+  filter(Model=="CES" | Model=="Ref.") %>% 
+  select(Country, Model, CSP, flavor, Energy, Nest, alpha_1, alpha_2, alpha_3) %>%
+  plyr::rename(c("flavor" = "Factors of prod.",
                  "alpha_1" = "$\\alpha_k$",
@@
 <<CES_sigma_nest_aware_inner, results="asis">>=
-sigma_inner_data <- filter(table_data, Model=="CES") %>% 
-  select(Country, CSP, flavor, Energy, Nest, sigma_12, sigma_23, sigma_13)
-sigma_inner_data <- plyr::rename(sigma_inner_data, c("flavor" = "Factors of prod.",
+sigma_inner_data <- 
+  table_data %>% 
+  filter(Model=="CES") %>% 
+  select(Country, CSP, flavor, Energy, Nest, sigma_12, sigma_23, sigma_13) %>%
+  plyr::rename( c("flavor" = "Factors of prod.",
                   "sigma_12" = "$\\sigma_{kl}$",
@@
 <<CES_sigma_nest_aware_outer, results="asis">>=
-sigma_outer_data <- filter(table_data, Model=="CES") %>% 
-  select(Country, CSP, flavor, Energy, Nest, sigma_12_3, sigma_23_1, sigma_13_2)
-sigma_outer_data <- plyr::rename(sigma_outer_data, c("flavor" = "Factors of prod.", 
+sigma_outer_data <- 
+  table_data %>% 
+  filter(Model=="CES") %>% 
+  select(Country, CSP, flavor, Energy, Nest, sigma_12_3, sigma_23_1, sigma_13_2) %>%
+  plyr::rename(c("flavor" = "Factors of prod.", 
                  "sigma_12_3" = "$\\sigma_{(kl)e}$",
@@
 <<Pre-econometric_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Pre-econometric data.", warning=FALSE>>=
-pre_econometric_data <- leaf_apply(formulas, class = "formula", f=function(form, name){
+pre_econometric_data <- 
+  leaf_apply(
+    formulas, class = "formula", 
+    f=function(form, name){
       meta <- strsplit(name, split="[.]") %>% unlist
@@
       return(mratio_data)
-}) %>% do.call(rbind, .)
+    }
+  ) %>%  
+  bind_rows()
 
@@
 <<Graphs_CD-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Cobb-Douglas models that reject the cost-share theorem. Solid line is historical GDP.">>=
-fittedGraphNoCSP(filter(fitted_and_resid_data, model=="CD" & CSP=="Reject CSP"))
+fittedGraphNoCSP(fitted_and_resid_data %>% filter(model=="CD" & CSP=="Reject CSP"))
 @
@@
 <<Graphs_CD-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for Cobb-Douglas models.">>=
-residualPlot(filter(fitted_and_resid_data, model=="CD" & CSP=="Reject CSP"))
+residualPlot(fitted_and_resid_data %>% filter(model=="CD" & CSP=="Reject CSP"))
 @
@@
 <<Effect_of_CSP_CD, results="asis">>=
-data_CSP_CD <- filter(AllCoeffs, (model=="CD" & flavor=="Unadjusted" & energy=="Without energy") | model=="exp") %>% 
+data_CSP_CD <- 
+  AllCoeffs %>%
+  filter((model=="CD" & flavor=="Unadjusted" & energy=="Without energy") | model=="exp") %>% 
   select(Country, model, CSP, scale, lambda, alpha_1, alpha_2, sse)
+
 data_CSP_CD <- plyr::rename(data_CSP_CD, c("alpha_1" = "$\\alpha_1$", "alpha_2" = "$\\alpha_2$"))
+
 myXTable(data_CSP_CD,
@@
 <<CD_coeffs, results="asis">>=
-data_CD_exp <- filter(AllCoeffs, model=="CD" | model=="exp") %>% 
+data_CD_exp <- 
+  AllCoeffs %>% 
+  filter(model=="CD" | model=="exp") %>% 
   select(Country, model, flavor, energy, CSP, scale, lambda, alpha_1, alpha_2, alpha_3, sse)
+
 data_CD_exp <- plyr::rename(data_CD_exp, c("alpha_1" = "$\\alpha_1$", 
@@
 <<DSRsse_CD, results="asis">>=
-myXTable(filter(AllCoeffs, model=="CD") %>% select(Country, model, flavor, energy, CSP, Dlambda, Dsse),
+myXTable(AllCoeffs %>% 
+           filter(model=="CD") %>% 
+           select(Country, model, flavor, energy, CSP, Dlambda, Dsse),
          caption="$\\Delta \\lambda$ and $\\Delta sse$ for Cobb-Douglas models.",
@@
 ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CD"), mapping=aes(x=Dsse, y=Dlambda, color=energy, size=CSP)) +
+  geom_point(data=AllCoeffs %>% filter(model=="CD"), 
+             mapping=aes(x=Dsse, y=Dlambda, color=energy, size=CSP)) +
   facet_grid(Country ~ flavor) +
@@
 ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CD"), mapping=aes(x=percDsse, y=percDlambda, color=energy, size=CSP)) +
+  geom_point(data=AllCoeffs %>% filter(model=="CD"), 
+             mapping=aes(x=percDsse, y=percDlambda, color=energy, size=CSP)) +
   facet_grid(Country ~ flavor) +
@@
 ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=Dsse, y=Dlambda, color=energy, size=CSP, shape=nest)) +
+  geom_point(data=AllCoeffs %>% filter(model=="CES"), 
+             mapping=aes(x=Dsse, y=Dlambda, color=energy, size=CSP, shape=nest)) +
   scale_size_manual(values=c(2,3.5)) +
@@
 ggplot() +
-  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=percDsse, y=percDlambda, color=energy, size=CSP, shape=nest)) +
+  geom_point(data=AllCoeffs %>% filter(model=="CES"), 
+             mapping=aes(x=percDsse, y=percDlambda, color=energy, size=CSP, shape=nest)) +
   scale_size_manual(values=c(2,3.5)) +
@@
 <<CES_sigma, results="asis">>=
+### Is sigma_data defined anywhere?
+
 data_CES_sigma_raw <- sigma_data %>% select(Country, Model, flavor, Energy, Nest, CSP, sigma_1, sigma)
@@
 <<Graphs_CESlek-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with ($le$)$k$ nesting.">>=
-residualPlot(filter(fitted_and_resid_data, model=="CES" & CSP=="Reject CSP" & (nest == "lek" | nest=="kl")),
+residualPlot(fitted_and_resid_data %>% 
+               filter(model=="CES" & CSP=="Reject CSP" & (nest == "lek" | nest=="kl")),
              withEnergyShape = 3) # plus
@@
 <<Graphs_CESekl-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(ek$)$l$ nesting.">>=
-residualPlot(filter(fitted_and_resid_data, model=="CES" & CSP=="Reject CSP" & (nest=="ekl" | nest=="kl")),
+residualPlot(fitted_and_resid_data %>% 
+               filter(model=="CES" & CSP=="Reject CSP" & (nest=="ekl" | nest=="kl")),
              withEnergyShape = 4) # times
@@
 <<Graphs_CESekl-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with $kl$ and ($ek$)$l$ nesting that reject the CSP. Solid line is historical GDP.">>=
-fittedGraphData_ekl <- fitted_and_resid_data %>% filter(model=="CES" & CSP=="Reject CSP" & (nest == "kl" | nest == "ekl"))
+fittedGraphData_ekl <- 
+  fitted_and_resid_data %>% 
+  filter(model=="CES" & CSP=="Reject CSP" & (nest == "kl" | nest == "ekl"))
 fittedGraphNoCSP(fittedGraphData_ekl)

### 2015-08-20 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
A few more ### comments

@@
 <<Fitted_and_Residuals>>=
+### Why are we going back and forth between CamelCase and interspersed_underscores?
+### If there isn't a reason, probably we should stick with one naming convention.
+
 temp_data_exp <- 
@@
 <<Fitted_and_Residual_Graph_Functions>>=
+
+### Can fittedGraphNoCSP and fittedGraphCSP be combined into one function with an argument?
+### Or can the data filtering happen outside and everything else be the same?
+### Did you copy and paste to make one from the other?  That should be a sign...
 fittedGraphNoCSP <- function(data){

### 2015-08-20 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
update to triPlot

@@
 
-<<>>=
+<<fig.height=3>>=
 triPlot(
-  data=AllCoeffs, 
+  data=
+    AllCoeffs %>% 
+    mutate( Model = interaction(nest, CSP, sep = " -- ", drop=TRUE),
+            Inputs = flavor), 
   aes(x = alpha_3, y = alpha_1, z = alpha_2, 
-      fill  = nest, 
-      shape = nest,
-      size = CSP, alpha = CSP)) +
+      fill  = Model, 
+      shape = Model,
+      size = Model, 
+      color = Inputs),
+  alpha = 0.6) +
   facet_grid(. ~ Country) +
-  scale_size_manual(values = c(5, 2)) +
-  scale_alpha_manual(values = c(.2, .6)) +
+  scale_colour_manual(values = c("gray70", "black")) +
+  scale_size_manual(values = c(5, 3,3,3,3)) +
+  # scale_alpha_manual(values = c(.2, .6,.6,.6,.6)) +
   scale_shape_manual(values = 21:25)  

### 2015-08-20 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
permuting order of vertices in triPlot()

@@
 standardTriPlot(data=resampleCoeffs, facet_formula=~Country, alpha=0.1,
-                labels=c("alpha[e]", "alpha[k]", "alpha[l]"), size=2.0)
+                labels=c("alpha[k]", "alpha[l]", "alpha[e]"), size=2.0)
 @
@@
             Inputs = flavor), 
-  aes(x = alpha_3, y = alpha_1, z = alpha_2, 
+  labels = c("alpha[k]", "alpha[l]", "alpha[e]"),
+  aes(x = alpha_1, y = alpha_2, z = alpha_3, 
       fill  = Model, 

### 2015-08-20 Packages/EconModels/R/Graphics.R

@@ -8,12 +8,12 @@
 
 #' @export
 tri2x <- function(x,y,z) {
-  return( x * 0.5 + y * 0 + z * 1 )
+    y * 1 + z * 0.5   # + x * 0 
 }
 
 #' @export
 tri2y <- function(x,y,z) {
-  return( x * 1 + y * 0 + z * 0 )
+  z * 1 # + x * 0 + y * 0 
 }
 
 #' @export
@@ -72,7 +72,7 @@ xy_theme <- function(base_size=12, base_family = "", base_theme=theme_bw, label_
 }
 
 #' @export
-triPlot <- function(data, mapping, labels=c("alpha[3]", "alpha[1]", "alpha[2]"), 
+triPlot <- function(data, mapping, labels=c("alpha[1]", "alpha[2]", "alpha[3]"), 
                     parse=TRUE, grid_lines=4, aes_string = NULL,
                     geom=geom_point, ...) {
   if (!is.null(aes_string)) 
@@ -115,10 +115,10 @@ triPlot <- function(data, mapping, labels=c("alpha[3]", "alpha[1]", "alpha[2]"),
               color=xy_theme_old()$axis.title$colour, 
               size=4,
               data=data.frame(label=rep(labels, length.out=3),
-                              x=c(.5,-.02,1.02), 
-                              y=c(1.02,0,0),
-                              hj = c(.5,1,0),
-                              vj = c(0,0.5,0.5)
+                              x=c(.5,-.02,1.02)[c(2, 3, 1)], 
+                              y=c(1.02,0,0)[c(2, 3, 1)],
+                              hj = c(.5,1,0)[ c(2, 3, 1)],
+                              vj = c(0,0.5,0.5)[c(2, 3, 1)]
               ), 
               parse=parse) 
     q + do.call( geom, c(list(mapping=mapping), list(...)) )
@@ -170,13 +170,13 @@ standardTriPlot <- function(
 {
   
   p <- triPlot(subset(data, method!="orig"), 
-               mapping = modifyList(aes(x=alpha_3, y=alpha_1, z=alpha_2), mapping),
+               mapping = modifyList(aes(x=alpha_1, y=alpha_2, z=alpha_3), mapping),
                labels=labels,
                grid_lines=grid_lines, 
                size=size, alpha=alpha ) + 
     geom_point(data=subset(data, method=="orig"), 
-               aes(x = tri2x(alpha_3, alpha_1, alpha_2),
[…]

### 2015-08-20 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
improved legend

@@
   # scale_alpha_manual(values = c(.2, .6,.6,.6,.6)) +
-  scale_shape_manual(values = 21:25)  
+  scale_shape_manual(values = 21:25) +
+  guides( 
+    col = guide_legend(override.aes = aes(size = 5, shape = 21)) )
 @

### 2015-08-21 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Completed a sentence.
Fixed sigma_graph_function.

@@
 
-<<sigma_graph_function>>=
+<<sigma_graph>>=
 ### A function named blah_function should return a function, not a plot.  Don't use function in the name 
@@
 
-sigma_graph_function <- function(data){
+sigma_graph <- function(data){
   sigma_graph_data <- 
@@
 
-  return(sigma_graph_data)
+  # return(sigma_graph_data)
 
@@
 <<sigma_graph_PT, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for Portugal.">>=
-sigma_graph_function(AllCoeffs %>% filter(model=="CES", Country=="PT"))
+sigma_graph(AllCoeffs %>% filter(model=="CES", Country=="PT"))
 @
@@
 <<sigma_graph_UK, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for the UK.">>=
-sigma_graph_function(AllCoeffs %>% filter(model=="CES", Country=="UK"))
+sigma_graph(AllCoeffs %>% filter(model=="CES", Country=="UK"))
 @
@@
 Here is a table of the raw CES coefficient values. 
-This table is not used in the paper, so I'm putting it in 
+This table is not used in the paper, so I'm putting it in the graveyard.
 <<CES_sigma, results="asis">>=

### 2015-08-21 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Fixed raw CES table.

@@
 
-data_CES_sigma_raw <- sigma_data %>% select(Country, Model, flavor, Energy, Nest, CSP, sigma_1, sigma)
-data_CES_sigma_raw <- plyr::rename(data_CES_sigma_raw, c("sigma" = "$\\sigma$",
-                                                         "sigma_1" = "$\\sigma_1$"))
-data_CES_sigma_raw <- plyr::rename(data_CES_sigma_raw, c("flavor" = "Factors of prod."))
-data_CES_sigma_raw$CSP <- plyr::mapvalues(data_CES_sigma_raw$CSP, 
+# data_CES_sigma_raw <- sigma_data %>% select(Country, Model, flavor, Energy, Nest, CSP, sigma_1, sigma)
+# data_CES_sigma_raw <- plyr::rename(data_CES_sigma_raw, c("sigma" = "$\\sigma$",
+#                                                          "sigma_1" = "$\\sigma_1$"))
+# data_CES_sigma_raw <- plyr::rename(data_CES_sigma_raw, c("flavor" = "Factors of prod."))
+# data_CES_sigma_raw$CSP <- plyr::mapvalues(data_CES_sigma_raw$CSP, 
+#                                          from=c("Adhere to CSP", "Reject CSP"), 
+#                                          to=c("Adhere", "Reject"))
+# data_CES_sigma_raw$Energy <- plyr::mapvalues(data_CES_sigma_raw$Energy, 
+#                                          from=c("Without energy", "With energy"), 
+#                                          to=c("Without", "With"))
+
+data_CES_sigma_raw <- AllCoeffs %>%
+  filter(model=="CES") %>%
+   mutate(
+     Nest = plyr::mapvalues(nest,
+                            from=c("kl", "kle", "lek", "ekl"),
+                            to=c("$kl$", "$(kl)e$", "$(le)k$", "$(ek)l$")),
+     CSP = plyr::mapvalues(CSP, 
                            from=c("Adhere to CSP", "Reject CSP"), 
-                                         to=c("Adhere", "Reject"))
-data_CES_sigma_raw$Energy <- plyr::mapvalues(data_CES_sigma_raw$Energy, 
+                           to=c("Adhere", "Reject")),
+     Energy = plyr::mapvalues(energy, 
                               from=c("Without energy", "With energy"), 
                               to=c("Without", "With"))
+     ) %>%
+  select(Country, flavor, Energy, Nest, CSP, sigma_1, sigma) %>%
+  plyr::rename(
+    c("sigma" = "$\\sigma$",
+      "sigma_1" = "$\\sigma_1$",
+      "flavor" = "Factors of Prod."))
 

### 2015-08-21 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
tweak triplot and add sigma plot

--- 2015-08-20 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
@@
 
+AllCoeffs <-
+  AllCoeffs %>% 
+  mutate( 
+    nest = ifelse(is.na(nest), "", nest)
+    )
+
 ### It looks like this could also be done the otehr way arround:  We could scoop up all the models
@@
 %++++++++++++++++++++++++++++++
+
+<<>>=
+ggplot(
+  AllCoeffs %>% 
+    gather(type, value, matches("sigma")) %>% 
+    filter(!is.na(value)) %>% 
+    filter(! type %in% c("sigma", "sigma_1")) %>%
+    mutate( Model = interaction(nest, CSP, sep = " ", drop=TRUE),
+            Inputs = flavor) 
+  ) + 
+  geom_point(aes(x=.0001 + value, y=type, 
+                 shape = Model, fill=Model, size=Model,
+                 color=Inputs
+                 )
+                 #position = position_jitter(height=0.2, width=0)
+             ) + 
+  facet_grid( type ~ Country, scales = "free_y" ) + 
+  scale_x_log10(limits = c(0.001,2000)) +
+  xy_theme() +
+  scale_colour_manual(values = c("gray70", "black")) +
+  scale_size_manual(values = c(5, 3,3,3,3,3,3)) +
+  # scale_alpha_manual(values = c(.2, .6,.6,.6,.6, .6, .6)) +
+  scale_fill_manual(values = c(scales::alpha("gray50", .2), rep("transparent", 6))) +
+  scale_shape_manual(values = c(21, 21, 23:27)) +
+  guides( 
+    col = guide_legend(override.aes = aes(size = 5, shape = 21))
+    )
+
+@
 
@@
   data=
-    AllCoeffs %>% 
-    mutate( Model = interaction(nest, CSP, sep = " -- ", drop=TRUE),
+    AllCoeffs %>% filter(model == "CES") %>%
+    mutate( Model = interaction(nest, CSP, sep = " ", drop=TRUE),
             Inputs = flavor), 
+  grid_lines = 5,
   labels = c("alpha[k]", "alpha[l]", "alpha[e]"),
@@
       size = Model,
-      color = Inputs),
-  alpha = 0.6) +
+      color = Inputs)
+  ) +
   facet_grid(. ~ Country) +
   scale_colour_manual(values = c("gray70", "black")) +
-  scale_size_manual(values = c(5, 3,3,3,3)) +
-  # scale_alpha_manual(values = c(.2, .6,.6,.6,.6)) +
-  scale_shape_manual(values = 21:25) +
+  scale_size_manual(values = c(5, 3,3,3,3,3,3)) +
+  # scale_alpha_manual(values = c(.2, .6,.6,.6,.6, .6, .6)) +
+  scale_fill_manual(values = c(scales::alpha("gray50", .2), rep("transparent", 6))) +
+  scale_shape_manual(values = c(21, 21, 23:27)) +
   guides( 

### 2015-08-21 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
add model_points(); rename levels of CSP

--- 2015-08-21 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
@@
 ### That's nice.  I assume that's why you wrote a function.  But what does it DO?
-
+@
+
+<<myXTable>>=
 myXTable <- function(data, caption, label, digits=2){
@@
 }
+@
+
+<<model_points>>=
+model_points <- function(p) {
+  p + 
+  scale_colour_manual(values = c("gray70", "black")) +
+  scale_size_manual(values = c(5, 3,3,3,3,3,3)) +
+  # scale_alpha_manual(values = c(.2, .6,.6,.6,.6, .6, .6)) +
+  scale_fill_manual(values = c(scales::alpha("gray50", .2), rep("transparent", 6))) +
+  scale_shape_manual(values = c(21, 21, 23:27)) +
+  guides( 
+    col = guide_legend(override.aes = aes(size = 5, shape = 21)) )
+}
+
 @
@@
   bind_rows() %>%
-  mutate(CSP = "Adhere to CSP")
+  mutate(CSP = "w/ CSP")
 
@@
   bind_rows() %>%
-  mutate(CSP="Reject CSP")
+  mutate(CSP="w/o CSP")
 
 AllCoeffs <- bind_rows(AllCoeffsExp, AllCoeffsCSP, AllCoeffsNoCSP)
+
+AllCoeffs <-
+  AllCoeffs %>% 
+  mutate( 
+    nest = ifelse(is.na(nest), "", nest),
+    CSP = ifelse( CSP == "w/ CSP", "w/ CSP", "w/o CSP")
+    )
 
@@
     nest = relevelFactor(factor(nest), c("kl", "kle", "lek", "ekl")),
-    CSP = relevelFactor(factor(CSP), c("Adhere to CSP", "Reject CSP"))
+    CSP = relevelFactor(factor(CSP), c("w/ CSP", "w/o CSP"))
   ) %>% 
@@
   bind_rows() %>%
-  mutate(CSP = "Reject CSP")
+  mutate(CSP = "w/o CSP")
 
@@
   fitted_and_resid_data %>% 
-  filter(model=="CES" & CSP=="Reject CSP" & (nest == "kl" | nest == "kle"))
+  filter(model=="CES" & CSP=="w/o CSP" & (nest == "kl" | nest == "kle"))
 
@@
   fitted_and_resid_data %>% 
-    filter(model=="CES" & CSP=="Reject CSP" & (nest=="kle" | nest=="kl")), 
+    filter(model=="CES" & CSP=="w/o CSP" & (nest=="kle" | nest=="kl")), 
   withEnergyShape = 0) # square
@@
 
+Clean up labeling, etc. later.
+
+<<fig.width=8.5, fig.height=5, out.width=".9\\textwidth">>=
+p <- 
+ggplot(
+  AllCoeffs %>% 
+    gather(type, value, matches("sigma")) %>% 
+    filter(!is.na(value)) %>% 
+    filter(! type %in% c("sigma", "sigma_1")) %>%
+    mutate( Model = interaction(nest, CSP, sep = " ", drop=TRUE),
+            Inputs = flavor) 
+  ) + 
+  geom_point(aes(x=.0001 + value, y=type, 
+                 shape = Model, fill=Model, size=Model,
+                 color=Inputs
+                 )
+                 #position = position_jitter(height=0.2, width=0)
+             ) + 
+  facet_grid( type ~ Country, scales = "free_y" ) + 
+  scale_x_log10(limits = c(0.001,2000)) +
+  xy_theme() +
+  theme(legend.position="top")
+
+model_points(p)
+@
+
 <<sigma_graph>>=
@@
              CSP, 
-             from=c("Adhere to CSP", "Reject CSP"), 
+             from=c("w/ CSP", "w/o CSP"), 
              to=c("Adhere", "Reject")),
@@
 <<Graphs_CD-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Cobb-Douglas models that reject the cost-share theorem. Solid line is historical GDP.">>=
-fittedGraphNoCSP(fitted_and_resid_data %>% filter(model=="CD" & CSP=="Reject CSP"))
+fittedGraphNoCSP(fitted_and_resid_data %>% filter(model=="CD" & CSP=="w/o CSP"))
 @
@@
 <<Graphs_CD-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for Cobb-Douglas models.">>=
-residualPlot(fitted_and_resid_data %>% filter(model=="CD" & CSP=="Reject CSP"))
+residualPlot(fitted_and_resid_data %>% filter(model=="CD" & CSP=="w/o CSP"))
 @
@@
 <<fig.height=3>>=
-triPlot(
+
+p <- triPlot(
   data=
-    AllCoeffs %>% 
-    mutate( Model = interaction(nest, CSP, sep = " -- ", drop=TRUE),
+    AllCoeffs %>% filter(model == "CES") %>%
+    mutate( Model = interaction(nest, CSP, sep = " ", drop=TRUE),
             Inputs = flavor), 
+  grid_lines = 5,
   labels = c("alpha[k]", "alpha[l]", "alpha[e]"),
@@
       size = Model,
-      color = Inputs),
-  alpha = 0.6) +
-  facet_grid(. ~ Country) +
-  scale_colour_manual(values = c("gray70", "black")) +
-  scale_size_manual(values = c(5, 3,3,3,3)) +
-  # scale_alpha_manual(values = c(.2, .6,.6,.6,.6)) +
-  scale_shape_manual(values = 21:25) +
-  guides( 
-    col = guide_legend(override.aes = aes(size = 5, shape = 21)) )
+      color = Inputs)
+  ) +
+  facet_grid(. ~ Country)
+  model_points(p)
 @
@@
 # data_CES_sigma_raw$CSP <- plyr::mapvalues(data_CES_sigma_raw$CSP, 
-#                                          from=c("Adhere to CSP", "Reject CSP"), 
+#                                          from=c("w/ CSP", "w/o CSP"), 
 #                                          to=c("Adhere", "Reject"))
@@
      CSP = plyr::mapvalues(CSP, 
-                           from=c("Adhere to CSP", "Reject CSP"), 
+                           from=c("w/ CSP", "w/o CSP"), 
                            to=c("Adhere", "Reject")),
@@
 residualPlot(fitted_and_resid_data %>% 
-               filter(model=="CES" & CSP=="Reject CSP" & (nest == "lek" | nest=="kl")),
+               filter(model=="CES" & CSP=="w/o CSP" & (nest == "lek" | nest=="kl")),
              withEnergyShape = 3) # plus
@@
 residualPlot(fitted_and_resid_data %>% 
-               filter(model=="CES" & CSP=="Reject CSP" & (nest=="ekl" | nest=="kl")),
+               filter(model=="CES" & CSP=="w/o CSP" & (nest=="ekl" | nest=="kl")),
              withEnergyShape = 4) # times
@@
 <<Graphs_CESlek-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with $kl$ and ($le$)$k$ nesting that reject the CSP. Solid line is historical GDP.">>=
-fittedGraphData_lek <- fitted_and_resid_data %>% filter(model=="CES" & CSP=="Reject CSP" & (nest == "kl" | nest == "lek"))
+fittedGraphData_lek <- fitted_and_resid_data %>% filter(model=="CES" & CSP=="w/o CSP" & (nest == "kl" | nest == "lek"))
 fittedGraphNoCSP(fittedGraphData_lek)
@@
   fitted_and_resid_data %>% 
-  filter(model=="CES" & CSP=="Reject CSP" & (nest == "kl" | nest == "ekl"))
+  filter(model=="CES" & CSP=="w/o CSP" & (nest == "kl" | nest == "ekl"))
 fittedGraphNoCSP(fittedGraphData_ekl)

### 2015-08-21 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
model_points --> model_points_style

@@
 <<model_points>>=
-model_points <- function(p) {
+model_points_style <- function(p) {
   p + 
@@
 
-model_points(p)
+model_points_style(p)
 @
@@
   facet_grid(. ~ Country)
-  model_points(p)
+  model_points_style(p)
 @

### 2015-08-21 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Added second alpha option. Cleaning sigma graph.

@@
 
+<<output_elasticities_graph_ternary, fig.pos="H", fig.align="center", fig.width=7.5, fig.height=2.8, fig.cap="Ternary graph of output elasticities~($\\alpha$).
+This version shows all Unadjusted and Quality-adjusted points on the same graph.
+Perhaps it is easier to see the effect of quality-adjustment of data this way.">>=
+p <- triPlot(
+  data=
+    AllCoeffs %>% filter(model == "CES") %>%
+    mutate( Model = interaction(nest, CSP, sep = " ", drop=TRUE),
+            Inputs = flavor), 
+  grid_lines = 5,
+  labels = c("alpha[k]", "alpha[l]", "alpha[e]"),
+  aes(x = alpha_1, y = alpha_2, z = alpha_3, 
+      fill  = Model, 
+      shape = Model,
+      size = Model,
+      color = Inputs)
+  ) +
+  facet_grid(. ~ Country)
+  model_points_style(p)
+@
+
+<<output_elasticities_graph_ternary_2, fig.pos="H", fig.align="center", fig.width=7.5, fig.height=5, fig.cap="Ternary graph of output elasticities~($\\alpha$).
+This version splits the Unadjusted and Quality-adjusted values on their own graphs.
+This approach is parallel to the previous figures (historical data, fitted GDP, and residuals.">>=
+triPlot(
+  data=
+    AllCoeffs %>% filter(model == "CES") %>%
+    mutate( Model = interaction(nest, CSP, sep = " ", drop=TRUE),
+            Inputs = flavor), 
+  grid_lines = 5,
+  labels = c("alpha[k]", "alpha[l]", "alpha[e]"),
+  aes(x = alpha_1, y = alpha_2, z = alpha_3, 
+      fill  = Model, 
+      shape = Model,
+      size = Model
+      # color = Inputs
+      )
+  ) +
+  facet_grid(Inputs ~ Country) +
+
+    # model_points_style(p)
+
+  # scale_colour_manual(values = c("gray70", "black")) +
+  scale_size_manual(values = c(5, 3,3,3,3,3,3)) +
+  # scale_alpha_manual(values = c(.2, .6,.6,.6,.6, .6, .6)) +
+  scale_fill_manual(values = c(scales::alpha("gray50", .2), rep("transparent", 6))) +
+  scale_shape_manual(values = c(21, 21, 23:27)) +
+  guides( 
+    col = guide_legend(override.aes = aes(size = 5, shape = 21)) )
+@
+
 %++++++++++++++++++++++++++++++
@@
 
-<<fig.width=8.5, fig.height=5, out.width=".9\\textwidth">>=
+<<sigma_graph_2, fig.pos="H", fig.align='center', fig.width=8.5, fig.height=5, out.width="0.9\\textwidth", fig.cap="Elasticities of substitution~($\\sigma$).">>=
 p <- 
@@
     filter(! type %in% c("sigma", "sigma_1")) %>%
-    mutate( Model = interaction(nest, CSP, sep = " ", drop=TRUE),
-            Inputs = flavor) 
+    mutate(Model = interaction(nest, CSP, sep = " ", drop=TRUE),
+           Inputs = flavor
+           )
   ) + 
-  geom_point(aes(x=.0001 + value, y=type, 
+  geom_point(aes(x=value, y=type, 
                  shape = Model, fill=Model, size=Model,
@@
   scale_x_log10(limits = c(0.001,2000)) +
+  geom_vline(xintercept = 1, color="gray50", size=0.2) +
   xy_theme() +
@@
 
-<<sigma_graph>>=
+<<sigma_graph, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for the UK.", eval=FALSE, include=FALSE>>=
 ### A function named blah_function should return a function, not a plot.  Don't use function in the name 
@@
 
-<<sigma_graph_PT, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for Portugal.">>=
+<<sigma_graph_PT, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for Portugal.", eval=FALSE, include=FALSE>>=
 sigma_graph(AllCoeffs %>% filter(model=="CES", Country=="PT"))
@@
 
-<<sigma_graph_UK, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for the UK.">>=
+<<sigma_graph_UK, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for the UK.", eval=FALSE, include=FALSE>>=
 sigma_graph(AllCoeffs %>% filter(model=="CES", Country=="UK"))
@@
 %
-
-<<fig.height=3>>=
-
-p <- triPlot(
-  data=
-    AllCoeffs %>% filter(model == "CES") %>%
-    mutate( Model = interaction(nest, CSP, sep = " ", drop=TRUE),
-            Inputs = flavor), 
-  grid_lines = 5,
-  labels = c("alpha[k]", "alpha[l]", "alpha[e]"),
-  aes(x = alpha_1, y = alpha_2, z = alpha_3, 
-      fill  = Model, 
-      shape = Model,
-      size = Model,
-      color = Inputs)
-  ) +
-  facet_grid(. ~ Country)
-  model_points_style(p)
-@
-
 Table~\ref{tab:CD_coeffs} shows coefficients for all fitted Cobb-Douglas models

### 2015-08-21 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Removed x,y labels and y strip text.

@@
   scale_x_log10(limits = c(0.001,2000)) +
+  xlab("") +
   geom_vline(xintercept = 1, color="gray50", size=0.2) +
+  ylab("") +
   xy_theme() +
-  theme(legend.position="top")
+  theme(
+    legend.position="top",
+    strip.text.y = element_blank())
 

### 2015-08-21 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Eliminated sci notation on x axis.

--- 2015-08-21 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
@@
 library(tidyr)
+library(scales)
 
@@
   facet_grid( type ~ Country, scales = "free_y" ) + 
-  scale_x_log10(limits = c(0.001,2000)) +
+  scale_x_log10(limits = c(0.001,2000), labels=comma) +
+  xlab("") +
   geom_vline(xintercept = 1, color="gray50", size=0.2) +
+  ylab("") +
   xy_theme() +
-  theme(legend.position="top")
+  theme(
+    legend.position="top",
+    strip.text.y = element_blank())
 

### 2015-08-21 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Better sigma graph x axis labels.

@@
 <<sigma_graph_2, fig.pos="H", fig.align='center', fig.width=8.5, fig.height=5, out.width="0.9\\textwidth", fig.cap="Elasticities of substitution~($\\sigma$).">>=
+breaks_labels = c(0.01, 1, 100)
 p <- 
@@
   facet_grid( type ~ Country, scales = "free_y" ) + 
-  scale_x_log10(limits = c(0.001,2000), labels=comma) +
+  scale_x_log10(limits = c(0.001,2000), breaks=breaks_labels, labels=breaks_labels) +
   xlab("") +

### 2015-08-22 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Move new sigma graph lower. 2nd option.

@@
 
-Clean up labeling, etc. later.
+<<sigma_graph, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for the UK.", eval=FALSE, include=FALSE>>=
+sigma_graph <- function(data){
+  sigma_graph_data <- 
+    data %>% 
+    select(Country, CSP, flavor, energy, nest, 
+           sigma_12, sigma_23, sigma_13, 
+           sigma_12_3, sigma_23_1, sigma_13_2) %>%
+    mutate(nest = plyr::mapvalues( # Change nest to a nicer-looking nest string
+      nest, 
+      from=c("kl", "kle", "lek", "ekl"), 
+      to=c("kl", "(kl)e", "(le)k", "(ek)l"))
+    ) %>%
+    gather(variable, value, sigma_12, sigma_23, sigma_13, sigma_12_3, sigma_23_1, sigma_13_2) %>%
+    mutate(label = paste(CSP, flavor, energy, nest, variable, sep=", ")) %>%
+    na.omit()
+
+  # return(sigma_graph_data)
+
+  # Make the plot
+  plot <- ggplot(sigma_graph_data, mapping=aes(x=label, y=value, fill=variable, width=0.4)) + 
+    geom_bar(stat="identity") + 
+    xlab("") +
+    # scale_x_discrete(limits=rev(order)) +
+    scale_x_discrete(labels=sigma_graph_data$label) +
+    geom_hline(aes(yintercept = 1), colour="gray50", size=0.1) +
+    ylab("") +
+    # coord_trans(y="sigma") +
+    scale_y_continuous(limits=c(0, 10), breaks=c(0, 1.0, 10)) +
+    guides(fill=guide_legend(title=NULL)) +
+    scale_fill_brewer(palette="OrRd") +
+#     scale_fill_brewer(palette="OrRd",
+#                       labels=c(expression(sigma[kl]), 
+#                                expression(sigma[le]), 
+#                                expression(sigma[ek]),
+#                                expression(sigma["(kl)e"]),
+#                                expression(sigma["(le)k"]),
+#                                expression(sigma["(ek)l"]))) +
+    coord_flip() + 
+    xy_theme() +
+    theme(axis.ticks.y = element_blank())
+  return(plot)
+}
+@
 
@@
 
-<<sigma_graph, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for the UK.", eval=FALSE, include=FALSE>>=
-### A function named blah_function should return a function, not a plot.  Don't use function in the name 
-### of a function unless it tells you something about the function.  All functions are functions, we don't
-### need to name them like that.
-
-sigma_graph <- function(data){
-  sigma_graph_data <- 
-    data %>% 
-    select(Country, CSP, flavor, energy, nest, 
-           sigma_12, sigma_23, sigma_13, 
-           sigma_12_3, sigma_23_1, sigma_13_2) %>%
-    mutate(nest = plyr::mapvalues( # Change nest to a nicer-looking nest string
-      nest, 
-      from=c("kl", "kle", "lek", "ekl"), 
-      to=c("kl", "(kl)e", "(le)k", "(ek)l"))
-    ) %>%
-    gather(variable, value, sigma_12, sigma_23, sigma_13, sigma_12_3, sigma_23_1, sigma_13_2) %>%
-    mutate(label = paste(CSP, flavor, energy, nest, variable, sep=", ")) %>%
-    na.omit()
-
-  # return(sigma_graph_data)
-
-  # Make the plot
-  plot <- ggplot(sigma_graph_data, mapping=aes(x=label, y=value, fill=variable, width=0.4)) + 
-    geom_bar(stat="identity") + 
+<<sigma_graph_3, fig.pos="H", fig.align='center', fig.width=8.5, fig.height=5, out.width="0.9\\textwidth", fig.cap="Elasticities of substitution~($\\sigma$) with factors of production on the vertical facet.">>=
+breaks_labels = c(0.01, 1, 100)
+p <- 
+ggplot(
+  AllCoeffs %>% 
+    gather(type, value, matches("sigma")) %>% 
+    filter(!is.na(value)) %>% 
+    filter(! type %in% c("sigma", "sigma_1")) %>%
+    mutate(Model = interaction(nest, CSP, sep = " ", drop=TRUE),
+           Inputs = flavor
+           )
+  ) + 
+  geom_point(aes(x=value, y=type, 
+                 shape = Model, fill=Model, size=Model,
+                 color=Inputs
+                 )
+                 #position = position_jitter(height=0.2, width=0)
+             ) + 
+  # facet_grid( type ~ Country, scales = "free_y" ) + 
+  facet_grid( Inputs ~ Country) + 
+  scale_x_log10(limits = c(0.001,2000), breaks=breaks_labels, labels=breaks_labels) +
   xlab("") +
-    # scale_x_discrete(limits=rev(order)) +
-    scale_x_discrete(labels=sigma_graph_data$label) +
-    geom_hline(aes(yintercept = 1), colour="gray50", size=0.1) +
+  geom_vline(xintercept = 1, color="gray50", size=0.2) +
   ylab("") +
-    # coord_trans(y="sigma") +
-    scale_y_continuous(limits=c(0, 10), breaks=c(0, 1.0, 10)) +
-    guides(fill=guide_legend(title=NULL)) +
-    scale_fill_brewer(palette="OrRd") +
-#     scale_fill_brewer(palette="OrRd",
-#                       labels=c(expression(sigma[kl]), 
-#                                expression(sigma[le]), 
-#                                expression(sigma[ek]),
-#                                expression(sigma["(kl)e"]),
-#                                expression(sigma["(le)k"]),
-#                                expression(sigma["(ek)l"]))) +
-    coord_flip() + 
-    xy_theme() +
-    theme(axis.ticks.y = element_blank())
-  return(plot)
-}
+  xy_theme() #+
+#   theme(
+#     legend.position="top",
+#     strip.text.y = element_blank())
+
+model_points_style(p)
 @

### 2015-08-22 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Moving sigma graphs and minor changes.

@@
 
+<<sigma_graph_PT, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for Portugal.", eval=FALSE, include=FALSE>>=
+sigma_graph(AllCoeffs %>% filter(model=="CES", Country=="PT"))
+@
+
+<<sigma_graph_UK, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for the UK.", eval=FALSE, include=FALSE>>=
+sigma_graph(AllCoeffs %>% filter(model=="CES", Country=="UK"))
+@
+
 <<sigma_graph_2, fig.pos="H", fig.align='center', fig.width=8.5, fig.height=5, out.width="0.9\\textwidth", fig.cap="Elasticities of substitution~($\\sigma$).">>=
-breaks_labels = c(0.01, 1, 100)
+breaks_labels = c(0.01, 0.1, 1, 10, 100)
 p <- 
@@
 <<sigma_graph_3, fig.pos="H", fig.align='center', fig.width=8.5, fig.height=5, out.width="0.9\\textwidth", fig.cap="Elasticities of substitution~($\\sigma$) with factors of production on the vertical facet.">>=
-breaks_labels = c(0.01, 1, 100)
+breaks_labels = c(0.01, 0.1, 1, 10, 100)
 p <- 
@@
              ) + 
-  # facet_grid( type ~ Country, scales = "free_y" ) + 
   facet_grid( Inputs ~ Country) + 
@@
   ylab("") +
-  xy_theme() #+
-#   theme(
-#     legend.position="top",
-#     strip.text.y = element_blank())
+  xy_theme()
 
 model_points_style(p)
-@
-
-<<sigma_graph_PT, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for Portugal.", eval=FALSE, include=FALSE>>=
-sigma_graph(AllCoeffs %>% filter(model=="CES", Country=="PT"))
-@
-
-<<sigma_graph_UK, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for the UK.", eval=FALSE, include=FALSE>>=
-sigma_graph(AllCoeffs %>% filter(model=="CES", Country=="UK"))
 @

### 2015-08-23 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Rearrange tables. Add subsections.
Cleaning up code for historical data graph.

@@
 
-<<model_points>>=
+<<model_points_style>>=
 model_points_style <- function(p) {
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Tables for paper} 
+\label{sec:tables_for_paper}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Table~\ref{tab:CES_sr_gof} shows estimated values of
+the scale parameter~($\theta$),
+the Solow residual~($\lambda$), and
+goodness of fit~(SSE)
+for all modeling choices.
+
+<<Table_data>>=
+table_data <- 
+  AllCoeffs %>%
+  plyr::rename(c(model = "Model", energy = "Energy", nest = "Nest")) %>%
+  mutate(Nest = 
+           plyr::mapvalues(
+             Nest,
+             from=c("kl", "kle", "lek", "ekl"),
+             to=c("$kl$", "$(kl)e$", "$(le)k$", "$(ek)l$")),
+         CSP =  
+           plyr::mapvalues(
+             CSP, 
+             from=c("w/ CSP", "w/o CSP"), 
+             to=c("Adhere", "Reject")),
+         Energy =
+           plyr::mapvalues(
+             Energy, 
+             from=c("Without energy", "With energy"), 
+             to=c("Without", "With")),
+         Model = 
+           plyr::mapvalues(
+             Model, 
+             from=c("exp"), 
+             to=c("Ref."))
+  )
+@
+
+<<CES_sr_gof, results="asis">>=
+data_CES_SR_gof <- 
+  table_data %>% 
+  filter(Model=="CES" | Model=="Ref.") %>% 
+  select(Country, Model, CSP, flavor, Energy, Nest, scale, lambda, sse) %>%
+  plyr::rename(c("flavor" = "Factors of prod.",
+                  "scale" = "$\\theta$",
+                  "lambda" = "$\\lambda$"))
+
+myXTable(data_CES_SR_gof,
+         caption="Scale parameter~($\\theta$), Solow residual~($\\lambda$), and sum of squared errors~($sse$) for all modeling choices.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=4)
+@
+
+Table~\ref{tab:CES_alpha} shows 
+output elasticities~($\alpha$) for all modeling choices.
+
+<<CES_alpha, results="asis">>=
+data_CES_alpha <- 
+  table_data %>% 
+  filter(Model=="CES" | Model=="Ref.") %>% 
+  select(Country, Model, CSP, flavor, Energy, Nest, alpha_1, alpha_2, alpha_3) %>%
+  plyr::rename(c("flavor" = "Factors of prod.",
+                 "alpha_1" = "$\\alpha_k$",
+                 "alpha_2" = "$\\alpha_l$",
+                 "alpha_3" = "$\\alpha_e$"))
+myXTable(data_CES_alpha,
+         caption="Output elasticities~($\\alpha$) for all models.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=2)
+@
+
+Table~\ref{tab:CES_sigma_nest_aware_inner} shows elasticity of substitution~($\sigma$)
+for inner nests.
+Note that the row with 
+``PT, Quality-adjusted, With energy, $(ek)l$ nesting, Rejecting the CSP''
+is, in fact, a boundary model that does not include energy.
+As such, the only knowable elasticity is $\sigma_{kl}$.
+
+<<CES_sigma_nest_aware_inner, results="asis">>=
+sigma_inner_data <- 
+  table_data %>% 
+  filter(Model=="CES") %>% 
+  select(Country, CSP, flavor, Energy, Nest, sigma_12, sigma_23, sigma_13) %>%
+  plyr::rename( c("flavor" = "Factors of prod.",
+                  "sigma_12" = "$\\sigma_{kl}$",
+                  "sigma_23" = "$\\sigma_{le}$",
+                  "sigma_13" = "$\\sigma_{ek}$"))
+#
+myXTable(sigma_inner_data,
+         caption="Elasticities of substitution~($\\sigma$) for inner nests of CES models.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=2)
+@
+
+Table~\ref{tab:CES_sigma_nest_aware_outer} shows elasticity of substitution~($\sigma$)
+for outer nests.
+Rows with the $kl$ nesting are blank, because they have no outer nest.
+The row with
+``PT, Quality-adjusted, With energy, $(ek)l$ nesting, Rejecting the CSP''
+has no values for $\sigma$, because it has no outer nest, being a boundary model
+that includes only~$k$ and~$l$.
+
+<<CES_sigma_nest_aware_outer, results="asis">>=
+sigma_outer_data <- 
+  table_data %>% 
+  filter(Model=="CES") %>% 
+  select(Country, CSP, flavor, Energy, Nest, sigma_12_3, sigma_23_1, sigma_13_2) %>%
+  plyr::rename(c("flavor" = "Factors of prod.", 
+                 "sigma_12_3" = "$\\sigma_{(kl)e}$",
+                 "sigma_23_1" = "$\\sigma_{(le)k}$",
+                 "sigma_13_2" = "$\\sigma_{(ek)l}$"))
+myXTable(sigma_outer_data,
+         caption="Elasticities of substitution~($\\sigma$) for outer nests of CES models.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=2)
+@
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Graphs for paper} 
@@
 
+%++++++++++++++++++++++++++++++
+\subsection{Historical data} 
+\label{sec:historical_data_graph}
+%++++++++++++++++++++++++++++++
+
 Unadjusted and quality-adjusted data for both Portugal and the United Kingdom 
@@
 <<Historical_Data_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Historical data.", warning=FALSE>>=
-# Melt the data into a form that is useful in a couple places
-### Don't write comments like that.  Say what you are doing to reshape and why.  
-### I figured you were going to use it and don't need a comment for that.
-### But it not at all easy to glance at this and see what the point is.
 
@@
   leaf_apply(formulas, class = "formula", f=function(form, name){
-    meta <- strsplit(name, split="[.]")[[1]] # %>% unlist  ### Why use unlist() here?
+    meta <- strsplit(name, split="[.]")[[1]]
     Country <- meta[1]
@@
     # return this.  ### No need to name and store it.
-    melt(trimmed_historical_data, measure.vars = measure.vars, 
-         value.name = "value", variable.name = "variable") %>%
+    melt(
+      trimmed_historical_data, 
+      measure.vars = measure.vars, 
+      value.name = "value",
+      variable.name = "variable") %>%
     mutate(
       Country = Country,
-        flavor =  ifelse (flavor == "adjusted", "Quality-adjusted", "Unadjusted")
+      flavor =  ifelse (flavor == "adjusted", "Quality-adjusted", "Unadjusted"),
+      variable = as.character(variable, stringsAsFactors=FALSE) # eliminate factors which cause problems with bind_rows() below.
       )
   }
-  ) %>% bind_rows()
-
+  ) %>% 
+  bind_rows() %>%
   # Change variable names to make a nicer-looking graph and relevel factors before plotting
-### Note: You an also change the order of things in the legend without changing the order in the data.
-
-histDataForGraph <- 
-  histDataForGraph %>% 
   mutate( variable = plyr::mapvalues(
@@
 
-### I think this exhibits poor use of white space.  See alternative below. 
-if (FALSE)
-historicalPlot(histDataForGraph, 
-               mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
-               facet_formula = Country ~ flavor, 
-               line_types = c(1,2,4,3,2,4,3,2,3,2,3)) + 
-  scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12)) +
-  coord_cartesian(ylim=c(0.5, 13)) +
-  xlab("") + 
-  ylab("Indexed (1960=1)")
-
-### Here each summand has the same indentation so you can see which things are being added together.
 historicalPlot(
@@
   mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
-  facet_formula = Country ~ flavor, 
+  # facet_formula = Country ~ flavor, 
+  facet_formula = flavor ~ Country, 
   line_types = c(1,2,4,3,2,4,3,2,3,2,3)) + 
-scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12)) +
-coord_cartesian(ylim=c(0.5, 13)) +
 xlab("") + 
+scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12), limits=c(0.5, 12)) +
 ylab("Indexed (1960=1)")
@@
 @
+
+%++++++++++++++++++++++++++++++
+\subsection{Residual plot} 
+\label{sec:residual_plot}
+%++++++++++++++++++++++++++++++
 
@@
 %++++++++++++++++++++++++++++++
-\subsection{Factor shares} 
-\label{sec:shares}
+\subsection{Output elasticities} 
+\label{sec:output_elasticities_graph}
 %++++++++++++++++++++++++++++++
@@
     labs(x=expression(delta), y=expression(sigma["(kl)"*e]))
-@
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Tables for paper} 
-\label{sec:tables_for_paper}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Table~\ref{tab:CES_sr_gof} shows estimated values of
-the scale parameter~($\theta$),
-the Solow residual~($\lambda$), and
-goodness of fit~(SSE)
-for all modeling choices.
-
-<<Table_data>>=
-table_data <- 
-  AllCoeffs %>%
-  plyr::rename(c(model = "Model", energy = "Energy", nest = "Nest")) %>%
-  mutate(Nest = 
-           plyr::mapvalues(
-             Nest,
-             from=c("kl", "kle", "lek", "ekl"),
-             to=c("$kl$", "$(kl)e$", "$(le)k$", "$(ek)l$")),
-         CSP =  
-           plyr::mapvalues(
-             CSP, 
-             from=c("w/ CSP", "w/o CSP"), 
-             to=c("Adhere", "Reject")),
-         Energy =
-           plyr::mapvalues(
-             Energy, 
-             from=c("Without energy", "With energy"), 
-             to=c("Without", "With")),
-         Model = 
-           plyr::mapvalues(
-             Model, 
-             from=c("exp"), 
-             to=c("Ref."))
-  )
-@
-
-<<CES_sr_gof, results="asis">>=
-data_CES_SR_gof <- 
-  table_data %>% 
-  filter(Model=="CES" | Model=="Ref.") %>% 
-  select(Country, Model, CSP, flavor, Energy, Nest, scale, lambda, sse) %>%
-  plyr::rename(c("flavor" = "Factors of prod.",
-                  "scale" = "$\\theta$",
-                  "lambda" = "$\\lambda$"))
-
-myXTable(data_CES_SR_gof,
-         caption="Scale parameter~($\\theta$), Solow residual~($\\lambda$), and sum of squared errors~($sse$) for all modeling choices.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=4)
-@
-
-Table~\ref{tab:CES_alpha} shows 
-output elasticities~($\alpha$) for all modeling choices.
-
-<<CES_alpha, results="asis">>=
-data_CES_alpha <- 
-  table_data %>% 
-  filter(Model=="CES" | Model=="Ref.") %>% 
-  select(Country, Model, CSP, flavor, Energy, Nest, alpha_1, alpha_2, alpha_3) %>%
-  plyr::rename(c("flavor" = "Factors of prod.",
-                 "alpha_1" = "$\\alpha_k$",
-                 "alpha_2" = "$\\alpha_l$",
-                 "alpha_3" = "$\\alpha_e$"))
-myXTable(data_CES_alpha,
-         caption="Output elasticities~($\\alpha$) for all models.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=2)
-@
-
-Table~\ref{tab:CES_sigma_nest_aware_inner} shows elasticity of substitution~($\sigma$)
-for inner nests.
-Note that the row with 
-``PT, Quality-adjusted, With energy, $(ek)l$ nesting, Rejecting the CSP''
-is, in fact, a boundary model that does not include energy.
-As such, the only knowable elasticity is $\sigma_{kl}$.
-
-<<CES_sigma_nest_aware_inner, results="asis">>=
-sigma_inner_data <- 
-  table_data %>% 
-  filter(Model=="CES") %>% 
-  select(Country, CSP, flavor, Energy, Nest, sigma_12, sigma_23, sigma_13) %>%
-  plyr::rename( c("flavor" = "Factors of prod.",
-                  "sigma_12" = "$\\sigma_{kl}$",
-                  "sigma_23" = "$\\sigma_{le}$",
-                  "sigma_13" = "$\\sigma_{ek}$"))
-#
-myXTable(sigma_inner_data,
-         caption="Elasticities of substitution~($\\sigma$) for inner nests of CES models.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=2)
-@
-
-Table~\ref{tab:CES_sigma_nest_aware_outer} shows elasticity of substitution~($\sigma$)
-for outer nests.
-Rows with the $kl$ nesting are blank, because they have no outer nest.
-The row with
-``PT, Quality-adjusted, With energy, $(ek)l$ nesting, Rejecting the CSP''
-has no values for $\sigma$, because it has no outer nest, being a boundary model
-that includes only~$k$ and~$l$.
-
-<<CES_sigma_nest_aware_outer, results="asis">>=
-sigma_outer_data <- 
-  table_data %>% 
-  filter(Model=="CES") %>% 
-  select(Country, CSP, flavor, Energy, Nest, sigma_12_3, sigma_23_1, sigma_13_2) %>%
-  plyr::rename(c("flavor" = "Factors of prod.", 
-                 "sigma_12_3" = "$\\sigma_{(kl)e}$",
-                 "sigma_23_1" = "$\\sigma_{(le)k}$",
-                 "sigma_13_2" = "$\\sigma_{(ek)l}$"))
-myXTable(sigma_outer_data,
-         caption="Elasticities of substitution~($\\sigma$) for outer nests of CES models.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=2)
 @

### 2015-08-24 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Adjusting spacing.

@@
       flavor =  ifelse (flavor == "adjusted", "Quality-adjusted", "Unadjusted"),
-      variable = as.character(variable, stringsAsFactors=FALSE) # eliminate factors which cause problems with bind_rows() below.
+      variable = as.character(variable, stringsAsFactors=FALSE) # eliminate factors which cause warnings with bind_rows() below.
       )
@@
   ) %>%
+
   bind_rows() %>%
+
   # Change variable names to make a nicer-looking graph and relevel factors before plotting

### 2015-08-24 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Eliminated stringsAsFactors=FALSE. Was unnecessary.

@@
       flavor =  ifelse (flavor == "adjusted", "Quality-adjusted", "Unadjusted"),
-      variable = as.character(variable, stringsAsFactors=FALSE) # eliminate factors which cause warnings with bind_rows() below.
+      variable = as.character(variable) # eliminate factors, which cause warnings with bind_rows() below.
       )

### 2015-08-24 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Eliminate unneeded line of code.

@@
     mutate(
-      Country = Country,
       flavor =  ifelse (flavor == "adjusted", "Quality-adjusted", "Unadjusted"),

### 2015-08-24 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Change order of legend.

@@
     mutate(
-      flavor =  ifelse (flavor == "adjusted", "Quality-adjusted", "Unadjusted"),
       variable = as.character(variable) # eliminate factors, which cause warnings with bind_rows() below.
@@
     Country = relevelFactor(factor(Country), c("PT", "UK")),
-    flavor = relevelFactor(factor(flavor), c("Unadjusted", "Quality-adjusted")),
-    variable = relevelFactor(factor(variable), unique(variable)) 
+    flavor = ifelse (flavor == "adjusted", "Quality-adjusted", "Unadjusted"),
+    flavor = relevelFactor(factor(flavor), c("Unadjusted", "Quality-adjusted"))
   )
@@
 scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12), limits=c(0.5, 12)) +
-ylab("Indexed (1960=1)")
+ylab("Indexed (1960=1)") +
+scale_fill_discrete(breaks=c("y", "k", "l", "e"))
+
 @

### 2015-08-24 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Minor edits.

@@
 
-    # return this.  ### No need to name and store it.
+    # return this.
     melt(
@@
   }
-  ) %>%
-
-  bind_rows() %>%
+  ) %>% bind_rows() %>%
 
@@
 scale_fill_discrete(breaks=c("y", "k", "l", "e"))
-
 @

### 2015-08-24 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Fix bug introduced when cleaning up code.

@@
     mutate(
-      variable = as.character(variable) # eliminate factors, which cause warnings with bind_rows() below.
+      variable = as.character(variable), # eliminate factors, which cause warnings with bind_rows() below.
+      Country = Country,
+      flavor =  ifelse (flavor == "adjusted", "Quality-adjusted", "Unadjusted")
       )
@@
     Country = relevelFactor(factor(Country), c("PT", "UK")),
-    flavor = ifelse (flavor == "adjusted", "Quality-adjusted", "Unadjusted"),
     flavor = relevelFactor(factor(flavor), c("Unadjusted", "Quality-adjusted"))

### 2015-08-24 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Adjust whitespace.

@@
 
+  mutate( 
     # Change variable names to make a nicer-looking graph and relevel factors before plotting
-  mutate( variable = plyr::mapvalues(
-    variable,
+    variable = plyr::mapvalues(variable,
                                from=c("iGDP", 
@@
                                     "e", "e", "e", "e")),
-    Country = relevelFactor(factor(Country), c("PT", "UK")),
-    flavor = relevelFactor(factor(flavor), c("Unadjusted", "Quality-adjusted"))
+    Country = relevelFactor(factor(Country), c("PT", "UK")), # Adjusts facet order
+    flavor = relevelFactor(factor(flavor), c("Unadjusted", "Quality-adjusted")) # Adjusts facet order
   )
@@
   mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
-  # facet_formula = Country ~ flavor, 
   facet_formula = flavor ~ Country, 

### 2015-08-24 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Change faceting on fitted model.

@@
     scale_linetype_manual(values=c(1,4,2,3), name="") +
-    facet_grid(Country ~ flavor) +
+    facet_grid(flavor ~ Country) +
     scale_x_continuous(breaks=c(1960, 1980, 2000)) +

### 2015-08-24 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Change faceting on fitted model.

@@
     scale_linetype_manual(values=c(1,4,2,3), name="") +
+    # facet_grid(Country ~ flavor) +
     facet_grid(flavor ~ Country) +

### 2015-08-24 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Change faceting of residual plot.

--- 2015-08-24 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
@@
 fittedGraphNoCSP(fittedGraphData_kle)
-
-### Note: I like a blank line have a chain of %>% operators to make it easy to spot where the chain ends.
 @
@@
     scale_size_manual(values=c(4,4)) +
-    facet_grid(Country ~ flavor) +
-    # geom_hline(aes(yintercept = 0), colour="gray50", size=0.1) +
+    facet_grid(flavor ~ Country) +
     geom_hline(yintercept = 0, colour="gray50", size=0.1) +

### 2015-08-24 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Change faceting of SSE, lambda graph.

@@
   scale_shape_manual(values=c(1,0,3,4)) + 
-  facet_grid(Country ~ flavor) +
+  facet_grid(flavor ~ Country) +
   scale_y_continuous(breaks=c(0, 0.01, 0.02, 0.03), limits=c(0, 0.035)) +
@@
 @
-
 %

### 2015-08-24 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Model --> Factors of production in guides.

@@
 
-### Put in a separate R chunk and use eval=FALSE, include=FALSE 
-# This version also plots reference model residuals.
+residualPlot2 <- function(data){
+  dataToPlot <- 
+    data %>%
+    mutate(nest = 
+             plyr::mapvalues(
+               nest, 
+               from=c("kl", "kle", "lek", "ekl"), 
+               to=c("kl", "(kl)e", "(le)k", "(ek)l")
+               ),
+           Model = interaction(nest, CSP, sep = " ", drop=TRUE),
+           Inputs = flavor)
+
+  p <- ggplot() +
+    geom_point(
+      data=dataToPlot, 
+      mapping=aes(
+        x=Year, 
+        y=Residuals, 
+        fill=Model, 
+        shape=Model, 
+        size=Model,
+        color=Inputs)
+      ) +
+    facet_grid(flavor ~ Country) +
+    geom_hline(yintercept = 0, colour="gray50", size=0.1) +
+    scale_x_continuous(breaks=c(1960, 1980, 2000)) +
+    xlab("") +
+    ylab("r") + 
+    xy_theme() +
+    labs(color = "Factors of production") # +
+    # theme(legend.title=element_blank())
+
+  model_points_style(p)
+}
+@
+
+<<Resid_plot_with_ref, eval=FALSE, include=FALSE>>=
+# This version of the residual plot includes reference model residuals.
 # But the reference model dwarfs all other residuals and looks bad on the graph.
@@
 %
+<<Graphs_CESkle-resid_2, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(kl$)$e$ nesting.
+This is an alternative version that uses our new plot style.">>=
+residualPlot2(
+  fitted_and_resid_data %>% 
+    filter(model=="CES" & CSP=="w/o CSP" & (nest=="kle" | nest=="kl"))
+  )
+@
 
@@
              to=c("kl", "(kl)e", "(le)k", "(ek)l")
+             ),
+         Model = interaction(nest, CSP, sep = " ", drop=TRUE),
+         Inputs = flavor
   )
-  )
-
 ggplot() +
@@
   theme(legend.title=element_blank())
+
+@
+
+<<SRsse_CES_graph_2, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Solow Residuals~($\\lambda$) and mean squared error~($sse$).
+$\\lambda$ and $sse$ values for the reference (exponential-only) model are shown as gridlines.
+This version uses our proposed new style.">>=
+data_sr_sse <- 
+  AllCoeffs %>% 
+  filter(model=="CES") %>% 
+  mutate(nest = 
+           plyr::mapvalues(
+             nest, 
+             from=c("kl", "kle", "lek", "ekl"), 
+             to=c("kl", "(kl)e", "(le)k", "(ek)l")
+             ),
+         Model = interaction(nest, CSP, sep = " ", drop=TRUE),
+         Inputs = flavor
+  )
+
+p <- ggplot() +
+  geom_point(
+    data=data_sr_sse, 
+    mapping=aes(
+      x=lambda, 
+      y=sse, 
+      fill=Model, 
+      shape=Model, 
+      size=Model, 
+      color=Inputs)) +
+  geom_vline(aes(xintercept = lambda), 
+             AllCoeffs %>% filter(model=="exp") %>% select(Country, lambda), 
+             colour="gray50", size=0.1) +
+  geom_hline(aes(yintercept = sse), 
+             AllCoeffs %>% filter(model=="exp") %>% select(Country, sse), 
+             colour="gray50", size=0.1) +
+  facet_grid(flavor ~ Country) +
+  scale_x_continuous(breaks=c(0, 0.01, 0.02, 0.03), limits=c(0, 0.035)) +
+  xlab(expression(lambda)) +
+  scale_y_continuous(limits=c(-0.05, 0.7)) +
+  ylab("SSE") + 
+  labs(color = "Factors of production") +
+  xy_theme() # +
+  # theme(legend.title=element_blank())
+
+# Add our style
+model_points_style(p)
+
 @
@@
   ) +
+  labs(color = "Factors of production") +
   facet_grid(. ~ Country)
@@
   ylab("") +
+  labs(color = "Factors of production") +
   xy_theme() +
@@
   ylab("") +
+  labs(color = "Factors of production") +
   xy_theme()

### 2015-08-24 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Better labels on fitted graphs.

@@
                                        "fitted With energy", "fitted Without energy"), 
-                              to = c("GDP",  "Reference model",
-                                     "With energy", "Without energy")),
+                              to = c("GDP",  "Ref. model",
+                                     "w/ energy", "w/o energy")),
       label = relevelFactor(factor(label), 
-                            c("GDP", "Reference model", "Without energy", "With energy"))
+                            c("GDP", "Ref. model", "w/o energy", "w/ energy"))
     )

### 2015-08-24 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Move alpha resampling graph.
New version of SSE vs. lambda graph.

@@
     col = guide_legend(override.aes = aes(size = 5, shape = 21)) )
+}
+
+model_points_style_quad <- function(p) {
+  p + 
+  # scale_colour_manual(values = c("gray70", "black")) +
+  scale_size_manual(values = c(5, 3,3,3,3,3,3)) +
+  # scale_alpha_manual(values = c(.2, .6,.6,.6,.6, .6, .6)) +
+  scale_fill_manual(values = c(scales::alpha("gray50", .2), rep("transparent", 6))) +
+  scale_shape_manual(values = c(21, 21, 23:27)) +
+  guides( 
+    col = guide_legend(override.aes = aes(size = 5, shape = 21)) 
+    ) + 
+  theme(legend.title=element_blank())
 }
@@
         shape=Model, 
-        size=Model,
-        color=Inputs)
+        size=Model #,
+        # color=Inputs
+        )
       ) +
@@
 
-  model_points_style(p)
+  model_points_style_quad(p)
 }
@@
 %++++++++++++++++++++++++++++++
-\subsection{Output elasticities} 
-\label{sec:output_elasticities_graph}
+\subsection{SSE and Solow residual} 
+\label{sec:SSE_and_SR_graphs}
 %++++++++++++++++++++++++++++++
@@
       size=Model, 
-      color=Inputs)) +
+      color=Inputs
+      )) +
+  geom_vline(aes(xintercept = lambda), 
+             AllCoeffs %>% filter(model=="exp") %>% select(Country, lambda), 
+             colour="gray50", size=0.1) +
+  geom_hline(aes(yintercept = sse), 
+             AllCoeffs %>% filter(model=="exp") %>% select(Country, sse), 
+             colour="gray50", size=0.1) +
+  facet_grid(. ~ Country) +
+  scale_x_continuous(breaks=c(0, 0.01, 0.02, 0.03), limits=c(0, 0.035)) +
+  xlab(expression(lambda)) +
+  scale_y_continuous(limits=c(-0.05, 0.7)) +
+  ylab("SSE") + 
+  labs(color = "Factors of production") +
+  xy_theme() # +
+  # theme(legend.title=element_blank())
+
+# Add our style
+model_points_style(p)
+
+@
+
+<<SRsse_CES_graph_3, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Solow Residuals~($\\lambda$) and mean squared error~($sse$).
+$\\lambda$ and $sse$ values for the reference (exponential-only) model are shown as gridlines.
+This version uses our proposed new style.">>=
+data_sr_sse <- 
+  AllCoeffs %>% 
+  filter(model=="CES") %>% 
+  mutate(nest = 
+           plyr::mapvalues(
+             nest, 
+             from=c("kl", "kle", "lek", "ekl"), 
+             to=c("kl", "(kl)e", "(le)k", "(ek)l")
+             ),
+         Model = interaction(nest, CSP, sep = " ", drop=TRUE),
+         Inputs = flavor
+  )
+
+p <- ggplot() +
+  geom_point(
+    data=data_sr_sse, 
+    mapping=aes(
+      x=lambda, 
+      y=sse, 
+      fill=Model, 
+      shape=Model, 
+      size=Model #, 
+      # color=Inputs
+      )) +
   geom_vline(aes(xintercept = lambda), 
@@
 # Add our style
-model_points_style(p)
-
-@
-%
+model_points_style_quad(p)
+
+@
+
+%++++++++++++++++++++++++++++++
+\subsection{Output elasticities} 
+\label{sec:output_elasticities_graph}
+%++++++++++++++++++++++++++++++
+
 Figures~\ref{fig:Factor_shares_graph_PT} and~\ref{fig:Factor_shares_graph_UK}
@@
 This approach is parallel to the previous figures (historical data, fitted GDP, and residuals.">>=
-triPlot(
+p <- triPlot(
   data=
@@
   ) +
-  facet_grid(Inputs ~ Country) +
-
-    # model_points_style(p)
-
-  # scale_colour_manual(values = c("gray70", "black")) +
-  scale_size_manual(values = c(5, 3,3,3,3,3,3)) +
-  # scale_alpha_manual(values = c(.2, .6,.6,.6,.6, .6, .6)) +
-  scale_fill_manual(values = c(scales::alpha("gray50", .2), rep("transparent", 6))) +
-  scale_shape_manual(values = c(21, 21, 23:27)) +
-  guides( 
-    col = guide_legend(override.aes = aes(size = 5, shape = 21)) )  
+  facet_grid(Inputs ~ Country)
+
+  model_points_style_quad(p)
 @
@@
   geom_point(aes(x=value, y=type, 
-                 shape = Model, fill=Model, size=Model,
-                 color=Inputs
+                 shape = Model, fill=Model, size=Model#,
+                 # color=Inputs
                  )
@@
   ylab("") +
-  labs(color = "Factors of production") +
+#   labs(color = "Factors of production") +
   xy_theme()
 
-model_points_style(p)
+model_points_style_quad(p)
 @
@@
     labs(x=expression(theta), y=expression(lambda))
-@
-
-<<resample_graph_alpha, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.0, fig.cap="$\\alpha_k$, $\\alpha_l$, and $\\alpha_e$ values for CES resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
-standardTriPlot(data=resampleCoeffs, facet_formula=~Country, alpha=0.1,
-                labels=c("alpha[k]", "alpha[l]", "alpha[e]"), size=2.0)
 @
@@
     labs(x=expression(delta), y=expression(sigma["(kl)"*e]))
+@
+
+<<resample_graph_alpha, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.0, fig.cap="$\\alpha_k$, $\\alpha_l$, and $\\alpha_e$ values for CES resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
+standardTriPlot(data=resampleCoeffs, facet_formula=~Country, alpha=0.1,
+                labels=c("alpha[k]", "alpha[l]", "alpha[e]"), size=2.0)
 @

### 2015-08-25 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Clean up graphs.

@@
 
-<<SRsse_CES_graph_2, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Solow Residuals~($\\lambda$) and mean squared error~($sse$).
+<<SRsse_CES_graph_2, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=2.5, fig.cap="Solow Residuals~($\\lambda$) and mean squared error~($sse$).
 $\\lambda$ and $sse$ values for the reference (exponential-only) model are shown as gridlines.
@@
     AllCoeffs %>% filter(model == "CES") %>%
-    mutate( Model = interaction(nest, CSP, sep = " ", drop=TRUE),
-            Inputs = flavor), 
+    mutate( nest = plyr::mapvalues(nest, 
+                                   from=c("kle", "lek", "ekl"), 
+                                   to=c("(kl)e", "(le)k", "(ek)l")),
+            Model = interaction(nest, CSP, sep = " ", drop=TRUE),
+            Inputs = flavor
+            ), 
   grid_lines = 5,
@@
     AllCoeffs %>% filter(model == "CES") %>%
-    mutate( Model = interaction(nest, CSP, sep = " ", drop=TRUE),
+    mutate( nest = plyr::mapvalues(nest, 
+                                   from=c("kle", "lek", "ekl"), 
+                                   to=c("(kl)e", "(le)k", "(ek)l")),
+            Model = interaction(nest, CSP, sep = " ", drop=TRUE),
             Inputs = flavor), 
@@
 
-<<sigma_graph, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for the UK.", eval=FALSE, include=FALSE>>=
+<<sigma_graph>>=
 sigma_graph <- function(data){
@@
 
-<<sigma_graph_PT, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for Portugal.", eval=FALSE, include=FALSE>>=
+<<sigma_graph_PT, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for Portugal.">>=
 sigma_graph(AllCoeffs %>% filter(model=="CES", Country=="PT"))
@@
 
-<<sigma_graph_UK, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for the UK.", eval=FALSE, include=FALSE>>=
+<<sigma_graph_UK, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for the UK.">>=
 sigma_graph(AllCoeffs %>% filter(model=="CES", Country=="UK"))
@@
     filter(! type %in% c("sigma", "sigma_1")) %>%
-    mutate(Model = interaction(nest, CSP, sep = " ", drop=TRUE),
+    mutate(nest = plyr::mapvalues(nest, 
+                                  from=c("kle", "lek", "ekl"), 
+                                  to=c("(kl)e", "(le)k", "(ek)l")),
+           Model = interaction(nest, CSP, sep = " ", drop=TRUE),
            Inputs = flavor
@@
       filter(! type %in% c("sigma", "sigma_1")) %>%
-      mutate(Model = interaction(nest, CSP, sep = " ", drop=TRUE),
-             Inputs = flavor
+      mutate(nest = plyr::mapvalues(nest, 
+                                    from=c("kle", "lek", "ekl"), 
+                                    to=c("(kl)e", "(le)k", "(ek)l")),
+             Model = interaction(nest, CSP, sep = " ", drop=TRUE),
+             Inputs = flavor,
+             type = relevelFactor(type, rev(c("sigma_12", "sigma_23", "sigma_13", "sigma_12_3", "sigma_23_1", "sigma_13_2")))
              )

### 2015-08-25 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Rearrange sigmas on axes in sigma plots.

@@
                                   to=c("(kl)e", "(le)k", "(ek)l")),
+           type = plyr::mapvalues(type,
+                                  from=c("sigma_12", "sigma_23", "sigma_13", "sigma_12_3", "sigma_23_1", "sigma_13_2"),
+                                  to  =c("sigma_kl", "sigma_le", "sigma_ek", "sigma_kl_e", "sigma_le_k", "sigma_ek_l")),
+           type = relevelFactor(type, c("sigma_kl", "sigma_le", "sigma_ek", "sigma_kl_e", "sigma_le_k", "sigma_ek_l")),
            Model = interaction(nest, CSP, sep = " ", drop=TRUE),
@@
              Inputs = flavor,
-             type = relevelFactor(type, rev(c("sigma_12", "sigma_23", "sigma_13", "sigma_12_3", "sigma_23_1", "sigma_13_2")))
+             type = plyr::mapvalues(type,
+                                    from=c("sigma_12", "sigma_23", "sigma_13", "sigma_12_3", "sigma_23_1", "sigma_13_2"),
+                                    to  =c("sigma_kl", "sigma_le", "sigma_ek", "sigma_kl_e", "sigma_le_k", "sigma_ek_l")),
+             type = relevelFactor(type, rev(c("sigma_kl", "sigma_le", "sigma_ek", "sigma_kl_e", "sigma_le_k", "sigma_ek_l")))
              )

### 2015-08-25 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Changed sigma graph width.

@@
 
-<<sigma_graph_2, fig.pos="H", fig.align='center', fig.width=8.5, fig.height=5, out.width="0.9\\textwidth", fig.cap="Elasticities of substitution~($\\sigma$).">>=
+<<sigma_graph_2, fig.pos="H", fig.align='center', fig.width=8.5, fig.height=5, fig.cap="Elasticities of substitution~($\\sigma$).">>=
 breaks_labels = c(0.01, 0.1, 1, 10, 100)
@@
 
-<<sigma_graph_3, fig.pos="H", fig.align='center', fig.width=8.5, fig.height=5, out.width="0.9\\textwidth", fig.cap="Elasticities of substitution~($\\sigma$) with factors of production on the vertical facet.">>=
+<<sigma_graph_3, fig.pos="H", fig.align='center', fig.width=8.5, fig.height=5, fig.cap="Elasticities of substitution~($\\sigma$) with factors of production on the vertical facet.">>=
 breaks_labels = c(0.01, 0.1, 1, 10, 100)

### 2015-08-25 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Now using greek letters in sigma graph scale.

@@
                                   to=c("(kl)e", "(le)k", "(ek)l")),
-           type = plyr::mapvalues(type,
-                                  from=c("sigma_12", "sigma_23", "sigma_13", "sigma_12_3", "sigma_23_1", "sigma_13_2"),
-                                  to  =c("sigma_kl", "sigma_le", "sigma_ek", "sigma_kl_e", "sigma_le_k", "sigma_ek_l")),
-           type = relevelFactor(type, c("sigma_kl", "sigma_le", "sigma_ek", "sigma_kl_e", "sigma_le_k", "sigma_ek_l")),
+           type = relevelFactor(type, c("sigma_12", "sigma_23", "sigma_13", "sigma_12_3", "sigma_23_1", "sigma_13_2")),
            Model = interaction(nest, CSP, sep = " ", drop=TRUE),
@@
   geom_vline(xintercept = 1, color="gray50", size=0.2) +
+  scale_y_discrete(labels = c(
+    sigma_12 = expression(sigma[kl]),
+    sigma_23 = expression(sigma[le]),
+    sigma_13 = expression(sigma[ek]),
+    sigma_12_3 = expression(sigma["(kl)"*e]),
+    sigma_23_1 = expression(sigma["(le)"*k]),
+    sigma_13_2 = expression(sigma["(ek)"*l]))
+    ) +
   ylab("") +

### 2015-08-25 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Now using greek sigmas on both sigma graphs.

@@
              Inputs = flavor,
-             type = plyr::mapvalues(type,
-                                    from=c("sigma_12", "sigma_23", "sigma_13", "sigma_12_3", "sigma_23_1", "sigma_13_2"),
-                                    to  =c("sigma_kl", "sigma_le", "sigma_ek", "sigma_kl_e", "sigma_le_k", "sigma_ek_l")),
-             type = relevelFactor(type, rev(c("sigma_kl", "sigma_le", "sigma_ek", "sigma_kl_e", "sigma_le_k", "sigma_ek_l")))
+#              type = plyr::mapvalues(type,
+#                                     from=c("sigma_12", "sigma_23", "sigma_13", "sigma_12_3", "sigma_23_1", "sigma_13_2"),
+#                                     to  =c("sigma_kl", "sigma_le", "sigma_ek", "sigma_kl_e", "sigma_le_k", "sigma_ek_l")),
+#              type = relevelFactor(type, rev(c("sigma_kl", "sigma_le", "sigma_ek", "sigma_kl_e", "sigma_le_k", "sigma_ek_l")))
+             type = relevelFactor(type, rev(c("sigma_12", "sigma_23", "sigma_13", "sigma_12_3", "sigma_23_1", "sigma_13_2")))
              )
@@
   ylab("") +
+  scale_y_discrete(labels = c(
+    sigma_12 = expression(sigma[kl]),
+    sigma_23 = expression(sigma[le]),
+    sigma_13 = expression(sigma[ek]),
+    sigma_12_3 = expression(sigma["(kl)"*e]),
+    sigma_23_1 = expression(sigma["(le)"*k]),
+    sigma_13_2 = expression(sigma["(ek)"*l]))
+    ) +
 #   labs(color = "Factors of production") +

### 2015-08-25 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Deleting commented lines in graphs.

--- 2015-08-25 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
@@
                  )
-                 #position = position_jitter(height=0.2, width=0)
+                 # position = position_jitter(height=0.2, width=0)
              ) + 
@@
              Inputs = flavor,
-             type = plyr::mapvalues(type,
-                                    from=c("sigma_12", "sigma_23", "sigma_13", "sigma_12_3", "sigma_23_1", "sigma_13_2"),
-                                    to  =c("sigma_kl", "sigma_le", "sigma_ek", "sigma_kl_e", "sigma_le_k", "sigma_ek_l")),
-             type = relevelFactor(type, rev(c("sigma_kl", "sigma_le", "sigma_ek", "sigma_kl_e", "sigma_le_k", "sigma_ek_l")))
+             type = relevelFactor(type, rev(c("sigma_12", "sigma_23", "sigma_13", "sigma_12_3", "sigma_23_1", "sigma_13_2")))
              )
     ) + 
-  geom_point(aes(x=value, y=type, 
-                 shape = Model, fill=Model, size=Model#,
-                 # color=Inputs
+  geom_point(aes(x=value, 
+                 y=type, 
+                 shape = Model, 
+                 fill=Model, 
+                 size=Model
                  )
-             #position = position_jitter(height=0.2, width=0)
              ) + 
@@
   ylab("") +
-#   labs(color = "Factors of production") +
+  scale_y_discrete(labels = c(
+    sigma_12 = expression(sigma[kl]),
+    sigma_23 = expression(sigma[le]),
+    sigma_13 = expression(sigma[ek]),
+    sigma_12_3 = expression(sigma["(kl)"*e]),
+    sigma_23_1 = expression(sigma["(le)"*k]),
+    sigma_13_2 = expression(sigma["(ek)"*l]))
+    ) +
   xy_theme()

### 2015-08-26 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Don't need col where we don't use it.

@@
   scale_shape_manual(values = c(21, 21, 23:27)) +
-  guides( 
-    col = guide_legend(override.aes = aes(size = 5, shape = 21)) 
-    ) + 
   theme(legend.title=element_blank())

### 2015-08-26 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Fixed residuals graph to match style of others.

@@
 
-  p <- ggplot() +
+  ggplot() +
     geom_point(
@@
         shape=Model, 
-        size=Model #,
-        # color=Inputs
+        size=Model
         )
@@
     xy_theme() +
-    labs(color = "Factors of production") # +
-    # theme(legend.title=element_blank())
-
-  model_points_style_quad(p)
+    labs(color = "Factors of production") +
+    # This is custom stuff here to match the model_points_style function. 
+    # We can't use model_points_style, because the aesthetics are different here
+    # with only two series (kl w/o CSP and (kl)e w/o CSP) in the graph.
+    scale_size_manual(values = c(3, 3)) +
+    scale_fill_manual(values = c("transparent", "transparent")) +
+    scale_shape_manual(values = c(21, 23)) +
+  theme(legend.title=element_blank())
 }

### 2015-08-26 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Changing figure sizes.

@@
 
-<<output_elasticities_graph_ternary, fig.pos="H", fig.align="center", fig.width=7.5, fig.height=2.8, fig.cap="Ternary graph of output elasticities~($\\alpha$).
+<<output_elasticities_graph_ternary, fig.pos="H", fig.align="center", fig.width=6.5, fig.height=2.3, fig.cap="Ternary graph of output elasticities~($\\alpha$).
 This version shows all Unadjusted and Quality-adjusted points on the same graph.
@@
 
-<<output_elasticities_graph_ternary_2, fig.pos="H", fig.align="center", fig.width=7.5, fig.height=5, fig.cap="Ternary graph of output elasticities~($\\alpha$).
+<<output_elasticities_graph_ternary_2, fig.pos="H", fig.align="center", fig.width=6.5, fig.height=4.1, fig.cap="Ternary graph of output elasticities~($\\alpha$).
 This version splits the Unadjusted and Quality-adjusted values on their own graphs.
@@
 
-<<sigma_graph_2, fig.pos="H", fig.align='center', fig.width=8.5, fig.height=5, fig.cap="Elasticities of substitution~($\\sigma$).">>=
+<<sigma_graph_2, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.82, fig.cap="Elasticities of substitution~($\\sigma$).">>=
 breaks_labels = c(0.01, 0.1, 1, 10, 100)
@@
     legend.position="top",
-    strip.text.y = element_blank())
+    strip.text.y = element_blank(),
+    axis.text.y = element_text(size=12)
+    )
 
@@
 
-<<sigma_graph_3, fig.pos="H", fig.align='center', fig.width=8.5, fig.height=5, fig.cap="Elasticities of substitution~($\\sigma$) with factors of production on the vertical facet.">>=
+<<sigma_graph_3, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.82, fig.cap="Elasticities of substitution~($\\sigma$) with factors of production on the vertical facet.">>=
 breaks_labels = c(0.01, 0.1, 1, 10, 100)
@@
     ) +
-  xy_theme()
+  xy_theme() +
+  theme(axis.text.y = element_text(size=12))
 

### 2015-09-02 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Fixed line order on historical graphs.

@@
     Country = relevelFactor(factor(Country), c("PT", "UK")), # Adjusts facet order
-    flavor = relevelFactor(factor(flavor), c("Unadjusted", "Quality-adjusted")) # Adjusts facet order
+    flavor = relevelFactor(factor(flavor), c("Unadjusted", "Quality-adjusted")), # Adjusts facet order
+    variable = relevelFactor(factor(variable), c("y", "k", "l", "e"))
   )
@@
 scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12), limits=c(0.5, 12)) +
-ylab("Indexed (1960=1)") +
-scale_fill_discrete(breaks=c("y", "k", "l", "e"))
+ylab("Indexed (1960=1)")
 @

### 2015-09-02 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Edits to residual plots.

@@
     geom_line(data=fittedGraphData, mapping=aes(x=Year, y=value, group=label, linetype=label)) +
-    scale_linetype_manual(values=c(1,4,2,3), name="") +
+    scale_linetype_manual(values=c(1,2,4,3), name="") +
     facet_grid(flavor ~ Country) +
@@
 <<ResidualPlotFunction>>=
-residualPlot <- function(data, withEnergyShape = 0){
-  ggplot() +
-    geom_point(data=data, mapping=aes(x=Year, y=Residuals, shape=energy, color=energy, size=energy)) +
-    scale_shape_manual(values=c(1, withEnergyShape)) +
-    scale_size_manual(values=c(4,4)) +
-    facet_grid(flavor ~ Country) +
-    geom_hline(yintercept = 0, colour="gray50", size=0.1) +
-    scale_x_continuous(breaks=c(1960, 1980, 2000)) +
-    xlab("") +
-    ylab("r") + 
-    xy_theme() +
-    theme(legend.title=element_blank())
-}
-
-residualPlot2 <- function(data){
+
+# residualPlot <- function(data, withEnergyShape = 0){
+#   ggplot() +
+#     geom_point(data=data, mapping=aes(x=Year, y=Residuals, shape=energy, color=energy, size=energy)) +
+#     scale_shape_manual(values=c(1, withEnergyShape)) +
+#     scale_size_manual(values=c(4,4)) +
+#     facet_grid(flavor ~ Country) +
+#     geom_hline(yintercept = 0, colour="gray50", size=0.1) +
+#     scale_x_continuous(breaks=c(1960, 1980, 2000)) +
+#     xlab("") +
+#     ylab("r") + 
+#     xy_theme() +
+#     theme(legend.title=element_blank())
+# }
+
+cesResidualPlot2 <- function(data){
   dataToPlot <- 
@@
 historical~($y_i$) and fitted~($\hat{y}_i$) economic output.
-
-Figures~\ref{fig:Graphs CESkle-resid}--\ref{fig:Graphs CESekl-resid}
-show fitting residuals for all CES models.
-%
-<<Graphs_CESkle-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(kl$)$e$ nesting.">>=
-residualPlot(
-  fitted_and_resid_data %>% 
-    filter(model=="CES" & CSP=="w/o CSP" & (nest=="kle" | nest=="kl")), 
-  withEnergyShape = 0) # square
-@
-%
-<<Graphs_CESkle-resid_2, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(kl$)$e$ nesting.
-This is an alternative version that uses our new plot style.">>=
-residualPlot2(
-  fitted_and_resid_data %>% 
-    filter(model=="CES" & CSP=="w/o CSP" & (nest=="kle" | nest=="kl"))
-  )
-@
 
@@
 @
-
-%
-<<Graphs_CD-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for Cobb-Douglas models.">>=
-residualPlot(fitted_and_resid_data %>% filter(model=="CD" & CSP=="w/o CSP"))
-@
-
+%
+<<Graphs_CD-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for Cobb-Douglas models that reject the CSP.">>=
+  ggplot() +
+    geom_point(
+      data=fitted_and_resid_data %>% 
+        filter(model=="CD" & CSP=="w/o CSP"), 
+      mapping=aes(
+        x=Year,
+        y=Residuals,
+        fill=energy, 
+        shape=energy 
+        )
+      ) +
+    facet_grid( flavor ~ Country) +
+    geom_hline(yintercept = 0, colour="gray50", size=0.1) +
+    scale_x_continuous(breaks=c(1960, 1980, 2000)) +
+    xlab("") +
+    ylab("r") + 
+    xy_theme() +
+    # This is custom stuff here to match the model_points_style function. 
+    # We can't use model_points_style, because the aesthetics are different here
+    scale_fill_manual(values = c("transparent", "transparent")) +
+    scale_shape_manual(values = c(21, 23)) +
+  theme(legend.title=element_blank())
+@
+%
 Table~\ref{tab:Effect_of_CSP_CD} shows the effect of the CSP 
@@
 @
-
-<<Graphs_CESlek-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with ($le$)$k$ nesting.">>=
-residualPlot(fitted_and_resid_data %>% 
-               filter(model=="CES" & CSP=="w/o CSP" & (nest == "lek" | nest=="kl")),
-             withEnergyShape = 3) # plus
-@
-%
-<<Graphs_CESekl-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(ek$)$l$ nesting.">>=
-residualPlot(fitted_and_resid_data %>% 
-               filter(model=="CES" & CSP=="w/o CSP" & (nest=="ekl" | nest=="kl")),
-             withEnergyShape = 4) # times
-@
-
 %
@@
 @
+%
+Figures~\ref{fig:Graphs CESkle-resid}--\ref{fig:Graphs CESekl-resid}
+show fitting residuals for all CES models.
+%
+<<Graphs_CESkle-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(kl$)$e$ nesting.">>=
+cesResidualPlot2(
+  fitted_and_resid_data %>% 
+    filter(model=="CES" & CSP=="w/o CSP" & (nest=="kle" | nest=="kl"))
+)
+@
+%
+<<Graphs_CESlek-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with ($le$)$k$ nesting.">>=
+cesResidualPlot2(
+  fitted_and_resid_data %>% 
+    filter(model=="CES" & CSP=="w/o CSP" & (nest == "lek" | nest=="kl"))
+)
+@
+%
+<<Graphs_CESekl-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(ek$)$l$ nesting.">>=
+cesResidualPlot2(
+  fitted_and_resid_data %>% 
+    filter(model=="CES" & CSP=="w/o CSP" & (nest=="ekl" | nest=="kl"))
+)
+@
 

### 2015-09-10 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Now using better digits in tables.

@@
          label=paste0("tab:", opts_current$get("label")), 
-         digits=4)
+         digits=c(1,1,1,1,1,1,1, 2, 4, 3))
 @
@@
          label=paste0("tab:", opts_current$get("label")), 
-         digits=2)
+         digits=3)
 @
@@
          label=paste0("tab:", opts_current$get("label")), 
-         digits=2)
+         digits=c(1,1,1,1,1,1, 3,3,3))
 @

### 2015-09-10 Articles/Brockway_Rebound_2015/Brockway_2015.Rnw
Now doing resampling in Rebound paper.

@@
 rerunModels=FALSE
+rerunResamples=FALSE
+nResamples <- 100 # Number of resamples
 # ********************************************************
@@
 <<Models>>=
-fileName <- file.path("models", "Brockway2015Models.rds")
+modelsFileName <- file.path("models", "Brockway2015Models.rds")
 if (!rerunModels){
   # load from the file on disk
-  models <- readRDS(fileName)
+  models <- readRDS(modelsFileName)
 } else {
@@
   # Save the models.
-  saveRDS(models, file = fileName)
+  saveRDS(models, file = modelsFileName)
 }
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
-\label{sec:results}
+\section{Resampling Calculations}
+\label{sec:resampling_calculations}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+<<Resampling>>=
+resampleFileName <- file.path("models", "Brockway2015Resamples.rds")
+if (!rerunResamples){
+  # load resample data from the file on disk
+    resampleCoeffs <- readRDS(resampleFileName)
+} else {
+  # Run resampling on models.
+  resampleCoeffs <- leaf_apply(l = models, class = c("cesModel", "plm"), f = function(mod, mod_name){
+    resampledFits(mod, method = "wild", n = nResamples)$coeffs %>%
+      mutate(
+        Country = mod_name
+      )
+  }) %>% bind_rows
+  saveRDS(resampleCoeffs, file = resampleFileName)
+}
+@
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Model Results}
+\label{sec:model_results}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Resampling Results}
+\label{sec:resampling_results}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Calculate rebound by Equation~\ref{eq:rebound}.
+%
+\begin{equation} \label{eq:rebound}
+  Re \approx 1 - \frac{\rho}{1 + \rho} = \sigma_{(kl)e}\; .
+\end{equation}
+%
+<<calc_rebound>>=
+# Add a Rebound column to the resample coefficients
+resampleCoeffs <- resampleCoeffs %>%
+  # Applying the approximation Re ~ 1 - rho/(1 + rho) = sigma
+  mutate(Re = sigma) 
+@
+%
+Plot resampling results for \Sexpr{nResamples} resamples in Figure~\ref{fig:rebound_graph}.
+%
+<<rebound_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=2.5, fig.cap="$\\alpha_e$ vs. $Re$ for all three countries.">>=
+standardScatterPlot(data=resampleCoeffs, mapping=aes(Re, alpha_3), facet_formula=~Country, alpha=0.2, orig_color = "black") +
+    # scale_x_continuous(limits=c(0, 5)) + 
+    scale_x_log10(limits = c(0.001,100), breaks = c(0.01, 0.1, 1, 10), labels = c(0.01, 0.1, 1, 10)) +
+
+    scale_y_continuous(breaks=c(seq(0, 1, 0.2))) +
+    geom_vline(xintercept = 1, colour="gray50", size=0.1) +
+    labs(y=expression(alpha[e]))
+@
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusion}

### 2015-09-12 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
No longer evaluating the texreg thing.

@@
 
-<<stat_details_table, results="asis", include=FALSE>>=
+<<stat_details_table, results="asis", include=FALSE, eval=FALSE>>=
 texreg(list(models$PT$adjusted$withE$CES$kle, models$UK$adjusted$withE$CES$kle), 

### 2015-09-12 Articles/Brockway_Rebound_2015/Brockway_2015.Rnw
Now doing 1000 resamples.

@@
 rerunResamples=FALSE
-nResamples <- 100 # Number of resamples
+nResamples <- 1000 # Number of resamples
 # ********************************************************
@@
 <<rebound_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=2.5, fig.cap="$\\alpha_e$ vs. $Re$ for all three countries.">>=
-standardScatterPlot(data=resampleCoeffs, mapping=aes(Re, alpha_3), facet_formula=~Country, alpha=0.2, orig_color = "black") +
+standardScatterPlot(data=resampleCoeffs, mapping=aes(Re, alpha_3), facet_formula=~Country, alpha=0.05, orig_color = "black") +
     # scale_x_continuous(limits=c(0, 5)) + 

### 2015-09-13 Workflow/Workflow.Rmd
Updated workflow document for torque.

--- 2015-01-02 Workflow/Workflow.Rmd
@@
 * Push the changes to GitHub.   
-* On `acc`, pull from GitHub.     
+* In RStudio at http://rstudio-acc.calvin.edu, pull from GitHub to ensure that RStudio on `acc` will use the same code.
 * Install the `EconData` package from GitHub to dahl
-    + `ssh` to node-00 on dahl. (For some reason, this doesn't work from `fs1` or any other node.)   
+    + Log in to dahl.
     + Open an R shell by saying `R` at the command prompt.    
@@
     + Say `install_github("MatthewHeun/Econ-Growth-R-Analysis/Packages/EconData")`.
+    + While you're at it, you might want to install the `EconModels` package, too. Say 
+        `install_github("MatthewHeun/Econ-Growth-R-Analysis/Packages/EconModels")`
 
-`install_github` makes the historical data available to the nodes of `dahl`.
-This command doesn't work from `fs1` or any of the other nodes of `dahl` (`node-01` through `node-42`).
+`install_github` installs the packages into your home directory, which is available to all nodes of `dahl`.
 
 ### Create the batch script
-* Run the script `r-versions` on `dahl` to see which nodes are operational and which nodes have a working version of `R`. (This script is located at `/usr/local/bin/r-versions`.)
-* Create the file `Scripts/<Source>_batch.bash` file.
-    + It is probably best to modify an existing `<Source>_batch.bash` file.      
+* Create the file `Scripts/<Source>-torque.bash` file.
+    + It is probably best to modify an existing `<Source>-torque.bash` file.      
     + Be sure to edit the `$SRC` variable.
-    + Distribute the work over the nodes in a way that makes sense.
-    + Avoid non-working nodes or nodes that have an out-of-date version of `R` as revealed by `r-versions`.
-* Push the `<Source>_batch.bash` file to GitHub.
-* On `acc`, pull from GitHub.
+* Push the `<Source>-torque.bash` file to GitHub.
+* On http://rstudio-acc.calvin.edu, pull from GitHub.
 
 ### Submit the job to dahl
-* `cd` to the `Econ-Growth-R-Analysis` directory from `fs1.calvin.edu`.
-* Run `Scripts/<Source>_batch.bash "-n 2 -C -d"` followed by `more data_resample/<SOURCE>/node*.txt` to obtain a printout of what will be executed.    
-* Run `Scripts/<Source>_batch.bash "-n 2 -C"` to test that things work as expected.
-* Then do `Scripts/<Source>_batch.bash "-n 1000 -C"` to do a complete run.
-* Check `dahl`'s status at (http://fs1.calvin.edu/ganglia/?m=load_one&r=hour&s=by%2520name&c=dahl&h=&sh=1&hc=4&z=small).
-* Check progress with `more data_resample/<Source>/node*.txt`.
+* `cd` to the `Econ-Growth-R-Analysis` directory on `node-00` of `dahl`.
+* Run `Scripts/<Source>-torque.bash "-n 2 -C -d"`.
+Sample status files will be saved in `Econ-Growth-R-Analysis`.
+(Would be nice to save these output files into `data_resample`.) Look at the status files to see that everything worked as expected.
+* Run `Scripts/<Source>-torque.bash "-n 2 -C"` to test that things work as expected.
+* Then do `Scripts/<Source>-torque.bash "-n 1000 -C"` to do a complete run.
+* Check `dahl`'s status at http://dahl.calvin.edu/ganglia/.
+* Check progress with commands such as `more JobF-CN-iU.e31170`, where `JobF-CN-iU.e31170` is the name of the process that you'd likt to check.
 
 ### Post-process the results
-* Run `Scripts/PostProcess.R -S <Source>` on a node of `dahl` to create:       
-    + `data_postprocessed/<Source>_Coeffs.rda` and
-    + `data_postprocessed/<Source>_Fitted.rda`.  
+* Run `Scripts/PostProcess.R -S <Source>` on `node-00` of `dahl` to create:       
+    + `data_postprocessed/<Source>_Coeffs.rds`,
+    + `data_postprocessed/<Source>_Fitted.rds`, and  
+    + `data_postprocessed/<Source>_oModels.rds`.
 * `PostProcess.R` will accept multiple `<Source>`s. E.g., `Scripts/PostProcess.R -S IST,Leeds,SUN,REXS1960`
-* Note that this command must be issued from a node of the cluster (e.g., `node-00`), not from `fs1.calvin.edu`.
-`fs1` does not have a full install of `R`.
 
@@
 the environment.
-* The `DownloadPostProcessed.R` script connects to `dahl.calvin.edu` (`node-00`). 
-The choice to connect to `node-00` was made to minimize the risk that a file won't propagate across the cluster's 
-file system prior to the download request.
 
@@
 As a consequence, `loadPostProcessedData` returns an object which must be assigned to a variable in `R`.
+
+### 
+* If Randy has run the analysis, resampling results can be placed in `/home/rpruim/Share`. 
+* To download resampling results to his laptop, Matt can say, for example, `scp -P 22122 mkh2@dahl.calvin.edu:/home/rpruim/Share/2015-06-11-run/data_resample/Calvin/* ~/github/Econ-Growth-R-Analysis/data_resample/Calvin`
+* Another way to run some of this is to say `qsub -N JobF-US -d `pwd` batchEcon.R -F "-c US -e all -f all -m fast -S Calvin -n 1000 -C"`

### 2015-09-14 Notes/CESStandardErrors.Rmd
Add CES function notes

---
title: "Estimating precision of estimated parameters in CES models"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(mosaic)
require(EconModels)
```

I was reading the help page to see what I could figure out about
just what `cesEst()` is doing to compute standard errors.  (That’s 
still not entirely clear to me, but I think it is making use of the 
derivatives of the objective function — the flatter the objective 
function the larger the standard error.)  But I don’t exactly 
understand the details yet.  I know what the scaled and unscaled 
covariance matrices are for a linear model (and cesEst() computes 
the scaled vcov matrix only when it is using a linear model, which 
it can do by fitting a linearised version of the actual 
CES function, but that’s not what we are doing.

Anyway, I’m trying to figure out what to make of this:

```{r}
usdata <- 
  read.csv("../Articles/Brockway_Rebound_2015/data/BrockwayData.csv") %>% filter(Country == "US")
mod <- 
  cesModel(iY ~ iK + iL + iU + iYear, data=usdata, nest=c(1,2,3))
```

## Computation of standard errors

### Degrees of freedom = n

Looks like there is no attempt to adjust degrees of freedom based on the 
number of parameters in the model:

```{r}
smod <- summary(mod)
mod$rss / nrow(usdata)
smod$sigma^2
```

```{r}
diag(mod$cov.unscaled) * smod$sigma^2 
diag(smod$vcov)
```

## Convergence observation
```{r}
mod$nlminb
```

### 2015-09-16 Testing/Elasticity.Rmd
add a document about elasticity trajectories.

---
title: "Triplots and Output Elasticities"
output:
  pdf_document: 
    fig_height: 3
    fig_width: 5
  html_document:
    fig_height: 3
    fig_width: 4
date: "September 16, 2015"
---

```{r include=FALSE}
require(mosaic)
require(EconModels)
require(EconData)
require(knitr)
knitr::opts_chunk$set(fig.show = "hold", cache=TRUE)
```

```{r}
UK <- Leeds %>% filter(Country == "UK")
PT <- IST %>% filter(Country == "PT")

modUK <- cesModel( iGDP ~ iKservO.WwithRD + ihLest + iU + iYear, data = UK)
modPT <- cesModel( iGDP ~ iKservS.L + ihLest + iUMP + iYear, data = PT)
```

```{r} 
model2OE <- function( model ) {
  data <- fortify(model)
  if (! "Country" %in% names(data)) data$Country <- "  "
  data <- data %>% group_by(Country) %>% mutate( start = iYear == min(iYear))

  ggplot() +
    tri_theme() +
    tri_grid() +
    tri_labels(labels = c("k", "l", "e"), parse = TRUE) +
    geom_tripath( 
      data = data, aes(x=oe1, y=oe2, z=oe3),
      alpha=0.6, colour = "black") +
    geom_tripoint( 
      data = data, aes(x=oe1, y=oe2, z=oe3, colour = start, size = start), 
      alpha=0.6) +
    facet_grid( ~ Country)
}
```

## Trajectories of Ouput Elasticities (2 examples)
```{r}
bigData <-
  bind_rows(
    fortify(modUK) %>% mutate(Country = "UK"),
    fortify(modPT) %>% mutate(Country = "PT")
  )
model2OE(bigData) + facet_wrap( ~ Country)

```

## Side note about bug in ggplot2

```{r}
  ggplot() +
    geom_text(
      data = data.frame(x = 0, y = 0, label = "alpha[1]"),
      parse = TRUE,
      aes(x=x, y=y, label=label)
    )

  ggplot() +
    geom_text(
      data = data.frame(x = 0, y = 0),
      parse = TRUE,
      aes(x=x, y=y, label=label),
      label = "alpha[1]"
    ) 
```

### 2015-09-16 Testing/Elasticity.Rmd
different color scheme

@@
   pdf_document: 
-    fig_height: 3
-    fig_width: 5
+    fig_height: 4
+    fig_width: 7
   html_document:
@@
 
-```{r include=FALSE}
+```{r, setup, include=FALSE}
 require(mosaic)
@@
 require(knitr)
-knitr::opts_chunk$set(fig.show = "hold", cache=TRUE)
+knitr::opts_chunk$set(cache=TRUE)
 ```
 
-```{r}
+```{r, models}
 UK <- Leeds %>% filter(Country == "UK")
@@
 
-```{r} 
+```{r, plotfun} 
 model2OE <- function( model ) {
@@
     geom_tripoint( 
-      data = data, aes(x=oe1, y=oe2, z=oe3, colour = start, size = start), 
+      data = data, aes(x=oe1, y=oe2, z=oe3, colour = Year), 
       alpha=0.6) +
+    scale_colour_gradient(low = scales::muted("navy"),  high = "green") +
     facet_grid( ~ Country)
@@
 ## Trajectories of Ouput Elasticities (2 examples)
-```{r}
+```{r, plots}
 bigData <-

### 2015-09-16 Testing/Elasticity.Rmd
work around for ggplot2 "bug" using data_frame()
update labeling

@@
     tri_grid() +
-    tri_labels(labels = c("k", "l", "e"), parse = TRUE) +
+    tri_labels(labels = c("alpha[k]", "alpha[l]", "alpha[e]"), parse = TRUE) +
     geom_tripath( 
@@
 ```
-
-## Side note about bug in ggplot2
-
-```{r}
-  ggplot() +
-    geom_text(
-      data = data.frame(x = 0, y = 0, label = "alpha[1]"),
-      parse = TRUE,
-      aes(x=x, y=y, label=label)
-    )
-
-  ggplot() +
-    geom_text(
-      data = data.frame(x = 0, y = 0),
-      parse = TRUE,
-      aes(x=x, y=y, label=label),
-      label = "alpha[1]"
-    ) 
-```

### 2015-09-17 Testing/Elasticity.Rmd
typo fix

@@
 
-```{r, plotfun} 
+```{r, plotfun, cache=FALSE} 
 model2OE <- function( model ) {
@@
 ## Trajectories of Ouput Elasticities (2 examples)
-```{r, plots}
+```{r, plots, cache = FALSE}
 bigData <-

### 2015-09-17 Testing/Elasticity.Rmd
add comparision with different reindexing

@@
 
+```{r}
+UK2 <- 
+  modUK$data %>%
+  mutate(
+    iGDP = iGDP / tail(iGDP, 1),
+    iKservO.WwithRD = iKservO.WwithRD / tail(iKservO.WwithRD, 1),
+    ihLest = ihLest / tail(ihLest, 1),
+    iU = iU / tail(iU, 1)
+  )
+
+PT2 <- 
+  modPT$data %>%
+  mutate(
+    iGDP = iGDP / tail(iGDP, 1),
+    iKservS.L = iKservS.L / tail(iKservS.L, 1),
+    ihLest = ihLest / tail(ihLest, 1),
+    iUMP = iUMP / tail(iUMP, 1)
+  )
+
+modUK2 <- cesModel( iGDP ~ iKservO.WwithRD + ihLest + iU + iYear, data = UK2)
+modPT2 <- cesModel( iGDP ~ iKservS.L + ihLest + iUMP + iYear, data = PT2)
+```
+
 ```{r, plotfun, cache=FALSE} 
@@
   bind_rows(
-    fortify(modUK) %>% mutate(Country = "UK"),
-    fortify(modPT) %>% mutate(Country = "PT")
+    fortify(modUK) %>% mutate(Country = "UK", reindex = "first"),
+    fortify(modPT) %>% mutate(Country = "PT", reindex = "first"),
+    fortify(modUK2) %>% mutate(Country = "UK", reindex = "last"),
+    fortify(modPT2) %>% mutate(Country = "PT", reindex = "last")
   )
-model2OE(bigData) + facet_wrap( ~ Country)
-
+model2OE(bigData) + facet_grid(reindex ~ Country)
 ```

### 2015-09-17 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
new plots

@@
 
+<<>>=
+leaf_apply(models, function(mod, id) class(mod), class="cesModel")
+@
+
+<<output-elasticity>>=
+mod2oedf <- function(mod, id){
+  # Parse the id to find out whether this is quality-adjusted data, etc.
+  ### Don't name non-lists with variables whose names sound like a list.
+  ### I'm guessing you just didn't know what kind of data you were working with here. 
+  ### Either way, it's a bad thing.
+  id_components <- strsplit(id, split = "[.]")[[1]]
+
+  # return this data frame 
+  ### NOTE: ifelse() and [ ] handle NAs the way we want here
+  ### The former use of [[ ]] was unnecessary and would break things in the new code
+  ### I'm guessing you had [[ ]] because you thought you had a list when you did not.
+
+  ### NOTE: data_frame does not auto-convert to factors.  It leaves things as strings.
+  message(class(mod))
+  if (! inherits(mod, "cesModel") ) return(NULL)
+
+  fortify(mod) %>%
+    mutate(
+      Country = id_components[1], 
+      flavor  = ifelse(id_components[2]=="unadjusted", "Unadjusted", "Quality-adjusted"),
+      energy  = ifelse(id_components[3]=="noE", "Without energy", "With energy"),
+      model   = id_components[4], 
+      nest    = id_components[5]
+    ) 
+}
+
+AllOE <- 
+  leaf_apply(
+    models, 
+    class = "cesModel", 
+    mod2oedf
+  ) %>% 
+  bind_rows()
+@
+
 <<Resampling>>=
@@
 
+<<>>=
+OEplot <- function( data ) {
+  ggplot( data %>% 
+          mutate(
+            slice = interaction(Country, flavor, lex.order=TRUE, sep= " ")
+            )
+          ) +
+    tri_theme() +
+    tri_grid() +
+    tri_labels(labels = c("alpha[k]", "alpha[l]", "alpha[e]"), parse = TRUE) +
+    geom_tripath( 
+      aes(x=oe1, y=oe2, z=oe3, 
+          colour = Year,
+          group=interaction(Country, nest, flavor)),
+      alpha=0.6,  size=1) +
+    geom_tripoint( 
+      aes(x=oe1, y=oe2, z=oe3, colour = Year, size=Year), 
+      alpha=0.7, shape=21)  +
+    scale_colour_gradient(low = scales::muted("navy"),  high = "green") +
+    facet_grid(nest ~ slice) +
+    scale_size_continuous( range = c(1.4, 4))
+}
+OEplot(AllOE) 
+@
+
+<<>>=
+require(tidyr)
+ggplot(AllOE %>% 
+         mutate(split = as.character(
+           interaction(Country, flavor, lex.order = TRUE))) %>%
+         gather(factor, elasticity, oe1, oe2, oe3), aes(x=Year)) +
+  geom_line( 
+    alpha = .5, size=1.8,
+    aes(y = elasticity, 
+        colour = factor, 
+        linetype=flavor
+    ) ) +
+  facet_grid(nest ~ Country) +
+  theme_minimal() 
+@
+
+<<>>=
+ggplot(AllOE %>% mutate(split = interaction(Country, flavor, lex.order=TRUE))) +
+  tri_theme() + 
+  tri_grid() +
+  tri_labels( labels = c("alpha[k]", "alpha[l]", "alpha[e]") ) +
+  geom_tripath(alpha = 0.8, size = 1.2,
+               aes(x = oe1, y = oe2, z = oe3,
+                   colour = Year, group = interaction(Country, nest, flavor)
+               ) ) +
+#  geom_tripoint( size = 1.8, alpha = 0.5,
+#                 aes(x = oe1, y = oe2, z = oe3,
+#                     shape = flavor,
+#                     colour = Year
+#                 ) ) +
+  facet_grid( nest~ split) + 
+  scale_shape_manual(values = c(21:25)) +
+  scale_colour_gradient2(low = scales::muted("navy"), mid="red", high = "green", midpoint = 1985)
+
+@
+
 \end{document}

### 2015-09-18 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
added another plot.

@@
 
+<<>>=
+ggplot(AllOE %>% mutate(split = interaction(Country, flavor, lex.order=TRUE))) +
+  tri_theme() + 
+  tri_grid() +
+  tri_labels( labels = c("alpha[k]", "alpha[l]", "alpha[e]") ) +
+  geom_tripath(alpha = 0.8, size = 1.2,
+               aes(x = oe1, y = oe2, z = oe3,
+                   alpha = Year, 
+                   colour = flavor,
+                   group = interaction(Country, nest, flavor)
+               ) ) +
+  facet_grid( nest~ Country)  +
+  scale_colour_manual(values = c("black", "gray70")) 
+@
+
 \end{document}

### 2015-09-21 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
tweaking output elasticities plots and removing ...TriPlot()

@@
 Perhaps it is easier to see the effect of quality-adjustment of data this way.">>=
-p <- triPlot(
-  data=
+#p <- triPlot(
+#  data=
+p <-
   AllCoeffs %>% filter(model == "CES") %>%
@@
             Inputs = flavor
-            ), 
-  grid_lines = 5,
-  labels = c("alpha[k]", "alpha[l]", "alpha[e]"),
-  aes(x = alpha_1, y = alpha_2, z = alpha_3, 
+            ) %>%
+  ggplot() +
+  tri_theme() +
+  tri_grid(grid_lines = 5) +
+#  tri_labels(labels = c("alpha[k]", "alpha[l]", "alpha[e]")) +
+  geom_tripoint(
+    aes(
+      x = alpha_1, y = alpha_2, z = alpha_3, 
       fill  = Model, 
@@
   facet_grid(. ~ Country)
+
   model_points_style(p)
@@
 This approach is parallel to the previous figures (historical data, fitted GDP, and residuals.">>=
-p <- triPlot(
-  data=
+p <- 
+#    triPlot(
+#  data=
     AllCoeffs %>% filter(model == "CES") %>%
@@
             Model = interaction(nest, CSP, sep = " ", drop=TRUE),
-            Inputs = flavor), 
-  grid_lines = 5,
-  labels = c("alpha[k]", "alpha[l]", "alpha[e]"),
-  aes(x = alpha_1, y = alpha_2, z = alpha_3, 
+            Inputs = flavor) %>%
+    ggplot() +
+    tri_theme() + 
+    tri_grid(grid_lines = 5) +
+    tri_labels(labels = c("alpha[k]", "alpha[l]", "alpha[e]")) +
+    geom_tripoint(
+      aes(
+        x = alpha_1, y = alpha_2, z = alpha_3, 
         fill  = Model, 
@@
 require(tidyr)
-ggplot(AllOE %>% 
-         mutate(split = as.character(
-           interaction(Country, flavor, lex.order = TRUE))) %>%
-         gather(factor, elasticity, oe1, oe2, oe3), aes(x=Year)) +
+AllOE %>% 
+  mutate(split =
+           as.character(
+             interaction(
+               factor(flavor, labels = c("QA", "UA")), 
+               factor(nest, 
+                      labels = c("(ek)l", "kl", "(kl)e", "(le)k")), 
+               sep = ", ",
+               lex.order = FALSE ) )
+  ) %>%
+  gather(factor, elasticity, oe1, oe2, oe3) %>%
+  mutate(
+    split2 = relevelFactor(
+      factor(split), 
+      paste( rep(c("UA", "QA"), times = 4 ), 
+             rep(c("kl", "(kl)e", "(le)k", "(ek)l"), each=2),
+             sep=", ")
+    )
+  ) %>%
+  ggplot(aes(x=Year)) + 
   geom_line( 
-    alpha = .5, size=1.8,
+    alpha = .8, # size=1.0,
     aes(y = elasticity, 
         colour = factor,
-        linetype=flavor
+        linetype=factor,
+        size = factor
     ) ) +
-  facet_grid(nest ~ Country) +
-  theme_minimal() 
+  facet_grid(split2 ~ Country) +
+  scale_color_manual(
+    name = "",
+    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
+    values=c("black", "black", "gray70")
+  ) +
+  scale_x_continuous(breaks = c(1960, 1980, 2000)) +
+  scale_size_manual(
+    name = "",
+    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
+    values = c(.9, .9, .6)) +
+  scale_linetype_manual( 
+    name = "",
+    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
+    values=c(2,3,1) ) + 
+  xy_theme()
+
 @

### 2015-09-22 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
New resampling data.

@@
 rerunResampling=FALSE
-nResamples <- 1000 # Number of resamples
+nResamples <- 10 # Number of resamples
 # ********************************************************
@@
   ### NOTE: data_frame does not auto-convert to factors.  It leaves things as strings.
-  message(class(mod))
+  # message(class(mod))
   if (! inherits(mod, "cesModel") ) return(NULL)
@@
 <<Resampling>>=
-resampleFilename <- "EcolEcon2015kleResamples.rds"
+resampleCoeffsFilename <- "EcolEcon2015kleResampleCoeffs.rds"
+resampleModelsFilename <- "EcolEcon2015kleResampleModels.rds"
 if (rerunResampling){
-  # Run some resampling on the PT and UK models that adhere to the cost-share theorem,
-  # includes energy, uses quality-adjusted variables, and employs the (kl)e nesting.
+  # Run some resampling on the PT and UK models that reject the cost-share theorem,
+  # include energy, use quality-adjusted variables, and employ the (kl)e nesting.
   # This is u-g-l-y code. Just getting something running for now.
@@
   resamplesUK <- resampledFits(modUK, method = "wild", n = nResamples)
+  # Resample coefficients
   resampleCoeffs <- rbind(cbind(resamplesPT$coeffs, Country="PT"), cbind(resamplesUK$coeffs, Country="UK"))
@@
   resampleCoeffs$nest <- "(kl)e"
-  saveRDS(resampleCoeffs, file = resampleFilename)
+  saveRDS(resampleCoeffs, file = resampleCoeffsFilename)
+  # Resample models
+  resampleModels <- list(PT=resamplesPT$models, UK=resamplesUK$models)
+  saveRDS(resampleModels, file = resampleModelsFilename)
 } else {
-  resampleCoeffs <- readRDS(resampleFilename)
+  resampleCoeffs <- readRDS(resampleCoeffsFilename)
+  resampleModels <- readRDS(resampleModelsFilename)
 }

### 2015-09-22 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Change y axis to be more readable.

@@
   scale_x_continuous(breaks = c(1960, 1980, 2000)) +
+  scale_y_continuous(breaks = c(0.0, 0.5, 1.0)) +
   scale_size_manual(

### 2015-09-22 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
plots for resamples;

@@
 }
+
+OEplot2 <- function( data ) {
+  ggplot( data %>% 
+          mutate(
+            slice = interaction(Country, flavor, lex.order=TRUE, sep= " ")
+            )
+          ) +
+    tri_theme() +
+    tri_grid() +
+    tri_labels(labels = c("alpha[k]", "alpha[l]", "alpha[e]"), parse = TRUE) +
+    geom_tripath( 
+      aes(x=oe1, y=oe2, z=oe3, 
+          colour = Year,
+          group=interaction(Country, nest, flavor)),
+      alpha=0.6,  size=1) +
+    scale_colour_gradient(low = scales::muted("navy"),  high = "green") +
+    facet_grid(nest ~ slice) +
+    scale_size_continuous( range = c(1.4, 4))
+}
 OEplot(AllOE) 
+OEplot2(AllOE) 
 @
@@
 
+<<>>=
+ReModels <-
+  bind_rows(
+  leaf_apply(resampleModels, 
+             function(x,id) {mod2oedf(x, id) %>% mutate(id = id)},
+             strict.lists = TRUE)
+)
+
+OEplot(ReModels)
+OEplot2(ReModels)
+@
+
+<<>>=
+ReModels %>% 
+  gather(factor, elasticity, oe1, oe2, oe3) %>%
+  ggplot(aes(x=Year)) + 
+  geom_line( 
+    aes(y = elasticity,
+        alpha = grepl("orig", id),
+        group = interaction(id, factor),
+        color = factor,
+        linetype = factor,
+        size = grepl("orig", id)
+    ) ) +
+  facet_grid(. ~ Country) +
+  scale_alpha_manual(
+    name = "",
+    values = c(.3, 1),
+    guide = FALSE
+  ) + 
+  scale_color_manual(
+    name = "",
+    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
+    values=c("black", "black", "gray70"),
+    guid=FALSE
+  ) +
+  scale_x_continuous(breaks = c(1960, 1980, 2000)) +
+  scale_y_continuous(breaks = c(0.0, 0.5, 1.0)) +
+  scale_size_manual(
+    name = "",
+    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
+    values = c(.3, .9),
+    guide = FALSE) +
+  scale_linetype_manual( 
+    name = "",
+    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
+    values=c(2,3,1) ) + 
+  xy_theme() +
+  labs(x="", y="")
+
+@
+
 \end{document}

### 2015-09-22 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Better graph name.

@@
 
-<<>>=
+<<Graphs_all_models_alphas_time, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap="Output elasticity ($\\alpha$) for all models.">>=
 require(tidyr)

### 2015-09-22 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Eliminating labels from alpha graph.

--- 2015-09-22 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
@@
     values=c(2,3,1) ) + 
+  labs(x="", y="") +
   xy_theme()
-
 @

### 2015-09-22 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Better graph file names.

@@
 
-<<>>=
+<<Graphs_CESkle_resample_alphas, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.2, fig.cap="Resample output elasticities for CES models with $(kl$)$e$ nesting.">>=
 ReModels %>% 
@@
   labs(x="", y="")
-
 @

### 2015-09-22 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Clean up graphs document. Now everthing we use in the paper is in one section. All other stuff is in a graveyard.

@@
 library(scales)
+library(tidyr)
 
@@
 
-<<>>=
-leaf_apply(models, function(mod, id) class(mod), class="cesModel")
-@
+%' <<>>=
+%' leaf_apply(models, function(mod, id) class(mod), class="cesModel")
+%' @
 
@@
 }
+@
+
+<<ReModels>>=
+ReModels <-
+  bind_rows(
+  leaf_apply(resampleModels, 
+             function(x,id) {mod2oedf(x, id) %>% mutate(id = id)},
+             strict.lists = TRUE)
+)
 @
@@
          digits=c(1,1,1,1,1,1,1, 2, 4, 3))
-@
-
-Table~\ref{tab:CES_alpha} shows 
-output elasticities~($\alpha$) for all modeling choices.
-
-<<CES_alpha, results="asis">>=
-data_CES_alpha <- 
-  table_data %>% 
-  filter(Model=="CES" | Model=="Ref.") %>% 
-  select(Country, Model, CSP, flavor, Energy, Nest, alpha_1, alpha_2, alpha_3) %>%
-  plyr::rename(c("flavor" = "Factors of prod.",
-                 "alpha_1" = "$\\alpha_k$",
-                 "alpha_2" = "$\\alpha_l$",
-                 "alpha_3" = "$\\alpha_e$"))
-myXTable(data_CES_alpha,
-         caption="Output elasticities~($\\alpha$) for all models.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=3)
 @
@@
 
-<<SRsse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Solow Residuals~($\\lambda$) and mean squared error~($sse$).
-$\\lambda$ and $sse$ values for the reference (exponential-only) model are shown as gridlines.">>=
-data_sr_sse <- 
-  AllCoeffs %>% 
-  filter(model=="CES") %>% 
-  mutate(nest = 
-           plyr::mapvalues(
-             nest, 
-             from=c("kl", "kle", "lek", "ekl"), 
-             to=c("kl", "(kl)e", "(le)k", "(ek)l")
-             ),
-         Model = interaction(nest, CSP, sep = " ", drop=TRUE),
-         Inputs = flavor
-  )
-ggplot() +
-  geom_point(data=data_sr_sse, mapping=aes(x=sse, y=lambda, color=energy, size=CSP, shape=nest)) +
-  geom_vline(aes(xintercept = sse), 
-             AllCoeffs %>% filter(model=="exp") %>% select(Country, sse), 
-             colour="gray50", size=0.1) +
-  geom_hline(aes(yintercept = lambda), 
-             AllCoeffs %>% filter(model=="exp") %>% select(Country, lambda), 
-             colour="gray50", size=0.1) +
-  scale_size_manual(values=c(2,4)) +
-  scale_shape_manual(values=c(1,0,3,4)) + 
-  facet_grid(flavor ~ Country) +
-  scale_y_continuous(breaks=c(0, 0.01, 0.02, 0.03), limits=c(0, 0.035)) +
-  xlab("SSE") + 
-  ylab(expression(lambda)) +
-  xy_theme() +
-  theme(legend.title=element_blank())
-
-@
-
-<<SRsse_CES_graph_2, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=2.5, fig.cap="Solow Residuals~($\\lambda$) and mean squared error~($sse$).
-$\\lambda$ and $sse$ values for the reference (exponential-only) model are shown as gridlines.
-This version uses our proposed new style.">>=
-data_sr_sse <- 
-  AllCoeffs %>% 
-  filter(model=="CES") %>% 
-  mutate(nest = 
-           plyr::mapvalues(
-             nest, 
-             from=c("kl", "kle", "lek", "ekl"), 
-             to=c("kl", "(kl)e", "(le)k", "(ek)l")
-             ),
-         Model = interaction(nest, CSP, sep = " ", drop=TRUE),
-         Inputs = flavor
-  )
-
-p <- ggplot() +
-  geom_point(
-    data=data_sr_sse, 
-    mapping=aes(
-      x=lambda, 
-      y=sse, 
-      fill=Model, 
-      shape=Model, 
-      size=Model, 
-      color=Inputs
-      )) +
-  geom_vline(aes(xintercept = lambda), 
-             AllCoeffs %>% filter(model=="exp") %>% select(Country, lambda), 
-             colour="gray50", size=0.1) +
-  geom_hline(aes(yintercept = sse), 
-             AllCoeffs %>% filter(model=="exp") %>% select(Country, sse), 
-             colour="gray50", size=0.1) +
-  facet_grid(. ~ Country) +
-  scale_x_continuous(breaks=c(0, 0.01, 0.02, 0.03), limits=c(0, 0.035)) +
-  xlab(expression(lambda)) +
-  scale_y_continuous(limits=c(-0.05, 0.7)) +
-  ylab("SSE") + 
-  labs(color = "Factors of production") +
-  xy_theme() # +
-  # theme(legend.title=element_blank())
-
-# Add our style
-model_points_style(p)
-
-@
-
 <<SRsse_CES_graph_3, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Solow Residuals~($\\lambda$) and mean squared error~($sse$).
@@
 
-Figures~\ref{fig:Factor_shares_graph_PT} and~\ref{fig:Factor_shares_graph_UK}
-show factor shares ($\alpha$ values) for CES models for
-Portugal and the UK, respectively.
-See Table~\ref{tab:CES_abg_equations} for details on the calculation
-of factor shares from fitted values of $\delta_1$ and $\delta$.
-%
-<<Factor_shares_bar_graph_function>>=
-fsbg <- function(coun, mod){
-  bar_chart_data <- 
-    AllCoeffs %>% 
-    filter(Country==coun & model==mod) %>% 
-    select(Country, model, flavor, energy, nest, CSP, alpha_1, alpha_2, alpha_3) %>%
-    mutate(nest =   # Change nest to a nicer-looking nest string
-             plyr::mapvalues(nest, 
-                             from=c("kl", "kle", "lek", "ekl"), 
-                             to=c("kl", "(kl)e", "(le)k", "(ek)l")),
-           label = # Add a label column
-              paste(CSP, flavor, energy, nest, sep=", "),
-           label =  # Add row numbers to the label column
-              paste(paste0(1:length(label), ". "), label)
-    )
-  # Capture the order that we want for the models on the vertical axis.
-  order <- bar_chart_data$label
-  # Now melt the data
-  ### tidyr::spread and tidyr::gather are preferred in most cases now
-#   bar_chart_data <- melt(bar_chart_data, 
-#                          measure.vars = c("alpha_1", "alpha_2", "alpha_3"), 
-#                          value.name = "value", 
-#                          variable.name = "variable")
-  bar_chart_data <-
-    bar_chart_data %>% gather( key=variable, value=value, alpha_1 : alpha_3 )
-
-  # Make the plot
-  plot <- ggplot(bar_chart_data, mapping=aes(x=label, y=value, fill=variable, width=0.4)) + 
-    geom_bar(stat="identity") + 
-    xlab("") +
-    scale_x_discrete(limits=rev(order)) +
-    ylab("") +
-    scale_y_continuous(breaks=c(0, 0.5, 1)) + 
-    guides(fill=guide_legend(title=NULL)) +
-    coord_flip() + 
-    scale_fill_brewer(palette="OrRd", 
-                      labels=c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e]))) +
-    xy_theme() +
-    theme(axis.ticks.y = element_blank())
-  return(plot)
-}
-@
-
-<<Factor_shares_graph_PT, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=2.5, fig.cap="Factor shares ($\\alpha$ values) for CES models for Portugal.">>=
-fsbg(coun = "PT", mod = "CES")
-@
-
-<<Factor_shares_graph_UK, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=2.5, fig.cap="Factor shares ($\\alpha$ values) for CES models for the UK.">>=
-fsbg(coun = "UK", mod = "CES")
-@
-
-<<output_elasticities_graph_ternary, fig.pos="H", fig.align="center", fig.width=6.5, fig.height=2.3, fig.cap="Ternary graph of output elasticities~($\\alpha$).
-This version shows all Unadjusted and Quality-adjusted points on the same graph.
-Perhaps it is easier to see the effect of quality-adjustment of data this way.">>=
-#p <- triPlot(
-#  data=
-p <-
-  AllCoeffs %>% filter(model == "CES") %>%
-    mutate( nest = plyr::mapvalues(nest, 
-                                   from=c("kle", "lek", "ekl"), 
-                                   to=c("(kl)e", "(le)k", "(ek)l")),
-            Model = interaction(nest, CSP, sep = " ", drop=TRUE),
-            Inputs = flavor
+<<Graphs_all_models_alphas_time, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap="Output elasticity ($\\alpha$) for all models.">>=
+AllOE %>% 
+  mutate(split =
+           as.character(
+             interaction(
+               factor(flavor, labels = c("QA", "UA")), 
+               factor(nest, 
+                      labels = c("(ek)l", "kl", "(kl)e", "(le)k")), 
+               sep = ", ",
+               lex.order = FALSE ) )
   ) %>%
-  ggplot() +
-  tri_theme() +
-  tri_grid(grid_lines = 5) +
-#  tri_labels(labels = c("alpha[k]", "alpha[l]", "alpha[e]")) +
-  geom_tripoint(
-    aes(
-      x = alpha_1, y = alpha_2, z = alpha_3, 
-      fill  = Model, 
-      shape = Model,
-      size = Model,
-      color = Inputs)
+  gather(factor, elasticity, oe1, oe2, oe3) %>%
+  mutate(
+    split2 = relevelFactor(
+      factor(split), 
+      paste( rep(c("UA", "QA"), times = 4 ), 
+             rep(c("kl", "(kl)e", "(le)k", "(ek)l"), each=2),
+             sep=", ")
+    )
+  ) %>%
+  ggplot(aes(x=Year)) + 
+  geom_line( 
+    alpha = .8, # size=1.0,
+    aes(y = elasticity, 
+        colour = factor,
+        linetype=factor,
+        size = factor
+    ) ) +
+  facet_grid(split2 ~ Country) +
+  scale_color_manual(
+    name = "",
+    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
+    values=c("black", "black", "gray70")
   ) +
-  labs(color = "Factors of production") +
-  facet_grid(. ~ Country)
-
-  model_points_style(p)
-@
-
-<<output_elasticities_graph_ternary_2, fig.pos="H", fig.align="center", fig.width=6.5, fig.height=4.1, fig.cap="Ternary graph of output elasticities~($\\alpha$).
-This version splits the Unadjusted and Quality-adjusted values on their own graphs.
-This approach is parallel to the previous figures (historical data, fitted GDP, and residuals.">>=
-p <- 
-#    triPlot(
-#  data=
-    AllCoeffs %>% filter(model == "CES") %>%
-    mutate( nest = plyr::mapvalues(nest, 
-                                   from=c("kle", "lek", "ekl"), 
-                                   to=c("(kl)e", "(le)k", "(ek)l")),
-            Model = interaction(nest, CSP, sep = " ", drop=TRUE),
-            Inputs = flavor) %>%
-    ggplot() +
-    tri_theme() + 
-    tri_grid(grid_lines = 5) +
-    tri_labels(labels = c("alpha[k]", "alpha[l]", "alpha[e]")) +
-    geom_tripoint(
-      aes(
-        x = alpha_1, y = alpha_2, z = alpha_3, 
-        fill  = Model, 
-        shape = Model,
-        size = Model
-      # color = Inputs
-      )
-  ) +
-  facet_grid(Inputs ~ Country)
-
-  model_points_style_quad(p)
+  scale_x_continuous(breaks = c(1960, 1980, 2000)) +
+  scale_y_continuous(breaks = c(0.0, 0.5, 1.0)) +
+  scale_size_manual(
+    name = "",
+    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
+    values = c(.9, .9, .6)) +
+  scale_linetype_manual( 
+    name = "",
+    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
+    values=c(2,3,1) ) + 
+  labs(x="", y="") +
+  xy_theme()
 @
@@
 %++++++++++++++++++++++++++++++
-
-<<sigma_graph>>=
-sigma_graph <- function(data){
-  sigma_graph_data <- 
-    data %>% 
-    select(Country, CSP, flavor, energy, nest, 
-           sigma_12, sigma_23, sigma_13, 
-           sigma_12_3, sigma_23_1, sigma_13_2) %>%
-    mutate(nest = plyr::mapvalues( # Change nest to a nicer-looking nest string
-      nest, 
-      from=c("kl", "kle", "lek", "ekl"), 
-      to=c("kl", "(kl)e", "(le)k", "(ek)l"))
-    ) %>%
-    gather(variable, value, sigma_12, sigma_23, sigma_13, sigma_12_3, sigma_23_1, sigma_13_2) %>%
-    mutate(label = paste(CSP, flavor, energy, nest, variable, sep=", ")) %>%
-    na.omit()
-
-  # return(sigma_graph_data)
-
-  # Make the plot
-  plot <- ggplot(sigma_graph_data, mapping=aes(x=label, y=value, fill=variable, width=0.4)) + 
-    geom_bar(stat="identity") + 
-    xlab("") +
-    # scale_x_discrete(limits=rev(order)) +
-    scale_x_discrete(labels=sigma_graph_data$label) +
-    geom_hline(aes(yintercept = 1), colour="gray50", size=0.1) +
-    ylab("") +
-    # coord_trans(y="sigma") +
-    scale_y_continuous(limits=c(0, 10), breaks=c(0, 1.0, 10)) +
-    guides(fill=guide_legend(title=NULL)) +
-    scale_fill_brewer(palette="OrRd") +
-#     scale_fill_brewer(palette="OrRd",
-#                       labels=c(expression(sigma[kl]), 
-#                                expression(sigma[le]), 
-#                                expression(sigma[ek]),
-#                                expression(sigma["(kl)e"]),
-#                                expression(sigma["(le)k"]),
-#                                expression(sigma["(ek)l"]))) +
-    coord_flip() + 
-    xy_theme() +
-    theme(axis.ticks.y = element_blank())
-  return(plot)
-}
-@
-
-<<sigma_graph_PT, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for Portugal.">>=
-sigma_graph(AllCoeffs %>% filter(model=="CES", Country=="PT"))
-@
-
-<<sigma_graph_UK, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for the UK.">>=
-sigma_graph(AllCoeffs %>% filter(model=="CES", Country=="UK"))
-@
-
-<<sigma_graph_2, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.82, fig.cap="Elasticities of substitution~($\\sigma$).">>=
-breaks_labels = c(0.01, 0.1, 1, 10, 100)
-p <- 
-ggplot(
-  AllCoeffs %>% 
-    gather(type, value, matches("sigma")) %>% 
-    filter(!is.na(value)) %>% 
-    filter(! type %in% c("sigma", "sigma_1")) %>%
-    mutate(nest = plyr::mapvalues(nest, 
-                                  from=c("kle", "lek", "ekl"), 
-                                  to=c("(kl)e", "(le)k", "(ek)l")),
-           type = relevelFactor(type, c("sigma_12", "sigma_23", "sigma_13", "sigma_12_3", "sigma_23_1", "sigma_13_2")),
-           Model = interaction(nest, CSP, sep = " ", drop=TRUE),
-           Inputs = flavor
-           )
-  ) + 
-  geom_point(aes(x=value, y=type, 
-                 shape = Model, fill=Model, size=Model,
-                 color=Inputs
-                 )
-                 # position = position_jitter(height=0.2, width=0)
-             ) + 
-  facet_grid( type ~ Country, scales = "free_y" ) + 
-  scale_x_log10(limits = c(0.001,2000), breaks=breaks_labels, labels=breaks_labels) +
-  xlab("") +
-  geom_vline(xintercept = 1, color="gray50", size=0.2) +
-  scale_y_discrete(labels = c(
-    sigma_12 = expression(sigma[kl]),
-    sigma_23 = expression(sigma[le]),
-    sigma_13 = expression(sigma[ek]),
-    sigma_12_3 = expression(sigma["(kl)"*e]),
-    sigma_23_1 = expression(sigma["(le)"*k]),
-    sigma_13_2 = expression(sigma["(ek)"*l]))
-    ) +
-  ylab("") +
-  labs(color = "Factors of production") +
-  xy_theme() +
-  theme(
-    legend.position="top",
-    strip.text.y = element_blank(),
-    axis.text.y = element_text(size=12)
-    )
-
-model_points_style(p)
-@
 
@@
 
-<<resample_graph_alpha, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.0, fig.cap="$\\alpha_k$, $\\alpha_l$, and $\\alpha_e$ values for CES resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
-standardTriPlot(data=resampleCoeffs, facet_formula=~Country, alpha=0.1,
-                labels=c("alpha[k]", "alpha[l]", "alpha[e]"), size=2.0)
+<<Graphs_CESkle_resample_alphas, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.2, fig.cap="Resample output elasticities for CES models with $(kl$)$e$ nesting.">>=
+ReModels %>% 
+  gather(factor, elasticity, oe1, oe2, oe3) %>%
+  ggplot(aes(x=Year)) + 
+  geom_line( 
+    aes(y = elasticity,
+        alpha = grepl("orig", id),
+        group = interaction(id, factor),
+        color = factor,
+        linetype = factor,
+        size = grepl("orig", id)
+    ) ) +
+  facet_grid(. ~ Country) +
+  scale_alpha_manual(
+    name = "",
+    values = c(.3, 1),
+    guide = FALSE
+  ) + 
+  scale_color_manual(
+    name = "",
+    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
+    values=c("black", "black", "gray70"),
+    guid=FALSE
+  ) +
+  scale_x_continuous(breaks = c(1960, 1980, 2000)) +
+  scale_y_continuous(breaks = c(0.0, 0.5, 1.0)) +
+  scale_size_manual(
+    name = "",
+    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
+    values = c(.3, .9),
+    guide = FALSE) +
+  scale_linetype_manual( 
+    name = "",
+    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
+    values=c(2,3,1) ) + 
+  xy_theme() +
+  labs(x="", y="")
 @
@@
 
-<<Correlograms_Exp, echo=FALSE, message=FALSE, include=FALSE>>=
+<<Correlograms_Exp, echo=FALSE, message=FALSE, include=FALSE, eval=FALSE>>=
 leaf_apply(l = modelsExp, class = c("lm"), f = function(model, name){
@@
 
-<<Correlograms_CSP, echo=FALSE, message=FALSE, include=FALSE>>=
+<<Correlograms_CSP, echo=FALSE, message=FALSE, include=FALSE, eval=FALSE>>=
 leaf_apply(l = modelsCSP, class = c("lm", "plm"), f = function(model, name){
@@
 
-<<Correlograms_noCSP, echo=FALSE, message=FALSE, include=FALSE>>=
+<<Correlograms_noCSP, echo=FALSE, message=FALSE, include=FALSE, eval=FALSE>>=
 leaf_apply(l = models, class = c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, name){
@@
 
+Table~\ref{tab:CES_alpha} shows 
+output elasticities~($\alpha$) for all modeling choices.
+
+Here is a table of $\alpha$ values. 
+These values represent the initial points of the trajectories. 
+We no longer use these values. 
+Instead, we use the time-dependent values of alpha.
+So, this table goes in the graveyard.
+
+<<CES_alpha, results="asis">>=
+data_CES_alpha <- 
+  table_data %>% 
+  filter(Model=="CES" | Model=="Ref.") %>% 
+  select(Country, Model, CSP, flavor, Energy, Nest, alpha_1, alpha_2, alpha_3) %>%
+  plyr::rename(c("flavor" = "Factors of prod.",
+                 "alpha_1" = "$\\alpha_k$",
+                 "alpha_2" = "$\\alpha_l$",
+                 "alpha_3" = "$\\alpha_e$"))
+myXTable(data_CES_alpha,
+         caption="Output elasticities~($\\alpha$) for all models.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=3)
+@
+
 Here is a table of the raw CES coefficient values. 
@@
 
+<<SRsse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Solow Residuals~($\\lambda$) and mean squared error~($sse$).
+$\\lambda$ and $sse$ values for the reference (exponential-only) model are shown as gridlines.">>=
+data_sr_sse <- 
+  AllCoeffs %>% 
+  filter(model=="CES") %>% 
+  mutate(nest = 
+           plyr::mapvalues(
+             nest, 
+             from=c("kl", "kle", "lek", "ekl"), 
+             to=c("kl", "(kl)e", "(le)k", "(ek)l")
+             ),
+         Model = interaction(nest, CSP, sep = " ", drop=TRUE),
+         Inputs = flavor
+  )
+ggplot() +
+  geom_point(data=data_sr_sse, mapping=aes(x=sse, y=lambda, color=energy, size=CSP, shape=nest)) +
+  geom_vline(aes(xintercept = sse), 
+             AllCoeffs %>% filter(model=="exp") %>% select(Country, sse), 
+             colour="gray50", size=0.1) +
+  geom_hline(aes(yintercept = lambda), 
+             AllCoeffs %>% filter(model=="exp") %>% select(Country, lambda), 
+             colour="gray50", size=0.1) +
+  scale_size_manual(values=c(2,4)) +
+  scale_shape_manual(values=c(1,0,3,4)) + 
+  facet_grid(flavor ~ Country) +
+  scale_y_continuous(breaks=c(0, 0.01, 0.02, 0.03), limits=c(0, 0.035)) +
+  xlab("SSE") + 
+  ylab(expression(lambda)) +
+  xy_theme() +
+  theme(legend.title=element_blank())
+
+@
+
+<<SRsse_CES_graph_2, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=2.5, fig.cap="Solow Residuals~($\\lambda$) and mean squared error~($sse$).
+$\\lambda$ and $sse$ values for the reference (exponential-only) model are shown as gridlines.
+This version uses our proposed new style.">>=
+data_sr_sse <- 
+  AllCoeffs %>% 
+  filter(model=="CES") %>% 
+  mutate(nest = 
+           plyr::mapvalues(
+             nest, 
+             from=c("kl", "kle", "lek", "ekl"), 
+             to=c("kl", "(kl)e", "(le)k", "(ek)l")
+             ),
+         Model = interaction(nest, CSP, sep = " ", drop=TRUE),
+         Inputs = flavor
+  )
+
+p <- ggplot() +
+  geom_point(
+    data=data_sr_sse, 
+    mapping=aes(
+      x=lambda, 
+      y=sse, 
+      fill=Model, 
+      shape=Model, 
+      size=Model, 
+      color=Inputs
+      )) +
+  geom_vline(aes(xintercept = lambda), 
+             AllCoeffs %>% filter(model=="exp") %>% select(Country, lambda), 
+             colour="gray50", size=0.1) +
+  geom_hline(aes(yintercept = sse), 
+             AllCoeffs %>% filter(model=="exp") %>% select(Country, sse), 
+             colour="gray50", size=0.1) +
+  facet_grid(. ~ Country) +
+  scale_x_continuous(breaks=c(0, 0.01, 0.02, 0.03), limits=c(0, 0.035)) +
+  xlab(expression(lambda)) +
+  scale_y_continuous(limits=c(-0.05, 0.7)) +
+  ylab("SSE") + 
+  labs(color = "Factors of production") +
+  xy_theme() # +
+  # theme(legend.title=element_blank())
+
+# Add our style
+model_points_style(p)
+
+@
+
+Figures~\ref{fig:Factor_shares_graph_PT} and~\ref{fig:Factor_shares_graph_UK}
+show factor shares ($\alpha$ values) for CES models for
+Portugal and the UK, respectively.
+See Table~\ref{tab:CES_abg_equations} for details on the calculation
+of factor shares from fitted values of $\delta_1$ and $\delta$.
+%
+<<Factor_shares_bar_graph_function>>=
+fsbg <- function(coun, mod){
+  bar_chart_data <- 
+    AllCoeffs %>% 
+    filter(Country==coun & model==mod) %>% 
+    select(Country, model, flavor, energy, nest, CSP, alpha_1, alpha_2, alpha_3) %>%
+    mutate(nest =   # Change nest to a nicer-looking nest string
+             plyr::mapvalues(nest, 
+                             from=c("kl", "kle", "lek", "ekl"), 
+                             to=c("kl", "(kl)e", "(le)k", "(ek)l")),
+           label = # Add a label column
+              paste(CSP, flavor, energy, nest, sep=", "),
+           label =  # Add row numbers to the label column
+              paste(paste0(1:length(label), ". "), label)
+    )
+  # Capture the order that we want for the models on the vertical axis.
+  order <- bar_chart_data$label
+  # Now melt the data
+  ### tidyr::spread and tidyr::gather are preferred in most cases now
+#   bar_chart_data <- melt(bar_chart_data, 
+#                          measure.vars = c("alpha_1", "alpha_2", "alpha_3"), 
+#                          value.name = "value", 
+#                          variable.name = "variable")
+  bar_chart_data <-
+    bar_chart_data %>% gather( key=variable, value=value, alpha_1 : alpha_3 )
+
+  # Make the plot
+  plot <- ggplot(bar_chart_data, mapping=aes(x=label, y=value, fill=variable, width=0.4)) + 
+    geom_bar(stat="identity") + 
+    xlab("") +
+    scale_x_discrete(limits=rev(order)) +
+    ylab("") +
+    scale_y_continuous(breaks=c(0, 0.5, 1)) + 
+    guides(fill=guide_legend(title=NULL)) +
+    coord_flip() + 
+    scale_fill_brewer(palette="OrRd", 
+                      labels=c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e]))) +
+    xy_theme() +
+    theme(axis.ticks.y = element_blank())
+  return(plot)
+}
+@
+
+<<Factor_shares_graph_PT, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=2.5, fig.cap="Factor shares ($\\alpha$ values) for CES models for Portugal.">>=
+fsbg(coun = "PT", mod = "CES")
+@
+
+<<Factor_shares_graph_UK, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=2.5, fig.cap="Factor shares ($\\alpha$ values) for CES models for the UK.">>=
+fsbg(coun = "UK", mod = "CES")
+@
+
+<<output_elasticities_graph_ternary, fig.pos="H", fig.align="center", fig.width=6.5, fig.height=2.3, fig.cap="Ternary graph of output elasticities~($\\alpha$).
+This version shows all Unadjusted and Quality-adjusted points on the same graph.
+Perhaps it is easier to see the effect of quality-adjustment of data this way.">>=
+#p <- triPlot(
+#  data=
+p <-
+  AllCoeffs %>% filter(model == "CES") %>%
+    mutate( nest = plyr::mapvalues(nest, 
+                                   from=c("kle", "lek", "ekl"), 
+                                   to=c("(kl)e", "(le)k", "(ek)l")),
+            Model = interaction(nest, CSP, sep = " ", drop=TRUE),
+            Inputs = flavor
+            ) %>%
+  ggplot() +
+  tri_theme() +
+  tri_grid(grid_lines = 5) +
+#  tri_labels(labels = c("alpha[k]", "alpha[l]", "alpha[e]")) +
+  geom_tripoint(
+    aes(
+      x = alpha_1, y = alpha_2, z = alpha_3, 
+      fill  = Model, 
+      shape = Model,
+      size = Model,
+      color = Inputs)
+  ) +
+  labs(color = "Factors of production") +
+  facet_grid(. ~ Country)
+
+  model_points_style(p)
+@
+
+<<output_elasticities_graph_ternary_2, fig.pos="H", fig.align="center", fig.width=6.5, fig.height=4.1, fig.cap="Ternary graph of output elasticities~($\\alpha$).
+This version splits the Unadjusted and Quality-adjusted values on their own graphs.
+This approach is parallel to the previous figures (historical data, fitted GDP, and residuals.">>=
+p <- 
+#    triPlot(
+#  data=
+    AllCoeffs %>% filter(model == "CES") %>%
+    mutate( nest = plyr::mapvalues(nest, 
+                                   from=c("kle", "lek", "ekl"), 
+                                   to=c("(kl)e", "(le)k", "(ek)l")),
+            Model = interaction(nest, CSP, sep = " ", drop=TRUE),
+            Inputs = flavor) %>%
+    ggplot() +
+    tri_theme() + 
+    tri_grid(grid_lines = 5) +
+    tri_labels(labels = c("alpha[k]", "alpha[l]", "alpha[e]")) +
+    geom_tripoint(
+      aes(
+        x = alpha_1, y = alpha_2, z = alpha_3, 
+        fill  = Model, 
+        shape = Model,
+        size = Model
+      # color = Inputs
+      )
+  ) +
+  facet_grid(Inputs ~ Country)
+
+  model_points_style_quad(p)
+@
+
 <<>>=
@@
 OEplot2(AllOE) 
-@
-
-<<Graphs_all_models_alphas_time, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap="Output elasticity ($\\alpha$) for all models.">>=
-require(tidyr)
-AllOE %>% 
-  mutate(split =
-           as.character(
-             interaction(
-               factor(flavor, labels = c("QA", "UA")), 
-               factor(nest, 
-                      labels = c("(ek)l", "kl", "(kl)e", "(le)k")), 
-               sep = ", ",
-               lex.order = FALSE ) )
-  ) %>%
-  gather(factor, elasticity, oe1, oe2, oe3) %>%
-  mutate(
-    split2 = relevelFactor(
-      factor(split), 
-      paste( rep(c("UA", "QA"), times = 4 ), 
-             rep(c("kl", "(kl)e", "(le)k", "(ek)l"), each=2),
-             sep=", ")
-    )
-  ) %>%
-  ggplot(aes(x=Year)) + 
-  geom_line( 
-    alpha = .8, # size=1.0,
-    aes(y = elasticity, 
-        colour = factor,
-        linetype=factor,
-        size = factor
-    ) ) +
-  facet_grid(split2 ~ Country) +
-  scale_color_manual(
-    name = "",
-    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
-    values=c("black", "black", "gray70")
-  ) +
-  scale_x_continuous(breaks = c(1960, 1980, 2000)) +
-  scale_y_continuous(breaks = c(0.0, 0.5, 1.0)) +
-  scale_size_manual(
-    name = "",
-    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
-    values = c(.9, .9, .6)) +
-  scale_linetype_manual( 
-    name = "",
-    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
-    values=c(2,3,1) ) + 
-  labs(x="", y="") +
-  xy_theme()
 @
@@
 <<>>=
-ReModels <-
-  bind_rows(
-  leaf_apply(resampleModels, 
-             function(x,id) {mod2oedf(x, id) %>% mutate(id = id)},
-             strict.lists = TRUE)
-)
 
@@
 
-<<Graphs_CESkle_resample_alphas, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.2, fig.cap="Resample output elasticities for CES models with $(kl$)$e$ nesting.">>=
-ReModels %>% 
-  gather(factor, elasticity, oe1, oe2, oe3) %>%
-  ggplot(aes(x=Year)) + 
-  geom_line( 
-    aes(y = elasticity,
-        alpha = grepl("orig", id),
-        group = interaction(id, factor),
-        color = factor,
-        linetype = factor,
-        size = grepl("orig", id)
-    ) ) +
-  facet_grid(. ~ Country) +
-  scale_alpha_manual(
-    name = "",
-    values = c(.3, 1),
-    guide = FALSE
+<<resample_graph_alpha, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.0, fig.cap="$\\alpha_k$, $\\alpha_l$, and $\\alpha_e$ values for CES resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
+standardTriPlot(data=resampleCoeffs, facet_formula=~Country, alpha=0.1,
+                labels=c("alpha[k]", "alpha[l]", "alpha[e]"), size=2.0)
+@
+
+<<sigma_graph>>=
+sigma_graph <- function(data){
+  sigma_graph_data <- 
+    data %>% 
+    select(Country, CSP, flavor, energy, nest, 
+           sigma_12, sigma_23, sigma_13, 
+           sigma_12_3, sigma_23_1, sigma_13_2) %>%
+    mutate(nest = plyr::mapvalues( # Change nest to a nicer-looking nest string
+      nest, 
+      from=c("kl", "kle", "lek", "ekl"), 
+      to=c("kl", "(kl)e", "(le)k", "(ek)l"))
+    ) %>%
+    gather(variable, value, sigma_12, sigma_23, sigma_13, sigma_12_3, sigma_23_1, sigma_13_2) %>%
+    mutate(label = paste(CSP, flavor, energy, nest, variable, sep=", ")) %>%
+    na.omit()
+
+  # return(sigma_graph_data)
+
+  # Make the plot
+  plot <- ggplot(sigma_graph_data, mapping=aes(x=label, y=value, fill=variable, width=0.4)) + 
+    geom_bar(stat="identity") + 
+    xlab("") +
+    # scale_x_discrete(limits=rev(order)) +
+    scale_x_discrete(labels=sigma_graph_data$label) +
+    geom_hline(aes(yintercept = 1), colour="gray50", size=0.1) +
+    ylab("") +
+    # coord_trans(y="sigma") +
+    scale_y_continuous(limits=c(0, 10), breaks=c(0, 1.0, 10)) +
+    guides(fill=guide_legend(title=NULL)) +
+    scale_fill_brewer(palette="OrRd") +
+#     scale_fill_brewer(palette="OrRd",
+#                       labels=c(expression(sigma[kl]), 
+#                                expression(sigma[le]), 
+#                                expression(sigma[ek]),
+#                                expression(sigma["(kl)e"]),
+#                                expression(sigma["(le)k"]),
+#                                expression(sigma["(ek)l"]))) +
+    coord_flip() + 
+    xy_theme() +
+    theme(axis.ticks.y = element_blank())
+  return(plot)
+}
+@
+
+<<sigma_graph_PT, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for Portugal.">>=
+sigma_graph(AllCoeffs %>% filter(model=="CES", Country=="PT"))
+@
+
+<<sigma_graph_UK, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for the UK.">>=
+sigma_graph(AllCoeffs %>% filter(model=="CES", Country=="UK"))
+@
+
+<<sigma_graph_2, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.82, fig.cap="Elasticities of substitution~($\\sigma$).">>=
+breaks_labels = c(0.01, 0.1, 1, 10, 100)
+p <- 
+ggplot(
+  AllCoeffs %>% 
+    gather(type, value, matches("sigma")) %>% 
+    filter(!is.na(value)) %>% 
+    filter(! type %in% c("sigma", "sigma_1")) %>%
+    mutate(nest = plyr::mapvalues(nest, 
+                                  from=c("kle", "lek", "ekl"), 
+                                  to=c("(kl)e", "(le)k", "(ek)l")),
+           type = relevelFactor(type, c("sigma_12", "sigma_23", "sigma_13", "sigma_12_3", "sigma_23_1", "sigma_13_2")),
+           Model = interaction(nest, CSP, sep = " ", drop=TRUE),
+           Inputs = flavor
+           )
   ) + 
-  scale_color_manual(
-    name = "",
-    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
-    values=c("black", "black", "gray70"),
-    guid=FALSE
+  geom_point(aes(x=value, y=type, 
+                 shape = Model, fill=Model, size=Model,
+                 color=Inputs
+                 )
+                 # position = position_jitter(height=0.2, width=0)
              ) + 
-  scale_x_continuous(breaks = c(1960, 1980, 2000)) +
-  scale_y_continuous(breaks = c(0.0, 0.5, 1.0)) +
-  scale_size_manual(
-    name = "",
-    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
-    values = c(.3, .9),
-    guide = FALSE) +
-  scale_linetype_manual( 
-    name = "",
-    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
-    values=c(2,3,1) ) + 
+  facet_grid( type ~ Country, scales = "free_y" ) + 
+  scale_x_log10(limits = c(0.001,2000), breaks=breaks_labels, labels=breaks_labels) +
+  xlab("") +
+  geom_vline(xintercept = 1, color="gray50", size=0.2) +
+  scale_y_discrete(labels = c(
+    sigma_12 = expression(sigma[kl]),
+    sigma_23 = expression(sigma[le]),
+    sigma_13 = expression(sigma[ek]),
+    sigma_12_3 = expression(sigma["(kl)"*e]),
+    sigma_23_1 = expression(sigma["(le)"*k]),
+    sigma_13_2 = expression(sigma["(ek)"*l]))
+    ) +
+  ylab("") +
+  labs(color = "Factors of production") +
   xy_theme() +
-  labs(x="", y="")
+  theme(
+    legend.position="top",
+    strip.text.y = element_blank(),
+    axis.text.y = element_text(size=12)
+    )
+
+model_points_style(p)
 @

### 2015-09-22 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Fixed misspelling.

@@
     values=c("black", "black", "gray70"),
-    guid=FALSE
+    guide=FALSE
   ) +

### 2015-09-23 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Now includes n=100 resample models.

@@
 rerunResampling=FALSE
-nResamples <- 10 # Number of resamples
+nResamples <- 100 # Number of resamples
 # ********************************************************

### 2015-09-23 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Deleted unused function.

@@
 
-# residualPlot <- function(data, withEnergyShape = 0){
-#   ggplot() +
-#     geom_point(data=data, mapping=aes(x=Year, y=Residuals, shape=energy, color=energy, size=energy)) +
-#     scale_shape_manual(values=c(1, withEnergyShape)) +
-#     scale_size_manual(values=c(4,4)) +
-#     facet_grid(flavor ~ Country) +
-#     geom_hline(yintercept = 0, colour="gray50", size=0.1) +
-#     scale_x_continuous(breaks=c(1960, 1980, 2000)) +
-#     xlab("") +
-#     ylab("r") + 
-#     xy_theme() +
-#     theme(legend.title=element_blank())
-# }
-
 cesResidualPlot2 <- function(data){

### 2015-09-23 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Historical plot now same style as alpha graph.

@@
 
-historicalPlot(
-  histDataForGraph, 
-  mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
-  facet_formula = flavor ~ Country, 
-  line_types = c(1,2,4,3,2,4,3,2,3,2,3)) + 
+ggplot(histDataForGraph) + 
+  geom_line(aes(x=Year, y=value, group=variable, linetype=variable, colour=variable, size=variable)) +
+  facet_grid(flavor ~ Country) + 
+  scale_color_manual(name = "", values=c("black", "black", "black", "gray70")) +
+  scale_linetype_manual(name="", values=c(1,2,3,1)) + 
+  scale_size_manual(name="", values = c(1, 0.9, 0.9, 0.6)) +
+  scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12), limits=c(0.5, 12)) +
   xlab("") + 
-scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12), limits=c(0.5, 12)) +
-ylab("Indexed (1960=1)")
+  ylab("Indexed (1960=1)") +
+  xy_theme()
 @

### 2015-09-23 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Corrected line types for historical data graph.

@@
 
-  # Make (and return) the graph
   ggplot() +
-    geom_line(data=fittedGraphData, mapping=aes(x=Year, y=value, group=label, linetype=label)) +
+    geom_line(data=fittedGraphData, mapping=aes(x=Year, y=value, group=label, linetype=label, size=label)) +
     scale_linetype_manual(values=c(1,2,4,3), name="") +
+    scale_size_manual(name = "", values=c(1, 0.5, 0.5, 0.5)) +
     facet_grid(flavor ~ Country) +
@@
 
-<<Graphs_CESkle_resample_alphas, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.2, fig.cap="Resample output elasticities for CES models with $(kl$)$e$ nesting.">>=
+<<resample_graph_alpha, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.2, fig.cap="Resample output elasticities for CES models with $(kl$)$e$ nesting.">>=
 ReModels %>% 
@@
 
-<<resample_graph_alpha, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.0, fig.cap="$\\alpha_k$, $\\alpha_l$, and $\\alpha_e$ values for CES resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
+<<resample_graph_alpha_ternary, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.0, fig.cap="$\\alpha_k$, $\\alpha_l$, and $\\alpha_e$ values for CES resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
 standardTriPlot(data=resampleCoeffs, facet_formula=~Country, alpha=0.1,

### 2015-09-23 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Line spacing now consistent.

@@
     values = c(.3, 1),
-    guide = FALSE
-  ) + 
+    guide = FALSE) + 
   scale_color_manual(
@@
     values=c("black", "black", "gray70"),
-    guide=FALSE
-  ) +
+    guide=FALSE) +
   scale_x_continuous(breaks = c(1960, 1980, 2000)) +

### 2015-09-23 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Improving grouping of scales.

@@
   facet_grid(. ~ Country) +
+
+  scale_x_continuous(breaks = c(1960, 1980, 2000)) +
+  scale_y_continuous(breaks = c(0.0, 0.5, 1.0)) +
+  labs(x="", y="") +
+
   scale_alpha_manual(
@@
     guide=FALSE) +
-  scale_x_continuous(breaks = c(1960, 1980, 2000)) +
-  scale_y_continuous(breaks = c(0.0, 0.5, 1.0)) +
   scale_size_manual(
@@
     values=c(2,3,1) ) +
-  xy_theme() +
-  labs(x="", y="")
+
+  xy_theme() 
 @

### 2015-09-24 Articles/Brockway_Rebound_2015/Brockway_2015.Rnw
Now creating sF and sK graphs.

@@
 
-<<Historical_Data_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Historical data.", warning=FALSE>>=
+<<Historical_Data_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=2.5, fig.cap="Historical data.", warning=FALSE>>=
 # Melt data for plotting
@@
   ylab("Indexed Quantities")
+@
+
+<<sF-sK-graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=2.5, fig.cap="$sF$ and $sK$ values.", warning=FALSE>>=
+ggplot(data=historicalData %>%
+         melt(measure.vars = c("sF", "sK"),
+              value.name = "value", variable.name = "variable")) + 
+  geom_line(mapping = aes(x=Year, y=value, group=variable, linetype=variable)) +
+  facet_grid(. ~ Country) +
+  scale_x_continuous(breaks=c(1960, 1980, 2000)) +
+  scale_y_continuous(breaks=c(0, 0.5, 1.0), limits=c(0, 1)) +
+  xlab("") + 
+  ylab("sF, sK") +
+  xy_theme()
 @

### 2015-09-25 Articles/Brockway_Rebound_2015/Brockway_2015.Rnw
Now creating a graph of Re vs. time.

@@
          melt(measure.vars = c("sF", "sK"),
-              value.name = "value", variable.name = "variable")) + 
+              value.name = "value", variable.name = "variable") %>%
+         mutate(
+           Country = relevelFactor(as.factor(Country), countries),
+           variable = relevelFactor(as.factor(variable), c("sK", "sF"))
+         )
+       ) + 
   geom_line(mapping = aes(x=Year, y=value, group=variable, linetype=variable)) +
@@
   ylab("sF, sK") +
-  xy_theme()
+  xy_theme() +
+  theme(legend.title=element_blank())
 @
@@
   saveRDS(models, file = modelsFileName)
-}
-@
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Resampling Calculations}
-\label{sec:resampling_calculations}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-<<Resampling>>=
-resampleFileName <- file.path("models", "Brockway2015Resamples.rds")
-if (!rerunResamples){
-  # load resample data from the file on disk
-    resampleCoeffs <- readRDS(resampleFileName)
-} else {
-  # Run resampling on models.
-  resampleCoeffs <- leaf_apply(l = models, class = c("cesModel", "plm"), f = function(mod, mod_name){
-    resampledFits(mod, method = "wild", n = nResamples)$coeffs %>%
-      mutate(
-        Country = mod_name
-      )
-  }) %>% bind_rows
-  saveRDS(resampleCoeffs, file = resampleFileName)
 }
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Resampling Results}
-\label{sec:resampling_results}
+\section{Resampling}
+\label{sec:resampling}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-Calculate rebound by Equation~\ref{eq:rebound}.
+<<Resampling>>=
+resampleFileName <- file.path("models", "Brockway2015Resamples.rds")
+if (!rerunResamples){
+  # load resample data from the file on disk
+    resampleCoeffs <- readRDS(resampleFileName)
+} else {
+  # Run resampling on models.
+  resampleCoeffs <- leaf_apply(l = models, class = c("cesModel", "plm"), f = function(mod, mod_name){
+    resampledFits(mod, method = "wild", n = nResamples)$coeffs %>%
+      mutate(
+        Country = mod_name
+      )
+  }) %>% bind_rows
+  saveRDS(resampleCoeffs, file = resampleFileName)
+}
+@
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Rebound}
+\label{sec:rebound_calculations}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%++++++++++++++++++++++++++++++
+\subsection{Basic Rebound} 
+\label{sec:basic_rebound}
+%++++++++++++++++++++++++++++++
+
+For the basic rebound calculations, 
+we can calculate rebound by Equation~\ref{eq:rebound}.
 %
@@
 Plot resampling results for \Sexpr{nResamples} resamples in Figure~\ref{fig:rebound_graph}.
+
+Note that the vertical axis is $\alpha_e$. We now know that this is the initial value for $\alpha_e$.
+In fact, there would be a trajectory with each dot as its starting point.
 %
@@
 @
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Full rebound}
+\label{sec:full_rebound}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Now, we calculate rebound by the full equation
+%
+\begin{equation} \label{eq:time_dependent_rebound}
+  Re = 1 + \frac{s_F \left[ s_F (1 + \rho) + \rho \right] + \rho (s_F - 1 - s_k) + s_F }{(1 + s_k + s_F)(1 + \rho)}
+\end{equation}
+%
+for each country.
+
+<<Rebound, echo=TRUE>>=
+Rebound <- leaf_apply(models, class = c("cesModel"), f = function(mod, id){
+  # "id" is the Country for mod
+  rho <- naturalCoef(mod)$rho
+  historicalData %>% 
+    filter(Country == id) %>%
+    mutate(
+      Re = 1 + 
+              (sF * (sF*(1+rho) + rho) + rho*(sF - 1  - sK) + sF) / 
+                    ( (1 + sK + sF ) * (1 + rho) )
+      )
+}) %>% 
+  bind_rows() %>%
+  mutate(
+    Country = relevelFactor(as.factor(Country), rev(countries))
+    )
+@
+
+<<Rebound-graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4.5, fig.cap="Time-dependent rebound.">>=
+ggplot(Rebound) + 
+  geom_line(mapping=aes(x=Year, y=Re, group=Country, linetype=Country)) +
+  geom_hline(y=1, color = "gray70", size=0.3) +
+  scale_y_continuous(breaks=c(0, 1, 2, 3), limits=c(0, 3)) +
+  scale_linetype_manual(values = c(3,2,1)) +
+  xlab("") +
+  ylab("Rebound") +
+  xy_theme() +
+  theme(legend.title=element_blank())
+@
+
+If we want to do so, we could apply the same calculation to each resampled model,
+which would give $n$ lines for each country in Figure~\ref{fig:Rebound-graph}.
+This would be similar to Figure~9 in the CES paper.
 

### 2015-09-27 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Get ticks out of lines in the graph.

@@
   scale_x_continuous(breaks = c(1960, 1980, 2000)) +
-  scale_y_continuous(breaks = c(0.0, 0.5, 1.0)) +
+  scale_y_continuous(breaks = c(0.0, 0.5, 1.0), limits=c(-0.2, 1.2)) +
   scale_size_manual(

### 2015-10-02 Articles/Article_EcolEcon_2015/Paper 0/Paper0-Resampling.Rnw
Add Paper0-Resampling.tex and .pdf to .gitignore.

%% This is file `elsarticle-template-2-harv.tex',
%%
%% Copyright 2009 Elsevier Ltd
%%
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%%
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%%
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%
%% Template article for Elsevier's document class `elsarticle'
%% with harvard style bibliographic references
%%
%% $Id: elsarticle-template-2-harv.tex 155 2009-10-08 05:35:05Z rishi $
%% $URL: http://lenova.river-valley.com/svn/elsbst/trunk/elsarticle-template-2-harv.tex $
%%
\documentclass[preprint,10pt,3p]{elsarticle}
\usepackage{setspace}
\doublespacing
%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,authoryear,1p,times]{elsarticle}
%% \documentclass[final,authoryear,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,authoryear,3p,times]{elsarticle}
%% \documentclass[final,authoryear,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,authoryear,5p,times]{elsarticle}
%% \documentclass[final,authoryear,5p,times,twocolumn]{elsarticle}

%% if you use PostScript figures in your article
%% use the graphics package for simple commands
\usepackage{graphics}
%% or use the graphicx package for more complicated commands
\usepackage{graphicx}
%% or use the epsfig package if you prefer to use the old commands
\usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
\bibpunct{(}{)}{,}{a}{,}{,}

\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{amsthm}
\usepackage{float}
\usepackage{epstopdf}
\usepackage{textcomp}
\usepackage{eurosym}
\usepackage{morefloats}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{caption}
\usepackage{csquotes}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{natbib}
\usepackage{booktabs}
\usepackage{rotating}

\usepackage{hyperref}

%\usepackage[hidenotes]{authNote}
\usepackage[shownotes]{authNote}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers after \end{frontmatter}.
\usepackage[right]{lineno}

%% natbib.sty is loaded by default. However, natbib options can be
%% provided with \biboptions{...} command. Following options are
%% valid:

%%   round  -  round parentheses are used (default)
%%   square -  square brackets are used   [option]
%%   curly  -  curly braces are used      {option}
%%   angle  -  angle brackets are used    <option>
%%   semicolon  -  multiple citations separated by semi-colon (default)
%%   colon  - same as semicolon, an earlier confusion
%%   comma  -  separated by comma
%%   authoryear - selects author-year citations (default)
%%   numbers-  selects numerical citations
%%   super  -  numerical citations as superscripts
%%   sort   -  sorts multiple citations according to order in ref. list
%%   sort&compress   -  like sort, but also compresses numerical citations
%%   compress - compresses without sorting
%%   longnamesfirst  -  makes first citation full author list
%%
%\biboptions{longnamesfirst,comma}

% \biboptions{}

%% Macros

% From http://economics.utoronto.ca/osborne/latex/BIBTEX.HTM
\newcommand{\citeapos}[1]{\citeauthor{#1}'s (\citeyear{#1})} % Posessive citations.

\newcommand{\sse}{\mbox{SSE}}
\newcommand{\mse}{\mbox{MSE}}

% Macros for graph symbols

\definecolor{light-gray}{gray}{0.9}

\newcommand{\klwCSPsymbol}{%
	\begin{picture}(9, 9)
		{\color{light-gray}\put(4.5,2.5){\circle*{9}}}%
		{\color{black}\put(4.5,2.5){\circle{9}}}
	\end{picture}%
}
\newcommand{\klwoCSPsymbol}{\raisebox{-0.2ex}{\Large$\circ$}}
\newcommand{\klesymbol}{\raisebox{-0.1ex}{\Large$\diamond$}}
\newcommand{\leksymbol}{{\small$\triangle$}}
% Flipping \triangle with 2x ``sideways'' with the ``rotating'' package 
% looks better than $\downtriangle$
\newcommand{\eklsymbol}{\begin{sideways}\begin{sideways}
							{\small$\triangle$}
						\end{sideways}\end{sideways}}
\newcommand{\wenergypoints}{\klesymbol, \leksymbol, and \eklsymbol}
\newcommand{\woenergypoints}{\klwCSPsymbol{} and \klwoCSPsymbol}
\newcommand{\wCSPpoints}{\klwCSPsymbol}
\newcommand{\woCSPpoints}{\klwoCSPsymbol, \wenergypoints}
\newcommand{\allpoints}{\wCSPpoints, \woCSPpoints}

\journal{Ecological Economics}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for the associated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for the associated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for the associated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%%
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{Estimating statical precison for parameters of Ecological Economics-inspired production functions}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{<author name>}
%% \address[label1]{<address>}
%% \address[label2]{<address>}

\author[label1]{Randall Pruim}
\ead{rpruim@calvin.edu}

\author[label2]{Matthew K. Heun}
\ead{mkh2@calvin.edu}

\address[label1]{Mathematics \& Statistics Department, Calvin College, Grand
Rapids, MI 49546, USA.}

\address[label2]{Engineering Department, Calvin College, Grand Rapids, MI 49546,
USA.}

\linenumbers

\begin{abstract}

Need abstract here.

\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
CES function \sep Cobb-Douglas function \sep statistical precision \sep aggregate production function
\end{keyword}

\end{frontmatter}

\linenumbers

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Highlights}
\label{sec:highlights}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\emph{This will go in a separate document eventually.}

\begin{itemize}
\item Highlight 1
\item Highlight 2
\item Highlight 3
\item Highlight 4
\end{itemize}

%\linenumbers

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction/Background}
\label{sec:intro}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Methods and data}
\label{sec:methods}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%++++++++++++++++++++++++++++++
\subsection{Production Functions}	% 202 words on 14-09-2015
\label{sec:models}
%++++++++++++++++++++++++++++++

%------------------------------
\subsubsection{Cobb-Douglas production function}
\label{sec:CD}
%------------------------------

Information about the C-D equation here.

%------------------------------
\subsubsection{CES production function}
\label{sec:CES}
%------------------------------

The CES production function shown in Equation~\ref{eq:CESkl} 
includes two factors of production, capital~($k$) and labor~($l$).
Extending to three factors of production can be accomplished by nesting
two factors of production against the third.
\authNote{rjp:  
This is not really the correct metaphor for ``nest".  They are nested 
because one CES formula is inside the other (like nested tables).  Basically
the inner CES formula is being plugged into the slot of one of the factors of production
of the outer CES formula.}%
Equation~\ref{eq:CESkle} augments Equation~\ref{eq:CESkl} with energy~($e$),
in a ($kl$)$e$ nesting structure, as is common in the literature:
%
\begin{equation} \label{eq:CESkle}
  y = \theta \: A \: \left\{\delta \left[\delta_1 k^{-\rho_1}
      + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1}
      + (1-\delta) e^{-\rho} \right\}^{-1/\rho} \; ; \;
      A \equiv \mathrm{e}^{\lambda t} \; .
\end{equation}
%
Note that Equation~\ref{eq:CESkl} is a degenerate form of Equation~\ref{eq:CESkle}
with $\delta = 1$ and $\rho$ and $e$ undetermined.
Two other nestings of the 
factors of production---($le$)$k$ and ($ek$)$l$---are possible 
with a three-factor CES function.
\authNoted{Do we need/want to comment about the other 3 nestings and that
each is just a reparameterization of one of the three we have given. ---rjp
I don't think we need to comment on the other three. ---MKH}
%
\begin{equation} \label{eq:CESlek}
  y = \theta \: A \: \left\{\delta \left[\delta_1 l^{-\rho_1}
      + (1-\delta_1) e^{-\rho_1} \right]^{\rho/\rho_1}
      + (1-\delta) k^{-\rho} \right\}^{-1/\rho};
      A \equiv \mathrm{e}^{\lambda t}
\end{equation}
%
\begin{equation} \label{eq:CESekl}
  y = \theta \: A \: \left\{\delta \left[\delta_1 e^{-\rho_1}
      + (1-\delta_1) k^{-\rho_1} \right]^{\rho/\rho_1}
      + (1-\delta) l^{-\rho} \right\}^{-1/\rho};
      A \equiv \mathrm{e}^{\lambda t}
\end{equation}
%
Each of the CES functions (Equations~\ref{eq:CESkl} 
and~\ref{eq:CESkle}--\ref{eq:CESekl}) assumes constant returns 
to scale.

Output elasticities~($\alpha$) are not constant;
rather, they vary with factors of production $k$, $l$, and $e$ over time.
For the $(kl)e$ nesting (Equation~\ref{eq:CESkle}),
output elasticities are shown in Equations~\ref{eq:alpha_k}--\ref{eq:alpha_e}.
Output elasticities for other nests can obtained by permutation of
the factors of production $k$, $l$, and $e$.
%
\begin{equation} \label{eq:alpha_k}
  \alpha_k \equiv
  \frac{
  \frac{\partial y}{\partial k} }{
  \frac{y}{k}
  } = \frac{\delta  \delta _1 k^{-\rho _1} \left[\delta _1 k^{-\rho _1}
  	+\left(1 - \delta_1 \right) 
		l^{-\rho _1}\right]{}^{\frac{\rho }{\rho _1}-1}}{\delta  
		\left[\delta _1
     k^{-\rho _1} + \left(1 - \delta _1 \right) l^{-\rho _1} \right]{}^{\frac{\rho }{\rho
     _1}} + (1 - \delta) e^{-\rho }}
\end{equation}
%
\begin{equation} \label{eq:alpha_l}
  \alpha_l \equiv 
  \frac{
  \frac{\partial y}{\partial l} }{
  \frac{y}{l}} =
  \frac{\delta  \left(1-\delta _1\right) l^{-\rho _1}
     \left[\delta _1 k^{-\rho _1}+\left(1 - \delta_1\right) l^{-\rho_1}\right]{}
	 				^{\frac{\rho }{\rho _1}-1}}
		{\delta  \left[\delta _1 k^{-\rho_1} + \left(1 - \delta_1\right) 
					l^{-\rho_1}\right]{}^{\frac{\rho }{\rho _1}}+ (1 - \delta) e^{-\rho }}
\end{equation}
%
\begin{equation} \label{eq:alpha_e}
  \alpha_e \equiv
  \frac{
  \frac{\partial y}{\partial e} }{
  \frac{y}{e}
  } =  \frac{1 - \delta}{\delta  e^{\rho } \left[\delta _1 k^{-\rho_1} 
  			+ \left(1 - \delta_1 \right) l^{-\rho _1}\right]{}
				^{\frac{\rho }{\rho_1}} + 1 - \delta}
\end{equation}
%
It can be verified that
%
\begin{equation} \label{eq:sum_betas}
  \alpha_k + \alpha_l + \alpha_e = 1
\end{equation}
%
for all nests.

Elasticities of substitution~($\sigma$) are a function of $\rho_1$, $\rho$, and
nesting as shown in 
Table~\ref{tab:CES_sigma_equations}.
\authNote{Need to use the equations for time-varying $\sigma$ values instead of this table.}
Note that $\sigma~\in~[0,\infty)$. 
The limiting case $\sigma \to 0$ is the Leontief production function and 
indicates perfect complementarity.  
The limiting case 
$\sigma \to \infty$ is a linear production function and 
indicates infinite substitutability.
When $\sigma = 1$, the CES production function simplifies to the
Cobb-Douglas production function.
%
\begin{table} \caption{Equations for elasticities of substitution~($\sigma$)
for various CES nests.}
\label{tab:CES_sigma_equations}
  \begin{center}
    \begin{tabular}{c c c c c c c c}
      \toprule
      Nest       & Equation
	  			 & $\sigma_{kl}$             & $\sigma_{(kl)e}$
	  			 & $\sigma_{le}$             & $\sigma_{(le)k}$
				 & $\sigma_{ek}$             & $\sigma_{(ek)l}$       \\
      \midrule
      ($kl$) \;  & \ref{eq:CESkl}
	  			 & $\frac{1}{1 + \rho_1}$   & --
	             & --                       & --
				 & --                       & --                    \\
      ($kl$)$e$  & \ref{eq:CESkle}
	  			 & $\frac{1}{1 + \rho_1}$   & $\frac{1}{1 + \rho}$
	             & --                       & --
				 & --                       & --                    \\
      ($le$)$k$  & \ref{eq:CESlek}
	  			 & --                       & --
	             & $\frac{1}{1 + \rho_1}$   & $\frac{1}{1 + \rho}$
				 & --                       & --                    \\
      ($ek$)$l$  & \ref{eq:CESekl}
	  			 & --                       & --
	             & --                       & --
	             & $\frac{1}{1 + \rho_1}$   & $\frac{1}{1 + \rho}$   \\
      \bottomrule
    \end{tabular}
  \end{center}
\end{table}

%++++++++++++++++++++++++++++++
\subsection{Parameter estimation} 
\label{sec:parameter_estimation}
%++++++++++++++++++++++++++++++

%------------------------------
\subsubsection{Technique} 
\label{sec:parameter_estimation_technique}
%------------------------------

To estimate values of parameters
($\theta$, $\lambda$, $\delta_1$, $\delta$, $\rho_1$, and $\rho$)
for the reference and CES models,
we use an ordinary least squares~(OLS) approach.
The objective of the OLS analysis is minimization of the sum of squared errors~(\sse):
%
\begin{equation} \label{eq:sse}
  \sse = \sum_{i} r_i^2 \; ,
\end{equation}
%
where
$r_i \equiv \ln (y_i / \hat{y}_i)$ is $i^{\mathrm{th}}$ residual 
(all models assume multiplicative errors),
and
$\hat{y}_i$ is the fitted value for economic output at time $t_i$.
In cases where a model adheres to the cost share principle,
output elasticities are fixed
in accordance with long-run historical cost shares
for capital and labor ($\hat{\alpha}_k = 0.3$ and $\hat{\alpha}_l = 0.7$).%
\authNoted{Randy put hats on 
$\alpha_k$ and $\alpha_l$, 
but I don't think they should be ``hatted.''
These are not estimated numbers. 
They are give \emph{a-priori} from national accounts data. ---MKH;

This is an edge case.  From data = estimated; just estimated in a different way,
and external to the data we are analyzing.  But that doesn't make those values
correct. ---rjp

OK. I'm willing to live with the hats. ---MKH}
We estimate parameters using a highly-customized version
of the \texttt{R} package \texttt{micEconCES} \citep{Henningsen:2011td}.
See the Supplemental Information
(\ref{sec:appendix_CES_fitting}) for additional details.
\authNoted{Is there a reason to use \mse{} rather than \sse?  Typically,
the denominator for \mse{} is not $N$ but the degrees of freedom
used to estimate the variance parameter of the model (typically $N - p$ for
a model with $p$ parameters).  Perhaps we should refer to this as
an ``unadjusted'' \mse{} if we stick with it.
I changed everything to sse. ---MKH}

\authNoted{What sort of ``expect'' is this? Can we say something more precise? ---rjp
I changed to ``know,'' which is more precise. ---MKH}

In the reference model,
all economic growth is attributed to the Solow residual. %~($\lambda$).
Indeed, the reference model will
have a larger estimated Solow 
residual~($\hat{\lambda}$) than
any CES model, because no factors of production are
included in the reference model to drive economic growth.
(If all of $y$, $k$, $l$, and $e$ are $\ge 1$,
the non-$A$ part of a CES model
will be $\ge 1$,
thereby driving $A$, and $\lambda$, to be smaller.)

\authNoted{I'm not sure this is true, and if it is, I think it is misleading, since
as $\rho \to 0$, CES $\to$ C-D, right?  Even if we disallow $\rho = 0$, this suggests
that the CES model can have \sse{} arbitrarily close to that for the C-D model, even if
the C-D model were best.  In practice, I'm guessing one will never see \sse{} for
CES exceeding that for C-D.  And in our CES function, we fit the limiting cases
explicitly, so it should be impossible.  Matt, am I forgetting something here? ---rjp
CD $\ne$ reference model.
The reference model is exponential-only. ---MKH}

On the other hand, it is not necessarily true that
CES models (Equations~\ref{eq:CESkl} and \ref{eq:CESkle}--\ref{eq:CESekl})
will exhibit lower \sse{} than the reference model
(Equation~\ref{eq:exponential-only-model}).
The CES production functions
have more parameters,
but there is no set 
of parameter 
estimates~($\hat\theta$, $\hat\lambda$, $\hat\delta_1$, 
$\hat\delta$, $\hat\rho_1$, and $\hat\rho$)
that mathematically eliminates 
the factors of production~($k$, $l$, and $e$)
from the CES models, 
thereby reproducing the reference model.%
\authNote{I added the clause ``but there is no combination of parameters
that can eliminate the factors of production
from the models.'' Is Randy OK with this? ---MKH}
%but they incorporate the factors of production
%at constant returns to scale, and we constrain them so that 
%$\alpha_k + \alpha_l + \alpha_e = 1$.
%In contrast, the reference model has $\alpha_k = \alpha_l = \alpha_e = 0$.
%\authNoted{Have we defined $\alpha_i$ for the reference model? ---rjp
%I have now added a sentence stating that reference models are a degenerate 
%form of CES models with $\alpha_i = 0$. ---MKH
%But this still isn't true --rjp}%
If the factors of production
are poorly correlated to output~($y$),
\sse{} may be higher for a CES model than for the reference model.
\authNoted{rjp:  removed bit about CRS.  I don't think CRS is the reason.
That's fine. ---MKH}%

%++++++++++++++++++++++++++++++
\subsection{CES fitting algorithm}
\label{sec:appendix_CES_fitting}
%++++++++++++++++++++++++++++++

We use the \texttt{R}~\citep{R}
package \texttt{micEconCES}
\citep{Henningsen:2011td}
with significant customization
to estimate parameters in the CES production function.
Our CES parameter estimation algorithm starts with an eleven-value grid search
in $\rho_1$ and $\rho$
(9, 2, 1, 0.43, 0.25, 0.1, -0.1, -0.5, -0.75, -0.9, -0.99),
corresponding to $\sigma_1$ and $\sigma$ values of
0.1, 0.33, 0.5, 0.7, 0.8, 0.9, 1.11, 2, 4, 10, and 100,
respectively.
During the grid search, values of $\rho_1$ and $\rho$ are fixed,
and values of $\theta$, $\lambda$, $\delta_1$, and $\delta$ are estimated
by gradient search with the \texttt{PORT} and \texttt{L-BFGS-B} algorithms
in the \texttt{micEconCES} package~\citep{Henningsen:2011td}.
In all, 121 gradient searches in $\theta$, $\lambda$, $\delta_1$, and $\delta$
at grid points representing all combinations of $\rho_1$ and $\rho$ are
attempted.
During the grid search portion of our algorithm, starting values for the free
parameters
are $\lambda$ = 0.015/year, $\delta_1$ = 0.5, $\delta$ = 0.5,
and $\theta$ is set by the \texttt{cesEst} function
to a value such that the mean of the residuals is zero.

Next, a gradient search (using both \texttt{PORT} and \texttt{L-BFGS-B})
is attempted wherein all parameters
($\theta$, $\lambda$, $\delta_1$, $\delta$, $\rho_1$, and $\rho$)
are allowed to float.
The starting values for fitting parameters are taken from
the grid search point that provided the lowest sum of squared errors~(\sse).

Henningsen and Henningsen~\cite{Henningsen:2011td},
in their detailed analysis of Kemfert~\cite{kemfert1998estimated}, found that
%
\begin{quote}
\ldots the Levenberg-Marquardt and the \texttt{PORT} algorithms
are---at least in this study---most likely to find the
coefficients that give the best fit to the model,
where the \texttt{PORT} algorithm can be used to restrict the estimates
to the economically meaningful region.
\end{quote}
%
In our testing, we found that to be mostly true.
\texttt{PORT} nearly always provides lower
\sse{} than \texttt{L-BFGS-B}, despite the fact that
\texttt{L-BFGS-B} often reports convergence
and \texttt{PORT} does not for the same data
(i.e., for the same $y$, $k$, $l$, and $e$ time series).

In addition to the above trials,
we also fit along all boundaries of the economically-meaningful region
of the CES model.
Boundaries are given by all combinations of the following:
$\delta_1$~=~0~or~1,
$\delta$~=~0~or~1,
$\sigma_1$~=~0~or~$\infty$, and
$\sigma$~=~0~or~$\infty$.
Table~\ref{tab:CES_boundary_models} shows the set
of 20 degenerate equations found along parameter boundaries~(rows~1--20),
wherein factors of production ($x_1$,~$x_2$,~$x_3$)
are permutations of ($k$,~$l$,~$e$).
The bottom (unnumbered) row of Table~\ref{tab:CES_boundary_models}
shows the generic three-factor CES equation.
Each degenerate equation provides a boundary model.
Note that many boundary parameter combinations
yield equivalent CES boundary models,%
  \footnote{
  For example, all boundary parameter combinations
  that include $\delta = 0$ yield the same boundary model, $y = \theta A x_3$.
  }
so there are far fewer boundary models~(20) than the maximum possible number
of degenerate equations~(81).%
  \footnote{
  There are three possible states (unspecified, lower boundary, upper boundary)
  for four constrained parameters ($\delta_1$, $\sigma_1$, $\delta$, $\sigma$),
  which gives $3^4 = 81$ possible boundary models.
  }
In the parameter columns of Table~\ref{tab:CES_boundary_models},
``---'' indicates that a parameter is unknowable on that boundary
(because it does not appear in the boundary model and
it is not part of the definition of the boundary), and
an empty space indicates that the parameter
is estimable on that boundary using the degenerate equation.

Fitting along boundaries is important for two reasons.
First, bounded, non-linear, ordinary least squares~(OLS) algorithms
that perform gradient searches within the parameter space
(such as the \texttt{PORT} and \texttt{L-BFGS-B} algorithms discussed above)
often have difficulties dealing with boundaries.
Fitting directly \emph{on} the boundaries
of the economically-meaningful region
ensures that a sum of squared errors~(\sse)
minimum located at a boundary will be found, if it exists.
Second, fitting on the boundaries of the economically-meaningful region
prevents erroneous reporting of unknowable parameters.
Table~\ref{tab:CES_boundary_models} includes many dashes~(``---'')
indicating that many fitting parameters are unknowable
in the boundary models.
For example, $\sigma_1$ and $\sigma$ are unknowable in
the boundary model shown in Row 1 of Table~\ref{tab:CES_boundary_models}.
If an OLS search algorithm
(such as \texttt{PORT} and \texttt{L-BFGS-B}, discussed above)
operating with the full CES model (bottom row of Table~\ref{tab:CES_boundary_models})
were to find an \sse{} minimum along that boundary,
it would report values for $\sigma_1$ and $\sigma$
\emph{in addition to} $\theta$, $\lambda$, $\delta_1$~(which will be unity),
and $\delta$~(also unity).
Under these conditions,
it is clearly erroneous to report
meaningless, because they are unknowable,
values for $\sigma_1$ and $\sigma$.
Fitting with the boundary models
shown in Table~\ref{tab:CES_boundary_models}
avoids this mistake.

Boundary models obtained when $\delta_1$ or $\delta$ is at an extreme value
(0 or 1)
are straightforward to derive from the bottom row of
Table~\ref{tab:CES_boundary_models}.
When $\sigma_1$ or $\sigma$ is 0,
factors of production are perfect complements
and the Leontief model applies.%
  \footnote{
  E.g., when $\sigma_1 = 0$ and $\delta~=~1$, the Leontief model is
  $y = \theta A \min (x_1, x_2)$, row 4 in Table~\ref{tab:CES_boundary_models}.
  }
When $\sigma_1$ or $\sigma$ is $\infty$,
factors of production are perfect substitutes
and the linear model applies.%
  \footnote{
  E.g., when $\sigma_1 = \infty$ and $\delta~=~1$, the linear model is
  $y = \theta A \left[ \delta_1 x_1 + (1 - \delta_1) x_2 \right]$,
  row 7 in Table~\ref{tab:CES_boundary_models}.
  }
If the fitted parameters in a boundary model violate constraints,
the boundary model is rejected.
%
\begin{table} \caption{CES boundary models (rows~1--20) and full model (bottom
row).}
\label{tab:CES_boundary_models}
  \begin{center}
    \begin{tabular}{r c c c c l}
      \toprule
      & $\delta_1$  & $\sigma_1$ & $\delta$   & $\sigma$ & Boundary model \\
      \midrule
      1. & 1           & ---        & 1          & ---      & $y = \theta A x_1$
      \\
      2. & 0           & ---        & 1          & ---      & $y = \theta A x_2$
      \\
      3. & ---         & ---        & 0          & ---      & $y = \theta A x_3$
      \\
      \midrule
      4. & ---         & 0          & 1          & ---      & $y = \theta A \min
      (x_1, \, x_2)$ \\
      5. & 1           & ---        & ---        & 0        & $y = \theta A \min
      (x_1, \, x_3)$ \\
      6. & 0           & ---        & ---        & 0        & $y = \theta A \min
      (x_2, \, x_3)$ \\
%
      7. &             & $\infty$   & 1          & ---
            & $y = \theta A \left[ \delta_1 x_1 + (1 - \delta_1) x_2 \right]$ \\
%
      8. & 1           & ---        &            & $\infty$
            & $y = \theta A \left[ \delta x_1 + (1 - \delta) x_3 \right]$ \\
%
      9. & 0           & ---        &            & $\infty$
            & $y = \theta A \left[ \delta x_2 + (1 - \delta) x_3 \right]$ \\
%
     10. &             &            & 1          & ---
            & $y = \theta A \left[ \delta_1 x_1^{-\rho_1}
                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{-1/
                    \rho_1}$ \\
%
     11. & 1           & ---        &         &
            & $y = \theta A \left[ \delta x_1^{-\rho}
                    + \left(1 - \delta \right) x_3^{-\rho} \right] ^ {-1/\rho}$
                    \\
%
     12. & 0           & ---        &            &
            & $y = \theta A \left[ \delta x_2^{-\rho} + \left(1 - \delta \right)
            x_3^{-\rho} \right]^{-1/\rho}$ \\
      \midrule
     13. & ---         & 0          & ---        & 0        & $y = \theta A \min
     (x_1, \, x_2, \, x_3)$ \\
%
     14. & ---         & 0          &            & $\infty$
            & $y = \theta A \left[ \delta \min (x_1, \, x_2) + \left( 1 - \delta
            \right) x_3  \right]$ \\
%
     15. &             & $\infty$   & ---        & 0
            & $y = \theta A \min \left[ \delta_1 x_1 + \left(1 - \delta_1
            \right) x_2, \, x_3  \right]$ \\
%
     16. &             & $\infty$   &            & $\infty$
            & $y = \theta A \left\{ \delta \left[ \delta_1 x_1 + \left( 1 -
            \delta_1 \right) x_2 \right]
                    + \left( 1 - \delta \right) x_3  \right\}$ \\
%
     17. & ---         & 0          &            &
            & $y = \theta A \left\{ \delta \left[ \min \left( x_1, \, x_2
            \right) \right]^{-\rho}
                    + \left( 1 - \delta \right) x_3^{-\rho}  \right\} ^
                    {-1/\rho}$ \\
%
     18. &            &            & ---     & 0
            & $y = \theta A \min \left\{ \left[ \delta_1 x_1^{-\rho_1}
                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{-1/
                    \rho_1}, \, x_3 \right\}$ \\
%
     19. &             &            &            & $\infty$
            & $y = \theta A \left\{ \delta \left[ \delta_1 x_1^{-\rho_1}
                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{-1/
                    \rho_1}
                    + \left( 1 - \delta \right) x_3  \right\}$ \\
%
     20. &             & $\infty$   &            &
            & $y = \theta A \left\{ \delta \left[ \delta_1 x_1
                    + \left( 1 - \delta_1 \right) x_2 \right]^{-\rho}
                    + \left( 1 - \delta \right) x_3^{-\rho}  \right\} ^
                    {-1/\rho}$ \\
\midrule
         &            &            &         &
            & $y = \theta A \left\{ \delta \left[ \delta_1 x_1^{-\rho_1}
                    + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{\rho/
                    \rho_1}
                    + \left( 1 - \delta \right) x_3^{-\rho}  \right\} ^
                    {-1/\rho}$ \\
      \bottomrule
    \end{tabular}
  \end{center}
\end{table}
%
The model with lowest \sse{} of all above trials
is deemed the winning (i.e.,~best) model,
and its parameters are presented herein.
In special cases, two boundary models will be equivalent.
For example, boundary model~4 is identical to boundary model~1~(2)
if $x_1$ is always less than (greater than) $x_2$ for all years.
If two or more models have the same \sse{} (to ten digits),
the model with the lowest row number in Table~\ref{tab:CES_boundary_models}
is deemed the winning model.

%------------------------------	439 words on 14-09-2015
\subsubsection{Precision} 
\label{sec:parameter_precision}
%------------------------------

Determining the precision of estimates for CES parameters
($\hat\theta$, $\hat\lambda$, $\hat\delta_1$, $\hat\delta$, $\hat\rho_1$, 
and $\hat\rho$, but also
$\hat\alpha_k$, $\hat\alpha_l$, $\hat\alpha_e$, 
$\hat\sigma_{kl}$, $\hat\sigma_{le}$, $\hat\sigma_{ek}$, 
$\hat\sigma_{(kl)e}$, $\hat\sigma_{(le)k}$, and $\hat\sigma_{(ek)l}$)
is important but challenging.
It is quite possible for substantial changes in a CES model parameter
to have a relatively modest effect on the objective function
that is determining the parameter estimates (in this case, \sse).
When this happens, the ``best estimate''
is not much better than many other good estimates, and parameter
estimates must be interpreted with caution.

The usual methods for quantifying the precision of parameter estimates
using standard errors, confidence intervals,
and $p$-values rely on an asymptotic theory that applies
on the interior of a parameter space and assumes independence of error terms.
% With $n \approx 50$\authNoted{We have 50 years, 1960--2009, not 30 years as Randy 
% originally thought. 
% Does this change the way we write this section? ---MKH
% Well, we're closer to infinity, but we still have edges --rjp} 
% (in this case, years)
% \authNoted{Do you mean 30 years?
% Should we rather say ``With 30 years of data''---MKH.
% Perhaps there is a better word than sample, but it isn't really primarily
% about time but about the number of rows of data.  That happens to equal the number
% of years of data in this case but isn't the real issue.
% For now, I'm punting and just using $N \approx 30$. ---rjp}%
% and with CES functions (Equations~\ref{eq:CESkl} and~\ref{eq:CESkle}--\ref{eq:CESekl})
% having as many as six parameters,
It can be difficult to provide an \emph{a priori} justification
for the use of such asymptotic results.
The authors of the \texttt{R} package \texttt{micEconCES}
acknowledge as much when they say that
``As [the computation of the variance-covariance
matrix] is only valid asymptotically,
we calculate the estimated variance of the residuals \dots
without correcting for degrees of freedom.'' \citep{Henningsen:2011td}

Further complicating matters is our interest in issues that arise on the
boundary of (the economically meaningful portion of) the parameter space.
In an investigation of whether energy is important, for example,
we may consider the null hypothesis that $\alpha_e = 0$.  
In the ($kl$)$e$ nesting, 
this null hypothesis is equivalent to $\delta = 1$.
While there is an asymptotic theory for this case as well,%
\authNote{%
Randy: can you provide a reference for the asymptotic theory? ---MKH}%
the distributions are, in general,
more complicated---mixtures of chi-squared variates---and the
precise mix may be difficult or impossible to determine analytically.
\authNote{Ideally, we should check that there is not an easy analytical solution
in our particular case.  We'll see if there is time. ---rjp}%

The situation is further complicated in the case of cross-model parameter
comparisons, although within-model precision estimates bring us a good deal
of the way to answering such questions as whether the Solow residual~($\lambda$)
is larger in the exponential reference model than in a CES function.%
\authNote{The example question given 
seems like a cross-model comparison (correct, ---rjp), 
but the text indicates it is a within-model comparison (it does not, ---rjp). 
Am I mis-reading this? ---MKH  yes.  The point is that if we had good within-model
estimates for the precision with which we estimate $lambda$, that would go part
of the way toward answering whether two different models have significantly 
different estiamtes of $\lambda$.  ---rjp}

\iffalse
Third, the default output from routines in statistical packages like \texttt{R},
assumes hypotheses wherein fitted parameters are equal to zero.
As shown above, determining the statistical precision of parameters in the CES model
is likely to involve many null hypotheses
where a parameter is \emph{not} equal to zero.
For simple cases where normality and independence assumptions are met,
a $p$-value for a null hypothesis where the value is zero
can be quickly transformed into a $p$-value for a different null hypothesis.
However, as discussed above,
determining (or estimating) the null distribution
can be extremely challenging, especially when the model is located
at the boundary of the economically-meaningful region.
\fi

For this paper, we perform limited, but enlightening,
statistical resampling analyses
to provide an indication of the precision with which parameters are known.
(See Section~\ref{sec:resampling}.)
In a section on future work (see Section~\ref{sec:conclusionsFinal}),%
\authNote{This section number is incorrect. Why?}
we provide some suggestions for a way forward.

%++++++++++++++++++++++++++++++
\subsection{Bootstrap resampling algorithm}
\label{sec:appendix_resampling}
%++++++++++++++++++++++++++++++

Bootstrapping is a statistical resampling technique for assigning
measures of accuracy and precision to sample estimates by measuring
properties of an estimator when sampling from a resampling
distribution.
Resampling distributions can be formed in a number of
ways in accordance with the type of data, experimental design,
and modeling assumptions involved.
In each case, many new resamples
are created, each of which is a randomized version of the original sample data to
which the desired analysis method can be applied.
By investigating, for example,
the variability of a parameter estimate from one resample to another,
one can learn about the precision of the estimation method.
**** Add some references here. ---rjp ****
% \authNote{Add some references here. ---rjp}

In the context of linear models (regression),
resamples are generally created
by residual resampling.
In our case, we formed resamples by adding to the fitted
response~($\hat{y}$) the product of a residual from the original CES function fit
(see Figure~\ref{fig:r_kle}) and
random sign ($-1$ or $1$, each with probability $0.5$).
This residual resampling occurs on the
log-transformed data.
Intuitively, this method assumes that the residuals are indicative of
the variability (from many potential sources) inherent in the data such that
it would be unsurprising if the residual from
any particular year had been observed in a different year.
Thus, a resampled response $\tilde Y'$ can be computed as
**** Randy edit the following equations to reflect the fact that
we're fitting in log space? ---MKH ****
%
\begin{equation}
  \tilde Y_i' = \hat y_i \pm r_j \; ,
\end{equation}
%
where
%
\begin{equation}
  r_i = y_i - \hat y_i \; .
\end{equation}
%
Both the sign~($\pm$) and the index
($j$,~typically different from $i$)
of the residual~($r_j$)
are chosen at random (with replacement).
We repeated the resampling process 1000 times for each
combination of growth model and country,
both with and without energy as appropriate.

The parameters from the fit to a resampled time series
(the ``resample parameters'') will be different from the parameters
obtained from the fit to historical data (the ``base parameters'').
When these resample parameters are highly variable,
it is an indication
that the data do not determine the parameter estimates very precisely.
Lack of precision can stem from a number of factors, most obviously
a poor model fit,
low model sensitivity to one or more parameters, or
correlations between parameter estimates.

It is important to note that large residuals can arise from either
poor quality historical time series data or
a mathematical model that does not describe the underlying phenomena well.
It is also important to note that even when the residuals are small and the
model produces fitted values that track the observed data closely, it may
yet be difficult to estimate some or all of the model parameters precisely.
The resampling method employed herein reflects all three of these potential
sources of uncertainty in parameter estimates.

We choose the resampling approach instead of the more-common technique
of estimating confidence intervals from standard errors for two reasons.
First, model parameters are highly constrained, and confidence intervals often violate the constraints.
For example, a result of $\alpha_k = 0.25 \pm 0.3$ is nonsensical,
because $ \alpha_k \in [0, 1]$.
Second, true confidence intervals for constrained parameters are often asymmetric
(e.g., $\alpha_k = 0.2 + 0.1, -0.05$),
but the standard error approach yields symmetric confidence intervals.
The resampling approach that we employed both respects constraints
and allows for asymmetric confidence intervals.%
In addition, we choose to present parameter uncertainty results visually
(see Figures~\ref{fig:resample_lambda_theta}--\ref{fig:resample_alpha}),
both because the resampling technique lends itself to visual presentation and
because we believe visual comparison is more effective
in communicating results than endless tables of numbers.

%++++++++++++++++++++++++++++++
\subsection{Historical data}
\label{sec:historical_data}
%++++++++++++++++++++++++++++++

Refer to other paper for historica data.

Focus on Portugal only.

Show graph of historical data here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results and Discussion}
\label{sec:results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%------------------------------
\subsubsection{Parameter precision}
\label{sec:resampling}
%------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\label{sec:conclusion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgements}
\label{sec:acknowledgements}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%References
%%
%% Following citation commands can be used in the body text:
%%
%%  \citet{key}  ==>>  Jones et al. (1990)
%%  \citep{key}  ==>>  (Jones et al., 1990)
%%
%% Multiple citations as normal:
%% \citep{key1,key2}         ==>> (Jones et al., 1990; Smith, 1989)
%%                            or  (Jones et al., 1990, 1991)
%%                            or  (Jones et al., 1990a,b)
%% \cite{key} is the equivalent of \citet{key} in author-year mode
%%
%% Full author lists may be forced with \citet* or \citep*, e.g.
%%   \citep*{key}            ==>> (Jones, Baker, and Williams, 1990)
%%
%% Optional notes as:
%%   \citep[chap. 2]{key}    ==>> (Jones et al., 1990, chap. 2)
%%   \citep[e.g.,][]{key}    ==>> (e.g., Jones et al., 1990)
%%   \citep[see][pg. 34]{key}==>> (see Jones et al., 1990, pg. 34)
%%  (Note: in standard LaTeX, only one note is allowed, after the ref.
%%   Here, one note is like the standard, two make pre- and post-notes.)
%%
%%   \citealt{key}          ==>> Jones et al. 1990
%%   \citealt*{key}         ==>> Jones, Baker, and Williams 1990
%%   \citealp{key}          ==>> Jones et al., 1990
%%   \citealp*{key}         ==>> Jones, Baker, and Williams, 1990
%%
%% Additional citation possibilities
%%   \citeauthor{key}       ==>> Jones et al.
%%   \citeauthor*{key}      ==>> Jones, Baker, and Williams
%%   \citeyear{key}         ==>> 1990
%%   \citeyearpar{key}      ==>> (1990)
%%   \citetext{priv. comm.} ==>> (priv. comm.)
%%   \citenum{key}          ==>> 11 [non-superscripted]
%% Note: full author lists depends on whether the bib style supports them;
%%       if not, the abbreviated list is printed even when full requested.
%%
%% For names like della Robbia at the start of a sentence, use
%%   \Citet{dRob98}         ==>> Della Robbia (1998)
%%   \Citep{dRob98}         ==>> (Della Robbia, 1998)
%%   \Citeauthor{dRob98}    ==>> Della Robbia

%% References with bibTeX database:

\bibliographystyle{agsm}
\bibliography{references}

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections

\newpage
\section*{Author Notes}

\authNotes

\end{document}

%%
%% End of file `elsarticle-template-2-harv.tex'.s

### 2015-10-02 Articles/Article_EcolEcon_2015/Paper0/Paper0-Resampling.Rnw
Rename Paper 0 folder to Paper0

--- 2015-10-02 Articles/Article_EcolEcon_2015/Paper 0/Paper0-Resampling.Rnw
@@
 %------------------------------
+
+%------------------------------
+\subsubsection{Constant Elasticity of Substitution Production Function (CES)} 
+\label{sec:CES}
+%------------------------------
+
+The energy-augmented 
+Constant Elasticity of Substitution (CES) production function%
+  \footnote{
+  We use the The \texttt{R} 
+  % \citep{R} 
+  package \texttt{micEconCES} 
+  % \citep{Henningsen:2011td} 
+  to estimate the CES production function.
+  }
+can be given as
+%
+\begin{equation} \label{eq:CESgeneric}
+  y = \gamma \: A \: \left\{\delta \left[\delta_1 x_1^{-\rho_1} 
+      + (1-\delta_1)x_2^{-\rho_1} \right]^{\rho/\rho_1} 
+      + (1-\delta) x_3^{-\rho} \right\}^{-1/\rho}; 
+      A \equiv \mathrm{e}^{\lambda (t-t_0)},
+\end{equation}
+%
+where
+$y \equiv Y/Y_{0}$,
+$\gamma$ is a scale parameter,
+e is the base of the natural logarithm, 
+$\lambda$ is the Solow residual (often thougth to represent the pace of technological progress),
+$t$ (time) is measured in years,
+$x_1$, $x_2$, and $x_3$ are factors of production
+and permutations of capital~($k$), labor~($l$), and energy~($e$),
+$k \equiv K/K_{0}$, 
+$l \equiv L/L_{0}$, 
+$Y$ (economic output) is represented by GDP, 
+$K$ (capital) is expressed in currency units, 
+$L$ (labor) is expressed in workers or work-hours/year, and
+the 0 subscript indicates values at an initial year.%
+  \footnote{Dimensionless, indexed quantities are represented by 
+  lower-case symbols 
+  ($y$, $k$, $l$, $e$, $q$, $x$, and $u$), and dimensional 
+  quantities are represented by upper-case symbols 
+  ($Y$, $K$, $L$, $E$, $Q$, $X$, and $U$). 
+  Model parameters are represented by Greek letters
+  ($\alpha_1$, $\alpha_2$, $\lambda$, $\theta$).
+  }
+The CES model without energy is given in Equation~\ref{eq:CESkl}.
+%
+\begin{equation} \label{eq:CESkl}
+  y = \gamma \: A \: \left[\delta_1 k^{-\rho_1} 
+      + (1-\delta_1)l^{-\rho_1} \right]^{-1/\rho_1}; 
+      A \equiv \mathrm{e}^{\lambda (t-t_0)} . 
+\end{equation}
+%
+Equation~\ref{eq:CESkle} augments Equation~\ref{eq:CESkl} with energy 
+using a ($kl$)($e$) nesting structure, as is typical in the literature. 
+Equation~\ref{eq:CESkl} is a degenerate form of Equation~\ref{eq:CESkle} 
+where $\delta \rightarrow 1$. 
+%
+\begin{equation} \label{eq:CESkle}
+  y = \gamma \: A \: \left\{\delta \left[\delta_1 k^{-\rho_1} 
+      + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1} 
+      + (1-\delta) e^{-\rho} \right\}^{-1/\rho}; 
+      A \equiv \mathrm{e}^{\lambda (t-t_0)}.
+\end{equation}
+%
+In the CES production function, 
+$\gamma$ is a fitting parameter that accounts for an atypical first year. 
+The fitting parameters $\rho_1$ and $\rho$ indicate elasticities 
+of substitution ($\sigma_1$ and $\sigma$).
+The elasticity of substitution 
+between capital ($k$) and labor ($l$) is given by 
+$\sigma_1 = \frac{1}{1+\rho_1}$, and
+the elasticity of substitution between ($kl$) and ($e$) is given by 
+$\sigma = \frac{1}{1+\rho}$. 
+As $\rho_1 \rightarrow 0$, $\sigma_1 \rightarrow 1$,
+and the embedded CES production function for $k$ and $l$ degenerates 
+to the Cobb-Douglas production function.
+Similarly, as $\rho \rightarrow 0$, $\sigma \rightarrow 1$,
+and the CES production function for $(kl)$ and $(e)$ degenerates 
+to the Cobb-Douglas production function.
+As $\sigma \rightarrow \infty$ ($\rho \rightarrow -1$), 
+($kl$) and ($e$) are perfect substitutes. 
+As $\sigma \rightarrow 0$ ($\rho \rightarrow \infty$), 
+($kl$) and ($e$) are perfect complements: 
+no substitution is possible. Similarly, 
+as $\sigma_1 \rightarrow 0$ ($\rho_1 \rightarrow \infty$),
+$k$ and $l$ are perfect complements.
+$\delta_1$ describes the relative importance of capital ($k$)
+and labor ($l$), and
+$\delta$ describes the importance of ($kl$) relative to ($e$).
 
@@
 
-For this paper, we perform limited, but enlightening,
-statistical resampling analyses
-to provide an indication of the precision with which parameters are known.
-(See Section~\ref{sec:resampling}.)
-In a section on future work (see Section~\ref{sec:conclusionsFinal}),%
-\authNote{This section number is incorrect. Why?}
-we provide some suggestions for a way forward.
-
 %++++++++++++++++++++++++++++++
@@
 
-%------------------------------
-\subsubsection{Parameter precision}
-\label{sec:resampling}
-%------------------------------
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-10-03 Articles/Article_EcolEcon_2015/Paper0/Paper0-Resampling.Rnw
Better title
Added framing to the paper

@@
 
-\title{Estimating statical precison for parameters of Ecological Economics-inspired production functions}
+\title{Parameter precision in economic growth models inspired by Ecological Economics}
 
@@
 
-\author[label1]{Randall Pruim}
+\author[label1]{Randall J. Pruim}
 \ead{rpruim@calvin.edu}
@@
 
+Ideas for an Ecological Economics frame for the paper:
+
+%
+\begin{itemize}
+
+  \item EE ideas (work of Kummel and Ayres and Warr, especially) 
+        inspire us to include energy, 
+        reject the CSP, and 
+        quality-adjust energy.
+
+  \item Another insight from Ayres and Warr (and Kummel before them) 
+        is that output elasticities can be functions of time. 
+        Linex gives this explicitly. 
+        But, so does CES.
+        This means moving away from Cobb-Douglas toward CES.
+
+  \item Also, inspired by Ayres and Warr, 
+        we don’t want to assume elasticity of substitution 
+        of unity as CD does.
+        (What does Linex give for the elasticity of substitution between factors of production?)
+
+  \item But, questions remain from Ayres and Warr's work.
+
+  \begin{itemize}
+
+    \item Ayres and Warr used a non-standard production function.
+          Will their insights hold true for standard production functinos like Cobb-Douglas and CES?
+
+    \item Ayres and Warr quality-adjusted only one factor of production, energy, by employing useful work.  
+          What happens when all factors of production, including capital and labor, are quality-adjusted?
+
+    \item Ayres and Warr expended minimal effort at statistical precision of estimated parameters. 
+          How robust are their findings, from a statistical point of view?
+
+  \end{itemize}
+
+  \item We want to explore the last point above (statistical precision of estimated parameters)
+        in the context of a standard production function (CES).
+
+  \item However, when moving away from CD and Linex toward CES, 
+        we leave the world of linear fitting behind.
+
+  \item Standard approaches assume normal distributions for model parameters. 
+        In the non-linear world of CES, 
+        those assumptions aren't appropriate. 
+        Need a new approach in the non-CD world.
+
+  \begin{itemize}
+
+    \item Need advanced techniques for fitting.
+
+    \item We use customized version of Henningsen and Henningsen for fitting.
+
+    \item Need advanced techniques for estimating precision of estimated parameters.
+
+    \item We use resampling to estimate precision of estimated parameters.
+
+  \end{itemize}
+
+\end{itemize}
+%
+This paper explores and justifies those choices by 
+%
+\begin{enumerate}
+
+  \item comparing standard techniques and our approaches for the Cobb-Douglas production function and
+
+  \item applying our techniques to the CES production production function.
+
+\end{enumerate}
+%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %++++++++++++++++++++++++++++++
-\subsection{Production Functions}	% 202 words on 14-09-2015
+\subsection{Production Functions}
 \label{sec:models}

### 2015-10-04 Articles/Article_EcolEcon_2015/Paper0/Paper0-Resampling.Rnw
Editing intro.

@@
 %
+for the Portuguese economy from 1960--2010.
 
@@
 
-Information about the C-D equation here.
-
-%------------------------------
-\subsubsection{CES production function}
-\label{sec:CES}
-%------------------------------
+**** Go completely generic everywhere ($x_1$ instead of $k$). ****
+
+The Cobb-Douglas production function 
+is the canonical representation of indexed economic output ($y$) 
+as a function of 
+indexed labor~($l$), 
+indexed capital stock~($k$), and 
+an additional exogenous, time-dependent term~($A$).
+This production function can be expressed as
+%
+\begin{equation} \label{eq:CD}
+  y = \theta A k^\alpha_k l^\alpha_l \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)},
+\end{equation}
+%
+where 
+$y \equiv Y/Y_{0}$,
+$\theta$ is a scale parameter,
+e is the base of the natural logarithm, 
+$\lambda$ is represents the pace of technological progress,
+$t$ is time (typically measured in years),
+$k \equiv K/K_{0}$, 
+$l \equiv L/L_{0}$, 
+$Y$ is represented by GDP, 
+$K$ is expressed in currency units, 
+$L$ is expressed in workers or work-hours/year, and
+0 subscripts indicate values at an initial year.
+The parameters $\alpha_k$ and $\alpha_l$ are output elasticities
+that indicate the marginal productivity of 
+capital and labor in the economy, respectively.
+Typically, the constraint $\alpha_k + \alpha_l = 1$ is assumed, 
+indicating constant returns to scale.%
+  \footnote{Dimensionless, indexed quantities are represented by lower-case symbols 
+  ($y$, $k$, $l$, and later $e$), 
+  and dimensional quantities are represented by upper-case symbols 
+  ($Y$, $K$, $L$, and later $E$). 
+  Model parameters are represented by Greek letters
+  ($\theta$, $\lambda$, $\alpha_k$, $\alpha_l$, 
+  later $\alpha_e$, $\delta_1$, $\delta$, $\sigma_1$, and $\sigma$).}
+
+The capital-labor Cobb-Douglas production function shown in Equation~\ref{eq:CD}
+can be augmented by energy:
+%
+\begin{equation} \label{eq:CDe}
+  y = \theta A k^\alpha_k l^\alpha_l e^\alpha_e \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)},
+\end{equation}
+%
+where $e \equiv E/E_0$, and $E$ is in units of energy per time, typically TJ/year. 
+The energy-augmented Cobb-Douglas production function 
+is often assumed to have constant returns to scale for the three factors 
+of production: $\alpha_k + \alpha_l + \alpha_e = 1$.
 
@@
 
-The energy-augmented 
-Constant Elasticity of Substitution (CES) production function%
-  \footnote{
-  We use the The \texttt{R} 
-  % \citep{R} 
-  package \texttt{micEconCES} 
-  % \citep{Henningsen:2011td} 
-  to estimate the CES production function.
-  }
+The Constant Elasticity of Substitution~(CES) model 
+without energy is given in Equation~\ref{eq:CESkl}.
+%
+\begin{equation} \label{eq:CESkl}
+  y = \gamma \: A \: \left[\delta_1 k^{-\rho_1} 
+      + (1-\delta_1)l^{-\rho_1} \right]^{-1/\rho_1}; \;
+      A \equiv \mathrm{e}^{\lambda (t-t_0)} . 
+\end{equation}
+%
+The generic CES production function
 can be given as
@@
 where
-$y \equiv Y/Y_{0}$,
-$\gamma$ is a scale parameter,
-e is the base of the natural logarithm, 
-$\lambda$ is the Solow residual (often thougth to represent the pace of technological progress),
-$t$ (time) is measured in years,
 $x_1$, $x_2$, and $x_3$ are factors of production
-and permutations of capital~($k$), labor~($l$), and energy~($e$),
-$k \equiv K/K_{0}$, 
-$l \equiv L/L_{0}$, 
-$Y$ (economic output) is represented by GDP, 
-$K$ (capital) is expressed in currency units, 
-$L$ (labor) is expressed in workers or work-hours/year, and
-the 0 subscript indicates values at an initial year.%
-  \footnote{Dimensionless, indexed quantities are represented by 
-  lower-case symbols 
-  ($y$, $k$, $l$, $e$, $q$, $x$, and $u$), and dimensional 
-  quantities are represented by upper-case symbols 
-  ($Y$, $K$, $L$, $E$, $Q$, $X$, and $U$). 
-  Model parameters are represented by Greek letters
-  ($\alpha_1$, $\alpha_2$, $\lambda$, $\theta$).
-  }
-The CES model without energy is given in Equation~\ref{eq:CESkl}.
-%
-\begin{equation} \label{eq:CESkl}
-  y = \gamma \: A \: \left[\delta_1 k^{-\rho_1} 
-      + (1-\delta_1)l^{-\rho_1} \right]^{-1/\rho_1}; 
-      A \equiv \mathrm{e}^{\lambda (t-t_0)} . 
-\end{equation}
+and permutations of capital~($k$), labor~($l$), and energy~($e$).
 %
 Equation~\ref{eq:CESkle} augments Equation~\ref{eq:CESkl} with energy 
-using a ($kl$)($e$) nesting structure, as is typical in the literature. 
+using a ($kl$)$e$ nesting structure, as is typical in the literature. 
 Equation~\ref{eq:CESkl} is a degenerate form of Equation~\ref{eq:CESkle} 
@@
 In the CES production function, 
-$\gamma$ is a fitting parameter that accounts for an atypical first year. 
+$\theta$ is a fitting parameter that accounts for an atypical first year. 
 The fitting parameters $\rho_1$ and $\rho$ indicate elasticities 
 of substitution ($\sigma_1$ and $\sigma$).
-The elasticity of substitution 
-between capital ($k$) and labor ($l$) is given by 
-$\sigma_1 = \frac{1}{1+\rho_1}$, and
-the elasticity of substitution between ($kl$) and ($e$) is given by 
-$\sigma = \frac{1}{1+\rho}$. 
-As $\rho_1 \rightarrow 0$, $\sigma_1 \rightarrow 1$,
-and the embedded CES production function for $k$ and $l$ degenerates 
-to the Cobb-Douglas production function.
-Similarly, as $\rho \rightarrow 0$, $\sigma \rightarrow 1$,
-and the CES production function for $(kl)$ and $(e)$ degenerates 
-to the Cobb-Douglas production function.
-As $\sigma \rightarrow \infty$ ($\rho \rightarrow -1$), 
-($kl$) and ($e$) are perfect substitutes. 
-As $\sigma \rightarrow 0$ ($\rho \rightarrow \infty$), 
-($kl$) and ($e$) are perfect complements: 
-no substitution is possible. Similarly, 
-as $\sigma_1 \rightarrow 0$ ($\rho_1 \rightarrow \infty$),
-$k$ and $l$ are perfect complements.
-$\delta_1$ describes the relative importance of capital ($k$)
-and labor ($l$), and
-$\delta$ describes the importance of ($kl$) relative to ($e$).
-
-The CES production function shown in Equation~\ref{eq:CESkl} 
-includes two factors of production, capital~($k$) and labor~($l$).
-Extending to three factors of production can be accomplished by nesting
-two factors of production against the third.
-\authNote{rjp:  
-This is not really the correct metaphor for ``nest".  They are nested 
-because one CES formula is inside the other (like nested tables).  Basically
-the inner CES formula is being plugged into the slot of one of the factors of production
-of the outer CES formula.}%
-Equation~\ref{eq:CESkle} augments Equation~\ref{eq:CESkl} with energy~($e$),
-in a ($kl$)$e$ nesting structure, as is common in the literature:
-%
-\begin{equation} \label{eq:CESkle}
-  y = \theta \: A \: \left\{\delta \left[\delta_1 k^{-\rho_1}
-      + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1}
-      + (1-\delta) e^{-\rho} \right\}^{-1/\rho} \; ; \;
-      A \equiv \mathrm{e}^{\lambda t} \; .
-\end{equation}
-%
-Note that Equation~\ref{eq:CESkl} is a degenerate form of Equation~\ref{eq:CESkle}
-with $\delta = 1$ and $\rho$ and $e$ undetermined.
+
 Two other nestings of the 
@@
 with a three-factor CES function.
-\authNoted{Do we need/want to comment about the other 3 nestings and that
-each is just a reparameterization of one of the three we have given. ---rjp
-I don't think we need to comment on the other three. ---MKH}
 %
@@
 
-Output elasticities~($\alpha$) are not constant;
+For the CES function, 
+output elasticities~($\alpha$) are not constant;
 rather, they vary with factors of production $k$, $l$, and $e$ over time.
@@
 
-Elasticities of substitution~($\sigma$) are a function of $\rho_1$, $\rho$, and
-nesting as shown in 
-Table~\ref{tab:CES_sigma_equations}.
-\authNote{Need to use the equations for time-varying $\sigma$ values instead of this table.}
-Note that $\sigma~\in~[0,\infty)$. 
-The limiting case $\sigma \to 0$ is the Leontief production function and 
-indicates perfect complementarity.  
-The limiting case 
-$\sigma \to \infty$ is a linear production function and 
-indicates infinite substitutability.
-When $\sigma = 1$, the CES production function simplifies to the
-Cobb-Douglas production function.
-%
-\begin{table} \caption{Equations for elasticities of substitution~($\sigma$)
-for various CES nests.}
-\label{tab:CES_sigma_equations}
-  \begin{center}
-    \begin{tabular}{c c c c c c c c}
-      \toprule
-      Nest       & Equation
-	  			 & $\sigma_{kl}$             & $\sigma_{(kl)e}$
-	  			 & $\sigma_{le}$             & $\sigma_{(le)k}$
-				 & $\sigma_{ek}$             & $\sigma_{(ek)l}$       \\
-      \midrule
-      ($kl$) \;  & \ref{eq:CESkl}
-	  			 & $\frac{1}{1 + \rho_1}$   & --
-	             & --                       & --
-				 & --                       & --                    \\
-      ($kl$)$e$  & \ref{eq:CESkle}
-	  			 & $\frac{1}{1 + \rho_1}$   & $\frac{1}{1 + \rho}$
-	             & --                       & --
-				 & --                       & --                    \\
-      ($le$)$k$  & \ref{eq:CESlek}
-	  			 & --                       & --
-	             & $\frac{1}{1 + \rho_1}$   & $\frac{1}{1 + \rho}$
-				 & --                       & --                    \\
-      ($ek$)$l$  & \ref{eq:CESekl}
-	  			 & --                       & --
-	             & --                       & --
-	             & $\frac{1}{1 + \rho_1}$   & $\frac{1}{1 + \rho}$   \\
-      \bottomrule
-    \end{tabular}
-  \end{center}
-\end{table}
+Elasticities of substitution~($\sigma$) between factors of production
+are a function of $\rho_1$, $\rho$, and nesting. 
+**** More here on the actual $\sigma$ equations. 
+Gather them from the Henningsen and Henningsen paper. ****
 
@@
 
+Teaser at the end that variability varies from one country to the next.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-10-04 Articles/Article_EcolEcon_2015/Paper0/Paper0-Resampling.Rnw
Editing introduction.

@@
 is the canonical representation of indexed economic output ($y$) 
-as a function of 
-indexed labor~($l$), 
-indexed capital stock~($k$), and 
+as a function of indexed factors of production~($x_1$, $x_2$, and $x_3$) and 
 an additional exogenous, time-dependent term~($A$).
@@
 \begin{equation} \label{eq:CD}
-  y = \theta A k^\alpha_k l^\alpha_l \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)},
+  y = \theta A \, {x_1}^{\alpha_1} \, {x_2}^{\alpha_2} \, {x_3}^{\alpha_3} \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)},
 \end{equation}
@@
 $\lambda$ is represents the pace of technological progress,
-$t$ is time (typically measured in years),
-$k \equiv K/K_{0}$, 
-$l \equiv L/L_{0}$, 
-$Y$ is represented by GDP, 
-$K$ is expressed in currency units, 
-$L$ is expressed in workers or work-hours/year, and
+$t$ is time measured in years,
+$x_1 \equiv K/K_{0}$, 
+$x_2 \equiv L/L_{0}$, 
+$Y$ is economic output represented by GDP, 
+$K$ is capital stock expressed in currency units, 
+$L$ is labor expressed in workers or work-hours/year, and
 0 subscripts indicate values at an initial year.

### 2015-10-05 Articles/Article_EcolEcon_2015/Paper0/Paper0-Resampling.Rnw
Editing intro to make generic eqns.

@@
 \begin{equation} \label{eq:CD}
-  y = \theta A \, {x_1}^{\alpha_1} \, {x_2}^{\alpha_2} \, {x_3}^{\alpha_3} \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)},
+  y = \theta A \, {x_1}^{\alpha_1} \, {x_2}^{\alpha_2} \, {x_3}^{\alpha_3} \; ; \; A \equiv \mathrm{e}^{\lambda t},
 \end{equation}
@@
 $t$ is time measured in years,
-$x_1 \equiv K/K_{0}$, 
-$x_2 \equiv L/L_{0}$, 
+$x_1 = k \equiv K/K_{0}$, 
+$x_2 = l \equiv L/L_{0}$, 
+$x_3 = e \equiv E/E_{0}$, 
 $Y$ is economic output represented by GDP, 
 $K$ is capital stock expressed in currency units, 
-$L$ is labor expressed in workers or work-hours/year, and
+$L$ is labor expressed in workers or work-hours/year, 
+$E$ is energy expressed in units of energy per time, typically TJ/year, and
 0 subscripts indicate values at an initial year.
-The parameters $\alpha_k$ and $\alpha_l$ are output elasticities
+All historical data~($y$, $k$, $l$, and $e$) are indexed (by ratio)
+relative to an initial year. 
+Time~($t$) is indexed (by difference) relative to an initial year.
+After indexing, $\theta$ is expected to be near unity,
+but no other parameters change.%
+  \footnote{Dimensionless, indexed quantities are represented by lower-case symbols 
+  ($y$, $x$, $k$, $l$, and $e$), 
+  and dimensional quantities are represented by upper-case symbols 
+  ($Y$, $K$, $L$, and $E$). 
+  Model parameters are represented by Greek letters
+  ($\theta$, $\lambda$, $\alpha_1$, $\alpha_2$, $\alpha_3$, and
+  later $\delta_1$, $\delta$, $\sigma_1$, and $\sigma$).}
+
+The parameters $\alpha_1$, $\alpha_2$, and $\alpha_3$ are output elasticities
 that indicate the marginal productivity of 
-capital and labor in the economy, respectively.
-Typically, the constraint $\alpha_k + \alpha_l = 1$ is assumed, 
-indicating constant returns to scale.%
-  \footnote{Dimensionless, indexed quantities are represented by lower-case symbols 
-  ($y$, $k$, $l$, and later $e$), 
-  and dimensional quantities are represented by upper-case symbols 
-  ($Y$, $K$, $L$, and later $E$). 
-  Model parameters are represented by Greek letters
-  ($\theta$, $\lambda$, $\alpha_k$, $\alpha_l$, 
-  later $\alpha_e$, $\delta_1$, $\delta$, $\sigma_1$, and $\sigma$).}
-
-The capital-labor Cobb-Douglas production function shown in Equation~\ref{eq:CD}
-can be augmented by energy:
-%
-\begin{equation} \label{eq:CDe}
-  y = \theta A k^\alpha_k l^\alpha_l e^\alpha_e \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)},
-\end{equation}
-%
-where $e \equiv E/E_0$, and $E$ is in units of energy per time, typically TJ/year. 
-The energy-augmented Cobb-Douglas production function 
-is often assumed to have constant returns to scale for the three factors 
-of production: $\alpha_k + \alpha_l + \alpha_e = 1$.
+$x_1$, $x_2$, and $x_3$ in the economy, respectively.
+Typically, the constraint $\alpha_1 + \alpha_2 + \alpha_3 = 1$ is assumed, 
+indicating constant returns to scale.
 
@@
 The Constant Elasticity of Substitution~(CES) model 
-without energy is given in Equation~\ref{eq:CESkl}.
-%
-\begin{equation} \label{eq:CESkl}
-  y = \gamma \: A \: \left[\delta_1 k^{-\rho_1} 
-      + (1-\delta_1)l^{-\rho_1} \right]^{-1/\rho_1}; \;
-      A \equiv \mathrm{e}^{\lambda (t-t_0)} . 
-\end{equation}
-%
-The generic CES production function
-can be given as
+is given as
 %
@@
 and permutations of capital~($k$), labor~($l$), and energy~($e$).
-%
-Equation~\ref{eq:CESkle} augments Equation~\ref{eq:CESkl} with energy 
-using a ($kl$)$e$ nesting structure, as is typical in the literature. 
-Equation~\ref{eq:CESkl} is a degenerate form of Equation~\ref{eq:CESkle} 
-where $\delta \rightarrow 1$. 
-%
-\begin{equation} \label{eq:CESkle}
-  y = \gamma \: A \: \left\{\delta \left[\delta_1 k^{-\rho_1} 
-      + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1} 
-      + (1-\delta) e^{-\rho} \right\}^{-1/\rho}; 
-      A \equiv \mathrm{e}^{\lambda (t-t_0)}.
+
+For the CES function, 
+output elasticities~($\alpha_1$, $\alpha_2$, and $\alpha_3$) are not constant;
+rather, they vary with factors of production ($x_1$, $x_2$, and $x_3$) over time.
+%
+\begin{equation} \label{eq:alpha_x_1}
+  \alpha_{x_1} \equiv
+  \frac{ \frac{\partial y}{\partial x_1} }
+          { \frac{y}{x_1} } 
+  = 
+  \frac{ \delta  \delta _1 x_1^{-\rho _1} \left[\delta _1 x_1^{-\rho _1} + \left(1 - \delta_1 \right) x_2^{-\rho _1}\right]
+                             ^{\frac{\rho}{\rho _1}-1} }
+  { \delta \left[\delta _1 x_1^{-\rho _1} + \left(1 - \delta _1 \right) x_2^{-\rho _1} \right]
+                             ^{ \frac{\rho }{\rho_1} } 
+                + (1 - \delta) x_3^{-\rho }}
 \end{equation}
 %
-In the CES production function, 
-$\theta$ is a fitting parameter that accounts for an atypical first year. 
-The fitting parameters $\rho_1$ and $\rho$ indicate elasticities 
-of substitution ($\sigma_1$ and $\sigma$).
-
-Two other nestings of the 
-factors of production---($le$)$k$ and ($ek$)$l$---are possible 
-with a three-factor CES function.
-%
-\begin{equation} \label{eq:CESlek}
-  y = \theta \: A \: \left\{\delta \left[\delta_1 l^{-\rho_1}
-      + (1-\delta_1) e^{-\rho_1} \right]^{\rho/\rho_1}
-      + (1-\delta) k^{-\rho} \right\}^{-1/\rho};
-      A \equiv \mathrm{e}^{\lambda t}
+\begin{equation} \label{eq:alpha_x_2}
+  \alpha_{x_2} \equiv \frac{ \frac{\partial y}{\partial x_2} }{\frac{y}{x_2}} =
+  \frac{ \delta  \left(1-\delta _1 \right) x_2^{-\rho _1} \left[\delta _1 x_1^{-\rho _1}+\left(1 - \delta_1\right) x_2^{-\rho_1}\right]
+	 				^{\frac{\rho }{\rho _1}-1} }
+		{\delta  \left[\delta _1 x_1^{-\rho_1} + \left(1 - \delta_1\right) x_2
+                                        ^{-\rho_1}\right]^{\frac{\rho }{\rho _1}}+ (1 - \delta) {x_3}^{-\rho }}
 \end{equation}
 %
-\begin{equation} \label{eq:CESekl}
-  y = \theta \: A \: \left\{\delta \left[\delta_1 e^{-\rho_1}
-      + (1-\delta_1) k^{-\rho_1} \right]^{\rho/\rho_1}
-      + (1-\delta) l^{-\rho} \right\}^{-1/\rho};
-      A \equiv \mathrm{e}^{\lambda t}
-\end{equation}
-%
-Each of the CES functions (Equations~\ref{eq:CESkl} 
-and~\ref{eq:CESkle}--\ref{eq:CESekl}) assumes constant returns 
-to scale.
-
-For the CES function, 
-output elasticities~($\alpha$) are not constant;
-rather, they vary with factors of production $k$, $l$, and $e$ over time.
-For the $(kl)e$ nesting (Equation~\ref{eq:CESkle}),
-output elasticities are shown in Equations~\ref{eq:alpha_k}--\ref{eq:alpha_e}.
-Output elasticities for other nests can obtained by permutation of
-the factors of production $k$, $l$, and $e$.
-%
-\begin{equation} \label{eq:alpha_k}
-  \alpha_k \equiv
-  \frac{
-  \frac{\partial y}{\partial k} }{
-  \frac{y}{k}
-  } = \frac{\delta  \delta _1 k^{-\rho _1} \left[\delta _1 k^{-\rho _1}
-  	+\left(1 - \delta_1 \right) 
-		l^{-\rho _1}\right]{}^{\frac{\rho }{\rho _1}-1}}{\delta  
-		\left[\delta _1
-     k^{-\rho _1} + \left(1 - \delta _1 \right) l^{-\rho _1} \right]{}^{\frac{\rho }{\rho
-     _1}} + (1 - \delta) e^{-\rho }}
-\end{equation}
-%
-\begin{equation} \label{eq:alpha_l}
-  \alpha_l \equiv 
-  \frac{
-  \frac{\partial y}{\partial l} }{
-  \frac{y}{l}} =
-  \frac{\delta  \left(1-\delta _1\right) l^{-\rho _1}
-     \left[\delta _1 k^{-\rho _1}+\left(1 - \delta_1\right) l^{-\rho_1}\right]{}
-	 				^{\frac{\rho }{\rho _1}-1}}
-		{\delta  \left[\delta _1 k^{-\rho_1} + \left(1 - \delta_1\right) 
-					l^{-\rho_1}\right]{}^{\frac{\rho }{\rho _1}}+ (1 - \delta) e^{-\rho }}
-\end{equation}
-%
-\begin{equation} \label{eq:alpha_e}
-  \alpha_e \equiv
-  \frac{
-  \frac{\partial y}{\partial e} }{
-  \frac{y}{e}
-  } =  \frac{1 - \delta}{\delta  e^{\rho } \left[\delta _1 k^{-\rho_1} 
-  			+ \left(1 - \delta_1 \right) l^{-\rho _1}\right]{}
+\begin{equation} \label{eq:alpha_x_3}
+  \alpha_{x_3} \equiv \frac{ \frac{\partial y}{\partial x_3} }{ \frac{y}{x_3} } =  
+      \frac{1 - \delta}{\delta  x_3^{\rho } \left[\delta _1 x_1^{-\rho_1} + \left(1 - \delta_1 \right) x_2^{-\rho _1}\right]
 				^{\frac{\rho }{\rho_1}} + 1 - \delta}
@@
 \begin{equation} \label{eq:sum_betas}
-  \alpha_k + \alpha_l + \alpha_e = 1
+  \alpha_{x_1} + \alpha_{x_2} + \alpha_{x_3} = 1
 \end{equation}

### 2015-10-05 Articles/Article_EcolEcon_2015/Paper0/Paper0-Resampling.Rnw
Edits to models and resampling sections.

@@
 \begin{equation} \label{eq:CESgeneric}
-  y = \gamma \: A \: \left\{\delta \left[\delta_1 x_1^{-\rho_1} 
-      + (1-\delta_1)x_2^{-\rho_1} \right]^{\rho/\rho_1} 
+  y = \theta \: A \: \left\{\delta B_1^{\rho/\rho_1} 
       + (1-\delta) x_3^{-\rho} \right\}^{-1/\rho}; 
-      A \equiv \mathrm{e}^{\lambda (t-t_0)},
+      A \equiv \mathrm{e}^{\lambda t},
 \end{equation}
@@
 where
+$B_1 \equiv \delta_1 x_1^{-\rho_1} + (1-\delta_1) x_2^{-\rho_1}$, and
 $x_1$, $x_2$, and $x_3$ are factors of production
@@
 %
-\begin{equation} \label{eq:alpha_x_1}
-  \alpha_{x_1} \equiv
+\begin{equation} \label{eq:alpha_1}
+  \alpha_1 \equiv
   \frac{ \frac{\partial y}{\partial x_1} }
@@
   = 
-  \frac{ \delta  \delta _1 x_1^{-\rho _1} \left[\delta _1 x_1^{-\rho _1} + \left(1 - \delta_1 \right) x_2^{-\rho _1}\right]
-                             ^{\frac{\rho}{\rho _1}-1} }
-  { \delta \left[\delta _1 x_1^{-\rho _1} + \left(1 - \delta _1 \right) x_2^{-\rho _1} \right]
-                             ^{ \frac{\rho }{\rho_1} } 
-                + (1 - \delta) x_3^{-\rho }}
-\end{equation}
-%
-\begin{equation} \label{eq:alpha_x_2}
-  \alpha_{x_2} \equiv \frac{ \frac{\partial y}{\partial x_2} }{\frac{y}{x_2}} =
-  \frac{ \delta  \left(1-\delta _1 \right) x_2^{-\rho _1} \left[\delta _1 x_1^{-\rho _1}+\left(1 - \delta_1\right) x_2^{-\rho_1}\right]
-	 				^{\frac{\rho }{\rho _1}-1} }
-		{\delta  \left[\delta _1 x_1^{-\rho_1} + \left(1 - \delta_1\right) x_2
-                                        ^{-\rho_1}\right]^{\frac{\rho }{\rho _1}}+ (1 - \delta) {x_3}^{-\rho }}
-\end{equation}
-%
-\begin{equation} \label{eq:alpha_x_3}
-  \alpha_{x_3} \equiv \frac{ \frac{\partial y}{\partial x_3} }{ \frac{y}{x_3} } =  
-      \frac{1 - \delta}{\delta  x_3^{\rho } \left[\delta _1 x_1^{-\rho_1} + \left(1 - \delta_1 \right) x_2^{-\rho _1}\right]
-				^{\frac{\rho }{\rho_1}} + 1 - \delta}
+  \frac{ \delta  \delta _1 x_1^{-\rho _1} B_1^{ ( \frac{\rho}{\rho_1}-1 ) }  }
+  { \delta B_1^{ ( \frac{\rho }{\rho_1} ) } + (1 - \delta) x_3^{-\rho }}
+\end{equation}
+%
+
+\begin{equation} \label{eq:alpha_2}
+  \alpha_2 \equiv \frac{ \frac{\partial y}{\partial x_2} }{\frac{y}{x_2}} =
+  \frac{ \delta  \left(1-\delta _1 \right) x_2^{-\rho _1} B_1^{ ( \frac{\rho }{\rho _1}-1 ) } }
+  { \delta B_1^{ ( \frac{\rho }{\rho_1} ) } + (1 - \delta) x_3^{-\rho }}
+\end{equation}
+%
+\begin{equation} \label{eq:alpha_3}
+  \alpha_3 \equiv \frac{ \frac{\partial y}{\partial x_3} }{ \frac{y}{x_3} } =  
+      \frac{1 - \delta}{\delta  x_3^{\rho } B_1^{(\frac{\rho }{\rho_1} ) } + 1 - \delta}
 \end{equation}
@@
 \begin{equation} \label{eq:sum_betas}
-  \alpha_{x_1} + \alpha_{x_2} + \alpha_{x_3} = 1
+  \alpha_1 + \alpha_2 + \alpha_3 = 1
 \end{equation}
@@
 
-Elasticities of substitution~($\sigma$) between factors of production
-are a function of $\rho_1$, $\rho$, and nesting. 
-**** More here on the actual $\sigma$ equations. 
-Gather them from the Henningsen and Henningsen paper. ****
+Similar to the output elasticities, 
+the elasticity of substitution between factors of production $x_1$ and $x_2$~($\sigma_{1,2}$) 
+is time-varying and given by the Allen-Uzawa elasticity of substitution:
+%
+\begin{equation} \label{eq:sigma_1_2}
+  \sigma_{1,2} = \frac{ (1 - \rho_1)^{-1} - (1-\rho)^{-1}}{\delta \left( \frac{y}{B_1^{-\frac{1}{\rho_1}}} \right) ^ {1 + \rho}}
+                      + (1 + \rho)^{-1} \; .
+\end{equation}
+%
+
+**** Add Hicks-McFadden elasticity of substitution here. ****
 
@@
 %------------------------------
-\subsubsection{Technique} 
-\label{sec:parameter_estimation_technique}
+\subsubsection{Cobb-Douglas model} 
+\label{sec:param_estimation_CD}
 %------------------------------
 
-To estimate values of parameters
-($\theta$, $\lambda$, $\delta_1$, $\delta$, $\rho_1$, and $\rho$)
-for the reference and CES models,
-we use an ordinary least squares~(OLS) approach.
-The objective of the OLS analysis is minimization of the sum of squared errors~(\sse):
+To estimate the parameters $\theta$, $\lambda$, $\alpha_1$, $\alpha_2$, and $\alpha_3$ 
+in the Cobb-Douglas model, 
+we reparameterized Equation~\ref{eq:CD} as
+%
+\begin{equation} \label{eq:CDe_AB_reparam}
+  y = \theta \, \mathrm{e}^{\lambda t} \, x_1^{\alpha_1} \, x_2^{\alpha_2} \, x_3^{1 - \alpha_1 - \alpha_2}
+\end{equation}
+%
+ensuring that $\alpha_1 + \alpha_2 + \alpha_3 = 1$,
+thereby providing constant returns to scale.
+The \texttt{R} \citep{R} function \texttt{lm} was used to estimate 
+values of $\lambda$, $\theta$, $\alpha_1$, and $\alpha_2$ in log-transform space.
+If the fitted value for $\alpha_1$ or $\alpha_2$ fell outside the interval $[0,1]$,
+we fit along all boundaries 
+($\alpha_1 = 1$,
+$\alpha_2 = 1$,
+$\alpha_3 = 1$,
+$\alpha_1 = 0$,
+$\alpha_2 = 0$, and
+$\alpha_3 = 0$)
+and chose the boundary fit with
+minimum sum of squared errors~(\sse) as the winning model:
 %
@@
 %
-where
-$r_i \equiv \ln (y_i / \hat{y}_i)$ is $i^{\mathrm{th}}$ residual 
-(all models assume multiplicative errors),
+where the residual is given as
+%
+\begin{equation} \label{eq:residual}
+  r_i \equiv \ln (y_i / \hat{y}_i)
+\end{equation}
+%
+is the $i^{\mathrm{th}}$ residual (all models assume multiplicative errors),
 and
 $\hat{y}_i$ is the fitted value for economic output at time $t_i$.
+$\alpha_3$ was recovered with $\alpha_3 = 1 - \alpha_1 - \alpha_2$.
+
 In cases where a model adheres to the cost share principle,
@@
 in accordance with long-run historical cost shares
-for capital and labor ($\hat{\alpha}_k = 0.3$ and $\hat{\alpha}_l = 0.7$).%
-\authNoted{Randy put hats on 
-$\alpha_k$ and $\alpha_l$, 
-but I don't think they should be ``hatted.''
-These are not estimated numbers. 
-They are give \emph{a-priori} from national accounts data. ---MKH;
-
-This is an edge case.  From data = estimated; just estimated in a different way,
-and external to the data we are analyzing.  But that doesn't make those values
-correct. ---rjp
-
-OK. I'm willing to live with the hats. ---MKH}
-We estimate parameters using a highly-customized version
-of the \texttt{R} package \texttt{micEconCES} \citep{Henningsen:2011td}.
-See the Supplemental Information
-(\ref{sec:appendix_CES_fitting}) for additional details.
-\authNoted{Is there a reason to use \mse{} rather than \sse?  Typically,
-the denominator for \mse{} is not $N$ but the degrees of freedom
-used to estimate the variance parameter of the model (typically $N - p$ for
-a model with $p$ parameters).  Perhaps we should refer to this as
-an ``unadjusted'' \mse{} if we stick with it.
-I changed everything to sse. ---MKH}
-
-\authNoted{What sort of ``expect'' is this? Can we say something more precise? ---rjp
-I changed to ``know,'' which is more precise. ---MKH}
-
-In the reference model,
-all economic growth is attributed to the Solow residual. %~($\lambda$).
-Indeed, the reference model will
-have a larger estimated Solow 
-residual~($\hat{\lambda}$) than
-any CES model, because no factors of production are
-included in the reference model to drive economic growth.
-(If all of $y$, $k$, $l$, and $e$ are $\ge 1$,
-the non-$A$ part of a CES model
-will be $\ge 1$,
-thereby driving $A$, and $\lambda$, to be smaller.)
-
-\authNoted{I'm not sure this is true, and if it is, I think it is misleading, since
-as $\rho \to 0$, CES $\to$ C-D, right?  Even if we disallow $\rho = 0$, this suggests
-that the CES model can have \sse{} arbitrarily close to that for the C-D model, even if
-the C-D model were best.  In practice, I'm guessing one will never see \sse{} for
-CES exceeding that for C-D.  And in our CES function, we fit the limiting cases
-explicitly, so it should be impossible.  Matt, am I forgetting something here? ---rjp
-CD $\ne$ reference model.
-The reference model is exponential-only. ---MKH}
-
-On the other hand, it is not necessarily true that
-CES models (Equations~\ref{eq:CESkl} and \ref{eq:CESkle}--\ref{eq:CESekl})
-will exhibit lower \sse{} than the reference model
-(Equation~\ref{eq:exponential-only-model}).
-The CES production functions
-have more parameters,
-but there is no set 
-of parameter 
-estimates~($\hat\theta$, $\hat\lambda$, $\hat\delta_1$, 
-$\hat\delta$, $\hat\rho_1$, and $\hat\rho$)
-that mathematically eliminates 
-the factors of production~($k$, $l$, and $e$)
-from the CES models, 
-thereby reproducing the reference model.%
-\authNote{I added the clause ``but there is no combination of parameters
-that can eliminate the factors of production
-from the models.'' Is Randy OK with this? ---MKH}
-%but they incorporate the factors of production
-%at constant returns to scale, and we constrain them so that 
-%$\alpha_k + \alpha_l + \alpha_e = 1$.
-%In contrast, the reference model has $\alpha_k = \alpha_l = \alpha_e = 0$.
-%\authNoted{Have we defined $\alpha_i$ for the reference model? ---rjp
-%I have now added a sentence stating that reference models are a degenerate 
-%form of CES models with $\alpha_i = 0$. ---MKH
-%But this still isn't true --rjp}%
-If the factors of production
-are poorly correlated to output~($y$),
-\sse{} may be higher for a CES model than for the reference model.
-\authNoted{rjp:  removed bit about CRS.  I don't think CRS is the reason.
-That's fine. ---MKH}%
-
-%++++++++++++++++++++++++++++++
-\subsection{CES fitting algorithm}
-\label{sec:appendix_CES_fitting}
-%++++++++++++++++++++++++++++++
-
-We use the \texttt{R}~\citep{R}
-package \texttt{micEconCES}
+for capital and labor ($\hat{\alpha}_1 = 0.3$ and $\hat{\alpha}_2 = 0.7$).
+Under these conditions, $\hat{\alpha}_3$ is assumed to be $0$.
+
+%------------------------------
+\subsubsection{CES model} 
+\label{sec:param_estimation_CES}
+%------------------------------
+
+To estimate values of parameters
+($\theta$, $\lambda$, $\delta_1$, $\delta$, $\rho_1$, and $\rho$)
+for the CES model,
+we use an ordinary least squares~(OLS) approach.
+The objective of the OLS analysis is minimization of the sum of squared errors~(Equation~\ref{eq:sse}).
+We estimate parameters using the \texttt{R}~\citep{R} package \texttt{micEconCES}
 \citep{Henningsen:2011td}
@@
 
-Henningsen and Henningsen~\cite{Henningsen:2011td},
+\citet{Henningsen:2011td},
 in their detailed analysis of Kemfert~\cite{kemfert1998estimated}, found that
@@
 
-%------------------------------	439 words on 14-09-2015
-\subsubsection{Precision} 
+%++++++++++++++++++++++++++++++
+\subsection{Parameter precision} 
 \label{sec:parameter_precision}
-%------------------------------
-
-Determining the precision of estimates for CES parameters
+%++++++++++++++++++++++++++++++
+
+Determining the precision of estimates for 
+Cobb-Douglas parameters
+($\hat\theta$, $\hat\lambda$, $\hat\alpha_1$, $\hat\alpha_2$, and $\hat\alpha_3$)
+and 
+CES parameters
 ($\hat\theta$, $\hat\lambda$, $\hat\delta_1$, $\hat\delta$, $\hat\rho_1$, 
-and $\hat\rho$, but also
-$\hat\alpha_k$, $\hat\alpha_l$, $\hat\alpha_e$, 
-$\hat\sigma_{kl}$, $\hat\sigma_{le}$, $\hat\sigma_{ek}$, 
-$\hat\sigma_{(kl)e}$, $\hat\sigma_{(le)k}$, and $\hat\sigma_{(ek)l}$)
+and $\hat\rho$, but also time series for
+$\hat\alpha_1$, $\hat\alpha_2$, $\hat\alpha_3$, 
+$\hat\sigma_{1,2}$, and $\hat\sigma_{(1,2)3}$)
 is important but challenging.
-It is quite possible for substantial changes in a CES model parameter
+It is quite possible for substantial changes in a model parameter
 to have a relatively modest effect on the objective function
@@
 on the interior of a parameter space and assumes independence of error terms.
-% With $n \approx 50$\authNoted{We have 50 years, 1960--2009, not 30 years as Randy 
-% originally thought. 
-% Does this change the way we write this section? ---MKH
-% Well, we're closer to infinity, but we still have edges --rjp} 
-% (in this case, years)
-% \authNoted{Do you mean 30 years?
-% Should we rather say ``With 30 years of data''---MKH.
-% Perhaps there is a better word than sample, but it isn't really primarily
-% about time but about the number of rows of data.  That happens to equal the number
-% of years of data in this case but isn't the real issue.
-% For now, I'm punting and just using $N \approx 30$. ---rjp}%
-% and with CES functions (Equations~\ref{eq:CESkl} and~\ref{eq:CESkle}--\ref{eq:CESekl})
-% having as many as six parameters,
 It can be difficult to provide an \emph{a priori} justification
@@
 In an investigation of whether energy is important, for example,
-we may consider the null hypothesis that $\alpha_e = 0$.  
-In the ($kl$)$e$ nesting, 
+we may consider the null hypothesis that $\alpha_3 = 0$.  
+In the ($kl$)$e$ nesting for the CES model, 
 this null hypothesis is equivalent to $\delta = 1$.
 While there is an asymptotic theory for this case as well,%
-\authNote{%
-Randy: can you provide a reference for the asymptotic theory? ---MKH}%
+  \authNote{Randy: can you provide a reference for the asymptotic theory? ---MKH}
 the distributions are, in general,
@@
 
-%++++++++++++++++++++++++++++++
-\subsection{Bootstrap resampling algorithm}
-\label{sec:appendix_resampling}
-%++++++++++++++++++++++++++++++
-
 Bootstrapping is a statistical resampling technique for assigning
@@
 one can learn about the precision of the estimation method.
-**** Add some references here. ---rjp ****
-% \authNote{Add some references here. ---rjp}
+\authNote{Add some references here. ---rjp}
 
@@
 any particular year had been observed in a different year.
-Thus, a resampled response $\tilde Y'$ can be computed as
-**** Randy edit the following equations to reflect the fact that
-we're fitting in log space? ---MKH ****
-%
-\begin{equation}
+Thus, a resampled response $\tilde Y'$ can be computed as%
+\authNote{Randy: edit the following equations to reflect the fact that
+we're fitting in log space? ---MKH}
+
+\begin{equation} \label{eq:resampled_y}
   \tilde Y_i' = \hat y_i \pm r_j \; ,
@@
 %
-\begin{equation}
+\authNote{Do we need this equation for $r_i$ here? We already have Equation~\ref{eq:residual}.}%
+%
+\begin{equation} \label{eq:residual_2}
   r_i = y_i - \hat y_i \; .

### 2015-10-05 Articles/Article_EcolEcon_2015/Paper0/Paper0-Resampling.Rnw
Editing methods section.

@@
 and permutations of capital~($k$), labor~($l$), and energy~($e$).
+The $(kl)e$ nesting has $x_1 = k$, $x_2 = l$, and $x_3 = e$; 
+the $(le)k$ nesting has $x_1 = l$, $x_2 = e$, and $x_3 = k$; and
+the $(ek)l$ nesting has $x_1 = e$, $x_2 = k$, and $x_3 = l$.
 
@@
 \begin{equation} \label{eq:sum_betas}
-  \alpha_1 + \alpha_2 + \alpha_3 = 1
+  \alpha_1 + \alpha_2 + \alpha_3 = 1 \; .
 \end{equation}
-%
-for all nests.
 
@@
 for the CES model,
-we use an ordinary least squares~(OLS) approach.
-The objective of the OLS analysis is minimization of the sum of squared errors~(Equation~\ref{eq:sse}).
+we use an ordinary least squares~(OLS) approach, 
+wherein the objective is minimization of the sum of squared errors~(Equation~\ref{eq:sse}).
 We estimate parameters using the \texttt{R}~\citep{R} package \texttt{micEconCES}
@@
 with significant customization
-to estimate parameters in the CES production function.
+to estimate parameters.
 Our CES parameter estimation algorithm starts with an eleven-value grid search
 in $\rho_1$ and $\rho$
-(9, 2, 1, 0.43, 0.25, 0.1, -0.1, -0.5, -0.75, -0.9, -0.99),
-corresponding to $\sigma_1$ and $\sigma$ values of
-0.1, 0.33, 0.5, 0.7, 0.8, 0.9, 1.11, 2, 4, 10, and 100,
-respectively.
+(9, 2, 1, 0.43, 0.25, 0.1, -0.1, -0.5, -0.75, -0.9, -0.99).
 During the grid search, values of $\rho_1$ and $\rho$ are fixed,
@@
 
-Next, a gradient search (using both \texttt{PORT} and \texttt{L-BFGS-B})
+Next, a gradient search (using \texttt{PORT} and \texttt{L-BFGS-B} algorithms available in \texttt{micEconCES})
 is attempted wherein all parameters
@@
 In our case, we formed resamples by adding to the fitted
-response~($\hat{y}$) the product of a residual from the original CES function fit
-(see Figure~\ref{fig:r_kle}) and
+response~($\hat{y}$) the product of a residual from the original function (Cobb-Douglas or CES) fit
+and
 random sign ($-1$ or $1$, each with probability $0.5$).
@@
 are chosen at random (with replacement).
-We repeated the resampling process 1000 times for each
-combination of growth model and country,
-both with and without energy as appropriate.
+We repeated the resampling process 1000 times.
 
@@
 First, model parameters are highly constrained, and confidence intervals often violate the constraints.
-For example, a result of $\alpha_k = 0.25 \pm 0.3$ is nonsensical,
-because $ \alpha_k \in [0, 1]$.
+For example, a result of $\alpha_1 = 0.25 \pm 0.3$ is nonsensical,
+because $ \alpha_1 \in [0, 1]$.
 Second, true confidence intervals for constrained parameters are often asymmetric
-(e.g., $\alpha_k = 0.2 + 0.1, -0.05$),
+(e.g., $\alpha_1 = 0.2 + 0.1, -0.05$),
 but the standard error approach yields symmetric confidence intervals.
 The resampling approach that we employed both respects constraints
-and allows for asymmetric confidence intervals.%
-In addition, we choose to present parameter uncertainty results visually
-(see Figures~\ref{fig:resample_lambda_theta}--\ref{fig:resample_alpha}),
-both because the resampling technique lends itself to visual presentation and
-because we believe visual comparison is more effective
-in communicating results than endless tables of numbers.
+and allows for asymmetric confidence intervals.
 

### 2015-10-05 Articles/Article_EcolEcon_2015/Paper0/Paper0-Resampling.Rnw
Fix to methods section.

@@
 boundary of (the economically meaningful portion of) the parameter space.
-In an investigation of whether energy is important, for example,
+In an investigation of the marginal productivity of energy 
+in the $(kl)e$ nesting of the CES model, for example,
 we may consider the null hypothesis that $\alpha_3 = 0$.  
-In the ($kl$)$e$ nesting for the CES model, 
-this null hypothesis is equivalent to $\delta = 1$.
+This null hypothesis is equivalent to $\delta = 1$.
 While there is an asymptotic theory for this case as well,%

### 2015-10-09 Articles/Article_EcolEcon_2015/Paper0/Paper0-Resampling.Rnw
Edit text to eliminate sigma in favor of rho.

@@
 
-**** Go completely generic everywhere ($x_1$ instead of $k$). ****
-
 The Cobb-Douglas production function 
@@
 e is the base of the natural logarithm, 
-$\lambda$ is represents the pace of technological progress,
+$\lambda$ is the so-called Solow residual,
 $t$ is time measured in years,
@@
 Time~($t$) is indexed (by difference) relative to an initial year.
-After indexing, $\theta$ is expected to be near unity,
-but no other parameters change.%
+Due to indexing, $\theta$ is expected to be near unity,
+but no other parameters are affected.%
   \footnote{Dimensionless, indexed quantities are represented by lower-case symbols 
@@
 
-The Constant Elasticity of Substitution~(CES) model 
+The Constant Elasticity of Substitution~(CES) production function 
 is given as
@@
 thereby providing constant returns to scale.
+$\alpha_3$ was recovered with $\alpha_3 = 1 - \alpha_1 - \alpha_2$.
 The \texttt{R} \citep{R} function \texttt{lm} was used to estimate 
@@
 %
-where the residual is given as
+where
 %
@@
 $\hat{y}_i$ is the fitted value for economic output at time $t_i$.
-$\alpha_3$ was recovered with $\alpha_3 = 1 - \alpha_1 - \alpha_2$.
 
@@
 for capital and labor ($\hat{\alpha}_1 = 0.3$ and $\hat{\alpha}_2 = 0.7$).
-Under these conditions, $\hat{\alpha}_3$ is assumed to be $0$.
+Under these conditions, $\hat{\alpha}_3$ is assumed to be $0$.%
+  \authNote{Need to fix the discussion of $\alpha$s and the CSP.}
 
@@
 are allowed to float.
-The starting values for fitting parameters are taken from
+The starting values for parameters are taken from
 the grid search point that provided the lowest sum of squared errors~(\sse).
@@
 \texttt{L-BFGS-B} often reports convergence
-and \texttt{PORT} does not for the same data
+and \texttt{PORT} does not for the same historical data
 (i.e., for the same $y$, $k$, $l$, and $e$ time series).
@@
 The bottom (unnumbered) row of Table~\ref{tab:CES_boundary_models}
-shows the generic three-factor CES equation.
+is a repeat of Equation~\ref{eq:CESgeneric}.
 Each degenerate equation provides a boundary model.
@@
 Table~\ref{tab:CES_boundary_models} includes many dashes~(``---'')
-indicating that many fitting parameters are unknowable
+indicating that many parameters are unknowable
 in the boundary models.
@@
 were to find an \sse{} minimum along that boundary,
-it would report values for $\sigma_1$ and $\sigma$
+it would report values for $\rho_1$ and $\rho$
 \emph{in addition to} $\theta$, $\lambda$, $\delta_1$~(which will be unity),
@@
 meaningless, because they are unknowable,
-values for $\sigma_1$ and $\sigma$.
+values for $\rho_1$ and $\rho$.
 Fitting with the boundary models
@@
 
+**** Change to talk about $\rho$ only. ****
 Boundary models obtained when $\delta_1$ or $\delta$ is at an extreme value
@@
 Table~\ref{tab:CES_boundary_models}.
-When $\sigma_1$ or $\sigma$ is 0,
+When $\rho_1$ or $\rho$ is $\infty$,
 factors of production are perfect complements
@@
   \footnote{
-  E.g., when $\sigma_1 = 0$ and $\delta~=~1$, the Leontief model is
+  E.g., when $\rho_1 = \infty$ and $\delta~=~1$, the Leontief model is
   $y = \theta A \min (x_1, x_2)$, row 4 in Table~\ref{tab:CES_boundary_models}.
   }
-When $\sigma_1$ or $\sigma$ is $\infty$,
+When $\rho_1$ or $\rho$ is $-1$,
 factors of production are perfect substitutes
@@
   \footnote{
-  E.g., when $\sigma_1 = \infty$ and $\delta~=~1$, the linear model is
+  E.g., when $\rho_1 = -1$ and $\delta~=~1$, the linear model is
   $y = \theta A \left[ \delta_1 x_1 + (1 - \delta_1) x_2 \right]$,
@@
       \toprule
-      & $\delta_1$  & $\sigma_1$ & $\delta$   & $\sigma$ & Boundary model \\
+      & $\delta_1$     & $\rho_1$   & $\delta$   & $\rho$   & Boundary model \\
       \midrule
@@
       \midrule
-      4. & ---         & 0          & 1          & ---      & $y = \theta A \min
+      4. & ---         & $\infty$   & 1          & ---      & $y = \theta A \min
       (x_1, \, x_2)$ \\
-      5. & 1           & ---        & ---        & 0        & $y = \theta A \min
+      5. & 1           & ---        & ---        & $\infty$ & $y = \theta A \min
       (x_1, \, x_3)$ \\
-      6. & 0           & ---        & ---        & 0        & $y = \theta A \min
+      6. & 0           & ---        & ---        & $\infty$ & $y = \theta A \min
       (x_2, \, x_3)$ \\
 %
-      7. &             & $\infty$   & 1          & ---
+      7. &             & $-1$       & 1          & ---
             & $y = \theta A \left[ \delta_1 x_1 + (1 - \delta_1) x_2 \right]$ \\
 %
-      8. & 1           & ---        &            & $\infty$
+      8. & 1           & ---        &            & $-1$
             & $y = \theta A \left[ \delta x_1 + (1 - \delta) x_3 \right]$ \\
 %
-      9. & 0           & ---        &            & $\infty$
+      9. & 0           & ---        &            & $-1$
             & $y = \theta A \left[ \delta x_2 + (1 - \delta) x_3 \right]$ \\
@@
       \midrule
-     13. & ---         & 0          & ---        & 0        & $y = \theta A \min
+     13. & ---         & $\infty$   & ---        & $\infty$   & $y = \theta A \min
      (x_1, \, x_2, \, x_3)$ \\
 %
-     14. & ---         & 0          &            & $\infty$
+     14. & ---         & $\infty$   &            & $-1$
             & $y = \theta A \left[ \delta \min (x_1, \, x_2) + \left( 1 - \delta
@@
 %
-     15. &             & $\infty$   & ---        & 0
+     15. &             & $-1$       & ---        & $\infty$
             & $y = \theta A \min \left[ \delta_1 x_1 + \left(1 - \delta_1
@@
 %
-     16. &             & $\infty$   &            & $\infty$
+     16. &             & $-1$       &            & $-1$
             & $y = \theta A \left\{ \delta \left[ \delta_1 x_1 + \left( 1 -
@@
 %
-     17. & ---         & 0          &            &
+     17. & ---         & $\infty$   &            &
             & $y = \theta A \left\{ \delta \left[ \min \left( x_1, \, x_2
@@
 %
-     18. &            &            & ---     & 0
+     18. &            &            & ---         & $\infty$
             & $y = \theta A \min \left\{ \left[ \delta_1 x_1^{-\rho_1}
@@
 %
-     19. &             &            &            & $\infty$
+     19. &             &            &            & $-1$
             & $y = \theta A \left\{ \delta \left[ \delta_1 x_1^{-\rho_1}
@@
 %
-     20. &             & $\infty$   &            &
+     20. &             & $-1$       &            &
             & $y = \theta A \left\{ \delta \left[ \delta_1 x_1
@@
 ($j$,~typically different from $i$)
-of the residual~($r_j$)
+of the residual~($r_j$) in Equation~\ref{eq:resampled_y}
 are chosen at random (with replacement).
@@
 obtained from the fit to historical data (the ``base parameters'').
-When these resample parameters are highly variable,
+When the distribution of these resample parameters 
+(the ``bootstrap resample distribution'') 
+is highly variable,
 it is an indication
@@
 Lack of precision can stem from a number of factors, most obviously
-a poor model fit,
+a poor model fit to historical data,
 low model sensitivity to one or more parameters, or
@@
 
-We choose the resampling approach instead of the more-common technique
+We choose the resampling approach to estimating parameter precision
+instead of the more-common technique
 of estimating confidence intervals from standard errors for two reasons.
@@
 %++++++++++++++++++++++++++++++
-
-Refer to other paper for historica data.
 

### 2015-10-09 Articles/Article_EcolEcon_2015/Paper0/Paper0-Resampling.Rnw
Fix misspelling.
Edits to framing.

@@
   \item Also, inspired by Ayres and Warr, 
-        we don’t want to assume elasticity of substitution 
+        we don't want to assume elasticity of substitution 
         of unity as CD does.
@@
     \item Ayres and Warr used a non-standard production function.
-          Will their insights hold true for standard production functinos like Cobb-Douglas and CES?
+          Will their insights hold true for standard production functions like Cobb-Douglas and CES?
 
@@
 
-  \item Standard approaches assume normal distributions for model parameters. 
+  \item Non-linear fitting has several complications in the fitting process.
+
+  \item Furthermore, standard approaches to determining parameter precision 
+        for linear and non-linear fitting
+        assume normal distributions for model parameters. 
         In the non-linear world of CES, 
         those assumptions aren't appropriate. 
-        Need a new approach in the non-CD world.
+        Need new approaches in the non-CD world.
 
@@
 %
-This paper explores and justifies those choices by
+This paper explores and justifies those choices by:
 %
@@
 
-  \item comparing standard techniques and our approaches for the Cobb-Douglas production function and
+  \item comparing standard techniques and our approaches for estimating parameter precision
+        for the Cobb-Douglas production function, and
 
-  \item applying our techniques to the CES production production function.
+  \item applying our advanced techniques for parameter estimation
+        (including precision)
+        to the CES production production function.
 

### 2015-10-12 Articles/Article_EcolEcon_2015/Paper0/Paper0-Resampling.Rnw
Added first 2 sentences of Paper0.

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The book entitled
+\emph{The Economic Growth Engine: How Energy and Work Drive Material Prosperity} 
+\citep{Ayres:2010ug} 
+was a watershed moment in the understanding 
+of interactions between energy and the economy.
+It represents the culmination of a decade of fruitful inquiry by Ayres and Warr, 
+whose greatest insights
+(that energy matters in economic growth,
+that ``useful work'' dissipated at the point of production
+is an essential factor of production, and
+that the ``Cost Share Principle'' from neoclassical economics should be rejected)
+were inspired by Ecological Economics in one way or another.
 

### 2015-10-12 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
set up parent and child docs -- eliminate text from child doc

--- 2015-09-27 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
@@
-% This article has been prepared for publication in RStudio with knitr.
-% According to http://www.elsevier.com/author-schemas/the-elsarticle-latex-document-class, we should be using the
-% elsarticle.cls file.
-% According to http://cdn.elsevier.com/assets/pdf_file/0006/109392/journal_refstyles.pdf, we should be using
-% elsarticle-template-2-harv.tex as the template for the text.
-% Furthermore, we should be using model2-names.bst for the bibliographic references.
-% The approach here is to load the frontmatter and backmatter from elsarticle-template-2-harv.tex
-% both ahead of and behind the text for our paper.
-% -- Matthew Kuperus Heun, 2014-08-01
-
-%% This is file `elsarticle-template-2-harv.tex',
-%%
-%% Copyright 2009 Elsevier Ltd
-%%
-%% This file is part of the 'Elsarticle  Bundle'.
-%% ---------------------------------------------
-%%
-%% It may be distributed under the conditions of the LaTeX Project Public
-%% License, either version 1.2 of this license or (at your option) any
-%% later version.  The latest version of this license is in
-%%    http://www.latex-project.org/lppl.txt
-%% and version 1.2 or later is part of all distributions of LaTeX
-%% version 1999/12/01 or later.
-%%
-%% The list of all files belonging to the 'Elsarticle Bundle' is
-%% given in the file `manifest.txt'.
-%%
-%% Template article for Elsevier's document class `elsarticle'
-%% with harvard style bibliographic references
-%%
-%% $Id: elsarticle-template-2-harv.tex 155 2009-10-08 05:35:05Z rishi $
-%% $URL: http://lenova.river-valley.com/svn/elsbst/trunk/elsarticle-template-2-harv.tex $
-%%
-\documentclass[preprint,authoryear,12pt]{elsarticle}
-
-%% Use the option review to obtain double line spacing
-%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}
-
-%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
-%% for a journal layout:
-%% \documentclass[final,authoryear,1p,times]{elsarticle}
-%% \documentclass[final,authoryear,1p,times,twocolumn]{elsarticle}
-%% \documentclass[final,authoryear,3p,times]{elsarticle}
-%% \documentclass[final,authoryear,3p,times,twocolumn]{elsarticle}
-%% \documentclass[final,authoryear,5p,times]{elsarticle}
-%% \documentclass[final,authoryear,5p,times,twocolumn]{elsarticle}
-
-%% if you use PostScript figures in your article
-%% use the graphics package for simple commands
-%% \usepackage{graphics}
-%% or use the graphicx package for more complicated commands
-%% \usepackage{graphicx}
-%% or use the epsfig package if you prefer to use the old commands
-%% \usepackage{epsfig}
-
-%% The amssymb package provides various useful mathematical symbols
-\usepackage{amssymb}
-%% The amsthm package provides extended theorem environments
-%% \usepackage{amsthm}
-
-\usepackage{wrapfig}    % Allows wrapping of text around figures
-\usepackage{soul}       % Provides strikethrough text
-\usepackage{float}      % Allows precise positioning of tables and figures within the text
-\usepackage{amsmath}    % Allows \begin{equation*} \end{equation*} for unnumbered equations
-\usepackage{multirow}   % To create multirow tables
-\usepackage{hyperref}   % To create hyperlinks in the paper
-\usepackage{microtype}  % produces hanging punctuation and beautiful type
-\usepackage{booktabs}   % for beautiful tables
-\usepackage{dcolumn}    % aligns table columns at decimal places
-
-% From http://economics.utoronto.ca/osborne/latex/BIBTEX.HTM
-\newcommand{\citeapos}[1]{\citeauthor{#1}'s (\citeyear{#1})} % Posessive citations.
-
-%% The lineno packages adds line numbers. Start line numbering with
-%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
-%% for the whole article with \linenumbers after \end{frontmatter}.
-%% \usepackage{lineno}
-
-%% natbib.sty is loaded by default. However, natbib options can be
-%% provided with \biboptions{...} command. Following options are
-%% valid:
-
-%%   round  -  round parentheses are used (default)
-%%   square -  square brackets are used   [option]
-%%   curly  -  curly braces are used      {option}
-%%   angle  -  angle brackets are used    <option>
-%%   semicolon  -  multiple citations separated by semi-colon (default)
-%%   colon  - same as semicolon, an earlier confusion
-%%   comma  -  separated by comma
-%%   authoryear - selects author-year citations (default)
-%%   numbers-  selects numerical citations
-%%   super  -  numerical citations as superscripts
-%%   sort   -  sorts multiple citations according to order in ref. list
-%%   sort&compress   -  like sort, but also compresses numerical citations
-%%   compress - compresses without sorting
-%%   longnamesfirst  -  makes first citation full author list
-%%
-%% \biboptions{longnamesfirst,comma}
-
-% \biboptions{}
-
-\journal{Ecological Economics}
-
-\begin{document}
+\Sexpr{set_parent('Paper0/Paper0-Resampling.Rnw')}
+
+\section{Begin EcolEcon2015A}
 
@@
   eval=TRUE,
+  include = FALSE,
   # ********************************************************
@@
 
-\begin{frontmatter}
-
-%% Title, authors and addresses
-
-%% use the tnoteref command within \title for footnotes;
-%% use the tnotetext command for the associated footnote;
-%% use the fnref command within \author or \address for footnotes;
-%% use the fntext command for the associated footnote;
-%% use the corref command within \author for corresponding author footnotes;
-%% use the cortext command for the associated footnote;
-%% use the ead command for the email address,
-%% and the form \ead[url] for the home page:
-%%
-%% \title{Title\tnoteref{label1}}
-%% \tnotetext[label1]{}
-%% \author{Name\corref{cor1}\fnref{label2}}
-%% \ead{email address}
-%% \ead[url]{home page}
-%% \fntext[label2]{}
-%% \cortext[cor1]{}
-%% \address{Address\fnref{label3}}
-%% \fntext[label3]{}
-
-\title{Energy and the CES production function}
-
-%% use optional labels to link authors explicitly to addresses:
-%% \author[label1,label2]{<author name>}
-%% \address[label1]{<address>}
-%% \address[label2]{<address>}
-
-\author[IST]{Jo\~{a}o dos Santos}
-\author[CalvinEngr]{Matthew Kuperus Heun\corref{cor1}}
-\author[Leeds]{Paul Brockway}
-\ead{mkh2@calvin.edu}
-\author[Leeds]{Marco Sekai}
-\author[IST]{Tiago Domingos}
-\author[CalvinMath]{Randall Pruim}
-
-\address[IST]{IST, Lisbon, Portugal}
-\address[Leeds]{Leeds University, Leeds, UK}
-\address[CalvinEngr]{Engineering Department, Calvin College, Grand Rapids, MI 49546, USA}
-\address[CalvinMath]{Mathematics \& Statistics Department, Calvin College, Grand Rapids, MI 49546, USA}
-\cortext[cor1]{Corresponding author}
-
-\begin{abstract}
-%% Text of abstract
-**** Add abstract ****
-\end{abstract}
-
-\begin{keyword}
-%% keywords here, in the form: keyword \sep keyword
-economic growth \sep exergy \sep energy \sep CES
-%% MSC codes here, in the form: \MSC code \sep code
-%% or \MSC[2008] code \sep code (2000 is the default)
-\end{keyword}
-
-\end{frontmatter}
-
-% \linenumbers
-%% main text
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction} 
-\label{sec:Introduction}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-This is a study of the effects of quality-adjusted production function inputs
-on the importance of energy in the production function.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Coordinates of Analysis} 
-\label{sec:Coordinates}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-This section describes the coordinates of analysis and briefly reviews 
-literature related to each.
-
-%++++++++++++++++++++++++++++++
-\subsection{Mathematical Forms of the Energy-augmented Production Function} 
-\label{sec:Prod_Func_Forms}
-%++++++++++++++++++++++++++++++
-
-In this paper, we assess a prominent energy-augmented production function:
-Constant Elasticity of Substitution (CES).
-The CES model is assessed relative to 
-a model of exponential growth only.
-The following subsections describe each.
-
-%------------------------------
-\subsubsection{Constant Elasticity of Substitution Production Function (CES)} 
-\label{sec:CES}
-%------------------------------
-
-The energy-augmented 
-Constant Elasticity of Substitution (CES) production function%
-  \footnote{
-  We use the The \texttt{R} 
-  % \citep{R} 
-  package \texttt{micEconCES} 
-  % \citep{Henningsen:2011td} 
-  to estimate the CES production function.
-  }
-can be given as
-%
-\begin{equation} \label{eq:CESgeneric}
-  y = \gamma \: A \: \left\{\delta \left[\delta_1 x_1^{-\rho_1} 
-      + (1-\delta_1)x_2^{-\rho_1} \right]^{\rho/\rho_1} 
-      + (1-\delta) x_3^{-\rho} \right\}^{-1/\rho}; 
-      A \equiv \mathrm{e}^{\lambda (t-t_0)},
-\end{equation}
-%
-where
-$y \equiv Y/Y_{0}$,
-$\gamma$ is a scale parameter,
-e is the base of the natural logarithm, 
-$\lambda$ is the Solow residual (often thougth to represent the pace of technological progress),
-$t$ (time) is measured in years,
-$x_1$, $x_2$, and $x_3$ are factors of production
-and permutations of capital~($k$), labor~($l$), and energy~($e$),
-$k \equiv K/K_{0}$, 
-$l \equiv L/L_{0}$, 
-$Y$ (economic output) is represented by GDP, 
-$K$ (capital) is expressed in currency units, 
-$L$ (labor) is expressed in workers or work-hours/year, and
-the 0 subscript indicates values at an initial year.%
-  \footnote{Dimensionless, indexed quantities are represented by 
-  lower-case symbols 
-  ($y$, $k$, $l$, $e$, $q$, $x$, and $u$), and dimensional 
-  quantities are represented by upper-case symbols 
-  ($Y$, $K$, $L$, $E$, $Q$, $X$, and $U$). 
-  Model parameters are represented by Greek letters
-  ($\alpha_1$, $\alpha_2$, $\lambda$, $\theta$).
-  }
-The CES model without energy is given in Equation~\ref{eq:CESkl}.
-%
-\begin{equation} \label{eq:CESkl}
-  y = \gamma \: A \: \left[\delta_1 k^{-\rho_1} 
-      + (1-\delta_1)l^{-\rho_1} \right]^{-1/\rho_1}; 
-      A \equiv \mathrm{e}^{\lambda (t-t_0)} . 
-\end{equation}
-%
-Equation~\ref{eq:CESkle} augments Equation~\ref{eq:CESkl} with energy 
-using a ($kl$)($e$) nesting structure, as is typical in the literature. 
-Equation~\ref{eq:CESkl} is a degenerate form of Equation~\ref{eq:CESkle} 
-where $\delta \rightarrow 1$. 
-%
-\begin{equation} \label{eq:CESkle}
-  y = \gamma \: A \: \left\{\delta \left[\delta_1 k^{-\rho_1} 
-      + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1} 
-      + (1-\delta) e^{-\rho} \right\}^{-1/\rho}; 
-      A \equiv \mathrm{e}^{\lambda (t-t_0)}.
-\end{equation}
-%
-In the CES production function, 
-$\gamma$ is a fitting parameter that accounts for an atypical first year. 
-The fitting parameters $\rho_1$ and $\rho$ indicate elasticities 
-of substitution ($\sigma_1$ and $\sigma$).
-The elasticity of substitution 
-between capital ($k$) and labor ($l$) is given by 
-$\sigma_1 = \frac{1}{1+\rho_1}$, and
-the elasticity of substitution between ($kl$) and ($e$) is given by 
-$\sigma = \frac{1}{1+\rho}$. 
-As $\rho_1 \rightarrow 0$, $\sigma_1 \rightarrow 1$,
-and the embedded CES production function for $k$ and $l$ degenerates 
-to the Cobb-Douglas production function.
-Similarly, as $\rho \rightarrow 0$, $\sigma \rightarrow 1$,
-and the CES production function for $(kl)$ and $(e)$ degenerates 
-to the Cobb-Douglas production function.
-As $\sigma \rightarrow \infty$ ($\rho \rightarrow -1$), 
-($kl$) and ($e$) are perfect substitutes. 
-As $\sigma \rightarrow 0$ ($\rho \rightarrow \infty$), 
-($kl$) and ($e$) are perfect complements: 
-no substitution is possible. Similarly, 
-as $\sigma_1 \rightarrow 0$ ($\rho_1 \rightarrow \infty$),
-$k$ and $l$ are perfect complements.
-$\delta_1$ describes the relative importance of capital ($k$)
-and labor ($l$), and
-$\delta$ describes the importance of ($kl$) relative to ($e$).
-
-Constraints on the fitting parameters include 
-$\delta_1 \in [0,1]$,
-$\delta \in [0,1]$,
-$\rho_1 \in [-1,0) \cup (0,\infty)$, and
-$\rho \in [-1,0) \cup (0,\infty)$.
-
-Two other nestings of the factors of production ($k$, $l$, and $e$)
-are possible with the CES model.
-%
-\begin{equation} \label{eq:CESlek}
-  y = \gamma \: A \: \left\{\delta \left[\delta_1 l^{-\rho_1} 
-      + (1-\delta_1) e^{-\rho_1} \right]^{\rho/\rho_1} 
-      + (1-\delta) k^{-\rho} \right\}^{-1/\rho}; 
-      A \equiv \mathrm{e}^{\lambda (t-t_0)}
-\end{equation}
-%
-\begin{equation} \label{eq:CESekl}
-  y = \gamma \: A \: \left\{\delta \left[\delta_1 e^{-\rho_1} 
-      + (1-\delta_1) k^{-\rho_1} \right]^{\rho/\rho_1} 
-      + (1-\delta) l^{-\rho} \right\}^{-1/\rho}; 
-      A \equiv \mathrm{e}^{\lambda (t-t_0)}
-\end{equation}
-% 
-Note that $\rho$ ($\sigma$), $\rho_1$ ($\sigma_1$), $\delta$, and $\delta_1$ have different
-meanings depending upon the nesting of the factors of production.
-
-For the CES model, factors shares~($\alpha_1$, $\alpha_2$, and $\alpha_3$) are calculated by
-$\alpha_1 = \delta_1$, $\alpha_2 = 1 - \delta_1$, and $\alpha_3 = 0$ 
-for the CES model with two factors of production
-and by 
-$\alpha_1 = \delta \delta_1$, $\alpha_2 = \delta(1 - \delta_1)$, and $\alpha_3 = 1 - \delta$
-for the CES model with three factors of production and the ($kl$)$e$ nesting.
-The values of $\alpha_1$, $\alpha_2$, and $\alpha_3$ are interpreted as
-factor shares for capital, labor, and energy, respectively,
-as shown in Table \ref{tab:CES_abg_equations}.
-
-\begin{table} \caption{Equations for $\alpha_1$, $\alpha_2$, and $\alpha_3$ 
-                        (factor shares for capital, labor, and energy, respectively)
-                        for the various CES nestings.} 
-\label{tab:CES_abg_equations} 
-  \begin{center}
-    \begin{tabular}{c c c c} 
-      \toprule
-      Nesting    & $\alpha_1$              & $\alpha_2$              & $\alpha_3$       \\
-      \midrule
-      ($kl$) \;  & $\delta_1$              & $1 - \delta_1$          & 0          \\
-      ($kl$)$e$  & $\delta \delta_1$       & $\delta (1 - \delta_1)$ & $1 - \delta$ \\   
-      ($le$)$k$  & $1 - \delta$            & $\delta \delta_1$       & $\delta (1 - \delta_1)$ \\
-      ($ek$)$l$  & $\delta (1 - \delta_1)$ & $1 - \delta$            & $\delta \delta_1$ \\
-      \bottomrule
-    \end{tabular}
-  \end{center}
-\end{table}
-
-%------------------------------
-\subsubsection{Exponential Production Function (reference model)} 
-\label{sec:exp}
-%------------------------------
-
-We define an exponential-only reference model for economic growth
-in Equation~\ref{eq:exponential-only-model}.
-%
-\begin{equation} \label{eq:exponential-only-model}
-  y = \theta A \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)} \; .
-\end{equation}
-%
-We expect that the reference model
-will have a larger fitted Solow residual term than
-the CES model, because no factors of production are
-included in the reference model to drive economic growth.
-Indeed, in the reference model, 
-all economic growth is attributed to the Solow residual~($\lambda$).
-
-In contrast, it is not necessarily true that 
-CES models will exhibit lower $sse$ than the reference model
-shown in Equation~\ref{eq:exponential-only-model}.
-The CES model has more fitting parameters,
-but it incorporates the factors of production
-at constant returns to scale. 
-The reference model has $\alpha_1 + \alpha_2 + \alpha_3 = 0$,
-whereas the CES model~(Equation~\ref{eq:CESgeneric})
-implicitly assumes constant returns to scale.
-Thus, if the factors of production~($\alpha_1$, $\alpha_2$, and $\alpha_3$) 
-are poorly correlated to output~($y$),
-the constant returns to scale constraint may cause higher $sse$ for
-the CES model relative to the reference model.
-
-%++++++++++++++++++++++++++++++
-\subsection{Economies} 
-\label{sec:Economies}
-%++++++++++++++++++++++++++++++
-
-Discuss economies here.
-
-UK and Portugal.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Sources of Data}
-\label{sec:Sources_of_Data}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Discuss data sources here.
-
-%++++++++++++++++++++++++++++++
-\subsection{Historical Data} 
-\label{sec:Historical_Data}
-%++++++++++++++++++++++++++++++
-
-Historical data are stored in the \texttt{IST} and \texttt{Leeds} data sets.
-
 <<Formulas>>=
@@
 @
-
-For unadjusted variables, we use the time series shown in Table~\ref{tab:unadjusted_variables}.
-
-\begin{table} \caption{Unadjusted time-series variables.} 
-\label{tab:unadjusted_variables} 
-  \begin{center}
-    \begin{tabular}{r l l} 
-      \toprule
-      Variable    & Portugal           & UK                 \\
-      \midrule
-      Output      & \Sexpr{summands(formulas$PT$unadjusted, n=1, right=FALSE)}   
-                                                             & \Sexpr{summands(formulas$UK$unadjusted, n=1, right=FALSE)}\\
-      Capital     & \Sexpr{summands(formulas$PT$unadjusted, 1)} & \Sexpr{summands(formulas$UK$unadjusted, 1)} \\
-      Labor       & \Sexpr{summands(formulas$PT$unadjusted, 2)} & \Sexpr{summands(formulas$UK$unadjusted, 2)} \\
-      Energy      & \Sexpr{summands(formulas$PT$unadjusted, 3)} & \Sexpr{summands(formulas$UK$unadjusted, 3)} \\
-      \bottomrule
-    \end{tabular}
-  \end{center}
-\end{table}
-
-For quality-adjusted variables, we use the time series shown in Table~\ref{tab:quality_adjusted_variables}.
-
-\begin{table} \caption{Quality-adjusted time series variables.} 
-\label{tab:quality_adjusted_variables} 
-  \begin{center}
-    \begin{tabular}{r l l} 
-      \toprule
-      Variable    & Portugal         & UK               \\
-      \midrule
-      Output      & \Sexpr{summands(formulas$PT$adjusted, n=1, right=FALSE)}   
-                                                           & \Sexpr{summands(formulas$UK$adjusted, n=1, right=FALSE)} \\
-      Capital     & \Sexpr{summands(formulas$PT$adjusted, 1)} & \Sexpr{summands(formulas$UK$adjusted, 1)} \\
-      Labor       & \Sexpr{summands(formulas$PT$adjusted, 2)} & \Sexpr{summands(formulas$UK$adjusted, 2)} \\
-      Energy      & \Sexpr{summands(formulas$PT$adjusted, 3)} & \Sexpr{summands(formulas$UK$adjusted, 3)} \\
-      \bottomrule
-    \end{tabular}
-  \end{center}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Parameter Estimation (Without Cost-share Theorem)}
-\label{sec:parameter_estimation_noCSP}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Parameter estimation is accomplished with \texttt{formula}s of the form
-% %
-% \begin{equation} \label{eq:formulas}
-%   y \sim x_1 + x_2 + x_3 + time,
-% \end{equation}
-% %
-% where $y$ is economic output and 
-% $x_1$, $x_2$, and $x_3$ are factors of production
-% and permutations of
-% capital ($k$), labor ($l$), and energy ($e$).
-% (The factors of production may be quality-adjusted.)
-% $time$ is the time variable, usually \texttt{iYear}. 
-% The \texttt{formula}s are used in a fitting function such as 
-% \texttt{cdModel} to create a \texttt{model} object.
-% The function \texttt{naturalCoef} extracts reasonable
-% coefficients from \texttt{model} objects.
-% 
-% Note that in the fitting process for the Cobb-Douglas equation,
-% $\texttt{scale} = \theta$, 
-% $\alpha_1 = \alpha$,
-% $\alpha_2 = \beta$, and
-% $\alpha_3 = \gamma$,
-% when the \texttt{formula} is specified as 
-% %
-% \begin{equation} \label{eq:formula_kle}
-%   \texttt{y} \sim \texttt{k + l + e + time}.
-% \end{equation}
-% %
-% Note that for the CES model, $\texttt{scale} = \gamma$ and is expected to be close to unity.
-
-The models being fit can be described by the algebraic form of the model 
-(Cobb-Douglas, CES, etc.) and a formula that enumerates 
-which data variables are being used in which roles to fit the model.  
-A formula of the form
-%
-\begin{equation} \label{eq:formulas-3-factor}
-y \sim x_1 + x_2 + x_3 + t,
-\end{equation}
-%
-or 
-%
-\begin{equation} \label{eq:formulas-2-factor}
-y \sim x_1 + x_2 + t,
-\end{equation}
-%
-describes the economic output variable ($y$, usually \texttt{iGDP},
-                                        indexed GDP) 
-and the factors of production ($x_1$, $x_2$, and $x_3$,
-                               which will be some measure of capital, labor, and energy, 
-                               but perhaps not in that order), 
-and a time variable ($t$, usually \texttt{iYear}, 
-                     the number of years since the beginning of data collection).  
-All of the models assume an error term that is additive on the 
-logarithmic scale and are fit by the method of least squares.  
-Model fitting provides estimates for all parameters in the model.
 
@@
 
-<<Resampling>>=
-resampleCoeffsFilename <- "EcolEcon2015kleResampleCoeffs.rds"
-resampleModelsFilename <- "EcolEcon2015kleResampleModels.rds"
+<<Resampling-CD>>=
+print("Top of Resampling-CD")
+
+resampleCoeffsCDFilename <- "EcolEcon2015ResampleCoeffsCD.rds"
+resampleModelsCDFilename <- "EcolEcon2015ResampleModelsCD.rds"
+if (rerunResampling){
+  resamplesCD <- leaf_apply(models, class = "CDEmodel", f = function(model, id){
+    id_components <- strsplit(id, split = "[.]")[[1]]
+    print(id_components)
+    resamples <- resampledFits(model, method = "wild", n = nResamples)
+    resamples$coeffs <- mutate(
+      resamples$coeffs, 
+      Country = id_components[[1]],
+      flavor = id_components[[2]],
+      energy = id_components[[3]],
+      model = id_components[[4]]
+    )
+    return(resamples)
+  })
+  # Resample coefficients
+  resampleCoeffsCD <- lapply(resamplesCD, function(resample){
+    resample$coeffs
+  }) %>% plyr::rbind.fill()
+  saveRDS(resampleCoeffsCD, resampleCoeffsCDFilename)
+  # Resample models
+  # At present these resample models are stored in a "flat" list.
+  # We may want to change that later.
+  resampleModelsCD <- lapply(resamplesCD, function(resample){
+    resample$models
+  })
+  saveRDS(resampleModelsCD, resampleModelsCDFilename)
+} else {
+  resampleCoeffsCD <- readRDS(resampleCoeffsCDFilename)
+  resampleModelsCD <- readRDS(resampleModelsCDFilename)
+}
+@
+
+<<Resampling-CES-adjusted-kle>>=
+print("Top of Resampling-CES-adjusted-kle")
+
+resampleCoeffsCESFilename <- "EcolEcon2015kleResampleCoeffsCES.rds"
+resampleModelsCESFilename <- "EcolEcon2015kleResampleModelsCES.rds"
 if (rerunResampling){
@@
   modUK <- models$UK$adjusted$withE$CES$kle
-  resamplesPT <- resampledFits(modPT, method = "wild", n = nResamples)
-  resamplesUK <- resampledFits(modUK, method = "wild", n = nResamples)
+  resamplesCESPT <- resampledFits(modPT, method = "wild", n = nResamples)
+  resamplesCESUK <- resampledFits(modUK, method = "wild", n = nResamples)
   # Resample coefficients
-  resampleCoeffs <- rbind(cbind(resamplesPT$coeffs, Country="PT"), cbind(resamplesUK$coeffs, Country="UK"))
-  resampleCoeffs$energy <- TRUE
-  resampleCoeffs$nest <- "(kl)e"
-  saveRDS(resampleCoeffs, file = resampleCoeffsFilename)
+  resampleCoeffsCES <- rbind(cbind(resamplesCESPT$coeffs, Country="PT"), cbind(resamplesCESUK$coeffs, Country="UK"))
+  resampleCoeffsCES$energy <- TRUE
+  resampleCoeffsCES$nest <- "(kl)e"
+  saveRDS(resampleCoeffsCES, file = resampleCoeffsCESFilename)
   # Resample models
-  resampleModels <- list(PT=resamplesPT$models, UK=resamplesUK$models)
-  saveRDS(resampleModels, file = resampleModelsFilename)
+  resampleModelsCES <- list(PT=resamplesCESPT$models, UK=resamplesCESUK$models)
+  saveRDS(resampleModelsCES, file = resampleModelsCESFilename)
 } else {
-  resampleCoeffs <- readRDS(resampleCoeffsFilename)
-  resampleModels <- readRDS(resampleModelsFilename)
+  resampleCoeffsCES <- readRDS(resampleCoeffsCESFilename)
+  resampleModelsCES <- readRDS(resampleModelsCESFilename)
 }
@@
 <<ReModels>>=
+print("Top of ReModels")
+
 ReModels <-
   bind_rows(
-  leaf_apply(resampleModels, 
+  leaf_apply(resampleModelsCES, 
              function(x,id) {mod2oedf(x, id) %>% mutate(id = id)},
@@
 ### If there isn't a reason, probably we should stick with one naming convention.
+
+print("top of Fitted_and_Residuals")
 
@@
 
-%++++++++++++++++++++++++++++++
-\subsection{Fitting residuals} 
-\label{sec:fitting_residuals}
-%++++++++++++++++++++++++++++++
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
-\label{sec:results}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The primary results from this paper involve the effects of
-the following modeling decisions:
-rejecting (or adhering to) the cost share theorem,
-quality-adjusting (or not) the factors of production,
-including energy (or not) in the production function, and
-nesting (in the CES model).
-
-We evaluate the effects of these modeling decisions 
-first on goodness of fit and Solow residual,
-next on factor shares, and 
-finally on factor substitutability.
-
-%++++++++++++++++++++++++++++++
-\subsection{Goodness of fit and Solow residual} 
-\label{sec:fit_and_sr}
-%++++++++++++++++++++++++++++++
-
-%
-We can evaluate the effect of modeling decisions on 
-goodness of fit and Solow residual by
-calculating values relative to the reference model.
-To do so, we define 
-$\Delta \lambda$ and $\Delta sse$, where
-%
-\begin{equation} \label{eq:delta_lambda}
-  \Delta \lambda \equiv \lambda - \lambda_{ref}
-\end{equation}
-%
-and
-%
-\begin{equation} \label{eq:delta_sse}
-  \Delta sse \equiv sse - sse_{ref},
-\end{equation}
-%
-with~$\lambda_{ref}$ and $sse_{ref}$ being the values 
-of the Solow residual and $sse$ for the reference model, respectively.
-On a percentage basis,
-%
-\begin{equation} \label{eq:delta_lambda_perc}
-  \Delta \lambda \, [\%] = \frac{100 \, \Delta \lambda}{\lambda_{ref}} 
-            = \frac{100 \, \lambda}{\lambda_{ref}} - 1 \; ,
-\end{equation}
-%
-and
-%
-\begin{equation} \label{eq:delta_sse_perc}
-  \Delta sse \, [\%] = \frac{100 \, \Delta sse}{sse_{ref}} 
-            = \frac{100 \, sse}{sse_{ref}} - 1 \; .
-\end{equation}
-
-When $\Delta \lambda$, $\Delta \lambda \, [\%]$, or $\Delta sse$ are negative, 
-we observe reduction in the Solow residual ($\lambda$) or
-the fitting residuals ($sse$)
-relative to the reference model.
-
-Figure~\ref{fig:DSRsse_CES_graph} summarizes 
-$\lambda$ and $sse$ 
-results for CES models.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Tables for paper} 
-\label{sec:tables_for_paper}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Table~\ref{tab:CES_sr_gof} shows estimated values of
-the scale parameter~($\theta$),
-the Solow residual~($\lambda$), and
-goodness of fit~(SSE)
-for all modeling choices.
-
 <<Table_data>>=
+print("Top of Table_data")
+
 table_data <- 
@@
 <<CES_sr_gof, results="asis">>=
+print("Top of CES sr gof")
+
 data_CES_SR_gof <- 
@@
 @
-
-Table~\ref{tab:CES_sigma_nest_aware_inner} shows elasticity of substitution~($\sigma$)
-for inner nests.
-Note that the row with 
-``PT, Quality-adjusted, With energy, $(ek)l$ nesting, Rejecting the CSP''
-is, in fact, a boundary model that does not include energy.
-As such, the only knowable elasticity is $\sigma_{kl}$.
 
@@
 
-Table~\ref{tab:CES_sigma_nest_aware_outer} shows elasticity of substitution~($\sigma$)
-for outer nests.
-Rows with the $kl$ nesting are blank, because they have no outer nest.
-The row with
-``PT, Quality-adjusted, With energy, $(ek)l$ nesting, Rejecting the CSP''
-has no values for $\sigma$, because it has no outer nest, being a boundary model
-that includes only~$k$ and~$l$.
-
 <<CES_sigma_nest_aware_outer, results="asis">>=
@@
 @
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Graphs for paper} 
-\label{sec:graphs_for_paper}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%++++++++++++++++++++++++++++++
-\subsection{Historical data} 
-\label{sec:historical_data_graph}
-%++++++++++++++++++++++++++++++
-
-Unadjusted and quality-adjusted data for both Portugal and the United Kingdom 
-are shown in Figure~\ref{fig:Historical_Data_Graph}.
 
@@
 @
-
-%++++++++++++++++++++++++++++++
-\subsection{Fits to historical data} 
-\label{sec:fits_to_historical_data}
-%++++++++++++++++++++++++++++++
 
@@
 
-Both historical GDP and fitted GDP are shown in 
-Figures~\ref{fig:Graphs_CESkle-fitted}--\ref{fig:Graphs_CESekl-fitted}.
-%
 <<Graphs_CESkle-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with $kl$ and ($kl$)$e$ nesting that reject the CSP. Solid line is historical GDP.">>=
@@
 @
-
-%++++++++++++++++++++++++++++++
-\subsection{Residual plot} 
-\label{sec:residual_plot}
-%++++++++++++++++++++++++++++++
 
@@
 
-Because we fit in log-space, fitting residuals ($r_i$) are defined as
-%
-\begin{equation} \label{eq:log-residuals}
-  r_i \equiv \ln(y_i) - \ln(\hat{y}_i) =\ln\left( \frac{y_i}{\hat{y}_i} \right), 
-\end{equation}
-%
-where $r_i$ will be zero when there is agreement between 
-historical~($y_i$) and fitted~($\hat{y}_i$) economic output.
-
-%++++++++++++++++++++++++++++++
-\subsection{SSE and Solow residual} 
-\label{sec:SSE_and_SR_graphs}
-%++++++++++++++++++++++++++++++
-
 <<SRsse_CES_graph_3, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Solow Residuals~($\\lambda$) and mean squared error~($sse$).
@@
 @
-
-%++++++++++++++++++++++++++++++
-\subsection{Output elasticities} 
-\label{sec:output_elasticities_graph}
-%++++++++++++++++++++++++++++++
 
@@
 
-%++++++++++++++++++++++++++++++
-\subsection{$\sigma$ graphs} 
-\label{sec:sigma_graphs}
-%++++++++++++++++++++++++++++++
-
 <<sigma_graph_3, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.82, fig.cap="Elasticities of substitution~($\\sigma$) with factors of production on the vertical facet.">>=
@@
 
-%++++++++++++++++++++++++++++++
-\subsection{Resampling} 
-\label{sec:resampling}
-%++++++++++++++++++++++++++++++
-
 <<resample_graph_lambda_theta, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.5, fig.cap="$\\lambda$ and $\\theta$ values for resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
-standardScatterPlot(data=resampleCoeffs, mapping=aes(scale, lambda), facet_formula=~Country, alpha=0.05, orig_color = "black") +
+standardScatterPlot(data=resampleCoeffsCES, mapping=aes(scale, lambda), facet_formula=~Country, alpha=0.05, orig_color = "black") +
     scale_x_continuous(breaks=c(0.95, 1.0, 1.05)) + 
@@
 <<resample_graph_sigma1_delta1, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.5, fig.cap="$\\sigma_{(kl)}$ and $\\delta_1$ values for resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
-standardScatterPlot(data=resampleCoeffs, mapping=aes(delta_1, sigma_1), 
+standardScatterPlot(data=resampleCoeffsCES, mapping=aes(delta_1, sigma_1), 
                     facet_formula=~Country, alpha=0.1) +
@@
 <<resample_graph_sigma_delta, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.5, fig.cap="$\\sigma_{(kl)e}$ and $\\delta$ values for resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
-standardScatterPlot(data=resampleCoeffs, mapping=aes(delta, sigma), 
+standardScatterPlot(data=resampleCoeffsCES, mapping=aes(delta, sigma), 
                     facet_formula=~Country, alpha=0.1) +
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusion}
-\label{sec:Conclusion}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Future Work}
-\label{sec:FutureWork}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Acknowledgements}
-\label{sec:Acknowledgements}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \section*{Reproducible Research}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% In the spirit of Reproducible Research \citep{Gandrud:2013vx}, 
-% all data, spreadsheets, \texttt{R} code \citep{R}, and other materials 
-% associated with this paper can be found at\\*
-% \protect\url{https://github.com/MatthewHeun/Econ-Growth-R-Analysis}.
-
-%% References
-%%
-%% Following citation commands can be used in the body text:
-%%
-%%  \citet{key}  ==>>  Jones et al. (1990)
-%%  \citep{key}  ==>>  (Jones et al., 1990)
-%%
-%% Multiple citations as normal:
-%% \citep{key1,key2}         ==>> (Jones et al., 1990; Smith, 1989)
-%%                            or  (Jones et al., 1990, 1991)
-%%                            or  (Jones et al., 1990a,b)
-%% \cite{key} is the equivalent of \citet{key} in author-year mode
-%%
-%% Full author lists may be forced with \citet* or \citep*, e.g.
-%%   \citep*{key}            ==>> (Jones, Baker, and Williams, 1990)
-%%
-%% Optional notes as:
-%%   \citep[chap. 2]{key}    ==>> (Jones et al., 1990, chap. 2)
-%%   \citep[e.g.,][]{key}    ==>> (e.g., Jones et al., 1990)
-%%   \citep[see][pg. 34]{key}==>> (see Jones et al., 1990, pg. 34)
-%%  (Note: in standard LaTeX, only one note is allowed, after the ref.
-%%   Here, one note is like the standard, two make pre- and post-notes.)
-%%
-%%   \citealt{key}          ==>> Jones et al. 1990
-%%   \citealt*{key}         ==>> Jones, Baker, and Williams 1990
-%%   \citealp{key}          ==>> Jones et al., 1990
-%%   \citealp*{key}         ==>> Jones, Baker, and Williams, 1990
-%%
-%% Additional citation possibilities
-%%   \citeauthor{key}       ==>> Jones et al.
-%%   \citeauthor*{key}      ==>> Jones, Baker, and Williams
-%%   \citeyear{key}         ==>> 1990
-%%   \citeyearpar{key}      ==>> (1990)
-%%   \citetext{priv. comm.} ==>> (priv. comm.)
-%%   \citenum{key}          ==>> 11 [non-superscripted]
-%% Note: full author lists depends on whether the bib style supports them;
-%%       if not, the abbreviated list is printed even when full requested.
-%%
-%% For names like della Robbia at the start of a sentence, use
-%%   \Citet{dRob98}         ==>> Della Robbia (1998)
-%%   \Citep{dRob98}         ==>> (Della Robbia, 1998)
-%%   \Citeauthor{dRob98}    ==>> Della Robbia
-
-%% References with bibTeX database:
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{References}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% \bibliographystyle{model2-names}
-%%\bibliography{<your-bib-database>}
-% \bibliography{Paper2.bib}
-
-%% Authors are advised to submit their bibtex database files. They are
-%% requested to list a bibtex style file in the manuscript if they do
-%% not want to use model2-names.bst.
-
-%% References without bibTeX database:
-
-% \begin{thebibliography}{00}
-
-%% \bibitem must have one of the following forms:
-%%   \bibitem[Jones et al.(1990)]{key}...
-%%   \bibitem[Jones et al.(1990)Jones, Baker, and Williams]{key}...
-%%   \bibitem[Jones et al., 1990]{key}...
-%%   \bibitem[\protect\citeauthoryear{Jones, Baker, and Williams}{Jones
-%%       et al.}{1990}]{key}...
-%%   \bibitem[\protect\citeauthoryear{Jones et al.}{1990}]{key}...
-%%   \bibitem[\protect\astroncite{Jones et al.}{1990}]{key}...
-%%   \bibitem[\protect\citename{Jones et al., }1990]{key}...
-%%   \harvarditem[Jones et al.]{Jones, Baker, and Williams}{1990}{key}...
-%%
-
-% \bibitem[ ()]{}
-
-% \end{thebibliography}
-
-%% The Appendices part is started with the command \appendix;
-%% appendix sections are then done as normal sections
-%% \appendix
-%% \section{}
-%% \label{}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\appendix
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Correlograms} 
-\label{sec:correlograms}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-This appendix contains correlograms for all models.
-But, they are not included for now.
-
-%++++++++++++++++++++++++++++++
-\subsection{Correlograms for the reference models} 
-\label{sec:correlograms_ref}
-%++++++++++++++++++++++++++++++
-
-In this section we present correlograms for the reference (exponential-only) models.
-
 <<Correlograms_Exp, echo=FALSE, message=FALSE, include=FALSE, eval=FALSE>>=
@@
 
-%++++++++++++++++++++++++++++++
-\subsection{Correlograms for models that adhere to the cost-share theorem} 
-\label{sec:correlograms_CSP}
-%++++++++++++++++++++++++++++++
-
-In this section we present correlograms for all models that adhere to the cost-share theorem.
-
 <<Correlograms_CSP, echo=FALSE, message=FALSE, include=FALSE, eval=FALSE>>=
@@
 
-%++++++++++++++++++++++++++++++
-\subsection{Correlograms for models that reject the cost-share theorem} 
-\label{sec:correlograms_noCSP}
-%++++++++++++++++++++++++++++++
-
-In this section we present correlograms for all models that reject the cost-share theorem.
-
 <<Correlograms_noCSP, echo=FALSE, message=FALSE, include=FALSE, eval=FALSE>>=
@@
 @
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Statistical details on all models} 
-\label{sec:staistical_details}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-In this section, we present statistical details of all models.
-
-At the moment, this is a simple example of two models.
-I hope to develop a table later, after I figure out some things.
-Both models are CES models with energy fitted to Quality-adjusted data using the ($kl$)($e$) nesting.
-In Table~\ref{tab:stat_details_table}, Model 1 is for Portugal, and Model 2 is for the UK.
-
-This information is not included at present.
 
@@
 @
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Pre-econometrics graph} 
-\label{sec:pre-econometric_graph}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Cobb-Douglas Graveyard} 
-\label{sec:cd_graveyard}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-This section is the graveyard for information pertaining to the Cobb-Douglas model.
-
-%------------------------------
-\subsubsection{Cobb-Douglas Production Function} 
-\label{sec:CDe}
-%------------------------------
-
-The Cobb-Douglas production function can be expressed as
-%
-\begin{equation} \label{eq:CD}
-  y = \theta A k^{\alpha_1} l^{\alpha_2} \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)} \; ,
-\end{equation}
-%
-where
-
-Constant returns to scale are represented by the constraint
-$\alpha_1 + \alpha_2 = 1$.
-
-The capital-labor Cobb-Douglas production function shown in Equation~\ref{eq:CD}
-can be augmented to include an energy term:
-%
-\begin{equation} \label{eq:CDe}
-  y = \theta A k^{\alpha_1} l^{\alpha_2} e^{\alpha_3} \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)} \; ,
-\end{equation}
-%
-where $e \equiv E/E_0$, and $E$ is in units of energy per time, typically TJ/year.
-The energy-augmented Cobb-Douglas production function 
-is often assumed to have constant returns to scale for the three factors 
-of production: $\alpha_1 + \alpha_2 + \alpha_3 = 1$.
-The term $A$ is known as total factor productivity,
-and $\lambda$ is the Solow residual.
-
-The Cobb-Douglas production function can be expressed as
-%
-\begin{equation} \label{eq:CD}
-  y = \theta A k^{\alpha_1} l^{\alpha_2} \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)} \; ,
-\end{equation}
-%
-where 
-$y \equiv Y/Y_{0}$,
-$\theta$ is a scale parameter,
-e is the base of the natural logarithm, 
-$\lambda$ is represents the pace of technological progress,
-$t$ (time) is measured in years,
-$k \equiv K/K_{0}$, 
-$l \equiv L/L_{0}$, 
-$Y$ (economic output) is represented by GDP, 
-$K$ (capital) is expressed in currency units, 
-$L$ (labor) is expressed in workers or work-hours/year, and
-the 0 subscript indicates values at an initial year.%
-  \footnote{Dimensionless, indexed quantities are represented by 
-  lower-case symbols 
-  ($y$, $k$, $l$, $e$, $q$, $x$, and $u$), and dimensional 
-  quantities are represented by upper-case symbols 
-  ($Y$, $K$, $L$, $E$, $Q$, $X$, and $U$). 
-  Model parameters are represented by Greek letters
-  ($\alpha_1$, $\alpha_2$, $\lambda$, $\theta$).
-  }
-Constant returns to scale are represented by the constraint
-$\alpha_1 + \alpha_2 = 1$.
-
-The capital-labor Cobb-Douglas production function shown in Equation~\ref{eq:CD}
-can be augmented to include an energy term:
-%
-\begin{equation} \label{eq:CDe}
-  y = \theta A k^{\alpha_1} l^{\alpha_2} e^{\alpha_3} \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)} \; ,
-\end{equation}
-%
-where $e \equiv E/E_0$, and $E$ is in units of energy per time, typically TJ/year.
-The energy-augmented Cobb-Douglas production function 
-is often assumed to have constant returns to scale for the three factors 
-of production: $\alpha_1 + \alpha_2 + \alpha_3 = 1$.
-The term $A$ is known as total factor productivity,
-and $\lambda$ is the Solow residual. 
-%
 <<Graphs_CD-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Cobb-Douglas models that reject the cost-share theorem. Solid line is historical GDP.">>=
@@
 @
-%
+
 <<Graphs_CD-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for Cobb-Douglas models that reject the CSP.">>=
@@
 %
-Table~\ref{tab:Effect_of_CSP_CD} shows the effect of the CSP 
-on fitted parameters for the Cobb-Douglas model and the exponential-only model.
-The Cobb-Douglas models show lower $sse$ than the exponential-only models.
-The Cobb-Douglas models also reduce solow residual ($\lambda$) relative
-to the exponential-only case.
-%
+
 <<Effect_of_CSP_CD, results="asis">>=
@@
 %
-Table~\ref{tab:CD_coeffs} shows coefficients for all fitted Cobb-Douglas models
-and the reference model (exponential-only).
-%
+
 <<CD_coeffs, results="asis">>=
@@
 @
-%
-
-Table~\ref{tab:DSRsse_CD} shows $\Delta \lambda$ and $\Delta sse$ results for the Cobb-Douglas models.
-%
+
 <<DSRsse_CD, results="asis">>=
@@
 @
-%
-
-%
-Figures~\ref{fig:DSRsse_CD_graph} and~\ref{fig:percDSRsse_CD_graph} summarize 
-$\Delta \lambda$ and $\Delta sse$ 
-results for the Cobb-Douglas model.
-%
+
 <<DSRsse_CD_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta sse$) for the Cobb-Douglas model relative to the exponential-only model.">>=
@@
 @
-%
+
 <<percDSRsse_CD_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Percentage change in Solow Residuals~($\\Delta\\lambda \\, [\\%]$) and mean squared error~($\\Delta sse \\, [\\%]$) for the Cobb-Douglas model relative to exponential-only models.">>=
@@
 @
-%
+
 <<DSRsse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta sse$) for the CES modles relative to the exponential-only model.">>=
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{CES Graveyard} 
-\label{sec:ces_graveyard}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Table~\ref{tab:CES_alpha} shows 
-output elasticities~($\alpha$) for all modeling choices.
-
-Here is a table of $\alpha$ values. 
-These values represent the initial points of the trajectories. 
-We no longer use these values. 
-Instead, we use the time-dependent values of alpha.
-So, this table goes in the graveyard.
-
 <<CES_alpha, results="asis">>=
@@
 
-Here is a table of the raw CES coefficient values. 
-This table is not used in the paper, so I'm putting it in the graveyard.
 <<CES_sigma, results="asis">>=
@@
 @
-%
+
 <<Graphs_CESlek-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with $kl$ and ($le$)$k$ nesting that reject the CSP. Solid line is historical GDP.">>=
@@
 @
-%
+
 <<Graphs_CESekl-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with $kl$ and ($ek$)$l$ nesting that reject the CSP. Solid line is historical GDP.">>=
@@
 %
-Figures~\ref{fig:Graphs CESkle-resid}--\ref{fig:Graphs CESekl-resid}
-show fitting residuals for all CES models.
-%
+
 <<Graphs_CESkle-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(kl$)$e$ nesting.">>=
@@
 @
-%
+
 <<Graphs_CESlek-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with ($le$)$k$ nesting.">>=
@@
 @
-%
+
 <<Graphs_CESekl-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(ek$)$l$ nesting.">>=
@@
 
-Figures~\ref{fig:Factor_shares_graph_PT} and~\ref{fig:Factor_shares_graph_UK}
-show factor shares ($\alpha$ values) for CES models for
-Portugal and the UK, respectively.
-See Table~\ref{tab:CES_abg_equations} for details on the calculation
-of factor shares from fitted values of $\delta_1$ and $\delta$.
-%
 <<Factor_shares_bar_graph_function>>=
@@
 <<resample_graph_alpha_ternary, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.0, fig.cap="$\\alpha_k$, $\\alpha_l$, and $\\alpha_e$ values for CES resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
-standardTriPlot(data=resampleCoeffs, facet_formula=~Country, alpha=0.1,
+standardTriPlot(data=resampleCoeffsCES, facet_formula=~Country, alpha=0.1,
                 labels=c("alpha[k]", "alpha[l]", "alpha[e]"), size=2.0)
@@
 
-\end{document}
-
-%%
-%% End of file `elsarticle-template-2-harv.tex'.
+\section{End EcolEcon2015A}

### 2015-10-12 Articles/Article_EcolEcon_2015/Paper0/Paper0-Resampling.Rnw
set up parent and child docs -- eliminate text from child doc

@@
 %\linenumbers
+
+%%%% Import Analysis chunks
+
+<<child="TestChild.Rnw", eval=TRUE>>=
+@
+
+<<child="../EcolEcon_2015A.Rnw", eval=TRUE>>=
+@
+
+<<include=FALSE>>=
+knitr::opts_chunk$set(include = TRUE)
+@
+
+<<replay, include=TRUE, echo=FALSE>>=
+<<Graphs_CESlek-fitted>>
+@
 
@@
 
+Looking at boostrap distribution of a parameter.
+<<>>=
+ggplot( aes(x = lambda, color = method), data = resampledCoeffsCD) + geom_line(stat="density") + facet_grid( foo ~ Country, scales = "free" ) 
+mod <- resampleModelsCD[["PT.adjusted.noE.CD"]][["orig"]]
+coef(summary(mod))
+
+@
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-10-15 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Commented texreg code that uses extract.

@@
 
-<<stat_details_table, results="asis", include=FALSE, eval=FALSE>>=
-texreg(list(models$PT$adjusted$withE$CES$kle, models$UK$adjusted$withE$CES$kle), 
-       dcolumn = TRUE, 
-       booktabs = TRUE, 
-       use.packages = FALSE, 
-       label=paste0("tab:", opts_current$get("label")), 
-       caption = "Example output from \\texttt{texreg}.",
-       caption.above = TRUE, 
-       digits = 6,
-       fontsize = "tiny",
-       float.pos = "hb")
-@
+%' <<stat_details_table, results="asis", include=FALSE, eval=FALSE>>=
+%' texreg(list(models$PT$adjusted$withE$CES$kle, models$UK$adjusted$withE$CES$kle), 
+%'        dcolumn = TRUE, 
+%'        booktabs = TRUE, 
+%'        use.packages = FALSE, 
+%'        label=paste0("tab:", opts_current$get("label")), 
+%'        caption = "Example output from \\texttt{texreg}.",
+%'        caption.above = TRUE, 
+%'        digits = 6,
+%'        fontsize = "tiny",
+%'        float.pos = "hb")
+%' @
 

### 2015-10-16 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Now fitting with gls. cesModCSP is now CD.

@@
 library(tidyr)
+library(nlme)
 
@@
 # ********************************************************
-rerunModels=FALSE
+rerunModels=TRUE
 rerunResampling=FALSE
@@
       # Cobb-Douglas
-      ### breaking a formerly long line
       cdModCSP <- 
@@
            data = data)
+      # cdModCSP is an "lm" object. It is not a "CDEmodel" object. 
+      # Thus, it needs its own "naturalCoeffs" attribute if it is to work correctly in the "naturalCoef" function.
       attr(cdModCSP, "naturalCoeffs") <- data.frame(lambda=coef(cdModCSP)[[2]],
@@
       # CES
-      cesModCSP <- plm(log(eval(yVar) / (alphaCSP*eval(kVar)^(-rho_1) + betaCSP*eval(lVar)^(-rho_1))^(-1/rho_1)) ~ eval(tVar),
-                       data = historicalData[[country]],
-                       params=c(rho_1=0.8))
-      names(cesModCSP$coefficients) <- c("logscale", "lambda", "rho_1")
-      cesModCSP$coefficients <- c(coef(cesModCSP), c(delta_1=alphaCSP, delta=1))
-      attr(cesModCSP, "naturalCoeffs") <- EconModels:::makeNatCoef(cesModCSP)
-      cesModCSP$formula <- form
-      cesModCSP$data <- sdata
+      # The only CES models that can adhere to the CSP are models where
+      # alpha values are constant with respect to time. 
+      # I.e., models where energy is not included AND where rho_1 = 0.
+      # CES models where rho_1 = 0 are the Cobb-Douglas model.
+      # Convienently, we previously fit that model.
+      cesModCSP <- cdModCSP
+      # Again, we need a customized "naturalCoeffs" attribute so that 
+      # the "naturalCoef" function will do the right thing.
+      # "naturalCoeffs" can be based on the same "naturalCoeffs"
+      # from the Cobb-Douglas model, but a few additions are needed.
+      attr(cesModCSP, "naturalCoeffs") <- 
+        naturalCoef(cdModCSP) %>%
+        mutate(
+          delta_1 = naturalCoef(cdModCSP)[["alpha_1"]],
+          delta = 1,
+          rho_1 = 0, 
+          rho = NA
+        )
       modelsCSP[[country]][[adj]][["noE"]][["CES"]][["kl"]] <- cesModCSP

### 2015-10-16 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Now loading models from disk.

@@
 # ********************************************************
-rerunModels=TRUE
+rerunModels=FALSE
 rerunResampling=FALSE

### 2015-10-16 Articles/Article_EcolEcon_2015/Paper0/Paper0-Resampling.Rnw
Note about bagging.

@@
 distribution.
+\authNote{We should point out that we are NOT doing bootstrap aggregating,
+  whose purpose is to obtain better initial fits to data. 
+  See \url{https://en.wikipedia.org/wiki/Bootstrap_aggregating}.
+}
 Resampling distributions can be formed in a number of

### 2015-10-16 Articles/Article_EcolEcon_2015/archive/EcolEcon_2015.Rnw
Moved EcolEcon_2015.Rnw to archive.

--- 2015-09-27 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
@@
 <<Table_data>>=
+print("Top of Table_data")
+
 table_data <- 
@@
 <<resample_graph_lambda_theta, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.5, fig.cap="$\\lambda$ and $\\theta$ values for resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
-standardScatterPlot(data=resampleCoeffs, mapping=aes(scale, lambda), facet_formula=~Country, alpha=0.05, orig_color = "black") +
+standardScatterPlot(data=resampleCoeffsCES, mapping=aes(scale, lambda), facet_formula=~Country, alpha=0.05, orig_color = "black") +
     scale_x_continuous(breaks=c(0.95, 1.0, 1.05)) + 
@@
 where 
-
-Constant returns to scale are represented by the constraint
-$\alpha_1 + \alpha_2 = 1$.
-
-The capital-labor Cobb-Douglas production function shown in Equation~\ref{eq:CD}
-can be augmented to include an energy term:
-%
-\begin{equation} \label{eq:CDe}
-  y = \theta A k^{\alpha_1} l^{\alpha_2} e^{\alpha_3} \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)} \; ,
-\end{equation}
-%
-where $e \equiv E/E_0$, and $E$ is in units of energy per time, typically TJ/year.
-The energy-augmented Cobb-Douglas production function 
-is often assumed to have constant returns to scale for the three factors 
-of production: $\alpha_1 + \alpha_2 + \alpha_3 = 1$.
-The term $A$ is known as total factor productivity,
-and $\lambda$ is the Solow residual.
-
-The Cobb-Douglas production function can be expressed as
-%
-\begin{equation} \label{eq:CD}
-  y = \theta A k^{\alpha_1} l^{\alpha_2} \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)} \; ,
-\end{equation}
-%
-where 
 $y \equiv Y/Y_{0}$,

### 2015-10-16 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Added sigma_1 and sigma to naturalCoeffs.

--- 2015-10-16 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
@@
           rho_1 = 0, 
-          rho = NA
+          rho = NA,
+          sigma_1 = 1,
+          sigma = NA
         )

### 2015-10-16 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Now CSP models contain sigma_12, sigma_12_3.

--- 2015-10-16 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
@@
           rho_1 = 0, 
-          rho = NA
+          rho = NA,
+          sigma_1 = 1,
+          sigma_12 = 1,
+          sigma = NA,
+          sigma_12_3 = NA
         )

### 2015-10-17 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Paper1 files.

--- 2015-10-16 Articles/Article_EcolEcon_2015/archive/EcolEcon_2015.Rnw
@@
-% This article has been prepared for publication in RStudio with knitr.
-% According to http://www.elsevier.com/author-schemas/the-elsarticle-latex-document-class, we should be using the
-% elsarticle.cls file.
-% According to http://cdn.elsevier.com/assets/pdf_file/0006/109392/journal_refstyles.pdf, we should be using
-% elsarticle-template-2-harv.tex as the template for the text.
-% Furthermore, we should be using model2-names.bst for the bibliographic references.
-% The approach here is to load the frontmatter and backmatter from elsarticle-template-2-harv.tex
-% both ahead of and behind the text for our paper.
-% -- Matthew Kuperus Heun, 2014-08-01
-
 %% This is file `elsarticle-template-2-harv.tex',
@@
 %%
-\documentclass[preprint,authoryear,12pt]{elsarticle}
-
+\documentclass[preprint,10pt,3p]{elsarticle}
+\usepackage{setspace}
+\doublespacing
 %% Use the option review to obtain double line spacing
@@
 %% use the graphics package for simple commands
-%% \usepackage{graphics}
+\usepackage{graphics}
 %% or use the graphicx package for more complicated commands
-%% \usepackage{graphicx}
+\usepackage{graphicx}
 %% or use the epsfig package if you prefer to use the old commands
-%% \usepackage{epsfig}
+\usepackage{epsfig}
 
@@
 %% The amsthm package provides extended theorem environments
-%% \usepackage{amsthm}
-
-\usepackage{wrapfig}    % Allows wrapping of text around figures
-\usepackage{soul}       % Provides strikethrough text
-\usepackage{float}      % Allows precise positioning of tables and figures within the text
-\usepackage{amsmath}    % Allows \begin{equation*} \end{equation*} for unnumbered equations
-\usepackage{multirow}   % To create multirow tables
-\usepackage{hyperref}   % To create hyperlinks in the paper
-\usepackage{microtype}  % produces hanging punctuation and beautiful type
-\usepackage{booktabs}   % for beautiful tables
-\usepackage{dcolumn}    % aligns table columns at decimal places
-
-% From http://economics.utoronto.ca/osborne/latex/BIBTEX.HTM
-\newcommand{\citeapos}[1]{\citeauthor{#1}'s (\citeyear{#1})} % Posessive citations.
+\bibpunct{(}{)}{,}{a}{,}{,}
+
+\usepackage[usenames,dvipsnames]{xcolor}
+\usepackage{amsthm}
+\usepackage{float}
+\usepackage{epstopdf}
+\usepackage{textcomp}
+\usepackage{eurosym}
+\usepackage{morefloats}
+\usepackage{graphicx}
+\usepackage{rotating}
+\usepackage{caption}
+\usepackage{csquotes}
+\usepackage{multirow}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{natbib}
+\usepackage{booktabs}
+\usepackage{rotating}
+
+\usepackage{hyperref}
+
+%\usepackage[hidenotes]{authNote}
+\usepackage[shownotes]{authNote}
 
@@
 %% for the whole article with \linenumbers after \end{frontmatter}.
-%% \usepackage{lineno}
+\usepackage[right]{lineno}
 
@@
 %%
-%% \biboptions{longnamesfirst,comma}
+%\biboptions{longnamesfirst,comma}
 
@@
 \begin{document}
-
-<<setup, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE>>=
-library(EconData)
-library(EconModels)
-library(dplyr)
-library(reshape2)
-library(ggplot2)
-library(mosaic)
-library(xtable)
-library(knitr)
-library(texreg)
-library(tidyr)
-library(scales)
-library(tidyr)
-
-# Tell whether to re-run the analysis to create the models
-# or the resampling on the (kl)e models.
-# This file will use previously-saved models and resampling to generate
-# the paper if set to FALSE, greatly reducing time.
-# If something changes in the data or in the code that
-# performs the analysis or resampling, set 
-# rerunModels = TRUE
-# rerunResampling = TRUE
-# once to re-generate the information needed to 
-# create the paper.
-# ********************************************************
-rerunModels=FALSE
-rerunResampling=FALSE
-nResamples <- 100 # Number of resamples
-# ********************************************************
-opts_chunk$set(
-  # ********************************************************
-  eval=TRUE,
-  # ********************************************************
-  # tikz allows LaTeX code in graphical output. 
-  # E.g., "$y$" for a variable name in the legend for a graph.  
-  # dev='tikz',
-  tidy=FALSE,
-  comment=NA,
-  # Tells whether to cache output from chunks are saved. Cacheing saves time. 
-  # However, references to LaTeX tables DO NOT WORK if cacheing is turned on.
-  cache=FALSE,
-  warning=FALSE,  #Tells whether to show warnings in the output.
-  # Turns off messages for all chunks. 
-  # Set TRUE on an individual chunk to see it.
-  message=FALSE, 
-  # Tells whether to echo code for all chunks. 
-  # Set TRUE on an individual chunk to see its code.
-  echo=FALSE,
-  # Sets all table captions to the top.
-  xtable.caption.placement="top"
-)
-
-# This function is used in many places below.
-### That's nice.  I assume that's why you wrote a function.  But what does it DO?
-@
-
-<<myXTable>>=
-myXTable <- function(data, caption, label, digits=2){
-  table <- xtable(data, caption=caption, label=label, digits=digits)
-  print(table, 
-        caption.placement="top", 
-        size="\\tiny", 
-        include.rownames=FALSE, 
-        math.style.negative=TRUE, 
-        sanitize.text.function=function(x){x},
-        booktabs=TRUE)
-}
-@
-
-<<model_points_style>>=
-model_points_style <- function(p) {
-  p + 
-  scale_colour_manual(values = c("gray70", "black")) +
-  scale_size_manual(values = c(5, 3,3,3,3,3,3)) +
-  # scale_alpha_manual(values = c(.2, .6,.6,.6,.6, .6, .6)) +
-  scale_fill_manual(values = c(scales::alpha("gray50", .2), rep("transparent", 6))) +
-  scale_shape_manual(values = c(21, 21, 23:27)) +
-  guides( 
-    col = guide_legend(override.aes = aes(size = 5, shape = 21)) )
-}
-
-model_points_style_quad <- function(p) {
-  p + 
-  # scale_colour_manual(values = c("gray70", "black")) +
-  scale_size_manual(values = c(5, 3,3,3,3,3,3)) +
-  # scale_alpha_manual(values = c(.2, .6,.6,.6,.6, .6, .6)) +
-  scale_fill_manual(values = c(scales::alpha("gray50", .2), rep("transparent", 6))) +
-  scale_shape_manual(values = c(21, 21, 23:27)) +
-  theme(legend.title=element_blank())
-}
-@
 
@@
 
-\title{Energy and the CES production function}
+\title{Paper 1}
 
@@
 
-\author[IST]{Jo\~{a}o dos Santos}
-\author[CalvinEngr]{Matthew Kuperus Heun\corref{cor1}}
-\author[Leeds]{Paul Brockway}
+\author[label1]{Randall J. Pruim}
+\ead{rpruim@calvin.edu}
+
+\author[label2]{Matthew K. Heun}
 \ead{mkh2@calvin.edu}
-\author[Leeds]{Marco Sekai}
-\author[IST]{Tiago Domingos}
-\author[CalvinMath]{Randall Pruim}
-
-\address[IST]{IST, Lisbon, Portugal}
-\address[Leeds]{Leeds University, Leeds, UK}
-\address[CalvinEngr]{Engineering Department, Calvin College, Grand Rapids, MI 49546, USA}
-\address[CalvinMath]{Mathematics \& Statistics Department, Calvin College, Grand Rapids, MI 49546, USA}
-\cortext[cor1]{Corresponding author}
+
+\address[label1]{Mathematics \& Statistics Department, Calvin College, Grand
+Rapids, MI 49546, USA.}
+
+\address[label2]{Engineering Department, Calvin College, Grand Rapids, MI 49546,
+USA.}
+
+\linenumbers
 
 \begin{abstract}
-%% Text of abstract
-**** Add abstract ****
+
+Need abstract here.
+
 \end{abstract}
@@
 %% keywords here, in the form: keyword \sep keyword
-economic growth \sep exergy \sep energy \sep CES
-%% MSC codes here, in the form: \MSC code \sep code
-%% or \MSC[2008] code \sep code (2000 is the default)
+CES function \sep Cobb-Douglas function \sep statistical precision \sep aggregate production function
 \end{keyword}
@@
 
-% \linenumbers
-%% main text
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction} 
-\label{sec:Introduction}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-This is a study of the effects of quality-adjusted production function inputs
-on the importance of energy in the production function.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Coordinates of Analysis} 
-\label{sec:Coordinates}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-This section describes the coordinates of analysis and briefly reviews 
-literature related to each.
-
-%++++++++++++++++++++++++++++++
-\subsection{Mathematical Forms of the Energy-augmented Production Function} 
-\label{sec:Prod_Func_Forms}
-%++++++++++++++++++++++++++++++
-
-In this paper, we assess a prominent energy-augmented production function:
-Constant Elasticity of Substitution (CES).
-The CES model is assessed relative to 
-a model of exponential growth only.
-The following subsections describe each.
-
-%------------------------------
-\subsubsection{Constant Elasticity of Substitution Production Function (CES)} 
-\label{sec:CES}
-%------------------------------
-
-The energy-augmented 
-Constant Elasticity of Substitution (CES) production function%
-  \footnote{
-  We use the The \texttt{R} 
-  % \citep{R} 
-  package \texttt{micEconCES} 
-  % \citep{Henningsen:2011td} 
-  to estimate the CES production function.
-  }
-can be given as
-%
-\begin{equation} \label{eq:CESgeneric}
-  y = \gamma \: A \: \left\{\delta \left[\delta_1 x_1^{-\rho_1} 
-      + (1-\delta_1)x_2^{-\rho_1} \right]^{\rho/\rho_1} 
-      + (1-\delta) x_3^{-\rho} \right\}^{-1/\rho}; 
-      A \equiv \mathrm{e}^{\lambda (t-t_0)},
-\end{equation}
-%
-where
-$y \equiv Y/Y_{0}$,
-$\gamma$ is a scale parameter,
-e is the base of the natural logarithm, 
-$\lambda$ is the Solow residual (often thougth to represent the pace of technological progress),
-$t$ (time) is measured in years,
-$x_1$, $x_2$, and $x_3$ are factors of production
-and permutations of capital~($k$), labor~($l$), and energy~($e$),
-$k \equiv K/K_{0}$, 
-$l \equiv L/L_{0}$, 
-$Y$ (economic output) is represented by GDP, 
-$K$ (capital) is expressed in currency units, 
-$L$ (labor) is expressed in workers or work-hours/year, and
-the 0 subscript indicates values at an initial year.%
-  \footnote{Dimensionless, indexed quantities are represented by 
-  lower-case symbols 
-  ($y$, $k$, $l$, $e$, $q$, $x$, and $u$), and dimensional 
-  quantities are represented by upper-case symbols 
-  ($Y$, $K$, $L$, $E$, $Q$, $X$, and $U$). 
-  Model parameters are represented by Greek letters
-  ($\alpha_1$, $\alpha_2$, $\lambda$, $\theta$).
-  }
-The CES model without energy is given in Equation~\ref{eq:CESkl}.
-%
-\begin{equation} \label{eq:CESkl}
-  y = \gamma \: A \: \left[\delta_1 k^{-\rho_1} 
-      + (1-\delta_1)l^{-\rho_1} \right]^{-1/\rho_1}; 
-      A \equiv \mathrm{e}^{\lambda (t-t_0)} . 
-\end{equation}
-%
-Equation~\ref{eq:CESkle} augments Equation~\ref{eq:CESkl} with energy 
-using a ($kl$)($e$) nesting structure, as is typical in the literature. 
-Equation~\ref{eq:CESkl} is a degenerate form of Equation~\ref{eq:CESkle} 
-where $\delta \rightarrow 1$. 
-%
-\begin{equation} \label{eq:CESkle}
-  y = \gamma \: A \: \left\{\delta \left[\delta_1 k^{-\rho_1} 
-      + (1-\delta_1)l^{-\rho_1} \right]^{\rho/\rho_1} 
-      + (1-\delta) e^{-\rho} \right\}^{-1/\rho}; 
-      A \equiv \mathrm{e}^{\lambda (t-t_0)}.
-\end{equation}
-%
-In the CES production function, 
-$\gamma$ is a fitting parameter that accounts for an atypical first year. 
-The fitting parameters $\rho_1$ and $\rho$ indicate elasticities 
-of substitution ($\sigma_1$ and $\sigma$).
-The elasticity of substitution 
-between capital ($k$) and labor ($l$) is given by 
-$\sigma_1 = \frac{1}{1+\rho_1}$, and
-the elasticity of substitution between ($kl$) and ($e$) is given by 
-$\sigma = \frac{1}{1+\rho}$. 
-As $\rho_1 \rightarrow 0$, $\sigma_1 \rightarrow 1$,
-and the embedded CES production function for $k$ and $l$ degenerates 
-to the Cobb-Douglas production function.
-Similarly, as $\rho \rightarrow 0$, $\sigma \rightarrow 1$,
-and the CES production function for $(kl)$ and $(e)$ degenerates 
-to the Cobb-Douglas production function.
-As $\sigma \rightarrow \infty$ ($\rho \rightarrow -1$), 
-($kl$) and ($e$) are perfect substitutes. 
-As $\sigma \rightarrow 0$ ($\rho \rightarrow \infty$), 
-($kl$) and ($e$) are perfect complements: 
-no substitution is possible. Similarly, 
-as $\sigma_1 \rightarrow 0$ ($\rho_1 \rightarrow \infty$),
-$k$ and $l$ are perfect complements.
-$\delta_1$ describes the relative importance of capital ($k$)
-and labor ($l$), and
-$\delta$ describes the importance of ($kl$) relative to ($e$).
-
-Constraints on the fitting parameters include 
-$\delta_1 \in [0,1]$,
-$\delta \in [0,1]$,
-$\rho_1 \in [-1,0) \cup (0,\infty)$, and
-$\rho \in [-1,0) \cup (0,\infty)$.
-
-Two other nestings of the factors of production ($k$, $l$, and $e$)
-are possible with the CES model.
-%
-\begin{equation} \label{eq:CESlek}
-  y = \gamma \: A \: \left\{\delta \left[\delta_1 l^{-\rho_1} 
-      + (1-\delta_1) e^{-\rho_1} \right]^{\rho/\rho_1} 
-      + (1-\delta) k^{-\rho} \right\}^{-1/\rho}; 
-      A \equiv \mathrm{e}^{\lambda (t-t_0)}
-\end{equation}
-%
-\begin{equation} \label{eq:CESekl}
-  y = \gamma \: A \: \left\{\delta \left[\delta_1 e^{-\rho_1} 
-      + (1-\delta_1) k^{-\rho_1} \right]^{\rho/\rho_1} 
-      + (1-\delta) l^{-\rho} \right\}^{-1/\rho}; 
-      A \equiv \mathrm{e}^{\lambda (t-t_0)}
-\end{equation}
-% 
-Note that $\rho$ ($\sigma$), $\rho_1$ ($\sigma_1$), $\delta$, and $\delta_1$ have different
-meanings depending upon the nesting of the factors of production.
-
-For the CES model, factors shares~($\alpha_1$, $\alpha_2$, and $\alpha_3$) are calculated by
-$\alpha_1 = \delta_1$, $\alpha_2 = 1 - \delta_1$, and $\alpha_3 = 0$ 
-for the CES model with two factors of production
-and by 
-$\alpha_1 = \delta \delta_1$, $\alpha_2 = \delta(1 - \delta_1)$, and $\alpha_3 = 1 - \delta$
-for the CES model with three factors of production and the ($kl$)$e$ nesting.
-The values of $\alpha_1$, $\alpha_2$, and $\alpha_3$ are interpreted as
-factor shares for capital, labor, and energy, respectively,
-as shown in Table \ref{tab:CES_abg_equations}.
-
-\begin{table} \caption{Equations for $\alpha_1$, $\alpha_2$, and $\alpha_3$ 
-                        (factor shares for capital, labor, and energy, respectively)
-                        for the various CES nestings.} 
-\label{tab:CES_abg_equations} 
-  \begin{center}
-    \begin{tabular}{c c c c} 
-      \toprule
-      Nesting    & $\alpha_1$              & $\alpha_2$              & $\alpha_3$       \\
-      \midrule
-      ($kl$) \;  & $\delta_1$              & $1 - \delta_1$          & 0          \\
-      ($kl$)$e$  & $\delta \delta_1$       & $\delta (1 - \delta_1)$ & $1 - \delta$ \\   
-      ($le$)$k$  & $1 - \delta$            & $\delta \delta_1$       & $\delta (1 - \delta_1)$ \\
-      ($ek$)$l$  & $\delta (1 - \delta_1)$ & $1 - \delta$            & $\delta \delta_1$ \\
-      \bottomrule
-    \end{tabular}
-  \end{center}
-\end{table}
-
-%------------------------------
-\subsubsection{Exponential Production Function (reference model)} 
-\label{sec:exp}
-%------------------------------
-
-We define an exponential-only reference model for economic growth
-in Equation~\ref{eq:exponential-only-model}.
-%
-\begin{equation} \label{eq:exponential-only-model}
-  y = \theta A \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)} \; .
-\end{equation}
-%
-We expect that the reference model
-will have a larger fitted Solow residual term than
-the CES model, because no factors of production are
-included in the reference model to drive economic growth.
-Indeed, in the reference model, 
-all economic growth is attributed to the Solow residual~($\lambda$).
-
-In contrast, it is not necessarily true that 
-CES models will exhibit lower $sse$ than the reference model
-shown in Equation~\ref{eq:exponential-only-model}.
-The CES model has more fitting parameters,
-but it incorporates the factors of production
-at constant returns to scale. 
-The reference model has $\alpha_1 + \alpha_2 + \alpha_3 = 0$,
-whereas the CES model~(Equation~\ref{eq:CESgeneric})
-implicitly assumes constant returns to scale.
-Thus, if the factors of production~($\alpha_1$, $\alpha_2$, and $\alpha_3$) 
-are poorly correlated to output~($y$),
-the constant returns to scale constraint may cause higher $sse$ for
-the CES model relative to the reference model.
-
-%++++++++++++++++++++++++++++++
-\subsection{Economies} 
-\label{sec:Economies}
-%++++++++++++++++++++++++++++++
-
-Discuss economies here.
-
-UK and Portugal.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Sources of Data}
-\label{sec:Sources_of_Data}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Discuss data sources here.
-
-%++++++++++++++++++++++++++++++
-\subsection{Historical Data} 
-\label{sec:Historical_Data}
-%++++++++++++++++++++++++++++++
-
-Historical data are stored in the \texttt{IST} and \texttt{Leeds} data sets.
-
-<<Formulas>>=
-# Set up the formulas for each type of analysis.
-# These formulas contain energy. 
-# We can use keep_summands to drop the energy term (3rd summand on the rhs)
-# later if needed.
-formulas <- 
-  list( 
-    PT = c(unadjusted = build_formula("iGDP", list("iKstkS.L", "iL", "iXpMP", "iYear")),
-             adjusted = build_formula("iGDP", list("iKservS.L", "ihLest", "iUMP", "iYear"))),
-    UK = c(unadjusted = build_formula("iGDP", list("iKstkO.WwithRD", "iL", "iXp", "iYear")),
-             adjusted = build_formula("iGDP", list("iKservO.WwithRD", "ihLest", "iU", "iYear")))
-  )
-countries <- names(formulas)
-flavors <- names(formulas$PT)
-@
-
-<<Data>>=
-# Create the historicalData data frames
-### If we need to select variables, we can do that.  Unfortunately, select() and select_() don't do
-### what we would like here (they don't accept a vector of character strings), so we'd have to use
-### something else.  I've kept the fake select_() command here just to record what was done earlier.
-
-commonVars <- c("Year", "Country", "Source")
-historicalData <- list(
-  PT =  IST %>% 
-    filter(Country == "PT"), 
-    #  %>% select_(unique(c(commonVars, all.vars(formulas$PT$unadjusted), all.vars(formulas$PT$adjusted)))),
-  UK = Leeds %>% 
-    filter(Country == "UK") 
-    # %>% select_(unique(c(commonVars, all.vars(formulas$UK$unadjusted), all.vars(formulas$UK$adjusted))))
-)
-@
-
-For unadjusted variables, we use the time series shown in Table~\ref{tab:unadjusted_variables}.
-
-\begin{table} \caption{Unadjusted time-series variables.} 
-\label{tab:unadjusted_variables} 
-  \begin{center}
-    \begin{tabular}{r l l} 
-      \toprule
-      Variable    & Portugal           & UK                 \\
-      \midrule
-      Output      & \Sexpr{summands(formulas$PT$unadjusted, n=1, right=FALSE)}   
-                                                             & \Sexpr{summands(formulas$UK$unadjusted, n=1, right=FALSE)}\\
-      Capital     & \Sexpr{summands(formulas$PT$unadjusted, 1)} & \Sexpr{summands(formulas$UK$unadjusted, 1)} \\
-      Labor       & \Sexpr{summands(formulas$PT$unadjusted, 2)} & \Sexpr{summands(formulas$UK$unadjusted, 2)} \\
-      Energy      & \Sexpr{summands(formulas$PT$unadjusted, 3)} & \Sexpr{summands(formulas$UK$unadjusted, 3)} \\
-      \bottomrule
-    \end{tabular}
-  \end{center}
-\end{table}
-
-For quality-adjusted variables, we use the time series shown in Table~\ref{tab:quality_adjusted_variables}.
-
-\begin{table} \caption{Quality-adjusted time series variables.} 
-\label{tab:quality_adjusted_variables} 
-  \begin{center}
-    \begin{tabular}{r l l} 
-      \toprule
-      Variable    & Portugal         & UK               \\
-      \midrule
-      Output      & \Sexpr{summands(formulas$PT$adjusted, n=1, right=FALSE)}   
-                                                           & \Sexpr{summands(formulas$UK$adjusted, n=1, right=FALSE)} \\
-      Capital     & \Sexpr{summands(formulas$PT$adjusted, 1)} & \Sexpr{summands(formulas$UK$adjusted, 1)} \\
-      Labor       & \Sexpr{summands(formulas$PT$adjusted, 2)} & \Sexpr{summands(formulas$UK$adjusted, 2)} \\
-      Energy      & \Sexpr{summands(formulas$PT$adjusted, 3)} & \Sexpr{summands(formulas$UK$adjusted, 3)} \\
-      \bottomrule
-    \end{tabular}
-  \end{center}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Parameter Estimation (Without Cost-share Theorem)}
-\label{sec:parameter_estimation_noCSP}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Parameter estimation is accomplished with \texttt{formula}s of the form
-% %
-% \begin{equation} \label{eq:formulas}
-%   y \sim x_1 + x_2 + x_3 + time,
-% \end{equation}
-% %
-% where $y$ is economic output and 
-% $x_1$, $x_2$, and $x_3$ are factors of production
-% and permutations of
-% capital ($k$), labor ($l$), and energy ($e$).
-% (The factors of production may be quality-adjusted.)
-% $time$ is the time variable, usually \texttt{iYear}. 
-% The \texttt{formula}s are used in a fitting function such as 
-% \texttt{cdModel} to create a \texttt{model} object.
-% The function \texttt{naturalCoef} extracts reasonable
-% coefficients from \texttt{model} objects.
-% 
-% Note that in the fitting process for the Cobb-Douglas equation,
-% $\texttt{scale} = \theta$, 
-% $\alpha_1 = \alpha$,
-% $\alpha_2 = \beta$, and
-% $\alpha_3 = \gamma$,
-% when the \texttt{formula} is specified as 
-% %
-% \begin{equation} \label{eq:formula_kle}
-%   \texttt{y} \sim \texttt{k + l + e + time}.
-% \end{equation}
-% %
-% Note that for the CES model, $\texttt{scale} = \gamma$ and is expected to be close to unity.
-
-The models being fit can be described by the algebraic form of the model 
-(Cobb-Douglas, CES, etc.) and a formula that enumerates 
-which data variables are being used in which roles to fit the model.  
-A formula of the form
-%
-\begin{equation} \label{eq:formulas-3-factor}
-y \sim x_1 + x_2 + x_3 + t,
-\end{equation}
-%
-or 
-%
-\begin{equation} \label{eq:formulas-2-factor}
-y \sim x_1 + x_2 + t,
-\end{equation}
-%
-describes the economic output variable ($y$, usually \texttt{iGDP},
-                                        indexed GDP) 
-and the factors of production ($x_1$, $x_2$, and $x_3$,
-                               which will be some measure of capital, labor, and energy, 
-                               but perhaps not in that order), 
-and a time variable ($t$, usually \texttt{iYear}, 
-                     the number of years since the beginning of data collection).  
-All of the models assume an error term that is additive on the 
-logarithmic scale and are fit by the method of least squares.  
-Model fitting provides estimates for all parameters in the model.
-
-<<Models>>=
-fileNameCDCES <- "EcolEcon2015ModelsCDCES.rds"
-fileNameCSP <- "EcolEcon2015ModelsCSP.rds"
-fileNameExp <- "EcolEcon2015ModelsExp.rds"
-if (!rerunModels){
-  # load from the file on disk
-  models <- readRDS(fileNameCDCES)
-  modelsCSP <- readRDS(fileNameCSP)
-  modelsExp <- readRDS(fileNameExp)
-} else {   ### PLEASE USE COMMENTS TO MARK WHERE LONG CHUNKS END; BETTER: AVOID LONG CHUNKS, WHERE POSSIBLE
-
-  ### This has not been inspected by rjp
-
-  # re-run the models and save to disk.
-  # In RStudio, be sure to set the working directory to the source file directory.
-
-  #
-  # Models that are exponential only, y = A * exp(lambda*t)
-  #
-  modelsExp <- list()
-  alphaExp <- 0
-  betaExp <- 0
-  gammaExp <- 0
-  for (country in countries){
-    # Replace with better code later. 
-    # Would like to say cdModel(formula, data, factorShares=c(alpha_1 = 0, alpha_2 = 0, alpha_3 = 0))
-    # or something like that.
-    form <- keep_summands(formulas[[country]][["unadjusted"]], n = c(-1, -2, -3)) # Keep none of the factors of production
-    yVar <- as.name(summands(form, n=1, right=FALSE))
-    tVar <- as.name(summands(form, n=1))
-    data <- historicalData[[country]]
-    expMod <- lm(log(eval(yVar)) ~ eval(tVar), data=data)
-    attr(expMod, "naturalCoeffs") <- data.frame(lambda=coef(expMod)[[2]],
-                                                  logscale=coef(expMod)[[1]], 
-                                                  scale=exp(coef(expMod)[[1]]),
-                                                  alpha_1=alphaExp,
-                                                  alpha_2=betaExp, 
-                                                  alpha_3=gammaExp)
-    expMod$formula <- form
-    sdata <- subset(data, select=all.vars(form))
-    sdata <- data[complete.cases(sdata), unique(c(all.vars(form), names(data)))]
-    expMod$data <- sdata
-    expMod$response <- sdata$iGDP 
-    modelsExp[[country]] <- expMod
-  }
-  # Save exponential models to disk.
-  saveRDS(modelsExp, file=fileNameExp)
-
-  #
-  # Models that adhere to the cost-share theorem
-  #
-
-  modelsCSP <- list()
-  # Output elasticities based on cost share theorem
-  alphaCSP <- 0.3 # Fraction of national accounts spent on capital
-  betaCSP <- 0.7 # Fraction of national accounts spent on labor
-  for (country in countries){
-    for (adj in c("unadjusted", "adjusted")){
-      # Replace with better code later. 
-      # Would like to say cdModel(formula, data, factorShares=c(alpha_1 = 0.3, alpha_2 = 0.7, alpha_3 = 0))
-      # or something like that.
-      form <- keep_summands(formulas[[country]][[adj]], n=-3) # Remove energy
-      yVar <- as.name(summands(form, n=1, right=FALSE))
-      kVar <- as.name(summands(form, n=1))
-      lVar <- as.name(summands(form, n=2))
-      tVar <- as.name(summands(form, n=3))
-      data <- historicalData[[country]]
-      # Cobb-Douglas
-      ### breaking a formerly long line
-      cdModCSP <- 
-        lm(log(eval(yVar)) - alphaCSP*log(eval(kVar)) - betaCSP*log(eval(lVar)) ~ eval(tVar), 
-           data = data)
-      attr(cdModCSP, "naturalCoeffs") <- data.frame(lambda=coef(cdModCSP)[[2]],
-                                                    logscale=coef(cdModCSP)[[1]], 
-                                                    scale=exp(coef(cdModCSP)[[1]]),
-                                                    alpha_1=alphaCSP,
-                                                    alpha_2=betaCSP, 
-                                                    alpha_3=0)
-      cdModCSP$formula <- form
-      sdata <- subset(data, select=all.vars(form))
-      sdata <- data[complete.cases(sdata), unique(c(all.vars(form), names(data)))]
-      cdModCSP$data <- sdata
-      cdModCSP$response <- sdata$iGDP
-      modelsCSP[[country]][[adj]][["noE"]][["CD"]] <- cdModCSP
-      # CES
-      cesModCSP <- plm(log(eval(yVar) / (alphaCSP*eval(kVar)^(-rho_1) + betaCSP*eval(lVar)^(-rho_1))^(-1/rho_1)) ~ eval(tVar),
-                       data = historicalData[[country]],
-                       params=c(rho_1=0.8))
-      names(cesModCSP$coefficients) <- c("logscale", "lambda", "rho_1")
-      cesModCSP$coefficients <- c(coef(cesModCSP), c(delta_1=alphaCSP, delta=1))
-      attr(cesModCSP, "naturalCoeffs") <- EconModels:::makeNatCoef(cesModCSP)
-      cesModCSP$formula <- form
-      cesModCSP$data <- sdata
-      modelsCSP[[country]][[adj]][["noE"]][["CES"]][["kl"]] <- cesModCSP
-    }
-  }
-  # Save cost-share theorem models to disk.
-  saveRDS(modelsCSP, file=fileNameCSP)
-
-  #
-  # Models where all parameters are estimated (models don't adhere to the cost share theorem)
-  #
-
-  models <- list()
-  for(country in countries){
-    for (flavor in flavors){
-      fnoE <- keep_summands(formulas[[country]][[flavor]], -3) # Drop the energy term (3rd term on RHS)
-      fwithE <- formulas[[country]][[flavor]]
-      # CD models
-      models[[country]][[flavor]][["noE"]][["CD"]]   <- cdModel(fnoE, data = historicalData[[country]])
-      models[[country]][[flavor]][["withE"]][["CD"]] <- cdModel(fwithE, data = historicalData[[country]])
-      # CES models
-      models[[country]][[flavor]][["noE"]][["CES"]][["kl"]] <- cesModel(fnoE, 
-                                                                        data = historicalData[[country]], 
-                                                                        nest=c(1,2), digits = 10)
-      nestsWithE <- list(kle=c(1,2,3), lek=c(2,3,1), ekl=c(3,1,2))
-      models[[country]][[flavor]][["withE"]][["CES"]] <- lapply(nestsWithE, function(nest){
-          cesModel(formula=fwithE, data=historicalData[[country]], nest=nest, digits = 10)
-        })
-    }      
-  }
-  # Save models to disk.
-  saveRDS(models, file=fileNameCDCES)
-}  ### END ELSE FROM WAY UP THERE???
-@
-
-<<Models2>>=
-### TIME FOR A NEW R CHUNK -- That helps detect the end of that long code chunk
-
-### This function is the same in each model group below.  DRY (Don't repeat yourself).
-### Using this makes it (a) easier to see what's going on, and (b) easier to make adjustments
-### that affect all of the situations simultaneously.
-
-### General hint:  If you find yourself wanting to copy and paste a chunk of code, there is usually
-### a better way to do what you are about to do.
-
-model2df <- function(mod, id){
-  # Parse the id to find out whether this is quality-adjusted data, etc.
-  ### Don't name non-lists with variables whose names sound like a list.
-  ### I'm guessing you just didn't know what kind of data you were working with here. 
-  ### Either way, it's a bad thing.
-  id_components <- strsplit(id, split = "[.]")[[1]]
-
-  # return this data frame 
-  ### NOTE: ifelse() and [ ] handle NAs the way we want here
-  ### The former use of [[ ]] was unnecessary and would break things in the new code
-  ### I'm guessing you had [[ ]] because you thought you had a list when you did not.
-
-  ### NOTE: data_frame does not auto-convert to factors.  It leaves things as strings.
-  data_frame(
-    Country = id_components[1], 
-    flavor  = ifelse(id_components[2]=="unadjusted", "Unadjusted", "Quality-adjusted"),
-    energy  = ifelse(id_components[3]=="noE", "Without energy", "With energy"),
-    model   = id_components[4], 
-    nest    = id_components[5]) %>%  
-  cbind(naturalCoef(mod)) %>% 
-  cbind(data.frame(sse = sum(resid(mod)^2)))
-}
-
-### AH: So much tidier here :-)
-### NOTE: dplyr::bind_rows() can replace plyr::rbind.fill() in most (all?) situations
-###       plyr should probably not be used for data frame level operations anymore.
-
-# Put all exponential model coefficients into a data frame
-AllCoeffsExp <- 
-  leaf_apply(modelsExp, class = c("lm"), f = model2df) %>%
-  bind_rows() %>%
-  mutate(model = "exp", CSP = NA)
-
-# Put all the cost-share theorem (CSP) model coefficients into a data frame
-AllCoeffsCSP <- 
-  leaf_apply(modelsCSP, class = c("lm"), f = model2df) %>% 
-  bind_rows() %>%
-  mutate(CSP = "w/ CSP")
-
-# Put all CD and CES model coefficients into a data frame.  
-AllCoeffsNoCSP <- 
-  leaf_apply(models, class = c("CDEmodel", "cesModel", "LINEXmodel"), f = model2df) %>%
-  bind_rows() %>%
-  mutate(CSP="w/o CSP")
-
-AllCoeffs <- bind_rows(AllCoeffsExp, AllCoeffsCSP, AllCoeffsNoCSP)
-
-AllCoeffs <-
-  AllCoeffs %>% 
-  mutate( 
-    nest = ifelse(is.na(nest), "", nest),
-    CSP = ifelse( CSP == "w/ CSP", "w/ CSP", "w/o CSP")
-    )
-
-### It looks like this could also be done the otehr way arround:  We could scoop up all the models
-### into AllCoeffs and then filter to the subsets.
-
-# Get reference values for lambda and sse.
-### This could be done without saving ref if we have no other need for it
-### I've renamed ref to Ref since it is a data frame.
-Ref <- 
-  AllCoeffs %>% 
-  filter(model=="exp") %>% 
-  select(Country, sse, lambda) %>%
-  rename(sse_ref = sse, lambda_ref = lambda)
-AllCoeffs <- merge(AllCoeffs, Ref)
-
-# Calculate differences relative to the reference model
-### If all we need are the differences, we could skip the part where we put the intermediate stuff 
-### into AllCoefs
-
-AllCoeffs <- 
-  AllCoeffs %>%
-  mutate(
-    Dlambda = abs(lambda) - abs(lambda_ref), 
-    Dsse = sse - sse_ref,
-    percDlambda = Dlambda / abs(lambda_ref) * 100, 
-    percDsse = Dsse / sse_ref * 100
-  )
-
-# Relevel factors and re-order data
-### NOTE:  Need to convert from strings to factors to use relevelFactor()
-###        We could modify relevelFacotr() to accept character inputs
-AllCoeffs <- 
-  AllCoeffs %>%
-  mutate(
-    Country = relevelFactor(factor(Country), c("PT", "UK")),
-    flavor = relevelFactor(factor(flavor), c("Unadjusted", "Quality-adjusted")),
-    energy = relevelFactor(factor(energy), c("Without energy", "With energy")),
-    model = relevelFactor(factor(model), c("exp", "CD", "CES")),
-    nest = relevelFactor(factor(nest), c("kl", "kle", "lek", "ekl")),
-    CSP = relevelFactor(factor(CSP), c("w/ CSP", "w/o CSP"))
-  ) %>% 
-  arrange(Country, model, flavor, energy, nest, CSP)
-@
-
-%' <<>>=
-%' leaf_apply(models, function(mod, id) class(mod), class="cesModel")
-%' @
-
-<<output-elasticity>>=
-mod2oedf <- function(mod, id){
-  # Parse the id to find out whether this is quality-adjusted data, etc.
-  ### Don't name non-lists with variables whose names sound like a list.
-  ### I'm guessing you just didn't know what kind of data you were working with here. 
-  ### Either way, it's a bad thing.
-  id_components <- strsplit(id, split = "[.]")[[1]]
-
-  # return this data frame 
-  ### NOTE: ifelse() and [ ] handle NAs the way we want here
-  ### The former use of [[ ]] was unnecessary and would break things in the new code
-  ### I'm guessing you had [[ ]] because you thought you had a list when you did not.
-
-  ### NOTE: data_frame does not auto-convert to factors.  It leaves things as strings.
-  # message(class(mod))
-  if (! inherits(mod, "cesModel") ) return(NULL)
-
-  fortify(mod) %>%
-    mutate(
-      Country = id_components[1], 
-      flavor  = ifelse(id_components[2]=="unadjusted", "Unadjusted", "Quality-adjusted"),
-      energy  = ifelse(id_components[3]=="noE", "Without energy", "With energy"),
-      model   = id_components[4], 
-      nest    = id_components[5]
-    ) 
-}
-
-AllOE <- 
-  leaf_apply(
-    models, 
-    class = "cesModel", 
-    mod2oedf
-  ) %>% 
-  bind_rows()
-@
-
-<<Resampling-CD>>=
-print("Top of Resampling-CD")
-
-resampleCoeffsCDFilename <- "EcolEcon2015ResampleCoeffsCD.rds"
-resampleModelsCDFilename <- "EcolEcon2015ResampleModelsCD.rds"
-if (rerunResampling){
-  resamplesCD <- leaf_apply(models, class = "CDEmodel", f = function(model, id){
-    id_components <- strsplit(id, split = "[.]")[[1]]
-    print(id_components)
-    resamples <- resampledFits(model, method = "wild", n = nResamples)
-    resamples$coeffs <- mutate(
-      resamples$coeffs, 
-      Country = id_components[[1]],
-      flavor = id_components[[2]],
-      energy = id_components[[3]],
-      model = id_components[[4]]
-    )
-    return(resamples)
-  })
-  # Resample coefficients
-  resampleCoeffsCD <- lapply(resamplesCD, function(resample){
-    resample$coeffs
-  }) %>% plyr::rbind.fill()
-  saveRDS(resampleCoeffsCD, resampleCoeffsCDFilename)
-  # Resample models
-  # At present these resample models are stored in a "flat" list.
-  # We may want to change that later.
-  resampleModelsCD <- lapply(resamplesCD, function(resample){
-    resample$models
-  })
-  saveRDS(resampleModelsCD, resampleModelsCDFilename)
-} else {
-  resampleCoeffsCD <- readRDS(resampleCoeffsCDFilename)
-  resampleModelsCD <- readRDS(resampleModelsCDFilename)
-}
-@
-
-<<Resampling-CES-adjusted-kle>>=
-print("Top of Resampling-CES-adjusted-kle")
-
-resampleCoeffsCESFilename <- "EcolEcon2015kleResampleCoeffsCES.rds"
-resampleModelsCESFilename <- "EcolEcon2015kleResampleModelsCES.rds"
-if (rerunResampling){
-  # Run some resampling on the PT and UK models that reject the cost-share theorem,
-  # include energy, use quality-adjusted variables, and employ the (kl)e nesting.
-  # This is u-g-l-y code. Just getting something running for now.
-  modPT <- models$PT$adjusted$withE$CES$kle
-  modUK <- models$UK$adjusted$withE$CES$kle
-  resamplesCESPT <- resampledFits(modPT, method = "wild", n = nResamples)
-  resamplesCESUK <- resampledFits(modUK, method = "wild", n = nResamples)
-  # Resample coefficients
-  resampleCoeffsCES <- rbind(cbind(resamplesCESPT$coeffs, Country="PT"), cbind(resamplesCESUK$coeffs, Country="UK"))
-  resampleCoeffsCES$energy <- TRUE
-  resampleCoeffsCES$nest <- "(kl)e"
-  saveRDS(resampleCoeffsCES, file = resampleCoeffsCESFilename)
-  # Resample models
-  resampleModelsCES <- list(PT=resamplesCESPT$models, UK=resamplesCESUK$models)
-  saveRDS(resampleModelsCES, file = resampleModelsCESFilename)
-} else {
-  resampleCoeffsCES <- readRDS(resampleCoeffsCESFilename)
-  resampleModelsCES <- readRDS(resampleModelsCESFilename)
-}
-@
-
-<<ReModels>>=
-print("Top of ReModels")
-
-ReModels <-
-  bind_rows(
-  leaf_apply(resampleModelsCES, 
-             function(x,id) {mod2oedf(x, id) %>% mutate(id = id)},
-             strict.lists = TRUE)
-)
-@
-
-<<Fitted_and_Residuals>>=
-### Why are we going back and forth between CamelCase and interspersed_underscores?
-### If there isn't a reason, probably we should stick with one naming convention.
-
-print("top of Fitted_and_Residuals")
-
-temp_data_exp <- 
-  leaf_apply(
-    modelsExp, class=c("lm"), 
-    f = function(model, id){
-      ### Why wrap in data.frame() something that already is a tbl_df?  If this is necessary, say why.
-      #  df <- data.frame(select(model$data, Year, Country))
-      ### Also: let's use a consistent style for the dplyr commands, prefering to use %>% in most cases.
-      ### Also: The following use of white space makes it clearer what is going on (and how many steps 
-      ###       are involved.  I'm going to change A LOT of code to this format.
-      ### In this format, there is no name to create a temporary variable (or to use return())
-
-      model$dat %>% 
-        select(Year, Country) %>%
-        mutate(
-          Country = as.character(Country),  # to avoid warning about unmatched levels of factors
-          fittedExp = exp(fitted(model)), # exp accounts for the fact that the model was fitted in log space.
-          ResidualsExp = resid(model)     ### Why is this capitalized?
-        )
-    }
-  ) %>% 
-  bind_rows()
-
-### If the function is this long, it should be separated out and named rather than embedded in another
-### function call.  
-### But this looks like model2df from above.  Let's use that instead.
-
-### Probably just junk now.
-# function_that_was_here_before <- function(model, id){
-#   df <- data.frame(select(model$data, Year, Country, iGDP))
-#   df$fitted <- exp(fitted(model)) # fitted is in log space. Return to regular space.
-#   df$Residuals <- resid(model) # residuals are in log space, and that is what we want.
-#   # Now add meta information
-#   id_list <- strsplit(id, split = "[.]")[[1]]
-#   df$flavor <- if (id_list[[2]] ==  "unadjusted") "Unadjusted" else "Quality-adjusted"
-#   df$energy <- if (id_list[[3]] == "noE") "Without energy" else "With energy"
-#   df$model <- id_list[[4]]
-#   df$nest <- if (length(id_list) > 4) id_list[[5]] else NA
-#   return(df)
-# }
-
-### One line for each operation:  first leaf_apply, then rbind, then mutate -- Clarity by Code Convention
-temp_data_CSP <- 
-  leaf_apply(modelsCSP, class=c("plm", "lm"), model2df) %>% 
-  bind_rows() %>%
-  mutate(CSP = "w/ CSP")
-
-### This looks like a candidate for clean up a la model2df
-
-function_that_was_here_before <- function(model, id){
-  df <- data.frame(select(model$data, Year)) 
-  # By including [c(1:length(df$Year))] on the end, we 
-  # add NAs (as appropriate) to the end of these columns
-  # if data do not exist.
-  df$fitted <- yhat(model)[c(1:length(df$Year))]
-  df$Residuals <- resid(model)[c(1:length(df$Year))]
-  # Now add the response, using the original variable name.
-  df[[summands(model$formula, right = FALSE)]] <- response(model)[c(1:length(df$Year))]
-  # Now add meta information
-  id_list <- strsplit(id, split = "[.]")[[1]]
-  len <- length(id_list)
-  df$Country <- id_list[[1]]
-  df$flavor <- if (id_list[[2]] ==  "unadjusted") "Unadjusted" else "Quality-adjusted"
-  df$energy <- if (id_list[[3]] == "noE") "Without energy" else "With energy"
-  df$model <- id_list[[4]]
-  df$nest <- if (length(id_list) > 4) id_list[[5]] else NA
-  return(df)  
-}
-
-temp_data_noCSP <- 
-  leaf_apply(models, class=c("CDEmodel", "cesModel", "LINEXmodel"), function_that_was_here_before) %>% 
-  bind_rows() %>%
-  mutate(CSP = "w/o CSP")
-
-temp_data_noExp <- 
-  bind_rows( temp_data_CSP, temp_data_noCSP )
-
-# Now merge the exponential-only model with the CSP and noCSP models. 
-# Doing this, because the exponential-only model is kind-of like iY:
-# it applies to all situations.
-fitted_and_resid_data <- 
-  merge(temp_data_noExp, temp_data_exp) %>% 
-  mutate( Dr = abs(Residuals) - abs(ResidualsExp) )  
-### Caps in bad places?
-
-# Create a column containing ∆r, the difference between a residual value
-# and the residual value in the same year for the reference model
-### BREAK LONG LINES IN REASONABLE PLACES
-### BUT better to use mutate here.  See above.
-# fitted_and_resid_data[["Dr"]] <- 
-#   abs(fitted_and_resid_data[["Residuals"]]) - abs(fitted_and_resid_data[["ResidualsExp"]])
-
-# Relevel factors before plotting
-### Use mutate for this stuff!
-### Align = to make similarities between successive lines stand out.
-
-fitted_and_resid_data <-
-  fitted_and_resid_data %>% 
-  mutate(
-    Country = relevelFactor(factor(Country), c("PT", "UK")),
-    flavor  = relevelFactor(factor(flavor), c("Unadjusted", "Quality-adjusted")),
-    energy  = relevelFactor(factor(energy), c("Without energy", "With energy")),
-    nest    = relevelFactor(factor(nest), c("kl", "kle", "lek", "ekl"))
-  ) %>%
-  arrange(Country, CSP, model, flavor, energy, nest)
-@
-
-%++++++++++++++++++++++++++++++
-\subsection{Fitting residuals} 
-\label{sec:fitting_residuals}
-%++++++++++++++++++++++++++++++
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
-\label{sec:results}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The primary results from this paper involve the effects of
-the following modeling decisions:
-rejecting (or adhering to) the cost share theorem,
-quality-adjusting (or not) the factors of production,
-including energy (or not) in the production function, and
-nesting (in the CES model).
-
-We evaluate the effects of these modeling decisions 
-first on goodness of fit and Solow residual,
-next on factor shares, and 
-finally on factor substitutability.
-
-%++++++++++++++++++++++++++++++
-\subsection{Goodness of fit and Solow residual} 
-\label{sec:fit_and_sr}
-%++++++++++++++++++++++++++++++
-
-%
-We can evaluate the effect of modeling decisions on 
-goodness of fit and Solow residual by
-calculating values relative to the reference model.
-To do so, we define 
-$\Delta \lambda$ and $\Delta sse$, where
-%
-\begin{equation} \label{eq:delta_lambda}
-  \Delta \lambda \equiv \lambda - \lambda_{ref}
-\end{equation}
-%
-and
-%
-\begin{equation} \label{eq:delta_sse}
-  \Delta sse \equiv sse - sse_{ref},
-\end{equation}
-%
-with~$\lambda_{ref}$ and $sse_{ref}$ being the values 
-of the Solow residual and $sse$ for the reference model, respectively.
-On a percentage basis,
-%
-\begin{equation} \label{eq:delta_lambda_perc}
-  \Delta \lambda \, [\%] = \frac{100 \, \Delta \lambda}{\lambda_{ref}} 
-            = \frac{100 \, \lambda}{\lambda_{ref}} - 1 \; ,
-\end{equation}
-%
-and
-%
-\begin{equation} \label{eq:delta_sse_perc}
-  \Delta sse \, [\%] = \frac{100 \, \Delta sse}{sse_{ref}} 
-            = \frac{100 \, sse}{sse_{ref}} - 1 \; .
-\end{equation}
-
-When $\Delta \lambda$, $\Delta \lambda \, [\%]$, or $\Delta sse$ are negative, 
-we observe reduction in the Solow residual ($\lambda$) or
-the fitting residuals ($sse$)
-relative to the reference model.
-
-Figure~\ref{fig:DSRsse_CES_graph} summarizes 
-$\lambda$ and $sse$ 
-results for CES models.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Tables for paper} 
-\label{sec:tables_for_paper}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Table~\ref{tab:CES_sr_gof} shows estimated values of
-the scale parameter~($\theta$),
-the Solow residual~($\lambda$), and
-goodness of fit~(SSE)
-for all modeling choices.
-
-<<Table_data>>=
-print("Top of Table_data")
-
-table_data <- 
-  AllCoeffs %>%
-  plyr::rename(c(model = "Model", energy = "Energy", nest = "Nest")) %>%
-  mutate(Nest = 
-           plyr::mapvalues(
-             Nest,
-             from=c("kl", "kle", "lek", "ekl"),
-             to=c("$kl$", "$(kl)e$", "$(le)k$", "$(ek)l$")),
-         CSP =  
-           plyr::mapvalues(
-             CSP, 
-             from=c("w/ CSP", "w/o CSP"), 
-             to=c("Adhere", "Reject")),
-         Energy =
-           plyr::mapvalues(
-             Energy, 
-             from=c("Without energy", "With energy"), 
-             to=c("Without", "With")),
-         Model = 
-           plyr::mapvalues(
-             Model, 
-             from=c("exp"), 
-             to=c("Ref."))
-  )
-@
+\linenumbers
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Highlights}
+\label{sec:highlights}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\emph{This will go in a separate document eventually.}
+
+\begin{itemize}
+\item Highlight 1
+\item Highlight 2
+\item Highlight 3
+\item Highlight 4
+\end{itemize}
+
+%\linenumbers
+
+%%%% Import Analysis chunks
+
+<<child="../EcolEcon_2015A.Rnw", eval=TRUE>>=
+@
+
+<<include=FALSE>>=
+knitr::opts_chunk$set(include = TRUE)
+@
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Tables}
+\label{sec:tables}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 <<CES_sr_gof, results="asis">>=
-print("Top of CES sr gof")
-
 data_CES_SR_gof <- 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Graphs for paper} 
-\label{sec:graphs_for_paper}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%++++++++++++++++++++++++++++++
-\subsection{Historical data} 
-\label{sec:historical_data_graph}
-%++++++++++++++++++++++++++++++
-
-Unadjusted and quality-adjusted data for both Portugal and the United Kingdom 
-are shown in Figure~\ref{fig:Historical_Data_Graph}.
-
-<<Historical_Data_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Historical data.", warning=FALSE>>=
-
-### Also, I find tidyr::gather() and tidyr::spread() easier to work with than melt() and cast()
-
-histDataForGraph <- 
-  leaf_apply(formulas, class = "formula", f=function(form, name){
-    meta <- strsplit(name, split="[.]")[[1]]
-    Country <- meta[1]
-    flavor <- meta[2]
-    measure.vars <- c(summands(form, right=FALSE), summands(form, 1:3))
-    ### Is there any reason to select away some of the columns?
-    trimmed_historical_data <- historicalData[[Country]][c("Year", measure.vars)]
-
-    # return this.
-    melt(
-      trimmed_historical_data, 
-      measure.vars = measure.vars, 
-      value.name = "value",
-      variable.name = "variable") %>%
-    mutate(
-      variable = as.character(variable), # eliminate factors, which cause warnings with bind_rows() below.
-      Country = Country,
-      flavor =  ifelse (flavor == "adjusted", "Quality-adjusted", "Unadjusted")
-      )
-  }
-  ) %>% bind_rows() %>%
-
-  mutate( 
-    # Change variable names to make a nicer-looking graph and relevel factors before plotting
-    variable = plyr::mapvalues(variable,
-                               from=c("iGDP", 
-                                      "iKstkS.L", "iKservS.L", "iKstkO.WwithRD", "iKservO.WwithRD",
-                                      "iL", "ihLest",
-                                      "iXpMP", "iXp", "iUMP", "iU"),
-                               to=c("y", 
-                                    "k", "k", "k", "k",
-                                    "l", "l",
-                                    "e", "e", "e", "e")),
-    Country = relevelFactor(factor(Country), c("PT", "UK")), # Adjusts facet order
-    flavor = relevelFactor(factor(flavor), c("Unadjusted", "Quality-adjusted")), # Adjusts facet order
-    variable = relevelFactor(factor(variable), c("y", "k", "l", "e"))
-  )
-
+Looking at boostrap distribution of a parameter.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Graphs}
+\label{sec:graphs}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+<<Historical_Plot, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4.0, fig.cap="Historical data.", warning=FALSE>>=
 ggplot(histDataForGraph) + 
@@
 
-%++++++++++++++++++++++++++++++
-\subsection{Fits to historical data} 
-\label{sec:fits_to_historical_data}
-%++++++++++++++++++++++++++++++
-
-<<Fitted_and_Residual_Graph_Functions>>=
-
-### Can fittedGraphNoCSP and fittedGraphCSP be combined into one function with an argument?
-### Or can the data filtering happen outside and everything else be the same?
-### Did you copy and paste to make one from the other?  That should be a sign...
-fittedGraphNoCSP <- function(data){
-  fittedGraphData <- 
-    data %>% 
-    select(Year, Country, iGDP, fitted, fittedExp, flavor, energy, CSP, nest) %>%
-    melt(measure.vars = c("iGDP", "fitted", "fittedExp"), 
-         value.name = "value", variable.name = "variable") %>%
-    mutate(label = paste(variable, energy)) %>%
-    # Now collapse some of the information. Don't need multiple versions of the exponential model, e.g.
-    filter(label %in% c("iGDP With energy", "fittedExp With energy", 
-                        "fitted With energy", "fitted Without energy")
-    ) %>% 
-    mutate(
-      label = plyr::mapvalues(label, 
-                              from = c("iGDP With energy",  "fittedExp With energy",
-                                       "fitted With energy", "fitted Without energy"), 
-                              to = c("GDP",  "Ref. model",
-                                     "w/ energy", "w/o energy")),
-      label = relevelFactor(factor(label), 
-                            c("GDP", "Ref. model", "w/o energy", "w/ energy"))
-    )
-
-  ggplot() +
-    geom_line(data=fittedGraphData, mapping=aes(x=Year, y=value, group=label, linetype=label, size=label)) +
-    scale_linetype_manual(values=c(1,2,4,3), name="") +
-    scale_size_manual(name = "", values=c(1, 0.5, 0.5, 0.5)) +
-    facet_grid(flavor ~ Country) +
-    scale_x_continuous(breaks=c(1960, 1980, 2000)) +
-    scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12)) +
-    xlab("") +
-    ylab("Indexed GDP (1960=1)") +
-    xy_theme()
-}
-@
-
-Both historical GDP and fitted GDP are shown in 
-Figures~\ref{fig:Graphs_CESkle-fitted}--\ref{fig:Graphs_CESekl-fitted}.
-%
-<<Graphs_CESkle-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with $kl$ and ($kl$)$e$ nesting that reject the CSP. Solid line is historical GDP.">>=
+<<Graphs_CESkle-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with $kl$ and $(kl)e$ nesting that reject the CSP. Solid line is historical GDP.">>=
 fittedGraphData_kle <- 
@@
 @
-
-%++++++++++++++++++++++++++++++
-\subsection{Residual plot} 
-\label{sec:residual_plot}
-%++++++++++++++++++++++++++++++
-
-<<ResidualPlotFunction>>=
-
-cesResidualPlot2 <- function(data){
-  dataToPlot <- 
-    data %>%
-    mutate(nest = 
-             plyr::mapvalues(
-               nest, 
-               from=c("kl", "kle", "lek", "ekl"), 
-               to=c("kl", "(kl)e", "(le)k", "(ek)l")
-               ),
-           Model = interaction(nest, CSP, sep = " ", drop=TRUE),
-           Inputs = flavor)
-
-  ggplot() +
-    geom_point(
-      data=dataToPlot, 
-      mapping=aes(
-        x=Year, 
-        y=Residuals, 
-        fill=Model, 
-        shape=Model, 
-        size=Model
-        )
-      ) +
-    facet_grid(flavor ~ Country) +
-    geom_hline(yintercept = 0, colour="gray50", size=0.1) +
-    scale_x_continuous(breaks=c(1960, 1980, 2000)) +
-    xlab("") +
-    ylab("r") + 
-    xy_theme() +
-    labs(color = "Factors of production") +
-    # This is custom stuff here to match the model_points_style function. 
-    # We can't use model_points_style, because the aesthetics are different here
-    # with only two series (kl w/o CSP and (kl)e w/o CSP) in the graph.
-    scale_size_manual(values = c(3, 3)) +
-    scale_fill_manual(values = c("transparent", "transparent")) +
-    scale_shape_manual(values = c(21, 23)) +
-  theme(legend.title=element_blank())
-}
-@
-
-<<Resid_plot_with_ref, eval=FALSE, include=FALSE>>=
-# This version of the residual plot includes reference model residuals.
-# But the reference model dwarfs all other residuals and looks bad on the graph.
-# So, I decided not to use this. ---MKH, 14 Aug 2015
-
-# residualPlot <- function(data, withEnergyShape = 0){
-#   # Keep only the data we need
-#   residGraphData <- select(data, Year, Country, Residuals, flavor, energy, model, nest, CSP, ResidualsExp)
-#   # Melt the data so that we can include the reference model, too.
-#   residGraphData <- melt(residGraphData, 
-#                          measure.vars=c("Residuals", "ResidualsExp"),
-#                          value.name="value",
-#                          variable.name="variable")
-#   residGraphData$label <- with(residGraphData, paste(variable, energy))
-#   
-#   # Now collapse some of the information. Don't need multiple versions of the exponential model, e.g.
-#   residGraphData <- filter(residGraphData, label=="Residuals With energy" | label=="Residuals Without energy" |
-#                              label=="ResidualsExp Without energy")
-#   
-#   residGraphData$label <- plyr::mapvalues(residGraphData$label, 
-#                                           from = c("Residuals With energy", 
-#                                                    "Residuals Without energy",
-#                                                    "ResidualsExp Without energy"), 
-#                                           to = c("With energy", 
-#                                                  "Without energy",
-#                                                  "Reference model"))
-#   # Relevel factors
-#   residGraphData$label <- relevelFactor(as.factor(residGraphData$label), 
-#                                          c("Without energy", "With energy", "Reference model"))
-#   
-#   ggplot() +
-#     geom_point(data=residGraphData, mapping=aes(x=Year, y=value, shape=label, color=label, size=label)) +
-#     scale_shape_manual(values=c(1, withEnergyShape, 5)) +
-#     scale_size_manual(values=c(4, 4, 2)) +
-#     # scale_color_manual(values=c("gray50", "green", "red")) +
-#     facet_grid(Country ~ flavor) +
-#     geom_hline(yintercept = 0, colour="gray50", size=0.1) +
-#     scale_x_continuous(breaks=c(1960, 1980, 2000)) +
-#     xlab("") +
-#     ylab("r") + 
-#     xy_theme() +
-#     theme(legend.title=element_blank())
-# }
-@
-
-Because we fit in log-space, fitting residuals ($r_i$) are defined as
-%
-\begin{equation} \label{eq:log-residuals}
-  r_i \equiv \ln(y_i) - \ln(\hat{y}_i) =\ln\left( \frac{y_i}{\hat{y}_i} \right), 
-\end{equation}
-%
-where $r_i$ will be zero when there is agreement between 
-historical~($y_i$) and fitted~($\hat{y}_i$) economic output.
-
-%++++++++++++++++++++++++++++++
-\subsection{SSE and Solow residual} 
-\label{sec:SSE_and_SR_graphs}
-%++++++++++++++++++++++++++++++
 
@@
 model_points_style_quad(p)
-
-@
-
-%++++++++++++++++++++++++++++++
-\subsection{Output elasticities} 
-\label{sec:output_elasticities_graph}
-%++++++++++++++++++++++++++++++
+@
 
@@
 @
-
-%++++++++++++++++++++++++++++++
-\subsection{$\sigma$ graphs} 
-\label{sec:sigma_graphs}
-%++++++++++++++++++++++++++++++
 
@@
 
-%++++++++++++++++++++++++++++++
-\subsection{Resampling} 
-\label{sec:resampling}
-%++++++++++++++++++++++++++++++
-
 <<resample_graph_lambda_theta, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.5, fig.cap="$\\lambda$ and $\\theta$ values for resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusion}
-\label{sec:Conclusion}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Future Work}
-\label{sec:FutureWork}
+\section{Conclusions}
+\label{sec:conclusion}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section*{Acknowledgements}
-\label{sec:Acknowledgements}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \section*{Reproducible Research}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% In the spirit of Reproducible Research \citep{Gandrud:2013vx}, 
-% all data, spreadsheets, \texttt{R} code \citep{R}, and other materials 
-% associated with this paper can be found at\\*
-% \protect\url{https://github.com/MatthewHeun/Econ-Growth-R-Analysis}.
-
-%% References
+\label{sec:acknowledgements}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%References
 %%
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{References}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% \bibliographystyle{model2-names}
-%%\bibliography{<your-bib-database>}
-% \bibliography{Paper2.bib}
-
-%% Authors are advised to submit their bibtex database files. They are
-%% requested to list a bibtex style file in the manuscript if they do
-%% not want to use model2-names.bst.
-
-%% References without bibTeX database:
-
-% \begin{thebibliography}{00}
-
-%% \bibitem must have one of the following forms:
-%%   \bibitem[Jones et al.(1990)]{key}...
-%%   \bibitem[Jones et al.(1990)Jones, Baker, and Williams]{key}...
-%%   \bibitem[Jones et al., 1990]{key}...
-%%   \bibitem[\protect\citeauthoryear{Jones, Baker, and Williams}{Jones
-%%       et al.}{1990}]{key}...
-%%   \bibitem[\protect\citeauthoryear{Jones et al.}{1990}]{key}...
-%%   \bibitem[\protect\astroncite{Jones et al.}{1990}]{key}...
-%%   \bibitem[\protect\citename{Jones et al., }1990]{key}...
-%%   \harvarditem[Jones et al.]{Jones, Baker, and Williams}{1990}{key}...
-%%
-
-% \bibitem[ ()]{}
-
-% \end{thebibliography}
+% \bibliographystyle{agsm}
+% \bibliography{references}
 
@@
 %% appendix sections are then done as normal sections
-%% \appendix
-%% \section{}
-%% \label{}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\appendix
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Correlograms} 
-\label{sec:correlograms}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-This appendix contains correlograms for all models.
-But, they are not included for now.
-
-%++++++++++++++++++++++++++++++
-\subsection{Correlograms for the reference models} 
-\label{sec:correlograms_ref}
-%++++++++++++++++++++++++++++++
-
-In this section we present correlograms for the reference (exponential-only) models.
-
-<<Correlograms_Exp, echo=FALSE, message=FALSE, include=FALSE, eval=FALSE>>=
-leaf_apply(l = modelsExp, class = c("lm"), f = function(model, name){
-  acf(resid(model), main=name)
-})
-@
-
-%++++++++++++++++++++++++++++++
-\subsection{Correlograms for models that adhere to the cost-share theorem} 
-\label{sec:correlograms_CSP}
-%++++++++++++++++++++++++++++++
-
-In this section we present correlograms for all models that adhere to the cost-share theorem.
-
-<<Correlograms_CSP, echo=FALSE, message=FALSE, include=FALSE, eval=FALSE>>=
-leaf_apply(l = modelsCSP, class = c("lm", "plm"), f = function(model, name){
-  acf(resid(model), main=name)
-})
-@
-
-%++++++++++++++++++++++++++++++
-\subsection{Correlograms for models that reject the cost-share theorem} 
-\label{sec:correlograms_noCSP}
-%++++++++++++++++++++++++++++++
-
-In this section we present correlograms for all models that reject the cost-share theorem.
-
-<<Correlograms_noCSP, echo=FALSE, message=FALSE, include=FALSE, eval=FALSE>>=
-leaf_apply(l = models, class = c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, name){
-  acf(resid(model), main=name)
-})
-@
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Statistical details on all models} 
-\label{sec:staistical_details}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-In this section, we present statistical details of all models.
-
-At the moment, this is a simple example of two models.
-I hope to develop a table later, after I figure out some things.
-Both models are CES models with energy fitted to Quality-adjusted data using the ($kl$)($e$) nesting.
-In Table~\ref{tab:stat_details_table}, Model 1 is for Portugal, and Model 2 is for the UK.
-
-This information is not included at present.
-
-<<stat_details_table, results="asis", include=FALSE, eval=FALSE>>=
-texreg(list(models$PT$adjusted$withE$CES$kle, models$UK$adjusted$withE$CES$kle), 
-       dcolumn = TRUE, 
-       booktabs = TRUE, 
-       use.packages = FALSE, 
-       label=paste0("tab:", opts_current$get("label")), 
-       caption = "Example output from \\texttt{texreg}.",
-       caption.above = TRUE, 
-       digits = 6,
-       fontsize = "tiny",
-       float.pos = "hb")
-@
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Pre-econometrics graph} 
-\label{sec:pre-econometric_graph}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-<<Pre-econometric_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Pre-econometric data.", warning=FALSE>>=
-pre_econometric_data <- 
-  leaf_apply(
-    formulas, class = "formula", 
-    f=function(form, name){
-      meta <- strsplit(name, split="[.]") %>% unlist
-      Country <- meta[1]
-      flavor <- meta[2]
-      nums <- summands(form, n=1:3)
-      denom <- summands(form, n=1, right=FALSE)
-      ratios <- lapply(nums, function(num) {paste(num, denom, sep="/")}) %>% unlist
-      coltemplate <- build_formula(NULL, c("Year", ratios))
-      trimmed_historical_data <- historicalData[[Country]][all.vars(coltemplate)]
-      ratio_data <- evalFormula(coltemplate, data=trimmed_historical_data)$right
-      mratio_data <- melt(ratio_data, measure.vars = ratios, value.name = "ratio", variable.name = "variable")
-      mratio_data$Country <- Country
-      mratio_data$flavor <- if (flavor == "adjusted") "Quality-adjusted" else "Unadjusted"
-      return(mratio_data)
-    }
-  ) %>%  
-  bind_rows()
-
-# Fix levels
-pre_econometric_data$flavor <- relevelFactor(as.factor(as.character(pre_econometric_data$flavor)), 
-                                               c("Unadjusted", "Quality-adjusted"))
-pre_econometric_data$Country <- relevelFactor(as.factor(pre_econometric_data$Country), 
-                                              c("PT", "UK"))
-pre_econometric_data$variable <- relevelFactor(as.factor(pre_econometric_data$variable),
-                                               unique(pre_econometric_data$variable))
-# Now make the plot of pre-econometric data
-historicalPlot(pre_econometric_data, 
-               mapping=aes(x=Year, y=ratio, group=variable, linetype=variable), 
-               facet_formula = Country ~ flavor, 
-               line_types = c(2,4,3, 2,4,3, 2,3,2, 3)) + 
-  xlab("") + 
-  ylab("Indexed (1960=1)")
-@
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Cobb-Douglas Graveyard} 
-\label{sec:cd_graveyard}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-This section is the graveyard for information pertaining to the Cobb-Douglas model.
-
-%------------------------------
-\subsubsection{Cobb-Douglas Production Function} 
-\label{sec:CDe}
-%------------------------------
-
-The Cobb-Douglas production function can be expressed as
-%
-\begin{equation} \label{eq:CD}
-  y = \theta A k^{\alpha_1} l^{\alpha_2} \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)} \; ,
-\end{equation}
-%
-where 
-$y \equiv Y/Y_{0}$,
-$\theta$ is a scale parameter,
-e is the base of the natural logarithm, 
-$\lambda$ is represents the pace of technological progress,
-$t$ (time) is measured in years,
-$k \equiv K/K_{0}$, 
-$l \equiv L/L_{0}$, 
-$Y$ (economic output) is represented by GDP, 
-$K$ (capital) is expressed in currency units, 
-$L$ (labor) is expressed in workers or work-hours/year, and
-the 0 subscript indicates values at an initial year.%
-  \footnote{Dimensionless, indexed quantities are represented by 
-  lower-case symbols 
-  ($y$, $k$, $l$, $e$, $q$, $x$, and $u$), and dimensional 
-  quantities are represented by upper-case symbols 
-  ($Y$, $K$, $L$, $E$, $Q$, $X$, and $U$). 
-  Model parameters are represented by Greek letters
-  ($\alpha_1$, $\alpha_2$, $\lambda$, $\theta$).
-  }
-Constant returns to scale are represented by the constraint
-$\alpha_1 + \alpha_2 = 1$.
-
-The capital-labor Cobb-Douglas production function shown in Equation~\ref{eq:CD}
-can be augmented to include an energy term:
-%
-\begin{equation} \label{eq:CDe}
-  y = \theta A k^{\alpha_1} l^{\alpha_2} e^{\alpha_3} \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)} \; ,
-\end{equation}
-%
-where $e \equiv E/E_0$, and $E$ is in units of energy per time, typically TJ/year.
-The energy-augmented Cobb-Douglas production function 
-is often assumed to have constant returns to scale for the three factors 
-of production: $\alpha_1 + \alpha_2 + \alpha_3 = 1$.
-The term $A$ is known as total factor productivity,
-and $\lambda$ is the Solow residual. 
-%
-<<Graphs_CD-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Cobb-Douglas models that reject the cost-share theorem. Solid line is historical GDP.">>=
-fittedGraphNoCSP(fitted_and_resid_data %>% filter(model=="CD" & CSP=="w/o CSP"))
-@
-%
-<<Graphs_CD-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for Cobb-Douglas models that reject the CSP.">>=
-  ggplot() +
-    geom_point(
-      data=fitted_and_resid_data %>% 
-        filter(model=="CD" & CSP=="w/o CSP"), 
-      mapping=aes(
-        x=Year,
-        y=Residuals,
-        fill=energy, 
-        shape=energy 
-        )
-      ) +
-    facet_grid( flavor ~ Country) +
-    geom_hline(yintercept = 0, colour="gray50", size=0.1) +
-    scale_x_continuous(breaks=c(1960, 1980, 2000)) +
-    xlab("") +
-    ylab("r") + 
-    xy_theme() +
-    # This is custom stuff here to match the model_points_style function. 
-    # We can't use model_points_style, because the aesthetics are different here
-    scale_fill_manual(values = c("transparent", "transparent")) +
-    scale_shape_manual(values = c(21, 23)) +
-  theme(legend.title=element_blank())
-@
-%
-Table~\ref{tab:Effect_of_CSP_CD} shows the effect of the CSP 
-on fitted parameters for the Cobb-Douglas model and the exponential-only model.
-The Cobb-Douglas models show lower $sse$ than the exponential-only models.
-The Cobb-Douglas models also reduce solow residual ($\lambda$) relative
-to the exponential-only case.
-%
-<<Effect_of_CSP_CD, results="asis">>=
-data_CSP_CD <- 
-  AllCoeffs %>%
-  filter((model=="CD" & flavor=="Unadjusted" & energy=="Without energy") | model=="exp") %>% 
-  select(Country, model, CSP, scale, lambda, alpha_1, alpha_2, sse)
-
-data_CSP_CD <- plyr::rename(data_CSP_CD, c("alpha_1" = "$\\alpha_1$", "alpha_2" = "$\\alpha_2$"))
-
-myXTable(data_CSP_CD,
-         caption="Model parameters for Cobb-Douglas models with unadjusted factors of production, without energy.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-%
-Table~\ref{tab:CD_coeffs} shows coefficients for all fitted Cobb-Douglas models
-and the reference model (exponential-only).
-%
-<<CD_coeffs, results="asis">>=
-data_CD_exp <- 
-  AllCoeffs %>% 
-  filter(model=="CD" | model=="exp") %>% 
-  select(Country, model, flavor, energy, CSP, scale, lambda, alpha_1, alpha_2, alpha_3, sse)
-
-data_CD_exp <- plyr::rename(data_CD_exp, c("alpha_1" = "$\\alpha_1$", 
-                                           "alpha_2" = "$\\alpha_2$", 
-                                           "alpha_3" = "$\\alpha_3$"))
-myXTable(data_CD_exp,
-         caption="Model parameters for all Cobb-Douglas models.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-%
-
-Table~\ref{tab:DSRsse_CD} shows $\Delta \lambda$ and $\Delta sse$ results for the Cobb-Douglas models.
-%
-<<DSRsse_CD, results="asis">>=
-myXTable(AllCoeffs %>% 
-           filter(model=="CD") %>% 
-           select(Country, model, flavor, energy, CSP, Dlambda, Dsse),
-         caption="$\\Delta \\lambda$ and $\\Delta sse$ for Cobb-Douglas models.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-%
-
-%
-Figures~\ref{fig:DSRsse_CD_graph} and~\ref{fig:percDSRsse_CD_graph} summarize 
-$\Delta \lambda$ and $\Delta sse$ 
-results for the Cobb-Douglas model.
-%
-<<DSRsse_CD_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta sse$) for the Cobb-Douglas model relative to the exponential-only model.">>=
-ggplot() +
-  geom_point(data=AllCoeffs %>% filter(model=="CD"), 
-             mapping=aes(x=Dsse, y=Dlambda, color=energy, size=CSP)) +
-  facet_grid(Country ~ flavor) +
-  scale_size_manual(values=c(2,3.5)) +
-  xlab(expression(Delta * sse)) + 
-  ylab(expression(Delta * lambda)) +
-  scale_y_continuous(limits=c(-0.04, 0)) +
-  xy_theme() + 
-  theme(legend.title=element_blank())
-@
-%
-<<percDSRsse_CD_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Percentage change in Solow Residuals~($\\Delta\\lambda \\, [\\%]$) and mean squared error~($\\Delta sse \\, [\\%]$) for the Cobb-Douglas model relative to exponential-only models.">>=
-ggplot() +
-  geom_point(data=AllCoeffs %>% filter(model=="CD"), 
-             mapping=aes(x=percDsse, y=percDlambda, color=energy, size=CSP)) +
-  facet_grid(Country ~ flavor) +
-  scale_size_manual(values=c(2,3.5)) +
-  xlab(expression(paste(Delta * sse, " [%]"))) + 
-  scale_x_continuous(breaks=seq(-50, 50, 50), limits=c(-90, 50)) +  
-  ylab(expression(paste(Delta * lambda, " [%]"))) +
-  scale_y_continuous(breaks=seq(-80, 0, 20), limits=c(-100, 10)) +  
-  xy_theme() + 
-  theme(legend.title=element_blank())
-@
-%
-<<DSRsse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta sse$) for the CES modles relative to the exponential-only model.">>=
-ggplot() +
-  geom_point(data=AllCoeffs %>% filter(model=="CES"), 
-             mapping=aes(x=Dsse, y=Dlambda, color=energy, size=CSP, shape=nest)) +
-  scale_size_manual(values=c(2,3.5)) +
-  scale_shape_manual(values=c(16,17,18,15)) +
-  facet_grid(Country ~ flavor) +
-  xlab(expression(Delta * sse)) + 
-  scale_x_continuous(breaks=seq(-0.005, 0, 0.005)) +  
-  ylab(expression(Delta * lambda)) +
-  xy_theme() +
-  theme(legend.title=element_blank())
-@
-%
-<<percDSRsse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Percentage change in Solow Residuals~($\\Delta\\lambda \\, [\\%]$) and mean squared error~($\\Delta sse \\, [\\%]$) for the CES models relative to the exponential-only model.">>=
-ggplot() +
-  geom_point(data=AllCoeffs %>% filter(model=="CES"), 
-             mapping=aes(x=percDsse, y=percDlambda, color=energy, size=CSP, shape=nest)) +
-  scale_size_manual(values=c(2,3.5)) +
-  scale_shape_manual(values=c(16,17,18,15)) +
-  facet_grid(Country ~ flavor) +
-  xlab(expression(paste(Delta * SSE, " [%]"))) + 
-  scale_x_continuous(breaks=seq(-80, 0, 20)) +  
-  ylab(expression(paste(Delta * lambda, " [%]"))) +
-  scale_y_continuous(breaks=seq(-80, 0, 20), limits=c(-100, 10)) +  
-  xy_theme() +
-  theme(legend.title=element_blank())
-@
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{CES Graveyard} 
-\label{sec:ces_graveyard}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Table~\ref{tab:CES_alpha} shows 
-output elasticities~($\alpha$) for all modeling choices.
-
-Here is a table of $\alpha$ values. 
-These values represent the initial points of the trajectories. 
-We no longer use these values. 
-Instead, we use the time-dependent values of alpha.
-So, this table goes in the graveyard.
-
-<<CES_alpha, results="asis">>=
-data_CES_alpha <- 
-  table_data %>% 
-  filter(Model=="CES" | Model=="Ref.") %>% 
-  select(Country, Model, CSP, flavor, Energy, Nest, alpha_1, alpha_2, alpha_3) %>%
-  plyr::rename(c("flavor" = "Factors of prod.",
-                 "alpha_1" = "$\\alpha_k$",
-                 "alpha_2" = "$\\alpha_l$",
-                 "alpha_3" = "$\\alpha_e$"))
-myXTable(data_CES_alpha,
-         caption="Output elasticities~($\\alpha$) for all models.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=3)
-@
-
-Here is a table of the raw CES coefficient values. 
-This table is not used in the paper, so I'm putting it in the graveyard.
-<<CES_sigma, results="asis">>=
-### Is sigma_data defined anywhere?
-
-# data_CES_sigma_raw <- sigma_data %>% select(Country, Model, flavor, Energy, Nest, CSP, sigma_1, sigma)
-# data_CES_sigma_raw <- plyr::rename(data_CES_sigma_raw, c("sigma" = "$\\sigma$",
-#                                                          "sigma_1" = "$\\sigma_1$"))
-# data_CES_sigma_raw <- plyr::rename(data_CES_sigma_raw, c("flavor" = "Factors of prod."))
-# data_CES_sigma_raw$CSP <- plyr::mapvalues(data_CES_sigma_raw$CSP, 
-#                                          from=c("w/ CSP", "w/o CSP"), 
-#                                          to=c("Adhere", "Reject"))
-# data_CES_sigma_raw$Energy <- plyr::mapvalues(data_CES_sigma_raw$Energy, 
-#                                          from=c("Without energy", "With energy"), 
-#                                          to=c("Without", "With"))
-
-data_CES_sigma_raw <- AllCoeffs %>%
-  filter(model=="CES") %>%
-   mutate(
-     Nest = plyr::mapvalues(nest,
-                            from=c("kl", "kle", "lek", "ekl"),
-                            to=c("$kl$", "$(kl)e$", "$(le)k$", "$(ek)l$")),
-     CSP = plyr::mapvalues(CSP, 
-                           from=c("w/ CSP", "w/o CSP"), 
-                           to=c("Adhere", "Reject")),
-     Energy = plyr::mapvalues(energy, 
-                              from=c("Without energy", "With energy"), 
-                              to=c("Without", "With"))
-     ) %>%
-  select(Country, flavor, Energy, Nest, CSP, sigma_1, sigma) %>%
-  plyr::rename(
-    c("sigma" = "$\\sigma$",
-      "sigma_1" = "$\\sigma_1$",
-      "flavor" = "Factors of Prod."))
-
-myXTable(data_CES_sigma_raw,
-         caption="Factor substitution~($\\sigma$) for CES models.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-%
-<<Graphs_CESlek-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with $kl$ and ($le$)$k$ nesting that reject the CSP. Solid line is historical GDP.">>=
-fittedGraphData_lek <- fitted_and_resid_data %>% filter(model=="CES" & CSP=="w/o CSP" & (nest == "kl" | nest == "lek"))
-fittedGraphNoCSP(fittedGraphData_lek)
-@
-%
-<<Graphs_CESekl-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with $kl$ and ($ek$)$l$ nesting that reject the CSP. Solid line is historical GDP.">>=
-fittedGraphData_ekl <- 
-  fitted_and_resid_data %>% 
-  filter(model=="CES" & CSP=="w/o CSP" & (nest == "kl" | nest == "ekl"))
-fittedGraphNoCSP(fittedGraphData_ekl)
-@
-%
-Figures~\ref{fig:Graphs CESkle-resid}--\ref{fig:Graphs CESekl-resid}
-show fitting residuals for all CES models.
-%
-<<Graphs_CESkle-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(kl$)$e$ nesting.">>=
-cesResidualPlot2(
-  fitted_and_resid_data %>% 
-    filter(model=="CES" & CSP=="w/o CSP" & (nest=="kle" | nest=="kl"))
-)
-@
-%
-<<Graphs_CESlek-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with ($le$)$k$ nesting.">>=
-cesResidualPlot2(
-  fitted_and_resid_data %>% 
-    filter(model=="CES" & CSP=="w/o CSP" & (nest == "lek" | nest=="kl"))
-)
-@
-%
-<<Graphs_CESekl-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(ek$)$l$ nesting.">>=
-cesResidualPlot2(
-  fitted_and_resid_data %>% 
-    filter(model=="CES" & CSP=="w/o CSP" & (nest=="ekl" | nest=="kl"))
-)
-@
-
-<<SRsse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Solow Residuals~($\\lambda$) and mean squared error~($sse$).
-$\\lambda$ and $sse$ values for the reference (exponential-only) model are shown as gridlines.">>=
-data_sr_sse <- 
-  AllCoeffs %>% 
-  filter(model=="CES") %>% 
-  mutate(nest = 
-           plyr::mapvalues(
-             nest, 
-             from=c("kl", "kle", "lek", "ekl"), 
-             to=c("kl", "(kl)e", "(le)k", "(ek)l")
-             ),
-         Model = interaction(nest, CSP, sep = " ", drop=TRUE),
-         Inputs = flavor
-  )
-ggplot() +
-  geom_point(data=data_sr_sse, mapping=aes(x=sse, y=lambda, color=energy, size=CSP, shape=nest)) +
-  geom_vline(aes(xintercept = sse), 
-             AllCoeffs %>% filter(model=="exp") %>% select(Country, sse), 
-             colour="gray50", size=0.1) +
-  geom_hline(aes(yintercept = lambda), 
-             AllCoeffs %>% filter(model=="exp") %>% select(Country, lambda), 
-             colour="gray50", size=0.1) +
-  scale_size_manual(values=c(2,4)) +
-  scale_shape_manual(values=c(1,0,3,4)) + 
-  facet_grid(flavor ~ Country) +
-  scale_y_continuous(breaks=c(0, 0.01, 0.02, 0.03), limits=c(0, 0.035)) +
-  xlab("SSE") + 
-  ylab(expression(lambda)) +
-  xy_theme() +
-  theme(legend.title=element_blank())
-
-@
-
-<<SRsse_CES_graph_2, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=2.5, fig.cap="Solow Residuals~($\\lambda$) and mean squared error~($sse$).
-$\\lambda$ and $sse$ values for the reference (exponential-only) model are shown as gridlines.
-This version uses our proposed new style.">>=
-data_sr_sse <- 
-  AllCoeffs %>% 
-  filter(model=="CES") %>% 
-  mutate(nest = 
-           plyr::mapvalues(
-             nest, 
-             from=c("kl", "kle", "lek", "ekl"), 
-             to=c("kl", "(kl)e", "(le)k", "(ek)l")
-             ),
-         Model = interaction(nest, CSP, sep = " ", drop=TRUE),
-         Inputs = flavor
-  )
-
-p <- ggplot() +
-  geom_point(
-    data=data_sr_sse, 
-    mapping=aes(
-      x=lambda, 
-      y=sse, 
-      fill=Model, 
-      shape=Model, 
-      size=Model, 
-      color=Inputs
-      )) +
-  geom_vline(aes(xintercept = lambda), 
-             AllCoeffs %>% filter(model=="exp") %>% select(Country, lambda), 
-             colour="gray50", size=0.1) +
-  geom_hline(aes(yintercept = sse), 
-             AllCoeffs %>% filter(model=="exp") %>% select(Country, sse), 
-             colour="gray50", size=0.1) +
-  facet_grid(. ~ Country) +
-  scale_x_continuous(breaks=c(0, 0.01, 0.02, 0.03), limits=c(0, 0.035)) +
-  xlab(expression(lambda)) +
-  scale_y_continuous(limits=c(-0.05, 0.7)) +
-  ylab("SSE") + 
-  labs(color = "Factors of production") +
-  xy_theme() # +
-  # theme(legend.title=element_blank())
-
-# Add our style
-model_points_style(p)
-
-@
-
-Figures~\ref{fig:Factor_shares_graph_PT} and~\ref{fig:Factor_shares_graph_UK}
-show factor shares ($\alpha$ values) for CES models for
-Portugal and the UK, respectively.
-See Table~\ref{tab:CES_abg_equations} for details on the calculation
-of factor shares from fitted values of $\delta_1$ and $\delta$.
-%
-<<Factor_shares_bar_graph_function>>=
-fsbg <- function(coun, mod){
-  bar_chart_data <- 
-    AllCoeffs %>% 
-    filter(Country==coun & model==mod) %>% 
-    select(Country, model, flavor, energy, nest, CSP, alpha_1, alpha_2, alpha_3) %>%
-    mutate(nest =   # Change nest to a nicer-looking nest string
-             plyr::mapvalues(nest, 
-                             from=c("kl", "kle", "lek", "ekl"), 
-                             to=c("kl", "(kl)e", "(le)k", "(ek)l")),
-           label = # Add a label column
-              paste(CSP, flavor, energy, nest, sep=", "),
-           label =  # Add row numbers to the label column
-              paste(paste0(1:length(label), ". "), label)
-    )
-  # Capture the order that we want for the models on the vertical axis.
-  order <- bar_chart_data$label
-  # Now melt the data
-  ### tidyr::spread and tidyr::gather are preferred in most cases now
-#   bar_chart_data <- melt(bar_chart_data, 
-#                          measure.vars = c("alpha_1", "alpha_2", "alpha_3"), 
-#                          value.name = "value", 
-#                          variable.name = "variable")
-  bar_chart_data <-
-    bar_chart_data %>% gather( key=variable, value=value, alpha_1 : alpha_3 )
-
-  # Make the plot
-  plot <- ggplot(bar_chart_data, mapping=aes(x=label, y=value, fill=variable, width=0.4)) + 
-    geom_bar(stat="identity") + 
-    xlab("") +
-    scale_x_discrete(limits=rev(order)) +
-    ylab("") +
-    scale_y_continuous(breaks=c(0, 0.5, 1)) + 
-    guides(fill=guide_legend(title=NULL)) +
-    coord_flip() + 
-    scale_fill_brewer(palette="OrRd", 
-                      labels=c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e]))) +
-    xy_theme() +
-    theme(axis.ticks.y = element_blank())
-  return(plot)
-}
-@
-
-<<Factor_shares_graph_PT, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=2.5, fig.cap="Factor shares ($\\alpha$ values) for CES models for Portugal.">>=
-fsbg(coun = "PT", mod = "CES")
-@
-
-<<Factor_shares_graph_UK, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=2.5, fig.cap="Factor shares ($\\alpha$ values) for CES models for the UK.">>=
-fsbg(coun = "UK", mod = "CES")
-@
-
-<<output_elasticities_graph_ternary, fig.pos="H", fig.align="center", fig.width=6.5, fig.height=2.3, fig.cap="Ternary graph of output elasticities~($\\alpha$).
-This version shows all Unadjusted and Quality-adjusted points on the same graph.
-Perhaps it is easier to see the effect of quality-adjustment of data this way.">>=
-#p <- triPlot(
-#  data=
-p <-
-  AllCoeffs %>% filter(model == "CES") %>%
-    mutate( nest = plyr::mapvalues(nest, 
-                                   from=c("kle", "lek", "ekl"), 
-                                   to=c("(kl)e", "(le)k", "(ek)l")),
-            Model = interaction(nest, CSP, sep = " ", drop=TRUE),
-            Inputs = flavor
-            ) %>%
-  ggplot() +
-  tri_theme() +
-  tri_grid(grid_lines = 5) +
-#  tri_labels(labels = c("alpha[k]", "alpha[l]", "alpha[e]")) +
-  geom_tripoint(
-    aes(
-      x = alpha_1, y = alpha_2, z = alpha_3, 
-      fill  = Model, 
-      shape = Model,
-      size = Model,
-      color = Inputs)
-  ) +
-  labs(color = "Factors of production") +
-  facet_grid(. ~ Country)
-
-  model_points_style(p)
-@
-
-<<output_elasticities_graph_ternary_2, fig.pos="H", fig.align="center", fig.width=6.5, fig.height=4.1, fig.cap="Ternary graph of output elasticities~($\\alpha$).
-This version splits the Unadjusted and Quality-adjusted values on their own graphs.
-This approach is parallel to the previous figures (historical data, fitted GDP, and residuals.">>=
-p <- 
-#    triPlot(
-#  data=
-    AllCoeffs %>% filter(model == "CES") %>%
-    mutate( nest = plyr::mapvalues(nest, 
-                                   from=c("kle", "lek", "ekl"), 
-                                   to=c("(kl)e", "(le)k", "(ek)l")),
-            Model = interaction(nest, CSP, sep = " ", drop=TRUE),
-            Inputs = flavor) %>%
-    ggplot() +
-    tri_theme() + 
-    tri_grid(grid_lines = 5) +
-    tri_labels(labels = c("alpha[k]", "alpha[l]", "alpha[e]")) +
-    geom_tripoint(
-      aes(
-        x = alpha_1, y = alpha_2, z = alpha_3, 
-        fill  = Model, 
-        shape = Model,
-        size = Model
-      # color = Inputs
-      )
-  ) +
-  facet_grid(Inputs ~ Country)
-
-  model_points_style_quad(p)
-@
-
-<<>>=
-OEplot <- function( data ) {
-  ggplot( data %>% 
-          mutate(
-            slice = interaction(Country, flavor, lex.order=TRUE, sep= " ")
-            )
-          ) +
-    tri_theme() +
-    tri_grid() +
-    tri_labels(labels = c("alpha[k]", "alpha[l]", "alpha[e]"), parse = TRUE) +
-    geom_tripath( 
-      aes(x=oe1, y=oe2, z=oe3, 
-          colour = Year,
-          group=interaction(Country, nest, flavor)),
-      alpha=0.6,  size=1) +
-    geom_tripoint( 
-      aes(x=oe1, y=oe2, z=oe3, colour = Year, size=Year), 
-      alpha=0.7, shape=21)  +
-    scale_colour_gradient(low = scales::muted("navy"),  high = "green") +
-    facet_grid(nest ~ slice) +
-    scale_size_continuous( range = c(1.4, 4))
-}
-
-OEplot2 <- function( data ) {
-  ggplot( data %>% 
-          mutate(
-            slice = interaction(Country, flavor, lex.order=TRUE, sep= " ")
-            )
-          ) +
-    tri_theme() +
-    tri_grid() +
-    tri_labels(labels = c("alpha[k]", "alpha[l]", "alpha[e]"), parse = TRUE) +
-    geom_tripath( 
-      aes(x=oe1, y=oe2, z=oe3, 
-          colour = Year,
-          group=interaction(Country, nest, flavor)),
-      alpha=0.6,  size=1) +
-    scale_colour_gradient(low = scales::muted("navy"),  high = "green") +
-    facet_grid(nest ~ slice) +
-    scale_size_continuous( range = c(1.4, 4))
-}
-OEplot(AllOE) 
-OEplot2(AllOE) 
-@
-
-<<>>=
-ggplot(AllOE %>% mutate(split = interaction(Country, flavor, lex.order=TRUE))) +
-  tri_theme() + 
-  tri_grid() +
-  tri_labels( labels = c("alpha[k]", "alpha[l]", "alpha[e]") ) +
-  geom_tripath(alpha = 0.8, size = 1.2,
-               aes(x = oe1, y = oe2, z = oe3,
-                   colour = Year, group = interaction(Country, nest, flavor)
-               ) ) +
-#  geom_tripoint( size = 1.8, alpha = 0.5,
-#                 aes(x = oe1, y = oe2, z = oe3,
-#                     shape = flavor,
-#                     colour = Year
-#                 ) ) +
-  facet_grid( nest~ split) + 
-  scale_shape_manual(values = c(21:25)) +
-  scale_colour_gradient2(low = scales::muted("navy"), mid="red", high = "green", midpoint = 1985)
-
-@
-
-<<>>=
-ggplot(AllOE %>% mutate(split = interaction(Country, flavor, lex.order=TRUE))) +
-  tri_theme() + 
-  tri_grid() +
-  tri_labels( labels = c("alpha[k]", "alpha[l]", "alpha[e]") ) +
-  geom_tripath(alpha = 0.8, size = 1.2,
-               aes(x = oe1, y = oe2, z = oe3,
-                   alpha = Year, 
-                   colour = flavor,
-                   group = interaction(Country, nest, flavor)
-               ) ) +
-  facet_grid( nest~ Country)  +
-  scale_colour_manual(values = c("black", "gray70")) 
-@
-
-<<>>=
-
-OEplot(ReModels)
-OEplot2(ReModels)
-@
-
-<<resample_graph_alpha_ternary, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.0, fig.cap="$\\alpha_k$, $\\alpha_l$, and $\\alpha_e$ values for CES resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
-standardTriPlot(data=resampleCoeffsCES, facet_formula=~Country, alpha=0.1,
-                labels=c("alpha[k]", "alpha[l]", "alpha[e]"), size=2.0)
-@
-
-<<sigma_graph>>=
-sigma_graph <- function(data){
-  sigma_graph_data <- 
-    data %>% 
-    select(Country, CSP, flavor, energy, nest, 
-           sigma_12, sigma_23, sigma_13, 
-           sigma_12_3, sigma_23_1, sigma_13_2) %>%
-    mutate(nest = plyr::mapvalues( # Change nest to a nicer-looking nest string
-      nest, 
-      from=c("kl", "kle", "lek", "ekl"), 
-      to=c("kl", "(kl)e", "(le)k", "(ek)l"))
-    ) %>%
-    gather(variable, value, sigma_12, sigma_23, sigma_13, sigma_12_3, sigma_23_1, sigma_13_2) %>%
-    mutate(label = paste(CSP, flavor, energy, nest, variable, sep=", ")) %>%
-    na.omit()
-
-  # return(sigma_graph_data)
-
-  # Make the plot
-  plot <- ggplot(sigma_graph_data, mapping=aes(x=label, y=value, fill=variable, width=0.4)) + 
-    geom_bar(stat="identity") + 
-    xlab("") +
-    # scale_x_discrete(limits=rev(order)) +
-    scale_x_discrete(labels=sigma_graph_data$label) +
-    geom_hline(aes(yintercept = 1), colour="gray50", size=0.1) +
-    ylab("") +
-    # coord_trans(y="sigma") +
-    scale_y_continuous(limits=c(0, 10), breaks=c(0, 1.0, 10)) +
-    guides(fill=guide_legend(title=NULL)) +
-    scale_fill_brewer(palette="OrRd") +
-#     scale_fill_brewer(palette="OrRd",
-#                       labels=c(expression(sigma[kl]), 
-#                                expression(sigma[le]), 
-#                                expression(sigma[ek]),
-#                                expression(sigma["(kl)e"]),
-#                                expression(sigma["(le)k"]),
-#                                expression(sigma["(ek)l"]))) +
-    coord_flip() + 
-    xy_theme() +
-    theme(axis.ticks.y = element_blank())
-  return(plot)
-}
-@
-
-<<sigma_graph_PT, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for Portugal.">>=
-sigma_graph(AllCoeffs %>% filter(model=="CES", Country=="PT"))
-@
-
-<<sigma_graph_UK, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for the UK.">>=
-sigma_graph(AllCoeffs %>% filter(model=="CES", Country=="UK"))
-@
-
-<<sigma_graph_2, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.82, fig.cap="Elasticities of substitution~($\\sigma$).">>=
-breaks_labels = c(0.01, 0.1, 1, 10, 100)
-p <- 
-ggplot(
-  AllCoeffs %>% 
-    gather(type, value, matches("sigma")) %>% 
-    filter(!is.na(value)) %>% 
-    filter(! type %in% c("sigma", "sigma_1")) %>%
-    mutate(nest = plyr::mapvalues(nest, 
-                                  from=c("kle", "lek", "ekl"), 
-                                  to=c("(kl)e", "(le)k", "(ek)l")),
-           type = relevelFactor(type, c("sigma_12", "sigma_23", "sigma_13", "sigma_12_3", "sigma_23_1", "sigma_13_2")),
-           Model = interaction(nest, CSP, sep = " ", drop=TRUE),
-           Inputs = flavor
-           )
-  ) + 
-  geom_point(aes(x=value, y=type, 
-                 shape = Model, fill=Model, size=Model,
-                 color=Inputs
-                 )
-                 # position = position_jitter(height=0.2, width=0)
-             ) + 
-  facet_grid( type ~ Country, scales = "free_y" ) + 
-  scale_x_log10(limits = c(0.001,2000), breaks=breaks_labels, labels=breaks_labels) +
-  xlab("") +
-  geom_vline(xintercept = 1, color="gray50", size=0.2) +
-  scale_y_discrete(labels = c(
-    sigma_12 = expression(sigma[kl]),
-    sigma_23 = expression(sigma[le]),
-    sigma_13 = expression(sigma[ek]),
-    sigma_12_3 = expression(sigma["(kl)"*e]),
-    sigma_23_1 = expression(sigma["(le)"*k]),
-    sigma_13_2 = expression(sigma["(ek)"*l]))
-    ) +
-  ylab("") +
-  labs(color = "Factors of production") +
-  xy_theme() +
-  theme(
-    legend.position="top",
-    strip.text.y = element_blank(),
-    axis.text.y = element_text(size=12)
-    )
-
-model_points_style(p)
-@
+
+\newpage
+\section*{Author Notes}
+
+\authNotes
 
@@
 %%
-%% End of file `elsarticle-template-2-harv.tex'.
+%% End of file `elsarticle-template-2-harv.tex'.s

### 2015-10-17 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Remove cruft from EcolEcon_2015A.Rnw

@@
 <<Table_data>>=
-print("Top of Table_data")
-
 table_data <- 
@@
 
-<<CES_sr_gof, results="asis">>=
-print("Top of CES sr gof")
-
-data_CES_SR_gof <- 
-  table_data %>% 
-  filter(Model=="CES" | Model=="Ref.") %>% 
-  select(Country, Model, CSP, flavor, Energy, Nest, scale, lambda, sse) %>%
-  plyr::rename(c("flavor" = "Factors of prod.",
-                  "scale" = "$\\theta$",
-                  "lambda" = "$\\lambda$"))
-
-myXTable(data_CES_SR_gof,
-         caption="Scale parameter~($\\theta$), Solow residual~($\\lambda$), and sum of squared errors~($sse$) for all modeling choices.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=c(1,1,1,1,1,1,1, 2, 4, 3))
-@
-
-<<CES_sigma_nest_aware_inner, results="asis">>=
-sigma_inner_data <- 
-  table_data %>% 
-  filter(Model=="CES") %>% 
-  select(Country, CSP, flavor, Energy, Nest, sigma_12, sigma_23, sigma_13) %>%
-  plyr::rename( c("flavor" = "Factors of prod.",
-                  "sigma_12" = "$\\sigma_{kl}$",
-                  "sigma_23" = "$\\sigma_{le}$",
-                  "sigma_13" = "$\\sigma_{ek}$"))
-#
-myXTable(sigma_inner_data,
-         caption="Elasticities of substitution~($\\sigma$) for inner nests of CES models.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=c(1,1,1,1,1,1, 3,3,3))
-@
-
-<<CES_sigma_nest_aware_outer, results="asis">>=
-sigma_outer_data <- 
-  table_data %>% 
-  filter(Model=="CES") %>% 
-  select(Country, CSP, flavor, Energy, Nest, sigma_12_3, sigma_23_1, sigma_13_2) %>%
-  plyr::rename(c("flavor" = "Factors of prod.", 
-                 "sigma_12_3" = "$\\sigma_{(kl)e}$",
-                 "sigma_23_1" = "$\\sigma_{(le)k}$",
-                 "sigma_13_2" = "$\\sigma_{(ek)l}$"))
-myXTable(sigma_outer_data,
-         caption="Elasticities of substitution~($\\sigma$) for outer nests of CES models.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=c(1,1,1,1,1,1, 3,3,3))
-@
-
-<<Historical_Data_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Historical data.", warning=FALSE>>=
+<<Historical_Data>>=
 
@@
   )
-
-ggplot(histDataForGraph) + 
-  geom_line(aes(x=Year, y=value, group=variable, linetype=variable, colour=variable, size=variable)) +
-  facet_grid(flavor ~ Country) + 
-  scale_color_manual(name = "", values=c("black", "black", "black", "gray70")) +
-  scale_linetype_manual(name="", values=c(1,2,3,1)) + 
-  scale_size_manual(name="", values = c(1, 0.9, 0.9, 0.6)) +
-  scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12), limits=c(0.5, 12)) +
-  xlab("") + 
-  ylab("Indexed (1960=1)") +
-  xy_theme()
 @
@@
 }
-@
-
-<<Graphs_CESkle-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with $kl$ and ($kl$)$e$ nesting that reject the CSP. Solid line is historical GDP.">>=
-fittedGraphData_kle <- 
-  fitted_and_resid_data %>% 
-  filter(model=="CES" & CSP=="w/o CSP" & (nest == "kl" | nest == "kle"))
-
-fittedGraphNoCSP(fittedGraphData_kle)
 @
@@
 
-<<Resid_plot_with_ref, eval=FALSE, include=FALSE>>=
-# This version of the residual plot includes reference model residuals.
-# But the reference model dwarfs all other residuals and looks bad on the graph.
-# So, I decided not to use this. ---MKH, 14 Aug 2015
-
-# residualPlot <- function(data, withEnergyShape = 0){
-#   # Keep only the data we need
-#   residGraphData <- select(data, Year, Country, Residuals, flavor, energy, model, nest, CSP, ResidualsExp)
-#   # Melt the data so that we can include the reference model, too.
-#   residGraphData <- melt(residGraphData, 
-#                          measure.vars=c("Residuals", "ResidualsExp"),
-#                          value.name="value",
-#                          variable.name="variable")
-#   residGraphData$label <- with(residGraphData, paste(variable, energy))
-#   
-#   # Now collapse some of the information. Don't need multiple versions of the exponential model, e.g.
-#   residGraphData <- filter(residGraphData, label=="Residuals With energy" | label=="Residuals Without energy" |
-#                              label=="ResidualsExp Without energy")
-#   
-#   residGraphData$label <- plyr::mapvalues(residGraphData$label, 
-#                                           from = c("Residuals With energy", 
-#                                                    "Residuals Without energy",
-#                                                    "ResidualsExp Without energy"), 
-#                                           to = c("With energy", 
-#                                                  "Without energy",
-#                                                  "Reference model"))
-#   # Relevel factors
-#   residGraphData$label <- relevelFactor(as.factor(residGraphData$label), 
-#                                          c("Without energy", "With energy", "Reference model"))
-#   
-#   ggplot() +
-#     geom_point(data=residGraphData, mapping=aes(x=Year, y=value, shape=label, color=label, size=label)) +
-#     scale_shape_manual(values=c(1, withEnergyShape, 5)) +
-#     scale_size_manual(values=c(4, 4, 2)) +
-#     # scale_color_manual(values=c("gray50", "green", "red")) +
-#     facet_grid(Country ~ flavor) +
-#     geom_hline(yintercept = 0, colour="gray50", size=0.1) +
-#     scale_x_continuous(breaks=c(1960, 1980, 2000)) +
-#     xlab("") +
-#     ylab("r") + 
-#     xy_theme() +
-#     theme(legend.title=element_blank())
-# }
-@
-
-<<SRsse_CES_graph_3, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Solow Residuals~($\\lambda$) and mean squared error~($sse$).
-$\\lambda$ and $sse$ values for the reference (exponential-only) model are shown as gridlines.
-This version uses our proposed new style.">>=
-data_sr_sse <- 
-  AllCoeffs %>% 
-  filter(model=="CES") %>% 
-  mutate(nest = 
-           plyr::mapvalues(
-             nest, 
-             from=c("kl", "kle", "lek", "ekl"), 
-             to=c("kl", "(kl)e", "(le)k", "(ek)l")
-             ),
-         Model = interaction(nest, CSP, sep = " ", drop=TRUE),
-         Inputs = flavor
-  )
-
-p <- ggplot() +
-  geom_point(
-    data=data_sr_sse, 
-    mapping=aes(
-      x=lambda, 
-      y=sse, 
-      fill=Model, 
-      shape=Model, 
-      size=Model #, 
-      # color=Inputs
-      )) +
-  geom_vline(aes(xintercept = lambda), 
-             AllCoeffs %>% filter(model=="exp") %>% select(Country, lambda), 
-             colour="gray50", size=0.1) +
-  geom_hline(aes(yintercept = sse), 
-             AllCoeffs %>% filter(model=="exp") %>% select(Country, sse), 
-             colour="gray50", size=0.1) +
-  facet_grid(flavor ~ Country) +
-  scale_x_continuous(breaks=c(0, 0.01, 0.02, 0.03), limits=c(0, 0.035)) +
-  xlab(expression(lambda)) +
-  scale_y_continuous(limits=c(-0.05, 0.7)) +
-  ylab("SSE") + 
-  labs(color = "Factors of production") +
-  xy_theme() # +
-  # theme(legend.title=element_blank())
-
-# Add our style
-model_points_style_quad(p)
-
-@
-
-<<Graphs_all_models_alphas_time, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap="Output elasticity ($\\alpha$) for all models.">>=
-AllOE %>% 
-  mutate(split =
-           as.character(
-             interaction(
-               factor(flavor, labels = c("QA", "UA")), 
-               factor(nest, 
-                      labels = c("(ek)l", "kl", "(kl)e", "(le)k")), 
-               sep = ", ",
-               lex.order = FALSE ) )
-  ) %>%
-  gather(factor, elasticity, oe1, oe2, oe3) %>%
-  mutate(
-    split2 = relevelFactor(
-      factor(split), 
-      paste( rep(c("UA", "QA"), times = 4 ), 
-             rep(c("kl", "(kl)e", "(le)k", "(ek)l"), each=2),
-             sep=", ")
-    )
-  ) %>%
-  ggplot(aes(x=Year)) + 
-  geom_line( 
-    alpha = .8, # size=1.0,
-    aes(y = elasticity, 
-        colour = factor,
-        linetype=factor,
-        size = factor
-    ) ) +
-  facet_grid(split2 ~ Country) +
-  scale_color_manual(
-    name = "",
-    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
-    values=c("black", "black", "gray70")
-  ) +
-  scale_x_continuous(breaks = c(1960, 1980, 2000)) +
-  scale_y_continuous(breaks = c(0.0, 0.5, 1.0), limits=c(-0.2, 1.2)) +
-  scale_size_manual(
-    name = "",
-    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
-    values = c(.9, .9, .6)) +
-  scale_linetype_manual( 
-    name = "",
-    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
-    values=c(2,3,1) ) + 
-  labs(x="", y="") +
-  xy_theme()
-@
-
-<<sigma_graph_3, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.82, fig.cap="Elasticities of substitution~($\\sigma$) with factors of production on the vertical facet.">>=
-breaks_labels = c(0.01, 0.1, 1, 10, 100)
-p <- 
-  ggplot(
-    AllCoeffs %>% 
-      gather(type, value, matches("sigma")) %>% 
-      filter(!is.na(value)) %>% 
-      filter(! type %in% c("sigma", "sigma_1")) %>%
-      mutate(nest = plyr::mapvalues(nest, 
-                                    from=c("kle", "lek", "ekl"), 
-                                    to=c("(kl)e", "(le)k", "(ek)l")),
-             Model = interaction(nest, CSP, sep = " ", drop=TRUE),
-             Inputs = flavor,
-             type = relevelFactor(type, rev(c("sigma_12", "sigma_23", "sigma_13", "sigma_12_3", "sigma_23_1", "sigma_13_2")))
-             )
-    ) + 
-  geom_point(aes(x=value, 
-                 y=type, 
-                 shape = Model, 
-                 fill=Model, 
-                 size=Model
-                 )
-             ) + 
-  facet_grid( Inputs ~ Country) + 
-  scale_x_log10(limits = c(0.001,2000), breaks=breaks_labels, labels=breaks_labels) +
-  xlab("") +
-  geom_vline(xintercept = 1, color="gray50", size=0.2) +
-  ylab("") +
-  scale_y_discrete(labels = c(
-    sigma_12 = expression(sigma[kl]),
-    sigma_23 = expression(sigma[le]),
-    sigma_13 = expression(sigma[ek]),
-    sigma_12_3 = expression(sigma["(kl)"*e]),
-    sigma_23_1 = expression(sigma["(le)"*k]),
-    sigma_13_2 = expression(sigma["(ek)"*l]))
-    ) +
-  xy_theme() +
-  theme(axis.text.y = element_text(size=12))
-
-model_points_style_quad(p)
-@
-
-<<resample_graph_lambda_theta, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.5, fig.cap="$\\lambda$ and $\\theta$ values for resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
-standardScatterPlot(data=resampleCoeffsCES, mapping=aes(scale, lambda), facet_formula=~Country, alpha=0.05, orig_color = "black") +
-    scale_x_continuous(breaks=c(0.95, 1.0, 1.05)) + 
-    scale_y_continuous(breaks=c(0, 0.005, 0.01), limits=c(0, 0.01)) +
-    labs(x=expression(theta), y=expression(lambda))
-@
-
-<<resample_graph_sigma1_delta1, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.5, fig.cap="$\\sigma_{(kl)}$ and $\\delta_1$ values for resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
-standardScatterPlot(data=resampleCoeffsCES, mapping=aes(delta_1, sigma_1), 
-                    facet_formula=~Country, alpha=0.1) +
-    coord_trans(y="sigma2") +
-    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0), limits=c(0,1)) +
-    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0), limits=c(0, 1e6)) +
-    labs(x=expression(delta[1]), y=expression(sigma[kl]))
-@
-
-<<resample_graph_sigma_delta, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.5, fig.cap="$\\sigma_{(kl)e}$ and $\\delta$ values for resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
-standardScatterPlot(data=resampleCoeffsCES, mapping=aes(delta, sigma), 
-                    facet_formula=~Country, alpha=0.1) +
-    coord_trans(y="sigma2") +
-    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0), limits=c(0,1)) +
-    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0), limits=c(0, 1e6)) +
-    labs(x=expression(delta), y=expression(sigma["(kl)"*e]))
-@
-
-<<resample_graph_alpha, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.2, fig.cap="Resample output elasticities for CES models with $(kl$)$e$ nesting.">>=
-ReModels %>% 
-  gather(factor, elasticity, oe1, oe2, oe3) %>%
-  ggplot(aes(x=Year)) + 
-  geom_line( 
-    aes(y = elasticity,
-        alpha = grepl("orig", id),
-        group = interaction(id, factor),
-        color = factor,
-        linetype = factor,
-        size = grepl("orig", id)
-    ) ) +
-  facet_grid(. ~ Country) +
-
-  scale_x_continuous(breaks = c(1960, 1980, 2000)) +
-  scale_y_continuous(breaks = c(0.0, 0.5, 1.0)) +
-  labs(x="", y="") +
-
-  scale_alpha_manual(
-    name = "",
-    values = c(.3, 1),
-    guide = FALSE) + 
-  scale_color_manual(
-    name = "",
-    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
-    values=c("black", "black", "gray70"),
-    guide=FALSE) +
-  scale_size_manual(
-    name = "",
-    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
-    values = c(.3, .9),
-    guide = FALSE) +
-  scale_linetype_manual( 
-    name = "",
-    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
-    values=c(2,3,1) ) +
-
-  xy_theme() 
-@
-
-<<Correlograms_Exp, echo=FALSE, message=FALSE, include=FALSE, eval=FALSE>>=
-leaf_apply(l = modelsExp, class = c("lm"), f = function(model, name){
-  acf(resid(model), main=name)
-})
-@
-
-<<Correlograms_CSP, echo=FALSE, message=FALSE, include=FALSE, eval=FALSE>>=
-leaf_apply(l = modelsCSP, class = c("lm", "plm"), f = function(model, name){
-  acf(resid(model), main=name)
-})
-@
-
-<<Correlograms_noCSP, echo=FALSE, message=FALSE, include=FALSE, eval=FALSE>>=
-leaf_apply(l = models, class = c("CDEmodel", "cesModel", "LINEXmodel"), f = function(model, name){
-  acf(resid(model), main=name)
-})
-@
-
-%' <<stat_details_table, results="asis", include=FALSE, eval=FALSE>>=
-%' texreg(list(models$PT$adjusted$withE$CES$kle, models$UK$adjusted$withE$CES$kle), 
-%'        dcolumn = TRUE, 
-%'        booktabs = TRUE, 
-%'        use.packages = FALSE, 
-%'        label=paste0("tab:", opts_current$get("label")), 
-%'        caption = "Example output from \\texttt{texreg}.",
-%'        caption.above = TRUE, 
-%'        digits = 6,
-%'        fontsize = "tiny",
-%'        float.pos = "hb")
-%' @
-
-<<Pre-econometric_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Pre-econometric data.", warning=FALSE>>=
-pre_econometric_data <- 
-  leaf_apply(
-    formulas, class = "formula", 
-    f=function(form, name){
-      meta <- strsplit(name, split="[.]") %>% unlist
-      Country <- meta[1]
-      flavor <- meta[2]
-      nums <- summands(form, n=1:3)
-      denom <- summands(form, n=1, right=FALSE)
-      ratios <- lapply(nums, function(num) {paste(num, denom, sep="/")}) %>% unlist
-      coltemplate <- build_formula(NULL, c("Year", ratios))
-      trimmed_historical_data <- historicalData[[Country]][all.vars(coltemplate)]
-      ratio_data <- evalFormula(coltemplate, data=trimmed_historical_data)$right
-      mratio_data <- melt(ratio_data, measure.vars = ratios, value.name = "ratio", variable.name = "variable")
-      mratio_data$Country <- Country
-      mratio_data$flavor <- if (flavor == "adjusted") "Quality-adjusted" else "Unadjusted"
-      return(mratio_data)
-    }
-  ) %>%  
-  bind_rows()
-
-# Fix levels
-pre_econometric_data$flavor <- relevelFactor(as.factor(as.character(pre_econometric_data$flavor)), 
-                                               c("Unadjusted", "Quality-adjusted"))
-pre_econometric_data$Country <- relevelFactor(as.factor(pre_econometric_data$Country), 
-                                              c("PT", "UK"))
-pre_econometric_data$variable <- relevelFactor(as.factor(pre_econometric_data$variable),
-                                               unique(pre_econometric_data$variable))
-# Now make the plot of pre-econometric data
-historicalPlot(pre_econometric_data, 
-               mapping=aes(x=Year, y=ratio, group=variable, linetype=variable), 
-               facet_formula = Country ~ flavor, 
-               line_types = c(2,4,3, 2,4,3, 2,3,2, 3)) + 
-  xlab("") + 
-  ylab("Indexed (1960=1)")
-@
-
-<<Graphs_CD-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Cobb-Douglas models that reject the cost-share theorem. Solid line is historical GDP.">>=
-fittedGraphNoCSP(fitted_and_resid_data %>% filter(model=="CD" & CSP=="w/o CSP"))
-@
-
-<<Graphs_CD-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for Cobb-Douglas models that reject the CSP.">>=
-  ggplot() +
-    geom_point(
-      data=fitted_and_resid_data %>% 
-        filter(model=="CD" & CSP=="w/o CSP"), 
-      mapping=aes(
-        x=Year,
-        y=Residuals,
-        fill=energy, 
-        shape=energy 
-        )
-      ) +
-    facet_grid( flavor ~ Country) +
-    geom_hline(yintercept = 0, colour="gray50", size=0.1) +
-    scale_x_continuous(breaks=c(1960, 1980, 2000)) +
-    xlab("") +
-    ylab("r") + 
-    xy_theme() +
-    # This is custom stuff here to match the model_points_style function. 
-    # We can't use model_points_style, because the aesthetics are different here
-    scale_fill_manual(values = c("transparent", "transparent")) +
-    scale_shape_manual(values = c(21, 23)) +
-  theme(legend.title=element_blank())
-@
-%
-
-<<Effect_of_CSP_CD, results="asis">>=
-data_CSP_CD <- 
-  AllCoeffs %>%
-  filter((model=="CD" & flavor=="Unadjusted" & energy=="Without energy") | model=="exp") %>% 
-  select(Country, model, CSP, scale, lambda, alpha_1, alpha_2, sse)
-
-data_CSP_CD <- plyr::rename(data_CSP_CD, c("alpha_1" = "$\\alpha_1$", "alpha_2" = "$\\alpha_2$"))
-
-myXTable(data_CSP_CD,
-         caption="Model parameters for Cobb-Douglas models with unadjusted factors of production, without energy.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-%
-
-<<CD_coeffs, results="asis">>=
-data_CD_exp <- 
-  AllCoeffs %>% 
-  filter(model=="CD" | model=="exp") %>% 
-  select(Country, model, flavor, energy, CSP, scale, lambda, alpha_1, alpha_2, alpha_3, sse)
-
-data_CD_exp <- plyr::rename(data_CD_exp, c("alpha_1" = "$\\alpha_1$", 
-                                           "alpha_2" = "$\\alpha_2$", 
-                                           "alpha_3" = "$\\alpha_3$"))
-myXTable(data_CD_exp,
-         caption="Model parameters for all Cobb-Douglas models.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-
-<<DSRsse_CD, results="asis">>=
-myXTable(AllCoeffs %>% 
-           filter(model=="CD") %>% 
-           select(Country, model, flavor, energy, CSP, Dlambda, Dsse),
-         caption="$\\Delta \\lambda$ and $\\Delta sse$ for Cobb-Douglas models.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-
-<<DSRsse_CD_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta sse$) for the Cobb-Douglas model relative to the exponential-only model.">>=
-ggplot() +
-  geom_point(data=AllCoeffs %>% filter(model=="CD"), 
-             mapping=aes(x=Dsse, y=Dlambda, color=energy, size=CSP)) +
-  facet_grid(Country ~ flavor) +
-  scale_size_manual(values=c(2,3.5)) +
-  xlab(expression(Delta * sse)) + 
-  ylab(expression(Delta * lambda)) +
-  scale_y_continuous(limits=c(-0.04, 0)) +
-  xy_theme() + 
-  theme(legend.title=element_blank())
-@
-
-<<percDSRsse_CD_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Percentage change in Solow Residuals~($\\Delta\\lambda \\, [\\%]$) and mean squared error~($\\Delta sse \\, [\\%]$) for the Cobb-Douglas model relative to exponential-only models.">>=
-ggplot() +
-  geom_point(data=AllCoeffs %>% filter(model=="CD"), 
-             mapping=aes(x=percDsse, y=percDlambda, color=energy, size=CSP)) +
-  facet_grid(Country ~ flavor) +
-  scale_size_manual(values=c(2,3.5)) +
-  xlab(expression(paste(Delta * sse, " [%]"))) + 
-  scale_x_continuous(breaks=seq(-50, 50, 50), limits=c(-90, 50)) +  
-  ylab(expression(paste(Delta * lambda, " [%]"))) +
-  scale_y_continuous(breaks=seq(-80, 0, 20), limits=c(-100, 10)) +  
-  xy_theme() + 
-  theme(legend.title=element_blank())
-@
-
-<<DSRsse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta sse$) for the CES modles relative to the exponential-only model.">>=
-ggplot() +
-  geom_point(data=AllCoeffs %>% filter(model=="CES"), 
-             mapping=aes(x=Dsse, y=Dlambda, color=energy, size=CSP, shape=nest)) +
-  scale_size_manual(values=c(2,3.5)) +
-  scale_shape_manual(values=c(16,17,18,15)) +
-  facet_grid(Country ~ flavor) +
-  xlab(expression(Delta * sse)) + 
-  scale_x_continuous(breaks=seq(-0.005, 0, 0.005)) +  
-  ylab(expression(Delta * lambda)) +
-  xy_theme() +
-  theme(legend.title=element_blank())
-@
-%
-<<percDSRsse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Percentage change in Solow Residuals~($\\Delta\\lambda \\, [\\%]$) and mean squared error~($\\Delta sse \\, [\\%]$) for the CES models relative to the exponential-only model.">>=
-ggplot() +
-  geom_point(data=AllCoeffs %>% filter(model=="CES"), 
-             mapping=aes(x=percDsse, y=percDlambda, color=energy, size=CSP, shape=nest)) +
-  scale_size_manual(values=c(2,3.5)) +
-  scale_shape_manual(values=c(16,17,18,15)) +
-  facet_grid(Country ~ flavor) +
-  xlab(expression(paste(Delta * SSE, " [%]"))) + 
-  scale_x_continuous(breaks=seq(-80, 0, 20)) +  
-  ylab(expression(paste(Delta * lambda, " [%]"))) +
-  scale_y_continuous(breaks=seq(-80, 0, 20), limits=c(-100, 10)) +  
-  xy_theme() +
-  theme(legend.title=element_blank())
-@
-
-<<CES_alpha, results="asis">>=
-data_CES_alpha <- 
-  table_data %>% 
-  filter(Model=="CES" | Model=="Ref.") %>% 
-  select(Country, Model, CSP, flavor, Energy, Nest, alpha_1, alpha_2, alpha_3) %>%
-  plyr::rename(c("flavor" = "Factors of prod.",
-                 "alpha_1" = "$\\alpha_k$",
-                 "alpha_2" = "$\\alpha_l$",
-                 "alpha_3" = "$\\alpha_e$"))
-myXTable(data_CES_alpha,
-         caption="Output elasticities~($\\alpha$) for all models.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=3)
-@
-
-<<CES_sigma, results="asis">>=
-### Is sigma_data defined anywhere?
-
-# data_CES_sigma_raw <- sigma_data %>% select(Country, Model, flavor, Energy, Nest, CSP, sigma_1, sigma)
-# data_CES_sigma_raw <- plyr::rename(data_CES_sigma_raw, c("sigma" = "$\\sigma$",
-#                                                          "sigma_1" = "$\\sigma_1$"))
-# data_CES_sigma_raw <- plyr::rename(data_CES_sigma_raw, c("flavor" = "Factors of prod."))
-# data_CES_sigma_raw$CSP <- plyr::mapvalues(data_CES_sigma_raw$CSP, 
-#                                          from=c("w/ CSP", "w/o CSP"), 
-#                                          to=c("Adhere", "Reject"))
-# data_CES_sigma_raw$Energy <- plyr::mapvalues(data_CES_sigma_raw$Energy, 
-#                                          from=c("Without energy", "With energy"), 
-#                                          to=c("Without", "With"))
-
-data_CES_sigma_raw <- AllCoeffs %>%
-  filter(model=="CES") %>%
-   mutate(
-     Nest = plyr::mapvalues(nest,
-                            from=c("kl", "kle", "lek", "ekl"),
-                            to=c("$kl$", "$(kl)e$", "$(le)k$", "$(ek)l$")),
-     CSP = plyr::mapvalues(CSP, 
-                           from=c("w/ CSP", "w/o CSP"), 
-                           to=c("Adhere", "Reject")),
-     Energy = plyr::mapvalues(energy, 
-                              from=c("Without energy", "With energy"), 
-                              to=c("Without", "With"))
-     ) %>%
-  select(Country, flavor, Energy, Nest, CSP, sigma_1, sigma) %>%
-  plyr::rename(
-    c("sigma" = "$\\sigma$",
-      "sigma_1" = "$\\sigma_1$",
-      "flavor" = "Factors of Prod."))
-
-myXTable(data_CES_sigma_raw,
-         caption="Factor substitution~($\\sigma$) for CES models.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=6)
-@
-
-<<Graphs_CESlek-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with $kl$ and ($le$)$k$ nesting that reject the CSP. Solid line is historical GDP.">>=
-fittedGraphData_lek <- fitted_and_resid_data %>% filter(model=="CES" & CSP=="w/o CSP" & (nest == "kl" | nest == "lek"))
-fittedGraphNoCSP(fittedGraphData_lek)
-@
-
-<<Graphs_CESekl-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with $kl$ and ($ek$)$l$ nesting that reject the CSP. Solid line is historical GDP.">>=
-fittedGraphData_ekl <- 
-  fitted_and_resid_data %>% 
-  filter(model=="CES" & CSP=="w/o CSP" & (nest == "kl" | nest == "ekl"))
-fittedGraphNoCSP(fittedGraphData_ekl)
-@
-%
-
-<<Graphs_CESkle-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(kl$)$e$ nesting.">>=
-cesResidualPlot2(
-  fitted_and_resid_data %>% 
-    filter(model=="CES" & CSP=="w/o CSP" & (nest=="kle" | nest=="kl"))
-)
-@
-
-<<Graphs_CESlek-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with ($le$)$k$ nesting.">>=
-cesResidualPlot2(
-  fitted_and_resid_data %>% 
-    filter(model=="CES" & CSP=="w/o CSP" & (nest == "lek" | nest=="kl"))
-)
-@
-
-<<Graphs_CESekl-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(ek$)$l$ nesting.">>=
-cesResidualPlot2(
-  fitted_and_resid_data %>% 
-    filter(model=="CES" & CSP=="w/o CSP" & (nest=="ekl" | nest=="kl"))
-)
-@
-
-<<SRsse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Solow Residuals~($\\lambda$) and mean squared error~($sse$).
-$\\lambda$ and $sse$ values for the reference (exponential-only) model are shown as gridlines.">>=
-data_sr_sse <- 
-  AllCoeffs %>% 
-  filter(model=="CES") %>% 
-  mutate(nest = 
-           plyr::mapvalues(
-             nest, 
-             from=c("kl", "kle", "lek", "ekl"), 
-             to=c("kl", "(kl)e", "(le)k", "(ek)l")
-             ),
-         Model = interaction(nest, CSP, sep = " ", drop=TRUE),
-         Inputs = flavor
-  )
-ggplot() +
-  geom_point(data=data_sr_sse, mapping=aes(x=sse, y=lambda, color=energy, size=CSP, shape=nest)) +
-  geom_vline(aes(xintercept = sse), 
-             AllCoeffs %>% filter(model=="exp") %>% select(Country, sse), 
-             colour="gray50", size=0.1) +
-  geom_hline(aes(yintercept = lambda), 
-             AllCoeffs %>% filter(model=="exp") %>% select(Country, lambda), 
-             colour="gray50", size=0.1) +
-  scale_size_manual(values=c(2,4)) +
-  scale_shape_manual(values=c(1,0,3,4)) + 
-  facet_grid(flavor ~ Country) +
-  scale_y_continuous(breaks=c(0, 0.01, 0.02, 0.03), limits=c(0, 0.035)) +
-  xlab("SSE") + 
-  ylab(expression(lambda)) +
-  xy_theme() +
-  theme(legend.title=element_blank())
-
-@
-
-<<SRsse_CES_graph_2, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=2.5, fig.cap="Solow Residuals~($\\lambda$) and mean squared error~($sse$).
-$\\lambda$ and $sse$ values for the reference (exponential-only) model are shown as gridlines.
-This version uses our proposed new style.">>=
-data_sr_sse <- 
-  AllCoeffs %>% 
-  filter(model=="CES") %>% 
-  mutate(nest = 
-           plyr::mapvalues(
-             nest, 
-             from=c("kl", "kle", "lek", "ekl"), 
-             to=c("kl", "(kl)e", "(le)k", "(ek)l")
-             ),
-         Model = interaction(nest, CSP, sep = " ", drop=TRUE),
-         Inputs = flavor
-  )
-
-p <- ggplot() +
-  geom_point(
-    data=data_sr_sse, 
-    mapping=aes(
-      x=lambda, 
-      y=sse, 
-      fill=Model, 
-      shape=Model, 
-      size=Model, 
-      color=Inputs
-      )) +
-  geom_vline(aes(xintercept = lambda), 
-             AllCoeffs %>% filter(model=="exp") %>% select(Country, lambda), 
-             colour="gray50", size=0.1) +
-  geom_hline(aes(yintercept = sse), 
-             AllCoeffs %>% filter(model=="exp") %>% select(Country, sse), 
-             colour="gray50", size=0.1) +
-  facet_grid(. ~ Country) +
-  scale_x_continuous(breaks=c(0, 0.01, 0.02, 0.03), limits=c(0, 0.035)) +
-  xlab(expression(lambda)) +
-  scale_y_continuous(limits=c(-0.05, 0.7)) +
-  ylab("SSE") + 
-  labs(color = "Factors of production") +
-  xy_theme() # +
-  # theme(legend.title=element_blank())
-
-# Add our style
-model_points_style(p)
-
-@
-
-<<Factor_shares_bar_graph_function>>=
-fsbg <- function(coun, mod){
-  bar_chart_data <- 
-    AllCoeffs %>% 
-    filter(Country==coun & model==mod) %>% 
-    select(Country, model, flavor, energy, nest, CSP, alpha_1, alpha_2, alpha_3) %>%
-    mutate(nest =   # Change nest to a nicer-looking nest string
-             plyr::mapvalues(nest, 
-                             from=c("kl", "kle", "lek", "ekl"), 
-                             to=c("kl", "(kl)e", "(le)k", "(ek)l")),
-           label = # Add a label column
-              paste(CSP, flavor, energy, nest, sep=", "),
-           label =  # Add row numbers to the label column
-              paste(paste0(1:length(label), ". "), label)
-    )
-  # Capture the order that we want for the models on the vertical axis.
-  order <- bar_chart_data$label
-  # Now melt the data
-  ### tidyr::spread and tidyr::gather are preferred in most cases now
-#   bar_chart_data <- melt(bar_chart_data, 
-#                          measure.vars = c("alpha_1", "alpha_2", "alpha_3"), 
-#                          value.name = "value", 
-#                          variable.name = "variable")
-  bar_chart_data <-
-    bar_chart_data %>% gather( key=variable, value=value, alpha_1 : alpha_3 )
-
-  # Make the plot
-  plot <- ggplot(bar_chart_data, mapping=aes(x=label, y=value, fill=variable, width=0.4)) + 
-    geom_bar(stat="identity") + 
-    xlab("") +
-    scale_x_discrete(limits=rev(order)) +
-    ylab("") +
-    scale_y_continuous(breaks=c(0, 0.5, 1)) + 
-    guides(fill=guide_legend(title=NULL)) +
-    coord_flip() + 
-    scale_fill_brewer(palette="OrRd", 
-                      labels=c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e]))) +
-    xy_theme() +
-    theme(axis.ticks.y = element_blank())
-  return(plot)
-}
-@
-
-<<Factor_shares_graph_PT, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=2.5, fig.cap="Factor shares ($\\alpha$ values) for CES models for Portugal.">>=
-fsbg(coun = "PT", mod = "CES")
-@
-
-<<Factor_shares_graph_UK, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=2.5, fig.cap="Factor shares ($\\alpha$ values) for CES models for the UK.">>=
-fsbg(coun = "UK", mod = "CES")
-@
-
-<<output_elasticities_graph_ternary, fig.pos="H", fig.align="center", fig.width=6.5, fig.height=2.3, fig.cap="Ternary graph of output elasticities~($\\alpha$).
-This version shows all Unadjusted and Quality-adjusted points on the same graph.
-Perhaps it is easier to see the effect of quality-adjustment of data this way.">>=
-#p <- triPlot(
-#  data=
-p <-
-  AllCoeffs %>% filter(model == "CES") %>%
-    mutate( nest = plyr::mapvalues(nest, 
-                                   from=c("kle", "lek", "ekl"), 
-                                   to=c("(kl)e", "(le)k", "(ek)l")),
-            Model = interaction(nest, CSP, sep = " ", drop=TRUE),
-            Inputs = flavor
-            ) %>%
-  ggplot() +
-  tri_theme() +
-  tri_grid(grid_lines = 5) +
-#  tri_labels(labels = c("alpha[k]", "alpha[l]", "alpha[e]")) +
-  geom_tripoint(
-    aes(
-      x = alpha_1, y = alpha_2, z = alpha_3, 
-      fill  = Model, 
-      shape = Model,
-      size = Model,
-      color = Inputs)
-  ) +
-  labs(color = "Factors of production") +
-  facet_grid(. ~ Country)
-
-  model_points_style(p)
-@
-
-<<output_elasticities_graph_ternary_2, fig.pos="H", fig.align="center", fig.width=6.5, fig.height=4.1, fig.cap="Ternary graph of output elasticities~($\\alpha$).
-This version splits the Unadjusted and Quality-adjusted values on their own graphs.
-This approach is parallel to the previous figures (historical data, fitted GDP, and residuals.">>=
-p <- 
-#    triPlot(
-#  data=
-    AllCoeffs %>% filter(model == "CES") %>%
-    mutate( nest = plyr::mapvalues(nest, 
-                                   from=c("kle", "lek", "ekl"), 
-                                   to=c("(kl)e", "(le)k", "(ek)l")),
-            Model = interaction(nest, CSP, sep = " ", drop=TRUE),
-            Inputs = flavor) %>%
-    ggplot() +
-    tri_theme() + 
-    tri_grid(grid_lines = 5) +
-    tri_labels(labels = c("alpha[k]", "alpha[l]", "alpha[e]")) +
-    geom_tripoint(
-      aes(
-        x = alpha_1, y = alpha_2, z = alpha_3, 
-        fill  = Model, 
-        shape = Model,
-        size = Model
-      # color = Inputs
-      )
-  ) +
-  facet_grid(Inputs ~ Country)
-
-  model_points_style_quad(p)
-@
-
-<<>>=
-OEplot <- function( data ) {
-  ggplot( data %>% 
-          mutate(
-            slice = interaction(Country, flavor, lex.order=TRUE, sep= " ")
-            )
-          ) +
-    tri_theme() +
-    tri_grid() +
-    tri_labels(labels = c("alpha[k]", "alpha[l]", "alpha[e]"), parse = TRUE) +
-    geom_tripath( 
-      aes(x=oe1, y=oe2, z=oe3, 
-          colour = Year,
-          group=interaction(Country, nest, flavor)),
-      alpha=0.6,  size=1) +
-    geom_tripoint( 
-      aes(x=oe1, y=oe2, z=oe3, colour = Year, size=Year), 
-      alpha=0.7, shape=21)  +
-    scale_colour_gradient(low = scales::muted("navy"),  high = "green") +
-    facet_grid(nest ~ slice) +
-    scale_size_continuous( range = c(1.4, 4))
-}
-
-OEplot2 <- function( data ) {
-  ggplot( data %>% 
-          mutate(
-            slice = interaction(Country, flavor, lex.order=TRUE, sep= " ")
-            )
-          ) +
-    tri_theme() +
-    tri_grid() +
-    tri_labels(labels = c("alpha[k]", "alpha[l]", "alpha[e]"), parse = TRUE) +
-    geom_tripath( 
-      aes(x=oe1, y=oe2, z=oe3, 
-          colour = Year,
-          group=interaction(Country, nest, flavor)),
-      alpha=0.6,  size=1) +
-    scale_colour_gradient(low = scales::muted("navy"),  high = "green") +
-    facet_grid(nest ~ slice) +
-    scale_size_continuous( range = c(1.4, 4))
-}
-OEplot(AllOE) 
-OEplot2(AllOE) 
-@
-
-<<>>=
-ggplot(AllOE %>% mutate(split = interaction(Country, flavor, lex.order=TRUE))) +
-  tri_theme() + 
-  tri_grid() +
-  tri_labels( labels = c("alpha[k]", "alpha[l]", "alpha[e]") ) +
-  geom_tripath(alpha = 0.8, size = 1.2,
-               aes(x = oe1, y = oe2, z = oe3,
-                   colour = Year, group = interaction(Country, nest, flavor)
-               ) ) +
-#  geom_tripoint( size = 1.8, alpha = 0.5,
-#                 aes(x = oe1, y = oe2, z = oe3,
-#                     shape = flavor,
-#                     colour = Year
-#                 ) ) +
-  facet_grid( nest~ split) + 
-  scale_shape_manual(values = c(21:25)) +
-  scale_colour_gradient2(low = scales::muted("navy"), mid="red", high = "green", midpoint = 1985)
-
-@
-
-<<>>=
-ggplot(AllOE %>% mutate(split = interaction(Country, flavor, lex.order=TRUE))) +
-  tri_theme() + 
-  tri_grid() +
-  tri_labels( labels = c("alpha[k]", "alpha[l]", "alpha[e]") ) +
-  geom_tripath(alpha = 0.8, size = 1.2,
-               aes(x = oe1, y = oe2, z = oe3,
-                   alpha = Year, 
-                   colour = flavor,
-                   group = interaction(Country, nest, flavor)
-               ) ) +
-  facet_grid( nest~ Country)  +
-  scale_colour_manual(values = c("black", "gray70")) 
-@
-
-<<>>=
-
-OEplot(ReModels)
-OEplot2(ReModels)
-@
-
-<<resample_graph_alpha_ternary, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.0, fig.cap="$\\alpha_k$, $\\alpha_l$, and $\\alpha_e$ values for CES resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
-standardTriPlot(data=resampleCoeffsCES, facet_formula=~Country, alpha=0.1,
-                labels=c("alpha[k]", "alpha[l]", "alpha[e]"), size=2.0)
-@
-
-<<sigma_graph>>=
-sigma_graph <- function(data){
-  sigma_graph_data <- 
-    data %>% 
-    select(Country, CSP, flavor, energy, nest, 
-           sigma_12, sigma_23, sigma_13, 
-           sigma_12_3, sigma_23_1, sigma_13_2) %>%
-    mutate(nest = plyr::mapvalues( # Change nest to a nicer-looking nest string
-      nest, 
-      from=c("kl", "kle", "lek", "ekl"), 
-      to=c("kl", "(kl)e", "(le)k", "(ek)l"))
-    ) %>%
-    gather(variable, value, sigma_12, sigma_23, sigma_13, sigma_12_3, sigma_23_1, sigma_13_2) %>%
-    mutate(label = paste(CSP, flavor, energy, nest, variable, sep=", ")) %>%
-    na.omit()
-
-  # return(sigma_graph_data)
-
-  # Make the plot
-  plot <- ggplot(sigma_graph_data, mapping=aes(x=label, y=value, fill=variable, width=0.4)) + 
-    geom_bar(stat="identity") + 
-    xlab("") +
-    # scale_x_discrete(limits=rev(order)) +
-    scale_x_discrete(labels=sigma_graph_data$label) +
-    geom_hline(aes(yintercept = 1), colour="gray50", size=0.1) +
-    ylab("") +
-    # coord_trans(y="sigma") +
-    scale_y_continuous(limits=c(0, 10), breaks=c(0, 1.0, 10)) +
-    guides(fill=guide_legend(title=NULL)) +
-    scale_fill_brewer(palette="OrRd") +
-#     scale_fill_brewer(palette="OrRd",
-#                       labels=c(expression(sigma[kl]), 
-#                                expression(sigma[le]), 
-#                                expression(sigma[ek]),
-#                                expression(sigma["(kl)e"]),
-#                                expression(sigma["(le)k"]),
-#                                expression(sigma["(ek)l"]))) +
-    coord_flip() + 
-    xy_theme() +
-    theme(axis.ticks.y = element_blank())
-  return(plot)
-}
-@
-
-<<sigma_graph_PT, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for Portugal.">>=
-sigma_graph(AllCoeffs %>% filter(model=="CES", Country=="PT"))
-@
-
-<<sigma_graph_UK, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for the UK.">>=
-sigma_graph(AllCoeffs %>% filter(model=="CES", Country=="UK"))
-@
-
-<<sigma_graph_2, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.82, fig.cap="Elasticities of substitution~($\\sigma$).">>=
-breaks_labels = c(0.01, 0.1, 1, 10, 100)
-p <- 
-ggplot(
-  AllCoeffs %>% 
-    gather(type, value, matches("sigma")) %>% 
-    filter(!is.na(value)) %>% 
-    filter(! type %in% c("sigma", "sigma_1")) %>%
-    mutate(nest = plyr::mapvalues(nest, 
-                                  from=c("kle", "lek", "ekl"), 
-                                  to=c("(kl)e", "(le)k", "(ek)l")),
-           type = relevelFactor(type, c("sigma_12", "sigma_23", "sigma_13", "sigma_12_3", "sigma_23_1", "sigma_13_2")),
-           Model = interaction(nest, CSP, sep = " ", drop=TRUE),
-           Inputs = flavor
-           )
-  ) + 
-  geom_point(aes(x=value, y=type, 
-                 shape = Model, fill=Model, size=Model,
-                 color=Inputs
-                 )
-                 # position = position_jitter(height=0.2, width=0)
-             ) + 
-  facet_grid( type ~ Country, scales = "free_y" ) + 
-  scale_x_log10(limits = c(0.001,2000), breaks=breaks_labels, labels=breaks_labels) +
-  xlab("") +
-  geom_vline(xintercept = 1, color="gray50", size=0.2) +
-  scale_y_discrete(labels = c(
-    sigma_12 = expression(sigma[kl]),
-    sigma_23 = expression(sigma[le]),
-    sigma_13 = expression(sigma[ek]),
-    sigma_12_3 = expression(sigma["(kl)"*e]),
-    sigma_23_1 = expression(sigma["(le)"*k]),
-    sigma_13_2 = expression(sigma["(ek)"*l]))
-    ) +
-  ylab("") +
-  labs(color = "Factors of production") +
-  xy_theme() +
-  theme(
-    legend.position="top",
-    strip.text.y = element_blank(),
-    axis.text.y = element_text(size=12)
-    )
-
-model_points_style(p)
-@
-
 \section{End EcolEcon2015A}

### 2015-10-18 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Move Historical_Plot to EcolEcon_2015A.Rnw. Will be used by more than one paper.

@@
 
+<<Historical_Plot>>=
+ggplot(histDataForGraph) + 
+  geom_line(aes(x=Year, y=value, group=variable, linetype=variable, colour=variable, size=variable)) +
+  facet_grid(flavor ~ Country) + 
+  scale_color_manual(name = "", values=c("black", "black", "black", "gray70")) +
+  scale_linetype_manual(name="", values=c(1,2,3,1)) + 
+  scale_size_manual(name="", values = c(1, 0.9, 0.9, 0.6)) +
+  scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12), limits=c(0.5, 12)) +
+  xlab("") + 
+  ylab("Indexed (1960=1)") +
+  xy_theme()
+@
+
 <<Fitted_and_Residual_Graph_Functions>>=

### 2015-10-18 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Move Historical_Plot to EcolEcon_2015A.Rnw. Will be used by more than one paper.

@@
 
-\title{Paper 1}
+\title{Paper 1 Analysis}
 
@@
 
-<<Historical_Plot, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4.0, fig.cap="Historical data.", warning=FALSE>>=
-ggplot(histDataForGraph) + 
-  geom_line(aes(x=Year, y=value, group=variable, linetype=variable, colour=variable, size=variable)) +
-  facet_grid(flavor ~ Country) + 
-  scale_color_manual(name = "", values=c("black", "black", "black", "gray70")) +
-  scale_linetype_manual(name="", values=c(1,2,3,1)) + 
-  scale_size_manual(name="", values = c(1, 0.9, 0.9, 0.6)) +
-  scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12), limits=c(0.5, 12)) +
-  xlab("") + 
-  ylab("Indexed (1960=1)") +
-  xy_theme()
+<<Historical_Plot_replay, include=TRUE, echo=FALSE, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4.0, fig.cap="Historical data.", warning=FALSE>>=
+<<Historical_Plot>>
 @
@@
   xy_theme()
-@
-
-<<sigma_graph_3, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.82, fig.cap="Elasticities of substitution~($\\sigma$) with factors of production on the vertical facet.">>=
-breaks_labels = c(0.01, 0.1, 1, 10, 100)
-p <- 
-  ggplot(
-    AllCoeffs %>% 
-      gather(type, value, matches("sigma")) %>% 
-      filter(!is.na(value)) %>% 
-      filter(! type %in% c("sigma", "sigma_1")) %>%
-      mutate(nest = plyr::mapvalues(nest, 
-                                    from=c("kle", "lek", "ekl"), 
-                                    to=c("(kl)e", "(le)k", "(ek)l")),
-             Model = interaction(nest, CSP, sep = " ", drop=TRUE),
-             Inputs = flavor,
-             type = relevelFactor(type, rev(c("sigma_12", "sigma_23", "sigma_13", "sigma_12_3", "sigma_23_1", "sigma_13_2")))
-             )
-    ) + 
-  geom_point(aes(x=value, 
-                 y=type, 
-                 shape = Model, 
-                 fill=Model, 
-                 size=Model
-                 )
-             ) + 
-  facet_grid( Inputs ~ Country) + 
-  scale_x_log10(limits = c(0.001,2000), breaks=breaks_labels, labels=breaks_labels) +
-  xlab("") +
-  geom_vline(xintercept = 1, color="gray50", size=0.2) +
-  ylab("") +
-  scale_y_discrete(labels = c(
-    sigma_12 = expression(sigma[kl]),
-    sigma_23 = expression(sigma[le]),
-    sigma_13 = expression(sigma[ek]),
-    sigma_12_3 = expression(sigma["(kl)"*e]),
-    sigma_23_1 = expression(sigma["(le)"*k]),
-    sigma_13_2 = expression(sigma["(ek)"*l]))
-    ) +
-  xy_theme() +
-  theme(axis.text.y = element_text(size=12))
-
-model_points_style_quad(p)
 @

### 2015-10-18 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Eliminate sigma tables from alpha paper.

@@
 
-<<CES_sigma_nest_aware_inner, results="asis">>=
-sigma_inner_data <- 
-  table_data %>% 
-  filter(Model=="CES") %>% 
-  select(Country, CSP, flavor, Energy, Nest, sigma_12, sigma_23, sigma_13) %>%
-  plyr::rename( c("flavor" = "Factors of prod.",
-                  "sigma_12" = "$\\sigma_{kl}$",
-                  "sigma_23" = "$\\sigma_{le}$",
-                  "sigma_13" = "$\\sigma_{ek}$"))
-#
-myXTable(sigma_inner_data,
-         caption="Elasticities of substitution~($\\sigma$) for inner nests of CES models.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=c(1,1,1,1,1,1, 3,3,3))
-@
-
-<<CES_sigma_nest_aware_outer, results="asis">>=
-sigma_outer_data <- 
-  table_data %>% 
-  filter(Model=="CES") %>% 
-  select(Country, CSP, flavor, Energy, Nest, sigma_12_3, sigma_23_1, sigma_13_2) %>%
-  plyr::rename(c("flavor" = "Factors of prod.", 
-                 "sigma_12_3" = "$\\sigma_{(kl)e}$",
-                 "sigma_23_1" = "$\\sigma_{(le)k}$",
-                 "sigma_13_2" = "$\\sigma_{(ek)l}$"))
-myXTable(sigma_outer_data,
-         caption="Elasticities of substitution~($\\sigma$) for outer nests of CES models.",
-         label=paste0("tab:", opts_current$get("label")), 
-         digits=c(1,1,1,1,1,1, 3,3,3))
-@
-
-Looking at boostrap distribution of a parameter.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-<<resample_graph_sigma1_delta1, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.5, fig.cap="$\\sigma_{(kl)}$ and $\\delta_1$ values for resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
-standardScatterPlot(data=resampleCoeffsCES, mapping=aes(delta_1, sigma_1), 
-                    facet_formula=~Country, alpha=0.1) +
-    coord_trans(y="sigma2") +
-    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0), limits=c(0,1)) +
-    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0), limits=c(0, 1e6)) +
-    labs(x=expression(delta[1]), y=expression(sigma[kl]))
-@
-
-<<resample_graph_sigma_delta, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.5, fig.cap="$\\sigma_{(kl)e}$ and $\\delta$ values for resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
-standardScatterPlot(data=resampleCoeffsCES, mapping=aes(delta, sigma), 
-                    facet_formula=~Country, alpha=0.1) +
-    coord_trans(y="sigma2") +
-    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0), limits=c(0,1)) +
-    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0), limits=c(0, 1e6)) +
-    labs(x=expression(delta), y=expression(sigma["(kl)"*e]))
+<<resample_graph_delta_delta_1, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.5, fig.cap="$\\delta$ and $\\delta_1$ values for resample models that reject the cost share theorem, include energy, use quality-adjusted factors of production, and employ the $(kl)e$ nesting.">>=
+standardScatterPlot(data=resampleCoeffsCES, mapping=aes(delta_1, delta), 
+                    facet_formula=~Country, alpha=0.1,
+                    orig_color="black") +
+  scale_x_continuous(limits=c(0, 1), breaks=c(0, 0.5, 1)) +
+  scale_y_continuous(limits=c(0,1), breaks=c(0, 0.5, 1)) +
+  labs(x=expression(delta[1]), y=expression(delta))
 @
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\appendix
+
+<<Graphs_CESlek-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with $kl$ and $(le)k$ nesting that reject the CSP. Solid line is historical GDP.">>=
+fittedGraphData_lek <- 
+  fitted_and_resid_data %>% 
+  filter(model=="CES" & CSP=="w/o CSP" & (nest == "kl" | nest == "lek"))
+
+fittedGraphNoCSP(fittedGraphData_lek)
+@
+
+<<Graphs_CESekl-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with $kl$ and $(ek)l$ nesting that reject the CSP. Solid line is historical GDP.">>=
+fittedGraphData_ekl <- 
+  fitted_and_resid_data %>% 
+  filter(model=="CES" & CSP=="w/o CSP" & (nest == "kl" | nest == "ekl"))
+
+fittedGraphNoCSP(fittedGraphData_ekl)
+@
+
+<<Graphs_CESkle-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(kl$)$e$ nesting.">>=
+cesResidualPlot2(
+  fitted_and_resid_data %>% 
+    filter(model=="CES" & CSP=="w/o CSP" & (nest=="kle" | nest=="kl"))
+)
+@
+
+<<Graphs_CESlek-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with ($le$)$k$ nesting.">>=
+cesResidualPlot2(
+  fitted_and_resid_data %>% 
+    filter(model=="CES" & CSP=="w/o CSP" & (nest == "lek" | nest=="kl"))
+)
+@
+
+<<Graphs_CESekl-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(ek$)$l$ nesting.">>=
+cesResidualPlot2(
+  fitted_and_resid_data %>% 
+    filter(model=="CES" & CSP=="w/o CSP" & (nest=="ekl" | nest=="kl"))
+)
+@
 

### 2015-10-19 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Split models chunk into smaller chunks.

@@
 
-<<Models>>=
-fileNameCDCES <- "EcolEcon2015ModelsCDCES.rds"
+<<Models_CSP>>=
 fileNameCSP <- "EcolEcon2015ModelsCSP.rds"
+if (!rerunModels){
+  # load from the file on disk
+  modelsCSP <- readRDS(fileNameCSP)
+} else {
+  #
+  # Models that adhere to the cost-share theorem
+  #
+
+  modelsCSP <- list()
+  # Output elasticities based on cost share principle
+  alphaCSP <- 0.3 # Fraction of national accounts spent on capital
+  betaCSP <- 0.7 # Fraction of national accounts spent on labor
+  for (country in countries){
+    for (adj in c("unadjusted", "adjusted")){
+      # Replace with better code later. 
+      # Would like to say cdModel(formula, data, factorShares=c(alpha_1 = 0.3, alpha_2 = 0.7, alpha_3 = 0))
+      # or something like that.
+      form <- keep_summands(formulas[[country]][[adj]], n=-3) # Remove energy
+      yVar <- as.name(summands(form, n=1, right=FALSE))
+      kVar <- as.name(summands(form, n=1))
+      lVar <- as.name(summands(form, n=2))
+      tVar <- as.name(summands(form, n=3))
+      data <- historicalData[[country]]
+      # Cobb-Douglas
+      cdModCSP <- 
+        lm(log(eval(yVar)) - alphaCSP*log(eval(kVar)) - betaCSP*log(eval(lVar)) ~ eval(tVar), 
+           data = data)
+      # cdModCSP is an "lm" object. It is not a "CDEmodel" object. 
+      # Thus, it needs its own "naturalCoeffs" attribute if it is to work correctly in the "naturalCoef" function.
+      attr(cdModCSP, "naturalCoeffs") <- data.frame(lambda=coef(cdModCSP)[[2]],
+                                                    logscale=coef(cdModCSP)[[1]], 
+                                                    scale=exp(coef(cdModCSP)[[1]]),
+                                                    alpha_1=alphaCSP,
+                                                    alpha_2=betaCSP, 
+                                                    alpha_3=0
+                                                    )
+      cdModCSP$formula <- form
+      sdata <- subset(data, select=all.vars(form))
+      sdata <- data[complete.cases(sdata), unique(c(all.vars(form), names(data)))]
+      cdModCSP$data <- sdata
+      cdModCSP$response <- sdata$iGDP
+      modelsCSP[[country]][[adj]][["noE"]][["CD"]] <- cdModCSP
+      # CES
+      # The only CES models that can adhere to the CSP are models where
+      # alpha values are constant with respect to time. 
+      # I.e., models where energy is not included AND where rho_1 = 0.
+      # CES models where rho_1 = 0 are the Cobb-Douglas model.
+      # Convienently, we previously fit that model.
+      cesModCSP <- cdModCSP
+      # Again, we need a customized "naturalCoeffs" attribute so that 
+      # the "naturalCoef" function will do the right thing.
+      # "naturalCoeffs" can be based on the same "naturalCoeffs"
+      # from the Cobb-Douglas model, but a few additions are needed.
+      attr(cesModCSP, "naturalCoeffs") <- 
+        naturalCoef(cdModCSP) %>%
+        mutate(
+          delta_1 = naturalCoef(cdModCSP)[["alpha_1"]],
+          delta = 1,
+          rho_1 = 0, 
+          rho = NA,
+          sigma_1 = 1,
+          sigma_12 = 1,
+          sigma = NA,
+          sigma_12_3 = NA
+        )
+      # Add output elasticities (as a function of time) to this model.
+      # This would have been done by a "fortify" function, 
+      # but this is not a typical CES model, so we can't "fortify" it.
+      # Add other metadata, too.
+      cesModCSP$data <- cesModCSP$data %>%
+        mutate(
+          oe1 = alphaCSP,
+          oe2 = betaCSP,
+          oe3 = 0,
+          Country = country, 
+          flavor  = ifelse(adj=="unadjusted", "Unadjusted", "Quality-adjusted"),
+          energy  = "Without energy",
+          model   = "CES", 
+          nest    = "kl",
+          CSP     = "w/ CSP"
+        )
+      modelsCSP[[country]][[adj]][["noE"]][["CES"]][["kl"]] <- cesModCSP
+    }
+  }
+  # Save cost-share theorem models to disk.
+  saveRDS(modelsCSP, file=fileNameCSP)
+}
+
+@
+
+<<Models_Exp>>=
 fileNameExp <- "EcolEcon2015ModelsExp.rds"
@@
   # load from the file on disk
-  models <- readRDS(fileNameCDCES)
-  modelsCSP <- readRDS(fileNameCSP)
   modelsExp <- readRDS(fileNameExp)
-} else {   ### PLEASE USE COMMENTS TO MARK WHERE LONG CHUNKS END; BETTER: AVOID LONG CHUNKS, WHERE POSSIBLE
-
-  ### This has not been inspected by rjp
-
-  # re-run the models and save to disk.
-  # In RStudio, be sure to set the working directory to the source file directory.
-
+} else {
   #
@@
   saveRDS(modelsExp, file=fileNameExp)
+}
 
-  #
-  # Models that adhere to the cost-share theorem
-  #
+@
 
-  modelsCSP <- list()
-  # Output elasticities based on cost share theorem
-  alphaCSP <- 0.3 # Fraction of national accounts spent on capital
-  betaCSP <- 0.7 # Fraction of national accounts spent on labor
-  for (country in countries){
-    for (adj in c("unadjusted", "adjusted")){
-      # Replace with better code later. 
-      # Would like to say cdModel(formula, data, factorShares=c(alpha_1 = 0.3, alpha_2 = 0.7, alpha_3 = 0))
-      # or something like that.
-      form <- keep_summands(formulas[[country]][[adj]], n=-3) # Remove energy
-      yVar <- as.name(summands(form, n=1, right=FALSE))
-      kVar <- as.name(summands(form, n=1))
-      lVar <- as.name(summands(form, n=2))
-      tVar <- as.name(summands(form, n=3))
-      data <- historicalData[[country]]
-      # Cobb-Douglas
-      cdModCSP <- 
-        lm(log(eval(yVar)) - alphaCSP*log(eval(kVar)) - betaCSP*log(eval(lVar)) ~ eval(tVar), 
-           data = data)
-      # cdModCSP is an "lm" object. It is not a "CDEmodel" object. 
-      # Thus, it needs its own "naturalCoeffs" attribute if it is to work correctly in the "naturalCoef" function.
-      attr(cdModCSP, "naturalCoeffs") <- data.frame(lambda=coef(cdModCSP)[[2]],
-                                                    logscale=coef(cdModCSP)[[1]], 
-                                                    scale=exp(coef(cdModCSP)[[1]]),
-                                                    alpha_1=alphaCSP,
-                                                    alpha_2=betaCSP, 
-                                                    alpha_3=0)
-      cdModCSP$formula <- form
-      sdata <- subset(data, select=all.vars(form))
-      sdata <- data[complete.cases(sdata), unique(c(all.vars(form), names(data)))]
-      cdModCSP$data <- sdata
-      cdModCSP$response <- sdata$iGDP
-      modelsCSP[[country]][[adj]][["noE"]][["CD"]] <- cdModCSP
-      # CES
-      # The only CES models that can adhere to the CSP are models where
-      # alpha values are constant with respect to time. 
-      # I.e., models where energy is not included AND where rho_1 = 0.
-      # CES models where rho_1 = 0 are the Cobb-Douglas model.
-      # Convienently, we previously fit that model.
-      cesModCSP <- cdModCSP
-      # Again, we need a customized "naturalCoeffs" attribute so that 
-      # the "naturalCoef" function will do the right thing.
-      # "naturalCoeffs" can be based on the same "naturalCoeffs"
-      # from the Cobb-Douglas model, but a few additions are needed.
-      attr(cesModCSP, "naturalCoeffs") <- 
-        naturalCoef(cdModCSP) %>%
-        mutate(
-          delta_1 = naturalCoef(cdModCSP)[["alpha_1"]],
-          delta = 1,
-          rho_1 = 0, 
-          rho = NA,
-          sigma_1 = 1,
-          sigma_12 = 1,
-          sigma = NA,
-          sigma_12_3 = NA
-        )
-      modelsCSP[[country]][[adj]][["noE"]][["CES"]][["kl"]] <- cesModCSP
-    }
-  }
-  # Save cost-share theorem models to disk.
-  saveRDS(modelsCSP, file=fileNameCSP)
-
+<<Models_CDCES>>=
+fileNameCDCES <- "EcolEcon2015ModelsCDCES.rds"
+if (!rerunModels){
+  # load from the file on disk
+  models <- readRDS(fileNameCDCES)
+} else {
   #
@@
   #
-
   models <- list()
@@
   saveRDS(models, file=fileNameCDCES)  
-}  ### END ELSE FROM WAY UP THERE???
+}
 @
 
-<<Models2>>=
-### TIME FOR A NEW R CHUNK -- That helps detect the end of that long code chunk
-
-### This function is the same in each model group below.  DRY (Don't repeat yourself).
-### Using this makes it (a) easier to see what's going on, and (b) easier to make adjustments
-### that affect all of the situations simultaneously.
-
-### General hint:  If you find yourself wanting to copy and paste a chunk of code, there is usually
-### a better way to do what you are about to do.
-
+<<AllCoeffs>>=
 model2df <- function(mod, id){
@@
 
-# Put all the cost-share theorem (CSP) model coefficients into a data frame
+# Put all the cost-share principle (CSP) model coefficients into a data frame
 AllCoeffsCSP <- 
@@
 
-### It looks like this could also be done the otehr way arround:  We could scoop up all the models
-### into AllCoeffs and then filter to the subsets.
-
-# Get reference values for lambda and sse.
-### This could be done without saving ref if we have no other need for it
-### I've renamed ref to Ref since it is a data frame.
-Ref <- 
-  AllCoeffs %>% 
-  filter(model=="exp") %>% 
-  select(Country, sse, lambda) %>%
-  rename(sse_ref = sse, lambda_ref = lambda)
-AllCoeffs <- merge(AllCoeffs, Ref)
-
-# Calculate differences relative to the reference model
-### If all we need are the differences, we could skip the part where we put the intermediate stuff 
-### into AllCoefs
-
-AllCoeffs <- 
-  AllCoeffs %>%
-  mutate(
-    Dlambda = abs(lambda) - abs(lambda_ref), 
-    Dsse = sse - sse_ref,
-    percDlambda = Dlambda / abs(lambda_ref) * 100, 
-    percDsse = Dsse / sse_ref * 100
-  )
-
 # Relevel factors and re-order data
@@
 
-%' <<>>=
-%' leaf_apply(models, function(mod, id) class(mod), class="cesModel")
-%' @
-
 <<output-elasticity>>=
@@
   id_components <- strsplit(id, split = "[.]")[[1]]
-
-  # return this data frame 
-  ### NOTE: ifelse() and [ ] handle NAs the way we want here
-  ### The former use of [[ ]] was unnecessary and would break things in the new code
-  ### I'm guessing you had [[ ]] because you thought you had a list when you did not.
 
@@
   ) %>% 
-  bind_rows()
+  bind_rows() %>%
+  # None of "models" adheres to the CSP.
+  mutate (CSP = "w/o CSP")
+
+# Now append to AllOE time-varying output elasticities from models that adhere to the CSP.
+# These output elasticities are stored with variable names oe1, oe2, and oe3 in the data object in the models.
+# See the <<Models_CSP>> chunk above.
+# Uncomment when we're ready to add the CSP models to the alpha vs. time graph.
+
+# AllOE <- leaf_apply(modelsCSP, class="lm", f=function(mod, id){
+#   id_components <- strsplit(id, split = "[.]")[[1]]
+#   if (id_components[4] == "CES") {
+#     return(mod$data)
+#   } else {
+#     return(NULL)
+#   }
+# }) %>% 
+#   do.call(plyr::rbind.fill, .) %>%
+#   bind_rows(AllOE, .)
+
 @
@@
 
-### One line for each operation:  first leaf_apply, then rbind, then mutate -- Clarity by Code Convention
 temp_data_CSP <- 

### 2015-10-19 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Now creating rho table.

@@
          digits=c(1,1,1,1,1,1,1, 2, 4, 3))
+@
+
+<<delta_table, results="asis">>=
+data_delta_table <- 
+  table_data %>% 
+  filter(Model=="CES") %>% 
+  select(Country, Model, CSP, flavor, Energy, Nest, delta_1, delta) %>%
+  plyr::rename(c("flavor" = "Factors of prod.",
+                  "scale" = "$\\theta$",
+                  "lambda" = "$\\lambda$",
+                  "delta_1" = "$\\delta_1$",
+                  "delta" = "$\\delta$"))
+
+myXTable(data_delta_table,
+         caption="Distribution parameters ($\\delta_1$ and $\\delta$) for all modeling choices.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=c(1,1,1,1,1,1,1, 3, 3)
+         )
+@
+
+<<rho_table, results="asis">>=
+data_rho_table <- 
+  table_data %>% 
+  filter(Model=="CES") %>% 
+  select(Country, Model, CSP, flavor, Energy, Nest, rho_1, rho) %>%
+  plyr::rename(c("flavor" = "Factors of prod.",
+                  "scale" = "$\\theta$",
+                  "lambda" = "$\\lambda$",
+                  "rho_1" = "$\\rho_1$",
+                  "rho" = "$\\rho$"))
+
+myXTable(data_rho_table,
+         caption="Values of ($\\rho_1$ and $\\rho$) for all modeling choices.",
+         label=paste0("tab:", opts_current$get("label")), 
+         digits=c(1,1,1,1,1,1,1, 3, 3)
+         )
 @

### 2015-10-20 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Added code to load CostShares.

@@
 )
+
+# Load historical cost shares
+CostShares <- read.table(file.path("cost_shares", "Cost_Shares_PT_UK.txt"), header=TRUE)
 @

### 2015-10-20 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Added a CR.
No reason to include Highlights.
Better appendices.
Now including a CostShare plot.

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Highlights}
-\label{sec:highlights}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\emph{This will go in a separate document eventually.}
-
-\begin{itemize}
-\item Highlight 1
-\item Highlight 2
-\item Highlight 3
-\item Highlight 4
-\end{itemize}
-
-%\linenumbers
-
 %%%% Import Analysis chunks
@@
 <<Historical_Plot>>
+@
+
+<<Cost_Share_Plot, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=1.5, fig.cap="Historical cost shares for capital, labor, and energy.">>=
+ggplot(
+  data = gather(CostShares, key=cost_share, value=value, cs_k, cs_l, cs_e)
+  ) + 
+  geom_line(mapping = aes(
+    x = Year, 
+    y = value, 
+    group = cost_share, 
+    linetype = cost_share,
+    color = cost_share)) +
+  facet_grid( ~ Country) +
+  ylab("Cost Share") +
+  scale_y_continuous(limits=c(-0.2, 1.1), breaks=c(0, 0.5, 1)) +
+  geom_hline(aes(yintercept = 0.3), colour="gray50", size=0.1) +
+  geom_hline(aes(yintercept = 0.7), colour="gray50", size=0.1) +
+  xlab("") +
+  scale_x_continuous(breaks=c(1960, 1980, 2000)) +
+  scale_color_manual(name = "", 
+                     labels=c("k", "l", "e"),
+                     values=c("black", "black", "gray70")) +
+  scale_linetype_manual(name="", 
+                        labels=c("k", "l", "e"),
+                        values=c(2,3,1)) + 
+  scale_size_manual(name="", 
+                    labels=c("k", "l", "e"),
+                    values = c(0.9, 0.9, 0.6)) +
+  xy_theme()
 @
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusions}
-\label{sec:conclusion}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\appendix
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Acknowledgements}
-\label{sec:acknowledgements}
+\section{Fitted Graphs}
+\label{sec:appendix_fitted}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\appendix
 
@@
 @
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Residual Graphs}
+\label{sec:appendix_residual}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2015-10-20 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
updates using "fake" objects of classes cdeModel and cesModel

@@
 fileNameCSP <- "EcolEcon2015ModelsCSP.rds"
-if (!rerunModels){
+if (FALSE && !rerunModels){
   # load from the file on disk
@@
     for (adj in c("unadjusted", "adjusted")){
+      print(adj)
       # Replace with better code later. 
@@
       data <- historicalData[[country]]
+      formula <- substitute(
+        log(Y) - alpha_1 * log(K) - alpha_2 * log(L) ~ T,
+        list( Y = yVar, K = kVar, L = lVar, T = tVar, A = alphaCSP, B = betaCSP)
+      )
       # Cobb-Douglas
       cdModCSP <- 
-        lm(log(eval(yVar)) - alphaCSP*log(eval(kVar)) - betaCSP*log(eval(lVar)) ~ eval(tVar), 
-           data = data)
-      # cdModCSP is an "lm" object. It is not a "CDEmodel" object. 
-      # Thus, it needs its own "naturalCoeffs" attribute if it is to work correctly in the "naturalCoef" function.
-      attr(cdModCSP, "naturalCoeffs") <- data.frame(lambda=coef(cdModCSP)[[2]],
-                                                    logscale=coef(cdModCSP)[[1]], 
-                                                    scale=exp(coef(cdModCSP)[[1]]),
-                                                    alpha_1=alphaCSP,
-                                                    alpha_2=betaCSP, 
-                                                    alpha_3=0
-                                                    )
+        eval(substitute( 
+          plm(formula, data = data, params = c(alpha_1 = 0.3, alpha_2 = 0.7, alpha_3 = 0.0), 
+              optimize = FALSE),
+          list(formula = formula)))
+
+      # convert hand-fit object into a CDEmodel object
+      names(cdModCSP$coefficients)[1:2] <- c("logscale", "lambda")
+      class(cdModCSP) <- c("CDEmodel", class(cdModCSP))
       cdModCSP$formula <- form
@@
       cdModCSP$response <- sdata$iGDP
+      cdModCSP$handcrafted <- TRUE
+
+      # store the result in our list
       modelsCSP[[country]][[adj]][["noE"]][["CD"]] <- cdModCSP
@@
       cesModCSP <- cdModCSP
-      # Again, we need a customized "naturalCoeffs" attribute so that 
-      # the "naturalCoef" function will do the right thing.
-      # "naturalCoeffs" can be based on the same "naturalCoeffs"
-      # from the Cobb-Douglas model, but a few additions are needed.
-      attr(cesModCSP, "naturalCoeffs") <- 
-        naturalCoef(cdModCSP) %>%
-        mutate(
-          delta_1 = naturalCoef(cdModCSP)[["alpha_1"]],
-          delta = 1,
+
+      cesModCSP$coefficients <- 
+        c(cesModCSP$coefficients, 
+          c(delta_1 = cesModCSP$coefficients["alpha_1"],
+            delta = 0,
             rho_1 = 0,
-          rho = NA,
-          sigma_1 = 1,
-          sigma_12 = 1,
-          sigma = NA,
-          sigma_12_3 = NA
+            rho = NA)
         )
-      # Add output elasticities (as a function of time) to this model.
-      # This would have been done by a "fortify" function, 
-      # but this is not a typical CES model, so we can't "fortify" it.
-      # Add other metadata, too.
-      cesModCSP$data <- cesModCSP$data %>%
-        mutate(
-          oe1 = alphaCSP,
-          oe2 = betaCSP,
-          oe3 = 0,
-          Country = country, 
-          flavor  = ifelse(adj=="unadjusted", "Unadjusted", "Quality-adjusted"),
-          energy  = "Without energy",
-          model   = "CES", 
-          nest    = "kl",
-          CSP     = "w/ CSP"
-        )
+      cesModCSP$handcrafted <- TRUE
+      class(cesModCSP) <- setdiff(c("cesModel", class(cesModCSP)), "CDEmodel")
+      # # Again, we need a customized "naturalCoeffs" attribute so that 
+      # # the "naturalCoef" function will do the right thing.
+      # # "naturalCoeffs" can be based on the same "naturalCoeffs"
+      # # from the Cobb-Douglas model, but a few additions are needed.
+      # attr(cesModCSP, "naturalCoeffs") <- 
+      #   naturalCoef(cdModCSP) %>%
+      #   mutate(
+      #     delta_1 = naturalCoef(cdModCSP)[["alpha_1"]],
+      #     delta = 1,
+      #     rho_1 = 0, 
+      #     rho = NA,
+      #     sigma_1 = 1,
+      #     sigma_12 = 1,
+      #     sigma = NA,
+      #     sigma_12_3 = NA
+      #   )
+      # # Add output elasticities (as a function of time) to this model.
+      # # This would have been done by a "fortify" function, 
+      # # but this is not a typical CES model, so we can't "fortify" it.
+      # # Add other metadata, too.
+      # cesModCSP$data <- cesModCSP$data %>%
+      #   mutate(
+      #     oe1 = alphaCSP,
+      #     oe2 = betaCSP,
+      #     oe3 = 0,
+      #     Country = country, 
+      #     flavor  = ifelse(adj=="unadjusted", "Unadjusted", "Quality-adjusted"),
+      #     energy  = "Without energy",
+      #     model   = "CES", 
+      #     nest    = "kl",
+      #     CSP     = "w/ CSP"
+      #   )
       modelsCSP[[country]][[adj]][["noE"]][["CES"]][["kl"]] <- cesModCSP

### 2015-10-21 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Beginnings of a <<Fitted_Graph>>=

@@
 
+<<Fitted_Graph, eval=FALSE>>=
+fitted_and_resid_data %>% 
+  filter(model=="CES") %>%
+  gather()
+  melt(measure.vars = c("iGDP", "fitted", "fittedExp"), 
+       value.name = "value", variable.name = "variable") %>%
+  mutate(label = paste(variable, energy)) %>%
+  # Now collapse some of the information. Don't need multiple versions of the exponential model, e.g.
+  filter(label %in% c("iGDP With energy", "fittedExp With energy", 
+                      "fitted With energy", "fitted Without energy")
+  ) %>% 
+  mutate(
+    label = plyr::mapvalues(label, 
+                            from = c("iGDP With energy",  "fittedExp With energy",
+                                     "fitted With energy", "fitted Without energy"), 
+                            to = c("GDP",  "Ref. model",
+                                   "w/ energy", "w/o energy")),
+    label = relevelFactor(factor(label), 
+                          c("GDP", "Ref. model", "w/o energy", "w/ energy"))
+  ) %>%
+
+  ggplot() +
+  geom_line( mapping=aes(x=Year, y=value, group=label, linetype=label, size=label)) +
+  scale_linetype_manual(values=c(1,2,4,3), name="") +
+  scale_size_manual(name = "", values=c(1, 0.5, 0.5, 0.5)) +
+  facet_grid(flavor ~ Country) +
+  scale_x_continuous(breaks=c(1960, 1980, 2000)) +
+  scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12)) +
+  xlab("") +
+  ylab("Indexed GDP (1960=1)") +
+  xy_theme()
+
+@
+
 <<SRsse_CES_graph_3, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Solow Residuals~($\\lambda$) and mean squared error~($sse$).

### 2015-10-21 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Cleaning up fitted_and_resid_data

--- 2015-10-20 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
@@
     f = function(model, id){
-      ### Why wrap in data.frame() something that already is a tbl_df?  If this is necessary, say why.
-      #  df <- data.frame(select(model$data, Year, Country))
-      ### Also: let's use a consistent style for the dplyr commands, prefering to use %>% in most cases.
-      ### Also: The following use of white space makes it clearer what is going on (and how many steps 
-      ###       are involved.  I'm going to change A LOT of code to this format.
-      ### In this format, there is no name to create a temporary variable (or to use return())
-
       model$dat %>% 
@@
           fittedExp = exp(fitted(model)), # exp accounts for the fact that the model was fitted in log space.
-          ResidualsExp = resid(model)     ### Why is this capitalized?
+          residualsExp = resid(model)     
         )
@@
 
-temp_data_CSP <- 
-  leaf_apply(modelsCSP, class=c("plm", "lm"), model2df) %>% 
-  bind_rows() %>%
-  mutate(CSP = "w/ CSP")
-
 ### This looks like a candidate for clean up a la model2df
@@
 function_that_was_here_before <- function(model, id){
-  df <- data.frame(select(model$data, Year)) 
+  id_list <- strsplit(id, split = "[.]")[[1]]
+  out <- model$data %>% 
+    select(Year) %>%
+    mutate(
       # By including [c(1:length(df$Year))] on the end, we 
@@
       # if data do not exist.
-  df$fitted <- yhat(model)[c(1:length(df$Year))]
-  df$Residuals <- resid(model)[c(1:length(df$Year))]
+      fitted = yhat(model)[c(1:length(Year))],
+      Residuals = resid(model)[c(1:length(Year))],
+      Country = id_list[[1]],
+      flavor = if (id_list[[2]] ==  "unadjusted") "Unadjusted" else "Quality-adjusted",
+      energy = if (id_list[[3]] == "noE") "Without energy" else "With energy",
+      model = id_list[[4]],
+      nest = if (length(id_list) > 4) id_list[[5]] else NA
+    )
   # Now add the response, using the original variable name.
-  df[[summands(model$formula, right = FALSE)]] <- response(model)[c(1:length(df$Year))]
-  # Now add meta information
-  id_list <- strsplit(id, split = "[.]")[[1]]
-  len <- length(id_list)
-  df$Country <- id_list[[1]]
-  df$flavor <- if (id_list[[2]] ==  "unadjusted") "Unadjusted" else "Quality-adjusted"
-  df$energy <- if (id_list[[3]] == "noE") "Without energy" else "With energy"
-  df$model <- id_list[[4]]
-  df$nest <- if (length(id_list) > 4) id_list[[5]] else NA
-  return(df)  
+  out[[summands(model$formula, right = FALSE)]] <- response(model)[c(1:length(out$Year))]
+  return(out)  
 }
+
+temp_data_CSP <- 
+  leaf_apply(modelsCSP, class=c("plm", "lm"), function_that_was_here_before) %>% 
+  bind_rows() %>%
+  mutate(CSP = "w/ CSP")
 
@@
 # it applies to all situations.
-fitted_and_resid_data <- 
-  merge(temp_data_noExp, temp_data_exp) %>% 
-  mutate( Dr = abs(Residuals) - abs(ResidualsExp) )  
-### Caps in bad places?
-
-# Create a column containing ∆r, the difference between a residual value
-# and the residual value in the same year for the reference model
-### BREAK LONG LINES IN REASONABLE PLACES
-### BUT better to use mutate here.  See above.
-# fitted_and_resid_data[["Dr"]] <- 
-#   abs(fitted_and_resid_data[["Residuals"]]) - abs(fitted_and_resid_data[["ResidualsExp"]])
+fitted_and_resid_data <- merge(temp_data_noExp, temp_data_exp)
 
 # Relevel factors before plotting
-### Use mutate for this stuff!
-### Align = to make similarities between successive lines stand out.
-
 fitted_and_resid_data <-

### 2015-10-21 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
rewrite formula -- noop in terms of meaning

--- 2015-10-20 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
@@
       formula <- substitute(
-        log(Y) - alpha_1 * log(K) - alpha_2 * log(L) ~ T,
+        log(Y) - (alpha_1 * log(K) + alpha_2 * log(L)) ~ T,
         list( Y = yVar, K = kVar, L = lVar, T = tVar, A = alphaCSP, B = betaCSP)

### 2015-10-21 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
New CSP models and code.

--- 2015-10-21 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
@@
 fileNameCSP <- "EcolEcon2015ModelsCSP.rds"
-if (FALSE && !rerunModels){
+if (!rerunModels){
   # load from the file on disk
@@
     for (adj in c("unadjusted", "adjusted")){
-      print(adj)
       # Replace with better code later. 
@@
           Country = as.character(Country),  # to avoid warning about unmatched levels of factors
-          fittedExp = exp(fitted(model)), # exp accounts for the fact that the model was fitted in log space.
-          residualsExp = resid(model)     
+          fitted = exp(fitted(model)), # exp accounts for the fact that the model was fitted in log space.
+          residuals = resid(model)     
         )
@@
       fitted = yhat(model)[c(1:length(Year))],
-      Residuals = resid(model)[c(1:length(Year))],
+      residuals = resid(model)[c(1:length(Year))],
       Country = id_list[[1]],
-      flavor = if (id_list[[2]] ==  "unadjusted") "Unadjusted" else "Quality-adjusted",
-      energy = if (id_list[[3]] == "noE") "Without energy" else "With energy",
+      flavor = ifelse (id_list[[2]] ==  "unadjusted", "Unadjusted", "Quality-adjusted"),
+      energy = ifelse(id_list[[3]] == "noE", "Without energy", "With energy"),
       model = id_list[[4]],
-      nest = if (length(id_list) > 4) id_list[[5]] else NA
+      nest = ifelse (length(id_list) > 4, id_list[[5]], NA)
     )

### 2015-10-21 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
New CSP models and code.

@@
 
-<<Cost_Share_Plot, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=1.5, fig.cap="Historical cost shares for capital, labor, and energy.">>=
-ggplot(
-  data = gather(CostShares, key=cost_share, value=value, cs_k, cs_l, cs_e)
-  ) + 
+<<Cost_Share_Plot, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=1.5, fig.cap="Historical cost shares for capital and labor.">>=
+ggplot(data = gather(CostShares, key=cost_share, value=value, cs_k, cs_l)) + 
   geom_line(mapping = aes(
@@
     linetype = cost_share,
-    color = cost_share)) +
+    color = cost_share,
+    size = cost_share)) +
   facet_grid( ~ Country) +
@@
   scale_color_manual(name = "", 
-                     labels=c("k", "l", "e"),
-                     values=c("black", "black", "gray70")) +
+                     labels=c("k", "l"),
+                     values=c("black", "black")) +
   scale_linetype_manual(name="", 
-                        labels=c("k", "l", "e"),
-                        values=c(2,3,1)) + 
+                        labels=c("k", "l"),
+                        values=c(2,3)) + 
   scale_size_manual(name="", 
-                    labels=c("k", "l", "e"),
-                    values = c(0.9, 0.9, 0.6)) +
+                    labels=c("k", "l"),
+                    values = c(0.9, 0.9)) +
   xy_theme()

### 2015-10-21 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
fix delta in hand-crafted model

--- 2015-10-21 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
@@
         c(cesModCSP$coefficients, 
-          c(delta_1 = cesModCSP$coefficients["alpha_1"],
-            delta = 0,
+          c(delta_1 = as.vector(cesModCSP$coefficients["alpha_1"]),
+            delta = 1,
             rho_1 = 0,

### 2015-10-21 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Updates for AllOE.

--- 2015-10-21 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
@@
       # CES models where rho_1 = 0 are the Cobb-Douglas model.
-      # Convienently, we previously fit that model.
+      # Convienently, we previously fit that model 
+      # with the required output elasticities.
       cesModCSP <- cdModCSP
@@
 AllOE <- 
-  leaf_apply(
-    models, 
-    class = "cesModel", 
-    mod2oedf
-  ) %>% 
+  leaf_apply(models, class = "cesModel", mod2oedf) %>% 
   bind_rows() %>%
@@
 # Now append to AllOE time-varying output elasticities from models that adhere to the CSP.
-# These output elasticities are stored with variable names oe1, oe2, and oe3 in the data object in the models.
-# See the <<Models_CSP>> chunk above.
-# Uncomment when we're ready to add the CSP models to the alpha vs. time graph.
 
-# AllOE <- leaf_apply(modelsCSP, class="lm", f=function(mod, id){
-#   id_components <- strsplit(id, split = "[.]")[[1]]
-#   if (id_components[4] == "CES") {
-#     return(mod$data)
-#   } else {
-#     return(NULL)
-#   }
-# }) %>% 
-#   do.call(plyr::rbind.fill, .) %>%
-#   bind_rows(AllOE, .)
+AllOE <- leaf_apply(modelsCSP, class="cesModel", f=mod2oedf) %>% 
+  bind_rows() %>%
+  mutate (CSP = "w/ CSP") %>%
+  bind_rows(AllOE, .)
 

### 2015-10-22 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Deleting CSP and Exp models from disk

@@
 <<Models_CSP>>=
-fileNameCSP <- "EcolEcon2015ModelsCSP.rds"
-if (!rerunModels){
-  # load from the file on disk
-  modelsCSP <- readRDS(fileNameCSP)
-} else {
 #
-  # Models that adhere to the cost-share theorem
+# Models that adhere to the cost-share principle
 # 
-
 modelsCSP <- list()
@@
 }
-  # Save cost-share theorem models to disk.
-  saveRDS(modelsCSP, file=fileNameCSP)
-}
 
@@
 <<Models_Exp>>=
-fileNameExp <- "EcolEcon2015ModelsExp.rds"
-if (!rerunModels){
-  # load from the file on disk
-  modelsExp <- readRDS(fileNameExp)
-} else {
 #
@@
   modelsExp[[country]] <- expMod
-  }
-  # Save exponential models to disk.
-  saveRDS(modelsExp, file=fileNameExp)
 }

### 2015-10-22 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
New version of alphas graph.

@@
 
-<<Cost_Share_Plot, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=1.5, fig.cap="Historical cost shares for capital and labor.">>=
+<<Cost_Share_Plot, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=1.5, fig.cap="Historical cost shares for capital and labor.", eval=FALSE>>=
 ggplot(data = gather(CostShares, key=cost_share, value=value, cs_k, cs_l)) + 
@@
 AllOE %>% 
-  mutate(split =
-           as.character(
-             interaction(
-               factor(flavor, labels = c("QA", "UA")), 
-               factor(nest, 
-                      labels = c("(ek)l", "kl", "(kl)e", "(le)k")), 
-               sep = ", ",
-               lex.order = FALSE ) )
-  ) %>%
-  gather(factor, elasticity, oe1, oe2, oe3) %>%
   mutate(
-    split2 = relevelFactor(
-      factor(split), 
-      paste( rep(c("UA", "QA"), times = 4 ), 
-             rep(c("kl", "(kl)e", "(le)k", "(ek)l"), each=2),
-             sep=", ")
+    xfacet = as.character(
+                interaction(Country, factor(flavor, labels = c("QA", "UA")), sep = " - ")
+    ),
+    yfacet = as.character(
+                interaction(factor(nest, labels = c("(ek)l", "kl", "(kl)e", "(le)k")), CSP, sep = " - ")
     )
   ) %>% 
-  ggplot(aes(x=Year)) + 
-  geom_line( 
-    alpha = .8, # size=1.0,
-    aes(y = elasticity, 
-        colour = factor,
-        linetype=factor,
-        size = factor
-    ) ) +
-  facet_grid(split2 ~ Country) +
+  gather(key = oe_type, value = oe_value, oe1, oe2, oe3) %>%
+
+  ggplot(aes(x = Year)) +
+  geom_line(alpha = 0.8, aes(y = oe_value, 
+            color = oe_type,
+            linetype = oe_type,
+            size = oe_type)) + 
+  facet_grid(yfacet ~ xfacet) + 
   scale_color_manual(
@@
   xy_theme()
+
+# AllOE %>% 
+#   mutate(split =
+#            as.character(
+#              interaction(
+#                factor(flavor, labels = c("QA", "UA")), 
+#                factor(nest, 
+#                       labels = c("(ek)l", "kl", "(kl)e", "(le)k")), 
+#                sep = ", ",
+#                lex.order = FALSE ) )
+#   ) %>%
+#   gather(factor, elasticity, oe1, oe2, oe3) %>%
+#   mutate(
+#     split2 = relevelFactor(
+#       factor(split), 
+#       paste( rep(c("UA", "QA"), times = 4 ), 
+#              rep(c("kl", "(kl)e", "(le)k", "(ek)l"), each=2),
+#              sep=", ")
+#     )
+#   ) %>%
+#
+#   ggplot(aes(x=Year)) + 
+#   geom_line( 
+#     alpha = .8, # size=1.0,
+#     aes(y = elasticity, 
+#         colour = factor,
+#         linetype=factor,
+#         size = factor
+#     ) ) +
+#   facet_grid(split2 ~ Country) +
+#   scale_color_manual(
+#     name = "",
+#     labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
+#     values=c("black", "black", "gray70")
+#   ) +
+#   scale_x_continuous(breaks = c(1960, 1980, 2000)) +
+#   scale_y_continuous(breaks = c(0.0, 0.5, 1.0), limits=c(-0.2, 1.2)) +
+#   scale_size_manual(
+#     name = "",
+#     labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
+#     values = c(.9, .9, .6)) +
+#   scale_linetype_manual( 
+#     name = "",
+#     labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
+#     values=c(2,3,1) ) + 
+#   labs(x="", y="") +
+#   xy_theme()
+
 @

### 2015-10-22 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Better alpha graph.

@@
   mutate(
-    xfacet = as.character(
-                interaction(Country, factor(flavor, labels = c("QA", "UA")), sep = " - ")
-    ),
-    yfacet = as.character(
-                interaction(factor(nest, labels = c("(ek)l", "kl", "(kl)e", "(le)k")), CSP, sep = " - ")
-    )
+    xfacet = as.character(interaction(Country, factor(flavor, labels = c("QA", "UA")), sep = " - ")),
+    xfacet = relevelFactor(factor(xfacet), c("PT - UA", "PT - QA", "UK - UA", "UK - QA")),
+    yfacet = as.character(interaction(factor(nest, labels = c("(ek)l", "kl", "(kl)e", "(le)k")), CSP, sep = " - ")),
+    yfacet = relevelFactor(factor(yfacet), c("kl - w/ CSP", "kl - w/o CSP", "(kl)e - w/o CSP", "(le)k - w/o CSP", "(ek)l - w/o CSP"))
   ) %>% 

### 2015-10-22 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Deleted old oe graph code.

@@
 
-# AllOE %>% 
-#   mutate(split =
-#            as.character(
-#              interaction(
-#                factor(flavor, labels = c("QA", "UA")), 
-#                factor(nest, 
-#                       labels = c("(ek)l", "kl", "(kl)e", "(le)k")), 
-#                sep = ", ",
-#                lex.order = FALSE ) )
-#   ) %>%
-#   gather(factor, elasticity, oe1, oe2, oe3) %>%
-#   mutate(
-#     split2 = relevelFactor(
-#       factor(split), 
-#       paste( rep(c("UA", "QA"), times = 4 ), 
-#              rep(c("kl", "(kl)e", "(le)k", "(ek)l"), each=2),
-#              sep=", ")
-#     )
-#   ) %>%
-#
-#   ggplot(aes(x=Year)) + 
-#   geom_line( 
-#     alpha = .8, # size=1.0,
-#     aes(y = elasticity, 
-#         colour = factor,
-#         linetype=factor,
-#         size = factor
-#     ) ) +
-#   facet_grid(split2 ~ Country) +
-#   scale_color_manual(
-#     name = "",
-#     labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
-#     values=c("black", "black", "gray70")
-#   ) +
-#   scale_x_continuous(breaks = c(1960, 1980, 2000)) +
-#   scale_y_continuous(breaks = c(0.0, 0.5, 1.0), limits=c(-0.2, 1.2)) +
-#   scale_size_manual(
-#     name = "",
-#     labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
-#     values = c(.9, .9, .6)) +
-#   scale_linetype_manual( 
-#     name = "",
-#     labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
-#     values=c(2,3,1) ) + 
-#   labs(x="", y="") +
-#   xy_theme()
-
 @

### 2015-10-22 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Deleted some unused code.

@@
   for (adj in c("unadjusted", "adjusted")){
-    # Replace with better code later. 
-    # Would like to say cdModel(formula, data, factorShares=c(alpha_1 = 0.3, alpha_2 = 0.7, alpha_3 = 0))
-    # or something like that.
+
+    # Cobb-Douglas
+
+    # Pull variables out of the formulas for use in fitting the model.
     form <- keep_summands(formulas[[country]][[adj]], n=-3) # Remove energy
@@
     modelsCSP[[country]][[adj]][["noE"]][["CD"]] <- cdModCSP
+
     # CES
+
     # The only CES models that can adhere to the CSP are models where
@@
     class(cesModCSP) <- setdiff(c("cesModel", class(cesModCSP)), "CDEmodel")
-    # # Again, we need a customized "naturalCoeffs" attribute so that 
-    # # the "naturalCoef" function will do the right thing.
-    # # "naturalCoeffs" can be based on the same "naturalCoeffs"
-    # # from the Cobb-Douglas model, but a few additions are needed.
-    # attr(cesModCSP, "naturalCoeffs") <- 
-    #   naturalCoef(cdModCSP) %>%
-    #   mutate(
-    #     delta_1 = naturalCoef(cdModCSP)[["alpha_1"]],
-    #     delta = 1,
-    #     rho_1 = 0, 
-    #     rho = NA,
-    #     sigma_1 = 1,
-    #     sigma_12 = 1,
-    #     sigma = NA,
-    #     sigma_12_3 = NA
-    #   )
-    # # Add output elasticities (as a function of time) to this model.
-    # # This would have been done by a "fortify" function, 
-    # # but this is not a typical CES model, so we can't "fortify" it.
-    # # Add other metadata, too.
-    # cesModCSP$data <- cesModCSP$data %>%
-    #   mutate(
-    #     oe1 = alphaCSP,
-    #     oe2 = betaCSP,
-    #     oe3 = 0,
-    #     Country = country, 
-    #     flavor  = ifelse(adj=="unadjusted", "Unadjusted", "Quality-adjusted"),
-    #     energy  = "Without energy",
-    #     model   = "CES", 
-    #     nest    = "kl",
-    #     CSP     = "w/ CSP"
-    #   )
     modelsCSP[[country]][[adj]][["noE"]][["CES"]][["kl"]] <- cesModCSP

### 2015-10-22 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Cleaned up cruft in CSP models.

@@
       log(Y) - (alpha_1 * log(K) + alpha_2 * log(L)) ~ T,
-      list( Y = yVar, K = kVar, L = lVar, T = tVar, A = alphaCSP, B = betaCSP)
+      list( Y = yVar, K = kVar, L = lVar, T = tVar)
     )
@@
       eval(substitute( 
-        plm(formula, data = data, params = c(alpha_1 = 0.3, alpha_2 = 0.7, alpha_3 = 0.0), 
+        plm(formula, data = data, params = c(alpha_1 = alphaCSP, alpha_2 = betaCSP, alpha_3 = 0.0), 
             optimize = FALSE),

### 2015-10-22 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Added gammaCSP.

@@
 betaCSP <- 0.7 # Fraction of national accounts spent on labor
+gammaCSP <- 0.0
 for (country in countries){
@@
       eval(substitute( 
-        plm(formula, data = data, params = c(alpha_1 = alphaCSP, alpha_2 = betaCSP, alpha_3 = 0.0), 
+        plm(formula, data = data, params = c(alpha_1 = alphaCSP, alpha_2 = betaCSP, alpha_3 = gammaCSP), 
             optimize = FALSE),

### 2015-10-22 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Now making better graphs.

@@
 
-print("top of Fitted_and_Residuals")
-
 temp_data_exp <- 
@@
     f = function(model, id){
-      model$dat %>% 
+      out <- model$dat %>% 
         select(Year, Country) %>%
@@
           fitted = exp(fitted(model)), # exp accounts for the fact that the model was fitted in log space.
-          residuals = resid(model)     
+          residuals = resid(model), 
+          model = "exp"
         )
+        # Now add the response, using the original variable name.
+      out[[summands(model$formula, right = FALSE)]] <- exp(response(model)[c(1:length(out$Year))])
+      return(out)
     }
@@
   bind_rows()
-
-### If the function is this long, it should be separated out and named rather than embedded in another
-### function call.  
-### But this looks like model2df from above.  Let's use that instead.
-
-### Probably just junk now.
-# function_that_was_here_before <- function(model, id){
-#   df <- data.frame(select(model$data, Year, Country, iGDP))
-#   df$fitted <- exp(fitted(model)) # fitted is in log space. Return to regular space.
-#   df$Residuals <- resid(model) # residuals are in log space, and that is what we want.
-#   # Now add meta information
-#   id_list <- strsplit(id, split = "[.]")[[1]]
-#   df$flavor <- if (id_list[[2]] ==  "unadjusted") "Unadjusted" else "Quality-adjusted"
-#   df$energy <- if (id_list[[3]] == "noE") "Without energy" else "With energy"
-#   df$model <- id_list[[4]]
-#   df$nest <- if (length(id_list) > 4) id_list[[5]] else NA
-#   return(df)
-# }
-
-### This looks like a candidate for clean up a la model2df
 
@@
 
-temp_data_noExp <- 
-  bind_rows( temp_data_CSP, temp_data_noCSP )
+FittedAndResid <- plyr::rbind.fill(temp_data_exp, temp_data_CSP, temp_data_noCSP)
 
-# Now merge the exponential-only model with the CSP and noCSP models. 
-# Doing this, because the exponential-only model is kind-of like iY:
-# it applies to all situations.
-fitted_and_resid_data <- merge(temp_data_noExp, temp_data_exp)
-
-# Relevel factors before plotting
-fitted_and_resid_data <-
-  fitted_and_resid_data %>% 
-  mutate(
-    Country = relevelFactor(factor(Country), c("PT", "UK")),
-    flavor  = relevelFactor(factor(flavor), c("Unadjusted", "Quality-adjusted")),
-    energy  = relevelFactor(factor(energy), c("Without energy", "With energy")),
-    nest    = relevelFactor(factor(nest), c("kl", "kle", "lek", "ekl"))
-  ) %>%
-  arrange(Country, CSP, model, flavor, energy, nest)
 @
@@
 
-<<Fitted_and_Residual_Graph_Functions>>=
-
-### Can fittedGraphNoCSP and fittedGraphCSP be combined into one function with an argument?
-### Or can the data filtering happen outside and everything else be the same?
-### Did you copy and paste to make one from the other?  That should be a sign...
-fittedGraphNoCSP <- function(data){
-  fittedGraphData <- 
-    data %>% 
-    select(Year, Country, iGDP, fitted, fittedExp, flavor, energy, CSP, nest) %>%
-    melt(measure.vars = c("iGDP", "fitted", "fittedExp"), 
-         value.name = "value", variable.name = "variable") %>%
-    mutate(label = paste(variable, energy)) %>%
-    # Now collapse some of the information. Don't need multiple versions of the exponential model, e.g.
-    filter(label %in% c("iGDP With energy", "fittedExp With energy", 
-                        "fitted With energy", "fitted Without energy")
-    ) %>% 
-    mutate(
-      label = plyr::mapvalues(label, 
-                              from = c("iGDP With energy",  "fittedExp With energy",
-                                       "fitted With energy", "fitted Without energy"), 
-                              to = c("GDP",  "Ref. model",
-                                     "w/ energy", "w/o energy")),
-      label = relevelFactor(factor(label), 
-                            c("GDP", "Ref. model", "w/o energy", "w/ energy"))
-    )
-
-  ggplot() +
-    geom_line(data=fittedGraphData, mapping=aes(x=Year, y=value, group=label, linetype=label, size=label)) +
-    scale_linetype_manual(values=c(1,2,4,3), name="") +
-    scale_size_manual(name = "", values=c(1, 0.5, 0.5, 0.5)) +
-    facet_grid(flavor ~ Country) +
-    scale_x_continuous(breaks=c(1960, 1980, 2000)) +
-    scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12)) +
-    xlab("") +
-    ylab("Indexed GDP (1960=1)") +
-    xy_theme()
-}
-@
-
-<<ResidualPlotFunction>>=
-
-cesResidualPlot2 <- function(data){
-  dataToPlot <- 
-    data %>%
-    mutate(nest = 
-             plyr::mapvalues(
-               nest, 
-               from=c("kl", "kle", "lek", "ekl"), 
-               to=c("kl", "(kl)e", "(le)k", "(ek)l")
-               ),
-           Model = interaction(nest, CSP, sep = " ", drop=TRUE),
-           Inputs = flavor)
-
-  ggplot() +
-    geom_point(
-      data=dataToPlot, 
-      mapping=aes(
-        x=Year, 
-        y=Residuals, 
-        fill=Model, 
-        shape=Model, 
-        size=Model
-        )
-      ) +
-    facet_grid(flavor ~ Country) +
-    geom_hline(yintercept = 0, colour="gray50", size=0.1) +
-    scale_x_continuous(breaks=c(1960, 1980, 2000)) +
-    xlab("") +
-    ylab("r") + 
-    xy_theme() +
-    labs(color = "Factors of production") +
-    # This is custom stuff here to match the model_points_style function. 
-    # We can't use model_points_style, because the aesthetics are different here
-    # with only two series (kl w/o CSP and (kl)e w/o CSP) in the graph.
-    scale_size_manual(values = c(3, 3)) +
-    scale_fill_manual(values = c("transparent", "transparent")) +
-    scale_shape_manual(values = c(21, 23)) +
-  theme(legend.title=element_blank())
-}
-@
-
 \section{End EcolEcon2015A}

### 2015-10-22 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Now making better graphs.

@@
 
-<<Graphs_CESkle-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with $kl$ and $(kl)e$ nesting that reject the CSP. Solid line is historical GDP.">>=
-fittedGraphData_kle <- 
-  fitted_and_resid_data %>% 
-  filter(model=="CES" & CSP=="w/o CSP" & (nest == "kl" | nest == "kle"))
+<<faceting_functions>>=
 
-fittedGraphNoCSP(fittedGraphData_kle)
+# Replicates exponential models for each flavor in the flavors vector
+replicateExpModels <- function(data, flavors){
+  lapply(flavors, function(flav){
+    data %>% 
+      filter(model=="exp") %>%
+      mutate(
+        flavor = flav,
+        nest = "exp",
+        CSP = "exp"
+      )
+  }) %>%
+    bind_rows() %>%
+
+    # Combine the replicated exponential models with everything else in data
+    rbind(., filter(data, model != "exp"))
+}
+
+# Add facet columns to data for both fitted and residuals graphs.
+addFacetCols <- function(data){
+  # Create the facet variables
+  mutate(data,
+    nest = plyr::mapvalues(nest, from=c("kle", "lek", "ekl"), to=c("(kl)e", "(le)k", "(ek)l")),
+    flavor = plyr::mapvalues(flavor, from=c("Unadjusted", "Quality-adjusted"), to=c("UA", "QA")),
+
+    xfacet = interaction(Country, flavor, sep = " - "),
+    xfacet = relevelFactor(factor(xfacet), c("PT - UA", "PT - QA", "UK - UA", "UK - QA")),
+
+    yfacet = interaction(model, nest, CSP, sep = " - "),
+    yfacet = plyr::mapvalues(yfacet, 
+                             from=c("exp - exp - exp", 
+                                    "CES - kl - w/ CSP",
+                                    "CES - kl - w/o CSP",
+                                    "CES - (kl)e - w/o CSP",
+                                    "CES - (le)k - w/o CSP",
+                                    "CES - (ek)l - w/o CSP"), 
+                             to  =c("Ref.",
+                                    "kl - w/ CSP",
+                                    "kl - w/o CSP",
+                                    "(kl)e - w/o CSP",
+                                    "(le)k - w/o CSP",
+                                    "(ek)l - w/o CSP")
+    ),
+    yfacet = relevelFactor(factor(yfacet), c("Ref.", 
+                                             "kl - w/ CSP", 
+                                             "kl - w/o CSP", 
+                                             "(kl)e - w/o CSP", 
+                                             "(le)k - w/o CSP", 
+                                             "(ek)l - w/o CSP"))
+  )
+}
+
 @
 
-<<Fitted_Graph, eval=FALSE>>=
-fitted_and_resid_data %>% 
-  filter(model=="CES") %>%
-  gather()
-  melt(measure.vars = c("iGDP", "fitted", "fittedExp"), 
-       value.name = "value", variable.name = "variable") %>%
-  mutate(label = paste(variable, energy)) %>%
-  # Now collapse some of the information. Don't need multiple versions of the exponential model, e.g.
-  filter(label %in% c("iGDP With energy", "fittedExp With energy", 
-                      "fitted With energy", "fitted Without energy")
-  ) %>% 
-  mutate(
-    label = plyr::mapvalues(label, 
-                            from = c("iGDP With energy",  "fittedExp With energy",
-                                     "fitted With energy", "fitted Without energy"), 
-                            to = c("GDP",  "Ref. model",
-                                   "w/ energy", "w/o energy")),
-    label = relevelFactor(factor(label), 
-                          c("GDP", "Ref. model", "w/o energy", "w/ energy"))
+<<Fitted_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=7, fig.cap="Fitted compared to historical GDP time series.">>=
+
+# Duplicate the exponential models for both Unadjusted and Quality-adjusted cases.
+replicateExpModels(
+  data = filter(FittedAndResid, model=="exp" | model=="CES"), 
+  flavors = c("Unadjusted", "Quality-adjusted")
   ) %>%
 
+  addFacetCols() %>%
+
+  gather(key = y_type, value = y_value, iGDP, fitted) %>%
+
   ggplot() +
-  geom_line( mapping=aes(x=Year, y=value, group=label, linetype=label, size=label)) +
-  scale_linetype_manual(values=c(1,2,4,3), name="") +
-  scale_size_manual(name = "", values=c(1, 0.5, 0.5, 0.5)) +
-  facet_grid(flavor ~ Country) +
-  scale_x_continuous(breaks=c(1960, 1980, 2000)) +
-  scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12)) +
-  xlab("") +
-  ylab("Indexed GDP (1960=1)") +
+  geom_line(alpha = 0.8, aes(x = Year, 
+                             y = y_value,
+                             group = y_type,
+                             color = y_type,
+                             linetype = y_type,
+                             size = y_type)
+  ) + 
+  facet_grid(yfacet ~ xfacet) + 
+  scale_x_continuous(breaks = c(1960, 1980, 2000)) +
+  scale_color_manual(
+    name = "",
+    labels = c("historical", "fitted"),
+    values=c("gray70", "black")
+  ) +
+  scale_size_manual(
+    name = "",
+    labels = c("historical", "fitted"),
+    values = c(1.5, 0.3)) +
+  scale_linetype_manual( 
+    name = "",
+    labels = c("historical", "fitted"),
+    values=c(1,1) ) + 
+  labs(x="", y="GDP") +
   xy_theme()
@@
              from=c("kl", "kle",   "lek",   "ekl"), 
-             to=c("kl", "(kl)e", "(le)k", "(ek)l")
+             to  =c("kl", "(kl)e", "(le)k", "(ek)l")
              ),
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Fitted Graphs}
-\label{sec:appendix_fitted}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-<<Graphs_CESlek-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with $kl$ and $(le)k$ nesting that reject the CSP. Solid line is historical GDP.">>=
-fittedGraphData_lek <- 
-  fitted_and_resid_data %>% 
-  filter(model=="CES" & CSP=="w/o CSP" & (nest == "kl" | nest == "lek"))
-
-fittedGraphNoCSP(fittedGraphData_lek)
-@
-
-<<Graphs_CESekl-fitted, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with $kl$ and $(ek)l$ nesting that reject the CSP. Solid line is historical GDP.">>=
-fittedGraphData_ekl <- 
-  fitted_and_resid_data %>% 
-  filter(model=="CES" & CSP=="w/o CSP" & (nest == "kl" | nest == "ekl"))
-
-fittedGraphNoCSP(fittedGraphData_ekl)
-@
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Residual Graphs}
@@
 
-<<Graphs_CESkle-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(kl$)$e$ nesting.">>=
-cesResidualPlot2(
-  fitted_and_resid_data %>% 
-    filter(model=="CES" & CSP=="w/o CSP" & (nest=="kle" | nest=="kl"))
-)
-@
+<<Residuals_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=7, fig.cap="Model residuals.">>=
 
-<<Graphs_CESlek-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with ($le$)$k$ nesting.">>=
-cesResidualPlot2(
-  fitted_and_resid_data %>% 
-    filter(model=="CES" & CSP=="w/o CSP" & (nest == "lek" | nest=="kl"))
-)
-@
+# Duplicate the exponential models for both Unadjusted and Quality-adjusted cases.
+replicateExpModels(
+  data = filter(FittedAndResid, model=="exp" | model=="CES"), 
+  flavors = c("Unadjusted", "Quality-adjusted")
+  ) %>%
 
-<<Graphs_CESekl-resid, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Fitting residuals for CES models with $(ek$)$l$ nesting.">>=
-cesResidualPlot2(
-  fitted_and_resid_data %>% 
-    filter(model=="CES" & CSP=="w/o CSP" & (nest=="ekl" | nest=="kl"))
-)
+  addFacetCols() %>%
+
+  ggplot() +
+  geom_point(alpha = 0.8, size = 0.5, aes(x = Year, y = residuals)) + 
+  facet_grid(yfacet ~ xfacet, scales = "free_y" ) + 
+  scale_x_continuous(breaks = c(1960, 1980, 2000)) +
+  labs(x="", y="Residuals") +
+  geom_hline(aes(yintercept = 0.0), colour="gray50", size=0.1) + 
+  xy_theme()
+
 @

### 2015-10-22 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Now refitting everything always, except CES.

@@
 # ********************************************************
-rerunModels=FALSE
+rerunCESModels=FALSE
 rerunResampling=FALSE
@@
 )
-
-# This function is used in many places below.
-### That's nice.  I assume that's why you wrote a function.  But what does it DO?
 @
@@
 <<Data>>=
-# Create the historicalData data frames
-### If we need to select variables, we can do that.  Unfortunately, select() and select_() don't do
-### what we would like here (they don't accept a vector of character strings), so we'd have to use
-### something else.  I've kept the fake select_() command here just to record what was done earlier.
-
+# Create the HistoricalData data frames
 commonVars <- c("Year", "Country", "Source")
-historicalData <- list(
+HistoricalData <- list(
   PT =  IST %>% 
     filter(Country == "PT"), 
-    #  %>% select_(unique(c(commonVars, all.vars(formulas$PT$unadjusted), all.vars(formulas$PT$adjusted)))),
   UK = Leeds %>% 
     filter(Country == "UK") 
-    # %>% select_(unique(c(commonVars, all.vars(formulas$UK$unadjusted), all.vars(formulas$UK$adjusted))))
 )
@@
 CostShares <- read.table(file.path("cost_shares", "Cost_Shares_PT_UK.txt"), header=TRUE)
+@
+
+<<Models_Exp>>=
+#
+# Models that are exponential only, y = A * exp(lambda*t)
+#
+modelsExp <- list()
+alphaExp <- 0
+betaExp <- 0
+gammaExp <- 0
+for (country in countries){
+  # Replace with better code later. 
+  # Would like to say cdModel(formula, data, factorShares=c(alpha_1 = 0, alpha_2 = 0, alpha_3 = 0))
+  # or something like that.
+  form <- keep_summands(formulas[[country]][["unadjusted"]], n = c(-1, -2, -3)) # Keep none of the factors of production
+  yVar <- as.name(summands(form, n=1, right=FALSE))
+  tVar <- as.name(summands(form, n=1))
+  data <- HistoricalData[[country]]
+  expMod <- lm(log(eval(yVar)) ~ eval(tVar), data=data)
+  attr(expMod, "naturalCoeffs") <- data.frame(lambda=coef(expMod)[[2]],
+                                              logscale=coef(expMod)[[1]], 
+                                              scale=exp(coef(expMod)[[1]]),
+                                              alpha_1=alphaExp,
+                                              alpha_2=betaExp, 
+                                              alpha_3=gammaExp)
+  expMod$formula <- form
+  sdata <- subset(data, select=all.vars(form))
+  sdata <- data[complete.cases(sdata), unique(c(all.vars(form), names(data)))]
+  expMod$data <- sdata
+  expMod$response <- sdata$iGDP 
+  modelsExp[[country]] <- expMod
+}
+
 @
@@
     tVar <- as.name(summands(form, n=3))
-    data <- historicalData[[country]]
+    data <- HistoricalData[[country]]
     formula <- substitute(
@@
 
-<<Models_Exp>>=
-#
-# Models that are exponential only, y = A * exp(lambda*t)
-#
-modelsExp <- list()
-alphaExp <- 0
-betaExp <- 0
-gammaExp <- 0
-for (country in countries){
-  # Replace with better code later. 
-  # Would like to say cdModel(formula, data, factorShares=c(alpha_1 = 0, alpha_2 = 0, alpha_3 = 0))
-  # or something like that.
-  form <- keep_summands(formulas[[country]][["unadjusted"]], n = c(-1, -2, -3)) # Keep none of the factors of production
-  yVar <- as.name(summands(form, n=1, right=FALSE))
-  tVar <- as.name(summands(form, n=1))
-  data <- historicalData[[country]]
-  expMod <- lm(log(eval(yVar)) ~ eval(tVar), data=data)
-  attr(expMod, "naturalCoeffs") <- data.frame(lambda=coef(expMod)[[2]],
-                                              logscale=coef(expMod)[[1]], 
-                                              scale=exp(coef(expMod)[[1]]),
-                                              alpha_1=alphaExp,
-                                              alpha_2=betaExp, 
-                                              alpha_3=gammaExp)
-  expMod$formula <- form
-  sdata <- subset(data, select=all.vars(form))
-  sdata <- data[complete.cases(sdata), unique(c(all.vars(form), names(data)))]
-  expMod$data <- sdata
-  expMod$response <- sdata$iGDP 
-  modelsExp[[country]] <- expMod
-}
+<<Models_CDC>>=
+models <- list()
 
-@
-
-<<Models_CDCES>>=
-fileNameCDCES <- "EcolEcon2015ModelsCDCES.rds"
-if (!rerunModels){
-  # load from the file on disk
-  models <- readRDS(fileNameCDCES)
-} else {
-  #
-  # Models where all parameters are estimated (models don't adhere to the cost share theorem)
-  #
-  models <- list()
 for(country in countries){
@@
     fwithE <- formulas[[country]][[flavor]]
-      # CD models
-      models[[country]][[flavor]][["noE"]][["CD"]]   <- cdModel(fnoE, data = historicalData[[country]])
-      models[[country]][[flavor]][["withE"]][["CD"]] <- cdModel(fwithE, data = historicalData[[country]])
-      # CES models
+    models[[country]][[flavor]][["noE"]][["CD"]]   <- cdModel(fnoE, data = HistoricalData[[country]])
+    models[[country]][[flavor]][["withE"]][["CD"]] <- cdModel(fwithE, data = HistoricalData[[country]])
+  }
+}
+@
+
+<<Models_CES>>=
+fileNameCES <- "EcolEcon2015ModelsCES.rds"
+if (!rerunCESModels){
+  # Load CES models from the file on disk
+  models <- readRDS(fileNameCES)
+} else {
+  # Re-fit CES models
+  for(country in countries){
+    for (flavor in flavors){
+      fnoE <- keep_summands(formulas[[country]][[flavor]], -3) # Drop the energy term (3rd term on RHS)
+      fwithE <- formulas[[country]][[flavor]]
       models[[country]][[flavor]][["noE"]][["CES"]][["kl"]] <- cesModel(fnoE, 
-                                                                        data = historicalData[[country]], 
+                                                                        data = HistoricalData[[country]], 
                                                                         nest=c(1,2), digits = 10)
@@
       models[[country]][[flavor]][["withE"]][["CES"]] <- lapply(nestsWithE, function(nest){
-          cesModel(formula=fwithE, data=historicalData[[country]], nest=nest, digits = 10)
+          cesModel(formula=fwithE, data=HistoricalData[[country]], nest=nest, digits = 10)
         })
@@
   # Save models to disk.
-  saveRDS(models, file=fileNameCDCES)  
+  saveRDS(models, file=fileNameCES)  
 }
@@
     ### Is there any reason to select away some of the columns?
-    trimmed_historical_data <- historicalData[[Country]][c("Year", measure.vars)]
+    trimmed_historical_data <- HistoricalData[[Country]][c("Year", measure.vars)]
 

### 2015-10-22 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Cleaning up TableData code.

@@
 
-<<Models_CDC>>=
+<<Models_CD>>=
+#
+# Cobb-Douglas models
+#
 models <- list()
@@
 <<Models_CES>>=
+#
+# CES models
+#
 fileNameCES <- "EcolEcon2015ModelsCES.rds"
@@
   # Parse the id to find out whether this is quality-adjusted data, etc.
-  ### Don't name non-lists with variables whose names sound like a list.
-  ### I'm guessing you just didn't know what kind of data you were working with here. 
-  ### Either way, it's a bad thing.
   id_components <- strsplit(id, split = "[.]")[[1]]
 
-  # return this data frame 
-  ### NOTE: ifelse() and [ ] handle NAs the way we want here
-  ### The former use of [[ ]] was unnecessary and would break things in the new code
-  ### I'm guessing you had [[ ]] because you thought you had a list when you did not.
-
-  ### NOTE: data_frame does not auto-convert to factors.  It leaves things as strings.
   data_frame(
@@
 }
-
-### AH: So much tidier here :-)
-### NOTE: dplyr::bind_rows() can replace plyr::rbind.fill() in most (all?) situations
-###       plyr should probably not be used for data frame level operations anymore.
 
@@
 # Relevel factors and re-order data
-### NOTE:  Need to convert from strings to factors to use relevelFactor()
-###        We could modify relevelFacotr() to accept character inputs
 AllCoeffs <- 
@@
   # Parse the id to find out whether this is quality-adjusted data, etc.
-  ### Don't name non-lists with variables whose names sound like a list.
-  ### I'm guessing you just didn't know what kind of data you were working with here. 
-  ### Either way, it's a bad thing.
   id_components <- strsplit(id, split = "[.]")[[1]]
 
-  ### NOTE: data_frame does not auto-convert to factors.  It leaves things as strings.
-  # message(class(mod))
   if (! inherits(mod, "cesModel") ) return(NULL)
@@
 # Now append to AllOE time-varying output elasticities from models that adhere to the CSP.
-
 AllOE <- leaf_apply(modelsCSP, class="cesModel", f=mod2oedf) %>% 
@@
 <<Resampling-CD>>=
-print("Top of Resampling-CD")
-
 resampleCoeffsCDFilename <- "EcolEcon2015ResampleCoeffsCD.rds"
@@
 <<ReModels>>=
-print("Top of ReModels")
-
 ReModels <-
@@
 
-<<Fitted_and_Residuals>>=
-### Why are we going back and forth between CamelCase and interspersed_underscores?
-### If there isn't a reason, probably we should stick with one naming convention.
-
+<<FittedAndResiduals>>=
 temp_data_exp <- 
@@
 
-<<Table_data>>=
-table_data <- 
+<<TableData>>=
+  TableData <- 
   AllCoeffs %>%

### 2015-10-22 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Cleaning up TableData code.

@@
 <<CES_sr_gof, results="asis">>=
-data_CES_SR_gof <- 
-  table_data %>% 
+TableData %>% 
   filter(Model=="CES" | Model=="Ref.") %>% 
@@
                  "scale" = "$\\theta$",
-                  "lambda" = "$\\lambda$"))
+                 "lambda" = "$\\lambda$")) %>%
 
-myXTable(data_CES_SR_gof,
-         caption="Scale parameter~($\\theta$), Solow residual~($\\lambda$), and sum of squared errors~($sse$) for all modeling choices.",
+  myXTable(caption="Scale parameter~($\\theta$), Solow residual~($\\lambda$), 
+           and sum of squared errors~($sse$) for all modeling choices.",
            label=paste0("tab:", opts_current$get("label")), 
@@
 <<delta_table, results="asis">>=
-data_delta_table <- 
-  table_data %>% 
+TableData %>% 
   filter(Model=="CES") %>% 
@@
                  "delta_1" = "$\\delta_1$",
-                  "delta" = "$\\delta$"))
+                 "delta" = "$\\delta$")) %>%
 
-myXTable(data_delta_table,
-         caption="Distribution parameters ($\\delta_1$ and $\\delta$) for all modeling choices.",
+  myXTable(caption="Distribution parameters ($\\delta_1$ and $\\delta$) for all modeling choices.",
            label=paste0("tab:", opts_current$get("label")), 
@@
 <<rho_table, results="asis">>=
-data_rho_table <- 
-  table_data %>% 
+TableData %>% 
   filter(Model=="CES") %>% 
@@
                  "rho_1" = "$\\rho_1$",
-                  "rho" = "$\\rho$"))
+                 "rho" = "$\\rho$")) %>%
 
-myXTable(data_rho_table,
-         caption="Values of ($\\rho_1$ and $\\rho$) for all modeling choices.",
+  myXTable(caption="Values of ($\\rho_1$ and $\\rho$) for all modeling choices.",
            label=paste0("tab:", opts_current$get("label")), 

### 2015-10-22 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Cleaned up HistoricalData.

@@
 
-<<Historical_Data>>=
-
-### Also, I find tidyr::gather() and tidyr::spread() easier to work with than melt() and cast()
-
-histDataForGraph <- 
-  leaf_apply(formulas, class = "formula", f=function(form, name){
-    meta <- strsplit(name, split="[.]")[[1]]
+<<Historical_Plot>>=
+leaf_apply(formulas, class = "formula", f=function(form, id){
+  meta <- strsplit(id, split="[.]")[[1]]
   Country <- meta[1]
@@
   measure.vars <- c(summands(form, right=FALSE), summands(form, 1:3))
-    ### Is there any reason to select away some of the columns?
+  # Trim to avoid plotting data which are unused for one coutry but included for the other.
   trimmed_historical_data <- HistoricalData[[Country]][c("Year", measure.vars)]
 
-    # return this.
   melt(
@@
     variable = relevelFactor(factor(variable), c("y", "k", "l", "e"))
-  )
-@
+  ) %>%
 
-<<Historical_Plot>>=
-ggplot(histDataForGraph) + 
+  ggplot() + 
   geom_line(aes(x=Year, y=value, group=variable, linetype=variable, colour=variable, size=variable)) +

### 2015-10-22 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Cleaned up alpha graph.

@@
 # Replicates exponential models for each flavor in the flavors vector
+# Exponential models cannot have 
+# a "flavor" (Quality-adjusted or Unadjusted),
+# because they do not utilize factors of production in the functional form.
+# Because we will be using the interaction of Country and flavor
+# as the x facet, we need to replicate the exponential models for the various flavors.
 replicateExpModels <- function(data, flavors){
@@
 
+  # Now make the plot
   ggplot() +
@@
   labs(color = "Factors of production") +
-  xy_theme() # +
-  # theme(legend.title=element_blank())
+  xy_theme()
 
@@
   mutate(
-    xfacet = as.character(interaction(Country, factor(flavor, labels = c("QA", "UA")), sep = " - ")),
+    flavor = plyr::mapvalues(flavor, from=c("Quality-adjusted", "Unadjusted"), to=c("QA", "UA")),
+    xfacet = interaction(Country, flavor, sep = " - "),
     xfacet = relevelFactor(factor(xfacet), c("PT - UA", "PT - QA", "UK - UA", "UK - QA")),
-    yfacet = as.character(interaction(factor(nest, labels = c("(ek)l", "kl", "(kl)e", "(le)k")), CSP, sep = " - ")),
+    nest = plyr::mapvalues(nest, from=c("kle", "lek", "ekl"), to=c("(kl)e", "(le)k", "(ek)l")),
+    yfacet = interaction(nest, CSP, sep = " - "),
     yfacet = relevelFactor(factor(yfacet), c("kl - w/ CSP", "kl - w/o CSP", "(kl)e - w/o CSP", "(le)k - w/o CSP", "(ek)l - w/o CSP"))

### 2015-10-23 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Improved scales of fitted graph.

@@
   facet_grid(yfacet ~ xfacet) + 
-  scale_x_continuous(breaks = c(1960, 1980, 2000)) +
+  scale_x_continuous(limits = c(1955, 2013), breaks = c(1960, 1980, 2000)) +
+  scale_y_continuous(limits = c(0.5, 7), breaks = c(1, 2, 4, 6)) +
   scale_color_manual(
@@
     values=c(1,1) ) + 
-  labs(x="", y="GDP") +
+  labs(x="", y="Indexed GDP (1960 = 1)") +
   xy_theme()

### 2015-11-03 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Added extra models.

@@
 
+<<Other_Models>>=
+# PT, unadjusted kl, quality-adjusted e
+mod_PT_uakl_qae <- cesModel(iGDP ~ iKstkS.L + iL + iUMP + iYear, HistoricalData$PT, nest=c(1,2,3))
+# PT, quality-adjusted kl, unadjusted e
+mod_PT_qakl_uae <- cesModel(iGDP ~ iKservS.L + ihLest + iXpMP + iYear, HistoricalData$PT, nest=c(1,2,3))
+
+# UK, unadjusted kl, quality-adjusted e
+mod_UK_uakl_qae <- cesModel(iGDP ~ iKstkO.WwithRD + iL + iU + iYear, HistoricalData$UK, nest=c(1,2,3))
+# UK, quality-adjusted kl, unadjusted e
+mod_UK_qakl_uae <- cesModel(iGDP ~ iKservO.WwithRD + ihLest + iXp + iYear, HistoricalData$UK, nest=c(1,2,3))
+@
+
 \section{End EcolEcon2015A}

### 2015-11-03 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Added extra models.

@@
 
+<<Other_Models_Results>>=
+# PT, unadjusted kl, quality-adjusted e
+summary(mod_PT_uakl_qae)
+naturalCoef(mod_PT_uakl_qae)
+
+# PT, quality-adjusted kl, unadjusted e
+summary(mod_PT_qakl_uae)
+naturalCoef(mod_PT_qakl_uae)
+
+# UK, unadjusted kl, quality-adjusted e
+summary(mod_UK_uakl_qae)
+naturalCoef(mod_UK_uakl_qae)
+
+# UK, quality-adjusted kl, unadjusted e
+summary(mod_UK_qakl_uae)
+naturalCoef(mod_UK_qakl_uae)
+@
+
 %%References

### 2015-11-04 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
eval=FALSE for Other_Models.

--- 2015-10-22 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
@@
 
+<<Other_Models, eval=FALSE>>=
+# These models were estimated and the results sent to Paul Brockway.
+# At this point, there is no reason to estimate the modesl every time.
+
+# PT, unadjusted kl, quality-adjusted e
+mod_PT_uakl_qae <- cesModel(iGDP ~ iKstkS.L + iL + iUMP + iYear, HistoricalData$PT, nest=c(1,2,3))
+# PT, quality-adjusted kl, unadjusted e
+mod_PT_qakl_uae <- cesModel(iGDP ~ iKservS.L + ihLest + iXpMP + iYear, HistoricalData$PT, nest=c(1,2,3))
+
+# UK, unadjusted kl, quality-adjusted e
+mod_UK_uakl_qae <- cesModel(iGDP ~ iKstkO.WwithRD + iL + iU + iYear, HistoricalData$UK, nest=c(1,2,3))
+# UK, quality-adjusted kl, unadjusted e
+mod_UK_qakl_uae <- cesModel(iGDP ~ iKservO.WwithRD + ihLest + iXp + iYear, HistoricalData$UK, nest=c(1,2,3))
+@
+
 \section{End EcolEcon2015A}

### 2015-11-08 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Additional info on corner models.

--- 2015-10-22 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
@@
 
+<<Other_Models, eval=FALSE>>=
+# These models were estimated and the results sent to Paul Brockway.
+# At this point, there is no reason to estimate the modesl every time.
+
+# PT, unadjusted kl, quality-adjusted e
+mod_PT_uakl_qae <- cesModel(iGDP ~ iKstkS.L + iL + iUMP + iYear, HistoricalData$PT, nest=c(1,2,3))
+summary(mod_PT_uakl_qae)
+naturalCoef(mod_PT_uakl_qae)
+sum(resid(mod_PT_uakl_qae)^2)
+
+# PT, quality-adjusted kl, unadjusted e
+mod_PT_qakl_uae <- cesModel(iGDP ~ iKservS.L + ihLest + iXpMP + iYear, HistoricalData$PT, nest=c(1,2,3))
+summary(mod_PT_qakl_uae)
+naturalCoef(mod_PT_qakl_uae)
+sum(resid(mod_PT_qakl_uae)^2)
+
+# UK, unadjusted kl, quality-adjusted e
+mod_UK_uakl_qae <- cesModel(iGDP ~ iKstkO.WwithRD + iL + iU + iYear, HistoricalData$UK, nest=c(1,2,3))
+summary(mod_UK_uakl_qae)
+naturalCoef(mod_UK_uakl_qae)
+sum(resid(mod_UK_uakl_qae)^2)
+
+# UK, quality-adjusted kl, unadjusted e
+mod_UK_qakl_uae <- cesModel(iGDP ~ iKservO.WwithRD + ihLest + iXp + iYear, HistoricalData$UK, nest=c(1,2,3))
+summary(mod_UK_qakl_uae)
+naturalCoef(mod_UK_qakl_uae)
+sum(resid(mod_UK_qakl_uae)^2)
+
+@
+
 \section{End EcolEcon2015A}

### 2015-11-11 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Now running off-axis models only when needed.

--- 2015-11-04 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
@@
 # These models were estimated and the results sent to Paul Brockway.
-# At this point, there is no reason to estimate the modesl every time.
+# At this point, there is no reason to estimate the models every time.
 
+fileNameOtherModels <- "EcolEcon2015kleOtherModelsCES.rds"
+
+if (!rerunCESModels){
+  # Load other models from the file on disk
+  other_models <- readRDS(fileNameOtherModels)
+} else {
+  other_models <- list()
   # PT, unadjusted kl, quality-adjusted e
-mod_PT_uakl_qae <- cesModel(iGDP ~ iKstkS.L + iL + iUMP + iYear, HistoricalData$PT, nest=c(1,2,3))
+  other_models$PT$uakl_qae <- cesModel(iGDP ~ iKstkS.L + iL + iUMP + iYear, HistoricalData$PT, nest=c(1,2,3))
   # PT, quality-adjusted kl, unadjusted e
-mod_PT_qakl_uae <- cesModel(iGDP ~ iKservS.L + ihLest + iXpMP + iYear, HistoricalData$PT, nest=c(1,2,3))
+  other_models$PT$qakl_uae <- cesModel(iGDP ~ iKservS.L + ihLest + iXpMP + iYear, HistoricalData$PT, nest=c(1,2,3))
+  # UK, unadjusted kl, quality-adjusted e
+  other_models$UK$uakl_qae <- cesModel(iGDP ~ iKstkO.WwithRD + iL + iU + iYear, HistoricalData$UK, nest=c(1,2,3))
+  # UK, quality-adjusted kl, unadjusted e
+  other_models$UK$qakl_uae <- cesModel(iGDP ~ iKservO.WwithRD + ihLest + iXp + iYear, HistoricalData$UK, nest=c(1,2,3))
+  saveRDS(other_models, fileNameOtherModels)
+}
 
-# UK, unadjusted kl, quality-adjusted e
-mod_UK_uakl_qae <- cesModel(iGDP ~ iKstkO.WwithRD + iL + iU + iYear, HistoricalData$UK, nest=c(1,2,3))
-# UK, quality-adjusted kl, unadjusted e
-mod_UK_qakl_uae <- cesModel(iGDP ~ iKservO.WwithRD + ihLest + iXp + iYear, HistoricalData$UK, nest=c(1,2,3))
 @

### 2015-11-11 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Beginning a table for Paper 1.

--- 2015-10-23 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
@@
 
+<<Other_Models_Results>>=
+  # PT, unadjusted kl, quality-adjusted e
+  summary(other_models$PT$uakl_qae)
+  naturalCoef(other_models$PT$uakl_qae)
+  sum(resid(other_models$PT$uakl_qae)^2)
+
+  # PT, quality-adjusted kl, unadjusted e
+  summary(other_models$PT$qakl_uae)
+  naturalCoef(other_models$PT$qakl_uae)
+  sum(resid(other_models$PT$qakl_uae)^2)
+
+  # UK, unadjusted kl, quality-adjusted e
+  summary(other_models$UK$uakl_qae)
+  naturalCoef(other_models$UK$uakl_qae)
+  sum(resid(other_models$UK$uakl_qae)^2)
+
+  # UK, quality-adjusted kl, unadjusted e
+  summary(other_models$UK$qakl_uae)
+  naturalCoef(other_models$UK$qakl_uae)
+  sum(resid(other_models$UK$qakl_uae)^2)
+@
+
+This is a table for Paper 1.
+
+<<Other_Models_table>>=
+  # Start with the exponential-only (reference) models
+  OMTable <- leaf_apply(modelsExp, class="lm", f=function(mod, id){
+    list(Model = "Ref.",
+         Country=id[[1]],
+         kl = NA,
+         e = NA,
+         Nest = NA,
+         lambda = coef(modelsExp[[id[[1]]]])[[2]],
+         lambda_ratio = 1,
+         SSE = sum(resid(mod)^2))
+  }) %>% bind_rows()
+
+  # Add all CES models
+  OMTable <- leaf_apply(models, class="cesModel", f=function(mod, id){
+  id_components <- strsplit(id, split = "[.]")[[1]]
+  list(Model = "CES",
+       Country = id_components[[1]],
+       kl = id_components[[2]],
+       e = id_components[[2]],
+       Nest = id_components[[5]],
+       lambda = naturalCoef(mod)$lambda,
+       lambda_ratio = naturalCoef(mod)$lambda / coef(modelsExp[[id_components[[1]]]])[[2]],
+       SSE = sum(resid(mod)^2))
+  }) %>% bind_rows() %>% bind_rows(OMTable, .)
+
+  # Add the off-axis models
+  OMTable <- leaf_apply(other_models, class="cesModel", f=function(mod, id){
+    id_components <- strsplit(id, split = "[.]")[[1]]
+    print(id_components)
+    adjusted_components <- strsplit(id_components[[2]], "[_]")[[1]]
+    print(adjusted_components)
+    list(Model = "CES",
+         Country = id_components[[1]],
+         kl = ifelse(substr(adjusted_components[[1]], 1, 2) == "ua", "unadjusted", "adjusted"),
+         e = ifelse(substr(adjusted_components[[2]], 1, 2) == "ua", "unadjusted", "adjusted"),
+         Nest = "kle",
+         lambda = naturalCoef(mod)$lambda,
+         lambda_ratio = naturalCoef(mod)$lambda / coef(modelsExp[[id_components[[1]]]])[[2]],
+         SSE = sum(resid(mod)^2)
+         )
+
+  }) %>% bind_rows() %>% bind_rows(OMTable, .)
+
+  OMTable <- 
+    # Keep only rows that we want
+    filter(OMTable, is.na(Nest) | Nest == "kl" | Nest == "kle")
+
+@
+
 %%References

### 2015-11-11 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Getting closer on off-axis model table.

--- 2015-10-23 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
@@
 
+<<Other_Models_Results>>=
+  # PT, unadjusted kl, quality-adjusted e
+  summary(other_models$PT$uakl_qae)
+  naturalCoef(other_models$PT$uakl_qae)
+  sum(resid(other_models$PT$uakl_qae)^2)
+
+  # PT, quality-adjusted kl, unadjusted e
+  summary(other_models$PT$qakl_uae)
+  naturalCoef(other_models$PT$qakl_uae)
+  sum(resid(other_models$PT$qakl_uae)^2)
+
+  # UK, unadjusted kl, quality-adjusted e
+  summary(other_models$UK$uakl_qae)
+  naturalCoef(other_models$UK$uakl_qae)
+  sum(resid(other_models$UK$uakl_qae)^2)
+
+  # UK, quality-adjusted kl, unadjusted e
+  summary(other_models$UK$qakl_uae)
+  naturalCoef(other_models$UK$qakl_uae)
+  sum(resid(other_models$UK$qakl_uae)^2)
+@
+
+This is a table for Paper 1.
+
+<<Other_Models_table>>=
+  # Start with the exponential-only (reference) models
+  OMTable <- leaf_apply(modelsExp, class="lm", f=function(mod, id){
+    list(Country=id[[1]],
+         Model = "Ref.",
+         Nest = NA,
+         kl = NA,
+         e = NA,
+         lambda = coef(modelsExp[[id[[1]]]])[[2]],
+         lambda_ratio = 1,
+         SSE = sum(resid(mod)^2))
+  }) %>% bind_rows()
+
+  # Add all CES models
+  OMTable <- leaf_apply(models, class="cesModel", f=function(mod, id){
+  id_components <- strsplit(id, split = "[.]")[[1]]
+  print(id_components)
+  list(Country = id_components[[1]],
+       Model = "CES",
+       Nest = id_components[[5]],
+       kl = id_components[[2]],
+       e = ifelse(id_components[[3]] == "noE", NA, id_components[[2]]),
+       lambda = naturalCoef(mod)$lambda,
+       lambda_ratio = naturalCoef(mod)$lambda / coef(modelsExp[[id_components[[1]]]])[[2]],
+       SSE = sum(resid(mod)^2))
+  }) %>% bind_rows() %>% bind_rows(OMTable, .)
+
+  # Add the off-axis models
+  OMTable <- leaf_apply(other_models, class="cesModel", f=function(mod, id){
+    id_components <- strsplit(id, split = "[.]")[[1]]
+    adjusted_components <- strsplit(id_components[[2]], "[_]")[[1]]
+    list(Country = id_components[[1]],
+         Model = "CES",
+         Nest = "kle",
+         kl = ifelse(substr(adjusted_components[[1]], 1, 2) == "ua", "unadjusted", "adjusted"),
+         e = ifelse(substr(adjusted_components[[2]], 1, 2) == "ua", "unadjusted", "adjusted"),
+         lambda = naturalCoef(mod)$lambda,
+         lambda_ratio = naturalCoef(mod)$lambda / coef(modelsExp[[id_components[[1]]]])[[2]],
+         SSE = sum(resid(mod)^2)
+         )
+
+  }) %>% bind_rows() %>% bind_rows(OMTable, .)
+
+  OMTable <- 
+    # Keep only rows that we want
+    filter(OMTable, is.na(Nest) | Nest == "kl" | Nest == "kle") %>%
+    # Sort rows as desired
+    mutate(
+      Country = relevelFactor(factor(Country), c("PT", "UK")),
+      Model = relevelFactor(factor(Model), c("Ref.", "CES")),
+      Nest = relevelFactor(factor(Nest), c("NA", "kl", "kle")),
+      kl = plyr::mapvalues(kl, from=c("unadjusted", "adjusted"), to=c("UA", "QA")),
+      kl = relevelFactor(factor(kl), c("UA", "QA")),
+      e = plyr::mapvalues(e, from=c("unadjusted", "adjusted"), to=c("UA", "QA")),
+      e = relevelFactor(factor(e), c("UA", "QA"))
+    ) %>%
+    arrange(Country, Model, Nest, kl, e)
+
+@
+
 %%References

### 2015-11-11 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Now making other models table.

--- 2015-11-03 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
@@
 
-<<Other_Models_Results>>=
+<<Other_Models_Results, eval=FALSE>>=
   # PT, unadjusted kl, quality-adjusted e
-summary(mod_PT_uakl_qae)
-naturalCoef(mod_PT_uakl_qae)
+  summary(other_models$PT$uakl_qae)
+  naturalCoef(other_models$PT$uakl_qae)
+  sum(resid(other_models$PT$uakl_qae)^2)
 
   # PT, quality-adjusted kl, unadjusted e
-summary(mod_PT_qakl_uae)
-naturalCoef(mod_PT_qakl_uae)
+  summary(other_models$PT$qakl_uae)
+  naturalCoef(other_models$PT$qakl_uae)
+  sum(resid(other_models$PT$qakl_uae)^2)
 
   # UK, unadjusted kl, quality-adjusted e
-summary(mod_UK_uakl_qae)
-naturalCoef(mod_UK_uakl_qae)
+  summary(other_models$UK$uakl_qae)
+  naturalCoef(other_models$UK$uakl_qae)
+  sum(resid(other_models$UK$uakl_qae)^2)
 
   # UK, quality-adjusted kl, unadjusted e
-summary(mod_UK_qakl_uae)
-naturalCoef(mod_UK_qakl_uae)
+  summary(other_models$UK$qakl_uae)
+  naturalCoef(other_models$UK$qakl_uae)
+  sum(resid(other_models$UK$qakl_uae)^2)
+@
+
+<<OMTable_df>>=
+  # Create a data frame containing exponential-only (reference) models
+  OMTable_exp <- leaf_apply(modelsExp, class="lm", f=function(mod, id){
+    list(Country=id[[1]],
+         Model = "Ref.",
+         Nest = NA,
+         kl = NA,
+         e = NA,
+         lambda = coef(modelsExp[[id[[1]]]])[[2]],
+         lambda_ratio = 1,
+         SSE = sum(resid(mod)^2))
+  }) %>% bind_rows()
+
+  # Create a data frame containing only the on-axis models, i.e., models that have all factors of production
+  # quality-adjusted simultaneously.
+  OMTable_onaxis <- leaf_apply(models, class="cesModel", f=function(mod, id){
+  id_components <- strsplit(id, split = "[.]")[[1]]
+  list(Country = id_components[[1]],
+       Model = "CES",
+       Nest = id_components[[5]],
+       kl = id_components[[2]],
+       e = ifelse(id_components[[3]] == "noE", NA, id_components[[2]]),
+       lambda = naturalCoef(mod)$lambda,
+       lambda_ratio = naturalCoef(mod)$lambda / coef(modelsExp[[id_components[[1]]]])[[2]],
+       SSE = sum(resid(mod)^2))
+  }) %>% bind_rows()
+
+  # Create a data frame containing only the off-axis models, i.e., models for which factors of production
+  # are quality-adjusted individually. that have all factors of production
+  OMTable_offaxis <- leaf_apply(other_models, class="cesModel", f=function(mod, id){
+    id_components <- strsplit(id, split = "[.]")[[1]]
+    adjusted_components <- strsplit(id_components[[2]], "[_]")[[1]]
+    list(Country = id_components[[1]],
+         Model = "CES",
+         Nest = "kle",
+         kl = ifelse(substr(adjusted_components[[1]], 1, 2) == "ua", "unadjusted", "adjusted"),
+         e = ifelse(substr(adjusted_components[[2]], 1, 2) == "ua", "unadjusted", "adjusted"),
+         lambda = naturalCoef(mod)$lambda,
+         lambda_ratio = naturalCoef(mod)$lambda / coef(modelsExp[[id_components[[1]]]])[[2]],
+         SSE = sum(resid(mod)^2)
+         )
+
+  }) %>% bind_rows()
+
+  OMTable <- bind_rows(OMTable_exp, OMTable_onaxis, OMTable_offaxis) %>%
+
+    # Keep only rows that we want
+    filter(is.na(Nest) | Nest == "kl" | Nest == "kle") %>%
+
+    # Adjust table as desired for printing    
+    mutate(
+      Country = relevelFactor(factor(Country), c("PT", "UK")),
+      Model = relevelFactor(factor(Model), c("Ref.", "CES")),
+      Nest = relevelFactor(factor(Nest), c("NA", "kl", "kle")),
+      kl = plyr::mapvalues(kl, from=c("unadjusted", "adjusted"), to=c("UA", "QA")),
+      kl = relevelFactor(factor(kl), c("UA", "QA")),
+      e = plyr::mapvalues(e, from=c("unadjusted", "adjusted"), to=c("UA", "QA")),
+      e = relevelFactor(factor(e), c("UA", "QA"))
+    ) %>%
+
+    # Sort rows as desired
+    arrange(Country, Model, Nest, kl, e) %>%
+
+    # Rename column titles
+    plyr::rename(c("kl" = "$kl$", 
+                   "e" = "$e$",
+                   "lambda" = "$\\lambda$",
+                   "lambda_ratio" = "$\\lambda / \\lambda_{Ref.}$"))
+
+@
+
+<<OMTable, results="asis">>=
+    # Make the LaTeX table
+    myXTable(OMTable, caption="Solow residual~($\\lambda$) and SSE for $(kl)e$ models.",
+           label=paste0("tab:", opts_current$get("label")), 
+           digits=c(1,1,1,1,1,1, 4, 2, 3))
 @

### 2015-11-12 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Moved OMTable.

@@
   )
+@
+
+<<OMTable_df>>=
+  # Create a data frame containing exponential-only (reference) models
+  OMTable_exp <- leaf_apply(modelsExp, class="lm", f=function(mod, id){
+    list(Country=id[[1]],
+         Model = "Ref.",
+         Nest = NA,
+         kl = NA,
+         e = NA,
+         lambda = coef(modelsExp[[id[[1]]]])[[2]],
+         lambda_ratio = 1,
+         SSE = sum(resid(mod)^2))
+  }) %>% bind_rows()
+
+  # Create a data frame containing only the on-axis models, i.e., models that have all factors of production
+  # quality-adjusted simultaneously.
+  OMTable_onaxis <- leaf_apply(models, class="cesModel", f=function(mod, id){
+  id_components <- strsplit(id, split = "[.]")[[1]]
+  list(Country = id_components[[1]],
+       Model = "CES",
+       Nest = id_components[[5]],
+       kl = id_components[[2]],
+       e = ifelse(id_components[[3]] == "noE", NA, id_components[[2]]),
+       lambda = naturalCoef(mod)$lambda,
+       lambda_ratio = naturalCoef(mod)$lambda / coef(modelsExp[[id_components[[1]]]])[[2]],
+       SSE = sum(resid(mod)^2))
+  }) %>% bind_rows()
+
+  # Create a data frame containing only the off-axis models, i.e., models for which factors of production
+  # are quality-adjusted individually. that have all factors of production
+  OMTable_offaxis <- leaf_apply(other_models, class="cesModel", f=function(mod, id){
+    id_components <- strsplit(id, split = "[.]")[[1]]
+    adjusted_components <- strsplit(id_components[[2]], "[_]")[[1]]
+    list(Country = id_components[[1]],
+         Model = "CES",
+         Nest = "kle",
+         kl = ifelse(substr(adjusted_components[[1]], 1, 2) == "ua", "unadjusted", "adjusted"),
+         e = ifelse(substr(adjusted_components[[2]], 1, 2) == "ua", "unadjusted", "adjusted"),
+         lambda = naturalCoef(mod)$lambda,
+         lambda_ratio = naturalCoef(mod)$lambda / coef(modelsExp[[id_components[[1]]]])[[2]],
+         SSE = sum(resid(mod)^2)
+         )
+
+  }) %>% bind_rows()
+
+  OMTable <- bind_rows(OMTable_exp, OMTable_onaxis, OMTable_offaxis) %>%
+
+    # Keep only rows that we want
+    filter(is.na(Nest) | Nest == "kl" | Nest == "kle") %>%
+
+    # Adjust table as desired for printing    
+    mutate(
+      Country = relevelFactor(factor(Country), c("PT", "UK")),
+      Model = relevelFactor(factor(Model), c("Ref.", "CES")),
+      Nest = relevelFactor(factor(Nest), c("NA", "kl", "kle")),
+      kl = plyr::mapvalues(kl, from=c("unadjusted", "adjusted"), to=c("UA", "QA")),
+      kl = relevelFactor(factor(kl), c("UA", "QA")),
+      e = plyr::mapvalues(e, from=c("unadjusted", "adjusted"), to=c("UA", "QA")),
+      e = relevelFactor(factor(e), c("UA", "QA"))
+    ) %>%
+
+    # Sort rows as desired
+    arrange(Country, Model, Nest, kl, e) %>%
+
+    # Rename column titles
+    plyr::rename(c("kl" = "$kl$", 
+                   "e" = "$e$",
+                   "lambda" = "$\\lambda$",
+                   "lambda_ratio" = "$\\lambda / \\lambda_{Ref.}$"))
+
+@
+
+<<OMTable, results="asis">>=
+  # Make the LaTeX table
+  myXTable(OMTable, 
+           caption="Solow residual~($\\lambda$) and sum of squared errors~(SSE) for $(kl)e$ models that reject the cost share principle. 
+             $\\lambda / \\lambda_{Ref.}$ is the ratio of Solow residual relative to the reference (exponential-only) model.
+             ``UA'' and ``QA'' indicate unadjusted and quality-adjusted factors of production, respectively.",
+           label=paste0("tab:", opts_current$get("label")), 
+           digits=c(1,1,1,1,1,1, 4, 2, 3))
 @
@@
 
-<<OMTable_df>>=
-  # Create a data frame containing exponential-only (reference) models
-  OMTable_exp <- leaf_apply(modelsExp, class="lm", f=function(mod, id){
-    list(Country=id[[1]],
-         Model = "Ref.",
-         Nest = NA,
-         kl = NA,
-         e = NA,
-         lambda = coef(modelsExp[[id[[1]]]])[[2]],
-         lambda_ratio = 1,
-         SSE = sum(resid(mod)^2))
-  }) %>% bind_rows()
-
-  # Create a data frame containing only the on-axis models, i.e., models that have all factors of production
-  # quality-adjusted simultaneously.
-  OMTable_onaxis <- leaf_apply(models, class="cesModel", f=function(mod, id){
-  id_components <- strsplit(id, split = "[.]")[[1]]
-  list(Country = id_components[[1]],
-       Model = "CES",
-       Nest = id_components[[5]],
-       kl = id_components[[2]],
-       e = ifelse(id_components[[3]] == "noE", NA, id_components[[2]]),
-       lambda = naturalCoef(mod)$lambda,
-       lambda_ratio = naturalCoef(mod)$lambda / coef(modelsExp[[id_components[[1]]]])[[2]],
-       SSE = sum(resid(mod)^2))
-  }) %>% bind_rows()
-
-  # Create a data frame containing only the off-axis models, i.e., models for which factors of production
-  # are quality-adjusted individually. that have all factors of production
-  OMTable_offaxis <- leaf_apply(other_models, class="cesModel", f=function(mod, id){
-    id_components <- strsplit(id, split = "[.]")[[1]]
-    adjusted_components <- strsplit(id_components[[2]], "[_]")[[1]]
-    list(Country = id_components[[1]],
-         Model = "CES",
-         Nest = "kle",
-         kl = ifelse(substr(adjusted_components[[1]], 1, 2) == "ua", "unadjusted", "adjusted"),
-         e = ifelse(substr(adjusted_components[[2]], 1, 2) == "ua", "unadjusted", "adjusted"),
-         lambda = naturalCoef(mod)$lambda,
-         lambda_ratio = naturalCoef(mod)$lambda / coef(modelsExp[[id_components[[1]]]])[[2]],
-         SSE = sum(resid(mod)^2)
-         )
-
-  }) %>% bind_rows()
-
-  OMTable <- bind_rows(OMTable_exp, OMTable_onaxis, OMTable_offaxis) %>%
-
-    # Keep only rows that we want
-    filter(is.na(Nest) | Nest == "kl" | Nest == "kle") %>%
-
-    # Adjust table as desired for printing    
-    mutate(
-      Country = relevelFactor(factor(Country), c("PT", "UK")),
-      Model = relevelFactor(factor(Model), c("Ref.", "CES")),
-      Nest = relevelFactor(factor(Nest), c("NA", "kl", "kle")),
-      kl = plyr::mapvalues(kl, from=c("unadjusted", "adjusted"), to=c("UA", "QA")),
-      kl = relevelFactor(factor(kl), c("UA", "QA")),
-      e = plyr::mapvalues(e, from=c("unadjusted", "adjusted"), to=c("UA", "QA")),
-      e = relevelFactor(factor(e), c("UA", "QA"))
-    ) %>%
-
-    # Sort rows as desired
-    arrange(Country, Model, Nest, kl, e) %>%
-
-    # Rename column titles
-    plyr::rename(c("kl" = "$kl$", 
-                   "e" = "$e$",
-                   "lambda" = "$\\lambda$",
-                   "lambda_ratio" = "$\\lambda / \\lambda_{Ref.}$"))
-
-@
-
-<<OMTable, results="asis">>=
-    # Make the LaTeX table
-    myXTable(OMTable, caption="Solow residual~($\\lambda$) and SSE for $(kl)e$ models.",
-           label=paste0("tab:", opts_current$get("label")), 
-           digits=c(1,1,1,1,1,1, 4, 2, 3))
-@
-
 %%References

### 2015-11-13 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Now making OMGraph.

--- 2015-11-11 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
@@
 
+<<OMTable_df>>=
+  # Create a data frame containing exponential-only (reference) models
+  OMTable_exp <- leaf_apply(modelsExp, class="lm", f=function(mod, id){
+    list(Country=id[[1]],
+         Model = "Ref.",
+         Nest = NA,
+         kl = NA,
+         e = NA,
+         lambda = coef(modelsExp[[id[[1]]]])[[2]],
+         lambda_ratio = 1,
+         SSE = sum(resid(mod)^2))
+  }) %>% bind_rows()
+
+  # Create a data frame containing only the on-axis models, i.e., models that have all factors of production
+  # quality-adjusted simultaneously.
+  OMTable_onaxis <- leaf_apply(models, class="cesModel", f=function(mod, id){
+  id_components <- strsplit(id, split = "[.]")[[1]]
+  list(Country = id_components[[1]],
+       Model = "CES",
+       Nest = id_components[[5]],
+       kl = id_components[[2]],
+       e = ifelse(id_components[[3]] == "noE", NA, id_components[[2]]),
+       lambda = naturalCoef(mod)$lambda,
+       lambda_ratio = naturalCoef(mod)$lambda / coef(modelsExp[[id_components[[1]]]])[[2]],
+       SSE = sum(resid(mod)^2))
+  }) %>% bind_rows()
+
+  # Create a data frame containing only the off-axis models, i.e., models for which factors of production
+  # are quality-adjusted individually. that have all factors of production
+  OMTable_offaxis <- leaf_apply(other_models, class="cesModel", f=function(mod, id){
+    id_components <- strsplit(id, split = "[.]")[[1]]
+    adjusted_components <- strsplit(id_components[[2]], "[_]")[[1]]
+    list(Country = id_components[[1]],
+         Model = "CES",
+         Nest = "kle",
+         kl = ifelse(substr(adjusted_components[[1]], 1, 2) == "ua", "unadjusted", "adjusted"),
+         e = ifelse(substr(adjusted_components[[2]], 1, 2) == "ua", "unadjusted", "adjusted"),
+         lambda = naturalCoef(mod)$lambda,
+         lambda_ratio = naturalCoef(mod)$lambda / coef(modelsExp[[id_components[[1]]]])[[2]],
+         SSE = sum(resid(mod)^2)
+         )
+
+  }) %>% bind_rows()
+
+  OMTable <- bind_rows(OMTable_exp, OMTable_onaxis, OMTable_offaxis) %>%
+
+    # Keep only rows that we want
+    filter(is.na(Nest) | Nest == "kl" | Nest == "kle") %>%
+
+    # Adjust table factors and levels
+    mutate(
+      Country = relevelFactor(factor(Country), c("PT", "UK")),
+      Model = relevelFactor(factor(Model), c("Ref.", "CES")),
+      Nest = relevelFactor(factor(Nest), c("NA", "kl", "kle")),
+      kl = plyr::mapvalues(kl, from=c("unadjusted", "adjusted"), to=c("UA", "QA")),
+      kl = relevelFactor(factor(kl), c("UA", "QA")),
+      e = plyr::mapvalues(e, from=c("unadjusted", "adjusted"), to=c("UA", "QA")),
+      e = relevelFactor(factor(e), c("UA", "QA"))
+    )
+
+@
+
+<<OMTable, results="asis">>=
+  OMTable %>%
+
+    # Sort rows as desired
+    arrange(Country, Model, Nest, kl, e) %>%
+
+    # Rename column titles
+    plyr::rename(c("kl" = "$kl$", 
+                   "e" = "$e$",
+                   "lambda" = "$\\lambda$",
+                   "lambda_ratio" = "$\\lambda / \\lambda_{Ref.}$")) %>%
+
+    # Make the LaTeX table
+    myXTable(caption="Solow residual~($\\lambda$) and sum of squared errors~(SSE) for $(kl)e$ models that reject the cost share principle. 
+             $\\lambda / \\lambda_{Ref.}$ is the ratio of Solow residual relative to the reference (exponential-only) model.
+             ``UA'' and ``QA'' indicate unadjusted and quality-adjusted factors of production, respectively.",
+             label=paste0("tab:", opts_current$get("label")), 
+             digits=c(1,1,1,1,1,1, 4, 2, 3))
+
+@
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+<<Other_Models_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Solow residual~($\\lambda$) for various models.">>=
+# Duplicate the reference models for each nest (kl and kle)
+bind_rows(
+  OMTable %>% filter(Model != "Ref."),
+  OMTable %>% filter(Model == "Ref.") %>% mutate(Nest = "kl"),
+  OMTable %>% filter(Model == "Ref.") %>% mutate(Nest = "kle")
+) %>%
+
+  # Add a new column that will become the x-axis labels for the bar graphs.
+  mutate(
+    klquality = paste0("kl-", kl),
+    equality  = paste0("e-", e),
+    xlabels   = ifelse (Model == "Ref.", "Ref.", ifelse(Nest == "kl", klquality, paste(klquality, equality, sep = ", "))),
+    xlabels   = relevelFactor(factor(xlabels), c("Ref.", "kl-UA", "kl-QA", "kl-UA, e-UA", "kl-UA, e-QA", "kl-QA, e-UA", "kl-QA, e-QA")),
+    Nest = plyr::mapvalues(Nest, from = c("kle"), to = c("(kl)e")),
+    Nest = relevelFactor(factor(Nest), c("kl", "(kl)e"))
+
+  ) %>%
+
+  ggplot(aes(x = xlabels, weight = lambda)) + 
+  facet_grid(Nest ~ Country) +
+  geom_bar(width = 0.5) +
+  xlab("") +
+  ylab(expression(lambda)) +
+  xy_theme() + 
+  theme(axis.text.x = element_text(angle = 90, hjust = 1))
+
+@
+
 <<Graphs_all_models_alphas_time, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap="Output elasticity ($\\alpha$) for all models.">>=

### 2015-11-13 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Get rid of unused blank line.

@@
     Nest = relevelFactor(factor(Nest), c("kl", "(kl)e"))
-
   ) %>%

### 2015-11-13 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Now can evaluate Other_Models.
rbind.fill -> bind_rows

--- 2015-11-04 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
@@
 
-FittedAndResid <- plyr::rbind.fill(temp_data_exp, temp_data_CSP, temp_data_noCSP)
-
+FittedAndResid <- bind_rows(temp_data_exp, temp_data_CSP, temp_data_noCSP)
 @
@@
   AllCoeffs %>%
-  plyr::rename(c(model = "Model", energy = "Energy", nest = "Nest")) %>%
+#  rename_(Model = "model", Energy = "energy", Nest = "nest") %>%
   mutate(Nest = 
            plyr::mapvalues(
-             Nest,
+             nest,
              from=c("kl", "kle", "lek", "ekl"),
@@
            plyr::mapvalues(
-             Energy, 
+             energy, 
              from=c("Without energy", "With energy"), 
@@
            plyr::mapvalues(
-             Model, 
+             model, 
              from=c("exp"), 
@@
 
-<<Other_Models, eval=FALSE>>=
-# These models were estimated and the results sent to Paul Brockway.
-# At this point, there is no reason to estimate the modesl every time.
-
-# PT, unadjusted kl, quality-adjusted e
-mod_PT_uakl_qae <- cesModel(iGDP ~ iKstkS.L + iL + iUMP + iYear, HistoricalData$PT, nest=c(1,2,3))
-# PT, quality-adjusted kl, unadjusted e
-mod_PT_qakl_uae <- cesModel(iGDP ~ iKservS.L + ihLest + iXpMP + iYear, HistoricalData$PT, nest=c(1,2,3))
-
-# UK, unadjusted kl, quality-adjusted e
-mod_UK_uakl_qae <- cesModel(iGDP ~ iKstkO.WwithRD + iL + iU + iYear, HistoricalData$UK, nest=c(1,2,3))
-# UK, quality-adjusted kl, unadjusted e
-mod_UK_qakl_uae <- cesModel(iGDP ~ iKservO.WwithRD + ihLest + iXp + iYear, HistoricalData$UK, nest=c(1,2,3))
-@
-
 \section{End EcolEcon2015A}

### 2015-11-13 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw

@@
 
+<<Other_Models>>=
+# These models were estimated and the results sent to Paul Brockway.
+# At this point, there is no reason to estimate the models every time.
+
+fileNameOtherModels <- "EcolEcon2015kleOtherModelsCES.rds"
+
+if (!rerunCESModels){
+  # Load other models from the file on disk
+  other_models <- readRDS(fileNameOtherModels)
+} else {
+  other_models <- list()
+  # PT, unadjusted kl, quality-adjusted e
+  other_models$PT$uakl_qae <- cesModel(iGDP ~ iKstkS.L + iL + iUMP + iYear, HistoricalData$PT, nest=c(1,2,3))
+  # PT, quality-adjusted kl, unadjusted e
+  other_models$PT$qakl_uae <- cesModel(iGDP ~ iKservS.L + ihLest + iXpMP + iYear, HistoricalData$PT, nest=c(1,2,3))
+  # UK, unadjusted kl, quality-adjusted e
+  other_models$UK$uakl_qae <- cesModel(iGDP ~ iKstkO.WwithRD + iL + iU + iYear, HistoricalData$UK, nest=c(1,2,3))
+  # UK, quality-adjusted kl, unadjusted e
+  other_models$UK$qakl_uae <- cesModel(iGDP ~ iKservO.WwithRD + ihLest + iXp + iYear, HistoricalData$UK, nest=c(1,2,3))
+  saveRDS(other_models, fileNameOtherModels)
+}
+
+@
+
 \section{End EcolEcon2015A}

### 2015-11-14 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Changed appearance of OMGraph.

@@
     facet_grid(Nest ~ Country) +
-  geom_bar(width = 0.5) +
+    geom_bar(fill = "white", colour = "black", width = 0.2) +
+    geom_hline(yintercept = 0, colour="gray50", size=0.1) +
     xlab("") +
@@
     xy_theme() + 
-  theme(axis.text.x = element_text(angle = 90, hjust = 1))
+    theme(
+      axis.text.x = element_text(angle = 90, hjust = 1),
+      axis.ticks.x = element_blank()
+    )
 

### 2015-12-04 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Added a blank line for testing purposes.
Models w/o energy now have no alpha_e line.

@@
 <<Graphs_all_models_alphas_time, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=6, fig.cap="Output elasticity ($\\alpha$) for all models.">>=
-AllOE %>% 
+# Models without energy should have NA for oe3. Doing so eliminates them from the graph.
+AllOE2 <- AllOE
+AllOE2$oe3[which(AllOE$energy == "Without energy")] <- NA
+AllOE2 %>% 
   mutate(

### 2015-12-04 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Cost share graph improvements.

@@
 
-<<Cost_Share_Plot, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=1.5, fig.cap="Historical cost shares for capital and labor.", eval=FALSE>>=
-ggplot(data = gather(CostShares, key=cost_share, value=value, cs_k, cs_l)) + 
+<<Cost_Share_Plot, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=2.8, fig.cap="Historical cost shares for capital and labor.">>=
+gather(CostShares, key=cost_share, value=value, cs_k, cs_l) %>%
+  mutate(
+    cost_share = relevelFactor(factor(cost_share), c("cs_l", "cs_k"))
+  ) %>%
+ggplot() + 
   geom_line(mapping = aes(
@@
   ylab("Cost Share") +
-  scale_y_continuous(limits=c(-0.2, 1.1), breaks=c(0, 0.5, 1)) +
+  scale_y_continuous(limits=c(0.0, 1.0), breaks=c(0, 0.5, 1)) +
   geom_hline(aes(yintercept = 0.3), colour="gray50", size=0.1) +
@@
   scale_color_manual(name = "", 
-                     labels=c("k", "l"),
+                     labels=c("l", "k"),
                      values=c("black", "black")) +
   scale_linetype_manual(name="", 
-                        labels=c("k", "l"),
+                        labels=c("l", "k"),
                         values=c(2,3)) + 
   scale_size_manual(name="", 
-                    labels=c("k", "l"),
+                    labels=c("l", "k"),
                     values = c(0.9, 0.9)) +

### 2015-12-04 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Darker resample dots.

@@
 <<resample_graph_lambda_theta, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.5, fig.cap="$\\lambda$ and $\\theta$ values for resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
-standardScatterPlot(data=resampleCoeffsCES, mapping=aes(scale, lambda), facet_formula=~Country, alpha=0.05, orig_color = "black") +
+standardScatterPlot(data=resampleCoeffsCES, mapping=aes(scale, lambda), facet_formula=~Country, alpha=0.25, orig_color = "black") +
     scale_x_continuous(breaks=c(0.95, 1.0, 1.05)) + 
@@
 standardScatterPlot(data=resampleCoeffsCES, mapping=aes(delta_1, delta), 
-                    facet_formula=~Country, alpha=0.1,
+                    facet_formula=~Country, alpha=0.2,
                     orig_color="black") +

### 2015-12-07 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Eliminated two unneeded library calls.

@@
 library(knitr)
-library(texreg)
-library(tidyr)
 library(scales)

### 2015-12-07 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Trying new version of models graph.

@@
   scale_y_continuous(limits = c(0.5, 7), breaks = c(1, 2, 4, 6)) +
+
+  # We had this code for a while
+#   scale_color_manual(
+#     name = "",
+#     labels = c("historical", "fitted"),
+#     values=c("gray70", "black")
+#   ) +
+#   scale_size_manual(
+#     name = "",
+#     labels = c("historical", "fitted"),
+#     values = c(1.5, 0.3)) +
+#   scale_linetype_manual( 
+#     name = "",
+#     labels = c("historical", "fitted"),
+#     values=c(1,1) ) + 
+#   labs(x="", y="Indexed GDP (1960 = 1)") +
+
+  # But Paul suggests some small changes:
+
   scale_color_manual(
@@
     labels = c("historical", "fitted"),
-    values=c("gray70", "black")
+    values=c("black", "black")
   ) +
@@
     labels = c("historical", "fitted"),
-    values = c(1.5, 0.3)) +
+    values = c(0.2, 0.2)) +
   scale_linetype_manual( 
@@
     labels = c("historical", "fitted"),
-    values=c(1,1) ) + 
+    values=c(1,2) ) + 
   labs(x="", y="Indexed GDP (1960 = 1)") +
+
   xy_theme()

### 2015-12-07 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Resample plots with smaller gray points.

@@
 <<resample_graph_lambda_theta, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.5, fig.cap="$\\lambda$ and $\\theta$ values for resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
-standardScatterPlot(data=resampleCoeffsCES, mapping=aes(scale, lambda), facet_formula=~Country, alpha=0.25, orig_color = "black") +
+standardScatterPlot(data=resampleCoeffsCES, mapping=aes(scale, lambda), facet_formula=~Country, alpha=0.25, size=1, orig_color = "black") +
     scale_x_continuous(breaks=c(0.95, 1.0, 1.05)) + 
@@
 standardScatterPlot(data=resampleCoeffsCES, mapping=aes(delta_1, delta), 
-                    facet_formula=~Country, alpha=0.2,
+                    facet_formula=~Country, alpha=0.2, size = 1,
                     orig_color="black") +

### 2015-12-07 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Deleted commented code.

@@
 
-  # We had this code for a while
-#   scale_color_manual(
-#     name = "",
-#     labels = c("historical", "fitted"),
-#     values=c("gray70", "black")
-#   ) +
-#   scale_size_manual(
-#     name = "",
-#     labels = c("historical", "fitted"),
-#     values = c(1.5, 0.3)) +
-#   scale_linetype_manual( 
-#     name = "",
-#     labels = c("historical", "fitted"),
-#     values=c(1,1) ) + 
-#   labs(x="", y="Indexed GDP (1960 = 1)") +
-
-  # But Paul suggests some small changes:
-
   scale_color_manual(

### 2015-12-09 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Now fitting only 1960--2009

@@
   PT = IST %>% 
-    filter(Country == "PT"), 
+    filter(Country == "PT", Year <= 2009), # Ensures all fits are done on equal basis.
   UK = Leeds %>% 
-    filter(Country == "UK") 
+    filter(Country == "UK", Year <= 2009)
 )

### 2016-02-04 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Expand x axis of lambda vs. sse graph.

@@
   facet_grid(flavor ~ Country) +
-  scale_x_continuous(breaks=c(0, 0.01, 0.02, 0.03), limits=c(0, 0.035)) +
+  scale_x_continuous(breaks=c(0, 0.01, 0.02, 0.03), limits=c(0, 0.036)) +
   xlab(expression(lambda)) +

### 2016-02-09 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Added a section on boundary models.

@@
 \usepackage[right]{lineno}
+
+\newcommand{\sse}{\mbox{SSE}}
 
@@
 @
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Boundary Model Discussion}
+\label{sec:boundary_model_discussion}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Many other modeling approaches estimate parameters that are close to, 
+but not exactly on, a boundary. 
+One example is the modeling approach for Portugal wherein
+all factors of production are quality-adjusted,
+the $(kl)e$ nesting structure is employed, and the CSP is rejected.
+The best fitting value of $\delta_1$ is rounds to 
+\Sexpr{format(round(naturalCoef(models$PT$adjusted$withE$CES$kle)$delta_1, 3), nsmall = 3)}.
+However, if all decimal places determined by the fitting algorithm are reported,
+the value of $\delta_1$ is shown to be 
+\Sexpr{format(round(naturalCoef(models$PT$adjusted$withE$CES$kle)$delta_1, 20), nsmall = 20)}. 
+The fitting algorithm
+finds a set of parameters that minimizes the objective function for the fitting algorithm, \sse.
+Indeed, the winning, near-boundary model has \sse{} = 
+\Sexpr{format(round(sum(resid(models$PT$adjusted$withE$CES$kle)^2), 3), nsmall = 3)},
+while the model on the boundary where 
+$\delta_1 = 1$ has \sse{} = 
+\Sexpr{format(round(sum(resid(attr(models$PT$adjusted$withE$CES$kle, "model.attempts")[[11]])^2), 3), nsmall = 3)}.
 

### 2016-02-10 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Including one more decimal place.

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Boundary Model Discussion}
+\section{Boundary model discussion}
 \label{sec:boundary_model_discussion}
@@
            label=paste0("tab:", opts_current$get("label")), 
-           digits=c(1,1,1,1,1,1,1, 2, 4, 3))
+           digits=c(1,1,1,1,1,1,1, 2, 4, 4))
 @

### 2016-02-16 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
sse --> SSE

@@
                  "scale" = "$\\theta$",
-                 "lambda" = "$\\lambda$")) %>%
+                 "lambda" = "$\\lambda$",
+                 "sse" = "SSE")) %>%
 

### 2016-02-16 Articles/Brockway_Rebound_2015/Brockway_2015.Rnw
Now uses aes for geom_hline.

@@
   geom_line(mapping=aes(x=Year, y=Re, group=Country, linetype=Country)) +
-  geom_hline(y=1, color = "gray70", size=0.3) +
+  geom_hline(mapping=aes(yintercept=1), color = "gray70", size=0.3) +
   scale_y_continuous(breaks=c(0, 1, 2, 3), limits=c(0, 3)) +

### 2016-02-16 Articles/Brockway_Rebound_2015/Brockway_2015.Rnw
Now fitting with iXp for energy.

@@
 modelsFileName <- file.path("models", "Brockway2015Models.rds")
+modelsiXpFileName <- file.path("models", "Brockway2015ModelsiXp.rds")
 if (!rerunModels){
@@
   models <- readRDS(modelsFileName)
+  modelsiXp <- readRDS(modelsiXpFileName)
 } else {
@@
   saveRDS(models, file = modelsFileName)
+
+  # Now models using iXp instead of iU
+  modelsiXp <- lapply(countries, function(coun){
+    return(cesModel(iY ~ iK + iL + iXp + iYear, filter(historicalData, Country == coun, nest = 1:3)))
+  })
+  names(modelsiXp) <- countries
+  # Save the models.
+  saveRDS(modelsiXp, file = modelsiXpFileName)
 }
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Primary Exergy} 
+\label{sec:primary_exergy}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We can also fit to historical data using quality-adjusted $kl$ and unadjusted $e$
+in the form of primary exergy ($iXp$). 
+Here are the results.
+
+<<iXp, echo=TRUE>>=
+# UK
+modelsiXp$UK
+# US
+modelsiXp$US
+# CN
+modelsiXp$CN
+
+# sse for each model
+
+# UK
+sum(resid(modelsiXp$UK)^2)
+# US
+sum(resid(modelsiXp$US)^2)
+# CN
+sum(resid(modelsiXp$CN)^2)
+
+# Compare to sse for models that use iU
+# UK
+sum(resid(models$UK)^2)
+# US
+sum(resid(models$US)^2)
+# CN
+sum(resid(models$CN)^2)
+
+@
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusion}

### 2016-03-18 Articles/Brockway_Rebound_2015/Brockway_2015.Rnw
New CES results for UK 1980 onward.

--- 2016-02-16 Articles/Brockway_Rebound_2015/Brockway_2015.Rnw
@@
 countries <- c("UK", "US", "CN")
+# There are places where we need to use data from 1980 onward for the UK only.
+UK1980Data <- historicalData %>% filter(Country == "UK") %>% subset(Year >= 1980) %>%
+  mutate(
+    # Re-normlaize to 1980.
+    iYear = iYear - iYear[1],
+    iY = iY / iY[1],
+    iK = iK / iK[1],
+    iL = iL / iL[1],
+    iXp = iXp / iXp[1],
+    iU = iU / iU[1],
+    sF = sF / sF[1],
+    sK = sK / sK[1]
+  )
 @
@@
 modelsFileName <- file.path("models", "Brockway2015Models.rds")
+modelsiXpFileName <- file.path("models", "Brockway2015ModelsiXp.rds")
+modelsUK1980FileName <- file.path("models", "Brockway2015ModelsUK1980.rds");
 if (!rerunModels){
@@
   models <- readRDS(modelsFileName)
+  modelsiXp <- readRDS(modelsiXpFileName)
+  modelsUK1980 <- readRDS(modelsUK1980FileName) # UK using only data from 1980 - 2010.
 } else {
@@
   models <- lapply(countries, function(coun){
-    return(cesModel(iY ~ iK + iL + iU + iYear, filter(historicalData, Country==coun, nest=1:3)))
+    return(cesModel(iY ~ iK + iL + iU + iYear, filter(historicalData, Country==coun), nest=1:3))
   })
@@
   saveRDS(models, file = modelsFileName)
+
+  # Now models using iXp instead of iU
+  modelsiXp <- lapply(countries, function(coun){
+    return(cesModel(iY ~ iK + iL + iXp + iYear, filter(historicalData, Country == coun), nest = 1:3))
+  })
+  names(modelsiXp) <- countries
+  # Save the models.
+  saveRDS(modelsiXp, file = modelsiXpFileName)
+
+  # Now run the UK model using only 1980--2010 data
+  modelsUK1980 <- list(
+    U = cesModel(iY ~ iK + iL + iU + iYear, UK1980Data),
+    iXp = cesModel(iY ~ iK + iL + iXp + iYear, UK1980Data)
+    )
+  saveRDS(modelsUK1980, file = modelsUK1980FileName)
 }
+
+# Run these models every time. They are fast.
+modelsKL <- lapply(countries, function(coun){
+  return(cesModel(iY ~ iK + iL + iYear, filter(historicalData, Country==coun), nest = 1:2))
+})
+names(modelsKL) <- countries
+
+modelKLUK1980 <- cesModel(iY ~ iK + iL + iYear, UK1980Data, nest = 1:2)
 @
@@
 
-First, look a the UK results.
+First, look a the UK results using all years: 
+\Sexpr{historicalData %>% subset(Country == "UK") %>% select(Year) %>% min()}--%
+\Sexpr{historicalData %>% subset(Country == "UK") %>% select(Year) %>% max()}.
 
@@
 summary(models[["UK"]])
-naturalCoef(models[["UK"]])
+naturalCoef(models[["UK"]]) %>% glimpse()
 @
@@
 
+Next, UK results using years 
+\Sexpr{min(UK1980Data$Year)} -- \Sexpr{max(UK1980Data$Year)}.
+
+<<resultsUK1980, echo=TRUE>>=
+summary(modelsUK1980$U)
+naturalCoef(modelsUK1980$U) %>% glimpse()
+@
+
+The above model with limited years is along a boundary ($\sigma_1 = \infty$) 
+and very different from the model using all years.
+However, the important thing for rebound is $\rho$,
+which is similar between the two models.
+
 Next, look at the US results.
@@
 summary(models[["US"]])
-naturalCoef(models[["US"]])
+naturalCoef(models[["US"]]) %>% glimpse()
 @
@@
 # and we have delta = 1.
-naturalCoef(bmod7)
+naturalCoef(bmod7) %>% glimpse()
 # Calculate the sse for bmod7
@@
 summary(models[["CN"]])
-naturalCoef(models[["CN"]])
+naturalCoef(models[["CN"]]) %>% glimpse()
 @
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Primary Exergy} 
+\label{sec:primary_exergy}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We can also fit to historical data using quality-adjusted $kl$ and unadjusted $e$
+in the form of primary exergy ($iXp$). 
+Here are the results.
+
+<<iXp, echo=TRUE>>=
+# UK
+modelsiXp$UK
+# UK starting from 1980
+modelsUK1980$iXp
+# US
+modelsiXp$US
+# CN
+modelsiXp$CN
+
+# sse for each model
+
+# UK
+sum(resid(modelsiXp$UK)^2)
+# UK 1980
+sum(resid(modelsUK1980$iXp)^2)
+# US
+sum(resid(modelsiXp$US)^2)
+# CN
+sum(resid(modelsiXp$CN)^2)
+
+# Compare to sse for models that use iU
+# UK
+sum(resid(models$UK)^2)
+# UK1980
+sum(resid(modelsUK1980$U)^2)
+# US
+sum(resid(models$US)^2)
+# CN
+sum(resid(models$CN)^2)
+
+@
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{$kl$-only models} 
+\label{sec:klmodels}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Here are some models fit with only k and l as factors of production.
+
+<<kl, echo=TRUE>>=
+# UK
+modelsKL$UK
+# UK 1980
+modelKLUK1980
+# US
+modelsKL$US
+# CN
+modelsKL$CN
+
+# sse for each model
+
+# UK
+sum(resid(modelsKL$UK)^2)
+# UK1980
+sum(resid(modelKLUK1980)^2)
+# US
+sum(resid(modelsKL$US)^2)
+# CN
+sum(resid(modelsKL$CN)^2)
+
+@
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusion}

### 2016-03-18 Articles/Brockway_Rebound_2015/Brockway_2015.Rnw
Now resamples UK 1980-->2010.

@@
 resampleFileName <- file.path("models", "Brockway2015Resamples.rds")
+resampleUK1980FileName <- file.path("models", "Brockway2015UK1980Resamples.rds")
 if (!rerunResamples){
@@
     resampleCoeffs <- readRDS(resampleFileName)
+    resampleCoeffsUK1980 <- readRDS(resampleUK1980FileName)
 } else {
@@
   saveRDS(resampleCoeffs, file = resampleFileName)
+
+  # UK model for years 1980-2010
+  resampleCoeffsUK1980 <- resampledFits(modelsUK1980$U, method = "wild", n = nResamples)$coeffs
+  saveRDS(resampleCoeffsUK1980, file = resampleUK1980FileName)
 }

### 2016-04-24 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Evaluated UK (kl)e model for boundary issues.

@@
 
+%++++++++++++++++++++++++++++++
+\subsection{Portugal} 
+\label{sec:boundary_portugal}
+%++++++++++++++++++++++++++++++
+
 Many other modeling approaches estimate parameters that are close to, 
@@
 \Sexpr{format(round(sum(resid(attr(models$PT$adjusted$withE$CES$kle, "model.attempts")[[11]])^2), 3), nsmall = 3)}.
+
+%++++++++++++++++++++++++++++++
+\subsection{United Kingdom} 
+\label{sec:boundary_uk}
+%++++++++++++++++++++++++++++++
+
+Many other modeling approaches estimate parameters that are close to, 
+but not exactly on, a boundary. 
+One example is the modeling approach for the UK wherein
+all factors of production are quality-adjusted,
+the $(kl)e$ nesting structure is employed, and the CSP is rejected.
+The best fitting value of $\delta_1$ rounds to 
+\Sexpr{format(round(naturalCoef(models$UK$adjusted$withE$CES$kle)$delta_1, 3), nsmall = 3)},
+and the best fitting value of $\delta$ rounds to
+\Sexpr{format(round(naturalCoef(models$UK$adjusted$withE$CES$kle)$delta, 3), nsmall = 3)}.
+So, it does not appear that the UK model is near a $\delta_1$ or $\delta$ 
+boundary in this instance.
+Nor is it near a $\rho_1$ or $\rho$ boundary. 
+Again, to three decimal places,
+$\rho_1$ is 
+\Sexpr{format(round(naturalCoef(models$UK$adjusted$withE$CES$kle)$rho_1, 3), nsmall = 3)},
+and 
+$\rho$ is
+\Sexpr{format(round(naturalCoef(models$UK$adjusted$withE$CES$kle)$rho, 3), nsmall = 3)}.
+This model is clear of any boundaries.
 

### 2016-05-17 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Changed x axis scale.

@@
   scale_size_manual(name="", values = c(1, 0.9, 0.9, 0.6)) +
+  scale_x_continuous(breaks=c(1960, 1980, 2000)) +
   scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12), limits=c(0.5, 12)) +

### 2016-06-06 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Fixed a bug in makdNatCoef. with was causing problems for sigma. It picked up the function rather than the variable.

@@
 # ********************************************************
-rerunCESModels=FALSE
-rerunResampling=FALSE
+rerunCESModels <- FALSE
+rerunResampling <- FALSE
 nResamples <- 100 # Number of resamples
@@
   eval=TRUE,
-  include = FALSE,
+  include=FALSE,
   # ********************************************************
@@
   bind_rows() %>%
-  mutate(CSP="w/o CSP")
+  mutate(CSP = "w/o CSP")
 

### 2016-06-06 Articles/Article_EcolEcon_2015/archive/EcolEcon_2015.Rnw
Fixed a bug in makdNatCoef. with was causing problems for sigma. It picked up the function rather than the variable.

@@
 library(knitr)
-library(texreg)
+# library(texreg)
 library(tidyr)
@@
 # ********************************************************
-rerunModels=FALSE
-rerunResampling=FALSE
+rerunModels <- FALSE
+rerunResampling <- FALSE
 nResamples <- 100 # Number of resamples
@@
   # ********************************************************
-  eval=TRUE,
+  eval <- TRUE,
   # ********************************************************

### 2016-06-09 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Text size now 8 points in graphs.

@@
 nResamples <- 100 # Number of resamples
+graph_text_size <- 8 # Points for labels, etc. on graphs.
 # ********************************************************
@@
 
-<<model_points_style>>=
+<<graph_styles>>=
 model_points_style <- function(p) {
@@
   theme(legend.title=element_blank())
+}
+
+graph_text_size_style <- function(p, text_size = 12) {
+  p +
+    theme(
+      text = element_text(size = text_size),
+      axis.text.x = element_text(size = text_size),
+      axis.text.y = element_text(size = text_size),
+      axis.title.x = element_text(size = text_size),
+      axis.title.y = element_text(size = text_size),
+      strip.text.x = element_text(size = text_size),
+      strip.text.y = element_text(size = text_size)
+    ) 
 }
@@
     id_components <- strsplit(id, split = "[.]")[[1]]
-    print(id_components)
+    # print(id_components)
     resamples <- resampledFits(model, method = "wild", n = nResamples)
@@
 <<Resampling-CES-adjusted-kle>>=
-print("Top of Resampling-CES-adjusted-kle")
+# print("Top of Resampling-CES-adjusted-kle")
 
@@
   ylab("Indexed (1960=1)") +
-  xy_theme()
+  xy_theme() %>%
+  graph_text_size_style(graph_text_size)
 @

### 2016-06-09 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Text size now 8 points in graphs.

@@
                     values = c(0.9, 0.9)) +
-  xy_theme()
+  xy_theme() %>%
+  graph_text_size_style(graph_text_size)
 @
@@
 
-  xy_theme()
-
+  xy_theme() %>%
+  graph_text_size_style(graph_text_size)
 @
@@
   labs(color = "Factors of production") +
-  xy_theme()
+  xy_theme() %>%
+  graph_text_size_style(graph_text_size)
 
@@
       axis.ticks.x = element_blank()
-    )
-
+    ) %>%
+  graph_text_size_style(graph_text_size)
 @
@@
   labs(x="", y="") +
-  xy_theme()
-
+  xy_theme() %>%
+  graph_text_size_style(graph_text_size)
 @
@@
 <<resample_graph_lambda_theta, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.5, fig.cap="$\\lambda$ and $\\theta$ values for resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
-standardScatterPlot(data=resampleCoeffsCES, mapping=aes(scale, lambda), facet_formula=~Country, alpha=0.25, size=1, orig_color = "black") +
+p <- standardScatterPlot(data=resampleCoeffsCES, mapping=aes(scale, lambda), facet_formula=~Country, alpha=0.25, size=1, orig_color = "black") +
     scale_x_continuous(breaks=c(0.95, 1.0, 1.05)) + 
@@
     labs(x=expression(theta), y=expression(lambda))
+
+graph_text_size_style(p, graph_text_size)
 @
@@
 <<resample_graph_delta_delta_1, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.5, fig.cap="$\\delta$ and $\\delta_1$ values for resample models that reject the cost share theorem, include energy, use quality-adjusted factors of production, and employ the $(kl)e$ nesting.">>=
-standardScatterPlot(data=resampleCoeffsCES, mapping=aes(delta_1, delta), 
+p <- standardScatterPlot(data=resampleCoeffsCES, mapping=aes(delta_1, delta), 
                     facet_formula=~Country, alpha=0.2, size = 1,
@@
   labs(x=expression(delta[1]), y=expression(delta))
+
+graph_text_size_style(p, graph_text_size)
 @
@@
 
-  xy_theme() 
+  xy_theme() %>%
+  graph_text_size_style(graph_text_size)
 @
@@
   geom_hline(aes(yintercept = 0.0), colour="gray50", size=0.1) + 
-  xy_theme()
+  xy_theme() %>%
+  graph_text_size_style(graph_text_size)
 

### 2016-06-12 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Change to n=1000 for later.

@@
 rerunResampling <- FALSE
-nResamples <- 100 # Number of resamples
+nResamples <- 1000 # Number of resamples
 graph_text_size <- 8 # Points for labels, etc. on graphs.

### 2016-06-12 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Now using alpha = 0.05.

@@
 <<resample_graph_lambda_theta, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.5, fig.cap="$\\lambda$ and $\\theta$ values for resample models that adhere to the cost share theorem, include energy, use quality-adjusted factors of production, and employ the ($kl$)$e$ nesting.">>=
-p <- standardScatterPlot(data=resampleCoeffsCES, mapping=aes(scale, lambda), facet_formula=~Country, alpha=0.25, size=1, orig_color = "black") +
+p <- standardScatterPlot(data=resampleCoeffsCES, mapping=aes(scale, lambda), facet_formula=~Country, alpha=0.05, size=1, orig_color = "black") +
     scale_x_continuous(breaks=c(0.95, 1.0, 1.05)) + 
@@
 p <- standardScatterPlot(data=resampleCoeffsCES, mapping=aes(delta_1, delta), 
-                    facet_formula=~Country, alpha=0.2, size = 1,
+                    facet_formula=~Country, alpha=0.05, size = 1,
                     orig_color="black") +

### 2016-06-12 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
New graph for delta_1 distribution.

@@
 
+<<rho_1-reample-dist-graph>>=
+fancy_scientific <- function(l) {
+     # turn in to character string in scientific notation
+     l <- format(l, scientific = TRUE)
+     # quote the part before the exponent to keep all the digits
+     l <- gsub("^(.*)e", "'\\1'e", l)
+     # turn the 'e+' into plotmath format
+     l <- gsub("e", "%*%10^", l)
+     # return this as an expression
+     parse(text=l)
+}
+
+Rho_1_PT_data <- resampleCoeffsCES %>% 
+  filter(Country == "PT") %>%
+  mutate(
+    delta_1_plot = 1 - delta_1
+  )
+
+ggplot(mapping = aes_string(x = "delta_1_plot")) +
+  geom_density(data = Rho_1_PT_data %>% filter(method != "orig")) +
+  geom_point(data = Rho_1_PT_data %>% filter(method == "orig"), aes(y = 0), shape = 4, size = 6) +
+  scale_x_log10(limits = c(1e-20, 1), breaks = c(1e-20, 1e-15, 1e-10, 1e-5, 1), labels=fancy_scientific) +
+  xlab(expression("1 - "*delta[1])) +
+  xy_theme()
+@
+
 \appendix

### 2016-06-12 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Improved PT resampling graph.

--- 2016-06-12 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
@@
 
+<<rho_1-PT-reample-dist-graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.2, fig.cap="Resampling distribution density plot of $1 - \\delta_1$ for the Portuguese modeling approach that employs the $(kl)e$ nesting, quality-adjusts the factors of production, and rejects the CSP.
+The ``x'' indicates location of base model value.">>=
+fancy_scientific <- function(l) {
+     # turn in to character string in scientific notation
+     l <- format(l, scientific = TRUE)
+     # quote the part before the exponent to keep all the digits
+     l <- gsub("^(.*)e", "'\\1'e", l)
+     # turn the 'e+' into plotmath format
+     l <- gsub("e", "%*%10^", l)
+     # return this as an expression
+     parse(text=l)
+}
+
+Rho_1_PT_data <- resampleCoeffsCES %>% 
+  filter(Country == "PT") %>%
+  mutate(
+    delta_1_plot = 1 - delta_1
+  )
+
+ggplot(mapping = aes_string(x = "delta_1_plot")) +
+  geom_density(data = Rho_1_PT_data %>% filter(method != "orig")) +
+  geom_point(data = Rho_1_PT_data %>% filter(method == "orig"), aes(y = 0), shape = 4, size = 3) +
+  scale_x_log10(limits = c(1e-20, 1), breaks = c(1e-20, 1e-15, 1e-10, 1e-5, 1), labels=fancy_scientific) +
+  xlab(expression("1 - "*delta[1])) +
+  xy_theme() %>%
+  graph_text_size_style(graph_text_size)
+
+@
+
 \appendix

### 2016-06-13 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Better figure caption.

@@
 
-<<rho_1-PT-reample-dist-graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.2, fig.cap="Resampling distribution density plot of $1 - \\delta_1$ for the Portuguese modeling approach that employs the $(kl)e$ nesting, quality-adjusts the factors of production, and rejects the CSP.
+<<rho_1-PT-reample-dist-graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.2, fig.cap="Bootstrap resampling distribution density plot of $1 - \\delta_1$ for the Portuguese modeling approach that employs the $(kl)e$ nesting, quality-adjusts the factors of production, and rejects the CSP.
 The ``x'' indicates location of base model value.">>=

### 2016-06-13 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
bind_rows and bind_cols.

@@
   # Resample coefficients
-  resampleCoeffsCES <- rbind(cbind(resamplesCESPT$coeffs, Country="PT"), cbind(resamplesCESUK$coeffs, Country="UK"))
+  resampleCoeffsCES <- bind_rows(
+    bind_cols(resamplesCESPT$coeffs %>% mutate(Country="PT")), 
+    bind_cols(resamplesCESUK$coeffs %>% mutate(Country="UK")))
   resampleCoeffsCES$energy <- TRUE

### 2016-06-13 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Now will resample.

@@
 # ********************************************************
-rerunCESModels <- FALSE
-rerunResampling <- FALSE
+rerunCESModels <- TRUE
+rerunResampling <- TRUE
 nResamples <- 1000 # Number of resamples

### 2016-06-13 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Now saving models before working on coeffs.

@@
   resamplesCESUK <- resampledFits(modUK, method = "wild", n = nResamples)
+  # Resample models
+  resampleModelsCES <- list(PT=resamplesCESPT$models, UK=resamplesCESUK$models)
+  saveRDS(resampleModelsCES, file = resampleModelsCESFilename)
   # Resample coefficients
@@
   saveRDS(resampleCoeffsCES, file = resampleCoeffsCESFilename)
-  # Resample models
-  resampleModelsCES <- list(PT=resamplesCESPT$models, UK=resamplesCESUK$models)
-  saveRDS(resampleModelsCES, file = resampleModelsCESFilename)
 } else {

### 2016-06-13 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
No longer do resamples.

@@
 # ********************************************************
-rerunCESModels <- TRUE
-rerunResampling <- TRUE
+rerunCESModels <- FALSE
+rerunResampling <- FALSE
 nResamples <- 1000 # Number of resamples

### 2016-06-13 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Made alpha_e gray in resample graph.

@@
     labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
-    values=c("black", "black", "gray70"),
-    guide=FALSE) +
+    values=c("black", "black", "gray70")) +
   scale_size_manual(
@@
     labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
-    values=c(2,3,1) ) +
+    values=c(2,3,1)) +
 

### 2016-06-13 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Uppercase lables. Switch linetypes.

@@
                         labels=c("l", "k"),
-                        values=c(2,3)) + 
+                        values=c(3,2)) + 
   scale_size_manual(name="", 
@@
     name = "",
-    labels = c("historical", "fitted"),
+    labels = c("Historical", "Fitted"),
     values=c("black", "black")
@@
     name = "",
-    labels = c("historical", "fitted"),
+    labels = c("Historical", "Fitted"),
     values = c(0.2, 0.2)) +
@@
     name = "",
-    labels = c("historical", "fitted"),
+    labels = c("Historical", "Fitted"),
     values=c(1,2) ) + 

### 2016-06-16 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Fixed misspelling.

@@
 
-<<rho_1-PT-reample-dist-graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.2, fig.cap="Bootstrap resampling distribution density plot of $1 - \\delta_1$ for the Portuguese modeling approach that employs the $(kl)e$ nesting, quality-adjusts the factors of production, and rejects the CSP.
+<<rho_1-PT-resample-dist-graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.2, fig.cap="Bootstrap resampling distribution density plot of $1 - \\delta_1$ for the Portuguese modeling approach that employs the $(kl)e$ nesting, quality-adjusts the factors of production, and rejects the CSP.
 The ``x'' indicates location of base model value.">>=

### 2016-06-16 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Now 1000 resamples for alpha graph.

@@
     labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
-    values = c(.3, .9),
+    values = c(0.05, 0.9),
     guide = FALSE) +
@@
 ggplot(mapping = aes_string(x = "delta_1_plot")) +
-  geom_density(data = Rho_1_PT_data %>% filter(method != "orig")) +
+  stat_density(data = Rho_1_PT_data %>% filter(method != "orig"), geom = "line") +
   geom_point(data = Rho_1_PT_data %>% filter(method == "orig"), aes(y = 0), shape = 4, size = 3) +
+  geom_hline(aes(yintercept = 0.0), colour="gray50", size=0.1) + 
   scale_x_log10(limits = c(1e-20, 1), breaks = c(1e-20, 1e-15, 1e-10, 1e-5, 1), labels=fancy_scientific) +

### 2016-06-16 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Now saving and loading ReModels. No longer loading and operating on EcolEcon2015kleResampleModelsCES.rds, because it can be a HUGE file, especially with 1000 resamples.

@@
 resampleModelsCESFilename <- "EcolEcon2015kleResampleModelsCES.rds"
+ReModelsFilename <- "ReModels.rds"
 if (rerunResampling){
@@
   resamplesCESUK <- resampledFits(modUK, method = "wild", n = nResamples)
-  # Resample models
+  # Resample model objects
   resampleModelsCES <- list(PT=resamplesCESPT$models, UK=resamplesCESUK$models)
+  # Save this object in case we need to interrogate it later.
+  # Note, however, that resampleModelsCES is NOT in the repository,
+  # because it can be a HUGE file when we're doing, say, 1000 resamples.
   saveRDS(resampleModelsCES, file = resampleModelsCESFilename)
+  # Resample time series
+  ReModels <-
+    bind_rows(
+      leaf_apply(resampleModelsCES, 
+                 function(x,id) {mod2oedf(x, id) %>% mutate(id = id)},
+                 strict.lists = TRUE)
+    )
+  saveRDS(ReModels, file = ReModelsFilename)
   # Resample coefficients
@@
   resampleCoeffsCES <- readRDS(resampleCoeffsCESFilename)
-  resampleModelsCES <- readRDS(resampleModelsCESFilename)
+  # We don't need to load resampelModelsCES, because we use only ReModels later.
+  # resampleModelsCES <- readRDS(resampleModelsCESFilename)
+  ReModels <- readRDS(ReModelsFilename)
 }
@@
 
-<<ReModels>>=
-ReModels <-
-  bind_rows(
-  leaf_apply(resampleModelsCES, 
-             function(x,id) {mod2oedf(x, id) %>% mutate(id = id)},
-             strict.lists = TRUE)
-)
-@
+% <<ReModels>>=
+% # ReModels is the data frame that holds time series of all the resample models.
+% # We save this to disk and include it in the repo, because it is much smaller than resampleModelsCES.
+% if (! rerunResampling){
+%   ReModels <- readRDS(ReModelsFilename)
+% } else {
+%   # This code is expensive, so run only if we re-ran the resampling.
+%   ReModels <-
+%     bind_rows(
+%       leaf_apply(resampleModelsCES, 
+%                  function(x,id) {mod2oedf(x, id) %>% mutate(id = id)},
+%                  strict.lists = TRUE)
+%     )
+% }
+% @
 

### 2016-06-17 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Additional info on PT delta_1 case.

--- 2016-06-16 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
@@
 
-<<rho_1-PT-resample-dist-graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.2, fig.cap="Bootstrap resampling distribution density plot of $1 - \\delta_1$ for the Portuguese modeling approach that employs the $(kl)e$ nesting, quality-adjusts the factors of production, and rejects the CSP.
-The ``x'' indicates location of base model value.">>=
+<<PT-resample-meta, echo = TRUE, include = TRUE>>=
+mod <- models$PT$adjusted$withE$CES$kle
+# mod
+print(mod$coefficients[["delta_1"]], digits = 20)
+1 - mod$coefficients[["delta_1"]]
+
+# Look at SSE of the actual model and the boundary model.
+# First, the actual model:
+sum(resid(mod)^2)
+# Now, the boundary model with delta_1 = 1, namely boundary model 11.
+mod11 <- attr(mod, "model.attempts")[[11]]
+# mod11
+sum(resid(mod11)^2)
+@
+
+<<PT-resample-quantiles, echo = TRUE, include = TRUE>>=
+PTresample <- resampleCoeffsCES %>% filter(Country == "PT", method != "orig")
+any(PTresample$delta_1 >= 1)
+1 - max(PTresample$delta_1)
+range95 <- quantile(PTresample$delta_1, probs=c(0.025, 0.975))
+range95
+1 - range95
+@
+
+<<rho_1-PT-resample-dist-graph, fig.pos="H", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap="Bootstrap resampling density distribution of $1 - \\delta_1$ for the Portuguese modeling approach that employs the $(kl)e$ nesting, quality-adjusts the factors of production, and rejects the CSP.
+The $\\times$ indicates location of base model value.
+Vertical lines show the range of the middle 95\\% of the distribution.">>=
 fancy_scientific <- function(l) {
@@
   geom_hline(aes(yintercept = 0.0), colour="gray50", size=0.1) + 
+  geom_vline(aes(xintercept = 1-range95), colour="gray50", size=0.1) +
   scale_x_log10(limits = c(1e-20, 1), breaks = c(1e-20, 1e-15, 1e-10, 1e-5, 1), labels=fancy_scientific) +

### 2016-06-17 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Adding more information about the PTkle models.

@@
 <<PT-resample-meta, echo = TRUE, include = TRUE>>=
-mod <- models$PT$adjusted$withE$CES$kle
-# mod
-print(mod$coefficients[["delta_1"]], digits = 20)
-1 - mod$coefficients[["delta_1"]]
+PTklemod <- models$PT$adjusted$withE$CES$kle
+# print(summary(PTklemod))
+# The standard error of delta_1
+summary(PTklemod)$coefficients[3, 2]
+print(PTklemod$coefficients[["delta_1"]], digits = 20)
+1 - PTklemod$coefficients[["delta_1"]]
+# Machine precision
+.Machine$double.eps
 
@@
 # First, the actual model:
-sum(resid(mod)^2)
+sum(resid(PTklemod)^2)
 # Now, the boundary model with delta_1 = 1, namely boundary model 11.
-mod11 <- attr(mod, "model.attempts")[[11]]
-# mod11
-sum(resid(mod11)^2)
+PTklemod11 <- attr(PTklemod, "model.attempts")[[11]]
+# print(summary(PTklemod11))
+sum(resid(PTklemod11)^2)
 @
@@
 <<PT-resample-quantiles, echo = TRUE, include = TRUE>>=
-PTresample <- resampleCoeffsCES %>% filter(Country == "PT", method != "orig")
-any(PTresample$delta_1 >= 1)
-1 - max(PTresample$delta_1)
-range95 <- quantile(PTresample$delta_1, probs=c(0.025, 0.975))
-range95
-1 - range95
+PTkleresample <- resampleCoeffsCES %>% filter(Country == "PT", method != "orig")
+any(PTkleresample$delta_1 >= 1)
+1 - max(PTkleresample$delta_1)
+PTklerange95 <- quantile(PTkleresample$delta_1, probs=c(0.025, 0.975))
+PTklerange95
+1 - PTklerange95
 @
@@
   geom_hline(aes(yintercept = 0.0), colour="gray50", size=0.1) + 
-  geom_vline(aes(xintercept = 1-range95), colour="gray50", size=0.1) +
+  geom_vline(aes(xintercept = 1-PTklerange95), colour="gray50", size=0.1) +
   scale_x_log10(limits = c(1e-20, 1), breaks = c(1e-20, 1e-15, 1e-10, 1e-5, 1), labels=fancy_scientific) +

### 2016-06-17 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
New sigma resample graph.

@@
   scale_x_continuous(limits=c(0, 1), breaks=c(0, 0.5, 1)) +
-  scale_y_continuous(limits=c(0,1), breaks=c(0, 0.5, 1)) +
+  scale_y_continuous(limits=c(0, 1), breaks=c(0, 0.5, 1)) +
   labs(x=expression(delta[1]), y=expression(delta))
+
+graph_text_size_style(p, graph_text_size)
+@
+
+<<resample_graph_sigma_sigma_1, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=3.5, fig.cap="$\\sigma$ and $\\sigma_1$ values for resample models that reject the cost share theorem, include energy, use quality-adjusted factors of production, and employ the $(kl)e$ nesting.">>=
+p <- standardScatterPlot(data=resampleCoeffsCES, mapping=aes(sigma_1, sigma), 
+                    facet_formula=~Country, alpha=0.05, size = 1,
+                    orig_color="black") +
+  scale_x_continuous(limits=c(0, 3)) +
+  scale_y_continuous(limits=c(0, 3)) +
+  labs(x=expression(sigma[1]), y=expression(sigma))
 

### 2016-06-17 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
delta_1 = 0.5?

@@
 1 - PTklerange95
+# See if there are any coefficients that are exactly 0.5, the starting value.
+any(resampleCoeffsCES$delta_1 == 0.5)
 @

### 2016-07-21 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Better comment. Deleted unneeded code.
"" --> NULL for xlab.

@@
   # We don't need to load resampelModelsCES, because we use only ReModels later.
+  # But, you can uncomment this line to load an archived file, if desired.
   # resampleModelsCES <- readRDS(resampleModelsCESFilename)
@@
 @
-
-% <<ReModels>>=
-% # ReModels is the data frame that holds time series of all the resample models.
-% # We save this to disk and include it in the repo, because it is much smaller than resampleModelsCES.
-% if (! rerunResampling){
-%   ReModels <- readRDS(ReModelsFilename)
-% } else {
-%   # This code is expensive, so run only if we re-ran the resampling.
-%   ReModels <-
-%     bind_rows(
-%       leaf_apply(resampleModelsCES, 
-%                  function(x,id) {mod2oedf(x, id) %>% mutate(id = id)},
-%                  strict.lists = TRUE)
-%     )
-% }
-% @
 
@@
   scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12), limits=c(0.5, 12)) +
-  xlab("") + 
+  xlab(NULL) + 
   ylab("Indexed (1960=1)") +

### 2016-07-21 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Add sd calc on delta_1.
"" --> NULL for xlab.

@@
   geom_hline(aes(yintercept = 0.7), colour="gray50", size=0.1) +
-  xlab("") +
+  xlab(NULL) +
   scale_x_continuous(breaks=c(1960, 1980, 2000)) +
@@
     geom_hline(yintercept = 0, colour="gray50", size=0.1) +
-    xlab("") +
+    xlab(NULL) +
     ylab(expression(lambda)) +
@@
 # See if there are any coefficients that are exactly 0.5, the starting value.
-any(resampleCoeffsCES$delta_1 == 0.5)
+any(PTkleresample$delta_1 == 0.5)
+# Calculate standard deviation of the delta_1 resampling distribution.
+sd(PTkleresample$delta_1)
 @

### 2016-07-21 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Now making data.frames rather than lists.

@@
   OMTable_exp <- leaf_apply(modelsExp, class="lm", f=function(mod, id){
-    list(Country=id[[1]],
+    data.frame(Country=id[[1]],
          Model = "Ref.",
@@
          lambda_ratio = 1,
-         SSE = sum(resid(mod)^2))
+         SSE = sum(resid(mod)^2), 
+         stringsAsFactors = FALSE)
   }) %>% bind_rows()
@@
   id_components <- strsplit(id, split = "[.]")[[1]]
-  list(Country = id_components[[1]],
+  data.frame(Country = id_components[[1]],
        Model = "CES",
@@
        lambda_ratio = naturalCoef(mod)$lambda / coef(modelsExp[[id_components[[1]]]])[[2]],
-       SSE = sum(resid(mod)^2))
+       SSE = sum(resid(mod)^2),
+       stringsAsFactors = FALSE)
   }) %>% bind_rows()
@@
     adjusted_components <- strsplit(id_components[[2]], "[_]")[[1]]
-    list(Country = id_components[[1]],
+    data.frame(Country = id_components[[1]],
          Model = "CES",
@@
          lambda_ratio = naturalCoef(mod)$lambda / coef(modelsExp[[id_components[[1]]]])[[2]],
-         SSE = sum(resid(mod)^2)
-         )
-
+         SSE = sum(resid(mod)^2),
+         stringsAsFactors = FALSE)
   }) %>% bind_rows()
@@
     )
-
 @
@@
     # Make the LaTeX table
-    myXTable(caption="Solow residual~($\\lambda$) and sum of squared errors~(SSE) for $(kl)e$ models that reject the cost share principle. 
-             $\\lambda / \\lambda_{Ref.}$ is the ratio of Solow residual relative to the reference (exponential-only) model.
+    myXTable(caption="Solow residual~($\\lambda$) and sum of squared errors~(SSE) 
+             for $(kl)e$ models that reject the cost share principle. 
+             $\\lambda / \\lambda_{Ref.}$ is the ratio of Solow residual relative 
+             to the reference (exponential-only) model.
              ``UA'' and ``QA'' indicate unadjusted and quality-adjusted factors of production, respectively.",

### 2016-08-08 NSF-ClusterGrant/EconOnePager.Rmd
add draft one pager for the NSF grant

---
title: "Econ Modeling One-pager"
author: "R Pruim"
date: "August 1, 2016"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Development of energy policy is often informed by economic considerations
via aggregate production functions (APFs) as part of a theory-to-policy
process comprised of six steps:

 1. selecting a theoretical energy-economy framework,
 2. formulating modeling approaches to be considered,
 3. econometrically fitting an APF to historical data,
 4. comparing and evaluating modeling approaches considered,
 5. interpreting the economy, and
 6. formulating economic policy.

Choices made in Steps 1--4
can lead to very different interpretations of the economy in Step 5
and subequently to the justification for different policies in Step 6.
In a recently submitted paper (citation can be provided, if needed),
we investigated these effects
by analyzing data from two countries (Portugal and the United Kingdom) 
using the Constant Elasticity of Substitution~(CES) APF (which subsumes
the familiar Cobb-Douglas models as a special case)
to evaluate four modeling choices:
(a) whether or not to simplify models by employing a certain cost-share principle 
that is often assumed in economic modeling,
(b) whether or not to include energy as a factor of production along with capital and labor,
(c) whether or not to make certain quality adjustments to factors of production in an
attempt to better quantify their impact on the economy, and 
(d) which CES nesting structure to use for models with three factors of production.

This paper includes a discussion of two revealing examples for which different
upstream modeling choices lead to very different policies. In the first example,
the $(kl)e$ nesting structure implies significant investment in energy, while
other nesting structures suggest otherwise. In the second example, unadjusted
factors of production suggest balanced investment in labor and energy, while 
quality-adjusting suggests significant investment in labor over energy. 
Divergent outcomes provide cautionary tales for policymakers and demand
greater understanding of upstream modeling choices and 
their downstream implications.

One challenge in this work is the computational difficulty involved in fitting CES models 
and quantifying the precision of the estimated parameters that result.  Because of 
numerical challenges, we fit each model with multiple non-linear optimization algorithms,
and because of boundary issues, we explicity refit models along boundaries.  Then, because
parameter precision is challenging to estimate using standard methods, we employ 
computationally intensive resampling and/or Bayesian models.  Our current exploration
is a sort of pilot study considering a limited number of countries, a limited number of 
modeling choices and reducing the number of resamples to an amount that can be readily handled 
on our current hardware in a few hours.  Further work in this area, especially any simulations
to explore the quality of the bootstrap resampling or Bayesian estimation, would require days 
to run currently.
Futhermore, we already have data from several additional countries that we would like to
anaylze by similar methods.

**Additional paragraph here** (when Matt returns to radio contact) about future related 
integrating the paper described above with cointegration work that Tiago has done.  [Tiago is
a possible letter writer, so this makes a nice connection between the grant proposal and his
letter, and also demonstrates its usefulness for things being done beyond Calvin.]

### 2016-08-08 NSF-ClusterGrant/EconOnePager.Rmd
add bib item for Energy Policy paper

@@
 output:
-  word_document: default
   pdf_document: default
   html_document: default
+  word_document: default
+bibliography: OnePager.bib
 ---
@@
 and subequently to the justification for different policies in Step 6.
-In a recently submitted paper (citation can be provided, if needed),
-we investigated these effects
+In a recently submitted paper [@Heun:2016] we investigated these effects
 by analyzing data from two countries (Portugal and the United Kingdom) 
@@
 letter, and also demonstrates its usefulness for things being done beyond Calvin.]
+
+# References

### 2016-08-08 NSF-ClusterGrant/EconOnePager.Rmd
New paragraph.

--- 2016-08-08 NSF-ClusterGrant/EconOnePager.Rmd
@@
 and because of boundary issues, we explicity refit models along boundaries.  Then, because
-parameter precision is challenging to estimate using standard methods, we employ 
+estimating parameter precision is challenging using standard methods, we employ 
 computationally intensive resampling and/or Bayesian models.  Our current exploration
@@
 modeling choices and reducing the number of resamples to an amount that can be readily handled 
-on our current hardware in a few hours.  Further work in this area, especially any simulations
-to explore the quality of the bootstrap resampling or Bayesian estimation, would require days 
-to run currently.
-Futhermore, we already have data from several additional countries that we would like to
-anaylze by similar methods.
+on our current hardware in a few hours.
+
+Our plans for future work will require significantly-improved computational capabilities.
+Each of our planned activities below will require days to run on existing hardware.
+
+* We have in hand data from several additional countries that we would like to
+anaylze by similar methods as discussed above.
+
+* We want to explore the quality and performance
+of the bootstrap resampling and/or Bayesian estimation techniques.
+
+* Our collaborators in Portugal have completed a paper that uses the 
+Cobb-Douglas APF in combination with co-integration techniques to understand
+the relationship between energy and the economy in Portugal. 
+At the Second Exergy Economics Workshop (Sussex, England)
 

### 2016-08-08 NSF-ClusterGrant/EconOnePager.Rmd
expanded intro with references.

--- 2016-08-08 NSF-ClusterGrant/EconOnePager.Rmd
@@
 
+Development of energy and economic policy is often informed 
+by energy-economic modeling via aggregate production functions (APFs) fitted
+to historical data in a theory-to-policy process utilized 
+in the literature [@Kummel:1985vz, @Turner:2012], 
+in government budget offices [@Congressional-Budget-Office:2001], and
+at the World Bank [@Bussolo:2010].
+Despite more than 60 years of criticism
+[@robinson1953production, shaikh1974laws, felipe2003aggregation], 
+the use of APFs continues and appears to be expanding, 
+with APFs moving from academic study
+[@solow1957technical, @easterly1995soviet] 
+to macroeconomic modeling that informs energy and economic policy
+[@szeto2001econometric, @pauw2003functional, @sancho2009calibration].
+Empirical applications of APFs
+are numerous, including analysis of 
+(a) technical change [@jorgenson1967explanation], 
+(b) substitution elasticities [@kemfert2000energy],
+(c) inter-country economic output 
+	and structure [@easterly1995soviet, @toh1996differential], and 
+(d) CO$_2$ emissions policy [@van2008production].
+One reason for the enduring allure of APFs is
+their promise to describe the intricate, complex 
+workings of entire economies by simple, aggregated measures
+of inputs (capital, labor, and sometimes energy) 
+and output (typically, Gross Domestic Product, GDP).
+
+The theory-to-policy process is not merely academic: 
+the policies it generates affect economic development and 
+quality of life for people worldwide.
 Development of energy policy is often informed by economic considerations

### 2016-08-08 NSF-ClusterGrant/EconOnePager.Rmd
Edited one-pager.

@@
 
-* Our collaborators in Portugal have completed a paper that uses the 
-Cobb-Douglas APF in combination with co-integration techniques to understand
-the relationship between energy and the economy in Portugal. 
-At the Second Exergy Economics Workshop (Sussex, England)
-
-**Additional paragraph here** (when Matt returns to radio contact) about future related 
-integrating the paper described above with cointegration work that Tiago has done.  [Tiago is
-a possible letter writer, so this makes a nice connection between the grant proposal and his
-letter, and also demonstrates its usefulness for things being done beyond Calvin.]
+* Our collaborators in Portugal have completed a paper that employs the 
+Cobb-Douglas APF in combination with statistical co-integration techniques to understand
+the relationship between energy and the economy in Portugal [@jsantos2016]. 
+Their next step is to switch from the Cobb-Douglas APF to the CES APF.
+At the Second Exergy Economics Workshop (Sussex, England, July 2016), 
+we made plans to collaborate. 
+Our CES fitting techniques and resampling methods
+will be applied to their cointegration analysis
+to write a new paper analyzing the Portuguese economy.
 

### 2016-08-08 NSF-ClusterGrant/EconOnePager.Rmd
update references

--- 2016-08-08 NSF-ClusterGrant/EconOnePager.Rmd
@@
 output:
-  pdf_document: default
+  pdf_document: 
+    keep_tex: yes
   html_document: default
@@
 Despite more than 60 years of criticism
-[@robinson1953production, shaikh1974laws, felipe2003aggregation], 
+[@robinson1953production, @shaikh1974laws, @felipe2003aggregation], 
 the use of APFs continues and appears to be expanding, 
@@
 and because of boundary issues, we explicity refit models along boundaries.  Then, because
-estimating parameter precision is challenging using standard methods, we employ 
+parameter precision is challenging to estimate using standard methods, we employ 
 computationally intensive resampling and/or Bayesian models.  Our current exploration
@@
 modeling choices and reducing the number of resamples to an amount that can be readily handled 
-on our current hardware in a few hours.
-
-Our plans for future work will require significantly-improved computational capabilities.
-Each of our planned activities below will require days to run on existing hardware.
-
-* We have in hand data from several additional countries that we would like to
-anaylze by similar methods as discussed above.
-
-* We want to explore the quality and performance
-of the bootstrap resampling and/or Bayesian estimation techniques.
-
-* Our collaborators in Portugal have completed a paper that uses the 
-Cobb-Douglas APF in combination with co-integration techniques to understand
-the relationship between energy and the economy in Portugal. 
-At the Second Exergy Economics Workshop (Sussex, England)
+on our current hardware in a few hours.  Further work in this area, especially any simulations
+to explore the quality of the bootstrap resampling or Bayesian estimation, would require days 
+to run currently.
+Futhermore, we already have data from several additional countries that we would like to
+anaylze by similar methods.
 

### 2016-08-08 NSF-ClusterGrant/EconOnePager.Rmd
ieee formatting, 3rd person

@@
 bibliography: OnePager.bib
+csl: ieee.csl
 ---
@@
 and subequently to the justification for different policies in Step 6.
-In a recently submitted paper [@Heun:2016] we investigated these effects
+In a recently submitted paper [@Heun:2016], Drs. Heun and Pruim and co-authors 
+investigated these effects
 by analyzing data from two countries (Portugal and the United Kingdom) 
-using the Constant Elasticity of Substitution~(CES) APF (which subsumes
+using the Constant Elasticity of Substitution (CES) APF (which subsumes
 the familiar Cobb-Douglas models as a special case)

### 2016-08-08 NSF-ClusterGrant/EconOnePager.Rmd
Edits.

@@
 modeling choices and reducing the number of resamples to an amount that can be readily handled 
-on our current hardware in a few hours.  Further work in this area, especially any simulations
-to explore the quality of the bootstrap resampling or Bayesian estimation, would require days 
-to run currently.
-Futhermore, we already have data from several additional countries that we would like to
-anaylze by similar methods.
+on our current hardware in a few hours.
 
-**Additional paragraph here** (when Matt returns to radio contact) about future related 
-integrating the paper described above with cointegration work that Tiago has done.  [Tiago is
-a possible letter writer, so this makes a nice connection between the grant proposal and his
-letter, and also demonstrates its usefulness for things being done beyond Calvin.]
+Our plans for future work will require significantly-improved computational capabilities.
+Each of our planned activities below will require days to run on existing hardware.
+
+* We have in hand data from several additional countries that we would like to
+anaylze by similar methods as discussed above.
+
+* We want to explore the quality and performance
+of the bootstrap resampling and/or Bayesian estimation techniques.
+
+* Our collaborators in Portugal have completed a paper that employs the 
+Cobb-Douglas APF in combination with statistical co-integration techniques to understand
+the relationship between energy and the economy in Portugal [@jsantos2016]. 
+Their next step is to switch from the Cobb-Douglas APF to the CES APF.
+At the Second Exergy Economics Workshop (Sussex, England, July 2016), 
+we made plans to collaborate. 
+Our CES fitting techniques and resampling methods
+will be applied to their cointegration analysis
+to write a new paper analyzing the Portuguese economy.
 

### 2016-08-08 NSF-ClusterGrant/EconOnePager.Rmd
MKH edits on one-pager.

@@
 and subequently to the justification for different policies in Step 6.
-In a recently submitted paper [@Heun:2016], Drs. Heun and Pruim and co-authors 
+In a recently submitted paper [@Heun:2016], Drs.\ Heun and Pruim and co-authors 
 investigated these effects
@@
 Our plans for future work will require significantly-improved computational capabilities.
-Each of our planned activities below will require days to run on existing hardware.
+Each of the planned activities below will require days to run on existing hardware.
+An enhanced cluster computing capability at Calvin College will 
+enable expansion of this research into several new areas
+and enable collaboration with international colleagues.
 
@@
 will be applied to their cointegration analysis
-to write a new paper analyzing the Portuguese economy.
+to develop the data for new paper analyzing the Portuguese economy.
 

### 2017-01-19 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Demo of indexing.

@@
     name = "",
-    labels = c("Historical", "Fitted"),
+    labels = c("Fitted", "Historical"),
     values=c("black", "black")
@@
     name = "",
-    labels = c("Historical", "Fitted"),
+    labels = c("Fitted", "Historical"),
     values = c(0.2, 0.2)) +
@@
     name = "",
-    labels = c("Historical", "Fitted"),
+    labels = c("Fitted", "Historical"),
     values=c(1,2) ) + 

### 2017-01-19 Articles/Brockway_Landscape_2017/Indexing_Demo.Rnw
Demo of indexing.

\documentclass{article}

\begin{document}

\title{Demonstration of Effect of Indexing on\\
Cobb-Douglas and CES\\
Aggregate Production Functions}
\author{Matthew Kuperus Heun}
\maketitle

<<setup, include=FALSE>>=
library(EconModels)
library(dplyr)
library(tidyr)
library(ggplot2)

opts_chunk$set(
  # ********************************************************
  eval = TRUE,
  include = TRUE,
  echo = TRUE
  # ********************************************************
)
@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Models} 
\label{sec:models}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

For demonstration purposes, 
we focus on models that assume capital and labor factors of production only.

%++++++++++++++++++++++++++++++
\subsection{Raw historical data} 
\label{sec:raw}
%++++++++++++++++++++++++++++++

The Cobb-Douglas model for using raw historical data is given by 
%
\begin{equation} \label{eq:CD_model_nonindexed}
  Y = \theta \: \mathrm{e}^{\lambda t} \: K^{\alpha_k} \, L^{\alpha_l} \; ,
\end{equation}
%
where $Y$, $K$, and $L$ are the raw (non-indexed) time series.
Time ($t$) is indexed by difference to the intial year (1960).

The CES model with raw historical data is given by
%
\begin{equation} \label{eq:CESkl_nonindexed}
  Y = \gamma \: \mathrm{e}^{\lambda t} \left[\delta K^{-\rho}
      + (1-\delta)L^{-\rho} \right]^{-1/\rho} \; .
\end{equation}

%++++++++++++++++++++++++++++++
\subsection{Indexed factors of production} 
\label{sec:indexed}
%++++++++++++++++++++++++++++++

The Cobb-Douglas model indexed historical data is given by
%
\begin{equation} \label{eq:CD_model}
  y = \theta \: \mathrm{e}^{\lambda t} \: k^{\alpha_k} \, l^{\alpha_l} \; ,
\end{equation}
%
where $y$, $k$, and $l$ are indexed by ratio to the initial year (1960). 
For example,
%
\begin{equation} \label{eq:indexing}
  y = Y/Y_{1960} \; .
\end{equation}

The CES model with indexed historical data is given by 
%
\begin{equation} \label{eq:CESkl}
  y = \gamma \: \mathrm{e}^{\lambda t} \left[\delta k^{-\rho}
      + (1-\delta)l^{-\rho} \right]^{-1/\rho} \; .
\end{equation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data} 
\label{sec:data}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

All data are from the Penn World Table.
Figure~\ref{fig:GDP-graph} below shows historical data as dots.

<<load-data>>=
UKdata <- read.csv(file.path("data", "IndexingDemoRawData.csv"))
@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Fitting} 
\label{sec:fitting}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Next, we fit both the Cobb-Douglas and CES aggregate production functions 
to both indexed and non-indexed data.
Figure~\ref{fig:GDP-graph} below shows historical data as lines.

<<fitting, warning=FALSE>>=
cd_nonindexed <- cdModel(GDP ~ K + L + iYear, data = UKdata)
cd_indexed <- cdModel(iGDP ~ iK + iL + iYear, data = UKdata)
ces_nonindexed <- cesModel(GDP ~ K + L + iYear, data = UKdata)
ces_indexed <- cesModel(iGDP ~ iK + iL + iYear, data = UKdata)
@

<<quadplot-data-frame, echo = FALSE>>=
quadplotdata <- UKdata %>% 
  mutate(
    yhat_cd_nonindexed = yhat(cd_nonindexed),
    yhat_cd_indexed = yhat(cd_indexed),
    yhat_ces_nonindexed = yhat(ces_nonindexed),
    yhat_ces_indexed = yhat(ces_indexed),
    Country = NULL,
    K = NULL,
    iK = NULL,
    L = NULL,
    iL = NULL
  )
# Eliminate attributes to avoid warning.
attr(quadplotdata$yhat_cd_nonindexed, "label") <- NULL
attr(quadplotdata$yhat_cd_indexed, "label") <- NULL
# Prepare format for quad plot
quadplotdata <- quadplotdata %>% 
  gather(key = variable, value = y_hat, 
         yhat_cd_nonindexed, yhat_cd_indexed, 
         yhat_ces_nonindexed, yhat_ces_indexed) %>% 
  mutate(
    y_historical = 
      case_when(
        .$variable %in% c("yhat_cd_nonindexed", "yhat_ces_nonindexed") ~ .$GDP,
        .$variable %in% c("yhat_cd_indexed", "yhat_ces_indexed")       ~ .$iGDP
      ),
    GDP = NULL, 
    iGDP = NULL,
    indexed = case_when(
        .$variable %in% c("yhat_cd_nonindexed", "yhat_ces_nonindexed") ~ "raw",
        .$variable %in% c("yhat_cd_indexed", "yhat_ces_indexed")       ~ "indexed"
    ),
    indexed = factor(indexed, c("raw", "indexed")),
    apf = case_when(
        .$variable %in% c("yhat_cd_nonindexed", "yhat_cd_indexed")     ~ "CD",
        .$variable %in% c("yhat_ces_nonindexed", "yhat_ces_indexed")   ~ "CES"
    )
  )
@

We graph each type of fitted model against historical data.
Note that all models provide excellent fits.

<<GDP-graph, fig.align="center", fig.width=6.5, fig.height=5, fig.cap="Fits to historical data. Dots are historical data. Lines are fits.">>=
ggplot(data = quadplotdata, mapping = aes_string(x = "Year")) + 
  geom_point(mapping = aes_string(y = "y_historical"), 
             size = 0.2) + 
  geom_line(mapping = aes_string(y = "y_hat")) + 
  facet_grid(indexed ~ apf, scales = "free") + 
  xlab(NULL) +
  ylab("GDP [raw: millions 2005$, indexed: 1960 = 1]") +
  xy_theme()
@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Coefficients} 
\label{sec:coefficients}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%++++++++++++++++++++++++++++++
\subsection{Cobb-Douglas} 
\label{sec:cd_coeffs}
%++++++++++++++++++++++++++++++

Here are the coefficients for the Cobb-Douglas models.
<<cd-coeffs>>=
cd_nonindexed
cd_indexed
@

Note that the fitted parameters 
output elasticity
\verb+alpha_1+ ($\alpha_k$) 
and 
Solow residual growth rate
\verb+lambda+
are identical,
regardless of whether the historical data are indexed or not.

The pre-multiplier (in this case \texttt{logscale})
accounts for the fact that historical data have been indexed.
We can convert \texttt{logscale} to $\theta$ as follows:

<<cd-logscale-to-theta>>=
exp(cd_nonindexed$coefficients[["logscale"]])
exp(cd_indexed$coefficients[["logscale"]])
@

Note that $\theta$ for the indexed model is near 1.0, as expected.

%++++++++++++++++++++++++++++++
\subsection{CES}
\label{sec:ces_coeffs}
%++++++++++++++++++++++++++++++

The following shows parameters for CES models
fitted to non-indexed and indexed historical data.

<<ces-coeffs>>=
ces_nonindexed
ces_indexed
@

As expected, and similar to the Cobb-Douglas model,
the growth rate of the Solow residual
(\verb+gamma+)
is identical, regardless of whether the historical data are indexed or not.
Again, similar to the Cobb-Douglas model, 
the pre-multiplier term
(in this case \verb+gamma+)
is different depending upon whether the historical data were indexed or not.
We note that the value of \verb+gamma+ is close to 1,
when fitting to indexed data,
as expected.
Furthermore, the elasticity of substitution parameters
(\verb+rho+)
are identical regardless of whether the historical data are indexed or not.

However, the share parameter
(\verb+delta+)
varies significantly, depending upon whether 
the historical data are indexed.
Any inferences about the economy that depend upon the share parameter (\verb+delta+)
will be significantly different depending upon whether the 
historical data are indexed prior to fitting.

\end{document}

### 2017-01-19 Articles/Brockway_Landscape_2017/Indexing_Demo.tex
Demo of indexing.

\documentclass{article}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

\title{Demonstration of Effect of Indexing on\\
Cobb-Douglas and CES\\
Aggregate Production Functions}
\author{Matthew Kuperus Heun}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Models} 
\label{sec:models}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

For demonstration purposes, 
we focus on models that assume capital and labor factors of production only.

%++++++++++++++++++++++++++++++
\subsection{Raw historical data} 
\label{sec:raw}
%++++++++++++++++++++++++++++++

The Cobb-Douglas model for using raw historical data is given by 
%
\begin{equation} \label{eq:CD_model_nonindexed}
  Y = \theta \: \mathrm{e}^{\lambda t} \: K^{\alpha_k} \, L^{\alpha_l} \; ,
\end{equation}
%
where $Y$, $K$, and $L$ are the raw (non-indexed) time series.
Time ($t$) is indexed by difference to the intial year (1960).

The CES model with raw historical data is given by
%
\begin{equation} \label{eq:CESkl_nonindexed}
  Y = \gamma \: \mathrm{e}^{\lambda t} \left[\delta K^{-\rho}
      + (1-\delta)L^{-\rho} \right]^{-1/\rho} \; .
\end{equation}

%++++++++++++++++++++++++++++++
\subsection{Indexed factors of production} 
\label{sec:indexed}
%++++++++++++++++++++++++++++++

The Cobb-Douglas model indexed historical data is given by
%
\begin{equation} \label{eq:CD_model}
  y = \theta \: \mathrm{e}^{\lambda t} \: k^{\alpha_k} \, l^{\alpha_l} \; ,
\end{equation}
%
where $y$, $k$, and $l$ are indexed by ratio to the initial year (1960). 
For example,
%
\begin{equation} \label{eq:indexing}
  y = Y/Y_{1960} \; .
\end{equation}

The CES model with indexed historical data is given by 
%
\begin{equation} \label{eq:CESkl}
  y = \gamma \: \mathrm{e}^{\lambda t} \left[\delta k^{-\rho}
      + (1-\delta)l^{-\rho} \right]^{-1/\rho} \; .
\end{equation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data} 
\label{sec:data}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

All data are from the Penn World Table.
Figure~\ref{fig:GDP-graph} below shows historical data as dots.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{UKdata} \hlkwb{<-} \hlkwd{read.csv}\hlstd{(}\hlkwd{file.path}\hlstd{(}\hlstr{"data"}\hlstd{,} \hlstr{"IndexingDemoRawData.csv"}\hlstd{))}
\end{alltt}
\end{kframe}
\end{knitrout}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Fitting} 
\label{sec:fitting}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Next, we fit both the Cobb-Douglas and CES aggregate production functions 
to both indexed and non-indexed data.
Figure~\ref{fig:GDP-graph} below shows historical data as lines.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{cd_nonindexed} \hlkwb{<-} \hlkwd{cdModel}\hlstd{(GDP} \hlopt{~} \hlstd{K} \hlopt{+} \hlstd{L} \hlopt{+} \hlstd{iYear,} \hlkwc{data} \hlstd{= UKdata)}
\hlstd{cd_indexed} \hlkwb{<-} \hlkwd{cdModel}\hlstd{(iGDP} \hlopt{~} \hlstd{iK} \hlopt{+} \hlstd{iL} \hlopt{+} \hlstd{iYear,} \hlkwc{data} \hlstd{= UKdata)}
\hlstd{ces_nonindexed} \hlkwb{<-} \hlkwd{cesModel}\hlstd{(GDP} \hlopt{~} \hlstd{K} \hlopt{+} \hlstd{L} \hlopt{+} \hlstd{iYear,} \hlkwc{data} \hlstd{= UKdata)}
\hlstd{ces_indexed} \hlkwb{<-} \hlkwd{cesModel}\hlstd{(iGDP} \hlopt{~} \hlstd{iK} \hlopt{+} \hlstd{iL} \hlopt{+} \hlstd{iYear,} \hlkwc{data} \hlstd{= UKdata)}
\end{alltt}
\end{kframe}
\end{knitrout}

We graph each type of fitted model against historical data.
Note that all models provide excellent fits.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{ggplot}\hlstd{(}\hlkwc{data} \hlstd{= quadplotdata,} \hlkwc{mapping} \hlstd{=} \hlkwd{aes_string}\hlstd{(}\hlkwc{x} \hlstd{=} \hlstr{"Year"}\hlstd{))} \hlopt{+}
  \hlkwd{geom_point}\hlstd{(}\hlkwc{mapping} \hlstd{=} \hlkwd{aes_string}\hlstd{(}\hlkwc{y} \hlstd{=} \hlstr{"y_historical"}\hlstd{),}
             \hlkwc{size} \hlstd{=} \hlnum{0.2}\hlstd{)} \hlopt{+}
  \hlkwd{geom_line}\hlstd{(}\hlkwc{mapping} \hlstd{=} \hlkwd{aes_string}\hlstd{(}\hlkwc{y} \hlstd{=} \hlstr{"y_hat"}\hlstd{))} \hlopt{+}
  \hlkwd{facet_grid}\hlstd{(indexed} \hlopt{~} \hlstd{apf,} \hlkwc{scales} \hlstd{=} \hlstr{"free"}\hlstd{)} \hlopt{+}
  \hlkwd{xlab}\hlstd{(}\hlkwa{NULL}\hlstd{)} \hlopt{+}
  \hlkwd{ylab}\hlstd{(}\hlstr{"GDP [raw: millions 2005$, indexed: 1960 = 1]"}\hlstd{)} \hlopt{+}
  \hlkwd{xy_theme}\hlstd{()}
\end{alltt}
\end{kframe}\begin{figure}

{\centering \includegraphics[width=\maxwidth]{figure/GDP-graph-1}

}

\caption[Fits to historical data]{Fits to historical data. Dots are historical data. Lines are fits.}\label{fig:GDP-graph}
\end{figure}

\end{knitrout}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Coefficients} 
\label{sec:coefficients}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%++++++++++++++++++++++++++++++
\subsection{Cobb-Douglas} 
\label{sec:cd_coeffs}
%++++++++++++++++++++++++++++++

Here are the coefficients for the Cobb-Douglas models.
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{cd_nonindexed}
\end{alltt}
\begin{verbatim}
## Generalized least squares fit by REML
##   Model: log(GDP) - log(L) ~ I(log(K) - log(L)) + iYear 
##   Data: sdata 
##   Log-restricted-likelihood: 107.8529
## 
## Coefficients:
##    logscale     alpha_1      lambda 
## -5.37466764  0.56178381  0.01019556 
## 
## Degrees of freedom: 52 total; 49 residual
## Residual standard error: 0.02369495
\end{verbatim}
\begin{alltt}
\hlstd{cd_indexed}
\end{alltt}
\begin{verbatim}
## Generalized least squares fit by REML
##   Model: log(iGDP) - log(iL) ~ I(log(iK) - log(iL)) + iYear 
##   Data: sdata 
##   Log-restricted-likelihood: 107.8529
## 
## Coefficients:
##     logscale      alpha_1       lambda 
## -0.002331844  0.561783810  0.010195560 
## 
## Degrees of freedom: 52 total; 49 residual
## Residual standard error: 0.02369495
\end{verbatim}
\end{kframe}
\end{knitrout}

Note that the fitted parameters 
output elasticity
\verb+alpha_1+ ($\alpha_k$) 
and 
Solow residual growth rate
\verb+lambda+
are identical,
regardless of whether the historical data are indexed or not.

The pre-multiplier (in this case \texttt{logscale})
accounts for the fact that historical data have been indexed.
We can convert \texttt{logscale} to $\theta$ as follows:

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{exp}\hlstd{(cd_nonindexed}\hlopt{$}\hlstd{coefficients[[}\hlstr{"logscale"}\hlstd{]])}
\end{alltt}
\begin{verbatim}
## [1] 0.004632458
\end{verbatim}
\begin{alltt}
\hlkwd{exp}\hlstd{(cd_indexed}\hlopt{$}\hlstd{coefficients[[}\hlstr{"logscale"}\hlstd{]])}
\end{alltt}
\begin{verbatim}
## [1] 0.9976709
\end{verbatim}
\end{kframe}
\end{knitrout}

Note that $\theta$ for the indexed model is near 1.0, as expected.

%++++++++++++++++++++++++++++++
\subsection{CES}
\label{sec:ces_coeffs}
%++++++++++++++++++++++++++++++

The following shows parameters for CES models
fitted to non-indexed and indexed historical data.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{ces_nonindexed}
\end{alltt}
\begin{verbatim}
## Estimated CES function
## 
## Call:
## cesEst(yName = "GDP", xNames = c("K", "L"), data = data, tName = "iYear", 
##     method = "PORT", start = c(0.0078125108214483, 0.00583042323510128, 
##     0.484469079677766, 0.1), lower = NULL, upper = NULL, multErr = TRUE, 
##     control = list(iter.max = 2000, eval.max = 2000))
## 
## Coefficients:
##     gamma    lambda     delta       rho 
## 2.047e-05 1.784e-02 2.855e-06 1.200e+00 
## 
## Elasticity of Substitution: 0.4546
\end{verbatim}
\begin{alltt}
\hlstd{ces_indexed}
\end{alltt}
\begin{verbatim}
## Estimated CES function
## 
## Call:
## cesEst(yName = "iGDP", xNames = c("iK", "iL"), data = data, tName = "iYear", 
##     method = "PORT", start = c(0.980366854292426, 0.0169427187219337, 
##     0.509982506947314, 1), lower = NULL, upper = NULL, multErr = TRUE, 
##     control = list(iter.max = 2000, eval.max = 2000))
## 
## Coefficients:
##   gamma  lambda   delta     rho 
## 0.97753 0.01784 0.50893 1.19979 
## 
## Elasticity of Substitution: 0.4546
\end{verbatim}
\end{kframe}
\end{knitrout}

As expected, and similar to the Cobb-Douglas model,
the growth rate of the Solow residual
(\verb+gamma+)
is identical, regardless of whether the historical data are indexed or not.
Again, similar to the Cobb-Douglas model, 
the pre-multiplier term
(in this case \verb+gamma+)
is different depending upon whether the historical data were indexed or not.
We note that the value of \verb+gamma+ is close to 1,
when fitting to indexed data,
as expected.
Furthermore, the elasticity of substitution parameters
(\verb+rho+)
are identical regardless of whether the historical data are indexed or not.

However, the share parameter
(\verb+delta+)
varies significantly, depending upon whether 
the historical data are indexed.
Any inferences about the economy that depend upon the share parameter (\verb+delta+)
will be significantly different depending upon whether the 
historical data are indexed prior to fitting.

\end{document}

### 2017-01-19 NSF-ClusterGrant/EconOnePager.Rmd

@@
 output:
+  html_document: default
   pdf_document:
     keep_tex: yes
-  html_document: default
   word_document: default
+csl: ieee.csl
 bibliography: OnePager.bib
-csl: ieee.csl
 ---
@@
 to historical data in a theory-to-policy process utilized 
-in the literature [@Kummel:1985vz, @Turner:2012], 
+in the literature [@Kummel:1985vz; @Turner:2012], 
 in government budget offices [@Congressional-Budget-Office:2001], and
 at the World Bank [@Bussolo:2010].
-Despite more than 60 years of criticism
-[@robinson1953production, @shaikh1974laws, @felipe2003aggregation], 
-the use of APFs continues and appears to be expanding, 
-with APFs moving from academic study
-[@solow1957technical, @easterly1995soviet] 
-to macroeconomic modeling that informs energy and economic policy
-[@szeto2001econometric, @pauw2003functional, @sancho2009calibration].
-Empirical applications of APFs
-are numerous, including analysis of 
+Applications of APFs are numerous, including analysis of 
 (a) technical change [@jorgenson1967explanation], 
 (b) substitution elasticities [@kemfert2000energy],
-(c) inter-country economic output 
-	and structure [@easterly1995soviet, @toh1996differential], and 
+(c) inter-country economic output and structure [@easterly1995soviet; @toh1996differential], and 
 (d) CO$_2$ emissions policy [@van2008production].
@@
 
-The theory-to-policy process is not merely academic: 
-the policies it generates affect economic development and 
-quality of life for people worldwide.
 Development of energy policy is often informed by economic considerations
@@
 process comprised of six steps:
-
- 1. selecting a theoretical energy-economy framework,
- 2. formulating modeling approaches to be considered,
- 3. econometrically fitting an APF to historical data,
- 4. comparing and evaluating modeling approaches considered,
- 5. interpreting the economy, and
+1. selecting a theoretical energy-economy framework;
+2. formulating modeling approaches to be considered;
+3. econometrically fitting an APF to historical data;
+4. comparing and evaluating modeling approaches considered;
+5. interpreting the economy; and
 6. formulating economic policy.
@@
 (d) which CES nesting structure to use for models with three factors of production.
-
-This paper includes a discussion of two revealing examples for which different
-upstream modeling choices lead to very different policies. In the first example,
-the $(kl)e$ nesting structure implies significant investment in energy, while
-other nesting structures suggest otherwise. In the second example, unadjusted
-factors of production suggest balanced investment in labor and energy, while 
-quality-adjusting suggests significant investment in labor over energy. 
-Divergent outcomes provide cautionary tales for policymakers and demand
+[@Heun:2016] includes a discussion of two revealing examples for which different
+upstream modeling choices lead to very different policies. 
+*Divergent outcomes provide cautionary tales for policymakers and demand
 greater understanding of upstream modeling choices and 
-their downstream implications.
+their downstream implications.*
 
@@
 estimating parameter precision is challenging using standard methods, we employ 
-computationally intensive resampling and/or Bayesian models.  Our current exploration
-is a sort of pilot study considering a limited number of countries, a limited number of 
-modeling choices and reducing the number of resamples to an amount that can be readily handled 
-on our current hardware in a few hours.
+computationally intensive resampling and/or Bayesian models.  *Our current exploration
+forms a pilot study considering a limited number of countries, a limited number of 
+modeling choices and reducing the number of resamples to an amount that can be readily 
+handled on our current hardware in a few hours.*
 
-Our plans for future work will require significantly-improved computational capabilities.
-Each of the planned activities below will require days to run on existing hardware.
-An enhanced cluster computing capability at Calvin College will 
+Plans for future work will be even more computationally intensive than the work
+done to date.
+*An enhanced cluster computing capability at Calvin College will 
 enable expansion of this research into several new areas
-and enable collaboration with international colleagues.
+and enable collaboration with international colleagues.*
 
-* We have in hand data from several additional countries that we would like to
-anaylze by similar methods as discussed above.
+ 1. Drs. Heun and Pruim have in hand data from several additional countries that they 
+ would like to anaylze by similar methods as discussed above.
 
-* We want to explore the quality and performance
-of the bootstrap resampling and/or Bayesian estimation techniques.
+ 2. Collaborators in Portugal have completed a paper that employs the 
+Cobb-Douglas APF in combination with statistical co-integration techniques 
+to understand the relationship between energy and the economy in 
+Portugal [@jsantos2016].  
+At the Second Exergy Economics Workshop (Sussex, England, July 2016), 
+plans were made to collaborate with them to generalize this to the CES APF
+using techniques from [@Heun:2016].
 
-* Our collaborators in Portugal have completed a paper that employs the 
-Cobb-Douglas APF in combination with statistical co-integration techniques to understand
-the relationship between energy and the economy in Portugal [@jsantos2016]. 
-Their next step is to switch from the Cobb-Douglas APF to the CES APF.
-At the Second Exergy Economics Workshop (Sussex, England, July 2016), 
-we made plans to collaborate. 
-Our CES fitting techniques and resampling methods
-will be applied to their cointegration analysis
-to develop the data for new paper analyzing the Portuguese economy.
+ 3. The use of bootstrapping and Bayesian methods to esimate the precision 
+ of CES parameters is new, and a computationally intensive simulation is planned
+ to investigate the quality and performance of the these methods in this setting.
 

### 2017-01-19 Articles/Brockway_Landscape_2017/Indexing_Demo.Rnw
Minor changes.

@@
   Y = \gamma \: \mathrm{e}^{\lambda t} \left[\delta K^{-\rho}
-      + (1-\delta)L^{-\rho} \right]^{-1/\rho} \; .
+      + (1-\delta)L^{-\rho} \right]^{-1/\rho} \; ,
+\end{equation}
+%
+where $\rho$ is related to the elasticity of substitution~($\sigma$) by 
+%
+\begin{equation} \label{eq:sigma}
+  \sigma = \frac{1}{1 + \rho} \; .
 \end{equation}
@@
 
-The Cobb-Douglas model indexed historical data is given by
+The Cobb-Douglas model with indexed historical data is given by
 %
@@
 
-All data are from the Penn World Table.
+All historical data are from the Penn World Table.
 Figure~\ref{fig:GDP-graph} below shows historical data as dots.
@@
 
-Next, we fit both the Cobb-Douglas and CES aggregate production functions 
-to both indexed and non-indexed data.
-Figure~\ref{fig:GDP-graph} below shows historical data as lines.
+We fit both the Cobb-Douglas and CES aggregate production functions 
+to both raw and indexed data.
+Figure~\ref{fig:GDP-graph} below shows fitted GDP as lines.
 
@@
 
-We graph each type of fitted model against historical data.
+Figure~\ref{fig:GDP-graph} compares each type of fitted model (lines) with historical data (dots).
 Note that all models provide excellent fits.
@@
 
-Here are the coefficients for the Cobb-Douglas models.
+The coefficients for Cobb-Douglas models are shown below.
 <<cd-coeffs>>=
@@
 
-Note that the fitted parameters 
-output elasticity
+Note that output elasticity
 \verb+alpha_1+ ($\alpha_k$) 
@@
 are identical,
-regardless of whether the historical data are indexed or not.
+regardless of whether the historical data are indexed or raw.
 
@@
 
-Note that $\theta$ for the indexed model is near 1.0, as expected.
+Note that $\theta$ for the model fit to indexed data is near 1.0, as expected.
 
@@
 The following shows parameters for CES models
-fitted to non-indexed and indexed historical data.
+fitted to raw and indexed historical data.
 
@@
 
+Similar to the Cobb-Douglas model,
+the pre-multiplier term
+(in this case \verb+gamma+)
+is different depending upon whether the historical data were indexed or raw.
 As expected, and similar to the Cobb-Douglas model,
@@
 (\verb+gamma+)
-is identical, regardless of whether the historical data are indexed or not.
-Again, similar to the Cobb-Douglas model, 
-the pre-multiplier term
-(in this case \verb+gamma+)
-is different depending upon whether the historical data were indexed or not.
-We note that the value of \verb+gamma+ is close to 1,
+is identical, regardless of whether the historical data are indexed or raw.
+We note that the value of \verb+gamma+ is close to 1.0,
 when fitting to indexed data,
 as expected.
-Furthermore, the elasticity of substitution parameters
+Furthermore, the elasticity of substitution exponents
 (\verb+rho+)

### 2017-01-19 Articles/Brockway_Landscape_2017/Indexing_Demo.Rnw
Slight edits

@@
 is different depending upon whether the historical data were indexed or raw.
-As expected, and similar to the Cobb-Douglas model,
-the growth rate of the Solow residual
-(\verb+gamma+)
-is identical, regardless of whether the historical data are indexed or raw.
 We note that the value of \verb+gamma+ is close to 1.0,
@@
 as expected.
+Also as expected, and similar to the Cobb-Douglas model,
+the growth rate of the Solow residual
+(\verb+lambda+)
+is identical, regardless of whether the historical data are indexed or raw.
 Furthermore, the elasticity of substitution exponents
@@
 the historical data are indexed.
-Any inferences about the economy that depend upon the share parameter (\verb+delta+)
+Any interpretation of the economy that relies upon the share parameter (\verb+delta+)
 will be significantly different depending upon whether the 
-historical data are indexed prior to fitting.
+CES function is fitted to raw or indexed data.
 

### 2017-01-19 Articles/Brockway_Landscape_2017/Indexing_Demo.Rnw
Using summary() now.

@@
 <<cd-coeffs>>=
-cd_nonindexed
-cd_indexed
+summary(cd_nonindexed)
+summary(cd_indexed)
 @
@@
 <<cd-logscale-to-theta>>=
-exp(cd_nonindexed$coefficients[["logscale"]])
-exp(cd_indexed$coefficients[["logscale"]])
+exp(coef(cd_nonindexed)[["logscale"]])
+exp(coef(cd_indexed)[["logscale"]])
 @
@@
 <<ces-coeffs>>=
-ces_nonindexed
-ces_indexed
+summary(ces_nonindexed)
+summary(ces_indexed)
 @

### 2017-01-25 Articles/Brockway_Landscape_2017/Indexing_Demo.Rnw
Updates to indexing demo.

@@
 \title{Demonstration of Effect of Indexing on\\
-Cobb-Douglas and CES\\
-Aggregate Production Functions}
+Cobb-Douglas (C-D) and 
+Constant Elasticity of Substitution (CES)\\
+Aggregate Production Functions (APFs)}
 \author{Matthew Kuperus Heun}
@@
 
-%++++++++++++++++++++++++++++++
-\subsection{Raw historical data} 
-\label{sec:raw}
-%++++++++++++++++++++++++++++++
-
-The Cobb-Douglas model for using raw historical data is given by 
+The C-D model for using raw historical data is given by 
 %
@@
 
-The CES model with raw historical data is given by
+The Constant Elasticity of Substitution~(CES) model with raw historical data is given by
 %
@@
 
-%++++++++++++++++++++++++++++++
-\subsection{Indexed factors of production} 
-\label{sec:indexed}
-%++++++++++++++++++++++++++++++
-
-The Cobb-Douglas model with indexed historical data is given by
+The C-D model with indexed historical data is given by
 %
@@
 
+When a third factor of production (in this case energy)
+is added to the C-D APF with raw historical data,
+we obtain
+%
+\begin{equation} \label{eq:CDe_model_raw}
+  Y = \theta \: \mathrm{e}^{\lambda t} \: K^{\alpha_k} \, L^{\alpha_l} \, E^{\alpha_e} \; ,
+\end{equation}
+%
+where $E$ is total primary energy supply.
+For the CES APF with raw historical data, we obtain
+%
+\begin{equation} \label{eq:CES3_raw}
+  Y = \theta \: \mathrm{e}^{\lambda t} \, \left\{\delta \left[\delta_1 K^{-\rho_1}
+      + (1-\delta_1) L^{-\rho_1} \right]^{\rho/\rho_1}
+      + (1-\delta) E^{-\rho} \right\}^{-1/\rho} \; .
+\end{equation}
+%
+For indexed historical data, we define
+$e \equiv E / E_{1960}$ to obtain
+%
+\begin{equation} \label{eq:CDe_model_indexed}
+  y = \theta \: \mathrm{e}^{\lambda t} \: k^{\alpha_k} \, l^{\alpha_l} \, e^{\alpha_e} \; ,
+\end{equation}
+%
+and
+%
+\begin{equation} \label{eq:CES3_indexed}
+  y = \theta \: \mathrm{e}^{\lambda t} \, \left\{\delta \left[\delta_1 k^{-\rho_1}
+      + (1-\delta_1) l^{-\rho_1} \right]^{\rho/\rho_1}
+      + (1-\delta) e^{-\rho} \right\}^{-1/\rho} \; .
+\end{equation}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-All historical data are from the Penn World Table.
-Figure~\ref{fig:GDP-graph} below shows historical data as dots.
+Historical data for $Y$, $K$, and $L$ are from the Penn World Table.
+Historical data for $E$ are from the International Energy Agency
+time series for total primary energy supply.
+Figure~\ref{fig:GDP-graph} below shows historical data for $Y$ and $y$ as dots.
 
@@
 
-We fit both the Cobb-Douglas and CES aggregate production functions 
-to both raw and indexed data.
+We fit both the C-D and CES aggregate production functions (APFs)
+both with and without energy to both raw and indexed data.
 Figure~\ref{fig:GDP-graph} below shows fitted GDP as lines.
@@
 ces_indexed <- cesModel(iGDP ~ iK + iL + iYear, data = UKdata)
+cd_nonindexed_e <- cdModel(GDP ~ K + L + E + iYear, data = UKdata)
+cd_indexed_e <- cdModel(iGDP ~ iK + iL + iE + iYear, data = UKdata)
+ces_nonindexed_e <- cesModel(GDP ~ K + L + E + iYear, data = UKdata)
+ces_indexed_e <- cesModel(iGDP ~ iK + iL + iE + iYear, data = UKdata)
 @
@@
     yhat_ces_indexed = yhat(ces_indexed),
+    yhat_cd_nonindexed_e = yhat(cd_nonindexed_e),
+    yhat_cd_indexed_e = yhat(cd_indexed_e),
+    yhat_ces_nonindexed_e = yhat(ces_nonindexed_e),
+    yhat_ces_indexed_e = yhat(ces_indexed_e),
     Country = NULL,
-    K = NULL,
-    iK = NULL,
-    L = NULL,
-    iL = NULL
+    K = NULL, iK = NULL, L = NULL, iL = NULL, E = NULL, iE = NULL
   )
@@
 attr(quadplotdata$yhat_cd_indexed, "label") <- NULL
+attr(quadplotdata$yhat_cd_nonindexed_e, "label") <- NULL
+attr(quadplotdata$yhat_cd_indexed_e, "label") <- NULL
 # Prepare format for quad plot
@@
          yhat_cd_nonindexed, yhat_cd_indexed, 
-         yhat_ces_nonindexed, yhat_ces_indexed) %>% 
+         yhat_ces_nonindexed, yhat_ces_indexed,
+         yhat_cd_nonindexed_e, yhat_cd_indexed_e,
+         yhat_ces_nonindexed_e, yhat_ces_indexed_e
+  ) %>% 
   mutate(
@@
       case_when(
-        .$variable %in% c("yhat_cd_nonindexed", "yhat_ces_nonindexed") ~ .$GDP,
-        .$variable %in% c("yhat_cd_indexed", "yhat_ces_indexed")       ~ .$iGDP
+        .$variable %in% c("yhat_cd_nonindexed", "yhat_ces_nonindexed",
+                          "yhat_cd_nonindexed_e", "yhat_ces_nonindexed_e") ~ .$GDP,
+        .$variable %in% c("yhat_cd_indexed", "yhat_ces_indexed",
+                          "yhat_cd_indexed_e", "yhat_ces_indexed_e")       ~ .$iGDP
       ),
@@
     indexed = case_when(
-        .$variable %in% c("yhat_cd_nonindexed", "yhat_ces_nonindexed") ~ "raw",
-        .$variable %in% c("yhat_cd_indexed", "yhat_ces_indexed")       ~ "indexed"
+      .$variable %in% c("yhat_cd_nonindexed", "yhat_ces_nonindexed",
+                        "yhat_cd_nonindexed_e", "yhat_ces_nonindexed_e") ~ "raw",
+      .$variable %in% c("yhat_cd_indexed", "yhat_ces_indexed",
+                        "yhat_cd_indexed_e", "yhat_ces_indexed_e")       ~ "indexed"
     ),
@@
     apf = case_when(
-        .$variable %in% c("yhat_cd_nonindexed", "yhat_cd_indexed")     ~ "CD",
-        .$variable %in% c("yhat_ces_nonindexed", "yhat_ces_indexed")   ~ "CES"
-    )
+      .$variable %in% c("yhat_cd_nonindexed", "yhat_cd_indexed",
+                        "yhat_cd_nonindexed_e", "yhat_cd_indexed_e")     ~ "CD",
+      .$variable %in% c("yhat_ces_nonindexed", "yhat_ces_indexed",
+                        "yhat_ces_nonindexed_e", "yhat_ces_indexed_e")   ~ "CES"
+    ),
+    energy = case_when(
+      .$variable %in% c("yhat_cd_nonindexed", "yhat_cd_indexed",
+                        "yhat_ces_nonindexed", "yhat_ces_indexed")       ~ "w/o energy",
+      .$variable %in% c("yhat_cd_nonindexed_e", "yhat_cd_indexed_e",
+                        "yhat_ces_nonindexed_e", "yhat_ces_indexed_e")   ~ "w/ energy"
+    ),
+    energy = factor(energy, c("w/o energy", "w/ energy"))
   )
@@
 
-Figure~\ref{fig:GDP-graph} compares each type of fitted model (lines) with historical data (dots).
+Figures~\ref{fig:GDP-graph} and~\ref{fig:GDP-graph-e} 
+compare each type of fitted model (lines) with historical data (dots).
 Note that all models provide excellent fits.
 
-<<GDP-graph, fig.align="center", fig.width=6.5, fig.height=5, fig.cap="Fits to historical data. Dots are historical data. Lines are fits.">>=
-ggplot(data = quadplotdata, mapping = aes_string(x = "Year")) + 
+<<GDP-graph, fig.align="center", fig.width=6.5, fig.height=5, fig.cap="Fits to historical data for models that exclude energy. Dots are historical data. Lines are fits.">>=
+ggplot(data = quadplotdata %>% filter(energy == "w/o energy"), 
+       mapping = aes_string(x = "Year")) + 
+  geom_point(mapping = aes_string(y = "y_historical"), 
+             size = 0.2) + 
+  geom_line(mapping = aes_string(y = "y_hat")) + 
+  facet_grid(indexed ~ apf, scales = "free") + 
+  xlab(NULL) +
+  ylab("GDP [raw: millions 2005$, indexed: 1960 = 1]") +
+  xy_theme()
+@
+
+<<GDP-graph-e, fig.align="center", fig.width=6.5, fig.height=5, fig.cap="Fits to historical data for models that include energy. Dots are historical data. Lines are fits.">>=
+ggplot(data = quadplotdata %>% filter(energy == "w/ energy"), 
+       mapping = aes_string(x = "Year")) + 
   geom_point(mapping = aes_string(y = "y_historical"), 
@@
 %++++++++++++++++++++++++++++++
-\subsection{Cobb-Douglas} 
-\label{sec:cd_coeffs}
+\subsection{Without energy} 
+\label{sec:coefficients_without_energy}
 %++++++++++++++++++++++++++++++
 
-The coefficients for Cobb-Douglas models are shown below.
+%------------------------------
+\subsubsection{Cobb-Douglas} 
+\label{sec:cd_coeffs}
+%------------------------------
+
+The coefficients for C-D models are shown below.
 <<cd-coeffs>>=
@@
 
-%++++++++++++++++++++++++++++++
-\subsection{CES}
+%------------------------------
+\subsubsection{CES}
 \label{sec:ces_coeffs}
-%++++++++++++++++++++++++++++++
+%------------------------------
 
@@
 
-Similar to the Cobb-Douglas model,
+Similar to the C-D model,
 the pre-multiplier term
@@
 as expected.
-Also as expected, and similar to the Cobb-Douglas model,
+Also as expected, and similar to the C-D model,
 the growth rate of the Solow residual
@@
 
+%++++++++++++++++++++++++++++++
+\subsection{With energy} 
+\label{sec:coefficients_with_energy}
+%++++++++++++++++++++++++++++++
+
+%------------------------------
+\subsubsection{Cobb-Douglas with energy} 
+\label{sec:cd_coeffs_e}
+%------------------------------
+
+The coefficients for C-D models with energy are shown below.
+<<cd-coeffs-e>>=
+summary(cd_nonindexed_e)
+summary(cd_indexed_e)
+@
+
+Again, output elasticities
+\verb+alpha_1+ ($\alpha_k$) 
+\verb+alpha_2+ ($\alpha_l$) 
+and 
+Solow residual growth rate
+\verb+lambda+
+are identical,
+regardless of whether the historical data are indexed or raw.
+
+The \texttt{logscale} pre-multiplier
+is converted to $\theta$ below:
+
+<<cd-logscale-to-theta-e>>=
+exp(coef(cd_nonindexed_e)[["logscale"]])
+exp(coef(cd_indexed_e)[["logscale"]])
+@
+
+Note that $\theta$ for the model fit to indexed data is near 1.0, as expected.
+
+%------------------------------
+\subsubsection{CES}
+\label{sec:ces_coeffs_e}
+%------------------------------
+
+The following shows parameters for CES models with energy
+fitted to raw and indexed historical data.
+
+<<ces-coeffs-e>>=
+summary(ces_nonindexed_e)
+summary(ces_indexed_e)
+@
+
+Note that the value of \verb+delta+ is shown as 1.0 for both models.
+However, the value is not exactly 1.0:
+
+<<ces-e-delta>>=
+1 - coef(ces_nonindexed_e)[["delta"]]
+1 - coef(ces_indexed_e)[["delta"]]
+@
+
+These values are close enough to exactly 1 to make 
+energy ($E$ and $e$) the only important factor of production in the fitting process.
+As such, the values of \verb+rho_1+ and \verb+rho+
+make little difference to the computed value of SSE, regardless of the values of the other parameters.
+Thus, the value of \verb+rho+ doesn't move from its initial guess (1).
+These effects are reflected in the non-convergence of the indexed model.
+It is surprising that the non-indexed model reports convergence, because
+the indexed model (which reported non-convergence) has a better fit than 
+the indexed model (which reported convergence).
+All in all, I think 
+this is not a very good example 
+on which to demonstrate the effect of indexing historical data
+with three factors of production.
+
+That said, and similar to the CES model without energy,
+the estimate of pre-multiplier term
+(in this case \verb+gamma+)
+is different depending upon whether the historical data were indexed or raw.
+We note that the value of \verb+gamma+ is close to 1.0,
+when fitting to indexed data,
+as expected.
+The growth rate of the Solow residual
+(\verb+lambda+)
+is slightly different, depending upon whether the historical data are indexed or raw,
+but that difference could be caused by the fact that the parameters are not determined 
+very precisely.
+The elasticity of substitution exponents
+(\verb+rho_1+ and \verb+rho+)
+are similar, but not identical, when we move from raw to indexed historical data.
+Again, this could be a reflection of the fact that these parameters are not determined very precisely.
+
+Similar to the CES model with two factors of production, 
+the share parameter (\verb+delta+)
+varies significantly, depending upon whether 
+the historical data are indexed.
+And again, 
+any interpretation of the economy that relies upon the share parameter (\verb+delta+)
+will be significantly different depending upon whether the 
+CES function is fitted to raw or indexed data.
+
+%++++++++++++++++++++++++++++++
+\subsection{With generated data} 
+\label{sec:generated_data}
+%++++++++++++++++++++++++++++++
+
+We can try again with generated data, 
+hoping to avoid the messiness that accompanies 
+raw data that is many orders of magnitude different from 
+indexed data.
+
+<<gen-data>>=
+# First, assume some nested 3-factor CES coefficients
+sigma_1 <- 0.4
+sigma <- 1.2
+coef_indexed_gen <- c(gamma = 1, lambda = 0.021, 
+                      delta_1 = 0.4, delta = 0.6, 
+                      rho_1 = 1/sigma_1 - 1, rho = 1/sigma - 1,
+                      nu = 1)
+# Calculate what output would have been with those coefficients
+y_gen <- cesCalc(xNames = c("iK", "iL", "iE"), data = UKdata, 
+                 coef = coef_indexed_gen, tName = "iYear", 
+                 nested = TRUE)
+# Put this generated data into the data frame 
+# that we'll use for fitting.
+UKwithGenData <- UKdata %>% 
+  mutate(
+    # Add the generated GDP values to our data frame
+    y_gen = y_gen,
+    # But also add some generated historical data.
+    # Perturb by rather small values to make fitting easier.
+    Y_gen = y_gen * 1.01,
+    K_gen = iK * 1.02,
+    L_gen = iL * 1.03,
+    E_gen = iE * 1.04
+  )
+
+# Fit to the generated GDP time series using indexed data. 
+ces_indexed_e_gen <- cesModel(y_gen ~ iK + iL + iE + iYear, 
+                              data = UKwithGenData)
+summary(ces_indexed_e_gen)
+# Compare with our assumed coefficients.  
+# We should get exact same coefficients back, and we do!
+coef_indexed_gen
+coef(ces_indexed_e_gen)
+# Fit to generated raw data.
+ces_raw_e_gen <- cesModel(Y_gen ~ K_gen + L_gen + E_gen + iYear, 
+                          data = UKwithGenData)
+summary(ces_raw_e_gen)
+# Compare.
+coef_indexed_gen
+coef(ces_raw_e_gen)
+@
+
+We find that the values for \verb+lambda+
+are identical when comparing fits to indexed and raw historical data (in this case, generated).
+Values for \verb+gamma+ are different, as expected.
+Values for \verb+delta_1+ and \verb+delta+ are different, as expected.
+The values for \verb+rho_1+ (in the inner next)
+and \verb+rho_1+ are identical
+across models fitted to raw and indexed historical data.
+
+To summarize, 
+when moving from indexed historical data to raw historical data,
+CES parameters have the following behavio(u)r:
+%
+\begin{itemize}
+
+  \item $\gamma$: changes
+
+  \item $\lambda$: stays same
+
+  \item $\delta_1$, $\delta$: change
+
+  \item $\rho_1$, $\rho$: stay same
+
+\end{itemize}
+
 \end{document}

### 2018-07-10 Articles/Court_Analysis_2018/FittingForCourt2018.Rmd
First document for Victor Court.

---
title: "Analysis for Victor Court"
author: "Matthew Kuperus Heun"
date: "7/10/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2018-07-10 Articles/Court_Analysis_2018/FittingForCourt2018.Rmd
Fitting information for Victor Court.

@@
 author: "Matthew Kuperus Heun"
-date: "7/10/2018"
+date: "10 July 2018"
 output: pdf_document
@@
 
-## R Markdown
+## Analysis for Victor Court
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+Victor has asked me to use my CES fitting functions on his US data
+as a point of comparison.
 
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
-
-```{r cars}
-summary(cars)
+```{r, include=FALSE}
+library(dplyr)
+library(EconModels)
+library(ggplot2)
+library(magrittr)
+library(tidyr)
 ```
 
-## Including Plots
+## Load and sanitize data
 
-You can also embed plots, for example:
+First, load the data.
 
-```{r pressure, echo=FALSE}
-plot(pressure)
+```{r}
+USData_raw <- read.csv(file = "CES_USA.csv", sep = ";")
+head(USData_raw, n = 3)
 ```
 
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+Next, sanitize the data a bit
+by removing non-indexed columns and
+renaming the columns.
+Lower-case variable names indicate indexing to 1 in 1960.
+
+```{r}
+USData <- USData_raw %>% 
+  select(-K.L...US.2010.per.hour., 
+         -Capital...US.2010., 
+         -Labor..millions.of.hours., 
+         -Primary.exergy..TJ.,
+         -GDP....US.2010.) %>% 
+  rename(
+    k = K..1960...1.,
+    l = L..1960...1.,
+    e = E..1960...1.,
+    y = Y..1960...1.
+  ) %>% 
+  mutate(
+    Country = "US"
+  ) %>% 
+  select(Country, Year, y, k, l, e)
+head(USData, n = 3)
+```
+
+Now review the data.
+
+```{r}
+USData %>% 
+  gather(key = variable, value = value, k, l, e, y) %>% 
+  mutate(
+    # Put variables in a reasonable order for the graph legend
+    variable = factor(variable, levels = c("y", "k", "e", "l"))
+  ) %>% 
+  ggplot(mapping = aes(x = Year, y = value, linetype = variable)) +
+  geom_line() +
+  geom_hline(yintercept = 1, colour = "gray50", size = 0.1) +
+  labs(y = NULL, x = NULL, linetype = NULL) +
+
+  xy_theme()
+```
+
+## Perform the fit
+
+We'll fit with the $(kl)e$ nesting.
+
+```{r}
+kleModel <- cesModel(y ~ k + l + e, data = USData)
+kleModel
+nckle <- naturalCoef(kleModel)
+nckle
+```
+
+Note that $\delta = 1$, so this is a boundary model.
+We also have $\rho_1 = -1$ (therefore, $\sigma_1 = \infty$). 
+We can query which boundary model we have: 
+```{r}
+kleModel$bname
+```
+So this is boundary model 7 of Table 2 in the ``Cautionary Tales'' paper.
+
+With $\theta = \mathrm{e}^{\mathrm{logscale}} = \mathrm{e}^
+{`r naturalCoef(kleModel)[["logscale"]]`} =
+`r naturalCoef(kleModel)[["scale"]]`$,
+these results mean that boundary model 7
+
+$$y = \theta A \left[ \delta_1 x_1 + (1 - \delta_1) x_2 \right]$$
+is filled with coefficients like this:
+
+$$y = `r exp(coef(kleModel)[["logscale"]])` 
+      \mathrm{e}^{-`r coef(kleModel)[["lambda"]]` (t-1960)} 
+      \left[ `r coef(kleModel)[["delta_1"]]` \, k 
+          + `r 1 - coef(kleModel)[["delta_1"]]` \, l \right] \; .$$
+
+## Compare with historical data
+
+We can compare the fitted model against the historical data
+as shown in the following graph.
+
+```{r}
+USData %>% 
+  mutate(
+    `y predicted` = yhat(kleModel) %>% as.numeric() # avoids an attributes warning
+  ) %>% 
+  select(Year, y, `y predicted`) %>% 
+  gather(key = var, value = value, y, `y predicted`) %>% 
+  ggplot(mapping = aes(x = Year, y = value, linetype = var)) +
+  geom_line() + 
+  geom_hline(yintercept = 1, colour = "gray50", size = 0.1) +
+  labs(x = NULL, y = NULL, linetype = NULL) +
+  xy_theme()
+```
+
+## Comments
+
+1. The fit is rather good.
+2. It is likely that the fitted model excludes energy ($e$), 
+   because the energy dip in 1980 is too large. 
+   Instead, by picking up the smaller dip in the $l$ data series, the fit is better.
+3. I find it interesting, but don't quite know what to make of it, that
+   the coefficients on $k$ and $l$ are approximately the neoclassical numbers 
+   (0.7 and 0.3, respectively).

### 2018-07-10 Articles/Court_Analysis_2018/FittingForCourt2018.Rmd
Working on Victor Court paper.

@@
 kleModel
-nckle <- naturalCoef(kleModel)
-nckle
 ```
-
 Note that $\delta = 1$, so this is a boundary model.
 We also have $\rho_1 = -1$ (therefore, $\sigma_1 = \infty$).
+
 We can query which boundary model we have: 
@@
 So this is boundary model 7 of Table 2 in the ``Cautionary Tales'' paper.
+
+We can see the ``natural'' coefficients for the model.
+```{r}
+nckle <- naturalCoef(kleModel)
+nckle
+```
 
@@
 $$y = `r exp(coef(kleModel)[["logscale"]])` 
-      \mathrm{e}^{-`r coef(kleModel)[["lambda"]]` (t-1960)} 
+      \mathrm{e}^{`r coef(kleModel)[["lambda"]]` (t-1960)} 
       \left[ `r coef(kleModel)[["delta_1"]]` \, k 
@@
 2. It is likely that the fitted model excludes energy ($e$), 
-   because the energy dip in 1980 is too large. 
+   because the energy dip in 1980 puts the energy trajectory at a very different
+   multiple of the $y$ curve. 
+   In contrast, the $l$ curve stays at about the same multiple of $y$
+   throughout the entire time series. 
+   Thus, the $l$ curve . 
    Instead, by picking up the smaller dip in the $l$ data series, the fit is better.

### 2018-07-11 Articles/Court_Analysis_2018/FittingForCourt2018.Rmd
Edits to Victor Court analysis.

@@
 ---
-title: "Analysis for Victor Court"
+title: "US CES Analysis for Victor Court"
 author: "Matthew Kuperus Heun"
@@
 
-## Analysis for Victor Court
-
-Victor has asked me to use my CES fitting functions on his US data
-as a point of comparison.
-
 ```{r, include=FALSE}
@@
 
+## Analysis for Victor Court
+
+Victor Court has asked me to fit US energy and economic data
+using the CES aggregate production function. 
+The energy and economic data have been supplied by Victor.
+
 ## Load and sanitize data
@@
 USData_raw <- read.csv(file = "CES_USA.csv", sep = ";")
-head(USData_raw, n = 3)
+head(USData_raw, n = 3) # Show the first 3 rows
 ```
@@
   ) %>% 
-  select(Country, Year, y, k, l, e)
+  select(Country, Year, y, k, l, e) # Re-order the columns
 head(USData, n = 3)
@@
 
-Now review the data.
+Now review the data in graphical form.
 
@@
 
-We can query which boundary model we have: 
+We can query which boundary model we have obtained: 
 ```{r}
@@
 With $\theta = \mathrm{e}^{\mathrm{logscale}} = \mathrm{e}^
-{`r naturalCoef(kleModel)[["logscale"]]`} =
-`r naturalCoef(kleModel)[["scale"]]`$,
+{`r nckle[["logscale"]]`} = `r nckle[["scale"]]`$,
 these results mean that boundary model 7
@@
 
-$$y = `r exp(coef(kleModel)[["logscale"]])` 
+$$y = `r nckle[["scale"]]` 
       \mathrm{e}^{`r coef(kleModel)[["lambda"]]` (t-1960)} 
@@
           + `r 1 - coef(kleModel)[["delta_1"]]` \, l \right] \; .$$
+
+At the moment, I'm a bit unclear about the $\theta$ coefficient.
+Inserting values for 1960 ($k = 1$, $l = 1$)
+gives $y = \theta \mathrm{e}^0 [1] = \theta = `r nckle[["scale"]]` \ne 1$,
+but it should be about 1.
+
+I probably have something wrong in my thinking about this.  
+Any ideas?
 
@@
   mutate(
-    `y predicted` = yhat(kleModel) %>% as.numeric() # avoids an attributes warning
+    `y fitted` = yhat(kleModel) %>% as.numeric() # avoids an attributes warning
   ) %>% 
-  select(Year, y, `y predicted`) %>% 
-  gather(key = var, value = value, y, `y predicted`) %>% 
+  select(Year, y, `y fitted`) %>% 
+  gather(key = var, value = value, y, `y fitted`) %>% 
   ggplot(mapping = aes(x = Year, y = value, linetype = var)) +
@@
 
-1. The fit is rather good.
+1. Visually, the fit is quite good.
 2. It is likely that the fitted model excludes energy ($e$), 
    because the energy dip in 1980 puts the energy trajectory at a very different
-   multiple of the $y$ curve. 
+   multiple of the $y$ curve before and after 1980. 
+   Mixing $e$ into the fit makes the fitted model worse!
    In contrast, the $l$ curve stays at about the same multiple of $y$
-   throughout the entire time series. 
-   Thus, the $l$ curve . 
-   Instead, by picking up the smaller dip in the $l$ data series, the fit is better.
+   throughout the entire time series, yet retains the dip in 1980. 
+   The $l$ curve provides a better approximation to the shape of $y$.
+   So, the fitting algorithm chooses to use $l$ instead of $e$ to fit $y$.
 3. I find it interesting, but don't quite know what to make of it, that
@@
    (0.7 and 0.3, respectively).
+   Maybe it's a result of the fact that the $k$ and $l$ lines are
+   approximately a ratio of 2 apart from each other.

### 2018-07-11 Articles/Court_Analysis_2018/FittingForCourt2018.Rmd
Report for Victor.

--- 2018-07-10 Articles/Court_Analysis_2018/FittingForCourt2018.Rmd
@@
 ---
-title: "Analysis for Victor Court"
-author: "Matthew Kuperus Heun"
-date: "10 July 2018"
+title: "US CES Analysis for Victor Court"
+author: "Matthew Kuperus Heun, Calvin College"
+date: "11 July 2018"
 output: pdf_document
@@
 ```
-
-## Analysis for Victor Court
-
-Victor has asked me to use my CES fitting functions on his US data
-as a point of comparison.
 
@@
 
+## Analysis for Victor Court
+
+Victor Court has asked me to fit US energy and economic data
+using the CES aggregate production function. 
+The energy and economic data have been supplied by Victor.
+I will use the fitting code that was created for the ``Cautionary Tales'' paper.
+
 ## Load and sanitize data
@@
   mutate(
-    Country = "US"
+    Country = "US",
+    time = Year - min(Year)
   ) %>% 
-  select(Country, Year, y, k, l, e)
+  select(Country, Year, time, y, k, l, e) # Re-order the columns
 head(USData, n = 3)
@@
 We'll fit with the $(kl)e$ nesting.
+The warning occurs in one of the many trials and can be ignored.
 
 ```{r}
-kleModel <- cesModel(y ~ k + l + e, data = USData)
+kleModel <- cesModel(y ~ k + l + e + time, data = USData)
 kleModel
-nckle <- naturalCoef(kleModel)
-nckle
 ```
+Note that $\rho_1 = -1$ (therefore, $\sigma_1 = \infty$). 
+Therefore, this is a boundary model.
 
-Note that $\delta = 1$, so this is a boundary model.
-We also have $\rho_1 = -1$ (therefore, $\sigma_1 = \infty$). 
-We can query which boundary model we have: 
+We can query which boundary model we have obtained: 
 ```{r}
@@
 ```
-So this is boundary model 7 of Table 2 in the ``Cautionary Tales'' paper.
+So this is boundary model 20 of Table 2 in the ``Cautionary Tales'' paper.
 
-With $\theta = \mathrm{e}^{\mathrm{logscale}} = \mathrm{e}^
-{`r naturalCoef(kleModel)[["logscale"]]`} =
-`r naturalCoef(kleModel)[["scale"]]`$,
-these results mean that boundary model 7
+We can see the "natural" coefficients for the model,
+which shows that the "scale" parameter ($\theta$) is close to 1, as expected.
+```{r}
+naturalCoef(kleModel)
+```
 
-$$y = \theta A \left[ \delta_1 x_1 + (1 - \delta_1) x_2 \right]$$
-is filled with coefficients like this:
+We can also try other nestings of the CES model, 
+which provide three degenerate cases: $(kl)$, $(le)$, and $(ek)$ nestings.
+In all of these, `delta` is 1 and `sigma` and `rho` are `NA`, 
+because the third factor of production is missing.
 
-$$y = `r exp(coef(kleModel)[["logscale"]])` 
-      \mathrm{e}^{-`r coef(kleModel)[["lambda"]]` (t-1960)} 
-      \left[ `r coef(kleModel)[["delta_1"]]` \, k 
-          + `r 1 - coef(kleModel)[["delta_1"]]` \, l \right] \; .$$
+```{r}
+klModel <- cesModel(y ~ k + l + time, data = USData)
+naturalCoef(klModel)
+leModel <- cesModel(y ~ l + e + time, data = USData)
+naturalCoef(leModel)
+ekModel <- cesModel(y ~ e + k + time, data = USData)
+naturalCoef(ekModel)
+```
 
@@
 
-We can compare the fitted model against the historical data
+We can compare the fitted models against the historical data
 as shown in the following graph.
+```yhat``` is a function that extracts the fitted values.
 
@@
   mutate(
-    `y predicted` = yhat(kleModel) %>% as.numeric() # avoids an attributes warning
+    `y fitted kle` = yhat(kleModel) %>% as.numeric(), # avoids an attributes warning
+    `y fitted kl` = yhat(klModel),
+    `y fitted le` = yhat(leModel),
+    `y fitted ek` = yhat(ekModel)
   ) %>% 
-  select(Year, y, `y predicted`) %>% 
-  gather(key = var, value = value, y, `y predicted`) %>% 
-  ggplot(mapping = aes(x = Year, y = value, linetype = var)) +
+  select(Year, y, `y fitted kle`, `y fitted kl`, `y fitted le`, `y fitted ek`) %>% 
+  gather(key = var, value = value, y, 
+         `y fitted kle`, `y fitted kl`, `y fitted le`, `y fitted ek`) %>% 
+  mutate(
+    var = factor(var, levels = c("y", "y fitted kle", 
+                                 "y fitted kl", "y fitted le", "y fitted ek"))
+  ) %>% 
+  ggplot(mapping = aes(x = Year, y = value, linetype = var, colour = var)) +
   geom_line() +
   geom_hline(yintercept = 1, colour = "gray50", size = 0.1) +
-  labs(x = NULL, y = NULL, linetype = NULL) +
+  labs(x = NULL, y = NULL, linetype = NULL, colour = NULL) +
   xy_theme()
+```
+
+We can also plot all of the residuals (which are calculated in log space).
+
+```{r}
+resids <- USData %>% 
+  select(Year) %>% 
+  mutate(
+    r_y = 0,
+    r_kle = residuals(kleModel) %>% as.numeric(),
+    r_kl = residuals(klModel) %>% as.numeric(),
+    r_le = residuals(leModel) %>% as.numeric(),
+    r_ek = residuals(ekModel) %>% as.numeric()
+  ) %>% 
+  gather(key = var, value = value, r_y, r_kle, r_kl, r_le, r_ek) %>% 
+  mutate(
+    var = factor(var, levels = c("r_y", "r_kle", "r_kl", "r_le", "r_ek"))
+  ) 
+resids %>% 
+  ggplot(mapping = aes(x = Year, y = value, linetype = var, colour = var)) +
+  geom_line() + 
+  labs(x = NULL, y = NULL, linetype = NULL, colour = NULL) +
+
+  xy_theme()
+```
+
+The sum of squared residuals (in log space) can be used to compare the models.
+
+```{r}
+SSE <- resids %>% 
+  mutate(
+    r2 = value^2
+  ) %>% 
+  select(-value) %>% 
+  spread(key = var, value = r2) %>% 
+  summarise(
+    sse_kle = sum(r_kle), 
+    sse_kl = sum(r_kl),
+    sse_le = sum(r_le),
+    sse_ek = sum(r_ek)
+  )
+SSE
 ```
@@
 
-1. The fit is rather good.
-2. It is likely that the fitted model excludes energy ($e$), 
-   because the energy dip in 1980 is too large. 
-   Instead, by picking up the smaller dip in the $l$ data series, the fit is better.
-3. I find it interesting, but don't quite know what to make of it, that
-   the coefficients on $k$ and $l$ are approximately the neoclassical numbers 
-   (0.7 and 0.3, respectively).
+Visually, the fit is quite good for all models. 
+It is difficult to say that one model is vastly superior to any other model.
+According to SSE, the $(kl)e$ model fits best, as would be expected.

### 2018-07-30 Notes/OutputElasticitiesFromData.R
big house cleaning -- keep just package-related stuff and rearranged directory organization

@@ -1,20 +1,0 @@
-require(EconData)
-require(mosaic)
-PT <- IST %>% filter(Country == "PT") %>% head(-2)
-
-( ediff(PT$iGDP) / ediff(PT$iKservS.L ) ) / (PT$iGDP / PT$iKservS.L) -> oK
-( ediff(PT$iGDP) / ediff(PT$ihLest ) ) / (PT$iGDP / PT$ihLest) -> oL
-( ediff(PT$iGDP) / ediff(PT$iUMP ) ) / (PT$iGDP / PT$iUMP) -> oE
-
-PT $ sGDP <- predict(loess(iGDP ~ iYear, data = PT))
-PT $ sK <- predict(loess(iKservS.L ~ iYear, data = PT))
-PT $ sL <- c(predict(loess(ihLest ~ iYear, data = PT)), NA)
-PT $ sU <- c(predict(loess(iUMP ~ iYear, data = PT)), NA, NA)
-
-( ediff(PT$sGDP) / ediff(PT$sK ) ) / (PT$sGDP / PT$sK) -> oKs
-( ediff(PT$sGDP) / ediff(PT$sL ) ) / (PT$sGDP / PT$sL) -> oLs
-( ediff(PT$sGDP) / ediff(PT$sU ) ) / (PT$sGDP / PT$sU) -> oEs
-
-qplot(x = Year, y = oLs, data = PT, geom = c("point", "smooth"))
-qplot(x = Year, y = oEs, data = PT, geom = c("point", "smooth"))
-qplot(x = Year, y = oKs, data = PT, geom = c("point", "smooth"))

### 2018-07-30 Packages/EconModels/R/Fitting.R

@@ -1,881 +1,0 @@
-#' @importFrom nlme gls
-
-standardES <- function( sigma=NA, sigma_1=NA, sigma_2=NA, nest=1:3, standardize=TRUE) {
-  if (standardize) {
-    nest <- c(nest, c(5,5,5,5))  # add dummy slots so nest has length >= 4
-    nest[1:2] <- sort(nest[1:2])
-    nest[3:4] <- sort(nest[3:4])
-    nest <- nest[nest < 5]      # remove dummy slots
-  }
-  
-  if (length(nest) == 2L) {
-    res <- data.frame(a=sigma_1)
-    names(res) <- paste0("sigma_", nest[1], nest[2])
-    return(res)
-  }
-  
-  if (length(nest) == 3L) {
-    res <- data.frame(a = sigma_1, b = sigma)
-    names(res) <- c( paste0("sigma_", nest[1], nest[2]),
-                     paste0("sigma_", nest[1], nest[2], "_", nest[3]) 
-    )
-    return(res)
-  }
-    res <- data.frame(a = sigma_1, b=sigma_2, c=sigma)
-    names(res) <- c( paste0("sigma_", nest[1], nest[2]),
-                     paste0("sigma_", nest[3], nest[4]),
-                     paste0("sigma_", nest[1], nest[2], "_", nest[3], nest[4])
-    )
-    return(res)
-}
-
-# This function provides alpha_i values for the CES model.
-# It converts from delta_1 and delta to alpha_i in a nest-aware way.
-# The standardCoefs provide the importance of each parameter
-# IN THE ORDER THEY APPEAR IN THE FORMULA,
-# regardless of which nest you choose
-# and regardless of how the values for delta and delta_1 turn out.
-# The point here is that the values of delta and delta_1 are applicable to the permuted
-# variable order during the fitting process.
-# But, we want coefficients that apply to the parameters in the order they appeared
-# in the formula. 
-# standardCoefs does just that.
-# Example: A formula is specified as y ~ a + b + c + time,
-# nest is given as c(3,1,2) such that the parameters (during the estimation process)
-# are permuted to y ~ c + a + b + time.
-# Results will be the following:
-# delta    delta_1    alpha_1   alpha_2    alpha_3
-# 1        1          0         0          1
-# 1        0          1         0          0
-# 0        0 or 1     0         1          0
[…]

### 2018-07-30 Packages/EconModels/R/Graphics.R

@@ -1,284 +1,0 @@
-#' Some Graphics functions
-#' 
-#' Some graphics functions for working with Economic Models.
-#'
-#' @import ggplot2
-#' @import mosaic
-#' @import scales
-
-#' @export
-tri2x <- function(x,y,z) {
-    y * 1 + z * 0.5   # + x * 0 
-}
-
-#' @export
-tri2y <- function(x,y,z) {
-  z * 1 # + x * 0 + y * 0 
-}
-
-#' @export
-tri_theme <- function(base_size=12, base_family = "", base_theme=theme_bw) {
-    xy_theme_old(base_size = base_size, base_family = base_family) %+replace% 
-      theme(panel.border = element_blank(), 
-            axis.line = element_blank(),
-            axis.text = element_blank(),
-            axis.ticks = element_blank(),
-            axis.title = element_blank(),
-            panel.grid.major = element_blank(), 
-            panel.grid.minor = element_blank(),
-            plot.background = element_blank(),  
-            strip.background =  element_rect(fill = NA, colour = xy_theme_old()$axis.text$colour)
-            )
-}  
-
-#' @export
-xy_theme_old <- function(base_size=12, base_family = "", base_theme=theme_bw, label_colour="gray50") {
-  base_theme(base_size = base_size, base_family = base_family) %+replace% 
-    theme(# panel.border = element_blank(), 
-          # panel.grid.major = element_blank(), 
-          panel.grid.minor = element_blank(),
-          plot.background = element_blank(),
-          strip.text = element_text(colour=label_colour, size=.8 * base_size),
-          strip.background =  element_rect(fill = NA, colour = NA),
-          legend.background = element_rect(fill=NA, colour=NA),
-          legend.key= element_rect(fill=NA, colour=NA),
-          legend.text=element_text(colour=label_colour),
-          axis.text = element_text(colour=label_colour, size=.8 * base_size), 
-          axis.ticks = element_blank(),
-          axis.title = element_text(colour=label_colour, size=base_size)
-    )
-}
-
-#' @export
-xy_theme <- function(base_size=12, base_family = "", base_theme=theme_bw, label_colour="gray50") {
-  # See https://github.com/infotroph/ggplot-ticks if we want to mirror ticks on top and right.
[…]

### 2018-07-30 Packages/EconModels/R/Resampling.R

@@ -1,187 +1,0 @@
-#' @import foreach
-#' @import doParallel
-
-# This file contains code to resample data for economic growth
-# functions. The idea is that we can resample the historical
-# data and then develop statistical confidence intervals
-# from the values of the model coefficients developed from 
-# thousands of different resamples.
-#
-# We do this multiple times and save a file that contains 
-# the results for later investigation
-
-#' @export
-timeFileName <- function(pre="",post="") {
-  dt <- Sys.time()
-  dt <- gsub(" ","-", dt)
-  return(paste(pre, dt, post, sep=""))
-}
-
-# Compute resampled responses for a model.
-
-#' @export
-resampledResponse <- function( object, ...) {
-  UseMethod("resampledResponse")
-}
-
-#' @export
-resampledResponse.default <- function( object, method=c("residual", "wild", "debug", "parametric"),  
-                                       reindex=FALSE,
-                                       multErr, tol=1e-6, ... ) {
-  if (missing(multErr)) {
-    multErr <- all( response(object) / yhat(object) / exp(resid(object)) - 1 < tol )
-  }
-  method <- match.arg(method)
-  n <- length(yhat(object))
-  sgn <- if (method=="wild") resample( c(-1,1), n ) else 1
-                             
-  if (multErr) {
-    if (method == "paramteric") {
-      res <- rlnorm( n, 0, sd(resid(object)) *sqrt((n-1) / (n - length(coef(object)))) )
-    } else {
-      res <- yhat(object) * resample( exp(resid(object)) ) ^ sgn
-    }
-  } else {
-    if (method == "paramteric") {
-      res <- rnorm( n, 0, sd(resid(object)) *sqrt((n-1) / (n - length(coef(object)))) )
-    } else {
-      res <- yhat(object) + resample( resid(object) ) * sgn
-    }
-  }
-  if (reindex) {
-    res <- res / res[1]  # normalize so first entry is 1.
-  }
-  return(res)
-}
-
-#' Perform resample fits for a model
-#' 
-#' This function returns a list containing models and coefficients from the resample fits.
-#' 
-#' @param model a model returned from \code{linexModel}, \code{cdModel}, 
-#' \code{cesModel}, or \code{sfModel}.  \code{model} must
-#' have been fit with \code{save.data = TRUE}.
-#' @param method one of \code{"resample"}, \code{"residual"}, \code{"wild"}, \code{"parametric"}, or \code{"debug"}
-#' @param n the number of resamples you want to perform
[…]

### 2018-07-30 Packages/EconModels/R/cesBoundaryModels.R

@@ -1,189 +1,0 @@
-
-#' Fits CES boundary models
-#' 
-#' The boundary models are given in Table 2 of 
-#' Heun, et al "An Empirical Investigation of the Role of Energy in Economic Growth"
-#'
-#' @param formula a CES formula in the form \code{y ~ a + b + c + d + time}
-#' @param data historical time series data
-#' @param nest a permutation of the integers 1 to the number of factors describing how to nest and permute
-#'   the variables in the formula.
-#' @return a list of boundary models.
-#' @examples 
-#' if (require(EconData) & require(dplyr)) {
-#'   cesBoundaryModels(iGDP ~ iK + iL + iQp + iYear, data=Calvin %>% filter(Country=="US"), nest=c(1,2,3))
-#'   cesBoundaryModels(iGDP ~ iK + iL + iQp + iYear, data=Calvin %>% filter(Country=="US"), nest=c(2,3,1))
-#'   cesBoundaryModels(iGDP ~ iK + iL + iYear, data=Calvin %>% filter(Country=="US"), nest=c(1,2))
-#'   }
-#' @export
-
-cesBoundaryModels <- function(formula, data, nest, method="nlm", subset=TRUE){
-  # f <- formula  # to avoid problems while renaming is happening.
- 
-  # use same data for all models, even if some models could make use of more complete data. 
-  d <- subset(data, select = intersect(all.vars(formula), names(data)))
-  sdata <- data[complete.cases(d), unique(c(intersect(all.vars(formula), names(data)), names(data)))]
-  
-
-  numFactors <- cesParseFormula(formula, nest)$numFactors
-  numFactorsInFormula <- cesParseFormula(formula, nest)$numFactorsInFormula
-    
-  if ( ! numFactors %in% 2:3 ) {
-    stop("model must have 2 or 3 factors.")
-  }
- 
-  if (numFactorsInFormula >=3) { 
-    formulaRosetta <- list(
-      y = formula[[2]],
-      x1 = formula[[3]][[2]][[2]][[2]],
-      x2 = formula[[3]][[2]][[2]][[3]],
-      x3 = formula[[3]][[2]][[3]],
-      time = formula[[3]][[3]]
-    ) 
-    
[…]

### 2018-07-30 Packages/EconModels/R/cesModel.R

@@ -1,422 +1,0 @@
-
-#' Fitting CES models
-#' 
-#' This function fits a CES model
-#' @param formula a formula of the form \code{response ~ a + b + c + d + time}.  
-#' \code{c} and \code{d} are optional.
-#' @param data a data frame, in which to evaluate the formula.
-#' @param response instead of specifying a formula, expressions for
-#' the components can be specified individually.
-#' @param x1 instead of specifying a formula, expressions for
-#' the components can be specified individually as character strings.
-#' @param x2 instead of specifying a formula, expressions for
-#' the components can be specified individually as character strings.
-#' @param x3 instead of specifying a formula, expressions for
-#' the components can be specified individually as character strings.
-#' @param x4 instead of specifying a formula, expressions for
-#' the components can be specified individually as character strings.
-#' @param time instead of specifying a formula, expressions for
-#' the components can be specified individually as character strings.
-#' @param nest a permutation (a,b,c,d) of the integers 1 through 4.
-#' For models with 3 factors, the nesting
-#' is (xa + xb) + xc.  For 4 factors, the nesting is (xa + xb) + (xc + xd)
-#' @param prevModel a model used to start a gradient search.
-#' \code{prevModel} will be used as a starting point for a gradient search after both
-#' (a) grid search in \code{rho} and \code{rho1} and 
-#' (b) a gradient search starting from the best grid search 
-#' are complete.
-#' #' Use \code{NULL} (the default value) 
-#' if you want to skip the gradient search from a previous model.
-#' @param multErr logical, tells whether errors are to be assessed in a multiplicative manner
-#' @param rho,rho1 creates a grid upon which gradient searches in all other (free) parameters will be made.
-#' (I.e., when \code{rho} and/or \code{rho1} are specified, 
-#' the algorithm performs gradient searches in the \code{scale} parameter, 
-#' \code{lambda}, \code{delta}, and \code{delta1} (if 3 factors of production are given)
-#' with \code{rho} and \code{rho1} fixed.)
-#' Note that the default arguments for both \code{rho} and \code{rho1} 
-#' include the value 0.25. 
[…]

### 2018-07-30 Packages/EconModels/R/formulaUtils.R

@@ -1,136 +1,0 @@
-#' Utilities for working with formulas
-#' 
-#' Some functions to make it easier to build and minipulate formulas
-
-#' @rdname formula.utils
-#' @param lhs,rhs list or vector of character strings containing summands for left and right hand sides
-#'   of a formula.  \code{NULL}'s are ignored.
-#' @param formula a formula
-#' @param n a vector of integer indices.  Negatives can be used to deselect.
-#' @param env an environment to attach to the formula
-#' @param term a character string containing a new term
-#' @param op The operator to use for splitting into terms.
-#' @param right a logical indicating whether to operate on the right side (else the left) of 
-#'   the formula.
-#' @export
-#' @examples
-#' a <- build_formula(c("a", "b"), c("x", "y", "log(x*y)")); a
-#' b <- build_formula("response", list("x", "y", NULL, "log(x)"), op="*"); b
-#' f <- build_formula( "iGDP", list("iK", "iL", "iQp", "iYear")); f
-#' g <- build_formula( "iGDP", c("iK", "iL", "iQp", "iYear")); g
-#' identical(f,g)
-#' summands(a)
-#' summands(a, right=FALSE)
-#' summands(b, op="*")
-#' keep_summands(f, 3)
-#' keep_summands(f, -3)
-#' keep_summands(f, 2:4)
-#' h <- replace_summand( f, 3, paste(summands(f, 3), lhs(f), sep="/")); h
- 
-build_formula <- function( lhs, rhs, env=parent.frame(), op="+" ) {
-  lhs <- lhs[sapply(lhs, function(x) !is.null(x))]
-  rhs <- rhs[sapply(rhs, function(x) !is.null(x))]
-  res <- as.formula(
-          paste(
-            paste(lhs,  collapse = op), 
-            paste(rhs, collapse = op), 
-            sep="~")
-    )
-  environment(res) <- env
-  res
-}
-
-# drop term n from the RHS of a formula
-# this isn't very robust if "terms" have + in them.  But for simple things it will work.
-
-#' @rdname formula.utils
-#' @export
-#' 
-keep_summands <- function(formula, n, right=TRUE, env=environment(formula), op="+") {
-  formulaString <- deparse(formula)
[…]

### 2018-07-30 Packages/EconModels/R/fortify.R

@@ -1,30 +1,0 @@
-#' fortify LINEX models
-#' 
-#' @param model a LINEX model
-#' @param data a data frame.  Typically this is not needed
-#' since the data are extra from \code{model}.  But this allows
-#' a drop in replacement data set, if desired.
-#' @param ... additional arguments (not currently used)
-#' @export
-#' 
-fortify.LINEXmodel <- function(model, data, ...) {
-  if(missing(data)) { data <- getData(model) }
-  formula <- model$formula
-  data <- model.frame(formula, data)
-  if (ncol(data) != 5) {
-    stop(paste0('Expected 5 variables; I see ', ncol(data)))
-  }
-  l <- data[,2]
-  k <- data[,3]
-  e <- data[,4]
-  a_0 <- naturalCoef(model)[, "a_0", drop=TRUE]
-  c_t <- naturalCoef(model)[, "c_t", drop=TRUE]
-  mutate( data, 
-    # These equations are from Equation 9 in 
-    # B.S. Warr and R.U. Ayres. Useful work and information as drivers of economic growth. 
-    # Ecological Economics, 73(C):93–102, Jan. 2012.
-    alpha = a_0 * (l+e)/k,
-    beta = a_0 * (c_t*l/e - l/k), # or beta = a_1*l/e - a_0*l/k
-    gamma = 1 - alpha - beta
-  )
-}

### 2018-07-30 Packages/EconModels/R/leaf_apply.R

@@ -1,61 +1,0 @@
-#' Applies a function to leaves of a list.
-#' 
-#' This function applies a function to leaves of a nested list (depth-first) if and only if the 
-#' class of the leaf matches one of the names in \code{class}.
-#' 
-#' @param l the list to be traversed.
-#' @param f the function to be applied to the leaves of the list. 
-#' @param class a vector of class names (as quoted strings).  
-#' All and only objects inheriting from any of 
-#' these will be considered a leaf, even if they are also lists.   
-#' Any objects that are neither lists nor inherit from \code{class} will be ignored.
-#' @param strict.lists a logical.  If \code{TRUE}, an item will only be considered a list
-#' if \code{"list"} is the first among its classes.  Setting this to \code{TRUE} may be 
-#' simpler than enumerating all of the possible leaf classes using \code{class}.
-#' @param is.parent a function of an item and item name that returns a logical
-#' indicating whether a node is a leaf.  See the default vaule for examples.
-#' @param name a prefix for the names in the resulting list
-#' @param sep the separator to be used when creating the names of the leaves from the list nesting.
-#' @return a flat, named list of the results of applying \code{f} to the leaves of \code{l}.
-#' @details \code{f} must be of the form \code{f(item, item_name)} where 
-#' \code{item} is a member of \code{l} and 
-#' \code{item_name} is the concatenated name of \code{item} created 
-#' by applying \code{sep} between node names in the list.
-#' @export
-leaf_apply <- 
-  function ( 
-    l, f, class=NULL, name="", sep=".", 
-    strict.lists = FALSE, 
-    is.parent = if (strict.lists) 
-      function(x, n, ...) { class(x)[1] == "list" }
-    else 
-      function(x, n, ...) { is.list(x) && (is.null(class) || !inherits(x, as.character(class))) }
-  ){                      
-  res <- list()
-  list_names <- names(l)
-  if (is.null(list_names)) {
-    list_names <- as.character(1L: length(l)) 
-  }
-  idx <- 0L
-  while(idx < length(l)) {
-    idx <- idx + 1
-    item <- l[[idx]]
-    if (nchar(name) > 0) {
-      item_name <- paste(name, list_names[idx], sep=sep)
-    } else {
-      item_name <- list_names[idx]
-    }
-    
-    if (is.parent(item, item_name)) {
-      # descend
-      res <- c(res, leaf_apply(item, f, name=item_name, is.parent=is.parent, class=class))
[…]

### 2018-07-30 Packages/EconModels/R/utils.R

@@ -1,57 +1,0 @@
-#' Quantiles from Data
-#'
-#' A thin wrapper around \code{\link{quantile}}
-
-
-
-# Provides access to data melting. See http://cran.r-project.org/web/packages/reshape2/reshape2.pdf
-# tikz allows use of LaTeX formatting and font in graphs. Allows for a consistent look across the paper.
-# See http://r-forge.r-project.org/R/?group_id=440 for instructions on installing tikzDevice.
-# require(tikzDevice) 
-# source("Graphics.R")
-
-
-
-#' @param p a vector of probabilities
-#' @param vals a numeric vector or a name of a variable in \code{data}
-#' @param data a data frame
-#' @param ... addtional arguments passed to \code{\link{quantile}}
-#' @return a vector of quantiles
-#' @export
-#' @examples
-#' myqdata( .5, eruptions, data=faithful)
-
-myqdata <- function( p, vals, data = parent.frame(), ...)  {
-  quantile( eval(substitute(vals), data, parent.frame() ), p, ... )
-}
-
-#' @export
-safeMatchArg <- function(arg, choices, several.ok=FALSE) {
-  return( tryCatch( match.arg( arg, choices, several.ok=several.ok), 
-            error=function(e) { choices[1] } )
-  )
-}
-
-
-#' @export
-safeDF <- function(object, nrow=1, ncol=0){
-  if (is.null(object)){
-    return (data.frame(matrix(nrow=nrow, ncol=ncol)))    
-  }
-  emptyDataFrame <- FALSE
-  if (inherits(object,"data.frame") ) {
-    if (nrow(object) + ncol(object) > 0){
-      # We're already a data.frame.
-      return (object)
-    }
-    emptyDataFrame <- TRUE
-  }
-  if ( emptyDataFrame ) {
-    return (data.frame(matrix(nrow=nrow, ncol=ncol)))
-  }
-  return(as.data.frame(object))
-}
-
-as_name_or_null <- function(x) {
-  tryCatch( as.name(x), error = function(e) NULL )
-}

### 2018-07-30 Packages/EconModels/tests/testthat/test-ces-fits.R

@@ -1,168 +1,0 @@
-
-context('Testing CES Model Fits')
-
-library(dplyr, quietly = TRUE)
-library(magrittr, quietly = TRUE)
-require(micEconCES)
-require(testthat)
-require(EconModels)
-
-test_that("cesModel() fits without energy give same results with either nesting.", {
-  testData <- subset(EconData::Calvin, Country=="US")
-  
-  # These models should all give the same results 
-  model12 <- cesModel(iGDP ~ iK + iL + iYear, data = testData, nest = c(1, 2), digits=30)
-  model21 <- cesModel(iGDP ~ iL + iK + iYear, data = testData, nest = c(2, 1), digits=30)
-  # Because both the order of the factors of production and the nest change, 
-  # the coef values from the model should be identical
-  expect_equivalent( coef(model12), coef(model21) )
-  
-  # Because the models are the same except for the order of the factors, the roles of 
-  # alpha_1 and alpha_2 are reversed.
-  expect_equivalent(naturalCoef(model12)["alpha_1", "alpha_2"], naturalCoef(model21)["alpha_2", "alpha_1"])
-  expect_equivalent(sort(naturalCoef(model12)), sort(naturalCoef(model21)))
-  
-  # In this case, we have maintained the order of the factors of production,
-  # but we have a new nest.  However, naturalCoef should associate alpha_1, alpha_2, and alpha_3
-  # with the variables in the order they appear in the production function. 
-  # Thus, we expect the following test to pass.
-  modelkl21 <- cesModel(iGDP ~ iK + iL + iYear, data = testData, nest = c(2, 1), digits=30)
-  expect_equivalent( naturalCoef(model12)[c("alpha_1", "alpha_2", "alpha_3")], 
-                     naturalCoef(modelkl21)[c("alpha_1", "alpha_2", "alpha_3")])
-})
-
-
-test_that("cesModel() fits without energy are correct", {
-  
-  # Use the US factors of production from the Calvin source
-  testData <- subset(EconData::Calvin, Country=="US")
-  
-  # Concoct some data and add it to testData
-  scale <- 1.0 # cesEst calls this "gamma"
-  lambda <- 0.02
-  delta <- 0.3
-  rho <- 0.4
-  nu <- 1.0
-  fitGDP <- cesCalc(xNames = c("iK", "iL"), data = testData, 
[…]

### 2018-07-30 Packages/EconModels/tests/testthat/test-model-fits.R

@@ -1,270 +1,0 @@
-
-context('Testing Model Fits')
-
-library(dplyr, quietly = TRUE)
-library(magrittr, quietly = TRUE)
-
-test_that("cdModel() without energy fits are correct", {
-  
-  # Use the US factors of production from the Calvin source
-  testData <- subset(EconData::Calvin, Country=="US")  
-  
-  # Cobb-Douglas without energy
-  alpha <- -0.1
-  beta <- 1.1
-  gamma <- 0
-  lambda <- 0.02
-  testData <- transform(testData,
-                        fitGDPnoe = exp(lambda * iYear) * iK^alpha * iL^beta)
-  
-  # Fit without constraints
-  modelFree <- cdModel(fitGDPnoe ~ iK + iL + iYear, data = testData, constrained = FALSE, 
-                       save.data = TRUE)
-  # We should obtain scale = 1, because every data point should be fit exactly.
-  # We should obtain gamma = 0, because there is no energy.
-  expect_equivalent(naturalCoef(modelFree)[, c("scale", "alpha_1", "alpha_2", "alpha_3", "lambda"), drop=TRUE], 
-                    list(1, alpha, beta, gamma, lambda) )
-  # Switch K and L in the formula to see if the results change appropriately
-  modelFree2 <- cdModel(fitGDPnoe ~ iL + iK + iYear, data = testData, constrained = FALSE, 
-                        save.data = TRUE)
-  expect_equivalent(naturalCoef(modelFree2)[, c("scale", "alpha_1", "alpha_2", "alpha_3", "lambda"), drop=TRUE], 
-                    list(1, beta, alpha, gamma, lambda) )
-  
-  # Hit the constraint of alpha < 0, beta > 1.
-  modelConstrained <- cdModel(fitGDPnoe ~ iK + iL + iYear, data = testData, 
-                              constrained = TRUE, save.data = TRUE)
-  # scale is not expected to be exactly 1.0, because we will not exactly fit the data. 
-  # lambda is not expected to be exactly the value we used to create testData, 
-  # because we will not exactly fit the data when constrained.
-  # alpha_1 will be 0 instead of -0.1.
-  expect_equivalent(naturalCoef(modelConstrained)[, c("alpha_1", "alpha_2", "alpha_3"), drop=TRUE], 
[…]

### 2018-07-30 ParallelTests/doRedisTest.R

@@ -1,25 +1,0 @@
-# Note: this won't do anything in parallel unless the 
-# redis server is running.
-require(doRedis)
-require(foreach)
-require(mosaic)
-library('doRedis')
-registerDoRedis(queue='jobs')
-startLocalWorkers(n=50, queue='jobs')
-setChunkSize(1)
-print(getDoParWorkers())
-
-sleepy <- 1 + runif(400,-.5,.5) 
-
-etime <- system.time(
-x <- foreach( i = 1:200, .combine=c, .inorder=FALSE ) %dopar% {
-  Sys.sleep(sleepy[i])
-  i
-}
-)[3]
-removeQueue('jobs')
-print(xyplot( x ~ 1:length(x), 
-              main=paste("total:", sum(sleepy[1:length(x)])),
-              sub=paste("time:", etime)
-              ))
-print(etime)

### 2018-07-30 R/Fitting.R

@@ -1,0 +1,881 @@
+#' @importFrom nlme gls
+
+standardES <- function( sigma=NA, sigma_1=NA, sigma_2=NA, nest=1:3, standardize=TRUE) {
+  if (standardize) {
+    nest <- c(nest, c(5,5,5,5))  # add dummy slots so nest has length >= 4
+    nest[1:2] <- sort(nest[1:2])
+    nest[3:4] <- sort(nest[3:4])
+    nest <- nest[nest < 5]      # remove dummy slots
+  }
+  
+  if (length(nest) == 2L) {
+    res <- data.frame(a=sigma_1)
+    names(res) <- paste0("sigma_", nest[1], nest[2])
+    return(res)
+  }
+  
+  if (length(nest) == 3L) {
+    res <- data.frame(a = sigma_1, b = sigma)
+    names(res) <- c( paste0("sigma_", nest[1], nest[2]),
+                     paste0("sigma_", nest[1], nest[2], "_", nest[3]) 
+    )
+    return(res)
+  }
+    res <- data.frame(a = sigma_1, b=sigma_2, c=sigma)
+    names(res) <- c( paste0("sigma_", nest[1], nest[2]),
+                     paste0("sigma_", nest[3], nest[4]),
+                     paste0("sigma_", nest[1], nest[2], "_", nest[3], nest[4])
+    )
+    return(res)
+}
+
+# This function provides alpha_i values for the CES model.
+# It converts from delta_1 and delta to alpha_i in a nest-aware way.
+# The standardCoefs provide the importance of each parameter
+# IN THE ORDER THEY APPEAR IN THE FORMULA,
+# regardless of which nest you choose
+# and regardless of how the values for delta and delta_1 turn out.
+# The point here is that the values of delta and delta_1 are applicable to the permuted
+# variable order during the fitting process.
+# But, we want coefficients that apply to the parameters in the order they appeared
+# in the formula. 
+# standardCoefs does just that.
+# Example: A formula is specified as y ~ a + b + c + time,
+# nest is given as c(3,1,2) such that the parameters (during the estimation process)
+# are permuted to y ~ c + a + b + time.
+# Results will be the following:
+# delta    delta_1    alpha_1   alpha_2    alpha_3
+# 1        1          0         0          1
+# 1        0          1         0          0
+# 0        0 or 1     0         1          0
[…]

### 2018-07-30 R/Graphics.R

@@ -1,0 +1,284 @@
+#' Some Graphics functions
+#' 
+#' Some graphics functions for working with Economic Models.
+#'
+#' @import ggplot2
+#' @import mosaic
+#' @import scales
+
+#' @export
+tri2x <- function(x,y,z) {
+    y * 1 + z * 0.5   # + x * 0 
+}
+
+#' @export
+tri2y <- function(x,y,z) {
+  z * 1 # + x * 0 + y * 0 
+}
+
+#' @export
+tri_theme <- function(base_size=12, base_family = "", base_theme=theme_bw) {
+    xy_theme_old(base_size = base_size, base_family = base_family) %+replace% 
+      theme(panel.border = element_blank(), 
+            axis.line = element_blank(),
+            axis.text = element_blank(),
+            axis.ticks = element_blank(),
+            axis.title = element_blank(),
+            panel.grid.major = element_blank(), 
+            panel.grid.minor = element_blank(),
+            plot.background = element_blank(),  
+            strip.background =  element_rect(fill = NA, colour = xy_theme_old()$axis.text$colour)
+            )
+}  
+
+#' @export
+xy_theme_old <- function(base_size=12, base_family = "", base_theme=theme_bw, label_colour="gray50") {
+  base_theme(base_size = base_size, base_family = base_family) %+replace% 
+    theme(# panel.border = element_blank(), 
+          # panel.grid.major = element_blank(), 
+          panel.grid.minor = element_blank(),
+          plot.background = element_blank(),
+          strip.text = element_text(colour=label_colour, size=.8 * base_size),
+          strip.background =  element_rect(fill = NA, colour = NA),
+          legend.background = element_rect(fill=NA, colour=NA),
+          legend.key= element_rect(fill=NA, colour=NA),
+          legend.text=element_text(colour=label_colour),
+          axis.text = element_text(colour=label_colour, size=.8 * base_size), 
+          axis.ticks = element_blank(),
+          axis.title = element_text(colour=label_colour, size=base_size)
+    )
+}
+
+#' @export
+xy_theme <- function(base_size=12, base_family = "", base_theme=theme_bw, label_colour="gray50") {
+  # See https://github.com/infotroph/ggplot-ticks if we want to mirror ticks on top and right.
[…]

### 2018-07-30 R/cesBoundaryModels.R

@@ -1,0 +1,189 @@
+
+#' Fits CES boundary models
+#' 
+#' The boundary models are given in Table 2 of 
+#' Heun, et al "An Empirical Investigation of the Role of Energy in Economic Growth"
+#'
+#' @param formula a CES formula in the form \code{y ~ a + b + c + d + time}
+#' @param data historical time series data
+#' @param nest a permutation of the integers 1 to the number of factors describing how to nest and permute
+#'   the variables in the formula.
+#' @return a list of boundary models.
+#' @examples 
+#' if (require(EconData) & require(dplyr)) {
+#'   cesBoundaryModels(iGDP ~ iK + iL + iQp + iYear, data=Calvin %>% filter(Country=="US"), nest=c(1,2,3))
+#'   cesBoundaryModels(iGDP ~ iK + iL + iQp + iYear, data=Calvin %>% filter(Country=="US"), nest=c(2,3,1))
+#'   cesBoundaryModels(iGDP ~ iK + iL + iYear, data=Calvin %>% filter(Country=="US"), nest=c(1,2))
+#'   }
+#' @export
+
+cesBoundaryModels <- function(formula, data, nest, method="nlm", subset=TRUE){
+  # f <- formula  # to avoid problems while renaming is happening.
+ 
+  # use same data for all models, even if some models could make use of more complete data. 
+  d <- subset(data, select = intersect(all.vars(formula), names(data)))
+  sdata <- data[complete.cases(d), unique(c(intersect(all.vars(formula), names(data)), names(data)))]
+  
+
+  numFactors <- cesParseFormula(formula, nest)$numFactors
+  numFactorsInFormula <- cesParseFormula(formula, nest)$numFactorsInFormula
+    
+  if ( ! numFactors %in% 2:3 ) {
+    stop("model must have 2 or 3 factors.")
+  }
+ 
+  if (numFactorsInFormula >=3) { 
+    formulaRosetta <- list(
+      y = formula[[2]],
+      x1 = formula[[3]][[2]][[2]][[2]],
+      x2 = formula[[3]][[2]][[2]][[3]],
+      x3 = formula[[3]][[2]][[3]],
+      time = formula[[3]][[3]]
+    ) 
+    
[…]

### 2018-07-30 R/cesModel.R

@@ -1,0 +1,422 @@
+
+#' Fitting CES models
+#' 
+#' This function fits a CES model
+#' @param formula a formula of the form \code{response ~ a + b + c + d + time}.  
+#' \code{c} and \code{d} are optional.
+#' @param data a data frame, in which to evaluate the formula.
+#' @param response instead of specifying a formula, expressions for
+#' the components can be specified individually.
+#' @param x1 instead of specifying a formula, expressions for
+#' the components can be specified individually as character strings.
+#' @param x2 instead of specifying a formula, expressions for
+#' the components can be specified individually as character strings.
+#' @param x3 instead of specifying a formula, expressions for
+#' the components can be specified individually as character strings.
+#' @param x4 instead of specifying a formula, expressions for
+#' the components can be specified individually as character strings.
+#' @param time instead of specifying a formula, expressions for
+#' the components can be specified individually as character strings.
+#' @param nest a permutation (a,b,c,d) of the integers 1 through 4.
+#' For models with 3 factors, the nesting
+#' is (xa + xb) + xc.  For 4 factors, the nesting is (xa + xb) + (xc + xd)
+#' @param prevModel a model used to start a gradient search.
+#' \code{prevModel} will be used as a starting point for a gradient search after both
+#' (a) grid search in \code{rho} and \code{rho1} and 
+#' (b) a gradient search starting from the best grid search 
+#' are complete.
+#' #' Use \code{NULL} (the default value) 
+#' if you want to skip the gradient search from a previous model.
+#' @param multErr logical, tells whether errors are to be assessed in a multiplicative manner
+#' @param rho,rho1 creates a grid upon which gradient searches in all other (free) parameters will be made.
+#' (I.e., when \code{rho} and/or \code{rho1} are specified, 
+#' the algorithm performs gradient searches in the \code{scale} parameter, 
+#' \code{lambda}, \code{delta}, and \code{delta1} (if 3 factors of production are given)
+#' with \code{rho} and \code{rho1} fixed.)
+#' Note that the default arguments for both \code{rho} and \code{rho1} 
+#' include the value 0.25. 
[…]

### 2018-07-30 R/elasticity.R

@@ -1,0 +1,107 @@
+
+#' @export
+inputs <- function(object, ...) {
+  UseMethod("inputs")
+}
+
+#' @export
+inputs.cesModel <- function(object, ...) {
+  head(tail(all.vars(object$formula), -1), -1)
+}
+
+
+#' @export
+fortify.cesModel <- function(model, data = NULL, ...) {
+  if (is.null(data)) data <- model$data
+  
+  bind_cols(
+    data,
+    output_elasticity(model) %>% 
+      select( starts_with("oe"), starts_with("alph"), starts_with("x"))
+    )
+}
+
+#' @export
+output_elasticity <- function(object, ...) {
+  UseMethod("output_elasticity")
+}
+
+#' @export
+output_elasticity.cesModel <- function(object, ...) {
+ 
+  cf <- naturalCoef(object)
+ 
+  inputVars <- inputs(object)
+  # adjust for nest, if we have one recorded:
+  if (!is.null(object$nest)) {
+    inputVars <- inputVars[object$nest] 
+  }
+  
+  output_elasticity(
+    delta = cf$delta, 
+    delta1 = cf$delta_1, 
+    alpha1 = cf$alpha_1,
+    alpha2 = cf$alpha_2,
+    alpha3 = cf$alpha_3, 
+    rho = cf$rho,
+    rho1 = cf$rho_1,
+    x1 = object$data[[inputVars[1]]],
+    x2 = object$data[[inputVars[2]]],
+    x3 = object$data[[inputVars[3]]]
+  )
+}
+
+#' @export
+output_elasticity.default <- function( 
+  object,
+  delta, delta1, 
+  alpha1 = delta * delta1,
+  alpha2 = delta * (1 - delta1),
+  alpha3 = (1 - delta),
+  rho,
+  rho1,
+  x1,
+  x2,
+  x3,
+  ...) {
+ 
+  product <- function( x, y ) {
+    ifelse( ((x == 0) & is.na(y)) | ((y == 0) & is.na(x)), 0, x * y )
+  }
+ 
+  delta <- 1 - alpha3
+  delta1 <- ifelse( delta == 0,  NA, alpha1 / delta )
[…]

### 2018-07-30 R/formulaUtils.R

@@ -1,0 +1,136 @@
+#' Utilities for working with formulas
+#' 
+#' Some functions to make it easier to build and minipulate formulas
+
+#' @rdname formula.utils
+#' @param lhs,rhs list or vector of character strings containing summands for left and right hand sides
+#'   of a formula.  \code{NULL}'s are ignored.
+#' @param formula a formula
+#' @param n a vector of integer indices.  Negatives can be used to deselect.
+#' @param env an environment to attach to the formula
+#' @param term a character string containing a new term
+#' @param op The operator to use for splitting into terms.
+#' @param right a logical indicating whether to operate on the right side (else the left) of 
+#'   the formula.
+#' @export
+#' @examples
+#' a <- build_formula(c("a", "b"), c("x", "y", "log(x*y)")); a
+#' b <- build_formula("response", list("x", "y", NULL, "log(x)"), op="*"); b
+#' f <- build_formula( "iGDP", list("iK", "iL", "iQp", "iYear")); f
+#' g <- build_formula( "iGDP", c("iK", "iL", "iQp", "iYear")); g
+#' identical(f,g)
+#' summands(a)
+#' summands(a, right=FALSE)
+#' summands(b, op="*")
+#' keep_summands(f, 3)
+#' keep_summands(f, -3)
+#' keep_summands(f, 2:4)
+#' h <- replace_summand( f, 3, paste(summands(f, 3), lhs(f), sep="/")); h
+ 
+build_formula <- function( lhs, rhs, env=parent.frame(), op="+" ) {
+  lhs <- lhs[sapply(lhs, function(x) !is.null(x))]
+  rhs <- rhs[sapply(rhs, function(x) !is.null(x))]
+  res <- as.formula(
+          paste(
+            paste(lhs,  collapse = op), 
+            paste(rhs, collapse = op), 
+            sep="~")
+    )
+  environment(res) <- env
+  res
+}
+
+# drop term n from the RHS of a formula
+# this isn't very robust if "terms" have + in them.  But for simple things it will work.
+
+#' @rdname formula.utils
+#' @export
+#' 
+keep_summands <- function(formula, n, right=TRUE, env=environment(formula), op="+") {
+  formulaString <- deparse(formula)
[…]

### 2018-07-30 R/leaf_apply.R

@@ -1,0 +1,61 @@
+#' Applies a function to leaves of a list.
+#' 
+#' This function applies a function to leaves of a nested list (depth-first) if and only if the 
+#' class of the leaf matches one of the names in \code{class}.
+#' 
+#' @param l the list to be traversed.
+#' @param f the function to be applied to the leaves of the list. 
+#' @param class a vector of class names (as quoted strings).  
+#' All and only objects inheriting from any of 
+#' these will be considered a leaf, even if they are also lists.   
+#' Any objects that are neither lists nor inherit from \code{class} will be ignored.
+#' @param strict.lists a logical.  If \code{TRUE}, an item will only be considered a list
+#' if \code{"list"} is the first among its classes.  Setting this to \code{TRUE} may be 
+#' simpler than enumerating all of the possible leaf classes using \code{class}.
+#' @param is.parent a function of an item and item name that returns a logical
+#' indicating whether a node is a leaf.  See the default vaule for examples.
+#' @param name a prefix for the names in the resulting list
+#' @param sep the separator to be used when creating the names of the leaves from the list nesting.
+#' @return a flat, named list of the results of applying \code{f} to the leaves of \code{l}.
+#' @details \code{f} must be of the form \code{f(item, item_name)} where 
+#' \code{item} is a member of \code{l} and 
+#' \code{item_name} is the concatenated name of \code{item} created 
+#' by applying \code{sep} between node names in the list.
+#' @export
+leaf_apply <- 
+  function ( 
+    l, f, class=NULL, name="", sep=".", 
+    strict.lists = FALSE, 
+    is.parent = if (strict.lists) 
+      function(x, n, ...) { class(x)[1] == "list" }
+    else 
+      function(x, n, ...) { is.list(x) && (is.null(class) || !inherits(x, as.character(class))) }
+  ){                      
+  res <- list()
+  list_names <- names(l)
+  if (is.null(list_names)) {
+    list_names <- as.character(1L: length(l)) 
+  }
+  idx <- 0L
+  while(idx < length(l)) {
+    idx <- idx + 1
+    item <- l[[idx]]
+    if (nchar(name) > 0) {
+      item_name <- paste(name, list_names[idx], sep=sep)
+    } else {
+      item_name <- list_names[idx]
+    }
+    
+    if (is.parent(item, item_name)) {
+      # descend
+      res <- c(res, leaf_apply(item, f, name=item_name, is.parent=is.parent, class=class))
[…]

### 2018-07-30 R/plm.R

@@ -1,0 +1,125 @@
+#' Parameterized Linear Models
+#' 
+#' The optimal model is fit in a case where aside from some parameters, the model is linear.  
+#' Numerical optimization is used over these parameters with \code{lm} fitting the rest.
+#' @param formula a formula describing the model
+#' @param data a data frame
+#' @param params a named vector of the parameters to be fit by numerical optimation outside of \code{lm}.
+#' @param optimize a logical indicating whether \code{params} should be plugged in or used as the seed
+#'   for the numerical optimization
+#' @param .ocall used for recursive calling
+#' @param ... additional arguments, currently ignored.
+#' @return On object of class \code{c("plm", "lm")} which is an enhanced \code{"lm"} object.
+#' @export
+#' @examples
+#' if( require(EconData) & require(dplyr) ) {
+#' plm( log(iGDP) - log(iK) ~ iYear, 
+#'      data=Calvin %>% filter(Country=="US"))
+#'      
+#' plm( log(iGDP) - delta * iK - (1-delta) * iL ~ iYear, 
+#'      data=Calvin %>% filter(Country=="US"), 
+#'      params=c(delta=0.4), 
+#'      optimize=FALSE ) 
+#' 
+#' plm( log(iGDP) - delta * iK - (1-delta) * iL ~ iYear, data=Calvin %>% filter(Country=="US"), 
+#'      params=c(delta=0.4), 
+#'      optimize=TRUE ) 
+#'      
+#' plm( log(iGDP) - delta * iK - (1-delta) * iL ~ iYear, data=Calvin %>% filter(Country=="US"), 
+#'      params=c(delta=0.4), method=c("nlm", "spg"),
+#'      optimize=TRUE ) 
+#' 
+#' foo <- plm( log(iGDP / delta*(delta_1*iK + (1-delta_1)*iL) + (1-delta)*iQp) ~ iYear,
+#'             data=Calvin %>% filter(Country=="US"), 
+#'             params=c(delta=0.5, delta_1=0.5))
+#' foo
+#' class(foo)
+#' }
+
+plm <- function( formula, data=parent.frame(), params=c(), optimize=TRUE, .ocall=NULL, method="nlm", ..., debug=FALSE ) {
+  if(is.null(.ocall)) .ocall <- match.call()
+ 
+  orig_params <- params
+  
+  used_params_names <- intersect( names(params), all.vars(formula))
+  unused_params_names <- setdiff( names(params), all.vars(formula))
[…]

### 2018-07-30 R/trianglePlots.R

@@ -1,0 +1,162 @@
+#' @rdname triplot
+#' @export
+StatTriangle <- 
+  ggproto("StatTriangle", Stat, 
+          compute_group = function(data, scales) {
+            x0 <- c(0, 0)
+            y0 <- c(1, 0)
+            z0 <- c(0.5, 1)
+            T <- as.matrix(data[, c("x", "y", "z")]) %*% rbind(x0, y0, z0)
+            data$xorig <- data$x
+            data$yorig <- data$y
+            data$zorig <- data$z
+            data$x <- T[,1]
+            data$y <- T[,2]
+            data['z'] <- NULL
+            data
+          },
+                     
+          required_aes = c("x", "y", "z")
+)
+
+#' @rdname triplot
+#' @export
+stat_triangle <- 
+  function(
+    mapping = NULL, data = NULL, 
+    geom = "point", position = "identity", 
+    show.legend = NA, inherit.aes = TRUE, ...) {
+    layer(
+      stat = StatTriangle, data = data, mapping = mapping, geom = geom, 
+      position = position, show.legend = show.legend, inherit.aes = inherit.aes,
+      params = list(...)
+    )
+  }
+
+#' Triangle Plots
+#' 
+#' Triangle Plots
+#' 
+#' @rdname triplot
+#' @export
+#' @examples
+#' ddd <- data_frame( x=c(1, 0, .5, .25, 0), y = c(0, .2, .2, .25, .8)) %>% mutate(z = 1 - x - y) 
+#' ggplot()  + 
+#'   tri_theme() + 
+#'   tri_grid(colour="red") +  
+#'   tri_labels(size=10, padding=.05) + 
+#'   geom_path(data=ddd, aes(x=x, y=y, z=z), stat="triangle", size=2, alpha=.3) +
+#'   geom_point(data=ddd, aes(x=x, y=y, z=z), stat="triangle", size=3, alpha=.6, colour="navy")
+#' 
+tri_grid <- function(colour = color, color = "gray70", grid_lines = 5, 
+                     labels = c("alpha[1]", "alpha[2]", "alpha[3]"), 
+                     ...) {
+  h <- seq(0, 1, by=1/grid_lines)
+  n <- length(h)
+  zero <- rep(0, n)
+  one <- rep(1, n)
+  ids <- 1:n
+  
+  lines_data <- data_frame(
+    x = c(   h,    h, zero,  1-h, zero,  1-h ), 
[…]

### 2018-07-30 R/utils.R

@@ -1,0 +1,57 @@
+#' Quantiles from Data
+#'
+#' A thin wrapper around \code{\link{quantile}}
+
+
+
+# Provides access to data melting. See http://cran.r-project.org/web/packages/reshape2/reshape2.pdf
+# tikz allows use of LaTeX formatting and font in graphs. Allows for a consistent look across the paper.
+# See http://r-forge.r-project.org/R/?group_id=440 for instructions on installing tikzDevice.
+# require(tikzDevice) 
+# source("Graphics.R")
+
+
+
+#' @param p a vector of probabilities
+#' @param vals a numeric vector or a name of a variable in \code{data}
+#' @param data a data frame
+#' @param ... addtional arguments passed to \code{\link{quantile}}
+#' @return a vector of quantiles
+#' @export
+#' @examples
+#' myqdata( .5, eruptions, data=faithful)
+
+myqdata <- function( p, vals, data = parent.frame(), ...)  {
+  quantile( eval(substitute(vals), data, parent.frame() ), p, ... )
+}
+
+#' @export
+safeMatchArg <- function(arg, choices, several.ok=FALSE) {
+  return( tryCatch( match.arg( arg, choices, several.ok=several.ok), 
+            error=function(e) { choices[1] } )
+  )
+}
+
+
+#' @export
+safeDF <- function(object, nrow=1, ncol=0){
+  if (is.null(object)){
+    return (data.frame(matrix(nrow=nrow, ncol=ncol)))    
+  }
+  emptyDataFrame <- FALSE
+  if (inherits(object,"data.frame") ) {
+    if (nrow(object) + ncol(object) > 0){
+      # We're already a data.frame.
+      return (object)
+    }
+    emptyDataFrame <- TRUE
+  }
+  if ( emptyDataFrame ) {
+    return (data.frame(matrix(nrow=nrow, ncol=ncol)))
+  }
+  return(as.data.frame(object))
+}
+
+as_name_or_null <- function(x) {
+  tryCatch( as.name(x), error = function(e) NULL )
+}

### 2018-07-30 Rbuildignore/ParallelTests/doRedisTest.R

@@ -1,0 +1,25 @@
+# Note: this won't do anything in parallel unless the 
+# redis server is running.
+require(doRedis)
+require(foreach)
+require(mosaic)
+library('doRedis')
+registerDoRedis(queue='jobs')
+startLocalWorkers(n=50, queue='jobs')
+setChunkSize(1)
+print(getDoParWorkers())
+
+sleepy <- 1 + runif(400,-.5,.5) 
+
+etime <- system.time(
+x <- foreach( i = 1:200, .combine=c, .inorder=FALSE ) %dopar% {
+  Sys.sleep(sleepy[i])
+  i
+}
+)[3]
+removeQueue('jobs')
+print(xyplot( x ~ 1:length(x), 
+              main=paste("total:", sum(sleepy[1:length(x)])),
+              sub=paste("time:", etime)
+              ))
+print(etime)

### 2018-07-30 Rbuildignore/Testing/FunkySpaghetti/FunkySpaghetti.R

@@ -1,0 +1,94 @@
+require(EconData)
+require(EconModels)
+require(ggplot2)
+
+# setwd() to the location of this file.
+ppData <- loadPostProcessedData(Source = "REXS1960", kind = "fitted", dir="../../data_postprocessed/")
+ppData <- subset(ppData, subset=model=="cd" & energy=="none" & Country=="US")
+
+# Find any fits where iGDP in 2009 is below 4. Resample 777 is the problem!
+ppData2009 <- subset(ppData, subset=Year==2009 & iGDP.hat<4)
+ppData2009_777 <- subset(ppData, subset=resampleNumber==777)
+
+# Make the graph without resample number 777. It looks clean!
+spaghettiPlot(data=subset(ppData, subset=resampleNumber != 777 | !resampled), facet_formula=Country~energy, level=1.0) + 
+  labs(y="Indexed GDP (1960=1)")
+
+# Now make the plot with resample number 777. Funky Spaghetti!
+plot <- spaghettiPlot(data=ppData, facet_formula=Country~energy, level=1.0) + labs(y="Indexed GDP (1960=1)")
+show(plot)
+
+# Get the original resamples from the "models_" file.
+resampleModels <- readRDS("models_US_cd_iK+iL.Rdata")
+model777 <- resampleModels[[778]] # the first model is the original fit to historical data
+data777 <- attr(model777, "data")
+yhat777 <- yhat(model777)
+data777 <- cbind(data777, yhat777)
+
+# Verify that we have the right model.
+cat(paste("Do we have the right model?", all.equal(ppData2009_777$iGDP.hat, data777$yhat777)))
+
+# Draw the plot using a red line for resampleNumber==777
+plot <- plot + geom_line(data=ppData2009_777, mapping=aes(x=Year, y=iGDP.hat, color=as.character(resampleNumber)))
+show(plot)
+
+# Draw dots for the resample data
+plot <- plot + geom_point(data=data777, mapping=aes(x=Year, y=iGDP))
+show(plot)
+
+# Fit data777 using our functions
+newModel777 <- cdModel(formula = iGDP ~ iK + iL + iYear, data = data777, constrained = TRUE, save.data = TRUE)
+# Compare coefficients of cdModel777 to coefficients of model777
+cat(paste("Are all coefficients of model777 and newModel777 same?", all.equal(model777$coefficients, newModel777$coefficients)))
[…]

### 2018-07-30 Scrap/Econ-Growth-Functions.R

@@ -1,2741 +1,0 @@
-## <<setup_parent, echo=FALSE, message=FALSE, eval=TRUE>>=
-require(lattice)
-require(latticeExtra)
-require(ggplot2)
-require(car)
-require(mosaic)
-require(xtable)
-require(nlmrt)
-require(micEconCES)
-require(reshape2) # Provides access to data melting. See http://cran.r-project.org/web/packages/reshape2/reshape2.pdf
-# tikz allows use of LaTeX formatting and font in graphs. Allows for a consistent look across the paper.
-# See http://r-forge.r-project.org/R/?group_id=440 for instructions on installing tikzDevice.
-if (! require(tikzDevice) ) warning( "tikzDevice not loaded" )
-
-# Statistical significance levels. We'll work with 95% CIs
-ciLevel <- 0.95
-ciHalfLevel <- ciLevel + (1.0-ciLevel)/2.0
-# List of countries
-countryAbbrevs <- c(US="US", UK="UK", JP="JP", CN="CN", ZA="ZA", SA="SA", IR="IR", TZ="TZ", ZM="ZM")
-countryAbbrevsAlph <- c(CN="CN", IR="IR", JP="JP", SA="SA", TZ="TZ", UK="UK", US="US", ZA="ZA", ZM="ZM")
-countryAbbrevsU <- c(US="US", UK="UK", JP="JP") #Only these countries have useful work data
-countryAbbrevsAlphU <- c(JP="JP", UK="UK", US="US")
-countryNamesAlph <- c(CN="China", IR="Iran", JP="Japan", SA="Saudi Arabia", TZ="Tanzania", UK="United Kingdom", US="USA", ZA="South Africa", ZM="Zambia") #In alphabetical order.
-countryNamesAlphU <- c(JP="Japan", UK="United Kingdom", US="USA") #In alphabetical order.
-yLimitsForGDPGraphs <- list(c(1,10), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4)) # Alph order
-energyTypes <- c(Q="Q", X="X", U="U") # List of energy types
-factors <- c(K="K", L="L", Q="Q", X="X", U="U") # List of factors of production
-########### Several global parameters for graphs. Set here and use below to ensure consistent appearance of graphs.
-# Set the order for presenting countries in 3x3 lattice graphs. Default is alphabetical. 
[…]

### 2018-07-30 Scrap/Econ-Growth-Functions2.R

@@ -1,3530 +1,0 @@
-require(lattice)
-require(latticeExtra)
-require(ggplot2)
-require(plyr)    # for rbind.fill
-require(car)
-require(mosaic)
-require(xtable)
-require(nlmrt)
-require(micEconCES)
-require(reshape2) # Provides access to data melting. See http://cran.r-project.org/web/packages/reshape2/reshape2.pdf
-# tikz allows use of LaTeX formatting and font in graphs. Allows for a consistent look across the paper.
-# See http://r-forge.r-project.org/R/?group_id=440 for instructions on installing tikzDevice.
-# require(tikzDevice) 
-source("Graphics.R")
-
-myqdata <- function( p, vals, data = parent.frame(), ...)  {
-  quantile( p, eval(vals, data, parent.frame() ) )
-}
-
-# Statistical significance levels. We'll work with 95% CIs
-ciLevel <- 0.95
-ciHalfLevel <- ciLevel + (1.0-ciLevel)/2.0
-ciVals <- c(lower=1-ciHalfLevel, upper=ciHalfLevel)
-# List of countries
-countryAbbrevs <- c(US="US", UK="UK", JP="JP", CN="CN", ZA="ZA", SA="SA", IR="IR", TZ="TZ", ZM="ZM")
-countryAbbrevsAlph <- sort(countryAbbrevs)
-countryAbbrevsFor3x3Graph <- c(US="US", UK="UK", JP="JP", CN="CN", ZA="ZA", TZ="TZ", SA="SA", IR="IR", ZM="ZM")
-countryAbbrevsU <- c(US="US", UK="UK", JP="JP") #Only these countries have useful work data
-countryAbbrevsAlphU <- sort(countryAbbrevsU)
-countryAbbrevsForGraphU <- c(US="US", UK="UK", JP="JP")
-countryNamesAlph <- c(CN="China", IR="Iran", JP="Japan", SA="Saudi Arabia", TZ="Tanzania", UK="United Kingdom", US="USA", ZA="South Africa", ZM="Zambia") #In alphabetical order.
-countryNamesAlphU <- c(JP="Japan", UK="United Kingdom", US="USA") #In alphabetical order.
-yLimitsForGDPGraphs <- list(c(1,10), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4)) # Alph order
[…]

### 2018-07-30 Scripts/DownloadPostProcessed.R

@@ -1,83 +1,0 @@
-#!/usr/bin/Rscript
-# 
-# This script rsyncs post-processed resampling results files 
-# from the directory specified by -p on dahl (or the default)
-# to the Packages/EconData/tmp_big_data directory on a local machine.
-# Files that are rsync-ed match the pattern "<SOURCE>_*"
-# 
-# IMPORTANT:
-# If you want to include the files in the EconData package for an analysis, 
-# move them manually to the Packages/EconData/data directory and build and reload the EconData package.
-# 
-# Usage: in the top-level directory of this repository (Econ-Growth-R-Analysis) on the destination machine, say
-# Scripts/DownloadResults.bash -u mkh2 -S REXS
-#   -u indicates the user you want to be on dahl
-#   -S identifies the data <Source> for which you want to rsync results.
-#   -p identifies the directory on dahl from which you want to rsync results.
-#
-# You'll be prompted for the password for the user specified by -u on dahl.
-
-suppressPackageStartupMessages(library("optparse"))
-
-option_list <- list(
-  make_option(c("-u", "--username"),
-              help="Sets the username for dahl."),
-  make_option(c("-S", "--Source"), default="Calvin",
-              help="Comma-separated list of <Source>s to be copied. No spaces allowed. [default=%default]"),
-  make_option(c("-d", "--debug"), default=FALSE, action="store_true",
-              help="Debug mode. No files transferred. Reports what would have been done. [default=%default]"),
-  make_option(c("-p", "--path"), default="/home/mkh2/github/Econ-Growth-R-Analysis/data_postprocessed",
-              help=paste("Sets path of postprocessed data directory on dahl from which you want to copy. \n",
-                         "               Do not include tralining file separator. \n",
-                         "               [default=%default]")),
-  make_option(c("-l", "--lpath"), default="data_postprocessed",
-              help=paste("Sets path of postprocessed data directory on local machine to which you want to copy. \n",
-                         "               This path must be relative to the Econ-Growth-R-Analysis directory. \n",
-                         "               Do not include trailing file separator. \n",
-                         "               [default=%default]"))
-)
-
-opts <- parse_args(OptionParser(
-  description = paste0("Copies post-processed resampling results from dahl to a local machine. \n",
[…]

### 2018-07-30 Scripts/OrigModels2.R

@@ -1,220 +1,0 @@
-#!/usr/bin/Rscript  --default-packages=utils,stats,lattice,grid,mosaic,methods,graphics,foreach,doParallel,xtable,nlmrt,micEconCES,systemfit,Matrix,lmtest,zoo,miscTools,micEcon,minpack.lm,DEoptim,iterators,parallel,latticeExtra,RColorBrewer,ggplot2,reshape2,scales
-#
-# This script fits all of the base models for each combination of 
-# source, country, model, factor, energy type, and nesting.
-# 
-# This script should be run from the top directory (Econ-Growth-R-Analysis) with the command
-# "Scripts/OrigModels.R -S <Sources>"
-#
-
-# Results are stored in the file "outputDir/<Source>/oModels.rds"
-# To load this data back in, do 
-# 
-# oModels <- readRDS(file="outputDir/<Source>/oModels.rds")
-#
-# To extract a model, do, for example
-# mod <- oModels$REXS$US$cd$`iK+iL+iQ`
-
-suppressPackageStartupMessages( require(EconModels) )
-suppressPackageStartupMessages( require(EconData) )
-suppressPackageStartupMessages( require(optparse) )
-suppressPackageStartupMessages( require(parallel) )
-
-nestStr <- function(nest){
-  paste(nest, collapse="")
-}
-
-defaultOutputDir <- "data_resample"
-filename_oModels <- "oModels.rds"
-filename_models <- "oModels_flat.rds"
-
-# Provide a way to specify data sources in a comma-separated list
-option_list <- list(
-  make_option(c("-S", "--Sources"), default="Calvin",
-              help="Comma-separated list of sources of data [default=%default]"),
-  make_option(c("-f", "--fast"), default=FALSE, action="store_true",
-              help="Runs fast models (skips CES with energy) [default=%default]"),
-  make_option(c("-v", "--veryfast"), default=FALSE, action="store_true",
-              help="Runs very fast models (skips CES altogether). Overrides -f. [default=%default]"),
-  make_option(c("-V", "--verbose"), default=FALSE, action="store_true",
-              help="More verbose output [default=%default]"),
-  make_option(c("-O", "--outputDir"), default=defaultOutputDir,
-              help=paste0("relative path to directory ",
-                          "in which original models are saved ",
-                          "(one level above the <Source> directories) [default=",
[…]

### 2018-07-30 Testing/FunkySpaghetti/FunkySpaghetti.R

@@ -1,94 +1,0 @@
-require(EconData)
-require(EconModels)
-require(ggplot2)
-
-# setwd() to the location of this file.
-ppData <- loadPostProcessedData(Source = "REXS1960", kind = "fitted", dir="../../data_postprocessed/")
-ppData <- subset(ppData, subset=model=="cd" & energy=="none" & Country=="US")
-
-# Find any fits where iGDP in 2009 is below 4. Resample 777 is the problem!
-ppData2009 <- subset(ppData, subset=Year==2009 & iGDP.hat<4)
-ppData2009_777 <- subset(ppData, subset=resampleNumber==777)
-
-# Make the graph without resample number 777. It looks clean!
-spaghettiPlot(data=subset(ppData, subset=resampleNumber != 777 | !resampled), facet_formula=Country~energy, level=1.0) + 
-  labs(y="Indexed GDP (1960=1)")
-
-# Now make the plot with resample number 777. Funky Spaghetti!
-plot <- spaghettiPlot(data=ppData, facet_formula=Country~energy, level=1.0) + labs(y="Indexed GDP (1960=1)")
-show(plot)
-
-# Get the original resamples from the "models_" file.
-resampleModels <- readRDS("models_US_cd_iK+iL.Rdata")
-model777 <- resampleModels[[778]] # the first model is the original fit to historical data
-data777 <- attr(model777, "data")
-yhat777 <- yhat(model777)
-data777 <- cbind(data777, yhat777)
-
-# Verify that we have the right model.
-cat(paste("Do we have the right model?", all.equal(ppData2009_777$iGDP.hat, data777$yhat777)))
-
-# Draw the plot using a red line for resampleNumber==777
-plot <- plot + geom_line(data=ppData2009_777, mapping=aes(x=Year, y=iGDP.hat, color=as.character(resampleNumber)))
-show(plot)
-
-# Draw dots for the resample data
-plot <- plot + geom_point(data=data777, mapping=aes(x=Year, y=iGDP))
-show(plot)
-
-# Fit data777 using our functions
-newModel777 <- cdModel(formula = iGDP ~ iK + iL + iYear, data = data777, constrained = TRUE, save.data = TRUE)
-# Compare coefficients of cdModel777 to coefficients of model777
-cat(paste("Are all coefficients of model777 and newModel777 same?", all.equal(model777$coefficients, newModel777$coefficients)))
[…]

### 2018-07-30 Testing/RefactorTesting.R

@@ -1,39 +1,0 @@
-require(EconModels)
-require(EconData)
-
-data(AllHistData)
-All <- subset(AllHistData, subset=Source=="Calvin2011")
-
-model.cd1 <-  cdwoeModel( response = iY, capital=iK, labor=iL, time=iYear, data=subset(All, Country=="US") )
-naturalCoef( model.cd1 )
-
-model.cd2 <- cdwoeModel( iY ~ iK + iL + iYear, data=subset(All, Country=="US") )
-naturalCoef( model.cd2 )
-
-model.cde1 <- cdeModel( response = iY, capital=iK, labor=iL, energy=iU, time=iYear, data=subset(All, Country=="US") )
-naturalCoef( model.cde1)
-
-model.cde2 <- cdeModel( iY ~ iK + iL + iU + iYear, data=subset(All, Country=="US") )
-naturalCoef( model.cde2 )
-
-model.linex1 <- linexModel( iY ~ iK + iL + iU + iYear, data=subset(All, Country=="US") )
-naturalCoef( model.linex1 )
-
-model.linex2 <-  linexModel( response=iY, capital= iK, labor=iL, energy=iU, time= iYear, 
-               data=subset(All, Country=="US") )
-naturalCoef( model.linex2 )
-
-model.sf1 <-  sfModel( iY ~ iK + iYear, data=subset(All, Country=="US") )
-naturalCoef( model.sf1 )
-
-model.sf2 <- sfModel( response=iY, factor=iK, time=iYear, data=subset(All, Country=="US") )
-naturalCoef( model.sf2 )
-
-model.sf3 <- sfModel( iY ~ iK + iYear, data=subset(All, Country=="US"), constrained=TRUE )
-naturalCoef( model.sf3 ) 
-
-model.ces1 <- cesModel( iY ~ iK + iL + iQ + iYear, data=subset(All, Country=="US"))
-naturalCoef(model.ces1)
-
-model.ces2 <- cesModel( iY ~ iK + iL + iU + iYear, data=subset(All, Country=="US"))
-naturalCoef(model.ces2)

### 2018-07-30 tests/testthat/test-ces-fits.R

@@ -1,0 +1,168 @@
+
+context('Testing CES Model Fits')
+
+library(dplyr, quietly = TRUE)
+library(magrittr, quietly = TRUE)
+require(micEconCES)
+require(testthat)
+require(EconModels)
+
+test_that("cesModel() fits without energy give same results with either nesting.", {
+  testData <- subset(EconData::Calvin, Country=="US")
+  
+  # These models should all give the same results 
+  model12 <- cesModel(iGDP ~ iK + iL + iYear, data = testData, nest = c(1, 2), digits=30)
+  model21 <- cesModel(iGDP ~ iL + iK + iYear, data = testData, nest = c(2, 1), digits=30)
+  # Because both the order of the factors of production and the nest change, 
+  # the coef values from the model should be identical
+  expect_equivalent( coef(model12), coef(model21) )
+  
+  # Because the models are the same except for the order of the factors, the roles of 
+  # alpha_1 and alpha_2 are reversed.
+  expect_equivalent(naturalCoef(model12)["alpha_1", "alpha_2"], naturalCoef(model21)["alpha_2", "alpha_1"])
+  expect_equivalent(sort(naturalCoef(model12)), sort(naturalCoef(model21)))
+  
+  # In this case, we have maintained the order of the factors of production,
+  # but we have a new nest.  However, naturalCoef should associate alpha_1, alpha_2, and alpha_3
+  # with the variables in the order they appear in the production function. 
+  # Thus, we expect the following test to pass.
+  modelkl21 <- cesModel(iGDP ~ iK + iL + iYear, data = testData, nest = c(2, 1), digits=30)
+  expect_equivalent( naturalCoef(model12)[c("alpha_1", "alpha_2", "alpha_3")], 
+                     naturalCoef(modelkl21)[c("alpha_1", "alpha_2", "alpha_3")])
+})
+
+
+test_that("cesModel() fits without energy are correct", {
+  
+  # Use the US factors of production from the Calvin source
+  testData <- subset(EconData::Calvin, Country=="US")
+  
+  # Concoct some data and add it to testData
+  scale <- 1.0 # cesEst calls this "gamma"
+  lambda <- 0.02
+  delta <- 0.3
+  rho <- 0.4
+  nu <- 1.0
+  fitGDP <- cesCalc(xNames = c("iK", "iL"), data = testData, 
[…]

### 2018-07-30 tests/testthat/test-model-fits.R

@@ -1,0 +1,270 @@
+
+context('Testing Model Fits')
+
+library(dplyr, quietly = TRUE)
+library(magrittr, quietly = TRUE)
+
+test_that("cdModel() without energy fits are correct", {
+  
+  # Use the US factors of production from the Calvin source
+  testData <- subset(EconData::Calvin, Country=="US")  
+  
+  # Cobb-Douglas without energy
+  alpha <- -0.1
+  beta <- 1.1
+  gamma <- 0
+  lambda <- 0.02
+  testData <- transform(testData,
+                        fitGDPnoe = exp(lambda * iYear) * iK^alpha * iL^beta)
+  
+  # Fit without constraints
+  modelFree <- cdModel(fitGDPnoe ~ iK + iL + iYear, data = testData, constrained = FALSE, 
+                       save.data = TRUE)
+  # We should obtain scale = 1, because every data point should be fit exactly.
+  # We should obtain gamma = 0, because there is no energy.
+  expect_equivalent(naturalCoef(modelFree)[, c("scale", "alpha_1", "alpha_2", "alpha_3", "lambda"), drop=TRUE], 
+                    list(1, alpha, beta, gamma, lambda) )
+  # Switch K and L in the formula to see if the results change appropriately
+  modelFree2 <- cdModel(fitGDPnoe ~ iL + iK + iYear, data = testData, constrained = FALSE, 
+                        save.data = TRUE)
+  expect_equivalent(naturalCoef(modelFree2)[, c("scale", "alpha_1", "alpha_2", "alpha_3", "lambda"), drop=TRUE], 
+                    list(1, beta, alpha, gamma, lambda) )
+  
+  # Hit the constraint of alpha < 0, beta > 1.
+  modelConstrained <- cdModel(fitGDPnoe ~ iK + iL + iYear, data = testData, 
+                              constrained = TRUE, save.data = TRUE)
+  # scale is not expected to be exactly 1.0, because we will not exactly fit the data. 
+  # lambda is not expected to be exactly the value we used to create testData, 
+  # because we will not exactly fit the data when constrained.
+  # alpha_1 will be 0 instead of -0.1.
+  expect_equivalent(naturalCoef(modelConstrained)[, c("alpha_1", "alpha_2", "alpha_3"), drop=TRUE], 
[…]

### 2018-08-13 README.Rmd
remove lattice and latticeExtra; add README

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# MacroGrowth

The MacroGrowth package provides sophisticated tools for fitting macroeconomic 
growth models to data. MacroGrowth has several desirable features for economic modelers:

* Functions that fit several different macroeconomic growth models.
* Functions fit along 
boundaries of the economically-meaningful region, 
thereby ensuring that the best possible fit is found.
* Options to perform residual resampling, 
thereby providing a way to assess the variability of estimated parameters.
* A consistent formula-based interface to fitting functions.

The functions in this package were developed for and used first in the paper
Heun, M.K., J. Santos, P.E. Brockway, R. Pruim, T. Domingos, and M. Sakai.
"From Theory to Econometrics to Energy Policy: 
Cautionary Tales for Policymaking Using Aggregate Production Functions".
*Energies*, pp. 1-44, 10 (203), 2017.
<http://doi.org/10.3390/en10020203>.

## Installation

You can install MacroGrowth from github with:

```{r gh-installation, eval = FALSE}
# install devtools if not already installed
# install.packages("devtools")
devtools::install_github("EconModels/MacroGrowth")
# To get vignettes built locally, use
devtools::install_github("EconModels/MacroGrowth", build_vignettes = TRUE)
```

### 2018-09-12 README.Rmd
Updates to vignette.

@@
 output: github_document
+bibliography: vignettes/References.bib
 ---
@@
 
-The MacroGrowth package provides sophisticated tools for fitting macroeconomic 
-growth models to data. MacroGrowth has several desirable features for economic modelers:
+The `MacroGrowth` package provides sophisticated tools for fitting macroeconomic 
+growth models to data. 
+`MacroGrowth` has several desirable features for economic modelers:
 
@@
 
-The functions in this package were developed for and used first in the paper
-Heun, M.K., J. Santos, P.E. Brockway, R. Pruim, T. Domingos, and M. Sakai.
-"From Theory to Econometrics to Energy Policy: 
-Cautionary Tales for Policymaking Using Aggregate Production Functions".
-*Energies*, pp. 1-44, 10 (203), 2017.
-<http://doi.org/10.3390/en10020203>.
+The functions in this package were developed for and used first in 
+Heun et al. [-@Heun:2017].
 
@@
 
-You can install MacroGrowth from github with:
+You can install `MacroGrowth` from github with:
 
@@
 devtools::install_github("EconModels/MacroGrowth")
-# To get vignettes built locally, use
+# To build vignettes locally, use
 devtools::install_github("EconModels/MacroGrowth", build_vignettes = TRUE)
 ```
+
+## More Information
+
+Find more information, including vignettes and function documentation at 
+<https://econmodels.github.io/MacroGrowth/>
+
+## References

### 2018-09-25 README.Rmd
Better lead identifying this as an R package.
New docs.

@@
 
-The `MacroGrowth` package provides sophisticated tools for fitting macroeconomic 
+The `R` package `MacroGrowth` provides sophisticated tools for fitting macroeconomic 
 growth models to data. 
@@
 The functions in this package were developed for and used first in 
-Heun et al. [-@Heun:2017].
+[Heun et al. [-@Heun:2017]](https://doi.org/10.3390/en10020203).
 
